### 2021-12-02 airy-resurgence.tex
Work through Laplace transform basics

\documentclass{article}

\usepackage{ajf}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
%%\newtheorem{obs}{Observation}
\newtheorem{prop}{Proposition}

% symbology
\newcommand{\laplace}{\mathcal{L}}

\title{Resurgence of the Airy function}
\author{Aaron Fenyes}

\begin{document}
\maketitle
\section{The Laplace transform}
\subsection{Regularity and decay properties}
The Laplace transform is defined by
\[ [\mathcal{L}\hat{\varphi}](z) = \int_0^\infty e^{-z \zeta} \hat{\varphi}(\zeta)\;d\zeta. \]
Recall that $O(g)$ is the space of functions $\varphi$ on $\R_{> 0}$ with $|\varphi| \lesssim g$. Let $\mathcal{E}$ be the space of subexponential functions: the intersection of $O(e^{cz})$ over all $c \in \R_{> 0}$. Observe that $\laplace$ maps $\mathcal{E}$ into $O(z^{-1})$.\footnote{For holomorphic functions, this is stated in Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}

If $\hat{\varphi}$ is $L^1$ and subexponential, $\laplace \varphi$ is holomorphic on the right half-plane \textbf{(Mitschi \& Sauzin, \S 5.6)}.
%%Observe that $\laplace \hat{\varphi}$ is in $O(z^{-1})$ whenever $|\hat{\varphi}|$ grows polynomially along $\R_{\ge 0}$.
\subsection{Action on differential equations}
If $\hat{\varphi}$ is subexponential, we can use differentiation under the integral to show that \textbf{[Schiff, Theorem~1.34]}
\[ \laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}. \]

%%Let $\mathcal{R}$ be the space of functions on $\R_{\ge 0}$ that approach zero as you go rightward.
Since $\C[z] + O(z^{-1})$ is a direct sum, there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$. It extends uniquely to holomorphic functions defined on a neighborhood of $\R_{> 0}$. Integration by parts shows that
\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n\,\laplace \hat{\varphi} + p \]
for some $p \in \C[z]$. Hence,
\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}) \]
whenever $\big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} \in \mathcal{E}$. It's useful here to note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$. Since constant functions are subexponential, we can assume without loss of generality that $f(0) = 0$ \textbf{[watch out: $f$ may not extend continuously to $0$]}. Then \[ |f(\zeta)| = \left|\int_0^\zeta f(\tau)\,d\tau\right| \le \int_0^\zeta |f(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\]}

Explicitly, integration by parts gives the formula
\begin{align*}
\laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace \hat{\varphi} - \left( \hat{\varphi}(0)\,z^{n-1} + \hat{\varphi}'(0)\,z^{n-2} + \hat{\varphi}''(0)\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)}(0) \right) \\
& = z^n\,\laplace\left[ \hat{\varphi} - \left( \hat{\varphi}(0) + \hat{\varphi}'(0)\,\zeta + \tfrac{\hat{\varphi}''(0)}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}(0)}{(n-1)!}\,\zeta^{n-1} \right) \right].
\end{align*}

\textbf{[This argument only works for holomorphic $\hat{\varphi}$, but the formula can be proven more generally using integration by parts.]} If $\hat{\varphi}$ is in $L^1 \cap O(e^{cz})$ for some $c < 0$, then $\laplace \hat{\varphi}$ is holomorphic on the half-plane $\Re(z) > c$, so it can be written as a convergent power series around zero. Thinking about how $\Lambda$ acts on power series gives the well-known explicit formula
\begin{align*}
\laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n\,\laplace\left[ \hat{\varphi} - \left( \hat{\varphi}(0) + \hat{\varphi}'(0)\,\zeta + \tfrac{\hat{\varphi}''(0)}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}(0)}{(n-1)!}\,\zeta^{n-1} \right) \right] \\
& = z^n \laplace \hat{\varphi} - \left( \hat{\varphi}(0)\,z^{n-1} + \hat{\varphi}'(0)\,z^{n-2} + \hat{\varphi}''(0)\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)}(0) \right).
\end{align*}

%%Integration by parts shows that $\laplace \frac{\partial}{\partial \zeta} \hat{\varphi} = z\,\mathcal{L}\hat{\varphi} - \hat{\varphi}(0)$. Hence,
%%\[ \Lambda \laplace \tfrac{\partial}{\partial \zeta} \hat{\varphi} = \Lambda(z\,\mathcal{L} \hat{\varphi}) \]
%%More generally,
%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n\,\mathcal{L} \hat{\varphi} - \left(z^{n-1}\,\hat{\varphi}(0) + z^{n-2}\,\big[\tfrac{\partial}{\partial \zeta} \hat{\varphi}\big](0) + \ldots + \big[\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \hat{\varphi}\big](0)\right), \]
%%so
%%\[ \Lambda \laplace \left(\tfrac{\partial}{\partial z}\right)^n \hat{\varphi} = \Lambda(\zeta^n\,\mathcal{L} \hat{\varphi}). \]
%%\begin{obs}\label{back-poly}
%%Suppose $P$ is a differential operator with polynomial coefficients. Then $Pf$ is a polynomial if and only if $f$ is.
%%\end{obs}
\begin{prop}
Let $\varphi = \laplace \hat{\varphi}$, and let $p_1, \ldots, p_r,\;q_1, \ldots, q_r$ be polynomials. Suppose $\hat{\varphi}$ is subexponential. Then
\[ P = p_1(z)\;q_1\big({-\tfrac{\partial}{\partial z}}\big) + \ldots + p_r(z)\;q_r\big({-\tfrac{\partial}{\partial z}}\big) \]
annihilates $\varphi$ if and only if
\[ \hat{P} = p_1\big(\tfrac{\partial}{\partial \zeta}\big)\;q_1(\zeta) + \ldots + p_r\big(\tfrac{\partial}{\partial \zeta})\;q_r(\zeta) \]
annihilates $\hat{\varphi}$. \textbf{[?]}
\end{prop}
\begin{proof}
Suppose $\hat{P} \hat{\varphi} = 0$. Taking the Laplace transform of both sides and using the identities above, we see that $\Lambda P \varphi = 0$. In other words, $P \varphi$ is a polynomial. \textbf{[\ldots?]}
\end{proof}
\end{document}

### 2021-12-03 airy-resurgence.tex
Clean up Laplace transform; start Airy equation
The Airy equation stuff was mostly copied out from my notes during
a call with Veronica. We worked out the correspondence with Mariño's
series during the call.

@@
 \theoremstyle{plain}
-%%\newtheorem{obs}{Observation}
 \newtheorem{prop}{Proposition}
@@
 % symbology
+\newcommand{\posreal}{\R_{> 0}}
 \newcommand{\laplace}{\mathcal{L}}
+\DeclareMathOperator{\Ai}{Ai}
 
@@
 \[ [\mathcal{L}\hat{\varphi}](z) = \int_0^\infty e^{-z \zeta} \hat{\varphi}(\zeta)\;d\zeta. \]
-Recall that $O(g)$ is the space of functions $\varphi$ on $\R_{> 0}$ with $|\varphi| \lesssim g$.
-Let $\mathcal{E}$ be the space of subexponential functions: the intersection of $O(e^{cz})$ over all $c \in \R_{> 0}$.
-Observe that $\laplace$ maps $\mathcal{E}$ into $O(z^{-1})$.\footnote{For holomorphic functions, this is stated in Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}
-
-If $\hat{\varphi}$ is $L^1$ and subexponential, $\laplace \varphi$ is holomorphic on the right half-plane \textbf{(Mitschi \& Sauzin, \S 5.6)}.
-%%Observe that $\laplace \hat{\varphi}$ is in $O(z^{-1})$ whenever $|\hat{\varphi}|$ grows polynomially along $\R_{\ge 0}$.
-\subsection{Action on differential equations}
-If $\hat{\varphi}$ is subexponential, we can use differentiation under the integral to show that \textbf{[Schiff, Theorem~1.34]}
+Recall that $O(g)$ is the space of functions $\varphi$ on $\posreal$ with $|\varphi| \lesssim g$.
+A function is {\em subexponential} if it's in $O(e^{cz})$ for all $c \in \posreal$.
+Let $\mathcal{E}$ be the space of subexponential functions on $\posreal$ which are $L^1$ both locally and around zero.
+Observe that $\laplace$ maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane \textbf{(Mitschi \& Sauzin, \S 5.6)} which restrict to $O(z^{-1})$ on $\posreal$ \textbf{(Schiff, equation~1.8---the argument still works in our generality)}.\footnote{For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}
+\subsection{Action on initial value problems}
+When $\hat{\varphi} \in \mathcal{E}$, we can use differentiation under the integral to show that \textbf{[Schiff, Theorem~1.34]}
 \[ \laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}. \]
 
-%%Let $\mathcal{R}$ be the space of functions on $\R_{\ge 0}$ that approach zero as you go rightward.
-Since $\C[z] + O(z^{-1})$ is a direct sum, there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
-It extends uniquely to holomorphic functions defined on a neighborhood of $\R_{> 0}$.
-Integration by parts shows that
-\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n\,\laplace \hat{\varphi} + p \]
-for some $p \in \C[z]$. Hence,
-\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}) \]
-whenever $\big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} \in \mathcal{E}$.
-It's useful here to note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$.
-Since constant functions are subexponential, we can assume without loss of generality that $f(0) = 0$ \textbf{[watch out: $f$ may not extend continuously to $0$]}.
-Then \[ |f(\zeta)| = \left|\int_0^\zeta f(\tau)\,d\tau\right| \le \int_0^\zeta |f(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\]}
-
-Explicitly, integration by parts gives the formula
+When $\hat{\varphi} \in C^n$ and $\big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} \in \mathcal{E}$, integration by parts gives the formula
 \begin{align*}
@@
 \end{align*}
+Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$.
+Since constant functions are subexponential, we can assume without loss of generality that $f(0) = 0$ \textbf{[watch out: $f$ may not extend continuously to $0$]}.
+Then \[ |f(\zeta)| = \left|\int_0^\zeta f(\tau)\,d\tau\right| \le \int_0^\zeta |f(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\]}
 
-\textbf{[This argument only works for holomorphic $\hat{\varphi}$, but the formula can be proven more generally using integration by parts.]} If $\hat{\varphi}$ is in $L^1 \cap O(e^{cz})$ for some $c < 0$, then $\laplace \hat{\varphi}$ is holomorphic on the half-plane $\Re(z) > c$, so it can be written as a convergent power series around zero.
-Thinking about how $\Lambda$ acts on power series gives the well-known explicit formula
+In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
+Applying $\Lambda$ to both sides of the formula above reveals that
+\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
+
+Say $A$ is an $n$th-order differential operator with polynomial coefficients.
+If we know that $A\hat{\varphi} = 0$, and we know the Taylor polynomial of $\hat{\varphi}$ at zero through degree $n - 1$, we can use the formulas above to find an inhomogeneous differential equation that $\laplace \hat{\varphi}$ must satisfy.
+\section{The Airy equation}
+\subsection{Basics}
+The Airy equation is
+\[ \left[\big(\tfrac{\partial}{\partial x}\big)^2 - x\right] \varphi = 0. \]
+One solution is given by the Airy function,
+\[ \Ai(x) = \frac{1}{2\pi i} \int_{\Gamma_0} \exp\left(\tfrac{1}{3}t^3 - xt\right)\,dt, \]
+where $\Gamma_0$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$. With the substitution $t = 2ux^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(x) = x^{1/2}\;\frac{1}{\pi i} \int_{x^{-1/2} \Gamma_0} \exp\left[\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+\subsection{Rewriting as a modified Bessel equation}
+We can distill the most interesting part of this expression by writing
+\[ \Ai(x) = \tfrac{1}{\pi\sqrt{3}}\,x^{1/2}\, K\big(\tfrac{2}{3} x^{3/2}\big), \]
+where
+\[ K(z) = \frac{\sqrt{3}}{i} \int_{z^{-1/3}\Gamma_0} \exp\left[z \left(4u^3 - 3u\right)\right]\,du. \]
+Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
+\[ \left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \big(\tfrac{\partial}{\partial z}\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K(z) = 0. \]
+
+Since our rewritten Airy integral only depends on the variable $z = \tfrac{2}{3} x^{3/2}$,
+
+we can \textbf{[...]}
+
+In terms of
+
+we have
+\[ \Ai(x) = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \]
+[DLMF~9.6.1].
+\subsection{Taking the Laplace transform}
+Tentatively (there's some details with initial values to work out),
+\[ \big(\zeta^2 - 1\big) \hat{K}'' + 3\zeta \hat{K}' + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\hat{K} = 0. \]
+With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, this becomes \textbf{[...]}
+
+The hypergeometric function
+\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
+satisfies the same equation as $\hat{K}$ by definition. Using DLMF~15.10.13, we can see that
+\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
+\textbf{Our desired solution has the 0th- and 1st-degree Taylor coefficients in a particular ratio. It should be given by a constant multiple of}
+\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) - F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
+The quadratic transformation identity DLMF~15.8.27 then shows that
+\[ \hat{K} \propto F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big). \]
+
+Using the DLMF identities 15.10.11 and 15.10.14, we can see that the functions
 \begin{align*}
-\laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n\,\laplace\left[ \hat{\varphi} - \left( \hat{\varphi}(0) + \hat{\varphi}'(0)\,\zeta + \tfrac{\hat{\varphi}''(0)}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}(0)}{(n-1)!}\,\zeta^{n-1} \right) \right] \\
-& = z^n \laplace \hat{\varphi} - \left( \hat{\varphi}(0)\,z^{n-1} + \hat{\varphi}'(0)\,z^{n-2} + \hat{\varphi}''(0)\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)}(0) \right).
+& (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) \\
+& (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big)
 \end{align*}
+also satisfy the same hypergeometric equation as $\hat{K}$.
+\subsection{Correspondence with Mari\~{n}o's series}
+Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.
 
-%%Integration by parts shows that $\laplace \frac{\partial}{\partial \zeta} \hat{\varphi} = z\,\mathcal{L}\hat{\varphi} - \hat{\varphi}(0)$. Hence,
-%%\[ \Lambda \laplace \tfrac{\partial}{\partial \zeta} \hat{\varphi} = \Lambda(z\,\mathcal{L} \hat{\varphi}) \]
-%%More generally,
-%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n\,\mathcal{L} \hat{\varphi} - \left(z^{n-1}\,\hat{\varphi}(0) + z^{n-2}\,\big[\tfrac{\partial}{\partial \zeta} \hat{\varphi}\big](0) + \ldots + \big[\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \hat{\varphi}\big](0)\right), \]
-%%so
-%%\[ \Lambda \laplace \left(\tfrac{\partial}{\partial z}\right)^n \hat{\varphi} = \Lambda(\zeta^n\,\mathcal{L} \hat{\varphi}). \]
-%%\begin{obs}\label{back-poly}
-%%Suppose $P$ is a differential operator with polynomial coefficients. Then $Pf$ is a polynomial if and only if $f$ is.
-%%\end{obs}
-\begin{prop}
-Let $\varphi = \laplace \hat{\varphi}$, and let $p_1, \ldots, p_r,\;q_1, \ldots, q_r$ be polynomials. Suppose $\hat{\varphi}$ is subexponential. Then
-\[ P = p_1(z)\;q_1\big({-\tfrac{\partial}{\partial z}}\big) + \ldots + p_r(z)\;q_r\big({-\tfrac{\partial}{\partial z}}\big) \]
-annihilates $\varphi$ if and only if
-\[ \hat{P} = p_1\big(\tfrac{\partial}{\partial \zeta}\big)\;q_1(\zeta) + \ldots + p_r\big(\tfrac{\partial}{\partial \zeta})\;q_r(\zeta) \]
-annihilates $\hat{\varphi}$. \textbf{[?]}
-\end{prop}
-\begin{proof}
-Suppose $\hat{P} \hat{\varphi} = 0$.
-Taking the Laplace transform of both sides and using the identities above, we see that $\Lambda P \varphi = 0$.
-In other words, $P \varphi$ is a polynomial.
-\textbf{[\ldots?]}
-\end{proof}
+\begin{align*}
+\Ai(x) & = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} \varphi_1\big(\tfrac{2}{3} z^{-1}\big) \\
+& = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) \\
+\Ai(x) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2})
+\end{align*}
+Putting together,
+\begin{align*}
+\tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;x^{-3/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;\big(\tfrac{3}{2} z)^{-1/2} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} f_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = \hat{K}(\zeta) \\
+\sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} \hat{f}_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = \hat{K}(\zeta) \\
+-\tfrac{1}{3\sqrt{2}}\;\left[\zeta^{-1/2}\right] * \hat{f}_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = \hat{K}(\zeta) \\
+\end{align*}
 \end{document}

### 2021-12-03 airy-resurgence.tex
Formalize citations; clean up labels

@@
 \usepackage{ajf}
+\usepackage{url}
 \usepackage{amsthm}
@@
 Let $\mathcal{E}$ be the space of subexponential functions on $\posreal$ which are $L^1$ both locally and around zero.
-Observe that $\laplace$ maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane \textbf{(Mitschi \& Sauzin, \S 5.6)} which restrict to $O(z^{-1})$ on $\posreal$ \textbf{(Schiff, equation~1.8---the argument still works in our generality)}.\footnote{For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}
+Observe that $\laplace$ maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane~\cite[\S 5.6]{diverg-resurg-i} which restrict to $O(z^{-1})$ on $\posreal$ \cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
+For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}
 \subsection{Action on initial value problems}
-When $\hat{\varphi} \in \mathcal{E}$, we can use differentiation under the integral to show that \textbf{[Schiff, Theorem~1.34]}
+When $\hat{\varphi} \in \mathcal{E}$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}. \]
@@
 Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$.
-Since constant functions are subexponential, we can assume without loss of generality that $f(0) = 0$ \textbf{[watch out: $f$ may not extend continuously to $0$]}.
-Then \[ |f(\zeta)| = \left|\int_0^\zeta f(\tau)\,d\tau\right| \le \int_0^\zeta |f(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\]}
+Then \[ \left|\int_0^\zeta f'(\tau)\,d\tau\right| \le \int_0^\zeta |f'(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f(\zeta) - f(0)| \lesssim e^{c\zeta}$.}
 
@@
 The Airy equation is
-\[ \left[\big(\tfrac{\partial}{\partial x}\big)^2 - x\right] \varphi = 0. \]
+\begin{equation}\label{eqn:airy}
+\left[\big(\tfrac{\partial}{\partial x}\big)^2 - x\right] \psi = 0.
+\end{equation}
 One solution is given by the Airy function,
@@
 \subsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of this expression by writing
+We can distill the most interesting part of the Airy function by writing
 \[ \Ai(x) = \tfrac{1}{\pi\sqrt{3}}\,x^{1/2}\, K\big(\tfrac{2}{3} x^{3/2}\big), \]
@@
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\[ \left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \big(\tfrac{\partial}{\partial z}\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K(z) = 0. \]
-
-Since our rewritten Airy integral only depends on the variable $z = \tfrac{2}{3} x^{3/2}$,
-
-we can \textbf{[...]}
-
-In terms of
-
-we have
-\[ \Ai(x) = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \]
-[DLMF~9.6.1].
+\begin{equation}\label{eqn:modbessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \big(\tfrac{\partial}{\partial z}\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
 \subsection{Taking the Laplace transform}
@@
 \end{align*}
+
+\bibliographystyle{utphys}
+\bibliography{airy-resurgence}
 \end{document}

### 2021-12-08 airy-resurgence.tex
Correct Laplace transform asymptotics; add hypergeometric equation

@@
 \[ [\mathcal{L}\hat{\varphi}](z) = \int_0^\infty e^{-z \zeta} \hat{\varphi}(\zeta)\;d\zeta. \]
-Recall that $O(g)$ is the space of functions $\varphi$ on $\posreal$ with $|\varphi| \lesssim g$.
-A function is {\em subexponential} if it's in $O(e^{cz})$ for all $c \in \posreal$.
+For $a \in [0, \infty]$, recall that recall that $O_a(g)$ is the space of functions $\varphi$ on $\posreal$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
+A function is {\em subexponential} if it's in $O_\infty(e^{cz})$ for all $c \in \posreal$.
 Let $\mathcal{E}$ be the space of subexponential functions on $\posreal$ which are $L^1$ both locally and around zero.
-Observe that $\laplace$ maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane~\cite[\S 5.6]{diverg-resurg-i} which restrict to $O(z^{-1})$ on $\posreal$ \cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
-For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.}
+The Laplace transform maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane~\cite[\S 5.6]{diverg-resurg-i}.
+If a function is in $O_0(1)$, its Laplace transform is in $O_\infty(z^{-1})$ \cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
+For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if a function is in $O_0(\zeta^\alpha)$, with $\alpha > -1$, its Laplace transform is in $O_\infty(z^{-(\alpha + 1)})$.
 \subsection{Action on initial value problems}
@@
 
-When $\hat{\varphi} \in C^n$ and $\big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} \in \mathcal{E}$, integration by parts gives the formula
+When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
 \begin{align*}
@@
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:modbessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \big(\tfrac{\partial}{\partial z}\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\begin{equation}\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
 \end{equation}
 In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-\subsection{Taking the Laplace transform}
-Tentatively (there's some details with initial values to work out),
-\[ \big(\zeta^2 - 1\big) \hat{K}'' + 3\zeta \hat{K}' + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\hat{K} = 0. \]
-With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, this becomes \textbf{[...]}
+\subsection{Going to the spatial domain}
+Let's find a function $\hat{K}$ with $K = \laplace \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
+\begin{equation}\label{eqn:spatial-mod-bessel}
+\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0,
+\end{equation}
+its Laplace transform $\varphi = \laplace \hat{\varphi}$ satisfies the equation
+\begin{align*}
+\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] + 3\big({-\tfrac{\partial}{\partial z}}\big)\Big[z\varphi - \hat{\varphi}(0)\Big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
+\end{align*}
+which simplifies to
+\begin{equation}\label{eqn:inhomog-mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big).
+\end{equation}
+Noticing that equation~\ref{eqn:inhomog-mod-bessel} is an inhomogeneous version of equation~\ref{eqn:mod-bessel}, we
+
+This suggests that $\hat{K}$ could be a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first degree at $\zeta = 0$.
+
+With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
+\begin{equation}\label{eqn:hypergeom}
+\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+\end{equation}
+\textbf{[...]}
 
@@
 \[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
-satisfies the same equation as $\hat{K}$ by definition. Using DLMF~15.10.13, we can see that
+satisfies equation~\ref{eqn:hypergeom} by definition. It has a singularity of type $\xi^{-1/2}$ at $\xi = 0$, and continues holomorphically to the rest of $\C$. Using DLMF~15.10.13, we can see that
 \[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
-\textbf{Our desired solution has the 0th- and 1st-degree Taylor coefficients in a particular ratio. It should be given by a constant multiple of}
+also satisies equation~\ref{eqn:hypergeom}. It has a singularity of type $(1 - \xi)^{-1/2}$ at $\xi = 1$, and continues holomorphically to the rest of $\C$.
+
+\textbf{[\ldots]} Our desired solution should be given by a constant multiple of
 \[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) - F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
@@
 
-Using the DLMF identities 15.10.11 and 15.10.14, we can see that the functions
+Using the DLMF identities 15.10.12 and 15.10.14, we can see that the functions
 \begin{align*}
-& (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) \\
-& (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big)
+\xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) \\
+(1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big)
 \end{align*}
-also satisfy the same hypergeometric equation as $\hat{K}$.
+also satisfy equation~\ref{eqn:hypergeom}. Numerically, these functions appear to sum to a constant multiple of $\hat{K}$.
 \subsection{Correspondence with Mari\~{n}o's series}

### 2021-12-09 airy-resurgence.tex
Introduce algebraic Laplace transform

@@
 \usepackage{url}
+\usepackage[hmargin=1.5in]{geometry}
 \usepackage{amsthm}
@@
 \section{The Laplace transform}
-\subsection{Regularity and decay properties}
+\subsection{Analytic version}
+\subsubsection{Regularity and decay properties}
 The Laplace transform is defined by
@@
 For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if a function is in $O_0(\zeta^\alpha)$, with $\alpha > -1$, its Laplace transform is in $O_\infty(z^{-(\alpha + 1)})$.
-\subsection{Action on initial value problems}
+\subsubsection{Action on differential operators}\label{L-diff-op}
 When $\hat{\varphi} \in \mathcal{E}$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\[ \laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}. \]
+\begin{equation}\label{id:L-mult}
+\laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}.
+\end{equation}
 
 When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
-\begin{align*}
+\begin{align}\label{id:L-diff}
 \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace \hat{\varphi} - \left( \hat{\varphi}(0)\,z^{n-1} + \hat{\varphi}'(0)\,z^{n-2} + \hat{\varphi}''(0)\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)}(0) \right) \\
 & = z^n\,\laplace\left[ \hat{\varphi} - \left( \hat{\varphi}(0) + \hat{\varphi}'(0)\,\zeta + \tfrac{\hat{\varphi}''(0)}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}(0)}{(n-1)!}\,\zeta^{n-1} \right) \right].
-\end{align*}
+\nonumber
+\end{align}
 Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$.
@@
 
-In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
+%%In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
 Applying $\Lambda$ to both sides of the formula above reveals that
-\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
+%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
 
-Say $A$ is an $n$th-order differential operator with polynomial coefficients.
+%%Say $A$ is an $n$th-order differential operator with polynomial coefficients.
 If we know that $A\hat{\varphi} = 0$, and we know the Taylor polynomial of $\hat{\varphi}$ at zero through degree $n - 1$, we can use the formulas above to find an inhomogeneous differential equation that $\laplace \hat{\varphi}$ must satisfy.
+\subsection{Algebraic version}
+\subsubsection{Definition}
+Let $\mathcal{P}$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
+Note that $\mathcal{P} \cap \mathcal{E}$ is $\mathcal{P}_{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
+Since $\laplace(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)}$ for all $\alpha > -1$, let's use the same formula to extend $\laplace$ to all of $\mathcal{P}$.
+This defines $\laplace$ consistently on $\mathcal{E} + \mathcal{P}$.
+\subsubsection{Action on differential operators}
+Observe that
+\[ \laplace(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace(\zeta^\alpha) \]
+for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}$.
+
+Observe that
+\[ \laplace\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
+z\,\laplace(\zeta^\alpha) & \alpha \neq 0 \\
+0 & \alpha = 0,
+\end{cases} \]
+and that $0 = z\,\laplace(1) - 1$.
+This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}$ whose $n$th derivative is in $\mathcal{P}_{> -1}$.
+Although the functions in $\mathcal{P}_{< 0}$ are singular at zero, let's pretend they vanish at zero.
+With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}$.
+
+Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E} + \mathcal{P}$.
+Identity~\ref{id:L-diff} is particularly simple for functions that can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}$ vanish at zero.
+For these functions, all the initial values vanish, and we have
+\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}) = z^n \laplace (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}). \]
 \section{The Airy equation}

### 2021-12-11 airy-resurgence.tex
Sketch complete contour argument

@@
 
-This suggests that $\hat{K}$ could be a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first degree at $\zeta = 0$.
+%%This suggests that $\hat{K}$ could be a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first degree at $\zeta = 0$.
 
@@
 
-\textbf{[\ldots]} Our desired solution should be given by a constant multiple of
-\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) - F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
+Based on the calculations in the other sheet, we should have
+\[ K(z) = i \frac{2}{\sqrt{3}} \int_{\text{Hankel at } 1} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+This is because the hypergeometric function in the integrand happens to be algebraic. It can be expressed in terms of Legendre functions and rearranged to get
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \frac{1}{4u^2 - 1} \]
+with $\zeta = -4u^3 + 3u$.
+
 The quadratic transformation identity DLMF~15.8.27 then shows that
-\[ \hat{K} \propto F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big). \]
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) \propto F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big), \]
+so we have
+\[ K(z) \propto \int_{\text{Hankel at } 1} e^{-z\zeta} \big[F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\big]\;d\zeta. \]
+The first term in the integrand is regular on $\zeta \in [1, \infty)$, so it integrates to zero.
+The second term looks like $(1 - \zeta)^{-1/2}$ times a function which is regular for $\zeta \in [1, \infty)$, so integrating it along a Hankel contour is the same as integrating it times two times a direct contour, with its value continued from below the singularity.
+Hence,
+\[ K(z) \propto \int^\infty_1 e^{-z\zeta} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\;d\zeta. \]
+With $\zeta = 1 + \tilde{\zeta}$, we get $1 - \xi = 1 + \tfrac{1}{2} \tilde{\zeta}$, so
+\begin{align*}
+K(z) & = \int^\infty_0 e^{-z(1 + \tilde{\zeta})} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta} \\
+e^z K(z) & = \int^\infty_0 e^{-z\tilde{\zeta}} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta}
+\end{align*}
+In other words, $\kappa(z) = e^z K(z)$ is the Laplace transform of $\hat{\kappa}(\tilde{\zeta}) = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)$.
+We've confirmed numerically that $\hat{\kappa}(\tilde{\zeta})$ seems to have a singularity of type $\tilde{\zeta}^{-1/2}$ at $\tilde{\zeta} = 0$, as expected.
+\textbf{Can we see this analytically?}
 
@@
 \end{align*}
-also satisfy equation~\ref{eqn:hypergeom}. Numerically, these functions appear to sum to a constant multiple of $\hat{K}$.
+also satisfy equation~\ref{eqn:hypergeom}. Numerically, these functions appear to sum to a constant multiple of $F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)$.
 \subsection{Correspondence with Mari\~{n}o's series}
@@
 \end{align*}
-
+Notice that if the hypergeometric differentiation formula holds for fractional derivatives,
+\[ \big(\tfrac{\partial}{\partial \xi}\big)^{1/2}F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \propto F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big) \]
 \bibliographystyle{utphys}

### 2021-12-14 airy-resurgence.tex
Transform equation using translation and scaling operators

@@
 This defines $\laplace$ consistently on $\mathcal{E} + \mathcal{P}$.
-\subsubsection{Action on differential operators}
+\subsubsection{Action on differential operators}\label{L-diff-op-alg}
 Observe that
@@
 \[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}) = z^n \laplace (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}). \]
+\subsection{Interactions with other operators}
+\subsubsection{Translation}
+Let $T_a$ be the left translation operator $[T_a f](\zeta) = f(\zeta + a)$. The Laplace transform commutes between $T_a$ and multiplication by $e^{az}$:
+\[ \laplace T_a \hat{\varphi} = e^{az} \laplace \hat{\varphi}. \]
+Consistent with Section~\ref{L-diff-op}, we have
+\begin{align*}
+(\zeta + a) T_a \hat{\varphi} & = T_a(\zeta \hat{\varphi}) \\
+\big(\tfrac{\partial}{\partial z} - a\big) e^{az} \varphi & = e^{az} \tfrac{\partial}{\partial z} \varphi
+\end{align*}
+and
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} T_a & = T_a \tfrac{\partial}{\partial \zeta} \\
+z e^{az} \varphi & = e^{az} z \varphi.
+\end{align*}
+\subsubsection{Scaling}
+Let $S^k_c$ be the homogeneous scaling operator $[S^k_c f](\zeta) = c^k f(c \zeta)$. The Laplace transform commutes between $S^1_c$ and $S^0_{c^{-1}}$:
+\[ \laplace S^1_c \hat{\varphi} = S^0_{c^{-1}} \laplace \hat{\varphi}. \]
+Consistent with Section~\ref{L-diff-op}, we have
+\begin{align*}
+c\zeta S^k_c \hat{\varphi} & = S^k_c(\zeta \hat{\varphi}) \\
+c \tfrac{\partial}{\partial z} S^k_{c^{-1}} \varphi & = S^k_{c^{-1}} \tfrac{\partial}{\partial z} \varphi.
+\end{align*}
 \section{The Airy equation}
@@
 In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
+
+As we'll see in Section~\ref{asymp}, $K$ is in $O_\infty(e^{-z})$.
+It'll be helpful to pull out the exponential decay factor and work instead with the function $\kappa$ defined by $K(z) = e^{-z} \kappa(z)$.
+Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $\kappa$ satisfies the equation
+\begin{equation}\label{eqn:shifted-mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z} + 1\big)^2 + z \big(\tfrac{\partial}{\partial z} + 1\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+%%\subsection{Asymptotic analysis}\label{asymp}
 \subsection{Going to the spatial domain}
-Let's find a function $\hat{K}$ with $K = \laplace \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
+\subsubsection{First try}
+Let's try to find a function $\hat{K}$ with $K = \laplace \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
 \begin{equation}\label{eqn:spatial-mod-bessel}
@@
 \end{equation}
-Noticing that equation~\ref{eqn:inhomog-mod-bessel} is an inhomogeneous version of equation~\ref{eqn:mod-bessel}, we
+Since we want $\laplace \hat{K}$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at zero.
+Unfortunately, this would force $\hat{K}$ to be zero.
+\subsubsection{Success}
+Let's instead try to find a function $\hat{\kappa}$ with $\laplace \hat{\kappa} = \kappa$, or equivalently $\hat{\kappa} = T_1 \hat{K}$.
+Applying $T_1$ to both sides of equation~\ref{eqn:spatial-mod-bessel}, we get the equivalent equation
+\begin{equation}\label{eqn:shifted-spatial-mod-bessel}
+\left[\zeta(\zeta + 2) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3(\zeta + 1) \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] T_1 \hat{\varphi} = 0.
+\end{equation}
+If $T_1 \hat{\varphi}$ satisfies equation~\ref{eqn:shifted-spatial-mod-bessel}, $e^z \laplace \hat{\varphi}$ will satisfy an inhomogeneous version of equation~\ref{eqn:shifted-mod-bessel}, analogous to equation~\ref{eqn:inhomog-mod-bessel}.
+This time, though, there's a trick we can use to zero out the inhomogeneity.
+Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at zero, with one solution line generated by a holomorphic multiple of $\zeta^{-1/2}$.
+The solutions on that line can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$ as described Section~\ref{L-diff-op-alg}, so their Laplace transforms satisfy equation~\ref{eqn:shifted-mod-bessel}.
 
-%%This suggests that $\hat{K}$ could be a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first degree at $\zeta = 0$.
-
-With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
+Following this plan, let's find $\hat{\kappa}$ explicitly. Applying $S^1_{-2}$ to both sides of equation~\ref{eqn:shifted-spatial-mod-bessel}, we get the equivalent equation
+\begin{align*}
+\left[(-2\zeta)(-2\zeta + 2) \big({-\tfrac{1}{2}} \tfrac{\partial}{\partial \zeta}\big)^2 + 3(-2\zeta + 1) \big({-\tfrac{1}{2}}\tfrac{\partial}{\partial \zeta}\big) + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] S^1_{-2} T_1 \hat{\varphi} & = 0 \\
+\left[\zeta(\zeta - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3(\zeta - \tfrac{1}{2}) \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] S^1_{-2} T_1 \hat{\varphi} & = 0,
+\end{align*}
+which simplifies to the hypergeometric equation
 \begin{equation}\label{eqn:hypergeom}
-\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+\left[\zeta(1 - \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3(\tfrac{1}{2} - \zeta) \tfrac{\partial}{\partial \zeta} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] S^1_{-2} T_1 \hat{\varphi} = 0.
 \end{equation}
-\textbf{[...]}
-
+%With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
+%%\begin{equation}\label{eqn:hypergeom}
+%%\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+%%\end{equation}
 The hypergeometric function

### 2021-12-14 airy-resurgence.tex
Find K-hat, with a small mistake
The misstep is described in bold, and should be easy to fix.

--- 2021-12-11 airy-resurgence.tex
@@
 \subsection{Analytic version}
-\subsubsection{Regularity and decay properties}
-The Laplace transform is defined by
-\[ [\mathcal{L}\hat{\varphi}](z) = \int_0^\infty e^{-z \zeta} \hat{\varphi}(\zeta)\;d\zeta. \]
-For $a \in [0, \infty]$, recall that recall that $O_a(g)$ is the space of functions $\varphi$ on $\posreal$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
-A function is {\em subexponential} if it's in $O_\infty(e^{cz})$ for all $c \in \posreal$.
-Let $\mathcal{E}$ be the space of subexponential functions on $\posreal$ which are $L^1$ both locally and around zero.
-The Laplace transform maps $\mathcal{E}$ into the space of holomorphic functions on the right half-plane~\cite[\S 5.6]{diverg-resurg-i}.
-If a function is in $O_0(1)$, its Laplace transform is in $O_\infty(z^{-1})$ \cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
-For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if a function is in $O_0(\zeta^\alpha)$, with $\alpha > -1$, its Laplace transform is in $O_\infty(z^{-(\alpha + 1)})$.
+\subsubsection{Regularity and decay properties}\label{reg-decay}
+Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively.
+The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
+\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
+For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
+A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$.
+Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$.
+If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\hat{\C}_{\Re(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
+If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
+For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
 \subsubsection{Action on differential operators}\label{L-diff-op}
-When $\hat{\varphi} \in \mathcal{E}$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}\label{id:L-mult}
-\laplace (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace \hat{\varphi}.
+\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
 \end{equation}
@@
 \begin{align}\label{id:L-diff}
-\laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace \hat{\varphi} - \left( \hat{\varphi}(0)\,z^{n-1} + \hat{\varphi}'(0)\,z^{n-2} + \hat{\varphi}''(0)\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)}(0) \right) \\
-& = z^n\,\laplace\left[ \hat{\varphi} - \left( \hat{\varphi}(0) + \hat{\varphi}'(0)\,\zeta + \tfrac{\hat{\varphi}''(0)}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}(0)}{(n-1)!}\,\zeta^{n-1} \right) \right].
+\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace_\zeta \hat{\varphi} - \left[ \hat{\varphi}\,z^{n-1} + \hat{\varphi}'\,z^{n-2} + \hat{\varphi}''\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)} \right]_{\zeta = 0} \\
+& = z^n\,\laplace\left( \hat{\varphi} - \left[ \hat{\varphi} + \hat{\varphi}'\,\zeta + \tfrac{\hat{\varphi}''}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right).
 \nonumber
 \end{align}
-Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O(e^{c\zeta})$.
-Then \[ \left|\int_0^\zeta f'(\tau)\,d\tau\right| \le \int_0^\zeta |f'(\tau)|\,d\tau \lesssim \int_0^\zeta e^{c\tau}\,d\tau = \tfrac{1}{c}(e^{c\zeta} - 1) \lesssim e^{c\zeta}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f(\zeta) - f(0)| \lesssim e^{c\zeta}$.}
+Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O_{\zeta \to \infty}(e^{c\zeta})$.
+Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
 
@@
 \subsubsection{Definition}
-Let $\mathcal{P}$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
-Note that $\mathcal{P} \cap \mathcal{E}$ is $\mathcal{P}_{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
-Since $\laplace(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)}$ for all $\alpha > -1$, let's use the same formula to extend $\laplace$ to all of $\mathcal{P}$.
-This defines $\laplace$ consistently on $\mathcal{E} + \mathcal{P}$.
-\subsubsection{Action on differential operators}
+Let $\mathcal{P}_\zeta$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
+Note that $\mathcal{P}_\zeta \cap \mathcal{E}_\zeta$ is $\mathcal{P}_\zeta^{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
+Since
+\[ \laplace_\zeta(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)} \]
+for all $\alpha > -1$, let's use the same formula to extend $\laplace_\zeta$ to all of $\mathcal{P}_\zeta$. This defines $\laplace_\zeta$ consistently on $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
+\subsubsection{Action on differential operators}\label{L-diff-op-alg}
 Observe that
-\[ \laplace(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace(\zeta^\alpha) \]
-for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}$.
+\[ \laplace_\zeta(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace_\zeta(\zeta^\alpha) \]
+for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}_\zeta$.
 
 Observe that
-\[ \laplace\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
-z\,\laplace(\zeta^\alpha) & \alpha \neq 0 \\
+\[ \laplace_\zeta\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
+z\,\laplace_\zeta(\zeta^\alpha) & \alpha \neq 0 \\
 0 & \alpha = 0,
 \end{cases} \]
-and that $0 = z\,\laplace(1) - 1$.
-This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}$ whose $n$th derivative is in $\mathcal{P}_{> -1}$.
-Although the functions in $\mathcal{P}_{< 0}$ are singular at zero, let's pretend they vanish at zero.
-With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}$.
+and that $0 = z\,\laplace_\zeta(1) - 1$.
+This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}_\zeta$ whose $n$th derivative is in $\mathcal{P}_\zeta^{> -1}$.
+Although the functions in $\mathcal{P}_\zeta^{< 0}$ are singular at zero, let's pretend they vanish at zero.
+With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}_\zeta$.
 
-Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E} + \mathcal{P}$.
-Identity~\ref{id:L-diff} is particularly simple for functions that can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}$ vanish at zero.
-For these functions, all the initial values vanish, and we have
-\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}) = z^n \laplace (\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}). \]
+Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
+Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$.
+By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
+Under this condition, all the initial value terms in the identity vanish, leaving
+\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
+\subsection{Change of coordinates}
+Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation
+\begin{align*}
+\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
+& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
+& = e^{-az} \laplace_{\zeta_a} \hat{\varphi},
+\end{align*}
+we learn that
+\[ \laplace_{\zeta_a} \hat{\varphi} = e^{az} \laplace_\zeta \hat{\varphi}. \]
+
+Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
+\begin{align*}
+\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
+& = b \laplace_\xi \hat{\varphi},
+\end{align*}
+we learn that
+\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
 \section{The Airy equation}
@@
 \begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial x}\big)^2 - x\right] \psi = 0.
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
 \end{equation}
 One solution is given by the Airy function,
-\[ \Ai(x) = \frac{1}{2\pi i} \int_{\Gamma_0} \exp\left(\tfrac{1}{3}t^3 - xt\right)\,dt, \]
-where $\Gamma_0$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$. With the substitution $t = 2ux^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(x) = x^{1/2}\;\frac{1}{\pi i} \int_{x^{-1/2} \Gamma_0} \exp\left[\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma_0} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
+where $\Gamma_0$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$. With the substitution $t = -2uy^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{-y^{-1/2} \Gamma_0} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
@@
 We can distill the most interesting part of the Airy function by writing
-\[ \Ai(x) = \tfrac{1}{\pi\sqrt{3}}\,x^{1/2}\, K\big(\tfrac{2}{3} x^{3/2}\big), \]
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\, K\big(\tfrac{2}{3} y^{3/2}\big), \]
 where
-\[ K(z) = \frac{\sqrt{3}}{i} \int_{z^{-1/3}\Gamma_0} \exp\left[z \left(4u^3 - 3u\right)\right]\,du. \]
+\[ K(z) = \frac{\sqrt{3}}{i} \int_{-z^{-1/3}\Gamma_0} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du. \]
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
@@
 In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
+
+As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$.
+It'll be helpful to pull out the exponential decay factor and work instead with the function $\kappa$ defined by $K = e^{-z} \kappa$.
+Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $\kappa$ satisfies the equation
+\begin{equation}\label{eqn:shifted-mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z} + 1\big)^2 + z \big(\tfrac{\partial}{\partial z} + 1\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+\subsection{Asymptotic analysis}
+From \cite{dlmf}, equations 10.40.2 and 10.17.1, we get the asymptotic series
+\begin{equation}\label{bessel-asymp}
+\kappa \sim \left(\tfrac{\pi}{2}\right)^{1/2} \left[ z^{-1/2} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-3/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-5/2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-7/2} + \ldots \right]
+\end{equation}
 \subsection{Going to the spatial domain}
-Let's find a function $\hat{K}$ with $K = \laplace \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
+\subsubsection{A good try at $\zeta = 0$}
+Let's try to find a function $\hat{K}$ with $K = \laplace_\zeta \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
 \begin{equation}\label{eqn:spatial-mod-bessel}
@@
 \end{equation}
-its Laplace transform $\varphi = \laplace \hat{\varphi}$ satisfies the equation
+its Laplace transform $\varphi = \laplace_\zeta \hat{\varphi}$ satisfies the equation
 \begin{align*}
-\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] + 3\big({-\tfrac{\partial}{\partial z}}\big)\Big[z\varphi - \hat{\varphi}(0)\Big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big[z^2 \varphi - \Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big)\Big] - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
+\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) + 3\big({-\tfrac{\partial}{\partial z}}\big)\big[z\varphi - \hat{\varphi}\big]_{\zeta = 0} + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
 \end{align*}
@@
 \begin{equation}\label{eqn:inhomog-mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\Big(\hat{\varphi}(0)\,z + \hat{\varphi}'(0)\Big).
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}.
 \end{equation}
-Noticing that equation~\ref{eqn:inhomog-mod-bessel} is an inhomogeneous version of equation~\ref{eqn:mod-bessel}, we
+Since we want $\laplace_\zeta \hat{K}$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
+Unfortunately, this would force $\hat{K}$ to be zero.
+\subsubsection{Success at $\zeta = 1$}
+Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. Since
+\begin{align*}
+\laplace_{\zeta_1} \hat{K} & = e^z \laplace_\zeta \hat{K} \\
+& = e^z K \\
+& = \kappa,
+\end{align*}
+we want $\laplace_{\zeta_1} \hat{K}$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
+\begin{equation}\label{eqn:shifted-spatial-mod-bessel}
+\left[\zeta_1(\zeta_1 + 2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(\zeta_1 + 1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+\end{equation}
+If $\hat{\varphi}$ satisfies equation~\ref{eqn:shifted-spatial-mod-bessel}, $\laplace_{\zeta_1} \hat{\varphi}$ will satisfy an inhomogeneous version of equation~\ref{eqn:shifted-mod-bessel}, analogous to equation~\ref{eqn:inhomog-mod-bessel}.
+This time, though, there's a trick we can use to zero out the inhomogeneity.
+Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.
+That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
 
-%%This suggests that $\hat{K}$ could be a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first degree at $\zeta = 0$.
-
-With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
+Following this plan, let's find $\hat{K}$ explicitly.
+Defining another coordinate $\xi$ on $\hat{\R}$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
 \begin{equation}\label{eqn:hypergeom}
@@
 \end{equation}
-\textbf{[...]}
+%With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
+The hypergeometric function
+\[ \hat{f}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
+satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Using DLMF~15.10.13, we can see that
+\[ \hat{f}_0 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
+also satisies equation~\ref{eqn:hypergeom}.
+It has a singularity of type $\xi^{-1/2}$ at $\xi = 0$, and continues holomorphically to the rest of $\hat{\C}$.
+Hence, by the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
+\textbf{[This isn't quite right!
+As the decomposition below shows, $\hat{f}_0$ isn't a holomorphic multiple of $\xi^{-1/2}$.
+We should take the first term of the decomposition instead.]} This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$.
 
+By DLMF~15.10.17,
+\[ \hat{f}_0 = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{4}{3})}\;\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) + \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}\;\hat{f}_1.
+\]
+The coefficients simplify to
+\begin{align*}
+\sqrt{\pi}\;\big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{2}{3} \pi)}{\pi} & = \frac{\sqrt{3}}{4} \\
+\big({-2}\sqrt{\pi}\big) \big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{1}{6} \pi)}{\pi} & = -\frac{1}{2}
+\end{align*}
+respectively, giving
+\begin{align*}
+\hat{f}_0 & = \tfrac{\sqrt{3}}{4}\,\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) - \tfrac{1}{2}\,\hat{f}_1 \\
+& \in \tfrac{\sqrt{3}}{4}\,\xi^{-1/2} + O_{\xi \to 0}(1).
+\end{align*}
+In terms of $\zeta_1$, we have
+\[ \hat{f}_0 \in -i\,\tfrac{\sqrt{3}}{4} \big(\tfrac{1}{2}\big)^{1/2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(1). \]
+Using the decay properties from Section~\ref{reg-decay}, we deduce that
+\[ f_0 \in -i\,\tfrac{\sqrt{3}}{4} \big(\tfrac{\pi}{2}\big)^{1/2}\,z^{-1/2} + O_{z \to \infty}(z^{-1}). \]
+Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
+Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{4}{\sqrt{3}}\,f_0$.
+We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
+\[ \hat{K} = i\,\tfrac{4}{\sqrt{3}}\,F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\zeta_1\big). \]
+The hypergeometric function is defined by its power series around $\zeta_1 = -2$, and continued counterclockwise around the singularity at $\zeta_1 = 0$ to the ray $\zeta_1 \in (0, \infty)$.
+\section{Sketches}
+\subsection{Contour argument}
 The hypergeometric function
 \[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
-satisfies equation~\ref{eqn:hypergeom} by definition. It has a singularity of type $\xi^{-1/2}$ at $\xi = 0$, and continues holomorphically to the rest of $\C$. Using DLMF~15.10.13, we can see that
-\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
-also satisies equation~\ref{eqn:hypergeom}. It has a singularity of type $(1 - \xi)^{-1/2}$ at $\xi = 1$, and continues holomorphically to the rest of $\C$.
+satisfies equation~\ref{eqn:hypergeom} by definition. It has a singularity of type $(1 - \xi)^{-1/2}$ at $\xi = 1$, and continues holomorphically to the rest of $\hat{\C}$.
 

### 2021-12-15 airy-resurgence.tex
Remove personal style dependency
Take the relevant lines from my personal `ajf` style package and
put them into the document.
Correct the mistake in finding K-hat

@@
 
-\usepackage{ajf}
 \usepackage{url}
 \usepackage[hmargin=1.5in]{geometry}
-\usepackage{amsthm}
+\usepackage{amsmath}
+\usepackage{amssymb}
+%%\usepackage{amsthm}
 
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}
-\theoremstyle{plain}
-\newtheorem{prop}{Proposition}
+%%\theoremstyle{definition}
+%%\newtheorem{defn}{Definition}
+%%\theoremstyle{plain}
+%%\newtheorem{prop}{Proposition}
+
+% convenience aliases
+\newcommand{\maps}{\colon}
 
 % symbology
-\newcommand{\posreal}{\R_{> 0}}
+\newcommand{\Z}{\mathbb{Z}}
+\newcommand{\R}{\mathbb{R}}
+\newcommand{\C}{\mathbb{C}}
 \newcommand{\laplace}{\mathcal{L}}
@@
 \[ \hat{f}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
-satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Using DLMF~15.10.13, we can see that
-\[ \hat{f}_0 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
-also satisies equation~\ref{eqn:hypergeom}.
-It has a singularity of type $\xi^{-1/2}$ at $\xi = 0$, and continues holomorphically to the rest of $\hat{\C}$.
-Hence, by the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
-\textbf{[This isn't quite right!
-As the decomposition below shows, $\hat{f}_0$ isn't a holomorphic multiple of $\xi^{-1/2}$.
-We should take the first term of the decomposition instead.]} This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$.
-
-By DLMF~15.10.17,
-\[ \hat{f}_0 = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{4}{3})}\;\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) + \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}\;\hat{f}_1.
+satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
+\[ \hat{f}_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
+which is a holomorphic multiple of $\xi^{-1/2}$ near $\xi = 0$.
+By the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
+This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$.
+The power series~\cite[equation~15.2.1]{dlmf}
+\[ \hat{f}_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
+converges near $\xi = 0$, showing that
+\[ \hat{f}_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
+In terms of $\zeta_1$, we have
+\[ \hat{f}_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
+%%Using DLMF~15.10.13, we can see that
+%%\[ \hat{f}_0 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
+%%also satisies equation~\ref{eqn:hypergeom}.
+%%-------------------------------------------------------------
+%%By DLMF~15.10.17,
+%%\[ \hat{f}_0 = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{4}{3})}\;\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) + \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}\;\hat{f}_1.
 \]
-The coefficients simplify to
-\begin{align*}
-\sqrt{\pi}\;\big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{2}{3} \pi)}{\pi} & = \frac{\sqrt{3}}{4} \\
-\big({-2}\sqrt{\pi}\big) \big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{1}{6} \pi)}{\pi} & = -\frac{1}{2}
-\end{align*}
-respectively, giving
-\begin{align*}
-\hat{f}_0 & = \tfrac{\sqrt{3}}{4}\,\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) - \tfrac{1}{2}\,\hat{f}_1 \\
-& \in \tfrac{\sqrt{3}}{4}\,\xi^{-1/2} + O_{\xi \to 0}(1).
-\end{align*}
-In terms of $\zeta_1$, we have
-\[ \hat{f}_0 \in -i\,\tfrac{\sqrt{3}}{4} \big(\tfrac{1}{2}\big)^{1/2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(1). \]
+%%The coefficients simplify to
+%%\begin{align*}
+%%\sqrt{\pi}\;\big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{2}{3} \pi)}{\pi} & = \frac{\sqrt{3}}{4} \\
+%%\big({-2}\sqrt{\pi}\big) \big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{1}{6} \pi)}{\pi} & = -\frac{1}{2}
+%%\end{align*}
+%%respectively, giving
 Using the decay properties from Section~\ref{reg-decay}, we deduce that
-\[ f_0 \in -i\,\tfrac{\sqrt{3}}{4} \big(\tfrac{\pi}{2}\big)^{1/2}\,z^{-1/2} + O_{z \to \infty}(z^{-1}). \]
+\[ f_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
 Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
-Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{4}{\sqrt{3}}\,f_0$.
+Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{1}{2}\,f_0$.
 We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
-\[ \hat{K} = i\,\tfrac{4}{\sqrt{3}}\,F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\zeta_1\big). \]
-The hypergeometric function is defined by its power series around $\zeta_1 = -2$, and continued counterclockwise around the singularity at $\zeta_1 = 0$ to the ray $\zeta_1 \in (0, \infty)$.
+\[ \hat{K} = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
 \section{Sketches}

### 2022-01-05 draft2.tex
new version
New formula that replace Maxim's one, and new comment about why Caputo is a good definition with respect to the convolutitve model

\DeclareSymbolFont{AMSb}{U}{msb}{m}{n}
\documentclass[11pt,a4paper,twoside,leqno,noamsfonts]{amsart}
           \usepackage{setspace}
\linespread{1.34}           
           %\onehalfspacing
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\definecolor{britishracinggreen}{rgb}{0.0, 0.26, 0.15}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\usepackage[utopia]{mathdesign}
    \DeclareSymbolFont{usualmathcal}{OMS}{cmsy}{m}{n}
    \DeclareSymbolFontAlphabet{\mathcal}{usualmathcal}
\usepackage[a4paper,top=4cm,bottom=3cm,left=3.5cm,
           right=3.5cm,bindingoffset=5mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{braket,caption,comment,mathtools,stmaryrd}
\usepackage{multirow,booktabs,microtype}
\usepackage{latexsym}
\usepackage{todonotes}
\usepackage{fancyhdr}
%\renewcommand{\sectionmark}[1]{\markboth{\thesection\ #1}{}}
\pagestyle{fancy}
% Clear the header and footer
\fancyhead{}
\fancyfoot{}
% Set the right side of the footer to be the page number
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{\baselineskip}
%\fancyhead[RE]{\rightmark}
%\fancyhead[RE]{}
\usepackage{soul} % per testo barrato
\usepackage[colorlinks,bookmarks]{hyperref} %
\hypersetup{colorlinks,%
            citecolor=britishracinggreen,%
            filecolor=black,%
            linkcolor=cobalt,%
            urlcolor=black}
\setcounter{tocdepth}{2}
%\setcounter{section}{-1}
\numberwithin{equation}{section}
\input{command}
\DeclareRobustCommand{\subtitle}[1]{\\#1}
\title[Exponential Integrals]{Exponential Integrals\\ [1ex]
  }

\author{
Veronica Fantini 
}
%\address{SISSA Trieste, Via Bonomea 265, 34136 Trieste, Italy}
%\email{ vfantini@sissa.it}
%
\begin{document}
\hbadness=150
\vbadness=150
%
%\begin{abstract}
%We show how wall-crossing formulas in coupled $2d$-$4d$ systems, introduced by Gaiotto, Moore and Neitzke, can be interpreted geometrically in terms of the deformation theory of holomorphic pairs, given by a complex manifold together with a holomorphic vector bundle. The main part of the paper studies the relation between scattering diagrams and deformations of holomorphic pairs, building on recent work by Chan, Conan Leung and Ma.      
%\end{abstract}
%
\maketitle
%
%
%
{
\hypersetup{linkcolor=black}
\tableofcontents}

\section{Introduction}

%\begin{example}[Airy]
%The Airy equation is 
%\begin{equation}
%y''=xy
%\end{equation}
% and a system of solutions is given by (see DLMF) 
%
%\begin{align*}
%&Ai(x)=\frac{1}{2\pi i}\int_{\infty e^{-i\pi/3}}^{\infty e^{i\pi/3}}e^{t^3/3-xt}dt\\
%&Bi(x)=\frac{1}{2\pi}\int_{-\infty}^{\infty e^{-i\pi/3}}e^{t^3/3-xt}dt+\frac{1}{2\pi}\int_{-\infty}^{\infty e^{i\pi/3}}e^{t^3/3-xt}dt
%\end{align*}
%
%
%
%Let $\psi(x)\defeq\sum_{n\geq 0}a_nx^{-n}$ be the asymptotic expansion of $Ai(x)$ as $x\to\infty$: from DLMF and Sauzin
%
%\begin{equation}
%Ai(x)\sim \frac{e^{-2/3x^{3/2}}}{2\sqrt{\pi}x^{1/4}}\sum_{n\geq 0}(-1)^n\frac{1}{2^{n+1}\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{2}x^{-3/2}\right)^n
%\end{equation}
%and $a_n\defeq (-1)^n\frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$. Analougusly, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
%
%\begin{equation}
%Bi(x)\sim \frac{e^{2/3x^{3/2}}}{\sqrt{\pi}x^{1/4}}\sum_{n\geq 0}\frac{1}{2^{n+1}\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{2}x^{-3/2}\right)^n
%\end{equation}
%
%and $b_n\defeq \frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$.
%\begin{prop}
%$\psi(x)$ and $\varphi(x)$ are resurgent series.
%\end{prop}
%\begin{proof}
%Let $\hat{\psi}(\zeta)=\frac{1}{2\pi}\sum_{n\geq 0}a_{n-1}\frac{\zeta^n}{(n-1)!}$, mathematica says 
%\begin{equation}
%\hat{\psi}(\zeta)=-\frac{5}{48} F_1(7/6,11/6,2,-3/4\zeta)
%\end{equation}
%which has a log singularity at $\zeta=-4/3$, namely 
%\begin{equation}
%\hat{\psi}(\zeta+4/3)=\log(\zeta)\hat{\psi}_{-4/3}(\zeta)+\text{hol.fct}
%\end{equation}
%where $\hat{\psi}_{-4/3}(\zeta)$ is holomorphic in a neighbourhood of the origin. In particular, $\hat{\psi}_{-4/3}(\zeta)=-\frac{1}{2}\varphi(\zeta)$.    
%Now, let $\hat{\varphi}(\zeta)=\frac{1}{2\pi}\sum_{n\geq 0}b_{n-1}\frac{\zeta^n}{(n-1)!}$, mathematica says 
%\begin{equation}
%\hat{\varphi}(\zeta)=\frac{5}{48} F_1(7/6,11/6,2,3/4\zeta)
%\end{equation}
%which has a log singularity at $\zeta=4/3$, namely 
%\begin{equation}
%\hat{\varphi}(\zeta-4/3)=\log(\zeta)\hat{\varphi}_{4/3}(\zeta)+\text{hol.fct}
%\end{equation}
%where $\hat{\varphi}_{4/3}(\zeta)$ is holomorphic in a neighbourhood of the origin. In particular, $\hat{\varphi}_{4/3}(\zeta)=\frac{1}{2}\psi(\zeta)$.    
%\end{proof}
%
%Comment on the asymptotic expansion of $Ai(x)$ and $Bi(x)$: the prepared form of the Airy equation is obtained after the change of coordinates $z=x^{3/2}$ and it reads
%
%\begin{equation}\label{prepform}
%y''(z)+\frac{y'(z)}{3z}=\frac{4}{9}y(z)
%\end{equation} 
%
%In particular, its Borel trasform is 
%\begin{equation}
%\zeta^2\hat{y}-\frac{1}{3}\ast (\zeta\hat{y})=\frac{4}{9}\hat{y}
%\end{equation}
%and we read the singularity of the Borel transform as solution of $z^2-4/9=0$, which are $z=\pm 2/3$. These are indeed the exponent of the exponential factor in the asymptotic of $Ai(z)$ and $Bi(z)$ respectively.  
%
%Alternatively, from the theory of ODE we can look for a solution of \eqref{prepform} of the form
%\begin{equation}
%y(z)=\sum_{k\in\Z^2}U^ke^{-k\cdot\lambda z}z^{-\tau\cdot k}w_{k}(z)
%\end{equation} 
%where $\lambda=(\lambda_1,\lambda_2)$ with $\lambda_i^2-4/9=0$, $\tau=(\tau_1,\tau_2)$ with $\tau_i=1/6$ and $w_k(z)\in\C[[z^{-1}]]$ is a formal series. Plugging in the ansatz in \eqref{prepform}, we fins that the only non zero solutions $w_k$ occurs for $k=(1,0)$ and $k=(0,1)$, meaning that the formal integral of the Airy equation is given by 
%\begin{equation}
%y(z)=U_1e^{-2/3z}z^{-1/6}w_{(1,0)}(z)+U_2e^{2/3z}z^{-1/6}w_{(0,1)}(z).
%\end{equation}
%The latter expression can be compared with the asymptotic behaviour of $Ai(z)+Bi(z)$ as $z\to\infty$. In particular, $w_{k}$ solves the following homogeneus equation:
%\begin{align*}
%\left(\partial_z^2-\frac{4}{3}\partial_z+\frac{5}{36z^2}\right)w_{(1,0)}=0\\
%\left(\partial_z^2+\frac{4}{3}\partial_z+\frac{5}{36z^2}\right)w_{(0,1)}=0
%\end{align*}
%Assuming $w_{(1,0)}=1+\sum_{n\geq 1}a_n^+z^{-n}$ and $w_{(0,1)}=1+\sum_{n\geq 1}a_n^-z^{-n}$ we get \[a_n^+=(-1)^n\left(\frac{3}{4}\right)^n\frac{\Gamma(n+\frac{1}{6})\Gamma(n+\frac{5}{6})}{2\pi n!}=a_n\] and \[a_n^-=\left(\frac{3}{4}\right)^n\frac{\Gamma(n+\frac{1}{6})\Gamma(n+\frac{5}{6})}{2\pi n!}=b_n.\] 
%
%Now, we investigate the exponential integral
%\begin{equation}
%I(z)\defeq\int_{\Gamma} \exp(-z\left(\frac{x^3}{3}-x\right))dx
%\end{equation}
%where $\Gamma$ is a suitable countour. By simple computation we notice that $I(z)=-2\pi iz^{-1/3}Ai(x)$ (where $z=x^{3/2}$). In particular, $I(z)$ is a solution of 
%\begin{equation}\label{eq:Iold}
%I''-\frac{4}{9}I+\frac{I'}{z}-\frac{1}{9}\frac{I}{z^2}=0
%\end{equation} 
% The Borel trasform of $\hat{I}(z)$ can be computed directly from the equation \eqref{eq:I}, namely the Borel transform of equation \eqref{eq:I} is
%\begin{equation}
%\zeta^2 \hat{I}-\frac{4}{9}\hat{I}-1\ast\zeta\hat{I}-\frac{1}{9}\zeta\ast\hat{I}=0
%\end{equation} 
%\begin{equation}
%\zeta^2 \hat{I}-\frac{4}{9}\hat{I}-\int_0^\zeta\zeta'\hat{I}(\zeta')d\zeta '-\frac{1}{9}\int_0^\zeta(\zeta-\zeta')\hat{I}(\zeta')d\zeta'=0
%\end{equation} 
%\begin{align*}
%2\zeta\hat{I}+\zeta^2\hat{I}'-\frac{4}{9}\hat{I}'-\zeta\hat{I}-\frac{1}{9}\int_0^\zeta\hat{I}(\zeta')d\zeta'=0\\
%\hat{I}+\zeta\hat{I}'+2\zeta\hat{I}'+\zeta^2\hat{I}''-\frac{4}{9}\hat{I}''-\frac{1}{9}\hat{I}=0
%\end{align*}
%\begin{equation}
%(\zeta^2-\frac{4}{9})\hat{I}''+3\zeta\hat{I}'+(1-\frac{1}{9})\hat{I}=0
%\end{equation} 
%and for some costants $c_1,c_2\in\C$ the solutions are
%\begin{equation}
%\hat{I}(\zeta)=\frac{9\zeta c_1}{4\sqrt{\frac{4}{9}-\zeta^2}}+c_2
%\end{equation}  
%\end{example}
%\textcolor{red}{Is $F_1(7/6,11/6,2,3/4\zeta)$ algebraic?}

\section{Fractional derivatives and Borel transform}

\begin{definition}
Let $\alpha\in (0,1)$ and $n\in\N$, then the $n+\alpha$-Caputo's derivative of a smooth fucntion $f$ is defined as
\begin{equation}
\partial_x^{n+\alpha}f(x)\defeq\frac{1}{\Gamma(1-\alpha)}\int_0^x(x-s)^{-\alpha}f^{(n+1)}(s)ds
\end{equation}
\end{definition}

In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$. Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways:
\begin{multline}
\label{mod1}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}(z^{\alpha+n})\ast\hat{\varphi}(\zeta)=\int_0^{\zeta}\frac{(\zeta-s)^{-1-n-\alpha}}{(-1-n-\alpha)!}\sum_{k\geq 0}\frac{a_k}{k!}s^{k}ds\\
=\frac{1}{(-\alpha)!}\int_0^{\zeta}(\zeta-s)^{-\alpha}\sum_{k\geq 0}\frac{a_k}{(k-n-1)!}s^{k-n-1}ds=\partial_{\zeta}^{n+\alpha}\hat{\varphi}(\zeta)
\end{multline}
\begin{equation}
\label{mod2}
\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}\left(\sum_{k\geq 0}a_kz^{-k-1+n+\alpha}\right)(\zeta)=\sum_{k>n}\frac{a_k}{(k-n-\alpha)!}\zeta^{k-n-\alpha}
\end{equation}

and computitng the integral which defines the $n+\alpha$-derivative we get exaclty the same result as \eqref{mod2}.

\section{Resurgence of exponential integrals}

Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set

\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
\begin{equation}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n}.
\end{equation}
\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$
\begin{enumerate}
\item $\tilde{\varphi}_\alpha$ is Gevrey-1;
\item $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ is a germ of analytic function at $\zeta=\zeta_{\alpha}=f(x_\alpha)$;
\item the following formual holds true
\begin{multline}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-N/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-N/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
\end{multline} 
\end{enumerate}
\end{theorem}
\begin{proof}
Part $(3)$: thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
\begin{equation}
\partial^{1/2}_{\zeta, \text{based at }\zeta_\alpha}\hat{I}_{\alpha}(\zeta)=\hat{\varphi}_{\alpha}(\zeta).
\end{equation} 
In addition, we notice 
\begin{align*}
I_{\alpha}(z)&=\int_{\mathcal{C}_{\alpha}}e^{-zf}\nu & f=\zeta\\
&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Heckel countour} \\
&=:\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\hat{I}_{\alpha}(\zeta)d\zeta &
\end{align*}
hence 
\begin{equation}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{1/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)\right)=\partial^{3/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)
\end{equation}
\end{proof}

\begin{example}[Airy]
Let $f(t)=\frac{t^3}{3}-t$ and \[I(z)\defeq\int_{\gamma} e^{-zf(t)}\text{dt}\]
where $\gamma$ is a countour where the integral is well defined.

By the change of coordinates $z=x^{3/2}$, $I(z)=-2\pi iz^{-1/3}Ai(x)$ where \[Ai(x)\defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{\frac{t^3}{3}-zt}\text{dt}\] 
hence $I(z)$ solves the following ODE\footnote{$Ai(x)$ solves the Airy equation $y''=xy$.}
\begin{equation}\label{eq:I}
I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2}=0
\end{equation}
A formal solution of \eqref{eq:I} can be computed by making the following ansatz 
\begin{equation}
\tilde{I}(z)=\sum_{k\in\N^2}U^ke^{-\lambda\cdot k z}z^{-\tau\cdot k}w_k(z)
\end{equation}
with $U^{(k_1,k_2)}=U_1^{k_1}U_2^{k_2}$ and $U_1,U_2\in\C$ are constant parameter, $\lambda=(\frac{2}{3},-\frac{2}{3})$, $\tau=(\frac{1}{2},\frac{1}{2})$, and $\tilde{w}_k(z)\in\C[[z^{-1}]]$. In addition, we can check that the only non zero $\tilde{w}_k(z)$ occurs at $k=(1,0)$ and $k=(0,1)$, therefore
\begin{equation}
\tilde{I}(z)=U_1e^{-2/3z}z^{-1/2}\tilde{w}_{+}(z)+U_2e^{2/3z}z^{-1/2}\tilde{w}_{-}(z)
\end{equation}  
where from now on we denote $\tilde{w}_+(z)=\tilde{w}_{(1,0)}(z)$ and $\tilde{w}_-(z)=\tilde{w}_{(0,1)}(z)$. In particular, $\tilde{w}_+(z)$ and $\tilde{w}_-(z)$ are formal solution of 
\begin{align}
\label{eq:w+} \tilde{w}_+''-\frac{4}{3}\tilde{w}_+'+\frac{5}{36}\frac{\tilde{w}_+}{z^2}=0\\
\label{eq:w-} \tilde{w}_-''+\frac{4}{3}\tilde{w}_-'+\frac{5}{36}\frac{\tilde{w}_-}{z^2}=0
\end{align}
Taking the Borel transform of \eqref{eq:w+}, \eqref{eq:w-} we get
\begin{align*}
&\zeta^2\hat{w}_{+}(\zeta)+\frac{4}{3}\zeta\hat{w}_{+}+\frac{5}{36}\zeta\ast\hat{w}_{+}=0\\
&\zeta^2\hat{w}_{+}(\zeta)+\frac{4}{3}\zeta\hat{w}_{+}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{w}_{+}(\zeta')d\zeta'=0
\end{align*}
\begin{align*}
&\zeta^2\hat{w}_{-}(\zeta)-\frac{4}{3}\zeta\hat{w}_{-}+\frac{5}{36}\zeta\ast\hat{w}_{-}=0\\
&\zeta^2\hat{w}_{-}(\zeta)-\frac{4}{3}\zeta\hat{w}_{-}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{w}_{-}(\zeta')d\zeta'=0
\end{align*}
and taking derivatives we get
\begin{align*}
&\zeta(\frac{4}{3}+ \zeta)\hat{w}_{+}''+(\frac{8}{3}+4\zeta)\hat{w}_+'+\frac{77}{36}\hat{w}_{+}=0 & \\
&\frac{4}{3}\zeta( 1+ \frac{3}{4}\zeta)\hat{w}_{+}''+(\frac{8}{3}+4\zeta)\hat{w}_+'+\frac{77}{36}\hat{w}_{+}=0 & \\
&\qquad u(1-u)\hat{w}_+''(u)+(2-4u)\hat{w}_+'(u)-\frac{77}{36}\hat{w}_+(u)=0 & u=-\frac{3}{4}\zeta\\
%&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}_-(u) & u=\frac{3}{4}\zeta
\end{align*} 
\begin{align*}
&\zeta(-\frac{4}{3}+ \zeta)\hat{w}_{-}''+(-\frac{8}{3}+4\zeta)\hat{w}_-'+\frac{77}{36}\hat{w}_{-}=0 & \\
&\frac{4}{3}\zeta(-1+ \frac{3}{4}\zeta)\hat{w}_{-}''+(-\frac{8}{3}+4\zeta)\hat{w}_-'+\frac{77}{36}\hat{w}_{-}=0 & \\
&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}(u) & u=\frac{3}{4}\zeta
\end{align*} 
Notice that the latter equations are hypergeometric, hence a solution is given by 
\begin{align}
\label{hat+}\hat{w}_+(\zeta)=\mathit{c}_1 \, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)\\
\label{hat-}\hat{w}_-(\zeta)=\mathit{c}_2 \, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)
\end{align}
for some constants $\mathit{c}_1, \mathit{c}_2\in\C$ (see DLMF 15.10.2). In addition $\hat{w}_{\pm}(\zeta)$ have a log singularity respectively at $\zeta=\mp\frac{4}{3}$, therefore they are $\lbrace\mp\frac{4}{3}\rbrace $-resurgent functions.\footnote{The solution we find are equal to the ones in DLMF $\mathsection 9.7$. They also agree with slide 10 of Maxim's talk for ERC and with the series (6.121) in Sauzin's book. However they do not agree with (2.16) in Mari\~no's Diablerets.}

\begin{remark}
$\hat{w}_{+}(\zeta)$ is Laplace summable along the positive real axis, and it can be analyticaly continued on $\C\setminus -\frac{4}{3}\R_{\leq 0}$ with (see 15.2.3 DLMF)
\begin{align*}
\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{k\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right) &\\
&=\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right) &\\
&=\mathbf{i}\hat{w}_{-}(\zeta+\frac{4}{3}) &
\end{align*}
Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
\begin{align*}
\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{k\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144} (-4 + 3 \zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right) &\\
&=-\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
&=-\mathbf{i}\hat{w}_{+}(\zeta-\frac{4}{3}) &
\end{align*}
These relations manifest the resurgence property of $\tilde{I}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.  
\end{remark}

%\begin{remark}
%In \cite{Marino-diableret}, Mari\~{n}o studies the example of the Airy function and its resurgent properties. According to his notation
%\begin{equation}
%Ai(x)=\frac{1}{2x^{1/4}\sqrt{\pi}}e^{-\frac{2}{3}x^{3/2}}\varphi_1(x^{-3/2})
%\end{equation}
%\begin{equation}
%Bi(x)=\frac{1}{2x^{1/4}\sqrt{\pi}}e^{\frac{2}{3}x^{3/2}}\varphi_2(x^{-3/2})
%\end{equation}
%with \[\varphi_{1,2}(z)=\sum_{k\geq 0}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^k\frac{\Gamma\left(k+\frac{1}{6}\right)\Gamma\left(k+\frac{5}{6}\right)}{k!}z^k.\]
%In particular, the Borel transform of $\varphi_1(z)$ and $\varphi_2(z)$ are respectively 
%\begin{align}
%\label{Marino_hat}
%\hat{\varphi}_1(\zeta)&={}_1F_2\left(\frac{1}{6},\frac{5}{6};1;-\frac{3}{4}\zeta\right)\\
%\label{Marino_hat2}\hat{\varphi}_2(\zeta)&={}_1F_2\left(\frac{1}{6},\frac{5}{6};1;\frac{3}{4}\zeta\right)
%\end{align} 
% In particular, we notice that $\hat{w}_+(\zeta)$ and $\hat{w}_-(\zeta)$ in \eqref{eq:w+}, \eqref{eq:w-} are (up to a constant) the first derivatives of
%\begin{align*}
%\hat{w}_+(\zeta)&\propto\frac{\dd}{\dd\zeta}\hat{\varphi}_1(\zeta)\\
%\hat{w}_-(\zeta)&\propto\frac{\dd}{\dd\zeta}\hat{\varphi}_2(\zeta)
%\end{align*} 
%\end{remark}

Our next goal is to prove that the Borel transform of $\tilde{I}(z)$ can be written in terms of $1/f'(f^{-1}(\zeta))$, namely formula \eqref{formula1}. It is convenient to consider the two asymptotic formal solutions separately, namely we define

\begin{align}
\tilde{I}_{-1}(z)\defeq e^{-2/3z}z^{-1/2}\tilde{w}_+(z)=\colon z^{-1/2}\tilde{u}_+(z) \\
\tilde{I}_{1}(z)\defeq e^{2/3z}z^{-1/2}\tilde{w}_-(z)=\colon z^{-1/2}\tilde{u}_-(z)
\end{align}

In particular, $\tilde{u}_{\pm}(z)$ are solutions of

\begin{equation}\label{eq:u}
\tilde{u}''(z)-\frac{4}{9}\tilde{u}(z)+\frac{5}{36}\frac{\tilde{u}(z)}{z^2}=0
\end{equation}

with asymptotic behaviour $\tilde{u}_\pm(z)\sim O(e^{\pm 2/3 z})$ as $z\to\infty$.

The Borel transforms $\hat{u}_{\pm}(\zeta)$ solve the same equation
\begin{align*}
&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\zeta\ast\hat{u}\\
&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{u}(\zeta')d\zeta'\\
&\text{taking derivatives is equivalent to} \\
&(\zeta^2-\frac{4}{9})\hat{u}''(\zeta)+4\zeta\hat{u}'(\zeta)+\frac{77}{36}\hat{u}(\zeta)=0
\end{align*}

and Mathematica gives the following solutions
\begin{align*}
\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &  
\end{align*}
Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
\begin{align*}
\hat{u}_+(\zeta)&=C_1 T_{-2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-2/3}\hat{w}_+(\zeta)\\
\hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
\end{align*}

\begin{claim}\label{claim1}
\begin{equation}
\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
\end{equation}
\end{claim}

\begin{lemma}
The following identity holds true
\begin{equation}
{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}\qquad \zeta=\frac{u^3}{3}-u
\end{equation}
\end{lemma}
\begin{proof}
\begin{align*}
{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)&=2\cos\left(\frac{1}{3}\arcsin\left(\frac{3}{2}\zeta\right)\right)(4-9\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
&=\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
&=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
&=\frac{1}{\cos(2y)-2\sin^2(y)} & \\
&=\frac{1}{1-4\sin^2(y)} & \zeta=2\sin(y)-\frac{8}{3}\sin^3(y)
\end{align*}
Therefore, if $u\defeq -2\sin(y)$, we have $\zeta=\frac{u^3}{3}-u=f(u)$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}=-\frac{1}{f'(u)}\]
\end{proof}

Hence claim \eqref{claim1} is equivalent to 
\begin{claim}\label{claim 2}
\begin{equation}
\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds
\end{equation}
\end{claim}

Let us study the RHS of claim \eqref{claim 2}
\begin{align*}
&\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
&= -\frac{2}{9}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right)ds+\frac{2}{9}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right)ds & 15.8.28 \text{ DLMF} \\
&=-\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};t\right)dt+\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt & \zeta'=\frac{1}{2}-\frac{3}{4}\zeta\\
&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt -\frac{9i}{32}\textcolor{gray}{\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};-\frac{1}{2};1-t\right)dt}& 15.10.21 \text{ DLMF }\\
&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{5}{2};1-t\right)t^{-3/2}dt &  15.10.13 \text{ DLMF }
\end{align*}

%By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
%
%\begin{align*}
%\int_{0}^{\zeta''}(\zeta''-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt=\sqrt{\pi}\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n \Gamma(3/2+n)}{\zeta''}^{n+\frac{1}{2}}= 2\sqrt{\zeta''}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta''\right)\\
%\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt= 2\sqrt{\zeta'}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta'\right)-\int_0^1(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt
%\end{align*}

%Using properties of Caputo's $1/2$-derivative we would like to express $\hat{w}_{\pm}(\zeta)$ as the $1/2$-derivatives of other hypergeometric series. From the integral representation of hypergeomtric functions (see DLMF 15.6.1)
%
%\begin{align*}
%{}_2F_1\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)&=\frac{3}{5\pi}\int_0^1t^{5/6}(1-t)^{-5/6}(1+\frac{3}{4}\zeta t)^{-7/6}dt & |u|<\frac{4}{3}\\
%&=\frac{3}{5\pi}\zeta^{-1}\int_0^{\zeta}u^{5/6}(\zeta-u)^{-5/6}(1+\frac{3}{4}u)^{-7/6}du &u=\zeta t\\
%&=\frac{3}{5\pi}\int_0^{\zeta}(\zeta-u)^{-1/2}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)du & \\
%&=\frac{3}{5\sqrt{\pi}}\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-u)^{-1/2}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)du & 
%%&=\textcolor{blue}{\frac{3}{5\sqrt{\pi}}\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-u)^{-1/2}\frac{1}{f'(f^{-1}(u))} du } & \\
%%&=\textcolor{blue}{\frac{3}{5\sqrt{\pi}}\zeta^{-1}\partial_{\zeta}^{1/2}f^{-1}(\zeta)} &  
%\end{align*}
%For formula \eqref{formula1} to hold true we must have
%\begin{equation}\label{claim}
%\frac{3}{5\sqrt{\pi}}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)= \frac{1}{f'(f^{-1}(u))}
%\end{equation}  
%however, $\frac{1}{f'(f^{-1}(u))}$ does not depend on $\zeta$, thus \eqref{claim} is false, and the Airy exponential integral is a counter example of the formula \eqref{formula1}.   
%%thus, we would like to see $\int_0^u(\zeta-t)^{-1/3}t^{5/6}(1+\frac{3}{4}t)^{-7/6}dt$ as the product of first derivatives of an hypergeomtric function and un unknown function $g(\zeta)$
%%\begin{align*}
%%\int_0^u(\zeta-t)^{-1/3}t^{5/6}(1+\frac{3}{4}t)^{-7/6}&\textcolor{blue}{=}\int
%%\end{align*}
%
%\subsection{Second temptative formula} Let us assume that the correct formula that replaces \eqref{formula1} in Theorem \ref{thm:maxim} is 
%\begin{multline}\label{formula2}
%\hat{I}_{\alpha}(\zeta)=\partial^{N/2}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-N/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-N/2}\int_{f^{-1}(\zeta')}\frac{\nu}{df} d\zeta'
%\end{multline} 
%then we compute $\hat{I}$ using properties of the Borel transform of a product:
%
%\begin{align*}
%\hat{I}(\zeta)&=\mathcal{B}(z^{-1/2})\ast\hat{u}(\zeta)\\
%&=\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-s)^{-1/2}\hat{u}(s)ds\\
%&=\frac{1}{\Gamma(1/2)}\int_0^\zeta (\zeta-s)^{-1/2}\left(T_{-2/3}\hat{w}_+(s)+T_{2/3}\hat{w}_-(s)\right)ds
%\end{align*}
%
%\begin{align*}
%&=\frac{1}{\Gamma(1/2)}\int_0^\zeta(\zeta-s)^{-1/2} \hat{w}_+(s-2/3)+\frac{1}{\Gamma(1/2)}\int_0^\zeta (\zeta-s)^{-1/2}\hat{w}_-(s+2/3)ds\\
%&=\frac{1}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-1/2} \hat{w}_+(s)+\frac{1}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-1/2}\hat{w}_-(s)ds\\
%&=\frac{C_1}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-1/2} {}_2F_1\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}s\right)ds+\frac{C_2}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-1/2}{}_2F_1\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}s\right)ds\\
%&=\frac{C_3}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-\frac{1}{2}} \frac{\partial}{\partial s}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,-\frac{3}{4}s\right)ds+\frac{C_4}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-\frac{1}{2}}\frac{\partial}{\partial s}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\frac{3}{4}s\right)ds\\
%&=\textcolor{red}{C_3\partial^{1/2}_{\zeta, \text{based at } -2/3}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,-\frac{3}{4}\zeta\right)+C_4\partial^{1/2}_{\zeta, \text{based at } 2/3}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\frac{3}{4}\zeta\right)}\, \textcolor{red}{\text{ is wrong!}}
%\end{align*}
%However, ${}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\mp\frac{3}{4}\zeta\right)$ are not algebraic, hence they can not be equal to $\frac{1}{f'(f^{-1}(\zeta))}$ as it is in in Theorem \ref{thm:maxim} part II \eqref{formula2}. 
%
%%Notice that $\pm\frac{2}{3}=f(\mp 1)$, i.e. they are the critical value of $f$. Thus, we  are left to check that ${}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\mp\frac{3}{4}\zeta\right) $ is equal to $1/f'(f^{-1}(\zeta)$. Using Mathamtica we simplify the hypergeometric function 
%%
%%\begin{equation}
%%{}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)= \frac{2\sqrt{3}\sinh\left(\frac{2}{3}\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4+3\zeta}}
%%\end{equation}
%%
%%then we did the following manipulations: we set $x=\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)$, then  
%%
%%\begin{multline}
%%\frac{2\sqrt{3}\sinh\left(\frac{2}{3}\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4+3\zeta}}= \frac{3\sinh\left(\frac{2}{3}x\right)}{2\sinh(x)\sqrt{1+\sinh(x)^2}} \\
%%= \frac{3\sinh\left(\frac{2}{3}x\right)}{2\sinh(x)\cosh(x)}=\frac{3\sinh\left(\frac{2}{3}x\right)}{\sinh(2x)}=\frac{3\sinh\left(\frac{2}{3}x\right)}{3\sinh\left(\frac{2}{3}x\right)+4\sinh^3\left(\frac{2}{3}x\right)}\\
%%=\frac{1}{1+\frac{4}{3}\sinh^2\left(\frac{2}{3}x\right)}
%%\end{multline}
%%
%%With respect to the other hypergeometric function, Mathematica gives
%%
%%\begin{equation}
%%{}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)= \frac{2\sqrt{3}\sin\left(\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4-3\zeta}}
%%\end{equation}
%% now we set $x=\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)$, then 
%% \begin{multline}
%% \frac{2\sqrt{3}\sin\left(\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4-3\zeta}}=\frac{2\sqrt{3}\sin(x)}{\frac{2}{\sqrt{3}}\sin\left(\frac{3}{2}x\right)\sqrt{4-4\sin^2\left(\frac{3}{2}x\right)}}\\
%% \frac{3\sin(x)}{2\sin\left(\frac{3}{2}x\right)\cos\left(\frac{3}{2}x\right)}=\frac{3\sin(x)}{\sin(3x)}=\frac{3\sin(x)}{3\sin(x)-4\sin^3(x)}\\
%% =\frac{1}{1-\frac{4}{3}\sin^2(x)}
%% \end{multline}
%
%
%%\begin{remark}
%%Notice that the half derivative of a simple pole gives a log singularity; indeed 
%%\begin{align*}
%%\frac{1}{1-\frac{4}{3}\sin^2(x)} \text{has simple poles at } \zeta=\frac{4}{3} \text{ and } \zeta=\infty \\
%%\frac{1}{1+\frac{4}{3}\sinh^2(x)} \text{has simple poles at } \zeta=\frac{4}{3} \text{ and } \zeta=\infty \\ 
%%\end{align*} 
%%\end{remark}
%%
%%
%%If $\tilde{I}(z)$ is Borel--Laplace summable, then for a suitable choice of $U_1,U_2$ and of a direction $\theta\in\R/2\pi i\Z$, $\mathcal{S}^{\theta}\tilde{I}(z)=I(z)$. Indeed 
%%\begin{align*}
%%I(z)&=\int_{\mathcal{C}} e^{-zf(t)}\text{dt}=\int_{\mathcal{C}_h} e^{-z\zeta}\frac{d\zeta}{f'(f^{-1}(\zeta))}=e^{-2/3z}\int_{T_{2/3}\mathcal{C}_h}e^{-z\zeta}\frac{d\zeta}{f'(f^{-1}(\zeta+2/3))}. 
%%\end{align*}
%%
%%However we are interested in resurgence properties of $\tilde{I}(z)$, thus we take its Borel transform. 
\subsubsection{Comparison with Aaron}

The Airy integral can be written in terms of the modified Bessel equation as

\begin{equation}
Ai(x)=\frac{1}{\pi\sqrt{3}}x^{1/2}K(\frac{2}{3}x^{3/2}).
\end{equation}
On the other hand we have, for $z=x^{3/2}$
\begin{equation}
Ai(x)=-\frac{z^{1/3}}{2\pi i}I(z)=-\frac{1}{2\pi i}x^{1/2}I(x^{3/2}) 
\end{equation} 
hence
\begin{align*}
-\frac{1}{2\pi i}I(x^{3/2})&=\frac{1}{\pi\sqrt{3}}K(\frac{2}{3}x^{3/2})\\
\frac{i}{2} I(z)&=\frac{1}{\sqrt{3}}K(\frac{2}{3}z)
\end{align*}
In particular, the Borel trasforms of LHS and RHS\footnote{The conjugate variable of $z$ is $\zeta$, hence $\hat{K}(\frac{2}{3}z)=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta)$. Indeed assuming $K(z)=\sum_{n\geq 0}a_nz^{-n}$, the Borel transform of $K(\frac{2}{3}z)=\sum_{n\geq 0}a_n\left(\frac{3}{2}\right)^nz^{-n}$ is by definition \[\hat{K}(\frac{2}{3}z)=\sum_{k\geq 0}a_{n+1}\left(\frac{3}{2}\right)^{n+1}\frac{\zeta^n}{n!}=\frac{3}{2}\sum_{k\geq 0}\frac{a_{n+1}}{n!}\left(\frac{3}{2}\zeta\right)^{n}=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta). \]} must be equal, i.e.
\begin{align*}
\frac{i}{2} \hat{I}(\zeta)&=\frac{\sqrt{3}}{2}\hat{K}(\frac{3}{2}\zeta)\\
&= \frac{\sqrt{3}}{2}\frac{1}{\sqrt{2}}(\frac{3}{2}\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
&=\frac{\sqrt{3}}{2}(3\zeta-2)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
&=\frac{\sqrt{3}}{2}T_{-2/3}\left((3\zeta)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
&=\frac{1}{2}T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
\hat{I}(\zeta)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)
\end{align*} 
%%In addition, since $\hat{I}(\zeta)=C_3\partial_{\zeta,\text{based at } -2/3}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)$ is a solution of the Borel transform of equation \eqref{eq:I}; thus
%%\begin{align*}
%%C_3\partial_{\zeta,\text{based at } -2/3}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
%%C_3\partial_{\zeta}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)&=-i \frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)
%%\end{align*} 
%
%Equation 5 in Aaron is 
%\begin{equation}
%\left[\frac{\partial^2}{\partial z^2}+2\frac{\partial}{\partial z}+\frac{1}{z}\frac{\partial}{\partial z}+\frac{1}{z}-\frac{1}{9z^2}\right]\kappa=0
%\end{equation}
%Its Borel transform is 
%\begin{align*}
%&\zeta^2\hat{\kappa}-2\zeta\hat{\kappa}+1\ast(-\zeta\hat{\kappa}+\hat{\kappa})-\frac{1}{9}\zeta\ast\hat{\kappa}=0 \\
%&\zeta^2\hat{\kappa}-2\zeta\hat{\kappa}-\int_{0}^\zeta (s\hat{\kappa}(s)-\hat{\kappa}(s))ds-\frac{1}{9}\int_0^{\zeta}(\zeta-s)\hat{\kappa}(s)ds=0 \\
%&\, \text{ taking derivatives once} \\
%& 2\zeta\hat{\kappa}+\zeta^2\hat{\kappa}'-2\hat{\kappa}-2\zeta\hat{\kappa}'-\zeta\hat{\kappa}+\hat{\kappa}-\frac{1}{9}\int_0^{\zeta}\hat{k}(s)ds=0\\
%& \zeta\hat{\kappa}+\zeta^2\hat{\kappa}'-\hat{\kappa}-2\zeta\hat{\kappa}'-\frac{1}{9}\int_0^{\zeta}\hat{k}(s)ds=0\\
%&\, \text{ taking derivatives once again} \\
%& \hat{\kappa}+\zeta\hat{\kappa}'+2\zeta\hat{k}'+\zeta^2\hat{\kappa}''-\hat{\kappa}'-2\hat{\kappa}'-2\zeta\hat{\kappa}''-\frac{1}{9}\hat{\kappa}=0\\
%&(\zeta^2-2\zeta)\hat{\kappa}''+(3\zeta-3)\hat{k}'+\frac{8}{9}\hat{\kappa}=0
%\end{align*} 
%The last equation is a hypergeomtric equation and the fundamental solutions are (see DLMF 15.10.2) 
%\begin{equation}
%\hat{\kappa}_1(\zeta)={}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta}{2}\right)
%\end{equation}
%\begin{equation}
%\hat{\kappa}_2(\zeta)=\frac{1}{\sqrt{2}}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta}{2}\right)
%\end{equation}
%
%In particular, comparing with $\hat{I}(\zeta)$ we have 
%
%\begin{equation}
%\hat{I}\left(\frac{2}{3}\zeta\right)=-i\sqrt{3}\hat{\kappa}_2(\zeta-1)
%\end{equation}
%
%------------------------------------------------------------------------
%
%However, at pag. 5 in Aaron there is a different solution, namely 
%\begin{align*}
%\hat{\kappa}(\zeta-1)&=-i\sqrt{2}(\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)\\
%\hat{\kappa}(\zeta)&=-i\sqrt{2}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right)=-2i\frac{\cosh\left(\frac{2}{3}\mathrm{arcsinh}\left(\frac{\sqrt{\zeta}}{\sqrt{2}}\right)\right)}{\sqrt{\zeta}\sqrt{2+\zeta}}
%\end{align*} 
%------------------------------------------------------------------------
%
%
%As written by Aaron in Section 2.3, the asymptotic behvaior of $\kappa(z)$ is given by 
%\begin{equation}
%\kappa(z)\sim \left(\frac{\pi}{2z}\right)^{1/2}\sum_{n\geq 0}a_n(1/3)z^{-n}
%\end{equation}
%where $a_n(1/3)=\frac{(1/6)_n(5/6)_n}{(-2)^nn!}$. Hence the Borel transform of $\kappa(z)$ is
%\begin{align*}
%\hat{\kappa}(\zeta)&=\left(\frac{\pi}{2}\right)^{1/2}\sum_{n\geq 0}a_n(1/3)\frac{\zeta^{n-1/2}}{\Gamma(n+1/2)}\\
%&=\left(\frac{\pi}{2}\right)^{1/2}\sum_{n\geq 0}\frac{(1/6)_n(5/6)_n}{(-2)^nn!}\frac{\zeta^{n-1/2}}{\Gamma(n+1/2)}\\
%&=\frac{1}{\sqrt{2}}\zeta^{-1/2}\sum_{n\geq 0}\frac{(1/6)_n(5/6)_n}{(1/2)_nn!}\left(-\frac{\zeta}{2}\right)^n\\
%&=\frac{1}{\sqrt{2}}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6}\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right)
%\end{align*}
%\begin{align*}
%\hat{\kappa}(\zeta)&=\left(\frac{\pi}{2}\right)^{1/2}\mathcal{B}(z^{-1/2})\ast\left(\delta+\sum_{n\geq 0}a_{n+1}(1/3)\frac{\zeta^n}{n!}\right)=\frac{1}{\sqrt{2}}\zeta^{-1/2}\ast\left(\delta-\frac{5}{72}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\right)\\
%&=\frac{1}{\sqrt{2\zeta}}-\frac{5}{72\sqrt{2}}\int_0^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{s}{2}\right)ds\\
%&=\frac{1}{\sqrt{2\zeta}}+\frac{1}{\sqrt{2}}\int_0^{\zeta}(\zeta-s)^{-1/2}\frac{d}{ds}\left({}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{s}{2}\right)\right)ds\\
%&\textcolor{red}{=\frac{1}{\sqrt{2}}\partial_\zeta^{1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)}\, \textcolor{red}{\text{ is wrong!}}\\
%\end{align*}
%
%\subsubsection{Algebraic Hypergeometric}
%Aaron cliams 
%\begin{equation}
%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)=\textcolor{red}{-}\frac{1}{4u^2-1}\qquad \text{wtih } \zeta=-4u^3+3u
%\end{equation}
%\begin{proof}
%\begin{align*}
%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)&=\cos\left(\frac{1}{3}\arcsin(\zeta)\right)(1-\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
%&=\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin(\zeta)\\
%&=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
%&=\frac{1}{\cos(2y)-2\sin^2(y)} & \\
%&=\frac{1}{1-4\sin^2(y)} & \zeta=3\sin(y)-4\sin^3(y)
%\end{align*}
%Therefore, if $u\defeq\sin(y)$, we have $\zeta=-4u^3+3u$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)=\frac{1}{1-4u^2}=\frac{1}{3}\frac{1}{f'(u)}\]
%\end{proof}
%Now, we notice that 
%\begin{align*}
%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)&=2 {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+2 {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) & 15.8.27 \text{ DLMF} \\
%&=-{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta}{2}\right)-3\sqrt{3}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta}{2}\right)+ & 15.10.17 \text{DLMF}\\
%&\qquad -{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{\zeta}{2}\right)+3\sqrt{3}i\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right) & 15.10.17 \text{DLMF}\\
%&=-\hat{\kappa}_1(\zeta)-3\sqrt{6}\hat{\kappa}_2(\zeta)-\hat{\kappa}_1(-\zeta)+3\sqrt{6}\hat{\kappa}_2(-\zeta) \\
%&=-(\hat{\kappa}_1(\zeta)+\hat{\kappa}_1(-\zeta))-3\sqrt{6}
%\end{align*}
\end{example}

\begin{example}[Bessel]

Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and $\nu=\frac{dx}{x}$, then 
\begin{equation}
I(z)\defeq\int_0^{\infty}e^{-zf(x)}\frac{dx}{x}.
\end{equation}
By change of cooridnates $t=zx$
\begin{align*}
I(z)=\int_0^{\infty}e^{-z\left(\frac{t}{z}+\frac{z}{t}\right)}\frac{dt}{t}=\int_0^{\infty}e^{-\left(t+\frac{z^2}{t}\right)}\frac{dt}{t}=2K_0(2z) \,\qquad |\arg z|<\frac{\pi}{4}
\end{align*}
where $K_0(z)$ is the modified Bessel function (see definition 10.32.10 DLMF). In particular, since $K_0(z)$ solves 
\begin{equation}
\frac{d^2}{dz^2}w(z)+\frac{1}{z}\frac{d}{dz}w(z)-w(z)=0
\end{equation}
and $K_0(z)\sim\left(\frac{\pi}{2}\right)^{1/2}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{(1/2)_k(1/2)_k}{(-2)^kk!}z^{-k}$ as $z\to\infty$ (see DLMF 10.40.2), then $I(z)$ is a solution of 
\begin{equation}
\label{eq:IB}
\frac{d^2}{dz^2}I(z)+\frac{1}{z}\frac{d}{dz}I(z)-4I(z)=0.
\end{equation} 
The formal integral of \eqref{eq:IB} is given by a two parameter formal solution $\tilde{I}(z)$
\begin{equation}
\tilde{I}(z)=\sum_{\mathbf{k}\in\N^2}U^ke^{-\mathbf{k}\cdot\lambda z}z^{-\tau\cdot \mathbf{k}}\tilde{w}_{\mathbf{k}}(z)
\end{equation}
where $\lambda=(2,-2)$, $\tau=(-\frac{1}{2},-\frac{1}{2})$, $U^k:=U_1^{k_1}U_2^{k_2}$ with $k=(k_1,k_2)$ and $U_1,U_2\in\C$, and $\tilde{w}_{\mathbf{k}}(z)\in\C[[z^{-1}]]$ is a formal solution of 
\begin{multline}
\tilde{w}_{\mathbf{k}}''(z)-4(k_1-k_2)\tilde{w}_{\mathbf{k}}'(z)+4(1-(k_1-k_2)^2)\tilde{w}_{\mathbf{k}}(z)+\frac{(k_1+k_2-1)}{z}\tilde{w}_{\mathbf{k}}'(z)+\\
-2(k_1-k_2)\frac{(k_1+k_2-1)}{z}\tilde{w}_{\mathbf{k}}(z)+\frac{(k_1+k_2)^2}{4z^2}\tilde{w}_{\mathbf{k}}(z)=0
\end{multline}
The only non zero $\tilde{w}_{\mathbf{k}}(z)$ occurs for $\mathbf{k}=(1,0)$ and $\mathbf{k}=(0,1)$, hence 
\begin{equation}
\tilde{I}(z)=U_1 e^{-2z}z^{-1/2}\tilde{w}_{(1,0)}(z)+U_2e^{2z}z^{-1/2}\tilde{w}_{(0,1)}(z)
\end{equation}
and according to our convention, we define
\begin{align}
\label{IB+} &\tilde{I}_{1}(z)\defeq e^{-2z}z^{-1/2}\tilde{w}_{(1,0)}(z)\\
\label{IB-} &\tilde{I}_{-1}(z)\defeq e^{2z}z^{-1/2}\tilde{w}_{(0,1)}(z).
\end{align}
We set $\tilde{w}_{(1,0)}=\tilde{w}_+$ and $\tilde{w}_{(0,1)}=\tilde{w}_-$, then their Borel transforms are solutions respectively of the following equations 
\begin{align*}
(+)\quad &\zeta^2\hat{w}_+(\zeta)+4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0\\
(-)\quad &\zeta^2\hat{w}_+(\zeta)-4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0
\end{align*}
taking twice derivative in $\zeta$ we get
\begin{align*}
(+)\quad &(\zeta^2+4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_++4(\zeta-1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_+=0 &\\
(-)\quad &(\zeta^2-4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_-+4(\zeta+1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_-=0 &\\
(+)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_++(1-4\xi)\frac{d}{d\xi}\hat{w}_+-\frac{9}{4}\hat{w}_+=0 & \xi=-\frac{\zeta}{4} \\
(-)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_-+(1-4\xi)\frac{d}{d\xi}\hat{w}_--\frac{9}{4}\hat{w}_-=0 & \xi=\frac{\zeta}{4}
\end{align*}
therefore, since equation $(+), (-)$ are hypergeometric the fundamental solution is (see DLMF 15.10.2)
\begin{align}
\label{w+}&\hat{w}_+(\zeta)={}_2F_1\left(\frac{1}{2},\frac{1}{2};1;-\frac{\zeta}{4}\right)\\
\label{w+}&\hat{w}_-(\zeta)={}_2F_1\left(\frac{1}{2},\frac{1}{2};1;\frac{\zeta}{4}\right)
\end{align}
\end{example}

\end{document}

### 2022-01-10 airy-resurgence.tex
Add figures for contour argument

@@
 %%\usepackage{amsthm}
+\usepackage{graphicx}
 
@@
 Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$.
-If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\hat{\C}_{\Re(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
+If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
 If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
@@
 One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma_0} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
-where $\Gamma_0$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$. With the substitution $t = -2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{-y^{-1/2} \Gamma_0} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
+where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
+\begin{center}
+\includegraphics{figures/u_contour.pdf} \\[1em]
+{\small The contour $\Gamma$ in the $u$ plane.}
+\end{center}
+With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
@@
 where
-\[ K(z) = \frac{\sqrt{3}}{i} \int_{-z^{-1/3}\Gamma_0} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du. \]
+\begin{equation}\label{integral:mod-bessel}
+K(z) = \frac{\sqrt{3}}{i} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
@@
 \end{equation}
-\subsection{Going to the spatial domain}
+\subsection{Going to the spatial domain}\label{spatial}
 \subsubsection{A good try at $\zeta = 0$}
@@
 Unfortunately, this would force $\hat{K}$ to be zero.
-\subsubsection{Success at $\zeta = 1$}
+\subsubsection{Success at $\zeta = 1$}\label{spatial-success}
 Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. Since
@@
 \end{equation}
-%With the change of variable $\xi = \tfrac{1}{2}(1-\zeta)$, equation~\ref{eqn:spatial-mod-bessel} becomes the hypergeometric equation
 The hypergeometric function
-\[ \hat{f}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
+\[ \hat{g}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
 satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
@@
 \[ \hat{f}_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
-%%Using DLMF~15.10.13, we can see that
-%%\[ \hat{f}_0 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big). \]
-%%also satisies equation~\ref{eqn:hypergeom}.
-%%-------------------------------------------------------------
-%%By DLMF~15.10.17,
-%%\[ \hat{f}_0 = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{4}{3})}\;\xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) + \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}\;\hat{f}_1.
-\]
-%%The coefficients simplify to
-%%\begin{align*}
-%%\sqrt{\pi}\;\big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{2}{3} \pi)}{\pi} & = \frac{\sqrt{3}}{4} \\
-%%\big({-2}\sqrt{\pi}\big) \big(\tfrac{1}{2}\sqrt{\pi}\big)\;\frac{\sin(\tfrac{1}{6} \pi)}{\pi} & = -\frac{1}{2}
-%%\end{align*}
-%%respectively, giving
 Using the decay properties from Section~\ref{reg-decay}, we deduce that
@@
 \subsection{Contour argument}
-The hypergeometric function
-\[ F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
-satisfies equation~\ref{eqn:hypergeom} by definition. It has a singularity of type $(1 - \xi)^{-1/2}$ at $\xi = 1$, and continues holomorphically to the rest of $\hat{\C}$.
+We can recast integral~\ref{integral:mod-bessel} into $\hat{\C}$ by setting $\zeta = 4u^3 - 3u$.
+Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in $\hat{\C}$ and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
+\begin{equation}\label{integral:mod-bessel-zeta}
+K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+\end{equation}
+For $z \in (0, \infty)$, the contour $\gamma(z)$ runns clockwise around $[1, \infty)$, as shown below.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textbf{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{center}
+\includegraphics{figures/zeta_contour.pdf} \\[1em]
+{\small The contour $\gamma_1$ in $\hat{\C}$.}
+\end{center}
 
-Based on the calculations in the other sheet, we should have
-\[ K(z) = i \frac{2}{\sqrt{3}} \int_{\text{Hankel at } 1} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This is because the hypergeometric function in the integrand happens to be algebraic. It can be expressed in terms of Legendre functions and rearranged to get
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \frac{1}{4u^2 - 1} \]
-with $\zeta = -4u^3 + 3u$.
+It happens\footnote{How to verify this? This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.} that for our desired branch of $u$,
+\[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
+so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
+\[ K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
 
-The quadratic transformation identity DLMF~15.8.27 then shows that
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) \propto F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big), \]
+In addition to the solutions $\hat{g}_1$ and $\hat{f}_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
+\begin{alignat*}{2}
+\hat{g}_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
+\hat{f}_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
+\end{alignat*}
+given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}. These four solutions are related by identities 15.10.18, and 15.10.22 from \cite{dlmf}:
+\begin{alignat*}{3}
+\hat{f}_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,\hat{g}_1 &\;+\;& \tfrac{1}{2}\,\hat{f}_0 \\
+\hat{f}_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,\hat{g}_0 &\;+\;& \tfrac{1}{2}\,\hat{f}_1.
+\end{alignat*}
+Summing these identities, we see that
+\[ \hat{g}_1 + \hat{g}_0 = \tfrac{\sqrt{3}}{2}\,(\hat{f}_1 + \hat{f}_0). \]
+
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+\begin{align*}
+F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) & = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0) \\
+& = \tfrac{1}{2\sqrt{3}}(\hat{f}_1 + \hat{f}_0)
+\end{align*}
 so we have
-\[ K(z) \propto \int_{\text{Hankel at } 1} e^{-z\zeta} \big[F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) + F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\big]\;d\zeta. \]
-The first term in the integrand is regular on $\zeta \in [1, \infty)$, so it integrates to zero.
-The second term looks like $(1 - \zeta)^{-1/2}$ times a function which is regular for $\zeta \in [1, \infty)$, so integrating it along a Hankel contour is the same as integrating it times two times a direct contour, with its value continued from below the singularity.
+\[ K(z) = \frac{1}{6i} \int_{\gamma_z} e^{-z\zeta} (\hat{f}_1 + \hat{f}_0)\;d\zeta. \]
+The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero.
+The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it negative-twice along the contour that goes rightward from $1$, with its value continued from above the singularity.
 Hence,
-\[ K(z) \propto \int^\infty_1 e^{-z\zeta} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)\;d\zeta. \]
-With $\zeta = 1 + \tilde{\zeta}$, we get $1 - \xi = 1 + \tfrac{1}{2} \tilde{\zeta}$, so
 \begin{align*}
-K(z) & = \int^\infty_0 e^{-z(1 + \tilde{\zeta})} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta} \\
-e^z K(z) & = \int^\infty_0 e^{-z\tilde{\zeta}} F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)\;d\tilde{\zeta}
+K(z) & = \frac{i}{3} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
+& = \tfrac{i}{3} \laplace_{\zeta_1} \hat{f}_0.
 \end{align*}
-In other words, $\kappa(z) = e^z K(z)$ is the Laplace transform of $\hat{\kappa}(\tilde{\zeta}) = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1 + \tfrac{1}{2}\tilde{\zeta}\big)$.
-We've confirmed numerically that $\hat{\kappa}(\tilde{\zeta})$ seems to have a singularity of type $\tilde{\zeta}^{-1/2}$ at $\tilde{\zeta} = 0$, as expected.
-\textbf{Can we see this analytically?}
-
-Using the DLMF identities 15.10.12 and 15.10.14, we can see that the functions
-\begin{align*}
-\xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big) \\
-(1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big)
-\end{align*}
-also satisfy equation~\ref{eqn:hypergeom}. Numerically, these functions appear to sum to a constant multiple of $F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)$.
+\textbf{[Constant conflicts with Section~\ref{spatial}]}
 \subsection{Correspondence with Mari\~{n}o's series}

### 2022-01-10 figures/contours.jl

@@ -1,0 +1,56 @@
+using Compose, Colors
+import Cairo, Fontconfig
+
+# === paths ===
+
+u_path(t) = -(0.02 + im*t)^(2/3)
+
+ζ(u) = 4u^3 - 3u
+
+# === plots ===
+
+function arrowhead(curve, time, size, color, eps = 1e-3)
+  place = curve(time)
+  dir = angle(conj(curve(time + eps) - curve(time - eps)))
+  ctx = context(
+    real(place)*cx - size, imag(place)*cy - size, 2size, 2size,
+    units = UnitBox(-1, -1, 2, 2),
+    rotation = Rotation(dir, 0, 0)
+  )
+  return compose(ctx,
+    polygon([(0.6, 0), (-0.7, 0.7), (-0.4, 0), (-0.7, -0.7)]),
+    fill(color)
+  )
+end
+
+u_window = context(units = UnitBox(-1, -1, 2, 2), mirror = Mirror(0, 0, 0))
+u_frame = compose(context(),
+  line([(-1, 0), (1, 0)]),
+  line([(-1/sqrt(3), -1), (1/sqrt(3), 1)]),
+  line([(1/sqrt(3), -1), (-1/sqrt(3), 1)]),
+  linewidth(1w/300), stroke(Gray(0.6))
+)
+u_contour = compose(u_window,
+  (context(), circle(-0.25, 0, 0.015w), fill("orangered")),
+  arrowhead(u_path, 0.5, 0.04w, "black"),
+  (context(), line(reim.([u_path(t^3) for t in LinRange(-1.09, 1.09, 60)])), stroke("black")),
+  u_frame
+)
+
+ζ_window = context(units = UnitBox(-6, -6, 12, 12), mirror = Mirror(0, 0, 0))
+ζ_frame = compose(context(),
+  line([(-6, 0), (6, 0)]),
+  line([(0, -6), (0, 6)]),
+  linewidth(1w/300), stroke(Gray(0.6))
+)
+ζ_contour = compose(ζ_window,
+  (context(), circle(ζ(-0.25), 0, 0.015w), fill("orangered")),
+  arrowhead(t -> ζ(u_path(t)), 0.7, 0.04w, "black"),
+  (context(), line(reim.(ζ.([u_path(sign(t)*t^2) for t in LinRange(-1.03, 1.03, 60)]))), stroke("black")),
+  ζ_frame
+)
+
+# === output ===
+
[…]

### 2022-01-10 draft2.tex

@@
 
-and computitng the integral which defines the $n+\alpha$-derivative we get exaclty the same result as \eqref{mod2}.
+and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
 
@@
 \begin{equation}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n}.
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
 \end{equation}
+where $\mathcal{C}_\alpha$ is a steepest descendet oath through the critical point $x_\alpha$. 
 \begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$
@@
 \begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-N/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-N/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-1/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
 \end{multline} 
@@
 \begin{proof}
+Part $(1)$:
+
+Part $(2)$: \begin{align*}
+\hat{\varphi}_\alpha(\zeta)=\mathcal{B}(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n})(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
+\end{align*}
+Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
+
 Part $(3)$: thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
@@
 
-Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and $\nu=\frac{dx}{x}$, then 
+Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and $\nu=\frac{dx}{x}$, then the ciritcal points of $f$ are $x=\pm1$ and 
 \begin{equation}
@@
 \end{equation}
+
 By change of cooridnates $t=zx$
@@
 \end{equation} 
-The formal integral of \eqref{eq:IB} is given by a two parameter formal solution $\tilde{I}(z)$
+The formal integral of \eqref{eq:IB} is given by a two parameter formal solution $\tilde{I}_1(z)$
 \begin{equation}
@@
 \begin{align}
-\label{w+}&\hat{w}_+(\zeta)={}_2F_1\left(\frac{1}{2},\frac{1}{2};1;-\frac{\zeta}{4}\right)\\
-\label{w+}&\hat{w}_-(\zeta)={}_2F_1\left(\frac{1}{2},\frac{1}{2};1;\frac{\zeta}{4}\right)
+\label{w+}&\hat{w}_+(\zeta)={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
+\label{w+}&\hat{w}_-(\zeta)={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
 \end{align}
+In particular, we notice that taking the series expansion of $\hat{w}_+$ and $\hat{w}_-$ we get numerically that
+\begin{align*}
+\hat{w}_+(\zeta-4)=\frac{1}{\pi}\log(z)\hat{w}_-(z)+\phi_{\text{reg}}\\
+\hat{w}_-(\zeta+4)=\frac{1}{\pi}\log(z)\hat{w}_+(z)+\psi_{\text{reg}}
+\end{align*}
+and analytically (thanks to 15.2.3 DLMF)
+\begin{align*}
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}+i0\right)-{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}-i0\right) &\qquad\zeta<-4\\
+&=-8i\left(-\frac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}+1\right)^n\\
+&=8i\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}+1\right)^{n-1} & \\
+&=8i\sum_{n\geq 0}\frac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(\frac{\zeta}{4}+1\right)^{n} &\\
+&=\mathbf{2i}\sum_{n\geq 0}\frac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(\frac{\zeta}{4}+1\right)^{n} & \\
+&=\mathbf{2i}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}+1\right)
+\end{align*}
+\begin{align*}
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}+i0\right)-{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}-i0\right)& \qquad\zeta>4\\
+&=8i\left(\frac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}-1\right)^n\\
+&=-8i\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(1-\frac{\zeta}{4}\right)^{n-1}\\
+&=-8i\sum_{n\geq 0}(-1)^n\frac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(1-\frac{\zeta}{4}\right)^{n}\\
+&=\mathbf{-2i}\sum_{n\geq 0}(-1)^n\frac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(1-\frac{\zeta}{4}\right)^{n}\\
+&=\mathbf{-2i}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;1-\frac{\zeta}{4}\right)
+\end{align*}
+These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.
+
+\begin{lemma}
+The following identity holds true
+\begin{equation}
+{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}\qquad \qquad \zeta=u+\frac{1}{u}
+\end{equation}
+\end{lemma}
+\begin{proof}
+From 15.4.13 DLMF, we have
+\begin{align*}
+{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)&=\frac{2}{\sqrt{4-\zeta^2}} & y=\mathrm{arccsc}(\zeta/2)\\
+&=\frac{1}{\sqrt{1-\mathrm{csc}^2(y)}} & \\
+&=-i\tan(y) &   \zeta=\frac{2}{\sin(y)}
+\end{align*}
+therefore if $u=\tan\left(\frac{y}{2}\right)$, we have $\zeta=\frac{1+u^2}{u}=f(u)$ and 
+\begin{equation*}
+{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}=\frac{2i}{f'(u)u}
+\end{equation*}  
+\end{proof}
+
+\begin{claim}
+\label{Bessel}
+\begin{equation}
+\hat{w}_{+}(\zeta-2)=i\pi\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'
+\end{equation}
+\end{claim}
+\begin{proof}
+Let us first consider the RHS of \eqref{Bessel}
+\begin{align*}
+2\pi\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'&= \frac{4}{3}\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]\\
+&=
+\end{align*}
+\end{proof}
+
 \end{example}
 
+\textcolor{red}{We should check that for Hypergeomtric function the following relation holds true
+\[{}_2F_1(a,b;c;z)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a-\frac{1}{2},b-\frac{1}{2};c-\frac{1}{2};1-t\right)-{}_2F_1\left(a-\frac{1}{2},b-\frac{1}{2};c-\frac{1}{2};1+t\right)\right]dt\]
+}
+
 \end{document}

### 2022-01-10 draft2.tex
update computations
Update computations

@@
 \begin{equation}
-\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
+\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
 \end{equation}
@@
 \begin{equation}
-\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds
+\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
 \end{equation}
@@
 \begin{align*}
-&\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
-&= -\frac{2}{9}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right)ds+\frac{2}{9}\int_{-2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right)ds & 15.8.28 \text{ DLMF} \\
-&=-\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};t\right)dt+\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt & \zeta'=\frac{1}{2}-\frac{3}{4}\zeta\\
-&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt -\frac{9i}{32}\textcolor{gray}{\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};-\frac{1}{2};1-t\right)dt}& 15.10.21 \text{ DLMF }\\
-&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{5}{2};1-t\right)t^{-3/2}dt &  15.10.13 \text{ DLMF }
+&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
+&= -\frac{2}{9}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right)ds+\frac{2}{9}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right)ds & 15.8.28 \text{ DLMF} \\
+&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1+y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)\right]dy & x\in (-\infty,0) \\
+&=-\frac{\sqrt{3\pi}}{4}\Gamma(1/6)e^{-\frac{3}{2}\pi i}\int_0^x(x-y)^{-1/2}y^{-5/3}{}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)dy & \\
+&=-\frac{\sqrt{3}\pi}{4}\frac{\Gamma(1/6)\Gamma(7/6)}{\Gamma(5/3)}e^{-\frac{3}{2}\pi i} |x|^{-7/6}{}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) & \eqref{4.8} \\
+&=\frac{5\pi^2}{24\sqrt{3}}\frac{\Gamma(1/3)}{\Gamma(5/3)}\left({}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{\zeta}{4}\right)-e^{-\frac{11}{6}\pi i}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in (2/3,+\infty)
+%&=-\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};t\right)dt+\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt & \zeta'=\frac{1}{2}-\frac{3}{4}\zeta\\
+%&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt -\frac{9i}{32}\textcolor{gray}{\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};-\frac{1}{2};1-t\right)dt}& 15.10.21 \text{ DLMF }\\
+%&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{5}{2};1-t\right)t^{-3/2}dt &  15.10.13 \text{ DLMF }
 \end{align*}
-
+however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$. 
 %By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
@@
 %%However we are interested in resurgence properties of $\tilde{I}(z)$, thus we take its Borel transform. 
-\subsubsection{Comparison with Aaron}
-
-The Airy integral can be written in terms of the modified Bessel equation as
-
-\begin{equation}
-Ai(x)=\frac{1}{\pi\sqrt{3}}x^{1/2}K(\frac{2}{3}x^{3/2}).
-\end{equation}
-On the other hand we have, for $z=x^{3/2}$
-\begin{equation}
-Ai(x)=-\frac{z^{1/3}}{2\pi i}I(z)=-\frac{1}{2\pi i}x^{1/2}I(x^{3/2}) 
-\end{equation} 
-hence
-\begin{align*}
--\frac{1}{2\pi i}I(x^{3/2})&=\frac{1}{\pi\sqrt{3}}K(\frac{2}{3}x^{3/2})\\
-\frac{i}{2} I(z)&=\frac{1}{\sqrt{3}}K(\frac{2}{3}z)
-\end{align*}
-In particular, the Borel trasforms of LHS and RHS\footnote{The conjugate variable of $z$ is $\zeta$, hence $\hat{K}(\frac{2}{3}z)=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta)$.
+%\subsubsection{Comparison with Aaron}
+%
+%The Airy integral can be written in terms of the modified Bessel equation as  
+%
+%\begin{equation}
+%Ai(x)=\frac{1}{\pi\sqrt{3}}x^{1/2}K(\frac{2}{3}x^{3/2}).
+%\end{equation}
+%On the other hand we have, for $z=x^{3/2}$
+%\begin{equation}
+%Ai(x)=-\frac{z^{1/3}}{2\pi i}I(z)=-\frac{1}{2\pi i}x^{1/2}I(x^{3/2}) 
+%\end{equation} 
+%hence
+%\begin{align*}
+%-\frac{1}{2\pi i}I(x^{3/2})&=\frac{1}{\pi\sqrt{3}}K(\frac{2}{3}x^{3/2})\\
+%\frac{i}{2} I(z)&=\frac{1}{\sqrt{3}}K(\frac{2}{3}z)
+%\end{align*}
+%In particular, the Borel trasforms of LHS and RHS\footnote{The conjugate variable of $z$ is $\zeta$, hence $\hat{K}(\frac{2}{3}z)=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta)$.
 Indeed assuming $K(z)=\sum_{n\geq 0}a_nz^{-n}$, the Borel transform of $K(\frac{2}{3}z)=\sum_{n\geq 0}a_n\left(\frac{3}{2}\right)^nz^{-n}$ is by definition \[\hat{K}(\frac{2}{3}z)=\sum_{k\geq 0}a_{n+1}\left(\frac{3}{2}\right)^{n+1}\frac{\zeta^n}{n!}=\frac{3}{2}\sum_{k\geq 0}\frac{a_{n+1}}{n!}\left(\frac{3}{2}\zeta\right)^{n}=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta).
 \]} must be equal, i.e.
-\begin{align*}
-\frac{i}{2} \hat{I}(\zeta)&=\frac{\sqrt{3}}{2}\hat{K}(\frac{3}{2}\zeta)\\
-&= \frac{\sqrt{3}}{2}\frac{1}{\sqrt{2}}(\frac{3}{2}\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
-&=\frac{\sqrt{3}}{2}(3\zeta-2)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
-&=\frac{\sqrt{3}}{2}T_{-2/3}\left((3\zeta)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
-&=\frac{1}{2}T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
-\hat{I}(\zeta)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)
-\end{align*} 
+%\begin{align*}
+%\frac{i}{2} \hat{I}(\zeta)&=\frac{\sqrt{3}}{2}\hat{K}(\frac{3}{2}\zeta)\\
+%&= \frac{\sqrt{3}}{2}\frac{1}{\sqrt{2}}(\frac{3}{2}\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
+%&=\frac{\sqrt{3}}{2}(3\zeta-2)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
+%&=\frac{\sqrt{3}}{2}T_{-2/3}\left((3\zeta)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
+%&=\frac{1}{2}T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
+%\hat{I}(\zeta)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)
+%\end{align*}
+
 %%In addition, since $\hat{I}(\zeta)=C_3\partial_{\zeta,\text{based at } -2/3}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)$ is a solution of the Borel transform of equation \eqref{eq:I}; thus
@@
 \begin{equation}
-\hat{w}_{+}(\zeta-2)=i\pi\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'
+\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
 \end{equation}
@@
 \begin{align*}
-2\pi\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'&= \frac{4}{3}\int_{-2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]\\
-&=
+&2\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'= &\\
+&\quad = \frac{4}{3}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' &\\
+&\quad =\frac{8}{3}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};y\right)-{}_2F_1\left(2,2;\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0)\\
+&\quad =2\pi\int_0^x(x-y)^{-1/2}y^{-2}F\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \eqref{4.8} \\
+&\quad =\pi^2|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & x\in (-\infty, 0)\\
+&\quad =\frac{\pi^2}{2}\left({}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}-\frac{\zeta}{4}\right)-i{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in(2,+\infty)
 \end{align*}
+however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$. 
 \end{proof}
@@
 
-\textcolor{red}{We should check that for Hypergeomtric function the following relation holds true
-\[{}_2F_1(a,b;c;z)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a-\frac{1}{2},b-\frac{1}{2};c-\frac{1}{2};1-t\right)-{}_2F_1\left(a-\frac{1}{2},b-\frac{1}{2};c-\frac{1}{2};1+t\right)\right]dt\]
-}
+\section{Useful identities for Gauss hypergeomtric functions}
+
+\begin{multline}
+\label{w1w3w5}
+{}_2F_1\left(a,b;c;z\right)=e^{b\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(a+b-c+1)\Gamma(c-b)}{}_2F_1\left(a,b;c;1-z\right)+\\
+-e^{(a+b-c)\pi i}\frac{\Gamma(c)\Gamma(a-c+1)}{\Gamma(b)\Gamma(a-b+1)}|z|^{-a}{}_2F_1\left(a,a-c+1;a-b+1;\frac{1}{z}\right)
+\end{multline}
+
+\begin{multline}
+\label{4.5}
+\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
+x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
+\end{multline}
+which can be rewritten as 
+\begin{multline}
+\label{4.8}
+\int_{y>x}|y|^{-a}|x-y|^{\mu-1}{}_2F_1\left(a,b;c;y^{-1}\right)dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{-a+\mu}{}_2F_1\left(a-\mu,b;c;x^{-1}\right)\\
+x\in(-\infty,0)\cup(1,\infty), \, \Re a>\Re\mu>0
+\end{multline}
+%\textcolor{red}{We should check that for Hypergeomtric functions the following relation holds true
+%\[{}_2F_1(a,b;c;z-1)\propto\int_1^z(z-t)^{-1/2}\left[{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};1-t\right)-{}_2F_1\left(a+\frac{1}{2},b+\frac{1}{2};c+\frac{1}{2};t\right)\right]dt\]
+%}
+%
+%The following identities hold true
+%\begin{multline}
+%\label{a+b+c+}
+%\int_{0<\frac{y}{x}<1}|y|^{c-1}(1-y)^{a+b-c}{}_2F_1\left(a,b;c;y\right)\frac{|x-y|^{\mu-1}}{\Gamma(\mu)}dy=\\
+%\frac{\Gamma(c)}{\Gamma(c+\mu)}|x|^{c-1+\mu}(1-x)^{a+b-c+\mu}{}_2F_1\left(a+\mu,b+\mu;c+\mu;x\right)\\
+% x\in (-\infty,0)\cup(0,1), \,\Re c>0,\,\Re\mu>0
+%\end{multline}
+%
+%\begin{multline}\label{a-b-c-}
+%\int_{-\infty}^x{}_2F_1\left(a,b;c;y\right) (x-y)^{\mu-1}dy=\Gamma(\mu)\frac{\Gamma(a-\mu)}{\Gamma(a)}\frac{\Gamma(b-\mu)}{\Gamma(b)}\frac{\Gamma(c)}{\Gamma(c-\mu)}{}_2F_1\left(a-\mu,b-\mu;c-\mu;x\right)\\
+%x<1, \Re a,\Re b>\Re\mu>0
+%\end{multline}
 

### 2022-01-12 airy-resurgence.tex
Add notes from 10 Jan conversation

@@
 
-It happens\footnote{How to verify this? This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.} that for our desired branch of $u$,
+It happens\footnote{How to verify this?
+This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.
+\textbf{Veronica:} Look at ``Special cases'' section in \cite{dlmf}, e.g.
+15.4.14!} that for our desired branch of $u$,
 \[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
@@
 
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textbf{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
 \begin{align*}

### 2022-01-13 figures/contours.jl
Spruce up contour figures

@@ -3,7 +3,7 @@ import Cairo, Fontconfig
 
 # === paths ===
 
-u_path(t) = -(0.02 + im*t)^(2/3)
+u_path(t) = 1/6 * cosh(2/3*π*im - t)
 
 ζ(u) = 4u^3 - 3u
 
@@ -32,8 +32,8 @@ u_frame = compose(context(),
 )
 u_contour = compose(u_window,
   (context(), circle(-0.25, 0, 0.015w), fill("orangered")),
-  arrowhead(u_path, 0.5, 0.04w, "black"),
-  (context(), line(reim.([u_path(t^3) for t in LinRange(-1.09, 1.09, 60)])), stroke("black")),
+  arrowhead(u_path, 2.1, 0.04w, "black"),
+  (context(), line(reim.([u_path(t) for t in LinRange(-2.65, 2.65, 60)])), stroke("black")),
   u_frame
 )
 
@@ -45,8 +45,8 @@ u_contour = compose(u_window,
 )
 ζ_contour = compose(ζ_window,
   (context(), circle(ζ(-0.25), 0, 0.015w), fill("orangered")),
-  arrowhead(t -> ζ(u_path(t)), 0.7, 0.04w, "black"),
-  (context(), line(reim.(ζ.([u_path(sign(t)*t^2) for t in LinRange(-1.03, 1.03, 60)]))), stroke("black")),
+  arrowhead(t -> ζ(u_path(t)), 2.2, 0.04w, "black"),
+  (context(), line(reim.(ζ.([u_path(t) for t in LinRange(-2.53, 2.53, 60)]))), stroke("black")),
   ζ_frame
 )
 

### 2022-01-13 airy-resurgence.tex
Check results numerically
Confirmed:
- The u-plane integral for K
- The zeta-plane integral in terms of F(1/3, 2/3, 1/2, zeta^2)
- The expression for K-hat in "Going to the spatial domain"

Inconsistent:
- The zeta-plane integral in terms of f0_hat only.

@@
 One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
+\[ \Ai(y) = \frac{i}{2\pi} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
 where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = y^{1/2}\;\frac{i}{\pi} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
@@
 \begin{equation}\label{integral:mod-bessel}
-K(z) = \frac{\sqrt{3}}{i} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
 \end{equation}
@@
 \begin{equation}\label{integral:mod-bessel-zeta}
-K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+K(z) = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
 \end{equation}
-For $z \in (0, \infty)$, the contour $\gamma(z)$ runns clockwise around $[1, \infty)$, as shown below.
+For $z \in (0, \infty)$, the contour $\gamma(z)$ runs clockwise around $[1, \infty)$, as shown below.
 Let's assume $z \in (0, \infty)$ for the rest of the section.
@@
 15.4.14!} that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
+\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
 so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
@@
 The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it negative-twice along the contour that goes rightward from $1$, with its value continued from above the singularity.
+\textbf{[This doesn't hold up numerically!]} The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it twice along the contour that goes rightward from $1$, with its value continued from above the singularity.
 Hence,
 \begin{align*}
-K(z) & = \frac{i}{3} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
-& = \tfrac{i}{3} \laplace_{\zeta_1} \hat{f}_0.
+K(z) & = \frac{1}{3i} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
+& = \tfrac{1}{3i} \laplace_{\zeta_1} \hat{f}_0.
 \end{align*}

### 2022-01-13 figures/contours.jl

@@ -1,17 +1,35 @@
+# for plots
 using Compose, Colors
 import Cairo, Fontconfig
+
+# for integral checks
+using QuadGK, SpecialFunctions, HypergeometricFunctions
+import Plots
 
 # === paths ===
 
 u_path(t) = 1/6 * cosh(2/3*π*im - t)
+u_jet(t) = (u_path(t), -1/6 * sinh(2/3*pi*im - t))
 
-ζ(u) = 4u^3 - 3u
+function ζ(u)
+  if length(u) == 1
+    return 4u^3 - 3u
+  else
+    return (4u[1]^3 - 3u[1], 3*(4u[1]^2 - 1)*u[2])
+  end
+end
 
 # === plots ===
 
-function arrowhead(curve, time, size, color, eps = 1e-3)
-  place = curve(time)
-  dir = angle(conj(curve(time + eps) - curve(time - eps)))
+function arrowhead(curve, time, size, color; eps = 1e-3)
+  jet = curve(time)
+  if length(jet) == 1
+    place = jet
+    dir = angle(conj(curve(time + eps) - curve(time - eps)))
+  else
+    place = jet[1]
+    dir = angle(conj(jet[2]))
+  end
   ctx = context(
     real(place)*cx - size, imag(place)*cy - size, 2size, 2size,
     units = UnitBox(-1, -1, 2, 2),
@@ -23,34 +41,98 @@ function arrowhead(curve, time, size, color, eps = 1e-3)
   )
 end
 
-u_window = context(units = UnitBox(-1, -1, 2, 2), mirror = Mirror(0, 0, 0))
-u_frame = compose(context(),
-  line([(-1, 0), (1, 0)]),
-  line([(-1/sqrt(3), -1), (1/sqrt(3), 1)]),
-  line([(1/sqrt(3), -1), (-1/sqrt(3), 1)]),
-  linewidth(1w/300), stroke(Gray(0.6))
-)
-u_contour = compose(u_window,
-  (context(), circle(-0.25, 0, 0.015w), fill("orangered")),
-  arrowhead(u_path, 2.1, 0.04w, "black"),
[…]

### 2022-01-14 airy-resurgence.tex
Finally get the contour argument right!
Add drawing code for other contours. Show both poles of du/dζ in
the figures. Sketch how our two ways of solving the frequency-domain
equation are associated with two bases of solutions for the spatial-
domain equation.

@@
 Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
-Comparing with series~\ref{bessel-asymp}, we see that $\kappa = i\,\tfrac{1}{2}\,f_0$.
+Comparing with series~\ref{bessel-asymp}, we see that $\kappa = \tfrac{i}{2}\,f_0$.
 We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
@@
 \section{Sketches}
-\subsection{Contour argument}
+\subsection{Contour argument}\label{contour-argument}
 We can recast integral~\ref{integral:mod-bessel} into $\hat{\C}$ by setting $\zeta = 4u^3 - 3u$.
@@
 \begin{equation}\label{integral:mod-bessel-zeta}
-K(z) = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
 \end{equation}
-For $z \in (0, \infty)$, the contour $\gamma(z)$ runs clockwise around $[1, \infty)$, as shown below.
+For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
 Let's assume $z \in (0, \infty)$ for the rest of the section.
@@
 so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
-\[ K(z) = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
 This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
@@
 \end{alignat*}
-given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}. These four solutions are related by identities 15.10.18, and 15.10.22 from \cite{dlmf}:
+given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}.
+
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textbf{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0), \]
+so we have
+\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (\hat{g}_1 + \hat{g}_0)\;d\zeta. \]
+The solution $\hat{g}_1$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
+The solution $\hat{g}_0$, in contrast, is non-meromorphic at $\zeta = 1$.
+Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,\hat{f}_0$,
+as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
+Hence,
+\begin{align*}
+K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
+e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} \hat{f}_0\;d\zeta \\
+\kappa & = \tfrac{i}{2} \laplace_{\zeta_1} \hat{f}_0,
+\end{align*}
+just as we found in Section~\ref{spatial-success}.
+\subsection{Another solution}
+Section~\ref{contour-argument} associates the solution $K$ of equation~\ref{eqn:mod-bessel} with the solution $\hat{g}_0$ of equation~\ref{eqn:hypergeom}, which contributes the pole at $\zeta = 1$ of
+\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0). \]
+The solution $\hat{g}_1$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+
+To express this other solution as a Laplace transform, following the method of Section~\ref{spatial-success}, we would use the solution
+\[ \hat{f}_1 = (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
+of equation~\ref{eqn:hypergeom}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
+
+In summary, the contour integration method of solving equation~\ref{eqn:mod-bessel} is associated with the basis
+\begin{align*}
+\hat{g}_1 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
+\hat{g}_0 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
+\end{align*}
+of solutions for equation~\ref{eqn:hypergeom}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
+These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
+
+The Laplace transformation method of solving equation~\ref{eqn:mod-bessel}, on the other hand, is associated with the basis
+\begin{alignat*}{2}
+\hat{f}_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
+\hat{f}_0 &\;=\:& \xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
+\end{alignat*}
+given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
+
+Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
 \begin{alignat*}{3}
@@
 Summing these identities, we see that
-\[ \hat{g}_1 + \hat{g}_0 = \tfrac{\sqrt{3}}{2}\,(\hat{f}_1 + \hat{f}_0). \]
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textbf{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\begin{align*}
-F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) & = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0) \\
-& = \tfrac{1}{2\sqrt{3}}(\hat{f}_1 + \hat{f}_0)
-\end{align*}
-so we have
-\[ K(z) = \frac{1}{6i} \int_{\gamma_z} e^{-z\zeta} (\hat{f}_1 + \hat{f}_0)\;d\zeta. \]
-The solution $\hat{f}_1$ is regular on $\zeta \in [1, \infty)$, so it integrates to zero.
-\textbf{[This doesn't hold up numerically!]} The solution $\hat{f}_0$ looks like $(1 - \zeta)^{-1/2}$ times a function which is regular on $\zeta \in [1, \infty)$, so integrating it along $\gamma_z$ is the same as integrating it twice along the contour that goes rightward from $1$, with its value continued from above the singularity.
-Hence,
-\begin{align*}
-K(z) & = \frac{1}{3i} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
-& = \tfrac{1}{3i} \laplace_{\zeta_1} \hat{f}_0.
-\end{align*}
-\textbf{[Constant conflicts with Section~\ref{spatial}]}
+\[ \hat{g}_1 + \hat{g}_0 = \tfrac{\sqrt{3}}{2}\,(\hat{f}_1 + \hat{f}_0), \]
+giving the alternate decomposition
+\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(\hat{f}_1 + \hat{f}_0). \]
 \subsection{Correspondence with Mari\~{n}o's series}

### 2022-01-14 figures/contours.jl

@@ -1,5 +1,7 @@
+module Contours
+
 # for plots
-using Compose, Colors
+using Compose, Colors, Roots
 import Cairo, Fontconfig
 
 # for integral checks
@@ -8,8 +10,8 @@ import Plots
 
 # === paths ===
 
-u_path(t) = 1/6 * cosh(2/3*π*im - t)
-u_jet(t) = (u_path(t), -1/6 * sinh(2/3*pi*im - t))
+u_path(θ, off) = t -> 1/6 * exp(-im*θ/3) * (cosh(2/3*π*im - t) - off*exp(2/3*π*im))
+u_jet(θ, off) = t -> (u_path(θ, off)(t), -1/6 * exp(-im*θ/3) * sinh(2/3*π*im - t))
 
 function ζ(u)
   if length(u) == 1
@@ -41,7 +43,15 @@ function arrowhead(curve, time, size, color; eps = 1e-3)
   )
 end
 
-function plotcontours()
+taxinorm(z) = max(abs(real(z)), abs(imag(z)))
+
+# for a nice contour with θ at π or 4π, set `off` to 1.6
+function plotcontours(θ = 0, off = 0)
+  dark = RGB(0, 0.5, 0.7)
+  light = RGB(0.6, 0.9, 1.0)
+  
+  u_range = [find_zero(t -> taxinorm(u_path(θ, off)(t)) - 1.01, search, Bisection()) for search in [(-3, 0), (0, 3)]]
+  u_mark = find_zero(t -> taxinorm(u_path(θ, off)(t)) - 0.5, (0, 3), Bisection())
   u_window = context(units = UnitBox(-1, -1, 2, 2), mirror = Mirror(0, 0, 0))
   u_frame = compose(context(),
     line([(-1, 0), (1, 0)]),
@@ -50,12 +60,15 @@ function plotcontours()
     linewidth(1w/300), stroke(Gray(0.6))
   )
   u_contour = compose(u_window,
-    (context(), circle(-0.25, 0, 0.015w), fill("orangered")),
-    arrowhead(u_jet, 2.1, 0.04w, "black"),
-    (context(), line(reim.([u_path(t) for t in LinRange(-2.65, 2.65, 60)])), stroke("black")),
[…]

### 2022-01-18 airy-resurgence.tex
Start contour argument for other modified Bessel functions

@@
 We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\, K\big(\tfrac{2}{3} y^{3/2}\big), \]
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
 where
@@
 
-It happens\footnote{How to verify this?
-This hypergeometric function can be written in terms of Legendre functions, but I don't know where to go from there.
-\textbf{Veronica:} Look at ``Special cases'' section in \cite{dlmf}, e.g.
-15.4.14!} that for our desired branch of $u$,
+It happens\footnote{\textbf{Veronica:} This comes from \cite[equation~15.4.14]{dlmf}.} that for our desired branch of $u$,
 \[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]

### 2022-01-18 draft2.tex
Add notes from 10 Jan conversation
add part 1 in the proof

@@
 where $\mathcal{C}_\alpha$ is a steepest descendet oath through the critical point $x_\alpha$. 
-\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$
+\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$
 \begin{enumerate}
@@
 \begin{proof}
-Part $(1)$:
+Part $(1)$: Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
+By the steepest descendet method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
+\begin{align*}
+I_\alpha(\zeta)&\sim e^{-zf(x_\alpha)}\int_{-\varepsilon}^{\varepsilon}\sum_{n\geq 0}t^{2n}b_{2n}^{\alpha}e^{-zf''(x_\alpha)\frac{t^2}{2}}dt\\
+&=e^{-zf(x_\alpha)}\sum_{n\geq 0}b_{2n}^{\alpha}\int_{-\varepsilon}^{\varepsilon}t^{2n}e^{-zf''(x_{\alpha})\frac{t^2}{2}}dt\\
+&=\sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}\mathrm{Erf}\left(\frac{\sqrt{z f''(x_\alpha)}}{\sqrt{2}}\varepsilon\right)+\\
+&-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
+&\sim_{\varepsilon<<1} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
+\end{align*} 
+therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]
+
+Since, $\tfrac{1}{\varepsilon}=\limsup_{n}\sqrt[n]{b_{n}^{\alpha}}$
+
+\[|a_{\alpha,n}|\leq CA^n n!\]
+where we use $(2n-1)!!\sim \tfrac{2^n}{\sqrt{\pi n}}n!$ as $n\to \infty$.
 
 Part $(2)$: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\mathcal{B}(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n})(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+\hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
 (2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
@@
 \begin{align*}
-\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{k\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
-&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right) &\\
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
+&=\frac{36}{5}i\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^{n-1} & \\
+&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right)\right) &\\
 &=\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right) &\\
@@
 \begin{align*}
-\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{k\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
-&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144} (-4 + 3 \zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right) &\\
-&=-\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
+&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144}(-4+3\zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right)  &\\
+&=-\mathbf{i}\pi\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
 &=-\mathbf{i}\hat{w}_{+}(\zeta-\frac{4}{3}) &
@@
 \end{align*}
-
-\begin{claim}\label{claim1}
-\begin{equation}
-\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
-\end{equation}
-\end{claim}
+%
+%\begin{claim}\label{claim1}
+%\begin{equation}
+%\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
+%\end{equation}
+%\end{claim}
 
@@
 
-Hence claim \eqref{claim1} is equivalent to 
+%Hence claim \eqref{claim1} is equivalent to
+Then equations \eqref{formula1} is equivalent to
+
 \begin{claim}\label{claim 2}
@@
 \end{align*}
-however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$. 
+however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$, thus the claim holds true.
+
+Analougusly, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
 %By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
@@
 \end{align*}
-however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$. 
+however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$, thus the claim holds true. 
 \end{proof}
-
+Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
 \end{example}

### 2022-01-19 draft2.tex
add general equation for cubic polynomial

@@
 
+\section{Resurgence for degree $3$ polynomials}
+
+Let $f$ be a degree $3$ polynomial, and $x_{\alpha_1},x_{\alpha_2}$ its critical points (not necessarily distinguished).
+Then \[I(z)=\int_{\mathcal{C}_{\alpha}}e^{-zf}dt\] is a solution of a second order ODE with regular/irregular singularity at zero/infinity.
+In particular, only two cases can occur: let $f(t)=a_1t^3+a_2t^2+a_3t+a_4$
+\begin{enumerate}
+\item if $a_2=0$, \begin{equation} I''+2a_4 I'+\left(a_4^2+\frac{4}{27}\frac{a_3^3}{a_1}\right)I+\frac{I'}{z}+\frac{a_4}{z}I-\frac{1}{9z^2}=0
+\end{equation}
+\item if $a_2=a_3=0$, $I$ solves
+\begin{equation}
+I''+aI'+(aa_4-a_4^2)I+\frac{4+9e}{3}\frac{I'}{z}+\frac{a+2a_4+9a_4e}{3}\frac{I}{z}+\frac{e}{z^2}I=0
+\end{equation}
+for every $a,e\in\C$, which is equivalent to say $I$ is a solution of
+\begin{equation}
+I'+\left(a_4+\frac{3}{z}\right)I=0
+\end{equation} 
+\end{enumerate}
+
 \end{document}

### 2022-01-19 airy-resurgence.tex
Correct Laplace transform starting points

@@
 \subsection{Change of coordinates}
-Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation
+Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
 \begin{align*}
-\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
 & = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
 & = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
-& = e^{-az} \laplace_{\zeta_a} \hat{\varphi},
+& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
 \end{align*}
 we learn that
-\[ \laplace_{\zeta_a} \hat{\varphi} = e^{az} \laplace_\zeta \hat{\varphi}. \]
+\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]
 
@@
 \subsubsection{A good try at $\zeta = 0$}
-Let's try to find a function $\hat{K}$ with $K = \laplace_\zeta \hat{K}$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
+Let's try to find a function $\hat{K}_0$ with $K = \laplace_\zeta \hat{K}_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
 \begin{equation}\label{eqn:spatial-mod-bessel}
@@
 \end{equation}
-Since we want $\laplace_\zeta \hat{K}$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
-Unfortunately, this would force $\hat{K}$ to be zero.
+Since we want $\laplace_\zeta \hat{K}_0$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}_0$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
+Unfortunately, this would force $\hat{K}_0$ to be zero.
 \subsubsection{Success at $\zeta = 1$}\label{spatial-success}
-Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. Since
+Let's try instead to find a function $\hat{K}_1$ with $K = \laplace_{\zeta, 1} \hat{K}_1$. Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. Since
 \begin{align*}
-\laplace_{\zeta_1} \hat{K} & = e^z \laplace_\zeta \hat{K} \\
+\laplace_{\zeta_1, 0} \hat{K}_1 & = e^z \laplace_{\zeta, 1} \hat{K}_1 \\
 & = e^z K \\
@@
 \end{align*}
-we want $\laplace_{\zeta_1} \hat{K}$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
+we want $\laplace_{\zeta_1} \hat{K}_1$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
 \begin{equation}\label{eqn:shifted-spatial-mod-bessel}
@@
 This time, though, there's a trick we can use to zero out the inhomogeneity.
-Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.
-That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
+Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.\footnote{\textbf{Explain how to see.}} That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
 
-Following this plan, let's find $\hat{K}$ explicitly.
+Following this plan, let's find $\hat{K}_1$ explicitly.
 Defining another coordinate $\xi$ on $\hat{\R}$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
@@
 By the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
-This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}$.
+This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}_1$.
 The power series~\cite[equation~15.2.1]{dlmf}
@@
 Comparing with series~\ref{bessel-asymp}, we see that $\kappa = \tfrac{i}{2}\,f_0$.
-We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}$ for
-\[ \hat{K} = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}_1$ for
+\[ \hat{K}_1 = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
 \section{Sketches}

### 2022-01-20 draft2.tex
add equations for cubic f

--- 2022-01-18 draft2.tex
@@
 \end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descendet oath through the critical point $x_\alpha$. 
-\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$
+where $\mathcal{C}_\alpha$ is a steepest descendet path through the critical point $x_\alpha$. 
+\begin{theorem}\label{thm:maxim} Let $N=1$.
+Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
+Then
 \begin{enumerate}
@@
 I_{\alpha}(z)&=\int_{\mathcal{C}_{\alpha}}e^{-zf}\nu & f=\zeta\\
-&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Heckel countour} \\
+&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Hankel countour} \\
 &=:\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\hat{I}_{\alpha}(\zeta)d\zeta &
@@
 \end{lemma}
-\begin{proof}
+\begin{proof}From the special case of hypergeometric function (see 15.4.14 DLMF) we have the following identity:
 \begin{align*}
-{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)&=2\cos\left(\frac{1}{3}\arcsin\left(\frac{3}{2}\zeta\right)\right)(4-9\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
-&=\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
+{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)&=%2\cos\left(\frac{1}{3}\arcsin\left(\frac{3}{2}\zeta\right)\right)(4-9\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
+\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
 &=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
@@
 
+\section{Resurgence for degree $3$ polynomials}
+
+Let $f$ be a degree $3$ polynomial, and $t_{1},t_{2}$ its critical points (not necessarily distinguished):
+\begin{enumerate}
+\item if $t_{1}\neq t_{2}$, then 
+\[I(z)=\int_{\mathcal{C}_{j}}e^{-zf}dt\]
+is a solution of 
+\begin{equation} I''+a I'+bI+c\frac{I'}{z}+\frac{d}{z}I+\frac{e}{z^2}I=0
+\end{equation}
+where $a,b,c,d,e$ are determined in terms of $f$.
+\item if $t_{1}=t_2$, then 
+\[I(z)=\int_{\mathcal{C}_{1}}e^{-zf}dt\]
+is a solution of a first order ODE
+\begin{equation}
+I'+\left(a_4-\frac{a_2^3}{27a_1^2}+\frac{1}{3z}\right)I=0
+\end{equation}
+\end{enumerate}
+
+\begin{proof}
+Let $f(t)=a_1t^3+a_2t^2+a_3t+a_4$ with $a_1\neq 0$, 
+\begin{align*}
+\int_{\mathcal{C}_j}e^{-fz}dt&=\int_{\mathcal{C}_j+\frac{a_2}{3a_1}}e^{-(a_1t^3+pt+q)z}dt & t\to t-\frac{a_2}{3a_1}
+\end{align*}
+where $p=a_3-\frac{a_2^2}{3a_1}$ and $q=a_4-\frac{a_2a_3}{3a_1}+\frac{2a_2^2}{27a_1^2}$.
+
+Case $(1)$: if $p\neq 0$,
+\begin{align*}
+I(z)=\int t(3a_1t^2+p)ze^{-fz}=\int(3a_1t^3+pt)ze^{-ft}=\\
+\int2a_1t^3ze^{-fz}+\int(a_1t^3+pt+q)ze^{-fz}-qzI\\
+2z\int a_1t^3e^{-fz}-zI'-qzI
+\end{align*}
+
+\begin{align*}
+2z\int a_1t^3e^{-fz}=2z^2\int\frac{t^4}{4}a_1(3a_1t^2+p)e^{-fz}=\frac{z^2}{2}\int (3a_1^2t^6+pa_1t^4)e^{-fz}=\\
+\frac{z^2}{2}\int(3a_1^2t^6+6pa_1t^4+3q^2+3p^2t^2+6pqt+6a_1qt^3)e^{-fz}+\\
++\frac{z^2}{2}\int(pa_1t^4-6pa_1t^4)e^{-fz}-\frac{z^2}{2}\int(3q^2+3p^2t^2+6pqt+6a_1qt^3)e^{-fz}\\
+=\frac{3z^2}{2}I''+\frac{3z^2}{2}q^2I+3qz^2I'-\frac{z^2}{2}p\int(3a_1t^4+pt^2)e^{-fz}-z^2p\int(a_1t^4+pt^2)e^{-fz}\\
+=\frac{3z^2}{2}I''+\frac{3z^2}{2}q^2I+3qz^2I'-\frac{5}{3}zp\int te^{-fz}-\frac{2}{3}z^2p^2\int t^2e^{-fz}
+\end{align*}
+
+hence
+
+\begin{align}
+I=-zI'-qzI+\frac{3z^2}{2}I''+\frac{3z^2}{2}q^2I+3qz^2I'-\frac{5}{3}zp\int te^{-fz}-\frac{2}{3}z^2p^2\int t^2e^{-fz}\\
+\frac{3z^2}{2}\left(I''+q^2I+2qI'-\frac{2}{3z}I'-\frac{2q}{3z}I-\frac{2}{3z^2}I-\frac{10}{9z}p\int te^{-fz}dt-\frac{4}{9}p^2\int t^2e^{-fz}\right)=0 
+\end{align}
+
+Notice that 
+\begin{align*}
+\frac{4}{9}p^2\int t^2e^{-fz}=\frac{4}{27a_1}p^2\int(3a_1t^2+p)e^{-fz}-\frac{4}{27a_1}p^3I=-\frac{4}{27a_1}p^3I
+\end{align*}
+
+\begin{align*}
+-\frac{10}{9z}p\int te^{-fz}dt=\frac{5}{9z}\int pte^{-fz}-\frac{5}{3z}\int(pt+q)e^{-fz}+\frac{5}{3z}qI=\\
+\frac{5}{9z}\int pte^{-fz}-\frac{5}{3z}\int(pt+q+a_1t^3)e^{-fz}+\frac{5}{3z}\int a_1t^3e^{-fz}+\frac{5}{3z}qI=\\
+\frac{5}{9z}\int t(3a_1t^2+p)e^{-fz}+\frac{5}{3z}I'+\frac{5}{3z}qI\\
+=\frac{5}{9z^2}I+\frac{5}{3z}I'+\frac{5}{3z}qI
+\end{align*}
+thefore, collecting all the contributions together we find
+
+\begin{align*}
+I''+q^2I+2qI'-\frac{2}{3z}I'-\frac{2q}{3z}I-\frac{2}{3z^2}I+\frac{5}{9z^2}I+\frac{5}{3z}I'+\frac{5}{3z}qI+\frac{4}{27a_1}p^3I=0\\
+I''+2qI'+\left(\frac{4p^3}{27a_1}+q^2\right)I+\frac{1}{z}I'+\frac{q}{z}I-\frac{1}{9z^2}I=0
+\end{align*}
+
+Case $(2)$: if $p=0$, then integrating by part we have
+\begin{align*}
+I(z)&=\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}e^{-(a_1t^3+q)z}dt\\
+&=\left[te^{-(a_1t^3+q)z}\right]_{\mathcal{C}_1+\frac{a_2}{3a_1}}+\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}3a_1t^3ze^{-(a_1t^3+q)z}dt\\
+&=3z\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}(a_1t^3+a_4)e^{-(a_1t^3+q)z}dt-3a_4z\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}e^{-(a_1t^3+q)z}dt\\
+&=-3zI'(z)-3a_4I(z)
+\end{align*}
+\end{proof}
+%  \[I(z)=\int_{\mathcal{C}_{\alpha}}e^{-zf}dt\] is a solution of a second order ODE with regular/irregular singularity at zero/infinity.
+In particular, only two cases can occur: let $f(t)=a_1t^3+a_2t^2+a_3t+a_4$
+%\begin{enumerate}
+%\item if $a_2=0$ and $a_3\neq 0$, \begin{equation} I''+2a_4 I'+\left(a_4^2+\frac{4}{27}\frac{a_3^3}{a_1}\right)I+\frac{I'}{z}+\frac{a_4}{z}I-\frac{1}{9z^2}=0
+%\end{equation}
+%\item if $a_2=a_3=0$, $I$ solves
+%\begin{equation}\label{eq:I,a,e}
+%I''+aI'+(aa_4-a_4^2)I+\frac{4+9e}{3}\frac{I'}{z}+\frac{a+2a_4+9a_4e}{3}\frac{I}{z}+\frac{e}{z^2}I=0
+%\end{equation}
+%for every $a,e\in\C$; in particular if $I$ is a solution of
+%\begin{equation}
+%I'+\left(a_4+\frac{1}{3z}\right)I=0
+%\end{equation}
+%then it solves equation \eqref{eq:I,a,e} for every $a,e\in\C$.   
+%\end{enumerate}  
+%We notice that in the first case (of which Airy is an example), since $a_3\neq 0$ $f(t)$ has always two distinct critical points. Wherease, if $a_3=0$ there is a single critical point at $t=0$.
+
 \end{document}

### 2022-01-24 draft2.tex
add stoke factors for non degenerate case

@@
 &\frac{4}{3}\zeta(-1+ \frac{3}{4}\zeta)\hat{w}_{-}''+(-\frac{8}{3}+4\zeta)\hat{w}_-'+\frac{77}{36}\hat{w}_{-}=0 & \\
-&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}(u) & u=\frac{3}{4}\zeta
+&\qquad u(1-u)\hat{w}_-''(u)+(2-4u)\hat{w}_-'(u)-\frac{77}{36}\hat{w}(u)=0 & u=\frac{3}{4}\zeta
 \end{align*} 
@@
 is a solution of 
-\begin{equation} I''+a I'+bI+c\frac{I'}{z}+\frac{d}{z}I+\frac{e}{z^2}I=0
+\begin{equation}
+\label{eq:I for p not 0}
+ I''+a I'+bI+c\frac{I'}{z}+\frac{d}{z}I+\frac{e}{z^2}I=0
 \end{equation}
@@
 \end{align*}
-where $p=a_3-\frac{a_2^2}{3a_1}$ and $q=a_4-\frac{a_2a_3}{3a_1}+\frac{2a_2^2}{27a_1^2}$.
+where $p=a_3-\frac{a_2^2}{3a_1}$ and $q=a_4-\frac{a_2a_3}{3a_1}+\frac{2a_2^3}{27a_1^2}$.
 
@@
 &=\left[te^{-(a_1t^3+q)z}\right]_{\mathcal{C}_1+\frac{a_2}{3a_1}}+\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}3a_1t^3ze^{-(a_1t^3+q)z}dt\\
-&=3z\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}(a_1t^3+a_4)e^{-(a_1t^3+q)z}dt-3a_4z\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}e^{-(a_1t^3+q)z}dt\\
-&=-3zI'(z)-3a_4I(z)
+&=3z\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}(a_1t^3+q)e^{-(a_1t^3+q)z}dt-3qz\int_{\mathcal{C}_1+\frac{a_2}{3a_1}}e^{-(a_1t^3+q)z}dt\\
+&=-3zI'(z)-3qzI(z)
 \end{align*}
@@
 
+We would like to verify that for every cubic function $f$, the Borel transform of the exponential integral can be expressed by an hypergeometric function and hence deduce its resurgent properties in full generality.
+If $p\neq 0$, $I(z)$ is a solution of
+
+\begin{equation}
+I''+2qI'+\left(\frac{4p^3}{27a_1}+q^2\right)I+\frac{1}{z}I'+\frac{q}{z}I-\frac{1}{9z^2}I=0
+\end{equation}
+
+hence a formal solution as $z\to \infty$ is given (up to constants $U_1,U_2\in\C$) by 
+\begin{align}
+\tilde{I}_{+}(z)&\defeq U_1e^{-(q+\sqrt{\frac{4p^3}{27a_1}})z}z^{1/2}\tilde{w}_+(z)\\
+\tilde{I}_-(z)&\defeq U_2 e^{-(q-\sqrt{\frac{4p^3}{27a_1}})z}z^{1/2}\tilde{w}_-(z)
+\end{align}
+where $\tilde{w}_{\pm}(z)\in\C[\![z^{-1}]\!]$ is the formal solution of
+\begin{equation}\label{w_general}
+\tilde{w}_{\pm}''\mp 2\sqrt{\frac{4p^3}{27a_1}}\tilde{w}_{\pm}'+\frac{5}{36}\frac{\tilde{w}_{\pm}}{z^2}=0
+\end{equation}
+with $\tilde{w}_{\pm}(z)=1+\sum_{k\geq 1}a_{\pm,k}z^{-k}$.
+
+We can now compute the Borel transform of \eqref{w_general}: for $\tilde{w}_+(z)$
+
+\begin{align*}
+\zeta^2\hat{w}-2\sqrt{\frac{4p^3}{27a_1}}\zeta\hat{w}+\frac{5}{36}\int_0^{\zeta}(\zeta-\zeta')\hat{w}(\zeta')d\zeta'&=0 &\\
+\zeta^2\hat{w}'+2\zeta\hat{w}+2\sqrt{\frac{4p^3}{27a_1}}\hat{w}+2\sqrt{\frac{4p^3}{27a_1}}\zeta\hat{w}'+\frac{5}{36}\int_0^\zeta\hat{w}(\zeta')&=0 &\\
+\left(\zeta^2+2\sqrt{\frac{4p^3}{27a_1}}\zeta\right)\hat{w}''+4\left(\zeta+\sqrt{\frac{4p^3}{27a_1}}\right)\hat{w}'+\frac{77}{36}\hat{w}&=0 &\\
+t(1-t)\hat{w}''+(2-4t)\hat{w}'-\frac{77}{36}\hat{w}&=0 &\zeta=-2t\sqrt{\frac{4p^3}{27a_1}}
+\end{align*}
+
+hence \[\hat{w}_+(\zeta)={}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right)\] and analougusly, \[\hat{w}_-(\zeta)={}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right).\] Notice that $\hat{w}_{\pm}(\zeta)$ has a branch cut singularity respectively at $\zeta=\zeta_{\pm}\defeq\pm \sqrt{\frac{16p^3}{27a_1}}$, and thanks to the well known formulas for the analytic continuation of hypergeometric functions (see 15.2.3 DLMF), if we assume the branch cut is from $\zeta_{\pm}$ to $+\infty$
+
+\begin{align*}
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_+}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \zeta\in\left(\zeta_+,+\infty\right) & \\
+&=-\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^{k-1} & \\
+&=\mathbf{-i}\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \\
+&=\mathbf{-i}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_+}\right) & \\
+&=\mathbf{-i}\hat{w}_+(\zeta-\zeta_+)
+\end{align*}
+
+Similarly, if we assume that the branch cut is from $\zeta_{\pm}$ to $-\infty$ then
+
+\begin{align*}
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_-}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \zeta\in\left(-\infty,\zeta_-\right) & \\
+&=\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^{k-1} & \\
+&=\mathbf{i}\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \\
+&=\mathbf{i}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_-}\right) & \\
+&=\mathbf{i}\hat{w}_-(\zeta-\zeta_-)
+\end{align*}
+
+therefore we see that the Stokes factors are given by $\pm i$ (as for Airy).
+
+\textbf{I think it will be nice to add the geometric interpretation of Maxim in term of Lefschetz thimbles}
+
+Let us first compute the Borel transform of \eqref{eq:I for p not 0} (indeed as in the proof of Theorem \ref{thm:maxim} we know that \eqref{eq:I for p not 0} admits a formal solution which is Gevrey-$1$)
+
+\begin{align*}
+\zeta^2\hat{I}-a\zeta\hat{I}+b\hat{I}-\int_0^{\zeta}\zeta'\hat{I}(\zeta')+d\int_0^{\zeta}\hat{I}(\zeta')-\frac{1}{9}\int_0^{\zeta}(\zeta-\zeta')\hat{I}(\zeta')=0\\
+2\zeta\hat{I}+\zeta^2\hat{I}'-a\hat{I}-a\zeta\hat{I}'+b\hat{I}'-\zeta\hat{I}+d\hat{I}-\frac{1}{9}\int\hat{I}(\zeta')=0\\
+(\zeta^2-a\zeta+b)\hat{I}''+(3\zeta-2a+d)\hat{I}'+\frac{8}{9}\hat{I}=0
+\end{align*}
+
+Now we denote by $\lambda_1,\lambda_2$ the distinguished (we assume that $p\neq 0$) roots of $\zeta^2-a\zeta+b$, then
+
+\begin{align}
+& (\zeta-\lambda_1)(\zeta-\lambda_2)\hat{I}''+(3\zeta-2a+d)\hat{I}'+\frac{8}{9}\hat{I}=0 & \\
+&(t+\lambda_2-\lambda_1)t\hat{I}''+(3t+3\lambda_2-2a+d)\hat{I}'+\frac{8}{9}=0 & t=\zeta-\lambda_2 \\
+& \label{eq:I hyper} s(1-s)\hat{I}''-\left(3s+\frac{3\lambda_2-2a+d}{\lambda_1-\lambda_2}\right)\hat{I}'-\frac{8}{9}\hat{I}=0 & t=(\lambda_1-\lambda_2)s
+\end{align}
+
+where \eqref{eq:I hyper} is an hypergeometric equation\footnote{Notice that $\lambda_{1,2}=q\pm \frac{2i}{3}p\sqrt{\frac{p}{3a_1}}$, $a=2q$ and $d=q$.
+Hence \[\frac{2a-d-3\lambda_2}{\lambda_1-\lambda_2}=\frac{4q-q-3q-2ip\sqrt{\frac{p}{3a_1}}}{-\frac{4i}{3}p\sqrt{\frac{p}{3a_1}}}=\frac{3}{2}\]} and a solution is given by
+
+\begin{equation}
+\hat{I}_{\lambda_1}(\zeta;U_1,U_2)=U_1\,{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta-\lambda_2}{\lambda_1-\lambda_2}\right)+U_2\left(\frac{\zeta-\lambda_2}{\lambda_1-\lambda_2}\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta-\lambda_2}{\lambda_1-\lambda_2}\right)
+\end{equation}
+
+which has a branch cut at $\zeta=\lambda_1$, where $U_1,U_2$ are constants. Of course, reversing the role of $\lambda_1$ and $\lambda_2$ we find
+
+\begin{equation}
+\hat{I}_{\lambda_2}(\zeta,;U_1,U_2)=U_1{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)+U_2\left(\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)
+\end{equation}
+
+is the Borel transform of $\tilde{I}_{\lambda_2}(z)$ and it has a branch cut singularity at $\zeta=\lambda_2$.
+It is remarkable that  the dependece on the function $f$ is only on the location of the singularities, but it is always an hypergeometric function with the same parameters.
+In addition, we can compute the Stokes constants thanks to the well known formula for analyitic continuation of hypergeometric (see 15.2.3 in DLMF)
+
+\begin{align*}
+\hat{I}_{\lambda_1}(\zeta+i0;U_1,0)-\hat{I}_{\lambda_1}(\zeta-i0;U_1,0)&=-U_1\frac{2\pi i}{\Gamma\left(\frac{2}{3}\right)\Gamma\left(\frac{4}{3}\right)}\left(\frac{\lambda_1-\zeta}{\lambda_2-\lambda_1}\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)\\
+&=\mathbf{-i}U_1\frac{2\pi i}{\Gamma\left(\frac{2}{3}\right)\Gamma\left(\frac{4}{3}\right)}\left(\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta-\lambda_1}{\lambda_2-\lambda_1}\right)\\
+&=\mathbf{-i} \hat{I}_{\lambda_2}\left(\zeta;0,\frac{U_1}{\Gamma(2/3)\Gamma(4/3)}\right)
+\end{align*}
+
 \end{document}

### 2022-01-24 draft2.tex
add the degenerate case

@@
 
+The situation is quite different if we consider the degenerate case, where we have only a singular point: indeed there is a one parameter family of solutions of 
+\begin{equation}
+I'(z)+\left(\frac{1}{3z}+q\right)I(z)=0
+\end{equation}
+namely for $U\in\C$
+\begin{equation}
+\tilde{I}(z)=Ue^{-qz}z^{1/3}\tilde{w}(z)\,\qquad \text{ where } \tilde{w}(z)\in\C[\![z^{-1}]\!.]
+\end{equation} 
+The Borel transform of $\tilde{w}$ is a solution of 
+\begin{equation}
+\zeta\hat{w}'+\frac{\hat{w}}{3}=0
+\end{equation}
+hence, up to rescaling by a constant, \[\hat{w}(\zeta)\propto \zeta^{-1/3}=\,\, {}_2F_1\left(a,\frac{1}{3};a;1-\zeta\right)\] for every $a\in \C$.
+In the degenerate case we get an hypergeometric function as well, but the resurgent structure is trivial, i.e.
+$\hat{w}(\zeta)$ is holomorphic on the Riemann surface of $\zeta^{1/3}$.
+
+\subsubsection{Alternative computation of the Borel transform of I}
+
 Let us first compute the Borel transform of \eqref{eq:I for p not 0} (indeed as in the proof of Theorem \ref{thm:maxim} we know that \eqref{eq:I for p not 0} admits a formal solution which is Gevrey-$1$)

### 2022-01-26 exp-resurgence.tex
Start article outline

\documentclass{article}

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
%%\usepackage{amsthm}
\usepackage{graphicx}

%%\theoremstyle{definition}
%%\newtheorem{defn}{Definition}
%%\theoremstyle{plain}
%%\newtheorem{prop}{Proposition}

% convenience aliases
\newcommand{\maps}{\colon}

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\laplace}{\mathcal{L}}
\DeclareMathOperator{\Ai}{Ai}

\title{Resurgence of the Airy function \\ and other exponential integrals}
\author{Veronica Fantini and Aaron Fenyes}

\begin{document}
\maketitle
\section{Introduction}
\subsection{Why does Borel resummation work?}
\begin{itemize}
\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
\item The resummation method works correctly for functions which satisfy that assumption.
\item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
\begin{itemize}
\item Different aspects of this example appear in various places (Mari\~{n}o, Kawai--Takei, Sauzin). We give a detailed, unified treatment.
\end{itemize}
\item We can generalize this argument to all $K_{1/n}$ and their limit $K_0$.
\item We can also generalize to all third-order exponential integrals.
\begin{itemize}
\item Most of them are equivalent to the $K_{1/3}$ integral, but there's also an interesting degeneration.
\end{itemize}
\end{itemize}
\subsection{Fractional derivative formula}
\begin{itemize}
\item Theorem~\ref{thm:three-halves} says that for a certain class of exponential integrals
\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
\end{itemize}
\subsection{Stokes phenomenon}
\begin{itemize}
\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
\item The jump comes from the branch cut difference identity for hypergeometric functions.
\end{itemize}
\section{The Laplace and Borel transforms}
\subsection{The Laplace transform}
\begin{itemize}
\item Action on differential equations.
\begin{itemize}
\item Can we find a way to prove this when the differential operator spits out a function that's not integrable around zero?
\end{itemize}
\item Global picture?
\end{itemize}
\subsection{The Borel transform}
\begin{itemize}
\item Action on differential equations.
\begin{itemize}
\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
\end{itemize}
\end{itemize}
\section{Third-order exponential integrals}
\begin{itemize}
\item Reduce to
\[ I(z) = \int \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
using change of coordinate.
\item When $p \neq 0$, can reduce further to
\[ I(z) = p^{1/2} e^{-qz} K_{1/3}(p^{3/2} z). \]
\item As $p$ goes to zero, $I(z)$ degenerates to
\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}). \]
\end{itemize}
\end{document}

### 2022-01-26 figures/contours.jl
Add 2d path offset and test-figure mode

@@ -1,7 +1,7 @@
 module Contours
 
 # for plots
-using Compose, Colors, Roots
+using Compose, Colors, LinearAlgebra, Roots
 import Cairo, Fontconfig
 
 # for integral checks
@@ -10,7 +10,7 @@ import Plots
 
 # === paths ===
 
-u_path(θ, off) = t -> 1/6 * exp(-im*θ/3) * (cosh(2/3*π*im - t) - off*exp(2/3*π*im))
+u_path(θ, off) = t -> 1/6 * exp(-im*θ/3) * (cosh(2/3*π*im - t) - dot(off, [exp(2/3*π*im), exp(-2/3*π*im)]))
 u_jet(θ, off) = t -> (u_path(θ, off)(t), -1/6 * exp(-im*θ/3) * sinh(2/3*π*im - t))
 
 function ζ(u)
@@ -45,8 +45,8 @@ end
 
 taxinorm(z) = max(abs(real(z)), abs(imag(z)))
 
-# for a nice contour with θ at π or 4π, set `off` to 1.6
-function plotcontours(θ = 0, off = 0)
+# for a nice contour with θ at π or 4π, set `off` to (1.6, 0)
+function plotcontours(θ = 0, off = (0, 0); test = true)
   dark = RGB(0, 0.5, 0.7)
   light = RGB(0.6, 0.9, 1.0)
   
@@ -85,8 +85,9 @@ function plotcontours(θ = 0, off = 0)
   
   # === output ===
   
-  draw(PDF("u_contour.pdf", 6cm, 6cm), u_contour)
-  draw(PDF("zeta_contour.pdf", 6cm, 6cm), ζ_contour)
+  tag = test ? "_test" : ""
+  draw(PDF(string("u_contour", tag, ".pdf"), 6cm, 6cm), u_contour)
+  draw(PDF(string("zeta_contour", tag, ".pdf"), 6cm, 6cm), ζ_contour)
 end
 
 # === contour integrals ===

### 2022-01-26 modified bessel.tex

\documentclass{article}

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}

% convenience aliases
\newcommand{\maps}{\colon}

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\laplace}{\mathcal{L}}

\title{Resurgence of modified Bessel functions of second kind}
\author{Veronica Fantini}

\begin{document}
\maketitle

\section{Modified Bessel function of second kind}

The modified Bessel function of the second kind is a solution of the equation
\begin{equation}\label{Bessel_nu}
w''+\frac{w'}{z}-w-\frac{\nu^2}{z^2}=0
\end{equation}
such that $K_{\nu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$. It has a branch point at $z=0$ for every $\nu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
\subsection{Differential equation}
From the general theory of ODE, the formal integral solution of \eqref{Bessel_nu} is two parameter family 
\begin{equation}
\tilde{w}(z)=U_1e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)+U_2e^{z}z^{-1/2}\tilde{w}_{\nu,-}(z)
\end{equation} 
where $\tilde{w}_{\nu,\pm}=1+\sum_{j\geq 1}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
\begin{align*}
\tilde{w}_{\nu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_+}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,+}=0\\
\tilde{w}_{\nu,-}''+2\tilde{w}_{\nu,-}'+\frac{\tilde{w}_{\nu,-}}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,-}=0
\end{align*} 
In particular, $K_{\nu}(z)=e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)$. We now compute the Borel transform of $\tilde{w}_+(z)$: it is a solution of 
\begin{align*}
&\zeta^2\hat{w}_{\nu,+}+2t\hat{w}_{\nu,+}+\left(\frac{1}{4}-\nu^2\right)\int_0^{\zeta}(\zeta-s)\hat{w}_{\nu,+}(s)ds=0 &\\
&\zeta^2\hat{w}_{\nu,+}''+2\zeta\hat{w}_+''+4\zeta\hat{w}_{\nu,+}'+\left(\frac{9}{4}-\nu^2\right)\hat{w}_{\nu,+}=0 & \\
&t(1-t)\hat{w}_{\nu,+}''+(2-4t)\hat{w}_{\nu,+}'-\left(\frac{9}{4}-\nu^2\right)\hat{w}_{\nu,+}=0 & t=-\frac{\zeta}{2}
\end{align*} 
therefore $\hat{w}_{\nu,+}(\zeta)$ is an hypergeometric function
\begin{equation}
\hat{w}_{\nu,+}(\zeta)={}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;-\frac{\zeta}{2}\right)
\end{equation}
and it has a branch point singularities at $\zeta=-2$. By the same reasoning, 
\begin{equation}
\hat{w}_{\nu,-}(\zeta)={}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;\frac{\zeta}{2}\right)
\end{equation} 
and it has branch point at $\zeta=2$. Thanks to explicit formula for the analytic continuation of hypergeomtric functions (see \cite{dlmf} 15.2.3)
\begin{align*}
\hat{w}_{\nu,+}(\zeta+i0)-\hat{w}_{\nu,+}(\zeta-i0)&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\nu,\frac{1}{2}+\nu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\nu+k\right)\Gamma\left(\tfrac{3}{2}+\nu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
&=-2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1+\frac{\zeta}{2}\right) & \\
&=-2i\cos(\nu \pi)\hat{w}_{\nu,-}(\zeta+2)
\end{align*} 
and for $\hat{w}_{\nu,-}(\zeta)$
\begin{align*}
\hat{w}_{\nu,-}(\zeta+i0)-\hat{w}_{\nu,-}(\zeta-i0)&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\nu,\frac{1}{2}+\nu;0;1-\frac{\zeta}{2}\right) & \zeta<2 \\
&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{2}\right)^{k-1} & \\
&=2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1-\frac{\zeta}{2}\right) & \\
&=2i\cos(\nu \pi)\hat{w}_{\nu,+}(\zeta-2)
\end{align*}
In addition, the previous relations computes the Stokes constants which are funtions of $\nu$ and are given by $\pm 2i\cos(\nu\pi)$.

\subsection{Exponential integral}
As showed by Aaron, if $T_n(u)$ and $U_n(u)$ denote the Chebyschev polynomials \footnote{$T_n(\cos(t))=\cos(nt)$ and $U_n(\cos(t))\sin(t)=\sin((n+1)t)$.}

\begin{multline}
K_{\nu}(z)=\frac{1}{2i\nu\sin(\nu\pi)}\int_{\mathcal{C}_{\alpha}}e^{zT_{\frac{1}{\nu}}(u)}du=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\frac{d\zeta}{U_{\frac{1}{\nu}-1}(u)}=\\
=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)d\zeta
\end{multline}
where $\mathcal{C}_{\alpha}$ \textbf{has to be checked, but I guess } $\alpha=1$

Indentity 15.10.17 from \cite{dlmf} splits the integrand above into
\begin{align*}
{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)&=C_1 \, {}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{1}{2};\zeta^2\right)+C_2\zeta \,{}_2F_1\left(1-\frac{\nu}{2},1+\frac{\nu}{2};\frac{3}{2};\zeta^2\right)\\
&=\tilde{C}_1\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right]+\\
&\qquad+\tilde{C}_2\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right]
\end{align*}
therefore, collecting the contrubutions together we have 
\begin{multline}
K_{\nu}(z)=\frac{i}{4\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right] d\zeta
\end{multline}

Since ${}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) $ is singular at $\zeta=1$, the inverse Laplace transform of $K_\nu(z)$ is 
\[
\hat{K}_{\nu}(\zeta)=\frac{i}{4\sin(\nu\pi)}{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
\] 
\bibliographystyle{utphys}
\bibliography{airy-resurgence}
\end{document}

### 2022-01-26 figures/contours.jl
Adjust contour scale automatically
It's kludgy, but it gets the job done in the cases we're focused on.

@@ -1,7 +1,7 @@
 module Contours
 
 # for plots
-using Compose, Colors, LinearAlgebra, Roots
+using Compose, Colors, Polynomials, LinearAlgebra, Roots
 import Cairo, Fontconfig
 
 # for integral checks
@@ -10,14 +10,26 @@ import Plots
 
 # === paths ===
 
-u_path(θ, off) = t -> 1/6 * exp(-im*θ/3) * (cosh(2/3*π*im - t) - dot(off, [exp(2/3*π*im), exp(-2/3*π*im)]))
-u_jet(θ, off) = t -> (u_path(θ, off)(t), -1/6 * exp(-im*θ/3) * sinh(2/3*π*im - t))
-
-function ζ(u)
-  if length(u) == 1
-    return 4u^3 - 3u
+function path_scale(n, k)
+  if k//n == 1//2
+    return 1
   else
-    return (4u[1]^3 - 3u[1], 3*(4u[1]^2 - 1)*u[2])
+    skip = mod(n, 2) == 0 ? 1 : 1/2
+    return cos(π*(1/2 - skip/3n)) / abs(cos(π*k/n))
+  end
+end
+u_path(θ, off, n = 3, k = 1) = t -> path_scale(n, k) * exp(-im*θ/n) * (cosh(π*(1-k/n)*im - t) - dot(off, [exp(π*(1-k/n)*im), exp(-π*(1-k/n)*im)]))
+u_jet(θ, off, n = 3, k = 1) = t -> (u_path(θ, off, n, k)(t), -path_scale(n, k) * exp(-im*θ/n) * sinh(π*(1-k/n)*im - t))
+
+function T_jet(n)
+  T_pt = convert(Polynomial, ChebyshevT(push!(fill(0, n), 1)))
+  T_push = derivative(T_pt)
+  u -> begin
+    if length(u) == 1
+      return T_pt(u)
+    else
+      return (T_pt(u[1]), T_push(u[1])*u[2])
+    end
   end
 end
 
@@ -45,30 +57,39 @@ end
 
 taxinorm(z) = max(abs(real(z)), abs(imag(z)))
 
-# for a nice contour with θ at π or 4π, set `off` to (1.6, 0)
-function plotcontours(θ = 0, off = (0, 0); test = true)
+function edgept(θ)
+  x = cos(θ)
+  y = sin(θ)
+  x < y ? [x/y, 1] : [1, y/x]
+end
+
[…]

### 2022-01-31 exp-resurgence.tex
add points in the index

@@
 the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
+\item the asymptotic expansion of $I(z)$ is a resurgent function.
+\item Is it always a \emph{simple} resurgent function?
+\begin{itemize}
+\item \textbf{Maxim belives it is in general, and indeed in our examples we get simple resurgent functions. But how to prove it in general?}
+\end{itemize} 
 \end{itemize}
@@
 \item The jump comes from the branch cut difference identity for hypergeometric functions.
+\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
 \end{itemize}

### 2022-02-07 airy-resurgence.tex
Draw contours for higher degrees

@@
 \begin{center}
-\includegraphics{figures/u_contour.pdf} \\[1em]
+\includegraphics{figures/u_contour_3.pdf} \\[1em]
 {\small The contour $\Gamma$ in the $u$ plane.}
@@
 \begin{center}
-\includegraphics{figures/zeta_contour.pdf} \\[1em]
+\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
 {\small The contour $\gamma_1$ in $\hat{\C}$.}

### 2022-02-07 figures/contours.jl

@@ -64,7 +64,7 @@ function edgept(θ)
 end
 
 # for a nice contour with θ at π or 4π, set `off` to (1.3, 0)
-function plotcontours(θ = 0, off = (0, 0), n = 3, k = 1; test = true)
+function plotcontour(θ = 0, off = (0, 0), n = 3, k = 1; tag = "test")
   dark = RGB(0, 0.5, 0.7)
   light = RGB(0.6, 0.9, 1.0)
   
@@ -106,9 +106,14 @@ function plotcontours(θ = 0, off = (0, 0), n = 3, k = 1; test = true)
   
   # === output ===
   
-  tag = test ? "_test" : ""
-  draw(PDF(string("u_contour", tag, ".pdf"), 6cm, 6cm), u_contour)
-  draw(PDF(string("zeta_contour", tag, ".pdf"), 6cm, 6cm), ζ_contour)
+  draw(PDF(string("u_contour_", tag, ".pdf"), 6cm, 6cm), u_contour)
+  draw(PDF(string("zeta_contour_", tag, ".pdf"), 6cm, 6cm), ζ_contour)
+end
+
+function plotmiddlecontours()
+  for (n, k) in [(3, 1), (5, 3), (7, 3), (9, 5)]
+    plotcontour(0, (0, 0), n, k, tag = string(n))
+  end
 end
 
 # === contour integrals ===

### 2022-02-10 draft2.tex
Clarify the 3/2-derivative formula check in the Airy case
The calculation was dubious as written. Now it should be almost
correct, pending a sign change in the definition of y.

@@
 
-Let us study the RHS of claim \eqref{claim 2}
+\textcolor{violet}{
+Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
+\begin{align*}
+w_1 & = \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6})} w_5 + \frac{\Gamma(\tfrac{5}{2}) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \\
+w_3 & = \frac{1}{e^{(5/3)\pi i} - e^{(7/3)\pi i}} \left[ e^{(-1/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3})} w_5 - e^{(-5/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3})} w_6 \right]
+\end{align*}
+Common denominators
+\begin{align*}
+w_1 & = \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 + \frac{\Gamma(\tfrac{5}{2}) \Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \\
+w_3 & = \frac{i}{\sqrt{3}} \left[ e^{(-1/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{(-5/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
+\end{align*}
+Extract
+\begin{align*}
+w_1 & = \frac{\Gamma(\tfrac{5}{2}) \tfrac{2}{\sqrt{3}}\pi}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 - \frac{\Gamma(\tfrac{5}{2}) \tfrac{2}{\sqrt{3}}\pi}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \\
+w_3 & = \frac{2\pi i}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{(-1/6) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{(-5/6) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
+\end{align*}
+\ldots
+\begin{align*}
+w_1 & = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 - \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \right] \\
+w_3 & = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
+\end{align*}
+Now subtract!
+\[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
+}
+Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that} $x = \tfrac{1}{2} + \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} + \tfrac{3}{4} s$
 \begin{align*}
 &\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
-&= -\frac{2}{9}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right)ds+\frac{2}{9}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right)ds & 15.8.28 \text{ DLMF} \\
-&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1+y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)\right]dy & x\in (-\infty,0) \\
-&=-\frac{\sqrt{3\pi}}{4}\Gamma(1/6)e^{-\frac{3}{2}\pi i}\int_0^x(x-y)^{-1/2}y^{-5/3}{}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)dy & \\
-&=-\frac{\sqrt{3}\pi}{4}\frac{\Gamma(1/6)\Gamma(7/6)}{\Gamma(5/3)}e^{-\frac{3}{2}\pi i} |x|^{-7/6}{}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) & \eqref{4.8} \\
-&=\frac{5\pi^2}{24\sqrt{3}}\frac{\Gamma(1/3)}{\Gamma(5/3)}\left({}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{\zeta}{4}\right)-e^{-\frac{11}{6}\pi i}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in (2/3,+\infty)
-%&=-\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};t\right)dt+\frac{4i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt & \zeta'=\frac{1}{2}-\frac{3}{4}\zeta\\
-%&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-t\right)dt -\frac{9i}{32}\textcolor{gray}{\int_{1}^{\zeta'}(\zeta'-t)^{-1/2}{}_2F_1\left(\frac{5}{3},\frac{7}{3};-\frac{1}{2};1-t\right)dt}& 15.10.21 \text{ DLMF }\\
-%&=\frac{2i}{9\sqrt{3}}\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{5}{2};1-t\right)t^{-3/2}dt &  15.10.13 \text{ DLMF }
+&= -\frac{2}{9} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
+&=-\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)\right]dy & x\in (-\infty,0) \\
+&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{(4/3) \pi i} \frac{y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{(5/3) \pi i} \frac{y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
+% do the integral
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \textcolor{red}{+} e^{(5/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) + e^{(5/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] & \eqref{4.8} \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\\
+& \qquad\qquad\qquad\qquad + \left.
+e^{(5/3) \pi i} e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/3) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{(2/3) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right.
+\\
+& \qquad\qquad\qquad\qquad \left.
++ i\tfrac{\sqrt{3}}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\\
+& \qquad\qquad\qquad\qquad \left.
+- i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{5}{6}) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{1}{6}) \Gamma(-\tfrac{2}{3})}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\\
+& \qquad\qquad\qquad\qquad \left.
+- i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
 \end{align*}
 however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$, thus the claim holds true.
+
+\textcolor{violet}{
+Alternate calculation with $\tfrac{1}{2}$ derivative:
+\begin{align*}
+&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2} {}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right) ds \\
+&= \frac{2}{3} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3s}{4}\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.27 \text{ DLMF} \\
+&=\frac{4}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1-y\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};y\right)\right]dy & x\in (-\infty,0) \\
+&=\frac{2i}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ \big(1+\tfrac{1}{\sqrt{3}}\big) y^{-2/3} {}_2F_1\left(\frac{2}{3}, \frac{1}{6}, \frac{1}{3};\frac{1}{y}\right) + \big(1-\tfrac{1}{\sqrt{3}}\big) y^{-4/3} {}_2F_1\left(\frac{4}{3}, \frac{5}{6}, \frac{5}{3};\frac{1}{y}\right) \right] ds \\
+&=\frac{2i}{3\sqrt{3}} \left[ \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{2}{3})} \big(1+\tfrac{1}{\sqrt{3}}\big) x^{-1/6} {}_2F_1\left(\frac{1}{6}, \frac{1}{6}, \frac{1}{3};\frac{1}{x}\right) + \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{4}{3})}\big(1-\tfrac{1}{\sqrt{3}}\big) x^{-5/6} {}_2F_1\left(\frac{5}{6}, \frac{5}{6}, \frac{5}{3};\frac{1}{x}\right) \right] ds & \eqref{4.8} \\
+&=??? & \zeta\in (2/3,+\infty)
+\end{align*}
+}
 

### 2022-02-11 draft2.tex
Confirm the 3/2-derivative formula in the Airy case?
I think the calculation works now, though it still needs double-
checking. I'm doubtful about the constant factor.

@@
 }
-Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that} $x = \tfrac{1}{2} + \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} + \tfrac{3}{4} s$
-\begin{align*}
-&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds=2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
+Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.
+\begin{align*}
+&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \\
+&= 2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
 &= -\frac{2}{9} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
-&=-\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)\right]dy & x\in (-\infty,0) \\
-&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{(4/3) \pi i} \frac{y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} + e^{(5/3) \pi i} \frac{y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
+&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
+&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+\\
+& \qquad\qquad\qquad\qquad\qquad\qquad\qquad \left.
++ e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0)
+\end{align*}
+Continue $w_5$ and $w_6$ clockwise around their singularities at zero.}
+\begin{align*}
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+\\
+& \qquad\qquad\qquad\qquad\qquad\qquad \left.
++ e^{-(2/3) \pi i} \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
 % do the integral
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \textcolor{red}{+} e^{(5/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) + e^{(5/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] & \eqref{4.8} \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{(4/3) \pi i} e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+\\
+& \qquad\qquad\qquad\qquad \left.
++ e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{-(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
+\\
+& \left.
+\qquad\qquad\qquad\qquad + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{-(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} e^{-(7/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
 & \qquad\qquad\qquad\qquad + \left.
-e^{(5/3) \pi i} e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{(1/3) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{(2/3) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right.
+e^{-(2/3) \pi i} e^{-(11/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(2/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\Gamma(\tfrac{3}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\Gamma(\tfrac{4}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(1/2) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
-& \qquad\qquad\qquad\qquad \left.
-+ i\tfrac{\sqrt{3}}{2} \left( e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad \left.
-- i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{5}{6}) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{1}{6}) \Gamma(-\tfrac{2}{3})}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ \tfrac{1}{2} \big(e^{(7/6) \pi i} - e^{(11/6) \pi i}\big)\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad \left.
-- i\tfrac{\sqrt{3}}{2} \left( e^{-(7/6) \pi i} \frac{\Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(11/6) \pi i} \frac{\Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right) \right] \\
-\end{align*}
-however, ${}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2/3,+\infty)$, thus the claim holds true.
+& \qquad\qquad\qquad\qquad\qquad\qquad\qquad + \left.
+e^{(1/2) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{5}{6^2} (-i) \left[ e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}}{\tfrac{4}{3}\,\tfrac{1}{3}\,\tfrac{2}{3}} \frac{5}{6^2} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{2}\pi)} (-i) \left[e^{(7/6) \pi i} - e^{(11/6) \pi i}\right]\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=\frac{5 \cdot 3\pi}{12^2} \frac{\sqrt{3}}{2} i\sqrt{3}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-x\right) \\
+&=\frac{5\pi i}{32} \,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{3\zeta}{4}\right) \\
+\end{align*}
+This matches the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}, as long as we continue from above the branch cut.
+This is consistent \textbf{(is it?)} with our continuations of $w_5$ and $w_6$ \textbf{(name)} in the calculation.
 

### 2022-02-11 draft2.tex
Fix sign error in y-x factor
Continue counterclockwise in 3/2-derivative check
Now we get w_+, as expected, instead of w_-.

@@
 \begin{claim}\label{claim 2}
+\textbf{[There should be a way to predict the correct normalization of the LHS.]}
 \begin{equation}
@@
 &\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \\
-&= 2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
-&= -\frac{2}{9} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
-&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
-&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+&= 2\int_{2/3}^{\zeta} (\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
+&= -\frac{2}{9} \int_{2/3}^{\zeta} (\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
+&=\frac{4}{9\sqrt{3}}\int_0^x (y-x)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
+&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x (y-x)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
@@
 \end{align*}
-Continue $w_5$ and $w_6$ clockwise around their singularities at zero.}
-\begin{align*}
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+Continue $w_5$ and $w_6$ counterclockwise around their singularities at zero.} Notice that $|y - x| = y - x$ on the integration path.
+\begin{align*}
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(10/3) \pi i} |y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
 & \qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ e^{-(2/3) \pi i} \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
++ e^{-(2/3) \pi i} \frac{e^{(14/3) \pi i} |y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ -\frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+\\
+& \qquad\qquad\qquad\qquad\qquad\qquad \left.
++ \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
 % do the integral
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ -\frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
 & \qquad\qquad\qquad\qquad \left.
-+ e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{-(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
++ \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
 \\
 & \left.
-\qquad\qquad\qquad\qquad + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{-(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} e^{-(7/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\qquad\qquad\qquad\qquad + \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{2}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
 & \qquad\qquad\qquad\qquad + \left.
-e^{-(2/3) \pi i} e^{-(11/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(2/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\Gamma(\tfrac{3}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\Gamma(\tfrac{4}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(1/2) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(-\tfrac{2}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{1}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
-& \qquad\qquad\qquad\qquad\qquad\qquad\qquad + \left.
-e^{(1/2) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{5}{6^2} (-i) \left[ e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}}{\tfrac{4}{3}\,\tfrac{1}{3}\,\tfrac{2}{3}} \frac{5}{6^2} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{2}\pi)} (-i) \left[e^{(7/6) \pi i} - e^{(11/6) \pi i}\right]\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=\frac{5 \cdot 3\pi}{12^2} \frac{\sqrt{3}}{2} i\sqrt{3}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-x\right) \\
-&=\frac{5\pi i}{32} \,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{3\zeta}{4}\right) \\
-\end{align*}
-This matches the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}, as long as we continue from above the branch cut.
-This is consistent \textbf{(is it?)} with our continuations of $w_5$ and $w_6$ \textbf{(name)} in the calculation.
+& \qquad\qquad\qquad\qquad + \left.
+\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{1}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{2}{3} \pi)}{\pi} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\\
+& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3} \pi)}{\pi} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\sqrt{3}}{2\pi} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right]
+\end{align*}
+Using DLMF~15.10.25, we see this is
+\begin{align*}
+&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{3})\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\pi \sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=-\frac{5\pi}{32} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;x\right) \\
+&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{3\zeta}{4}\right) \\
+&=-\frac{5\pi}{32}\hat{w}_+(\zeta - 2/3)
+\end{align*}
+This matches $-\sqrt{\pi}$ times the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}.
 

### 2022-02-17 draft2.tex
Include whole thimble in 3/2-derivative argument
Also make some stylistic changes. Feel free to revert those!

@@
 \end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descendet path through the critical point $x_\alpha$. 
+where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
+Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
 \begin{theorem}\label{thm:maxim} Let $N=1$.
 Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then
+Then:
 \begin{enumerate}
-\item $\tilde{\varphi}_\alpha$ is Gevrey-1;
-\item $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ is a germ of analytic function at $\zeta=\zeta_{\alpha}=f(x_\alpha)$;
-\item the following formual holds true
-\begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-1/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
-\end{multline} 
+\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
+\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
+\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
+\begin{align*}\label{formula1}
+\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha}\left(\int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
+& = \Gamma\big(-\tfrac{1}{2}\big)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta')}^{\operatorname{end} \mathcal{C}_\alpha(\zeta')} \right)}\,d\zeta',
+\end{align*}
+where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
 \end{enumerate}
@@
 \begin{proof}
-Part $(1)$: Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
-By the steepest descendet method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
+Part~(1): Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
+By the steepest descent method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
 \begin{align*}
@@
 
-Part $(2)$: \begin{align*}
+Part~(2): \begin{align*}
 \hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
@@
 
-Part $(3)$: thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
-\begin{equation}
-\partial^{1/2}_{\zeta, \text{based at }\zeta_\alpha}\hat{I}_{\alpha}(\zeta)=\hat{\varphi}_{\alpha}(\zeta).
-\end{equation} 
-In addition, we notice 
-\begin{align*}
-I_{\alpha}(z)&=\int_{\mathcal{C}_{\alpha}}e^{-zf}\nu & f=\zeta\\
-&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Hankel countour} \\
-&=:\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\hat{I}_{\alpha}(\zeta)d\zeta &
-\end{align*}
-hence 
-\begin{equation}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{1/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)\right)=\partial^{3/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)
-\end{equation}
+Part~(3): thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
+\begin{equation}
+\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\hat{I}_{\alpha}(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
+\end{equation}
+%%Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
+Noticing that $f \circ \mathcal{C}^\pm_\alpha$ are both injective, we can recast the integral $I_\alpha$ into the $f$ plane.
+%%\[ I_{\alpha}(z) = \int_{\mathcal{C}^-_{\alpha}} e^{-zf} \nu + \int_{\mathcal{C}^+_{\alpha}} e^{-zf} \nu \]
+Let's recast the integral $I_\alpha$ into the $f$ plane.
+Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
+As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
+Hence, we have
+\begin{align*}
+I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
+& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
+\end{align*}
+Noticing that the right-hand side is a Laplace transform, we learn that
+\[ \hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}. \]
+Observing that
+\[ \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}, \]
+we conclude that
+\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta. \]
+Hence
+\begin{align*}
+\hat{\varphi}_{\alpha}(\zeta) & = \partial^{1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha \\
+& = \partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta.
+\end{align*}
 \end{proof}
@@
 \end{multline}
-which can be rewritten as 
+which can be rewritten as \textbf{(\texttt{arXiv:1504.08144}, formula~4.8)}
 \begin{multline}

### 2022-02-18 draft2.tex
Show Borel resummation works in 3/2-derivative argument
Also, spell out more details of the saddle point approximation.

@@
 \end{align*}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
+Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
+\item
 \end{enumerate}
@@
 \begin{proof}
+Part~(1): Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
+
+Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
+Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+\textbf{[We should explicitly spell out and check the conditions that make this possible.
+I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
+that converges in some disk $|\tau| < \varepsilon$.
+
+By the steepest descent method,
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
+\begin{align*}
+e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
+\end{align*}
+By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
+= 1$.}
+\begin{align*}
+e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
+These terms are crucial, however, for the convergence of the sum.
+To see why, consider their absolute sum $C_\text{exp}$.
+When $z \in [0, \infty)$,
+\begin{align*}
+C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
+& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
+& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
+\end{align*}
+which diverges for typical $f$ and $\nu$.
+
+This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. For each cutoff $N$, the tail
+\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
+is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
+\begin{align*}
+C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
+& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
+& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
+\end{align*}
+is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}. Hence,
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
+Call the right-hand side $\tilde{I}_\alpha$.
+We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
+\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
+\begin{align*}
+\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha) & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
+\end{align*}
+
+We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
+Recalling that $(2n - 1)!!
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
+
+\color{violet}
 Part~(1): Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
@@
 &-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
-&\sim_{\varepsilon<<1} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
+&\sim_{\textcolor{red}{\varepsilon \ll 1}} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
 \end{align*} 
 therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]
+\textbf{[The value of $\varepsilon$ shouldn't affect the asymptotic series! I think we want the limit $z \to \infty$ rather than $\varepsilon \ll 1$.]}
 
@@
 where we use $(2n-1)!!\sim \tfrac{2^n}{\sqrt{\pi n}}n!$ as $n\to \infty$.
+\color{black}
 
@@
 Part~(3): thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
-\begin{equation}
-\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\hat{I}_{\alpha}(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
+\begin{equation}\label{formal-half-deriv}
+\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\mathcal{B}(\tilde{I}_{\alpha})(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
 \end{equation}
@@
 Let's recast the integral $I_\alpha$ into the $f$ plane.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
 As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
@@
 \[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta. \]
-Hence
+
+We can rewrite our Taylor series for $\nu$ as
+\begin{align*}
+\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
+& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
+\begin{align*}
+\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
+& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
+& = \mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha).
+\end{align*}
+We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ would be asymptotic to $\hat{I}_\alpha$.
+We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ is actually equal to $\hat{I}_\alpha$, strengthening the formal series identity~\ref{formal-half-deriv} to the analytic identity
 \begin{align*}
@@
 
-\textcolor{violet}{
+\color{violet}
 Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
@@
 \[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
-}
+\color{black}
 Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.

### 2022-02-19 draft2.tex
Write more details about fractional derivatives
Start explaining why the Riemann-Liouville derivative should work
best for our purposes. Watch out: later text still uses the Caputo
ordering!

@@
 \numberwithin{equation}{section}
+
+% Veronica's custom commands
 \input{command}
+
+% Laplace and Borel transforms
+\newcommand{\laplace}{\mathcal{L}}
+\newcommand{\borel}{\mathcal{B}}
+
 \DeclareRobustCommand{\subtitle}[1]{\\#1}
@@
 %and $a_n\defeq (-1)^n\frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$.
-Analougusly, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
+Analogously, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
 %
@@
 \section{Fractional derivatives and Borel transform}
-
+\begin{definition}
+For $\alpha \in (0, 1)$, the fractional integral $\partial^{\alpha-1}_{x \text{ from } 0}$ is defined by
+\[ \partial^{\alpha-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\alpha)} \int_0^x (x-x')^{-\alpha} f(x')\,dx'. \]
+\end{definition}
+Fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined for integers $n \ge -1$ by composing the fractional integral with powers of $\tfrac{\partial}{\partial x}$.
+However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
+Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that depend on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
+We'll use the {\em Riemann-Liouville} convention.
+\begin{definition}
+For $\alpha \in (0, 1)$ and $n \ge -1$ integer, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
+\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
+\end{definition}
+Each convention brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for more.} The Riemann-Liouville convention will be the least annoying for our purposes.
+\begin{theorem}
+Take a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$. For $\alpha \in (0, 1)$ and $n \ge -1$, we have
+\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^{n+\alpha} \varphi \right](\zeta) \]
+\end{theorem}
+
+\begin{lemma}
+For $\alpha \in (0, 1)$ and $n \ge -1$,
+\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^{n+\alpha} z^{-(k+1)} \right](\zeta) \]
+\end{lemma}
+\begin{proof}
+First, evaluate
+\begin{align*}
+\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(k-\alpha)}
+%%& = \left[ \borel z^{-[k-(\alpha-1)+1]} \right](\zeta) \\
+%%& = \left[ \borel z^{\alpha-1} z^{-[k+1]} \right](\zeta)
+\end{align*}
+by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
+\begin{equation}\label{frac-diff-laplace}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\end{equation}
+for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
+\end{align*}
+Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
+The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
+This is how we avoid the initial value corrections that appear in integer-order derivatives of Borel transforms.
+\end{proof}
+\color{MidnightBlue}
 \begin{definition}
@@
 In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$.
-Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways:
+Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways: \textbf{[Can we do this when $\varphi$ isn't in $o(z^n)$?]}
 \begin{multline}
@@
 and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
-
+\color{black}
 \section{Resurgence of exponential integrals}
-
 Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
-
 \begin{equation}
@@
 \begin{align*}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha}\left(\int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
-& = \Gamma\big(-\tfrac{1}{2}\big)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta')}^{\operatorname{end} \mathcal{C}_\alpha(\zeta')} \right)}\,d\zeta',
+\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
+& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)}\,d\zeta',
 \end{align*}
@@
 Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
+\textbf{[The integral over $\mathcal{C}_\alpha(\zeta)$ needs to satisfy some condition near $\zeta = 0$ for this to hold.
+Figure out what that is!
+Also, be careful about the orientation of $\mathcal{C}_\alpha$.]}
 \item
@@
 \begin{equation}
-\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
+\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s} \left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]\,ds \qquad \zeta\in(2/3,+\infty)
 \end{equation}
@@
 
-\color{violet}
+\color{Turquoise}
 Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
@@
 \[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
-\color{black}
+\color{MidnightBlue}
 Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.
@@
 
-\textcolor{violet}{
+\color{violet}
 Alternate calculation with $\tfrac{1}{2}$ derivative:
@@
 \end{align*}
-}
-
-Analougusly, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
+\color{black}
+
+Analogously, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
 %By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus

### 2022-02-19 draft2.tex
Start from higher-order fractional integrals

@@
 \section{Fractional derivatives and Borel transform}
-\begin{definition}
-For $\alpha \in (0, 1)$, the fractional integral $\partial^{\alpha-1}_{x \text{ from } 0}$ is defined by
-\[ \partial^{\alpha-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\alpha)} \int_0^x (x-x')^{-\alpha} f(x')\,dx'. \]
-\end{definition}
-Fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined for integers $n \ge -1$ by composing the fractional integral with powers of $\tfrac{\partial}{\partial x}$.
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
+\[ \partial^{\nu-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
+It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
+\begin{align*}
+\partial^{\mu-1}_{x \text{ from } 0} \partial^{\nu-1}_{x \text{ from } 0} & = \partial^{(\mu-1)+(\nu-1)}_{x \text{ from } 0} & \mu, \nu \in (-\infty, 1),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
+
+For $\alpha \in (0, 1)$ and integers $n \ge -1$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
 However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
-Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that depend on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
+Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
 We'll use the {\em Riemann-Liouville} convention.
 \begin{definition}
-For $\alpha \in (0, 1)$ and $n \ge -1$ integer, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
+For $\alpha \in (0, 1)$ and integers $n \ge -1$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
 \[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
 \end{definition}
-Each convention brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for more.} The Riemann-Liouville convention will be the least annoying for our purposes.
+Each convention brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville convention will be the least annoying for our purposes.
+Here's what's nice about it.
 \begin{theorem}
-Take a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$. For $\alpha \in (0, 1)$ and $n \ge -1$, we have
+Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
 \[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^{n+\alpha} \varphi \right](\zeta) \]
+for all $\alpha \in (0, 1)$ and $n \ge -1$.
 \end{theorem}
@@
 The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in integer-order derivatives of Borel transforms.
+This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
 \end{proof}

### 2022-02-21 draft2.tex
Sketch more careful 3/2-derivative argument
Also, simplify notation in fractional calculus identities.

@@
 \begin{align*}
-\partial^{\mu-1}_{x \text{ from } 0} \partial^{\nu-1}_{x \text{ from } 0} & = \partial^{(\mu-1)+(\nu-1)}_{x \text{ from } 0} & \mu, \nu \in (-\infty, 1),
+\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda, \mu \in (-\infty, 0),
 \end{align*}
@@
 
-For $\alpha \in (0, 1)$ and integers $n \ge -1$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
 However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
@@
 \begin{definition}
-For $\alpha \in (0, 1)$ and integers $n \ge -1$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
 \[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
 \end{definition}
-Each convention brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville convention will be the least annoying for our purposes.
+The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+
+Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
 Here's what's nice about it.
@@
 Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
-\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^{n+\alpha} \varphi \right](\zeta) \]
-for all $\alpha \in (0, 1)$ and $n \ge -1$.
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
+for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
 \end{theorem}
+\color{Turquoise}
+Here's how we'll use this later. By definition, $\tilde{I}_p(z) = z^{-1/2}\tilde{\varphi}_p(z)$, so the theorem gives
+\begin{align*}
+\left[ \borel_{\zeta_\alpha} \tilde{I}_p \right](\zeta) & = \left[ \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_p \right](\zeta) \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \left[ \borel \tilde{\varphi}_p \right](\zeta) \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta).
+\end{align*}
+Once we show that $\borel \tilde{I}_p = \hat{I}_p$, we have
+\begin{align*}
+\hat{I}_p(\zeta) & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta) \\
+\partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) & = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta)
+\end{align*}
+thanks to the semigroup law. Once we show that
+\[ \hat{I}_p(\zeta) = \tfrac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right), \]
+we can deduce that
+\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) = \int_{\mathcal{C}_p(\zeta)} \nu - \int_{\mathcal{C}_p(0)} \nu. \]
+The path $\mathcal{C}_p(0)$ is a point, so the initial value term vanishes, and we can conclude that
+\[ \int_{\mathcal{C}_p(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta). \]
+Finally, recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we see that
+\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \int_{\mathcal{C}_p(\zeta)} \nu = \hat{\varphi}_p(\zeta). \]
+\color{black}
 
 \begin{lemma}
-For $\alpha \in (0, 1)$ and $n \ge -1$,
-\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^{n+\alpha} z^{-(k+1)} \right](\zeta) \]
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^\mu z^{-(k+1)} \right](\zeta). \]
 \end{lemma}
 \begin{proof}
-First, evaluate
+We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
 \begin{align*}
@@
 & = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(k-\alpha)}
-%%& = \left[ \borel z^{-[k-(\alpha-1)+1]} \right](\zeta) \\
-%%& = \left[ \borel z^{\alpha-1} z^{-[k+1]} \right](\zeta)
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
 \end{align*}

### 2022-02-21 draft2.tex
Write out careful 3/2-derivative argument

@@
 Here's what's nice about it.
-\begin{theorem}
+\begin{theorem}\label{thm:frac-diff-borel}
 Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
@@
 \begin{enumerate}
-\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
-\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
+\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
+\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
+\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
+\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
 \begin{align*}\label{formula1}
 \hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
-& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)}\,d\zeta',
+& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
 \end{align*}
@@
 Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[The integral over $\mathcal{C}_\alpha(\zeta)$ needs to satisfy some condition near $\zeta = 0$ for this to hold.
-Figure out what that is!
-Also, be careful about the orientation of $\mathcal{C}_\alpha$.]}
-\item
+\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
 \end{enumerate}
@@
 \begin{proof}
-Part~(1): Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
+Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
 
@@
 \begin{align*}
-\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha) & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
 & = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
@@
 
-Part~(2): \begin{align*}
+Part~\eqref{int:resum-converges}: \begin{align*}
 \hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
@@
 
-Part~(3): thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
-\begin{equation}\label{formal-half-deriv}
-\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\mathcal{B}(\tilde{I}_{\alpha})(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
-\end{equation}
-%%Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-Noticing that $f \circ \mathcal{C}^\pm_\alpha$ are both injective, we can recast the integral $I_\alpha$ into the $f$ plane.
-%%\[ I_{\alpha}(z) = \int_{\mathcal{C}^-_{\alpha}} e^{-zf} \nu + \int_{\mathcal{C}^+_{\alpha}} e^{-zf} \nu \]
-Let's recast the integral $I_\alpha$ into the $f$ plane.
+Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
 As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
@@
 Noticing that the right-hand side is a Laplace transform, we learn that
-\[ \hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}. \]
-Observing that
-\[ \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}, \]
-we conclude that
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta. \]
+\begin{equation}\label{thimble-difference}
+\hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
+\end{equation}
 
@@
 & = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha).
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ is actually equal to $\hat{I}_\alpha$, strengthening the formal series identity~\ref{formal-half-deriv} to the analytic identity
-\begin{align*}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha \\
-& = \partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta.
-\end{align*}
+& = \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha.
+\end{align*}
+We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
+We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
+
+Theorem~\ref{thm:frac-diff-borel} tells us that
+\begin{align*}
+\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\end{align*}
+It follows, from our conclusion above, that
+\begin{equation}\label{shifted-resum-valid}
+\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\end{equation}
+Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
+\begin{align*}
+I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
+& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
+\end{align*}
+as we claimed.
+
+Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
+\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
+Rewriting equation~\eqref{thimble-difference} as
+\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
+we can see that
+\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
+The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
+\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
+Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
+\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
 \end{proof}

### 2022-02-22 draft2.tex
changes

--- 2022-02-19 draft2.tex
@@
 \numberwithin{equation}{section}
-
-% Veronica's custom commands
 \input{command}
-
-% Laplace and Borel transforms
-\newcommand{\laplace}{\mathcal{L}}
-\newcommand{\borel}{\mathcal{B}}
-
 \DeclareRobustCommand{\subtitle}[1]{\\#1}
@@
 %and $a_n\defeq (-1)^n\frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$.
-Analogously, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
+Analougusly, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
 %
@@
 \section{Fractional derivatives and Borel transform}
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-\[ \partial^{\nu-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
-\begin{align*}
-\partial^{\mu-1}_{x \text{ from } 0} \partial^{\nu-1}_{x \text{ from } 0} & = \partial^{(\mu-1)+(\nu-1)}_{x \text{ from } 0} & \mu, \nu \in (-\infty, 1),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
-
-For $\alpha \in (0, 1)$ and integers $n \ge -1$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
-However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
-Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}
-For $\alpha \in (0, 1)$ and integers $n \ge -1$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
-\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
-\end{definition}
-Each convention brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville convention will be the least annoying for our purposes.
-Here's what's nice about it.
-\begin{theorem}
-Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
-\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^{n+\alpha} \varphi \right](\zeta) \]
-for all $\alpha \in (0, 1)$ and $n \ge -1$.
-\end{theorem}
-
-\begin{lemma}
-For $\alpha \in (0, 1)$ and $n \ge -1$,
-\[ \partial^{n+\alpha}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^{n+\alpha} z^{-(k+1)} \right](\zeta) \]
-\end{lemma}
-\begin{proof}
-First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(k-\alpha)}
-%%& = \left[ \borel z^{-[k-(\alpha-1)+1]} \right](\zeta) \\
-%%& = \left[ \borel z^{\alpha-1} z^{-[k+1]} \right](\zeta)
-\end{align*}
-by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-\color{MidnightBlue}
+
 \begin{definition}
@@
 In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$.
-Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways: \textbf{[Can we do this when $\varphi$ isn't in $o(z^n)$?]}
+Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways:
 \begin{multline}
@@
 and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
-\color{black}
+
 \section{Resurgence of exponential integrals}
+
 Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
+
 \begin{equation}
@@
 \end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+where $\mathcal{C}_\alpha$ is a steepest descendet path through the critical point $x_\alpha$. 
 \begin{theorem}\label{thm:maxim} Let $N=1$.
 Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then:
+Then
 \begin{enumerate}
-\item The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item The series $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
-\item For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
-\begin{align*}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
-& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)}\,d\zeta',
-\end{align*}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
-Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[The integral over $\mathcal{C}_\alpha(\zeta)$ needs to satisfy some condition near $\zeta = 0$ for this to hold.
-Figure out what that is!
-Also, be careful about the orientation of $\mathcal{C}_\alpha$.]}
-\item
+\item $\tilde{\varphi}_\alpha$ is Gevrey-1;
+\item $\hat{\varphi}(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ is a germ of analytic function at $\zeta=\zeta_{\alpha}=f(x_\alpha)$;
+\item the following formual holds true
+\begin{multline}\label{formula1}
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-1/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\int_{f^{-1}(\zeta')}\frac{\nu}{df}\right)} d\zeta'
+\end{multline} 
 \end{enumerate}
@@
 \begin{proof}
-Part~(1): Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
-
-Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
-\textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-These terms are crucial, however, for the convergence of the sum.
-To see why, consider their absolute sum $C_\text{exp}$.
-When $z \in [0, \infty)$,
-\begin{align*}
-C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-which diverges for typical $f$ and $\nu$.
-
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. For each cutoff $N$, the tail
-\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
-is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
-\begin{align*}
-C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \N_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}. Hence,
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
-Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
-\begin{align*}
-\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha) & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-\color{violet}
-Part~(1): Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
-By the steepest descent method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
+Part $(1)$: Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
+By the steepest descendet method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
 \begin{align*}
@@
 &-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
-&\sim_{\textcolor{red}{\varepsilon \ll 1}} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
+&\sim_{\varepsilon<<1} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
 \end{align*} 
 therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]
-\textbf{[The value of $\varepsilon$ shouldn't affect the asymptotic series! I think we want the limit $z \to \infty$ rather than $\varepsilon \ll 1$.]}
 
@@
 where we use $(2n-1)!!\sim \tfrac{2^n}{\sqrt{\pi n}}n!$ as $n\to \infty$.
-\color{black}
-
-Part~(2): \begin{align*}
+
+Part $(2)$: \begin{align*}
 \hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
@@
 
-Part~(3): thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
-\begin{equation}\label{formal-half-deriv}
-\partial^{1/2}_{\zeta \text{ from }\zeta_\alpha}\mathcal{B}(\tilde{I}_{\alpha})(\zeta) = \hat{\varphi}_{\alpha}(\zeta).
-\end{equation}
-%%Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-Noticing that $f \circ \mathcal{C}^\pm_\alpha$ are both injective, we can recast the integral $I_\alpha$ into the $f$ plane.
-%%\[ I_{\alpha}(z) = \int_{\mathcal{C}^-_{\alpha}} e^{-zf} \nu + \int_{\mathcal{C}^+_{\alpha}} e^{-zf} \nu \]
-Let's recast the integral $I_\alpha$ into the $f$ plane.
-As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
-Hence, we have
-\begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
-\end{align*}
-Noticing that the right-hand side is a Laplace transform, we learn that
-\[ \hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}. \]
-Observing that
-\[ \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}, \]
-we conclude that
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta. \]
-
-We can rewrite our Taylor series for $\nu$ as
-\begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
-\begin{align*}
-\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha).
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha}(\tilde{I}_\alpha)$ is actually equal to $\hat{I}_\alpha$, strengthening the formal series identity~\ref{formal-half-deriv} to the analytic identity
-\begin{align*}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha \\
-& = \partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)\,d\zeta.
-\end{align*}
+Part $(3)$: thanks to properties of Caputo's fractional derivatives, we have that the Borel transform of $\tilde{I}_{\alpha}(z)=z^{-1/2}\tilde{\varphi}_\alpha(z)$ is 
+\begin{equation}
+\partial^{1/2}_{\zeta, \text{based at }\zeta_\alpha}\hat{I}_{\alpha}(\zeta)=\hat{\varphi}_{\alpha}(\zeta).
+\end{equation} 
+In addition, we notice 
+\begin{align*}
+I_{\alpha}(z)&=\int_{\mathcal{C}_{\alpha}}e^{-zf}\nu & f=\zeta\\
+&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)d\zeta   & \mathcal{H}_{\alpha} \text{ is Hankel countour} \\
+&=:\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\hat{I}_{\alpha}(\zeta)d\zeta &
+\end{align*}
+hence 
+\begin{equation}
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{1/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\partial_{\zeta}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)\right)=\partial^{3/2}_{\zeta, \text{based at } \zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)
+\end{equation}
 \end{proof}
@@
 \begin{align*}
-\hat{u}_+(\zeta)&=C_1 T_{-2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-2/3}\hat{w}_+(\zeta)\\
-\hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
-%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
+\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\,\, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\,\,\hat{w}_+(\zeta)\\
+\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\,\, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\,\,\hat{w}_-(\zeta) & \\
+%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{2}F_{1}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{2}F_{1}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
 \end{align*}
@@
 \begin{claim}\label{claim 2}
-\textbf{[There should be a way to predict the correct normalization of the LHS.]}
-\begin{equation}
-\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s} \left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]\,ds \qquad \zeta\in(2/3,+\infty)
+\begin{equation}
+\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
 \end{equation}
@@
 
-\color{Turquoise}
+\textcolor{violet}{
 Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
@@
 \[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
-\color{MidnightBlue}
+}
 Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.
@@
 &\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds   \\
-&= 2\int_{2/3}^{\zeta} (\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
-&= -\frac{2}{9} \int_{2/3}^{\zeta} (\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
-&=\frac{4}{9\sqrt{3}}\int_0^x (y-x)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
-&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x (y-x)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+&= 2\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds  \\
+&= -\frac{2}{9} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
+&=\frac{4}{9\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
+&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
@@
 \end{align*}
-Continue $w_5$ and $w_6$ counterclockwise around their singularities at zero.} Notice that $|y - x| = y - x$ on the integration path.
-\begin{align*}
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(10/3) \pi i} |y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+Continue $w_5$ and $w_6$ clockwise around their singularities at zero.}
+\begin{align*}
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x(x-y)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
 & \qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ e^{-(2/3) \pi i} \frac{e^{(14/3) \pi i} |y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ -\frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
-\\
-& \qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
++ e^{-(2/3) \pi i} \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
 % do the integral
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ -\frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
+&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
 \\
 & \qquad\qquad\qquad\qquad \left.
-+ \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
++ e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{-(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
 \\
 & \left.
-\qquad\qquad\qquad\qquad + \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{2}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+\qquad\qquad\qquad\qquad + e^{-(2/3) \pi i} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{-(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ e^{-(1/3) \pi i} e^{-(7/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
 & \qquad\qquad\qquad\qquad + \left.
-\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(-\tfrac{2}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{1}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
+e^{-(2/3) \pi i} e^{-(11/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \frac{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(2/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) + e^{-(1/3) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\Gamma(\tfrac{3}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\Gamma(\tfrac{4}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})} \left[ e^{-(1/2) \pi i} e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
 \\
-& \qquad\qquad\qquad\qquad + \left.
-\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{1}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{2}{3} \pi)}{\pi} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3} \pi)}{\pi} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\sqrt{3}}{2\pi} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right]
-\end{align*}
-Using DLMF~15.10.25, we see this is
-\begin{align*}
-&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{3})\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\pi \sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\pi}{32} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;x\right) \\
-&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{3\zeta}{4}\right) \\
-&=-\frac{5\pi}{32}\hat{w}_+(\zeta - 2/3)
-\end{align*}
-This matches $-\sqrt{\pi}$ times the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}.
-
-\color{violet}
+& \qquad\qquad\qquad\qquad\qquad\qquad\qquad + \left.
+e^{(1/2) \pi i} e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{2})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} \frac{5}{6^2} (-i) \left[ e^{-(1/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - e^{-(5/6) \pi i} \frac{\Gamma(2) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
+&=\frac{8\pi}{27} \frac{\tfrac{3}{2}\,\tfrac{1}{2}}{\tfrac{4}{3}\,\tfrac{1}{3}\,\tfrac{2}{3}} \frac{5}{6^2} \frac{\sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{2}\pi)} (-i) \left[e^{(7/6) \pi i} - e^{(11/6) \pi i}\right]\,w_3(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
+&=\frac{5 \cdot 3\pi}{12^2} \frac{\sqrt{3}}{2} i\sqrt{3}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-x\right) \\
+&=\frac{5\pi i}{32} \,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}+\frac{3\zeta}{4}\right) \\
+\end{align*}
+This matches the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}, as long as we continue from above the branch cut.
+This is consistent \textbf{(is it?)} with our continuations of $w_5$ and $w_6$ \textbf{(name)} in the calculation.
+
+\textcolor{violet}{
 Alternate calculation with $\tfrac{1}{2}$ derivative:
@@
 \end{align*}
-\color{black}
-
-Analogously, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
+}
+
+Analougusly, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.  
 %By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
@@
 \begin{equation}
-\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
+\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta'^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
 \end{equation}
@@
 \begin{proof}
-Let us first consider the RHS of \eqref{Bessel}
-\begin{align*}
-&2\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'= &\\
-&\quad = \frac{4}{3}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' &\\
-&\quad =\frac{8}{3}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};y\right)-{}_2F_1\left(2,2;\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0)\\
-&\quad =2\pi\int_0^x(x-y)^{-1/2}y^{-2}F\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \eqref{4.8} \\
-&\quad =\pi^2|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & x\in (-\infty, 0)\\
-&\quad =\frac{\pi^2}{2}\left({}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}-\frac{\zeta}{4}\right)-i{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in(2,+\infty)
-\end{align*}
+Let us first consider the RHS of \eqref{Bessel}. Note $x=\frac{1}{2}-\frac{\zeta}{4}$ and $y=\frac{1}{2}-\frac{\zeta'}{4}$
+\begin{align*}
+&2\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta'^2}{4}\right)d\zeta'= &\\
+&\quad =- \frac{2}{3\pi}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' & 15.8.28 \text{ DLMF}\\
+&\quad =- \frac{4}{3\pi}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};1-y\right)-{}_2F_1\left(2,2;\frac{5}{2};y\right)\right]dy & x\in (-\infty,0)\\
+&\quad = -\frac{4}{3\pi}\int_0^xe^{-(1/2)\pi i}(x-y)^{-1/2}\left[\frac{3\pi}{4}e^{-(1/2)\pi i}y^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)\right]dy & 15.10.30 \text{ DLMF} \\
+&\quad = -\int_0^x e^{-(1/2)\pi i}(x-y)^{-1/2}e^{-(1/2)\pi i}y^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
+&\quad = -\int_0^x(x-y)^{-1/2} |y|^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
+&\quad = -\int_0^x e^{-(1/2)\pi i}|x-y|^{-1/2} |y|^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
+&\quad = -e^{-(1/2)\pi i}\frac{\Gamma\left(\frac{1}{2}\right)\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & \eqref{4.8} \\
+&\quad = -e^{-(1/2)\pi i}\frac{\pi}{2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) &  \\
+&\quad =-\frac{\pi}{2}w_6(3/2,3/2,2) & \\
+&\quad =-\frac{\pi}{2}\frac{\Gamma\left(3/2\right)\Gamma(1)}{\Gamma(2)\Gamma(3/2)}e^{(c-a)\pi i}\left(w_1(a,b,c)-e^{a\pi i}\frac{\Gamma(2)\Gamma(1/2)}{\Gamma(2)\Gamma(1/2)}w_3\right)
+\end{align*}
+
+\textcolor{violet}{ From DLMF 15.10.17
+\begin{align*}
+w_3(a,b,c)&=\frac{\Gamma\left(1-c\right)\Gamma\left(a+b-c+1\right)}{\Gamma\left(a-c+1\right)\Gamma\left(b-c+1\right)}w_1(a,b,c)+\frac{\Gamma\left(c-1\right)\Gamma\left(a+b-c+1\right)}{\Gamma\left(a\right)\Gamma\left(b\right)}w_2(a,b,c)\\
+w_3(2,2,\frac{5}{2})&=w_1(2,2,\frac{5}{2})+\frac{3\pi}{8}w_2(2,2,\frac{5}{2})\\
+\end{align*}
+}
 however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$, thus the claim holds true. 
@@
 \end{multline}
+%\begin{multline}
+%\label{4.1}
+%\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)|x-y|^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
+%x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
+%\end{multline}
 
@@
 \label{4.5}
-\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
+\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)|x-y|^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
 x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0
 \end{multline}
-which can be rewritten as \textbf{(\texttt{arXiv:1504.08144}, formula~4.8)}
+which can be rewritten as 
 \begin{multline}

### 2022-02-22 modified bessel.tex
changes

@@
 
-The modified Bessel function of the second kind is a solution of the equation
+The modified Bessel function of the second kind $K_\nu(z)$ is a solution of the equation
 \begin{equation}\label{Bessel_nu}
@@
 \end{equation}
-such that $K_{\nu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$.
-It has a branch point at $z=0$ for every $\nu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$.
+such that $K_{\nu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$\footnote{A system of solution of Bessel equation is given by $I_\nu(z)$ and $K_\nu(z)$.
+In particular, their asymptotic behaviour as $z\to\infty$ is given by \begin{align}
+\tilde{I}_\nu(z)&=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\nu\right)_k\left(\frac{1}{2}+\nu\right)_k}{2^kk!}z^{-k}\\
+\tilde{K}_{\nu}(z)&=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\nu\right)_k\left(\frac{1}{2}+\nu\right)_k}{(-2)^kk!}z^{-k}
+\end{align}}. It has a branch point at $z=0$ for every $\nu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
 \subsection{Differential equation}
-From the general theory of ODE, the formal integral solution of \eqref{Bessel_nu} is two parameter family 
+From the general theory of ODE, the formal integral solution of \eqref{Bessel_nu} is two parameters family 
 \begin{equation}
@@
 \end{equation} 
-where $\tilde{w}_{\nu,\pm}=1+\sum_{j\geq 1}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
+where $\tilde{w}_{\nu,\pm}=\sum_{j\geq 0}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
 \begin{align*}
-\tilde{w}_{\nu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_+}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,+}=0\\
+\tilde{w}_{\nu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_{\nu,+}}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,+}=0\\
 \tilde{w}_{\nu,-}''+2\tilde{w}_{\nu,-}'+\frac{\tilde{w}_{\nu,-}}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,-}=0
 \end{align*} 
-In particular, $K_{\nu}(z)=e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)$. We now compute the Borel transform of $\tilde{w}_+(z)$: it is a solution of 
+In particular, $\tilde{K}_{\nu}(z)=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)$ and $\tilde{I}_\nu(z)=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\tilde{w}_{\nu,-}(z)$ (once we choose $a_{\pm,0}=1$).
+We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\nu,\pm}$, i.e.
+$\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.} it is a solution of
 \begin{align*}
@@
 \begin{align*}
-\hat{w}_{\nu,+}(\zeta+i0)-\hat{w}_{\nu,+}(\zeta-i0)&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\nu,\frac{1}{2}+\nu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
+\hat{w}_{\nu,+}(\zeta+i0)-\hat{w}_{\nu,+}(\zeta-i0)&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}+\nu,\frac{1}{2}-\nu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
 &=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
 &=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\nu+k\right)\Gamma\left(\tfrac{3}{2}+\nu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
-&=-2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1+\frac{\zeta}{2}\right) & \\
+&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\frac{1}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\sum_{k\geq 1}\frac{\Gamma\left(\tfrac{1}{2}-\nu+k\right)\Gamma\left(\tfrac{1}{2}+\nu+k\right)}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\frac{1}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\nu+k\right)\Gamma\left(\tfrac{3}{2}+\nu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
+&=-\frac{2\pi i}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1+\frac{\zeta}{2}\right) & \\
 &=-2i\cos(\nu \pi)\hat{w}_{\nu,-}(\zeta+2)
@@
 
-\begin{multline}
-K_{\nu}(z)=\frac{1}{2i\nu\sin(\nu\pi)}\int_{\mathcal{C}_{\alpha}}e^{zT_{\frac{1}{\nu}}(u)}du=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\frac{d\zeta}{U_{\frac{1}{\nu}-1}(u)}=\\
-=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)d\zeta
-\end{multline}
+\begin{align*}
+K_{\nu}(z)&=\frac{1}{2 i\sin(\nu \pi)}\int_{\mathcal{C}_{\alpha}}e^{z\cosh(t)}\sinh(\nu t) dt & u=\cosh(\nu t)\\
+&=-\frac{1}{2i\nu\sin(\nu\pi)}\int_{\mathcal{C}_{\alpha}}e^{zT_{\frac{1}{\nu}}(u)}du & \zeta=T_{\frac{1}{\nu}}(u)\\
+&=\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\frac{d\zeta}{U_{\frac{1}{\nu}-1}(u)}\\
+&=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)d\zeta
+\end{align*}
 where $\mathcal{C}_{\alpha}$ \textbf{has to be checked, but I guess } $\alpha=1$

### 2022-02-22 draft2.tex

--- 2022-02-21 draft2.tex
@@
 \section{Fractional derivatives and Borel transform}
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-\[ \partial^{\nu-1}_{x \text{ from } 0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
-\begin{align*}
-\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
-However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
-Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
-\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
-\end{definition}
-The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-
-Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-Here's what's nice about it.
-\begin{theorem}
-Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
-for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-\end{theorem}
-\color{Turquoise}
-Here's how we'll use this later. By definition, $\tilde{I}_p(z) = z^{-1/2}\tilde{\varphi}_p(z)$, so the theorem gives
-\begin{align*}
-\left[ \borel_{\zeta_\alpha} \tilde{I}_p \right](\zeta) & = \left[ \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_p \right](\zeta) \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \left[ \borel \tilde{\varphi}_p \right](\zeta) \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta).
-\end{align*}
-Once we show that $\borel \tilde{I}_p = \hat{I}_p$, we have
-\begin{align*}
-\hat{I}_p(\zeta) & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta) \\
-\partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) & = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta)
-\end{align*}
-thanks to the semigroup law. Once we show that
-\[ \hat{I}_p(\zeta) = \tfrac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right), \]
-we can deduce that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) = \int_{\mathcal{C}_p(\zeta)} \nu - \int_{\mathcal{C}_p(0)} \nu. \]
-The path $\mathcal{C}_p(0)$ is a point, so the initial value term vanishes, and we can conclude that
-\[ \int_{\mathcal{C}_p(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta). \]
-Finally, recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we see that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \int_{\mathcal{C}_p(\zeta)} \nu = \hat{\varphi}_p(\zeta). \]
-\color{black}
-
-\begin{lemma}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^\mu z^{-(k+1)} \right](\zeta). \]
-\end{lemma}
-\begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-\color{MidnightBlue}
+
 \begin{definition}
@@
 \begin{align*}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
-& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right)}\,d\zeta',
+\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha}\left(\int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
+& = \Gamma\big(-\tfrac{1}{2}\big)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2}\textcolor{red}{\partial_{\zeta'}\left(\left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta')}^{\operatorname{end} \mathcal{C}_\alpha(\zeta')} \right)}\,d\zeta',
 \end{align*}
@@
 Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[The integral over $\mathcal{C}_\alpha(\zeta)$ needs to satisfy some condition near $\zeta = 0$ for this to hold.
-Figure out what that is!
-Also, be careful about the orientation of $\mathcal{C}_\alpha$.]}
+\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
 \item
@@
 \begin{equation}
-\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s} \left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]\,ds \qquad \zeta\in(2/3,+\infty)
+\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \qquad \zeta\in(2/3,+\infty)
 \end{equation}
@@
 
-\color{Turquoise}
+\color{violet}
 Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
@@
 \[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
-\color{MidnightBlue}
+\color{black}
 Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.
@@
 
-\color{violet}
+\textcolor{violet}{
 Alternate calculation with $\tfrac{1}{2}$ derivative:
@@
 \label{4.5}
-\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)(x-y)^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
+\int_0^x |y|^{a-\mu-1}{}_2F_1\left(a,b;c,y\right)|x-y|^{\mu-1}dy=\frac{\Gamma(\mu)\Gamma(a-\mu)}{\Gamma(a)}|x|^{a-1}{}_2F_1\left(a-\mu,b;c;x\right)\\
 x\in(-\infty,0)\cup(0,1), \, \Re a>\Re\mu>0

### 2022-02-22 draft2.tex
Update 3/2-derivative calculation in Airy example

--- 2022-02-21 draft2.tex
@@
 
-% Laplace and Borel transforms
+% symbology
 \newcommand{\laplace}{\mathcal{L}}
 \newcommand{\borel}{\mathcal{B}}
+\DeclareMathOperator{\Ai}{Ai}
 
@@
 \begin{example}[Airy]
-Let $f(t)=\frac{t^3}{3}-t$ and \[I(z)\defeq\int_{\gamma} e^{-zf(t)}\text{dt}\]
-where $\gamma$ is a countour where the integral is well defined.
-
-By the change of coordinates $z=x^{3/2}$, $I(z)=-2\pi iz^{-1/3}Ai(x)$ where \[Ai(x)\defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{\frac{t^3}{3}-zt}\text{dt}\]
-hence $I(z)$ solves the following ODE\footnote{$Ai(x)$ solves the Airy equation $y''=xy$.}
+%%Let $f(t)=\frac{t^3}{3}-t$ and \[I(z)\defeq\int_{\gamma} e^{-zf(t)}\text{dt}\]
+%%where $\gamma$ is a countour where the integral is well defined.
+By definition,
+\[ \Ai(x) \defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{t^3/3 - \textcolor{red}{x} t}\,dt. \]
+Define $I(z)$ by the change of coordinates $z=x^{3/2}$, $I(z)=-2\pi iz^{-1/3}\Ai(x)$. This new function satisfies the ODE\footnote{$\Ai(x)$ solves the Airy equation $y''=xy$.}
 \begin{equation}\label{eq:I}
-I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2}=0
+I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2} = 0.
 \end{equation}
@@
 \end{claim}
+\begin{proof}
+With the substitution $t = -2ux^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_+} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
+where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. This leads to the expression
+\[ I_+(z) = \int_{\mathcal{C}_+} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
+\end{align*}
+Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi (\xi' - \xi)^{-1/2} \Big[ -\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = -\frac{8}{9} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = \frac{4}{9} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{-3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{4}{9} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = \tfrac{\sqrt{\pi}}{4} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = \tfrac{\sqrt{\pi}}{4}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = \tfrac{\sqrt{\pi}}{4}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = \tfrac{\sqrt{\pi}\,5}{4 \cdot 36}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
 

### 2022-02-23 draft2.tex
update Bessel example

--- 2022-02-22 draft2.tex
@@
 
-By change of cooridnates $t=zx$
-\begin{align*}
-I(z)=\int_0^{\infty}e^{-z\left(\frac{t}{z}+\frac{z}{t}\right)}\frac{dt}{t}=\int_0^{\infty}e^{-\left(t+\frac{z^2}{t}\right)}\frac{dt}{t}=2K_0(2z) \,\qquad |\arg z|<\frac{\pi}{4}
+Let $\pi\colon\tilde{\C}\to \C^*$ be the universal cover of $\C^*$, where $\pi(u)=e^u$, then on $\tilde{\C}$, $I(z)$ turns into
+\begin{align*}
+I(z)=\int_{-\infty}^{\infty}e^{-2z\cosh(u)}du=2\int_0^{\infty}e^{-2z\cosh(u)}du=2K_0(2z) \,\qquad |\arg z|<\frac{\pi}{2}
 \end{align*}
@@
 \end{equation} 
-The formal integral of \eqref{eq:IB} is given by a two parameter formal solution $\tilde{I}_1(z)$
+The formal integral of \eqref{eq:IB} is given by a two parameter formal solution $\tilde{I}(z)$
 \begin{equation}
@@
 \end{equation}
-and according to our convention, we define
+and we define
 \begin{align}
@@
 We set $\tilde{w}_{(1,0)}=\tilde{w}_+$ and $\tilde{w}_{(0,1)}=\tilde{w}_-$, then their Borel transforms are solutions respectively of the following equations 
-\begin{align*}
-(+)\quad &\zeta^2\hat{w}_+(\zeta)+4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0\\
-(-)\quad &\zeta^2\hat{w}_+(\zeta)-4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0
-\end{align*}
-taking twice derivative in $\zeta$ we get
-\begin{align*}
-(+)\quad &(\zeta^2+4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_++4(\zeta-1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_+=0 &\\
-(-)\quad &(\zeta^2-4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_-+4(\zeta+1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_-=0 &\\
-(+)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_++(1-4\xi)\frac{d}{d\xi}\hat{w}_+-\frac{9}{4}\hat{w}_+=0 & \xi=-\frac{\zeta}{4} \\
+\begin{align}
+\zeta^2\hat{w}_+(\zeta)+4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0\\
+\zeta^2\hat{w}_-(\zeta)-4\zeta\hat{w}_-(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_-(\zeta)=0
+\end{align}
+taking twice derivative in $\zeta$ we get respectively for $\hat{w}_+(\zeta)$ and $\hat{w}_-(\zeta)$
+\begin{align*}
+&(\zeta^2+4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_++4(\zeta-1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_+=0 &\\
+(+)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_++(1-4\xi)\frac{d}{d\xi}\hat{w}_+-\frac{9}{4}\hat{w}_+=0 & \xi=-\frac{\zeta}{4} 
+\end{align*}
+\begin{align*}
+&(\zeta^2-4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_-+4(\zeta+1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_-=0 &\\
 (-)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_-+(1-4\xi)\frac{d}{d\xi}\hat{w}_--\frac{9}{4}\hat{w}_-=0 & \xi=\frac{\zeta}{4}
 \end{align*}
-therefore, since equation $(+), (-)$ are hypergeometric the fundamental solution is (see DLMF 15.10.2)
+Since equation $(+), (-)$ are hypergeometric, the fundamental solutions are respectively (see DLMF 15.10.2)
 \begin{align}
@@
 These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.
-
-\begin{lemma}
-The following identity holds true
-\begin{equation}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}\qquad \qquad \zeta=u+\frac{1}{u}
-\end{equation}
-\end{lemma}
-\begin{proof}
-From 15.4.13 DLMF, we have
-\begin{align*}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)&=\frac{2}{\sqrt{4-\zeta^2}} & y=\mathrm{arccsc}(\zeta/2)\\
-&=\frac{1}{\sqrt{1-\mathrm{csc}^2(y)}} & \\
-&=-i\tan(y) &   \zeta=\frac{2}{\sin(y)}
-\end{align*}
-therefore if $u=\tan\left(\frac{y}{2}\right)$, we have $\zeta=\frac{1+u^2}{u}=f(u)$ and 
-\begin{equation*}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}=\frac{2i}{f'(u)u}
-\end{equation*}  
-\end{proof}
-
-\begin{claim}
-\label{Bessel}
-\begin{equation}
-\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta'^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
-\end{equation}
-\end{claim}
-\begin{proof}
-Let us first consider the RHS of \eqref{Bessel}. Note $x=\frac{1}{2}-\frac{\zeta}{4}$ and $y=\frac{1}{2}-\frac{\zeta'}{4}$
-\begin{align*}
-&2\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta'^2}{4}\right)d\zeta'= &\\
-&\quad =- \frac{2}{3\pi}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' & 15.8.28 \text{ DLMF}\\
-&\quad =- \frac{4}{3\pi}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};1-y\right)-{}_2F_1\left(2,2;\frac{5}{2};y\right)\right]dy & x\in (-\infty,0)\\
-&\quad = -\frac{4}{3\pi}\int_0^xe^{-(1/2)\pi i}(x-y)^{-1/2}\left[\frac{3\pi}{4}e^{-(1/2)\pi i}y^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)\right]dy & 15.10.30 \text{ DLMF} \\
-&\quad = -\int_0^x e^{-(1/2)\pi i}(x-y)^{-1/2}e^{-(1/2)\pi i}y^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
-&\quad = -\int_0^x(x-y)^{-1/2} |y|^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
-&\quad = -\int_0^x e^{-(1/2)\pi i}|x-y|^{-1/2} |y|^{-2}{}_2F_1\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \\
-&\quad = -e^{-(1/2)\pi i}\frac{\Gamma\left(\frac{1}{2}\right)\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & \eqref{4.8} \\
-&\quad = -e^{-(1/2)\pi i}\frac{\pi}{2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) &  \\
-&\quad =-\frac{\pi}{2}w_6(3/2,3/2,2) & \\
-&\quad =-\frac{\pi}{2}\frac{\Gamma\left(3/2\right)\Gamma(1)}{\Gamma(2)\Gamma(3/2)}e^{(c-a)\pi i}\left(w_1(a,b,c)-e^{a\pi i}\frac{\Gamma(2)\Gamma(1/2)}{\Gamma(2)\Gamma(1/2)}w_3\right)
-\end{align*}
-
-\textcolor{violet}{ From DLMF 15.10.17
-\begin{align*}
-w_3(a,b,c)&=\frac{\Gamma\left(1-c\right)\Gamma\left(a+b-c+1\right)}{\Gamma\left(a-c+1\right)\Gamma\left(b-c+1\right)}w_1(a,b,c)+\frac{\Gamma\left(c-1\right)\Gamma\left(a+b-c+1\right)}{\Gamma\left(a\right)\Gamma\left(b\right)}w_2(a,b,c)\\
-w_3(2,2,\frac{5}{2})&=w_1(2,2,\frac{5}{2})+\frac{3\pi}{8}w_2(2,2,\frac{5}{2})\\
-\end{align*}
+\textbf{Hopefully, the latter identities show that the Stokes constants can be computed via Alien calculus and they are equal to $\pm 2$.
 }
-however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$, thus the claim holds true. 
-\end{proof}
-Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
+
+Now we show that the fractional derivative formula holds in this example: first we write a parametrization of the integration path in the Borel plane.
+Let $\mathcal{C}_p=\R$, $p\in \pi\Z$, be the contour of integration in $\tilde{\C}$ which is parametrized as
+
+\begin{align*}
+{C}_p\colon \R & \to \tilde{\C} \\
+\theta & \to \theta+i p
+\end{align*}
+
+Then in the Borel plane $\C_\zeta$, where $\zeta=2\cosh(u)$, the path $\mathcal{C}_0$ is parametrized as  
+\begin{align*}
+\mathcal{C}_0\colon\R &\to \C_\zeta \\
+\theta & \to 2\cosh(\theta)
+\end{align*}
+
+\begin{figure}
+\caption{Integration path in the $u$-plane and in the Borel plane $\zeta=2\cosh(u)$. }
+\end{figure}
+
+\textbf{Check Aaron notation}
+
+\begin{equation}
+\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)=\int_{\mathcal{C}_0(\zeta)}du=\Big[ u\Big]^{\mathrm{end}\mathcal{C}_0(\zeta)}_{\mathrm{start}\mathcal{C}_0(\zeta)}=2\mathrm{arc}\cosh\left(\frac{\zeta}{2}\right)
+\end{equation}
+
+We can now write $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 14.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta-1\right)=\frac{1}{2}\left(\cosh(\theta)-1\right)=\sinh^2\left(\frac{\theta}{2}\right)$, then
+
+\begin{align*}
+\sinh\left(\frac{\theta}{2}\right)\,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\sinh^2\left(\frac{\theta}{2}\right)\right)&=i\frac{\theta}{2} \\
+\xi^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi\right)&=i\frac{\theta}{2}\\
+ &=\frac{i}{2}\left(\frac{1}{2}\mathrm{arcosh}\left(\frac{\zeta}{2}\right)\right)\\
+ &=\frac{i}{4}\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)
+\end{align*}
+
+The $3/2$-derivative of $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ can be computed as follows: we compute the $-1/2$-derivatve and then we differentiate twice
+
+\begin{align*}
+\partial_{\zeta}^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_2^\zeta (\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)d\zeta'\\
+&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)\xi'^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi'\right) 4d\xi'\\
+&=-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)
+\end{align*}
+
+\begin{align*}
+\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \\
+&=\frac{1}{16}\partial_\xi^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
+&=+\frac{i}{2}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,-\xi\right)\right) & \textbf{DLMF} 15.5.4\\
+&=-\frac{i}{8}\Gamma\left(\frac{3}{2}\right){}_2F_1\left(\frac{3}{2},\frac{3}{2};2,-\xi\right) & \\
+&=-\frac{i\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}-\frac{\zeta}{4}\right) & \\
+&=-\frac{i\sqrt{\pi}}{16} \hat{w}_+(\zeta-2) &
+\end{align*}
+
+%Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
 \end{example}

### 2022-02-23 draft2.tex
Add discussion notes and corrections

--- 2022-02-22 draft2.tex
@@
 \end{align*}
-which diverges for typical $f$ and $\nu$.
+which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
 
@@
 \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha \\
 & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
@@
 \begin{example}[Airy]
-%%Let $f(t)=\frac{t^3}{3}-t$ and \[I(z)\defeq\int_{\gamma} e^{-zf(t)}\text{dt}\]
-%%where $\gamma$ is a countour where the integral is well defined.
 By definition,
-\[ \Ai(x) \defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{t^3/3 - \textcolor{red}{x} t}\,dt. \]
+\[ \Ai(x) \defeq \frac{1}{2\pi i}\int_{-\infty e^{-i\frac{\pi}{3}}}^{\infty e^{i\frac{\pi}{3}}} e^{t^3/3 - xt}\,dt. \]
 Define $I(z)$ by the change of coordinates $z=x^{3/2}$, $I(z)=-2\pi iz^{-1/3}\Ai(x)$. This new function satisfies the ODE\footnote{$\Ai(x)$ solves the Airy equation $y''=xy$.}
@@
 \begin{claim}\label{claim 2}
-\textbf{[There should be a way to predict the correct normalization of the LHS.]}
-\begin{equation}
-\hat{w}_+(\zeta-2/3)=-\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s} \left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]\,ds \qquad \zeta\in(2/3,+\infty)
-\end{equation}
+\textbf{[There should be a way to predict the correct normalization of the RHS.]}
+\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{5}{36}\,\hat{w}_+(\zeta-2/3), \]
+consistent with Theorem~\ref{thm:maxim}~\eqref{int:deriv-formula}.
 \end{claim}
@@
 \[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_+} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
-where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. This leads to the expression
+where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression
 \[ I_+(z) = \int_{\mathcal{C}_+} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
@@
 & = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -\sinh(\theta)
+& = -i\sqrt{3}\,\sinh(\theta)
 \end{align*}
@@
 then shows us that
-\[ -\int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
 
@@
 \partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi (\xi' - \xi)^{-1/2} \Big[ -\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = -\frac{8}{9} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = \frac{4}{9} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{2}{\sqrt{3}} (\xi' - \xi)^{-1/2} \Big[ \tfrac{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = i \frac{16}{27} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = i \frac{8}{27} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
 \end{align*}
@@
 \begin{align*}
-\partial^{-3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{4}{9} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = \tfrac{\sqrt{\pi}}{4} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = \tfrac{\sqrt{\pi}}{4}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = \tfrac{\sqrt{\pi}}{4}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = \tfrac{\sqrt{\pi}\,5}{4 \cdot 36}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{8}{27} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{6} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{5}{36}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\textbf{[Check comparison with Mari\~{n}o's result more carefully?]}
 \end{proof}

### 2022-02-23 draft2.tex
Drop old material and scratch work

@@
 \section{Introduction}
-
-%\begin{example}[Airy]
-%The Airy equation is 
-%\begin{equation}
-%y''=xy
-%\end{equation}
-% and a system of solutions is given by (see DLMF) 
-%
-%\begin{align*}
-%&Ai(x)=\frac{1}{2\pi i}\int_{\infty e^{-i\pi/3}}^{\infty e^{i\pi/3}}e^{t^3/3-xt}dt\\
-%&Bi(x)=\frac{1}{2\pi}\int_{-\infty}^{\infty e^{-i\pi/3}}e^{t^3/3-xt}dt+\frac{1}{2\pi}\int_{-\infty}^{\infty e^{i\pi/3}}e^{t^3/3-xt}dt
-%\end{align*}
-%
-%
-%
-%Let $\psi(x)\defeq\sum_{n\geq 0}a_nx^{-n}$ be the asymptotic expansion of $Ai(x)$ as $x\to\infty$: from DLMF and Sauzin
-%
-%\begin{equation}
-%Ai(x)\sim \frac{e^{-2/3x^{3/2}}}{2\sqrt{\pi}x^{1/4}}\sum_{n\geq 0}(-1)^n\frac{1}{2^{n+1}\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{2}x^{-3/2}\right)^n
-%\end{equation}
-%and $a_n\defeq (-1)^n\frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$.
-Analogously, let $\varphi(x)\defeq\sum_{n\geq 0}b_nx^{-n}$ be the asymptotic expansion of $Bi(x)$ as $x\to\infty$: from DLMF and Sauzin
-%
-%\begin{equation}
-%Bi(x)\sim \frac{e^{2/3x^{3/2}}}{\sqrt{\pi}x^{1/4}}\sum_{n\geq 0}\frac{1}{2^{n+1}\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{2}x^{-3/2}\right)^n
-%\end{equation}
-%
-%and $b_n\defeq \frac{1}{2\pi n!}\Gamma\left(n+\frac{5}{6}\right)\Gamma\left(n+\frac{1}{6}\right)\left(\frac{3}{4}\right)^n$.
-%\begin{prop}
-%$\psi(x)$ and $\varphi(x)$ are resurgent series.
-%\end{prop}
-%\begin{proof}
-%Let $\hat{\psi}(\zeta)=\frac{1}{2\pi}\sum_{n\geq 0}a_{n-1}\frac{\zeta^n}{(n-1)!}$, mathematica says 
-%\begin{equation}
-%\hat{\psi}(\zeta)=-\frac{5}{48} F_1(7/6,11/6,2,-3/4\zeta)
-%\end{equation}
-%which has a log singularity at $\zeta=-4/3$, namely 
-%\begin{equation}
-%\hat{\psi}(\zeta+4/3)=\log(\zeta)\hat{\psi}_{-4/3}(\zeta)+\text{hol.fct}
-%\end{equation}
-%where $\hat{\psi}_{-4/3}(\zeta)$ is holomorphic in a neighbourhood of the origin. In particular, $\hat{\psi}_{-4/3}(\zeta)=-\frac{1}{2}\varphi(\zeta)$.    
-%Now, let $\hat{\varphi}(\zeta)=\frac{1}{2\pi}\sum_{n\geq 0}b_{n-1}\frac{\zeta^n}{(n-1)!}$, mathematica says 
-%\begin{equation}
-%\hat{\varphi}(\zeta)=\frac{5}{48} F_1(7/6,11/6,2,3/4\zeta)
-%\end{equation}
-%which has a log singularity at $\zeta=4/3$, namely 
-%\begin{equation}
-%\hat{\varphi}(\zeta-4/3)=\log(\zeta)\hat{\varphi}_{4/3}(\zeta)+\text{hol.fct}
-%\end{equation}
-%where $\hat{\varphi}_{4/3}(\zeta)$ is holomorphic in a neighbourhood of the origin. In particular, $\hat{\varphi}_{4/3}(\zeta)=\frac{1}{2}\psi(\zeta)$.    
-%\end{proof}
-%
-%Comment on the asymptotic expansion of $Ai(x)$ and $Bi(x)$: the prepared form of the Airy equation is obtained after the change of coordinates $z=x^{3/2}$ and it reads
-%
-%\begin{equation}\label{prepform}
-%y''(z)+\frac{y'(z)}{3z}=\frac{4}{9}y(z)
-%\end{equation} 
-%
-%In particular, its Borel trasform is 
-%\begin{equation}
-%\zeta^2\hat{y}-\frac{1}{3}\ast (\zeta\hat{y})=\frac{4}{9}\hat{y}
-%\end{equation}
-%and we read the singularity of the Borel transform as solution of $z^2-4/9=0$, which are $z=\pm 2/3$.
-These are indeed the exponent of the exponential factor in the asymptotic of $Ai(z)$ and $Bi(z)$ respectively.
-%
-%Alternatively, from the theory of ODE we can look for a solution of \eqref{prepform} of the form
-%\begin{equation}
-%y(z)=\sum_{k\in\Z^2}U^ke^{-k\cdot\lambda z}z^{-\tau\cdot k}w_{k}(z)
-%\end{equation} 
-%where $\lambda=(\lambda_1,\lambda_2)$ with $\lambda_i^2-4/9=0$, $\tau=(\tau_1,\tau_2)$ with $\tau_i=1/6$ and $w_k(z)\in\C[[z^{-1}]]$ is a formal series.
-Plugging in the ansatz in \eqref{prepform}, we fins that the only non zero solutions $w_k$ occurs for $k=(1,0)$ and $k=(0,1)$, meaning that the formal integral of the Airy equation is given by
-%\begin{equation}
-%y(z)=U_1e^{-2/3z}z^{-1/6}w_{(1,0)}(z)+U_2e^{2/3z}z^{-1/6}w_{(0,1)}(z).
-%\end{equation}
-%The latter expression can be compared with the asymptotic behaviour of $Ai(z)+Bi(z)$ as $z\to\infty$. In particular, $w_{k}$ solves the following homogeneus equation:
-%\begin{align*}
-%\left(\partial_z^2-\frac{4}{3}\partial_z+\frac{5}{36z^2}\right)w_{(1,0)}=0\\
-%\left(\partial_z^2+\frac{4}{3}\partial_z+\frac{5}{36z^2}\right)w_{(0,1)}=0
-%\end{align*}
-%Assuming $w_{(1,0)}=1+\sum_{n\geq 1}a_n^+z^{-n}$ and $w_{(0,1)}=1+\sum_{n\geq 1}a_n^-z^{-n}$ we get \[a_n^+=(-1)^n\left(\frac{3}{4}\right)^n\frac{\Gamma(n+\frac{1}{6})\Gamma(n+\frac{5}{6})}{2\pi n!}=a_n\] and \[a_n^-=\left(\frac{3}{4}\right)^n\frac{\Gamma(n+\frac{1}{6})\Gamma(n+\frac{5}{6})}{2\pi n!}=b_n.\]
-%
-%Now, we investigate the exponential integral
-%\begin{equation}
-%I(z)\defeq\int_{\Gamma} \exp(-z\left(\frac{x^3}{3}-x\right))dx
-%\end{equation}
-%where $\Gamma$ is a suitable countour. By simple computation we notice that $I(z)=-2\pi iz^{-1/3}Ai(x)$ (where $z=x^{3/2}$). In particular, $I(z)$ is a solution of 
-%\begin{equation}\label{eq:Iold}
-%I''-\frac{4}{9}I+\frac{I'}{z}-\frac{1}{9}\frac{I}{z^2}=0
-%\end{equation} 
-% The Borel trasform of $\hat{I}(z)$ can be computed directly from the equation \eqref{eq:I}, namely the Borel transform of equation \eqref{eq:I} is
-%\begin{equation}
-%\zeta^2 \hat{I}-\frac{4}{9}\hat{I}-1\ast\zeta\hat{I}-\frac{1}{9}\zeta\ast\hat{I}=0
-%\end{equation} 
-%\begin{equation}
-%\zeta^2 \hat{I}-\frac{4}{9}\hat{I}-\int_0^\zeta\zeta'\hat{I}(\zeta')d\zeta '-\frac{1}{9}\int_0^\zeta(\zeta-\zeta')\hat{I}(\zeta')d\zeta'=0
-%\end{equation} 
-%\begin{align*}
-%2\zeta\hat{I}+\zeta^2\hat{I}'-\frac{4}{9}\hat{I}'-\zeta\hat{I}-\frac{1}{9}\int_0^\zeta\hat{I}(\zeta')d\zeta'=0\\
-%\hat{I}+\zeta\hat{I}'+2\zeta\hat{I}'+\zeta^2\hat{I}''-\frac{4}{9}\hat{I}''-\frac{1}{9}\hat{I}=0
-%\end{align*}
-%\begin{equation}
-%(\zeta^2-\frac{4}{9})\hat{I}''+3\zeta\hat{I}'+(1-\frac{1}{9})\hat{I}=0
-%\end{equation} 
-%and for some costants $c_1,c_2\in\C$ the solutions are
-%\begin{equation}
-%\hat{I}(\zeta)=\frac{9\zeta c_1}{4\sqrt{\frac{4}{9}-\zeta^2}}+c_2
-%\end{equation}  
-%\end{example}
-%\textcolor{red}{Is $F_1(7/6,11/6,2,3/4\zeta)$ algebraic?}
-
 \section{Fractional derivatives and Borel transform}
@@
 \end{theorem}
-\color{Turquoise}
-Here's how we'll use this later. By definition, $\tilde{I}_p(z) = z^{-1/2}\tilde{\varphi}_p(z)$, so the theorem gives
-\begin{align*}
-\left[ \borel_{\zeta_\alpha} \tilde{I}_p \right](\zeta) & = \left[ \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_p \right](\zeta) \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \left[ \borel \tilde{\varphi}_p \right](\zeta) \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta).
-\end{align*}
-Once we show that $\borel \tilde{I}_p = \hat{I}_p$, we have
-\begin{align*}
-\hat{I}_p(\zeta) & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta) \\
-\partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) & = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta)
-\end{align*}
-thanks to the semigroup law. Once we show that
-\[ \hat{I}_p(\zeta) = \tfrac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right), \]
-we can deduce that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_p(\zeta) = \int_{\mathcal{C}_p(\zeta)} \nu - \int_{\mathcal{C}_p(0)} \nu. \]
-The path $\mathcal{C}_p(0)$ is a point, so the initial value term vanishes, and we can conclude that
-\[ \int_{\mathcal{C}_p(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_p(\zeta). \]
-Finally, recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we see that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \int_{\mathcal{C}_p(\zeta)} \nu = \hat{\varphi}_p(\zeta). \]
-\color{black}
-
 \begin{lemma}
@@
 \approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-\color{violet}
-Part~(1): Let us assume that locally $\nu=\sum_{j\geq 0}b_j^{\alpha}(t-t_{\alpha})^{j}dt$ for $|t-t_\alpha|<\varepsilon$.
-By the steepest descent method, $I_\alpha(z)$ can be aproximated as $z\to\infty$ as
-\begin{align*}
-I_\alpha(\zeta)&\sim e^{-zf(x_\alpha)}\int_{-\varepsilon}^{\varepsilon}\sum_{n\geq 0}t^{2n}b_{2n}^{\alpha}e^{-zf''(x_\alpha)\frac{t^2}{2}}dt\\
-&=e^{-zf(x_\alpha)}\sum_{n\geq 0}b_{2n}^{\alpha}\int_{-\varepsilon}^{\varepsilon}t^{2n}e^{-zf''(x_{\alpha})\frac{t^2}{2}}dt\\
-&=\sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}\mathrm{Erf}\left(\frac{\sqrt{z f''(x_\alpha)}}{\sqrt{2}}\varepsilon\right)+\\
-&-2e^{-zf(x_\alpha)}\sum_{n\geq 1}b_{2n}^{\alpha}(2n-1)!!e^{-zf''(x_{\alpha})\frac{\varepsilon^2}{2}}\sum_{j=1}^n\frac{\varepsilon^{2j-1}}{(2j-1)!!}\left(f''(x_\alpha)z\right)^{n-j+1}\\
-&\sim_{\textcolor{red}{\varepsilon \ll 1}} 2\varepsilon \sqrt{2\pi}e^{-zf(x_\alpha)}z^{-1/2}\sum_{n\geq 0}\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!! z^{-n}
-\end{align*} 
-therefore \[a_{\alpha,n}\defeq 2\varepsilon\frac{b_{2n}^{\alpha}}{(f''(x_{\alpha}))^{n+1/2}}(2n-1)!!\]
-\textbf{[The value of $\varepsilon$ shouldn't affect the asymptotic series! I think we want the limit $z \to \infty$ rather than $\varepsilon \ll 1$.]}
-
-Since, $\tfrac{1}{\varepsilon}=\limsup_{n}\sqrt[n]{b_{n}^{\alpha}}$
-
-\[|a_{\alpha,n}|\leq CA^n n!\]
-where we use $(2n-1)!!\sim \tfrac{2^n}{\sqrt{\pi n}}n!$ as $n\to \infty$.
-\color{black}
 
@@
 \hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
-%&=C_3 T_{-2/3}\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_{\zeta} {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)}+ C_4\textcolor{red}{\left(\frac{3}{2\sqrt{\zeta}}\right)^{-1}\partial^{1/2}_\zeta {}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)}
-\end{align*}
-%
-%\begin{claim}\label{claim1}
-%\begin{equation}
-%\hat{w}_+(\zeta-2/3)=\frac{1}{\sqrt{\pi}}\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left(\frac{1}{f'(u)}\right)ds \,\,\qquad s=f(u)
-%\end{equation}
-%\end{claim}
+\end{align*}
 
@@
 \begin{align*}
-{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)&=%2\cos\left(\frac{1}{3}\arcsin\left(\frac{3}{2}\zeta\right)\right)(4-9\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
-\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
+{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right) &= \frac{\cos(y)}{\cos(3y)} & 3y=\arcsin\left(\frac{3}{2}\zeta\right)\\
 &=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
@@
 
-%Hence claim \eqref{claim1} is equivalent to
-Then equations \eqref{formula1} is equivalent to
+Then equations \eqref{formula1} is equivalent to: \textbf{[Now that we've switched to the Riemann-Liouville derivative, the claim that was referenced here no longer involves $\nu/df$.
+The calculation above is still useful, but it should go somewhere else.]}
 
@@
 \end{proof}
-
-\color{Turquoise}
-Using $a = \tfrac{5}{3}$, $b = \tfrac{7}{3}$, $c = \tfrac{5}{2}$:
-\begin{align*}
-w_1 & = \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6})} w_5 + \frac{\Gamma(\tfrac{5}{2}) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \\
-w_3 & = \frac{1}{e^{(5/3)\pi i} - e^{(7/3)\pi i}} \left[ e^{(-1/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3})} w_5 - e^{(-5/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3})} w_6 \right]
-\end{align*}
-Common denominators
-\begin{align*}
-w_1 & = \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 + \frac{\Gamma(\tfrac{5}{2}) \Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \\
-w_3 & = \frac{i}{\sqrt{3}} \left[ e^{(-1/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{(-5/6) \pi i} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
-\end{align*}
-Extract
-\begin{align*}
-w_1 & = \frac{\Gamma(\tfrac{5}{2}) \tfrac{2}{\sqrt{3}}\pi}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 - \frac{\Gamma(\tfrac{5}{2}) \tfrac{2}{\sqrt{3}}\pi}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \\
-w_3 & = \frac{2\pi i}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{(-1/6) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{(-5/6) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
-\end{align*}
-\ldots
-\begin{align*}
-w_1 & = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{6}) \Gamma(\tfrac{1}{3})} w_5 - \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{3})} w_6 \right] \\
-w_3 & = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 - e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right]
-\end{align*}
-Now subtract!
-\[ w_1 - w_3 = \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \left[ e^{-(1/3) \pi i} \frac{1}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} w_5 + e^{-(2/3) \pi i} \frac{1}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} w_6 \right] \]
-\color{MidnightBlue}
-Let us study the RHS of claim \eqref{claim 2}. \textbf{Note that $x = \tfrac{1}{2} - \tfrac{3}{4} \zeta$ and $y = \tfrac{1}{2} - \tfrac{3}{4} s$.
-\begin{align*}
-&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2}\textcolor{red}{\partial_s}\left[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right)\right]ds \\
-&= 2\int_{2/3}^{\zeta} (\zeta-s)^{-1/2}s\,\,{}_2F_1\left(\frac{4}{3},\frac{5}{3};\frac{3}{2};\frac{9}{4}s^2\right)ds & \\
-&= -\frac{2}{9} \int_{2/3}^{\zeta} (\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}-\frac{3s}{4}\right) - {}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.28 \text{ DLMF} \\
-&=\frac{4}{9\sqrt{3}}\int_0^x (y-x)^{-1/2}\left[{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};y\right)-{}_2F_1\left(\frac{5}{3},\frac{7}{3};\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0) \\
-&=\frac{4}{9\sqrt{3}} \frac{2\pi}{\sqrt{3}} \Gamma(\tfrac{5}{2}) \int_0^x (y-x)^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(5/3) \pi i} y^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
-\\
-& \qquad\qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ e^{-(2/3) \pi i} \frac{e^{(7/3) \pi i} y^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0)
-\end{align*}
-Continue $w_5$ and $w_6$ counterclockwise around their singularities at zero.} Notice that $|y - x| = y - x$ on the integration path.
-\begin{align*}
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ e^{-(1/3) \pi i} \frac{e^{(10/3) \pi i} |y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
-\\
-& \qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ e^{-(2/3) \pi i} \frac{e^{(14/3) \pi i} |y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \int_0^x |y-x|^{-1/2}\left[ -\frac{|y|^{-5/3} {}_2F_1\left(\frac{5}{3},\frac{1}{6};\frac{1}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
-\\
-& \qquad\qquad\qquad\qquad\qquad\qquad \left.
-+ \frac{|y|^{-7/3} {}_2F_1\left(\frac{7}{3},\frac{5}{6};\frac{5}{3};\frac{1}{y}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right]dy & x\in (-\infty,0) \\
-% do the integral
-&=\frac{8\pi}{27} \Gamma(\tfrac{5}{2}) \left[ -\frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{5}{3})} \frac{|x|^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} \right.
-\\
-& \qquad\qquad\qquad\qquad \left.
-+ \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3})} \frac{|x|^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right)}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} \right] & \eqref{4.8} \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3}) \Gamma(\tfrac{5}{6})} e^{(7/6) \pi i} x^{-7/6} {}_2F_1\left(\frac{7}{6},\frac{1}{6};\frac{1}{3};\frac{1}{x}\right) \right.
-\\
-& \left.
-\qquad\qquad\qquad\qquad + \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3}) \Gamma(\tfrac{1}{6})} e^{(11/6) \pi i} x^{-11/6} {}_2F_1\left(\frac{11}{6},\frac{5}{6};\frac{5}{3};\frac{1}{x}\right) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(2) \Gamma(\tfrac{2}{3})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad + \left.
-\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\Gamma(\tfrac{7}{6})}{\Gamma(2) \Gamma(-\tfrac{2}{3})} \frac{\Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{1}{\Gamma(\tfrac{2}{3}) \Gamma(\tfrac{1}{3})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad + \left.
-\frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{1}{\Gamma(-\tfrac{2}{3}) \Gamma(\tfrac{5}{3})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} \frac{\sin(\tfrac{2}{3} \pi)}{\pi} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right.
-\\
-& \qquad\qquad\qquad\qquad + \left. \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} \frac{\sin(-\tfrac{2}{3} \pi)}{\pi} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right] \\
-&=\frac{8\pi}{27} \frac{\sqrt{3}}{2\pi} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} \left[ -\frac{\Gamma(2) \Gamma(\tfrac{2}{3})}{\Gamma(\tfrac{11}{6}) \Gamma(\tfrac{5}{6})} w_5(\tfrac{7}{6}, \tfrac{11}{6}, 2) - \frac{\Gamma(2) \Gamma(-\tfrac{2}{3})}{\Gamma(\tfrac{7}{6}) \Gamma(\tfrac{1}{6})} w_6(\tfrac{7}{6}, \tfrac{11}{6}, 2) \right]
-\end{align*}
-Using DLMF~15.10.25, we see this is
-\begin{align*}
-&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\Gamma(\tfrac{5}{2}) \Gamma(\tfrac{1}{2}) \Gamma(\tfrac{7}{6}) \Gamma(\tfrac{11}{6})}{\Gamma(\tfrac{7}{3}) \Gamma(\tfrac{5}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{8}{27} \frac{\sqrt{3}}{2} \frac{\tfrac{3}{2}\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\,\tfrac{5}{6}\Gamma(\tfrac{5}{6})}{\tfrac{4}{3}\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\,\tfrac{2}{3}\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{1}{2})\,\Gamma(\tfrac{1}{6}) \Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{1}{3})\Gamma(\tfrac{2}{3})} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\sqrt{3}}{6 \cdot 2^4} \frac{\pi \sin(\tfrac{1}{3}\pi)}{\sin(\tfrac{1}{6}\pi)} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\pi}{32} w_1(\tfrac{7}{6}, \tfrac{11}{6}, 2) \\
-&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;x\right) \\
-&=-\frac{5\pi}{32}\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{1}{2}-\frac{3\zeta}{4}\right) \\
-&=-\frac{5\pi}{32}\hat{w}_+(\zeta - 2/3)
-\end{align*}
-This matches $-\sqrt{\pi}$ times the LHS of claim~\eqref{claim 2} \textbf{(up to scaling)}.
-
-\color{violet}
-Alternate calculation with $\tfrac{1}{2}$ derivative:
-\begin{align*}
-&\int_{2/3}^{\zeta}(\zeta-s)^{-1/2} {}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}s^2\right) ds \\
-&= \frac{2}{3} \int_{2/3}^{\zeta}(\zeta-s)^{-1/2} \left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3s}{4}\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3s}{4}\right) \right] ds & 15.8.27 \text{ DLMF} \\
-&=\frac{4}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1-y\right) + {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};y\right)\right]dy & x\in (-\infty,0) \\
-&=\frac{2i}{3\sqrt{3}}\int_0^x(x-y)^{-1/2}\left[ \big(1+\tfrac{1}{\sqrt{3}}\big) y^{-2/3} {}_2F_1\left(\frac{2}{3}, \frac{1}{6}, \frac{1}{3};\frac{1}{y}\right) + \big(1-\tfrac{1}{\sqrt{3}}\big) y^{-4/3} {}_2F_1\left(\frac{4}{3}, \frac{5}{6}, \frac{5}{3};\frac{1}{y}\right) \right] ds \\
-&=\frac{2i}{3\sqrt{3}} \left[ \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{1}{6})}{\Gamma(\tfrac{2}{3})} \big(1+\tfrac{1}{\sqrt{3}}\big) x^{-1/6} {}_2F_1\left(\frac{1}{6}, \frac{1}{6}, \frac{1}{3};\frac{1}{x}\right) + \frac{\Gamma(\tfrac{1}{2})\Gamma(\tfrac{5}{6})}{\Gamma(\tfrac{4}{3})}\big(1-\tfrac{1}{\sqrt{3}}\big) x^{-5/6} {}_2F_1\left(\frac{5}{6}, \frac{5}{6}, \frac{5}{3};\frac{1}{x}\right) \right] ds & \eqref{4.8} \\
-&=??? & \zeta\in (2/3,+\infty)
-\end{align*}
-\color{black}
-
 Analogously, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.
-%By definition ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)=\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n n!}t^n$, thus
-%
-%\begin{align*}
-%\int_{0}^{\zeta''}(\zeta''-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt=\sqrt{\pi}\sum_{n\geq 0}\frac{(2/3)_n(4/3)_n}{(3/2)_n \Gamma(3/2+n)}{\zeta''}^{n+\frac{1}{2}}= 2\sqrt{\zeta''}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta''\right)\\
-%\int_{1}^{\zeta'}(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt= 2\sqrt{\zeta'}{}_3F_2\left(\frac{2}{3},\frac{4}{3},1;\frac{3}{2},\frac{3}{2};\zeta'\right)-\int_0^1(\zeta'-t)^{-1/2} {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};t\right)dt
-%\end{align*}
-
-%Using properties of Caputo's $1/2$-derivative we would like to express $\hat{w}_{\pm}(\zeta)$ as the $1/2$-derivatives of other hypergeometric series.
-From the integral representation of hypergeomtric functions (see DLMF 15.6.1)
-%
-%\begin{align*}
-%{}_2F_1\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)&=\frac{3}{5\pi}\int_0^1t^{5/6}(1-t)^{-5/6}(1+\frac{3}{4}\zeta t)^{-7/6}dt & |u|<\frac{4}{3}\\
-%&=\frac{3}{5\pi}\zeta^{-1}\int_0^{\zeta}u^{5/6}(\zeta-u)^{-5/6}(1+\frac{3}{4}u)^{-7/6}du &u=\zeta t\\
-%&=\frac{3}{5\pi}\int_0^{\zeta}(\zeta-u)^{-1/2}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)du & \\
-%&=\frac{3}{5\sqrt{\pi}}\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-u)^{-1/2}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)du & 
-%%&=\textcolor{blue}{\frac{3}{5\sqrt{\pi}}\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-u)^{-1/2}\frac{1}{f'(f^{-1}(u))} du } & \\
-%%&=\textcolor{blue}{\frac{3}{5\sqrt{\pi}}\zeta^{-1}\partial_{\zeta}^{1/2}f^{-1}(\zeta)} &  
-%\end{align*}
-%For formula \eqref{formula1} to hold true we must have
-%\begin{equation}\label{claim}
-%\frac{3}{5\sqrt{\pi}}\left(\zeta^{-1/2}(1-\frac{u}{\zeta})^{-1/3}\left(\frac{u}{\zeta}\right)^{5/6}(1+\frac{3}{4}u)^{-7/6}\right)= \frac{1}{f'(f^{-1}(u))}
-%\end{equation}  
-%however, $\frac{1}{f'(f^{-1}(u))}$ does not depend on $\zeta$, thus \eqref{claim} is false, and the Airy exponential integral is a counter example of the formula \eqref{formula1}.   
-%%thus, we would like to see $\int_0^u(\zeta-t)^{-1/3}t^{5/6}(1+\frac{3}{4}t)^{-7/6}dt$ as the product of first derivatives of an hypergeomtric function and un unknown function $g(\zeta)$
-%%\begin{align*}
-%%\int_0^u(\zeta-t)^{-1/3}t^{5/6}(1+\frac{3}{4}t)^{-7/6}&\textcolor{blue}{=}\int
-%%\end{align*}
-%
-%\subsection{Second temptative formula} Let us assume that the correct formula that replaces \eqref{formula1} in Theorem \ref{thm:maxim} is 
-%\begin{multline}\label{formula2}
-%\hat{I}_{\alpha}(\zeta)=\partial^{N/2}_{\zeta, \text{based at }\zeta_\alpha}\left(\int_{f^{-1}(\zeta_\alpha)}^{f^{-1}(\zeta)}\nu\right)=\Gamma(-N/2)\int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-N/2}\int_{f^{-1}(\zeta')}\frac{\nu}{df} d\zeta'
-%\end{multline} 
-%then we compute $\hat{I}$ using properties of the Borel transform of a product:
-%
-%\begin{align*}
-%\hat{I}(\zeta)&=\mathcal{B}(z^{-1/2})\ast\hat{u}(\zeta)\\
-%&=\frac{1}{\Gamma(1/2)}\int_0^{\zeta}(\zeta-s)^{-1/2}\hat{u}(s)ds\\
-%&=\frac{1}{\Gamma(1/2)}\int_0^\zeta (\zeta-s)^{-1/2}\left(T_{-2/3}\hat{w}_+(s)+T_{2/3}\hat{w}_-(s)\right)ds
-%\end{align*}
-%
-%\begin{align*}
-%&=\frac{1}{\Gamma(1/2)}\int_0^\zeta(\zeta-s)^{-1/2} \hat{w}_+(s-2/3)+\frac{1}{\Gamma(1/2)}\int_0^\zeta (\zeta-s)^{-1/2}\hat{w}_-(s+2/3)ds\\
-%&=\frac{1}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-1/2} \hat{w}_+(s)+\frac{1}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-1/2}\hat{w}_-(s)ds\\
-%&=\frac{C_1}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-1/2} {}_2F_1\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}s\right)ds+\frac{C_2}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-1/2}{}_2F_1\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}s\right)ds\\
-%&=\frac{C_3}{\Gamma(1/2)}\int_{-2/3}^{\zeta-2/3}(\zeta-\frac{2}{3}-s)^{-\frac{1}{2}} \frac{\partial}{\partial s}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,-\frac{3}{4}s\right)ds+\frac{C_4}{\Gamma(1/2)}\int_{2/3}^{\zeta+2/3} (\zeta+\frac{2}{3}-s)^{-\frac{1}{2}}\frac{\partial}{\partial s}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\frac{3}{4}s\right)ds\\
-%&=\textcolor{red}{C_3\partial^{1/2}_{\zeta, \text{based at } -2/3}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,-\frac{3}{4}\zeta\right)+C_4\partial^{1/2}_{\zeta, \text{based at } 2/3}{}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\frac{3}{4}\zeta\right)}\, \textcolor{red}{\text{ is wrong!}}
-%\end{align*}
-%However, ${}_2F_1\left(\frac{1}{6},\frac{5}{6},1,\mp\frac{3}{4}\zeta\right)$ are not algebraic, hence they can not be equal to $\frac{1}{f'(f^{-1}(\zeta))}$ as it is in in Theorem \ref{thm:maxim} part II \eqref{formula2}.
-%
-%%Notice that $\pm\frac{2}{3}=f(\mp 1)$, i.e.
-they are the critical value of $f$.
-Thus, we  are left to check that ${}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\mp\frac{3}{4}\zeta\right) $ is equal to $1/f'(f^{-1}(\zeta)$.
-Using Mathamtica we simplify the hypergeometric function
-%%
-%%\begin{equation}
-%%{}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},-\frac{3}{4}\zeta\right)= \frac{2\sqrt{3}\sinh\left(\frac{2}{3}\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4+3\zeta}}
-%%\end{equation}
-%%
-%%then we did the following manipulations: we set $x=\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)$, then  
-%%
-%%\begin{multline}
-%%\frac{2\sqrt{3}\sinh\left(\frac{2}{3}\mathrm{ArcCsch}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4+3\zeta}}= \frac{3\sinh\left(\frac{2}{3}x\right)}{2\sinh(x)\sqrt{1+\sinh(x)^2}} \\
-%%= \frac{3\sinh\left(\frac{2}{3}x\right)}{2\sinh(x)\cosh(x)}=\frac{3\sinh\left(\frac{2}{3}x\right)}{\sinh(2x)}=\frac{3\sinh\left(\frac{2}{3}x\right)}{3\sinh\left(\frac{2}{3}x\right)+4\sinh^3\left(\frac{2}{3}x\right)}\\
-%%=\frac{1}{1+\frac{4}{3}\sinh^2\left(\frac{2}{3}x\right)}
-%%\end{multline}
-%%
-%%With respect to the other hypergeometric function, Mathematica gives
-%%
-%%\begin{equation}
-%%{}_{1}F_{2}\left(\frac{2}{3},\frac{4}{3},\frac{3}{2},\frac{3}{4}\zeta\right)= \frac{2\sqrt{3}\sin\left(\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4-3\zeta}}
-%%\end{equation}
-%% now we set $x=\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)$, then 
-%% \begin{multline}
-%% \frac{2\sqrt{3}\sin\left(\frac{2}{3}\mathrm{ArcCsc}\left(\frac{2}{\sqrt{3\zeta}}\right)\right)}{\sqrt{\zeta}\sqrt{4-3\zeta}}=\frac{2\sqrt{3}\sin(x)}{\frac{2}{\sqrt{3}}\sin\left(\frac{3}{2}x\right)\sqrt{4-4\sin^2\left(\frac{3}{2}x\right)}}\\
-%% \frac{3\sin(x)}{2\sin\left(\frac{3}{2}x\right)\cos\left(\frac{3}{2}x\right)}=\frac{3\sin(x)}{\sin(3x)}=\frac{3\sin(x)}{3\sin(x)-4\sin^3(x)}\\
-%% =\frac{1}{1-\frac{4}{3}\sin^2(x)}
-%% \end{multline}
-%
-%
-%%\begin{remark}
-%%Notice that the half derivative of a simple pole gives a log singularity; indeed 
-%%\begin{align*}
-%%\frac{1}{1-\frac{4}{3}\sin^2(x)} \text{has simple poles at } \zeta=\frac{4}{3} \text{ and } \zeta=\infty \\
-%%\frac{1}{1+\frac{4}{3}\sinh^2(x)} \text{has simple poles at } \zeta=\frac{4}{3} \text{ and } \zeta=\infty \\ 
-%%\end{align*} 
-%%\end{remark}
-%%
-%%
-%%If $\tilde{I}(z)$ is Borel--Laplace summable, then for a suitable choice of $U_1,U_2$ and of a direction $\theta\in\R/2\pi i\Z$, $\mathcal{S}^{\theta}\tilde{I}(z)=I(z)$. Indeed 
-%%\begin{align*}
-%%I(z)&=\int_{\mathcal{C}} e^{-zf(t)}\text{dt}=\int_{\mathcal{C}_h} e^{-z\zeta}\frac{d\zeta}{f'(f^{-1}(\zeta))}=e^{-2/3z}\int_{T_{2/3}\mathcal{C}_h}e^{-z\zeta}\frac{d\zeta}{f'(f^{-1}(\zeta+2/3))}. 
-%%\end{align*}
-%%
-%%However we are interested in resurgence properties of $\tilde{I}(z)$, thus we take its Borel transform. 
-%\subsubsection{Comparison with Aaron}
-%
-%The Airy integral can be written in terms of the modified Bessel equation as  
-%
-%\begin{equation}
-%Ai(x)=\frac{1}{\pi\sqrt{3}}x^{1/2}K(\frac{2}{3}x^{3/2}).
-%\end{equation}
-%On the other hand we have, for $z=x^{3/2}$
-%\begin{equation}
-%Ai(x)=-\frac{z^{1/3}}{2\pi i}I(z)=-\frac{1}{2\pi i}x^{1/2}I(x^{3/2}) 
-%\end{equation} 
-%hence
-%\begin{align*}
-%-\frac{1}{2\pi i}I(x^{3/2})&=\frac{1}{\pi\sqrt{3}}K(\frac{2}{3}x^{3/2})\\
-%\frac{i}{2} I(z)&=\frac{1}{\sqrt{3}}K(\frac{2}{3}z)
-%\end{align*}
-%In particular, the Borel trasforms of LHS and RHS\footnote{The conjugate variable of $z$ is $\zeta$, hence $\hat{K}(\frac{2}{3}z)=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta)$.
-Indeed assuming $K(z)=\sum_{n\geq 0}a_nz^{-n}$, the Borel transform of $K(\frac{2}{3}z)=\sum_{n\geq 0}a_n\left(\frac{3}{2}\right)^nz^{-n}$ is by definition \[\hat{K}(\frac{2}{3}z)=\sum_{k\geq 0}a_{n+1}\left(\frac{3}{2}\right)^{n+1}\frac{\zeta^n}{n!}=\frac{3}{2}\sum_{k\geq 0}\frac{a_{n+1}}{n!}\left(\frac{3}{2}\zeta\right)^{n}=\frac{3}{2}\hat{K}(\frac{3}{2}\zeta).
-\]} must be equal, i.e.
-%\begin{align*}
-%\frac{i}{2} \hat{I}(\zeta)&=\frac{\sqrt{3}}{2}\hat{K}(\frac{3}{2}\zeta)\\
-%&= \frac{\sqrt{3}}{2}\frac{1}{\sqrt{2}}(\frac{3}{2}\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
-%&=\frac{\sqrt{3}}{2}(3\zeta-2)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)\\
-%&=\frac{\sqrt{3}}{2}T_{-2/3}\left((3\zeta)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
-%&=\frac{1}{2}T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
-%\hat{I}(\zeta)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)
-%\end{align*}
-
-%%In addition, since $\hat{I}(\zeta)=C_3\partial_{\zeta,\text{based at } -2/3}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)$ is a solution of the Borel transform of equation \eqref{eq:I}; thus
-%%\begin{align*}
-%%C_3\partial_{\zeta,\text{based at } -2/3}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)&=-i T_{-2/3}\left(\frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\right)\\
-%%C_3\partial_{\zeta}^{1/2} {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)&=-i \frac{1}{\sqrt{\zeta}}\,\,{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)
-%%\end{align*} 
-%
-%Equation 5 in Aaron is 
-%\begin{equation}
-%\left[\frac{\partial^2}{\partial z^2}+2\frac{\partial}{\partial z}+\frac{1}{z}\frac{\partial}{\partial z}+\frac{1}{z}-\frac{1}{9z^2}\right]\kappa=0
-%\end{equation}
-%Its Borel transform is 
-%\begin{align*}
-%&\zeta^2\hat{\kappa}-2\zeta\hat{\kappa}+1\ast(-\zeta\hat{\kappa}+\hat{\kappa})-\frac{1}{9}\zeta\ast\hat{\kappa}=0 \\
-%&\zeta^2\hat{\kappa}-2\zeta\hat{\kappa}-\int_{0}^\zeta (s\hat{\kappa}(s)-\hat{\kappa}(s))ds-\frac{1}{9}\int_0^{\zeta}(\zeta-s)\hat{\kappa}(s)ds=0 \\
-%&\, \text{ taking derivatives once} \\
-%& 2\zeta\hat{\kappa}+\zeta^2\hat{\kappa}'-2\hat{\kappa}-2\zeta\hat{\kappa}'-\zeta\hat{\kappa}+\hat{\kappa}-\frac{1}{9}\int_0^{\zeta}\hat{k}(s)ds=0\\
-%& \zeta\hat{\kappa}+\zeta^2\hat{\kappa}'-\hat{\kappa}-2\zeta\hat{\kappa}'-\frac{1}{9}\int_0^{\zeta}\hat{k}(s)ds=0\\
-%&\, \text{ taking derivatives once again} \\
-%& \hat{\kappa}+\zeta\hat{\kappa}'+2\zeta\hat{k}'+\zeta^2\hat{\kappa}''-\hat{\kappa}'-2\hat{\kappa}'-2\zeta\hat{\kappa}''-\frac{1}{9}\hat{\kappa}=0\\
-%&(\zeta^2-2\zeta)\hat{\kappa}''+(3\zeta-3)\hat{k}'+\frac{8}{9}\hat{\kappa}=0
-%\end{align*} 
-%The last equation is a hypergeomtric equation and the fundamental solutions are (see DLMF 15.10.2) 
-%\begin{equation}
-%\hat{\kappa}_1(\zeta)={}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta}{2}\right)
-%\end{equation}
-%\begin{equation}
-%\hat{\kappa}_2(\zeta)=\frac{1}{\sqrt{2}}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta}{2}\right)
-%\end{equation}
-%
-%In particular, comparing with $\hat{I}(\zeta)$ we have 
-%
-%\begin{equation}
-%\hat{I}\left(\frac{2}{3}\zeta\right)=-i\sqrt{3}\hat{\kappa}_2(\zeta-1)
-%\end{equation}
-%
-%------------------------------------------------------------------------
-%
-%However, at pag. 5 in Aaron there is a different solution, namely 
-%\begin{align*}
-%\hat{\kappa}(\zeta-1)&=-i\sqrt{2}(\zeta-1)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)\\
-%\hat{\kappa}(\zeta)&=-i\sqrt{2}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right)=-2i\frac{\cosh\left(\frac{2}{3}\mathrm{arcsinh}\left(\frac{\sqrt{\zeta}}{\sqrt{2}}\right)\right)}{\sqrt{\zeta}\sqrt{2+\zeta}}
-%\end{align*} 
-%------------------------------------------------------------------------
-%
-%
-%As written by Aaron in Section 2.3, the asymptotic behvaior of $\kappa(z)$ is given by 
-%\begin{equation}
-%\kappa(z)\sim \left(\frac{\pi}{2z}\right)^{1/2}\sum_{n\geq 0}a_n(1/3)z^{-n}
-%\end{equation}
-%where $a_n(1/3)=\frac{(1/6)_n(5/6)_n}{(-2)^nn!}$. Hence the Borel transform of $\kappa(z)$ is
-%\begin{align*}
-%\hat{\kappa}(\zeta)&=\left(\frac{\pi}{2}\right)^{1/2}\sum_{n\geq 0}a_n(1/3)\frac{\zeta^{n-1/2}}{\Gamma(n+1/2)}\\
-%&=\left(\frac{\pi}{2}\right)^{1/2}\sum_{n\geq 0}\frac{(1/6)_n(5/6)_n}{(-2)^nn!}\frac{\zeta^{n-1/2}}{\Gamma(n+1/2)}\\
-%&=\frac{1}{\sqrt{2}}\zeta^{-1/2}\sum_{n\geq 0}\frac{(1/6)_n(5/6)_n}{(1/2)_nn!}\left(-\frac{\zeta}{2}\right)^n\\
-%&=\frac{1}{\sqrt{2}}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6}\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right)
-%\end{align*}
-%\begin{align*}
-%\hat{\kappa}(\zeta)&=\left(\frac{\pi}{2}\right)^{1/2}\mathcal{B}(z^{-1/2})\ast\left(\delta+\sum_{n\geq 0}a_{n+1}(1/3)\frac{\zeta^n}{n!}\right)=\frac{1}{\sqrt{2}}\zeta^{-1/2}\ast\left(\delta-\frac{5}{72}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\right)\\
-%&=\frac{1}{\sqrt{2\zeta}}-\frac{5}{72\sqrt{2}}\int_0^{\zeta}(\zeta-s)^{-1/2}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{s}{2}\right)ds\\
-%&=\frac{1}{\sqrt{2\zeta}}+\frac{1}{\sqrt{2}}\int_0^{\zeta}(\zeta-s)^{-1/2}\frac{d}{ds}\left({}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{s}{2}\right)\right)ds\\
-%&\textcolor{red}{=\frac{1}{\sqrt{2}}\partial_\zeta^{1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)}\, \textcolor{red}{\text{ is wrong!}}\\
-%\end{align*}
-%
-%\subsubsection{Algebraic Hypergeometric}
-%Aaron cliams 
-%\begin{equation}
-%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)=\textcolor{red}{-}\frac{1}{4u^2-1}\qquad \text{wtih } \zeta=-4u^3+3u
-%\end{equation}
-%\begin{proof}
-%\begin{align*}
-%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)&=\cos\left(\frac{1}{3}\arcsin(\zeta)\right)(1-\zeta^2)^{-1/2} & \text{Mathematica [Fullsimplify] } \\
-%&=\frac{\cos(y)}{\cos(3y)} & 3y=\arcsin(\zeta)\\
-%&=\frac{\cos(y)}{\cos(2y)\cos(y)-\sin(2y)\sin(y)} & \\
-%&=\frac{1}{\cos(2y)-2\sin^2(y)} & \\
-%&=\frac{1}{1-4\sin^2(y)} & \zeta=3\sin(y)-4\sin^3(y)
-%\end{align*}
-%Therefore, if $u\defeq\sin(y)$, we have $\zeta=-4u^3+3u$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)=\frac{1}{1-4u^2}=\frac{1}{3}\frac{1}{f'(u)}\]
-%\end{proof}
-%Now, we notice that 
-%\begin{align*}
-%{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\zeta^2\right)&=2 {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+2 {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) & 15.8.27 \text{ DLMF} \\
-%&=-{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{\zeta}{2}\right)-3\sqrt{3}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{\zeta}{2}\right)+ & 15.10.17 \text{DLMF}\\
-%&\qquad -{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{\zeta}{2}\right)+3\sqrt{3}i\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta}{2}\right) & 15.10.17 \text{DLMF}\\
-%&=-\hat{\kappa}_1(\zeta)-3\sqrt{6}\hat{\kappa}_2(\zeta)-\hat{\kappa}_1(-\zeta)+3\sqrt{6}\hat{\kappa}_2(-\zeta) \\
-%&=-(\hat{\kappa}_1(\zeta)+\hat{\kappa}_1(-\zeta))-3\sqrt{6}
-%\end{align*}
 \end{example}

### 2022-02-23 modified bessel.tex
update modified Bessel

@@
 \usepackage{graphicx}
-
+\usepackage{xcolor}
 % convenience aliases
@@
 \newcommand{\laplace}{\mathcal{L}}
+\include{command}
 
@@
 
-The modified Bessel function of the second kind $K_\nu(z)$ is a solution of the equation
+The modified Bessel function of the second kind $K_\mu(z)$ is a solution of the equation
 \begin{equation}\label{Bessel_nu}
-w''+\frac{w'}{z}-w-\frac{\nu^2}{z^2}=0
+w''+\frac{w'}{z}-w-\frac{\mu^2}{z^2}=0
 \end{equation}
-such that $K_{\nu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$\footnote{A system of solution of Bessel equation is given by $I_\nu(z)$ and $K_\nu(z)$.
+such that $K_{\mu}(z)\sim\sqrt{\pi/(2z)}e^{-z}$ as $z\to\infty$ in $|\arg z|<\frac{3\pi}{2}$\footnote{A system of solution of Bessel equation is given by $I_\mu(z)$ and $K_\mu(z)$.
 In particular, their asymptotic behaviour as $z\to\infty$ is given by \begin{align}
-\tilde{I}_\nu(z)&=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\nu\right)_k\left(\frac{1}{2}+\nu\right)_k}{2^kk!}z^{-k}\\
-\tilde{K}_{\nu}(z)&=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\nu\right)_k\left(\frac{1}{2}+\nu\right)_k}{(-2)^kk!}z^{-k}
-\end{align}}. It has a branch point at $z=0$ for every $\nu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
+\tilde{I}_\mu(z)&=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{2^kk!}z^{-k}\\
+\tilde{K}_{\mu}(z)&=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\sum_{k\geq 0}\frac{\left(\frac{1}{2}-\mu\right)_k\left(\frac{1}{2}+\mu\right)_k}{(-2)^kk!}z^{-k}
+\end{align}}. It has a branch point at $z=0$ for every $\mu\in\C$ and  the principal branch is analytic in $\C\setminus(-\infty,0]$. 
 \subsection{Differential equation}
@@
 \begin{equation}
-\tilde{w}(z)=U_1e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)+U_2e^{z}z^{-1/2}\tilde{w}_{\nu,-}(z)
+\tilde{w}(z)=U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)+U_2e^{z}z^{-1/2}\tilde{w}_{\mu,-}(z)
 \end{equation} 
-where $\tilde{w}_{\nu,\pm}=\sum_{j\geq 0}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
+where $\tilde{w}_{\mu,\pm}=\sum_{j\geq 0}a_{\pm,j}z^{-j}\in\C[\![z^{-1}]\!]$ are unique formal solutions of
 \begin{align*}
-\tilde{w}_{\nu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_{\nu,+}}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,+}=0\\
-\tilde{w}_{\nu,-}''+2\tilde{w}_{\nu,-}'+\frac{\tilde{w}_{\nu,-}}{4z^2}-\frac{\nu^2}{z^2}\tilde{w}_{\nu,-}=0
+\tilde{w}_{\mu,+}''-2\tilde{w}_{\nu,+}'+\frac{\tilde{w}_{\mu,+}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,+}=0\\
+\tilde{w}_{\mu,-}''+2\tilde{w}_{\mu,-}'+\frac{\tilde{w}_{\mu,-}}{4z^2}-\frac{\mu^2}{z^2}\tilde{w}_{\mu,-}=0
 \end{align*} 
-In particular, $\tilde{K}_{\nu}(z)=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\tilde{w}_{\nu,+}(z)$ and $\tilde{I}_\nu(z)=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\tilde{w}_{\nu,-}(z)$ (once we choose $a_{\pm,0}=1$).
-We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\nu,\pm}$, i.e.
+In particular, $\tilde{K}_{\mu}(z)=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)$ and $\tilde{I}_\mu(z)=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\tilde{w}_{\mu,-}(z)$ (once we choose $a_{\pm,0}=1$).
+We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\mu,\pm}$, i.e.
 $\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.} it is a solution of
 \begin{align*}
-&\zeta^2\hat{w}_{\nu,+}+2t\hat{w}_{\nu,+}+\left(\frac{1}{4}-\nu^2\right)\int_0^{\zeta}(\zeta-s)\hat{w}_{\nu,+}(s)ds=0 &\\
-&\zeta^2\hat{w}_{\nu,+}''+2\zeta\hat{w}_+''+4\zeta\hat{w}_{\nu,+}'+\left(\frac{9}{4}-\nu^2\right)\hat{w}_{\nu,+}=0 & \\
-&t(1-t)\hat{w}_{\nu,+}''+(2-4t)\hat{w}_{\nu,+}'-\left(\frac{9}{4}-\nu^2\right)\hat{w}_{\nu,+}=0 & t=-\frac{\zeta}{2}
+&\zeta^2\hat{w}_{\mu,+}+2t\hat{w}_{\mu,+}+\left(\frac{1}{4}-\nu^2\right)\int_0^{\zeta}(\zeta-s)\hat{w}_{\nu,+}(s)ds=0 &\\
+&\zeta^2\hat{w}_{\mu,+}''+2\zeta\hat{w}_+''+4\zeta\hat{w}_{\mu,+}'+\left(\frac{9}{4}-\mu^2\right)\hat{w}_{\mu,+}=0 & \\
+&t(1-t)\hat{w}_{\mu,+}''+(2-4t)\hat{w}_{\mu,+}'-\left(\frac{9}{4}-\mu^2\right)\hat{w}_{mu,+}=0 & t=-\frac{\zeta}{2}
 \end{align*} 
-therefore $\hat{w}_{\nu,+}(\zeta)$ is an hypergeometric function
+therefore $\hat{w}_{\mu,+}(\zeta)$ is an hypergeometric function
 \begin{equation}
-\hat{w}_{\nu,+}(\zeta)={}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;-\frac{\zeta}{2}\right)
+\hat{w}_{\mu,+}(\zeta)={}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\frac{\zeta}{2}\right)
 \end{equation}
@@
 \begin{equation}
-\hat{w}_{\nu,-}(\zeta)={}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;\frac{\zeta}{2}\right)
+\hat{w}_{\mu,-}(\zeta)={}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{\zeta}{2}\right)
 \end{equation} 
@@
 \begin{align*}
-\hat{w}_{\nu,+}(\zeta+i0)-\hat{w}_{\nu,+}(\zeta-i0)&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}+\nu,\frac{1}{2}-\nu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
-&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\frac{1}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\sum_{k\geq 1}\frac{\Gamma\left(\tfrac{1}{2}-\nu+k\right)\Gamma\left(\tfrac{1}{2}+\nu+k\right)}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\frac{1}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\nu+k\right)\Gamma\left(\tfrac{3}{2}+\nu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
-&=-\frac{2\pi i}{\Gamma\left(\frac{1}{2}-\nu\right)\Gamma\left(\frac{1}{2}+\nu\right)}\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1+\frac{\zeta}{2}\right) & \\
-&=-2i\cos(\nu \pi)\hat{w}_{\nu,-}(\zeta+2)
+\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\left(\hat{w}_{\mu,+}(\zeta+i0)-\hat{w}_{\mu,+}(\zeta-i0)\right)&=\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}+\mu,\frac{1}{2}-\mu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot\\
+& \qquad\cdot \sum_{k\geq 1}\frac{\Gamma\left(\tfrac{1}{2}-\mu+k\right)\Gamma\left(\tfrac{1}{2}+\mu+k\right)}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot \\
+&\qquad\cdot \sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\mu+k\right)\Gamma\left(\tfrac{3}{2}+\mu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1+\frac{\zeta}{2}\right) & \\
+&=-2i\textcolor{red}{\sqrt{\pi}}\hat{w}_{\mu,-}(\zeta+2)
 \end{align*} 
-and for $\hat{w}_{\nu,-}(\zeta)$
+and for $\hat{w}_{\mu,-}(\zeta)$
 \begin{align*}
-\hat{w}_{\nu,-}(\zeta+i0)-\hat{w}_{\nu,-}(\zeta-i0)&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\left(\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\nu,\frac{1}{2}+\nu;0;1-\frac{\zeta}{2}\right) & \zeta<2 \\
-&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\nu)\Gamma(\tfrac{3}{2}+\nu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\nu\right)_k\left(\tfrac{1}{2}+\nu\right)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{2}\right)^{k-1} & \\
-&=2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\nu,\frac{3}{2}+\nu;2;1-\frac{\zeta}{2}\right) & \\
-&=2i\cos(\nu \pi)\hat{w}_{\nu,+}(\zeta-2)
+\hat{w}_{\mu,-}(\zeta+i0)-\hat{w}_{\mu,-}(\zeta-i0)&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\left(\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;0;1-\frac{\zeta}{2}\right) & \zeta<2 \\
+&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{2}\right)^{k-1} & \\
+&=2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1-\frac{\zeta}{2}\right) & \\
+&=2i\cos(\mu \pi)\hat{w}_{\mu,+}(\zeta-2)
 \end{align*}
-In addition, the previous relations computes the Stokes constants which are funtions of $\nu$ and are given by $\pm 2i\cos(\nu\pi)$.
+In addition, the previous relations computes the Stokes constants which are funtions of $\nu$ and are given by $\pm 2i\cos(\mu\pi)$.
 
 \subsection{Exponential integral}
+
+Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and for every $\mu\in [0,+\infty)$ let $\nu=x^{\mu-1}+\frac{1}{x^{\mu+1}}dx$, then
+
+\begin{equation}
+I(z;m)\defeq\int_{0}^{\infty}e^{-zf}\nu
+\end{equation}
+
+In particulr, on the universal cover $\pi\colon\tilde{C}\to \C^*$ setting $x=e^u$ 
+\begin{equation}
+I(\frac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
+\end{equation} 
+where $K_\mu(z)$ is the second kind modified Bessel function with parameter $\mu$.
+It is worth mentioning that $I(z;\mu)$ differs from $I(z;0)$ only in $\pi^*(\nu)$ while $\pi^*(f)$ stays the same for every $\mu\in [0,\infty)$.
+Hence we can adapt part of the argument used in Bessel example (see ), and verify the $3/2$-derivative formula: let $\zeta=\cosh(u)$
+
+\begin{align*}
+\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)&=\int_{\mathcal{C}_0(\zeta)}\cosh(\mu u)du\\
+&=\frac{1}{\mu}\Big[\sinh(\mu u)\Big]_{\mathrm{start}\mathcal{C}_0(\zeta)}^{\mathrm{end}\mathcal{C}_0(\zeta)}\\
+&=\frac{1}{\mu}\left(\sinh\left(\mu\,\mathrm{acosh}\left(\zeta\right)\right)-\sinh\left(-\mu\,\mathrm{acosh}\left(\zeta\right)\right)\right)\\
+&=\frac{2}{\mu}\sinh\left(\mu\,\mathrm{acosh}\left(\zeta\right)\right)
+\end{align*}
+
+The we set $\xi=\frac{1}{2}\left(\zeta-1\right)$, thanks to identity 15.4.16 \textbf{DLMF}
+
+\begin{align*}
+\sinh(\tau) {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\sinh^2(\tau)\right)&=\frac{1}{2\mu}\sinh(2\mu\tau) & \\
+\xi^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\xi\right)&=\frac{1}{2\mu}\sinh(2\mu\tau)  & \sinh^2(\tau)=\xi \\
+\xi^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\xi\right)&=\frac{1}{2\mu}\sinh(\mu\,\,\mathrm{acosh}\left(\zeta\right))  & \cosh(2\tau)=\zeta \\
+&=\frac{1}{4}\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu) &\\
+\end{align*}
+
+Thus we take $3/2$-derivative based at $\zeta=1$
+
+\begin{align*}
+\partial_{\zeta}^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_1^\zeta(\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta')}\pi^*(\nu)\right)d\zeta'\right)\\
+&=4\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^\xi\frac{1}{2}(\xi-\xi')^{-1/2}\xi^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\xi'\right) 4\,\,d\xi'\right)\\
+&=8\partial_\zeta^2\left(\Gamma\left(\frac{3}{2}\right)\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right) \\
+&=4\sqrt{\pi}\frac{1}{4}\partial_\xi^2\left(\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right)\\
+&=-\sqrt{\pi}\partial_{\xi}\,\, {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;1;-\xi\right)\\
+&=\sqrt{\pi}\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right){}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\xi\right)\\
+&=\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}{}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{1}{2}-\frac{\zeta}{2}\right)\\
+&=\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}\hat{w}_{\mu,+}(\zeta-1)
+\end{align*}
+
+\color{orange}
 As showed by Aaron, if $T_n(u)$ and $U_n(u)$ denote the Chebyschev polynomials \footnote{$T_n(\cos(t))=\cos(nt)$ and $U_n(\cos(t))\sin(t)=\sin((n+1)t)$.}
@@
 \] 
+\color{black}
+
 \bibliographystyle{utphys}

### 2022-02-23 draft2.tex

@@
 \begin{align*}
-\hat{u}_+(\zeta)&=C_1 T_{-2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-2/3}\hat{w}_+(\zeta)\\
-\hat{u}_-(\zeta)&= C_2 T_{2/3} {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{2/3}\hat{w}_-(\zeta) & \\
+\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\;\hat{w}_+(\zeta)\\
+\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\;\hat{w}_-(\zeta)
 \end{align*}
@@
 
-By change of cooridnates $t=zx$
+Let $\pi\colon\tilde{\C}\to \C^*$ be the universal cover of $\C^*$, where $\pi(u)=e^u$, then on $\tilde{\C}$, $I(z)$ turns into
 \begin{align*}
-I(z)=\int_0^{\infty}e^{-z\left(\frac{t}{z}+\frac{z}{t}\right)}\frac{dt}{t}=\int_0^{\infty}e^{-\left(t+\frac{z^2}{t}\right)}\frac{dt}{t}=2K_0(2z) \,\qquad |\arg z|<\frac{\pi}{4}
+I(z)=\int_{-\infty}^{\infty}e^{-2z\cosh(u)}du=2\int_0^{\infty}e^{-2z\cosh(u)}du=2K_0(2z) \,\qquad |\arg z|<\frac{\pi}{2}
 \end{align*}
@@
 We set $\tilde{w}_{(1,0)}=\tilde{w}_+$ and $\tilde{w}_{(0,1)}=\tilde{w}_-$, then their Borel transforms are solutions respectively of the following equations 
+\begin{align}
+\zeta^2\hat{w}_+(\zeta)+4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0\\
+\zeta^2\hat{w}_-(\zeta)-4\zeta\hat{w}_-(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_-(\zeta)=0
+\end{align}
+taking twice derivative in $\zeta$ we get respectively for $\hat{w}_+(\zeta)$ and $\hat{w}_-(\zeta)$
 \begin{align*}
-(+)\quad &\zeta^2\hat{w}_+(\zeta)+4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0\\
-(-)\quad &\zeta^2\hat{w}_+(\zeta)-4\zeta\hat{w}_+(\zeta)+\frac{1}{4}\zeta\ast\hat{w}_+(\zeta)=0
+&(\zeta^2+4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_++4(\zeta-1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_+=0 &\\
+(+)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_++(1-4\xi)\frac{d}{d\xi}\hat{w}_+-\frac{9}{4}\hat{w}_+=0 & \xi=-\frac{\zeta}{4} 
 \end{align*}
-taking twice derivative in $\zeta$ we get
 \begin{align*}
-(+)\quad &(\zeta^2+4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_++4(\zeta-1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_+=0 &\\
-(-)\quad &(\zeta^2-4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_-+4(\zeta+1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_-=0 &\\
-(+)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_++(1-4\xi)\frac{d}{d\xi}\hat{w}_+-\frac{9}{4}\hat{w}_+=0 & \xi=-\frac{\zeta}{4} \\
+&(\zeta^2-4\zeta)\frac{d^2}{d\zeta^2}\hat{w}_-+4(\zeta+1)\frac{d}{d\zeta}\hat{w}_++\frac{9}{4}\hat{w}_-=0 &\\
 (-)\quad &\xi(1-\xi)\frac{d^2}{d\xi^2}\hat{w}_-+(1-4\xi)\frac{d}{d\xi}\hat{w}_--\frac{9}{4}\hat{w}_-=0 & \xi=\frac{\zeta}{4}
 \end{align*}
-therefore, since equation $(+), (-)$ are hypergeometric the fundamental solution is (see DLMF 15.10.2)
+Since equation $(+), (-)$ are hypergeometric, the fundamental solutions are respectively (see DLMF 15.10.2)
 \begin{align}
@@
 These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.
+\textbf{Hopefully, the latter identities show that the Stokes constants can be computed via Alien calculus and they are equal to $\pm 2$.
+}
 
-\begin{lemma}
-The following identity holds true
+Now we show that the fractional derivative formula holds in this example: first we write a parametrization of the integration path in the Borel plane.
+Let $\mathcal{C}_p=\R$, $p\in \pi\Z$, be the contour of integration in $\tilde{\C}$ which is parametrized as
+
+\begin{align*}
+{C}_p\colon \R & \to \tilde{\C} \\
+\theta & \to \theta+i p
+\end{align*}
+
+Then in the Borel plane $\C_\zeta$, where $\zeta=2\cosh(u)$, the path $\mathcal{C}_0$ is parametrized as  
+\begin{align*}
+\mathcal{C}_0\colon\R &\to \C_\zeta \\
+\theta & \to 2\cosh(\theta)
+\end{align*}
+
+\begin{figure}
+\caption{Integration path in the $u$-plane and in the Borel plane $\zeta=2\cosh(u)$. }
+\end{figure}
+
+\textbf{Check Aaron notation}
+
 \begin{equation}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}\qquad \qquad \zeta=u+\frac{1}{u}
+\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)=\int_{\mathcal{C}_0(\zeta)}du=\Big[ u\Big]^{\mathrm{end}\mathcal{C}_0(\zeta)}_{\mathrm{start}\mathcal{C}_0(\zeta)}=2\mathrm{arc}\cosh\left(\frac{\zeta}{2}\right)
 \end{equation}
-\end{lemma}
-\begin{proof}
-From 15.4.13 DLMF, we have
+
+We can now write $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 14.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta-1\right)=\frac{1}{2}\left(\cosh(\theta)-1\right)=\sinh^2\left(\frac{\theta}{2}\right)$, then
+
 \begin{align*}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)&=\frac{2}{\sqrt{4-\zeta^2}} & y=\mathrm{arccsc}(\zeta/2)\\
-&=\frac{1}{\sqrt{1-\mathrm{csc}^2(y)}} & \\
-&=-i\tan(y) &   \zeta=\frac{2}{\sin(y)}
+\sinh\left(\frac{\theta}{2}\right)\,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\sinh^2\left(\frac{\theta}{2}\right)\right)&=i\frac{\theta}{2} \\
+\xi^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi\right)&=i\frac{\theta}{2}\\
+ &=\frac{i}{2}\left(\frac{1}{2}\mathrm{arcosh}\left(\frac{\zeta}{2}\right)\right)\\
+ &=\frac{i}{4}\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)
 \end{align*}
-therefore if $u=\tan\left(\frac{y}{2}\right)$, we have $\zeta=\frac{1+u^2}{u}=f(u)$ and 
-\begin{equation*}
-{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{1}{2};\frac{\zeta^2}{4}\right)=2i\frac{u}{u^2-1}=\frac{2i}{f'(u)u}
-\end{equation*}  
-\end{proof}
 
-\begin{claim}
-\label{Bessel}
-\begin{equation}
-\hat{w}_{+}(\zeta-2)=i\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}2\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'\,\qquad \zeta\in(2,+\infty)
-\end{equation}
-\end{claim}
-\begin{proof}
-Let us first consider the RHS of \eqref{Bessel}
+The $3/2$-derivative of $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ can be computed as follows: we compute the $-1/2$-derivatve and then we differentiate twice
+
 \begin{align*}
-&2\pi\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\zeta'\,\,{}_2F_1\left(\frac{3}{2},\frac{3}{2};\frac{3}{2};\frac{\zeta^2}{4}\right)d\zeta'= &\\
-&\quad = \frac{4}{3}\int_{2}^\zeta(\zeta-\zeta')^{-1/2}\left[{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}+\frac{\zeta'}{4}\right)-{}_2F_1\left(2,2;\frac{5}{2};\frac{1}{2}-\frac{\zeta'}{4}\right)\right]d\zeta' &\\
-&\quad =\frac{8}{3}\int_0^x(y-x)^{-1/2}\left[{}_2F_1\left(2,2,;\frac{5}{2};y\right)-{}_2F_1\left(2,2;\frac{5}{2};1-y\right)\right]dy & x\in (-\infty,0)\\
-&\quad =2\pi\int_0^x(x-y)^{-1/2}y^{-2}F\left(2,\frac{1}{2};1;\frac{1}{y}\right)dy & \eqref{4.8} \\
-&\quad =\pi^2|x|^{-3/2}{}_2F_1\left(\frac{3}{2},\frac{1}{2};1;\frac{1}{x}\right) & x\in (-\infty, 0)\\
-&\quad =\frac{\pi^2}{2}\left({}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}-\frac{\zeta}{4}\right)-i{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)\right) & \zeta\in(2,+\infty)
+\partial_{\zeta}^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_2^\zeta (\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)d\zeta'\\
+&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)\xi'^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi'\right) 4d\xi'\\
+&=-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)
 \end{align*}
-however ${}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{1}{2}+\frac{\zeta}{4}\right)$ has a branch cut at $\zeta\in(2,+\infty)$, thus the claim holds true. 
-\end{proof}
-Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
+
+\begin{align*}
+\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \\
+&=\frac{1}{16}\partial_\xi^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
+&=+\frac{i}{2}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,-\xi\right)\right) & \textbf{DLMF} 15.5.4\\
+&=-\frac{i}{8}\Gamma\left(\frac{3}{2}\right){}_2F_1\left(\frac{3}{2},\frac{3}{2};2,-\xi\right) & \\
+&=-\frac{i\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}-\frac{\zeta}{4}\right) & \\
+&=-\frac{i\sqrt{\pi}}{16} \hat{w}_+(\zeta-2) &
+\end{align*}
+
+%Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
 \end{example}

### 2022-02-25 exp-resurgence.tex
Introduce to Borel regularity

@@
 \usepackage{amssymb}
+\usepackage{bm} %% for putting series names in bold
 %%\usepackage{amsthm}
-\usepackage{graphicx}
+%%\usepackage{graphicx}
+
+%% colors
+\usepackage[dvipsnames]{xcolor}
 
@@
 \newcommand{\C}{\mathbb{C}}
+%%\let\Re\relax
+%%\DeclareMathOperator{\Re}{Re}
+\DeclareMathOperator{\Ai}{Ai}
 \newcommand{\laplace}{\mathcal{L}}
-\DeclareMathOperator{\Ai}{Ai}
+\newcommand{\borel}{\mathcal{B}}
+\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
+\newcommand{\series}[1]{#1_\bullet}
 
@@
 \subsection{Why does Borel resummation work?}
+Borel resummation is a way of turning a formal power series
+\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
+with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
+Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
+When a function matches its Borel sum, we'll say it's {\em Borel regular}.
+Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
+%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
+%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
+\begin{itemize}
+\item \textbf{Having a good asymptotic approximation}
+
+Let $R_N$ be the difference between a function and the partial sum
+\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+\item \textbf{Satisfying a singular differential equation}
+\item \textbf{Being a thimble integral}
+
+Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
+Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\bar{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
+A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
+
+Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \bar{X} \to \bar{B}$ that sends punctures to punctures.
+Suppose the critical points of $f$ are all simple.
+For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
+These are well-defined as long as $\Gamma_p$ misses the singularities of $B$.
+The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
+\textbf{[Is $B$ is the Borel plane?
+Can we assume all its singularities are critical values of $f$?]} The {\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
+The {\em thimble integral}
+\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
+is a holomorphic function on the right half-plane parameterized by $z$, and it turns out \textbf{[we hope]} to be Borel regular.
+
+\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
+
+In higher-dimensional complex manifolds, integrals over Lefschetz thimbles are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
+This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
+Physicists often use Borel summation and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...'']}.
+
+\color{Turquoise}
+Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
+\textbf{[How do we get jumps at the critical values?]} Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
+This data defines the {\em exponential integral}
+\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
+a holomorphic function on the right half-plane parameterized by $z$.
+It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points.
+The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
+\color{black}
+\end{itemize}
 \begin{itemize}

### 2022-02-25 modified bessel.tex

@@
 \newcommand{\laplace}{\mathcal{L}}
-\include{command}
+\include{command2}
 
@@
 
-\color{orange}
-As showed by Aaron, if $T_n(u)$ and $U_n(u)$ denote the Chebyschev polynomials \footnote{$T_n(\cos(t))=\cos(nt)$ and $U_n(\cos(t))\sin(t)=\sin((n+1)t)$.}
-
-\begin{align*}
-K_{\nu}(z)&=\frac{1}{2 i\sin(\nu \pi)}\int_{\mathcal{C}_{\alpha}}e^{z\cosh(t)}\sinh(\nu t) dt & u=\cosh(\nu t)\\
-&=-\frac{1}{2i\nu\sin(\nu\pi)}\int_{\mathcal{C}_{\alpha}}e^{zT_{\frac{1}{\nu}}(u)}du & \zeta=T_{\frac{1}{\nu}}(u)\\
-&=\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\frac{d\zeta}{U_{\frac{1}{\nu}-1}(u)}\\
-&=-\frac{1}{2i\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)d\zeta
-\end{align*}
-where $\mathcal{C}_{\alpha}$ \textbf{has to be checked, but I guess } $\alpha=1$
-
-Indentity 15.10.17 from \cite{dlmf} splits the integrand above into
-\begin{align*}
-{}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{3}{2};1-\zeta^2\right)&=C_1 \, {}_2F_1\left(\frac{1-\nu}{2},\frac{1+\nu}{2};\frac{1}{2};\zeta^2\right)+C_2\zeta \,{}_2F_1\left(1-\frac{\nu}{2},1+\frac{\nu}{2};\frac{3}{2};\zeta^2\right)\\
-&=\tilde{C}_1\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right]+\\
-&\qquad+\tilde{C}_2\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right]
-\end{align*}
-therefore, collecting the contrubutions together we have 
-\begin{multline}
-K_{\nu}(z)=\frac{i}{4\sin(\nu\pi)}\int_{\mathcal{H}_{\alpha}}e^{-\zeta z}\left[{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\right] d\zeta
-\end{multline}
-
-Since ${}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) $ is singular at $\zeta=1$, the inverse Laplace transform of $K_\nu(z)$ is 
-\[
-\hat{K}_{\nu}(\zeta)=\frac{i}{4\sin(\nu\pi)}{}_2F_1\left({1-\nu},{1+\nu};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
-\] 
-\color{black}
-
 \bibliographystyle{utphys}

### 2022-02-25 draft2.tex
minor changes

@@
 
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. For each cutoff $N$, the tail
+This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
+We can, however, set aside any finite set of them.
+\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.]} For each cutoff $N$, the tail
 \[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
+
+\color{CarnationPink}
+For each cutoff $N$, the tail error \textbf{[check]}
+\begin{align*}
+\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
+& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
+& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
+& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
+& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
+& = \textbf{uh-oh!}
+\end{align*}
+\color{violet}
 is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
@@
 \end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}. Hence,
+is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
 \[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]

### 2022-03-02 exp-resurgence.tex
Add notes about differential equation regularity

@@
 Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches its Borel sum, we'll say it's {\em Borel regular}.
+When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
 Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
@@
 \item \textbf{Satisfying a singular differential equation}
+
+\begin{itemize}
+\item Think about conditions where this works.
+\item Maybe the correct place is the setting of Ecalle's formal integral. See \S 5.2.2.1 of Delabaere's {\em Divergent Series, Summability and Resurgence III}.
+\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform.
+\item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resugence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.
+\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+\end{itemize}
 \item \textbf{Being a thimble integral}

### 2022-03-07 draft2.tex
Add preliminaries on resurgence

@@
 
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}$ for all $\lambda \in (0, \infty)$.
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
 This extends the semigroup law:
@@
 Here's what's nice about it.
-\begin{theorem}\label{thm:frac-diff-borel}
-Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
-for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-\end{theorem}
+
+\subsection{Borel transform}
+\color{black}
+We breifly recall some basic facts on Borel transform and its properties (more details can be founded at \cite{MS}, \cite{MDiablerets}, \cite{}, \cite{}).
+The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$: \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
+\mathcal{B}(1)&\defeq\delta 
+\end{align*}
+
+where $\delta$ is the element $(1,0)\in\C\times\C[\![\zeta]\!]$\footnote{In the physical literature (\cite{MDiablerets}\cite{SGM}) many authors adopt a different convention, namely they define $\mathbb{B}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+However, we find more natural the mathematical convention as the Laplace transform is the inverse of $\mathcal{B}$ under suitable growth conditions.
+}, and $\mathcal{B}$ extends formally by linearity to
+
+\begin{align*}
+\mathcal{B}\colon \C[\![z^{-1}]\!] & \to \C\delta\oplus\C[\![\zeta\!]] \\
+\sum_{n\geq 0}a_n z^{-n} & \to  a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}
+\end{align*}
+
+Notice that we are at the level of formal series, so there are no convergence assumptions.
+However, there is a special class of formal series that behaves well under Borel transform, meaning that its Borel transform gives a holomorphic fucntion at the origin in $\C_{\zeta}$.
+These are the so called Gevrey-$1$ series: $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
+}
+
 \begin{lemma}
+Let $f(z)=\sum_{n\geq 0}a_nz^{-n}$, $f(z)$ is Gevrey-$1$ if and only if $\hat{f}(\zeta)\defeq\mathcal{B}(f)\in\C\lbrace\zeta\rbrace$.  
+\end{lemma}
+In particular, we deduce from the lemma that the Borel transform is an isomorphism between Gevrey-$1$ series and $\C\delta\oplus\C\lbrace\zeta\rbrace$.
+
+For what follows, it is convenient to extend the definition of $\mathcal{B}$ to fractional power of $z$, replacing the factorial with the Gamma function: 
+\begin{align*}
+\mathcal{B}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
+\end{align*}
+
+\subsubsection{Properties of the Borel transform}
+We now recall some properties of the Borel transform: let $f(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\hat{f}(\zeta)\defeq\mathcal{B}(f(z))$
+
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R\setminus\Z_{\leq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^nf(z))=\partial_\zeta^n\hat{f}(\zeta)$ 
+\item[(iv)] $\mathcal{B}\left(\partial_z^{n} f(z)\right)=(-\zeta)^n\hat{f}(\zeta)$, for every $n\geq 0$
+\item[(v)] $\mathcal{B}(f(z-c))=e^{-c\zeta}\hat{f}(\zeta)$
+\item[(vi)] if $g(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(f(z)g(z))=\int_0^{\zeta}d\zeta \hat{f}(\zeta-\zeta')\hat{g}(\zeta')=:\hat{f}\ast \hat{g}$, where $\hat{g}(\zeta)=\mathcal{B}(g(z))$.
+\end{itemize}
+
+\begin{lemma}\label{lem:frac-deriv-Borel}
 For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
@@
 \end{proof}
+
+\begin{proof}
+(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel (z^\alpha f(z))=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\hat{f}(\zeta).\]
+
+(iii) $z^nf(z)=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel (z^n f(z))=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\hat{f}(\zeta).\]
+
+(vi) $\partial_z^n f(z)=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel (z^\alpha f(z))=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\hat{f}(\zeta).\]
+
+(v) see Lemma 5.10 \cite{MS16}.
+
+(vi) see Definition 5.12 and Lemma 5.14 \cite{MS16}. 
+\end{proof}
+
+\begin{remark}
+We notice that properties (i) and (ii) are special cases of property (vi), indeed we can use the convolution product 
+\begin{align*}
+\borel (z^\alpha f(z))&=\borel (z^\alpha)\ast \hat{f}(\zeta)\\
+&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\hat{f}(\zeta)\\
+&=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\int_0^1(t\zeta)^{-\alpha-1}(\zeta-t\zeta)^k\zeta dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\int_0^1 t^{-\alpha-1}(1-t)^k dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\frac{\Gamma(k+1)\Gamma(-\alpha)}{\Gamma(k-\alpha+1)}\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
+&=\partial_\zeta^\alpha\hat{f}(\zeta)
+\end{align*}
+\end{remark}
+
+\subsection{Laplace transform}
+ \textbf{Copy from Aaron}
+
+\subsection{Borel--Laplace summability}
+
+\[
+\begin{tikzcd}
+\C\oplus z^{-1}\C[\![z^{-1}]\!]_1\arrow[rr,"\borel"]& & \C\delta\oplus \C\lbrace\zeta\rbrace\cap\mathcal{N}\arrow[dl,"\mathcal{L}"]\\
+& s \arrow[lu, "\text{Gevrey asymptotic}"] & 
+\end{tikzcd}
+\]
+
+\subsection{Resurgence}
+
+Alternative to Borel--Laplace summability, J.
+Ecalle introduced the theory of resurgence: divergent power series that are Gevrey-$1$ become germs of holomorphic functions at the origin in the Borel plane.
+Being divergent, they have singularities in Borel plane and the aim is to investigate the type of singularities and the analytic continuation of the germ.
+Indeed a formal series is resurgent if it admits an \textit{endless} analytic continuation.
+
+\begin{definition}
+A germ of analytic functions $\hat{f}$ at the origin is \emph{endlessly continuable }on $\C$ if for all $L>0$, there exists a finite set $\Omega\subset\C$ of singularities, such that $\hat{f}$ can be analytically continued along all paths whose length is less than $L$, avoiding the singularities $\Omega$.
+\end{definition}
+
+\[
+\begin{tikzcd}
+\C\oplus z^{-1}\C[\![z^{-1}]\!]_1\arrow[r,"\borel"]& \C\delta\oplus \C\lbrace\zeta\rbrace\arrow[rr,"\text{analytic cont.} "] & & \mathcal{R}_{\Omega}\arrow[r, "\pi"]& \widetilde{\C\setminus\Omega}
+\end{tikzcd}
+\]
+
+Among resurgent series, the class of simple resurgent series is caracterized by having a special type of singularities:
+
+\begin{definition}
+A holomorphic function $\hat{f}$ in an open disk $D\subset \C_{\zeta}$ has a simple singularity at $\omega$, adherent to $D$, if there exist $\alpha\in\C$ and a germs of analytic functions at
+the origin $\hat{\Phi}(\zeta)\in\C\lbrace\zeta\rbrace$, such that
+\begin{equation}
+\hat{f}(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\log(\zeta-\omega)\hat{\Phi}(\zeta-\omega)+\text{hol. fct.}
+\end{equation}
+for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\Phi}$ the minor.
+\end{definition}
+
+The holomorphic function $\hat{\Phi}$ associated with the logarithmic singularity can be obtained by considering the analytic continuation of $\hat{f}$ across the logarithmic branch cut
+\begin{equation}
+\hat{\Phi}(\zeta)=\hat{f}(\zeta+\omega)-\hat{f}(\zeta e^{-2\pi i}+\omega)
+\end{equation}
+where with $\hat{f}(\zeta e^{-2\pi i}+\omega)$ is the analytic continuation of $\hat{f}$ along the circular
+path $\omega+\zeta e^{-2\pi i t}$ with $t\in [0,1]$.
+
+\begin{definition}[\cite{Sauzin_notes} Definition 7]
+A simple resurgent function is a resurgent function $c\delta +\hat{f}(\zeta)$ such that, for each $\omega\in\Omega$ and for each path $\gamma$ which starts from the origin $0\in\C_{\zeta}$, lies in $\C\setminus\Omega$ and has its extremity in the disc of radius $\pi$ centred at $\omega$, the branch $\text{cont}_\gamma\hat{f}$ has a simple singularity at $\omega$.
+\end{definition}
+
+\color{orange}
+
+\begin{theorem}\label{thm:frac-diff-borel}
+Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
+for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+\end{theorem}
+
 \color{MidnightBlue}
@@
 where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha + [0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
 \begin{theorem}\label{thm:maxim} Let $N=1$.

### 2022-03-08 exp-resurgence.tex
Only allow base singularities at critical values

@@
 Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
-Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\bar{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
+Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
 A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
 
-Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \bar{X} \to \bar{B}$ that sends punctures to punctures.
-Suppose the critical points of $f$ are all simple.
-For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the singularities of $B$.
+Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ that sends punctures to punctures.
+Suppose every singularity of $B$ is a critical value of $f$.
+\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
+How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
+We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
+These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
 The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-\textbf{[Is $B$ is the Borel plane?
-Can we assume all its singularities are critical values of $f$?]} The {\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
+The {\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
 The {\em thimble integral}
@@
 Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
-\textbf{[How do we get jumps at the critical values?]} Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
+Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
 This data defines the {\em exponential integral}
@@
 a holomorphic function on the right half-plane parameterized by $z$.
-It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points.
-The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
+It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
+\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
 \color{black}

### 2022-03-10 draft2.tex
update computation stokes factors

@@
 
-\begin{remark}
-$\hat{w}_{+}(\zeta)$ is Laplace summable along the positive real axis, and it can be analyticaly continued on $\C\setminus -\frac{4}{3}\R_{\leq 0}$ with (see 15.2.3 DLMF)
-\begin{align*}
-\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
-&=\frac{36}{5}i\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^{n-1} & \\
-&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right)\right) &\\
-&=\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right) &\\
-&=\mathbf{i}\hat{w}_{-}(\zeta+\frac{4}{3}) &
-\end{align*}
-Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
-\begin{align*}
-\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
-&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144}(-4+3\zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right)  &\\
-&=-\mathbf{i}\pi\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
-&=-\mathbf{i}\hat{w}_{+}(\zeta-\frac{4}{3}) &
-\end{align*}
-These relations manifest the resurgence property of $\tilde{I}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.
-\end{remark}
-
 %\begin{remark}
@@
 \textbf{[There should be a way to predict the correct normalization of the RHS.]}
-\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{5}{36}\,\hat{w}_+(\zeta-2/3), \]
+\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,\hat{w}_+(\zeta-2/3), \]
 consistent with Theorem~\ref{thm:maxim}~\eqref{int:deriv-formula}.
@@
 \partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{2}{\sqrt{3}} (\xi' - \xi)^{-1/2} \Big[ \tfrac{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = i \frac{16}{27} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = i \frac{8}{27} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = i \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
 \end{align*}
@@
 \begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{8}{27} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{6} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{6}\,\tfrac{5}{36}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
 \end{align*}
@@
 Analogously, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.
+
+\begin{claim}\label{claim 3}
+
+\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,\hat{w}_-(\zeta+2/3), \]
+consistent with Theorem~\ref{thm:maxim}~\eqref{int:deriv-formula}.
+\end{claim}
+\begin{proof}
+As before, with the substitution $t = -2ux^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_-} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
+where $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression
+\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
+& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\textbf{[Check comparison with Mari\~{n}o's result more carefully?]}
+\end{proof}
+
+In particular, from the previous computations we get the right normalization constants for $\hat{w}_{\pm}(\zeta)$, which allows to compute the Stokes factors from the analytic continuation of $\hat{w}_{\pm}(\zeta)$ at the branch cut: from \cite{DLMF}~15.2.3
+
+\begin{align*}
+\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left[\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)\right]&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left(-\tfrac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\tfrac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\tfrac{3}{4}\zeta)^n\right) &\zeta<-\tfrac{4}{3}\\
+&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i\sum_{n\geq 0}\tfrac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\tfrac{3}{4}\zeta)^{n-1} & \\
+&=-\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i(-\tfrac{3}{4}\zeta-1)^{-1}\left(\tfrac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right)\right)\right) &\\
+&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}i \,\,{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right) &\\
+&=\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right) & \\
+&=\mathbf{+1}\hat{w}_{-}(\zeta+\tfrac{4}{3}) &
+\end{align*}
+Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
+\begin{align*}
+\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left[\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)\right]&=\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left(-\tfrac{36}{5}i(\tfrac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\tfrac{3}{4}\zeta)^n\right) & \zeta>\tfrac{4}{3}\\
+&=-\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i(\tfrac{3}{4}\zeta-1)^{-1}\left(-\tfrac{5}{144}(-4+3\zeta){}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right)\right)  &\\
+&=i\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right) &\\
+&=-\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right) &\\
+&=\mathbf{-1}\hat{w}_{+}(\zeta-\tfrac{4}{3}) &
+\end{align*}
+These relations manifest the resurgence property of $\tilde{I}_{\pm 1}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.
+
+\color{pink}
+\begin{remark}
+$\hat{w}_{+}(\zeta)$ is Laplace summable along the positive real axis, and it can be analyticaly continued on $\C\setminus -\frac{4}{3}\R_{\leq 0}$ with (see 15.2.3 DLMF)
+\begin{align*}
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
+&=\frac{36}{5}i\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^{n-1} & \\
+&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right)\right) &\\
+&=\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right) &\\
+&=\mathbf{i}\hat{w}_{-}(\zeta+\frac{4}{3}) &
+\end{align*}
+Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
+\begin{align*}
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
+&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144}(-4+3\zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right)  &\\
+&=-\mathbf{i}\pi\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
+&=-\mathbf{i}\hat{w}_{+}(\zeta-\frac{4}{3}) &
+\end{align*}
+These relations manifest the resurgence property of $\tilde{I}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.
+\end{remark}
+
+\color{black}
 \end{example}
@@
 \begin{align}
-\label{w+}&\hat{w}_+(\zeta)={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
-\label{w+}&\hat{w}_-(\zeta)={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
+\label{w+}&\hat{w}_+(\zeta)=c_1\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
+\label{w+}&\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
 \end{align}
-In particular, we notice that taking the series expansion of $\hat{w}_+$ and $\hat{w}_-$ we get numerically that
-\begin{align*}
-\hat{w}_+(\zeta-4)=\frac{1}{\pi}\log(z)\hat{w}_-(z)+\phi_{\text{reg}}\\
-\hat{w}_-(\zeta+4)=\frac{1}{\pi}\log(z)\hat{w}_+(z)+\psi_{\text{reg}}
-\end{align*}
-and analytically (thanks to 15.2.3 DLMF)
-\begin{align*}
-\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}+i0\right)-{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}-i0\right) &\qquad\zeta<-4\\
-&=-8i\left(-\frac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}+1\right)^n\\
-&=8i\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}+1\right)^{n-1} & \\
-&=8i\sum_{n\geq 0}\frac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(\frac{\zeta}{4}+1\right)^{n} &\\
-&=\mathbf{2i}\sum_{n\geq 0}\frac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(\frac{\zeta}{4}+1\right)^{n} & \\
-&=\mathbf{2i}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}+1\right)
-\end{align*}
-\begin{align*}
-\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&={}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}+i0\right)-{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}-i0\right)& \qquad\zeta>4\\
-&=8i\left(\frac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\frac{\zeta}{4}-1\right)^n\\
-&=-8i\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(1-\frac{\zeta}{4}\right)^{n-1}\\
-&=-8i\sum_{n\geq 0}(-1)^n\frac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(1-\frac{\zeta}{4}\right)^{n}\\
-&=\mathbf{-2i}\sum_{n\geq 0}(-1)^n\frac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(1-\frac{\zeta}{4}\right)^{n}\\
-&=\mathbf{-2i}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;1-\frac{\zeta}{4}\right)
-\end{align*}
-These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.
-\textbf{Hopefully, the latter identities show that the Stokes constants can be computed via Alien calculus and they are equal to $\pm 2$.
-}
 
@@
 
-We can now write $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 14.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta-1\right)=\frac{1}{2}\left(\cosh(\theta)-1\right)=\sinh^2\left(\frac{\theta}{2}\right)$, then
+We can now write $\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 14.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta-1\right)=\frac{1}{2}\left(\cosh(\theta)-1\right)=-\sinh^2\left(\frac{\theta}{2}\right)$, then
 
@@
 \sinh\left(\frac{\theta}{2}\right)\,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\sinh^2\left(\frac{\theta}{2}\right)\right)&=i\frac{\theta}{2} \\
-\xi^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi\right)&=i\frac{\theta}{2}\\
- &=\frac{i}{2}\left(\frac{1}{2}\mathrm{arcosh}\left(\frac{\zeta}{2}\right)\right)\\
+(-\xi)^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi\right)&=i\frac{\theta}{2}\\
+ &=\frac{i}{2}\mathrm{arcosh}\left(\frac{\zeta}{2}\right)\\
  &=\frac{i}{4}\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)
@@
 \partial_{\zeta}^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_2^\zeta (\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)d\zeta'\\
-&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)\xi'^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi'\right) 4d\xi'\\
-&=-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)
-\end{align*}
-
-\begin{align*}
-\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \\
-&=\frac{1}{16}\partial_\xi^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
-&=+\frac{i}{2}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,-\xi\right)\right) & \textbf{DLMF} 15.5.4\\
-&=-\frac{i}{8}\Gamma\left(\frac{3}{2}\right){}_2F_1\left(\frac{3}{2},\frac{3}{2};2,-\xi\right) & \\
-&=-\frac{i\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}-\frac{\zeta}{4}\right) & \\
-&=-\frac{i\sqrt{\pi}}{16} \hat{w}_+(\zeta-2) &
-\end{align*}
-
-%Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$.  
+&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)(-\xi')^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};-\xi'\right) 4d\xi'\\
+&=-8i (i)\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\\
+&=4\sqrt{\pi} \xi \,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)
+\end{align*}
+
+\begin{align*}
+\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(4\sqrt{\pi}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \\
+&=\frac{1}{16}\partial_\xi^2\left(4\sqrt{\pi}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,-\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
+&=-\frac{\sqrt{\pi}}{4}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,-\xi\right)\right) & \textbf{DLMF} 15.5.4\\
+&=\frac{\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,-\xi\right) & \\
+&=\frac{\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}-\frac{\zeta}{4}\right) & \\
+\end{align*}
+
+Analougusly, it can be verified for $\hat{w}_-(\zeta+2)$ for $\zeta\in(-\infty,-2)$. The path $\mathcal{C}_\pi$ is parametrized as  
+\begin{align*}
+\mathcal{C}_\pi\colon\R &\to \C_\zeta \\
+\theta & \to 2\cosh(\theta-i\pi)=-2\cosh(\theta)
+\end{align*}
+
+\begin{equation}
+\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)=\int_{\mathcal{C}_\pi(\zeta)}du=\Big[ u\Big]^{\mathrm{end}\mathcal{C}_\pi(\zeta)}_{\mathrm{start}\mathcal{C}_\pi(\zeta)}=2\mathrm{arc}\cosh\left(-\frac{\zeta}{2}\right)
+\end{equation}
+
+We can now write $\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)$ as an hypergeometric function thanks to identity 15.4.4 \cite{DLMF}: set $\xi=\frac{1}{2}\left(\frac{1}{2}\zeta+1\right)=\frac{1}{2}\left(-\cosh(\theta)+1\right)=\sinh^2\left(\frac{\theta}{2}\right)$, then
+
+\begin{align*}
+\sinh\left(\frac{\theta}{2}\right)\,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\sinh^2\left(\frac{\theta}{2}\right)\right)&=i\frac{\theta}{2} \\
+(\xi)^{1/2}{}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\xi\right)&=i\frac{\theta}{2}\\
+ &=\frac{i}{2}\mathrm{arcosh}\left(-\frac{\zeta}{2}\right)\\
+ &=\frac{i}{4}\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)
+\end{align*}
+
+The $3/2$-derivative of $\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)$ is computed in two steps: first we compute the $-1/2$-derivatve and then we differentiate twice
+
+\begin{align*}
+\partial_{\zeta}^{-1/2}\left(\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)\right)&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_{-2}^\zeta (\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)\right)d\zeta'\\
+&=\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^{\xi}\frac{1}{2}(\xi-\xi')^{-1/2}(-4i)\xi'^{1/2} {}_2F_1\left(\frac{1}{2},\frac{1}{2};\frac{3}{2};\xi'\right) 4d\xi'\\
+&=-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,\xi\right)
+\end{align*}
+
+\begin{align*}
+\partial_\zeta^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,\xi\right)\right) & \\
+&=\frac{1}{16}\partial_\xi^2\left(-8i\frac{\Gamma\left(\frac{3}{2}\right)}{\Gamma(2)}\xi \,\,{}_2F_1\left(\frac{1}{2},\frac{1}{2};2,\xi\right)\right) & \partial_\xi=4\partial_\zeta\\
+&=-\frac{i}{2}\Gamma\left(\frac{3}{2}\right)\partial_\xi\left({}_2F_1\left(\frac{1}{2},\frac{1}{2};1,\xi\right)\right) & \textbf{DLMF} 15.5.4\\
+&=-\frac{i}{8}\Gamma\left(\frac{3}{2}\right){}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\xi\right) & \\
+&=-\frac{i\sqrt{\pi}}{16}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2,\frac{1}{2}+\frac{\zeta}{4}\right) & 
+\end{align*}
+
+Once we have determined the right constants $c_1,c_2$ we can compute the Stokes constants. 
+\color{blue}
+First, we notice that taking the series expansion of $\hat{w}_+$ and $\hat{w}_-$ at the critical point we get numerically that
+\begin{align*}
+\hat{w}_+(\zeta-4)=\frac{1}{\pi}\log(z)\hat{w}_-(z)+\phi_{\text{reg}}\\
+\hat{w}_-(\zeta+4)=\frac{1}{\pi}\log(z)\hat{w}_+(z)+\psi_{\text{reg}}
+\end{align*}
+and analytically (thanks to ~15.2.3 DLMF)
+
+\color{black}
+
+Let us redefine $\hat{w}_{+}(\zeta)\defeq -i\tfrac{\sqrt{\pi}}{16} {}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;\tfrac{1}{2}-\tfrac{\zeta}{4}\right)$ and $\hat{w}_-(\zeta)\defeq\tfrac{\sqrt{\pi}}{16} {}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;\tfrac{\zeta}{4}+\tfrac{1}{2}\right)$.
+From equation ~15.2.3 in \cite{DLMF}
+\begin{align*}
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=\textcolor{red}{-\tfrac{i\sqrt{\pi}}{16}}\left({}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;-\tfrac{\zeta}{4}+i0\right)-{}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;-\tfrac{\zeta}{4}-i0\right)\right) &\qquad\zeta<-4\\
+&=-8i\textcolor{red}{\left(\tfrac{\sqrt{\pi}}{16}\right)}\left(-\tfrac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\tfrac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\tfrac{\zeta}{4}+1\right)^n\\
+&=8i\textcolor{red}{\left(\tfrac{\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}\frac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\tfrac{\zeta}{4}+1\right)^{n-1} & \\
+&=8i\textcolor{red}{\left(\tfrac{\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}\tfrac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(\tfrac{\zeta}{4}+1\right)^{n} &\\
+&={2i}\textcolor{red}{\left(\tfrac{\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}\tfrac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(\tfrac{\zeta}{4}+1\right)^{n} & \\
+&=\mathbf{-2}\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}{}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;\tfrac{\zeta}{4}+1\right)\\
+&=\mathbf{-2}\hat{w}_-(\zeta+2)
+\end{align*}
+\begin{align*}
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}\left[{}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;\tfrac{\zeta}{4}+i0\right)-{}_2F_1\left(\tfrac{3}{2},\tfrac{3}{2};2;\tfrac{\zeta}{4}-i0\right)\right]& \qquad\zeta>4\\
+&=-8i\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}\left(\tfrac{\zeta}{4}-1\right)^{-1}\sum_{n\geq 0}\tfrac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(\tfrac{\zeta}{4}-1\right)^n\\
+&=8i\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}\tfrac{(1/2)_n(1/2)_n}{n!\Gamma(n)}\left(1-\tfrac{\zeta}{4}\right)^{n-1}\\
+&=8i\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}(-1)^n\frac{(1/2)_{n+1}(1/2)_{n+1}}{(n+1)!\Gamma(n+1)}\left(1-\tfrac{\zeta}{4}\right)^{n}\\
+&=2i\textcolor{red}{\left(-\tfrac{i\sqrt{\pi}}{16}\right)}\sum_{n\geq 0}(-1)^n\tfrac{(3/2)_{n}(3/2)_{n}}{(n)!\Gamma(n+2)}\left(1-\tfrac{\zeta}{4}\right)^{n}\\
+&=\mathbf{+2}\textcolor{red}{\left(\tfrac{\sqrt{\pi}}{16}\right)}{}_2F_1\left(\frac{3}{2},\frac{3}{2};2;1-\frac{\zeta}{4}\right)\\
+&=\mathbf{+2}\hat{w}_+(\zeta-2)
+\end{align*}
+These are evidence of the resurgent properties of $\tilde{I}_{\pm 1}(z)$.
+\textbf{With the correct normalization, the latter identities show that the Stokes constants can be computed via Alien calculus and they are equal to $\pm 2$.
+}
 \end{example}
@@
 
-hence \[\hat{w}_+(\zeta)={}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right)\] and analougusly, \[\hat{w}_-(\zeta)={}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right).\] Notice that $\hat{w}_{\pm}(\zeta)$ has a branch cut singularity respectively at $\zeta=\zeta_{\pm}\defeq\pm \sqrt{\frac{16p^3}{27a_1}}$, and thanks to the well known formulas for the analytic continuation of hypergeometric functions (see 15.2.3 DLMF), if we assume the branch cut is from $\zeta_{\pm}$ to $+\infty$
-
-\begin{align*}
-\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_+}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \zeta\in\left(\zeta_+,+\infty\right) & \\
-&=-\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^{k-1} & \\
-&=\mathbf{-i}\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \\
-&=\mathbf{-i}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_+}\right) & \\
-&=\mathbf{-i}\hat{w}_+(\zeta-\zeta_+)
-\end{align*}
-
-Similarly, if we assume that the branch cut is from $\zeta_{\pm}$ to $-\infty$ then
-
-\begin{align*}
-\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_-}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \zeta\in\left(-\infty,\zeta_-\right) & \\
-&=\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^{k-1} & \\
-&=\mathbf{i}\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \\
-&=\mathbf{i}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_-}\right) & \\
-&=\mathbf{i}\hat{w}_-(\zeta-\zeta_-)
+hence \[\hat{w}_+(\zeta)=c_1 \,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right)\] and analougusly, \[\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{3}{4p}\sqrt{\frac{3a_1}{p}}\zeta\right).\] Notice that $\hat{w}_{\pm}(\zeta)$ has a branch cut singularity respectively at $\zeta=\zeta_{\pm}\defeq\pm \sqrt{\frac{16p^3}{27a_1}}$, and thanks to the well known formulas for the analytic continuation of hypergeometric functions (see 15.2.3 DLMF), if we assume the branch cut is from $\zeta_{\pm}$ to $+\infty$
+
+\begin{align*}
+\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=c_2 \frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_+}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \zeta\in\left(\zeta_+,+\infty\right) & \\
+&=-c_2\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_+}\right)^{k-1} & \\
+&={-i}c_2\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_+}\right)^k & \\
+&={-i}c_2 \,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_+}\right) & \\
+&={-i}\frac{c_2}{c_1}\hat{w}_+(\zeta-\zeta_+)
+\end{align*}
+
+Similarly,
+
+\begin{align*}
+\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=c_1\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)}\left(\frac{\zeta}{\zeta_-}-1\right)^{-1}\sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \zeta\in\left(-\infty,\zeta_-\right) & \\
+&=-c_1\frac{2\pi i}{\Gamma(7/6)\Gamma(11/6)} \sum_{k\geq 0}\frac{(5/6)_k(1/6)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{\zeta_-}\right)^{k-1} & \\
+&=-ic_1\frac{1}{\Gamma(7/6)\Gamma(11/6)}\sum_{k\geq 0}\frac{\Gamma\left(\tfrac{7}{6}+k\right)\Gamma\left(\tfrac{11}{6}+k\right)}{\Gamma(2+k)\Gamma(k+1)}\left(1-\frac{\zeta}{\zeta_-}\right)^k & \\
+&=-ic_1\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;1-\frac{\zeta}{\zeta_-}\right) & \\
+&=-i\frac{c_1}{c_2}\hat{w}_-(\zeta-\zeta_-)
 \end{align*}

### 2022-03-10 modified bessel.tex
Add stokes factor computations

@@
 \begin{equation}
-\hat{w}_{\mu,+}(\zeta)={}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\frac{\zeta}{2}\right)
+\hat{w}_{\mu,+}(\zeta)=c_{\mu,+} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\frac{\zeta}{2}\right)
 \end{equation}
@@
 \begin{equation}
-\hat{w}_{\mu,-}(\zeta)={}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{\zeta}{2}\right)
+\hat{w}_{\mu,-}(\zeta)=c_{\mu,-} {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{\zeta}{2}\right)
 \end{equation} 
-and it has branch point at $\zeta=2$. Thanks to explicit formula for the analytic continuation of hypergeomtric functions (see \cite{dlmf} 15.2.3)
-\begin{align*}
-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\left(\hat{w}_{\mu,+}(\zeta+i0)-\hat{w}_{\mu,+}(\zeta-i0)\right)&=\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\left(-\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}+\mu,\frac{1}{2}-\mu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
-&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot\\
-& \qquad\cdot \sum_{k\geq 1}\frac{\Gamma\left(\tfrac{1}{2}-\mu+k\right)\Gamma\left(\tfrac{1}{2}+\mu+k\right)}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
-&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot \\
-&\qquad\cdot \sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\mu+k\right)\Gamma\left(\tfrac{3}{2}+\mu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
-&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}}\frac{2\pi i}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1+\frac{\zeta}{2}\right) & \\
-&=-2i\textcolor{red}{\sqrt{\pi}}\hat{w}_{\mu,-}(\zeta+2)
-\end{align*} 
-and for $\hat{w}_{\mu,-}(\zeta)$
-\begin{align*}
-\hat{w}_{\mu,-}(\zeta+i0)-\hat{w}_{\mu,-}(\zeta-i0)&=-\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\left(\frac{\zeta}{2}-1\right)^{-1}{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;0;1-\frac{\zeta}{2}\right) & \zeta<2 \\
-&=\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{2}\right)^{k-1} & \\
-&=2i\cos(\nu \pi)\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1-\frac{\zeta}{2}\right) & \\
-&=2i\cos(\mu \pi)\hat{w}_{\mu,+}(\zeta-2)
-\end{align*}
-In addition, the previous relations computes the Stokes constants which are funtions of $\nu$ and are given by $\pm 2i\cos(\mu\pi)$.
+and it has branch point at $\zeta=2$.
 
@@
 where $K_\mu(z)$ is the second kind modified Bessel function with parameter $\mu$.
+
+\textbf{Add definition of $\tilde{I}_{\pm}$}
+
 It is worth mentioning that $I(z;\mu)$ differs from $I(z;0)$ only in $\pi^*(\nu)$ while $\pi^*(f)$ stays the same for every $\mu\in [0,\infty)$.
-Hence we can adapt part of the argument used in Bessel example (see ), and verify the $3/2$-derivative formula: let $\zeta=\cosh(u)$
+Hence we can adapt part of the argument used in Bessel example (see ), and apply the $3/2$-derivative formula: let $\zeta=\cosh(u)$
 
@@
 \partial_{\zeta}^{3/2}\left(\int_{\mathcal{C}_0(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_1^\zeta(\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_0(\zeta')}\pi^*(\nu)\right)d\zeta'\right)\\
-&=4\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^\xi\frac{1}{2}(\xi-\xi')^{-1/2}\xi^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\xi'\right) 4\,\,d\xi'\right)\\
-&=8\partial_\zeta^2\left(\Gamma\left(\frac{3}{2}\right)\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right) \\
-&=4\sqrt{\pi}\frac{1}{4}\partial_\xi^2\left(\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right)\\
-&=-\sqrt{\pi}\partial_{\xi}\,\, {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;1;-\xi\right)\\
-&=\sqrt{\pi}\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right){}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\xi\right)\\
-&=\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}{}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{1}{2}-\frac{\zeta}{2}\right)\\
-&=\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}\hat{w}_{\mu,+}(\zeta-1)
+&=4\partial_\zeta^2\left[\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^\xi\frac{1}{\sqrt{2}}(\xi-\xi')^{-1/2}(\xi')^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\xi'\right) 2\,\,d\xi'\right]\\
+&=\frac{8}{\sqrt{2}}\partial_\zeta^2\left[\Gamma\left(\frac{3}{2}\right)\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right] \\
+&=\frac{8}{\sqrt{2}}\frac{\sqrt{\pi}}{2}\frac{1}{4}\partial_\xi^2\left[\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;-\xi\right)\right]\\
+&=-\frac{\sqrt{\pi}}{\sqrt{2}}\partial_{\xi}\,\, {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;1;-\xi\right)\\
+&=\frac{\sqrt{\pi}}{\sqrt{2}}\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right){}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;-\xi\right)\\
+&=\frac{\sqrt{\pi}}{\sqrt{2}}\frac{\pi}{\cos(\mu \pi)}{}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{1}{2}-\frac{\zeta}{2}\right)
 \end{align*}
+
+Let us now consider the integral whose asymptotic behvaior is given in terms of $\hat{w}_{\mu,-}(z)$:
+
+\textbf{I have to check the correct form of the integral I which correspond to the path $C_\pi$. I suspect a scaling factor of $\cos(\pi \mu)$ that will adjust the Stokes factor computations.}
+
+set $\zeta=-\cosh(u)$,
+
+\begin{align*}
+\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)&=\int_{\mathcal{C}_\pi(\zeta)}\cosh(\mu u)du\\
+&=\frac{1}{\mu}\Big[\sinh(\mu u)\Big]_{\mathrm{start}\mathcal{C}_\pi(\zeta)}^{\mathrm{end}\mathcal{C}_\pi(\zeta)}\\
+&=\frac{1}{\mu}\left(\sinh\left(\mu\,\mathrm{acosh}\left(-\zeta\right)\right)-\sinh\left(-\mu\,\mathrm{acosh}\left(-\zeta\right)\right)\right)\\
+&=\frac{2}{\mu}\sinh\left(\mu\,\mathrm{acosh}\left(-\zeta\right)\right)
+\end{align*}
+
+The we set $\xi=\frac{1}{2}\left(\zeta+1\right)$, thanks to identity 15.4.16 \textbf{DLMF}
+
+\begin{align*}
+\sinh(\tau) {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};-\sinh^2(\tau)\right)&=\frac{1}{2\mu}\sinh(2\mu\tau) & \\
+(-\xi)^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};\xi\right)&=\frac{1}{2\mu}\sinh(2\mu\tau)  & \sinh^2(\tau)=-\xi \\
+(-\xi)^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};\xi\right)&=\frac{1}{2\mu}\sinh(\mu\,\,\mathrm{acosh}\left(-\zeta\right))  & \cosh(2\tau)=-\zeta \\
+&=\frac{1}{4}\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu) &\\
+\end{align*}
+
+Thus we take $3/2$-derivative based at $\zeta=-1$
+
+\begin{align*}
+\partial_{\zeta}^{3/2}\left(\int_{\mathcal{C}_\pi(\zeta)}\pi^*(\nu)\right)&=\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_{-1}^\zeta(\zeta-\zeta')^{-1/2}\left(\int_{\mathcal{C}_\pi(\zeta')}\pi^*(\nu)\right)d\zeta'\right)\\
+&=4\partial_\zeta^2\left(\frac{1}{\Gamma\left(\frac{1}{2}\right)}\int_0^\xi\frac{1}{\sqrt{2}}(\xi-\xi')^{-1/2}(-\xi')^{1/2} {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;\frac{3}{2};\xi'\right) 2\,\,d\xi'\right)\\
+&=-i\frac{8}{\sqrt{2}}\partial_\zeta^2\left(\Gamma\left(\tfrac{3}{2}\right)(-\xi) \,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;\xi\right)\right) \\
+&=i\frac{8}{\sqrt{2}}\frac{\sqrt{\pi}}{2}\frac{1}{4}\partial_\xi^2\left(\xi\,\,{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;2;\xi\right)\right)\\
+&=i\frac{\sqrt{\pi}}{\sqrt{2}}\partial_{\xi}\,\, {}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;1;\xi\right)\\
+&=i\frac{\sqrt{\pi}}{\sqrt{2}}\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right){}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\xi\right)\\
+&=i\frac{\sqrt{\pi}}{\sqrt{2}}\frac{\pi}{\cos(\mu \pi)}{}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;\frac{1}{2}-\frac{\zeta}{2}\right)
+\end{align*}
+
+\color{black}
+
+\subsection{Stokes factors}
+
+Thanks to explicit formula for the analytic continuation of hypergeomtric functions (see \cite{dlmf} 15.2.3) and using the constants prescribed by the fractional derivative formula we are able ot compute the Stokes constants: set $\hat{w}_{+,\mu}(\zeta)=\textcolor{red}{\frac{\pi\sqrt{\pi}}{\cos(\mu \pi)}} {}_2F_1\left(\tfrac{3}{2}-\mu,\tfrac{3}{2}-\mu;2,1-\tfrac{\zeta}{2}\right)$ and $\hat{w}_{-,\mu}(\zeta)\defeq \textcolor{red}{i\tfrac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}} {}_2F_1\left(\tfrac{3}{2}-\mu,\tfrac{3}{2}-\mu;2,1+\tfrac{\zeta}{2}\right)$
+
+\begin{align*}
+\hat{w}_{\mu,+}(\zeta+i0)-\hat{w}_{\mu,+}(\zeta-i0)&=\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\big(-\frac{\zeta}{2}-1\big)^{-1}{}_2F_1\left(\frac{1}{2}+\mu,\frac{1}{2}-\mu;0;1+\frac{\zeta}{2}\right) & \zeta>-2 \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 1}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot\\
+& \qquad\cdot \sum_{k\geq 1}\frac{\Gamma\left(\tfrac{1}{2}-\mu+k\right)\Gamma\left(\tfrac{1}{2}+\mu+k\right)}{\Gamma(k)k!}\left(1+\frac{\zeta}{2}\right)^{k-1} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\frac{1}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\cdot \\
+&\qquad\cdot \sum_{k\geq 0}\frac{\Gamma\left(\tfrac{3}{2}-\mu+k\right)\Gamma\left(\tfrac{3}{2}+\mu+k\right)}{\Gamma(k+1)(k+1)!}\left(1+\frac{\zeta}{2}\right)^{k} & \\
+&=-\textcolor{red}{\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma\left(\frac{1}{2}-\mu\right)\Gamma\left(\frac{1}{2}+\mu\right)}\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1+\frac{\zeta}{2}\right) & \\
+&=-2\pi i\textcolor{red}{\frac{\sqrt{\pi}}{2}}\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1+\frac{\zeta}{2}\right)\\
+&=\mathbf{-2}\cos(\pi\mu)\hat{w}_{-,\mu}(\zeta+2)
+\end{align*} 
+and for $\hat{w}_{\mu,-}(\zeta)$
+\begin{align*}
+\hat{w}_{\mu,-}(\zeta+i0)-\hat{w}_{\mu,-}(\zeta-i0)&=\textcolor{red}{i\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\big(\frac{\zeta}{2}-1\big)^{-1}{}_2F_1\left(\frac{1}{2}-\mu,\frac{1}{2}+\mu;0;1-\frac{\zeta}{2}\right) & \zeta<2 \\
+&=-\textcolor{red}{i\frac{\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\frac{2\pi i}{\Gamma(\tfrac{3}{2}-\mu)\Gamma(\tfrac{3}{2}+\mu)}\sum_{k\geq 0}\frac{\left(\tfrac{1}{2}-\mu\right)_k\left(\tfrac{1}{2}+\mu\right)_k}{\Gamma(k)k!}\left(1-\frac{\zeta}{2}\right)^{k-1} & \\
+&=-2i\cos(\mu \pi)\,\textcolor{red}{\frac{i\pi\sqrt{\pi}}{\sqrt{2}\cos(\mu \pi)}}\,\, {}_2F_1\left(\frac{3}{2}-\mu,\frac{3}{2}+\mu;2;1-\frac{\zeta}{2}\right) & \\
+&=\mathbf{+2}\cos(\mu \pi)\hat{w}_{\mu,+}(\zeta-2)
+\end{align*}
+
+Therefore we have shown that Stokes constants are independent on $\mu$ and equal to $\pm 2$.
 

### 2022-03-11 modified bessel.tex

@@
 \end{align*} 
-In particular, $\tilde{K}_{\mu}(z)=\sqrt{\frac{\pi}{2}}e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)$ and $\tilde{I}_\mu(z)=\frac{1}{\sqrt{2\pi}}e^zz^{-1/2}\tilde{w}_{\mu,-}(z)$ (once we choose $a_{\pm,0}=1$).
+In particular, $\tilde{K}_{\mu}(z)=\sqrt{\frac{\pi}{2}}U_1e^{-z}z^{-1/2}\tilde{w}_{\mu,+}(z)$ and $\tilde{I}_\mu(z)=\frac{1}{\sqrt{2\pi}}U_2 e^zz^{-1/2}\tilde{w}_{\mu,-}(z)$ (we assume $a_{\pm,0}=1$) for some constants $U_1, U_2$.
 We now compute the Borel transform of $\tilde{w}_+(z)$\footnote{We do not consider constant term of $\tilde{w}_{\mu,\pm}$, i.e.
-$\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.} it is a solution of
+$\mathcal{B}:\C[\![z^{-1}]\!]\to \C[\zeta]$.}: it is a solution of
 \begin{align*}
@@
 \begin{equation}
-I(\frac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
+I(\tfrac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
 \end{equation} 
@@
 
-\textbf{Add definition of $\tilde{I}_{\pm}$}
+The critical points of $\pi^* f$ are at $u=k i \pi$, for $k\in\Z$ and we denote $\tilde{I}_{1}(z;\mu)$ the asymptotic expansion of $I(\tfrac{z}{2};\mu)$ at $u=0$ and $\tilde{I}_{-1}(z;\mu)$ the expansion at $u=i \pi$.
+They are respectively multiple of $\tilde{K}_{\mu}$ and $\tilde{I}_{\mu}$, because they solve \eqref{Bessel_nu} and they have the same leading order asymptotic of $\tilde{K}_{\mu}, \tilde{I}_{\mu}$ which are a basis.
 
-It is worth mentioning that $I(z;\mu)$ differs from $I(z;0)$ only in $\pi^*(\nu)$ while $\pi^*(f)$ stays the same for every $\mu\in [0,\infty)$.
-Hence we can adapt part of the argument used in Bessel example (see ), and apply the $3/2$-derivative formula: let $\zeta=\cosh(u)$
+Notice that $I(z;\mu)$ differs from $I(z;0)$ only in $\pi^*(\nu)$ while $\pi^*(f)$ stays the same for every $\mu\in [0,\infty)$.
+Hence we can adapt part of the argument used in Bessel example (see ), and apply the $3/2$-derivative formula: let $\zeta=\cosh(u)$ and $\mathcal{C}_0(\zeta)\colon\theta\in\R\to\cosh(\theta)\in\C_\zeta$
 

### 2022-03-21 draft2.tex
updates

@@
 
+However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin: indeed 
+\begin{align*}
+\mathcal{B}(z^{\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
+\end{align*}
+
+In particular, if $\alpha\in (1,+\infty)$, then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
+^{\alpha-1}$, otherwise if $\alpha\in (-\infty,1)$ then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is a meromorphic functions on the Riemann surface where $\zeta^{\alpha-1}$ defines an analytic coordinate.
+The case of interest for usa in the following is when $\alpha=\tfrac{1}{2}$, hence if $a_0\neq 0$, the Borel trasform will be merorphic at the origin and definied on the Riemann surface of the square root.
+
 \subsubsection{Properties of the Borel transform}
@@
 \begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R\setminus\Z_{\leq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
 \item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^nf(z))=\partial_\zeta^n\hat{f}(\zeta)$ 
@@
 \item[(v)] $\mathcal{B}(f(z-c))=e^{-c\zeta}\hat{f}(\zeta)$
-\item[(vi)] if $g(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(f(z)g(z))=\int_0^{\zeta}d\zeta \hat{f}(\zeta-\zeta')\hat{g}(\zeta')=:\hat{f}\ast \hat{g}$, where $\hat{g}(\zeta)=\mathcal{B}(g(z))$.
+\item[(vi)] if $g(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(f(z)g(z))=\int_0^{\zeta}d\zeta' \hat{f}(\zeta-\zeta')\hat{g}(\zeta')=:\hat{f}\ast \hat{g}$, where $\hat{g}(\zeta)=\mathcal{B}(g(z))$.
 \end{itemize}
@@
 
-\color{orange}
-
-\begin{theorem}\label{thm:frac-diff-borel}
-Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
-for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-\end{theorem}
-
-\color{MidnightBlue}
-\begin{definition}
-Let $\alpha\in (0,1)$ and $n\in\N$, then the $n+\alpha$-Caputo's derivative of a smooth fucntion $f$ is defined as
-\begin{equation}
-\partial_x^{n+\alpha}f(x)\defeq\frac{1}{\Gamma(1-\alpha)}\int_0^x(x-s)^{-\alpha}f^{(n+1)}(s)ds
-\end{equation}
-\end{definition}
-
-In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$.
+%\color{orange}
+%
+%
+%\begin{theorem}\label{thm:frac-diff-borel}
+%Given a Gevrey-$1$ formal series $\varphi(z) = \sum_{k \ge 0}a_kz^{-(k+1)}$, we have
+%\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \varphi \right](\zeta) = \left[ \borel z^\mu \varphi \right](\zeta) \]
+%for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+%\end{theorem}
+
+%\color{MidnightBlue}
+%\begin{definition}
+%Let $\alpha\in (0,1)$ and $n\in\N$, then the $n+\alpha$-Caputo's derivative of a smooth fucntion $f$ is defined as
+%\begin{equation}
+%\partial_x^{n+\alpha}f(x)\defeq\frac{1}{\Gamma(1-\alpha)}\int_0^x(x-s)^{-\alpha}f^{(n+1)}(s)ds
+%\end{equation}
+%\end{definition}
+%
+%In particular, this definition is well suited for the differential calculus in the convolutive model $\left(\C[\![\zeta]\!], \ast\right)$.
 Let $\varphi(z)\defeq\sum_{k\geq 0}a_kz^{-k-1}\in\C[\![z^{-1}]\!]$ be Gevrey $1$, then assuming $a_k=0$ for every $k<n$, the Borel transform of $z^{n+\alpha}\varphi(z)$ can be computed in two different ways: \textbf{[Can we do this when $\varphi$ isn't in $o(z^n)$?]}
-\begin{multline}
-\label{mod1}
-\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}(z^{\alpha+n})\ast\hat{\varphi}(\zeta)=\int_0^{\zeta}\frac{(\zeta-s)^{-1-n-\alpha}}{(-1-n-\alpha)!}\sum_{k\geq 0}\frac{a_k}{k!}s^{k}ds\\
-=\frac{1}{(-\alpha)!}\int_0^{\zeta}(\zeta-s)^{-\alpha}\sum_{k\geq 0}\frac{a_k}{(k-n-1)!}s^{k-n-1}ds=\partial_{\zeta}^{n+\alpha}\hat{\varphi}(\zeta)
-\end{multline}
-\begin{equation}
-\label{mod2}
-\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}\left(\sum_{k\geq 0}a_kz^{-k-1+n+\alpha}\right)(\zeta)=\sum_{k>n}\frac{a_k}{(k-n-\alpha)!}\zeta^{k-n-\alpha}
-\end{equation}
-
-and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
+%\begin{multline}
+%\label{mod1}
+%\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}(z^{\alpha+n})\ast\hat{\varphi}(\zeta)=\int_0^{\zeta}\frac{(\zeta-s)^{-1-n-\alpha}}{(-1-n-\alpha)!}\sum_{k\geq 0}\frac{a_k}{k!}s^{k}ds\\
+%=\frac{1}{(-\alpha)!}\int_0^{\zeta}(\zeta-s)^{-\alpha}\sum_{k\geq 0}\frac{a_k}{(k-n-1)!}s^{k-n-1}ds=\partial_{\zeta}^{n+\alpha}\hat{\varphi}(\zeta)
+%\end{multline}
+%\begin{equation}
+%\label{mod2}
+%\mathcal{B}\left(z^{n+\alpha}\varphi(z)\right)(\zeta)=\mathcal{B}\left(\sum_{k\geq 0}a_kz^{-k-1+n+\alpha}\right)(\zeta)=\sum_{k>n}\frac{a_k}{(k-n-\alpha)!}\zeta^{k-n-\alpha}
+%\end{equation}
+%
+%and computitng the integral which defines the $n+\alpha$-derivative in \eqref{mod1} we get exaclty the same result as \eqref{mod2}.
 \color{black}
@@
 \begin{align*}
-{C}_p\colon \R & \to \tilde{\C} \\
+\mathcal{C}_p\colon \R & \to \tilde{\C} \\
 \theta & \to \theta+i p
@@
 \begin{align*}
-\mathcal{C}_0\colon\R &\to \C_\zeta \\
+\mathcal{C}_0(\zeta)\colon\R &\to \C_\zeta \\
 \theta & \to 2\cosh(\theta)

### 2022-03-21 draft2.tex
Edit section on Puiseux series property

@@
 
-However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin: indeed 
-\begin{align*}
-\mathcal{B}(z^{\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-In particular, if $\alpha\in (1,+\infty)$, then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
-^{\alpha-1}$, otherwise if $\alpha\in (-\infty,1)$ then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is a meromorphic functions on the Riemann surface where $\zeta^{\alpha-1}$ defines an analytic coordinate.
-The case of interest for usa in the following is when $\alpha=\tfrac{1}{2}$, hence if $a_0\neq 0$, the Borel trasform will be merorphic at the origin and definied on the Riemann surface of the square root.
-
+However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, and $\alpha$ is a rational number with denominator $q$, then $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin of the Riemann surface of $\zeta^{1/q}$.
+Indeed,
+\begin{align*}
+\mathcal{B}(z^{-\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}.
+\end{align*}
+If $\alpha > 1$, then $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
+^{1/q}$. We're interested in the case where $\alpha=\tfrac{1}{2}$, so the Borel transform is meromorphic on the Riemann surface of $\zeta^{1/2}$, and has a pole at $\zeta = 0$ unless $a_0 = 0$.
 \subsubsection{Properties of the Borel transform}

### 2022-03-24 airy-resurgence.tex
Write about shifting integro-differential equations
Present the simple formula for the Laplace transform of an integral
operator instead of the tricky formula for the Laplace transform of
a differential operator. Start rewriting Borel regularity argument
with integral equations in the frequency domain.

@@
 \usepackage{amssymb}
-%%\usepackage{amsthm}
+\usepackage{amsthm}
 \usepackage{graphicx}
+\usepackage{xcolor} %% for revisions
 
@@
 %%\newtheorem{defn}{Definition}
-%%\theoremstyle{plain}
-%%\newtheorem{prop}{Proposition}
+\theoremstyle{plain}
+\newtheorem{prop}{Proposition}
 
@@
 \newcommand{\laplace}{\mathcal{L}}
+\newcommand{\series}[1]{\tilde{#1}}
+\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
 \DeclareMathOperator{\Ai}{Ai}
@@
 For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
-\subsubsection{Action on differential operators}\label{L-diff-op}
-When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\subsubsection{Action on differential and integral operators}\label{L-diff-op}
+When $\hat{\varphi} \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}\label{id:L-mult}
@@
 \end{equation}
+for all integers $n \ge 0$.
+You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} = z^{-\lambda} \laplace_{\zeta, a} \hat{\varphi} \]
+for all $\lambda \in (0, \infty)$.
 
+\color{violet}
 When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
@@
 Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
-
-%%In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
-Applying $\Lambda$ to both sides of the formula above reveals that
-%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
-
-%%Say $A$ is an $n$th-order differential operator with polynomial coefficients.
-If we know that $A\hat{\varphi} = 0$, and we know the Taylor polynomial of $\hat{\varphi}$ at zero through degree $n - 1$, we can use the formulas above to find an inhomogeneous differential equation that $\laplace \hat{\varphi}$ must satisfy.
 \subsection{Algebraic version}
@@
 \[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
+\color{black}
 \subsection{Change of coordinates}
@@
 \[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
+\section{Shifting integro-differential equations}
+Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
+A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
+We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
+\begin{equation}\label{eqn:slight-defn}
+\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
+\end{equation}
+where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
+
+Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
+This is because differential equations in the spatial domain arise most naturally from integral equations in the frequency domain, but we'd like to work with differential equations in the frequency domain too.
+In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
+\begin{prop}\label{prop:shift}
+When $\psi$ is slight and locally integrable at $\zeta = 0$,
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+if and only if
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+where $h_n, \ldots, h_{-m}$ are regular functions.
+\end{prop}
+To prove this result, we'll need a little background.
+
+Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
+The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
+If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
+A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
+
+Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
+Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
+Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
+Each basic operation has a simple effect on a slight function's order.
+Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
+Differentiation and integration add $-1$ and $1$, respectively.
+\begin{proof}[Proof of Proposition~\ref{prop:shift}]
+The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
+
+To prove the forward implication, rewrite the first equation in the statement as
+\begin{equation}\label{eqn:diff-int-split}
+\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
+\end{equation}
+The function
+\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
+is slight.
+Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
+Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
+
+Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi. \]
+Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
+\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi, \]
+which rearranges to the second equation in the statement.
+\end{proof}
+
+\color{magenta}
+A holomorphic function on an open neighborhood of $\zeta = 0$ defines a germ in $\C\{\zeta\}$.
+A holomorphic function on an open sector $\zeta \in (0, \epsilon)\,e^{i[\theta + (-\delta, \delta)]}$ defines a germ in a ring we'll call $\mathcal{F}_\zeta^\theta$.
+We'll think of $\mathcal{F}_\zeta^\theta$ as an algebra over $\C\{\zeta\}$.
+
+Let's say a germ in $\mathcal{F}_\zeta^\theta$ is {\em slight} if it belongs to the cone generated by the functions $z^\alpha$ with $\alpha \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+\color{black}
 \section{The Airy equation}
@@
 
+The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
+\[ \left[ z P\big(\tfrac{\partial}{\partial z}\big) + Q\big(\tfrac{\partial}{\partial z}\big) + R(z^{-1}) \right] \varphi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function with no constant term. We'll recast equation~\ref{eqn:mod-bessel} in this form:
+\begin{equation}\label{eqn:std-mod-bessel}
+\left[z \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-1} \right] \varphi = 0.
+\end{equation}
+
+\color{violet}
 As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$.
@@
 \end{equation}
+\color{black}
+\subsection{Guessing solutions}
 \subsection{Asymptotic analysis}
-From \cite{dlmf}, equations 10.40.2 and 10.17.1, we get the asymptotic series
+Equation~\ref{eqn:mod-bessel} has a regular singularity at $0$ and an irregular singularity at $\infty$.
+From the general theory of such equations, we know that the space of trans-series solutions has a basis of the form
+\[ \{e^{-\alpha z} z^{\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
+where the $\series{W}_\alpha$ are formal power series in $z^{-1}$ with no constant term.
+From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp}
-\kappa \sim \left(\tfrac{\pi}{2}\right)^{1/2} \left[ z^{-1/2} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-3/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-5/2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-7/2} + \ldots \right]
+\series{W}_1 = z^{-1} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-3} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-4} + \ldots
 \end{equation}
@@
 \subsubsection{Success at $\zeta = 1$}\label{spatial-success}
-Let's try instead to find a function $\hat{K}_1$ with $K = \laplace_{\zeta, 1} \hat{K}_1$. Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$. Since
+Let's try instead to find a function $\hat{K}_1$ with $K = \laplace_{\zeta, 1} \hat{K}_1$ \textcolor{magenta}{[This would be called $K_1$ in our new notation.]}.
+Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$.
+Since
 \begin{align*}

### 2022-03-27 airy-resurgence.tex
Rewrite Borel regularity argument using slight functions

@@
 \usepackage{graphicx}
-\usepackage{xcolor} %% for revisions
+\usepackage[svgnames]{xcolor} %% for revisions
 
@@
 For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
-\subsubsection{Action on differential and integral operators}\label{L-diff-op}
+\subsubsection{Action on integral operators}\label{L-int-op}
 When $\hat{\varphi} \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}\label{id:L-mult}
+\begin{equation}%%\label{id:L-mult}
 \laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
@@
 \color{black}
-\subsection{Change of coordinates}
+\subsection{Change of coordinates}\label{translation}
 Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
@@
 \[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
-\section{Shifting integro-differential equations}
+\section{Shifting integro-differential equations}\label{shifting}
 Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
@@
 Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the spatial domain arise most naturally from integral equations in the frequency domain, but we'd like to work with differential equations in the frequency domain too.
+This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
 In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shift}
+\begin{prop}\label{prop:shifting}
 When $\psi$ is slight and locally integrable at $\zeta = 0$,
@@
 Differentiation and integration add $-1$ and $1$, respectively.
-\begin{proof}[Proof of Proposition~\ref{prop:shift}]
+\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
 The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
@@
 Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi. \]
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
 Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k-1} \right] \psi, \]
+\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
 which rearranges to the second equation in the statement.
@@
 The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-\[ \left[ z P\big(\tfrac{\partial}{\partial z}\big) + Q\big(\tfrac{\partial}{\partial z}\big) + R(z^{-1}) \right] \varphi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function with no constant term. We'll recast equation~\ref{eqn:mod-bessel} in this form:
-\begin{equation}\label{eqn:std-mod-bessel}
-\left[z \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-1} \right] \varphi = 0.
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
+\begin{equation}\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
 \end{equation}
@@
 \color{black}
-\subsection{Guessing solutions}
 \subsection{Asymptotic analysis}
-Equation~\ref{eqn:mod-bessel} has a regular singularity at $0$ and an irregular singularity at $\infty$.
-From the general theory of such equations, we know that the space of trans-series solutions has a basis of the form
-\[ \{e^{-\alpha z} z^{\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
+Equation~\ref{eqn:mod-bessel} has a regular singularity at $z = 0$ and an irregular singularity at $z = \infty$.
+From the general theory of such equations, we know that the space of trans-series solutions has a basis of trans-monomials
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
 where the $\series{W}_\alpha$ are formal power series in $z^{-1}$ with no constant term.
@@
 \end{equation}
+
+The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+which seem analogous to the trans-monomials above.
+Borel summation makes the analogy precise.
+We'll see in Section~\ref{bessel-regularity} that each $z^{\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{\tau_\alpha}\,\series{W}_\alpha$.
 \subsection{Going to the spatial domain}\label{spatial}
+\color{violet}
 \subsubsection{A good try at $\zeta = 0$}
 Let's try to find a function $\hat{K}_0$ with $K = \laplace_\zeta \hat{K}_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
-\begin{equation}\label{eqn:spatial-mod-bessel}
+\begin{equation}%%\label{eqn:spatial-mod-bessel}
 \left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0,
@@
 Unfortunately, this would force $\hat{K}_0$ to be zero.
+\color{black}
+\subsubsection{The big idea}\label{big-idea}
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-mod-bessel}.
+We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+It's tempting to differentiate both sides of this equation until we get
+\begin{equation}\label{diff-eq:spatial-mod-bessel}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
+\end{equation}
+which is easier to solve.
+Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
+
+This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+We can see the regular singularities by moving the derivatives to the right:
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
+
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed.
+For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
+This not only gives us solutions of equation~\ref{eqn:reg-mod-bessel}, but also tells us something about their asymptotics.
+Recall from Section~\ref{translation} that
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha, \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+Observing that the order $\tau_\alpha$ of $v_\alpha$ is greater than $-1$, we can work out that $V_\alpha$ is in $o_{z \to \infty}(z^{-1-\tau_\alpha})$ \textbf{[recall definition of $o$]}.
+Now we can write our solution as
+\[ e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is in $o_{z \to \infty}(z^{-1})$.
+\color{Peru}
+\begin{align*}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
+\end{align*}
+\color{Sienna}
+\begin{align*}
+\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
+\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
+\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
+\end{align*}
+\color{black}
+%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
+%%\begin{equation}\label{eqn:centered-mod-bessel}
+%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
+\]
+%%\end{equation}
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
+\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
+\begin{equation}\label{diff-eq:hypergeom-pos}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1 \in o_{z \to \infty}(z^{-1})$.
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
+In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_{-1} \in o_{z \to \infty}(z^{-1})$.
+
+In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
+Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
+In our case, though, exchanging $1$ with $-1$ keeps equation~\ref{diff-eq:spatial-mod-bessel} the same.
+
+\color{magenta}
+If we'd followed the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we would've arrived at the hypergeometric equation
+\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
+where $\zeta_{-1} = 2\xi_{-1}$.
+This is the same as what we'd get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
+In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$
+\color{black}
+\color{violet}
 \subsubsection{Success at $\zeta = 1$}\label{spatial-success}
@@
 \[ \hat{K}_1 = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+\color{black}
 \section{Sketches}

### 2022-03-28 airy-resurgence.tex
Update intro to Laplace transform
In the process, replace little-o with asymptotic equality, which
is what I actually meant. Notation for asymptotic equality up to
scaling might be the best, though.

@@
 \usepackage[svgnames]{xcolor} %% for revisions
+\usepackage{xparse} %% for squiggly underlines
+\usepackage{tikz} %% for squiggly underlines
+
+% TikZ libraries
+\usetikzlibrary{decorations.pathmorphing} %% for squiggly underlines
 
@@
 \newcommand{\C}{\mathbb{C}}
+\let\Re\relax
+\DeclareMathOperator{\Re}{Re}
+\newcommand{\freqdom}{\undersquiggle{\C}}
+\newcommand{\spacedom}{\dot{\C}}
 \newcommand{\laplace}{\mathcal{L}}
@@
 \DeclareMathOperator{\Ai}{Ai}
+
+% frougon's squiggly underlines
+% https://tex.stackexchange.com/a/532011/6934
+\makeatletter
+% Command from egreg (https://tex.stackexchange.com/a/499972/73317)
+\newcommand{\math@param}[3]{%
+  \fontdimen#3
+  \ifx#1\displaystyle\textfont#2
+  \else\ifx#1\textstyle\textfont#2
+  \else\ifx#1\scriptstyle\scriptfont#2
+  \else\scriptscriptfont#2 \fi\fi\fi
+}
+
+\newdimen\@squiggle@yshift
+\NewDocumentCommand{\undersquiggle}{m}{\mathord{\mathpalette\@undersquiggle{#1}}}
+
+\newcommand*{\@undersquiggle}[2]{%
+  \begin{tikzpicture}[baseline=(n.base)]
+  \node (n) [inner sep=0]
+    {\global\@squiggle@yshift=-0.5\math@param{#1}{2}{5}%
+     $\m@th #1#2$};
+    \draw[decorate, decoration={snake, amplitude=0.3pt, segment length=2pt}]
+      ([yshift=\@squiggle@yshift]n.south west) -- ([yshift=\@squiggle@yshift]n.south east);
+  \end{tikzpicture}%
+}
+\makeatother
 
@@
 \subsubsection{Regularity and decay properties}\label{reg-decay}
-Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively.
-The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
-\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
-For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
+Take two copies of the complex plane: the {\em frequency domain} $\freqdom$ and the {\em spatial domain} $\spacedom$, with standard coordinates $z$ and $\zeta$ respectively.
+The Laplace transform in $\zeta$ based at $\zeta = \alpha$ turns a function $f$ on $\zeta \in \alpha + (0, \infty)$ into a function $\laplace_{\zeta, \alpha} f$ on $z \in (0, \infty)$, defined by the integral
+\[ \laplace_{\zeta, \alpha} f = \int_\alpha^{\alpha + \infty} e^{-z \zeta}\,f\;d\zeta. \]
+For $\rho \in [0, \infty]$, recall that a function $f$ is in $O_{\zeta \to \rho}(g)$ if $|f| \lesssim g$ on some neighborhood\footnote{An open neighborhood in $\freqdom$ intersected with the domain of $f$.} of $\zeta = \rho$.
 A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$.
-If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
-If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
-For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
+Let $\mathcal{E}_{\zeta, \alpha}$ be the space of subexponential functions on $\zeta \in \alpha + (0, \infty)$ which are locally integrable throughout $\zeta \in \alpha + [0, \infty)$.
+If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined, and it extends to a holomorphic function on $\Re(z) > 0$~\cite[\S 5.6]{diverg-resurg-i}.
+
+For the Laplace transform based at $\zeta = 0$
+
+The asymptotics of $f$ at $\zeta = \alpha$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at $z = \infty$.
+Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
+Let $F = \laplace_{\zeta, 0} f$.
+Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality.
+For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} that
+\[ f \in O_{\zeta \to 0}(1) \quad\Longrightarrow\quad F \in O_{z \to \infty}\left(\frac{1}{z}\right). \]
+More generally, for $\tau > -1$ \textbf{[prove or cite]},
+\[ f \in O_{\zeta \to 0}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z \to \infty}\left(\frac{1}{z^{1 + \tau}}\right). \]
+Exact power law asymptotics relate similarly \textbf{[prove or cite]}:
+\[ f \sim \zeta^\tau \text{ at } \zeta = 0 \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at } z = \infty. \]
 \subsubsection{Action on integral operators}\label{L-int-op}
@@
 For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-This not only gives us solutions of equation~\ref{eqn:reg-mod-bessel}, but also tells us something about their asymptotics.
-Recall from Section~\ref{translation} that
+Calling its order $\tau_\alpha$, we'll normalize it so that $v_\alpha \sim \zeta^{\tau_\alpha}$ at $\zeta = \alpha$.
+We know $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even work out its asymptotics.
+We know from Section~\ref{translation} that
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha, \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-Observing that the order $\tau_\alpha$ of $v_\alpha$ is greater than $-1$, we can work out that $V_\alpha$ is in $o_{z \to \infty}(z^{-1-\tau_\alpha})$ \textbf{[recall definition of $o$]}.
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we know from Section~\ref{reg-decay} that $V_\alpha \sim \Gamma(1 + \tau_\alpha)\,z^{-1 - \tau_\alpha}$ at $z = \infty$.
 Now we can write our solution as
 \[ e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is in $o_{z \to \infty}(z^{-1})$.
+where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to $\Gamma(1 + \tau_\alpha)\,z^{-1}$ at $z = \infty$.
 \color{Peru}
@@
 Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$.
+Define a new coordinate $\zeta_1$ on $\spacedom$ so that $\zeta = 1 + \zeta_1$.
 In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1 \in o_{z \to \infty}(z^{-1})$.
+Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ with $W_1 \sim \Gamma\big(\tfrac{1}{2}\big)\,z^{-1}$ at $z = \infty$.
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root}

### 2022-03-29 airy-resurgence.tex
Correct notation for asymptotics of v_1 and v_{-1}

@@
 For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-Calling its order $\tau_\alpha$, we'll normalize it so that $v_\alpha \sim \zeta^{\tau_\alpha}$ at $\zeta = \alpha$.
-We know $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even work out its asymptotics.
-We know from Section~\ref{translation} that
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+We learned in Section~\ref{translation} that
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha, \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we know from Section~\ref{reg-decay} that $V_\alpha \sim \Gamma(1 + \tau_\alpha)\,z^{-1 - \tau_\alpha}$ at $z = \infty$.
-Now we can write our solution as
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we learned in Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$.
+That means we can write our solution as
 \[ e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to $\Gamma(1 + \tau_\alpha)\,z^{-1}$ at $z = \infty$.
+where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 \color{Peru}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ with $W_1 \sim \Gamma\big(\tfrac{1}{2}\big)\,z^{-1}$ at $z = \infty$.
+Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_{-1} \in o_{z \to \infty}(z^{-1})$.
+Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 

### 2022-03-29 airy-resurgence.tex
Polish discussion of asymptotics

@@
 We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha, \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and we learned in Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$.
-That means we can write our solution as
-\[ e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-where $W_\alpha = z^{\tau_\alpha} V_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 \color{Peru}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Observing that $v_1$ has order $-1/2$, we learn that $V_1 = z^{1/2} W_1$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Like our other solution, $v_{-1}$ has order $-1/2$, we again have $V_{-1} = z^{1/2} W_{-1}$ for some $W_1$ which is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 

### 2022-03-31 draft2.tex
update notation and add Laplace section

--- 2022-03-21 draft2.tex
@@
 \subsection{Borel transform}
-\color{black}
-We breifly recall some basic facts on Borel transform and its properties (more details can be founded at \cite{MS}, \cite{MDiablerets}, \cite{}, \cite{}).
-The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$: \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
+
+We breifly recall some basic facts on Borel transform and its properties (more details can be founded in \cite{MS}, \cite{MDiablerets}, \cite{}, \cite{}).
+
+The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$ such that  \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
 \mathcal{B}(1)&\defeq\delta 
@@
 
-where $\delta$ is the element $(1,0)\in\C\times\C[\![\zeta]\!]$\footnote{In the physical literature (\cite{MDiablerets}\cite{SGM}) many authors adopt a different convention, namely they define $\mathbb{B}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
-However, we find more natural the mathematical convention as the Laplace transform is the inverse of $\mathcal{B}$ under suitable growth conditions.
+where $\delta$ is the element $(1,0)\in\C\times\C[\![\zeta]\!]$\footnote{Sometimes, in physics it is common to adopt a differnt convention, i.e.
+$\mathcal{B}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$ (see\cite{MDiablerets}\cite{SGM}, for example).
+However, we find natural for our pourposes the mathematical convention, as the Laplace transform is the inverse of $\mathcal{B}$ under suitable growth conditions.
 }, and $\mathcal{B}$ extends formally by linearity to
@@
 Notice that we are at the level of formal series, so there are no convergence assumptions.
-However, there is a special class of formal series that behaves well under Borel transform, meaning that its Borel transform gives a holomorphic fucntion at the origin in $\C_{\zeta}$.
-These are the so called Gevrey-$1$ series: $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+However, there is a special class of formal series that behaves well under Borel transform, meaning that its Borel transform gives a germ of holomorphic fucntions at the origin in $\C_{\zeta}$.
+These formal series are the so called Gevrey-$1$ series: $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
 there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
+The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series.
 }
 
+\begin{notation*}
+We want to distinghuish between formal series and holomorphic functions, as well as between the Borel plane (spatial domain) and the $z$-plane (time domain). Therefore we adopt the following notation:
+\begin{itemize}
+\item $\Phi(z)$: upper-case letters are holomorphic functions in the $z$-plane;
+\item $\tilde{\Phi}(z)$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the $z$-plane;
+\item $\phi(\zeta)$: lower-case letter are holomorphic functions in the Borel plane (time domain).
+We follow the convention for Laplace transform of holomorphic functions, namely $\mathcal{L}(\phi(\zeta)((z)=\Phi(z)$.
+\item $\tilde{\phi}(\zeta)$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
+As we will see, the Borel transform of $\tilde{\Phi}(z)$ is $\mathcal{B}(\tilde{\Phi})(\zeta)=:\tilde{\phi}(\zeta)$;
+\item $\hat{\phi}(\zeta)$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}(\zeta)$, when it exists.  
+\end{itemize}
+\end{notation*}
+
 \begin{lemma}
-Let $f(z)=\sum_{n\geq 0}a_nz^{-n}$, $f(z)$ is Gevrey-$1$ if and only if $\hat{f}(\zeta)\defeq\mathcal{B}(f)\in\C\lbrace\zeta\rbrace$.  
+Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$, it is Gevrey-$1$ if and only if \[\hat{\phi}(\zeta)=\tilde{\phi}(\zeta)\defeq\mathcal{B}(\tilde{\Phi})\in\C\lbrace\zeta\rbrace.\]  
 \end{lemma}
@@
 \end{align*} 
-
-However, if $f(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}f)(\zeta)$ is a germ of meromorphic function at the oringin: indeed 
-\begin{align*}
-\mathcal{B}(z^{\alpha}f)(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+\color{VioletRed}
+However, if $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}\Phi)(\zeta)$ is a germ of meromorphic function at the oringin: indeed
+\begin{align*}
+\mathcal{B}(z^{\alpha}\tilde{\Phi})(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
 &=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
@@
 The case of interest for usa in the following is when $\alpha=\tfrac{1}{2}$, hence if $a_0\neq 0$, the Borel trasform will be merorphic at the origin and definied on the Riemann surface of the square root.
-
+\color{black}
 \subsubsection{Properties of the Borel transform}
-We now recall some properties of the Borel transform: let $f(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\hat{f}(\zeta)\defeq\mathcal{B}(f(z))$
+We now recall some properties of the Borel transform: let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\tilde{\phi}(\zeta)\defeq\mathcal{B}(\tilde{\Phi}(z))$
 
 \begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha f(z)\right)=\partial_{\zeta}^{\alpha}\hat{f}(\zeta)$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^nf(z))=\partial_\zeta^n\hat{f}(\zeta)$ 
-\item[(iv)] $\mathcal{B}\left(\partial_z^{n} f(z)\right)=(-\zeta)^n\hat{f}(\zeta)$, for every $n\geq 0$
-\item[(v)] $\mathcal{B}(f(z-c))=e^{-c\zeta}\hat{f}(\zeta)$
-\item[(vi)] if $g(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(f(z)g(z))=\int_0^{\zeta}d\zeta' \hat{f}(\zeta-\zeta')\hat{g}(\zeta')=:\hat{f}\ast \hat{g}$, where $\hat{g}(\zeta)=\mathcal{B}(g(z))$.
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^n\tilde{\Phi}(z))=\partial_\zeta^n\tilde{\phi}(\zeta)$ 
+\item[(iv)] $\mathcal{B}\left(\partial_z^{n} \tilde{\Phi}(z)\right)=(-\zeta)^n\tilde{\phi}(\zeta)$, for every $n\geq 0$
+\item[(v)] $\mathcal{B}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}(\zeta)$
+\item[(vi)] if $\tilde{\Psi}(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(\tilde{\Phi}(z)\tilde{\Psi}(z))=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}(\zeta)=\mathcal{B}(\tilde{\Psi}(z))$.
 \end{itemize}
@@
 For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \left[ \borel z^\mu z^{-(k+1)} \right](\zeta). \]
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] =  \borel \left(z^\mu z^{-(k+1)}\right)(\zeta). \]
 \end{lemma}
@@
 \begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
@@
 \begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
 \end{equation}
@@
 \begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel z^{-(k+1)} \right](\zeta) & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
 & = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
@@
 \begin{proof}
+
+We are going to prove properties (i)--(vi).
+
 (i) follows from Lemma \ref{lem:frac-deriv-Borel}.
 
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel (z^\alpha f(z))=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\hat{f}(\zeta).\]
-
-(iii) $z^nf(z)=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel (z^n f(z))=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\hat{f}(\zeta).\]
-
-(vi) $\partial_z^n f(z)=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel (z^\alpha f(z))=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\hat{f}(\zeta).\]
+(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}(\zeta).\]
+
+(iii) $z^n\tilde{\Phi}(z)=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel (z^n \tilde{\Phi}(z))=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}(\zeta).\]
+
+(vi) $\partial_z^n \tilde{\Phi}(z)=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}(\zeta).\]
 
@@
 \begin{align*}
-\borel (z^\alpha f(z))&=\borel (z^\alpha)\ast \hat{f}(\zeta)\\
-&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\hat{f}(\zeta)\\
+\borel (z^\alpha \tilde{\Phi}(z))&=\borel (z^\alpha)\ast \tilde{\phi}(\zeta)\\
+&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}(\zeta)\\
 &=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
@@
 &=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
-&=\partial_\zeta^\alpha\hat{f}(\zeta)
+&=\partial_\zeta^\alpha\tilde{\phi}(\zeta)
 \end{align*}
@@
 
-\subsection{Laplace transform}
- \textbf{Copy from Aaron}
-
-\subsection{Borel--Laplace summability}
+\section{Laplace transform}
+
+\subsection{Analytic version}
+\textcolor{LimeGreen}{Check notation with Aaron}
+\subsubsection{Regularity and decay properties}\label{reg-decay}
+Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively.
+The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
+\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
+For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
+A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$.
+Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$.
+If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
+If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
+For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
+\subsubsection{Action on differential operators}\label{L-diff-op}
+When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\begin{equation}\label{id:L-mult}
+\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
+\end{equation}
+
+When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
+\begin{align}\label{id:L-diff}
+\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace_\zeta \hat{\varphi} - \left[ \hat{\varphi}\,z^{n-1} + \hat{\varphi}'\,z^{n-2} + \hat{\varphi}''\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)} \right]_{\zeta = 0} \\
+& = z^n\,\laplace\left( \hat{\varphi} - \left[ \hat{\varphi} + \hat{\varphi}'\,\zeta + \tfrac{\hat{\varphi}''}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right).
+\nonumber
+\end{align}
+Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O_{\zeta \to \infty}(e^{c\zeta})$.
+Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
+
+%%In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
+Applying $\Lambda$ to both sides of the formula above reveals that
+%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
+
+%%Say $A$ is an $n$th-order differential operator with polynomial coefficients.
+If we know that $A\hat{\varphi} = 0$, and we know the Taylor polynomial of $\hat{\varphi}$ at zero through degree $n - 1$, we can use the formulas above to find an inhomogeneous differential equation that $\laplace \hat{\varphi}$ must satisfy.
+\subsection{Algebraic version}
+
+Let $\mathcal{P}_\zeta$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
+Note that $\mathcal{P}_\zeta \cap \mathcal{E}_\zeta$ is $\mathcal{P}_\zeta^{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
+Since
+\[ \laplace_\zeta(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)} \]
+for all $\alpha > -1$, let's use the same formula to extend $\laplace_\zeta$ to all of $\mathcal{P}_\zeta$. This defines $\laplace_\zeta$ consistently on $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
+\subsubsection{Action on differential operators}\label{L-diff-op-alg}
+Observe that
+\[ \laplace_\zeta(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace_\zeta(\zeta^\alpha) \]
+for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}_\zeta$.
+
+Observe that
+\[ \laplace_\zeta\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
+z\,\laplace_\zeta(\zeta^\alpha) & \alpha \neq 0 \\
+0 & \alpha = 0,
+\end{cases} \]
+and that $0 = z\,\laplace_\zeta(1) - 1$.
+This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}_\zeta$ whose $n$th derivative is in $\mathcal{P}_\zeta^{> -1}$.
+Although the functions in $\mathcal{P}_\zeta^{< 0}$ are singular at zero, let's pretend they vanish at zero.
+With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}_\zeta$.
+
+Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
+Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$.
+By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
+Under this condition, all the initial value terms in the identity vanish, leaving
+\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
+\subsubsection{Change of coordinates}
+Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
+\begin{align*}
+\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
+& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
+& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
+\end{align*}
+we learn that
+\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]
+
+Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
+\begin{align*}
+\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
+& = b \laplace_\xi \hat{\varphi},
+\end{align*}
+we learn that
+\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
+
+\section{Borel--Laplace summability and Resurgence}
 
@@
 Ecalle introduced the theory of resurgence: divergent power series that are Gevrey-$1$ become germs of holomorphic functions at the origin in the Borel plane.
-Being divergent, they have singularities in Borel plane and the aim is to investigate the type of singularities and the analytic continuation of the germ.
+Being divergent, they have singularities in Borel plane and the aim of resurgence theory is to investigate the type of singularities and the analytic continuation of the germ.
 Indeed a formal series is resurgent if it admits an \textit{endless} analytic continuation.
@@
 \begin{equation}
-\hat{f}(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\log(\zeta-\omega)\hat{\Phi}(\zeta-\omega)+\text{hol. fct.}
-\end{equation}
-for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\Phi}$ the minor.
+\hat{f}(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\log(\zeta-\omega)\hat{\phi}(\zeta-\omega)+\text{hol. fct.}
+\end{equation}
+for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\phi}$ the minor.
 \end{definition}
 
-The holomorphic function $\hat{\Phi}$ associated with the logarithmic singularity can be obtained by considering the analytic continuation of $\hat{f}$ across the logarithmic branch cut
-\begin{equation}
-\hat{\Phi}(\zeta)=\hat{f}(\zeta+\omega)-\hat{f}(\zeta e^{-2\pi i}+\omega)
+The holomorphic function $\hat{\phi}$ associated with the logarithmic singularity can be obtained by considering the analytic continuation of $\hat{f}$ across the logarithmic branch cut
+\begin{equation}
+\hat{\phi}(\zeta)=\hat{f}(\zeta+\omega)-\hat{f}(\zeta e^{-2\pi i}+\omega)
 \end{equation}
@@
 \color{black}
-\section{Resurgence of exponential integrals}
+\section{Exponential integrals}
+\subsection{Borel }
 Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set

### 2022-04-01 exp-resurgence.tex
Veronica proposal

@@
 \item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform.
-\item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resugence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.
+\item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resurgence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.
 \item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
@@
 \[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parameterized by $z$, and it turns out \textbf{[we hope]} to be Borel regular.
+is a holomorphic function on the right half-plane parametrized by $z$, and it turns out \textbf{[we hope]} to be Borel regular.
 
@@
 \[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-a holomorphic function on the right half-plane parameterized by $z$.
+a holomorphic function on the right half-plane parametrized by $z$.
 It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
@@
 \begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
+\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behaviour.
 \item The resummation method works correctly for functions which satisfy that assumption.
@@
 \begin{itemize}
-\item \textbf{Maxim belives it is in general, and indeed in our examples we get simple resurgent functions. But how to prove it in general?}
+\item \textbf{Maxim belies it is in general, and indeed in our examples we get simple resurgent functions. But how to prove it in general?}
 \end{itemize} 
@@
 \end{itemize}
+
+\color{orange}
+\textbf{Veronica's proposal}
+
+\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
+
+\begin{enumerate}
+\item what are exponential integrals? Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}). In physics ?? \textcolor{gray}{has to be done}
+\item what does it mean being Borel regular? and when does it happen? \textcolor{gray}{has to be done}
+\begin{itemize}
+\item Watson condition
+\item linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday--Richaud ?, big idea in {\tt airy-resurgence}]
+\item our theorem [{\tt draft2}]
+\end{itemize}
+\item Resurgence of exponential integrals and Stokes phenomena
+\begin{itemize}
+\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
+\item ODE and fractional derivative formula [{\tt draft2}]: hypergeometric functions \textcolor{gray}{has to be done}
+\end{itemize}
+\item The Airy example
+\begin{itemize}
+\item $I(z)$ is a solution of a linear ODE.
+We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
+\item Stokes constants using fractional derivative formula and Borel transform computation [{\tt draft2}]
+\item Comparison with the literature (Marino, Sauzin, Kontsevich slides) \textcolor{gray}{has to be done}
+\end{itemize}
+\item Bessel $1/n$ (follows from Airy) we compute Borel transform and Stokes constants \textcolor{gray}{has to be done}
+\item Bessel 0 (it is different because we have infinite cover) we compute Stokes constants [{\tt draft2}]
+\item Bessel $\mu$ (follows from Bessel 0) we compute Stokes constants [{\tt modified Bessel}]
+\end{enumerate}
+
 \end{document}

### 2022-04-01 draft2.tex

@@
 \end{align*}
-\color{VioletRed}
-However, if $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, then the Borel transform of $\mathcal{B}(z^{-\alpha}\Phi)(\zeta)$ is a germ of meromorphic function at the oringin: indeed
-\begin{align*}
-\mathcal{B}(z^{\alpha}\tilde{\Phi})(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-In particular, if $\alpha\in (1,+\infty)$, then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
-^{\alpha-1}$, otherwise if $\alpha\in (-\infty,1)$ then $\mathcal{B}(z^{\alpha}f)(\zeta)$ is a meromorphic functions on the Riemann surface where $\zeta^{\alpha-1}$ defines an analytic coordinate.
-The case of interest for usa in the following is when $\alpha=\tfrac{1}{2}$, hence if $a_0\neq 0$, the Borel trasform will be merorphic at the origin and definied on the Riemann surface of the square root.
-\color{black}
+However, if $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ is a Gevrey-$1$ series, and $\alpha$ is a rational number with denominator $q$, then $\mathcal{B}(z^{-\alpha}\tilde{\Phi})(\zeta)$ is a germ of meromorphic function at the oringin of the Riemann surface of $\zeta^{1/q}$.
+Indeed,
+\begin{align*}
+\mathcal{B}(z^{-\alpha}\tilde{\Phi})(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+&=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}.
+\end{align*}
+If $\alpha > 1$, then $\mathcal{B}(z^{-\alpha}\tilde{\Phi})(\zeta)$ is actually a germ of holomorphic functions on the Riemann surface of $\zeta
+^{1/q}$. We're interested in the case where $\alpha=\tfrac{1}{2}$, so the Borel transform is meromorphic on the Riemann surface of $\zeta^{1/2}$, and has a pole at $\zeta = 0$ unless $a_0 = 0$.
 \subsubsection{Properties of the Borel transform}

### 2022-04-01 draft2.tex
Keep working on outline

--- 2022-03-21 draft2.tex
@@
 We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.]} For each cutoff $N$, the tail
+\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
+See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
 \[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]

### 2022-04-01 exp-resurgence.tex
Keep working on outline

@@
 \color{orange}
-\textbf{Veronica's proposal}
+\section*{Veronica's proposal}
 
@@
 \begin{enumerate}
-\item what are exponential integrals? Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}). In physics ?? \textcolor{gray}{has to be done}
-\item what does it mean being Borel regular? and when does it happen? \textcolor{gray}{has to be done}
+\item introduction
 \begin{itemize}
-\item Watson condition
-\item linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday--Richaud ?, big idea in {\tt airy-resurgence}]
-\item our theorem [{\tt draft2}]
+\item what are exponential integrals? \textcolor{gray}{has to be done}
+\begin{itemize}
+\item motivation
+\begin{itemize}
+\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
+\item In physics ??
+\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
 \end{itemize}
-\item Resurgence of exponential integrals and Stokes phenomena
+\end{itemize}
+\item Borel regularity
+\begin{itemize}
+\item what does it mean being Borel regular?
+\item when does it happen?
+\begin{itemize}
+\item Recall Watson condition (old)
+\item State new Borel regularity results
+\begin{itemize}
+\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday-Richaud ?, big idea in {\tt airy-resurgence}]
+\item Thimble integral [{\tt draft2}]
+\end{itemize}
+\end{itemize}
+\end{itemize}
+\item State results about resurgence of exponential integrals and Stokes phenomena
 \begin{itemize}
 \item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]: hypergeometric functions \textcolor{gray}{has to be done}
+\item ODE and fractional derivative formula [{\tt draft2}]
+\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
 \end{itemize}
+\end{itemize}
+\item Formalism for Laplace transform
+\begin{enumerate}
+\item Introduction
+\begin{enumerate}
+\item
+\end{enumerate}
+\end{enumerate}
+\item General cases
+\begin{enumerate}
+\item Borel regularity
+\begin{itemize}
+\item General ODE of the form
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
+\item General thimble integral (conditions?)
+\end{itemize}
+\item Resurgence
+\end{enumerate}
 \item The Airy example

### 2022-04-04 draft2.tex
comparison with Mairno

@@
 
-\begin{example}[Airy]
+\section{Airy exponential integral}
 By definition,
@@
 \color{black}
-\end{example}
-
-\begin{example}[Bessel]
+\subsection{Comparison with other Airy examples}
+
+\subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+It is also commun to deal with formal power series in small parameters, like $\Phi(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ as $\hbar\to 0$.
+Then the Borel transform of $\Phi$ is defined as $\phi(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author study the resurgent properties of the Airy functions: his starting point is the formal solution of Airy differential equation
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\end{align*}  
+where 
+\begin{align*}
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n
+\end{align*}
+Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) \\
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
+\end{align*}
+%That ambiguity comes from the different definitions of Borel transforms: 
+%\begin{align*}
+%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%\end{align*}
+
+Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $w_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
+
+\section{Bessel 0}
 
@@
 \begin{align}
-\label{w+}&\hat{w}_+(\zeta)=c_1\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
-\label{w+}&\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
+\label{wB+}&\hat{w}_+(\zeta)=c_1\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
+\label{wB-}&\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
 \end{align}
@@
 }
-\end{example}
 

### 2022-04-04 kawai+takei vs mariño.tex
Add comparison notes for Kawai & Takei

\documentclass{article}

\usepackage{ajf}
\usepackage{amsthm}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

\DeclareMathOperator{\Ai}{Ai}

\title{Airy function: Kawai+Takei vs. Mari\~{n}o}
\author{Aaron Fenyes}

\begin{document}
\maketitle
Kawai and Takei want to solve
\[ \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0. \]
They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.

With $w = x \eta^{2/3}$, the equation above is equivalent to
\[ \left[\left(\frac{d}{dw}\right)^2 - w \right] \psi(w \eta^{-2/3}, \eta) = 0. \]
Proof: substitute back to get
\begin{align*}
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{2/3} x \right] \psi(x, \eta) = 0 \\
\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{-4/3} \eta^2 x \right] \psi(x, \eta) = 0 \\
\eta^{-4/3} \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0.
\end{align*}
Hence, $\psi(w \eta^{-2/3}, \eta) = k(\eta) \Ai(w)$ is a solution for any holomorphic function $k$.

%y = x eta^(2/3)
%d/dy^2 = eta^(-4/3) d/dx^2
%eta^(4/3) d/dy^2 = d/dx^2
%
%eta^2 x = eta^2 y eta^(-2/3)
%        = eta^(4/3) y
%
%[(d/dy)^2 - y] psi(x, eta) = 0
%
%psi(x, eta) = Ai(y) is a solution
%psi(eta^(-2/3) y, eta) = Ai(y)
\end{document}

### 2022-04-04 draft2.tex
sauzin comparison

--- 2022-04-01 draft2.tex
@@
 \color{black}
-\end{example}
-
-\begin{example}[Bessel]
+\subsection{Comparison with other Airy examples}
+
+\subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+It is also commun to deal with formal power series in small parameters, like $\Phi(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ as $\hbar\to 0$.
+Then the Borel transform of $\Phi$ is defined as $\phi(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author study the resurgent properties of the Airy functions: his starting point is the formal solution of Airy differential equation
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\end{align*}  
+where 
+\begin{align*}
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n
+\end{align*}
+Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) \\
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
+\end{align*}
+%That ambiguity comes from the different definitions of Borel transforms: 
+%\begin{align*}
+%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%\end{align*}
+
+Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $w_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
+
+\subsubsection{Integral formula for hypergeometric functions}
+
+In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
+He defines the formal series $\Phi(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
+
+\begin{equation}
+\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\left(\tilde{\Phi}_1\left(\frac{2}{3}w^{3/2}\right)\right)
+\end{equation}
+
+Notice $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$.
+
+\section{Bessel 0}
 

### 2022-04-04 draft2.tex
end comparison Sauzin

@@
 In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
-He defines the formal series $\Phi(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
-
-\begin{equation}
-\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\left(\tilde{\Phi}_1\left(\frac{2}{3}w^{3/2}\right)\right)
-\end{equation}
-
-Notice $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$.
+He defines the formal series $\tilde{\Phi}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
+
+\begin{equation}
+\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}\left(\tfrac{2}{3}w^{3/2}\right)
+\end{equation}
+
+Notice that $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$, hence
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\mathcal{B}\tilde{W}_1(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) 
+\end{align*}
+
+However, the author adopts a different approach to compute $\tilde{\phi}(\zeta)$: he argues that $\Phi_{\mathrm{Ai}}$ is a solution of Airy equation if and only if
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\delta+\frac{d}{d\zeta}\tilde{\chi}(\zeta) & \qquad \text{ where }\,\, \chi(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}
+\end{align*}
+
+The function $\chi$ is an hypergeometric function:
+
+\begin{align*}
+\chi(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
+\end{align*}
+where in the last step we use the Euler formula for hypergeometric functions (see \eqref{Euler formula}). Finally, we take the derivative
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right).
+\end{align*}
 
@@
 
+\begin{equation}\label{Euler formula}
+{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt
+\end{equation}
+
 \section{Resurgence for degree $3$ polynomials}

### 2022-04-10 draft2.tex
Introduce frequency coordinates for translation surfaces
Add notes from discussion with Richard Derryberry.

--- 2022-04-04 draft2.tex
@@
 % symbology
+\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
+\newcommand{\maps}{\colon}
+\newcommand{\van}{\mathfrak{m}}
 \newcommand{\laplace}{\mathcal{L}}
@@
 
-\section{Laplace transform}
-
-\subsection{Analytic version}
-\textcolor{LimeGreen}{Check notation with Aaron}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-Take two copies $\R$ and $\hat{\R}$ of the real line, with standard coordinates $z$ and $\zeta$ respectively.
-The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\hat{\R}_{\zeta > 0}$ into a function $\laplace_\zeta \hat{\varphi}$ on $\R_{z > 0}$, defined by the integral
-\[ \laplace_\zeta \hat{\varphi} = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta. \]
-For $a \in [0, \infty]$, recall that recall that $O_{\zeta \to a}(g)$ is the space of functions $\varphi$ on $\hat{\R}_{\zeta > 0}$ with $|\varphi| \lesssim g$ in some neighborhood of $a$.
-A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_\zeta$ be the space of subexponential functions on $\hat{\R}_{\zeta > 0}$ which are $L^1$ both locally and around $\zeta = 0$.
-If $\hat{\varphi}$ is in $\mathcal{E}_\zeta$, then $\varphi = \laplace_\zeta \hat{\varphi}$ is well-defined, and it extends to a holomorphic function on the right half-plane $\C_{\operatorname{Re}(z) > 0}$~\cite[\S 5.6]{diverg-resurg-i}.
-If $\hat{\varphi}$ is in $O_{\zeta \to 0}(1)$, then $\varphi$ is in $O_{z \to \infty}(z^{-1})$~\cite[equation~1.8]{laplace-tfm}.\footnote{The argument cited still works in our generality.
-For holomorphic $\hat{\varphi}$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} More generally, if $\hat{\varphi}$ is in $O_{\zeta \to 0}(\zeta^{\alpha})$, with $\alpha > -1$, then $\varphi$ is in $O_{z \to \infty}\big(z^{-(\alpha + 1)}\big)$.
-\subsubsection{Action on differential operators}\label{L-diff-op}
-When $\hat{\varphi} \in \mathcal{E}_\zeta$, we can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}\label{id:L-mult}
-\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
-\end{equation}
-
-When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
-\begin{align}\label{id:L-diff}
-\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace_\zeta \hat{\varphi} - \left[ \hat{\varphi}\,z^{n-1} + \hat{\varphi}'\,z^{n-2} + \hat{\varphi}''\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)} \right]_{\zeta = 0} \\
-& = z^n\,\laplace\left( \hat{\varphi} - \left[ \hat{\varphi} + \hat{\varphi}'\,\zeta + \tfrac{\hat{\varphi}''}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right).
-\nonumber
-\end{align}
-Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O_{\zeta \to \infty}(e^{c\zeta})$.
-Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
-
-%%In the space of holomorphic functions on the right half-plane, $\C[z] + O(z^{-1})$ is a direct sum, so there's a unique linear projection $\Lambda \maps \C[z] + O(z^{-1}) \to O(z^{-1})$.
-Applying $\Lambda$ to both sides of the formula above reveals that
-%%\[ \laplace \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = \Lambda (z^n\,\laplace \hat{\varphi}). \]
-
-%%Say $A$ is an $n$th-order differential operator with polynomial coefficients.
-If we know that $A\hat{\varphi} = 0$, and we know the Taylor polynomial of $\hat{\varphi}$ at zero through degree $n - 1$, we can use the formulas above to find an inhomogeneous differential equation that $\laplace \hat{\varphi}$ must satisfy.
-\subsection{Algebraic version}
-
-Let $\mathcal{P}_\zeta$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
-Note that $\mathcal{P}_\zeta \cap \mathcal{E}_\zeta$ is $\mathcal{P}_\zeta^{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
-Since
-\[ \laplace_\zeta(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)} \]
-for all $\alpha > -1$, let's use the same formula to extend $\laplace_\zeta$ to all of $\mathcal{P}_\zeta$. This defines $\laplace_\zeta$ consistently on $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
-\subsubsection{Action on differential operators}\label{L-diff-op-alg}
-Observe that
-\[ \laplace_\zeta(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace_\zeta(\zeta^\alpha) \]
-for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}_\zeta$.
-
-Observe that
-\[ \laplace_\zeta\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
-z\,\laplace_\zeta(\zeta^\alpha) & \alpha \neq 0 \\
-0 & \alpha = 0,
-\end{cases} \]
-and that $0 = z\,\laplace_\zeta(1) - 1$.
-This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}_\zeta$ whose $n$th derivative is in $\mathcal{P}_\zeta^{> -1}$.
-Although the functions in $\mathcal{P}_\zeta^{< 0}$ are singular at zero, let's pretend they vanish at zero.
-With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}_\zeta$.
-
-Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
-Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$.
-By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
-Under this condition, all the initial value terms in the identity vanish, leaving
-\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
-\subsubsection{Change of coordinates}
-Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
-\begin{align*}
-\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
-& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
-& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
-\end{align*}
-we learn that
-\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]
-
-Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
-\begin{align*}
-\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
-& = b \laplace_\xi \hat{\varphi},
-\end{align*}
-we learn that
-\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
-
+\section{The geometry of the Laplace transform}
+\subsection{Introduction}
+Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
+In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
+Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
+\subsection{Translation surfaces, briefly}
+A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
+A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
+The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
+\textcolor{VioletRed}{The zeros of $\lambda$ can be called {\em branch points}.} We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
+This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
+
+The translation structure of $B$ gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+At an ordinary point, we can define $z$ simply as the map
+\begin{align*}
+z \maps T^*B_b & \to \C \\
+\lambda(b) & \mapsto 1.
+\end{align*}
+To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
+Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
+Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
+Around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
+When $b$ is an ordinary point, $\zeta_b$ is a translation chart, and it represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda(b)$.
+In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$, and $z$ is the isomorphism
+\begin{align*}
+z \maps \van_b^n / \van_b^{n+1} & \to \C \\
+\zeta_b + \van^{n+1} & \mapsto 1.
+\end{align*}
+
+Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is again the cone angle at $b$. This gives us an isomorphism
+\begin{align*}
+w_b \maps T^*B_b & \to \C \\
+\omega_b + \van^2 & \mapsto 1
+\end{align*}
+that makes the diagram
+\begin{center}
+\begin{tikzcd}
+T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
+T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
+\end{tikzcd}
+\end{center}
+commute.
 \section{Borel--Laplace summability and Resurgence}
@@
 We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
-See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
+\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.]} For each cutoff $N$, the tail
 \[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
@@
 
-\section{Airy exponential integral}
+\begin{example}[Airy]
 By definition,
@@
 \color{black}
-\subsection{Comparison with other Airy examples}
-
-\subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
-It is also commun to deal with formal power series in small parameters, like $\Phi(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ as $\hbar\to 0$.
-Then the Borel transform of $\Phi$ is defined as $\phi(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
-In \cite{Diablerets}, the author study the resurgent properties of the Airy functions: his starting point is the formal solution of Airy differential equation
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
-\end{align*}  
-where 
-\begin{align*}
-\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n
-\end{align*}
-Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-\begin{align*}
-w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
-&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) \\
-\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
-\end{align*}
-%That ambiguity comes from the different definitions of Borel transforms: 
-%\begin{align*}
-%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%\end{align*}
-
-Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $w_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
-
-\subsubsection{Integral formula for hypergeometric functions}
-
-In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
-He defines the formal series $\Phi(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
-
-\begin{equation}
-\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\left(\tilde{\Phi}_1\left(\frac{2}{3}w^{3/2}\right)\right)
-\end{equation}
-
-Notice $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$.
-
-\section{Bessel 0}
+\end{example}
+
+\begin{example}[Bessel]
 
@@
 \begin{align}
-\label{wB+}&\hat{w}_+(\zeta)=c_1\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
-\label{wB-}&\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
+\label{w+}&\hat{w}_+(\zeta)=c_1\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;-\frac{\zeta}{4}\right)\\
+\label{w+}&\hat{w}_-(\zeta)=c_2\,\, {}_2F_1\left(\frac{3}{2},\frac{3}{2};2;\frac{\zeta}{4}\right)
 \end{align}
@@
 }
+\end{example}
 

### 2022-04-12 draft2.tex
Describe the Laplace transform on translation surfaces
Talk about directions and rays on translation surfaces.

@@
 \subsection{Translation surfaces, briefly}
+\subsubsection{Definition}
 A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
@@
 The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-\textcolor{VioletRed}{The zeros of $\lambda$ can be called {\em branch points}.} We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
+We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
 This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
-
-The translation structure of $B$ gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+\subsubsection{Direction}\label{transl:dir}
+The translation structure gives $B$ a notion of direction as well as distance.
+Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
+At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
+To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
+\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
+In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
+
+Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
+This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
+Of course, there are $n$ different choices for $\omega_b$.
+\subsubsection{Frequency}\label{transl-freq}
+The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
 At an ordinary point, we can define $z$ simply as the map
@@
 z \maps T^*B_b & \to \C \\
-\lambda(b) & \mapsto 1.
+\lambda\big|_b & \mapsto 1.
 \end{align*}
@@
 Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
-Around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-When $b$ is an ordinary point, $\zeta_b$ is a translation chart, and it represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda(b)$.
-In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$, and $z$ is the isomorphism
+When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
+In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
+We define $z$ as the isomorphism
 \begin{align*}
@@
 
-Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is again the cone angle at $b$. This gives us an isomorphism
+When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
 \begin{align*}
@@
 commute.
+\subsubsection{Boundary}
+\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}
+\subsection{The Laplace transform}
+\subsubsection{Over an ordinary point}%%\label{laplace:ordinary}
+Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
+\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
+When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
+\begin{equation}\label{laplace:int}
+\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
+\end{equation}
+where $z$ is the frequency function defined in Section~\ref{transl:freq} and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
+
+To make sense of this formula, we ask for the following conditions.
+\begin{itemize}
+\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
+\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
+\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
+\begin{itemize}
+\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
+\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
+%%defined as $e^{-i\theta}$ times the right half-plane.
+\end{itemize}
+\end{itemize}
+%%When $b \in B$ is an ordinary point, there's a unique ray $\Gamma_b^\theta$ leaving $b$ at angle $\theta$.
+Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, we can say the same when $b$ is a branch point.
+
+%%Pick a point $b \in B$ and an extended angle $\theta \in \R/2\pi n\Z$, where $2\pi n$ is the cone angle at $b$.
+Pick a translation chart $\zeta$ whose domain includes the beginning of the ray that leaves $b$ at angle $\theta$.
+Since $b$ might be a branch point, we don't require the domain of $\zeta$ to include $b$ itself.
+Make sure the ray $\Gamma_b^\theta$ described above doesn't hit a branch point.
+\subsubsection{Over a branch point}
+When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
+Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
+The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
+This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
+The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
+We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+
+%%We only define $\laplace_\zeta^\theta f$ on one of them: the sector $w_b \in \R\exp\Big(-\tfrac{\theta}{n} + \big(-\tfrac{\pi}{2n}, \tfrac{\pi}{2n}\big)\Big)$.
+
+%%the sector where the phase of $w_b$ is in $\tfrac{1}{n}\big(-\theta + (-\frac{\pi}{2}, \frac{\pi}{2})\big)$.
+
+%%$w_b \in \R \exp\big(\frac{1}{n}(-\theta - \frac{\pi}{2}, -\theta + \frac{\pi}{2})\big)$
+
+%%We define $\laplace_\zeta^\theta f$ on the one where $e^{i\theta/n} w_b$ is closest to the positive real axis.
 \section{Borel--Laplace summability and Resurgence}

### 2022-04-12 draft2.tex

@@
 \color{black}
-\end{example}
-
-\begin{example}[Bessel]
+\subsection{Comparison with other Airy examples}
+
+\subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+It is also commun to deal with formal power series in small parameters, like $\Phi(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ as $\hbar\to 0$.
+Then the Borel transform of $\Phi$ is defined as $\phi(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author study the resurgent properties of the Airy functions: his starting point is the formal solution of Airy differential equation
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\end{align*}  
+where 
+\begin{align*}
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n
+\end{align*}
+Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) \\
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
+\end{align*}
+%That ambiguity comes from the different definitions of Borel transforms: 
+%\begin{align*}
+%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%\end{align*}
+
+Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $w_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
+
+\subsubsection{Integral formula for hypergeometric functions}
+
+In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
+He defines the formal series $\tilde{\Phi}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
+
+\begin{equation}
+\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}\left(\tfrac{2}{3}w^{3/2}\right)
+\end{equation}
+
+Notice that $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$, hence
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\mathcal{B}\tilde{W}_1(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) 
+\end{align*}
+
+However, the author adopts a different approach to compute $\tilde{\phi}(\zeta)$: he argues that $\Phi_{\mathrm{Ai}}$ is a solution of Airy equation if and only if
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\delta+\frac{d}{d\zeta}\tilde{\chi}(\zeta) & \qquad \text{ where }\,\, \chi(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}
+\end{align*}
+
+The function $\chi$ is an hypergeometric function:
+
+\begin{align*}
+\chi(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
+\end{align*}
+where in the last step we use the Euler formula for hypergeometric functions (see \eqref{Euler formula}). Finally, we take the derivative
+
+\begin{align*}
+\tilde{\phi}(\zeta)=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right).
+\end{align*}
+
+\section{Bessel 0}
 

### 2022-04-14 draft2.tex
Write down the PDE the Laplace transform satisfies
Also, add a reminder to talk about about Ecalle's singularity
formalism.

@@
 \newcommand{\borel}{\mathcal{B}}
+\newcommand{\laplacepde}{\mathcal{D}}
 \DeclareMathOperator{\Ai}{Ai}
@@
 \item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
-%%defined as $e^{-i\theta}$ times the right half-plane.
 \end{itemize}
 \end{itemize}
-%%When $b \in B$ is an ordinary point, there's a unique ray $\Gamma_b^\theta$ leaving $b$ at angle $\theta$.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, we can say the same when $b$ is a branch point.
-
-%%Pick a point $b \in B$ and an extended angle $\theta \in \R/2\pi n\Z$, where $2\pi n$ is the cone angle at $b$.
-Pick a translation chart $\zeta$ whose domain includes the beginning of the ray that leaves $b$ at angle $\theta$.
-Since $b$ might be a branch point, we don't require the domain of $\zeta$ to include $b$ itself.
-Make sure the ray $\Gamma_b^\theta$ described above doesn't hit a branch point.
 \subsubsection{Over a branch point}
@@
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-
-%%We only define $\laplace_\zeta^\theta f$ on one of them: the sector $w_b \in \R\exp\Big(-\tfrac{\theta}{n} + \big(-\tfrac{\pi}{2n}, \tfrac{\pi}{2n}\big)\Big)$.
-
-%%the sector where the phase of $w_b$ is in $\tfrac{1}{n}\big(-\theta + (-\frac{\pi}{2}, \frac{\pi}{2})\big)$.
-
-%%$w_b \in \R \exp\big(\frac{1}{n}(-\theta - \frac{\pi}{2}, -\theta + \frac{\pi}{2})\big)$
-
-%%We define $\laplace_\zeta^\theta f$ on the one where $e^{i\theta/n} w_b$ is closest to the positive real axis.
+\subsubsection{Differential equation}
+If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
+In these coordinates, we can write down the partial differential operator
+\begin{equation}%%\label{laplace:op}
+\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
+\end{equation}
+The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
+
+Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$.
+\begin{problem}
+Find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
+\end{problem}
+The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem. In fact, it produces all the solutions \textbf{[check argument]}.
 \section{Borel--Laplace summability and Resurgence}
@@
 \end{equation}
+\color{Aquamarine}
+In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{I}_\alpha$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
+[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
+Or something even simpler?]
+\color{black}
 

### 2022-04-15 airy-resurgence.tex
Align Laplace transform intro in `airy-resurgence` with `draft2`

@@
 \usepackage{xparse} %% for squiggly underlines
-\usepackage{tikz} %% for squiggly underlines
-
-% TikZ libraries
-\usetikzlibrary{decorations.pathmorphing} %% for squiggly underlines
 
@@
 \DeclareMathOperator{\Re}{Re}
-\newcommand{\freqdom}{\undersquiggle{\C}}
-\newcommand{\spacedom}{\dot{\C}}
 \newcommand{\laplace}{\mathcal{L}}
@@
 \DeclareMathOperator{\Ai}{Ai}
-
-% frougon's squiggly underlines
-% https://tex.stackexchange.com/a/532011/6934
-\makeatletter
-% Command from egreg (https://tex.stackexchange.com/a/499972/73317)
-\newcommand{\math@param}[3]{%
-  \fontdimen#3
-  \ifx#1\displaystyle\textfont#2
-  \else\ifx#1\textstyle\textfont#2
-  \else\ifx#1\scriptstyle\scriptfont#2
-  \else\scriptscriptfont#2 \fi\fi\fi
-}
-
-\newdimen\@squiggle@yshift
-\NewDocumentCommand{\undersquiggle}{m}{\mathord{\mathpalette\@undersquiggle{#1}}}
-
-\newcommand*{\@undersquiggle}[2]{%
-  \begin{tikzpicture}[baseline=(n.base)]
-  \node (n) [inner sep=0]
-    {\global\@squiggle@yshift=-0.5\math@param{#1}{2}{5}%
-     $\m@th #1#2$};
-    \draw[decorate, decoration={snake, amplitude=0.3pt, segment length=2pt}]
-      ([yshift=\@squiggle@yshift]n.south west) -- ([yshift=\@squiggle@yshift]n.south east);
-  \end{tikzpicture}%
-}
-\makeatother
 
@@
 \subsubsection{Regularity and decay properties}\label{reg-decay}
-Take two copies of the complex plane: the {\em frequency domain} $\freqdom$ and the {\em spatial domain} $\spacedom$, with standard coordinates $z$ and $\zeta$ respectively.
-The Laplace transform in $\zeta$ based at $\zeta = \alpha$ turns a function $f$ on $\zeta \in \alpha + (0, \infty)$ into a function $\laplace_{\zeta, \alpha} f$ on $z \in (0, \infty)$, defined by the integral
-\[ \laplace_{\zeta, \alpha} f = \int_\alpha^{\alpha + \infty} e^{-z \zeta}\,f\;d\zeta. \]
-For $\rho \in [0, \infty]$, recall that a function $f$ is in $O_{\zeta \to \rho}(g)$ if $|f| \lesssim g$ on some neighborhood\footnote{An open neighborhood in $\freqdom$ intersected with the domain of $f$.} of $\zeta = \rho$.
-A function is {\em subexponential} if it's in $O_{\zeta \to \infty}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of subexponential functions on $\zeta \in \alpha + (0, \infty)$ which are locally integrable throughout $\zeta \in \alpha + [0, \infty)$.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined, and it extends to a holomorphic function on $\Re(z) > 0$~\cite[\S 5.6]{diverg-resurg-i}.
+Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
+The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\C$ into a function $\laplace_\zeta \hat{\varphi}$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
+\[ \laplace_\zeta \hat{\varphi} \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta, \]
+where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
 
-For the Laplace transform based at $\zeta = 0$
+Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
+A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
+Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
+If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
 
-The asymptotics of $f$ at $\zeta = \alpha$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at $z = \infty$.
+The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
 Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
@@
 For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} that
-\[ f \in O_{\zeta \to 0}(1) \quad\Longrightarrow\quad F \in O_{z \to \infty}\left(\frac{1}{z}\right). \]
+\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
 More generally, for $\tau > -1$ \textbf{[prove or cite]},
-\[ f \in O_{\zeta \to 0}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z \to \infty}\left(\frac{1}{z^{1 + \tau}}\right). \]
+\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
 Exact power law asymptotics relate similarly \textbf{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at } \zeta = 0 \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at } z = \infty. \]
+\[ f \sim \zeta^\tau \text{ at the starting point of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the infinite end of } \Gamma_{z, 0}. \]
 \subsubsection{Action on integral operators}\label{L-int-op}
@@
 Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\spacedom$ so that $\zeta = 1 + \zeta_1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
 In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like

### 2022-04-15 airy-resurgence.tex
Update notation in Laplace transform coordinate change formulas

@@
 Exact power law asymptotics relate similarly \textbf{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the starting point of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the infinite end of } \Gamma_{z, 0}. \]
+\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
 \subsubsection{Action on integral operators}\label{L-int-op}
@@
 \color{black}
-\subsection{Change of coordinates}\label{translation}
-Define a new coordinate $\zeta_a$ on $\hat{\R}$ so that $\zeta = a + \zeta_a$. From the calculation \textbf{[using variable starting point notation]}
+\subsection{Change of translation chart}\label{translation}
+Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
 \begin{align*}
-\laplace_{\zeta, a} \hat{\varphi} & = \int_a^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_0^\infty e^{-z(a + \zeta_a)}\,\hat{\varphi}\;d\zeta_a \\
-& = e^{-az} \int_0^\infty e^{-z\zeta_a}\,\hat{\varphi}\;d\zeta_a \\
-& = e^{-az} \laplace_{\zeta_a, 0} \hat{\varphi},
+\laplace_{\zeta, a} \hat{\varphi} & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\hat{\varphi}\;d\zeta_\alpha \\
+& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\hat{\varphi}\;d\zeta_\alpha \\
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \hat{\varphi},
 \end{align*}
 we learn that
-\[ \laplace_{\zeta_a, 0} \hat{\varphi} = e^{az} \laplace_{\zeta, a} \hat{\varphi}. \]
-
-Define new coordinates $x$ and $\xi$ on $\R$ and $\hat{\R}$, respectively, so that $\zeta = b\xi$ and $z\,d\zeta = x\,d\xi$. Explicitly, $z = b^{-1}x$. From the calculation
+\[ \laplace_{\zeta_\alpha, 0} \hat{\varphi} = e^{\alpha z} \laplace_{\zeta, \alpha} \hat{\varphi}. \]
+\subsection{Rescaling of translation structure}
+The coordinate $\xi$ given by $\zeta = m\xi$ defines a new translation structure on $\C$.
+The corresponding frequency variable $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so we have $z = m^{-1} x$.
+From the calculation
 \begin{align*}
-\laplace_\zeta \hat{\varphi} & = \int_0^\infty e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_0^\infty e^{-x\xi}\,\hat{\varphi}\;b\,d\xi \\
-& = b \laplace_\xi \hat{\varphi},
+\laplace_{\zeta, 0} \hat{\varphi} & = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
+& = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\hat{\varphi}\;m\,d\xi \\
+& = m \laplace_{\xi, 0} \hat{\varphi},
 \end{align*}
 we learn that
-\[ \laplace_\xi \hat{\varphi} = b^{-1} \laplace_\zeta \hat{\varphi}. \]
+\[ \laplace_{\xi, 0} \hat{\varphi} = m^{-1} \laplace_{\zeta, 0} \hat{\varphi}. \]
 \section{Shifting integro-differential equations}\label{shifting}

### 2022-04-27 airy-resurgence.tex
Invert translation structure scaling parameter

@@
 \subsection{Rescaling of translation structure}
-The coordinate $\xi$ given by $\zeta = m\xi$ defines a new translation structure on $\C$.
-The corresponding frequency variable $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so we have $z = m^{-1} x$.
+Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
+The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
 From the calculation
 \begin{align*}
-\laplace_{\zeta, 0} \hat{\varphi} & = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\hat{\varphi}\;m\,d\xi \\
-& = m \laplace_{\xi, 0} \hat{\varphi},
+\laplace_{\xi, 0} \hat{\varphi} & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\hat{\varphi}\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\hat{\varphi}\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \hat{\varphi}
 \end{align*}
 we learn that
-\[ \laplace_{\xi, 0} \hat{\varphi} = m^{-1} \laplace_{\zeta, 0} \hat{\varphi}. \]
+\[ \laplace_{\xi, 0} \hat{\varphi} = \mu\,\laplace_{\zeta, 0} \hat{\varphi}. \]
+Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
 \section{Shifting integro-differential equations}\label{shifting}

### 2022-04-27 airy-resurgence.tex
Note Laplce transform fiber shorthand
Also, drop the old extra-dry definition of a slight function.

@@
 where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
+\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
 
@@
 Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textbf{(Sternin \& Shatalov)}.} that
+For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
 \[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\tau > -1$ \textbf{[prove or cite]},
+More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
 \[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
-Exact power law asymptotics relate similarly \textbf{[prove or cite]}:
+Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
 \[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
+\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
 \subsubsection{Action on integral operators}\label{L-int-op}
@@
 \end{proof}
-
-\color{magenta}
-A holomorphic function on an open neighborhood of $\zeta = 0$ defines a germ in $\C\{\zeta\}$.
-A holomorphic function on an open sector $\zeta \in (0, \epsilon)\,e^{i[\theta + (-\delta, \delta)]}$ defines a germ in a ring we'll call $\mathcal{F}_\zeta^\theta$.
-We'll think of $\mathcal{F}_\zeta^\theta$ as an algebra over $\C\{\zeta\}$.
-
-Let's say a germ in $\mathcal{F}_\zeta^\theta$ is {\em slight} if it belongs to the cone generated by the functions $z^\alpha$ with $\alpha \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-\color{black}
 \section{The Airy equation}
@@
 
-\color{magenta}
+\color{DodgerBlue}
 If we'd followed the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we would've arrived at the hypergeometric equation
@@
 This time, though, there's a trick we can use to zero out the inhomogeneity.
-Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.\footnote{\textbf{Explain how to see.}} That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
+Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.\footnote{\textcolor{magenta}{Explain how to see.}} That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
 
@@
 Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textbf{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
 \begin{center}
@@
 
-It happens\footnote{\textbf{Veronica:} This comes from \cite[equation~15.4.14]{dlmf}.} that for our desired branch of $u$,
+It happens\footnote{\textcolor{magenta}{Veronica:} This comes from \cite[equation~15.4.14]{dlmf}.} that for our desired branch of $u$,
 \[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
@@
 
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textbf{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
 \[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0), \]

### 2022-04-27 airy-resurgence.tex
Capitalize functions of frequency in comparison with Mariño

@@
 \subsection{Contour argument}\label{contour-argument}
-We can recast integral~\ref{integral:mod-bessel} into $\hat{\C}$ by setting $\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in $\hat{\C}$ and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
+We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $\zeta = 4u^3 - 3u$.
+Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
 \begin{equation}\label{integral:mod-bessel-zeta}
@@
 \includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ in $\hat{\C}$.}
+{\small The contour $\gamma_1$ in the $\zeta$ plane.}
 \end{center}
@@
 \subsection{Correspondence with Mari\~{n}o's series}
-Let $f_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $f$ will be written in the variable $z$.
+Let $F_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $F_1$ will be written in the variable $z$.
 
@@
 \Ai(x) & = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} \varphi_1\big(\tfrac{2}{3} z^{-1}\big) \\
-& = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) \\
+& = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) \\
 \Ai(x) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2})
@@
 \begin{align*}
-\tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \\
-\tfrac{\sqrt{3\pi}}{2}\;x^{-3/4} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(\tfrac{2}{3} x^{3/2}) \\
-\tfrac{\sqrt{3\pi}}{2}\;\big(\tfrac{3}{2} z)^{-1/2} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(z) \\
-\sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} f_1\big(\tfrac{3}{2} z\big) & = K(z) \\
-\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} f_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = \hat{K}(\zeta) \\
+\tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;x^{-3/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;\big(\tfrac{3}{2} z)^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} F_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = \hat{K}(\zeta) \\
 \sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} \hat{f}_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = \hat{K}(\zeta) \\

### 2022-04-27 airy-resurgence.tex
Hats off!
This should bring `airy-resurgence` in line with the new convention.

@@
 Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
-The Laplace transform in $\zeta$ turns a function $\hat{\varphi}$ on $\C$ into a function $\laplace_\zeta \hat{\varphi}$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
-\[ \laplace_\zeta \hat{\varphi} \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta, \]
+The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
+\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
 where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
@@
 \subsubsection{Action on integral operators}\label{L-int-op}
-When $\hat{\varphi} \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \hat{\varphi}) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \hat{\varphi}.
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
 \end{equation}
 for all integers $n \ge 0$.
-You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \hat{\varphi} = z^{-\lambda} \laplace_{\zeta, a} \hat{\varphi} \]
+You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
 for all $\lambda \in (0, \infty)$.
@@
 \color{violet}
-When $\hat{\varphi}$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
+When $\varphi$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
 \begin{align}\label{id:L-diff}
-\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} & = z^n \laplace_\zeta \hat{\varphi} - \left[ \hat{\varphi}\,z^{n-1} + \hat{\varphi}'\,z^{n-2} + \hat{\varphi}''\,z^{n-3} + \ldots + \hat{\varphi}^{(n-1)} \right]_{\zeta = 0} \\
-& = z^n\,\laplace\left( \hat{\varphi} - \left[ \hat{\varphi} + \hat{\varphi}'\,\zeta + \tfrac{\hat{\varphi}''}{2!}\,\zeta^2 + \ldots + \tfrac{\hat{\varphi}^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right).
-\nonumber
+\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi & = z^n \laplace_\zeta \varphi - \left[ \varphi\,z^{n-1} + \varphi'\,z^{n-2} + \varphi''\,z^{n-3} + \ldots + \varphi^{(n-1)} \right]_{\zeta = 0} \\
+& = z^n\,\laplace\left( \varphi - \left[ \varphi + \varphi'\,\zeta + \tfrac{\varphi''}{2!}\,\zeta^2 + \ldots + \tfrac{\varphi^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right). \nonumber
 \end{align}
@@
 Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
-Identity~\ref{id:L-diff} is particularly simple when $\hat{\varphi}$ has a {\em fractional power singularity} at $\zeta = 0$.
-By this, I mean that $\hat{\varphi}$ can be written as $\hat{\varphi}_\text{frac} + \hat{\varphi}_\text{reg}$, where $\hat{\varphi}_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\hat{\varphi}_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
+Identity~\ref{id:L-diff} is particularly simple when $\varphi$ has a {\em fractional power singularity} \textcolor{magenta}{[new terminology: when $\varphi$ is {\em slight}]} at $\zeta = 0$.
+By this, I mean that $\varphi$ can be written as $\varphi_\text{frac} + \varphi_\text{reg}$, where $\varphi_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\varphi_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
 Under this condition, all the initial value terms in the identity vanish, leaving
-\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \hat{\varphi} = z^n \laplace_\zeta \hat{\varphi}. \]
+\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi = z^n \laplace_\zeta \varphi. \]
 \color{black}
@@
 \begin{align*}
-\laplace_{\zeta, a} \hat{\varphi} & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\hat{\varphi}\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\hat{\varphi}\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\hat{\varphi}\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \hat{\varphi},
+\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
 \end{align*}
 we learn that
-\[ \laplace_{\zeta_\alpha, 0} \hat{\varphi} = e^{\alpha z} \laplace_{\zeta, \alpha} \hat{\varphi}. \]
+\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
 \subsection{Rescaling of translation structure}
@@
 \begin{align*}
-\laplace_{\xi, 0} \hat{\varphi} & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\hat{\varphi}\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\hat{\varphi}\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \hat{\varphi}
+\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \varphi
 \end{align*}
 we learn that
-\[ \laplace_{\xi, 0} \hat{\varphi} = \mu\,\laplace_{\zeta, 0} \hat{\varphi}. \]
+\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
 Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
@@
 As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$.
-It'll be helpful to pull out the exponential decay factor and work instead with the function $\kappa$ defined by $K = e^{-z} \kappa$.
-Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $\kappa$ satisfies the equation
+It'll be helpful to pull out the exponential decay factor and work instead with the function $K_1$ defined by $K = e^{-z} K_1$.
+Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $K_1$ satisfies the equation
 \begin{equation}\label{eqn:shifted-mod-bessel}
@@
 \subsubsection{A good try at $\zeta = 0$}
-Let's try to find a function $\hat{K}_0$ with $K = \laplace_\zeta \hat{K}_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\hat{\varphi}$ satisfies the equation
+Let's try to find a function $k_0$ with $K = \laplace_\zeta k_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\varphi$ satisfies the equation
 \begin{equation}%%\label{eqn:spatial-mod-bessel}
-\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0,
+\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0,
 \end{equation}
-its Laplace transform $\varphi = \laplace_\zeta \hat{\varphi}$ satisfies the equation
+its Laplace transform $\varphi = \laplace_\zeta \varphi$ satisfies the equation
 \begin{align*}
-\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) + 3\big({-\tfrac{\partial}{\partial z}}\big)\big[z\varphi - \hat{\varphi}\big]_{\zeta = 0} + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big(z^2 \varphi - \big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}\Big) - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
+\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) + 3\big({-\tfrac{\partial}{\partial z}}\big)\big[z\varphi - \varphi\big]_{\zeta = 0} + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
+\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
 \end{align*}
@@
 \begin{equation}\label{eqn:inhomog-mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\big[\hat{\varphi}\,z + \hat{\varphi}'\big]_{\zeta = 0}.
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\big[\varphi\,z + \varphi'\big]_{\zeta = 0}.
 \end{equation}
-Since we want $\laplace_\zeta \hat{K}_0$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $\hat{K}_0$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
-Unfortunately, this would force $\hat{K}_0$ to be zero.
+Since we want $\laplace_\zeta k_0$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $k_0$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
+Unfortunately, this would force $k_0$ to be zero.
 \color{black}
@@
 \subsubsection{Success at $\zeta = 1$}\label{spatial-success}
-Let's try instead to find a function $\hat{K}_1$ with $K = \laplace_{\zeta, 1} \hat{K}_1$ \textcolor{magenta}{[This would be called $K_1$ in our new notation.]}.
-Define a new coordinate $\zeta_1$ on $\hat{\R}$ so that $\zeta = 1 + \zeta_1$.
+Let's try instead to find a function $k_1$ with $K = \laplace_{\zeta, 1} k_1$ \textcolor{magenta}{[This would be called $K_1$ in our new notation.]}.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
 Since
 \begin{align*}
-\laplace_{\zeta_1, 0} \hat{K}_1 & = e^z \laplace_{\zeta, 1} \hat{K}_1 \\
+\laplace_{\zeta_1, 0} k_1 & = e^z \laplace_{\zeta, 1} k_1 \\
 & = e^z K \\
-& = \kappa,
+& = K_1,
 \end{align*}
-we want $\laplace_{\zeta_1} \hat{K}_1$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
+we want $\laplace_{\zeta_1} k_1$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
 \begin{equation}\label{eqn:shifted-spatial-mod-bessel}
-\left[\zeta_1(\zeta_1 + 2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(\zeta_1 + 1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+\left[\zeta_1(\zeta_1 + 2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(\zeta_1 + 1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0.
 \end{equation}
-If $\hat{\varphi}$ satisfies equation~\ref{eqn:shifted-spatial-mod-bessel}, $\laplace_{\zeta_1} \hat{\varphi}$ will satisfy an inhomogeneous version of equation~\ref{eqn:shifted-mod-bessel}, analogous to equation~\ref{eqn:inhomog-mod-bessel}.
+If $\varphi$ satisfies equation~\ref{eqn:shifted-spatial-mod-bessel}, $\laplace_{\zeta_1} \varphi$ will satisfy an inhomogeneous version of equation~\ref{eqn:shifted-mod-bessel}, analogous to equation~\ref{eqn:inhomog-mod-bessel}.
 This time, though, there's a trick we can use to zero out the inhomogeneity.
@@
 
-Following this plan, let's find $\hat{K}_1$ explicitly.
-Defining another coordinate $\xi$ on $\hat{\R}$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
+Following this plan, let's find $k_1$ explicitly.
+Defining another coordinate $\xi$ on $\C$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
 \begin{equation}\label{eqn:hypergeom}
-\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \hat{\varphi} = 0.
+\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0.
 \end{equation}
 The hypergeometric function
-\[ \hat{g}_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
+\[ g_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
 satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
-\[ \hat{f}_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
+\[ f_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
 which is a holomorphic multiple of $\xi^{-1/2}$ near $\xi = 0$.
-By the argument above, $f_0 = \laplace_{\zeta_1} \hat{f}_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
-This suggests that a constant multiple of $\hat{f}_0$ is our desired $\hat{K}_1$.
+By the argument above, $F_0 = \laplace_{\zeta_1} f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
+This suggests that a constant multiple of $f_0$ is our desired $k_1$.
 The power series~\cite[equation~15.2.1]{dlmf}
-\[ \hat{f}_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
+\[ f_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
 converges near $\xi = 0$, showing that
-\[ \hat{f}_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
+\[ f_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
 In terms of $\zeta_1$, we have
-\[ \hat{f}_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
+\[ f_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
 Using the decay properties from Section~\ref{reg-decay}, we deduce that
-\[ f_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
-Since we know that $f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $f_0$ is a constant multiple of $\kappa$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
-Comparing with series~\ref{bessel-asymp}, we see that $\kappa = \tfrac{i}{2}\,f_0$.
-We conclude that $\kappa = \laplace_{\zeta_1} \hat{K}_1$ for
-\[ \hat{K}_1 = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+\[ F_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
+Since we know that $F_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $F_0$ is a constant multiple of $K_1$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
+Comparing with series~\ref{bessel-asymp}, we see that $K_1 = \tfrac{i}{2}\,F_0$.
+We conclude that $K_1 = \laplace_{\zeta_1} k_1$ for
+\[ k_1 = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
 \color{black}
@@
 
-In addition to the solutions $\hat{g}_1$ and $\hat{f}_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
+In addition to the solutions $g_1$ and $f_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
 \begin{alignat*}{2}
-\hat{g}_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
-\hat{f}_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
+g_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
+f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
 \end{alignat*}
@@
 The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0), \]
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_0), \]
 so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (\hat{g}_1 + \hat{g}_0)\;d\zeta. \]
-The solution $\hat{g}_1$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $\hat{g}_0$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,\hat{f}_0$,
+\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_0)\;d\zeta. \]
+The solution $g_1$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
+The solution $g_0$, in contrast, is non-meromorphic at $\zeta = 1$.
+Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,f_0$,
 as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
@@
 \begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} \hat{f}_0\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} \hat{f}_0\;d\zeta \\
-\kappa & = \tfrac{i}{2} \laplace_{\zeta_1} \hat{f}_0,
+K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} f_0\;d\zeta \\
+e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} f_0\;d\zeta \\
+K_1 & = \tfrac{i}{2} \laplace_{\zeta_1} f_0,
 \end{align*}
@@
 \subsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\ref{eqn:mod-bessel} with the solution $\hat{g}_0$ of equation~\ref{eqn:hypergeom}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(\hat{g}_1 + \hat{g}_0). \]
-The solution $\hat{g}_1$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+Section~\ref{contour-argument} associates the solution $K$ of equation~\ref{eqn:mod-bessel} with the solution $g_0$ of equation~\ref{eqn:hypergeom}, which contributes the pole at $\zeta = 1$ of
+\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_0). \]
+The solution $g_1$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
 
 To express this other solution as a Laplace transform, following the method of Section~\ref{spatial-success}, we would use the solution
-\[ \hat{f}_1 = (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
+\[ f_1 = (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
 of equation~\ref{eqn:hypergeom}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
@@
 \begin{align*}
-\hat{g}_1 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-\hat{g}_0 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
+g_1 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
+g_0 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
 \end{align*}
@@
 \begin{alignat*}{2}
-\hat{f}_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-\hat{f}_0 &\;=\:& \xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
+f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
+f_0 &\;=\:& \xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
 \end{alignat*}
@@
 \begin{alignat*}{3}
-\hat{f}_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,\hat{g}_1 &\;+\;& \tfrac{1}{2}\,\hat{f}_0 \\
-\hat{f}_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,\hat{g}_0 &\;+\;& \tfrac{1}{2}\,\hat{f}_1.
+f_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,g_1 &\;+\;& \tfrac{1}{2}\,f_0 \\
+f_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_0 &\;+\;& \tfrac{1}{2}\,f_1.
 \end{alignat*}
 Summing these identities, we see that
-\[ \hat{g}_1 + \hat{g}_0 = \tfrac{\sqrt{3}}{2}\,(\hat{f}_1 + \hat{f}_0), \]
+\[ g_1 + g_0 = \tfrac{\sqrt{3}}{2}\,(f_1 + f_0), \]
 giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(\hat{f}_1 + \hat{f}_0). \]
+\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_0). \]
 \subsection{Correspondence with Mari\~{n}o's series}
@@
 \sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
-\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} F_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = \hat{K}(\zeta) \\
-\sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} \hat{f}_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = \hat{K}(\zeta) \\
--\tfrac{1}{3\sqrt{2}}\;\left[\zeta^{-1/2}\right] * \hat{f}_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = \hat{K}(\zeta) \\
+\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} F_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = k(\zeta) \\
+\sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
+-\tfrac{1}{3\sqrt{2}}\;\left[\zeta^{-1/2}\right] * f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
 \end{align*}

### 2022-05-02 airy-resurgence.tex
Sketch Airy-Lucas basics

@@
 \color{black}
+\section{The Airy-Lucas equation}
+\subsection{Basics}
+The Airy-Lucas equation is
+\begin{equation}\label{eqn:airy-lucas}
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
+\end{equation}
+with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+\subsection{Rewriting as a \textcolor{DarkCyan}{modified Bessel (?)} equation}
+We can distill the most interesting parts of the Airy-Lucas function by writing
+\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{\textcolor{DarkCyan}{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
+where
+\begin{equation}
+K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
+\end{equation}
+Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
+\begin{equation}%%\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\textcolor{DarkCyan}{\tfrac{m}{n} (?)}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{\textcolor{DarkCyan}{m/n}}$.
+
+Like we did in equation~\ref{eqn:reg-mod-bessel}, we can rewrite the modified Bessel equation above as
+\begin{equation}%%\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\textcolor{DarkCyan}{\tfrac{m}{n}}\big)^2 z^{-2} \right] \varphi = 0.
+\end{equation}
 \section{Sketches}

### 2022-05-10 airy-resurgence.tex
Sketch higher Airy basics

@@
 \end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
+Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
 \begin{equation}%%\label{eqn:mod-bessel}
@@
 \left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\textcolor{DarkCyan}{\tfrac{m}{n}}\big)^2 z^{-2} \right] \varphi = 0.
+\end{equation}
+\section{The higher Airy equation}
+\subsection{Basics}
+The higher Airy equation is
+\begin{equation}\label{eqn:airy-lucas}
+\left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
+\end{equation}
+with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+
+\color{Peru}
+With
+\begin{align*}
+z & = (-1)^{n-1} \tfrac{n-1}{n} y^{n/(n-1)} & w & = (-1)^n (n-1) y^{1/(n-1)} u,
+\end{align*}
+we have
+\begin{align*}
+\widetilde{\Ai}^{(k)}_n(y) & = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w^n - yw\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \left(w^{n-1} - ny\right)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \big((n-1)^{n-1} yu^{n-1} - ny\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}yw \big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[(-1)^n \tfrac{n-1}{n} y^{n/(n-1)} u\big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,dw \\
+& = (-1)^n (n-1) \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+& = (-1)^n (n-1) \frac{\exp\left(\pi ik \big(1 - \tfrac{1}{n-1}\big)\right)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+& = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+\end{align*}
+\color{black}
+\[ \widetilde{\Ai}^{(k)}_n(y) = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\, \]
+where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+\subsection{Rewriting as a \textcolor{magenta}{(???)} equation}
+We can distill the most interesting parts of the hyper-Airy function by writing
+\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
+where
+\begin{equation}
+K(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
+\end{equation}
+Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
+\begin{equation}%%\label{eqn:mod-bessel}
+\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z \big({-}\tfrac{\partial}{\partial z}\big) - c_0 \right] \varphi = 0,
+\end{equation}
+or equivalently
+\begin{equation}%%\label{eqn:mod-bessel}
+\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z^{3-n} \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z^{2-n} \big({-}\tfrac{\partial}{\partial z}\big) - c_0 z^{1-n} \right] \varphi = 0,
 \end{equation}

### 2022-05-13 airy-resurgence.tex
Higher Airy scratch work
Improve coefficient calculation tools
Pull out falling factorials
Big thanks to Peter Taylor from MathOverflow.

@@
 \usepackage{amsthm}
+\usepackage{eqnarray}
 \usepackage{graphicx}
@@
 \end{equation}
+\color{DarkCyan}
 Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
 \begin{equation}%%\label{eqn:mod-bessel}
-\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z \big({-}\tfrac{\partial}{\partial z}\big) - c_0 \right] \varphi = 0,
+\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{n-3} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-2)} z \big({-}\tfrac{\partial}{\partial z}\big) - c_n^{(n-1)} \right] \varphi = 0,
 \end{equation}
@@
 \begin{equation}%%\label{eqn:mod-bessel}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z^{3-n} \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z^{2-n} \big({-}\tfrac{\partial}{\partial z}\big) - c_0 z^{1-n} \right] \varphi = 0,
+\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-2)} z^{-(n-2)} \big({-}\tfrac{\partial}{\partial z}\big) - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
 \end{equation}
+The coefficients are straightforward to calculate, but their pattern is hard to describe. Peter Taylor suggests writing
+\[ c_n^{(k)} = (n+1)^{\underline{k+2}}\;R^{(k)} / n^k, \]
+for $k > 1$, where the underlined power denotes the falling factorial. Then we get
+\begin{equationarray*}{*{11}{c}}
+R^{(2)} & = & \tfrac{1}{24} \\
+R^{(3)} & = & \tfrac{1}{48} n \\
+R^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
+R^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
+R^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440} \end{equationarray*}
+Searching for 580608 in the OEIS reveals that the leading coefficients are ``fractions appearing in a generalization of Carleman's inequality,'' listed in the OEIS as {\tt A249276} and {\tt A249277}.
+\paragraph{Old scratch work}
+For now, we can at least say with confidence that
+\begin{align*}
+c_3^{(1)} & = 1 & c_{n+1}^{(1)} & = \frac{n}{n-1}\,c_{n}^{(1)} & c_n^{(1)} & = \frac{1}{n} \left(\begin{matrix} n \\ 2 \end{matrix}\right)
+\end{align*}
+and
+\[ c_n^{(2)} = \frac{1}{n^2} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \]
+and
+\begin{align*}
+c_n^{(3)} & = \frac{5}{2} \cdot \frac{1}{n^2} \left(\begin{matrix} n+1 \\ 5 \end{matrix}\right) \\
+c_4^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-5)(n-2) = \frac{3 \cdot 2}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) = \frac{1 \cdot 1}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \\
+c_5^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-5)(n-3) = \frac{5 \cdot 2}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) = \frac{3 \cdot 1}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \sim \frac{3}{1} \cdot \frac{6}{3} \\
+c_6^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-7)(n-3) = \frac{5 \cdot 3}{n^3} \left(\begin{matrix} n+2 \\ 4 \end{matrix}\right) = \frac{3 \cdot 2}{(n-1)^2} \frac{(n+2)(n+1)n}{4!} \sim \frac{2}{1} \cdot \frac{7}{4} \\
+c_7^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-7)(n-4) = \frac{7 \cdot 3}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{5}{3} \cdot \frac{8}{5} \\
+c_8^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-9)(n-4) = \frac{7 \cdot 4}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{3}{2} \cdot \frac{9}{6} \\
+c_9^{(3)} & = \frac{1}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) (2n-9)(n-5) = \frac{9 \cdot 4}{n^3} \left(\begin{matrix} n+1 \\ 4 \end{matrix}\right) \sim \frac{7}{5} \cdot \frac{10}{7} \\
+n^2 c_{n+1}^{(3)} & = \frac{n+3}{n-2} (n-1)^2 c_n^{(3)} \\
+c_{n+1}^{(3)} & = \frac{n+3}{n-2} \left(\frac{n-1}{n}\right)^2 c_n^{(3)} \\
+(n+1)^3 c_{n+1}^{(3)} & = \frac{n+3}{n-2} \left(\frac{n-1}{n}\right)^2 \left(\frac{n+1}{n}\right)^3 n^3 c_n^{(3)} = \frac{(n+3)(n+1)}{n(n-2)} \left(\frac{n^2 - 1}{n^2}\right)^2 \\
+c_4^{(3)} & = \frac{5}{32}
+\end{align*}
+and
+\begin{align*}
+c_n^{(n-1)} & = \frac{1}{n^{n-1}}\,(n-2)(2n-3)(3n-4) \cdots [(n-2)n - (n-1)] \\
+& = \frac{1}{n} \left(1 - \frac{2}{n}\right) \left(2 - \frac{3}{n}\right) \left(3 - \frac{4}{n}\right) \cdots \left((n-2) - \frac{n-1}{n}\right).
+\end{align*}
+\color{black}
 \section{Sketches}

### 2022-05-14 airy-resurgence.tex
Clean up sketch of higher Airy coefficients

--- 2022-05-10 airy-resurgence.tex
@@
 \begin{equation}%%\label{eqn:mod-bessel}
-\left[ z^{n-1} \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{n-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z \big({-}\tfrac{\partial}{\partial z}\big) - c_0 \right] \varphi = 0,
+\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
 \end{equation}
-or equivalently
-\begin{equation}%%\label{eqn:mod-bessel}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_{n-2} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - \ldots - c_2 z^{3-n} \big({-}\tfrac{\partial}{\partial z}\big)^2 - c_1 z^{2-n} \big({-}\tfrac{\partial}{\partial z}\big) - c_0 z^{1-n} \right] \varphi = 0,
-\end{equation}
+The sub-leading coefficients are the triangular numbers
+\[ c_n^{(1)} = \frac{n(n-1)}{2}. \]
+\color{DarkCyan}
+The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
+\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,(n+1)^{\underline{k+2}} \]
+in terms of the polynomials
+\begin{equationarray*}{*{11}{c}}
+b_n^{(2)} & = & \tfrac{1}{24} \\
+b_n^{(3)} & = & \tfrac{1}{48} n \\
+b_n^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
+b_n^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
+b_n^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440}. \end{equationarray*}
+Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}.
+They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
+\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
+which tells us that
+\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots.
+\]
+The last coefficient can be written as
+\[ c_n^{(n-1)} = \left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, \]
+giving
+\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
+\color{black}
 \section{Sketches}

### 2022-05-16 draft2.tex
Remove some hats

--- 2022-04-12 draft2.tex
@@
 \begin{definition}
-A holomorphic function $\hat{f}$ in an open disk $D\subset \C_{\zeta}$ has a simple singularity at $\omega$, adherent to $D$, if there exist $\alpha\in\C$ and a germs of analytic functions at
-the origin $\hat{\Phi}(\zeta)\in\C\lbrace\zeta\rbrace$, such that
-\begin{equation}
-\hat{f}(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\log(\zeta-\omega)\hat{\phi}(\zeta-\omega)+\text{hol. fct.}
-\end{equation}
-for all $\zeta\in D$ close enough to $\omega$. The constant $\alpha$ is called the residuum and $\hat{\phi}$ the minor.
+A function $f$ defined in an open disk $D\subset \C_{\zeta}$ has a simple singularity at $\omega$, adherent to $D$, if there exist $\alpha\in\C$ and a germ of analytic functions at
+the origin $\hat{\phi}(\zeta)\in\C\lbrace\zeta\rbrace$, such that
+\begin{equation}
+f(\zeta)=\frac{\alpha}{2\pi i(\zeta-\omega)}+\frac{1}{2\pi i}\text{Log}(\zeta-\omega)\hat{\phi}(\zeta-\omega)+\text{hol. fct.}
+\end{equation}
+for all $\zeta\in D$ close enough to $\omega$.
+The constant $\alpha$ is called the residuum and $\hat{\phi}$ the minor.
+$\mathrm{Log}(\zeta)$ is the principal branch of $\log(\zeta)$ in $D$; different branches of $\log(\zeta)$ differs by a multiple of $\hat{\phi}(\zeta)$, hence they define the same singularity $\overset{\triangledown}{\phi} $.
 \end{definition}
@@
 \begin{equation}
-\hat{\phi}(\zeta)=\hat{f}(\zeta+\omega)-\hat{f}(\zeta e^{-2\pi i}+\omega)
+\hat{\phi}(\zeta)={f}(\zeta+\omega)-{f}(\zeta e^{-2\pi i}+\omega)
 \end{equation}
@@
 Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
-\begin{equation}
+\begin{equation}\label{exp-int}
 I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
@@
 \item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
-\begin{align*}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta) & = \partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) \\
-& = \textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
-\end{align*}
+\begin{multline}\label{formula1}
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\end{multline}
 where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
@@
 
-\section{Airy exponential integral}
+\section{Airy exponential integral: Stokes constants using fractional derivative formula and Borel transform computation}
+
+We study the resurgent properties of the Airy function $\mathrm{Ai}(x)$.
+As in section 3.2 {\tt airy-resurgence}, it is convenient to change coordinates and turn $\mathrm{Ai}(x)$ in exponential integral like \eqref{exp-int}: with the substitution $t=-2ux^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_+} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
+where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression
+
+\[ I_+(z) \defeq \int_{\mathcal{C}_+} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
+
+Since $\mathrm{Ai}(x)$ is a solution of Airy equation, $I(z)$ is a solution of 
+\begin{equation}\label{eq:I}
+I''(z)-\frac{4}{9}I(z)+\frac{I'(z)}{z}-\frac{1}{9}\frac{I(z)}{z^2} = 0.
+\end{equation}
+
+From the general theory of linear ODE, \eqref{eq:I} has a two--parameter formal integral solution $\tilde{I}(z)\in z^{-1/2}\C[\![z^{-1}]\!]$
+
+\begin{equation}
+\tilde{I}(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_{+}(z)+U_2e^{2/3z}z^{-1/2}\tilde{W}_{-}(z)
+\end{equation}
+where $\tilde{W}_+(z)=1+\sum_{n=1}^{\infty}a_{+,n}z^{-n}$ and $\tilde{W}_-(z)=1+\sum_{n=1}^{\infty}a_{-,n}z^{-n}$ are the unique formal solutions of 
+\begin{align}
+\label{eq:w+} \tilde{W}_+''-\frac{4}{3}\tilde{W}_+'+\frac{5}{36}\frac{\tilde{W}_+}{z^2}=0\\
+\label{eq:w-} \tilde{W}_-''+\frac{4}{3}\tilde{W}_-'+\frac{5}{36}\frac{\tilde{W}_-}{z^2}=0
+\end{align}
+
+Notice that $I_+(z)$ is asymptotic to $U_1e^{-2/3z}z^{-1/2}\tilde{W}_{+}(z)$ as $\Re z\to+\infty$. Recursively, we determine $a_{\pm,n}$: set $a_{\pm,0}=1$, then
+
+\begin{align*}
+a_{\pm, n+1}=\mp\frac{3}{4}\left(n+\frac{1}{6}\right)\left(n+\frac{5}{6}\right)\frac{1}{n+1}a_{\pm,n} \, \qquad n\geq 0
+\end{align*}
+hence $a_{\pm,n}=\frac{1}{2\pi}(\mp 1)^n\left(\frac{3}{4}\right)^{n}\Gamma(n+\tfrac{1}{6})\Gamma(n+\tfrac{5}{6})\frac{1}{n!}$ for $n\geq 1$ and they are factorially divergent.
+Thus, $\tilde{W}_{\pm}(z)$ are Gevrey-1 series.
+
+We now compute the  Borel transform $\tilde{w}_{\pm}(\zeta)=\mathcal{B}\tilde{W}_{\pm}$: it can be done in different ways, on one hand we can compute the Borel transform of $\tilde{W}_{\pm}$ via their explicit formal expansion, namely
+
+\begin{align*}
+\tilde{w}_{\pm}(\zeta)&=\delta+\sum_{n\geq 1}a_{\pm,n}\frac{\zeta^{n-1}}{(n-1)!}=\delta+\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma\left(n+\frac{7}{6}\right)\Gamma\left(n+\frac{11}{6}\right)}{(n+1)!}\frac{\zeta^n}{n!}\\
+&=\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)
+\end{align*}
+On the other hand, we can look at the Borel transform of the ODEs \eqref{eq:w+}\eqref{eq:w-} and solve them. Thanks to properties of $\mathcal{B}$, $\tilde{w}_{\pm}(\zeta)$ are solution of
+
+\begin{align*}
+&\zeta^2\tilde{w}_{\pm}(\zeta)\pm\frac{4}{3}\zeta\tilde{w}_{\pm}+\frac{5}{36}\zeta\ast\tilde{w}_{\pm}=0\\
+&\zeta^2\tilde{w}_{\pm}(\zeta)\pm\frac{4}{3}\zeta\tilde{w}_{\pm}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\tilde{w}_{\pm}(\zeta')d\zeta'=0
+\end{align*}
+
+\color{Plum}
+Differentiating twice, we get the following equations
+
+\begin{equation}\label{eq:hypergeomtric w}
+\zeta\left(\pm\frac{4}{3}+ \zeta\right)\tilde{w}_{+}''+\left(\pm\frac{8}{3}+4\zeta\right)\tilde{w}_+'+\frac{77}{36}\tilde{w}_{+}=0 
+\end{equation}
+
+which after the change of coordinates $u=\mp\frac{3}{4}\zeta$ they are hypergeometric equations with parameters $\left(\frac{7}{6}, \frac{11}{6}; 2\right)$.
+However, being a solution of \eqref{eq:hypergeomtric w} is not equivalent to being a solution of the integral equation; it holds only up to constants.
+In our example, the constant is given by $\delta$, hence we conclude
+
+\begin{align}
+\label{hat+}\hat{w}_+(\zeta)=\delta+\mathit{c}_1 \, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)\\
+\label{hat-}\hat{w}_-(\zeta)=\delta+\mathit{c}_2 \, {}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)
+\end{align}
+for some constants $\mathit{c}_1, \mathit{c}_2\in\C$.
+
+\color{black}
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula ~\eqref{int:deriv-formula}.
+This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
+Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
+%In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
+\begin{lemma}\label{claim 2}
+The following formula holds true
+\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
+for any $\zeta\in [2/3,+\infty)$.
+\end{lemma}
+\begin{proof}
+In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
+Hence,
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
+\end{align*}
+Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
+
+\begin{lemma}\label{claim 3}
+For any $\zeta\in (-\infty,-2/3]$
+\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
+\end{lemma}
+\begin{proof}
+Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
+\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
+& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+
+We can now compute the Stokes factors from the analytic continuation of $\hat{w}_{\pm}(\zeta)$ at the branch cut: it is a well-known fact that Gauss hypergeometric functions ${}_2F_1(a,b;c;x)$ have branch cut singulairty at $x=1$ and their analytitc continuation is explicitly computed as in \cite{DLMF}~15.2.3.
+In our example, $\hat{w}_{\pm}(\zeta)$ have singularities respectively at $\zeta=\mp\tfrac{2}{3}$, and their analytic continuation is respectively: for $\zeta<-\tfrac{4}{3}$
+
+\begin{align*}
+\left(-i\frac{\sqrt{\pi}}{2}\right)\left[\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)\right]&=i\frac{\sqrt{\pi}}{2}\frac{5}{48}\left(-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 1}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n\right) \\
+&=i\frac{\sqrt{\pi}}{2}\frac{5}{48}\left(\frac{36}{5}i\sum_{n\geq 1}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^{n-1}\right)  \\
+&=-\frac{\sqrt{\pi}}{2}\frac{5}{48}\frac{36}{5}\sum_{n\geq 0}\frac{(5/6)_{n+1}(1/6)_{n+1}}{\Gamma(n+1)(n+1)!}(1+\frac{3}{4}\zeta)^{n}  \\
+&=-\frac{\sqrt{\pi}}{2}\frac{5}{48}\frac{36}{5}\frac{\Gamma(11/6)\Gamma(7/6)}{\Gamma(1/6)\Gamma(5/6)}\sum_{n\geq 0}\frac{(11/6)_{n}(7/6)_{n}}{n!\,\Gamma(n+2)}(1+\frac{3}{4}\zeta)^{n}  \\
+&=-\frac{\sqrt{\pi}}{2}\frac{5}{48}\sum_{n\geq 0}\frac{(11/6)_{n}(7/6)_{n}}{\Gamma(n+2) n!}(1+\frac{3}{4}\zeta)^{n}  \\
+&=\mathbf{+1}\left(-\frac{\sqrt{\pi}}{2}\right)\hat{w}_{-}(\zeta+\tfrac{4}{3}) 
+\end{align*}
+Analogously, the analytic continuation of $\hat{w}_-(\zeta)$  as $\zeta\in [\frac{4}{3},+\infty)$ is 
+\begin{align*}
+\left(-\frac{\sqrt{\pi}}{2}\right)\left[\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)\right]&=-\frac{\sqrt{\pi}}{2}\frac{5}{48}\left(-\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 1}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n\right) \\
+&=-\frac{\sqrt{\pi}}{2}\frac{5}{48}\left(\frac{36}{5}i\sum_{n\geq 1}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^{n-1}\right) \\
+&=-i\frac{\sqrt{\pi}}{2}\frac{5}{48}\frac{36}{5}\sum_{n\geq 0}\frac{(5/6)_{n+1}(1/6)_{n+1}}{\Gamma(n+1)(n+1)!}(1-\frac{3}{4}\zeta)^{n} \\
+&=-i\frac{\sqrt{\pi}}{2}\frac{5}{48}\frac{36}{5}\frac{\Gamma(11/6)\Gamma(7/6)}{\Gamma(1/6)\Gamma(5/6)}\sum_{n\geq 0}\frac{(11/6)_{n}(7/6)_{n}}{n!\,\Gamma(n+2)}(1-\frac{3}{4}\zeta)^{n} \\
+&=-i\frac{\sqrt{\pi}}{2}\frac{5}{48}\sum_{n\geq 0}\frac{(11/6)_{n}(7/6)_{n}}{\Gamma(n+2) n!}(1-\frac{3}{4}\zeta)^{n} \\
+&=\mathbf{-1}\left(-i\frac{\sqrt{\pi}}{2}\right)\hat{w}_{+}(\zeta-\tfrac{4}{3}) 
+\end{align*}
+
+These relations manifest the resurgence property of $\tilde{I}_{\pm}$: \textbf{Add figure}
+
+\begin{prop}
+The functions $\hat{w}_{\pm}(\zeta)$ are simple resurgent functions with Stokes constants respectively $\pm 1$. 
+\end{prop}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{remark}
+The Stokes constants computed form the explicit expression of the Borel transform $\hat{w}_{\pm}$ agree with the prediction of singularity theory.
+Indeed the Airy equation has an irregular singularity at $\infty$, and it corresponds to a \textit{simple singularity} $f\colon(\C^n,0)\to (\C,0)$.
+\textbf{Trova corrispondenza singolarità e equazione differenziale.}
+\end{remark}
+
+\color{Tan}
 By definition,
@@
 \end{equation}  
-where from now on we denote $\tilde{w}_+(z)=\tilde{w}_{(1,0)}(z)$ and $\tilde{w}_-(z)=\tilde{w}_{(0,1)}(z)$. In particular, $\tilde{w}_+(z)$ and $\tilde{w}_-(z)$ are formal solution of 
+where from now on we denote $\tilde{w}_+(z)=\tilde{w}_{(1,0)}(z)$ and $\tilde{w}_-(z)=\tilde{w}_{(0,1)}(z)$. In particular, $\tilde{w}_+(z)$ and $\tilde{w}_-(z)$ are formal solutions of 
 \begin{align}
@@
 %\end{remark}
-
-Our next goal is to prove that the Borel transform of $\tilde{I}(z)$ can be written in terms of $1/f'(f^{-1}(\zeta))$, namely formula \eqref{formula1}.
-It is convenient to consider the two asymptotic formal solutions separately, namely we define
-
-\begin{align}
-\tilde{I}_{-1}(z)\defeq e^{-2/3z}z^{-1/2}\tilde{w}_+(z)=\colon z^{-1/2}\tilde{u}_+(z) \\
-\tilde{I}_{1}(z)\defeq e^{2/3z}z^{-1/2}\tilde{w}_-(z)=\colon z^{-1/2}\tilde{u}_-(z)
-\end{align}
-
-In particular, $\tilde{u}_{\pm}(z)$ are solutions of
-
-\begin{equation}\label{eq:u}
-\tilde{u}''(z)-\frac{4}{9}\tilde{u}(z)+\frac{5}{36}\frac{\tilde{u}(z)}{z^2}=0
-\end{equation}
-
-with asymptotic behaviour $\tilde{u}_\pm(z)\sim O(e^{\pm 2/3 z})$ as $z\to\infty$.
-
-The Borel transforms $\hat{u}_{\pm}(\zeta)$ solve the same equation
-\begin{align*}
-&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\zeta\ast\hat{u}\\
-&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{u}(\zeta')d\zeta'\\
-&\text{taking derivatives is equivalent to} \\
-&(\zeta^2-\frac{4}{9})\hat{u}''(\zeta)+4\zeta\hat{u}'(\zeta)+\frac{77}{36}\hat{u}(\zeta)=0
-\end{align*}
-
-and Mathematica gives the following solutions
-\begin{align*}
-\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
-&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
-&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
-&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
-&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &
-\end{align*}
-Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
-\begin{align*}
-\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\;\hat{w}_+(\zeta)\\
-\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\;\hat{w}_-(\zeta)
-\end{align*}
-
+\color{black}
+\subsubsection{Computing the Borel transform of $\tilde{I}_{\pm}$ using Ecalle's formalism of singularities}
+
+We prove that the Borel transform of $\tilde{I}_{\pm}(z)$ can be computed in terms of $1/f'(f^{-1}(\zeta))$.
+This is a consequence of Ecalle's formalism of singularities, as well as of properties of hypergeometric functions.
+
+%It is convenient to consider the two asymptotic formal solutions separately, namely we define
+
+%\begin{align}
+%\tilde{I}_{-1}(z)\defeq e^{-2/3z}z^{-1/2}\tilde{w}_+(z)=\colon z^{-1/2}\tilde{u}_+(z) \\
+%\tilde{I}_{1}(z)\defeq e^{2/3z}z^{-1/2}\tilde{w}_-(z)=\colon z^{-1/2}\tilde{u}_-(z)
+%\end{align}
+% 
+%In particular, $\tilde{u}_{\pm}(z)$ are solutions of 
+%
+%\begin{equation}\label{eq:u}
+%\tilde{u}''(z)-\frac{4}{9}\tilde{u}(z)+\frac{5}{36}\frac{\tilde{u}(z)}{z^2}=0
+%\end{equation} 
+%
+%with asymptotic behaviour $\tilde{u}_\pm(z)\sim O(e^{\pm 2/3 z})$ as $z\to\infty$. 
+%
+%The Borel transforms $\hat{u}_{\pm}(\zeta)$ solve the same equation
+%\begin{align*}
+%&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\zeta\ast\hat{u}\\
+%&\zeta^2\hat{u}-\frac{4}{9}\hat{u}+\frac{5}{36}\int_0^\zeta(\zeta-\zeta')\hat{u}(\zeta')d\zeta'\\
+%&\text{taking derivatives is equivalent to} \\
+%&(\zeta^2-\frac{4}{9})\hat{u}''(\zeta)+4\zeta\hat{u}'(\zeta)+\frac{77}{36}\hat{u}(\zeta)=0
+%\end{align*}
+%
+%and Mathematica gives the following solutions
+%\begin{align*}
+%\hat{u}(\zeta)&=c_1 \, {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{9}{4}\zeta^2\right) +\frac{3i}{2}\zeta c_2 \, {}_{1}F_{2}\left(\frac{13}{12},\frac{17}{12},\frac{3}{2},\frac{9}{4}\zeta^2\right)= &\\
+%&=c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}}\left({}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}-\frac{3}{4}\zeta\right)- {}_{1}F_{2}\left(\frac{7}{12},\frac{11}{12},\frac{1}{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right) & \text{see DLMF 15.8.27} \\
+%&\qquad +\frac{3i}{2}\zeta c_2 \left(\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{3\zeta\Gamma(-\frac{1}{2})\Gamma(2)}\right)\left( {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}-\frac{3}{4}\zeta\right)-{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},{2},\frac{1}{2}+\frac{3}{4}\zeta\right)\right)  & \text{see DLMF 15.8.28}\\
+%&=\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} -c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}-\frac{3}{4}\zeta\right)  + & \\
+%&\qquad\qquad +\left(c_1\frac{\Gamma(\frac{13}{12})\Gamma(\frac{17}{12})}{2\sqrt{\pi}} +c_2i\frac{\Gamma(\frac{7}{12})\Gamma(\frac{11}{12})}{4\sqrt{\pi}}\right)\, {}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,\frac{1}{2}+\frac{3}{4}\zeta\right) &
+%\end{align*}
+%Since $\hat{u}_+$ has a simple singularity at $\zeta=-2/3$ and $\hat{u}_-$ has a simple singularity at $\zeta=2/3$, we have
+%\begin{align*}
+%\hat{u}_+(\zeta)&=C_1 T_{-\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,-\frac{3}{4}\zeta\right)=C_1 T_{-\tfrac{2}{3}}\;\hat{w}_+(\zeta)\\
+%\hat{u}_-(\zeta)&= C_2 T_{\tfrac{2}{3}}\;{}_{2}F_{1}\left(\frac{7}{6},\frac{11}{6},2,\frac{3}{4}\zeta\right)= C_2 T_{\tfrac{2}{3}}\;\hat{w}_-(\zeta)
+%\end{align*}
+
+As in the proof of Theorem \ref{thm:maxim} (iii), via the change of coordinates $\zeta=f(t)$, we turn the thimble integrals $I_{\pm}(z)$ into an integral on an Hankel contour through the critical values $\pm\frac{2}{3}$
+\begin{equation}\label{eq:Laplace_Hankel}
+I_{\pm}(z)=\int_{\mathcal{C}_{\pm}}e^{-zf}\nu=\int_{\mathcal{H}_{\pm}}e^{-\zeta z}\frac{\nu}{df}\Big\vert_{f^{-1}(\zeta}d\zeta
+\end{equation}  
+where $\mathcal{H}_{\pm}$ is represented in figure \textbf{add figure for Hankel contours}.
+In Ecalle's formalism of singularities (see \textbf{add references}), the right hand side of \eqref{eq:Laplace_Hankel} is a generalized Laplace transform for \textit{majors}, namely
+\begin{equation}
+\frac{\nu}{df}\Big\vert_{f^{-1}(\zeta)}=:\overset{\vee}{\phi}(\zeta)
+\end{equation}
+and it is the same major for both $\overset{\triangledown}{\phi}_+(\zeta)$ and $\overset{\triangledown}{\phi}_-(\zeta)$ even if $\overset{\triangledown}{\phi}_\pm(\zeta)$ are distinct. 
 \begin{lemma}
@@
 \begin{equation}
-{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}\qquad \zeta=\frac{u^3}{3}-u
+\overset{\vee}{\phi}(\zeta)=-\frac{1}{2}\,\, {}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)
 \end{equation}
 \end{lemma}
-\begin{proof}From the special case of hypergeometric function (see 15.4.14 DLMF) we have the following identity:
+\begin{proof} Recall $f(t)=\frac{2}{3}(4u^3-3u)$ and $\nu=dt$, thus 
+\begin{align*}
+\overset{\vee}{\phi}(\zeta)=\frac{\nu}{df}\Big\vert_{f^{-1}(\zeta)}=\frac{dt}{f'(t)dt}\Big\vert_{f^{-1}(\zeta)}=\frac{1}{f'(t)}\Big\vert_{f^{-1}(\zeta)}
+\end{align*}
+
+From the special case of hypergeometric function (see 15.4.14 DLMF) we have the following identity:
 \begin{align*}
@@
 &=\frac{1}{\cos(2y)-2\sin^2(y)} & \\
-&=\frac{1}{1-4\sin^2(y)} & \zeta=2\sin(y)-\frac{8}{3}\sin^3(y)
-\end{align*}
-Therefore, if $u\defeq -2\sin(y)$, we have $\zeta=\frac{u^3}{3}-u=f(u)$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-u^2}=-\frac{1}{f'(u)}\]
+&=\frac{1}{1-4\sin^2(y)} & \zeta=\frac{2}{3}\left(3\sin(y)-4\sin^3(y)\right)
+\end{align*}
+Therefore, if $u= -\sin(y)$, we have $\zeta=\frac{2}{3}\left(4u^3-3u\right)=f(u)$ and \[{}_2F_1\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)=\frac{1}{1-4u^2}=-\frac{2}{f'(u)}=-2\overset{\vee}{\phi}(\zeta)\]
 \end{proof}
 
-Then equations \eqref{formula1} is equivalent to: \textbf{[Now that we've switched to the Riemann-Liouville derivative, the claim that was referenced here no longer involves $\nu/df$.
-The calculation above is still useful, but it should go somewhere else.]}
-
-\begin{claim}\label{claim 2}
-\textbf{[There should be a way to predict the correct normalization of the RHS.]}
-\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,\hat{w}_+(\zeta-2/3), \]
-consistent with Theorem~\ref{thm:maxim}~\eqref{int:deriv-formula}.
-\end{claim}
-\begin{proof}
-With the substitution $t = -2ux^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_+} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
-where $\mathcal{C}_+$ is the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression
-\[ I_+(z) = \int_{\mathcal{C}_+} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
-In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = i \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\textbf{[Check comparison with Mari\~{n}o's result more carefully?]}
-\end{proof}
-Analogously, it can be verified for $\hat{w}_-(\zeta+2/3)$ for $\zeta\in(-\infty,-2/3)$.
-
-\begin{claim}\label{claim 3}
-
-\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,\hat{w}_-(\zeta+2/3), \]
-consistent with Theorem~\ref{thm:maxim}~\eqref{int:deriv-formula}.
-\end{claim}
-\begin{proof}
-As before, with the substitution $t = -2ux^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(x) = x^{1/2}\;\frac{i}{\pi} \int_{x^{-1/2} \mathcal{C}_-} \exp\left[-\tfrac{2}{3}x^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
-where $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. When $x \in [0, \infty)$, this leads to the expression
-\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
-In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,F\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ F\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\,F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\textbf{[Check comparison with Mari\~{n}o's result more carefully?]}
-\end{proof}
-
-In particular, from the previous computations we get the right normalization constants for $\hat{w}_{\pm}(\zeta)$, which allows to compute the Stokes factors from the analytic continuation of $\hat{w}_{\pm}(\zeta)$ at the branch cut: from \cite{DLMF}~15.2.3
-
-\begin{align*}
-\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left[\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)\right]&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left(-\tfrac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\tfrac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\tfrac{3}{4}\zeta)^n\right) &\zeta<-\tfrac{4}{3}\\
-&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i\sum_{n\geq 0}\tfrac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\tfrac{3}{4}\zeta)^{n-1} & \\
-&=-\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i(-\tfrac{3}{4}\zeta-1)^{-1}\left(\tfrac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right)\right)\right) &\\
-&=\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}i \,\,{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right) &\\
-&=\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{1}F_{2}\left(\tfrac{7}{6},\tfrac{11}{6},2,1+\tfrac{3}{4}\zeta\right) & \\
-&=\mathbf{+1}\hat{w}_{-}(\zeta+\tfrac{4}{3}) &
-\end{align*}
-Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
-\begin{align*}
-\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left[\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)\right]&=\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\left(-\tfrac{36}{5}i(\tfrac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\tfrac{3}{4}\zeta)^n\right) & \zeta>\tfrac{4}{3}\\
-&=-\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\tfrac{36}{5}i(\tfrac{3}{4}\zeta-1)^{-1}\left(-\tfrac{5}{144}(-4+3\zeta){}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right)\right)  &\\
-&=i\textcolor{red}{\left(-\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right) &\\
-&=-\textcolor{red}{\left(i\tfrac{\sqrt{\pi}}{8}\tfrac{5}{12}\right)}\,\,{}_{2}F_{1}\left(\tfrac{7}{6},\tfrac{11}{6},2,1-\tfrac{3}{4}\zeta\right) &\\
-&=\mathbf{-1}\hat{w}_{+}(\zeta-\tfrac{4}{3}) &
-\end{align*}
-These relations manifest the resurgence property of $\tilde{I}_{\pm 1}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.
-
-\color{pink}
-\begin{remark}
-$\hat{w}_{+}(\zeta)$ is Laplace summable along the positive real axis, and it can be analyticaly continued on $\C\setminus -\frac{4}{3}\R_{\leq 0}$ with (see 15.2.3 DLMF)
-\begin{align*}
-\hat{w}_+(\zeta+i0)-\hat{w}_+(\zeta-i0)&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^n &\zeta<-\frac{4}{3}\\
-&=\frac{36}{5}i\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1+\frac{3}{4}\zeta)^{n-1} & \\
-&=-\frac{36}{5}i(-\frac{3}{4}\zeta-1)^{-1}\left(\frac{5}{144} (4 + 3 \zeta)\left(1+{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right)\right)\right) &\\
-&=\mathbf{i}\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1+\frac{3}{4}\zeta\right) &\\
-&=\mathbf{i}\hat{w}_{-}(\zeta+\frac{4}{3}) &
-\end{align*}
-Anolougusly, $\hat{w}_-(\zeta)$ is Laplace summable along the negative real axis, and it jumps across the branch cut $\frac{4}{3}\R_{\geq 0}$ as 
-\begin{align*}
-\hat{w}_-(\zeta+i0)-\hat{w}_-(\zeta-i0)&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\sum_{n\geq 0}\frac{(5/6)_n(1/6)_n}{\Gamma(n)n!}(1-\frac{3}{4}\zeta)^n & \zeta>\frac{4}{3}\\
-&=\frac{36}{5}i(\frac{3}{4}\zeta-1)^{-1}\left(-\frac{5}{144}(-4+3\zeta){}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right)\right)  &\\
-&=-\mathbf{i}\pi\,\,{}_{1}F_{2}\left(\frac{7}{6},\frac{11}{6},2,1-\frac{3}{4}\zeta\right) &\\
-&=-\mathbf{i}\hat{w}_{+}(\zeta-\frac{4}{3}) &
-\end{align*}
-These relations manifest the resurgence property of $\tilde{I}$, indeed near the singularities in the Borel plane of either $\hat{w}_+$ or $\hat{w}_-$, $\hat{w}_-$ and $\hat{w}_+$ respectively contribute to the jump of the former solution.
-\end{remark}
+We compute the singularities $\overset{\triangledown}{\phi}_\pm(\zeta)$: notice that $\overset{\vee}{\phi}(\zeta)$ can be splitted in two hypergeomtric functions
+
+\begin{align*}
+\overset{\vee}{\phi}(\zeta)&=-\frac{1}{2}{}_2F_2\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)\\
+&=-\frac{1}{2}\frac{\Gamma(5/6)\Gamma(7/6)}{2\Gamma(1/2)\Gamma(3/2)}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3}{4}\zeta\right)\right]\\
+&=-\frac{1}{6}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3}{4}\zeta\right)\right]
+\end{align*}  
+ and the two hypergeometric functions ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}\mp\frac{3}{4}\zeta\right)$ are respectively singular at $\mp\frac{2}{3}$ and holomorphic at $\pm\frac{2}{3}$.
+Therefore, we can compute the minors of $\overset{\triangledown}{\phi}_{\pm}$
+
+\begin{align*}
+\hat{\phi}_{+}(\zeta)&\defeq\overset{\vee}{\phi}\big(\zeta-\frac{2}{3}\big)-\overset{\vee}{\phi}\big(e^{-2\pi i}(\zeta-\frac{2}{3})\big)\\
+&=-\frac{1}{6}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1-\frac{3}{4}\zeta\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{3}{4}\zeta\right)\right]+\\
+&\quad + \frac{1}{6}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};(1-\frac{3}{4}\zeta)e^{-2\pi i}\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{3}{4}\zeta e^{-2\pi i}\right)\right]\\
+&=-\frac{1}{6}\frac{2\pi i}{\Gamma(2/3)\Gamma(4/3)}\left(-\frac{3}{4}\zeta\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{3}{4}\zeta\right)\\
+&=-\frac{\sqrt{3}}{2}i\left(-\frac{3}{4}\zeta\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{3}{4}\zeta\right)\\
+&=\textcolor{red}{-}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};\frac{3}{4}\zeta\right)
+\end{align*}
+
+\begin{align*}
+\hat{\phi}_{-}(\zeta)&\defeq\overset{\vee}{\phi}\big(\zeta+\frac{2}{3}\big)-\overset{\vee}{\phi}\big(e^{-2\pi i}(\zeta+\frac{2}{3})\big)\\
+&=-\frac{1}{6}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{3}{4}\zeta\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1+\frac{3}{4}\zeta\right)\right]+\\
+&\quad +\frac{1}{6}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{3}{4}\zeta e^{-2\pi i}\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};(1+\frac{3}{4}\zeta )e^{-2\pi i}\right)\right]\\
+&=-\frac{1}{6}\frac{2\pi i}{\Gamma(2/3)\Gamma(4/3)}\left(\frac{3}{4}\zeta\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\\
+&=-\frac{\sqrt{3}}{2}i\left(\frac{3}{4}\zeta\right)^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)\\
+&=\textcolor{red}{-i}\zeta^{-1/2}{}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{3}{4}\zeta\right)
+\end{align*}
+
+These results agree with the one computed by the contour argument in {\tt airy-resurgence}.
+
+%\begin{itemize}
+%\item at $\frac{2}{3}$, the function ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3}{4}\zeta\right) $ is another major for $\overset{\triangledown}{\phi}_+(\zeta)$, in other words
+%\begin{align*}
+%\mathrm{sing}_0(\overset{\vee}{\phi})=\mathrm{sing}_0 (\, {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3}{4}\zeta\right) )=:\overset{\triangledown}{\phi}_+(\zeta)
+%\end{align*} 
+%\item at $-\frac{2}{3}$, conversely ${}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3}{4}\zeta\right) $ is another major for $\overset{\triangledown}{\phi}_-(\zeta)$, i.e.
+%\begin{align*}
+%\mathrm{sing}_0(\overset{\vee}{\phi}(\zeta+\frac{2}{3}))=\mathrm{sing}_0 (\, {}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1+\frac{3}{4}\zeta\right) )=:\overset{\triangledown}{\phi}_-(\zeta).
+%\end{align*} 
+%\end{itemize}
+
+%\begin{align*}
+%I_+(\zeta)&=\int_{\mathcal{H}_+}e^{-z\zeta}\overset{\vee}{\zeta}d\zeta\\
+%&=-\frac{1}{2}\int_{\mathcal{H}_+}e^{-z\zeta}{}_2F_2\left(\frac{1}{3},\frac{2}{3};\frac{1}{2};\frac{9}{4}\zeta^2\right)d\zeta \\
+%&=-\frac{1}{2}\frac{\Gamma(5/6)\Gamma(7/6)}{2\Gamma(1/2)\Gamma(3/2)} \int_{\mathcal{H}_+}e^{-z\zeta}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}-\frac{3}{4}\zeta\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};\frac{1}{2}+\frac{3}{4}\zeta\right)\right]d\zeta\\
+%&=-\frac{1}{6}\int_{\mathcal{H}_{0,+}}e^{-z(\zeta'+2/3)}\left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{3}{4}\zeta'\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1+\frac{3}{4}\zeta'\right)\right]d\zeta'\\
+%&=-e^{-2/3z}\frac{1}{6}\int_{\mathcal{H}_{0,+}}e^{-z\zeta'} \left[{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};-\frac{3}{4}\zeta'\right)+{}_2F_1\left(\frac{2}{3},\frac{4}{3};\frac{3}{2};1+\frac{3}{4}\zeta'\right)\right]d\zeta'
+%\end{align*}
 
 \color{black}
+
 \subsection{Comparison with other Airy examples}
@@
 \subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
-It is also commun to deal with formal power series in small parameters, like $\Phi(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ as $\hbar\to 0$.
-Then the Borel transform of $\Phi$ is defined as $\phi(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
-In \cite{Diablerets}, the author study the resurgent properties of the Airy functions: his starting point is the formal solution of Airy differential equation
+It is also commun to consider formal power series in small parameters, like $\tilde{\Phi}(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ where $\hbar\to 0$.
+Then the Borel transform of $\tilde{\Phi}$ is defined as $\tilde{\phi}(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author studies resurgent properties of the Airy functions: his starting point are the formal solutions of Airy differential equation
 \begin{align*}
@@
 
-Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $w_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
+Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $\hat{w}_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
 
@@
 In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
-He defines the formal series $\tilde{\Phi}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
-
-\begin{equation}
-\Phi_{\mathrm{Ai}}(w)=\frac{1}{2\sqrt{\pi}}w^{-1/4}e^{-\tfrac{2}{3}w^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}\left(\tfrac{2}{3}w^{3/2}\right)
-\end{equation}
-
-Notice that $\tilde{W}_1(\tfrac{2}{3}\hbar)=\tilde{\Phi}(z)$ for $\hbar=z^{-1}$, hence
-
-\begin{align*}
-\tilde{\phi}(\zeta)=\mathcal{B}\tilde{W}_1(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) 
-\end{align*}
-
-However, the author adopts a different approach to compute $\tilde{\phi}(\zeta)$: he argues that $\Phi_{\mathrm{Ai}}$ is a solution of Airy equation if and only if
-
-\begin{align*}
-\tilde{\phi}(\zeta)=\delta+\frac{d}{d\zeta}\tilde{\chi}(\zeta) & \qquad \text{ where }\,\, \chi(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}
-\end{align*}
-
-The function $\chi$ is an hypergeometric function:
+He defines the formal series $\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
+
+\begin{align*}
+\Phi_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
+\Phi_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
+\end{align*}
+
+Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence
+
+\begin{align*}
+\tilde{\phi}_{+}(\zeta)&=\mathcal{B}\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
+\tilde{\phi}_{-}(\zeta)&=\mathcal{B}\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
+\end{align*}
+which up to a constant factor for $\delta$, they agree with our results.
+
+However, the author adopts a different approach to compute $\tilde{\phi}_{\pm}(\zeta)$: he argues that $\Phi_{\mathrm{Ai}}, \Phi_{\mathrm{Bi}}$ are solutions of Airy equation if and only if
+
+\begin{align*}
+\tilde{\phi}_+(\zeta)=\delta+\frac{d}{d\zeta}\tilde{\chi}(\zeta)  \qquad \tilde{\phi}_-(\zeta)=\delta-\frac{d}{d\zeta}\tilde{\chi}(-\zeta)
+\end{align*}
+ where $\chi(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$. Function $\chi(\zeta)$ is an hypergeometric function:
 
@@
 \begin{align*}
-\tilde{\phi}(\zeta)=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right).
-\end{align*}
+\tilde{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
+\tilde{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right).
+\end{align*}
+
+The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
+Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
+Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
 

### 2022-05-16 airy-resurgence.tex

@@
 where
-\begin{equation}
+\begin{equation}\label{integral:mod-bessel-rational}
 K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
@@
 \[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_0). \]
+\subsection{Lifting to a countable cover}
+Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
+Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
+
+Setting $u = \cosh(t/n)$ and recalling that
+\begin{align*}
+\cosh(n\tau) & := T_n(\cosh(\tau)) \\
+\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
+\end{align*}
+we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
+\begin{align}
+\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
+\label{integral:mod-bessel-lifted} & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\end{align}
+For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
+\begin{align}
+\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
+\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
+\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
+\end{align}
+where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
+The integral converges when $z$ is in the right half-plane.
+We get formula~\ref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
+
+When $\nu$ goes to $0$, formula~\ref{integral:mod-bessel-lifted} becomes
+\[ K_\nu(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
+Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
+\begin{align*}
+K_\nu(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
+& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
+& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
+\end{align*}
+with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
 \subsection{Correspondence with Mari\~{n}o's series}

### 2022-05-19 airy-resurgence.tex
Generalize contour argument to all Airy-Lucas functions

@@
 \section{Sketches}
-\subsection{Contour argument}\label{contour-argument}
+\subsection{Contour argument for the Airy function}\label{contour-argument}
 We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $\zeta = 4u^3 - 3u$.
@@
 \[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_0). \]
+\subsection{Contour argument for Airy-Lucas functions}
+Generalizing from Section~\ref{contour-argument}, we can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+Projecting as before, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
+\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
+& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
+\end{align*}
+\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
+For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{center}
+\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
+{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
+\end{center}
+
+The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
+\begin{align*}
+& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
+\end{align*}
+as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
+Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
+\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta). \]
+\color{DarkCyan}
+Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
+\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta). \]
+\color{black}
 \subsection{Lifting to a countable cover}
@@
 \notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
 \end{align}

### 2022-05-20 airy-resurgence.tex
Start exploring link to dihedral triangulations

@@
 \begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
+& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
 \end{align*}
@@
 Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta). \]
+\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
 \color{DarkCyan}
 Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta). \]
+\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
+\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
+where $\zeta = -1 + \zeta_{-1}$.
 \color{black}
@@
 with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
+\subsection{Link to dihedral triangulations}
+At $\xi = \infty$, the function $F(a, b, c, \xi)$ is slight, with normal form $(-\xi^{-1})^a f_1 + (-\xi^{-1})^b f_2$~\cite[identity~15.8.2]{dlmf}.
+At $\xi = 0$, it's holomorphic with order $0$, and at $\xi = 1$ it has the form $h + (1-\xi)^{c-a-b} f$, where $h$ is holomorphic with order $0$~\cite[identity~15.8.4]{dlmf},
+
+For example, at $\zeta = \infty$, the function
+\[ u_{-1} = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, 1 - \tfrac{1}{2} \zeta_{-1}) \]
+is slight, with normal form $(1/\zeta_{-1})^{1 - m/n} f_1 + (1/\zeta_{-1})^{1 + m/n} f_2$~\cite[identity~15.8.3]{dlmf}.
+At $\zeta = 1$, it's holomorphic with order $0$.
+At $\zeta = -1$, it has the form $h + \zeta_{-1}^{-1/2} f$, where $h$ is holomorphic with order $0$.
+
+On the other hand, the function
+\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}) \]
+is slight at $\zeta = \pm 1$ with order $-\tfrac{1}{2}$, and slight at $\infty$ with order $1 - \tfrac{m}{n}$.
+
+Hence, the ratio $u_{-1} / v_{-1}$ looks like a holomorphic multiple of $\zeta_1^{1/2}$ near $\zeta = 1$, a holomorphic function plus a holomorphic multiple of $\zeta_{-1}^{1/2}$ near $\zeta = -1$, and a holomorphic function plus a holomorphic multiple of $(1/\zeta_{-1})^{2m/n}$ near $\zeta = \infty$.
+This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.
+
+\color{orange}
+In DLMF notation, let's try
+\begin{align*}
+u_1 & = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \xi_{-1}) \\
+& = w_1(\xi_{-1}) \\
+u_{-1} & = w_3(\xi_{-1}) \\
+v_{-1} & = w_2(\xi_{-1}) \\
+v_1 & = -i\sqrt{2}\,\zeta_1^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
+& = (-\tfrac{1}{2}\zeta_1)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
+& = (1 - \tfrac{1}{2}\zeta_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \tfrac{1}{2}\zeta_{-1}) \\
+& = (1 - \xi_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \xi_{-1}) \\
+& = w_4(\xi_{-1}),
+\end{align*}
+where $\xi_{-1} = \tfrac{1}{2}\zeta_{-1}$.
+
+\color{RoyalBlue}
+Let's guess that we're working with the map $\phi / \psi$ with
+\begin{align*}
+\phi & = \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{2} - \tfrac{m}{2n})\Gamma(\tfrac{1}{2} + \tfrac{m}{2n})}\,(\mp \zeta)\,F(1 - \tfrac{m}{2n}, 1 + \tfrac{m}{2n}, \tfrac{3}{2}; \zeta^2) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
+\psi & = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(1 - \tfrac{m}{2n})\Gamma(1 + \tfrac{m}{2n})} F(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}, \tfrac{1}{2}; \zeta^2) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
+\end{align*}
+\color{black}
 \subsection{Correspondence with Mari\~{n}o's series}

### 2022-05-24 airy-resurgence.tex
Add tetrahedral and dihedral tiling scratch work

@@
 \subsection{Link to dihedral triangulations}
-At $\xi = \infty$, the function $F(a, b, c, \xi)$ is slight, with normal form $(-\xi^{-1})^a f_1 + (-\xi^{-1})^b f_2$~\cite[identity~15.8.2]{dlmf}.
-At $\xi = 0$, it's holomorphic with order $0$, and at $\xi = 1$ it has the form $h + (1-\xi)^{c-a-b} f$, where $h$ is holomorphic with order $0$~\cite[identity~15.8.4]{dlmf},
+Here are the local normal forms of Kummer's first and second solutions. In the table, $[\bullet]$ denotes a local holomorphic function of order $0$ \cite[identities 15.8.2--4]{dlmf}, and
+\begin{align*}
+a' & = a+(1-c) \\
+b' & = b+(1-c) \\
+c' & = 2-c
+\end{align*}
+\begin{center}
+\begin{tabular}{c|c|c|c}
+Function & $0$ & $1$ & $\infty$ \\ \hline
+$F(a, b, c, \xi)$ & $[\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$ \\
+$\xi^{1-c} F(a', b', c', \xi)$ & $\xi^{1-c} [\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$
+\end{tabular}
+\end{center}
 
@@
 This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.
+
+\color{ForestGreen}
+Let's try to get the small tetrahedral tiling by setting
+\begin{align*}
+1 - c & = \tfrac{1}{3} \\
+c - a - b & = \tfrac{1}{3} \\
+b - a & = \tfrac{1}{2},
+\end{align*}
+so $(a, b, c) = (-\tfrac{1}{12}, \tfrac{5}{12}, \tfrac{2}{3})$. The general hypergeometric equation is
+\begin{align*}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + \big[c - (a+b+1)\xi_1\big] \tfrac{\partial}{\partial \xi_1} - ab\right] & v = 0 \\
+\left[-\tfrac{1}{2}\zeta_1 (1 + \tfrac{1}{2}\zeta_1) 4 \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + \big[c + \tfrac{1}{2}(a+b+1)\zeta_1\big] (-2) \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
+\left[-\zeta_1 (2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 - \big[2c + (a+b+1)\zeta_1\big] \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
+\left[(1 - \zeta)(1 + \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[2c + (a+b+1)(\zeta - 1)\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[(c - a - b) + (c - 1) + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[\mu - \lambda + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[\big[\tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta\big] \tfrac{\partial}{\partial \zeta} - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
+\left[\tfrac{\partial}{\partial \zeta} \circ \big[ \tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta \big] + 2\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
+\left[\big[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) + 4 \tfrac{\partial}{\partial \zeta} \circ \zeta - 2 \big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ (a+b+1) - ab \big]\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ {-}1 + a + b - ab \big]\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta - (a-1)(b-1)\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta^2 - 1) + (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (a+b-3) \tfrac{\partial}{\partial \zeta} \circ \zeta + (a-1)(b-1)\right] & v = 0,
+\end{align*}
+For the tetrahedral tiling, we get
+\[ \left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big(\zeta^2 - 1\big) - \tfrac{8}{3} \tfrac{\partial}{\partial \zeta} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\right] v = 0, \]
+which comes from the integral equation
+\[ \left[\big(\zeta^2 - 1\big) - \tfrac{8}{3}\,\fracderiv{-1}{\zeta}{\alpha} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\,\fracderiv{-2}{\zeta}{\alpha}\right] v = 0. \]
+In the frequency domain, this equation becomes
+\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
+\color{black}
+\color{SpringGreen}
+Set
+\[ \laplace_{\zeta, \alpha} v = \int_\Lambda e^{-zf}\,p\,du. \]
+Observe that
+\[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] \int_\Lambda e^{-zf}\,p\,du = \int_\Lambda e^{-zf}\,(f^2 - 1)p\,du \]
+and
+\begin{align*}
+z^{-1} \tfrac{\partial}{\partial z} \int_\Lambda e^{-zf}\,p\,du & = z^{-1} \int_\Lambda e^{-zf}\,(-fp)\,du \\
+& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')q_1\,du \\
+& = \int_\Lambda e^{-zf}\,f'q_1\,du
+\end{align*}
+where $q_1' = -fp$.
+and
+\begin{align*}
+z^{-2} \int_\Lambda e^{-zf}\,p\,du
+& = -z^{-2} \int_\Lambda e^{-zf}\,(-zf')p_1\,du \\
+& = z^{-1} \int_\Lambda e^{-zf}\,f'p_1\,du \\
+& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')p_2\,du \\
+& = \int_\Lambda e^{-zf}\,f'p_2\,du \\
+\end{align*}
+with $p_1' = p$ and $p_2' = f'p_1$.
+\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
+\color{black}
 
@@
 \color{black}
+\subsection{Comparison with Ghate and Venkataramana}
+\begin{align*}
+\mu_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \lambda & = 1 - c \\
+\nu_\text{GV} & = 1 - \left\{\frac{k_2}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \mu & = c - a - b \\
+\lambda_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_2}{d}\right\} & \nu & = b - a
+\end{align*}
+The hyperelliptic curve in Section~4 is
+\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
+
+Dihedral case (Theorem~2):
+\begin{align*}
+\frac{k_1}{d} & = \frac{p}{2m} \\
+\frac{k_2}{d} & = \frac{p}{2m} \\
+\frac{k_3}{d} & = \frac{m - p}{2m}
+\end{align*}
+Note that $\lambda = p'/m$ with $p + p' = m$. The hyperelliptic curve is
+\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
+Cosines appear in Section~2.3: $x_j = \exp(2\pi i\,\tfrac{k_j}{d})$, and we work in the totally real field $\mathbb{Q}(\cos(\frac{2\pi}{m}))$.
+
+Airy case:
+\begin{align*}
+\frac{k_1}{d} & = \frac{1}{3} \\
+\frac{k_2}{d} & = \frac{1}{3} \\
+\frac{k_3}{d} & = \frac{1}{6},
+\end{align*}
+so $(k_1, k_2, k_3, d) = (2, 2, 1, 6)$, and the hyperelliptic curve is
+\[ y^6 = (x - \alpha_1)^2 (x - \alpha_2)^2 (x - \alpha_3). \]
 \subsection{Correspondence with Mari\~{n}o's series}

### 2022-05-27 exercise-3.20.tex
Start working on Andy's exercise

\documentclass{article}

\usepackage{ajf}
\usepackage{amsthm}
\usepackage{stmaryrd}

\theoremstyle{definition}
\newtheorem{defn}{Definition}
\newtheorem*{exr}{Exercise}
\theoremstyle{plain}
\newtheorem{prop}{Proposition}
\newtheorem{thm}{Theorem}

\title{Exercise~3.20}
\author{Aaron Fenyes}

\newcommand{\phborel}{\mathcal{B}_\text{ph}}
\newcommand{\dict}{\mathcal{F}}

\begin{document}
\maketitle
Let $N_t = t \tfrac{\partial}{\partial t}$ and $N_\zeta = \zeta \tfrac{\partial}{\partial \zeta}$. We use the physicist's Borel transform,
\begin{align*}
\phborel \maps \C\llbracket t \rrbracket & \to \C\llbracket \zeta \rrbracket \\
t^n & \mapsto \zeta^n/n!.
\end{align*}
\begin{exr}
Suppose the formal series $f \in \C\llbracket t \rrbracket$ is annihilated by a differential operator $D \maps \C\llbracket t \rrbracket \to \C\llparenthesis t \rrparenthesis$ in the $\C$-algebra generated by $t^{-1}$ and $N_t$. Prove that $\phborel f$ is annihilated by the operator $\dict(D)$, where
\begin{align*}
\dict \maps t^{-1} & \mapsto \frac{\partial}{\partial \zeta} \\
N_t & \mapsto N_\zeta.
\end{align*}
\end{exr}
\begin{proof}[Solution]
Moving $t^{-1}$ to the right, we can write
\[ D = P_n(N_t)\,t^{-n} + P_{n-1}\,t^{-(n-1)} + \ldots + P_1(N_t)\,t^{-1} + P_0(N_t) \]
in terms of polynomials $P_n, \ldots, P_0$. After rescaling $f$ so its lowest-order coefficient is one, we can write $f = t^a + c_1 t^{a+1} + c_2 t^{a+2} + \ldots\,$. Monomials are eigenvectors of the number operator $N_t$, so $P_n(N_t)\,t^{-n} \cdot t^a$ is the lowest-order term of $Df$, unless it vanishes. The assumption that $Df = 0$ implies that this term does vanish. Simplifying the term to $P_n(a-n)\,t^{a-n}$, we learn that $P_n(a-n) = 0$.

Now we know that
\[ P_n(N_t)\,t^{-n} \cdot c_1 t^{a+1} + P_{n-1}(N_t)\,t^{-(n-1)} \cdot t^a \]
is the lowest-order term of $Df$, unless it vanishes. Again, by assumption, this term must vanish, so we learn that $c_1 P_n(a+1-n) + P_{n-1}(a+1-n) = 0$. \textbf{[...]}
\end{proof}
\end{document}

### 2022-05-27 exercise-3.20.tex
Try matrix approach

@@
 \maketitle
-Let $N_t = t \tfrac{\partial}{\partial t}$ and $N_\zeta = \zeta \tfrac{\partial}{\partial \zeta}$. We use the physicist's Borel transform,
+Let $\mathcal{D}$ be the noncommutative $\C$-algebra generated by the number operator $N$ and the lowering operator $A$, with the relation $NA = A(N-1)$.
+Let $N$ act as $t \tfrac{\partial}{\partial t}$ on $\C\llparenthesis t \rrparenthesis$ and $\zeta \tfrac{\partial}{\partial \zeta}$ on $\C\llparenthesis \zeta \rrparenthesis$.
+Let $A$ act as $t^{-1}$ on $\C\llparenthesis t \rrparenthesis$ and
+\begin{align*}
+\frac{\zeta^n}{n!} & \mapsto \frac{\zeta^{n-1}}{(n-1)!} & n & > 0 \\
+\zeta^n & \mapsto \zeta^{n-1} & n & \le 0
+\end{align*}
+on $\C\llparenthesis \zeta \rrparenthesis$. We use the physicist's Borel transform,
 \begin{align*}
 \phborel \maps \C\llbracket t \rrbracket & \to \C\llbracket \zeta \rrbracket \\
-t^n & \mapsto \zeta^n/n!.
+t^n & \mapsto \frac{\zeta^n}{n!}.
 \end{align*}
 \begin{exr}
-Suppose the formal series $f \in \C\llbracket t \rrbracket$ is annihilated by a differential operator $D \maps \C\llbracket t \rrbracket \to \C\llparenthesis t \rrparenthesis$ in the $\C$-algebra generated by $t^{-1}$ and $N_t$.
-Prove that $\phborel f$ is annihilated by the operator $\dict(D)$, where
+Suppose $f \in \C\llbracket t \rrbracket$ is annihilated by $D \in \mathcal{D}$.
+Prove that $\phborel f \in \C\llbracket \zeta \rrbracket$ is annihilated by the operator $\dict(D)$ given by the alternate representation
 \begin{align*}
-\dict \maps t^{-1} & \mapsto \frac{\partial}{\partial \zeta} \\
-N_t & \mapsto N_\zeta.
+\dict \maps \mathcal{D} & \to \big\{\C\llbracket \zeta \rrbracket \to \C\llparenthesis \zeta \rrparenthesis\big\} \\
+A & \mapsto \tfrac{\partial}{\partial \zeta} \\
+N & \mapsto t \tfrac{\partial}{\partial t}.
 \end{align*}
@@
 Moving $t^{-1}$ to the right, we can write
-\[ D = P_n(N_t)\,t^{-n} + P_{n-1}\,t^{-(n-1)} + \ldots + P_1(N_t)\,t^{-1} + P_0(N_t) \]
-in terms of polynomials $P_n, \ldots, P_0$.
-After rescaling $f$ so its lowest-order coefficient is one, we can write $f = t^a + c_1 t^{a+1} + c_2 t^{a+2} + \ldots\,$.
-Monomials are eigenvectors of the number operator $N_t$, so $P_n(N_t)\,t^{-n} \cdot t^a$ is the lowest-order term of $Df$, unless it vanishes.
-The assumption that $Df = 0$ implies that this term does vanish.
-Simplifying the term to $P_n(a-n)\,t^{a-n}$, we learn that $P_n(a-n) = 0$.
+\[ D = P_0(N)\,t^{-n} + P_1\,t^{1-n} + \ldots + P_{n-1}(N)\,t^{-1} + P_n(N) \]
+in terms of polynomials $P_0, \ldots, P_n$. Recalling that the number operator $N$ is diagonal in the monomial basis, we can write $D$ as the matrix
+\[ \begin{array}{l|lllll}
+& 1 & t & t^2 & t^3 & \ldots \\ \hline
+t^{0-n} & P_0(0-n) & \cdot & \cdot & \cdot & \ldots \\
+t^{1-n} & P_1(1-n) & P_0(1-n) & \cdot & \cdot & \ldots \\
+t^{2-n} & P_2(2-n) & P_1(2-n) & P_0(2-n) & \cdot & \ldots \\
+t^{3-n} & P_3(3-n) & P_2(3-n) & P_1(3-n) & P_0(3-n) & \ldots \\
+\vdots & \vdots & \vdots & \vdots & \vdots \\
+t^{-1} & P_{n-1}(-1) & P_{n-2}(-1) & P_{n-3}(-1) & P_{n-4}(-1) & \cdots \\
+1 & P_n(0) & P_{n-1}(0) & P_{n-2}(0) & P_{n-3}(0) & \cdots \\
+t & \cdot & P_n(1) & P_{n-1}(1) & P_{n-2}(1) & \cdots \\
+t^2 & \cdot & \cdot & P_n(2) & P_{n-1}(2) & \cdots \\
+t^3 & \cdot & \cdot & \cdot & P_n(3) & \cdots \\
+\vdots & \vdots & \vdots & \vdots & \vdots & \ddots \\
+\end{array} \]
 
-Now we know that
-\[ P_n(N_t)\,t^{-n} \cdot c_1 t^{a+1} + P_{n-1}(N_t)\,t^{-(n-1)} \cdot t^a \]
-is the lowest-order term of $Df$, unless it vanishes. Again, by assumption, this term must vanish, so we learn that $c_1 P_n(a+1-n) + P_{n-1}(a+1-n) = 0$. \textbf{[...]}
+Now, observe that
+\[ \dict(D) = P_0(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^n + P_1(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} + \ldots + P_{n-1}(N)\,\tfrac{\partial}{\partial \zeta} + P_n(N). \]
+Since $\big(\tfrac{\partial}{\partial \zeta}\big)^k = \Pi A^k$, where $\Pi$ is the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis, we can instead write
+\[ \dict(D) = \Pi \left[ P_0(N)\,A^n + P_1(N)\,A^{n-1} + \ldots + P_{n-1}(N)\,A^1 + P_n(N) \right]. \]
 \end{proof}

### 2022-05-27 exercise-3.20.tex
Finish exercise with representation theory approach

@@
 \end{align*}
-on $\C\llparenthesis \zeta \rrparenthesis$. We use the physicist's Borel transform,
+on $\C\llparenthesis \zeta \rrparenthesis$. These actions commute with the physicist's Borel transform
 \begin{align*}
 \phborel \maps \C\llbracket t \rrbracket & \to \C\llbracket \zeta \rrbracket \\
-t^n & \mapsto \frac{\zeta^n}{n!}.
+t^n & \mapsto \frac{\zeta^n}{n!}
 \end{align*}
+whenever both paths through the commutative square are well-defined.
 \begin{exr}
@@
 A & \mapsto \tfrac{\partial}{\partial \zeta} \\
-N & \mapsto t \tfrac{\partial}{\partial t}.
+N & \mapsto \zeta \tfrac{\partial}{\partial \zeta}.
 \end{align*}
@@
 \begin{proof}[Solution]
-Moving $t^{-1}$ to the right, we can write
-\[ D = P_0(N)\,t^{-n} + P_1\,t^{1-n} + \ldots + P_{n-1}(N)\,t^{-1} + P_n(N) \]
-in terms of polynomials $P_0, \ldots, P_n$. Recalling that the number operator $N$ is diagonal in the monomial basis, we can write $D$ as the matrix
-\[ \begin{array}{l|lllll}
-& 1 & t & t^2 & t^3 & \ldots \\ \hline
-t^{0-n} & P_0(0-n) & \cdot & \cdot & \cdot & \ldots \\
-t^{1-n} & P_1(1-n) & P_0(1-n) & \cdot & \cdot & \ldots \\
-t^{2-n} & P_2(2-n) & P_1(2-n) & P_0(2-n) & \cdot & \ldots \\
-t^{3-n} & P_3(3-n) & P_2(3-n) & P_1(3-n) & P_0(3-n) & \ldots \\
-\vdots & \vdots & \vdots & \vdots & \vdots \\
-t^{-1} & P_{n-1}(-1) & P_{n-2}(-1) & P_{n-3}(-1) & P_{n-4}(-1) & \cdots \\
-1 & P_n(0) & P_{n-1}(0) & P_{n-2}(0) & P_{n-3}(0) & \cdots \\
-t & \cdot & P_n(1) & P_{n-1}(1) & P_{n-2}(1) & \cdots \\
-t^2 & \cdot & \cdot & P_n(2) & P_{n-1}(2) & \cdots \\
-t^3 & \cdot & \cdot & \cdot & P_n(3) & \cdots \\
-\vdots & \vdots & \vdots & \vdots & \vdots & \ddots \\
-\end{array} \]
-
-Now, observe that
-\[ \dict(D) = P_0(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^n + P_1(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} + \ldots + P_{n-1}(N)\,\tfrac{\partial}{\partial \zeta} + P_n(N). \]
-Since $\big(\tfrac{\partial}{\partial \zeta}\big)^k = \Pi A^k$, where $\Pi$ is the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis, we can instead write
-\[ \dict(D) = \Pi \left[ P_0(N)\,A^n + P_1(N)\,A^{n-1} + \ldots + P_{n-1}(N)\,A^1 + P_n(N) \right]. \]
+Moving $A$ to the right, we can write
+\begin{align*}
+D & = P_0(N)\,A^n + P_1(N)\,A^{n-1} + \ldots + P_{n-1}(N)\,A + P_n(N) \\
+\dict(D) & = P_0(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^n + P_1(N)\,\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} + \ldots + P_{n-1}(N)\,\tfrac{\partial}{\partial \zeta} + P_n(N)
+\end{align*}
+in terms of polynomials $P_0, \ldots, P_n$.
+Notice that $\big(\tfrac{\partial}{\partial \zeta}\big)^k = \Pi A^k$, where $\Pi$ is the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis.
+Since $\Pi$ commutes with $N$, it follows that $\dict(D) = \Pi D$.
+Since the action of $\mathcal{D}$ commutes with $\phborel$, the assumption that $Df = 0$ implies that
+\begin{align*}
+\dict(D)\,\phborel f & = \Pi D \phborel f \\
+& = \Pi \phborel Df \\
+& = 0.
+\end{align*}
 \end{proof}

### 2022-05-30 airy-resurgence.tex
Drop old version of analysis at critical values

@@
 \end{equation}
-
-\color{violet}
-As we'll see in Section~\ref{asymp}, $K$ is in $O_{z \to \infty}(e^{-z})$.
-It'll be helpful to pull out the exponential decay factor and work instead with the function $K_1$ defined by $K = e^{-z} K_1$.
-Saying that $K$ satisfies equation~\ref{eqn:mod-bessel} is equivalent to saying that $K_1$ satisfies the equation
-\begin{equation}\label{eqn:shifted-mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z} + 1\big)^2 + z \big(\tfrac{\partial}{\partial z} + 1\big) - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-\color{black}
 \subsection{Asymptotic analysis}
@@
 \subsection{Going to the spatial domain}\label{spatial}
-\color{violet}
-\subsubsection{A good try at $\zeta = 0$}
-Let's try to find a function $k_0$ with $K = \laplace_\zeta k_0$, which is unique if it exists~\cite[Theorem~1.23]{laplace-tfm}. If a function $\varphi$ satisfies the equation
-\begin{equation}%%\label{eqn:spatial-mod-bessel}
-\left[\big(\zeta^2 - 1\big) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0,
-\end{equation}
-its Laplace transform $\varphi = \laplace_\zeta \varphi$ satisfies the equation
-\begin{align*}
-\left[\big({-\tfrac{\partial}{\partial z}}\big)^2 - 1\right] \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) + 3\big({-\tfrac{\partial}{\partial z}}\big)\big[z\varphi - \varphi\big]_{\zeta = 0} + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\big(\tfrac{\partial}{\partial z}\big)^2 \big[z^2 \varphi\big] - \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) - 3\big(\tfrac{\partial}{\partial z}\big)\big[z\varphi\big] + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0 \\
-\Big[2 + 4z\tfrac{\partial}{\partial z} + z^2\big(\tfrac{\partial}{\partial z}\big)^2\Big]\varphi - \Big(z^2 \varphi - \big[\varphi\,z + \varphi'\big]_{\zeta = 0}\Big) - 3\Big[1 + z\tfrac{\partial}{\partial z}\Big]\varphi + \big[1 - \big(\tfrac{1}{3}\big)^2\big] \varphi & = 0,
-\end{align*}
-which simplifies to
-\begin{equation}\label{eqn:inhomog-mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = -\big[\varphi\,z + \varphi'\big]_{\zeta = 0}.
-\end{equation}
-Since we want $\laplace_\zeta k_0$ to satisfy equation~\ref{eqn:mod-bessel}, which is the homogeneous version of equation~\ref{eqn:inhomog-mod-bessel}, we might guess that $k_0$ is a solution of equation~\ref{eqn:spatial-mod-bessel} that vanishes through first order at $\zeta = 0$.
-Unfortunately, this would force $k_0$ to be zero.
-\color{black}
 \subsubsection{The big idea}\label{big-idea}
@@
 In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$
-\color{black}
-\color{violet}
-\subsubsection{Success at $\zeta = 1$}\label{spatial-success}
-Let's try instead to find a function $k_1$ with $K = \laplace_{\zeta, 1} k_1$ \textcolor{magenta}{[This would be called $K_1$ in our new notation.]}.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-Since
-\begin{align*}
-\laplace_{\zeta_1, 0} k_1 & = e^z \laplace_{\zeta, 1} k_1 \\
-& = e^z K \\
-& = K_1,
-\end{align*}
-we want $\laplace_{\zeta_1} k_1$ to satisfy equation~\ref{eqn:shifted-mod-bessel}. Rewrite equation~\ref{eqn:spatial-mod-bessel} as
-\begin{equation}\label{eqn:shifted-spatial-mod-bessel}
-\left[\zeta_1(\zeta_1 + 2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(\zeta_1 + 1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0.
-\end{equation}
-If $\varphi$ satisfies equation~\ref{eqn:shifted-spatial-mod-bessel}, $\laplace_{\zeta_1} \varphi$ will satisfy an inhomogeneous version of equation~\ref{eqn:shifted-mod-bessel}, analogous to equation~\ref{eqn:inhomog-mod-bessel}.
-This time, though, there's a trick we can use to zero out the inhomogeneity.
-Equation~\ref{eqn:shifted-spatial-mod-bessel} has a regular singularity at $\zeta_1 = 0$, and one solution (up to scaling) is a holomorphic multiple of $\zeta_1^{-1/2}$.\footnote{\textcolor{magenta}{Explain how to see.}} That solution has a fractional power singularity at $\zeta_1 = 0$, as defined in Section~\ref{L-diff-op-alg}, so its Laplace transform in $\zeta_1$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
-
-Following this plan, let's find $k_1$ explicitly.
-Defining another coordinate $\xi$ on $\C$ so that $\zeta_1 = -2\xi$, we can rewrite equation~\ref{eqn:shifted-spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{eqn:hypergeom}
-\left[\xi(1 - \xi) \big(\tfrac{\partial}{\partial \xi}\big)^2 + 3(\tfrac{1}{2} - \xi) \tfrac{\partial}{\partial \xi} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] \varphi = 0.
-\end{equation}
-The hypergeometric function
-\[ g_1 = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \]
-satisfies equation~\ref{eqn:hypergeom} by definition. It's not the solution we want, though, because it's holomorphic around $\xi = 0$. Formula~15.10.12 from \cite{dlmf} gives another solution,
-\[ f_0 = \xi^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big), \]
-which is a holomorphic multiple of $\xi^{-1/2}$ near $\xi = 0$.
-By the argument above, $F_0 = \laplace_{\zeta_1} f_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}.
-This suggests that a constant multiple of $f_0$ is our desired $k_1$.
-The power series~\cite[equation~15.2.1]{dlmf}
-\[ f_0 = \xi^{-1/2} + \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{(\tfrac{1}{2})_1 \; 1!}\;\xi^{1/2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{(\tfrac{1}{2})_2 \; 2!}\;\xi^{3/2} + \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{(\tfrac{1}{2})_3 \; 3!}\;\xi^{5/2} + \ldots \]
-converges near $\xi = 0$, showing that
-\[ f_0 \in \xi^{-1/2} + O_{\xi \to 0}(\xi^{1/2}). \]
-In terms of $\zeta_1$, we have
-\[ f_0 \in -i \sqrt{2}\,\zeta_1^{-1/2} + O_{\zeta_1 \to 0}(\zeta_1^{1/2}). \]
-Using the decay properties from Section~\ref{reg-decay}, we deduce that
-\[ F_0 \in -i \sqrt{2\pi}\,z^{-1/2} + O_{z \to \infty}(z^{-3/2}). \]
-Since we know that $F_0$ satisfies equation~\ref{eqn:shifted-mod-bessel}, this confirms that $F_0$ is a constant multiple of $K_1$, which is the only subexponential solution of equation~\ref{eqn:shifted-mod-bessel} (up to scaling).
-Comparing with series~\ref{bessel-asymp}, we see that $K_1 = \tfrac{i}{2}\,F_0$.
-We conclude that $K_1 = \laplace_{\zeta_1} k_1$ for
-\[ k_1 = \tfrac{1}{\sqrt{2}}\,\zeta_1^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
 \color{black}

### 2022-05-30 airy-resurgence.tex
Drop Laplace transforms of differential operators
In the new argument, we only need Laplace transforms of integral
operators.

@@
 for all $\lambda \in (0, \infty)$.
-
-\color{violet}
-When $\varphi$ is $n$ times differentiable, its $n$th derivative is in $\mathcal{E}$, and its zeroth through $(n - 1)$st derivatives extend continuously to zero, integration by parts gives the formula
-\begin{align}\label{id:L-diff}
-\laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi & = z^n \laplace_\zeta \varphi - \left[ \varphi\,z^{n-1} + \varphi'\,z^{n-2} + \varphi''\,z^{n-3} + \ldots + \varphi^{(n-1)} \right]_{\zeta = 0} \\
-& = z^n\,\laplace\left( \varphi - \left[ \varphi + \varphi'\,\zeta + \tfrac{\varphi''}{2!}\,\zeta^2 + \ldots + \tfrac{\varphi^{(n-1)}}{(n-1)!}\,\zeta^{n-1} \right]_{\zeta = 0} \right). \nonumber
-\end{align}
-Note that if a function's derivative is subexponential, so is the function itself.\footnote{Say $f' \in O_{\zeta \to \infty}(e^{c\zeta})$.
-Then \[ \left|\int_0^Z f'\,d\zeta\right| \le \int_0^Z |f'|\,d\zeta \lesssim \int_0^Z e^{c\zeta}\,d\zeta = \tfrac{1}{c}(e^{cZ} - 1) \lesssim e^{cZ}.\] Now we know the integral on the left-hand side converges, implying that $f$ extends continuously to zero, with $|f - f_{\zeta = 0}| \lesssim e^{c\zeta}$.}
-\subsection{Algebraic version}
-\subsubsection{Definition}
-Let $\mathcal{P}_\zeta$ be the vector space spanned by $\zeta^\alpha$ for $\alpha \in \R \smallsetminus \Z_{< 0}$.
-Note that $\mathcal{P}_\zeta \cap \mathcal{E}_\zeta$ is $\mathcal{P}_\zeta^{> -1}$, the subspace spanned by $\zeta^\alpha$ with $\alpha > -1$.
-Since
-\[ \laplace_\zeta(\zeta^\alpha) = \Gamma(\alpha+1)\,z^{-(\alpha + 1)} \]
-for all $\alpha > -1$, let's use the same formula to extend $\laplace_\zeta$ to all of $\mathcal{P}_\zeta$. This defines $\laplace_\zeta$ consistently on $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
-\subsubsection{Action on differential operators}\label{L-diff-op-alg}
-Observe that
-\[ \laplace_\zeta(\zeta^{\alpha + 1}) = -\tfrac{\partial}{\partial z}\,\laplace_\zeta(\zeta^\alpha) \]
-for $\alpha \neq -1$. This extends identity~\ref{id:L-mult} to all of $\mathcal{P}_\zeta$.
-
-Observe that
-\[ \laplace_\zeta\tfrac{\partial}{\partial \zeta}(\zeta^\alpha) = \begin{cases}
-z\,\laplace_\zeta(\zeta^\alpha) & \alpha \neq 0 \\
-0 & \alpha = 0,
-\end{cases} \]
-and that $0 = z\,\laplace_\zeta(1) - 1$.
-This recovers identity~\ref{id:L-diff} for any function in $\mathcal{P}_\zeta$ whose $n$th derivative is in $\mathcal{P}_\zeta^{> -1}$.
-Although the functions in $\mathcal{P}_\zeta^{< 0}$ are singular at zero, let's pretend they vanish at zero.
-With that convention, formula~\ref{id:L-diff} extends to all of $\mathcal{P}_\zeta$.
-
-Now we have the results of Section~\ref{L-diff-op} for all functions in $\mathcal{E}_\zeta + \mathcal{P}_\zeta$.
-Identity~\ref{id:L-diff} is particularly simple when $\varphi$ has a {\em fractional power singularity} \textcolor{magenta}{[new terminology: when $\varphi$ is {\em slight}]} at $\zeta = 0$.
-By this, I mean that $\varphi$ can be written as $\varphi_\text{frac} + \varphi_\text{reg}$, where $\varphi_\text{frac} \in \mathcal{P}_\zeta$ has only non-integer exponents, and the zeroth through $(n-1)$st derivatives of $\varphi_\text{reg} \in \mathcal{E}_\zeta$ vanish at zero.
-Under this condition, all the initial value terms in the identity vanish, leaving
-\[ \laplace_\zeta \big(\tfrac{\partial}{\partial \zeta}\big)^n \varphi = z^n \laplace_\zeta \varphi. \]
-\color{black}
 \subsection{Change of translation chart}\label{translation}

### 2022-06-02 airy-resurgence.tex
Start writing about integral equations
Also, add Alex's comments on Andy's exercise

--- 2022-05-30 airy-resurgence.tex
@@
 \newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
+\newcommand{\holoL}[1]{\mathcal{H}L^{#1}}
 \DeclareMathOperator{\Ai}{Ai}
@@
 We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-\section{Shifting integro-differential equations}\label{shifting}
+\section{Integro-differential equations}
+\subsection{Existence of solutions}
+\subsubsection{Function spaces for contour integration}
+Take a simply connected open set $\Omega$ that touches but doesn't contain $\zeta = 0$.
+Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
+Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.
+
+If you give a Riemann surface a metric which is compatible with its conformal structure, you get a norm on each tangent space.
+A {\em density} on a Riemann surface is a norm that arises in this way.
+Given a density $\rho$ on $\Omega$, let $\ell_\rho$ be the continuous function on $\Omega$ that measures distance from $\zeta = 0$ with respect to $\rho$.
+The value of $\ell_\rho$ at $a \in \Omega$ is the infimal length of a rectifiable path that runs from $\zeta = 0$ to $a$ within $\Omega$.
+Keep in mind that $\Omega$ touches but doesn't contain $\zeta = 0$, and $\ell_\rho$ is only well-defined when $\rho$ puts $\zeta = 0$ at finite distance from the points in $\Omega$.
+\textcolor{magenta}{[...]}
+
+\color{gray}
+A bounded holomorphic map
+\begin{align*}
+\Omega & \to \holoL{1}(\Omega) \\
+\alpha & \mapsto g_\alpha
+\end{align*}
+defines a bounded linear operator
+\[ \mathcal{G}f\big|_{\zeta = \alpha} = \int_0^\alpha  g_\alpha f \]
+on $\holoL{\infty}(\Omega)$. Noting that
+\color{black}
+
+%%with\footnote{We're using the operator norm on the left-hand side and the $L^1$ norm on the right-hand side.} $\|\mathcal{G}\| = \sup_{\alpha \in \Omega} \|g_\alpha\|_1$.
+\subsection{Order shifting}\label{shifting}
 Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.

### 2022-06-02 exercise-3.20.tex
Start writing about integral equations
Also, add Alex's comments on Andy's exercise

@@
 in terms of polynomials $P_0, \ldots, P_n$.
-Notice that $\big(\tfrac{\partial}{\partial \zeta}\big)^k = \Pi A^k$, where $\Pi$ is the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis.
+Let $\Pi$ be the projection $\C\llparenthesis \zeta \rrparenthesis \to \C\llbracket \zeta \rrbracket$ in the monomial basis.
+Notice that $\big(\tfrac{\partial}{\partial \zeta}\big)^k$ and $\Pi A^k$ act the same on elements of $\C\llbracket \zeta \rrbracket$.
 Since $\Pi$ commutes with $N$, it follows that $\dict(D) = \Pi D$.
@@
 \end{proof}
+{\it Note from Alex: For holomorphic functions, the correct statement might be that $Df = 0$ implies $\tfrac{\partial}{\partial \zeta} \mathcal{F}(D)\,\phborel f = 0$.
+The idea is that $\mathcal{F}(A)$ only differs from $A$ because it annihilates constants, so a ``translation error'' in the differential equation can only leave constants left over.}
 \end{document}

### 2022-06-02 exp-resurgence.tex

@@
 %% colors
-\usepackage[dvipsnames]{xcolor}
+\usepackage[svgnames]{xcolor}
 
@@
 
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ that sends punctures to punctures.
+Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
 Suppose every singularity of $B$ is a critical value of $f$.
@@
 \end{itemize}
-\item We can generalize this argument to all $K_{1/n}$ and their limit $K_0$.
+\item We can generalize this argument to all $K_\nu$ with $\nu \in \mathbb{Q}$.
 \item We can also generalize to all third-order exponential integrals.
@@
 \end{itemize}
-\item Formalism for Laplace transform
+\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
+\begin{enumerate}
+\item Analytic
 \begin{enumerate}
 \item Introduction
+\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
+\item The Laplace transform of a holomorphic function
 \begin{enumerate}
-\item
+\item Over an ordinary point
+\item Over a branch point
+\item Differential equation
+\end{enumerate}
+\item Relating differential equations in the frequency domain to integral equations in the position domain
+\end{enumerate}
+\item Formal
+\begin{enumerate}
+\item Laplace transform of a formal series
+\item Borel transform
+\item Relating differential equations in the frequency variable to integral equations in the position variable
 \end{enumerate}
 \end{enumerate}
+\item Review of integral equations
+\begin{itemize}
+\item Existence of solutions
+\item Fractional integrals and derivatives
+\item Going between integral and differential equations (slight functions)
+\end{itemize}
 \item General cases
@@
 where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
+\begin{itemize}
+\color{DarkCyan}
+\item More generally, for $P$ of degree $n$, we should be able to handle
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q_1\big(\tfrac{\partial}{\partial z}\big) + z^{-2} Q_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} Q_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
+where $Q_k$ has degree $n-k$. \textcolor{gray}{has to be done}
+\begin{itemize}
+\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
+\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
+\end{itemize}
+\color{orange}
+\item Show that we can find a slight solution at each critical value.
+\item Show that $\hat{\iota} = \tilde{\iota}$, where:
+\begin{itemize}
+\item $I = \laplace \iota$
+\item $\hat{\iota}$ is the Taylor expansion of $\iota$
+\item $\tilde{I}$ is the asymptotic series of $I$
+\item $\tilde{\iota} = \borel \tilde{I}$
+\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
+\end{itemize}
+\end{itemize}
 \item General thimble integral (conditions?)
+\begin{itemize}
+\item Proof of Borel regularity
+\item $3/2$-derivative formula
+\item Contour argument
+\end{itemize}
 \end{itemize}
 \item Resurgence
+\begin{itemize}
+\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
+\item Relate to Ecalle's formalism and the alien derivative
+\item Stokes factors
+\begin{itemize}
+\item For ODEs
+\item For thimble integrals
+\end{itemize}
+\end{itemize}
 \end{enumerate}
+\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
+\begin{enumerate}
 \item The Airy example
@@
 \item Stokes constants using fractional derivative formula and Borel transform computation [{\tt draft2}]
-\item Comparison with the literature (Marino, Sauzin, Kontsevich slides) \textcolor{gray}{has to be done}
+\item Comparison with the literature \textcolor{gray}{has to be done}
+\begin{itemize}
+\item Mari\~{n}o
+\item Sauzin
+\item Kontsevich slides
+\item Kawai--Takei? [might take too long to understand well enough]
 \end{itemize}
-\item Bessel $1/n$ (follows from Airy) we compute Borel transform and Stokes constants \textcolor{gray}{has to be done}
-\item Bessel 0 (it is different because we have infinite cover) we compute Stokes constants [{\tt draft2}]
-\item Bessel $\mu$ (follows from Bessel 0) we compute Stokes constants [{\tt modified Bessel}]
+\end{itemize}
+\item The Airy--Lucas examples
+\begin{itemize}
+\item Compute Borel transform [{\tt airy-resurgence}]
+\item Compute Stokes constants \textcolor{gray}{has to be done}
+\end{itemize}
+\item Bessel 0 (it is different because we have infinite cover)
+\begin{itemize}
+\item Compute Stokes constants [{\tt draft2}]
+\end{itemize}
+\item Bessel $\mu$ (follows from Bessel 0)
+\begin{itemize}
+\item Compute Stokes constants [{\tt modified Bessel}]
+\end{itemize}
+\item The generalized Airy example
+\item The vibrating beam example
+\begin{itemize}
+\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals, since Andy is interested in that sort of thing
+\end{itemize}
+\end{enumerate}
 \end{enumerate}

### 2022-06-13 General thimble integral.tex
general thimbles integrals

\DeclareSymbolFont{AMSb}{U}{msb}{m}{n}
\documentclass[11pt,a4paper,twoside,leqno,noamsfonts]{amsart}
           \usepackage{setspace}
\linespread{1.34}           
           %\onehalfspacing
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\definecolor{britishracinggreen}{rgb}{0.0, 0.26, 0.15}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\usepackage[utopia]{mathdesign}
    \DeclareSymbolFont{usualmathcal}{OMS}{cmsy}{m}{n}
    \DeclareSymbolFontAlphabet{\mathcal}{usualmathcal}
\usepackage[a4paper,top=4cm,bottom=3cm,left=3.5cm,
           right=3.5cm,bindingoffset=5mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{braket,caption,comment,mathtools,stmaryrd}
\usepackage{multirow,booktabs,microtype}
\usepackage{latexsym}
\usepackage{todonotes}
\usepackage{fancyhdr}
%\renewcommand{\sectionmark}[1]{\markboth{\thesection\ #1}{}}
\pagestyle{fancy}
% Clear the header and footer
\fancyhead{}
\fancyfoot{}
% Set the right side of the footer to be the page number
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{\baselineskip}
%\fancyhead[RE]{\rightmark}
%\fancyhead[RE]{}
\usepackage{soul} % per testo barrato
\usepackage[colorlinks,bookmarks]{hyperref} %
\hypersetup{colorlinks,%
            citecolor=britishracinggreen,%
            filecolor=black,%
            linkcolor=cobalt,%
            urlcolor=black}
\setcounter{tocdepth}{2}
%\setcounter{section}{-1}
\numberwithin{equation}{section}

% Veronica's custom commands
\input{command}

% symbology
\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
\newcommand{\maps}{\colon}
\newcommand{\van}{\mathfrak{m}}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\laplacepde}{\mathcal{D}}
\DeclareMathOperator{\Ai}{Ai}

\DeclareRobustCommand{\subtitle}[1]{\\#1}
\title[General thimbles integrals]{General thimbles integrals\\ [1ex]
  }

\author{
Veronica Fantini 
}
\begin{document}
\maketitle

\section{Proof of Borel regularity}

We are going to prove Theorem 5.1 {\tt draft2}. 
Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
\begin{equation}
I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
\end{equation}
where $\mathcal{C}$ is a suitable contour such that the integral is well defined. Indeed, $I(z)$ represents a pairing between a relative homology class $\mathcal{C}\in H_{N}^{B}(X,zf)$ and a cohomology class $\nu\in H_{dR}^N(X,zf)$ (see Section 1.3.1 Thimble integrals in the introduction). 
Let us restrict to one dimensional $X$. For any Morse critical points $x_\alpha$\footnote{By Morse critical points we mean non--degenerate isolated critical points.} of $f$, the saddle point approximation allows to compute the asymptotic expansion of $I_\alpha(z)$ 
\begin{equation}\label{exp-int}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } \operatorname{Re} (ze^{i\theta})\to\infty
\end{equation}
where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}. Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, e^{i\theta}\infty)$, where $\zeta_\alpha := f(x_\alpha)$.

\begin{theorem}\label{thm:maxim} Let $N=1$. Let ${I}_{\alpha}(z)$ defined as in \eqref{exp-int} for every critical point $x_\alpha$. Then $\tilde{I}_\alpha$ is Borel regular for $\operatorname{Re}(ze^{i\theta})>0$:
\begin{enumerate}
\item\label{int:series-gevrey} The series $\tilde{I}_\alpha(z)=e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n}$ is Gevrey-1.
\item\label{int:resum-converges} The series $\tilde{\iota}_\alpha(\zeta)\defeq\mathcal{B}(\tilde{I}_\alpha)$ converges near $\zeta=\zeta_{\alpha}$.
\item\label{int:resum-valid} If you continue the sum of $\tilde{\iota}_\alpha$ along the ray going rightward from $\zeta_\alpha$ in the direction $\theta$, and take its Laplace transform along that ray, you'll recover $I_\alpha$.
\end{enumerate}
\end{theorem}

\begin{remark}
\begin{enumerate}
\item We may drop the assumption of non degenerate critical points for $f$, however the asymptotic expansion of $I_\alpha(z)$ will depend on the order $m$ such that $f^{(m)}(x_\alpha)\neq 0$ and $f^{(j)}(x_\alpha)=0$ for every $j=1,...,m-1$ (see [Zorich] Theorem 1 Section 19.2.5).  
\item in [Malgrange74] (see also Chapter 5 of [Mistergard Phd thesis] for a general review), the author computes the asymptotic expansion of exponential integrals for $N>1$ which get logarithmic terms like 
\[\tilde{I}(z)=\sum_{j\in A} \sum_{n\geq 0}\sum_{q=0}^{N-1}a_{n,q,j}z^{-n-j}(\log z)^q,\] for $A\subset\Q_{\geq 0}$ finite. Due to the presence of logarithmic terms, the definition of Borel transform has to be further extended  (see [Mistergard phd] Definition pag 5) and the study of Borel regularity becomes more involved.   
\end{enumerate}
\end{remark}
\begin{proof}
Part~\eqref{int:series-gevrey}: Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$. Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively. We can arrange for $\tau$ to be valued in $(-\infty e^{i\theta}, 0]$ and $[0, e^{i\theta}\infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively. \textbf{[We should explicitly spell out and check the conditions that make this possible. I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
that converges in some disk $|\tau| < \varepsilon$.

In coordinates $\tau $ the integral $I_\alpha(z)$ can be approximated as 
\[ I_\alpha(z) \sim  e^{-z\zeta_\alpha}\int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
as $\operatorname{Re}(ze^{i\theta}) \to \infty$ (see Lemma 1 in Section 19.2.2  Zorich). \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
\begin{align*}
 I_\alpha(z) & \sim e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
& = e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau\\
& = 2e^{-z\zeta_\alpha}\int_{0}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
\end{align*}

By Watson's Lemma (see Lemma 4 Section 19.2.2 Zorich)

\begin{align*}
I_\alpha(z) &\sim e^{-z\zeta_\alpha}\sum_{n \ge 0} b_{2n}^\alpha \Gamma\left(n+\tfrac{1}{2}\right)2^{n+1/2}z^{-n-1/2}\\
&= e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n \ge 0} b_{2n}^\alpha (2n-1)!!z^{-n-1/2}
\end{align*}

%By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.}
%\begin{align*}
%I_\alpha(z) & \approx e^{-z\zeta_\alpha} \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
%& = e^{-z\zeta_\alpha} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{k=1}^n \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
%\end{align*}

%The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large. These terms are crucial, however, for the convergence of the sum. To see why, consider their absolute sum $C_\text{exp}$. When $z \in [0, \infty)$,
%\begin{align*}
%C_\text{exp} & = -2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{k=1}^n \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-(n-k+1)} \right| \\
%& =-2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{k=1}^n \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-(n-k+1)} \\
%& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| nz^{-n},
%\end{align*}
%which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}

%This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside. We can, however, set aside any finite set of them. \color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots. See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
%\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
%
%\color{CarnationPink}
%For each cutoff $N$, the tail error \textbf{[check]}
%\begin{align*}
%\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
%& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
%& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
%& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
%& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
%& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
%& = \textbf{uh-oh!}
%\end{align*}
%\color{violet}
%is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
%\begin{align*}
%C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{k=1}^n \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-(n-k+1)} \right| \\
%& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{k=1}^n \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{-(n-k+1)} \\
%& \leq 2\varepsilon e^{-\operatorname{Re}(z)\varepsilon^2/2}\sum_{n=1}^{N-1}(2n-1)!!|b_{2n}^\alpha|n z^{-n}\\
%%& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^{-n},
%\end{align*}
%is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
%\[  I_\alpha(z) \sim e^{-z\zeta_\alpha}\sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
%The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
%\[  I_\alpha(z) \sim e^{-z\zeta_\alpha}\sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
Call the right-hand side $\tilde{I}_\alpha$. We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem. We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$. Recalling that $(2n - 1)!! \sim (\pi n)^{-1/2}\,4^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{4}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_\alpha$ is Gevrey-1.%

Part~\eqref{int:resum-converges}: note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
\begin{align*}
\tilde{\iota}_{\alpha}\defeq \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} 
\end{align*}

Since ${(2n-1)!!}=\pi^{-1/2} 2^n{\Gamma\left(n+\tfrac{1}{2}\right)}$ and $|b_n^\alpha|\epsilon^n\lesssim 1$, then $\tilde{\iota}_{\alpha}(\zeta)$ has a finite radius of convergence.

%\begin{multline*}
%\tilde{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_{\alpha,0}+\sum_{n\geq 0}a_{\alpha,n+1}\frac{\zeta^n}{n!}\right)\\
%=(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_{\alpha,0}+\sum_{n\geq 0}a_{\alpha,n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
%\end{multline*}
%Since $|a_{\alpha,n}|\leq C_\alpha A_\alpha^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.

Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane. As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively. Hence, we have
\begin{align*}
I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\left(\int_{f^{-1}(\zeta)}\frac{\nu}{df}\right)d\zeta \\
& = \int_{\zeta_\alpha}^{e^{i\theta}\infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
\end{align*}
where $\mathcal{H}_{\alpha}$ is the Hanckel contour through the point $\zeta_{\alpha}$ (see Figure \cite{fig.paths}) with ends in the $\theta$ direction.
\begin{figure}
\caption{The contour $\mathcal{C}_\alpha$, its image under $f$ which is the Hankel contour $\mathcal{H}_{\alpha}=f(\mathcal{C}_{\alpha})$ and the ray $[\zeta_\alpha,+\infty]$. }
\end{figure}   
Noticing that the last integral is a Laplace transform for the initial choice of $\theta$, we learn that
\begin{equation}\label{thimble-difference}
\hat{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
\end{equation}
In Ecalle's formalism, $\int_{f^{-1}(\zeta)}\frac{\nu}{df}$ and $\hat{\iota}_\alpha$ are respectively a major and a minor of the singularity $\overset{\triangledown}{\iota}_\alpha$ and they differ by an holomorphic function (we will see this in the examples Section Airy, Bessel).

We can rewrite our Taylor series for $\nu$ as
\begin{align*}
\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
\end{align*}
taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{\iota}_\alpha$, we learn that
\begin{align*}
\hat{\iota}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
& = \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha.
\end{align*}
We have now shown that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{\iota}_\alpha$ as $\zeta\in\zeta_\alpha+[0,e^{i\theta}\infty)$.
\end{proof}

\begin{remark}
Different choices of admissible $\theta$ correspond to different choices of thimbles $[\mathcal{C}_{\alpha}]\in H_N^{B}(X,zf)$, but the Borel transform of $\tilde{I}_{\alpha}$ does not depend on $\theta$. However, if $\theta_*\defeq\arg(\zeta_{\alpha}-\zeta_{\beta})$ and $\theta_{\pm}\defeq\theta_*\pm\delta$ for small $\delta$, then $I_{\alpha}(z)$ jumps on the intersection between $\operatorname{Re}(e^{i\theta_+}z)>0$ and $\operatorname{Re}(e^{i\theta_-}z)>0$. This is known as the Stokes phenomenon (see Section resurgence thimbles integrals).  
\end{remark}

\section{$3/2$ derivative formula}

In Theorem \ref{thm:maxim} we have seen that the asymptotic behaviour of $I_\alpha(z)$ has a fractional power contribution namely $\tilde{I}_{\alpha}(z)=e^{-z\zeta_\alpha}z^{-1/2}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}$, hence we have used the extended notion of Borel transform to deal with fractional powers. Now we will focus on the formal series $\tilde{\Phi}_\alpha(z)\defeq e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}=z^{1/2}\tilde{I}_\alpha(z)$ which does not contain any fractional power and we prove a fractional derivative formula which relates the Borel transform s $\hat{\varphi}_\alpha(\zeta)$ and $\hat{\iota}_{\alpha}(\zeta)$. Moreover we show that the $\hat{\varphi}_{\alpha}(\zeta)$ depends on $\nu$ and $df$ as well as $\hat{\iota}_{\alpha}(\zeta)$ does.

\begin{corollary}\label{int:deriv-formula} 
Under the same assumptions of Theorem \ref{thm:maxim}, for any $\zeta$ on the ray going rightward from $\zeta_\alpha$ in the direction of $\theta$, we have
\begin{multline}\label{formula1}
\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
\end{multline}
where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $e^{-i\theta}f^{-1}([\zeta_\alpha, \zeta ])$. Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $e^{-i\theta}f^{-1}(\zeta)$. \textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
\end{corollary}

\begin{proof}
Theorem~\ref{thm:frac-diff-borel} tells us that
\begin{align*}
\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha \\
& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
\end{align*}
It follows, from the proof of part $3$ of Theorem \ref{thm:maxim}, that
\begin{equation}\label{shifted-resum-valid}
\hat{\iota}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
\end{equation}
Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{\iota}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
Rewriting equation~\eqref{thimble-difference} as
\[ \hat{\iota}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
we can see that
\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{\iota}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right) = \hat{\varphi}_\alpha(\zeta). \]
\end{proof}

\subsection{Singularities} 
From equation \eqref{shifted-resum-valid} we see that singularities of $\hat{\iota}_{\alpha}(\zeta)$ in the Borel plane comes from either poles of $\nu$ or zeros of $df$. Instead, the fractional derivatives formula tells that singularities of $\hat{\varphi}_\alpha$ are given by convolutions of $\zeta^{-1/2}/\Gamma(1/2)$ with $\hat{\iota}_{\alpha}$. Since $\zeta^{-1/2}/\Gamma(1/2)$ is singular at $\zeta=0$ the set of singularities of $\hat{\varphi}_{\alpha}(\zeta)$ is exactly the same as the one of $\hat{\iota}_{\alpha}(\zeta)$. However, the type of singularities will change and we expect $\hat{\varphi}_{\alpha}(\zeta)$ to have only simple singularities.

\section{Contour argument}

\end{document}

### 2022-06-14 General thimble integral.tex
update

@@
 \end{equation}
-In Ecalle's formalism, $\int_{f^{-1}(\zeta)}\frac{\nu}{df}$ and $\hat{\iota}_\alpha$ are respectively a major and a minor of the singularity $\overset{\triangledown}{\iota}_\alpha$ and they differ by an holomorphic function (we will see this in the examples Section Airy, Bessel).
+In Ecalle's formalism, $\overset{\triangledown}{\iota}_\alpha\defeq\int_{f^{-1}(\zeta)}\frac{\nu}{df}$ and $\hat{\iota}_\alpha$ are respectively a major and a minor of the singularity and they differ by an holomorphic function (we will see this in the examples Section Airy, Bessel).
 
@@
 In Theorem \ref{thm:maxim} we have seen that the asymptotic behaviour of $I_\alpha(z)$ has a fractional power contribution namely $\tilde{I}_{\alpha}(z)=e^{-z\zeta_\alpha}z^{-1/2}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}$, hence we have used the extended notion of Borel transform to deal with fractional powers.
-Now we will focus on the formal series $\tilde{\Phi}_\alpha(z)\defeq e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}=z^{1/2}\tilde{I}_\alpha(z)$ which does not contain any fractional power and we prove a fractional derivative formula which relates the Borel transform s $\hat{\varphi}_\alpha(\zeta)$ and $\hat{\iota}_{\alpha}(\zeta)$.
+Now we will focus on the formal series $\tilde{\Phi}_\alpha(z)\defeq e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}=z^{1/2}\tilde{I}_\alpha(z)$ which does not contain any fractional power and we prove a fractional derivative formula which relates the Borel transforms $\hat{\varphi}_\alpha(\zeta)$ and $\hat{\iota}_{\alpha}(\zeta)$.
 Moreover we show that the $\hat{\varphi}_{\alpha}(\zeta)$ depends on $\nu$ and $df$ as well as $\hat{\iota}_{\alpha}(\zeta)$ does.
@@
 \begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)={\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} {\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
 \end{multline}
@@
 
+In the examples we noticed that $\hat{\varphi}_{\alpha}(\zeta)$ is always an hypergeometric function.
+In particular when there are only two critical values (see Airy, Bessel) the $\hat{\varphi}_{\alpha}(\zeta)$ is a Gaussian hypergeometric function ${}_2F_1\left(a,b;c;\tfrac{\zeta}{\zeta_\alpha}\right)$ with $c=2$ and $a+b=c+1$.
+Whereas, in the generalized Airy example (see Section ??) we get generalized hypergeometric functions ${}_3F_2\left(\mathbf{a};\mathbf{b};(\tfrac{\zeta}{\zeta_\alpha}-1)^2\right)$ and ${}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;(\tfrac{\zeta}{\zeta_\alpha})^2\right)$ with $|\mathbf{a}|=|\mathbf{b}|+1$.
+This behaviour reflects the resurgence properties of $\hat{\varphi}_{\alpha}$ (as well as the one of $\hat
+{\iota}_{\alpha}$), indeed the analytic continuation of $\hat{\varphi}_{\alpha}(\zeta)$ at $\zeta_\alpha$ is given in terms of $\hat{\varphi}_{\beta}(\zeta)$, $\zeta_\beta\neq\zeta_\alpha$ when $\hat{\varphi}_{\alpha}(\zeta), \hat{\varphi}_{\beta}(\zeta)$ are hypergeometric functions of the previous type.
+
+\begin{lemma}
+Let us assume $f$ has only two critical values $\zeta_\alpha=-\zeta_\beta$ and let $\hat{\varphi}_{\alpha}(\zeta)={}_2F_1(a,b;2;\tfrac{\zeta}{\zeta_\alpha})$ with $a+b=c+1$, then across the branch cut
+\begin{equation}
+\hat{\varphi}_{\alpha}(\zeta+i0)-\hat{\varphi}_{\alpha}(\zeta-i0)=C\,\,{}_2F_1\left(a,b;2;1+\tfrac{\zeta}{\zeta_{\beta}}\right)
+\end{equation}
+\begin{equation}
+\hat{\varphi}_{\beta}(\zeta+i0)-\hat{\varphi}_{\beta}(\zeta-i0)=-C\,\,{}_2F_1\left(a,b;2;1+\tfrac{\zeta}{\zeta_{\alpha}}\right)
+\end{equation}
+\end{lemma}
+\begin{proof}
+It follows from DLMF eq. 15.2.2. 
+\end{proof}
+
 \section{Contour argument}
 
+As noticed in proof of Theorem \ref{thm:maxim}, the integral $I_{\alpha}(z)$ can be written as 
+\begin{enumerate}
+\item[$(i)$] the Laplace transform of $\hat{\iota}_{\alpha}(\zeta)$
+\item[$(ii)$] the Hankel contour integral of the major $\overset{\triangledown}{\iota}_\alpha(\zeta)$
+\end{enumerate}
+and $\overset{\triangledown}{\iota}_\alpha(\zeta)=\hat{
+\iota}_{\alpha}(\zeta)+\text{hol.fct.}$.
+In the applications we have evidence that $\overset{\triangledown}{\iota}_\alpha(\zeta)$ is an algebraic hypergeometric function and when there are only two critical values, it decomposes as a sum of two germs of holomorphic functions at each critical values respectively (see {\tt airy-resurgence} Section 6.1, 6.3).
 \end{document}

### 2022-06-23 General thimble integral.tex
Add Zorich's book to bibliography
Make other tweaks for e-mail to Dunne and Ünsal.

@@
 \author{
-Veronica Fantini 
+Veronica Fantini, Aaron Fenyes
 }
@@
 \begin{enumerate}
-\item We may drop the assumption of non degenerate critical points for $f$, however the asymptotic expansion of $I_\alpha(z)$ will depend on the order $m$ such that $f^{(m)}(x_\alpha)\neq 0$ and $f^{(j)}(x_\alpha)=0$ for every $j=1,...,m-1$ (see [Zorich] Theorem 1 Section 19.2.5).
+\item We may drop the assumption of non degenerate critical points for $f$, however the asymptotic expansion of $I_\alpha(z)$ will depend on the order $m$ such that $f^{(m)}(x_\alpha)\neq 0$ and $f^{(j)}(x_\alpha)=0$ for every $j=1,...,m-1$ \cite[Theorem 1 Section 19.2.5]{math-analysis-ii}.
 \item in [Malgrange74] (see also Chapter 5 of [Mistergard Phd thesis] for a general review), the author computes the asymptotic expansion of exponential integrals for $N>1$ which get logarithmic terms like
@@
 \[ I_\alpha(z) \sim  e^{-z\zeta_\alpha}\int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\operatorname{Re}(ze^{i\theta}) \to \infty$ (see Lemma 1 in Section 19.2.2  Zorich).
-\textbf{[I need to learn how this works!
-Do we get asymptoticity at all orders?
----Aaron]} Plugging in the Taylor series above, we get
+as $\operatorname{Re}(ze^{i\theta}) \to \infty$ \cite[Lemma 1 in Section 19.2.2]{math-analysis-ii}). Plugging in the Taylor series above, we get
 \begin{align*}
@@
 
-By Watson's Lemma (see Lemma 4 Section 19.2.2 Zorich)
+By Watson's Lemma~\cite[Lemma 4, \S 19.2.2]{math-analysis-ii}
 
@@
 I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-&=\int_{\mathcal{H}_{\alpha}}e^{-z\zeta}\left(\int_{f^{-1}(\zeta)}\frac{\nu}{df}\right)d\zeta \\
+& = \int_{\mathcal{H}_{\alpha}} e^{-z\zeta} \left.\frac{\nu}{df}\right|_{f^{-1}(\zeta)}\,d\zeta \\
 & = \int_{\zeta_\alpha}^{e^{i\theta}\infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
 \end{align*}
-where $\mathcal{H}_{\alpha}$ is the Hanckel contour through the point $\zeta_{\alpha}$ (see Figure \cite{fig.paths}) with ends in the $\theta$ direction.
+where $\mathcal{H}_{\alpha}$ is the Hankel contour through the point $\zeta_{\alpha}$ (see Figure \cite{fig.paths}) with ends in the $\theta$ direction.
 \begin{figure}
@@
 In the applications we have evidence that $\overset{\triangledown}{\iota}_\alpha(\zeta)$ is an algebraic hypergeometric function and when there are only two critical values, it decomposes as a sum of two germs of holomorphic functions at each critical values respectively (see {\tt airy-resurgence} Section 6.1, 6.3).
+
+\bibliographystyle{amsplain}
+\bibliography{airy-resurgence.bib}
+
 \end{document}

### 2022-06-30 airy-resurgence.tex
Bound norms of algebraic integral operators

@@
 \newcommand{\maps}{\colon}
+
+% group action
+\newcommand{\acts}{\mathbin{\raisebox{\depth}{\rotatebox{-90}{$\circlearrowright$}}}}
 
@@
 \subsection{Existence of solutions}
-\subsubsection{Function spaces for contour integration}
-Take a simply connected open set $\Omega$ that touches but doesn't contain $\zeta = 0$.
+\subsubsection{Algebraic integral operators}
+Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
 Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
@@
 
-If you give a Riemann surface a metric which is compatible with its conformal structure, you get a norm on each tangent space.
-A {\em density} on a Riemann surface is a norm that arises in this way.
-Given a density $\rho$ on $\Omega$, let $\ell_\rho$ be the continuous function on $\Omega$ that measures distance from $\zeta = 0$ with respect to $\rho$.
-The value of $\ell_\rho$ at $a \in \Omega$ is the infimal length of a rectifiable path that runs from $\zeta = 0$ to $a$ within $\Omega$.
-Keep in mind that $\Omega$ touches but doesn't contain $\zeta = 0$, and $\ell_\rho$ is only well-defined when $\rho$ puts $\zeta = 0$ at finite distance from the points in $\Omega$.
-\textcolor{magenta}{[...]}
+We'll study integral operators $\mathcal{G} \acts \holoL{\infty}(\Omega)$ of the form
+\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
+where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
+The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
+Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
+That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
 
-\color{gray}
-A bounded holomorphic map
+For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure.
+The square of a density is a Riemannian metric.
+Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
+The bound
 \begin{align*}
-\Omega & \to \holoL{1}(\Omega) \\
-\alpha & \mapsto g_\alpha
+\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
+& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
+& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
 \end{align*}
-defines a bounded linear operator
-\[ \mathcal{G}f\big|_{\zeta = \alpha} = \int_0^\alpha  g_\alpha f \]
-on $\holoL{\infty}(\Omega)$. Noting that
-\color{black}
-
-%%with\footnote{We're using the operator norm on the left-hand side and the $L^1$ norm on the right-hand side.} $\|\mathcal{G}\| = \sup_{\alpha \in \Omega} \|g_\alpha\|_1$.
+holds for any integration path. Taking the infimum over all paths, we see that
+\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
+so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
+\subsubsection{The example of fractional integrals}
+Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\nu}$ with $\nu \in (-\infty, 1)$, we get the fractional integral $\partial^{\nu-1}_{\zeta \text{ from } 0}$.
+The density $|\zeta(a) - \zeta|^{-\nu}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
+It follows that
+\begin{align*}
+\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\nu}\,dt \\
+& = \tfrac{1}{1-\nu} |\zeta(a)|^{1-\nu},
+\end{align*}
+so
+\[ \|\partial^{\nu-1}_{\zeta \text{ from } 0}\| \le \sup_\Omega \tfrac{1}{1-\nu} |\zeta|^{1-\nu}. \]
+In particular, $\partial^{\nu-1}_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ whenever $\|\zeta\|_\infty < (1-\nu)^{1/(1-\nu)}$.
 \subsection{Order shifting}\label{shifting}

### 2022-06-30 airy-resurgence.tex
Switch to more convenient exponent

@@
 \subsubsection{The example of fractional integrals}
-Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\nu}$ with $\nu \in (-\infty, 1)$, we get the fractional integral $\partial^{\nu-1}_{\zeta \text{ from } 0}$.
-The density $|\zeta(a) - \zeta|^{-\nu}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
+Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
+The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
 It follows that
 \begin{align*}
-\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\nu}\,dt \\
-& = \tfrac{1}{1-\nu} |\zeta(a)|^{1-\nu},
+\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
+& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
 \end{align*}
 so
-\[ \|\partial^{\nu-1}_{\zeta \text{ from } 0}\| \le \sup_\Omega \tfrac{1}{1-\nu} |\zeta|^{1-\nu}. \]
-In particular, $\partial^{\nu-1}_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ whenever $\|\zeta\|_\infty < (1-\nu)^{1/(1-\nu)}$.
+\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
+In particular, when $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, 0)$.
 \subsection{Order shifting}\label{shifting}

### 2022-07-03 General thimble integral.tex
update
I've updated the introduction and the bibliography

--- 2022-06-14 General thimble integral.tex
@@
 
-\begin{theorem}\label{thm:maxim} Let $N=1$.
+\begin{theorem}[Theorem ??]\label{thm:maxim} Let $N=1$.
 Let ${I}_{\alpha}(z)$ defined as in \eqref{exp-int} for every critical point $x_\alpha$.
@@
 Due to the presence of logarithmic terms, the definition of Borel transform has to be further extended  (see [Mistergard phd] Definition pag 5) and the study of Borel regularity becomes more involved.
+\item in the proof of Theorem \ref{thm:maxim} we will derive formula \eqref{exp-int} using Watson's lemma.
+However, the same result can be computed from geometric arguments as in Theorem 5.3.3 [Mistergard phd].
 \end{enumerate}
@@
 This behaviour reflects the resurgence properties of $\hat{\varphi}_{\alpha}$ (as well as the one of $\hat
-{\iota}_{\alpha}$), indeed the analytic continuation of $\hat{\varphi}_{\alpha}(\zeta)$ at $\zeta_\alpha$ is given in terms of $\hat{\varphi}_{\beta}(\zeta)$, $\zeta_\beta\neq\zeta_\alpha$ when $\hat{\varphi}_{\alpha}(\zeta), \hat{\varphi}_{\beta}(\zeta)$ are hypergeometric functions of the previous type.
+{\iota}_{\alpha}$), meaning the analytic continuation of $\hat{\varphi}_{\alpha}(\zeta)$ at $\zeta_\alpha$ is given in terms of $\hat{\varphi}_{\beta}(\zeta)$, $\zeta_\beta\neq\zeta_\alpha$ when $\hat{\varphi}_{\alpha}(\zeta), \hat{\varphi}_{\beta}(\zeta)$ are hypergeometric functions of the previous type.
 
@@
 
+It would be interesting to further investigate the relationship between the properties of resurgent functions (with finitely many singularities in the Borel plane) and hypergeometric functions.
+
 \section{Contour argument}
@@
 In the applications we have evidence that $\overset{\triangledown}{\iota}_\alpha(\zeta)$ is an algebraic hypergeometric function and when there are only two critical values, it decomposes as a sum of two germs of holomorphic functions at each critical values respectively (see {\tt airy-resurgence} Section 6.1, 6.3).
+
 \end{document}

### 2022-07-03 Introduction.tex
update
I've updated the introduction and the bibliography

--- 2022-07-03 General thimble integral.tex
@@
 \usepackage{fancyhdr}
+\usepackage{tikz-cd}
 %\renewcommand{\sectionmark}[1]{\markboth{\thesection\ #1}{}}
@@
 \DeclareMathOperator{\Ai}{Ai}
+\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
+\newcommand{\series}[1]{#1_\bullet}
 
 \DeclareRobustCommand{\subtitle}[1]{\\#1}
-\title[General thimbles integrals]{General thimbles integrals\\ [1ex]
+\title[Borel regularity for exponential integrals and ODEs]{Borel regularity for exponential integrals and ODEs\\ [1ex]
   }
@@
 \author{
-Veronica Fantini 
+Veronica Fantini and  Aaron Fenyes 
 }
@@
 \maketitle
+\tableofcontents
 
-\section{Proof of Borel regularity}
+\section{Introduction}
 
-We are going to prove Theorem 5.1 {\tt draft2}. 
-Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
+\subsection{Motivation}
+
+\subsection{What are exponential integrals}
+
+Let $X$ be an $n$-dimensional algebraic variety, we consider exponential integrals of the form 
+\begin{equation}
+\label{:exp_integral}
+I(z)=\int_{\mathcal{C}}e^{-zf}\nu
+\end{equation}
+where $f\colon X\to \C$ is an algebraic function, $\nu\in\Gamma(X,\Omega^n)$, $z\in\C$ and $\mathcal{C}$ is an $n$-cycle of integration such that the integral is well defined.
+Assuming $\theta\defeq\arg(z)$ fixed, we define for every $c>0$
+\begin{align*}
+S^+_c\defeq\lbrace \zeta\in\C\vert \mathrm{Re}(\zeta e^{i\theta})\geq c\rbrace\\
+S^-_c\defeq\lbrace \zeta\in\C\vert \mathrm{Re}(\zeta e^{i\theta})\leq c\rbrace.
+\end{align*}
+and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)=H_{\bullet}(X,f^{-1}(S_c^+))\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
+points $\zeta_\alpha\defeq f(x_\alpha)$ where $df(x_\alpha)=0$ \footnote{In dimension $n>1$ there are other singular values due to the fact that $f$ is not proper.
+However under suitable assumptions it is possible to overcome this issue (see \cite{pham} part $1$, $\S 2$).}).
+Then we assume $[\mathcal{C}]\in H_n(X,zf)$.
+
+Notice that $I(z)$ only depends on the class of $\mathcal{C}$ and on the class of $[\nu]\in H_{dR}^n(X,zf)\defeq\mathbb{H}^n\left(X,(\Omega^\bullet_X,d_W\defeq e^{zf}\circ d\circ e^{-zf})\right)$: indeed let $\mathcal{C}'=\mathcal{C}+\partial\gamma\in [\mathcal{C}]$,
+\begin{align*}
+\int_{\mathcal{C}'}e^{-zf}\nu=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\partial\gamma}e^{-zf}\nu=\int_{\mathcal{C}}e^{-zf}\nu
+\end{align*} 
+because $e^{-zf}$ is rapidly decaying at $\partial\gamma$. Similarly, if $\nu'=\nu+d_W\eta\in [\nu]$
+\begin{multline*}
+\int_{\mathcal{C}}e^{-zf}\nu'=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\mathcal{C}}e^{-zf}d_{W}\eta=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\mathcal{C}}d(e^{-zf}\eta)=\\
+=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\partial\mathcal{C}}e^{-zf}\eta=\int_{\mathcal{C}}e^{-zf}\nu.
+\end{multline*}
+Moreover, for $\theta$ generic, i.e.
+$\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the singular values of $f$ of the homology relative to these singular values (see \cite{pham}\cite{KKP}):
+\begin{align}\label{decomposition H_B}
+H_\bullet(X,zf)=\bigoplus_{\alpha}H_\bullet\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)
+\end{align}     
+where $B_\alpha(\varepsilon)\defeq\lbrace \zeta \in\C\big\vert\,\, |\zeta-\zeta_\alpha|<\varepsilon\rbrace$ and $S_\alpha^+(\theta,\varepsilon)\defeq B_\alpha(\varepsilon)\cap\lbrace \mathrm{Re}(\zeta e^{i\theta})\geq \tfrac{\varepsilon}{2}\rbrace$ (see Figure \ref{fig:relative_homology}).
+\begin{figure}
+\caption{Relative homology}\label{fig:relative_homology}
+\end{figure}
+We furthermore assume the following:
+\begin{assumption}\label{assumption_on_f}
+The map $f\colon X\to\C$ has isolated, simple and non degenerate critical values $\zeta_\alpha$. 
+\end{assumption}
+
+which guarantees that 
+\begin{itemize}
+\item $H_k\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ is isomorphic to $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))$, where $B_\alpha
+^M(\varepsilon)$ is an open ball centred at $x_\alpha$ of radius $\varepsilon$ such that for every $\varepsilon'<\varepsilon$ $B_\alpha(\varepsilon')$ is transverse to $f^{-1}(\zeta_\alpha)$. 
+\item $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))=0$ if $k\neq n$ and $H_{n-1}(B_\alpha^M(\varepsilon)\,\cap f^{-1}(\zeta-\zeta_\alpha))=\Z^\mu$, where $\mu$ is called the Milnor number.
+\end{itemize}
+\color{magenta}
+Let $\theta=0$, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$.
+The Lefschetz thimbles $\Gamma_{\alpha,z}$ are defined as follows (see \cite{pham}): denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then
+\begin{equation}
+\mathcal{C}_{\alpha,z}\defeq\lbrace x\in X\vert x_1''=x_2''=...=x_n''=0, x_1'^2+...+x_n'^2\leq \zeta-\zeta_\alpha\rbrace
+\end{equation}
+\begin{figure}
+\caption{Lefschetz thimbles}\label{Lefschetz_thimbles}
+\end{figure}
+In addition, they generate the relative homology for every critical values \textbf{Why?}. If $\theta\neq 0$ we consider $xe^{i\theta/2}$.
+
+\textbf{[add duality]}  
+\color{black}
+
+Therefore for $\theta$ generic, the integral $I(z)$ can be decomposed as sum over Lefschetz thimbles: we denote 
+\begin{equation}\label{int_alpha}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_{\alpha,z}}e^{-zf}\nu
+\end{equation}
+and we refer to $I_{\alpha}(z)$ as a thimble integral. Then as a consequence of Pham's duality result ($\S 5$ \cite{pham}), for every $\mathcal{C}\in H_n(X,zf)$
+\begin{align*}
+I(z)=\sum_{\alpha}(-1)^{n(n-1)/2}\langle \mathcal{C}_{\alpha,\theta+\pi},\mathcal{C}\rangle I_{\alpha}(z). 
+\end{align*}
+
+\subsection{Borel regularity}
+
+Borel resummation is a way of turning a formal power series
+\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
+with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
+Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
+When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
+Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
+%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
+%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
+\begin{itemize}
+\item \textbf{Having a good asymptotic approximation}
+
+Let $R_N$ be the difference between a function and the partial sum
+\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+\item \textbf{Satisfying a singular differential equation}
+
+\begin{itemize}
+\item Think about conditions where this works.
+\item Maybe the correct place is the setting of Ecalle's formal integral. See \S 5.2.2.1 of Delabaere's {\em Divergent Series, Summability and Resurgence III}.
+\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform.
+\item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resurgence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.
+\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+\end{itemize}
+\item \textbf{Being a thimble integral}
+
+Under the previous assumptions, we can now state a Borel regularity result for thimble integrals:
+
+\begin{theorem}\label{thm:borel integrals}
+Borel regularity for thimbles integrals can be stated a the commutativity of the following diagram:
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\end{theorem}
+
+A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+We give a proof of Theorem \ref{thm:borel integrals} in Section ??
+\ref{thm:maxim} when $N=1$, and the proof is based on the fact that $I_\alpha(z)$ can be rewritten as the Laplace transform--type integral.
+In higher dimension the same result was stated in \cite{Dunne-Unsal 15} (but the proof was not written).
+
+Generically, $\tilde{I}_{\alpha}(z)$ is a divergent series whose coefficients factorially grow and, as proved by Berry and Howls \cite{BH}\cite{H} the divergence of $\tilde{I}_{\alpha}(z)$ encodes contributions from the other critical points of $f$ in the form of \textit{exact resurgence relation} (see equation 19 \cite{BH}).
+Indeed, the Borel transform $\hat{\iota}_\alpha(\zeta)$ yet contains information about the Borel transform $\hat{\iota}_{\beta}(\zeta)$ at other critical values $\zeta_\beta$.
+This is the idea of resurgence of $\tilde{I}_{\alpha}(z)$ \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}.
+However, since $f$ has finitely many critical points and $\nu$ is meromorphic, Borel--Laplace summability properties and resurgence of exponential integrals are straightforward to be proven.
+However, in order to completely describe the Borel plane one needs to compute the Stokes data which provide the analytic continuation across the branch cut.
+In particular for a certain class of exponential integrals the analytic theory developed by J.
+Ecalle to compute the Stokes data (see \cite{Ecalle}\cite{diverg-resurg-i}\cite{Dorigoni}\cite{Schiappa}) has a geometric interpretation relying on intersection theory of dual relative homology classes in the sense of F.
+Pham \cite{pham} (see also \cite{Maxim_lectures}\cite{Maxim_slide_ERC}).
+\end{itemize}
+
+\subsection{Stokes phenomena for exponential integrals}
+So far we have considered $\theta=\arg(z)$ fixed and generic (i.e.
+$\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$), but as we let $\theta$ varying $I_{\alpha}(z)$ becomes a multivalued function, indeed when $\theta$ crosses a Stokes ray $\ell_{\alpha\beta}\defeq\arg(\zeta_\alpha-\zeta_\beta)\R$, $I_\alpha(z)$ jumps.
+Computing the jumps of $I_{\alpha}(z)$ is equivalent to determine the analytic continuation of $I_\alpha(z)$ for $z\in\C$.
+There are different ways to compute the Stokes jumps across the rays $\ell_{\alpha\beta}$: one is purely geometric, based on the way the decomposition \eqref{decomposition H_B} varies as $\theta$ varies.
+Another one is based on the resurgence analysis of the asymptotic expansion of $I_{\alpha}(z)$ as $\mathrm{Re}(z e^{i\theta})\to +\infty$.
+In Section \ref{sec:Stokes} we prove that the geometric and the resurgence approach to compute the Stokes jumps are equivalent:
+\begin{theorem}[Theorem \ref{Stokes}]
+
+\end{theorem}
+
+\subsubsection{Thimbles integrals [Kontsevich]: geometric computation of Stokes constants}
+
+\subsubsection{ ODE and fractional derivative formula [draft2]}
+
+\subsubsection{If hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions }
+
+\subsection{Plan of the paper}
+
+\section{Formalism of the Laplace transform}
+
+\section{Borel regularity}
+
+\subsection{ODEs}
+
+\subsection{Thimble integrals}
+We are going to prove Theorem \ref{thm:borel integrals}. 
+Let $X$ be a $n$-dimensional algebraic variety, $f\colon X\to\C$ be an algebraic function with simple, isolated, non-degenerate critical points, and $\nu\in\Gamma(X,\Omega^n)$, and set
 \begin{equation}
@@
 where $\mathcal{C}$ is a suitable contour such that the integral is well defined.
-Indeed, $I(z)$ represents a pairing between a relative homology class $\mathcal{C}\in H_{N}^{B}(X,zf)$ and a cohomology class $\nu\in H_{dR}^N(X,zf)$ (see Section 1.3.1 Thimble integrals in the introduction).
+Indeed, $I(z)$ represents the pairing between a relative homology class $[\mathcal{C}]\in H_{n}^{B}(X,zf)$ and a cohomology class $[\nu]\in H_{dR}^n(X,zf)$ (see Section 1.3.1 Thimble integrals in the introduction).
 Let us restrict to one dimensional $X$.
-For any Morse critical points $x_\alpha$\footnote{By Morse critical points we mean non--degenerate isolated critical points.} of $f$, the saddle point approximation allows to compute the asymptotic expansion of $I_\alpha(z)$
+For any critical points $x_\alpha$ (satisfying the previous assumptions) of $f$, the saddle point approximation allows to compute the asymptotic expansion of $I_\alpha(z)$
 \begin{equation}\label{exp-int}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } \operatorname{Re} (ze^{i\theta})\to\infty
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{k\geq 0}a_{\alpha,k}z^{-k} \qquad \text{ as } \operatorname{Re} (ze^{i\theta})\to\infty
 \end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
+where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
 Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, e^{i\theta}\infty)$, where $\zeta_\alpha := f(x_\alpha)$.
 
-\begin{theorem}[Theorem ??]\label{thm:maxim} Let $N=1$.
+\begin{theorem}[Theorem ??]\label{thm:maxim} Let $n=1$.
 Let ${I}_{\alpha}(z)$ defined as in \eqref{exp-int} for every critical point $x_\alpha$.
@@
 \begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{I}_\alpha(z)=e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n}$ is Gevrey-1.
+\item\label{int:series-gevrey} The series $\tilde{I}_\alpha(z)=e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{k\geq 0}a_{\alpha,k}z^{-k}$ is Gevrey-1.
 \item\label{int:resum-converges} The series $\tilde{\iota}_\alpha(\zeta)\defeq\mathcal{B}(\tilde{I}_\alpha)$ converges near $\zeta=\zeta_{\alpha}$.
@@
 \item We may drop the assumption of non degenerate critical points for $f$, however the asymptotic expansion of $I_\alpha(z)$ will depend on the order $m$ such that $f^{(m)}(x_\alpha)\neq 0$ and $f^{(j)}(x_\alpha)=0$ for every $j=1,...,m-1$ (see [Zorich] Theorem 1 Section 19.2.5).
-\item in [Malgrange74] (see also Chapter 5 of [Mistergard Phd thesis] for a general review), the author computes the asymptotic expansion of exponential integrals for $N>1$ which get logarithmic terms like
-\[\tilde{I}(z)=\sum_{j\in A} \sum_{n\geq 0}\sum_{q=0}^{N-1}a_{n,q,j}z^{-n-j}(\log z)^q,\] for $A\subset\Q_{\geq 0}$ finite.
+\item in [Malgrange74] (see also Chapter 5 of [Mistergard Phd thesis] for a general review), the author computes the asymptotic expansion of exponential integrals for $n>1$ which get logarithmic terms like
+\[\tilde{I}(z)=\sum_{j\in A} \sum_{k\geq 0}\sum_{q=0}^{n-1}a_{k,q,j}z^{-k-j}(\log z)^q,\] for $A\subset\Q_{\geq 0}$ finite.
 Due to the presence of logarithmic terms, the definition of Borel transform has to be further extended  (see [Mistergard phd] Definition pag 5) and the study of Borel regularity becomes more involved.
@@
 I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
+\[ \nu = \sum_{k \ge 0} b_k^\alpha \tau^k\,d\tau \]
 that converges in some disk $|\tau| < \varepsilon$.
@@
 \begin{align*}
- I_\alpha(z) & \sim e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau\\
-& = 2e^{-z\zeta_\alpha}\int_{0}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
+ I_\alpha(z) & \sim e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{k \ge 0} b_k^\alpha \tau^k\,d\tau \\
+& = e^{-z\zeta_\alpha}\int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{k \ge 0} b_{2k}^\alpha \tau^{2k}\,d\tau\\
+& = 2e^{-z\zeta_\alpha}\int_{0}^\varepsilon e^{-z\tau^2/2} \sum_{k \ge 0} b_{2k}^\alpha \tau^{2k}\,d\tau.
 \end{align*}
@@
 \begin{align*}
-I_\alpha(z) &\sim e^{-z\zeta_\alpha}\sum_{n \ge 0} b_{2n}^\alpha \Gamma\left(n+\tfrac{1}{2}\right)2^{n+1/2}z^{-n-1/2}\\
-&= e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n \ge 0} b_{2n}^\alpha (2n-1)!!z^{-n-1/2}
+I_\alpha(z) &\sim e^{-z\zeta_\alpha}\sum_{k \ge 0} b_{2k}^\alpha \Gamma\left(k+\tfrac{1}{2}\right)2^{k+1/2}z^{-k-1/2}\\
+&= e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{k \ge 0} b_{2k}^\alpha (2k-1)!!z^{-k-1/2}
 \end{align*}
@@
 Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\sim (\pi n)^{-1/2}\,4^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{4}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_\alpha$ is Gevrey-1.%
+We now see that $a_{\alpha,k} = (2k-1)!!\,b_{2k}^\alpha$ in the statement of the theorem.
+We know from the definition of $\varepsilon$ that $\left|b_k^\alpha\right| \varepsilon^k \lesssim 1$.
+Recalling that $(2k - 1)!!
+\sim (\pi k)^{-1/2}\,4^k\,k!$ as $k \to \infty$, we deduce that $|a_{\alpha,k}| \lesssim \left(\tfrac{4}{\varepsilon^2}\right)^k\,k!\,$, showing that $\tilde{I}_\alpha$ is Gevrey-1.%
 
@@
 \begin{align*}
-\tilde{\iota}_{\alpha}\defeq \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} 
+\tilde{\iota}_{\alpha}\defeq \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{k \ge 0} (2k-1)!!\,b_{2k}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{k-1/2}}{\Gamma\big(k+\tfrac{1}{2}\big)} 
 \end{align*}
 
-Since ${(2n-1)!!}=\pi^{-1/2} 2^n{\Gamma\left(n+\tfrac{1}{2}\right)}$ and $|b_n^\alpha|\epsilon^n\lesssim 1$, then $\tilde{\iota}_{\alpha}(\zeta)$ has a finite radius of convergence.
+Since ${(2k-1)!!}=\pi^{-1/2} 2^k{\Gamma\left(k+\tfrac{1}{2}\right)}$ and $|b_k^\alpha|\epsilon^n\lesssim 1$, then $\tilde{\iota}_{\alpha}(\zeta)$ has a finite radius of convergence.
 
@@
 \begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
+\nu & = \sum_{k \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{k/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
+& = \sum_{k \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(k - 1)/2}\,df,
 \end{align*}
@@
 \begin{align*}
-\hat{\iota}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
+\hat{\iota}_\alpha(\zeta) & = \left[ \sum_{k \ge 0} b_k^\alpha [2(f - \zeta_\alpha)]^{(k - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
+& = \sum_{k \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(k - 1)/2} - (-1)^{k-1}[2(\zeta - \zeta_\alpha)]^{(k - 1)/2} \Big) \\
+& = \sum_{k \ge 0} 2 b_{2k}^\alpha [2(\zeta - \zeta_\alpha)]^{k - 1/2} \\
+& = \sum_{k \ge 0} 2^{k+1/2} b_{2k}^\alpha (\zeta - \zeta_\alpha)^{k - 1/2} \\
 & = \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha.
@@
 \begin{remark}
-Different choices of admissible $\theta$ correspond to different choices of thimbles $[\mathcal{C}_{\alpha}]\in H_N^{B}(X,zf)$, but the Borel transform of $\tilde{I}_{\alpha}$ does not depend on $\theta$.
+Different choices of admissible $\theta$ correspond to different choices of thimbles $[\mathcal{C}_{\alpha}]\in H_n^{B}(X,zf)$, but the Borel transform of $\tilde{I}_{\alpha}$ does not depend on $\theta$.
 However, if $\theta_*\defeq\arg(\zeta_{\alpha}-\zeta_{\beta})$ and $\theta_{\pm}\defeq\theta_*\pm\delta$ for small $\delta$, then $I_{\alpha}(z)$ jumps on the intersection between $\operatorname{Re}(e^{i\theta_+}z)>0$ and $\operatorname{Re}(e^{i\theta_-}z)>0$.
@@
 
-\section{$3/2$ derivative formula}
+\subsubsection{$3/2$ derivative formula}
 
-In Theorem \ref{thm:maxim} we have seen that the asymptotic behaviour of $I_\alpha(z)$ has a fractional power contribution namely $\tilde{I}_{\alpha}(z)=e^{-z\zeta_\alpha}z^{-1/2}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}$, hence we have used the extended notion of Borel transform to deal with fractional powers.
-Now we will focus on the formal series $\tilde{\Phi}_\alpha(z)\defeq e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{n\geq 0}a_{\alpha,n}z^{-n}=z^{1/2}\tilde{I}_\alpha(z)$ which does not contain any fractional power and we prove a fractional derivative formula which relates the Borel transforms $\hat{\varphi}_\alpha(\zeta)$ and $\hat{\iota}_{\alpha}(\zeta)$.
+In Theorem \ref{thm:maxim} we have seen that the asymptotic behaviour of $I_\alpha(z)$ has a fractional power contribution, namely \[\tilde{I}_{\alpha}(z)=e^{-z\zeta_\alpha}z^{-1/2}\sqrt{2\pi}\sum_{k\geq 0}a_{\alpha,k}z^{-k},\] hence we have used the extended notion of Borel transform to deal with fractional powers.
+Now we will focus on the formal series $\tilde{\Phi}_\alpha(z)\defeq e^{-z\zeta_\alpha}\sqrt{2\pi}\sum_{k\geq 0}a_{\alpha,k}z^{-k}=z^{1/2}\tilde{I}_\alpha(z)$ which does not contain any fractional power and we prove a fractional derivative formula which relates the Borel transforms $\hat{\varphi}_\alpha(\zeta)$ and $\hat{\iota}_{\alpha}(\zeta)$.
 Moreover we show that the $\hat{\varphi}_{\alpha}(\zeta)$ depends on $\nu$ and $df$ as well as $\hat{\iota}_{\alpha}(\zeta)$ does.
@@
 \begin{align*}
-\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha  = \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
 \end{align*}
@@
 
-\subsection{Singularities} 
+\subsubsection{Singularities} 
 From equation \eqref{shifted-resum-valid} we see that singularities of $\hat{\iota}_{\alpha}(\zeta)$ in the Borel plane comes from either poles of $\nu$ or zeros of $df$.
@@
 
-\section{Contour argument}
+\subsubsection{Contour argument}
 
@@
 
+\section{Stokes phenomenon for thimble integrals}
+
+\section{Examples}
+
+\bibliographystyle{amsplain}
+\bibliography{airy-resurgence}
+
 \end{document}

### 2022-07-04 airy-resurgence.tex
Start sketching solutions for singular integral equations

@@
 \[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
-In particular, when $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, 0)$.
+In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
+\subsubsection{Fractional integral equations near a regular singular point}
+Consider an integral operator $\mathcal{J}$ of the form
+\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
+where:
+\begin{itemize}
+\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
+\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
+\item $p$ has a first-order zero at $\zeta = 0$.
+\end{itemize}
+
+\textcolor{DodgerBlue}{We want to solve the equation $\mathcal{J}f = 0$.
+Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty}(\Omega)$.}
+
+\color{SeaGreen}
+\begin{prop}\label{prop:frac-mollify}
+If $f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^\alpha)$ with $\alpha \in (-1, \infty)$, then $\partial^\lambda_{\zeta \text{ from } 0}\,f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^{\alpha-\lambda})$ for all $\lambda \in (-\infty, 0)$.
+\end{prop}
+\color{magenta}
+\begin{proof}
+??????
+\end{proof}
+\color{SeaGreen}
+\begin{prop}\label{prop:frac-int-growth}
+For any $f \in \holoL{\infty}(\Omega)$ and $\lambda \in (-\infty, 0)$, the bound
+\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\,f\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \|f\|_\infty \]
+holds pointwise throughout $\Omega$.
+\end{prop}
+\color{magenta}
+\begin{proof}
+??????
+\end{proof}
+\color{black}
+
+Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+Since $p$, $q$, and $r_\lambda$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
+\begin{alignat*}{2}
+p & = p'_0 \zeta &\;+\;& \tilde{p} \zeta^2 \\
+q & = q_0 &\;+\;& \tilde{q} \zeta \\
+\textcolor{orange}{r_\lambda} & = r_{\lambda,0} &\;+\;& \tilde{r}_\lambda \zeta,
+\end{alignat*}
+where $\tilde{p}, \tilde{q} \in \holoL{\infty}(\Omega)$ extend holomorphically over $\zeta = 0$ too. For any $\tau \in (0, \infty)$,
+\begin{align*}
+\mathcal{J} \zeta^{\tau-1} & = p'_0 \zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(q_0 \zeta^{\tau-1}\big) + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big) \\
+& = (p'_0 + q_0/\tau)\zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).
+\end{align*}
+Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
+\begin{align*}
+\mathcal{J} \zeta^{\tau-1} & = \textcolor{SeaGreen}{\tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).} \\
+\mathcal{J} \zeta^{\tau-1} & = \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_{\lambda,0} \zeta^{\tau-1} + \tilde{r}_\lambda \zeta^\tau\big) \\
+& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-1-\lambda} + \partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right]} \\
+& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-(\lambda+1)} \right] + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau.}
+\end{align*}
+Now we can rewrite the equation $\mathcal{J}(\zeta^{\tau-1} + \tilde{f}) = 0$ as
+\begin{align*}
+\mathcal{J} \zeta^{\tau-1} + \left[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = 0 \\
+\mathcal{J} \zeta^{\tau-1} + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = -p\tilde{f}.
+\end{align*}
+Observing that
+\[ \frac{1}{p} = \frac{\zeta^{-1}}{p_0 + \tilde{p} \zeta}, \]
+we have
+\begin{align*}
+\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} + \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right] \right] \\
+\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} \right] \right] + \frac{1}{p_0 + \tilde{p} \zeta} \left[ \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau
+\end{align*}
+Proposition~\ref{prop:frac-int-growth} guarantees that
+\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \le |\zeta|\,\big\|\tilde{q} \zeta^\tau\big\|_\infty, \]
+so
+\begin{align*}
+\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \\
+& \le \big\|\tilde{q} \zeta^\tau\big\|_\infty \\
+& \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty.
+\end{align*}
+Similarly,
+\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty, \]
+so
+\begin{align*}
+\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \\
+& \le (-\tfrac{1}{\lambda}) |\zeta|^{-(\lambda+1)} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty \\
+& \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{-(\lambda+1)}\big\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
+& = \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty.
+\end{align*}
+In short,
+\begin{align*}
+\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big\|_\infty & \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
+\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big\|_\infty & \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty
+\end{align*}
 \subsection{Order shifting}\label{shifting}

### 2022-07-04 General thimble integral.tex

--- 2022-06-23 General thimble integral.tex
@@
 \bibliography{airy-resurgence.bib}
-
 \end{document}

### 2022-07-04 Introduction.tex

@@
 \end{align*}
-and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)=H_{\bullet}(X,f^{-1}(S_c^+))\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
+and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)=H_{\bullet}\left(X,f^{-1}(S_c^+);\Z\right)\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
 points $\zeta_\alpha\defeq f(x_\alpha)$ where $df(x_\alpha)=0$ \footnote{In dimension $n>1$ there are other singular values due to the fact that $f$ is not proper.
@@
 \end{itemize}
+
+where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
 \color{magenta}
 Let $\theta=0$, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$.
-The Lefschetz thimbles $\Gamma_{\alpha,z}$ are defined as follows (see \cite{pham}): denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then
+Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points.
+We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\Gamma_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}): denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then
 \begin{equation}
@@
 \end{equation}
-and we refer to $I_{\alpha}(z)$ as a thimble integral. Then as a consequence of Pham's duality result ($\S 5$ \cite{pham}), for every $\mathcal{C}\in H_n(X,zf)$
+and we refer to $I_{\alpha}(z)$ as a thimble integral. Then as a consequence of Pham's duality result ($\S 5$ \cite{pham}), for every $[\mathcal{C}]\in H_n(X,zf)$
 \begin{align*}
@@
 So far we have considered $\theta=\arg(z)$ fixed and generic (i.e.
-$\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$), but as we let $\theta$ varying $I_{\alpha}(z)$ becomes a multivalued function, indeed when $\theta$ crosses a Stokes ray $\ell_{\alpha\beta}\defeq\arg(\zeta_\alpha-\zeta_\beta)\R$, $I_\alpha(z)$ jumps.
+$\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$), but as we let $\theta$ varying $I_{\alpha}(z)$ becomes a multivalued function.
+Indeed when $\theta$ crosses a Stokes ray $\ell_{\alpha\beta}\defeq\arg(\zeta_\alpha-\zeta_\beta)\R$, $I_\alpha(z)$ jumps.
 Computing the jumps of $I_{\alpha}(z)$ is equivalent to determine the analytic continuation of $I_\alpha(z)$ for $z\in\C$.
@@
 We are going to prove Theorem \ref{thm:borel integrals}. 
-Let $X$ be a $n$-dimensional algebraic variety, $f\colon X\to\C$ be an algebraic function with simple, isolated, non-degenerate critical points, and $\nu\in\Gamma(X,\Omega^n)$, and set
+Let $X$ be a $n$-dimensional algebraic variety, $f\colon X\to\C$ be an algebraic function with simple, isolated, non-degenerate critical points, and $\nu\in\Gamma(X,\Omega^n)$, and we consider
 \begin{equation}
-I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu
 \end{equation}
-where $\mathcal{C}$ is a suitable contour such that the integral is well defined.
-Indeed, $I(z)$ represents the pairing between a relative homology class $[\mathcal{C}]\in H_{n}^{B}(X,zf)$ and a cohomology class $[\nu]\in H_{dR}^n(X,zf)$ (see Section 1.3.1 Thimble integrals in the introduction).
+where $\mathcal{C}_{\alpha,z}$ is a Lefschetz thimble $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf) $ for $\arg(z)$ generic.
+
+%Indeed, $I(z)$ represents the pairing between a relative homology class $[\mathcal{C}]\in H_{n}^{B}(X,zf)$ and a cohomology class $[\nu]\in H_{dR}^n(X,zf)$ (see Section 1.3.1 Thimble integrals in the introduction).
 Let us restrict to one dimensional $X$.
@@
 \begin{equation}\label{exp-int}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{k\geq 0}a_{\alpha,k}z^{-k} \qquad \text{ as } \operatorname{Re} (ze^{i\theta})\to\infty
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}\sqrt{2\pi} z^{-1/2}\sum_{k\geq 0}a_{\alpha,k}z^{-k} \qquad \text{ as } \operatorname{Re} (ze^{i\theta})\to\infty.
 \end{equation}
-where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
 Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, e^{i\theta}\infty)$, where $\zeta_\alpha := f(x_\alpha)$.

### 2022-07-04 Introduction.tex
picture
Picture from PhD thesis of Niklas Zorbach: Computing Pat integrals with Lefschetz thimbles

@@
 Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points.
-We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\Gamma_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}): denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then
+We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\mathcal{C}_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}):
+\begin{equation}
+\mathcal{C}_{\alpha,z}=\lbrace x\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
+\end{equation}
+
+denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then 
 \begin{equation}

### 2022-07-04 Introduction.tex
pictures

@@
 S^+_c\defeq\lbrace \zeta\in\C\vert \mathrm{Re}(\zeta e^{i\theta})\geq c\rbrace\\
-S^-_c\defeq\lbrace \zeta\in\C\vert \mathrm{Re}(\zeta e^{i\theta})\leq c\rbrace.
+S^-_c\defeq\lbrace \zeta\in\C\vert \mathrm{Re}(\zeta e^{i\theta})\leq c\rbrace
 \end{align*}
-and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)=H_{\bullet}\left(X,f^{-1}(S_c^+);\Z\right)\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
+and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)\defeq H_{\bullet}\left(X,f^{-1}(S_c^+);\Z\right)\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
 points $\zeta_\alpha\defeq f(x_\alpha)$ where $df(x_\alpha)=0$ \footnote{In dimension $n>1$ there are other singular values due to the fact that $f$ is not proper.
@@
 Moreover, for $\theta$ generic, i.e.
-$\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the singular values of $f$ of the homology relative to these singular values (see \cite{pham}\cite{KKP}):
+when $\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the singular values of $f$ of the homology relative to these singular values (see \cite{pham}\cite{KKP}):
 \begin{align}\label{decomposition H_B}
@@
 where $B_\alpha(\varepsilon)\defeq\lbrace \zeta \in\C\big\vert\,\, |\zeta-\zeta_\alpha|<\varepsilon\rbrace$ and $S_\alpha^+(\theta,\varepsilon)\defeq B_\alpha(\varepsilon)\cap\lbrace \mathrm{Re}(\zeta e^{i\theta})\geq \tfrac{\varepsilon}{2}\rbrace$ (see Figure \ref{fig:relative_homology}).
-\begin{figure}
+\begin{figure}[h]
+\includegraphics[scale=0.5]{Cattura}
+\includegraphics[scale=0.3]{Cattura2}
 \caption{Relative homology}\label{fig:relative_homology}
 \end{figure}
+
+Let $\theta=0$ (if $\theta\neq 0$ we consider $xe^{i\theta/2}$), locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$.
+Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points.
+We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\mathcal{C}_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{Witten}):
+\begin{equation}
+\mathcal{C}_{\alpha,z}=\lbrace x\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
+\end{equation}
+where $x(t)$ is the solution of the gradient flow equation \[\frac{\dd x_i(t)}{\dd t}=-g_{ij}x_j(t)\] and $x_i(0)=x_i$ \footnote{An equivalent definition is given by F. Pham in \cite{pham}.}.
+
+\begin{figure}[h]
+\includegraphics[scale=0.075]{veer-left_matching}
+\includegraphics[scale=0.075]{veer-right_matching}
+\caption{Lefschetz thimbles for the Airy integral $f(t)=t^3/3-t$ at $\theta=?$ (left) and $\theta=??$ (right). }\label{Lefschetz_thimbles}
+\end{figure}
+
+Notice that $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf)$ and they generate the relative homology for every critical values $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$.
+In fact,
+
+\begin{itemize}
+\item $H_k\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ is isomorphic to $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))$, where $B_\alpha
+^M(\varepsilon)$ is an open ball centred at $x_\alpha$ of radius $\varepsilon$ such that for every $\varepsilon'<\varepsilon$ $B_\alpha(\varepsilon')$ is transverse to $f^{-1}(\zeta_\alpha)$. 
+\item $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))=0$ if $k\neq n$ and $H_{n-1}(B_\alpha^M(\varepsilon)\,\cap f^{-1}(\zeta-\zeta_\alpha))=\Z^\mu$, where $\mu$ is the Milnor number;
+\end{itemize}
+
+hence $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ has rank $\mu$. \textbf{Mostra che Lefschetz thimbles sono lin indip.}
+
+\color{magenta}
 We furthermore assume the following:
@@
 
-which guarantees that 
-\begin{itemize}
-\item $H_k\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ is isomorphic to $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))$, where $B_\alpha
-^M(\varepsilon)$ is an open ball centred at $x_\alpha$ of radius $\varepsilon$ such that for every $\varepsilon'<\varepsilon$ $B_\alpha(\varepsilon')$ is transverse to $f^{-1}(\zeta_\alpha)$. 
-\item $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))=0$ if $k\neq n$ and $H_{n-1}(B_\alpha^M(\varepsilon)\,\cap f^{-1}(\zeta-\zeta_\alpha))=\Z^\mu$, where $\mu$ is called the Milnor number.
-\end{itemize}
-
-where \textcolor{magenta}{ $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and $\theta$ is chosen such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$}\footnote{Such a $\theta$ exists because $f$ has a finite number of critical points.}.
-\color{magenta}
-Let $\theta=0$, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$.
-Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points.
-We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\mathcal{C}_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{pham}\cite{Witten}):
-\begin{equation}
-\mathcal{C}_{\alpha,z}=\lbrace x\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
-\end{equation}
-
-denote $x'=\mathrm{Re}(x)$ and $x''=\mathrm{Im}(x)$, then 
-\begin{equation}
-\mathcal{C}_{\alpha,z}\defeq\lbrace x\in X\vert x_1''=x_2''=...=x_n''=0, x_1'^2+...+x_n'^2\leq \zeta-\zeta_\alpha\rbrace
-\end{equation}
-\begin{figure}
-\caption{Lefschetz thimbles}\label{Lefschetz_thimbles}
-\end{figure}
-In addition, they generate the relative homology for every critical values \textbf{Why?}. If $\theta\neq 0$ we consider $xe^{i\theta/2}$.
-
-\textbf{[add duality]}  
 \color{black}
 
-Therefore for $\theta$ generic, the integral $I(z)$ can be decomposed as sum over Lefschetz thimbles: we denote 
+Since for $\theta$ generic the $\mathcal{C}_{\alpha,z}$ are a basis for the relative homology $H_n(X,zf)$, the integral $I(z)$ can be decomposed as sum over Lefschetz thimbles: we denote 
 \begin{equation}\label{int_alpha}
@@
 \end{equation}
-and we refer to $I_{\alpha}(z)$ as a thimble integral. Then as a consequence of Pham's duality result ($\S 5$ \cite{pham}), for every $[\mathcal{C}]\in H_n(X,zf)$
+and we refer to $I_{\alpha}(z)$ as a thimble integral. Then  for every $[\mathcal{C}]\in H_n(X,zf)$
 \begin{align*}
-I(z)=\sum_{\alpha}(-1)^{n(n-1)/2}\langle \mathcal{C}_{\alpha,\theta+\pi},\mathcal{C}\rangle I_{\alpha}(z). 
+I(z)=\sum_{\alpha}n_\alpha I_{\alpha}(z). 
 \end{align*}
+Moreover the coeficients $n_\alpha$ can be computed via intersection theory, as a consequence of Pham's duality result ($\S 5$ \cite{pham}).
+
+\color{magenta}
+$n_\alpha=(-1)^{n(n-1)/2}\langle \mathcal{C}_{\alpha,\theta+\pi},\mathcal{C}\rangle$
+
+\color{black}
 
@@
 \end{equation}
-where $\mathcal{C}_{\alpha,z}$ is a Lefschetz thimble $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf) $ for $\arg(z)$ generic.
+where $\mathcal{C}_{\alpha,z}$ is a Lefschetz thimble $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf)$ for $\theta=\arg(z)$ generic.
 
@@
 Let us restrict to one dimensional $X$.
-For any critical points $x_\alpha$ (satisfying the previous assumptions) of $f$, the saddle point approximation allows to compute the asymptotic expansion of $I_\alpha(z)$
+In particular,  $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$ and generic $\theta$ are such that $f(x_\beta)\notin f(x_\alpha)+[0,e^{i\theta}\infty)$ for $\beta\neq\alpha$.
+For any critical points $x_\alpha$ (satisfying the previous assumptions), the saddle point approximation allows to compute the asymptotic expansion of $I_\alpha(z)$ 
 \begin{equation}\label{exp-int}

### 2022-07-07 airy-resurgence.tex
Try solving in Hardy spaces

@@
 \newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
-\newcommand{\holoL}[1]{\mathcal{H}L^{#1}}
+\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
 \DeclareMathOperator{\Ai}{Ai}
@@
 \subsubsection{Algebraic integral operators}
+Let $D \subset \C$ be an open disk of radius $R$ whose boundary $\partial D$ contains $\zeta = 0$.
+The Hardy space $H^p(D)$ is the space of holomorphic functions on $D$ which converge pointwise, almost everywhere, to $L^p$ functions on $\partial D$~\cite[Theorem~3.8]{intro-harmonic}.
+Its norm $\|\cdot\|_p$ is the $L^p$ norm on $\partial D$ with respect to the rotation-invariant probability measure.
+
+We'll study integral operators $\mathcal{G} \acts H^p(D)$ of the form
+\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
+where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
+The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
+Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
+That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
+
+\color{SeaGreen}
+Assume $p \le q$.
+
+Functions that extend continuously to $\partial D$ are dense in $H^p(D)$ \textcolor{magenta}{[check]}.
+\color{black}
+
+\begin{align*}
+\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left|\int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \int_{a \in \partial D} \left(\int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+\end{align*}
+Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
+\begin{align*}
+\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
+\end{align*}
+Then, by H\"{o}lder's inequality,
+\begin{align*}
+\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
+\end{align*}
+Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
+\begin{align*}
+\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
+& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
+\end{align*}
+which simplifies to
+\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
+That means
+\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
+where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.
+
+\color{DodgerBlue}
+\subsubsection{Algebraic integral operators}
 Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
@@
 \end{proof}
-\color{black}
+\color{DodgerBlue}
 
@@
 \end{align*}
+\color{black}
 \subsection{Order shifting}\label{shifting}

### 2022-07-08 airy-resurgence.tex
Try solving in weighted L^infinity spaces

@@
 
+\color{DarkBlue}
 \begin{align*}
-\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left|\int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \int_{a \in \partial D} \left(\int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+\|\mathcal{G}f\|_1 & = \int_{a \in \partial D} \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right|\,\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \left( \sup_D |f| \right) \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}.
+\end{align*}
+By the maximum principle, $\sup_D |f| = \sup_{\partial D} |f|$, so
+\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}. \]
+Taking the infimum over all the integration paths we could use to evaluate $[\mathcal{G}f](a)$, we see that
+\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \ell_{g, D}(a)\,\frac{|d\zeta(a)|}{2\pi R}. \]
+\color{black}
+
+\begin{align*}
+\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left| \int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
+& \le \int_{a \in \partial D} \left( \int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
 \end{align*}
@@
 
-\color{DodgerBlue}
+\color{DarkBlue}
 \subsubsection{Algebraic integral operators}
@@
 Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.
+Multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
+We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
+\begin{align*}
+\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
+\phi & \mapsto \zeta^{-\sigma} \phi
+\end{align*}
+is an isometry.
 
-We'll study integral operators $\mathcal{G} \acts \holoL{\infty}(\Omega)$ of the form
+%%Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.
+
+We'll study integral operators $\mathcal{G} \acts \holoL{\infty, \sigma}(\Omega)$ of the form
 \[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
@@
 The square of a density is a Riemannian metric.
-Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
+Let $\ell_{g, \sigma, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma} d\zeta|$ on $\Omega \smallsetminus \{a\}$.
 The bound
 \begin{align*}
-\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
-& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
+\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
+& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta| \\
+& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta|
 \end{align*}
 holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
-so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
+\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \sigma, \Omega}(a)\,\|f\|_\infty. \]
+so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \sigma, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
 \subsubsection{The example of fractional integrals}
-Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
-The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
+Setting
+\[ g(a, a') = \zeta(a)^\rho\,(\zeta(a) - \zeta(a'))^{-\lambda-1}\,\zeta(a')^\mu \]
+with $\lambda \in (-\infty, 0)$, we get the operator
+\[ \zeta^\rho \circ \partial^\lambda_{\zeta \text{ from } 0} \circ \zeta^\mu. \]
+The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\sigma}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
 It follows that
 \begin{align*}
-\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
-& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
+\ell_{g, \sigma, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\sigma}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{\mu-\sigma}\,dr \\
+& = |\zeta(a)|^{\rho+\sigma} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{\mu-\sigma}\,|\zeta(a)|\,dt \\
+& = |\zeta(a)|^{\rho+\sigma-\lambda-1+\mu-\sigma+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{\mu-\sigma}\,dt \\
+& = |\zeta(a)|^{\rho-\lambda} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{\mu-\sigma}\,dt \\
+& = |\zeta(a)|^{\rho-\lambda+\mu}\,B(-\lambda, \mu-\sigma+1),
 \end{align*}
-so
-\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
-In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
+where $B$ is the beta function. Hence, on $\holoL{\infty, \sigma}(\Omega)$,
+\[ \|\zeta^\rho \circ \partial^\lambda_{\zeta \text{ from } 0} \circ \zeta^\mu\| \le B(-\lambda,\mu-\sigma+1)\,\sup_\Omega |\zeta|^{\rho-\lambda+\mu}. \]
+In particular, when $\Omega$ is small enough that \textcolor{magenta}{[???]}, the operator on the left-hand side is a contraction of $\holoL{\infty, \sigma}(\Omega)$ for all $\lambda \in (-\infty, -\rho]$.
 \subsubsection{Fractional integral equations near a regular singular point}
@@
 \end{itemize}
+
+\textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$.
+Let's look for a solution of the form $f = \zeta^{\tau-1}(1 + \tilde{f})$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty}(\Omega)$.}
+
+Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+Since $p$, $q$, and $r_\lambda$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
+\begin{alignat*}{2}
+p & = p'_0 \zeta &\;+\;& \tilde{p} \zeta^2 \\
+q & = q_0 &\;+\;& \tilde{q} \zeta
+\end{alignat*}
+where $\tilde{p}, \tilde{q} \in \holoL{\infty}(\Omega)$ extend holomorphically over $\zeta = 0$ too. Then we have
+\begin{align*}
+\mathcal{J} & = (p_0'\zeta + \tilde{p}\zeta^2) + (q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \partial^{-1}_{\zeta \text{ from } 0} \circ \zeta \circ \tilde{q}) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \\
+& = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \zeta \circ \tilde{\mathcal{J}},
+\end{align*}
+where
+\[ \tilde{\mathcal{J}} = \tilde{p}\zeta + (\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} \circ \zeta) \circ \tilde{q} + \sum_{\lambda \in \Lambda} (\zeta^{-1} \circ \partial^\lambda_{\zeta \text{ from } 0}) \circ r_\lambda.
+\]
+For any $\tau \in (0, \infty)$,
+\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + [\zeta \circ \tilde{\mathcal{J}}]\,\zeta^{\tau-1}. \]
+Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
+\[ \mathcal{J} \zeta^{\tau-1} = [\zeta \circ \tilde{\mathcal{J}}]\,\zeta^{\tau-1}. \]
+The equation $\mathcal{J}f = 0$ then becomes
+\begin{align*}
+\mathcal{J}\zeta^{\tau-1} + \mathcal{J}(\zeta^{\tau-1}\zeta\tilde{f}) & = 0 \\
+\tilde{\mathcal{J}}\zeta^{\tau-1} + [\mathcal{J} \circ \zeta](\zeta^{\tau-1}\tilde{f}) & = 0 \\
+\end{align*}
 

### 2022-07-13 modified bessel.tex
general thimbles integrals
Jot down notes on dihedral group action
From tea conversation with Maxim.

@@
 \begin{equation}\label{Bessel_nu}
-w''+\frac{w'}{z}-w-\frac{\mu^2}{z^2}=0
+w''+\frac{w'}{z}-w-\frac{\mu^2}{z^2}w=0
 \end{equation}
@@
 
-Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and for every $\mu\in [0,+\infty)$ let $\nu=x^{\mu-1}+\frac{1}{x^{\mu+1}}dx$, then
+Let $X=\C^*$, $f(x)=x+\frac{1}{x}$ and for every $\mu\in [0,+\infty)$ let $\nu=\left(x^\mu+x^{-\mu}\right) \tfrac{dx}{x}$, then
 
@@
 
-In particulr, on the universal cover $\pi\colon\tilde{C}\to \C^*$ setting $x=e^u$ 
+In particular, on the universal cover $\pi\colon\tilde{C}\to \C^*$ setting $x=e^u$ \textbf{[DLMF, Identity~10.32.9]}
 \begin{equation}
-I(\tfrac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
+I(\tfrac{z}{2};\mu)=2\int_{-\infty}^{\infty}e^{-z\cosh(u)}\cosh(\mu u)\,du=4K_\mu(z)\,\quad |\arg(z)|<\pi/2
 \end{equation} 
@@
 Therefore we have shown that Stokes constants are independent on $\mu$ and equal to $\pm 2$.
+\subsection{Why the Stokes factors are non-integer}
+The infinite dihedral group $D_{2\infty} \isom \Z \ltimes \Z/2\Z$ has a nice action on $\tilde{C}$ that leaves $e^{-z \cosh(u)}$ invariant.
+The action of $1 \in \Z$ adds $2\pi i$ to the value of $u$, and the actions of $\{\pm 1\} \isom \Z/2$ multiply the value of $u$ by $\pm 1$.
+
+Consider exponential integrals of the form
+\[ \langle \Gamma, e^{-z \cosh(u)}\,\alpha\rangle := \int_\Gamma e^{-z \cosh(u)}\,\alpha, \]
+where the variety $\tilde{C}$ and the twisting factor $e^{-z \cosh(u)}$ are fixed, while the integration path $\Gamma$ and the twisted 1-form $e^{-z \cosh(u)}\,\alpha$ are allowed to vary.
+We can apply the action of $D_{2\infty}$ to these integrals by pushing forward the integration contour, or equivalently by pulling back the twisted 1-form.
+This makes the vector space of exponential integrals into a representation of $D_{2\infty}$.
+
+Let's see what the action does to $I(\tfrac{z}{2}; \mu) = \langle -\infty \to \infty, e^{-z \cosh(u)}\,\nu \rangle$, recalling that $\nu = \cosh(\mu u)\,du$. Pulling $\nu$ back along $1 \in \Z$ gives
+\begin{align*}
+\cosh(\mu u + 2\pi i \mu)\,du & = \big[\cosh(2\pi i \mu) \cosh(\mu u) + \sinh(2\pi i \mu) \sinh(\mu u)\big]\,du \\
+& = \cos(2\pi \mu)\,\nu + i\sin(2\pi \mu) \sinh(\mu u)\,du.
+\end{align*}
+and pulling it back along $\pm 1 \in \Z/2\Z$ gives $\pm\nu$. Hence, $1 \in \Z$ sends
+\[ I(\tfrac{z}{2}; \mu) = 2\int_{-\infty}^{\infty} e^{-z\cosh(u)}\,\nu \]
+to
+\begin{align*}
+& 2\int_{-\infty}^{\infty} e^{-z\cosh(u)} \big[\cos(2\pi \mu)\,\nu + i\sin(2\pi \mu) \sinh(\mu u)\,du\big] \\
+& = 2\cos(2\pi \mu) \int_{-\infty}^{\infty} e^{-z\cosh(u)}\,\nu + 2i\sin(2\pi \mu) \int_{-\infty}^{\infty} e^{-z\cosh(u)} \sinh(\mu u)\,du \\
+& = \cos(2\pi \mu)\,I(\tfrac{z}{2}; \mu),
+\end{align*}
+with the second term vanishing in the last step because $\sinh(\mu u)$ is odd.
+Also, $\pm 1 \in \Z/2\Z$ sends $I(\tfrac{z}{2}; \mu)$ to $\pm I(\tfrac{z}{2}; \mu)$.
+Now we see that in the space of exponential integrals, considered as a representation of $D_{2\infty}$, the span of $I(\tfrac{z}{2}; \mu)$ is a one-dimensional subrepresentation, giving the character \textbf{[correct word?]}
+\begin{align*}
+D_{2\infty} & \to \C^\times \\
+1 \in \Z & \mapsto \cos(2\pi \mu) \\
+\pm 1 \in \Z/2\Z & \mapsto \pm 1.
+\end{align*}
+
+\textbf{[The other invariant subspace should be generated by the path $-\infty + \pi i \to \infty + \pi i$.]}
+
+Another way to think of this: if we choose bases for the space of (relative homology classes of) integration paths and the space of (relative cohomology classes of) twisted 1-forms, we can write a period matrix for $\langle\;,\;\rangle$.
+The entries of the period matrix form a basis for the space of exponential integrals.
+The action of $D_{2\infty}$ on exponential integrals can be seen as an action on the period matrix.
+When $D_{2\infty}$ acts on integration paths, it acts on the period matrix by left multiplication; when it acts on 1-forms, it acts on the period matrix by right multiplication.
+The the left and right action matrices are adjoints with respect to $\langle\;,\;\rangle$.
+The argument above shows that for well-chosen bases, we can make the action matrices block-diagonal, with two blocks.
+
+When $\mu = 1/n$ for $n \in \N$, the space of integration paths and the space of twisted 1-forms are both $n$-dimensional, and \textbf{[...]}
 

### 2022-07-13 Introduction.tex

@@
 
-\subsection{What are exponential integrals}
+\subsection{What are exponential integrals}\label{what-are-exp-inte}
 
@@
 \end{align*}
-and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)\defeq H_{\bullet}\left(X,f^{-1}(S_c^+);\Z\right)\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain singular values of $f$ (i.e.
-points $\zeta_\alpha\defeq f(x_\alpha)$ where $df(x_\alpha)=0$ \footnote{In dimension $n>1$ there are other singular values due to the fact that $f$ is not proper.
+and we define $H_\bullet(X,zf)$ as the relative homology groups, namely \[H_{\bullet}(X,zf)\defeq H_{\bullet}\left(X,f^{-1}(S_c^+);\Z\right)\] for $c$ large enough so that $f^{-1}(S_c^+)$ does not contain critical values of $f$ (i.e.
+points $\zeta_\alpha\defeq f(x_\alpha)$ where $df(x_\alpha)=0$ \footnote{In dimension $n>1$ there are other critical values due to the fact that $f$ is not proper.
 However under suitable assumptions it is possible to overcome this issue (see \cite{pham} part $1$, $\S 2$).}).
@@
 
-Notice that $I(z)$ only depends on the class of $\mathcal{C}$ and on the class of $[\nu]\in H_{dR}^n(X,zf)\defeq\mathbb{H}^n\left(X,(\Omega^\bullet_X,d_W\defeq e^{zf}\circ d\circ e^{-zf})\right)$: indeed let $\mathcal{C}'=\mathcal{C}+\partial\gamma\in [\mathcal{C}]$,
+Notice that $I(z)$ only depends on $[\mathcal{C}]\in H_n(X,zf)$ and on $[\nu]\in H_{dR}^n(X,zf)\defeq\mathbb{H}^n\left(X,(\Omega^\bullet_X,d_W\defeq e^{zf}\circ d\circ e^{-zf})\right)$: indeed let $\mathcal{C}'=\mathcal{C}+\partial\gamma\in [\mathcal{C}]$,
 \begin{align*}
@@
 Moreover, for $\theta$ generic, i.e.
-when $\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the singular values of $f$ of the homology relative to these singular values (see \cite{pham}\cite{KKP}):
+when $\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the critical values of $f$ of the homology relative to these critical values (see \cite{pham}\cite{KKP}):
 \begin{align}\label{decomposition H_B}
@@
 
-hence $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ has rank $\mu$. \textbf{Mostra che Lefschetz thimbles sono lin indip.}
+hence $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ has rank $\mu$.
+In addition from singularity theory we know that the set of vanishing cycles $\partial\mathcal{C}_{\alpha,z}$ forms a basis of $H_{n-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha)) $ (see Theorem 2.1 \cite{Arnold}).
 
@@
 \end{align*}
-Moreover the coeficients $n_\alpha$ can be computed via intersection theory, as a consequence of Pham's duality result ($\S 5$ \cite{pham}).
+Moreover the coeficients $n_\alpha$ can be computed via intersection theory (see $\S 5$ \cite{pham}, $\S 3.1.5$ \cite{Witten}).
+When $X$ is not compact the intersection paring is defined introducing dual cycles: let
+\begin{align*}
+\mathcal{K}_{\alpha,z}\defeq\lbrace x\in X\,\big\vert\, \lim_{t\to -\infty} x(t)=x_\alpha \rbrace
+\end{align*} 
+where $x(t)$ solve the upward flow equation
+\begin{align*}
+\frac{\dd x_i(t)}{\dd t}= g_{ij}x_j(t) \qquad \text{ with } x_i(0)=x_i
+\end{align*}
+then $\mathcal{K}_{\alpha,z}\in H_{n}(X,f^{-1}(S^-_c);\Z)$ for $c$ large enough and they define a basis (for $\theta$ generic).
+Furthermore, $\mathcal{K}_{\alpha,z}$ and $\mathcal{C}_{\alpha,z}$ intersect transversely at the critical point $x_\alpha$, hence they define a non degenerate pairing
+\begin{align*}
+\langle -, -\rangle\colon H_n&(X,f^{-1}(S^+_c);\Z)\otimes H_n(X,f^{-1}(S^-_c);\Z)\to \Z \\
+& \qquad \mathcal{C} \qquad\quad , \qquad\qquad \mathcal{K} \qquad \to \quad \langle\mathcal{C} , \, \mathcal{K}\rangle. 
+\end{align*}
+Now looking at the intersection of $\mathcal{C}\in H_n(X,zf)$ with the basis $\mathcal{K}_{\alpha,z}$ we can compute the constants $n_\alpha$ in terms of intersection pairing:
+\begin{align*}
+\langle \mathcal{C},\mathcal{K}_{\alpha,z}\rangle=\sum_{\beta}n_\beta\langle \mathcal{C}_{\beta,z},\mathcal{K}_{\alpha,z}\rangle=n_\alpha
+\end{align*}
+\color{magenta}
+ORIENTATION?
 
-\color{magenta}
 $n_\alpha=(-1)^{n(n-1)/2}\langle \mathcal{C}_{\alpha,\theta+\pi},\mathcal{C}\rangle$
@@
 
-\subsubsection{Thimbles integrals [Kontsevich]: geometric computation of Stokes constants}
+\subsubsection{Geometric computation of Stokes constants}
+As we discuss in $\S$\ref{what-are-exp-inte}, at $\theta$ generic, the relative homology groups $H_n(X,zf)$ admits a decomposition in terms of the homology relative to each critical values $H_n(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon)))$.
+As $\theta$ varies, without crossing a Stokes line, $H_n(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon)))$ defines a rank $\mu$ local system over $\mathbb{S}^1$
 

### 2022-08-16 Introduction.tex
update introduction

@@
 
-Notice that $I(z)$ only depends on $[\mathcal{C}]\in H_n(X,zf)$ and on $[\nu]\in H_{dR}^n(X,zf)\defeq\mathbb{H}^n\left(X,(\Omega^\bullet_X,d_W\defeq e^{zf}\circ d\circ e^{-zf})\right)$: indeed let $\mathcal{C}'=\mathcal{C}+\partial\gamma\in [\mathcal{C}]$,
-\begin{align*}
-\int_{\mathcal{C}'}e^{-zf}\nu=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\partial\gamma}e^{-zf}\nu=\int_{\mathcal{C}}e^{-zf}\nu
-\end{align*} 
-because $e^{-zf}$ is rapidly decaying at $\partial\gamma$. Similarly, if $\nu'=\nu+d_W\eta\in [\nu]$
+\color{Aquamarine}
+Notice that $I(z)$ only depends on $[\mathcal{C}]\in H_n(X,zf)$ and on $[\nu]\in H_{dR}^n(X,zf)\defeq\mathbb{H}^n\left(X,(\Omega^\bullet_X,d_W\defeq e^{zf}\circ d\circ e^{-zf})\right)$: indeed let $\mathcal{C}'=\mathcal{C}+\partial\Gamma_1+\Gamma_2\in [\mathcal{C}]$ with $\Gamma_2\in X\cap f^{-1}(S_c^-)$,
+\begin{multline*}
+\int_{\mathcal{C}'}e^{-zf}\nu=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\partial\Gamma_1}e^{-zf}\nu+\int_{\Gamma_2}e^{-zf}\nu
+=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\Gamma_1}d\left(e^{-zf}\nu\right)=\\
+=\int_{\mathcal{C}}e^{-zf}\nu+\int_{\Gamma_1}e^{-zf}d_W\nu=\int_{\mathcal{C}}e^{-zf}\nu
+\end{multline*} 
+because $e^{-zf}$ is rapidly decaying at $\Gamma_2$. Similarly, if $\nu'=\nu+d_W\eta\in [\nu]\in H_{dR}^n(X,zf)$
 \begin{multline*}
@@
 \end{multline*}
+
+Therefore the exponential integral defines a non--degenerate  paring \[\int\colon H_k(X,zf)\otimes_\Z\C\,\times\, H^k_{dR}(X,zf)\to \C_z. \]
 Moreover, for $\theta$ generic, i.e.
-when $\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$ and $\alpha\neq\beta$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the critical values of $f$ of the homology relative to these critical values (see \cite{pham}\cite{KKP}):
-\begin{align}\label{decomposition H_B}
-H_\bullet(X,zf)=\bigoplus_{\alpha}H_\bullet\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)
-\end{align}     
-where $B_\alpha(\varepsilon)\defeq\lbrace \zeta \in\C\big\vert\,\, |\zeta-\zeta_\alpha|<\varepsilon\rbrace$ and $S_\alpha^+(\theta,\varepsilon)\defeq B_\alpha(\varepsilon)\cap\lbrace \mathrm{Re}(\zeta e^{i\theta})\geq \tfrac{\varepsilon}{2}\rbrace$ (see Figure \ref{fig:relative_homology}).
+when $\theta\neq\arg(\zeta_\alpha-\zeta_\beta)$, there is a decomposition of $H_\bullet(X,zf)$ as direct sum over the critical values of $f$ of the homology relative to these critical values (see \cite{pham}\cite{KKP}): let \[H_\bullet^{\theta,\alpha}(X,f)\defeq H_\bullet\left(f^{-1}(B_\alpha(\varepsilon))\cap \,f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)\] where $B_\alpha(\varepsilon))\defeq\lbrace \zeta \in\C\big\vert\,\, |\zeta-\zeta_\alpha|<\varepsilon\rbrace$ and $S_\alpha^+(\theta,\varepsilon)\defeq B_\alpha(\varepsilon)\cap\lbrace \mathrm{Re}(\zeta e^{i\theta})\geq \tfrac{\varepsilon}{2}\rbrace$ (Figure \ref{fig:ball}).
 \begin{figure}[h]
 \includegraphics[scale=0.5]{Cattura}
+\caption{Representation of $B_\alpha(\varepsilon)$ and the half-moon $S_\alpha^+(\theta,\varepsilon)$.}\label{fig:ball} 
+\end{figure}
+
+Then the decomposition is 
+\begin{align}\label{decomposition H_B}
+H_\bullet(X,zf)=\bigoplus_{\alpha}H_\bullet^{\theta,\alpha}(X,f)
+\end{align}     
+and the idea of the proof is sketched in Figure \ref{fig:relative_homology}.
+\begin{figure}[h]
+%\includegraphics[scale=0.5]{Cattura}
 \includegraphics[scale=0.3]{Cattura2}
@@
 
-Let $\theta=0$ (if $\theta\neq 0$ we consider $xe^{i\theta/2}$), locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a coordinate system $x_1,...,x_n$ such that $f(x)-f(x_\alpha)=x_1^2+...+x_n^2$.
-Then $\mathrm{Re}(f)$ is a Morse function with simple, isolated and non degenerate critical points.
-We choose a Riemannian metric $g$ on $X$ and we define the Lefschetz thimbles $\mathcal{C}_{\alpha,z}$ as the steepstet descendet path issuing from a critcal point $x_\alpha$ (see \cite{Witten}):
+Let $\theta$ be generic, locally in a neighbourhood of a critcal point $x_\alpha$ we can choose a (real) coordinate system $\xi_1,...,\xi_{2n}$ such that \[e^{i\theta}\left(f(x)-f(x_\alpha)\right)=\sum_{j=1}^n(\xi_j+i\xi_{j+1})^2.\] Then $\mathrm{Re}(e^{i\theta}f)$ is a Morse function with simple, isolated and non degenerate critical points (which are the cirtical points of $f$).
+We choose a Riemannian metric $g$ on $X$ and we define the \textit{Lefschetz thimbles} $\mathcal{C}_{\alpha,z}$ as the steepstet descendent path issuing from a critcal point $x_\alpha$ (see \cite{Witten}):
 \begin{equation}
-\mathcal{C}_{\alpha,z}=\lbrace x\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
+\mathcal{C}_{\alpha,z}=\lbrace x=(x_1,...,x_{2n})\in X\,\big\vert \, \lim_{t\to -\infty} x(t)=x_\alpha\rbrace
 \end{equation}
-where $x(t)$ is the solution of the gradient flow equation \[\frac{\dd x_i(t)}{\dd t}=-g_{ij}x_j(t)\] and $x_i(0)=x_i$ \footnote{An equivalent definition is given by F. Pham in \cite{pham}.}.
+where $x(t)$ is the solution of the gradient flow equation \[\frac{\dd x_i(t)}{\dd t}=-g_{ij}\frac{\partial}{\partial \xi_j}\mathrm{Re}f(x(t))\] and $x_i(0)=x_i$ \footnote{An equivalent definition is given by F.
+Pham in \cite{pham}.}.
 
@@
 
-Notice that $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf)$ and they generate the relative homology for every critical values $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$.
-In fact,
+Notice that $[\mathcal{C}_{\alpha,z}]\in H_n(X,zf)$ and they generate the relative homology. In fact,
 
 \begin{itemize}
-\item $H_k\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ is isomorphic to $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))$, where $B_\alpha
+\item $H_k^{\theta,\alpha}(X,f)$ is isomorphic to $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))$, where $B_\alpha
 ^M(\varepsilon)$ is an open ball centred at $x_\alpha$ of radius $\varepsilon$ such that for every $\varepsilon'<\varepsilon$ $B_\alpha(\varepsilon')$ is transverse to $f^{-1}(\zeta_\alpha)$. 
-\item $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))=0$ if $k\neq n$ and $H_{n-1}(B_\alpha^M(\varepsilon)\,\cap f^{-1}(\zeta-\zeta_\alpha))=\Z^\mu$, where $\mu$ is the Milnor number;
+\item $H_{k-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha))=0$ if $k\neq n$ and $H_{n-1}(B_\alpha^M(\varepsilon)\,\cap f^{-1}(\zeta-\zeta_\alpha))=\Z^\mu$, where $\mu$ is the Milnor number \footnote{The Milnor number counts how many pre-image of a critical value are critical points, or equivalently how many Lefschetz thimbles are in the pre-image of $f^{-1}(\zeta_\alpha+\R_{\geq 0}e^{i\theta})$.};
 \end{itemize}
 
-hence $H_n\left(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon))\right)$ has rank $\mu$.
+hence $H_n^{\theta,\alpha}(X,f)$ has rank $\mu$.
 In addition from singularity theory we know that the set of vanishing cycles $\partial\mathcal{C}_{\alpha,z}$ forms a basis of $H_{n-1}(B_\alpha^M(\varepsilon)\cap f^{-1}(\zeta-\zeta_\alpha)) $ (see Theorem 2.1 \cite{Arnold}).
 
-\color{magenta}
-We furthermore assume the following:
-\begin{assumption}\label{assumption_on_f}
-The map $f\colon X\to\C$ has isolated, simple and non degenerate critical values $\zeta_\alpha$. 
-\end{assumption}
-
-\color{black}
-
-Since for $\theta$ generic the $\mathcal{C}_{\alpha,z}$ are a basis for the relative homology $H_n(X,zf)$, the integral $I(z)$ can be decomposed as sum over Lefschetz thimbles: we denote 
+Since for $\theta$ generic the collection of the Lefschetz thimbles $\mathcal{C}_{\alpha,z}\in H_n^{\theta,\alpha}(X,f)$ (for all $\alpha$ and fixed $\theta$)are a basis for the relative homology $H_n(X,zf)$, the integral $I(z)$ can be decomposed as sum over Lefschetz thimbles: we denote
 \begin{equation}\label{int_alpha}
@@
 \begin{align*}
-\frac{\dd x_i(t)}{\dd t}= g_{ij}x_j(t) \qquad \text{ with } x_i(0)=x_i
+\frac{\dd x_i(t)}{\dd t}= g_{ij}\frac{\partial}{\partial \xi_j}\mathrm{Re}f(x(t)) \qquad \text{ with } x_i(0)=x_i
 \end{align*}
@@
 \end{align*}
+\color{magenta}
+Should I mention the Betti--DeRham iso?
+
+\color{black}
+
 Now looking at the intersection of $\mathcal{C}\in H_n(X,zf)$ with the basis $\mathcal{K}_{\alpha,z}$ we can compute the constants $n_\alpha$ in terms of intersection pairing:
 \begin{align*}
-\langle \mathcal{C},\mathcal{K}_{\alpha,z}\rangle=\sum_{\beta}n_\beta\langle \mathcal{C}_{\beta,z},\mathcal{K}_{\alpha,z}\rangle=n_\alpha
+\langle \mathcal{C},\mathcal{K}_{\alpha,z}\rangle=\langle \sum_\beta n_\beta\mathcal{C}_{\beta,z},\mathcal{K}_{\alpha,z}\rangle=\sum_{\beta}n_\beta\langle \mathcal{C}_{\beta,z},\mathcal{K}_{\alpha,z}\rangle=\sum_{\beta}n_\beta\delta_{\alpha\beta}=n_\alpha
 \end{align*}
+
+hence $n_\alpha$ are integers. However, there are examples in which $n_\alpha\in\C$ (see modified Bessel): indeed if there exists a group $G$ that leaves $f$ invariant, namely
+\begin{align*}
+f(g.x)=f(x)\,\,\forall g\in G
+\end{align*} 
+then different critical points can be mapped to the same critical value.
+It follows that for every $x_j$ in the orbit of $x_\alpha$, the thimbles $\mathcal{C}_{j,z}=f^{-1}(\zeta_\alpha+ \R_{\geq 0} e^{i\theta})$ are $\C$-linear dependent.
+
+% $H_\bullet(X,zf)$ such that the orbits of $\mathcal{C}_{\alpha,z}\in H_n^{\theta,\alpha}(X,f)$ contains the Lefschetz thimbles $\mathcal{C}_{j,z}\in H_n^{\theta,z}(X,zf)$ for every $j$ such that $f(x_j)=\zeta_\alpha$.
+When it happens, $\mathcal{C}_{j,z}$ and $\mathcal{C}_{\alpha,z}$ are $\C$- linear dependent, hence the coefficients $n_j$ are complex valued.
+
 \color{magenta}
@@
 \subsubsection{Geometric computation of Stokes constants}
-As we discuss in $\S$\ref{what-are-exp-inte}, at $\theta$ generic, the relative homology groups $H_n(X,zf)$ admits a decomposition in terms of the homology relative to each critical values $H_n(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon)))$.
-As $\theta$ varies, without crossing a Stokes line, $H_n(f^{-1}(B_\alpha(\varepsilon))\cap f^{-1}(S_\alpha^+(\theta,\varepsilon)))$ defines a rank $\mu$ local system over $\mathbb{S}^1$
+As we discuss in $\S$\ref{what-are-exp-inte}, at $\theta$ generic, the relative homology groups $H_n(X,zf)$ admits a decomposition in terms of the homology relative to each critical values $H_n^{\theta,\alpha}(X,f)$.
+As $\theta$ varies, $H_n^{\theta,\alpha}(X,f)$ defines a rank $\mu$ local system over $\mathbb{S}^1$ which has non trivial monodromy at the singular points $\theta=\arg(\zeta_\alpha-\zeta_\beta)$.
+Our goal is to compute these monodromy matrices: on a Stokes ray $\ell_{\alpha\beta}=\zeta_\alpha+e^{i\theta}\R$ the imaginary part of $\zeta_j\in\ell_{\alpha\beta}$ is constant and we order the critical values as $\mathrm{Re}(\zeta_1)<\mathrm{Re}(\zeta_2)<...<\mathrm{Re}(\zeta_j)$.
+Then the monodromy matrices are upper triangular and the off diagonal terms are the so called Stokes constants.
+In order to compute the Stokes constants we follow Kontsevich's proposal in \cite{Maxim_lectures} which is in terms of intersection numbers of thimbles.
+
+\begin{figure}[h]
+\includegraphics[scale=0.065]{veer-left_matching}
+\includegraphics[scale=0.26]{thimble-degenerate}
+\includegraphics[scale=0.065]{veer-right_matching}
+\includegraphics[scale=0.33]{borel-left}
+\includegraphics[scale=0.33]{borel-left}
+\includegraphics[scale=0.33]{borel-left}
+\end{figure}
 
 \subsubsection{ ODE and fractional derivative formula [draft2]}
+
+From an analytic perspective, Stokes phenomena occurs studying the analytic continuation of germs of holomorphic function in the Borel plane.
+Indeed, Borel transform of divergent series usually have singularities and the aim of resurgence theory is to investigate the analytic continuation away from the singularities.
+We will mainly refer to J.
+Ecalle's orginal papers \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII} as well as the following introductive reviews by different authors \cite{Schiappa}\cite{Dorigoni}\cite{diablerets}\cite{MS16}\cite{sauzin_Gamma}.
+
+Among the most common type of singularities of $\hat{\iota}(\zeta)\in\C\lbrace\zeta\rbrace$ there are simple singularities and fractional power singularities: 
+\begin{itemize}
+\item $\hat{\iota}(\zeta)$ has a simple singularity at $\omega\in\C$ if there exist a constant $C_\omega\in\C$ and a germ of holomorphic function at the origin $\hat{\phi}_\omega(\zeta)\in\C\lbrace\zeta\rbrace$ such that in a neighbourhood of $\omega$
+\begin{align*}
+\hat{\iota}(\zeta-\omega)=\frac{C_\omega}{2\pi i \zeta}+\frac{\mathrm{Log}(\zeta)}{2\pi i}\hat{\phi}_{\omega}(\zeta)+\text{ hol. fct.}
+\end{align*} 
+and $\mathrm{Log}(\zeta)$ is any branch of the logarithm;
+\item $\hat{\iota}(\zeta)$ has a fractional power singularity at $\omega\in\C$ if there exist $\mu\in\Q\setminus\Z$ and a germ of holomorphic function at the origin $\hat{\phi}_\omega(\zeta)\in\C\lbrace\zeta\rbrace$ such that in a neighbourhood of $\omega$
+\begin{align*}
+\hat{\iota}(\zeta-\omega)=\zeta^{\mu}\hat{\phi}_\omega(\zeta)+ \text{ hol. fct.}
+\end{align*}
+\end{itemize}
+
+From the type of singularities we can study the analytic continuation of $\hat{\iota}$; for instance in both the previous examples we look for singularities of the germ $\hat{\phi}_\omega(\zeta)$ iterating the same procedure.
+In general, this iterative procedure may be infinite as at every step we may found new singularities, however resurgence function are endlessly analytic continuable, meaning that at each step they admit only finitely many singularities.
+There are also examples where the resurgence structure of germs is easier because there are only finitely many singularities, as it happens for exponential integrals and for solutions of linear ODEs.
+In particular, in the former case the singularities are the critical values of the potential $f$ while in the latter they are determined from the equation written in the \textit{prepared form}.
+In both cases the singularities are fractional power singularities but for exponential integrals (as a corollary of Theorem \ref{thm:borel integrals}) we will prove a fractional derivative formula which expresses the non-fractional singularity $\hat{\varphi}_\alpha(\zeta)$ in terms of the Borel transform  $\hat{\iota}_\alpha(\zeta)$:
+
+\begin{corollary}[see Corollary \ref{int:deriv-formula}]\label{cor:deriv-formula} 
+Under the same assumptions of Theorem \ref{thm:borel integrals}, for any $\zeta$ on the ray going rightward from $\zeta_\alpha$ in the direction of $\theta$, we have
+\begin{multline}
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{3/2}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)={\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} {\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\end{multline}
+where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $e^{-i\theta}f^{-1}([\zeta_\alpha, \zeta ])$.
+Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $e^{-i\theta}f^{-1}(\zeta)$.
+\end{corollary}
+
+Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities.
+Moreover, in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical points.
+We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
+In addition,  \textbf{Aaron-> what do you expect to be true in terms of the algebraic hypergeometric?}
+
+%Another difficulty of studying the analytic continuation of a germ is that often we only know its series expansion $\tilde{\iota}(\zeta)$ and not its sum $\hat{\iota}(\zeta)$ which
+
+Once we know the location of singularities hence the analytic continuation of the germ, the Stokes constant are determined either by comparing the behaviour across a branch cut or the residue at a simple pole.
+We discuss the two cases separately: let $\hat{\iota}(\zeta)\in\C\lbrace\zeta\rbrace$ be a germ at the origin with a log singularity at $\omega\in\C$
+
+\begin{equation}
+\hat{\iota}(\zeta-\omega)=\frac{\mathrm{Log}(\zeta)}{2\pi i}\hat{\phi}_{\omega}(\zeta)+\text{ hol. fct.}
+\end{equation}
+
+with $\hat{\phi}_{\omega}(\zeta)\in\C\lbrace\zeta\rbrace$.
+If  $\hat{\phi}_{\omega}(\zeta)$ has no singularities for $\mathrm{Re}(\zeta)\geq \mathrm{Re}(\omega)$, then $\hat{\iota}$ has a branch cut for $\zeta=\omega+\R_{\geq 0}$  and its analytic continuation is easily computed
+
+\begin{align*}
+\hat{\iota}(\zeta-\omega+i\epsilon)-\hat{\iota}(\zeta-\omega-i\epsilon)&=\frac{\mathrm{Log}(\zeta+i\epsilon)}{2\pi i}\hat{\phi}_\omega(\zeta+i\epsilon)-\frac{\mathrm{Log}(\zeta-i\epsilon)}{2\pi i}\hat{\phi}_\omega(\zeta-i\epsilon)\\
+&=\frac{\mathrm{Log}(\zeta-i\epsilon)+2\pi i}{2\pi i}\hat{\phi}_\omega(\zeta)-\frac{\mathrm{Log}(\zeta-i\epsilon)}{2\pi i}\hat{\phi}_\omega(\zeta)\\
+&=\hat{\phi}_\omega(\zeta). 
+\end{align*} 
+We can deduce that the log singularity is represented by $\hat{\phi}_{\omega}(\zeta)$ also called \textit{minor} in Ecalle formalism.
+
+Similarly, if $\hat{\iota}$ has fractional power singularity $\mu\in\C\setminus\Z$ and $\hat{\phi}_{\omega}$ has no singularities in $\omega+\R_{\geq 0}$, across the branch cut $\omega+\R_{\geq 0}$
+
+\begin{align*}
+\hat{\iota}(\zeta-\omega+i\epsilon)-\hat{\iota}(\zeta-\omega-i\epsilon)&=(\zeta+i\epsilon)^{\mu}\hat{\phi}_\omega(\zeta+i\epsilon)- (\zeta-i\epsilon)^{\mu}\hat{\phi}_\omega(\zeta-i\epsilon)\\
+&=e^{2\pi i\mu}(\zeta-i\epsilon)^\mu\hat{\phi}_\omega(\zeta)-(\zeta-i\epsilon)^{\mu}\hat{\phi}_\omega(\zeta)\\
+&=(e^{2\pi i\mu}-1)(\zeta-i\epsilon)^{\mu}\hat{\phi}_{\omega}(\zeta).
+\end{align*} 
+In this case, a \textit{minor} is given by $(e^{2\pi i\mu}-1)(\zeta-i\epsilon)^{\mu}\hat{\phi}_{\omega}(\zeta)$.
+
+In Ecalle formalism, pole singularities are usually denoted by the symbol $\delta^{(k)}$ where $k$ represent the order of the pole:
+\begin{align*}
+\delta\defeq\mathrm{sing}_0\left(\frac{1}{2\pi i\zeta}\right) \qquad\qquad \delta^{(k)}\defeq\mathrm{sing}_0\left(\frac{(-1)^kk!}{2\pi i\zeta^{k+1}}\right),\quad k\geq 0
+\end{align*}
+where $\mathrm{sing}_0$ denotes the quotient map by germs of holomorphic functions. According to that notation, simple singularities are denoted by 
+\begin{equation}
+\overset{\triangledown}\iota(\zeta)=C_\omega\delta+\hat{\varphi}_{\omega}(\zeta).
+\end{equation}
+
+\color{green}
+
+parla Stokes constant in generale
+
+\color{black}
+
+Let us focus on the Stokes phenomena for exponential integrals: let $\zeta_{\alpha_i}$, $i=1,...,N$ be the critical values of $f$ and $x_1,...,x_d$ be the critical points (where $d$ might be grater than $N$).
+For each critical point, the asymptotic behaviour of $I_{j}(z)$ is given by a formal power series $\tilde{I}_{j}(z)$ whose Borel transform is a germ of holomorphic functions at $f(x_j)=\zeta_{\alpha_i}$ for some $i$.
+In addition, $\hat{\iota}_{j}(\zeta)$ has singularities in the Borel plane exactly at points $\zeta_{\alpha_l}$ for $l\neq i$.
+Hence, if we define $R_{jk}\defeq |\zeta_{\alpha_i}-\zeta_{\alpha_l}|$ for $k$ such that $f(x_k)=\zeta_{\alpha_l}$ and we order $\zeta_{\alpha_l}$ so that $R_{jk_1}\leq R_{jk_2}\leq ...\leq R_{jk_N}$ in a neighbourhood of $\zeta_{\alpha_l}$ we expect
+
+\begin{equation}
+\hat{\iota}_j(\zeta-\zeta_{\alpha_l})=\sum_{r: R_{jk_1}=R_{jk_r}}S_{jk_r}\hat{\iota}_{k_r}(\zeta) 
+\end{equation}  
+where $S_{jk}$ are constants.
+Notice that there might be more values of $k$ such that $f(x_k)=\zeta_{\alpha_l}$ for a fixed $l$; hence the constants $S_{jk}$ are defined only after a choice of normalization.
+\textbf{Discuss with Aaron what is the best choice; should we fix a basis of critical points and relate the thimbles with the same image via the action of some group?
+How this affect the constants?}
+
+Going back to the $z-$ plane, from the analysis on the Borel plane we deduce the following: let ...
+
+we can also compute the Stokes constants via direct computation of the analytic continuation of the Borel--Laplace sum of $\tilde{I}_{j}(z)$ for every $j$ such that $\zeta_j\in\ell_{\alpha\beta}$.
+This is about computing the difference between $\mathcal{L}_{\theta_\pm}\hat{\iota}_{j}\defeq\int_{
+\zeta_j}^{e^{i\theta_\pm}\infty}e^{-z\zeta}\hat{\iota}_{j}(\zeta)d\zeta$ such that $\theta_\pm=\arg(\zeta_\alpha-\zeta_\beta)\pm\epsilon$, $\epsilon <\!\!< 1$ does not contain other singularities of $\hat{\iota}_j(\zeta)$.
+Following the convention of \cite{Dorigoni}\cite{Schiappa} we define the Stokes automorphisms $\mathfrak{S}_\theta$ associated to the critical direction $\theta$ as
+
+\begin{align*}
+\mathcal{L}_{\theta_+}=\mathcal{L}_{\theta_-}\circ\mathfrak{S}_{\theta}
+\end{align*}
+which measures the jump between the Borel--Laplace sum of $\tilde{I}_j(z)$ across the ray $\ell_{\alpha\beta}$.
+In addition it can be expressed in terms of the so called \textit{Alien derivatives} $\Delta_{\zeta_{j}}$ for every $\zeta_{j}\in\ell_{\alpha\beta}$ which are derivations on the algebra of resurgent functions
+
+\begin{align*}
+\Delta_{\zeta_j}\colon 
+\end{align*}
+
+in particular, if $\hat{\iota}_j(\zeta)$ is a resurgent function 
+Then
+
+\begin{align*}
+\mathfrak{S}_{\theta}= \exp\left(\right)
+\end{align*}
 
@@
 
+\color{Aquamarine}
+\begin{remark}
+There is an ambiguity in the proof: on one side, when we choose a coordinates $\tau$ and we write the asymptotic expansion $\tilde{I}_j(z)$ of a thimble integral $I_j(z)$, it only depends on $f(x_j)$.
+So if $f(x_j)=f(x_k)=\zeta_\alpha$, then $\tilde{I}_j(z)=\tilde{I}_k(z)\doteq\tilde{I}_\alpha(z)$.
+Consequently their Borel transform is the same: $\tilde{\iota}_j(\zeta)=\tilde{\iota}_k(\zeta)\doteq\tilde{\iota}_\alpha(\zeta)$.
+However, in the second part of the proof, the Borel transform of $I_j(z)$ is computed from the Laplace integral and its definition depends on the ends of the thimble $\mathcal{C}_j$.
+So a question arises naturally, what is the relation between ends of thimbles which are mapped to the same path in the Borel plane?
+\end{remark}
+
+\color{black}
+
 \begin{remark}
@@
 
+\subsection{How to find singularities in the Borel plane}
+
+\begin{lemma}
+Let $\tilde{\Phi}(z)$ be a solution of a linear ODE
+\begin{equation}
+P(\partial_z)+z^{-1}Q_1(\partial_z)+...+z^{-d+1}Q_{d-1}(\partial_z)+z^{-d}Q_d(\partial_z)=0
+\end{equation}
+with $P(-)$ a degree $d$ polynomial and $Q_j(-)$ a degree $d-j$ polynomial. Then $\hat{\phi}(\zeta)$ is resurgent in $\C\setminus\lbrace \lambda\in\C \vert  P(\lambda)=0\rbrace$.  
+\end{lemma}
+
+\begin{proof}
+
+\end{proof}
+
+\begin{remark}
+For non linear ODEs, the previous result is not valid anymore, because non linear terms propagate singularities via convolution. 
+\end{remark}
+
+\begin{lemma}Let $I(z)$ be an exponential integral and $\tilde{I}_j(z)\in z^{1/2}\C_1[\![z^{-1}]\!]$ be its asymptotic behaviour at the critical point $x_j$ as $\mathrm{Re}(z)\to e^{i\theta}\infty$.
+Then $\hat{\iota}_j(\zeta)$ has singularities at the critical values $\zeta_\alpha$.
+\end{lemma}
+
+\subsection{Stokes factors from geometric computations}
+
+Let $I_j(z)$ be a thimble integral labeled by the set of thimbles, one for each critical points and let $\zeta_{\alpha_i}$ be the critical values of $f$.
+Recall that Stokes rays $\ell_{il}$ are defined along the direction $\arg(\zeta_{\alpha_i}-\zeta_{\alpha_l})$ and
+
 \section{Examples}

### 2022-08-16 airy-resurgence.tex
Work on integral equation existence argument
After talking with Angeliki, Piet, Kihyun, and Kihyun's guest.

--- 2022-07-07 airy-resurgence.tex
@@
 \usepackage{xparse} %% for squiggly underlines
+\usepackage{tikz-cd} %% for term norm scratch work
 
@@
 Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-Let $\mathcal{S} \subset \holoL{\infty}(\Omega)$ be the union of $O_{\zeta, 0 \leftarrow}(\zeta^\tau)$ over all $\tau > 0$.
+For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
+We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
+\begin{align*}
+\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
+\phi & \mapsto \zeta^{-\sigma} \phi
+\end{align*}
+is an isometry. More generally,
+\begin{align*}
+\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
+f & \mapsto \zeta^{-\delta} f
+\end{align*}
+is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$.
+This reduces to the previous statement when $\rho = 0$.
+For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
+Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
 
-We'll study integral operators $\mathcal{G} \acts \holoL{\infty}(\Omega)$ of the form
+Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
+For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
+
+We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
 \[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
@@
 The square of a density is a Riemannian metric.
-Let $\ell_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|g(a, \cdot)\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
+Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
 The bound
 \begin{align*}
-\big|[\mathcal{G}f](a)\big| & \le \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \\
-& \le \|f\|_\infty \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta|
+\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
+& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
+& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
 \end{align*}
 holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell_{g, \Omega}(a)\,\|f\|_\infty. \]
-so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
+\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_\infty. \]
+so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
 \subsubsection{The example of fractional integrals}
 Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
-The density $|\zeta(a) - \zeta|^{-\lambda-1}\,|d\zeta|$ is rotationally symmetric around $a$, so the shortest path from $\zeta = 0$ to $a$ is a straight line with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
+The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
 It follows that
 \begin{align*}
-\ell_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} t^{-\lambda-1}\,dt \\
-& = -\tfrac{1}{\lambda} |\zeta(a)|^{-\lambda},
+\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
+& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
+& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
+& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
+& = B(-\lambda,\,1-\rho).
 \end{align*}
-so
-\[ \|\partial^\lambda_{\zeta \text{ from } 0}\| \le \sup_\Omega {(-\tfrac{1}{\lambda}) |\zeta|^{-\lambda}}. \]
-In particular, when $\Omega$ is small enough that $\|\zeta\|_\infty < 1$, the operator $\partial^\lambda_{\zeta \text{ from } 0}$ is a contraction of $\holoL{\infty}(\Omega)$ for all $\lambda \in (-\infty, -1]$.
+The beta function $B$ can be written more explicitly as
+\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
+Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
+%%In particular, when $\Omega$ is small enough that \textcolor{magenta}{[???]}, the operator on the left-hand side is a contraction of $\holoL{\infty, \sigma}(\Omega)$ for all $\lambda \in (-\infty, -\rho]$.
 \subsubsection{Fractional integral equations near a regular singular point}
+\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
+
 Consider an integral operator $\mathcal{J}$ of the form
@@
 \begin{itemize}
+%%\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and $1/p$ is in $\holoL{\infty, 1}(\Omega)$.
+%%\item $q$ and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
+%%\item $p \in \holoL{\infty, -1}(\Omega)$ and $1/p \in \holoL{\infty, 1}(\Omega)$.
+\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
+%%\item $q, r_\lambda \in \holoL{\infty}(\Omega)$.
+\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
+\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
+%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
 \item $\Lambda$ is a countable subset of $(-\infty, -1)$.
-\item $p$, $q$, and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
-\item $p$ has a first-order zero at $\zeta = 0$.
 \end{itemize}
+Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough.
+We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.
+
+\textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$.
+Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, \tau}(\Omega)$.}
+
+Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.
+
+Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
+\begin{alignat*}{2}
+p & = p'_0 \zeta &\;+\;& \tilde{p} \\
+q & = q_0 &\;+\;& \tilde{q}
+\end{alignat*}
+with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
+\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
+with
+\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
+For any $\tau \in (0, \infty)$,
+\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
+Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
+\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
+Then the equation $\mathcal{J}f = 0$ becomes
+\begin{align*}
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \\
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
+-p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
+\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f} \\
+\end{align*}
+
+\color{Indigo}
+\begin{center}
+\begin{tikzcd}[column sep=25mm, row sep=2mm]
+& & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
+& & \holoL{\infty, \rho}(\Omega) \\
+& & & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
+& & & \holoL{\infty, \rho}(\Omega) \\
+& & & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-\lambda}"'] \\
+& & & \holoL{\infty, \rho}(\Omega)
+\end{tikzcd}
+\end{center}
+\color{DarkBlue}
+
+From \textbf{[our previous discussion]}, we can work out that
+\begin{align*}
+\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}
+\end{align*}
+and
+\begin{align*}
+\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -1-\tau}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\end{align*}
+Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
+\begin{align*}
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
+\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\end{align*}
 

### 2022-08-16 airy-resurgence.tex
Finish integral equation existence argument

@@
 %%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
-\item $\Lambda$ is a countable subset of $(-\infty, -1)$.
+\item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
 \end{itemize}
@@
 \textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$.
-Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, \tau}(\Omega)$.}
+Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+When $\epsilon$ is small enough that $\Lambda \subset (-\infty, -1 - \epsilon]$, we'll see that we can always find such a solution, as long as we're willing to shrink $\Omega$.
+In fact, there's exactly one such solution.
+\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}}
 
@@
 Then the equation $\mathcal{J}f = 0$ becomes
-\begin{align*}
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \\
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
--p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \\
-\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f} \\
-\end{align*}
+\begin{align}
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \nonumber \\
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
+-p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
+\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f}.
+\label{fixed-pt}
+\end{align}
 
@@
 & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
-& & \holoL{\infty, \rho}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^{1-\epsilon}"'] \\
+& & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
 & & & \holoL{\infty, \rho-1}(\Omega) \\
@@
 & & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-\lambda}"'] \\
-& & & \holoL{\infty, \rho}(\Omega)
+\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-1-\epsilon-\lambda}"'] \\
+& & & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 1-\rho) = \frac{1}{1-\rho}}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\zeta^{-1}", "\|\zeta^{-1}\|_{\infty, 1} = 1"'] & \holoL{\infty, \rho}(\Omega) \\
 \end{tikzcd}
@@
 \begin{align*}
-\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}
+\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
 \end{align*}
@@
 \begin{align*}
-\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -1-\tau}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega) \to \mathcal{H}L^{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
 \end{align*}
 Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
+\begin{align}
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
+\end{align}
+and
+\begin{align}
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\label{bound:perturb}
+\end{align}
+We can also see that
+\begin{align}
+\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
+\end{align}
+
+Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textbf{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
 \begin{align*}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, -\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau}(\Omega)\;\text{with} \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{2+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, 1+\tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\mathcal{A} & = \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \\
+b & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1}
 \end{align*}
+Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
+We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
+
+An affine map is a contraction if and only if its linear part is a contraction.
+We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$.
+Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
+Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
 

### 2022-08-16 airy-resurgence.tex
Drop old variants of integral equation existence argument

@@
 \subsubsection{Algebraic integral operators}
-Let $D \subset \C$ be an open disk of radius $R$ whose boundary $\partial D$ contains $\zeta = 0$.
-The Hardy space $H^p(D)$ is the space of holomorphic functions on $D$ which converge pointwise, almost everywhere, to $L^p$ functions on $\partial D$~\cite[Theorem~3.8]{intro-harmonic}.
-Its norm $\|\cdot\|_p$ is the $L^p$ norm on $\partial D$ with respect to the rotation-invariant probability measure.
-
-We'll study integral operators $\mathcal{G} \acts H^p(D)$ of the form
-\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
-where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
-The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
-Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
-That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
-
-\color{SeaGreen}
-Assume $p \le q$.
-
-Functions that extend continuously to $\partial D$ are dense in $H^p(D)$ \textcolor{magenta}{[check]}.
-\color{black}
-
-\color{DarkBlue}
-\begin{align*}
-\|\mathcal{G}f\|_1 & = \int_{a \in \partial D} \left| \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right|\,\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |f|\,|g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \left( \sup_D |f| \right) \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}.
-\end{align*}
-By the maximum principle, $\sup_D |f| = \sup_{\partial D} |f|$, so
-\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \left( \int_{\zeta = 0}^{a} |g(a, \cdot)\,d\zeta| \right)\,\frac{|d\zeta(a)|}{2\pi R}. \]
-Taking the infimum over all the integration paths we could use to evaluate $[\mathcal{G}f](a)$, we see that
-\[ \|\mathcal{G}f\|_1 \le \|f\|_\infty \int_{a \in \partial D} \ell_{g, D}(a)\,\frac{|d\zeta(a)|}{2\pi R}. \]
-\color{black}
-
-\begin{align*}
-\|\mathcal{G}f\|_p^p & = \int_{a \in \partial D} \left| \int_{\zeta(a') = 0}^{a} g(a, a')\,f(a')\,d\zeta(a') \right|^p\,\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \int_{a \in \partial D} \left( \int_{\zeta(a') = 0}^{a} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
-\end{align*}
-Since $\zeta = 0$ and $a$ are both in $\partial D$, and we're assuming that $f$ extends continuously to $\partial D$, we can compute $[\mathcal{G}f](a)$ using an integration path that runs along $\partial D$.
-\begin{align*}
-\|\mathcal{G}f\|_p^p & \le \int_{a \in \partial D} \left(\int_{a' \in \partial D} |g(a, a')\,f(a')|\,|d\zeta(a')| \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
-& = \int_{a \in \partial D} \left(2\pi R \int_{a' \in \partial D} |g(a, a')\,f(a')|\,\frac{|d\zeta(a')|}{2\pi R} \right)^p\,\frac{|d\zeta(a)|}{2\pi R} \\
-& = (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\,f\|_1^p\;\frac{|d\zeta(a)|}{2\pi R}.
-\end{align*}
-Then, by H\"{o}lder's inequality,
-\begin{align*}
-\|\mathcal{G}f\|_p^p & \le (2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\|f\|_p^p\;\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \|g(a, \cdot)\|_q^p\;\frac{|d\zeta(a)|}{2\pi R} \\
-& \le \|f\|_p^p\;(2\pi R)^p \int_{a \in \partial D} \left( \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R} \right)^{p/q}\,\frac{|d\zeta(a)|}{2\pi R}.
-\end{align*}
-Since we're assuming $p \le q$, we can apply Jensen's inequality to the concave function $(\cdot)^{p/q}$ and conclude that
-\begin{align*}
-\|\mathcal{G}f\|_p^p & \le \|f\|_p^p\;(2\pi R)^p \left( \int_{a \in \partial D} \int_{a' \in \partial D} |g(a, a')|^q\,\frac{|d\zeta(a')|}{2\pi R}\,\frac{|d\zeta(a)|}{2\pi R} \right)^{p/q} \\
-& = \|f\|_p^p\;(2\pi R)^p\,\|g\|_q^p,
-\end{align*}
-which simplifies to
-\[ \|\mathcal{G}f\|_p \le \|f\|_p\;2\pi R\,\|g\|_q. \]
-That means
-\[ \|\mathcal{G}\| \le 2\pi R\,\|g\|_q, \]
-where the norm of $g$ is taken with respect to the rotation-invariant probability measure on $(\partial D)^2$.
-
-\color{DarkBlue}
-\subsubsection{Algebraic integral operators}
 Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
@@
 Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
-%%In particular, when $\Omega$ is small enough that \textcolor{magenta}{[???]}, the operator on the left-hand side is a contraction of $\holoL{\infty, \sigma}(\Omega)$ for all $\lambda \in (-\infty, -\rho]$.
 \subsubsection{Fractional integral equations near a regular singular point}
@@
 \begin{itemize}
-%%\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and $1/p$ is in $\holoL{\infty, 1}(\Omega)$.
-%%\item $q$ and $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$ that extend holomorphically over $\zeta = 0$.
-%%\item $p \in \holoL{\infty, -1}(\Omega)$ and $1/p \in \holoL{\infty, 1}(\Omega)$.
 \item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
-%%\item $q, r_\lambda \in \holoL{\infty}(\Omega)$.
 \item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
 \item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
-%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
 \item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
@@
 
-\textcolor{Indigo}{We want to solve the equation $\mathcal{J}f = 0$.
+We want to solve the equation $\mathcal{J}f = 0$.
 Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
@@
 In fact, there's exactly one such solution.
-\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}}
+\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}
 
@@
 \[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
+Setting $\tau = -q_0 / p'_0$ makes the first term vanish, leaving
 \[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
@@
 \end{center}
-\color{DarkBlue}
+\color{black}
 
@@
 \begin{align*}
-\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
 \|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
@@
 \begin{align*}
-\tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega) \to \mathcal{H}L^{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau-\epsilon}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
 \|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
@@
 \begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \mathcal{H}L^{\infty, 1-\tau}(\Omega) \to \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
 \|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
@@
 \begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
 \|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
@@
 \begin{align}
-\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
 \|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
@@
 
-Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textbf{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
+Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
 \begin{align*}
@@
 \end{align*}
-Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
-We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
+Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
+We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
 
 An affine map is a contraction if and only if its linear part is a contraction.
-We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$.
+We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$.
 Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
-Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\mathcal{H}L^{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
-
-\textcolor{DodgerBlue}{We want to solve the equation $\mathcal{J}f = 0$.
-Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty}(\Omega)$.}
-
-\color{SeaGreen}
-\begin{prop}\label{prop:frac-mollify}
-If $f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^\alpha)$ with $\alpha \in (-1, \infty)$, then $\partial^\lambda_{\zeta \text{ from } 0}\,f$ is in $O_{\zeta, 0 \leftarrow}(\zeta^{\alpha-\lambda})$ for all $\lambda \in (-\infty, 0)$.
-\end{prop}
-\color{magenta}
-\begin{proof}
-??????
-\end{proof}
-\color{SeaGreen}
-\begin{prop}\label{prop:frac-int-growth}
-For any $f \in \holoL{\infty}(\Omega)$ and $\lambda \in (-\infty, 0)$, the bound
-\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\,f\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \|f\|_\infty \]
-holds pointwise throughout $\Omega$.
-\end{prop}
-\color{magenta}
-\begin{proof}
-??????
-\end{proof}
-\color{DodgerBlue}
-
-Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
-Since $p$, $q$, and $r_\lambda$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
-\begin{alignat*}{2}
-p & = p'_0 \zeta &\;+\;& \tilde{p} \zeta^2 \\
-q & = q_0 &\;+\;& \tilde{q} \zeta \\
-\textcolor{orange}{r_\lambda} & = r_{\lambda,0} &\;+\;& \tilde{r}_\lambda \zeta,
-\end{alignat*}
-where $\tilde{p}, \tilde{q} \in \holoL{\infty}(\Omega)$ extend holomorphically over $\zeta = 0$ too. For any $\tau \in (0, \infty)$,
-\begin{align*}
-\mathcal{J} \zeta^{\tau-1} & = p'_0 \zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(q_0 \zeta^{\tau-1}\big) + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big) \\
-& = (p'_0 + q_0/\tau)\zeta^\tau + \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).
-\end{align*}
-Setting $\tau = -q_o / p'_0$ makes the first term vanish, leaving
-\begin{align*}
-\mathcal{J} \zeta^{\tau-1} & = \textcolor{SeaGreen}{\tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_\lambda \zeta^{\tau-1}\big).} \\
-\mathcal{J} \zeta^{\tau-1} & = \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \big(r_{\lambda,0} \zeta^{\tau-1} + \tilde{r}_\lambda \zeta^\tau\big) \\
-& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-1-\lambda} + \partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right]} \\
-& \textcolor{orange}{= \tilde{p} \zeta^{\tau+1} + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau)}{\Gamma(\tau-\lambda)} \zeta^{\tau-(\lambda+1)} \right] + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau.}
-\end{align*}
-Now we can rewrite the equation $\mathcal{J}(\zeta^{\tau-1} + \tilde{f}) = 0$ as
-\begin{align*}
-\mathcal{J} \zeta^{\tau-1} + \left[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = 0 \\
-\mathcal{J} \zeta^{\tau-1} + \left[ \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \right] \tilde{f} & = -p\tilde{f}.
-\end{align*}
-Observing that
-\[ \frac{1}{p} = \frac{\zeta^{-1}}{p_0 + \tilde{p} \zeta}, \]
-we have
-\begin{align*}
-\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big) + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} + \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \big(\tilde{r}_\lambda \zeta^\tau\big) \right] \right] \\
-\frac{1}{p}\,\mathcal{J} \zeta^{\tau-1} & = \frac{1}{p_0 + \tilde{p} \zeta} \left[ \tilde{p} \zeta^\tau + \sum_{\lambda \in \Lambda} \left[ r_{\lambda,0} \tfrac{\Gamma(\tau+1)}{\Gamma(\tau-\lambda+1)} \zeta^{\tau-(\lambda+\textcolor{magenta}{2})} \right] \right] + \frac{1}{p_0 + \tilde{p} \zeta} \left[ \zeta^{-1}\,\partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0} \circ \tilde{r}_\lambda \right] \zeta^\tau
-\end{align*}
-Proposition~\ref{prop:frac-int-growth} guarantees that
-\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \le |\zeta|\,\big\|\tilde{q} \zeta^\tau\big\|_\infty, \]
-so
-\begin{align*}
-\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big| \\
-& \le \big\|\tilde{q} \zeta^\tau\big\|_\infty \\
-& \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty.
-\end{align*}
-Similarly,
-\[ \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \le (-\tfrac{1}{\lambda}) |\zeta|^{-\lambda} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty, \]
-so
-\begin{align*}
-\big|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| & \le |\zeta|^{-1} \big|\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big| \\
-& \le (-\tfrac{1}{\lambda}) |\zeta|^{-(\lambda+1)} \big\|\tilde{r}_\lambda \zeta^\tau\big\|_\infty \\
-& \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{-(\lambda+1)}\big\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
-& = \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty.
-\end{align*}
-In short,
-\begin{align*}
-\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{q} \zeta^\tau\big)\big\|_\infty & \le \|\tilde{q}\|_\infty\,\big\|\zeta^\tau\big\|_\infty \\
-\big\|\zeta^{-1}\,\partial^\lambda_{\zeta \text{ from } 0}\big(\tilde{r}_\lambda \zeta^\tau\big)\big\|_\infty & \le \|\tilde{r}_\lambda\|_\infty\,\big\|\zeta^{\tau-(\lambda+1)}\big\|_\infty
-\end{align*}
-\color{black}
+Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
 \subsection{Order shifting}\label{shifting}
@@
 A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
+We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
 \begin{equation}\label{eqn:slight-defn}

### 2022-08-18 exp-resurgence.tex
Plan to discuss Stokes constants as intersection numbers
Work on outline of introduction
Add motivation and keep developing other parts.

@@
 \color{orange}
-\section*{Veronica's proposal}
+\section*{Outline}
 
@@
 \begin{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
 \item motivation
 \begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
+\item Setting
+\begin{itemize}
+\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
+\begin{itemize}
+\item Exponential integral: na\"{i}ve saddle point expansion.
+\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
+\item Feynman diagram series?
+\end{itemize}
+\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+\begin{itemize}
+\item Borel summation work in three steps.
+First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
+\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item {[Draw the square!]}
+\end{itemize}
+\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+\item In many cases, it picks correctly, producing an actual solution to your problem.
+\begin{itemize}
+\item The question of how that happens is the starting point for this paper.
+\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
+\end{itemize}
+\end{itemize}
+\item Goals
+\begin{itemize}
+\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+\begin{itemize}
+\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+\item The second problem is solving a certain kind of ODE.
+\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+\end{itemize}
+\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+\begin{itemize}
+\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\end{itemize}
+\item Illustrate with detailed treatments of several examples.
+\begin{itemize}
+\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function.
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+\item Others haven't been discussed much.
+\end{itemize}
+\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
+[How do we work this into the introduction?]}
+\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
 \end{itemize}
@@
 \end{itemize}
+\item what are exponential integrals? \textcolor{gray}{has to be done}
+\begin{itemize}
+\item motivation
+\begin{itemize}
+\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
+\item In physics ??
+\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
+\end{itemize}
+\end{itemize}
+\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
 \item State results about resurgence of exponential integrals and Stokes phenomena
@@
 We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Stokes constants using fractional derivative formula and Borel transform computation [{\tt draft2}]
+\item Compute Stokes constants
+\begin{itemize}
+\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]
+\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
+\end{itemize}
 \item Comparison with the literature \textcolor{gray}{has to be done}
@@
 
+\bibliographystyle{plain}
+\bibliography{airy-resurgence}
 \end{document}

### 2022-08-19 exp-resurgence.tex
Start turning motivation section into prose
Sketch out I_{1/3} integral example. Mark typo in Borel regularity
argument for exponential integrals.

@@
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
-\newcommand{\series}[1]{#1_\bullet}
+\newcommand{\series}{\tilde}
 
@@
 \section{Introduction}
+\subsection{Motivation}
+\subsubsection{Setting}
+You can often find a formal power series
+\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
+with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
+\color{SeaGreen}
+\begin{align*}
+\zeta_\alpha & = -1 \\
+\tfrac{1}{2} \tau^2 & = f - \zeta_\alpha \\
+& = 4u^3 - 3u + 1 \\
+\tau & = 0 \text{ and } u_\tau = 0 \text{ at } u = \tfrac{1}{2} \\
+\tfrac{1}{2} \tau^2 & = 6w^2 + 4w^3 \text{ with } u := \tfrac{1}{2} + w \\
+I_\alpha(z) & = e^{z\zeta_\alpha} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \\
+& = e^{-z} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu
+\end{align*}
+\begin{align*}
+w & = \sum_{n = 1}^\infty a_n \tau^n \\
+w^2 & = \sum_{n = 2}^\infty \left( \sum_{k + k' = n} a_k a_{k'} \right) \tau^n \\
+& = a_1^2 \tau^2 + 2 a_1 a_2 \tau^3 + (2 a_1 a_3 + a_2^2) \tau^4 + (2 a_1 a_4 + 2 a_2 a_3) \tau^5 + (2 a_1 a_5 + 2 a_2 a_4 + a_3^2) \tau^6 + \ldots \\
+w^3 & = \sum_{n = 3}^\infty \left( \sum_{k + k' + k'' = n} a_k a_{k'} a_{k''} \right) \tau^n \\
+& = a_1^3 \tau^3 + 3 a_1^2 a_2 \tau^4 + (3a_1 a_2^2 + 3 a_1^2 a_3) \tau^5 + (3 a_1^2 a_4 + 6 a_1 a_2 a_3 + a_2^3) \tau^6 + \ldots
+\end{align*}
+\begin{align*}
+\tau^2 & = 12w^2 + 8w^3\\
+\tau^2 & = 12 a_1^2 \tau^2 & 1 & = 12 a_1^2 \\
+0 & = 24 a_1 a_2 \tau^3 + 8a_1^3 \tau^3 & 0 & = 36 a_2 + 12 a_1^2 \\
+& & -1 & = 36 a_2 \\
+0 & = (24a_1 a_3 + 12 a_2^2) \tau^4 + 24 a_1^2 a_2 \tau^4 & 0 & = 24 a_1 a_3 + 12 a_2^2 + 24 a_1^2 a_2 \\
+& & & = 24 a_1 a_3 + 12 a_2^2 + 2 a_2 \\
+& & & = 24 a_1 a_3 + \frac{1}{3 \cdot 36} - \frac{1}{18} \\
+& & \frac{5}{108} & = 24 a_1 a_3 \\
+& & \frac{5}{216} a_1 & = a_3 \\
+0 & = (24 a_1 a_4 + 24 a_2 a_3) \tau^5 + (24 a_1 a_2^2 + 24 a_1^2 a_3) \tau^5 & 0 & = 24 a_1 a_4 + 24 a_2 a_3 + 24 a_1 a_2^2 + 2 a_3 \\
+& & & = 24 a_1 a_4 + \frac{5}{9} a_2 a_1 + 24 a_1 a_2^2 + \frac{5}{108} a_1 \\
+& & 0 & = 24 a_4 + \frac{5}{9} a_2 + 24 a_2^2 + \frac{5}{108} \\
+& & 0 & = 24 a_4 - \frac{5}{324} + \frac{1}{54} + \frac{5}{108} \\
+& & -\frac{4}{81} & = 24 a_4 \\
+& & -\frac{1}{486} & = a_4 \\
+\end{align*}
+\begin{align*}
+a_1 & = \frac{1}{\sqrt{12}} \\
+2 a_2 & = -\frac{1}{18} \\
+3 a_3 & = \frac{5}{72\sqrt{12}} \\
+4 a_4 & = -\frac{2}{243} \\
+du & = dw = w_\tau\,d\tau \\
+& = \left[ \frac{1}{\sqrt{12}} - \frac{1}{18} \tau + \frac{5}{72\sqrt{12}} \tau^2 - \frac{2}{243} \tau^3 + \ldots \right] d\tau \\
+& = \left[ 1 - \frac{1}{3\sqrt{12}} \tau + \frac{5}{72} \tau^2 - \frac{8}{81\sqrt{12}} \tau^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
+& = \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
+\end{align*}
+\color{black}
+
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du \]
+as
+\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
+using the substitution $\tfrac{1}{2} \tau^2 = 4u^3 - 3u + 1$.
+\begin{itemize}
+\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
+\begin{itemize}
+\item Exponential integral: na\"{i}ve saddle point expansion.
+\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
+\item Feynman diagram series?
+\end{itemize}
+\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+\begin{itemize}
+\item Borel summation work in three steps.
+First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
+\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item {[Draw the square!]}
+\end{itemize}
+\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+\item In many cases, it picks correctly, producing an actual solution to your problem.
+\begin{itemize}
+\item The question of how that happens is the starting point for this paper.
+\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
+\end{itemize}
+\end{itemize}
+\subsubsection{Goals}
+\begin{itemize}
+\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+\begin{itemize}
+\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+\item The second problem is solving a certain kind of ODE.
+\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+\end{itemize}
+\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+\begin{itemize}
+\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\end{itemize}
+\item Illustrate with detailed treatments of several examples.
+\begin{itemize}
+\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function.
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+\item Others haven't been discussed much.
+\end{itemize}
+\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
+[How do we work this into the introduction?]}
+\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\end{itemize}
+\color{DarkBlue}
 \subsection{Why does Borel resummation work?}
@@
 \end{itemize}
+\color{black}
 \subsection{Fractional derivative formula}
@@
 \begin{itemize}
-\item motivation
-\begin{itemize}
-\item Setting
-\begin{itemize}
-\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
-\begin{itemize}
-\item Exponential integral: na\"{i}ve saddle point expansion.
-\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
-\item Feynman diagram series?
-\end{itemize}
-\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-\begin{itemize}
-\item Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
-\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-\item {[Draw the square!]}
-\end{itemize}
-\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-\item In many cases, it picks correctly, producing an actual solution to your problem.
-\begin{itemize}
-\item The question of how that happens is the starting point for this paper.
-\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-\end{itemize}
-\end{itemize}
-\item Goals
-\begin{itemize}
-\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-\begin{itemize}
-\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-\item The second problem is solving a certain kind of ODE.
-\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-\end{itemize}
-\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-\begin{itemize}
-\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-\end{itemize}
-\item Illustrate with detailed treatments of several examples.
-\begin{itemize}
-\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function.
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-\item Others haven't been discussed much.
-\end{itemize}
-\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
-[How do we work this into the introduction?]}
-\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-\end{itemize}
-\end{itemize}
 \item Borel regularity

### 2022-08-19 Introduction.tex
update outline
I've added the intro on exp integral and the one on Borel regularity for integral

@@
 This is the idea of resurgence of $\tilde{I}_{\alpha}(z)$ \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}.
-However, since $f$ has finitely many critical points and $\nu$ is meromorphic, Borel--Laplace summability properties and resurgence of exponential integrals are straightforward to be proven.
+However, since $f$ has finitely many critical points and $\nu$ is meromorphic, Borel--Laplace summability properties and resurgence of exponential integrals are straightforward.
 However, in order to completely describe the Borel plane one needs to compute the Stokes data which provide the analytic continuation across the branch cut.

### 2022-08-19 exp-resurgence.tex
update outline
I've added the intro on exp integral and the one on Borel regularity for integral

--- 2022-08-18 exp-resurgence.tex
@@
 %%\usepackage{graphicx}
-
+\usepackage{tikz-cd}
 %% colors
@@
 \newcommand{\series}[1]{#1_\bullet}
-
+\input{command}
 \title{Resurgence of the Airy function \\ and other exponential integrals}
@@
 First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
-\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+\item The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
 By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
@@
 If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
 We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.\textcolor{black}{[Veronica---I dont't see why]}
 \end{itemize}
@@
 We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function.
+$\bullet$ The Airy function (Marino, Sauzin).
 $\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
@@
 \item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\end{itemize}
+\item Exponential integrals
+\begin{itemize}
+\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
+\item the choice of the path $\mathcal{C}$: 
+\begin{itemize}
+\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
+\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
+\end{itemize}
+\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
+\begin{itemize}
+\item there is a comparison isomorphism (Maxim)
+\end{itemize}
+\item varying $z$ we have the Stokes phenomena
+\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
+\begin{itemize}
+\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
+\item it is an example of resurgent series (\'Ecalle)
+\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
+\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
+\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
+There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
+\end{itemize} 
 \end{itemize}
@@
 \item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday-Richaud ?, big idea in {\tt airy-resurgence}]
-\item Thimble integral [{\tt draft2}]
+\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item fractional derivative formula
 \end{itemize}

### 2022-08-19 exp-resurgence.tex
Try to get K_{1/3} integral example
There's a problem with a_4, which should have the same absolute
value in both K_{1/3} and I_{1/3}.

--- 2022-08-18 exp-resurgence.tex
@@
 \section{Introduction}
+\subsection{Motivation}
+\subsubsection{Setting}
+You can often find a formal power series
+\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
+with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
+\color{SeaGreen}
+\begin{align*}
+\zeta_\alpha & = \textcolor{orange}{\pm}1 \\
+\tfrac{1}{2} \tau^2 & = f - \zeta_\alpha \\
+& = 4u^3 - 3u \textcolor{orange}{\mp} 1 \\
+\tau & = 0 \text{ and } u_\tau = 0 \text{ at } u = \textcolor{orange}{\mp}\tfrac{1}{2} \\
+\tfrac{1}{2} \tau^2 & = \textcolor{orange}{\mp}6w^2 + 4w^3 \text{ with } u := \textcolor{orange}{\mp}\tfrac{1}{2} + w \\
+I_\alpha(z) & = e^{\textcolor{magenta}{-}z\zeta_\alpha} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \\
+& = e^{\textcolor{orange}{\mp}z} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu
+\end{align*}
+\begin{align*}
+w & = \sum_{n = 1}^\infty a_n \tau^n \\
+w^2 & = \sum_{n = 2}^\infty \left( \sum_{k + k' = n} a_k a_{k'} \right) \tau^n \\
+& = a_1^2 \tau^2 + 2 a_1 a_2 \tau^3 + (2 a_1 a_3 + a_2^2) \tau^4 + (2 a_1 a_4 + 2 a_2 a_3) \tau^5 + (2 a_1 a_5 + 2 a_2 a_4 + a_3^2) \tau^6 + \ldots \\
+w^3 & = \sum_{n = 3}^\infty \left( \sum_{k + k' + k'' = n} a_k a_{k'} a_{k''} \right) \tau^n \\
+& = a_1^3 \tau^3 + 3 a_1^2 a_2 \tau^4 + (3a_1 a_2^2 + 3 a_1^2 a_3) \tau^5 + (3 a_1^2 a_4 + 6 a_1 a_2 a_3 + a_2^3) \tau^6 + \ldots
+\end{align*}
+\begin{align*}
+\tau^2 & = \textcolor{orange}{\mp}12w^2 + 8w^3\\
+\tau^2 & = \textcolor{orange}{\mp}12 a_1^2 \tau^2 & 1 & = \textcolor{orange}{\mp}12 a_1^2 \\
+0 & = \textcolor{orange}{\mp}24 a_1 a_2 \tau^3 + 8a_1^3 \tau^3 & 0 & = \textcolor{orange}{\mp}36 a_2 + 12 a_1^2 \\
+& & -1 & = 36 a_2 \\
+0 & = \textcolor{orange}{\mp}(24a_1 a_3 + 12 a_2^2) \tau^4 + 24 a_1^2 a_2 \tau^4 & 0 & = \textcolor{orange}{\mp}24 a_1 a_3 \textcolor{orange}{\mp} 12 a_2^2 + 24 a_1^2 a_2 \\
+& & & = \textcolor{orange}{\mp}24 a_1 a_3 \textcolor{orange}{\mp} 12 a_2^2 \textcolor{orange}{\mp} 2 a_2 \\
+& & & = 24 a_1 a_3 + \frac{1}{3 \cdot 36} - \frac{1}{18} \\
+& & \frac{5}{108} & = 24 a_1 a_3 \\
+& & \frac{5}{216} a_1 & = a_3 \\
+0 & = \textcolor{orange}{\mp}(24 a_1 a_4 + 24 a_2 a_3) \tau^5 + (24 a_1 a_2^2 + 24 a_1^2 a_3) \tau^5 & 0 & = \textcolor{orange}{\mp}24 a_1 a_4 \textcolor{orange}{\mp} 24 a_2 a_3 + 24 a_1 a_2^2 \textcolor{orange}{\mp} 2 a_3 \\
+& & & = 24 a_1 a_4 + \frac{5}{9} a_2 a_1 \textcolor{orange}{\mp} 24 a_1 a_2^2 + \frac{5}{108} a_1 \\
+& & 0 & = 24 a_4 + \frac{5}{9} a_2 \textcolor{orange}{\mp} 24 a_2^2 + \frac{5}{108} \\
+& & 0 & = 24 a_4 - \frac{5}{324} \textcolor{orange}{\mp} \frac{1}{54} + \frac{5}{108} \\
+& & \left\{ -\frac{1}{81} \right\}_{\textcolor{orange}{\zeta = -1}} \left\{ -\frac{4}{81} \right\}_{\textcolor{orange}{\zeta = 1}} & = 24 a_4 \\
+& & \left\{ -\frac{1}{1944} \right\}_{\textcolor{orange}{\zeta = -1}} \left\{ -\frac{1}{486} \right\}_{\textcolor{orange}{\zeta = 1}} & = a_4
+\end{align*}
+\begin{align*}
+0 & = \textcolor{orange}{\mp}12(2 a_1 a_5 + 2 a_2 a_4 + a_3^2) \tau^6 + 8(3 a_1^2 a_4 + 6 a_1 a_2 a_3 + a_2^3) \tau^6 \\
+0 & = \textcolor{orange}{\mp}24 a_1 a_5 \textcolor{orange}{\mp} 24 a_2 a_4 \textcolor{orange}{\mp} 12 a_3^2 + 24 a_1^2 a_4 + 48 a_1 a_2 a_3 + 8 a_2^3\\
+0 & = \textcolor{orange}{\mp}24 a_1 a_5 \textcolor{orange}{\mp} 24 a_2 a_4 \textcolor{orange}{\mp} \left(\frac{5}{216}\right)^2 12 a_1^2 \textcolor{orange}{\mp} 2 a_4 + \frac{5 \cdot 48}{216} a_1^2 a_2 + 8 a_2^3 \\
+0 & = \textcolor{orange}{\mp}24 a_1 a_5 \textcolor{orange}{\mp} 24 a_2 a_4 + \left(\frac{5}{216}\right)^2 \textcolor{orange}{\mp} 2 a_4 \textcolor{orange}{\mp} \frac{5}{54} a_2 + 8 a_2^3 \\
+\left\{ \frac{77}{15552} \right\}_{\textcolor{orange}{\zeta = 1}} & = 24 a_1 a_5 \\
+\left\{ \frac{77}{31104} a_1 \right\}_{\textcolor{orange}{\zeta = 1}} & = a_5
+\end{align*}
+\begin{align*}
+a_1 & = \textcolor{orange}{\{i, 1\}}\frac{1}{\sqrt{12}} \\
+2 a_2 & = -\frac{1}{18} \\
+3 a_3 & = \frac{5}{72\sqrt{12}} \\
+4 a_4 & = -\frac{2}{243} \\
+du & = dw = w_\tau\,d\tau \\
+& = \left[ \frac{1}{\sqrt{12}} - \frac{1}{18} \tau + \frac{5}{72\sqrt{12}} \tau^2 - \frac{2}{243} \tau^3 + \ldots \right] d\tau \\
+& = \left[ 1 - \frac{1}{3\sqrt{12}} \tau + \frac{5}{72} \tau^2 - \frac{8}{81\sqrt{12}} \tau^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
+& = \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
+\end{align*}
+\color{black}
+
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du \]
+as
+\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
+using the substitution $\tfrac{1}{2} \tau^2 = 4u^3 - 3u \textcolor{orange}{\mp} 1$.
+\begin{itemize}
+\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
+\begin{itemize}
+\item Exponential integral: na\"{i}ve saddle point expansion.
+\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
+\item Feynman diagram series?
+\end{itemize}
+\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+\begin{itemize}
+\item Borel summation work in three steps.
+First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
+\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item {[Draw the square!]}
+\end{itemize}
+\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+\item In many cases, it picks correctly, producing an actual solution to your problem.
+\begin{itemize}
+\item The question of how that happens is the starting point for this paper.
+\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
+\end{itemize}
+\end{itemize}
+\subsubsection{Goals}
+\begin{itemize}
+\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+\begin{itemize}
+\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+\item The second problem is solving a certain kind of ODE.
+\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+\end{itemize}
+\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+\begin{itemize}
+\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\end{itemize}
+\item Illustrate with detailed treatments of several examples.
+\begin{itemize}
+\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function.
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+\item Others haven't been discussed much.
+\end{itemize}
+\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
+[How do we work this into the introduction?]}
+\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\end{itemize}
+\color{DarkBlue}
 \subsection{Why does Borel resummation work?}

### 2022-08-19 exp-resurgence.tex
Fix K_{1/3} integral computation using Sage
See `expansion.sage`.
Fix sign error in Bessel integral example
Drop Bessel integral example scratch work

--- 2022-08-19 exp-resurgence.tex
@@
 with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
-\color{SeaGreen}
-\begin{align*}
-\zeta_\alpha & = -1 \\
-\tfrac{1}{2} \tau^2 & = f - \zeta_\alpha \\
-& = 4u^3 - 3u + 1 \\
-\tau & = 0 \text{ and } u_\tau = 0 \text{ at } u = \tfrac{1}{2} \\
-\tfrac{1}{2} \tau^2 & = 6w^2 + 4w^3 \text{ with } u := \tfrac{1}{2} + w \\
-I_\alpha(z) & = e^{z\zeta_\alpha} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \\
-& = e^{-z} \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu
-\end{align*}
-\begin{align*}
-w & = \sum_{n = 1}^\infty a_n \tau^n \\
-w^2 & = \sum_{n = 2}^\infty \left( \sum_{k + k' = n} a_k a_{k'} \right) \tau^n \\
-& = a_1^2 \tau^2 + 2 a_1 a_2 \tau^3 + (2 a_1 a_3 + a_2^2) \tau^4 + (2 a_1 a_4 + 2 a_2 a_3) \tau^5 + (2 a_1 a_5 + 2 a_2 a_4 + a_3^2) \tau^6 + \ldots \\
-w^3 & = \sum_{n = 3}^\infty \left( \sum_{k + k' + k'' = n} a_k a_{k'} a_{k''} \right) \tau^n \\
-& = a_1^3 \tau^3 + 3 a_1^2 a_2 \tau^4 + (3a_1 a_2^2 + 3 a_1^2 a_3) \tau^5 + (3 a_1^2 a_4 + 6 a_1 a_2 a_3 + a_2^3) \tau^6 + \ldots
-\end{align*}
-\begin{align*}
-\tau^2 & = 12w^2 + 8w^3\\
-\tau^2 & = 12 a_1^2 \tau^2 & 1 & = 12 a_1^2 \\
-0 & = 24 a_1 a_2 \tau^3 + 8a_1^3 \tau^3 & 0 & = 36 a_2 + 12 a_1^2 \\
-& & -1 & = 36 a_2 \\
-0 & = (24a_1 a_3 + 12 a_2^2) \tau^4 + 24 a_1^2 a_2 \tau^4 & 0 & = 24 a_1 a_3 + 12 a_2^2 + 24 a_1^2 a_2 \\
-& & & = 24 a_1 a_3 + 12 a_2^2 + 2 a_2 \\
-& & & = 24 a_1 a_3 + \frac{1}{3 \cdot 36} - \frac{1}{18} \\
-& & \frac{5}{108} & = 24 a_1 a_3 \\
-& & \frac{5}{216} a_1 & = a_3 \\
-0 & = (24 a_1 a_4 + 24 a_2 a_3) \tau^5 + (24 a_1 a_2^2 + 24 a_1^2 a_3) \tau^5 & 0 & = 24 a_1 a_4 + 24 a_2 a_3 + 24 a_1 a_2^2 + 2 a_3 \\
-& & & = 24 a_1 a_4 + \frac{5}{9} a_2 a_1 + 24 a_1 a_2^2 + \frac{5}{108} a_1 \\
-& & 0 & = 24 a_4 + \frac{5}{9} a_2 + 24 a_2^2 + \frac{5}{108} \\
-& & 0 & = 24 a_4 - \frac{5}{324} + \frac{1}{54} + \frac{5}{108} \\
-& & -\frac{4}{81} & = 24 a_4 \\
-& & -\frac{1}{486} & = a_4 \\
-\end{align*}
-\begin{align*}
-a_1 & = \frac{1}{\sqrt{12}} \\
-2 a_2 & = -\frac{1}{18} \\
-3 a_3 & = \frac{5}{72\sqrt{12}} \\
-4 a_4 & = -\frac{2}{243} \\
-du & = dw = w_\tau\,d\tau \\
-& = \left[ \frac{1}{\sqrt{12}} - \frac{1}{18} \tau + \frac{5}{72\sqrt{12}} \tau^2 - \frac{2}{243} \tau^3 + \ldots \right] d\tau \\
-& = \left[ 1 - \frac{1}{3\sqrt{12}} \tau + \frac{5}{72} \tau^2 - \frac{8}{81\sqrt{12}} \tau^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
-& = \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \\
-\end{align*}
-\color{black}
-
 \[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du \]
 as
-\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{1}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
+% see expansion.sage
+\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \frac{385}{216} \left(\frac{\tau}{\sqrt{12}}\right)^4 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
 using the substitution $\tfrac{1}{2} \tau^2 = 4u^3 - 3u + 1$.

### 2022-08-19 exp-resurgence.tex
small updates

--- 2022-08-19 exp-resurgence.tex
@@
 %%\usepackage{graphicx}
-\usepackage{tikz-cd}
+
 %% colors
@@
 \newcommand{\C}{\mathbb{C}}
+\usepackage{tikz}
+\usepackage{tikz-cd}
+\usepackage{rotating}
+\newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
+]}
+\usetikzlibrary{matrix,shapes,arrows,decorations.pathmorphing}
+\tikzset{commutative diagrams/arrow style=math font}
+\tikzset{commutative diagrams/.cd,
+mysymbol/.style={start anchor=center,end anchor=center,draw=none}}
+\newcommand\MySymb[2][\square]{%
+  \arrow[mysymbol]{#2}[description]{#1}}
+\tikzset{
+shift up/.style={
+to path={([yshift=#1]\tikztostart.east) -- ([yshift=#1]\tikztotarget.west) \tikztonodes}
+}
+}
+\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}
+
+\newcommand*{\defeq}{\mathrel{\vcenter{\baselineskip0.5ex \lineskiplimit0pt
+                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
+                     =}
+\newcommand*{\defeqin}{\mathrel{\vcenter{\lineskiplimit0pt\baselineskip0.5ex
+                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
+                     =}
+
 %%\let\Re\relax
@@
 \newcommand{\series}[1]{#1_\bullet}
-\input{command}
+%\input{command}
 \title{Resurgence of the Airy function \\ and other exponential integrals}
@@
 \item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
-[How do we work this into the introduction?]}
+[How do we work this into the introduction?]} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
+Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
+For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
 \item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
@@
 \begin{itemize}
-\item Recall Watson condition (old)
+\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
+\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
 \item State new Borel regularity results
@@
 \item fractional derivative formula
+\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
+\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
+\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
 \end{itemize}

### 2022-08-19 exp-resurgence.tex
Rescale `z` for nicer series
Sketch ODE example

--- 2022-08-19 exp-resurgence.tex
@@
 with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du \]
+\color{DodgerBlue}
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
+\color{black}
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
 as
 % see expansion.sage
-\[ e^z \int_{\Lambda} e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \left(\frac{\tau}{\sqrt{12}}\right) + \frac{5}{6} \left(\frac{\tau}{\sqrt{12}}\right)^2 - \frac{32}{27} \left(\frac{\tau}{\sqrt{12}}\right)^3 + \frac{385}{216} \left(\frac{\tau}{\sqrt{12}}\right)^4 + \ldots \right] \frac{d\tau}{\sqrt{12}} \]
-using the substitution $\tfrac{1}{2} \tau^2 = 4u^3 - 3u + 1$.
+\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
+using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you get the series
+\color{DodgerBlue}
+\[ e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \]
+\[ e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \]
+\color{black}
+\begin{equation}
+e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+\end{equation}
+which has zero radius of convergence, but still makes sense as a formal power series.
+As another example, if you want to construct a holomorphic function $\Phi$ that satisfies the ordinary differential equation (ODE)
+\begin{center}
+\textbf{[shifted Bessel matching example above]},
+\end{center}
+you might start by trying to construct a formal power series solution instead.
+Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
+
 \begin{itemize}

### 2022-08-19 Introduction.tex

@@
 Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities.
-Moreover, in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical points.
+Moreover, in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values.
 We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.

### 2022-08-19 exp-resurgence.tex
Copy intro outline back into its old place

--- 2022-08-19 exp-resurgence.tex
@@
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
-\newcommand{\series}[1]{#1_\bullet}
-%\input{command}
+\newcommand{\series}{\tilde}
+
 \title{Resurgence of the Airy function \\ and other exponential integrals}
@@
 \section{Introduction}
+\subsection{Motivation}
+\subsubsection{Setting}
+You can often find a formal power series
+\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
+with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
+\color{DodgerBlue}
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
+\color{black}
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
+as
+% see expansion.sage
+\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
+using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you get the series
+\color{DodgerBlue}
+\[ e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \]
+\[ e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \]
+\color{black}
+\begin{equation}
+e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+\end{equation}
+which has zero radius of convergence, but still makes sense as a formal power series.
+As another example, if you want to construct a holomorphic function $\Phi$ that satisfies the ordinary differential equation (ODE)
+\begin{center}
+\textbf{[shifted Bessel matching example above]},
+\end{center}
+you might start by trying to construct a formal power series solution instead.
+Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
+
+\begin{itemize}
+\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
+\begin{itemize}
+\item Exponential integral: na\"{i}ve saddle point expansion.
+\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
+\item Feynman diagram series?
+\end{itemize}
+\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+\begin{itemize}
+\item Borel summation work in three steps.
+First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
+\item The series $\tilde{\phi}$ turns out to have a positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item {[Draw the square!]}
+\end{itemize}
+\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+\item In many cases, it picks correctly, producing an actual solution to your problem.
+\begin{itemize}
+\item The question of how that happens is the starting point for this paper.
+\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
+\end{itemize}
+\end{itemize}
+\subsubsection{Goals}
+\begin{itemize}
+\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+\begin{itemize}
+\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+\item The second problem is solving a certain kind of ODE.
+\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+\end{itemize}
+\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+\begin{itemize}
+\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\item \textbf{A new dictionary for ODEs.} The Laplace transform is often usd to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\end{itemize}
+\item Illustrate with detailed treatments of several examples.
+\begin{itemize}
+\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function.
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+\item Others haven't been discussed much.
+\end{itemize}
+\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
+[How do we work this into the introduction?]}
+\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\end{itemize}
+\color{DarkBlue}
 \subsection{Why does Borel resummation work?}

### 2022-08-19 exp-resurgence.tex
Move into outline into section

@@
 \begin{itemize}
-\item motivation
-\begin{itemize}
-\item Setting
-\begin{itemize}
-\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
-\begin{itemize}
-\item Exponential integral: na\"{i}ve saddle point expansion.
-\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
-\item Feynman diagram series?
-\end{itemize}
-\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-\begin{itemize}
-\item Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
-\item The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-\item {[Draw the square!]}
-\end{itemize}
-\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-\item In many cases, it picks correctly, producing an actual solution to your problem.
-\begin{itemize}
-\item The question of how that happens is the starting point for this paper.
-\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-\end{itemize}
-\end{itemize}
-\item Goals
-\begin{itemize}
-\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-\begin{itemize}
-\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-\item The second problem is solving a certain kind of ODE.
-\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-\end{itemize}
-\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-\begin{itemize}
-\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.\textcolor{black}{[Veronica---I dont't see why]}
-\end{itemize}
-\item Illustrate with detailed treatments of several examples.
-\begin{itemize}
-\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-\item Others haven't been discussed much.
-\end{itemize}
-\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
-[How do we work this into the introduction?]} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-\end{itemize}
 \item Exponential integrals
@@
 \end{itemize}
-\end{itemize}
+%%\end{itemize}
 \item Borel regularity

### 2022-08-20 exp-resurgence.tex
Move "Goals" outline into section

@@
 \section{Introduction}
-\subsection{Motivation}
-\subsubsection{Setting}
-You can often find a formal power series
-\[ \series{\Phi} = z^\sigma \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
-with $\sigma \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example, you might rewrite the integral
+\subsection{Setting \textcolor{orange}{[change title?]}}
+You can often find a formal power series \textcolor{magenta}{[check whether this exponent is $\tau$ on the nose or $\tau$ plus a constant]}
+\[ \series{\Phi} = z^\tau \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
+with $\tau \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
+For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
+\begin{center}
+\textbf{[shifted Bessel matching example above]},
+\end{center}
+behave near $z = \infty$, you might start by looking for ``transmonomial'' solutions $e^{\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
+
+you might start by trying to construct a formal power series solution instead.
+Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
+
+%%%
+
+For example, you might rewrite the integral
 \color{DodgerBlue}
@@
 which has zero radius of convergence, but still makes sense as a formal power series.
-As another example, if you want to construct a holomorphic function $\Phi$ that satisfies the ordinary differential equation (ODE)
-\begin{center}
-\textbf{[shifted Bessel matching example above]},
-\end{center}
-you might start by trying to construct a formal power series solution instead.
-Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
-
 \begin{itemize}
@@
 \end{itemize}
-\subsubsection{Goals}
+\subsection{Goals}
 \begin{itemize}
@@
 \item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\end{itemize}
+\subsection{Results}
+
+\color{orange}
+\begin{itemize}
+\item what does it mean being Borel regular?
+\item when does it happen?
+\begin{itemize}
+\item State new Borel regularity results
+\begin{itemize}
+\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
+\begin{itemize}
+\item Contextualize with previous work of P. Ramis
+\item Also contextualize with Loday-Richaud
+\end{itemize}
+\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item fractional derivative formula
+\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
+\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
+\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
+\end{itemize}
+\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
+\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+\end{itemize}
 \end{itemize}
@@
 \end{itemize}
-%%\end{itemize}
-\item Borel regularity
-\begin{itemize}
-\item what does it mean being Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [P.Ramis ?, Loday-Richaud ?, big idea in {\tt airy-resurgence}]
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
-\end{itemize}
-\end{itemize}
-\end{itemize}
 \item what are exponential integrals? \textcolor{gray}{has to be done}

### 2022-09-28 hypergeometric.tex
2nd order ODE and slight hypergeometric solutions

\DeclareSymbolFont{AMSb}{U}{msb}{m}{n}
\documentclass[11pt,a4paper,twoside,leqno,noamsfonts]{amsart}
           \usepackage{setspace}
\linespread{1.34}           
           %\onehalfspacing
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\definecolor{britishracinggreen}{rgb}{0.0, 0.26, 0.15}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\usepackage[utopia]{mathdesign}
    \DeclareSymbolFont{usualmathcal}{OMS}{cmsy}{m}{n}
    \DeclareSymbolFontAlphabet{\mathcal}{usualmathcal}
\usepackage[a4paper,top=4cm,bottom=3cm,left=3.5cm,
           right=3.5cm,bindingoffset=5mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{braket,caption,comment,mathtools,stmaryrd}
\usepackage{multirow,booktabs,microtype}
\usepackage{latexsym}
\usepackage{todonotes}
\usepackage{fancyhdr}
%\renewcommand{\sectionmark}[1]{\markboth{\thesection\ #1}{}}
\pagestyle{fancy}
% Clear the header and footer
\fancyhead{}
\fancyfoot{}
% Set the right side of the footer to be the page number
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{\baselineskip}
%\fancyhead[RE]{\rightmark}
%\fancyhead[RE]{}
\usepackage{soul} % per testo barrato
\usepackage[colorlinks,bookmarks]{hyperref} %
\hypersetup{colorlinks,%
            citecolor=britishracinggreen,%
            filecolor=black,%
            linkcolor=cobalt,%
            urlcolor=black}
\setcounter{tocdepth}{2}
%\setcounter{section}{-1}
\numberwithin{equation}{section}

% Veronica's custom commands
\input{command}

% symbology
\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
\newcommand{\maps}{\colon}
\newcommand{\van}{\mathfrak{m}}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\laplacepde}{\mathcal{D}}
\DeclareMathOperator{\Ai}{Ai}

\DeclareRobustCommand{\subtitle}[1]{\\#1}

\title{Resurgence of the Airy function \\ and other exponential integrals}
\author{Veronica Fantini and Aaron Fenyes}

\begin{document}
\maketitle
\section{Hypergeometric functions as Borel transform of second order ODE (\textit{series normales de \emph{I}er ordre})}

Let us consider the following linear second order ODE

\begin{equation}\label{eq}
\big[P(\tfrac{\partial}{\partial z})+\tfrac{1}{z}Q(\tfrac{\partial}{\partial z})+\tfrac{1}{z}R(\tfrac{1}{z})\big]f(z)=0
\end{equation}
with $\deg P=2$, $\deg Q=1$ and $R=O(\tfrac{1}{z})$. We denote by $\alpha_1,\alpha_2$ the roots of $P(\lambda)$ and we assume they are distinct. Furthermore we assume $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\neq 0$. The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be two independent solutions.

Under the previous assumptions we prove that the Borel transformed solution $\hat{f}(\zeta_j)$ is a Gauss hypergeometric function, $\zeta_j=\zeta-\alpha_j$.

\begin{prop}
Let $P(\lambda)=\lambda^2+a_1\lambda+a_0$, $Q(\lambda)=b_1\lambda+b_0$ and $R(\tfrac{1}{z})=\tfrac{c_1}{z}$ satisfying the previous assumptions. Then 
\begin{align}
\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(a,b;c;1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_2F_1\left(a,b;c;1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)
\end{align}
where the coefficients $a,b,c$ depend on the parameter of $P,Q,R$. 
\end{prop}

\begin{proof}
We start by taking the Borel transform of \eqref{eq}:
\begin{align}\label{eq:B}
(\zeta^2-a_1\zeta+a_0)\hat{f}(\zeta)+\int_0^\zeta b_1(-\zeta')\hat{f}(\zeta')d\zeta'+b_0\int_0^\zeta\hat{f}(\zeta')d\zeta'+c_1\int_0^\zeta(\zeta-\zeta')\hat{f}(\zeta')d\zeta'=0
\end{align} 
then we differentiate twice in order to have a differential equation which can be easier recognized as a hypergeometric equation. Since $\tilde{F}$ is slight and locally integrable at $0$ by assumption, Proposition 1 {\tt Resurgent Airy doc by Aaron} tells we are not loosing information taking derivatives, and that $\hat{f}(\zeta)$ is a solution of \eqref{eq:B} if and only if it is a solution of \eqref{eq:B_deriv}
\begin{align}
\label{eq:B_deriv}
\big[(\zeta^2-a_1\zeta+a_0)\partial_\zeta^2+(4\zeta-b_1\zeta-2a_1+b_0)\partial_\zeta+(c_1+2-b_1)\big]\hat{f}(\zeta)=0
\end{align}
We introduce some notation to simplify the computations, we denote by $\beta_1=4-b_1$, $\beta_0=b_0-2a_1$, $\gamma=c_1+2-b_1$ so \eqref{eq:B_deriv} turns into
\begin{align*}
\big[(\zeta-\alpha_1)(\zeta-\alpha_2)\partial_\zeta^2+(\beta_1\zeta+\beta_0)\partial_\zeta+\gamma\big]\hat{f}(\zeta)=0
\end{align*}
We consider the following change of coordinates $\zeta=\alpha_2-(\alpha_2-\alpha_1)\xi$\footnote{$\partial_\zeta=(\alpha_1-\alpha_2)^{-1}\partial_\xi$ and $\partial_\zeta^2=(\alpha_1-\alpha_2)^{-2}\partial_\xi^2$}
\begin{align*}
&\big[(\alpha_2-(\alpha_2-\alpha_1)\xi-\alpha_1)(\alpha_2-(\alpha_2-\alpha_1)\xi-\alpha_2)(\alpha_1-\alpha_2)^{-2}\partial_\xi^2+(\beta_1(\alpha_2-(\alpha_2-\alpha_1)\xi)+\beta_0)(\alpha_1-\alpha_2)^{-1}\partial_\xi+\gamma\big]\hat{f}(\xi)=0\\
&\big[(\alpha_2-\alpha_1)(1-\xi)(\alpha_1-\alpha_2)\xi(\alpha_1-\alpha_2)^{-2}\partial_\xi^2+(\beta_1\alpha_2-\beta_1(\alpha_2-\alpha_1)\xi+\beta_0)(\alpha_1-\alpha_2)^{-1}\partial_\xi+\gamma\big]\hat{f}(\xi)=0\\
&\big[-(1-\xi)\xi\partial_\xi^2+((\beta_1\alpha_2+\beta_0)(\alpha_1-\alpha_2)^{-1}+\beta_1\xi)\partial_\xi+\gamma\big]\hat{f}(\xi)=0\\
&\big[(1-\xi)\xi\partial_\xi^2-((\beta_1\alpha_2+\beta_0)(\alpha_1-\alpha_2)^{-1}+\beta_1\xi)\partial_\xi-\gamma\big]\hat{f}(\xi)=0
\end{align*}

The latter equation is an hypergeometric equation of parameters 
\begin{align*}
&C=(\beta_1\alpha_2+\beta_0)(\alpha_2-\alpha_1)^{-1}\\
&A+B+1=\beta_1=4-b_1 \Rightarrow A+B=3-b_1\\
&AB=\gamma=c_1+2-b_1
\end{align*}
and a solution is given by 
\begin{align*}
%\hat{f}(\xi)=(1-\xi)^{C-A-B} {}_2F_1(C-A,C-B;C;\xi)\\
\hat{f}(\xi)&=\xi^{1-C} {}_2F_1(A-C+1,B-C+1;2-C;\xi)\\
&=\left(\frac{\alpha_2-\zeta}{\alpha_2-\alpha_1}\right)^{1-C} {}_2F_1\left(A-C+1,B-C+1;2-C;\frac{\alpha_2-\zeta}{\alpha_2-\alpha_1}\right)\\
&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{1-C} {}_2F_1\left(A-C+1,B-C+1;2-C;1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)
\end{align*}

\end{proof}

\bibliographystyle{plain}
\bibliography{airy-resurgence}
\end{document}

### 2022-11-28 exp-resurgence.tex
Revise "Setting" based on end-of-summer meeting
I think this is from our last meeting before I moved to New Hampshire.

@@
 \subsection{Setting \textcolor{orange}{[change title?]}}
-You can often find a formal power series \textcolor{magenta}{[check whether this exponent is $\tau$ on the nose or $\tau$ plus a constant]}
-\[ \series{\Phi} = z^\tau \left( \frac{c_0}{z} + \frac{c_1}{z^2} + \frac{c_2}{z^3} + \frac{c_3}{z^4} + \ldots \right), \]
-with $\tau \in [0, 1)$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
+You can often find a formal power series \textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
+\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
+with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
 For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
-\begin{center}
-\textbf{[shifted Bessel matching example above]},
-\end{center}
-behave near $z = \infty$, you might start by looking for ``transmonomial'' solutions $e^{\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
+\begin{equation}
+\text{\bf [one-third Bessel equation, rescaled to match integral example]} \label{eqn:bessel-rescaled}
+\end{equation}
+behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
+Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+\begin{equation}
+e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+\end{equation}
+and its constant multiples.
 
@@
 \begin{equation}
-e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] %%\label{series:bessel-ex}
 \end{equation}

### 2022-11-28 hypergeometric.tex

@@
 with $\deg P=2$, $\deg Q=1$ and $R=O(\tfrac{1}{z})$.
-We denote by $\alpha_1,\alpha_2$ the roots of $P(\lambda)$ and we assume they are distinct.
-Furthermore we assume $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\neq 0$.
+We denote by $\alpha_1,\alpha_2$ the roots of $P(-\lambda)$ and we assume they are distinct.
+Furthermore we assume $\tau_j:=\frac{Q(\alpha_j)}{P'(\alpha_j)}\neq 0$.
 The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be two independent solutions.
@@
 
+\begin{prop}
+We verify that 
+\begin{equation}
+\hat{f}(\zeta_1)=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{1-C} \, {}_2F_1\left(A-C+1,B-C+1;2-C;1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)
+\end{equation}
+\begin{equation}
+\hat{f}(\zeta_2)=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{1-C} \, {}_2F_1\left(A-C+1,B-C+1;2-C;1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)
+\end{equation}
+are indeed resurgent.  
+\end{prop}
+
+\begin{proof}
+\color{Tan}
+Recall that the analytic continuation of Gauss hypergeometric functions is given in terms of other hypergeometric fucntions (see DLMF 15.2.3):
+\begin{align*}
+\hat{f}(\zeta_1+i0)-\hat{f}(\zeta_1-i0)&\propto\left(\frac{\zeta_1}{\alpha_1-\alpha_2}\right)^{C-A-B}\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{1-C} {}_2F_1\left(1-A,1-B;C+1-A-B;\frac{\zeta_1}{\alpha_2-\alpha_1}\right)\\
+&=(-1)^{C-A-B}\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{C-A-B}\left(\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{1-C}\cdot\\
+&\qquad\qquad \cdot {}_2F_1\left(1-A,1-B;C+1-A-B;1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)\\
+\end{align*}
+\color{black}
+\end{proof}
+
+\section{Hypergeometric functions as Borel transform of third order ODE}
+
+Let us consider the following linear third order ODE
+
+\begin{equation}\label{eq3}
+\big[P(\tfrac{\partial}{\partial z})+\tfrac{1}{z}Q(\tfrac{\partial}{\partial z})+\tfrac{1}{z}R(\tfrac{1}{z})\big]f(z)=0
+\end{equation}
+with $\deg P=3$, $\deg Q=2$ and $R=O(\tfrac{1}{z})$.
+We denote by $\alpha_1,\alpha_2,\alpha_3$ the roots of $P(-\lambda)$ and we assume they are distinct.
+There are three possible scenarios illustrated in figure \ref{fig3} below:
+\begin{itemize}
+\item $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$
+\item $|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|<|\alpha_1-\alpha_2|$
+\item $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$
+\end{itemize}
+
+\begin{figure}[h]\label{fig3}
+\begin{tikzpicture}
+\draw [red](-1,1)--(-3,1);
+\draw [green](-1,1)--(-1.25,3);
+\draw [blue](-3,1)--(-1.25,3);
+\node[font=\tiny, below] at (-3,1) {$\alpha_1$};
+\node[font=\tiny, below] at (-1,1) {$\alpha_2$};
+\node[font=\tiny, above] at (-1.25,3) {$\alpha_3$};
+\draw [green](0.25,1)--(1.5,2);
+\draw [red](0.25,1)--(2.75,1);
+\draw [green](1.5,2)--(2.75,1);
+\node[font=\tiny, below] at (0.25,1) {$\alpha_1$};
+\node[font=\tiny, below] at (2.75,1) {$\alpha_2$};
+\node[font=\tiny, above] at (1.5,2) {$\alpha_3$};
+\draw [red](4,1)--(6,1);
+\draw [red](4,1)--(5,2.73);
+\draw [red](6,1)--(5,2.73);
+\node[font=\tiny, below] at (4,1) {$\alpha_1$};
+\node[font=\tiny, below] at (6,1) {$\alpha_2$};
+\node[font=\tiny, above] at (5,2.73) {$\alpha_3$};
+\end{tikzpicture}
+\end{figure}
+
+Furthermore we assume $\tau_j:=\frac{Q(\alpha_j)}{P'(\alpha_j)}\in\mathbb{Q}$.
+The latter assumption guarantees the formal solution $\tilde{f}$ being slight, while the former assumption implies there will be three independent solutions.
+
+Under the previous assumptions we prove that the Borel transformed solution $\hat{f}(\zeta_j)$ is hypergeometric, $\zeta_j=\zeta-\alpha_j$.
+
+\begin{prop}
+Let $P(\lambda)=\lambda^3+a_2\lambda^2+a_1\lambda+a_0$, $Q(\lambda)=b_2\lambda^2+b_1\lambda+b_0$ and $R(\tfrac{1}{z})=\tfrac{c_1}{z}+\tfrac{c_2}{z^2}$ satisfying the previous assumptions. Then 
+\begin{itemize}
+\item if $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$
+\color{red}
+\begin{align}
+\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
+\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
+\hat{f}(\zeta_3)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_3}{\alpha_2-\alpha_1} \right)
+\end{align}
+\color{black}
+\item if $|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$
+\color{red}
+\begin{align}
+\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
+\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_2F_1\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
+\hat{f}(\zeta_3)&=?
+\end{align}
+\color{black}
+\item if $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|$ 
+\color{red}
+\begin{align}
+\hat{f}(\zeta_1)&=\left(1-\frac{\zeta_1}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_1}{\alpha_2-\alpha_1} \right)\\
+\hat{f}(\zeta_2)&=\left(1-\frac{\zeta_2}{\alpha_1-\alpha_2}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_2}{\alpha_1-\alpha_2} \right)\\
+\hat{f}(\zeta_3)&=\left(1-\frac{\zeta_3}{\alpha_2-\alpha_1}\right)^{c-1} \, {}_3F_2\left(\mathbf{m};\mathbf{n};1-\frac{\zeta_3}{\alpha_2-\alpha_1} \right)
+\end{align}
+
+\end{itemize}
+
+\color{black}
+where the coefficients $\mathbf{m}=(m_1,m_2,m_3),\mathbf{n}=(n_1,n_2)$ depend on the parameter of $P,Q,R$. 
+\end{prop}
+
+\begin{proof}
+The strategy is analogous to the one for second order ODEs. Hence, we first consider the Borel transform of equation \ref{eq3}: 
+\begin{multline}\label{borel 3}
+P(-\zeta)\hat{f}+\int_0^\zeta Q(-\zeta')\hat{f}(\zeta')d\zeta'+c_1\int_0^\zeta(\zeta-\zeta')\hat{f}(\zeta')d\zeta'+\frac{c_2}{2}\int_0^\zeta(\zeta-\zeta')^2\hat{f}(\zeta')d\zeta'=0
+\end{multline}
+
+Although equation \eqref{borel 3} is an integral equation, since $\tilde{f}$ is slight, $\hat{f}$ is a solution of \eqref{borel 3} if and only if it is a solution of the third order ODE obtained by differentiating \eqref{borel 3} three times:
+\begin{multline}\label{borel_ODE 3}
+\big[P(-\zeta)\partial_\zeta^3+(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2+(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta+(-P'''(-\zeta)+Q''(-\zeta)+c_2)\big]\hat{f}=0
+\end{multline}
+
+Notice that
+
+\begin{align*}
+P(-\zeta)&=(\zeta-\alpha_1)(\zeta-\alpha_2)(\zeta-\alpha_3)\\
+-P'(-\zeta)&=(\zeta-\alpha_2)(\zeta-\alpha_3)+(\zeta-\alpha_1)(\zeta-\alpha_3)+(\zeta-\alpha_2)(\zeta-\alpha_1)\\
+P''(-\zeta)&=6\zeta-2\alpha_1-2\alpha_2-2\alpha_3
+\end{align*}
+
+We now study separately the three scenarios:
+\begin{itemize}
+\item if $\ell=|\alpha_1-\alpha_2|<|\alpha_2-\alpha_3|<|\alpha_1-\alpha_3|$ we claim that \eqref{borel_ODE 3} is ??
+\item if $\alpha_2=\alpha_3+\ell,\, \alpha_1=\alpha_3-\ell$ we claim that \eqref{borel_ODE 3} is a ??
+\color{Aquamarine}
+Change coordinates $y=\frac{\zeta-\alpha_1}{\ell}$:
+\begin{align*}
+P(-\zeta)\partial_\zeta^3&\longrightarrow -\ell^3y(\ell y+\alpha_1-\alpha_2)(\ell y+\alpha_1-\alpha_3)\frac{1}{\ell^3}\partial_y^3=y(1-y^2)\partial_y^3\\
+(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2&\longrightarrow (3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2\\
+(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta&\longrightarrow(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y\\
+-P'''(-\zeta)+Q''(-\zeta)+c_2&\longrightarrow -6+2b_2+c_2
+\end{align*}
+
+Change coordinates $s=y^2$:
+\begin{align*}
+y(1-y^2)\partial_y^3&\longrightarrow 8(1-s)s^2\partial_s^3+12(1-s)s\partial_s^2\\
+(3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2&\longrightarrow \big[6(3s-1)+2(b_2s+\frac{2b_2\alpha_1-b_1}{\ell}y+\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2})\big](\partial_s+2s\partial_s^2)\\
+(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y&\longrightarrow 4(2b_2-9)s\partial_s+2\frac{4b_2\alpha_1-2b_1+c_1}{\ell}y\partial_s
+\end{align*}
+
+\begin{multline}
+\Big[8(1-s)s^2\partial_s^3+\big[4(6+b_2)s+4\frac{2b_2\alpha_1-b_1}{\ell}y+4\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}\big]s\partial_s^2\Big.\\
+\Big.\big[-2(9-2b_2)s-2(3-2b_2)+2\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}+2\frac{6b_2\alpha_1-3b_1+c_1}{\ell}y\big]\partial_s-6+2b_2+c_2\Big]\hat{f}=0
+\end{multline}
+
+\begin{align*}
+\frac{2b_2\alpha_1-b_1}{\ell}y+\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2}=2n_1+2n_2-2\\
+6+b_2=-2(3+m_1+m_2+m_3)\\
+\big[-(3-2b_2)+2(\frac{b_2\alpha_1^2-\alpha_1b_1+b_0}{\ell^2})+\frac{8b_2\alpha_1-4b_1+c_1}{\ell}y\big]=4n_1n_2\\
+(9-2b_2)=4(1+m_1+m_2+m_3+m_1m_2+m_1m_3+m_2m_3)\\
+-6+2b_2+c_2=8m_1m_2m_3
+\end{align*}
+\color{black}
+\item if $|\alpha_1-\alpha_2|=|\alpha_2-\alpha_3|=|\alpha_1-\alpha_3|=\ell$ we claim that \eqref{borel_ODE 3} is a generalized hypergeometric equation.
+Without loss of generality we assume $\alpha_2=\alpha_1+\ell$ and $\alpha_3=\alpha_1+\frac{\ell}{2}+i\frac{\sqrt{3}}{2}\ell$.
+
+Change coordinates $y=\frac{\zeta-\alpha_1}{\ell}+\frac{\sqrt{3}+i}{2}$, then 
+\begin{align*}
+P(-\zeta)\partial_\zeta^3&\longrightarrow -\ell y(\ell y+\alpha_1-\alpha_2)(\ell y+\alpha_1-\alpha_3)\frac{1}{\ell^3}\partial_y^3=y(1-y^2)\partial_y^3\\
+(-3P'(-\zeta)+Q(-\zeta))\partial_\zeta^2&\longrightarrow (3\ell^{2}(3y^2-1)+Q(-\ell y-\alpha_1))\frac{1}{\ell^2}\partial_y^2\\
+(3P''(-\zeta)-2Q'(-\zeta)+c_1)\partial_\zeta&\longrightarrow(-18\ell y-2Q'(-\ell y-\alpha_1)+c_1)\frac{1}{\ell}\partial_y\\
+-P'''(-\zeta)+Q''(-\zeta)+c_2&\longrightarrow -6+2b_2+c_2
+\end{align*} 
+\end{itemize}
+
+\end{proof}
+
 \bibliographystyle{plain}

### 2022-11-28 kawai+takei vs mariño.tex

@@
 
-\usepackage{ajf}
+%\usepackage{ajf}
 \usepackage{amsthm}
@@
 \newtheorem{thm}{Theorem}
-
-\DeclareMathOperator{\Ai}{Ai}
+\usepackage{url}
+\usepackage[hmargin=1.5in]{geometry}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{xcolor}
+%\DeclareMathOperator{\Ai}{Ai}
 
@@
 \begin{align*}
-\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{2/3} x \right] \psi(x, \eta) = 0 \\
-\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{-4/3} \eta^2 x \right] \psi(x, \eta) = 0 \\
-\eta^{-4/3} \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0.
+\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{2/3} x\right] \psi(x, \eta) = 0 \\
+\left[\eta^{-4/3} \left(\frac{d}{dx}\right)^2 - \eta^{-4/3}\eta^2 x \right] \psi(x, \eta) = 0 \\
+\eta^{-4/3} \left[\left(\frac{d}{dx}\right)^2 - \eta^2 x\right] \psi(x, \eta) = 0.
 \end{align*}
-Hence, $\psi(w \eta^{-2/3}, \eta) = k(\eta) \Ai(w)$ is a solution for any holomorphic function $k$.
+Hence, $\psi(w \eta^{-2/3}, \eta) = k(\eta) \mathsf{Ai}(w)$ is a solution for any holomorphic function $k$.
+
+\section{Veronica's change of coordinates}
+
+Kawai and Takei study the WKB analysis of the equation
+
+\begin{equation}
+\label{WKB_Airy} 
+\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
+\end{equation}
+as $\eta\to\infty$.
+They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
+In the coordinates $t=yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
+\begin{align*}
+\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
+\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
+\end{align*}
+where $s=3t/4+1/2$. 
+The same hypergeometric functions have been computed in Section ?? as the Borel transform of the formal solutions of the Airy equation
+
+\begin{equation}
+\label{Airy}
+\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
+\end{equation}
+
+Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
+So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
+
+First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
+\begin{align*}
+\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
+\end{align*} 
+then $t=yx^{-3/2}$ is the conjugate variable of $q=\eta x^{3/2}$ up to correction by a factor of $x^{-3/2}$
+\begin{align*}
+\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!} y^{n}=x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}. 
+\end{align*}
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
+\begin{equation}
+\label{eq_Phi}
+\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
+\end{equation}
+
+\begin{proof}
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
+&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
+&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
+&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
+\end{align*}
+\end{proof}
+Now rewrite \eqref{eq_Phi} in the coordinates $q=\eta x^{3/2}$: 
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\frac{9}{4}\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{4}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\frac{3}{2}\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{3}\eta x^{-1/2}\frac{d}{dq}+\frac{2}{3}\, \eta\,  x^{-1/2}\frac{d}{dq}-\frac{1}{9}x^{-2}-\frac{4}{9}\eta^2x\right]\Phi=0\\
+&\left[\eta^2\left(\frac{d}{dq}\right)^2+\eta x^{-3/2}\frac{d}{dq}-\frac{1}{9}x^{-3}-\frac{4}{9}\eta^2\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-\frac{4}{9}\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-\frac{4}{9}\right]\Phi=0
+\end{align*}
+
+therefore $\Phi(q)$ is a solution of the transform Airy equation (see draft2).
 

### 2022-11-28 seminar at Matamzee -- Veronica.tex

\DeclareSymbolFont{AMSb}{U}{msb}{m}{n}
\documentclass[11pt,a4paper,twoside,leqno,noamsfonts]{amsart}
           \usepackage{setspace}
\linespread{1.34}           
           %\onehalfspacing
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
\definecolor{britishracinggreen}{rgb}{0.0, 0.26, 0.15}
\definecolor{cobalt}{rgb}{0.0, 0.28, 0.67}
\usepackage[utopia]{mathdesign}
    \DeclareSymbolFont{usualmathcal}{OMS}{cmsy}{m}{n}
    \DeclareSymbolFontAlphabet{\mathcal}{usualmathcal}
\usepackage[a4paper,top=4cm,bottom=3cm,left=3.5cm,
           right=3.5cm,bindingoffset=5mm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{braket,caption,comment,mathtools,stmaryrd}
\usepackage{multirow,booktabs,microtype}
\usepackage{latexsym}
\usepackage{todonotes}
\usepackage{fancyhdr}
%\renewcommand{\sectionmark}[1]{\markboth{\thesection\ #1}{}}
\pagestyle{fancy}
% Clear the header and footer
\fancyhead{}
\fancyfoot{}
% Set the right side of the footer to be the page number
\fancyfoot[R]{\thepage}
\addtolength{\headheight}{\baselineskip}
%\fancyhead[RE]{\rightmark}
%\fancyhead[RE]{}
\usepackage{soul} % per testo barrato
\usepackage[colorlinks,bookmarks]{hyperref} %
\hypersetup{colorlinks,%
            citecolor=britishracinggreen,%
            filecolor=black,%
            linkcolor=cobalt,%
            urlcolor=black}
\setcounter{tocdepth}{2}
%\setcounter{section}{-1}
\numberwithin{equation}{section}

% Veronica's custom commands
\input{command}

% symbology
\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
\newcommand{\maps}{\colon}
\newcommand{\van}{\mathfrak{m}}
\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\laplacepde}{\mathcal{D}}
\DeclareMathOperator{\Ai}{Ai}

\DeclareRobustCommand{\subtitle}[1]{\\#1}

\title{Resurgence and Borel regularity for ODEs \\ Seminar at Matamzee}
\author{Veronica Fantini}

\begin{document}
\maketitle
\section{What is resurgence}

Theory of resurgence was introduced by Ecalle in the '80 and it deals with divergent power series

\begin{equation}
\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n-1}\in\C[\![z^{-1}]\!], \quad \text{ with } a_n\sim n!
\end{equation}

they have zero radius of convergence.

\subsection{Paradigma of Borel--Laplace sum}

\[
\begin{tikzcd}
\C[\![z^{-1}]\!]\ni\tilde{\Phi}\defeq\sum_{n\geq 0}a_nz^{-n-1} \arrow[rr, "\mathcal{B}"] & & \tilde{\phi}(\zeta)=\sum_{n\geq 0}\frac{a_n}{n!}\zeta^{n}\in\C\lbrace\zeta\rbrace
\end{tikzcd}
\]
\textcolor{magenta}{[make drawings of the Borel plane]}

Study the analytic continuation of $\tilde{\phi}(\zeta)$ and if $\hat{\phi}(\zeta)$ \textbf{behaves well} you can go back to the $z$-plane via Laplace transform

\[
\begin{tikzcd}
\C[\![z^{-1}]\!]\ni\tilde{\Phi}\defeq\sum_{n\geq 0}a_nz^{-n-1} \arrow[rr, "\mathcal{B}"] & & \tilde{\phi}(\zeta)=\sum_{n\geq 0}\frac{a_n}{n!}\zeta^{n}\in\C\lbrace\zeta\rbrace\arrow[ld,"\mathcal{L}^\theta "]\\
& \Phi\in\mathcal{O}(H_\theta) &
\end{tikzcd}
\]

\textcolor{magenta}{[make drawings of the $z$-plane]}

The relation with $\tilde{F}$ is via asymptotic expansion as $\Re ze^{i\theta}\to \infty$

\[
\begin{tikzcd}
\C[\![z^{-1}]\!]\ni\tilde{\Phi}\defeq\sum_{n\geq 0}a_nz^{-n-1} \arrow[rr, "\mathcal{B}"] & & \tilde{\phi}(\zeta)=\sum_{n\geq 0}\frac{a_n}{n!}\zeta^{n}\in\C\lbrace\zeta\rbrace\arrow[ld,"\mathcal{L}^\theta "]\\
& \Phi\in\mathcal{O}(H_\theta)\arrow[lu,dashed, "\text{asymptotics}"] &
\end{tikzcd}
\]

The Laplace transform is defined

\begin{equation}
F(z)\cong\mathcal{L}^{\theta}f(z)=\int_0^{+\infty e^{i\theta}}e^{-z\zeta}f(\zeta)d\zeta
\end{equation}
for $\theta\in [0,2\pi)$ and $F\in\mathcal{O}(H_\theta)$ if and only if $|f|\leq Ae^{-c|z|}$ for every $z$ in a tubular neighbourhood. In general one has to check 
\begin{itemize}
\item $\hat{f}$ can be defined through infinity;
\item $\hat{f}$ has the right decaying at $\infty$. \textcolor{red}{HARDER}
\end{itemize}

For the first one, we have to study the singularities of $\hat{f}$.

\subsubsection{Ecalle's resurgent function}

$f\in\C\lbrace \zeta\rbrace$ is resurgent if it endlessly analytically continuable, i.e.

\textcolor{magenta}{[draw picture]}

He defined the \textbf{theory of singularities} and \textbf{relaxed the definition of Laplace transform} to deal with log- singularities, square root, poles, etc.

Examples of (\textit{minor} of) singularities 
\begin{align*}
\overset{\vee}{I}_c(\zeta)\defeq\frac{\zeta^{c-1}}{(1-e^{-2\pi ic})\Gamma(c)}\quad c\in\C\setminus\Z_{>0}\\
\overset{\vee}{I}_c(\zeta)\defeq\frac{\zeta^{c-1}}{2\pi i \Gamma(c)}\log\zeta \quad c\in\Z_{>0}
\end{align*}

\textcolor{magenta}{draw singularity in a row (like Painlev\'e)}

\subsubsection{The role of $\theta$}

Varying $\theta$, as long as $|\theta-\theta'|<\pi$, $\mathcal{L}^\theta f=\mathcal{L}^{\theta'}$ on $H_\theta\cap H_{\theta'}$. More generally, they disagree

\begin{align*}
\mathcal{L}^\theta-\mathcal{L}^{\theta'}=S_{\theta\theta'}\mathcal{L}^{\theta'}\quad S_{\theta\theta'}\in\C
\end{align*}

These phenomena is called the Stokes phenomena. Computing the Stokes constant is crucial to understand the structure of $F$, and Ecalle developed the\textit{ Alien calculus} to study the  Stokes phenomena.

Summarizing: the core of resurgence theory is 
\begin{enumerate}
\item study the Borel plane;
\item compute the Stokes constants. 
\end{enumerate}

\textcolor{blue}{stress that resurgence is about Borel plane, but knows about the $z$-plane.}

\subsection{Motivation: why divergent series?}

\begin{itemize}
\item \textbf{thimbles integrals}:

\textcolor{Orchid}{COOL}: if $f$ is algebraic, $I(z)$ is a period, i.e. it is a geometric object studied (Deligne, Malgrange, Pham, Kontsevich--Soibelman $\sim$ generalization when $f$ is local coordinate for 1-form $f=\int \alpha$) and the resurgence of $\tilde{I}$ has a geometric nature 
\begin{itemize}
\item critical values of $f$ $\sim$ singularity in the Borel plane
\item Picard--Lefschetz theory $\sim$ Stokes phenomena
\item gradient lines $\sim$ Stokes indexes
\end{itemize}
\item \textbf{ODEs} with irregular singularity at $\infty$: they admits formal solutions, and if the ODE is regular enough M.A.E.T. assures the existence of a holomorphic solution asymptotic to the formal one. 
\begin{itemize}
\item non linear ODEs have interesting behaviours (maybe be resonant)
\end{itemize}
\item \textbf{q--difference equation}: like ODEs, 
\begin{equation}
n! \rightsquigarrow q^{n(n+1)/2}\,\, |q|>1
\end{equation}
there is a dictionary between ODEs and q-difference equation. 
\end{itemize}

\section{ODEs}
\subsection{Which class of ODEs we consider}
\begin{equation}\label{eq}
[P(\partial/\partial_z)+\frac{1}{z}Q(\partial/\partial_z)+\sum_{j=2}^dz^{-j}R_j(\partial/\partial_z)]\Phi(z)=0
\end{equation}
with
\begin{itemize}
\item $P(\lambda)$ a degree $d$ polynomial
\item $Q(\lambda)$ a degree $d-1$ polynomial 
\item $R_j(\lambda)$ are degree $d-j$ polynomials 
\end{itemize}
they are defined by Poincar\'e as \textit{series normal de Ier ordre}. As a general fact, if $P(-\lambda)$ has simple roots $\alpha_1,...,\alpha_d$ then \eqref{eq} admits $d$ formal solution of the form
\begin{equation}
\tilde{\Phi}_j(z)=e^{-\alpha_jz}z^{-\tau_j}\tilde{\phi}_j(z)\in e^{-\alpha_jz}z^{-\tau_j}\C[\![z^{-1}]\!][\log(z)]
\end{equation}  
where $\tau_j=-Q(\alpha_j)/P'(\alpha_j)$.

The M.A.E.T theorem, guarantees under suitable assumptions on the ODE, the existence of an holomorphic solution $\Phi_j(z)$ asymptotic to $\tilde{\Phi}_j$ in a suitable sector.

Our goal is to prove that $\Phi_j(z)\propto\mathcal{L}_{\zeta_j}^{\theta}\mathcal{B}\tilde{\Phi}_j$ for some angle $\theta$.

Equivalently said, Borel--Laplace summability picks an actual solution of the ODE.

\subsection{Borel regularity for ODEs}

\[
\begin{tikzcd}
& P\left(\frac{\partial}{\partial_z}\right)+\frac{1}{z}Q\left(\frac{\partial}{\partial_z}\right)+\sum_{j=2}^dz^{-j}R_j\left(\frac{\partial}{\partial_z}\right) & \\
\Phi_j\arrow[ru,red] & & \tilde{\Phi}_j\arrow[lu]\arrow[dd, "\mathcal{B}"] \\
& & \\
\hat{\phi}_j\arrow[uu,  "\mathcal{L}_{\zeta,\alpha_j}^\theta"]& & \tilde{\phi}_j(\zeta)\arrow[ll,"\text{sum}"] 
\end{tikzcd}
\]
a priori it is not guarantee that $\mathsf{L}_{\zeta,\alpha_j}^\theta\mathcal{B}\tilde{\Phi}_j$ is a solution of \eqref{eq}, because different functions may have the same asymptotic.

Idea of the proof is based on the following diagram:

\[
\begin{tikzcd}
& P\left(\frac{\partial}{\partial_z}\right)+\frac{1}{z}Q\left(\frac{\partial}{\partial_z}\right)+\sum_{j=2}^dz^{-j}R_j\left(\frac{\partial}{\partial_z}\right)\arrow[dd,"\mathcal{B}"] & \\
\Phi_j\arrow[ru,red] & & \tilde{\Phi}_j\arrow[lu]\arrow[dd, "\mathcal{B}"] \\
&P(-\zeta)+\partial_\zeta^{-1}\circ Q(-\zeta)+\sum_{j=2}^d \partial_\zeta^{-j}\circ R_j(-\zeta) & \\
\hat{\phi}_j\arrow[uu,  "\mathcal{L}_{\zeta,\alpha_j}^\theta"]& & \tilde{\phi}_j(\zeta)\arrow[ll,"\text{sum}"]\arrow[ul] 
\end{tikzcd}
\]

there exists a solution $\tilde{\phi}_j(\zeta)$ which is also slight, and in suitable coordinates it is a convergent series in $\overset{\vee}{I}_{n+\tau_j}(\zeta_j)$.  
\[
\begin{tikzcd}
& P\left(\frac{\partial}{\partial_z}\right)+\frac{1}{z}Q\left(\frac{\partial}{\partial_z}\right)+\sum_{j=2}^dz^{-j}R_j\left(\frac{\partial}{\partial_z}\right)\arrow[dd,"\mathcal{B}"] & \\
\Phi_j\arrow[ru,red] & & \tilde{\Phi}_j\arrow[lu]\arrow[dd, "\mathcal{B}"] \\
&P(-\zeta)+\partial_\zeta^{-1}\circ Q(-\zeta)+\sum_{j=2}^d \partial_\zeta^{-j}\circ R_j(-\zeta)\arrow[uu,"\mathcal{L}"] & \\
\hat{\phi}_j\arrow[uu,  "\mathcal{L}_{\zeta,\alpha_j}^\theta"]& & \tilde{\phi}_j(\zeta)\arrow[ll,"\text{sum}"] \arrow[ul] 
\end{tikzcd}
\]

the Laplace transform along a Hankel contour gives an inverse for $\mathcal{B}$.

[repeat again the idea: a solution of \eqref{eq} is Borel regular, because its Borel--Laplace sum gives an actual solution.]

\begin{remark}
\textbf{[Extend the definition of $\mathcal{B}$ and $\mathcal{L}$]}
\begin{itemize}
\item As far as $\Gamma(\tau)$ is well defined, we can allow $\tau\in\R$ and extend the definition of $\mathcal{B}$. 
\item Ecalle's theory of singularity introduces a generalized Laplace transform which take as contour a Hankel contour rather than a straight line. This is not the only generalization of Laplace transform Ecalle introduced. 
\end{itemize}
\end{remark}

\subsection{Proof of Borel regularity}
\begin{itemize}
\item Borel transform the $\text{ODE}_z$ and we get $\text{IE}_\zeta$. 
\begin{itemize}
 \item IE are not easy to be solved so usually in the application we differentiate them to get an $\text{ODE}_\zeta$. If $\hat{\phi}$ is slight we don't loose informations by differentiating.
\end{itemize}
\item by Prop 1, there exists a solution $\hat{\phi}(\zeta_j)$ 
\begin{align*}
\hat{\phi}(\zeta_j)&=\zeta_j^{\tau_j-1}+\tilde{g}_j & \tilde{g}_j\in\mathcal{HL}^{\infty,1-\tau_j-\epsilon}\\
&=\sum_{k\geq 0}a_k\zeta_j^{\tau_j-1+k} +\text{h.f.} & \\
&=(1-e^{-2\pi i\tau_j})\sum_{n\geq 0}\tilde{a}_n\overset{\vee}{I}_{\tau_j+n}(\zeta_j) & \quad \tilde{a}_n=a_n\Gamma(\tau_j+n), \\
& & \overset{\vee}{I}_c(\xi)=\frac{\xi^{c-1}}{(1-e^{-2\pi ic})\Gamma(c)}\\
\end{align*}
\item $\hat{\phi}(\zeta_j) $ is a germ of meromorphic function
\begin{align*}
\limsup_{n\to\infty}\sqrt[n]{\frac{|\tilde{a}_n|}{\Gamma(\tau_j+n)(1-e^{-2\pi i(\tau_j+n)}}}&=\limsup_{n\to\infty}\sqrt[n]{\frac{{a}_n\Gamma(\tau_j+n)}{\Gamma(\tau_j+n)(1-e^{-2\pi i(\tau_j+n)}}}=\\
&=\limsup_{n\to\infty}\sqrt[n]{\frac{{a}_n}{(1-e^{-2\pi i(\tau_j+n)}}}<+\infty
\end{align*}
 where in the last step we use 
 \begin{multline}
 \infty+>||\tilde{g}_j \zeta_j^{\tau_j+\epsilon-1}||_\infty=||\sum_{n\geq 1}\zeta_j^{\tau_j-1+n}\zeta_j^{-(\tau_j+\epsilon)+1} ||_\infty=||\sum_{n\geq 1}a_n\zeta_j^{n-\varepsilon}||_\infty
 \end{multline}
 \item by Ecalle definition of Laplace transform [see Sauzin], $\hat{\phi}(\zeta_j)$ has a well defined Laplace transform which is asymptotic to $\sum_{n\geq 0}\tilde{a}_nz^{-\tau_j-n}(1-e^{-2\pi i \tau_j})=(1-e^{-2\pi i \tau_j})\sum_{n\geq 0}a_n\Gamma(\tau_j+n)z^{-\tau_j-n}$
 \begin{align*}
 (1-e^{-2\pi i \tau_j})\sum_{n\geq 0}a_n\Gamma(\tau_j+n)z^{-\tau_j-n}\sim \mathcal{L}_{\zeta_j}^\theta\hat{\phi}_j=e^{\alpha_jz}\mathcal{L}_{\zeta,\alpha_j}^\theta\hat{\phi}
 \end{align*}
 hence 
 \begin{equation}
 \mathcal{L}_{\zeta,\alpha_j}^\theta\hat{\phi} \sim e^{-\alpha_jz}z^{-\tau_j} \sum_{n\geq 0}a_n\Gamma(\tau_j+n)z^{-n}\propto \tilde{\Phi}_j(z)
 \end{equation}
\end{itemize}

\subsection{Corollary: construct an explicit holomorphic solution predicted by M.A.E.T.}

\begin{corollary}
The holomorphic solution which exists by M.A.E.T. can be characterized as the Borel--Laplace sum of $\tilde{\Phi}_j$.  
\end{corollary}

\section{q-difference equations}

\subsection{Formal solutions vs actual solutions: paradigma of $q$-Borel Laplace summability}

\subsubsection{From ODEs to $q$- difference equations}

\begin{center}
\begin{tabular}{c|c}
\hline
ODE     & $q$-difference, $|q|>1$ \\
\hline
$\sum_{n\geq 0}^d a_{n}(z)\frac{\partial^n}{\partial z^n}\Phi=a\in\mathbb{C}(z)$ and $a_n\in\mathbb{C} (z)$    & $\sum_{n\geq 0} a_{q,n}\sigma_q^n f=a_q\in\mathbb{C}(x)$ and $a_{q,n}\in\mathbb{C}(x)$ \\
& \\
$z^2\Phi'(z)+\Phi(z)=z$ & $x\sigma_q f(x)+f(x)=x$\\
$\tilde{\Phi}(z)=\sum_{n\geq 0}(-1)^{n+1} n!z^{-n-1}$ & $\hat{f}(x)=\sum_{n\geq 0}(-1)^{n}q^{n(n+1)/2}x^{n+1}$ \\
& \\
\hline
General notation & \\
\hline
$z\frac{d}{dz}$ & $\sigma_qf(x)=f(qx)$ \\
$\frac{d}{dz}$ & $\delta_q f(x)=\frac{f(qx)-f(x)}{(q-1)x}$ \\
$n!$ & $q^{n(n+1)/2}$ \\
$e^z$ & $e_q(x)=\log(1/q)\Theta_q(x)$
\end{tabular}

\end{center}

\begin{remark} Why $n!$ corresponds to $q^{-n(n+1)/2}$
\begin{equation}
\Gamma(n)=\int_0^{+\infty}e^{-t}t^n\frac{dt}{t}
\end{equation}

\begin{equation}
q^{-n(n-1)/2}=\int_0^{+\infty}\frac{t^n}{e_q(t)}\frac{dt}{t}
\end{equation}
\end{remark}

There is also another interesting relation between $q$- factorial and $n!$

\begin{equation}
[n]_q!= \frac{(q;q)_n}{(1-q)^n} \rightarrow_{q\to 1} n!
\end{equation}

\[
\begin{tikzcd}
\hat{f}(x)=\sum_{n\geq 0}a_n x^n\in\mathbb{C}[\![x]\!]_{(q;1)} \arrow[rr,"\mathcal{B}_{(q;1)}"] & & \varphi(\xi)=\sum_{n\geq 0}a_n q^{-n(n-1)/2}\xi^n\arrow[dl,"\mathsf{L}^{[\lambda]}_{q;1}"]\\
&f(x)\arrow[lu,dashed ,"\text{asymptotics}"] &
\end{tikzcd}
\]

\subsection{Borel regularity: Dreyfus's theorem}

Let $\mathcal{B}_{\mu}$ be the $q$- Borel transform for $q$-Gevrey $\mu$ series
\begin{equation}
    \mathcal{B}_{\mu}\colon\sum_{n\geq 0}a_nx^n\to \sum_{n\geq 0}a_n q^{-n(n-1)/(2\mu)}\xi^n
\end{equation}
and let $\mathsf{L}_{\mu,\kappa}^{[\lambda]}$ be the $q$- Laplace transform with parameters $\mu\in\Q_{>0}$, $\kappa\in\N^*$ ($\mathsf{L}_{q;1}^{[\lambda]}:=\mathsf{L}_{1,1}^{[\lambda]}$)
\begin{equation}
    \mathsf{L}_{\mu,\kappa}^{[\lambda]}\varphi(x)=\frac{\mu}{\kappa}\sum_{l\in \kappa^{-1}\mathbb{Z}}\frac{\varphi(q^l\lambda)}{\Theta_{q^{1/\mu}}(\frac{q^{1/\mu+l}\lambda}{x})}\quad \lambda\in\C^*/q^{\kappa^{-1}\Z}
\end{equation}
Let $\mathbb{H}_{\mu,\kappa}^{[\lambda]}$ be the space of functions $\varphi\in\mathcal{M}(\C^*)$, such that there exists $\varepsilon>0$, $\Omega\subset \C$ connected 
\begin{itemize}
\item $\bigcup_{l\in\kappa^{-1}\Z}\lbrace x\in\C^* | |x-\lambda q^{l}|<\varepsilon |\lambda q^l|\rbrace\subset\Omega$
\item $\varphi$ can be continued analytically in $\Omega$ with $q^{1/\mu}$ exponential growth
\[|\varphi(\xi)|<C|\Theta_{|q|^{1/\mu}}(A|\xi|)|\] 
\end{itemize}

For every $\varphi(\xi)\in\mathbb{H}_{\mu,\kappa}^{[\lambda]}$, $\mathsf{L}_{\mu,\kappa}^[\lambda]\varphi(x)\in$.

Under suitable assumptions on the $q$-difference equation, the following result holds true 
\begin{theorem}
Let $\hat{h}$ be a formal power series solution of a linear q-difference equation with coefficients in $\mathbb{C}(x)$. There exist $\kappa_1,...,\kappa_r\in\mathbb{Q}_{>0}$, $n,K\in\mathbb{N}^*$ and a finite set $\Sigma\subset\mathbb{C}^*/ q^{n^{-1}\mathbb{Z}}$, we may compute from the q-difference equation, such that for all $\lambda\in (\mathbb{C}^*/q^{n^{-1}\mathbb{Z}})\setminus\mathbb{Z} $,
\[
\mathsf{S}^{[\lambda]}(\hat{h}):=\mathsf{L}^{[\lambda]}_{\kappa_r,n}\circ\mathsf{L}^{[\lambda]}_{\kappa_{r-1},K}\circ...\circ\mathsf{L}^{[\lambda]}_{\kappa_1,K}\circ\mathcal{B}_{\kappa_1}\circ...\circ\mathcal{B}_{\kappa_r}\hat{h}\]
is meromorphic on $\mathbb{C}^*$, and is solution of the same equation as $\hat{h}$. Moreover, $\mathsf{S}^{[\lambda]}(\hat{h})$ is asymptotic to $\hat{h}$ and, for $|x|$ close to $0$ it has poles of order at most $1$ that are contained in $\lambda q^{n-1}, n\in\mathbb{Z}$. 
\end{theorem}

Idea of the proof: let $P(\hat{f})=\big[\sum_{n=0}^ma_n\sigma_q^n\big]\hat{f}$

\[
\begin{tikzcd}
& P\hat{f}=a\arrow[dd] & \\
f(x)\arrow[ru,red] & &\hat{f}(x)\arrow[lu]\arrow[dd, "\mathcal{B}_{\kappa_1}\circ...\circ\mathcal{B}_{\kappa_r}"] \\
& q-\text{difference equation} & \\
\varphi(\xi)\in\mathbb{H}^{[\lambda]}_{\kappa_1,K}, \text{ for some }\lambda \arrow[uu,  "\mathsf{L}^{[\lambda]}_{\kappa_r,n}\circ...\circ\mathsf{L}^{[\lambda]}_{\kappa_1,K}"]& & \varphi(\xi)\in\C\lbrace\xi\rbrace, \text{ of slope } 0 \arrow[ll,Leftrightarrow]\arrow[ul] 
\end{tikzcd}
\]

\subsection{Summary}

\begin{center}
\begin{tabular}{c|c}
\hline
\textbf{Formal series} & \\
\hline
$\tilde{\Phi}(z)=\sum_{n\geq 0} a_n z^{-n-1}\in\mathbb{C}[\![z^{-1}]\!]_1$     &  $\hat{f}(x)=\sum_{n\geq 0}a_n x^n\in\mathbb{C}[\![x]\!]_{(q;1)}$ \\
& \\
\hline
\textbf{Borel transform} & \\
\hline
  $\tilde{\phi}(\zeta)=\sum_{n\geq0}a_n\frac{\zeta^n}{n!}\in\mathbb{C}\lbrace \zeta\rbrace$   & $\varphi(\xi)=\sum_{n\geq 0}a_n q^{n(n-1)/2}\xi^n \in\mathbb{C}(\!(\xi)\!)$\\
  & \\
  \hline
  \textbf{Laplace transform} & \\
  \hline
 $\mathcal{L}_\zeta^{\theta}\hat{\phi}(z)=\int_0^{+e^{i\theta}\infty} e^{-z\zeta}\hat{\phi}(\zeta)d\zeta\in\mathcal{O}(H_\theta)$ & $\mathcal{L}^{\theta}_{q;1}\varphi(x)=\int_0^{e^{i\theta} \infty}\frac{\varphi(\xi)}{e_q(\frac{\xi}{x})}d\xi $ \\
 & $\Theta$ function: $\Theta_q(x)=\sum_{n\in\mathbb{Z}}q^{-n(n+1)/2}x^n$\\
 & $\mathsf{L}_{q;1}^{[\lambda]}\varphi(x)=\sum_{n\geq 0}\frac{\varphi(\lambda q^n)}{\Theta_q(\frac{\lambda q^n}{x})}\in\mathcal{O}(H^{\lambda}),\, \lambda\in\mathbb{C}^*$\\
 & $H^{\lambda}=D_r^*\setminus\lbrace -\lambda q^n, n\in\mathbb{Z}\rbrace$ \\
 & \\
 \hline
 \textbf{Domain of definition} & \\
 \hline 
 $\hat{\phi}(\zeta)$ s.t. $\exists C,a>0 $ & $\varphi(\xi)$ s.t. $\exists C,a>0 $\\
 $|\hat{\phi}(\zeta)|<Ce^{a|\zeta|}$, $\zeta\in S_{\delta}$ & $|\varphi(\xi)|<C|\xi|^aq^{\frac{1}{2}\left(\frac{\log|\xi|}{\log q}\right)^2}$, $\xi\in S_{\delta}\cap\C^*$ \\
 $S_\delta$ is an half-strip& \\
 & $\varphi(\xi)\in\mathbb{H}_{\mu,\kappa}^{[\lambda]}$\\
 & \\
 \hline
 \textbf{Gevrey asymptotics} & \\
 \hline
$\mathcal{L}_{\zeta}^{\theta}\hat{\phi}(z)\sim_1 \tilde{\Phi}(z)$ & $\mathsf{L}_{q;1}^{[\lambda]}\varphi(x)\sim_{q;1} \hat{f}(x)$ \\
& \\
\hline
\textbf{Stokes phenomena} & \\
\hline 
 varying $\theta$, $\mathcal{L}^{\theta}$ jumps & varying $\mu\not\equiv_{q}\lambda$, $\mathsf{L}_{q;1}^{[\mu]}$ jumps\\
 & \\
 \hline
 \textbf{Borel regularity} & \\
 \hline
 M.A.E.T: existence of hol. solutions & [Praagman, 86]: existence of merom. solutions \\
 F.,Feynes : BL sum gives an actual solution & [Dreyfus, 14]: q--BL gives an actual solution \\
 \textit{slight functions} & \textit{slope} $0$ operators \\
\end{tabular}
\end{center}

\bibliographystyle{plain}
\bibliography{airy-resurgence}
\end{document}

### 2022-11-30 exp-resurgence.tex
Turn more of the "Setting" outline into prose

@@
 \usepackage{amssymb}
+\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
 \usepackage{bm} %% for putting series names in bold
@@
 \usepackage[svgnames]{xcolor}
+
+%% editing
+\newcommand{\done}[1]{\textcolor{gray}{#1}}
 
@@
 behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
 \begin{equation}
@@
 \end{equation}
-and its constant multiples.
-
-you might start by trying to construct a formal power series solution instead.
-Observing that the leading term must be a multiple of $z^{-1/2}$ and then extending term by term, you again \textcolor{magenta}{[check]} get series~\eqref{series:bessel-ex}.
-
-%%%
-
-For example, you might rewrite the integral
+and its constant multiples. As another example, you might rewrite the integral
 \color{DodgerBlue}
@@
 \[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
-using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you get the series
+using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
 \color{DodgerBlue}
-\[ e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \]
-\[ e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \]
+\begin{align*}
+& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
+& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
+& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
+\end{align*}
 \color{black}
-\begin{equation}
-e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] %%\label{series:bessel-ex}
-\end{equation}
-which has zero radius of convergence, but still makes sense as a formal power series.
+
+Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+Borel summation works in three steps.
+\begin{enumerate}
+\item Thinking of $z$ as a ``frequency variable,'' we take the formal inverse Laplace transform of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
+\item With luck, $\series{\phi}$ has a positive radius of convergence.
+In this case, we say $\series{\Phi}$ is {\em $1$-Gevrey}.
+We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
+Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item With more luck, $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} for its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\end{enumerate}
+The Borel summation process is summarized in the following diagram.
+\begin{center}
+\begin{tikzcd}
+& \text{problem} & \\
+\Phi \arrow[ru, dotted, no head, tail] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+& & \\
+\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi}(\zeta) \arrow[ll, mapsto, "\text{sum}"] 
+\end{tikzcd}
+\end{center}
+
 \begin{itemize}
-\item You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots
+\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
 \begin{itemize}
-\item Exponential integral: na\"{i}ve saddle point expansion.
-\item ODE: formal solution. Existence theorem in \cite{diverg-resurg-iii}?
+\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
+\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
 \item Feynman diagram series?
@@
 \begin{itemize}
-\item Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.
-\item The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item \done{Borel summation work in three steps.
+First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
+\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
+\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
 \item {[Draw the square!]}

### 2022-12-02 kawai+takei vs mariño.tex
Weber example

@@
 \newtheorem{prop}{Proposition}
+\newtheorem{lemma}{Lemma}
 \newtheorem{thm}{Theorem}
@@
 \usepackage{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{cd}
 %\DeclareMathOperator{\Ai}{Ai}
@@
 \title{Airy function: Kawai+Takei vs. Mari\~{n}o}
-\author{Aaron Fenyes}
+\author{Aaron Fenyes, Veronica Fantini}
 
@@
 %psi(eta^(-2/3) y, eta) = Ai(y)
+
+\section{Weber equation: WKB vs modifield Bessel ODE}
+
+In [Takei] the author studied the Borel summation of WKB solutions of the harmonic oscillator
+
+\begin{equation}\label{eq:weber}
+\left[\frac{d^2}{dx^2}-\eta^2x^2-\lambda\eta\right]\psi=0
+\end{equation}
+
+with a parameter $\lambda$. He proved that the WKB solutions
+\begin{equation}
+\psi_{\pm}(x,\eta)=e^{\pm\eta x^2/2}\sum_{n=0}^{\infty}\frac{\psi_{\pm,n}}{x^{2n+(1\pm\lambda)/2}}\eta^{-\left(\frac{1}{2}\pm\frac{\lambda}{4}+n\right)}
+\end{equation}
+ where $\psi_{\pm,n}$ are constants independent of $x$ and $\eta$ have Borel transform (in the variable $y$ conjugate to $\eta$) 
+ \begin{align}
+ \psi_{+,B}(x,y)&=\frac{x^{-3/2}}{\Gamma\left(\frac{1}{2}+\frac{\lambda}{4}\right)}s^{-1/2+\lambda/4} F\left(\frac{1}{4}+\frac{\lambda}{4},\frac{3}{4}+\frac{\lambda}{4};\frac{1}{2}+\frac{\lambda}{4};s\right)\\
+ \psi_{-,B}(x,y)&=\frac{x^{-3/2}}{\Gamma\left(\frac{1}{2}+\frac{\lambda}{4}\right)}(s-1)^{-1/2+\lambda/4} F\left(\frac{1}{4}+\frac{\lambda}{4},\frac{3}{4}+\frac{\lambda}{4};\frac{1}{2}+\frac{\lambda}{4};1-s\right)
+ \end{align}
+where $s=y/x^2+1/2$.
+
+\begin{lemma}
+Set $\lambda=0$.
+Let $\eta=2zx^{-2}$ then $\psi_-(x,\eta)=\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)$ is a solution of \eqref{eq:weber} if and only if $K_{1/4}(z)$ is a solution of the modified Bessel equation
+
+\begin{equation}
+\left[\frac{d^2}{dz^2}-1+\frac{1}{z}\frac{d}{dz}-\frac{1}{16 z^2}\right]\tilde{K}_{1/4}(z)=0
+\end{equation}
+
+\end{lemma}
+
+\begin{proof}
+We start with the Weber equation \eqref{eq:weber}
+
+\begin{align*}
+&\left[\frac{d^2}{dx^2}-\eta^2x^2\right]\psi_-=0\\
+&\left[\frac{d^2}{dx^2}-\eta^2x^2\right]x^{1/2}\tilde{K}_{1/4}(z)=0\\
+&\frac{d}{dx}\left(\frac{1}{2}x^{-1/2}\tilde{K}_{1/4}(z)+x^{1/2}\frac{d}{dx}\tilde{K}_{1/4}(z)\right)-\eta^2x^{5/2}\tilde{K}_{1/4}(z)=0\\
+&-\frac{1}{4}x^{-3/2}\tilde{K}_{1/4}(z)+x^{-1/2}\frac{d}{dx}\tilde{K}_{1/4}(z)+x^{1/2}\frac{d^2}{dx^2}\tilde{K}_{1/4}(z)-\eta^2x^{5/2}\tilde{K}_{1/4}(z)=0\\
+&-\frac{1}{4}x^{-2}\tilde{K}_{1/4}(z)+x^{-1}\frac{d}{dx}\tilde{K}_{1/4}(z)+\frac{d^2}{dx^2}\tilde{K}_{1/4}(z)-\eta^2x^{2}\tilde{K}_{1/4}(z)=0
+\end{align*}
+
+Under the change of coordinates $\eta=2zx^{-2}$ we have
+\begin{align*}
+\frac{d}{dx}=\eta x\frac{d}{dz} & \qquad \qquad \frac{d^2}{dx^2}=\eta\frac{d}{dz}+\eta^2 x^2\frac{d^2}{dz^2}
+\end{align*}
+therefore
+
+\begin{align*}
+&-\frac{1}{4}x^{-2}\tilde{K}_{1/4}(z)+x^{-1}\frac{d}{dx}\tilde{K}_{1/4}(z)+\frac{d^2}{dx^2}\tilde{K}_{1/4}(z)-\eta^2x^{2}\tilde{K}_{1/4}(z)=0\\
+&-\frac{1}{4}x^{-2}\tilde{K}_{1/4}(z)+\eta\frac{d}{dz}K_{1/4}(z)+\left(\eta\frac{d}{dz}+\eta^2 x^2\frac{d^2}{dz^2}\right)\tilde{K}_{1/4}(z)-\eta^2x^{2}\tilde{K}_{1/4}(z)=0\\
+&-\frac{1}{4}\frac{\eta}{2z}\tilde{K}_{1/4}(z)+\eta\frac{d}{dz}\tilde{K}_{1/4}(z)+\eta\frac{d}{dz}\tilde{K}_{1/4}(z)+2z\eta \frac{d^2}{dz^2}\tilde{K}_{1/4}(z)-2z\eta \tilde{K}_{1/4}(z)=0\\
+&-\frac{1}{4}\frac{1}{4z^2}K_{1/4}(z)+\frac{1}{z}\frac{d}{dz}\tilde{K}_{1/4}(z)+ \frac{d^2}{dz^2}K_{1/4}(z)- \tilde{K}_{1/4}(z)=0\\
+&\qquad\qquad\qquad\qquad\qquad \left[\frac{d^2}{dz^2}-1+\frac{1}{z}\frac{d}{dz}-\frac{1}{16 z^2}\right]\tilde{K}_{1/4}(z)=0
+\end{align*}
+
+\end{proof}
+
+\begin{lemma}
+Set $\lambda=0$. Let $\eta=2zx^{-2}$ then \[\psi_{-,B}(x,y)=x^{-3/2}\hat{\kappa}_{1/4}(\zeta)\] where $\hat{\kappa}_{1/4}(\zeta)=\mathcal{B}(\tilde{K}_{1/4})(\zeta)$. 
+\end{lemma}
+
+\begin{proof}
+We move to the Borel plane: let $\zeta$ be the variable conjugate to $z$ and let $y$ the conjugate to $\eta$, i.e.
+\begin{align*}
+\mathcal{B}\colon & \sum_{n\geq 0}a_nz^{-n-1}\to \sum_{n\geq 0}a_n\frac{\zeta^n}{n!}\\
+\mathcal{B}\colon&\sum_{n\geq 0}a_n\eta^{-n-1}\to \sum_{n\geq 0}a_n\frac{y^n}{n!}
+\end{align*}
+
+if $\eta=2zx^{-2}$ then $y=\frac{\zeta}{2}x^2$, indeed
+
+\begin{tikzcd}
+\sum_{n\geq 0}a_n\eta^{-n-1} \arrow[d,equal]\arrow[rr,"\mathcal{B}"] & & \sum_{n\geq 0}a_n\frac{y^n}{n!}\\
+\sum_{n\geq 0}a_n\left(\frac{2}{x^2}\right)^{-n-1}z^{-n-1}\arrow[r,equal]&\frac{x^2}{2}\sum_{n\geq 0}a_n\left(\frac{2}{x^2}\right)^{-n}z^{-n-1}\arrow[r,"\mathcal{B}"] &\frac{x^2}{2}\sum_{n\geq 0}a_n\left(\frac{x^2}{2}\right)^{n}\frac{\zeta^n}{n!}
+\end{tikzcd}
+
+In particular, $\tilde{K}_{1/4}(z)$ is known as the asymptotics of the modified Bessel function $K_{1/4}(z)$ which is equal to
+
+\begin{align*}
+\tilde{K}_{1/4}(z)&=\sqrt{\pi}e^{-z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(\frac{z}{2}\right)^{-n-1/2}
+\end{align*}
+
+Then we can compute its Borel transform:
+
+\begin{align*}
+\hat{\kappa}_{1/4}&=\sqrt{\pi}\sum_{n\geq 0}\frac{(-1)^n\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{\Gamma(n+1/2) n!}\left(\frac{\zeta-1}{2}\right)^{n-1/2}\\
+&=\sqrt{\pi}\left(\frac{\zeta-1}{2}\right)^{-1/2}\sum_{n\geq 0}\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{\Gamma(n+1/2) n!}\left(\frac{1-\zeta}{2}\right)^{n}\\
+&=\sqrt{2}(\zeta-1)^{-1/2}F\left(\frac{1}{4},\frac{3}{4};\frac{1}{2};\frac{1-\zeta}{2}\right)
+\end{align*}
+
+hence
+
+\begin{tikzcd}
+\psi_-(x,\eta) \arrow[d,equal]\arrow[r,"\mathcal{B}"]   & \psi_{-,B}(x,y)=\frac{x^{-3/2}}{\sqrt{\pi}}(s-1)^{-1/2+\lambda/4} F\left(\frac{1}{4},\frac{3}{4};\frac{1}{2}+;1-s\right)\arrow[d,equal,red,"\cdot \frac{x^2}{2}"]\\
+\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)\arrow[r,"\mathcal{B}"] &\frac{1}{2\sqrt{\pi}}x^{1/2}\sqrt{2}(\zeta-1)^{-1/2}F\left(\frac{1}{4},\frac{3}{4};\frac{1}{2};\frac{1-\zeta}{2}\right)
+\end{tikzcd}
+
+\end{proof}
+
 \end{document}

### 2022-12-02 kawai+takei vs mariño.tex
minor changes

@@
 Set $\lambda=0$.
-Let $\eta=2zx^{-2}$ then $\psi_-(x,\eta)=\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)$ is a solution of \eqref{eq:weber} if and only if $K_{1/4}(z)$ is a solution of the modified Bessel equation
+Let $\eta=2zx^{-2}$ then $\psi_-(x,\eta)=\frac{1}{2\sqrt{\pi}}x^{1/2}\tilde{K}_{1/4}(z)$ is a solution of \eqref{eq:weber} if and only if $\tilde{K}_{1/4}(z)$ is a formal solution of the modified Bessel equation
 
-\begin{equation}
+\begin{equation}\label{eq:Bessel 1/4}
 \left[\frac{d^2}{dz^2}-1+\frac{1}{z}\frac{d}{dz}-\frac{1}{16 z^2}\right]\tilde{K}_{1/4}(z)=0
@@
 \begin{lemma}
-Set $\lambda=0$. Let $\eta=2zx^{-2}$ then \[\psi_{-,B}(x,y)=x^{-3/2}\hat{\kappa}_{1/4}(\zeta)\] where $\hat{\kappa}_{1/4}(\zeta)=\mathcal{B}(\tilde{K}_{1/4})(\zeta)$. 
+Set $\lambda=0$. Let $\eta=2zx^{-2}$ then \[\psi_{-,B}(x,y)=x^{-3/2}\hat{\kappa}_{1/4}(\zeta)\] where $y=\frac{\zeta}{2}x^2$ and $\hat{\kappa}_{1/4}(\zeta)=\mathcal{B}(\tilde{K}_{1/4})(\zeta)$. 
 \end{lemma}
@@
 \begin{align*}
-\tilde{K}_{1/4}(z)&=\sqrt{\pi}e^{-z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(\frac{z}{2}\right)^{-n-1/2}
+\tilde{K}_{1/4}(z)&=\sqrt{\pi}e^{-z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(2z\right)^{-n-1/2}
 \end{align*}
@@
 
+Furthermore, the modified Bessel equation \eqref{eq:Bessel 1/4} has another holomorphic solution $I_{1/4}(z)$ (which together with ${K}_{1/4}$ forms a basis) whose asymptotic behaviour is
+
+\begin{equation}
+\tilde{I}_{1/4}(z)=\frac{1}{\sqrt{\pi}}e^{z}\sum_{n= 0}^{\infty}(-1)^n\frac{\left(\frac{1}{4}\right)_n\left(\frac{3}{4}\right)_n}{n!}\left(2z\right)^{-n-1/2}
+\end{equation}
+
 \end{document}

### 2023-01-02 kawai+takei vs mariño.tex
Update kawai+takei vs mariño.tex

@@
 \end{equation}
+\section{Physical picture}
+Here are some vague physical ideas about why the change of coordinates described above works. They're pretty incoherent, and they should all be taken with a grain of salt.
 
+Consider an equation of the form
+\begin{equation}\label{eq:deformed-airy-lucas}
+\left[\left(\frac{\partial}{\partial x}\right)^2-\eta^2x^{n-2}(1 + f) - \lambda\eta\right] \psi = 0,
+\end{equation}
+where $n \in \{3, 4, 5, 6, \ldots\}$ and the function $f$ goes to zero as $x \to \infty$.
+It's reasonable to look for trans-series solutions with the exponential factor $e^{\pm z}$, where $z = \tfrac{2}{n} \eta x^{n/2}$,
+%% \[ e^{\pm z} z^{1-4/n} \big(\text{series in}\;1/z\big) \]
+because \textcolor{magenta}{(I don't think the following calculation works)}
+\begin{align*}
+\left[\left(\frac{\partial}{\partial x}\right)^2-\eta^2x^{n+2}\right] e^{\pm z} & = -\big(\tfrac{n}{2} - 1\big) \eta x^{n/2 - 2} e^{\pm z} \\
+& = -\big(\tfrac{n}{2} - 1\big) \eta \big(\tfrac{n}{2} \eta^{-1} z\big)^{1 - 4/n} e^{\pm z} \\
+& = -\big(\tfrac{n}{2} - 1\big) \big(\tfrac{n}{2}\big)^{1- 4/n} \eta^{4/n} z^{1 - 4/n} e^{\pm z} \\
+& = \ldots
+\end{align*}
+The corresponding holomorphic solutions should have the same exponential decay.
+The $e^z$ and $e^{-z}$ solutions are usually linearly independent, but they can become linearly dependent when $\lambda\eta$ is in the spectrum of the rest of the operator acting on $L^2(\mathbb{R})$.
+In this case, we should get a solution in $O_{z \to -\infty}(e^z) \cap O_{z \to \infty}(e^{-z})$, which decays exponentially in both directions.
+You can see this explicitly for the $n = 2$ case: each eigenvector of the harmonic oscillator Hamiltonian is $e^{-\eta x^2/2}$ times a polynomial in $x$.
+The exponential decay of the eigenvectors sets a natural length scale, and $z$ measures distance with respect to it.
+
+When $f = 0$ and $\lambda = 0$, rescalings of $x$ and $\eta$ that keep $z$ fixed have no effect on the equation.
+Thus, any rescaling of $x$ has the same effect on the equation as a corresponding rescaling of $\eta$.
+This scale-invariance is why taking the Borel transforms with respect to $\tfrac{2}{n} x^{n/2}$ and $\eta$ give the same result.
+
+The $|x| \to \infty$ limit, $f$ is very small by assumption, so we're approximately in the scale-invariant situation described above.
+In the $\eta \to \infty$ limit, the eigenvectors of the Hamiltonian get very narrow, so it's similar to making $|x|$ large whie keeping $\eta$ fixed.
+This should mean once again that we can neglect $f$.
+The upshot is that both the $|x| \to \infty$ limit and the $\eta \to \infty$ limit take us toward the scale-invariant situation where the two Borel transforms give the same result.
 \end{document}

### 2023-01-03 exp-resurgence.tex
Put Borel regularity up front
Feature Borel regularity more prominently in the intro. We started
working on these changes during our Jan 2 meeting.

@@
 \section{Introduction}
-\subsection{Setting \textcolor{orange}{[change title?]}}
+\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
+%%\subsection{A familiar process: Borel summation}\label{intro:summation}
 You can often find a formal power series \textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
+Ask more about this.]}
 \item With more luck, $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} for its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
@@
 & \text{problem} & \\
-\Phi \arrow[ru, dotted, no head, tail] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
@@
 \end{itemize}
+\subsection{A new perspective: Borel regularity}
+\begin{itemize}
+\item The central goal of this paper is to present a new perspective on Borel summation which helps explain why it works for at least two kinds of problems.
+\begin{itemize}
+\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+\item The second problem is solving a certain kind of ODE.
+\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+\end{itemize}
+\item Suppose you have a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $z$ goes to $\infty$ along a given ray.
+\item If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum is a new holomorphic function.
+%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
+%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
+We'll call it {\em Borel regularization}.
+%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
+We'll call this process {\em Borel regularization}.
+\item Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
+We'll therefore call this process {\em Borel regularization}.
+\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
+\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+\item We have the following vector space inclusions:
+\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
+\item Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
+\begin{itemize}
+\item $\Phi$ is Borel regular.
+\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
+\item $\phi$ grows at most exponentially along the Laplace transform ray.
+\end{itemize}
+\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
+\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
+Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.
+\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
+\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
+\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
+\item \ldots
+\end{itemize}
 \subsection{Goals}
@@
 We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.\textcolor{black}{[Veronica---I dont't see why]}
+This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\textcolor{orange}{[Veronica---I dont't see why]}
+\end{itemize}
+\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
+\begin{itemize}
+\item Integral equations are more regular than differential equations.
+\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
 \end{itemize}
@@
 \begin{itemize}
-\item Contextualize with previous work of P. Ramis
+\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
+\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
 \item Also contextualize with Loday-Richaud
@@
 \[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
 \item \textbf{Satisfying a singular differential equation}

### 2023-01-03 exp-resurgence.tex
add comments about Nevanlinna

@@
 \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.
+Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\mathcal{L}\circ\mathcal{B}\tilde{\Phi}$ (i.e.
+it is Borel regular)?
+P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
+In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
+When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
 \item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
@@
 \subsection{Goals}
+
+\color{gray}
 \begin{itemize}
@@
 \end{itemize}
+\color{black}
 \item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
@@
 \end{itemize}
-\item \textcolor{magenta}{To understand, for example, the Ecalle formalism, you can start with these toy examples, which illustrate what's going on, but can also be studied in a more elementary way.
-[How do we work this into the introduction?]} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
 Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).

### 2023-01-20 exp-resurgence.tex
updates

@@
 \[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-\item Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
+\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+
+Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
 \begin{itemize}
@@
 \subsection{Why does Borel resummation work?}
+
+\color{gray}
+
 Borel resummation is a way of turning a formal power series
@@
 over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
+\color{DarkBlue}
+
 \item \textbf{Satisfying a singular differential equation}
@@
 \item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+
+\begin{center}
+\begin{tikzcd}
+& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
+\Phi\arrow[rru,dashed] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red] & & & \tilde{\Phi}\arrow[llu,"formal",swap]\arrow[dd,"\mathcal{B}"]\\
+& & IE & & \\
+\phi\arrow[rru]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu]
+\end{tikzcd}
+\end{center}
+
+where the arrow in red are a consequence of multisummability.
+In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
+On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
 \end{itemize}
+
 \item \textbf{Being a thimble integral}

### 2023-01-21 exp-resurgence.tex
updates

@@
 \begin{itemize}
-\item Think about conditions where this works.
+\item Think about conditions where this works. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
+\begin{equation}\label{eq:ODE}
+\big[ P(\partial_z)+\frac{1}{z}Q(\partial_z)+R(z^{-1})\big]\Psi=0
+\end{equation}
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R(z^{-1})=O(z^{-2})$.
+Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
+Under these assumptions, \eqref{eq:ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
+\begin{equation}
+\label{formal solution}
+\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z }\C[\![z^{-\tau_j}]\!]
+\end{equation}
 \item Maybe the correct place is the setting of Ecalle's formal integral. See \S 5.2.2.1 of Delabaere's {\em Divergent Series, Summability and Resurgence III}.
-\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially. Then this is the only solution that can be expressed as a Laplace transform.
+\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+Then this is the only solution that can be expressed as a Laplace transform.
+[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
 \item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resurgence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.

### 2023-01-21 exp-resurgence.tex
update with Aaron

@@
 \end{itemize}
-\subsection{Goals}
+
+\subsection{Goals and Results}
 
@@
 \begin{itemize}
-\item Think about conditions where this works. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
+\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
 \begin{equation}\label{eq:ODE}
@@
 \end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R(z^{-1})=O(z^{-2})$.
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R(z^{-1})=O(z^{-2})$ [Looking at the existence theorem in {\tt airy.resurgence 2.1.3} we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well].
 Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-Under these assumptions, \eqref{eq:ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
+\item (backgrounds) Under these assumptions, 
+\begin{itemize}
+\item \eqref{eq:ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form  
 \begin{equation}
@@
 \end{equation}
+Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
+\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eq:ODE}
+\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
+\end{itemize}
+\item Can we see there exists a distinguished basis in a purely analytic way?
+YES.
+The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
 \item Maybe the correct place is the setting of Ecalle's formal integral. See \S 5.2.2.1 of Delabaere's {\em Divergent Series, Summability and Resurgence III}.
@@
 On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
+\item here is the way 
+there are many ways to see this porblem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, Ecalle figured it out how to see it formally in the Borel plane, our results shows how to see it analytically in  the Borel plane.
+\item  M.A.E.T.
+says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
+Our method uses just Laplace transform.
+\item How do we know we are picking the same frame?
+from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
+From uniqueness result we get a frame equivalent to Ecalle's frame.
+\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+Borel regularity is instead based on the analytic solution in the $z$-plane.
+The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
 \end{itemize}

### 2023-01-22 exp-resurgence.tex
section 2
add a new section with the preliminary results on Borel and Laplace transform, using what we had in draft2.pdf and airy-resurgence.pdf

@@
 \usepackage{amssymb}
+\usepackage{amsthm}
 \usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
@@
 %%\usepackage{amsthm}
-%%\usepackage{graphicx}
-
+\usepackage{graphicx}
+\usepackage{fancyhdr}
+\usepackage{xparse} 
+%\usepackage{eqnarray}
 %% colors
 \usepackage[svgnames]{xcolor}
+\let\Re\relax
+\DeclareMathOperator{\Re}{Re}
 
@@
 \newcommand{\maps}{\colon}
+\newcommand{\acts}{\mathbin{\raisebox{\depth}{\rotatebox{-90}{$\circlearrowright$}}}}
 
@@
 ]}
+
+\newcommand{\series}[1]{\tilde{#1}}
+\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
+\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
+\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
+\newcommand{\laplacepde}{\mathcal{D}}
+\newcommand{\van}{\mathfrak{m}}
+\DeclareMathOperator{\Ai}{Ai}
 \usetikzlibrary{matrix,shapes,arrows,decorations.pathmorphing}
@@
 %%\DeclareMathOperator{\Re}{Re}
-\DeclareMathOperator{\Ai}{Ai}
+
 \newcommand{\laplace}{\mathcal{L}}
@@
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
-\newcommand{\series}{\tilde}
+
+\newtheorem{definition}{Definition}[section]
+\newtheorem{problem}[definition]{Problem}
+\newtheorem{example}[definition]{Example}
+\newtheorem{fact}[definition]{Fact}
+\newtheorem{aside}[definition]{Aside}
+\newtheorem{prop}[definition]{Proposition}
+\newtheorem{question}[definition]{Question}
+\newtheorem{remark}[definition]{Remark}
+\newtheorem{theorem}[definition]{Theorem}
+\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{lemma}[definition]{Lemma}
+%\newtheorem{conjecture}[definition]{Conjecture}
+\newtheorem{claim}[definition]{Claim}
+%\newtheorem{exercise}[definition]{Exercise}
+\newtheorem*{notation*}{Notation}
 
@@
 \section{The Laplace and Borel transforms}
+\subsection{The geometry of the Laplace transform}
+
+Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
+In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
+Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
+\subsubsection{Translation surfaces, briefly}
+
+A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
+A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
+The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
+We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
+This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
+\subsubsection{Direction}\label{transl:dir}
+The translation structure gives $B$ a notion of direction as well as distance.
+Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
+At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
+To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
+\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
+In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
+
+Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
+This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
+Of course, there are $n$ different choices for $\omega_b$.
+\subsubsection{Frequency}\label{transl-freq}
+The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+At an ordinary point, we can define $z$ simply as the map
+\begin{align*}
+z \maps T^*B_b & \to \C \\
+\lambda\big|_b & \mapsto 1.
+\end{align*}
+To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
+Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
+Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
+When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
+In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
+We define $z$ as the isomorphism
+\begin{align*}
+z \maps \van_b^n / \van_b^{n+1} & \to \C \\
+\zeta_b + \van^{n+1} & \mapsto 1.
+\end{align*}
+
+When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
+\begin{align*}
+w_b \maps T^*B_b & \to \C \\
+\omega_b + \van^2 & \mapsto 1
+\end{align*}
+that makes the diagram
+\begin{center}
+\begin{tikzcd}
+T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
+T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
+\end{tikzcd}
+\end{center}
+commute.
+\subsubsection{Boundary}
+\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}
+
+\subsubsection{The Laplace transform over an ordinary point}%%\label{laplace:ordinary}
+Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
+\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
+When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
+\begin{equation}\label{laplace:int}
+\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
+\end{equation}
+where $z$ is the frequency function defined in Section~\ref{transl:freq} and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
+
+To make sense of this formula, we ask for the following conditions.
+\begin{itemize}
+\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
+\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
+\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
+\begin{itemize}
+\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
+\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
+\end{itemize}
+\end{itemize}
+\subsubsection{The Laplace transform over a branch point}
+When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
+Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
+The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
+This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
+The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
+We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+
+\subsection{The Laplace transform: analytic version}
+\subsubsection{Regularity and decay properties}\label{reg-decay}
+%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
+The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
+%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
+where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
+\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
+
+Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
+A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
+Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
+If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
+
+The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
+Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
+Let $F = \laplace_{\zeta, 0} f$.
+Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality.
+For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
+\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
+More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
+\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
+Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
+\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
+\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
+\subsubsection{Action on integral operators}\label{L-int-op}
+When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\begin{equation}%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\end{equation}
+for all integers $n \ge 0$.
+You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+for all $\lambda \in (0, \infty)$.
+\subsubsection{Change of translation chart}\label{translation}
+Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
+\begin{align*}
+\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
+\end{align*}
+we learn that
+\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
+\subsubsection{Rescaling of translation structure}
+Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
+The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
+From the calculation
+\begin{align*}
+\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \varphi
+\end{align*}
+we learn that
+\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
+
+\color{gray}
 \subsection{The Laplace transform}
@@
 \end{itemize}
+\color{black}
+
 \subsection{The Borel transform}
+\color{gray}
 \begin{itemize}
@@
 \end{itemize}
+\color{black}
+
+The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$ such that  \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
+\mathcal{B}(1)&\defeq\delta 
+\end{align*}
+
+where $\delta$ is the element $(1,0)\in\C\times\C[\![\zeta]\!]$\footnote{Sometimes, in physics it is common to adopt a differnt convention, i.e.
+$\mathcal{B}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$ (see\cite{MDiablerets}\cite{SGM}, for example).
+However, we find natural for our purposes the mathematical convention, as the Laplace transform is the inverse of $\mathcal{B}$ under suitable growth conditions.
+}, and by linearity
+
+\begin{align*}
+\mathcal{B}\colon \C[\![z^{-1}]\!] & \to \C\delta\oplus\C[\![\zeta]\!] \\
+\sum_{n\geq 0}a_n z^{-n} & \to  a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}
+\end{align*}
+
+Notice that we are at the level of formal series, so there are no convergence assumptions.
+However, there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic fucntions at the origin in $\C_{\zeta}$.
+These formal series are the so called Gevrey-$1$ series: \[\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C[\![z^{-1}]\!]_1\] is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
+The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series.
+}
+
+\begin{notation*}
+We want to distinghuish between formal series and holomorphic functions, as well as between the Borel plane (time domain) and the $z$-plane (spatial domain). Therefore we adopt the following notation:
+\begin{itemize}
+\item $\Phi(z)$: upper-case letters are holomorphic functions in the $z$-plane;
+\item $\tilde{\Phi}(z)$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the $z$-plane;
+\item $\phi(\zeta)$: lower-case letter are holomorphic functions in the Borel plane.
+We follow the convention for Laplace transform of holomorphic functions, namely $\mathcal{L}(\phi(\zeta)((z)=\Phi(z)$.
+\item $\tilde{\phi}(\zeta)$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
+As we will see, the Borel transform of $\tilde{\Phi}(z)$ is $\mathcal{B}(\tilde{\Phi})(\zeta)=:\tilde{\phi}(\zeta)$;
+\item $\hat{\phi}(\zeta)$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}(\zeta)$, when it exists.  
+\end{itemize}
+\end{notation*}
+
+\begin{lemma}
+Let $\tilde{\Phi}(z)\in\C[\![z^{-1}]\!]$. Then, $\tilde{\Phi}\in\C[\![z^{-1}]\!]_1$ is Gevrey-1 if and only if $\mathcal{B}(\tilde{\Phi})\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
+\end{lemma}
+In particular, we deduce from the lemma that the Borel transform is an isomorphism between Gevrey-$1$ series and $\C\delta\oplus\C\lbrace\zeta\rbrace$.
+
+The inverse of $\mathcal{B}$ is what we call a \textbf{formal Laplace transform}.
+
+\textcolor{magenta}{[add definition of convolution product and $\mathcal{B}$ being an algebra isomorphisms]}
+
+\subsubsection{Generalization of the Borel transform}
+The definition of $\mathcal{B}$ can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
+\begin{align*}
+\mathcal{B}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
+\end{align*}
+and then extending by linearity.
+
+If $\alpha\in\mathbb{R}\setminus\Z$ is not an integer, then $\mathcal{B}$ is an isomorphisms from Gevrey-$1$ formal power series $\C[\![z^{-\alpha}]\!]_1$ to the germs of holomorphic functions $\C{\zeta^{\alpha-1}}$, with inverse given by the formal Laplace transform.
+Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C[\![z^{-\alpha}]\!]_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
+\begin{align*}
+\mathcal{B}(z^{-\alpha}\tilde{\Phi})(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
+\end{align*}
+
+and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
+\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
+
+\subsubsection{Properties of the Borel transform}
+We now recall some properties of the Borel transform: let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\tilde{\phi}(\zeta)\defeq\mathcal{B}(\tilde{\Phi}(z))$
+
+\textcolor{orange}{[check notation]}
+
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^n\tilde{\Phi}(z))=\partial_\zeta^n\tilde{\phi}(\zeta)$ 
+\item[(iv)] $\mathcal{B}\left(\partial_z^{n} \tilde{\Phi}(z)\right)=(-\zeta)^n\tilde{\phi}(\zeta)$, for every $n\geq 0$
+\item[(v)] $\mathcal{B}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}(\zeta)$
+\item[(vi)] if $\tilde{\Psi}(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(\tilde{\Phi}(z)\tilde{\Psi}(z))=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}(\zeta)=\mathcal{B}(\tilde{\Psi}(z))$.
+\end{itemize}
+
+\begin{lemma}\label{lem:frac-deriv-Borel}
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] =  \borel \left(z^\mu z^{-(k+1)}\right)(\zeta). \]
+\end{lemma}
+\begin{proof}
+We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+\begin{align*}
+\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
+\end{align*}
+by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
+\begin{equation}\label{frac-diff-laplace}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\end{equation}
+for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
+\end{align*}
+Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
+The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
+This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
+\end{proof}
+
+\begin{proof}
+
+We are going to prove properties (i)--(vi).
+
+(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}(\zeta).\]
+
+(iii) $z^n\tilde{\Phi}(z)=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel (z^n \tilde{\Phi}(z))=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}(\zeta).\]
+
+(vi) $\partial_z^n \tilde{\Phi}(z)=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}(\zeta).\]
+
+(v) see Lemma 5.10 \cite{MS16}.
+
+(vi) see Definition 5.12 and Lemma 5.14 \cite{MS16}. 
+\end{proof}
+
+\begin{remark}
+We notice that properties (i) and (ii) are special cases of property (vi), indeed we can use the convolution product 
+\begin{align*}
+\borel (z^\alpha \tilde{\Phi}(z))&=\borel (z^\alpha)\ast \tilde{\phi}(\zeta)\\
+&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}(\zeta)\\
+&=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\int_0^1(t\zeta)^{-\alpha-1}(\zeta-t\zeta)^k\zeta dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\int_0^1 t^{-\alpha-1}(1-t)^k dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\frac{\Gamma(k+1)\Gamma(-\alpha)}{\Gamma(k-\alpha+1)}\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
+&=\partial_\zeta^\alpha\tilde{\phi}(\zeta)
+\end{align*}
+\end{remark}
+
+\subsection{Differential equation}
+\textcolor{orange}{Should we keep this section?}
+If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
+In these coordinates, we can write down the partial differential operator
+\begin{equation}%%\label{laplace:op}
+\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
+\end{equation}
+The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
+
+Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
+%\end{problem}
+The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
+\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
+
+\subsubsection{Order shifting}\label{shifting}
+\textcolor{orange}{[why the name order shifting?]}
+Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
+A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
+We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
+\begin{equation}\label{eqn:slight-defn}
+\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
+\end{equation}
+where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
+
+Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
+This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
+In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
+\begin{prop}\label{prop:shifting}
+When $\psi$ is slight and locally integrable at $\zeta = 0$,
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+if and only if
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+where $h_n, \ldots, h_{-m}$ are regular functions.
+\end{prop}
+To prove this result, we'll need a little background.
+
+Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
+The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
+If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
+A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
+
+Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
+Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
+Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
+Each basic operation has a simple effect on a slight function's order.
+Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
+Differentiation and integration add $-1$ and $1$, respectively.
+\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
+The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
+
+To prove the forward implication, rewrite the first equation in the statement as
+\begin{equation}\label{eqn:diff-int-split}
+\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
+\end{equation}
+The function
+\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
+is slight.
+Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
+Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
+
+Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
+Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
+\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
+which rearranges to the second equation in the statement.
+\end{proof}
+
+\section{Proof of main results}
+\subsection{Borel regularity for ODEs}
+\subsection{Borel regularity for thimble integrals}
+
 \section{Third-order exponential integrals}
@@
 
+\color{black}
+
+\appendix
+
+\section{Integro-differential equations}
+\subsection{Existence of solutions}
+\subsubsection{Algebraic integral operators}
+Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
+Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
+For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
+We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
+\begin{align*}
+\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
+\phi & \mapsto \zeta^{-\sigma} \phi
+\end{align*}
+is an isometry. More generally,
+\begin{align*}
+\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
+f & \mapsto \zeta^{-\delta} f
+\end{align*}
+is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$.
+This reduces to the previous statement when $\rho = 0$.
+For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
+Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
+
+Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
+For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
+
+We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
+\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
+where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
+The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
+Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
+That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
+
+For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure.
+The square of a density is a Riemannian metric.
+Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
+The bound
+\begin{align*}
+\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
+& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
+& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
+\end{align*}
+holds for any integration path. Taking the infimum over all paths, we see that
+\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_\infty. \]
+so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
+\subsubsection{The example of fractional integrals}
+Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
+The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
+It follows that
+\begin{align*}
+\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
+& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
+& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
+& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
+& = B(-\lambda,\,1-\rho).
+\end{align*}
+The beta function $B$ can be written more explicitly as
+\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
+Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
+\subsubsection{Fractional integral equations near a regular singular point}
+\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
+
+Consider an integral operator $\mathcal{J}$ of the form
+\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
+where:
+\begin{itemize}
+\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
+\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
+\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
+\item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
+\end{itemize}
+Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough.
+We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.
+
+We want to solve the equation $\mathcal{J}f = 0$.
+Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+When $\epsilon$ is small enough that $\Lambda \subset (-\infty, -1 - \epsilon]$, we'll see that we can always find such a solution, as long as we're willing to shrink $\Omega$.
+In fact, there's exactly one such solution.
+\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}
+
+Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.
+
+Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
+\begin{alignat*}{2}
+p & = p'_0 \zeta &\;+\;& \tilde{p} \\
+q & = q_0 &\;+\;& \tilde{q}
+\end{alignat*}
+with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
+\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
+with
+\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
+For any $\tau \in (0, \infty)$,
+\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
+Setting $\tau = -q_0 / p'_0$ makes the first term vanish, leaving
+\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
+Then the equation $\mathcal{J}f = 0$ becomes
+\begin{align}
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \nonumber \\
+0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
+-p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
+\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f}.
+\label{fixed-pt}
+\end{align}
+
+\color{Indigo}
+\begin{center}
+\begin{tikzcd}[column sep=25mm, row sep=2mm]
+& & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^{1-\epsilon}"'] \\
+& & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
+& & & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
+& & & \holoL{\infty, \rho}(\Omega) \\
+& & & \holoL{\infty, \rho-1}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-1-\epsilon-\lambda}"'] \\
+& & & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
+\holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 1-\rho) = \frac{1}{1-\rho}}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\zeta^{-1}", "\|\zeta^{-1}\|_{\infty, 1} = 1"'] & \holoL{\infty, \rho}(\Omega) \\
+\end{tikzcd}
+\end{center}
+\color{black}
+
+From \textbf{[our previous discussion]}, we can work out that
+\begin{align*}
+\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
+\end{align*}
+and
+\begin{align*}
+\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau-\epsilon}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
+\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\end{align*}
+Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
+\begin{align*}
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\
+\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
+\end{align*}
+and
+\begin{align}
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
+\label{bound:perturb}
+\end{align}
+We can also see that
+\begin{align}
+\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with}   \nonumber \\
+\|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
+\end{align}
+
+Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
+\begin{align*}
+\mathcal{A} & = \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}}  \\
+b & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1}
+\end{align*}
+Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
+We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
+
+An affine map is a contraction if and only if its linear part is a contraction.
+We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$.
+Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
+Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
+%\input{chapters/appendix}
+
 \bibliographystyle{plain}

### 2023-01-28 exp-resurgence.tex
updates

@@
 \item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+\begin{itemize}
+\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
+\end{itemize}
 \item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
@@
 We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-\textcolor{orange}{[Veronica---I dont't see why]}
+\begin{itemize}
+\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+\end{itemize}
 \end{itemize}
@@
 \item Illustrate with detailed treatments of several examples.
+\begin{itemize}
+\item Contour argument (thimble integrals)
+\item solving integral equation (ODE)
+\item How thimble integrals and ODE are related in our examples?
+\end{itemize}
 \begin{itemize}
@@
 \item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+\begin{itemize}
+\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
+\item computation of Stokes constants via Picard--Lefschetz theory
+\end{itemize}
 \end{itemize}
@@
 YES.
-The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
 \item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-\item Maybe the correct place is the setting of Ecalle's formal integral. See \S 5.2.2.1 of Delabaere's {\em Divergent Series, Summability and Resurgence III}.
+\begin{itemize}
+\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+(proof based on existence theorem \ref{frac_int_exist})
+\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+\end{itemize}
 \item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
@@
 [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-\item If the Borel-transformed equation has a subexponential solution $\hat{f}$ which is ``shifted holomorphic'' (we called this having a ``fractional power singularity'' in {\tt airy-resurgence}), then $\laplace \hat{f}$ satisfies the original equation, because there are no boundary terms.
+\color{DarkBlue}
 \item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
@@
 \item \textbf{Being a thimble integral}
+
+\begin{itemize}
+\item take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series
+\item see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform)
+\item {[Thm 4]} 1-dim thimbles integrals are Borel regular.
+\end{itemize}
 
@@
 Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
-\subsubsection{Fractional integral equations near a regular singular point}
+\subsubsection{Fractional integral equations near a regular singular point}\label{frac_int_exist}
 \textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
@@
 \begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
+\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\%\nonumber \\
 \|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.

### 2023-02-04 exp-resurgence.tex
updates

@@
 \usepackage{amsthm}
+%\usepackage{eqnarray}
 \usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
@@
 
+\section{Examples}
+
+\subsection{Modifield Bessel equation}
+
+\subsection{Airy}
+
+The Airy equation is
+\begin{equation}\label{eqn:airy}
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
+\end{equation}
+One solution is given by the Airy function,
+\[ \Ai(y) = \frac{i}{2\pi} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
+where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
+\begin{center}
+\includegraphics{figures/u_contour_3.pdf} \\[1em]
+{\small The contour $\Gamma$ in the $u$ plane.}
+\end{center}
+With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
+\[ \Ai(y) = y^{1/2}\;\frac{i}{\pi} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+\subsubsection{Rewriting as a modified Bessel equation}
+We can distill the most interesting part of the Airy function by writing
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+where
+\begin{equation}\label{integral:mod-bessel}
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
+\begin{equation}\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
+
+The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
+\begin{equation}\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
+\end{equation}
+
+\textcolor{orange}{[copy the result of Bessel with parameter $\nu=1/3$.]}
+
+\subsection{Airy--Lucas}
+The Airy-Lucas equation is
+\begin{equation}\label{eqn:airy-lucas}
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
+\end{equation}
+with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+\subsubsection{Rewriting as a \textcolor{DarkCyan}{modified Bessel (?)} equation}
+We can distill the most interesting parts of the Airy-Lucas function by writing
+\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{\textcolor{DarkCyan}{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
+where
+\begin{equation}\label{integral:mod-bessel-rational}
+K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
+\end{equation}
+Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
+\begin{equation}%%\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\textcolor{DarkCyan}{\tfrac{m}{n} (?)}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{\textcolor{DarkCyan}{m/n}}$.
+
+Like we did in equation~\ref{eqn:reg-mod-bessel}, we can rewrite the modified Bessel equation above as
+\begin{equation}%%\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\textcolor{DarkCyan}{\tfrac{m}{n}}\big)^2 z^{-2} \right] \varphi = 0.
+\end{equation}
+
+\textcolor{orange}{[copy the result of Bessel with parameter $\nu=m/n$.]}
+
+\subsection{Higher Airy}
+
+The higher Airy equation is
+\begin{equation}\label{eqn:airy-lucas}
+\left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
+\end{equation}
+with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+
+\color{Peru}
+With
+\begin{align*}
+z & = (-1)^{n-1} \tfrac{n-1}{n} y^{n/(n-1)} & w & = (-1)^n (n-1) y^{1/(n-1)} u,
+\end{align*}
+we have
+\begin{align*}
+\widetilde{\Ai}^{(k)}_n(y) & = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w^n - yw\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \left(w^{n-1} - ny\right)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \big((n-1)^{n-1} yu^{n-1} - ny\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}yw \big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[(-1)^n \tfrac{n-1}{n} y^{n/(n-1)} u\big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
+& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,dw \\
+& = (-1)^n (n-1) \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+& = (-1)^n (n-1) \frac{\exp\left(\pi ik \big(1 - \tfrac{1}{n-1}\big)\right)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+& = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
+\end{align*}
+\color{black}
+\[ \widetilde{\Ai}^{(k)}_n(y) = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\, \]
+where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+\subsubsection{Rewriting as a \textcolor{magenta}{(???)} equation}
+We can distill the most interesting parts of the hyper-Airy function by writing
+\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
+where
+\begin{equation}
+K(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
+\end{equation}
+Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
+\begin{equation}%%\label{eqn:mod-bessel}
+\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
+\end{equation}
+The sub-leading coefficients are the triangular numbers
+\[ c_n^{(1)} = \frac{n(n-1)}{2}. \]
+\color{DarkCyan}
+The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
+\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,(n+1)^{\underline{k+2}} \]
+in terms of the polynomials
+
+\begin{align*}
+b_n^{(2)} & = & \tfrac{1}{24} \\
+b_n^{(3)} & = & \tfrac{1}{48} n \\
+b_n^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
+b_n^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
+b_n^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440}. 
+\end{align*}
+
+Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}.
+They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
+\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
+which tells us that
+\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots.
+\]
+The last coefficient can be written as
+\[ c_n^{(n-1)} = \left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, \]
+giving
+\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
+\color{black}
+
+\textcolor{red}{[What about doing degree 3 or 4 example/ degree 2 is again Bessel?]}
+
+\subsection{Generalized Airy}
+
 \section{Third-order exponential integrals}

### 2023-02-05 exp-resurgence.tex
Outline example reorganization

@@
 
-\subsection{Modifield Bessel equation}
-
 \subsection{Airy}
@@
 We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+\begin{itemize}
+\item By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}.
+\item The arguments we'll do for the Airy function work essentially the same for all Airy-Lucas functions, so we'll go straight to the general case.
+\item However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see on its own.
+Appendix~\textbf{[airy-appendix]} shows the same arguments in this special case.
+\end{itemize}
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 \textcolor{orange}{[copy the result of Bessel with parameter $\nu=m/n$.]}
+
+\subsection{Modified Bessel}
+
+\textcolor{magenta}{[For this, we lift to a countable cover; see {\tt airy-resurgence.tex}, currently \S 6.4]}
 

### 2023-02-05 exp-resurgence.tex
updates

--- 2023-02-04 exp-resurgence.tex
@@
 Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
-\begin{equation}%%\label{eqn:mod-bessel}
+\begin{equation}\label{eqn:higher-Airy}
 \left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
@@
 
-\textcolor{red}{[What about doing degree 3 or 4 example/ degree 2 is again Bessel?]}
+\subsubsection{Higher Airy of degree $3$}
+Setting $n=4$, equation \ref{eqn:higher-Airy} turns into
+
+\begin{equation}\label{eqn:reg-higher3}
+\left[\frac{\partial^3}{\partial z^3}+1+\frac{6}{z}\frac{\partial^2}{\partial z^2}-\frac{35}{8}\frac{1}{z^2}\frac{\partial}{\partial z}+\frac{315}{16}\frac{1}{z^3}\right]\varphi=0
+\end{equation}
+
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-higher3}.
+We'll succeed when $\alpha^3 + 1 = 0$.%, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-higher3} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:higher3}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+It's tempting to differentiate both sides of this equation until we get
+\begin{equation}\label{diff-eq:higher3}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
+\end{equation}
+which is easier to solve.
+Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
+
+This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+We can see the regular singularities by moving the derivatives to the right:
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
+
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed.
+For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+We learned in Section~\ref{translation} that
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\color{Peru}
+\begin{align*}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
+\end{align*}
+\color{Sienna}
+\begin{align*}
+\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
+\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
+\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
+\end{align*}
+\color{black}
+%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
+%%\begin{equation}\label{eqn:centered-mod-bessel}
+%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
+\]
+%%\end{equation}
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
+\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
+\begin{equation}\label{diff-eq:hypergeom-pos}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
+In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+
+In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
+Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
+In our case, though, exchanging $1$ with $-1$ keeps equation~\ref{diff-eq:spatial-mod-bessel} the same.
+
+\color{DodgerBlue}
+If we'd followed the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we would've arrived at the hypergeometric equation
+\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
+where $\zeta_{-1} = 2\xi_{-1}$.
+This is the same as what we'd get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
+In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$
 

### 2023-02-19 exp-resurgence.tex
updates

@@
-\documentclass{article}
+c\documentclass{article}
 
@@
 \maketitle
+
 \section{Introduction}
@@
 \end{itemize}
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
-The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
-\end{equation}
-
-\textcolor{orange}{[copy the result of Bessel with parameter $\nu=1/3$.]}
 
@@
 where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+We can see from Section~\ref{reg-decay} that $V_\alpha\in z^{-\tau_\alpha}\C[\![z^{-1}]\!]$, so we further decompose
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+with $W_\alpha\in\C[\![z^{-1}]\!]$.
 \color{Peru}
@@
 This is the same as what we'd get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$
+In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
+
+\color{black}
 
@@
 
+\section{The Airy equation}
+\color{Peru}
+\subsubsection{Rewriting as a modified Bessel equation}
+We can distill the most interesting part of the Airy function by writing
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+where
+\begin{equation}\label{integral:mod-bessel}
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
+\begin{equation}\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
+\end{equation}
+In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
+
+The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
+\begin{equation}\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
+\end{equation}
+
+\color{black}
+\subsection{Asymptotic analysis}
+Equation~\ref{eqn:mod-bessel} has a regular singularity at $z = 0$ and an irregular singularity at $z = \infty$.
+From the general theory of such equations, we know that the space of trans-series solutions has a basis of trans-monomials
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
+where the $\series{W}_\alpha\in\C[\![z^{-1}]\!]$ are formal power series in $z^{-1}$ with no constant term.
+From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{1/2}\,\series{W}_1$, with
+\begin{equation}\label{bessel-asymp}
+\series{W}_1 = z^{-1} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-3} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-4} + \ldots
+\end{equation}
+
+The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+which seem analogous to the trans-monomials above.
+Borel summation makes the analogy precise.
+We'll see in Section~\ref{bessel-regularity} that each $z^{\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{\tau_\alpha}\,\series{W}_\alpha$.
+\subsection{Going to the spatial domain}\label{spatial}
+%\subsubsection{The big idea}\label{big-idea}
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-mod-bessel}.
+We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+It's tempting to differentiate both sides of this equation until we get
+\begin{equation}\label{diff-eq:spatial-mod-bessel}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
+\end{equation}
+which is easier to solve.
+Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
+
+This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+We can see the regular singularities by moving the derivatives to the right:
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
+
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed.
+For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+We learned in Section~\ref{translation} that
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+%\color{Peru}
+%\begin{align*}
+%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
+%\end{align*}
+%\color{Sienna}
+%\begin{align*}
+%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
+%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
+%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
+%\end{align*}
+%\color{black}
+%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
+%%\begin{equation}\label{eqn:centered-mod-bessel}
+%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
+\]
+%%\end{equation}
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
+\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
+\begin{equation}\label{diff-eq:hypergeom-pos}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
+In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+
+In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
+Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
+In our case, though, exchanging $1$ with $-1$ keeps equation~\ref{diff-eq:spatial-mod-bessel} the same.
+
+%\color{DodgerBlue}
+%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
+%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
+%where $\zeta_{-1} = 2\xi_{-1}$.
+This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
+In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
+
+\subsection{Contour argument for the Airy function}\label{contour-argument}
+We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $\zeta = 4u^3 - 3u$.
+Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
+\begin{equation}\label{integral:mod-bessel-zeta}
+K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+\end{equation}
+For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{center}
+\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
+{\small The contour $\gamma_1$ in the $\zeta$ plane.}
+\end{center}
+
+It happens\footnote{\textcolor{magenta}{Veronica:} This comes from \cite[equation~15.4.14]{dlmf}.} that for our desired branch of $u$,
+\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
+so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
+\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
+
+In addition to the solutions $g_1$ and $f_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
+\begin{alignat*}{2}
+g_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
+f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
+\end{alignat*}
+given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}.
+
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_0), \]
+so we have
+\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_0)\;d\zeta. \]
+The solution $g_1$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
+The solution $g_0$, in contrast, is non-meromorphic at $\zeta = 1$.
+Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,f_0$,
+as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
+Hence,
+\begin{align*}
+K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} f_0\;d\zeta \\
+e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} f_0\;d\zeta \\
+K_1 & = \tfrac{i}{2} \laplace_{\zeta_1} f_0,
+\end{align*}
+just as we found in Section~\ref{spatial-success}.
+\subsection{Another solution}
+Section~\ref{contour-argument} associates the solution $K$ of equation~\ref{eqn:mod-bessel} with the solution $g_0$ of equation~\ref{eqn:hypergeom}, which contributes the pole at $\zeta = 1$ of
+\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_0). \]
+The solution $g_1$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+
+To express this other solution as a Laplace transform, following the method of Section~\ref{spatial-success}, we would use the solution
+\[ f_1 = (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
+of equation~\ref{eqn:hypergeom}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
+
+In summary, the contour integration method of solving equation~\ref{eqn:mod-bessel} is associated with the basis
+\begin{align*}
+g_1 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
+g_0 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
+\end{align*}
+of solutions for equation~\ref{eqn:hypergeom}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
+These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
+
+The Laplace transformation method of solving equation~\ref{eqn:mod-bessel}, on the other hand, is associated with the basis
+\begin{alignat*}{2}
+f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
+f_0 &\;=\:& \xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
+\end{alignat*}
+given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
+
+Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
+\begin{alignat*}{3}
+f_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,g_1 &\;+\;& \tfrac{1}{2}\,f_0 \\
+f_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_0 &\;+\;& \tfrac{1}{2}\,f_1.
+\end{alignat*}
+Summing these identities, we see that
+\[ g_1 + g_0 = \tfrac{\sqrt{3}}{2}\,(f_1 + f_0), \]
+giving the alternate decomposition
+\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_0). \]
+
+\subsection{Correspondence with Mari\~{n}o's series}
+Let $F_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $F_1$ will be written in the variable $z$.
+
+\begin{align*}
+\Ai(x) & = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} \varphi_1\big(\tfrac{2}{3} z^{-1}\big) \\
+& = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) \\
+\Ai(x) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2})
+\end{align*}
+Putting together,
+\begin{align*}
+\tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;x^{-3/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(\tfrac{2}{3} x^{3/2}) \\
+\tfrac{\sqrt{3\pi}}{2}\;\big(\tfrac{3}{2} z)^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
+\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} F_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = k(\zeta) \\
+\sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
+-\tfrac{1}{3\sqrt{2}}\;\left[\zeta^{-1/2}\right] * f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
+\end{align*}
+Notice that if the hypergeometric differentiation formula holds for fractional derivatives,
+\[ \big(\tfrac{\partial}{\partial \xi}\big)^{1/2}F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \propto F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big) \]
+
+\subsection{Comparison with other Airy examples}
+
+\subsubsection{Different Borel transform convention} In physics, sometimes it happens that authors find more convenient a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+It is also commun to consider formal power series in small parameters, like $\tilde{\Phi}(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ where $\hbar\to 0$.
+Then the Borel transform of $\tilde{\Phi}$ is defined as $\tilde{\phi}(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author studies resurgent properties of the Airy functions: his starting point are the formal solutions of Airy differential equation
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\end{align*}  
+where 
+\begin{align*}
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n
+\end{align*}
+Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) \\
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
+\end{align*}
+%That ambiguity comes from the different definitions of Borel transforms: 
+%\begin{align*}
+%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%\end{align*}
+
+Comparing $\mathcal{B}(\tilde{W}_{1,2})(\zeta)$ with $\hat{w}_{\pm}$ in \eqref{hat+}\eqref{hat-}, they differ only by a constant which multiplies the $\delta$.
+\subsubsection{Integral formula for hypergeometric functions}
+
+In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
+He defines the formal series $\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}$ such that
+
+\begin{align*}
+\Phi_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
+\Phi_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\mathcal{L}\circ\mathcal{B}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
+\end{align*}
+
+Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence
+
+\begin{align*}
+\tilde{\phi}_{+}(\zeta)&=\mathcal{B}\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
+\tilde{\phi}_{-}(\zeta)&=\mathcal{B}\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
+\end{align*}
+which up to a constant factor for $\delta$, they agree with our results.
+
+However, the author adopts a different approach to compute $\tilde{\phi}_{\pm}(\zeta)$: he argues that $\Phi_{\mathrm{Ai}}, \Phi_{\mathrm{Bi}}$ are solutions of Airy equation if and only if
+
+\begin{align*}
+\tilde{\phi}_+(\zeta)=\delta+\frac{d}{d\zeta}\tilde{\chi}(\zeta)  \qquad \tilde{\phi}_-(\zeta)=\delta-\frac{d}{d\zeta}\tilde{\chi}(-\zeta)
+\end{align*}
+ where $\chi(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$. Function $\chi(\zeta)$ is an hypergeometric function:
+
+\begin{align*}
+\chi(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\zeta t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
+\end{align*}
+where in the last step we use the Euler formula for hypergeometric functions (see \eqref{Euler formula}). Finally, we take the derivative
+
+\begin{align*}
+\tilde{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
+\tilde{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right).
+\end{align*}
+
+The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
+Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
+Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
+
+\subsubsection{Comparison with exact WKB}
+
+Kawai and Takei study the WKB analysis of the equation
+
+\begin{equation}
+\label{WKB_Airy} 
+\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
+\end{equation}
+as $\eta\to\infty$.
+They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
+In the coordinates $t=yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
+\begin{align*}
+\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
+\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
+\end{align*}
+where $s=3t/4+1/2$. 
+The same hypergeometric functions have been computed in Section ?? as the Borel transform of the formal solutions of the Airy equation
+
+\begin{equation}
+\label{Airy}
+\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
+\end{equation}
+
+Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
+So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
+
+First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
+\begin{align*}
+\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
+\end{align*} 
+then $t=yx^{-3/2}$ is the conjugate variable of $q=\eta x^{3/2}$ up to correction by a factor of $x^{-3/2}$
+\begin{align*}
+\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!} y^{n}=x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}. 
+\end{align*}
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
+\begin{equation}
+\label{eq_Phi}
+\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
+\end{equation}
+
+\begin{proof}
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
+&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
+&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
+&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
+\end{align*}
+\end{proof}
+Now rewrite \eqref{eq_Phi} in the coordinates $q=\eta x^{3/2}$: 
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\frac{9}{4}\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{4}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\frac{3}{2}\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{3}\eta x^{-1/2}\frac{d}{dq}+\frac{2}{3}\, \eta\,  x^{-1/2}\frac{d}{dq}-\frac{1}{9}x^{-2}-\frac{4}{9}\eta^2x\right]\Phi=0\\
+&\left[\eta^2\left(\frac{d}{dq}\right)^2+\eta x^{-3/2}\frac{d}{dq}-\frac{1}{9}x^{-3}-\frac{4}{9}\eta^2\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-\frac{4}{9}\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-\frac{4}{9}\right]\Phi=0
+\end{align*}
+
+therefore $\Phi(q)$ is a solution of the transform Airy equation (see draft2).
+
 \bibliographystyle{plain}
 \bibliography{airy-resurgence}
+
 \end{document}

### 2023-02-20 exp-resurgence.tex
Switch Airy and Airy-Lucas to standard sign convention
This matches the DLMF (for Airy) and Elba's paper (for Airy-Lucas).
Still need to switch hyper-Airy.

@@
-c\documentclass{article}
+\documentclass{article}
 
@@
 One solution is given by the Airy function,
-\[ \Ai(y) = \frac{i}{2\pi} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
+\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
+where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
 \begin{center}
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{i}{\pi} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
@@
 \begin{equation}\label{integral:mod-bessel-rational}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
+K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
 \end{equation}
@@
 \subsection{Contour argument for the Airy function}\label{contour-argument}
-We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $\zeta = 4u^3 - 3u$.
+We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
 Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have

### 2023-02-20 figures/contours.jl

@@ -18,17 +18,17 @@ function path_scale(n, k)
     return cos(π*(1/2 - skip/3n)) / abs(cos(π*k/n))
   end
 end
-u_path(θ, off, n = 3, k = 1) = t -> path_scale(n, k) * exp(-im*θ/n) * (cosh(π*(1-k/n)*im - t) - dot(off, [exp(π*(1-k/n)*im), exp(-π*(1-k/n)*im)]))
-u_jet(θ, off, n = 3, k = 1) = t -> (u_path(θ, off, n, k)(t), -path_scale(n, k) * exp(-im*θ/n) * sinh(π*(1-k/n)*im - t))
+u_path(θ, off, n = 3, k = 1) = t -> path_scale(n, k) * exp(-im*θ/n) * (cosh(π*(k/n)*im + t) - dot(off, [exp(π*(k/n)*im), exp(-π*(k/n)*im)]))
+u_jet(θ, off, n = 3, k = 1) = t -> (u_path(θ, off, n, k)(t), path_scale(n, k) * exp(-im*θ/n) * sinh(π*(k/n)*im + t))
 
 function T_jet(n)
   T_pt = convert(Polynomial, ChebyshevT(push!(fill(0, n), 1)))
   T_push = derivative(T_pt)
   u -> begin
     if length(u) == 1
-      return T_pt(u)
+      return -T_pt(u)
     else
-      return (T_pt(u[1]), T_push(u[1])*u[2])
+      return (-T_pt(u[1]), -T_push(u[1])*u[2])
     end
   end
 end

### 2023-02-25 exp-resurgence.tex
updates

--- 2023-02-05 exp-resurgence.tex
@@
 \item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-\begin{equation}\label{eq:ODE}
+\begin{equation}\label{eqn:standard ODE}
 \big[ P(\partial_z)+\frac{1}{z}Q(\partial_z)+R(z^{-1})\big]\Psi=0
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{i}{\pi} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
-\begin{itemize}
-\item By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}.
-\item The arguments we'll do for the Airy function work essentially the same for all Airy-Lucas functions, so we'll go straight to the general case.
-\item However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see on its own.
-Appendix~\textbf{[airy-appendix]} shows the same arguments in this special case.
-\end{itemize}
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
-The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
-\end{equation}
-
-\textcolor{orange}{[copy the result of Bessel with parameter $\nu=1/3$.]}
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+
+By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we will go straight to the general case.
+However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
+For this reason, in Appendix~\cite{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
 
@@
 where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-\subsubsection{Rewriting as a \textcolor{DarkCyan}{modified Bessel (?)} equation}
+
+\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{\textcolor{DarkCyan}{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
 where
-\begin{equation}\label{integral:mod-bessel-rational}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
-\begin{equation}%%\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\textcolor{DarkCyan}{\tfrac{m}{n} (?)}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{\textcolor{DarkCyan}{m/n}}$.
-
-Like we did in equation~\ref{eqn:reg-mod-bessel}, we can rewrite the modified Bessel equation above as
-\begin{equation}%%\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\textcolor{DarkCyan}{\tfrac{m}{n}}\big)^2 z^{-2} \right] \varphi = 0.
-\end{equation}
-
-\textcolor{orange}{[copy the result of Bessel with parameter $\nu=m/n$.]}
+\begin{equation}\label{integral:mod-bessel-rational-AL}
+K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+\end{equation}
+Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation
+\begin{equation}\label{eqn:mod-bessel-AL}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
+\end{equation}
+In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{{m/n}}$.
+
+Let's put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
+\begin{equation}\label{eqn:reg-mod-bessel-AL}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] K = 0.
+\end{equation}
+
+%\subsection{Going to the spatial domain}\label{spatial-AL}
+\subsubsection{The big idea}\label{big-idea}
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
+We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+It's tempting to differentiate both sides of this equation until we get
+\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
+\end{equation}
+which is easier to solve.
+Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it's slight and locally integrable at $\zeta = \alpha$.
+
+This is great news, because equation~\ref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+We can see the regular singularities by moving the derivatives to the right:
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
+
+In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
+For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = \alpha$.
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+We learned in Section~\ref{translation} that
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+%\color{Peru}
+%\begin{align*}
+%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
+%\end{align*}
+%\color{Sienna}
+%\begin{align*}
+%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
+%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
+%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
+%\end{align*}
+%\color{black}
+%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
+%%\begin{equation}\label{eqn:centered-mod-bessel}
+%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
+\]
+%%\end{equation}
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel-AL} looks like
+\begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
+\end{equation}
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
+\begin{equation}\label{diff-eq:hypergeom-pos-AL}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
+\end{equation}
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = -1$.
+In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+
+In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
+Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
+In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
+
+\color{Turquoise}
+\subsubsection{Borel regularity}\label{bessel-regularity-AL}
+Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel-AL}
+
+\begin{equation}
+\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
+\end{equation}
+Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
+%
+%\subsubsection{Borel sum of $\tilde{W}_1$}
+%
+%Let us first compute the Borel transform of $\tilde{W}_1$:
+%
+%
+%\begin{align*}
+%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
+%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
+%\end{align*}
+
+Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
+
+\begin{align*}
+\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
+&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
+&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
+\end{align*}
+
+Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
+therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
+In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
+
+Similarly, if we consider the formal power series
+
+\begin{equation}
+\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
+\end{equation}
+
+analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
+
+\color{black}
+
+\subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
+We can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
+\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
+& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
+\end{align*}
+\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
+For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{center}
+\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
+{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
+\end{center}
+
+The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
+\begin{align*}
+& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
+\end{align*}
+as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
+Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
+\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+\color{DarkCyan}
+Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
+\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
+\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
+where $\zeta = -1 + \zeta_{-1}$.
+\color{black}
+\subsubsection{Lifting to a countable cover}
+Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
+Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
+
+Setting $u = \cosh(t/n)$ and recalling that
+\begin{align*}
+\cosh(n\tau) & := T_n(\cosh(\tau)) \\
+\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
+\end{align*}
+we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
+\begin{align}
+\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\end{align}
+For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
+\begin{align}
+\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
+\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
+\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
+\end{align}
+where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
+The integral converges when $z$ is in the right half-plane.
+We get formula~\ref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
+
+When $\nu$ goes to $0$, formula~\ref{integral:mod-bessel-lifted} becomes
+\[ K_\nu(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
+Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
+\begin{align*}
+K_\nu(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
+& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
+& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
+\end{align*}
+with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
+\subsubsection{Link to dihedral triangulations}
+Here are the local normal forms of Kummer's first and second solutions. In the table, $[\bullet]$ denotes a local holomorphic function of order $0$ \cite[identities 15.8.2--4]{dlmf}, and
+\begin{align*}
+a' & = a+(1-c) \\
+b' & = b+(1-c) \\
+c' & = 2-c
+\end{align*}
+\begin{center}
+\begin{tabular}{c|c|c|c}
+Function & $0$ & $1$ & $\infty$ \\ \hline
+$F(a, b, c, \xi)$ & $[\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$ \\
+$\xi^{1-c} F(a', b', c', \xi)$ & $\xi^{1-c} [\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$
+\end{tabular}
+\end{center}
+
+For example, at $\zeta = \infty$, the function
+\[ u_{-1} = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, 1 - \tfrac{1}{2} \zeta_{-1}) \]
+is slight, with normal form $(1/\zeta_{-1})^{1 - m/n} f_1 + (1/\zeta_{-1})^{1 + m/n} f_2$~\cite[identity~15.8.3]{dlmf}.
+At $\zeta = 1$, it's holomorphic with order $0$.
+At $\zeta = -1$, it has the form $h + \zeta_{-1}^{-1/2} f$, where $h$ is holomorphic with order $0$.
+
+On the other hand, the function
+\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}) \]
+is slight at $\zeta = \pm 1$ with order $-\tfrac{1}{2}$, and slight at $\infty$ with order $1 - \tfrac{m}{n}$.
+
+Hence, the ratio $u_{-1} / v_{-1}$ looks like a holomorphic multiple of $\zeta_1^{1/2}$ near $\zeta = 1$, a holomorphic function plus a holomorphic multiple of $\zeta_{-1}^{1/2}$ near $\zeta = -1$, and a holomorphic function plus a holomorphic multiple of $(1/\zeta_{-1})^{2m/n}$ near $\zeta = \infty$.
+This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.
+
+\color{ForestGreen}
+Let's try to get the small tetrahedral tiling by setting
+\begin{align*}
+1 - c & = \tfrac{1}{3} \\
+c - a - b & = \tfrac{1}{3} \\
+b - a & = \tfrac{1}{2},
+\end{align*}
+so $(a, b, c) = (-\tfrac{1}{12}, \tfrac{5}{12}, \tfrac{2}{3})$. The general hypergeometric equation is
+\begin{align*}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + \big[c - (a+b+1)\xi_1\big] \tfrac{\partial}{\partial \xi_1} - ab\right] & v = 0 \\
+\left[-\tfrac{1}{2}\zeta_1 (1 + \tfrac{1}{2}\zeta_1) 4 \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + \big[c + \tfrac{1}{2}(a+b+1)\zeta_1\big] (-2) \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
+\left[-\zeta_1 (2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 - \big[2c + (a+b+1)\zeta_1\big] \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
+\left[(1 - \zeta)(1 + \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[2c + (a+b+1)(\zeta - 1)\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[(c - a - b) + (c - 1) + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[\mu - \lambda + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
+\left[\big[\tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta\big] \tfrac{\partial}{\partial \zeta} - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
+\left[\tfrac{\partial}{\partial \zeta} \circ \big[ \tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta \big] + 2\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
+\left[\big[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) + 4 \tfrac{\partial}{\partial \zeta} \circ \zeta - 2 \big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ (a+b+1) - ab \big]\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ {-}1 + a + b - ab \big]\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta - (a-1)(b-1)\right] & v = 0 \\
+\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta^2 - 1) + (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (a+b-3) \tfrac{\partial}{\partial \zeta} \circ \zeta + (a-1)(b-1)\right] & v = 0,
+\end{align*}
+For the tetrahedral tiling, we get
+\[ \left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big(\zeta^2 - 1\big) - \tfrac{8}{3} \tfrac{\partial}{\partial \zeta} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\right] v = 0, \]
+which comes from the integral equation
+\[ \left[\big(\zeta^2 - 1\big) - \tfrac{8}{3}\,\fracderiv{-1}{\zeta}{\alpha} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\,\fracderiv{-2}{\zeta}{\alpha}\right] v = 0. \]
+In the frequency domain, this equation becomes
+\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
+\color{black}
+\color{SpringGreen}
+Set
+\[ \laplace_{\zeta, \alpha} v = \int_\Lambda e^{-zf}\,p\,du. \]
+Observe that
+\[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] \int_\Lambda e^{-zf}\,p\,du = \int_\Lambda e^{-zf}\,(f^2 - 1)p\,du \]
+and
+\begin{align*}
+z^{-1} \tfrac{\partial}{\partial z} \int_\Lambda e^{-zf}\,p\,du & = z^{-1} \int_\Lambda e^{-zf}\,(-fp)\,du \\
+& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')q_1\,du \\
+& = \int_\Lambda e^{-zf}\,f'q_1\,du
+\end{align*}
+where $q_1' = -fp$.
+and
+\begin{align*}
+z^{-2} \int_\Lambda e^{-zf}\,p\,du
+& = -z^{-2} \int_\Lambda e^{-zf}\,(-zf')p_1\,du \\
+& = z^{-1} \int_\Lambda e^{-zf}\,f'p_1\,du \\
+& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')p_2\,du \\
+& = \int_\Lambda e^{-zf}\,f'p_2\,du \\
+\end{align*}
+with $p_1' = p$ and $p_2' = f'p_1$.
+\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
+\color{black}
+
+\color{orange}
+In DLMF notation, let's try
+\begin{align*}
+u_1 & = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \xi_{-1}) \\
+& = w_1(\xi_{-1}) \\
+u_{-1} & = w_3(\xi_{-1}) \\
+v_{-1} & = w_2(\xi_{-1}) \\
+v_1 & = -i\sqrt{2}\,\zeta_1^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
+& = (-\tfrac{1}{2}\zeta_1)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
+& = (1 - \tfrac{1}{2}\zeta_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \tfrac{1}{2}\zeta_{-1}) \\
+& = (1 - \xi_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \xi_{-1}) \\
+& = w_4(\xi_{-1}),
+\end{align*}
+where $\xi_{-1} = \tfrac{1}{2}\zeta_{-1}$.
+
+\color{RoyalBlue}
+Let's guess that we're working with the map $\phi / \psi$ with
+\begin{align*}
+\phi & = \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{2} - \tfrac{m}{2n})\Gamma(\tfrac{1}{2} + \tfrac{m}{2n})}\,(\mp \zeta)\,F(1 - \tfrac{m}{2n}, 1 + \tfrac{m}{2n}, \tfrac{3}{2}; \zeta^2) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
+\psi & = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(1 - \tfrac{m}{2n})\Gamma(1 + \tfrac{m}{2n})} F(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}, \tfrac{1}{2}; \zeta^2) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
+\end{align*}
+\color{black}
+\subsubsection{Comparison with Ghate and Venkataramana}
+\begin{align*}
+\mu_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \lambda & = 1 - c \\
+\nu_\text{GV} & = 1 - \left\{\frac{k_2}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \mu & = c - a - b \\
+\lambda_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_2}{d}\right\} & \nu & = b - a
+\end{align*}
+The hyperelliptic curve in Section~4 is
+\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
+
+Dihedral case (Theorem~2):
+\begin{align*}
+\frac{k_1}{d} & = \frac{p}{2m} \\
+\frac{k_2}{d} & = \frac{p}{2m} \\
+\frac{k_3}{d} & = \frac{m - p}{2m}
+\end{align*}
+Note that $\lambda = p'/m$ with $p + p' = m$. The hyperelliptic curve is
+\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
+Cosines appear in Section~2.3: $x_j = \exp(2\pi i\,\tfrac{k_j}{d})$, and we work in the totally real field $\mathbb{Q}(\cos(\frac{2\pi}{m}))$.
+
+Airy case:
+\begin{align*}
+\frac{k_1}{d} & = \frac{1}{3} \\
+\frac{k_2}{d} & = \frac{1}{3} \\
+\frac{k_3}{d} & = \frac{1}{6},
+\end{align*}
+so $(k_1, k_2, k_3, d) = (2, 2, 1, 6)$, and the hyperelliptic curve is
+\[ y^6 = (x - \alpha_1)^2 (x - \alpha_2)^2 (x - \alpha_3). \]
 
@@
 \[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
-\color{black}
+\color{DarkBlue}
 
@@
 
+\section{The Airy equation}\label{airy-appendix}
+
+\subsubsection{Rewriting as a modified Bessel equation}
+We can distill the most interesting part of the Airy function by writing
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+where
+\begin{equation}\label{integral:mod-bessel}
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
+\begin{equation}\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
+\end{equation}
+In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
+
+%The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
+%\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
+%where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
+Like we did in equation~\ref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
+
+\begin{equation}\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
+\end{equation}
+
+\subsection{Asymptotic analysis}
+From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
+where the $\series{W}_\alpha\in\C[\![z^{-1}]\!]$ are formal power series in $z^{-1}$.
+From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+\begin{equation}\label{bessel-asymp}
+\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
+\end{equation}
+
+The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+which seem analogous to the trans-monomials above.
+Borel summation makes the analogy precise.
+We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
+This is an evidence of Theorem~\ref{thm:1}
+
+\subsection{Building a distinguished frame of analytic solution}
+\subsubsection{Going to the spatial domain}\label{spatial}
+%\subsubsection{The big idea}\label{big-idea}
+We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
+We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+
+It's tempting to differentiate both sides of this equation until we get
+\begin{equation}\label{diff-eq:spatial-mod-bessel}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
+\end{equation}
+which is easier to solve.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
+
+This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+We can see the regular singularities by moving the derivatives to the right:
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
+
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
+For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+We learned in Section~\ref{translation} that
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+%\textcolor{Magenta}{Show that $W_1$ is asymptotic to $\tilde{W}_1$!}
+%\color{Peru}
+%\begin{align*}
+%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
+%\end{align*}
+%\color{Sienna}
+%\begin{align*}
+%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
+%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
+%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
+%\end{align*}
+%\color{black}
+%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
+%%\begin{equation}\label{eqn:centered-mod-bessel}
+%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
+\]
+%%\end{equation}
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel} looks like
+\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
+\begin{equation}\label{diff-eq:hypergeom-pos}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
+\end{equation}
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
+In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+
+In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
+Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
+In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
+
+%\color{DodgerBlue}
+%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
+%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
+%where $\zeta_{-1} = 2\xi_{-1}$.
+This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
+In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
+\subsection{Borel regularity}\label{bessel-regularity}
+Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
+
+\begin{equation}
+\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
+\end{equation}
+Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
+%
+%\subsubsection{Borel sum of $\tilde{W}_1$}
+%
+%Let us first compute the Borel transform of $\tilde{W}_1$:
+%
+%
+%\begin{align*}
+%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
+%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
+%\end{align*}
+
+Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
+
+\begin{align*}
+\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
+&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
+&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
+\end{align*}
+
+Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
+therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
+In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
+
+Similarly, if we consider the formal power series
+
+\begin{equation}
+\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
+\end{equation}
+
+analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
+
+\subsection{Contour argument for the Airy function}\label{contour-argument}
+Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
+Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
+\begin{equation}\label{integral:mod-bessel-zeta}
+K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+\end{equation}
+For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{center}
+\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
+{\small The contour $\gamma_1$ in the $\zeta$ plane.}
+\end{center}
+
+From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
+\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
+so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
+\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
+
+In addition to the solutions $v_1$ and $v_{-1}$ from Section~\ref{pos-root}\,--\, \ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
+\begin{alignat*}{2}
+g_1 &\;=\;& & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi_1\big) \\
+g_{-1} &\;=\;&  & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi_1\big),
+\end{alignat*}
+given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
+
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
+so we have
+\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
+The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
+The solution $g_1$, in contrast, is non-meromorphic at $\zeta = 1$.
+Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,v_1$,
+as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
+Hence,
+\begin{align*}
+K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} v_1\;d\zeta \\
+e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} v_1\;d\zeta \\
+e^z K & = \tfrac{i}{2} \laplace_{\zeta_1} v_1,
+\end{align*}
+just as we found in Section~\ref{bessel-regularity}.
+\subsection{Another solution}
+Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
+\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
+The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+
+To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
+\[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
+of equation~\ref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
+
+In summary, the contour integration method of solving equation~\eqref{eqn:mod-bessel} is associated with the basis
+\begin{align*}
+g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
+g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
+\end{align*}
+of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
+These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
+
+The Laplace transformation method of solving equation~\eqref{eqn:mod-bessel}, on the other hand, is associated with the basis
+\begin{alignat*}{2}
+v_{-1} &\;=\;& (1-\xi)^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
+v_1 &\;=\:& \xi^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
+\end{alignat*}
+given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
+
+Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
+\begin{alignat*}{3}
+v_{-1} &\;=\;&\tfrac{1}{\sqrt{3}}\,g_{-1} &\;+\;& \tfrac{1}{2}\,v_1 \\
+v_1 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_{1} &\;+\;& \tfrac{1}{2}\,v_{-1}.
+\end{alignat*}
+Summing these identities, we see that
+\[ g_1 + g_{-1} = \tfrac{\sqrt{3}}{2}\,(f_1 + f_{-1}), \]
+giving the alternate decomposition
+\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
+
+\subsection{Comparison with other Airy examples}
+
+\subsubsection{Different Borel transform convention} In the physic literature it is common that authors adopt a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+It is also commun to consider formal power series in small parameters, like $\tilde{\Phi}(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ where $\hbar\to 0$ rather than formal series at $\infty$.
+Then the Borel transform of $\tilde{\Phi}$ is defined as $\tilde{\phi}(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
+In \cite{Diablerets}, the author studies, as example of resurgent functions, the Airy functions.
+His starting point are the formal solutions of Airy differential equation
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\end{align*}  
+where 
+\begin{align*}
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
+\end{align*}
+%Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
+Then, by applying the two definitions of the Borel transform $\mathcal{B}_{\textit{phys}}$ and $\mathcal{B}$, on the one hand we have  
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) 
+\end{align*}
+on the other hand, we find
+\begin{align*}
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
+\end{align*}
+%That ambiguity comes from the different definitions of Borel transforms: 
+%\begin{align*}
+%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
+%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
+%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
+%\end{align*}
+
+and comparing the two solutions we notice that up to the factor of $\delta$
+
+\begin{equation}\label{Borel-W12}
+\mathcal{B}(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)
+\end{equation}
+More generally, if $\tilde{\Phi}(z)\in z^{-1}\C[\![z^{-1}]\!]$, i.e. it has no constant term, then
+
+\begin{equation}
+\frac{d}{d\zeta}\circ\mathcal{B}_{\textit{phys}}\tilde{\Phi}=\mathcal{B}\tilde{\Phi}.
+\end{equation}
+In particular, $\frac{d}{d\zeta}\circ\mathcal{B}_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
+
+%Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
+We want to compare $v_1$ with the \textit{physic} Borel transform $\mathcal{B}_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
+%
+%\begin{align*}
+%\mathcal{B}_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
+%&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
+%&=\frac{1}{2\pi}\zeta^{1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right) 
+%\end{align*}
+%
+%Now taking the $-1$- derivative of $v_1(\zeta)$ we get
+%
+%\begin{align*}
+%\partial_\zeta^{-1} v_1&=\frac{1}{\Gamma(1)}\int_0^{\zeta}(\zeta-\zeta') v_1(\zeta')d\zeta'\\
+%&=\int_0^{\zeta}(\zeta-\zeta') \zeta'^{-1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta'}{2}\right)d\zeta'\\
+%&=\frac{\Gamma(1/2)}{\Gamma(3/2)}\zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)\\
+%&=2 \zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)
+%\end{align*}
+
+\subsubsection{Integral formula for hypergeometric functions}
+
+In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
+
+He considers the formal power series  
+\[\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
+such that
+\begin{align*}
+\tilde{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
+\tilde{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
+\end{align*} 
+are formal solutions of the Airy equation. Notice that compared to Marino's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
+
+By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\tilde{\Phi}_{\pm}$ as a convolution product:
+
+\begin{align*}
+\hat{\phi}_+(\zeta):=\mathcal{B}\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\mathcal{B}\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
+\end{align*}
+ where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$.
+
+%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
+%
+%\begin{align*}
+%\tilde{\phi}_{+}(\zeta)&=\mathcal{B}\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
+%\tilde{\phi}_{-}(\zeta)&=\mathcal{B}\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
+%\end{align*}
+%which up to a constant factor for $\delta$, they agree with our results.
+
+Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
+
+\begin{align*}
+\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
+&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
+&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
+\end{align*}
+where in the last step we use the Euler formula for hypergeometric functions \footnote{The Euler formula is \begin{equation}\label{Euler formula}
+{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
+\end{equation}}. Then, by taking derivatives we recover $\hat{\phi}_{\pm}(\zeta)$:
+
+\begin{align*}
+\hat{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
+\hat{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)
+\end{align*} 
+and up to a multiplicative constant they match our computations for $\mathcal{B}(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
+The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
+Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
+Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see Lemma 6.106 \cite{MS}).
+%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
+
+\subsubsection{Comparison with exact WKB}
+
+Kawai and Takei study the WKB analysis of the Airy--type Schrodinger equation
+
+\begin{equation}
+\label{WKB_Airy} 
+\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
+\end{equation}
+as $\eta\to\infty$.
+They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
+In the coordinate $t=\frac{3}{2}yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
+\begin{align*}
+\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
+\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
+\end{align*}
+where $s=t/2+1/2$. 
+The same hypergeometric functions have been computed in Section \ref{Airy} as the Borel transform of the formal solutions of the Airy equation
+
+\begin{equation}
+\label{Airy}
+\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
+\end{equation}
+
+Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
+So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
+
+First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
+\begin{align*}
+\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
+\end{align*} 
+then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
+\begin{align*}
+\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
+\end{align*}
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
+\begin{equation}
+\label{eq_Phi}
+\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
+\end{equation}
+
+\begin{proof}
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
+&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
+&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
+&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
+&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
+\end{align*}
+\end{proof}
+Now rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
+\begin{align*}
+&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{2}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta x^{-1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
+%&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
+&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-1\right]\Phi=0
+\end{align*}
+
+therefore $\Phi(q)$ is a solution of the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
+
+\begin{remark}
+The change of coordinate $q=\frac{2}{3}\eta x^{3/2}$ is not casual: recall that the WKB ansatz for a Schrodinger type equation is
+
+\begin{equation}
+\psi(x,\eta)=\exp\left(\int_{x_0}^xS(\eta,x')dx'\right)
+\end{equation} 
+ and $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. In addition, for the Airy--type Schrodinger equation 
+ \begin{align*}
+ S_{-1}^2=x
+ \end{align*}
+hence, up to a choice of sign for the square root
+\begin{align*}
+q&=\frac{2}{3}\eta x^{3/2}=\eta\int_0^x\sqrt{x'}dx'=\eta\int_{0}^xS_{-1}(x')dx'.
+\end{align*}
+We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.
+\end{remark}
+
 \bibliographystyle{plain}
 \bibliography{airy-resurgence}
+
 \end{document}

### 2023-02-26 exp-resurgence.tex
updates

@@
 where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+
+\subsubsection{Asymptotic analysis}
 
@@
 \color{black}
+
+\subsection{Modified Bessel}
+
 \subsubsection{Lifting to a countable cover}
@@
 The integral converges when $z$ is in the right half-plane.
-We get formula~\ref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
-
-When $\nu$ goes to $0$, formula~\ref{integral:mod-bessel-lifted} becomes
-\[ K_\nu(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
+We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
+
+When $\nu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
+\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
 Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
 \begin{align*}
-K_\nu(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
+K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
 & = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
@@
 with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
-\subsubsection{Link to dihedral triangulations}
-Here are the local normal forms of Kummer's first and second solutions. In the table, $[\bullet]$ denotes a local holomorphic function of order $0$ \cite[identities 15.8.2--4]{dlmf}, and
-\begin{align*}
-a' & = a+(1-c) \\
-b' & = b+(1-c) \\
-c' & = 2-c
-\end{align*}
-\begin{center}
-\begin{tabular}{c|c|c|c}
-Function & $0$ & $1$ & $\infty$ \\ \hline
-$F(a, b, c, \xi)$ & $[\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$ \\
-$\xi^{1-c} F(a', b', c', \xi)$ & $\xi^{1-c} [\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$
-\end{tabular}
-\end{center}
-
-For example, at $\zeta = \infty$, the function
-\[ u_{-1} = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, 1 - \tfrac{1}{2} \zeta_{-1}) \]
-is slight, with normal form $(1/\zeta_{-1})^{1 - m/n} f_1 + (1/\zeta_{-1})^{1 + m/n} f_2$~\cite[identity~15.8.3]{dlmf}.
-At $\zeta = 1$, it's holomorphic with order $0$.
-At $\zeta = -1$, it has the form $h + \zeta_{-1}^{-1/2} f$, where $h$ is holomorphic with order $0$.
-
-On the other hand, the function
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}) \]
-is slight at $\zeta = \pm 1$ with order $-\tfrac{1}{2}$, and slight at $\infty$ with order $1 - \tfrac{m}{n}$.
-
-Hence, the ratio $u_{-1} / v_{-1}$ looks like a holomorphic multiple of $\zeta_1^{1/2}$ near $\zeta = 1$, a holomorphic function plus a holomorphic multiple of $\zeta_{-1}^{1/2}$ near $\zeta = -1$, and a holomorphic function plus a holomorphic multiple of $(1/\zeta_{-1})^{2m/n}$ near $\zeta = \infty$.
-This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.
-
-\color{ForestGreen}
-Let's try to get the small tetrahedral tiling by setting
-\begin{align*}
-1 - c & = \tfrac{1}{3} \\
-c - a - b & = \tfrac{1}{3} \\
-b - a & = \tfrac{1}{2},
-\end{align*}
-so $(a, b, c) = (-\tfrac{1}{12}, \tfrac{5}{12}, \tfrac{2}{3})$. The general hypergeometric equation is
-\begin{align*}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + \big[c - (a+b+1)\xi_1\big] \tfrac{\partial}{\partial \xi_1} - ab\right] & v = 0 \\
-\left[-\tfrac{1}{2}\zeta_1 (1 + \tfrac{1}{2}\zeta_1) 4 \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + \big[c + \tfrac{1}{2}(a+b+1)\zeta_1\big] (-2) \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
-\left[-\zeta_1 (2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 - \big[2c + (a+b+1)\zeta_1\big] \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
-\left[(1 - \zeta)(1 + \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[2c + (a+b+1)(\zeta - 1)\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[(c - a - b) + (c - 1) + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[\mu - \lambda + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[\big[\tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta\big] \tfrac{\partial}{\partial \zeta} - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
-\left[\tfrac{\partial}{\partial \zeta} \circ \big[ \tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta \big] + 2\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
-\left[\big[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) + 4 \tfrac{\partial}{\partial \zeta} \circ \zeta - 2 \big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ (a+b+1) - ab \big]\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ {-}1 + a + b - ab \big]\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta - (a-1)(b-1)\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta^2 - 1) + (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (a+b-3) \tfrac{\partial}{\partial \zeta} \circ \zeta + (a-1)(b-1)\right] & v = 0,
-\end{align*}
-For the tetrahedral tiling, we get
-\[ \left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big(\zeta^2 - 1\big) - \tfrac{8}{3} \tfrac{\partial}{\partial \zeta} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\right] v = 0, \]
-which comes from the integral equation
-\[ \left[\big(\zeta^2 - 1\big) - \tfrac{8}{3}\,\fracderiv{-1}{\zeta}{\alpha} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\,\fracderiv{-2}{\zeta}{\alpha}\right] v = 0. \]
-In the frequency domain, this equation becomes
-\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
-\color{black}
-\color{SpringGreen}
-Set
-\[ \laplace_{\zeta, \alpha} v = \int_\Lambda e^{-zf}\,p\,du. \]
-Observe that
-\[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] \int_\Lambda e^{-zf}\,p\,du = \int_\Lambda e^{-zf}\,(f^2 - 1)p\,du \]
-and
-\begin{align*}
-z^{-1} \tfrac{\partial}{\partial z} \int_\Lambda e^{-zf}\,p\,du & = z^{-1} \int_\Lambda e^{-zf}\,(-fp)\,du \\
-& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')q_1\,du \\
-& = \int_\Lambda e^{-zf}\,f'q_1\,du
-\end{align*}
-where $q_1' = -fp$.
-and
-\begin{align*}
-z^{-2} \int_\Lambda e^{-zf}\,p\,du
-& = -z^{-2} \int_\Lambda e^{-zf}\,(-zf')p_1\,du \\
-& = z^{-1} \int_\Lambda e^{-zf}\,f'p_1\,du \\
-& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')p_2\,du \\
-& = \int_\Lambda e^{-zf}\,f'p_2\,du \\
-\end{align*}
-with $p_1' = p$ and $p_2' = f'p_1$.
-\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
-\color{black}
-
-\color{orange}
-In DLMF notation, let's try
-\begin{align*}
-u_1 & = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \xi_{-1}) \\
-& = w_1(\xi_{-1}) \\
-u_{-1} & = w_3(\xi_{-1}) \\
-v_{-1} & = w_2(\xi_{-1}) \\
-v_1 & = -i\sqrt{2}\,\zeta_1^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
-& = (-\tfrac{1}{2}\zeta_1)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
-& = (1 - \tfrac{1}{2}\zeta_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \tfrac{1}{2}\zeta_{-1}) \\
-& = (1 - \xi_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \xi_{-1}) \\
-& = w_4(\xi_{-1}),
-\end{align*}
-where $\xi_{-1} = \tfrac{1}{2}\zeta_{-1}$.
-
-\color{RoyalBlue}
-Let's guess that we're working with the map $\phi / \psi$ with
-\begin{align*}
-\phi & = \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{2} - \tfrac{m}{2n})\Gamma(\tfrac{1}{2} + \tfrac{m}{2n})}\,(\mp \zeta)\,F(1 - \tfrac{m}{2n}, 1 + \tfrac{m}{2n}, \tfrac{3}{2}; \zeta^2) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
-\psi & = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(1 - \tfrac{m}{2n})\Gamma(1 + \tfrac{m}{2n})} F(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}, \tfrac{1}{2}; \zeta^2) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
-\end{align*}
-\color{black}
-\subsubsection{Comparison with Ghate and Venkataramana}
-\begin{align*}
-\mu_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \lambda & = 1 - c \\
-\nu_\text{GV} & = 1 - \left\{\frac{k_2}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \mu & = c - a - b \\
-\lambda_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_2}{d}\right\} & \nu & = b - a
-\end{align*}
-The hyperelliptic curve in Section~4 is
-\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
-
-Dihedral case (Theorem~2):
-\begin{align*}
-\frac{k_1}{d} & = \frac{p}{2m} \\
-\frac{k_2}{d} & = \frac{p}{2m} \\
-\frac{k_3}{d} & = \frac{m - p}{2m}
-\end{align*}
-Note that $\lambda = p'/m$ with $p + p' = m$. The hyperelliptic curve is
-\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
-Cosines appear in Section~2.3: $x_j = \exp(2\pi i\,\tfrac{k_j}{d})$, and we work in the totally real field $\mathbb{Q}(\cos(\frac{2\pi}{m}))$.
-
-Airy case:
-\begin{align*}
-\frac{k_1}{d} & = \frac{1}{3} \\
-\frac{k_2}{d} & = \frac{1}{3} \\
-\frac{k_3}{d} & = \frac{1}{6},
-\end{align*}
-so $(k_1, k_2, k_3, d) = (2, 2, 1, 6)$, and the hyperelliptic curve is
-\[ y^6 = (x - \alpha_1)^2 (x - \alpha_2)^2 (x - \alpha_3). \]
-
-\subsection{Modified Bessel}
-
-\textcolor{magenta}{[For this, we lift to a countable cover; see {\tt airy-resurgence.tex}, currently \S 6.4]}
 
@@
 We can distill the most interesting parts of the hyper-Airy function by writing
-\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
+\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K^{(k)}\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
 where
 \begin{equation}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
+K^{(k)}(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
 \end{equation}
@@
 \begin{equation}\label{eqn:higher-Airy}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
-\end{equation}
-The sub-leading coefficients are the triangular numbers
-\[ c_n^{(1)} = \frac{n(n-1)}{2}. \]
-\color{DarkCyan}
+\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] K^{(k)} = 0.
+\end{equation}
+The sub-leading coefficients are 
+\[ c_n^{(1)} = \frac{n-1}{2}. \]
+
 The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
-\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,(n+1)^{\underline{k+2}} \]
+\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,\frac{\Gamma(n+2)}{\Gamma(n-k)} \]
 in terms of the polynomials
 
-\begin{align*}
-b_n^{(2)} & = & \tfrac{1}{24} \\
-b_n^{(3)} & = & \tfrac{1}{48} n \\
-b_n^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
-b_n^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
-b_n^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440}. 
-\end{align*}
+\begin{tabular}{llllllllllll}
+$b_n^{(2)}$ & = & $\frac{1}{24}$ \\
+$b_n^{(3)}$ & = & $\frac{1}{48} n$ \\
+$b_n^{(4)}$ & = & $\frac{73}{5760} n^2$ & + & $\frac{1}{1152} n$ & - & $\frac{1}{2880}$ \\
+$b_n^{(5)}$ & = & $\frac{11}{1280} n^{3}$ & + & $\frac{1}{768} n^{2}$ & - & $\frac{1}{1920} n$ \\
+$b_n^{(6)}$ & = & $\frac{3625}{580608} n^{4}$ & + & $\frac{61}{41472} n^{3}$ & - & $\frac{181}{322560} n^{2}$ & - & $\frac{1}{41472} n$ & + & $\frac{1}{181440}$. 
+\end{tabular}
+
+\vspace{5mm}
 
@@
 The last coefficient can be written as
-\[ c_n^{(n-1)} = \left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, \]
+\[ c_n^{(n-1)} =\left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, 
+\]
 giving
-\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
+\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ \Gamma(n+2). \]
+
+\subsubsection{Building a frame of analytic solutions}
+
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:higher-Airy}.
+We'll succeed when $\alpha^{n-1} - 1 = 0$, and we'll see that $K^{(k)}$ is a scalar multiple of $\laplace_{\zeta, \alpha_k} v_k$ with $\alpha_k=e^{2\pi i \tfrac{k}{n-1}}$.
+
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha_k} v$ satisfies the differential equation~\eqref{eqn:higher-Airy} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-higher-Airy}
+\left[ \big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \partial_{\zeta,\alpha_k}^{-1}\circ \zeta^{n-2} - c_n^{(2)} \partial_{\zeta,\alpha_k}^{-2} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \partial_{\zeta,\alpha_k}^{-(n-1)} \right] v = 0.
+\end{equation}
+
+Since equation \eqref{eqn:higher-Airy} is written in form \eqref{eqn:standard ODE} and the coefficient $c_n^{(1)}$ is explicitly known, we deduce that equation \eqref{int-eq:spatial-higher-Airy} admits a slight solution at $\zeta={\alpha_k} $ of order $\tau_{\alpha_k}=\frac{1}{2}$.
+In particular, $v$ is a solution of \eqref{int-eq:spatial-higher-Airy} if and only if it solves the following differential equation
+
+\begin{equation}\label{diff-eq:spatial-higher-Airy}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \partial_{\zeta,\alpha_k}^{n-2}\circ \zeta^{n-2} - c_n^{(2)} \partial_{\zeta,\alpha_k}^{n-3} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \right] v = 0.
+\end{equation}
+
+Using the Liebniz rule for the differential, we get
+
+\begin{itemize}
+\item $\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big]=\sum_{j=0}^{n-1} (n-1 j) v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]=(\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}v+ (n-1)^2\zeta^{n-2} \partial_\zeta^{n-2}v +...+(n-1)!
+v $
+\end{itemize}
+
 \color{DarkBlue}
@@
 
-\subsection{Building a distinguished frame of analytic solution}
+\subsection{Building a distinguished frame of analytic solutions}
 \subsubsection{Going to the spatial domain}\label{spatial}

### 2023-03-02 exp-resurgence.tex
updates

@@
 
-\title{Resurgence of the Airy function \\ and other exponential integrals}
+\title{Borel regularity for ODEs and exponential integrals}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 
-\color{Turquoise}
+\color{DarkTurquoise}
 Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
@@
 
+Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
+\begin{equation}\label{exp-int}
+I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
+\end{equation}
+where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
+For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
+\begin{equation}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
+\end{equation}
+where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
+Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+\begin{theorem}\label{thm:maxim} Let $N=1$.
+Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
+Then:
+\begin{enumerate}
+\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
+\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
+\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
+\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
+\begin{multline}\label{formula1}
+\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\end{multline}
+where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
+Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
+
+Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
+Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+\textbf{[We should explicitly spell out and check the conditions that make this possible.
+I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
+that converges in some disk $|\tau| < \varepsilon$.
+
+By the steepest descent method,
+%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
+\begin{align*}
+e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
+\end{align*}
+By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
+= 1$.}
+\begin{align*}
+e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
+These terms are crucial, however, for the convergence of the sum.
+To see why, consider their absolute sum $C_\text{exp}$.
+When $z \in [0, \infty)$,
+\begin{align*}
+C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
+& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
+& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
+\end{align*}
+which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
+
+This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
+We can, however, set aside any finite set of them.
+\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
+See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
+\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
+
+\color{Purple}
+For each cutoff $N$, the tail error \textbf{[check]}
+\begin{align*}
+\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
+& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
+& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
+& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
+& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
+& = \textbf{uh-oh!}
+\end{align*}
+\color{violet}
+is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
+\begin{align*}
+C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
+& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
+& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
+\end{align*}
+is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
+Call the right-hand side $\tilde{I}_\alpha$.
+We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
+\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
+\begin{align*}
+\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
+\end{align*}
+
+We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
+Recalling that $(2n - 1)!!
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
+
+Part~\eqref{int:resum-converges}: \begin{align*}
+\hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
+\end{align*}
+Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
+
+Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
+As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
+Hence, we have
+\begin{align*}
+I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
+& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
+\end{align*}
+Noticing that the right-hand side is a Laplace transform, we learn that
+\begin{equation}\label{thimble-difference}
+\hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
+\end{equation}
+\color{Aquamarine}
+In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{I}_\alpha$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
+[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
+Or something even simpler?]
+\color{black}
+
+We can rewrite our Taylor series for $\nu$ as
+\begin{align*}
+\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
+& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
+\begin{align*}
+\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
+& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
+& = \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha.
+\end{align*}
+We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
+We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
+
+Theorem~\ref{thm:frac-diff-borel} tells us that
+\begin{align*}
+\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\end{align*}
+It follows, from our conclusion above, that
+\begin{equation}\label{shifted-resum-valid}
+\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\end{equation}
+Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
+\begin{align*}
+I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
+& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
+\end{align*}
+as we claimed.
+
+Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
+\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
+Rewriting equation~\eqref{thimble-difference} as
+\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
+we can see that
+\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
+The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
+\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
+Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
+\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
+\end{proof}
+
 \section{Examples}
@@
 \subsubsection{Asymptotic analysis}
+
+\textcolor{lime}{[Use Poincar\'e algorithm to compute the asymptotic expansion]}
 
@@
 
-\color{Turquoise}
+\color{DarkTurquoise}
 \subsubsection{Borel regularity}\label{bessel-regularity-AL}
@@
 
-\subsubsection{Lifting to a countable cover}
-Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
+The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
+
+\begin{equation}\label{eqn:mod-bessel}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
+\end{equation}
+
+and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf})
+
+\begin{align*}
+I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
+K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]
+\end{align*}
+
+where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
+
+\begin{figure}[h]
+\caption{Add figure path $\Omega$}
+\end{figure}
+
+On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results:
+
+\begin{itemize}
+ \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
+ \begin{align*}
+ \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
+ \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
+\end{align*}   
+ \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\mathcal{L}_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
+
+\begin{align*}
+v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{1}\big)\\
+v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{align*}
+\item \textbf{Borel regularity} \textcolor{Lime}{[Check with Aaron how to phrase it]} 
+\end{itemize}
+
+On the other hand, the contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
+
+\subsubsection{Lifting to a countable cover}\label{countable-cover}
+Formula~\eqref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
 Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
@@
 \end{align}
-For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
+For any $\mu \in \C \smallsetminus \Z$, 
 \begin{align}
-\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
+\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
+\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
+\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
 \end{align}
@@
 The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
-
-When $\nu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
+We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
+
+When $\mu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
 \[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
@@
 \begin{equation}\label{diff-eq:spatial-higher-Airy}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \partial_{\zeta,\alpha_k}^{n-2}\circ \zeta^{n-2} - c_n^{(2)} \partial_{\zeta,\alpha_k}^{n-3} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \right] v = 0.
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-2}\circ \zeta^{n-2} - c_n^{(2)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \right] v = 0.
 \end{equation}
@@
 
-\begin{itemize}
-\item $\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big]=\sum_{j=0}^{n-1} (n-1 j) v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]=(\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}v+ (n-1)^2\zeta^{n-2} \partial_\zeta^{n-2}v +...+(n-1)!
-v $
-\end{itemize}
-
-\color{DarkBlue}
+\color{Peru}
+
+\begin{align*}
+\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big]v&=\sum_{j=0}^{n-1} \binom{n-1}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]\\
+&=(\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}v+ (n-1)^2\zeta^{n-2} \partial_\zeta^{n-2}v +\\
+&\qquad \sum_{j=2}^{n-1} \binom{n-2}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-1)! v\\
+\big(\tfrac{\partial}{\partial {\zeta}}\big)^{n-2}\circ \zeta^{n-2}v&=\zeta^{n-2}\partial_\zeta^{n-2}v+\sum_{j=1}^{n-3} \binom{n-2}{j} v^{(n-j-2)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-2)!v \\
+\big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3}v&=\sum_{j=0}^{n-4} \binom{n-3}{j} v^{(n-j-3)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-3)!v\\
+\tfrac{\partial}{\partial \zeta} \circ\zeta v&=\zeta \partial_\zeta v+v
+\end{align*}
+
+\color{black}
+\begin{equation}\label{diff-eq:spatial-mod-higher-Airy}
+\left[ (\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}+ \big[(n-1)^2-c_n^{(1)}\big]\zeta^{n-2} \partial_\zeta^{n-2}+...+\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big] \right] v = 0.
+\end{equation}
+
+Let's find a solution of equation~\ref{diff-eq:spatial-mod-higher-Airy} which is slight and locally integrable at $\zeta = 1$.
+Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
+In this coordinate, equation~\ref{diff-eq:spatial-mod-higher-Airy} looks like
+\begin{multline}\label{diff-eq:spatial-mod-higher-Airy-1}
+\left[\zeta_1(n-1+...+(n-1)\zeta_1^{n-3} + \zeta_1^{n-2}) \big(\tfrac{\partial}{\partial \zeta_1}\big)^{n-1} + \big[(n-1)^2-c_n^{(1)}\big](1+\zeta_1)^{n-2} \tfrac{\partial}{\partial \zeta_1}^{n-2} + ...
+\right.\\
+ \left. +\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big]\right] v = 0.
+\end{multline}
 
@@
 \begin{equation}\label{eqn:reg-higher3}
-\left[\frac{\partial^3}{\partial z^3}+1+\frac{6}{z}\frac{\partial^2}{\partial z^2}-\frac{35}{8}\frac{1}{z^2}\frac{\partial}{\partial z}+\frac{315}{16}\frac{1}{z^3}\right]\varphi=0
-\end{equation}
-
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-higher3}.
-We'll succeed when $\alpha^3 + 1 = 0$.%, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-higher3} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:higher3}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:higher3}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha\in z^{-\tau_\alpha}\C[\![z^{-1}]\!]$, so we further decompose
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-with $W_\alpha\in\C[\![z^{-1}]\!]$.
-\color{Peru}
-\begin{align*}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-\end{align*}
-\color{Sienna}
-\begin{align*}
-\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-\end{align*}
-\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+\left[\frac{\partial^3}{\partial z^3}+1+\frac{3}{2z}\frac{\partial^2}{\partial z^2}-\frac{5}{16}\frac{1}{z^2}\frac{\partial}{\partial z}+\frac{5}{32}\frac{1}{z^3}\right]\varphi=0
+\end{equation}
+
+and going to the spatial domain, $\mathcal{L}_{\zeta,\alpha_k}$ satisfies equation~\eqref{eqn:reg-higher3} if and only if $v$ satisfies
+
+\begin{equation}\label{diff-eq:spatial-higher3}
+\left[(\zeta^3-1)\partial_\zeta^3-\frac{15}{2}\zeta^2\partial_\zeta^2-\frac{187}{16}\zeta\partial_\zeta+\frac{81}{32}\right]\varphi=0
+\end{equation}
+
+Let's find a solution of equation~\eqref{diff-eq:spatial-higher3} which is slight and locally integrable at $\zeta = 1$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
+In this coordinate, equation~\eqref{diff-eq:spatial-higher3} looks like
 \begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\ref{diff-eq:spatial-mod-bessel} the same.
-
-\color{DodgerBlue}
-If we'd followed the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we would've arrived at the hypergeometric equation
-\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we'd get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-
-\color{black}
+\left[\zeta_1(3 + 3\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^3 - \frac{15}{2}(1 + 2\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 -\frac{187}{16}(1+\zeta_1)\tfrac{\partial}{\partial \zeta_1} + \frac{81}{32}\right] v = 0.
+\end{equation}
+
+\textcolor{DarkBlue}{[Find solutions using hypergeometric functions]}
+
+\subsubsection{Contour argument for higher Airy of degree $3$}
 
 \subsection{Generalized Airy}
+
+In \cite{Reid} \cite{Drazin-Reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
+They are defined as countour integral (\cite{DLMF} \S 9.13(ii))
+
+\begin{align*}
+\mathrm{A}_k(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
+\mathrm{B}_0(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
+\mathrm{B}_k(z,p)&=\int_{\gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
+\end{align*}
+where the countours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig.countours}
+
+\begin{figure}
+%\includegraphics[scale=0.5]{countours}
+\end{figure}
+
+Each generalize Airy functions is a solution of
+
+\begin{equation}
+\left[\partial_z^3-z\partial_z+(p-1)\right]f(z,p)=0
+\end{equation}
+
+and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
+
+We define the following exponential integral: let $p\geq 0$, $f(t)=\tfrac{t^3}{3}-t$ and $\nu_p=\tfrac{dt}{t^p}$.
+The critical points of $f$ are $\pm\tfrac{2}{3}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
+
+\begin{equation}
+I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p}
+\end{equation}
+
+where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}).
+In particular, $I_{+}(z,p)=z^{\tfrac{p-1}{3}}\mathrm{A}_1(z^{2/3},p)$:
+
+\begin{align*}
+I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p} &\\
+&=\frac{z^{(p-1)/2}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\tfrac{s^3}{3}-z^{-1/3}s)}\frac{ds}{s^p} & t=z^{-\tfrac{1}{3}}s\\
+&=\frac{z^{(p-1)/3}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\tfrac{s^3}{3}-z^{2/3}s\right)}\frac{ds}{s^p} & \\
+&=z^{(p-1)/3}\mathrm{A}_1(z^{2/3},p)
+\end{align*}
+
+It follows that $I_+(z)$ is a solution of
+
+\begin{equation}\label{eq:I}
+\left[\partial_z^3-\frac{4}{9}\partial_z+\frac{2-p}{z}\partial_z^2-\frac{4(1-p)}{9z}-\frac{1+3p-3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
+\end{equation}
+
+From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
+\begin{equation}
+\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-\tfrac{2}{3}z}z^{-1/2}\tilde{W}_2(z)+U_3e^{\tfrac{2}{3}z}z^{-1/2}\tilde{W}_3(z)
+\end{equation}
+
+where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
+
+\begin{multline}\label{w1}
+\left[\partial_z^3-\frac{4}{9}\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6p^2+11p-6}{z^3}\right]\tilde{W}_1(z)=0
+\end{multline}
+
+\begin{multline}\label{w2}
+\left[\partial_z^3-2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
+\left.-\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
+\end{multline}
+
+\begin{multline}\label{w3}
+\left[\partial_z^3+2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
+\left.+\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
+\end{multline}
+Let us first study equation \eqref{w1}: its Borel transform is
+
+\begin{multline*}
+-\zeta^3\tilde{w}_1+\frac{4}{9}\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
++\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
+\end{multline*}
+
+We differentiate three times, getting
+
+\begin{multline*}
+\left(\frac{4}{9}\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(\frac{4}{3}-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\tilde{w}_1'(\zeta)+\\
++\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
+\end{multline*}
+
+we set $y=\tfrac{9}{4}\zeta^2$
+
+%\begin{multline}
+%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
+%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
+%\end{multline}
+\begin{multline}\label{eq:hw1}
+y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left(\left(p-\frac{13}{2}\right)y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{1}{3}(10-p)p\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
++\frac{1}{27}\left(p-\frac{5}{2}\right)\tilde{w}_1(y)=0
+\end{multline}
+
+which is a generalized hypergeomtric equation (~16.8.5 \cite{DLMF}) with parameters
+
+\begin{align*}
+\mathbf{a}_0=\left(\frac{3}{2}-\frac{p}{3};\frac{7}{6}-\frac{p}{3};\frac{5}{6}-\frac{p}{3}\right) & \qquad\qquad \mathbf{b}_0=\left(\frac{1}{2};\frac{3}{2}\right)
+\end{align*}
+
+therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)+R(\zeta)$ for some function $R(\zeta)$ which can be determined from the integral equation.
+
+Then we look at equation \eqref{w2}: its Borel transform is
+
+\begin{multline}
+-\zeta^3\tilde{w}_2(\zeta)-2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
++\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
+-\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
+-\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
+\end{multline}
+
+and taking three derivatives it simplifies to
+
+\begin{multline}
+\left[\left(\zeta^3+2\zeta^2+\frac{8}{9}\zeta\right)\partial_\zeta^3 +\frac{8}{3}\partial_\zeta^2+\left(\frac{17}{2}+p\right)\zeta\left(\zeta+\frac{4}{3}\right)\partial_\zeta^2+\right.\\
+\left.
+\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+\frac{2}{3}\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
+\end{multline}
+
+define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
+
+\begin{multline}\label{eq1}
+\left[y\left(y+\frac{4}{9}\right)^2\partial_y^3+2\left(\frac{3}{2}y+\frac{4}{3}+\frac{y}{2}\left(\frac{17}{2}+p\right)\right)\left(y+\frac{4}{9}\right)\partial_y^2+\left(\frac{2}{3}+\frac{y}{4}\left(\frac{17}{2}+p\right)\right)\partial_y\right.\\
+\left.+\frac{1}{4}\left(\frac{p^3}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(y+\frac{4}{9}\right)\partial_y+\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(y)=0
+\end{multline}
+
+which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
+
+\begin{multline}
+\left[t^2(1-t)\partial_t^3-t\left(\big(\frac{23}{4}+\frac{p}{2}\big)t-\frac{p}{2}-\frac{11}{4}\right)\partial_t^2-\left(-\frac{5}{8}-\frac{p}{4}+t\Big(\frac{887}{144}+\frac{17}{12}p+\frac{p^2}{12}\Big)\right)\partial_t +\right.\\
+\left. -\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(t)=0
+\end{multline}
+hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
+
+\begin{align*}
+\mathbf{a}=\left(\frac{5}{4}+\frac{p}{6};\frac{7}{12}+\frac{p}{6};\frac{11}{12}+\frac{p}{6}\right) & \qquad\qquad \mathbf{b}=\left(\frac{1}{2};\frac{5}{4}+\frac{p}{2}\right)
+\end{align*}
+
+and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
+The equation \eqref{w3} differes from \eqref{w2} for few signs: we find that its Borel transform is
+
+\begin{multline}
+-\zeta^3\tilde{w}_2(\zeta)+2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt+\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
++\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
++\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
+-\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
+\end{multline}
+
+and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
+$\hat{w}_3(\zeta)= c_3\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta-1\right)^2\right)$.
+In particular,
+
+\begin{equation}
+\hat{w}_3(\zeta)=C_{23}\hat{w}_2(\zeta-\tfrac{4}{3})
+\end{equation}
+
+\color{DarkTurquoise}
 
@@
 
+\section{Application of the integral formula}
+
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
+
+By general theory it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
+Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the contour argument and from the integral formula.
+When computed from the ODE, there is an ambiguity in the choice of the constant, while with the contour argument and the fractional integral formula the ambiguity is solved.
+We will see this for the modified Bessel equation.
+
+This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
+Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
+%In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
+\begin{lemma}\label{claim 2}
+The following formula holds true
+\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
+for any $\zeta\in [2/3,+\infty)$.
+\end{lemma}
+\begin{proof}
+In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
+Hence,
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
+\end{align*}
+Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
+
+\begin{lemma}\label{claim 3}
+For any $\zeta\in (-\infty,-2/3]$
+\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
+\end{lemma}
+\begin{proof}
+Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
+\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity \textbf{[DLMF~15.4.16]}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
+& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+
 \bibliographystyle{plain}

### 2023-03-03 exp-resurgence.tex
updates
I added exponential integrals introduction

@@
 \end{itemize}
-\color{DarkBlue}
+
 \subsection{Why does Borel resummation work?}
@@
 over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-\color{DarkBlue}
+\color{black}
 
@@
 [Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-\color{DarkBlue}
+
 \item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
@@
 
+\color{DarkBlue}
+
 \item \textbf{Being a thimble integral}
@@
 \begin{itemize}
-\item take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series
-\item see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform)
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular.
-\end{itemize}
-
+\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
+\begin{itemize}
+\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
+\end{itemize} 
+\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
+His proof is geometric [it may be useful to add it in Appendix].
+\item \textcolor{red}{We give an analytic proof analogous of Pham.}
+\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
+\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely the commutativity of the following diagram
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\begin{itemize}
+\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
+\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item A corollary of [Thm 4] is the fractional derivative formula.
+\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+\end{itemize}
+\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
+Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
+\end{itemize}
+
+\color{DarkGreen}
 Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.

### 2023-03-12 exp-resurgence.tex
Reflect proof of Theorem 2 in "Borel regularity"

@@
 In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-
+\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
+The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{diff-eq:reg-mod-bessel-AL}.
+The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
 \color{DarkTurquoise}
-\subsubsection{Borel regularity}\label{bessel-regularity-AL}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel-AL}
-
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
-
-\begin{align*}
-\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-
+\begin{quote}
+We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
+\begin{align*}
+v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
+& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
+\end{align*}
+In this case, $\tau = \tfrac{1}{2}$.
+\end{quote}
 \color{black}
 
+The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{diff-eq:reg-mod-bessel-AL}.
+The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
+We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+
+The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
+Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-3/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
+
+When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
+It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
+That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
+Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
+\subsubsection{Confirmation of Borel regularity}
+We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
+We found in Section~\textbf{[asymptotic analysis]} that
+\begin{align*}
+\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
+\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
+\end{align*}
+Computing
+\begin{align*}
+\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \mathcal{B}\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
+& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
+\end{align*}
+we see that $\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
+
+Through a similar calculation, we see that $\mathcal{B}\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
 \subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}

### 2023-03-12 exp-resurgence.tex
Fix equation references

@@
 \subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{diff-eq:reg-mod-bessel-AL}.
+The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
@@
 
-The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{diff-eq:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.

### 2023-03-12 exp-resurgence.tex
Replace double-struck brackets; suggest wording revisions

@@
 \label{formal solution}
-\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z }\C[\![z^{-\tau_j}]\!]
+\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
 \end{equation}
@@
 \color{black}
-
+The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
+\begin{align*}
+\borel \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
+1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
+z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
+\end{align*}
+In general, by linearity,
+\begin{align*}
+\mathcal{B}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+\end{align*}
+The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
+
+\color{DarkTurquoise}
 The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$ such that  \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
@@
 }, and by linearity
-
 \begin{align*}
@@
 \end{align*}
+\color{black}
 
@@
 However, there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic fucntions at the origin in $\C_{\zeta}$.
-These formal series are the so called Gevrey-$1$ series: \[\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C[\![z^{-1}]\!]_1\] is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+These formal series are the so called Gevrey-$1$ series:
+\[\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
+is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
 there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
@@
 \begin{lemma}
-Let $\tilde{\Phi}(z)\in\C[\![z^{-1}]\!]$. Then, $\tilde{\Phi}\in\C[\![z^{-1}]\!]_1$ is Gevrey-1 if and only if $\mathcal{B}(\tilde{\Phi})\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions. 
+Let $\tilde{\Phi}(z)\in\C \llbracket z^{-1} \rrbracket$.
+Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\mathcal{B}(\tilde{\Phi})\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
 \end{lemma}
@@
 
-If $\alpha\in\mathbb{R}\setminus\Z$ is not an integer, then $\mathcal{B}$ is an isomorphisms from Gevrey-$1$ formal power series $\C[\![z^{-\alpha}]\!]_1$ to the germs of holomorphic functions $\C{\zeta^{\alpha-1}}$, with inverse given by the formal Laplace transform.
-Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C[\![z^{-\alpha}]\!]_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
+If $\alpha\in\mathbb{R}\setminus\Z$ is not an integer, then $\mathcal{B}$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
+Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-\alpha} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
 \begin{align*}
@@
 \item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(z^n\tilde{\Phi}(z))=\partial_\zeta^n\tilde{\phi}(\zeta)$ 
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\mathcal{B}(z^n\tilde{\Phi}(z))=\partial_\zeta^n\tilde{\phi}(\zeta)$ 
 \item[(iv)] $\mathcal{B}\left(\partial_z^{n} \tilde{\Phi}(z)\right)=(-\zeta)^n\tilde{\phi}(\zeta)$, for every $n\geq 0$
 \item[(v)] $\mathcal{B}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}(\zeta)$
-\item[(vi)] if $\tilde{\Psi}(z)\in z^{-1}\C[\![z^{-1}]\!]$, then $\mathcal{B}(\tilde{\Phi}(z)\tilde{\Psi}(z))=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}(\zeta)=\mathcal{B}(\tilde{\Psi}(z))$.
+\item[(vi)] if $\tilde{\Psi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\mathcal{B}(\tilde{\Phi}(z)\tilde{\Psi}(z))=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}(\zeta)=\mathcal{B}(\tilde{\Psi}(z))$.
 \end{itemize}
@@
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C[\![z^{-1}]\!]$ are formal power series in $z^{-1}$.
+where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
 From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
@@
 
-\subsection{Comparison with other Airy examples}
-
-\subsubsection{Different Borel transform convention} In the physic literature it is common that authors adopt a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
+\subsection{Comparison with other treatments of the Airy equation \\ \textcolor{DarkTurquoise}{Comparison with other Airy examples}}
+
+\subsubsection{Different Borel transform convention} Physicists often use a different version of the Borel transform:
+\begin{align*}
+\mathcal{B}_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+z^{-n} & \mapsto \frac{\zeta^n}{n!}.
+\end{align*}
+This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
+It's sometimes convenient to $\mathcal{B}_\textit{phys}(f) = \borel(z^{-1} f)$.
+
+For problems involving a small parameter $\hbar$ rather than a large parameter $z$, physicists also define
+\begin{align*}
+\mathcal{B}_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+\hbar^n & \mapsto \frac{\zeta^n}{n!}.
+\end{align*}
+From a combinatorial perspective, this is just the transformation that sends an ordinary generating function to the corresponding exponential generating function.
+
+In \cite{Diablerets}, the author studies the Airy functions as example of resurgent functions. He starts with the formal trans-monomial solutions of Airy equation:
+
+\color{DarkTurquoise}
+In the physic literature it is common that authors adopt a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
 It is also commun to consider formal power series in small parameters, like $\tilde{\Phi}(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ where $\hbar\to 0$ rather than formal series at $\infty$.
@@
 His starting point are the formal solutions of Airy differential equation
+\color{black}
 \begin{align*}
@@
 \end{equation}
-More generally, if $\tilde{\Phi}(z)\in z^{-1}\C[\![z^{-1}]\!]$, i.e. it has no constant term, then
+More generally, if $\tilde{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
 

### 2023-03-12 exp-resurgence.tex
updates

--- 2023-03-12 exp-resurgence.tex
@@
 \begin{enumerate}
-\item Thinking of $z$ as a ``frequency variable,'' we take the formal inverse Laplace transform of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
+\item Thinking of $z$ as a ``frequency variable,'' we take the formal inverse Laplace transform (also known as Borel transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
 \item With luck, $\series{\phi}$ has a positive radius of convergence.
@@
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+By definition, the Borel sum is asymptotic to $\tilde{\Phi}$
 \end{enumerate}
-The Borel summation process is summarized in the following diagram.
+
+The Borel summation process is summarized in the following diagram:
 \begin{center}
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail]\arrow[rr,red,dashed,"\parbox{15mm}{\footnotesize asymptotics}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi}(\zeta) \arrow[ll, mapsto, "\text{sum}"] 
+\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
 \end{tikzcd}
@@
 
-\begin{itemize}
-\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$. For example\ldots}
-\begin{itemize}
-\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
-\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
-\item Feynman diagram series?
-\end{itemize}
-\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-\begin{itemize}
-\item \done{Borel summation work in three steps.
+we start from the upper-right corner with the formal solution $\tilde{\Phi}$, then, moving clockwise, we take the Borel transform $\mathcal{B}$ which produces a germ of holomorphic function at the origin.
+If we can sum it and its sum $\hat{\phi}$ has a controlled behaviour at infinity, we can take the Laplace transform $\hat{\Phi}=\mathcal{L}_b^{\theta}\hat{\phi}$ which produces a holomorphic function asymptotic to $\tilde{\Phi}$ in a given half plane.
+A priori it is not guaranteed that $\hat{\Phi}$ solves our original problem, as different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+However, in many cases, it picks correctly, producing an actual solution to your problem.
+
+The question of how that happens is the starting point for this paper.
+
+In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.
+
+%\color{gray}
+%\begin{itemize}
+%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
+For example\ldots}
+%\begin{itemize}
+%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
+%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
+%\item Feynman diagram series?
+%\end{itemize}
+%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
+%\begin{itemize}
+%\item \done{Borel summation work in three steps.
 First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
-\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
+%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
 By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
-\item {[Draw the square!]}
-\end{itemize}
-\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-\item In many cases, it picks correctly, producing an actual solution to your problem.
-\begin{itemize}
-\item The question of how that happens is the starting point for this paper.
-\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+%\item {[Draw the square!]}
+%\end{itemize}
+%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+%\item In many cases, it picks correctly, producing an actual solution to your problem.
+%\begin{itemize}
+%\item The question of how that happens is the starting point for this paper.
+%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
 For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-\end{itemize}
-\end{itemize}
+%\end{itemize}
+%\end{itemize}
+%\color{black}
 \subsection{A new perspective: Borel regularity}
-\begin{itemize}
-\item The central goal of this paper is to present a new perspective on Borel summation which helps explain why it works for at least two kinds of problems.
-\begin{itemize}
-\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-\item The second problem is solving a certain kind of ODE.
-\item These two problems are closely linked.
+
+The central goal of this paper is to present a new perspective on Borel summation which helps explain why it works for at least two kinds of problems: 
+\begin{enumerate}
+\item the first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral} such as
+
+\begin{equation}
+\int_{\Lambda}\exp\big[-z(\tfrac{1}{3}u^3-\tfrac{1}{4}u)\big] du
+\end{equation}
+\item the second problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled}. We will mainly focus on Poincar\'e rank $1$ ODEs. 
+\end{enumerate}
+
+These two problems are closely linked.
 By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
 Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-\end{itemize}
-\item Suppose you have a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $z$ goes to $\infty$ along a given ray.
-\item If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum is a new holomorphic function.
+
+Let us change perspective: we start from the upper-left corner of the diagram, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $z$ goes to $\infty$ along a given ray.
+
+\begin{center}
+\begin{tikzcd}
+& \text{problem} & \\
+\Phi \arrow[ru, no head, tail,swap,"\parbox{15mm}{\centering\footnotesize solves}"' ]\arrow[rrd,dashed,swap,"\parbox{15mm}{\centering\footnotesize asymptotics}"']& & \\
+\hat{\Phi} \arrow[rr,red,dashed,"\parbox{15mm}{\footnotesize asymptotics}"'] & & \series{\Phi} \arrow[dd, mapsto, "\mathcal{B}"] \\
+& & \\
+\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
+\end{tikzcd}
+\end{center}
+
+Reading the diagram clockwise, if $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
+Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
+We'll therefore call this process {\em Borel regularization}.
+We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
+
+The natural question is then about the relationship between $\hat{\Phi}$ and $\Phi$: we'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged, i.e.
+$\Phi$ is {\em Borel regular} if $\Phi=\hat{\Phi}$.
+
+Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+
 %%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
@@
 We'll call this process {\em Borel regularization}.
-\item Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
-We'll therefore call this process {\em Borel regularization}.
+\begin{itemize}
+\item 
 \item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
@@
 \begin{equation}\label{eqn:standard ODE}
-\big[ P(\partial_z)+\frac{1}{z}Q(\partial_z)+R(z^{-1})\big]\Psi=0
-\end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R(z^{-1})=O(z^{-2})$ [Looking at the existence theorem in {\tt airy.resurgence 2.1.3} we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well].
+\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
+\end{equation}
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial [Looking at the existence theorem in {\tt airy.resurgence 2.1.3} we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well].
 Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
@@
 \begin{itemize}
-\item \eqref{eq:ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form  
+\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
 \begin{equation}
@@
 Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eq:ODE}
+\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
 \item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
@@
 On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-\item here is the way 
-there are many ways to see this porblem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, Ecalle figured it out how to see it formally in the Borel plane, our results shows how to see it analytically in  the Borel plane.
+\item  
+there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
 \item  M.A.E.T.
@@
 \item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
+See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
 Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
@@
 In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
+
 \color{DarkTurquoise}
-\begin{quote}
-We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
-\begin{align*}
-v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
-& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
-\end{align*}
-In this case, $\tau = \tfrac{1}{2}$.
-\end{quote}
+\subsubsection{Borel regularity}\label{bessel-regularity-AL}
+Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel-AL}
+
+\begin{equation}
+\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
+\end{equation}
+Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
+%
+%\subsubsection{Borel sum of $\tilde{W}_1$}
+%
+%Let us first compute the Borel transform of $\tilde{W}_1$:
+%
+%
+%\begin{align*}
+%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
+%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
+%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
+%\end{align*}
+
+Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
+
+\begin{align*}
+\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
+&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
+&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
+\end{align*}
+
+Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
+therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
+In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
+
+Similarly, if we consider the formal power series
+
+\begin{equation}
+\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
+\end{equation}
+
+analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
+
 \color{black}
 
-The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
-We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-
-The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-3/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
-
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
-It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-\subsubsection{Confirmation of Borel regularity}
-We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
-We found in Section~\textbf{[asymptotic analysis]} that
-\begin{align*}
-\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
-Computing
-\begin{align*}
-\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \mathcal{B}\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
-we see that $\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
-Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-
-Through a similar calculation, we see that $\mathcal{B}\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
-Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
 \subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
@@
 where
-\begin{equation}
+\begin{equation}\label{int_higher-Ariy}
 K^{(k)}(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
@@
 \subsubsection{Contour argument for higher Airy of degree $3$}
+
+We can recast integral \eqref{int_higher-Ariy} into the $\zeta$-plane by setting $\zeta=27 u^4-4 u$, which implies that $d\zeta=4 (27 u^3-1) du$.
+Projecting $z^{-1/4}\Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing a branch of that lifts $\gamma_z$ back to $z^{-1/4}\Lambda^{(k)}$, we get
+
+\begin{align*}
+K^{(k)}(z)&=\textcolor{magenta}{const.} \int_{\textcolor{magenta}{const.}z^{-1/4}\Lambda^{(k)}}\exp\big[- z \big(27 u^4-4 u\big)\big] du\\
+&=\textcolor{magenta}{const.} \int_{\gamma_z}e^{-z\zeta} \frac{d\zeta}{4(27u^3-1)}\\
+&=\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta}\frac{1}{3}\left[\frac{1}{3u-1}+\frac{1}{3e^{\frac{2\pi i}{3}} u -1}+\frac{1}{3e^{\frac{4\pi i}{3}} u-1}\right] d\zeta\\
+&=-\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta} {}_3F_2\left(\frac{1}{3},\frac{2}{3},1;\frac{2}{3};27 u^3\right) d\zeta
+\end{align*}
+\[
+\frac{1}{4}\frac{1}{27u^3-1}=\frac{1}{4}(\frac{A}{3u-1}+\frac{B}{3u-\omega}+\frac{C}{3u-\omega^2})
+\]
 

### 2023-03-12 exp-resurgence.tex

@@
 In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-
+\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
+The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
+The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
 \color{DarkTurquoise}
-\subsubsection{Borel regularity}\label{bessel-regularity-AL}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel-AL}
-
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
-
-\begin{align*}
-\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-
+\begin{quote}
+We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
+\begin{align*}
+v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
+& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
+\end{align*}
+In this case, $\tau = \tfrac{1}{2}$.
+\end{quote}
 \color{black}
 
+The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
+We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+
+The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
+Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-3/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
+
+When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
+It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
+That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
+Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
+\subsubsection{Confirmation of Borel regularity}
+We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
+We found in Section~\textbf{[asymptotic analysis]} that
+\begin{align*}
+\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
+\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
+\end{align*}
+Computing
+\begin{align*}
+\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \mathcal{B}\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
+& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
+\end{align*}
+we see that $\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
+
+Through a similar calculation, we see that $\mathcal{B}\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
 \subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}

### 2023-03-12 exp-resurgence.tex
updates

@@
 The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-\color{DarkTurquoise}
-The Borel transform $\mathcal{B}$ is a linear map from formal power seires in the time domain $\C_z$ to the space domain $\C_{\zeta}$ such that  \begin{align*}\mathcal{B}(z^{-n-1})&\defeq\tfrac{\zeta^n}{n!} \qquad, \text{ if } n\geq 0 \\
-\mathcal{B}(1)&\defeq\delta 
-\end{align*}
-
-where $\delta$ is the element $(1,0)\in\C\times\C[\![\zeta]\!]$\footnote{Sometimes, in physics it is common to adopt a differnt convention, i.e.
-$\mathcal{B}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$ (see\cite{MDiablerets}\cite{SGM}, for example).
-However, we find natural for our purposes the mathematical convention, as the Laplace transform is the inverse of $\mathcal{B}$ under suitable growth conditions.
-}, and by linearity
-\begin{align*}
-\mathcal{B}\colon \C[\![z^{-1}]\!] & \to \C\delta\oplus\C[\![\zeta]\!] \\
-\sum_{n\geq 0}a_n z^{-n} & \to  a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}
-\end{align*}
-\color{black}
 
@@
 The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-3/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
 Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
@@
 
-\subsection{Comparison with other treatments of the Airy equation \\ \textcolor{DarkTurquoise}{Comparison with other Airy examples}}
+\subsection{Comparison with other treatments of the Airy equation}
 
@@
 
-\color{DarkTurquoise}
-In the physic literature it is common that authors adopt a different definition of the Borel transform which does not involve the \textit{delta} element for the unit: they define $\mathcal{B}_{\textit{phys}}\colon \C [\![ z^{-1}]\!] \to \C \lbrace \zeta\rbrace$ such that $\mathcal{B}_{\textit{phys}}(z^{-n})\defeq \tfrac{\zeta^n}{n!}$.
-It is also commun to consider formal power series in small parameters, like $\tilde{\Phi}(\hbar)=\sum_{n\geq 0} a_n\hbar^n$ where $\hbar\to 0$ rather than formal series at $\infty$.
-Then the Borel transform of $\tilde{\Phi}$ is defined as $\tilde{\phi}(\zeta)=\sum_{n\geq 0}a_n\tfrac{\zeta^n}{n!}$.
-In \cite{Diablerets}, the author studies, as example of resurgent functions, the Airy functions.
-His starting point are the formal solutions of Airy differential equation
-\color{black}
 \begin{align*}

### 2023-03-12 exp-resurgence.tex
updates

@@
 &=\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta}\frac{1}{3}\left[\frac{1}{3u-1}+\frac{1}{3e^{\frac{2\pi i}{3}} u -1}+\frac{1}{3e^{\frac{4\pi i}{3}} u-1}\right] d\zeta\\
-&=-\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta} {}_3F_2\left(\frac{1}{3},\frac{2}{3},1;\frac{2}{3};27 u^3\right) d\zeta
+&=-\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta} {}_3F_2\left(\frac{1}{3},\frac{2}{3},1;\frac{1}{3},\frac{2}{3};27 u^3\right) d\zeta
 \end{align*}

### 2023-03-15 exp-resurgence.tex
updates

@@
 
-\subsubsection{Asymptotic analysis}
-
-\textcolor{lime}{[Use Poincar\'e algorithm to compute the asymptotic expansion]}
-
 \subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
@@
 
+\subsubsection{Asymptotic analysis}
+
+From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
+where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
+From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+\begin{equation}\label{bessel-asymp-AL}
+\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
+\end{equation}
+
+The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+which seem analogous to the trans-monomials above.
+Borel summation makes the analogy precise.
+We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
+This is an evidence of Theorem~\ref{thm:1}.
 %\subsection{Going to the spatial domain}\label{spatial-AL}
@@
 
-We define the following exponential integral: let $p\geq 0$, $f(t)=\tfrac{t^3}{3}-t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\pm\tfrac{2}{3}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
+We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
+The critical points of $f$ are $\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
 
 \begin{equation}
-I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p}
+I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
 \end{equation}
@@
 where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}).
-In particular, $I_{+}(z,p)=z^{\tfrac{p-1}{3}}\mathrm{A}_1(z^{2/3},p)$:
-
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(\tfrac{t^3}{3}-t)}\frac{dt}{t^p} &\\
-&=\frac{z^{(p-1)/2}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\tfrac{s^3}{3}-z^{-1/3}s)}\frac{ds}{s^p} & t=z^{-\tfrac{1}{3}}s\\
-&=\frac{z^{(p-1)/3}}{2\pi i}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\tfrac{s^3}{3}-z^{2/3}s\right)}\frac{ds}{s^p} & \\
-&=z^{(p-1)/3}\mathrm{A}_1(z^{2/3},p)
+In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$:
+
+\begin{align*}
+I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
+&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
 \end{align*}
@@
 \begin{equation}\label{eq:I}
-\left[\partial_z^3-\frac{4}{9}\partial_z+\frac{2-p}{z}\partial_z^2-\frac{4(1-p)}{9z}-\frac{1+3p-3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
+\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
 \end{equation}
@@
 \begin{equation}
-\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-\tfrac{2}{3}z}z^{-1/2}\tilde{W}_2(z)+U_3e^{\tfrac{2}{3}z}z^{-1/2}\tilde{W}_3(z)
+\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
 \end{equation}
@@
 \begin{multline}\label{w1}
-\left[\partial_z^3-\frac{4}{9}\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6p^2+11p-6}{z^3}\right]\tilde{W}_1(z)=0
+\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
 \end{multline}
@@
 \begin{multline}\label{w2}
-\left[\partial_z^3-2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.-\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
+\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
+\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
 \end{multline}
@@
 \begin{multline}\label{w3}
-\left[\partial_z^3+2\partial_z^2+\frac{8}{9}\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{2-4p}{3z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.+\frac{5+24p+12p^2}{54z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
+\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
+\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
 \end{multline}
+
 Let us first study equation \eqref{w1}: its Borel transform is
@@
 \begin{multline*}
--\zeta^3\tilde{w}_1+\frac{4}{9}\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
+-\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
 +\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
@@
 \begin{multline*}
-\left(\frac{4}{9}\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(\frac{4}{3}-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\tilde{w}_1'(\zeta)+\\
+\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
 +\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
@@
 
-we set $y=\tfrac{9}{4}\zeta^2$
+we set $y=\zeta^2$
 
@@
 \begin{multline}\label{eq:hw1}
-y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left(\left(p-\frac{13}{2}\right)y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{1}{3}(10-p)p\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
-+\frac{1}{27}\left(p-\frac{5}{2}\right)\tilde{w}_1(y)=0
+y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
++\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
 \end{multline}
@@
 
-therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)+R(\zeta)$ for some function $R(\zeta)$ which can be determined from the integral equation.
+therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$.
 
@@
 \begin{multline}
--\zeta^3\tilde{w}_2(\zeta)-2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
+-\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
 +\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
--\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
+-\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
 -\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
@@
 \begin{multline}
-\left[\left(\zeta^3+2\zeta^2+\frac{8}{9}\zeta\right)\partial_\zeta^3 +\frac{8}{3}\partial_\zeta^2+\left(\frac{17}{2}+p\right)\zeta\left(\zeta+\frac{4}{3}\right)\partial_\zeta^2+\right.\\
+\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
 \left.
-\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+\frac{2}{3}\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
+\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
 \end{multline}
@@
 \item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q_1\big(\tfrac{\partial}{\partial z}\big) + z^{-2} Q_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} Q_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $Q_k$ has degree $n-k$. \textcolor{gray}{has to be done}
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
+where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
 \begin{itemize}
@@
 We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}
+This is an evidence of Theorem~\ref{thm:1}.
 

### 2023-03-15 reg-sing-volterra.tex
Start separating integral equation results
It might be possible, and convenient, to publish these separately.

--- 2022-08-16 airy-resurgence.tex
@@
 
-\title{Resurgence of the Airy function}
+\title{Regular singular Volterra equations on complex domains}
 \author{Aaron Fenyes}
+\date{}
 
@@
 \maketitle
-\section{The Laplace transform}
-\subsection{Analytic version}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
-The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
-\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
-where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
-\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
+\section{Introduction}
+\subsection{Motivation}
+In its most basic form, the Laplace transform $\laplace$ turns $L^1$ functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+Through identities like
+\begin{align*}
+\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
+\laplace k\;\laplace f & = k * \varphi \\
+z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,
+\end{align*}
+where $\fracderiv{-\lambda}{}{}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.
 
-Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
-
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
-Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
-\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
-Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
-\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-\subsubsection{Action on integral operators}\label{L-int-op}
-When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-for all $\lambda \in (0, \infty)$.
-\subsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
-\subsection{Rescaling of translation structure}
-Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-\section{Integro-differential equations}
+If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
+\subsection{Main result}
+\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
 \subsection{Existence of solutions}
@@
 \end{center}
-\color{black}
+\color{gray}
 
@@
 Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
-\subsection{Order shifting}\label{shifting}
-Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
-A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
-\begin{equation}\label{eqn:slight-defn}
-\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-\end{equation}
-where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-
-Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
-When $\psi$ is slight and locally integrable at $\zeta = 0$,
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are regular functions.
-\end{prop}
-To prove this result, we'll need a little background.
-
-Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-is slight.
-Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
-Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
-\section{The Airy equation}
-\subsection{Basics}
-The Airy equation is
-\begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
-\end{equation}
-One solution is given by the Airy function,
-\[ \Ai(y) = \frac{i}{2\pi} \int_{\Gamma} \exp\left(-\tfrac{1}{3}t^3 + yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $120^\circ$ and goes to $\infty$ at $-120^\circ$.
-\begin{center}
-\includegraphics{figures/u_contour_3.pdf} \\[1em]
-{\small The contour $\Gamma$ in the $u$ plane.}
-\end{center}
-With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{i}{\pi} \int_{y^{-1/2} \Gamma} \exp\left[-\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We've rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
-\subsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
-The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function. Let's put equation~\ref{eqn:mod-bessel} in that form:
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \varphi = 0.
-\end{equation}
-\subsection{Asymptotic analysis}
-Equation~\ref{eqn:mod-bessel} has a regular singularity at $z = 0$ and an irregular singularity at $z = \infty$.
-From the general theory of such equations, we know that the space of trans-series solutions has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha$ are formal power series in $z^{-1}$ with no constant term.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp}
-\series{W}_1 = z^{-1} - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-2} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-3} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-4} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We'll see in Section~\ref{bessel-regularity} that each $z^{\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{\tau_\alpha}\,\series{W}_\alpha$.
-\subsection{Going to the spatial domain}\label{spatial}
-\subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\ref{eqn:reg-mod-bessel}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\ref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-Unfortunately, a solution of equation~\ref{diff-eq:spatial-mod-bessel} won't satisfy equation~\ref{int-eq:spatial-mod-bessel} in general.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\ref{diff-eq:spatial-mod-bessel} {\em will} satisfy equation~\ref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\ref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we'll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\ref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\color{Peru}
-\begin{align*}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-\end{align*}
-\color{Sienna}
-\begin{align*}
-\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-\end{align*}
-\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\ref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\ref{diff-eq:spatial-mod-bessel} the same.
-
-\color{DodgerBlue}
-If we'd followed the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we would've arrived at the hypergeometric equation
-\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we'd get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$
-\color{black}
-\section{The Airy-Lucas equation}
-\subsection{Basics}
-The Airy-Lucas equation is
-\begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-\subsection{Rewriting as a \textcolor{DarkCyan}{modified Bessel (?)} equation}
-We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{\textcolor{DarkCyan}{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel-rational}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the \textcolor{DarkCyan}{modified Bessel (?)} equation
-\begin{equation}%%\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\textcolor{DarkCyan}{\tfrac{m}{n} (?)}\big)^2 + z^2\big]\right] \varphi = 0.
-\end{equation}
-In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{\textcolor{DarkCyan}{m/n}}$.
-
-Like we did in equation~\ref{eqn:reg-mod-bessel}, we can rewrite the modified Bessel equation above as
-\begin{equation}%%\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\textcolor{DarkCyan}{\tfrac{m}{n}}\big)^2 z^{-2} \right] \varphi = 0.
-\end{equation}
-\section{The higher Airy equation}
-\subsection{Basics}
-The higher Airy equation is
-\begin{equation}\label{eqn:airy-lucas}
-\left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
-
-\color{Peru}
-With
-\begin{align*}
-z & = (-1)^{n-1} \tfrac{n-1}{n} y^{n/(n-1)} & w & = (-1)^n (n-1) y^{1/(n-1)} u,
-\end{align*}
-we have
-\begin{align*}
-\widetilde{\Ai}^{(k)}_n(y) & = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w^n - yw\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \left(w^{n-1} - ny\right)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \big((n-1)^{n-1} yu^{n-1} - ny\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}yw \big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[(-1)^n \tfrac{n-1}{n} y^{n/(n-1)} u\big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,dw \\
-& = (-1)^n (n-1) \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^n (n-1) \frac{\exp\left(\pi ik \big(1 - \tfrac{1}{n-1}\big)\right)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-\end{align*}
-\color{black}
-\[ \widetilde{\Ai}^{(k)}_n(y) = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-\subsection{Rewriting as a \textcolor{magenta}{(???)} equation}
-We can distill the most interesting parts of the hyper-Airy function by writing
-\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
-where
-\begin{equation}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
-\end{equation}
-Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
-\begin{equation}%%\label{eqn:mod-bessel}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] \varphi = 0.
-\end{equation}
-The sub-leading coefficients are the triangular numbers
-\[ c_n^{(1)} = \frac{n(n-1)}{2}. \]
-\color{DarkCyan}
-The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
-\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,(n+1)^{\underline{k+2}} \]
-in terms of the polynomials
-\begin{equationarray*}{*{11}{c}}
-b_n^{(2)} & = & \tfrac{1}{24} \\
-b_n^{(3)} & = & \tfrac{1}{48} n \\
-b_n^{(4)} & = & \tfrac{73}{5760} n^2 & + & \tfrac{1}{1152} n & - & \tfrac{1}{2880} \\
-b_n^{(5)} & = & \tfrac{11}{1280} n^{3} & + & \tfrac{1}{768} n^{2} & - & \tfrac{1}{1920} n \\
-b_n^{(6)} & = & \tfrac{3625}{580608} n^{4} & + & \tfrac{61}{41472} n^{3} & - & \tfrac{181}{322560} n^{2} & - & \tfrac{1}{41472} n & + & \tfrac{1}{181440}. \end{equationarray*}
-Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}.
-They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
-which tells us that
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots.
-\]
-The last coefficient can be written as
-\[ c_n^{(n-1)} = \left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, \]
-giving
-\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ (n+1)^{\underline{n+1}}. \]
-\color{black}
-\section{Sketches}
-\subsection{Contour argument for the Airy function}\label{contour-argument}
-We can recast integral~\ref{integral:mod-bessel} into the $\zeta$ plane by setting $\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
-\begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ in the $\zeta$ plane.}
-\end{center}
-
-It happens\footnote{\textcolor{magenta}{Veronica:} This comes from \cite[equation~15.4.14]{dlmf}.} that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
-so we can rewrite integral~\ref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
-
-In addition to the solutions $g_1$ and $f_0$ from Section~\ref{spatial-success}, equation~\ref{eqn:hypergeom} has the solutions
-\begin{alignat*}{2}
-g_0 &\;=\;& & F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big) \\
-f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big),
-\end{alignat*}
-given by formulas 15.10.13 and 15.10.14 from \cite{dlmf}.
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_0), \]
-so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_0)\;d\zeta. \]
-The solution $g_1$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $g_0$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,f_0$,
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
-Hence,
-\begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} f_0\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} f_0\;d\zeta \\
-K_1 & = \tfrac{i}{2} \laplace_{\zeta_1} f_0,
-\end{align*}
-just as we found in Section~\ref{spatial-success}.
-\subsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\ref{eqn:mod-bessel} with the solution $g_0$ of equation~\ref{eqn:hypergeom}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_0). \]
-The solution $g_1$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
-
-To express this other solution as a Laplace transform, following the method of Section~\ref{spatial-success}, we would use the solution
-\[ f_1 = (1-\xi)^{-1/2} F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\ref{eqn:hypergeom}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the contour integration method of solving equation~\ref{eqn:mod-bessel} is associated with the basis
-\begin{align*}
-g_1 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-g_0 & = F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
-\end{align*}
-of solutions for equation~\ref{eqn:hypergeom}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
-
-The Laplace transformation method of solving equation~\ref{eqn:mod-bessel}, on the other hand, is associated with the basis
-\begin{alignat*}{2}
-f_1 &\;=\;& (1-\xi)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-f_0 &\;=\:& \xi^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
-\end{alignat*}
-given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
-
-Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
-\begin{alignat*}{3}
-f_1 &\;=\;&\tfrac{1}{\sqrt{3}}\,g_1 &\;+\;& \tfrac{1}{2}\,f_0 \\
-f_0 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_0 &\;+\;& \tfrac{1}{2}\,f_1.
-\end{alignat*}
-Summing these identities, we see that
-\[ g_1 + g_0 = \tfrac{\sqrt{3}}{2}\,(f_1 + f_0), \]
-giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_0). \]
-\subsection{Contour argument for Airy-Lucas functions}
-Generalizing from Section~\ref{contour-argument}, we can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting as before, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
-& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
-\end{center}
-
-The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-\begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-\end{align*}
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
-Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-\color{DarkCyan}
-Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-where $\zeta = -1 + \zeta_{-1}$.
-\color{black}
-\subsection{Lifting to a countable cover}
-Formula~\ref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
-Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
-
-Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
-we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
-\begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
-\end{align}
-For any $\nu \in \C \smallsetminus \Z$, formulas~10.27.4 and 10.32.12 from \cite{dlmf} tell us that
-\begin{align}
-\notag K_\nu(z) & = \frac{\pi}{\sin(\nu \pi)} \cdot \frac{1}{2}\big[ I_{-\nu}(z) - I_\nu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\nu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\nu t} - e^{-\nu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\nu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\nu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\ref{integral:mod-bessel-lifted} when we choose a rational parameter $\nu = m/n$.
-
-When $\nu$ goes to $0$, formula~\ref{integral:mod-bessel-lifted} becomes
-\[ K_\nu(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
-\begin{align*}
-K_\nu(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
-\subsection{Link to dihedral triangulations}
-Here are the local normal forms of Kummer's first and second solutions. In the table, $[\bullet]$ denotes a local holomorphic function of order $0$ \cite[identities 15.8.2--4]{dlmf}, and
-\begin{align*}
-a' & = a+(1-c) \\
-b' & = b+(1-c) \\
-c' & = 2-c
-\end{align*}
-\begin{center}
-\begin{tabular}{c|c|c|c}
-Function & $0$ & $1$ & $\infty$ \\ \hline
-$F(a, b, c, \xi)$ & $[\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$ \\
-$\xi^{1-c} F(a', b', c', \xi)$ & $\xi^{1-c} [\bullet]$ & $[\bullet] + (1-\xi)^{c-a-b} [\bullet]$ & $(1/\xi)^a [\bullet] + (1/\xi)^b [\bullet]$
-\end{tabular}
-\end{center}
-
-For example, at $\zeta = \infty$, the function
-\[ u_{-1} = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, 1 - \tfrac{1}{2} \zeta_{-1}) \]
-is slight, with normal form $(1/\zeta_{-1})^{1 - m/n} f_1 + (1/\zeta_{-1})^{1 + m/n} f_2$~\cite[identity~15.8.3]{dlmf}.
-At $\zeta = 1$, it's holomorphic with order $0$.
-At $\zeta = -1$, it has the form $h + \zeta_{-1}^{-1/2} f$, where $h$ is holomorphic with order $0$.
-
-On the other hand, the function
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}) \]
-is slight at $\zeta = \pm 1$ with order $-\tfrac{1}{2}$, and slight at $\infty$ with order $1 - \tfrac{m}{n}$.
-
-Hence, the ratio $u_{-1} / v_{-1}$ looks like a holomorphic multiple of $\zeta_1^{1/2}$ near $\zeta = 1$, a holomorphic function plus a holomorphic multiple of $\zeta_{-1}^{1/2}$ near $\zeta = -1$, and a holomorphic function plus a holomorphic multiple of $(1/\zeta_{-1})^{2m/n}$ near $\zeta = \infty$.
-This is consistent with $u_{-1}/v_{-1}$ being a conformal map that sends the upper half-plane to a triangle with interior angle $\pi/2$ at the images of $\zeta = \pm 1$ and interior angle $2\pi\,\tfrac{m}{n}$ at the image of $\infty$.
-
-\color{ForestGreen}
-Let's try to get the small tetrahedral tiling by setting
-\begin{align*}
-1 - c & = \tfrac{1}{3} \\
-c - a - b & = \tfrac{1}{3} \\
-b - a & = \tfrac{1}{2},
-\end{align*}
-so $(a, b, c) = (-\tfrac{1}{12}, \tfrac{5}{12}, \tfrac{2}{3})$. The general hypergeometric equation is
-\begin{align*}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + \big[c - (a+b+1)\xi_1\big] \tfrac{\partial}{\partial \xi_1} - ab\right] & v = 0 \\
-\left[-\tfrac{1}{2}\zeta_1 (1 + \tfrac{1}{2}\zeta_1) 4 \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + \big[c + \tfrac{1}{2}(a+b+1)\zeta_1\big] (-2) \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
-\left[-\zeta_1 (2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 - \big[2c + (a+b+1)\zeta_1\big] \tfrac{\partial}{\partial \zeta_1} - ab\right] & v = 0 \\
-\left[(1 - \zeta)(1 + \zeta) \big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[2c + (a+b+1)(\zeta - 1)\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[(c - a - b) + (c - 1) + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[(1 - \zeta^2)\big(\tfrac{\partial}{\partial \zeta}\big)^2 - \big[\mu - \lambda + (a+b+1)\zeta\big] \tfrac{\partial}{\partial \zeta} - ab\right] & v = 0 \\
-\left[\big[\tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta\big] \tfrac{\partial}{\partial \zeta} - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
-\left[\tfrac{\partial}{\partial \zeta} \circ \big[ \tfrac{\partial}{\partial \zeta} \circ (1 - \zeta^2) + 2\zeta \big] + 2\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1)\big[\tfrac{\partial}{\partial \zeta} \circ \zeta - 1\big] - ab\right] & v = 0 \\
-\left[\big[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) + 4 \tfrac{\partial}{\partial \zeta} \circ \zeta - 2 \big] - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} - (a+b+1) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ (a+b+1) - ab \big]\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta + \big[ {-}1 + a + b - ab \big]\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (1 - \zeta^2) - (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (3-a-b) \tfrac{\partial}{\partial \zeta} \circ \zeta - (a-1)(b-1)\right] & v = 0 \\
-\left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta^2 - 1) + (\mu - \lambda) \tfrac{\partial}{\partial \zeta} + (a+b-3) \tfrac{\partial}{\partial \zeta} \circ \zeta + (a-1)(b-1)\right] & v = 0,
-\end{align*}
-For the tetrahedral tiling, we get
-\[ \left[\big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big(\zeta^2 - 1\big) - \tfrac{8}{3} \tfrac{\partial}{\partial \zeta} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\right] v = 0, \]
-which comes from the integral equation
-\[ \left[\big(\zeta^2 - 1\big) - \tfrac{8}{3}\,\fracderiv{-1}{\zeta}{\alpha} \circ \zeta + \tfrac{7 \cdot 13}{12^2}\,\fracderiv{-2}{\zeta}{\alpha}\right] v = 0. \]
-In the frequency domain, this equation becomes
-\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
-\color{black}
-\color{SpringGreen}
-Set
-\[ \laplace_{\zeta, \alpha} v = \int_\Lambda e^{-zf}\,p\,du. \]
-Observe that
-\[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] \int_\Lambda e^{-zf}\,p\,du = \int_\Lambda e^{-zf}\,(f^2 - 1)p\,du \]
-and
-\begin{align*}
-z^{-1} \tfrac{\partial}{\partial z} \int_\Lambda e^{-zf}\,p\,du & = z^{-1} \int_\Lambda e^{-zf}\,(-fp)\,du \\
-& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')q_1\,du \\
-& = \int_\Lambda e^{-zf}\,f'q_1\,du
-\end{align*}
-where $q_1' = -fp$.
-and
-\begin{align*}
-z^{-2} \int_\Lambda e^{-zf}\,p\,du
-& = -z^{-2} \int_\Lambda e^{-zf}\,(-zf')p_1\,du \\
-& = z^{-1} \int_\Lambda e^{-zf}\,f'p_1\,du \\
-& = -z^{-1} \int_\Lambda e^{-zf}\,(-zf')p_2\,du \\
-& = \int_\Lambda e^{-zf}\,f'p_2\,du \\
-\end{align*}
-with $p_1' = p$ and $p_2' = f'p_1$.
-\[ \left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + \tfrac{8}{3}\,z^{-1} \tfrac{\partial}{\partial z} + \tfrac{7 \cdot 13}{12^2}\,z^{-2}\right] \laplace_{\zeta, \alpha} v = 0. \]
-\color{black}
-
-\color{orange}
-In DLMF notation, let's try
-\begin{align*}
-u_1 & = F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \xi_{-1}) \\
-& = w_1(\xi_{-1}) \\
-u_{-1} & = w_3(\xi_{-1}) \\
-v_{-1} & = w_2(\xi_{-1}) \\
-v_1 & = -i\sqrt{2}\,\zeta_1^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
-& = (-\tfrac{1}{2}\zeta_1)^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, -\tfrac{1}{2}\zeta_1) \\
-& = (1 - \tfrac{1}{2}\zeta_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \tfrac{1}{2}\zeta_{-1}) \\
-& = (1 - \xi_{-1})^{-1/2} F(\tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2}, 1 - \xi_{-1}) \\
-& = w_4(\xi_{-1}),
-\end{align*}
-where $\xi_{-1} = \tfrac{1}{2}\zeta_{-1}$.
-
-\color{RoyalBlue}
-Let's guess that we're working with the map $\phi / \psi$ with
-\begin{align*}
-\phi & = \frac{\Gamma(-\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(\tfrac{1}{2} - \tfrac{m}{2n})\Gamma(\tfrac{1}{2} + \tfrac{m}{2n})}\,(\mp \zeta)\,F(1 - \tfrac{m}{2n}, 1 + \tfrac{m}{2n}, \tfrac{3}{2}; \zeta^2) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) - \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
-\psi & = \frac{\Gamma(\tfrac{1}{2}) \Gamma(\tfrac{3}{2})}{\Gamma(1 - \tfrac{m}{2n})\Gamma(1 + \tfrac{m}{2n})} F(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}, \tfrac{1}{2}; \zeta^2) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-& = \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, -\tfrac{1}{2}\zeta_1) + \tfrac{1}{2} F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2}\zeta_{-1}) \quad\text{[choosing negative sign]} \\
-\end{align*}
-\color{black}
-\subsection{Comparison with Ghate and Venkataramana}
-\begin{align*}
-\mu_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \lambda & = 1 - c \\
-\nu_\text{GV} & = 1 - \left\{\frac{k_2}{d}\right\} - \left\{\frac{k_3}{d}\right\} & \mu & = c - a - b \\
-\lambda_\text{GV} & = 1 - \left\{\frac{k_1}{d}\right\} - \left\{\frac{k_2}{d}\right\} & \nu & = b - a
-\end{align*}
-The hyperelliptic curve in Section~4 is
-\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
-
-Dihedral case (Theorem~2):
-\begin{align*}
-\frac{k_1}{d} & = \frac{p}{2m} \\
-\frac{k_2}{d} & = \frac{p}{2m} \\
-\frac{k_3}{d} & = \frac{m - p}{2m}
-\end{align*}
-Note that $\lambda = p'/m$ with $p + p' = m$. The hyperelliptic curve is
-\[ y^d = (x - \alpha_1)^{k_1} (x - \alpha_2)^{k_2} (x - \alpha_3)^{k_3}. \]
-Cosines appear in Section~2.3: $x_j = \exp(2\pi i\,\tfrac{k_j}{d})$, and we work in the totally real field $\mathbb{Q}(\cos(\frac{2\pi}{m}))$.
-
-Airy case:
-\begin{align*}
-\frac{k_1}{d} & = \frac{1}{3} \\
-\frac{k_2}{d} & = \frac{1}{3} \\
-\frac{k_3}{d} & = \frac{1}{6},
-\end{align*}
-so $(k_1, k_2, k_3, d) = (2, 2, 1, 6)$, and the hyperelliptic curve is
-\[ y^6 = (x - \alpha_1)^2 (x - \alpha_2)^2 (x - \alpha_3). \]
-\subsection{Correspondence with Mari\~{n}o's series}
-Let $F_1(z)$ be the holomorphic function corresponding to Mari\~{n}o's formal power series $\varphi_1(z^{-1})$. The formal power series corresponding to $F_1$ will be written in the variable $z$.
-
-\begin{align*}
-\Ai(x) & = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} \varphi_1\big(\tfrac{2}{3} z^{-1}\big) \\
-& = \tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) \\
-\Ai(x) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2})
-\end{align*}
-Putting together,
-\begin{align*}
-\tfrac{1}{2\sqrt{\pi}} x^{-1/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = \frac{1}{\pi\sqrt{3}} x^{1/2} K(\tfrac{2}{3} x^{3/2}) \\
-\tfrac{\sqrt{3\pi}}{2}\;x^{-3/4} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(\tfrac{2}{3} x^{3/2}) \\
-\tfrac{\sqrt{3\pi}}{2}\;\big(\tfrac{3}{2} z)^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
-\sqrt{\tfrac{\pi}{2}}\;z^{-1/2} e^{-z} F_1\big(\tfrac{3}{2} z\big) & = K(z) \\
-\sqrt{\tfrac{\pi}{2}}\;\big[\laplace^{-1} z^{-1/2}\big] * \big[\laplace^{-1} F_1\big(\tfrac{3}{2} z\big)\big](\zeta - 1) & = k(\zeta) \\
-\sqrt{\tfrac{\pi}{2}}\;\left[\Gamma\big({-\tfrac{1}{2}}\big)^{-1} \zeta^{-1/2}\right] * \tfrac{2}{3} f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
--\tfrac{1}{3\sqrt{2}}\;\left[\zeta^{-1/2}\right] * f_1\big[\tfrac{2}{3}(\zeta - 1)\big] & = k(\zeta) \\
-\end{align*}
-Notice that if the hypergeometric differentiation formula holds for fractional derivatives,
-\[ \big(\tfrac{\partial}{\partial \xi}\big)^{1/2}F\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \propto F\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big) \]
-\bibliographystyle{utphys}
-\bibliography{airy-resurgence}
 \end{document}

### 2023-03-15 project-description.tex
Start drafting project description
Introduce motivation, past work, and goals.

\documentclass{article}[a4paper]

\usepackage[left=3.5cm, right=3.5cm, top=1.5cm, bottom=1.5cm]{geometry}
\usepackage{amsmath}
\usepackage{titlesec}

\titleformat*{\section}{\large\bfseries}
\titlespacing{\section}{0pt}{*2}{*1}
\titleformat{\subsection}[runin]{\normalsize\bfseries}{\thesubsection\hspace{2ex}}{0pt}{}{}
\titlespacing{\subsection}{0pt}{*1}{*2}

\begin{document}
\begin{center}
\Large Synthesizing perspectives on Borel summation
\end{center}

\section*{Motivation}
In winter 2021--2022, we (Veronica Fantini and Aaron Fenyes) and some of our colleagues at IH\'{E}S met regularly to learn about Borel summation and resurgence. While discussing sources that introduce various aspects of Borel summation from different perspectives, we saw a need for sources that would detail the common threads binding together different approaches, examples, and parts of the theory.
\section*{Past work and goals}
Since then, we've been drafting an article---suitable for readers new to the field---which describes some of the common threads that have emerged from our discussions. Our main goals are:

\begin{itemize}
\item To focus on examples of functions which are both exponential integrals and solutions of differential equations, and to show how the same Borel plane emerges in different ways from these two characterizations.
\item To present Borel summation as a regularization process, and to explain from this common perspective why Borel summation can reconstruct both exponential integrals and solutions of certain differential equations from their asymptotic series.
\item To show how Borel summation links analogous structures across the division between functions and series, and the division between the frequency and position domains (that is, the $z$ and Borel planes).
\item To give the frequency and position domains a common geometry by presenting them as the singular fiber space and the base space of a cotangent bundle.
\end{itemize}

\section*{Plans for this visit}

\end{document}

### 2023-03-16 project-description.tex
Add some plans for this visit (not used)

@@
 \end{itemize}
+\section*{Plans for this visit}
+During the proposed two-week visit, we expect to increase our writing pace through the more frequent, efficient, and spontaneous meetings made possible by working in person.
 
-\section*{Plans for this visit}
-
+We also plan to disseminate and get feedback on our draft article through a series of two to four talks. Being close to the Plateau de Saclay and to Paris
 \end{document}

### 2023-03-18 exp-resurgence.tex

@@
 %%\subsection{A familiar process: Borel summation}\label{intro:summation}
-You can often find a formal power series \textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
+You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
 \[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
@@
 \begin{equation}
-\text{\bf [one-third Bessel equation, rescaled to match integral example]} \label{eqn:bessel-rescaled}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
 \end{equation}
@@
 \begin{enumerate}
-\item Thinking of $z$ as a ``frequency variable,'' we take the formal inverse Laplace transform (also known as Borel transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item With luck, $\series{\phi}$ has a positive radius of convergence.
-In this case, we say $\series{\Phi}$ is {\em $1$-Gevrey}.
+\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
+\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}.
 We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
@@
 Ask more about this.]}
-\item With more luck, $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} for its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-By definition, the Borel sum is asymptotic to $\tilde{\Phi}$
+By definition, the Borel sum is asymptotic to $\tilde{\Phi}$.
 \end{enumerate}
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail]\arrow[rr,red,dashed,"\parbox{15mm}{\footnotesize asymptotics}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail]\arrow[rr,red,dashed,"\text{\footnotesize Gevrey asymptotics}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
@@
 
-we start from the upper-right corner with the formal solution $\tilde{\Phi}$, then, moving clockwise, we take the Borel transform $\mathcal{B}$ which produces a germ of holomorphic function at the origin.
-If we can sum it and its sum $\hat{\phi}$ has a controlled behaviour at infinity, we can take the Laplace transform $\hat{\Phi}=\mathcal{L}_b^{\theta}\hat{\phi}$ which produces a holomorphic function asymptotic to $\tilde{\Phi}$ in a given half plane.
+we read the diagram from the upper-right corner with the formal solution $\tilde{\Phi}$, then, moving clockwise, we take the Borel transform $\mathcal{B}$ which produces a germ of holomorphic function at the origin.
+If we can sum it and its sum $\hat{\phi}$ has a controlled behaviour along a ray going to infinity, we can take the Laplace transform $\hat{\Phi}=\mathcal{L}_b^{\theta}\hat{\phi}$ which produces a holomorphic function asymptotic to $\tilde{\Phi}$ in a given half plane.
 A priori it is not guaranteed that $\hat{\Phi}$ solves our original problem, as different functions can be asymptotic to the same power series, and Borel summation picks one of them.
@@
 
-The central goal of this paper is to present a new perspective on Borel summation which helps explain why it works for at least two kinds of problems: 
-\begin{enumerate}
-\item the first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral} such as
-
-\begin{equation}
-\int_{\Lambda}\exp\big[-z(\tfrac{1}{3}u^3-\tfrac{1}{4}u)\big] du
-\end{equation}
-\item the second problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled}. We will mainly focus on Poincar\'e rank $1$ ODEs. 
-\end{enumerate}
-
-These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-
-Let us change perspective: we start from the upper-left corner of the diagram, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $z$ goes to $\infty$ along a given ray.
+We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$
 
@@
 \begin{tikzcd}
-& \text{problem} & \\
+& \text{Problem} & \\
 \Phi \arrow[ru, no head, tail,swap,"\parbox{15mm}{\centering\footnotesize solves}"' ]\arrow[rrd,dashed,swap,"\parbox{15mm}{\centering\footnotesize asymptotics}"']& & \\
-\hat{\Phi} \arrow[rr,red,dashed,"\parbox{15mm}{\footnotesize asymptotics}"'] & & \series{\Phi} \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[rr,red,dashed,"\text{\footnotesize Gevrey asymptotics}"'] & & \series{\Phi} \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
@@
 
+\textcolor{red}{[explain difference between Poincar\'e asymptotics and Gevrey asymptotics]}
+
 Reading the diagram clockwise, if $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
@@
 We'll therefore call this process {\em Borel regularization}.
-We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-
-The natural question is then about the relationship between $\hat{\Phi}$ and $\Phi$: we'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged, i.e.
-$\Phi$ is {\em Borel regular} if $\Phi=\hat{\Phi}$.
+We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series (namely if we can draw the square in the lower part of the diagram).
+
+The natural question is then about the relationship between $\hat{\Phi}$ and $\Phi$: we say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged, i.e.
+$\Phi$ is {\em Borel regular} if $\Phi\propto \hat{\Phi}$.
 
@@
 \[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+over all orders $N$ and all $z$ in a wide enough sector around infinity.
+
+Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'', see a proof in Nikita, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15) tells us that a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
+Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\mathcal{B}\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
+Hence $\Phi$ is Borel-regularizable.
+In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$.
+In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
+
+Using our new perspective on Borel summation, the central goal of this paper is to explain why it works for at least two kinds of problems: 
+\begin{enumerate}
+\item the first problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled-1}. We will mainly focus on Poincar\'e rank $1$ ODEs
+\begin{equation}\label{eqn:standard ODE}
+\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
+\end{equation}
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
+
+\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
+
+\begin{equation}
+I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
+\end{equation}
+where $f\colon X\to \mathbb{C}$ is an algebraic map, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+\end{enumerate}
+
+These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+
+Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
+Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
+We will give precise statements in the following section.
 
@@
 We'll call this process {\em Borel regularization}.
-\begin{itemize}
-\item 
-\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-\item We have the following vector space inclusions:
-\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-
-Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-\begin{itemize}
-\item $\Phi$ is Borel regular.
-\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-\item $\phi$ grows at most exponentially along the Laplace transform ray.
-\end{itemize}
-\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
+%\begin{itemize}
+%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
+%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+%\item We have the following vector space inclusions:
+%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
+%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
+%
+%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
+%\begin{itemize}
+%\item $\Phi$ is Borel regular.
+%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
+%\item $\phi$ grows at most exponentially along the Laplace transform ray.
+%\end{itemize}
+%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
 \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
@@
 When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
-\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-\item \ldots
-\end{itemize}
+%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
+%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
+%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
+%\item \ldots
+%\end{itemize}
 
 \subsection{Goals and Results}
+
+We summarize our main goals and results in this section: first of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1} ), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
+
+Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain); on the hand integral equations are more regular than differential equations.On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
+
+As part of the treatment, we have made use of some new perspectives on the Laplace transform.
+Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
+
+Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
+
+We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
+Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
+On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
+Borel regularity will be evident from the explicit computations.
+Some examples have been discussed many times, using different approaches and conventions.
+We try to give an idea of how all these different treatments fit together.
+For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
+The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
+Other example haven't been discussed much, as for Airy--Lucas functions.
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
+Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
+For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
 
@@
 \end{itemize}
-\color{black}
+
 \item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.

### 2023-03-19 exp-resurgence.tex
Revise introduction
Try to organize the "new perspective" section.

Mention that a series is 1-Gevrey-asymptotic to its Borel sum. Add
steps for Borel regularization.

Propose a more general form for the ODEs we consider, based on
volume III of Écalle's _Les fonctions résurgentes_.

@@
 \usepackage{xparse}
+\usepackage{enumitem}
 %\usepackage{eqnarray}
@@
 \newcommand{\borel}{\mathcal{B}}
+\newcommand{\aexp}{\ae}
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
@@
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-By definition, the Borel sum is asymptotic to $\tilde{\Phi}$.
+\end{enumerate}
+The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship.
+\begin{enumerate}[start=4]
+\item By construction, taking the asymptotic expansion of $\hat{\Phi}$ along the half-plane $\Re e^{i\theta}z > 0$ gives back $\series{\Phi}$.
+In other words, $\aexp^\theta \hat{\Phi} = \series{\Phi}$, in the notation of \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
+
+The asymptotic expansion map $\aexp^\theta$ sends each function $F$ to the unique formal power series $a_0 + a_1 z + a_2 z^2 + \ldots$ for which
+\[ |F - (a_0 + a_1 z + \ldots + a_n z^n)| \in o\big(|z|^n\big), \]
+as $\Re e^{i\theta} z$ grows, over all orders $n$. \textcolor{magenta}{[Wait, don't we want a series in $z^{-1}$?]}
+
+It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em \textcolor{magenta}{uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}: there are constants $C, A \in (0, \infty)$ for which
+\[ |F - (a_0 + a_1 z + \ldots + a_{n-1} z^{n-1})| \le C A^n n!\,|z|^n, \]
+on the half-plane $\Re e^{i\theta}z > 0$, over all orders $n$.
+\textcolor{magenta}{[I think this condition is actually \textbf{uniform} $1$-Gevrey asymptoticity on the half-plane, as defined in \cite[Definition~5.21]{diverg-resurg-i}.
+Note that Mitschi and Sauzin actually say ``uniformly'' in Corollary~5.23.]}
 \end{enumerate}
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail]\arrow[rr,red,dashed,"\text{\footnotesize Gevrey asymptotics}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{15mm}{\centering\footnotesize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
@@
 
-we read the diagram from the upper-right corner with the formal solution $\tilde{\Phi}$, then, moving clockwise, we take the Borel transform $\mathcal{B}$ which produces a germ of holomorphic function at the origin.
-If we can sum it and its sum $\hat{\phi}$ has a controlled behaviour along a ray going to infinity, we can take the Laplace transform $\hat{\Phi}=\mathcal{L}_b^{\theta}\hat{\phi}$ which produces a holomorphic function asymptotic to $\tilde{\Phi}$ in a given half plane.
-A priori it is not guaranteed that $\hat{\Phi}$ solves our original problem, as different functions can be asymptotic to the same power series, and Borel summation picks one of them.
+We can't be sure {\em a priori} that $\hat{\Phi}$ solves our original problem.
+\textbf{[\ldots]} Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
 However, in many cases, it picks correctly, producing an actual solution to your problem.
@@
 \subsection{A new perspective: Borel regularity}
-
-We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$
+\subsubsection{Introducing Borel regularity}
+\begin{itemize}
+\item Start instead with a holomorphic solution $\Phi$.
+\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
+\end{itemize}
+\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
 
@@
 \begin{tikzcd}
-& \text{Problem} & \\
-\Phi \arrow[ru, no head, tail,swap,"\parbox{15mm}{\centering\footnotesize solves}"' ]\arrow[rrd,dashed,swap,"\parbox{15mm}{\centering\footnotesize asymptotics}"']& & \\
-\hat{\Phi} \arrow[rr,red,dashed,"\text{\footnotesize Gevrey asymptotics}"'] & & \series{\Phi} \arrow[dd, mapsto, "\mathcal{B}"] \\
+& \text{problem} & \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\mathcal{B}"] \\
 & & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
+\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
 \end{tikzcd}
 \end{center}
-
-\textcolor{red}{[explain difference between Poincar\'e asymptotics and Gevrey asymptotics]}
-
-Reading the diagram clockwise, if $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
+If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
 Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
 We'll therefore call this process {\em Borel regularization}.
-We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series (namely if we can draw the square in the lower part of the diagram).
-
-The natural question is then about the relationship between $\hat{\Phi}$ and $\Phi$: we say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged, i.e.
-$\Phi$ is {\em Borel regular} if $\Phi\propto \hat{\Phi}$.
-
-Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+Explicitly, Borel regularization works in four steps.
+\begin{enumerate}
+\item Take the asymptotic expansion $\series{\Phi} = \aexp^\theta \Phi$.
+\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
+This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.
+\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
+This is possible, by definition, if $\series{\Phi}$ is Borel-summable.
+\textbf{[Should we be allowed to take the Laplace transform at another points $b \in B$ instead?]}
+\end{enumerate}
+We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
+
+Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
+We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
+\subsubsection{Borel regularity as a good approximation condition}
+Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
+Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever there's an obtuse-angled sector around $\infty$ and a pair of constants $C, A \in (0, \infty)$ for which
+\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \le \frac{C A^n n!}{|z|^n} \]
+over all orders $n$ and all $z$ in the sector.
+
+\textcolor{gray}{Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
 \[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-over all orders $N$ and all $z$ in a wide enough sector around infinity.
+over all orders $N$ and all $z$ in a wide enough sector around infinity.}
 
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-
-Using our new perspective on Borel summation, the central goal of this paper is to explain why it works for at least two kinds of problems: 
+\subsubsection{Borel regularity sometimes explains why Borel summation works}
+The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
+Roughly speaking, Borel summation works well for problems with Borel regular solutions that stand out asymptotically \textcolor{magenta}{[this may need refining]}.
+
+The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
 \begin{enumerate}
-\item the first problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled-1}. We will mainly focus on Poincar\'e rank $1$ ODEs
+\item \color{DarkTurquoise}
+Solving a linear ODE of Poincar\'{e} rank~$1$. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ for a differential operator of the form
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
+
+We'll restrict our attention to the case where the roots of $P$ are distinct.
+
+The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of Poincar\'{e} rank~$1$.
+Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.
+
+\color{Tan}
+the first problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled-1}. We will mainly focus on Poincar\'e rank $1$ ODEs
 \begin{equation}\label{eqn:standard ODE}
@@
 where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-
+\color{black}
 \item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
@@
 \end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial [Looking at the existence theorem in {\tt airy.resurgence 2.1.3} we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well].
-Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
+\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
+\item \color{DarkTurquoise}
+I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
+\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
+where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
+\color{black}
 \item (backgrounds) Under these assumptions, 
 \begin{itemize}
-\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
+\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
 \begin{equation}

### 2023-03-19 exp-resurgence.tex
Define asymptoticity better; restrict o(1/z) parts of ODEs

@@
 
-%%\theoremstyle{definition}
-%%\newtheorem{defn}{Definition}
+\theoremstyle{definition}
+\newtheorem{defn}{Definition}
 %%\theoremstyle{plain}
@@
 \end{enumerate}
-The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship.
+The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
+\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
+Hopefully it wouldn't be too hard, but it would be a pain.]}
+\begin{defn}
+On an open sector $\Omega$ around $\infty$, a power series
+\begin{equation}\label{series:asymp-defn}
+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
+\end{equation}
+is {\em asymptotic} to a holomorphic function $F$ if
+\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
+over all orders $n$.
+
+The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
+\end{defn}
+\begin{defn}
+On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
+\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
+over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of.''
+\end{defn}
+To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
+
 \begin{enumerate}[start=4]
-\item By construction, taking the asymptotic expansion of $\hat{\Phi}$ along the half-plane $\Re e^{i\theta}z > 0$ gives back $\series{\Phi}$.
-In other words, $\aexp^\theta \hat{\Phi} = \series{\Phi}$, in the notation of \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
-
-The asymptotic expansion map $\aexp^\theta$ sends each function $F$ to the unique formal power series $a_0 + a_1 z + a_2 z^2 + \ldots$ for which
-\[ |F - (a_0 + a_1 z + \ldots + a_n z^n)| \in o\big(|z|^n\big), \]
-as $\Re e^{i\theta} z$ grows, over all orders $n$. \textcolor{magenta}{[Wait, don't we want a series in $z^{-1}$?]}
-
-It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em \textcolor{magenta}{uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}: there are constants $C, A \in (0, \infty)$ for which
-\[ |F - (a_0 + a_1 z + \ldots + a_{n-1} z^{n-1})| \le C A^n n!\,|z|^n, \]
-on the half-plane $\Re e^{i\theta}z > 0$, over all orders $n$.
-\textcolor{magenta}{[I think this condition is actually \textbf{uniform} $1$-Gevrey asymptoticity on the half-plane, as defined in \cite[Definition~5.21]{diverg-resurg-i}.
-Note that Mitschi and Sauzin actually say ``uniformly'' in Corollary~5.23.]}
+\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
+It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em \textcolor{magenta}{uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
 \end{enumerate}
@@
 
-We can't be sure {\em a priori} that $\hat{\Phi}$ solves our original problem.
-\textbf{[\ldots]} Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-However, in many cases, it picks correctly, producing an actual solution to your problem.
-
+You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
+After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
+In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
 The question of how that happens is the starting point for this paper.
-
-In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
+\color{DarkTurquoise}
+\begin{itemize}
+\item In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
 For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.
-
+\end{itemize}
+\color{black}
 %\color{gray}
@@
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type.
 

### 2023-03-20 exp-resurgence.tex
minor changes
I agree with Aaron changes and I removed the comments

@@
 The question of how that happens is the starting point for this paper.
-\color{DarkTurquoise}
-\begin{itemize}
-\item In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.
-\end{itemize}
-\color{black}
+
 %\color{gray}
@@
 
-\textcolor{gray}{Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-over all orders $N$ and all $z$ in a wide enough sector around infinity.}
-
 Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'', see a proof in Nikita, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15) tells us that a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
@@
 \end{equation}
-where $f\colon X\to \mathbb{C}$ is an algebraic map, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+where $f\colon X\to \mathbb{C}$ is a Morse function, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
 \end{enumerate}
@@
 & & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
-\Phi\arrow[rru,dashed] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red] & & & \tilde{\Phi}\arrow[llu,"formal",swap]\arrow[dd,"\mathcal{B}"]\\
+\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
 & & IE & & \\
-\phi\arrow[rru]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu]
+\phi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu, no head, tail]
 \end{tikzcd}
@@
 \item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely the commutativity of the following diagram
+\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+\begin{equation}
+I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+\end{equation}
+
+then the following diagram is commutative
 \begin{equation}
 \begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
 & \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\hat{\iota}_\alpha(\zeta)\arrow[uu, "\mathcal{L}^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
 \end{tikzcd}

### 2023-03-22 exp-resurgence.tex
Updates intro

@@
 \newtheorem{definition}{Definition}[section]
-\newtheorem{problem}[definition]{Problem}
-\newtheorem{example}[definition]{Example}
-\newtheorem{fact}[definition]{Fact}
-\newtheorem{aside}[definition]{Aside}
 \newtheorem{prop}[definition]{Proposition}
-\newtheorem{question}[definition]{Question}
 \newtheorem{remark}[definition]{Remark}
-\newtheorem{theorem}[definition]{Theorem}
-\newtheorem{corollary}[definition]{Corollary}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}[theorem]{Corollary}
 \newtheorem{lemma}[definition]{Lemma}
@@
 \item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
-It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em \textcolor{magenta}{uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
+It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
 \end{enumerate}
@@
 \begin{enumerate}
-\item \color{DarkTurquoise}
-Solving a linear ODE of Poincar\'{e} rank~$1$. One example is Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ for a differential operator of the form
+\item Solving a linear ODE as the one in example Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ for a differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
@@
 
-\color{Tan}
-the first problem is solving a certain kind of ODE as \eqref{eqn:bessel-rescaled-1}. We will mainly focus on Poincar\'e rank $1$ ODEs
-\begin{equation}\label{eqn:standard ODE}
-\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-\end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\color{black}
 \item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
@@
 
-Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
+%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
 Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
@@
 
-We summarize our main goals and results in this section: first of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1} ), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain); on the hand integral equations are more regular than differential equations.On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-
-As part of the treatment, we have made use of some new perspectives on the Laplace transform.
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
-
-Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
-
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
-Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
-Borel regularity will be evident from the explicit computations.
-Some examples have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
-The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
-Other example haven't been discussed much, as for Airy--Lucas functions.
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-
-\color{gray}
-\begin{itemize}
-\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-\begin{itemize}
-\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-\item The second problem is solving a certain kind of ODE.
-\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-\end{itemize}
-
-\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-\begin{itemize}
-\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-\end{itemize}
-\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-\begin{itemize}
-\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-\begin{itemize}
-\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-\end{itemize}
-\end{itemize}
-\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
-\begin{itemize}
-\item Integral equations are more regular than differential equations.
-\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-\end{itemize}
-\item Illustrate with detailed treatments of several examples.
-\begin{itemize}
-\item Contour argument (thimble integrals)
-\item solving integral equation (ODE)
-\item How thimble integrals and ODE are related in our examples?
-\end{itemize}
-\begin{itemize}
-\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-\item Others haven't been discussed much.
-\end{itemize}
-\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-\begin{itemize}
-\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-\item computation of Stokes constants via Picard--Lefschetz theory
-\end{itemize}
-\end{itemize}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean being Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
-\end{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
-
-\subsection{Why does Borel resummation work?}
-
-\color{gray}
-
-Borel resummation is a way of turning a formal power series
-\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-\begin{itemize}
-\item \textbf{Having a good asymptotic approximation}
-
-Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-\color{black}
-
-\item \textbf{Satisfying a singular differential equation}
-
-\begin{itemize}
-\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
+First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
+
+Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the hand integral equations are more regular than differential equations.
+On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
+
+\subsubsection{Why does Borel resummation work for solutions of irregular singular ODEs?}
+
+We restrict to ODEs with irregular singularity at $\infty$ \textcolor{magenta}{and of Poincar\'e rank $1$}: 
 \begin{equation}\label{eqn:standard ODE}
-\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-\end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-\item \color{DarkTurquoise}
-I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-\color{black}
-\item (backgrounds) Under these assumptions, 
-\begin{itemize}
-\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
+P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b]
+\end{equation}
+where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_0, \ldots, R_d$ are holomorphic functions on $\C$ \footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
+Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+
+Under these assumptions, \eqref{eqn:standard ODE} admits a basis of formal solutions \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
 \begin{equation}
@@
 Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions.
-\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-\end{itemize}
+
+Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sum $\hat{\Psi}_j$ satisfies the original equation \eqref{eqn:standard ODE} \cite{Ramis?}\textcolor{magenta}{[Check references]}.
+Therefore, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
+
+However, can we find a distinguished basis of solutions in a purely analytic way?
+This should be possible as the coefficients of the ODE are regular enough.
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotics to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
+14).
+Conversely, we can explicitly built a distinguished basis of analytic solutions:
+
+\begin{theorem}\label{thm1}
+In the previous set-up, for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$: set $\zeta_j=\zeta-\alpha_j$,
+
+\[{\psi}_j(\zeta_j)=\textcolor{magenta}{\zeta_j^{\tau_j-1}}+f_j\] .
+\end{theorem}
+\textcolor{magenta}{[verify the exponent, is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}
+
+At this point, we may ask what is the relationship between the two frame of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
+Our main result says they are actually the same, hence proving Borel summation works.
+
+\begin{theorem}\label{thm2}
+Let $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ be the Laplace transform of $\psi_j$ solutions constructed in Theorem~\ref{thm1}. The following results hold true
+\begin{enumerate}
+\item $\Psi_j$ is asymptotic to $\series{\Psi}_j$;
+\item the Borel sum of $\series{\Psi}_j$ is the same as $\Psi_j$
+\end{enumerate}
+\end{theorem}
+
+In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
+
+In the following diagram we sketch the main step of the proof of Theorem~\ref{thm2}: on the right hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
+Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
+
+\begin{center}
+\begin{tikzcd}
+& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
+\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
+& & IE & & \\
+\psi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\psi}\arrow[llu, no head, tail]
+\end{tikzcd}
+\end{center}
+
+Conversely, on the left hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
+
+The key step, is then comparing $\psi_j$ and $\hat{\psi}_j$.
+First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too.
+In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
+therefore, by our uniqueness result~\ref{thm1}, we conclude that $\psi_j$ and $\hat{\psi}_j$ must coincide up to scaling by a constant.
+
+As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
+Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.
+
+\begin{remark}
+There are many ways to built a frame of solutions for these kind of ODE: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
+Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}.
+It can indeed been seen as a consequence of ``resurgence'' of the ODE.
+Our results show how to built a frame of solutions, analytically in the Borel plane.
+Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
+From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
+\end{remark}
+
+\begin{remark}
+Although, in our proof we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
+\textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
+For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behaviour is enough to say that it is the sum of $\series{\psi}_j$?
+Check carefully the argument of multi-summability]}
+\end{remark}
+
+\color{gray}
+\begin{itemize}
 \item Can we see there exists a distinguished basis in a purely analytic way?
@@
 \item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+\end{itemize}
 \begin{itemize}
@@
 \item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-\end{itemize}
 \item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
@@
 
-\item \textbf{Being a thimble integral}
+\subsubsection{Why does Borel resummation work for thimbles integrals?}
 
@@
 \end{itemize}
+
+\color{black}
+
+\subsubsection{Other results}
+
+As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
+Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
+
+Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
+
+We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
+Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
+On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
+Borel regularity will be evident from the explicit computations.
+Some examples have been discussed many times, using different approaches and conventions.
+We try to give an idea of how all these different treatments fit together.
+For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
+The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
+Other example haven't been discussed much, as for Airy--Lucas functions.
+
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}).
+Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
+For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
+
+%\color{gray}
+%\begin{itemize}
+%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+%\begin{itemize}
+%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+%\item The second problem is solving a certain kind of ODE.
+%\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+%\end{itemize}
+%
+%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+%\begin{itemize}
+%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
+%\end{itemize}
+%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+%\begin{itemize}
+%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+%\begin{itemize}
+%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+%\end{itemize}
+%\end{itemize}
+%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
+%\begin{itemize}
+%\item Integral equations are more regular than differential equations.
+%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
+%\end{itemize}
+%\item Illustrate with detailed treatments of several examples.
+%\begin{itemize}
+%\item Contour argument (thimble integrals)
+%\item solving integral equation (ODE)
+%\item How thimble integrals and ODE are related in our examples?
+%\end{itemize}
+%\begin{itemize}
+%\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function (Marino, Sauzin).
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+%\item Others haven't been discussed much.
+%\end{itemize}
+%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
+Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
+For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
+%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+%\begin{itemize}
+%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
+%\item computation of Stokes constants via Picard--Lefschetz theory
+%\end{itemize}
+%\end{itemize}
+\subsection{Results}
+
+\color{orange}
+\begin{itemize}
+\item what does it mean being Borel regular?
+\item when does it happen?
+\begin{itemize}
+\item State new Borel regularity results
+\begin{itemize}
+\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
+\begin{itemize}
+\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
+\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
+\item Also contextualize with Loday-Richaud
+\end{itemize}
+\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item fractional derivative formula
+\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
+\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
+\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
+\end{itemize}
+\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
+\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+\end{itemize}
+\end{itemize}
+
+%\subsection{Why does Borel resummation work?}
+%
+%\color{gray}
+%
+%Borel resummation is a way of turning a formal power series
+%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
+%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
+Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
+When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
+Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
+%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
+%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
+%\begin{itemize}
+%\item \textbf{Having a good asymptotic approximation}
+%
+%Let $R_N$ be the difference between a function and the partial sum
+%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
+%\color{black}
+%
+%\item \textbf{Satisfying a singular differential equation}
+%
+%\begin{itemize}
+%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
+%\begin{equation}\label{eqn:standard ODE}
+%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
+%\end{equation}
+%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
+\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
+%\item \color{DarkTurquoise}
+%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
+%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
+%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
+%\color{black}
+%\item (backgrounds) Under these assumptions, 
+%\begin{itemize}
+%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
+%\begin{equation}
+%\label{formal solution}
+%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
+%\end{equation}
+%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
+%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
+%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
+%\end{itemize}
+%\item Can we see there exists a distinguished basis in a purely analytic way?
+YES.
+[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+%\begin{itemize}
+%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+(proof based on existence theorem \ref{frac_int_exist})
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+%\end{itemize}
+%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+Then this is the only solution that can be expressed as a Laplace transform.
+[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
+%
+%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+%
+%\begin{center}
+%\begin{tikzcd}
+%& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
+%& & IE & & \\
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\end{tikzcd}
+%\end{center}
+%
+%where the arrow in red are a consequence of multisummability.
+In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
+On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
+%\item  
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%\item  M.A.E.T.
+says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
+Our method uses just Laplace transform.
+%\item How do we know we are picking the same frame?
+from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
+From uniqueness result we get a frame equivalent to Ecalle's frame.
+%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+Borel regularity is instead based on the analytic solution in the $z$-plane.
+The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
+%\end{itemize}
+%
+%\color{DarkBlue}
+%
+%\item \textbf{Being a thimble integral}
+%
+%\begin{itemize}
+%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
+%\begin{itemize}
+%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
+%\end{itemize} 
+%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
+His proof is geometric [it may be useful to add it in Appendix].
+%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
+%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
+%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+%\begin{equation}
+%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+%\end{equation}
+%
+%then the following diagram is commutative
+%\begin{equation}
+%\begin{tikzcd}
+%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+%& \\
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\mathcal{L}^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\end{tikzcd}
+%\end{equation}
+%\begin{itemize}
+%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
+%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
+%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+%\item A corollary of [Thm 4] is the fractional derivative formula.
+%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+%\end{itemize}
+%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
+See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
+Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
+%\end{itemize}
 
@@
 \color{black}
-\end{itemize}
+%\end{itemize}
 \begin{itemize}
@@
 \end{itemize}
-\section{The Laplace and Borel transforms}
+\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
 \subsection{The geometry of the Laplace transform}

### 2023-03-24 exp-resurgence.tex
updates

@@
 \end{itemize} 
-\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-\item \textcolor{red}{We give an analytic proof analogous of Pham.}
+\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
+His proof uses microlocal analysis and classical results due to Varchenko.
+In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
+\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
 \item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
@@
 \item A corollary of [Thm 4] is the fractional derivative formula.
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\end{itemize}
-\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
+\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
+\begin{equation}
+mmm
+\end{equation} 
+\end{itemize}
+\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
 See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-\end{itemize}
+\begin{itemize}
+\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
+\end{itemize}
+\end{itemize}
+
+\color{DarkGreen}
+We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
+Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
+A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
+
+Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
+Suppose every singularity of $B$ is a critical value of $f$.
+\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
+How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
+We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
+These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
+The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
+The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
+\textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
+\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
+is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
+
+\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
+
+In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
+This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],[Delabere \& Howls, Howls, Dingle]}.
+
+\color{DarkTurquoise}
+Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
+Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
+This data defines the {\em exponential integral}
+\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
+a holomorphic function on the right half-plane parametrized by $z$.
+It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
+\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
 
@@
 
-\color{DarkGreen}
-Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
-Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
-A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-Suppose every singularity of $B$ is a critical value of $f$.
-\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-The {\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
-The {\em thimble integral}
-\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parametrized by $z$, and it turns out \textbf{[we hope]} to be Borel regular.
-
-\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
-
-In higher-dimensional complex manifolds, integrals over Lefschetz thimbles are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
-This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...'']}.
-
-\color{DarkTurquoise}
-Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
-Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
-This data defines the {\em exponential integral}
-\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-a holomorphic function on the right half-plane parametrized by $z$.
-It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
-\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
 \color{black}

### 2023-04-16 exp-resurgence.tex
Think more carefully about which ODEs we're considering
Also, state Nevanlinna & Sokal's improvement of Watson's theorem.

@@
 \end{defn}
-\begin{defn}
+\begin{defn}\label{def:unif-gevrey-asymp}
 On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
 \[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
-over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of.''
+over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
 \end{defn}
@@
 \begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^\theta \Phi$.
+\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
 \item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
@@
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever there's an obtuse-angled sector around $\infty$ and a pair of constants $C, A \in (0, \infty)$ for which
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \le \frac{C A^n n!}{|z|^n} \]
-over all orders $n$ and all $z$ in the sector.
-
-Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'', see a proof in Nikita, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15) tells us that a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
+Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
+
+Watson's theorem was soon improved by Nevanlinna (see a modern proof in Nikolaev, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15), and improved again later by Sokal (Sokal, ``An improvement of Watson's theorem on Borel summability'').
+These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
+\begin{center}
+\begin{tikzpicture}
+\newcommand{\size}{3}
+\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
+\newcommand{\ang}{35}
+\newcommand{\dis}{1.2}
+\begin{scope}
+  \clip (-\size, -\size) rectangle (\size, \size);
+  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
+  \begin{scope}[violet]
+    \draw (0, 0) -- (-\ang:\outsize);
+    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
+    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
+    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
+  \end{scope}
+\end{scope}
+%%\begin{scope}[violet]
+%%  \draw (0, 0) -- (center);
+%%  \fill (center) circle (0.05);
+%%\end{scope}
+\draw[->] (-\size, 0) -- (\size, 0);
+\draw[->] (0, -\size) -- (0, \size);
+\node[anchor=north east] at (\size, \size) {$z$};
+\end{tikzpicture}
+\end{center}
+When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
+
+%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
 Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\mathcal{B}\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsubsection{Borel regularity sometimes explains why Borel summation works}
+\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
 The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
@@
 \begin{enumerate}
-\item Solving a linear ODE as the one in example Equation~\eqref{eqn:bessel-rescaled-1}. The general example is the equation $\mathcal{P} \Phi = 0$ for a differential operator of the form
+\item Solving a linear ODE of level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Definition~5.5]{diverg-resurg-iii}}.
+One example is Equation~\eqref{eqn:bessel-rescaled-1}.
+The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
@@
 
-The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of Poincar\'{e} rank~$1$.
+The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
 Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.
@@
 
-Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the hand integral equations are more regular than differential equations.
+Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the one hand integral equations are more regular than differential equations.
 On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
 
-\subsubsection{Why does Borel resummation work for solutions of irregular singular ODEs?}
-
-We restrict to ODEs with irregular singularity at $\infty$ \textcolor{magenta}{and of Poincar\'e rank $1$}: 
+\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
+As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
 \begin{equation}\label{eqn:standard ODE}
-P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b]
-\end{equation}
-where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_0, \ldots, R_d$ are holomorphic functions on $\C$ \footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
+\end{equation}
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
 Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-
-Under these assumptions, \eqref{eqn:standard ODE} admits a basis of formal solutions \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form
+Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
+It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.
+
+\color{DarkTurquoise}
+In \cite[Proposition~2.2.7]{EcalleIII}, where
+\begin{align*}
+P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
+Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
+\end{align*}
+(with the coefficients renamed to avoid a conflict with the zeros $\alpha_j$), the recurrence that gives the solution simplifies
+\begin{align*} b_q & = P_q + Q_q z^{-1} - \frac{\partial}{\partial x^{(q)}} b(z, x, x^{(1)}, \ldots x^{(d)}) \\
+& = P_q + Q_q z^{-1} - R_q(z^{-1}).
+\end{align*}
+
+Following the argument of Delabaere Lemma~6.2, we can prove that $\series{F}_j(z)$ is $1$-Gevrey by taking the formal Borel transform of the ODE it satisfies and showing it is regular singular at $\zeta=0$.
+
+Roughly speaking, factoring out $e^{-\alpha_j z}$ removes the constant term of $P$, and factoring out $z^{-\tau_j}$ changes $Q$ to give factorial growth instead of gamma function growth (?).
+
+\begin{align*}
+\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
+& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
+&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
+\end{align*}
+where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
+\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
+corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).
+
+From the Bessel equation, for example, we get
+\begin{align*}
+(-w^{-2}\partial_w)^2&=-w^{-2}\partial_w(-w^{-2}\partial_w)\\
+&=-w^{-2}(2w^{-3}\partial_w-w^{-2}\partial_w^2)\\
+&=-2w^{-5}\partial_w+w^{-4}\partial_w^2,
+\end{align*}
+giving two half-planes around $\infty$, as expected.
+\color{black}
+
+Under these assumptions, $\mathcal{P}\Phi = 0$ admits a basis of formal solutions \cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^\times$, then the formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ are of the form
 \begin{equation}
 \label{formal solution}
-\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
+\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket
 \end{equation}
@@
 
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sum $\hat{\Psi}_j$ satisfies the original equation \eqref{eqn:standard ODE} \cite{Ramis?}\textcolor{magenta}{[Check references]}.
-Therefore, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis of solutions in a purely analytic way?
+Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
+Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
+
+However, can we find a distinguished basis for solutions in a purely analytic way?
 This should be possible as the coefficients of the ODE are regular enough.
@@
 14).
-Conversely, we can explicitly built a distinguished basis of analytic solutions:
+Conversely, we can explicitly build a distinguished basis of analytic solutions:
 
@@
 \end{theorem}
-\textcolor{magenta}{[verify the exponent, is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}
+\textcolor{magenta}{[Paste in statement from {\tt reg-sing-volterra}. Verify the exponent: is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}
 
@@
 
-In the following diagram we sketch the main step of the proof of Theorem~\ref{thm2}: on the right hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
+In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
 Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
@@
 
-Conversely, on the left hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
-
-The key step, is then comparing $\psi_j$ and $\hat{\psi}_j$.
+Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
+
+The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
 First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too.
@@
 \begin{remark}
-There are many ways to built a frame of solutions for these kind of ODE: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
+There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
 Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}.
-It can indeed been seen as a consequence of ``resurgence'' of the ODE.
-Our results show how to built a frame of solutions, analytically in the Borel plane.
+It can indeed be seen as a consequence of ``resurgence'' of the ODE.
+Our results show how to build a frame of solutions, analytically in the Borel plane.
 Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
@@
 \begin{remark}
-Although, in our proof we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
+Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
 \textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
-For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behaviour is enough to say that it is the sum of $\series{\psi}_j$?
+For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$?
 Check carefully the argument of multi-summability]}

### 2023-04-24 exp-resurgence.tex
update section proof

@@
 \begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
 \end{equation}
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
-Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
 Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
@@
 
-\begin{theorem}\label{thm1}
-In the previous set-up, for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$: set $\zeta_j=\zeta-\alpha_j$,
-
-\[{\psi}_j(\zeta_j)=\textcolor{magenta}{\zeta_j^{\tau_j-1}}+f_j\] .
+\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
+In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with
+
+\begin{equation}
+\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
+\end{equation}
+
+such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
+${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
 \end{theorem}
-\textcolor{magenta}{[Paste in statement from {\tt reg-sing-volterra}. Verify the exponent: is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}
 
@@
 \begin{theorem}\label{thm2}
-Let $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ be the Laplace transform of $\psi_j$ solutions constructed in Theorem~\ref{thm1}. The following results hold true
-\begin{enumerate}
-\item $\Psi_j$ is asymptotic to $\series{\Psi}_j$;
-\item the Borel sum of $\series{\Psi}_j$ is the same as $\Psi_j$
-\end{enumerate}
+For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
+Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
 \end{theorem}
@@
 \subsection{Borel regularity for ODEs}
+
+\begin{theorem}\label{thm1-dim}
+Let $\mathcal{P}$ be a linear differential operator 
+\begin{equation}
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
+\end{equation}
+
+\begin{itemize}
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
+\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
+\item $R_0, \ldots, R_d$ are entire functions of exponential type
+\end{itemize}
+
+Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
+
+\begin{equation}
+\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
+\end{equation}
+
+such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
+${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
+\end{theorem}
+\begin{proof}
+It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
+In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$.
+$Q$ is also a polynomial defined at $\zeta_j=0$.
+Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
+
+\begin{align*}
+&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
+&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
+\end{align*}
+
+%In particular, $\Lambda=(-\infty,-2]$.
+
+Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
+
+\end{proof}
+
+\begin{theorem}\label{thm2-dim}
+For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
+Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
+Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
+\end{theorem}
+\begin{proof}
+We divide the proof in the following steps:
+\begin{itemize}
+\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
+\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\tilde{\psi}_j:=\mathcal{B}\Psi_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
+\item[$(c)$] prove that $\mathcal{L}_{\zeta_j}^{\theta_j}\circ\mathcal{B}\series{\Psi}_j\propto \Psi_j $. 
+\end{itemize}
+\end{proof}
+
 \subsection{Borel regularity for thimble integrals}

### 2023-05-01 reg-sing-volterra.tex
Sketch a statement of the improved existence and uniqueness result

@@
 %%\theoremstyle{definition}
-%%\newtheorem{defn}{Definition}
+\newtheorem{defn}{Definition}
 \theoremstyle{plain}
-\newtheorem{prop}{Proposition}
+%%\newtheorem{prop}{Proposition}
+\newtheorem{thm}{Theorem}
 
@@
 \section{Introduction}
-\subsection{Motivation}
+\subsection{Motivation}\label{motivation}
 In its most basic form, the Laplace transform $\laplace$ turns $L^1$ functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
@@
 \subsection{Main result}
+\begin{defn}\label{fin-order}
+Consider a Volterra operator $\mathcal{V}$ of the form
+\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
+We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
+\begin{itemize}
+\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
+\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
+\end{itemize}
+and at one of the following holds:
+\begin{enumerate}
+\item\label{case:0th-order} $m$ isn't the zero function.
+\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
+\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
+where {\rm ``diag''} means the diagonal in $\Omega^2$.
+\end{enumerate}
+We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
+\end{defn}
+\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
+It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}.
+Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
+\begin{thm}
+Let $\Omega$ be an acute-angled sector around $0$ in the complex plane.
+\textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}
+
+Consider a Volterra operator
+\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
+over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$.
+To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
+\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
+which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
+
+Assume, furthermore, that:
+\begin{itemize}
+\item There's some $c \in (0, \infty)$ for which
+$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
+\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
+\item $p$ has a simple zero at $\zeta = 0$.
+\end{itemize}
+Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+
+Under these conditions, let's try to solve the regular singular Volterra equation
+\[ \mathcal{V}f = 0. \]
+The leading-order part of the equation,
+\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
+has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$.
+If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
+\[ f = \zeta^{\tau-1} + f_*, \]
+where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
+\end{thm}
+\section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
+Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
+Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
+Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
+For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
+We'll call this space $\holoL{\infty, \sigma}_Z(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
+\begin{align*}
+\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
+\phi & \mapsto \zeta^{-\sigma} \phi
+\end{align*}
+is an isometry. More generally,
+\begin{align*}
+\holoL{\infty, \rho}_Z(\Omega) & \to \holoL{\infty, \rho+\delta}_Z(\Omega) \\
+f & \mapsto \zeta^\delta f
+\end{align*}
+is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
+%------------------------------------------------------------------------
 \section{Integro-differential equations {[from {\tt airy-resurgence}]}}
+\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
 \subsection{Existence of solutions}
@@
 \end{center}
-\color{gray}
+\color{black}
 

### 2023-05-01 exp-resurgence.tex
Fix typo in norm bound for algebraic integral operators
Veronica, thanks for spotting the typo independently. Now I'm sure
it wasn't just something I was too tired to understand.
updates

@@
 
-\title{Borel regularity for ODEs and exponential integrals}
+\title{Borel regularity for ODEs and thimble integrals}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 \[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
+
+\color{magenta}
+
+Write explicit definition $\mathcal{L}_{\zeta_{\alpha},0}^{\theta}\varphi$ specifying the argument of $\varphi$ in the integration.
+
+\begin{equation}
+\mathcal{L}_{\zeta_\alpha,0}^{\theta}\varphi:=\int_{\Gamma_{\zeta_\alpha,0}^{\theta}}e^{-z\zeta_\alpha}\varphi(\zeta_\alpha-\alpha)d\zeta_\alpha
+\end{equation}
+
+\color{black}
+
 \subsubsection{Rescaling of translation structure}
@@
 \begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
@@
 
+\color{brown}
 \begin{equation}
@@
 \end{equation}
-
+\color{black}
 such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
@@
 Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
+Furthermore, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$ for every $j=1,...,d$.
+Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
 \end{theorem}
@@
 \item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\tilde{\psi}_j:=\mathcal{B}\Psi_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
+\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\mathcal{B}\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
 \item[$(c)$] prove that $\mathcal{L}_{\zeta_j}^{\theta_j}\circ\mathcal{B}\series{\Psi}_j\propto \Psi_j $. 
 \end{itemize}
+
+Step $(c)$ clearly follows from steps $(a)$ and $(b)$.
+We now prove step $(b)$: first notice that if $\series{\Psi}_j$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
+
+\begin{equation}
+\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
+\end{equation}
+
+\color{brown}
+Then taking the (formal) Borel transform:for every $j=1,...,d$ we denote $\zeta_j=\zeta-\alpha_j$ and we consider the Borel transform of $\mathcal{P}\series{\Psi}_j$ in the coordinate $\zeta_j$
+
+\begin{multline*}
+\mathcal{B}\left(\mathcal{P}\series{\Psi}_j\right)=\mathcal{B}\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
+\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
+\left[P(-\zeta)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
+\end{multline*}
+%where 
+%
+%\begin{align*}
+%\series{\psi}_j(\zeta_j):=\mathcal{B}\series{\Psi}_j(\zeta_j)&=\mathcal{B}\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\mathcal{B}\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
+%&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
+%\end{align*}
+
+Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0.
+from the properties of the Borel transform we deduce that $\hat{P}\series{\psi}_j=0$ first notice that $\series{\psi}_j$ is a solution of
+\color{black}
 \end{proof}

### 2023-05-07 exp-resurgence.tex
updates

@@
 
-Under these assumptions, $\mathcal{P}\Phi = 0$ admits a basis of formal solutions \cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^\times$, then the formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ are of the form
-\begin{equation}
-\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket
-\end{equation}
-Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions.
+Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
+\begin{equation}\label{formal solution}
+\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
+\end{equation}
+where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
+Since the roots $\alpha_1, \ldots, \alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
 
@@
 However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible as the coefficients of the ODE are regular enough.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotics to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
+This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
 14).
@@
 \big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |\zeta^\sigma f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
-& \le \|f\|_{\infty, \sigma} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
+& \le \int_{\zeta = 0}^{a} |\zeta^\rho f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
+& \le \|f\|_{\infty, \rho} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
 \end{align*}
 holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_\infty. \]
+\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_{\infty, \rho}. \]
 so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.

### 2023-05-07 exp-resurgence.tex
Updates from Overleaf

--- 2023-04-24 exp-resurgence.tex
@@
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
-Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
 Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
@@
 
-\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
-In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with
-
-\begin{equation}
-\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
+\begin{theorem}\label{thm1}
+In the previous set-up, for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$: set $\zeta_j=\zeta-\alpha_j$,
+
+\[{\psi}_j(\zeta_j)=\textcolor{magenta}{\zeta_j^{\tau_j-1}}+f_j\] .
 \end{theorem}
+\textcolor{magenta}{[Paste in statement from {\tt reg-sing-volterra}. Verify the exponent: is it $\tau_j-1$ or $\tau_j$? What are the conditions for $f_j$?]}
 
@@
 \begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
+Let $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ be the Laplace transform of $\psi_j$ solutions constructed in Theorem~\ref{thm1}. The following results hold true
+\begin{enumerate}
+\item $\Psi_j$ is asymptotic to $\series{\Psi}_j$;
+\item the Borel sum of $\series{\Psi}_j$ is the same as $\Psi_j$
+\end{enumerate}
 \end{theorem}
@@
 \subsection{Borel regularity for ODEs}
-
-\begin{theorem}\label{thm1-dim}
-Let $\mathcal{P}$ be a linear differential operator 
-\begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_d$ are entire functions of exponential type
-\end{itemize}
-
-Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-
-\begin{equation}
-\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
-\end{theorem}
-\begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
-In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$.
-$Q$ is also a polynomial defined at $\zeta_j=0$.
-Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
-
-\begin{align*}
-&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
-\end{align*}
-
-%In particular, $\Lambda=(-\infty,-2]$.
-
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
-
-\end{proof}
-
-\begin{theorem}\label{thm2-dim}
-For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
-\end{theorem}
-\begin{proof}
-We divide the proof in the following steps:
-\begin{itemize}
-\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\tilde{\psi}_j:=\mathcal{B}\Psi_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
-\item[$(c)$] prove that $\mathcal{L}_{\zeta_j}^{\theta_j}\circ\mathcal{B}\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-\end{proof}
-
 \subsection{Borel regularity for thimble integrals}

### 2023-05-08 exp-resurgence.tex
updates

--- 2023-05-07 exp-resurgence.tex
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 \Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\mathcal{B}"] \\
+\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 %%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
-Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\mathcal{B}\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
+Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
 Hence $\Phi$ is Borel-regularizable.
@@
 \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\mathcal{L}\circ\mathcal{B}\tilde{\Phi}$ (i.e.
+Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
 it is Borel regular)?
@@
 \begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
 \end{equation}
@@
 \begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
+For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
 Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
@@
 \begin{tikzcd}
-& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
+& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
 & & IE & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\psi}\arrow[llu, no head, tail]
+\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
 \end{tikzcd}
@@
 
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\mathcal{L}_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
+As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
 Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.
@@
 \begin{tikzcd}
-& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
-\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
+& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
 & & IE & & \\
-\phi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
 \end{tikzcd}
@@
 \begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\
-\hat{\iota}_\alpha(\zeta)\arrow[uu, "\mathcal{L}^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
 \end{tikzcd}
@@
 \item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
 \item A corollary of [Thm 4] is the fractional derivative formula.
@@
 \begin{itemize}
-\item what does it mean being Borel regular?
+\item what does it mean to be Borel regular?
 \item when does it happen?
@@
 \begin{itemize}
-\item Linear, homogeneous ODE with regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
+\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
 \begin{itemize}
@@
 \begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\mathcal{L}^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\
@@
 \end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
 \item fractional derivative formula
@@
 \item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeomtric functions}
+\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
 \end{itemize}
@@
 %\begin{tikzcd}
-%& & ODE\arrow[dd,"\mathcal{B}"]\arrow[dd,"\mathcal{L}^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\mathcal{B}"]\\
+%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
 %& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\mathcal{L}"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\mathcal{L}"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
 %\end{tikzcd}
@@
 %\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\mathcal{B}"]\\
+%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 %& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\mathcal{L}^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
 %\end{tikzcd}
@@
 %\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\mathcal{L}^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
 %\item A corollary of [Thm 4] is the fractional derivative formula.
@@
 \begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behaviour.
-\item The resummation method works correctly for functions which satisfy that assumption.
+\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
+\item The resummation method works correctly for functions that satisfy that assumption.
 \item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
@@
 \begin{itemize}
-\item \textbf{Maxim belies it is in general, and indeed in our examples we get simple resurgent functions. But how to prove it in general?}
+\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
 \end{itemize} 
@@
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+
+\subsection{The geometry of the Borel transform}
+\begin{itemize}
+  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+It's a formal inverse of the $\laplace_{\zeta, 0}$.
+  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
+  \begin{itemize}
+    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
+\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
+[Not quite\ldots figure out how to make this precise.] }
+  \end{itemize}
+  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
+\end{itemize}
 
@@
 
-\color{magenta}
-
-Write explicit definition $\mathcal{L}_{\zeta_{\alpha},0}^{\theta}\varphi$ specifying the argument of $\varphi$ in the integration.
-
-\begin{equation}
-\mathcal{L}_{\zeta_\alpha,0}^{\theta}\varphi:=\int_{\Gamma_{\zeta_\alpha,0}^{\theta}}e^{-z\zeta_\alpha}\varphi(\zeta_\alpha-\alpha)d\zeta_\alpha
-\end{equation}
-
-\color{black}
-
 \subsubsection{Rescaling of translation structure}
@@
 We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-
 \color{gray}
-\subsection{The Laplace transform}
-\begin{itemize}
-\item Action on differential equations.
-\begin{itemize}
-\item Can we find a way to prove this when the differential operator spits out a function that's not integrable around zero?
-\end{itemize}
-\item Global picture?
-\end{itemize}
-\color{black}
-
 \subsection{The Borel transform}
@@
 \begin{align*}
-\borel \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
+\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
 1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
@@
 \begin{align*}
-\mathcal{B}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
 \end{align*}
@@
 Notice that we are at the level of formal series, so there are no convergence assumptions.
-However, there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic fucntions at the origin in $\C_{\zeta}$.
-These formal series are the so called Gevrey-$1$ series:
-\[\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
+However, there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
+These formal series are the so-called Gevrey-$1$ series:
+\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
 is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
@@
 \begin{notation*}
-We want to distinghuish between formal series and holomorphic functions, as well as between the Borel plane (time domain) and the $z$-plane (spatial domain). Therefore we adopt the following notation:
-\begin{itemize}
-\item $\Phi(z)$: upper-case letters are holomorphic functions in the $z$-plane;
-\item $\tilde{\Phi}(z)$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the $z$-plane;
-\item $\phi(\zeta)$: lower-case letter are holomorphic functions in the Borel plane.
-We follow the convention for Laplace transform of holomorphic functions, namely $\mathcal{L}(\phi(\zeta)((z)=\Phi(z)$.
-\item $\tilde{\phi}(\zeta)$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we will see, the Borel transform of $\tilde{\Phi}(z)$ is $\mathcal{B}(\tilde{\Phi})(\zeta)=:\tilde{\phi}(\zeta)$;
-\item $\hat{\phi}(\zeta)$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}(\zeta)$, when it exists.  
+We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane).
+Therefore we adopt the following notation:
+\begin{itemize}
+\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
+\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
+\item $\phi$: lower-case letters are holomorphic functions on the frequency domain.
+Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
+\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
+As we will see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
+\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
 \end{itemize}
@@
 \begin{lemma}
-Let $\tilde{\Phi}(z)\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\mathcal{B}(\tilde{\Phi})\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
+Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
+Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
 \end{lemma}
@@
 
-The inverse of $\mathcal{B}$ is what we call a \textbf{formal Laplace transform}.
-
-\textcolor{magenta}{[add definition of convolution product and $\mathcal{B}$ being an algebra isomorphisms]}
+The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
+
+\textcolor{magenta}{[add definition of convolution product and $\borel$ being an algebra isomorphisms]}
 
 \subsubsection{Generalization of the Borel transform}
-The definition of $\mathcal{B}$ can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
-\begin{align*}
-\mathcal{B}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
+The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
+\begin{align*}
+\borel\textcolor{orange}{_\zeta}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
 \end{align*}
@@
 
-If $\alpha\in\mathbb{R}\setminus\Z$ is not an integer, then $\mathcal{B}$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
+If $\alpha\in\mathbb{R}\setminus\Z$, then $\borel$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
 Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-\alpha} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
 \begin{align*}
-\mathcal{B}(z^{-\alpha}\tilde{\Phi})(\zeta)&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
+\borel\textcolor{orange}{_\zeta} (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
 \end{align*}
@@
 \subsubsection{Properties of the Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}$ and denote by $\tilde{\phi}(\zeta)\defeq\mathcal{B}(\tilde{\Phi}(z))$
+We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
 
@@
 \begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\mathcal{B}\left(z^\alpha \tilde{\Phi}(z)\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}(\zeta)$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\mathcal{B}(z^n\tilde{\Phi}(z))=\partial_\zeta^n\tilde{\phi}(\zeta)$ 
-\item[(iv)] $\mathcal{B}\left(\partial_z^{n} \tilde{\Phi}(z)\right)=(-\zeta)^n\tilde{\phi}(\zeta)$, for every $n\geq 0$
-\item[(v)] $\mathcal{B}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}(\zeta)$
-\item[(vi)] if $\tilde{\Psi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\mathcal{B}(\tilde{\Phi}(z)\tilde{\Psi}(z))=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}(\zeta)=\mathcal{B}(\tilde{\Psi}(z))$.
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel(z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
+\item[(iv)] $\borel\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
+\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
+\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel(\tilde{\Phi}\tilde{\Psi}=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
 \end{itemize}
@@
 For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] =  \borel \left(z^\mu z^{-(k+1)}\right)(\zeta). \]
+\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
 \end{lemma}
@@
 \begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
@@
 
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}(\zeta).\]
-
-(iii) $z^n\tilde{\Phi}(z)=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel (z^n \tilde{\Phi}(z))=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}(\zeta).\]
-
-(vi) $\partial_z^n \tilde{\Phi}(z)=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel (z^\alpha \tilde{\Phi}(z))=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}(\zeta).\]
+(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
+
+(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
+
+(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
 
@@
 \begin{align*}
-\borel (z^\alpha \tilde{\Phi}(z))&=\borel (z^\alpha)\ast \tilde{\phi}(\zeta)\\
-&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}(\zeta)\\
+\borel_\zeta (z^\alpha \tilde{\Phi})&=\borel_\zeta (z^\alpha)\ast \tilde{\phi}\\
+&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}\\
 &=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
@@
 &=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
-&=\partial_\zeta^\alpha\tilde{\phi}(\zeta)
+&=\partial_\zeta^\alpha\tilde{\phi}
 \end{align*}
@@
 For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\mathcal{L}_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
+Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
 Furthermore, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$ for every $j=1,...,d$.
@@
 \item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\mathcal{B}\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
-\item[$(c)$] prove that $\mathcal{L}_{\zeta_j}^{\theta_j}\circ\mathcal{B}\series{\Psi}_j\propto \Psi_j $. 
+\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\borel\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
+\item[$(c)$] prove that $\laplace_{\zeta_j}^{\theta_j}\circ\borel\series{\Psi}_j\propto \Psi_j $. 
 \end{itemize}
@@
 \begin{multline*}
-\mathcal{B}\left(\mathcal{P}\series{\Psi}_j\right)=\mathcal{B}\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
+\borel\left(\mathcal{P}\series{\Psi}_j\right)=\borel\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
 \left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
@@
 %\begin{align*}
-%\series{\psi}_j(\zeta_j):=\mathcal{B}\series{\Psi}_j(\zeta_j)&=\mathcal{B}\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\mathcal{B}\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
+%\series{\psi}_j(\zeta_j):=\borel\series{\Psi}_j(\zeta_j)&=\borel\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\borel\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
 %&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
@@
 \item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\mathcal{B}(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
+\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\borel(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
 \item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
@@
 \begin{align*}
-\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+\borel_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
 & = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
@@
 Part~\eqref{int:resum-converges}: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\mathcal{B}\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
 (2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
@@
 & = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha.
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
+& = \borel_{\zeta_\alpha} \tilde{I}_\alpha.
+\end{align*}
+We already knew, from the general theory of the Borel transform, that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
+We've now shown that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
 
@@
 \begin{align*}
-\mathcal{B}_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \mathcal{B}_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \mathcal{B} \tilde{\varphi}_\alpha \\
+\borel_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
+& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \borel \tilde{\varphi}_\alpha \\
 & = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
@@
 \begin{align*}
-\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \mathcal{B}\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
+\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
@@
 \end{align*}
-we see that $\mathcal{B}\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
+we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
 \[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
@@
 
-Through a similar calculation, we see that $\mathcal{B}\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
+Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
 \[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
@@
 \end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\mathcal{L}_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
+ \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
 
@@
 
-and going to the spatial domain, $\mathcal{L}_{\zeta,\alpha_k}$ satisfies equation~\eqref{eqn:reg-higher3} if and only if $v$ satisfies
+and going to the spatial domain, $\laplace_{\zeta,\alpha_k}$ satisfies equation~\eqref{eqn:reg-higher3} if and only if $v$ satisfies
 
@@
 \end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\mathcal{L}_{\zeta_1,0}v_1$. 
+Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\laplace_{\zeta_1,0}v_1$. 
 %
@@
 \begin{align*}
-\mathcal{B}\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\mathcal{B}\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
+\borel\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\borel\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
 &=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
@@
 
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \mathcal{B}\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
+Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
 therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
@@
 
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\mathcal{B}\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
+analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
 
@@
 \begin{align*}
-\mathcal{B}_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+\borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
 z^{-n} & \mapsto \frac{\zeta^n}{n!}.
@@
 This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
-It's sometimes convenient to $\mathcal{B}_\textit{phys}(f) = \borel(z^{-1} f)$.
+It's sometimes convenient to $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
 
@@
 \begin{align*}
-\mathcal{B}_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+\borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
 \hbar^n & \mapsto \frac{\zeta^n}{n!}.
@@
 %Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-Then, by applying the two definitions of the Borel transform $\mathcal{B}_{\textit{phys}}$ and $\mathcal{B}$, on the one hand we have  
-\begin{align*}
-w_{1,2}(\zeta)&\defeq\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
+Then, by applying the two definitions of the Borel transform $\borel_{\textit{phys}}$ and $\borel$, on the one hand we have  
+\begin{align*}
+w_{1,2}(\zeta)&\defeq\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
 &=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
@@
 \begin{align*}
-\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
 &=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
@@
 %\begin{align*}
-%\mathcal{B}(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
+%\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
 %&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
@@
 \begin{equation}\label{Borel-W12}
-\mathcal{B}(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\mathcal{B}_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)
+\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta) 
 \end{equation}
@@
 \begin{equation}
-\frac{d}{d\zeta}\circ\mathcal{B}_{\textit{phys}}\tilde{\Phi}=\mathcal{B}\tilde{\Phi}.
-\end{equation}
-In particular, $\frac{d}{d\zeta}\circ\mathcal{B}_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
+\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\tilde{\Phi}=\borel\tilde{\Phi}.
+\end{equation}
+In particular, $\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
 
 %Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
-We want to compare $v_1$ with the \textit{physic} Borel transform $\mathcal{B}_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
+We want to compare $v_1$ with the \textit{physic} Borel transform $\borel_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
 %
 %\begin{align*}
-%\mathcal{B}_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
+%\borel_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
 %&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
@@
 \begin{align*}
-\hat{\phi}_+(\zeta):=\mathcal{B}\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\mathcal{B}\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
+\hat{\phi}_+(\zeta):=\borel\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
 \end{align*}
@@
 %\begin{align*}
-%\tilde{\phi}_{+}(\zeta)&=\mathcal{B}\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\tilde{\phi}_{-}(\zeta)&=\mathcal{B}\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
+%\tilde{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
+%\tilde{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
 %\end{align*}
@@
 \end{align*} 
-and up to a multiplicative constant they match our computations for $\mathcal{B}(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
+and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
 The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
@@
 \begin{align*}
-\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
+\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
 \end{align*} 
@@
 \begin{align*}
-\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\mathcal{B}}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
+\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
 \end{align*}

### 2023-05-09 exp-resurgence.tex
Updates from Overleaf

@@
 
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
+The {\em asymptotic expansion} map $\text{\ae}^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
 \end{defn}
@@
 \begin{enumerate}[start=4]
-\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
+\item By construction, $\text{\ae}^\theta \hat{\Phi} = \series{\Phi}$.
 It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\text{\ae}^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\text{\ae}^{\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\text{\ae}^{\theta}", "\text{($1$-Gevrey)}"] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 \begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
+\item Take the asymptotic expansion $\series{\Phi} = \text{\ae}^{-\theta} \Phi$.
 \item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
@@
 \end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\text{\ae}^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
@@
 \begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+I_{\alpha}(z) \arrow[r,"\text{\ae}^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\
@@
 
-\subsection{The geometry of the Borel transform}
-\begin{itemize}
-  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  \begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-\end{itemize}
-
 \subsection{The Laplace transform: analytic version}
@@
 Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \ref{laplace-tfm} shows\footnote{The argument cited still works in our generality.
+Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
 For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
@@
 we learn that
-\[ \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi. \]
+
+\begin{equation}
+    \label{change-chart}
+    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
+\end{equation}
 
@@
 We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-\color{gray}
-\subsection{The Borel transform}
-\color{gray}
-\begin{itemize}
-\item Action on differential equations.
-\begin{itemize}
-\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-\end{itemize}
-\end{itemize}
-\color{black}
-The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
+
+\subsection{The geometry of the Borel transform}
+
+The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+More precisely,   $\borel_\zeta$ is a $\C$-linear map
   \begin{align*}
@@
 \end{align*}
+where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
 In general, by linearity,
@@
 \end{align*}
-The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-Notice that we are at the level of formal series, so there are no convergence assumptions.
-However, there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
+
+It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
+\begin{align*}
+    \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
+    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
+    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
+    &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
+\end{align*}
+where in the second step we formally interchange the integral and the sum.
+
+\subsubsection{Action on transseries}
+
+A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$:
+
+\[T_{\alpha,\varphi}:=\sum_{n=0}^{\infty} e^{\alpha_n z} \varphi_n(z) \]
+
+The main feature of $T_{\alpha,\varphi}$ is that its asymptotics as $\text{ Re } e^{i\theta}z \to +\infty$ is $\varphi_0$.
+In fact, they play a crucial role in the theory of ODEs with irregular singularities.
+
+It is natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries.
+Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
+
+We extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
+
+Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, then from identity \eqref{change-chart}
+
+  \begin{align*}
+      \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z
+      }\laplace_{\zeta_\alpha,0}\varphi\right]
+  \end{align*}
+We compute the left-hand-side
+  \begin{align*}
+      \borel_\zeta\laplace_{\zeta,\alpha}\varphi&=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\\
+      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
+      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
+      &=\sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
+  \end{align*}
+  and the right-hand-side
+  \begin{align*}
+      \borel_\zeta\left[e^{-\alpha z
+      }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
+      }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
+      &=\borel_\zeta\left[
+      \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
+      &=\borel_\zeta\left[
+      \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
+      &=\borel_\zeta\left[
+      \sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
+      &= \sum_{n=0}^{\infty}a_n \zeta^n
+  \end{align*}
+In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
+
+\[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
+
+Then, comparing term by term in powers of $\zeta$ in the second identity we get 
+  \begin{align*}
+      \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})&=\zeta^n\\
+      \sum_{k=0}^n {n\choose k} \alpha^{n-k} \borel_\zeta(e^{-z\alpha} k! z^{-k-1})&=\sum_{k=0}^n {n\choose k} \alpha^{n-k}(\zeta-\alpha)^k
+  \end{align*}
+  and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
+\begin{itemize}
+    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
+\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
+[Not quite\ldots figure out how to make this precise.] }
+  \end{itemize}
+
+\subsubsection{Change of translation chart}
+
+Following Section \ref{translation}, we introduce $\borel_{\zeta_\alpha}$
+as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. Explicitly, from identity \eqref{change-chart}
+  \begin{align*}
+      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi
+  \end{align*}
+  now the LHS reads
+  \begin{align*}
+      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\left[e^{z\alpha} \int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\right]\\
+      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_n\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\right]\\
+      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_ne^{-z\alpha}\sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
+      &=\borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}  z^{-k-1}\right]
+  \end{align*}
+  the RHS is 
+  \begin{align*}
+      \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
+      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
+      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
+      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
+      &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
+      \end{align*}
+     If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
+      \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
+       \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
+ Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
+ \begin{align*}
+     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
+     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
+ \end{align*}
+ Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
+
+ \textcolor{magenta}{I think we should add a remark, saying that on $B$ there is no special coordinate, and this reflects on the fact that $\borel$ is defined equivalently for every choice of coordinates.}
+
+\subsection{The Borel transform}
+%\color{gray}
+%\begin{itemize}
+%\item Action on differential equations.
+%\begin{itemize}
+%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
+%\end{itemize}
+%\end{itemize}
+%\color{black}
+
+%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
+%\begin{align*}
+%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
+%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
+%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
+%\end{align*}
+%In general, by linearity,
+%\begin{align*}
+%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+%\end{align*}
+%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
+
+So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
 These formal series are the so-called Gevrey-$1$ series:
@@
 
-\subsubsection{Generalization of the Borel transform}
+\subsubsection{Action on power series with fractional exponents}
 The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
@@
 
-\textcolor{orange}{[check notation]}
-
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel(z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[(iv)] $\borel\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
+\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
+\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
+\item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
 \item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
-\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel(\tilde{\Phi}\tilde{\Psi}=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
+\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
 \end{itemize}
@@
 For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
+\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
 \end{lemma}
@@
 \begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
@@
 \end{align*}
-by reducing the integral to Euler's beta function \textbf{[DLMF 5.12.1]}. This establishes that
+by reducing the integral to Euler's beta function (see 5.12.1 in \cite{dlmf}). This establishes that
 \begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
 \end{equation}
@@
 \begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b],
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
 \end{equation}
@@
 However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
-For this reason, in Appendix~\cite{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
+For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
 
@@
 The higher Airy equation is
-\begin{equation}\label{eqn:airy-lucas}
+\begin{equation}\label{eqn:higher-airy}
 \left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
@@
 In \cite{Reid} \cite{Drazin-Reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as countour integral (\cite{DLMF} \S 9.13(ii))
+They are defined as countour integral (\cite{dlmf} \S 9.13(ii))
 
@@
 
-which is a generalized hypergeomtric equation (~16.8.5 \cite{DLMF}) with parameters
+which is a generalized hypergeomtric equation (~16.8.5 \cite{dlmf}) with parameters
 
@@
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel}
+\begin{equation}\label{eqn:mod-bessel-1/3}
 \left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.

### 2023-05-09 exp-resurgence.tex

@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\text{\ae}^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\text{\ae}^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\text{\ae}^{\theta}", "\text{($1$-Gevrey)}"] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 \begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\text{\ae}^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\
@@
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-
+\subsection{The geometry of the Borel transform}
+\begin{itemize}
+  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+It's a formal inverse of the $\laplace_{\zeta, 0}$.
+  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
+  \begin{itemize}
+    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
+\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
+[Not quite\ldots figure out how to make this precise.] }
+  \end{itemize}
+  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
+\end{itemize}
 \subsection{The Laplace transform: analytic version}
@@
 we learn that
-
 \begin{equation}
@@
 \end{equation}
-
 \subsubsection{Rescaling of translation structure}
@@
 We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-
 \subsection{The geometry of the Borel transform}
@@
 We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
-
 \begin{itemize}
@@
 \begin{align*}
-\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\

### 2023-05-09 exp-resurgence.tex
Redefine \aexp to put \ae in text mode

--- 2023-05-09 exp-resurgence.tex
@@
 \newcommand{\borel}{\mathcal{B}}
-\newcommand{\aexp}{\ae}
+\newcommand{\aexp}{\text{\ae}}
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
@@
 
-The {\em asymptotic expansion} map $\text{\ae}^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
+The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
 \end{defn}
@@
 \begin{enumerate}[start=4]
-\item By construction, $\text{\ae}^\theta \hat{\Phi} = \series{\Phi}$.
+\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
 It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\text{\ae}^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\text{\ae}^{\theta}", "\text{($1$-Gevrey)}"] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 \begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \text{\ae}^{-\theta} \Phi$.
+\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
 \item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
@@
 \end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\text{\ae}^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
@@
 \begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\text{\ae}^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\

### 2023-05-09 exp-resurgence.tex

--- 2023-05-09 exp-resurgence.tex
@@
 \begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 & \\

### 2023-06-17 exp-resurgence.tex
Work on Borel regularity proofs

@@
 where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $\alpha_1, \ldots, \alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
+Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
+
+Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
 Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
@@
 \begin{equation}
-\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
+\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
 \end{equation}
@@
 \subsubsection{Frequency}\label{transl-freq}
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+\textcolor{DarkCyan}{[Instead of thinking of $z$ this way, maybe we should think of it as the coordinate on the ``generic cotangent fiber'' over a non-singular point?]} The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
 At an ordinary point, we can define $z$ simply as the map
@@
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+\color{gray}
 \subsection{The geometry of the Borel transform}
@@
 \end{itemize}
+\color{black}
 \subsection{The Laplace transform: analytic version}
@@
 Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
+A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
 Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
@@
 \textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-\subsubsection{Action on integral operators}\label{L-int-op}
-When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm} 
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-for all $\lambda \in (0, \infty)$.
+
 \subsubsection{Change of translation chart}\label{translation}
@@
 We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
+
+\subsubsection{Action on integral operators}\label{L-int-op}
+%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
+%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on
+
+It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
+\begin{align*}
+\partial^{\lambda}_{\zeta, \alpha}\,\partial^{\mu}_{\zeta, \alpha} & = \partial^{\lambda+\mu}_{\zeta, \alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
+However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
+Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
+We'll use the {\em Riemann-Liouville} convention.
+\begin{definition}
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
+\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
+\end{definition}
+The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+
+Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
+Here's what's nice about it.
+
+You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\begin{equation}%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\end{equation}
+for all integers $n \ge 0$.
+
+\color{magenta}
+Furthermore, if $\varphi\in\mathcal{E}_{\zeta,\alpha}$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\mathcal{E}_{\zeta,\alpha}$ and 
+\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
+for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by
+
+\begin{equation}
+    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
+\end{equation}
+
+Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\mathcal{E}_{\zeta_\alpha,0}$ and 
+\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
+for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by
+
+\begin{equation}
+    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
+\end{equation}
+
+Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
+However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
+
+We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
+
+%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
+In fact, as we will see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
+
+%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
+
+\color{black}
+
 \subsection{The geometry of the Borel transform}
-
-The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
+\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
+Here, we're thinking of $z$ as the standard coordinate on $T^*B_{\zeta = 0}$, as described in Section~\ref{transl-freq}.
+We can get a function on $T^*B_{\zeta = \alpha}$ instead by taking the Laplace transform with respect to the coordinate $\zeta_\alpha$ defined by $\zeta = \zeta_\alpha + \alpha$:
+\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}. \]
+On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
+This formal inverse is called the {\em Borel transform}.
+
+The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
+\begin{align*}
+\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
+\end{align*}
+In general, by linearity,
+\begin{align*}
+\borel\textcolor{orange}{_\zeta}\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+\end{align*}
+If a function $\varphi$ belongs to $\mathcal{E}_\zeta$, and its Taylor series
+\[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
+has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{MS}:
+\begin{align*}
+  \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
+  &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
+  &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
+\end{align*}
+As a result, we can recover the Taylor series $\series{\varphi}$ from the series
+\[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
+using the Borel transform:
+\begin{align*}
+\borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
+&=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
+\end{align*}
+We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*B_{\zeta = 0}$.
+
+If we'd expanded $\varphi$ as a Taylor series $\series{\varphi}_\alpha$ in the translated coordinate $\zeta_\alpha$ from above, we could've taken the Laplace transform $\laplace_{\zeta_\alpha,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*B_{\zeta = \alpha}$.
+Using the Borel transform with respect to $\zeta_\alpha$, defined like before as a formal inverse of $\laplace_{\zeta_\alpha,0}$
+
+\begin{align*}
+     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
+     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
+ \end{align*}
+
+we could again recover $\series{\varphi}_\alpha$.
+
+It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha}$, as discussed in Section~\ref{transl-borel}.
+
+%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
+%%\begin{align*}
+%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
+%%z^{-n-1} & \mapsto \frac{\zeta_\alpha^n}{n!}.
+%%\end{align*}
+
+%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.
+
+\color{Peru}
+\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
 More precisely, $\borel_\zeta$ is a $\C$-linear map
@@
 where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
-In general, by linearity,
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-\end{align*}
-
-It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
+
+%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
 \begin{align*}
@@
 where in the second step we formally interchange the integral and the sum. 
-
+\color{black}
 \subsubsection{Action on transseries}
@@
 
-Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, then from identity \eqref{change-chart}
-
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha,0}\varphi\right]
-  \end{align*}
-We compute the left-hand-side
+Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, %then from identity \eqref{change-chart}
+
+ % \begin{align*}
+  %    \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z }\laplace_{\zeta_\alpha,0}\varphi\right]
+  %\end{align*}
+%We compute the left-hand-side
   \begin{align*}
@@
   \end{align*}
-  and the right-hand-side
-  \begin{align*}
-      \borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
-      }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-      &= \sum_{n=0}^{\infty}a_n \zeta^n
-  \end{align*}
-In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-
+  %and the right-hand-side
+  %\begin{align*}
+   %   \borel_\zeta\left[e^{-\alpha z
+    %  }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
+     % }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
+     % &=\borel_\zeta\left[
+     % \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
+     % &=\borel_\zeta\left[ \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
+    %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
+     % &= \sum_{n=0}^{\infty}a_n \zeta^n
+  %\end{align*}
+%In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
+hence we require the following equality to hold  
 \[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
 
-Then, comparing term by term in powers of $\zeta$ in the second identity we get 
+and, comparing term by term in powers of $\zeta$ %in the second identity we get 
   \begin{align*}
@@
   \end{align*}
-  and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
+  thus we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
 \begin{itemize}
@@
 
-\subsubsection{Change of translation chart}
-
-Following Section \ref{translation}, we introduce $\borel_{\zeta_\alpha}$
-as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. Explicitly, from identity \eqref{change-chart}
+\subsubsection{Change of translation chart}\label{transl-borel}
+
+Following Section \ref{translation}, we can recover the definition of $\borel_{\zeta_\alpha}$
+as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $\alpha$. Explicitly, from identity \eqref{change-chart}
   \begin{align*}
@@
   \end{align*}
-  now the LHS reads
+  now the left-hand-side reads
   \begin{align*}
@@
   \end{align*}
-  the RHS is 
-  \begin{align*}
-      \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
-      &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
-      \end{align*}
+  %the RHS is 
+  %\begin{align*}
+   %   \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
+    %  &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
+     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
+     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
+     % &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
+     % \end{align*}
      If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
-      \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
+     % \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
        \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
@@
 
-\subsection{The Borel transform}
+\subsection{The Borel transform on Gevrey-$1$ series}
 %\color{gray}
@@
 
-\subsubsection{Properties of the Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
+\subsection{Properties of the Borel transform}
+We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
 \begin{itemize}
@@
 \item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
-\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
 \end{itemize}
@@
 \begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
@@
 \begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
 \end{equation}
@@
 \begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
 & = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
@@
 
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
+(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
 
@@
 
-(vi) see Definition 5.12 and Lemma 5.14 \cite{MS16}. 
 \end{proof}
 
+\subsection{The convolution product}\label{convolution}
+
+The space of Gevrey-$1$ formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
+The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta$.
+Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then
+\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}\]
+
+and $\delta:=\borel 1$. In addition, it follows that the convolution product $\ast$ can be explicitly characterized as
+
+\begin{equation}
+    \tilde{\psi}\ast\Tilde{\phi}=\int_0^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
+\end{equation}
+
+the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 \cite{MS16}.
+
+The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_\alpha B$ and let $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$
+
+\[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=\series{\psi}\ast \series{\phi}=\int_{0}^{\zeta_\alpha}\series{\psi}(\zeta_\alpha-\zeta')\series{\phi}(\zeta')d\zeta'\]
+
+Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_0 B$, we define  \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}\]
+then $\ast_\alpha$ can be explicitly written as
+
+\begin{equation}
+    \tilde{\psi}\ast_\alpha\Tilde{\phi}=\int_\alpha^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
+\end{equation}
+where $\series{\phi}=\borel_\zeta\series{\Phi}$ and $\series{\psi}=\borel_\zeta\series{\Psi}$.
+We also introduce the unit $\delta_\alpha$ as \[\delta_\alpha\ast_\alpha\borel_\zeta\series{\Phi}=\borel_\zeta(1\cdot\series{\Phi})=\borel_\zeta\laplace_{\zeta,\alpha}\phi=\phi\]
+thus $\delta_\alpha\ast_\alpha\phi=\phi\ast_\alpha\delta_\alpha=\phi$.
+
 \begin{remark}
-We notice that properties (i) and (ii) are special cases of property (vi), indeed we can use the convolution product 
+We notice that properties (i) and (ii) are special cases of the convolution product:
 \begin{align*}
@@
 
+\begin{remark}
+We can express the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ as convolution products, and we will see how the definitions vary depending on the fibers of $T^*B$ in consideration.
+
+We first assume $\series{\Phi}=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\mathcal{E}_{\zeta,\alpha}$, then for every $\lambda\in (0,\infty)$
+\begin{align*}
+    \borel_\zeta(z^{-\lambda}\series{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta z^{-\lambda}\ast_\alpha\phi
+\end{align*}
+hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\phi.\]
+
+%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
+Then, we assume $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ and we get for every $\lambda\in (0,\infty)$
+\begin{multline*}
+    \borel_{\zeta_\alpha}(z^{-\lambda}\series{\Phi})=\borel_{\zeta_\alpha}(z^{-\lambda}\laplace_{\zeta_\alpha,0}\phi)=\borel_{\zeta_\alpha}(\laplace_{\zeta_\alpha,0}\partial_{\zeta_\alpha,0}^{-\lambda}\phi)=\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha} (\zeta_\alpha-t)^{\lambda-1}\phi(t+\alpha)dt\\
+    =\borel_{\zeta_\alpha}(z^{-\lambda})\ast\phi(\zeta_\alpha+\alpha)
+\end{multline*}
+hence, recalling $\zeta=\zeta_\alpha+\alpha$ \[\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}\]
+
+Finally, recall that for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
+$\fracderiv{-\lambda}{\zeta_\alpha}{0}\varphi$ coincide, therefore 
+\begin{align}\label{change_chart_convolution}
+    \borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}
+\end{align}
+in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $\alpha\in B$.
+\end{remark}
+
+\color{black}
+
 \subsection{Differential equation}
@@
 \subsubsection{Order shifting}\label{shifting}
-\textcolor{orange}{[why the name order shifting?]}
+\textcolor{orange}{[Veronica:I think we should move this section, maybe when we do examples]}
 Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
@@
 
-\begin{theorem}\label{thm1-dim}
 Let $\mathcal{P}$ be a linear differential operator 
@@
 \begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ \textcolor{orange}{[} i.e such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
@@
 
-Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-
-\color{brown}
-\begin{equation}
-\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-\color{black}
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
+\begin{theorem}\label{thm1-dim}
+In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
+\begin{equation}\label{P-hat_j}
+\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+\end{equation}
+such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
+${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
 \end{theorem}
@@
 It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
-In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$.
-$Q$ is also a polynomial defined at $\zeta_j=0$.
+In fact, $P(-\zeta_j-\alpha_j)=P(-\zeta)$ is a polynomial also defined at $\zeta=\alpha_j$ and by assumption $P'(-\alpha_j)\neq 0$.
+$Q$ is also a polynomial defined at $\zeta=\alpha_j$.
 Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
@@
 \begin{align*}
-&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
+&\partial_{\zeta,\alpha_j}^{-2}\circ\left[R_0(\partial_{\zeta,\alpha_j}^{-1})+R_1(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)+...+R_d(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta,\alpha_j}^\lambda\circ r_\lambda \\
+&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta)^k.
 \end{align*}
@@
 
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
+Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=-\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ \footnote{Since $\sup\Lambda\leq -2$ we can assume $\varepsilon=1$ in Theorem 2.1.3 of {\tt regular Volterra}}.
 
@@
 
+\begin{lemma}
+ Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined by \eqref{P-hat_j}.
+If $\hat{\psi}_j$ admits a Laplace transform $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.
+\end{lemma}
+
+\begin{proof}
+    \begin{align*}
+        \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
+    \end{align*}
+    \textcolor{magenta}{[do we really need the assumption on $\theta_j$, namely $\theta_j\neq\arg(\alpha_j-\alpha_k)$ for every $k=1,...,d$?]} \textcolor{orange}{[At first, I didn't think we need that assumption for the Volterra equation existence theorem to hold, or for the Laplace transform to exist.
+When the integration path crosses over $\alpha_k$, I thought that only $\psi_k$ would jump, so only $\psi_k$ would need to become ill-defined when the integration path goes through $\alpha_k$.
+\textbf{However, it's true that $v_1$ and $v_{-1}$ each blow up at both singularities, so maybe there's a problem with the construction!}]}
+\end{proof}
+
 \begin{theorem}\label{thm2-dim}
-For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$ for every $j=1,...,d$.
+%For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
+Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
+For every $j=1,...,d$, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$.
 Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
@@
 \begin{proof}
-We divide the proof in the following steps:
-\begin{itemize}
-\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\borel\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
-\item[$(c)$] prove that $\laplace_{\zeta_j}^{\theta_j}\circ\borel\series{\Psi}_j\propto \Psi_j $. 
+We divide the proof into the following steps:
+\begin{itemize}
+\item[$(a)$] prove that $\hat{\psi}_j(\zeta_j)$ admits Laplace transform (see Lemma \ref{step a}) 
+\item[$(b)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
+\item[$(c)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
 \end{itemize}
@@
 Step $(c)$ clearly follows from steps $(a)$ and $(b)$.
-We now prove step $(b)$: first notice that if $\series{\Psi}_j$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
-
-\begin{equation}
-\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
-\end{equation}
-
-\color{brown}
-Then taking the (formal) Borel transform:for every $j=1,...,d$ we denote $\zeta_j=\zeta-\alpha_j$ and we consider the Borel transform of $\mathcal{P}\series{\Psi}_j$ in the coordinate $\zeta_j$
-
-\begin{multline*}
-\borel\left(\mathcal{P}\series{\Psi}_j\right)=\borel\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
-\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
-\left[P(-\zeta)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
-\end{multline*}
+In fact, from step $(b)$ and Theorem 3.1 $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+Then, by step $(a)$ we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.
+
+We now prove step $(b)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$.
+Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.
+
+%First notice that if $\series{\Psi}_j=e^{-\alpha_jz}\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
+
+%\begin{equation}
+%\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
+%\end{equation}
+
+%Hence
+
+%\begin{
+
+%Then we take the (formal) Borel transform $\borel_\zeta$ of  $\mathcal{P}_j \sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$
+
+\begin{align*}
+  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_j\right)&= \left[P(-\zeta)+1\ast_{\alpha_j} Q(-\zeta)+\zeta \ast_{\alpha_j} \left(\sum_{r=0}^{d}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha_j}(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\
+  &=\left[P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j} \left(\sum_{r=0}^{d}R_r(\fracderiv{-1}{\zeta}{\alpha_j} )(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\&=\hat{P}_j\tilde{\psi}_j(\zeta_j)
+\end{align*}
+%\begin{multline*}
+%\borel_\zeta\left(\mathcal{P}\series{\Psi}_j\right)=\borel_\zeta\left[e^{-\alpha_j z}\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right]=\\
+%\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
+%\left[P(-\zeta)+\partial_{\zeta_j,0}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
+%\end{multline*}
 %where 
@@
 Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0. 
-from the properties of the Borel transform we deduce that $\hat{P}\series{\psi}_j=0$ first notice that $\series{\psi}_j$ is a solution of
+\end{proof}
+
+\color{Turquoise}
+\begin{lemma}\label{step a}
+    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
+\end{lemma}
+
+\begin{proof}
+    We will prove the following: 
+    \begin{itemize}
+        \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
+        \item along that direction, the germ $\tilde{\psi}_j$ grows sub-exponentially. 
+    \end{itemize}
+    The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
+\textcolor{magenta}{[why they are there?
+add comment][Take a more careful look at Lemma 3.9 \cite{Del}]}
+\end{proof}
+
 \color{black}
-\end{proof}
-
 \subsection{Borel regularity for thimble integrals}
 
-Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
+Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic Morse function $f\colon X\to\C$ with only simple critical points. Set
 \begin{equation}\label{exp-int}
@@
 \end{equation}
-where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
-For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
+where $\mathcal{C}$ is a contour chosen to make the integral well-defined.  
+At a Morse critical point $x_\alpha$ of $f$, the saddle point approximation gives the formal series 
 \begin{equation}
@@
 Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+
 \begin{theorem}\label{thm:maxim} Let $N=1$.
@@
 \begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\borel(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
+\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1, thus $\hat{\varphi}_\alpha(\zeta)\defeq\borel_\zeta(\tilde{\varphi}_\alpha)$ converges near $\zeta=\zeta_{\alpha}$
 \item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
@@
 \end{theorem}
+
+\textcolor{magenta}{[In the proof we use $\zeta_\alpha=f(x_\alpha)$; however this is in contrast with our notation as $\zeta_\alpha=\zeta-f(x_\alpha)$. Should we change it?]}
 \begin{proof}
@@
 \textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
 \[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
@@
 
-By the steepest descent method,
+\color{magenta}{By the steepest descent method,
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 \[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
+as $z \to \infty$. [Veronica: I don't think this is the claim of steepest descendet method]} 
+\color{black}\textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
 \begin{align*}
@@
 & = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
+& \color{magenta}\ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
+\end{align*}
+\color{black}
 which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
@@
 \end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
+is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.
+\color{magenta}
+\begin{claim}
     \[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\end{claim}
+
+By the dominant convergence theorem ...
+\begin{equation}
+    e^{-zf(x_\alpha)}I_\alpha(z)\approx\sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,\left[z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)-2e^{-z\varepsilon^2/2}\sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\right]
+\end{equation}
+hence we have to estimate the growth of 
+\[-2\sqrt{2\pi} e^{-z\varepsilon^2/2} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\]
+
+as $\Re z\to\infty$. 
+\color{black} %Hence,
+%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
@@
 We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
+\textbf{[Resolve discrepancy with previous calculation.]} Note that
 \begin{align*}
@@
 
-Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
+Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega):= \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
 For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.

### 2023-07-08 figures/contours.jl
Draw multiple lifts of zeta contour

@@ -18,8 +18,10 @@ function path_scale(n, k)
     return cos(π*(1/2 - skip/3n)) / abs(cos(π*k/n))
   end
 end
-u_path(θ, off, n = 3, k = 1) = t -> path_scale(n, k) * exp(-im*θ/n) * (cosh(π*(k/n)*im + t) - dot(off, [exp(π*(k/n)*im), exp(-π*(k/n)*im)]))
-u_jet(θ, off, n = 3, k = 1) = t -> (u_path(θ, off, n, k)(t), path_scale(n, k) * exp(-im*θ/n) * sinh(π*(k/n)*im + t))
+##u_path(θ, off, n = 3, k = 1) = t -> path_scale(n, k) * exp(-im*θ/n) * (cosh(π*(k/n)*im + t) - dot(off, [exp(π*(k/n)*im), exp(-π*(k/n)*im)]))
+##[TO DO] find a convenient family of u paths that all project to the same ζ path
+u_path(θ, off, n = 3, k = 1) = t -> exp(-im*θ/n) * cosh((π*k*im + (2k < n ? 1 : -1)*((π/3)*im/(1+t^2/12) + t)) / n)
+u_jet(θ, off, n = 3, k = 1) = t -> (u_path(θ, off, n, k)(t), exp(-im*θ/(2k < n ? 1 : -1)*n) * ((2k < n ? 1 : -1)*((π/3)*im * (-t/6) / (1+t^2/12)^2 + 1))/n * sinh((π*k*im + (2k < n ? 1 : -1)*((π/3)*im/(1+t^2/12) + t)) / n))
 
 function T_jet(n)
   T_pt = convert(Polynomial, ChebyshevT(push!(fill(0, n), 1)))
@@ -64,7 +66,7 @@ function edgept(θ)
 end
 
 # for a nice contour with θ at π or 4π, set `off` to (1.3, 0)
-function plotcontour(θ = 0, off = (0, 0), n = 3, k = 1; tag = "test")
+function plotcontour(θ = 0, off = (0, 0), n = 3, lifts = [1]; tag = "test")
   dark = RGB(0, 0.5, 0.7)
   light = RGB(0.6, 0.9, 1.0)
   
@@ -73,41 +75,51 @@ function plotcontour(θ = 0, off = (0, 0), n = 3, k = 1; tag = "test")
   crit_pos = crit[ζ.(crit) .> 0]
   crit_neg = crit[ζ.(crit) .< 0]
   
[…]

### 2023-07-20 reg-sing-volterra.tex
Fix typo in norm bound for algebraic integral operators
Veronica, thanks for spotting the typo independently. Now I'm sure
it wasn't just something I was too tired to understand.
Start adding exponential cutoff to function spaces

@@
 \newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
+\newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
 \DeclareMathOperator{\Ai}{Ai}
+
+% drafting environments
+\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
 
@@
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
+\subsection{Weighted holomorphic $L^\infty$ spaces}
 Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
@@
 For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
-We'll call this space $\holoL{\infty, \sigma}_Z(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
+We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
 \begin{align*}
-\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
-\phi & \mapsto \zeta^{-\sigma} \phi
+\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
+\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
 \end{align*}
@@
 \begin{align*}
-\holoL{\infty, \rho}_Z(\Omega) & \to \holoL{\infty, \rho+\delta}_Z(\Omega) \\
+\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
 f & \mapsto \zeta^\delta f
@@
 is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
+\subsection{Graded algebra structure}
+For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
+\begin{verify}
+\begin{align*}
+\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
+& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
+& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
+& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
+\end{align*}
+\end{verify}
+Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade.
+For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
+\subsection{Norms of effectively finite-order operators}
+\begin{itemize}
+\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
+\begin{align*}
+\|mf\|_{\infty, \sigma; Z} =
+\end{align*}
+\end{itemize}
+
+which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
 %------------------------------------------------------------------------
+\color{SteelBlue}
 \section{Integro-differential equations {[from {\tt airy-resurgence}]}}
@@
 \end{center}
-\color{black}
+\color{SteelBlue}
 

### 2023-07-20 draft--Tu.tex

--- 2023-06-17 exp-resurgence.tex
@@
 \DeclareMathOperator{\Re}{Re}
+\let\Im\relax
+\DeclareMathOperator{\Im}{Im}
 
@@
 \newcommand{\C}{\mathbb{C}}
+\newcommand{\Q}{\mathbb{Q}}
 \usepackage{tikz}
@@
 
-\title{Borel regularity for ODEs and thimble integrals}
+\title{Borel regularity for ODEs and thimble integrals \\ \textbf{[DRAFT]}}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 and its constant multiples. As another example, you might rewrite the integral
-\color{DodgerBlue}
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
-\color{black}
 \[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
@@
 using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{DodgerBlue}
-\begin{align*}
-& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
-& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
-& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
-\end{align*}
-\color{black}
 
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
+\textcolor{orange}{[Nikita has a complementary picture where the position domain is the cotangent fiber?
 Ask more about this.]}
 \item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
 \end{enumerate}
@@
 is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
+\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
 over all orders $n$.
 
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
+The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
 \end{defn}
@@
 \item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
-It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
+It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
 \end{enumerate}
@@
 \end{itemize}
-\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
+%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
 
@@
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
-
-Watson's theorem was soon improved by Nevanlinna (see a modern proof in Nikolaev, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15), and improved again later by Sokal (Sokal, ``An improvement of Watson's theorem on Borel summability'').
+Watson showed a century ago \cite{watson} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
+
+Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
 These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
@@
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
+\begin{center}
+\begin{tikzpicture}
+\newcommand{\size}{3}
+\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
+\newcommand{\ang}{35}
+\newcommand{\dis}{1.2}
+\begin{scope}
+  \clip (-\size, -\size) rectangle (\size, \size);
+  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
+  \begin{scope}[violet]
+    \draw (0, 0) -- (-\ang:\outsize);
+    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
+    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
+    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
+  \end{scope}
+\end{scope}
+%%\begin{scope}[violet]
+%%  \draw (0, 0) -- (center);
+%%  \fill (center) circle (0.05);
+%%\end{scope}
+\draw[->] (-\size, 0) -- (\size, 0);
+\draw[->] (0, -\size) -- (0, \size);
+\node[anchor=north east] at (\size, \size) {$z$};
+\end{tikzpicture}
+\end{center}
 
@@
 \begin{enumerate}
-\item Solving a linear ODE of level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Definition~5.5]{diverg-resurg-iii}}.
+\item Solving a linear ODE of single level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
 One example is Equation~\eqref{eqn:bessel-rescaled-1}.
 The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type.
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e.
+$|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).
 
@@
 First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
+Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
 
@@
 
-\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
+\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
+As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
 \begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
+\end{equation}
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{A function $f$ is of exponential type if $|f(z)|\leq C e^{-a|z|}$ for $C,a>0$.
+Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
 Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
@@
 where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
+\color{Tan}
 \[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
+\color{DarkTurquoise}
+\[ \frac{P_d}{w^{2d}}  \left(\frac{\partial}{\partial w}\right)^d , \]
 corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).
@@
 
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
+Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Braaksma,Loday-Richaud, check]}.
 Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
@@
 This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
-14).
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method \textbf{(see Balser chap.
+14)}.
 Conversely, we can explicitly build a distinguished basis of analytic solutions:
@@
 \begin{equation}
-\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
 \end{equation}
@@
 such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
+${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ for a small compact domain $\Omega\subset\C$. 
 \end{theorem}
@@
 In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
+Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
 
@@
 There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}.
+Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII}\cite{loday-Remy2011}}.
 It can indeed be seen as a consequence of ``resurgence'' of the ODE.
@@
 
-\begin{remark}
-Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
-\textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
-For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$?
-Check carefully the argument of multi-summability]}
-\end{remark}
-
-\color{gray}
-\begin{itemize}
-\item Can we see there exists a distinguished basis in a purely analytic way?
+%\color{gray}
+%\begin{itemize}
+%\item Can we see there exists a distinguished basis in a purely analytic way?
 YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-\end{itemize}
-\begin{itemize}
-\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+%\end{itemize}
+%\begin{itemize}
+%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
 (proof based on existence theorem \ref{frac_int_exist})
-\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
 Then this is the only solution that can be expressed as a Laplace transform.
@@
 
-\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-where the arrow in red are a consequence of multisummability.
+%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+
+%\begin{center}
+%\begin{tikzcd}
+%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+%& & IE & & \\
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\end{tikzcd}
+%\end{center}
+
+%where the arrow in red are a consequence of multisummability.
 In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
 On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-\item  
-there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-\item  M.A.E.T.
+%\item  
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%\item  M.A.E.T.
 says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
 Our method uses just Laplace transform.
-\item How do we know we are picking the same frame?
+%\item How do we know we are picking the same frame?
 from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
 From uniqueness result we get a frame equivalent to Ecalle's frame.
-\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
 Borel regularity is instead based on the analytic solution in the $z$-plane.
 The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-\end{itemize}
-
-\color{DarkBlue}
-
-\subsubsection{Why does Borel resummation work for thimbles integrals?}
-
-\begin{itemize}
-\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-\begin{itemize}
-\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-\end{itemize} 
-\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
-His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
-\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
-\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+%\end{itemize}
+
+\color{black}
+
+\subsubsection{Why does Borel resummation work for thimble integrals?}
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
+
+\[
+I(z):=\int_{\mathcal{C}}e^{-zf}\nu
+\]
+
+regarded as holomorphic functions in the position domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
+In fact, we introduce homology and cohomology groups $H_{z,\cdot}^B$ and $H_{dR,z}^\cdot$ so that the function $I(z)$ will represent the Poincar\'e pairing.
+
+We begin with the definition of $H_{z,\cdot}^B$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
+We follow \cite{pham} and $\S 1$ in \cite{Arnold}.
+Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
+\begin{align*}
+    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
+    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
+\end{align*}
+and $H_{z,\cdot}^B:=H_\cdot(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{z,\cdot}^B$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t.
+} \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}.
+Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{f(\alpha_j)\}$.
+This leads to further identifications:
+
 \begin{equation}
-I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-\end{equation}
-
-then the following diagram is commutative
+    H_{z,n}^B\cong \bigoplus_{f(\alpha_i)} H_{n}(B_j, B_j^+(\theta))
+\end{equation}
+where $B_j:=f^{-1}(B_r(f(\alpha_j)))$ is the preimage of a small ball or radius $r$, containing only the critical value $\alpha_i$ and $B_j^+(\theta):=f^{-1}\left(B_r(f(\alpha_j))\cap \{ \Re (\zeta e^{i\theta})\geq r/2\}\right)$.
+Notice that we are not assuming $f$ to be Morse, hence $B_j$ may have different connected components.
+Then
+
 \begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-\end{tikzcd}
-\end{equation}
-\begin{itemize}
-\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the fractional derivative formula.
-\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
-\begin{equation}
-mmm
-\end{equation} 
-\end{itemize}
-\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-\begin{itemize}
-\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
-\end{itemize}
-\end{itemize}
-
-\color{DarkGreen}
+    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
+     0 & \text{otherwise}
+    \end{cases}
+\end{equation}
+where $|p_j-f(\alpha_j)|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical point $\alpha_j$.
+
+\begin{center}
+    \begin{tikzpicture}
+        \draw (2,2) circle (2);
+        \node[font=\tiny,red] at (1,1) {$f(\alpha_1)$};
+        \draw (1,1.2) circle (0.4);
+        \node[font=\tiny,red] at (3,1.3) {$f(\alpha_2)$};
+        \draw (3,1.5) circle (0.4);
+        \node[font=\tiny,red] at (2.3,3.2) {$f(\alpha_3)$};
+        \draw (2.3,3.4) circle (0.4);
+        \node[above,red] at (1,1) {$\bullet$};
+        \node[above,red] at (3,1.3) {$\bullet$};
+        \node[above,red] at (2.3,3.2) {$\bullet$};
+        \draw[rounded corners] (2.7,1.76)--(2,2)--(1,3.71);
+        \draw[rounded corners] (1,1.6)--(0.5,2)--(1.2,2.5)--(1,3.71);
+        \draw[rounded corners] (1.9,3.4)--(1,3.71);
+        \node[font=\tiny, above] at (1,3.71) {$p_0$};
+        \node[font=\tiny, above] at (2.7,1.76) {$p_2$};
+        \node[font=\tiny, above] at (1,1.6) {$p_1$};
+        \node[font=\tiny, above] at (1.75,3.4) {$p_3$};
+    \end{tikzpicture}
+\end{center}
+
+From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
+Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $\alpha_j$ there are local coordinates $x_1,...,x_N$ such that
+\[f=f(\alpha_j)+\sum_{k=1}^N x_k^2\]
+
+and for $p=c e^{i\theta}\in\C$, the thimble $\Lambda_j(p)$ is defined by 
+\begin{align*}
+    \Im(x_1)=...=\Im(x_N)=0 \text{ and } \Re(e^{-i\theta/2}x_1)^2+....+\Re(e^{-i\theta/2}x_N)^2\leq c
+\end{align*}
+Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite{Witten} page 10).
+
+Hence we deduce that $H_{z, N}^B$ admits a distinguished basis of Lefschetz thimbles labeled by critical points.
+
+Then we recall the definition of $H_{dR,z}^\cdot$: it is the hypercohomolgy of the twisted de Rham complex
+
+\begin{equation*}
+    H_{dR,z}^\cdot:=\mathbb{H}^\cdot( \Omega^\bullet(X), zd+df)
+\end{equation*}
+where $(\Omega^\bullet(X), d)$ is the de Rham complex of differential forms on $X$.
+
+Therefore, the integral $I(z)$ can e regarded as the image of the following map:
+
+\begin{align*}
+    \int \colon  H_{z,N}^{B} \times & H_{dR,z}^N \to \C \\
+       [\mathcal{C}] ,\,\, & [\nu] \to \int_{\mathcal{C}}e^{-zf}\nu
+\end{align*}
+
+\textcolor{orange}{[the Betti--de Rham isomorphism is necessery?]}
+
+Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_\alpha$, namely the integrals over Lefschetz thimbles labeled by the critical points $\alpha\in\text{Crit}(f)$.
+
+As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$).
+The jumps can be described geometrically using the theory of Picard--Lefschetz.
+Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
+
+Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, Andersen, Mistergad, the Stirling series for Gamma function in \cite{Maxim_slide_ERC}).
+
+Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$.
+
+These questions have been classically addressed by Pham (\S 3.3 \cite{pham}), Malgrange (Theorem 6 in \cite{Malgrange22}), Delabere and Pham \cite{Delabaere-Pham99}, Berry and Howls \cite{berry1991hyperasymptotics}, Dunne and Unsal \cite{dunne-unsal}, and others.
+\textcolor{orange}{[add references]}
+
+Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+
 We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
@@
 A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-Suppose every singularity of $B$ is a critical value of $f$.
-\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
-\textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
-\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
-
-\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
+Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \overline{X} \to \overline{B}$ with non--degenerate critical points \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
+\textcolor{red}{Suppose every singularity of $B$ is a critical value of $f$.[Veronica: Is it a good assumption?]} \textcolor{DarkGreen}{\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
+How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)?
+We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}} For each critical point $\alpha_j$, let $\Gamma_j$ be the ray going rightward from $f(\alpha_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $f(\alpha_j)$.
+These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
+The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves \textcolor{magenta}{[add picture]}, as long as $\Gamma_j$ misses the other critical values of $f$.
+The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $\alpha_j$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$.
+%The {\em thimble integral}
+%\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
+%is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
+
+Then, our main result for thimble integrals is proving that $1$- dimensional thimble integrals are indeed Borel regular:
+
+\begin{theorem}[see Theorem \ref{thm:maxim}]
+    Let $\tilde{I}_{j}(z)\defeq e^{-zf(\alpha_j)}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
+Then:
+\begin{enumerate}
+\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is Gevrey-1, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\zeta_{j}+f(\alpha_j)$
+\item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $f(\alpha_j)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item For any $\zeta$ on the ray going rightward from $f(\alpha_j)$, we have
+\begin{multline}
+\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta}{f(\alpha_j)} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
+\end{multline}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([f(\alpha_j), \zeta])$.
+Notice that $\Lambda_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\Lambda_j$.]}
+\end{enumerate}
+\end{theorem}
+
+The idea of the proof is sketched below and represented in the following diagram:
+\[
+\begin{tikzcd}
+{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
+& & &\\
+\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
+\end{tikzcd}
+\]
+
+On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
+as the Laplace transform of a function $\iota_j$.
+In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}.
+On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal Gevrey-1 series.
+Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
+At this point we realise that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
+In a nutshell, thimble integrals are Borel regular because they are Laplace transforms.
 
@@
 This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],[Delabere \& Howls, Howls, Dingle]}.
-
-\color{DarkTurquoise}
-Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls}, \cite{dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.
+
+%Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
 Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
 This data defines the {\em exponential integral}
-\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-a holomorphic function on the right half-plane parametrized by $z$.
+%\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
+%a holomorphic function on the right half-plane parametrized by $z$.
 It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
 \textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
-
-\color{black}
 
@@
 In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
+Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.
 
@@
 If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
+\textcolor{magenta}{[Add this part in Airy with pictures]}
 
@@
 Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
-Borel regularity will be evident from the explicit computations.
-Some examples have been discussed many times, using different approaches and conventions.
+On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+
+Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
 We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
-The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
+For instance, for the Airy function we will make a comparison with \S 2.2 in \cite{lectures-Marino}, \S 6.14 in \cite{diverg-resurg-i}, and \S 2.2 \cite{kawai-takei}).
+The anharmonic oscillator was also discussed in (Bender--Wu, Appendix B in \cite{aniceto2019primer}).
 Other example haven't been discussed much, as for Airy--Lucas functions.
 
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}, \cite{loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
+For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
 Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
@@
 %\end{itemize}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean to be Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
-\end{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
 
 \color{black}
-%\end{itemize}
-\begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
-\item The resummation method works correctly for functions that satisfy that assumption.
-\item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
-\begin{itemize}
-\item Different aspects of this example appear in various places (Mari\~{n}o, Kawai--Takei, Sauzin). We give a detailed, unified treatment.
-\end{itemize}
-\item We can generalize this argument to all $K_\nu$ with $\nu \in \mathbb{Q}$.
-\item We can also generalize to all third-order exponential integrals.
-\begin{itemize}
-\item Most of them are equivalent to the $K_{1/3}$ integral, but there's also an interesting degeneration.
-\end{itemize}
-\end{itemize}
-\color{black}
+
 \subsection{Fractional derivative formula}
 \begin{itemize}
-\item Theorem~\ref{thm:three-halves} says that for a certain class of exponential integrals
+\item formula \eqref{formula1} Theorem~\ref{thm:maxim} says that for a certain class of exponential integrals
 \[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
-the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
+the inverse Laplace transform is the $\tfrac{3}{2}$ derivative of $\nu/df$ at $\zeta=f$.
 \item the asymptotic expansion of $I(z)$ is a resurgent function.
@@
 \begin{itemize}
-\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
+\item \textbf{Maxim believes it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
 \end{itemize} 
 \end{itemize}
-\subsection{Stokes phenomenon}
-\begin{itemize}
-\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-\item The jump comes from the branch cut difference identity for hypergeometric functions.
-\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-\end{itemize}
+
+%\subsection{Stokes phenomenon}
+%\begin{itemize}
+%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
+%\item The jump comes from the branch cut difference identity for hypergeometric functions.
+%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
+%\end{itemize}
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 
-A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
+A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}.
 A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
@@
 We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
+This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\cite{gupta2013meromorphic} \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
 \subsubsection{Direction}\label{transl:dir}
@@
 Of course, there are $n$ different choices for $\omega_b$.
+
 \subsubsection{Frequency}\label{transl-freq}
-\textcolor{DarkCyan}{[Instead of thinking of $z$ this way, maybe we should think of it as the coordinate on the ``generic cotangent fiber'' over a non-singular point?]} The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+
+The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
 At an ordinary point, we can define $z$ simply as the map
@@
 \end{equation}
-where $z$ is the frequency function defined in Section~\ref{transl:freq} and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
+where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
+We will use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
 
@@
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-\color{gray}
-\subsection{The geometry of the Borel transform}
-\begin{itemize}
-  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+%\color{gray}
+%\subsection{The geometry of the Borel transform}
+%\begin{itemize}
+  %\item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
 It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  \begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
+  %\item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
+  %\begin{itemize}
+   % \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
 \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
 [Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-\end{itemize}
-\color{black}
+  %\end{itemize}
+  %\item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
+%\end{itemize}
+%\color{black}
 \subsection{The Laplace transform: analytic version}
 \subsubsection{Regularity and decay properties}\label{reg-decay}
-%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
-The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
-%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
-where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
-\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
 
@@
 Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
+For holomorphic $f$, one can also use Equation 1.5 of \cite{sternin1995borel}.} that
 \[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
@@
 \end{equation}
+
 \subsubsection{Rescaling of translation structure}
+
 Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
@@
 
-It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
+It obeys the expected semigroup law \cite[\S 1.3]{mladenov2014advanced}
 \begin{align*}
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
+and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).
 
@@
 However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
-Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
+Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero (see \S 1.3 \cite{mladenov2014advanced} \textbf{---original source Podlubny}).
 We'll use the {\em Riemann-Liouville} convention.
@@
 Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-Here's what's nice about it.
-
-You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+%\color{Tan}
+%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+%for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+%\begin{equation}%%\label{id:L-mult}
+%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+%\end{equation}
+%for all integers $n \ge 0$.
+
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
 for all $\lambda \in (0, \infty)$.
@@
 for all integers $n \ge 0$.
-
-\color{magenta}
 Furthermore, if $\varphi\in\mathcal{E}_{\zeta,\alpha}$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\mathcal{E}_{\zeta,\alpha}$ and 
@@
 
-We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
+%We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
 
@@
 %We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
-
-\color{black}
 
@@
 \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
-has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{MS}:
+has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
 \begin{align*}
@@
 
-\color{Peru}
-\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
+%\color{Peru}
+%\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
 More precisely, $\borel_\zeta$ is a $\C$-linear map
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-\end{align*}
-where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
+%\begin{align*}
+%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
+%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
+%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
+%\end{align*}
+%where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
 
 %%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
-\begin{align*}
-    \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-    &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
-\end{align*}
-where in the second step we formally interchange the integral and the sum. 
-\color{black}
-\subsubsection{Action on transseries}
+%\begin{align*}
+ %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
+  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
+  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
+  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
+%\end{align*}
+%where in the second step we formally interchange the integral and the sum. 
+%\color{black}
+\subsubsection{Action on transseries}\label{sec:action_transseries}
 
@@
   thus we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
-\begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
+%\begin{itemize}
+ %   \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
 \textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
 [Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
+%  \end{itemize}
 
@@
  Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
-
- \textcolor{magenta}{I think we should add a remark, saying that on $B$ there is no special coordinate, and this reflects on the fact that $\borel$ is defined equivalently for every choice of coordinates.}
 
@@
 \end{lemma}
-In particular, we deduce from the lemma that the Borel transform is an isomorphism between Gevrey-$1$ series and $\C\delta\oplus\C\lbrace\zeta\rbrace$.
-
+
+In fact, we deduce that the Borel transform is an isomorphism between Gevrey-$1$ series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
 The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
-
-\textcolor{magenta}{[add definition of convolution product and $\borel$ being an algebra isomorphisms]}
+In addition, in Section \ref{convolution} we will prove that the Borel transform is an algebra isomoprhisms.
 
@@
 
-If $\alpha\in\mathbb{R}\setminus\Z$, then $\borel$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
-Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-\alpha} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
-\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
-
-\subsection{Properties of the Borel transform}
+\subsection{Properties of the Borel transform}\label{properties Borel transform}
 We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
@@
 
-(v) see Lemma 5.10 \cite{MS16}.
+(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
 
@@
 The space of Gevrey-$1$ formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta$.
+The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
 Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then
-\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}\]
-
-and $\delta:=\borel 1$. In addition, it follows that the convolution product $\ast$ can be explicitly characterized as
+\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+
+In addition, it follows that the convolution product $\ast$ can be explicitly characterized as
 
@@
 
-the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 \cite{MS16}.
+the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 in \cite{diverg-resurg-i}.
+\begin{lemma}
+    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
+\end{lemma}
+\begin{proof}
+    Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then  
+\begin{align*}
+\borel_\zeta (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
+\end{align*}
+
+and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
+\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
+\end{proof}
 
@@
 is slight.
-Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
+Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
 Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
 
-Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
+Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
 \[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
@@
 
+\subsubsection{Regularity}
+
+We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
+
+\begin{lemma}\label{lemma-3.5}
+    Let $R_0>0$.
+Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$.
+Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
+    \begin{equation}
+        |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
+    \end{equation}
+\end{lemma}
+
+\begin{proof}
+    The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
+By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$.
+The formal Borel transform of $f$ reads
+    \begin{align*}
+        \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
+    \end{align*}
+   and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
+   \begin{align*}
+       |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
+       &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
+       &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
+       &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
+   \end{align*}
+
+   This ensures the uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
+   \color{Turquoise}
+In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
+\begin{align*}
+    \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+    &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+    &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
+    &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
+\end{align*}
+   \color{black}
+\end{proof}
+
+\begin{lemma}\label{lemma-3.8}
+    Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
+    \begin{equation}\label{eqn:convolution}
+        \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
+    \end{equation}
+    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
+\end{lemma}
+
+We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
+
+\begin{proof}
+    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
+Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
+    \begin{equation}
+        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
+    \end{equation}
+    This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
+Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
+By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
+\end{proof}
+
+\begin{lemma}\label{lemma-3.8bis}
+    Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
+Then, the convolution equation
+    \begin{equation}\label{eqn:convolution-bis}
+        \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
+    \end{equation}
+    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
+\end{lemma}
+
+\begin{proof}
+    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
+Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
+    \begin{equation}
+        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
+    \end{equation}
+    where $R_n(z)$ are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
+This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
+Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
+By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
+\end{proof}
+
+\begin{remark}
+    Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
+\end{remark}
+
 \section{Proof of main results}
-\subsection{Borel regularity for ODEs}
-
-Let $\mathcal{P}$ be a linear differential operator 
+\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
+
+Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
 \begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
 \end{equation}
@@
 \begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ \textcolor{orange}{[} i.e such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
+such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_d$ are entire functions of exponential type
+\item $R_0, \ldots, R_{d-1}$ are entire functions of exponential type. 
 \end{itemize}
@@
 \begin{equation}\label{P-hat_j}
-\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^dR_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
 \end{equation}
 such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
+${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ with $\Omega$ an open sectorial domain which touches but not contains $\alpha_j$.
 \end{theorem}
@@
 \begin{align*}
-&\partial_{\zeta,\alpha_j}^{-2}\circ\left[R_0(\partial_{\zeta,\alpha_j}^{-1})+R_1(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)+...+R_d(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta,\alpha_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta)^k.
+&\partial_{\zeta,\alpha_j}^{-2}\circ\left[R_0(\partial_{\zeta,\alpha_j}^{-1})+R_1(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)+...+R_{d-1}(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^{d-1}\right]=\sum_{\lambda\leq -2} \partial_{\zeta,\alpha_j}^\lambda\circ r_\lambda \\
+&\text{ with }r_\lambda=\sum_{k=0}^{d-1} R_{k,\lambda}(-\zeta)^k.
 \end{align*}
@@
 \begin{lemma}
- Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined by \eqref{P-hat_j}.
+ Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined in \eqref{P-hat_j}.
 If $\hat{\psi}_j$ admits a Laplace transform $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.
@@
         \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
         &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
     \end{align*}
-    \textcolor{magenta}{[do we really need the assumption on $\theta_j$, namely $\theta_j\neq\arg(\alpha_j-\alpha_k)$ for every $k=1,...,d$?]} \textcolor{orange}{[At first, I didn't think we need that assumption for the Volterra equation existence theorem to hold, or for the Laplace transform to exist.
-When the integration path crosses over $\alpha_k$, I thought that only $\psi_k$ would jump, so only $\psi_k$ would need to become ill-defined when the integration path goes through $\alpha_k$.
-\textbf{However, it's true that $v_1$ and $v_{-1}$ each blow up at both singularities, so maybe there's a problem with the construction!}]}
+
 \end{proof}
@@
 \begin{align*}
-  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_j\right)&= \left[P(-\zeta)+1\ast_{\alpha_j} Q(-\zeta)+\zeta \ast_{\alpha_j} \left(\sum_{r=0}^{d}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha_j}(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\
-  &=\left[P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j} \left(\sum_{r=0}^{d}R_r(\fracderiv{-1}{\zeta}{\alpha_j} )(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\&=\hat{P}_j\tilde{\psi}_j(\zeta_j)
+  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_j\right)&= \left[P(-\zeta)+1\ast_{\alpha_j} Q(-\zeta)+\zeta \ast_{\alpha_j} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha_j}(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\
+  &=\left[P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha_j} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j} )(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\&=\hat{P}_j\tilde{\psi}_j(\zeta_j)
 \end{align*}
@@
 
-\color{Turquoise}
-\begin{lemma}\label{step a}
-    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
-\end{lemma}
-
-\begin{proof}
-    We will prove the following: 
-    \begin{itemize}
-        \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
-        \item along that direction, the germ $\tilde{\psi}_j$ grows sub-exponentially. 
-    \end{itemize}
-    The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-\textcolor{magenta}{[why they are there?
-add comment][Take a more careful look at Lemma 3.9 \cite{Del}]}
-\end{proof}
-
 \color{black}
-\subsection{Borel regularity for thimble integrals}
-
-Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic Morse function $f\colon X\to\C$ with only simple critical points. Set
+\subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
+
+Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{\alpha_1,...,\alpha_N\}$.
+Set
 \begin{equation}\label{exp-int}
-I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
-\end{equation}
-where $\mathcal{C}$ is a contour chosen to make the integral well-defined.  
-At a Morse critical point $x_\alpha$ of $f$, the saddle point approximation gives the formal series 
+I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
+\end{equation}
+where $\Lambda_j$ is the thimble associated with the critical point $\alpha_j$.  
+The saddle point approximation gives the formal series 
 \begin{equation}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
-\end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-
-\begin{theorem}\label{thm:maxim} Let $N=1$.
-Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then:
+{I}_{j}(z)\defeq\int_{\Lambda_j}e^{-zf}\nu\sim \tilde{I}_{j}\defeq e^{-zf(\alpha_j)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to\infty
+\end{equation}
+
+\textcolor{orange}{[cite or prove]}
+%Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+
+\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-zf(\alpha_j)}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
 \begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1, thus $\hat{\varphi}_\alpha(\zeta)\defeq\borel_\zeta(\tilde{\varphi}_\alpha)$ converges near $\zeta=\zeta_{\alpha}$
-\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
+\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is Gevrey-1, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\zeta_j+f(\alpha_j)$
+\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $f(\alpha_j)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $f(\alpha_j)$, we have
 \begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\hat{\phi}_{j}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
 \end{multline}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
-Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([f(\alpha_j), \zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\Lambda_j$.]}
 \end{enumerate}
@@
 
-\textcolor{magenta}{[In the proof we use $\zeta_\alpha=f(x_\alpha)$; however this is in contrast with our notation as $\zeta_\alpha=\zeta-f(x_\alpha)$. Should we change it?]}
 \begin{proof}
@@
 
-Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $\alpha_j$ with $\tfrac{1}{2} \tau^2 = f - f(\alpha_j)$.
+Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
 \textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
+I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
 that converges in some disk $|\tau| < \varepsilon$.
 
-\color{magenta}{By the steepest descent method,
+By the steepest descent method,
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. [Veronica: I don't think this is the claim of steepest descendet method]} 
-\color{black}\textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
+\[ e^{\textcolor{magenta}{+}z f(\alpha_j)} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $\Re z \to \infty$ \textbf{[see, for example, Miller's ``Applied Asymptotic Analysis,'' Proposition 2.1---the argument through equation~(2.9).]} Plugging in the Taylor series above, we get
+\begin{align*}
+e^{-z f(\alpha_j)} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
 \end{align*}
@@
 \begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-These terms are crucial, however, for the convergence of the sum.
-To see why, consider their absolute sum $C_\text{exp}$.
-When $z \in [0, \infty)$,
-\begin{align*}
-C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \color{magenta}\ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-\color{black}
-which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
-
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
-We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
-See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
-\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
-
-\color{Purple}
-For each cutoff $N$, the tail error \textbf{[check]}
-\begin{align*}
-\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
-& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
-& = \textbf{uh-oh!}
-\end{align*}
-\color{violet}
-is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
-\begin{align*}
-C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.
-\color{magenta}
-\begin{claim}
-    \[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-\end{claim}
-
-By the dominant convergence theorem ...
-\begin{equation}
-    e^{-zf(x_\alpha)}I_\alpha(z)\approx\sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,\left[z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)-2e^{-z\varepsilon^2/2}\sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\right]
-\end{equation}
-hence we have to estimate the growth of 
-\[-2\sqrt{2\pi} e^{-z\varepsilon^2/2} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\]
-
-as $\Re z\to\infty$. 
-\color{black} %Hence,
+e^{-z f(\alpha_j)} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z f(\alpha_j)} I_\alpha(z)$.
+In other words,
+\[ e^{-z f(\alpha_j)} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+To see why, cut the sum off after $N$ terms, and observe that
+\begin{align*}
+  \Bigg | \sum_{n= 0}^N(2n-1)!!
+b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
+b_{2n}^j n|z|^{-n}.
+\end{align*}
+The right-hand side goes to $0$ as $\Re(z)$ grows.
+
+%Hence,
 %\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
-Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \textbf{[Chiani, Dardari, and Simon, ``New Exponential Bounds and Approximations
+for the Computation of Error Probability in
+Fading Channels,'' inequality~(5)]}, allowing the simpler estimate
+\[ e^{-zf(\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
+
+Call the right-hand side $\tilde{I}_j$. We now see that $a_{j,n} = (2n-1)!!\,b_{2n}^j$ in the statement of the theorem. %\textbf{[Resolve discrepancy with previous calculation.]}
+
+Note that 
+\begin{align*}
+\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
+\end{align*}
+
+We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
 Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-Part~\eqref{int:resum-converges}: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
-\end{align*}
-Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
-
-Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
-As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is Gevrey-1.
+
+%Part~\eqref{int:resum-converges}: \begin{align*}
+%\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+%(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
+%\end{align*}
+%Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
+
+Part~\eqref{int:resum-valid}: Let us recast the integral $I_j$ into the $f$ plane.
+As $\zeta$ goes rightward from $f(\alpha_j)$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
 Hence, we have
 \begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
+I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
+& = \int_{f(\alpha_j)}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
 \end{align*}
@@
 \begin{equation}\label{thimble-difference}
-\hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
-\end{equation}
-\color{Aquamarine}
-In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{I}_\alpha$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
+\hat{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
+\end{equation}
+%\color{Aquamarine}
+%In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{\iota}_j$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
 [Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
 Or something even simpler?]
-\color{black}
+%\color{black}
 
@@
 \begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
-\begin{align*}
-\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \borel_{\zeta_\alpha} \tilde{I}_\alpha.
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
-
-Theorem~\ref{thm:frac-diff-borel} tells us that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \borel \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\nu & = \sum_{n \ge 0} b_n^j [2(f - f(\alpha_j))]^{n/2}\,\frac{df}{[2(f - f(\alpha_j))]^{1/2}} \\
+& = \sum_{n \ge 0} b_n^j [2(f - f(\alpha_j))]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\hat{\iota}_j$, we learn that
+\begin{align*}
+\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(\alpha_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
+& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \\
+& = \borel_{\zeta} \tilde{I}_j.
+\end{align*}
+
+We have now shown that the sum of $\borel_{\zeta} \tilde{I}_j$ is actually equal to $\hat{\iota}_j$.
+
+%Let $\tilde{\Phi}_j\in\C[\![z^{-1}]\!]$ be such that $\tilde{I}_j(z)=e^{-zf(\alpha_j)}z^{-1/2}\tilde{\Phi}_j(z)$,  
+By the action of $\borel_\zeta$ on transseries (\S \ref{sec:action_transseries}) and the properties of convolution (\S \ref{convolution}) we know 
+\begin{align*}
+\borel_{\zeta} \tilde{I}_j & = \borel_{\zeta}( z^{-1/2} \tilde{\Phi}_j) \\
+&=\borel_\zeta z^{-1/2}\ast_{f(\alpha_j)}\borel_\zeta\tilde{\Phi}_j\\
+& = \fracderiv{-1/2}{\zeta}{f(\alpha_j)}  \tilde{\phi}_j \\
+%& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
 \end{align*}
@@
 \begin{equation}\label{shifted-resum-valid}
-\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{equation}
-Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
-\begin{align*}
-I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
-& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
-\end{align*}
-as we claimed.
+\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{f(\alpha_j)} \tilde{\phi}_j.
+\end{equation}
+Taking the Laplace transform of both sides and applying properties of the Borel transform (\S \ref{properties Borel transform}), we see that
+\begin{align*}
+I_j(z) & = \laplace_{\zeta, f(\alpha_j)} \left[ \partial^{-1/2}_{\zeta, f(\alpha_j)}  \tilde{\phi}_j \right] \\
+& = z^{-1/2} \laplace_{\zeta, f(\alpha_j)} \tilde{\phi}_j,
+\end{align*}
+as we claimed. \textcolor{orange}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
 
 Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
+\[ \fracderiv{-1}{\zeta}{f(\alpha_j)} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{f(\alpha_j)} \tilde{\phi}_j. \]
+
 Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
+\[ \hat{\iota}_j(\zeta) = \partial_\zeta \left( \int_{\Lambda_j(\zeta)} \nu \right), \]
 we can see that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
-The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
-\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
+\[ \fracderiv{-1}{\zeta}{f(\alpha_j)} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(f(\alpha_j))} \nu. \]
+The initial value term vanishes because the path $\Lambda_j(f(\alpha_j))$ is a point. Hence,
+\[ \int_{\Lambda_j(\zeta)} \nu = \fracderiv{-3/2}{\zeta}{f(\alpha_j)} \hat{\phi}_j(\zeta). \]
 Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
+\[ \fracderiv{3/2}{\zeta}{f(\alpha_j)} \left( \int_{\Lambda_j(\zeta)} \nu \right) = \hat{\phi}_j(\zeta). \]
+
 \end{proof}
@@
 For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
-
 \subsection{Airy--Lucas}
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
 \[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
@@
 \end{equation}
-In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{{m/n}}$.
+In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
 
@@
 
-\subsubsection{Asymptotic analysis}
+\subsubsection{Asymptotic analysis}\label{sec:asympt-AL}
 
@@
 We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
+This is an evidence of Theorem~\ref{thm1-dim}.
 %\subsection{Going to the spatial domain}\label{spatial-AL}
@@
 
-This is great news, because equation~\ref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
 We can see the regular singularities by moving the derivatives to the right:
@@
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel-AL} looks like
+In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel-AL} looks like
 \begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
@@
 \end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
+With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
 \begin{equation}\label{diff-eq:hypergeom-pos-AL}
@@
 
-The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as we saw in Section~\ref{sec:asympt-AL}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
@@
 
-The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
+Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation~\textcolor{magenta}{[prove or cite]}.
 Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
@@
 Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-\subsubsection{Confirmation of Borel regularity}
+
+\subsubsection{Confirmation of Borel regularity}\label{confirmation-borel-regularity}
 We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
-We found in Section~\textbf{[asymptotic analysis]} that
+We found in Section~\ref{sec:asympt-AL} that
 \begin{align*}
@@
 \begin{align*}
-\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
+\borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
@@
 Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
+
 \subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
-We can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
 Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
@@
 K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
-& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
+& = -\frac{1}{2  \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta %\\
+%& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
+\end{align*}
+
 For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
@@
 \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+
 \begin{center}
@@
 
-The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-\begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-\end{align*}
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
+Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$:
+
+\begin{align*}
+    \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))}&=\frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
+    &=\frac{\sin(m\phi)}{\sin(n \phi)}\\
+    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};\sin^2(n \phi)\right)\\
+    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right) 
+\end{align*}
+where in the last step we use $-\zeta=T_n(u)=T_n(\cos\phi)=\cos(n\phi)$. Applying identity 15.8.4, 15.8.27 and 15.8.28 from \cite{dlmf},
+
+\begin{align*}
+    &{}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right)=\\
+    &\qquad = \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right)\Gamma\left(1+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{1}{2};\zeta^2\right)+\\
+    &\qquad \qquad\qquad - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2}-\frac{m}{2n}\right)\Gamma\left(\frac{1}{2}+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(1-\frac{m}{2n},1+\frac{m}{2n};\frac{3}{2};\zeta^2\right)\\
+    &\qquad ={}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)+\\
+    &\qquad\qquad +\frac{1}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)-\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\\
+    &\qquad =\frac{3}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
+\end{align*}
+In addition, recall that ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ has a branch cut singularity at $\zeta=-1$ while ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ has a branch cut at $\zeta=1$; hence
+
+\begin{align*}
+    K_{m/n}(z)&=-\frac{m}{4 n\sinh(\tfrac{m}{n}i\pi)}\int_{\gamma_z}e^{-z\zeta} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) d\zeta\\
+    &=-\frac{1}{2}\int_{1}^{+\infty}e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right) d\zeta
+\end{align*}
+
+where in the second step we use the analytic continuation of the hypergeometric function (equation 15.2.3 in \cite{dlmf}).
+
+Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
+\begin{align*}
+    K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
+\end{align*}
+
+\subsubsection{A flavour of resurgence}\label{resurgence-AL}
+
+In the previous sections we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (\S\ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (\S\ref{contour-argument-AL}).
+Up to a constants, in both cases we find
+
+\begin{align*}
+    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
+\end{align*}
+
+which has a fractional power singularity at $\zeta=1$.
+In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of Ecalle's resurgent functions.
+More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new germ of holomorphic function, which has a branch cut singularity at $\zeta=-1$.
+Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
+
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
+\end{align*}
+
+Hence, we deduce  
+\begin{equation}\label{resurgent-relation-1}
+    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
+\end{equation}
+
+namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
+
+We can repeat the same reasoning with $v_{-1}$:
+
+\begin{align*}
+    v_{-1}(\zeta)=  \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
+\end{align*}
+
+and ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ is singular at $\zeta=1$. Hence
+
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right)=\\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
+&=2 i\cos(\pi m/n) \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
+&=2i \cos(\pi m/n)\, \left(\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right)
+\end{align*}
+
+and the analogue of \eqref{resurgent-relation-1} is 
+\begin{equation}\label{resurgent-realtion-2}
+    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
+\end{equation}
+
+Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are crucial to understanding the Stokes phenomena.
+Indeed, when we start varying the contour of integration for the Laplace transform, we know that $\laplace_{\zeta,1}^\pi$ and $\laplace_{\zeta,-1}^0$ are not well defined because the contour hits the other singularity.
+The Stokes phenomenon is about comparing the Laplace transform below and above the critical angle and it quantifies the jump as a constant times another function.
+In our example:
+
+\begin{align*}
+    \laplace_{\zeta,1}^{\pi+\varepsilon} v_1-\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = 2 i \cos(\pi m/n) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
+    \laplace_{\zeta,-1}^{\varepsilon} v_{-1}-\laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = - 2 i \cos(\pi m/n)  \, e^z \, \laplace_{\zeta,1} v_{1} 
+\end{align*}
+
+thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$.
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as in the generic situation we expect the Stokes constants to be integers (in a suitable normalization).
+However, in these examples, $f$ is not Morse (unless $m=1$ and $n=3$) and \textcolor{orange}{we have multiple cover contributions [I'm not sure].
+I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
+
+\textcolor{orange}{Do we need assumptions on the value of $m,n$ to make sense of the hypergeometric functions? Explain why from the picture we see always 2 intersection points even for Airy case}.
+
+%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
+%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+
+%The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
+%\begin{align*}
+%& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+%= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
+%\end{align*}
+%as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
 Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-\color{DarkCyan}
-Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-where $\zeta = -1 + \zeta_{-1}$.
-\color{black}
-
-\subsection{Modified Bessel}
-
-The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
-
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
-\end{equation}
-
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf})
-
-\begin{align*}
-I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]
-\end{align*}
-
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-
-\begin{figure}[h]
-\caption{Add figure path $\Omega$}
-\end{figure}
-
-On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results:
-
-\begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
- \begin{align*}
- \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
-\end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-
-\begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{1}\big)\\
-v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
-\item \textbf{Borel regularity} \textcolor{Lime}{[Check with Aaron how to phrase it]} 
-\end{itemize}
-
-On the other hand, the contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
-
-\subsubsection{Lifting to a countable cover}\label{countable-cover}
-Formula~\eqref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
-Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
-
-Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
-we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
-\begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
-\end{align}
-For any $\mu \in \C \smallsetminus \Z$, 
-\begin{align}
-\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-
-When $\mu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
+%\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+%\color{DarkCyan}
+%Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
+%\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+%In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
+%\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
+%where $\zeta = -1 + \zeta_{-1}$.
+%\color{black}
 
 \subsection{Higher Airy}
+
+\textcolor{magenta}{[The higher Airy example is not completed and there are still some difficulties in the computations, even for simple examples. Should we remove it?]}
 
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\cite{charbonnier22}, equation~3.8
 
@@
 
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-higher-Airy} which is slight and locally integrable at $\zeta = 1$.
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-higher-Airy} which is slight and locally integrable at $\zeta = 1$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-higher-Airy} looks like
+In this coordinate, equation~\eqref{diff-eq:spatial-mod-higher-Airy} looks like
 \begin{multline}\label{diff-eq:spatial-mod-higher-Airy-1}
@@
 \subsubsection{Higher Airy of degree $3$}
-Setting $n=4$, equation \ref{eqn:higher-Airy} turns into
+Setting $n=4$, equation \eqref{eqn:higher-Airy} turns into
 
@@
 
-In \cite{Reid} \cite{Drazin-Reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
+\textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations.
+In particular the thimble integral interpretation is missing Should we remove it?]}
+
+In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
 They are defined as countour integral (\cite{dlmf} \S 9.13(ii))
@@
 \end{align*}
-where the countours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig.countours}
+where the contours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}
 
 \begin{figure}
-%\includegraphics[scale=0.5]{countours}
+\center
+\begin{tikzpicture}
+    \draw[->] (4,0)--(4,8);
+    \draw[->] (0,4)--(8,4);
+    \draw[blue,very thick] (4,4) circle (0.5) ;
+    \node[blue,font=\tiny] at (4.5,3.5) {$\Gamma_0$};
+    \node[red,font=\tiny] at (1.4,1.3) {$\Gamma_1$};
+    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
+    \node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
+    \draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
+     \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
+    \draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
+    \draw[orange,very thick,->] (4,4)--(6.5,4);
+    \draw[orange,very thick] (6.5,4)--(8,4);
+    \node[orange,font=\tiny,below] at (7,4) {$\gamma_1$};
+    \draw[orange,very thick,->] (4,4)--(2.7,6);
+    \draw[orange,very thick] (2.7,6)--(1.4,8);
+    \node[orange,font=\tiny,right] at (2.2,6) {$\gamma_2$};
+    \draw[orange,very thick,->] (4,4)--(2.7,2);
+    \draw[orange,very thick] (2.7,2)--(1.4,0);
+    \node[orange,font=\tiny,right] at (2.2,2) {$\gamma_3$};
+    \node at (5.1,4) {$\bullet$};
+    \node at (2.9,4) {$\bullet$};
+    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
+    \node[font=\tiny,below] at (5.3,4) {$1$};
+    \end{tikzpicture}
+    \caption{Representation of the path of integration for $A_k,B_0,B_k$ respectively in red, blue and orange.}\label{fig:path-generalized-Airy}
 \end{figure}
 
-Each generalize Airy functions is a solution of
+Each generalized Airy function is a solution of
 
@@
 We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
+The critical points of $f$ are $\alpha_{\pm}:=\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
 
 \begin{equation}
-I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
-\end{equation}
-
-where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}).
+I_\pm(z,p)\defeq\frac{1}{2\pi i}\int_{\Lambda_{\pm}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
+\end{equation}
+
+where $\Lambda_{\pm}$ are the paths through the points $\alpha_\pm$, starting and ending at infinity (as in Figure \ref{fig:path-generalized-Airy-Lambda+-}).
+
+\begin{figure}
+\center
+\begin{tikzpicture}
+    \draw[->] (4,0)--(4,8);
+    \draw[->] (0,4)--(8,4);
+    \node[red,font=\tiny] at (1.4,1.3) {$\Lambda_-$};
+    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
+    %\node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
+    %\draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
+    % \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
+    %\draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
+    \node[red,font=\tiny] at (7.4,1.3) {$\Lambda_+$};
+    \draw[red,very thick,->] (7,0.2) .. controls (4.5,4) .. (7,7.8);
+    \node at (5.1,4) {$\bullet$};
+    \node at (2.9,4) {$\bullet$};
+    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
+    \node[font=\tiny,below] at (5.3,4) {$1$};
+    \end{tikzpicture}
+    \caption{The paths of integration $\Lambda_\pm$ for $I_{\pm}$.}\label{fig:path-generalized-Airy-Lambda+-}
+\end{figure}
+
 In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$:
@@
 \begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
+I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\Lambda_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
 &=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
@@
 
-From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
+From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combination of three generators 
 \begin{equation}
-\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
+U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
 \end{equation}
@@
 
+\textcolor{orange}{we may try to do the computations of Stokes constants for $p=1$, when $\hat{w}_1$ simplifies to a Gauss hypergeometric.
+Use also information about the monodromy.
+Check change of coordinates $y=\zeta^2$.}
+
+\textcolor{magenta}{[add contour argument]}
+
+\subsection{Third-order thimble integrals}
+
+Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
+Furthermore, we can restrict to monic polynomials by setting $a_3=1$.}, we are going to consider thimble integrals of the form
+
+\[ I_j(z) = \int_{\Lambda_j} \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
+
+where $\Lambda_j$ is a thimble in $H_{z,1}^B$ through a critical point of $f$.
+We can distinguish between the case when $f$ has two distinct critical points $\alpha_+, \alpha_-$ and only one critical point $\alpha$.
+In both cases, we will compute the differential equation satisfied by $I$.
+
+\begin{lemma}
+    Let $f(u)=u^3+pu+q$, 
+    \begin{itemize}
+        \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
+        \begin{equation}\label{eqn:degree-3-poly-2roots}
+            \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
+        \end{equation}
+        \item  if $p=0$, then $I(z)$ solves
+        \begin{equation}\label{eqn:degree-3-poly-1root}
+            \left[\partial_z+q+\frac{1}{3z}\right]I=0
+        \end{equation}
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    The proof follows from a direct computation. 
+\end{proof}
+
+Let us first assume $p\neq 0$, then $\alpha_{\pm}=\pm\sqrt{-p/3}$.
+Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=-\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
+
+\begin{equation}\label{eqn:deg3-borel-ODE}
+    \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
+\end{equation}
+
+Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=f(\alpha_+)$: in the new coordinate $\zeta_+:=\zeta-f(\alpha_+)$, equation \eqref{eqn:deg3-borel-ODE} becomes
+
+\begin{equation*}
+    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, \alpha_+)\partial_{\zeta_+}^2+ \left[2p\, \alpha_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
+\end{equation*}
+
+which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,\alpha_+}\zeta_+$
+
+\begin{equation*}
+    \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
+\end{equation*}
+
+and it admits a slight solution
+
+\begin{align*}
+    v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
+    &=\left(\frac{3}{4p\,\alpha_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_+}\zeta_-\right). 
+\end{align*}
+
+Notice that $v_+$ is an hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-f(\alpha_-)$
+
+\begin{equation*}
+    v_- =\left(\frac{3}{4p\,\alpha_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_-}\zeta_-\right). 
+\end{equation*}
+
+When $p=0$, the critical point of $f$ is $\alpha=0$ and we can argue as before: $\laplace_{\zeta,f(\alpha)}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
+
+\begin{align*}
+   \left[ (\zeta-q)\partial_\zeta +\frac{2}{3}\right] v=0
+\end{align*}
+
+namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
+The same result is confirmed by the contour argument which in this simple case reads
+
+\begin{align*}
+    \int_{\Lambda} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
+    &= e^{i\pi/3} \int_q^{+e^{i\theta}\infty} e^{-z\zeta} \, \zeta_q^{-2/3}\,  d\zeta
+\end{align*}
+
+where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin.
+
+\textcolor{orange}{[It'd be nice to have the contour argument for $p\neq 0$ too, however we don't have the same nice coordinates as in the other examples--maybe we can do a change of coordinates to recover $K_{1/3}$ as suggested below.]}
 \color{DarkTurquoise}
-
-\section{Third-order exponential integrals}
 \begin{itemize}
@@
 \end{itemize}
-
-\color{orange}
-\section*{Outline}
-
-\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
-
-\begin{enumerate}
-\item introduction
-\begin{itemize}
-\item Exponential integrals
-\begin{itemize}
-\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
-\item the choice of the path $\mathcal{C}$: 
-\begin{itemize}
-\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
-\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
-\end{itemize}
-\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
-\begin{itemize}
-\item there is a comparison isomorphism (Maxim)
-\end{itemize}
-\item varying $z$ we have the Stokes phenomena
-\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
-\begin{itemize}
-\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
-\item it is an example of resurgent series (\'Ecalle)
-\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
-\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
-\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
-There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
-\end{itemize} 
-\end{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
-\item motivation
-\begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
-\end{itemize}
-\end{itemize}
-\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
-\item State results about resurgence of exponential integrals and Stokes phenomena
-\begin{itemize}
-\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]
-\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
-\end{itemize}
-\end{itemize}
-\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
-\begin{enumerate}
-\item Analytic
-\begin{enumerate}
-\item Introduction
-\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
-\item The Laplace transform of a holomorphic function
-\begin{enumerate}
-\item Over an ordinary point
-\item Over a branch point
-\item Differential equation
-\end{enumerate}
-\item Relating differential equations in the frequency domain to integral equations in the position domain
-\end{enumerate}
-\item Formal
-\begin{enumerate}
-\item Laplace transform of a formal series
-\item Borel transform
-\item Relating differential equations in the frequency variable to integral equations in the position variable
-\end{enumerate}
-\end{enumerate}
-\item Review of integral equations
-\begin{itemize}
-\item Existence of solutions
-\item Fractional integrals and derivatives
-\item Going between integral and differential equations (slight functions)
-\end{itemize}
-\item General cases
-\begin{enumerate}
-\item Borel regularity
-\begin{itemize}
-\item General ODE of the form
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
-\begin{itemize}
-\color{DarkCyan}
-\item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
-\begin{itemize}
-\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
-\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
-\end{itemize}
-\color{orange}
-\item Show that we can find a slight solution at each critical value.
-\item Show that $\hat{\iota} = \tilde{\iota}$, where:
-\begin{itemize}
-\item $I = \laplace \iota$
-\item $\hat{\iota}$ is the Taylor expansion of $\iota$
-\item $\tilde{I}$ is the asymptotic series of $I$
-\item $\tilde{\iota} = \borel \tilde{I}$
-\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
-\end{itemize}
-\end{itemize}
-\item General thimble integral (conditions?)
-\begin{itemize}
-\item Proof of Borel regularity
-\item $3/2$-derivative formula
-\item Contour argument
-\end{itemize}
-\end{itemize}
-\item Resurgence
-\begin{itemize}
-\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
-\item Relate to Ecalle's formalism and the alien derivative
-\item Stokes factors
-\begin{itemize}
-\item For ODEs
-\item For thimble integrals
-\end{itemize}
-\end{itemize}
-\end{enumerate}
-\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
-\begin{enumerate}
-\item The Airy example
-\begin{itemize}
-\item $I(z)$ is a solution of a linear ODE.
-We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Compute Stokes constants
-\begin{itemize}
-\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]
-\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
-\end{itemize}
-\item Comparison with the literature \textcolor{gray}{has to be done}
-\begin{itemize}
-\item Mari\~{n}o
-\item Sauzin
-\item Kontsevich slides
-\item Kawai--Takei? [might take too long to understand well enough]
-\end{itemize}
-\end{itemize}
-\item The Airy--Lucas examples
-\begin{itemize}
-\item Compute Borel transform [{\tt airy-resurgence}]
-\item Compute Stokes constants \textcolor{gray}{has to be done}
-\end{itemize}
-\item Bessel 0 (it is different because we have infinite cover)
-\begin{itemize}
-\item Compute Stokes constants [{\tt draft2}]
-\end{itemize}
-\item Bessel $\mu$ (follows from Bessel 0)
-\begin{itemize}
-\item Compute Stokes constants [{\tt modified Bessel}]
-\end{itemize}
-\item The generalized Airy example
-\item The vibrating beam example
-\begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals, since Andy is interested in that sort of thing
-\end{itemize}
-\end{enumerate}
-\end{enumerate}
 
@@
 
-Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
+Now, let's return to equation~\eqref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
 \begin{align*}
@@
 %where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
-Like we did in equation~\ref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
+Like we did in equation~\eqref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
 
@@
 We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
+This is an evidence of Theorem~\ref{thm1-dim}.
 
@@
 %\color{DodgerBlue}
-%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
+%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\eqref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
 %\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
@@
 therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
+In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:reg-mod-bessel} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
 
@@
 
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
+The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
 \[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
@@
 \[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\eqref{eqn:mod-bessel}.
 
@@
 \[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\ref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
+of equation~\eqref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
 
@@
 
-In \cite{Diablerets}, the author studies the Airy functions as example of resurgent functions. He starts with the formal trans-monomial solutions of Airy equation:
+In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions. He starts with the formal trans-monomial solutions of the Airy equation:
 
@@
 
-In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
+In \cite{diverg-resurg-i} the author studies summability and resurgent properties of solutions of the Airy equation.
 
@@
 Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see Lemma 6.106 \cite{MS}).
+Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see \cite[Lemma 6.106]{diverg-resurg-i}).
 %Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
@@
 
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
+As shown in the previous examples, the Borel transform  of thimble integrals can be computed in different ways: from the ODE they solve, from the contour argument and from the integral formula \ref{formula1}.
+When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneus, while with the contour argument and the fractional integral formula the ambiguity is solved.
+
+In addition, since thimble integrals have a geometric interpretation, the Stokes constants that encode the jumps of thimble integrals when $z$ crosses a Stokes ray are expected to be integers as indeed they are intersection numbers of dual pairs of thimbles.
+
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
 
@@
 Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
+The identity~15.4.16 \cite{dlmf}
 \[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
@@
 
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
 \begin{align*}
@@
 \end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
 \begin{align*}
@@
 Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
+The identity~15.4.16 in \cite{dlmf}
 \[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
@@
 
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \S 4.1 in \cite{koornwinder2015fractional}).
 \begin{align*}
@@
 \end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
 \begin{align*}
@@
 
+\color{black}
+
 \bibliographystyle{plain}

### 2023-07-21 exp-resurgence.tex

@@
 \item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
 \end{enumerate}
@@
 This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
-14).
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
 Conversely, we can explicitly build a distinguished basis of analytic solutions:
@@
 
+\color{Tan}
 \begin{remark}
-Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
+Although, in our proof, we use $1$-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
 \textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
@@
 
-\color{gray}
-\begin{itemize}
-\item Can we see there exists a distinguished basis in a purely analytic way?
+\color{magenta}
+[Veronica]
+
+Although, in our proof, we adapt an argument by M.
+Loday-Richaud and P.
+Remy (see \S 2 in\cite{loday-Remy2011}) to guarantee Borel--Laplace summability, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
+In addition, our proof stresses the importance of the position domain, where in fact the crucial step of the proof is done.
+
+%\color{gray}
+%\begin{itemize}
+%\item Can we see there exists a distinguished basis in a purely analytic way?
 YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-\end{itemize}
-\begin{itemize}
-\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+%\end{itemize}
+%\begin{itemize}
+%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
 (proof based on existence theorem \ref{frac_int_exist})
-\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
 Then this is the only solution that can be expressed as a Laplace transform.
@@
 
-\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-where the arrow in red are a consequence of multisummability.
+%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+
+%\begin{center}
+%\begin{tikzcd}
+%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+%& & IE & & \\
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\end{tikzcd}
+%\end{center}
+
+%where the arrow in red are a consequence of multisummability.
 In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
 On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-\item  
-there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-\item  M.A.E.T.
+%\item  
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%\item  M.A.E.T.
 says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
 Our method uses just Laplace transform.
-\item How do we know we are picking the same frame?
+%\item How do we know we are picking the same frame?
 from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
 From uniqueness result we get a frame equivalent to Ecalle's frame.
-\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
 Borel regularity is instead based on the analytic solution in the $z$-plane.
 The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-\end{itemize}
+%\end{itemize}
+
+\color{black}
+
+\subsubsection{Why does Borel resummation work for thimbles integrals?}
 
 \color{DarkBlue}
-
-\subsubsection{Why does Borel resummation work for thimbles integrals?}
-
-\begin{itemize}
-\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-\begin{itemize}
-\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-\end{itemize} 
+\begin{itemize}
+%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
+%\begin{itemize}
+%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
+%\end{itemize} 
 \item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
@@
 \item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-\begin{equation}
-I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-\end{equation}
-
-then the following diagram is commutative
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-\end{tikzcd}
-\end{equation}
-\begin{itemize}
-\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
+%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+%\begin{equation}
+%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+%\end{equation}
+
+%then the following diagram is commutative
+%\begin{equation}
+%\begin{tikzcd}
+%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+%& \\
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\end{tikzcd}
+%\end{equation}
+\begin{itemize}
+%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
 \item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
@@
 \end{itemize}
-
-\color{DarkGreen}
+\color{black}
+
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
+
+\[
+I(z):=\int_{\mathcal{C}}e^{-zf}\nu
+\]
+
+regarded as holomorphic functions in the position domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
+In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.
+
+We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
+We follow \cite{pham} and $\S 1$ in \cite{Arnold}.
+Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
+\begin{align*}
+    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
+    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
+\end{align*}
+and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t.
+} \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}.
+Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$.
+This leads to further identifications:
+
+\begin{equation}
+    H_{*}^{B,z}\cong \bigoplus_{\alpha_i} H_{*}(B_j, B_j^+(\theta))
+\end{equation}
+where $B_j:=f^{-1}(B_r(\alpha_j))$ is the preimage of a small ball or radius $r$, containing only the critical value $\alpha_i$ and $B_j^+(\theta):=f^{-1}\left(B_r(\alpha_j)\cap \{ \Re (\zeta e^{i\theta})\geq r/2\}\right)$.
+Notice that we are not assuming $f$ to be Morse, hence $B_j$ may have different connected components.
+Then
+
+\begin{equation}
+    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
+     0 & \text{otherwise}
+    \end{cases}
+\end{equation}
+where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical point $\alpha_j$.
+
+\begin{center}
+    \begin{tikzpicture}
+        \draw (2,2) circle (2);
+        \node[font=\tiny,red] at (1,1) {$\alpha_1$};
+        \draw (1,1.2) circle (0.4);
+        \node[font=\tiny,red] at (3,1.3) {$\alpha_2$};
+        \draw (3,1.5) circle (0.4);
+        \node[font=\tiny,red] at (2.3,3.2) {$\alpha_3$};
+        \draw (2.3,3.4) circle (0.4);
+        \node[above,red] at (1,1) {$\bullet$};
+        \node[above,red] at (3,1.3) {$\bullet$};
+        \node[above,red] at (2.3,3.2) {$\bullet$};
+        \draw[rounded corners] (2.7,1.76)--(2,2)--(1,3.71);
+        \draw[rounded corners] (1,1.6)--(0.5,2)--(1.2,2.5)--(1,3.71);
+        \draw[rounded corners] (1.9,3.4)--(1,3.71);
+        \node[font=\tiny, above] at (1,3.71) {$p_0$};
+        \node[font=\tiny, above] at (2.7,1.76) {$p_2$};
+        \node[font=\tiny, above] at (1,1.6) {$p_1$};
+        \node[font=\tiny, above] at (1.75,3.4) {$p_3$};
+    \end{tikzpicture}
+\end{center}
+
+From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
+Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $\alpha_j$ there are local coordinates $x_1,...,x_N$ such that
+\[f=\alpha_j+\sum_{k=1}^N x_k^2\]
+
+and for $p=c e^{i\theta}\in\C$, the thimble $\Lambda_j(p)$ is defined by 
+\begin{align*}
+    \Im(x_1)=...=\Im(x_N)=0 \text{ and } \Re(e^{-i\theta/2}x_1)^2+....+\Re(e^{-i\theta/2}x_N)^2\leq c
+\end{align*}
+Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite{Witten} page 10).
+
+Hence we deduce that $H_{z, N}^B$ admits a distinguished basis of Lefschetz thimbles labeled by critical points.
+
+Then we recall the definition of $H_{dR,z}^\cdot$: it is the hypercohomolgy of the twisted de Rham complex
+
+\begin{equation*}
+    H_{dR,z}^*:=\mathbb{H}^*( \Omega^\bullet(X), zd+df)
+\end{equation*}
+where $(\Omega^\bullet(X), d)$ is the de Rham complex of differential forms on $X$.
+
+Therefore, the integral $I(z)$ can e regarded as the image of the following map:
+
+\begin{align*}
+    \int \colon  H_{z,N}^{B} \times & H_{dR,z}^N \to \C \\
+       [\mathcal{C}] ,\,\, & [\nu] \to \int_{\mathcal{C}}e^{-zf}\nu
+\end{align*}
+
+\textcolor{orange}{[the Betti--de Rham isomorphism is necessery?]}
+
+Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_\alpha$, namely the integrals over Lefschetz thimbles labeled by the critical points $x_j\in\text{Crit}(f)$.
+
+As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$).
+The jumps can be described geometrically using the theory of Picard--Lefschetz.
+Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
+
+Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, Andersen, Mistergad, the Stirling series for Gamma function in \cite{Maxim_slide_ERC}).
+
+Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$.
+
+These questions have been classically addressed by Pham (\S 3.3 \cite{pham}), Malgrange (Theorem 6 in \cite{Malgrange22}), Delabere and Pham \cite{Delabaere-Pham99}, Berry and Howls \cite{berry1991hyperasymptotics}, Dunne and Unsal \cite{dunne-unsal}, and others.
+\textcolor{orange}{[add references]}
+
+Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+
 We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
@@
 A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-Suppose every singularity of $B$ is a critical value of $f$.
-\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
-\textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
-\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
-
-\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
+Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \overline{X} \to \overline{B}$ with non--degenerate critical points \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
+\textcolor{red}{Suppose every singularity of $B$ is a critical value of $f$.[Veronica: Is it a good assumption?]} \textcolor{DarkGreen}{\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
+How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)?
+We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}} For each critical point $\alpha_j$, let $\Gamma_j$ be the ray going rightward from $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
+These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
+The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves \textcolor{magenta}{[add picture]}, as long as $\Gamma_j$ misses the other critical values of $f$.
+The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $\alpha_j$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$.
+%The {\em thimble integral}
+%\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
+%is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
+
+Then, our main result for thimble integrals is proving that $1$- dimensional thimble integrals are indeed Borel regular:
+
+\begin{theorem}[see Theorem \ref{thm:maxim}]
+    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
+Then:
+\begin{enumerate}
+\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is Gevrey-1, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+\item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
+\begin{multline}
+\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
+\end{multline}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\Lambda_j$.]}
+\end{enumerate}
+\end{theorem}
+
+The idea of the proof is sketched below and represented in the following diagram:
+\[
+\begin{tikzcd}
+{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
+& & &\\
+\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
+\end{tikzcd}
+\]
+
+On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
+as the Laplace transform of a function $\iota_j$.
+In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}.
+On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal Gevrey-1 series.
+Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
+At this point we realise that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
+In a nutshell, thimble integrals are Borel regular because they are Laplace transforms.
 
@@
 \end{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
+%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
 \end{itemize}
@@
 \color{black}
-%\end{itemize}
-\begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
-\item The resummation method works correctly for functions that satisfy that assumption.
-\item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
-\begin{itemize}
-\item Different aspects of this example appear in various places (Mari\~{n}o, Kawai--Takei, Sauzin). We give a detailed, unified treatment.
-\end{itemize}
-\item We can generalize this argument to all $K_\nu$ with $\nu \in \mathbb{Q}$.
-\item We can also generalize to all third-order exponential integrals.
-\begin{itemize}
-\item Most of them are equivalent to the $K_{1/3}$ integral, but there's also an interesting degeneration.
-\end{itemize}
-\end{itemize}
-\color{black}
+
 \subsection{Fractional derivative formula}
 \begin{itemize}
-\item Theorem~\ref{thm:three-halves} says that for a certain class of exponential integrals
+\item formula \eqref{formula1} Theorem~\ref{thm:maxim} says that for a certain class of exponential integrals
 \[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
-the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
+the inverse Laplace transform is the $\tfrac{3}{2}$ derivative of $\nu/df$ at $\zeta=f$.
 \item the asymptotic expansion of $I(z)$ is a resurgent function.
@@
 \end{itemize}
-\subsection{Stokes phenomenon}
-\begin{itemize}
-\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-\item The jump comes from the branch cut difference identity for hypergeometric functions.
-\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-\end{itemize}
+
+%\subsection{Stokes phenomenon}
+%\begin{itemize}
+%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
+%\item The jump comes from the branch cut difference identity for hypergeometric functions.
+%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
+%\end{itemize}
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
+Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
+If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
 
@@
 \subsubsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
+Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
 \begin{align*}
@@
 \end{equation}
+
 \subsubsection{Rescaling of translation structure}
-Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+
+Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
 The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
+The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
 From the calculation
@@
 \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
+Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
 
@@
 \[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on
-
-It obeys the expected semigroup law \textbf{[Lazarevi\'{c}, \S 1.3]}
-\begin{align*}
-\partial^{\lambda}_{\zeta, \alpha}\,\partial^{\mu}_{\zeta, \alpha} & = \partial^{\lambda+\mu}_{\zeta, \alpha} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \textbf{[Lazarevi\'{c}, equation~35]}.
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\partial^{n+\alpha}_{x \text{ from } 0}$ are defined by composing $\partial^{\alpha-1}_{x \text{ from } 0}$ with powers of $\tfrac{\partial}{\partial x}$.
-However, $\partial^{\alpha-1}_{x \text{ from } 0}$ and $\tfrac{\partial}{\partial x}$ don't commute: their commutator is an initial value operator \textbf{[check, clarify]}.
-Various ordering conventions give various definitions of $\partial^{n+\alpha}_{x \text{ from } 0} f(x)$, which differ by operators that act on the germ of $f$ at zero \textbf{[Lazarevi\'{c}, \S 1.3---original source Podlubny]}.
+where $p$ is any point on the position domain $B$.
+
+It obeys the expected semigroup law \cite[\S 1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
 We'll use the {\em Riemann-Liouville} convention.
 \begin{definition}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\partial^{n+\alpha}_{x \text{ from } 0}$ is defined by
-\[ \partial^{n+\alpha}_{x \text{ from } 0} \defeq \left(\tfrac{\partial}{\partial x}\right)^{n+1} \partial^{\alpha-1}_{x \text{ from } 0}. \]
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
 \end{definition}
-The symbol $\partial^\mu_{\zeta \text{ from } 0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
 It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
 
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\partial^\lambda_{x \text{ from } 0}\,\partial^{-\lambda}_{x \text{ from } 0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
 This extends the semigroup law:
 \begin{align*}
-\partial^{\lambda}_{x \text{ from } 0}\,\partial^{\mu}_{x \text{ from } 0} & = \partial^{\lambda+\mu}_{x \text{ from } 0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-
-Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-Here's what's nice about it.
-
-You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+
+%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
+
+%\color{Tan}
+%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+%for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+%\begin{equation}%%\label{id:L-mult}
+%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+%\end{equation}
+%for all integers $n \ge 0$.
+
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
 for all $\lambda \in (0, \infty)$.
@@
 
- \textcolor{magenta}{I think we should add a remark, saying that on $B$ there is no special coordinate, and this reflects on the fact that $\borel$ is defined equivalently for every choice of coordinates.}
-
 \subsection{The Borel transform on Gevrey-$1$ series}
@@
 
+\subsubsection{Regularity}
+
+We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
+
+\begin{lemma}\label{lemma-3.5}
+    Let $R_0>0$.
+Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$.
+Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
+    \begin{equation}
+        |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
+    \end{equation}
+\end{lemma}
+
+\begin{proof}
+    The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
+By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$.
+The formal Borel transform of $f$ reads
+    \begin{align*}
+        \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
+    \end{align*}
+   and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
+   \begin{align*}
+       |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
+       &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
+       &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
+       &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
+   \end{align*}
+
+   This ensures the uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
+   \color{Turquoise}
+In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
+\begin{align*}
+    \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+    &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+    &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
+    &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
+\end{align*}
+   \color{black}
+\end{proof}
+
+\begin{lemma}\label{lemma-3.8}
+    Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
+    \begin{equation}\label{eqn:convolution}
+        \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
+    \end{equation}
+    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
+\end{lemma}
+
+We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
+
+\begin{proof}
+    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
+Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
+    \begin{equation}
+        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
+    \end{equation}
+    This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
+Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
+By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
+\end{proof}
+
+\begin{lemma}\label{lemma-3.8bis}
+    Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
+Then, the convolution equation
+    \begin{equation}\label{eqn:convolution-bis}
+        \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
+    \end{equation}
+    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
+\end{lemma}
+
+\begin{proof}
+    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
+Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
+    \begin{equation}
+        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
+    \end{equation}
+    where $R_n(z)$ are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
+This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
+Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
+By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
+\end{proof}
+
+\begin{remark}
+    Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
+\end{remark}
+
 \section{Proof of main results}
-\subsection{Borel regularity for ODEs}
-
-Let $\mathcal{P}$ be a linear differential operator 
+\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
+
+Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
 \begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ \textcolor{orange}{[} i.e such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
+\end{equation}
+
+\begin{itemize}
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
+such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_d$ are entire functions of exponential type
+\item $R_0, \ldots, R_{d-1}$ are entire functions of exponential type. 
 \end{itemize}
@@
 
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=-\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ \footnote{Since $\sup\Lambda\leq -2$ we can assume $\varepsilon=1$ in Theorem 2.1.3 of {\tt regular Volterra}}.
+Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ \footnote{Since $\sup\Lambda\leq -2$ we can assume $\varepsilon=1$ in Theorem 2.1.3 of {\tt regular Volterra}}.
 
@@
         \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^dR_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
         &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
@@
         \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
-        \item along that direction, the germ $\tilde{\psi}_j$ grows sub-exponentially. 
+        \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
     \end{itemize}
     The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-\textcolor{magenta}{[why they are there?
-add comment][Take a more careful look at Lemma 3.9 \cite{Del}]}
+In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII},\S 2.5 \cite{loday-Remy2011}).
+Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
+    \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
+    \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero
+
+    \begin{align*}
+        &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
+        &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
+        &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
+    \end{align*}
+    If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
+    \begin{align*}
+        f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
+        &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
+    \end{align*}
+    Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
+
+    \begin{align*}
+        \left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)\right]f_{j,n}=-\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r f_{j,n-1}
+    \end{align*}
+    and since $R_r$ is entire, the right-hand side is an infinite sum of the convolution product of an entire function with $f_{j,n-1}$, hence it  has the same singularities as $f_{j,n-1}$ (see Lemma 6.15 \cite{diverg-resurg-i}).
+Therefore, we deduce $f_{j,1}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$ and inductively, $f_{j,n}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$.
+
+    Let $\theta$ be the direction that avoids all the singularities, we now prove that the analytic continuation of $\hat{\psi}_j$ grows sub-exponentially.
+In fact, it is enough to adapt the Gr\"onwall lemma to integral equations (see Lemma 3.9 \cite{diverg-resurg-iii}]).
+   Let $\Omega$ be the open domain where $\hat{\psi}_j$ is analytic and let $p$ be a point in $\Omega$ such that $\Omega':=\Omega\setminus B_{r}(\alpha_j)$ is star-shaped from $p$ ($B_r(\alpha_j)$ is the ball of radius $r$ and center in $\alpha_j$).
+By assumption on the coefficients of the ODE \eqref{eqn:standard ODE}
+   \begin{align*}
+       a:=\sup_{\zeta\in\Omega'}\frac{|Q|(|\zeta|)}{|P(-\zeta)|}<\infty\, \qquad b:=\sup_{\zeta\in\Omega'}\frac{1}{|P(-\zeta)|}<\infty
+   \end{align*}
+   hence, for every $\zeta\in\Omega'$, writing $\xi=|\zeta|$ and $\zeta=p+\xi e^{i\eta}$
+   \begin{align*}
+       |\hat{\psi}_j(\zeta)|&\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+       &\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+       &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
+       &\qquad +c\left[\int_{|\alpha_j|}^{|p|}|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|} \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+       &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
+       &\qquad + a'\int_{|\alpha_j|}^{|p|}|\hat{\psi}_j(\rho e^{i\theta})|d\rho+ c\sum_{r=0}^{d-1}\int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot  \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho%\\
+       %&\leq a \int_{|\alpha_j|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho \\
+       %&=a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|p|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho+\\
+       %&\qquad + a \int_{|\alpha_j|}^{|p|}  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho
+   \end{align*}
+   where $\hat{R}_r=\borel(z^{-2}R_r)$, for every $r=0,...,d-1$. 
+   %For every $r=0,...,d-1$, we define $F_r(z)=R_r(z)$
+   We want to show that for every $m\geq 0$, $|\hat{\psi}_j(\zeta)|<\hat{W}_m(\xi)$ for $\zeta$ on the ray $\zeta=p+\xi e^{i\theta}\in\Omega'$, where $\hat{W}_m$ is the unique solution of
+
+   \begin{equation}
+       \hat{W}=m+a\ast_{|p|}\hat{W}+c\sum_{r=0}^{d-1}\hat{R}_r\ast_{|p|} (-\zeta^r\hat{W})
+   \end{equation}
+
+   \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them.
+This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
+   There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$.
+Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$?
+}
 \end{proof}
@@
 \color{black}
-\subsection{Borel regularity for thimble integrals}
-
-Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic Morse function $f\colon X\to\C$ with only simple critical points. Set
+\subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
+
+Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{x_1,...,x_N\}$. Set
 \begin{equation}\label{exp-int}
-I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
-\end{equation}
-where $\mathcal{C}$ is a contour chosen to make the integral well-defined.  
-At a Morse critical point $x_\alpha$ of $f$, the saddle point approximation gives the formal series 
+I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
+\end{equation}
+where $\Lambda_j$ is the thimble associated with the critical point $x_j$.  
+The saddle point approximation gives the formal series 
 \begin{equation}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
-\end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-
-\begin{theorem}\label{thm:maxim} Let $N=1$.
-Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then:
+{I}_{j}(z)\defeq\int_{\Lambda_j}e^{-zf}\nu\sim \tilde{I}_{j}\defeq e^{-z\alpha_j}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to\infty
+\end{equation}
+
+\textcolor{orange}{[cite or prove]}
+%Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
+
+\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
 \begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1, thus $\hat{\varphi}_\alpha(\zeta)\defeq\borel_\zeta(\tilde{\varphi}_\alpha)$ converges near $\zeta=\zeta_{\alpha}$
-\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
+\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is Gevrey-1, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
 \begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
+\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
 \end{multline}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
-Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textbf{[Be careful about the orientation of $\Lambda_j$.]}
 \end{enumerate}
@@
 
-Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $f(x_j)$ with $\tfrac{1}{2} \tau^2 = f - f(x_j)$.
+Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
 \textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
+I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
 that converges in some disk $|\tau| < \varepsilon$.
 
-\color{magenta}{By the steepest descent method,
+By the steepest descent method,
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. [Veronica: I don't think this is the claim of steepest descendet method]} 
+\[ e^{\textcolor{magenta}{+}z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $\Re z \to \infty$. 
 \color{black}\textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
 \begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
+e^{-z \alpha_j} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
 \end{align*}
@@
 \begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
-\end{align*}
+e^{-z \alpha_j} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+\end{align*}
+
+----------- TO BE VERIFIED ---------------
 
 The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-These terms are crucial, however, for the convergence of the sum.
-To see why, consider their absolute sum $C_\text{exp}$.
+\textcolor{magenta}{These terms are crucial, however, for the convergence of the sum.[Veronica: I don't understand why the sum should be convergent...in fact I think we should get a divergent series]} To see why, consider their absolute sum $C_\text{exp}$.
 When $z \in [0, \infty)$,
@@
 is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.
+
 \color{magenta}
+[Veronica suggestion]
+
 \begin{claim}
@@
 
-By the dominant convergence theorem ...
-\begin{equation}
-    e^{-zf(x_\alpha)}I_\alpha(z)\approx\sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,\left[z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)-2e^{-z\varepsilon^2/2}\sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\right]
-\end{equation}
-hence we have to estimate the growth of 
-\[-2\sqrt{2\pi} e^{-z\varepsilon^2/2} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \sum_{\substack{k\in\mathbb{N}_+\\k\leq n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!}z^{n-k+1}\]
-
-as $\Re z\to\infty$. 
+Indeed,
+
+\begin{align*}
+    \Bigg | 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | \leq 
+\end{align*}
+
 \color{black} %Hence,
 %\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
-Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$\textcolor{magenta}{ shrink exponentially as $z$ grows, allowing the simpler estimate
+\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]} 
+\textcolor{magenta}{[check!]}
+Call the right-hand side $\tilde{I}_\alpha$. We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem. \textbf{[Resolve discrepancy with previous calculation.]}
+
+-------- From here it is OK---------
+
+\vspace{5mm}
+
+Note that 
+\begin{align*}
+\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
+\end{align*}
+
+We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
 Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-Part~\eqref{int:resum-converges}: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
-\end{align*}
-Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
-
-Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
-As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is Gevrey-1.
+
+%Part~\eqref{int:resum-converges}: \begin{align*}
+%\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+%(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
+%\end{align*}
+%Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
+
+Part~\eqref{int:resum-valid}: Let us recast the integral $I_j$ into the $f$ plane.
+As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
 Hence, we have
 \begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
+I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
+& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
 \end{align*}
@@
 \begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
-\begin{align*}
-\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \borel_{\zeta_\alpha} \tilde{I}_\alpha.
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
-
-Theorem~\ref{thm:frac-diff-borel} tells us that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \borel \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
+\nu & = \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{n/2}\,\frac{df}{[2(f - f(x_j))]^{1/2}} \\
+& = \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\hat{\iota}_j$, we learn that
+\begin{align*}
+\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
+& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \\
+& = \borel_{\zeta} \tilde{I}_j.
+\end{align*}
+
+We have now shown that the sum of $\borel_{\zeta} \tilde{I}_j$ is actually equal to $\hat{\iota}_j$.
+
+%Let $\tilde{\Phi}_j\in\C[\![z^{-1}]\!]$ be such that $\tilde{I}_j(z)=e^{-z\alpha_j}z^{-1/2}\tilde{\Phi}_j(z)$,  
+By the action of $\borel_\zeta$ on transseries (\S \ref{sec:action_transseries}) and the properties of convolution (\S \ref{convolution}) we know 
+\begin{align*}
+\borel_{\zeta} \tilde{I}_j & = \borel_{\zeta}( z^{-1/2} \tilde{\Phi}_j) \\
+&=\borel_\zeta z^{-1/2}\ast_{\alpha_j}\borel_\zeta\tilde{\Phi}_j\\
+& = \fracderiv{-1/2}{\zeta}{\alpha_j}  \tilde{\phi}_j \\
+%& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
 \end{align*}
@@
 \begin{equation}\label{shifted-resum-valid}
-\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{equation}
-Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
-\begin{align*}
-I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
-& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
-\end{align*}
-as we claimed.
+\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{\alpha_j} \tilde{\phi}_j.
+\end{equation}
+Taking the Laplace transform of both sides and applying properties of the Borel transform (\S \ref{properties Borel transform}), we see that
+\begin{align*}
+I_j(z) & = \laplace_{\zeta, \alpha_j} \left[ \partial^{-1/2}_{\zeta, \alpha_j}  \tilde{\phi}_j \right] \\
+& = z^{-1/2} \laplace_{\zeta, \alpha_j} \tilde{\phi}_j,
+\end{align*}
+as we claimed. \textcolor{orange}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
 
 Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
+\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{\alpha_j} \tilde{\phi}_j. \]
+
 Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
+\[ \hat{\iota}_j(\zeta) = \partial_\zeta \left( \int_{\Lambda_j(\zeta)} \nu \right), \]
 we can see that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
-The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
-\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
+\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(\textcolor{Magenta}{\alpha_j})} \nu. \]
+The initial value term vanishes because the path $\textcolor{Magenta}{\alpha_j}$ is a point. Hence,
+\[ \int_{\Lambda_j(\zeta)} \nu = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j(\zeta). \]
 Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
+\[ \fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)} \nu \right) = \hat{\phi}_j(\zeta). \]
 \end{proof}
 
-\section{Examples}
+\section{Examples}\label{sec:examples}
 
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
 \[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
+where $\Lambda_{j}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$ (see Figure \ref{fig:thimble_n_5}).
+
+\begin{figure}[h]
+    \centering
+   % \includegraphics{}
+    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.}
+    \label{fig:thimble_n_5}
+\end{figure}
 
@@
 
-The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
+Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns \textcolor{orange}{convergent formal solutions [Veronica: what do you mean by convergent formal?
+It looks like a contradiction]} of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
 Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
@@
 Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
+
 \subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
-We can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
+
+We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
 Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
@@
 
-The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-\begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-\end{align*}
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
+Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$:
+
+\begin{align*}
+    \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))}&=\frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
+    &=\frac{\sin(m\phi)}{\sin(n \phi)}\\
+    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};\sin^2(n \phi)\right)\\
+    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right) 
+\end{align*}
+where in the last step we use $-\zeta=T_n(u)=T_n(\cos\phi)=\cos(n\phi)$. Applying identity 15.8.4, 15.8.27 and 15.8.28 from \cite{dlmf},
+
+\begin{align*}
+    &{}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right)=\\
+    &\qquad = \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right)\Gamma\left(1+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{1}{2};\zeta^2\right)+\\
+    &\qquad \qquad\qquad - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2}-\frac{m}{2n}\right)\Gamma\left(\frac{1}{2}+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(1-\frac{m}{2n},1+\frac{m}{2n};\frac{3}{2};\zeta^2\right)\\
+    &\qquad ={}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)+\\
+    &\qquad\qquad +\frac{1}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)-\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\\
+    &\qquad =\frac{3}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
+\end{align*}
+In addition, recall that ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ has a branch cut singularity at $\zeta=-1$ while ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ has a branch cut at $\zeta=1$; hence
+
+\begin{align*}
+    K_{m/n}(z)&=-\frac{m}{4 n\sinh(\tfrac{m}{n}i\pi)}\int_{\gamma_z}e^{-z\zeta} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) d\zeta\\
+    &=-\frac{1}{2}\int_{1}^{+\infty}e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right) d\zeta
+\end{align*}
+
+where in the second step we use the analytic continuation of the hypergeometric function (equation 15.2.3 in \cite{dlmf}).
+
+Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
+\begin{align*}
+    K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
+\end{align*}
+
+\subsubsection{A flavour of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
+
+In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (\S\ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (\S\ref{contour-argument-AL}).
+Up to a constant, in both cases we find
+
+\begin{align*}
+    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
+\end{align*}
+
+which has a fractional power singularity at $\zeta=1$.
+In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of Ecalle's resurgent functions.
+More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new germ of holomorphic function, which has a branch cut singularity at $\zeta=-1$.
+Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
+
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
+\end{align*}
+
+Hence, we deduce  
+\begin{equation}\label{resurgent-relation-1}
+    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
+\end{equation}
+
+namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
+This is an instance of \textit{resurgent functions}, introduced by Ecalle in \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}\footnote{If the reader is interesting in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i}\cite{Dorigoni}\cite{aniceto2019primer}.}.
+Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
+The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
+
+We can repeat the same reasoning with $v_{-1}$:
+
+\begin{align*}
+    v_{-1}(\zeta)=  \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
+\end{align*}
+
+and ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ is singular at $\zeta=1$. Hence
+
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right)=\\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
+&=2 i\cos(\pi m/n) \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
+&=2i \cos(\pi m/n)\, \left(\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right)
+\end{align*}
+
+and the analogue of \eqref{resurgent-relation-1} is 
+\begin{equation}\label{resurgent-realtion-2}
+    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
+\end{equation}
+
+Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are a manifestation of the Stokes phenomena, already in the position domain.
+Indeed, when we start varying the contour of integration for the Laplace transform, we know that $\laplace_{\zeta,1}^\pi$ and $\laplace_{\zeta,-1}^0$ are not well defined because the contour hits the other singularity (respectively at $\zeta=-1$ and $\zeta=1$).
+The Stokes phenomenon consists of comparing the Laplace transform below and above the critical direction and it quantifies the jump as a constant (the so-called Stokes constant) times another function.
+In our example:
+
+\begin{align*}
+    \laplace_{\zeta,1}^{\pi+\varepsilon} v_1-\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = 2 i \cos(\pi m/n) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
+    \laplace_{\zeta,-1}^{\varepsilon} v_{-1}-\laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = - 2 i \cos(\pi m/n)  \, e^z \, \laplace_{\zeta,1} v_{1} 
+\end{align*}
+
+thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$\footnote{If we think of the Laplace transforms of $v_1$ and $v_{-1}$ as a frame of solutions for the Airy--Lucas differential equation, the equations above define the so-called Stokes matrices for the ODE.}.
+
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pair of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Figure \ref{fig:intersection_thimbles}.
+However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on a lift of a path in the position domain.
+\textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
+
+\begin{figure}[h]
+    \centering
+    %\includegraphics{}
+    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$.
+We choose $n=4$ and $n=5$.
+}
+    \label{fig:intersection_thimbles}
+\end{figure}
+
+%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
+%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
+Let's assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+
+%The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
+%\begin{align*}
+%& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
+%= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
+%\end{align*}
+%as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
 Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-\color{DarkCyan}
-Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-where $\zeta = -1 + \zeta_{-1}$.
-\color{black}
+%\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+%\color{DarkCyan}
+%Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
+%\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
+%In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
+%\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
+%where $\zeta = -1 + \zeta_{-1}$.
+%\color{black}
 
@@
 
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf})
+and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf} \textcolor{red}{10 \cite{watson1922treatise}})
 
@@
 I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]
-\end{align*}
-
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
+K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]\\
+\color{red}K_{\mu}(z)& \color{red}=\int_{-\infty+i\pi/2}^{+\infty+\pi i/2} e^{-\cosh(t)+\mu t} dt \text{  for } -1<\Re \mu<1
+\end{align*}
+
+where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ (see Figure \ref{fig:Omega_path}).
 
 \begin{figure}[h]
-\caption{Add figure path $\Omega$}
+\center
+\begin{tikzpicture}
+        \draw[->] (0,2)--(4,2);
+        \draw[->] (2,0)--(2,4);
+        \draw[red,very thick,->] (4,1.5)--(3,1.5);
+        \draw[red,very thick] (3,1.5)--(2,1.5);
+        \draw[red,very thick] (4,2.5)--(3,2.5);
+        \draw[red,very thick,->] (2,2.5)--(3,2.5);
+        \draw[red,very thick] (2,1.5)--(2,2.5);
+        \node[red,below, font=\tiny] at (4,1.5) {$\Omega$};
+        \node[font=\tiny,left,below] at (1.75,1.5) {$-i\pi$};
+        \node[font=\tiny] at (1.8,2.5) {$i\pi$};
+\end{tikzpicture}
+\caption{The path $\Omega$. }\label{fig:Omega_path}
 \end{figure}
@@
 \begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{1}\big)\\
+v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_{1}\big)\\
 v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
 \end{align*}
-\item \textbf{Borel regularity} \textcolor{Lime}{[Check with Aaron how to phrase it]} 
-\end{itemize}
-
-On the other hand, the contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
+\item \textbf{Borel regularity} We can compare the Borel transform of the formal solutions $\tilde{W}_{\mu,\pm1}$ with the analytic solutions $v_{\mu,\pm 1}$.
+They agree (up to the choice of a constant), hence we have another example where Borel regularity can be checked explicitly.
+\end{itemize}
+
+The contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
 
 \subsubsection{Lifting to a countable cover}\label{countable-cover}
-Formula~\eqref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
+Formula~\eqref{integral:mod-bessel-rational-AL} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
 Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
@@
 \end{align*}
-we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
+we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
 \begin{align}
@@
 \notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
+& \label{int:mod-bessel-gen} = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
 \end{align}
@@
 
-When $\mu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
+\begin{center}
+    \begin{tikzpicture}
+        \draw[->] (6,2)--(10,2);
+        \draw[->] (8,0)--(8,4);
+        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
+        %\draw[red,thick,->] (10,2)--(9,2);
+        %\draw[red,thick] (9,2)--(8.5,2);
+        %\draw[red,thick] (10,2)--(9.3,2);
+        %\draw[red,thick,->] (8.5,2)--(9.3,2);
+        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
+        \node[font=\tiny,below] at (8.5,2) {$1$};
+    \end{tikzpicture}
+\end{center}
+
+We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
+
+\begin{align*}
+    K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
+    &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
+\end{align*}
+
+where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf}
+
+\begin{multline*}
+     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) = \\
+     =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
+\end{multline*}
+hence
+
+\[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
+
+Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
+
+\begin{align}
+    K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
+    &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
+\end{align}
+
+When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
 \[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
@@
 \end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
+with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
+
+\begin{equation}
+    K_0(z)=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
+\end{equation}
+\textcolor{orange}{[can we use (51) directly?
+It seems to me that if I try the contour argument from the integral expression directly, I'm not able to write write $1/\sinh(it)$ as a function of $\zeta$.
+]}
 
 \subsection{Higher Airy}
+
+\textcolor{magenta}{[The higher Airy example is not completed and there are still some difficulties in the computations, even for simple examples. Should we remove it?]}
 
@@
 
+\textcolor{orange}{we may try to do the computations of Stokes constants for $p=1$, when $\hat{w}_1$ simplifies to a Gauss hypergeometric.
+Use also information about the monodromy.
+Check change of coordinates $y=\zeta^2$.}
+
+\subsubsection{Fractional derivative formula}
+
+In Theorem \ref{thm:maxim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
+
+\subsection{Third-order thimble integrals}
+
+Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
+Furthermore, we can restrict to monic polynomials by setting $a_3=1$.}, we are going to consider thimble integrals of the form
+
+\[ I_j(z) = \int_{\Lambda_j} \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
+
+where $\Lambda_j$ is a thimble in $H_{z,1}^B$ through a critical point of $f$.
+We can distinguish between the case when $f$ has two distinct critical points $\alpha_+, \alpha_-$ and only one critical point $\alpha$.
+In both cases, we will compute the differential equation satisfied by $I$.
+
+\begin{lemma}
+    Let $f(u)=u^3+pu+q$, 
+    \begin{itemize}
+        \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
+        \begin{equation}\label{eqn:degree-3-poly-2roots}
+            \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
+        \end{equation}
+        \item  if $p=0$, then $I(z)$ solves
+        \begin{equation}\label{eqn:degree-3-poly-1root}
+            \left[\partial_z+q+\frac{1}{3z}\right]I=0
+        \end{equation}
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    The proof follows from a direct computation. 
+\end{proof}
+
+Let us first assume $p\neq 0$, then $\alpha_{\pm}=\pm\sqrt{-p/3}$.
+Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=-\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
+
+\begin{equation}\label{eqn:deg3-borel-ODE}
+    \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
+\end{equation}
+
+Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=f(\alpha_+)$: in the new coordinate $\zeta_+:=\zeta-f(\alpha_+)$, equation \eqref{eqn:deg3-borel-ODE} becomes
+
+\begin{equation*}
+    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, \alpha_+)\partial_{\zeta_+}^2+ \left[2p\, \alpha_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
+\end{equation*}
+
+which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,\alpha_+}\zeta_+$
+
+\begin{equation*}
+    \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
+\end{equation*}
+
+and it admits a slight solution
+
+\begin{align*}
+    v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
+    &=\left(\frac{3}{4p\,\alpha_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_+}\zeta_-\right). 
+\end{align*}
+
+Notice that $v_+$ is an hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-f(\alpha_-)$
+
+\begin{equation*}
+    v_- =\left(\frac{3}{4p\,\alpha_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_-}\zeta_-\right). 
+\end{equation*}
+
+When $p=0$, the critical point of $f$ is $\alpha=0$ and we can argue as before: $\laplace_{\zeta,f(\alpha)}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
+
+\begin{align*}
+   \left[ (\zeta-q)\partial_\zeta +\frac{2}{3}\right] v=0
+\end{align*}
+
+namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
+The same result is confirmed by the contour argument which in this simple case reads
+
+\begin{align*}
+    \int_{\Lambda} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
+    &= e^{i\pi/3} \int_q^{+e^{i\theta}\infty} e^{-z\zeta} \, \zeta_q^{-2/3}\,  d\zeta
+\end{align*}
+
+where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin.
+
+\textcolor{orange}{[It'd be nice to have the contour argument for $p\neq 0$ too, however we don't have the same nice coordinates as in the other examples--maybe we can do a change of coordinates to recover $K_{1/3}$ as suggested below.]}
 \color{DarkTurquoise}
-
-\section{Third-order exponential integrals}
 \begin{itemize}
@@
 \begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
 \end{equation}
@@
 \end{alignat*}
-From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:reg-mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
 Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
@@
 \[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
+The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\eqref{eqn:reg-mod-bessel}.
 
@@
 \[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\ref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the contour integration method of solving equation~\eqref{eqn:mod-bessel} is associated with the basis
+of equation~\eqref{diff-eq:spatial-mod-bessel}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
+
+In summary, the contour integration method of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
 \begin{align*}
@@
 
-The Laplace transformation method of solving equation~\eqref{eqn:mod-bessel}, on the other hand, is associated with the basis
+The Laplace transformation method of solving equation~\eqref{eqn:reg-mod-bessel}, on the other hand, is associated with the basis
 \begin{alignat*}{2}
@@
 The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
-Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see Lemma 6.106 \cite{MS}).
+Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see part c of \cite[Section 6.14.5]{diverg-resurg-i}).
+Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see \cite[Lemma 6.106]{diverg-resurg-i}).
 %Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
@@
 
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
-
-By general theory it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
+In Section \ref{sec:examples}, we computed the Borel transform of the asymptotics of thimble integrals in different ways: on the one hand, using the contour argument and on the other hand, solving an integral equation with a specified behavior near the singular point.
+In particular, we noticed that the two approaches give the same result up to the choice of a constant, as the integral equation is homogeneous.
+However, Theorem \ref{thm:maxim} suggests another approach, namely to use the fractional integral formula \eqref{formula1}.
+This approach
+As shown in the previous examples, the Borel transform  of the asymptotics of thimble integrals can be computed in different ways: from the ODE they solve, from the contour argument, and from the integral formula \eqref{formula1}.
+When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneous, while with the contour argument and the fractional integral formula the ambiguity is solved.
+
+%In addition, since thimble integrals have a geometric interpretation, the Stokes constants that encode the jumps of thimble integrals when $z$ crosses a Stokes ray are expected to be integers as they are intersection numbers of dual pairs of thimbles.
+
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
+
+By general theory, it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
 Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the contour argument and from the integral formula.

### 2023-07-23 reg-sing-volterra.tex
Revise hypotheses and function spaces
Argue that the new function spaces are complete. Since our exponential
weight isn't holomorphic, the argument is more involved than before.

@@
 \theoremstyle{plain}
-%%\newtheorem{prop}{Proposition}
+\newtheorem{prop}{Proposition}
 \newtheorem{thm}{Theorem}
@@
 \newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
+\newcommand{\cont}{\mathcal{C}}
+\newcommand{\holo}{\mathcal{H}}
+\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
 \newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
@@
 \frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
-\laplace k\;\laplace f & = k * \varphi \\
+\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
 z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,
@@
 \subsection{Main result}
-\begin{defn}\label{fin-order}
-Consider a Volterra operator $\mathcal{V}$ of the form
-\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
-We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
-\begin{itemize}
-\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
-\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
-\end{itemize}
-and at one of the following holds:
-\begin{enumerate}
-\item\label{case:0th-order} $m$ isn't the zero function.
-\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
-\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
-where {\rm ``diag''} means the diagonal in $\Omega^2$.
-\end{enumerate}
-We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
-\end{defn}
+%%\begin{defn}\label{fin-order}
+%%Consider a Volterra operator $\mathcal{V}$ of the form
+%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
+%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
+%%\begin{itemize}
+%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
+%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
+%%\end{itemize}
+%%and at one of the following holds:
+%%\begin{enumerate}
+%%\item\label{case:0th-order} $m$ isn't the zero function.
+%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
+%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
+%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
+%%\end{enumerate}
+%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
+%%\end{defn}
 \textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
@@
 \begin{thm}
-Let $\Omega$ be an acute-angled sector around $0$ in the complex plane.
+Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane.
+\textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
+\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
+where
+\begin{itemize}
+\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
+\begin{itemize}
+\item a simple zero at $\zeta = 0$,
+\item no zeros in $\Omega$ (as the next condition implies), and
+\item a positive lower bound $C_p |z|^d \le |p|$;
+\end{itemize}
+\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
+\begin{itemize}
+\item an upper bound $|q| \le C_q |z|^{d-1}$; and
+\end{itemize}
+\item $\mathcal{R}$ is an integral kernel operator
+\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
+where $k$ is a holomorphic function on $\Omega^2$, with
+\begin{itemize}
+\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
+\end{itemize}
+\end{itemize}
+Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.
+
+For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
+\[ \mathcal{V}f = 0 \]
+has a unique solution in the affine subspace
+\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
+of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
+\end{thm}
+%%\begin{thm}
+%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane.
 \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}
 
-Consider a Volterra operator
-\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
-over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$.
+%%Consider a Volterra operator
+%%\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
+%%over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$.
 To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
-\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
-which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
+%%\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
+%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
 
-Assume, furthermore, that:
-\begin{itemize}
-\item There's some $c \in (0, \infty)$ for which
-$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
-\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
-\item $p$ has a simple zero at $\zeta = 0$.
-\end{itemize}
-Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
+%%Assume, furthermore, that:
+%%\begin{itemize}
+%%\item There's some $c \in (0, \infty)$ for which
+%%$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
+%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
+%%\item $p$ has a simple zero at $\zeta = 0$.
+%%\end{itemize}
+%%Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
 
-Under these conditions, let's try to solve the regular singular Volterra equation
-\[ \mathcal{V}f = 0. \]
-The leading-order part of the equation,
-\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
-has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$.
+%%Under these conditions, let's try to solve the regular singular Volterra equation
+%%\[ \mathcal{V}f = 0. \]
+%%The leading-order part of the equation,
+%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
+%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$.
 If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
-\[ f = \zeta^{\tau-1} + f_*, \]
-where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
-\end{thm}
+%%\[ f = \zeta^{\tau-1} + f_*, \]
+%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
+%%\end{thm}
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
@@
 Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
+Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$.
+Give $\cont(\Omega)$ the compact-open topology, recalling that this is the finest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}.
+The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.
+
+Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.
+They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
+With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
+That means the inclusion is continuous.
+\begin{prop}\label{exp-complete}
+The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
+\end{prop}
+\begin{proof}
+\textcolor{orange}{[Check!]} Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$.
+The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$, as discussed above, so our sequence is Cauchy in $\holo(\Omega)$ too.
+Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal}, our sequence converges to a function $f$ there.
+
+The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|} |f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|} |f - f_n| \le r$.
+This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
+We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$.
+Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
+\end{proof}
+
+Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
+Let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
+Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
+Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
+\begin{prop}
+The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
+\end{prop}
+%%Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
 For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
 We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
-\begin{align*}
-\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
-\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
-\end{align*}
-is an isometry. More generally,
-\begin{align*}
-\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
-f & \mapsto \zeta^\delta f
-\end{align*}
-is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
+%%\begin{align*}
+%%\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
+%%\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
+%%\end{align*}
+%%is an isometry. More generally,
+%%\begin{align*}
+%%\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
+%%f & \mapsto \zeta^\delta f
+%%\end{align*}
+%%is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
 \subsection{Graded algebra structure}

### 2023-07-24 reg-sing-volterra.tex
Outline proof of main result
Comment out sketch of graded algebra structure.

@@
 \newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
+
+% function spaces
 \newcommand{\cont}{\mathcal{C}}
@@
 \newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
-\DeclareMathOperator{\Ai}{Ai}
+
+% operator under consideration
+\newcommand{\volterra}{\mathcal{V}}
+\newcommand{\hardpart}{\mathcal{V}_\text{hard}}
+\newcommand{\softpart}{\mathcal{V}_\text{soft}}
 
@@
 \title{Regular singular Volterra equations on complex domains}
-\author{Aaron Fenyes}
+\author{Aaron Fenyes and Veronica Fantini}
 \date{}
@@
 %%is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
-\subsection{Graded algebra structure}
-For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
-\begin{verify}
-\begin{align*}
-\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
-& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
-& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
-& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
-\end{align*}
-\end{verify}
-Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade.
+%%\subsection{Graded algebra structure}
+%%For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
+%%\begin{verify}
+%%\begin{align*}
+%%\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
+%%& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
+%%& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
+%%& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
+%%\end{align*}
+%%\end{verify}
+%%Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade.
 For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
-\subsection{Norms of effectively finite-order operators}
-\begin{itemize}
-\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
-\begin{align*}
-\|mf\|_{\infty, \sigma; Z} =
-\end{align*}
-\end{itemize}
+%%\subsection{Norms of effectively finite-order operators}
+%%\begin{itemize}
+%%\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
+%%\begin{align*}
+%%\|mf\|_{\infty, \sigma; Z} =
+%%\end{align*}
+%%\end{itemize}
 
-which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
+%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
+\section{\textcolor{orange}{[Proof of main result]}}
+\subsection{Overview}
+\subsection{An approximate solution}
+\subsubsection{Construction}
+\subsubsection{Asymptotics}
+\subsubsection{Image under $\softpart$}
+\subsection{Making $\volterra$ a contraction}
+\subsubsection{Near the origin}
+\subsubsection{Away from the origin}
 %------------------------------------------------------------------------

### 2023-07-24 exp-resurgence.tex
Updates from Overleaf

@@
 \begin{enumerate}
-\item Solving a linear ODE of single level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
+\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
 One example is Equation~\eqref{eqn:bessel-rescaled-1}.
@@
 \end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{A function $f$ is of exponential type if $|f(z)|\leq C e^{-a|z|}$ for $C,a>0$.
-Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
-Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
 Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
@@
 
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ in \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Braaksma,Loday-Richaud, check]}.
-Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
+Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
+Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
 
@@
 There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII}\cite{loday-Remy2011}}.
+Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII,loday-Remy2011}}.
 It can indeed be seen as a consequence of ``resurgence'' of the ODE.
@@
 
-Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, Andersen, Mistergad, the Stirling series for Gamma function in \cite{Maxim_slide_ERC}).
+Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
 
@@
 We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+\color{DarkBlue}
 Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
@@
 How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}} For each critical point $\alpha_j$, let $\Gamma_j$ be the ray going rightward from $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
+We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}}
+\color{black}
+For each critical point $x_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j:=f(x_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
 These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves \textcolor{magenta}{[add picture]}, as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $\alpha_j$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$.
+The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
+The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $x_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.
+
+\begin{figure}[h]
+    \centering
+    %\includegraphics{}
+    \caption{The preimage of a ray departing from the critical value and going to infinity.}
+    \label{fig:thimble_vs_rays}
+\end{figure}
+
 %The {\em thimble integral}
@@
 \begin{enumerate}
-\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is Gevrey-1, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
 \item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
@@
 
-The idea of the proof is sketched below and represented in the following diagram:
+The idea of the proof is sketched below in the following diagram:
 \[
@@
 
-On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
+on the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
 as the Laplace transform of a function $\iota_j$.
 In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}.
-On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal Gevrey-1 series.
-Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-At this point we realise that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
-In a nutshell, thimble integrals are Borel regular because they are Laplace transforms.
+On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
+Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
+At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
+In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
 
@@
 This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls}, \cite{dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls,dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.
 
@@
 If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\textcolor{magenta}{[Add this part in Airy with pictures]}
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
+
+\begin{figure}[h]
+    \centering
+    %\includegraphics[]{}
+    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
+However, the fiber over a singular point of $B$ has an interesting structure.
+Here we represent the example of Airy functions.}
+    \label{fig:different_fibres}
+\end{figure}
 
@@
 Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}, \cite{loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
+Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
 For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
@@
 
-It obeys the expected semigroup law \cite[\S 1.3]{mladenov2014advanced}
+It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
 \begin{align*}
@@
 
-\subsection{The Borel transform on Gevrey-$1$ series}
+\subsection{The Borel transform on $1$-Gevrey series}
 %\color{gray}
@@
 So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
-These formal series are the so-called Gevrey-$1$ series:
+These formal series are the so-called $1$-Gevrey series:
 \[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+is $1$-Gevrey if there exists $A>0$ such that $|a_n|\leq A^n n!$ \textcolor{magenta}{[isn't it $\lesssim$\,?]} for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
 there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
@@
 Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
+Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
 \end{lemma}
 
-In fact, we deduce that the Borel transform is an isomorphism between Gevrey-$1$ series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
+In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
 The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
@@
 
-The space of Gevrey-$1$ formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
+The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
 The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
@@
 \begin{lemma}
-    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
+    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
 \end{lemma}
@@
     \end{equation}
-    where $R_n(z)$ are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
+    where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
 This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
@@
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_{d-1}$ are entire functions of exponential type. 
+\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
 \end{itemize}
@@
 \begin{theorem}\label{thm1-dim}
-In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
+\textcolor{orange}{[Revise to match \texttt{reg-sing-volterra}]} In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
 \begin{equation}\label{P-hat_j}
@@
 \begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
+It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}.
 In fact, $P(-\zeta_j-\alpha_j)=P(-\zeta)$ is a polynomial also defined at $\zeta=\alpha_j$ and by assumption $P'(-\alpha_j)\neq 0$.
@@
     The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII},\S 2.5 \cite{loday-Remy2011}).
+In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
 Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
@@
 \begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is Gevrey-1, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
 \item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
@@
 Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is Gevrey-1.
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
 
@@
 
-where $\Lambda_j$ is a thimble in $H_{z,1}^B$ through a critical point of $f$.
-We can distinguish between the case when $f$ has two distinct critical points $\alpha_+, \alpha_-$ and only one critical point $\alpha$.
+where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
+We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$.
 In both cases, we will compute the differential equation satisfied by $I$.
@@
 
-Let us first assume $p\neq 0$, then $\alpha_{\pm}=\pm\sqrt{-p/3}$.
-Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=-\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
+Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$.
+Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
 
@@
 
-Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=f(\alpha_+)$: in the new coordinate $\zeta_+:=\zeta-f(\alpha_+)$, equation \eqref{eqn:deg3-borel-ODE} becomes
+Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes
 
 \begin{equation*}
-    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, \alpha_+)\partial_{\zeta_+}^2+ \left[2p\, \alpha_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
+    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
 \end{equation*}
 
-which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,\alpha_+}\zeta_+$
+which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$
 
@@
     v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
-    &=\left(\frac{3}{4p\,\alpha_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_+}\zeta_-\right). 
-\end{align*}
-
-Notice that $v_+$ is an hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-f(\alpha_-)$
+    &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
+\end{align*}
+
+Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$
 
 \begin{equation*}
-    v_- =\left(\frac{3}{4p\,\alpha_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,\alpha_-}\zeta_-\right). 
+    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
 \end{equation*}
 
-When $p=0$, the critical point of $f$ is $\alpha=0$ and we can argue as before: $\laplace_{\zeta,f(\alpha)}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
+When $p=0$, the critical point of $f$ is $x=0$ and we can argue as before: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
 
@@
 v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+&=\;& -i\,\left(\frac{\zeta_1}{2}\right)^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
 \end{alignat*}
@@
 v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+&=\;& \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
 \end{alignat*}

### 2023-07-25 reg-sing-volterra.tex
Show that V is a contraction near the origin

@@
 \newtheorem{thm}{Theorem}
+\newtheorem{rmk}{Remark}
 
@@
 \newcommand{\softpart}{\mathcal{V}_\text{soft}}
+
+% domain
+\newcommand{\domain}{\Omega}
+\newcommand{\near}{\Omega_\text{near}}
+\newcommand{\far}{\Omega_\text{far}}
 
@@
 \subsubsection{Image under $\softpart$}
-\subsection{Making $\volterra$ a contraction}
-\subsubsection{Near the origin}
-\subsubsection{Away from the origin}
+\subsection{Finding spaces where $\volterra$ is a contraction}
+In this section, we'll prove the following proposition.
+\begin{prop}\label{get-contraction}
+For each $\rho \in (\tau, \tau + \epsilon)$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
+\end{prop}
+\begin{rmk}
+For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda$, and may require $\Lambda \gg \lambda$.
+\end{rmk}
+First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By \textcolor{orange}{[limit property]}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+\begin{equation}\label{near-limit}
+|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
+\end{equation}
+for all $a, a' \in \near$.
+By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$.
+Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.
+
+Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$.
+In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
+In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
+Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
+Since we set $\sigma < \rho$, this proves Proposition~\ref{get-contraction}.
+\subsubsection{Near the origin}\label{near-bound}
+For each $a \in \domain$, we have
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)\,\varphi\;d\zeta| \]
+for any choice of integration path.\footnote{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
+& = \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
+\end{align*}
+Now, suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le
+\|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
+& \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
+\end{align*}
+for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight-line path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+& \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\;dt \\
+& = \frac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}.
+\end{align*}
+Since we set $\sigma < \rho$, this brings us halfway to proving that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$.
+\subsubsection{Away from the origin}\label{far-bound}
 %------------------------------------------------------------------------

### 2023-07-25 exp-resurgence.tex

@@
 
-\subsubsection{Regularity}
-
-We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
-
-\begin{lemma}\label{lemma-3.5}
-    Let $R_0>0$.
+%\subsubsection{Regularity}
+
+%We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
+
+%\begin{lemma}\label{lemma-3.5}
+ %   Let $R_0>0$.
 Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$.
 Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
-    \begin{equation}
-        |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
-    \end{equation}
-\end{lemma}
-
-\begin{proof}
-    The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
+  %  \begin{equation}
+   %     |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
+   % \end{equation}
+%\end{lemma}
+
+%\begin{proof}
+ %   The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
 By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$.
 The formal Borel transform of $f$ reads
-    \begin{align*}
-        \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
-    \end{align*}
-   and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
-   \begin{align*}
-       |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
-       &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
-       &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
-       &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
-   \end{align*}
-
-   This ensures the uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
-   \color{Turquoise}
-In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
-\begin{align*}
-    \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-    &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-    &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
-    &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
-\end{align*}
-   \color{black}
-\end{proof}
-
-\begin{lemma}\label{lemma-3.8}
-    Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
-    \begin{equation}\label{eqn:convolution}
-        \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
-    \end{equation}
-    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+  %  \begin{align*}
+   %     \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
+    %\end{align*}
+   %and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
+   %\begin{align*}
+    %   |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
+    %   &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
+   %    &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
+    %   &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
+   %\end{align*}
+
+  % This ensures uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
+   %\color{Turquoise}
+%In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
+%\begin{align*}
+ %   \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+  %  &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
+   % &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
+   % &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
+%\end{align*}
+%   \color{black}
+%\end{proof}
+
+%\begin{lemma}\label{lemma-3.8}
+ %   Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
+  %  \begin{equation}\label{eqn:convolution}
+   %     \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
+   % \end{equation}
+   % has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
 In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-\end{lemma}
-
-We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
-
-\begin{proof}
-    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+%\end{lemma}
+
+%We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
+
+%\begin{proof}
+ %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
 If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
 Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-    \begin{equation}
-        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
-    \end{equation}
+  %  \begin{equation}
+        %\tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
+   % \end{equation}
+   % This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
+Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
+By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
+%\end{proof}
+
+%\begin{lemma}\label{lemma-3.8bis}
+ %Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
+Then, the convolution equation
+ %   \begin{equation}\label{eqn:convolution-bis}
+  %      \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
+   %\end{equation}
+    %has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
+In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
+%\end{lemma}
+
+%\begin{proof}
+ %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
+If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
+Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
+  %  \begin{equation}
+   %     \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
+    %\end{equation}
+    %where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
 This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
@@
 By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-\end{proof}
-
-\begin{lemma}\label{lemma-3.8bis}
-    Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
-Then, the convolution equation
-    \begin{equation}\label{eqn:convolution-bis}
-        \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
-    \end{equation}
-    has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
-In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-\end{lemma}
-
-\begin{proof}
-    If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
-If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
-Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-    \begin{equation}
-        \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
-    \end{equation}
-    where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
-This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
-Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
-By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-\end{proof}
-
-\begin{remark}
-    Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
-\end{remark}
+%\end{proof}
+
+%\begin{remark}
+ %   Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
+%\end{remark}
 
@@
 such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ with $\Omega$ an open sectorial domain which touches but not contains $\alpha_j$.
+${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$ an open sectorial domain which closure contains $\alpha_j$.
 \end{theorem}
 \begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}.
-In fact, $P(-\zeta_j-\alpha_j)=P(-\zeta)$ is a polynomial also defined at $\zeta=\alpha_j$ and by assumption $P'(-\alpha_j)\neq 0$.
-$Q$ is also a polynomial defined at $\zeta=\alpha_j$.
-Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
-
-\begin{align*}
-&\partial_{\zeta,\alpha_j}^{-2}\circ\left[R_0(\partial_{\zeta,\alpha_j}^{-1})+R_1(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)+...+R_{d-1}(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^{d-1}\right]=\sum_{\lambda\leq -2} \partial_{\zeta,\alpha_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^{d-1} R_{k,\lambda}(-\zeta)^k.
-\end{align*}
+It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}. Without loss of generality, we will consider $\hat{P}_1$.
+
+\begin{align*}
+    \lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(\alpha_1-\zeta')}{P(-\alpha_1-\zeta_1)}\Big\vert &=\lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(-\alpha_1-\zeta')}{\zeta_1(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)}\Big\vert\\
+    &=\Big\vert \frac{Q(-\alpha_1)}{(\alpha_2-\alpha_1)...(\alpha_d-\alpha_1)}\Big\vert\\
+    &=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert
+\end{align*}
+in particular notice that $\tau_1:=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert>0$ (since $Q(-\alpha_j)\neq 0$).
+
+Since $P$ and $Q$ are polynomials, we get the following estimates:
+
+\begin{align*}
+    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{1}{P(-\alpha_1-\zeta_1)}\Big\vert=|P(-\alpha_1-\delta)|^{-1}
+\end{align*}
+
+\begin{align*}
+    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{Q(-\alpha_1-\zeta_1)}{P(-\alpha_1-\zeta_1)}\Big\vert=\Big\vert\frac{Q(-\alpha_1-\delta)}{P(-\alpha_1-\delta)}\Big\vert
+\end{align*}
+
+We are left with the bounds on the kernel: following the notation of \textcolor{orange}{\texttt{reg-sing-volterra}}, we set
+
+\begin{equation}
+    K_{\text{soft}}(\zeta_1,s)=\sum_{r=0}^{d-1}\sum_{j=0}^{\infty}R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r
+\end{equation}
+where, since $R_r$ are holomorphic functions in some disk of radius $A$ centered at $\infty$, we define $R_r(z)=\sum_{j=0}^\infty R_{r,j}z^{-j}$ and $|R_{r,j}|\leq A^{-j}$. In particular,
+
+\begin{align*}
+    \Big\vert \sum_{j=0}^\infty \frac{R_{r,j}}{j!}(\zeta_1-s)^{j+1}\Big\vert \leq |\zeta_1-s| e^{\frac{|\zeta_1-s|}{A}}
+\end{align*}
+
+If $|\zeta_1|\geq\delta$ and $s\in\Omega_1$
+
+\begin{align*}
+    \Big\vert-\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}-\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq  \Big\vert\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}\Big\vert+\Big\vert\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert\\
+    &\leq C+ |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}\sum_{j=0}^{\infty} \Big\vert R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r\Big\vert\\
+    &\leq C + |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}|\zeta_1-s|e^{|\zeta_1-s|/A} |s-\alpha_1|^r
+\end{align*}
+
+In particular, for every $\zeta_1,s\in\Omega_1$
+
+\begin{align*}
+    \Big\vert \zeta_1 \frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq |\zeta_1-s| e^{|\zeta_1-s|/A} \sum_{r=0}^{d-1}\frac{|s-\alpha_1|^r}{|(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)|}\\
+\end{align*}
+
+\textcolor{magenta}{[to conclude, we need assumption on how $s$ and $\zeta_1$ respectively move in $\Omega_1$. ]}
 
@@
 
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ \footnote{Since $\sup\Lambda\leq -2$ we can assume $\varepsilon=1$ in Theorem 2.1.3 of {\tt regular Volterra}}.
+Therefore, there exists a unique solution
+
+\begin{equation}\label{eqn:slight_solution}
+    \psi_1(\zeta_1)=\zeta_1^{\tau_1-1}+f_1(\zeta_1)
+\end{equation}
+ and $f_1\in\mathcal{HL}^{\infty}_{\tau_1,1/A}(\Omega_1)$.
+
+\end{proof}
+
+\begin{corollary}\label{cor:existence_Laplace}
+    Under the assumption of Theorem \ref{thm1-dim}, the function $\hat{\psi}_j$ defined in Equation \eqref{eqn:slight_solution} admits a Laplace transform. 
+\end{corollary}
+
+\begin{proof}
 
@@
  Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined in \eqref{P-hat_j}.
-If $\hat{\psi}_j$ admits a Laplace transform $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.
+Let $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ be the Laplace transform of $\hat{\psi}_j$, for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.
 \end{lemma}
@@
 \begin{itemize}
-\item[$(a)$] prove that $\hat{\psi}_j(\zeta_j)$ admits Laplace transform (see Lemma \ref{step a}) 
-\item[$(b)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
-\item[$(c)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-
-Step $(c)$ clearly follows from steps $(a)$ and $(b)$.
-In fact, from step $(b)$ and Theorem 3.1 $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
-Then, by step $(a)$ we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.
-
-We now prove step $(b)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$.
+\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
+\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
+\end{itemize}
+
+Step $(b)$ clearly follows from Corollary \ref{cor:existence_Laplace} and step $(a)$.
+In fact, from step $(a)$ and Theorem \ref{thm1-dim}, $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+Then, by Corollary \ref{cor:existence_Laplace} we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.
+
+We now prove step $(a)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$.
 Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.
@@
 
-\color{Turquoise}
-\begin{lemma}\label{step a}
-    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
-\end{lemma}
-
-\begin{proof}
-    We will prove the following: 
-    \begin{itemize}
-        \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
-        \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
-    \end{itemize}
-    The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
+%\color{Turquoise}
+%\begin{lemma}\label{step a}
+%    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
+%\end{lemma}
+
+%\begin{proof}
+ %   We will prove the following: 
+  %  \begin{itemize}
+   %     \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
+    %    \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
+    %\end{itemize}
+    %The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
 In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
 Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
-    \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
-    \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero
-
-    \begin{align*}
-        &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
-        &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
-        &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
-    \end{align*}
-    If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
-    \begin{align*}
-        f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
-        &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
-    \end{align*}
-    Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
-
-    \begin{align*}
-        \left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)\right]f_{j,n}=-\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r f_{j,n-1}
-    \end{align*}
-    and since $R_r$ is entire, the right-hand side is an infinite sum of the convolution product of an entire function with $f_{j,n-1}$, hence it  has the same singularities as $f_{j,n-1}$ (see Lemma 6.15 \cite{diverg-resurg-i}).
+   % \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
+   % \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero
+
+    %\begin{align*}
+     %   &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
+      %  &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
+       % &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
+    %\end{align*}
+    %If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
+    %\begin{align*}
+     %   f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
+      %  &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
+    %\end{align*}
+    %Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
+
+    %\begin{align*}
+     %   \left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)\right]f_{j,n}=-\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r f_{j,n-1}
+    %\end{align*}
+    %and since $R_r$ is entire, the right-hand side is an infinite sum of the convolution product of an entire function with $f_{j,n-1}$, hence it  has the same singularities as $f_{j,n-1}$ (see Lemma 6.15 \cite{diverg-resurg-i}).
 Therefore, we deduce $f_{j,1}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$ and inductively, $f_{j,n}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$.
 
-    Let $\theta$ be the direction that avoids all the singularities, we now prove that the analytic continuation of $\hat{\psi}_j$ grows sub-exponentially.
+    %Let $\theta$ be the direction that avoids all the singularities, we now prove that the analytic continuation of $\hat{\psi}_j$ grows sub-exponentially.
 In fact, it is enough to adapt the Gr\"onwall lemma to integral equations (see Lemma 3.9 \cite{diverg-resurg-iii}]).
-   Let $\Omega$ be the open domain where $\hat{\psi}_j$ is analytic and let $p$ be a point in $\Omega$ such that $\Omega':=\Omega\setminus B_{r}(\alpha_j)$ is star-shaped from $p$ ($B_r(\alpha_j)$ is the ball of radius $r$ and center in $\alpha_j$).
+   %Let $\Omega$ be the open domain where $\hat{\psi}_j$ is analytic and let $p$ be a point in $\Omega$ such that $\Omega':=\Omega\setminus B_{r}(\alpha_j)$ is star-shaped from $p$ ($B_r(\alpha_j)$ is the ball of radius $r$ and center in $\alpha_j$).
 By assumption on the coefficients of the ODE \eqref{eqn:standard ODE}
-   \begin{align*}
-       a:=\sup_{\zeta\in\Omega'}\frac{|Q|(|\zeta|)}{|P(-\zeta)|}<\infty\, \qquad b:=\sup_{\zeta\in\Omega'}\frac{1}{|P(-\zeta)|}<\infty
-   \end{align*}
-   hence, for every $\zeta\in\Omega'$, writing $\xi=|\zeta|$ and $\zeta=p+\xi e^{i\eta}$
-   \begin{align*}
-       |\hat{\psi}_j(\zeta)|&\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-       &\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-       &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-       &\qquad +c\left[\int_{|\alpha_j|}^{|p|}|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|} \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-       &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-       &\qquad + a'\int_{|\alpha_j|}^{|p|}|\hat{\psi}_j(\rho e^{i\theta})|d\rho+ c\sum_{r=0}^{d-1}\int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot  \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho%\\
-       %&\leq a \int_{|\alpha_j|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho \\
-       %&=a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|p|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho+\\
-       %&\qquad + a \int_{|\alpha_j|}^{|p|}  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho
-   \end{align*}
-   where $\hat{R}_r=\borel(z^{-2}R_r)$, for every $r=0,...,d-1$. 
-   %For every $r=0,...,d-1$, we define $F_r(z)=R_r(z)$
-   We want to show that for every $m\geq 0$, $|\hat{\psi}_j(\zeta)|<\hat{W}_m(\xi)$ for $\zeta$ on the ray $\zeta=p+\xi e^{i\theta}\in\Omega'$, where $\hat{W}_m$ is the unique solution of
-
-   \begin{equation}
-       \hat{W}=m+a\ast_{|p|}\hat{W}+c\sum_{r=0}^{d-1}\hat{R}_r\ast_{|p|} (-\zeta^r\hat{W})
-   \end{equation}
-
-   \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them.
+   %\begin{align*}
+    %   a:=\sup_{\zeta\in\Omega'}\frac{|Q|(|\zeta|)}{|P(-\zeta)|}<\infty\, \qquad b:=\sup_{\zeta\in\Omega'}\frac{1}{|P(-\zeta)|}<\infty
+   %\end{align*}
+   %hence, for every $\zeta\in\Omega'$, writing $\xi=|\zeta|$ and $\zeta=p+\xi e^{i\eta}$
+   %\begin{align*}
+    %|\hat{\psi}_j(\zeta)|&\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+     %  &\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
+      % &\qquad +c\left[\int_{|\alpha_j|}^{|p|}|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|} \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
+      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
+      % &\qquad + a'\int_{|\alpha_j|}^{|p|}|\hat{\psi}_j(\rho e^{i\theta})|d\rho+ c\sum_{r=0}^{d-1}\int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot  \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho%\\
+      % %&\leq a \int_{|\alpha_j|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho \\
+      % %&=a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|p|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho+\\
+      % %&\qquad + a \int_{|\alpha_j|}^{|p|}  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho
+   %\end{align*}
+   %where $\hat{R}_r=\borel(z^{-2}R_r)$, for every $r=0,...,d-1$. 
+   %%For every $r=0,...,d-1$, we define $F_r(z)=R_r(z)$
+   %We want to show that for every $m\geq 0$, $|\hat{\psi}_j(\zeta)|<\hat{W}_m(\xi)$ for $\zeta$ on the ray $\zeta=p+\xi e^{i\theta}\in\Omega'$, where $\hat{W}_m$ is the unique solution of
+
+   %\begin{equation}
+    %   \hat{W}=m+a\ast_{|p|}\hat{W}+c\sum_{r=0}^{d-1}\hat{R}_r\ast_{|p|} (-\zeta^r\hat{W})
+ %  \end{equation}
+
+ %  \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them.
 This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
-   There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$.
+  % There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$.
 Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$?
 }
-\end{proof}
-
-\color{black}
+%\end{proof}
+
 \subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
@@
 \begin{proof}
+
 Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
+
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $\alpha_j$ with $\tfrac{1}{2} \tau^2 = f - f(\alpha_j)$.
+Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
+\textbf{[We should explicitly spell out and check the conditions that make this possible.
+I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
+that converges in some disk $|\tau| < \varepsilon$.
+
+By the steepest descent method,
+%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{\textcolor{magenta}{+}z f(\alpha_j)} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $\Re z \to \infty$ \textbf{[see, for example, Miller's ``Applied Asymptotic Analysis,'' Proposition 2.1---the argument through equation~(2.9).]} Plugging in the Taylor series above, we get
+\begin{align*}
+e^{-z f(\alpha_j)} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
+\end{align*}
+By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
+= 1$.}
+\begin{align*}
+e^{-z f(\alpha_j)} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z f(\alpha_j)} I_\alpha(z)$.
+In other words,
+\[ e^{-z f(\alpha_j)} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+To see why, cut the sum off after $N$ terms, and observe that
+\begin{align*}
+  \Bigg | \sum_{n= 0}^N(2n-1)!!
+b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
+b_{2n}^j n|z|^{-n}.
+\end{align*}
+The right-hand side goes to $0$ as $\Re(z)$ grows.
+
+%Hence,
+%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \textbf{[Chiani, Dardari, and Simon, ``New Exponential Bounds and Approximations
+for the Computation of Error Probability in
+Fading Channels,'' inequality~(5)]}, allowing the simpler estimate
+\[ e^{-zf(\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
+
+Call the right-hand side $\tilde{I}_j$. We now see that $a_{j,n} = (2n-1)!!\,b_{2n}^j$ in the statement of the theorem. %\textbf{[Resolve discrepancy with previous calculation.]}
+
+Note that 
+\begin{align*}
+\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
+& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
+\end{align*}
+
+We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
+Recalling that $(2n - 1)!!
+\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is Gevrey-1.
+
+\textcolor{red}{[From here the old proof begins]}
 
@@
 %Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
+
+\textcolor{red}{From here the proof continues}
 
@@
 \begin{quote}
-We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
 Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
@@
 The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns \textcolor{orange}{convergent formal solutions [Veronica: what do you mean by convergent formal?
-It looks like a contradiction]} of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
+Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation~\textcolor{magenta}{[prove or cite]}.
 Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
 
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
+When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}.
 It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
@@
 \begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals, since Andy is interested in that sort of thing
+\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
 \end{itemize}
@@
 \appendix
-
-\section{Integro-differential equations}
-\subsection{Existence of solutions}
-\subsubsection{Algebraic integral operators}
-Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
-We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
-\begin{align*}
-\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
-\phi & \mapsto \zeta^{-\sigma} \phi
-\end{align*}
-is an isometry. More generally,
-\begin{align*}
-\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
-f & \mapsto \zeta^{-\delta} f
-\end{align*}
-is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$.
-This reduces to the previous statement when $\rho = 0$.
-For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
-Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
-
-Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega):= \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
-For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
-
-We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
-\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
-where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
-The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
-Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
-That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
-
-For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure.
-The square of a density is a Riemannian metric.
-Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
-The bound
-\begin{align*}
-\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |\zeta^\rho f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
-& \le \|f\|_{\infty, \rho} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
-\end{align*}
-holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_{\infty, \rho}. \]
-so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
-\subsubsection{The example of fractional integrals}
-Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
-The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
-It follows that
-\begin{align*}
-\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
-& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
-& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = B(-\lambda,\,1-\rho).
-\end{align*}
-The beta function $B$ can be written more explicitly as
-\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
-Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
-\subsubsection{Fractional integral equations near a regular singular point}\label{frac_int_exist}
-\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
-
-Consider an integral operator $\mathcal{J}$ of the form
-\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
-where:
-\begin{itemize}
-\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
-\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
-\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
-\item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
-\end{itemize}
-Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough.
-We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.
-
-We want to solve the equation $\mathcal{J}f = 0$.
-Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-When $\epsilon$ is small enough that $\Lambda \subset (-\infty, -1 - \epsilon]$, we'll see that we can always find such a solution, as long as we're willing to shrink $\Omega$.
-In fact, there's exactly one such solution.
-\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}
-
-Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
-We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.
-
-Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
-\begin{alignat*}{2}
-p & = p'_0 \zeta &\;+\;& \tilde{p} \\
-q & = q_0 &\;+\;& \tilde{q}
-\end{alignat*}
-with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
-\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
-with
-\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
-For any $\tau \in (0, \infty)$,
-\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Setting $\tau = -q_0 / p'_0$ makes the first term vanish, leaving
-\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Then the equation $\mathcal{J}f = 0$ becomes
-\begin{align}
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \nonumber \\
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
--p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
-\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f}.
-\label{fixed-pt}
-\end{align}
-
-\color{Indigo}
-\begin{center}
-\begin{tikzcd}[column sep=25mm, row sep=2mm]
-& & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^{1-\epsilon}"'] \\
-& & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
-& & & \holoL{\infty, \rho}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-1-\epsilon-\lambda}"'] \\
-& & & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 1-\rho) = \frac{1}{1-\rho}}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\zeta^{-1}", "\|\zeta^{-1}\|_{\infty, 1} = 1"'] & \holoL{\infty, \rho}(\Omega) \\
-\end{tikzcd}
-\end{center}
-\color{black}
-
-From \textbf{[our previous discussion]}, we can work out that
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
-\end{align*}
-and
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau-\epsilon}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\end{align*}
-Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
-\begin{align*}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
-\end{align*}
-and
-\begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\%\nonumber \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\label{bound:perturb}
-\end{align}
-We can also see that
-\begin{align}
-\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with}   \nonumber \\
-\|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
-\end{align}
-
-Now, let's return to equation~\eqref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
-\begin{align*}
-\mathcal{A} & = \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}}  \\
-b & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1}
-\end{align*}
-Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
-We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
-
-An affine map is a contraction if and only if its linear part is a contraction.
-We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$.
-Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
-Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
-%\input{chapters/appendix}
 

### 2023-07-25 old-reg-volterra.tex

--- 2023-05-09 exp-resurgence.tex
@@
 
-\title{Borel regularity for ODEs and thimble integrals}
+\title{Old regular Volterra equations}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 \maketitle
-
-\section{Introduction}
-\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
-%%\subsection{A familiar process: Borel summation}\label{intro:summation}
-You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
-\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
-with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
-\begin{equation}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
-\end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
-\begin{equation}
-e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
-\end{equation}
-and its constant multiples. As another example, you might rewrite the integral
-\color{DodgerBlue}
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
-\color{black}
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
-as
-% see expansion.sage
-\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
-using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{DodgerBlue}
-\begin{align*}
-& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
-& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
-& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
-\end{align*}
-\color{black}
-
-Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-Borel summation works in three steps.
-\begin{enumerate}
-\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}.
-We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
-Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-\end{enumerate}
-The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
-Hopefully it wouldn't be too hard, but it would be a pain.]}
-\begin{defn}
-On an open sector $\Omega$ around $\infty$, a power series
-\begin{equation}\label{series:asymp-defn}
-\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
-\end{equation}
-is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$.
-
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
-\end{defn}
-\begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
-over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
-\end{defn}
-To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
-
-\begin{enumerate}[start=4]
-\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
-It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
-\end{enumerate}
-
-The Borel summation process is summarized in the following diagram:
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-
-You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
-After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
-In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
-The question of how that happens is the starting point for this paper.
-
-%\color{gray}
-%\begin{itemize}
-%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example\ldots}
-%\begin{itemize}
-%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
-%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
-%\item Feynman diagram series?
-%\end{itemize}
-%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-%\begin{itemize}
-%\item \done{Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
-%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
-%\item {[Draw the square!]}
-%\end{itemize}
-%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-%\item In many cases, it picks correctly, producing an actual solution to your problem.
-%\begin{itemize}
-%\item The question of how that happens is the starting point for this paper.
-%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-\subsection{A new perspective: Borel regularity}
-\subsubsection{Introducing Borel regularity}
-\begin{itemize}
-\item Start instead with a holomorphic solution $\Phi$.
-\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
-\end{itemize}
-\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
-
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
-Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
-We'll therefore call this process {\em Borel regularization}.
-Explicitly, Borel regularization works in four steps.
-\begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
-\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
-This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.
-\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.
-\textbf{[Should we be allowed to take the Laplace transform at another points $b \in B$ instead?]}
-\end{enumerate}
-We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
-
-Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
-We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
-\subsubsection{Borel regularity as a good approximation condition}
-Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
-
-Watson's theorem was soon improved by Nevanlinna (see a modern proof in Nikolaev, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15), and improved again later by Sokal (Sokal, ``An improvement of Watson's theorem on Borel summability'').
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
-\begin{center}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\dis}{1.2}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
-  \begin{scope}[violet]
-    \draw (0, 0) -- (-\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
-\end{tikzpicture}
-\end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
-
-%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
-Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
-Hence $\Phi$ is Borel-regularizable.
-In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$.
-In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
-The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
-Roughly speaking, Borel summation works well for problems with Borel regular solutions that stand out asymptotically \textcolor{magenta}{[this may need refining]}.
-
-The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
-\begin{enumerate}
-\item Solving a linear ODE of level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Definition~5.5]{diverg-resurg-iii}}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type.
-
-We'll restrict our attention to the case where the roots of $P$ are distinct.
-
-The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
-Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.
-
-\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
-
-\begin{equation}
-I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
-\end{equation}
-where $f\colon X\to \mathbb{C}$ is a Morse function, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
-\end{enumerate}
-
-These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-
-%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
-Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We will give precise statements in the following section.
-
-%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We'll call it {\em Borel regularization}.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We'll call this process {\em Borel regularization}.
-%\begin{itemize}
-%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-%\item We have the following vector space inclusions:
-%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
-%
-%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-%\begin{itemize}
-%\item $\Phi$ is Borel regular.
-%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-%\item $\phi$ grows at most exponentially along the Laplace transform ray.
-%\end{itemize}
-%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
-\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
-it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
-%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-%\item \ldots
-%\end{itemize}
-
-\subsection{Goals and Results}
-
-First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-
-\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
-\begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
-Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
-It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.
-
-\color{DarkTurquoise}
-In \cite[Proposition~2.2.7]{EcalleIII}, where
-\begin{align*}
-P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
-Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
-\end{align*}
-(with the coefficients renamed to avoid a conflict with the zeros $\alpha_j$), the recurrence that gives the solution simplifies
-\begin{align*} b_q & = P_q + Q_q z^{-1} - \frac{\partial}{\partial x^{(q)}} b(z, x, x^{(1)}, \ldots x^{(d)}) \\
-& = P_q + Q_q z^{-1} - R_q(z^{-1}).
-\end{align*}
-
-Following the argument of Delabaere Lemma~6.2, we can prove that $\series{F}_j(z)$ is $1$-Gevrey by taking the formal Borel transform of the ODE it satisfies and showing it is regular singular at $\zeta=0$.
-
-Roughly speaking, factoring out $e^{-\alpha_j z}$ removes the constant term of $P$, and factoring out $z^{-\tau_j}$ changes $Q$ to give factorial growth instead of gamma function growth (?).
-
-\begin{align*}
-\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
-& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
-&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
-\end{align*}
-where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
-\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
-corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).
-
-From the Bessel equation, for example, we get
-\begin{align*}
-(-w^{-2}\partial_w)^2&=-w^{-2}\partial_w(-w^{-2}\partial_w)\\
-&=-w^{-2}(2w^{-3}\partial_w-w^{-2}\partial_w^2)\\
-&=-2w^{-5}\partial_w+w^{-4}\partial_w^2,
-\end{align*}
-giving two half-planes around $\infty$, as expected.
-\color{black}
-
-Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
-\end{equation}
-where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $\alpha_1, \ldots, \alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
-Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
-14).
-Conversely, we can explicitly build a distinguished basis of analytic solutions:
-
-\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
-In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with
-
-\begin{equation}
-\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
-\end{theorem}
-
-At this point, we may ask what is the relationship between the two frame of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually the same, hence proving Borel summation works.
-
-\begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
-\end{theorem}
-
-In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
-
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
-
-The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too.
-In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result~\ref{thm1}, we conclude that $\psi_j$ and $\hat{\psi}_j$ must coincide up to scaling by a constant.
-
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.
-
-\begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}.
-It can indeed be seen as a consequence of ``resurgence'' of the ODE.
-Our results show how to build a frame of solutions, analytically in the Borel plane.
-Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
-\end{remark}
-
-\begin{remark}
-Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
-\textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
-For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$?
-Check carefully the argument of multi-summability]}
-\end{remark}
-
-\color{gray}
-\begin{itemize}
-\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-\end{itemize}
-\begin{itemize}
-\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-
-\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-\item  
-there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-\end{itemize}
-
-\color{DarkBlue}
-
-\subsubsection{Why does Borel resummation work for thimbles integrals?}
-
-\begin{itemize}
-\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-\begin{itemize}
-\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-\end{itemize} 
-\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
-His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
-\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
-\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-\begin{equation}
-I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-\end{equation}
-
-then the following diagram is commutative
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-\end{tikzcd}
-\end{equation}
-\begin{itemize}
-\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the fractional derivative formula.
-\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
-\begin{equation}
-mmm
-\end{equation} 
-\end{itemize}
-\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-\begin{itemize}
-\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
-\end{itemize}
-\end{itemize}
-
-\color{DarkGreen}
-We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
-Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
-A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-Suppose every singularity of $B$ is a critical value of $f$.
-\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
-\textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
-\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
-
-\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
-
-In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
-This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],[Delabere \& Howls, Howls, Dingle]}.
-
-\color{DarkTurquoise}
-Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
-Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
-This data defines the {\em exponential integral}
-\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-a holomorphic function on the right half-plane parametrized by $z$.
-It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
-\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
-
-\color{black}
-
-\subsubsection{Other results}
-
-As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
-
-Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
-
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
-Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
-Borel regularity will be evident from the explicit computations.
-Some examples have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
-The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
-Other example haven't been discussed much, as for Airy--Lucas functions.
-
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-
-%\color{gray}
-%\begin{itemize}
-%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-%\begin{itemize}
-%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-%\item The second problem is solving a certain kind of ODE.
-%\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-%\end{itemize}
-%
-%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-%\begin{itemize}
-%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-%\end{itemize}
-%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-%\begin{itemize}
-%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-%\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-%\end{itemize}
-%\end{itemize}
-%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
-%\begin{itemize}
-%\item Integral equations are more regular than differential equations.
-%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-%\end{itemize}
-%\item Illustrate with detailed treatments of several examples.
-%\begin{itemize}
-%\item Contour argument (thimble integrals)
-%\item solving integral equation (ODE)
-%\item How thimble integrals and ODE are related in our examples?
-%\end{itemize}
-%\begin{itemize}
-%\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-%\item Others haven't been discussed much.
-%\end{itemize}
-%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-%\begin{itemize}
-%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-%\item computation of Stokes constants via Picard--Lefschetz theory
-%\end{itemize}
-%\end{itemize}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean to be Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
-\end{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
-
-\color{black}
-%\end{itemize}
-\begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
-\item The resummation method works correctly for functions that satisfy that assumption.
-\item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
-\begin{itemize}
-\item Different aspects of this example appear in various places (Mari\~{n}o, Kawai--Takei, Sauzin). We give a detailed, unified treatment.
-\end{itemize}
-\item We can generalize this argument to all $K_\nu$ with $\nu \in \mathbb{Q}$.
-\item We can also generalize to all third-order exponential integrals.
-\begin{itemize}
-\item Most of them are equivalent to the $K_{1/3}$ integral, but there's also an interesting degeneration.
-\end{itemize}
-\end{itemize}
-\color{black}
-\subsection{Fractional derivative formula}
-\begin{itemize}
-\item Theorem~\ref{thm:three-halves} says that for a certain class of exponential integrals
-\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
-the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
-\item the asymptotic expansion of $I(z)$ is a resurgent function.
-\item Is it always a \emph{simple} resurgent function?
-\begin{itemize}
-\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
-\end{itemize} 
-\end{itemize}
-\subsection{Stokes phenomenon}
-\begin{itemize}
-\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-\item The jump comes from the branch cut difference identity for hypergeometric functions.
-\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-\end{itemize}
-\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
-\subsection{The geometry of the Laplace transform}
-
-Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
-In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
-Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
-\subsubsection{Translation surfaces, briefly}
-
-A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
-A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
-The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
-\subsubsection{Direction}\label{transl:dir}
-The translation structure gives $B$ a notion of direction as well as distance.
-Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
-At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
-To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
-In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
-
-Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
-This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
-Of course, there are $n$ different choices for $\omega_b$.
-\subsubsection{Frequency}\label{transl-freq}
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
-At an ordinary point, we can define $z$ simply as the map
-\begin{align*}
-z \maps T^*B_b & \to \C \\
-\lambda\big|_b & \mapsto 1.
-\end{align*}
-To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
-Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
-Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
-When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
-In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
-We define $z$ as the isomorphism
-\begin{align*}
-z \maps \van_b^n / \van_b^{n+1} & \to \C \\
-\zeta_b + \van^{n+1} & \mapsto 1.
-\end{align*}
-
-When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
-\begin{align*}
-w_b \maps T^*B_b & \to \C \\
-\omega_b + \van^2 & \mapsto 1
-\end{align*}
-that makes the diagram
-\begin{center}
-\begin{tikzcd}
-T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
-T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
-\end{tikzcd}
-\end{center}
-commute.
-\subsubsection{Boundary}
-\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}
-
-\subsubsection{The Laplace transform over an ordinary point}%%\label{laplace:ordinary}
-Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
-\begin{equation}\label{laplace:int}
-\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function defined in Section~\ref{transl:freq} and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-
-To make sense of this formula, we ask for the following conditions.
-\begin{itemize}
-\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
-\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
-\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-\begin{itemize}
-\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
-\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
-\end{itemize}
-\end{itemize}
-\subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
-The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
-This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
-The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
-We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-\subsection{The geometry of the Borel transform}
-\begin{itemize}
-  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  \begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-\end{itemize}
-\subsection{The Laplace transform: analytic version}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
-The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
-%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
-where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
-\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
-
-Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
-
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
-Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
-\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
-Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
-\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-\subsubsection{Action on integral operators}\label{L-int-op}
-When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm} 
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-for all $\lambda \in (0, \infty)$.
-\subsubsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    \label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-\subsubsection{Rescaling of translation structure}
-Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-\subsection{The geometry of the Borel transform}
-
-The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-More precisely, $\borel_\zeta$ is a $\C$-linear map
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-\end{align*}
-where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
-In general, by linearity,
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-\end{align*}
-
-It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
-\begin{align*}
-    \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-    &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
-\end{align*}
-where in the second step we formally interchange the integral and the sum.
-
-\subsubsection{Action on transseries}
-
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$:
-
-\[T_{\alpha,\varphi}:=\sum_{n=0}^{\infty} e^{\alpha_n z} \varphi_n(z) \]
-
-The main feature of $T_{\alpha,\varphi}$ is that its asymptotics as $\text{ Re } e^{i\theta}z \to +\infty$ is $\varphi_0$.
-In fact, they play a crucial role in the theory of ODEs with irregular singularities.
-
-It is natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries.
-Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-
-We extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-
-Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, then from identity \eqref{change-chart}
-
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha,0}\varphi\right]
-  \end{align*}
-We compute the left-hand-side
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi&=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
-  \end{align*}
-  and the right-hand-side
-  \begin{align*}
-      \borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
-      }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-      &= \sum_{n=0}^{\infty}a_n \zeta^n
-  \end{align*}
-In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-
-\[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
-
-Then, comparing term by term in powers of $\zeta$ in the second identity we get 
-  \begin{align*}
-      \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})&=\zeta^n\\
-      \sum_{k=0}^n {n\choose k} \alpha^{n-k} \borel_\zeta(e^{-z\alpha} k! z^{-k-1})&=\sum_{k=0}^n {n\choose k} \alpha^{n-k}(\zeta-\alpha)^k
-  \end{align*}
-  and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
-\begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-
-\subsubsection{Change of translation chart}
-
-Following Section \ref{translation}, we introduce $\borel_{\zeta_\alpha}$
-as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. Explicitly, from identity \eqref{change-chart}
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi
-  \end{align*}
-  now the LHS reads
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\left[e^{z\alpha} \int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_n\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_ne^{-z\alpha}\sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}  z^{-k-1}\right]
-  \end{align*}
-  the RHS is 
-  \begin{align*}
-      \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
-      &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
-      \end{align*}
-     If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
-      \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
-       \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
- Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
- \begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
- Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
-
- \textcolor{magenta}{I think we should add a remark, saying that on $B$ there is no special coordinate, and this reflects on the fact that $\borel$ is defined equivalently for every choice of coordinates.}
-
-\subsection{The Borel transform}
-%\color{gray}
-%\begin{itemize}
-%\item Action on differential equations.
-%\begin{itemize}
-%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-
-%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
-These formal series are the so-called Gevrey-$1$ series:
-\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
-there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series.
-}
-
-\begin{notation*}
-We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane).
-Therefore we adopt the following notation:
-\begin{itemize}
-\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
-\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
-\item $\phi$: lower-case letters are holomorphic functions on the frequency domain.
-Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
-\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we will see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
-\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
-\end{itemize}
-\end{notation*}
-
-\begin{lemma}
-Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
-\end{lemma}
-In particular, we deduce from the lemma that the Borel transform is an isomorphism between Gevrey-$1$ series and $\C\delta\oplus\C\lbrace\zeta\rbrace$.
-
-The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
-
-\textcolor{magenta}{[add definition of convolution product and $\borel$ being an algebra isomorphisms]}
-
-\subsubsection{Action on power series with fractional exponents}
-The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
-\end{align*}
-and then extending by linearity.
-
-If $\alpha\in\mathbb{R}\setminus\Z$, then $\borel$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
-Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-\alpha} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
-\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
-
-\subsubsection{Properties of the Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
-\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
-\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
-\end{itemize}
-
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
-\begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see 5.12.1 in \cite{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-
-\begin{proof}
-
-We are going to prove properties (i)--(vi).
-
-(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see Lemma 5.10 \cite{MS16}.
-
-(vi) see Definition 5.12 and Lemma 5.14 \cite{MS16}. 
-\end{proof}
-
-\begin{remark}
-We notice that properties (i) and (ii) are special cases of property (vi), indeed we can use the convolution product 
-\begin{align*}
-\borel_\zeta (z^\alpha \tilde{\Phi})&=\borel_\zeta (z^\alpha)\ast \tilde{\phi}\\
-&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\int_0^1(t\zeta)^{-\alpha-1}(\zeta-t\zeta)^k\zeta dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\int_0^1 t^{-\alpha-1}(1-t)^k dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\frac{\Gamma(k+1)\Gamma(-\alpha)}{\Gamma(k-\alpha+1)}\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
-&=\partial_\zeta^\alpha\tilde{\phi}
-\end{align*}
-\end{remark}
-
-\subsection{Differential equation}
-\textcolor{orange}{Should we keep this section?}
-If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-\begin{equation}%%\label{laplace:op}
-\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-\end{equation}
-The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-\subsubsection{Order shifting}\label{shifting}
-\textcolor{orange}{[why the name order shifting?]}
-Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
-A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
-\begin{equation}\label{eqn:slight-defn}
-\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-\end{equation}
-where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-
-Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
-When $\psi$ is slight and locally integrable at $\zeta = 0$,
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are regular functions.
-\end{prop}
-To prove this result, we'll need a little background.
-
-Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-is slight.
-Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
-Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
-
-\section{Proof of main results}
-\subsection{Borel regularity for ODEs}
-
-\begin{theorem}\label{thm1-dim}
-Let $\mathcal{P}$ be a linear differential operator 
-\begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_d$ are entire functions of exponential type
-\end{itemize}
-
-Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-
-\color{brown}
-\begin{equation}
-\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-\color{black}
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
-\end{theorem}
-\begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
-In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$.
-$Q$ is also a polynomial defined at $\zeta_j=0$.
-Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
-
-\begin{align*}
-&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
-\end{align*}
-
-%In particular, $\Lambda=(-\infty,-2]$.
-
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
-
-\end{proof}
-
-\begin{theorem}\label{thm2-dim}
-For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$ for every $j=1,...,d$.
-Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
-\end{theorem}
-\begin{proof}
-We divide the proof in the following steps:
-\begin{itemize}
-\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\borel\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
-\item[$(c)$] prove that $\laplace_{\zeta_j}^{\theta_j}\circ\borel\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-
-Step $(c)$ clearly follows from steps $(a)$ and $(b)$.
-We now prove step $(b)$: first notice that if $\series{\Psi}_j$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
-
-\begin{equation}
-\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
-\end{equation}
-
-\color{brown}
-Then taking the (formal) Borel transform:for every $j=1,...,d$ we denote $\zeta_j=\zeta-\alpha_j$ and we consider the Borel transform of $\mathcal{P}\series{\Psi}_j$ in the coordinate $\zeta_j$
-
-\begin{multline*}
-\borel\left(\mathcal{P}\series{\Psi}_j\right)=\borel\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
-\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
-\left[P(-\zeta)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
-\end{multline*}
-%where 
-%
-%\begin{align*}
-%\series{\psi}_j(\zeta_j):=\borel\series{\Psi}_j(\zeta_j)&=\borel\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\borel\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
-%&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
-%\end{align*}
-
-Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0.
-from the properties of the Borel transform we deduce that $\hat{P}\series{\psi}_j=0$ first notice that $\series{\psi}_j$ is a solution of
-\color{black}
-\end{proof}
-
-\subsection{Borel regularity for thimble integrals}
-
-Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
-\begin{equation}\label{exp-int}
-I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
-\end{equation}
-where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
-For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
-\begin{equation}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
-\end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-\begin{theorem}\label{thm:maxim} Let $N=1$.
-Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then:
-\begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\borel(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
-\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
-\begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
-\end{multline}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
-Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
-\end{enumerate}
-\end{theorem}
-\begin{proof}
-Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
-
-Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
-\textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-These terms are crucial, however, for the convergence of the sum.
-To see why, consider their absolute sum $C_\text{exp}$.
-When $z \in [0, \infty)$,
-\begin{align*}
-C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
-
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
-We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
-See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
-\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
-
-\color{Purple}
-For each cutoff $N$, the tail error \textbf{[check]}
-\begin{align*}
-\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
-& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
-& = \textbf{uh-oh!}
-\end{align*}
-\color{violet}
-is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
-\begin{align*}
-C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
-Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-Part~\eqref{int:resum-converges}: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
-\end{align*}
-Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
-
-Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
-As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
-Hence, we have
-\begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
-\end{align*}
-Noticing that the right-hand side is a Laplace transform, we learn that
-\begin{equation}\label{thimble-difference}
-\hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
-\end{equation}
-\color{Aquamarine}
-In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{I}_\alpha$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
-[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
-Or something even simpler?]
-\color{black}
-
-We can rewrite our Taylor series for $\nu$ as
-\begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
-\begin{align*}
-\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \borel_{\zeta_\alpha} \tilde{I}_\alpha.
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
-
-Theorem~\ref{thm:frac-diff-borel} tells us that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \borel \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{align*}
-It follows, from our conclusion above, that
-\begin{equation}\label{shifted-resum-valid}
-\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{equation}
-Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
-\begin{align*}
-I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
-& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
-\end{align*}
-as we claimed.
-
-Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
-Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
-we can see that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
-The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
-\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
-Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
-\end{proof}
-
-\section{Examples}
-
-\subsection{Airy}
-
-The Airy equation is
-\begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
-\end{equation}
-One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
-\begin{center}
-\includegraphics{figures/u_contour_3.pdf} \\[1em]
-{\small The contour $\Gamma$ in the $u$ plane.}
-\end{center}
-With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
-
-By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we will go straight to the general case.
-However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
-For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
-
-\subsection{Airy--Lucas}
-The Airy-Lucas equation is
-\begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-
-\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
-We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel-rational-AL}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation
-\begin{equation}\label{eqn:mod-bessel-AL}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{{m/n}}$.
-
-Let's put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
-\begin{equation}\label{eqn:reg-mod-bessel-AL}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsubsection{Asymptotic analysis}
-
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp-AL}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
-%\subsection{Going to the spatial domain}\label{spatial-AL}
-\subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\ref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel-AL} looks like
-\begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos-AL}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
-\color{DarkTurquoise}
-\begin{quote}
-We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
-\begin{align*}
-v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
-& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
-\end{align*}
-In this case, $\tau = \tfrac{1}{2}$.
-\end{quote}
-\color{black}
-
-The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
-We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-
-The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
-
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
-It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-\subsubsection{Confirmation of Borel regularity}
-We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
-We found in Section~\textbf{[asymptotic analysis]} that
-\begin{align*}
-\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
-Computing
-\begin{align*}
-\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
-we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
-Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-
-Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
-Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
-\subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
-We can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
-& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
-\end{center}
-
-The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-\begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-\end{align*}
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
-Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-\color{DarkCyan}
-Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-where $\zeta = -1 + \zeta_{-1}$.
-\color{black}
-
-\subsection{Modified Bessel}
-
-The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
-
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
-\end{equation}
-
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf})
-
-\begin{align*}
-I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]
-\end{align*}
-
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-
-\begin{figure}[h]
-\caption{Add figure path $\Omega$}
-\end{figure}
-
-On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results:
-
-\begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
- \begin{align*}
- \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
-\end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-
-\begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{1}\big)\\
-v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
-\item \textbf{Borel regularity} \textcolor{Lime}{[Check with Aaron how to phrase it]} 
-\end{itemize}
-
-On the other hand, the contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
-
-\subsubsection{Lifting to a countable cover}\label{countable-cover}
-Formula~\eqref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
-Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
-
-Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
-we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
-\begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
-\end{align}
-For any $\mu \in \C \smallsetminus \Z$, 
-\begin{align}
-\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-
-When $\mu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
-
-\subsection{Higher Airy}
-
-The higher Airy equation is
-\begin{equation}\label{eqn:higher-airy}
-\left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
-
-\color{Peru}
-With
-\begin{align*}
-z & = (-1)^{n-1} \tfrac{n-1}{n} y^{n/(n-1)} & w & = (-1)^n (n-1) y^{1/(n-1)} u,
-\end{align*}
-we have
-\begin{align*}
-\widetilde{\Ai}^{(k)}_n(y) & = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w^n - yw\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \left(w^{n-1} - ny\right)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \big((n-1)^{n-1} yu^{n-1} - ny\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}yw \big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[(-1)^n \tfrac{n-1}{n} y^{n/(n-1)} u\big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,dw \\
-& = (-1)^n (n-1) \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^n (n-1) \frac{\exp\left(\pi ik \big(1 - \tfrac{1}{n-1}\big)\right)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-\end{align*}
-\color{black}
-\[ \widetilde{\Ai}^{(k)}_n(y) = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-\subsubsection{Rewriting as a \textcolor{magenta}{(???)} equation}
-We can distill the most interesting parts of the hyper-Airy function by writing
-\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K^{(k)}\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
-where
-\begin{equation}\label{int_higher-Ariy}
-K^{(k)}(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
-\end{equation}
-Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
-\begin{equation}\label{eqn:higher-Airy}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] K^{(k)} = 0.
-\end{equation}
-The sub-leading coefficients are 
-\[ c_n^{(1)} = \frac{n-1}{2}. \]
-
-The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
-\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,\frac{\Gamma(n+2)}{\Gamma(n-k)} \]
-in terms of the polynomials
-
-\begin{tabular}{llllllllllll}
-$b_n^{(2)}$ & = & $\frac{1}{24}$ \\
-$b_n^{(3)}$ & = & $\frac{1}{48} n$ \\
-$b_n^{(4)}$ & = & $\frac{73}{5760} n^2$ & + & $\frac{1}{1152} n$ & - & $\frac{1}{2880}$ \\
-$b_n^{(5)}$ & = & $\frac{11}{1280} n^{3}$ & + & $\frac{1}{768} n^{2}$ & - & $\frac{1}{1920} n$ \\
-$b_n^{(6)}$ & = & $\frac{3625}{580608} n^{4}$ & + & $\frac{61}{41472} n^{3}$ & - & $\frac{181}{322560} n^{2}$ & - & $\frac{1}{41472} n$ & + & $\frac{1}{181440}$. 
-\end{tabular}
-
-\vspace{5mm}
-
-Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}.
-They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
-which tells us that
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots.
-\]
-The last coefficient can be written as
-\[ c_n^{(n-1)} =\left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, 
-\]
-giving
-\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ \Gamma(n+2). \]
-
-\subsubsection{Building a frame of analytic solutions}
-
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:higher-Airy}.
-We'll succeed when $\alpha^{n-1} - 1 = 0$, and we'll see that $K^{(k)}$ is a scalar multiple of $\laplace_{\zeta, \alpha_k} v_k$ with $\alpha_k=e^{2\pi i \tfrac{k}{n-1}}$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha_k} v$ satisfies the differential equation~\eqref{eqn:higher-Airy} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-higher-Airy}
-\left[ \big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \partial_{\zeta,\alpha_k}^{-1}\circ \zeta^{n-2} - c_n^{(2)} \partial_{\zeta,\alpha_k}^{-2} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \partial_{\zeta,\alpha_k}^{-(n-1)} \right] v = 0.
-\end{equation}
-
-Since equation \eqref{eqn:higher-Airy} is written in form \eqref{eqn:standard ODE} and the coefficient $c_n^{(1)}$ is explicitly known, we deduce that equation \eqref{int-eq:spatial-higher-Airy} admits a slight solution at $\zeta={\alpha_k} $ of order $\tau_{\alpha_k}=\frac{1}{2}$.
-In particular, $v$ is a solution of \eqref{int-eq:spatial-higher-Airy} if and only if it solves the following differential equation
-
-\begin{equation}\label{diff-eq:spatial-higher-Airy}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-2}\circ \zeta^{n-2} - c_n^{(2)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \right] v = 0.
-\end{equation}
-
-Using the Liebniz rule for the differential, we get
-
-\color{Peru}
-
-\begin{align*}
-\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big]v&=\sum_{j=0}^{n-1} \binom{n-1}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]\\
-&=(\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}v+ (n-1)^2\zeta^{n-2} \partial_\zeta^{n-2}v +\\
-&\qquad \sum_{j=2}^{n-1} \binom{n-2}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-1)! v\\
-\big(\tfrac{\partial}{\partial {\zeta}}\big)^{n-2}\circ \zeta^{n-2}v&=\zeta^{n-2}\partial_\zeta^{n-2}v+\sum_{j=1}^{n-3} \binom{n-2}{j} v^{(n-j-2)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-2)!v \\
-\big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3}v&=\sum_{j=0}^{n-4} \binom{n-3}{j} v^{(n-j-3)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-3)!v\\
-\tfrac{\partial}{\partial \zeta} \circ\zeta v&=\zeta \partial_\zeta v+v
-\end{align*}
-
-\color{black}
-\begin{equation}\label{diff-eq:spatial-mod-higher-Airy}
-\left[ (\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}+ \big[(n-1)^2-c_n^{(1)}\big]\zeta^{n-2} \partial_\zeta^{n-2}+...+\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big] \right] v = 0.
-\end{equation}
-
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-higher-Airy} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-higher-Airy} looks like
-\begin{multline}\label{diff-eq:spatial-mod-higher-Airy-1}
-\left[\zeta_1(n-1+...+(n-1)\zeta_1^{n-3} + \zeta_1^{n-2}) \big(\tfrac{\partial}{\partial \zeta_1}\big)^{n-1} + \big[(n-1)^2-c_n^{(1)}\big](1+\zeta_1)^{n-2} \tfrac{\partial}{\partial \zeta_1}^{n-2} + ...
-\right.\\
- \left. +\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big]\right] v = 0.
-\end{multline}
-
-\subsubsection{Higher Airy of degree $3$}
-Setting $n=4$, equation \ref{eqn:higher-Airy} turns into
-
-\begin{equation}\label{eqn:reg-higher3}
-\left[\frac{\partial^3}{\partial z^3}+1+\frac{3}{2z}\frac{\partial^2}{\partial z^2}-\frac{5}{16}\frac{1}{z^2}\frac{\partial}{\partial z}+\frac{5}{32}\frac{1}{z^3}\right]\varphi=0
-\end{equation}
-
-and going to the spatial domain, $\laplace_{\zeta,\alpha_k}$ satisfies equation~\eqref{eqn:reg-higher3} if and only if $v$ satisfies
-
-\begin{equation}\label{diff-eq:spatial-higher3}
-\left[(\zeta^3-1)\partial_\zeta^3-\frac{15}{2}\zeta^2\partial_\zeta^2-\frac{187}{16}\zeta\partial_\zeta+\frac{81}{32}\right]\varphi=0
-\end{equation}
-
-Let's find a solution of equation~\eqref{diff-eq:spatial-higher3} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-higher3} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(3 + 3\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^3 - \frac{15}{2}(1 + 2\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 -\frac{187}{16}(1+\zeta_1)\tfrac{\partial}{\partial \zeta_1} + \frac{81}{32}\right] v = 0.
-\end{equation}
-
-\textcolor{DarkBlue}{[Find solutions using hypergeometric functions]}
-
-\subsubsection{Contour argument for higher Airy of degree $3$}
-
-We can recast integral \eqref{int_higher-Ariy} into the $\zeta$-plane by setting $\zeta=27 u^4-4 u$, which implies that $d\zeta=4 (27 u^3-1) du$.
-Projecting $z^{-1/4}\Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing a branch of that lifts $\gamma_z$ back to $z^{-1/4}\Lambda^{(k)}$, we get
-
-\begin{align*}
-K^{(k)}(z)&=\textcolor{magenta}{const.} \int_{\textcolor{magenta}{const.}z^{-1/4}\Lambda^{(k)}}\exp\big[- z \big(27 u^4-4 u\big)\big] du\\
-&=\textcolor{magenta}{const.} \int_{\gamma_z}e^{-z\zeta} \frac{d\zeta}{4(27u^3-1)}\\
-&=\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta}\frac{1}{3}\left[\frac{1}{3u-1}+\frac{1}{3e^{\frac{2\pi i}{3}} u -1}+\frac{1}{3e^{\frac{4\pi i}{3}} u-1}\right] d\zeta\\
-&=-\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta} {}_3F_2\left(\frac{1}{3},\frac{2}{3},1;\frac{1}{3},\frac{2}{3};27 u^3\right) d\zeta
-\end{align*}
-\[
-\frac{1}{4}\frac{1}{27u^3-1}=\frac{1}{4}(\frac{A}{3u-1}+\frac{B}{3u-\omega}+\frac{C}{3u-\omega^2})
-\]
-
-\subsection{Generalized Airy}
-
-In \cite{Reid} \cite{Drazin-Reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as countour integral (\cite{dlmf} \S 9.13(ii))
-
-\begin{align*}
-\mathrm{A}_k(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
-\mathrm{B}_k(z,p)&=\int_{\gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
-\end{align*}
-where the countours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig.countours}
-
-\begin{figure}
-%\includegraphics[scale=0.5]{countours}
-\end{figure}
-
-Each generalize Airy functions is a solution of
-
-\begin{equation}
-\left[\partial_z^3-z\partial_z+(p-1)\right]f(z,p)=0
-\end{equation}
-
-and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
-
-We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
-
-\begin{equation}
-I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
-\end{equation}
-
-where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}).
-In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$:
-
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
-&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
-\end{align*}
-
-It follows that $I_+(z)$ is a solution of
-
-\begin{equation}\label{eq:I}
-\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
-\end{equation}
-
-From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
-\begin{equation}
-\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
-\end{equation}
-
-where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
-
-\begin{multline}\label{w1}
-\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
-\end{multline}
-
-\begin{multline}\label{w2}
-\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
-\end{multline}
-
-\begin{multline}\label{w3}
-\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
-\end{multline}
-
-Let us first study equation \eqref{w1}: its Borel transform is
-
-\begin{multline*}
--\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
-+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
-\end{multline*}
-
-We differentiate three times, getting
-
-\begin{multline*}
-\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
-+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
-\end{multline*}
-
-we set $y=\zeta^2$
-
-%\begin{multline}
-%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
-%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
-%\end{multline}
-\begin{multline}\label{eq:hw1}
-y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
-+\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
-\end{multline}
-
-which is a generalized hypergeomtric equation (~16.8.5 \cite{dlmf}) with parameters
-
-\begin{align*}
-\mathbf{a}_0=\left(\frac{3}{2}-\frac{p}{3};\frac{7}{6}-\frac{p}{3};\frac{5}{6}-\frac{p}{3}\right) & \qquad\qquad \mathbf{b}_0=\left(\frac{1}{2};\frac{3}{2}\right)
-\end{align*}
-
-therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$.
-
-Then we look at equation \eqref{w2}: its Borel transform is
-
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
--\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-
-and taking three derivatives it simplifies to
-
-\begin{multline}
-\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
-\left.
-\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
-\end{multline}
-
-define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
-
-\begin{multline}\label{eq1}
-\left[y\left(y+\frac{4}{9}\right)^2\partial_y^3+2\left(\frac{3}{2}y+\frac{4}{3}+\frac{y}{2}\left(\frac{17}{2}+p\right)\right)\left(y+\frac{4}{9}\right)\partial_y^2+\left(\frac{2}{3}+\frac{y}{4}\left(\frac{17}{2}+p\right)\right)\partial_y\right.\\
-\left.+\frac{1}{4}\left(\frac{p^3}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(y+\frac{4}{9}\right)\partial_y+\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(y)=0
-\end{multline}
-
-which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
-
-\begin{multline}
-\left[t^2(1-t)\partial_t^3-t\left(\big(\frac{23}{4}+\frac{p}{2}\big)t-\frac{p}{2}-\frac{11}{4}\right)\partial_t^2-\left(-\frac{5}{8}-\frac{p}{4}+t\Big(\frac{887}{144}+\frac{17}{12}p+\frac{p^2}{12}\Big)\right)\partial_t +\right.\\
-\left. -\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(t)=0
-\end{multline}
-hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
-
-\begin{align*}
-\mathbf{a}=\left(\frac{5}{4}+\frac{p}{6};\frac{7}{12}+\frac{p}{6};\frac{11}{12}+\frac{p}{6}\right) & \qquad\qquad \mathbf{b}=\left(\frac{1}{2};\frac{5}{4}+\frac{p}{2}\right)
-\end{align*}
-
-and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
-The equation \eqref{w3} differes from \eqref{w2} for few signs: we find that its Borel transform is
-
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)+2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt+\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-+\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-
-and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
-$\hat{w}_3(\zeta)= c_3\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta-1\right)^2\right)$.
-In particular,
-
-\begin{equation}
-\hat{w}_3(\zeta)=C_{23}\hat{w}_2(\zeta-\tfrac{4}{3})
-\end{equation}
-
-\color{DarkTurquoise}
-
-\section{Third-order exponential integrals}
-\begin{itemize}
-\item Reduce to
-\[ I(z) = \int \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
-using change of coordinate.
-\item When $p \neq 0$, can reduce further to
-\[ I(z) = p^{1/2} e^{-qz} K_{1/3}(p^{3/2} z). \]
-\item As $p$ goes to zero, $I(z)$ degenerates to
-\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}).
-\]
-\end{itemize}
-
-\color{orange}
-\section*{Outline}
-
-\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
-
-\begin{enumerate}
-\item introduction
-\begin{itemize}
-\item Exponential integrals
-\begin{itemize}
-\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
-\item the choice of the path $\mathcal{C}$: 
-\begin{itemize}
-\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
-\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
-\end{itemize}
-\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
-\begin{itemize}
-\item there is a comparison isomorphism (Maxim)
-\end{itemize}
-\item varying $z$ we have the Stokes phenomena
-\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
-\begin{itemize}
-\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
-\item it is an example of resurgent series (\'Ecalle)
-\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
-\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
-\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
-There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
-\end{itemize} 
-\end{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
-\item motivation
-\begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
-\end{itemize}
-\end{itemize}
-\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
-\item State results about resurgence of exponential integrals and Stokes phenomena
-\begin{itemize}
-\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]
-\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
-\end{itemize}
-\end{itemize}
-\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
-\begin{enumerate}
-\item Analytic
-\begin{enumerate}
-\item Introduction
-\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
-\item The Laplace transform of a holomorphic function
-\begin{enumerate}
-\item Over an ordinary point
-\item Over a branch point
-\item Differential equation
-\end{enumerate}
-\item Relating differential equations in the frequency domain to integral equations in the position domain
-\end{enumerate}
-\item Formal
-\begin{enumerate}
-\item Laplace transform of a formal series
-\item Borel transform
-\item Relating differential equations in the frequency variable to integral equations in the position variable
-\end{enumerate}
-\end{enumerate}
-\item Review of integral equations
-\begin{itemize}
-\item Existence of solutions
-\item Fractional integrals and derivatives
-\item Going between integral and differential equations (slight functions)
-\end{itemize}
-\item General cases
-\begin{enumerate}
-\item Borel regularity
-\begin{itemize}
-\item General ODE of the form
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
-\begin{itemize}
-\color{DarkCyan}
-\item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
-\begin{itemize}
-\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
-\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
-\end{itemize}
-\color{orange}
-\item Show that we can find a slight solution at each critical value.
-\item Show that $\hat{\iota} = \tilde{\iota}$, where:
-\begin{itemize}
-\item $I = \laplace \iota$
-\item $\hat{\iota}$ is the Taylor expansion of $\iota$
-\item $\tilde{I}$ is the asymptotic series of $I$
-\item $\tilde{\iota} = \borel \tilde{I}$
-\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
-\end{itemize}
-\end{itemize}
-\item General thimble integral (conditions?)
-\begin{itemize}
-\item Proof of Borel regularity
-\item $3/2$-derivative formula
-\item Contour argument
-\end{itemize}
-\end{itemize}
-\item Resurgence
-\begin{itemize}
-\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
-\item Relate to Ecalle's formalism and the alien derivative
-\item Stokes factors
-\begin{itemize}
-\item For ODEs
-\item For thimble integrals
-\end{itemize}
-\end{itemize}
-\end{enumerate}
-\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
-\begin{enumerate}
-\item The Airy example
-\begin{itemize}
-\item $I(z)$ is a solution of a linear ODE.
-We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Compute Stokes constants
-\begin{itemize}
-\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]
-\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
-\end{itemize}
-\item Comparison with the literature \textcolor{gray}{has to be done}
-\begin{itemize}
-\item Mari\~{n}o
-\item Sauzin
-\item Kontsevich slides
-\item Kawai--Takei? [might take too long to understand well enough]
-\end{itemize}
-\end{itemize}
-\item The Airy--Lucas examples
-\begin{itemize}
-\item Compute Borel transform [{\tt airy-resurgence}]
-\item Compute Stokes constants \textcolor{gray}{has to be done}
-\end{itemize}
-\item Bessel 0 (it is different because we have infinite cover)
-\begin{itemize}
-\item Compute Stokes constants [{\tt draft2}]
-\end{itemize}
-\item Bessel $\mu$ (follows from Bessel 0)
-\begin{itemize}
-\item Compute Stokes constants [{\tt modified Bessel}]
-\end{itemize}
-\item The generalized Airy example
-\item The vibrating beam example
-\begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals, since Andy is interested in that sort of thing
-\end{itemize}
-\end{enumerate}
-\end{enumerate}
-
-\color{black}
-
-\appendix
 
@@
 
-\section{The Airy equation}\label{airy-appendix}
-
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel-1/3}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
-%The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-%\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-%where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
-Like we did in equation~\ref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
-
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsection{Asymptotic analysis}
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
-
-\subsection{Building a distinguished frame of analytic solutions}
-\subsubsection{Going to the spatial domain}\label{spatial}
-%\subsubsection{The big idea}\label{big-idea}
-We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-%\textcolor{Magenta}{Show that $W_1$ is asymptotic to $\tilde{W}_1$!}
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
-
-%\color{DodgerBlue}
-%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
-%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-%where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-\subsection{Borel regularity}\label{bessel-regularity}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
-
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\laplace_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
-
-\begin{align*}
-\borel\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\borel\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-
-\subsection{Contour argument for the Airy function}\label{contour-argument}
-Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
-\begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ in the $\zeta$ plane.}
-\end{center}
-
-From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
-so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
-
-In addition to the solutions $v_1$ and $v_{-1}$ from Section~\ref{pos-root}\,--\, \ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
-\begin{alignat*}{2}
-g_1 &\;=\;& & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi_1\big) \\
-g_{-1} &\;=\;&  & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi_1\big),
-\end{alignat*}
-given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
-so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
-The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $g_1$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,v_1$,
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
-Hence,
-\begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} v_1\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} v_1\;d\zeta \\
-e^z K & = \tfrac{i}{2} \laplace_{\zeta_1} v_1,
-\end{align*}
-just as we found in Section~\ref{bessel-regularity}.
-\subsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
-
-To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
-\[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\ref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the contour integration method of solving equation~\eqref{eqn:mod-bessel} is associated with the basis
-\begin{align*}
-g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
-\end{align*}
-of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
-
-The Laplace transformation method of solving equation~\eqref{eqn:mod-bessel}, on the other hand, is associated with the basis
-\begin{alignat*}{2}
-v_{-1} &\;=\;& (1-\xi)^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-v_1 &\;=\:& \xi^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
-\end{alignat*}
-given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
-
-Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
-\begin{alignat*}{3}
-v_{-1} &\;=\;&\tfrac{1}{\sqrt{3}}\,g_{-1} &\;+\;& \tfrac{1}{2}\,v_1 \\
-v_1 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_{1} &\;+\;& \tfrac{1}{2}\,v_{-1}.
-\end{alignat*}
-Summing these identities, we see that
-\[ g_1 + g_{-1} = \tfrac{\sqrt{3}}{2}\,(f_1 + f_{-1}), \]
-giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
-
-\subsection{Comparison with other treatments of the Airy equation}
-
-\subsubsection{Different Borel transform convention} Physicists often use a different version of the Borel transform:
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
-It's sometimes convenient to $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
-
-For problems involving a small parameter $\hbar$ rather than a large parameter $z$, physicists also define
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\hbar^n & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-From a combinatorial perspective, this is just the transformation that sends an ordinary generating function to the corresponding exponential generating function.
-
-In \cite{Diablerets}, the author studies the Airy functions as example of resurgent functions. He starts with the formal trans-monomial solutions of Airy equation:
-
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
-\end{align*}  
-where 
-\begin{align*}
-\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
-\end{align*}
-%Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-Then, by applying the two definitions of the Borel transform $\borel_{\textit{phys}}$ and $\borel$, on the one hand we have  
-\begin{align*}
-w_{1,2}(\zeta)&\defeq\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
-&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) 
-\end{align*}
-on the other hand, we find
-\begin{align*}
-\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
-\end{align*}
-%That ambiguity comes from the different definitions of Borel transforms: 
-%\begin{align*}
-%\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%\end{align*}
-
-and comparing the two solutions we notice that up to the factor of $\delta$
-
-\begin{equation}\label{Borel-W12}
-\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta) 
-\end{equation}
-More generally, if $\tilde{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
-
-\begin{equation}
-\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\tilde{\Phi}=\borel\tilde{\Phi}.
-\end{equation}
-In particular, $\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
-
-%Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
-We want to compare $v_1$ with the \textit{physic} Borel transform $\borel_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
-%
-%\begin{align*}
-%\borel_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
-%&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
-%&=\frac{1}{2\pi}\zeta^{1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right) 
-%\end{align*}
-%
-%Now taking the $-1$- derivative of $v_1(\zeta)$ we get
-%
-%\begin{align*}
-%\partial_\zeta^{-1} v_1&=\frac{1}{\Gamma(1)}\int_0^{\zeta}(\zeta-\zeta') v_1(\zeta')d\zeta'\\
-%&=\int_0^{\zeta}(\zeta-\zeta') \zeta'^{-1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta'}{2}\right)d\zeta'\\
-%&=\frac{\Gamma(1/2)}{\Gamma(3/2)}\zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)\\
-%&=2 \zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)
-%\end{align*}
-
-\subsubsection{Integral formula for hypergeometric functions}
-
-In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
-
-He considers the formal power series  
-\[\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
-such that
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
-\tilde{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
-\end{align*} 
-are formal solutions of the Airy equation. Notice that compared to Marino's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
-
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\tilde{\Phi}_{\pm}$ as a convolution product:
-
-\begin{align*}
-\hat{\phi}_+(\zeta):=\borel\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
-\end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$.
-
-%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
-%
-%\begin{align*}
-%\tilde{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\tilde{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
-%\end{align*}
-%which up to a constant factor for $\delta$, they agree with our results.
-
-Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
-
-\begin{align*}
-\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
-\end{align*}
-where in the last step we use the Euler formula for hypergeometric functions \footnote{The Euler formula is \begin{equation}\label{Euler formula}
-{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
-\end{equation}}. Then, by taking derivatives we recover $\hat{\phi}_{\pm}(\zeta)$:
-
-\begin{align*}
-\hat{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
-\hat{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)
-\end{align*} 
-and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
-The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
-Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see Lemma 6.106 \cite{MS}).
-%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
-
-\subsubsection{Comparison with exact WKB}
-
-Kawai and Takei study the WKB analysis of the Airy--type Schrodinger equation
-
-\begin{equation}
-\label{WKB_Airy} 
-\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
-\end{equation}
-as $\eta\to\infty$.
-They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
-In the coordinate $t=\frac{3}{2}yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
-\begin{align*}
-\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
-\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
-\end{align*}
-where $s=t/2+1/2$. 
-The same hypergeometric functions have been computed in Section \ref{Airy} as the Borel transform of the formal solutions of the Airy equation
-
-\begin{equation}
-\label{Airy}
-\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
-\end{equation}
-
-Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
-So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
-
-First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
-\begin{align*}
-\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
-\end{align*} 
-then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
-\begin{align*}
-\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
-\end{align*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
-\begin{equation}
-\label{eq_Phi}
-\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
-\end{equation}
-
-\begin{proof}
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
-&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
-&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
-&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
-\end{align*}
-\end{proof}
-Now rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{2}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta x^{-1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-%&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-1\right]\Phi=0
-\end{align*}
-
-therefore $\Phi(q)$ is a solution of the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
-
-\begin{remark}
-The change of coordinate $q=\frac{2}{3}\eta x^{3/2}$ is not casual: recall that the WKB ansatz for a Schrodinger type equation is
-
-\begin{equation}
-\psi(x,\eta)=\exp\left(\int_{x_0}^xS(\eta,x')dx'\right)
-\end{equation} 
- and $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. In addition, for the Airy--type Schrodinger equation 
- \begin{align*}
- S_{-1}^2=x
- \end{align*}
-hence, up to a choice of sign for the square root
-\begin{align*}
-q&=\frac{2}{3}\eta x^{3/2}=\eta\int_0^x\sqrt{x'}dx'=\eta\int_{0}^xS_{-1}(x')dx'.
-\end{align*}
-We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.
-\end{remark}
-
-\section{Application of the integral formula}
-
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
-
-By general theory it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
-Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the contour argument and from the integral formula.
-When computed from the ODE, there is an ambiguity in the choice of the constant, while with the contour argument and the fractional integral formula the ambiguity is solved.
-We will see this for the modified Bessel equation.
-
-This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
-Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
-%In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
-\begin{lemma}\label{claim 2}
-The following formula holds true
-\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
-for any $\zeta\in [2/3,+\infty)$.
-\end{lemma}
-\begin{proof}
-In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
-Hence,
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
-
-\begin{lemma}\label{claim 3}
-For any $\zeta\in (-\infty,-2/3]$
-\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
-\end{lemma}
-\begin{proof}
-Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
-\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
-In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-
-\bibliographystyle{plain}
-\bibliography{airy-resurgence}
-
 \end{document}

### 2023-07-25 reg-sing-volterra.tex
Show that V is a contraction away from the origin

@@
 \subsection{Finding spaces where $\volterra$ is a contraction}
+\subsubsection{Overview}
 In this section, we'll prove the following proposition.
@@
 Since we set $\sigma < \rho$, this proves Proposition~\ref{get-contraction}.
-\subsubsection{Near the origin}\label{near-bound}
-For each $a \in \domain$, we have
+\subsubsection{First steps}\label{first-steps}
+The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)\,\varphi\;d\zeta| \]
@@
 \end{align*}
-Now, suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that
+What we do next depends on whether $a$ is in $\near$ or $\far$.
+\subsubsection{Near the origin}\label{near-bound}
+Suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that
 \begin{align*}
@@
 \end{align*}
-for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight-line path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 \begin{align*}
@@
 \end{align*}
-Since we set $\sigma < \rho$, this brings us halfway to proving that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$.
+Since we set $\sigma < \rho$, this brings us halfway to proving Proposition~\ref{get-contraction}.
 \subsubsection{Away from the origin}\label{far-bound}
+Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from \textcolor{orange}{[difference bound]} that we can find a constant $M$ for which
+\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
+for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\]
+Let's again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.
+\end{align*}
+Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt. \]
+
+We can make this bound as small as we want by increasing $\Lambda$.
+To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and of the integration separately.
+At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
+\begin{align*}
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda - \lambda)R} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda - \lambda)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\end{align*}
+At the end, we instead use a worst-case estimate on $t^{1-\rho}$:
+\begin{align*}
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)R(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)R} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}.
+\end{align*}
+\textcolor{ForestGreen}{[Consider just writing ``const.'' instead of explicit constants.]}
+
+We now know that by setting $\Lambda > \lambda$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+This completes our proof of Proposition~\ref{get-contraction}.
+%%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
+%%\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\]
+%%This time, we'll use the parameterization $\zeta = s \frac{\zeta(a)}{|\zeta(a)|}$, with $s \in (0, |\zeta(a)|]$:
+%%\begin{align*}
+%%|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{|\zeta(a)|} \left(\frac{s}{|\zeta(a)|}\right)^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+%%\end{align*}
 %------------------------------------------------------------------------

### 2023-07-25 exp-resurgence.tex
Updates from Overleaf

@@
 \item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the fractional derivative formula.
+\item A corollary of [Thm 4] is the thimble projection formula.
 \item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
@@
 We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
-Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+Then, on the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.
+On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
 
@@
 The anharmonic oscillator was also discussed in (Bender--Wu, Appendix B in \cite{aniceto2019primer}).
-Other example haven't been discussed much, as for Airy--Lucas functions.
-
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in mathematics and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
+Other examples haven't been discussed much, as for Airy--Lucas functions.
+
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics as a powerful alternative to Borel summability.
+The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
 For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.
 
@@
 \item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
+\item thimble projection formula
 \item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
@@
 
-\subsection{Fractional derivative formula}
+\subsection{thimble projection formula}
 \begin{itemize}
@@
 
-\subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
+\subsubsection{Thimble projection technique for Airy-Lucas functions}\label{contour-argument-AL}
 \textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
@@
 
-The contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
+The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
 
@@
 \textcolor{orange}{[can we use (51) directly?
-It seems to me that if I try the contour argument from the integral expression directly, I'm not able to write write $1/\sinh(it)$ as a function of $\zeta$.
+It seems to me that if I try the thimble projection reasoning from the integral expression directly, I'm not able to write $1/\sinh(it)$ as a function of $\zeta$.
 ]}
@@
 
-\subsubsection{Contour argument for higher Airy of degree $3$}
+\subsubsection{thimble projection reasoning for higher Airy of degree $3$}
 
@@
 and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
-The equation \eqref{w3} differes from \eqref{w2} for few signs: we find that its Borel transform is
+The equation \eqref{w3} differs from \eqref{w2} for few signs: we find that its Borel transform is
 
@@
 
-\subsubsection{Fractional derivative formula}
+\subsubsection{thimble projection formula}
 
@@
 
-\[ I_j(z) = \int_{\Lambda_j} \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
+\[ I_j(z) = \int_{\Lambda_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
 
 where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
-We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$.
-In both cases, we will compute the differential equation satisfied by $I$.
-
-\begin{lemma}
-    Let $f(u)=u^3+pu+q$, 
-    \begin{itemize}
-        \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
-        \begin{equation}\label{eqn:degree-3-poly-2roots}
-            \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
-        \end{equation}
-        \item  if $p=0$, then $I(z)$ solves
+We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$.
+\footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}
+
+Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:
+
+\begin{itemize}
+    \item \textbf{Action of translations:} let $q\in\C$, post-composing with translation of $q$ maps $f\to f+q$, thus 
+    \begin{align*}
+        \int_{\Lambda_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
+    \end{align*}
+    \item  \textbf{Action of scaling-rotations:} let $\gamma\in\C$, post-composing with scaling-rotations by $\gamma$ maps $f\to \gamma\cdot f$, thus 
+    \begin{align*}
+        \int_{\Lambda_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
+    \end{align*}
+\end{itemize}
+
+In particular, we can always reduce to study the thimble integral in simpler situations.
+
+As an example, every degree three polynomial with distinct critical points can be transformed in the Chebyshev polynomial $T_3(t)=4 t^3-3t$, implying that the thimble integral $I_+$ can be transformed into the Airy--Lucas integral with parameter $m=1, n=3$.
+This follows by post-composing $f$ with a translation of $-q$ followed by a scaling-rotation of $\frac{ -i 3^{3/2}}{2 p^{3/2}}$
+
+\begin{align*}
+    f-q &= u^3 + pu \\
+    (f-q) \cdot \frac{ -i 3^{3/2}}{2 p^{3/2}} &= 4 \Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big)^{3} - 3\Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big) \\
+    &= 4 t^3- 3t 
+\end{align*}
+
+with $t= \sqrt{-\frac{3}{p}} \frac{u}{2}$. Then the thimble integral $I_+$ gets transformed into
+
+\begin{align*}
+    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\Lambda_+} e^{z (4t^3-3t)} du\\
+    &= 2\sqrt{-\tfrac{p}{3}} \int_{\Lambda_+} e^{z (4t^3-3t)} dt \\
+    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
+\end{align*}
+
+In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
+%In both cases, we will compute the differential equation satisfied by $I$.
+
+%\begin{lemma}
+ %Let $f(u)=u^3+pu+q$, 
+  %  \begin{itemize}
+   %     \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
+    %    \begin{equation}\label{eqn:degree-3-poly-2roots}
+    %        \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
+    %    \end{equation}
+    %    \item  if $p=0$, then $I(z)$ solves
+     %   \begin{equation}\label{eqn:degree-3-poly-1root}
+      %      \left[\partial_z+q+\frac{1}{3z}\right]I=0
+      %  \end{equation}
+    %\end{itemize}
+%\end{lemma}
+%\begin{proof}
+ %   The proof follows from a direct computation. 
+%\end{proof}
+
+%Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$.
+Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
+
+%\begin{equation}\label{eqn:deg3-borel-ODE}
+ %   \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
+%\end{equation}
+
+%Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes
+
+%\begin{equation*}
+ %   \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
+%\end{equation*}
+
+%which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$
+
+%\begin{equation*}
+ %   \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
+%\end{equation*}
+
+%and it admits a slight solution \textcolor{red}{the solution should match with the one of airy, so choose $w_2$ in DLMf list and not $w_1$}
+
+%\begin{align*}
+ %   v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
+  %  &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
+%\end{align*}
+
+%Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$
+
+%\begin{equation*}
+%    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
+%\end{equation*}
+
+We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.
+
+First, notice that $I(z)$ solves
        \begin{equation}\label{eqn:degree-3-poly-1root}
@@
        \end{equation}
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    The proof follows from a direct computation. 
-\end{proof}
-
-Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$.
-Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
-
-\begin{equation}\label{eqn:deg3-borel-ODE}
-    \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
-\end{equation}
-
-Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes
-
-\begin{equation*}
-    \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
-\end{equation*}
-
-which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$
-
-\begin{equation*}
-    \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
-\end{equation*}
-
-and it admits a slight solution
-
-\begin{align*}
-    v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
-    &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
-\end{align*}
-
-Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$
-
-\begin{equation*}
-    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
-\end{equation*}
-
-When $p=0$, the critical point of $f$ is $x=0$ and we can argue as before: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
+
+and we can find a Borel regular solution following the argument of \S \ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
 
@@
 namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
-The same result is confirmed by the contour argument which in this simple case reads
+
+The result is confirmed by the thimble projection reasoning which in this simple case reads
 
@@
 
-\textcolor{orange}{[It'd be nice to have the contour argument for $p\neq 0$ too, however we don't have the same nice coordinates as in the other examples--maybe we can do a change of coordinates to recover $K_{1/3}$ as suggested below.]}
 \color{DarkTurquoise}
 \begin{itemize}
-\item Reduce to
-\[ I(z) = \int \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
-using change of coordinate.
-\item When $p \neq 0$, can reduce further to
-\[ I(z) = p^{1/2} e^{-qz} K_{1/3}(p^{3/2} z). \]
 \item As $p$ goes to zero, $I(z)$ degenerates to
@@
 \item $3/2$-derivative formula
-\item Contour argument
+\item thimble projection reasoning
 \end{itemize}
@@
 \begin{itemize}
-\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]
+\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
 \item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
@@
 
-\subsection{Contour argument for the Airy function}\label{contour-argument}
+\subsection{thimble projection reasoning for the Airy function}\label{contour-argument}
 Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
@@
 
-In summary, the contour integration method of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
+In summary, the thimble projection technique of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
 \begin{align*}
@@
 \[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
+
+\subsection{Thimble projection formula}
+
+In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using a trigonometric substitution.
+As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time using applying the thimble projection formula to the generalized Cardano's formula.
+
+Recall that the roots of $f(u)-\zeta$ can be written explicitly as
+
+\begin{equation}
+    u=
+\end{equation}
 
@@
 
-In Section \ref{sec:examples}, we computed the Borel transform of the asymptotics of thimble integrals in different ways: on the one hand, using the contour argument and on the other hand, solving an integral equation with a specified behavior near the singular point.
+In Section \ref{sec:examples}, we computed the Borel transform of the asymptotics of thimble integrals in different ways: on the one hand, using the thimble projection reasoning and on the other hand, solving an integral equation with a specified behavior near the singular point.
 In particular, we noticed that the two approaches give the same result up to the choice of a constant, as the integral equation is homogeneous.
@@
 This approach
-As shown in the previous examples, the Borel transform  of the asymptotics of thimble integrals can be computed in different ways: from the ODE they solve, from the contour argument, and from the integral formula \eqref{formula1}.
-When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneous, while with the contour argument and the fractional integral formula the ambiguity is solved.
+As shown in the previous examples, the Borel transform  of the asymptotics of thimble integrals can be computed in different ways: from the ODE they solve, from the thimble projection reasoning, and from the integral formula \eqref{formula1}.
+When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneous, while with the thimble projection reasoning and the fractional integral formula the ambiguity is solved.
 
@@
 
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the thimble projection formula~\eqref{int:deriv-formula}. \color{olive}
 
 By general theory, it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
-Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the contour argument and from the integral formula.
-When computed from the ODE, there is an ambiguity in the choice of the constant, while with the contour argument and the fractional integral formula the ambiguity is solved.
+Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the thimble projection reasoning, and from the integral formula.
+When computed from the ODE, there is an ambiguity in the choice of the constant, while with the thimble projection reasoning and the thimble projection formula the ambiguity is solved.
 We will see this for the modified Bessel equation.
 
-This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
+This method allows us to uniquely determine the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
 Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.

### 2023-07-26 reg-sing-volterra.tex
Version of the proof where we take the expansion of p/q

@@
 If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
-\subsection{Main result}
+\subsection{Main results}
 %%\begin{defn}\label{fin-order}
@@
 %%\end{defn}
+The
+\begin{thm}
+
+\end{thm}
+\begin{thm}
+\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
+\end{thm}
 \textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
@@
 Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
+\color{RoyalBlue}
 \begin{thm}
@@
 \end{thm}
+\color{black}
 %%\begin{thm}
@@
 %------------------------------------------------------------------------
+
+\subsection{The test function is in $\singexp{\tau-1}{\lambda}(\Omega)$}
+
+\begin{prop}
+    Let $f_0$ be the solution of \textcolor{orange}{Volterra simplified equation}, namely
+
+\begin{equation}\label{eqn:test_solution}
+    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]
+\end{equation}
+for a point $\zeta(b)\in\Omega$. Then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$. 
+\end{prop}
+
+\begin{proof}
+    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
+\begin{itemize}
+    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by assumption \eqref{h1} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+  \begin{equation}\label{eqn:limit_h1}
+      \Big\vert\frac{q(a')}{p(a)}+\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
+  \end{equation}
+  notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$.
+Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
+  \begin{align*}
+      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
+      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q(a')+q'(a')(\zeta-\zeta(a')+...)}{p(a')+p'(a')(\zeta-\zeta(a'))+\tfrac{p''(a')}{2}\zeta^2+...}\Big\vert \, |d\zeta|\\
+      &\leq \int_{\zeta(b)}^{\zeta(a)} \left\vert\frac{q(a')}{p'(0)\zeta}\right\vert \Big\vert \frac{1+q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...}{1+p_1\zeta+p_2\zeta^2+...}\Big\vert \, |d\zeta|\\
+      &\leq c \left\vert\frac{q(a')}{p'(0)}\right\vert \int_{\zeta(b)}^{\zeta(a)} \frac{|d\zeta|}{|\zeta|}  + c \left\vert\frac{q(a')}{p'(0)}\right\vert \int_{\zeta(b)}^{\zeta(a)}\Big\vert \frac{q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...}{\zeta}\Big\vert \, |d\zeta|\\
+      &\leq c \left\vert\frac{q(a')}{p'(0)}\right\vert \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ C(\delta) 
+  \end{align*}
+  where in the last step we use that holomorphic function $\frac{q_1(\zeta-\zeta(a'))+q_2(\zeta-\zeta(a'))^2+...)}{\zeta}$ is bounded on $[\tfrac{\delta}{2},\delta]$ and $c>0$. 
+  Now we look at $f_0$: let $b'$ such that $|\zeta(b')|\leq \delta$ and $q(b')\neq 0$
+  \begin{align*}
+      \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert &\leq \Big\vert\frac{p(b)}{q(b')}\Big\vert \Big\vert\zeta(a)\frac{q(b')}{p(a)}\Big\vert \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[\left\vert\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta \right\vert\right]\\
+      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[ c \left\vert\frac{q(a')}{p'(0)}\right\vert \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ C\right]\\
+      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau'} \, e^{C(\delta)} \\
+      &\leq C_2 |\zeta(a)|^{\tau'-1}
+  \end{align*}
+  where $\tau':=c \left\vert\frac{q(a')}{p'(0)}\right\vert$. In particular,
+
+  \begin{align*}
+      \tau' &\leq \left\vert c\frac{q(a')}{p'(0)}-\zeta(a)\frac{c q(a')}{p(a)}\right\vert + \left\vert\zeta(a)\frac{c q(a')}{p(a)}-\tau\right\vert + \tau\\
+      &\leq c |q(a')|\, \left\vert\frac{1}{p'(0)}-\frac{\zeta(a)}{p(a)}\right\vert+\varepsilon+ \tau\\
+      &= \frac{c}{|p'(0)|} \frac{|q(a') \zeta(a)|}{|p(a)|} \Big\vert \frac{p(a)}{\zeta(a)}-p'(0)\Big\vert +\tau+\varepsilon\\
+      &\leq c_1(\delta,\varepsilon) +  \tau
+  \end{align*}
+where in the last step we use that $p'(0):=\lim_{\zeta(a)\to 0} \frac{p(a)}{\zeta(a)}$ and $p(0)=0$. 
+Finally, we get  
+  \begin{align*}
+      |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|&\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau'-1} \\&
+      \leq C_2(\delta) |\zeta(a)|^{\tau'-\tau} \\
+      &\leq C_3(\delta)
+  \end{align*}
+      \item \textbf{$\zeta(a)$ far to the origin.}
+\end{itemize}
+
+\end{proof}
+
 \color{SteelBlue}

### 2023-07-27 reg-sing-volterra.tex
Fill in more details about regular singular Volterra equations
Describe setting, fill in reasoning about prototype solution, and show
inclusions between weighted holomorphic L-infinity spaces.

--- 2023-07-25 reg-sing-volterra.tex
@@
 \usepackage[hmargin=1.5in]{geometry}
+\usepackage{enumitem}
 \usepackage{amsmath}
@@
 \usepackage{tikz-cd} %% for term norm scratch work
+\usepackage{tikz}
+
+% TikZ libraries
+\usetikzlibrary{bbox}
+\usetikzlibrary{fadings}
+
+% hat tip TeX.SE user marsupilam - https://tex.stackexchange.com/a/351570/6934
+%%\tikzfading[
+%%  name=radial,
+%%  inner color=transparent!0,
+%%  outer color=transparent!100
+%%]
+% hat tip TeX.SE user Andrew Stacey
+%   https://tex.stackexchange.com/a/82503/6934
+%   https://tex.stackexchange.com/questions/82425/tikz-radial-shading-of-a-ring#comment176908_82503
+\pgfdeclareradialshading{infinifade}{\pgfpointorigin}{%
+  color(0bp)=(transparent!0);
+  color(20bp)=(transparent!0);
+  color(22bp)=(transparent!10);
+  color(24bp)=(transparent!90);
+  color(25bp)=(transparent!100)
+}
+\pgfdeclarefading{infinity}{\pgfuseshading{infinifade}}%
 
@@
 \newtheorem{rmk}{Remark}
+
+% format lists
+\setlist[itemize]{leftmargin=15mm}
+\makeatletter
+% hat tip TeX.SE user31729
+%   https://tex.stackexchange.com/a/328393/6934
+\newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
+\makeatother
 
@@
 \newcommand{\volterra}{\mathcal{V}}
-\newcommand{\hardpart}{\mathcal{V}_\text{hard}}
-\newcommand{\softpart}{\mathcal{V}_\text{soft}}
+\newcommand{\hardpart}{\mathcal{V}_\text{basic}}
+\newcommand{\softpart}{\mathcal{V}_\text{extra}}
+\newcommand{\hardker}{k_\text{basic}}
+\newcommand{\softker}{k_\text{extra}}
 
@@
 If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
-\subsection{Main result}
+\subsection{Setting}
+\subsubsection{The domain}\label{setting:domain}
+Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
+Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
+For some of our results, we'll need an extra condition on $\domain$:
+\begin{itemize}
+\cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$.
+In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$.
+Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
+\end{itemize}
+For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
+\begin{center}
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=infinity]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (160:\spill)
+  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
+  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
+  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
+  arc (-60:-130:\spill) -- (0, 0);
+\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
+\end{tikzpicture}
+\end{center}
+\subsubsection{The prototype operator}\label{setting:basic}
+The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.
+
+Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
+\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
+Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
+\[ \hardker(a, a') = \frac{q(a')}{p(a)}, \]
+where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
+\[ -\frac{\tau}{\zeta(a)} - \hardker(a, a') \]
+is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.
+
+Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
+\begin{verify}
+[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded.
+By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition.
+Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
+\end{verify}
+For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
+\begin{itemize}
+\cond{slow}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
+\begin{align*}
+\left|\frac{1}{p}\right| & \le e^{\lambda_p |\zeta|} &
+\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
+\end{align*}
+outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
+\end{itemize}
+This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
+As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+\subsubsection{The perturbed operator}
+\subsection{Main results}
 %%\begin{defn}\label{fin-order}
@@
 %%\end{defn}
+\begin{thm}
+For the regular singular Volterra equation
+\[ f = \hardpart f \]
+given by an operator of the kind described in Section~\ref{setting:basic}, we have the {\em prototype solution}
+\begin{equation}\label{eqn:test_solution}
+f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
+\end{equation}
+Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
+
+The size $|f_0|$ goes like $|\zeta|^{\tau-1}$ as $\zeta$ goes to $0$. More precisely, as $|\zeta|$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
+
+If $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}, then $f_0$ is uniformly of exponential type $\lambda$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
+In light of the behavior at $\zeta = 0$ described above, this tells us that for every $\Lambda > \lambda$, the solution $f_0$ belongs to the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+\end{thm}
+\begin{thm}
+\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
+\end{thm}
 \textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
@@
 \textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
-\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R}, \]
+\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
 where
@@
 \begin{itemize}
-\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$.
+\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
+\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
 \end{itemize}
@@
 For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
-\[ \mathcal{V}f = 0 \]
+\[ \mathcal{P}f = 0 \]
 has a unique solution in the affine subspace
@@
 Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$.
-Give $\cont(\Omega)$ the compact-open topology, recalling that this is the finest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}.
+Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}.
 The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.
@@
 \begin{proof}
-\textcolor{orange}{[Check!]} Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$.
-The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$, as discussed above, so our sequence is Cauchy in $\holo(\Omega)$ too.
-Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal}, our sequence converges to a function $f$ there.
+Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$.
+The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too.
+Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
 
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|} |f_k - f_n| \le r$ whenever $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|} |f - f_n| \le r$.
+The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
 This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$.
+We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}$: picking some $r > 0$, we observe that
+\begin{align*}
+e^{-\Lambda |\zeta|}\,|f| & \le e^{-\Lambda |\zeta|}\,|f - f_n| + e^{-\Lambda |\zeta|}\,|f_n| \\
+& \le r + \|f_n\|_{0,\Lambda}
+\end{align*}
+for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
+
+%%We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$ uniformly over all $n$.
 Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
@@
 \end{prop}
+
+\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}
+\begin{prop}
+    If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
+\end{prop}
+
+\begin{proof}
+    \begin{align*}
+        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,  e^{-\Lambda |\zeta|}\, |f|\\
+        &= \sup_{\Omega} e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,e^{-(\Lambda-\Lambda') |\zeta|}\,|f|\\
+        &\leq \sup_\Omega e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,|f|\\
+        &=\|f\|_{\sigma,\Lambda'}
+    \end{align*}
+\end{proof}
+\color{OrangeRed}
+\begin{proof}
+    \begin{align*}
+        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|\\
+        &\leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
+        &=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
+        &\leq \|f\|_{\sigma,\Lambda'}
+    \end{align*}
+\end{proof}
+\color{black}
+
+\begin{prop}
+    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
+\end{prop}
+
+\begin{proof}
+    \begin{align*}
+        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}  e^{-\Lambda |\zeta|} |f|\\
+        &= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|\\
+    \end{align*}
+    The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it's bounded far from $\zeta = 0$ thanks to the decaying exponential.
+Hence,
+    \begin{align*}
+       \|f\|_{\sigma,\Lambda}&\leq C\sup_\Omega  |\zeta|^{-\sigma'}\, e^{-\Lambda'|\zeta|} \, |f|\\
+        &=C \|f\|_{\sigma',\Lambda'}
+    \end{align*}
+    for $C = \sup_{\Omega}  |\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$.
+\end{proof}
+
 %%Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
@@
 %%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
-\section{\textcolor{orange}{[Proof of main result]}}
+\section{\textcolor{orange}{[Proof of main results]}}
 \subsection{Overview}
-\subsection{An approximate solution}
+\color{ForestGreen}
+\begin{align*}
+f & = \volterra f \\
+f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
+f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
+f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
+f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
+\end{align*}
+Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
+\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
+\color{black}
+\subsection{Solving the basic \textcolor{orange}{[prototype]} equation}
 \subsubsection{Construction}
+
+\begin{prop}
+    Let $b\in\Omega$, the function 
+    \begin{equation}%%\label{eqn:test_solution}
+    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
+   \end{equation}
+is a solution of the Volterra equation $\volterra_{proto} f_0=f_0$. We call $f_0$ a prototype solution.  
+\end{prop}
+
+\begin{proof}
+    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
+    \begin{align*}
+        \big[\volterra_{proto}f_0\big](a) &= \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
+        &= \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
+        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
+        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
+    \end{align*}
+    Now we claim $\lim_{a\to 0}\Psi_0(a)=0$: in fact,
+    \begin{align*}
+        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
+        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
+        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
+    \end{align*}
+    and by \textcolor{orange}{[limit assumption]}
+\begin{align*}
+     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
+     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
+\end{align*}
+ which ends the proof of the claim. We deduce that $\volterra_{proto} f_0=f_0 $. 
+\end{proof}
+
 \subsubsection{Asymptotics}
+
+\begin{prop}
+    Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}
+
+\end{prop}
+
+\begin{proof}
+    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
+\begin{itemize}
+    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \textcolor{orange}{[limit assumption]} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+  \begin{equation}\label{eqn:limit_h1}
+      \Big\vert\frac{q(a')}{p(a)}+\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
+  \end{equation}
+ % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
+ Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
+  \begin{align*}
+      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
+      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} +\frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
+      &\leq \varepsilon \frac{\delta}{2} + \tau \log \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert
+        \end{align*}
+
+ Now we look at $f_0$: let $b'$ such that $|\zeta(b')|\leq \delta$ and $q(b')\neq 0$
+  \begin{align*}
+      \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert &\leq \Big\vert\frac{p(b)}{q(b')}\Big\vert \Big\vert\zeta(a)\frac{q(b')}{p(a)}\Big\vert \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[\left\vert\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta \right\vert\right]\\
+      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[ \tau \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ \varepsilon \frac{\delta}{2}\right]\\
+      &\leq C_2(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \Big\vert\zeta(a)\Big\vert^{\tau}   
+      \end{align*}
+
+Finally, we get  
+  \begin{align*}
+      |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
+  \end{align*}
+      \item \textbf{$\zeta(a)$ far from the origin.} Using assumptions \textcolor{orange}{[two bounds assumption]}
+
+      \begin{align*}
+          |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert \\
+          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|}  \, e^{c_p|\zeta(a)|}\exp\left[\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-c_p) |\zeta(a)|} \exp\Big[(\lambda-c_p) |\zeta(a)-\zeta(b)| \Big]
+      \end{align*}
+   which is bounded because $|\zeta(a)|>\delta$. 
+\end{itemize}
+
+\end{proof}
+
 \subsubsection{Image under $\softpart$}
+
+\begin{prop}
+    Assuming \textcolor{orange}{[bound K soft]}, namely 
+    \begin{equation}
+        |K_{soft}(a,a')|\leq C \frac{|\zeta(a)-\zeta{a'}|^{\epsilon}}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta(a')|}
+    \end{equation}
+    for every $a, a'\in\Omega$, the Volterra operator $\volterra_{soft}$ maps continuously $\singexp{\sigma}{\Lambda}(\Omega)$ to $\singexp{\sigma+\epsilon,}{\Lambda}(\Omega)$, for $\Lambda,\epsilon>0$ and $\sigma>-1$.
+\end{prop}
+
+\begin{proof}
+    Let $f\in\singexp{\sigma}{\Lambda}$,
+    \begin{align*}
+        |\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \volterra_{soft} f\big](a)\Big\vert
+        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+    \end{align*}
+    By assumption on $K_{soft}(a,a')$
+
+    \begin{align*}
+         \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\, |d\zeta|\\
+         &=C |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\Lambda |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\, dt\\
+         &=C |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\, dt\\
+         &= C \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)} |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|}
+    \end{align*}
+    where the product of Gamma functions is well-defined.
+
+    We conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \volterra_{soft} f\big](a)\Big\vert$ is uniformly bounded in $\Omega$. 
+\end{proof}
+
 \subsection{Finding spaces where $\volterra$ is a contraction}
@@
 %------------------------------------------------------------------------
+
+%\subsection{The prototypical function $f_0$}
+
 \color{SteelBlue}

### 2023-07-27 reg-sing-volterra.tex
Work on setting and results; add level-1 ODE example

@@
 
-% hat tip TeX.SE user marsupilam - https://tex.stackexchange.com/a/351570/6934
-%%\tikzfading[
-%%  name=radial,
-%%  inner color=transparent!0,
-%%  outer color=transparent!100
-%%]
 % hat tip TeX.SE user Andrew Stacey
@@
 %   https://tex.stackexchange.com/questions/82425/tikz-radial-shading-of-a-ring#comment176908_82503
-\pgfdeclareradialshading{infinifade}{\pgfpointorigin}{%
+\pgfdeclareradialshading{radialedge}{\pgfpointorigin}{%
   color(0bp)=(transparent!0);
@@
 }
-\pgfdeclarefading{infinity}{\pgfuseshading{infinifade}}%
+\pgfdeclarefading{radial edge}{\pgfuseshading{radialedge}}%
 
@@
 \newtheorem{prop}{Proposition}
+\newtheorem{lem}{Lemma}
 \newtheorem{thm}{Theorem}
 \newtheorem{rmk}{Remark}
+\newtheorem{lemma}{Lemma}
 
-% format lists
-\setlist[itemize]{leftmargin=15mm}
+% list formatting
+\setlist[itemize]{leftmargin=24mm, rightmargin=12mm}
 \makeatletter
@@
 \newcommand{\cond}[1]{\item[(\textsc{#1})]\protected@edef\@currentlabel{\textsc{#1}}}
+\newcommand{\condconst}[2]{\item[($\text{\textsc{#1}} \mid #2$)]\protected@edef\@currentlabel{$\text{\textsc{#1}} \mid #2$}}
 \makeatother
@@
 If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
-\subsection{Setting}
+\subsection{Setting}\label{setting}
 \subsubsection{The domain}\label{setting:domain}
@@
 \newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=infinity]
+\fill[violet!20, bezier bounding box, path fading=radial edge]
   (-\spill, -\spill) (\spill, \spill)
@@
 Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
-\[ \hardker(a, a') = \frac{q(a')}{p(a)}, \]
+\[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
 where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
-\[ -\frac{\tau}{\zeta(a)} - \hardker(a, a') \]
+\[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.
@@
 \begin{itemize}
-\cond{slow}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
+%%\item[($\text{\textsc{slow}} \mid \lambda_0$)]
+\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
 \begin{align*}
-\left|\frac{1}{p}\right| & \le e^{\lambda_p |\zeta|} &
+\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
 \left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
 \end{align*}
-outside some neighborhood of $\zeta = 0$ in $\Omega$. Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
+outside some neighborhood of $\zeta = 0$ in $\Omega$.
+Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
+The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
 \end{itemize}
@@
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-\subsubsection{The perturbed operator}
+\subsubsection{The perturbed operator}\label{setting:perturbed}
+\color{RoyalBlue}
+We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel, but does have a smoothing effect that counteracts the singularity of $\hardpart$.
+To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$.
+This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
+
+Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$.
+We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $p(a)^{-1}$ does, but we won't allow any sharper singularity.
+We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:slow} on $p$ and $q$.
+Altogether, we'll require:
+\begin{itemize}
+\condconst{diag}{\epsilon, \lambda}\label{cond:eps-lambda} We have
+\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda|\zeta(a)-\zeta(a')|}\]
+over all $a, a' \in \domain$.
+\end{itemize}
+\color{black}
+
+Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$.
+In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.
+
+For some of our results, we need to keep $k_\text{ext}$ under control at two different regimes: close to the point $\zeta=0$ and far toward infinity.
+In the former case, we require $k_\text{extra}$ to grow as $|\zeta|^{\epsilon-1}$ for some positive constant $\epsilon$; in the latter, we require $k_\text{ext}$ to be exponentially bounded
+\begin{itemize}
+\condconst{bounds}{\epsilon, \lambda}%%\label{cond:eps-lambda} (remove line break)
+for every $a,a'\in\Omega$
+\[ \big| k_\text{extra} (a, a') \big|\le C_{k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\lambda|\zeta(a)-\zeta(a')|}\]
+\end{itemize}
+
+Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$.
+Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
 \subsection{Main results}
@@
 %%\end{defn}
-\begin{thm}
-For the regular singular Volterra equation
+\begin{thm}\label{thm:basic_volterra}
+For a regular singular Volterra equation
 \[ f = \hardpart f \]
-given by an operator of the kind described in Section~\ref{setting:basic}, we have the {\em prototype solution}
+involving the kind of operator described in Section~\ref{setting:basic}, we have the {\em prototype solution}
 \begin{equation}\label{eqn:test_solution}
@@
 
-The size $|f_0|$ goes like $|\zeta|^{\tau-1}$ as $\zeta$ goes to $0$. More precisely, as $|\zeta|$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
-
-If $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}, then $f_0$ is uniformly of exponential type $\lambda$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
-In light of the behavior at $\zeta = 0$ described above, this tells us that for every $\Lambda > \lambda$, the solution $f_0$ belongs to the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
 \end{thm}
 \begin{thm}
-\textcolor{DarkTurquoise}{Existence and uniqueness for deformed operator}
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}.
+Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
+In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
 \end{thm}
+\begin{thm}\label{thm:perturbed_volterra}
+\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
+Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
+\[ f = \Big[\hardpart +\softpart \Big] f + g \]
+given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.
+\end{thm}
+
 \textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
@@
 %%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
-\section{\textcolor{orange}{[Proof of main results]}}
-\subsection{Overview}
-\color{ForestGreen}
-\begin{align*}
-f & = \volterra f \\
-f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
-f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
-f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
-f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
-\end{align*}
-Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
-\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
-\color{black}
-\subsection{Solving the basic \textcolor{orange}{[prototype]} equation}
-\subsubsection{Construction}
+
+\section{Construction and regularity of the prototype solution}
+
+\subsection{Construction}\label{sec:construction}
 
@@
    \end{equation}
-is a solution of the Volterra equation $\volterra_{proto} f_0=f_0$. We call $f_0$ a prototype solution.  
+is a solution of the Volterra equation $\hardpart f_0=f_0$. We call $f_0$ a prototype solution.  
 \end{prop}
@@
 \begin{proof}
-    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
+    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = - \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
     \begin{align*}
-        \big[\volterra_{proto}f_0\big](a) &= \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
-        &= \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
-        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
+        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
+        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
+        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
         &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
@@
         \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
-        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
-        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}+\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
+        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
+        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
     \end{align*}
@@
 \end{align*}
- which ends the proof of the claim. We deduce that $\volterra_{proto} f_0=f_0 $. 
+ which ends the proof of the claim. We deduce that $\hardpart  f_0=f_0 $. 
 \end{proof}
 
-\subsubsection{Asymptotics}
+\subsection{Asymptotics}\label{sec:asymptotics}
 
@@
   \begin{equation}\label{eqn:limit_h1}
-      \Big\vert\frac{q(a')}{p(a)}+\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
+      \Big\vert\frac{q(a')}{p(a)}\textcolor{magenta}{-}\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
   \end{equation}
@@
       \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
-      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} +\frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
+      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} \textcolor{magenta}{-} \frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
       &\leq \varepsilon \frac{\delta}{2} + \tau \log \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert
@@
           |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert \\
-          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|}  \, e^{c_p|\zeta(a)|}\exp\left[\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-c_p) |\zeta(a)|} \exp\Big[(\lambda-c_p) |\zeta(a)-\zeta(b)| \Big]
+          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
       \end{align*}
@@
 
-\subsubsection{Image under $\softpart$}
+\section{Existence and uniqueness of solutions of the perturbed equation}
+
+\subsection{Image under $\softpart$}\label{sec:image under soft_part}
 
 \begin{prop}
-    Assuming \textcolor{orange}{[bound K soft]}, namely 
-    \begin{equation}
-        |K_{soft}(a,a')|\leq C \frac{|\zeta(a)-\zeta{a'}|^{\epsilon}}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta(a')|}
-    \end{equation}
-    for every $a, a'\in\Omega$, the Volterra operator $\volterra_{soft}$ maps continuously $\singexp{\sigma}{\Lambda}(\Omega)$ to $\singexp{\sigma+\epsilon,}{\Lambda}(\Omega)$, for $\Lambda,\epsilon>0$ and $\sigma>-1$.
+   The Volterra operator $\softpart$ maps continuously $\singexp{\sigma}{\Lambda}(\Omega)$ to $\singexp{\sigma+\epsilon,}{\Lambda}(\Omega)$, for $\Lambda,\epsilon>0$ and $\sigma>-1$.
 \end{prop}
@@
     \begin{align*}
-        |\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \volterra_{soft} f\big](a)\Big\vert
-        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |f| \, |d\zeta| \\
-        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+        |\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
+        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
     \end{align*}
-    By assumption on $K_{soft}(a,a')$
+    By assumption on $k_\text{extra}(a,a')$
 
     \begin{align*}
-         \int_{\zeta=0}^a |K_{soft}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\, |d\zeta|\\
+         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\, |d\zeta|\\
          &=C |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\Lambda |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\, dt\\
@@
 
-    We conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \volterra_{soft} f\big](a)\Big\vert$ is uniformly bounded in $\Omega$. 
+    We conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\Omega$. 
 \end{proof}
 
-\subsection{Finding spaces where $\volterra$ is a contraction}
+\subsection{Finding spaces where $\volterra$ is a contraction}\label{sec:V is a contraction}
 \subsubsection{Overview}
@@
 This completes our proof of Proposition~\ref{get-contraction}.
+
+\section{A motivating example}
+%\color{black}
+%\section{\textcolor{orange}{[Proof of main results]}}
+\subsection{Overview}
+
+We can apply the theory of regular singular Volterra operators to the study of the so-called \textit{level 1 ODE}, which have an irregular singularity at $\infty$.
+In particular, we can built a frame of analytic solutions in the frequency domain studying solutions of an integral equation in the position domain.
+The latter is an example of regular singular Volterra equations we introduced above.
+
+\subsubsection{Level $1$ ODE}
+
+Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
+\begin{equation}\label{eqn:level 1 ode}
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
+\end{equation}
+
+\begin{itemize}
+\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
+such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
+\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
+\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
+\end{itemize}
+
+Equations of the form \eqref{eqn:level 1 ode} were named by Ecalle of \textit{level $1$} (see \cite[Section 2.1]{EcalleIII}).
+For instance, the modified Bessel equation is of level $1$, and we study its solutions explicitly in {\tt borel-regularity}.
+
+\subsection{The Laplace transform}
+
+Let $\mathcal{E}_{\alpha}^{\theta}$ \textcolor{orange}{[replace with a function space from this paper]} be the space of functions that are subexponential on $\Gamma_{\alpha}^{\theta}$, integrable at the starting point $\zeta=\alpha$, and locally integrable throughout.
+
+The Laplace transform $\laplace_{\zeta, \alpha}^{\theta} $ maps functions in $\mathcal{E}_{\zeta,\alpha}$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$ ~\cite[Section 5.6]{diverg-resurg-i}.
+It is defined by the formula
+
+\begin{equation}\label{laplace:int} 
+    \laplace_{\zeta, \alpha}^{\theta} f := \int_{\Gamma_{\alpha}^\theta} e^{-z\zeta} f\, d\zeta
+\end{equation}
+
+where $z$ is the frequency function and $\Gamma_\alpha^\theta$ is the ray that leaves $\alpha$ at angle $\theta$.
+
+\subsubsection{Action on integral operators}\label{L-int-op}
+%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
+%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $B$.
+
+It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
+We'll use the {\em Riemann-Liouville} convention.
+
+%For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} := \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+
+%The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+%\begin{align*}
+%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+%\end{align*}
+
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \mathcal{E}_\zeta$ and
+\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
+for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\begin{equation}%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\end{equation}
+for all integers $n \ge 0$.
+
+\subsection{Going to the position domain}
+
+By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain
+
+\begin{lemma}
+ For every $j=1,...,d$, let $\hat{P}_j$ be the Volterra operator
+
+\begin{equation}\label{P-hat_j}
+\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+\end{equation}
+
+If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$, defined for a suitable direction $\theta_j$, is a solution of $\mathcal{P}\Psi_j=0$.
+\end{lemma}
+
+\begin{proof}
+Using the properties of the Laplace transform,
+
+    \begin{align*}
+        \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
+    \end{align*}
+\end{proof}
+
+\begin{thm}\label{thm:general_volterra}
+    In the setting of \S \ref{setting}, we consider a Volterra operator 
+    \[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
+    where $\mathcal{R}$ is an integral kernel operator
+\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
+and $k$ is a holomorphic function on $\Omega^2$, and $\frac{ k(a, \cdot)}{p(a)}$ satisfies  Condition~\eqref{cond:eps-lambda}.
+
+When the constant $\Lambda \geq \lambda$ \textcolor{magenta}{[check]}, the regular singular Volterra equation
+\[ \mathcal{P}f = 0 \]
+has a unique solution in the affine subspace
+\[ f_0 + \singexp{\tau-1+\epsilon}{\Lambda}(\Omega) \]
+of the function space $\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, defined in Section~\ref{fn-spaces}.
+The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda}(\Omega)$.
+\end{thm}
+
+\begin{proof}
+The proof of Theorem \ref{thm:general_volterra} is built on Theorem \ref{thm:basic_volterra} and Theorem \ref{thm:perturbed_volterra}: indeed $\varphi$ is a solution of $\mathcal{P} \varphi=0$ if and only if
+
+\begin{align*}
+    -p(a)\varphi= \int_{\zeta=0}^a q \, \varphi \, d\zeta + \int_{\zeta=0}^a k(a,\cdot)  \, \varphi \, d\zeta
+\end{align*}
+
+hence, setting $\big[\softpart \varphi\big](a)=-\int_{\zeta=0}^a \frac{k(a,\cdot)}{p(a)} \, \varphi \,  d\zeta $, it becomes equivalent to
+
+\begin{align}\label{eqn:volterra}
+    \varphi = \hardpart \varphi + \softpart \varphi
+\end{align}
+
+%\textcolor{magenta}{[we have to change the definition of $k_\text{basic}$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
+
+Notice that $\softpart$ is of the type introduced in \S \ref{setting:perturbed}, namely its kernel is holomorphic and satisfies the Condition \eqref{cond:eps-lambda}.
+Now by Theorem \ref{thm:basic_volterra} (proved in \S \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$, hence we make the following \textit{ansatz}
+
+\[ \varphi= f_0 + f\]
+
+with $f\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get
+
+\begin{align*}
+    f_0 + f & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f \\
+f_0 + f & = f_0 + \softpart \,f_0 + \volterra f \\
+f & = \softpart \,f_0 + \volterra f
+\end{align*}
+
+Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f$ of the affine-linear map
+
+\[ \varphi \mapsto \softpart\,f_0 + \volterra \varphi. \]
+
+This follows by Theorem \ref{thm:perturbed_volterra}.
+\end{proof}
+
+%\color{ForestGreen}
+%\begin{align*}
+%f & = \volterra f \\
+%f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
+%f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
+%f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
+%f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
+%\end{align*}
+%Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
+%\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
+
 %%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
@@
 Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
+
+\color{black}
+
+\bibliographystyle{plain}
+\bibliography{airy-resurgence}
+
 \end{document}

### 2023-07-27 reg-sing-volterra.tex
Drop copy of original argument

@@
 
-By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain
+By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain.
 
@@
 %\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
-
-%%Let's again integrate along a straight path, where the fact that $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$ allows us to combine the exponential factors in our bound:
-%%\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
-\]
-%%This time, we'll use the parameterization $\zeta = s \frac{\zeta(a)}{|\zeta(a)|}$, with $s \in (0, |\zeta(a)|]$:
-%%\begin{align*}
-%%|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^{|\zeta(a)|} \left(\frac{s}{|\zeta(a)|}\right)^{\rho-1}\,e^{-(\Lambda - \lambda)(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
-%%\end{align*}
-%------------------------------------------------------------------------
-
-%\subsection{The prototypical function $f_0$}
-
-\color{SteelBlue}
-\section{Integro-differential equations {[from {\tt airy-resurgence}]}}
-\textcolor{DarkTurquoise}{\textbf{Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}}
-\subsection{Existence of solutions}
-\subsubsection{Algebraic integral operators}
-Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
-We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
-\begin{align*}
-\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
-\phi & \mapsto \zeta^{-\sigma} \phi
-\end{align*}
-is an isometry. More generally,
-\begin{align*}
-\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
-f & \mapsto \zeta^{-\delta} f
-\end{align*}
-is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$.
-This reduces to the previous statement when $\rho = 0$.
-For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
-Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
-
-Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
-For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
-
-We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
-\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
-where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
-The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
-Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
-That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
-
-For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure.
-The square of a density is a Riemannian metric.
-Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
-The bound
-\begin{align*}
-\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |\zeta^\rho f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
-& \le \|f\|_{\infty, \rho} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
-\end{align*}
-holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_{\infty, \rho}. \]
-so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
-\subsubsection{The example of fractional integrals}
-Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
-The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
-It follows that
-\begin{align*}
-\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
-& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
-& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = B(-\lambda,\,1-\rho).
-\end{align*}
-The beta function $B$ can be written more explicitly as
-\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
-Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
-\subsubsection{Fractional integral equations near a regular singular point}\label{frac_int_exist}
-\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
-
-Consider an integral operator $\mathcal{J}$ of the form
-\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
-where:
-\begin{itemize}
-\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
-\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
-\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
-\item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
-\end{itemize}
-Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough.
-We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.
-
-We want to solve the equation $\mathcal{J}f = 0$.
-Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-When $\epsilon$ is small enough that $\Lambda \subset (-\infty, -1 - \epsilon]$, we'll see that we can always find such a solution, as long as we're willing to shrink $\Omega$.
-In fact, there's exactly one such solution.
-\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}
-
-Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
-We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.
-
-Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
-\begin{alignat*}{2}
-p & = p'_0 \zeta &\;+\;& \tilde{p} \\
-q & = q_0 &\;+\;& \tilde{q}
-\end{alignat*}
-with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
-\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
-with
-\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
-For any $\tau \in (0, \infty)$,
-\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Setting $\tau = -q_0 / p'_0$ makes the first term vanish, leaving
-\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Then the equation $\mathcal{J}f = 0$ becomes
-\begin{align}
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \nonumber \\
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
--p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
-\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f}.
-\label{fixed-pt}
-\end{align}
-
-\color{Indigo}
-\begin{center}
-\begin{tikzcd}[column sep=25mm, row sep=2mm]
-& & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^{1-\epsilon}"'] \\
-& & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
-& & & \holoL{\infty, \rho}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-1-\epsilon-\lambda}"'] \\
-& & & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 1-\rho) = \frac{1}{1-\rho}}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\zeta^{-1}", "\|\zeta^{-1}\|_{\infty, 1} = 1"'] & \holoL{\infty, \rho}(\Omega) \\
-\end{tikzcd}
-\end{center}
-\color{SteelBlue}
-
-From \textbf{[our previous discussion]}, we can work out that
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
-\end{align*}
-and
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau-\epsilon}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\end{align*}
-Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
-\begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
-\end{align}
-and
-\begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\label{bound:perturb}
-\end{align}
-We can also see that
-\begin{align}
-\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \nonumber \\
-\|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
-\end{align}
-
-Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
-\begin{align*}
-\mathcal{A} & = \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \\
-b & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1}
-\end{align*}
-Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
-We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
-
-An affine map is a contraction if and only if its linear part is a contraction.
-We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$.
-Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
-Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
-
-\color{black}
-
 \bibliographystyle{plain}

### 2023-07-27 reg-sing-volterra.tex
Remove old version of main result
We'll remember this ponderous, unreadable statement fondly.

@@
 \end{thm}
-
-\textcolor{DarkTurquoise}{The result below might not be stated perfectly, but it gives at least a rough sense of what I expect.
-It's an improved version of the result stated in Section~\ref{frac_int_exist}, which is copied from {\tt airy-resurgence}.
-Note that {\tt airy-resurgence} uses the opposite sign convention for the parameter $\sigma$ in $\holoL{\infty, \sigma}$.}
-\color{RoyalBlue}
-\begin{thm}
-Let $\Omega$ be an acute-angled open sector around $\zeta = 0$ in the complex plane.
-\textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.} Over $\Omega$, consider a Volterra operator
-\[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
-where
-\begin{itemize}
-\item $p$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
-\begin{itemize}
-\item a simple zero at $\zeta = 0$,
-\item no zeros in $\Omega$ (as the next condition implies), and
-\item a positive lower bound $C_p |z|^d \le |p|$;
-\end{itemize}
-\item $q$ is a holomorphic function on $\Omega$ that extends holomorphically over $\zeta = 0$, with
-\begin{itemize}
-\item an upper bound $|q| \le C_q |z|^{d-1}$; and
-\end{itemize}
-\item $\mathcal{R}$ is an integral kernel operator
-\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
-where $k$ is a holomorphic function on $\Omega^2$, with
-\begin{itemize}
-\item an exponential upper bound $k(a, a') \le C_k e^{A|\zeta(a) - \zeta(a')|}$,
-\item \textcolor{orange}{[bound K soft]} \[ | k (a, a') |\le \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\Lambda|\zeta(a)-\zeta(a')|}\]
-\end{itemize}
-\end{itemize}
-Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$, and let $\tau = q_0 / p_1$.
-
-For any $\epsilon > 0$, when the constant $\Lambda > A$ is large enough, the regular singular Volterra equation
-\[ \mathcal{P}f = 0 \]
-has a unique solution in the affine subspace
-\[ \zeta^{\tau-1} + \holoL{\infty, \tau-1+\epsilon}_\Lambda(\Omega) \]
-of the function space $\holoL{\infty, \tau-1}_\Lambda(\Omega)$, defined in Section~\ref{fn-spaces}.
-\end{thm}
-\color{black}
 %%\begin{thm}

### 2023-07-28 reg-sing-volterra.tex
Add motivating example
Also work on regularity result for prototype solution, add conditions to
propositions, and add some references.

@@
 \newtheorem{prop}{Proposition}
-\newtheorem{lem}{Lemma}
+\newtheorem{lemma}{Lemma}
 \newtheorem{thm}{Theorem}
 \newtheorem{rmk}{Remark}
-\newtheorem{lemma}{Lemma}
 
@@
 If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
+
 \subsection{Setting}\label{setting}
@@
 \[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
-where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means that for some constant $\tau$---the {\em residue} of the singularity---the difference
+where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
+\begin{itemize}
+\condconst{sing}{\tau}\label{cond:sing} For some constant $\tau$---the {\em residue} of the singularity---the difference
 \[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
-is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$. We'll assume that $\tau$ is real and positive.
+is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
+\end{itemize}
+We'll assume that $\tau$ is real and positive.
 
@@
 \end{verify}
-For some of our results, we'll also need to keep $|p|$ and $|q|$ under control as $|\zeta|$ goes to infinity.
+For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
 \begin{itemize}
-%%\item[($\text{\textsc{slow}} \mid \lambda_0$)]
 \condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
@@
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+\begin{itemize}
+\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
+\[ \big| \hardker(a, a') \big| \textcolor{magenta}{\lesssim} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
+\end{itemize}
 \subsubsection{The perturbed operator}\label{setting:perturbed}
-\color{RoyalBlue}
-We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel, but does have a smoothing effect that counteracts the singularity of $\hardpart$.
+We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
 To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$.
@@
 Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$.
-We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $p(a)^{-1}$ does, but we won't allow any sharper singularity.
-We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:slow} on $p$ and $q$.
+We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity.
+We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we'll require:
 \begin{itemize}
-\condconst{diag}{\epsilon, \lambda}\label{cond:eps-lambda} We have
-\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda|\zeta(a)-\zeta(a')|}\]
+\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
+\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
 \end{itemize}
-\color{black}
-
+Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.
+\color{RoyalBlue}
 Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$.
@@
 Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
+\color{black}
 \subsection{Main results}
@@
 \begin{thm}\label{thm:basic_volterra}
-For a regular singular Volterra equation
+\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}.
+Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
 \[ f = \hardpart f \]
-involving the kind of operator described in Section~\ref{setting:basic}, we have the {\em prototype solution}
+have the {\em prototype solution}
 \begin{equation}\label{eqn:test_solution}
@@
 
-The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to $0$. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
+The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
 \end{thm}
-\begin{thm}
-Suppose $\hardpart$ satisfies Condition~\eqref{cond:slow} from Section~\ref{setting:basic}.
-Then the solution $f_0$ from Theorem~\ref{thm:basic_volterra} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
+\begin{proof}
+Section~\ref{sec:proto-construction-regularity}.
+Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} shows that it scales as desired as $\zeta$ goes to zero.
+\end{proof}
+\begin{thm}\label{thm:proto-growth}
+\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}.
+Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}.
+Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
 In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
 \end{thm}
-\begin{thm}\label{thm:perturbed_volterra}
-\textcolor{DarkTurquoise}{Existence and uniqueness for perturbed operator}
+\begin{lemma}\label{thm:perturbed_volterra}
 Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
@@
 given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.
+\end{lemma}
+
+\begin{thm}\label{thm:general_volterra}
+    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
+Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}.
+Then the Volterra equation
+    \[f = \left[ \hardpart + \softpart \right] f\]
+    admits a unique solution in the affine subspace
+\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
+of the function space $\singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$).
+The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
 \end{thm}
@@
 %%\end{thm}
+
+\subsection{Acknowledgements}
+
+This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
+
+We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
@@
 Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}.
-The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}\textcolor{orange}{[Luecking \& Rubel]}.
+The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
 
@@
 %%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
+\section{Solving holomorphic Volterra equations}
+\subsection{Overview}
+\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
 
-\section{Construction and regularity of the prototype solution}
+\subsubsection{Construction}\label{sec:construction}
 
-\subsection{Construction}\label{sec:construction}
-
-\begin{prop}
+\begin{prop}\label{prop:construction}
     Let $b\in\Omega$, the function 
@@
 \begin{proof}
-    Let $\Psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \Psi_0 = - \frac{q}{p} \Psi_0 d\zeta $. Hence, for every $a\in\Omega$ 
+    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
     \begin{align*}
         \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
-        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\Psi_0 d\zeta \\
-        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \Psi_0 d\zeta\\
-        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\Psi_0  \\
+        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
+        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
+        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
     \end{align*}
-    Now we claim $\lim_{a\to 0}\Psi_0(a)=0$: in fact,
+    \textcolor{orange}{Bring the proof of Proposition~\ref{prop:asymptotic at zero} in here.
+Prove Proposition~\ref{prop:asymptotic at zero} by noting that our argument that $\lim_{\zeta(a) \to 0} \psi_0(a) = 0$ actually proves something stronger.}
+    \color{RoyalBlue}
+    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact,
     \begin{align*}
@@
     \end{align*}
-    and by \textcolor{orange}{[limit assumption]}
+    and by Condition \eqref{cond:sing}
 \begin{align*}
@@
 \end{align*}
- which ends the proof of the claim. We deduce that $\hardpart  f_0=f_0 $. 
+ which ends the proof of the claim.\color{black} We deduce that $\hardpart  f_0=f_0$. 
 \end{proof}
 
-\subsection{Asymptotics}\label{sec:asymptotics}
+\subsubsection{Regularity}\label{sec:asymptotics}
 
-\begin{prop}
-    Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}
-
+\begin{prop}\label{prop:asymptotic at zero}
+    \textcolor{orange}{Assume $\domain$ satisfies Condition~\eqref{cond:star}.} Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}
 \end{prop}
@@
 \begin{proof}
-    We study separately the case when $\zeta(a)$ is close to the origin and far from the origin.  
-\begin{itemize}
-    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \textcolor{orange}{[limit assumption]} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+Choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
 \begin{equation}\label{eqn:limit_h1}
@@
 \begin{align*}
-      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{p}{q}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
+-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
+& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
+\end{align*}
+Exponentiating both sides, we see that
+\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+The exponential factor is bounded between $\exp[-\varepsilon\big(\tfrac{3}{2} \delta\big)]$ and $\exp[\varepsilon\big(\tfrac{3}{2} \delta\big)]$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
+\textcolor{orange}{We get $\delta$ in the last step because it should be possible to get from $b$ to $a$ by first going toward $\zeta = 0$, using a path of length at most $\tfrac{1}{2} \delta$, and then going outward again, using a path of length at most $\delta$.}
+
+\textcolor{OrangeRed}{Add argument about $p(b)/p(a)$ factor.}
+\end{proof}
+
+\begin{rmk}
+    Proposition \ref{prop:construction} and Proposition \ref{prop:asymptotic at zero} together prove Theorem \ref{thm:basic_volterra}. 
+\end{rmk}
+
+\begin{prop}\label{prop:asymptotic at infinity}
+    \textcolor{orange}{Assume $\domain$ satisfies Condition \eqref{cond:star}} and let $b\in\domain$.
+Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
+Then the prototype solution $f_0$ constructed in {\em Proposition \ref{prop:construction}} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+\end{prop}
+
+\begin{rmk}
+    {\em Proposition \ref{prop:asymptotic at infinity}} is an equivalent formulation of {\em Theorem \ref{thm:proto-growth}}.
+\end{rmk}
+
+\begin{proof}
+
+We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
+
+\[   |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
+\]
+
+Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$.
+Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.
+
+In particular, 
+      \begin{align*}
+          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
+          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
+      \end{align*}
+   which is bounded because $|\zeta(a)|>\delta$.
+
+\end{proof}
+
+\color{RoyalBlue}
+
+\begin{proof}
+    \begin{itemize}
+    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \em Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+ \begin{equation}
+      \Big\vert\frac{q(a')}{p(a)}\textcolor{magenta}{-}\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
+  \end{equation}
+ % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
+ Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
+  \begin{align*}
+      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{q}{p}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
       &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} \textcolor{magenta}{-} \frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
@@
 \end{proof}
+\color{black}
 
-\section{Existence and uniqueness of solutions of the perturbed equation}
+\subsection{How $\softpart$ perturbs the prototype solution \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
 
-\subsection{Image under $\softpart$}\label{sec:image under soft_part}
-
-\begin{prop}
-   The Volterra operator $\softpart$ maps continuously $\singexp{\sigma}{\Lambda}(\Omega)$ to $\singexp{\sigma+\epsilon,}{\Lambda}(\Omega)$, for $\Lambda,\epsilon>0$ and $\sigma>-1$.
+\begin{prop}\label{prop:smoothing}
+Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
+\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\epsilon}{\Lambda}(\Omega) \]
+continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
 \end{prop}
@@
     \begin{align*}
-        |\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |f| \, |d\zeta| \\
-        &\leq |\zeta(a)|^{-\sigma-\epsilon}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
     \end{align*}
-    By assumption on $k_\text{extra}(a,a')$
-
+    By Condition~\eqref{cond:eps-lambda},
     \begin{align*}
-         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\Lambda |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\, |d\zeta|\\
-         &=C |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\Lambda |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\, dt\\
-         &=C |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\, dt\\
-         &= C \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)} |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|}
+         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+         &=C |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+         &=C |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+         &\le C |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
     \end{align*}
-    where the product of Gamma functions is well-defined.
-
-    We conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\Omega$. 
+    The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
+    \[ \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
+\]
+    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
+    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
+    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
 \end{proof}
 
-\subsection{Finding spaces where $\volterra$ is a contraction}\label{sec:V is a contraction}
+\subsection{Showing that $\volterra$ shrinks perturbations \\ \textit{(toward Lemma~\ref{thm:perturbed_volterra})}}\label{sec:V is a contraction}
 \subsubsection{Overview}
-In this section, we'll prove the following proposition.
-\begin{prop}\label{get-contraction}
+In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
+
+\begin{prop}\label{prop:get-contraction}
+Assume $\hardpart$ satisfies {\em Condition \eqref{cond:sing}} and {\em Condition \eqref{cond:diag-basic}}.
+Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
 For each $\rho \in (\tau, \tau + \epsilon)$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
@@
 \begin{rmk}
-For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda$, and may require $\Lambda \gg \lambda$.
+For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
 \end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By \textcolor{orange}{[limit property]}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
 \begin{equation}\label{near-limit}
@@
 Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
-Since we set $\sigma < \rho$, this proves Proposition~\ref{get-contraction}.
+Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
 \subsubsection{First steps}\label{first-steps}
@@
 \end{align*}
-Since we set $\sigma < \rho$, this brings us halfway to proving Proposition~\ref{get-contraction}.
+Since we set $\sigma < \rho$, this brings us halfway to proving Proposition~\ref{prop:get-contraction}.
 \subsubsection{Away from the origin}\label{far-bound}
-Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from \textcolor{orange}{[difference bound]} that we can find a constant $M$ for which
-\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
+Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$.
+We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that \textcolor{orange}{[by nudging the exponent a little bigger than $\lambda_\Delta$---change this in what follows]} we can find a constant $M$ for which
+\[ |k(a, \cdot)| \le M e^{\lambda_\Delta |\zeta(a) - \zeta|} \]
 for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda_\Delta |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
-& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda_\Delta |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)|\zeta(a)|(1 - t)}\;dt.
 \end{align*}
-Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows. Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt. \]
+Let's set $\Lambda > \lambda_\Delta$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
+Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt. \]
 
-We can make this bound as small as we want by increasing $\Lambda$.
+We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
 To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and of the integration separately.
@@
 \begin{align*}
-\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda - \lambda)R} \int_0^{1/5} t^{\rho-1}\;dt \\
-& = e^{-\frac{4}{5}(\Lambda - \lambda)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda - \lambda_\Delta)R} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda - \lambda_\Delta)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
 \end{align*}
@@
 \begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)R(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)R} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)R}.
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda_\Delta)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda_\Delta)R} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda_\Delta)R}.
 \end{align*}
@@
 
-We now know that by setting $\Lambda > \lambda$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
-This completes our proof of Proposition~\ref{get-contraction}.
+We now know that by setting $\Lambda > \lambda_\Delta$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+This completes our proof of Proposition~\ref{prop:get-contraction}.
+\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}
+
+\begin{proof}
+
+%\textcolor{magenta}{[we have to change the definition of $k_\text{basic}$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
+
+By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$, hence we make the following \textit{ansatz}
+
+\[ \varphi= f_0 + f\]
+
+with $f\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation $\varphi= \volterra \varphi$ we get
+
+\begin{align*}
+    f_0 + f & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f \\
+f_0 + f & = f_0 + \softpart \,f_0 + \volterra f \\
+f & = \softpart \,f_0 + \volterra f
+\end{align*}
+
+Therefore, solving the equation $ \varphi = \volterra \varphi$ is equivalent to finding a fixed point $\varphi$ of the affine-linear map
+
+\[ \varphi \mapsto \softpart\,f_0 + \volterra \varphi. \]
+
+This follows by Theorem \ref{thm:perturbed_volterra}.
+\end{proof}
 
@@
 We can apply the theory of regular singular Volterra operators to the study of the so-called \textit{level 1 ODE}, which have an irregular singularity at $\infty$.
-In particular, we can built a frame of analytic solutions in the frequency domain studying solutions of an integral equation in the position domain.
-The latter is an example of regular singular Volterra equations we introduced above.
+In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain.
+The latter is an example of the regular singular Volterra equations we introduced above.
 
-\subsubsection{Level $1$ ODE}
+\subsubsection{Level $1$ ODE}\label{sec:level 1 ODE}
 
@@
 
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
-such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
-\end{itemize}
+\begin{enumerate}
+\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e. such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; 
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
+\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, for every $|z|>A$
+\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j}. \]
+\end{enumerate}
 
@@
 
-Let $\mathcal{E}_{\alpha}^{\theta}$ \textcolor{orange}{[replace with a function space from this paper]} be the space of functions that are subexponential on $\Gamma_{\alpha}^{\theta}$, integrable at the starting point $\zeta=\alpha$, and locally integrable throughout.
+%Let $\mathcal{E}_{\alpha}^{\theta}$ \textcolor{orange}{[replace with a function space from this paper]} be the space of functions that are subexponential on $\Gamma_{\alpha}^{\theta}$, integrable at the starting point $\zeta=\alpha$, and locally integrable throughout.
 
-The Laplace transform $\laplace_{\zeta, \alpha}^{\theta} $ maps functions in $\mathcal{E}_{\zeta,\alpha}$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$ ~\cite[Section 5.6]{diverg-resurg-i}.
+Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$.
+If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\lambda>0$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$ ~\cite[Section 5.6]{diverg-resurg-i}.
 It is defined by the formula
@@
 \begin{equation}\label{laplace:int} 
-    \laplace_{\zeta, \alpha}^{\theta} f := \int_{\Gamma_{\alpha}^\theta} e^{-z\zeta} f\, d\zeta
+    \laplace_{\zeta, a}^{\theta} f := \int_{\Gamma_{a}^\theta} e^{-z\zeta} f\, d\zeta
 \end{equation}
 
-where $z$ is the frequency function and $\Gamma_\alpha^\theta$ is the ray that leaves $\alpha$ at angle $\theta$.
+where $z$ is the frequency function.
 
@@
 %%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $\Omega$.
 
@@
 \begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\fracderiv{\lambda}{\zeta}{a}\,\fracderiv{\mu}{\zeta}{a} & = \fracderiv{\lambda+\mu}{\zeta}{a} & \lambda, \mu \in (-\infty, 0),
 \end{align*}
@@
 
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
+%For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\mu}{\zeta}{0}$ are defined by composing $\fracderiv{\mu-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
 We'll use the {\em Riemann-Liouville} convention.
@@
 %For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} := \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+%\[ \fracderiv{n+\mu}{\zeta}{\alpha} := \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\mu-1}{\zeta}{\alpha}. \]
 
@@
 
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ and
+\[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
 for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
 \end{equation}
-for all integers $n \ge 0$.
+for all integers $n \ge 0$ and suitable direction $\theta$.
 
@@
 \begin{equation}\label{P-hat_j}
-\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
 \end{equation}
 
-If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$, defined for a suitable direction $\theta_j$, is a solution of $\mathcal{P}\Psi_j=0$.
+If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta}\hat{\psi}_j$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_j=0$.
+By suitable direction we mean that the ray $\Gamma_{\alpha_j}^\theta$ must be contained in the domain $\Omega_j$\footnote{We use the shorthand notation $\Omega_j$ for $\Omega_{\alpha_j}$}.
 \end{lemma}
@@
         &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
         &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
@@
 
-\begin{thm}\label{thm:general_volterra}
-    In the setting of \S \ref{setting}, we consider a Volterra operator 
-    \[ \mathcal{P} = p + \partial^{-1} \circ q + \mathcal{R}, \]
-    where $\mathcal{R}$ is an integral kernel operator
-\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta, \]
-and $k$ is a holomorphic function on $\Omega^2$, and $\frac{ k(a, \cdot)}{p(a)}$ satisfies  Condition~\eqref{cond:eps-lambda}.
+We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_j$ admits a unique solution $\hat{\psi}_j$ in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
 
-When the constant $\Lambda \geq \lambda$ \textcolor{magenta}{[check]}, the regular singular Volterra equation
-\[ \mathcal{P}f = 0 \]
-has a unique solution in the affine subspace
-\[ f_0 + \singexp{\tau-1+\epsilon}{\Lambda}(\Omega) \]
-of the function space $\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, defined in Section~\ref{fn-spaces}.
-The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda}(\Omega)$.
+\begin{thm}\label{thm:example}
+    There exists a unique solution of $\hat{P}_j\hat{\psi}_j=0$ such that 
+    \[\hat{\psi}_j = f_{0,j}+ f_j\]
+
+    where $f_{0,j}$ scales like $\zeta^{\tau_j-1}$ as $\zeta$ goes to $\alpha_j$ and $f_j\in\singexp{\tau_j}{\Lambda}(\Omega_j)$ for $\Lambda$ ``big enough'' (meaning $\Lambda>2A$, and we may require $\Lambda \gg 2A$).
+The result holds for every $j=1,...,d$.
 \end{thm}
@@
 \begin{proof}
-The proof of Theorem \ref{thm:general_volterra} is built on Theorem \ref{thm:basic_volterra} and Theorem \ref{thm:perturbed_volterra}: indeed $\varphi$ is a solution of $\mathcal{P} \varphi=0$ if and only if
+First of all, we rewrite $\hat{P}_j\varphi=0$ as $\varphi = \volterra_j \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
 
 \begin{align*}
-    -p(a)\varphi= \int_{\zeta=0}^a q \, \varphi \, d\zeta + \int_{\zeta=0}^a k(a,\cdot)  \, \varphi \, d\zeta
+    -P(-\zeta)\varphi= \int_{\zeta=\alpha_j}^\zeta Q(-\zeta')  \, \varphi \, d\zeta' + \int_{\zeta=\alpha_j}^\zeta k_R(\zeta,\cdot)  \, \varphi \, d\zeta
 \end{align*}
+with \[k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, (\zeta(a)-\zeta(a'))^{j+1} \, (-\zeta(a'))^r\]
 
-hence, setting $\big[\softpart \varphi\big](a)=-\int_{\zeta=0}^a \frac{k(a,\cdot)}{p(a)} \, \varphi \,  d\zeta $, it becomes equivalent to
+is equivalent to
 
-\begin{align}\label{eqn:volterra}
-    \varphi = \hardpart \varphi + \softpart \varphi
+\begin{align}
+   \nonumber \varphi& =-\int_{\zeta=\alpha_j}^\zeta \frac{Q(-\zeta')}{P(-\zeta)}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha_j}^\zeta \frac{k_R(\zeta,\cdot)}{P(-\zeta)}  \, \varphi \, d\zeta' \\
+   \nonumber \varphi& = \hardpart^j \, \varphi+ \softpart^j \, \varphi \\
+   \varphi &= \volterra^j \, \varphi
 \end{align}
 
-%\textcolor{magenta}{[we have to change the definition of $k_\text{basic}$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
-
-Notice that $\softpart$ is of the type introduced in \S \ref{setting:perturbed}, namely its kernel is holomorphic and satisfies the Condition \eqref{cond:eps-lambda}.
-Now by Theorem \ref{thm:basic_volterra} (proved in \S \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$, hence we make the following \textit{ansatz}
-
-\[ \varphi= f_0 + f\]
-
-with $f\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get
+Notice that $\hardpart^j$ is holomorphic and separable, while $\softpart^j$ is holomorphic and non-separable.
+In addition, $\hardpart^j$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $P$ and $Q$ at $-\alpha_j$
 
 \begin{align*}
-    f_0 + f & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f \\
-f_0 + f & = f_0 + \softpart \,f_0 + \volterra f \\
-f & = \softpart \,f_0 + \volterra f
+    -\frac{Q(-\zeta')}{P(-\zeta)}&=-\frac{Q(-\alpha_j)+q_1(\zeta'-\alpha_j)+q_2 (\zeta'-\alpha_j)^2+...}{P'(-\alpha_j)(-\zeta+\alpha_j)+ p_2 (\zeta-\alpha_j)^2+p_3(\zeta-\alpha_j)^3+...}\\
+    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+ p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}\\
+    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}
 \end{align*}
+hence setting $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}$, we find
 
-Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f$ of the affine-linear map
+\begin{equation*}
+    -\frac{Q(-\zeta')}{P(-\zeta)}-\frac{\tau_j}{\zeta-\alpha_j}
+\end{equation*}
+is bounded as $\zeta'$ and $\zeta$ approach $\alpha_j$. \textcolor{orange}{[Is there a nice way to write the prototype solution?]}
 
-\[ \varphi \mapsto \softpart\,f_0 + \volterra \varphi. \]
+Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^j$ satisfies the required assumptions.
 
-This follows by Theorem \ref{thm:perturbed_volterra}.
+\begin{enumerate}
+    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:slow}: by assumption $P$ and $Q$ are polynomials, and $Q$ has degree less that $P$.
+Hence for $\zeta$ outside some neighbourhood $U$ of $\zeta=\alpha_j$
+\begin{align*}
+    \sup_U \Big\vert \frac{1}{P}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{Q}{P}\Big\vert =:\lambda_\text{ration} 
+\end{align*}
+    and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
+    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:diag-basic}: in fact $P$ and $Q$ are polynomials and $Q$ has degree less than $P$, hence their ratio is exponentially bounded if $a,a'$ far from $\alpha_j$.
+In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
+    \item[$\bullet$]  $\softpart^j$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,
+
+    \begin{align*}
+        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta-\zeta'|^j}{P(-\zeta)}|\zeta'|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta-\zeta'|^{j+1}}{|P(-\zeta)|}|\zeta'|^r \\
+        & =C |\zeta-\zeta'| \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|P(-\zeta)|}\,  e^{A |\zeta-\zeta'|}\\
+        &=C |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|Q(-\zeta')|} \, e^{A |\zeta-\zeta'|}\\
+        &\leq C_1 |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \,  e^{A |\zeta-\zeta'|}
+    \end{align*}
+now we notice that $\Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert$ is bounded for $\zeta,\zeta'$ far from $\alpha_j$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
+If $\zeta,\zeta'$ are close to $\alpha_j$ we can use Condition \eqref{cond:sing}
+
+\[    \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert  \leq \Big\vert \frac{Q(-\zeta')}{P(-\zeta)} -\frac{\tau_j}{\zeta-\alpha_j}\Big\vert + \frac{\tau_j}{|\zeta-\alpha_j|}\leq C +  \frac{\tau_j}{|\zeta-\alpha_j|} \]
+
+We conclude that
+
+\[\left\vert \frac{k_R(\zeta,\zeta')}{P(-\zeta)}\right\vert\leq C_2 \frac{|\zeta-\zeta'|}{|\zeta-\alpha_j|}\, e^{2A |\zeta-\zeta'} \]
+
+and $\epsilon=1$.
+
+\end{enumerate}
+
 \end{proof}

### 2023-07-28 reg-sing-volterra.tex
Add to-do list
Make a lot of other revisions too.

@@
 \newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
+\newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
 \newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
@@
 \newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
 
@@
 \maketitle
+\begin{brainstorm}
+\item \textit{(Aaron)} State Lemma~\ref{thm:perturbed_volterra} just the way we want it.
+\item Finish introduction
+\begin{itemize}
+\item \textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.
+\end{itemize}
+\item \textit{(Veronica)} Say in Section~\ref{setting:perturbed} that $\volterra = \hardpart + \softpart$ and write arguments we need for bounds on whole kernel (for example, in Equation~\ref{near-limit}.
+\item \textit{(Veronica)} Review old blue text in Section~\ref{setting:perturbed} and decide whether we want to keep any of it. Can drop unilaterally.
+\item Revise stuff related to proof of main results.
+\begin{itemize}
+        \item \textit{(Aaron)} Add proofs of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra} to Section~\ref{sec:existence and uniqueness}
+        \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.
+        \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}).
+        \item \textbf{(Aaron)} Confirm again that removed $\tau+\epsilon$ upper bound on $\rho$ was unnecessary.
+\end{itemize}
+\item Revise text around main results.
+\begin{itemize}
+    \item Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.
+    \item \textit{(Veronica)} Convert ``proof'' blocks to plain prose after main results.
+\end{itemize}
+\item \textbf{(Veronica)} Edit statement of Theorem~\ref{thm:example}
+\begin{itemize}
+    \item Edit or remove statements about making $\Lambda$ big enough
+    \item Figure out how to clean up $Q(-\zeta')$ business
+\end{itemize}
+\item Start finalizing notation for the two parts of the operator and the two parts of the solution.
+\begin{itemize}
+    \item Choose subscripts or decorations to tell things apart in equations.
+    \item Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.
+\end{itemize}
+\item \textbf{(Aaron)} Read through Section~\ref{sec:example}.
+\item \textbf{(Veronica)} Consider revising notation for roots.
+\begin{itemize}
+\item ``$P$ is a monic degree-$d$ polynomial with only simple zeros;''
+\item ``$Q$ is a degree-$(d-1)$ polynomial, and $Q(-\alpha) \neq 0$ for for every zero $-\alpha$ of $P$;''---or even say it without formulas.
+\end{itemize}
+\item \textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.
+\item Work on acknowledgements
+\begin{itemize}
+\item \textbf{(Aaron)} Add people Aaron had conversations with
+\item \textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).
+\end{itemize}
+\item Reconsider using $\lesssim$ (but still leaning not to)
+\begin{itemize}
+    \item \textbf{(Aaron)} As an example, show how we could rewrite the argument in proof of Proposition~\ref{prop:asymptotic at infinity} with $\lesssim$.
+\end{itemize}
+\end{brainstorm}
 \section{Introduction}
@@
 If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
-
+\begin{brainstorm}
+    \item \textit{Brainstorm motivation ideas here\ldots}
+\end{brainstorm}
 \subsection{Setting}\label{setting}
@@
 Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
-For some of our results, we'll need an extra condition on $\domain$:
+We also assume:
 \begin{itemize}
@@
 Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
-\[ \hardker(a, a') = \textcolor{magenta}{-} \frac{q(a')}{p(a)}, \]
+\[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
 where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
 \begin{itemize}
-\condconst{sing}{\tau}\label{cond:sing} For some constant $\tau$---the {\em residue} of the singularity---the difference
-\[ \hardker(a, a') \textcolor{magenta}{-} \frac{\tau}{\zeta(a)} \]
+\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
+\[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
@@
 \[ \big| \hardker(a, a') \big| \textcolor{magenta}{\lesssim} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
-outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
+over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
+%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
 \end{itemize}
@@
 \begin{thm}\label{thm:basic_volterra}
-\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}.
 Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
@@
 
-The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
+The magnitude $|f_0|$ is bounded by a constant multiple of $|\zeta|^{\tau-1}$ near $\zeta = 0$.
+
+%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
 \end{thm}
@@
 \end{proof}
+\begin{rmk}
+If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.
+
+\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
+\end{rmk}
 \begin{thm}\label{thm:proto-growth}
-\textcolor{orange}{[Assume the domain $\domain$ satisfies {\em Condition \eqref{cond:star}}] from Section \ref{setting:domain}}.
-Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}.
-Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly'']}.
+Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}.
+Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly''---for example, by mentioning the discussion in Section~\ref{sec:fn-space-defs}, including the footnote]}.
 In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
@@
 \[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
-of the function space $\singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$).
+of the function space $\singexp{\tau-1}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$).
 The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
@@
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
-\subsection{Weighted holomorphic $L^\infty$ spaces}
+\subsection{Weighted holomorphic $L^\infty$ spaces}\label{sec:fn-space-defs}
 Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
@@
 Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.
-They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
 With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
@@
 
-\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}
+\subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
 \begin{prop}
@@
 \end{prop}
-
 \begin{proof}
+By definition,
+\[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
+The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
 \begin{align*}
-        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,  e^{-\Lambda |\zeta|}\, |f|\\
-        &= \sup_{\Omega} e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,e^{-(\Lambda-\Lambda') |\zeta|}\,|f|\\
-        &\leq \sup_\Omega e^{-\Lambda'|\zeta|}\,|\zeta|^{-\sigma}\,|f|\\
-        &=\|f\|_{\sigma,\Lambda'}
+\|f\|_{\sigma,\Lambda} & \leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
+&=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
+&\leq \|f\|_{\sigma,\Lambda'}.
 \end{align*}
+In the last step, we use the assumption that $\Lambda' \le \Lambda$.
 \end{proof}
-\color{OrangeRed}
-\begin{proof}
-    \begin{align*}
-        \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|\\
-        &\leq \sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\,|\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
-        &=\sup_{\Omega} e^{-(\Lambda-\Lambda') |\zeta|}\,\|f\|_{\sigma, \Lambda'}\\
-        &\leq \|f\|_{\sigma,\Lambda'}
-    \end{align*}
-\end{proof}
-\color{black}
-
+As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.
+Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type.
+Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
 \begin{prop}
@@
 \subsection{Overview}
+\begin{brainstorm}
+\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
+\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
+\begin{itemize}
+\item Link to subsections during description.
+\end{itemize}
+\item Rough sketch of proof story:
+\begin{itemize}
+    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
+    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\lambda_0}$.
+    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in.
+    \item Use the contraction mapping theorem to prove Lemma~\ref{thm:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
+\end{itemize}
+\end{brainstorm}
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 \begin{prop}\label{prop:construction}
-    Let $b\in\Omega$, the function 
+    The function 
     \begin{equation}%%\label{eqn:test_solution}
@@
    \end{equation}
-is a solution of the Volterra equation $\hardpart f_0=f_0$. We call $f_0$ a prototype solution.  
+is a solution of the Volterra equation $\hardpart f_0=f_0$, for some $b\in\Omega$. We call $f_0$ a prototype solution.  
 \end{prop}
@@
     \end{align*}
-    \textcolor{orange}{Bring the proof of Proposition~\ref{prop:asymptotic at zero} in here.
-Prove Proposition~\ref{prop:asymptotic at zero} by noting that our argument that $\lim_{\zeta(a) \to 0} \psi_0(a) = 0$ actually proves something stronger.}
-    \color{RoyalBlue}
-    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact,
-    \begin{align*}
-        \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert&\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\Big \vert\, |d\zeta|\right)\\
-        &\leq \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta| + \tau \int_b^a\frac{|d\zeta|}{|\zeta|} \right)\\
-        &\Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\left(\int_b^a \Big\vert\frac{q}{p}\textcolor{magenta}{-}\frac{\tau}{\zeta}\Big \vert\, |d\zeta|  \right)
-    \end{align*}
-    and by Condition \eqref{cond:sing}
-\begin{align*}
-     \Big\vert \exp\left(-\int_b^a\frac{q}{p}d\zeta\right) \Big\vert& \leq \Big\vert \frac{\zeta(a)}{\zeta(b)}\Big\vert^{\tau} \, \exp\Big(c |\zeta(a)-\zeta(b)|\Big)\\
-     &\leq C |\zeta(a)|^\tau e^{c|\zeta(a)|}
-\end{align*}
- which ends the proof of the claim.\color{black} We deduce that $\hardpart  f_0=f_0$. 
-\end{proof}
 
-\subsubsection{Regularity}\label{sec:asymptotics}
-
-\begin{prop}\label{prop:asymptotic at zero}
-    \textcolor{orange}{Assume $\domain$ satisfies Condition~\eqref{cond:star}.} Let $b\in\Omega$ and $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $f_0\in\singexp{\tau-1}{\lambda}(\Omega)$ with $\tau$ and $\lambda$ defined as in {\tt setting}
-\end{prop}
-
-\begin{proof}
-Choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact, choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
 \begin{equation}\label{eqn:limit_h1}
-\Big\vert\frac{q(a')}{p(a)}\textcolor{magenta}{-}\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
+\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
 \end{equation}
@@
 \[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-The exponential factor is bounded between $\exp[-\varepsilon\big(\tfrac{3}{2} \delta\big)]$ and $\exp[\varepsilon\big(\tfrac{3}{2} \delta\big)]$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
-\textcolor{orange}{We get $\delta$ in the last step because it should be possible to get from $b$ to $a$ by first going toward $\zeta = 0$, using a path of length at most $\tfrac{1}{2} \delta$, and then going outward again, using a path of length at most $\delta$.}
+The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
+We deduce that $\hardpart  f_0=f_0$.
+\end{proof}
 
-\textcolor{OrangeRed}{Add argument about $p(b)/p(a)$ factor.}
+\subsubsection{Regularity}\label{sec:asymptotics}
+
+\begin{prop}\label{prop:asymptotic at zero}
+    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
+\end{prop}
+
+\begin{proof}
+The proof follows the argument we use at the end of the proof of proposition \ref{prop:construction}.
+In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
+
+\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+
+is bounded by $C_1 \, |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big)$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
+
+\begin{align*}
+|f_0| & \leq C_1 |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big) \left\vert  \frac{p(b)}{p(a)}\right\vert \\
+& = C_2 |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
+& \leq C_3 |\zeta(a)|^{\tau-1}.
+\end{align*}
+The last step uses Condition~\eqref{cond:sing}. 
 \end{proof}
@@
 
+%In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$
+
 \begin{prop}\label{prop:asymptotic at infinity}
-    \textcolor{orange}{Assume $\domain$ satisfies Condition \eqref{cond:star}} and let $b\in\domain$.
+    Let $b\in\domain$.
 Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
@@
 
-\begin{proof}
-
+\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
 We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
@@
 \end{proof}
-
-\color{RoyalBlue}
-
-\begin{proof}
-    \begin{itemize}
-    \item \textbf{$\zeta(a)$ close to the origin.} We choose $\varepsilon>0$, then by \em Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
- \begin{equation}
-      \Big\vert\frac{q(a')}{p(a)}\textcolor{magenta}{-}\frac{\tau}{\zeta(a)}\Big\vert<\varepsilon
-  \end{equation}
- % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
- Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
-  \begin{align*}
-      \left\vert\int_{\zeta(b)}^{\zeta(a)} \frac{q}{p}d\zeta\right\vert&\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p}\Big\vert \, |d\zeta| \\
-      &\leq \int_{\zeta(b)}^{\zeta(a)} \Big\vert \frac{q}{p} \textcolor{magenta}{-} \frac{\tau}{\zeta}\Big\vert \, |d\zeta| +\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{\tau}{\zeta}\Big\vert \, |d\zeta| \\
-      &\leq \varepsilon \frac{\delta}{2} + \tau \log \Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert
-        \end{align*}
-
- Now we look at $f_0$: let $b'$ such that $|\zeta(b')|\leq \delta$ and $q(b')\neq 0$
-  \begin{align*}
-      \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert &\leq \Big\vert\frac{p(b)}{q(b')}\Big\vert \Big\vert\zeta(a)\frac{q(b')}{p(a)}\Big\vert \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[\left\vert\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta \right\vert\right]\\
-      &\leq C_1(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \exp\left[ \tau \log\Big\vert\frac{\zeta(a)}{\zeta(b)}\Big\vert+ \varepsilon \frac{\delta}{2}\right]\\
-      &\leq C_2(\delta) \Big\vert \zeta(a)\Big\vert^{-1} \Big\vert\zeta(a)\Big\vert^{\tau}   
-      \end{align*}
-
-Finally, we get  
-  \begin{align*}
-      |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
-  \end{align*}
-      \item \textbf{$\zeta(a)$ far from the origin.} Using assumptions \textcolor{orange}{[two bounds assumption]}
-
-      \begin{align*}
-          |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{\zeta(b)}^{\zeta(a)}\frac{q}{p} d\zeta\right]\right\vert \\
-          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{\zeta(b)}^{\zeta(a)} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
-      \end{align*}
-   which is bounded because $|\zeta(a)|>\delta$. 
-\end{itemize}
-
-\end{proof}
-\color{black}
 
@@
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and of the integration separately.
+To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration separately.
 At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
@@
 \end{align*}
-\textcolor{ForestGreen}{[Consider just writing ``const.'' instead of explicit constants.]}
 
-We now know that by setting $\Lambda > \lambda_\Delta$ and then increasing $\Lambda$ as needed, we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+We now know that by setting $\Lambda > \lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
 This completes our proof of Proposition~\ref{prop:get-contraction}.
-\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}
+\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
 
@@
 
-\section{A motivating example}
+\section{A motivating example}\label{sec:example}
 %\color{black}
@@
 \begin{enumerate}
-\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e. such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; 
+\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with only simple zeros; 
 \item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
@@
 If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta}\hat{\psi}_j$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_j=0$.
-By suitable direction we mean that the ray $\Gamma_{\alpha_j}^\theta$ must be contained in the domain $\Omega_j$\footnote{We use the shorthand notation $\Omega_j$ for $\Omega_{\alpha_j}$}.
+By suitable direction we mean that the ray $\Gamma_{\alpha_j}^\theta$ must be contained in the domain $\Omega_j$.
+\footnote{We use the shorthand notation $\Omega_j$ for $\Omega_{\alpha_j}$} In particular, $\Omega_j$ does not contain the tubolar neighbourhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}.
 \end{lemma}
@@
 
-We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_j$ admits a unique solution $\hat{\psi}_j$ in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
+We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_j$ admits a unique solution $\hat{\psi}_j$ %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
 
@@
 \begin{proof}
+\textcolor{orange}{One option: ``Let $p = P(-\zeta)$ and $q = Q(-\zeta)$, as written in commented-out line. Another: $P(-\zeta(a)) = \int_{\zeta = \alpha}^{\zeta(a)}$}
+
 First of all, we rewrite $\hat{P}_j\varphi=0$ as $\varphi = \volterra_j \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
@@
 \end{equation*}
-is bounded as $\zeta'$ and $\zeta$ approach $\alpha_j$. \textcolor{orange}{[Is there a nice way to write the prototype solution?]}
+is bounded as $\zeta'$ and $\zeta$ approach $\alpha_j$.
 

### 2023-07-29 reg-sing-volterra.tex
Discuss exponential-type functions, rather than L^1, in the introduction
Sketch a proof that the Laplace transform turns functions of exponential type
into to holomorphic functions, even when the integral is improper at zero. Show
how complex extensions of the position domain arise naturally from Volterra
operators with real-analytic kernels.

@@
 \subsection{Motivation}\label{motivation}
-In its most basic form, the Laplace transform $\laplace$ turns $L^1$ functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic\begin{verify}\footnote{\begin{verify}Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
+Write $z$ in terms of its real and imaginary parts as $x + iy$.
+Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it.
+Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.\end{verify}}\end{verify} functions of a complex ``frequency'' variable $z$.
 Through identities like
@@
 
-If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically. \textbf{[...]}
+If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel.
+This extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain.
+\textcolor{orange}{[...]}
+
+\textcolor{RoyalBlue}{If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically.}
 \begin{brainstorm}

### 2023-07-29 reg-sing-volterra.tex
Veronica add changes according to the gray items of brainstorming

@@
 \item \textit{(Veronica)} Say in Section~\ref{setting:perturbed} that $\volterra = \hardpart + \softpart$ and write arguments we need for bounds on whole kernel (for example, in Equation~\ref{near-limit}.
+\color{gray}
 \item \textit{(Veronica)} Review old blue text in Section~\ref{setting:perturbed} and decide whether we want to keep any of it. Can drop unilaterally. 
+\color{violet}
 \item Revise stuff related to proof of main results.
@@
     \item Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.
+    \color{gray}
     \item \textit{(Veronica)} Convert ``proof'' blocks to plain prose after main results. 
 \end{itemize}
+\color{gray}
 \item \textbf{(Veronica)} Edit statement of Theorem~\ref{thm:example} 
@@
 \end{itemize}
+\color{violet}
 \item Start finalizing notation for the two parts of the operator and the two parts of the solution.
@@
 \item \textbf{(Aaron)} Read through Section~\ref{sec:example}.
+\color{gray}
 \item \textbf{(Veronica)} Consider revising notation for roots. 
@@
 \end{itemize}
+\color{violet}
 \item \textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.
@@
 Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.
-\color{RoyalBlue}
-Our ultimate goal is the study of certain integral equations where the integral kernel is a perturbation of $k_\text{basic}$.
-In particular, we are interested in holomorphic Volterra operators $\volterra=\hardpart+\softpart$, hence the kernel $k_\text{extra}$ of $\softpart$ is a holomorphic function on $\Omega^2$.
 
-For some of our results, we need to keep $k_\text{ext}$ under control at two different regimes: close to the point $\zeta=0$ and far toward infinity.
-In the former case, we require $k_\text{extra}$ to grow as $|\zeta|^{\epsilon-1}$ for some positive constant $\epsilon$; in the latter, we require $k_\text{ext}$ to be exponentially bounded
-\begin{itemize}
-\condconst{bounds}{\epsilon, \lambda}%%\label{cond:eps-lambda} (remove line break)
-for every $a,a'\in\Omega$
-\[ \big| k_\text{extra} (a, a') \big|\le C_{k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} e^{\lambda|\zeta(a)-\zeta(a')|}\]
-\end{itemize}
-
-Notice that if $a$ and $a'$ are close to $\zeta=0$, then the exponential factor is bounded and $k_\text{extra}(a,a')$ goes like $|\zeta(a)|^{\epsilon-1}$.
-Conversely, as $|\zeta(a)|$ goes to infinity (far from $\zeta=0$), the exponential term will be dominant because the polynomial growth of $|\zeta(a)|^{\epsilon-\tau}$ can be bounded by $e^{|\zeta(a)|}$.
-\color{black}
 \subsection{Main results}
@@
 \end{thm}
-\begin{proof}
-Section~\ref{sec:proto-construction-regularity}.
-Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} shows that it scales as desired as $\zeta$ goes to zero.
-\end{proof}
+We'll prove this result in Section~\ref{sec:proto-construction-regularity}: by Proposition~\ref{prop:construction} we show that $f_0$ is a solution, and by Proposition~\ref{prop:asymptotic at zero} we show that it scales as desired as $\zeta$ goes to zero.
+
 \begin{rmk}
@@
 \end{thm}
+
+We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
+
 \begin{lemma}\label{thm:perturbed_volterra}
@@
 \end{lemma}
+
+We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction.
+Then the result follows by the contraction mapping theorem.
 
@@
 \end{thm}
+
+We'll prove this result in Sections~\ref{sec:existence and uniqueness}: by Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
+Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.
+
 %%\begin{thm}
@@
 \item[$\bullet$] $P$ is a monic degree-$d$ polynomial with only simple zeros; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and it does not vanish at the critical point of $P$;
 \item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, for every $|z|>A$
@@
 \begin{lemma}
- For every $j=1,...,d$, let $\hat{P}_j$ be the Volterra operator
+ For every root of $P$, let $\hat{P}_{\alpha}$ be the Volterra operator
 
 \begin{equation}\label{P-hat_j}
-\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
+\hat{P}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
 \end{equation}
 
-If $\hat{\psi}_j$ is a solution of $\hat{P}_j\hat{\psi}_j=0$ then its Laplace transform $\Psi_j:=\laplace_{\zeta,\alpha_j}^{\theta}\hat{\psi}_j$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_j=0$.
-By suitable direction we mean that the ray $\Gamma_{\alpha_j}^\theta$ must be contained in the domain $\Omega_j$.
-\footnote{We use the shorthand notation $\Omega_j$ for $\Omega_{\alpha_j}$} In particular, $\Omega_j$ does not contain the tubolar neighbourhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}.
+If $\hat{\psi}_\alpha$ is a solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
+By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$.
+\footnote{The domain $\Omega_{\alpha}$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}}.
 \end{lemma}
@@
     \begin{align*}
-        \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
+        \mathcal{P}\Psi_\alpha&=\mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha\\
+        &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
+        &=\laplace_{\zeta,\alpha}^{\theta}\hat{P}_\alpha\hat{\psi}_\alpha
     \end{align*}
@@
 
-We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_j$ admits a unique solution $\hat{\psi}_j$ %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
+We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$.
+%in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
 
 \begin{thm}\label{thm:example}
-    There exists a unique solution of $\hat{P}_j\hat{\psi}_j=0$ such that 
-    \[\hat{\psi}_j = f_{0,j}+ f_j\]
+    There exists a unique solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ such that 
+    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_\alpha\]
 
-    where $f_{0,j}$ scales like $\zeta^{\tau_j-1}$ as $\zeta$ goes to $\alpha_j$ and $f_j\in\singexp{\tau_j}{\Lambda}(\Omega_j)$ for $\Lambda$ ``big enough'' (meaning $\Lambda>2A$, and we may require $\Lambda \gg 2A$).
-The result holds for every $j=1,...,d$.
+    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\zeta(\alpha)$ and $f_\alpha\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+The result holds for every critical point of $P$.
 \end{thm}
@@
 \begin{proof}
-\textcolor{orange}{One option: ``Let $p = P(-\zeta)$ and $q = Q(-\zeta)$, as written in commented-out line. Another: $P(-\zeta(a)) = \int_{\zeta = \alpha}^{\zeta(a)}$}
+Let $p = P(-\zeta)$ and $q = Q(-\zeta)$ and let $\alpha$ be a simple root of $p$. Hence, by assumptions that $p(\zeta=\alpha)=0$, $p'(\zeta=\alpha)\neq 0$ and $q(\zeta=\alpha)\neq 0$.
 
-First of all, we rewrite $\hat{P}_j\varphi=0$ as $\varphi = \volterra_j \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
+First of all, we rewrite $\hat{P}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
 
 \begin{align*}
-    -P(-\zeta)\varphi= \int_{\zeta=\alpha_j}^\zeta Q(-\zeta')  \, \varphi \, d\zeta' + \int_{\zeta=\alpha_j}^\zeta k_R(\zeta,\cdot)  \, \varphi \, d\zeta
+    -\big[ p\, \varphi \big](a)= \int_{\zeta=\alpha}^a q  \, \varphi \, d\zeta' + \int_{\zeta=\alpha}^a k_R(a,\cdot)  \, \varphi \, d\zeta
 \end{align*}
@@
 \begin{align}
-   \nonumber \varphi& =-\int_{\zeta=\alpha_j}^\zeta \frac{Q(-\zeta')}{P(-\zeta)}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha_j}^\zeta \frac{k_R(\zeta,\cdot)}{P(-\zeta)}  \, \varphi \, d\zeta' \\
-   \nonumber \varphi& = \hardpart^j \, \varphi+ \softpart^j \, \varphi \\
-   \varphi &= \volterra^j \, \varphi
+   \nonumber \varphi (a)& =-\int_{\zeta=\alpha}^a \frac{q}{p(\zeta(a))}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(\zeta(a))}  \, \varphi \, d\zeta' \\
+   \nonumber \varphi (a)& =\Big[ \hardpart^\alpha \, \varphi \Big](a)+ \Big[\softpart^\alpha \, \varphi\Big](a) \\
+   \varphi(a) &=\Big[ \volterra^j \, \varphi \Big](a)
 \end{align}
 
-Notice that $\hardpart^j$ is holomorphic and separable, while $\softpart^j$ is holomorphic and non-separable.
-In addition, $\hardpart^j$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $P$ and $Q$ at $-\alpha_j$
+Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable.
+In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ at $\alpha$
 
 \begin{align*}
-    -\frac{Q(-\zeta')}{P(-\zeta)}&=-\frac{Q(-\alpha_j)+q_1(\zeta'-\alpha_j)+q_2 (\zeta'-\alpha_j)^2+...}{P'(-\alpha_j)(-\zeta+\alpha_j)+ p_2 (\zeta-\alpha_j)^2+p_3(\zeta-\alpha_j)^3+...}\\
-    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+ p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}\\
-    &=\frac{Q(-\alpha_j)}{P'(-\alpha_j)(\zeta-\alpha_j)}\frac{1+q_1'(\zeta'-\alpha_j)+q_2' (\zeta'-\alpha_j)^2+...}{1+p_2' (\zeta-\alpha_j)+p_3'(\zeta-\alpha_j)^2+...}
+    -\frac{q}{p(\zeta(a))}&=-\frac{q(\zeta(\alpha))+c_1(\zeta'-\zeta(\alpha))+c_2 (\zeta'-\zeta(\alpha))^2+...}{-p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))+ b_2 (\zeta(a)-\zeta(\alpha))^2+b_3(\zeta(a)-\zeta(\alpha))^3+...}\\
+    &=\frac{q\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+ b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}\\
+    &=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}
 \end{align*}
-hence setting $\tau_j:=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}$, we find
+hence setting $\tau_\alpha:=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))}\neq 0$, we find
 
 \begin{equation*}
-    -\frac{Q(-\zeta')}{P(-\zeta)}-\frac{\tau_j}{\zeta-\alpha_j}
+    -\frac{q(\zeta(a'))}{p(\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}
 \end{equation*}
-is bounded as $\zeta'$ and $\zeta$ approach $\alpha_j$.
+is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\zeta(\alpha)$.
 
-Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^j$ satisfies the required assumptions.
+Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^\alpha$ satisfies the required assumptions.
 
 \begin{enumerate}
-    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:slow}: by assumption $P$ and $Q$ are polynomials, and $Q$ has degree less that $P$.
-Hence for $\zeta$ outside some neighbourhood $U$ of $\zeta=\alpha_j$
+    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$.
+Hence for $a$ outside some neighbourhood $U$ of $\alpha$
 \begin{align*}
-    \sup_U \Big\vert \frac{1}{P}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{Q}{P}\Big\vert =:\lambda_\text{ration} 
+    \sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
 \end{align*}
     and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
-    \item[$\bullet$] $\hardpart^j$ satisfies Condition \eqref{cond:diag-basic}: in fact $P$ and $Q$ are polynomials and $Q$ has degree less than $P$, hence their ratio is exponentially bounded if $a,a'$ far from $\alpha_j$.
+    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $a,a'$ are far from $\alpha$.
 In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
-    \item[$\bullet$]  $\softpart^j$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,
+    \item[$\bullet$]  $\softpart^\alpha$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,
 
     \begin{align*}
-        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta-\zeta'|^j}{P(-\zeta)}|\zeta'|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta-\zeta'|^{j+1}}{|P(-\zeta)|}|\zeta'|^r \\
-        & =C |\zeta-\zeta'| \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|P(-\zeta)|}\,  e^{A |\zeta-\zeta'|}\\
-        &=C |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|Q(-\zeta')|} \, e^{A |\zeta-\zeta'|}\\
-        &\leq C_1 |\zeta-\zeta'| \, \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert \,  e^{A |\zeta-\zeta'|}
+        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
+        & =C |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
+        &=C |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
+        &\leq C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
     \end{align*}
-now we notice that $\Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert$ is bounded for $\zeta,\zeta'$ far from $\alpha_j$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
-If $\zeta,\zeta'$ are close to $\alpha_j$ we can use Condition \eqref{cond:sing}
+now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
+If $a, a'$ are close to $\alpha$ we can use Condition \eqref{cond:sing}
 
-\[    \Big\vert \frac{Q(-\zeta')}{P(-\zeta)}\Big\vert  \leq \Big\vert \frac{Q(-\zeta')}{P(-\zeta)} -\frac{\tau_j}{\zeta-\alpha_j}\Big\vert + \frac{\tau_j}{|\zeta-\alpha_j|}\leq C +  \frac{\tau_j}{|\zeta-\alpha_j|} \]
+\[    \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert  \leq \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}\Big\vert + \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|} \]
 
@@
 
-\[\left\vert \frac{k_R(\zeta,\zeta')}{P(-\zeta)}\right\vert\leq C_2 \frac{|\zeta-\zeta'|}{|\zeta-\alpha_j|}\, e^{2A |\zeta-\zeta'} \]
+\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert\leq C_2 \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\zeta(\alpha)|}\, e^{2A |\zeta(a)-\zeta(a')} \]
 

### 2023-07-30 reg-sing-volterra.tex
Finish drafting introduction
Include older draft paragraphs in comments. Also, correct name alphabetization.

@@
 \newtheorem{rmk}{Remark}
+\newtheorem{cor}{Corollary}
 
@@
 \title{Regular singular Volterra equations on complex domains}
-\author{Aaron Fenyes and Veronica Fantini}
+\author{Veronica Fantini and Aaron Fenyes}
 \date{}
@@
 \item \textit{(Aaron)} State Lemma~\ref{thm:perturbed_volterra} just the way we want it.
-\item Finish introduction
+\item \textit{(Aaron)} Finish introduction
 \begin{itemize}
-\item \textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.
+\item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}
 \end{itemize}
+\color{gray}
 \item \textit{(Veronica)} Say in Section~\ref{setting:perturbed} that $\volterra = \hardpart + \softpart$ and write arguments we need for bounds on whole kernel (for example, in Equation~\ref{near-limit}.
@@
         \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.
+        \color{gray}
         \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}).
+\textcolor{green}{I added a Corollary to explicitly write how Proposition \ref{prop:smoothing} implies the regularity we want for $\softpart f_0$}
+        \color{violet}
         \item \textbf{(Aaron)} Confirm again that removed $\tau+\epsilon$ upper bound on $\rho$ was unnecessary.
@@
 \begin{itemize}
-    \item Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary. Change order as appropriate.
+    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary.
+Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{thm:perturbed_volterra} as a lemma.
+State it after Theorem~\ref{thm:general_volterra}.}
     \color{gray}
@@
 \begin{itemize}
-    \item Choose subscripts or decorations to tell things apart in equations.
+    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$.
+Same for $\hardker$ and $\softker$.
     \item Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.
@@
 \laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-z^{-\lambda} \laplace \varphi & = \laplace\,\fracderiv{-\lambda}{}{} \varphi,
+z^{-\lambda} \laplace \varphi & = \laplace\,\partial^{-\lambda} \varphi,
 \end{align*}
-where $\fracderiv{-\lambda}{}{}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.
 
-If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel.
-This extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain.
-\textcolor{orange}{[...]}
+Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
+Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino}}.
 
-\textcolor{RoyalBlue}{If we complexify the position variable $\zeta$, the functions on the position domain whose Laplace transforms satisfy a given differential equation will often extend holomorphically.}
-\begin{brainstorm}
-    \item \textit{Brainstorm motivation ideas here\ldots}
-\end{brainstorm}
+\textcolor{RoyalBlue}{A nice feature of the Laplace transform is that} Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
+In Section~\ref{sec:example}, we'll see this \textcolor{purple}{helpful} behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
+This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.
+\textcolor{RoyalBlue}{In Section~\ref{sec:example}, we'll see this behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical and not-so-classical examples like the modified Bessel equation; some cases of the equation describing the vibration modes of a beam \textcolor{orange}{[find citation]}, and---after a change of coordinate---the Airy, Airy-Lucas~\cite[Equation 3.2]{charbonnier22}, higher Airy~\cite[Equation 3.8]{charbonnier22}\cite{durugo_higher}, and generalized Airy equations \cite[Equation 9.13.31]{dlmf}.}
+
+From our experience with solving level 1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
+Let's say we've chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
+Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
+\begin{itemize}
+\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
+\item It's of exponential type, meaning that it's $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
+\end{itemize}
+These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
+The first condition also tells us that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
+%%\begin{itemize}
+%%\item They have singularities that look like $(\zeta - \alpha)^{\tau-1}$ with $\tau > 0$, where $\zeta$ is the position variable and $\zeta = \alpha$ is a place where the Volterra equation has a regular singularity.
+%%\item They're of exponential type.
+%%\item They grow slowly enough as $|\zeta| \to \infty$ to have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
+%%\end{itemize}
+%%Thanks to their mild singularities and moderate growth, these solutions have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
+%%This has led us to look for solutions of regular singular Volterra equations in the the function spaces defined in Section~\ref{fn-spaces}, which are designed to capture the properties above.
+\textcolor{orange}{[Describe existence and uniqueness result.]}
+
+Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
+We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+\textcolor{orange}{[Mention treatment of motivating example in Section~\ref{sec:example}.]}
+
+% -------------------------------------------
+
+%%If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel, which extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain.
+By analytically continuing the eigenfunctions of the Volterra operator around singularities in the position domain, you might discover hidden relationships between the eigenfunctions of the original differential operator.
+In its nicest cases, this phenomenon is called {\em resurgence} \textcolor{orange}{[cite]}.
+
 \subsection{Setting}\label{setting}
 \subsubsection{The domain}\label{setting:domain}
-Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
+Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
 Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
@@
 \condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
-\[ \big| \hardker(a, a') \big| \textcolor{magenta}{\lesssim} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+\[ \big| \hardker(a, a') \big| \leq \,  \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
@@
 \subsubsection{The perturbed operator}\label{setting:perturbed}
-We'll generalize $\hardpart$ by adding a perturbation $\softpart$ that doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
+
+Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
+The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
 To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$.
@@
 \condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
-\[ \big| k_\text{extra} (a, a') \big| \lesssim \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\[ \big| k_\text{extra} (a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
@@
 
-\subsection{Main results}
+Like $\hardker$, the combined kernel $k = \hardker + \softker$ of $\volterra$ grows in a controlled way when its arguments are near $\zeta = 0$, and when the difference between its arguments grows.
+We'll provide specific bounds in Section~\ref{sec:bounds on k}.
+
+\subsection{Main results}\label{sec:results}
 %%\begin{defn}\label{fin-order}
@@
 
-We'll prove this result in Sections~\ref{sec:existence and uniqueness}: by Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
+We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
 Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.
@@
     \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
-    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\lambda_0}$.
-    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in.
+    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
+    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
     \item Use the contraction mapping theorem to prove Lemma~\ref{thm:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
@@
 \end{brainstorm}
+\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
+ When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.
+Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
+
+\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]
+
+Then,
+
+\begin{align*}
+    |k(a,a')&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
+    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
+\end{align*}
+
+\textcolor{orange}{[edit to emphasize instead that we can make $\sigma - \tau$ arbitrarily small]} 
+The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small.
+We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
+
+Similarly, we can estimate the kernel $k$ far from $\zeta=0$.
+Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$
+
+\begin{align*}
+    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+\end{align*}
+Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
+
+\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+We deduce that
+
+\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.
+
+\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely
+
+\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}
+
+\begin{verify}
+    \begin{align*}
+        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
+        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
+        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
+    \end{align*}
+\end{verify}
+
+%notice that $\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon$ is bounded by a constant which depends on $|\zeta(a')|$ (and of course on $\delta$ and $\epsilon$)
+
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 \end{align*}
+
 The last step uses Condition~\eqref{cond:sing}. 
@@
           |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
-          &\leq C  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \leq C |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
+          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
       \end{align*}
@@
 \subsection{How $\softpart$ perturbs the prototype solution \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
+
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
 
@@
     \begin{align*}
-         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-         &=C |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-         &=C |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-         &\le C |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
+         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
     \end{align*}
     The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-    \[ \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
+    \[ \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
 \]
     Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
-    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
+    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
     we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
+\end{proof}
+
+\begin{cor}\label{cor:pertub_f0}
+    Let $f_0$ be the prototype solution in equation \eqref{eqn:test_solution}.
+If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
+\end{cor}
+\begin{proof}
+    Notice that since $\tau-1>-1$ the hypothesis of Proposition \ref{prop:smoothing} are satisfied. In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$. 
 \end{proof}
@@
 Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-For each $\rho \in (\tau, \tau + \epsilon)$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
+For each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
 \end{prop}
 \begin{rmk}
-For the argument we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
+For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
 \end{rmk}
@@
 \end{equation}
-for all $a, a' \in \near$.
+for all $a, a' \in \near$ (see Section \ref{sec:bounds on k}).
 By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$.
@@
 We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that \textcolor{orange}{[by nudging the exponent a little bigger than $\lambda_\Delta$---change this in what follows]} we can find a constant $M$ for which
-\[ |k(a, \cdot)| \le M e^{\lambda_\Delta |\zeta(a) - \zeta|} \]
-for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda_\Delta |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\[ |k(a, \cdot)| \le M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a) - \zeta|} \]
+for all $a \in \far$ (see Section \ref{sec:bounds on k}).
+Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument.
+Applying this bound, we learn that
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda_\Delta |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
-& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)|\zeta(a)|(1 - t)}\;dt.
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)|\zeta(a)|(1 - t)}\;dt.
 \end{align*}
@@
 Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt. \]
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt. \]
 
@@
 \begin{align*}
-\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda - \lambda_\Delta)R} \int_0^{1/5} t^{\rho-1}\;dt \\
-& = e^{-\frac{4}{5}(\Lambda - \lambda_\Delta)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
 \end{align*}
@@
 \begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda_\Delta)R(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda_\Delta)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda_\Delta)R} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda_\Delta)R}.
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}.
 \end{align*}
 
-We now know that by setting $\Lambda > \lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
 This completes our proof of Proposition~\ref{prop:get-contraction}.
@@
 
-\[ \varphi= f_0 + f\]
+\[ f= f_0 + f_\star\]
 
-with $f\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation $\varphi= \volterra \varphi$ we get
+with $f_\star\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation $\varphi= \volterra \varphi$ we get
 
 \begin{align*}
-    f_0 + f & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f \\
-f_0 + f & = f_0 + \softpart \,f_0 + \volterra f \\
-f & = \softpart \,f_0 + \volterra f
+    f_0 + f_\star & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f_\star \\
+f_0 + f_\star & = f_0 + \softpart \,f_0 + \volterra f_\star \\
+f_\star & = \softpart \,f_0 + \volterra f_\star
 \end{align*}
 
-Therefore, solving the equation $ \varphi = \volterra \varphi$ is equivalent to finding a fixed point $\varphi$ of the affine-linear map
+Therefore, solving the equation $ f = \volterra f$ is equivalent to finding a fixed point $f_\star$ of the affine-linear map
 
-\[ \varphi \mapsto \softpart\,f_0 + \volterra \varphi. \]
+\[ f_\star \mapsto \softpart\,f_0 + \volterra f_\star. \]
 
-This follows by Theorem \ref{thm:perturbed_volterra}.
+This follows by Lemma \ref{thm:perturbed_volterra}.
 \end{proof}
@@
 
-Equations of the form \eqref{eqn:level 1 ode} were named by Ecalle of \textit{level $1$} (see \cite[Section 2.1]{EcalleIII}).
+Equations of the form \eqref{eqn:level 1 ode} were called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}).
 For instance, the modified Bessel equation is of level $1$, and we study its solutions explicitly in {\tt borel-regularity}.
@@
     There exists a unique solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ such that 
-    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_\alpha\]
+    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
 
-    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\zeta(\alpha)$ and $f_\alpha\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The result holds for every critical point of $P$.
@@
 \begin{proof}
-Let $p = P(-\zeta)$ and $q = Q(-\zeta)$ and let $\alpha$ be a simple root of $p$. Hence, by assumptions that $p(\zeta=\alpha)=0$, $p'(\zeta=\alpha)\neq 0$ and $q(\zeta=\alpha)\neq 0$.
+Let $p = P(-\zeta)$ and $q = Q(-\zeta)$ and let $\alpha$ be a simple root of $p$. Hence, by assumptions that $p(\alpha)=0$, $p'(\alpha)\neq 0$ and $q(\alpha)\neq 0$.
 
@@
    \nonumber \varphi (a)& =\Big[ \hardpart^\alpha \, \varphi \Big](a)+ \Big[\softpart^\alpha \, \varphi\Big](a) \\
-   \varphi(a) &=\Big[ \volterra^j \, \varphi \Big](a)
+   \varphi(a) &=\Big[ \volterra^\alpha \, \varphi \Big](a)
 \end{align}
@@
 \begin{align*}
-    -\frac{q}{p(\zeta(a))}&=-\frac{q(\zeta(\alpha))+c_1(\zeta'-\zeta(\alpha))+c_2 (\zeta'-\zeta(\alpha))^2+...}{-p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))+ b_2 (\zeta(a)-\zeta(\alpha))^2+b_3(\zeta(a)-\zeta(\alpha))^3+...}\\
-    &=\frac{q\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+ b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}\\
-    &=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))(\zeta(a)-\zeta(\alpha))}\frac{1+c_1'(\zeta'-\zeta(\alpha))+c_2' (\zeta'-\zeta(\alpha))^2+...}{1+b_2' (\zeta(a)-\zeta(\alpha))+b_3'(\zeta(a)-\zeta(\alpha))^2+...}
+    -\frac{q}{p(\zeta(a))}&=-\frac{q(\alpha)+c_1(\zeta'-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-p'(\alpha)(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
+    &=\frac{q\alpha)}{p'(\alpha)(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
+    &=\frac{q(\alpha)}{p'(\alpha)(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
 \end{align*}
-hence setting $\tau_\alpha:=\frac{q(\zeta(\alpha))}{p'(\zeta(\alpha))}\neq 0$, we find
+hence setting $\tau_\alpha:=\frac{q(\alpha)}{p'(\alpha)}\neq 0$, we find
 
 \begin{equation*}
-    -\frac{q(\zeta(a'))}{p(\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}
+    -\frac{q(\zeta(a'))}{p(\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
 \end{equation*}
-is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\zeta(\alpha)$.
+is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
 
@@
     and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
-    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $a,a'$ are far from $\alpha$.
+    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$.
 In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
@@
     \begin{align*}
-        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
-        & =C |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
-        &=C |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
-        &\leq C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
+        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C_1 \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
+        & =C_1 |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
+        &=C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
+        &\leq C_2 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
     \end{align*}
 now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
-If $a, a'$ are close to $\alpha$ we can use Condition \eqref{cond:sing}
+If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}
 
-\[    \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert  \leq \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\zeta(\alpha)}\Big\vert + \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\zeta(\alpha)|} \]
+\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]
 
@@
 
-\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert\leq C_2 \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\zeta(\alpha)|}\, e^{2A |\zeta(a)-\zeta(a')} \]
+\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert\textcolor{magenta}{\lesssim} \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')} | \]
 

### 2023-08-01 reg-sing-volterra.tex
Fix the comments in orange

@@
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}.
-Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$ \textcolor{orange}{[explain what we mean by ``uniformly''---for example, by mentioning the discussion in Section~\ref{sec:fn-space-defs}, including the footnote]}.
-In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
+Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
 \end{thm}
@@
     admits a unique solution in the affine subspace
-\[ f_0 + \singexp{\tau-1+\epsilon}{{\Lambda}}(\Omega) \]
-of the function space $\singexp{\tau-1}{{\Lambda}}(\Omega)$, defined in Section~\ref{fn-spaces}, for $\Lambda$ ``big enough'' (meaning $\Lambda>\lambda_\Delta$, and we may require $\Lambda \gg \lambda_\Delta$).
+\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
+of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}.
 The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
@@
 Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.
+They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
 With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
@@
 
-\textcolor{orange}{[edit to emphasize instead that we can make $\sigma - \tau$ arbitrarily small]} 
 The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small.
@@
 \begin{rmk}
-    Proposition \ref{prop:construction} and Proposition \ref{prop:asymptotic at zero} together prove Theorem \ref{thm:basic_volterra}. 
+   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
 \end{rmk}
@@
 \subsubsection{Away from the origin}\label{far-bound}
-Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$.
-We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that \textcolor{orange}{[by nudging the exponent a little bigger than $\lambda_\Delta$---change this in what follows]} we can find a constant $M$ for which
+Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that we can find a constant $M$ for which
 \[ |k(a, \cdot)| \le M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a) - \zeta|} \]
@@
 
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
 
@@
 
-By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$, hence we make the following \textit{ansatz}
+By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$.
+Hence we can solve the Volterra equation
+
+\begin{equation}\label{eqn:volterra}
+    f = \volterra f
+\end{equation}
+
+by the following \textit{ansatz}
 
@@
 
-with $f_\star\in\singexp{\tau-1+\epsilon}{\lambda}(\Omega)$. Plugging-it in equation $\varphi= \volterra \varphi$ we get
+with $f_\star\in\singexpalg{\tau-1+\epsilon}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get
 
@@
 
-Therefore, solving the equation $ f = \volterra f$ is equivalent to finding a fixed point $f_\star$ of the affine-linear map
+Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f_\star$ of the affine-linear map
 
@@
 
-Equations of the form \eqref{eqn:level 1 ode} were called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}).
-For instance, the modified Bessel equation is of level $1$, and we study its solutions explicitly in {\tt borel-regularity}.
+Equations of the form \eqref{eqn:level 1 ode} are called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}).
+For instance, the modified Bessel equation is of level $1$, and we'll study its solutions explicitly in \cite{borel_reg}.
 

### 2023-08-01 exp-resurgence.tex
Version of the proof where we take the expansion of p/q
Fill in more details about regular singular Volterra equations
Describe setting, fill in reasoning about prototype solution, and show
inclusions between weighted holomorphic L-infinity spaces.
Drop draft text from intro

@@
 \usepackage{fancyhdr}
-\usepackage{xparse}
 \usepackage{enumitem}
+\usepackage[svgnames]{xcolor} %% for revisions
+\usepackage{xparse} %% for squiggly underlines
+\usepackage{tikz-cd} %% for term norm scratch work
+\usepackage{tikz}
 %\usepackage{eqnarray}
-%% colors
-\usepackage[svgnames]{xcolor}
+
 \let\Re\relax
@@
 \DeclareMathOperator{\Im}{Im}
+
+\usetikzlibrary{bbox}
+\usetikzlibrary{fadings}
+
+\pgfdeclareradialshading{radialedge}{\pgfpointorigin}{%
+  color(0bp)=(transparent!0);
+  color(20bp)=(transparent!0);
+  color(22bp)=(transparent!10);
+  color(24bp)=(transparent!90);
+  color(25bp)=(transparent!100)
+}
+\pgfdeclarefading{radial edge}{\pgfuseshading{radialedge}}%
+
+% function spaces
+\newcommand{\cont}{\mathcal{C}}
+\newcommand{\holo}{\mathcal{H}}
+\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
+\newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
 
@@
 
+% drafting environments
+\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+
 \title{Borel regularity for ODEs and thimble integrals}
@@
 and its constant multiples. As another example, you might rewrite the integral
-\color{DodgerBlue}
+\begin{verify}
     \[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
-\color{black}
+\end{verify}
+
 \[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
@@
 using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{DodgerBlue}
+
+\begin{verify}
     \begin{align*}
@@
 \end{align*}
-\color{black}
+\end{verify}
 
@@
 Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
@@
 The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
-Roughly speaking, Borel summation works well for problems with Borel regular solutions that stand out asymptotically \textcolor{magenta}{[this may need refining]}.
+Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.
 
@@
 \end{equation}
-where $f\colon X\to \mathbb{C}$ is a Morse function, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
 \end{enumerate}
@@
 such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$ for a small compact domain $\Omega\subset\C$. 
+\textcolor{red}{${\psi}_j=\zeta_j^{-\tau_j-1}+f_{j,\star}$} and $f_{j,\star}\in\singexpalg{\tau_j-1}(\Omega_j)$ for an open star-shaped domain $\Omega_j$ which avoids the other critical points (see the definition in Section \ref{setting-ODE}).
 \end{theorem}
@@
 \begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
+For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta}$ for some direction $\theta$.
 Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
@@
 
-\subsubsection{Why does Borel resummation work for thimbles integrals?}
-
-\color{DarkBlue}
-\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
-His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
-\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
-\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the thimble projection formula.
-\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
-\begin{equation}
-mmm
-\end{equation} 
-\end{itemize}
-\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-\begin{itemize}
-\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
-\end{itemize}
-\end{itemize}
-\color{black}
+\subsubsection{Why does Borel summation work for thimbles integrals?}
 
@@
 
-These questions have been classically addressed by Pham (\S 3.3 \cite{pham}), Malgrange (Theorem 6 in \cite{Malgrange22}), Delabere and Pham \cite{Delabaere-Pham99}, Berry and Howls \cite{berry1991hyperasymptotics}, Dunne and Unsal \cite{dunne-unsal}, and others.
+These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22},Berry and Howls \cite{berry1991hyperasymptotics}, Delabere and Pham \cite{Delabaere-Pham99}, Dunne and Unsal \cite{dunne-unsal}, and others.
 \textcolor{orange}{[add references]}
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
@@
 This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],\cite{delabaere-howls,dingle1973asymptotic}[Delabere \& Howls, Howls, Dingle]}.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic}\textbf{[Delabere \& Howls, Howls, Dingle]}.
 
@@
 We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with \S 2.2 in \cite{lectures-Marino}, \S 6.14 in \cite{diverg-resurg-i}, and \S 2.2 \cite{kawai-takei}).
-The anharmonic oscillator was also discussed in (Bender--Wu, Appendix B in \cite{aniceto2019primer}).
-Other examples haven't been discussed much, as for Airy--Lucas functions.
+For instance, for the Airy function we will make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
+The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).
+Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
 
 Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics as a powerful alternative to Borel summability.
-The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI}, \cite{costin-PI} \textcolor{magenta}{[check also paper by Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \S 6.2 in \cite{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
+The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
+For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
 Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.
@@
 %\end{itemize}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean to be Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item thimble projection formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
-\end{itemize}
-%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
 
@@
 %\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{\'Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
 %\item  M.A.E.T.
@@
 from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
+From uniqueness result we get a frame equivalent to \'Ecalle's frame.
 %\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
@@
 We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\cite{gupta2013meromorphic} \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
+This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
+
+\begin{figure}[ht]
+    \centering
+    %\includegraphics{}
+    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
+    \label{fig:translation_surface}
+\end{figure}
+
 \subsubsection{Direction}\label{transl:dir}
@@
 
-\subsubsection{The Laplace transform over an ordinary point}%%\label{laplace:ordinary}
+\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
 Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
@@
 \item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-\begin{itemize}
-\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
-\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
-\end{itemize}
-\end{itemize}
+\color{RoyalBlue}
+\begin{itemize}
+\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}, and is locally integrable throughout.
+Following {\tt reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
+\item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
+\end{itemize}
+\end{itemize}
+\color{black}
 \subsubsection{The Laplace transform over a branch point}
@@
 This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
-The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
+The half-plane $z \in H_{\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
@@
 
-Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
+Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$.
+Assume the $\Gamma_{\zeta,\alpha}^\theta$ is contained in $\Omega_\alpha$.
+In {\tt reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namley of the form $|\zeta|^\sigma$.
+When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta,\alpha}^\theta$ is a well--defined and holomorphic function for $\Re e^{-i\theta}z>0$ on the fiber $T^*B\vert_{\zeta=0}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
+%Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
 A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
 Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
-
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
+If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[Section  5.6]{diverg-resurg-i}.
+
+The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$.
 Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
+In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$.
 Let $F = \laplace_{\zeta, 0} f$.
@@
 \[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
+More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
+\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
 Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
@@
 
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \mathcal{E}_\zeta$ and
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
 \[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
 for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}%%\label{id:L-mult}
@@
 for all integers $n \ge 0$.
-Furthermore, if $\varphi\in\mathcal{E}_{\zeta,\alpha}$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\mathcal{E}_{\zeta,\alpha}$ and 
+Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
 \[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
@@
 
-Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\mathcal{E}_{\zeta_\alpha,0}$ and 
+Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
 \[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
@@
 \end{align*}
-If a function $\varphi$ belongs to $\mathcal{E}_\zeta$, and its Taylor series
+If a function $\varphi$ belongs to $\singexpalg{0}$, and its Taylor series
 \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
@@
 \[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is $1$-Gevrey if there exists $A>0$ such that $|a_n|\leq A^n n!$ \textcolor{magenta}{[isn't it $\lesssim$\,?]} for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+is $1$-Gevrey if there exists $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
 there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series.
+The Borel transform can be generalized in order to obtain germs of holomorphic function for higher Gevrey series.
 }
@@
 
-We first assume $\series{\Phi}=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\mathcal{E}_{\zeta,\alpha}$, then for every $\lambda\in (0,\infty)$
+We first assume $\series{\Phi}=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, then for every $\lambda\in (0,\infty)$
 \begin{align*}
@@
 
-Finally, recall that for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
+Finally, recall that for every $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
 $\fracderiv{-\lambda}{\zeta_\alpha}{0}\varphi$ coincide, therefore 
@@
 
-Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
+\subsubsection{Setting}\label{setting-ODE}
+
+Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
 \begin{equation}
@@
 \item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
-such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
+such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
 \item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
@@
 
+For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
+\begin{itemize}
+\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$.
+In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $Omega_j$.
+Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
+\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}
+\end{itemize}
+
+\begin{figure}
+\center
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=radial edge]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (160:\spill)
+  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
+  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
+  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
+  arc (-60:-130:\spill) -- (0, 0);
+\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
+\node at (1.7,1.8) {$\bullet$};
+\node[below] at (1.7,1.8) {$\zeta=\alpha_k$};
+\node at (1.25,-1.85) {$\bullet$};
+\node at (-0.58,1.85) {$\bullet$};
+\end{tikzpicture}
+\caption{The domain $\Omega_j$}\label{Fig:domain}
+\end{figure}
+\subsubsection{Main results}
+
+As a consequence of Theorem 4 in {\tt reg-volterra} we get
+
 \begin{theorem}\label{thm1-dim}
-\textcolor{orange}{[Revise to match \texttt{reg-sing-volterra}]} In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
+In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
 \begin{equation}\label{P-hat_j}
@@
 such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$ an open sectorial domain which closure contains $\alpha_j$.
+${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
 \end{theorem}
-\begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of \textcolor{orange}{\texttt{reg-sing-volterra}}. Without loss of generality, we will consider $\hat{P}_1$.
-
-\begin{align*}
-    \lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(\alpha_1-\zeta')}{P(-\alpha_1-\zeta_1)}\Big\vert &=\lim_{\substack{\zeta_1\to 0\\ \zeta'\to 0}}\Big\vert \zeta_1\frac{Q(-\alpha_1-\zeta')}{\zeta_1(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)}\Big\vert\\
-    &=\Big\vert \frac{Q(-\alpha_1)}{(\alpha_2-\alpha_1)...(\alpha_d-\alpha_1)}\Big\vert\\
-    &=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert
-\end{align*}
-in particular notice that $\tau_1:=\Big\vert\frac{Q(-\alpha_1)}{P'(-\alpha_1)}\Big\vert>0$ (since $Q(-\alpha_j)\neq 0$).
-
-Since $P$ and $Q$ are polynomials, we get the following estimates:
-
-\begin{align*}
-    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{1}{P(-\alpha_1-\zeta_1)}\Big\vert=|P(-\alpha_1-\delta)|^{-1}
-\end{align*}
-
-\begin{align*}
-    \sup_{|\zeta_1|\geq\delta}\Big\vert\frac{Q(-\alpha_1-\zeta_1)}{P(-\alpha_1-\zeta_1)}\Big\vert=\Big\vert\frac{Q(-\alpha_1-\delta)}{P(-\alpha_1-\delta)}\Big\vert
-\end{align*}
-
-We are left with the bounds on the kernel: following the notation of \textcolor{orange}{\texttt{reg-sing-volterra}}, we set
-
-\begin{equation}
-    K_{\text{soft}}(\zeta_1,s)=\sum_{r=0}^{d-1}\sum_{j=0}^{\infty}R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r
-\end{equation}
-where, since $R_r$ are holomorphic functions in some disk of radius $A$ centered at $\infty$, we define $R_r(z)=\sum_{j=0}^\infty R_{r,j}z^{-j}$ and $|R_{r,j}|\leq A^{-j}$. In particular,
-
-\begin{align*}
-    \Big\vert \sum_{j=0}^\infty \frac{R_{r,j}}{j!}(\zeta_1-s)^{j+1}\Big\vert \leq |\zeta_1-s| e^{\frac{|\zeta_1-s|}{A}}
-\end{align*}
-
-If $|\zeta_1|\geq\delta$ and $s\in\Omega_1$
-
-\begin{align*}
-    \Big\vert-\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}-\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq  \Big\vert\frac{Q(-s-\alpha_1)}{P(-\zeta_1-\alpha_1)}\Big\vert+\Big\vert\frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert\\
-    &\leq C+ |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}\sum_{j=0}^{\infty} \Big\vert R_{r,j}\frac{(\zeta_1-s)^{j+1}}{j!}(-s-\alpha_1)^r\Big\vert\\
-    &\leq C + |P(-\alpha_1-\delta)|^{-1} \sum_{r=0}^{d-1}|\zeta_1-s|e^{|\zeta_1-s|/A} |s-\alpha_1|^r
-\end{align*}
-
-In particular, for every $\zeta_1,s\in\Omega_1$
-
-\begin{align*}
-    \Big\vert \zeta_1 \frac{K_{\text{soft}}(\zeta_1,s)}{P(-\alpha_1-\zeta_1)}\Big\vert&\leq |\zeta_1-s| e^{|\zeta_1-s|/A} \sum_{r=0}^{d-1}\frac{|s-\alpha_1|^r}{|(\zeta_1+\alpha_2)...(\zeta_1+\alpha_d)|}\\
-\end{align*}
-
-\textcolor{magenta}{[to conclude, we need assumption on how $s$ and $\zeta_1$ respectively move in $\Omega_1$. ]}
-
-%In particular, $\Lambda=(-\infty,-2]$.
-
-Therefore, there exists a unique solution
-
-\begin{equation}\label{eqn:slight_solution}
-    \psi_1(\zeta_1)=\zeta_1^{\tau_1-1}+f_1(\zeta_1)
-\end{equation}
- and $f_1\in\mathcal{HL}^{\infty}_{\tau_1,1/A}(\Omega_1)$.
-
-\end{proof}
-
-\begin{corollary}\label{cor:existence_Laplace}
-    Under the assumption of Theorem \ref{thm1-dim}, the function $\hat{\psi}_j$ defined in Equation \eqref{eqn:slight_solution} admits a Laplace transform. 
-\end{corollary}
-
-\begin{proof}
-
-\end{proof}
-
-\begin{lemma}
- Let $\hat{\psi}_j$ be a solution of $\hat{P}_j\hat{\psi}_j=0$ for every $j=1,...,d$ and $\hat{P}_j$ defined in \eqref{P-hat_j}.
-Let $\Psi_j=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j$ be the Laplace transform of $\hat{\psi}_j$, for $j=1,...,d$ and for a suitable direction $\theta_j$, then $\mathcal{P}\Psi_j=0$.
-\end{lemma}
-
-\begin{proof}
-    \begin{align*}
-        \mathcal{P}\Psi_j&=\mathcal{P}\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\left[P(-\zeta_j-\alpha_j)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta_j-\alpha_j)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta_j-\alpha_j)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha_j}^{\theta_j}\hat{P}_j\hat{\psi}_j
-    \end{align*}
-    \textcolor{magenta}{[do we really need the assumption on $\theta_j$, namely $\theta_j\neq\arg(\alpha_j-\alpha_k)$ for every $k=1,...,d$?]} \textcolor{orange}{[At first, I didn't think we need that assumption for the Volterra equation existence theorem to hold, or for the Laplace transform to exist.
-When the integration path crosses over $\alpha_k$, I thought that only $\psi_k$ would jump, so only $\psi_k$ would need to become ill-defined when the integration path goes through $\alpha_k$.
-\textbf{However, it's true that $v_1$ and $v_{-1}$ each blow up at both singularities, so maybe there's a problem with the construction!}]}
-\end{proof}
 
@@
 \item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
-\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta_j}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-
-Step $(b)$ clearly follows from Corollary \ref{cor:existence_Laplace} and step $(a)$.
-In fact, from step $(a)$ and Theorem \ref{thm1-dim}, $\Tilde{\psi}_j$ and $\hat{\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
-Then, by Corollary \ref{cor:existence_Laplace} we can Laplace transform both $\hat{\psi}_j$ and $\tilde{\psi}_j$.
+\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
+\end{itemize}
+
+Step $(b)$ clearly follows from Theorem  \ref{thm1-dim} and step $(a)$.
+In fact, from step $(a)$ and Theorem \ref{thm1-dim}, $\Tilde{\psi}_j$ and ${\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+Then, by Corollary \ref{thm1-dim} we can Laplace transform ${\psi}_j$ along a ray $\Gamma_{\alpha_j}^\theta$ in $\Omega_j$.
+Hence if $\hat{\psi}_j$ denotes the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$, we can Laplace transform $\hat{\psi}_j$ along $\Gamma_{\alpha_j}^\theta$, too.
 
@@
     %The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-In fact, we can prove this statement using a perturbative method that goes back to Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
+In fact, we can prove this statement using a perturbative method that goes back to \'Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
 Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
@@
 
+\subsubsection{Setting}
+
 Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{x_1,...,x_N\}$. Set
@@
 
+\subsubsection{Main result}
 \begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
@@
 
-\textcolor{red}{[From here the old proof begins]}
-
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $f(x_j)$ with $\tfrac{1}{2} \tau^2 = f - f(x_j)$.
-Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
-\textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\Re z \to \infty$. 
-\color{black}\textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z \alpha_j} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z \alpha_j} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
-\end{align*}
-
------------ TO BE VERIFIED ---------------
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-\textcolor{magenta}{These terms are crucial, however, for the convergence of the sum.[Veronica: I don't understand why the sum should be convergent...in fact I think we should get a divergent series]} To see why, consider their absolute sum $C_\text{exp}$.
-When $z \in [0, \infty)$,
-\begin{align*}
-C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \color{magenta}\ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-\color{black}
-which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
-
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
-We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
-See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
-\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
-
-\color{Purple}
-For each cutoff $N$, the tail error \textbf{[check]}
-\begin{align*}
-\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
-& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
-& = \textbf{uh-oh!}
-\end{align*}
-\color{violet}
-is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
-\begin{align*}
-C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.
-
-\color{magenta}
-[Veronica suggestion]
-
-\begin{claim}
-    \[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-\end{claim}
-
-Indeed,
-
-\begin{align*}
-    \Bigg | 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | \leq 
-\end{align*}
-
-\color{black} %Hence,
-%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$\textcolor{magenta}{ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]} 
-\textcolor{magenta}{[check!]}
-Call the right-hand side $\tilde{I}_\alpha$. We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem. \textbf{[Resolve discrepancy with previous calculation.]}
-
--------- From here it is OK---------
-
-\vspace{5mm}
-
-Note that 
-\begin{align*}
-\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
-
-%Part~\eqref{int:resum-converges}: \begin{align*}
-%\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-%(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
-%\end{align*}
-%Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
-
-\textcolor{red}{From here the proof continues}
-
 Part~\eqref{int:resum-valid}: Let us recast the integral $I_j$ into the $f$ plane.
@@
 %\color{Aquamarine}
-%In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{\iota}_j$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
+%In \'Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{\iota}_j$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
 [Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
@@
 where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
-\begin{center}
-\includegraphics{figures/u_contour_3.pdf} \\[1em]
-{\small The contour $\Gamma$ in the $u$ plane.}
-\end{center}
+
+\begin{figure}[ht]
+    \centering
+    %\includegraphics{figures/u_contour_3.pdf}
+    \includegraphics[scale=0.3]{figures/thimble_Airy.png}
+    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the region indicate and what the color]}}
+    \label{fig:path_Airy}
+\end{figure}
+
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
-   % \includegraphics{}
+   \includegraphics[scale=0.3]{figures/thimble-n5.png}
     \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.}
@@
 which has a fractional power singularity at $\zeta=1$.
-In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of Ecalle's resurgent functions.
+In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.
 More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new germ of holomorphic function, which has a branch cut singularity at $\zeta=-1$.
@@
 namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
-This is an instance of \textit{resurgent functions}, introduced by Ecalle in \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}\footnote{If the reader is interesting in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i}\cite{Dorigoni}\cite{aniceto2019primer}.}.
+This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}\footnote{If the reader is interesting in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i}\cite{Dorigoni}\cite{aniceto2019primer}.}.
 Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
 \center
@@
 
-\color{orange}
-\section*{Outline}
-
-\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
-
-\begin{enumerate}
-\item introduction
-\begin{itemize}
-\item Exponential integrals
-\begin{itemize}
-\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
-\item the choice of the path $\mathcal{C}$: 
-\begin{itemize}
-\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
-\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
-\end{itemize}
-\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
-\begin{itemize}
-\item there is a comparison isomorphism (Maxim)
-\end{itemize}
-\item varying $z$ we have the Stokes phenomena
-\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
-\begin{itemize}
-\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
-\item it is an example of resurgent series (\'Ecalle)
-\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
-\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
-\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
-There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
-\end{itemize} 
-\end{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
-\item motivation
-\begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
-\end{itemize}
-\end{itemize}
-\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
-\item State results about resurgence of exponential integrals and Stokes phenomena
-\begin{itemize}
-\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]
-\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
-\end{itemize}
-\end{itemize}
-\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
-\begin{enumerate}
-\item Analytic
-\begin{enumerate}
-\item Introduction
-\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
-\item The Laplace transform of a holomorphic function
-\begin{enumerate}
-\item Over an ordinary point
-\item Over a branch point
-\item Differential equation
-\end{enumerate}
-\item Relating differential equations in the frequency domain to integral equations in the position domain
-\end{enumerate}
-\item Formal
-\begin{enumerate}
-\item Laplace transform of a formal series
-\item Borel transform
-\item Relating differential equations in the frequency variable to integral equations in the position variable
-\end{enumerate}
-\end{enumerate}
-\item Review of integral equations
-\begin{itemize}
-\item Existence of solutions
-\item Fractional integrals and derivatives
-\item Going between integral and differential equations (slight functions)
-\end{itemize}
-\item General cases
-\begin{enumerate}
-\item Borel regularity
-\begin{itemize}
-\item General ODE of the form
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
-\begin{itemize}
-\color{DarkCyan}
-\item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
-\begin{itemize}
-\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
-\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
-\end{itemize}
-\color{orange}
-\item Show that we can find a slight solution at each critical value.
-\item Show that $\hat{\iota} = \tilde{\iota}$, where:
-\begin{itemize}
-\item $I = \laplace \iota$
-\item $\hat{\iota}$ is the Taylor expansion of $\iota$
-\item $\tilde{I}$ is the asymptotic series of $I$
-\item $\tilde{\iota} = \borel \tilde{I}$
-\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
-\end{itemize}
-\end{itemize}
-\item General thimble integral (conditions?)
-\begin{itemize}
-\item Proof of Borel regularity
-\item $3/2$-derivative formula
-\item thimble projection reasoning
-\end{itemize}
-\end{itemize}
-\item Resurgence
-\begin{itemize}
-\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
-\item Relate to Ecalle's formalism and the alien derivative
-\item Stokes factors
-\begin{itemize}
-\item For ODEs
-\item For thimble integrals
-\end{itemize}
-\end{itemize}
-\end{enumerate}
-\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
-\begin{enumerate}
-\item The Airy example
-\begin{itemize}
-\item $I(z)$ is a solution of a linear ODE.
-We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Compute Stokes constants
-\begin{itemize}
-\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
-\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
-\end{itemize}
-\item Comparison with the literature \textcolor{gray}{has to be done}
-\begin{itemize}
-\item Mari\~{n}o
-\item Sauzin
-\item Kontsevich slides
-\item Kawai--Takei? [might take too long to understand well enough]
-\end{itemize}
-\end{itemize}
-\item The Airy--Lucas examples
-\begin{itemize}
-\item Compute Borel transform [{\tt airy-resurgence}]
-\item Compute Stokes constants \textcolor{gray}{has to be done}
-\end{itemize}
-\item Bessel 0 (it is different because we have infinite cover)
-\begin{itemize}
-\item Compute Stokes constants [{\tt draft2}]
-\end{itemize}
-\item Bessel $\mu$ (follows from Bessel 0)
-\begin{itemize}
-\item Compute Stokes constants [{\tt modified Bessel}]
-\end{itemize}
-\item The generalized Airy example
-\item The vibrating beam example
-\begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
-\end{itemize}
-\end{enumerate}
-\end{enumerate}
-
 \color{black}
@@
 \end{equation}
+and the contour $\Gamma$ is represented in Figure \ref{fig:path_Airy}.
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
@@
 \begin{equation}
-    u=
+    u=????
 \end{equation}
@@
 and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
-The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
+The main advantage of writing Gauss hypergeometric functions as a convolution product relies on \'Ecalle's singularity theory.
 Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see part c of \cite[Section 6.14.5]{diverg-resurg-i}).
@@
 \color{black}
+\newpage
+
+\section{Plan of the paper}
+\subsection{Results}
+
+\color{orange}
+\begin{itemize}
+\item what does it mean to be Borel regular?
+\item when does it happen?
+\begin{itemize}
+\item State new Borel regularity results
+\begin{itemize}
+\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
+\begin{itemize}
+\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
+\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
+\item Also contextualize with Loday-Richaud
+\end{itemize}
+\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
+\begin{equation}
+\begin{tikzcd}
+I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+& \\
+\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
+\end{tikzcd}
+\end{equation}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item thimble projection formula
+\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
+\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
+\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
+\end{itemize}
+%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
+%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
+\end{itemize}
+\end{itemize}
+
+\color{orange}
+\subsection*{Outline}
+
+\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
+
+\begin{enumerate}
+\item introduction
+\begin{itemize}
+\item Exponential integrals
+\begin{itemize}
+\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
+\item the choice of the path $\mathcal{C}$: 
+\begin{itemize}
+\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
+\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
+\end{itemize}
+\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
+\begin{itemize}
+\item there is a comparison isomorphism (Maxim)
+\end{itemize}
+\item varying $z$ we have the Stokes phenomena
+\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
+\begin{itemize}
+\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
+\item it is an example of resurgent series (\'Ecalle)
+\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
+\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
+\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
+There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
+\end{itemize} 
+\end{itemize}
+\item what are exponential integrals? \textcolor{gray}{has to be done}
+\begin{itemize}
+\item motivation
+\begin{itemize}
+\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
+\item In physics ??
+\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
+\end{itemize}
+\end{itemize}
+\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
+\item State results about resurgence of exponential integrals and Stokes phenomena
+\begin{itemize}
+\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
+\item ODE and fractional derivative formula [{\tt draft2}]
+\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
+\end{itemize}
+\end{itemize}
+\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
+\begin{enumerate}
+\item Analytic
+\begin{enumerate}
+\item Introduction
+\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
+\item The Laplace transform of a holomorphic function
+\begin{enumerate}
+\item Over an ordinary point
+\item Over a branch point
+\item Differential equation
+\end{enumerate}
+\item Relating differential equations in the frequency domain to integral equations in the position domain
+\end{enumerate}
+\item Formal
+\begin{enumerate}
+\item Laplace transform of a formal series
+\item Borel transform
+\item Relating differential equations in the frequency variable to integral equations in the position variable
+\end{enumerate}
+\end{enumerate}
+\item Review of integral equations
+\begin{itemize}
+\item Existence of solutions
+\item Fractional integrals and derivatives
+\item Going between integral and differential equations (slight functions)
+\end{itemize}
+\item General cases
+\begin{enumerate}
+\item Borel regularity
+\begin{itemize}
+\item General ODE of the form
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
+where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
+\begin{itemize}
+\color{DarkCyan}
+\item More generally, for $P$ of degree $n$, we should be able to handle
+\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
+where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
+\begin{itemize}
+\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
+\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
+\end{itemize}
+\color{orange}
+\item Show that we can find a slight solution at each critical value.
+\item Show that $\hat{\iota} = \tilde{\iota}$, where:
+\begin{itemize}
+\item $I = \laplace \iota$
+\item $\hat{\iota}$ is the Taylor expansion of $\iota$
+\item $\tilde{I}$ is the asymptotic series of $I$
+\item $\tilde{\iota} = \borel \tilde{I}$
+\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
+\end{itemize}
+\end{itemize}
+\item General thimble integral (conditions?)
+\begin{itemize}
+\item Proof of Borel regularity
+\item $3/2$-derivative formula
+\item thimble projection reasoning
+\end{itemize}
+\end{itemize}
+\item Resurgence
+\begin{itemize}
+\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
+\item Relate to \'Ecalle's formalism and the alien derivative
+\item Stokes factors
+\begin{itemize}
+\item For ODEs
+\item For thimble integrals
+\end{itemize}
+\end{itemize}
+\end{enumerate}
+\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
+\begin{enumerate}
+\item The Airy example
+\begin{itemize}
+\item $I(z)$ is a solution of a linear ODE.
+We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
+\item Compute Stokes constants
+\begin{itemize}
+\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
+\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
+\end{itemize}
+\item Comparison with the literature \textcolor{gray}{has to be done}
+\begin{itemize}
+\item Mari\~{n}o
+\item Sauzin
+\item Kontsevich slides
+\item Kawai--Takei? [might take too long to understand well enough]
+\end{itemize}
+\end{itemize}
+\item The Airy--Lucas examples
+\begin{itemize}
+\item Compute Borel transform [{\tt airy-resurgence}]
+\item Compute Stokes constants \textcolor{gray}{has to be done}
+\end{itemize}
+\item Bessel 0 (it is different because we have infinite cover)
+\begin{itemize}
+\item Compute Stokes constants [{\tt draft2}]
+\end{itemize}
+\item Bessel $\mu$ (follows from Bessel 0)
+\begin{itemize}
+\item Compute Stokes constants [{\tt modified Bessel}]
+\end{itemize}
+\item The generalized Airy example
+\item The vibrating beam example
+\begin{itemize}
+\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
+\end{itemize}
+\end{enumerate}
+\end{enumerate}
+
+\subsection{Why Borel regularity works for thimble integrals}
+\color{DarkBlue}
+\begin{itemize}
+%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
+%\begin{itemize}
+%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
+%\end{itemize} 
+\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
+His proof uses microlocal analysis and classical results due to Varchenko.
+In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
+\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
+\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
+%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+%\begin{equation}
+%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+%\end{equation}
+
+%then the following diagram is commutative
+%\begin{equation}
+%\begin{tikzcd}
+%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+%& \\
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\end{tikzcd}
+%\end{equation}
+\begin{itemize}
+%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
+\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
+\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+\item A corollary of [Thm 4] is the thimble projection formula.
+\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
+\begin{equation}
+mmm
+\end{equation} 
+\end{itemize}
+\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
+See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
+\begin{itemize}
+\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
+\end{itemize}
+\end{itemize}
+\color{black}
 

### 2023-08-01 reg-sing-volterra.tex
Drop draft text from intro

@@
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino}}.
-
-\textcolor{RoyalBlue}{A nice feature of the Laplace transform is that} Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this \textcolor{purple}{helpful} behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
+Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}}.
+
+Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
+In Section~\ref{sec:example}, we'll see this helpful behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
 This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.
-\textcolor{RoyalBlue}{In Section~\ref{sec:example}, we'll see this behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical and not-so-classical examples like the modified Bessel equation; some cases of the equation describing the vibration modes of a beam \textcolor{orange}{[find citation]}, and---after a change of coordinate---the Airy, Airy-Lucas~\cite[Equation 3.2]{charbonnier22}, higher Airy~\cite[Equation 3.8]{charbonnier22}\cite{durugo_higher}, and generalized Airy equations \cite[Equation 9.13.31]{dlmf}.}
 
@@
 The first condition also tells us that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-%%\begin{itemize}
-%%\item They have singularities that look like $(\zeta - \alpha)^{\tau-1}$ with $\tau > 0$, where $\zeta$ is the position variable and $\zeta = \alpha$ is a place where the Volterra equation has a regular singularity.
-%%\item They're of exponential type.
-%%\item They grow slowly enough as $|\zeta| \to \infty$ to have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
-%%\end{itemize}
-%%Thanks to their mild singularities and moderate growth, these solutions have well-defined Laplace transforms, which by construction will satisfy the differential equation we started with in the frequency domain.
-%%This has led us to look for solutions of regular singular Volterra equations in the the function spaces defined in Section~\ref{fn-spaces}, which are designed to capture the properties above.
-\textcolor{orange}{[Describe existence and uniqueness result.]}
 
@@
 \textcolor{orange}{[Mention treatment of motivating example in Section~\ref{sec:example}.]}
-
-% -------------------------------------------
-
-%%If you pull back a nice enough differential operator, you might get a Volterra operator with a real-analytic kernel, which extends uniquely to a holomorphic Volterra operator on a complex extension of the position domain.
-By analytically continuing the eigenfunctions of the Volterra operator around singularities in the position domain, you might discover hidden relationships between the eigenfunctions of the original differential operator.
-In its nicest cases, this phenomenon is called {\em resurgence} \textcolor{orange}{[cite]}.
-
 \subsection{Setting}\label{setting}

### 2023-08-02 exp-resurgence.tex
exp-resurgence: cleaning the introduction, the statements of the theorems, and some references.
Change the notation of the example in the introduction, in fact, it didn't match the dlmf and Mathematica conventions. 

Removing hold version in proof of main results. 

Add pictures for thimbles.

@@
 behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
+Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
 \begin{equation}
-e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
-\end{equation}
-and its constant multiples. As another example, you might rewrite the integral
-\begin{verify}
-    \[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
-\end{verify}
-
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
+e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{85085}{33592320} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+\end{equation}
+and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
+
+\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
 as
-% see expansion.sage
-\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
-using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-
-\begin{verify}
-    \begin{align*}
-& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
-& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
-& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
-\end{align*}
-\end{verify}
-
+\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
+\color{orange}
+\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
+using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
+\color{black}
 Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
+%\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
 Ask more about this.]}
@@
 \subsubsection{Introducing Borel regularity}
-\begin{itemize}
-\item Start instead with a holomorphic solution $\Phi$.
-\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
-\end{itemize}
+We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
+
 %\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
@@
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are entire functions of exponential type (i.e.
-$|R_j(z)|<C_j e^{a_j|z|}$ as $|z|\to+\infty$, for $C_j,a_j>0$ ).
-
-We'll restrict our attention to the case where the roots of $P$ are distinct.
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
+We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).
 
 The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
-Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.
-
-\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
+Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
+
+\item the second problem is evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
 
@@
 In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
-Conversely, we can explicitly build a distinguished basis of analytic solutions:
-
-\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
-In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with
+Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
 
 \begin{equation}
-\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
-\end{equation}
-
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-\textcolor{red}{${\psi}_j=\zeta_j^{-\tau_j-1}+f_{j,\star}$} and $f_{j,\star}\in\singexpalg{\tau_j-1}(\Omega_j)$ for an open star-shaped domain $\Omega_j$ which avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
+\end{equation}
+
+labeled by the roots of $P$.
+This type of operators are the one we studied in {\tt reg-sing-volterra}, hence we know there exists a unique solution $\psi_j=f_{j,0}+f_{j,\star}$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and $f_{j,\star}\in\singexpalg{\tau_j}(\Omega_j)$ for an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}$.
+
+\begin{theorem}\label{thm1}
+    The holomoprhic functions $\Psi_j$ are solutions of $\mathcal{P}\Psi_j=0$. In particular, they are a frame of analytic solutions.
 \end{theorem}
@@
 \begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta}$ for some direction $\theta$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
+The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
 \end{theorem}
@@
 
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
+In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
+%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
 
@@
 
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
+Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 {\tt reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (Theorem \ref{thm1}).
 
 The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too.
+First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE).
 In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result~\ref{thm1}, we conclude that $\psi_j$ and $\hat{\psi}_j$ must coincide up to scaling by a constant.
-
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.
+therefore, by our uniqueness result, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
+Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
+
+As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
+Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.
 
@@
 
-\color{Tan}
 \begin{remark}
-Although, in our proof, we use $1$-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
-\textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
-For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$?
-Check carefully the argument of multi-summability]}
+The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namley, drawing the red arrow of the diagram).
+This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE.
+However, the approach of Borel regularity is different as it is based on the analytic solution in the position domain.
 \end{remark}
-
-\color{magenta}
-[Veronica]
-
-Although, in our proof, we adapt an argument by M.
-Loday-Richaud and P.
-Remy (see \S 2 in\cite{loday-Remy2011}) to guarantee Borel--Laplace summability, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
-In addition, our proof stresses the importance of the position domain, where in fact the crucial step of the proof is done.
 
@@
 
-\color{black}
-
 \subsubsection{Why does Borel summation work for thimbles integrals?}
@@
 We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
-We follow \cite{pham} and $\S 1$ in \cite{Arnold}.
+We follow \cite{pham} and \cite[Section 1]{Arnold}.
 Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
@@
 
-Then we recall the definition of $H_{dR,z}^\cdot$: it is the hypercohomolgy of the twisted de Rham complex
+Then we recall the definition of $H_{dR,z}^*$: it is the hypercohomolgy of the twisted de Rham complex
 
@@
 Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
-
-Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_\alpha$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
+We will discuss this phenomena from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
+\textcolor{orange}{[Can we comment more about this?
+For instance as a consequence of Theorem 3.3]}
+
+Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
 
@@
 
-These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22},Berry and Howls \cite{berry1991hyperasymptotics}, Delabere and Pham \cite{Delabaere-Pham99}, Dunne and Unsal \cite{dunne-unsal}, and others.
-\textcolor{orange}{[add references]}
+These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
+In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[Delabere \& Howls, Howls, Dingle]}.
 
@@
 We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-\color{DarkBlue}
-Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
-Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
-A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-Take another meromorphic-type translation surface $B$ and a holomorphic map $f \maps \overline{X} \to \overline{B}$ with non--degenerate critical points \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-\textcolor{red}{Suppose every singularity of $B$ is a critical value of $f$.[Veronica: Is it a good assumption?]} \textcolor{DarkGreen}{\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (\cite{dlmf}~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]}}
-\color{black}
+The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
+
 For each critical point $x_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j:=f(x_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
@@
 \item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
-\begin{multline}
-\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
+\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
+\begin{multline}\label{eqn:formula}
+\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
 \end{multline}
@@
 
-The idea of the proof is sketched below in the following diagram:
+The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}):
 \[
@@
 as the Laplace transform of a function $\iota_j$.
-In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{formula1}.
+In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}.
 On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
@@
 
-In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
+\begin{remark}
+    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
+When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\iota_j$ explicitly as
+    \begin{equation}\label{eqn:Pham}
+        (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
+    \end{equation}
+
+    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
+   \begin{equation*}
+       \delta^{-\alpha}:=\begin{cases}
+           \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
+           & \\
+           \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
+       \end{cases}
+   \end{equation*}
+
+    In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\phi_j$ is the $1/2-$ derivative of $\iota_j$, \textcolor{orange}{hence it has simple singularities [it has to be verified]}.
+We expect this result to hold beyond the polynomial case.
+We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
+\end{remark}
+
+%In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
 This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
@@
 We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem 4 in {\tt reg-sing-volterra}).
 Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.
@@
 
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
+We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), the anharmonic oscillator...).
 Then, on the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}.
+In the Airy example (\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
+Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.
 
@@
 
-\color{black}
-
-\subsection{thimble projection formula}
-\begin{itemize}
-\item formula \eqref{formula1} Theorem~\ref{thm:maxim} says that for a certain class of exponential integrals
-\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
-the inverse Laplace transform is the $\tfrac{3}{2}$ derivative of $\nu/df$ at $\zeta=f$.
-\item the asymptotic expansion of $I(z)$ is a resurgent function.
-\item Is it always a \emph{simple} resurgent function?
-\begin{itemize}
-\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
-\end{itemize} 
-\end{itemize}
-
 %\subsection{Stokes phenomenon}
@@
 %\end{itemize}
+
+\subsection{Acknowledgements}
+
+This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
+
+We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+
+We thank Maxim Kontsevich, David Sauzin, Frederic Fauvet, Andrew Neitzke, for fruitful discussions and suggestions.
+
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 \begin{itemize}
-\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}, and is locally integrable throughout.
-Following {\tt reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
+\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following {\tt reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
 \item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
@@
 Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{\alpha_j} \tilde{\phi}_j. \]
+\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j. \]
 
@@
 
-\subsection{Airy--Lucas}
+\subsection{Airy--Lucas}\label{example_AL}
 The Airy-Lucas equation is
@@
 \end{equation}
+
+\textcolor{orange}{[add the numerical check to show simple resurgence]}
 

### 2023-08-02 reg-sing-volterra.tex
exp-resurgence: cleaning the introduction, the statements of the theorems, and some references.
Change the notation of the example in the introduction, in fact, it didn't match the dlmf and Mathematica conventions. 

Removing hold version in proof of main results. 

Add pictures for thimbles.

@@
 \textcolor{orange}{[Mention treatment of motivating example in Section~\ref{sec:example}.]}
+\subsection{Notation for uniform bounds}
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we'll write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
 \subsection{Setting}\label{setting}
@@
 \begin{proof}
+By definition,
 \begin{align*}
 \|f\|_{\sigma,\Lambda}&=\sup_{\Omega} |\zeta|^{-\sigma}  e^{-\Lambda |\zeta|} |f|\\
-        &= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|\\
+&= \sup_{\Omega} |\zeta|^{\sigma'-\sigma}\,|\zeta|^{-\sigma'}\,e^{-\Lambda'|\zeta|}\,  e^{-(\Lambda-\Lambda') |\zeta|} \, |f|.
 \end{align*}

### 2023-08-07 exp-resurgence.tex
Write last sentence of intro; label perturbed_volterra as lemma

@@
 
-\item the second problem is evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
-
-\begin{equation}
+\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
+
+\begin{equation*}
 I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
-\end{equation}
+\end{equation*}
 where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
@@
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
-It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.
-
-\color{DarkTurquoise}
-In \cite[Proposition~2.2.7]{EcalleIII}, where
+Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
+
+\begin{verify}
+    Turn the ODE into a system: assume 
     \begin{align*}
@@
 \end{align*}
-(with the coefficients renamed to avoid a conflict with the zeros $\alpha_j$), the recurrence that gives the solution simplifies
-\begin{align*} b_q & = P_q + Q_q z^{-1} - \frac{\partial}{\partial x^{(q)}} b(z, x, x^{(1)}, \ldots x^{(d)}) \\
-& = P_q + Q_q z^{-1} - R_q(z^{-1}).
-\end{align*}
-
-Following the argument of Delabaere Lemma~6.2, we can prove that $\series{F}_j(z)$ is $1$-Gevrey by taking the formal Borel transform of the ODE it satisfies and showing it is regular singular at $\zeta=0$.
-
-Roughly speaking, factoring out $e^{-\alpha_j z}$ removes the constant term of $P$, and factoring out $z^{-\tau_j}$ changes $Q$ to give factorial growth instead of gamma function growth (?).
-
-\begin{align*}
-\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
-& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
-&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
-\end{align*}
-where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
-\color{Tan}
-\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
-\color{DarkTurquoise}
-\[ \frac{P_d}{w^{2d}}  \left(\frac{\partial}{\partial w}\right)^d , \]
-corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).
-
-From the Bessel equation, for example, we get
-\begin{align*}
-(-w^{-2}\partial_w)^2&=-w^{-2}\partial_w(-w^{-2}\partial_w)\\
-&=-w^{-2}(2w^{-3}\partial_w-w^{-2}\partial_w^2)\\
-&=-2w^{-5}\partial_w+w^{-4}\partial_w^2,
-\end{align*}
-giving two half-planes around $\infty$, as expected.
-\color{black}
+then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
+    \begin{equation}
+        \frac{d}{dz}Y= B(z) Y 
+    \end{equation}
+    \[
+    B(z)=\begin{pmatrix}
+            0 & 1 & 0 & \ldots & 0 \\
+            0 & 0 & 1 & \ldots & 0 \\
+            \vdots & &\ddots & & 1\\
+            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
+        \end{pmatrix}, \quad Y=\begin{pmatrix}
+            \psi \\
+            \psi ' \\
+            \vdots \\
+            \psi^{(d-1)}
+        \end{pmatrix}
+    \]
+
+ and $b_j(z)=-P_j-\frac{1}{z}Q_j-\frac{R_j(z)}{z^2}$. A formal system of solutions is given by the matrix 
+\begin{equation}
+    Y=\begin{pmatrix}
+       \psi_1 & \psi_2 & \ldots & \psi_d  \\
+       \psi_1' & \psi_2' & \ldots & \psi_d'  \\
+       \vdots & \vdots  & \ldots & \vdots  \\
+       \psi_1^{(d-1)} & \psi_2^{(d-1)} & \ldots & \psi_d^{(d-1)} 
+    \end{pmatrix}, \qquad \psi_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{f}_j
+\end{equation}
+
+To prove that $z=\infty$ is an irregular singular point we change coordinates and set $w=1/z$:
+
+ \begin{equation}
+        -w^2 \frac{d}{dw}Y= B(1/w) Y 
+    \end{equation}
+
+and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
+\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
+hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular. 
+\end{verify}
 
@@
 \item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-\color{RoyalBlue}
+%\color{RoyalBlue}
 \begin{itemize}
@@
 and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
-\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
+which grows as $n(n+1)^{-\alpha} A^{n+1}$.
+\begin{verify}
+    we use $\Gamma(n+1+\alpha)\sim \Gamma(n+1) (n+1)^\alpha$ as $n\to\infty$. 
+\end{verify}
 \end{proof}
@@
 \textcolor{orange}{[Veronica:I think we should move this section, maybe when we do examples]}
-Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
-A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
-\begin{equation}\label{eqn:slight-defn}
-\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-\end{equation}
-where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-
-Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
+Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.
+%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
+%We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
+%\begin{equation}\label{eqn:slight-defn}
+%\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
+%\end{equation}
+%where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
+As we've seen in Section \ref{reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
 This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
+In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
 \begin{prop}\label{prop:shifting}
-When $\psi$ is slight and locally integrable at $\zeta = 0$,
+Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
 \[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
@@
 \[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are regular functions.
+where $h_n, \ldots, h_{-m}$ are holomorphic functions.
 \end{prop}
-To prove this result, we'll need a little background.
-
-Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
+%To prove this result, we'll need a little background.
+
+%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
 The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
@@
 
-Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
+%Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
 Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
@@
 Differentiation and integration add $-1$ and $1$, respectively.
-\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
+
+\begin{proof}%[Proof of Proposition~\ref{prop:shifting}]
 The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
@@
 \[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-is slight.
-Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
-Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
+belongs to the function space $\singexpalg{\sigma}(\Omega)$.
+Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
+Hence, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
 

### 2023-08-07 reg-sing-volterra.tex
Write last sentence of intro; label perturbed_volterra as lemma

@@
 \begin{brainstorm}
-\item \textit{(Aaron)} State Lemma~\ref{thm:perturbed_volterra} just the way we want it.
+\item \textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.
 \item \textit{(Aaron)} Finish introduction
@@
 \begin{itemize}
-        \item \textit{(Aaron)} Add proofs of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra} to Section~\ref{sec:existence and uniqueness}
+        \item \textit{(Aaron)} Add proofs of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra} to Section~\ref{sec:existence and uniqueness}
         \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.
@@
 \begin{itemize}
-    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{thm:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary.
-Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{thm:perturbed_volterra} as a lemma.
+    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{lem:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary.
+Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{lem:perturbed_volterra} as a lemma.
 State it after Theorem~\ref{thm:general_volterra}.}
@@
 We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-\textcolor{orange}{[Mention treatment of motivating example in Section~\ref{sec:example}.]}
+We'll apply our results to level $1$ differential equations in Section~\ref{sec:example}.
 \subsection{Notation for uniform bounds}
@@
 
-\begin{lemma}\label{thm:perturbed_volterra}
+\begin{lemma}\label{lem:perturbed_volterra}
 Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
@@
 We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
-Then the result follows as a consequence of Lemma \ref{thm:perturbed_volterra}.
+Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.
 
@@
     \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
-    \item Use the contraction mapping theorem to prove Lemma~\ref{thm:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
+    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
 \end{itemize}
@@
 
-\subsection{Showing that $\volterra$ shrinks perturbations \\ \textit{(toward Lemma~\ref{thm:perturbed_volterra})}}\label{sec:V is a contraction}
+\subsection{Showing that $\volterra$ shrinks perturbations \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
 \subsubsection{Overview}
@@
 This completes our proof of Proposition~\ref{prop:get-contraction}.
-\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{thm:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
+\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
 
@@
 
-This follows by Lemma \ref{thm:perturbed_volterra}.
+This follows by Lemma \ref{lem:perturbed_volterra}.
 \end{proof}

### 2023-08-07 reg-sing-volterra.tex
Revise statement of lem:perturbed_volterra
Propose revisions to the text around the statement too.

@@
 We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
-
-\begin{lemma}\label{lem:perturbed_volterra}
-Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
-\[ f = \Big[\hardpart +\softpart \Big] f + g \]
-given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.
-\end{lemma}
-
-We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction.
-Then the result follows by the contraction mapping theorem.
-
 \begin{thm}\label{thm:general_volterra}
-    Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
+In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
+Then the Volterra equation
+\[f = \volterra f\]
+has a unique solution $f$ in the affine subspace
+\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
+of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
+Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
+\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
 Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}.
@@
 of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}.
-The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
 \end{thm}
-
-We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
-Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.
-
-%%\begin{thm}
-%%Let $\Omega$ be an acute-angled sector around $0$ in the complex plane.
-\textcolor{DarkTurquoise}{I don't think it's really necessary for $\Omega$ to have a sharp point at $0$, but the condition of being an acute-angled sector is sufficient and easy to state.}
-
-%%Consider a Volterra operator
-%%\[ \mathcal{V} = p + \partial^{-1} \circ q + \mathcal{R} \]
-%%over $\Omega$ which can be decomposed, as shown above, into the sum of a zeroth-order part $p$, a first-order part $\partial^{-1} \circ q$, and an effectively higher-order part $\mathcal{R}$.
-To be precise, $\mathcal{R}$ is supposed to be an integral operator of the form
-%%\[ [\mathcal{R}\varphi](a) = \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta \]
-%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
-
-%%Assume, furthermore, that:
-%%\begin{itemize}
-%%\item There's some $c \in (0, \infty)$ for which
-%%$|p(a)| \lesssim e^{c|\zeta(a)|}$ and $|q(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$.
-%%\item $p$ and $q$ extend holomorphically over $\zeta = 0$.
-%%\item $p$ has a simple zero at $\zeta = 0$.
-%%\end{itemize}
-%%Let $p_1$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
-
-%%Under these conditions, let's try to solve the regular singular Volterra equation
-%%\[ \mathcal{V}f = 0. \]
-%%The leading-order part of the equation,
-%%\[ \big[p_1 \zeta + \partial^{-1} \circ q_0\big]f = 0, \]
-%%has $\zeta^{\tau-1}$ as a solution, where $\tau = p_1/q_0$.
-If we guess that the function spaces defined in Section~\ref{fn-spaces} are well suited for this problem, we might hope for the full equation to have a solution of the form
-%%\[ f = \zeta^{\tau-1} + f_*, \]
-%%where $f_* \in \holoL{\infty, 1-\tau-\epsilon}_Z(\Omega)$ for some $Z \in \C$. When $Z\Omega$ is in the right half-plane and $|Z|$ is large enough, there is in fact a unique solution of this form.
-%%\end{thm}
-
+\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
+Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
+%--------
+This result will follow from a more general result about inhomogeneous equations.
+\begin{lemma}\label{lem:perturbed_volterra}
+In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
+Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
+Then the inhomogeneous Volterra equation
+\[ f = \volterra f + g, \]
+has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
+
+\textcolor{RoyalBlue}{Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
+\[ f = \Big[\hardpart +\softpart \Big] f + g \]
+given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.}
+\end{lemma}
+\textcolor{RoyalBlue}{We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction.
+Then the result follows by the contraction mapping theorem.}\par
+%---------
+We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
+The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.
+
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular function space.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+
+%%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.
+
+%%We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, with the help of Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part}, which can be used to show that $\softpart f_0$ is regular enough to serve as the inhomogeneous term in the lemma.
 \subsection{Acknowledgements}

### 2023-08-07 reg-sing-volterra.tex
Start switching to 0 and \star for prototype and perturbation parts
Change macro definitions for operator and kernel parts. Switch hand-written
instances to macros. Introduce macros for solution parts, but leave all
instances hand-written for now.

@@
 \newcommand{\volterra}{\mathcal{V}}
-\newcommand{\hardpart}{\mathcal{V}_\text{basic}}
-\newcommand{\softpart}{\mathcal{V}_\text{extra}}
-\newcommand{\hardker}{k_\text{basic}}
-\newcommand{\softker}{k_\text{extra}}
+\newcommand{\hardpart}{\mathcal{V}_0}
+\newcommand{\softpart}{\mathcal{V}_\star}
+\newcommand{\hardker}{k_0}
+\newcommand{\softker}{k_\star}
+\newcommand{\solproto}{f_0}
+\newcommand{\solptb}{f_\star}
 
@@
 \begin{itemize}
-\condconst{diag}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
-\[ \big| k_\text{extra} (a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
+\[ \big| \softker(a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
@@
         |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |f| \, |d\zeta| \\
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
     \end{align*}
@@
     \begin{align*}
-         \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
          &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
@@
     The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-    \[ \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
+    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
 \]
     Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
-    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |k_\text{extra}(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
+    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
     we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
@@
 
-%\textcolor{magenta}{[we have to change the definition of $k_\text{basic}$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
+%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
 

### 2023-08-08 reg-sing-volterra.tex
Prove lem:perturbed_volterra

@@
 \begin{thm}\label{thm:general_volterra}
-In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
+In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
 Then the Volterra equation
@@
 \begin{lemma}\label{lem:perturbed_volterra}
-In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
+In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} \textcolor{magenta}{[I don't think we actually use \texttt{cond:slow}]} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}.
 Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
@@
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
-\begin{prop}
+\begin{prop}\label{prop:exp-inclus}
 If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
@@
 \begin{prop}\label{prop:get-contraction}
-Assume $\hardpart$ satisfies {\em Condition \eqref{cond:sing}} and {\em Condition \eqref{cond:diag-basic}}.
-Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-For each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
+Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
+Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
 \end{prop}
@@
 \subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
-
+\begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
+Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
+Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
+Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
+
+To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:exp-inclus} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
+Next, observe that for any $\Lambda'' \ge \Lambda$, the map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda''}(\Omega)$.
+The inclusion $\singexp{\rho-1}{\Lambda}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda''}(\Omega)$ must send the unique fixed point in the smaller space to the unique fixed point in the larger one.
+Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
+\end{proof}
 \begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
-
 %\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
-
 By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$.

### 2023-08-08 reg-sing-volterra.tex
Mark completed tasks on to-do list

@@
 \begin{brainstorm}
-\item \textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.
-\item \textit{(Aaron)} Finish introduction
+\item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
+\begin{itemize}
+    \item Proofread and drop old version.
+\end{itemize}
+\item \textcolor{gray}{\textit{(Aaron)} Finish introduction}
 \begin{itemize}
 \item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}
+\item \textit{(Veronica)} Revise introduction, if desired.
 \end{itemize}
@@
 \begin{itemize}
-        \item \textit{(Aaron)} Add proofs of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra} to Section~\ref{sec:existence and uniqueness}
+        \item \textcolor{gray}{\textit{(Aaron)} Add proof of Lemma~\ref{lem:perturbed_volterra} to Section~\ref{sec:existence and uniqueness}}
+        \item \textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}
         \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.

### 2023-08-08 reg-sing-volterra.tex
Revise proof of thm:general_volterra

@@
 \newcommand{\softker}{k_\star}
+\newcommand{\solwhole}{f}
 \newcommand{\solproto}{f_0}
@@
 Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
-For any $\rho > \tau$, the uniqueness of the solution still holds in the larger affine subspace $f_0 + \singexpalg{\rho-1}(\Omega)$.
-\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
+
+For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
+In other words, lowering $\rho$ into $(\tau, \tau+\epsilon)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$ will leave no solution at all.
+\par\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
 Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}.
@@
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
-\begin{prop}\label{prop:exp-inclus}
+\begin{prop}\label{prop:inclus-ge-exp}
 If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
@@
 Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
-\begin{prop}
-    If $\Lambda'<\Lambda$ and $\sigma'>\sigma$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
+\begin{prop}\label{prop:inclus-lt-pow-gt-exp}
+If $\sigma'>\sigma$ and $\Lambda'<\Lambda$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
 \end{prop}
-
 \begin{proof}
@@
 for $C = \sup_{\Omega}  |\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$.
+\end{proof}
+\begin{prop}\label{prop:inclus-lt-pow-alg}
+When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
+\end{prop}
+\begin{proof}
+For each $\Lambda'$, we can get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
+For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we're ultimately working in the vector space of holomorphic functions on $\Omega$.
+Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
 \end{proof}
@@
 
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+\textcolor{orange}{[Read through and revise]} In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
@@
 
-To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:exp-inclus} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 %\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
+Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}, which satisfies the equation
+\[ \solproto = \hardpart \solproto. \]
+The base point for the construction can be chosen arbitrarily.
+Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\epsilon}(\Omega)$ that makes $\solwhole = \solproto + \solptb$ a solution of
+\begin{equation}\label{eqn:orig-homog}
+\solwhole = \volterra \solwhole.
+\end{equation}
+Observing that
+\begin{align*}
+\volterra \solproto & = \hardpart\solproto + \softpart\solproto \\
+& = \solproto + \softpart \solproto,
+\end{align*}
+we can rewrite the homogeneous equation we're trying to solve as an inhomogeneous equation for $\solptb$:
+\begin{align}
+\solproto + \solptb & = \volterra\solproto + \volterra\solptb \nonumber \\
+& = \solproto + \softpart\solproto + \volterra\solptb \nonumber \\
+\solptb & = \softpart\solproto + \volterra\solptb. \label{eqn:equiv-inhomog}
+\end{align}
+Since we know that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexp{\tau-1+\epsilon}{\lambda_0}(\Omega)$.
+Since $\tau+\epsilon > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$.
+
+Now, we just want to show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
+
+First, suppose $\rho \in (\tau, \tau+\epsilon)$.
+In this case, we can use the inclusion $\singexpalg{\tau-1+\epsilon}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+
+On the other hand, suppose $\rho > \tau+\epsilon$.
+In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\epsilon}(\Omega)$.
+Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+
+%%the inhomogeneous term $\softpart\solproto$ is still in $\singexpalg{\rho-1}(\Omega)$ by Proposition~\ref{prop:inclus-lt-pow-gt-exp}, so Lemma~\ref{lem:perturbed_volterra} still guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found.
+
+\color{RoyalBlue}
 By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$.

### 2023-08-08 reg-sing-volterra.tex
Make new list type for conditions

@@
 % list formatting
-\setlist[itemize]{leftmargin=24mm, rightmargin=12mm}
+\newlist{conditions}{itemize}{1}
+\setlist[conditions]{leftmargin=24mm, rightmargin=12mm}
 \makeatletter
@@
 We also assume:
-\begin{itemize}
+\begin{conditions}
 \cond{star}\label{cond:star} The set $\domain$ is star-shaped around $\zeta = 0$.
@@
 Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
-\end{itemize}
+\end{conditions}
 For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
@@
 where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
-\begin{itemize}
+\begin{conditions}
 \condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
@@
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
-\end{itemize}
+\end{conditions}
 We'll assume that $\tau$ is real and positive.
@@
 For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
-\begin{itemize}
+\begin{conditions}
 \condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
@@
 The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
-\end{itemize}
+\end{conditions}
 This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-\begin{itemize}
+\begin{conditions}
 \condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
@@
 %%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
-\end{itemize}
+\end{conditions}
 \subsubsection{The perturbed operator}\label{setting:perturbed}
@@
 Altogether, we'll require:
-\begin{itemize}
+\begin{conditions}
 \condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
@@
 over all $a, a' \in \domain$.
-\end{itemize}
+\end{conditions}
 Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.

### 2023-08-08 reg-sing-volterra.tex
Mark completed tasks on to-do list

@@
         \item \textcolor{gray}{\textit{(Aaron)} Add proof of Lemma~\ref{lem:perturbed_volterra} to Section~\ref{sec:existence and uniqueness}}
-        \item \textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}
+        \item \textcolor{gray}{\textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}}
+        \begin{itemize}
+            \item Proofread revised proof.
+        \end{itemize}
         \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.
@@
 \color{violet}
-\item \textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.
+\item \textcolor{gray}{\textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.}
 \item Work on acknowledgements

### 2023-08-09 reg-sing-volterra.tex
Add comments to sec:example

@@
 Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$.
-If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\lambda>0$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$ ~\cite[Section 5.6]{diverg-resurg-i}.
+If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\textcolor{magenta}{\Lambda}>0$ \textcolor{magenta}{[I don't think we need $\Lambda > 0$.
+For $\Lambda \le 0$, the Laplace transform should still produce functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$, which in this case will include $z = 0$]} to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$~\cite[Section 5.6]{diverg-resurg-i} \textcolor{magenta}{[I think we want $\Re(z e^{-i\theta}) > \Lambda$]}.
 It is defined by the formula
@@
 %%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by \textcolor{orange}{[are we changing the definition of $\partial^{\nu-1}_{\zeta, a}$ so that $a$ is a point, rather than a $\zeta$ value?]}
 \[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $\Omega$.
+where $p$ is any point on the position domain $\Omega$ \textcolor{orange}{[let's use a different letter here, since $p$ is already used; maybe $b$ for the base point and $a$ for the evaluation point, to match our discussion of $f_0$]}.
 
@@
 
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ and
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$?
+can we do this with Proposition~\ref{prop:smoothing}?]} and
 \[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
@@
 
-    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ \textcolor{magenta}{[to get this from our uniqueness result, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]} and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The result holds for every critical point of $P$.

### 2023-08-09 reg-sing-volterra.tex
Drop old versions of thm:general_volterra and lem:perturbed_volterra

@@
 \begin{itemize}
-    \item Proofread and drop old version.
+    \item \textcolor{gray}{Proofread and drop old version.}
 \end{itemize}
@@
 In other words, lowering $\rho$ into $(\tau, \tau+\epsilon)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$ will leave no solution at all.
-\par\textcolor{RoyalBlue}{Assume $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}, \eqref{cond:slow}} and {\em \eqref{cond:diag-basic}} from Section \ref{setting:basic}.
-Assume $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section \ref{setting:perturbed}.
-Then the Volterra equation
-\[f = \left[ \hardpart + \softpart \right] f\]
-admits a unique solution in the affine subspace
-\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
-of the function space $\singexpalg{\tau-1}(\Omega)$, defined in Section~\ref{fn-spaces}.
-The function $f_0$ is the prototypical solution of \eqref{eqn:test_solution} and it belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.}
 \end{thm}
-\textcolor{RoyalBlue}{We'll prove this result in Sections~\ref{sec:existence and uniqueness}: using Proposition \ref{prop:smoothing} we show that $\softpart$ maps the prototype solution into a more regular function space.
-Then the result follows as a consequence of Lemma \ref{lem:perturbed_volterra}.}\par
-%--------
 This result will follow from a more general result about inhomogeneous equations.
 \begin{lemma}\label{lem:perturbed_volterra}
-In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} \textcolor{magenta}{[I don't think we actually use \texttt{cond:slow}]} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}.
+In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}.
 Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
@@
 has a unique solution $f$ in the space $\singexpalg{\rho-1}(\Omega)$.
-
-\textcolor{RoyalBlue}{Let $g$ be a function in the space $\in\singexp{\sigma+\epsilon}{A}(\Omega)$ defined in Section~\ref{fn-spaces}. The Volterra equation
-\[ f = \Big[\hardpart +\softpart \Big] f + g \]
-given by an operator of the kind described in Sections \ref{setting:basic} and \ref{setting:perturbed}, admits a unique solution $f$ that belongs to $\singexp{\sigma+\epsilon}{\Lambda}(\Omega)$, for every $\Lambda\geq A$ \textcolor{magenta}{[check]}.}
 \end{lemma}
-\textcolor{RoyalBlue}{We'll prove this result in Section~\ref{sec:V is a contraction}: in Proposition \ref{prop:get-contraction} we construct the functions space where $\volterra$ is a contraction.
-Then the result follows by the contraction mapping theorem.}\par
-%---------
-We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
+We'll prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
 The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.
 
-We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular function space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular function space.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
 

### 2023-08-10 reg-sing-volterra.tex
Revise thm:basic_volterra and thm:proto-growth
Add introductory text. Revise the statements, moving both of the the regularity
results into thm:proto-growth. Start reorganizing the proof sections to match.

@@
 \item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}
-\item \textit{(Veronica)} Revise introduction, if desired.
+\item \textcolor{gray}{\textit{(Veronica)} Revise introduction, if desired.}
 \end{itemize}
@@
 \subsection{Main results}\label{sec:results}
-%%\begin{defn}\label{fin-order}
-%%Consider a Volterra operator $\mathcal{V}$ of the form
-%%\[ [\mathcal{V}\varphi](a) = m(a)\,\varphi(a) + \int_{\zeta = 0}^{a} k(a, \cdot)\,\varphi\,d\zeta. \]
-%%We'll say $\mathcal{V}$ is {\em effectively finite-order} over a domain $\Omega$ if there are some $c, c' \in (0, \infty)$ for which
-%%\begin{itemize}
-%%\item $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$
-%%\item $|k(a, a')| \lesssim e^{c|\zeta(a)| + c'|\zeta(a')|}$ over all $a, a' \in \Omega$
-%%\end{itemize}
-%%and at one of the following holds:
-%%\begin{enumerate}
-%%\item\label{case:0th-order} $m$ isn't the zero function.
-%%\item\label{case:pos-order} $m$ is the zero function, and there's some $\lambda \in (0, \infty)$ for which
-%%\[ |k(a, a')| \in O_\text{\rm diag}\big( |\zeta(a) - \zeta(a')|^{\lambda-1} \big), \]
-%%where {\rm ``diag''} means the diagonal in $\Omega^2$.
-%%\end{enumerate}
-%%We'll say $\mathcal{V}$ has order $0$ in case~\ref{case:0th-order}, and order at least $\lambda$ in case~\ref{case:pos-order}.
-%%\end{defn}
+We want to show that when $\volterra$ is a regular singular Volterra operator of the kind described in Section~\ref{setting:perturbed}, the equation $f = \volterra f$ has a unique solution of a certain form.
+For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
 \begin{thm}\label{thm:basic_volterra}
+Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
+\[ f = \hardpart f \]
+has the {\em prototype solution}
+\begin{equation}\label{eqn:test_solution}
+\solproto(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
+\end{equation}
+Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
+\end{thm}
+We'll prove this result in Section~\ref{sec:construction}.
+\color{Tomato}
+\begin{thm}%%\label{thm:basic_volterra}
 Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
@@
 have the {\em prototype solution}
-\begin{equation}\label{eqn:test_solution}
+\begin{equation}%%\label{eqn:test_solution}
 f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
@@
 \end{thm}
-We'll prove this result in Section~\ref{sec:proto-construction-regularity}: by Proposition~\ref{prop:construction} we show that $f_0$ is a solution, and by Proposition~\ref{prop:asymptotic at zero} we show that it scales as desired as $\zeta$ goes to zero.
-
+We'll prove this result in Section~\ref{sec:proto-construction-regularity}.
+Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} bounds it as desired near $\zeta = 0$.
+\color{RoyalBlue}
 \begin{rmk}
@@
 
-\textcolor{RoyalBlue}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
+\textcolor{SeaGreen}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
 \end{rmk}
+\color{black}
+%%To control the growth of $\solproto$ away from $\zeta = 0$, we'll assume that $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}.
+Under this condition, $\solproto$ is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}
+The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
+With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
+The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
 \begin{thm}\label{thm:proto-growth}
-Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}} and {\em \eqref{cond:slow}} from Section~\ref{setting:basic}.
+Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
+
+Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
+\end{thm}
+We'll prove this result in Section~\ref{sec:asymptotics}.
+\color{Tomato}
+\begin{thm}%%\label{thm:proto-growth}
+Suppose $\hardpart$ satisfies both {\em Condition~\eqref{cond:sing}} and {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}.
 Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior at $\zeta = 0$ described above, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior near $\zeta = 0$ described in, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
 \end{thm}
-
-We'll prove this result in Section~\ref{sec:proto-construction-regularity}, Proposition~\ref{prop:asymptotic at infinity}.
+We'll prove this result in Section~\ref{sec:proto-construction-regularity}, where it's restated as Proposition~\ref{prop:asymptotic at infinity}.
+\color{black}
 \begin{thm}\label{thm:general_volterra}
@@
 \begin{align*}
-    |k(a,a')&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
     &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
@@
 \subsubsection{Construction}\label{sec:construction}
-
+\color{Tomato}
 \begin{prop}\label{prop:construction}
@@
 \end{prop}
-
-\begin{proof}
+\color{black}
+\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
     Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
@@
 \end{proof}
-
+\color{Tomato}
 \begin{rmk}
@@
 \end{rmk}
-
+\color{black}
 %In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$
@@
 \end{prop}
-
+\color{Tomato}
 \begin{rmk}
@@
 \end{rmk}
-
-\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
+\color{black}
+
+%%\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
+\begin{proof}
 We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
@@
 
-Let $\Omega_{a}$ be a simply connected open set $\Omega_a\subset\C$ that touches but doesn't contain $\zeta=a$ and let $\Gamma_a^\theta$ be the ray that leaves $a$ at angle $\theta$.
-If $\Gamma_a^\theta$ is contained in $\Omega_a$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\Omega_a)$ with $\sigma>-1$ and $\textcolor{magenta}{\Lambda}>0$ \textcolor{magenta}{[I don't think we need $\Lambda > 0$.
-For $\Lambda \le 0$, the Laplace transform should still produce functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$, which in this case will include $z = 0$]} to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > 0$~\cite[Section 5.6]{diverg-resurg-i} \textcolor{magenta}{[I think we want $\Re(z e^{-i\theta}) > \Lambda$]}.
+Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
+If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}.
 It is defined by the formula
@@
 \begin{equation}\label{laplace:int} 
-    \laplace_{\zeta, a}^{\theta} f := \int_{\Gamma_{a}^\theta} e^{-z\zeta} f\, d\zeta
+\laplace_{\zeta, \alpha}^{\theta} f := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} f\, d\zeta
 \end{equation}
@@
 %%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, a}$ is defined by \textcolor{orange}{[are we changing the definition of $\partial^{\nu-1}_{\zeta, a}$ so that $a$ is a point, rather than a $\zeta$ value?]}
-\[ [\partial^{\nu-1}_{\zeta, a} f](p) := \frac{1}{\Gamma(1-\nu)} \int_{a}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $\Omega$ \textcolor{orange}{[let's use a different letter here, since $p$ is already used; maybe $b$ for the base point and $a$ for the evaluation point, to match our discussion of $f_0$]}.
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} f\,d\zeta \]
+for each $a \in \domain_\alpha$.
 
@@
 \begin{align*}
-\fracderiv{\lambda}{\zeta}{a}\,\fracderiv{\mu}{\zeta}{a} & = \fracderiv{\lambda+\mu}{\zeta}{a} & \lambda, \mu \in (-\infty, 0),
+\fracderiv{\nu}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\nu+\mu}{\zeta}{\alpha} & \nu, \mu \in (-\infty, 0),
 \end{align*}
@@
 
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$?
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that if $\partial^{-\nu}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$?
 can we do this with Proposition~\ref{prop:smoothing}?]} and
-\[ \laplace_{\zeta,a}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-for all $\lambda \in (0, \infty)$.
+\[ \laplace_{\zeta,a}\,\partial^{-\nu}_{\zeta} \varphi = z^{-\nu} \laplace_{\zeta, a} \varphi \]
+for all $\nu \in (0, \infty)$.
 This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
@@
 
+\begin{rmk}
+    Increasing the regularity in the position domain, then the Laplace transform gives something which is faster decaying in the frequency domain. This is a general feature of the Laplace transform.
+\end{rmk}
+
 \subsection{Going to the position domain}
@@
 \end{enumerate}
+
+Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that
+
+\begin{align*}
+    f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
+    &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
+    &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
+\end{align*}
 

### 2023-08-10 reg-sing-volterra.tex
Split up bounds on perturbed kernel
Also, drop old versions of thm:basic_volterra and thm:proto-growth.

@@
 \condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
-\[ \big| \hardker(a, a') \big| \leq \,  \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+\[ \big| \hardker(a, a') \big| \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
@@
 \condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
-\[ \big| \softker(a, a') \big| \leq \textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
@@
 We'll prove this result in Section~\ref{sec:construction}.
-\color{Tomato}
-\begin{thm}%%\label{thm:basic_volterra}
-Let $\hardpart$ be the operator described in Section~\ref{setting:basic} and assume it satisfies {\em Condition \eqref{cond:sing}}. Then the regular singular Volterra equation
-\[ f = \hardpart f \]
-have the {\em prototype solution}
-\begin{equation}%%\label{eqn:test_solution}
-f_0(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
-\end{equation}
-Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
-
-The magnitude $|f_0|$ is bounded by a constant multiple of $|\zeta|^{\tau-1}$ near $\zeta = 0$.
-
-%%The solution $f_0$ scales like $\zeta^{\tau-1}$ as $\zeta$ goes to zero. To be precise, as $\zeta$ goes to zero, $|f_0/\zeta^{\tau-1}|$ settles into a compact interval that doesn't include zero.
-\end{thm}
-We'll prove this result in Section~\ref{sec:proto-construction-regularity}.
-Proposition~\ref{prop:construction} shows that $f_0$ is a solution, and Proposition~\ref{prop:asymptotic at zero} bounds it as desired near $\zeta = 0$.
 \color{RoyalBlue}
@@
 We'll prove this result in Section~\ref{sec:asymptotics}.
-\color{Tomato}
-\begin{thm}%%\label{thm:proto-growth}
-Suppose $\hardpart$ satisfies both {\em Condition~\eqref{cond:sing}} and {\em Condition~\eqref{cond:slow}} from Section~\ref{setting:basic}.
-Then the solution $f_0$ from {\em Theorem~\ref{thm:basic_volterra}} is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} In light of the behavior near $\zeta = 0$ described in, this tells us that $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
-\end{thm}
-We'll prove this result in Section~\ref{sec:proto-construction-regularity}, where it's restated as Proposition~\ref{prop:asymptotic at infinity}.
-\color{black}
 \begin{thm}\label{thm:general_volterra}
@@
  When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.
+On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by letting $a,a'$ close enough to $\zeta=0$.
+If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
+
+\begin{align*}
+    |\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|}\\
+    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} 
+\end{align*}
+
+On the other hand, we can make the kernel $\softker$ arbitrary small by letting $a,a'$ close enough to $\zeta=0$.
+Assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$, by Condition \eqref{cond:eps-lambda}
+
+\begin{align*}
+    |\softker(a,a')|&\lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+    &\lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}
+\end{align*}
+
+Hence, collecting these results together, if $a,a'$ are close enough to $\zeta=0$, there exists a constant $\sigma>\tau$ such that
+
+\[
+    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
+\]
+
+We'll use this fact is Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
+
+ \color{Tomato}
+
  Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
@@
 
+\color{black}
+
 Similarly, we can estimate the kernel $k$ far from $\zeta=0$.
@@
 
+\begin{align*}
+    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+    &\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+    &\lesssim \big(1 + \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+\end{align*}
+Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
+
+\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+We deduce that
+
+\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+for some constant $M>0$.
+
+\color{Tomato}
 \begin{align*}
@@
 \end{verify}
+\color{black}
 
@@
 
-is bounded by $C_1 \, |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big)$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
-
-\begin{align*}
-|f_0| &  \leq C_1 |\zeta(a)|^\tau \, \exp\big(\tfrac{3}{2}\varepsilon\delta\big) \left\vert  \frac{p(b)}{p(a)}\right\vert \\
-& =  C_2 |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
-&  \leq C_3 |\zeta(a)|^{\tau-1}.
+is bounded by $ |\zeta(a)|^\tau$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
+
+\begin{align*}
+|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
+& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
+&  \lesssim |\zeta(a)|^{\tau-1}.
 \end{align*}
@@
 Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
-If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, a}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}.
+If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, \alpha}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}.
 It is defined by the formula
@@
     \begin{align*}
-        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{p(\zeta(a))}|\zeta(a')|^r  &\leq C_1 \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
-        & =C_1 |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
-        &=C_1 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
-        &\leq C_2 |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
+        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{|p(\zeta(a))|}|\zeta(a')|^r  &\lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
+        & \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
+        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
+        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
     \end{align*}
@@
 
-\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\leq C +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]
+\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\lesssim 1 +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]
 
@@
 
-\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert\textcolor{magenta}{\lesssim} \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')} | \]
+\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert \lesssim \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')|}  \]
 
@@
 
-Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that
-
-\begin{align*}
-    f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
-    &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
-    &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
-\end{align*}
+%Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. %Following the computation we did above we get that
+
+%\begin{align*}
+ %   f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
+  %  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
+  %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
+%\end{align*}
 

### 2023-08-10 reg-sing-volterra.tex
Add introductory text for thm:general_volterra
Taking advantage of the introductory text, state thm:general_volterra and
lem:perturbed_volterra more simply.

@@
 We'll prove this result in Section~\ref{sec:asymptotics}.
+
+%%---------
+%%Once we've understood the prototype solution $\solproto$, we can deform it to a solution of the equation we originaly set out to solve---the one involving the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}.
+
+%%The prototype solution $\solproto$ will be our reference point for studying the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}.
+
+%%Once we've understood the prototypical operator $\hardpart$, we perturb it to the more general operator $\volterra = \hardpart + \softpart$ described in Section~\ref{setting:perturbed}.
+The prototypical
+
+%%Since $\hardpart$ is the regular singular part of the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed},
+%%---------
+When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we're trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
+We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
 \begin{thm}\label{thm:general_volterra}
-In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies Condition \eqref{cond:eps-lambda} from Section~\ref{setting:perturbed}.
-Then the Volterra equation
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
 \[f = \volterra f\]
@@
 \[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
-of the function space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
-Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the function space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
+Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
 
@@
 \begin{lemma}\label{lem:perturbed_volterra}
-In the perturbed operator $\volterra = \hardpart +\softpart$ from Section~\ref{setting}, suppose the prototypical part $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic} from Section~\ref{setting:basic}, and the perturbation $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}} from Section~\ref{setting:perturbed}.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
 Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
-Then the inhomogeneous Volterra equation
+Then the inhomogeneous equation
 \[ f = \volterra f + g, \]
@@
 
-We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular function space.
+We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.

### 2023-08-11 reg-sing-volterra.tex
Work on "Action on integral operators"

@@
 \color{black}
-%%To control the growth of $\solproto$ away from $\zeta = 0$, we'll assume that $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}.
-Under this condition, $\solproto$ is uniformly of exponential type $\lambda_0$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.}
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
@@
 Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.
-They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{(\Lambda+\varepsilon)|x|}$.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
 With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
@@
 \subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
- When $\hardpart$ satisfies Condition \eqref{cond:sing} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.
-On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by letting $a,a'$ close enough to $\zeta=0$.
+\subsubsection{Overview}
+The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
+\subsubsection{Bounds near $\zeta = 0$}
+When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.
+
+Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$.
+However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin.
+Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
+\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
+\begin{align*}
+|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
+&\leq \frac{\tau}{|\zeta(a)|} + C \\
+&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
+&\le \frac{\tau + C\delta}{|\zeta(a)|}
+\end{align*}
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
+\textcolor{orange}{[\ldots]}
+
+\color{RoyalBlue}
+On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by keeping $a,a'$ close enough to $\zeta=0$.
 If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
-
-\begin{align*}
-    |\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|}\\
-    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} 
-\end{align*}
-
-On the other hand, we can make the kernel $\softker$ arbitrary small by letting $a,a'$ close enough to $\zeta=0$.
-Assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$, by Condition \eqref{cond:eps-lambda}
+\begin{align*}
+|\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)}\right\vert +\frac{\tau}{|\zeta(a)|}\\
+&\leq \varepsilon +\frac{\tau}{|\zeta(a)|}.
+\end{align*}
+\textcolor{magenta}{[Condition~\eqref{cond:sing} doesn't say that for every $\varepsilon > 0$, this bound holds for small enough $\delta > 0$.
+It only says that when $\delta > 0$ is small enough, the bound holds for some $\varepsilon$]}
+\color{black}
+
+Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
+\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+over all $a, a' \in \domain$, which means that
+\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
+over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+\par\color{RoyalBlue}
+Condition \eqref{cond:eps-lambda} gives a bound on $\softker$, which can be made arbitrarily small by keeping $a,a'$ close enough to $\zeta=0$.
+Indeed, assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
 
@@
 
-Hence, collecting these results together, if $a,a'$ are close enough to $\zeta=0$, there exists a constant $\sigma>\tau$ such that
+Hence, collecting these results together, we can find a constant $\sigma>\tau$ such that for $a,a'$ close enough to $\zeta=0$
 
@@
 \]
-
-We'll use this fact is Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
+We'll use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
 
@@
 \color{black}
-
+\subsubsection{Bounds far from the diagonal}
 Similarly, we can estimate the kernel $k$ far from $\zeta=0$.
@@
 \end{equation}
-for all $a, a' \in \near$ (see Section \ref{sec:bounds on k}).
-By choosing a small enough positive radius $R$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$.
+for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}).
+By choosing a small enough positive radius $R$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$.
 Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.
@@
 
-\color{RoyalBlue}
-By Theorem \ref{thm:basic_volterra} and \ref{thm:proto-growth} (proved in Section \ref{sec:construction}), there exists a function $f_0\in \singexp{\tau-1}{\lambda_0}(\Omega)$ such that $\hardpart f_0= f_0$.
-Hence we can solve the Volterra equation
-
-\begin{equation}\label{eqn:volterra}
-    f = \volterra f
-\end{equation}
-
-by the following \textit{ansatz}
-
-\[ f= f_0 + f_\star\]
-
-with $f_\star\in\singexpalg{\tau-1+\epsilon}(\Omega)$. Plugging-it in equation \eqref{eqn:volterra} we get
-
-\begin{align*}
-    f_0 + f_\star & = \hardpart\,f_0 - \softpart \,f_0 + \volterra f_\star \\
-f_0 + f_\star & = f_0 + \softpart \,f_0 + \volterra f_\star \\
-f_\star & = \softpart \,f_0 + \volterra f_\star
-\end{align*}
-
-Therefore, solving the equation \eqref{eqn:volterra} is equivalent to finding a fixed point $f_\star$ of the affine-linear map
-
-\[ f_\star \mapsto \softpart\,f_0 + \volterra f_\star. \]
-
-This follows by Lemma \ref{lem:perturbed_volterra}.
 \end{proof}
@@
 %%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} f\,d\zeta \]
+For $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{-\nu}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} f\,d\zeta \]
 for each $a \in \domain_\alpha$.
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\nu}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\nu+\mu}{\zeta}{\alpha} & \nu, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).
+\par\color{RoyalBlue}
+For $\nu' \in (-\infty, 1)$, the fractional integral $\partial^{\nu'-1}_{\zeta, \alpha}$ is defined by \textcolor{orange}{[$-\nu = \nu'-1$ and $1-\nu = \nu'$]}
+\[ [\partial^{\nu'-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu')} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu'} f\,d\zeta \]
+for each $a \in \domain_\alpha$.
+\color{black}
+
+It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.
 
@@
 %\end{align*}
-
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that if $\partial^{-\nu}_{\zeta,a} \varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$ \textcolor{orange}{[under what condition on $\varphi$?
-can we do this with Proposition~\ref{prop:smoothing}?]} and
-\[ \laplace_{\zeta,a}\,\partial^{-\nu}_{\zeta} \varphi = z^{-\nu} \laplace_{\zeta, a} \varphi \]
-for all $\nu \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\Omega_a)$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ and maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$.
+Indeed, if $\zeta(a)\neq 0$ \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
+
+\begin{align*}
+    \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
+    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\,  \zeta(a)\, \varphi \, d\zeta\\
+    &=\frac{\zeta(a)}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta
+\end{align*}
+Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) \textcolor{orange}{- \alpha}}$, it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$.
+Hence by Proposition \ref{prop:smoothing}
+
+\[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
+
+Multiplication by \textcolor{orange}{$\zeta - \alpha$} then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed.
+In particular, $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
+Thus, using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that
+\[ \laplace_{\zeta,\alpha}^{\theta}\,\fracderiv{-\nu}{\zeta}{\alpha} \varphi = z^{-\nu} \laplace_{\zeta, \alpha}^{\theta} \varphi \]
+for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\domain_\alpha)$ and $\sigma>-1$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \begin{equation}%%\label{id:L-mult}
-\laplace_{\zeta,a}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,a}^\theta \varphi.
+\laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi.
 \end{equation}

### 2023-08-13 reg-sing-volterra.tex
Draft overview of main result proofs

@@
 As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.
-Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}$ that contains all functions of exponential type.
-Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
+Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
+Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
 \begin{prop}\label{prop:inclus-lt-pow-gt-exp}
@@
 \subsection{Overview}
+In this section, we'll prove the results stated in Section~\ref{sec:results}.
+Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.
+
+The prototype solution $\solproto$ is our initial guess.
+When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}.
+We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+
+To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.
+
+When we apply $\volterra$ again, it contracts the perturbation term in $\singexpalg{\tau-1+\epsilon}(\domain)$.
+More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$.
+We'll prove this in Section~\ref{sec:V is a contraction}.
+
+We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
+\[ \solproto + \solptb, \]
+with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
+\[ \solproto + \softpart \solproto + \volterra \solptb, \]
+where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$.
+The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
+\[ \solptb = \softpart \solproto + \volterra \solptb. \]
+We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
+
+%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations
+
+%%To see what the perturbation $\softpart$ does to $\solproto$, we first show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+We then show in Section~\ref{sec:image under soft_part} that $\softpart$ has the
+
+%%The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+In this section, we prove the results, showing that our solution method works as expected.
+
+%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}.
+We start by constructing the {\em prototype solution} $\solproto$ of the simpler equation $\solwhole = \hardpart \solwhole$, which has essentially the same singularity.
+
+%%The plan starts with the explicit
+
+%%The first step of the plan is to construct the {\em prototype solution} $\solproto$, which satisfies the simpler equation $\solwhole = \hardpart \solwhole$.
+In Section~\ref{sec:proto-construction-regularity}, we
+
+%%with the ultimate goal of proving Theorem~\ref{thm:general_volterra}.
+This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by first constructing the {\em prototype solution} $\solproto$, which explicitly describes what's going on near the singularity, and then adding a less singular perturbation $\solptb$.
+
+%%the explicit {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ can be perturbed uniquely
+
+%%when we perturb the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ to the more general equation $\solwhole = \volterra \solwhole$, the prototype solution $\solproto$ gets perturbed
+
+%%the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where the {\em prototype solution} $\solproto$ captures
+
+%%This equation says that once we have the {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$, we can
+
+%%This theorem says that if we start with a certain explicit solution $\solproto$ of the equation $\solwhole = \hardpart \solwhole$,
+
+%%This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by splitting $\volterra$ into the singular part $\hardpart$ and the perturbation $\softpart$,
+
+%%constructing an explicit {\em prototype solution} of the equation $\solwhole = \hardpart \solwhole$
+
+%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
 \begin{brainstorm}
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
-\textcolor{orange}{[\ldots]}
-
-\color{RoyalBlue}
-On the one hand, we can make the kernel $\hardker$ arbitrary close to $\frac{\tau}{|\zeta(a)|}$, by keeping $a,a'$ close enough to $\zeta=0$.
-If we choose $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
-\begin{align*}
-|\hardker(a,a')| &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)}\right\vert +\frac{\tau}{|\zeta(a)|}\\
-&\leq \varepsilon +\frac{\tau}{|\zeta(a)|}.
-\end{align*}
-\textcolor{magenta}{[Condition~\eqref{cond:sing} doesn't say that for every $\varepsilon > 0$, this bound holds for small enough $\delta > 0$.
-It only says that when $\delta > 0$ is small enough, the bound holds for some $\varepsilon$]}
-\color{black}
 
@@
 
- \color{Tomato}
-
- Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
-
-\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]
-
-Then,
-
-\begin{align*}
-    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
-    &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-    &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
-    &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
-\end{align*}
-
-The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small.
+% \color{Tomato}
+
+ %Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
+
+%\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]
+
+%Then,
+
+%\begin{align*}
+ %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+ %   &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+  %  &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
+   % &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
+%\end{align*}
+
+%The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small.
 We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
@@
 
-\color{Tomato}
-\begin{align*}
-    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
-    &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-    &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+%\color{Tomato}
+%\begin{align*}
+ %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+  %  &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+   % &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
     %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
-\end{align*}
-Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
-
-\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-We deduce that
-
-\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.
-
-\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely
-
-\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}
-
-\begin{verify}
-    \begin{align*}
-        \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
-        &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
-        &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
-    \end{align*}
-\end{verify}
-\color{black}
+%\end{align*}
+%Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
+
+%\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+%We deduce that
+
+%\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+%with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.
+
+%\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely
+
+%\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
+
+%with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}
+
+%\begin{verify}
+ %   \begin{align*}
+  %      \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
+   %     &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
+    %    &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
+    %\end{align*}
+%\end{verify}
+%\color{black}
 
@@
 for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}).
-By choosing a small enough positive radius $R$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < R$.
-Complementarily, let $\far$ be the part of $\domain$ where $R \le |\zeta|$.
+By choosing a small enough positive radius $\textcolor{orange}{\delta}$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$.
+Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.
 
@@
 Let's set $\Lambda > \lambda_\Delta$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge R$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt. \]
+Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \textcolor{orange}{\delta}$ for these points:
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt.
+\]
 
@@
 \begin{align*}
-\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R} \int_0^{1/5} t^{\rho-1}\;dt \\
-& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)R}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
 \end{align*}
@@
 \begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)R(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)R}.
-\end{align*}
-
-We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 R^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}.
+\end{align*}
+
+We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 \textcolor{orange}{\delta}^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
 This completes our proof of Proposition~\ref{prop:get-contraction}.
@@
 for each $a \in \domain_\alpha$.
-\par\color{RoyalBlue}
-For $\nu' \in (-\infty, 1)$, the fractional integral $\partial^{\nu'-1}_{\zeta, \alpha}$ is defined by \textcolor{orange}{[$-\nu = \nu'-1$ and $1-\nu = \nu'$]}
-\[ [\partial^{\nu'-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu')} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu'} f\,d\zeta \]
-for each $a \in \domain_\alpha$.
-\color{black}
+%\par\color{RoyalBlue}
+%For $\nu' \in (-\infty, 1)$, the fractional integral $\partial^{\nu'-1}_{\zeta, \alpha}$ is defined by \textcolor{orange}{[$-\nu = \nu'-1$ and $1-\nu = \nu'$]}
+%\[ [\partial^{\nu'-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu')} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu'} f\,d\zeta \]
+%for each $a \in \domain_\alpha$.
+%\color{black}
 
@@
 %\end{align*}
-For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ and maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$.
-Indeed, if $\zeta(a)\neq 0$ \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
+For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ which is singular at $\zeta=\alpha$ but it has a smoothing effect on functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$.
+In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
 
@@
     \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
-    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\,  \zeta(a)\, \varphi \, d\zeta\\
-    &=\frac{\zeta(a)}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta
-\end{align*}
-Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) \textcolor{orange}{- \alpha}}$, it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$.
+    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \zeta(a)\, \varphi \, d\zeta\\
+    &=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta
+\end{align*}
+Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.
 Hence by Proposition \ref{prop:smoothing}
 
-\[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)\textcolor{orange}{- \alpha}}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
-
-Multiplication by \textcolor{orange}{$\zeta - \alpha$} then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed.
+\[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
+
+Multiplication by $\zeta - \alpha$ then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed.
 In particular, $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.

### 2023-08-14 reg-sing-volterra.tex
Conclude new whole kernel bound near zeta = 0
Add the conclusion and drop the old version.

@@
 \newcommand{\softpart}{\mathcal{V}_\star}
+\newcommand{\kerwhole}{k}
 \newcommand{\hardker}{k_0}
@@
 \subsubsection{Overview}
-The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined
+The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$.
+We'll use these bounds in Section~\ref{sec:V is a contraction}.
+\textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else?
+If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
 \subsubsection{Bounds near $\zeta = 0$}
-When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $k$ near $\zeta=0$.
+When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.
 
@@
 over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-\par\color{RoyalBlue}
-Condition \eqref{cond:eps-lambda} gives a bound on $\softker$, which can be made arbitrarily small by keeping $a,a'$ close enough to $\zeta=0$.
-Indeed, assuming $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
-
-\begin{align*}
-    |\softker(a,a')|&\lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-    &\lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}
-\end{align*}
-
-Hence, collecting these results together, we can find a constant $\sigma>\tau$ such that for $a,a'$ close enough to $\zeta=0$
-
-\[
-    |k(a,a')|\leq \frac{\sigma}{|\zeta(a)|}
-\]
-We'll use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
-
-% \color{Tomato}
-
- %Let $\varepsilon>0$, we can choose $\delta$ such that for every $\zeta(a)<\delta$ and $\zeta(a') <\delta$
-
-%\[ \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert \leq \varepsilon\]
-
-%Then,
-
-%\begin{align*}
- %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
- %   &\leq \left\vert\hardker(a,a')-\frac{\tau}{\zeta(a)} \right\vert +\frac{\tau}{|\zeta(a)|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-  %  &\leq \varepsilon +\frac{\tau}{|\zeta(a)|} + \textcolor{magenta}{C_k}\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta (2\delta)}\\
-   % &\leq \frac{\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} }{|\zeta(a)|}
-%\end{align*}
-
-%The constant $\sigma:=\varepsilon\delta+\tau+ \textcolor{magenta}{C_k} (2\delta)^\epsilon e^{2\delta \lambda_\Delta} > \tau $, and by choosing $\delta$ small enough we can make $\sigma-\tau$ arbitrary small.
-We will use this fact in Sections \ref{sec:V is a contraction} and \ref{sec:existence and uniqueness}.
-
-\color{black}
+
+Putting these results together, we see that for any $\sigma > \tau$, we can ensure that
+\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
+by keeping $a$ and $a'$ close enough to $\zeta = 0$.
 \subsubsection{Bounds far from the diagonal}

### 2023-08-14 reg-sing-volterra.tex
Drop remnants of old layout for results on the prototype solution
Also, revise overview of main result proofs.

@@
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \textcolor{orange}{\cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}}.
+Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}.
 
@@
 When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}.
-We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+In addition, $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$, as shown in Section~\ref{sec:asymptotics}.\textcolor{RoyalBlue}{We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.}
 
@@
 
-When we apply $\volterra$ again, it contracts the perturbation term in $\singexpalg{\tau-1+\epsilon}(\domain)$.
+When we apply $\volterra$ again, it contracts the perturbation term $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\domain)$.
 More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$.
@@
 
+We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
+\[ \solproto + \solptb, \]
+with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
+\[ \solproto + \softpart \solproto + \volterra \solptb, \]
+where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$.
+The contraction mapping theorem guarantees the existence and uniqueness of the fixed point
+\[ \solptb = \softpart \solproto + \volterra \solptb. \]
+We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
+
+\color{RoyalBlue}
 We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
@@
 We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
-
+\color{black}
 %%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations
@@
 \subsubsection{Construction}\label{sec:construction}
-\color{Tomato}
-\begin{prop}\label{prop:construction}
-    The function 
-    \begin{equation}%%\label{eqn:test_solution}
-    f_0(a)=\frac{p(b)}{p(a)} \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]
-   \end{equation}
-is a solution of the Volterra equation $\hardpart f_0=f_0$, for some $b\in\Omega$. We call $f_0$ a prototype solution.  
-\end{prop}
-\color{black}
 \begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
@@
 \subsubsection{Regularity}\label{sec:asymptotics}
-
+Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
+%%\begin{rmk}
+%%{\em Propositions \ref{prop:asymptotic at zero}} and \ref{prop:asymptotic at infinity} together prove {\em Theorem \ref{thm:proto-growth}}. 
+%%\end{rmk}
 \begin{prop}\label{prop:asymptotic at zero}
@@
 \begin{proof}
-The proof follows the argument we use at the end of the proof of proposition \ref{prop:construction}.
+The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
 In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
@@
 \end{proof}
-\color{Tomato}
-\begin{rmk}
-   {\em Proposition \ref{prop:construction}} and {\em Proposition \ref{prop:asymptotic at zero}} together prove {\em Theorem \ref{thm:basic_volterra}}. 
-\end{rmk}
-\color{black}
-%In fact, if we assume $q$ to be more regular near $\zeta=0$, we get that $|f_0|/\zeta^{\tau-1}$
-
 \begin{prop}\label{prop:asymptotic at infinity}
@@
 Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
-Then the prototype solution $f_0$ constructed in {\em Proposition \ref{prop:construction}} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+Then the prototype solution $f_0$ defined in \eqref{eqn:test_solution} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
 \end{prop}
-\color{Tomato}
-\begin{rmk}
-    {\em Proposition \ref{prop:asymptotic at infinity}} is an equivalent formulation of {\em Theorem \ref{thm:proto-growth}}.
-\end{rmk}
-\color{black}
-
-%%\begin{proof}[Proof of Proposition~\ref{prop:asymptotic at infinity}]
 \begin{proof}
@@
           |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
-          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \textcolor{magenta}{\lesssim}  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
+          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
       \end{align*}
@@
 for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}).
-By choosing a small enough positive radius $\textcolor{orange}{\delta}$ \textcolor{orange}{[let's choose $R$ or $\delta$ to use both here and in Section~\ref{sec:bounds on k}]}, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$.
+By choosing a small enough positive radius $\textcolor{orange}{\delta}$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$.
 Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.
@@
 For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ which is singular at $\zeta=\alpha$ but it has a smoothing effect on functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$.
-In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: \textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
+In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: %\textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
 
@@
 \end{align*}
-Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.
-Hence by Proposition \ref{prop:smoothing}
+Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}.
+This explains the definition of $\softker(a,a')$ with $\zeta(a)-\alpha$ at the denominator (instead of $\zeta(a)$).
+More generally, working in the domain $\domain_\alpha$, we'll adapt the conventions used for $\domain$.} Hence by Proposition \ref{prop:smoothing}
 

### 2023-08-14 reg-sing-volterra.tex
Redo far bound with variable exponent

@@
 If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
-\subsubsection{Bounds near $\zeta = 0$}
+\subsubsection{Bounds near the origin}
 When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.
@@
 by keeping $a$ and $a'$ close enough to $\zeta = 0$.
-\subsubsection{Bounds far from the diagonal}
-Similarly, we can estimate the kernel $k$ far from $\zeta=0$.
-Assuming $\hardpart$ satisfies Condition \eqref{cond:diag-basic} and $\softpart$ satisfies Condition \eqref{cond:eps-lambda}, for $|\zeta(a)|\geq \delta$ and for every $a'\in\Omega$
-
-\begin{align*}
-    |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
+\subsubsection{Bounds away from the origin}
+We can also bound the kernel $\kerwhole$ when $a$ is kept away from $\zeta = 0$.
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:diag-basic} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
+Then
+\begin{align*}
+|\kerwhole(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
 &\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-    &\lesssim \big(1 + \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
 %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
 \end{align*}
-Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
-
-\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-We deduce that
-
-\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-for some constant $M>0$.
-
+over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$.
+Since $|\zeta(a)-\zeta(a')|^\epsilon$ has power-law growth, we can bound it with any exponential.
+In other words, for any $\lambda > \lambda_\Delta$,
+\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain$. It follows that
+\[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$.
 %\color{Tomato}
@@
 \subsubsection{Away from the origin}\label{far-bound}
-Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$. We know from Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} that we can find a constant $M$ for which
-\[ |k(a, \cdot)| \le M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a) - \zeta|} \]
-for all $a \in \far$ (see Section \ref{sec:bounds on k}).
-Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument.
-Applying this bound, we learn that
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$.
+Choosing some $\lambda > \lambda_\Delta$, as discussed in Section~\ref{sec:bounds on k}, we can use Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} to find a constant $M$ for which
+\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
+for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\textcolor{orange}{2}\lambda_\Delta |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
-& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)|\zeta(a)|(1 - t)}\;dt.
-\end{align*}
-Let's set $\Lambda > \lambda_\Delta$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+& \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.
+\end{align*}
+Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
 Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \textcolor{orange}{\delta}$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt.
-\]
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt. \]
 
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration separately.
-At the beginning---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
-\begin{align*}
-\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
-& = e^{-\frac{4}{5}(\Lambda \textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
-\end{align*}
-At the end, we instead use a worst-case estimate on $t^{1-\rho}$:
-\begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda -\textcolor{orange}{2} \lambda_\Delta)\textcolor{orange}{\delta}(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \textcolor{orange}{2}\lambda_\Delta)\textcolor{orange}{\delta}}.
-\end{align*}
-
-We now know that by setting $\Lambda > \textcolor{orange}{2}\lambda_\Delta+ (1/5)^{\rho-1 \textcolor{orange}{\delta}^{-1}}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
-This completes our proof of Proposition~\ref{prop:get-contraction}.
+To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately.
+At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
+\begin{align*}
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\lambda)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\end{align*}
+At the end of the path, we instead use a worst-case estimate on $t^{1-\rho}$:
+\begin{align*}
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}.
+\end{align*}
+
+We now know that by setting $\Lambda > \lambda + \textcolor{orange}{\delta}^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+\textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$.
+To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above.
+To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
 \subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
@@
 
-%Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. %Following the computation we did above we get that
-
-%\begin{align*}
- %   f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
-  %  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)\\
+Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that
+
+\begin{align*}
+  f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
+  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)
   %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
-%\end{align*}
+\end{align*}
+Expanding $p(a)$ near $\zeta=\alpha$,
+
+\begin{align*}
+     \frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(a)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right) 
+\end{align*}
 

### 2023-08-15 reg-sing-volterra.tex
Rewrite main results overview from fixed-point perspective
Also, keep working on the argument that the prototype solution is equivalent to
zeta^(tau - 1) modulo less singular stuff.

@@
 \subsection{Overview}
+The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+We'll now show that the method works by proving those results.
+
+We start by constructing the prototype solution $\solproto$ from the kernel of $\hardpart$, which is the separable operator that gives $\volterra = \hardpart + \softpart$ its regular singularity.
+We'll show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+
+To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$.
+
+Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
+
+%%In Section~\ref{setting}, we built $\volterra$ by taking a separable operator $\hardpart$ with a regular singularity at $\zeta = 0$ and adding a perturbation $\softpart$.
+Correspondingly, our solution method starts with the prototype solution $\solproto$,
+
+%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}.
+Recall that $\volterra$ is the sum of a separable operator $\hardpart$, which has a regular singularity at $\zeta = 0$, and a perturbation $\softpart$.
+
+\color{SeaGreen}
 In this section, we'll prove the results stated in Section~\ref{sec:results}.
@@
 To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$.
 The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.
@@
 
+\color{RoyalBlue}
 We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
@@
 
-\color{RoyalBlue}
+\color{MediumBlue}
 We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
@@
 
-\subsection{How $\softpart$ perturbs the prototype solution \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
+\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
 
@@
 
-\subsection{Showing that $\volterra$ shrinks perturbations \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
+\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
 \subsubsection{Overview}
@@
 To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
-\subsection{Existence and uniqueness of the perturbed solution \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
+\subsection{Existence and uniqueness of a fixed point \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
@@
 
-    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ \textcolor{magenta}{[to get this from our uniqueness result, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]} and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The result holds for every critical point of $P$.
 \end{thm}
+
+ \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
 
@@
 \end{align*}
-Expanding $p(a)$ near $\zeta=\alpha$,
-
-\begin{align*}
-     \frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(a)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right) 
-\end{align*}
-
+Expanding $p(a)$ near $\zeta=\alpha$, we find that $f_{0,\alpha}$ is proportional to
+
+\begin{align*}
+\frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right)
+\end{align*}
+where both the exponential and the denominator are bounded as $\zeta(a)$ approaches $\alpha$.
+
+\color{DarkTurquoise}
+From Condition~\eqref{cond:sing}, we have
+\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < \varepsilon \]
+in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that
+\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
+converges for $a \in \domain_\text{near}$, so we have
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
+for $a \in \domain_\text{near}$. Observe that $|S| \le \varepsilon |\zeta - \alpha|$ in $\domain_\text{near}$.
+
+The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$ and
+
+\[
+\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq 
+\]
+
+We should be able to deduce from this that
+\begin{align*}
+f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
+& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
+\end{align*}
+when we restrict to $\domain_\text{near}$.
+\color{black}
 \end{proof}

### 2023-08-15 reg-sing-volterra.tex
Drop old versions of overview of main results proofs

@@
 This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
-
-%%In Section~\ref{setting}, we built $\volterra$ by taking a separable operator $\hardpart$ with a regular singularity at $\zeta = 0$ and adding a perturbation $\softpart$.
-Correspondingly, our solution method starts with the prototype solution $\solproto$,
-
-%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}.
-Recall that $\volterra$ is the sum of a separable operator $\hardpart$, which has a regular singularity at $\zeta = 0$, and a perturbation $\softpart$.
-
-\color{SeaGreen}
-In this section, we'll prove the results stated in Section~\ref{sec:results}.
-Our arguments will follow the process of solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by Picard iteration.
-
-The prototype solution $\solproto$ is our initial guess.
-When we apply $\volterra = \hardpart + \softpart$ to it, the singular part $\hardpart$ leaves it unchanged, as we'll show in Section~\ref{sec:construction}.
-In addition, $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$, as shown in Section~\ref{sec:asymptotics}.\textcolor{RoyalBlue}{We'll show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.}
-
-To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$.
-The perturbed operator $\volterra$ therefore sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$.
-
-When we apply $\volterra$ again, it contracts the perturbation term $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\domain)$.
-More precisely, by making $\Lambda$ large enough, we can ensure that the subspace $\singexp{\tau+1+\epsilon}{\Lambda}(\domain)$ both contains the perturbation term and is contracted by $\volterra$.
-We'll prove this in Section~\ref{sec:V is a contraction}.
-
-\color{RoyalBlue}
-We can now see that at each stage of the Picard iteration process, we start with an approximate solution of the form
-\[ \solproto + \solptb, \]
-with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives 
-\[ \solproto + \softpart \solproto + \volterra \solptb, \]
-where the perturbation $\solptb$ has been contracted by $\volterra$, and $\softpart f_0$ has been smoothed and it lies in the same function space as $\solptb$.
-The contraction mapping theorem guarantees the existence and uniqueness of the fixed point
-\[ \solptb = \softpart \solproto + \volterra \solptb. \]
-We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
-
-\color{MediumBlue}
-We can now see that at each stage of the Picard iteration process, we have an approximate solution of the form
-\[ \solproto + \solptb, \]
-with $\solptb \in \singexp{\tau-1+\epsilon}{\Lambda}(\domain)$. Applying $\volterra$ gives us the new approximate solution
-\[ \solproto + \softpart \solproto + \volterra \solptb, \]
-where the perturbation $\solptb$ has been contracted by $\volterra$ but also augmented with another $\softpart \solproto$.
-The contraction mapping theorem guarantees that these opposing processes will eventually balance out, bringing us to a unique fixed point where
-\[ \solptb = \softpart \solproto + \volterra \solptb. \]
-We'll fill out the details of this argument in Section~\ref{sec:existence and uniqueness}.
-\color{black}
-%%To prove that the Picard iteration process converges, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ shrinks perturbations
-
-%%To see what the perturbation $\softpart$ does to $\solproto$, we first show in Section~\ref{sec:asymptotics} that $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
-We then show in Section~\ref{sec:image under soft_part} that $\softpart$ has the
-
-%%The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
-In this section, we prove the results, showing that our solution method works as expected.
-
-%%In this section, we'll prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$ from Section~\ref{setting}.
-We start by constructing the {\em prototype solution} $\solproto$ of the simpler equation $\solwhole = \hardpart \solwhole$, which has essentially the same singularity.
-
-%%The plan starts with the explicit
-
-%%The first step of the plan is to construct the {\em prototype solution} $\solproto$, which satisfies the simpler equation $\solwhole = \hardpart \solwhole$.
-In Section~\ref{sec:proto-construction-regularity}, we
-
-%%with the ultimate goal of proving Theorem~\ref{thm:general_volterra}.
-This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by first constructing the {\em prototype solution} $\solproto$, which explicitly describes what's going on near the singularity, and then adding a less singular perturbation $\solptb$.
-
-%%the explicit {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ can be perturbed uniquely
-
-%%when we perturb the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$ to the more general equation $\solwhole = \volterra \solwhole$, the prototype solution $\solproto$ gets perturbed
-
-%%the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where the {\em prototype solution} $\solproto$ captures
-
-%%This equation says that once we have the {\em prototype solution} $\solproto$ of the prototypical regular singular Volterra equation $\solwhole = \hardpart \solwhole$, we can
-
-%%This theorem says that if we start with a certain explicit solution $\solproto$ of the equation $\solwhole = \hardpart \solwhole$,
-
-%%This theorem says that we can solve the regular singular Volterra equation $\solwhole = \volterra \solwhole$ by splitting $\volterra$ into the singular part $\hardpart$ and the perturbation $\softpart$,
-
-%%constructing an explicit {\em prototype solution} of the equation $\solwhole = \hardpart \solwhole$
-
-%%This theorem says that for a perturbed Volterra operator $\volterra = \hardpart + \softpart$ of the kind described in Section~\ref{setting}, the equation $\solwhole = \volterra \solwhole$ has a unique solution of the form $\solproto + \solptb$, where $\solproto = \hardpart \solproto$ and $\solptb$ is a less singular perturbation.
-\begin{brainstorm}
-\item Explain how we're going to prove Theorem~\ref{thm:general_volterra}.
-\item Roughly follow the sections. Eventual goal: make section titles match proof steps.
-\begin{itemize}
-\item Link to subsections during description.
-\end{itemize}
-\item Rough sketch of proof story:
-\begin{itemize}
-    \item Construct prototype solution $f_0$. Show it's in $\singexp{\tau-1}{\lambda_0}$.
-    \item Show that $\softpart$ maps $f_0$ into $\singexp{\tau-1+\varepsilon}{\Lambda}$ for $\Lambda\geq\lambda_\Delta$ (see Corollary \ref{cor:pertub_f0}).
-    \item Show that $\volterra$ contracts $\singexp{\rho-1}{\Lambda}$ when $\rho > \tau$ and $\Lambda$ is big enough (done in Proposition \ref{prop:get-contraction}).
-    \item Use the contraction mapping theorem to prove Lemma~\ref{lem:perturbed_volterra}, and then use that lemma to prove Theorem~\ref{thm:general_volterra}.
-\end{itemize}
-\end{brainstorm}
 \subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
@@
 \[
-\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq 
+\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.}  
 \]

### 2023-08-15 reg-sing-volterra.tex
Reformat whole kernel bounds for move into {sec:V is a contraction}

@@
 The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$.
-We'll use these bounds in Section~\ref{sec:V is a contraction}.
+One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
+%%We'll use these bounds in Section~\ref{sec:V is a contraction}.
 \textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else?
 If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
-\subsubsection{Bounds near the origin}
-When $\hardpart$ satisfies Condition~\eqref{cond:sing} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, we can estimate the kernel $\kerwhole$ near $\zeta=0$.
-
+\begin{prop}\label{prop:whole-ker-near-bound}
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
+\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
+by keeping $a$ and $a'$ close enough to $\zeta = 0$.
+\end{prop}
+\begin{proof}
 Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$.
@@
 \[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
-over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-
-Putting these results together, we see that for any $\sigma > \tau$, we can ensure that
-\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
-by keeping $a$ and $a'$ close enough to $\zeta = 0$.
-\subsubsection{Bounds away from the origin}
-We can also bound the kernel $\kerwhole$ when $a$ is kept away from $\zeta = 0$.
-Suppose $\hardpart$ satisfies Condition~\eqref{cond:diag-basic} and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
-Then
+over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Combining this conclusion with the previous one, we get the desired result.
+\end{proof}
+Another bound, which works when the first argumetn of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
+\begin{prop}\label{prop:whole-ker-far-bound}
+Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
+Choose a subset $\domain_\text{far} \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
+\[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
+over all $a \in \domain_\text{far}$ and $a' \in \domain$.
+\end{prop}
+\begin{proof}
+Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\domain_\text{far}$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that
 \begin{align*}
@@
 &\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
-%&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
-\end{align*}
-over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$.
-Since $|\zeta(a)-\zeta(a')|^\epsilon$ has power-law growth, we can bound it with any exponential.
-In other words, for any $\lambda > \lambda_\Delta$,
-\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
+\end{align*}
+over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since
+\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \]
+grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
+\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
 over all $a, a' \in \domain$. It follows that
-\[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
-over all $a, a' \in \domain$ with  $|\zeta(a)| \ge \delta$.
-%\color{Tomato}
-%\begin{align*}
- %   |k(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
-  %  &\leq \textcolor{magenta}{C_\Delta} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} +\textcolor{magenta}{C_k}\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-   % &\leq \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, \delta |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
-    %&\leq  \big(\textcolor{magenta}{C_\Delta} + \textcolor{magenta}{C_k}\, |\zeta(a)|^{\epsilon-1}\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
-%\end{align*}
-%Since the growth of $|\zeta(a)-\zeta(a')|^\epsilon$ is polynomial, we can roughly estimate it by an exponential factor like
-
-%\[|\zeta(a)-\zeta(a')|^\epsilon\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-%We deduce that
-
-%\[ |k(a,a')| \leq M\, e^{2 \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-%with $M= \textcolor{magenta}{C_\Delta} + \delta \textcolor{magenta}{C_k}$.
-
-%\color{purple}If $\epsilon\in (0,1]$, we actually get a better estimate, namely
-
-%\[ |k(a,a')| \leq M\textcolor{magenta}{(a')}\, e^{ \lambda_\Delta |\zeta(a)-\zeta(a')|} \]
-
-%with $M\textcolor{magenta}{(a')} = \textcolor{magenta}{C_\Delta} + (\delta^{\epsilon-1}+\delta |\zeta(a')|^\epsilon ) \,  \textcolor{magenta}{C_k}$.\color{black}
-
-%\begin{verify}
- %   \begin{align*}
-  %      \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|} & \leq \frac{|\zeta(a)|^\epsilon + |\zeta(a')|^\epsilon}{|\zeta(a)|}\\
-   %     &= |\zeta(a)|^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon\\
-    %    &\leq \delta^{\epsilon-1}+ \delta |\zeta(a')|^\epsilon 
-    %\end{align*}
-%\end{verify}
-%\color{black}
-
-%notice that $\left\vert 1-\frac{\zeta(a')}{\zeta(a)}\right\vert^\epsilon$ is bounded by a constant which depends on $|\zeta(a')|$ (and of course on $\delta$ and $\epsilon$)
-
+\[ |\kerwhole(a,a')| \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+over all $a \in \domain_\text{far}$ and $a' \in \domain$. This simplifies to the desired result.
+\end{proof}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 
-\textcolor{orange}{[Read through and revise]} In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
@@
 for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}).
-By choosing a small enough positive radius $\textcolor{orange}{\delta}$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \textcolor{orange}{\delta}$.
-Complementarily, let $\far$ be the part of $\domain$ where $\textcolor{orange}{\delta} \le |\zeta|$.
+By choosing a small enough positive radius $\delta$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$.
+Complementarily, let $\far$ be the part of $\domain$ where $\delta \le |\zeta|$.
 
@@
 Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \textcolor{orange}{\delta}$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt. \]
+Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
 
@@
 \begin{align*}
-\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\lambda)\textcolor{orange}{\delta}} \int_0^{1/5} t^{\rho-1}\;dt \\
-& = e^{-\frac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
+\int_0^{1/5} t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le e^{-\frac{4}{5}(\Lambda -\lambda)\delta} \int_0^{1/5} t^{\rho-1}\;dt \\
+& = e^{-\frac{4}{5}(\Lambda - \lambda)\delta}\,\tfrac{1}{\rho} \big(\tfrac{1}{5}\big)^\rho.
 \end{align*}
@@
 \begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\textcolor{orange}{\delta}(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\textcolor{orange}{\delta}} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\textcolor{orange}{\delta}}.
-\end{align*}
-
-We now know that by setting $\Lambda > \lambda + \textcolor{orange}{\delta}^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt \\
+& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\delta} \right] \\
+& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}.
+\end{align*}
+
+We now know that by setting $\Lambda > \lambda + \delta^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
 \textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$.
@@
 
- \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
+ %\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
 
@@
 
-The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$ and
-
+The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
+\begin{verify}
+By definition of limit, as $\zeta(a)\to\alpha$ we should get
 \[
-\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.}  
+\left\vert\frac{1}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...}-\frac{1}{p'(\alpha)}\right\vert\leq \varepsilon
 \]
-
-We should be able to deduce from this that
+\end{verify}
+
+\[
+\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.} |\zeta(a)-\alpha| + O(|\zeta(a)-\alpha|^2)
+\]
+
+Therefore, we deduce from this that
 \begin{align*}

### 2023-08-15 reg-sing-volterra.tex
Move whole kernel bounds into {sec:V is a contraction}

@@
 This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
-\subsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
+\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
+
+\subsubsection{Construction}\label{sec:construction}
+\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
+    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
+    \begin{align*}
+        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
+        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
+        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
+        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
+    \end{align*}
+
+    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact, choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+\begin{equation}\label{eqn:limit_h1}
+\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
+\end{equation}
+ % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
+ Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
+\begin{align*}
+-\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
+& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
+\end{align*}
+Exponentiating both sides, we see that
+\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
+We deduce that $\hardpart  f_0=f_0$.
+\end{proof}
+
+\subsubsection{Regularity}\label{sec:asymptotics}
+Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
+%%\begin{rmk}
+%%{\em Propositions \ref{prop:asymptotic at zero}} and \ref{prop:asymptotic at infinity} together prove {\em Theorem \ref{thm:proto-growth}}. 
+%%\end{rmk}
+\begin{prop}\label{prop:asymptotic at zero}
+    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
+\end{prop}
+
+\begin{proof}
+The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
+In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
+
+\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+
+is bounded by $ |\zeta(a)|^\tau$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
+
+\begin{align*}
+|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
+& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
+&  \lesssim |\zeta(a)|^{\tau-1}.
+\end{align*}
+
+The last step uses Condition~\eqref{cond:sing}. 
+\end{proof}
+\begin{prop}\label{prop:asymptotic at infinity}
+    Let $b\in\domain$.
+Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
+Then the prototype solution $f_0$ defined in \eqref{eqn:test_solution} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+\end{prop}
+\begin{proof}
+We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
+
+\[   |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
+\]
+
+Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$.
+Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.
+
+In particular, 
+      \begin{align*}
+          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
+          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
+          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
+      \end{align*}
+   which is bounded because $|\zeta(a)|>\delta$.
+
+\end{proof}
+
+\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
+
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
+
+\begin{prop}\label{prop:smoothing}
+Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
+\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\epsilon}{\Lambda}(\Omega) \]
+continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
+\end{prop}
+
+\begin{proof}
+    Let $f\in\singexp{\sigma}{\Lambda}$,
+    \begin{align*}
+        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+    \end{align*}
+    By Condition~\eqref{cond:eps-lambda},
+    \begin{align*}
+         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
+    \end{align*}
+    The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
+    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
+\]
+    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
+    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
+    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
+\end{proof}
+
+\begin{cor}\label{cor:pertub_f0}
+    Let $f_0$ be the prototype solution in equation \eqref{eqn:test_solution}.
+If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
+\end{cor}
+\begin{proof}
+    Notice that since $\tau-1>-1$ the hypothesis of Proposition \ref{prop:smoothing} are satisfied. In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$. 
+\end{proof}
+
+\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
 \subsubsection{Overview}
+In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
+
+\begin{prop}\label{prop:get-contraction}
+Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
+Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
+\end{prop}
+\begin{rmk}
+For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
+\end{rmk}
+First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Proposition~\ref{prop:whole-ker-near-bound}, which we'll state and prove in Section~\ref{sec:bounds on k}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+\begin{equation}\label{near-limit}
+|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
+\end{equation}
+for all $a, a' \in \near$.
+By choosing a small enough positive radius $\delta$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$.
+Complementarily, let $\far$ be the part of $\domain$ where $\delta \le |\zeta|$.
+
+Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$.
+In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
+In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
+Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
+Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
+\subsubsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
 The conditions on $\hardker$ and $\softker$ described in Sections \ref{setting:basic} and \ref{setting:perturbed} can be combined into convenient bounds on the kernel $\kerwhole = \hardker + \softker$ of $\volterra$.
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-%%We'll use these bounds in Section~\ref{sec:V is a contraction}.
-\textcolor{orange}{[Are these bounds actually used in Section~\ref{sec:existence and uniqueness}, or anywhere else?
-If not, maybe we should move this stuff into Section~\ref{sec:V is a contraction} after all.]}
 \begin{prop}\label{prop:whole-ker-near-bound}
@@
 \end{proof}.
-\subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
-
-\subsubsection{Construction}\label{sec:construction}
-\begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
-    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
-    \begin{align*}
-        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
-        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
-        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
-        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
-    \end{align*}
-
-    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact, choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
-\begin{equation}\label{eqn:limit_h1}
-\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
-\end{equation}
- % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
- Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
-\begin{align*}
--\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
-& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
-\end{align*}
-Exponentiating both sides, we see that
-\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
-We deduce that $\hardpart  f_0=f_0$.
-\end{proof}
-
-\subsubsection{Regularity}\label{sec:asymptotics}
-Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
-%%\begin{rmk}
-%%{\em Propositions \ref{prop:asymptotic at zero}} and \ref{prop:asymptotic at infinity} together prove {\em Theorem \ref{thm:proto-growth}}. 
-%%\end{rmk}
-\begin{prop}\label{prop:asymptotic at zero}
-    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
-\end{prop}
-
-\begin{proof}
-The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
-In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
-
-\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-
-is bounded by $ |\zeta(a)|^\tau$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
-
-\begin{align*}
-|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
-& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
-&  \lesssim |\zeta(a)|^{\tau-1}.
-\end{align*}
-
-The last step uses Condition~\eqref{cond:sing}. 
-\end{proof}
-\begin{prop}\label{prop:asymptotic at infinity}
-    Let $b\in\domain$.
-Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
-Then the prototype solution $f_0$ defined in \eqref{eqn:test_solution} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
-\end{prop}
-\begin{proof}
-We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
-
-\[   |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
-\]
-
-Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$.
-Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.
-
-In particular, 
-      \begin{align*}
-          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
-          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
-      \end{align*}
-   which is bounded because $|\zeta(a)|>\delta$.
-
-\end{proof}
-
-\subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
-
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
-This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
-
-\begin{prop}\label{prop:smoothing}
-Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
-\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\epsilon}{\Lambda}(\Omega) \]
-continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
-\end{prop}
-
-\begin{proof}
-    Let $f\in\singexp{\sigma}{\Lambda}$,
-    \begin{align*}
-        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
-    \end{align*}
-    By Condition~\eqref{cond:eps-lambda},
-    \begin{align*}
-         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
-    \end{align*}
-    The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
-\]
-    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
-    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
-    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
-\end{proof}
-
-\begin{cor}\label{cor:pertub_f0}
-    Let $f_0$ be the prototype solution in equation \eqref{eqn:test_solution}.
-If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
-\end{cor}
-\begin{proof}
-    Notice that since $\tau-1>-1$ the hypothesis of Proposition \ref{prop:smoothing} are satisfied. In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$. 
-\end{proof}
-
-\subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
-\subsubsection{Overview}
-In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
-
-\begin{prop}\label{prop:get-contraction}
-Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
-\end{prop}
-\begin{rmk}
-For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
-\end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
-\begin{equation}\label{near-limit}
-|k(a, a')| \le \frac{\sigma}{|\zeta(a)|}
-\end{equation}
-for all $a, a' \in \near$ (see Section~\ref{sec:bounds on k}).
-By choosing a small enough positive radius $\delta$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$.
-Complementarily, let $\far$ be the part of $\domain$ where $\delta \le |\zeta|$.
-
-Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$.
-In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
-In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
-Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
-Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
-\subsubsection{First steps}\label{first-steps}
+\subsubsection{First steps toward showing that $\volterra$ is a contraction}\label{first-steps}
 The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
@@
 Going back to the end of Section~\ref{first-steps}, suppose that $a \in \far$.
-Choosing some $\lambda > \lambda_\Delta$, as discussed in Section~\ref{sec:bounds on k}, we can use Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} to find a constant $M$ for which
+Choose some $\lambda > \lambda_\Delta$.
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, we can find a constant $M$ for which
 \[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]

### 2023-08-15 reg-sing-volterra.tex
Revise concluding remarks in contraction argument far from the origin
Replace threshold with scaling summary, and correct t^(1-rho) typo.

@@
 \end{align*}
-At the end of the path, we instead use a worst-case estimate on $t^{1-\rho}$:
-\begin{align*}
-\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt \\
-& = \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\delta} \right] \\
-& \le \left\{\begin{array}{cc}(1/5)^{\rho-1} & \rho \le 1 \\ 1 & \rho \ge 1 \end{array}\right\} \frac{1}{(\Lambda - \lambda)\delta}.
-\end{align*}
-
-We now know that by setting $\Lambda > \lambda + \delta^{-1} \max\{1, (1/5)^{\rho-1}\}$ (in fact $1/5$ can be replaced by any number in $(0,1)$), we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
-\textcolor{orange}{[I think this explicit bound only accounts for the integral over the end of the path, $t \in [1/5, 1)$.
-To ensure that the whole integral is less than $1$, we also need to look at the integral over the beginning of the path, $t \in (0, 1/5]$, which is calculated above.
-To me, that seems to make the bound too complicated to be worth stating---but maybe you can find a simplification.]} This completes our proof of Proposition~\ref{prop:get-contraction}.
+At the end of the path, we instead use a worst-case estimate on $t^{\rho-1}$:
+\begin{align*}
+\int_{1/5}^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt & \le \max\{(1/5)^{\rho-1}, 1\} \int_{1/5}^1 e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt \\
+& = \max\{(1/5)^{\rho-1}, 1\} \frac{1}{(\Lambda - \lambda)\delta}\left[ 1 - e^{-\tfrac{4}{5}(\Lambda - \lambda)\delta} \right] \\
+& \le \max\{(1/5)^{\rho-1}, 1\} \frac{1}{(\Lambda - \lambda)\delta}.
+\end{align*}
+In summary, the beginning of the integral is bounded by a decaying exponential function of $(\Lambda - \lambda)\delta$, and the end of the integral is bounded by a reciprocal function of $(\Lambda - \lambda)\delta$.
+That means we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+This completes our proof of Proposition~\ref{prop:get-contraction}.
 \subsection{Existence and uniqueness of a fixed point \\ \textit{(proof of Lemma~\ref{lem:perturbed_volterra} and Theorem~\ref{thm:general_volterra})}}\label{sec:existence and uniqueness}

### 2023-08-15 reg-sing-volterra.tex
Drop draft text from Section fn-spaces

@@
 for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
-
-%%We can also use the Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ to bound the norms $\|f_n\|_{0,\Lambda}$ uniformly over all $n$.
-Then, from the pointwise convergence argument above, we can draw the additional conclusion that $f$ is in $\singexp{0}{\Lambda}(\Omega)$.
 \end{proof}
@@
 \end{prop}
-
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
@@
 \end{proof}
-
-%%Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-For any $\sigma \in \R$ and $Z \in \C$, multiplying by $\zeta^\sigma e^{\Re(Z\zeta)}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
-We'll call this space $\expHoloL{\infty, \sigma}{Z}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma; Z} = \|\zeta^{-\sigma} e^{-\Re(Z\zeta)} f\|_\infty$, so that
-%%\begin{align*}
-%%\holoL{\infty}(\Omega) & \to \expHoloL{\infty, \sigma}{Z}(\Omega) \\
-%%\varphi & \mapsto \zeta^\sigma e^{\Re(Z\zeta)} \varphi
-%%\end{align*}
-%%is an isometry. More generally,
-%%\begin{align*}
-%%\expHoloL{\infty, \rho}{Z}(\Omega) & \to \expHoloL{\infty, \rho+\delta}{Z}(\Omega) \\
-%%f & \mapsto \zeta^\delta f
-%%\end{align*}
-%%is an isometry for all $\rho, \delta \in \R$ and $Z \in \C$. This reduces to the previous statement when $\rho = 0$ and $Z = 0$.
-%%\subsection{Graded algebra structure}
-%%For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho-\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho-\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
-%%\begin{verify}
-%%\begin{align*}
-%%\|f\|_{\infty, \rho+\delta, Z} & = \|\zeta^{-(\rho-\delta)} e^{-\Re(Z\zeta)} f\|_\infty \\
-%%& = \|\zeta^\delta \zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty \\
-%%& = \|\zeta^\delta\|_\infty\,\|\zeta^{-\rho} e^{-\Re(Z\zeta)} f\|_\infty & \text{(Banach algebra)} \\
-%%& \le \|\zeta^\delta\|_\infty\,\|f\|_{\infty, \rho; Z}
-%%\end{align*}
-%%\end{verify}
-%%Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\expHoloL{\infty, -\infty}{Z}(\Omega) := \bigcup_{\sigma \in \R} \expHoloL{\infty, \sigma}{Z}(\Omega)$ is a graded algebra, with a different norm on each grade.
-For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
-%%\subsection{Norms of effectively finite-order operators}
-%%\begin{itemize}
-%%\item Say $|m(a)| \lesssim e^{c|\zeta(a)|}$ over all $a \in \Omega$. For any $f \in \expHoloL{\infty, \rho}{Z}$,
-%%\begin{align*}
-%%\|mf\|_{\infty, \sigma; Z} =
-%%\end{align*}
-%%\end{itemize}
-
-%%which is effectively finite-order over $\Omega$ in the sense of Definition~\ref{fin-order}, with order at least $1 + \epsilon$ for some $\epsilon \in (0, \infty)$.
 \section{Solving holomorphic Volterra equations}

### 2023-08-15 reg-sing-volterra.tex
Start revising proof that prototype solution works

@@
 \begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
-    Let $\psi_0(a)= \exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]$, then $ d \psi_0 = -\frac{q}{p} \psi_0\;d\zeta $. Hence, for every $a\in\Omega$ 
-    \begin{align*}
-        \big[\hardpart f_0\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} f_0 d\zeta \\
-        &= - \int_{\zeta=0}^{a} \frac{q}{p(a)} \frac{p(b)}{p}\psi_0 d\zeta \\
-        &= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0 d\zeta\\
-        &= \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} d\psi_0  \\
-    \end{align*}
-
-    Now we claim $\lim_{a\to 0}\psi_0(a)=0$: in fact, choose some $\varepsilon>0$. By Condition~\eqref{cond:sing}, we can find $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$
+Let
+\[ \psi_0(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
+so $\solproto = \frac{p(b)}{p} \psi_0$.
+Observing that $d\psi_0 = -\frac{q}{p} \psi_0\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\psi_0$.
+For each $a \in \Omega$, we have
+\begin{align*}
+\big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
+&= -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
+&= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
+&= \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0.
+\end{align*}
+
+To evaluate this improper integral using the fundamental theorem of calculus, we need to find $\lim_{a \to 0} \psi_0(a)$.
+This limit turns out to be $0$, as shown by the following argument.
+Choose some $\varepsilon>0$.
+By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ such that
 \begin{equation}\label{eqn:limit_h1}
@@
 \end{equation}
- % notice that $|p(a)|\leq \varepsilon$ for $|zeta(a)|\leq \delta$, while $|q(a')-\ell|\leq \varepsilon$ for $|\zeta(a')|\leq \delta$ and $\ell>0$. 
- Then, we choose $b\in\Omega$ such that $\tfrac{\delta}{2}=|\zeta(b)|$.
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
+\textcolor{orange}{[...]}
 \begin{align*}

### 2023-08-15 reg-sing-volterra.tex
Write abstract
Also: check off completed tasks.

@@
 
+\setcounter{tocdepth}{2}
+
 %%\theoremstyle{definition}
@@
 \maketitle
+
+\begin{abstract}
+The inverse Laplace transform can turn a linear differential equation on a complex domain into an equivalent Volterra integral equation on a real domain.
+This can make things simpler: for example, a differential equation with irregular singularities can become a Volterra equation with regular singularities.
+It can also reveal hidden structure, especially when the Volterra equation extends to a complex domain.
+
+Our main result is to show that for a certain kind of regular singular Volterra equation on a complex domain, there is always a unique solution of a certain form.
+As a motivating example, this kind of Volterra equation arises when using Laplace transform methods to solve a ``level~$1$'' differential equation.
+
+%Our main result is to show that certain kind of regular singular Volterra equations on complex domains have unique solutions of a characteristic form.
+\end{abstract}
+
+\tableofcontents
+
 \begin{brainstorm}
@@
         \begin{itemize}
-            \item Proofread revised proof.
+            \item \textcolor{gray}{Proofread revised proof.}
         \end{itemize}
@@
 \end{itemize}
-\item Revise text around main results.
+\item \textcolor{gray}{Revise text around main results.}
 \begin{itemize}
@@
 \color{violet}
-\item Start finalizing notation for the two parts of the operator and the two parts of the solution.
+\item \textcolor{gray}{Start finalizing notation for the two parts of the operator and the two parts of the solution.}
 \begin{itemize}
-    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$.
-Same for $\hardker$ and $\softker$.
-    \item Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.
+    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} \textcolor{gray}{Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$.
+Same for $\hardker$ and $\softker$.}
+    \item \textcolor{gray}{Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.}
 \end{itemize}
@@
 \end{itemize}
-\item Reconsider using $\lesssim$ (but still leaning not to)
+\item \textcolor{gray}{Reconsider using $\lesssim$ (but still leaning not to)}
 \begin{itemize}
-    \item \textbf{(Aaron)} As an example, show how we could rewrite the argument in proof of Proposition~\ref{prop:asymptotic at infinity} with $\lesssim$.
+    \item \textcolor{gray}{\textbf{(Aaron)} As an example, show how we could rewrite the argument in proof of Proposition~\ref{prop:asymptotic at infinity} with $\lesssim$.}
 \end{itemize}
+\item \textcolor{gray}{Write abstract.}
+\item \textcolor{gray}{\textbf{(Veronica)} Add table of contents.}
+\item \textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)
 \end{brainstorm}
@@
 where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
-The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on differential equations.
+The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.
 
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino} \cite[Section 2.4]{sternin1995borel}.
+Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino}\cite[Section 2.4]{sternin1995borel}.
 
@@
 We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
-
+\begin{brainstorm}
+\item Kihyun Kim and his visitor (possibly Prof. Soonsik Kwon or Sung-Jin Oh)
+\item Angeliki Menegaki
+\end{brainstorm}
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}

### 2023-08-15 reg-sing-volterra.tex
Finish proving that the prototype solution is equivalent to zeta^(tau - 1)

@@
         \color{violet}
-        \item \textbf{(Aaron)} Confirm again that removed $\tau+\epsilon$ upper bound on $\rho$ was unnecessary.
+        \item \textbf{(Aaron)} Confirm again that removed $\tau+\gamma$ upper bound on $\rho$ was unnecessary.
 \end{itemize}
@@
 \item \textcolor{gray}{\textbf{(Veronica)} Add table of contents.}
+\item Replace $\psi_0$ with $\chi$.
+\item Replace $\epsilon$ with $\gamma$.
 \item \textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)
@@
 The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
-To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\epsilon > 0$ on the diagonal in $\Omega^2$.
+To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\Omega^2$.
 This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
@@
 \begin{conditions}
-\condconst{diag$_\star$}{\epsilon, \lambda_\Delta}\label{cond:eps-lambda} We have
-\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} We have
+\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
@@
 has a unique solution $f$ in the affine subspace
-\[ f_0 + \singexpalg{\tau-1+\epsilon}(\Omega) \]
+\[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
 of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
@@
 For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
-In other words, lowering $\rho$ into $(\tau, \tau+\epsilon)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$ will leave no solution at all.
+In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
 \end{thm}
@@
 To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\epsilon}(\domain)$.
-
-Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\epsilon}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\epsilon}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
+
+Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 This limit turns out to be $0$, as shown by the following argument.
-Choose some $\varepsilon>0$.
-By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ such that
+By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:limit_h1}
-\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right|<\varepsilon
+\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right| < C
 \end{equation}
@@
 \[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}\varepsilon\delta}\big)$ and $\exp\big(\tfrac{3}{2}\varepsilon\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
+The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
 We deduce that $\hardpart  f_0=f_0$.
@@
 
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\gamma}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
@@
 Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
-\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\epsilon}{\Lambda}(\Omega) \]
+\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma+\gamma}{\Lambda}(\Omega) \]
 continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
@@
     \begin{align*}
-        |\zeta(a)|^{-(\sigma+\epsilon)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
-        &\leq |\zeta(a)|^{-(\sigma+\epsilon)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
+        |\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
+        &\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
+        &\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
     \end{align*}
@@
     \begin{align*}
-         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\epsilon}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-         &=C_k |\zeta(a)|^{\epsilon+\sigma} \int_{0}^1 (1-t)^\epsilon e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-         &=C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\epsilon  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-         &\le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\epsilon  t^{\sigma}\;dt.
+         \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+         &=C_k |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+         &=C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+         &\le C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
     \end{align*}
     The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\epsilon+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}.
+    \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-    Our assumptions that $\epsilon > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
-    \[ |\zeta(a)|^{-(\epsilon+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\epsilon+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\epsilon+2)}, \]
-    we conclude that $|\zeta(a)|^{-\sigma-\epsilon} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
+    Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
+    \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
+    we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
 \end{proof}
@@
     Let $f_0$ be the prototype solution in equation \eqref{eqn:test_solution}.
-If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\epsilon}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
+If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
 \end{cor}
@@
 Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
-\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$, which means that
-\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
+\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
 over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Combining this conclusion with the previous one, we get the desired result.
@@
 |\kerwhole(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
-&\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\epsilon}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\epsilon \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+&\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\gamma \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
 \end{align*}
 over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since
-\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \]
+\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\gamma \]
 grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
-\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\epsilon \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
+\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
 over all $a, a' \in \domain$. It follows that
@@
 Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$.
-Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\epsilon}(\Omega)$ that makes $\solwhole = \solproto + \solptb$ a solution of
+Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\Omega)$ that makes $\solwhole = \solproto + \solptb$ a solution of
 \begin{equation}\label{eqn:orig-homog}
@@
 \end{align}
-Since we know that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexp{\tau-1+\epsilon}{\lambda_0}(\Omega)$.
-Since $\tau+\epsilon > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
-Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\epsilon}(\Omega)$.
+Since we know that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexp{\tau-1+\gamma}{\lambda_0}(\Omega)$.
+Since $\tau+\gamma > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$.
 
@@
 
-First, suppose $\rho \in (\tau, \tau+\epsilon)$.
-In this case, we can use the inclusion $\singexpalg{\tau-1+\epsilon}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
-Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
-
-On the other hand, suppose $\rho > \tau+\epsilon$.
-In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\epsilon}(\Omega)$.
-Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\epsilon}(\Omega)$.
+First, suppose $\rho \in (\tau, \tau+\gamma)$.
+In this case, we can use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+
+On the other hand, suppose $\rho > \tau+\gamma$.
+In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\gamma}(\Omega)$.
+Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
 
@@
 \end{align*}
-Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\epsilon=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}.
+Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}.
 This explains the definition of $\softker(a,a')$ with $\zeta(a)-\alpha$ at the denominator (instead of $\zeta(a)$).
@@
 
- %\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
+ \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
 
@@
 \begin{align*}
-    -\frac{q}{p(\zeta(a))}&=-\frac{q(\alpha)+c_1(\zeta'-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-p'(\alpha)(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
-    &=\frac{q\alpha)}{p'(\alpha)(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
-    &=\frac{q(\alpha)}{p'(\alpha)(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
+    -\frac{q}{p(\zeta(a))}&=-\frac{q(\alpha)+c_1(\zeta'-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
+    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
+    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
 \end{align*}
@@
 
-and $\epsilon=1$.
+and $\gamma=1$.
 
@@
 
-Finally, we look closer to the prototype solution $f_{0,\alpha}$ from Theorem \ref{thm:basic_volterra}, Equation \eqref{eqn:test_solution}. Following the computation we did above we get that
-
-\begin{align*}
-  f_{0,\alpha}(a)&=\frac{p(b)}{p(a)} \exp\left(-\int_b^a\frac{q}{p} d\zeta\right)\\
-  &=\frac{p(b)}{p(a)} \frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}} \exp\left(-\int_b^a\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} d\zeta\right)
-  %  &=(\zeta(a)-\alpha)^{\tau_\alpha-1} \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}} \frac{1}{p'(\alpha)+b_2'(\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2}
-\end{align*}
-Expanding $p(a)$ near $\zeta=\alpha$, we find that $f_{0,\alpha}$ is proportional to
-
-\begin{align*}
-\frac{(\zeta(a)-\alpha)^{\tau_\alpha-1}}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right)
-\end{align*}
-where both the exponential and the denominator are bounded as $\zeta(a)$ approaches $\alpha$.
+Finally, to get the result as stated, we need to show that
+\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
+for some constant $M$. Since we already know that $f_{0, \alpha}$ is of exponential type, it's enough to show that $f_{0, \alpha}$ falls into the class
+\[ (\zeta - \alpha)^{\tau_\alpha-1}\Big[M + O\big(|\zeta - \alpha|\big)\Big] \]
+when it's restricted to some neighborhood of $\zeta = \alpha$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
+\begin{align*}
+f_{0,\alpha}(a)&=\frac{p(b)}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
+&=\frac{p(b)}{p(a)}\,\frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,\exp\left(-\int_b^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right)\\
+& = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,(\zeta(a)-\alpha)^{\tau_\alpha-1}\,\frac{(\zeta(a) - \alpha)}{p(a)} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right),
+\end{align*}
+concluding that $f_{0,\alpha}$ is a constant multiple of
+\[ (\zeta(a)-\alpha)^{\tau_\alpha-1}\,\frac{\zeta(a)-\alpha}{p(a)} \, \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right). \]
+
+Since $p$ is a polynomial with a simple zero at $\zeta = \alpha$, we can deduce that
+\[ \frac{\zeta(a)-\alpha}{p(a)} \in b_1^{-1} + O\big(|\zeta - \alpha|\big), \]
+recalling that $b_1$ is the derivative of $p$ at $\zeta = \alpha$.
+
+Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
+\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < C \]
+in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $\alpha \in \domain_\text{near}$, the integral
+\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
+converges, allowing us to write
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
+for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta - \alpha|$ in $\domain_\text{near}$, implying that
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta - \alpha|\big) \Big] \]
+when we restrict to $\domain_\text{near}$.
+
+Combining the arguments above, we see as desired that
+\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha), \]
+with
+\[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]
 
@@
 
-The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
+Since $p$ has a simple zero at $\zeta=\alpha$ The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
 \begin{verify}

### 2023-08-15 reg-sing-volterra.tex
Strengthen statement of thm:example

@@
 \begin{lemma}
- For every root of $P$, let $\hat{P}_{\alpha}$ be the Volterra operator
+ For every root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator
 
 \begin{equation}\label{P-hat_j}
-\hat{P}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
+\hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
 \end{equation}
 
-If $\hat{\psi}_\alpha$ is a solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
+If $\hat{\psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
 By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$.
@@
         &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha}^{\theta}\hat{P}_\alpha\hat{\psi}_\alpha
-    \end{align*}
-\end{proof}
-
-We can now state and prove the main result of this section, namely that the Volterra operator $\hat{P}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$.
+        &=\laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha
+    \end{align*}
+\end{proof}
+
+We can now state and prove the main result of this section, namely that the Volterra operator $\hat{\mathcal{P}}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$.
 %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
@@
 \begin{thm}\label{thm:example}
-    There exists a unique solution of $\hat{P}_\alpha\hat{\psi}_\alpha=0$ such that 
-    \[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
-
-    where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+For each root $-\alpha$ of $P$, the equation
+\[ \hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0 \]
+has a unique solution $\hat{\psi}_\alpha$ in the affine subspace
+\[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
+%%The equation $\hat{P}_\alpha\hat{\psi}_\alpha=0$ has a unique solution of the form
+%%\[ \hat{\psi}_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
+%%\[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
+%%where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The result holds for every critical point of $P$.
 \end{thm}
-
- \textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
+%%\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
 
@@
 
-First of all, we rewrite $\hat{P}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
+First of all, we rewrite $\hat{\mathcal{P}}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
 
@@
 \[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]
-
-\color{DarkTurquoise}
-From Condition~\eqref{cond:sing}, we have
-\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < \varepsilon \]
-in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that
-\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
-converges for $a \in \domain_\text{near}$, so we have
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
-for $a \in \domain_\text{near}$. Observe that $|S| \le \varepsilon |\zeta - \alpha|$ in $\domain_\text{near}$.
-
-Since $p$ has a simple zero at $\zeta=\alpha$ The denominator is bounded in some neighbourhood $\domain_{\text{near}}$ of $\zeta=\alpha$
-\begin{verify}
-By definition of limit, as $\zeta(a)\to\alpha$ we should get
-\[
-\left\vert\frac{1}{p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...}-\frac{1}{p'(\alpha)}\right\vert\leq \varepsilon
-\]
-\end{verify}
-
-\[
-\frac{1}{|p'(\alpha)+b_2(\zeta(a)-\alpha)+b_3(\zeta(a)-\alpha)^2+...|}\leq  \text{const.} |\zeta(a)-\alpha| + O(|\zeta(a)-\alpha|^2)
-\]
-
-Therefore, we deduce from this that
-\begin{align*}
-f_{0,\alpha} & \in \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} O(|\zeta - \alpha|) \\
-& \subset \text{const.}\,(\zeta-\alpha)^{\tau_\alpha-1} + \text{const.}\,O\big(|\zeta-\alpha|^{\tau_\alpha}\big) \\
-\end{align*}
-when we restrict to $\domain_\text{near}$.
-\color{black}
-\end{proof}
-
-%\color{ForestGreen}
-%\begin{align*}
-%f & = \volterra f \\
-%f_\text{basic} + f_\text{extra} & = \volterra f_\text{basic} + \volterra f_\text{extra} \\
-%f_\text{basic} + f_\text{extra} & = \hardpart\,f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
-%f_\text{basic} + f_\text{extra} & = f_\text{basic} + \softpart \,f_\text{basic} + \volterra f_\text{extra} \\
-%f_\text{extra} & = \softpart \,f_\text{basic} + \volterra f_\text{extra}
-%\end{align*}
-%Solving the original equation is equivalent to finding a fixed point $f_\text{extra}$ of the affine-linear map
-%\[ \varphi \mapsto \softpart\,f_\text{basic} + \volterra \varphi. \]
+\end{proof}
+
 \bibliographystyle{plain}

### 2023-08-15 reg-sing-volterra.tex
Finish revising proof that prototype solution works

@@
 \item Replace $\psi_0$ with $\chi$.
-\item Replace $\epsilon$ with $\gamma$.
+\item \textcolor{gray}{Replace $\epsilon$ with $\gamma$.}
 \item \textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)
@@
 \end{conditions}
+We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
+\begin{conditions}
+\condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
+When $p$ is restricted to a small enough neighborhood of $\zeta = 0$, it falls into the class
+\[ B\zeta + O\big(|\zeta|^{1 + \textcolor{orange}{\epsilon}}\big) \]
+for some non-zero constant $B$ and some $\textcolor{orange}{\epsilon} > 0$.
+\end{conditions}
 \subsubsection{The perturbed operator}\label{setting:perturbed}
@@
 We'll prove this result in Section~\ref{sec:construction}.
-\color{RoyalBlue}
-\begin{rmk}
-If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant mutiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.
-
-\textcolor{SeaGreen}{$f_0 \in F\zeta^{\tau-1} + O(\zeta^\tau)$ near $\zeta = 0$ for some non-zero constant $F$.}
-\end{rmk}
-\color{black}
+
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
@@
 We'll prove this result in Section~\ref{sec:asymptotics}.
+
+\begin{rmk}
+Under stronger conditions on $p$, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics} for details.
+
+%%Suppose $p$ falls into the class $B\zeta + O\big(|\zeta|^2\big)$, for some constant $B$, when it's restricted to some neighborhood of $\zeta = 0$.
+
+%%for some constant $B$, we can strengthen the conclusion of Theorem~\ref{thm:proto-growth}.
+Under {\em Condition~\eqref{cond:sing}}, we can show that $\solproto \in B\zeta^{\tau-1} + O(|\zeta|^\tau)$.
+
+%%If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant multiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.
+\end{rmk}
+\color{black}
 
@@
 
+\begin{rmk}
+Under stronger conditions on $p$, Theorem~\ref{thm:general_volterra} can be restated to provide a unique solution in the affine subspace
+\[ \zeta^{\tau-1} + \singexpalg{\tau-1+\gamma}(\Omega). \]
+as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
+\end{rmk}
 %%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.
@@
 \big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
-&= -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
-&= - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
-&= \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0.
-\end{align*}
-
-To evaluate this improper integral using the fundamental theorem of calculus, we need to find $\lim_{a \to 0} \psi_0(a)$.
-This limit turns out to be $0$, as shown by the following argument.
+& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
+& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
+& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0 \\
+& = \frac{p(b)}{p(a)} \left[ \psi_0(a) - \lim_{\zeta \to 0} \psi_0 \right] \\
+& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \psi_0.
+\end{align*}
+Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \psi_0 = 0$.
+
 By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
@@
 \end{equation}
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
-\textcolor{orange}{[...]}
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\psi_0$:
 \begin{align*}
@@
 \[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-The exponential factor is bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ for all points $a$ in our chosen neighborhood of $\zeta = 0$.
-We deduce that $\hardpart  f_0=f_0$.
+Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
+The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$.
+Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \psi_0 = 0$.
+It follows, as discussed above, that $\hardpart \solproto = \solproto$.
 \end{proof}
@@
    which is bounded because $|\zeta(a)|>\delta$.
+
+\end{proof}
+
+\begin{prop}\label{prop:better-proto-estimate}
+Suppose $p$ falls into the class $B\zeta + O\big(|\zeta|^{1 + \textcolor{orange}{\epsilon}}\big)$, for some constants $B$ and $\textcolor{orange}{\epsilon}$, when it's restricted to some neighborhood of $\zeta = 0$.
+In addition, suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}.
+Then $\solproto \in B\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\textcolor{orange}{\epsilon}})$.
+\end{prop}
+\begin{proof}
 
@@
 %%the inhomogeneous term $\softpart\solproto$ is still in $\singexpalg{\rho-1}(\Omega)$ by Proposition~\ref{prop:inclus-lt-pow-gt-exp}, so Lemma~\ref{lem:perturbed_volterra} still guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found.
+
+\end{proof}
+
+\begin{prop}\label{prop:alt-general_volterra}
+    Suppose $p$ satisfies Condition \eqref{cond:reg-p}, and $\volterra$ satisfies assumptions of Theorem \ref{thm:general_volterra}. Then equation 
+    \[f=\volterra f\]
+    has a unique solution $f$ in the affine subspace
+    \[ B \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
+    of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon,\gamma\}$. 
+\end{prop}
+
+\begin{proof}
 

### 2023-08-15 reg-sing-volterra.tex
Rename prototype solution factor from psi_0 to chi

@@
 \item \textcolor{gray}{\textbf{(Veronica)} Add table of contents.}
-\item Replace $\psi_0$ with $\chi$.
+\item \textcolor{gray}{Replace $\psi_0$ with $\chi$.}
 \item \textcolor{gray}{Replace $\epsilon$ with $\gamma$.}
@@
 Let
-\[ \psi_0(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
-so $\solproto = \frac{p(b)}{p} \psi_0$.
-Observing that $d\psi_0 = -\frac{q}{p} \psi_0\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\psi_0$.
-For each $a \in \Omega$, we have
+\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
+so $\solproto = \frac{p(b)}{p} \chi$. Observing that $d\chi = -\frac{q}{p} \chi\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\chi$. For each $a \in \domain$, we have
 \begin{align*}
 \big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
-& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\psi_0\;d\zeta \\
-& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \psi_0\;d\zeta\\
-& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\psi_0 \\
-& = \frac{p(b)}{p(a)} \left[ \psi_0(a) - \lim_{\zeta \to 0} \psi_0 \right] \\
-& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \psi_0.
-\end{align*}
-Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \psi_0 = 0$.
+& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\chi\;d\zeta \\
+& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \chi\;d\zeta\\
+& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
+& = \frac{p(b)}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
+& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \chi.
+\end{align*}
+Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \chi = 0$.
 
@@
 \end{equation}
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\psi_0$:
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
 \begin{align*}
@@
 Exponentiating both sides, we see that
-\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
 Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
 The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$.
-Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \psi_0 = 0$.
+Since $\tau$ is positive, this is enough to show that $\lim_{\zeta \to 0} \chi = 0$.
 It follows, as discussed above, that $\hardpart \solproto = \solproto$.
@@
 
-\[ \psi_0(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
 
@@
 |f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
-& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(q)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
+& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(b)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
 &  \lesssim |\zeta(a)|^{\tau-1}.
@@
 \[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < C \]
-in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $\alpha \in \domain_\text{near}$, the integral
+in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $a \in \domain_\text{near}$, the integral
 \[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]

### 2023-08-15 reg-sing-volterra.tex
Work on {prop:asymptotic at zero} and prop:better-proto-estimate
Revise the proof of {prop:asymptotic at zero}. Move the proof of
prop:better-proto-estimate to its new home in sec:asymptotics.

@@
 \begin{equation}\label{eqn:test_solution}
-\solproto(a)=\frac{p(b)}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
+\solproto(a)=\frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
 \end{equation}
@@
 \begin{proof}[Proof of Theorem~\ref{thm:basic_volterra}]
-Let
-\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right), \]
-so $\solproto = \frac{p(b)}{p} \chi$. Observing that $d\chi = -\frac{q}{p} \chi\;d\zeta$, we can write $\hardpart \solproto$ in terms of an integral of $d\chi$. For each $a \in \domain$, we have
+Rewrite $\solproto$ as $(1/p)\,\chi$, where
+\[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
+Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ greatly simplifies the calculation of $\hardpart \solproto$. For each $a \in \domain$,
 \begin{align*}
 \big[\hardpart \solproto\big](a) &= - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\solproto\;d\zeta \\
-& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{p(b)}{p}\chi\;d\zeta \\
-& = - \frac{p(b)}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p} \chi\;d\zeta\\
-& = \frac{p(b)}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
-& = \frac{p(b)}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
-& = \solproto(a) - \frac{p(b)}{p(a)} \lim_{\zeta \to 0} \chi.
+& = -\int_{\zeta=0}^{a} \frac{q}{p(a)}\,\frac{1}{p}\,\chi\;d\zeta \\
+& = - \frac{1}{p(a)}  \int_{\zeta=0}^{a} \frac{q}{p}\,\chi\;d\zeta\\
+& = \frac{1}{p(a)} \int_{\zeta=0}^{a}\;d\chi \\
+& = \frac{1}{p(a)} \left[ \chi(a) - \lim_{\zeta \to 0} \chi \right] \\
+& = \solproto(a) - \frac{1}{p(a)} \lim_{\zeta \to 0} \chi.
 \end{align*}
@@
 By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
-\begin{equation}\label{eqn:limit_h1}
+\begin{equation}\label{eqn:sing-bound}
 \left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right| < C
@@
 \begin{prop}\label{prop:asymptotic at zero}
-    Let $f_0$ be the prototype solution defined in \eqref{eqn:test_solution}, then $|f_0|$ is bounded by a constant multiple of $\zeta^{\tau-1}$ near $\zeta=0$. 
-\end{prop}
-
-\begin{proof}
-The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
+Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
+\end{prop}
+
+\begin{proof}
+Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that Inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+The subsequent argument, which we used to show that $\lim_{\zeta \to 0} \chi = 0$, actually supports a stronger conclusion: it shows that $|\chi| \lesssim |\zeta|^\tau$ on the region $|\zeta| < \delta$.
+This tells us that
+%%Like we did in the proof of Theorem~\ref{thm:basic_volterra}, find a radius $\delta > 0$ and a constant $C$ such that the bound \eqref{eqn:sing-bound} holds whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+At the end of the proof of Theorem~\ref{thm:basic_volterra}, we showed that $\chi(a)$
+
+%%The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
 In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
 
-\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-
-is bounded by $ |\zeta(a)|^\tau$. Therefore, assuming $b'\in\Omega$ and $q(b') \neq 0$
-
-\begin{align*}
-|f_0| &  \lesssim |\zeta(a)|^\tau  \left\vert  \frac{p(b)}{p(a)}\right\vert \\
-& \lesssim |\zeta(a)|^\tau \, \left\vert\frac{p(b)}{q(b')} \right\vert \, \left\vert \frac{q(b')}{p(a)} \zeta(a)\right\vert \, |\zeta(a)|^{-1} \\
-&  \lesssim |\zeta(a)|^{\tau-1}.
-\end{align*}
-
-The last step uses Condition~\eqref{cond:sing}. 
+%%\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
+\[ |\solproto| \lesssim \left|\frac{1}{p}\right|\,|\zeta|^\tau \]
+on the region $|\zeta| < \delta$. Choosing a point $b'$ with $|\zeta(b')| < \delta$ and $q(b') \neq 0$, we can deduce that
+\begin{align*}
+|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
+& \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p} \zeta\right|\,|\zeta|^{\tau-1}.
+\end{align*}
+Since Inequality~\ref{eqn:sing-bound} implies that
+\begin{align*}
+\left|\frac{q(a')}{p(a)}\zeta(a)\right| & \le \tau + C|\zeta(a)| \\
+& \le \tau + C\delta
+\end{align*}
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$, we can conclude that $|\solproto| \lesssim |\zeta|^{\tau-1}$ on the region $|\zeta| < \delta$, as desired.
 \end{proof}
 \begin{prop}\label{prop:asymptotic at infinity}
-    Let $b\in\domain$.
-Assume $\hardpart$ satisfies {\em Condition} \eqref{cond:slow}.
-Then the prototype solution $f_0$ defined in \eqref{eqn:test_solution} belongs to the function space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:slow}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
 \end{prop}
@@
 \begin{prop}\label{prop:better-proto-estimate}
-Suppose $p$ falls into the class $B\zeta + O\big(|\zeta|^{1 + \textcolor{orange}{\epsilon}}\big)$, for some constants $B$ and $\textcolor{orange}{\epsilon}$, when it's restricted to some neighborhood of $\zeta = 0$.
+Suppose $p$ satisfies Condition \eqref{cond:reg-p} in some neighborhood of $\zeta = 0$.
 In addition, suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}.
-Then $\solproto \in B\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\textcolor{orange}{\epsilon}})$.
-\end{prop}
-\begin{proof}
-
+Then $\solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\lambda'})$, for some constant $M$ and $\lambda'=\min\{\epsilon, 1\}$.
+\end{prop}
+\begin{proof}
+Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
+\begin{align*}
+\solproto(a)&=\frac{p(b)}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
+&=\frac{p(b)}{p(a)}\,\frac{\zeta(a)^{\tau}}{\zeta(b)^{\tau}}\,\exp\left(-\int_b^a \left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right)\\
+& = \frac{p(b)}{\zeta(b)^{\tau}}\,\zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right),
+\end{align*}
+concluding that $\solproto$ is a constant multiple of
+\[ \zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \, \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right). \]
+
+By Condition \eqref{cond:reg-p}, we can deduce that
+\[ \frac{\zeta(a)}{p(a)} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
+in a small enough neighborhood $\domain_\text{near}$ of $\zeta=0$.
+
+Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
+\[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
+in $\domain_\text{near}$. It follows that for all $a \in \domain_\text{near}$, the integral
+\[ S(a) = \int_{0}^a \left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta \]
+converges, allowing us to write
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
+for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta|$ in $\domain_\text{near}$, implying that
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta|\big) \Big] \]
+when we restrict to $\domain_\text{near}$.
+
+Combining the arguments above, we see as desired that
+\[ \solproto \in M\zeta^{\tau - 1} + \singexpalg{\tau-1+\lambda'}(\domain), \]
+with 
+\[ M = \frac{p(b)}{\zeta(b)^{\tau}}\,B^{-1}\,e^{S(b)}. \]
 \end{proof}
@@
 \begin{prop}\label{prop:alt-general_volterra}
-    Suppose $p$ satisfies Condition \eqref{cond:reg-p}, and $\volterra$ satisfies assumptions of Theorem \ref{thm:general_volterra}. Then equation 
+    Suppose $p$ satisfies Condition \eqref{cond:reg-p}, and $\volterra$ satisfies the assumptions of Theorem \ref{thm:general_volterra}. Then equation 
     \[f=\volterra f\]
     has a unique solution $f$ in the affine subspace
-    \[ B \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
+    \[ M \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
     of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon,\gamma\}$. 

### 2023-08-15 reg-sing-volterra.tex
Revise proof of {prop:asymptotic at infinity}
Also, strengthen cond:slow so that the result actually holds.

@@
 \end{align*}
-outside some neighborhood of $\zeta = 0$ in $\Omega$.
+outside some neighborhood of $\zeta = 0$ in $\domain$.
+In addition, $|1/p|$ and $|q/p|$ are bounded outside every neighborhood of $\zeta = 0$ in $\domain$; the bound may depend on the neighborhood.
 Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
@@
 \begin{equation}\label{eqn:test_solution}
-\solproto(a)=\frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
+\solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right).
 \end{equation}
@@
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:slow}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
-\end{prop}
-\begin{proof}
-We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:slow}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+\end{prop}
+\begin{proof}
+We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.
+
+Find a neighborhood $\domain_\text{near}$ of $\zeta = 0$ where $|\solproto| \lesssim |\zeta|^{\tau-1}$, as Proposition~\ref{prop:asymptotic at zero} says we can do.
+By making $\domain_\text{near}$ bounded, we can prevent $e^{\lambda_0|\zeta|}$ from getting arbitrarily close to zero on $\domain_\text{near}$.
+Then we have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{near}$.
+
+Recall that in Condition~\eqref{cond:slow}, the constant $\lambda_0$ is the sum of two constants: $\lambda_p$, which controls the growth of $1/p$ at infinity, and $\lambda_\text{ratio}$, which controls the growth of $p/q$ at infinity.
+By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ where $|1/p| \lesssim e^{\lambda_p |\zeta|}$ and $|q/p| \le \lambda_\text{ratio}$, as Condition~\eqref{cond:slow} says we can do.
+Observe that
+\begin{align*}
+|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
+& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
+& \lesssim e^{\lambda_p|\zeta(a)|}\,e^{\lambda_\text{ratio}(|\zeta(a)| + |\zeta(b)|)} \\
+& \lesssim e^{\lambda_0|\zeta(a)|}\,e^{\lambda_\text{ratio}|\zeta(b)|} \\
+& \lesssim e^{\lambda_0|\zeta(a)|}
+\end{align*}
+over all $a \in \domain_\text{far}$.
+Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$.
+Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
+
+Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$.
+Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and Condition~\eqref{cond:slow} guarantees that $|\solproto|$ is bounded there.
+Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.
+
+Combining the conclusions above, we see that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain = \domain_\text{near} \cup \domain_\text{mid} \cup \domain_\text{far}$, as desired.
+\par\color{RoyalBlue}
+We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ \textcolor{orange}{[there's no $a'$ here]} (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
 
@@
 
-Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$.
+Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$ \textcolor{orange}{[there's no $a'$ here]}.
 Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.
@@
    which is bounded because $|\zeta(a)|>\delta$.
-
+\textcolor{orange}{[As Condition~\eqref{cond:slow} is currently stated, $|\zeta| > \delta$ may not be far enough from $\zeta = 0$ to get the $\lambda_p$ and $\lambda_\delta$ bounds.
+I've strengthened the condition so that $|1/p|$ and $|q/p|$ are at least bounded outside every neighborhood of $\zeta = 0$.]}
 \end{proof}
@@
     \[ M \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
-    of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon,\gamma\}$. 
-\end{prop}
-
-\begin{proof}
-
+    of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon, 1, \gamma\}$. 
+\end{prop}
+
+\begin{proof}
+ By Theorem \ref{thm:general_volterra}, we already know there exists a unique solution $f$ which belongs to the affine subspace
+ \[f_0+\singexpalg{\tau+1-\gamma}(\domain)\]
+ of the space $\singexpalg{\tau-1}(\domain)$. In addition, in Proposition \ref{prop:better-proto-estimate}, we learnt that in a neighbourhood of $\zeta=0$
+ \[\solproto\in M\zeta^{\tau-1}+ O(|\zeta|^{\tau-1+\lambda'})\]
+ for some constant $M$ and $\lambda'=\min\{\epsilon, 1\}$. We conclude, by combining these results. 
 \end{proof}
@@
 \[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
-for some constant $M$. Since we already know that $f_{0, \alpha}$ is of exponential type, it's enough to show that $f_{0, \alpha}$ falls into the class
+for some constant $M$.
+Like in the proof of Proposition \ref{prop:alt-general_volterra}, it's enough to show that $p$ satisfies Condition \eqref{cond:reg-p} with $\epsilon=1$.
+Since $p$ is a polynomial with a simple zero at $\zeta=\alpha$, we have that
+
+\[ p \in (\zeta-\alpha)\Big[ b_1 + O(\zeta-\alpha)\Big] \]
+in a small enough neighborhood of $\zeta=\alpha$.
+
+\color{RoyalBlue}
+Since we already know that $f_{0, \alpha}$ is of exponential type, it's enough to show that $f_{0, \alpha}$ falls into the class
 \[ (\zeta - \alpha)^{\tau_\alpha-1}\Big[M + O\big(|\zeta - \alpha|\big)\Big] \]
@@
 \[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]
+
+\color{black}
 \end{proof}

### 2023-08-16 reg-sing-volterra.tex
Revise proof of prop:better-proto-estimate

@@
 \condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
-When $p$ is restricted to a small enough neighborhood of $\zeta = 0$, it falls into the class
-\[ B\zeta + O\big(|\zeta|^{1 + \textcolor{orange}{\epsilon}}\big) \]
-for some non-zero constant $B$ and some $\textcolor{orange}{\epsilon} > 0$.
+For some non-zero constant $B$ and some $\epsilon > 0$,
+\[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
+at $\zeta = 0$.
 \end{conditions}
@@
 \end{proof}
-
 \begin{prop}\label{prop:better-proto-estimate}
-Suppose $p$ satisfies Condition \eqref{cond:reg-p} in some neighborhood of $\zeta = 0$.
-In addition, suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}.
-Then $\solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\lambda'})$, for some constant $M$ and $\lambda'=\min\{\epsilon, 1\}$.
-\end{prop}
-\begin{proof}
-Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
-\begin{align*}
-\solproto(a)&=\frac{p(b)}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
-&=\frac{p(b)}{p(a)}\,\frac{\zeta(a)^{\tau}}{\zeta(b)^{\tau}}\,\exp\left(-\int_b^a \left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right)\\
-& = \frac{p(b)}{\zeta(b)^{\tau}}\,\zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right),
-\end{align*}
-concluding that $\solproto$ is a constant multiple of
-\[ \zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \, \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right). \]
-
-By Condition \eqref{cond:reg-p}, we can deduce that
-\[ \frac{\zeta(a)}{p(a)} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
-in a small enough neighborhood $\domain_\text{near}$ of $\zeta=0$.
-
-Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
+\[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
+at $\zeta = 0$, where $\epsilon'=\min\{\epsilon, 1\}$.
+\end{prop}
+\begin{proof}
+It's enough to show that
+\[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
+at $\zeta = 0$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
+\begin{align*}
+\solproto(a)&=\frac{1}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
+& = \frac{1}{p(a)}\,\frac{\zeta(a)^{\tau}}{\zeta(b)^{\tau}}\,\exp\left[-\int_b^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right]\\
+& = \zeta(b)^{-\tau}\,\zeta(a)^{\tau-1}\,\frac{\zeta(a)}{p(a)} \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right].
+\end{align*}
+Since $\zeta(b)^{-\tau}$ is a constant, the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want.
+
+With a little work, the $\zeta/p$ factor also looks like what we want. Condition \eqref{cond:reg-p} implies that
+\[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
+at $\zeta = 0$.
+
+Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
-in $\domain_\text{near}$. It follows that for all $a \in \domain_\text{near}$, the integral
-\[ S(a) = \int_{0}^a \left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta \]
-converges, allowing us to write
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
-for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta|$ in $\domain_\text{near}$, implying that
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta|\big) \Big] \]
-when we restrict to $\domain_\text{near}$.
-
+in $\domain_\text{near}$. It follows that the improper integral
+\[ \eta(a) = \int_{\zeta = 0}^a \left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta \]
+converges for all $a \in \domain$, allowing us to write
+\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
+Observing that $|\eta| \le C |\zeta|$ in $\domain_\text{near}$, we can conclude that
+\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
+at $\zeta(a) = 0$.
+
+Combining the arguments above, we learn that
+\begin{align*}
+\solproto & \in \zeta(b)^{-\tau}\,\zeta^{\tau-1}\;\Big[ B^{-1} + O\big(|\zeta|^{\epsilon}\big) \Big]\;e^{\eta(b)} \Big[1 + O\big(|\zeta|\big) \Big] \\
+& = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}\;\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) \Big] \Big[1 + O\big(|\zeta|\big) \Big] \\
+& = M\zeta^{\tau-1} \Big[ 1 + O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) \Big]
+\end{align*}
+at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
+\par\color{RoyalBlue}
 Combining the arguments above, we see as desired that
@@
 \end{proof}
-
 \subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
@@
 \subsection{Overview}
-
-We can apply the theory of regular singular Volterra operators to the study of the so-called \textit{level 1 ODE}, which have an irregular singularity at $\infty$.
+We can apply the theory of regular singular Volterra operators to the study of so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
 In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain.
 The latter is an example of the regular singular Volterra equations we introduced above.
-
-\subsubsection{Level $1$ ODE}\label{sec:level 1 ODE}
-
-Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
+\subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
+Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
 \begin{equation}\label{eqn:level 1 ode}

### 2023-08-16 reg-sing-volterra.tex
Work on sec:example

@@
 Our main result is to show that for a certain kind of regular singular Volterra equation on a complex domain, there is always a unique solution of a certain form.
-As a motivating example, this kind of Volterra equation arises when using Laplace transform methods to solve a ``level~$1$'' differential equation.
-
-%Our main result is to show that certain kind of regular singular Volterra equations on complex domains have unique solutions of a characteristic form.
+As a motivating example, this kind of Volterra equation arises when using Laplace transform methods to solve a {\em level~1} differential equation.
 \end{abstract}
@@
 Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this helpful behavior in the class of differential equations that Ecalle calls {\em level $1$}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
+In Section~\ref{sec:example}, we'll see this helpful behavior in the class of differential equations that Ecalle calls {\em level~1}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
 This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.
 
-From our experience with solving level 1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
+From our experience with solving level~1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
 Let's say we've chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
@@
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} We have
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
 \[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{prop}
-
-\begin{proof}
-    Let $f\in\singexp{\sigma}{\Lambda}$,
+\begin{rmk}
+We're assuming that $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We'll take advantage of this in Section~\ref{sec:L-int-op}
+\end{rmk}
+\begin{proof}[Proof of Proposition~\ref{prop:smoothing}]
+For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
 \begin{align*}
@@
 \]
-    Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined. Rearranging to get
+Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 \begin{cor}\label{cor:pertub_f0}
-    Let $f_0$ be the prototype solution in equation \eqref{eqn:test_solution}.
+Let $f_0$ be the prototype solution from Equation~\eqref{eqn:test_solution}.
 If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
@@
 \begin{proof}
-    Notice that since $\tau-1>-1$ the hypothesis of Proposition \ref{prop:smoothing} are satisfied. In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$. 
+Since $\tau-1>-1$ the hypothesis of Proposition~\ref{prop:smoothing} are satisfied.
+In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$ \textcolor{orange}{[inconsistent with statement, which only mentions $\lambda_\Delta$?]}.
 \end{proof}
@@
 \subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
-Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
-\begin{equation}\label{eqn:level 1 ode}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-
+Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
+%%\begin{equation}\label{eqn:level 1 ode}
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
+%%\end{equation}
+where
 \begin{enumerate}
@@
 \item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and it does not vanish at the critical point of $P$;
-\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, for every $|z|>A$
-\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j}. \]
+\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
+\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
+converge in the region $|z| > A$.
 \end{enumerate}
-
-Equations of the form \eqref{eqn:level 1 ode} are called {\em level $1$} by Ecalle (see \cite[Section 2.1]{EcalleIII}).
-For instance, the modified Bessel equation is of level $1$, and we'll study its solutions explicitly in \cite{borel_reg}.
-
+Equations of the form $\mathcal{P}\Phi = 0$ \textcolor{orange}{[the line $\mathcal{P} = \ldots$ is the definition of an operator, not a differential equation]} are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}.
+\textcolor{RoyalBlue}{As an example, the modified Bessel equation is of level~$1$; we'll study its solutions explicitly in \cite{borel_reg}.}
 \subsection{The Laplace transform}
-
-%Let $\mathcal{E}_{\alpha}^{\theta}$ \textcolor{orange}{[replace with a function space from this paper]} be the space of functions that are subexponential on $\Gamma_{\alpha}^{\theta}$, integrable at the starting point $\zeta=\alpha$, and locally integrable throughout.
-
-Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
-If $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform $\laplace_{\zeta, \alpha}^{\theta} $ maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions in the half plane $\Re(z e^{-i\theta}) > \Lambda$~\cite[Section 5.6]{diverg-resurg-i}.
-It is defined by the formula
-
+\subsubsection{Definition}
+Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, \textcolor{orange}{[maybe talk about adapting conventions here, since we need that already for the definition of $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to make sense]} and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
+When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
+The Laplace transform of $\varphi$ is defined by the formula
 \begin{equation}\label{laplace:int} 
-\laplace_{\zeta, \alpha}^{\theta} f := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} f\, d\zeta
+\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
 \end{equation}
-
-where $z$ is the frequency function.
-
-\subsubsection{Action on integral operators}\label{L-int-op}
+It's a function on the frequency domain because it depends on the frequency variable $z$.
+\subsubsection{Action on integral operators}\label{sec:L-int-op}
 %%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
 %%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{-\nu}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} f\,d\zeta \]
-for each $a \in \domain_\alpha$.
-%\par\color{RoyalBlue}
-%For $\nu' \in (-\infty, 1)$, the fractional integral $\partial^{\nu'-1}_{\zeta, \alpha}$ is defined by \textcolor{orange}{[$-\nu = \nu'-1$ and $1-\nu = \nu'$]}
-%\[ [\partial^{\nu'-1}_{\zeta, \alpha} f](a) := \frac{1}{\Gamma(1-\nu')} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu'} f\,d\zeta \]
-%for each $a \in \domain_\alpha$.
-%\color{black}
-
-It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
+For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
+\[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
+for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
 \begin{align*}
@@
 %\end{align*}
-For all $\nu\in (0,\infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ behaves as a Volterra operator $\softpart$ which is singular at $\zeta=\alpha$ but it has a smoothing effect on functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$.
-In fact, it maps functions $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to $\fracderiv{-\nu}{\zeta}{\alpha}\varphi\in\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$: %\textcolor{orange}{[if we want our previous results to apply for a singularity at $\zeta = \alpha$, I think we need to redefine our function spaces for that context]}
-
-\begin{align*}
-    \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \, d\zeta\\
-    &=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \zeta(a)\, \varphi \, d\zeta\\
-    &=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta
-\end{align*}
+Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
+\begin{prop}\label{prop:frac-int-smoothing}
+For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
+\[ \varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
+continuously for all $\sigma > -1$ and $\Lambda \ge 0$.
+\end{prop}
+\begin{proof}
+Rewrite the fractional integral as
+\begin{align*}
+\left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \; d\zeta\\
+%%&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \big(\zeta(a) - \alpha\big)\, \varphi \; d\zeta\\
+&=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,\varphi \; d\zeta.
+\end{align*}
+The Volterra operator with kernel
+\[ h(a, a') = \frac{1}{\Gamma(\nu)}\,\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a)- \alpha} \]
+satisfies Condition~\eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, as long as we loosen the condition to allow any $\gamma > -1$.
+Hence, by Proposition~\ref{prop:smoothing}, this operator maps
+\[ \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
+continuously for all $\sigma > -1$ and $\Lambda \ge 0$. Multiplication by $\zeta - \alpha$ then maps
+\[ \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
+continuously.
+
+\color{RoyalBlue}
 Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}.
@@
 More generally, working in the domain $\domain_\alpha$, we'll adapt the conventions used for $\domain$.} Hence by Proposition \ref{prop:smoothing}
-
 \[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
@@
 Multiplication by $\zeta - \alpha$ then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed.
+\end{proof}
 In particular, $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
@@
 \subsection{Going to the position domain}
-
 By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
-
 \begin{lemma}
- For every root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator
-
-\begin{equation}\label{P-hat_j}
-\hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r
-\end{equation}
-
-If $\hat{\psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$ then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
+For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
+\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
+If $\hat{\psi}_\alpha$ \textcolor{orange}{[the lower-case letter tells us this is a position-domain function, so why do we need the hat?]} satisfies the equation $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
 By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$.
@@
 
-We can now state and prove the main result of this section, namely that the Volterra operator $\hat{\mathcal{P}}_\alpha$ admits a unique solution $\hat{\psi}_\alpha$.
+We can now state and prove the main result of this section, namely that the Volterra equation $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0$ admits a unique solution $\hat{\psi}_\alpha$.
 %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
@@
 Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable.
-In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ at $\alpha$
-
-\begin{align*}
-    -\frac{q}{p(\zeta(a))}&=-\frac{q(\alpha)+c_1(\zeta'-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
+In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by \textcolor{RoyalBlue}{Taylor} expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial willhave the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
+notation $\zeta'$ not defined; switch to $\zeta(a')$?]}.
+
+\begin{align*}
+    -\frac{q}{p(a)}&=-\frac{\textcolor{magenta}{q(\alpha)}+c_1(\zeta\textcolor{magenta}{'}-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
     &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
@@
 \begin{equation*}
-    -\frac{q(\zeta(a'))}{p(\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
+    -\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
 \end{equation*}

### 2023-08-16 reg-sing-volterra.tex
Revise prop:alt-general_volterra and associated remarks

@@
 We'll prove this result in Section~\ref{sec:asymptotics}.
-
 \begin{rmk}
-Under stronger conditions on $p$, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics} for details.
-
-%%Suppose $p$ falls into the class $B\zeta + O\big(|\zeta|^2\big)$, for some constant $B$, when it's restricted to some neighborhood of $\zeta = 0$.
-
-%%for some constant $B$, we can strengthen the conclusion of Theorem~\ref{thm:proto-growth}.
-Under {\em Condition~\eqref{cond:sing}}, we can show that $\solproto \in B\zeta^{\tau-1} + O(|\zeta|^\tau)$.
-
-%%If $q$ has a limit at $\zeta = 0$, the solution $f_0$ from Theorem~\ref{thm:basic_volterra} can be written as a constant multiple of $\zeta^{\tau-1}$ plus a function which is $O(\zeta^\tau)$ at $\zeta = 0$.
+When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, we can get a better estimate of the prototype solution near $\zeta = 0$, as described in Proposition~\ref{prop:better-proto-estimate} from Section~\ref{sec:asymptotics}.
 \end{rmk}
@@
 \begin{rmk}
-Under stronger conditions on $p$, Theorem~\ref{thm:general_volterra} can be restated to provide a unique solution in the affine subspace
-\[ \zeta^{\tau-1} + \singexpalg{\tau-1+\gamma}(\Omega). \]
-as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
+When $\hardpart$ also satisfies Condition~\eqref{cond:reg-p}, Theorem~\ref{thm:general_volterra} can be restated to give a unique solution in the affine subspace
+\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) \]
+when $\rho > \tau$ is low enough, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
 \end{rmk}
@@
 \begin{prop}\label{prop:alt-general_volterra}
-    Suppose $p$ satisfies Condition \eqref{cond:reg-p}, and $\volterra$ satisfies the assumptions of Theorem \ref{thm:general_volterra}. Then equation 
-    \[f=\volterra f\]
+Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other conditions we assume in {\em Theorem~\ref{thm:general_volterra}}.
+Then, as long as $\rho > \tau$ is low enough, the equation
+\[f = \volterra f\]
 has a unique solution $f$ in the affine subspace
-    \[ M \zeta^{\tau-1}+\singexpalg{\tau-1+\gamma'}(\domain)\]
-    of the space $\singexpalg{\tau-1}(\domain)$, where $\gamma'=\min\{\epsilon, 1, \gamma\}$. 
-\end{prop}
-
-\begin{proof}
- By Theorem \ref{thm:general_volterra}, we already know there exists a unique solution $f$ which belongs to the affine subspace
- \[f_0+\singexpalg{\tau+1-\gamma}(\domain)\]
- of the space $\singexpalg{\tau-1}(\domain)$. In addition, in Proposition \ref{prop:better-proto-estimate}, we learnt that in a neighbourhood of $\zeta=0$
- \[\solproto\in M\zeta^{\tau-1}+ O(|\zeta|^{\tau-1+\lambda'})\]
- for some constant $M$ and $\lambda'=\min\{\epsilon, 1\}$. We conclude, by combining these results. 
+\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
+of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it's in the interval
+\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
+\end{prop}
+
+\begin{proof}
+Proposition~\ref{prop:better-proto-estimate} implies that for some constant $M$,
+\[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
+whenever $\rho \le \tau + \min\{\epsilon, 1\}$. Theorem~\ref{thm:general_volterra} implies that our equation has a unique solution in
+\[ M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
+as long as $\rho \in (\tau, \tau + \gamma]$. Putting these facts together, we get the desired result.
 \end{proof}

### 2023-08-16 reg-sing-volterra.tex
Use hyperref
Play with figure colors, matching link color.

@@
 \newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+
+% colors
+\definecolor{ietocean}{RGB}{0, 30, 140}
+\definecolor{ietcoast}{RGB}{0, 150, 173}
+\definecolor{ietlagoon}{RGB}{0, 216, 180}
+
+% pretty prince hyperref must always be the last thing in the preamble, always
+\usepackage{hyperref}
+\hypersetup{
+  colorlinks,
+  linkcolor={ietcoast},
+  citecolor={ietcoast},
+  urlcolor={ietcoast}
+}
 
@@
 \item \textcolor{gray}{Replace $\epsilon$ with $\gamma$.}
-\item \textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)
+\item \textcolor{gray}{\textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)}
 \end{brainstorm}
@@
 \newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
+%% previously violet!20
+\fill[ietcoast!33, bezier bounding box, path fading=radial edge]
   (-\spill, -\spill) (\spill, \spill)
@@
   arc (-60:-130:\spill) -- (0, 0);
-\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
+%% previously violet
+\fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
 \end{tikzpicture}

### 2023-08-16 reg-sing-volterra.tex
Draft partial fraction version of cond:sing argument for level 1 example

@@
 \newcommand{\solptb}{f_\star}
+\newcommand{\roots}{\mathfrak{B}}
 
@@
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
-\subsection{Weighted holomorphic $L^\infty$ spaces}\label{sec:fn-space-defs}
+\subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
 Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
@@
 \begin{proof}
-Proposition~\ref{prop:better-proto-estimate} implies that for some constant $M$,
+Propositions \ref{prop:asymptotic at infinity} and \ref{prop:better-proto-estimate} imply that for some constant $M$,
 \[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) = M^{-1}\solproto + \singexpalg{\rho-1}(\domain) \]
@@
 \end{align*}
-hence setting $\tau_\alpha:=\frac{q(\alpha)}{p'(\alpha)}\neq 0$, we find
+hence setting $\tau_\alpha:=\textcolor{magenta}{-}\frac{q}{p'}\textcolor{orange}{\big|_{\zeta = \alpha}}\neq 0$, we find
 
@@
 is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
+\par\color{SkyBlue}
+Since $p$ has only simple roots, the partial fraction decomposition of $1/p$ is
+\[ \sum_{\beta = \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
+where $\roots$ is the set containing the values of $\zeta$ at the roots of $p$.
+\par\color{DarkTurquoise}
+\textcolor{orange}{Nicer formulation; note different definition of $\roots$:}\par
+Since $P(-\zeta)$ has only simple roots, the partial fraction decomposition of $1/P(-\zeta)$ is
+\[ \sum_{-\beta = \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
+where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. It follows that
+\begin{align*}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta = \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& \in \sum_{-\beta = \roots} \frac{Q(-\alpha) + O\big(|\zeta(a') - \alpha|\big)}{P'(-\beta)\,(\zeta - \beta)} \\
+%%& \in \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\alpha)\,(\zeta - \alpha)} + \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\beta)\,(\zeta - \beta)} \\
+& \subset \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} + O\big(1\big)
+\end{align*}
+at $(\zeta(a), \zeta(a')) = (\alpha, \alpha)$. In other words, for $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, the difference
+\[ -\frac{Q(-\zeta(a'))}{P(-\zeta(a))} - \frac{\tau_\alpha}{\zeta - \alpha} \]
+is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$, showing that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:sing}.
+
+\begin{verify}
+A kind of klunky way to do the Ahlfors exercise:
+\begin{align*}
+\frac{1}{p} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
+-\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
+p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
+p'\big|_{\zeta = \alpha} & = \left.\left(\frac{p}{\zeta - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
+& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
+& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
+\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
+\end{align*}
+\end{verify}
+\color{black}
 

### 2023-08-16 reg-sing-volterra.tex
Revise dictionary lemma

@@
 \end{equation}
-for all integers $n \ge 0$ and suitable direction $\theta$.
+for all integers $n \ge 0$ and suitable directions $\theta$.
 
@@
 By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
-\begin{lemma}
+\begin{lemma}\label{lem:use-dict}
 For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
 \[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
-If $\hat{\psi}_\alpha$ \textcolor{orange}{[the lower-case letter tells us this is a position-domain function, so why do we need the hat?]} satisfies the equation $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha$, defined for a suitable direction $\theta$, is a solution of $\mathcal{P}\Psi_\alpha=0$.
-By suitable direction, we mean that the ray $\Gamma_{\alpha}^\theta$ must be contained in the domain $\Omega_{\alpha}$.
-\footnote{The domain $\Omega_{\alpha}$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}}.
+If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.\footnote{\textcolor{RoyalBlue}{The domain $\domain_\alpha$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}.}}
 \end{lemma}
-
-\begin{proof}
-Using the properties of the Laplace transform,
-
-    \begin{align*}
-        \mathcal{P}\Psi_\alpha&=\mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha\\
-        &=\laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\hat{\psi}_j\\
-        &=\laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha
-    \end{align*}
-\end{proof}
-
-We can now state and prove the main result of this section, namely that the Volterra equation $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0$ admits a unique solution $\hat{\psi}_\alpha$.
+\begin{rmk}
+For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
+We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\end{rmk}
+\begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Hence,
+\begin{align*}
+\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
+%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
+& = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
+\end{align*}
+\end{proof}
+
+We can now state and prove the main result of this section, namely that the Volterra equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ admits a unique solution $\psi_\alpha$.
 %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.

### 2023-08-16 reg-sing-volterra.tex
Ready to switch to new cond:sing argument

@@
 We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to show that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
 
@@
 \begin{align*}
-\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\leq C_k \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-&=C_k |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-&=C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-&\le C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
+\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
 \end{align*}
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
+\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
 Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
-\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \le C_k \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
+\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
 we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
@@
 Since $\tau-1>-1$ the hypothesis of Proposition~\ref{prop:smoothing} are satisfied.
-In addition, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$ \textcolor{orange}{[inconsistent with statement, which only mentions $\lambda_\Delta$?]}.
+In addition, recall that by Theorem \ref{thm:proto-growth}, $\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$.
+Therefore, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$.
 \end{proof}
@@
 \subsection{Overview}
-We can apply the theory of regular singular Volterra operators to the study of so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
 In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain.
@@
 \begin{enumerate}
-\item[$\bullet$] $P$ is a monic degree-$d$ polynomial with only simple zeros; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial and it does not vanish at the critical point of $P$;
+\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
 \item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
@@
 \end{enumerate}
-Equations of the form $\mathcal{P}\Phi = 0$ \textcolor{orange}{[the line $\mathcal{P} = \ldots$ is the definition of an operator, not a differential equation]} are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}.
-\textcolor{RoyalBlue}{As an example, the modified Bessel equation is of level~$1$; we'll study its solutions explicitly in \cite{borel_reg}.}
+Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}.
+In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}.
 \subsection{The Laplace transform}
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open set $\domain_\alpha\subset\C$ that touches but doesn't contain $\zeta=\alpha$, \textcolor{orange}{[maybe talk about adapting conventions here, since we need that already for the definition of $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to make sense]} and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, \textcolor{orange}{[maybe talk about adapting conventions here, since we need that already for the definition of $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to make sense]} and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
 When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
@@
 continuously.
-
-\color{RoyalBlue}
-Define $\softker(a,a'):=\frac{(\zeta(a)-\zeta(a'))^{\nu-1}}{\zeta(a) - \alpha}$, it is singular at $\zeta(a)=\alpha$ and it satisfies Condition \eqref{cond:eps-lambda} with $\gamma=\nu-1$ and $\lambda_\Delta=0$, for every $a,a'\in\domain_\alpha$.\footnote{Notice that $\softker$ has a singularity at $\zeta=\alpha$ and not at $\zeta=0$ as in Section \ref{setting:perturbed}.
-This explains the definition of $\softker(a,a')$ with $\zeta(a)-\alpha$ at the denominator (instead of $\zeta(a)$).
-More generally, working in the domain $\domain_\alpha$, we'll adapt the conventions used for $\domain$.} Hence by Proposition \ref{prop:smoothing}
-\[ \frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\, \varphi \, d\zeta \in \singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha) \]
-
-Multiplication by $\zeta - \alpha$ then maps functions in $\singexp{\sigma+\nu-1}{\Lambda}(\domain_\alpha)$ to $\singexp{\sigma+\nu}{\Lambda}(\domain_\alpha)$, as claimed.
-\end{proof}
-In particular, $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
+\end{proof}
+
+From Proposition \ref{prop:frac-int-smoothing}, we deduce that $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
 Thus, using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that
@@
 \[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
-If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.\footnote{\textcolor{RoyalBlue}{The domain $\domain_\alpha$ does not contain the tubular neighborhood of all the other critical points toward infinity as drawn in Section \ref{setting:domain}.}}
+If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
 \end{lemma}
+\textcolor{orange}{[Where do we explain what $\domain_\alpha$ needs to look like in this example?]}
 \begin{rmk}
@@
 We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain} replacing the origin $\zeta=0$ with $\zeta=\alpha$.
 \end{rmk}
@@
 For each root $-\alpha$ of $P$, the equation
-\[ \hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0 \]
-has a unique solution $\hat{\psi}_\alpha$ in the affine subspace
+\[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
+has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
 of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
-%%The equation $\hat{P}_\alpha\hat{\psi}_\alpha=0$ has a unique solution of the form
-%%\[ \hat{\psi}_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
-%%\[\hat{\psi}_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
+%%The equation $\hat{P}_\alpha\psi_\alpha=0$ has a unique solution of the form
+%%\[ \psi_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
+%%\[\psi_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
 %%where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
@@
 \begin{proof}
-Let $p = P(-\zeta)$ and $q = Q(-\zeta)$ and let $\alpha$ be a simple root of $p$. Hence, by assumptions that $p(\alpha)=0$, $p'(\alpha)\neq 0$ and $q(\alpha)\neq 0$.
-
+Choose a root $-\alpha$ of $P$.
+For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
+The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.
+
+To apply Theorem~\ref{thm:general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}.
+\textcolor{orange}{[Explain how conditions shift from $\zeta = 0$ to $\zeta = \alpha$?]} When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
+where
+\[ k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} \, \big(-\zeta(a')\big)^r. \]
+Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
+\begin{equation}\label{eqn:divided}
+\varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
+\end{equation}
+Let $\hardpart^\alpha$ be the Volterra operator with kernel
+\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]
+and let $\softpart^\alpha$ be the Volterra operator with kernel
+\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
+Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+\par\color{RoyalBlue}
 First of all, we rewrite $\hat{\mathcal{P}}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
@@
 \end{align}
-
+\color{black}
+\par\color{RoyalBlue}
 Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable.
-In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by \textcolor{RoyalBlue}{Taylor} expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial willhave the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
+In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial willhave the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
 notation $\zeta'$ not defined; switch to $\zeta(a')$?]}.
-
 \begin{align*}
@@
 hence setting $\tau_\alpha:=\textcolor{magenta}{-}\frac{q}{p'}\textcolor{orange}{\big|_{\zeta = \alpha}}\neq 0$, we find
-
 \begin{equation*}
@@
 is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
+\color{black}
 \par\color{SkyBlue}
 Since $p$ has only simple roots, the partial fraction decomposition of $1/p$ is
-\[ \sum_{\beta = \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
+\[ \sum_{\beta \in \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
 where $\roots$ is the set containing the values of $\zeta$ at the roots of $p$.
@@
 Since $P(-\zeta)$ has only simple roots, the partial fraction decomposition of $1/P(-\zeta)$ is
-\[ \sum_{-\beta = \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
+\[ \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
 where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. It follows that
 \begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta = \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& \in \sum_{-\beta = \roots} \frac{Q(-\alpha) + O\big(|\zeta(a') - \alpha|\big)}{P'(-\beta)\,(\zeta - \beta)} \\
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& \in \sum_{-\beta \in \roots} \frac{Q(-\alpha) + O\big(|\zeta(a') - \alpha|\big)}{P'(-\beta)\,(\zeta - \beta)} \\
 %%& \in \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\alpha)\,(\zeta - \alpha)} + \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\beta)\,(\zeta - \beta)} \\
@@
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$, showing that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:sing}.
+
+\textcolor{orange}{[Another phrasing:]}
+It follows that
+\begin{align*}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta - \alpha)}
+\end{align*}
+As $a$ and $a'$ approach $\zeta = \alpha$, the
+\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
+part approaches the limit
+\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
+Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. \textcolor{orange}{[\ldots]}
 

### 2023-08-16 reg-sing-volterra.tex
Show that kernel of V^alpha is meromorphic

@@
 Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+
+The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
+To do this, recall that the functions $R_r(z^{-1})$ are all holomorphic on the disk $|z| > A$.
+Consequently, for any $\lambda > A$, we have $R_{r,j} \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and all $j \in \{0, 1, 2, \ldots\}$.
+This is enough to show that $k_R$ is well-defined throughout $\C^2$.
+In fact, as we'll see later, it also leads to a useful bound on $k_R$.
+\begin{verify}
+\begin{align*}
+& \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z| > A \\
+\Longrightarrow & \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
+\Longrightarrow & A^{-1} \le \operatorname{radius} R_{r,j} \\
+\Longrightarrow & A \ge \big(\operatorname{radius} R_{r,j}\big)^{-1} \\
+\Longrightarrow & A \ge \limsup_{j \to \infty} R_{r,j}^{1/j} \\
+\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
+\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_{r,j}^{1/j} < \lambda \\
+\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j}^{1/j} < \lambda \\
+\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j} < \lambda^j
+\end{align*}
+\end{verify}
+
+%%The least straightforward part of this observation is confirming that $k_R(a, a')$ is well-defined for all $a, a' \in \C$, which you can do by observing that
+
+Since $P$ is a monic polynomial whose roots are all simple, $1/P(-\zeta)$ has the nice partial fraction decomposition
+\[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
+where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. 
+It follows that
+\begin{align*}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}
+\end{align*}
+As $a$ and $a'$ approach $\zeta = \alpha$, the
+\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
+part approaches the limit
+\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
+Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Conversely, as $a$ and $a'$ approach $\zeta=\alpha$, the term
+
+\[\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}\]
+
+converges to $\frac{\tau_\alpha}{\zeta(a)-\alpha}$ with $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$. We conclude that 
+\[-\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}\]
+
+is bounded as $a,a'$ approach $\zeta=\alpha$, showing that $\hardpart^\alpha$ satisfies Condition \eqref{cond:sing}.
+
+\begin{verify}
+A kind of klunky way to do the Ahlfors exercise:
+\begin{align*}
+\frac{1}{p} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
+-\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
+p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
+p'\big|_{\zeta = \alpha} & = \left.\left(\frac{p}{\zeta - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
+& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
+& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
+\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
+\end{align*}
+
+\color{magenta}
+\begin{align*}
+    \frac{1}{P} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
+-\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
+p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
+&\\
+& \\
+P'\big|_{\zeta = \alpha} & = \left.\left(\frac{P}{t - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
+& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
+& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
+\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
+\end{align*}
+for some constant $c_\beta$.
+\par\color{ForestGreen}
+First, observe that
+\begin{align*}
+P(t) &= (t + \beta_1) \cdots (t + \beta_d) \\
+P'(t) &= \sum_k \left[ \prod_{j \neq k} (t + \beta_j) \right] \\
+P'(-\beta_1) &= \prod_{j\neq 1} (-\beta_1 + \beta_j) 
+\end{align*}
+
+\begin{align*}
+\frac{1}{P(t)} & = \sum_{j} \frac{\pi_j}{t + \beta_j}\\
+-\frac{P'(t)}{P(t)^2} &= -\sum_{j} \frac{\pi_\beta}{(t + \beta_j)^2}\\
+P'(t) &= \sum_{j} \pi_j \left(\frac{P(t)}{t + \beta_j}\right)^2\\
+P'(-\beta_1) &=  \pi_1 \prod_{j\neq 1} (-\beta_1+\beta_j)^2\\
+\frac{1}{P'(-\beta_1)} &= \pi_1
+\end{align*}
+\end{verify}
+
 \par\color{RoyalBlue}
@@
 \textcolor{orange}{Nicer formulation; note different definition of $\roots$:}\par
-Since $P(-\zeta)$ has only simple roots, the partial fraction decomposition of $1/P(-\zeta)$ is
-\[ \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
-where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. It follows that
-\begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& \in \sum_{-\beta \in \roots} \frac{Q(-\alpha) + O\big(|\zeta(a') - \alpha|\big)}{P'(-\beta)\,(\zeta - \beta)} \\
-%%& \in \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\alpha)\,(\zeta - \alpha)} + \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha) + O\big(|\zeta - \alpha|\big)}{-P'(-\beta)\,(\zeta - \beta)} \\
-& \subset \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} + O\big(1\big)
-\end{align*}
-at $(\zeta(a), \zeta(a')) = (\alpha, \alpha)$. In other words, for $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, the difference
-\[ -\frac{Q(-\zeta(a'))}{P(-\zeta(a))} - \frac{\tau_\alpha}{\zeta - \alpha} \]
-is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$, showing that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:sing}.
-
-\textcolor{orange}{[Another phrasing:]}
-It follows that
-\begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta - \alpha)}
-\end{align*}
-As $a$ and $a'$ approach $\zeta = \alpha$, the
-\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
-part approaches the limit
-\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
-Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. \textcolor{orange}{[\ldots]}
-
-\begin{verify}
-A kind of klunky way to do the Ahlfors exercise:
-\begin{align*}
-\frac{1}{p} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
--\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
-p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
-p'\big|_{\zeta = \alpha} & = \left.\left(\frac{p}{\zeta - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
-& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
-& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
-\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
-\end{align*}
-\end{verify}
+
 \color{black}

### 2023-08-16 reg-sing-volterra.tex
Sketch instructions for working at zeta = alpha

@@
 \end{brainstorm}
-\section{Introduction}
+\section{Introduction}\label{sec:intro}
 \subsection{Motivation}\label{motivation}
@@
 \end{proof}
-\section{Solving holomorphic Volterra equations}
+\section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
 \subsection{Overview}
@@
 Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-
-%%the inhomogeneous term $\softpart\solproto$ is still in $\singexpalg{\rho-1}(\Omega)$ by Proposition~\ref{prop:inclus-lt-pow-gt-exp}, so Lemma~\ref{lem:perturbed_volterra} still guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found.
-
-\end{proof}
-
+\end{proof}
 \begin{prop}\label{prop:alt-general_volterra}
@@
 In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}.
+\subsection{\textcolor{orange}{Notation}}
+\begin{brainstorm}
+\item Previously, we always looked at Volterra operators with a regular singularity at $\zeta = 0$.
+\item When we try to solve a level~1 differential equation, we'll get an operator with many regular singularities---one at each root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
+\item Rules for working at $\zeta = \alpha$:
+\begin{itemize}
+    \item In all our work from Sections~\ref{sec:intro}--\ref{sec:proof_main_results}, the role of the coordinate $\zeta$ is played instead by $\zeta - \alpha$. Concrete examples of how to do that:
+    \begin{itemize}
+        \item References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.
+        \item Conditions on operators, location of regular singularity.
+        \item Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.
+        \item Definition of $\singexp{\sigma}{\Lambda}$ spaces.
+    \end{itemize}
+\end{itemize}
+\end{brainstorm}
 \subsection{The Laplace transform}
@@
 
-%%The least straightforward part of this observation is confirming that $k_R(a, a')$ is well-defined for all $a, a' \in \C$, which you can do by observing that
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Theorem~\ref{thm:general_volterra}.
+To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
+\begin{itemize}
+\item Condition~\eqref{cond:sing} {\em on $\hardpart^\alpha$ is satisfied}.
 
@@
 \[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
-Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Conversely, as $a$ and $a'$ approach $\zeta=\alpha$, the term
+Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Now we just have to deal with the term
+\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)}. \]
+%%From the fact that
+%%\[ Q(-\zeta) \in Q(-\alpha) + O\big(|\zeta - \alpha|\big) \]
+%%at $\zeta = \alpha$, we reason that
+%%\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)} \in \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a)-\alpha)} + O(1) \]
+%%at $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$.
+
+\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\]
+is bounded as $\zeta(a')$ approaches $\alpha$.
+\color{RoyalBlue}
+\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)(\zeta(a)-\alpha)}\right|< C  \]
+
+we know
+\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\right|< C  \]
+\color{black}
+Conversely, as $a'$ approaches $\zeta=\alpha$, the term
 
@@
 
-is bounded as $a,a'$ approach $\zeta=\alpha$, showing that $\hardpart^\alpha$ satisfies Condition \eqref{cond:sing}.
-
+is bounded as $a,a'$ approach $\zeta=\alpha$.
 \begin{verify}
-A kind of klunky way to do the Ahlfors exercise:
-\begin{align*}
-\frac{1}{p} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
--\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
-p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
-p'\big|_{\zeta = \alpha} & = \left.\left(\frac{p}{\zeta - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
-& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
-& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
-\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
-\end{align*}
-
-\color{magenta}
-\begin{align*}
-    \frac{1}{P} & = \sum_{\beta \in \roots} \frac{\pi_\beta}{\zeta - \beta} \\
--\frac{p'}{p^2} & = -\sum_{\beta \in \roots} \frac{\pi_\beta}{(\zeta - \beta)^2} \\
-p' & = \sum_{\beta \in \roots} \left(\frac{p}{\zeta - \beta}\right)^2 \pi_\beta \\
-&\\
-& \\
-P'\big|_{\zeta = \alpha} & = \left.\left(\frac{P}{t - \alpha}\right)^2\right|_{\zeta = \alpha} \pi_\alpha \\
-& = \left[\prod_{\beta \in \roots \smallsetminus \alpha} (\alpha - \beta)\right]^2 \pi_\alpha \\
-& = \left(p'\big|_{\zeta = \alpha}\right)^2 \pi_\alpha \\
-\frac{1}{p'\big|_{\zeta = \alpha}} & = \pi_\alpha
-\end{align*}
-for some constant $c_\beta$.
-\par\color{ForestGreen}
-First, observe that
+\par Proof of Ahlfors exercise. First, observe that
 \begin{align*}
@@
 \end{align*}
-
+Then we see that
 \begin{align*}
@@
 \end{verify}
-
-\par\color{RoyalBlue}
-First of all, we rewrite $\hat{\mathcal{P}}_{\alpha}\varphi=0$ as $\varphi = \volterra_\alpha \varphi $: %we introduce the notation $p(a):=P(-\zeta(a))$ and $q(a)=Q(-\zeta(a))$, then $\hat{P}_j$ is
-
-\begin{align*}
-    -\big[ p\, \varphi \big](a)= \int_{\zeta=\alpha}^a q  \, \varphi \, d\zeta' + \int_{\zeta=\alpha}^a k_R(a,\cdot)  \, \varphi \, d\zeta
-\end{align*}
-with \[k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, (\zeta(a)-\zeta(a'))^{j+1} \, (-\zeta(a'))^r\]
-
-is equivalent to
-
-\begin{align}
-   \nonumber \varphi (a)& =-\int_{\zeta=\alpha}^a \frac{q}{p(\zeta(a))}  \, \varphi \, d\zeta' - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(\zeta(a))}  \, \varphi \, d\zeta' \\
-   \nonumber \varphi (a)& =\Big[ \hardpart^\alpha \, \varphi \Big](a)+ \Big[\softpart^\alpha \, \varphi\Big](a) \\
-   \varphi(a) &=\Big[ \volterra^\alpha \, \varphi \Big](a)
-\end{align}
-\color{black}
+\end{itemize}
+
 \par\color{RoyalBlue}
 Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable.
-In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial willhave the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
+In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial will have the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
 notation $\zeta'$ not defined; switch to $\zeta(a')$?]}.

### 2023-08-17 reg-sing-volterra.tex
Work on cond:diag-basic and cond:eps-lambda in example
Flag failure of cond:eps-lambda in general case. Mention that cond:slow isn't
needed.

@@
 \begin{brainstorm}
+\item Deal with Condition~\eqref{cond:sing}
+\begin{itemize}
+\item In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?
+\end{itemize}
 \item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
@@
 \[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
+\textcolor{magenta}{\[ \zeta(a)\hardker(a, a') - \tau \]}
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
@@
 
-To apply Theorem~\ref{thm:general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}.
+To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}.
 \textcolor{orange}{[Explain how conditions shift from $\zeta = 0$ to $\zeta = \alpha$?]} When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
@@
 To do this, recall that the functions $R_r(z^{-1})$ are all holomorphic on the disk $|z| > A$.
-Consequently, for any $\lambda > A$, we have $R_{r,j} \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and all $j \in \{0, 1, 2, \ldots\}$.
+Consequently, for any $\lambda > A$, we have $|R_{r,j}| \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$.
 This is enough to show that $k_R$ is well-defined throughout $\C^2$.
@@
 
-Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Theorem~\ref{thm:general_volterra}.
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Proposition~\ref{prop:alt-general_volterra}.
 To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
 \begin{itemize}
-\item Condition~\eqref{cond:sing} {\em on $\hardpart^\alpha$ is satisfied}.
+\item Condition~\eqref{cond:sing} {\em on $\hardpart^\alpha$ is satisfied.}
 
@@
 \[ \frac{1}{P(-\zeta)} = \sum_{-\beta \in \roots} \frac{1}{-P'(-\beta)\,(\zeta - \beta)}, \]
-where $\roots$ is the zero set of $P$ \textcolor{orange}{[Ahlfors, {\em Complex Analysis}, \S1.4, Exercise~2]}. 
+where $\roots$ is the zero set of $P$ \cite[Section 1.4, Exercise~2]{ahlfors}. 
 It follows that
@@
 \end{verify}
-\end{itemize}
-
-\par\color{RoyalBlue}
-Notice that $\hardpart^\alpha$ is holomorphic and separable, while $\softpart^\alpha$ is holomorphic and non-separable.
-In addition, $\hardpart^\alpha$ is of the type defined in Section \ref{setting:basic} and it satisfies Condition \eqref{cond:sing}: by Taylor expanding the polynomials $p$ and $q$ around $\zeta = \alpha$ \textcolor{orange}{[the shifted polynomial will have the same degree as the original]} \textcolor{magenta}{[$\alpha$ is a number, not a point; write $c_0$ in place of $q(\alpha)$?
-notation $\zeta'$ not defined; switch to $\zeta(a')$?]}.
-\begin{align*}
-    -\frac{q}{p(a)}&=-\frac{\textcolor{magenta}{q(\alpha)}+c_1(\zeta\textcolor{magenta}{'}-\alpha)+c_2 (\zeta'-\alpha)^2+...}{-b_1(\zeta(a)-\alpha)+ b_2 (\zeta(a)-\alpha)^2+b_3(\zeta(a)-\alpha)^3+...}\\
-    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+ b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}\\
-    &=\frac{q(\alpha)}{b_1(\zeta(a)-\alpha)}\frac{1+c_1'(\zeta'-\alpha)+c_2' (\zeta'-\alpha)^2+...}{1+b_2' (\zeta(a)-\alpha)+b_3'(\zeta(a)-\alpha)^2+...}
-\end{align*}
-hence setting $\tau_\alpha:=\textcolor{magenta}{-}\frac{q}{p'}\textcolor{orange}{\big|_{\zeta = \alpha}}\neq 0$, we find
-\begin{equation*}
-    -\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}
-\end{equation*}
-is bounded as $\zeta(a')$ and $\zeta(a)$ approach $\alpha$.
+\color{Tan}
+\item \textcolor{orange}{[Condition~\eqref{cond:diag-basic} implies Condition~\eqref{cond:slow}, so we can drop this.]}
+
+$\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$. Hence for $a$ outside some neighbourhood $U$ of $\alpha$  
+\begin{align*}
+\sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
+\end{align*}
+and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$.
 \color{black}
-\par\color{SkyBlue}
-Since $p$ has only simple roots, the partial fraction decomposition of $1/p$ is
-\[ \sum_{\beta \in \roots} \left.\frac{1}{p'}\right|_{\zeta = \beta} \frac{1}{\zeta - \beta}, \]
-where $\roots$ is the set containing the values of $\zeta$ at the roots of $p$.
-\par\color{DarkTurquoise}
-\textcolor{orange}{Nicer formulation; note different definition of $\roots$:}\par
-
+\item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}
+
+Since we're trying to bound $\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
+First, rewrite
+\begin{align*}
+q(a') & = Q\big(-\zeta(a')\big) \\
+& = Q\big(\omega(a, a') - \zeta(a)\big)
+\end{align*}
+in the form
+\[ q(a') = Q_{d-1}\big(\zeta(a)\big)\;\omega(a, a')^{d-1} + \ldots + Q_1\big(\zeta(a)\big)\;\omega(a, a') + Q_0\big(\zeta(a)\big), \]
+where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$. We can then write $-\hardker^\alpha(a, a')$ in the form
+\[ \frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}, \]
+viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$.
+If we keep $a$ away from the roots of from the roots of $p$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$.
+It follows that for any $\lambda_\Delta > 0$, we have
+\[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
+over all $a$ outside a neighborhoood of the roots of $p$ and all $a'$ without restriction.
+
+For consistency with Condition~\eqref{cond:eps-lambda}, we choose $\lambda_\Delta > A$.
+\color{RoyalBlue}
+\item $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$.
+In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
 \color{black}
-
-Then, the proof will follow by Theorem \ref{thm:general_volterra}, once we proved that $\volterra^\alpha$ satisfies the required assumptions.
-
-\begin{enumerate}
-    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$.
-Hence for $a$ outside some neighbourhood $U$ of $\alpha$
-\begin{align*}
-    \sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
-\end{align*}
-    and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$. 
-    \item[$\bullet$] $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$.
-In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
-    \item[$\bullet$]  $\softpart^\alpha$ satisfies Condition \eqref{cond:eps-lambda}: recall that all functions $R_r(z^{-1})$ are holomorphic for $|z|>A$,
-
-    \begin{align*}
-        \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{| R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^j}{|p(\zeta(a))|}|\zeta(a')|^r  &\lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{A^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(\zeta(a))|}|\zeta(a')|^r \\
-        & \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(\zeta(a))|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
-        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
-        &\lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
-    \end{align*}
-now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
+\item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.} \textcolor{magenta}{[I think this bound fails unless $R_1, \ldots, R_{d-1}$ are zero, so let's restrict our attention to that case.]}
+
+First, obseve that
+\begin{align*}
+|\softker^\alpha(a, a')| & = \left|\frac{k_R(a, a')}{p(a)}\right| \\
+& \le \frac{1}{|p(a)|} \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^{j+1} |\zeta(a')|^r \\
+& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j.
+\end{align*}
+Now, choose $\lambda_\Delta > A$.
+Since the functions $R_r(z^{-1})$ are holomorphic on the disk $|z| > A$, we have $|R_{r,j}| \lesssim \lambda_\Delta^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$, as mentioned earlier.
+It follows that
+\begin{align*}
+\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j
+& \lesssim \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
+& \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+\end{align*}
+over all $a, a' \in \domain_\alpha^2$, so
+\begin{align*}
+|\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}.
+\end{align*}
+over all $a, a' \in \domain_\alpha^2$.
+\color{RoyalBlue}
+\begin{align*}
+|k_R(a,a')| & \le \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
+& \lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
+& \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
+& \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(a)|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
+& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
+& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
+\end{align*}
+\color{black}
+\textcolor{magenta}{[I'm pretty sure this is false, because $q(a')$ and $p(a)$ have independent arguments] $\langle$} now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ \textcolor{magenta}{$\rangle$} by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
 If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}
@@
 and $\gamma=1$.
-
-\end{enumerate}
-
+\end{itemize}
+\begin{brainstorm}
+\item Show that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:reg-p}.
+\item Apply Prosposition~\ref{prop:alt-general_volterra} to get result.
+\end{brainstorm}
+\par\color{Tomato}
 Finally, to get the result as stated, we need to show that
-\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha) \]
-for some constant $M$.
+\[ f_{0, \alpha} \in \zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha). \]
 Like in the proof of Proposition \ref{prop:alt-general_volterra}, it's enough to show that $p$ satisfies Condition \eqref{cond:reg-p} with $\epsilon=1$.

### 2023-08-21 reg-sing-volterra.tex
Revise cond:sing

@@
 \item In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?
+\end{itemize}
+\item Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}
+\begin{itemize}
+  \item Add $\lambda_\text{ratio}$ to Condition~\eqref{cond:diag-basic} as multiplicative constant.
+  \item \textcolor{gray}{Refer to Condition~\eqref{cond:diag-basic} in proof of Theorem~\ref{thm:proto-growth}.}
+  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSeaGreen}{[No other direct references found.]}
 \end{itemize}
@@
 \begin{conditions}
-\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
+\color{RoyalBlue}
+\condconst{sing}{\tau}%%\label{cond:sing}
+For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
 \[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
@@
 is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
+\color{black}
+\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
+\[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
+is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
+
+In addition, for each $\sigma > \tau$, the bound
+\[ |\hardker(a, a')| < \frac{\sigma}{\zeta(a)} \]
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
+%%by bringing $a$ and $a'$ close enough to $\zeta = 0$.
+%%is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
 \end{conditions}
@@
 
+\color{Brown}By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
+\[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
+for all $a \in \domain_\text{far}$ and $a' \in \domain$, as Condition~\eqref{cond:diag-basic} says we can do.
+Applying this bound on the diagonal in $\domain_\text{far}^2$, we learn that $|q/p| \le c_\Delta$ on $\domain_\text{far}$.
+In addition, by fixing some arbitrary  $b' \in \domain$, see that
+\begin{align*}
+\left|\frac{q(b')}{p(a)}\right| & \lesssim e^{\lambda_\Delta|\zeta(a) - \zeta(b')|} \\
+& \lesssim e^{\lambda_\Delta(|\zeta(a)| + |\zeta(b')|)} \\
+& \lesssim e^{\lambda_\Delta|\zeta(a)|} e^{\lambda_\Delta|\zeta(b')|} \\
+& \lesssim e^{\lambda_\Delta|\zeta(a)|}
+\end{align*}
+over all $a \in \domain_\text{far}$. Hence, $|1/p| \lesssim e^{\lambda_\Delta|\zeta|}$ on $\domain_\text{far}$. Using both of the bounds we just found, we reason that
+\begin{align*}
+|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
+& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
+& \lesssim e^{\lambda_\Delta|\zeta(a)|}\,e^{c_\Delta(|\zeta(a)| + |\zeta(b)|)} \\
+& \lesssim e^{(\lambda_\Delta + c_\Delta)|\zeta(a)|}\,e^{c_\Delta|\zeta(b)|} \\
+& \lesssim e^{\lambda_0|\zeta(a)|}
+\end{align*}
+over all $a \in \domain_\text{far}$, recalling that $\lambda_0 = \lambda_\Delta + c_\Delta$.
+Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$.
+Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
+\color{black}
+
+\color{MediumSpringGreen}
 Recall that in Condition~\eqref{cond:slow}, the constant $\lambda_0$ is the sum of two constants: $\lambda_p$, which controls the growth of $1/p$ at infinity, and $\lambda_\text{ratio}$, which controls the growth of $p/q$ at infinity.
@@
 Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
+\color{black}
 
 Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$.
-Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and Condition~\eqref{cond:slow} guarantees that $|\solproto|$ is bounded there.
+Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~\eqref{cond:slow} [add a new condition for this]} guarantees that $|\solproto|$ is bounded there.
 Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.
@@
 \end{align*}
+\color{OrangeRed}
+\begin{align*}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|
+\end{align*}
+Want: for all $\sigma > \tau$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
+\par\color{black}
 As $a$ and $a'$ approach $\zeta = \alpha$, the

### 2023-08-21 reg-sing-volterra.tex
Base sec:proto-construction-regularity proofs on new cond:sing

@@
 \begin{conditions}
-\color{RoyalBlue}
-\condconst{sing}{\tau}%%\label{cond:sing}
-For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
-\[ \hardker(a, a') - \frac{\tau}{\zeta(a)} \]
-\textcolor{magenta}{\[ \zeta(a)\hardker(a, a') - \tau \]}
-is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
-\color{black}
 \condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
@@
 \begin{equation}\label{eqn:sing-bound}
-\left|\frac{q(a')}{p(a)} - \frac{\tau}{\zeta(a)}\right| < C
+\left|\frac{q}{p} - \frac{\tau}{\zeta}\right| < C
 \end{equation}
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
+whenever $|\zeta| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
 \begin{align*}
@@
 \begin{proof}
-Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that Inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that Inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta| < \delta$.
 The subsequent argument, which we used to show that $\lim_{\zeta \to 0} \chi = 0$, actually supports a stronger conclusion: it shows that $|\chi| \lesssim |\zeta|^\tau$ on the region $|\zeta| < \delta$.
 This tells us that
-%%Like we did in the proof of Theorem~\ref{thm:basic_volterra}, find a radius $\delta > 0$ and a constant $C$ such that the bound \eqref{eqn:sing-bound} holds whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-At the end of the proof of Theorem~\ref{thm:basic_volterra}, we showed that $\chi(a)$
-
-%%The proof follows the argument we use at the end of the proof of Theorem \ref{thm:basic_volterra}.
-In particular, once we choose $\varepsilon>0$ we can choose $\delta>0$ such that for $\zeta(a)<\delta$ and $\zeta(a')<\delta$ the function
-
-%%\[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
 \[ |\solproto| \lesssim \left|\frac{1}{p}\right|\,|\zeta|^\tau \]
-on the region $|\zeta| < \delta$. Choosing a point $b'$ with $|\zeta(b')| < \delta$ and $q(b') \neq 0$, we can deduce that
+on the region $|\zeta| < \delta$.
+
+Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
+\[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
+\begin{align*}
+|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
+& \lesssim \left|\frac{1}{q(b')}\right|\,\frac{\sigma}{|\zeta|}\,|\zeta|^\tau \\
+& \lesssim |\zeta|^{\tau-1}
+\end{align*}
+on the region $|\zeta| < r$, as desired.
+
+\par\color{RoyalBlue}Choosing a point $b'$ with $|\zeta(b')| < \delta$ and $q(b') \neq 0$, we can deduce that
 \begin{align*}

### 2023-08-22 reg-sing-volterra.tex
Condition sing_tau updated

@@
 \begin{brainstorm}
-\item Deal with Condition~\eqref{cond:sing}
-\begin{itemize}
-\item In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?
-\end{itemize}
-\item Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}
-\begin{itemize}
-  \item Add $\lambda_\text{ratio}$ to Condition~\eqref{cond:diag-basic} as multiplicative constant.
+\item \textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}
+\begin{itemize}
+\item \textcolor{gray}{In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?} \textcolor{MediumSpringGreen}{[Yes.]}
+\item Rewrite arguments using new Condition~\eqref{cond:sing}.
+\item Show that example satisfies Condition~\eqref{cond:sing}.
+\end{itemize}
+\item \textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}
+\begin{itemize}
+  \item Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.
+  \item When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.
   \item \textcolor{gray}{Refer to Condition~\eqref{cond:diag-basic} in proof of Theorem~\ref{thm:proto-growth}.}
-  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSeaGreen}{[No other direct references found.]}
+  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSpringGreen}{[No other direct references found.]}
+\end{itemize}
+\item Set $R_1, \ldots, \ldots R_{d-1}$ to zero.
+\begin{itemize}
+\item Change definition.
+\item Change intro to clarify that our results only apply to some level~1 equations.
+\item Change intro to clarify that our results only apply to some level~1 equations.
 \end{itemize}
@@
 on the region $|\zeta| < r$, as desired.
-
-\par\color{RoyalBlue}Choosing a point $b'$ with $|\zeta(b')| < \delta$ and $q(b') \neq 0$, we can deduce that
-\begin{align*}
-|\solproto| & \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p}\right|\,|\zeta|^\tau \\
-& \lesssim \left|\frac{1}{q(b')}\right|\,\left|\frac{q(b')}{p} \zeta\right|\,|\zeta|^{\tau-1}.
-\end{align*}
-Since Inequality~\ref{eqn:sing-bound} implies that
-\begin{align*}
-\left|\frac{q(a')}{p(a)}\zeta(a)\right| & \le \tau + C|\zeta(a)| \\
-& \le \tau + C\delta
-\end{align*}
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$, we can conclude that $|\solproto| \lesssim |\zeta|^{\tau-1}$ on the region $|\zeta| < \delta$, as desired.
 \end{proof}
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:slow}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}} \textcolor{MediumSpringGreen}{\eqref{cond:slow}}.
+Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
 \end{prop}
@@
 Combining the conclusions above, we see that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain = \domain_\text{near} \cup \domain_\text{mid} \cup \domain_\text{far}$, as desired.
-\par\color{RoyalBlue}
-We choose $\varepsilon>0$, then by Condition \eqref{cond:sing} we can choose $\delta>0$ such that for $|\zeta(a)|<\delta$ and $|\zeta(a')|<\delta$ \textcolor{orange}{[there's no $a'$ here]} (arguing as in the proof of Proposition \ref{prop:asymptotic at zero}) we get a uniform bound
-
-\[   |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |f_0(a)|\leq  C_2(\delta)\, |\zeta(a)|^{-(\tau-1)} e^{-\lambda |\zeta(a)|} |\zeta(a)|^{\tau-1} \leq C_3(\delta)
-\]
-
-Now we study the regime $|\zeta(a)|>\delta$ and $|\zeta(a')|>\delta$ \textcolor{orange}{[there's no $a'$ here]}.
-Recall that in Condition \eqref{cond:slow} the constant $\lambda_0$ is the sum of two constants $\lambda_0=\lambda_p+\lambda_\text{ratio}$: $\lambda_p$ controls the growth of $p^{-1}$ at infinity, and $\lambda_\text{ratio}$ controls the growth of $p/q$ at infinity.
-
-In particular, 
-      \begin{align*}
-          |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} |f_0|&\leq  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|} \left\vert\frac{p(b)}{p(a)}\exp\left[-\int_{b}^{a}\frac{q}{p} d\zeta\right]\right\vert \\
-          & \lesssim  |\zeta(a)|^{1-\tau} e^{-\lambda_0 |\zeta(a)|}  \, e^{\lambda_p|\zeta(a)|}\exp\left[\int_{b}^{a} \Big\vert\frac{q}{p} \Big\vert |d\zeta| \right]\\
-          & \lesssim  |\zeta(a)|^{1-\tau} e^{-(\lambda-\lambda_p) |\zeta(a)|} \exp\Big[\lambda_\text{ratio} |\zeta(a)-\zeta(b)| \Big]
-      \end{align*}
-   which is bounded because $|\zeta(a)|>\delta$.
-\textcolor{orange}{[As Condition~\eqref{cond:slow} is currently stated, $|\zeta| > \delta$ may not be far enough from $\zeta = 0$ to get the $\lambda_p$ and $\lambda_\delta$ bounds.
-I've strengthened the condition so that $|1/p|$ and $|q/p|$ are at least bounded outside every neighborhood of $\zeta = 0$.]}
 \end{proof}
@@
 at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
-\par\color{RoyalBlue}
-Combining the arguments above, we see as desired that
-\[ \solproto \in M\zeta^{\tau - 1} + \singexpalg{\tau-1+\lambda'}(\domain), \]
-with 
-\[ M = \frac{p(b)}{\zeta(b)^{\tau}}\,B^{-1}\,e^{S(b)}. \]
 \end{proof}
@@
 \begin{proof}
+For the kernel $\hardker$ the claim follows from Condition \eqref{cond:sing}, namely for any $\sigma>\tau$ we can find a neighbourhood of $(0,0)\in\domain^2$ such that 
+\[ |\hardker(a, a')| \le \frac{\sigma}{|\zeta(a)|}. \]
+\color{RoyalBlue}
 Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$.
-However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrariy small margin.
+However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrary small margin.
 Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
-
+\color{black}
 Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
@@
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, \textcolor{orange}{[maybe talk about adapting conventions here, since we need that already for the definition of $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ to make sense]} and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
 When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
@@
 \end{lemma}
-\textcolor{orange}{[Where do we explain what $\domain_\alpha$ needs to look like in this example?]}
+
 \begin{rmk}
@@
 It follows that
+
+\begin{align*}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+\end{align*}
+
+Now we expand $Q$ at $\zeta=\alpha$ writing $Q=Q(-\alpha)+(\zeta-\alpha)Q_\text{extra}(\zeta)$ and we continue the previous computations, getting
+
+\begin{align}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & \notag =
+ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+ &\label{eqn:step} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
+ \end{align}
+
+First we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded when $a$ is close enough to $\zeta = \alpha$. In fact we have
+
+\begin{align*}
+-\frac{Q(-\zeta(a))}{P(-\zeta(a))} & =
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a) - \alpha)\,Q_\text{extra}(\zeta(a))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
+ \end{align*}
+
+Define $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$, then
+
+\[-\frac{Q(-\zeta(a))}{P(-\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)}\]
+
+Since $Q$ is a polynomial, by bringing $a$ close enough to $\zeta=\alpha$ we can bound both $Q(-\zeta(a))/(\zeta(a)-\beta)$ and $Q_\text{extra}(\zeta(a))$.
+
+Then, we want to prove that for all $\sigma > \tau_\alpha$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
+From Equation \eqref{eqn:step}, taking the absolute value we get
+
+\begin{align*}
+\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|
+\end{align*}
+
+Notice that by bringing $\zeta(a')$ close enough to $0$ we can make the middle term
+
+\[\left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right|\]
+
+arbitrary small. Similarly, by bringing also $\zeta(a)$ close to $0$ we can make the first term
+
+\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right|\]
+
+as small as we want. Hence, setting $\tau_\alpha=\left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|$, we have that for any $\sigma>\tau_\alpha$
+
+\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma. \]
+
+ %Want: for all $\sigma > \tau$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
+
+\color{RoyalBlue}
 \begin{align*}
@@
 \end{align*}
-\color{OrangeRed}
-\begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|
-\end{align*}
-Want: for all $\sigma > \tau$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
-\par\color{black}
 As $a$ and $a'$ approach $\zeta = \alpha$, the
@@
 is bounded as $\zeta(a')$ approaches $\alpha$.
-\color{RoyalBlue}
+\color{DarkTurquoise}
 \[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)(\zeta(a)-\alpha)}\right|< C  \]
@@
 \[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\right|< C  \]
-\color{black}
+
 Conversely, as $a'$ approaches $\zeta=\alpha$, the term
@@
 is bounded as $a,a'$ approach $\zeta=\alpha$.
+\color{black}
 \begin{verify}
@@
 \[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
-over all $a$ outside a neighborhoood of the roots of $p$ and all $a'$ without restriction.
+over all $a$ outside a neighborhood of the roots of $p$ and all $a'$ without restriction.
 

### 2023-08-25 reg-sing-volterra.tex
Clean up revisions related to cond:sing

@@
 holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
-%%by bringing $a$ and $a'$ close enough to $\zeta = 0$.
-%%is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
 \end{conditions}
@@
 \subsection{\textcolor{orange}{Notation}}
+Previously, we studied Volterra operators with a regular singularity at $\zeta=0$.
+However, when we study solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.
+Therefore, we have to set the notation, to deal with this more general situation.
+
+Here, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to be able to deal with singularities different from the origin.
+In fact, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.
+
 \begin{brainstorm}
@@
 We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
-For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain} replacing the origin $\zeta=0$ with $\zeta=\alpha$.
+For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain}, replacing the origin $\zeta=0$ with $\zeta=\alpha$.
 \end{rmk}
@@
 \begin{thm}\label{thm:example}
-For each root $-\alpha$ of $P$, the equation
+For each root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive, the equation
 \[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
@@
 of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
-%%The equation $\hat{P}_\alpha\psi_\alpha=0$ has a unique solution of the form
-%%\[ \psi_\alpha = \zeta^{\tau_\alpha-1} + f_{\star,\alpha} \]
-%%\[\psi_\alpha = f_{0,\alpha}+ f_{\star,\alpha}\]
-%%where $f_{0,\alpha}$ scales like $\zeta^{\tau_\alpha-1}$ as $\zeta$ goes to $\alpha$ and $f_{\star,\alpha}\in\singexpalg{\tau_\alpha}(\Omega_\alpha)$.
-The result holds for every critical point of $P$.
 \end{thm}
-%%\textcolor{magenta}{[In the old version, we need to show somewhere that $\zeta^{\tau_\alpha - 1}$ differs from a multiple of the prototype solution $f_{0,\alpha}$ by an element of $\singexpalg{\tau_\alpha}(\Omega_\alpha)$]}
-
 \begin{proof}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
@@
 It follows that
-
 \begin{align*}
 -\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-\end{align*}
-
-Now we expand $Q$ at $\zeta=\alpha$ writing $Q=Q(-\alpha)+(\zeta-\alpha)Q_\text{extra}(\zeta)$ and we continue the previous computations, getting
-
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
+\end{align*}
+Now we expand $Q$ around $-\alpha$, using the decomposition $Q(\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(\zeta)$ to split up the last term of the expression above:
 \begin{align}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & \notag =
- \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
- &\label{eqn:step} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} %% & \notag = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
+&\label{eqn:split-numerator} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
 \end{align}
-
-First we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded when $a$ is close enough to $\zeta = \alpha$. In fact we have
-
-\begin{align*}
--\frac{Q(-\zeta(a))}{P(-\zeta(a))} & =
-\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a) - \alpha)\,Q_\text{extra}(\zeta(a))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
- \end{align*}
-
-Define $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$, then
-
-\[-\frac{Q(-\zeta(a))}{P(-\zeta(a))}-\frac{\tau_\alpha}{\zeta(a)-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q_\text{extra}(\zeta(a))}{P'(-\alpha)}\]
-
-Since $Q$ is a polynomial, by bringing $a$ close enough to $\zeta=\alpha$ we can bound both $Q(-\zeta(a))/(\zeta(a)-\beta)$ and $Q_\text{extra}(\zeta(a))$.
-
-Then, we want to prove that for all $\sigma > \tau_\alpha$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
-From Equation \eqref{eqn:step}, taking the absolute value we get
-
-\begin{align*}
-\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right| + \left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|
-\end{align*}
-
-Notice that by bringing $\zeta(a')$ close enough to $0$ we can make the middle term
-
-\[\left|\frac{(\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)}\right|\]
-
-arbitrary small. Similarly, by bringing also $\zeta(a)$ close to $0$ we can make the first term
-
+First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. Equation~\eqref{eqn:split-numerator} tells us that
+\begin{align*}
+-\frac{Q(-\zeta)}{P(-\zeta)} & =
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
+&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
+\end{align*}
+Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
+\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)}\]
+Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.
+
+Next, we want to show that for any $\sigma > \tau_\alpha$, the bound
+\[ |\zeta(a) - \alpha| \left|\frac{q(a')}{p(a)}\right| < \sigma \]
+holds when $a$ and $a'$ are close enough to $\zeta = \alpha$.
+Taking the absolute value of both sides of Equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
+\begin{align*}
+\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right| + \tau_\alpha.
+\end{align*}
+By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
+\[\left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right|\]
+as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right|\]
 
-as small as we want. Hence, setting $\tau_\alpha=\left|\frac{Q(-\alpha)}{P'(-\alpha)}\right|$, we have that for any $\sigma>\tau_\alpha$
-
-\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma. \]
-
- %Want: for all $\sigma > \tau$, we have $|q(a')/p(a)| < \sigma/|\zeta(a) - \alpha|$ when $a, a'$ close enough to $\zeta = 0$.
-
-\color{RoyalBlue}
-\begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}
-\end{align*}
-As $a$ and $a'$ approach $\zeta = \alpha$, the
-\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \]
-part approaches the limit
-\[ \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\alpha)}{P'(-\beta)\,(\alpha - \beta)}. \]
-Hence, that part is bounded on a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$. Now we just have to deal with the term
-\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)}. \]
-%%From the fact that
-%%\[ Q(-\zeta) \in Q(-\alpha) + O\big(|\zeta - \alpha|\big) \]
-%%at $\zeta = \alpha$, we reason that
-%%\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a)-\alpha)} \in \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a)-\alpha)} + O(1) \]
-%%at $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$.
-
-\[ \frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\]
-is bounded as $\zeta(a')$ approaches $\alpha$.
-\color{DarkTurquoise}
-\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)(\zeta(a)-\alpha)}\right|< C  \]
-
-we know
-\[ \left|\frac{Q(-\zeta(a'))}{P'(-\alpha)}-\frac{Q(-\alpha)}{P'(-\alpha)}\right|< C  \]
-
-Conversely, as $a'$ approaches $\zeta=\alpha$, the term
-
-\[\frac{Q(-\zeta(a'))}{P'(-\alpha)(\zeta(a)-\alpha)}\]
-
-converges to $\frac{\tau_\alpha}{\zeta(a)-\alpha}$ with $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$. We conclude that 
-\[-\frac{q(a')}{p(a)}-\frac{\tau_\alpha}{\zeta(a)-\alpha}\]
-
-is bounded as $a,a'$ approach $\zeta=\alpha$.
-\color{black}
+as small as we want. Hence, for any $\sigma > \tau_\alpha$, the bound
+\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma \]
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$.
 \begin{verify}
-\par Proof of Ahlfors exercise. First, observe that
+\par Solution of Ahlfors exercise. First, observe that
 \begin{align*}
@@
 \end{verify}
-\color{Tan}
-\item \textcolor{orange}{[Condition~\eqref{cond:diag-basic} implies Condition~\eqref{cond:slow}, so we can drop this.]}
-
-$\hardpart^\alpha$ satisfies Condition \eqref{cond:slow}: by assumption $p$ and $q$ are polynomials, and $q$ has degree less that $p$. Hence for $a$ outside some neighbourhood $U$ of $\alpha$  
-\begin{align*}
-\sup_U \Big\vert \frac{1}{p}\Big\vert =:c_p \qquad\qquad \sup_U \Big\vert\frac{q}{p}\Big\vert =:\lambda_\text{ration} 
-\end{align*}
-and we set $\lambda_0:=\log(c_p)+\lambda_\text{ratio}$.
-\color{black}
 \item Condition~\eqref{cond:diag-basic} {\em on $\hardpart^\alpha$ is satisfied.}
@@
 For consistency with Condition~\eqref{cond:eps-lambda}, we choose $\lambda_\Delta > A$.
-\color{RoyalBlue}
-\item $\hardpart^\alpha$ satisfies Condition \eqref{cond:diag-basic}: in fact $p$ and $q$ are polynomials and $q$ has degree less than $p$, hence their ratio is exponentially bounded if $\zeta(a), \zeta(a')$ are far from $\alpha$.
-In particular, $\lambda_\Delta=2A$ is a possible choice, where $A$ is the radius of convergence of the functions $R_r$ (see \ref{sec:level 1 ODE}).
-\color{black}
 \item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.} \textcolor{magenta}{[I think this bound fails unless $R_1, \ldots, R_{d-1}$ are zero, so let's restrict our attention to that case.]}

### 2023-08-29 reg-sing-volterra.tex
Work on replacing cond:slow with revised cond:diag-basic

@@
 \newlist{conditions}{itemize}{1}
-\setlist[conditions]{leftmargin=24mm, rightmargin=12mm}
+\setlist[conditions]{leftmargin=28mm, rightmargin=12mm}
 \makeatletter
@@
 \item Rewrite arguments using new Condition~\eqref{cond:sing}.
-\item Show that example satisfies Condition~\eqref{cond:sing}.
+\item \textcolor{gray}{Show that example satisfies Condition~\eqref{cond:sing}.}
 \end{itemize}
@@
 \begin{itemize}
-  \item Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.
-  \item When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.
+  \item Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.
+  \item \textcolor{gray}{Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.}
+  \item \textcolor{gray}{When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.} \textcolor{MediumSpringGreen}{[No change required]}
   \item \textcolor{gray}{Refer to Condition~\eqref{cond:diag-basic} in proof of Theorem~\ref{thm:proto-growth}.}
@@
 Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this helpful behavior in the class of differential equations that Ecalle calls {\em level~1}, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
-This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.
+In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
+\textcolor{SpringGreen}{This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.}
 
@@
 In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$.
-Since $\domain$ doesn't contain $\zeta = 0$, we'll always leave that starting point out of the path.
+Since $\domain$ doesn't contain $\zeta = 0$, we'll always omit that starting point from the path.
 \end{conditions}
@@
 \begin{conditions}
-\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---the {\em residue} of the singularity---the difference
+\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
 \[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
@@
 In addition, for each $\sigma > \tau$, the bound
-\[ |\hardker(a, a')| < \frac{\sigma}{\zeta(a)} \]
+\[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
 holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
 \end{conditions}
-We'll assume that $\tau$ is real and positive.
-
-Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
-\begin{verify}
-[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded.
+%%Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
+%%\begin{verify}
+%%[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded.
 By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition.
 Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
-\end{verify}
-For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
-\begin{conditions}
-\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
-\begin{align*}
-\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
-\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
-\end{align*}
-outside some neighborhood of $\zeta = 0$ in $\domain$.
+%%\end{verify}
+%%For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
+%%\begin{conditions}
+%%\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
+%%\begin{align*}
+%%\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
+%%\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
+%%\end{align*}
+%%outside some neighborhood of $\zeta = 0$ in $\domain$.
 In addition, $|1/p|$ and $|q/p|$ are bounded outside every neighborhood of $\zeta = 0$ in $\domain$; the bound may depend on the neighborhood.
@@
 The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
-\end{conditions}
-This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
+%%\end{conditions}
+%%This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+For most of our results, we'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$.
+We'll require $\hardker$ to be bounded on the diagonal in $\domain^2$, and to grow at most exponentially as we move away from the diagonal.
+Conveniently, these two requirements can be combined into one condition.
+\textcolor{Tomato}{[Add only-singularity condition.]}
 \begin{conditions}
-\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} We can find a constant $\lambda_\Delta$ with
-\[ \big| \hardker(a, a') \big| \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
-over all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
+\condconst{diag$_0$}{\lambda_\Delta, \lambda_0}\label{cond:diag-basic} We can find constants $\lambda_\Delta$ and $c_\Delta$ with
+\[ \big| \hardker(a, a') \big| \le c_\Delta e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+for all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
+In most cases, $c_\Delta$ will only enter our reasoning through the sum $\lambda_0 = \lambda_\Delta + c_\Delta$.
 %%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
@@
 The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
-To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\Omega^2$.
+To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
 This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
@@
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}} \textcolor{MediumSpringGreen}{\eqref{cond:slow}}.
-Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
 \end{prop}
@@
 
-\color{Brown}By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
+By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
 \[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
@@
 Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
-\color{black}
-
-\color{MediumSpringGreen}
-Recall that in Condition~\eqref{cond:slow}, the constant $\lambda_0$ is the sum of two constants: $\lambda_p$, which controls the growth of $1/p$ at infinity, and $\lambda_\text{ratio}$, which controls the growth of $p/q$ at infinity.
-By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ where $|1/p| \lesssim e^{\lambda_p |\zeta|}$ and $|q/p| \le \lambda_\text{ratio}$, as Condition~\eqref{cond:slow} says we can do.
-Observe that
-\begin{align*}
-|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
-& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
-& \lesssim e^{\lambda_p|\zeta(a)|}\,e^{\lambda_\text{ratio}(|\zeta(a)| + |\zeta(b)|)} \\
-& \lesssim e^{\lambda_0|\zeta(a)|}\,e^{\lambda_\text{ratio}|\zeta(b)|} \\
-& \lesssim e^{\lambda_0|\zeta(a)|}
-\end{align*}
-over all $a \in \domain_\text{far}$.
-Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$.
-Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
-\color{black}
 
 Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$.
-Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~\eqref{cond:slow} [add a new condition for this]} guarantees that $|\solproto|$ is bounded there.
+Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~[add a new condition for this]} guarantees that $|\solproto|$ is bounded there.
 Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.
@@
 \begin{proof}
-For the kernel $\hardker$ the claim follows from Condition \eqref{cond:sing}, namely for any $\sigma>\tau$ we can find a neighbourhood of $(0,0)\in\domain^2$ such that 
-\[ |\hardker(a, a')| \le \frac{\sigma}{|\zeta(a)|}. \]
-\color{RoyalBlue}
+First, choose some $\sigma_0 \in (\tau, \sigma)$. Condition~\eqref{cond:sing} tells us that by making $\delta > 0$ small enough, we can ensure that
+\[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
+whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
+\par\color{RoyalBlue}
 Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$.
@@
 In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}.
-\subsection{\textcolor{orange}{Notation}}
+\subsection{Notation}\label{sec:notation_alpha}
 Previously, we studied Volterra operators with a regular singularity at $\zeta=0$.
-However, when we study solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.
-Therefore, we have to set the notation, to deal with this more general situation.
-
-Here, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to be able to deal with singularities different from the origin.
-In fact, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.
+However, when we look at solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.
+
+Here, we adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results}, to deal with this more general situation.
+First of all, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.
+As a consequence, references to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, or equivalently $\zeta=\alpha$.
+
+Recalling that $\domain$ is star-shaped around $\zeta=0$ (see Condition \eqref{cond:star}), we introduce the notation $\domain_\alpha$ for domains star-shaped around $\zeta=\alpha$.
+Then, the function space $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ is the space of holomorphic functions in $\domain_\alpha$, uniformly of exponential type $\Lambda$ and with a power-law singularity at $\zeta=\alpha$.
+Explicitly, $f\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ if
+
+\[ e^{-\Lambda |\zeta-\alpha|} |\zeta-\alpha|^{-\sigma} |f| \]
+
+is uniformly bounded in $\domain_\alpha$.
+
+Finally, we rewrite conditions for Volterra operators with a regular singularity at $\zeta=\alpha$: the changes will affect only Conditions that control the behaviour of the operator near $\zeta=\alpha$, namely Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}.
+We say that a Volterra operator $\volterra_\alpha$ with a regular singularity at $\zeta=\alpha$ satisfies Condition \eqref{cond:sing} if for some non-zero constant $\tau$, the difference
+\[k_\alpha(a,a')-\frac{\tau}{\zeta(a)-\alpha}\]
+is bounded in a neighbourhood of $\zeta(a)=\alpha$ in $\domain_\alpha$, where $k_\alpha$ denotes the kernel of $\volterra$. In addition, we require that for any $\sigma>\tau$, the bound 
+\[|k_\alpha(a,a')|<\frac{\sigma}{\zeta(a)-\alpha}\]
+holds over some neighbourhood of $\big(\zeta(a),\zeta(a')\big)=(\alpha,\alpha)$ in $\domain_\alpha^2$. 
+The operator $\volterra_\alpha$ satisfies Condition \eqref{cond:eps-lambda} if for some constant $\gamma>0$, we have
+\[ |k_\alpha(a,a')|\lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
+over all $a,a'\in\domain_\alpha$.
 

### 2023-08-30 reg-sing-volterra.tex
Make cond:diag-basic global using 1/zeta(a) factor
This makes lambda_0 annoying to define, so stop using it outside the proof of
thm:proto-growth.

@@
 \newlist{conditions}{itemize}{1}
-\setlist[conditions]{leftmargin=28mm, rightmargin=12mm}
+\setlist[conditions]{leftmargin=26mm, rightmargin=12mm}
 \makeatletter
@@
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-For most of our results, we'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$.
-We'll require $\hardker$ to be bounded on the diagonal in $\domain^2$, and to grow at most exponentially as we move away from the diagonal.
-Conveniently, these two requirements can be combined into one condition.
-\textcolor{Tomato}{[Add only-singularity condition.]}
+For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
+We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
+These requirements can be combined into one condition.
 \begin{conditions}
-\condconst{diag$_0$}{\lambda_\Delta, \lambda_0}\label{cond:diag-basic} We can find constants $\lambda_\Delta$ and $c_\Delta$ with
-\[ \big| \hardker(a, a') \big| \le c_\Delta e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
-for all $a$ in $\domain$ outside some neighborhood of $\zeta = 0$, and all $a' \in \domain$.
-In most cases, $c_\Delta$ will only enter our reasoning through the sum $\lambda_0 = \lambda_\Delta + c_\Delta$.
-%%outside a neighborhood of $\zeta(a) = 0$ in $\domain^2$.
+\condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
+\[ \big| \hardker(a, a') \big| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain$.
 \end{conditions}
+This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
+As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+
 We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
@@
 
-Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:slow}}. Then $f_0$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$ defined in Section~\ref{fn-spaces}.
+Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}.
+Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$} defined in Section~\ref{fn-spaces}.
 \end{thm}
@@
 \begin{thm}\label{thm:general_volterra}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}}, \eqref{cond:slow}, and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
 \[f = \volterra f\]
@@
 of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
-Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexp{\tau-1}{\lambda_0}(\Omega)$.
+Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\Omega)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\Omega)$}.
 
@@
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}. Then $\solproto$ belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}.
+Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}.
 \end{prop}
 \begin{proof}
-We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$.
-
-Find a neighborhood $\domain_\text{near}$ of $\zeta = 0$ where $|\solproto| \lesssim |\zeta|^{\tau-1}$, as Proposition~\ref{prop:asymptotic at zero} says we can do.
+We want to show that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ for some real constant $\lambda_0$.
+
+By Proposition~\ref{prop:asymptotic at zero}, we can find a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero on a bounded region, so we'll have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+
+%%On a bounded region, $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero, so we also have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+
+%%Find a neighborhood $\domain_\text{near}$ of $\zeta = 0$ where $|\solproto| \lesssim |\zeta|^{\tau-1}$, as Proposition~\ref{prop:asymptotic at zero} says we can do.
 By making $\domain_\text{near}$ bounded, we can prevent $e^{\lambda_0|\zeta|}$ from getting arbitrarily close to zero on $\domain_\text{near}$.
@@
 
-By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
+By Condition~\eqref{cond:diag-basic}, we have
+\begin{align*}
+|\hardker(a, a')| & \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \\
+& \lesssim \frac{1}{\delta} e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \\
+& \lesssim e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}
+\end{align*}
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. One consequence is that, for some $c_\Delta > 0$, we have
+\[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
+whenever $|\zeta(a)| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we learn that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
+\begin{align*}
+\left|\frac{q(b')}{p(a)}\right| & \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a) - \zeta(b')|} \\
+& \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta(|\zeta(a)| + |\zeta(b')|)} \\
+& \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)|} e^{\lambda_\Delta|\zeta(b')|} \\
+& \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)|}
+\end{align*}
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we reason that
+\begin{align*}
+|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
+& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
+& \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)|}\,e^{c_\Delta(|\zeta(a)| + |\zeta(b)|)} \\
+& \lesssim \frac{1}{|\zeta(a)|} e^{(\lambda_\Delta + c_\Delta)|\zeta(a)|}\,e^{c_\Delta|\zeta(b)|}
+\end{align*}
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$.
+Setting $\lambda_0 = \lambda_\Delta + c_\Delta$, we have $|\solproto| \lesssim |\zeta|^{-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| \ge \delta$.
+Since we're assuming $\tau$ is real and positive, $|\zeta|^\tau$ can't get arbitrarily close to zero on the region $|\zeta| > \delta$.
+It follows that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| \ge \delta$.
+Combining this with our earlier argument on the region $|\zeta| < \delta$, we get the desired result.
+
+\par\color{RoyalBlue}By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
 \[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
@@
 over all $a \in \domain_\text{far}$, recalling that $\lambda_0 = \lambda_\Delta + c_\Delta$.
-Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$.
+Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$ \textcolor{Tomato}{[oops, wrong direction]}.
 Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
@@
 
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $f_0\in\singexp{\tau-1}{\lambda_0}(\Omega)$, then we'll show $\softpart f_0 \in\singexp{\tau-1+\gamma}{\Lambda}(\Omega)$ for $\Lambda\geq \lambda_\Delta$.
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$}, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\softpart \solproto \in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ for $\Lambda\geq \lambda_\Delta$}.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
@@
 \begin{cor}\label{cor:pertub_f0}
-Let $f_0$ be the prototype solution from Equation~\eqref{eqn:test_solution}.
-If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\Omega)$, for $\Lambda\geq \lambda_\Delta$.
+Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}.
+If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1+\gamma}{\Lambda}(\domain)$, for $\Lambda\geq \lambda_\Delta$}.
 \end{cor}
 \begin{proof}
-Since $\tau-1>-1$ the hypothesis of Proposition~\ref{prop:smoothing} are satisfied.
-In addition, recall that by Theorem \ref{thm:proto-growth}, $\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$.
-Therefore, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$.
+\textcolor{Tomato}{[Revise]}
+We know from Theorem~\ref{thm:proto-growth} that $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$.
+Choose a constant $\Lambda \ge \lambda_\Delta$ big enough that $\solproto$ is in $\singexp{\tau-1}{\Lambda}(\domain)$.
+Since we're assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
+
+\textcolor{RoyalBlue}{Since $\tau-1>-1$ the hypothesis of Proposition~\ref{prop:smoothing} are satisfied.
+In addition, recall that by Theorem~\ref{thm:proto-growth}, $\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$.
+Therefore, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$.}
 \end{proof}
@@
 The base point for the construction can be chosen arbitrarily.
-Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$.
-Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\Omega)$ that makes $\solwhole = \solproto + \solptb$ a solution of
+Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}.
+Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of
 \begin{equation}\label{eqn:orig-homog}
@@
 \end{align}
-Since we know that $\solproto$ is in $\singexp{\tau-1}{\lambda_0}(\Omega)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexp{\tau-1+\gamma}{\lambda_0}(\Omega)$.
+Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1+\gamma}{\lambda_0}(\domain)$}.
 Since $\tau+\gamma > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$.
+Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
 

### 2023-08-30 reg-sing-volterra.tex
Show that example satisfies new cond:diag-basic

@@
 However, when we look at solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.
+\textcolor{orange}{[I agree that the equation $\hat{\mathcal{P}}\Phi=0$ has a regular singularityat each root of $P(-\zeta)$, but I'm not sure I'd say $\hat{\mathcal{P}}_\alpha$ is singular in the way we've been using the term.
+Isn't it the operators $\volterra_\alpha$ which are clearly singular in our sense?]}
 
@@
 
-Since we're trying to bound $\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
+Since we're trying to bound $\zeta(a)\,\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
 First, rewrite
@@
 \[ q(a') = Q_{d-1}\big(\zeta(a)\big)\;\omega(a, a')^{d-1} + \ldots + Q_1\big(\zeta(a)\big)\;\omega(a, a') + Q_0\big(\zeta(a)\big), \]
-where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$. We can then write $-\hardker^\alpha(a, a')$ in the form
-\[ \frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P\big(-\zeta(a)\big)}, \]
+where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$.
+Next, knowing that $-\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
+We can then write $-\zeta(a)\,\hardker^\alpha(a, a')$ in the form
+\[ \zeta(a)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]
 viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$.
-If we keep $a$ away from the roots of from the roots of $p$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$.
-It follows that for any $\lambda_\Delta > 0$, we have
-\[ |\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
-over all $a$ outside a neighborhood of the roots of $p$ and all $a'$ without restriction.
+If we keep $a$ away from the roots of $p$ other than $\zeta = \alpha$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$.
+It follows that for any $\lambda_\Delta > 0$, and any domain $\domain_\alpha$ that avoids all the roots of $p$ other than $\zeta = \alpha$, we have
+\[ |\zeta(a)|\,|\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
+over all $a, a' \in \domain_\alpha$.
 

### 2023-08-30 reg-sing-volterra.tex
Revise description of notation for example section

@@
 \end{itemize}
-\item \textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}
-\begin{itemize}
-  \item Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.
+\item \textcolor{gray}{\textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}}
+\begin{itemize}
+  \item \textcolor{gray}{Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.}
   \item \textcolor{gray}{Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.}
@@
 \end{proof}
-Another bound, which works when the first argumetn of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
+Another bound, which works when the first argument of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
 \begin{prop}\label{prop:whole-ker-far-bound}
@@
 \subsection{Notation}\label{sec:notation_alpha}
-Previously, we studied Volterra operators with a regular singularity at $\zeta=0$.
-However, when we look at solutions of a level 1 differential equation $\mathcal{P}\Phi=0$, we'll get many Volterra-type operators $\hat{\mathcal{P}}_\alpha$---one at each root of $\zeta=\alpha$ of the polynomial $P(-\zeta)$---with a regular singularity at $\zeta=\alpha$.
-\textcolor{orange}{[I agree that the equation $\hat{\mathcal{P}}\Phi=0$ has a regular singularityat each root of $P(-\zeta)$, but I'm not sure I'd say $\hat{\mathcal{P}}_\alpha$ is singular in the way we've been using the term.
-Isn't it the operators $\volterra_\alpha$ which are clearly singular in our sense?]}
-
-Here, we adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results}, to deal with this more general situation.
-First of all, the role of the coordinate $\zeta$ will be played by $\zeta-\alpha$.
-As a consequence, references to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, or equivalently $\zeta=\alpha$.
-
-Recalling that $\domain$ is star-shaped around $\zeta=0$ (see Condition \eqref{cond:star}), we introduce the notation $\domain_\alpha$ for domains star-shaped around $\zeta=\alpha$.
-Then, the function space $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ is the space of holomorphic functions in $\domain_\alpha$, uniformly of exponential type $\Lambda$ and with a power-law singularity at $\zeta=\alpha$.
-Explicitly, $f\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ if
-
-\[ e^{-\Lambda |\zeta-\alpha|} |\zeta-\alpha|^{-\sigma} |f| \]
-
-is uniformly bounded in $\domain_\alpha$.
-
-Finally, we rewrite conditions for Volterra operators with a regular singularity at $\zeta=\alpha$: the changes will affect only Conditions that control the behaviour of the operator near $\zeta=\alpha$, namely Conditions \eqref{cond:sing} and \eqref{cond:eps-lambda}.
-We say that a Volterra operator $\volterra_\alpha$ with a regular singularity at $\zeta=\alpha$ satisfies Condition \eqref{cond:sing} if for some non-zero constant $\tau$, the difference
-\[k_\alpha(a,a')-\frac{\tau}{\zeta(a)-\alpha}\]
-is bounded in a neighbourhood of $\zeta(a)=\alpha$ in $\domain_\alpha$, where $k_\alpha$ denotes the kernel of $\volterra$. In addition, we require that for any $\sigma>\tau$, the bound 
-\[|k_\alpha(a,a')|<\frac{\sigma}{\zeta(a)-\alpha}\]
-holds over some neighbourhood of $\big(\zeta(a),\zeta(a')\big)=(\alpha,\alpha)$ in $\domain_\alpha^2$. 
-The operator $\volterra_\alpha$ satisfies Condition \eqref{cond:eps-lambda} if for some constant $\gamma>0$, we have
-\[ |k_\alpha(a,a')|\lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
-over all $a,a'\in\domain_\alpha$.
-
+So far, we've studied a Volterra equation with a regular singularity at $\zeta = 0$.
+When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we'll end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
+
+Throughout Section~\ref{sec:example}, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to this more general situation.
+The role of the coordinate $\zeta$ in those earlier sections will now be played by $\zeta-\alpha$.
+This substitution leads to several other reinterpretations, summarized below.
+
+References to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, which we'll rewrite as $\zeta=\alpha$.
+For example, we'll now work on a domain that touches but doesn't contain $\zeta = \alpha$, introducing the notation $\domain_\alpha$ as a reminder of this change.
+Condition~\eqref{cond:star} now says that $\domain_\alpha$ is star-shaped around $\zeta = \alpha$.
+The function space $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ becomes a space of holomorphic functions on $\domain_\alpha$ which have a power-law singularity at $\zeta=\alpha$ and are uniformly of exponential type $\Lambda$.
+Explicitly, $f$ is in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ if
+\[ |f| \lesssim |\zeta-\alpha|^{-\sigma} e^{-\Lambda |\zeta-\alpha|} \]
+over $\domain_\alpha$, making the norm
+\[ \|f\|_{\sigma, \Lambda} = \sup_{\domain_\alpha} |\zeta-\alpha|^{-\sigma} e^{-\Lambda |\zeta-\alpha|} |f| \]
+well-defined.
+
+Our conditions on Volterra operators change to describe a regular singularity at $\zeta = \alpha$.
+For example, consider a Volterra operator $\hardpart^\alpha$ of the kind described in Section~\ref{setting:basic}, with kernel $\hardker^\alpha$.
+This operator now satisfies Condition~\eqref{cond:sing} if for some real, positive constant $\tau_\alpha$, the difference
+\[ \hardker^\alpha(a, a) - \frac{\tau_\alpha}{\zeta(a) - \alpha} \]
+is bounded on a neighborhood of $\zeta(a) = \alpha$ in $\domain_\alpha$, and for each $\sigma > \tau_\alpha$, the bound
+\[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
+\textcolor{Tomato}{[Also describe change for Condition~\eqref{cond:diag-basic}.]} Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
+\[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]
+over all $a, a' \in \domain_\alpha$.
 \begin{brainstorm}
@@
     \begin{itemize}
-        \item References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.
-        \item Conditions on operators, location of regular singularity.
-        \item Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.
-        \item Definition of $\singexp{\sigma}{\Lambda}$ spaces.
+        \item \textcolor{gray}{References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.}
+        \item \textcolor{gray}{Conditions on operators, location of regular singularity.}
+        \item \textcolor{gray}{Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.}
+        \item \textcolor{gray}{Definition of $\singexp{\sigma}{\Lambda}$ spaces.}
     \end{itemize}
@@
 
-From Proposition \ref{prop:frac-int-smoothing}, we deduce that $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ admits a well defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
-Thus, using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that
+From Proposition \ref{prop:frac-int-smoothing}, we deduce that $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ has a well-defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that
 \[ \laplace_{\zeta,\alpha}^{\theta}\,\fracderiv{-\nu}{\zeta}{\alpha} \varphi = z^{-\nu} \laplace_{\zeta, \alpha}^{\theta} \varphi \]
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexp{\sigma}{\Lambda}(\domain_\alpha)$ and $\sigma>-1$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}%%\label{id:L-mult}
-\laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi.
-\end{equation}
+This generalizes the Laplace transform's action on derivatives: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+%%\begin{equation}\label{id:L-mult}
+\[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
+%%\end{equation}
 for all integers $n \ge 0$ and suitable directions $\theta$.
@@
 \begin{rmk}
+In the relationship between $\fracderiv{-\nu}{\zeta}{\alpha}$ and multiplication by $z^{-\nu}$ described above, smoothing out the singularity at $\zeta = \alpha$ in the position domain corresponds to speeding up the decay as $|z| \to \infty$ in the frequency domain.
+This is a general feature of the Laplace transform.
+\par\color{RoyalBlue}
 Increasing the regularity in the position domain, then the Laplace transform gives something which is faster decaying in the frequency domain. This is a general feature of the Laplace transform.
+\color{black}
 \end{rmk}
-
 \subsection{Going to the position domain}

### 2023-08-30 reg-sing-volterra.tex
Adapt proof of prop:whole-ker-far-bound to new cond:diag-basic

@@
 |\hardker(a, a')| & \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \\
-& \lesssim \frac{1}{\delta} e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \\
+& \lesssim \delta^{-1} e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \\
 & \lesssim e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-\par\color{RoyalBlue}
-Condition~\eqref{cond:sing} doesn't stop $|\hardker(a, a')|$ from exceeding $\frac{\tau}{|\zeta(a)|}$.
-However, by keeping $a$ and $a'$ close to $\zeta = 0$, we can make sure that $|\hardker(a, a')|$ only exceeds $\frac{\tau}{|\zeta(a)|}$ by an arbitrary small margin.
-Condition~\eqref{cond:sing} tells us that when $\delta > 0$ is small enough, there's a constant $C$ with
-\[ \left| \hardker(a, a') - \frac{\tau}{\zeta(a)} \right| < C \]
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. It follows that
-\begin{align*}
-|\hardker(a,a')| &\leq \frac{\tau}{|\zeta(a)|}+\left\vert\frac{\tau}{\zeta(a)} - \hardker(a,a')\right\vert \\
-&\leq \frac{\tau}{|\zeta(a)|} + C \\
-&= \frac{\tau + C|\zeta(a)|}{|\zeta(a)|} \\
-&\le \frac{\tau + C\delta}{|\zeta(a)|}
-\end{align*}
-whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. By shrinking the radius $\delta$, we can make $C\delta$ as small as we want.
-\color{black}
-Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$. The condition tells us that
+Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
+The condition tells us that
 \[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 |\kerwhole(a,a')|&\leq |\hardker(a,a')| + |\softker(a,a')|\\
-&\lesssim e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
-&\lesssim \big(1 + \delta^{-1} |\zeta(a)-\zeta(a')|^\gamma \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
+&\lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} + \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+&\lesssim \delta^{-1} \big(1 + |\zeta(a)-\zeta(a')|^\gamma \big) \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
 \end{align*}
 over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since
-\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\gamma \]
+\[ 1 + |\zeta(a)-\zeta(a')|^\gamma \]
 grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
-\[ 1 + \delta^{-1}|\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
+\[ 1 + |\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
 over all $a, a' \in \domain$. It follows that

### 2023-08-31 reg-sing-volterra.tex
Finish acknowledgements

@@
 \begin{brainstorm}
-\item \textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}
+\item \textcolor{gray}{\textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}}
 \begin{itemize}
 \item \textcolor{gray}{In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?} \textcolor{MediumSpringGreen}{[Yes.]}
-\item Rewrite arguments using new Condition~\eqref{cond:sing}.
+\item \textcolor{gray}{Rewrite arguments using new Condition~\eqref{cond:sing}.}
 \item \textcolor{gray}{Show that example satisfies Condition~\eqref{cond:sing}.}
@@
 \end{itemize}
+\item \textbf{(Veronica)} Make sure that everything is switched to the new Condition~\eqref{cond:diag-basic}.
+\textcolor{gray}{
 \item Set $R_1, \ldots, \ldots R_{d-1}$ to zero.
@@
 \item Change intro to clarify that our results only apply to some level~1 equations.
-\end{itemize}
+\end{itemize}}
 \item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
@@
 \end{rmk}
-%%To prove Theorem~\ref{thm:general_volterra}, we will rewrite the homogeneous equation we want to solve as an inhomogeneous one, with $\softpart f_0$ as the inhomogeneous term.
-
-%%We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, with the help of Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part}, which can be used to show that $\softpart f_0$ is regular enough to serve as the inhomogeneous term in the lemma.
 \subsection{Acknowledgements}
-
+We are grateful for the conversations with Kihyun Kim, Angeliki Menegaki, and Sung-Jin Oh that informed the early stages of this work.
 This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
-
-We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
-\begin{brainstorm}
-\item Kihyun Kim and his visitor (possibly Prof. Soonsik Kwon or Sung-Jin Oh)
-\item Angeliki Menegaki
-\end{brainstorm}
+It was also made possible by the hospitality of the Institut des Hautes \'{E}tudes Scientifiques during a return visit by AF, funded by the Fondation Math\'{e}matique Jacques Hadamard under the \textit{Junior Scientific Visibility} program.
 \section{Function spaces for holomorphic Volterra operators}\label{fn-spaces}
@@
 %%\begin{equation}\label{eqn:level 1 ode}
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
 %%\end{equation}
@@
 \item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
-\item[$\bullet$] $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
-\[ R_r(z^{-1}) = \sum_{j=0}^\infty R_{r,j} z^{-j} \]
-converge in the region $|z| > A$.
+\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
+\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
+converges in the region $|z| > A$.
 \end{enumerate}
-Equations of the form $\mathcal{P}\Phi = 0$ are called {\em level~1} by Ecalle~\cite[Section 2.1]{EcalleIII}.
-In \cite{borel_reg}, we'll study different examples using Laplace transform method and our existence and uniqueness result Theorem \ref{thm:general_volterra}.
+Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section 2.1]{EcalleIII}.
+In \cite{borel_reg}, we'll study different examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem \ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
@@
 over all $a, a' \in \domain_\alpha$.
-\begin{brainstorm}
-\item Previously, we always looked at Volterra operators with a regular singularity at $\zeta = 0$.
-\item When we try to solve a level~1 differential equation, we'll get an operator with many regular singularities---one at each root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
-\item Rules for working at $\zeta = \alpha$:
-\begin{itemize}
-    \item In all our work from Sections~\ref{sec:intro}--\ref{sec:proof_main_results}, the role of the coordinate $\zeta$ is played instead by $\zeta - \alpha$. Concrete examples of how to do that:
-    \begin{itemize}
-        \item \textcolor{gray}{References to the point $\zeta = 0$ become references to the point $\zeta - \alpha = 0$, or equivalently $\zeta = \alpha$.}
-        \item \textcolor{gray}{Conditions on operators, location of regular singularity.}
-        \item \textcolor{gray}{Since the $\domain$ is star-shaped around $\zeta = 0$, it's now star-shaped around $\zeta = \alpha$. Introduce notation $\domain_\alpha$.}
-        \item \textcolor{gray}{Definition of $\singexp{\sigma}{\Lambda}$ spaces.}
-    \end{itemize}
-\end{itemize}
-\end{brainstorm}
 \subsection{The Laplace transform}
@@
 This is a general feature of the Laplace transform.
-\par\color{RoyalBlue}
-Increasing the regularity in the position domain, then the Laplace transform gives something which is faster decaying in the frequency domain. This is a general feature of the Laplace transform.
-\color{black}
 \end{rmk}
@@
 For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
-\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha}^{-1})\circ (-\zeta)^r. \]
+\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
 If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
@@
 
-We can now state and prove the main result of this section, namely that the Volterra equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ admits a unique solution $\psi_\alpha$.
+We can now state and prove the main result of this section.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and doesn't touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain}.
+We'll show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
+By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
 %in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
-
 \begin{thm}\label{thm:example}
-For each root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive, the equation
+Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
+Then the equation
 \[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
@@
 \end{thm}
-\begin{proof}
+\begin{proof}[Proof of Theorem~\ref{thm:example}]
 Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
@@
 
-To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting}.
-\textcolor{orange}{[Explain how conditions shift from $\zeta = 0$ to $\zeta = \alpha$?]} When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
+To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
+When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
 \[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
 where
-\[ k_R(a,a')=\sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{R_{r,j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} \, \big(-\zeta(a')\big)^r. \]
+\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
-To do this, recall that the functions $R_r(z^{-1})$ are all holomorphic on the disk $|z| > A$.
-Consequently, for any $\lambda > A$, we have $|R_{r,j}| \lesssim \lambda^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$.
+To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
+Consequently, for any $\lambda > A$, we have $|R_{j}| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
 This is enough to show that $k_R$ is well-defined throughout $\C^2$.
@@
 \begin{align*}
-& \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z| > A \\
-\Longrightarrow & \sum_{j = 0}^\infty R_{r,j} z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
-\Longrightarrow & A^{-1} \le \operatorname{radius} R_{r,j} \\
-\Longrightarrow & A \ge \big(\operatorname{radius} R_{r,j}\big)^{-1} \\
-\Longrightarrow & A \ge \limsup_{j \to \infty} R_{r,j}^{1/j} \\
+& \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z| > A \\
+\Longrightarrow & \sum_{j = 0}^\infty R_j z^{-j} \text{ converges when } |z^{-1}| < A^{-1} \\
+\Longrightarrow & A^{-1} \le \operatorname{radius} R_j \\
+\Longrightarrow & A \ge \big(\operatorname{radius} R_j\big)^{-1} \\
+\Longrightarrow & A \ge \limsup_{j \to \infty} R_j^{1/j} \\
 \Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
@@
 For consistency with Condition~\eqref{cond:eps-lambda}, we choose $\lambda_\Delta > A$.
-\item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.} \textcolor{magenta}{[I think this bound fails unless $R_1, \ldots, R_{d-1}$ are zero, so let's restrict our attention to that case.]}
+\item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.}
 
@@
 |\softker^\alpha(a, a')| & = \left|\frac{k_R(a, a')}{p(a)}\right| \\
-& \le \frac{1}{|p(a)|} \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^{j+1} |\zeta(a')|^r \\
-& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j.
+& \le \frac{1}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^{j+1} \\
+& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^j.
 \end{align*}
 Now, choose $\lambda_\Delta > A$.
-Since the functions $R_r(z^{-1})$ are holomorphic on the disk $|z| > A$, we have $|R_{r,j}| \lesssim \lambda_\Delta^j$ over all $r \in \{1, \ldots, d-1\}$ and $j \in \{0, 1, 2, \ldots\}$, as mentioned earlier.
+Since $R(z^{-1})$ is holomorphic on the disk $|z| > A$, we have $|R_j| \lesssim \lambda_\Delta^j$ over all and $j \in \{0, 1, 2, \ldots\}$, as mentioned earlier.
 It follows that
 \begin{align*}
-\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, |\zeta(a)-\zeta(a')|^j
+\sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^j
 & \lesssim \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
@@
 over all $a, a' \in \domain_\alpha^2$, so
-\begin{align*}
-|\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}.
-\end{align*}
-over all $a, a' \in \domain_\alpha^2$.
-\color{RoyalBlue}
-\begin{align*}
-|k_R(a,a')| & \le \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{|R_{r,j}|}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
-& \lesssim \sum_{r=0}^{d-1}\sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, \frac{|\zeta(a)-\zeta(a')|^{j+1}}{|p(a)|}|\zeta(a')|^r \\
-& \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{r=0}^{d-1} |\zeta(a')|^r \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
-& \lesssim |\zeta(a)-\zeta(a')| \sum_{r=0}^{d-1} \frac{|\zeta(a')|^r}{|p(a)|}\,  e^{A |\zeta(a)-\zeta(a')|}\\
-& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \sum_{r=0}^{d-1} \frac{|\zeta'|^r}{|q(\zeta(a'))|} \, e^{A |\zeta(a)-\zeta(a')|}\\
-& \lesssim |\zeta(a)-\zeta(a')| \, \Big\vert \frac{q(\zeta(a'))}{p(a)}\Big\vert \,  e^{A |\zeta(a)-\zeta(a')|}
-\end{align*}
-\color{black}
-\textcolor{magenta}{[I'm pretty sure this is false, because $q(a')$ and $p(a)$ have independent arguments] $\langle$} now we notice that $\Big\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\Big\vert$ is bounded for $a,a'$ far from $\alpha$ \textcolor{magenta}{$\rangle$} by the argument we use in the proof of Condition \eqref{cond:diag-basic}.
-If $\zeta(a), \zeta(a')$ are close to $\alpha$ we can use Condition \eqref{cond:sing}
-
-\[    \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))}\right\vert  \leq \left\vert \frac{q(\zeta(a'))}{p(\zeta(a))} -\frac{\tau_\alpha}{\zeta(a)-\alpha}\right\vert + \frac{\tau_\alpha}{|\zeta(a)-\alpha|}\lesssim 1 +  \frac{\tau_\alpha}{|\zeta(a)-\alpha|} \]
-
+\[ |\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain_\alpha^2$. Like before, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, so we have
+\[ |\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a) - \alpha|\,\big|P_\alpha\big(\zeta(a)\big)\big|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain_\alpha$.
+Since $P_\alpha$ is a polynomial with a finite number of roots, and $\domain_\alpha$ doesn't touch any of the roots, $\big|P_\alpha\big(\zeta\big)\big|^{-1}$ is bounded on $\domain_\alpha$.
 We conclude that
-
-\[\left\vert \frac{k_R(a,a')}{p(\zeta(a))}\right\vert \lesssim \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a)-\alpha|}\, e^{2A |\zeta(a)-\zeta(a')|}  \]
-
-and $\gamma=1$.
+\[ |\softker^\alpha(a, a')| \lesssim \frac{|\zeta(a)-\zeta(a')|}{|\zeta(a) - \alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+over all $a, a' \in \domain_\alpha$, so Condition~\eqref{cond:eps-lambda} is satisfied with $\gamma = 1$.
 \end{itemize}
@@
 \end{brainstorm}
-\par\color{Tomato}
-Finally, to get the result as stated, we need to show that
-\[ f_{0, \alpha} \in \zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha). \]
-Like in the proof of Proposition \ref{prop:alt-general_volterra}, it's enough to show that $p$ satisfies Condition \eqref{cond:reg-p} with $\epsilon=1$.
-Since $p$ is a polynomial with a simple zero at $\zeta=\alpha$, we have that
-
-\[ p \in (\zeta-\alpha)\Big[ b_1 + O(\zeta-\alpha)\Big] \]
-in a small enough neighborhood of $\zeta=\alpha$.
-
-\color{RoyalBlue}
-Since we already know that $f_{0, \alpha}$ is of exponential type, it's enough to show that $f_{0, \alpha}$ falls into the class
-\[ (\zeta - \alpha)^{\tau_\alpha-1}\Big[M + O\big(|\zeta - \alpha|\big)\Big] \]
-when it's restricted to some neighborhood of $\zeta = \alpha$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
-\begin{align*}
-f_{0,\alpha}(a)&=\frac{p(b)}{p(a)}\, \exp\left(-\int_b^a\frac{q}{p} d\zeta\;\right)\\
-&=\frac{p(b)}{p(a)}\,\frac{(\zeta(a)-\alpha)^{\tau_\alpha}}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,\exp\left(-\int_b^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right)\\
-& = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,(\zeta(a)-\alpha)^{\tau_\alpha-1}\,\frac{(\zeta(a) - \alpha)}{p(a)} \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right),
-\end{align*}
-concluding that $f_{0,\alpha}$ is a constant multiple of
-\[ (\zeta(a)-\alpha)^{\tau_\alpha-1}\,\frac{\zeta(a)-\alpha}{p(a)} \, \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right). \]
-
-Since $p$ is a polynomial with a simple zero at $\zeta = \alpha$, we can deduce that
-\[ \frac{\zeta(a)-\alpha}{p(a)} \in b_1^{-1} + O\big(|\zeta - \alpha|\big), \]
-recalling that $b_1$ is the derivative of $p$ at $\zeta = \alpha$.
-
-Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ for which
-\[ \left| \frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha} \right| < C \]
-in some neighborhood $\domain_\text{near}$ of $\zeta = \alpha$. It follows that for all $a \in \domain_\text{near}$, the integral
-\[ S(a) = \int_{\zeta = \alpha}^a \left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta \]
-converges, allowing us to write
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) = e^{S(b)} e^{-S(a)} \]
-for $a \in \domain_\text{near}$. Observe that $|S| \le C |\zeta - \alpha|$ in $\domain_\text{near}$, implying that
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau_\alpha}{\zeta-\alpha}\right] d\zeta\right) \in e^{S(b)} \Big[1 + O\big(|\zeta - \alpha|\big) \Big] \]
-when we restrict to $\domain_\text{near}$.
-
-Combining the arguments above, we see as desired that
-\[ f_{0, \alpha} \in M\zeta^{\tau_\alpha - 1} + \singexpalg{\tau_\alpha}(\domain_\alpha), \]
-with
-\[ M = \frac{p(b)}{(\zeta(b)-\alpha)^{\tau_\alpha}}\,b_1^{-1}\,e^{S(b)}. \]
-
-\color{black}
 \end{proof}
@@
 \bibliography{airy-resurgence}
-
 \end{document}

### 2023-08-31 reg-sing-volterra.tex
Revise overview of {sec:image under soft_part}

@@
         \end{itemize}
-        \item \textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.
+        \item \textcolor{gray}{\textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.}
         \color{gray}
@@
 \subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
-
+Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$.
+This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
+\par\color{RoyalBlue}
 In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$}, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\softpart \solproto \in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ for $\Lambda\geq \lambda_\Delta$}.
-This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.
+This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}
 

### 2023-08-31 reg-sing-volterra.tex
Drop old references to lambda_0 in function space specifications
Also, drop old proofs of {prop:asymptotic at infinity} and cor:pertub_f0.

@@
 
-Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}.
-Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$} defined in Section~\ref{fn-spaces}.
+Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}. Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ defined in Section~\ref{fn-spaces}.
 \end{thm}
@@
 of the space $\singexpalg{\tau-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
-Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\Omega)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\Omega)$}.
+Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
 
@@
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}.
-Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
 \end{prop}
@@
 Combining this with our earlier argument on the region $|\zeta| < \delta$, we get the desired result.
-
-\par\color{RoyalBlue}By removing a bounded neighborhood of $\zeta = 0$ from $\domain$, make a set $\domain_\text{far}$ with
-\[ \hardker(a, a') \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|}, \]
-for all $a \in \domain_\text{far}$ and $a' \in \domain$, as Condition~\eqref{cond:diag-basic} says we can do.
-Applying this bound on the diagonal in $\domain_\text{far}^2$, we learn that $|q/p| \le c_\Delta$ on $\domain_\text{far}$.
-In addition, by fixing some arbitrary  $b' \in \domain$, see that
-\begin{align*}
-\left|\frac{q(b')}{p(a)}\right| & \lesssim e^{\lambda_\Delta|\zeta(a) - \zeta(b')|} \\
-& \lesssim e^{\lambda_\Delta(|\zeta(a)| + |\zeta(b')|)} \\
-& \lesssim e^{\lambda_\Delta|\zeta(a)|} e^{\lambda_\Delta|\zeta(b')|} \\
-& \lesssim e^{\lambda_\Delta|\zeta(a)|}
-\end{align*}
-over all $a \in \domain_\text{far}$. Hence, $|1/p| \lesssim e^{\lambda_\Delta|\zeta|}$ on $\domain_\text{far}$. Using both of the bounds we just found, we reason that
-\begin{align*}
-|\solproto(a)| & = \left| \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \right| \\
-& \le \left|\frac{1}{p(a)}\right| \exp\left(\int_{b}^{a}\left|\frac{q}{p}\right|\;d\zeta\right) \\
-& \lesssim e^{\lambda_\Delta|\zeta(a)|}\,e^{c_\Delta(|\zeta(a)| + |\zeta(b)|)} \\
-& \lesssim e^{(\lambda_\Delta + c_\Delta)|\zeta(a)|}\,e^{c_\Delta|\zeta(b)|} \\
-& \lesssim e^{\lambda_0|\zeta(a)|}
-\end{align*}
-over all $a \in \domain_\text{far}$, recalling that $\lambda_0 = \lambda_\Delta + c_\Delta$.
-Since $\domain_\text{far}$ avoids a neighborhood of $\zeta = 0$, we know $|\zeta|^{\tau-1}$ is bounded on $\domain_\text{far}$ \textcolor{Tomato}{[oops, wrong direction]}.
-Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{far}$.
-
-Finally, let $\domain_\text{mid}$ be the set that remains when you remove $\domain_\text{near}$ and $\domain_\text{far}$ from $\domain$.
-Since $\domain_\text{mid}$ avoids $\zeta = 0$ and is bounded, $|\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ can't get arbitrarily small there, and \textcolor{MediumSpringGreen}{Condition~[add a new condition for this]} guarantees that $|\solproto|$ is bounded there.
-Therefore, $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{mid}$.
-
-Combining the conclusions above, we see that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain = \domain_\text{near} \cup \domain_\text{mid} \cup \domain_\text{far}$, as desired.
 \end{proof}
@@
 Observing that $|\eta| \le C |\zeta|$ in $\domain_\text{near}$, we can conclude that
-\[ \exp\left(-\int_b^a\left[\frac{q}{p}+\frac{\tau}{\zeta}\right] d\zeta\right) \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
+\[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
 at $\zeta(a) = 0$.
@@
 \par\color{RoyalBlue}
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$}, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\softpart \solproto \in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ for $\Lambda\geq \lambda_\Delta$}.
+In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}
@@
 \end{proof}
-
 \begin{cor}\label{cor:pertub_f0}
 Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}.
-If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1+\gamma}{\Lambda}(\domain)$, for $\Lambda\geq \lambda_\Delta$}.
+If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
 \end{cor}
 \begin{proof}
-\textcolor{Tomato}{[Revise]}
 We know from Theorem~\ref{thm:proto-growth} that $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$.
@@
 Since we're assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
-
-\textcolor{RoyalBlue}{Since $\tau-1>-1$ the hypothesis of Proposition~\ref{prop:smoothing} are satisfied.
-In addition, recall that by Theorem~\ref{thm:proto-growth}, $\solproto\in\singexp{\tau-1}{\lambda_0}(\domain)$.
-Therefore, we can choose the constant $\Lambda=\max \{\lambda_0 , \lambda_\Delta\}$.}
-\end{proof}
-
+\end{proof}
 \subsection{Showing that $\volterra$ shrinks less singular functions \\ \textit{(toward Lemma~\ref{lem:perturbed_volterra})}}\label{sec:V is a contraction}
@@
 The base point for the construction can be chosen arbitrarily.
-Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}.
+Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$.
 Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of
@@
 \end{align}
-Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1}{\lambda_0}(\domain)$}, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$ \textcolor{MediumSpringGreen}{$\singexp{\tau-1+\gamma}{\lambda_0}(\domain)$}.
+Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
 Since $\tau+\gamma > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.

### 2023-08-31 reg-sing-volterra.tex
Hide verifications

@@
 \usepackage{tikz-cd} %% for term norm scratch work
+\usepackage{environ} % to hide verifications
 \usepackage{tikz}
@@
 % drafting environments
+\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+
+% hideable verifications
+\newif\ifshowverify
+\showverifyfalse
+\ifshowverify
 \newenvironment{verify}{\color{ForestGreen}}{\color{black}}
-\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+\else
+\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
+\fi
 
@@
 \subsection{Motivation}\label{motivation}
-In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic\begin{verify}\footnote{\begin{verify}Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
+In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+\begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
 Write $z$ in terms of its real and imaginary parts as $x + iy$.
 Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it.
-Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.\end{verify}}\end{verify} functions of a complex ``frequency'' variable $z$.
-Through identities like
+Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
 \begin{align*}
@@
 This is enough to show that $k_R$ is well-defined throughout $\C^2$.
-In fact, as we'll see later, it also leads to a useful bound on $k_R$.
+As we'll see later, it also leads to a useful bound on $k_R$.
 \begin{verify}
@@
 \Longrightarrow & A \ge \limsup_{j \to \infty} R_j^{1/j} \\
-\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_{r,j}^{1/j} \\
-\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_{r,j}^{1/j} < \lambda \\
-\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j}^{1/j} < \lambda \\
-\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_{r,j} < \lambda^j
+\Longrightarrow & A \ge \inf_{J \ge 0} \sup_{j \ge J} R_j^{1/j} \\
+\Longrightarrow & \forall \lambda > A: \exists J: \sup_{j \ge J} R_j^{1/j} < \lambda \\
+\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_j^{1/j} < \lambda \\
+\Longrightarrow & \forall \lambda > A: \exists J: \forall j \ge J: R_j < \lambda^j
 \end{align*}

### 2023-08-31 reg-sing-volterra.tex
Put the finishing touches on the proof of thm:example

@@
 For consistency with Condition~\eqref{cond:eps-lambda}, we choose $\lambda_\Delta > A$.
+\item Condition~\eqref{cond:reg-p} {\em on $\hardpart^\alpha$ is satisfied.}
+
+This is true because $p$ is a polynomial.
 \item Condition~\eqref{cond:eps-lambda} {\em on $\softpart^\alpha$ is satisfied.}
@@
 \end{itemize}
-\begin{brainstorm}
-\item Show that $\hardpart^\alpha$ satisfies Condition~\eqref{cond:reg-p}.
-\item Apply Prosposition~\ref{prop:alt-general_volterra} to get result.
-\end{brainstorm}
-\end{proof}
-
+We can now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
+\end{proof}
 \bibliographystyle{plain}

### 2023-08-31 reg-sing-volterra.tex
Drop commented-out draft text
Also, remove extra line breaks.

@@
 \newcommand{\spill}{4}
-%% previously violet!20
 \fill[ietcoast!33, bezier bounding box, path fading=radial edge]
@@
   arc (-60:-130:\spill) -- (0, 0);
-%% previously violet
 \fill[ietcoast!33!black] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = 0$};
@@
 \end{conditions}
-%%Our definition of a regular singularity implies that as $|\zeta|$ goes to zero, $|p|$ also goes to zero, while $|q|$ settles into a compact interval that doesn't include zero.
-%%\begin{verify}
-%%[\textit{Proof.} Fix any $a'$ in the neighborhood where the difference above is bounded.
-By confining $a$ to small enough neighborhoods of $\zeta = 0$, we can make $|\tau/\zeta(a)|$ arbitrarily large, forcing $|q(a')/p(a)|$ to become arbitrarily large to satisfy the definition.
-Since $a'$ is fixed, the only way for this ratio to get arbitrarily large is for $|p(a)|$ to get arbitrarily small.]
-%%\end{verify}
-%%For some of our results, we'll also need to control $|p|$ and $|q|$ in various ways as $|\zeta|$ goes to infinity.
-%%\begin{conditions}
-%%\condconst{slow}{\lambda_0}\label{cond:slow} We can find constants $\lambda_p$ and $\lambda_\text{ratio}$ with
-%%\begin{align*}
-%%\left|\frac{1}{p}\right| & \lesssim e^{\lambda_p |\zeta|} &
-%%\left|\frac{q}{p}\right| & \le \lambda_\text{ratio}
-%%\end{align*}
-%%outside some neighborhood of $\zeta = 0$ in $\domain$.
-In addition, $|1/p|$ and $|q/p|$ are bounded outside every neighborhood of $\zeta = 0$ in $\domain$; the bound may depend on the neighborhood.
-Note that this only constrains the ratio of $p$ and $q$ when they're evaluated at the same point.
-The constants will only enter our reasoning through their sum, $\lambda_0 = \lambda_p + \lambda_\text{ratio}$.
-%%\end{conditions}
-%%This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
-As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
@@
 \end{rmk}
-\color{black}
-
-%%---------
-%%Once we've understood the prototype solution $\solproto$, we can deform it to a solution of the equation we originaly set out to solve---the one involving the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}.
-
-%%The prototype solution $\solproto$ will be our reference point for studying the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}.
-
-%%Once we've understood the prototypical operator $\hardpart$, we perturb it to the more general operator $\volterra = \hardpart + \softpart$ described in Section~\ref{setting:perturbed}.
-The prototypical
-
-%%Since $\hardpart$ is the regular singular part of the perturbed operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed},
-%%---------
+
 When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we're trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
@@
 \end{proof}
-
 \subsubsection{Regularity}\label{sec:asymptotics}
 Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
-%%\begin{rmk}
-%%{\em Propositions \ref{prop:asymptotic at zero}} and \ref{prop:asymptotic at infinity} together prove {\em Theorem \ref{thm:proto-growth}}. 
-%%\end{rmk}
 \begin{prop}\label{prop:asymptotic at zero}
@@
 No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero on a bounded region, so we'll have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
-
-%%On a bounded region, $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero, so we also have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
-
-%%Find a neighborhood $\domain_\text{near}$ of $\zeta = 0$ where $|\solproto| \lesssim |\zeta|^{\tau-1}$, as Proposition~\ref{prop:asymptotic at zero} says we can do.
-By making $\domain_\text{near}$ bounded, we can prevent $e^{\lambda_0|\zeta|}$ from getting arbitrarily close to zero on $\domain_\text{near}$.
-Then we have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ on $\domain_\text{near}$.
 
@@
 \begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
-%\textcolor{magenta}{[we have to change the definition of $\hardker$ in \S \ref{setting:basic} in $-\frac{q(a')}{p(a)}$.]}
 Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}, which satisfies the equation
@@
 \end{proof}
-
 \section{A motivating example}\label{sec:example}
-%\color{black}
-%\section{\textcolor{orange}{[Proof of main results]}}
 \subsection{Overview}
@@
 Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
-%%\begin{equation}\label{eqn:level 1 ode}
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
-%%\end{equation}
 where
@@
 \subsubsection{Action on integral operators}\label{sec:L-int-op}
-%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
 For each $\nu \in (0, \infty)$, the fractional integral $\partial^{-\nu}_{\zeta, \alpha}$ is the Volterra operator defined by
@@
 
-%For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\mu}{\zeta}{0}$ are defined by composing $\fracderiv{\mu-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
-
-%For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-%\[ \fracderiv{n+\mu}{\zeta}{\alpha} := \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\mu-1}{\zeta}{\alpha}. \]
-
-%The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-%The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-%\begin{align*}
-%\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-%\end{align*}
 Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
@@
 \left[\fracderiv{-\nu}{\zeta}{\alpha} \varphi\right](a)&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a (\zeta(a)-\zeta)^{\nu-1} \, \varphi \; d\zeta\\
-%%&=\frac{1}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,  \big(\zeta(a) - \alpha\big)\, \varphi \; d\zeta\\
 &=\frac{\zeta(a)-\alpha}{\Gamma(\nu)}\int_{\zeta=\alpha}^a \frac{(\zeta(a)-\zeta)^{\nu-1}}{\zeta(a)- \alpha}\,\varphi \; d\zeta.
@@
 This generalizes the Laplace transform's action on derivatives: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-%%\begin{equation}\label{id:L-mult}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
-%%\end{equation}
 for all integers $n \ge 0$ and suitable directions $\theta$.
@@
 \begin{align*}
-\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha\\
-%%& = \laplace_{\zeta,\alpha}^{\theta}\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha})(-\zeta)^r\right]\psi_j\\
+\mathcal{P}\Psi_\alpha & = \mathcal{P}\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha \\
 & = \laplace_{\zeta,\alpha}^{\theta}\hat{\mathcal{P}}_\alpha\psi_\alpha.
@@
 By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
-%in the function space $(\zeta-\alpha_j)^{\tau_j}+\singexp{\tau_j}{\lambda}(\Omega_j)$.
 \begin{thm}\label{thm:example}
@@
 Now we expand $Q$ around $-\alpha$, using the decomposition $Q(\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(\zeta)$ to split up the last term of the expression above:
-\begin{align}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} %% & \notag = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\alpha) + (\zeta(a') - \alpha)\,Q_\text{extra}(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} \\
-&\label{eqn:split-numerator} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}
-\end{align}
+\begin{equation}\label{eqn:split-numerator}
+-\frac{Q(-\zeta(a'))}{P(-\zeta(a))} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
+\end{equation}
 First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. Equation~\eqref{eqn:split-numerator} tells us that

### 2023-08-31 reg-sing-volterra.tex
Update condition diag0 in section 4.3 Notation

@@
 \item \textcolor{gray}{\textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.}
-\item Work on acknowledgements
-\begin{itemize}
-\item \textbf{(Aaron)} Add people Aaron had conversations with
-\item \textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).
+\item \textcolor{gray}{Work on acknowledgements}
+\begin{itemize}
+\item \textcolor{gray}{\textbf{(Aaron)} Add people Aaron had conversations with}
+\item \textcolor{gray}{\textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).}
 \end{itemize}
@@
 \[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. \textcolor{orange}{[shouldn't be $|\zeta(a)|$ in the denominator?]}
 \end{conditions}
@@
 holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.  
-\textcolor{Tomato}{[Also describe change for Condition~\eqref{cond:diag-basic}.]} Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
+In addition, $\hardker^\alpha$ satisfies Condition~\eqref{cond:diag-basic} if for some constant $\lambda_\Delta$
+\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{|\zeta(a)-\zeta(a')|}\]
+over all $a,a'\in\domain_\alpha$. 
+Similarly, an operator $\softpart^\alpha$ with kernel $\softker^\alpha$ now satisfies Condition~\eqref{cond:eps-lambda} if for some constants $\gamma > 0$ and $\lambda_\Delta$, we have
 \[ |\softker^\alpha(a,a')| \lesssim \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)-\alpha|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|}\]

### 2023-08-31 reg-sing-volterra.tex
Fix typos and revise example list in intro

@@
 \end{itemize}
-\item \textbf{(Veronica)} Make sure that everything is switched to the new Condition~\eqref{cond:diag-basic}.
+\item \textcolor{gray}{\textbf{(Veronica)} Make sure that everything is switched to the new Condition~\eqref{cond:diag-basic}.}
 \textcolor{gray}{
@@
 Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equations describing the vibration modes of beams that taper in certain ways \textcolor{orange}{[find citation]}, and the Airy equation after a change of coordinate.
-\textcolor{SpringGreen}{This last example generalizes to some level 1 equations that feature in current research, like the Airy-Lucas and higher Airy equations~\cite[Equations 3.2 and 3.8]{charbonnier22}\cite{durugo_higher}.}
+In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
+This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.
+\begin{verify}
+[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
+This example works because the linear density of the beam and the second moment of area perpemdicular to the vibration direction are proportional, so they both end up in the $P(\partial)$ term.]\end{verify}
 
@@
 is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
-
 In addition, for each $\sigma > \tau$, the bound
-\[ \big|\hardker(a, a')\big| < \frac{\sigma}{\zeta(a)} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. \textcolor{orange}{[shouldn't be $|\zeta(a)|$ in the denominator?]}
+\[ \big|\hardker(a, a')\big| < \frac{\sigma}{|\zeta(a)|} \]
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
 \end{conditions}
@@
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-
+%\color{Tomato}
+%Furthermore, Condition \eqref{cond:diag-basic} tells us that for any $\sigma>0$ we can find a neighbourhood of $(0,0)\in\domain^2$ where 
+%\[|\hardker(a,a')|\le\frac{\sigma}{|\zeta(a)|}.\]
+\begin{verify}
+    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ \big| \hardker(a, a') \big| \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
+\begin{align*}
+    |\hardker(a,a')|&\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\\
+    &\le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta(|\zeta(a)|+|\zeta(a')|)}\\
+    &\frac{c}{|\zeta(a)|} e^{2\lambda_\Delta \delta}\\
+    &=\frac{\sigma}{|\zeta(a)|}
+\end{align*}
+\end{verify}
+\color{black}
 We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
@@
 The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
+%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
 \begin{thm}\label{thm:proto-growth}
@@
 \subsubsection{Regularity}\label{sec:asymptotics}
+%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}.
+The proofs of the Proposition below can be combined together.}
 Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
@@
 \begin{prop}\label{prop:asymptotic at infinity}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \textcolor{brown}{\eqref{cond:diag-basic}}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
 \end{prop}
@@
 This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
-\par\color{RoyalBlue}
-In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$.
+%\par\color{RoyalBlue}
+%In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$.
 This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}
@@
 \item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every critical point of $P$;
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
 \item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
@@
 Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section 2.1]{EcalleIII}.
-In \cite{borel_reg}, we'll study different examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem \ref{thm:general_volterra}.
+In \cite{borel_reg}, we'll study different examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
@@
 \[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$.  
-In addition, $\hardker^\alpha$ satisfies Condition~\eqref{cond:diag-basic} if for some constant $\lambda_\Delta$
-\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{|\zeta(a)-\zeta(a')|}\]
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$
+\[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a,a'\in\domain_\alpha$. 
@@
 We can now state and prove the main result of this section.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and doesn't touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain}.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and doesn't touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
 We'll show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
@@
 
-Since we're trying to bound $\zeta(a)\,\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
+Since we're trying to bound $\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
 First, rewrite
@@
 Next, knowing that $-\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
-We can then write $-\zeta(a)\,\hardker^\alpha(a, a')$ in the form
-\[ \zeta(a)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]
+We can then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
+\[ \big(\zeta(a)-\alpha\big)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]
 viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$.
@@
 It follows that for any $\lambda_\Delta > 0$, and any domain $\domain_\alpha$ that avoids all the roots of $p$ other than $\zeta = \alpha$, we have
-\[ |\zeta(a)|\,|\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
+\[ |\zeta(a)-\alpha|\,|\hardker^\alpha(a, a')| \lesssim e^{\lambda_\Delta|\omega(a, a')|} \]
 over all $a, a' \in \domain_\alpha$.

### 2023-08-31 reg-sing-volterra.tex

@@
 \end{abstract}
-
 \tableofcontents
-
-\begin{brainstorm}
-\item \textcolor{gray}{\textbf{(Veronica)} Deal with Condition~\eqref{cond:sing}}
-\begin{itemize}
-\item \textcolor{gray}{In Section~\ref{sec:V is a contraction}, do we only use Condition~\eqref{cond:sing} through Proposition~\ref{prop:whole-ker-near-bound}?} \textcolor{MediumSpringGreen}{[Yes.]}
-\item \textcolor{gray}{Rewrite arguments using new Condition~\eqref{cond:sing}.}
-\item \textcolor{gray}{Show that example satisfies Condition~\eqref{cond:sing}.}
-\end{itemize}
-\item \textcolor{gray}{\textbf{(Aaron)} Drop Condition~\eqref{cond:slow}, which is implied by Condition~\eqref{cond:diag-basic}}
-\begin{itemize}
-  \item \textcolor{gray}{Add a condition to ensure that $\zeta(a) = 0$ is the only singularity.}
-  \item \textcolor{gray}{Add $c_\Delta$ to Condition~\eqref{cond:diag-basic} as multiplicative constant, and export both of the constants $\lambda_\Delta$ and $\lambda_0 = \lambda_\Delta + c_\Delta$ from the condition.}
-  \item \textcolor{gray}{When showing that the example satisfies Condition~\eqref{cond:diag-basic}, make it consistent with new condition wording.} \textcolor{MediumSpringGreen}{[No change required]}
-  \item \textcolor{gray}{Refer to Condition~\eqref{cond:diag-basic} in proof of Theorem~\ref{thm:proto-growth}.}
-  \item \textcolor{gray}{Look for other direct references to Condition~\eqref{cond:slow}.} \textcolor{MediumSpringGreen}{[No other direct references found.]}
-\end{itemize}
-\item \textcolor{gray}{\textbf{(Veronica)} Make sure that everything is switched to the new Condition~\eqref{cond:diag-basic}.}
-\textcolor{gray}{
-\item Set $R_1, \ldots, \ldots R_{d-1}$ to zero.
-\begin{itemize}
-\item Change definition.
-\item Change intro to clarify that our results only apply to some level~1 equations.
-\item Change intro to clarify that our results only apply to some level~1 equations.
-\end{itemize}}
-\item \textcolor{gray}{\textit{(Aaron)} State Lemma~\ref{lem:perturbed_volterra} just the way we want it.}
-\begin{itemize}
-    \item \textcolor{gray}{Proofread and drop old version.}
-\end{itemize}
-\item \textcolor{gray}{\textit{(Aaron)} Finish introduction}
-\begin{itemize}
-\item \textcolor{gray}{\textit{(Veronica)} Brainstorm: what are we trying to say in this paper? Write ideas in the to-do list at the bottom of the motivation section.}
-\item \textcolor{gray}{\textit{(Veronica)} Revise introduction, if desired.}
-\end{itemize}
-\color{gray}
-\item \textit{(Veronica)} Say in Section~\ref{setting:perturbed} that $\volterra = \hardpart + \softpart$ and write arguments we need for bounds on whole kernel (for example, in Equation~\ref{near-limit}.
-\color{gray}
-\item \textit{(Veronica)} Review old blue text in Section~\ref{setting:perturbed} and decide whether we want to keep any of it. Can drop unilaterally. 
-\color{violet}
-\item Revise stuff related to proof of main results.
-\begin{itemize}
-        \item \textcolor{gray}{\textit{(Aaron)} Add proof of Lemma~\ref{lem:perturbed_volterra} to Section~\ref{sec:existence and uniqueness}}
-        \item \textcolor{gray}{\textit{(Aaron)} Revise proof of Theorem~\ref{thm:general_volterra} in Section~\ref{sec:existence and uniqueness}}
-        \begin{itemize}
-            \item \textcolor{gray}{Proofread revised proof.}
-        \end{itemize}
-        \item \textcolor{gray}{\textit{(Aaron)} State the desired result of Section~\ref{sec:image under soft_part}.}
-        \color{gray}
-        \item \textit{(Veronica)} Add motivation to Section~\ref{sec:image under soft_part}, explaining that the desired result of the section follows from a more general result about the smoothing effect of $\softpart$ (Proposition~\ref{prop:smoothing}).
-\textcolor{green}{I added a Corollary to explicitly write how Proposition \ref{prop:smoothing} implies the regularity we want for $\softpart f_0$}
-        \color{violet}
-        \item \textbf{(Aaron)} Confirm again that removed $\tau+\gamma$ upper bound on $\rho$ was unnecessary.
-\end{itemize}
-\item \textcolor{gray}{Revise text around main results.}
-\begin{itemize}
-    \item \textcolor{gray}{Decide whether to keep Lemma~\ref{lem:perturbed_volterra} as a lemma, or to make it a theorem, and make Theorem~\ref{thm:general_volterra} its corollary.
-Change order as appropriate.} \textcolor{purple}{Keep Lemma~\ref{lem:perturbed_volterra} as a lemma.
-State it after Theorem~\ref{thm:general_volterra}.}
-    \color{gray}
-    \item \textit{(Veronica)} Convert ``proof'' blocks to plain prose after main results. 
-\end{itemize}
-\color{gray}
-\item \textbf{(Veronica)} Edit statement of Theorem~\ref{thm:example} 
-\begin{itemize}
-    \item Edit or remove statements about making $\Lambda$ big enough
-    \item Figure out how to clean up $Q(-\zeta')$ business
-\end{itemize}
-\color{violet}
-\item \textcolor{gray}{Start finalizing notation for the two parts of the operator and the two parts of the solution.}
-\begin{itemize}
-    \item \textcolor{gray}{Choose subscripts or decorations to tell things apart in equations.} \textcolor{gray}{Change $\hardpart$ with $\volterra_0$ and $\softpart$ with $\volterra_\star$.
-Same for $\hardker$ and $\softker$.}
-    \item \textcolor{gray}{Choose names to tell things apart in prose. Currently using ``prototypical operator,'' ``prototype solution.'' Come up with names for perturbation stuff.}
-\end{itemize}
-\item \textbf{(Aaron)} Read through Section~\ref{sec:example}.
-\color{gray}
-\item \textbf{(Veronica)} Consider revising notation for roots. 
-\begin{itemize}
-\item ``$P$ is a monic degree-$d$ polynomial with only simple zeros;''
-\item ``$Q$ is a degree-$(d-1)$ polynomial, and $Q(-\alpha) \neq 0$ for for every zero $-\alpha$ of $P$;''---or even say it without formulas.
-\end{itemize}
-\color{violet}
-\item \textcolor{gray}{\textbf{(Aaron)} Change list formatting so that extra indentation applies only to conditions. We're using the \texttt{enumitem} package.}
-\item \textcolor{gray}{Work on acknowledgements}
-\begin{itemize}
-\item \textcolor{gray}{\textbf{(Aaron)} Add people Aaron had conversations with}
-\item \textcolor{gray}{\textbf{(Aaron)} Think about rephrasing FMHJ acknowledgement (ERC one can't be changed).}
-\end{itemize}
-\item \textcolor{gray}{Reconsider using $\lesssim$ (but still leaning not to)}
-\begin{itemize}
-    \item \textcolor{gray}{\textbf{(Aaron)} As an example, show how we could rewrite the argument in proof of Proposition~\ref{prop:asymptotic at infinity} with $\lesssim$.}
-\end{itemize}
-\item \textcolor{gray}{Write abstract.}
-\item \textcolor{gray}{\textbf{(Veronica)} Add table of contents.}
-\item \textcolor{gray}{Replace $\psi_0$ with $\chi$.}
-\item \textcolor{gray}{Replace $\epsilon$ with $\gamma$.}
-\item \textcolor{gray}{\textbf{(Aaron)} Use hyperref package. (For link color, use the same green as the verify environment, or maybe turquoise or RoyalBlue?)}
-\end{brainstorm}
 \section{Introduction}\label{sec:intro}
@@
 In addition, for each $\sigma > \tau$, the bound
-\[ \big|\hardker(a, a')\big| < \frac{\sigma}{|\zeta(a)|} \]
+\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|} \]
 holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
@@
 \condconst{diag$_0$}{\lambda_\Delta}\label{cond:diag-basic} For some constant $\lambda_\Delta$, we have
-\[ \big| \hardker(a, a') \big| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+\[ |\hardker(a, a')| \lesssim \frac{1}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 over all $a, a' \in \domain$.
@@
 \begin{verify}
-    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ \big| \hardker(a, a') \big| \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
@@
 \condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
-\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$.
@@
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
-Observing that $|\eta| \le C |\zeta|$ in $\domain_\text{near}$, we can conclude that
+Observing that $|\eta| \le C |\zeta|$ in $\near$, we can conclude that
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
@@
 This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
-%\par\color{RoyalBlue}
-%In this Section, we show that, under Condition \eqref{cond:eps-lambda}, the smoothing effect of the operator $\softpart$ regularizes the prototype solution $f_0$: recall from Section \ref{sec:asymptotics} that $\solproto \in \singexpalg{\tau-1}(\domain)$, then we'll show $\softpart \solproto \in\singexpalg{\tau-1+\gamma}(\domain)$.
-This is a consequence of a more general result (see Proposition \ref{prop:smoothing}), namely that $\softpart$ regularises functions in $\singexp{\sigma}{\Lambda}(\Omega)$ which are not too singular at $\zeta=0$.\color{black}
 
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-Under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
+Now, we'll show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
 The condition tells us that
-\[ \big| \softker(a, a') \big| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
+\[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
 over all $a, a' \in \domain$, which means that
-\[ \big| \softker(a, a') \big| \lesssim\frac{(2\delta)^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
+\[ | \softker(a, a') | \lesssim\frac{(2\delta)^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta(2\delta)}\]
 over all $a, a' \in \domain$ with $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$. Combining this conclusion with the previous one, we get the desired result.
@@
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
-Choose a subset $\domain_\text{far} \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
+Choose a subset $\far \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
 \[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
-over all $a \in \domain_\text{far}$ and $a' \in \domain$.
-\end{prop}
-\begin{proof}
-Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\domain_\text{far}$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that
+over all $a \in \far$ and $a' \in \domain$.
+\end{prop}
+\begin{proof}
+Find a radius $\delta > 0$ with $|\zeta| \ge \delta$ on $\far$, and choose some $\lambda > \lambda_\Delta$. Conditions \eqref{cond:diag-basic} and \eqref{cond:eps-lambda} tell us that
 \begin{align*}
@@
 \end{align*}
-over all $a \in \domain_\text{far}$ and $a' \in \domain$. Since
+over all $a \in \far$ and $a' \in \domain$. Since
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \]
@@
 \[ |\kerwhole(a,a')| \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \, e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
-over all $a \in \domain_\text{far}$ and $a' \in \domain$. This simplifies to the desired result.
+over all $a \in \far$ and $a' \in \domain$. This simplifies to the desired result.
 \end{proof}.
@@
 The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)\,\varphi\;d\zeta| \]
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
 for any choice of integration path.\footnote{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|} \int_0^{\zeta(a)} |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
-& = \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
+& = \|\varphi\|_{\rho-1, \Lambda}  \int_0^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
 \end{align*}
@@
 |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le
-\|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
-& \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
+\|\varphi\|_{\rho-1, \Lambda}  \int_0^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
+& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_0^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
 \end{align*}
@@
 for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^{\zeta(a)} M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \end{proof}
-\bibliographystyle{plain}
+
+\bibliographystyle{utphys}
 \bibliography{airy-resurgence}

### 2023-08-31 reg-sing-volterra.tex
remove unused libraries
Start tracking BBL file
Revise example introduction

@@
 \usepackage{amsthm}
-\usepackage{eqnarray}
 \usepackage{graphicx}
-\usepackage[svgnames]{xcolor} %% for revisions
-\usepackage{xparse} %% for squiggly underlines
-\usepackage{tikz-cd} %% for term norm scratch work
+\usepackage[svgnames]{xcolor} % for verifications
 \usepackage{environ} % to hide verifications
@@
 \subsection{Overview}
-We can use our understanding of regular singular Volterra equations study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-In particular, we can build a frame of analytic solutions in the frequency domain by studying solutions of an integral equation in the position domain.
-The latter is an example of the regular singular Volterra equations we introduced above.
+We can use our understanding of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+In particular, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
 \subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
@@
 \bibliographystyle{utphys}
-\bibliography{airy-resurgence}
+\bibliography{reg-sing-volterra}
 \end{document}

### 2023-08-31 reg-sing-volterra.tex
Revise and correct example intro

@@
 Choose a constant $\Lambda \ge \lambda_\Delta$ big enough that $\solproto$ is in $\singexp{\tau-1}{\Lambda}(\domain)$.
-Since we're assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
+Since we're assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\softpart \solproto$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
 \end{proof}
@@
 \subsection{Level $1$ differential equations}\label{sec:level 1 ODE}
-Let $\mathcal{P}$ be a linear differential operator of the form\footnote{ We follow Delabaere, rather than Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}.}
+Let $\mathcal{P}$ be a linear differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
@@
 \end{enumerate}
-Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section 2.1]{EcalleIII}.
-In \cite{borel_reg}, we'll study different examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
+Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
+In an upcoming paper \cite{borel_reg}, we'll study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
 So far, we've studied a Volterra equation with a regular singularity at $\zeta = 0$.
-When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we'll end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
-
-Throughout Section~\ref{sec:example}, we'll adapt the notation of Sections \ref{sec:intro}--\ref{sec:proof_main_results} to this more general situation.
-The role of the coordinate $\zeta$ in those earlier sections will now be played by $\zeta-\alpha$.
+When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we'll end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
+
+To adapt our previous reasoning to this more general situation, we'll reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
 This substitution leads to several other reinterpretations, summarized below.
@@
 Explicitly, $f$ is in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ if
-\[ |f| \lesssim |\zeta-\alpha|^{-\sigma} e^{-\Lambda |\zeta-\alpha|} \]
+\[ |f| \lesssim |\zeta-\alpha|^\sigma e^{\Lambda |\zeta-\alpha|} \]
 over $\domain_\alpha$, making the norm

### 2023-08-31 reg-sing-volterra.tex
Work on Laplace transform section

@@
 \[ |\hardker^\alpha(a, a')| < \frac{\sigma}{|\zeta(a) - \alpha|} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$
+holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha,\alpha)$ in $\domain_\alpha^2$. Condition~\eqref{cond:diag-basic} now requires that for some constant $\lambda_\Delta$,
 \[|\hardker^\alpha(a,a')|\lesssim\frac{1}{|\zeta(a)-\alpha|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \begin{align*}
-\fracderiv{-\nu}{\zeta}{\alpha}\,\fracderiv{-\mu}{\zeta}{\alpha} & = \fracderiv{-\nu-\mu}{\zeta}{\alpha} & \nu, \mu \in (0, \infty),
+\fracderiv{-\mu}{\zeta}{\alpha}\,\fracderiv{-\nu}{\zeta}{\alpha} & = \fracderiv{-\mu-\nu}{\zeta}{\alpha} & \mu, \nu \in (0, \infty),
 \end{align*}
@@
 For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
-\[ \varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
+\[ \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \singexp{\sigma+\nu}{\Lambda}(\domain_\alpha) \]
 continuously for all $\sigma > -1$ and $\Lambda \ge 0$.
@@
 
-From Proposition \ref{prop:frac-int-smoothing}, we deduce that $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ has a well-defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
+From Proposition~\ref{prop:frac-int-smoothing}, we deduce that when $\varphi$ belongs to $\singexpalg{\sigma}(\domain_\alpha)$ for some $\sigma > -1$, its fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}\varphi$ has a well-defined Laplace transform along any ray $\Gamma_{\zeta,\alpha}^{\theta}\subset\domain_\alpha$.
 Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that

### 2023-08-31 reg-sing-volterra.tex
Do some rewording in example section

@@
 \subsection{Going to the position domain}
-By the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
+Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
 \begin{lemma}\label{lem:use-dict}
@@
 We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
-For instance, $\domain_\alpha$ looks like the domain drawn in Section \ref{setting:domain}, replacing the origin $\zeta=0$ with $\zeta=\alpha$.
+As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
 \end{rmk}

### 2023-09-01 reg-sing-volterra.tex
Correct a few more typos and misleading wordings
This commit also includes a few cosmetic changes.

@@
 \begin{align*}
-\frac{\partial}{\partial z} \laplace \varphi & = \laplace(z\varphi) \\
+\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
 \laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-z^{-\lambda} \laplace \varphi & = \laplace\,\partial^{-\lambda} \varphi,
-\end{align*}
-where $\partial^{-\lambda}$ is the Riemann-Liouville fractional integral of order $\lambda \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+\end{align*}
+where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.
@@
 Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
-We also assume:
+Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$, and satisfies the following condition.
 \begin{conditions}
@@
 \end{conditions}
-For the applications we have in mind, $\domain$ might look something like the set pictured below, which satisfies Condition~\eqref{cond:star}.
+For the applications we have in mind, $\domain$ might look something like the set pictured below.
 \begin{center}
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This generalizes the Laplace transform's action on derivatives: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 viewing it as a polynomial in $\omega(a, a')$ whose coefficients are rational functions in $\zeta(a)$.
-If we keep $a$ away from the roots of $p$ other than $\zeta = \alpha$, each coefficient is bounded, so $|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$.
+If we keep $a$ away from the roots of $p$ other than $\zeta = \alpha$, each coefficient is bounded, so $|\zeta(a) - \alpha|\,|\hardker^\alpha(a, a')|$ is bounded by a polynomial in $|\omega(a, a')|$.
 It follows that for any $\lambda_\Delta > 0$, and any domain $\domain_\alpha$ that avoids all the roots of $p$ other than $\zeta = \alpha$, we have
@@
 over all $a, a' \in \domain_\alpha$.
-Since $P_\alpha$ is a polynomial with a finite number of roots, and $\domain_\alpha$ doesn't touch any of the roots, $\big|P_\alpha\big(\zeta\big)\big|^{-1}$ is bounded on $\domain_\alpha$.
+Since $P_\alpha$ is a polynomial with a finite number of roots, and $\domain_\alpha$ doesn't touch any of the roots, $|P_\alpha(\zeta)|^{-1}$ is bounded on $\domain_\alpha$.
 We conclude that

### 2023-09-01 reg-sing-volterra.tex
Put remarks in roman type instead of italic
If you intentionally put the remarks in italics, I'd be happy to
switch back to that convention.
Enlarge outer parentheses

@@
 
-%%\theoremstyle{definition}
-\newtheorem{defn}{Definition}
+\theoremstyle{definition}
+\newtheorem{rmk}{Remark}
 \theoremstyle{plain}
@@
 \newtheorem{thm}{Theorem}
-\newtheorem{rmk}{Remark}
 \newtheorem{cor}{Corollary}
@@
 \begin{align*}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} & = \sum_{-\beta \in \roots} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} \\
-& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q(-\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
+-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} & = \sum_{-\beta \in \roots} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} \\
+& = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{Q\big(-\zeta(a')\big)}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
 \end{align*}
@@
 \begin{equation}\label{eqn:split-numerator}
--\frac{Q(-\zeta(a'))}{P(-\zeta(a))} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)} + \frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta(a) - \alpha)}.
+-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
 \end{equation}
@@
 \begin{align*}
-\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)\,(\zeta(a) - \alpha)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right| + \tau_\alpha.
+\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha.
 \end{align*}
 By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
-\[\left|\frac{(\zeta(a') - \alpha)\,Q_\alpha(\zeta(a'))}{P'(-\alpha)}\right|\]
+\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right|\]
 as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
-\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q(-\zeta(a'))\,(\zeta(a) - \alpha)}{P'(-\beta)\,(\zeta(a) - \beta)}\right|\]
-
+\[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
 as small as we want. Hence, for any $\sigma > \tau_\alpha$, the bound
-\[|\zeta(a)-\alpha| \, \left|\frac{Q(-\zeta(a'))}{P(-\zeta(a))}\right| \le \sigma \]
+\[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
 holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (\alpha, \alpha)$ in $\domain_\alpha^2$.

### 2023-09-01 reg-sing-volterra.tex
no changes

@@
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
-
 \begin{rmk}
@@
 Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\cont(\Omega)$ be the space of continuous complex-valued functions on $\Omega$.
-Give $\cont(\Omega)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \Omega$~\cite[Example~2.6 and \S 4 notes]{fnl-cpx-anal}.
-The holomorphic functions form a closed subspace $\holo(\Omega) \subset \cont(\Omega)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-
-Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\Omega$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{(\Lambda+\varepsilon)|x|}$.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} They form a space $\singexp{0}{\Lambda}(\Omega)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\Omega e^{-\Lambda|\zeta|}\,|f|$.
-With respect to the seminorm on $\holo(\Omega)$ given by a compact set $K \subset \Omega$, the inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
+Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
+Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
+Give $\cont(\domain)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
+The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
+
+Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$, there's a constant $A_\varepsilon$---which may depends on $\varepsilon$---such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
+With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
 That means the inclusion is continuous.
 \begin{prop}\label{exp-complete}
-The space $\singexp{0}{\Lambda}(\Omega)$ is complete.
+The space $\singexp{0}{\Lambda}(\domain)$ is complete.
 \end{prop}
@@
 This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}$: picking some $r > 0$, we observe that
+We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
 \begin{align*}
@@
 Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
-Let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
+For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
 Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
@@
 Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
-Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.}
+Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
 \begin{prop}\label{prop:inclus-lt-pow-gt-exp}
@@
 \begin{prop}\label{prop:inclus-lt-pow-alg}
-When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
+When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
 \end{prop}
@@
 Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}$ by making $\Lambda$ big enough.
+Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\domain)$ by making $\Lambda$ big enough.
 \end{prop}

### 2023-09-01 reg-sing-volterra.tex
Tweak exponential type footnote

@@
 Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$, there's a constant $A_\varepsilon$---which may depends on $\varepsilon$---such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there's a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
 We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.

### 2023-10-17 exp-resurgence.tex
Clean up revisions related to cond:sing
Typos correction, update to-do list

@@
 
-\title{Borel regularity for ODEs and thimble integrals}
+\title{Borel regularity for ODEs and Thimble Integrals}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 \maketitle
+
+\begin{brainstorm}
+    \item Section~\ref{borel_reg-ODE}---definitely Section~\ref{setting-ODE}, and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
+    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
+    \item Section~\ref{contour-argument-AL}---revise the general contour argument
+    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
+    \begin{itemize}
+    \item Replace formalism in Section~\label{reg-decay}
+    \end{itemize}
+    \item Replace {\tt reg-sing-volterra} with the citation from Arxiv
+    \item Check which examples are still in the framework of our theorem
+    \begin{itemize}
+    \item Start a storage document for shelved examples
+    \end{itemize}
+    \item Section~\ref{resurgence-AL}---Draw intersection points figure
+    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
+    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
+    \begin{itemize}
+    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
+    \end{itemize}
+    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
+    \begin{itemize}
+    \item Put future goals in storage document
+    \end{itemize}
+\end{brainstorm}
 
@@
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
+\textcolor{orange}{[Picture below should show the constant-radius neighborhood]}
 \begin{center}
@@
   \begin{scope}[violet]
-    \draw (0, 0) -- (-\ang:\outsize);
+    \draw (0, 0) -- (\ang:\outsize);
     \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
@@
 
-\subsubsection{Why does Borel summation work for thimbles integrals?}
+\subsubsection{Why does Borel summation work for thimble integrals?}
 
@@
 \subsubsection{Setting}\label{setting-ODE}
-
-Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
+\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
 \begin{equation}
@@
 \item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$.
-In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $Omega_j$.
+In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$.
 Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
@@
     \includegraphics[scale=0.3]{figures/thimble_Airy.png}
-    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the region indicate and what the color]}}
+    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the regions indicate and what the color]}}
     \label{fig:path_Airy}
@@
 
-\subsection{Modified Bessel}
+\subsection{Modified Bessel}\label{sec:mod-bessel-lift}
 
@@
 
-\subsubsection{thimble projection formula}
+\subsubsection{Thimble projection formula}
 
@@
 
-In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using a trigonometric substitution.
-As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time using applying the thimble projection formula to the generalized Cardano's formula.
+In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using trigonometric substitution.
+As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time applying the thimble projection formula to the generalized Cardano's formula.
 
@@
 
-\textcolor{orange}{[add the numerical check to show simple resurgence]}
+\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of magnitude of function on position domain]}
 

### 2023-10-27 exp-resurgence.tex
Minor updates: add reference to our paper

@@
     \end{itemize}
-    \item Replace {\tt reg-sing-volterra} with the citation from Arxiv
     \item Check which examples are still in the framework of our theorem
@@
 
-Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite{nikolaev2023exact} Theorem~B.15 and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
+Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
 These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
@@
 labeled by the roots of $P$.
-This type of operators are the one we studied in {\tt reg-sing-volterra}, hence we know there exists a unique solution $\psi_j=f_{j,0}+f_{j,\star}$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and $f_{j,\star}\in\singexpalg{\tau_j}(\Omega_j)$ for an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+This type of operators are the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j=f_{j,0}+f_{j,\star}$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and $f_{j,\star}\in\singexpalg{\tau_j}(\Omega_j)$ for an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
 In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}$.
@@
 
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 {\tt reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (Theorem \ref{thm1}).
+Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (Theorem \ref{thm1}).
 
@@
 \end{align*}
-Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite{Witten} page 10).
+Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite[pag.10]{Witten}).
 
@@
 We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem 4 in {\tt reg-sing-volterra}).
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
 Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.
@@
 \item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following {\tt reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
 \item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
@@
 Assume the $\Gamma_{\zeta,\alpha}^\theta$ is contained in $\Omega_\alpha$.
-In {\tt reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namley of the form $|\zeta|^\sigma$.
+In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namley of the form $|\zeta|^\sigma$.
 When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta,\alpha}^\theta$ is a well--defined and holomorphic function for $\Re e^{-i\theta}z>0$ on the fiber $T^*B\vert_{\zeta=0}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
@@
 Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of \cite{sternin1995borel}.} that
+For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
 \[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see equation~35 in \cite{mladenov2014advanced}).
+and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
 
@@
 \end{align*}
-by reducing the integral to Euler's beta function (see 5.12.1 in \cite{dlmf}). This establishes that
+by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
 \begin{equation}\label{frac-diff-laplace}
@@
 
-the proof is a simple computation, and we refer to Definition 5.12 and Lemma 5.14 in \cite{diverg-resurg-i}.
+the proof is a simple computation, and we refer to  \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}.
 \begin{lemma}
@@
 \subsubsection{Setting}\label{setting-ODE}
-\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see footnote~1 in \S 5.2.2.1 of \cite{diverg-resurg-iii}}
+\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
 \begin{equation}
@@
 where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp-AL}
@@
 
-where in the second step we use the analytic continuation of the hypergeometric function (equation 15.2.3 in \cite{dlmf}).
+where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.
 
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\cite{charbonnier22}, equation~3.8
+with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\cite[Equation~3.8]{charbonnier22},
 
@@
 In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as countour integral (\cite{dlmf} \S 9.13(ii))
+They are defined as countour integral \cite[Section 9.13(ii)]{dlmf}
 
@@
 
-which is a generalized hypergeomtric equation (~16.8.5 \cite{dlmf}) with parameters
+which is a generalized hypergeometric equation  \cite[Equation 16.8.5]{dlmf} with parameters
 
@@
 
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \S 4.1 in \cite{koornwinder2015fractional}).
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
 \begin{align*}
@@
 His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
+In the same algebraic setting, Malgrange states the Borel regularity result \cite[Theorem 6]{Malgrange22}
 \item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}

### 2023-10-31 siam/reg-sing-volterra.tex
Start SIAM submission

--- 2023-09-01 reg-sing-volterra.tex
@@
-\documentclass{article}
+\documentclass[review]{siamart220329}
 
@@
 \usepackage{amssymb}
-\usepackage{amsthm}
+%%\usepackage{amsthm}
 \usepackage{graphicx}
-\usepackage[svgnames]{xcolor} % for verifications
+%%\usepackage[svgnames]{xcolor} % for verifications
 \usepackage{environ} % to hide verifications
@@
 
-\theoremstyle{definition}
-\newtheorem{rmk}{Remark}
-\theoremstyle{plain}
-\newtheorem{prop}{Proposition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{thm}{Theorem}
-\newtheorem{cor}{Corollary}
+\newsiamremark{rmk}{Remark}
 
@@
 \ifshowverify
-\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+\newenvironment{verify}{\color{veriforest}}{\color{black}}
 \else
@@
 \definecolor{ietlagoon}{RGB}{0, 216, 180}
+\definecolor{veriforest}{RGB}{0, 80, 40}
 
@@
 It can also reveal hidden structure, especially when the Volterra equation extends to a complex domain.
-
 Our main result is to show that for a certain kind of regular singular Volterra equation on a complex domain, there is always a unique solution of a certain form.
@@
 For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
-\begin{thm}\label{thm:basic_volterra}
+\begin{theorem}\label{thm:basic_volterra}
 Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
@@
 Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
-\end{thm}
+\end{theorem}
 We'll prove this result in Section~\ref{sec:construction}.
@@
 %\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
-\begin{thm}\label{thm:proto-growth}
+\begin{theorem}\label{thm:proto-growth}
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
@@
 Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}. Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ defined in Section~\ref{fn-spaces}.
-\end{thm}
+\end{theorem}
 We'll prove this result in Section~\ref{sec:asymptotics}.
@@
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
-\begin{thm}\label{thm:general_volterra}
+\begin{theorem}\label{thm:general_volterra}
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
@@
 In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
-\end{thm}
+\end{theorem}
 This result will follow from a more general result about inhomogeneous equations.
@@
 That means the inclusion is continuous.
-\begin{prop}\label{exp-complete}
+\begin{proposition}\label{exp-complete}
 The space $\singexp{0}{\Lambda}(\domain)$ is complete.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
-\begin{prop}
+\begin{proposition}
 The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
-\end{prop}
+\end{proposition}
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
-\begin{prop}\label{prop:inclus-ge-exp}
+\begin{proposition}\label{prop:inclus-ge-exp}
 If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
-\begin{prop}\label{prop:inclus-lt-pow-gt-exp}
+\begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
 If $\sigma'>\sigma$ and $\Lambda'<\Lambda$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-\begin{prop}\label{prop:inclus-lt-pow-alg}
+\begin{proposition}\label{prop:inclus-lt-pow-alg}
 When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
-\begin{prop}\label{prop:asymptotic at zero}
+\begin{proposition}\label{prop:asymptotic at zero}
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
-\end{prop}
+\end{proposition}
 
@@
 \end{proof}
-\begin{prop}\label{prop:asymptotic at infinity}
+\begin{proposition}\label{prop:asymptotic at infinity}
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}. Then $\solproto$ belongs to the space $\singexpalg{\tau-1}(\domain)$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-\begin{prop}\label{prop:better-proto-estimate}
+\begin{proposition}\label{prop:better-proto-estimate}
 Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
@@
 at $\zeta = 0$, where $\epsilon'=\min\{\epsilon, 1\}$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 
-\begin{prop}\label{prop:smoothing}
+\begin{proposition}\label{prop:smoothing}
 Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
@@
 continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
-\end{prop}
+\end{proposition}
 \begin{rmk}
@@
 \end{proof}
-\begin{cor}\label{cor:pertub_f0}
+\begin{corollary}\label{cor:pertub_f0}
 Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}.
 If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 
-\begin{prop}\label{prop:get-contraction}
+\begin{proposition}\label{prop:get-contraction}
 Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
 Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\domain)$ by making $\Lambda$ big enough.
-\end{prop}
+\end{proposition}
 \begin{rmk}
@@
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-\begin{prop}\label{prop:whole-ker-near-bound}
+\begin{proposition}\label{prop:whole-ker-near-bound}
 Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
@@
 by keeping $a$ and $a'$ close enough to $\zeta = 0$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 Another bound, which works when the first argument of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
-\begin{prop}\label{prop:whole-ker-far-bound}
+\begin{proposition}\label{prop:whole-ker-far-bound}
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
@@
 over all $a \in \far$ and $a' \in \domain$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 over all $a \in \far$ and $a' \in \domain$. This simplifies to the desired result.
-\end{proof}.
+\end{proof}
 \subsubsection{First steps toward showing that $\volterra$ is a contraction}\label{first-steps}
@@
 \end{proof}
-\begin{prop}\label{prop:alt-general_volterra}
+\begin{proposition}\label{prop:alt-general_volterra}
 Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other conditions we assume in {\em Theorem~\ref{thm:general_volterra}}.
@@
 \[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
-\end{prop}
+\end{proposition}
 
@@
 Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
-\begin{prop}\label{prop:frac-int-smoothing}
+\begin{proposition}\label{prop:frac-int-smoothing}
 For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
@@
 continuously for all $\sigma > -1$ and $\Lambda \ge 0$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
-\begin{thm}\label{thm:example}
+\begin{theorem}\label{thm:example}
 Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
@@
 of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
-\end{thm}
+\end{theorem}
 \begin{proof}[Proof of Theorem~\ref{thm:example}]
@@
 \bibliographystyle{utphys}
-\bibliography{reg-sing-volterra}
+\bibliography{airy-resurgence}
 \end{document}

### 2023-11-01 exp-resurgence.tex
Updates from Overleaf

@@
 
+% colors
+\definecolor{ietocean}{RGB}{0, 30, 140}
+\definecolor{ietcoast}{RGB}{0, 150, 173}
+\definecolor{ietlagoon}{RGB}{0, 216, 180}
+
+% pretty prince hyperref must always be the last thing in the preamble, always
+\usepackage{hyperref}
+\hypersetup{
+  colorlinks,
+  linkcolor={ietcoast},
+  citecolor={ietcoast},
+  urlcolor={ietcoast}
+}
+
+\setcounter{tocdepth}{2}
+
 \title{Borel regularity for ODEs and Thimble Integrals}
@@
 \maketitle
+
+\begin{abstract}
+    ...
+\end{abstract}
+\tableofcontents
 
@@
 
-\subsection{Higher Airy}
-
-\textcolor{magenta}{[The higher Airy example is not completed and there are still some difficulties in the computations, even for simple examples. Should we remove it?]}
-
-The higher Airy equation is
-\begin{equation}\label{eqn:higher-airy}
-\left[\big({-}\tfrac{\partial}{\partial y}\big)^{n-1} - y\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\cite[Equation~3.8]{charbonnier22},
-
-\color{Peru}
-With
-\begin{align*}
-z & = (-1)^{n-1} \tfrac{n-1}{n} y^{n/(n-1)} & w & = (-1)^n (n-1) y^{1/(n-1)} u,
-\end{align*}
-we have
-\begin{align*}
-\widetilde{\Ai}^{(k)}_n(y) & = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w^n - yw\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \left(w^{n-1} - ny\right)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}w \big((n-1)^{n-1} yu^{n-1} - ny\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[\tfrac{1}{n}yw \big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[(-1)^n \tfrac{n-1}{n} y^{n/(n-1)} u\big((n-1)^{n-1} u^{n-1} - n\big)\right]\,dw \\
-& = \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} \int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,dw \\
-& = (-1)^n (n-1) \frac{\exp\big(\pi ik \tfrac{n-2}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^n (n-1) \frac{\exp\left(\pi ik \big(1 - \tfrac{1}{n-1}\big)\right)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-& = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\
-\end{align*}
-\color{black}
-\[ \widetilde{\Ai}^{(k)}_n(y) = (-1)^{n+k} (n-1) \frac{\exp\big({-}\pi i \tfrac{k}{n-1}\big)}{2\pi i} y^{1/(n-1)}\int_{\Lambda^{(j)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du \\, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-\subsubsection{Rewriting as a \textcolor{magenta}{(???)} equation}
-We can distill the most interesting parts of the hyper-Airy function by writing
-\[ \widetilde{\Ai}^{(k)}_n(y) = \textcolor{magenta}{\text{const.}}\,y^{1/(n-1)}\,K^{(k)}\left((-1)^n\,\tfrac{n-1}{n}\,y^{n/(n-1)}\right), \]
-where
-\begin{equation}\label{int_higher-Ariy}
-K^{(k)}(z) = \textcolor{magenta}{\text{const.}} \int_{\textcolor{magenta}{\text{const.}(n)} z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[-z\big((n-1)^{n-1} u^n - nu\big)\right]\,du.
-\end{equation}
-Saying that $\widetilde{\Ai}^{(k)}_n$ satisfies the higher Airy equation is equivalent to saying that $K$ satisfies an equation of the form
-\begin{equation}\label{eqn:higher-Airy}
-\left[ \big[ \big({-}\tfrac{\partial}{\partial z}\big)^{n-1} - 1 \big] - c_n^{(1)} z^{-1} \big({-}\tfrac{\partial}{\partial z}\big)^{n-2} - c_n^{(2)} z^{-2} \big({-}\tfrac{\partial}{\partial z}\big)^{n-3} - \ldots - c_n^{(n-1)} z^{-(n-1)} \right] K^{(k)} = 0.
-\end{equation}
-The sub-leading coefficients are 
-\[ c_n^{(1)} = \frac{n-1}{2}. \]
-
-The later coefficients can be written as\footnote{Many thanks to Peter Taylor for noticing this [\url{https://mathoverflow.net/q/422337/1096}].}
-\[ c_n^{(k)} = \frac{b_n^{(k)}}{n^k}\,\frac{\Gamma(n+2)}{\Gamma(n-k)} \]
-in terms of the polynomials
-
-\begin{tabular}{llllllllllll}
-$b_n^{(2)}$ & = & $\frac{1}{24}$ \\
-$b_n^{(3)}$ & = & $\frac{1}{48} n$ \\
-$b_n^{(4)}$ & = & $\frac{73}{5760} n^2$ & + & $\frac{1}{1152} n$ & - & $\frac{1}{2880}$ \\
-$b_n^{(5)}$ & = & $\frac{11}{1280} n^{3}$ & + & $\frac{1}{768} n^{2}$ & - & $\frac{1}{1920} n$ \\
-$b_n^{(6)}$ & = & $\frac{3625}{580608} n^{4}$ & + & $\frac{61}{41472} n^{3}$ & - & $\frac{181}{322560} n^{2}$ & - & $\frac{1}{41472} n$ & + & $\frac{1}{181440}$. 
-\end{tabular}
-
-\vspace{5mm}
-
-Searching for 580608 in the OEIS turns up the leading coefficients $\beta^{(k)}$ of these polynomials, which are listed as {\tt A249276} and {\tt A249277}.
-They're defined by the identity [Yang, ``Approximations for Constant $e$ and Their Applications'']
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{\beta^{(2)}}{n^2} - \frac{\beta^{(3)}}{n^3} - \frac{\beta^{(4)}}{n^4} - \frac{\beta^{(5)}}{n^5} - \ldots, \]
-which tells us that
-\[ \frac{1}{e} \left(\frac{n}{n-1}\right)^{n-1} = 1 - \frac{1/2}{n} - \frac{b_n^{(2)}}{n^2} - \frac{b_n^{(3)}}{n^4} - \left[\frac{b_n^{(4)}}{n^6} + o\left(\frac{1}{n^5}\right)\right] - \left[\frac{b_n^{(5)}}{n^8} + o\left(\frac{1}{n^6}\right)\right] - \ldots.
-\]
-The last coefficient can be written as
-\[ c_n^{(n-1)} =\left(\frac{n-1}{n}\right)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}}, 
-\]
-giving
-\[ b_n^{(n-1)} = (n-1)^{n-1} \left(\frac{1}{n-1}\right)^{\underline{n-1}} \Big/ \Gamma(n+2). \]
-
-\subsubsection{Building a frame of analytic solutions}
-
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:higher-Airy}.
-We'll succeed when $\alpha^{n-1} - 1 = 0$, and we'll see that $K^{(k)}$ is a scalar multiple of $\laplace_{\zeta, \alpha_k} v_k$ with $\alpha_k=e^{2\pi i \tfrac{k}{n-1}}$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha_k} v$ satisfies the differential equation~\eqref{eqn:higher-Airy} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-higher-Airy}
-\left[ \big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \partial_{\zeta,\alpha_k}^{-1}\circ \zeta^{n-2} - c_n^{(2)} \partial_{\zeta,\alpha_k}^{-2} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \partial_{\zeta,\alpha_k}^{-(n-1)} \right] v = 0.
-\end{equation}
-
-Since equation \eqref{eqn:higher-Airy} is written in form \eqref{eqn:standard ODE} and the coefficient $c_n^{(1)}$ is explicitly known, we deduce that equation \eqref{int-eq:spatial-higher-Airy} admits a slight solution at $\zeta={\alpha_k} $ of order $\tau_{\alpha_k}=\frac{1}{2}$.
-In particular, $v$ is a solution of \eqref{int-eq:spatial-higher-Airy} if and only if it solves the following differential equation
-
-\begin{equation}\label{diff-eq:spatial-higher-Airy}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big] - c_n^{(1)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-2}\circ \zeta^{n-2} - c_n^{(2)} \big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3} - \ldots - c_n^{(n-1)} \right] v = 0.
-\end{equation}
-
-Using the Liebniz rule for the differential, we get
-
-\color{Peru}
-
-\begin{align*}
-\big(\tfrac{\partial}{\partial \zeta}\big)^{n-1} \circ\big[ \zeta^{n-1} - 1 \big]v&=\sum_{j=0}^{n-1} \binom{n-1}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]\\
-&=(\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}v+ (n-1)^2\zeta^{n-2} \partial_\zeta^{n-2}v +\\
-&\qquad \sum_{j=2}^{n-1} \binom{n-2}{j} v^{(n-j-1)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-1)! v\\
-\big(\tfrac{\partial}{\partial {\zeta}}\big)^{n-2}\circ \zeta^{n-2}v&=\zeta^{n-2}\partial_\zeta^{n-2}v+\sum_{j=1}^{n-3} \binom{n-2}{j} v^{(n-j-2)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-2)!v \\
-\big(\tfrac{\partial}{\partial \zeta}\big)^{n-3} \circ\zeta^{n-3}v&=\sum_{j=0}^{n-4} \binom{n-3}{j} v^{(n-j-3)}\big(\tfrac{\partial}{\partial \zeta}\big)^{j} \big[ \zeta^{n-1} - 1 \big]+(n-3)!v\\
-\tfrac{\partial}{\partial \zeta} \circ\zeta v&=\zeta \partial_\zeta v+v
-\end{align*}
-
-\color{black}
-\begin{equation}\label{diff-eq:spatial-mod-higher-Airy}
-\left[ (\zeta^{n-1} - 1)\partial_{\zeta}^{n-1}+ \big[(n-1)^2-c_n^{(1)}\big]\zeta^{n-2} \partial_\zeta^{n-2}+...+\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big] \right] v = 0.
-\end{equation}
-
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-higher-Airy} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-higher-Airy} looks like
-\begin{multline}\label{diff-eq:spatial-mod-higher-Airy-1}
-\left[\zeta_1(n-1+...+(n-1)\zeta_1^{n-3} + \zeta_1^{n-2}) \big(\tfrac{\partial}{\partial \zeta_1}\big)^{n-1} + \big[(n-1)^2-c_n^{(1)}\big](1+\zeta_1)^{n-2} \tfrac{\partial}{\partial \zeta_1}^{n-2} + ...
-\right.\\
- \left. +\big[(n-1)!-c_n^{(1)}(n-2)!-...-c_n^{(n-1)}\big]\right] v = 0.
-\end{multline}
-
-\subsubsection{Higher Airy of degree $3$}
-Setting $n=4$, equation \eqref{eqn:higher-Airy} turns into
-
-\begin{equation}\label{eqn:reg-higher3}
-\left[\frac{\partial^3}{\partial z^3}+1+\frac{3}{2z}\frac{\partial^2}{\partial z^2}-\frac{5}{16}\frac{1}{z^2}\frac{\partial}{\partial z}+\frac{5}{32}\frac{1}{z^3}\right]\varphi=0
-\end{equation}
-
-and going to the spatial domain, $\laplace_{\zeta,\alpha_k}$ satisfies equation~\eqref{eqn:reg-higher3} if and only if $v$ satisfies
-
-\begin{equation}\label{diff-eq:spatial-higher3}
-\left[(\zeta^3-1)\partial_\zeta^3-\frac{15}{2}\zeta^2\partial_\zeta^2-\frac{187}{16}\zeta\partial_\zeta+\frac{81}{32}\right]\varphi=0
-\end{equation}
-
-Let's find a solution of equation~\eqref{diff-eq:spatial-higher3} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-higher3} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(3 + 3\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^3 - \frac{15}{2}(1 + 2\zeta_1 + \zeta_1^2) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 -\frac{187}{16}(1+\zeta_1)\tfrac{\partial}{\partial \zeta_1} + \frac{81}{32}\right] v = 0.
-\end{equation}
-
-\textcolor{DarkBlue}{[Find solutions using hypergeometric functions]}
-
-\subsubsection{thimble projection reasoning for higher Airy of degree $3$}
-
-We can recast integral \eqref{int_higher-Ariy} into the $\zeta$-plane by setting $\zeta=27 u^4-4 u$, which implies that $d\zeta=4 (27 u^3-1) du$.
-Projecting $z^{-1/4}\Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing a branch of that lifts $\gamma_z$ back to $z^{-1/4}\Lambda^{(k)}$, we get
-
-\begin{align*}
-K^{(k)}(z)&=\textcolor{magenta}{const.} \int_{\textcolor{magenta}{const.}z^{-1/4}\Lambda^{(k)}}\exp\big[- z \big(27 u^4-4 u\big)\big] du\\
-&=\textcolor{magenta}{const.} \int_{\gamma_z}e^{-z\zeta} \frac{d\zeta}{4(27u^3-1)}\\
-&=\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta}\frac{1}{3}\left[\frac{1}{3u-1}+\frac{1}{3e^{\frac{2\pi i}{3}} u -1}+\frac{1}{3e^{\frac{4\pi i}{3}} u-1}\right] d\zeta\\
-&=-\textcolor{magenta}{const.} \frac{1}{4}\int_{\gamma_z}e^{-z\zeta} {}_3F_2\left(\frac{1}{3},\frac{2}{3},1;\frac{1}{3},\frac{2}{3};27 u^3\right) d\zeta
-\end{align*}
-\[
-\frac{1}{4}\frac{1}{27u^3-1}=\frac{1}{4}(\frac{A}{3u-1}+\frac{B}{3u-\omega}+\frac{C}{3u-\omega^2})
-\]
-
 \subsection{Generalized Airy}

### 2023-11-01 Higher_Airy.tex

--- 2023-05-09 exp-resurgence.tex
@@
 \usepackage{amssymb}
-\usepackage{amsthm}
-%\usepackage{eqnarray}
-\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
-\usepackage{bm} %% for putting series names in bold
-%%\usepackage{amsthm}
 \usepackage{graphicx}
-\usepackage{fancyhdr}
-\usepackage{xparse}
-\usepackage{enumitem}
-%\usepackage{eqnarray}
-%% colors
 \usepackage[svgnames]{xcolor}
-\let\Re\relax
-\DeclareMathOperator{\Re}{Re}
-
-%% editing
-\newcommand{\done}[1]{\textcolor{gray}{#1}}
-
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}
-%%\theoremstyle{plain}
-%%\newtheorem{prop}{Proposition}
-
+\usepackage{tikz-cd}
 % convenience aliases
 \newcommand{\maps}{\colon}
-\newcommand{\acts}{\mathbin{\raisebox{\depth}{\rotatebox{-90}{$\circlearrowright$}}}}
 
@@
 \newcommand{\C}{\mathbb{C}}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usepackage{rotating}
-\newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
-]}
 
@@
 %\newtheorem{exercise}[definition]{Exercise}
-\newtheorem*{notation*}{Notation}
+%\newtheorem*{notation*}{Notation}
 
-\title{Borel regularity for ODEs and thimble integrals}
-\author{Veronica Fantini and Aaron Fenyes}
+% drafting environments
+\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+
+% colors
+\definecolor{ietocean}{RGB}{0, 30, 140}
+\definecolor{ietcoast}{RGB}{0, 150, 173}
+\definecolor{ietlagoon}{RGB}{0, 216, 180}
+
+% pretty prince hyperref must always be the last thing in the preamble, always
+\usepackage{hyperref}
+\hypersetup{
+  colorlinks,
+  linkcolor={ietcoast},
+  citecolor={ietcoast},
+  urlcolor={ietcoast}
+}
+
+\title{Higher Airy}
+\author{Veronica Fantini}
 
@@
 
-\section{Introduction}
-\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
-%%\subsection{A familiar process: Borel summation}\label{intro:summation}
-You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
-\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
-with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
-\begin{equation}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
-\end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -\tfrac{1}{12}$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution \textcolor{magenta}{[check]}
-\begin{equation}
-e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
-\end{equation}
-and its constant multiples. As another example, you might rewrite the integral
-\color{DodgerBlue}
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-\tfrac{1}{12} z \left(4u^3 - 3u\right)\right]\,du \]
-\color{black}
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(\tfrac{1}{3} u^3 - \tfrac{1}{4} u\right)\right]\,du \]
-as
-% see expansion.sage
-\[ e^{z/12} \int_{-\infty}^\infty e^{-z\tau^2/2} \left[ 1 - \frac{2}{3} \tau + \frac{5}{6} \tau^2 - \frac{32}{27} \tau^3 + \frac{385}{216} \tau^4 - \frac{224}{81} \tau^5 + \frac{17017}{3888} \tau^6 - \ldots \right] d\tau \]
-using the substitution $\tfrac{1}{2} \tau^2 = \tfrac{1}{3} u^3 - \tfrac{1}{4} u + \tfrac{1}{12}$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{DodgerBlue}
-\begin{align*}
-& e^{z/12} z^{-1/2} \left[ (-1)!! + \frac{5}{6}\,1!!\,z^{-1} + \frac{385}{216}\,3!!\,z^{-2} + \ldots \right] \\
-& = e^{z/12} z^{1/2} \left[ \frac{(-1)!!}{z} + \frac{5}{6} \cdot \frac{1!!}{z^2} + \frac{385}{216} \cdot \frac{3!!}{z^3} + \frac{17017}{3888} \cdot \frac{5!!}{z^4} + \ldots \right] \\
-& = e^{z/12} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{6} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{216} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{3888} \cdot \frac{5!!}{z^{7/2}} + \ldots \right]
-\end{align*}
-\color{black}
-
-Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-Borel summation works in three steps.
-\begin{enumerate}
-\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}.
-We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
-Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ \textcolor{magenta}{[link to definition]} turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-\end{enumerate}
-The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
-Hopefully it wouldn't be too hard, but it would be a pain.]}
-\begin{defn}
-On an open sector $\Omega$ around $\infty$, a power series
-\begin{equation}\label{series:asymp-defn}
-\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
-\end{equation}
-is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$.
-
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ \textcolor{orange}{[Theorem~C.11, Nikolaev, ``Existence and uniqueness\ldots'']}.
-\end{defn}
-\begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
-over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
-\end{defn}
-To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
-
-\begin{enumerate}[start=4]
-\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
-It turns out that $\series{\Phi}$ is not only asymptotic to $\hat{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
-\end{enumerate}
-
-The Borel summation process is summarized in the following diagram:
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-
-You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
-After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
-In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
-The question of how that happens is the starting point for this paper.
-
-%\color{gray}
-%\begin{itemize}
-%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example\ldots}
-%\begin{itemize}
-%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
-%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
-%\item Feynman diagram series?
-%\end{itemize}
-%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-%\begin{itemize}
-%\item \done{Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
-%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
-%\item {[Draw the square!]}
-%\end{itemize}
-%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-%\item In many cases, it picks correctly, producing an actual solution to your problem.
-%\begin{itemize}
-%\item The question of how that happens is the starting point for this paper.
-%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-\subsection{A new perspective: Borel regularity}
-\subsubsection{Introducing Borel regularity}
-\begin{itemize}
-\item Start instead with a holomorphic solution $\Phi$.
-\item Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
-\end{itemize}
-\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
-
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
-Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
-We'll therefore call this process {\em Borel regularization}.
-Explicitly, Borel regularization works in four steps.
-\begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
-\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
-This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.
-\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.
-\textbf{[Should we be allowed to take the Laplace transform at another points $b \in B$ instead?]}
-\end{enumerate}
-We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
-
-Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
-We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
-\subsubsection{Borel regularity as a good approximation condition}
-Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \textcolor{orange}{[Watson]} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
-
-Watson's theorem was soon improved by Nevanlinna (see a modern proof in Nikolaev, ``Exact Solutions for the Singularly Perturbed Riccati Equation and Exact WKB Analysis'' Theorem~B.15), and improved again later by Sokal (Sokal, ``An improvement of Watson's theorem on Borel summability'').
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
-\begin{center}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\dis}{1.2}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
-  \begin{scope}[violet]
-    \draw (0, 0) -- (-\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
-\end{tikzpicture}
-\end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
-
-%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
-Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
-Hence $\Phi$ is Borel-regularizable.
-In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$.
-In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
-The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
-Roughly speaking, Borel summation works well for problems with Borel regular solutions that stand out asymptotically \textcolor{magenta}{[this may need refining]}.
-
-The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
-\begin{enumerate}
-\item Solving a linear ODE of level~$1$ \cite[\S 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Definition~5.5]{diverg-resurg-iii}}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type.
-
-We'll restrict our attention to the case where the roots of $P$ are distinct.
-
-The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
-Borel summation still works well for the nonlinear ones, raising the question of whether our analysis generalizes.
-
-\item the second problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}
-
-\begin{equation}
-I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
-\end{equation}
-where $f\colon X\to \mathbb{C}$ is a Morse function, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
-\end{enumerate}
-
-These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-
-%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
-Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We will give precise statements in the following section.
-
-%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We'll call it {\em Borel regularization}.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We'll call this process {\em Borel regularization}.
-%\begin{itemize}
-%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-%\item We have the following vector space inclusions:
-%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
-%
-%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-%\begin{itemize}
-%\item $\Phi$ is Borel regular.
-%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-%\item $\phi$ grows at most exponentially along the Laplace transform ray.
-%\end{itemize}
-%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
-\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
-it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
-%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-%\item \ldots
-%\end{itemize}
-
-\subsection{Goals and Results}
-
-First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 4 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-
-\subsubsection{Why does Borel summation work for solutions of certain level-$1$ ODEs?}
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
-\begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_d$ are entire functions of exponential type\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]}.
-Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ \textcolor{magenta}{[Verify this more carefully!
-It seems like there should be $2(d-1)$ Stokes sectors, as described below]}.
-
-\color{DarkTurquoise}
-In \cite[Proposition~2.2.7]{EcalleIII}, where
-\begin{align*}
-P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
-Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
-\end{align*}
-(with the coefficients renamed to avoid a conflict with the zeros $\alpha_j$), the recurrence that gives the solution simplifies
-\begin{align*} b_q & = P_q + Q_q z^{-1} - \frac{\partial}{\partial x^{(q)}} b(z, x, x^{(1)}, \ldots x^{(d)}) \\
-& = P_q + Q_q z^{-1} - R_q(z^{-1}).
-\end{align*}
-
-Following the argument of Delabaere Lemma~6.2, we can prove that $\series{F}_j(z)$ is $1$-Gevrey by taking the formal Borel transform of the ODE it satisfies and showing it is regular singular at $\zeta=0$.
-
-Roughly speaking, factoring out $e^{-\alpha_j z}$ removes the constant term of $P$, and factoring out $z^{-\tau_j}$ changes $Q$ to give factorial growth instead of gamma function growth (?).
-
-\begin{align*}
-\mathcal{P} & = \sum_j^d f_j \frac{\partial}{\partial z}^j \\
-& = \sum_j^d f_j \left(-\frac{1}{w^2} \frac{\partial}{\partial w}\right)^j\\
-&=  \sum_j^d \tilde{f}_j \frac{\partial}{\partial w}^j
-\end{align*}
-where $w=1/z$.  if $\tilde{f}_j $ has a pole of order at most $d-j$ at 0 then it's regular singular, otherwise it's irregular. The relevant term should be
-\[ \left(\frac{P_d}{w^{2d}} + \frac{R_d(w)}{w^{2d-2}}\right) \left(\frac{\partial}{\partial w}\right)^d , \]
-corresponding to the quadratic differential $dw^2/w^{2d}$, whose trajectories form $2(d-1)$ half-planes around $\infty$ (see Bridgeland \& Smith's ``Quadratic differential as stability conditions,'' Figure~10).
-
-From the Bessel equation, for example, we get
-\begin{align*}
-(-w^{-2}\partial_w)^2&=-w^{-2}\partial_w(-w^{-2}\partial_w)\\
-&=-w^{-2}(2w^{-3}\partial_w-w^{-2}\partial_w^2)\\
-&=-2w^{-5}\partial_w+w^{-4}\partial_w^2,
-\end{align*}
-giving two half-planes around $\infty$, as expected.
-\color{black}
-
-Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
-\end{equation}
-where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $\alpha_1, \ldots, \alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-
-Classically it has been proved that the formal solutions $\series{\Psi}_j$ \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums $\hat{\Psi}_j$ satisfy the original equation $\mathcal{P}\hat{\Psi}_j=0$ \cite{Ramis?}\textcolor{magenta}{[Check references]}.
-Therefore, the distinguished frame of formal solutions becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame \textcolor{magenta}{[reference-see Sauzin-Mitchi or Delabere book]}, but it is not a constructive method (see Balser chap.
-14).
-Conversely, we can explicitly build a distinguished basis of analytic solutions:
-
-\begin{theorem}[see Theorem \ref{thm1-dim}]\label{thm1}
-In the previous set-up, for every $\alpha_j$ we set $\zeta_j=\zeta-\alpha_j$. Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with
-
-\begin{equation}
-\hat{P}_j:=P(\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
-\end{theorem}
-
-At this point, we may ask what is the relationship between the two frame of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually the same, hence proving Borel summation works.
-
-\begin{theorem}\label{thm2}
-For every $j=1,...,d$ the solution $\psi_j(\zeta_j)$ of Theorem \ref{thm1} admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
-\end{theorem}
-
-In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
-
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2}: on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-Then, the theory of multi-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem~\ref{thm1} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE).
-
-The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE), hence its sum $\hat{\psi}_j$ must be a solution too.
-In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result~\ref{thm1}, we conclude that $\psi_j$ and $\hat{\psi}_j$ must coincide up to scaling by a constant.
-
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$.
-
-\begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]}.
-It can indeed be seen as a consequence of ``resurgence'' of the ODE.
-Our results show how to build a frame of solutions, analytically in the Borel plane.
-Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
-\end{remark}
-
-\begin{remark}
-Although, in our proof, we use multi-summability to ensure that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE, the approach of Borel regularity is different as it is based on the analytic solution in the frequency domain ($z$-plane).
-\textcolor{magenta}{[Is it possible to prove Borel regularity without proving Borel summability?
-For instance, can we argue that $\psi_j$ being the unique solution of (IE) with a certain behavior is enough to say that it is the sum of $\series{\psi}_j$?
-Check carefully the argument of multi-summability]}
-\end{remark}
-
-\color{gray}
-\begin{itemize}
-\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-\end{itemize}
-\begin{itemize}
-\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-
-\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-\begin{center}
-\begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
-\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-\item  
-there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-\end{itemize}
-
-\color{DarkBlue}
-
-\subsubsection{Why does Borel resummation work for thimbles integrals?}
-
-\begin{itemize}
-\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-\begin{itemize}
-\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-\end{itemize} 
-\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
-His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result Theorem 6 \cite{Malgrange22}
-\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
-\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-\begin{equation}
-I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-\end{equation}
-
-then the following diagram is commutative
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-\end{tikzcd}
-\end{equation}
-\begin{itemize}
-\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the fractional derivative formula.
-\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
-\begin{equation}
-mmm
-\end{equation} 
-\end{itemize}
-\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-\begin{itemize}
-\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
-\end{itemize}
-\end{itemize}
-
-\color{DarkGreen}
-We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-Let $X$ be a translation surface---a Riemann surface carrying a holomorphic 1-form $\nu$.
-Suppose $X$ is of {\em meromorphic type}, meaning that we got it by puncturing a compact Riemann surface $\overline{X}$ at finitely many points, and $\nu$ has a pole at each puncture.
-A {\em translation coordinate} on $X$ is a local coordinate whose derivative is $\nu$.
-
-Take another meromorphic-type translation surface $B$ and a holomorphic Morse\footnote{This condition means that the critical points of $f$ are isolated (the compactness of $\overline{X}$ guarantees this) and the 2-jet of $f$ is non-zero at every critical point.} map $f \maps \overline{X} \to \overline{B}$ \textcolor{magenta}{that sends punctures to punctures [actually, don't require this; the Orr--Sommerfeld integrals, for example, don't satisfy it]}.
-Suppose every singularity of $B$ is a critical value of $f$.
-\textbf{[Typical usage of ``Borel plane'' seems ambiguous, so maybe we can use ``Borel plane'' for $B$ and ``Borel cover'' for the Riemann surface of the Borel-transformed series.
-How to handle the Orr–Sommerfeld functions (DLMF~\S 9.13)?
-We know $f = 4u^3 - 3u$ is the pullback of a translation coordinate, but we also need a puncture at $f(0)$\ldots]} For each critical point $p$, let $\Gamma_p$ be the ray going rightward from $f(p)$, and let $\zeta_p$ be the translation coordinate around $\Gamma_p$ which vanishes at $f(p)$.
-These are well-defined as long as $\Gamma_p$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_p)$ is a bunch of disjoint curves, as long as $\Gamma_p$ misses the other critical values of $f$.
-The \textcolor{red}{\em Lefschetz thimble} $\Lambda_p$ is the component of $f^{-1}(\Gamma_p)$ that goes through $p$, oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_p$.
-\textcolor{red}{Can we say that in $1$-dimension there the two definitions of thimble integrals are actually the same?} The {\em thimble integral}
-\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
-
-\textbf{[Talk about exponential integrals and their decomposition into thimble integrals.]}
-
-In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
-This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \textbf{[Costin \& Kruskal, ``On optimal truncation...''],[Delabere \& Howls, Howls, Dingle]}.
-
-\color{DarkTurquoise}
-Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
-Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
-This data defines the {\em exponential integral}
-\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-a holomorphic function on the right half-plane parametrized by $z$.
-It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
-\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
-
-\color{black}
-
-\subsubsection{Other results}
-
-As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see Theorem~\ref{thm1}).
-
-Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-\textcolor{magenta}{[where do we do that?]} \textcolor{orange}{Explain why this new perspective is useful}
-
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals (the Airy--Lucas functions, modified Bessel function, Airy function, the anharmonic oscillator...).
-Then, on the one hand we explicitly solves the integral equation associated to the ODE, building a frame of analytic solutions as Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{contour argument} shows how to rewrite explicitly thimble integrals as a Laplace transform.
-Borel regularity will be evident from the explicit computations.
-Some examples have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with (Marino, Sauzin, Takei).
-The anharmonic oscillator was also discussed by (Bender--Wu, Schiappa).
-Other example haven't been discussed much, as for Airy--Lucas functions.
-
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum, \cite{EcalleIII}).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum, KS paper analytic WCS), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-
-%\color{gray}
-%\begin{itemize}
-%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-%\begin{itemize}
-%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-%\item The second problem is solving a certain kind of ODE.
-%\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-%\end{itemize}
-%
-%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-%\begin{itemize}
-%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-%\end{itemize}
-%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-%\begin{itemize}
-%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-%\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-%\end{itemize}
-%\end{itemize}
-%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
-%\begin{itemize}
-%\item Integral equations are more regular than differential equations.
-%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-%\end{itemize}
-%\item Illustrate with detailed treatments of several examples.
-%\begin{itemize}
-%\item Contour argument (thimble integrals)
-%\item solving integral equation (ODE)
-%\item How thimble integrals and ODE are related in our examples?
-%\end{itemize}
-%\begin{itemize}
-%\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-%\item Others haven't been discussed much.
-%\end{itemize}
-%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-%\begin{itemize}
-%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-%\item computation of Stokes constants via Picard--Lefschetz theory
-%\end{itemize}
-%\end{itemize}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean to be Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item fractional derivative formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
-\end{itemize}
-\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
-
-\color{black}
-%\end{itemize}
-\begin{itemize}
-\item Each resummation method for asymptotic series makes some implicit assumption that allows us to reconstruct a holomorphic function from its asymptotic behavior.
-\item The resummation method works correctly for functions that satisfy that assumption.
-\item For the modified Bessel function $K_{1/3}$, Borel resummation works because the asymptotic series encodes a second-order differential equation.
-\begin{itemize}
-\item Different aspects of this example appear in various places (Mari\~{n}o, Kawai--Takei, Sauzin). We give a detailed, unified treatment.
-\end{itemize}
-\item We can generalize this argument to all $K_\nu$ with $\nu \in \mathbb{Q}$.
-\item We can also generalize to all third-order exponential integrals.
-\begin{itemize}
-\item Most of them are equivalent to the $K_{1/3}$ integral, but there's also an interesting degeneration.
-\end{itemize}
-\end{itemize}
-\color{black}
-\subsection{Fractional derivative formula}
-\begin{itemize}
-\item Theorem~\ref{thm:three-halves} says that for a certain class of exponential integrals
-\[ I(z) = \int_\Gamma e^{-zf}\;\nu, \]
-the inverse Laplace \textbf{[better to say Borel?]} transform is the $\tfrac{3}{2}$ derivative of $d\zeta/df$, where $f^* d\zeta = \nu$ \textbf{[check]}.
-\item the asymptotic expansion of $I(z)$ is a resurgent function.
-\item Is it always a \emph{simple} resurgent function?
-\begin{itemize}
-\item \textbf{Maxim belies it is in general, and indeed in our examples, we get simple resurgent functions. But how to prove it in general?}
-\end{itemize} 
-\end{itemize}
-\subsection{Stokes phenomenon}
-\begin{itemize}
-\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-\item The jump comes from the branch cut difference identity for hypergeometric functions.
-\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-\end{itemize}
-\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
-\subsection{The geometry of the Laplace transform}
-
-Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
-In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
-Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
-\subsubsection{Translation surfaces, briefly}
-
-A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\textbf{[Zorich, ``Flat Surfaces''?]}.
-A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
-The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' \textbf{(figure)} at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' \textbf{(figure)} at each puncture where $\lambda$ has order $n-1 < -1$~\textbf{[Gupta, ``Meromorphic quadratic differentials with half-plane structures,'' \S 2.5] (or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
-\subsubsection{Direction}\label{transl:dir}
-The translation structure gives $B$ a notion of direction as well as distance.
-Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
-At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
-To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
-In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
-
-Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
-This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
-Of course, there are $n$ different choices for $\omega_b$.
-\subsubsection{Frequency}\label{transl-freq}
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
-At an ordinary point, we can define $z$ simply as the map
-\begin{align*}
-z \maps T^*B_b & \to \C \\
-\lambda\big|_b & \mapsto 1.
-\end{align*}
-To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
-Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
-Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
-When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
-In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
-We define $z$ as the isomorphism
-\begin{align*}
-z \maps \van_b^n / \van_b^{n+1} & \to \C \\
-\zeta_b + \van^{n+1} & \mapsto 1.
-\end{align*}
-
-When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
-\begin{align*}
-w_b \maps T^*B_b & \to \C \\
-\omega_b + \van^2 & \mapsto 1
-\end{align*}
-that makes the diagram
-\begin{center}
-\begin{tikzcd}
-T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
-T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
-\end{tikzcd}
-\end{center}
-commute.
-\subsubsection{Boundary}
-\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}
-
-\subsubsection{The Laplace transform over an ordinary point}%%\label{laplace:ordinary}
-Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
-\begin{equation}\label{laplace:int}
-\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function defined in Section~\ref{transl:freq} and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-
-To make sense of this formula, we ask for the following conditions.
-\begin{itemize}
-\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
-\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
-\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-\begin{itemize}
-\item With respect to the flat metric, $f$ grows subexponentially along $\Gamma_b^\theta$~\textbf{[define]}, and is locally integrable throughout.
-\item The value of $z$ is in the half-plane $H_{-\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
-\end{itemize}
-\end{itemize}
-\subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
-The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
-This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
-The half-plane $z \in H_{-\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
-We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-\subsection{The geometry of the Borel transform}
-\begin{itemize}
-  \item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  \item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  \begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-  \item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-\end{itemize}
-\subsection{The Laplace transform: analytic version}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-%Let $\zeta$ be the standard coordinate on $\C$, and let $z \maps T^*\C \to \C$ be the fiberwise-linear map $d\zeta \mapsto 1$ (see ``The Geometry of the Laplace Transform'' in {\tt draft2}).
-The Laplace transform in $\zeta$ turns a function $\varphi$ on $\C$ into a function $\laplace_\zeta \varphi$ on $T^*\C$, defined on the cotangent space of $\zeta = \alpha$ by the integral
-%\[ \laplace_\zeta \varphi \big|_{\zeta = \alpha} = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta, \]
-where $\Gamma_{\zeta, \alpha}$ is the rightward ray starting at $\zeta = \alpha$ (compare {\tt draft2}).
-\textcolor{magenta}{We'll use the shorthand $\laplace_{\zeta, \alpha} f := \laplace_\zeta f \big|_{\zeta = \alpha}$ throughout this document [but maybe we should get rid of it].}
-
-Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions which are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*\C$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[\S 5.6]{diverg-resurg-i}.
-
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}$ control the asymptotics of $\laplace_{\zeta, \alpha} f$ at the infinite end of $\Gamma_{z, 0}$.
-Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use Equation 1.5 of {\em Borel-Laplace Transform and Asymptotic Theory} \textcolor{magenta}{(Sternin \& Shatalov)}.} that
-\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\tau > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\tau) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \tau}}\right). \]
-Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
-\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-\subsubsection{Action on integral operators}\label{L-int-op}
-When $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm} 
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-You can also use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-for all $\lambda \in (0, \infty)$.
-\subsubsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $\C$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    \label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-\subsubsection{Rescaling of translation structure}
-Let's rescale the translation structure of $\C$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*\C \to \C$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $\C$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them, because they both turn complex-valued functions on $\C$ into holomorphic functions on $T^*\C$.
-\subsection{The geometry of the Borel transform}
-
-The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-More precisely, $\borel_\zeta$ is a $\C$-linear map
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-\end{align*}
-where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
-In general, by linearity,
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-\end{align*}
-
-It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
-\begin{align*}
-    \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
-    &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-    &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
-\end{align*}
-where in the second step we formally interchange the integral and the sum.
-
-\subsubsection{Action on transseries}
-
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$:
-
-\[T_{\alpha,\varphi}:=\sum_{n=0}^{\infty} e^{\alpha_n z} \varphi_n(z) \]
-
-The main feature of $T_{\alpha,\varphi}$ is that its asymptotics as $\text{ Re } e^{i\theta}z \to +\infty$ is $\varphi_0$.
-In fact, they play a crucial role in the theory of ODEs with irregular singularities.
-
-It is natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries.
-Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-
-We extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-
-Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, then from identity \eqref{change-chart}
-
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha,0}\varphi\right]
-  \end{align*}
-We compute the left-hand-side
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi&=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
-  \end{align*}
-  and the right-hand-side
-  \begin{align*}
-      \borel_\zeta\left[e^{-\alpha z
-      }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
-      }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
-      &=\borel_\zeta\left[
-      \sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-      &= \sum_{n=0}^{\infty}a_n \zeta^n
-  \end{align*}
-In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-
-\[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
-
-Then, comparing term by term in powers of $\zeta$ in the second identity we get 
-  \begin{align*}
-      \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})&=\zeta^n\\
-      \sum_{k=0}^n {n\choose k} \alpha^{n-k} \borel_\zeta(e^{-z\alpha} k! z^{-k-1})&=\sum_{k=0}^n {n\choose k} \alpha^{n-k}(\zeta-\alpha)^k
-  \end{align*}
-  and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
-\begin{itemize}
-    \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  \end{itemize}
-
-\subsubsection{Change of translation chart}
-
-Following Section \ref{translation}, we introduce $\borel_{\zeta_\alpha}$
-as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. Explicitly, from identity \eqref{change-chart}
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi
-  \end{align*}
-  now the LHS reads
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\left[e^{z\alpha} \int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_n\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_ne^{-z\alpha}\sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}  z^{-k-1}\right]
-  \end{align*}
-  the RHS is 
-  \begin{align*}
-      \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
-      &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
-      \end{align*}
-     If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
-      \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
-       \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
- Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
- \begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
- Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
-
- \textcolor{magenta}{I think we should add a remark, saying that on $B$ there is no special coordinate, and this reflects on the fact that $\borel$ is defined equivalently for every choice of coordinates.}
-
-\subsection{The Borel transform}
-%\color{gray}
-%\begin{itemize}
-%\item Action on differential equations.
-%\begin{itemize}
-%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-
-%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
-These formal series are the so-called Gevrey-$1$ series:
-\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is Gevrey-$1$ if there exists $A>0$ such that $|a_n|\leq A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis Gevrey-$k$ series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
-there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obatin germs of holomorphic function for higher Gevrey series.
-}
-
-\begin{notation*}
-We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane).
-Therefore we adopt the following notation:
-\begin{itemize}
-\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
-\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
-\item $\phi$: lower-case letters are holomorphic functions on the frequency domain.
-Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
-\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we will see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
-\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
-\end{itemize}
-\end{notation*}
-
-\begin{lemma}
-Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is Gevrey-1 if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
-\end{lemma}
-In particular, we deduce from the lemma that the Borel transform is an isomorphism between Gevrey-$1$ series and $\C\delta\oplus\C\lbrace\zeta\rbrace$.
-
-The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
-
-\textcolor{magenta}{[add definition of convolution product and $\borel$ being an algebra isomorphisms]}
-
-\subsubsection{Action on power series with fractional exponents}
-The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
-\end{align*}
-and then extending by linearity.
-
-If $\alpha\in\mathbb{R}\setminus\Z$, then $\borel$ is an isomorphisms from Gevrey-$1$ formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
-Indeed, let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-\alpha} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then
-\begin{align*}
-\borel\textcolor{orange}{_\zeta} (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
-\textcolor{magenta}{Under which conditions it doesn't grow faster than factorial?}
-
-\subsubsection{Properties of the Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
-\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
-\item[(vi)] if $\tilde{\Psi}\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\int_0^{\zeta}d\zeta' \tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')=:\tilde{\phi}\ast \tilde{\psi}$, where $\tilde{\psi}=\borel_{\zeta}\tilde{\Psi}$.
-\end{itemize}
-
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
-\begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see 5.12.1 in \cite{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta \text{ from } 0} \left[ \borel \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-
-\begin{proof}
-
-We are going to prove properties (i)--(vi).
-
-(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by defintion \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see Lemma 5.10 \cite{MS16}.
-
-(vi) see Definition 5.12 and Lemma 5.14 \cite{MS16}. 
-\end{proof}
-
-\begin{remark}
-We notice that properties (i) and (ii) are special cases of property (vi), indeed we can use the convolution product 
-\begin{align*}
-\borel_\zeta (z^\alpha \tilde{\Phi})&=\borel_\zeta (z^\alpha)\ast \tilde{\phi}\\
-&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\int_0^1(t\zeta)^{-\alpha-1}(\zeta-t\zeta)^k\zeta dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\int_0^1 t^{-\alpha-1}(1-t)^k dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\frac{\Gamma(k+1)\Gamma(-\alpha)}{\Gamma(k-\alpha+1)}\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
-&=\partial_\zeta^\alpha\tilde{\phi}
-\end{align*}
-\end{remark}
-
-\subsection{Differential equation}
-\textcolor{orange}{Should we keep this section?}
-If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-\begin{equation}%%\label{laplace:op}
-\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-\end{equation}
-The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-\subsubsection{Order shifting}\label{shifting}
-\textcolor{orange}{[why the name order shifting?]}
-Consider holomorphic functions on a simply connected open set that touches but doesn't contain $\zeta = 0$.
-A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as \textcolor{magenta}{[rephrase in terms of $\holoL{\infty, \rho}$]}
-\begin{equation}\label{eqn:slight-defn}
-\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-\end{equation}
-where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-
-Locally integrable slight functions play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In the space of locally integrable slight functions, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
-When $\psi$ is slight and locally integrable at $\zeta = 0$,
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are regular functions.
-\end{prop}
-To prove this result, we'll need a little background.
-
-Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-\begin{proof}[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-is slight.
-Looking at the right-hand side of equation~\ref{eqn:diff-int-split}, we can see that $\phi'$ is slight and locally integrable, so its order is greater than $-1$.
-Hence, $\phi$ has positive order, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\ref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
-
-\section{Proof of main results}
-\subsection{Borel regularity for ODEs}
-
-\begin{theorem}\label{thm1-dim}
-Let $\mathcal{P}$ be a linear differential operator 
-\begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \big],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $\alpha_j$ for $j=1,...,d$ and such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$;
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0, \ldots, R_d$ are entire functions of exponential type
-\end{itemize}
-
-Then, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-
-\color{brown}
-\begin{equation}
-\hat{P}_j:=P(-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta_j)+\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]
-\end{equation}
-\color{black}
-such that $\psi_j$ blows-up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$. 
-\end{theorem}
-\begin{proof}
-It is enough to show that $\hat{P}_j$ satisfies the assumptions of Theorem 2.1.3 of {\tt regular singular Volterra equations}.
-In fact, $P(-\zeta_j)$ is a polynomial, also defined at $\zeta_j=0$ and by assumption $P'(0)\neq 0$.
-$Q$ is also a polynomial defined at $\zeta_j=0$.
-Finally, assuming $R_k(z)=\sum_{j\geq 0} R_{k,j}z^j$
-
-\begin{align*}
-&\partial_{\zeta_j}^{-2}\circ\left[R_0(\partial_{\zeta_j}^{-1})+R_1(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)+...+R_d(\partial_{\zeta_j}^{-1})\circ (-\zeta_j)^d\right]=\sum_{\lambda\leq -2} \partial_{\zeta_j}^\lambda\circ r_\lambda \\
-&\text{ with }r_\lambda=\sum_{k=0}^d R_{k,\lambda}(-\zeta_j)^k.
-\end{align*}
-
-%In particular, $\Lambda=(-\infty,-2]$.
-
-Therefore, there exists a unique solution \[\psi_j(\zeta_j)=\zeta_j^{-\tau_j-1}+f_j(\zeta_j) \text{ with } \tau_j=\frac{Q(\zeta_j=0)}{P'(\zeta_j=0)}=\frac{Q(-\alpha_j)}{P'(-\alpha_j)}\] and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega)$.
-
-\end{proof}
-
-\begin{theorem}\label{thm2-dim}
-For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j}^{\theta_j}$ for some direction $\theta_j$.
-Furthermore, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$ for every $j=1,...,d$.
-Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
-\end{theorem}
-\begin{proof}
-We divide the proof in the following steps:
-\begin{itemize}
-\item[$(a)$] prove that $\psi_j(\zeta_j)$ admits Laplace transform 
-\item[$(b)$] let $\hat{\psi}_j$ be the sum of the germ $\series{\psi}_j:=\borel\series{\Psi}_j$; prove that $\hat{\psi}_j \propto \psi_j$ 
-\item[$(c)$] prove that $\laplace_{\zeta_j}^{\theta_j}\circ\borel\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-
-Step $(c)$ clearly follows from steps $(a)$ and $(b)$.
-We now prove step $(b)$: first notice that if $\series{\Psi}_j$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
-
-\begin{equation}
-\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
-\end{equation}
-
-\color{brown}
-Then taking the (formal) Borel transform:for every $j=1,...,d$ we denote $\zeta_j=\zeta-\alpha_j$ and we consider the Borel transform of $\mathcal{P}\series{\Psi}_j$ in the coordinate $\zeta_j$
-
-\begin{multline*}
-\borel\left(\mathcal{P}\series{\Psi}_j\right)=\borel\left(\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right)=\\
-\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
-\left[P(-\zeta)+\partial_{\zeta_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
-\end{multline*}
-%where 
-%
-%\begin{align*}
-%\series{\psi}_j(\zeta_j):=\borel\series{\Psi}_j(\zeta_j)&=\borel\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\borel\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
-%&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
-%\end{align*}
-
-Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0.
-from the properties of the Borel transform we deduce that $\hat{P}\series{\psi}_j=0$ first notice that $\series{\psi}_j$ is a solution of
-\color{black}
-\end{proof}
-
-\subsection{Borel regularity for thimble integrals}
-
-Let $X$ be a $N-\dim$ manifold, $f\colon X\to\C$ be a holomorphic Morse function with only simple critical points, and $\nu\in\Gamma(X,\Omega^N)$, and set
-\begin{equation}\label{exp-int}
-I(z)\defeq\int_{\mathcal{C}}e^{-zf}\nu
-\end{equation}
-where $\mathcal{C}$ is a suitable countur such that the integral is well defined.  
-For any Morse cirtial points $x_\alpha$ of $f$, the saddle point approximation gives the following formal series 
-\begin{equation}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu\sim \tilde{I}_{\alpha}\defeq e^{-zf(x_\alpha)}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{\alpha,n}z^{-n} \qquad \text{ as } z\to\infty
-\end{equation}
-where $\mathcal{C}_\alpha$ is a steepest descent path through the critical point $x_\alpha$.
-Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-\begin{theorem}\label{thm:maxim} Let $N=1$.
-Let $\tilde{\varphi}_{\alpha}(z)\defeq e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}$ and assume $f''(x_\alpha)\neq 0$ for every critical point $x_\alpha$.
-Then:
-\begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\varphi}_\alpha$ is Gevrey-1.
-\item\label{int:resum-converges} The series $\hat{\varphi}_\alpha(\zeta)\defeq\borel(\tilde{\varphi})$ converges near $\zeta=\zeta_{\alpha}$.
-\item\label{int:resum-valid} If you continue the sum of $\hat{\phi}_\alpha$ along the ray going rightward from $\zeta_\alpha$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_\alpha$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\zeta_\alpha$, we have
-\begin{multline}\label{formula1}
-\hat{\varphi}_{\alpha}(\zeta)=\partial^{\textcolor{red}{3/2}}_{\zeta \text{ from }\zeta_\alpha} \left( \int_{\mathcal{C}_\alpha(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\zeta_\alpha}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\mathcal{C}_\alpha(\zeta')} \nu \right)}\,d\zeta',
-\end{multline}
-where $\mathcal{C}_\alpha(\zeta)$ is the part of $\mathcal{C}_\alpha$ that goes through $f^{-1}([\zeta_\alpha, \zeta])$.
-Notice that $\mathcal{C}_\alpha(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\mathcal{C}_\alpha$.]}
-\end{enumerate}
-\end{theorem}
-\begin{proof}
-Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
-
-Since $f$ is Morse, we can find a holomorphic chart $\tau$ around $x_\alpha$ with $\tfrac{1}{2} \tau^2 = f - \zeta_\alpha$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_\alpha$ that go from the past to $x_\alpha$ and from $x_\alpha$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
-\textbf{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\mathcal{C}_\alpha$ so that $\tau$ in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^\alpha \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^\alpha \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z\zeta_\alpha} I_\alpha(z) & \approx \sum_{n \ge 0} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are dwarfed by their $z^{-(n+1/2)}$ counterparts when $z$ is large.
-These terms are crucial, however, for the convergence of the sum.
-To see why, consider their absolute sum $C_\text{exp}$.
-When $z \in [0, \infty)$,
-\begin{align*}
-C_\text{exp} & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& = 2e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-which diverges for typical $f$ and $\nu$. \textbf{[Does it? Veronica points out that we expect $b_{2n}$ to shrink at least as fast as $(n!)^{-1}$.]}
-
-This argument suggests that no matter how tiny the correction terms get, we can't expect to swat them all aside.
-We can, however, set aside any finite set of them.
-\color{violet}\textbf{[Use Miller's proof of Watson's lemma in place of the following argument, which has a few soft spots.
-See also Loday-Richaud, \S 5.1.5, Theorem~5.1.3]} For each cutoff $N$, the tail
-\[ \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \]
-
-\color{Purple}
-For each cutoff $N$, the tail error \textbf{[check]}
-\begin{align*}
-\left| \sum_{n \ge N} b_{2n}^\alpha \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \right| & \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\varepsilon}^\varepsilon e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& \le \sum_{n \ge N} \left| b_{2n}^\alpha \right| \int_{-\infty}^\infty e^{-|z|\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sqrt{2\pi} \sum_{n \ge N} (2n-1)!!\,\left| b_{2n}^\alpha \right| |z|^{-(n+1/2)} \\
-& \lesssim \sum_{n \ge N} (2n-1)!!\,\varepsilon^{-2n} |z|^{-(n+1/2)} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1}\big)^{2n+1} \big(|z|^{-1/2}\big)^{2n+1} \\
-& = \varepsilon \sum_{n \ge N} (2n-1)!!\,\big(\varepsilon^{-1} |z|^{-1/2}\big)^{2n+1} \\
-& = \textbf{uh-oh!}
-\end{align*}
-\color{violet}
-is in $o_{z \to \infty}(z^{-N})$ \textbf{[check]}, and the absolute sum
-\begin{align*}
-C_\text{exp}^N & = 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left| b_{2n}^\alpha \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{n-k+1} \right| \\
-& \le 2e^{-\operatorname{Re}(z)\varepsilon^2/2} \sum_{n = 1}^{N-1} (2n-1)!!\,\left|b_{2n}^\alpha\right| \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} |z|^{n-k+1} \\
-& \ge -2\varepsilon e^{-z\varepsilon^2/2} \sum_{n \ge 1} (2n-1)!!\,\left|b_{2n}^\alpha\right| z^n,
-\end{align*}
-is in $o_{z \to \infty}(z^{-m})$ for every $m$ \textbf{[check]}.\color{black} Hence,
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows, allowing the simpler estimate
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)}. \]
-Call the right-hand side $\tilde{I}_\alpha$.
-We now see that $a_{\alpha,n} = (2n-1)!!\,b_{2n}^\alpha$ in the statement of the theorem.
-\textbf{[Resolve discrepancy with previous calculation.]} Note that \textbf{[explain formally what it means to center at $\zeta_\alpha$]}
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^\alpha\,\frac{(\zeta - \zeta_\alpha)^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^\alpha\,(\zeta - \zeta_\alpha)^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^\alpha\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{\alpha,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{\varphi}_\alpha$ is Gevrey-1.
-
-Part~\eqref{int:resum-converges}: \begin{align*}
-\hat{\varphi}_\alpha(\zeta)=\borel\left(e^{-zf(x_\alpha)}(2\pi)^{1/2} \sum_{n\geq 0}a_{\alpha,n}z^{-n}\right)(\zeta)=T_{f(x_\alpha)}(2\pi)^{1/2} \left(\delta a_0+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-(2\pi)^{1/2} \left(\delta(f_{x_\alpha}) a_0+\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}\right)
-\end{align*}
-Since $a_{n}\leq CA^nn!$, the series $\sum_{n\geq 0}a_{n+1}\frac{(\zeta-f(x_\alpha))^n}{n!}$ has a finite radius of convergence.
-
-Part~\eqref{int:resum-valid}: Let's recast the integral $I_\alpha$ into the $f$ plane.
-As $\zeta$ goes rightward from $\zeta_\alpha$, the start and end points of $\mathcal{C}_\alpha(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
-Hence, we have
-\begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_{\alpha}} e^{-zf} \nu \\
-& = \int_{\zeta_\alpha}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}\,d\zeta.
-\end{align*}
-Noticing that the right-hand side is a Laplace transform, we learn that
-\begin{equation}\label{thimble-difference}
-\hat{I}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)}.
-\end{equation}
-\color{Aquamarine}
-In Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{I}_\alpha$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
-[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
-Or something even simpler?]
-\color{black}
-
-We can rewrite our Taylor series for $\nu$ as
-\begin{align*}
-\nu & = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{n/2}\,\frac{df}{[2(f - \zeta_\alpha)]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\mathcal{C}^+_\alpha$ and the negative branch on $\mathcal{C}^-_\alpha$. Plugging this into our expression for $\hat{I}_\alpha$, we learn that
-\begin{align*}
-\hat{I}_\alpha(\zeta) & = \left[ \sum_{n \ge 0} b_n^\alpha [2(f - \zeta_\alpha)]^{(n - 1)/2} \right]_{\operatorname{start} \mathcal{C}_\alpha(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha(\zeta)} \\
-& = \sum_{n \ge 0} b_n^\alpha \Big( [2(\zeta - \zeta_\alpha)]^{(n - 1)/2} - (-1)^{n-1}[2(\zeta - \zeta_\alpha)]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^\alpha [2(\zeta - \zeta_\alpha)]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^\alpha (\zeta - \zeta_\alpha)^{n - 1/2} \\
-& = \borel_{\zeta_\alpha} \tilde{I}_\alpha.
-\end{align*}
-We already knew, from the general theory of the Borel transform, that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ would be asymptotic to $\hat{I}_\alpha$.
-We've now shown that the sum of $\borel_{\zeta_\alpha} \tilde{I}_\alpha$ is actually equal to $\hat{I}_\alpha$.
-
-Theorem~\ref{thm:frac-diff-borel} tells us that
-\begin{align*}
-\borel_{\zeta_\alpha} \tilde{I}_\alpha & \defeq \borel_{\zeta_\alpha} z^{-1/2} \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \borel \tilde{\varphi}_\alpha \\
-& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{align*}
-It follows, from our conclusion above, that
-\begin{equation}\label{shifted-resum-valid}
-\hat{I}_\alpha(\zeta) = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{equation}
-Taking the Laplace transform of both sides and applying \textbf{the inverse of Theorem~\ref{thm:frac-diff-borel} that works for shifted analytic functions}, we see that
-\begin{align*}
-I_\alpha(z) & = \laplace_{\zeta, \zeta_\alpha} \left[ \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha \right] \\
-& = z^{-1/2} \laplace_{\zeta, \zeta_\alpha} \hat{\varphi}_\alpha,
-\end{align*}
-as we claimed.
-
-Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha. \]
-Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{I}_\alpha(\zeta) = \partial_\zeta \left( \int_{\mathcal{C}_\alpha(\zeta)} \nu \right), \]
-we can see that
-\[ \partial^{-1}_{\zeta \text{ from } \zeta_\alpha} \hat{I}_\alpha(\zeta) = \int_{\mathcal{C}_\alpha(\zeta)} \nu - \int_{\mathcal{C}_\alpha(0)} \nu. \]
-The initial value term vanishes, because the path $\mathcal{C}_\alpha(0)$ is a point. Hence,
-\[ \int_{\mathcal{C}_\alpha(\zeta)} \nu = \partial^{-3/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha(\zeta). \]
-Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \partial^{3/2}_{\zeta \text{ from } \zeta_\alpha} \left( \int_{\mathcal{C}_p(\zeta)} \nu \right) = \hat{\varphi}_p(\zeta). \]
-\end{proof}
-
-\section{Examples}
-
-\subsection{Airy}
-
-The Airy equation is
-\begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
-\end{equation}
-One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
-\begin{center}
-\includegraphics{figures/u_contour_3.pdf} \\[1em]
-{\small The contour $\Gamma$ in the $u$ plane.}
-\end{center}
-With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
-
-By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we will go straight to the general case.
-However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
-For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
-
-\subsection{Airy--Lucas}
-The Airy-Lucas equation is
-\begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, r-1\}$. A few solutions are given by the Airy-Lucas functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda^{(k)}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{k}{n}\pi\big)$.
-
-\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
-We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel-rational-AL}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation
-\begin{equation}\label{eqn:mod-bessel-AL}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, as we'll see in Section~\textcolor{magenta}{?}, $K$ is the modified Bessel function $K_{{m/n}}$.
-
-Let's put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
-\begin{equation}\label{eqn:reg-mod-bessel-AL}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsubsection{Asymptotic analysis}
-
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp-AL}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
-%\subsection{Going to the spatial domain}\label{spatial-AL}
-\subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\ref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\ref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\ref{diff-eq:spatial-mod-bessel-AL} looks like
-\begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\ref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos-AL}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
-\color{DarkTurquoise}
-\begin{quote}
-We get $v_\alpha$ from the existence result in Section~\ref{frac_int_exist}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
-\begin{align*}
-v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
-& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
-\end{align*}
-In this case, $\tau = \tfrac{1}{2}$.
-\end{quote}
-\color{black}
-
-The Poincar\'{e} algorithm, as we saw in Section~\textbf{[asymptotic analysis]}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
-We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-
-The Borel transform \textcolor{magenta}{[if we define it for trans-monomials, to take care of exponential tilt]} maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL} \textcolor{magenta}{[make sure we include the relevant correspondences in our Borel transform dictionary]}.
-Summation sends convergent elements of $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent formal solutions of a fractional integral equation into analytic solutions \textcolor{magenta}{[prove or cite]}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
-
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{frac_int_exist}.
-It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-\subsubsection{Confirmation of Borel regularity}
-We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
-We found in Section~\textbf{[asymptotic analysis]} that
-\begin{align*}
-\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
-Computing
-\begin{align*}
-\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel\left[ \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
-we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
-Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-
-Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
-Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
-\subsubsection{Contour argument for Airy-Lucas functions}\label{contour-argument-AL}
-We can recast integral~\ref{integral:mod-bessel-rational} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta \\
-& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
-\end{center}
-
-The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-\begin{align*}
-& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-\end{align*}
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
-Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-\color{DarkCyan}
-Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-where $\zeta = -1 + \zeta_{-1}$.
-\color{black}
-
-\subsection{Modified Bessel}
-
-The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
-
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
-\end{equation}
-
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf})
-
-\begin{align*}
-I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]
-\end{align*}
-
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-
-\begin{figure}[h]
-\caption{Add figure path $\Omega$}
-\end{figure}
-
-On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results:
-
-\begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
- \begin{align*}
- \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
-\end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-
-\begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{1}\big)\\
-v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
-\item \textbf{Borel regularity} \textcolor{Lime}{[Check with Aaron how to phrase it]} 
-\end{itemize}
-
-On the other hand, the contour argument we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
-
-\subsubsection{Lifting to a countable cover}\label{countable-cover}
-Formula~\eqref{integral:mod-bessel-rational} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
-Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
-
-Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
-we can rewrite formula~\ref{integral:mod-bessel-rational} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
-\begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
-\end{align}
-For any $\mu \in \C \smallsetminus \Z$, 
-\begin{align}
-\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-\label{intgral:mod-bessel-general} & = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-
-When $\mu$ goes to $0$, formula~\eqref{integral:mod-bessel-lifted} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
-
-\subsection{Higher Airy}
+\textcolor{magenta}{[The higher Airy example is not completed and there are still some difficulties in the computations, even for simple examples. Should we remove it?]}
 
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\textcolor{magenta}{[Charbonnier et al., equation~3.6]}
+with $n \in \{3, 4, 5, \ldots\}$. A few solutions are given by the hyper-Airy functions~\cite[Equation~3.8]{charbonnier22},
 
@@
 
-\subsection{Generalized Airy}
-
-In \cite{Reid} \cite{Drazin-Reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as countour integral (\cite{dlmf} \S 9.13(ii))
-
-\begin{align*}
-\mathrm{A}_k(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
-\mathrm{B}_k(z,p)&=\int_{\gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
-\end{align*}
-where the countours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig.countours}
-
-\begin{figure}
-%\includegraphics[scale=0.5]{countours}
-\end{figure}
-
-Each generalize Airy functions is a solution of
-
-\begin{equation}
-\left[\partial_z^3-z\partial_z+(p-1)\right]f(z,p)=0
-\end{equation}
-
-and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
-
-We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
-
-\begin{equation}
-I_\alpha(z,p)\defeq\frac{1}{2\pi i}\int_{\mathcal{C}_{\alpha}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
-\end{equation}
-
-where $\mathcal{C}_\alpha$ is the path through the point $\alpha$, starting and ending at infinity (as in Figure \ref{fig:path for I}).
-In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$:
-
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\mathcal{C}_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
-&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
-\end{align*}
-
-It follows that $I_+(z)$ is a solution of
-
-\begin{equation}\label{eq:I}
-\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
-\end{equation}
-
-From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combinations of three generators 
-\begin{equation}
-\tilde{I}_+(z,p)=U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
-\end{equation}
-
-where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
-
-\begin{multline}\label{w1}
-\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
-\end{multline}
-
-\begin{multline}\label{w2}
-\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
-\end{multline}
-
-\begin{multline}\label{w3}
-\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
-\end{multline}
-
-Let us first study equation \eqref{w1}: its Borel transform is
-
-\begin{multline*}
--\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
-+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
-\end{multline*}
-
-We differentiate three times, getting
-
-\begin{multline*}
-\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
-+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
-\end{multline*}
-
-we set $y=\zeta^2$
-
-%\begin{multline}
-%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
-%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
-%\end{multline}
-\begin{multline}\label{eq:hw1}
-y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
-+\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
-\end{multline}
-
-which is a generalized hypergeomtric equation (~16.8.5 \cite{dlmf}) with parameters
-
-\begin{align*}
-\mathbf{a}_0=\left(\frac{3}{2}-\frac{p}{3};\frac{7}{6}-\frac{p}{3};\frac{5}{6}-\frac{p}{3}\right) & \qquad\qquad \mathbf{b}_0=\left(\frac{1}{2};\frac{3}{2}\right)
-\end{align*}
-
-therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$.
-
-Then we look at equation \eqref{w2}: its Borel transform is
-
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
--\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-
-and taking three derivatives it simplifies to
-
-\begin{multline}
-\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
-\left.
-\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
-\end{multline}
-
-define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
-
-\begin{multline}\label{eq1}
-\left[y\left(y+\frac{4}{9}\right)^2\partial_y^3+2\left(\frac{3}{2}y+\frac{4}{3}+\frac{y}{2}\left(\frac{17}{2}+p\right)\right)\left(y+\frac{4}{9}\right)\partial_y^2+\left(\frac{2}{3}+\frac{y}{4}\left(\frac{17}{2}+p\right)\right)\partial_y\right.\\
-\left.+\frac{1}{4}\left(\frac{p^3}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(y+\frac{4}{9}\right)\partial_y+\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(y)=0
-\end{multline}
-
-which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
-
-\begin{multline}
-\left[t^2(1-t)\partial_t^3-t\left(\big(\frac{23}{4}+\frac{p}{2}\big)t-\frac{p}{2}-\frac{11}{4}\right)\partial_t^2-\left(-\frac{5}{8}-\frac{p}{4}+t\Big(\frac{887}{144}+\frac{17}{12}p+\frac{p^2}{12}\Big)\right)\partial_t +\right.\\
-\left. -\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(t)=0
-\end{multline}
-hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
-
-\begin{align*}
-\mathbf{a}=\left(\frac{5}{4}+\frac{p}{6};\frac{7}{12}+\frac{p}{6};\frac{11}{12}+\frac{p}{6}\right) & \qquad\qquad \mathbf{b}=\left(\frac{1}{2};\frac{5}{4}+\frac{p}{2}\right)
-\end{align*}
-
-and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
-The equation \eqref{w3} differes from \eqref{w2} for few signs: we find that its Borel transform is
-
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)+2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt+\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-+\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-
-and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
-$\hat{w}_3(\zeta)= c_3\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta-1\right)^2\right)$.
-In particular,
-
-\begin{equation}
-\hat{w}_3(\zeta)=C_{23}\hat{w}_2(\zeta-\tfrac{4}{3})
-\end{equation}
-
-\color{DarkTurquoise}
-
-\section{Third-order exponential integrals}
-\begin{itemize}
-\item Reduce to
-\[ I(z) = \int \exp\left[-z\big(u^3 + pu + q)\right]\,du \]
-using change of coordinate.
-\item When $p \neq 0$, can reduce further to
-\[ I(z) = p^{1/2} e^{-qz} K_{1/3}(p^{3/2} z). \]
-\item As $p$ goes to zero, $I(z)$ degenerates to
-\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}).
-\]
-\end{itemize}
-
-\color{orange}
-\section*{Outline}
-
-\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
-
-\begin{enumerate}
-\item introduction
-\begin{itemize}
-\item Exponential integrals
-\begin{itemize}
-\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
-\item the choice of the path $\mathcal{C}$: 
-\begin{itemize}
-\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
-\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
-\end{itemize}
-\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
-\begin{itemize}
-\item there is a comparison isomorphism (Maxim)
-\end{itemize}
-\item varying $z$ we have the Stokes phenomena
-\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
-\begin{itemize}
-\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
-\item it is an example of resurgent series (\'Ecalle)
-\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
-\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
-\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
-There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
-\end{itemize} 
-\end{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
-\item motivation
-\begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
-\end{itemize}
-\end{itemize}
-\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
-\item State results about resurgence of exponential integrals and Stokes phenomena
-\begin{itemize}
-\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]
-\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
-\end{itemize}
-\end{itemize}
-\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
-\begin{enumerate}
-\item Analytic
-\begin{enumerate}
-\item Introduction
-\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
-\item The Laplace transform of a holomorphic function
-\begin{enumerate}
-\item Over an ordinary point
-\item Over a branch point
-\item Differential equation
-\end{enumerate}
-\item Relating differential equations in the frequency domain to integral equations in the position domain
-\end{enumerate}
-\item Formal
-\begin{enumerate}
-\item Laplace transform of a formal series
-\item Borel transform
-\item Relating differential equations in the frequency variable to integral equations in the position variable
-\end{enumerate}
-\end{enumerate}
-\item Review of integral equations
-\begin{itemize}
-\item Existence of solutions
-\item Fractional integrals and derivatives
-\item Going between integral and differential equations (slight functions)
-\end{itemize}
-\item General cases
-\begin{enumerate}
-\item Borel regularity
-\begin{itemize}
-\item General ODE of the form
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
-\begin{itemize}
-\color{DarkCyan}
-\item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
-\begin{itemize}
-\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
-\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
-\end{itemize}
-\color{orange}
-\item Show that we can find a slight solution at each critical value.
-\item Show that $\hat{\iota} = \tilde{\iota}$, where:
-\begin{itemize}
-\item $I = \laplace \iota$
-\item $\hat{\iota}$ is the Taylor expansion of $\iota$
-\item $\tilde{I}$ is the asymptotic series of $I$
-\item $\tilde{\iota} = \borel \tilde{I}$
-\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
-\end{itemize}
-\end{itemize}
-\item General thimble integral (conditions?)
-\begin{itemize}
-\item Proof of Borel regularity
-\item $3/2$-derivative formula
-\item Contour argument
-\end{itemize}
-\end{itemize}
-\item Resurgence
-\begin{itemize}
-\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
-\item Relate to Ecalle's formalism and the alien derivative
-\item Stokes factors
-\begin{itemize}
-\item For ODEs
-\item For thimble integrals
-\end{itemize}
-\end{itemize}
-\end{enumerate}
-\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
-\begin{enumerate}
-\item The Airy example
-\begin{itemize}
-\item $I(z)$ is a solution of a linear ODE.
-We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Compute Stokes constants
-\begin{itemize}
-\item Using fractional derivative formula and Borel transform computation [{\tt draft2}]
-\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
-\end{itemize}
-\item Comparison with the literature \textcolor{gray}{has to be done}
-\begin{itemize}
-\item Mari\~{n}o
-\item Sauzin
-\item Kontsevich slides
-\item Kawai--Takei? [might take too long to understand well enough]
-\end{itemize}
-\end{itemize}
-\item The Airy--Lucas examples
-\begin{itemize}
-\item Compute Borel transform [{\tt airy-resurgence}]
-\item Compute Stokes constants \textcolor{gray}{has to be done}
-\end{itemize}
-\item Bessel 0 (it is different because we have infinite cover)
-\begin{itemize}
-\item Compute Stokes constants [{\tt draft2}]
-\end{itemize}
-\item Bessel $\mu$ (follows from Bessel 0)
-\begin{itemize}
-\item Compute Stokes constants [{\tt modified Bessel}]
-\end{itemize}
-\item The generalized Airy example
-\item The vibrating beam example
-\begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals, since Andy is interested in that sort of thing
-\end{itemize}
-\end{enumerate}
-\end{enumerate}
-
-\color{black}
-
-\appendix
-
-\section{Integro-differential equations}
-\subsection{Existence of solutions}
-\subsubsection{Algebraic integral operators}
-Take a simply connected open set $\Omega \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\holoL{\infty}(\Omega)$ be the space of bounded holomorphic functions on $\Omega$ with the supremum norm $\|\cdot\|_\infty$.
-For any $\sigma \in \R$, multiplying by $\zeta^{-\sigma}$ maps $\holoL{\infty}(\Omega)$ isomorphically onto another space of holomorphic functions on $\Omega$.
-We'll call this space $\holoL{\infty, \sigma}(\Omega)$ and give it the norm $\|f\|_{\infty, \sigma} = \|\zeta^\sigma f\|_\infty$, so that
-\begin{align*}
-\holoL{\infty}(\Omega) & \to \holoL{\infty, \sigma}(\Omega) \\
-\phi & \mapsto \zeta^{-\sigma} \phi
-\end{align*}
-is an isometry. More generally,
-\begin{align*}
-\holoL{\infty, \rho}(\Omega) & \to \holoL{\infty, \rho+\delta}(\Omega) \\
-f & \mapsto \zeta^{-\delta} f
-\end{align*}
-is an isometry for all $\rho \in \R$ and $\delta \in [0, \infty)$.
-This reduces to the previous statement when $\rho = 0$.
-For each $\delta \in [0, \infty)$, the functions in $\holoL{\infty, \rho}(\Omega)$ belong to $\holoL{\infty, \rho+\delta}(\Omega)$ too, and the inclusion map $\holoL{\infty, \rho}(\Omega) \hookrightarrow \holoL{\infty, \rho+\delta}(\Omega)$ has norm $\|\zeta^\delta\|_\infty$.
-Conceptually, $\|\zeta^\delta\|_\infty$ measures of the size of $\Omega$, so let's write it as $M^\delta$ with $M = \|\zeta\|_\infty$.
-
-Since $\holoL{\infty}(\Omega)$ is a Banach algebra, the function space $\holoL{\infty, \infty}(\Omega) := \bigcup_{\sigma \in \R} \holoL{\infty, \sigma}(\Omega)$ is a graded algebra, with a different norm on each grade.
-For each $\rho, \delta \in \R$, multiplication by a function $m \in \holoL{\infty, \delta}(\Omega)$ gives a map $\holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \rho+\delta}(\Omega)$ with norm $\|m\|_{\infty, \delta}$.
-
-We'll study integral operators $\mathcal{G} \maps \holoL{\infty, \rho}(\Omega) \to \holoL{\infty, \sigma}(\Omega)$ of the form
-\[ [\mathcal{G}f](a) = \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta, \]
-where the kernel $g$ is an algebraic function over $\C^2$ which can be singular on $\Delta$, the diagonal.\footnote{Thanks to Alex Takeda for suggesting this.} To avoid ambiguity, we fix a branch of $g$ to use at the start of the integration path.
-The domain of $g$ is a covering of $\C^2$ which can be branched over $\Delta$.
-Continuing $g$ around $\Delta$ changes its phase by a root of unity, leaving its absolute value the same \textbf{[check]}.
-That makes $|g|$ a well-defined function on $\C^2 \smallsetminus \Delta$, which we can use to bound $\|\mathcal{G}\|$.
-
-For each $a \in \C$, the expression $|g(a, \cdot)\,d\zeta|$ defines a {\em density} on $\Omega \smallsetminus \{a\}$---a norm on the tangent bundle which is compatible with the conformal structure.
-The square of a density is a Riemannian metric.
-Let $\ell^{\sigma, \rho}_{g, \Omega}(a)$ be the distance from $\zeta = 0$ to $a$ with respect to the density $|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ on $\Omega \smallsetminus \{a\}$.
-The bound
-\begin{align*}
-\big|[\zeta^\sigma \mathcal{G}f](a)\big| & \le \left| \zeta(a)^\sigma \int_{\zeta = 0}^{a} g(a, \cdot)\,f\,d\zeta \right| \\
-& \le \int_{\zeta = 0}^{a} |\zeta^\rho f|\,|\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta| \\
-& \le \|f\|_{\infty, \rho} \int_{\zeta = 0}^{a} |\zeta(a)^\sigma\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|
-\end{align*}
-holds for any integration path. Taking the infimum over all paths, we see that
-\[ \big|[\mathcal{G}f](a)\big| \le \ell^{\sigma, \rho}_{g, \Omega}(a)\,\|f\|_{\infty, \rho}. \]
-so $\|\mathcal{G}\| \le \sup_{a \in \Omega} \ell^{\sigma, \rho}_{g, \Omega}(a)$. Crucially, we can always make $\|\mathcal{G}\|$ a contraction by restricting $\Omega$.
-\subsubsection{The example of fractional integrals}
-Setting $g(a, a') = (\zeta(a) - \zeta(a'))^{-\lambda-1}$ with $\lambda \in (-\infty, 0)$, we get the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$.
-The shortest path from $\zeta = 0$ to $a$ with respect to $|\zeta(a)^{\rho+\lambda}\,g(a, \cdot)\,\zeta^{-\rho}\,d\zeta|$ is the same as the shortest path with respect to $|d\zeta|$ \textcolor{magenta}{[check]}.
-It follows that
-\begin{align*}
-\ell^{\sigma, \rho}_{g, \Omega}(a) & = \int_0^{|\zeta(a)|} |\zeta(a)|^{\rho+\lambda}\,(|\zeta(a)| - r)^{-\lambda-1}\,r^{-\rho}\,dr \\
-& = |\zeta(a)|^{\rho+\lambda} \int_0^1 \,(|\zeta(a)| - |\zeta(a)| t)^{-\lambda-1}\,(|\zeta(a)| t)^{-\rho}\,|\zeta(a)|\,dt \\
-& = |\zeta(a)|^{\rho+\lambda-\lambda-1-\rho+1} \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = \int_0^1 \,(1-t)^{-\lambda-1}\,t^{-\rho}\,dt \\
-& = B(-\lambda,\,1-\rho).
-\end{align*}
-The beta function $B$ can be written more explicitly as
-\[ B(-\lambda,\,1-\rho) = \frac{\Gamma(-\lambda)\,\Gamma(1-\rho)}{\Gamma(1-\lambda-\rho)}. \]
-Now we can see that for each $\lambda \in (-\infty, 0)$ and $\rho \in \R$, the fractional integral $\partial^\lambda_{\zeta \text{ from } 0}$ maps $\holoL{\infty, \rho}(\Omega)$ into $\holoL{\infty, \rho+\lambda}(\Omega)$, with norm $\|\partial^\lambda_{\zeta \text{ from } 0}\| \le B(-\lambda,\,1-\rho)$.
-\subsubsection{Fractional integral equations near a regular singular point}\label{frac_int_exist}
-\textcolor{SeaGreen}{\textbf{Angeliki:} Maybe Kato--Rellich perturbation theory can give existence immediately. It might not give uniqueness, though.}
-
-Consider an integral operator $\mathcal{J}$ of the form
-\[ p + \partial^{-1}_{\zeta \text{ from } 0} \circ q + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda, \]
-where:
-\begin{itemize}
-\item $p$ is a function in $\holoL{\infty, -1}(\Omega)$ that extends holomorphically over $\zeta = 0$, and its derivative at $\zeta = 0$ is non-zero.
-\item $q$ is a function in $\holoL{\infty}(\Omega)$ that extends holomorphically over $\zeta = 0$.
-\item $r_\lambda$ are functions in $\holoL{\infty}(\Omega)$.
-\item $\Lambda$ is a countable subset of $(-\infty, -1)$ whose supremum is less than $-1$.
-\end{itemize}
-Our demand that $p$ and $q$ have convergent power series at $\zeta = 0$ can probably be relaxed; having convergent Novikov series, for example, should be enough.
-We could also probably replace $\partial^{-1}_{\zeta \text{ from } 0}$ with $\partial^{-1+\delta}_{\zeta \text{ from } 0} \circ \zeta^\delta$ for some $\delta \in [0, 1)$, or adjust the $\partial^\lambda_{\zeta \text{ from } 0}$ similarly.
-
-We want to solve the equation $\mathcal{J}f = 0$.
-Let's look for a solution of the form $f = \zeta^{\tau-1} + \tilde{f}$ with $\tau \in (0, \infty)$ and $\tilde{f} \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-When $\epsilon$ is small enough that $\Lambda \subset (-\infty, -1 - \epsilon]$, we'll see that we can always find such a solution, as long as we're willing to shrink $\Omega$.
-In fact, there's exactly one such solution.
-\textcolor{magenta}{[Add convergence conditions for $\partial^\lambda$ terms.]}
-
-Let $p'_0$ and $q_0$ be the values of $\tfrac{\partial}{\partial \zeta} p$ and $q$, respectively, at $\zeta = 0$.
-We're assuming that $p$ and $q$ extend holomorphically over $\zeta = 0$, and the additional assumption that $p \in \holoL{\infty, -1}(\Omega)$ implies that $p$ has a first-order zero at $\zeta = 0$.
-
-Since $p$ and $q$ extend holomorphically over $\zeta = 0$, and $p$ vanishes at $\zeta = 0$, we can write
-\begin{alignat*}{2}
-p & = p'_0 \zeta &\;+\;& \tilde{p} \\
-q & = q_0 &\;+\;& \tilde{q}
-\end{alignat*}
-with $\tilde{p} \in \holoL{\infty, -2}(\Omega)$ and $\tilde{q} \in \holoL{\infty, -1}(\Omega)$. Then we have
-\[ \mathcal{J} = p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \]
-with
-\[ \tilde{\mathcal{J}} = \tilde{p} + \partial^{-1}_{\zeta \text{ from } 0} \circ \tilde{q} + \sum_{\lambda \in \Lambda} \partial^\lambda_{\zeta \text{ from } 0} \circ r_\lambda \]
-For any $\tau \in (0, \infty)$,
-\[ \mathcal{J} \zeta^{\tau-1} = (p'_0 + q_0/\tau)\,\zeta^\tau + \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Setting $\tau = -q_0 / p'_0$ makes the first term vanish, leaving
-\[ \mathcal{J} \zeta^{\tau-1} = \tilde{\mathcal{J}} \zeta^{\tau-1}. \]
-Then the equation $\mathcal{J}f = 0$ becomes
-\begin{align}
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \mathcal{J}\tilde{f} \nonumber \\
-0 & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ p'_0\zeta + q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
--p'_0\zeta\tilde{f} & = \tilde{\mathcal{J}}\zeta^{\tau-1} + \left[ q_0\,\partial^{-1}_{\zeta \text{ from } 0} + \tilde{\mathcal{J}} \right]\tilde{f} \nonumber \\
-\tilde{f} & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1} + \left[ \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\tilde{f}.
-\label{fixed-pt}
-\end{align}
-
-\color{Indigo}
-\begin{center}
-\begin{tikzcd}[column sep=25mm, row sep=2mm]
-& & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{p}", "\|\tilde{p}\|_{\infty, -2}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^{1-\epsilon}"'] \\
-& & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\tilde{q}", "\|\tilde{q}\|_{\infty, -1}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 2-\rho) = \frac{1}{2-\rho}}"'] & \holoL{\infty, \rho-2}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty"'] \arrow[rd, hook, "\|\zeta\|_\infty^2"'] \\
-& & & \holoL{\infty, \rho}(\Omega) \\
-& & & \holoL{\infty, \rho-1}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "r_\lambda", "\|r_\lambda\|_\infty"'] & \holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^\lambda", "{B(-\lambda, 1-\rho)}"'] & \holoL{\infty, \rho+\lambda}(\Omega) \arrow[ru, hook, "\|\zeta\|_\infty^{-1-\lambda}"'] \arrow[rd, hook, "\|\zeta\|_\infty^{-1-\epsilon-\lambda}"'] \\
-& & & \holoL{\infty, \rho-1-\epsilon}(\Omega) \\
-\holoL{\infty, \rho}(\Omega) \arrow[r, "\partial^{-1}", "{B(1, 1-\rho) = \frac{1}{1-\rho}}"'] & \holoL{\infty, \rho-1}(\Omega) \arrow[r, "\zeta^{-1}", "\|\zeta^{-1}\|_{\infty, 1} = 1"'] & \holoL{\infty, \rho}(\Omega) \\
-\end{tikzcd}
-\end{center}
-\color{black}
-
-From \textbf{[our previous discussion]}, we can work out that
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda}
-\end{align*}
-and
-\begin{align*}
-\tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau-\epsilon}(\Omega) \to \holoL{\infty, -\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\end{align*}
-Since $\|\zeta^{-1}\|_{\infty, 1} = 1$, it follows that
-\begin{align*}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \maps \holoL{\infty, 1-\tau}(\Omega) \to \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau}\,\|\tilde{q}\|_{\infty, -1} \right) M^{1-\epsilon} + \sum_{\lambda \in \Lambda} B(-\lambda, \tau)\,\|r_\lambda\|_{\infty}\,M^{-1-\epsilon-\lambda} \label{bound:mollify}
-\end{align*}
-and
-\begin{align}
-\zeta^{-1} \circ \tilde{\mathcal{J}} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with} \\%\nonumber \\
-\|\zeta^{-1} \circ \tilde{\mathcal{J}}\| & \le \left(\|\tilde{p}\|_{\infty, -2} + \tfrac{1}{1+\tau+\epsilon}\,\|\tilde{q}\|_{\infty, -1} \right) M + \sum_{\lambda \in \Lambda} B(-\lambda, \tau+\epsilon)\,\|r_\lambda\|_{\infty}\,M^{-1-\lambda}.
-\label{bound:perturb}
-\end{align}
-We can also see that
-\begin{align}
-\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} & \acts \holoL{\infty, 1-\tau-\epsilon}(\Omega)\;\text{with}   \nonumber \\
-\|\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}\| & = \tfrac{\tau}{\tau+\epsilon} < 1 \label{bound:contract}.
-\end{align}
-
-Now, let's return to equation~\ref{fixed-pt}, which tells us that $f = \zeta^{\tau-1} + \tilde{f}$ satisfies $\mathcal{J}f = 0$ when \textcolor{magenta}{[and only when?]} $\tilde{f}$ is a fixed point of the affine map $\mathcal{A}(\cdot) + b$, where
-\begin{align*}
-\mathcal{A} & = \tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0} - \tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}}  \\
-b & = \left[ -\tfrac{1}{p'_0}\,\zeta^{-1} \circ \tilde{\mathcal{J}} \right]\,\zeta^{\tau-1}
-\end{align*}
-Choosing $\epsilon \in (0, 1]$ so that $\Lambda \subset (-\infty, -1 - \epsilon]$ has given us the domain and codomain statements in bounds \ref{bound:mollify} and \ref{bound:perturb}, which tell us that $\mathcal{A}(\cdot) + b$ sends $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ into itself.
-We'll show that when $\Omega$ is small enough, $\mathcal{A}(\cdot) + b$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$, and thus---by the contraction mapping theorem---has a unique fixed point.
-
-An affine map is a contraction if and only if its linear part is a contraction.
-We know from bound~\ref{bound:contract} that $\tau\,\zeta^{-1} \circ \partial^{-1}_{\zeta \text{ from } 0}$ contracts $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$.
-Since the supremum of $\Lambda$ is less than $-1$, all the powers of $M = \|\zeta\|_\infty$ in bound~\ref{bound:perturb} are positive.
-Thus, by shrinking $\Omega$, we can make the norm of $\zeta^{-1} \circ \tilde{\mathcal{J}}$ on $\holoL{\infty, 1-\tau-\epsilon}(\Omega)$ as small as we want---small enough to make $\mathcal{A}$ a contraction.
-%\input{chapters/appendix}
-
-\section{The Airy equation}\label{airy-appendix}
-
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[-z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel-1/3}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
-%The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-%\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-%where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
-Like we did in equation~\ref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
-
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsection{Asymptotic analysis}
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm:1}.
-
-\subsection{Building a distinguished frame of analytic solutions}
-\subsubsection{Going to the spatial domain}\label{spatial}
-%\subsubsection{The big idea}\label{big-idea}
-We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-%\textcolor{Magenta}{Show that $W_1$ is asymptotic to $\tilde{W}_1$!}
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
-
-%\color{DodgerBlue}
-%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\ref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
-%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-%where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-\subsection{Borel regularity}\label{bessel-regularity}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
-
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\laplace_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$
-
-\begin{align*}
-\borel\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\borel\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:bessel-rescaled} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-
-\subsection{Contour argument for the Airy function}\label{contour-argument}
-Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
-\begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ in the $\zeta$ plane.}
-\end{center}
-
-From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
-so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
-
-In addition to the solutions $v_1$ and $v_{-1}$ from Section~\ref{pos-root}\,--\, \ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
-\begin{alignat*}{2}
-g_1 &\;=\;& & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi_1\big) \\
-g_{-1} &\;=\;&  & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi_1\big),
-\end{alignat*}
-given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows \textcolor{magenta}{[verified numerically]} that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
-so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
-The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $g_1$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,v_1$,
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
-Hence,
-\begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} v_1\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} v_1\;d\zeta \\
-e^z K & = \tfrac{i}{2} \laplace_{\zeta_1} v_1,
-\end{align*}
-just as we found in Section~\ref{bessel-regularity}.
-\subsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\ref{eqn:mod-bessel}.
-
-To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
-\[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\ref{eqn:hypergeom-neg}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the contour integration method of solving equation~\eqref{eqn:mod-bessel} is associated with the basis
-\begin{align*}
-g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
-\end{align*}
-of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
-
-The Laplace transformation method of solving equation~\eqref{eqn:mod-bessel}, on the other hand, is associated with the basis
-\begin{alignat*}{2}
-v_{-1} &\;=\;& (1-\xi)^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-v_1 &\;=\:& \xi^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
-\end{alignat*}
-given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
-
-Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
-\begin{alignat*}{3}
-v_{-1} &\;=\;&\tfrac{1}{\sqrt{3}}\,g_{-1} &\;+\;& \tfrac{1}{2}\,v_1 \\
-v_1 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_{1} &\;+\;& \tfrac{1}{2}\,v_{-1}.
-\end{alignat*}
-Summing these identities, we see that
-\[ g_1 + g_{-1} = \tfrac{\sqrt{3}}{2}\,(f_1 + f_{-1}), \]
-giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
-
-\subsection{Comparison with other treatments of the Airy equation}
-
-\subsubsection{Different Borel transform convention} Physicists often use a different version of the Borel transform:
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
-It's sometimes convenient to $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
-
-For problems involving a small parameter $\hbar$ rather than a large parameter $z$, physicists also define
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\hbar^n & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-From a combinatorial perspective, this is just the transformation that sends an ordinary generating function to the corresponding exponential generating function.
-
-In \cite{Diablerets}, the author studies the Airy functions as example of resurgent functions. He starts with the formal trans-monomial solutions of Airy equation:
-
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
-\end{align*}  
-where 
-\begin{align*}
-\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
-\end{align*}
-%Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-Then, by applying the two definitions of the Borel transform $\borel_{\textit{phys}}$ and $\borel$, on the one hand we have  
-\begin{align*}
-w_{1,2}(\zeta)&\defeq\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
-&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) 
-\end{align*}
-on the other hand, we find
-\begin{align*}
-\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
-\end{align*}
-%That ambiguity comes from the different definitions of Borel transforms: 
-%\begin{align*}
-%\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%\end{align*}
-
-and comparing the two solutions we notice that up to the factor of $\delta$
-
-\begin{equation}\label{Borel-W12}
-\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta) 
-\end{equation}
-More generally, if $\tilde{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
-
-\begin{equation}
-\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\tilde{\Phi}=\borel\tilde{\Phi}.
-\end{equation}
-In particular, $\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
-
-%Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
-We want to compare $v_1$ with the \textit{physic} Borel transform $\borel_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
-%
-%\begin{align*}
-%\borel_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
-%&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
-%&=\frac{1}{2\pi}\zeta^{1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right) 
-%\end{align*}
-%
-%Now taking the $-1$- derivative of $v_1(\zeta)$ we get
-%
-%\begin{align*}
-%\partial_\zeta^{-1} v_1&=\frac{1}{\Gamma(1)}\int_0^{\zeta}(\zeta-\zeta') v_1(\zeta')d\zeta'\\
-%&=\int_0^{\zeta}(\zeta-\zeta') \zeta'^{-1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta'}{2}\right)d\zeta'\\
-%&=\frac{\Gamma(1/2)}{\Gamma(3/2)}\zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)\\
-%&=2 \zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)
-%\end{align*}
-
-\subsubsection{Integral formula for hypergeometric functions}
-
-In \cite{MS16} the author studies summability and resurgent properties of solutions of the Airy equation.
-
-He considers the formal power series  
-\[\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
-such that
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
-\tilde{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
-\end{align*} 
-are formal solutions of the Airy equation. Notice that compared to Marino's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
-
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\tilde{\Phi}_{\pm}$ as a convolution product:
-
-\begin{align*}
-\hat{\phi}_+(\zeta):=\borel\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
-\end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$.
-
-%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
-%
-%\begin{align*}
-%\tilde{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\tilde{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
-%\end{align*}
-%which up to a constant factor for $\delta$, they agree with our results.
-
-Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
-
-\begin{align*}
-\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
-\end{align*}
-where in the last step we use the Euler formula for hypergeometric functions \footnote{The Euler formula is \begin{equation}\label{Euler formula}
-{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
-\end{equation}}. Then, by taking derivatives we recover $\hat{\phi}_{\pm}(\zeta)$:
-
-\begin{align*}
-\hat{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
-\hat{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)
-\end{align*} 
-and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
-The main advantage of writing Gauss hypergeometric functions as a convolution product relies on Ecalle's singularity theory.
-Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see \textbf{Sauzin notes}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see Lemma 6.106 \cite{MS}).
-%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
-
-\subsubsection{Comparison with exact WKB}
-
-Kawai and Takei study the WKB analysis of the Airy--type Schrodinger equation
-
-\begin{equation}
-\label{WKB_Airy} 
-\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
-\end{equation}
-as $\eta\to\infty$.
-They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
-In the coordinate $t=\frac{3}{2}yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
-\begin{align*}
-\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
-\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
-\end{align*}
-where $s=t/2+1/2$. 
-The same hypergeometric functions have been computed in Section \ref{Airy} as the Borel transform of the formal solutions of the Airy equation
-
-\begin{equation}
-\label{Airy}
-\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
-\end{equation}
-
-Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
-So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
-
-First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
-\begin{align*}
-\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
-\end{align*} 
-then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
-\begin{align*}
-\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
-\end{align*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
-\begin{equation}
-\label{eq_Phi}
-\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
-\end{equation}
-
-\begin{proof}
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
-&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
-&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
-&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
-\end{align*}
-\end{proof}
-Now rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{2}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta x^{-1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-%&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-1\right]\Phi=0
-\end{align*}
-
-therefore $\Phi(q)$ is a solution of the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
-
-\begin{remark}
-The change of coordinate $q=\frac{2}{3}\eta x^{3/2}$ is not casual: recall that the WKB ansatz for a Schrodinger type equation is
-
-\begin{equation}
-\psi(x,\eta)=\exp\left(\int_{x_0}^xS(\eta,x')dx'\right)
-\end{equation} 
- and $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. In addition, for the Airy--type Schrodinger equation 
- \begin{align*}
- S_{-1}^2=x
- \end{align*}
-hence, up to a choice of sign for the square root
-\begin{align*}
-q&=\frac{2}{3}\eta x^{3/2}=\eta\int_0^x\sqrt{x'}dx'=\eta\int_{0}^xS_{-1}(x')dx'.
-\end{align*}
-We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.
-\end{remark}
-
-\section{Application of the integral formula}
-
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{\varphi}_{\alpha}$ can be computed by the fractional derivative formula~\eqref{int:deriv-formula}. \color{olive}
-
-By general theory it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
-Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the contour argument and from the integral formula.
-When computed from the ODE, there is an ambiguity in the choice of the constant, while with the contour argument and the fractional integral formula the ambiguity is solved.
-We will see this for the modified Bessel equation.
-
-This method allows to uniquely determined the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
-Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
-%In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
-\begin{lemma}\label{claim 2}
-The following formula holds true
-\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
-for any $\zeta\in [2/3,+\infty)$.
-\end{lemma}
-\begin{proof}
-In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
-Hence,
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
-
-\begin{lemma}\label{claim 3}
-For any $\zeta\in (-\infty,-2/3]$
-\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
-\end{lemma}
-\begin{proof}
-Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
-\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
-In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity \textbf{[DLMF~15.4.16]}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions~\textbf{[Koornwinder, \S 4.1]}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using \textbf{[DLMF 15.5.4]} and \textbf{[DLMF 15.5.1]}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-
-\bibliographystyle{plain}
+\bibliographystyle{utphys}
 \bibliography{airy-resurgence}
-
 \end{document}

### 2023-11-01 exp-resurgence.tex
Updates from Overleaf

@@
 
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $\alpha_1,...,\alpha_N$ \footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
 
@@
 
-regarded as holomorphic functions in the position domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
+regarded as holomorphic functions in the frequency domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
 In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.
@@
 \end{equation}
-where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical point $\alpha_j$.
+where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical \textcolor{red}{point/value $a_j/\alpha_j$}.
 
@@
 From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
-Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $\alpha_j$ there are local coordinates $x_1,...,x_N$ such that
+Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $a_j$ there are local coordinates $x_1,...,x_N$ such that
 \[f=\alpha_j+\sum_{k=1}^N x_k^2\]
@@
 
-Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_\alpha$, namely the integrals over Lefschetz thimbles labeled by the critical points $x_j\in\text{Crit}(f)$.
-
-As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,k$ (and $l\neq j$).
+Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_j$, namely the integrals over Lefschetz thimbles labeled by the critical points $a_j\in\text{Crit}(f)$.
+
+As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$).
 The jumps can be described geometrically using the theory of Picard--Lefschetz.
@@
 
-For each critical point $x_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j:=f(x_j)$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
+For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
 These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
 The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $x_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.
+The Lefschetz thimble  $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.
 
@@
 Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
-In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
+\textcolor{red}{At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.--I think we realise they have the same expansion at $\alpha_j$, thus they must agree.} In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
 
@@
 In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
-Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the spatial domain.
-
-Furthermore, we introduce a geometric picture where the spatial domain $B$ is a translation surface.
+Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain.
+
+Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
 If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
@@
 
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), the anharmonic oscillator...).
-Then, on the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.
-On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
 The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}.
-In the Airy example (\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
-Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.
+In the Airy example (see Section \ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
+Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.}
 
@@
 
-\subsection{thimble projection reasoning for the Airy function}\label{contour-argument}
+\subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
 Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
@@
 
-\section{Plan of the paper}
-\subsection{Results}
-
-\color{orange}
-\begin{itemize}
-\item what does it mean to be Borel regular?
-\item when does it happen?
-\begin{itemize}
-\item State new Borel regularity results
-\begin{itemize}
-\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
-\begin{itemize}
-\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
-\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
-\item Also contextualize with Loday-Richaud
-\end{itemize}
-\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
-\begin{equation}
-\begin{tikzcd}
-I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-& \\
-\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
-\end{tikzcd}
-\end{equation}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item thimble projection formula
-\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
-\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
-\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
-\end{itemize}
-%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
-\end{itemize}
-\end{itemize}
-
-\color{orange}
-\subsection*{Outline}
-
-\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}
-
-\begin{enumerate}
-\item introduction
-\begin{itemize}
-\item Exponential integrals
-\begin{itemize}
-\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
-\item the choice of the path $\mathcal{C}$: 
-\begin{itemize}
-\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
-\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
-\end{itemize}
-\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
-\begin{itemize}
-\item there is a comparison isomorphism (Maxim)
-\end{itemize}
-\item varying $z$ we have the Stokes phenomena
-\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
-\begin{itemize}
-\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
-\item it is an example of resurgent series (\'Ecalle)
-\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
-\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
-\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$.
-There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism
-\end{itemize} 
-\end{itemize}
-\item what are exponential integrals? \textcolor{gray}{has to be done}
-\begin{itemize}
-\item motivation
-\begin{itemize}
-\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
-\item In physics ??
-\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
-\end{itemize}
-\end{itemize}
-\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
-\item State results about resurgence of exponential integrals and Stokes phenomena
-\begin{itemize}
-\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
-\item ODE and fractional derivative formula [{\tt draft2}]
-\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
-\end{itemize}
-\end{itemize}
-\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
-\begin{enumerate}
-\item Analytic
-\begin{enumerate}
-\item Introduction
-\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
-\item The Laplace transform of a holomorphic function
-\begin{enumerate}
-\item Over an ordinary point
-\item Over a branch point
-\item Differential equation
-\end{enumerate}
-\item Relating differential equations in the frequency domain to integral equations in the position domain
-\end{enumerate}
-\item Formal
-\begin{enumerate}
-\item Laplace transform of a formal series
-\item Borel transform
-\item Relating differential equations in the frequency variable to integral equations in the position variable
-\end{enumerate}
-\end{enumerate}
-\item Review of integral equations
-\begin{itemize}
-\item Existence of solutions
-\item Fractional integrals and derivatives
-\item Going between integral and differential equations (slight functions)
-\end{itemize}
-\item General cases
-\begin{enumerate}
-\item Borel regularity
-\begin{itemize}
-\item General ODE of the form
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
-where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
-\begin{itemize}
-\color{DarkCyan}
-\item More generally, for $P$ of degree $n$, we should be able to handle
-\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
-where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
-\begin{itemize}
-\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
-\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
-\end{itemize}
-\color{orange}
-\item Show that we can find a slight solution at each critical value.
-\item Show that $\hat{\iota} = \tilde{\iota}$, where:
-\begin{itemize}
-\item $I = \laplace \iota$
-\item $\hat{\iota}$ is the Taylor expansion of $\iota$
-\item $\tilde{I}$ is the asymptotic series of $I$
-\item $\tilde{\iota} = \borel \tilde{I}$
-\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
-\end{itemize}
-\end{itemize}
-\item General thimble integral (conditions?)
-\begin{itemize}
-\item Proof of Borel regularity
-\item $3/2$-derivative formula
-\item thimble projection reasoning
-\end{itemize}
-\end{itemize}
-\item Resurgence
-\begin{itemize}
-\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
-\item Relate to \'Ecalle's formalism and the alien derivative
-\item Stokes factors
-\begin{itemize}
-\item For ODEs
-\item For thimble integrals
-\end{itemize}
-\end{itemize}
-\end{enumerate}
-\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
-\begin{enumerate}
-\item The Airy example
-\begin{itemize}
-\item $I(z)$ is a solution of a linear ODE.
-We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
-\item Compute Stokes constants
-\begin{itemize}
-\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
-\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
-\end{itemize}
-\item Comparison with the literature \textcolor{gray}{has to be done}
-\begin{itemize}
-\item Mari\~{n}o
-\item Sauzin
-\item Kontsevich slides
-\item Kawai--Takei? [might take too long to understand well enough]
-\end{itemize}
-\end{itemize}
-\item The Airy--Lucas examples
-\begin{itemize}
-\item Compute Borel transform [{\tt airy-resurgence}]
-\item Compute Stokes constants \textcolor{gray}{has to be done}
-\end{itemize}
-\item Bessel 0 (it is different because we have infinite cover)
-\begin{itemize}
-\item Compute Stokes constants [{\tt draft2}]
-\end{itemize}
-\item Bessel $\mu$ (follows from Bessel 0)
-\begin{itemize}
-\item Compute Stokes constants [{\tt modified Bessel}]
-\end{itemize}
-\item The generalized Airy example
-\item The vibrating beam example
-\begin{itemize}
-\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
-\end{itemize}
-\end{enumerate}
-\end{enumerate}
-
-\subsection{Why Borel regularity works for thimble integrals}
-\color{DarkBlue}
-\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial.
-His proof uses microlocal analysis and classical results due to Varchenko.
-In the same algebraic setting, Malgrange states the Borel regularity result \cite[Theorem 6]{Malgrange22}
-\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
-\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-\item A corollary of [Thm 4] is the thimble projection formula.
-\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
-\begin{equation}
-mmm
-\end{equation} 
-\end{itemize}
-\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-\begin{itemize}
-\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
-\end{itemize}
-\end{itemize}
-\color{black}
-
 \bibliographystyle{plain}

### 2023-11-01 Plan.tex

\documentclass{article}

\usepackage{url}
\usepackage[hmargin=1.5in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage{tikz-cd}
% convenience aliases
\newcommand{\maps}{\colon}

% symbology
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}

\newcommand{\series}[1]{\tilde{#1}}
\newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
\newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
\newcommand{\laplacepde}{\mathcal{D}}
\newcommand{\van}{\mathfrak{m}}
\DeclareMathOperator{\Ai}{Ai}
\usetikzlibrary{matrix,shapes,arrows,decorations.pathmorphing}
\tikzset{commutative diagrams/arrow style=math font}
\tikzset{commutative diagrams/.cd,
mysymbol/.style={start anchor=center,end anchor=center,draw=none}}
\newcommand\MySymb[2][\square]{%
  \arrow[mysymbol]{#2}[description]{#1}}
\tikzset{
shift up/.style={
to path={([yshift=#1]\tikztostart.east) -- ([yshift=#1]\tikztotarget.west) \tikztonodes}
}
}
\DeclareMathAlphabet{\mathpzc}{OT1}{pzc}{m}{it}

\newcommand*{\defeq}{\mathrel{\vcenter{\baselineskip0.5ex \lineskiplimit0pt
                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
                     =}
\newcommand*{\defeqin}{\mathrel{\vcenter{\lineskiplimit0pt\baselineskip0.5ex
                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
                     =}

%%\let\Re\relax
%%\DeclareMathOperator{\Re}{Re}

\newcommand{\laplace}{\mathcal{L}}
\newcommand{\borel}{\mathcal{B}}
\newcommand{\aexp}{\text{\ae}}
\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}

\newtheorem{definition}{Definition}[section]
\newtheorem{prop}[definition]{Proposition}
\newtheorem{remark}[definition]{Remark}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{conjecture}[definition]{Conjecture}
\newtheorem{claim}[definition]{Claim}
%\newtheorem{exercise}[definition]{Exercise}
%\newtheorem*{notation*}{Notation}

% drafting environments
\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}

% colors
\definecolor{ietocean}{RGB}{0, 30, 140}
\definecolor{ietcoast}{RGB}{0, 150, 173}
\definecolor{ietlagoon}{RGB}{0, 216, 180}

% pretty prince hyperref must always be the last thing in the preamble, always
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  linkcolor={ietcoast},
  citecolor={ietcoast},
  urlcolor={ietcoast}
}

\title{Plan of the paper---old material}
\author{Veronica Fantini}

\begin{document}
\maketitle

\section{Plan of the paper}
\subsection{Results}

\color{orange}
\begin{itemize}
\item what does it mean to be Borel regular?
\item when does it happen?
\begin{itemize}
\item State new Borel regularity results
\begin{itemize}
\item Linear, homogeneous ODE with a regular singularity at 0 and irregular singularity at infinity [big idea in {\tt airy-resurgence}]
\begin{itemize}
\item Contextualize with previous work of Braaksma (``Multisummability and Stokes multipliers of linear meromorphic differential equations'')
\item Also contextualize with Balser, Braaksma, Sibuya, and Ramis (``Multisummability of formal power series solutions of linear ordinary differential equations'')
\item Also contextualize with Loday-Richaud
\end{itemize}
\item \emph{Borel regularity} for \textbf{thimbles integrals} can be stated a the commutativity of the following diagram:
\begin{equation}
\begin{tikzcd}
I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu \arrow[r,"\sim"]\arrow[dd, swap, "\laplace^\theta "] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
& \\
\hat{\iota}_\alpha(\zeta)\arrow[r,equal,swap, "\text{sum}"] & \tilde{\iota}_{\alpha}(\zeta) 
\end{tikzcd}
\end{equation}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behavior in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item thimble projection formula
\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
\item in the examples, $\hat{\varphi}_\alpha(\zeta)$ turn out be an hypergeometric function of type ${}_pF_{p-1}$ where $p$ is the number of critical values. 
\item We expect that hypergeometric functions play a special role in resurgence theory as they may always appear when there are only finitely many singularities.
\item \textcolor{magenta}{maybe we can say more about algebraic hypergeometric functions}
\end{itemize}
%\item Recall Watson condition (old): Let $R_N$ be the difference between a function and the partial sum
%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
%over all orders $N$ and all $z$ in a wide enough wedge around infinity.
\end{itemize}
\end{itemize}

\color{orange}
\subsection*{Outline}

\textbf{Title: Borel regularity and Resurgence of Exponential Integrals}

\begin{enumerate}
\item introduction
\begin{itemize}
\item Exponential integrals
\begin{itemize}
\item they are function of $z$ and they are defined from the data of $(X,f)$ and $[\mathcal{C}], [\nu]$
\item the choice of the path $\mathcal{C}$: 
\begin{itemize}
\item $\mathcal{C}\in H^{B,z}_{n}(X,f)$
\item Witten's formalism, $\mathcal{C}$ is a Lefschetz thimbles (or steepest descendent path)
\end{itemize}
\item they define a paring between the relative homology (rapid decaying homology)$H^{B,z}_{\bullet}(X,f)$ and the twisted de Rham cohomology  $H_{dR,z}^{\bullet}(X,f)$
\begin{itemize}
\item there is a comparison isomorphism (Maxim)
\end{itemize}
\item varying $z$ we have the Stokes phenomena
\item as $z\to\infty$, the asymptotic expansion of $I$ is a divergent series $\tilde{I}$, usually of Gevrey-class
\begin{itemize}
\item {\it exact resurgence relation} (Berry--Howls): divergence encodes contributions from other critical values
\item it is an example of resurgent series (\'Ecalle)
\item $\tilde{I}$ is resurgent in $\C\setminus\lbrace \text{poles of } \nu\,, \text{cirtical values of } f\rbrace$
\item it is a toy example of resurgent series because there are only finitely many singularities in the Borel plane
\item we have to compute the \textbf{Stokes constants} relative to the singular points in $B$ to fully understand $B$. There are two methods to compute Stokes constants: $\bullet$ geometric: using intersection theory of thimbles (Picard--Lefschtez, Witten, Maxim), $\bullet$ analytic: using \'Ecalle formalism   
\end{itemize} 
\end{itemize}
\item what are exponential integrals? \textcolor{gray}{has to be done}
\begin{itemize}
\item motivation
\begin{itemize}
\item In the classical theory of special functions, exponential integrals are often used to express solutions of linear differential and difference equations.
\item In physics ??
\item Geometrically they represent a Poincar\'e pairing (as explained by Kontsevich in \textbf{IHES lectures}).
\end{itemize}
\end{itemize}
\item What is the class of ODEs that we study? \textcolor{gray}{has to be done}
\item State results about resurgence of exponential integrals and Stokes phenomena
\begin{itemize}
\item Thimbles integrals [Kontsevich]: geometric computation of Stokes constants \textcolor{gray}{has to be done}
\item ODE and fractional derivative formula [{\tt draft2}]
\item if hypergeometric functions appear in a large class of examples: integral formulas for hypergeometric functions \textcolor{gray}{has to be done}
\end{itemize}
\end{itemize}
\item Formalism for Laplace transform [{\tt draft2}, ``The geometry of the Laplace transform'']
\begin{enumerate}
\item Analytic
\begin{enumerate}
\item Introduction
\item Brief revew of translation surfaces (we can refer to this from the introduction if we need to)
\item The Laplace transform of a holomorphic function
\begin{enumerate}
\item Over an ordinary point
\item Over a branch point
\item Differential equation
\end{enumerate}
\item Relating differential equations in the frequency domain to integral equations in the position domain
\end{enumerate}
\item Formal
\begin{enumerate}
\item Laplace transform of a formal series
\item Borel transform
\item Relating differential equations in the frequency variable to integral equations in the position variable
\end{enumerate}
\end{enumerate}
\item Review of integral equations
\begin{itemize}
\item Existence of solutions
\item Fractional integrals and derivatives
\item Going between integral and differential equations (slight functions)
\end{itemize}
\item General cases
\begin{enumerate}
\item Borel regularity
\begin{itemize}
\item General ODE of the form
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \Phi = 0, \]
where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function~\text[see {\tt airy-resurgence} and written notes]
\begin{itemize}
\color{DarkCyan}
\item More generally, for $P$ of degree $n$, we should be able to handle
\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R_2\big(\tfrac{\partial}{\partial z}\big) + \ldots + z^{-(n-1)} R_{n-1}\big(\tfrac{\partial}{\partial z}\big) + z^{-n} R(z^{-1}) \right] \Phi = 0, \]
where $R_k$ has degree $n-k$. \textcolor{gray}{has to be done}
\begin{itemize}
\item We want the most general ODE with a regular singularity at $z = 0$ and its only other singularity, typically irregular, at $z = \infty$. \textcolor{gray}{has to be done}
\item The singularity at $\infty$ should only be regular for an Euler equation. \textcolor{gray}{has to be done}
\end{itemize}
\color{orange}
\item Show that we can find a slight solution at each critical value.
\item Show that $\hat{\iota} = \tilde{\iota}$, where:
\begin{itemize}
\item $I = \laplace \iota$
\item $\hat{\iota}$ is the Taylor expansion of $\iota$
\item $\tilde{I}$ is the asymptotic series of $I$
\item $\tilde{\iota} = \borel \tilde{I}$
\item Idea: Show that $\hat{\iota}$ and $\tilde{\iota}$ have matching asymptotics at $\zeta = 0$. Since they both satisfy the position-domain integral equation, they must coincide.
\end{itemize}
\end{itemize}
\item General thimble integral (conditions?)
\begin{itemize}
\item Proof of Borel regularity
\item $3/2$-derivative formula
\item thimble projection reasoning
\end{itemize}
\end{itemize}
\item Resurgence
\begin{itemize}
\item Explain how Borel regularity relates resurgence of formal series to resurgence of holomorphic functions in the position domain. \textcolor{gray}{think more about what we're trying to say here}
\item Relate to \'Ecalle's formalism and the alien derivative
\item Stokes factors
\begin{itemize}
\item For ODEs
\item For thimble integrals
\end{itemize}
\end{itemize}
\end{enumerate}
\item Examples \textcolor{gray}{make sure each example contains a computation of the Borel transform, so we can see it matches}
\begin{enumerate}
\item The Airy example
\begin{itemize}
\item $I(z)$ is a solution of a linear ODE. We explicitly find its Borel transform, knowing the nature of singularities and the asymptotic behaviour of a basis of solution for the ODE  [{\tt airy-resurgence}]
\item Compute Stokes constants
\begin{itemize}
\item Using thimble projection formula and Borel transform computation [{\tt draft2}]
\item Using Picard-Lefschetz theory (Pham, Kontsevich, etc.)
\end{itemize}
\item Comparison with the literature \textcolor{gray}{has to be done}
\begin{itemize}
\item Mari\~{n}o
\item Sauzin
\item Kontsevich slides
\item Kawai--Takei? [might take too long to understand well enough]
\end{itemize}
\end{itemize}
\item The Airy--Lucas examples
\begin{itemize}
\item Compute Borel transform [{\tt airy-resurgence}]
\item Compute Stokes constants \textcolor{gray}{has to be done}
\end{itemize}
\item Bessel 0 (it is different because we have infinite cover)
\begin{itemize}
\item Compute Stokes constants [{\tt draft2}]
\end{itemize}
\item Bessel $\mu$ (follows from Bessel 0)
\begin{itemize}
\item Compute Stokes constants [{\tt modified Bessel}]
\end{itemize}
\item The generalized Airy example
\item The vibrating beam example
\begin{itemize}
\item In addition to the simple example, maybe we can do an example where the equation on the spatial domain includes fractional integrals since Andy is interested in that sort of thing
\end{itemize}
\end{enumerate}
\end{enumerate}

\subsection{Why Borel regularity works for thimble integrals}
\color{DarkBlue}
\begin{itemize}
%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
%\begin{itemize}
%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
%\end{itemize} 
\item background: Pham studied the asymptotic behaviour of thimble integrals and we may interpret his result as a prof of Borel regularity in the algebraic setting, namely assuming $f$ a polynomial with distinct critical points (not necessary non--degenerate), $X=\C^N$, $\nu=g(x)dx_1\wedge...\wedge dx_N$ with $g(x)$ a polynomial. His proof uses microlocal analysis and classical results due to Varchenko. In the same algebraic setting, Malgrange states the Borel regularity result \cite[Theorem 6]{Malgrange22} 
\item \textcolor{red}{We give an explicit proof of Borel regularity beyond the polynomial case. Indeed I think we can simply assume $f$ holomorphic and proper.}
\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
%\begin{equation}
%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
%\end{equation}

%then the following diagram is commutative
%\begin{equation}
%\begin{tikzcd}
%I_{\alpha}(z) \arrow[r,"\aexp^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
%& \\
%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
%\end{tikzcd}
%\end{equation}
\begin{itemize}
%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
\item A corollary of [Thm 4] is the thimble projection formula.
\item \textcolor{red}{As a consequence of Thm 2.4 Pham}, if $f$ and $\nu$ are algebraic, we get that $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities 
\begin{equation}
mmm
\end{equation} 
\end{itemize}
\item \text{[Cor]:} combining our result and the result of Maxim [IHES lectures] (generalizing Pham) we can deduce that Stokes constants for the Borel--Laplace sum of $\tilde{I}_j(z)$ are always integers as they are intersection numbers (use same argument of Maxim). See also the argument of KS21 sec 6.2 in the framework of analytic WCFs. 
\begin{itemize}
\item Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C) 
\end{itemize}
\end{itemize}
\color{black}

\bibliographystyle{utphys}
\bibliography{airy-resurgence}
\end{document}

### 2023-11-07 exp-resurgence.tex
Typos correction, working on Section  A.5, change notations work on general organization

@@
 \item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
-This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
+Being Gevrey implies that the Borel transform is convergent, not that we can analytically continue it]}
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.
-\textbf{[Should we be allowed to take the Laplace transform at another points $b \in B$ instead?]}
+This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we're allowed to take the Laplace transform at another point $b \in B$.
+This would be natural in our study of ODEs and thimble integrals.}
 \end{enumerate}
@@
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \cite{watson} that a function $F$ that vanishes at $\infty$ is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around $\infty$ (see Definition~\ref{def:unif-gevrey-asymp}).
+Watson showed a century ago \cite{watson} that a function $F$ that vanishes at infinity is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around infinity (see Definition~\ref{def:unif-gevrey-asymp}).
 
 Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches $\infty$---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
+These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
 \begin{center}
@@
 
-The form of $\mathcal{P}$ derives from Equation~2.2.3 \textcolor{orange}{(p.~105)} of \cite{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
+The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag.
+105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
 Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
@@
 Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We will give precise statements in the following section.
+We’ll give precise statements in the following section.
 
@@
 
-First of all we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, for ODEs, we can build an analytic frame of solutions with an explicit growth behaviour (see Theorem~\ref{thm1}), while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the spatial domain): on the one hand integral equations are more regular than differential equations.
+First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+Indeed, \textcolor{red}{for ODEs, we can build an analytic frame of solutions with an explicit growth behavior (see Theorem~\ref{thm1})}, while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
+
+Second of all, we want to explain why it is useful to work in the Borel plane (the position domain): on the one hand integral equations are more regular than differential equations.
 On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
@@
 \end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
 Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
@@
 labeled by the roots of $P$.
-This type of operators are the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j=f_{j,0}+f_{j,\star}$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and $f_{j,\star}\in\singexpalg{\tau_j}(\Omega_j)$ for an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
-In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}$.
-
-\begin{theorem}\label{thm1}
-    The holomoprhic functions $\Psi_j$ are solutions of $\mathcal{P}\Psi_j=0$. In particular, they are a frame of analytic solutions.
+This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
+At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
+Our main result says they are actually proportional, hence proving Borel summation works.
+\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
+The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.  
 \end{theorem}
-
-At this point, we may ask what is the relationship between the two frame of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually the same, hence proving Borel summation works.
-
-\begin{theorem}\label{thm2}
-The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. 
-\end{theorem}
-
-In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
-
 In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
@@
 \begin{tikzcd}
-& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+& & \text{ODE }\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
 \Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & IE & & \\
+& & \text{IE} & & \\
 \psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
@@
 
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (Theorem \ref{thm1}).
-
+Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
 The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
@@
 In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
+therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
 Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
-
 As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
@@
 It can indeed be seen as a consequence of ``resurgence'' of the ODE.
-Our results show how to build a frame of solutions, analytically in the Borel plane.
-Furthermore, it shows we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of Theorem~\ref{thm1}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
+Our results of \cite{reg-sing-volterra} show how to build a frame of solutions, analytically in the Borel plane.
+Here, we show we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
+From the uniqueness result of \cite[Theorem~4]{reg-sing-volterra}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
 \end{remark}
@@
 \begin{remark}
-The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namley, drawing the red arrow of the diagram).
+The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namely, drawing the red arrow of the diagram).
 This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE.
@@
 \subsubsection{Why does Borel summation work for thimble integrals?}
-
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\mathbb{A}^1$ be a proper algebraic map with non--degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we will discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
-
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
 \[
-I(z):=\int_{\mathcal{C}}e^{-zf}\nu
+I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
 \]
-
-regarded as holomorphic functions in the frequency domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
-In fact, we introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ so that the function $I(z)$ will represent the Poincar\'e pairing.
-
-We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
-We follow \cite{pham} and \cite[Section 1]{Arnold}.
-Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
-\begin{align*}
-    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
-    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
-\end{align*}
-and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t.
-} \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}.
-Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$.
-This leads to further identifications:
-
-\begin{equation}
-    H_{*}^{B,z}\cong \bigoplus_{\alpha_i} H_{*}(B_j, B_j^+(\theta))
-\end{equation}
-where $B_j:=f^{-1}(B_r(\alpha_j))$ is the preimage of a small ball or radius $r$, containing only the critical value $\alpha_i$ and $B_j^+(\theta):=f^{-1}\left(B_r(\alpha_j)\cap \{ \Re (\zeta e^{i\theta})\geq r/2\}\right)$.
-Notice that we are not assuming $f$ to be Morse, hence $B_j$ may have different connected components.
-Then
-
-\begin{equation}
-    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
-     0 & \text{otherwise}
-    \end{cases}
-\end{equation}
-where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$ and $\mu_j$ is the Milnor number of the critical \textcolor{red}{point/value $a_j/\alpha_j$}.
-
-\begin{center}
-    \begin{tikzpicture}
-        \draw (2,2) circle (2);
-        \node[font=\tiny,red] at (1,1) {$\alpha_1$};
-        \draw (1,1.2) circle (0.4);
-        \node[font=\tiny,red] at (3,1.3) {$\alpha_2$};
-        \draw (3,1.5) circle (0.4);
-        \node[font=\tiny,red] at (2.3,3.2) {$\alpha_3$};
-        \draw (2.3,3.4) circle (0.4);
-        \node[above,red] at (1,1) {$\bullet$};
-        \node[above,red] at (3,1.3) {$\bullet$};
-        \node[above,red] at (2.3,3.2) {$\bullet$};
-        \draw[rounded corners] (2.7,1.76)--(2,2)--(1,3.71);
-        \draw[rounded corners] (1,1.6)--(0.5,2)--(1.2,2.5)--(1,3.71);
-        \draw[rounded corners] (1.9,3.4)--(1,3.71);
-        \node[font=\tiny, above] at (1,3.71) {$p_0$};
-        \node[font=\tiny, above] at (2.7,1.76) {$p_2$};
-        \node[font=\tiny, above] at (1,1.6) {$p_1$};
-        \node[font=\tiny, above] at (1.75,3.4) {$p_3$};
-    \end{tikzpicture}
-\end{center}
-
-From the classical theory of singularities \cite{Arnold} we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
-Moreover, the vanishing cycles can be identified with the so-called \textit{Lefschetz thimbles}: since we assumed critical points to be non--degenerate, in a neighborhood of $a_j$ there are local coordinates $x_1,...,x_N$ such that
-\[f=\alpha_j+\sum_{k=1}^N x_k^2\]
-
-and for $p=c e^{i\theta}\in\C$, the thimble $\Lambda_j(p)$ is defined by 
-\begin{align*}
-    \Im(x_1)=...=\Im(x_N)=0 \text{ and } \Re(e^{-i\theta/2}x_1)^2+....+\Re(e^{-i\theta/2}x_N)^2\leq c
-\end{align*}
-Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite[pag.10]{Witten}).
-
-Hence we deduce that $H_{z, N}^B$ admits a distinguished basis of Lefschetz thimbles labeled by critical points.
-
-Then we recall the definition of $H_{dR,z}^*$: it is the hypercohomolgy of the twisted de Rham complex
-
-\begin{equation*}
-    H_{dR,z}^*:=\mathbb{H}^*( \Omega^\bullet(X), zd+df)
-\end{equation*}
-where $(\Omega^\bullet(X), d)$ is the de Rham complex of differential forms on $X$.
-
-Therefore, the integral $I(z)$ can e regarded as the image of the following map:
-
-\begin{align*}
-    \int \colon  H_{z,N}^{B} \times & H_{dR,z}^N \to \C \\
-       [\mathcal{C}] ,\,\, & [\nu] \to \int_{\mathcal{C}}e^{-zf}\nu
-\end{align*}
-
-\textcolor{orange}{[the Betti--de Rham isomorphism is necessery?]}
-
-Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_j$, namely the integrals over Lefschetz thimbles labeled by the critical points $a_j\in\text{Crit}(f)$.
-
-As we let $z$ vary, we will observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$).
-The jumps can be described geometrically using the theory of Picard--Lefschetz.
-Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
-We will discuss this phenomena from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
-\textcolor{orange}{[Can we comment more about this?
-For instance as a consequence of Theorem 3.3]}
-
+regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
 Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
 
-Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$.
-
-These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
+Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.
+
+\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
 In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[Delabere \& Howls, Howls, Dingle]}.
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[ Howls]}.}
 
@@
 
-We will restrict to $1$-dimensional thimble integrals, and in this special case we will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
 The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-
 For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
@@
 \end{figure}
-
-%The {\em thimble integral}
-%\[ I_p = \int_{\Lambda_p} e^{-z f^*\zeta_p} \nu \]
-%is a holomorphic function on the right half-plane parametrized by $z$, and it turns out to be Borel regular.
-
 Then, our main result for thimble integrals is proving that $1$- dimensional thimble integrals are indeed Borel regular:
-
 \begin{theorem}[see Theorem \ref{thm:maxim}]
@@
 Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textbf{[Be careful about the orientation of $\Lambda_j$.]}
+\textcolor{magenta}{[Be careful about the orientation of $\Lambda_j$.]}
 \end{enumerate}
@@
 
-The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}):
+The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
 \[
@@
 \]
-
-on the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
+On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
 as the Laplace transform of a function $\iota_j$.
@@
    \end{equation*}
-
 In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\phi_j$ is the $1/2-$ derivative of $\iota_j$, \textcolor{orange}{hence it has simple singularities [it has to be verified]}.
@@
 
-%In higher-dimensional complex manifolds, integrals over Lefschetz thimbles \textcolor{red}{[I'm not so sure]} are still Borel regular~\textbf{[``Exponential integrals, Lefschetz thimbles and linear resurgence''][``Exponential Integral'' lectures?]}.
-This fact plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic}\textbf{[Delabere \& Howls, Howls, Dingle]}.
-
-%Choose a path $\gamma \maps \R \to X$ whose projection $f \circ \gamma$ starts out going leftward out of a puncture, ends up going rightward into a puncture, and never touches a critical value of $f$.
-Choose a translation coordinate $\zeta$ on $B$ and continue it along $f \circ \gamma$, noting that it may become multi-valued if $f \circ \gamma$ intersects itself.
-This data defines the {\em exponential integral}
-%\[ I = \int_\gamma e^{-z f^*\zeta} \nu, \]
-%a holomorphic function on the right half-plane parametrized by $z$.
-It turns out \textbf{[we hope]} that we can get $I$ by summing $e^{-\alpha_p z} I_p$ over various critical points---as long as none of the $\Gamma_p$ run into each other.
-\textbf{[We get jumps at phases where the $\Gamma_p$ do hit each other.]} The constants $\alpha_p$ are values of $\zeta$, continued to the critical points along certain paths.
-
 \subsubsection{Other results}
@@
 As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain.
 We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
@@
 \end{figure}
-
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
 The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}.
-In the Airy example (see Section \ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
+In the Airy example (see Section \ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
 Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.}
@@
 We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
+For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
 The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).
@@
 
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics as a powerful alternative to Borel summability.
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
 The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains a conjecture.
+For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC} \textcolor{red}{add reference to state integrals}) resurgence remains a conjecture.
 Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.
@@
 %\end{itemize}
+\subsection{Plan of the paper}
 
@@
 \subsubsection{Boundary}
-\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}
+\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
 
@@
 where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We will use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
+We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
 
@@
 \begin{itemize}
-\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+\item With respect to the flat metric, \textcolor{red}{$f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.}\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
 We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
@@
 \subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\ref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
+When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
 Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
 The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
-This amounts to substituting $w_b^n$ for $z$ in formula~\ref{laplace:int}.
+This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}.
 The half-plane $z \in H_{\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
@@
 
-Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$.
+Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
 Assume the $\Gamma_{\zeta,\alpha}^\theta$ is contained in $\Omega_\alpha$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namley of the form $|\zeta|^\sigma$.
+In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namely of the form $|\zeta|^\sigma$.
 When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta,\alpha}^\theta$ is a well--defined and holomorphic function for $\Re e^{-i\theta}z>0$ on the fiber $T^*B\vert_{\zeta=0}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
@@
 However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[\S 1.3]{mladenov2014advanced} \textbf{---original source Podlubny}).
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
 We'll use the {\em Riemann-Liouville} convention.
@@
 %Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
-In fact, as we will see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
+In fact, as we’ll see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
 
@@
 
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$:
+A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
 
@@
 \item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we will see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
+As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
 \item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
@@
 In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textbf{formal Laplace transform}.
-In addition, in Section \ref{convolution} we will prove that the Borel transform is an algebra isomoprhisms.
+The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textit{formal Laplace transform}.
+In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra isomoprhisms.
 
@@
 \begin{lemma}
-    Let $\alpha\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\alpha} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\alpha-1} \rbrace$, with inverse given by the formal Laplace transform.
+    Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\tau} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\tau-1} \rbrace$, with inverse given by the formal Laplace transform.
 \end{lemma}
@@
 \begin{align*}
-\borel_\zeta (z^{-\alpha}\tilde{\Phi})&=\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\alpha-1}}{\Gamma(\alpha)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\alpha}}{\Gamma(1+n+\alpha)}
-\end{align*}
-
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\alpha)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\alpha)|} \]
-which grows as $n(n+1)^{-\alpha} A^{n+1}$.
+\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
+\end{align*}
+
+and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
+which grows as $n(n+1)^{-\tau} A^{n+1}$.
 \begin{verify}
-    we use $\Gamma(n+1+\alpha)\sim \Gamma(n+1) (n+1)^\alpha$ as $n\to\infty$. 
+    we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
 \end{verify}
@@
 \begin{align*}
-\borel_\zeta (z^\alpha \tilde{\Phi})&=\borel_\zeta (z^\alpha)\ast \tilde{\phi}\\
-&=\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast\tilde{\phi}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\alpha-1}}{\Gamma(-\alpha)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\int_0^1(t\zeta)^{-\alpha-1}(\zeta-t\zeta)^k\zeta dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\int_0^1 t^{-\alpha-1}(1-t)^k dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\alpha)}\zeta^{k-\alpha}\frac{\Gamma(k+1)\Gamma(-\alpha)}{\Gamma(k-\alpha+1)}\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\alpha} \zeta^k \\
-&=\partial_\zeta^\alpha\tilde{\phi}
+\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \tilde{\phi}\\
+&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\tilde{\phi}\\
+&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\int_0^1(t\zeta)^{-\tau-1}(\zeta-t\zeta)^k\zeta dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\alpha}\int_0^1 t^{-\tau-1}(1-t)^k dt\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\tau}\frac{\Gamma(k+1)\Gamma(-\tau)}{\Gamma(k-\tau+1)}\\
+&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\tau} \zeta^k \\
+&=\partial_\zeta^\tau\tilde{\phi}
 \end{align*}
@@
 \begin{remark}
-We can express the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ as convolution products, and we will see how the definitions vary depending on the fibers of $T^*B$ in consideration.
+We can express the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
 
@@
 
-\color{black}
-
-\subsection{Differential equation}
-\textcolor{orange}{Should we keep this section?}
-If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
+%\subsection{Differential equation}
+%\textcolor{orange}{Should we keep this section?}
+%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
 In these coordinates, we can write down the partial differential operator
-\begin{equation}%%\label{laplace:op}
-\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-\end{equation}
-The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
+%\begin{equation}%%\label{laplace:op}
+%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
+%\end{equation}
+%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
+
+%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
 %\end{problem}
-The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
+%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
 \textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-\subsubsection{Order shifting}\label{shifting}
-\textcolor{orange}{[Veronica:I think we should move this section, maybe when we do examples]}
-Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.
-%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-%We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
-%\begin{equation}\label{eqn:slight-defn}
-%\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-%\end{equation}
-%where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-As we've seen in Section \ref{reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
-Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are holomorphic functions.
-\end{prop}
-%To prove this result, we'll need a little background.
-
-%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-%Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-
-\begin{proof}%[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-belongs to the function space $\singexpalg{\sigma}(\Omega)$.
-Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
-Hence, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
 
@@
 Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
-\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}
+\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}.
 \end{itemize}
@@
 \subsubsection{Main results}
-
-As a consequence of Theorem 4 in {\tt reg-volterra} we get
-
-\begin{theorem}\label{thm1-dim}
-In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-\begin{equation}\label{P-hat_j}
-\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
-\end{equation}
-such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
-\end{theorem}
+%As a consequence of Theorem 4 in {\tt reg-volterra} we get 
+%
+%\begin{theorem}\label{thm1-dim}
+%In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
+%\begin{equation}\label{P-hat_j}
+%\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
+%\end{equation}
+%such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
+%${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
+%\end{theorem}
 
@@
 \begin{itemize}
-\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$
+\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$.
 \item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
@@
 
-Step $(b)$ clearly follows from Theorem  \ref{thm1-dim} and step $(a)$.
-In fact, from step $(a)$ and Theorem \ref{thm1-dim}, $\Tilde{\psi}_j$ and ${\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
-Then, by Corollary \ref{thm1-dim} we can Laplace transform ${\psi}_j$ along a ray $\Gamma_{\alpha_j}^\theta$ in $\Omega_j$.
+Step $(b)$ clearly follows from \cite[Theorem 4]{reg-sing-volterra} and step $(a)$.
+In fact, $\Tilde{\psi}_j$ and ${\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+Then, we can Laplace transform ${\psi}_j$ along a ray $\Gamma_{\alpha_j}^\theta$ in $\Omega_j$.
 Hence if $\hat{\psi}_j$ denotes the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$, we can Laplace transform $\hat{\psi}_j$ along $\Gamma_{\alpha_j}^\theta$, too.
@@
 %\begin{proof}
- %   We will prove the following: 
+ %   We’ll prove the following: 
   %  \begin{itemize}
@@
 We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
-\textbf{[We should explicitly spell out and check the conditions that make this possible.
+\textcolor{magenta}{[We should explicitly spell out and check the conditions that make this possible.
 I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
@@
 \[ e^{\textcolor{magenta}{+}z f(\alpha_j)} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\Re z \to \infty$ \textbf{[see, for example, Miller's ``Applied Asymptotic Analysis,'' Proposition 2.1---the argument through equation~(2.9).]} Plugging in the Taylor series above, we get
+as $\Re z \to \infty$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)). Plugging in the Taylor series above, we get
 \begin{align*}
@@
 
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z f(\alpha_j)} I_\alpha(z)$.
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha_j} I_j(z)$.
 In other words,
-\[ e^{-z f(\alpha_j)} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\[ e^{-z \alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 To see why, cut the sum off after $N$ terms, and observe that
@@
 The right-hand side goes to $0$ as $\Re(z)$ grows.
-
 %Hence,
 %\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \textbf{[Chiani, Dardari, and Simon, ``New Exponential Bounds and Approximations
-for the Computation of Error Probability in
-Fading Channels,'' inequality~(5)]}, allowing the simpler estimate
-\[ e^{-zf(\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
+\[ e^{-z\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
 
@@
 \begin{align*}
-\nu & = \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{n/2}\,\frac{df}{[2(f - f(x_j))]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{(n - 1)/2}\,df,
+\nu & = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{n/2}\,\frac{df}{[2(f - f(a_j))]^{1/2}} \\
+& = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2}\,df,
 \end{align*}
@@
 \begin{align*}
-\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(x_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
+\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
 & = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
@@
 %Let $\tilde{\Phi}_j\in\C[\![z^{-1}]\!]$ be such that $\tilde{I}_j(z)=e^{-z\alpha_j}z^{-1/2}\tilde{\Phi}_j(z)$,  
-By the action of $\borel_\zeta$ on transseries (\S \ref{sec:action_transseries}) and the properties of convolution (\S \ref{convolution}) we know 
+By the action of $\borel_\zeta$ on transseries (Section \ref{sec:action_transseries}) and the properties of convolution (Section \ref{convolution}) we know 
 \begin{align*}
@@
 \end{align*}
-as we claimed. \textcolor{orange}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
+as we claimed. \textcolor{cyan}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
 
@@
     \includegraphics[scale=0.3]{figures/thimble_Airy.png}
-    \caption{\small The contour $\Gamma$ in the $u$ plane is represented by the light blue path.\textcolor{orange}{[explain what the regions indicate and what the color]}}
+    \caption{\small The contour $\Lambda_1$ in the $u$ plane is represented by the light blue path.
+More generally, the dark blue contour corresponds to the preimage of the ray $+1+e^{i\theta}\infty$ and $\theta=$.
+While the light blue contour corresponds to the preimage of the ray $-1+e^{i\theta}\infty$.
+The gray regions correspond to the preimage of $\Re \zeta> \textcolor{orange}{const}$.
+\textcolor{orange}{[for Aaron: could you please add the correct constant in the description of the figure, and explain what are the different colored regions?
+Thanks]}}
     \label{fig:path_Airy}
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Gamma} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Lambda_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
 
-By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we will go straight to the general case.
+By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we’ll go straight to the general case.
 However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
@@
    \includegraphics[scale=0.3]{figures/thimble-n5.png}
-    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.}
+    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.
+The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=$.
+While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
     \label{fig:thimble_n_5}
@@
 \end{equation}
-In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
+In fact, as we’ll see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
 
@@
 where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
-From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n}(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp-AL}
@@
 Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
+We’ll see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
 This is an evidence of Theorem~\ref{thm1-dim}.
@@
 We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
 
@@
 Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
+However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (0,1)$.
+
+This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of order $\sigma=1/2$ at each regular singular point.
 We can see the regular singularities by moving the derivatives to the right:
@@
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = \alpha$.
+For each root $\alpha_j$, we'll find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in Figure \ref{Fig:domain}.
 We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
 We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} V_j \]
+where $V_j = \laplace_{\zeta_j, 0} v_\alpha$ and $\zeta = \alpha_j + \zeta_j$.
+We can see from Section~\ref{reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} z^{-\tau_j} W_j, \]
+makes $W_j$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 %\color{Peru}
@@
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = 1$.
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_1)$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
@@
 \end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 0$:
 \begin{alignat*}{2}
@@
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is slight and locally integrable at $\zeta = -1$.
+Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$.
 In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 1$:
 \begin{alignat*}{2}
@@
 The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$.
+The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_j\in\singexpalg{1/2}(\Omega_j)$.
 \color{DarkTurquoise}
 \begin{quote}
-We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
 Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
 \begin{align*}
-v_\alpha' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ is bounded near } \zeta_\alpha = 0 \\
-& \Longrightarrow \zeta_\alpha^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longleftrightarrow v_\alpha' \in o\big(\zeta_\alpha^{\tau-1}\big).
+v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
+& \Longrightarrow \zeta_j^\epsilon\,\zeta_j^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
+& \Longrightarrow \zeta_j^{1-\tau}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
+& \Longrightarrow v_j' / \zeta_j^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
+& \Longleftrightarrow v_j' \in o\big(\zeta_j^{\tau-1}\big).
 \end{align*}
@@
 The Poincar\'{e} algorithm, as we saw in Section~\ref{sec:asympt-AL}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_\alpha \in \C\llbracket z^{-1} \rrbracket$.
+The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket$.
 We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
 
-The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation~\textcolor{magenta}{[prove or cite]}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$ for $\alpha = 1$ and $\alpha = -1$, respectively.
+The Borel transform maps $e^{-\alpha_j z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
+Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
+Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ for $\alpha = 1$ and $\alpha = -1$, respectively.
 
 When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}.
-It therefore has exactly one solution in $\zeta_\alpha^{-1/2} + o\big(\zeta_\alpha^{-1/2}\big)$, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
+It therefore has exactly one solution in $\singexpalg{1/2}$, up to scaling.
+That means $\borel\big[ e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j \big]$ must sum to a scalar multiple of $v_j$.
+Thus, if $e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha_j} v_j$.
 
@@
 Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
+In fact, with the thimble projection reasoning, there is no ambiguity in the choice of the multiplicative constant.
 
@@
 
-\subsubsection{Thimble projection technique for Airy-Lucas functions}\label{contour-argument-AL}
+\subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
 \textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
-
+We follow the reasoning of the proof of Theorem~\ref{thm:maxim}.
 We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]} \textcolor{DarkCyan}{[see identity in \texttt{cyl-resurgence.tex}]}
+Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]}
+
 \begin{align*}%%\label{integral:mod-bessel-rational-zeta}
@@
 \includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane.}
+{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane, slightly off from the critical value $\zeta=1$.}
 \end{center}
@@
 
-\subsubsection{A flavour of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
+\subsubsection{A flavor of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
 
 In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (\S\ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (\S\ref{contour-argument-AL}).
-Up to a constant, in both cases we find
-
+In both cases we find
 \begin{align*}
@@
 \end{align*}
-
 which has a fractional power singularity at $\zeta=1$.
@@
 Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
-
 \begin{align*}
@@
 \end{align*}
-
 Hence, we deduce  
@@
 \end{equation}
-
 namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
-This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI}\cite{EcalleII}\cite{EcalleIII}\footnote{If the reader is interesting in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i}\cite{Dorigoni}\cite{aniceto2019primer}.}.
-Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
+This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.
+Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
 The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
@@
 We can repeat the same reasoning with $v_{-1}$:
-
 \begin{align*}
@@
 \end{align*}
-
 and ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ is singular at $\zeta=1$. Hence
-
 \begin{align*}
@@
 \end{align*}
-
 and the analogue of \eqref{resurgent-relation-1} is 
@@
 \end{equation}
-
 Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are a manifestation of the Stokes phenomena, already in the position domain.
@@
 In our example:
-
 \begin{align*}
@@
 \end{align*}
-
 thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$\footnote{If we think of the Laplace transforms of $v_1$ and $v_{-1}$ as a frame of solutions for the Airy--Lucas differential equation, the equations above define the so-called Stokes matrices for the ODE.}.
@@
 It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pair of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Figure \ref{fig:intersection_thimbles}.
-However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on a lift of a path in the position domain.
+However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
 \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
@@
 The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
-
 \begin{equation}\label{eqn:mod-bessel}
@@
 \end{equation}
-
 and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf} \textcolor{red}{10 \cite{watson1922treatise}}) 
-
 \begin{align*}
@@
 \end{align*} 
-
 where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ (see Figure \ref{fig:Omega_path}).
-
 \begin{figure}[ht]
@@
 \end{figure}
-
 On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results: 
-
 \begin{itemize}
@@
 
-The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
+The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we’ll discuss in the following Section~\ref{countable-cover}.
 
@@
 \end{equation} 
-
 and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
@@
 The critical points of $f$ are $\alpha_{\pm}:=\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
-
 \begin{equation}
@@
 \end{equation}
-
 where $\Lambda_{\pm}$ are the paths through the points $\alpha_\pm$, starting and ending at infinity (as in Figure \ref{fig:path-generalized-Airy-Lambda+-}).
-
 \begin{figure}
@@
 \end{figure}
-
 In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$: 
-
 \begin{align*}
@@
 \end{align*}
-
 It follows that $I_+(z)$ is a solution of
-
 \begin{equation}\label{eq:I}
@@
 \end{equation}
-
 From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combination of three generators 
@@
 \end{equation}
-
 where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
-
 \begin{multline}\label{w1}
@@
 \end{multline}
-
 \begin{multline}\label{w2}
@@
 \end{multline}
-
 \begin{multline}\label{w3}
@@
 \end{multline}
-
 Let us first study equation \eqref{w1}: its Borel transform is
-
 \begin{multline*}
@@
 \end{multline*}
-
 We differentiate three times, getting 
-
 \begin{multline*}
@@
 \end{multline*}
-
 we set $y=\zeta^2$
-
 %\begin{multline}
@@
 \end{multline}
-
 which is a generalized hypergeometric equation  \cite[Equation 16.8.5]{dlmf} with parameters
-
 \begin{align*}
@@
 \end{align*}
-
 therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$. 
-
 Then we look at equation \eqref{w2}: its Borel transform is
-
 \begin{multline}
@@
 \end{multline} 
-
 and taking three derivatives it simplifies to 
-
 \begin{multline}
@@
 \end{multline}
-
 define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
-
 \begin{multline}\label{eq1}
@@
 \end{multline}
-
 which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
-
 \begin{multline}
@@
 hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
-
 \begin{align*}
@@
 \end{align*}
-
 and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
 The equation \eqref{w3} differs from \eqref{w2} for few signs: we find that its Borel transform is
-
 \begin{multline}
@@
 \end{multline}
-
 and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
@@
 In particular,
-
 \begin{equation}
@@
 \end{equation}
-
 \textcolor{orange}{we may try to do the computations of Stokes constants for $p=1$, when $\hat{w}_1$ simplifies to a Gauss hypergeometric.
@@
 Check change of coordinates $y=\zeta^2$.}
-
 \subsubsection{Thimble projection formula}
-
 In Theorem \ref{thm:maxim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral. 
-
 \subsection{Third-order thimble integrals}
-
 Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
@@
 \footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}
-
 Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:
-
 \begin{itemize}
@@
 \end{itemize}
-
 In particular, we can always reduce to study the thimble integral in simpler situations. 
-
 As an example, every degree three polynomial with distinct critical points can be transformed in the Chebyshev polynomial $T_3(t)=4 t^3-3t$, implying that the thimble integral $I_+$ can be transformed into the Airy--Lucas integral with parameter $m=1, n=3$.
 This follows by post-composing $f$ with a translation of $-q$ followed by a scaling-rotation of $\frac{ -i 3^{3/2}}{2 p^{3/2}}$
-
 \begin{align*}
@@
 \end{align*}
-
 with $t= \sqrt{-\frac{3}{p}} \frac{u}{2}$. Then the thimble integral $I_+$ gets transformed into 
-
 \begin{align*}
@@
 \end{align*}
-
 In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
-%In both cases, we will compute the differential equation satisfied by $I$.
+%In both cases, we’ll compute the differential equation satisfied by $I$.
 
@@
 %\end{equation*}
-
 We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.
-
 First, notice that $I(z)$ solves
@@
        \end{equation}
-
-and we can find a Borel regular solution following the argument of \S \ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
-
+and we can find a Borel regular solution following the argument of Section~\ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
 \begin{align*}
@@
 \end{align*}
-
 namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
@@
 The result is confirmed by the thimble projection reasoning which in this simple case reads
-
 \begin{align*}
@@
 \end{align*}
-
 where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin.
@@
 \begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Gamma} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-and the contour $\Gamma$ is represented in Figure \ref{fig:path_Airy}.
+K(z) = i\sqrt{3} \int_{z^{-1/3}\Lambda_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+and the contour $\Lambda_1$ is represented in Figure \ref{fig:path_Airy}.
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
@@
 In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-
 %The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
@@
 \end{equation}
-
 The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
@@
 Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm1-dim}.
+We’ll see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
+This is an evidence of \cite[Theorem~4]{reg-sing-volterra}.
 
@@
 %\subsubsection{The big idea}\label{big-idea}
-We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+We are going to look for functions $v_j$ whose Laplace transforms $\laplace_{\zeta, \alpha_j} v_j$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
+We’ll succeed when $\alpha^2 - 1 = 0$, and we’ll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
 
@@
 \end{equation}
-
 It's tempting to differentiate both sides of this equation until we get
@@
 \[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we’ll see this approach succeed.
 For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
@@
 In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
-
 %\color{DodgerBlue}
@@
 Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
-
 \begin{equation}
@@
 %\end{align*}
-
 Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$ 
-
 \begin{align*}
@@
 \end{align*}
-
 Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
@@
 Similarly, if we consider the formal power series
-
 \begin{equation}
@@
 \end{equation}
-
 analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-
 \subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
 Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Gamma$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/3} \Gamma$, we have
+Projecting $z^{-1/3} \Lambda_1$ to a contour $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \Lambda_1$, we have
 \begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\gamma_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs clockwise around $[1, \infty)$, as shown below.
+K = \frac{i}{\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
+\end{equation}
+For $z \in (0, \infty)$, the contour $\mathcal{H}^1_z$ runs clockwise around $[1, \infty)$, as shown below.
 Let's assume $z \in (0, \infty)$ for the rest of the section.
@@
 \includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ in the $\zeta$ plane.}
+{\small The contour $\mathcal{H}^1_z$ in the $\zeta$ plane.}
 \end{center}
-
 From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
@@
 so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
+\[ K = \frac{1}{i\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
 This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
@@
 so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\gamma_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
+\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
 The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
@@
 \end{align*}
-just as we found in Section~\ref{bessel-regularity}.
-\subsection{Another solution}
+just as we found in Section~\ref{bessel-regularity}. However, in this case, we get an exact equality (compared to the proportionality of Section~\ref{bessel-regularity}). 
+\subsubsection{Another solution}
 Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
@@
 The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\eqref{eqn:reg-mod-bessel}.
-
 To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
@@
 
-In an Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (\S \ref{contour-argument-AL}) or apply the thimble projection formula \eqref{formula1} \textcolor{red}{\footnote{We have this done in \texttt{draft2}, but we'll probably leave it out of the article}} using trigonometric substitution.
+In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula~\eqref{formula1} using trigonometric substitution.
 As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time applying the thimble projection formula to the generalized Cardano's formula.
@@
 Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
-
-\begin{equation}
-    u=????
-\end{equation}
-
-\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of magnitude of function on position domain]}
+\begin{align*}
+    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
+    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
+\end{align*}
+\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
+\subsubsection{An eye on resurgence}
 
@@
 
-\section{Application of the integral formula}
+\section{Application of the projection formula}
 
@@
 When computed from the ODE, there is an ambiguity in the choice of the constant, while with the thimble projection reasoning and the thimble projection formula the ambiguity is solved.
-We will see this for the modified Bessel equation.
+We’ll see this for the modified Bessel equation.
 
@@
 Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
-%In order to compute the Stokes constants we will first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
+%In order to compute the Stokes constants we’ll first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
 \begin{lemma}\label{claim 2}
@@
 \color{black}
+\section{Geometry of thimble integrals}
+
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
+\[
+I(z):=\int_{\mathcal{C}}e^{-zf}\nu
+\]
+regarded as holomorphic functions on the frequency domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
+In fact, we'll introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ for which the function $I(z)$ will represent the Poincar\'e pairing.
+
+We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
+We follow \cite{pham} and \cite[Section 1]{Arnold}.
+Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
+\begin{align*}
+    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
+    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
+\end{align*}
+and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t.
+} \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}.
+Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$.
+This leads to further identifications:
+
+\begin{equation}
+    H_{*}^{B,z}\cong \bigoplus_{\alpha_i} H_{*}(B_j, B_j^+(\theta))
+\end{equation}
+where $B_j:=f^{-1}(B_r(\alpha_j))$ is the preimage of a small ball or radius $r$, containing only the critical value $\alpha_i$ and $B_j^+(\theta):=f^{-1}\left(B_r(\alpha_j)\cap \{ \Re (\zeta e^{i\theta})\geq r/2\}\right)$.
+Notice that we are not assuming $f$ to be Morse, hence $B_j$ may have different connected components.
+Then
+
+\begin{equation}
+    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
+     0 & \text{otherwise}
+    \end{cases}
+\end{equation}
+where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$, and $\mu_j$ is a number in $\{\textcolor{magenta}{???}\}$ called the {\em Milnor number} of the critical \textcolor{red}{point/value $a_j/\alpha_j$}.
+
+\begin{center}
+    \begin{tikzpicture}
+        \draw (2,2) circle (2);
+        \node[font=\tiny,red] at (1,1) {$\alpha_1$};
+        \draw (1,1.2) circle (0.4);
+        \node[font=\tiny,red] at (3,1.3) {$\alpha_2$};
+        \draw (3,1.5) circle (0.4);
+        \node[font=\tiny,red] at (2.3,3.2) {$\alpha_3$};
+        \draw (2.3,3.4) circle (0.4);
+        \node[above,red] at (1,1) {$\bullet$};
+        \node[above,red] at (3,1.3) {$\bullet$};
+        \node[above,red] at (2.3,3.2) {$\bullet$};
+        \draw[rounded corners] (2.7,1.76)--(2,2)--(1,3.71);
+        \draw[rounded corners] (1,1.6)--(0.5,2)--(1.2,2.5)--(1,3.71);
+        \draw[rounded corners] (1.9,3.4)--(1,3.71);
+        \node[font=\tiny, above] at (1,3.71) {$p_0$};
+        \node[font=\tiny, above] at (2.7,1.76) {$p_2$};
+        \node[font=\tiny, above] at (1,1.6) {$p_1$};
+        \node[font=\tiny, above] at (1.75,3.4) {$p_3$};
+    \end{tikzpicture}
+\end{center}
+
+From the classical theory of singularities \cite[\textcolor{magenta}{add section; move to end of sentence}]{Arnold}, we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
+Each vanishing cycle is represented by the boundary of a so-called \textit{Lefschetz thimble}: since we assumed critical points to be non--degenerate, in a neighborhood of $a_j$ there are local coordinates $x_1,...,x_N$ such that
+\[f=\alpha_j+\sum_{k=1}^N x_k^2\]
+
+and for $p=c e^{i\theta}\in\C$, the thimble $\Lambda_j(p)$ is defined by 
+\begin{align*}
+    \Im(x_1)=...=\Im(x_N)=0 \text{ and } \Re(e^{-i\theta/2}x_1)^2+....+\Re(e^{-i\theta/2}x_N)^2\leq c
+\end{align*}
+Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite[page~10]{Witten}).
+
+Hence we deduce that $H_{z, N}^B$ admits a distinguished basis of Lefschetz thimbles labeled by critical points.
+
+Then we recall the definition of $H_{dR,z}^*$: it is the hypercohomolgy of the twisted de Rham complex
+
+\begin{equation*}
+    H_{dR,z}^*:=\mathbb{H}^*( \Omega^\bullet(X), zd+df)
+\end{equation*}
+where $(\Omega^\bullet(X), d)$ is the de Rham complex of differential forms on $X$.
+
+Therefore, the integral $I(z)$ can e regarded as the image of the following map:
+
+\begin{align*}
+    \int \colon  H_{z,N}^{B} \times & H_{dR,z}^N \to \C \\
+       [\mathcal{C}] ,\,\, & [\nu] \to \int_{\mathcal{C}}e^{-zf}\nu
+\end{align*}
+
+\textcolor{orange}{[the Betti--de Rham isomorphism is necessary?]}
+
+Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_j$, namely the integrals over Lefschetz thimbles labeled by the critical points $a_j\in\text{Crit}(f)$.
+
+As we let $z$ vary, we’ll observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$).
+The jumps can be described geometrically using the theory of Picard--Lefschetz.
+Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
+We’ll discuss this phenomenon from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
+\textcolor{orange}{[Can we comment more about this?
+For instance as a consequence of Theorem 3.3]}
+
+\section{Generalities about ODEs and Integral Equations}
+\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
+
+\subsubsection{Order shifting}\label{shifting}
+Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.
+%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
+%We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
+%\begin{equation}\label{eqn:slight-defn}
+%\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
+%\end{equation}
+%where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
+As we've seen in Section \ref{reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
+This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
+In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
+\begin{prop}\label{prop:shifting}
+Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+if and only if
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+where $h_n, \ldots, h_{-m}$ are holomorphic functions.
+\end{prop}
+%To prove this result, we'll need a little background.
+
+%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
+The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
+If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
+A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
+
+%Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
+Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
+Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
+Each basic operation has a simple effect on a slight function's order.
+Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
+Differentiation and integration add $-1$ and $1$, respectively.
+
+\begin{proof}%[Proof of Proposition~\ref{prop:shifting}]
+The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
+
+To prove the forward implication, rewrite the first equation in the statement as
+\begin{equation}\label{eqn:diff-int-split}
+\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
+\end{equation}
+The function
+\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
+belongs to the function space $\singexpalg{\sigma}(\Omega)$.
+Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
+Hence, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
+
+Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
+Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
+\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
+which rearranges to the second equation in the statement.
+\end{proof}
+
 \newpage

### 2023-11-07 exp-resurgence.tex
Removed two comments

@@
     \begin{itemize}
-    \item Replace formalism in Section~\label{reg-decay}
+    \item Replace formalism in Section~\ref{reg-decay}
     \end{itemize}
@@
 The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
+%\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
 Hopefully it wouldn't be too hard, but it would be a pain.]}
@@
 \item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.%\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
 Being Gevrey implies that the Borel transform is convergent, not that we can analytically continue it]}
@@
 First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, \textcolor{red}{for ODEs, we can build an analytic frame of solutions with an explicit growth behavior (see Theorem~\ref{thm1})}, while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
+Indeed, \textcolor{red}{for ODEs, we can build an analytic frame of solutions with an explicit growth behavior (see \cite[Theorem~4]{reg-sing-volterra})}, while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
 
@@
 We’ll see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~\ref{thm1-dim}.
+This is an evidence of Theorem~4 from \cite{reg-sing-volterra}.
 %\subsection{Going to the spatial domain}\label{spatial-AL}

### 2023-11-07 exp-resurgence.tex
add pictures intersection thimbles

@@
 In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence}\textbf{[ Howls]}.}
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.}
 
@@
 
+\begin{remark}
+    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the Borel transform of $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
+Furthermore, expanding $\hat{\phi}_j$ at its critical points we recover the germs $\series{\phi}_k$ for $k\neq j$.
+This is an instance of resurgence, indeed according to the theory of Ecalle, $\hat{\phi}_j$ are all resurgent functions.
+We'll see an example in Section~\ref{sec:eye-res-airy}.
+\end{remark}
+
 \section{Examples}\label{sec:examples}
@@
     \centering
-    %\includegraphics{}
+    \includegraphics[scale=0.45]{figures/contour1-AL4--12.jpg}
+    \includegraphics[scale=0.45]{figures/contour2-AL4--12.jpg}
+    \includegraphics[scale=0.45]{figures/contour--AL4--12--inter.jpg}
+    \includegraphics[scale=0.45]{figures/contour1-AL5--12.jpg}
+    \includegraphics[scale=0.45]{figures/contour2-AL5--12.jpg}
+    \includegraphics[scale=0.45]{figures/contour--AL5--12--inter.jpg}
     \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$.
@@
 \textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
-\subsubsection{An eye on resurgence}
+\subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
+Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behaviour near the singular points.
+A prototypical class of resurgent functions is the so-called simple resurgent functions, namely analytic function $\hat{\phi}$ with singularities $\omega$ such that
+\begin{align*}
+    \hat{\phi}(\zeta-\omega)=\frac{S_\omega}{2\pi i} \log(\zeta) \series{\phi}_\omega(\zeta) + \text{ hol. funct.}
+\end{align*}
+where $S_\omega$ is a constant, typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
+The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
+The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$  
+Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent functions.
+Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.
+Hence the set of singularities is given by the critical values of $f$.
+Since $f$ has finitely many critical values, we can
 
@@
 
+\subsection{Picard--Lefschetz formula in pictures}
+We'll compute the Picard--Lefschetz formula as intersection of the base of thimbles and its dual, relative the singular direction $\theta=0$.
+We'll do it graphically, by plotting the steepest decent contours center at the critical points of $f$.
+We'll consider the example of Airy and Airy--Lucas with $n=4$.
+
+For the classical Airy function, we have a two dimensional base of thimbles, thus we have to compute only one intersection:
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.7]{figures/contour1--airy.jpg}
+    \includegraphics[scale=0.7]{figures/contour2--airy.jpg}
+     \includegraphics[scale=0.7]{figures/contour--Airy--intersection.jpg}
+    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$.
+With respect to the Stokes line $\theta=0$, we choose $\theta=0.1$ for the picture on the left and $\theta=-0.1+\pi$ for the picture in the center.
+The picture on the right shows the intersection of the thimbles which is given by a single point.
+Thus up to normalization, the Stokes constant is $1$.
+The images were obtained with Mathematica, and the thimbles are computed as the steepest descent contours from the critical points.}
+    \label{fig:intersection_thimbles-Airy}
+\end{figure}
+We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{sec:eye-res-airy}.
+
+For Airy--Lucas with parameter $n=4$, we have a three dimensional base of thimbles, graphically represented as 
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.35]{figures/thimble-n4.png}
+    \caption{Caption}
+    \label{fig:thimble-n4}
+\end{figure}
+Then computing intersections of dual pairs of thimbles we get 
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.4]{figures/contour1-AL4--12.jpg}
+    \includegraphics[scale=0.4]{figures/contour2-AL4--12.jpg}
+     \includegraphics[scale=0.4]{figures/contour--AL4--12--inter.jpg}
+     \includegraphics[scale=0.4]{figures/contour1-AL4--13.jpg}
+    \includegraphics[scale=0.4]{figures/contour2-AL4--13.jpg}
+     \includegraphics[scale=0.4]{figures/contour--AL4--13--inter.jpg}
+     \includegraphics[scale=0.4]{figures/contour1-AL4--32.jpg}
+    \includegraphics[scale=0.4]{figures/contour2-AL4--32.jpg}
+     \includegraphics[scale=0.4]{figures/contour--AL4--32--inter.jpg}
+    \caption{First line computes the intersection of $\Lambda_1$ and $\Lambda_2$.
+Second line computed the interaction of $\Lambda_3$ and $\Lambda_2$.
+Third line computed the intersection of $\Lambda_3$ and $\Lambda_1$.}
+    \label{fig:intersection_thimbles-AL4}
+\end{figure}
+Notice that $\Lambda_1$ and $\Lambda_3$ do not intersect as they are in the same class, because they are preimages of the same rays through infinity.   
 \section{Generalities about ODEs and Integral Equations}

### 2023-11-08 draft2.tex
Start turning motivation section into prose
Sketch out I_{1/3} integral example. Mark typo in Borel regularity
argument for exponential integrals.
Appendix B moved to draf2.tex part of the content of Appedix B is now in thimble proj formula for Airy.

@@
 By the steepest descent method,
-\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{\textcolor{magenta}{+}z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 as $z \to \infty$. \textbf{[I need to learn how this works! Do we get asymptoticity at all orders? ---Aaron]} Plugging in the Taylor series above, we get
@@
 
+\section{Application of the projection formula}
+
+In Section \ref{sec:examples}, we computed the Borel transform of the asymptotics of thimble integrals in different ways: on the one hand, using the thimble projection reasoning and on the other hand, solving an integral equation with a specified behavior near the singular point.
+In particular, we noticed that the two approaches give the same result up to the choice of a constant, as the integral equation is homogeneous.
+However, Theorem \ref{thm:maxim} suggests another approach, namely to use the fractional integral formula \eqref{formula1}.
+This approach
+As shown in the previous examples, the Borel transform  of the asymptotics of thimble integrals can be computed in different ways: from the ODE they solve, from the thimble projection reasoning, and from the integral formula \eqref{formula1}.
+When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneous, while with the thimble projection reasoning and the fractional integral formula the ambiguity is solved.
+
+%In addition, since thimble integrals have a geometric interpretation, the Stokes constants that encode the jumps of thimble integrals when $z$ crosses a Stokes ray are expected to be integers as they are intersection numbers of dual pairs of thimbles.
+
+In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the thimble projection formula~\eqref{int:deriv-formula}. \color{olive}
+
+By general theory, it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
+Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the thimble projection reasoning, and from the integral formula.
+When computed from the ODE, there is an ambiguity in the choice of the constant, while with the thimble projection reasoning and the thimble projection formula the ambiguity is solved.
+We’ll see this for the modified Bessel equation.
+
+This method allows us to uniquely determine the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
+Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
+%In order to compute the Stokes constants we’ll first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
+\begin{lemma}\label{claim 2}
+The following formula holds true
+\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
+for any $\zeta\in [2/3,+\infty)$.
+\end{lemma}
+\begin{proof}
+In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
+Hence,
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
+\end{align*}
+Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity~15.4.16 \cite{dlmf}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
+& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
+
+\begin{lemma}\label{claim 3}
+For any $\zeta\in (-\infty,-2/3]$
+\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
+\end{lemma}
+\begin{proof}
+Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
+\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
+In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
+Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
+The identity~15.4.16 in \cite{dlmf}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
+& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
+\begin{align*}
+\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{proof}
+
+\color{black}
+
 \end{document}

### 2023-11-08 exp-resurgence.tex
Appendix B moved to draf2.tex part of the content of Appedix B is now in thimble proj formula for Airy.

@@
 The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$, \textcolor{orange}{oriented so that shifting it to its left would make its projection run clockwise around $\Gamma_j$}.
+The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
+However, this only seems to be possible when $X$ is 1-dimensional.}}
 
@@
 \end{figure}
-Then, our main result for thimble integrals is proving that $1$- dimensional thimble integrals are indeed Borel regular:
+Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
 \begin{theorem}[see Theorem \ref{thm:maxim}]
@@
 Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[Be careful about the orientation of $\Lambda_j$.]}
+\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
 \end{enumerate}
@@
 \item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}.
+\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_j$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
+Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
 \end{itemize}
@@
 \fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
-\node at (1.7,1.8) {$\bullet$};
-\node[below] at (1.7,1.8) {$\zeta=\alpha_k$};
-\node at (1.25,-1.85) {$\bullet$};
-\node at (-0.58,1.85) {$\bullet$};
+\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\alpha_k$};
+\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+  \fill \p circle (0.7mm);
+}
 \end{tikzpicture}
@@
 
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $\alpha_j$ with $\tfrac{1}{2} \tau^2 = f - f(\alpha_j)$.
-Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $\alpha_j$ and from $\alpha_j$ to the future, respectively.
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$.
+Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively.
 We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
-\textcolor{magenta}{[We should explicitly spell out and check the conditions that make this possible.
-I think we're implicitly orienting $\Lambda_j$ so that $\tau$ is in the upper half-plane.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
 \[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
@@
     \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.
-The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=$.
+The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=???$.
 While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
@@
 
-In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (\S\ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (\S\ref{contour-argument-AL}).
+In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
 In both cases we find
@@
 which has a fractional power singularity at $\zeta=1$.
-In addition, notice that the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.
-More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new germ of holomorphic function, which has a branch cut singularity at $\zeta=-1$.
+In addition, the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.
+More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$.
 Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
@@
 
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pair of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Figure \ref{fig:intersection_thimbles}.
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Section \ref{sec:Picard-Lefschetz}.
 However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
 \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.45]{figures/contour1-AL4--12.jpg}
-    \includegraphics[scale=0.45]{figures/contour2-AL4--12.jpg}
-    \includegraphics[scale=0.45]{figures/contour--AL4--12--inter.jpg}
-    \includegraphics[scale=0.45]{figures/contour1-AL5--12.jpg}
-    \includegraphics[scale=0.45]{figures/contour2-AL5--12.jpg}
-    \includegraphics[scale=0.45]{figures/contour--AL5--12--inter.jpg}
-    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$.
-We choose $n=4$ and $n=5$.
-}
-    \label{fig:intersection_thimbles}
-\end{figure}
 
@@
 \textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations.
-In particular the thimble integral interpretation is missing Should we remove it?]}
+In particular, the thimble integral interpretation is missing Should we remove it?]}
 
 In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as countour integral \cite[Section 9.13(ii)]{dlmf}
+They are defined as contour integral \cite[Section 9.13(ii)]{dlmf}
 
@@
 \textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
+The thimble $\Lambda_1$ \textcolor{red}{is/can be} parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+\begin{align*}
+\int_{\Lambda_1(\zeta)} \nu & = \int_{\Lambda_1(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}.
+\end{align*}
+Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\Lambda_1(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -i\sqrt{3}\,\sinh(\theta).
+\end{align*}
+Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh( \theta)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
+\[ \sinh(\theta) =  \sinh( \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
+then shows us that
+\[ \frac{i}{\sqrt{3}} \int_{\Lambda_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\Lambda_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_1(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
+& = -i \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = \frac{i}{2} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
+\begin{align*}
+\fracderiv{3/2}{\zeta}{1} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+%
+For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\Lambda_{-1}$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+\begin{align*}
+\int_{\Lambda_{-1}(\zeta)} \nu & = \int_{\Lambda_{-1}(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \Lambda_{-1}(\zeta)}^{\operatorname{end}\Lambda_{-1}(\zeta)}.
+\end{align*}
+The start and end points of $\Lambda_{-1}$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\Lambda_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
+\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\Lambda_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
+\begin{align*}
+\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
+& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
+\begin{align*}
+\fracderiv{3/2}{\zeta}{-1} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
 \subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
-Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behaviour near the singular points.
-A prototypical class of resurgent functions is the so-called simple resurgent functions, namely analytic function $\hat{\phi}$ with singularities $\omega$ such that
+Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behavior near the singular points.
+A prototypical class of resurgent functions is the so-called simple resurgent functions, namely an analytic function $\hat{\phi}$ with singularities $\omega$ such that
 \begin{align*}
@@
 The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
-The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$  
-Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent functions.
+%The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$
+
+Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent.
 Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.
 Hence the set of singularities is given by the critical values of $f$.
-Since $f$ has finitely many critical values, we can
+Then, the computation of the Stokes constants and of the other germs $\series{\phi}_k$ is done by studying $\hat{\phi}_j$ near its singular points.
+For example, for the Airy function, we can expand $\hat{\phi}_1$ near $\zeta=-1$:
+\begin{align*}
+    \hat{\phi}_1(\zeta)=\log(\zeta+1) (1+...) +\text{ hol. funct. }
+\end{align*}
+
+Notice that $(1+...)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin. Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
+\begin{align*}
+    \hat{\phi}_{-1}(\zeta)=\log(\zeta-1) (1+...) +\text{ hol. funct. }
+\end{align*}
+where the germ $(1+...)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin.
 
@@
 
-\section{Application of the projection formula}
-
-In Section \ref{sec:examples}, we computed the Borel transform of the asymptotics of thimble integrals in different ways: on the one hand, using the thimble projection reasoning and on the other hand, solving an integral equation with a specified behavior near the singular point.
-In particular, we noticed that the two approaches give the same result up to the choice of a constant, as the integral equation is homogeneous.
-However, Theorem \ref{thm:maxim} suggests another approach, namely to use the fractional integral formula \eqref{formula1}.
-This approach
-As shown in the previous examples, the Borel transform  of the asymptotics of thimble integrals can be computed in different ways: from the ODE they solve, from the thimble projection reasoning, and from the integral formula \eqref{formula1}.
-When computed from the ODE, there is an ambiguity in the choice of a constant because the equation they satisfy is homogeneous, while with the thimble projection reasoning and the fractional integral formula the ambiguity is solved.
-
-%In addition, since thimble integrals have a geometric interpretation, the Stokes constants that encode the jumps of thimble integrals when $z$ crosses a Stokes ray are expected to be integers as they are intersection numbers of dual pairs of thimbles.
-
-In Theorem \eqref{thm:maxim} we prove that the Borel transform of $\tilde{I}_{\alpha}$ can be computed by the thimble projection formula~\eqref{int:deriv-formula}. \color{olive}
-
-By general theory, it is expected that Stokes constants are integers, and numerically this can be verified only when a suitable normalization is chosen.
-Indeed as we have seen, if we consider exponential integrals the Borel transform can be computed in different ways: from the ODE, from the thimble projection reasoning, and from the integral formula.
-When computed from the ODE, there is an ambiguity in the choice of the constant, while with the thimble projection reasoning and the thimble projection formula the ambiguity is solved.
-We’ll see this for the modified Bessel equation.
-
-This method allows us to uniquely determine the constants $U_1,U_2$ that appear in the formal integral solution $\tilde{I}(z)$.
-Indeed, $\tilde{I}$ is a solution of an homogeneous linear ODE and $\tilde{I}_+(z)=U_1e^{-2/3z}z^{-1/2}\tilde{W}_+(z)$ for a particular choice of $U_1$.
-%In order to compute the Stokes constants we’ll first use the fractional derivative formula to compute the correct normalization of \[\hat{w}_\pm(\zeta)=\delta\mp \frac{5}{48}{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right).\]
-\begin{lemma}\label{claim 2}
-The following formula holds true
-\[ \partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) = -i \frac{\sqrt{\pi}}{2}\,\hat{w}_+(\zeta-2/3), \]
-for any $\zeta\in [2/3,+\infty)$.
-\end{lemma}
-\begin{proof}
-In our general picture of exponential integrals, for $I_+(z)$ the thimble $\mathcal{C}_+$ is parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$.
-Hence,
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \int_{\mathcal{C}_+(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_+(\zeta)}^{\operatorname{end} \mathcal{C}_+(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_+(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_+(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = \cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 - \tfrac{3}{2}\zeta)$, and notice that $\xi = -\sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity~15.4.16 \cite{dlmf}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_+(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_+} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_+(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\tfrac{4}{3}\,d\xi' \big) \\
-& = -i \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(-\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ i \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = i \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = i \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-Analogously, we can compute the correct constants for $\hat{w}_-(\zeta)$:
-
-\begin{lemma}\label{claim 3}
-For any $\zeta\in (-\infty,-2/3]$
-\[ \partial^{3/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) = - \frac{\sqrt{\pi}}{2}\,\hat{w}_-(\zeta+2/3). \]
-\end{lemma}
-\begin{proof}
-Let $\mathcal{C}_-$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$, when $x \in [0, \infty)$ 
-\[ I_-(z) = \int_{\mathcal{C}_-} \exp\left[-\tfrac{2}{3} z \left(4u^3 - 3u\right)\right]\,du. \]
-In our general picture of exponential integrals, $f = \tfrac{2}{3}(4u^3 - 3u)$ and $\nu = du$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & = \int_{\mathcal{C}_-(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_-(\zeta)}^{\operatorname{end} \mathcal{C}_-(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_-(\zeta)$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_-(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-with $\tfrac{3}{2} \zeta = -\cosh(3\theta)$.
-Let $\xi = \tfrac{1}{2}(1 + \tfrac{3}{2}\zeta)$, and notice that $\xi =- \sinh(\tfrac{3}{2} \theta)^2$ at the start and end points.
-The identity~15.4.16 in \cite{dlmf}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_-} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\mathcal{C}_-(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
-\begin{align*}
-\partial^{3/2}_{\zeta \text{ from } 2/3} \left( \int_{\mathcal{C}_+(\zeta)} \nu \right) & = \left(\tfrac{3}{4} \tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{proof}
-
-\color{black}
 \section{Geometry of thimble integrals}
@@
 As we let $z$ vary, we’ll observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$).
-The jumps can be described geometrically using the theory of Picard--Lefschetz.
-Indeed, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
-We’ll discuss this phenomenon from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
+The jumps can be described geometrically using the pairing between dual cycles.
+Equivalently, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
+%We’ll discuss this phenomenon from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
 \textcolor{orange}{[Can we comment more about this?
@@
 
-\subsection{Picard--Lefschetz formula in pictures}
-We'll compute the Picard--Lefschetz formula as intersection of the base of thimbles and its dual, relative the singular direction $\theta=0$.
+\subsection{Picard--Lefschetz formula}\label{sec:Picard-Lefschetz}
+We'll compute the Picard--Lefschetz formula as the intersection of the base of thimbles and its dual, relative to the singular direction $\theta=0$.
 We'll do it graphically, by plotting the steepest decent contours center at the critical points of $f$.
@@
 
-For the classical Airy function, we have a two dimensional base of thimbles, thus we have to compute only one intersection:
+For the classical Airy function, we have a two-dimensional base of thimbles, thus we have to compute only one intersection: we choose the Stokes direction $\theta=0$, and we take a base of thimbles $\Lambda_j\in H_1(B_j,B_j^+(0.1))$.
+Then
+\begin{equation}
+    \begin{pmatrix}
+        \Lambda_1\\
+        \Lambda_2
+    \end{pmatrix} = \begin{pmatrix}
+        1 & \\
+        0 & 1
+    \end{pmatrix}\begin{pmatrix}
+        \Lambda_1\\
+        \Lambda_2
+    \end{pmatrix}
+\end{equation}
 \begin{figure}[ht]
@@
 \end{figure}
+
 We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{sec:eye-res-airy}.
 
-For Airy--Lucas with parameter $n=4$, we have a three dimensional base of thimbles, graphically represented as 
+For Airy--Lucas with parameter $n=4$, we have a three thimbles, graphically represented in Figure \ref{fig:thimble-n4}. 
 \begin{figure}[ht]
@@
     \includegraphics[scale=0.35]{figures/thimble-n4.png}
-    \caption{Caption}
+    \caption{Caption.}
     \label{fig:thimble-n4}
@@
      \includegraphics[scale=0.4]{figures/contour--AL4--12--inter.jpg}
-     \includegraphics[scale=0.4]{figures/contour1-AL4--13.jpg}
-    \includegraphics[scale=0.4]{figures/contour2-AL4--13.jpg}
-     \includegraphics[scale=0.4]{figures/contour--AL4--13--inter.jpg}
-     \includegraphics[scale=0.4]{figures/contour1-AL4--32.jpg}
-    \includegraphics[scale=0.4]{figures/contour2-AL4--32.jpg}
-     \includegraphics[scale=0.4]{figures/contour--AL4--32--inter.jpg}
-    \caption{First line computes the intersection of $\Lambda_1$ and $\Lambda_2$.
-Second line computed the interaction of $\Lambda_3$ and $\Lambda_2$.
-Third line computed the intersection of $\Lambda_3$ and $\Lambda_1$.}
+    \caption{...}
     \label{fig:intersection_thimbles-AL4}

### 2023-11-20 exp-resurgence.tex
Revise modified Bessel example Revise first part of generalized Airy example Revise third order thimble example

@@
 \newtheorem{definition}{Definition}[section]
+\newtheorem{remark}[definition]{Remark}
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{prop}[definition]{Proposition}
-\newtheorem{remark}[definition]{Remark}
-\newtheorem{theorem}{Theorem}[section]
 \newtheorem{corollary}[theorem]{Corollary}
@@
     \end{itemize}
+    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
 \end{brainstorm}
@@
 \begin{defn}
-On an open sector $\Omega$ around $\infty$, a power series
+On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
 \begin{equation}\label{series:asymp-defn}
@@
 \[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$.
-
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
+over all orders $n$. \textcolor{orange}{Introduce $\sim$ notation.}
 \end{defn}
+If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
+The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the the function's {\em asymptotic expansion} on that sector.
+The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
+
+\begin{defn}
+\textcolor{orange}{[Define $\aexp^\theta$ homomorphism that sends a function with an asymptotic expansion on a sector that contains the $\theta$-ray to its asymptotic expansion on that sector.\ldots]}
+\end{defn}
+\textcolor{RoyalBlue}{The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).}
 \begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
+On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
 \[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
@@
 First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, \textcolor{red}{for ODEs, we can build an analytic frame of solutions with an explicit growth behavior (see \cite[Theorem~4]{reg-sing-volterra})}, while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the position domain): on the one hand integral equations are more regular than differential equations.
+For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
+
+Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations.
 On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-
 \subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
@@
 \end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
 Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
@@
 Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
-
 \begin{equation}
@@
 \end{equation}
-
 labeled by the roots of $P$.
@@
 \end{remark}
-
 %\color{gray}
@@
 Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
-\begin{theorem}[see Theorem \ref{thm:maxim}]
+\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
     Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
@@
 Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-\textcolor{red}{At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.--I think we realise they have the same expansion at $\alpha_j$, thus they must agree.} In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
-
-\begin{remark}
-    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
-When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\iota_j$ explicitly as
-    \begin{equation}\label{eqn:Pham}
-        (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
-    \end{equation}
-
-    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
-   \begin{equation*}
-       \delta^{-\alpha}:=\begin{cases}
-           \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
-           & \\
-           \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
-       \end{cases}
-   \end{equation*}
-In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\phi_j$ is the $1/2-$ derivative of $\iota_j$, \textcolor{orange}{hence it has simple singularities [it has to be verified]}.
-We expect this result to hold beyond the polynomial case.
+At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
+In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
+%% the following remark has been moved to Section of the proof
+%\begin{remark}\label{rmk:Pham formula}
+%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
+When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as
+%    \begin{equation}\label{eqn:Pham}
+ %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
+ %   \end{equation}
+%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
+ %  \begin{equation*}
+  %     \delta^{-\alpha}:=\begin{cases}
+   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
+    %       & \\
+     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
+      % \end{cases}
+   %\end{equation*}
+%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
 We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
-\end{remark}
-
+%\end{remark}
+%     
 \subsubsection{Other results}
-
+%
 As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
@@
 \end{figure}
-We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}.
-In the Airy example (see Section \ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
-Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.}
+We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}
+
+On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}.
+In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
 
@@
 The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC} \textcolor{red}{add reference to state integrals}) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.
+For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals are toy-models that show some features of resurgent functions.
 
@@
 \subsection{Plan of the paper}
-
+The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
+The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
+Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
+Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
+We include three appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
+Then, Appendix~\ref{apx:geometry_thimble_integrals} has an algebraic geometric flavour and it describes some properties of thimbles integrals regarded as relative homology cycles.
+Finally, Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.
+%
 \subsection{Acknowledgements}
-
 This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
@@
 
-We thank Maxim Kontsevich, David Sauzin, Frederic Fauvet, Andrew Neitzke, for fruitful discussions and suggestions.
-
+We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
+%
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
 \subsection{The geometry of the Laplace transform}
-
 Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
@@
 Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
+%
 \subsubsection{Translation surfaces, briefly}
-
+%
 A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}.
@@
 This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
-
 \begin{figure}[ht]
@@
 \end{figure}
-
+%
 \subsubsection{Direction}\label{transl:dir}
+%
 The translation structure gives $B$ a notion of direction as well as distance.
@@
 In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
+%
 
@@
 Of course, there are $n$ different choices for $\omega_b$.
-
+%
 \subsubsection{Frequency}\label{transl-freq}
-
+%
 The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
@@
 \end{align*}
-
 When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
@@
 \textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
-
+%
 \subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
@@
 %\color{black}
-\subsection{The Laplace transform: analytic version}
+\subsection{The Laplace transform: analytic version}\label{sec:laplace_analytic}
 \subsubsection{Regularity and decay properties}\label{reg-decay}
-
+%
 Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
@@
 \end{equation}
-
+%
 \subsubsection{Rescaling of translation structure}
-
+%
 Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
@@
 We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-
+%
 \subsubsection{Action on integral operators}\label{L-int-op}
@@
 for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by 
-
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
@@
 
-\subsection{The geometry of the Borel transform}
+\subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
 The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
@@
 
-\subsection{The Borel transform on $1$-Gevrey series}
+\subsection{The Borel transform on $1$-Gevrey series}\label{sec:formal_borel}
 %\color{gray}
@@
 
-\section{Proof of main results}
+\section{Proof of main results}\label{sec:proof_main_results}
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
@@
 \subsubsection{Main result}
-\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
+\begin{theorem}\label{thm:maxim-dim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
 \begin{enumerate}
@@
 Furthermore, expanding $\hat{\phi}_j$ at its critical points we recover the germs $\series{\phi}_k$ for $k\neq j$.
-This is an instance of resurgence, indeed according to the theory of Ecalle, $\hat{\phi}_j$ are all resurgent functions.
-We'll see an example in Section~\ref{sec:eye-res-airy}.
+This is an instance of resurgence, indeed according to the theory of \'Ecalle, $\hat{\phi}_j$ are all resurgent functions.
+We'll see an example in Appendix~\ref{apx:eye-res-airy}.
 \end{remark}
-
+\textcolor{orange}{
+\begin{corollary}\label{simple-res-thimble}
+    If $f$ and $\nu$ are polynomials, the function $\hat{\phi}_j$ defined in \eqref{formula1} ha simple resurgent singularities at $\zeta=\alpha_k$.  
+\end{corollary}
+\begin{proof}
+    Recall $\hat{\iota}_j$ is the sum of the Borel transform of $z^{1/2}\tilde{I}_j$, namely 
+    \[\hat{\iota}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
+    Then by Pham's result (see \eqref{rmk:Pham formula}) we know 
+    \[\hat{\iota}_j(\zeta_j)=\frac{(-\zeta_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-\zeta_j)^{-k} + \text{ hol. funct. }\]
+hence 
+\[\hat{\iota}_j(\zeta)=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\frac{(-s+\alpha_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-s+\alpha_j)^{-k} \, ds + \text{ hol. funct. }\]
+\end{proof}
+}
+\begin{remark}\label{rmk:Pham formula}
+    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
+    \begin{equation}\label{eqn:Pham}
+        (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
+    \end{equation}
+    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
+   \begin{equation*}
+       \delta^{-\alpha}:=\begin{cases}
+           \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
+           & \\
+           \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
+       \end{cases}
+   \end{equation*}
+In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
+We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
+\end{remark}
 \section{Examples}\label{sec:examples}
@@
 \begin{equation}\label{integral:mod-bessel-rational-AL}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+K_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
 \end{equation}
@@
 \end{equation}
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf} \textcolor{red}{10 \cite{watson1922treatise}}) 
-\begin{align*}
-I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]\\
-\color{red}K_{\mu}(z)& \color{red}=\int_{-\infty+i\pi/2}^{+\infty+\pi i/2} e^{-\cosh(t)+\mu t} dt \text{  for } -1<\Re \mu<1
-\end{align*} 
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ (see Figure \ref{fig:Omega_path}).
-\begin{figure}[ht]
-\center
-\begin{tikzpicture}
-        \draw[->] (0,2)--(4,2);
-        \draw[->] (2,0)--(2,4);
-        \draw[red,very thick,->] (4,1.5)--(3,1.5);
-        \draw[red,very thick] (3,1.5)--(2,1.5);
-        \draw[red,very thick] (4,2.5)--(3,2.5);
-        \draw[red,very thick,->] (2,2.5)--(3,2.5);
-        \draw[red,very thick] (2,1.5)--(2,2.5);
-        \node[red,below, font=\tiny] at (4,1.5) {$\Omega$};
-        \node[font=\tiny,left,below] at (1.75,1.5) {$-i\pi$};
-        \node[font=\tiny] at (1.8,2.5) {$i\pi$};
-\end{tikzpicture}
-\caption{The path $\Omega$. }\label{fig:Omega_path}
-\end{figure}
 On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results: 
 \begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
+ \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions \[\series{I}_{\mu,1}(z)=e^{-z} z^{-1/2} \tilde{W}_{\mu, 1} \quad \text{ and } \quad \series{I}_{\mu,-1}(z)=e^z z^{-1/2} \series{W}_{\mu, -1}\] with
  \begin{align*}
  \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
+ \series{W}_{\mu,-1} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
 \end{align*}   
  \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-
 \begin{align*}
@@
 \end{align*}
-\item \textbf{Borel regularity} We can compare the Borel transform of the formal solutions $\tilde{W}_{\mu,\pm1}$ with the analytic solutions $v_{\mu,\pm 1}$.
-They agree (up to the choice of a constant), hence we have another example where Borel regularity can be checked explicitly.
+\item \textbf{Borel regularity} We can compare the Borel transform of the formal solutions $\series{W}_{\mu,\pm1}$ with the analytic solutions $v_{\mu,\pm 1}$.
+They agree (up to the choice of a constant), hence we have another example where Borel regularity can be explicitly verified.
 \end{itemize}
-
-The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we’ll discuss in the following Section~\ref{countable-cover}.
+On the other hand, the thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we’ll discuss in the following Section~\ref{countable-cover}.
 
@@
 \begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
+\cosh(n\tau) & = T_n(\cosh(\tau)) \\
+\sinh(m\tau) & = U_{m-1}(\cosh(\tau)) \sinh(\tau),
 \end{align*}
@@
 \notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Lambda_j}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Lambda_j}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
 \end{align}
-For any $\mu \in \C \smallsetminus \Z$, 
-\begin{align}
-\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-& \label{int:mod-bessel-gen} = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-
-\begin{center}
-    \begin{tikzpicture}
-        \draw[->] (6,2)--(10,2);
-        \draw[->] (8,0)--(8,4);
-        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
-        %\draw[red,thick,->] (10,2)--(9,2);
-        %\draw[red,thick] (9,2)--(8.5,2);
-        %\draw[red,thick] (10,2)--(9.3,2);
-        %\draw[red,thick,->] (8.5,2)--(9.3,2);
-        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
-        \node[font=\tiny,below] at (8.5,2) {$1$};
-    \end{tikzpicture}
-\end{center}
-
-We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
-
+where $\Lambda_j$ is the path coming from infinity along $-i\pi+2\pi i j+(-\infty,0]$ and going to infinity along $i \pi+2\pi i j+[0,+\infty)$, as represented in Figure \ref{fig:bessel_unrolled}.
+In fact, since $\cosh(t)$ is periodic, the integral has the same value for every choice of $\Lambda_j$ with $j\in\Z$.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[scale=0.3]{figures/Bessel0_unrolled_lightblue.png}
+    \caption{The paths $\Lambda_j$.}
+    \label{fig:bessel_unrolled}
+\end{figure}
+
+For any $\mu \in \C \smallsetminus \Z$, we have a thimble integral representation of $K_{\mu}$ given by formulas 10.32(ii) and 10.27.4 of \cite{dlmf} 
+\begin{equation}\label{int:mod-bessel-gen}
+ K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\Lambda_0} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
+\end{equation}
+\begin{verify}
+   % \begin{align*}
+   %    \notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
+%\notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\Lambda'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
+ %   \end{align*}
+  %  where $\Lambda'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
+  Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it's the reference in \cite{dlmf})
+    \begin{align*}
+        2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)} da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b} db\\
+        &=-\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)} da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b) db\\
+        &=-\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)} da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b) db
+    \end{align*}
+    hence 
+    \begin{align*}
+   4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big]\\
+     &= \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right] da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right] da \\
+        &=2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh(a+i\pi) da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(i\pi+a) da\\
+        &=2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh(a-i\pi) da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(i\pi+a) da
+    \end{align*}
+\end{verify}
+\textcolor{orange}{The integral converges when $z$ is in the right half-plane.} We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
+%
+%\begin{center}
+%    \begin{tikzpicture}
+%        \draw[->] (6,2)--(10,2);
+%        \draw[->] (8,0)--(8,4);
+%        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
+%        %\draw[red,thick,->] (10,2)--(9,2);
+%        %\draw[red,thick] (9,2)--(8.5,2);
+%        %\draw[red,thick] (10,2)--(9.3,2);
+%        %\draw[red,thick,->] (8.5,2)--(9.3,2);
+%        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
+%        \node[font=\tiny,below] at (8.5,2) {$1$};
+%    \end{tikzpicture}
+%\end{center}
+
+We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of the asymptotic of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
 \begin{align*}
@@
 \end{align*}
-
 where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf}
@@
 hence 
-
+%
 \[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
-
+%
 Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
@@
 \end{align}
-
+\subsubsection{The case $\mu=0$}
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 
+\begin{equation}\label{eqn:borel_bessel0}
+    K_0(z)=\textcolor{red}{-}\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
+\end{equation}
+\begin{verify}
+    We can also very equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
     \begin{equation}
-    K_0(z)=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
-\end{equation}
-\textcolor{orange}{[can we use (51) directly?
-It seems to me that if I try the thimble projection reasoning from the integral expression directly, I'm not able to write $1/\sinh(it)$ as a function of $\zeta$.
-]}
+        K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt
+    \end{equation}
+    we set $\zeta=\cosh(t)$, and choosing a branch for the square root
+    \begin{align*}
+        d\zeta & = \sinh(t) dt\\
+        & =  \sqrt{\zeta^2-1} \, dt
+    \end{align*}
+    we finally get 
+    \[\int_1^{\infty} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
+\end{verify}
 
 \subsection{Generalized Airy}
-
-\textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations.
-In particular, the thimble integral interpretation is missing Should we remove it?]}
-
-In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
+In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k, B_0, B_k$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
 They are defined as contour integral \cite[Section 9.13(ii)]{dlmf}
@@
 \begin{align*}
-\mathrm{A}_k(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
-\mathrm{B}_k(z,p)&=\int_{\gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
-\end{align*}
-where the contours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}
-
-\begin{figure}
+\mathrm{A}_k(y,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
+\mathrm{B}_0(y,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
+\mathrm{B}_k(y,p)&=\int_{\gamma_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
+\end{align*}
+where the contours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}. 
+\begin{figure}[ht]
 \center
@@
     \end{tikzpicture}
-    \caption{Representation of the path of integration for $A_k,B_0,B_k$ respectively in red, blue and orange.}\label{fig:path-generalized-Airy}
+    \caption{Representation of the path of integration for $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$ respectively in red, blue and orange.}\label{fig:path-generalized-Airy}
 \end{figure}
@@
 Each generalized Airy function is a solution of
-
 \begin{equation}
-\left[\partial_z^3-z\partial_z+(p-1)\right]f(z,p)=0
-\end{equation} 
-and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
-
-We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\alpha_{\pm}:=\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
-\begin{equation}
-I_\pm(z,p)\defeq\frac{1}{2\pi i}\int_{\Lambda_{\pm}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
-\end{equation}
-where $\Lambda_{\pm}$ are the paths through the points $\alpha_\pm$, starting and ending at infinity (as in Figure \ref{fig:path-generalized-Airy-Lambda+-}).
-\begin{figure}
-\center
-\begin{tikzpicture}
-    \draw[->] (4,0)--(4,8);
-    \draw[->] (0,4)--(8,4);
-    \node[red,font=\tiny] at (1.4,1.3) {$\Lambda_-$};
-    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
-    %\node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
-    %\draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
-    % \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
-    %\draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
-    \node[red,font=\tiny] at (7.4,1.3) {$\Lambda_+$};
-    \draw[red,very thick,->] (7,0.2) .. controls (4.5,4) .. (7,7.8);
-    \node at (5.1,4) {$\bullet$};
-    \node at (2.9,4) {$\bullet$};
-    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
-    \node[font=\tiny,below] at (5.3,4) {$1$};
-    \end{tikzpicture}
-    \caption{The paths of integration $\Lambda_\pm$ for $I_{\pm}$.}\label{fig:path-generalized-Airy-Lambda+-}
-\end{figure}
-In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$: 
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\Lambda_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
+\left[\partial_y^3-y\partial_y+(p-1)\right]f=0
+\end{equation} 
+and if $p=0$ they reduce to the classical Airy functions.
+
+Following the treatment of the Airy--Lucas functions, we'll rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ as thimble integrals with the function $f=4u^3-3u$.
+This follows from the change of coordinates $z=\tfrac{2}{3}y^{3/2}$, and gives $\mathrm{A}_1(y,p) = (12 z)^{\tfrac{1-p}{3}}\, I_+(z,p)$ with
+%
+\[I_+(z,p):=\frac{1}{2\pi i}\int_{z^{-1/3}\Gamma_1} e^{-z(4u^3-3u)} \frac{du}{u^p}\]
+%
+\begin{verify}
+  \begin{align*}
+I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\Lambda_{+}}e^{-z(4u^3-3u)}\, \frac{du}{u^p} &\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\Lambda_{+}}e^{-z(\tfrac{4}{12}\tfrac{t^3}{z}-3 (12 z)^{-1/3}t)}\frac{dt}{t^p} & u=(12 z)^{-\tfrac{1}{3}}t\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\Lambda_{+}}e^{-\left(\frac{t^3}{3}-(\tfrac{3}{2} z)^{2/3}t\right)}\frac{dt}{t^p} & \\
 &=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
 \end{align*}  
-It follows that $I_+(z)$ is a solution of
+\end{verify}
+%
+Notice that, the critical points of $f$ are $\alpha_{\pm}=\pm\tfrac{1}{2}$, as in the Airy case.
+However, the volume form $\nu_p$ is meromorphic, hence $f$ should be regarded as a function from $\C^*$ to $\C$.
+In particular, in this example we'll see that there is a new singularity at the origin due to the singularity of $\nu_p$.
+For simplicity, we'll restrict to the case $p=1$.
+Then, $I_+(z,1)$ solves
 \begin{equation}\label{eq:I}
-\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
-\end{equation}
-From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combination of three generators 
-\begin{equation}
-U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
-\end{equation}
-where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
-\begin{multline}\label{w1}
-\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
-\end{multline}
-\begin{multline}\label{w2}
-\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
-\end{multline}
-\begin{multline}\label{w3}
-\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
-\end{multline}
-Let us first study equation \eqref{w1}: its Borel transform is
-\begin{multline*}
--\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
-+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
-\end{multline*}
-We differentiate three times, getting 
-\begin{multline*}
-\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
-+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
-\end{multline*}
-we set $y=\zeta^2$
-%\begin{multline}
-%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
-%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
-%\end{multline}
-\begin{multline}\label{eq:hw1}
-y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
-+\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
-\end{multline}
-which is a generalized hypergeometric equation  \cite[Equation 16.8.5]{dlmf} with parameters
-\begin{align*}
-\mathbf{a}_0=\left(\frac{3}{2}-\frac{p}{3};\frac{7}{6}-\frac{p}{3};\frac{5}{6}-\frac{p}{3}\right) & \qquad\qquad \mathbf{b}_0=\left(\frac{1}{2};\frac{3}{2}\right)
-\end{align*}
-therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$. 
-Then we look at equation \eqref{w2}: its Borel transform is
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
--\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline} 
-and taking three derivatives it simplifies to 
-\begin{multline}
-\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
-\left.
-\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
-\end{multline}
-define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
-\begin{multline}\label{eq1}
-\left[y\left(y+\frac{4}{9}\right)^2\partial_y^3+2\left(\frac{3}{2}y+\frac{4}{3}+\frac{y}{2}\left(\frac{17}{2}+p\right)\right)\left(y+\frac{4}{9}\right)\partial_y^2+\left(\frac{2}{3}+\frac{y}{4}\left(\frac{17}{2}+p\right)\right)\partial_y\right.\\
-\left.+\frac{1}{4}\left(\frac{p^3}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(y+\frac{4}{9}\right)\partial_y+\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(y)=0
-\end{multline}
-which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
-\begin{multline}
-\left[t^2(1-t)\partial_t^3-t\left(\big(\frac{23}{4}+\frac{p}{2}\big)t-\frac{p}{2}-\frac{11}{4}\right)\partial_t^2-\left(-\frac{5}{8}-\frac{p}{4}+t\Big(\frac{887}{144}+\frac{17}{12}p+\frac{p^2}{12}\Big)\right)\partial_t +\right.\\
-\left. -\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(t)=0
-\end{multline}
-hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
-\begin{align*}
-\mathbf{a}=\left(\frac{5}{4}+\frac{p}{6};\frac{7}{12}+\frac{p}{6};\frac{11}{12}+\frac{p}{6}\right) & \qquad\qquad \mathbf{b}=\left(\frac{1}{2};\frac{5}{4}+\frac{p}{2}\right)
-\end{align*}
-and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
-The equation \eqref{w3} differs from \eqref{w2} for few signs: we find that its Borel transform is
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)+2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt+\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-+\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
-$\hat{w}_3(\zeta)= c_3\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta-1\right)^2\right)$.
-In particular,
-\begin{equation}
-\hat{w}_3(\zeta)=C_{23}\hat{w}_2(\zeta-\tfrac{4}{3})
-\end{equation}
-\textcolor{orange}{we may try to do the computations of Stokes constants for $p=1$, when $\hat{w}_1$ simplifies to a Gauss hypergeometric.
-Use also information about the monodromy.
-Check change of coordinates $y=\zeta^2$.}
+\left[\partial_z^3-\partial_z+\frac{1}{z}\partial_z^2-\frac{1}{9}\frac{\partial_z}{z^2}\right]\varphi=0
+\end{equation}
+or equivalently, $\partial_z\varphi$ solves the modified Bessel equation \eqref{eqn:mod-bessel-AL} with parameter $1/3$.
+Therefore, following the reasoning of Section \ref{big-idea} and the results of Sections \ref{pos-root-AL} and \ref{neg-root-AL}, we get two analytic solutions of \eqref{eq:I}: $\laplace_{\zeta,1}v_{1,1}$ and $\laplace_{\zeta,-1}v_{-1,1}$
+\[ v_{1,1}=-i\sqrt{2}\, (\zeta_1+1)^{-1}\, \zeta_1^{-1/2}\, {}_2F_1\Big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};-\tfrac{1}{2}\zeta_{1}\Big)\]
+\[ v_{-1,1}=-\sqrt{2}\, (1-\zeta_{-1})^{-1}\, \zeta_{-1}^{-1/2}\, {}_2F_1\Big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};\tfrac{1}{2}\zeta_{-1}\Big)\]
+where $\zeta_1=\zeta-1$ and $\zeta_{-1}=\zeta+1$. 
+\begin{verify}
+Form the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eq:I}.
+Then we argue as follows:
+\begin{align*}
+    \partial_z\varphi_1&=\laplace_{\zeta,1}v_1\\
+    \varphi_1-\varphi_1(a)&=\int_a^z\int_1^{\infty}e^{-zy} v_1 d\zeta \, dy\\
+    &=\int_1^{\infty}d\zeta\,  v_1 \, \int_a^ze^{-zy}  \, dy\\
+    &=\int_1^{\infty}d\zeta\,  v_1 \, \Big[\frac{e^{-\zeta a}}{\zeta}-\frac{e^{-z\zeta}}{\zeta}\Big]\\
+    &=\laplace_{\zeta,1} \tfrac{v_1}{\zeta}-\Big[\laplace_{\zeta,1}\tfrac{v_1}{\zeta}\Big](a)
+\end{align*}
+\end{verify}
+Notice that $v_{1,1}\in\singexpalg{1/2}(\Omega_1)$, it has a simple pole at $\zeta_1=-1$ and it is a log--singularity at $\zeta_1=-2$.
+Similarly, $v_{-1,1}\in\singexpalg{1/2}(\Omega_{-1})$, it has a simple pole at $\zeta_{-1}=1$ and it is a log--singularity at $\zeta_{-1}=2$.
+
+Notice that $\laplace_{\zeta,1}v_{1,1}$ and $\laplace_{\zeta,-1}v_{-1,1}$ are not a frame of solutions; the equation \eqref{eq:I} is of degree three, but it is enough to consider the constant function $1=\laplace_\zeta \delta$ to build a frame of analytic solutions, where $\delta$ is the formal unit (see the definition in Section \ref{convolution}).
+In particular, $1=B_0(z,1)$ and confirms Borel regularity for the constant solution.
+%
+\color{RoyalBlue}
 \subsubsection{Thimble projection formula}
-In Theorem \ref{thm:maxim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral. 
+In Theorem \ref{thm:maxim-dim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
+\color{black}
 \subsection{Third-order thimble integrals}
@@
 where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin. 
-
-\color{DarkTurquoise}
-\begin{itemize}
-\item As $p$ goes to zero, $I(z)$ degenerates to
-\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}).
-\]
-\end{itemize}
-
-\color{black}
+\begin{remark}
+    The degenerate case $p=0$ can be recovered from the generic case, taking the limit of $I_+(z)$ as $p\to 0$. Indeed, 
+    \[ e^{-zq} I_+(z)=2 \sqrt{-\frac{p}{3}} K_{1/3}\Big(\frac{2p^{3/2}}{i3^{3/2}}z\Big)\]
+    and its limit as $p\to 0$ can be computed from equations 10.25.2 and 10.27.4 in \cite{dlmf} giving 
+    \[ e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) e^{-zq} z^{-1/3}.  \]
+    \begin{verify}
+        \begin{align*}
+            2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big)&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
+            &=\frac{2}{3}\pi ip^{1/2}\left[\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{-1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}\right]\\
+            &=\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\frac{2\pi }{3\sqrt{3}} e^{2\pi i/3} z^{1/3} p \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}
+        \end{align*}
+         Now we take the limit as $p\to 0$ and we find 
+         \[\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)}=e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}\]
+    \end{verify}
+    From the properties of the Laplace transform, we then deduce
+    \[e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) e^{-zq} z^{-1/3}= e^{\pi i/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = e^{\pi i/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3})\]
+    which agrees with the thimble integral representation of $I$ computed above. 
+\end{remark}
 
@@
 In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula~\eqref{formula1} using trigonometric substitution.
-As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time applying the thimble projection formula to the generalized Cardano's formula.
-
-Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
+As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
+
+\textcolor{RoyalBlue}{[\ldots] this time applying the thimble projection formula to the generalized Cardano's formula.}
+
+\textcolor{Peru}{Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
 \begin{align*}
@@
     &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
-\end{align*}
+\end{align*}}
 \textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
-The thimble $\Lambda_1$ \textcolor{red}{is/can be} parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+The thimble $\Lambda_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
+Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are then characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \cosh(3\theta).
+\end{align*}
+It follows that
 \begin{align*}
 \int_{\Lambda_1(\zeta)} \nu & = \int_{\Lambda_1(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\Lambda_1(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}\\
+ & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
 & = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
@@
 \end{align*}
-Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh( \theta)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
-\[ \sinh(\theta) =  \sinh( \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
+Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh\big(\tfrac{3}{2} \theta\big)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
+\[ \sinh( \theta) = \tfrac{1}{3} \sinh\big( \tfrac{3}{2}\theta\big)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh\big(\tfrac{3}{2}\theta\big)^2\big) \]
 then shows us that
@@
 
-Now we can evaluate the half-integral of $\int_{\Lambda_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_1(\zeta')} \nu \right)\,d\zeta' \\
+Now we can evaluate the half-integral of $\int_{\Lambda_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
+\begin{align*}
+\fracderiv{-1/2}{\zeta}{1} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_1(\zeta')} \nu \right)\,d\zeta' \\
 & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
@@
 %
-For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\Lambda_{-1}$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\Lambda_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
 \begin{align*}
@@
 Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
+\[ \sinh(\theta) = \sinh(\theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
 then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\Lambda_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu =  (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\Lambda_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
+\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_{-1}(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\, (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \,d\xi' \big) \\
+& =  \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
 \end{align*}
@@
 \begin{align*}
-\fracderiv{3/2}{\zeta}{-1} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
-Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behavior near the singular points.
-A prototypical class of resurgent functions is the so-called simple resurgent functions, namely an analytic function $\hat{\phi}$ with singularities $\omega$ such that
-\begin{align*}
-    \hat{\phi}(\zeta-\omega)=\frac{S_\omega}{2\pi i} \log(\zeta) \series{\phi}_\omega(\zeta) + \text{ hol. funct.}
-\end{align*}
-where $S_\omega$ is a constant, typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
+\fracderiv{3/2}{\zeta}{-1} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
+Resurgent functions are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}}.
+\textcolor{MediumSeaGreen}{[Focus on endlessly continuable functions instead?
+See~[Section~2, ``Variations on the resurgence of the gamma function''.]} \textcolor{red}{They have the special property that by studying their analytic continuation around one singularity, we can typically discover the germ of another singularity.} \textcolor{RoyalBlue}{They have the very special property that by studying one germ, we can typically reconstruct the others by looking at the behavior near the singular points.} \textcolor{MediumSeaGreen}{[They are ``self-reproducing'' in a certain remarkable way involving holonomy around singularities, as we'll see in the example below\ldots]} A prototypical class of resurgent functions is the so-called simple resurgent functions~\textcolor{magenta}{\cite[Section~1.2.3]{intro-to-ecalle}\{oops, this source defines simple resurgent functions in the frequency domain\}}.
+namely an \textcolor{Maroon}{[resurgent]} analytic function $\hat{\phi}$ in the position domain with singularities $\omega$ such that
+
+\textcolor{Maroon}{[\ldots] resurgent function with the property that at each singularity $\omega$, we have an expansion of the form}
+\begin{align*}
+    \hat{\phi} = \frac{C_\omega}{\zeta_\omega}+\frac{S_\omega}{2\pi i} \log(\zeta_\omega)\,\series{\phi}_\omega + \text{ hol. funct.} \textcolor{Maroon}{[\text{convergent series in}\,\zeta_\omega]}
+\end{align*}
+where \textcolor{Maroon}{$\zeta = \omega + \zeta_\omega$, $\series{\phi}_\omega$ is a series in $\zeta_\omega$} $C_\omega, S_\omega$ are constants and $S_\omega$ is typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
 The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
@@
 \begin{align*}
-    \hat{\phi}_1(\zeta)=\log(\zeta+1) (1+...) +\text{ hol. funct. }
-\end{align*}
-
-Notice that $(1+...)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin. Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
-\begin{align*}
-    \hat{\phi}_{-1}(\zeta)=\log(\zeta-1) (1+...) +\text{ hol. funct. }
-\end{align*}
-where the germ $(1+...)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin.
+    \hat{\phi}_1(\zeta-1)=\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1+\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2+\frac{7436429}{53747712}\zeta^3+\ldots\right)  +\text{ hol.
+funct.
+}
+\end{align*}
+
+Notice that $(1+\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2+\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin.
+So we see that expanding $\hat{\phi}_1$ at the singularity we see the germ of another singularity $\series{\phi}_{-1}$.
+Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
+\begin{align*}
+    \hat{\phi}_{-1}(\zeta+1)=-\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1-\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2-\frac{7436429}{53747712}\zeta^3+\ldots\right) +\text{ hol.
+funct.
+}
+\end{align*}
+where the germ $(1-\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2-\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin. 
+From these expressions, we also noticed that $\hat{\phi}_i$ are simple resurgent functions.
 
@@
 
-\section{Geometry of thimble integrals}
+\section{Geometry of thimble integrals}\label{apx:geometry_thimble_integrals}
 
@@
 
-We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{sec:eye-res-airy}.
+We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{apx:eye-res-airy}.
 
@@
 Notice that $\Lambda_1$ and $\Lambda_3$ do not intersect as they are in the same class, because they are preimages of the same rays through infinity.    
-\section{Generalities about ODEs and Integral Equations}
+\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
 \textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}

### 2023-11-24 Geometry of thimble.tex
Moved some part of the intro into the historical section Removed appendix on the geometry of thimbles and create a new doc.

--- 2023-11-08 exp-resurgence.tex
@@
 \newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
+\newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
+\newcommand{\dualsingexpalg}[1]{\singexp{#1}{\bullet}}
+\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments
 
@@
 \newcommand{\fracderiv}[3]{\partial^{#1}_{#2, #3}}
-\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
 \newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
@@
 
-\title{Borel regularity for ODEs and Thimble Integrals}
-\author{Veronica Fantini and Aaron Fenyes}
+\title{Geometry of thimble integrals}
+\author{Veronica Fantini}
 
@@
 
-\begin{abstract}
-    ...
-\end{abstract}
-\tableofcontents
-
-\begin{brainstorm}
-    \item Section~\ref{borel_reg-ODE}---definitely Section~\ref{setting-ODE}, and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
-    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
-    \item Section~\ref{contour-argument-AL}---revise the general contour argument
-    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
-    \begin{itemize}
-    \item Replace formalism in Section~\ref{reg-decay}
-    \end{itemize}
-    \item Check which examples are still in the framework of our theorem
-    \begin{itemize}
-    \item Start a storage document for shelved examples
-    \end{itemize}
-    \item Section~\ref{resurgence-AL}---Draw intersection points figure
-    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
-    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
-    \begin{itemize}
-    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
-    \end{itemize}
-    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
-    \begin{itemize}
-    \item Put future goals in storage document
-    \end{itemize}
-\end{brainstorm}
-
-\section{Introduction}
-\subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
-%%\subsection{A familiar process: Borel summation}\label{intro:summation}
-You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
-\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
-with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example, if you want to understand how the solutions of the holomorphic ordinary differential equation (ODE)
-\begin{equation}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
-\end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
-\begin{equation}
-e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{85085}{33592320} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
-\end{equation}
-and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
-
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
-as
-\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
-\color{orange}
-\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{black}
-Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-Borel summation works in three steps.
-\begin{enumerate}
-\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}.
-We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-%\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
-Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
-\end{enumerate}
-The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-%\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
-Hopefully it wouldn't be too hard, but it would be a pain.]}
-\begin{defn}
-On an open sector $\Omega$ around $\infty$, a power series
-\begin{equation}\label{series:asymp-defn}
-\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
-\end{equation}
-is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$.
-
-The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function \textcolor{orange}{that vanishes at $\infty$ [if it vanishes at $\infty$ it sent to zero, so why this assumption?]} to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).
-\end{defn}
-\begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey-asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
-over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
-\end{defn}
-To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
-
-\begin{enumerate}[start=4]
-\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
-It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
-\end{enumerate}
-
-The Borel summation process is summarized in the following diagram:
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-
-You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
-After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
-In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
-The question of how that happens is the starting point for this paper.
-
-%\color{gray}
-%\begin{itemize}
-%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example\ldots}
-%\begin{itemize}
-%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
-%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
-%\item Feynman diagram series?
-%\end{itemize}
-%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-%\begin{itemize}
-%\item \done{Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
-%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
-%\item {[Draw the square!]}
-%\end{itemize}
-%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-%\item In many cases, it picks correctly, producing an actual solution to your problem.
-%\begin{itemize}
-%\item The question of how that happens is the starting point for this paper.
-%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-\subsection{A new perspective: Borel regularity}
-\subsubsection{Introducing Borel regularity}
-We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
-
-%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
-
-\begin{center}
-\begin{tikzcd}
-& \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
-& & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
-\end{tikzcd}
-\end{center}
-If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
-Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
-We'll therefore call this process {\em Borel regularization}.
-Explicitly, Borel regularization works in four steps.
-\begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
-\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.%\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
-Being Gevrey implies that the Borel transform is convergent, not that we can analytically continue it]}
-\item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we're allowed to take the Laplace transform at another point $b \in B$.
-This would be natural in our study of ODEs and thimble integrals.}
-\end{enumerate}
-We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
-
-Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
-We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
-\subsubsection{Borel regularity as a good approximation condition}
-Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \cite{watson} that a function $F$ that vanishes at infinity is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around infinity (see Definition~\ref{def:unif-gevrey-asymp}).
-
-Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
-\begin{center}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\dis}{1.2}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
-  \begin{scope}[violet]
-    \draw (0, 0) -- (-\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
-\end{tikzpicture}
-\end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
-\textcolor{orange}{[Picture below should show the constant-radius neighborhood]}
-\begin{center}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\dis}{1.2}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
-  \begin{scope}[violet]
-    \draw (0, 0) -- (\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
-\end{tikzpicture}
-\end{center}
-
-%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
-Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
-Hence $\Phi$ is Borel-regularizable.
-In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$.
-In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
-The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
-Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.
-
-The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
-\begin{enumerate}
-\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
-We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).
-
-The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag.
-105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
-Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
-
-\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
-
-\begin{equation*}
-I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
-\end{equation*}
-where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
-\end{enumerate}
-
-These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-
-%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
-Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We’ll give precise statements in the following section.
-
-%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We'll call it {\em Borel regularization}.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We'll call this process {\em Borel regularization}.
-%\begin{itemize}
-%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-%\item We have the following vector space inclusions:
-%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
-%
-%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-%\begin{itemize}
-%\item $\Phi$ is Borel regular.
-%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-%\item $\phi$ grows at most exponentially along the Laplace transform ray.
-%\end{itemize}
-%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
-\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
-it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
-%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-%\item \ldots
-%\end{itemize}
-
-\subsection{Goals and Results}
-
-First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-Indeed, \textcolor{red}{for ODEs, we can build an analytic frame of solutions with an explicit growth behavior (see \cite[Theorem~4]{reg-sing-volterra})}, while for thimble integrals we can write an explicit analytic function whose Laplace transform is the thimble integral itself (see part 3 of Theorem~\ref{thm:maxim}).
-
-Second of all, we want to explain why it is useful to work in the Borel plane (the position domain): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-
-\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
-\begin{equation}\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
-
-\begin{verify}
-    Turn the ODE into a system: assume 
-    \begin{align*}
-P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
-Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
-\end{align*}
-then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
-    \begin{equation}
-        \frac{d}{dz}Y= B(z) Y 
-    \end{equation}
-    \[
-    B(z)=\begin{pmatrix}
-            0 & 1 & 0 & \ldots & 0 \\
-            0 & 0 & 1 & \ldots & 0 \\
-            \vdots & &\ddots & & 1\\
-            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
-        \end{pmatrix}, \quad Y=\begin{pmatrix}
-            \psi \\
-            \psi ' \\
-            \vdots \\
-            \psi^{(d-1)}
-        \end{pmatrix}
-    \]
-
- and $b_j(z)=-P_j-\frac{1}{z}Q_j-\frac{R_j(z)}{z^2}$. A formal system of solutions is given by the matrix 
-\begin{equation}
-    Y=\begin{pmatrix}
-       \psi_1 & \psi_2 & \ldots & \psi_d  \\
-       \psi_1' & \psi_2' & \ldots & \psi_d'  \\
-       \vdots & \vdots  & \ldots & \vdots  \\
-       \psi_1^{(d-1)} & \psi_2^{(d-1)} & \ldots & \psi_d^{(d-1)} 
-    \end{pmatrix}, \qquad \psi_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{f}_j
-\end{equation}
-
-To prove that $z=\infty$ is an irregular singular point we change coordinates and set $w=1/z$:
-
- \begin{equation}
-        -w^2 \frac{d}{dw}Y= B(1/w) Y 
-    \end{equation}
-
-and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
-\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
-hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular. 
-\end{verify}
-
-Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
-\end{equation}
-where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-
-Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
-Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
-Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
-
-\begin{equation}
-\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
-\end{equation}
-
-labeled by the roots of $P$.
-This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
-In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
-At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually proportional, hence proving Borel summation works.
-\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
-The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.  
-\end{theorem}
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & \text{ODE }\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & \text{IE} & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
-The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE).
-In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
-Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.
-
-\begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII,loday-Remy2011}}.
-It can indeed be seen as a consequence of ``resurgence'' of the ODE.
-Our results of \cite{reg-sing-volterra} show how to build a frame of solutions, analytically in the Borel plane.
-Here, we show we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of \cite[Theorem~4]{reg-sing-volterra}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
-\end{remark}
-
-\begin{remark}
-The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namely, drawing the red arrow of the diagram).
-This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE.
-However, the approach of Borel regularity is different as it is based on the analytic solution in the position domain.
-\end{remark}
-
-%\color{gray}
-%\begin{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\end{itemize}
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-
-\subsubsection{Why does Borel summation work for thimble integrals?}
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
-\[
-I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
-\]
-regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
-Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
-
-Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.
-
-\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
-In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.}
-
-Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
-
-We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
-These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
-However, this only seems to be possible when $X$ is 1-dimensional.}}
-
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{}
-    \caption{The preimage of a ray departing from the critical value and going to infinity.}
-    \label{fig:thimble_vs_rays}
-\end{figure}
-Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
-\begin{theorem}[see Theorem \ref{thm:maxim}]
-    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
-Then:
-\begin{enumerate}
-\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
-\begin{multline}\label{eqn:formula}
-\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
-\end{multline}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{enumerate}
-\end{theorem}
-
-The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
-\[
-\begin{tikzcd}
-{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
-& & &\\
-\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
-\end{tikzcd}
-\]
-On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
-as the Laplace transform of a function $\iota_j$.
-In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}.
-On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
-Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-\textcolor{red}{At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.--I think we realise they have the same expansion at $\alpha_j$, thus they must agree.} In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
-
-\begin{remark}
-    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
-When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\iota_j$ explicitly as
-    \begin{equation}\label{eqn:Pham}
-        (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
-    \end{equation}
-
-    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
-   \begin{equation*}
-       \delta^{-\alpha}:=\begin{cases}
-           \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
-           & \\
-           \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
-       \end{cases}
-   \end{equation*}
-In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\phi_j$ is the $1/2-$ derivative of $\iota_j$, \textcolor{orange}{hence it has simple singularities [it has to be verified]}.
-We expect this result to hold beyond the polynomial case.
-We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
-\end{remark}
-
-\subsubsection{Other results}
-
-As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
-Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain.
-
-Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
-
-\begin{figure}[h]
-    \centering
-    %\includegraphics[]{}
-    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
-However, the fiber over a singular point of $B$ has an interesting structure.
-Here we represent the example of Airy functions.}
-    \label{fig:different_fibres}
-\end{figure}
-We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section \ref{example_AL}), modified Bessel function, Airy function (Appendix \ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, \textcolor{red}{we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions as the Laplace transform of the solutions of the integral equation.} On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-The thimble projection reasoning is the one we use in the proof of Theorem \ref{thm:maxim} part \ref{part3}.
-In the Airy example (see Section \ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and \textcolor{red}{by numerical check we show $\hat{\phi}_j$ is a simple resurgent function.
-Conjecturally, we expect $\hat{\phi}_j$ to be always a simple resurgent function, but so far we don't have a general proof.}
-
-Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
-The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).
-Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
-
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
-The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC} \textcolor{red}{add reference to state integrals}) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals show some features of resurgence and they are toy-model to get a feeling of \'Ecalle formalism.
-
-%\color{gray}
-%\begin{itemize}
-%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-%\begin{itemize}
-%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-%\item The second problem is solving a certain kind of ODE.
-%\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-%\end{itemize}
-%
-%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-%\begin{itemize}
-%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-%\end{itemize}
-%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-%\begin{itemize}
-%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-%\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-%\end{itemize}
-%\end{itemize}
-%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
-%\begin{itemize}
-%\item Integral equations are more regular than differential equations.
-%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-%\end{itemize}
-%\item Illustrate with detailed treatments of several examples.
-%\begin{itemize}
-%\item Contour argument (thimble integrals)
-%\item solving integral equation (ODE)
-%\item How thimble integrals and ODE are related in our examples?
-%\end{itemize}
-%\begin{itemize}
-%\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-%\item Others haven't been discussed much.
-%\end{itemize}
-%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-%\begin{itemize}
-%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-%\item computation of Stokes constants via Picard--Lefschetz theory
-%\end{itemize}
-%\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{\'Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to \'Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
-
-%\subsection{Stokes phenomenon}
-%\begin{itemize}
-%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-%\item The jump comes from the branch cut difference identity for hypergeometric functions.
-%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-%\end{itemize}
-\subsection{Plan of the paper}
-
-\subsection{Acknowledgements}
-
-This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
-
-We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
-
-We thank Maxim Kontsevich, David Sauzin, Frederic Fauvet, Andrew Neitzke, for fruitful discussions and suggestions.
-
-\section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
-\subsection{The geometry of the Laplace transform}
-
-Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
-In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
-Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
-\subsubsection{Translation surfaces, briefly}
-
-A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}.
-A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
-The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
-
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{}
-    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
-    \label{fig:translation_surface}
-\end{figure}
-
-\subsubsection{Direction}\label{transl:dir}
-The translation structure gives $B$ a notion of direction as well as distance.
-Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
-At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
-To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
-In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
-
-Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
-This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
-Of course, there are $n$ different choices for $\omega_b$.
-
-\subsubsection{Frequency}\label{transl-freq}
-
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
-At an ordinary point, we can define $z$ simply as the map
-\begin{align*}
-z \maps T^*B_b & \to \C \\
-\lambda\big|_b & \mapsto 1.
-\end{align*}
-To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
-Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
-Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
-When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
-In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
-We define $z$ as the isomorphism
-\begin{align*}
-z \maps \van_b^n / \van_b^{n+1} & \to \C \\
-\zeta_b + \van^{n+1} & \mapsto 1.
-\end{align*}
-
-When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
-\begin{align*}
-w_b \maps T^*B_b & \to \C \\
-\omega_b + \van^2 & \mapsto 1
-\end{align*}
-that makes the diagram
-\begin{center}
-\begin{tikzcd}
-T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
-T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
-\end{tikzcd}
-\end{center}
-commute.
-\subsubsection{Boundary}
-\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
-
-\subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
-Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
-\begin{equation}\label{laplace:int}
-\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
-
-To make sense of this formula, we ask for the following conditions.
-\begin{itemize}
-\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
-\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
-\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-%\color{RoyalBlue}
-\begin{itemize}
-\item With respect to the flat metric, \textcolor{red}{$f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.}\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
-\item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
-\end{itemize}
-\end{itemize}
-\color{black}
-\subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
-The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
-This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}.
-The half-plane $z \in H_{\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
-We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-%\color{gray}
-%\subsection{The geometry of the Borel transform}
-%\begin{itemize}
-  %\item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  %\item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  %\begin{itemize}
-   % \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  %\end{itemize}
-  %\item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-%\end{itemize}
-%\color{black}
-\subsection{The Laplace transform: analytic version}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-
-Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
-Assume the $\Gamma_{\zeta,\alpha}^\theta$ is contained in $\Omega_\alpha$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namely of the form $|\zeta|^\sigma$.
-When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta,\alpha}^\theta$ is a well--defined and holomorphic function for $\Re e^{-i\theta}z>0$ on the fiber $T^*B\vert_{\zeta=0}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
-%Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[Section  5.6]{diverg-resurg-i}.
-
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$.
-Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$.
-Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
-\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
-Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
-\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-
-\subsubsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    \label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-
-\subsubsection{Rescaling of translation structure}
-
-Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-
-\subsubsection{Action on integral operators}\label{L-int-op}
-%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-
-%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-
-%\color{Tan}
-%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-%for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-%\begin{equation}%%\label{id:L-mult}
-%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-%\end{equation}
-%for all integers $n \ge 0$.
-
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
-\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
-for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
-\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
-for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by
-
-\begin{equation}
-    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
-\end{equation}
-
-Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
-\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
-for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by
-
-\begin{equation}
-    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
-\end{equation}
-
-Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
-However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
-
-%We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
-
-%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
-In fact, as we’ll see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
-
-%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
-
-\subsection{The geometry of the Borel transform}
-The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
-\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
-Here, we're thinking of $z$ as the standard coordinate on $T^*B_{\zeta = 0}$, as described in Section~\ref{transl-freq}.
-We can get a function on $T^*B_{\zeta = \alpha}$ instead by taking the Laplace transform with respect to the coordinate $\zeta_\alpha$ defined by $\zeta = \zeta_\alpha + \alpha$:
-\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}. \]
-On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
-This formal inverse is called the {\em Borel transform}.
-
-The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
-\begin{align*}
-\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-In general, by linearity,
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-\end{align*}
-If a function $\varphi$ belongs to $\singexpalg{0}$, and its Taylor series
-\[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
-has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
-\begin{align*}
-  \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
-  &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
-  &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
-\end{align*}
-As a result, we can recover the Taylor series $\series{\varphi}$ from the series
-\[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
-using the Borel transform:
-\begin{align*}
-\borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
-&=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
-\end{align*}
-We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*B_{\zeta = 0}$.
-
-If we'd expanded $\varphi$ as a Taylor series $\series{\varphi}_\alpha$ in the translated coordinate $\zeta_\alpha$ from above, we could've taken the Laplace transform $\laplace_{\zeta_\alpha,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*B_{\zeta = \alpha}$.
-Using the Borel transform with respect to $\zeta_\alpha$, defined like before as a formal inverse of $\laplace_{\zeta_\alpha,0}$
-
-\begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
-
-we could again recover $\series{\varphi}_\alpha$.
-
-It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha}$, as discussed in Section~\ref{transl-borel}.
-
-%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
-%%\begin{align*}
-%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
-%%z^{-n-1} & \mapsto \frac{\zeta_\alpha^n}{n!}.
-%%\end{align*}
-
-%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.
-
-%\color{Peru}
-%\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-More precisely, $\borel_\zeta$ is a $\C$-linear map
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
-
-%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
-%\begin{align*}
- %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
-  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
-%\end{align*}
-%where in the second step we formally interchange the integral and the sum. 
-%\color{black}
-\subsubsection{Action on transseries}\label{sec:action_transseries}
-
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
-
-\[T_{\alpha,\varphi}:=\sum_{n=0}^{\infty} e^{\alpha_n z} \varphi_n(z) \]
-
-The main feature of $T_{\alpha,\varphi}$ is that its asymptotics as $\text{ Re } e^{i\theta}z \to +\infty$ is $\varphi_0$.
-In fact, they play a crucial role in the theory of ODEs with irregular singularities.
-
-It is natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries.
-Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-
-We extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-
-Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, %then from identity \eqref{change-chart}
-
- % \begin{align*}
-  %    \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z }\laplace_{\zeta_\alpha,0}\varphi\right]
-  %\end{align*}
-%We compute the left-hand-side
-  \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi&=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
-  \end{align*}
-  %and the right-hand-side
-  %\begin{align*}
-   %   \borel_\zeta\left[e^{-\alpha z
-    %  }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
-     % }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
-     % &=\borel_\zeta\left[
-     % \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
-     % &=\borel_\zeta\left[ \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
-    %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-     % &= \sum_{n=0}^{\infty}a_n \zeta^n
-  %\end{align*}
-%In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-hence we require the following equality to hold  
-\[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
-
-and, comparing term by term in powers of $\zeta$ %in the second identity we get 
-  \begin{align*}
-      \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})&=\zeta^n\\
-      \sum_{k=0}^n {n\choose k} \alpha^{n-k} \borel_\zeta(e^{-z\alpha} k! z^{-k-1})&=\sum_{k=0}^n {n\choose k} \alpha^{n-k}(\zeta-\alpha)^k
-  \end{align*}
-  thus we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
-%\begin{itemize}
- %   \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-%  \end{itemize}
-
-\subsubsection{Change of translation chart}\label{transl-borel}
-
-Following Section \ref{translation}, we can recover the definition of $\borel_{\zeta_\alpha}$
-as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $\alpha$. Explicitly, from identity \eqref{change-chart}
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi
-  \end{align*}
-  now the left-hand-side reads
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\left[e^{z\alpha} \int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_n\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_ne^{-z\alpha}\sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}  z^{-k-1}\right]
-  \end{align*}
-  %the RHS is 
-  %\begin{align*}
-   %   \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
-    %  &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
-     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
-     % &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
-     % \end{align*}
-     If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
-     % \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
-       \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
- Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
- \begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
- Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
-
-\subsection{The Borel transform on $1$-Gevrey series}
-%\color{gray}
-%\begin{itemize}
-%\item Action on differential equations.
-%\begin{itemize}
-%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-
-%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
-These formal series are the so-called $1$-Gevrey series:
-\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is $1$-Gevrey if there exists $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
-there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obtain germs of holomorphic function for higher Gevrey series.
-}
-
-\begin{notation*}
-We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane).
-Therefore we adopt the following notation:
-\begin{itemize}
-\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
-\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
-\item $\phi$: lower-case letters are holomorphic functions on the frequency domain.
-Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
-\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
-\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
-\end{itemize}
-\end{notation*}
-
-\begin{lemma}
-Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
-\end{lemma}
-
-In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textit{formal Laplace transform}.
-In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra isomoprhisms.
-
-\subsubsection{Action on power series with fractional exponents}
-The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
-\begin{align*}
-\borel\textcolor{orange}{_\zeta}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
-\end{align*}
-and then extending by linearity.
-
-\subsection{Properties of the Borel transform}\label{properties Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
-\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
-\end{itemize}
-
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
-\begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-
-\begin{proof}
-
-We are going to prove properties (i)--(vi).
-
-(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
-
-\end{proof}
-
-\subsection{The convolution product}\label{convolution}
-
-The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
-Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then
-\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-
-In addition, it follows that the convolution product $\ast$ can be explicitly characterized as
-
-\begin{equation}
-    \tilde{\psi}\ast\Tilde{\phi}=\int_0^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
-\end{equation}
-
-the proof is a simple computation, and we refer to  \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}.
-\begin{lemma}
-    Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\tau} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\tau-1} \rbrace$, with inverse given by the formal Laplace transform.
-\end{lemma}
-\begin{proof}
-    Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then  
-\begin{align*}
-\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
-\end{align*}
-
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
-which grows as $n(n+1)^{-\tau} A^{n+1}$.
-\begin{verify}
-    we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
-\end{verify}
-\end{proof}
-
-The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_\alpha B$ and let $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$
-
-\[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=\series{\psi}\ast \series{\phi}=\int_{0}^{\zeta_\alpha}\series{\psi}(\zeta_\alpha-\zeta')\series{\phi}(\zeta')d\zeta'\]
-
-Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_0 B$, we define  \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}\]
-then $\ast_\alpha$ can be explicitly written as
-
-\begin{equation}
-    \tilde{\psi}\ast_\alpha\Tilde{\phi}=\int_\alpha^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
-\end{equation}
-where $\series{\phi}=\borel_\zeta\series{\Phi}$ and $\series{\psi}=\borel_\zeta\series{\Psi}$.
-We also introduce the unit $\delta_\alpha$ as \[\delta_\alpha\ast_\alpha\borel_\zeta\series{\Phi}=\borel_\zeta(1\cdot\series{\Phi})=\borel_\zeta\laplace_{\zeta,\alpha}\phi=\phi\]
-thus $\delta_\alpha\ast_\alpha\phi=\phi\ast_\alpha\delta_\alpha=\phi$.
-
-\begin{remark}
-We notice that properties (i) and (ii) are special cases of the convolution product:
-\begin{align*}
-\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \tilde{\phi}\\
-&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\tilde{\phi}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\int_0^1(t\zeta)^{-\tau-1}(\zeta-t\zeta)^k\zeta dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\alpha}\int_0^1 t^{-\tau-1}(1-t)^k dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\tau}\frac{\Gamma(k+1)\Gamma(-\tau)}{\Gamma(k-\tau+1)}\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\tau} \zeta^k \\
-&=\partial_\zeta^\tau\tilde{\phi}
-\end{align*}
-\end{remark}
-
-\begin{remark}
-We can express the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
-
-We first assume $\series{\Phi}=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, then for every $\lambda\in (0,\infty)$
-\begin{align*}
-    \borel_\zeta(z^{-\lambda}\series{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta z^{-\lambda}\ast_\alpha\phi
-\end{align*}
-hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\phi.\]
-
-%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
-Then, we assume $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ and we get for every $\lambda\in (0,\infty)$
-\begin{multline*}
-    \borel_{\zeta_\alpha}(z^{-\lambda}\series{\Phi})=\borel_{\zeta_\alpha}(z^{-\lambda}\laplace_{\zeta_\alpha,0}\phi)=\borel_{\zeta_\alpha}(\laplace_{\zeta_\alpha,0}\partial_{\zeta_\alpha,0}^{-\lambda}\phi)=\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha} (\zeta_\alpha-t)^{\lambda-1}\phi(t+\alpha)dt\\
-    =\borel_{\zeta_\alpha}(z^{-\lambda})\ast\phi(\zeta_\alpha+\alpha)
-\end{multline*}
-hence, recalling $\zeta=\zeta_\alpha+\alpha$ \[\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}\]
-
-Finally, recall that for every $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
-$\fracderiv{-\lambda}{\zeta_\alpha}{0}\varphi$ coincide, therefore 
-\begin{align}\label{change_chart_convolution}
-    \borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}
-\end{align}
-in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $\alpha\in B$.
-\end{remark}
-
-%\subsection{Differential equation}
-%\textcolor{orange}{Should we keep this section?}
-%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-%\begin{equation}%%\label{laplace:op}
-%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-%\end{equation}
-%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-%\subsubsection{Regularity}
-
-%We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
-
-%\begin{lemma}\label{lemma-3.5}
- %   Let $R_0>0$.
-Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$.
-Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
-  %  \begin{equation}
-   %     |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
-   % \end{equation}
-%\end{lemma}
-
-%\begin{proof}
- %   The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
-By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$.
-The formal Borel transform of $f$ reads
-  %  \begin{align*}
-   %     \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
-    %\end{align*}
-   %and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
-   %\begin{align*}
-    %   |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
-    %   &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
-   %    &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
-    %   &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
-   %\end{align*}
-
-  % This ensures uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
-   %\color{Turquoise}
-%In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
-%\begin{align*}
- %   \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-  %  &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-   % &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
-   % &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
-%\end{align*}
-%   \color{black}
-%\end{proof}
-
-%\begin{lemma}\label{lemma-3.8}
- %   Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
-  %  \begin{equation}\label{eqn:convolution}
-   %     \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
-   % \end{equation}
-   % has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
-In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-%\end{lemma}
-
-%We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
-
-%\begin{proof}
- %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
-If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
-Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-  %  \begin{equation}
-        %\tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
-   % \end{equation}
-   % This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
-Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
-By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-%\end{proof}
-
-%\begin{lemma}\label{lemma-3.8bis}
- %Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
-Then, the convolution equation
- %   \begin{equation}\label{eqn:convolution-bis}
-  %      \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
-   %\end{equation}
-    %has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
-In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-%\end{lemma}
-
-%\begin{proof}
- %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
-If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
-Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-  %  \begin{equation}
-   %     \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
-    %\end{equation}
-    %where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
-This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
-Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
-By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-%\end{proof}
-
-%\begin{remark}
- %   Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
-%\end{remark}
-
-\section{Proof of main results}
-\subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-
-\subsubsection{Setting}\label{setting-ODE}
-\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
-\begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
-such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
-\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
-\end{itemize}
-
-For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
-\begin{itemize}
-\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$.
-In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$.
-Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
-\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}.
-\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_j$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
-Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
-\end{itemize}
-
-\begin{figure}
-\center
-\begin{tikzpicture}
-\newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
-  (-\spill, -\spill) (\spill, \spill)
-  (0, 0) -- (160:\spill)
-  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
-  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
-  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
-  arc (-60:-130:\spill) -- (0, 0);
-\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
-\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\alpha_k$};
-\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill \p circle (0.7mm);
-}
-\end{tikzpicture}
-\caption{The domain $\Omega_j$}\label{Fig:domain}
-\end{figure}
-\subsubsection{Main results}
-%As a consequence of Theorem 4 in {\tt reg-volterra} we get 
-%
-%\begin{theorem}\label{thm1-dim}
-%In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-%\begin{equation}\label{P-hat_j}
-%\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
-%\end{equation}
-%such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-%${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
-%\end{theorem}
-
-\begin{theorem}\label{thm2-dim}
-%For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
-For every $j=1,...,d$, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$.
-Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
-\end{theorem}
-\begin{proof}
-We divide the proof into the following steps:
-\begin{itemize}
-\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$.
-\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
-\end{itemize}
-
-Step $(b)$ clearly follows from \cite[Theorem 4]{reg-sing-volterra} and step $(a)$.
-In fact, $\Tilde{\psi}_j$ and ${\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
-Then, we can Laplace transform ${\psi}_j$ along a ray $\Gamma_{\alpha_j}^\theta$ in $\Omega_j$.
-Hence if $\hat{\psi}_j$ denotes the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$, we can Laplace transform $\hat{\psi}_j$ along $\Gamma_{\alpha_j}^\theta$, too.
-
-We now prove step $(a)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$.
-Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.
-
-%First notice that if $\series{\Psi}_j=e^{-\alpha_jz}\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
-
-%\begin{equation}
-%\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
-%\end{equation}
-
-%Hence
-
-%\begin{
-
-%Then we take the (formal) Borel transform $\borel_\zeta$ of  $\mathcal{P}_j \sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$
-
-\begin{align*}
-  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_j\right)&= \left[P(-\zeta)+1\ast_{\alpha_j} Q(-\zeta)+\zeta \ast_{\alpha_j} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha_j}(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\
-  &=\left[P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha_j} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j} )(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\&=\hat{P}_j\tilde{\psi}_j(\zeta_j)
-\end{align*}
-%\begin{multline*}
-%\borel_\zeta\left(\mathcal{P}\series{\Psi}_j\right)=\borel_\zeta\left[e^{-\alpha_j z}\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right]=\\
-%\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
-%\left[P(-\zeta)+\partial_{\zeta_j,0}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
-%\end{multline*}
-%where 
-%
-%\begin{align*}
-%\series{\psi}_j(\zeta_j):=\borel\series{\Psi}_j(\zeta_j)&=\borel\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\borel\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
-%&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
-%\end{align*}
-
-Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0. 
-\end{proof}
-
-%\color{Turquoise}
-%\begin{lemma}\label{step a}
-%    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
-%\end{lemma}
-
-%\begin{proof}
- %   We’ll prove the following: 
-  %  \begin{itemize}
-   %     \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
-    %    \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
-    %\end{itemize}
-    %The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-In fact, we can prove this statement using a perturbative method that goes back to \'Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
-Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
-   % \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
-   % \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero
-
-    %\begin{align*}
-     %   &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
-      %  &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
-       % &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
-    %\end{align*}
-    %If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
-    %\begin{align*}
-     %   f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
-      %  &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
-    %\end{align*}
-    %Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
-
-    %\begin{align*}
-     %   \left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)\right]f_{j,n}=-\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r f_{j,n-1}
-    %\end{align*}
-    %and since $R_r$ is entire, the right-hand side is an infinite sum of the convolution product of an entire function with $f_{j,n-1}$, hence it  has the same singularities as $f_{j,n-1}$ (see Lemma 6.15 \cite{diverg-resurg-i}).
-Therefore, we deduce $f_{j,1}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$ and inductively, $f_{j,n}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$.
-
-    %Let $\theta$ be the direction that avoids all the singularities, we now prove that the analytic continuation of $\hat{\psi}_j$ grows sub-exponentially.
-In fact, it is enough to adapt the Gr\"onwall lemma to integral equations (see Lemma 3.9 \cite{diverg-resurg-iii}]).
-   %Let $\Omega$ be the open domain where $\hat{\psi}_j$ is analytic and let $p$ be a point in $\Omega$ such that $\Omega':=\Omega\setminus B_{r}(\alpha_j)$ is star-shaped from $p$ ($B_r(\alpha_j)$ is the ball of radius $r$ and center in $\alpha_j$).
-By assumption on the coefficients of the ODE \eqref{eqn:standard ODE}
-   %\begin{align*}
-    %   a:=\sup_{\zeta\in\Omega'}\frac{|Q|(|\zeta|)}{|P(-\zeta)|}<\infty\, \qquad b:=\sup_{\zeta\in\Omega'}\frac{1}{|P(-\zeta)|}<\infty
-   %\end{align*}
-   %hence, for every $\zeta\in\Omega'$, writing $\xi=|\zeta|$ and $\zeta=p+\xi e^{i\eta}$
-   %\begin{align*}
-    %|\hat{\psi}_j(\zeta)|&\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-     %  &\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-      % &\qquad +c\left[\int_{|\alpha_j|}^{|p|}|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|} \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-      % &\qquad + a'\int_{|\alpha_j|}^{|p|}|\hat{\psi}_j(\rho e^{i\theta})|d\rho+ c\sum_{r=0}^{d-1}\int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot  \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho%\\
-      % %&\leq a \int_{|\alpha_j|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho \\
-      % %&=a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|p|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho+\\
-      % %&\qquad + a \int_{|\alpha_j|}^{|p|}  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho
-   %\end{align*}
-   %where $\hat{R}_r=\borel(z^{-2}R_r)$, for every $r=0,...,d-1$. 
-   %%For every $r=0,...,d-1$, we define $F_r(z)=R_r(z)$
-   %We want to show that for every $m\geq 0$, $|\hat{\psi}_j(\zeta)|<\hat{W}_m(\xi)$ for $\zeta$ on the ray $\zeta=p+\xi e^{i\theta}\in\Omega'$, where $\hat{W}_m$ is the unique solution of
-
-   %\begin{equation}
-    %   \hat{W}=m+a\ast_{|p|}\hat{W}+c\sum_{r=0}^{d-1}\hat{R}_r\ast_{|p|} (-\zeta^r\hat{W})
- %  \end{equation}
-
- %  \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them.
-This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
-  % There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$.
-Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$?
-}
-%\end{proof}
-
-\subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
-
-\subsubsection{Setting}
-
-Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{x_1,...,x_N\}$. Set
-\begin{equation}\label{exp-int}
-I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
-\end{equation}
-where $\Lambda_j$ is the thimble associated with the critical point $x_j$.  
-The saddle point approximation gives the formal series 
-\begin{equation}
-{I}_{j}(z)\defeq\int_{\Lambda_j}e^{-zf}\nu\sim \tilde{I}_{j}\defeq e^{-z\alpha_j}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to\infty
-\end{equation}
-
-\textcolor{orange}{[cite or prove]}
-%Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-
-\subsubsection{Main result}
-\begin{theorem}\label{thm:maxim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
-\begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
-\begin{multline}\label{formula1}
-\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
-\end{multline}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-
-Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
-
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$.
-Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
-\textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z f(\alpha_j)} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\Re z \to \infty$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)). Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z f(\alpha_j)} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z f(\alpha_j)} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha_j} I_j(z)$.
-In other words,
-\[ e^{-z \alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-To see why, cut the sum off after $N$ terms, and observe that
-\begin{align*}
-  \Bigg | \sum_{n= 0}^N(2n-1)!!
-b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
-b_{2n}^j n|z|^{-n}.
-\end{align*}
-The right-hand side goes to $0$ as $\Re(z)$ grows.
-%Hence,
-%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{-z\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
-
-Call the right-hand side $\tilde{I}_j$. We now see that $a_{j,n} = (2n-1)!!\,b_{2n}^j$ in the statement of the theorem. %\textbf{[Resolve discrepancy with previous calculation.]}
-
-Note that 
-\begin{align*}
-\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
-
-Part~\eqref{int:resum-valid}: Let us recast the integral $I_j$ into the $f$ plane.
-As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
-Hence, we have
-\begin{align*}
-I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
-& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
-\end{align*}
-Noticing that the right-hand side is a Laplace transform, we learn that
-\begin{equation}\label{thimble-difference}
-\hat{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
-\end{equation}
-%\color{Aquamarine}
-%In \'Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{\iota}_j$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
-[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
-Or something even simpler?]
-%\color{black}
-
-We can rewrite our Taylor series for $\nu$ as
-\begin{align*}
-\nu & = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{n/2}\,\frac{df}{[2(f - f(a_j))]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\hat{\iota}_j$, we learn that
-\begin{align*}
-\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
-& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \\
-& = \borel_{\zeta} \tilde{I}_j.
-\end{align*}
-
-We have now shown that the sum of $\borel_{\zeta} \tilde{I}_j$ is actually equal to $\hat{\iota}_j$.
-
-%Let $\tilde{\Phi}_j\in\C[\![z^{-1}]\!]$ be such that $\tilde{I}_j(z)=e^{-z\alpha_j}z^{-1/2}\tilde{\Phi}_j(z)$,  
-By the action of $\borel_\zeta$ on transseries (Section \ref{sec:action_transseries}) and the properties of convolution (Section \ref{convolution}) we know 
-\begin{align*}
-\borel_{\zeta} \tilde{I}_j & = \borel_{\zeta}( z^{-1/2} \tilde{\Phi}_j) \\
-&=\borel_\zeta z^{-1/2}\ast_{\alpha_j}\borel_\zeta\tilde{\Phi}_j\\
-& = \fracderiv{-1/2}{\zeta}{\alpha_j}  \tilde{\phi}_j \\
-%& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{align*}
-It follows, from our conclusion above, that
-\begin{equation}\label{shifted-resum-valid}
-\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{\alpha_j} \tilde{\phi}_j.
-\end{equation}
-Taking the Laplace transform of both sides and applying properties of the Borel transform (\S \ref{properties Borel transform}), we see that
-\begin{align*}
-I_j(z) & = \laplace_{\zeta, \alpha_j} \left[ \partial^{-1/2}_{\zeta, \alpha_j}  \tilde{\phi}_j \right] \\
-& = z^{-1/2} \laplace_{\zeta, \alpha_j} \tilde{\phi}_j,
-\end{align*}
-as we claimed. \textcolor{cyan}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
-
-Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j. \]
-
-Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{\iota}_j(\zeta) = \partial_\zeta \left( \int_{\Lambda_j(\zeta)} \nu \right), \]
-we can see that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(\textcolor{Magenta}{\alpha_j})} \nu. \]
-The initial value term vanishes because the path $\textcolor{Magenta}{\alpha_j}$ is a point. Hence,
-\[ \int_{\Lambda_j(\zeta)} \nu = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j(\zeta). \]
-Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)} \nu \right) = \hat{\phi}_j(\zeta). \]
-\end{proof}
-
-\begin{remark}
-    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the Borel transform of $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
-Furthermore, expanding $\hat{\phi}_j$ at its critical points we recover the germs $\series{\phi}_k$ for $k\neq j$.
-This is an instance of resurgence, indeed according to the theory of Ecalle, $\hat{\phi}_j$ are all resurgent functions.
-We'll see an example in Section~\ref{sec:eye-res-airy}.
-\end{remark}
-
-\section{Examples}\label{sec:examples}
-
-\subsection{Airy}
-
-The Airy equation is
-\begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
-\end{equation}
-One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
-
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{figures/u_contour_3.pdf}
-    \includegraphics[scale=0.3]{figures/thimble_Airy.png}
-    \caption{\small The contour $\Lambda_1$ in the $u$ plane is represented by the light blue path.
-More generally, the dark blue contour corresponds to the preimage of the ray $+1+e^{i\theta}\infty$ and $\theta=$.
-While the light blue contour corresponds to the preimage of the ray $-1+e^{i\theta}\infty$.
-The gray regions correspond to the preimage of $\Re \zeta> \textcolor{orange}{const}$.
-\textcolor{orange}{[for Aaron: could you please add the correct constant in the description of the figure, and explain what are the different colored regions?
-Thanks]}}
-    \label{fig:path_Airy}
-\end{figure}
-
-With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Lambda_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
-
-By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we’ll go straight to the general case.
-However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
-For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
-
-\subsection{Airy--Lucas}\label{example_AL}
-The Airy-Lucas equation is
-\begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
-\end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda_{j}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$ (see Figure \ref{fig:thimble_n_5}).
-
-\begin{figure}[ht]
-    \centering
-   \includegraphics[scale=0.3]{figures/thimble-n5.png}
-    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.
-The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=???$.
-While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
-    \label{fig:thimble_n_5}
-\end{figure}
-
-\subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
-We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel-rational-AL}
-K(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation
-\begin{equation}\label{eqn:mod-bessel-AL}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, as we’ll see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
-
-Let's put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
-\begin{equation}\label{eqn:reg-mod-bessel-AL}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsubsection{Asymptotic analysis}\label{sec:asympt-AL}
-
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
-From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n}(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp-AL}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-
-The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We’ll see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~4 from \cite{reg-sing-volterra}.
-%\subsection{Going to the spatial domain}\label{spatial-AL}
-\subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (0,1)$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of order $\sigma=1/2$ at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
-
-In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
-For each root $\alpha_j$, we'll find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in Figure \ref{Fig:domain}.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} V_j \]
-where $V_j = \laplace_{\zeta_j, 0} v_\alpha$ and $\zeta = \alpha_j + \zeta_j$.
-We can see from Section~\ref{reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} z^{-\tau_j} W_j, \]
-makes $W_j$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_1)$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel-AL} looks like
-\begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel-AL} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos-AL}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$.
-In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel-AL} the same.
-\subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_j\in\singexpalg{1/2}(\Omega_j)$.
-\color{DarkTurquoise}
-\begin{quote}
-We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
-Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
-\begin{align*}
-v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
-& \Longrightarrow \zeta_j^\epsilon\,\zeta_j^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longrightarrow \zeta_j^{1-\tau}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longrightarrow v_j' / \zeta_j^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longleftrightarrow v_j' \in o\big(\zeta_j^{\tau-1}\big).
-\end{align*}
-In this case, $\tau = \tfrac{1}{2}$.
-\end{quote}
-\color{black}
-
-The Poincar\'{e} algorithm, as we saw in Section~\ref{sec:asympt-AL}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket$.
-We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-
-The Borel transform maps $e^{-\alpha_j z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ for $\alpha = 1$ and $\alpha = -1$, respectively.
-
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}.
-It therefore has exactly one solution in $\singexpalg{1/2}$, up to scaling.
-That means $\borel\big[ e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j \big]$ must sum to a scalar multiple of $v_j$.
-Thus, if $e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha_j} v_j$.
-
-\subsubsection{Confirmation of Borel regularity}\label{confirmation-borel-regularity}
-We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
-We found in Section~\ref{sec:asympt-AL} that
-\begin{align*}
-\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
-Computing
-\begin{align*}
-\borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
-we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
-Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-In fact, with the thimble projection reasoning, there is no ambiguity in the choice of the multiplicative constant.
-
-Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
-Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
-
-\subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
-\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
-We follow the reasoning of the proof of Theorem~\ref{thm:maxim}.
-We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]}
-
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2  \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta %\\
-%& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane, slightly off from the critical value $\zeta=1$.}
-\end{center}
-
-Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$:
-
-\begin{align*}
-    \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))}&=\frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
-    &=\frac{\sin(m\phi)}{\sin(n \phi)}\\
-    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};\sin^2(n \phi)\right)\\
-    &=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right) 
-\end{align*}
-where in the last step we use $-\zeta=T_n(u)=T_n(\cos\phi)=\cos(n\phi)$. Applying identity 15.8.4, 15.8.27 and 15.8.28 from \cite{dlmf},
-
-\begin{align*}
-    &{}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right)=\\
-    &\qquad = \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right)\Gamma\left(1+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{1}{2};\zeta^2\right)+\\
-    &\qquad \qquad\qquad - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2}-\frac{m}{2n}\right)\Gamma\left(\frac{1}{2}+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(1-\frac{m}{2n},1+\frac{m}{2n};\frac{3}{2};\zeta^2\right)\\
-    &\qquad ={}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)+\\
-    &\qquad\qquad +\frac{1}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)-\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\\
-    &\qquad =\frac{3}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
-\end{align*}
-In addition, recall that ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ has a branch cut singularity at $\zeta=-1$ while ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ has a branch cut at $\zeta=1$; hence
-
-\begin{align*}
-    K_{m/n}(z)&=-\frac{m}{4 n\sinh(\tfrac{m}{n}i\pi)}\int_{\gamma_z}e^{-z\zeta} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) d\zeta\\
-    &=-\frac{1}{2}\int_{1}^{+\infty}e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right) d\zeta
-\end{align*}
-
-where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.
-
-Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
-\begin{align*}
-    K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
-\end{align*}
-
-\subsubsection{A flavor of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
-
-In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
-In both cases we find
-\begin{align*}
-    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
-\end{align*}
-which has a fractional power singularity at $\zeta=1$.
-In addition, the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.
-More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$.
-Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
-\begin{align*}
-&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
-&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
-\end{align*}
-Hence, we deduce  
-\begin{equation}\label{resurgent-relation-1}
-    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
-\end{equation}
-namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
-This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.
-Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
-The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
-
-We can repeat the same reasoning with $v_{-1}$:
-\begin{align*}
-    v_{-1}(\zeta)=  \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
-\end{align*}
-and ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ is singular at $\zeta=1$. Hence
-\begin{align*}
-&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right)=\\
-&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
-&=2 i\cos(\pi m/n) \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
-&=2i \cos(\pi m/n)\, \left(\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right)
-\end{align*}
-and the analogue of \eqref{resurgent-relation-1} is 
-\begin{equation}\label{resurgent-realtion-2}
-    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
-\end{equation}
-Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are a manifestation of the Stokes phenomena, already in the position domain.
-Indeed, when we start varying the contour of integration for the Laplace transform, we know that $\laplace_{\zeta,1}^\pi$ and $\laplace_{\zeta,-1}^0$ are not well defined because the contour hits the other singularity (respectively at $\zeta=-1$ and $\zeta=1$).
-The Stokes phenomenon consists of comparing the Laplace transform below and above the critical direction and it quantifies the jump as a constant (the so-called Stokes constant) times another function.
-In our example:
-\begin{align*}
-    \laplace_{\zeta,1}^{\pi+\varepsilon} v_1-\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = 2 i \cos(\pi m/n) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
-    \laplace_{\zeta,-1}^{\varepsilon} v_{-1}-\laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = - 2 i \cos(\pi m/n)  \, e^z \, \laplace_{\zeta,1} v_{1} 
-\end{align*}
-thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$\footnote{If we think of the Laplace transforms of $v_1$ and $v_{-1}$ as a frame of solutions for the Airy--Lucas differential equation, the equations above define the so-called Stokes matrices for the ODE.}.
-
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Section \ref{sec:Picard-Lefschetz}.
-However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
-\textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
-
-%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
-%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-
-%The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-%\begin{align*}
-%& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-%= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-%\end{align*}
-%as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
-Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-%\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-%\color{DarkCyan}
-%Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-%\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-%In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-%\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-%where $\zeta = -1 + \zeta_{-1}$.
-%\color{black}
-
-\subsection{Modified Bessel}\label{sec:mod-bessel-lift}
-
-The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
-\begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
-\end{equation}
-and a basis of solutions is given by the modified Bessel functions (see formulas~10.27.4 and 10.32.12 from \cite{dlmf} \textcolor{red}{10 \cite{watson1922treatise}}) 
-\begin{align*}
-I_{\mu}(z)&=\frac{1}{2\pi i}\int_{\Omega} e^{z\cosh t - \mu t} dt \\
-K_{\mu}(z)&=\frac{\pi}{\sin(\mu \pi)}\cdot \frac{1}{2}[ I_{-\mu}(z) - I_{\mu}(z)]\\
-\color{red}K_{\mu}(z)& \color{red}=\int_{-\infty+i\pi/2}^{+\infty+\pi i/2} e^{-\cosh(t)+\mu t} dt \text{  for } -1<\Re \mu<1
-\end{align*} 
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ (see Figure \ref{fig:Omega_path}).
-\begin{figure}[ht]
-\center
-\begin{tikzpicture}
-        \draw[->] (0,2)--(4,2);
-        \draw[->] (2,0)--(2,4);
-        \draw[red,very thick,->] (4,1.5)--(3,1.5);
-        \draw[red,very thick] (3,1.5)--(2,1.5);
-        \draw[red,very thick] (4,2.5)--(3,2.5);
-        \draw[red,very thick,->] (2,2.5)--(3,2.5);
-        \draw[red,very thick] (2,1.5)--(2,2.5);
-        \node[red,below, font=\tiny] at (4,1.5) {$\Omega$};
-        \node[font=\tiny,left,below] at (1.75,1.5) {$-i\pi$};
-        \node[font=\tiny] at (1.8,2.5) {$i\pi$};
-\end{tikzpicture}
-\caption{The path $\Omega$. }\label{fig:Omega_path}
-\end{figure}
-On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results: 
-\begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions $K_{\mu}\sim e^{-z} z^{-1/2} \tilde{W}_{\mu, 1}$ and $I_{\mu} \sim e^z z^{-1/2} \tilde{W}_{\mu, 2}$ with
- \begin{align*}
- \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \tilde{W}_{\mu,2} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
-\end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-
-\begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_{1}\big)\\
-v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
-\item \textbf{Borel regularity} We can compare the Borel transform of the formal solutions $\tilde{W}_{\mu,\pm1}$ with the analytic solutions $v_{\mu,\pm 1}$.
-They agree (up to the choice of a constant), hence we have another example where Borel regularity can be checked explicitly.
-\end{itemize}
-
-The thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we’ll discuss in the following Section~\ref{countable-cover}.
-
-\subsubsection{Lifting to a countable cover}\label{countable-cover}
-Formula~\eqref{integral:mod-bessel-rational-AL} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
-Lifting to a countable cover reveals this formula as a special case of a general integral formula for modified Bessel functions.
-
-Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
-\cosh(n\tau) & := T_n(\cosh(\tau)) \\
-\sinh(m\tau) & := U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
-we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
-\begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Omega}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
-\end{align}
-For any $\mu \in \C \smallsetminus \Z$, 
-\begin{align}
-\notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-\notag & = \frac{1}{2i \sin(\mu \pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt \\
-& \label{int:mod-bessel-gen} = \frac{1}{2 \sinh(\mu\,i\pi)} \int_\Omega \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{align}
-where $\Omega$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$.
-The integral converges when $z$ is in the right half-plane.
-We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-
-\begin{center}
-    \begin{tikzpicture}
-        \draw[->] (6,2)--(10,2);
-        \draw[->] (8,0)--(8,4);
-        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
-        %\draw[red,thick,->] (10,2)--(9,2);
-        %\draw[red,thick] (9,2)--(8.5,2);
-        %\draw[red,thick] (10,2)--(9.3,2);
-        %\draw[red,thick,->] (8.5,2)--(9.3,2);
-        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
-        \node[font=\tiny,below] at (8.5,2) {$1$};
-    \end{tikzpicture}
-\end{center}
-
-We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
-
-\begin{align*}
-    K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
-    &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
-\end{align*}
-
-where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf}
-
-\begin{multline*}
-     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) = \\
-     =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
-\end{multline*}
-hence
-
-\[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
-
-Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
-
-\begin{align}
-    K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
-    &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
-\end{align}
-
-When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
-
-\begin{equation}
-    K_0(z)=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
-\end{equation}
-\textcolor{orange}{[can we use (51) directly?
-It seems to me that if I try the thimble projection reasoning from the integral expression directly, I'm not able to write $1/\sinh(it)$ as a function of $\zeta$.
-]}
-
-\subsection{Generalized Airy}
-
-\textcolor{magenta}{[The generalized Airy example is not completed and there are still some difficulties in the computations.
-In particular, the thimble integral interpretation is missing Should we remove it?]}
-
-In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k(z), B_0(z), B_k(z)$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as contour integral \cite[Section 9.13(ii)]{dlmf}
-
-\begin{align*}
-\mathrm{A}_k(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(z,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
-\mathrm{B}_k(z,p)&=\int_{\gamma_k}e^{zt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
-\end{align*}
-where the contours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}
-
-\begin{figure}
-\center
-\begin{tikzpicture}
-    \draw[->] (4,0)--(4,8);
-    \draw[->] (0,4)--(8,4);
-    \draw[blue,very thick] (4,4) circle (0.5) ;
-    \node[blue,font=\tiny] at (4.5,3.5) {$\Gamma_0$};
-    \node[red,font=\tiny] at (1.4,1.3) {$\Gamma_1$};
-    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
-    \node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
-    \draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
-     \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
-    \draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
-    \draw[orange,very thick,->] (4,4)--(6.5,4);
-    \draw[orange,very thick] (6.5,4)--(8,4);
-    \node[orange,font=\tiny,below] at (7,4) {$\gamma_1$};
-    \draw[orange,very thick,->] (4,4)--(2.7,6);
-    \draw[orange,very thick] (2.7,6)--(1.4,8);
-    \node[orange,font=\tiny,right] at (2.2,6) {$\gamma_2$};
-    \draw[orange,very thick,->] (4,4)--(2.7,2);
-    \draw[orange,very thick] (2.7,2)--(1.4,0);
-    \node[orange,font=\tiny,right] at (2.2,2) {$\gamma_3$};
-    \node at (5.1,4) {$\bullet$};
-    \node at (2.9,4) {$\bullet$};
-    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
-    \node[font=\tiny,below] at (5.3,4) {$1$};
-    \end{tikzpicture}
-    \caption{Representation of the path of integration for $A_k,B_0,B_k$ respectively in red, blue and orange.}\label{fig:path-generalized-Airy}
-\end{figure}
-
-Each generalized Airy function is a solution of
-
-\begin{equation}
-\left[\partial_z^3-z\partial_z+(p-1)\right]f(z,p)=0
-\end{equation} 
-and if $p=0$ they reduced to the classical Airy functions: $\mathrm{Ai}(z)=\mathrm{A}_1(z,0)$ and $\mathrm{Bi}(z)=\mathrm{B}_1(z,0)$.
-
-We define the following exponential integral: let $p\geq 0$, $f(t)=4t^3-3t$ and $\nu_p=\tfrac{dt}{t^p}$.
-The critical points of $f$ are $\alpha_{\pm}:=\pm\tfrac{1}{2}$ (as for the classical Airy case), however the volume form $\nu_p$ is meromorphic
-\begin{equation}
-I_\pm(z,p)\defeq\frac{1}{2\pi i}\int_{\Lambda_{\pm}}e^{-z(4t^3-3t)}\frac{dt}{t^p}
-\end{equation}
-where $\Lambda_{\pm}$ are the paths through the points $\alpha_\pm$, starting and ending at infinity (as in Figure \ref{fig:path-generalized-Airy-Lambda+-}).
-\begin{figure}
-\center
-\begin{tikzpicture}
-    \draw[->] (4,0)--(4,8);
-    \draw[->] (0,4)--(8,4);
-    \node[red,font=\tiny] at (1.4,1.3) {$\Lambda_-$};
-    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
-    %\node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
-    %\draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
-    % \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
-    %\draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
-    \node[red,font=\tiny] at (7.4,1.3) {$\Lambda_+$};
-    \draw[red,very thick,->] (7,0.2) .. controls (4.5,4) .. (7,7.8);
-    \node at (5.1,4) {$\bullet$};
-    \node at (2.9,4) {$\bullet$};
-    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
-    \node[font=\tiny,below] at (5.3,4) {$1$};
-    \end{tikzpicture}
-    \caption{The paths of integration $\Lambda_\pm$ for $I_{\pm}$.}\label{fig:path-generalized-Airy-Lambda+-}
-\end{figure}
-In particular, $I_{+}(z,p)=(12 z)^{\tfrac{p-1}{3}}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)$: 
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\Lambda_{+}}e^{-z(4t^3-3t)}\frac{dt}{t^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-z(z^{-1}\frac{s^3}{3}-3 (12 z)^{-1/3}s)}\frac{ds}{s^p} & t=(12 z)^{-\tfrac{1}{3}}s\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{-1/3}\Lambda_{+}}e^{-\left(\frac{s^3}{3}-(\tfrac{3}{2} z)^{2/3}s\right)}\frac{ds}{s^p} & \\
-&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
-\end{align*}
-It follows that $I_+(z)$ is a solution of
-\begin{equation}\label{eq:I}
-\left[\partial_z^3-\partial_z+\frac{2-p}{z}\partial_z^2+\frac{p-1}{z}+\frac{-1-3p+3p^2}{9}\frac{\partial_z}{z^2}+\frac{3+p-3p^2-p^3}{27z^3}\right]I_+(z,p)=0
-\end{equation}
-From the general theory of linear ODE, the formal integral solution of \eqref{eq:I} is a linear combination of three generators 
-\begin{equation}
-U_1z^{p-1}\tilde{W}_1(z)+U_2e^{-z}z^{-1/2}\tilde{W}_2(z)+U_3e^{z}z^{-1/2}\tilde{W}_3(z)
-\end{equation}
-where $\tilde{W}_1, \tilde{W}_2$ and $\tilde{W}_3$ are formal power seirs $\tilde{W}_{\mathbf{k}}(z)=\sum_{j\geq 0}a_{\mathbf{k},j}z^{-j}$, which are the unique (we fix $a_{k,0}=1$ for $k=1,2,3$) solution of
-\begin{multline}\label{w1}
-\left[\partial_z^3-\partial_z-\frac{1-2p}{z}\partial_z^2+\frac{17-30p+12p^2}{9z^2}\partial_z+\frac{8}{27}\frac{p^3-6 p^2+ 11p- 6}{z^3}\right]\tilde{W}_1(z)=0
-\end{multline}
-\begin{multline}\label{w2}
-\left[\partial_z^3-3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2-\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.-\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_2(z)=0
-\end{multline}
-\begin{multline}\label{w3}
-\left[\partial_z^3+3\partial_z^2+2\partial_z+\frac{1-2p}{2z}\partial_z^2+\frac{1-2p}{z}\partial_z+\frac{5+24p+12p^2}{36z^2}\partial_z+\right.\\
-\left.+\frac{5+24p+12p^2}{36z^2}-\frac{1}{z^3}\left(\frac{5}{24}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\right]\tilde{W}_3(z)=0
-\end{multline}
-Let us first study equation \eqref{w1}: its Borel transform is
-\begin{multline*}
--\zeta^3\tilde{w}_1+\zeta\tilde{w}_1-(1-2p)\int_0^\zeta\tilde{w}_1(t)t^2dt+\frac{(17-30p+12p^2)}{9}\int_0^\zeta(-t\tilde{w}_1(t))(\zeta-t)dt+\\
-+\frac{8}{27}(p^3-6p^2+11p-6)\int_0^\zeta\tilde{w}_1(t)\frac{(\zeta-t)^2}{2}dt=0
-\end{multline*}
-We differentiate three times, getting 
-\begin{multline*}
-\left(\zeta-\zeta^3\right)\tilde{w}_1^{(3)}(\zeta)+\left(3-2(5-p)\zeta^2\right)\tilde{w}_1''(\zeta)-\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\zeta\tilde{w}_1'(\zeta)+\\
-+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\tilde{w}_1(\zeta)=0
-\end{multline*}
-we set $y=\zeta^2$
-%\begin{multline}
-%\left[-4y(y-1)(2y\partial_y^3+3\partial_y^2)+3(4y\partial_y^2+2\partial_y)-2(5-p)y(4y\partial_y^2+2\partial_y)+\right.\\
-%\left.-2y\left(\frac{215}{9}-\frac{34}{3}p+\frac{4}{3}p^2\right)\partial_y+\frac{8}{27}\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\left(p-\frac{5}{2}\right)\right]\tilde{w}_1(y)=0
-%\end{multline}
-\begin{multline}\label{eq:hw1}
-y^2(1-y)\tilde{w}_1^{(3)}(y)+y\left((p-\frac{13}{2})y+3\right)\tilde{w}_1''(y)-\left(y\left(\frac{305}{36}-\frac{10}{3}p+\frac{p^2}{3}\right)-\frac{3}{4}\right)\tilde{w}_1'(y)+\\
-+\frac{1}{27}\left(p-\frac{5}{2}\right)\left(p-\frac{9}{2}\right)\left(p-\frac{7}{2}\right)\tilde{w}_1(y)=0
-\end{multline}
-which is a generalized hypergeometric equation  \cite[Equation 16.8.5]{dlmf} with parameters
-\begin{align*}
-\mathbf{a}_0=\left(\frac{3}{2}-\frac{p}{3};\frac{7}{6}-\frac{p}{3};\frac{5}{6}-\frac{p}{3}\right) & \qquad\qquad \mathbf{b}_0=\left(\frac{1}{2};\frac{3}{2}\right)
-\end{align*}
-therefore, $\tilde{w}_1(y)=c_1\,\,{}_3F_2\left(\mathbf{a}_0;\mathbf{b}_0;y\right)$. 
-Then we look at equation \eqref{w2}: its Borel transform is
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)-3\zeta^2\tilde{w}_2(\zeta)-2\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt-(1-2p)\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
--\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline} 
-and taking three derivatives it simplifies to 
-\begin{multline}
-\left[\left(\zeta^3+3\zeta^2+2\zeta\right)\partial_\zeta^3 +6\partial_\zeta^2+\left(p-\frac{17}{2}\right)\zeta\left(\zeta+\frac{1}{2}\right)\partial_\zeta^2+\right.\\
-\left.
-\left(\frac{p^2}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(\zeta+1\right)\partial_\zeta+\frac{1}{27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(\zeta)=0
-\end{multline}
-define $y=\zeta\left(\zeta+\frac{4}{3}\right)$
-\begin{multline}\label{eq1}
-\left[y\left(y+\frac{4}{9}\right)^2\partial_y^3+2\left(\frac{3}{2}y+\frac{4}{3}+\frac{y}{2}\left(\frac{17}{2}+p\right)\right)\left(y+\frac{4}{9}\right)\partial_y^2+\left(\frac{2}{3}+\frac{y}{4}\left(\frac{17}{2}+p\right)\right)\partial_y\right.\\
-\left.+\frac{1}{4}\left(\frac{p^3}{3}+\frac{14}{3}p+\frac{581}{36}\right)\left(y+\frac{4}{9}\right)\partial_y+\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(y)=0
-\end{multline}
-which now looks like a generalized hypergeometric equation. Indeed setting $t=\tfrac{9}{4}y+1$, \eqref{eq1} reads
-\begin{multline}
-\left[t^2(1-t)\partial_t^3-t\left(\big(\frac{23}{4}+\frac{p}{2}\big)t-\frac{p}{2}-\frac{11}{4}\right)\partial_t^2-\left(-\frac{5}{8}-\frac{p}{4}+t\Big(\frac{887}{144}+\frac{17}{12}p+\frac{p^2}{12}\Big)\right)\partial_t +\right.\\
-\left. -\frac{1}{8\cdot 27}\left(p+\frac{7}{2}\right)\left(p+\frac{11}{2}\right)\left(p+\frac{15}{2}\right)\right]\tilde{w}_2(t)=0
-\end{multline}
-hence a solution is given by the generalized hypergeometric function ${}_3F_2\left(\mathbf{a};\mathbf{b};y\right)$ with parameters
-\begin{align*}
-\mathbf{a}=\left(\frac{5}{4}+\frac{p}{6};\frac{7}{12}+\frac{p}{6};\frac{11}{12}+\frac{p}{6}\right) & \qquad\qquad \mathbf{b}=\left(\frac{1}{2};\frac{5}{4}+\frac{p}{2}\right)
-\end{align*}
-and we denote $\hat{w}_2(\zeta)=c_2\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta+1\right)^2\right)$.
-The equation \eqref{w3} differs from \eqref{w2} for few signs: we find that its Borel transform is
-\begin{multline}
--\zeta^3\tilde{w}_2(\zeta)+2\zeta^2\tilde{w}_2(\zeta)-\frac{8}{9}\zeta\tilde{w}_2(\zeta)+\frac{1-2p}{2}\int_0^\zeta t^2\tilde{w}_2(t)dt+\frac{2-4p}{3}\int_0^\zeta(-t\tilde{w}_2(t))dt+\\
-+\frac{5+24p+12p^2}{36}\int_0^\zeta(\zeta-t)(-t\tilde{w}_2(t))dt
-+\frac{5+24p+12p^2}{54}\int_0^\zeta(\zeta-t)\tilde{w}_2(t)dt +\\
--\left(\frac{5}{54}+\frac{59}{108}p+\frac{5}{18}p^2+\frac{1}{27}p^3\right)\int_0^\zeta\frac{(\zeta-t)^2}{2}\tilde{w}_2(t)dt=0
-\end{multline}
-and differentiating three times we find a generalized hypergeometric equation with parameters $\mathbf{a},\mathbf{b}$ in the variable $y=\left(\tfrac{3}{2}\zeta-1\right)^2$, i.e.
-$\hat{w}_3(\zeta)= c_3\,\, {}_3F_2\left(\mathbf{a};\mathbf{b};\left(\tfrac{3}{2}\zeta-1\right)^2\right)$.
-In particular,
-\begin{equation}
-\hat{w}_3(\zeta)=C_{23}\hat{w}_2(\zeta-\tfrac{4}{3})
-\end{equation}
-\textcolor{orange}{we may try to do the computations of Stokes constants for $p=1$, when $\hat{w}_1$ simplifies to a Gauss hypergeometric.
-Use also information about the monodromy.
-Check change of coordinates $y=\zeta^2$.}
-\subsubsection{Thimble projection formula}
-In Theorem \ref{thm:maxim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral. 
-\subsection{Third-order thimble integrals}
-Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
-Furthermore, we can restrict to monic polynomials by setting $a_3=1$.}, we are going to consider thimble integrals of the form
-
-\[ I_j(z) = \int_{\Lambda_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
-
-where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
-We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$.
-\footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}
-Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:
-\begin{itemize}
-    \item \textbf{Action of translations:} let $q\in\C$, post-composing with translation of $q$ maps $f\to f+q$, thus 
-    \begin{align*}
-        \int_{\Lambda_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
-    \end{align*}
-    \item  \textbf{Action of scaling-rotations:} let $\gamma\in\C$, post-composing with scaling-rotations by $\gamma$ maps $f\to \gamma\cdot f$, thus 
-    \begin{align*}
-        \int_{\Lambda_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
-    \end{align*}
-\end{itemize}
-In particular, we can always reduce to study the thimble integral in simpler situations. 
-As an example, every degree three polynomial with distinct critical points can be transformed in the Chebyshev polynomial $T_3(t)=4 t^3-3t$, implying that the thimble integral $I_+$ can be transformed into the Airy--Lucas integral with parameter $m=1, n=3$.
-This follows by post-composing $f$ with a translation of $-q$ followed by a scaling-rotation of $\frac{ -i 3^{3/2}}{2 p^{3/2}}$
-\begin{align*}
-    f-q &= u^3 + pu \\
-    (f-q) \cdot \frac{ -i 3^{3/2}}{2 p^{3/2}} &= 4 \Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big)^{3} - 3\Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big) \\
-    &= 4 t^3- 3t 
-\end{align*}
-with $t= \sqrt{-\frac{3}{p}} \frac{u}{2}$. Then the thimble integral $I_+$ gets transformed into 
-\begin{align*}
-    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\Lambda_+} e^{z (4t^3-3t)} du\\
-    &= 2\sqrt{-\tfrac{p}{3}} \int_{\Lambda_+} e^{z (4t^3-3t)} dt \\
-    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
-\end{align*}
-In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
-%In both cases, we’ll compute the differential equation satisfied by $I$.
-
-%\begin{lemma}
- %Let $f(u)=u^3+pu+q$, 
-  %  \begin{itemize}
-   %     \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
-    %    \begin{equation}\label{eqn:degree-3-poly-2roots}
-    %        \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
-    %    \end{equation}
-    %    \item  if $p=0$, then $I(z)$ solves
-     %   \begin{equation}\label{eqn:degree-3-poly-1root}
-      %      \left[\partial_z+q+\frac{1}{3z}\right]I=0
-      %  \end{equation}
-    %\end{itemize}
-%\end{lemma}
-%\begin{proof}
- %   The proof follows from a direct computation. 
-%\end{proof}
-
-%Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$.
-Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
-
-%\begin{equation}\label{eqn:deg3-borel-ODE}
- %   \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
-%\end{equation}
-
-%Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes
-
-%\begin{equation*}
- %   \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
-%\end{equation*}
-
-%which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$
-
-%\begin{equation*}
- %   \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
-%\end{equation*}
-
-%and it admits a slight solution \textcolor{red}{the solution should match with the one of airy, so choose $w_2$ in DLMf list and not $w_1$}
-
-%\begin{align*}
- %   v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
-  %  &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
-%\end{align*}
-
-%Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$
-
-%\begin{equation*}
-%    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
-%\end{equation*}
-We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.
-First, notice that $I(z)$ solves
-       \begin{equation}\label{eqn:degree-3-poly-1root}
-          \left[\partial_z+q+\frac{1}{3z}\right]I=0
-       \end{equation}
-and we can find a Borel regular solution following the argument of Section~\ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
-\begin{align*}
-   \left[ (\zeta-q)\partial_\zeta +\frac{2}{3}\right] v=0
-\end{align*}
-namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
-
-The result is confirmed by the thimble projection reasoning which in this simple case reads
-\begin{align*}
-    \int_{\Lambda} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
-    &= e^{i\pi/3} \int_q^{+e^{i\theta}\infty} e^{-z\zeta} \, \zeta_q^{-2/3}\,  d\zeta
-\end{align*}
-where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin.
-
-\color{DarkTurquoise}
-\begin{itemize}
-\item As $p$ goes to zero, $I(z)$ degenerates to
-\[ \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \Gamma(\tfrac{1}{3}) z^{-1/3} = \left(\tfrac{1}{2}\right)^{2/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = \left(\tfrac{1}{2}\right)^{2/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3}).
-\]
-\end{itemize}
-
-\color{black}
-
-\appendix
-
-\section{The Airy equation}\label{airy-appendix}
-
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Lambda_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-and the contour $\Lambda_1$ is represented in Figure \ref{fig:path_Airy}.
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel-1/3}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-%The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
-%\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-%where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
-Like we did in equation~\eqref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
-
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-
-\subsection{Asymptotic analysis}
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We’ll see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of \cite[Theorem~4]{reg-sing-volterra}.
-
-\subsection{Building a distinguished frame of analytic solutions}
-\subsubsection{Going to the spatial domain}\label{spatial}
-%\subsubsection{The big idea}\label{big-idea}
-We are going to look for functions $v_j$ whose Laplace transforms $\laplace_{\zeta, \alpha_j} v_j$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We’ll succeed when $\alpha^2 - 1 = 0$, and we’ll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we’ll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-%\textcolor{Magenta}{Show that $W_1$ is asymptotic to $\tilde{W}_1$!}
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\,\left(\frac{\zeta_1}{2}\right)^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:reg-mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
-%\color{DodgerBlue}
-%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\eqref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
-%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-%where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-\subsection{Borel regularity}\label{bessel-regularity}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\laplace_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$ 
-\begin{align*}
-\borel\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\borel\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:reg-mod-bessel} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-\subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
-Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Lambda_1$ to a contour $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \Lambda_1$, we have
-\begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\mathcal{H}^1_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\mathcal{H}^1_z$ in the $\zeta$ plane.}
-\end{center}
-From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
-so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
-
-In addition to the solutions $v_1$ and $v_{-1}$ from Section~\ref{pos-root}\,--\, \ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
-\begin{alignat*}{2}
-g_1 &\;=\;& & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi_1\big) \\
-g_{-1} &\;=\;&  & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi_1\big),
-\end{alignat*}
-given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
-so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
-The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $g_1$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,v_1$,
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
-Hence,
-\begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} v_1\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} v_1\;d\zeta \\
-e^z K & = \tfrac{i}{2} \laplace_{\zeta_1} v_1,
-\end{align*}
-just as we found in Section~\ref{bessel-regularity}. However, in this case, we get an exact equality (compared to the proportionality of Section~\ref{bessel-regularity}). 
-\subsubsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\eqref{eqn:reg-mod-bessel}.
-To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
-\[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\eqref{diff-eq:spatial-mod-bessel}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the thimble projection technique of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
-\begin{align*}
-g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
-\end{align*}
-of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
-
-The Laplace transformation method of solving equation~\eqref{eqn:reg-mod-bessel}, on the other hand, is associated with the basis
-\begin{alignat*}{2}
-v_{-1} &\;=\;& (1-\xi)^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-v_1 &\;=\:& \xi^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
-\end{alignat*}
-given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
-
-Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
-\begin{alignat*}{3}
-v_{-1} &\;=\;&\tfrac{1}{\sqrt{3}}\,g_{-1} &\;+\;& \tfrac{1}{2}\,v_1 \\
-v_1 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_{1} &\;+\;& \tfrac{1}{2}\,v_{-1}.
-\end{alignat*}
-Summing these identities, we see that
-\[ g_1 + g_{-1} = \tfrac{\sqrt{3}}{2}\,(f_1 + f_{-1}), \]
-giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
-
-\subsection{Thimble projection formula}
-
-In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula~\eqref{formula1} using trigonometric substitution.
-As an example of how one might reason in the latter case, we look at the Airy function ($f = 4u^3-3u$), this time applying the thimble projection formula to the generalized Cardano's formula.
-
-Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
-\begin{align*}
-    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
-    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
-\end{align*}
-\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
-The thimble $\Lambda_1$ \textcolor{red}{is/can be} parametrized as the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
-\begin{align*}
-\int_{\Lambda_1(\zeta)} \nu & = \int_{\Lambda_1(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}.
-\end{align*}
-Since $4u^3 - 3u$ is the third Chebyshev polynomial, and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\Lambda_1(\zeta)} \nu & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta).
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh( \theta)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
-\[ \sinh(\theta) =  \sinh( \theta)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\Lambda_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\Lambda_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \S 4.1 in \cite{koornwinder2015fractional}.
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } 2/3} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_1(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
-& = -i \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = \frac{i}{2} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
-\begin{align*}
-\fracderiv{3/2}{\zeta}{1} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-%
-For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\Lambda_{-1}$ is the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
-\begin{align*}
-\int_{\Lambda_{-1}(\zeta)} \nu & = \int_{\Lambda_{-1}(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \Lambda_{-1}(\zeta)}^{\operatorname{end}\Lambda_{-1}(\zeta)}.
-\end{align*}
-The start and end points of $\Lambda_{-1}$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\Lambda_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
-\[ \sinh(\theta) = \tfrac{2}{3} \sinh(\tfrac{3}{2} \theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\tfrac{3}{2} \theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu = \tfrac{2}{3} (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\Lambda_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions (see \cite[Section 4.1 ]{koornwinder2015fractional}).
-\begin{align*}
-\partial^{-1/2}_{\zeta \text{ from } -2/3} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-2/3}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_-(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi \tfrac{\sqrt{3}}{2} (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\,\tfrac{2}{3} (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \tfrac{4}{3}\,d\xi' \big) \\
-& =  \frac{4}{3} \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \frac{2}{3} \sqrt{\pi}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
-\begin{align*}
-\fracderiv{3/2}{\zeta}{-1} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \frac{2}{3} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{3\sqrt{\pi}}{8}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{8}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\subsubsection{An eye on resurgence}\label{sec:eye-res-airy}
-Resurgent functions have very special features: they are \textit{endlessly} analytically continuable away from the singularities, and by studying one germ we could typically reconstruct the others by looking at the behavior near the singular points.
-A prototypical class of resurgent functions is the so-called simple resurgent functions, namely an analytic function $\hat{\phi}$ with singularities $\omega$ such that
-\begin{align*}
-    \hat{\phi}(\zeta-\omega)=\frac{S_\omega}{2\pi i} \log(\zeta) \series{\phi}_\omega(\zeta) + \text{ hol. funct.}
-\end{align*}
-where $S_\omega$ is a constant, typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
-The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
-%The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$
-
-Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent.
-Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.
-Hence the set of singularities is given by the critical values of $f$.
-Then, the computation of the Stokes constants and of the other germs $\series{\phi}_k$ is done by studying $\hat{\phi}_j$ near its singular points.
-For example, for the Airy function, we can expand $\hat{\phi}_1$ near $\zeta=-1$:
-\begin{align*}
-    \hat{\phi}_1(\zeta)=\log(\zeta+1) (1+...) +\text{ hol. funct. }
-\end{align*}
-
-Notice that $(1+...)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin. Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
-\begin{align*}
-    \hat{\phi}_{-1}(\zeta)=\log(\zeta-1) (1+...) +\text{ hol. funct. }
-\end{align*}
-where the germ $(1+...)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin.
-
-\subsection{Comparison with other treatments of the Airy equation}
-
-\subsubsection{Different Borel transform convention} Physicists often use a different version of the Borel transform:
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
-It's sometimes convenient to $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
-
-For problems involving a small parameter $\hbar$ rather than a large parameter $z$, physicists also define
-\begin{align*}
-\borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\hbar^n & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-From a combinatorial perspective, this is just the transformation that sends an ordinary generating function to the corresponding exponential generating function.
-
-In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions. He starts with the formal trans-monomial solutions of the Airy equation:
-
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
-\end{align*}  
-where 
-\begin{align*}
-\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
-\end{align*}
-%Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-Then, by applying the two definitions of the Borel transform $\borel_{\textit{phys}}$ and $\borel$, on the one hand we have  
-\begin{align*}
-w_{1,2}(\zeta)&\defeq\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
-&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^n}{n!}\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) 
-\end{align*}
-on the other hand, we find
-\begin{align*}
-\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
-\end{align*}
-%That ambiguity comes from the different definitions of Borel transforms: 
-%\begin{align*}
-%\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%\end{align*}
-
-and comparing the two solutions we notice that up to the factor of $\delta$
-
-\begin{equation}\label{Borel-W12}
-\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta) 
-\end{equation}
-More generally, if $\tilde{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
-
-\begin{equation}
-\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\tilde{\Phi}=\borel\tilde{\Phi}.
-\end{equation}
-In particular, $\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$.
-
-%Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
-We want to compare $v_1$ with the \textit{physic} Borel transform $\borel_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
-%
-%\begin{align*}
-%\borel_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
-%&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
-%&=\frac{1}{2\pi}\zeta^{1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right) 
-%\end{align*}
-%
-%Now taking the $-1$- derivative of $v_1(\zeta)$ we get
-%
-%\begin{align*}
-%\partial_\zeta^{-1} v_1&=\frac{1}{\Gamma(1)}\int_0^{\zeta}(\zeta-\zeta') v_1(\zeta')d\zeta'\\
-%&=\int_0^{\zeta}(\zeta-\zeta') \zeta'^{-1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta'}{2}\right)d\zeta'\\
-%&=\frac{\Gamma(1/2)}{\Gamma(3/2)}\zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)\\
-%&=2 \zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)
-%\end{align*}
-
-\subsubsection{Integral formula for hypergeometric functions}
-
-In \cite{diverg-resurg-i} the author studies summability and resurgent properties of solutions of the Airy equation.
-
-He considers the formal power series  
-\[\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
-such that
-\begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
-\tilde{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
-\end{align*} 
-are formal solutions of the Airy equation. Notice that compared to Marino's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
-
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\tilde{\Phi}_{\pm}$ as a convolution product:
-
-\begin{align*}
-\hat{\phi}_+(\zeta):=\borel\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
-\end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$.
-
-%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
-%
-%\begin{align*}
-%\tilde{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\tilde{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
-%\end{align*}
-%which up to a constant factor for $\delta$, they agree with our results.
-
-Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
-
-\begin{align*}
-\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1}(\zeta t)^{-1/6}(2+\zeta t)^{-1/6} (\zeta-\zeta t)^{-5/6} \zeta dt\\
-&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} 2^{-1/6}(1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&=\frac{1}{\Gamma(1/6)\Gamma(5/6)}\int_0^{1} t^{-1/6} (1+\frac{\zeta}{2} t)^{-1/6} (1-t)^{-5/6}d\zeta'\\
-&={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
-\end{align*}
-where in the last step we use the Euler formula for hypergeometric functions \footnote{The Euler formula is \begin{equation}\label{Euler formula}
-{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
-\end{equation}}. Then, by taking derivatives we recover $\hat{\phi}_{\pm}(\zeta)$:
-
-\begin{align*}
-\hat{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
-\hat{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)
-\end{align*} 
-and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
-The main advantage of writing Gauss hypergeometric functions as a convolution product relies on \'Ecalle's singularity theory.
-Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see part c of \cite[Section 6.14.5]{diverg-resurg-i}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see \cite[Lemma 6.106]{diverg-resurg-i}).
-%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
-
-\subsubsection{Comparison with exact WKB}
-
-Kawai and Takei study the WKB analysis of the Airy--type Schrodinger equation
-
-\begin{equation}
-\label{WKB_Airy} 
-\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
-\end{equation}
-as $\eta\to\infty$.
-They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
-In the coordinate $t=\frac{3}{2}yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
-\begin{align*}
-\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
-\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
-\end{align*}
-where $s=t/2+1/2$. 
-The same hypergeometric functions have been computed in Section \ref{Airy} as the Borel transform of the formal solutions of the Airy equation
-
-\begin{equation}
-\label{Airy}
-\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
-\end{equation}
-
-Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
-So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
-
-First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
-\begin{align*}
-\sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
-\end{align*} 
-then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
-\begin{align*}
-\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
-\end{align*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
-\begin{equation}
-\label{eq_Phi}
-\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
-\end{equation}
-
-\begin{proof}
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
-&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
-&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
-&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
-\end{align*}
-\end{proof}
-Now rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{2}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta x^{-1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-%&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-1\right]\Phi=0
-\end{align*}
-
-therefore $\Phi(q)$ is a solution of the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
-
-\begin{remark}
-The change of coordinate $q=\frac{2}{3}\eta x^{3/2}$ is not casual: recall that the WKB ansatz for a Schrodinger type equation is
-
-\begin{equation}
-\psi(x,\eta)=\exp\left(\int_{x_0}^xS(\eta,x')dx'\right)
-\end{equation} 
- and $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. In addition, for the Airy--type Schrodinger equation 
- \begin{align*}
- S_{-1}^2=x
- \end{align*}
-hence, up to a choice of sign for the square root
-\begin{align*}
-q&=\frac{2}{3}\eta x^{3/2}=\eta\int_0^x\sqrt{x'}dx'=\eta\int_{0}^xS_{-1}(x')dx'.
-\end{align*}
-We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.
-\end{remark}
-
-\section{Geometry of thimble integrals}
+\section{Geometry of thimble integrals}\label{apx:geometry_thimble_integrals}
 
@@
 Notice that $\Lambda_1$ and $\Lambda_3$ do not intersect as they are in the same class, because they are preimages of the same rays through infinity.
-\section{Generalities about ODEs and Integral Equations}
-\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
-
-\subsubsection{Order shifting}\label{shifting}
-Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.
-%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-%We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
-%\begin{equation}\label{eqn:slight-defn}
-%\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-%\end{equation}
-%where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-As we've seen in Section \ref{reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
-In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
-Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are holomorphic functions.
-\end{prop}
-%To prove this result, we'll need a little background.
-
-%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-%Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-
-\begin{proof}%[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-belongs to the function space $\singexpalg{\sigma}(\Omega)$.
-Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
-Hence, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
-
-\newpage
 

### 2023-11-24 exp-resurgence.tex
Moved some part of the intro into the historical section Removed appendix on the geometry of thimbles and create a new doc.

@@
 In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
-\subsubsection{Borel regularity as a good approximation condition}
+
+\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
+The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
+Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.
+
+The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
+\begin{enumerate}
+\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
+One example is Equation~\eqref{eqn:bessel-rescaled-1}.
+The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
+We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).
+
+The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag.
+105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
+Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
+%
+\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
+%
+\begin{equation*}
+I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
+\end{equation*}
+where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+\end{enumerate}
+These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+
+%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
+Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
+We’ll give precise statements in the following section.
+
+%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
+%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
+We'll call it {\em Borel regularization}.
+%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
+We'll call this process {\em Borel regularization}.
+%\begin{itemize}
+%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
+%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+%\item We have the following vector space inclusions:
+%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
+%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
+%
+%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
+%\begin{itemize}
+%\item $\Phi$ is Borel regular.
+%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
+%\item $\phi$ grows at most exponentially along the Laplace transform ray.
+%\end{itemize}
+%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
+\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
+Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
+it is Borel regular)?
+P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
+In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
+When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
+%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
+%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
+%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
+%\item \ldots
+%\end{itemize}
+
+\subsection{Goals and Results}
+
+First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
+
+Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations.
+On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
+\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
+As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
+\begin{equation}\label{eqn:standard ODE}
+\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
+\end{equation}
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
+Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
+
+\begin{verify}
+    Turn the ODE into a system: assume 
+    \begin{align*}
+P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
+Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
+\end{align*}
+then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
+    \begin{equation}
+        \frac{d}{dz}Y= B(z) Y 
+    \end{equation}
+    \[
+    B(z)=\begin{pmatrix}
+            0 & 1 & 0 & \ldots & 0 \\
+            0 & 0 & 1 & \ldots & 0 \\
+            \vdots & &\ddots & & 1\\
+            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
+        \end{pmatrix}, \quad Y=\begin{pmatrix}
+            \psi \\
+            \psi ' \\
+            \vdots \\
+            \psi^{(d-1)}
+        \end{pmatrix}
+    \]
+
+ and $b_j(z)=-P_j-\frac{1}{z}Q_j-\frac{R_j(z)}{z^2}$. A formal system of solutions is given by the matrix 
+\begin{equation}
+    Y=\begin{pmatrix}
+       \psi_1 & \psi_2 & \ldots & \psi_d  \\
+       \psi_1' & \psi_2' & \ldots & \psi_d'  \\
+       \vdots & \vdots  & \ldots & \vdots  \\
+       \psi_1^{(d-1)} & \psi_2^{(d-1)} & \ldots & \psi_d^{(d-1)} 
+    \end{pmatrix}, \qquad \psi_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{f}_j
+\end{equation}
+
+To prove that $z=\infty$ is an irregular singular point we change coordinates and set $w=1/z$:
+
+ \begin{equation}
+        -w^2 \frac{d}{dw}Y= B(1/w) Y 
+    \end{equation}
+
+and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
+\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
+hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular. 
+\end{verify}
+
+Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
+\begin{equation}\label{formal solution}
+\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
+\end{equation}
+where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
+Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
+\textcolor{orange}{Add that the formal series is $1$-Gevrey.}
+\color{gray}
+Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
+Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
+
+However, can we find a distinguished basis for solutions in a purely analytic way?
+This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).\color{black} Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
+\begin{equation}
+\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
+\end{equation}
+labeled by the roots of $P$.
+This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
+At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
+Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.
+\color{Maroon}
+\begin{theorem}
+For each root $\alpha$ of $P$,
+\end{theorem}
+\color{black}
+\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
+The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$.
+In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
+\textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
+\end{theorem}
+In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
+%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
+
+\begin{center}
+\begin{tikzcd}
+& & \text{ODE }\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+& & \text{IE} & & \\
+\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
+\end{tikzcd}
+\end{center}
+
+Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
+The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
+First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE).
+In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
+therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
+Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
+As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
+Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.
+
+%\color{gray}
+%\begin{itemize}
+%\item Can we see there exists a distinguished basis in a purely analytic way?
+YES.
+%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+%\end{itemize}
+%\begin{itemize}
+%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+(proof based on existence theorem \ref{frac_int_exist})
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+Then this is the only solution that can be expressed as a Laplace transform.
+[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
+
+%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+
+%\begin{center}
+%\begin{tikzcd}
+%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+%& & IE & & \\
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\end{tikzcd}
+%\end{center}
+
+%where the arrow in red are a consequence of multisummability.
+In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
+On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
+%\item  
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%\item  M.A.E.T.
+says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
+Our method uses just Laplace transform.
+%\item How do we know we are picking the same frame?
+from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
+From uniqueness result we get a frame equivalent to Ecalle's frame.
+%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+Borel regularity is instead based on the analytic solution in the $z$-plane.
+The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
+%\end{itemize}
+
+\subsubsection{Why does Borel summation work for thimble integrals?}
+Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
+\[
+I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
+\]
+regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
+Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
+
+Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.
+We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
+For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
+These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
+Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
+The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
+However, this only seems to be possible when $X$ is 1-dimensional.}}
+
+\begin{figure}[ht]
+    \centering
+    %\includegraphics{}
+    \caption{The preimage of a ray departing from the critical value and going to infinity.}
+    \label{fig:thimble_vs_rays}
+\end{figure}
+Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
+\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
+    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
+Then:
+\begin{enumerate}
+\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
+\begin{multline}\label{eqn:formula}
+\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
+\end{multline}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+\end{enumerate}
+\end{theorem}
+The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
+\[
+\begin{tikzcd}
+{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
+& & &\\
+\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
+\end{tikzcd}
+\]
+On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
+as the Laplace transform of a function $\iota_j$.
+In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}.
+On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
+Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
+At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
+In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
+%% the following remark has been moved to Section of the proof
+%\begin{remark}\label{rmk:Pham formula}
+%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
+When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as
+%    \begin{equation}\label{eqn:Pham}
+ %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
+ %   \end{equation}
+%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
+ %  \begin{equation*}
+  %     \delta^{-\alpha}:=\begin{cases}
+   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
+    %       & \\
+     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
+      % \end{cases}
+   %\end{equation*}
+%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
+We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
+%\end{remark}
+%     
+\subsubsection{Other results}
+%
+As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
+Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain.
+We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
+
+Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
+
+\begin{figure}[h]
+    \centering
+    %\includegraphics[]{}
+    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
+However, the fiber over a singular point of $B$ has an interesting structure.
+Here we represent the example of Airy functions.}
+    \label{fig:different_fibres}
+\end{figure}
+We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}
+
+On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
+The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}.
+In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
+
+Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
+We try to give an idea of how all these different treatments fit together.
+For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
+\textcolor{red}{The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
+
+Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
+The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
+For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals are toy-models that show some features of resurgent functions.
+
+%\color{gray}
+%\begin{itemize}
+%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
+%\begin{itemize}
+%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
+%\item The second problem is solving a certain kind of ODE.
+%\item These two problems are closely linked.
+By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
+%\end{itemize}
+%
+%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
+%\begin{itemize}
+%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
+%\end{itemize}
+%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
+%\begin{itemize}
+%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
+We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+%\begin{itemize}
+%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+%\end{itemize}
+%\end{itemize}
+%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
+%\begin{itemize}
+%\item Integral equations are more regular than differential equations.
+%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
+%\end{itemize}
+%\item Illustrate with detailed treatments of several examples.
+%\begin{itemize}
+%\item Contour argument (thimble integrals)
+%\item solving integral equation (ODE)
+%\item How thimble integrals and ODE are related in our examples?
+%\end{itemize}
+%\begin{itemize}
+%\item Some have been discussed many times, using different approaches and conventions.
+We'll try to give an idea of how all these different treatments fit together.
+$\bullet$ The Airy function (Marino, Sauzin).
+$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
+%\item Others haven't been discussed much.
+%\end{itemize}
+%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
+Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
+Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
+For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
+Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
+%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
+%\begin{itemize}
+%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
+%\item computation of Stokes constants via Picard--Lefschetz theory
+%\end{itemize}
+%\end{itemize}
+
+%\subsection{Why does Borel resummation work?}
+%
+%\color{gray}
+%
+%Borel resummation is a way of turning a formal power series
+%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
+%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
+Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
+When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
+Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
+%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
+%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
+%\begin{itemize}
+%\item \textbf{Having a good asymptotic approximation}
+%
+%Let $R_N$ be the difference between a function and the partial sum
+%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
+%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
+%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
+%\color{black}
+%
+%\item \textbf{Satisfying a singular differential equation}
+%
+%\begin{itemize}
+%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
+%\begin{equation}\label{eqn:standard ODE}
+%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
+%\end{equation}
+%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
+\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
+%\item \color{DarkTurquoise}
+%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
+%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
+%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
+%\color{black}
+%\item (backgrounds) Under these assumptions, 
+%\begin{itemize}
+%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
+%\begin{equation}
+%\label{formal solution}
+%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
+%\end{equation}
+%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
+%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
+%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
+%\end{itemize}
+%\item Can we see there exists a distinguished basis in a purely analytic way?
+YES.
+[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
+%\begin{itemize}
+%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
+(proof based on existence theorem \ref{frac_int_exist})
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
+%\end{itemize}
+%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+Then this is the only solution that can be expressed as a Laplace transform.
+[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
+%
+%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
+%
+%\begin{center}
+%\begin{tikzcd}
+%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+%& & IE & & \\
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\end{tikzcd}
+%\end{center}
+%
+%where the arrow in red are a consequence of multisummability.
+In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
+On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
+%\item  
+%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{\'Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
+%\item  M.A.E.T.
+says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
+Our method uses just Laplace transform.
+%\item How do we know we are picking the same frame?
+from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
+From uniqueness result we get a frame equivalent to \'Ecalle's frame.
+%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
+Borel regularity is instead based on the analytic solution in the $z$-plane.
+The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
+%\end{itemize}
+%
+%\color{DarkBlue}
+%
+%\item \textbf{Being a thimble integral}
+%
+%\begin{itemize}
+%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
+%\begin{itemize}
+%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
+%\end{itemize} 
+%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
+His proof is geometric [it may be useful to add it in Appendix].
+%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
+%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
+%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
+%\begin{equation}
+%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+%\end{equation}
+%
+%then the following diagram is commutative
+%\begin{equation}
+%\begin{tikzcd}
+%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+%& \\
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\end{tikzcd}
+%\end{equation}
+%\begin{itemize}
+%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
+%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
+%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
+%\item A corollary of [Thm 4] is the fractional derivative formula.
+%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
+%\end{itemize}
+%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
+See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
+Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
+%\end{itemize}
+
+%\subsection{Stokes phenomenon}
+%\begin{itemize}
+%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
+%\item The jump comes from the branch cut difference identity for hypergeometric functions.
+%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
+%\end{itemize}
+\subsection{Plan of the paper}
+The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
+The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
+Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
+Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
+We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
+The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.
+%
+\subsection{Acknowledgements}
+This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
+
+We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+
+We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
+%
+\section{Historical context}\label{sec:historical-context}
+%
+\subsection{Borel regularity as a good approximation condition}
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsubsection{Borel regularity sometimes explains why Borel summation works}\label{borel-reg:explanatory-power}
-The idea of Borel regularity can help us understand why Borel summation is so effective in some situations.
-Roughly speaking, Borel summation works well for problems that admit solutions in terms of Laplace transform.
-
-The central goal of this paper is to explain, from this perspective, why Borel summation works well for the two kinds of problems exemplified in Section~\ref{intro:summation}.
-\begin{enumerate}
-\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
-We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).
-
-The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag.
-105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
-Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
-
-\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
-
-\begin{equation*}
-I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
-\end{equation*}
-where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
-\end{enumerate}
-
-These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-
-%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
-Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We’ll give precise statements in the following section.
-
-%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We'll call it {\em Borel regularization}.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We'll call this process {\em Borel regularization}.
-%\begin{itemize}
-%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
-%\item We have the following vector space inclusions:
-%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
-%
-%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-%\begin{itemize}
-%\item $\Phi$ is Borel regular.
-%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-%\item $\phi$ grows at most exponentially along the Laplace transform ray.
-%\end{itemize}
-%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
-\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
-it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
-%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-%\item \ldots
-%\end{itemize}
-
-\subsection{Goals and Results}
-
-First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
-
-Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-\subsubsection{Why does Borel summation work for solutions of single level-$1$ ODEs?}
+\subsection{Borel regularity for level-$1$ ODEs}
 As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
-\begin{equation}\label{eqn:standard ODE}
+\begin{equation}%\label{eqn:standard ODE}
 \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
@@
 
-\begin{verify}
-    Turn the ODE into a system: assume 
-    \begin{align*}
-P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
-Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
-\end{align*}
-then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
-    \begin{equation}
-        \frac{d}{dz}Y= B(z) Y 
-    \end{equation}
-    \[
-    B(z)=\begin{pmatrix}
-            0 & 1 & 0 & \ldots & 0 \\
-            0 & 0 & 1 & \ldots & 0 \\
-            \vdots & &\ddots & & 1\\
-            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
-        \end{pmatrix}, \quad Y=\begin{pmatrix}
-            \psi \\
-            \psi ' \\
-            \vdots \\
-            \psi^{(d-1)}
-        \end{pmatrix}
-    \]
-
- and $b_j(z)=-P_j-\frac{1}{z}Q_j-\frac{R_j(z)}{z^2}$. A formal system of solutions is given by the matrix 
-\begin{equation}
-    Y=\begin{pmatrix}
-       \psi_1 & \psi_2 & \ldots & \psi_d  \\
-       \psi_1' & \psi_2' & \ldots & \psi_d'  \\
-       \vdots & \vdots  & \ldots & \vdots  \\
-       \psi_1^{(d-1)} & \psi_2^{(d-1)} & \ldots & \psi_d^{(d-1)} 
-    \end{pmatrix}, \qquad \psi_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{f}_j
-\end{equation}
-
-To prove that $z=\infty$ is an irregular singular point we change coordinates and set $w=1/z$:
-
- \begin{equation}
-        -w^2 \frac{d}{dw}Y= B(1/w) Y 
-    \end{equation}
-
-and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
-\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
-hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular. 
-\end{verify}
-
 Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}\label{formal solution}
+\begin{equation}%\label{formal solution}
 \series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
@@
 Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
+\textcolor{orange}{Add that the formal series is $1$-Gevrey.}
 
@@
 At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually proportional, hence proving Borel summation works.
-\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
-The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable and its Borel sum is proportional to $\Psi_j$. In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.  
-\end{theorem}
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & \text{ODE }\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & \text{IE} & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
-The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE).
-In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
-Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.
 
@@
 \end{remark}
-%\color{gray}
-%\begin{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\end{itemize}
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-
-\subsubsection{Why does Borel summation work for thimble integrals?}
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
-\[
-I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
-\]
-regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
-Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
-
-Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.
-
-\textcolor{red}{These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
+\begin{remark}
+    Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain. 
+\end{remark}
+
+\subsection{Borel regularity for thimble integrals}
+These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
 In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.}
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.
 
@@
 
-We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
-These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
-The preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
-However, this only seems to be possible when $X$ is 1-dimensional.}}
-
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{}
-    \caption{The preimage of a ray departing from the critical value and going to infinity.}
-    \label{fig:thimble_vs_rays}
-\end{figure}
-Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
-\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
-    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
-Then:
-\begin{enumerate}
-\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
-\begin{multline}\label{eqn:formula}
-\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
-\end{multline}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{enumerate}
-\end{theorem}
-
-The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
-\[
-\begin{tikzcd}
-{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
-& & &\\
-\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
-\end{tikzcd}
-\]
-On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
-as the Laplace transform of a function $\iota_j$.
-In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}.
-On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
-Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
-In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
-%% the following remark has been moved to Section of the proof
-%\begin{remark}\label{rmk:Pham formula}
-%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
-When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as
-%    \begin{equation}\label{eqn:Pham}
- %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
- %   \end{equation}
-%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
- %  \begin{equation*}
-  %     \delta^{-\alpha}:=\begin{cases}
-   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
-    %       & \\
-     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
-      % \end{cases}
-   %\end{equation*}
-%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
-We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
-%\end{remark}
-%     
-\subsubsection{Other results}
-%
-As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
-Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain.
-
-Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
-
-\begin{figure}[h]
-    \centering
-    %\includegraphics[]{}
-    \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
-However, the fiber over a singular point of $B$ has an interesting structure.
-Here we represent the example of Airy functions.}
-    \label{fig:different_fibres}
-\end{figure}
-We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}
-
-On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
-On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}.
-In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
-
-Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
-The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).
-Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
-
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
-The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals are toy-models that show some features of resurgent functions.
-
-%\color{gray}
-%\begin{itemize}
-%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-%\begin{itemize}
-%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-%\item The second problem is solving a certain kind of ODE.
-%\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-%\end{itemize}
-%
-%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-%\begin{itemize}
-%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-%\end{itemize}
-%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-%\begin{itemize}
-%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
-%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-%\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
-%\end{itemize}
-%\end{itemize}
-%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
-%\begin{itemize}
-%\item Integral equations are more regular than differential equations.
-%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-%\end{itemize}
-%\item Illustrate with detailed treatments of several examples.
-%\begin{itemize}
-%\item Contour argument (thimble integrals)
-%\item solving integral equation (ODE)
-%\item How thimble integrals and ODE are related in our examples?
-%\end{itemize}
-%\begin{itemize}
-%\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-%\item Others haven't been discussed much.
-%\end{itemize}
-%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-%\begin{itemize}
-%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-%\item computation of Stokes constants via Picard--Lefschetz theory
-%\end{itemize}
-%\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{\'Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to \'Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
-
-%\subsection{Stokes phenomenon}
-%\begin{itemize}
-%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-%\item The jump comes from the branch cut difference identity for hypergeometric functions.
-%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-%\end{itemize}
-\subsection{Plan of the paper}
-The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
-The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
-Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
-Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
-We include three appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-Then, Appendix~\ref{apx:geometry_thimble_integrals} has an algebraic geometric flavour and it describes some properties of thimbles integrals regarded as relative homology cycles.
-Finally, Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.
-%
-\subsection{Acknowledgements}
-This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
-
-We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
-
-We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
 %     
@@
 In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namely of the form $|\zeta|^\sigma$.
-When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta,\alpha}^\theta$ is a well--defined and holomorphic function for $\Re e^{-i\theta}z>0$ on the fiber $T^*B\vert_{\zeta=0}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
+When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ is a well--defined and holomorphic function for $\Re(e^{i\theta} z) > 0$ on the fiber $T^*B_{\zeta=\alpha}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
 %Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
@@
 
-The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$.
+\color{Maroon}
+Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
+In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
+Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \delta^\sigma$, where $\delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+The norm $\|F\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \delta^{-\sigma} |F|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
+\begin{theorem}
+Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
+For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with norm $\Gamma(\sigma)$.
+\end{theorem}
+\begin{proof}
+Given some $f \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
+\begin{align*}
+\left| \laplace_{\zeta_\alpha, 0}^\theta f \right| & = \left| \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
+& \le \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& \le \int_{\Gamma_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
+\end{align*}
+where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$.
+When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows.
+This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta f$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$.
+It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta f$ match where their domains overlap.
+We can therefore glue these functions together into one big Laplace transform of $f$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.
+
+We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta f$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. Doing this gives
+%%\begin{align*}
+%%\left| \laplace_{\zeta_\alpha, 0}^{\arg(z)} f \right| & \le \int_{\Gamma_{\zeta, \alpha}^{\arg(z)}} e^{(\Lambda - |z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+%%& = \int_0^\infty e^{(\Lambda - |z|)t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
+%%\end{align*}
+\textcolor{orange}{[\ldots]}
+\end{proof}
+
+\color{RoyalBlue}
+\textcolor{orange}{[We might be able to remove the decay properties completely!]} The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$.
 Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
@@
 \textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
-
+\color{black}
 \subsubsection{Change of translation chart}\label{translation}
@@
 \begin{multline}\label{formula1}
-\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\textcolor{red}{\left(\tfrac{\partial}{\partial \zeta}\right)^2}\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \textcolor{red}{\left( \int_{\Lambda_j(\zeta')} \nu \right)}\,d\zeta',
+\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
 \end{multline}
@@
 \begin{quote}
-We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ for some $\epsilon \in (0, 1]$.
+We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
+Doesn't match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$.
 Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
@@
 
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and Section \ref{sec:Picard-Lefschetz}.
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and \cite[Chapter ??]{Arnold}.
 However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
@@
 \end{align}
-where $\Lambda_j$ is the path coming from infinity along $-i\pi+2\pi i j+(-\infty,0]$ and going to infinity along $i \pi+2\pi i j+[0,+\infty)$, as represented in Figure \ref{fig:bessel_unrolled}.
+where $\Lambda_j$ is the path coming from infinity along $-i\pi+(2\pi i) j+(-\infty,0]$ and going to infinity along $i \pi+(2\pi i) j+[0,+\infty)$, as represented in Figure \ref{fig:bessel_unrolled}.
 In fact, since $\cosh(t)$ is periodic, the integral has the same value for every choice of $\Lambda_j$ with $j\in\Z$.
@@
 
-For any $\mu \in \C \smallsetminus \Z$, we have a thimble integral representation of $K_{\mu}$ given by formulas 10.32(ii) and 10.27.4 of \cite{dlmf} 
+For any $\mu \in \C \smallsetminus \Z$, we have a thimble integral representation of $K_{\mu}$ given by formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\textcolor{DarkCyan}{[Cite Watson too?]}
 \begin{equation}\label{int:mod-bessel-gen}
@@
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_\Omega \exp\left[z \cosh(t)\right]\,t\,dt. \]
-Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$, we can rewrite this formula as
+\[ K_0(z) = \frac{1}{2\pi i} \int_ {\textcolor{orange}{\Omega}} \exp\left[z \cosh(t)\right]\,t\,dt. \]
+\textcolor{orange}{Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$,} we can rewrite this formula as
 \begin{align*}
@@
 \begin{verify}
-    We can also very equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
+    We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
     \begin{equation}
@@
 \begin{verify}
-Form the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eq:I}.
+From the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eq:I}.
 Then we argue as follows:
@@
     \partial_z\varphi_1&=\laplace_{\zeta,1}v_1\\
-    \varphi_1-\varphi_1(a)&=\int_a^z\int_1^{\infty}e^{-zy} v_1 d\zeta \, dy\\
-    &=\int_1^{\infty}d\zeta\,  v_1 \, \int_a^ze^{-zy}  \, dy\\
+    \varphi_1-\varphi_1(a)&=\int_a^z\int_1^{\infty}e^{-y\zeta} v_1 d\zeta \, dy\\
+    &=\int_1^{\infty}d\zeta\,  v_1 \, \int_a^ze^{-y\zeta}  \, dy\\
     &=\int_1^{\infty}d\zeta\,  v_1 \, \Big[\frac{e^{-\zeta a}}{\zeta}-\frac{e^{-z\zeta}}{\zeta}\Big]\\
@@
 \subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
-Resurgent functions are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}}.
+\textcolor{orange}{[Add link to general references in intro].} Resurgent functions in the position domain are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}\{For definition in the position domain, cite \S 6.1 of Mitschi and Sauzin~\cite{diverg-resurg-i}\}}.
 \textcolor{MediumSeaGreen}{[Focus on endlessly continuable functions instead?
@@
 
-\section{Geometry of thimble integrals}\label{apx:geometry_thimble_integrals}
-
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for a fixed $z\in\C$, we are interested in integrals of the form
-\[
-I(z):=\int_{\mathcal{C}}e^{-zf}\nu
-\]
-regarded as holomorphic functions on the frequency domain for a suitable choice of a contour $\mathcal{C}$ and an $N$-form $\nu$.
-In fact, we'll introduce homology and cohomology groups $H_{*}^{B,z}$ and $H_{dR,z}^*$ for which the function $I(z)$ will represent the Poincar\'e pairing.
-
-We begin with the definition of $H_{*}^{B,z}$: it is the relative homology group with respect to $zf$, and its definition requires some preliminaries.
-We follow \cite{pham} and \cite[Section 1]{Arnold}.
-Let us fix $z\in\C$ and $\theta=\arg z$; for every $c>0$ we define
-\begin{align*}
-    S_c^+(\theta) &:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\geq c \rbrace\\
-    S_c^-(\theta)&:=\lbrace \zeta\in\C \vert \Re (\zeta e^{i\theta})\leq c \rbrace
-\end{align*}
-and $H_{*}^{B,z}:=H_{*}(X,f^{-1}(S_c^+(\theta)))$ for $c$ large enough\footnote{In fact $H_{*}^{B,z}$ is defined after taking the projective limit $c\to\infty$ of the chain complex with support $\{A\subset X \text{ closed s.t.
-} \forall c>0 f^{-1}(S_c^-(\theta))\cup A \text{ is compact }  \}$.}.
-Moreover, $H_n(X,f^{-1}(S_c^+(\theta)))$ can be identified with the homology of a generic fiber $H_{n-1}(f^{-1}(p_0))$ with $p_0\neq \{\alpha_j\}$.
-This leads to further identifications:
-
-\begin{equation}
-    H_{*}^{B,z}\cong \bigoplus_{\alpha_i} H_{*}(B_j, B_j^+(\theta))
-\end{equation}
-where $B_j:=f^{-1}(B_r(\alpha_j))$ is the preimage of a small ball or radius $r$, containing only the critical value $\alpha_i$ and $B_j^+(\theta):=f^{-1}\left(B_r(\alpha_j)\cap \{ \Re (\zeta e^{i\theta})\geq r/2\}\right)$.
-Notice that we are not assuming $f$ to be Morse, hence $B_j$ may have different connected components.
-Then
-
-\begin{equation}
-    H_{n}(B_j, B_j^+(\theta))\cong H_{n-1}(f^{-1}(p_j))\cong \begin{cases} \Z^{\mu_j} & \text{if } n=N\\
-     0 & \text{otherwise}
-    \end{cases}
-\end{equation}
-where $|p_j-\alpha_j|=r$, $\Re(p_j e^{i\theta})=r$, and $\mu_j$ is a number in $\{\textcolor{magenta}{???}\}$ called the {\em Milnor number} of the critical \textcolor{red}{point/value $a_j/\alpha_j$}.
-
-\begin{center}
-    \begin{tikzpicture}
-        \draw (2,2) circle (2);
-        \node[font=\tiny,red] at (1,1) {$\alpha_1$};
-        \draw (1,1.2) circle (0.4);
-        \node[font=\tiny,red] at (3,1.3) {$\alpha_2$};
-        \draw (3,1.5) circle (0.4);
-        \node[font=\tiny,red] at (2.3,3.2) {$\alpha_3$};
-        \draw (2.3,3.4) circle (0.4);
-        \node[above,red] at (1,1) {$\bullet$};
-        \node[above,red] at (3,1.3) {$\bullet$};
-        \node[above,red] at (2.3,3.2) {$\bullet$};
-        \draw[rounded corners] (2.7,1.76)--(2,2)--(1,3.71);
-        \draw[rounded corners] (1,1.6)--(0.5,2)--(1.2,2.5)--(1,3.71);
-        \draw[rounded corners] (1.9,3.4)--(1,3.71);
-        \node[font=\tiny, above] at (1,3.71) {$p_0$};
-        \node[font=\tiny, above] at (2.7,1.76) {$p_2$};
-        \node[font=\tiny, above] at (1,1.6) {$p_1$};
-        \node[font=\tiny, above] at (1.75,3.4) {$p_3$};
-    \end{tikzpicture}
-\end{center}
-
-From the classical theory of singularities \cite[\textcolor{magenta}{add section; move to end of sentence}]{Arnold}, we know that $H_{N-1}(f^{-1}(p_0))$ has a distinguished basis of \textit{vanishing cycles} from the generic fiber over $p_0$ to the preimage of each critical value.
-Each vanishing cycle is represented by the boundary of a so-called \textit{Lefschetz thimble}: since we assumed critical points to be non--degenerate, in a neighborhood of $a_j$ there are local coordinates $x_1,...,x_N$ such that
-\[f=\alpha_j+\sum_{k=1}^N x_k^2\]
-
-and for $p=c e^{i\theta}\in\C$, the thimble $\Lambda_j(p)$ is defined by 
-\begin{align*}
-    \Im(x_1)=...=\Im(x_N)=0 \text{ and } \Re(e^{-i\theta/2}x_1)^2+....+\Re(e^{-i\theta/2}x_N)^2\leq c
-\end{align*}
-Equivalently, Lefschetz thimbles are gradient flow trajectories departing from the critical points of $f$ (see \cite[page~10]{Witten}).
-
-Hence we deduce that $H_{z, N}^B$ admits a distinguished basis of Lefschetz thimbles labeled by critical points.
-
-Then we recall the definition of $H_{dR,z}^*$: it is the hypercohomolgy of the twisted de Rham complex
-
-\begin{equation*}
-    H_{dR,z}^*:=\mathbb{H}^*( \Omega^\bullet(X), zd+df)
-\end{equation*}
-where $(\Omega^\bullet(X), d)$ is the de Rham complex of differential forms on $X$.
-
-Therefore, the integral $I(z)$ can e regarded as the image of the following map:
-
-\begin{align*}
-    \int \colon  H_{z,N}^{B} \times & H_{dR,z}^N \to \C \\
-       [\mathcal{C}] ,\,\, & [\nu] \to \int_{\mathcal{C}}e^{-zf}\nu
-\end{align*}
-
-\textcolor{orange}{[the Betti--de Rham isomorphism is necessary?]}
-
-Since every cycle $\mathcal{C}$ can be written as a linear combination of Lefschetz thimbles, we restrict our attention to  \textit{thimbles} integrals $I_j$, namely the integrals over Lefschetz thimbles labeled by the critical points $a_j\in\text{Crit}(f)$.
-
-As we let $z$ vary, we’ll observe the so-called \textit{Stokes phenomena}, namely the integral $I_j(z)$ jumps across the rays $\ell_{jl}=\arg(\alpha_j-\alpha_l)\R_{\geq 0}$ for $l=1,...,N$ (and $l\neq j$).
-The jumps can be described geometrically using the pairing between dual cycles.
-Equivalently, the jumps of $I_j(z)$ are encoded in the jumps of the Lefschetz thimbles $[\Lambda_j]\in H_{z,N}^B$ as $\arg z$ varies.
-%We’ll discuss this phenomenon from a different perspective in Section \ref{resurgence-AL} in the example of Airy--Lucas functions.
-\textcolor{orange}{[Can we comment more about this?
-For instance as a consequence of Theorem 3.3]}
-
-\subsection{Picard--Lefschetz formula}\label{sec:Picard-Lefschetz}
-We'll compute the Picard--Lefschetz formula as the intersection of the base of thimbles and its dual, relative to the singular direction $\theta=0$.
-We'll do it graphically, by plotting the steepest decent contours center at the critical points of $f$.
-We'll consider the example of Airy and Airy--Lucas with $n=4$.
-
-For the classical Airy function, we have a two-dimensional base of thimbles, thus we have to compute only one intersection: we choose the Stokes direction $\theta=0$, and we take a base of thimbles $\Lambda_j\in H_1(B_j,B_j^+(0.1))$.
-Then
-\begin{equation}
-    \begin{pmatrix}
-        \Lambda_1\\
-        \Lambda_2
-    \end{pmatrix} = \begin{pmatrix}
-        1 & \\
-        0 & 1
-    \end{pmatrix}\begin{pmatrix}
-        \Lambda_1\\
-        \Lambda_2
-    \end{pmatrix}
-\end{equation}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.7]{figures/contour1--airy.jpg}
-    \includegraphics[scale=0.7]{figures/contour2--airy.jpg}
-     \includegraphics[scale=0.7]{figures/contour--Airy--intersection.jpg}
-    \caption{Graphically, we can describe the Stokes phenomenon by looking at the intersection points of \textit{dual pairs of thimbles}, which differ by a rotation of angle $\pi$.
-With respect to the Stokes line $\theta=0$, we choose $\theta=0.1$ for the picture on the left and $\theta=-0.1+\pi$ for the picture in the center.
-The picture on the right shows the intersection of the thimbles which is given by a single point.
-Thus up to normalization, the Stokes constant is $1$.
-The images were obtained with Mathematica, and the thimbles are computed as the steepest descent contours from the critical points.}
-    \label{fig:intersection_thimbles-Airy}
-\end{figure}
-
-We deduce that the Stokes constant $S_{12}=\pm 1$ (to specify the sign it is enough to pick an orientation). This agrees with the computations we made in Section \ref{apx:eye-res-airy}.
-
-For Airy--Lucas with parameter $n=4$, we have a three thimbles, graphically represented in Figure \ref{fig:thimble-n4}. 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.35]{figures/thimble-n4.png}
-    \caption{Caption.}
-    \label{fig:thimble-n4}
-\end{figure}
-Then computing intersections of dual pairs of thimbles we get 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[scale=0.4]{figures/contour1-AL4--12.jpg}
-    \includegraphics[scale=0.4]{figures/contour2-AL4--12.jpg}
-     \includegraphics[scale=0.4]{figures/contour--AL4--12--inter.jpg}
-    \caption{...}
-    \label{fig:intersection_thimbles-AL4}
-\end{figure}
-Notice that $\Lambda_1$ and $\Lambda_3$ do not intersect as they are in the same class, because they are preimages of the same rays through infinity.    
 \section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}

### 2023-11-28 exp-resurgence.tex
Work on Laplace transform continuity

@@
 %
-Let $\Omega_\alpha\subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
-Assume the $\Gamma_{\zeta,\alpha}^\theta$ is contained in $\Omega_\alpha$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions of exponential type $\Lambda$ with singular behaviour at $\zeta=\alpha$, namely of the form $|\zeta|^\sigma$.
-When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable, hence the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ is a well--defined and holomorphic function for $\Re(e^{i\theta} z) > 0$ on the fiber $T^*B_{\zeta=\alpha}$ (see for instance ~\cite[Section  5.6]{diverg-resurg-i}.)
+Let $\Omega_\alpha \subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
+Suppose $\Omega_\alpha$ contains the ray $\Gamma_{\zeta,\alpha}^\theta$.
+In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions on $\Omega_\alpha$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta|^\sigma$ as $\zeta$ approaches $\alpha$.
+When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable.
+Hence, the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T^*B_{\zeta=\alpha}$~\cite[Section  5.6]{diverg-resurg-i}.
 %Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
@@
 In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
-Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \delta^\sigma$, where $\delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-The norm $\|F\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \delta^{-\sigma} |F|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
-\begin{theorem}
+Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+The norm $\|F\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |F|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
+\textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.}
+\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
 Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with norm $\Gamma(\sigma)$.
-\end{theorem}
+For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with a norm of at most $\Gamma(\sigma)$.
+\end{prop}
 \begin{proof}
@@
 \begin{align*}
-\left| \laplace_{\zeta_\alpha, 0}^\theta f \right| & = \left| \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
+|\laplace_{\zeta_\alpha, 0}^\theta f| & = \left| \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
 & \le \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
@@
 
-We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta f$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$. Doing this gives
-%%\begin{align*}
-%%\left| \laplace_{\zeta_\alpha, 0}^{\arg(z)} f \right| & \le \int_{\Gamma_{\zeta, \alpha}^{\arg(z)}} e^{(\Lambda - |z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-%%& = \int_0^\infty e^{(\Lambda - |z|)t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
-%%\end{align*}
-\textcolor{orange}{[\ldots]}
+We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta f$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$.
+This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+It follows that
+\begin{align*}
+|\laplace_{\zeta_\alpha, 0}^\theta f| & \le \int_{\Gamma_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
+\end{align*}
+The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that this bound on the Laplace transform of $f$ is itself a Laplace transform:
+\[ |\laplace_{\zeta_\alpha, 0}^\theta f| \le \Gamma(\sigma) \Delta^{-\sigma} \|f\|_{\sigma-1, \Lambda}. \]
+In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
+\[ \|\laplace_{\zeta_\alpha, 0}^\theta f\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|f\|_{\sigma-1, \Lambda}, \]
+which is what we wanted to show.
+\end{proof}
+\begin{prop}
+Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
+Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
+\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \]
+has a continuous left inverse
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \to \singexp{\sigma-1}{\Lambda}(\Omega_\alpha^\varepsilon), \]
+with a norm of at most \textcolor{orange}{\ldots}
+\end{prop}
+\begin{proof}
+Choose any path $\textcolor{magenta}{\Lambda}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
+The inverse Laplace transform is given by the formula
+\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\Lambda}} e^{z\zeta_\alpha} F\,dz. \]
+When $F$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
+\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\Lambda}} e^{\Re(z\zeta_\alpha)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz, \]
+where $\Delta_{\textcolor{magenta}{\Lambda}}$ is the constant distance from $\Lambda$ to the boundary.
+
+Choose an arc-length parameter $t$ on $\textcolor{magenta}{\Lambda}$, with $t = 0$ at the middle of circular-arc-shaped part.
+On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon$ away from the asymptotic directions of the boundary of $\widehat{\Omega}_\alpha^\Lambda$, $\textcolor{magenta}{\Lambda}$.
+Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
+\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon)\,|t|\big) \]
+for some constant $\lambda' \in \R$. It follows that
+\begin{align*}
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
+& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
+\end{align*}
+\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
 \end{proof}

### 2023-12-05 exp-resurgence.tex
Rewrite Section 2.2 Borel regularity for ODEs Rewrite parts of the introduction Add some references

@@
 
+% domains
+\newcommand{\dualsector}[2]{\Omega_{#1|#2}}
+
 % function spaces
@@
 \newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
-\newcommand{\dualsingexpalg}[1]{\singexp{#1}{\bullet}}
+\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
 \newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments
@@
 \end{equation*}
-where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex algebraic variety, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex manifold, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
 \end{enumerate}
@@
 For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
+\textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}
 
@@
 \subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
+\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}
+
+Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}.
+This operator will always have an irregular singularity at $z = \infty$.
+
+\color{Goldenrod}
+[These details are right above in Section~\ref{borel-reg:explanatory-power}!]
 \begin{equation}\label{eqn:standard ODE}
@@
 Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
-
+\color{black}
 \begin{verify}
@@
 
-Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
+\color{gray}
+[This is now a corollary; moved to historical.] Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
 \begin{equation}\label{formal solution}
@@
 Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-\textcolor{orange}{Add that the formal series is $1$-Gevrey.}
-\color{gray}
-Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
+\textcolor{orange}{Add that the formal series is $1$-Gevrey.} Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
 Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
@@
 This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).\color{black} Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
+In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
+\color{black} \color{Goldenrod}[Let's try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
 \begin{equation}
@@
 At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.
+Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.\color{black}
+\textcolor{Cyan}{Using the dictionary for the Laplace transform associated with some point $\zeta = \alpha$ in the frequency domain, (link section), we can turn $\mathcal{P}$ into an integral operator $\hat{\mathcal{P}}_\alpha$.
+If we choose $-\alpha$ to be a root of $P$, then $\hat{\mathcal{P}}_\alpha$ will have a regular singularity at $\zeta = \alpha$, and we understand a lot of details about its specific form~\cite{reg-sing-volterra}.
+We show in~\cite{reg-sing-volterra} that $\hat{\mathcal{P}}_\alpha \phi = 0$ has a distinguished solution $\psi_\alpha$ which is characterized by having a power-law singularity with a known exponent $\tau_\alpha - 1$ at $\zeta = \alpha$ and having exponentially bounded growth at infinity.}
+
+We know from experience that we can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
+However, this only works when there's a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
+Why?
+
+A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_\alpha^\theta \phi$ of a function on $\phi$ the position domain.
+In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.
+
+Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$.
+Because this solution is so unique, its Laplace transform $\Phi_\alpha$ turns out to be Borel regular.
+
+%%The Laplace transform commutes this distinguishing behavior into asymptotics at $z = \infty$, which can be recognized even if we turn $\Phi$ into a formal series $
+
+%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
 \color{Maroon}
-\begin{theorem}
-For each root $\alpha$ of $P$,
+\begin{theorem}\label{thm:borel_reg_ODE}
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}.
+That solution is Borel regular.
 \end{theorem}
+\begin{corollary}\label{cor:borel_reg_ODE}
+For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
+That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
+\end{corollary}
 \color{black}
@@
 \end{theorem}
+\color{Goldenrod}
 In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
@@
 
+\color{black}
+We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
+On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$.
+%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
+
+\begin{center}
+\begin{tikzcd}
+& & \text{ODE }\arrow[dd,"\laplace^{-1}",swap] & & \\
+ {\Psi}_\alpha\arrow[urr, no head, tail] & & & & \tilde{\Psi}_\alpha\arrow[llu,"\text{formal}",swap, no head, tail]\arrow[dd,"\borel"]\\
+& & \text{IE} & & \\
+\psi_\alpha\arrow[urr, no head, tail]\arrow[uu,"\laplace"]\arrow[r,equal] & \hat{\psi}_\alpha & & & \tilde{\psi}_\alpha\arrow[llu, no head, tail]\arrow[lll,"\text{sum}"]
+\end{tikzcd}
+\end{center}
+
+Conversely, on the left-hand side, by our existence and uniqueness result \cite[Theorem 4]{reg-sing-volterra} we have an analytic function $\psi_\alpha$ with a distinguished behaviour near $\zeta=\alpha$, which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
+The key step is then comparing $\psi_\alpha$ and $\tilde{\psi}_\alpha$.
+First, by the properties of the Borel transform, it is easy to show that $\series{\psi}_\alpha$ is a formal solution of the integral equation (IE).
+Then, from the explicit formula for $\tilde{\Psi}_\alpha$, we can show that if $\tilde{\psi}_\alpha$ grows as $\psi_\alpha$ near $\zeta=\alpha$.
+Therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\tilde{\psi}_j$ is indeed summable and ${\psi}_\alpha$ is the analytic continuation of $\tilde{\psi}_\alpha$.
+
 \subsubsection{Why does Borel summation work for thimble integrals?}
+\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
+Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
+\color{Goldenrod}
 Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
@@
 We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+\color{black}
+We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
 The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
@@
     \centering
-    %\includegraphics{}
-    \caption{The preimage of a ray departing from the critical value and going to infinity.}
+    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
+    \hspace{1cm}
+    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
+    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity.}
     \label{fig:thimble_vs_rays}
@@
 \begin{tikzcd}
-{I}_{j} \arrow[rrr,"\aexp"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
+{I}_{j} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
 & & &\\
@@
 \]
-On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e.
-as the Laplace transform of a function $\iota_j$.
-In addition, $\iota_j$ can be written explicitly in an integral formula \eqref{eqn:formula}.
-On the other hand, reading the diagram from the right-hand side, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series.
-Thus, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\alpha_j$ which can be summed to a holomorphic function $\hat{\iota}_j$.
-At this point, we realize that $\iota_j$ and $\hat{\iota}_j$ are indeed the same.
-In a nutshell, thimble integrals are Borel regular because they can be turned into Laplace transforms.
+On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}. 
+On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain.
+Consequently, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta=\alpha_j$ in the position domain.
+Then, we'll show that the Taylor expansion of $\iota_j$ at $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.
+
+The upshot is that thimble integrals are Borel regular because they can be turned into Laplace transforms.
 %% the following remark has been moved to Section of the proof
@@
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \cite{watson} that a function $F$ that vanishes at infinity is Borel regular whenever its asymptotic expansion is uniformly $1$-Gevrey-asymptotic to it on an obtuse-angled sector around infinity (see Definition~\ref{def:unif-gevrey-asymp}).
+Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $F$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).
 
 Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an open half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
+These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
 \begin{center}
@@
     \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
+    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
     \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
@@
 \draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
+\node[anchor=north west] at (-\size, \size) {$z$};
 \end{tikzpicture}
@@
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
-\textcolor{orange}{[Picture below should show the constant-radius neighborhood]}
 \begin{center}
@@
 \newcommand{\ang}{35}
+\newcommand{\radius}{1}
 \newcommand{\dis}{1.2}
@@
   \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
+  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
   \begin{scope}[violet]
     \draw (0, 0) -- (\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.6mm, shorten >=0.6mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
+    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
+    %%\begin{scope}[rotate=\ang]
+    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
+    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
+    %%\end{scope}
+    %%\fill (mark) circle (0.05);
   \end{scope}
@@
 \draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north east] at (\size, \size) {$z$};
+\node[anchor=north west] at (-\size, \size) {$\zeta$};
 \end{tikzpicture}
 \end{center}
+
+The Watson--Nevanlinna--Sokal characterization of Borel regular functions is totally general, which means it can't take advantage of any extra structure provided by the problem you're trying to solve.
+We take the opposite approach, showing that certain functions are Borel regular just because of the extra structure provided by the problems they solve.
 
@@
 \subsection{Borel regularity for level-$1$ ODEs}
+
+From a formal perspective, the general theory of linear level-$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_j$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_j\in e^{-\alpha_j z} z^{-\tau_j}\C\llbracket z^{-1}\rrbracket$, where $\tau_j=Q(-\alpha_j)/P’(-\alpha_j)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Since $-\alpha_1,…,-\alpha_d$ are distinct, the transmonomials $\tilde{\Psi}_1,…,\tilde{\Psi}_d$ determine a basis up to scaling, giving the space of formal solutions a a distinguished frame.
+Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a constructive method (see~\cite[Chapter 14]{balser}).
+Therefore, noticing that $\tilde{\Psi}_j$ are 1-Gevrey series (Ramis Index Theorem \cite{ramis_index}), a classical problem was to investigate Borel summability of these formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}, which consequently become a distinguished frame of analytic solutions.
+
+At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without going to a formal frame.
+This is possible, as we proved in~\cite{reg-sing-volterra}.
+By construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_1,…,\tilde{\Psi}_d$ (see Corollary~\ref{cor:borel_reg_ODE}).
+As briefly discussed in Section when we sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha_j$.
+Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+
+\begin{remark}
+Our approach of solving regular singular Volterra equation is analogous to the one that Braaksma~\cite{braaksma2006laplace} used to solve a different class of non linear ODEs and difference equations whose coefficients are themselves Laplace transforms.
+\end{remark}
+
+\begin{remark}
+There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
+Formally in the position domain \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \cite{EcalleIII,loday-Remy2011}.
+It can indeed be seen as a consequence of ``resurgence'' of the ODE that the formal solutiomns can be analytically continued.
+Our results of \cite{reg-sing-volterra} show how to build a frame of solutions, analytically in the Borel plane.
+Here, we show we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
+From the uniqueness result of \cite[Theorem~4]{reg-sing-volterra}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
+\end{remark}
+
+\color{gray}
+
 As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
@@
 
+\color{black}
+
 \subsection{Borel regularity for thimble integrals}
-These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{berry1991hyperasymptotics} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
+%
+Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
+In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion.
+For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
+\textcolor{orange}{Take a look at Witten's paper on knots}
+
+In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, they are known as period integrals \cite{Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^B_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.
+Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_B^N(X,f)$.
+Then varying $\theta$, $H_B^N(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ whose monodromy can be computed by Picard--Lefschetz formula.
+it is possible understand the Stokes phenomena.
+
+Then, when $X$ is an $N$-dimensional complex manifold and $f$ is a Morse function\footnote{In fact, $f$ might satisfy milder assumptions (see for instance \cite[Section 1.2.2]{mistegard_phdthesis}).}, the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $\hbar\to 0$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
+In addition, varying the direction ....
+However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
+This raises the question we address in this paper, namely to understand why Borel summation is effective for thimbles integrals.
+
+Special functions are classical examples of thimble integrals, and the Borel summability properties of their asymptotics can be studied either analytically (through resurgence or Borel-summability, see Section \ref{sec:examples}, and for the Gamma function \cite[Section 5.11]{diverg-resurg-i}\cite{sauzin2021variations}) or geometrically (as a Riemann--Hilbert problem  \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
+In addition, they typically come as \textcolor{orange}{[Stokes phenomena in one case ...
+in the other is ...]}
+
+\textcolor{orange}{Borel regularity: \cite[Part II, Section 3.3]{pham}} Assume we want to solve a problem whose solution is expected to be a thimble integral, but that is hard to be defined explicitly.
+However, we know the perturbative expansion of this expected solution, then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
+\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
+
+\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
+\color{DarkTurquoise}
+These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
 In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,delabaere_dillinger_pham,delabaere-howls,Delabaere-Pham99,dingle1973asymptotic,dunne-unsal,gukov-marino-purtrov-resurgence,pham1988resurgence,Howls}.
-
+Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
+\color{black}
 Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
-
+In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.
 %     
@@
 
+\color{RoyalBlue}{$\singexpalg{\sigma}(\Omega_\alpha^\Lambda)$}
 \color{Maroon}
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
+In this case, for any $\Lambda \in \R$, let \textcolor{magenta}{$\widehat{\Omega}_\alpha^\Lambda$} $\dualsector{\alpha}{\lambda}$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
 Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
+Choose any $\lambda' > \Lambda$.
 Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
@@
 has a continuous left inverse
-\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \to \singexp{\sigma-1}{\Lambda}(\Omega_\alpha^\varepsilon), \]
-with a norm of at most \textcolor{orange}{\ldots}
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
+with a norm of at most
+\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
 \end{prop}
 \begin{proof}
-Choose any path $\textcolor{magenta}{\Lambda}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
+Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$.
+Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\textcolor{magenta}{\Lambda}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+Parameterize $\textcolor{magenta}{\Lambda}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\textcolor{magenta}{\Lambda}$.
+Along $\Lambda$, we have
+\[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
+for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+On $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
+\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]
+
+%%Choose a path $\textcolor{magenta}{\Lambda}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
+%%\[ \Delta = m + \sin(\varepsilon)\,|t|, \]
+%%where $t$ is an arc length parameter.
+
+%Choose any path $\textcolor{magenta}{\Lambda}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
+The inverse Laplace transform is given by the formula
+
 The inverse Laplace transform is given by the formula
@@
 When $F$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
-\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\Lambda}} e^{\Re(z\zeta_\alpha)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz, \]
-where $\Delta_{\textcolor{magenta}{\Lambda}}$ is the constant distance from $\Lambda$ to the boundary.
-
-Choose an arc-length parameter $t$ on $\textcolor{magenta}{\Lambda}$, with $t = 0$ at the middle of circular-arc-shaped part.
-On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon$ away from the asymptotic directions of the boundary of $\widehat{\Omega}_\alpha^\Lambda$, $\textcolor{magenta}{\Lambda}$.
+\begin{align*}
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\Lambda}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz \\
+& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
+\end{align*}
+which we can rewrite as
+\begin{align*}
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
+& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
+& \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
+\end{align*}
+using the new parameter $s = \sin(\varepsilon/2)\,t$. Recognizing the integral in the last line as itself a Laplace transform, we have
+\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
+which is what we wanted to show.
+
+%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$.
 Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
-\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon)\,|t|\big) \]
-for some constant $\lambda' \in \R$. It follows that
-\begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
-& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
-\end{align*}
+%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
+%%for some constant $\lambda' \in \R$. It follows that
+%%\begin{align*}
+%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
+%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
+%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
+%%\end{align*}
 \textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
@@
 %\end{theorem}
+\color{Maroon}
+For each root $\alpha$ of $P$,
+\color{black}
 
@@
 Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
-The same phenomena were described by Berry and Howls \cite{berry1991hyperasymptotics} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
+The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
 

### 2023-12-05 exp-resurgence.tex
Removed old part from Section 2.2

@@
 \end{remark} 
-
-\color{gray}
-
-As described in Section~\ref{borel-reg:explanatory-power}, we consider a linear single level-$1$ ODE $\mathcal{P}\Phi = 0$ given by a differential operator of the form
-\begin{equation}%\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
-
-Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}%\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
-\end{equation}
-where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-\textcolor{orange}{Add that the formal series is $1$-Gevrey.}
-
-Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
-Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
-Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
-\begin{equation}
-\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
-\end{equation}
-labeled by the roots of $P$.
-This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
-In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
-At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-
-\begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the $\zeta$-plane \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \textcolor{magenta}{[add reference]\cite{EcalleIII,loday-Remy2011}}.
-It can indeed be seen as a consequence of ``resurgence'' of the ODE.
-Our results of \cite{reg-sing-volterra} show how to build a frame of solutions, analytically in the Borel plane.
-Here, we show we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of \cite[Theorem~4]{reg-sing-volterra}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
-\end{remark}
-
-\begin{remark}
-The theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$ (namely, drawing the red arrow of the diagram).
-This ensures that the Borel sum of the formal solution $\series{\Psi}_j$ exists and it solves the ODE.
-However, the approach of Borel regularity is different as it is based on the analytic solution in the position domain.
-\end{remark}
-\begin{remark}
-    Our approach is different from the one of Malgrange in \cite{malgrange--fourier} where he uses differential equations in the \textcolor{red}{spatial/frequency?} domain. 
-\end{remark}
-
-\color{black}
-
+%
+%
+%
 \subsection{Borel regularity for thimble integrals}

### 2023-12-05 exp-resurgence.tex
Removed old sketch of the proof for ODE Removed old part in 1.3.2

@@
 \end{theorem}
-\color{Goldenrod}
-In the following diagram, we sketch the main step of the proof of Theorem~\ref{thm2} (the rigorous proof is given in Section \ref{borel_reg-ODE}): on the right-hand side of the diagram, we have the formal solution $\series{\Psi }_j$ and its Borel transform $\series{\psi}_j$.
-%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & \text{ODE }\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-\Psi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Psi}}\arrow[ur,red, no head, tail] & & & \tilde{\Psi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & \text{IE} & & \\
-\psi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\psi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\psi}\arrow[llu, no head, tail]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, we have the unique (up to scaling) analytic function $\psi_j$ of Theorem 4 \cite{reg-sing-volterra} which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
-The key step is then comparing $\psi_j$ and $\hat{\psi}_j$.
-First, using properties of the Borel transform, it is easy to show that $\series{\psi}_j$ is a formal solution of the integral equation (IE).
-In addition, from the explicit formula for $\tilde{\Psi}_j$, we can show that $\hat{\psi}_j$ grows as $\zeta^{-\tau_j+1}$ near $\zeta=\alpha_j$
-therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\psi_j$ and $\tilde{\psi}_j$ must coincide up to scaling by a constant.
-Hence, we define $\hat{\psi}_j$ as the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$.
-As a consequence, by properties of the Laplace transform, $\Psi_j\defeq\laplace_{\zeta,\alpha_j}^{\theta}\psi_j$ is an analytic solution of the (ODE) and it is asymptotic to $\series{\Psi}_j$.
-Furthermore, $\Psi_j$ is proportional to $\hat{\Psi}_j$, by construction.
-
-%\color{gray}
-%\begin{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-%%[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\end{itemize}
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-
-\color{black}
+%
 We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
@@
 \subsubsection{Why does Borel summation work for thimble integrals?}
-\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
+%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
 Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
-\color{Goldenrod}
-Let $X$ be an $N$-dimensional complex algebraic variety and $f\colon X\to\C$ a proper algebraic map with non-degenerate critical points $a_1,...,a_N$ and critical values $\alpha_j=f(a_j)$\footnote{Everything we’ll discuss, applies also when $X$ is a $N$-dimensional complex (K\"ahler) manifold and $f\colon X\to\C$ is a holomorphic function with non-degenerates critical points, which is, for example, the setting in \cite{Witten}.}: for $z\in\C$, we are interested in integrals of the form
-\[
-I_j(z):=\int_{\Lambda_j}e^{-zf}\nu
-\]
-regarded as holomorphic functions on the frequency domain, where $\Lambda_j$ is the Lefschetz thimble through the critical point $a_j$ and $\nu$ is a holomorphic $N$-form on $X$.
-Now using the steepest descendent method we can compute the asymptotic expansion of thimble integrals which in general gives a formal series $\tilde{I}_j$ (see Malgrange, Pham, and for more general thimble integrals see \cite[Section 1.2.2]{mistegard_phdthesis} and \cite{andersen2020resurgence}, the Stirling series for Gamma function in \cite{Maxim_slide_ERC,Maxim_talk_2023}).
-
-Our goal is to study whether $\tilde{I}_j$ is Borel summable and whether its Borel--Laplace sum agrees with the integral $I_j$ itself.
-We’ll restrict to $1$-dimensional thimble integrals, and in this special case we’ll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-\color{black}
 We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.

### 2023-12-07 exp-resurgence.tex
Rephrase Borel regularity for thimbles and new proofs

@@
 \begin{brainstorm}
-    \item Section~\ref{borel_reg-ODE}---definitely Section~\ref{setting-ODE}, and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
+    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
     \item Do flagged revisions in Section~\ref{borel-reg-thimble}
@@
 \[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$. \textcolor{orange}{Introduce $\sim$ notation.}
+over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
 \end{defn}
 If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
-The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the the function's {\em asymptotic expansion} on that sector.
+The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector.
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
@@
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
-We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{setting-ODE}).
+We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
 
@@
 On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
-\subsubsection{Why does Borel summation work for solutions of level-$1$ ODEs?}
-\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}
-
+\subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
+%\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}
+%
 Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}.
@@
 labeled by the roots of $P$.
-This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{setting-ODE}).
+This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{borel_reg-ODE}).
 In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
@@
 We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-The image of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
+The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
+\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
 These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
 Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\footnote{\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
-However, this only seems to be possible when $X$ is 1-dimensional.}}
+The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
+However, this only seems to be possible when $X$ is 1-dimensional.}
 
@@
 \end{figure}
-Then, our main result for thimble integrals is proving that $1$-dimensional thimble integrals are indeed Borel regular:
-\begin{theorem}[see Theorem \ref{thm:maxim-dim}]\label{thm:maxim}
-    Let $\tilde{I}_{j}(z)\defeq e^{-z \alpha_j}(2\pi)^{1/2} z^{-1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for a generic direction $\theta$.
-Then:
+
+Let $I_j$ be the thimble integral through the thimble $\Lambda_j$ 
+\begin{equation}
+I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
+\end{equation}
+our main results give an explicit description of $I_j$ as a Laplace transform, and show that $I_j$ is indeed Borel regular.
+In fact, thimble integrals are Borel regular because they can be turned into Laplace transforms.
+\begin{theorem}[see Theorem \ref{thm:thimble_proj_formula-proof}]\label{thm:thimble_proj_formula}
+The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
+\begin{align}\label{eqn:formula}
+\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
+\end{align}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+\end{theorem}
+%\begin{remark}
+%The operator $\fracderiv{1/2}{\zeta}{\alpha}$ is the fractional derivative based at $\zeta = \alpha$, as defined in Section~\ref{L-int-op}:
+%\begin{align*}
+%\partial^{1/2}_{\zeta, \alpha} & \defeq \tfrac{\partial}{\partial \zeta} \, \partial^{3/2}_{\zeta, %\alpha} \\[2mm]
+%[\partial^{3/2}_{\zeta, \alpha} g](p) & \defeq \frac{1}{\Gamma(\tfrac{1}{2})} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} g\,d\zeta.
+%\end{align*}
+%\begin{verify}
+%\begin{align*}
+%[\partial^{0+1/2}_{\zeta, \alpha} f](p) & = \left(\tfrac{\partial}{\partial \zeta}\right)^{0+1} \partial^{1/2-1}_{\zeta, \alpha} \\
+%& = \left(\tfrac{\partial}{\partial \zeta(p)}\right)^{0+1} \frac{1}{\Gamma(1-1/2)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} f\,d\zeta
+%\end{align*}
+%\end{verify}
+%\end{remark}
+\begin{theorem}[see Theorem \ref{thm:maxim-proof}]\label{thm:maxim}
+The function $I_j$ is Borel regular. More explicitly: \textcolor{orange}{[Try to keep on one line]}
+\begin{enumerate}
+\item As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\phi}_j \defeq \borel_\zeta \tilde{\Phi}_j$ converges near $\zeta=\alpha_j$.
+\item If you continue the sum of $\tilde{\phi}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\end{enumerate}
+\end{theorem}
+\color{Goldenrod}
+Then, our main result for thimble integrals is proving they are indeed Borel regular:
+\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
+    Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
 \begin{enumerate}
@@
 \item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
-\begin{multline}\label{eqn:formula}
+\begin{multline}
 \hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
@@
 \end{theorem}
-The idea of the proof is sketched below in the following diagram (for the rigorous one we refer to Section \ref{borel-reg-thimble}).
+\color{black}
+We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
 \[
@@
 \]
-On the one hand, the thimble integral $I_j$ can be regarded as a Laplace type integral, i.e. as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}. 
+On the one hand, with a change of coordinates, the thimble integral $I_j$ can be written as a Laplace type integral, i.e.
+as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}.
 On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain.
@@
 
-The upshot is that thimble integrals are Borel regular because they can be turned into Laplace transforms.
 %% the following remark has been moved to Section of the proof
@@
 
-\begin{figure}[h]
+\begin{figure}[ht]
     \centering
-    %\includegraphics[]{}
+    \includegraphics[scale=0.15]{figures/cotg_singular_fibre_laplace.PNG}
     \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
-However, the fiber over a singular point of $B$ has an interesting structure.
-Here we represent the example of Airy functions.}
+However, the fiber over a singular point $s$ of $B$ has an interesting structure.
+Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
     \label{fig:different_fibres}
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsection{Borel regularity for level-$1$ ODEs}
-
-From a formal perspective, the general theory of linear level-$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_j$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_j\in e^{-\alpha_j z} z^{-\tau_j}\C\llbracket z^{-1}\rrbracket$, where $\tau_j=Q(-\alpha_j)/P’(-\alpha_j)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Since $-\alpha_1,…,-\alpha_d$ are distinct, the transmonomials $\tilde{\Psi}_1,…,\tilde{\Psi}_d$ determine a basis up to scaling, giving the space of formal solutions a a distinguished frame.
-Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a constructive method (see~\cite[Chapter 14]{balser}).
-Therefore, noticing that $\tilde{\Psi}_j$ are 1-Gevrey series (Ramis Index Theorem \cite{ramis_index}), a classical problem was to investigate Borel summability of these formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}, which consequently become a distinguished frame of analytic solutions.
-
-At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without going to a formal frame.
-This is possible, as we proved in~\cite{reg-sing-volterra}.
-By construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_1,…,\tilde{\Psi}_d$ (see Corollary~\ref{cor:borel_reg_ODE}).
-As briefly discussed in Section when we sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha_j$.
-Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+\subsection{Borel regularity for level~$1$ ODEs}
+%
+From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_j$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_j\in e^{-\alpha_j z} z^{-\tau_j}\C\llbracket z^{-1}\rrbracket$, where $\tau_j=Q(-\alpha_j)/P’(-\alpha_j)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Since $-\alpha_1,\ldots,-\alpha_d$ are distinct, the transmonomials $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ determine a basis up to scaling, giving the space of formal solutions a a distinguished frame.
+Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}).
+To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_j$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+
+At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
+This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ (see Corollary~\ref{cor:borel_reg_ODE}).
+As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha_j$.
+Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations analytically in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
 
 \begin{remark}
-Our approach of solving regular singular Volterra equation is analogous to the one that Braaksma~\cite{braaksma2006laplace} used to solve a different class of non linear ODEs and difference equations whose coefficients are themselves Laplace transforms.
+Our approach of solving regular singular Volterra equation is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
+\textcolor{orange}{[Let's do more compare-and-contrast!
+Our problem space is sort of orthogonal to Braaksma's, but we use the same solution space, so it seems like there could be a cool interaction there.]}
 \end{remark}
@@
 \begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs: formally in the $z$-plane Poincar\'e gave an explicit solution \cite{int-irreg}.
-Formally in the position domain \'Ecalle figured out how to find a frame of formal solutions of the Borel transformed ODE \cite{EcalleIII,loday-Remy2011}.
-It can indeed be seen as a consequence of ``resurgence'' of the ODE that the formal solutiomns can be analytically continued.
-Our results of \cite{reg-sing-volterra} show how to build a frame of solutions, analytically in the Borel plane.
-Here, we show we are picking the same frame: from the properties of the Laplace transform we get an analytic frame asymptotic to Poincar\'e frame $\series{\Psi}_j$.
-From the uniqueness result of \cite[Theorem~4]{reg-sing-volterra}, we get a frame of analytic solutions equivalent to \'Ecalle's ones.
+There are many ways to build a frame of solutions for these kinds of ODEs.
+\begin{center}
+\begin{tabular}{l|l|l}
+& \textbf{Analytic} & \textbf{Formal} \\ \hline
+\textbf{Frequency domain} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+\textbf{Position domain} & \'{E}calle: resurgence \textcolor{orange}{$\longleftarrow$} & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
+& Fixed-point iteration~\cite{reg-sing-volterra} \\
+\end{tabular}
+\end{center}
+In the late 1800s, Poincar\'{e} did it formally in the frequency domain~\cite{int-irreg}.
+In the late 1900s, \'{E}calle and later authors did it formally in the position domain~\cite{EcalleIII,loday-Remy2011}.
+\'{E}calle also showed that each of his formal solutions sums to a resurgent analytic solution, from which a frame of analytic solutions can be extracted.
+Most recently, we directly constructed a frame of analytic solutions in the position domain~\cite{reg-sing-volterra}.
+
+In Section~\ref{borel_reg-ODE}, we show that we're all finding the same frame.
+The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and the properties of the Laplace transform guarantee that our solutions, cast into in the frequency domain, are asymptotic to Poincar\'{e}'s.
 \end{remark} 
@@
 For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\textcolor{orange}{Take a look at Witten's paper on knots}
-
-In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, they are known as period integrals \cite{Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^B_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.
-Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_B^N(X,f)$.
-Then varying $\theta$, $H_B^N(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ whose monodromy can be computed by Picard--Lefschetz formula.
-it is possible understand the Stokes phenomena.
-
-Then, when $X$ is an $N$-dimensional complex manifold and $f$ is a Morse function\footnote{In fact, $f$ might satisfy milder assumptions (see for instance \cite[Section 1.2.2]{mistegard_phdthesis}).}, the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $\hbar\to 0$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
-In addition, varying the direction ....
+\textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could of a problem that is known to admit a thimble integral solution but hard to be defined explicitly.
+However, we know the perturbative expansion of this expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
+In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
+
+In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, they are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
+Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$.
+} Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$.
+Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha_i-\alpha_j)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).
+
+\textcolor{orange}{thimble integral as solution of ODE with irregular singularity and the Stokes phenomena. }
+
+Indeed, the Stokes data of an irregular singular connection can be computed by the Picard--Lefschetz formula (see~\cite[Section 3.3, Part II]{pham}).\textcolor{orange}{add references}  This can be also considered a consequence of our Borel regularity result when $f$ is a polynomial.
+For instance, special functions are classical examples of thimble integrals (with polynomial $f$), thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
+
+In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power}\footnote{In fact, $f$ might satisfy milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).}, the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z\to e^{i\theta}\infty$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
 However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
-This raises the question we address in this paper, namely to understand why Borel summation is effective for thimbles integrals.
-
-Special functions are classical examples of thimble integrals, and the Borel summability properties of their asymptotics can be studied either analytically (through resurgence or Borel-summability, see Section \ref{sec:examples}, and for the Gamma function \cite[Section 5.11]{diverg-resurg-i}\cite{sauzin2021variations}) or geometrically (as a Riemann--Hilbert problem  \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
-In addition, they typically come as \textcolor{orange}{[Stokes phenomena in one case ...
-in the other is ...]}
-
-\textcolor{orange}{Borel regularity: \cite[Part II, Section 3.3]{pham}} Assume we want to solve a problem whose solution is expected to be a thimble integral, but that is hard to be defined explicitly.
-However, we know the perturbative expansion of this expected solution, then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
-\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
+This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
+In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
+In addition.
+our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+
+ %In addition, they typically come as \textcolor{orange}{[Stokes phenomena in one case ... in the other is ...]}
 
@@
 \color{black}
-Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
 In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.
@@
 We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}
+\begin{definition}\label{defn:frac_driv}
 For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-
-\subsubsection{Setting}\label{setting-ODE}
-\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
+\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
 \begin{equation}
@@
 
-\subsubsection{Setting}
-
-Let $X$ be a $N$-dimensional manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^N)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{x_1,...,x_N\}$. Set
+Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{a_1,...,a_d\}$.
+Let $I_j$ be the thimble integral
 \begin{equation}\label{exp-int}
@@
 \end{equation}
-where $\Lambda_j$ is the thimble associated with the critical point $x_j$.  
-The saddle point approximation gives the formal series 
+where $\Lambda_j$ is the thimble through the critical point $a_j$.
+In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
+The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the thimble projection formula \eqref{eqn:formula-proof}.
+\begin{theorem}\label{thm:thimble_proj_formula-proof}
+The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
+\begin{align}\label{eqn:formula-proof}
+\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
+\end{align}
+where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
+Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+\end{theorem}
+\begin{proof}
+    Let us recast the integral $I_j$ into the position domain.
+As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
+Hence, we have
+\begin{align*}
+I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
+& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
+\end{align*}
+Noticing that the right-hand side is a Laplace transform, we learn that
+\begin{equation}\label{thimble-difference}
+{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
+\end{equation}
+\end{proof}
+We'll now prove that $I_j$ is Borel regular:
+\begin{theorem}\label{thm:maxim-proof}
+The function $I_j$ is Borel regular. More explicitly: 
+\begin{enumerate}
+\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
+\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $I_j$.
+\end{enumerate}
+\end{theorem}
+\begin{proof}
+    Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$.
+Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
+\textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
+that converges in some disk $|\tau| < \varepsilon$.
+
+By the steepest descent method,
+%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $\Re z \to \infty$ along the ray $e^{i\theta}\, \R_{> 0}$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)).
+Plugging in the Taylor series above, we get
+\begin{align*}
+e^{z \alpha_j} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
+\end{align*}
+By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
+= 1$.}
+\begin{align*}
+e^{z \alpha_j} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha_j} I_j(z)$.
+In other words,
+\[ e^{z \alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+To see why, cut the sum off after $N$ terms, and observe that
+\begin{align*}
+  \Bigg | \sum_{n= 0}^N(2n-1)!!
+b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
+b_{2n}^j n|z|^{-n}.
+\end{align*}
+The right-hand side goes to $0$ as $\Re(z)$ grows.
+%Hence,
+%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
+\[ e^{z\alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
+Hence, defining the formal series $\tilde{I_j}$
+\[\tilde{I}_j(z):=e^{-z\alpha_j} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-n}\]
+we get $\tilde{I}_j\in e^{-z\alpha_j}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
+
+Using the porperties of the Borel tranform acting on trans-mononials \ref{sec:action_transseries} we get 
+\begin{align*}
+\tilde{\iota}_j & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^j\,\frac{\zeta_j^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
+&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^j\,\zeta_j^{n+\tfrac{1}{2}}
+\end{align*}
+We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$, thus we deduce that $\tilde{\iota}_j$ has a finite radius of convergence.
+This ends the proof of part \ref{part-2}.
+%$|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
+
+The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; in fact we'll show that the Taylor expansion of $\iota_j$ near $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.
+
+We can rewrite the Taylor series for $\nu$ as
+\begin{align*}
+\nu & = \sum_{n \ge 0} b_n^j [2(f - \alpha_j)]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\iota_j$ \eqref{eqn:formula-proof}, we learn that
+\begin{align*}
+\iota_j & = \left[ \sum_{n \ge 0} b_n^j [2(f - \alpha_j)]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
+& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} 
+\end{align*}
+In particular, $\tilde{\iota}_j$ can be analytically continued along $\Gamma_j^\theta$ and its sum is given by $\iota_j$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
+%\begin{align*}
+ %   \laplace_{\zeta,\alpha_j}^\theta \phi_j &= \laplace_{\zeta,\alpha_j}^\theta \fracderiv{-1/2}{\zeta}{\alpha_j} \iota_j \\
+ %   &= z^{-1/2} \laplace_{\zeta,\alpha_j}^\theta  \iota_j \\
+ %   &= z^{-1/2} I_j
+%\end{align*}
+\end{proof}
+\begin{remark}
+    For some applications, it might be more convenient to study Borel regularity of $\Phi_j=z^{-1/2}I_j$, as its asymptotics won't have fractional power singularities.
+The proof follows the same steps we did for $I_j$, so we won't repeat them in deltails.
+However, we remark that also $\Phi_j$ is the Laplace transform of a function $\phi_j$ which can be explicitly computed using the thimble projection formula \eqref{eqn:formula-proof}.
+Indeed, first notice that \[\phi_j = \fracderiv{-1/2}{\zeta}{\alpha_j} \, \iota_j \]
+    Then, we can take the $1/2$ fractional integral on both side  
+    \begin{align*}
+        \fracderiv{-1/2}{\zeta}{\alpha_j} \phi_j &= \fracderiv{-1}{\zeta}{\alpha_j} \, \iota_j \\ 
+        &= \fracderiv{-1}{\zeta}{\alpha_j} \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)\\
+        &=  \int_{\Lambda_j(\zeta)}\nu
+    \end{align*}
+    and, finally we use that fractional derivatives are is left inverse of fractional integrals
+    \[\phi_j= \fracderiv{1/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right).\]
+\end{remark}
+
+\color{RoyalBlue}
+The saddle point approximation\footnote{When $f$ is a polynomial see \cite{Malgrange22,pham}. More generally, if $f$ is holomorphic \textcolor{orange}{see \cite{Pham83}?}} gives the formal series 
 \begin{equation}
-{I}_{j}(z)\defeq\int_{\Lambda_j}e^{-zf}\nu\sim \tilde{I}_{j}\defeq e^{-z\alpha_j}(2\pi)^{N/2} z^{-N/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to\infty
-\end{equation}
-
-\textcolor{orange}{[cite or prove]}
-%Notice that $f \circ \mathcal{C}_\alpha$ lies in the ray $\zeta_\alpha +[0, \infty)$, where $\zeta_\alpha := f(x_\alpha)$.
-
-\subsubsection{Main result}
-\begin{theorem}\label{thm:maxim-dim} Let $N=1$. Let $\tilde{\Phi}_{j}(z)\defeq e^{-z\alpha_j}(2\pi)^{1/2} \sum_{n\geq 0}a_{j,n}z^{-n}$. Then:
+{I}_{j}(z)\sim \tilde{I}_{j}\defeq e^{-z\alpha_j}(2\pi)^{1/2} z^{-1/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to \infty. 
+\end{equation}
+%
+Then our main result states that for every $j=1,\ldots,d$, the thimble integral $I_j$ is Borel regular:
+\begin{theorem}\label{thm:maxim-dim} Let $\tilde{\Phi}_{j}(z)=z^{1/2}\,\tilde{I}_j(z)\in e^{-z\alpha_j}\C\llbracket z^{-1}\rrbracket$. Then:
 \begin{enumerate}
@@
 \begin{multline}\label{formula1}
-\hat{\phi}_{j}(\zeta)=\fracderiv{\textcolor{red}{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
+\hat{\phi}_{j}(\zeta)=\fracderiv{{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
 \end{multline}
@@
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z f(\alpha_j)} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{\textcolor{magenta}{+}z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 as $\Re z \to \infty$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)). Plugging in the Taylor series above, we get
@@
 \begin{equation}\label{shifted-resum-valid}
-\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{\alpha_j} \tilde{\phi}_j.
+\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{\alpha_j} \hat{\phi}_j.
 \end{equation}
@@
 \begin{align*}
-I_j(z) & = \laplace_{\zeta, \alpha_j} \left[ \partial^{-1/2}_{\zeta, \alpha_j}  \tilde{\phi}_j \right] \\
+I_j(z) & = \laplace_{\zeta, \alpha_j} \left[ \partial^{-1/2}_{\zeta, \alpha_j}  \hat{\phi}_j \right] \\
 & = z^{-1/2} \laplace_{\zeta, \alpha_j} \tilde{\phi}_j,
 \end{align*}
-as we claimed. \textcolor{cyan}{[should we use $\hat{\phi}_j$ when we write the convolution product, assuming the germ is continuable in certain direction?]}
+as we claimed.
 
@@
 we can see that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(\textcolor{Magenta}{\alpha_j})} \nu. \]
-The initial value term vanishes because the path $\textcolor{Magenta}{\alpha_j}$ is a point. Hence,
+\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(\alpha_j)} \nu. \]
+The initial value term vanishes because the path $\alpha_j$ is a point. Hence,
 \[ \int_{\Lambda_j(\zeta)} \nu = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j(\zeta). \]
@@
 \end{proof}
-
+\color{black}
 \begin{remark}
-    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the Borel transform of $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
-Furthermore, expanding $\hat{\phi}_j$ at its critical points we recover the germs $\series{\phi}_k$ for $k\neq j$.
+    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the germ $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
+Furthermore, expanding $\hat{\phi}_j$ at its critical points, we recover the germs $\series{\phi}_k$ for $k\neq j$.
 This is an instance of resurgence, indeed according to the theory of \'Ecalle, $\hat{\phi}_j$ are all resurgent functions.
@@
 \begin{remark}\label{rmk:Pham formula}
-    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as 
+    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}_j$ explicitly as 
     \begin{equation}\label{eqn:Pham}
@@
    \end{equation*}
-In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
+In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of ${\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
 We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.

### 2023-12-21 exp-resurgence.tex
Update thimble integral proof

@@
 The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j$ be the ray going rightward from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j$ which vanishes at $\alpha_j$.
-These are well-defined as long as $\Gamma_j$ misses the critical values of $f$.
-Then, the preimage $f^{-1}(\Gamma_j)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j$ can be regarded as the component of $f^{-1}(\Gamma_j)$ that goes through $a_j$.\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
+\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j^\theta$ which vanishes at $\alpha_j$.
+These are well-defined as long as $\Gamma_j^\theta$ misses the critical values of $f$.
+Then, the preimage $f^{-1}(\Gamma_j^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j^\theta$ misses the other critical values of $f$.
+The Lefschetz thimble $\Lambda_j^\theta$ can be regarded as the component of $f^{-1}(\Gamma_j^\theta)$ that goes through $a_j$.
+\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
 However, this only seems to be possible when $X$ is 1-dimensional.}
@@
     \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
-    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity.}
+    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity along the positive real axis.}
     \label{fig:thimble_vs_rays}
@@
 
-Let $I_j$ be the thimble integral through the thimble $\Lambda_j$ 
+Let $I_j$ be the thimble integral through the thimble $\Lambda_j^\theta$,
 \begin{equation}
-I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
-\end{equation}
-our main results give an explicit description of $I_j$ as a Laplace transform, and show that $I_j$ is indeed Borel regular.
-In fact, thimble integrals are Borel regular because they can be turned into Laplace transforms.
-\begin{theorem}[see Theorem \ref{thm:thimble_proj_formula-proof}]\label{thm:thimble_proj_formula}
-The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
-\begin{align}\label{eqn:formula}
-\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
-\end{align}
+I_j(z)\defeq\int_{\Lambda_j^\theta}e^{-zf}\nu
+\end{equation}
+our main results show that $I_j$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. Thus, we recall the well-known result
+\begin{lemma}[see Lemma \ref{lem:thimble_proj_formula-proof}]\label{lem:thimble_proj_formula}
+A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
+\begin{equation}\label{eqn:formula}
+\iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right),
+\end{equation}
 where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
@@
 \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{theorem}
+\end{lemma}
 %\begin{remark}
@@
 %\end{remark}
+Then, Borel regularity for thimble integrals is stated in the following theorem: 
 \begin{theorem}[see Theorem \ref{thm:maxim-proof}]\label{thm:maxim}
-The function $I_j$ is Borel regular. More explicitly: \textcolor{orange}{[Try to keep on one line]}
+If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\phi}_j \defeq \borel_\zeta \tilde{\Phi}_j$ converges near $\zeta=\alpha_j$.
-\item If you continue the sum of $\tilde{\phi}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
+\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.
 \end{enumerate}
@@
 
-In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, they are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
+In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
 Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$.
@@
 where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
+We’ll use the shorthand $\laplace_{\zeta, \beta}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = \beta}$ throughout this document.
 
@@
 \[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
-for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by 
+for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
 %
@@
     \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
-\end{equation}
-%
-Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
+\end{equation}\color{black}
+%
+\color{RoyalBlue}Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
 \[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
-for all $\lambda \in (0, \infty)$, where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by
-
+for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
+%
 \begin{equation}
     \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
-\end{equation}
-
+\end{equation}\color{RoyalBlue}
+%
 Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
 However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
+[Isn't this a special case of the $\laplace_{\zeta, \alpha}$ statement?]\color{black}
 
@@
 \begin{equation}\label{exp-int}
-I_j(z)\defeq\int_{\Lambda_j}e^{-zf}\nu
+I_j \defeq \int_{\Lambda_j} e^{-zf} \nu
 \end{equation}
@@
 In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the thimble projection formula \eqref{eqn:formula-proof}.
-\begin{theorem}\label{thm:thimble_proj_formula-proof}
-The intgral $I_j$ is the Laplace transform $\laplace_{\alpha_j}^\theta \iota_j$ of the function $\iota_j$ given by the {\em thimble projection formula}
-\begin{align}\label{eqn:formula-proof}
-\iota_{j} & = \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)
-\end{align}
+The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
+\begin{lemma}\label{lem:thimble_proj_formula-proof}
+\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
+\[ \iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right), \]
 where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
@@
 \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{theorem}
+\end{lemma}
 \begin{proof}
@@
 \begin{theorem}\label{thm:maxim-proof}
-The function $I_j$ is Borel regular. More explicitly: 
+If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 \item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
-\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray \textcolor{magenta}{$\Gamma_j^\theta$}, and take its Laplace transform along that ray, you'll recover $I_j$.
+\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.
 \end{enumerate}
@@
 \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
+\[ \nu = \sum_{m \ge 0} b_m^j \tau^m\,d\tau \]
 that converges in some disk $|\tau| < \varepsilon$.
 
-By the steepest descent method,
+Let's write $\approx$ when two functions are asymptotic at all orders around the base poin; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} t
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\Re z \to \infty$ along the ray $e^{i\theta}\, \R_{> 0}$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)).
-Plugging in the Taylor series above, we get
-\begin{align*}
-e^{z \alpha_j} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
+\[ e^{z \alpha_j} I_j \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $z \to \infty$ along the ray $e^{-i\theta}\, \R_{> 0}$. Plugging in the Taylor series for $\nu$, we get
+\begin{align*}
+e^{z \alpha_j} I_j & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^j \tau^m\,d\tau \\
 & = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
@@
 \begin{align*}
-e^{z \alpha_j} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+e^{z \alpha_j} I_j & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
 & = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
@@
 
-The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; in fact we'll show that the Taylor expansion of $\iota_j$ near $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; \textcolor{pink}{in fact, we'll show that the Taylor expansion of $\iota_j$ near $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.}
 
@@
 \end{align*}
-taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\iota_j$ \eqref{eqn:formula-proof}, we learn that
-\begin{align*}
-\iota_j & = \left[ \sum_{n \ge 0} b_n^j [2(f - \alpha_j)]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
-& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
+taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$.
+Plugging this into our expression for $\iota_j$ (in Theorem \ref{thm:thimble_proj_formula-proof}), we learn that
+\begin{align*}
+\iota_j & = \left[ \sum_{m \ge 0} b_m^j [2(f - \alpha_j)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
+& = \sum_{m \ge 0} b_m^j \Big( [2\zeta_j]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_j]^{(m - 1)/2} \Big) \\
 & = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
@@
 %\end{align*}
+
+\color{RoyalBlue}
+Theorem~\ref{thm:thimble_proj_formula-proof} tells us that
+\begin{align*}
+I_j & = \laplace_{\zeta, \alpha_j}^\theta \iota_j \\
+e^{z\alpha_j} I_j & = \laplace_{\zeta_j, 0}^\theta \iota_j \\
+& = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} + \textcolor{orange}{\zeta^{N+1/2} f}\right) \\
+& \color{magenta} = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = 0}^\infty 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right).
+%%& = \int_{\Gamma_j^\theta} e^{-z\zeta_j} \iota_j\,d\zeta_j \\
+%%& = \int_{\Gamma_j^\theta} e^{-z\zeta_j} \left( \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right) d\zeta_j
+\end{align*}
+Over any finite number of terms, we can exchange the sum with the Laplace transform, giving
+\begin{align*}
+e^{z\alpha_j} I_j & = \Delta_n + \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j\,\laplace_{\zeta_j, 0}^\theta \zeta_j^{n - 1/2} \\
+& = \Delta_n + \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j \Gamma(n + \tfrac{1}{2})\,z^{-n - 1/2} \\
+& = \Delta_n + \sum_{n = 0}^N \sqrt{2\pi}\,(2n - 1)!!\,b_{2n}^j\,z^{-n - 1/2},
+\end{align*}
+where
+\[ \Delta_n = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = N+1}^\infty 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right). \]
+\begin{verify}
+\begin{align*}
+2^n \Gamma(n + \tfrac{1}{2}) & = \sqrt{\pi}\,(2n - 1)!! \\
+2^{n + 1/2} \Gamma(n + \tfrac{1}{2}) & = \sqrt{2\pi}\,(2n - 1)!!
+\end{align*}
+\end{verify}
+
+\begin{prop}
+Consider a function
+\[ \varphi = \sum_{\kappa \in K} a_\kappa \zeta^\kappa \]
+defined by a power series with real exponents $K \subset (-1, \infty)$, with a positive lower bound on the distances between the exponents.
+If the series converges throughout the disk $|\zeta| < \varepsilon$, then
+\[ \partial_{\zeta, 0}^{-\nu} \varphi = \sum_{\kappa \in K} \tfrac{\Gamma(\kappa+1)}{\Gamma(\kappa+\nu+1)} \zeta^{\kappa + \nu} \]
+on that disk.
+\end{prop}
+\begin{proof}
+The convergence of the series for $\varphi$ in the disk $|\zeta| < \varepsilon$ implies that for each $\eta \in (0, \varepsilon)$, we have $|a_\kappa| \lesssim \eta^{-\kappa}$ over all $\kappa \in K$.
+The
+\end{proof}
+\begin{verify}
+Reference for monomials: ``Evaluation of Fractional Integrals and Derivatives of Elementary Functions''
+
+For convenience, think of $K$ as sequence, in increasing order. At any point $\zeta = \rho$ with $|\rho| < \varepsilon$, the series defining $\varphi$ converges, implying that
+\begin{align*}
+& \lim_{\kappa \in K} |a_\kappa \rho^\kappa| = 0 \\
+& \lim_{\kappa \in K} |a_\kappa| |\rho|^\kappa = 0 \\
+& |a_\kappa| |\rho|^\kappa \lesssim 1 \text{ over all } \kappa \in K \\
+& |a_\kappa| \lesssim |\rho|^{-\kappa} \text{ over all } \kappa \in K.
+\end{align*}
+In other words, for every $r \in (0, \varepsilon)$, we have $|a_\kappa| \lesssim r^{-\kappa}$ over all $\kappa in K$.
+
+Hence, on the region $|\zeta| < |\rho|$, we have
+\begin{align*}
+|\varphi| & \le \sum_{\kappa \in K} |a_n| |\zeta|^\kappa \\
+& \lesssim \sum_{\kappa \in K} r^{-\kappa} |\zeta|^\kappa \\
+& = \sum_{\kappa \in K} |\zeta/r|^\kappa.
+\end{align*}
+In the disk $|\zeta| < r$, the ratio $|\zeta/r|$ is smaller than $1$, so increasing its exponent always decreases the value.
+
+Let $c > 0$ be the lower bound on the distances between the exponents.
+Choose some $\lambda \in (-1, \infty)$ so that $K \subset (\lambda, \infty)$.
+For each $n \in \mathbb{N}_{\ge 0}$, the $n$th element of $K$ must be greater than $\lambda + nc$, so
+\begin{align*}
+|\varphi| & \lesssim \sum_{n = 0}^\infty |\zeta/r|^{\lambda + nc} \\
+& = |\zeta/r|^\lambda \sum_{n = 0}^\infty (|\zeta/r|^c)^n \\
+& = \frac{|\zeta/r|^\lambda}{1 - |\zeta/r|^c} \\
+& = \frac{1}{|\zeta/\rho| - |\zeta/r|^{1+c}}.
+\end{align*}
+We now see that the series defining $\varphi$ converges absolutely on $|\zeta| < |\rho|$.
+
+The kernel of $\partial_{\zeta, 0}^{\nu-1}$ is $\big(\zeta(p) - \zeta\big)^{\nu-1}$. It has an integrable singularity at $p$, and it's non-singular at $\zeta = 0$.
+\end{verify}
+
+\begin{prop}
+Suppose $f_0, f_1, f_2, \ldots$ is a sequence of holomorphic functions on some connected domain $\Omega$, and the series $\sum_{k=0}^\infty |f_k|$ converges at each point in $\Omega$.
+Then, for any $\nu > 0$,
+\[ \partial_{\zeta, \alpha}^{-\nu} \left( \sum_{k=0}^\infty f_k \right) = \sum_{k=0}^\infty \partial_{\zeta, \alpha}^{-\nu} f_k \]
+throughout $\Omega$.
+\end{prop}
+\begin{proof}
+Given any point $p \in \Omega$, choose a path $\gamma$ that runs through $\Omega$ from $\zeta = \alpha$ to $p$.
+Since $\gamma$ is the continous image of a closed interval, it's compact, so $\zeta$ is bounded
+
+Recalling that
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+\textcolor{orange}{[\ldots]}
+\end{proof}
+
+By the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} \textcolor{magenta}{[define $\approx$]}
+%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{z \alpha_j} I_j \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $z \to \infty$ along the ray $e^{-i\theta}\, \R_{> 0}$.
+%%Since the Taylor series for $\nu$ converges in the disk $|\tau| < \varepsilon$, we know that $|b_m^j| \lesssim \varepsilon^{-m}$ over all $m \ge 0$, giving
+%%\[ \left| e^{-z\zeta_j}\;2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right| \lesssim 2^{n+1/2} \varepsilon^{-2n} e^{-\Re(z\zeta_j)} |\zeta_j|^{n - 1/2}. \]
+%%When $z\zeta_j \in \R_{> 0}$, that implies
+%%\begin{align*}
+%%\left| e^{-z\zeta_j}\;2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right| \lesssim 2^{n+1/2} \varepsilon^{-2n} e^{-|z||\zeta_j|} |\zeta_j|^{n - 1/2}.
+%%\end{align*}
+\color{black}
 \end{proof}
 \begin{remark}
-    For some applications, it might be more convenient to study Borel regularity of $\Phi_j=z^{-1/2}I_j$, as its asymptotics won't have fractional power singularities.
-The proof follows the same steps we did for $I_j$, so we won't repeat them in deltails.
-However, we remark that also $\Phi_j$ is the Laplace transform of a function $\phi_j$ which can be explicitly computed using the thimble projection formula \eqref{eqn:formula-proof}.
+    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_j$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_j=z^{-1/2}I_j$, as its asymptotics won't have fractional power singularities.
+The proof follows the same argument we chose for $I_j$, but there's one subtulty to be aware of when rewriting $\Phi_j$ as the Laplace transform of $\phi_j$.
 Indeed, first notice that \[\phi_j = \fracderiv{-1/2}{\zeta}{\alpha_j} \, \iota_j \]
-    Then, we can take the $1/2$ fractional integral on both side  
+    Then, we can take the $1/2$ fractional integral on both sides:
     \begin{align*}
         \fracderiv{-1/2}{\zeta}{\alpha_j} \phi_j &= \fracderiv{-1}{\zeta}{\alpha_j} \, \iota_j \\
-        &= \fracderiv{-1}{\zeta}{\alpha_j} \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right)\\
-        &=  \int_{\Lambda_j(\zeta)}\nu
-    \end{align*}
-    and, finally we use that fractional derivatives are is left inverse of fractional integrals
+        & = \fracderiv{-1}{\zeta}{\alpha_j} \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right) \\
+        & = \int_{\Lambda_j(\zeta)}\nu - \int_{\Lambda_j(\alpha_j)}\nu.
+    \end{align*}
+    The second term vanishes because $\Lambda_j(\alpha)$ is a single point, leaving
+    \[ \fracderiv{-1/2}{\zeta}{\alpha_j} \phi_j = \int_{\Lambda_j(\zeta)}\nu. \]
+    Since the $1/2$ derivative of
+    Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral:
     \[\phi_j= \fracderiv{1/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right).\]
+    \textcolor{orange}{[This argument works for any function that vanishes at $\alpha_j$, so maybe we should instead prove it generally in the section on fractional calculus.]}
 \end{remark}
@@
 \begin{corollary}\label{simple-res-thimble}
-    If $f$ and $\nu$ are polynomials, the function $\hat{\phi}_j$ defined in \eqref{formula1} ha simple resurgent singularities at $\zeta=\alpha_k$.  
+    If $f$ and $\nu$ are polynomials, the function $\hat{\phi}_j$ defined in \eqref{formula1} has simple resurgent singularities at $\zeta=\alpha_k$.  
 \end{corollary}
@@
 We’ll see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of Theorem~4 from \cite{reg-sing-volterra}.
+This is evidence of Theorem~4 from \cite{reg-sing-volterra}.
 %\subsection{Going to the spatial domain}\label{spatial-AL}
 \subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
 We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
@@
 \end{remark}
+\subsection{The triangular catilever}\label{sec:catilever}
+The equation of a triangular cantilever with \textcolor{orange}{[...]} $\mu\in\R\setminus\{0\}$ is 
+\begin{equation}\label{eqn:triangular_cantilever}
+    \Big[\big[\Big(\frac{\partial}{\partial z}\Big)^4 +\mu\big]+\frac{2}{z}\Big(\frac{\partial}{\partial z}\Big)^3\Big]\varphi=0 .
+\end{equation}
+Going to the position domain we can solve the equation explicitly: let $\alpha_1,\ldots,\alpha_4$ be the solutions of $\lambda^4+\mu=0$; we'll look for solutions $v_j$ whose Laplace transform $\laplace_{\zeta,\alpha_j}v_j$ satisfies the equation \eqref{eqn:triangular_cantilever}.
+For $j=1,\ldots,4$, $v_j$ solves
+\begin{equation}\label{eqn:position_j}
+    \Big[\big[\zeta^4+\mu\big]+2\fracderiv{-1}{\zeta}{\alpha_j}\circ(-\zeta)^3\Big] v_j=0
+\end{equation}
+As we'll show in Section \ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 
+\begin{equation}
+    \Big[\big[\zeta^4+\mu\big]\tfrac{\partial}{\partial\zeta}-2\zeta^3\Big]v_j = 0
+\end{equation}
+In particular, at $\zeta_j=\zeta-\alpha_j$ we find 
+\[v_j \propto \frac{1}{\zeta_j^{1/2}}\, \prod_{k\neq j}(\zeta_j-\alpha_k+\alpha_j)^{-1/2}.\]
+\textcolor{orange}{[Stokes? Thimbles?]}
+%\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}
 

### 2023-12-21 exp-resurgence.tex
Updates from Overleaf

@@
 \item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+Recall that $\theta$ is the direction of the ray $\Gamma^\theta_j$.
 \item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
@@
 
-Let's write $\approx$ when two functions are asymptotic at all orders around the base poin; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} t
+Let's write $\approx$ when two functions are asymptotic at all orders around the base poin; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
@@
 \begin{remark}
+We can use the $3/2$ derivative formula~\eqref{formula1} to see that the functions $\phi_j$ are all resurgent, in the sense of \'{E}calle~\cite[\textcolor{orange}{section?}]{EcalleI}.
+Let's say $\Gamma_j(\beta)$ is the straight path from $\zeta = \alpha_j$ to $\zeta = \beta$ in $\C$.
+As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\Lambda_j(\beta)$ in $X$.
+This lets us analytically continue $\int_{\Lambda_j(\zeta)} \nu$ to a star-shaped domain $\Omega \subset \C$.
+Intuitively, $\Omega$ is constructed by drawing rays from $\zeta = \alpha_j$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$.
+\begin{center}
+\textcolor{orange}{FIGURE OF SLIT DOMAIN}
+\end{center}
+Let's calculate the jump of $\int_{\Lambda_j(\zeta)}$ across the cut starting at $\zeta = \alpha_k$.
+Write $\alpha_k$ as $\alpha_j + re^{i\theta}$, and let $\alpha_k^+$ and $\alpha_k^-$ be the points we get by infinitesimally increasing or decreasing $\theta$.
+The jump is then given by $\int_{\Lambda_j(\alpha_k^+)} \nu - \int_{\Lambda_j(\alpha_k^-)} \nu$.
+
+\textcolor{Navy}{Initially, the function $\int_{\Lambda_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\Lambda_j(\zeta)$.
+Since $\nu$ is holomorphic, the only way for $\int_{\Lambda_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\Lambda_j(\zeta)$.
+At a critical point of $f$, the ends of the homotoped path $\Lambda_j(\zeta)$ come together, telling us that.}
+\end{remark}
+\color{DarkSeaGreen}
+\begin{remark}
     The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the germ $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
 Furthermore, expanding $\hat{\phi}_j$ at its critical points, we recover the germs $\series{\phi}_k$ for $k\neq j$.
-This is an instance of resurgence, indeed according to the theory of \'Ecalle, $\hat{\phi}_j$ are all resurgent functions.
+This is an instance of resurgence, indeed according to the theory of \'{E}calle, $\hat{\phi}_j$ are all resurgent functions.
 We'll see an example in Appendix~\ref{apx:eye-res-airy}.
 \end{remark}
+\color{black}
 \textcolor{orange}{

### 2023-12-30 exp-resurgence.tex
Correction of eq 2 in the introduction check thimble integrals

--- 2023-12-21 exp-resurgence.tex
@@
 ]}
+
+%% for the figure
+% colors
+\definecolor{smoked}{RGB}{216, 212, 204}
+\definecolor{mauve}{RGB}{200, 55, 171}
+\definecolor{apricot}{RGB}{250, 144, 4}
+\definecolor{sky}{RGB}{66, 169, 244}
+\definecolor{plum}{RGB}{76, 0, 102}
+
+% === phase space laplace ===
+\include{../figures/phase-space-laplace.tex}
 
@@
 \begin{equation}
-e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{85085}{33592320} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
 \end{equation}
@@
 as
-\textcolor{orange}{[How do we know it is a solution of Equation (1)?]}
-\color{orange}
-\[ e^{z}\, (2\pi)^{-\tfrac{1}{2}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{2}{3} t + \frac{5}{72} t^2 - \frac{32}{27} t^3 + \frac{385}{31104} t^4 - \frac{224}{81} t^5 + \frac{85085}{33592320} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}.
-\color{black}
+\[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
+using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}---up to a constant.\begin{verify}
+    see Mathematica document.
+\end{verify}
+
 Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
@@
 The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a_j$, let $\Gamma_j^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha_j$, and let $\zeta_{\alpha_j}$ be the translation coordinate around $\Gamma_j^\theta$ which vanishes at $\alpha_j$.
-These are well-defined as long as $\Gamma_j^\theta$ misses the critical values of $f$.
-Then, the preimage $f^{-1}(\Gamma_j^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_j^\theta$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_j^\theta$ can be regarded as the component of $f^{-1}(\Gamma_j^\theta)$ that goes through $a_j$.
-\textcolor{orange}{We could orient so that shifting $\Lambda_j$ to its left would make its projection run clockwise around $\Gamma_j$.
+\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a$, let $\Gamma_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\Gamma_\alpha^\theta$ which vanishes at $\alpha$.
+These are well-defined as long as $\Gamma_\alpha^\theta$ misses the critical values of $f$.
+Then, the preimage $f^{-1}(\Gamma_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_\alpha^\theta$ misses the other critical values of $f$.
+The Lefschetz thimble $\Lambda_a^\theta$ can be regarded as the component of $f^{-1}(\Gamma_\alpha^\theta)$ that goes through $a$.
+\textcolor{orange}{We could orient so that shifting $\Lambda_a$ to its left would make its projection run clockwise around $\Gamma_\alpha$.
 However, this only seems to be possible when $X$ is 1-dimensional.}
@@
 \end{figure}
-
-Let $I_j$ be the thimble integral through the thimble $\Lambda_j^\theta$,
+Choose $a$ a ciritcal point of $f$ and $\alpha=f(a)$, let $I$ be the thimble integral through the thimble $\Lambda_a^\theta$,
 \begin{equation}
-I_j(z)\defeq\int_{\Lambda_j^\theta}e^{-zf}\nu
-\end{equation}
-our main results show that $I_j$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. Thus, we recall the well-known result
+I(z)\defeq\int_{\Lambda_a^\theta}e^{-zf}\nu
+\end{equation}
+our main results show that $I$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. We recall the well-known result
 \begin{lemma}[see Lemma \ref{lem:thimble_proj_formula-proof}]\label{lem:thimble_proj_formula}
-A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
+A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula}
-\iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right),
-\end{equation}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+\iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\Lambda^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\Lambda(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\Lambda$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
@@
 \begin{theorem}[see Theorem \ref{thm:maxim-proof}]\label{thm:maxim}
-If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 
+If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
-\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.
+\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+Recall that $\theta$ is the direction of the ray $\Gamma^\theta_\alpha$.
+\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
+\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
 \end{enumerate}
@@
 \begin{tikzcd}
-{I}_{j} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}_{j}\arrow[dd,"\borel"]\\
+{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
 & & &\\
-\iota_j \arrow[r,equal] & \hat{\iota}_j & &\tilde{\iota}_{j} \arrow[ll, "\text{sum}"]
+\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]
 \end{tikzcd}
 \]
-On the one hand, with a change of coordinates, the thimble integral $I_j$ can be written as a Laplace type integral, i.e.
-as the Laplace transform of a function $\iota_j$, written explicitly in equation~\eqref{eqn:formula}.
-On the other hand, we compute the asymptotic expansion of $I_j$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain.
-Consequently, its Borel transform $\series{\iota}_j$ is a germ of holomorphic functions at $\zeta=\alpha_j$ in the position domain.
-Then, we'll show that the Taylor expansion of $\iota_j$ at $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.
+On the one hand, with a change of coordinates, the thimble integral $I$ can be written as a Laplace type integral, i.e.
+as the Laplace transform of a function $\iota$, written explicitly in equation~\eqref{eqn:formula}.
+On the other hand, we compute the asymptotic expansion of $I$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain.
+Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain.
+Finally, we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
 
@@
 \centering
-    \includegraphics[scale=0.15]{figures/cotg_singular_fibre_laplace.PNG}
+    \includegraphics{testbed/testbed1.pdf}
     \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
-However, the fiber over a singular point $s$ of $B$ has an interesting structure.
+However, the fiber over a singular point of $B$ has an interesting structure.
 Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
@@
 The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}.
-In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}_j$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
+In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
 
@@
 %
-From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_j$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_j\in e^{-\alpha_j z} z^{-\tau_j}\C\llbracket z^{-1}\rrbracket$, where $\tau_j=Q(-\alpha_j)/P’(-\alpha_j)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Since $-\alpha_1,\ldots,-\alpha_d$ are distinct, the transmonomials $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ determine a basis up to scaling, giving the space of formal solutions a a distinguished frame.
+From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame.
 Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}).
 To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_j$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
 
 At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
-This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_1,\ldots,\tilde{\Psi}_d$ (see Corollary~\ref{cor:borel_reg_ODE}).
-As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha_j$.
+This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Corollary~\ref{cor:borel_reg_ODE}).
+As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
 Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations analytically in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
@@
 In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
-Generic directions correspond to $\theta\neq \arg (\alpha_k-\alpha_j)$, and $k\neq j$.
+Generic directions correspond to $\theta\neq \arg (\alpha-\beta)$.
 } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$.
-Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha_i-\alpha_j)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).
+Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha-\beta)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).
 
@@
 \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T^*B_b$ by the formula
+When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
 \begin{equation}\label{laplace:int}
@@
 \subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T^*B_b$, as long as we take care of a few subtleties.
+When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties.
 Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
-The function $z$ is defined on $T^*B_b^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
+The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
 This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}.
-The half-plane $z \in H_{\theta}$ in $T^*B_b^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T^*B_b$.
+The half-plane $z \in H_{\theta}$ in $T_b^*B^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T_b^*B$.
 We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
@@
 When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable.
-Hence, the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T^*B_{\zeta=\alpha}$~\cite[Section  5.6]{diverg-resurg-i}.
+Hence, the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=\alpha}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
 %Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
@@
 \begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros at $-\alpha_j$ for $j=1,...,d$ i.e.
-such that $P'(-\alpha_j)\neq 0$ for every $j=1,...,d$; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha_j)\neq 0$ for all $j=1,...,d$;
+\item $P$ is a monic degree-$d$ polynomial with simple zeros; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
+\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha)\neq 0$ for all zeros $\alpha$;
 \item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
@@
 
-For every $j=1,...,d$, let $\Omega_j\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha_j$. We also assume:
+For every zeros $\alpha$, let $\Omega_\alpha\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha$. We also assume:
 \begin{itemize}
-\item The set $\Omega_j$ is star-shaped around $\zeta = \alpha_j$.
-In other words, for any $a \in \Omega_j$, a straight path from $\zeta = \alpha_j$ to $a$ stays in $\Omega_j$.
-Since $\Omega_j$ doesn't contain $\zeta = \alpha_j$, we'll always leave that starting point out of the path.
-\item The set $\Omega_j$ does not contain the tubular neighborhood of the other critical points $-\alpha_k$, for $k\neq j$, as shown in Figure \ref{Fig:domain}.
-\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_j$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
+\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$.
+In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$.
+Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we'll always leave that starting point out of the path.
+\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
+\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
 Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
@@
   arc (-60:-130:\spill) -- (0, 0);
-\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha_j$};
-\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\alpha_k$};
+\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha$};
+\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
 \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
@@
 %\end{theorem}
-\color{Maroon}
-For each root $\alpha$ of $P$,
-\color{black}
-
 \begin{theorem}\label{thm2-dim}
@@
 Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
-For every $j=1,...,d$, let $\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{j,0}=1$.
-Then $\series{\Psi}_j(z)$ is Borel summable and its Borel sum is proportional to $\Psi_j$.
+For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)=e^{-\alpha z}z^{-\tau_\alpha}\sum_{n=0}^{\infty}a_{\alpha,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$.
+Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum is proportional to $\Psi_\alpha$.
 \end{theorem}
@@
 \begin{itemize}
-\item[$(a)$] let $\series{\psi}_j:=\borel_{\zeta}\series{\Psi}_j$, then $\hat{P}_j\series{\psi}_j=0$.
-\item[$(b)$] prove that $\laplace_{\zeta,\alpha_j}^{\theta}\circ\borel_\zeta\series{\Psi}_j\propto \Psi_j $. 
+\item[$(a)$] let $\series{\psi}_\alpha:=\borel_{\zeta}\series{\Psi}_\alpha$, then $\hat{P}_\alpha\series{\psi}_\alpha=0$.
+\item[$(b)$] prove that $\laplace_{\zeta,\alpha}^{\theta}\circ\borel_\zeta\series{\Psi}_\alpha\propto \Psi_\alpha $. 
 \end{itemize}
@@
 Step $(b)$ clearly follows from \cite[Theorem 4]{reg-sing-volterra} and step $(a)$.
-In fact, $\Tilde{\psi}_j$ and ${\psi}_j$ are both solutions of $\hat{P}_j\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
-Then, we can Laplace transform ${\psi}_j$ along a ray $\Gamma_{\alpha_j}^\theta$ in $\Omega_j$.
-Hence if $\hat{\psi}_j$ denotes the analytic continuation of $\tilde{\psi}_j$ which agrees with $\psi_j$, we can Laplace transform $\hat{\psi}_j$ along $\Gamma_{\alpha_j}^\theta$, too.
-
-We now prove step $(a)$: we want to show that $\series{\psi}_j=\borel_{\zeta}\series{\Psi}_j$ is a solution of $\hat{\mathcal{P}}_j\series{\psi}_j=0$.
-Recall that $\tilde{\Psi}_j$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_j$ is written in terms of the convolution product $\ast_{\alpha_j}$.
+In fact, $\Tilde{\psi}_\alpha$ and ${\psi}_\alpha$ are both solutions of $\hat{P}_\alpha\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+Then, we can Laplace transform ${\psi}_\alpha$ along a ray $\Gamma_{\alpha}^\theta$ in $\Omega_\alpha$.
+Hence if $\hat{\psi}_\alpha$ denotes the analytic continuation of $\tilde{\psi}_\alpha$ which agrees with $\psi_\alpha$, we can Laplace transform $\hat{\psi}_\alpha$ along $\Gamma_{\alpha}^\theta$, too.
+
+We now prove step $(a)$: we want to show that $\series{\psi}_\alpha=\borel_{\zeta}\series{\Psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha=0$.
+Recall that $\tilde{\Psi}_\alpha$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_\alpha$ is written in terms of the convolution product $\ast_{\alpha}$.
 
@@
 \begin{align*}
-  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_j\right)&= \left[P(-\zeta)+1\ast_{\alpha_j} Q(-\zeta)+\zeta \ast_{\alpha_j} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha_j}(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\
-  &=\left[P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha_j} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j} )(-\zeta)^r\right)\right]\series{\psi}_j(\zeta_j)\\&=\hat{P}_j\tilde{\psi}_j(\zeta_j)
+  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_\alpha\right)&= \left[P(-\zeta)+1\ast_{\alpha} Q(-\zeta)+\zeta \ast_{\alpha} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha}(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
+  &=\left[P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha} )(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_j)\\&=\hat{P}_\alpha\tilde{\psi}_\alpha(\zeta_\alpha)
 \end{align*}
@@
 
-Hence, the Borel transform of $\series{\Psi}_j$ is a solution of $\hat{P}_j\series{\psi}_j$=0. 
+Hence, the Borel transform of $\series{\Psi}_\alpha$ is a solution of $\hat{P}_\alpha\series{\psi}_\alpha$=0. 
 \end{proof}
@@
 
-Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points $\{a_1,...,a_d\}$.
-Let $I_j$ be the thimble integral
+Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
+Let $I$ be the thimble integral
 \begin{equation}\label{exp-int}
-I_j \defeq \int_{\Lambda_j} e^{-zf} \nu
-\end{equation}
-where $\Lambda_j$ is the thimble through the critical point $a_j$.
+I \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
+\end{equation}
+where $\Lambda_a^\theta$ is the thimble through the critical point $a$.
 In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_j$ as the Laplace transform of a function $\iota_j$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
+The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
 \begin{lemma}\label{lem:thimble_proj_formula-proof}
-\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota_j$ with $I_j = \laplace_{\zeta, \alpha_j}^\theta \iota_j$ is given by the {\em thimble projection formula}
-\[ \iota_{j} = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_j(\zeta)}\nu \right), \]
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j,\zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
+\begin{equation}\label{eqn:formula-proof}
+    \iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\Lambda_\alpha^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\Lambda_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\Lambda_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
 \begin{proof}
-    Let us recast the integral $I_j$ into the position domain.
-As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
+    Let us recast the integral $I$ into the position domain.
+As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\Lambda_\alpha^\theta(\zeta)$ sweep backward along $\Lambda^-_\alpha(\zeta)$ and forward along $\Lambda^+_\alpha(\zeta)$, respectively.
 Hence, we have
 \begin{align*}
-I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
-& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
+I(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
+& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}\,d\zeta.
 \end{align*}
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
+{\iota}(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
 \end{equation}
 \end{proof}
-We'll now prove that $I_j$ is Borel regular:
+We'll now prove that $I$ is Borel regular:
 \begin{theorem}\label{thm:maxim-proof}
-If the integral defining $I_j$ is absolutely convergent, then $I_j$ is Borel regular. More explicitly: 
+If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I_j$ is asymptotic to a trans-monomial $\tilde{I}_{j}\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item\label{part-2} The series $\tilde{I}_j$ is $1$-Gevrey. In other words, $\tilde{\iota}_j \defeq \borel_\zeta \tilde{I}_j$ converges near $\zeta=\alpha_j$.
-\item\label{part-3} If you continue the sum of $\tilde{\iota}_j$ along the ray $\Gamma_j^\theta$, and take its Laplace transform along that ray, you'll recover $I_j$.
+\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
+\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
 \end{enumerate}
@@
 \begin{proof}
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$.
-Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
+Let $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$ be the parts of $\Lambda_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$, respectively.
 \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{m \ge 0} b_m^j \tau^m\,d\tau \]
+\[ \nu = \sum_{m \ge 0} b_m^a \tau^m\,d\tau \]
 that converges in some disk $|\tau| < \varepsilon$.
 
-Let's write $\approx$ when two functions are asymptotic at all orders around the base poin; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} t
+Let's write $\approx$ when two functions are asymptotic at all orders around the base point; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{z \alpha_j} I_j \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$ along the ray $e^{-i\theta}\, \R_{> 0}$. Plugging in the Taylor series for $\nu$, we get
-\begin{align*}
-e^{z \alpha_j} I_j & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^j \tau^m\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
+\[ e^{z \alpha} I \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+as $z \to \infty$. Plugging in the Taylor series for $\nu$, we get
+\begin{align*}
+e^{z \alpha} I & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau.
 \end{align*}
@@
 \begin{align*}
-e^{z \alpha_j} I_j & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha_j} I_j(z)$.
+e^{z \alpha} I & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+\end{align*}
+
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha} I(z)$.
 In other words,
-\[ e^{z \alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\[ e^{z \alpha} I(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 To see why, cut the sum off after $N$ terms, and observe that
@@
   \Bigg | \sum_{n= 0}^N(2n-1)!!
-b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
-b_{2n}^j n|z|^{-n}.
+b_{2n}^a  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
+b_{2n}^a n|z|^{-n}.
 \end{align*}
@@
 The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{z\alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
-Hence, defining the formal series $\tilde{I_j}$
-\[\tilde{I}_j(z):=e^{-z\alpha_j} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-n}\]
-we get $\tilde{I}_j\in e^{-z\alpha_j}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
+\[ e^{z\alpha} I(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
+Hence, defining the formal series $\tilde{I}$
+\[\tilde{I}(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
+we get $\tilde{I}\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
 
@@
 \begin{align*}
-\tilde{\iota}_j & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^j\,\frac{\zeta_j^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
-&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^j\,\zeta_j^{n+\tfrac{1}{2}}
-\end{align*}
-We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$, thus we deduce that $\tilde{\iota}_j$ has a finite radius of convergence.
+\tilde{\iota} & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
+&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
+\end{align*}
+We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\tilde{\iota}$ has a finite radius of convergence.
 This ends the proof of part \ref{part-2}.
@@
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; \textcolor{pink}{in fact, we'll show that the Taylor expansion of $\iota_j$ near $\zeta=\alpha_j$ agrees with $\tilde{\iota}_j$.}
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; \textcolor{pink}{in fact, we'll show that the Taylor expansion of $\iota$ near $\zeta=\alpha$ agrees with $\tilde{\iota}$.}
 
@@
 \begin{align*}
-\nu & = \sum_{n \ge 0} b_n^j [2(f - \alpha_j)]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$.
-Plugging this into our expression for $\iota_j$ (in Theorem \ref{thm:thimble_proj_formula-proof}), we learn that
-\begin{align*}
-\iota_j & = \left[ \sum_{m \ge 0} b_m^j [2(f - \alpha_j)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
-& = \sum_{m \ge 0} b_m^j \Big( [2\zeta_j]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_j]^{(m - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2}
-\end{align*}
-In particular, $\tilde{\iota}_j$ can be analytically continued along $\Gamma_j^\theta$ and its sum is given by $\iota_j$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
+\nu & = \sum_{n \ge 0} b_n^a [2(f - \alpha)]^{(n - 1)/2}\,df,
+\end{align*}
+taking the positive branch of the square root on $\Lambda^+_a$ and the negative branch on $\Lambda^-_a$.
+Plugging this into our expression for $\iota$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
+\begin{align*}
+\iota & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_a(\zeta)}^{\operatorname{end} \Lambda_a(\zeta)} \\
+& = \sum_{m \ge 0} b_m^a \Big( [2\zeta_\alpha]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_\alpha]^{(m - 1)/2} \Big) \\
+& = \sum_{n \ge 0} 2 b_{2n}^a [2\zeta_\alpha]^{n - 1/2} \\
+& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^a \zeta_\alpha^{n - 1/2}
+\end{align*}
+In particular, $\tilde{\iota}$ can be analytically continued along $\Gamma_\alpha^\theta$ and its sum is given by $\iota$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
 %\begin{align*}
@@
 \color{RoyalBlue}
-Theorem~\ref{thm:thimble_proj_formula-proof} tells us that
+Lemma~\ref{lem:thimble_proj_formula-proof} tells us that
 \begin{align*}
@@
 \end{proof}
-\begin{remark}
-    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_j$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_j=z^{-1/2}I_j$, as its asymptotics won't have fractional power singularities.
-The proof follows the same argument we chose for $I_j$, but there's one subtulty to be aware of when rewriting $\Phi_j$ as the Laplace transform of $\phi_j$.
-Indeed, first notice that \[\phi_j = \fracderiv{-1/2}{\zeta}{\alpha_j} \, \iota_j \]
+\begin{remark}\label{rmk:1/2-deriv}
+    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi=z^{-1/2}I$, as its asymptotics won't have fractional power singularities.
+The proof follows the same argument we chose for $I$, but there's one subtulty to be aware of when rewriting $\Phi$ as the Laplace transform of a function $\phi$.
+Indeed, first notice that \[\phi = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota \]
     Then, we can take the $1/2$ fractional integral on both sides:
     \begin{align*}
-        \fracderiv{-1/2}{\zeta}{\alpha_j} \phi_j &= \fracderiv{-1}{\zeta}{\alpha_j} \, \iota_j \\
-        & = \fracderiv{-1}{\zeta}{\alpha_j} \partial_\zeta \left( \int_{\Lambda_j(\zeta)}\nu \right) \\
-        & = \int_{\Lambda_j(\zeta)}\nu - \int_{\Lambda_j(\alpha_j)}\nu.
-    \end{align*}
-    The second term vanishes because $\Lambda_j(\alpha)$ is a single point, leaving
-    \[ \fracderiv{-1/2}{\zeta}{\alpha_j} \phi_j = \int_{\Lambda_j(\zeta)}\nu. \]
+        \fracderiv{-1/2}{\zeta}{\alpha} \phi &= \fracderiv{-1}{\zeta}{\alpha} \, \iota \\
+        & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\Lambda_a^\theta(\zeta)}\nu \right) \\
+        & = \int_{\Lambda_\alpha^\theta(\zeta)}\nu - \int_{\Lambda_\alpha^\theta(\alpha)}\nu.
+    \end{align*}
+    The second term vanishes because $\Lambda_\alpha^\theta(\alpha)$ is a single point, leaving
+    \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
     Since the $1/2$ derivative of
     Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral:
-    \[\phi_j= \fracderiv{1/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right).\]
-    \textcolor{orange}{[This argument works for any function that vanishes at $\alpha_j$, so maybe we should instead prove it generally in the section on fractional calculus.]}
+    \[\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\]
+    \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
 \end{remark}
@@
 \begin{remark}
+We can use the $3/2$ derivative formula~\eqref{formula1} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[\textcolor{orange}{section?}]{EcalleI}.
+Let's say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
+As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\Lambda_\alpha^\theta(\beta)$ in $X$.
+This lets us analytically continue $\int_{\Lambda_\alpha^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
+Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$.
+\begin{figure}
+\center
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=radial edge]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (180:\spill)
+  arc (180:113:\spill) -- (112:2) .. controls (112:1.7) and (111:1.7) .. (111:2) -- (111:\spill)
+  arc (111:50:\spill) -- (50:2.6) .. controls (50:2.2) and (49:2.2) .. (49:2.6) -- (49:\spill)
+  arc (49:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-53:2) .. (-53:2.3) -- (-53:\spill)
+  arc (-53:-180:\spill) -- (0, 0);
+  \node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
+\foreach \p in {(111.5:1.9), (49.5:2.4), (-52.5:2.2)} {
+  \fill \p circle (0.7mm);
+  \draw[dashed,violet!50] \p -- (0,0); 
+  }
+\fill[violet] circle (0.7mm) node[anchor=180, outer sep=1mm] {$\zeta = \alpha$};
+\end{tikzpicture}
+\caption{The domain $\Omega_\alpha$}\label{Fig:slit domain}
+\end{figure}
+Let's calculate the jump of $\int_{\Lambda_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
+Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
+The jump is then given by $\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu$ which turns out to be proportional to $\tilde{\phi}_\beta$, namely the germ of analytic functions at $\zeta_\alpha=\beta$.
+We'll see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
+
+\textcolor{Navy}{Initially, the function $\int_{\Lambda_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\Lambda_j(\zeta)$.
+Since $\nu$ is holomorphic, the only way for $\int_{\Lambda_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\Lambda_j(\zeta)$.
+At a critical point of $f$, the ends of the homotoped path $\Lambda_j(\zeta)$ come together, telling us that.}
+\end{remark}
+\color{DarkSeaGreen}
+\begin{remark}
     The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the germ $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
 Furthermore, expanding $\hat{\phi}_j$ at its critical points, we recover the germs $\series{\phi}_k$ for $k\neq j$.
-This is an instance of resurgence, indeed according to the theory of \'Ecalle, $\hat{\phi}_j$ are all resurgent functions.
+This is an instance of resurgence, indeed according to the theory of \'{E}calle, $\hat{\phi}_j$ are all resurgent functions.
 We'll see an example in Appendix~\ref{apx:eye-res-airy}.
 \end{remark}
+\color{black}
 \textcolor{orange}{
@@
 \begin{remark}\label{rmk:Pham formula}
-    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}_j$ explicitly as 
+    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}$ explicitly as 
     \begin{equation}\label{eqn:Pham}
@@
     \end{equation}
-    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
+    for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\ell}$ be defined as
    \begin{equation*}
-       \delta^{-\alpha}:=\begin{cases}
-           \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
+       \delta^{-\ell}:=\begin{cases}
+           \frac{\zeta^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \ell\in\mathbb{N}^*\\
            & \\
-           \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
+           \frac{(-\zeta)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \text{ hol. funct.} & \text{ if } \ell\notin \mathbb{N}^* 
        \end{cases}
    \end{equation*}
-In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of ${\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
-We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
+In particular, if $N=1$, as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.
+\textcolor{magenta}{We expect this result to hold beyond the polynomial case.} We also expect that equation \eqref{eqn:formula-proof} can be generalized to the $N$-dimensional case replacing the $1/2$-derivative with the $N/2$ one.
 \end{remark}

### 2024-01-17 exp-resurgence.tex
Sync before meeting

@@
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
+We'll denote such map with the symbol $\aexp$.
+More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e.
+as $z\to e^{i\theta}\infty$, we'll write $\aexp^\theta$.
 
@@
 \begin{enumerate}
-\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\textcolor{DarkTurquoise}{\cite[Section~5.2.2.1]{diverg-resurg-iii}}.
+\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
 One example is Equation~\eqref{eqn:bessel-rescaled-1}.
@@
 \begin{remark}
-Our approach of solving regular singular Volterra equation is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
+Our approach of solving regular singular Volterra equation---based on the contraction mapping theorem for suitable Banach spaces \cite{reg-sing-volterra}---is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
+What distinguishs our result from the one of Braaksma is to consider the Laplace transform of functions with integrable fractional power singuarities, and even if our result has been proved for linear level~1 ODEs, we allow holomorphic coefficents that are not necesserly Laplace transforms.
+
+We leave a possible generalization of our result to other classes of ODEs and difference equations for further pubblications.
 \textcolor{orange}{[Let's do more compare-and-contrast!
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion.
+In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion (see also \cite{Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}).
 For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could of a problem that is known to admit a thimble integral solution but hard to be defined explicitly.
-However, we know the perturbative expansion of this expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
+\textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly.
+However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
 In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
@@
 } Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$.
-Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha-\beta)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite{pham,Arnold}).
-
-\textcolor{orange}{thimble integral as solution of ODE with irregular singularity and the Stokes phenomena. }
-
-Indeed, the Stokes data of an irregular singular connection can be computed by the Picard--Lefschetz formula (see~\cite[Section 3.3, Part II]{pham}).\textcolor{orange}{add references}  This can be also considered a consequence of our Borel regularity result when $f$ is a polynomial.
-For instance, special functions are classical examples of thimble integrals (with polynomial $f$), thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
-
-In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power}\footnote{In fact, $f$ might satisfy milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).}, the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z\to e^{i\theta}\infty$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
-However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
+Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha-\beta)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite[Section~1]{Arnold} and \cite[Section~3.3, Part II]{pham}).
+Equivalently, the monodromy data can be computed as the Stokes phenomena for Laplace transforms; indeed as a consequence of our Borel regularity result Theorem~\ref{thm:maxim}, thimble integrals can be turned into Laplace transforms.
+
+Classical examples of thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
+
+In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z\to e^{i\theta}\infty$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
 This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
 In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
-In addition.
-our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
 
@@
 
-\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
-\color{DarkTurquoise}
-These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
+%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
+%\color{DarkTurquoise}
+%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
 In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
 Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
-\color{black}
-%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
+%\color{black}
+%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
 In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.
@@
 \begin{itemize}
-\item With respect to the flat metric, \textcolor{red}{$f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.}\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
 We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
@@
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-In this case, for any $\Lambda \in \R$, let \textcolor{magenta}{$\widehat{\Omega}_\alpha^\Lambda$} $\dualsector{\alpha}{\lambda}$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
+In this case, for any $\Lambda \in \R$, let \textcolor{magenta}{$\widehat{\Omega}_\alpha^\Lambda$} $\dualsector{\alpha}{\Lambda}$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
 Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \end{proof}
-
 \color{RoyalBlue}
@@
 \color{black}
-\subsubsection{Change of translation chart}\label{translation}
-Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
+\subsubsection{Properties of the Laplace transform}
+%\subsubsection{Change of translation chart}\label{translation}
+\begin{lemma}\label{translation}
+Let $\zeta_\alpha$ be a coordinate on $B$ so that $\zeta = \alpha + \zeta_\alpha$, then
+   \begin{equation}
+    \label{change-chart}
+    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
+\end{equation} 
+\end{lemma}
+\begin{proof}
+    The result follws from a simple calculation:
     \begin{align*}
@@
 & = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    \label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-%
-\subsubsection{Rescaling of translation structure}
-%
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi.
+\end{align*}
+\end{proof}
 Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
@@
 The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
+\begin{lemma}
+Under the previous assumptions
+    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+\end{lemma}
+\begin{proof}
+    From the computation 
     \begin{align*}
@@
 \end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+we get the desired result. 
+\end{proof}
+%
 Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
 We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-%
-\subsubsection{Action on integral operators}\label{L-int-op}
-%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+
+For applications is useful to study the action of the Laplace transform on both fractional integral and fractional derivative operators.
+Recall that for $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
 \[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
+where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
+%
+\begin{equation*}
+    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi(\zeta_\alpha+\alpha)\, d\zeta_\alpha.
+\end{equation*}}
 
@@
 \end{align*}
+\begin{lemma}\label{L-int-op}
+    The following identities hols true:
+    \begin{itemize}
+        \item[i)]\label{item:i} for some $\sigma>-1$, $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ and for all $\lambda \in (0, \infty)$
+        \[%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\]
+\item[ii)]\label{item:ii} if $\varphi \in \singexpalg{\sigma}$, for all integers $n \ge 0$
+\[%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\]
+\item[iii)]\label{item:iii} if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
+\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
+for all $\lambda \in (0, \infty)$. 
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    The result of \emph{i)} follows from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
+Similarly, one can prove \emph{iii)}.
+\end{proof}
+%
+\color{RoyalBlue}
+Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
+\begin{align*}
+\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
+\end{align*}
+we learn that
+\begin{equation}
+    %\label{change-chart}
+    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
+\end{equation}
+%
+\subsubsection{Rescaling of translation structure}
+%
+Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
+The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
+From the calculation
+\begin{align*}
+\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \varphi
+\end{align*}
+we learn that
+\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
+%
+\subsubsection{Action on integral operators}\label{L-int-op}
+%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
+%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $B$.
+
+It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+We'll use the {\em Riemann-Liouville} convention.
+\begin{definition}\label{defn:frac_driv}
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+\end{definition}
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
 
@@
 \begin{align*}
-\borel\textcolor{orange}{_\zeta}\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+\borel_\zeta\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
 \end{align*}
@@
     \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
-    Since the $1/2$ derivative of
     Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral:
-    \[\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\]
+    \begin{equation}\label{eqn:formula--1/2}\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
     \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
@@
 \begin{remark}
-We can use the $3/2$ derivative formula~\eqref{formula1} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[\textcolor{orange}{section?}]{EcalleI}.
+We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[\textcolor{orange}{section?}]{EcalleI}.
 Let's say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
@@
 Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
-The jump is then given by $\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu$ which turns out to be proportional to $\tilde{\phi}_\beta$, namely the germ of analytic functions at $\zeta_\alpha=\beta$.
+The jump is then given by $\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu$ which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
 We'll see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
@@
 \end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation
+Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name?
+Is that standard?]}
 \begin{equation}\label{eqn:mod-bessel-AL}
@@
 The Borel transform maps $e^{-\alpha_j z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ for $\alpha = 1$ and $\alpha = -1$, respectively.
+Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
+Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
 
 When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}.
-It therefore has exactly one solution in $\singexpalg{1/2}$, up to scaling.
+It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling.
 That means $\borel\big[ e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j \big]$ must sum to a scalar multiple of $v_j$.

### 2024-01-17 to-do.tex
Sync before meeting

\documentclass{article}

\title{To-do}
\date{}

\begin{document}
\maketitle
\section{Intro}
\begin{itemize}
\item Finish new version of ``Why does Borel summation work for solutions of level 1 ODEs?''
\end{itemize}
\section{The Laplace and Borel transforms}
\begin{itemize}
\item Finish ``Regularity and decay properties''
\end{itemize}
\section{Proof of main results}
\begin{itemize}
    \item Finish new version of ''Borel regularity for ODEs''
\end{itemize}
\section{Examples}
\begin{itemize}
\item Revise Borel regularity argument for Airy-Lucas
\item Rewrite thimble projection reasoning for Airy-Lucas functions
\item Explain equation of tringular cantilver
\end{itemize}
\section{Figures}
For some reason all figures move at the end of the document. Moreover I'd prefer to add the picture of the Borel plane as translation surface as tikzpicture and not as pdf.
\end{document}

### 2024-01-19 exp-resurgence.tex
Updates from Overleaf

@@
 \newcommand{\done}[1]{\textcolor{gray}{#1}}
-
-\theoremstyle{definition}
-\newtheorem{defn}{Definition}
-%%\theoremstyle{plain}
-%%\newtheorem{prop}{Proposition}
 
@@
 
+% theorem environments
+\theoremstyle{definition}
+\newtheorem{defn}{Definition}
 \newtheorem{definition}{Definition}[section]
@@
     \begin{itemize}
-    \item Replace formalism in Section~\ref{reg-decay}
+    \item Replace formalism in Section~\ref{sec:reg-decay}
     \end{itemize}
@@
     \item Section~\ref{sec:mod-bessel-lift}---pin down contour
-    \item Explain contour figure in Airy example [explain what the regions indicate and what the color]
+    \item Explain contour figure in Airy example (explain what the regions indicate and what the color)
     \begin{itemize}
@@
 \end{theorem}
+\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
 \begin{corollary}\label{cor:borel_reg_ODE}
@@
 \end{corollary}
+\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable.
+See Section~\ref{sec:new-summability-proof}.}
+\textcolor{violet}{[In another section, do the ``mirror image'' argument.
+Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way.
+Use the Ramis index theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
+%%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
+%%\begin{corollary}
+%%\textcolor{orange}{[The Poincar\'{e} solution is Borel summable.]}
+%%\end{corollary}
 \color{black}
+\textcolor{Violet}{[This is sort of a mirror image of the Ramis index theorem?]}
 \begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
@@
 The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
-The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
+The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
 Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
@@
 We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} (or cite Aaron's article, which will hopefully present the same background in the translation surface context).
+This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
 \begin{figure}[ht]
@@
 %
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.
+The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}.
 At an ordinary point, we can define $z$ simply as the map
@@
 \begin{equation}\label{laplace:int}
-\laplace_\zeta^\theta f\big|_b = \int_{\Gamma_b^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function and $\Gamma_b^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We’ll use the shorthand $\laplace_{\zeta, \beta}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = \beta}$ throughout this document.
+\laplace_{\zeta}^\theta f\big|_b = \int_{\Gamma_{b}^\theta} e^{-z\zeta} f\,d\zeta,
+\end{equation}
+where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$.
+We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
 
@@
 %\color{black}
-\subsection{The Laplace transform: analytic version}\label{sec:laplace_analytic}
-\subsubsection{Regularity and decay properties}\label{reg-decay}
-%
-Let $\Omega_\alpha \subset B$ be an open, simply connected set that touches but does not contain $\zeta=\alpha$ (see Figure \ref{Fig:domain}).
-Suppose $\Omega_\alpha$ contains the ray $\Gamma_{\zeta,\alpha}^\theta$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ of holomorphic functions on $\Omega_\alpha$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta|^\sigma$ as $\zeta$ approaches $\alpha$.
-When $\sigma>-1$, the singularity at $\zeta=\alpha$ is integrable.
-Hence, the Laplace transform $\laplace_{\zeta, \alpha}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=\alpha}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
+\subsubsection{Change of translation chart}\label{sec:change-translation}
+Let $b\in B$ be an ordinary point, and let $\zeta_b$ be a coordinate on $B$ so that $\zeta = b + \zeta_b$, then the Laplace transform $\laplace_{\zeta_b,0}$ is defined on $T^*_{b}B$ and it's compatible with $\laplace_{\zeta,b}$.
+\begin{lemma}\label{translation}
+Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
+   \begin{equation}
+    \label{change-chart}
+    \laplace_{\zeta_b, 0} \varphi = e^{b z} \laplace_{\zeta, b} \varphi.
+\end{equation}
+In other words, the diagram 
+\begin{center}
+\begin{tikzcd}
+ \mathcal{O}(H) \arrow[rr, "e^{bz}"]  &  & e^{zb}\,\mathcal{O}(H)\\
+& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
+\end{tikzcd}
+\end{center}
+commutes, and $H$ is the right half plane $\Re z>0$.
+\end{lemma}
+\begin{proof}
+    The result follws from a simple calculation:
+    \begin{align*}
+\laplace_{\zeta, b} \varphi & = \int_{\Gamma_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\Gamma_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
+& = e^{-b z} \int_{\Gamma_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
+& = e^{-b z} \laplace_{\zeta_b, 0} \varphi.
+\end{align*}
+\end{proof}
+We now consider a rescale of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
+The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
+\begin{lemma}
+Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and for some $\Lambda>0$, then
+    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+\end{lemma}
+\begin{proof}
+    From the computation 
+    \begin{align*}
+\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \varphi
+\end{align*}
+we get the desired result. 
+\end{proof}
+%
+%Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
+\subsection{Analysis of the Laplace transform}\label{sec:laplace_analytic}
+
+\subsubsection{Regularity and decay properties}\label{sec:reg-decay}
+%
+Let $\Omega_b \subset B$ be an open, simply connected set that touches but does not contain $\zeta=b$ (see Figure \ref{Fig:domain}).
+Suppose $\Omega_b$ contains the ray $\Gamma_{\zeta,b}^\theta$.
+In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_b)$ of holomorphic functions on $\Omega_b$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta|^\sigma$ as $\zeta$ approaches $b$.
+When $\sigma>-1$, the singularity at $\zeta=b$ is integrable.
+Hence, the Laplace transform $\laplace_{\zeta, b}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_b)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=b}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
 %Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
@@
 \color{black}
-\subsubsection{Properties of the Laplace transform}
-%\subsubsection{Change of translation chart}\label{translation}
-\begin{lemma}\label{translation}
-Let $\zeta_\alpha$ be a coordinate on $B$ so that $\zeta = \alpha + \zeta_\alpha$, then
-   \begin{equation}
-    \label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation} 
-\end{lemma}
-\begin{proof}
-    The result follws from a simple calculation:
-    \begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi.
-\end{align*}
-\end{proof}
-Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-\begin{lemma}
-Under the previous assumptions
-    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-\end{lemma}
-\begin{proof}
-    From the computation 
-    \begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we get the desired result. 
-\end{proof}
-%
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-
-For applications is useful to study the action of the Laplace transform on both fractional integral and fractional derivative operators.
-Recall that for $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
-%
-\begin{equation*}
-    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi(\zeta_\alpha+\alpha)\, d\zeta_\alpha.
-\end{equation*}}
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}\label{defn:frac_driv}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-\begin{lemma}\label{L-int-op}
-    The following identities hols true:
-    \begin{itemize}
-        \item[i)]\label{item:i} for some $\sigma>-1$, $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ and for all $\lambda \in (0, \infty)$
-        \[%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\]
-\item[ii)]\label{item:ii} if $\varphi \in \singexpalg{\sigma}$, for all integers $n \ge 0$
-\[%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\]
-\item[iii)]\label{item:iii} if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
-\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
-for all $\lambda \in (0, \infty)$. 
-    \end{itemize}
-\end{lemma}
-\begin{proof}
-    The result of \emph{i)} follows from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
-This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
-Similarly, one can prove \emph{iii)}.
-\end{proof}
-%
-\color{RoyalBlue}
-Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    %\label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-%
-\subsubsection{Rescaling of translation structure}
-%
-Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-%
-\subsubsection{Action on integral operators}\label{L-int-op}
-%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}\label{defn:frac_driv}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-
-%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-
-%\color{Tan}
-%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-%for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-%\begin{equation}%%\label{id:L-mult}
-%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-%\end{equation}
-%for all integers $n \ge 0$.
-
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
-\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
-for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
-\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
-for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
-%
-\begin{equation}
-    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
-\end{equation}\color{black}
-%
-\color{RoyalBlue}Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
-\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
-for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
-%
-\begin{equation}
-    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
-\end{equation}\color{RoyalBlue}
-%
-Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
-However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
-[Isn't this a special case of the $\laplace_{\zeta, \alpha}$ statement?]\color{black}
-
-%We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
-
-%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
-In fact, as we’ll see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
-
-%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
-
+%
+%
+%
 \subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
@@
 \[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
-Here, we're thinking of $z$ as the standard coordinate on $T^*B_{\zeta = 0}$, as described in Section~\ref{transl-freq}.
-We can get a function on $T^*B_{\zeta = \alpha}$ instead by taking the Laplace transform with respect to the coordinate $\zeta_\alpha$ defined by $\zeta = \zeta_\alpha + \alpha$:
-\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}. \]
+Here, we're thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
+We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
+\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
+
+\color{orange}
+\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
+\color{black}
 On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
 This formal inverse is called the {\em Borel transform}.
-
-The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
+To be more precise, the Borel transform $\borel_\zeta$ on $T^*_{\zeta = 0}B$ is the inverse of $\laplace_{\zeta,0}$ on monomials
+\begin{center}
+\begin{tikzcd}[every arrow/.append style={shift left}]
+ \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow{u}{\laplace_{\zeta, 0}}
+\end{tikzcd}
+\end{center}
+and it extends to formal power series by linearity 
 \begin{align*}
 \borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
-In general, by linearity,
-\begin{align*}
-\borel_\zeta\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-\end{align*}
-If a function $\varphi$ belongs to $\singexpalg{0}$, and its Taylor series
+\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
+\end{align*}
+
+\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
+
+%The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
+%\begin{align*}
+%\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
+%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
+%\end{align*}
+%In general, by linearity,
+%\begin{align*}
+%\borel_\zeta\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+%\end{align*}
+If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
 \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
@@
 
-If we'd expanded $\varphi$ as a Taylor series $\series{\varphi}_\alpha$ in the translated coordinate $\zeta_\alpha$ from above, we could've taken the Laplace transform $\laplace_{\zeta_\alpha,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*B_{\zeta = \alpha}$.
-Using the Borel transform with respect to $\zeta_\alpha$, defined like before as a formal inverse of $\laplace_{\zeta_\alpha,0}$
-
-\begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
-
-we could again recover $\series{\varphi}_\alpha$.
-
-It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha}$, as discussed in Section~\ref{transl-borel}.
+If we'd expanded $\varphi$ as a Taylor series ${\varphi}_b$ in the translated coordinate $\zeta_b$ from above, we could have taken the Laplace transform $\laplace_{\zeta_b,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*_{\zeta = b}B$.
+Using the Borel transform with respect to $\zeta_b$, defined like the formal inverse of $\laplace_{\zeta_b,0}$
+\begin{center}
+\begin{tikzcd}[every arrow/.append style={shift left}]
+ \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \zeta_b^2, \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
+\end{tikzcd}
+\end{center}
+and extended to formal power series by linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$,
+%\begin{align*}
+%\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C %\llbracket \zeta_b \rrbracket \\
+%\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta_b^n}{n!},
+%\end{align*}
+%%\begin{align*}
+ %%    \borel_{\zeta_b}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_b \rrbracket  \\
+  %%   z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
+ %%\end{align*}
+we could again recover ${\varphi}_b$.
+
+Summarizing, we can describe the geometry of Borel and Laplace transforms by drawing the following diagram
+\begin{center}
+\begin{tikzcd}[every arrow/.append style={shift left}]
+ \text{functions on } T^*_{\zeta=0}B \arrow{d}{\borel_{\zeta}} & & \text{functions on } T^*_{\zeta=b}B \arrow{d}{\borel_{\zeta_b}}\arrow[ll,swap,"\mathsf{T}_b^*"] \\ 
+ \text{functions of } \zeta \arrow{u}{\laplace_{\zeta, 0}}\arrow[rr,"\mathsf{T}_b"'] & & \text{functions of } \zeta_b \arrow{u}{\laplace_{\zeta_b, 0}}
+\end{tikzcd}
+\end{center}
+where $\mathsf{T}_b$ denotes the map of change of variables $\mathsf{T}_b(\zeta)=\zeta_b$.
+\textcolor{orange}{I don't like much the word function and the map $\mathsf{T}_b$, but we could change later.}
+
+%It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha,0}$, as discussed in Section~\ref{transl-borel}.
 
@@
 
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $a_n$ is a sequence of complex numbers such that $0=a_0 e^{-i\theta}< a_1 e^{-i\theta}<...<a_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
+A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
 
@@
 
-We extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-
-Let $\varphi=\sum_{n=0}^{\infty}a_n\zeta^n$, %then from identity \eqref{change-chart}
-
+We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$.
+To be more precise, we define the action on trans-monomial so that the diagram
+%%\begin{center}
+%%\begin{tikzcd}
+%%& e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \arrow[rd, "\borel_\zeta"] \\
+%%\C\llbracket \zeta \rrbracket \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \C\llbracket \zeta_\alpha \rrbracket
+%%\end{tikzcd}
+%%\end{center}
+\begin{center}
+\begin{tikzcd}
+& e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[rd, "\borel_\zeta"] & \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}
+\end{tikzcd}
+\end{center}
+commutes. Then we'll extend the definition by linearity.%then from identity \eqref{change-chart}
  % \begin{align*}
@@
   \begin{align*}
-      \borel_\zeta\laplace_{\zeta,\alpha}\varphi&=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
-      &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
-  \end{align*}
+\borel_\zeta\laplace_{\zeta,\alpha}\zeta^n &=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\\
+      &=\borel_\zeta\left[ \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
+      &=\borel_\zeta\left[e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
+      &=\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
+  \end{align*}
+ % 
   %and the right-hand-side
@@
 %In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-hence we require the following equality to hold  
-\[ \sum_{n=0}^{\infty}a_n \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\sum_{n=0}^{\infty}a_n \zeta^n\]
-
-and, comparing term by term in powers of $\zeta$ %in the second identity we get 
+hence we require %the following equality to hold  
+%\[ \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\zeta^n\]
+%and, comparing term by term in powers of $\zeta$ %in the second identity we get 
   \begin{align*}
@@
   \end{align*}
-  thus we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
+and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
+
 %\begin{itemize}
@@
 %  \end{itemize}
-
 \subsubsection{Change of translation chart}\label{transl-borel}
-
-Following Section \ref{translation}, we can recover the definition of $\borel_{\zeta_\alpha}$
-as the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $\alpha$. Explicitly, from identity \eqref{change-chart}
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi
+We'll show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}. To be more precise, we want to show that
+\[ \borel_{\zeta_\alpha} [e^{z \alpha} \varphi] = \borel_\zeta \varphi \]
+for all $\varphi \in e^{-z\alpha}\C\llbracket z^{-1} \rrbracket$, implying that the diagram
+\begin{center}
+\begin{tikzcd}
+& e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[rd, "\borel_\zeta"] \arrow[rr, "e^{\alpha z}"] & & \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[ld, "\borel_{\zeta_\alpha}"'] \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}
+\end{tikzcd}
+\end{center}
+commutes. Let $\varphi=e^{-z\alpha}\sum_{n=0}^\infty a_n z^{-n-1}$
+\begin{align*}
+    \borel_{\zeta_\alpha}\varphi&=\borel_{\zeta_\alpha}\big[e^{-z \alpha}\sum_{n=0}^\infty a_n z^{-n-1}\big]\\
+    &=\sum_{n=0}^\infty a_n \borel_{\zeta_\alpha}\big[e^{-z\alpha} z^{-n-1}\big]\\
+    &\textcolor{orange}{...}
+\end{align*}
+
+Recall that $\borel_{\zeta_\alpha}$
+is the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $\alpha$.
+Thus, we can compute the Borel transform on both side of the identity~\eqref{change-chart}.
+Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$
+  \begin{align*}
+      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\varphi
   \end{align*}
@@
      % \end{align*}
-     If we require $\borel_{\zeta_\alpha}$ to be $\C$-linear, we deduce 
+     Since $\borel_{\zeta_\alpha}$ is $\C$-linear and
      % \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
        \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
- Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
- \begin{align*}
-     \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-     z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- \end{align*}
- Furthermore, its action extends to trans-monomials: $\borel_{\zeta_\alpha}e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta_\alpha \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
-
-\subsection{The Borel transform on $1$-Gevrey series}\label{sec:formal_borel}
-%\color{gray}
-%\begin{itemize}
-%\item Action on differential equations.
-%\begin{itemize}
-%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-
-%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
+       we deduce
+       \begin{align*}
+           \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k} \frac{\zeta_\alpha^k}{k!}\\
+           &=\sum_{n=0}^{\infty}a_n(\zeta_\alpha+\alpha)^n\\
+           &=\varphi.
+       \end{align*}
+ %Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
  %\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
+    % \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
+    % z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
  %\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-So far, our discussion was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
+\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
+\subsection{Borel and Laplace transforms as algebra homomorphisms}
+So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
 These formal series are the so-called $1$-Gevrey series:
@@
 In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The inverse of $\borel\textcolor{orange}{_\zeta}$ is what we call a \textit{formal Laplace transform}.
-In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra isomoprhisms.
+The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}.
+In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhisms.
 
@@
 \begin{align*}
-\borel\textcolor{orange}{_\zeta}(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
+\borel_\zeta(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
 \end{align*}
@@
 
-\subsection{Properties of the Borel transform}\label{properties Borel transform}
+\subsubsection{Action on fractional derivatives and fractional integrals}
+For applications is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
+
+Recall that for $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
+%
+\begin{equation*}
+    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi(\zeta_\alpha+\alpha)\, d\zeta_\alpha.
+\end{equation*}}
+
+It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+We'll use the {\em Riemann-Liouville} convention.
+\begin{definition}\label{defn:frac_driv}
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+\end{definition}
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+\begin{lemma}\label{L-int-op}
+    The following identities hols true:
+    \begin{itemize}
+        \item[i)]\label{item:i} \textcolor{orange}{for some $\sigma>-1$, $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ and for all $\lambda \in (0, \infty)$
+        \[%%\label{id:L-mult}
+\laplace_\zeta (\partial^{\lambda}_{\zeta} \varphi) = (-z)^n \laplace_\zeta \varphi.
+\]}
+\item[ii)]\label{item:ii} if $\varphi \in \singexpalg{\sigma}$, for all integers $n \ge 0$
+\[%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\]
+\item[iii)]\label{item:iii} if $\varphi\in\singexpalg{\sigma}(\Omega_b)$, then $\partial_{\zeta,b}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_b)$ and 
+\[ \laplace_{\zeta, b}\,\fracderiv{-\lambda}{\zeta}{b} \varphi = z^{-\lambda} \laplace_{\zeta, b} \varphi \]
+for all $\lambda \in (0, \infty)$. 
+    \end{itemize}
+\end{lemma}
+\begin{proof}
+    The result of \emph{i)} follows from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
+Similarly, one can prove \emph{iii)}.
+\end{proof}
+\begin{lemma}\label{lem:frac-deriv-Borel}
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
+\end{lemma}
+\begin{proof}
+We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+\begin{align*}
+\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
+\end{align*}
+by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
+\begin{equation}\label{frac-diff-laplace}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\end{equation}
+for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
+\end{align*}
+Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
+The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
+This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
+\end{proof}
+We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Lemma~\ref{L-int-op}.
+\color{orange}
+\begin{lemma}
+    Let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ 
+\begin{itemize}
+\item[i)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^\lambda \tilde{\Phi}\big)=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\tilde{\Phi}.\]
+\item[ii)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^{-\lambda} \tilde{\Phi}\big)=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]
+%\item[iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
+\item[iii)] for every $n\geq 0$ \[\borel_\zeta\big(\partial_z^{n} \tilde{\Phi}\big)=(-\zeta)^n\borel_\zeta\tilde{\Phi}.\]
+\end{itemize} 
+\end{lemma}
+\begin{proof} 
+The result of $i)$ follows from Lemma~\ref{lem:frac-deriv-Borel}.
+Then to prove the result of $ii)$, notice that for $\lambda\in (0,\infty)$ \[\fracderiv{-\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\tfrac{k!}{\Gamma(k-\lambda+1)},\] hence \[\borel_\zeta (z^\lambda \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{k!}\tfrac{k!}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\fracderiv{-\lambda}{\zeta}{0}\zeta^k=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]
+
+(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
+
+(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
+
+(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
+
+\end{proof}
+%
+\color{RoyalBlue}
+Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
+\begin{align*}
+\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
+& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
+\end{align*}
+we learn that
+\begin{equation}
+    %\label{change-chart}
+    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
+\end{equation}
+%
+\subsubsection{Rescaling of translation structure}
+%
+Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
+The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
+From the calculation
+\begin{align*}
+\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+& = \mu\,\laplace_{\zeta, 0} \varphi
+\end{align*}
+we learn that
+\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
+We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
+%
+\subsubsection{Action on integral operators}\label{L-int-op}
+%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
+%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
+For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $B$.
+
+It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+We'll use the {\em Riemann-Liouville} convention.
+\begin{definition}\label{defn:frac_driv}
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+\end{definition}
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+
+%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
+
+%\color{Tan}
+%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
+%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
+%for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+%\begin{equation}%%\label{id:L-mult}
+%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+%\end{equation}
+%for all integers $n \ge 0$.
+
+Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
+\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
+for all $\lambda \in (0, \infty)$.
+This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+\begin{equation}%%\label{id:L-mult}
+\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
+\end{equation}
+for all integers $n \ge 0$.
+Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
+\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
+for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
+%
+\begin{equation}
+    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
+\end{equation}\color{black}
+%
+\color{RoyalBlue}Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
+\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
+for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
+%
+\begin{equation}
+    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
+\end{equation}\color{RoyalBlue}
+%
+Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
+However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
+[Isn't this a special case of the $\laplace_{\zeta, \alpha}$ statement?]\color{black}
+
+%We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
+
+%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
+In fact, as we’ll see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
+
+%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
+
+%\color{gray}
+%\begin{itemize}
+%\item Action on differential equations.
+%\begin{itemize}
+%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
+%\end{itemize}
+%\end{itemize}
+%\color{black}
+
+%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
+%\begin{align*}
+%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
+%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
+%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
+%\end{align*}
+%In general, by linearity,
+%\begin{align*}
+%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
+%\end{align*}
+%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
+
+%\subsection{Properties of the Borel transform}\label{properties Borel transform}
 We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
@@
 \item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
-\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$
+\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$ \textcolor{orange}{[put analogue of this in Laplace section]}
 \end{itemize}
 
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
 \begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
+
+We are going to prove properties (i)--(vi).
+
+(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
+
+(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
+
+(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
+
+(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
+
 \end{proof}
 
-\begin{proof}
-
-We are going to prove properties (i)--(vi).
-
-(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
-
-\end{proof}
-
-\subsection{The convolution product}\label{convolution}
-
-The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
+\subsubsection{The convolution product}\label{convolution}
+%
+The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel_\zeta$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
 The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
@@
 \[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-
 In addition, it follows that the convolution product $\ast$ can be explicitly characterized as 
-
 \begin{equation}
@@
 \end{equation}
-
 the proof is a simple computation, and we refer to  \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}.
 \begin{lemma}
-    Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\tau} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\tau-1} \rbrace$, with inverse given by the formal Laplace transform.
+    Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an algebra isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\tau} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\tau-1} \rbrace$, with inverse given by the formal Laplace transform.
 \end{lemma}
@@
 \end{align*}  
-
 and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
@@
 \end{proof}
-
+In addition, the convolution product gives an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$: let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
+\begin{verify}
+    \begin{align*}
+        | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
+        &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
+        &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+        &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+    \end{align*}
+\end{verify}
+We deduce that also the Laplace transform is an algebra isomorphisms from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
+\begin{lemma}
+    Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
+Then the Laplace transform $\laplace_\zeta^\theta$ is an algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
+\end{lemma}
+\begin{proof}
+    Then we can prove $\delta$ is a unit: 
+    \begin{align*}
+    \delta\ast\tilde{\phi}&=\borel_\zeta(1)\ast\tilde{\phi}=\borel_\zeta(1\cdot ?)
+    \end{align*}
+    we'll show $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$ and that $\laplace_\zeta^\theta\big(\tilde{\phi}\ast\tilde{\psi}\big)=\laplace_\zeta^\theta\big(\tilde{\phi}\big)\laplace_\zeta^\theta\big(\tilde{\psi}\big)$
+\end{proof}
+\begin{remark}
+    it is possible to define an inverse Laplace transform, so that $\laplace_\zeta^0$ becomes an algebra isomorphisms.
+However we'll refer to \textcolor{magenta}{[standard reference]} for details.
+\textcolor{magenta}{[see also section on Regularity for Laplace]}
+\end{remark}
 The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_\alpha B$ and let $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$
-
 \[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=\series{\psi}\ast \series{\phi}=\int_{0}^{\zeta_\alpha}\series{\psi}(\zeta_\alpha-\zeta')\series{\phi}(\zeta')d\zeta'\]
-
 Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_0 B$, we define  \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}\]
 then $\ast_\alpha$ can be explicitly written as 
-
 \begin{equation}
@@
 thus $\delta_\alpha\ast_\alpha\phi=\phi\ast_\alpha\delta_\alpha=\phi$. 
-
 \begin{remark}
@@
 \end{remark}
-
+%
 \begin{remark}
@@
 hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\phi.\]
-
 %However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
@@
 hence, recalling $\zeta=\zeta_\alpha+\alpha$ \[\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}\]
-
 Finally, recall that for every $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
@@
 \end{tikzpicture}
-\caption{The domain $\Omega_j$}\label{Fig:domain}
+\caption{The domain $\Omega_\alpha$}\label{Fig:domain}
 \end{figure}
 \subsubsection{Main results}
+\color{Maroon}
+\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in \textcolor{magenta}{[the appropriate affine subspace of]} the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}.
+That solution is Borel regular.
+\end{theorem}
+\begin{proof}
+Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}.
+Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}.
+Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.
+
+By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
+The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
+It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
+\end{proof}
+\color{black}
+
 %As a consequence of Theorem 4 in {\tt reg-volterra} we get 
@@
 Step $(b)$ clearly follows from \cite[Theorem 4]{reg-sing-volterra} and step $(a)$.
-In fact, $\Tilde{\psi}_\alpha$ and ${\psi}_\alpha$ are both solutions of $\hat{P}_\alpha\psi=0$ and by uniqueness they are proportional in a neighbourhood of $\alpha_j$.
+In fact, $\Tilde{\psi}_\alpha$ and ${\psi}_\alpha$ are both solutions of $\hat{P}_\alpha\psi=0$ and \textcolor{magenta}{by uniqueness}\footnote{\color{magenta} One possibility: show that a solution of a formal Volterra equation of the type we have is determined by the $z^{-\tau_\alpha}$ asymptotics somehow?
+Not enough in general.
+Another possibility: [\ldots]} they are proportional in a neighbourhood of $\alpha_j$.
 Then, we can Laplace transform ${\psi}_\alpha$ along a ray $\Gamma_{\alpha}^\theta$ in $\Omega_\alpha$.
@@
 %\end{proof}
-
+\color{violet}
+\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
+\color{black}
 \subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
@@
 This lets us analytically continue $\int_{\Lambda_\alpha^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
-Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$.
+Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
 \begin{figure}
@@
 where $V_j = \laplace_{\zeta_j, 0} v_\alpha$ and $\zeta = \alpha_j + \zeta_j$.
-We can see from Section~\ref{reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
+We can see from Section~\ref{sec:reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
 \[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} z^{-\tau_j} W_j, \]
@@
 The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_j\in\singexpalg{1/2}(\Omega_j)$.
-\color{DarkTurquoise}
-\begin{quote}
+\begin{verify}
 We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
@@
 In this case, $\tau = \tfrac{1}{2}$.
-\end{quote}
-\color{black}
+\end{verify}
 
@@
 where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
@@
 %where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-As we've seen in Section \ref{reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
+As we've seen in Section~\ref{sec:reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
 This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.

### 2024-01-19 to-do.tex

@@
 \maketitle
-\section{Intro}
+\section{Borel regularity paper}
+\subsection{Intro}
 \begin{itemize}
@@
 \end{itemize}
-\section{The Laplace and Borel transforms}
+\subsection{The Laplace and Borel transforms}
 \begin{itemize}
@@
 \end{itemize}
-\section{Proof of main results}
+\subsection{Proof of main results}
 \begin{itemize}
@@
 \end{itemize}
-\section{Examples}
+\subsection{Laplace and Borel transforms}
 \begin{itemize}
-\item Revise Borel regularity argument for Airy-Lucas
+\item Harmonize layout of Laplace and Borel properties.
+\begin{itemize}
+  \item Maybe split properties into two parts.
+  \item Geometric properties: change of chart, change of fiber
+  \item Laplace and Borel transforms as algebra homomorphisms (``The Laplace/Borel transform as an algebra homomorphism'')
+\end{itemize}
+\item \textbf{(Aaron)} Understand why \texttt{lem:frac-deriv-Borel} works without boundary terms, and explain this in text.
+\item \textbf{(Aaron)} Clarify what the Borel transforms with respect to different charts are doing.
+\item Talk about higher Laplace transform at singular point? (Low-priority. Maybe just mention in a footnote.)
+\end{itemize}
+\subsection{Examples}
+\begin{itemize}
+\item Revise Borel regularity argument for Airy-Lucas.
+Instead of assuming that the Poincar\'{e} solutions are Borel-summable, follow the general argument more closely, starting from the analytic position corner and using the asymptotics implied by the regularity and decay properties.
 \item Rewrite thimble projection reasoning for Airy-Lucas functions
@@
 \end{itemize}
-\section{Figures}
-For some reason all figures move at the end of the document. Moreover I'd prefer to add the picture of the Borel plane as translation surface as tikzpicture and not as pdf.
+\subsection{Figures}
+\begin{itemize}
+\item For some reason all figures move at the end of the document.
+\item Add the picture of the Borel plane as translation surface as tikzpicture and not as pdf.
+\end{itemize}
+\section{Part-time projects}
+\begin{itemize}
+\item Try to come up with a concrete goal and plan for a short project that we can do February--June
+\begin{itemize}
+\item \textbf{(Veronica)} Look into the Braaksma generalization project
+\item \textbf{(Aaron)} Look into the algebraic hypergeometric project
+\item \textbf{(Both)} Look into Varchenko's project
+\end{itemize}
+\item Look into projects that Veronica could continue with other collaborators
+\begin{itemize}
+\item Connection to two-variable exact WKB formalism (with Nikita)
+\end{itemize}
+\end{itemize}
 \end{document}

### 2024-01-21 exp-resurgence.tex
Rewrite geometry of Borel and Laplace

@@
 is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
+\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
 over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
@@
 \textcolor{RoyalBlue}{The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).}
+
+\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances. See Erdelyi's {\em Asymptotic Expansions}, \S 1.6]}
+
 \begin{defn}\label{def:unif-gevrey-asymp}
@@
 %
-The translation structure also gives us an isomorphism $z \maps T^*B_b \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*B_b^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}.
+The translation structure also gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}.
 At an ordinary point, we can define $z$ simply as the map
 \begin{align*}
-z \maps T^*B_b & \to \C \\
+z \maps T^*_bB & \to \C \\
 \lambda\big|_b & \mapsto 1.
@@
 To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
-Recall that $T^*B_b = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
-Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*B_b^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
+Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
+Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
 When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
@@
 \begin{align*}
-w_b \maps T^*B_b & \to \C \\
+w_b \maps T^*_bB & \to \C \\
 \omega_b + \van^2 & \mapsto 1
@@
 \begin{tikzcd}
-T^*B_b^{\otimes n} \arrow[r,"z"] & \C \\
-T^*B_b \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
+T^*_bB^{\otimes n} \arrow[r,"z"] & \C \\
+T^*_bB \arrow[u,"\blankbox^n"] \arrow[r,"w"'] & \C \arrow[u,"\blankbox^n"']
 \end{tikzcd}
@@
 Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
-The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*B_b$ along the $n$th-power map.
+The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*_bB$ along the $n$th-power map.
 This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}.
@@
     \label{change-chart}
-    \laplace_{\zeta_b, 0} \varphi = e^{b z} \laplace_{\zeta, b} \varphi.
+    e^{-b z} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
 \end{equation}
@@
 \begin{tikzcd}
- \mathcal{O}(H) \arrow[rr, "e^{bz}"]  &  & e^{zb}\,\mathcal{O}(H)\\
+ \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{zb}\,\mathcal{O}_{T^*B}(H)\\
 & \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
@@
 \end{center}
-commutes, and $H$ is the right half plane $\Re z>0$.
+commutes, where $H$ on the left-hand-side is the right half plane $\Re z>0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
 \end{lemma}
@@
 \end{align*}
-We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*B_{\zeta = 0}$.
+We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*_{\zeta = 0}B$.
 
@@
 
-Summarizing, we can describe the geometry of Borel and Laplace transforms by drawing the following diagram
-\begin{center}
-\begin{tikzcd}[every arrow/.append style={shift left}]
- \text{functions on } T^*_{\zeta=0}B \arrow{d}{\borel_{\zeta}} & & \text{functions on } T^*_{\zeta=b}B \arrow{d}{\borel_{\zeta_b}}\arrow[ll,swap,"\mathsf{T}_b^*"] \\ 
- \text{functions of } \zeta \arrow{u}{\laplace_{\zeta, 0}}\arrow[rr,"\mathsf{T}_b"'] & & \text{functions of } \zeta_b \arrow{u}{\laplace_{\zeta_b, 0}}
-\end{tikzcd}
-\end{center}
-where $\mathsf{T}_b$ denotes the map of change of variables $\mathsf{T}_b(\zeta)=\zeta_b$.
-\textcolor{orange}{I don't like much the word function and the map $\mathsf{T}_b$, but we could change later.}
-
-%It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha,0}$, as discussed in Section~\ref{transl-borel}.
-
-%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
-%%\begin{align*}
-%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
+%Summarizing, we can describe the geometry of Borel and Laplace transforms by drawing the following diagram
+%\begin{center}
+%\begin{tikzcd}[every arrow/.append style={shift left}]
+ %\text{functions on } T^*_{\zeta=0}B \arrow{d}{\borel_{\zeta}} & & \text{functions on } T^*_{\zeta=b}B \arrow{d}{\borel_{\zeta_b}}\arrow[ll,swap,"\mathsf{T}_b^*"] \\ 
+ %\text{functions of } \zeta \arrow{u}{\laplace_{\zeta, 0}}\arrow[rr,"\mathsf{T}_b"'] & & \text{functions of } \zeta_b \arrow{u}{\laplace_{\zeta_b, 0}}
+%\end{tikzcd}
+%\end{center}
+%where $\mathsf{T}_b$ denotes the translation map $\mathsf{T}_b(\zeta)=\zeta_b$. \textcolor{orange}{I don't like much the word function and the map $\mathsf{T}_b$, but we could change later.}
+
+%%It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha,0}$, as discussed in Section~\ref{transl-borel}.
+
+%%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
+%%%\begin{align*}
+%%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
 %%z^{-n-1} & \mapsto \frac{\zeta_\alpha^n}{n!}.
@@
 
-%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.
+%%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.
 
@@
 
-It is natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries.
-Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-
-We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$.
+It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we'll achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
+\begin{definition}
+    The action of $\borel_\zeta$ on trans-monomials is the formal inverse of $\laplace_{\zeta,\alpha}$
+    \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha}z^{-n-1}\big]=e^{-z\alpha}z^{-n-1}\]
+    %\begin{center}
+%\begin{tikzcd}[every arrow/.append style={shift left}]
+ %e^{-z\alpha}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta,\alpha}}
+%\end{tikzcd}
+%\end{center}
+    and it extends by linearity to transseries. 
+\end{definition}
+In particular, from identity~\eqref{change-chart} we deduce 
+\begin{align*}
+    e^{-z\alpha}z^{-n-1}&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]\\
+     z^{-n-1}&=\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]
+\end{align*}
+and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
+%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
+
+%We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$.
 To be more precise, we define the action on trans-monomial so that the diagram
@@
 %%\end{center}
+%\begin{lemma}
+    \[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
+In other words, the following diagram 
+    \begin{center}
+\begin{tikzcd}[every arrow/.append style={shift left}]
+\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"']\arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"]    \\
+& & \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_\alpha"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}
+\end{tikzcd}
+\end{center}
+commutes, where $\mathsf{T}_\alpha$ denote the traslation by $\alpha$. Notice that the functions on the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 
+%\end{lemma} 
+\subsubsection{Change of translation chart}\label{transl-borel}
+We'll show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}.
+To be more precise, we'll show that the diagram
 \begin{center}
 \begin{tikzcd}
-& e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[rd, "\borel_\zeta"] & \\
-\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}
+e^{-zb}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}  \arrow[r,"e^{zb}"]  & \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}\arrow[d, "\borel_{\zeta_b}"] \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\}\arrow[u,"\laplace_{\zeta,b}"]\arrow[r,"\text{change chart}"'] &  \{1, \zeta_b, \zeta_b^2, \zeta_b^3, \ldots\}  
 \end{tikzcd}
 \end{center}
-commutes. Then we'll extend the definition by linearity.%then from identity \eqref{change-chart}
- % \begin{align*}
-  %    \borel_\zeta\laplace_{\zeta,\alpha}\varphi=\borel_\zeta\left[e^{-\alpha z }\laplace_{\zeta_\alpha,0}\varphi\right]
-  %\end{align*}
-%We compute the left-hand-side
-  \begin{align*}
-\borel_\zeta\laplace_{\zeta,\alpha}\zeta^n &=\borel_\zeta\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\\
-      &=\borel_\zeta\left[ \int_{\alpha}^{\infty}e^{-z\zeta} \zeta^nd\zeta\right]\\
-      &=\borel_\zeta\left[e^{-z\alpha}\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})
-  \end{align*}
- % 
-  %and the right-hand-side
-  %\begin{align*}
-   %   \borel_\zeta\left[e^{-\alpha z
-    %  }\laplace_{\zeta_\alpha}\varphi\right]&=\borel_\zeta\left[e^{-\alpha z
-     % }\int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta_\alpha z} \varphi d\zeta\right]\\
-     % &=\borel_\zeta\left[
-     % \int_{\Gamma_{\zeta_\alpha,0}} e^{-\zeta z} \varphi d\zeta\right]\\
-     % &=\borel_\zeta\left[ \sum_{n=0}^{\infty}a_n\int_{0}^{\infty} e^{-\zeta z} \zeta^n d\zeta\right]\\
-    %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-     % &= \sum_{n=0}^{\infty}a_n \zeta^n
-  %\end{align*}
-%In particular, we get \[\borel_{\zeta}\laplace_{\zeta,\alpha}\varphi=\varphi\]
-hence we require %the following equality to hold  
-%\[ \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})=\zeta^n\]
-%and, comparing term by term in powers of $\zeta$ %in the second identity we get 
-  \begin{align*}
-      \sum_{k=0}^n \frac{n!}{(n-k)!}\alpha^{n-k}\borel_\zeta(e^{-z\alpha}z^{-k-1})&=\zeta^n\\
-      \sum_{k=0}^n {n\choose k} \alpha^{n-k} \borel_\zeta(e^{-z\alpha} k! z^{-k-1})&=\sum_{k=0}^n {n\choose k} \alpha^{n-k}(\zeta-\alpha)^k
-  \end{align*}
-and we deduce \[\borel_\zeta(e^{-z\alpha}z^{-k-1})=\frac{1}{k!}(\zeta-\alpha)^k.\]
-
-%\begin{itemize}
- %   \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-%  \end{itemize}
-\subsubsection{Change of translation chart}\label{transl-borel}
-We'll show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}. To be more precise, we want to show that
-\[ \borel_{\zeta_\alpha} [e^{z \alpha} \varphi] = \borel_\zeta \varphi \]
-for all $\varphi \in e^{-z\alpha}\C\llbracket z^{-1} \rrbracket$, implying that the diagram
-\begin{center}
-\begin{tikzcd}
-& e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[rd, "\borel_\zeta"] \arrow[rr, "e^{\alpha z}"] & & \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[ld, "\borel_{\zeta_\alpha}"'] \\
-\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}
-\end{tikzcd}
-\end{center}
-commutes. Let $\varphi=e^{-z\alpha}\sum_{n=0}^\infty a_n z^{-n-1}$
-\begin{align*}
-    \borel_{\zeta_\alpha}\varphi&=\borel_{\zeta_\alpha}\big[e^{-z \alpha}\sum_{n=0}^\infty a_n z^{-n-1}\big]\\
-    &=\sum_{n=0}^\infty a_n \borel_{\zeta_\alpha}\big[e^{-z\alpha} z^{-n-1}\big]\\
-    &\textcolor{orange}{...}
-\end{align*}
-
-Recall that $\borel_{\zeta_\alpha}$
-is the formal inverse of $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $\alpha$.
-Thus, we can compute the Borel transform on both side of the identity~\eqref{change-chart}.
-Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\varphi
-  \end{align*}
-  now the left-hand-side reads
-  \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\borel_{\zeta_\alpha}\left[e^{z\alpha} \int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\varphi d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_n\int_{\Gamma_{\zeta,\alpha}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-      &=\borel_{\zeta_\alpha}\left[e^{z\alpha} \sum_{n=0}^{\infty}a_ne^{-z\alpha}\sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}z^{-k-1}\right]\\
-      &=\borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k}  z^{-k-1}\right]
-  \end{align*}
-  %the RHS is 
-  %\begin{align*}
-   %   \borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\varphi&=\borel_{\zeta_\alpha}\left[\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta_\alpha}\varphi d\zeta\right]\\
-    %  &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\varphi d\zeta\right]\\
-     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}\int_{\Gamma_{\zeta_\alpha,0}}e^{-z\zeta}\zeta^n d\zeta\right]\\
-     % &=\borel_{\zeta_\alpha}\left[e^{z\alpha}\sum_{n=0}^{\infty}a_nz^{-n-1}n!\right]\\
-     % &= \borel_{\zeta_\alpha}\left[\sum_{n=0}^{\infty}a_n n!e^{z\alpha}z^{-n-1}\right]
-     % \end{align*}
-     Since $\borel_{\zeta_\alpha}$ is $\C$-linear and
-     % \[\borel_{\zeta_\alpha}\left[e^{z\alpha}z^{-n-1}\right]=\frac{\zeta^n}{n!}=\frac{(\zeta_\alpha+\alpha)^n}{n!}\]
-       \[\borel_{\zeta_\alpha}\left[z^{-k-1}\right]=\frac{\zeta_\alpha^k}{k!}\]
-       we deduce
-       \begin{align*}
-           \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\varphi\right]&=\sum_{n=0}^{\infty}a_n \sum_{k=0}^{n}\frac{n!}{(n-k)!}\alpha^{n-k} \frac{\zeta_\alpha^k}{k!}\\
-           &=\sum_{n=0}^{\infty}a_n(\zeta_\alpha+\alpha)^n\\
-           &=\varphi.
-       \end{align*}
+commutes, where the functions of $z$ are functions on the fiber $T^*_{\zeta=b}B$. 
+\begin{proof}
+We want to show that 
+\[\borel_{\zeta_b}\left[e^{zb} \laplace_{\zeta,b}\big[\zeta^n\big]\right]=\zeta^n.\]
+Recall that $\borel_{\zeta_b}$
+is the formal inverse of $\laplace_{\zeta_b,0}$ on the cotangent fibre over $b$. Thus, taking the Borel transform on both side of the identity~\eqref{change-chart} we find
+  \begin{align*}
+      \borel_{\zeta_b}\left[e^{zb} \laplace_{\zeta,b}\big[\zeta^n\big]\right]&=\borel_{\zeta_b}\laplace_{\zeta_b,0}\big[\zeta^n\big]\\
+      &=\borel_{\zeta_b}\laplace_{\zeta_b,0}\left[\sum_{k=0}^n{n\choose k}\zeta_b^k b^{n-k}\right]\\
+      &=\sum_{k=0}^n{n\choose k} b^{n-k}\borel_{\zeta_b}\laplace_{\zeta_b,0}\big[\zeta_b^k \big]\\
+      &=\sum_{k=0}^n{n\choose k} b^{n-k}\zeta_b^k\\
+      &=\zeta^n.
+  \end{align*}
+\end{proof}
  %Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
@@
  %\end{align*}
-\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
+%\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
 \subsection{Borel and Laplace transforms as algebra homomorphisms}
@@
 Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel\textcolor{orange}{_\zeta}\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
+Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
 \end{lemma}
@@
 of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
+
+To show that $\Psi_\alpha$ is Borel regular,
 \end{proof}

### 2024-01-25 exp-resurgence.tex
Revise Section 3

@@
 
-\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances. See Erdelyi's {\em Asymptotic Expansions}, \S 1.6]}
+\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances.
+See Erdelyi's {\em Asymptotic Expansions}, \S 1.6.
+For basic facts about uniform asymptoticity, see \S 5.7.2 of Mitschi and Sauzin.
+Theorem~5.20 and its rephrasing say that the Laplace transform of a function is uniformly asymptotic to the formal Laplace transform of the function's Taylor series.]}
 
@@
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-Let $b\in B$ be an ordinary point, and let $\zeta_b$ be a coordinate on $B$ so that $\zeta = b + \zeta_b$, then the Laplace transform $\laplace_{\zeta_b,0}$ is defined on $T^*_{b}B$ and it's compatible with $\laplace_{\zeta,b}$.
+Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$.
+Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.
 \begin{lemma}\label{translation}
@@
     \label{change-chart}
-    e^{-b z} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
+    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
 \end{equation}
@@
 \begin{tikzcd}
- \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{zb}\,\mathcal{O}_{T^*B}(H)\\
+ \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
 & \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
@@
 \end{center}
-commutes, where $H$ on the left-hand-side is the right half plane $\Re z>0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
+commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
 \end{lemma}
 \begin{proof}
-    The result follws from a simple calculation:
+With a change of variable in the integral that defines the Laplace transform, we see that
 \begin{align*}
@@
 \begin{tikzcd}[every arrow/.append style={shift left}]
- \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow{u}{\laplace_{\zeta, 0}}
+ \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \left\{1, \zeta, \frac{1}{2!} \zeta^2, \frac{1}{3!} \zeta^3, \ldots\right\} \arrow{u}{\laplace_{\zeta, 0}}
 \end{tikzcd}
@@
 \end{align*}
-
-\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
+\begin{remark}
+The definition of the Borel transform can be easily extended to fractional power of $z$: indeed notice that   
+\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
+for every $\sigma\in\R\setminus\Z_{\leq 0}$. Thus 
+\begin{align*}
+\borel_\zeta(z^{-\sigma-1})\defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)} 
+\end{align*}
+and then extended by linearity to $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$. 
+\end{remark}
+%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
 
@@
 \begin{tikzcd}[every arrow/.append style={shift left}]
- \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \zeta_b^2, \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
+ \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \frac{1}{2!} \zeta_b^2, \frac{1}{3!} \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
 \end{tikzcd}
@@
 & & \\
-\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_\alpha"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}
 \end{tikzcd}
 \end{center}
-commutes, where $\mathsf{T}_\alpha$ denote the traslation by $\alpha$. Notice that the functions on the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 
+commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that the functions of the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 
 %\end{lemma} 
@@
 %\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
+\subsubsection{Action on translations in the frequency domain}
+Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can deduce how $\borel_\zeta$ acts on translations in the frequency domain, namely we can show that for $\varphi=\sum_{n=0}^\infty a_n z^{-n-1}$
+\[\borel_\zeta \mathsf{T}_{-c}^* \varphi=e^{-c\zeta }\borel_\zeta\varphi.\]
+Indeed, the following diagram
+\begin{center}
+\begin{tikzcd}[every arrow/.append style={shift left}]
+\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{dd}{\borel_\zeta}\arrow[rr,"\mathsf{T}_{-c}^*"]& &  \{(z+c)^{-1}, (z+c)^{-2}, (z+c)^{-3}, (z+c)^{-4}, \ldots \} \arrow{dd}{\borel_\zeta}    \\
+& & \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "e^{-c\zeta}"'] \arrow{uu}{\laplace_{\zeta,0}}     &  & e^{-c\zeta}\{1, \zeta, \zeta^2, \zeta^3, \ldots\}\arrow{uu}{\laplace_{\zeta,0}}
+\end{tikzcd}
+\end{center}
+commutes, where the functions of the variable $z$ belong to the fiber $T^*_{\zeta=0}B$.
+If $z$ is a function on the fiber over $\zeta=b$, then it's enough to replace $\borel_\zeta$ with $\borel_{\zeta_b}$ and to use  $\laplace_{\zeta_b,0}$ as the inverse.
+%\color{orange}
+%\subsubsection{Action on power series with fractional exponents}
+%\color{black}
 \subsection{Borel and Laplace transforms as algebra homomorphisms}
-So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at the origin in $\C_{\zeta}$.
-These formal series are the so-called $1$-Gevrey series:
-\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is $1$-Gevrey if there exists $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
-there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obtain germs of holomorphic function for higher Gevrey series.
-}
-
+The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-algebra homomorphisms between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.
+
+In fact, since $\borel_\zeta$ is deifned as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by linearity.
+As a result, we find that the \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\]
+is a $\C$-algebra isomorphism whose inverse is the formal Laplace transform.
+
+However, as we discussed in Section~\ref{sec:reg-decay}, the Laplace transform $\laplace_{\zeta,0}$ is naturally defined on the space of integrable, holomorphic functions, namely $\singexpalg{\sigma}(\Omega)\subset \zeta^{\sigma}\C\lbrace\zeta\rbrace$ for $\sigma>-1$, hence we might expect it extends to a $\C$-algebra homomorphism from $\singexpalg{\sigma}(\Omega)$ to $\mathcal{O}(H)$.
+Indeed, that's the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$.
+We'll discuss it in Section~\ref{convolution}.
+
+Consequently, also at the formal level we can restric to a subalgebra of $\C\llbracket z^{-1}\rrbracket$ whose image under $\borel_\zeta$ lies in $\C\lbrace\zeta\rbrace$.
+This subalgebra is the so called space of $1$-Gevrey series $\C\llbracket z^{-1}\rrbracket_1\subset\C\llbracket z^{-1}\rrbracket$ and $\borel_\zeta\colon \C\llbracket z^{-1}\rrbracket_1\to\C\delta+\C\lbrace\zeta\rbrace$ is a $\C$-algebra homomorphism (see Section~\ref{sec:Borel-gevrey}).
+
+Finally in Section~\ref{sec:frac-diff-laplace}, we'll consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives both in the frequency and the position domain, and fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
+%We'll see that the Borel transform and formal Laplace transform commutes with the action of derivatives and moltiplication.
+%from the space of Puiseux series in the frequency domain to  $\C\llbracket z^{-1}\rrbracket$
+
+We end this paragraph introducing the notation we'll be using in the following. 
 \begin{notation*}
@@
 Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
-\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane.
-As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel\textcolor{orange}{_\zeta} \tilde{\Phi}=:\tilde{\phi}$;
+\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel_\zeta \tilde{\Phi}=:\tilde{\phi}$; 
 \item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
@@
 \end{notation*}  
-
+%between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with th
+%In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
+\textcolor{orange}{[Why not say this more generally, with $\C\llbracket z^{-1} \rrbracket$ and $\C\llbracket\zeta\rrbracket$?]} The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}.
+\textcolor{orange}{[This seems a little weird to me, since we define the Borel transform as a formal inverse to the Laplace transform.
+Wouldn't it be easier to define the formal Laplace transform as a formal version of the Laplace transform, and then define the Borel transform as its inverse?]} In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhism.
+
+\subsubsection{The convolution product}\label{convolution}
+%
+Let $\series{\phi},\series{\psi}\in\C\lbrace\zeta\rbrace$ be two convergent formal series in a neighbourhood of $\zeta=0$, and let $\hat{\phi}$ and $\hat{\psi}$ be respectively their sum in a common region of convergence, say $|\zeta|<R$.
+Then the convolution product $\hat{\phi}\ast\hat{\phi}$ is defined as
+\begin{equation}\label{eq:convolution}
+    \hat{\phi}\ast\hat{\psi}:=\int_0^{\zeta}\hat{\phi}(\zeta-\zeta')\hat{\psi}(\zeta')\, d\zeta'
+\end{equation}
+and it admits a convergent power series expansion for $|\zeta|<R$ (see \cite[Lemma 5.14]{diverg-resurg-i}).
+
+In addition, we can relax the assumption on $\series{\phi},\series{\psi}$ by allowing integrable singularties at $\zeta=0$, namely  $\series{\phi}\in\zeta^{\sigma}\C\lbrace\zeta\rbrace$ and $\series{\psi}\in\zeta^{\tau}\C\lbrace\zeta\rbrace$ with $\sigma,\tau>-1$.
+In this case, $\hat{\phi}$ and $\hat{\psi}$ will be respectively the sum of the series $\series{\phi}$ and $\series{\psi}$ in an open domain $\Omega\cap \lbrace |\zeta|<R\rbrace$ (that may not contain $\zeta=0$).
+In fact, this leads to the definition of the convolution product for functions in $\singexp{\sigma}{\Lambda}(\Omega)$:
+\begin{lemma}
+    Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega)$ for $\sigma>-1$, then $\phi\ast\psi\in\singexp{\sigma}{\Lambda}(\Omega)$.
+\end{lemma}
+\begin{verify}
+\begin{proof}
+    \begin{align*}
+        | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
+        &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
+        &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+        &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+    \end{align*}
+\end{proof}
+\end{verify}
+In addition, we can show that $\laplace_{\zeta,0}$ is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on the right-half-plane $\Re z>0$. 
+\begin{prop}
+    Let $\sigma>-1$ and $\Lambda>0$.
+The Laplace transform $\laplace_{\zeta,0}$ is $\C$-algebra homomorphism from $(\singexp{\sigma}{\Lambda}(\Omega),\ast)$ to to the space of holomorphic functions on the right-half-plane $\Re z>0$ with the standard multiplication of functions.
+\end{prop}
+\begin{proof}
+It is enough to show that
+\[\laplace_{\zeta,0}\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}\big[{\phi}\big]\laplace_{\zeta,0}\big[{\psi}\big],\]
+which indeed follows from simple integral computations (see for instance ~\cite[Theorem 2.39]{laplace-tfm}). 
+\end{proof}
+\begin{remark}
+    it is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms.
+However we'll refer to \textcolor{magenta}{[standard reference]} for details.
+\textcolor{magenta}{[see also section on Regularity for Laplace]}
+\end{remark}
+%The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus in order to prove that $\borel_\zeta$ is an algebra homomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
+
+%Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
+%\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+%In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
+%\[
+ %   \series{\psi}\ast\series{\phi}=\int_0^{\zeta}d\zeta' \series{\psi}(\zeta-\zeta')\series{\phi}(\zeta').
+%\]
+%\begin{lemma}
+%The convolution product induces an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$.
+%\end{lemma}
+%\begin{proof}
+%    Let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
+%\begin{verify}
+ %   \begin{align*}
+  %      | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
+   %     &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
+    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+    %\end{align*}
+%\end{verify}
+%\end{proof}
+%We deduce that also the Laplace transform is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
+%\begin{prop}
+ %   Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
+Then the Laplace transform $\laplace_{\zeta,0}^\theta$ is $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
+%\end{prop}
+%\begin{proof}
+%First of all, from the properties of $\laplace_{\zeta,0}^\theta$ we know that if $\phi, \psi\in\singexp{\sigma}{\Lambda}(\Omega)$, then
+%\[\laplace_{\zeta,0}^\theta\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}^\theta\big[{\phi}\big]\laplace_{\zeta,0}^\theta\big[{\psi}\big],\]
+%see for instance \cite[Theorem 2.39]{laplace-tfm}.
+Then we should prove that $\delta$ is a unit: from its definition and the fact that $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we deduce that
+ %   \[
+%\laplace_{\zeta,0}^\theta\big[\delta\big]:=\laplace_{\zeta,0}^\theta\big[\borel_\zeta(1)\big]=1.
+ %   \]
+%Thus, $\delta$ behaves as a Dirac delta distribution acting on $\singexpalg{\sigma}(\Omega)$. Then, if ${\phi}\in\singexp{\sigma}{\Lambda}(\Omega)$
+  %   \begin{align*}
+%\big[\delta\ast\phi\big](p)&=\int_0^{\zeta(p)} \delta(\zeta(p)-\zeta)\phi(\zeta) \, d\zeta=\phi(p)
+ %   \end{align*}
+%\end{proof}
+\subsubsection{Borel transforms on $1$-Gevrey series}\label{sec:Borel-gevrey}
+So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.
+These formal series are the so-called $1$-Gevrey series:
+\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
+is $1$-Gevrey if there exists $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
+there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
+The Borel transform can be generalized in order to obtain germs of holomorphic function for higher Gevrey series.
+}
 \begin{lemma}
@@
 \end{lemma}
-
-In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}.
-In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhisms.
-
-\subsubsection{Action on power series with fractional exponents}
-The definition of the Borel transform can be easily extended to fractional power of $z$, replacing the factorial with the Gamma function: 
-\begin{align*}
-\borel_\zeta(z^{-\alpha})\defeq \frac{\zeta^{\alpha-1}}{\Gamma(\alpha)} & \qquad \text{ if } \alpha\in\R\setminus\Z_{\leq 0}
-\end{align*}
-and then extending by linearity.
-
-\subsubsection{Action on fractional derivatives and fractional integrals}
-For applications is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
-
-Recall that for $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$: 
+Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (assuming they are series of $z$ on the fiber over $\zeta=0$), then following \cite[Definition 5.12]{diverg-resurg-i}, the convolution product $*$ of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
+\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+Furthermore, since $\tilde{\phi}$ and $\tilde{\psi}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is $\hat{\psi}\ast\hat{\phi}$ (see the discussion in Section~\ref{convolution}).
+%It's not accidentely that we use the same symbol $*$ that denotes the convolution product to denote the product of two convergent series; indeed, as proved in , %the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
+%\[
+ %   \hat{\psi}\ast\hat{\phi}=\int_0^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta'),
+%\]
+%and we refer to \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i} for a proof. 
+%\textcolor{orange}{check Lemma 5.14}{where $\hat{\phi}$ and $\hat{\psi}$ are the sum of $\series{\phi}$ and $\series{\psi}$, respectively. }
+%\begin{prop}
+ %   Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is a $\C$-algebra homomorphism from $1$-Gevrey formal power series $z^{-\tau} \C\llbracket z^{-1} \rrbracket$ to the germs of holomorphic functions $\zeta^{\tau-1} \C\{ z^{-1} \}$.
+%\end{prop}
+%\begin{proof}
+ %   Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ %with $|a_n|\leq A^n n!$ and $A>0$ then  
+%\begin{align*}
+%\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\int_0^\zeta\sum_{n\geq 0}\frac{a_{n+1}}{n!}(\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
+%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\sum_{n\geq 0} \frac{a_{n+1}}{n!} \int_0^\zeta (\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
+%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1} \frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
+%\end{align*}  
+%where in the third step we use that the Borel transform of $\tilde{\Phi}$ is convergent in a neighbourhood of $\zeta=0$.
+and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
+%which grows as $n(n+1)^{-\tau} A^{n+1}$.
+%\begin{verify}
+ %   we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
+%\end{verify}
+%\end{proof}
+
+%
+\subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
+As we'll see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
+\begin{defn}
+    Let $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, b}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, b} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =b}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
+where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_b,0}^{-\lambda}$: 
 %
 \begin{equation*}
-    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi(\zeta_\alpha+\alpha)\, d\zeta_\alpha.
+    \partial_{\zeta_b,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_b=0}^{p}(\zeta_b(p)-\zeta_b)^{\lambda-1} \varphi(\zeta_b+b)\, d\zeta_b.
 \end{equation*}} 
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
+\end{defn}
+Notice that the fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{b}\,\fracderiv{\mu}{\zeta}{b} & = \fracderiv{\lambda+\mu}{\zeta}{b} \qquad \lambda, \mu \in (-\infty, 0),
 \end{align*}
@@
 \end{align*}
-\begin{lemma}\label{L-int-op}
-    The following identities hols true:
+\begin{prop}\label{prop:L-int-op}
+    Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
     \begin{itemize}
-        \item[i)]\label{item:i} \textcolor{orange}{for some $\sigma>-1$, $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ and for all $\lambda \in (0, \infty)$
-        \[%%\label{id:L-mult}
-\laplace_\zeta (\partial^{\lambda}_{\zeta} \varphi) = (-z)^n \laplace_\zeta \varphi.
-\]}
-\item[ii)]\label{item:ii} if $\varphi \in \singexpalg{\sigma}$, for all integers $n \ge 0$
-\[%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\]
-\item[iii)]\label{item:iii} if $\varphi\in\singexpalg{\sigma}(\Omega_b)$, then $\partial_{\zeta,b}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_b)$ and 
-\[ \laplace_{\zeta, b}\,\fracderiv{-\lambda}{\zeta}{b} \varphi = z^{-\lambda} \laplace_{\zeta, b} \varphi \]
-for all $\lambda \in (0, \infty)$. 
+        \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
+         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
+        for every $\lambda\in\R_{<0}$;
+        \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
+Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
+         \item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
+        for every $n\in\Z_{\geq 0}$.
     \end{itemize}
-\end{lemma}
+\end{prop}
 \begin{proof}
-    The result of \emph{i)} follows from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
+%\begin{align*}
+ %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
+  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
+   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
+%\end{align*}
+
+   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
+    \begin{align*}
+        z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
+        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
+        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
+        &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
+        \end{align*}
+        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
+\begin{align*}
+    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
+    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
+    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
+\end{align*}
+     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
+        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
 This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
@@
 \end{proof}
-We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Lemma~\ref{L-int-op}.
+We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
+\begin{prop}\label{prop:frac-der-int-borel}
+Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
+\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
+\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
+\end{itemize} 
+\end{prop}
+\begin{proof} 
+The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
+\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
+Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
+\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\partial_\zeta^\lambda\borel_\zeta\series{\Phi}\]
+where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
+
+Finally, $(iii)$ follows from a simple computation: 
+\begin{align*}
+\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
+&=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
+&=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
+&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
+\end{align*}
+\end{proof}
+\begin{remark}
+We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\tau\in\R\setminus\Z_{>0}$ 
+\[\fracderiv{\tau}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\tau \tilde{\Phi}\big]=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}.\]
+\begin{verify}
+\begin{align*}
+\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
+&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
+&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
+&=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
+\end{align*}
+Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
+$\tau>0$ and $\tau\notin\Z_{>0}$, 
+\[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
+\]
+and if $\tau<0$, by definition 
+\[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
+therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
+\end{verify}
+\end{remark}
+\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
+The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
+\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
+Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
+Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
+\begin{equation}
+    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
+\end{equation}
+where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\tilde{\phi}$ and $\tilde{\psi}$ in a neighbourhood of $\zeta=\alpha$.
+
+We also introduce $\delta_\alpha$ as the unit for the product $\ast_\alpha$
+\[\delta_\alpha\ast_\alpha\borel_\zeta(e^{-\alpha z}z^{-n-1}):=\borel_\zeta(1\cdot e^{-\alpha z} z^{-n-1})=\borel_\zeta\laplace_{\zeta,\alpha}\frac{\zeta_\alpha^n}{n!}=\frac{\zeta_\alpha^n}{n!},\]
+where in the last step we used the properties of $\borel_\zeta$ acting on transseries (see Section~\ref{sec:action_transseries}).
+More generally, if $\borel_\zeta\tilde{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
+\begin{remark}
+We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
+
+We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
+\begin{align*}
+    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta z^{-\lambda}\ast_\alpha\phi
+\end{align*}
+where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
+Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
+%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
+Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
+For every $\lambda\in (-1,\infty)$
+\begin{multline*}
+    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
+    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
+\end{multline*}
+hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
+%Finally, recall that for every holomorphic function $\Phi$ regareded as a function on $T^*_{\zeta=b}B$, the Borel transform  the fractional integrals $\fracderiv{-\lambda}{\zeta}{b}\varphi$ and 
+%$\fracderiv{-\lambda}{\zeta_b}{0}\varphi$ coincide, therefore 
+%\begin{align}\label{change_chart_convolution}
+ %   \borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_b\borel_\zeta\series{\Phi}
+%\end{align}
+%in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $b\in B$.
+\end{remark}
+
+%\subsection{Differential equation}
+%\textcolor{orange}{Should we keep this section?}
+%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
+In these coordinates, we can write down the partial differential operator
+%\begin{equation}%%\label{laplace:op}
+%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
+%\end{equation}
+%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
+
+%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
+%\end{problem}
+%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
+\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
+
 \color{orange}
@@
 \end{proof}
-
-\subsubsection{The convolution product}\label{convolution}
-%
-The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus we may wonder if $\borel_\zeta$ is an algebra isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-The answer is yes, once we endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
-Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $0$), then
-\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-In addition, it follows that the convolution product $\ast$ can be explicitly characterized as 
-\begin{equation}
-    \tilde{\psi}\ast\Tilde{\phi}=\int_0^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
-\end{equation}
-the proof is a simple computation, and we refer to  \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}.
-\begin{lemma}
-    Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is an algebra isomorphisms from $1$-Gevrey formal power series $\C \llbracket z^{-\tau} \rrbracket_1$ to the germs of holomorphic functions $\C \lbrace \zeta^{\tau-1} \rbrace$, with inverse given by the formal Laplace transform.
-\end{lemma}
-\begin{proof}
-    Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ with $|a_n|\leq A^n n!$ and $A>0$ then  
-\begin{align*}
-\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1}\frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
-\end{align*}  
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
-which grows as $n(n+1)^{-\tau} A^{n+1}$.
-\begin{verify}
-    we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
-\end{verify}
-\end{proof}
-In addition, the convolution product gives an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$: let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
-\begin{verify}
-    \begin{align*}
-        | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
-        &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
-        &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-        &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
-    \end{align*}
-\end{verify}
-We deduce that also the Laplace transform is an algebra isomorphisms from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
-\begin{lemma}
-    Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
-Then the Laplace transform $\laplace_\zeta^\theta$ is an algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
-\end{lemma}
-\begin{proof}
-    Then we can prove $\delta$ is a unit: 
-    \begin{align*}
-    \delta\ast\tilde{\phi}&=\borel_\zeta(1)\ast\tilde{\phi}=\borel_\zeta(1\cdot ?)
-    \end{align*}
-    we'll show $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$ and that $\laplace_\zeta^\theta\big(\tilde{\phi}\ast\tilde{\psi}\big)=\laplace_\zeta^\theta\big(\tilde{\phi}\big)\laplace_\zeta^\theta\big(\tilde{\psi}\big)$
-\end{proof}
-\begin{remark}
-    it is possible to define an inverse Laplace transform, so that $\laplace_\zeta^0$ becomes an algebra isomorphisms.
-However we'll refer to \textcolor{magenta}{[standard reference]} for details.
-\textcolor{magenta}{[see also section on Regularity for Laplace]}
-\end{remark}
-The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_\alpha B$ and let $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$
-\[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=\series{\psi}\ast \series{\phi}=\int_{0}^{\zeta_\alpha}\series{\psi}(\zeta_\alpha-\zeta')\series{\phi}(\zeta')d\zeta'\]
-Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_0 B$, we define  \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}\]
-then $\ast_\alpha$ can be explicitly written as 
-\begin{equation}
-    \tilde{\psi}\ast_\alpha\Tilde{\phi}=\int_\alpha^{\zeta}d\zeta' \tilde{\psi}(\zeta-\zeta')\tilde{\phi}(\zeta')
-\end{equation}
-where $\series{\phi}=\borel_\zeta\series{\Phi}$ and $\series{\psi}=\borel_\zeta\series{\Psi}$.
-We also introduce the unit $\delta_\alpha$ as \[\delta_\alpha\ast_\alpha\borel_\zeta\series{\Phi}=\borel_\zeta(1\cdot\series{\Phi})=\borel_\zeta\laplace_{\zeta,\alpha}\phi=\phi\]
-thus $\delta_\alpha\ast_\alpha\phi=\phi\ast_\alpha\delta_\alpha=\phi$. 
-\begin{remark}
-We notice that properties (i) and (ii) are special cases of the convolution product:
-\begin{align*}
-\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \tilde{\phi}\\
-&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\tilde{\phi}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{k\geq 0}a_k\frac{(\zeta-\zeta')^k}{k!}d\zeta'\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\int_0^1(t\zeta)^{-\tau-1}(\zeta-t\zeta)^k\zeta dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\alpha}\int_0^1 t^{-\tau-1}(1-t)^k dt\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\frac{1}{\Gamma(-\tau)}\zeta^{k-\tau}\frac{\Gamma(k+1)\Gamma(-\tau)}{\Gamma(k-\tau+1)}\\
-&=\sum_{k\geq 0}\frac{a_k}{k!}\partial_\zeta^{\tau} \zeta^k \\
-&=\partial_\zeta^\tau\tilde{\phi}
-\end{align*}
-\end{remark}
-%
-\begin{remark}
-We can express the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
-
-We first assume $\series{\Phi}=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, then for every $\lambda\in (0,\infty)$
-\begin{align*}
-    \borel_\zeta(z^{-\lambda}\series{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta z^{-\lambda}\ast_\alpha\phi
-\end{align*}
-hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\phi.\]
-%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
-Then, we assume $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ and we get for every $\lambda\in (0,\infty)$
-\begin{multline*}
-    \borel_{\zeta_\alpha}(z^{-\lambda}\series{\Phi})=\borel_{\zeta_\alpha}(z^{-\lambda}\laplace_{\zeta_\alpha,0}\phi)=\borel_{\zeta_\alpha}(\laplace_{\zeta_\alpha,0}\partial_{\zeta_\alpha,0}^{-\lambda}\phi)=\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha} (\zeta_\alpha-t)^{\lambda-1}\phi(t+\alpha)dt\\
-    =\borel_{\zeta_\alpha}(z^{-\lambda})\ast\phi(\zeta_\alpha+\alpha)
-\end{multline*}
-hence, recalling $\zeta=\zeta_\alpha+\alpha$ \[\partial_{\zeta_\alpha,0}^{-\lambda}\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\phi=\borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}\]
-Finally, recall that for every $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$ the fractional derivatives $\fracderiv{-\lambda}{\zeta}{\alpha}\varphi$ and 
-$\fracderiv{-\lambda}{\zeta_\alpha}{0}\varphi$ coincide, therefore 
-\begin{align}\label{change_chart_convolution}
-    \borel_{\zeta_\alpha} (z^{-\lambda})\ast\borel_{\zeta_\alpha}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta\series{\Phi}
-\end{align}
-in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $\alpha\in B$.
-\end{remark}
-
-%\subsection{Differential equation}
-%\textcolor{orange}{Should we keep this section?}
-%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-%\begin{equation}%%\label{laplace:op}
-%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-%\end{equation}
-%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-%\subsubsection{Regularity}
-
-%We generalize the result of Delabere (Lemma~3.5 \cite{diverg-resurg-iii}) to deal with fractional power singularities:
-
-%\begin{lemma}\label{lemma-3.5}
- %   Let $R_0>0$.
-Assume $f\in\mathcal{O}(\bar{D}(\infty,R_0))$ with $f(z)=O(z^{-\tau})$ at infinity for a certain $\tau\in\Q_{> 0}$, and let $M=\sup_{z\in D(\infty,R_0)} |f(z)|$.
-Then $\borel{f}$ is analytic on the Riemann surface of $\zeta^\tau$ and for every $\zeta$
-  %  \begin{equation}
-   %     |\borel{f}(\zeta)|\leq \frac{M}{\Gamma(\tau)}|\zeta|^\tau e^{\frac{|\zeta|}{R_0}}.
-   % \end{equation}
-%\end{lemma}
-
-%\begin{proof}
- %   The Taylor series expansion of $f$, $\sum_{k\geq 0}f_k z^{-k-\tau}$ converges in $D(\infty,R_0)$.
-By Cauchy inequalities, $|f_k|\leq M R_0^{-k}$ for any $k\in\Z_{\geq 0}$.
-The formal Borel transform of $f$ reads
-  %  \begin{align*}
-   %     \borel{f}(\zeta)=\frac{\zeta^{\tau-2}}{\Gamma(\tau-1)}\ast\sum_{k\geq 0} f_k \frac{\zeta^k}{k!}
-    %\end{align*}
-   %and for every $\zeta\in\C$, $\sum_{k\geq 0}|f_k|\frac{|\zeta|^k}{k!}\leq M e^{\frac{|\zeta|}{R_0}}$. Therefore
-   %\begin{align*}
-    %   |\borel{f}(\zeta)|&=\Big|\frac{1}{\Gamma(\tau-1)} \int_0^\zeta (\zeta-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{t^k}{k!} dt\Big|\\
-    %   &=\Big|\frac{\zeta^\tau}{\Gamma(\tau-1)} \int_0^1 (1-t)^{\tau-1} \sum_{k\geq 0} f_k \frac{(\zeta t)^k}{k!} dt\Big|\\
-   %    &\leq \frac{|\zeta|^\tau}{|\Gamma(\tau-1)|} \int_0^1 (1-t)^{\tau-1} M e^{\frac{|\zeta| t}{R_0}} dt\\
-    %   &=M\frac{|\zeta|^\tau}{|\Gamma(\tau)|} e^{\frac{|\zeta|}{R_0}} 
-   %\end{align*}
-
-  % This ensures uniform convergence on any compact set of $\C$, thus $\borel{f}$ is analytic.
-   %\color{Turquoise}
-%In the last step of the bound, we argue as follows: if $\tau>1$ then $\sup_{t\in [0,1]]}(1-t)^{\tau-1}= 1$. If $\tau\in (0,1)$ we integrate by part 
-%\begin{align*}
- %   \int_0^1 (1-t)^{\tau-1}  e^{\frac{|\zeta| t}{R_0}} dt&=-\frac{1}{\tau}(1-t)^{\tau}e^{\frac{|\zeta| t}{R_0}} \Big\vert_{t=0}^{t=1}+\frac{1}{\tau}\int_0^1(1-t)^\tau \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-  %  &\leq \frac{1}{\tau}+\frac{1}{\tau}\int_0^1 \frac{|\zeta|}{R_0}e^{\frac{|\zeta| t}{R_0}} dt\\
-   % &=\frac{1}{\tau}+\frac{1}{\tau} e^{\frac{|\zeta| t}{R_0}}\Big\vert_{t=0}^{t=1}\\
-   % &=\frac{1}{\tau} e^{\frac{|\zeta| }{R_0}}
-%\end{align*}
-%   \color{black}
-%\end{proof}
-
-%\begin{lemma}\label{lemma-3.8}
- %   Let $a,b,c,m\geq 0$ and for $r=0,...,N$ let $R_r$ be a sequence of holomorphic functions in a neighborhood of infinity, real and positive on $\R^+$. Then, the convolution equation 
-  %  \begin{equation}\label{eqn:convolution}
-   %     \hat{W}=m+[a+b\xi]\ast\hat{W}+c \sum_{r=0}^N \borel(z^{-2}R_r(z^{-1}))\ast\hat{W}
-   % \end{equation}
-   % has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
-In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-%\end{lemma}
-
-%We recall the following result which is a generalization of Lemma~3.8 in \cite{diverg-resurg-iii}:
-
-%\begin{proof}
- %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
-If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
-Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-  %  \begin{equation}
-        %\tilde{W}(z)=\frac{m}{z}+\left[\frac{a}{z}+\frac{b}{z^2}\right]\tilde{W}(z)+c\sum_{r=0}^{N}\frac{R_r(z^{-1})}{z^2}\tilde{W}(z)
-   % \end{equation}
-   % This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
-Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
-By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-%\end{proof}
-
-%\begin{lemma}\label{lemma-3.8bis}
- %Let $a_1,a_2,...,a_d,c,m\geq 0$ and $(\hat{R}_n)_{0\leq n\leq N}$ be a sequence of entire functions, real and positive on $\R^+$ with at most exponential growth of order $1$ at infinity.
-Then, the convolution equation
- %   \begin{equation}\label{eqn:convolution-bis}
-  %      \hat{W}=m+[a_1+a_2\xi+...+\frac{a_d}{(d-1)!}\xi^{d-1}]\ast\hat{W}+c\left(\hat{R}_0\ast\hat{W} +\sum_{n=1}^N\hat{R}_n\ast\hat{W}^n\right)
-   %\end{equation}
-    %has a unique solution in $\C[\![\xi]\!]$, whose sum converges to an entire function $\hat{W}_m(\xi)$ with at most exponential growth of order $1$.
-In addition, $\hat{W}_m$ is real, positive and non decreasing on $\R^+$ and for every $\xi\in\C$ the map $m\to\hat{W}_m(\xi)$ is continuous on $\R^+$.
-%\end{lemma}
-
-%\begin{proof}
- %   If $m\neq 0$, equation \eqref{eqn:convolution} admits a unique solution.
-If $m=0$, then we assume $\hat{W}_m\in\R[\![\xi]\!]$ is the unique solution once we fix a normalization.
-Then, the formal inverse Borel transform $\tilde{W}_m\in\R^+[\![z^{-1}]\!]$ solves an algebraic equation
-  %  \begin{equation}
-   %     \tilde{W}(z)=\frac{m}{z}+\left[\frac{a_1}{z}+\frac{a_2}{z^2}+...+\frac{a_d}{z^d}\right]\tilde{W}(z)+c\sum_{n=0}^NR_n(z)\tilde{W}^n(z)
-    %\end{equation}
-    %where $R_n(z)$ \textcolor{orange}{[maybe write these as $R_n(z^{-1})$ to match statement of ODE result]} are holomorphic in a neighborhood of infinity with $R_n(z)=O(z^{-1})$.
-This shows $\tilde{W}_m(z)=O(z^{-1})$ is holomorphic in $m,z$ for $m\in\C$ and $z$ in a neighbourhood of infinity (independent on $m$).
-Therefore, by Lemma~\ref{lemma-3.5} we deduce $\hat{W}_m$ is holomorphic in $\xi,m\in\C$ with at most exponential growth of order $1$ at infinity in $\xi$.
-By the general theory of ODEs, we also know $\hat{W}_m$ is real, positive and non-decreasing on $\R^+$.
-%\end{proof}
-
-%\begin{remark}
- %   Lemma \ref{lemma-3.8} and \ref{lemma-3.8bis} holds also when the convolution product $\ast$ is replaced by $\ast_p$ for every $p\in\C$. 
-%\end{remark}
 
@@
 \end{figure}
-\subsubsection{Main results}
+\subsubsection{Proof of main results}
 \color{Maroon}
@@
 \end{theorem}
+\begin{lemma}
+\textcolor{orange}{[The solution $\zeta_\alpha^{\tau_\alpha - 1} \psi_\alpha$ (or something) extends holomorphically over $\zeta = \alpha$.]}
+\end{lemma}
 \begin{proof}
@@
 
-To show that $\Psi_\alpha$ is Borel regular,
+To show that $\Psi_\alpha$ is Borel regular, first observe that by \textcolor{orange}{[Erdelyi \S 1.6---cite earlier]}, the asymptotic expansion $\series{\Psi}_\alpha = \aexp^\theta \Psi_\alpha$ satisfies the same differential equation that $\Psi_\alpha$ does.
+In addition, the leadeing term of $\series{\Psi}_\alpha$ is $z^{-\tau_\alpha}$.
+Thus, $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ satisfies the same intergral equation that $\psi_\alpha$ does, and its leading term is $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$.
 \end{proof}

### 2024-02-06 exp-resurgence.tex
Sync before working on proof of main results

@@
 The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
-The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section \ref{sec:geometry_borel},  \ref{sec:formal_borel}, and \ref{properties Borel transform}.
+The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}.
 Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
@@
 For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+\textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}
 
@@
 In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
-Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^* B$.
+Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^*B$.
 %
@@
 \[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
-
-\color{orange}
-\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
-\color{black}
 On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
@@
 %\color{black}
-\subsection{Borel and Laplace transforms as algebra homomorphisms}
+\subsection{Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
 The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-algebra homomorphisms between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.
@@
 
-\color{orange}
-\begin{lemma}
-    Let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ 
-\begin{itemize}
-\item[i)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^\lambda \tilde{\Phi}\big)=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\tilde{\Phi}.\]
-\item[ii)] for every $\lambda\in (0,\infty)$, \[\borel_\zeta\big(z^{-\lambda} \tilde{\Phi}\big)=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]
-%\item[iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[iii)] for every $n\geq 0$ \[\borel_\zeta\big(\partial_z^{n} \tilde{\Phi}\big)=(-\zeta)^n\borel_\zeta\tilde{\Phi}.\]
-\end{itemize} 
-\end{lemma}
-\begin{proof} 
-The result of $i)$ follows from Lemma~\ref{lem:frac-deriv-Borel}.
-Then to prove the result of $ii)$, notice that for $\lambda\in (0,\infty)$ \[\fracderiv{-\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\tfrac{k!}{\Gamma(k-\lambda+1)},\] hence \[\borel_\zeta (z^\lambda \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\lambda}}{k!}\tfrac{k!}{\Gamma(k-\lambda+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\fracderiv{-\lambda}{\zeta}{0}\zeta^k=\fracderiv{-\lambda}{\zeta}{0}\borel_\zeta\tilde{\Phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
-
-\end{proof}
-%
-\color{RoyalBlue}
-Define a new coordinate $\zeta_\alpha$ on $B$ so that $\zeta = \alpha + \zeta_\alpha$. From the calculation
-\begin{align*}
-\laplace_{\zeta, a} \varphi & = \int_{\Gamma_{\zeta, \alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \int_{\Gamma_{\zeta_\alpha, 0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-\alpha z} \laplace_{\zeta_\alpha, 0} \varphi,
-\end{align*}
-we learn that
-\begin{equation}
-    %\label{change-chart}
-    \laplace_{\zeta_\alpha, 0} \varphi = e^{\alpha z} \laplace_{\zeta, \alpha} \varphi.
-\end{equation}
-%
-\subsubsection{Rescaling of translation structure}
-%
-Let us rescale the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
-The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
-The corresponding frequency coordinate $x \maps T^*B \to B$ is given by $d\xi \mapsto 1$, so $x = \mu^{-1} z$.
-From the calculation
-\begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
-& = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
-we learn that
-\[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
-Note that $\laplace_{\xi, 0}$ is defined in the new translation structure on $B$, while $\laplace_{\zeta, 0}$ is defined in the old translation structure.
-We can still compare them because they both turn complex-valued functions on $B$ into holomorphic functions on $T^*B$.
-%
-\subsubsection{Action on integral operators}\label{L-int-op}
-%%For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{x \text{ from } 0}$ is defined by
-%%\[ \partial^{\nu-1}_{x,0} f(x) \defeq \frac{1}{\Gamma(1-\nu)} \int_0^x (x-x')^{-\nu} f(x')\,dx'. \]
-For $\nu \in (-\infty, 1)$, the fractional integral $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
-
-It obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} & \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
-\begin{definition}\label{defn:frac_driv}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-
-%Each convention for the fractional derivative brings its own annoyances to interactions with the Borel transform.\footnote{See Remark~\ref{rmk:caputo} for examples.} The Riemann-Liouville derivative will be the least annoying for our purposes.
-
-%\color{Tan}
-%You can use a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, to show that $\fracderiv{-\lambda}{\zeta}{a} \varphi \in \mathcal{E}_\zeta$ and
-%\[ \laplace_{\zeta, a}\,\fracderiv{-\lambda}{\zeta}{a} \varphi = z^{-\lambda} \laplace_{\zeta, a} \varphi \]
-%for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \mathcal{E}_\zeta$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-%\begin{equation}%%\label{id:L-mult}
-%\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-%\end{equation}
-%for all integers $n \ge 0$.
-
-Using a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}, one can show that $\partial^{-\lambda}_{\zeta} \varphi \in \singexpalg{\sigma}$ for some $\sigma>-1$ and
-\[ \laplace_{\zeta,0}\,\partial^{-\lambda}_{\zeta} \varphi = z^{-\lambda} \laplace_{\zeta, 0} \varphi \]
-for all $\lambda \in (0, \infty)$.
-This generalizes the Laplace transform's action on derivatives: when $\varphi \in \singexpalg{\sigma}$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
-\begin{equation}%%\label{id:L-mult}
-\laplace_\zeta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_\zeta \varphi.
-\end{equation}
-for all integers $n \ge 0$.
-Furthermore, if $\varphi\in\singexpalg{\sigma}(\Omega_\alpha)$, then $\partial_{\zeta,\alpha}^{-\lambda}\varphi\in\singexpalg{\sigma+\lambda}(\Omega_\alpha)$ and 
-\[ \laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi \]
-for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta,\alpha}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
-%
-\begin{equation}
-    \partial_{\zeta,\alpha}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^{\zeta}(\zeta-t)^{\lambda-1} \varphi(t) dt
-\end{equation}\color{black}
-%
-\color{RoyalBlue}Similarly, $\partial_{\zeta_\alpha,0}^{-\lambda}\varphi\in\singexpalg{\sigma}(\Omega_{\zeta_\alpha})$ and 
-\[ \laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi \]
-for all $\lambda \in (0, \infty)$, \color{orange}where the operator $\partial_{\zeta_\alpha,0}^{-\lambda}$ is defined by [the fractional integral was already defined at the beginning of the section]
-%
-\begin{equation}
-    \partial_{\zeta_\alpha,0}^{-\lambda}\varphi:=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_\alpha}(\zeta_\alpha-t)^{\lambda-1} \varphi(t+\alpha) dt
-\end{equation}\color{RoyalBlue}
-%
-Notice that the definition of $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ are indeed the same as it follows by a simple change of coordinates $t\to t+\alpha$.
-However, there is no contradiction as it can be easily verified using the relation \eqref{change-chart}.
-[Isn't this a special case of the $\laplace_{\zeta, \alpha}$ statement?]\color{black}
-
-%We remark that on a translation surface, there is no preferred coordinate chart, hence either $\zeta$ as local coordinate at $\alpha$ or $\zeta_\alpha$ as local coordinate at $0$ are equivalent choices.
-
-%Notice that $z^{-\lambda}$ is a coordinate on different fibres of $T^*B$: $z\in T_0^*B$ in equation $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, while $z\in T^*_\alpha B$ in equation $\laplace_{\zeta_\alpha,0}\,\fracderiv{-\lambda}{\zeta_\alpha}{0} \varphi = z^{-\lambda} \laplace_{\zeta_\alpha,0} \varphi$.
-In fact, as we’ll see in Section \ref{convolution}, both $\fracderiv{-\lambda}{\zeta}{\alpha}$ and $\fracderiv{-\lambda}{\zeta_\alpha}{0}$ can be regarded as a convolution product which depends on the fibre.
-
-%We also remark that $\partial_{\zeta,\alpha}^{-\lambda}\varphi=\partial_{\zeta_\alpha,0}^{-\lambda}\varphi$ for every $\varphi\in\mathcal{E}_{\zeta,\alpha}$ (in fact the path $\Gamma_{\zeta,\alpha}$ is equivalent to the path $\Gamma_{\zeta_\alpha,0}$).
-
-%\color{gray}
-%\begin{itemize}
-%\item Action on differential equations.
-%\begin{itemize}
-%\item No inhomogeneous terms! How is this consistent with the Laplace transform's action? Is there always an inhomogeneous solution with subexponential asymptotics?
-%\end{itemize}
-%\end{itemize}
-%\color{black}
-
-%The Borel transform is a linear map from formal power series in the {\em frequency variable} $z$ to formal power series in the {\em position variable} $\zeta$, defined by
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta}\big[a_0 + a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_0\delta + a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-%The motivation for adding the formal ``convolution unit'' $\delta$ to the codomain is discussed \textcolor{magenta}{[in the convolution product section]}.
-
-%\subsection{Properties of the Borel transform}\label{properties Borel transform}
-We now recall some properties of the Borel transform: let $\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C\llbracket z^{-1}\rrbracket$ and $\tilde{\phi}\defeq\borel\textcolor{orange}{_\zeta}\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} if $\alpha\in\R_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(ii)] \emph{[fractional integral]} if $\alpha\in\R_{<0}\setminus\Z_{\geq 0}$, $\borel_\zeta\left(z^\alpha \tilde{\Phi}\right)=\partial_{\zeta}^{\alpha}\tilde{\phi}$
-\item[(iii)] if $n\in\Z$ and $z^nf(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, then $\borel_\zeta (z^n\tilde{\Phi})=\partial_\zeta^n\tilde{\phi}$ 
-\item[(iv)] $\borel_\zeta\left(\partial_z^{n} \tilde{\Phi}\right)=(-\zeta)^n\tilde{\phi}$, for every $n\geq 0$
-\item[(v)] $\borel_{\zeta}(\tilde{\Phi}(z-c))=e^{-c\zeta}\tilde{\phi}$ \textcolor{orange}{[put analogue of this in Laplace section]}
-\end{itemize}
-
-\begin{proof}
-
-We are going to prove properties (i)--(vi).
-
-(i) follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-(ii) Notice that for $\alpha\in\R\setminus\Z_{\geq 0}$ the fractional integral $\partial_\zeta^{\alpha}\zeta^{k}=\zeta^{k-\alpha}\tfrac{k!}{\Gamma(k-\alpha+1)}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k\tfrac{\zeta^{k-\alpha}}{k!}\tfrac{k!}{\Gamma(k-\alpha+1)}=\sum_{k\geq 0}a_k \tfrac{1}{k!}\partial_\zeta^{\alpha}\zeta^k=\partial_\zeta^\alpha\tilde{\phi}.\]
-
-(iii) $z^n\tilde{\Phi}=\sum_{k\geq 0}a_kz^{-(k-n)-1} $ and by assumption $k-n\geq 0$, hence by definition \[\borel_\zeta (z^n \tilde{\Phi})=\sum_{k\geq n} a_k\tfrac{\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\tfrac{k!\zeta^{k-n}}{(k-n)!}=\sum_{k\geq n} a_k\tfrac{1}{k!}\partial_\zeta^n\zeta^k=\partial_\zeta^n\tilde{\phi}.\]
-
-(vi) $\partial_z^n \tilde{\Phi}=\sum_{k\geq 0}a_k(-1)^{n}z^{-k-n-1}\tfrac{\Gamma(k+n+1)}{k!}$, hence \[\borel_\zeta (z^\alpha \tilde{\Phi})=\sum_{k\geq 0}a_k(-1)^{n}\tfrac{\zeta^{k+n}}{\Gamma(k+n+1)}\tfrac{\Gamma(k+n+1)}{k!}=(-\zeta)^{n}\tilde{\phi}.\]
-
-(v) see \cite[Lemma 5.10]{diverg-resurg-i}.
-
-\end{proof}
-
 \section{Proof of main results}\label{sec:proof_main_results}
@@
 \end{theorem}
+The key to our proof is recasting Equation~\eqref{eqn:standard ODE} as an integral equation in the position domain.
+This integral equation belongs to a well-behaved class of regular singular Volterra equations, which we study in~\cite{reg-sing-volterra}.
+In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction.
+We'll use the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$ \cite[Theorem~4]{reg-sing-volterra}.
+%%\begin{theorem}(Theorem~4 from \cite{reg-sing-volterra})
+%%\textcolor{orange}{[\ldots]}
+%%\end{theorem}
+
+For the Borel regularity part of the proof, we need to make a connection between the analytic and formal worlds.
+To do this in the position domain, we again use Picard iteration.
+\textcolor{orange}{[Does this generalize Delabaere's argument?
+If so, mention that.]}
 \begin{lemma}
-\textcolor{orange}{[The solution $\zeta_\alpha^{\tau_\alpha - 1} \psi_\alpha$ (or something) extends holomorphically over $\zeta = \alpha$.]}
+\textcolor{orange}{[The solution $\zeta_\alpha^{1 - \tau_\alpha} \psi_\alpha$ (or something) extends holomorphically over $\zeta = \alpha$.]}
 \end{lemma}
+\begin{proof}
+\textcolor{orange}{[\ldots]}
+\end{proof}
+\begin{lemma}
+The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
+\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
+of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
+\end{lemma}
+\begin{proof}
+\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
+\end{proof}
 \begin{proof}
@@
 
-To show that $\Psi_\alpha$ is Borel regular, first observe that by \textcolor{orange}{[Erdelyi \S 1.6---cite earlier]}, the asymptotic expansion $\series{\Psi}_\alpha = \aexp^\theta \Psi_\alpha$ satisfies the same differential equation that $\Psi_\alpha$ does.
+To show that $\Psi_\alpha$ is Borel regular, first observe that by \textcolor{orange}{[Erdelyi \S 1.6---cite in appdendix; to get uniformity, we might need a constant-width strip, rather than a sector]}, the asymptotic expansion $\series{\Psi}_\alpha = \aexp^\theta \Psi_\alpha$ satisfies the same differential equation that $\Psi_\alpha$ does.
 In addition, the leadeing term of $\series{\Psi}_\alpha$ is $z^{-\tau_\alpha}$.
@@
 \subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
+\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
 \color{black}
@@
 \end{equation}
-Taking the Laplace transform of both sides and applying properties of the Borel transform (\S \ref{properties Borel transform}), we see that
+Taking the Laplace transform of both sides and applying properties of the Borel transform (see Proposition~\ref{prop:frac-der-int-borel}), we see that
 \begin{align*}
@@
 
-\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
+\section{Facts about differential and integral equations}
+%%\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
 \textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
-
-\subsubsection{Order shifting}\label{shifting}
+\subsection{Passing between the analytic world and the formal world}
+\textcolor{orange}{Show that the Taylor expansion of an analytic solution of an integral equation satisfies the same equation (or just cite the statement in Erdelyi).
+Cite the theorem of Erdelyi which shows that a solution of a differential equation (under certain conditions) has an asymptotic expansion, which satisfies the corresponding differential equation.}
+\subsection{Order shifting}\label{shifting}
 Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.

### 2024-02-07 exp-resurgence.tex
Start writing up proof of lem:picard-power
Also, change ODE setting to match regular singular Volterra paper.

@@
 ]}
+
+% regular singular volterra operator
+\newcommand{\volterra}{\mathcal{V}}
+\newcommand{\hardpart}{\mathcal{V}_0}
+\newcommand{\softpart}{\mathcal{V}_\star}
+%%\newcommand{\kerwhole}{k}
+\newcommand{\hardker}{k_0}
+%%\newcommand{\softker}{k_\star}
+\newcommand{\solwhole}{f}
+\newcommand{\solproto}{f_0}
+\newcommand{\solptb}{f_\star}
+%%\newcommand{\roots}{\mathfrak{B}}
 
@@
 One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-The general example is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big], \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_0, \ldots, R_{d-1}$ are holomorphic functions in some disk $|z|>A$ around infinity.
+\textcolor{magenta}{The general example [not anymore---we've restricted]} is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
 We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}.
-That solution is Borel regular.
+Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
 \end{theorem}
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-\textcolor{orange}{[Make sure this matches regular singular Volterra paper!]} Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $\mathcal{P}$ be a linear differential operator\footnote{ We follow Delabaere, rather than \'Ecalle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
-\begin{equation}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-
-\begin{itemize}
-\item $P$ is a monic degree-$d$ polynomial with simple zeros; \footnote{Unlike \'Ecalle, we don't require all the roots of $P$ to be non-zero, because  we can translate in the position domain.}
-\item $Q$ is a degree-$(d-1)$ polynomial and $Q(-\alpha)\neq 0$ for all zeros $\alpha$;
-\item $R_0(z^{-1}), \ldots, R_{d-1}(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$.
-\end{itemize}
-
-For every zeros $\alpha$, let $\Omega_\alpha\subset B$ be a simply connected open set that touches but doesn't contain $\zeta = \alpha$. We also assume:
-\begin{itemize}
-\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$.
+\subsubsection{Proof of main results}
+Let's recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
+%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
+\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
+where
+\begin{enumerate}
+\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
+\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
+\[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
+converges in the region $|z| > A$.
+\end{enumerate}
+%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
+\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
+%%%\begin{itemize}
+%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$.
 In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$.
 Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we'll always leave that starting point out of the path.
-\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
+%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
 \textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
 Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
-\end{itemize}
+%%%\end{itemize}
 
@@
 \end{tikzpicture}
-\caption{The domain $\Omega_\alpha$}\label{Fig:domain}
+\caption{The domain $\Omega_\alpha$ \textcolor{orange}{[Revise to show asector]}}\label{Fig:domain}
 \end{figure}
-\subsubsection{Proof of main results}
 \color{Maroon}
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in \textcolor{magenta}{[the appropriate affine subspace of]} the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}.
-That solution is Borel regular.
+Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
 \end{theorem}
@@
 In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction.
-We'll use the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$ \cite[Theorem~4]{reg-sing-volterra}.
-%%\begin{theorem}(Theorem~4 from \cite{reg-sing-volterra})
-%%\textcolor{orange}{[\ldots]}
+We'll use \textcolor{magenta}{the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ [actually, use prototype solution instead]} to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$.
+%%\begin{theorem}[Theorem~4 from \cite{reg-sing-volterra}]\label{thm:sing-soln}
+%%The equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+%%\[ \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
 %%\end{theorem}
@@
 To do this in the position domain, we again use Picard iteration.
-\textcolor{orange}{[Does this generalize Delabaere's argument?
-If so, mention that.]}
-\begin{lemma}
-\textcolor{orange}{[The solution $\zeta_\alpha^{1 - \tau_\alpha} \psi_\alpha$ (or something) extends holomorphically over $\zeta = \alpha$.]}
+\textcolor{orange}{[This does seem to generalize Delabaere's argument!
+We should confirm and mention that.]}
+\begin{lemma}\label{lem:picard-power}
+In Theorem~4 of \cite{reg-sing-volterra}, the solution $\psi_\alpha$ can be expressed as the sum of a power series in $\zeta_\alpha^{\tau_\alpha - 1} \C\{\zeta_\alpha\}$.
+%%can be expressed as a convergent power series of the form
+%%\[ c_1 \zeta_\alpha^{\tau_\alpha - 1} + c_2 \zeta_\alpha^{\tau_\alpha} + c_3 \zeta_\alpha^{\tau_\alpha + 1} + c_4 \zeta_\alpha^{\tau_\alpha + 2} + \ldots. \]
 \end{lemma}
 \begin{proof}
+%%Theorem~\ref{thm:sing-soln} is a corollary of Theorem~\ref{thm:general_volterra} of \cite{reg-sing-volterra}.
+The ring of formal power series $\C\{\zeta_\alpha\}$ is isomorphic to the ring of germs of holomorphic functions at $\zeta = \alpha$.
+This isomorphism identifies the analytic and formal versions of the integration operator $\partial^{-1}_{\zeta, \alpha}$.
+In the argument that follows, we'll only distinguish the analytic and formal interpretations of $\C\{\zeta_\alpha\}$ when we need to.
+
+For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
+The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
+%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
+\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
+and the perturbation
+%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
+\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}). \]
+
+Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
+satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
+We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
+This is equivalent to solving the inhomogeneous equation
+\begin{equation}\label{eqn:inhomog-volterra}
+\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
+\end{equation}
+
+The central idea of the proof is to show that $\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
+It follows, by the Banach fixed point theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
+More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
+Starting with any initial guess $\solptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
+\begin{align*}
+\solptb^{(1)} & = \volterra^\alpha \solptb^{(0)} \\
+\solptb^{(2)} & = \volterra^\alpha \solptb^{(1)} \\
+\solptb^{(3)} & = \volterra^\alpha \solptb^{(2)} \\
+& \;\;\vdots
+\end{align*}
+we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ to a solution.
+
 \textcolor{orange}{[\ldots]}
+
+%%Let's recall some notation from the proof. For convenience, we let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+
+%%For convenience, let $p = P(-\zeta_\alpha)$ and $q = Q(-\zeta_\alpha)$. In \cite{reg-sing-volterra}, we observed that the Volterra operator $\hardpart^\alpha$ with kernel
+%%Let $\hardpart^\alpha$ be the Volterra operator with kernel
+%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)} \]
+%%and let $\softpart^\alpha$ be the Volterra operator with kernel
+%%\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
+
+%%For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+
+%%As we did in the proof of Theorem~\ref{thm:sing-soln} from \cite{reg-sing-volterra}, let
+
+%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]
+
+%%\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+
+Since $p$ has a simple root at $\zeta = \alpha$, the prototypical part $\hardpart^\alpha$ sends $\C\{\zeta_\alpha\}$ to itself.
+In fact, for any real number $\sigma$ that's not a negative integer, $\hardpart^\alpha$ maps $\zeta^\sigma \C\{\zeta_\alpha\}$ to itself.
+Under the same condition on $\sigma$, the operator $R(\partial^{-1}_{\zeta, \alpha})$ is well-defined as a map from $\zeta_\alpha^\sigma \C\{\zeta_\alpha\}$ to itself,\footnote{This is easiest to see from the formal point of view.
+Multiplication by $R(\zeta)$ sends convergent series to convergent series, and $\partial^{-1}_{\zeta, \alpha}$ acts like multiplication by $\zeta$ followed by the map $\zeta^\rho \mapsto \tfrac{1}{\Gamma(\rho+1)} \zeta^\rho$.
+A convergent series stays convergent under any operation that leaves its coefficients the same or smaller.
+\textcolor{orange}{[Discuss convergence of the operator series from the analytic point of view?]}.} so the perturbation can be seen as a map $\softpart^\alpha \maps \zeta_\alpha^\sigma \C\{\zeta_\alpha\} \to \zeta_\alpha^{\sigma + 1} \C\{\zeta_\alpha\}$.
+
+\textcolor{orange}{[\ldots]}
+
 \end{proof}
-\begin{lemma}
+\begin{lemma}\label{lem:formal-general-volterra}
 The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
@@
 
-By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+As a consequence of Theorem~\ref{thm:sing-soln}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]

### 2024-02-08 exp-resurgence.tex
rewrite and cleaning

@@
 
+\usepackage{etoolbox}
+
+\usetikzlibrary{math, 3d, calligraphy}
+
+% --- styles ---
+
+\definecolor{pwbeige}{RGB}{172, 146, 122}
+\definecolor{pworange}{RGB}{245, 153, 30}
+
+\tikzset{
+  surf/.style={pwbeige!10},
+  leaf/.style={thin, pwbeige!60},
+  sing/.style={thick, pworange},
+  ray/.style={thick}
+}
+
+% --- cotangent fibers ---
+
+\newcommand{\rfiber}{1.5}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+
+\newcommand{\drawfiber}{
+  \foreach \sgn in {-1, 1} {
+    \calligraphy[scale=\sgn, copperplate, heavy, heavy line width=0.25mm]
+      (\rfiber, \rfiber) -- (\rfiber, -\rfiber)
+      (\rfiber, -\rfiber) -- (-\rfiber, -\rfiber);
+  };
+}
+
+% set up PGF keys
+\pgfkeys{
+  /laplace/.cd,
+  drop/.store in=\fiberdrop,   drop/.value required,
+  shade/.store in=\fibershade, shade/.default=true,
+  degree/.store in=\fiberdeg,  degree/.value required,
+  phase/.store in=\fiberphase, phase/.value required,
+  dual/.store in=\fiberdual,   dual/.default=true
+}
+
+\newcommand{\fiberdescender}[1]{
+  \calligraphy[copperplate, light, thin] (0, -\rfiber) -- (0, -#1);
+}
+
+\newcommand{\fibershading}[2]{
+  \tikzmath{
+    \shadestart = (-90 - #1) / \fiberdeg;
+    \shadeend = (90 - #1) / \fiberdeg;
+  }
+  \fill[pwbeige!30, draw=pwbeige!60] (0, 0) -- (\shadestart:\rshade) arc (\shadestart:\shadeend:\rshade) -- cycle;
+}
+
+\newenvironment{fiber}[1][]{%
+  \pgfkeys{/laplace/.cd, drop=0, shade=false, degree=1, phase=0, #1}
+  \begin{scope}
+    \fill[surf] (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
+    \clip (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
+    \tikzmath{
+      if \fibershade then {
+        print \fibershading{\fiberphase}{0};
+      };
+    }
+}{% ...
+  \end{scope}
+  % see TikZ docs for branching statements
+  % https://tikz.dev/library-math#sec-58.5
+  \tikzmath{
+    if \fiberdrop > 0 then {
+      print \fiberdescender{\fiberdrop};
+    };
+  }
+  \drawfiber
+}
+
+\newcommand{\genfibercontent}[1][]{
+  \pgfkeys{/laplace/.cd, dual=false, #1}
+  \pgfmathsetmacro{\hatch}{\rfiber/8};
+  \pgfmathsetmacro{\firsthatch}{-\rfiber+\hatch}
+  \pgfmathsetmacro{\nexthatch}{-\rfiber+2*\hatch}
+  \pgfmathsetmacro{\hatchstop}{\rfiber-\hatch/2}
+  \foreach \y in {\firsthatch, \nexthatch, ..., \hatchstop} {
+    \tikzmath{
+      coordinate \drawfrom;
+      coordinate \drawto;
+      if \fiberdual then {
+        \drawfrom = (\y, -\rfiber);
+        \drawto = (\y, \rfiber);
+      } else {
+        \drawfrom = (-\rfiber, \y);
+        \drawto = (\rfiber, \y);
+      };
+    }
+    \draw[leaf] (\drawfrom) -- (\drawto);
+  };
+  \fill circle (\dotsize);
+}
+
+\newcommand{\singfibercontent}{
+  % nonsingular leaves
+  \foreach \sector in {30, 90, ..., 330} {
+    \tikzmath{
+      \farout = 45*floor((\sector + 59) / 45);
+      \tfarout = 3*(\farout - \sector);
+      \rfarout = \rfiber/sin(45+mod(\farout-45, 90));
+    }
+    \pgfmathsetmacro{\rmax}{sin(\tfarout) * pow(\rfarout, 3)}
+    \foreach \r in {0.5, 1.0, ..., \rmax} {
+      \pgfmathsetmacro{\win}{asin(\r/(2*\rmax))}
+      \draw[leaf, rotate=\sector, domain=\win:{180-\win}, variable=\t] plot ({\t/3}:{(\r/sin(\t))^(1/3)});
+    };
+
+    % singular leaves
+    \foreach \ang in {90, 210, 330} {
+      \draw[sing] (\ang:{-sqrt(2)*\rfiber}) -- (\ang:{sqrt(2)*\rfiber});
+    };
+    \fill[sing] circle (\dotsize);
+  };
+}
+
+% --- posititon plane ---
+
+\pgfmathsetmacro{\hatch}{2/3}
+\tikzmath{
+  \phase = 15;
+  \dotsize = 0.04;
+  \drop = 3.5;
+  \xsing = 2;
+  \zsing = 4*\hatch;
+  \xgen = 6;
+  \zgen = 8*\hatch;
+  \rcut = 1/5;
+}
+
+\newcommand{\ray}[2]{
+  \draw[ray] (#1, #2) -- (8, {#2 + (8-#1)*tan(\phase)});
+}
+
+% local picture of the Laplace transform
+\newcommand{\basicLaplace}{
+\begin{tikzpicture}[scale=0.9]
+% position space
+\begin{fiber}
+  \genfibercontent
+  \ray{0}{0}
+\end{fiber}
+\node[anchor=north, outer sep=1mm, font=\footnotesize]
+  at (0, -\rfiber) {position space};
+
+% frequency space
+\begin{scope}[shift={(4 + 0.25*8/3, 0)}]
+  \begin{fiber}[shade, phase=\phase]
+    \genfibercontent[dual]
+  \end{fiber}
+  \node[anchor=north, outer sep=1mm, font=\footnotesize]
+    at (0, -\rfiber) {frequency space};
+\end{scope}
+\end{tikzpicture}
+} % \basicLaplace
+
+% phase space picture of the Laplace transform
+\newcommand{\phaseSpaceLaplace}{
+\begin{tikzpicture}[z={(0.25cm, 0.2cm)}, scale=0.9]
+% position plane
+\begin{scope}[canvas is xz plane at y=0]
+  % surface
+  \fill[surf]
+    (0, 0) -- (0, \zsing-\rcut)
+    -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut})
+    -- (0, 8) --(8, 8) -- (8, 0) -- cycle;
+
+  % hatching
+  \pgfmathsetmacro{\nexthatch}{2*\hatch}
+  \pgfmathsetmacro{\singstop}{\zsing - \hatch/2}
+  \foreach \z in {\hatch, \nexthatch, ..., \singstop} {
+    \draw[leaf] (0, \z) -- (8, \z);
+  };
+  \pgfmathsetmacro{\singstart}{\zsing + \hatch}
+  \pgfmathsetmacro{\singnext}{\zsing + 2*\hatch}
+  \pgfmathsetmacro{\hatchstop}{8 - \hatch/2}
+  \foreach \z in {\singstart, \singnext, ..., \hatchstop} {
+    \draw[leaf] (0, \z) -- (8, \z);
+  };
+
+  % singular leaves
+  \begin{scope}[sing]
+    \draw (\xsing, \zsing) -- (8, \zsing);
+    \draw (0, \zsing-\rcut) -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut});
+  \end{scope}
+
+  % integration rays
+  \ray{\xgen}{\zgen}
+  \ray{\xsing}{\zsing}
+
+  % outline
+  \calligraphy[copperplate, heavy, heavy line width=0.25mm]
+    (0, 0) -- (0, \zsing-\rcut)
+    (0, \zsing+\rcut) -- (0, 8)
+    (0, 8) -- (8, 8)
+    (8, 8) -- (8, 0)
+    (8, 0) -- (0, 0);
+\end{scope}
+
+% generic fiber
+\begin{scope}[canvas is xy plane at z=\zgen, shift={(\xgen, \drop)}]
+  \begin{fiber}[drop=\drop, shade, phase=\phase]
+    \genfibercontent[dual]
+  \end{fiber}
+\end{scope}
+
+% singular fiber
+\begin{scope}[canvas is xy plane at z=\zsing, shift={(\xsing, \drop)}]
+  \begin{fiber}[drop=\drop, shade, degree=3, phase=\phase]
+    \singfibercontent
+  \end{fiber}
+\end{scope}
+
+% generic point
+\fill (\xgen, 0, \zgen) circle (\dotsize);
+
+% singular point
+\fill[sing] (\xsing, 0, \zsing) circle (\dotsize);
+
+% labels
+\begin{scope}[overlay]
+  \node (surf label) at (9, 0, 4) {$B$};
+  \path (surf label) ++(0, \drop, 0) node {$T^*B$};
+  \node[outer sep=0.15mm, font=\footnotesize, align=left]
+    (cut label) at (-1.25, 1.2, \zsing) {branch cut \\ at conical \\ singularity};
+  \draw[->] (cut label) to[out=-75, in=180] (-0.25, 0, \zsing);
+\end{scope}
+\end{tikzpicture}
+} % \phaseSpaceLaplace
+
 \setcounter{tocdepth}{2}
@@
 \begin{abstract}
-    ...
+    Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
+Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
+In addition, we give a geometric description of the Borel plane.
 \end{abstract}
 \tableofcontents
-
-\begin{brainstorm}
-    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
-    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
-    \item Section~\ref{contour-argument-AL}---revise the general contour argument
-    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
-    \begin{itemize}
-    \item Replace formalism in Section~\ref{sec:reg-decay}
-    \end{itemize}
-    \item Check which examples are still in the framework of our theorem
-    \begin{itemize}
-    \item Start a storage document for shelved examples
-    \end{itemize}
-    \item Section~\ref{resurgence-AL}---Draw intersection points figure
-    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
-    \item Explain contour figure in Airy example (explain what the regions indicate and what the color)
-    \begin{itemize}
-    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
-    \end{itemize}
-    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
-    \begin{itemize}
-    \item Put future goals in storage document
-    \end{itemize}
-    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
-\end{brainstorm}
-
+%
+%
+%
 \section{Introduction}
@@
 Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_b^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_{\zeta,b}^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_{\zeta,b}^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
 \end{enumerate}
@@
 \item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}.
-\textcolor{magenta}{The general example [not anymore---we've restricted]} is the equation $\mathcal{P} \Phi = 0$ given by a differential operator of the form
+One example is Equation~\eqref{eqn:bessel-rescaled-1}, and we will cosndier equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
@@
 [These details are right above in Section~\ref{borel-reg:explanatory-power}!]
-\begin{equation}\label{eqn:standard ODE}
+\begin{equation}%\label{eqn:standard ODE}
 \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
@@
 
-A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_\alpha^\theta \phi$ of a function on $\phi$ the position domain.
+A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function on $\phi$ the position domain.
 In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.
@@
 Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$.
-Because this solution is so unique, its Laplace transform $\Phi_\alpha$ turns out to be Borel regular.
+Because this solution is so unique, its Laplace transform $\Psi_\alpha$ turns out to be Borel regular.
 
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
+Equation $\mathcal{P}\Psi=0$ has a unique solution $\Psi_\alpha$ in the affine subspace
 \[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
 \end{theorem}
@@
 \begin{corollary}\label{cor:borel_reg_ODE}
-For each root $-\alpha$ of $P$, Equation~\eqref{eqn:standard ODE} has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
+For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
 That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
@@
 Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way.
-Use the Ramis index theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
+Use the Ramis Index Theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
 %%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
@@
 \color{black}
-\textcolor{Violet}{[This is sort of a mirror image of the Ramis index theorem?]}
-\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
-The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$.
+\textcolor{Violet}{[This is sort of a mirror image of the Ramis Index Theorem?]}
+%\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
+%The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$.
 In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
 \textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
-\end{theorem}
-%
-We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
+%\end{theorem}
+%
+\textcolor{red}{[Change or actually delete]}We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
 On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$.
@@
 \end{theorem}
-\color{Goldenrod}
-Then, our main result for thimble integrals is proving they are indeed Borel regular:
-\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
-    Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
-\begin{enumerate}
-\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
-\begin{multline}
-\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
-\end{multline}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
+%\color{Goldenrod}
+%Then, our main result for thimble integrals is proving they are indeed Borel regular:
+%\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
+ %   Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
+%\begin{enumerate}
+%\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
+%\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+%\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
+%\begin{multline}
+%\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
+%\end{multline}
+%where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
 Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
 \textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{enumerate}
-\end{theorem}
-\color{black}
+%\end{enumerate}
+%\end{theorem}
+%\color{black}
+\color{RoyalBlue}
 We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
-\[
-\begin{tikzcd}
-{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
-& & &\\
-\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]
-\end{tikzcd}
-\]
+%\[
+%\begin{tikzcd}
+%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
+%& & &\\
+%\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]
+%\end{tikzcd}
+%\]
 On the one hand, with a change of coordinates, the thimble integral $I$ can be written as a Laplace type integral, i.e.
@@
 Finally, we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
-
+\color{black}
 %% the following remark has been moved to Section of the proof
@@
 We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs (see \cite[Theorem 4]{reg-sing-volterra}).
+In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs, building on our previous result \cite[Theorem 4]{reg-sing-volterra}.
 
 Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
+If $b \in B$ is non-singular, the frequency domain for $\laplace_{\zeta,b}^\theta$ is $T^*_{\zeta=b} B$.
 If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
-
 \begin{figure}[ht]
 \centering
-    \includegraphics{testbed/testbed1.pdf}
+\basicLaplace
+\vspace{1cm}
+
+\phaseSpaceLaplace
 \caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
@@
 \end{figure}
-We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), modified Bessel function, Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).}
-
-On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+
+We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-The thimble projection reasoning is the one we use in the proof of Theorem~\ref{thm:maxim} part~\ref{part3}.
+The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
 In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
@@
 We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}).
+For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}.
 \textcolor{red}{The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
@@
 Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
-The resurgence of linear ODEs have been intensively studied (see Costin slides for ReNewQuantum, \cite{EcalleIII,loday1994stokes,diverg-resurg--ii}) and many results are also known for non-linear ODEs (see \cite{schiappa-PI,costin-PI,diverg-resurg-iii} \textcolor{magenta}{[check also paper by \'Ecalle and Sauzin]}).
-For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see examples in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional integrals are toy-models that show some features of resurgent functions.
+The resurgence of linear ODEs have been intensively studied \cite{loday1994stokes,diverg-resurg--ii} and many results are also known for non-linear ODEs \cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see the last example in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional thimble integrals are toy-models that show some features of resurgent functions.
 
@@
 \subsection{Plan of the paper}
-The paper is organized as follows: Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
-The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{sec:reg-decay}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}.
-Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm2} and Theorem~\ref{thm:maxim}.
+The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
+This could help the reader to contextualize our results in the literature.
+Then, in Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
+The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}.
+Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm:borel_reg_ODE} and Theorem~\ref{thm:maxim}.
 Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
-We include two appendices: the first one (Appendix~\ref{airy-appendix}) contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.
+We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
+\textcolor{red}{The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.}
 %
@@
 We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' (see Figure \ref{fig:translation_surface}) at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}.
+This kind of translation surface has a ``cylindrical end'' at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}(see Figure~\ref{fig:translation_surface}).
 \begin{figure}[ht]
@@
 %%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
+\begin{equation}\label{eqn:operator-P}
+    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
+\end{equation}
 where
@@
 \color{Maroon}
-\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]
+\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
 Choose a root $-\alpha$ of $P$.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation~\eqref{eqn:standard ODE} has a unique solution $\Psi_\alpha$ in the affine subspace
+Equation
+\begin{equation}\label{eqn:standard ODE}
+    \mathcal{P}\Psi=0
+\end{equation}
+has a unique solution $\Psi_\alpha$ in the affine subspace
 \[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\textcolor{orange}{[figure out where to put definition]}. That solution is Borel regular.
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
 \end{theorem}
@@
 %\end{theorem}
+
+\color{black}
+\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
+%\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
+Given a differential operator $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
+\begin{equation}
+    \tilde{\Psi}_\alpha(z):=e^{-z\alpha}z^{-\tau_\alpha}\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket.
+\end{equation}
+Then solving order by order in $n$ it's possible to compute the coefficients of the formal series $\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}$, which will turn out to be a $1$-Gevrey series because of Ramis
+Index Theorem \cite{ramis_index}.
+When applicable, Borel summability is an effective method to produce an analytic frame of solutions from the formal Poincar\'e frame $\tilde{\Psi}_\alpha$.
+In particular, as a consequence of our result in Theorem~\ref{thm:borel_reg_ODE_proof} we deduce that the Poincar\'e frame of solutions is Borel summable (proving Corollary~\ref{cor:borel_reg_ODE}).
 \begin{theorem}\label{thm2-dim}
-%For every $j=1,...,d$ let $\psi_j(\zeta_j)$ be the unique solution of $\hat{P}_j\psi_j=0$ as in in Theorem \ref{thm1-dim}.
-Then $\psi_j(\zeta_j)$ admits a well defined Laplace transform $\Psi_j:=\laplace_{\zeta_j,-\alpha_j}^{\theta_j}$ for some direction $\theta_j$.
-For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)=e^{-\alpha z}z^{-\tau_\alpha}\sum_{n=0}^{\infty}a_{\alpha,n}z^{-n}$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$.
-Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum is proportional to $\Psi_\alpha$.
+For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket_1$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$.
+Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum $\hat{\Psi}_\alpha(z)$ is proportional to the analytic solution $\Psi_\alpha$ of Theorem~\ref{thm:borel_reg_ODE_proof}.
 \end{theorem}
 \begin{proof}
-We divide the proof into the following steps:
+We divide the proof in the following steps:
 \begin{itemize}
-\item[$(a)$] let $\series{\psi}_\alpha:=\borel_{\zeta}\series{\Psi}_\alpha$, then $\hat{P}_\alpha\series{\psi}_\alpha=0$.
-\item[$(b)$] prove that $\laplace_{\zeta,\alpha}^{\theta}\circ\borel_\zeta\series{\Psi}_\alpha\propto \Psi_\alpha $. 
+\item[$(a)$] let $\series{\psi}_\alpha:=\borel_{\zeta}\series{\Psi}_\alpha$, then $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha=0$.
+\item[$(b)$] $\tilde{\psi}_\alpha\in\C\lbrace\zeta_\alpha\rbrace$ can be analytically continued and its sum $\hat{\psi}_\alpha$ solves $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$. 
+\item[$(c)$] $\hat{\psi}_\alpha$ admits a Laplace transform $\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha=:\hat{\Psi}_\alpha$ and that $\hat{\Psi}_\alpha\propto\Psi_\alpha $. 
 \end{itemize}
-
-Step $(b)$ clearly follows from \cite[Theorem 4]{reg-sing-volterra} and step $(a)$.
-In fact, $\Tilde{\psi}_\alpha$ and ${\psi}_\alpha$ are both solutions of $\hat{P}_\alpha\psi=0$ and \textcolor{magenta}{by uniqueness}\footnote{\color{magenta} One possibility: show that a solution of a formal Volterra equation of the type we have is determined by the $z^{-\tau_\alpha}$ asymptotics somehow?
-Not enough in general.
-Another possibility: [\ldots]} they are proportional in a neighbourhood of $\alpha_j$.
-Then, we can Laplace transform ${\psi}_\alpha$ along a ray $\Gamma_{\alpha}^\theta$ in $\Omega_\alpha$.
-Hence if $\hat{\psi}_\alpha$ denotes the analytic continuation of $\tilde{\psi}_\alpha$ which agrees with $\psi_\alpha$, we can Laplace transform $\hat{\psi}_\alpha$ along $\Gamma_{\alpha}^\theta$, too.
-
-We now prove step $(a)$: we want to show that $\series{\psi}_\alpha=\borel_{\zeta}\series{\Psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha=0$.
-Recall that $\tilde{\Psi}_\alpha$ is a trans-series, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_\alpha$ is written in terms of the convolution product $\ast_{\alpha}$.
+Step $(a)$ follows from the properties of the Borel transform: recall from Section~\ref{sec:convolution-compatible} that $\tilde{\Psi}_\alpha$ is a transmonomial, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_\alpha$ is written in terms of the convolution product $\ast_{\alpha}$:
+\begin{align*}
+  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_\alpha\right)&= \left[P(-\zeta)+1\ast_{\alpha} Q(-\zeta)+\zeta \ast_{\alpha} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha}(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
+  &=\left[P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha} )(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
+  &=\hat{\mathcal{P}}_\alpha\tilde{\psi}_\alpha(\zeta_\alpha)
+\end{align*}
+Hence, the Borel transform of $\series{\Psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha$=0.
+
+To prove Step $(b)$ we'll use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$.
+First, recall that ${\psi}_\alpha$ is the uniques solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}.
+Then, as shown in Lemma~\ref{lem:picard-power}, the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$.
+Since by direct computations $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$
+\[\tilde{\psi}_\alpha=\sum_{n=0}^\infty a_{\alpha,n}\frac{\zeta_\alpha^{n+\tau_\alpha-1}}{\Gamma(n+\tau_\alpha)},\]
+our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$.
+Thus if $\hat{\psi}_\alpha$ denotes the sum of $\tilde{\psi}_\alpha$, we deduce that $\tilde{\psi}_\alpha\propto\psi_\alpha$.
+
+Finally, we can Laplace transform $\hat{\psi}_\alpha$ along a ray $\Gamma_{\alpha}^\theta$ in $\Omega_\alpha$, proving the $\tilde{\Psi}_\alpha$ is Borel summable.
+In addition, since $\tilde{\psi}_\alpha\propto\psi_\alpha$, their Laplace transform will be proportional too $\laplace_{\zeta,\alpha}^\theta\hat{\psi}_\alpha\propto \Psi_\alpha$.
+This ends the proof of Step $(c)$.
 
@@
 
-\begin{align*}
-  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_\alpha\right)&= \left[P(-\zeta)+1\ast_{\alpha} Q(-\zeta)+\zeta \ast_{\alpha} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha}(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
-  &=\left[P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha} )(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_j)\\&=\hat{P}_\alpha\tilde{\psi}_\alpha(\zeta_\alpha)
-\end{align*}
 %\begin{multline*}
@@
 
-Hence, the Borel transform of $\series{\Psi}_\alpha$ is a solution of $\hat{P}_\alpha\series{\psi}_\alpha$=0. 
 \end{proof}
@@
 %\end{proof}
-\color{violet}
-\subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
-\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
 \color{black}
@@
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}; \textcolor{pink}{in fact, we'll show that the Taylor expansion of $\iota$ near $\zeta=\alpha$ agrees with $\tilde{\iota}$.}
-
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with $\tilde{\iota}$.
 We can rewrite the Taylor series for $\nu$ as
@@
 
-\section{Facts about differential and integral equations}
+\section{Facts about differential and integral equations}\label{apx:generalities_ODEs}
 %%\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}

### 2024-02-09 exp-resurgence.tex
Brainstorm titles

@@
 \newcommand{\solptb}{f_\star}
+\newcommand{\fmlsolwhole}{\series{f}}
+\newcommand{\fmlsolproto}{\series{f}_0}
+\newcommand{\fmlsolptb}{\series{f}_\star}
 %%\newcommand{\roots}{\mathfrak{B}}
@@
 
-\title{Borel regularity for ODEs and Thimble Integrals}
+\title{Borel regularity for ODEs and Thimble Integrals \\
+\textcolor{Maroon}{Borel summation: new perspectives and examples (?)} \\
+\color{Violet}Differential equations, thimble integrals, \\
+and Borel summation as a regularization \\
+\color{Tan} Borel summation as a regularization, and \\
+the regularity of ODEs and thimble integrals \\
+\color{CornflowerBlue} Borel summation as a regularization: \\
+Borel regularity for ODEs and thimble integrals \\
+\color{LimeGreen} The regularity of ODEs and thimble integrals \\
+with respect to Borel summation}
 \author{Veronica Fantini and Aaron Fenyes}
@@
 \begin{abstract}
+\textcolor{Violet}{Through Borel summation, one can often turn a formal solution of a problem into an analytic one.
+We take the perspective that the effectiveness of Borel summation is a regularity property}
     Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
-Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
+\textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
 In addition, we give a geometric description of the Borel plane.
@@
 %%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
-\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}). \]
+\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
 
@@
 \[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
-satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
+lies in the space $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
 We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
@@
 \end{equation}
-
-The central idea of the proof is to show that $\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
-It follows, by the Banach fixed point theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
+The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
+It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
 More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
@@
 \end{proof}
+\textcolor{orange}{[We'll prove a formal analogue of Theorem~4 from \cite{reg-sing-volterra}.
+We use essentially the same technique]}, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ under \color{Tan}{the non-archimedean norm
+\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = \lambda^{-(\sigma+n)} \]
+\color{Maroon}
+the weighted $L^1$ norm \textcolor{orange}{[whoops, not defined for all formal power series]}
+\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = |c_n| \lambda^{-(\sigma+n)} + |c_{n+1}| \lambda^{-(\sigma+n+1)} + |c_{n+2}| \lambda^{\sigma+n+2} + \ldots\]
+for some $\lambda > 1$.
+\textcolor{orange}{[My hope was to use a non-archimedean norm to give a contraction mapping theorem formulation of an argument that more and more terms match, but it's hard to split up the operator in a way that makes more and more terms match\ldots]}
 \begin{lemma}\label{lem:formal-general-volterra}
@@
 \begin{proof}
+In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
+Instead of looking for an analytic solution, like we do in \cite{reg-sing-volterra}, we'll seek a formal solution $\fmlsolwhole$.
+First, we have to make sure the equation makes sense in the space of formal power series.
+Let $\series{p} = P(-\zeta)$ and $\series{q} = Q(-\zeta)$, thinking of the polynomials as formal power series, and let $\series{R}$ be the Taylor series of $R$.
+The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
+%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
+\color{magenta}
+\[ \hardpart^\alpha = -\tfrac{1}{\series{p}} \circ \partial^{-1}_{\zeta, \alpha} \circ \series{q} \]
+\color{Maroon}
+and the perturbation
+\color{magenta}
+\[ \softpart^\alpha = \tfrac{1}{\series{p}} \circ \partial^{-2}_{\zeta, \alpha} \circ \series{R}\big(\partial^{-1}_{\zeta, \alpha}\big), \]
+[have to get a contraction somehow for this to work like I imagined] \color{Maroon} which are both written here as operators on $\C\llbracket \zeta_\alpha \rrbracket$.
+
+Now, let's run through the proof of Theorem~3, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ in the ``$\lambda$-adic'' norms described above.
+For simplicity, we'll specialize the proof to the case we consider in Theorem~4.
+First, picking an arbitrary point $\zeta = \eta$ in $\Omega_\alpha$, we show that the {\em prototype solution}
+%%\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
+%%\[ \solproto = \frac{1}{\series{p}(a)} \exp\big(-\partial^{-1}_{\zeta, \eta} (\series{q}/\series{p})\big) \]
+\[ \fmlsolproto = \frac{1}{\series{p}} \left(\frac{\zeta}{\eta}\right)^{\tau_\alpha} \exp\left[-\partial^{-1}_{\zeta, \eta} \left( \frac{\series{q}}{\series{p}} + \frac{\tau_\alpha}{\zeta} \right)\right] \]
+satisfies the equation $\fmlsolproto = \hardpart^\alpha \fmlsolproto$.
+Our expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, gives a convergent power series expansion of the analytic prototype solution defined in \cite{reg-sing-volterra}.
+
+This definition of the prototype solution is taken from an intermediate step of the calculate in Section~3.2.1 \textcolor{orange}{\tt sec:construction} of \cite{reg-sing-volterra}, in which
+
+to express the prototype solution as a formal power series that satisfies the same equation.
+The definition of $\tau_\alpha$ ensures that $\series{q}/\series{p} + \tau_\alpha/\zeta$ is in $\C\llbracket \zeta_\alpha \rrbracket$, so $\fmlsolproto$ is in $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
+
+Next, we look for a perturbation $\fmlsolptb$ that makes $\fmlsolwhole = \fmlsolproto + \fmlsolptb$ a solution of the Volterra equation we're trying to solve.
+This is equivalent to solving the inhomogeneous equation
+\begin{equation}\label{eqn:inhomog-volterra2}
+\fmlsolptb = \softpart^\alpha \fmlsolproto + \volterra^\alpha \fmlsolptb
+\end{equation}
+The central idea of the proof is to show that $\softpart^\alpha$ maps $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ and that $\volterra^\alpha$ is a contraction of $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
+
+$\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
+It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
+More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
+Starting with any initial guess $\fmlsolptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
+\begin{align*}
+\fmlsolptb^{(1)} & = \volterra^\alpha \fmlsolptb^{(0)} \\
+\fmlsolptb^{(2)} & = \volterra^\alpha \fmlsolptb^{(1)} \\
+\fmlsolptb^{(3)} & = \volterra^\alpha \fmlsolptb^{(2)} \\
+& \;\;\vdots
+\end{align*}
+we get a sequence of functions that converges in $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ to a solution.
+
 \textcolor{orange}{[Argument of Loday-Richaud\ldots]}
@@
 \[\tilde{\psi}_\alpha=\sum_{n=0}^\infty a_{\alpha,n}\frac{\zeta_\alpha^{n+\tau_\alpha-1}}{\Gamma(n+\tau_\alpha)},\]
-our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$.
+our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ in their common region of convergence.
 Thus if $\hat{\psi}_\alpha$ denotes the sum of $\tilde{\psi}_\alpha$, we deduce that $\tilde{\psi}_\alpha\propto\psi_\alpha$.
@@
 In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the\textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
+The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
 \begin{lemma}\label{lem:thimble_proj_formula-proof}
@@
     \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
-    Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral:
+    Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral, and we find
     \begin{equation}\label{eqn:formula--1/2}\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
@@
 \end{remark}
-
-\color{RoyalBlue}
-The saddle point approximation\footnote{When $f$ is a polynomial see \cite{Malgrange22,pham}. More generally, if $f$ is holomorphic \textcolor{orange}{see \cite{Pham83}?}} gives the formal series 
-\begin{equation}
-{I}_{j}(z)\sim \tilde{I}_{j}\defeq e^{-z\alpha_j}(2\pi)^{1/2} z^{-1/2}\sum_{n\geq 0}a_{j,n}z^{-n} \qquad \text{ as } \Re z\to \infty. 
-\end{equation}
-%
-Then our main result states that for every $j=1,\ldots,d$, the thimble integral $I_j$ is Borel regular:
-\begin{theorem}\label{thm:maxim-dim} Let $\tilde{\Phi}_{j}(z)=z^{1/2}\,\tilde{I}_j(z)\in e^{-z\alpha_j}\C\llbracket z^{-1}\rrbracket$. Then:
-\begin{enumerate}
-\item\label{int:series-gevrey} The series $\tilde{\Phi}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-\item\label{int:resum-valid} If you continue the sum of $\tilde{\phi}_j$ along the ray going rightward from $\alpha_j$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-\item\label{int:deriv-formula} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have
-\begin{multline}\label{formula1}
-\hat{\phi}_{j}(\zeta)=\fracderiv{{3/2}}{\zeta} {\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2} \left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
-\end{multline}
-where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
-\end{enumerate}
-\end{theorem}
-
-\begin{proof}
-
-Part~\eqref{int:series-gevrey}: Let's write $\approx$ when two functions are asymptotic (at all orders around the base point \textbf{[is this the right condition?]}), and $\sim$ when a function is asymptotic to a formal power series (at the truncation order of each partial sum).
-
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a_j$ with $\tfrac{1}{2} \tau^2 = f - f(a_j)$.
-Let $\Lambda^-_j$ and $\Lambda^+_j$ be the parts of $\Lambda_j$ that go from the past to $a_j$ and from $a_j$ to the future, respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0, \infty)$ on $\Lambda^-_j$ and $\Lambda^+_j$, respectively.
-\textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
-\[ \nu = \sum_{n \ge 0} b_n^j \tau^n\,d\tau \]
-that converges in some disk $|\tau| < \varepsilon$.
-
-By the steepest descent method,
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{\textcolor{magenta}{+}z \alpha_j} I_j(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $\Re z \to \infty$ (see, for example, \cite[Proposition 2.1]{miller2006applied}---the argument through equation~(2.9)). Plugging in the Taylor series above, we get
-\begin{align*}
-e^{-z f(\alpha_j)} I_j(z) & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_n^j \tau^n\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^j \tau^{2n}\,d\tau.
-\end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
-Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
-= 1$.}
-\begin{align*}
-e^{-z f(\alpha_j)} I_j(z) & \approx \sum_{n \ge 0} b_{2n}^j \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
-\end{align*}
-
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha_j} I_j(z)$.
-In other words,
-\[ e^{-z \alpha_j} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^j\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-To see why, cut the sum off after $N$ terms, and observe that
-\begin{align*}
-  \Bigg | \sum_{n= 0}^N(2n-1)!!
-b_{2n}^j  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
-b_{2n}^j n|z|^{-n}.
-\end{align*}
-The right-hand side goes to $0$ as $\Re(z)$ grows.
-%Hence,
-%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{-z\alpha_j)} I_j(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^j \,z^{-(n+1/2)}. \]
-
-Call the right-hand side $\tilde{I}_j$. We now see that $a_{j,n} = (2n-1)!!\,b_{2n}^j$ in the statement of the theorem. %\textbf{[Resolve discrepancy with previous calculation.]}
-
-Note that 
-\begin{align*}
-\borel_{\zeta} \tilde{I}_j & = \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \Gamma\big(n+\tfrac{1}{2}\big)\,b_{2n}^j\,\frac{\zeta_j^{n-1/2}}{\Gamma\big(n+\tfrac{1}{2}\big)} \\
-& = \sum_{n \ge 0} 2^{n+1/2}\,b_{2n}^j \,\zeta_j^{n-1/2}.
-\end{align*}
-
-We know from the definition of $\varepsilon$ that $\left|b_n^j\right| \varepsilon^n \lesssim 1$.
-Recalling that $(2n - 1)!!
-\approx (\pi n)^{-1/2}\,2^n\,n!$ as $n \to \infty$, we deduce that $|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
-
-Part~\eqref{int:resum-valid}: Let us recast the integral $I_j$ into the $f$ plane.
-As $\zeta$ goes rightward from $\alpha_j$, the start and end points of $\Lambda_j(\zeta)$ sweep backward along $\Lambda^-_j(\zeta)$ and forward along $\Lambda^+_j(\zeta)$, respectively.
-Hence, we have
-\begin{align*}
-I_j(z) & = \int_{\Lambda_j} e^{-zf} \nu \\
-& = \int_{\alpha_j}^\infty e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}\,d\zeta.
-\end{align*}
-Noticing that the right-hand side is a Laplace transform, we learn that
-\begin{equation}\label{thimble-difference}
-\hat{\iota}_j(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)}.
-\end{equation}
-%\color{Aquamarine}
-%In \'Ecalle's formalism, $\frac{\nu}{df}$ and $\hat{\iota}_j$ are a major and a minor of the singularity $\overset{\triangledown}{I}_\alpha$.
-[Can we say: $\frac{\nu}{df}$ is a major representing the singularity $\overset{\triangledown}{I}_\alpha$?
-Or something even simpler?]
-%\color{black}
-
-We can rewrite our Taylor series for $\nu$ as
-\begin{align*}
-\nu & = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{n/2}\,\frac{df}{[2(f - f(a_j))]^{1/2}} \\
-& = \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2}\,df,
-\end{align*}
-taking the positive branch of the square root on $\Lambda^+_j$ and the negative branch on $\Lambda^-_j$. Plugging this into our expression for $\hat{\iota}_j$, we learn that
-\begin{align*}
-\hat{\iota}_j(\zeta) & = \left[ \sum_{n \ge 0} b_n^j [2(f - f(a_j))]^{(n - 1)/2} \right]_{\operatorname{start} \Lambda_j(\zeta)}^{\operatorname{end} \Lambda_j(\zeta)} \\
-& = \sum_{n \ge 0} b_n^j \Big( [2\zeta_j]^{(n - 1)/2} - (-1)^{n-1}[2\zeta_j]^{(n - 1)/2} \Big) \\
-& = \sum_{n \ge 0} 2 b_{2n}^j [2\zeta_j]^{n - 1/2} \\
-& = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \\
-& = \borel_{\zeta} \tilde{I}_j.
-\end{align*}
-
-We have now shown that the sum of $\borel_{\zeta} \tilde{I}_j$ is actually equal to $\hat{\iota}_j$.
-
-%Let $\tilde{\Phi}_j\in\C[\![z^{-1}]\!]$ be such that $\tilde{I}_j(z)=e^{-z\alpha_j}z^{-1/2}\tilde{\Phi}_j(z)$,  
-By the action of $\borel_\zeta$ on transseries (Section \ref{sec:action_transseries}) and the properties of convolution (Section \ref{convolution}) we know 
-\begin{align*}
-\borel_{\zeta} \tilde{I}_j & = \borel_{\zeta}( z^{-1/2} \tilde{\Phi}_j) \\
-&=\borel_\zeta z^{-1/2}\ast_{\alpha_j}\borel_\zeta\tilde{\Phi}_j\\
-& = \fracderiv{-1/2}{\zeta}{\alpha_j}  \tilde{\phi}_j \\
-%& = \partial^{-1/2}_{\zeta \text{ from } \zeta_\alpha} \hat{\varphi}_\alpha.
-\end{align*}
-It follows, from our conclusion above, that
-\begin{equation}\label{shifted-resum-valid}
-\hat{\iota}_j(\zeta) = \fracderiv{-1/2}{\zeta}{\alpha_j} \hat{\phi}_j.
-\end{equation}
-Taking the Laplace transform of both sides and applying properties of the Borel transform (see Proposition~\ref{prop:frac-der-int-borel}), we see that
-\begin{align*}
-I_j(z) & = \laplace_{\zeta, \alpha_j} \left[ \partial^{-1/2}_{\zeta, \alpha_j}  \hat{\phi}_j \right] \\
-& = z^{-1/2} \laplace_{\zeta, \alpha_j} \tilde{\phi}_j,
-\end{align*}
-as we claimed.
-
-Part~\eqref{int:deriv-formula}: Since fractional integrals form a semigroup, equation~\eqref{shifted-resum-valid} implies that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j. \]
-
-Rewriting equation~\eqref{thimble-difference} as
-\[ \hat{\iota}_j(\zeta) = \partial_\zeta \left( \int_{\Lambda_j(\zeta)} \nu \right), \]
-we can see that
-\[ \fracderiv{-1}{\zeta}{\alpha_j} \hat{\iota}_j(\zeta) = \int_{\Lambda_j(\zeta)} \nu - \int_{\Lambda_j(\alpha_j)} \nu. \]
-The initial value term vanishes because the path $\alpha_j$ is a point. Hence,
-\[ \int_{\Lambda_j(\zeta)} \nu = \fracderiv{-3/2}{\zeta}{\alpha_j} \hat{\phi}_j(\zeta). \]
-Recalling that the Riemann-Liouville fractional derivative is a left inverse of the fractional integral, we conclude that
-\[ \fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)} \nu \right) = \hat{\phi}_j(\zeta). \]
-\end{proof}
-\color{black}
 \begin{remark}
-We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[\textcolor{orange}{section?}]{EcalleI}.
+We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
 Let's say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
@@
 Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
-The jump is then given by $\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu$ which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
-We'll see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
+The jump is then given by \[\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu\]
+and it is 
+which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$. We'll see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
 
@@
 \end{remark}
-\color{DarkSeaGreen}
-\begin{remark}
-    The $3/2$ derivative formula~\eqref{formula1} allows us to compute the sum of the germ $\series{\phi}_j$, hence it is enough to use it to study the location of singularities in the position domain and its growth behavior at infinity\footnote{For instance in \cite{sauzin2021variations}, the analogous of formula~\eqref{formula1} is used to compute a close formula for the Borel sum of the Stirling approximation of the Gamma function.}.
-Furthermore, expanding $\hat{\phi}_j$ at its critical points, we recover the germs $\series{\phi}_k$ for $k\neq j$.
-This is an instance of resurgence, indeed according to the theory of \'{E}calle, $\hat{\phi}_j$ are all resurgent functions.
-We'll see an example in Appendix~\ref{apx:eye-res-airy}.
-\end{remark}
-\color{black}
 \textcolor{orange}{
 \begin{corollary}\label{simple-res-thimble}
-    If $f$ and $\nu$ are polynomials, the function $\hat{\phi}_j$ defined in \eqref{formula1} has simple resurgent singularities at $\zeta=\alpha_k$.  
+    If $f$ and $\nu$ are polynomials, the function ${\phi}=\fracderiv{-1/2}{\zeta}{\alpha}\iota$ defined in Remark~\ref{rmk:1/2-deriv} has simple resurgent singularities at $\zeta=\beta$, for all $\beta$ roots of $P$ such that $\beta\neq\alpha$.
 \end{corollary}
 \begin{proof}
-    Recall $\hat{\iota}_j$ is the sum of the Borel transform of $z^{1/2}\tilde{I}_j$, namely 
-    \[\hat{\iota}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
+    Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\tilde{I}_j$, namely 
+    \[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
     Then by Pham's result (see \eqref{rmk:Pham formula}) we know 
@@
    \end{equation*}
-In particular, if $N=1$, as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.
+In particular, if $N=1$, the inverse Laplace transform of $I$ has a fractional power singularity of order $1/2$ at the origin, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
+%as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.
 \textcolor{magenta}{We expect this result to hold beyond the polynomial case.} We also expect that equation \eqref{eqn:formula-proof} can be generalized to the $N$-dimensional case replacing the $1/2$-derivative with the $N/2$ one.

### 2024-02-09 exp-resurgence.tex
Write second draft of abstract

@@
 
-\title{Borel regularity for ODEs and Thimble Integrals \\
-\textcolor{Maroon}{Borel summation: new perspectives and examples (?)} \\
-\color{Violet}Differential equations, thimble integrals, \\
-and Borel summation as a regularization \\
-\color{Tan} Borel summation as a regularization, and \\
-the regularity of ODEs and thimble integrals \\
-\color{CornflowerBlue} Borel summation as a regularization: \\
-Borel regularity for ODEs and thimble integrals \\
-\color{LimeGreen} The regularity of ODEs and thimble integrals \\
+\title{The regularity of ODEs and thimble integrals \\
 with respect to Borel summation}
+%%\color{Tan} Borel summation as a regularization, and \\
+%%the regularity of ODEs and thimble integrals \\
+%%\color{CornflowerBlue} Borel summation as a regularization: \\
+%%Borel regularity for ODEs and thimble integrals \\
+%%Borel regularity for ODEs and Thimble Integrals
+%%\textcolor{Maroon}{Borel summation: new perspectives and examples (?)} \\
+%% \color{Violet}Differential equations, thimble integrals, \\
+%%and Borel summation as a regularization
 \author{Veronica Fantini and Aaron Fenyes}
@@
 \begin{abstract}
-\textcolor{Violet}{Through Borel summation, one can often turn a formal solution of a problem into an analytic one.
-We take the perspective that the effectiveness of Borel summation is a regularity property}
+Through Borel summation, one can often reconstruct an analytic solution of a problem from its asymptotic expansion.
+%%can often turn a formal solution of a problem into an analytic one.
+We view the effectiveness of Borel summation as a regularity property of the solution, and we show that the solutions of certain differential equation and integration problems are regular in this sense.
+By taking a geometric perspective on the Laplace and Borel transforms, we also clarify why ``Borel regular'' solutions are associated with special points on the Borel plane.
+
+The particular classes of problems we look at are level~1 ODEs and exponential period integrals over Lefschetz thimbles.
+To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
+
+\textcolor{RoyalBlue}{
 Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
 \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
-In addition, we give a geometric description of the Borel plane.
+In addition, we give a geometric description of the Borel plane.}
 \end{abstract}

### 2024-02-12 exp-resurgence.tex
Sync before flight

@@
 \begin{equation}\label{series:asymp-defn}
-\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
+\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
 \end{equation}
 is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{z \to \infty}\big(|z|^{-n}\big) \]
+\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(|z|^{-n}\big) \]
 over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
 \end{defn}
+\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we'll say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if
+\[\left|F - e^{\lambda z}z^{\tau}\left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(e^{\lambda\Re(z)}|z|^{\tau-n}\big).\]}
 If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
@@
 \begin{enumerate}
-\item Solving a linear ODE of single level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-One example is Equation~\eqref{eqn:bessel-rescaled-1}, and we will cosndier equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
+\item Solving a single-level linear ODE, with level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii} \textcolor{orange}{[awkward?]}.
+Equation~\eqref{eqn:bessel-rescaled-1} is an example.
+More generally, we'll consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
@@
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-In this case, for any $\Lambda \in \R$, let \textcolor{magenta}{$\widehat{\Omega}_\alpha^\Lambda$} $\dualsector{\alpha}{\Lambda}$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
-Then, let $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
+Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
 The norm $\|F\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |F|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
@@
 Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
-\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \]
+\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
 has a continuous left inverse
-\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
 with a norm of at most
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-\subsubsection{Proof of main results}
+\textcolor{orange}{[Explain the contents of the section]}
+\subsubsection{Regularity results}
 Let's recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
@@
 \begin{enumerate}
-\item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
-\item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
+\item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
+\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
+\item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
 \[ R(z^{-1}) = \sum_{j=0}^\infty R_j z^{-j} \]
@@
 %%%\end{itemize}
-
-\begin{figure}
-\center
-\begin{tikzpicture}
-\newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
-  (-\spill, -\spill) (\spill, \spill)
-  (0, 0) -- (160:\spill)
-  arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
-  arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
-  arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
-  arc (-60:-130:\spill) -- (0, 0);
-\fill[violet] circle (0.7mm) node[anchor=195, outer sep=1mm] {$\zeta = \alpha$};
-\node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
-\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill \p circle (0.7mm);
-}
-\end{tikzpicture}
-\caption{The domain $\Omega_\alpha$ \textcolor{orange}{[Revise to show asector]}}\label{Fig:domain}
-\end{figure}
 \color{Maroon}
@@
 \[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}
+\begin{proof}
+%Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}.
+Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}.
+Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.
+%
+As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
+The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
+It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
+\end{proof}
+\begin{theorem}
+That solution $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} is Borel regular.
+\end{theorem}
+\color{Violet}
+\begin{proof}
+    \begin{itemize}
+        \item the asymptotitics of $\Psi_\alpha$ \textcolor{LimeGreen}{[exist and]} are $1$-Gevrey
+        \item \textcolor{LimeGreen}{The solution $\Psi_\alpha$ has an asymptotic expansion} indeed it's the Laplace transform of $\psi_\alpha$, thus if we consider the Taylor expansion of $\psi_\alpha$ at $\zeta=\alpha$ and then we integrate term by term we can compute the asymptotic.
+Notice that Poincar\'e asymptotic doesn't have to be to a power series, but it can be mor generally to a trans-monomial.
+I think we should state the definition for trans-monomials.
+        \begin{align}
+            \Psi_\alpha&=\int_\alpha^\infty e^{-z\zeta} \sum_{n=0}^\infty a_n (\zeta-\eta)^n d\zeta \\
+            & = \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z\zeta}   (\zeta-\eta)^n d\zeta+\int_\alpha^\infty e^{-z\zeta} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta \\
+            & = e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta + e^{-z\eta} \int_\alpha^\infty e^{-z(\zeta - \eta)} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta
+        \end{align}
+        \begin{multline*}
+            \left|\Psi_\alpha- e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta\right|\leq e^{-\Re(z)|\eta|} \int_\alpha^R |e^{-z(\zeta - \eta)} |\sum_{n=N+1}^\infty R^{-n} |(\zeta-\eta)|^n d\zeta +\\
+            e^{-\Re(z)|\eta|} \int_R^\infty |e^{-z(\zeta - \eta)} | |\psi_\alpha| d\zeta \qquad\text{[use that $\psi_\alpha$ is exponentially bounded]}
+        \end{multline*}
+       \[\Psi_\alpha=\lim_{b \to (\zeta = \alpha)}\int_b^\infty e^{-z\zeta} f\;d\zeta \]
+       \item Say $\left|\Psi_\alpha - \int_b^{\infty}\right| \leq \epsilon$ over all $z$. Then $|z|^n\;\left|\Psi_\alpha - \int_b^{\infty}\right| \leq |z|^n \epsilon$
+       \item \begin{align*}
+       \int_\alpha^\infty e^{-z\zeta} |z|^n |\psi_\alpha-\text{poly}(\zeta)| d\zeta \\
+       \int_\alpha^\infty \left[\left(\tfrac{\partial}{\partial \zeta}\right)^n e^{-z\zeta}\right] |\psi_\alpha-\text{poly}(\zeta)| d\zeta
+       \end{align*}
+       \item Need $\lim_{z \to \infty} z^n |\Psi_\alpha - \text{poly}|$ for all $n \in \Z_{\ge 0}$
+        \item $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha}\C\lbrace\zeta_\alpha\rbrace$ and solves $\hat{\mathcal{P}}_\alpha\phi=0$
+        \item Integral looks like
+        \begin{align*}
+        \int_0^\infty e^{-z\zeta} f\;d\zeta & = \int_0^r e^{-z\zeta} f\;d\zeta + \int_r^\infty e^{-z\zeta} f\;d\zeta \\
+        & \text{``}\approx\text{''} \int_0^r e^{-z\zeta} f\;d\zeta + e^{-z \Re(\zeta)} \|f\|_1 \\
+        & \text{``}\approx\text{''} \|f\|_1 + e^{-zr} \|f\|_1
+        \end{align*}
+        \item $\hat{\mathcal{P}}_\alpha\phi=0$ admits a unique formal solution
+        \item  $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ \textcolor{LimeGreen}{[which exists]}
+    \end{itemize}
+\end{proof}
+\color{Maroon}
+\begin{figure}[h]
+\center
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=radial edge]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
+  %arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
+  %arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
+  %arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
+  %arc (-60:-130:\spill) -- (0, 0);
+  %%arc (46:-51:\spill) -- (-51:2.5) .. controls (-51:6.4) and (-55.8:6.4) .. (-55.8:-1) -- (-55.8:\spill);
+ %arc (-59:-57:\spill)--(0, 0);
+\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
+%%\node[anchor=south east, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
+\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+  \fill \p circle (0.7mm);
+  %\draw[dashed,violet!50] \p -- (0,0);
+}
+\end{tikzpicture}
+\caption{The domain $\Omega_\alpha$}\label{Fig:domain}
+\end{figure}
 The key to our proof is recasting Equation~\eqref{eqn:standard ODE} as an integral equation in the position domain.

### 2024-02-24 exp-resurgence.tex
Verify equation for triangular cantilever

@@
 \begin{theorem}
-That solution $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} is Borel regular.
+\textcolor{Turquoise}{Assuming $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} admits an asymptotic expansion as $\Re z\to e^{i\theta}\infty$ along some rays contained in the sector $\Omega_\alpha$, then $\Psi_\alpha$ is Borel regular.} That solution $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} is Borel regular.
 \end{theorem}
+\begin{proof}
+\color{Turquoise}
+If $\Psi_\alpha$ admits an asymptotic expansion $\tilde{\Psi}_\alpha$, then $\Psi_\alpha$ is a formal solution of Equation~\eqref{eqn:operator-P}, thus by Ramis Index Theorem is $1$-Gevrey.
+The Borel transform of $\tilde{\Psi}_\alpha$ is a germ of convergent power series, and by the properties of the Borel transform, it's a formal solution of $\hat{\mathcal{P}}_\alpha \phi=0$.
+\textcolor{red}{[check the exponential term $e^{-z\alpha}$, otherwise get different points]}
 \color{Violet}
-\begin{proof}
     \begin{itemize}
@@
 \subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
 We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
@@
 \end{remark}
-\subsection{The triangular catilever}\label{sec:catilever}
+\subsection{The triangular cantilever}\label{sec:catilever}
+%% genta2009vibration
 The equation of a triangular cantilever with \textcolor{orange}{[...]} $\mu\in\R\setminus\{0\}$ is 
 \begin{equation}\label{eqn:triangular_cantilever}
-    \Big[\big[\Big(\frac{\partial}{\partial z}\Big)^4 +\mu\big]+\frac{2}{z}\Big(\frac{\partial}{\partial z}\Big)^3\Big]\varphi=0 .
-\end{equation}
-Going to the position domain we can solve the equation explicitly: let $\alpha_1,\ldots,\alpha_4$ be the solutions of $\lambda^4+\mu=0$; we'll look for solutions $v_j$ whose Laplace transform $\laplace_{\zeta,\alpha_j}v_j$ satisfies the equation \eqref{eqn:triangular_cantilever}.
-For $j=1,\ldots,4$, $v_j$ solves
+    \left[\big[\big(\tfrac{\partial}{\partial z}\big)^4 +\mu\big] + \tfrac{2}{z}\big(\tfrac{\partial}{\partial z}\big)^3\right] \Phi = 0.
+\end{equation}
+\begin{verify}
+The vertical displacement of a vibrating beam is annihilated by the operator
+\[ \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 + m \big(\tfrac{\partial}{\partial t}\big)^2, \]
+as described in equation~12.58 of \cite{genta2009vibration}.
+Here, $m$ is the mass per unit length, $E$ is the elastic modulus, and $I_\text{roll}$ is the second moment of area about the axis the beam ``rolls'' around as it vibrates.
+We can write the displacement as $\cos(\omega t)$ times a time-independent envelope, which is annihilated by the operator
+\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
+We're assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length isproportional to $st$, giving
+\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
+For the triangular cantilever, $t$ is constant, and $s$ is proportional to $z$. Since the constant of proportionality only affects the equation by scaling it, we can assume it's one, so we have
+\begin{align*}
+\mathcal{P} & = \big(\tfrac{\partial}{\partial z}\big)^2 \circ c_1 z \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 \tfrac{\partial}{\partial z} \circ \big[ 1 + z \tfrac{\partial}{\partial z} \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 \circ \big[ \tfrac{\partial}{\partial z} + \tfrac{\partial}{\partial z} + z \big(\tfrac{\partial}{\partial z}\big)^2 \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 2\big(\tfrac{\partial}{\partial z}\big)^3 + c_1 z \big(\tfrac{\partial}{\partial z}\big)^4 - c_2 z \\
+\tfrac{1}{c_1 z} \mathcal{P} & = \tfrac{2}{z} \big(\tfrac{\partial}{\partial z}\big)^3 + \big(\tfrac{\partial}{\partial z}\big)^4 - \tfrac{c_2}{c_1}.
+\end{align*}
+Now, set $\mu = \tfrac{c_2}{c_1} = \tfrac{3}{4} \tfrac{1}{E} \big(\tfrac{\omega}{t}\big)^2$.
+
+[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
+This example works because the linear density of the beam and the second moment of area perpemdicular to the vibration direction are proportional, so they both end up in the $P(\partial)$ term.]\end{verify}
+\color{Tan}
+\begin{equation}\label{eqn:mod-bessel-AL}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
+\end{equation}
+\color{black}
+We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:triangular_cantilever}.
+\textcolor{RoyalBlue}{Going to the position domain we can solve the equation explicitly: let $\alpha_1,\ldots,\alpha_4$ be the solutions of $\lambda^4+\mu=0$; we'll look for solutions $v_j$ whose Laplace transform $\laplace_{\zeta,\alpha_j}v_j$ satisfies the equation \eqref{eqn:triangular_cantilever}.
+For $j=1,\ldots,4$, $v_j$ solves}
 \begin{equation}\label{eqn:position_j}
-    \Big[\big[\zeta^4+\mu\big]+2\fracderiv{-1}{\zeta}{\alpha_j}\circ(-\zeta)^3\Big] v_j=0
-\end{equation}
+    \left[ \big[ \zeta^4 + \mu \big] + 2\fracderiv{-1}{\zeta}{\alpha} \circ (-\zeta)^3 \right] v_\alpha = 0
+\end{equation}
+\color{Tan}
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel-AL}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+\color{black}
 As we'll show in Section \ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 

### 2024-02-27 exp-resurgence.tex
Revise triangular cantilever example

--- 2024-02-12 exp-resurgence.tex
@@
 \end{remark}
-\subsection{The triangular catilever}\label{sec:catilever}
-The equation of a triangular cantilever with \textcolor{orange}{[...]} $\mu\in\R\setminus\{0\}$ is 
+\subsection{The triangular cantilever}\label{sec:catilever}
+A {\em triangular cantilever} is a flexible strip with constant thickness and linearly tapered width, clamped at the broad end so it sticks out horizontally like a diving board.
+\begin{center}
+\begin{tikzpicture}
+\fill[black!10] (0, 0.1, 0) -- (6, 0.1, -1) -- (6, -0.1, -1) -- (6, -0.1, 1) -- (0, -0.1, 0);
+\draw (0, -0.1, 0) -- (6, -0.1, 1) -- (6, -0.1, -1);
+\draw[black!50] (0, 0, 0) -- (6, 0, 0);
+\draw[->] (6, 0, 0) -- (7, 0, 0) node[anchor=west] {$z$};
+\draw (0, 0.1, 0) -- (6, 0.1, 1) -- (6, 0.1, -1) -- cycle;
+\foreach \x / \y in {0 / 0, 6 / 1, 6 / -1} {
+  \draw (\x, 0.1, \y) -- (\x, -0.1, \y);
+}
+\end{tikzpicture}
+\end{center}
+If you strike the strip from above, it vibrates up and down.
+Let's suppose the vibrations are small, and uniform across the width of the strip, so we can describe them using the Euler--Bernoulli beam model~\cite[\S 12.4]{genta2009vibration}.
+The vibration modes of frequency $\omega$ are described by the vertical displacement profiles $\Phi$ that satisfy the equation
 \begin{equation}\label{eqn:triangular_cantilever}
-    \Big[\big[\Big(\frac{\partial}{\partial z}\Big)^4 +\mu\big]+\frac{2}{z}\Big(\frac{\partial}{\partial z}\Big)^3\Big]\varphi=0 .
-\end{equation}
-Going to the position domain we can solve the equation explicitly: let $\alpha_1,\ldots,\alpha_4$ be the solutions of $\lambda^4+\mu=0$; we'll look for solutions $v_j$ whose Laplace transform $\laplace_{\zeta,\alpha_j}v_j$ satisfies the equation \eqref{eqn:triangular_cantilever}.
-For $j=1,\ldots,4$, $v_j$ solves
-\begin{equation}\label{eqn:position_j}
-    \Big[\big[\zeta^4+\mu\big]+2\fracderiv{-1}{\zeta}{\alpha_j}\circ(-\zeta)^3\Big] v_j=0
-\end{equation}
+    \left[\big[\big(\tfrac{\partial}{\partial z}\big)^4 - \omega^2\big] + \tfrac{2}{z}\big(\tfrac{\partial}{\partial z}\big)^3\right] \Phi = 0,
+\end{equation}
+where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, we've adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
+
+\begin{verify}
+The vertical displacement of a vibrating beam is annihilated by the operator
+\[ \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 + m \big(\tfrac{\partial}{\partial t}\big)^2, \]
+as described in equation~12.58 of \cite{genta2009vibration}.
+Here, $m$ is the mass per unit length, $E$ is the elastic modulus, and $I_\text{roll}$ is the second moment of area about the axis the beam ``rolls'' around as it vibrates.
+We can write the displacement as $\cos(\omega t)$ times a time-independent envelope, which is annihilated by the operator
+\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
+We're assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length isproportional to $st$, giving
+\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
+For the triangular cantilever, $t$ is constant, and $s = \sigma z$ for some constant $\sigma$. Letting $c_1 = \tfrac{4}{3}\sigma Et^3$ and $c_2 = t\sigma\omega^2$, we have
+\begin{align*}
+\mathcal{P} & = \big(\tfrac{\partial}{\partial z}\big)^2 \circ c_1 z \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 \tfrac{\partial}{\partial z} \circ \big[ 1 + z \tfrac{\partial}{\partial z} \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 \circ \big[ \tfrac{\partial}{\partial z} + \tfrac{\partial}{\partial z} + z \big(\tfrac{\partial}{\partial z}\big)^2 \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
+& = c_1 2\big(\tfrac{\partial}{\partial z}\big)^3 + c_1 z \big(\tfrac{\partial}{\partial z}\big)^4 - c_2 z \\
+\tfrac{1}{c_1 z} \mathcal{P} & = \tfrac{2}{z} \big(\tfrac{\partial}{\partial z}\big)^3 + \big(\tfrac{\partial}{\partial z}\big)^4 - \tfrac{c_2}{c_1}.
+\end{align*}
+Now, set $\mu = \tfrac{c_2}{c_1} = \tfrac{3}{4} \tfrac{1}{E} \big(\tfrac{\omega}{t}\big)^2$.
+This example works because the linear density of the beam and the second moment of area about the side-to-side axis are proportional, so they both end up in the $P(\partial/\partial z)$ term.\par
+\end{verify}
+\color{black}
+We're going to look for functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
+We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies equation~\eqref{eqn:triangular_cantilever} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{eqn:position_cantilever}
+    \left[ \big[ \zeta^4 - \omega^2 \big] - 2\fracderiv{-1}{\zeta}{\alpha} \circ \zeta^3 \right] v = 0.
+\end{equation}
+Observing that
+\[ \tfrac{\partial}{\partial \zeta}\,(\zeta^4 - \omega^2)^{1/2} = 2\zeta^3\,(\zeta^4 - \omega^2)^{-1/2}, \]
+we learn that $v_\text{uni} = (\zeta^4 - \omega^2)^{-1/2}$ satisfies equation~\eqref{eqn:position_cantilever} whenever $\alpha^4 - \omega = 0$.
+Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}.
+\par\color{RoyalBlue}
 As we'll show in Section \ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 
@@
 \[v_j \propto \frac{1}{\zeta_j^{1/2}}\, \prod_{k\neq j}(\zeta_j-\alpha_k+\alpha_j)^{-1/2}.\]
+\color{black}
 \textcolor{orange}{[Stokes? Thimbles?]}

### 2024-02-28 exp-resurgence.tex
Sync before seminar

@@
 The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
-It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
+It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
 More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
@@
 \begin{align*}
-\solptb^{(1)} & = \volterra^\alpha \solptb^{(0)} \\
-\solptb^{(2)} & = \volterra^\alpha \solptb^{(1)} \\
-\solptb^{(3)} & = \volterra^\alpha \solptb^{(2)} \\
+\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
+\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
+\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
 & \;\;\vdots
@@
 \begin{tikzpicture}
-\fill[black!10] (0, 0.1, 0) -- (6, 0.1, -1) -- (6, -0.1, -1) -- (6, -0.1, 1) -- (0, -0.1, 0);
-\draw (0, -0.1, 0) -- (6, -0.1, 1) -- (6, -0.1, -1);
-\draw[black!50] (0, 0, 0) -- (6, 0, 0);
-\draw[->] (6, 0, 0) -- (7, 0, 0) node[anchor=west] {$z$};
-\draw (0, 0.1, 0) -- (6, 0.1, 1) -- (6, 0.1, -1) -- cycle;
+\newcommand{\clen}{6}
+\newcommand{\ctaper}{1}
+\newcommand{\cthic}{0.1}
+\fill[black!10] (0, \cthic, 0) -- ++(6, 0, -\ctaper) -- ++(0, -2*\cthic, 0) -- ++(0, 0, 2*\ctaper) -- (0, -\cthic, 0);
+\draw (0, -\cthic, 0) -- ++(\clen, 0, \ctaper) -- ++(0, 0, -2*\ctaper);
+\draw[black!50] (0, 0, 0) -- ++(\clen, 0, 0);
+\draw[->] (\clen, 0, 0) -- ++(1, 0, 0) node[anchor=west] {$z$};
+\draw (0, \cthic, 0) -- ++(\clen, 0, \ctaper) -- ++(0, 0, -2*\ctaper) -- cycle;
 \foreach \x / \y in {0 / 0, 6 / 1, 6 / -1} {
@@
 Observing that
-\[ \tfrac{\partial}{\partial \zeta}\,(\zeta^4 - \omega^2)^{1/2} = 2\zeta^3\,(\zeta^4 - \omega^2)^{-1/2}, \]
-we learn that $v_\text{uni} = (\zeta^4 - \omega^2)^{-1/2}$ satisfies equation~\eqref{eqn:position_cantilever} whenever $\alpha^4 - \omega = 0$.
-Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}.
+\[ \tfrac{\partial}{\partial \zeta} \sqrt{\zeta^4 - \omega^2} = \frac{2\zeta^3}{\sqrt{\zeta^4 - \omega^2}}, \]
+we learn that
+\[ v_\text{uni} = \frac{1}{\sqrt{\zeta^4 - \omega^2}} \]
+satisfies equation~\eqref{eqn:position_cantilever} whenever $\alpha^4 - \omega = 0$.
+Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}, indexed by the fourth roots of $\omega^2$.
 \par\color{RoyalBlue}

### 2024-03-04 exp-resurgence.tex
Argue that special ODE solutions have asymptotic expansions

@@
 %%\newcommand{\roots}{\mathfrak{B}}
+\DeclareMathOperator{\hol}{hol}
 
@@
 %We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
+\color{BlueViolet}
+\begin{theorem}\label{thm:exist_uniq_ODE}
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
+\end{theorem}
+\begin{theorem}\label{thm:has_ae_ODE}
+The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+In fact, up to scaling, it's asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
+\end{theorem}
+Combining our uniqueness and regularity results for $\psi_\alpha$ with uniqueness and regularity results for the Poincar\'{e} solutions, we can show that $\Psi_\alpha$ is Borel regular.
+\begin{corollary}
+The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
+\end{corollary}
+\color{black}
 \color{Maroon}
@@
 %%%\end{itemize}
+\color{BlueViolet}
+\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
+\end{theorem}
+\begin{proof}
+After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
+The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
+It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
+\end{proof}
+\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
+Let's use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
+\begin{lemma}\label{lem:shifted_holo_closed}
+Choose a root $-\alpha$ of $P$.
+Consider a simply connected open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ which touches but doesn't contain $\zeta = \alpha$, is star-shaped around $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
+Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it's two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it's one-to-one everywhere else.
+\begin{center}
+\begin{tikzpicture}
+  \newcommand{\spill}{4}
+  \fill[violet!20, bezier bounding box, path fading=radial edge]
+    (-\spill, -\spill) (\spill, \spill)
+    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
+  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
+  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
+  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
+  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+    \fill \p circle (0.7mm);
+  }
+\end{tikzpicture}
+\end{center}
+For any real numbers $\sigma$, $\Lambda$ and any $\delta \in [0, 1)$, the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
+\end{lemma}
+\begin{proof}
+Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
+The operator $\hol \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$ defined by
+\[ \hol \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
+is bounded.
+The intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\Upsilon_\Delta)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\hol - e^{2\pi i \delta}$, so it's closed.
+\end{proof}
+\begin{theorem}[restatement of \ref{thm:has_ae_ODE}]
+The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+In fact, up to scaling, it's asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
+\end{theorem}
+\begin{proof}
+Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4.
+To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we'll show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+
+%%The key step of our proof will be to show that $\psi_\alpha$ lies in
+
+%%The uniqueness part of the Theorem~4 ensures that restricting $\psi_\alpha$ to $\Omega_\alpha$ gives the analogous solution used in the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}.
+
+%%%In the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, we used Theorem~4 of \cite{reg-sing-volterra} to show that the equation $\mathcal
+
+%%%$\psi_\alpha$ in the affine subspace
+%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$
+
+For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
+The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
+%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
+\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
+and the perturbation
+%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
+\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
+\color{SlateBlue}
+\begin{itemize}
+\item Prove Theorem~3 using Picard iteration, using the {\em prototype solution}
+\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
+given by an arbitary point $b \in \Omega_\alpha$ as our initial guess.
+\item This expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, makes it clear that the prototype solution belongs to $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+\item The operator $\volterra^\alpha$ preserves the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$.
+Hence, the Picard iteration sequence must lie in this subspace.
+\item We know from Lemma~\ref{lem:shifted_holo_closed} that the intersection of $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
+Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
+\item Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
+\end{itemize}
+\color{BlueViolet}
+
+%%Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that
+
+%%Picking an arbitrary point $b \in \Omega_\alpha$, we observe that the {\em prototype solution}
+%%\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right] \]
+
+%% \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]
+
+%%Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the subspace
+
+%%The restriction map $\singexp{\sigma}{\Lambda}(\Upsilon) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega_\alpha)$ \textcolor{orange}{\ldots}
+\end{proof}
+\color{black}
 \color{Maroon}
@@
   (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
-  %arc (160:112:\spill) -- (112:2) .. controls (112:1.7) and (103:1.7) .. (103:2) -- (103:\spill)
-  %arc (103:50:\spill) -- (50:2.6) .. controls (50:2.2) and (43:2.2) .. (43:2.6) -- (43:\spill)
-  %arc (43:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-60:2) .. (-60:2.3) -- (-60:\spill)
-  %arc (-60:-130:\spill) -- (0, 0);
-  %%arc (46:-51:\spill) -- (-51:2.5) .. controls (-51:6.4) and (-55.8:6.4) .. (-55.8:-1) -- (-55.8:\spill);
- %arc (-59:-57:\spill)--(0, 0);
 \fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
-%%\node[anchor=south east, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
 \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
   \fill \p circle (0.7mm);
-  %\draw[dashed,violet!50] \p -- (0,0);
 }

### 2024-03-11 exp-resurgence.tex
Keep arguing that special solutions have asymptotic expansions

@@
 \end{proof}
-\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
+\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
 Let's use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
@@
 \[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
+
+Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
+lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
+We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
+This is equivalent to solving the inhomogeneous equation
+\begin{equation}\label{eqn:inhomog-volterra}
+\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
+\end{equation}
+The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
+It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
+Defining
+\begin{align*}
+\solptb^{(0)} & = \softpart^\alpha \solproto \\
+\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
+\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
+\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
+& \;\;\vdots
+\end{align*}
+we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.
+
+In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
+\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
+which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
+\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
+and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies within the intersection of $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of the latter.
+The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
+Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.
+
+%%Consider any $\rho > \tau$, recalling our assumption that $\tau > 0$.
+We know from Propositions \textcolor{orange}{\tt prop:smoothing} 9 and \textcolor{orange}{\tt prop:get-contraction} 10 of \cite{reg-sing-volterra} that $\softpart^\alpha$ maps
+%%\[ \singexp{\tau-1}{\Lambda}(\Upsilon) \to \singexp{\tau}{\Lambda}(\Upsilon) \]
+%%continuously and $\volterra^\alpha$ contracts $\singexp{\rho-1}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
+Under the same conditions, by working with Taylor series, we can show that $\softpart^\alpha$ maps
+%%\[ \zeta^{\tau-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau}\,\mathcal{O}(\pi \Upsilon) \]
+%%and $\volterra^\alpha$ maps $\zeta^{\rho-1}\,\mathcal{O}(\pi \Upsilon)$ to itself.
 \color{SlateBlue}
@@
 Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
-\item Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
+\color{SteelBlue}
+\item \textbf{[still to do]} Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
 \end{itemize}
@@
 \color{black}
-\color{Maroon}
-\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
-Choose a root $-\alpha$ of $P$.
+%%%\color{Maroon}
+%%%\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
+%%%Choose a root $-\alpha$ of $P$.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
 Equation
-\begin{equation}\label{eqn:standard ODE}
-\mathcal{P}\Psi=0
-\end{equation}
-has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
-\end{theorem}
-\begin{proof}
+%%%\begin{equation}\label{eqn:standard ODE}
+%%%\mathcal{P}\Psi=0
+%%%\end{equation}
+%%%has a unique solution $\Psi_\alpha$ in the affine subspace
+%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
+%%%\end{theorem}
+%%%\begin{proof}
 %Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}.
@@
 %
-As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
-\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
+%%%As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+%%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+%%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
 The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
 It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
-\end{proof}
+%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
+%%%\end{proof}
 \begin{theorem}

### 2024-03-12 exp-resurgence.tex
Rewrite first paragraph of Airy-Lucas contour argument

@@
 %%\newcommand{\roots}{\mathfrak{B}}
-\DeclareMathOperator{\hol}{hol}
+\DeclareMathOperator{\var}{var}
 
@@
 \[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$. We'll use the symbol $\sim$ to denote the asymptotic of $F$, namely we'll write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
+over all orders $n$. We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
 \end{defn}
-\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we'll say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if
+\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we will say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if
 \[\left|F - e^{\lambda z}z^{\tau}\left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(e^{\lambda\Re(z)}|z|^{\tau-n}\big).\]}
 If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
-The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it's the function's {\em asymptotic expansion} on that sector.
+The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it is the function's {\em asymptotic expansion} on that sector.
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
-We'll denote such map with the symbol $\aexp$.
+We will denote such map with the symbol $\aexp$.
 More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e.
-as $z\to e^{i\theta}\infty$, we'll write $\aexp^\theta$.
+as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.
 
@@
 \[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
-over all orders $n$ and all $z \in \Omega$. We'll use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
+over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
 \end{defn}
@@
 Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
-We'll therefore call this process {\em Borel regularization}.
+We will therefore call this process {\em Borel regularization}.
 Explicitly, Borel regularization works in four steps.
@@
 \end{enumerate}
-We'll say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
+We will say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
 
 Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
-We'll say a function is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+We will say a function is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
 In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
@@
 Equation~\eqref{eqn:bessel-rescaled-1} is an example.
-More generally, we'll consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
+More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
 \[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
-We'll restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
+We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
 
@@
 %%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We'll call it {\em Borel regularization}.
+We will call it {\em Borel regularization}.
 %%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We'll call this process {\em Borel regularization}.
+We will call this process {\em Borel regularization}.
 %\begin{itemize}
-%\item We'll say $\Phi$ is {\em Borel-regularizable} if it's asymptotic to a Borel-summable power series.
-%\item We'll say $\Phi$ is {\em Borel regular} if it's Borel-regularizable and Borel regularization leaves it unchanged.
+%\item We will say $\Phi$ is {\em Borel-regularizable} if it is asymptotic to a Borel-summable power series.
+%\item We will say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
 %\item We have the following vector space inclusions:
@@
 First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we'll prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
+For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
 \textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}
@@
 \subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
-%\textcolor{DarkCyan}{[Let's try to move some technical detail from here to the section where the result is proved. For example:]}
+%\textcolor{DarkCyan}{[Let us try to move some technical detail from here to the section where the result is proved. For example:]}
 %
@@
 In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
-\color{black} \color{Goldenrod}[Let's try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
+\color{black} \color{Goldenrod}[Let us try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
 \begin{equation}
@@
 The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-In fact, up to scaling, it's asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
+In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
 \end{theorem}
@@
 Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way.
-Use the Ramis Index Theorem to show that it's Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it's not only Gevrey-$1$, but in fact Borel summable.]}
+Use the Ramis Index Theorem to show that it is Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it is not only Gevrey-$1$, but in fact Borel summable.]}
 %%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
@@
 Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
-We'll define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
+We will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
 The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is htat it's a translation surface---\ldots]} For each critical point $a$, let $\Gamma_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\Gamma_\alpha^\theta$ which vanishes at $\alpha$.
+\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\Gamma_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\Gamma_\alpha^\theta$ which vanishes at $\alpha$.
 These are well-defined as long as $\Gamma_\alpha^\theta$ misses the critical values of $f$.
@@
 Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain.
-Finally, we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
+Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
 \color{black}
@@
 If $b \in B$ is non-singular, the frequency domain for $\laplace_{\zeta,b}^\theta$ is $T^*_{\zeta=b} B$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example (see Figure \ref{fig:different_fibres}).
+If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example (see Figure \ref{fig:different_fibres}).
 \begin{figure}[ht]
@@
 If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we'll see in our main example.
+If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example.
 %\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it's much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
+We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
 %\begin{itemize}
@@
 %\end{itemize}
-%\item Our picture helps explain why it's useful to work on the Borel plane (the position domain).
+%\item Our picture helps explain why it is useful to work on the Borel plane (the position domain).
 %\begin{itemize}
@@
 %\item Some have been discussed many times, using different approaches and conventions.
-We'll try to give an idea of how all these different treatments fit together.
+We will try to give an idea of how all these different treatments fit together.
 $\bullet$ The Airy function (Marino, Sauzin).
@@
 Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we'll say it's {\em Borel regular}.
+When a function matches the Borel sum of its asymptotic series, we will say it is {\em Borel regular}.
 Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
@@
 %\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it's essentially Borel-Laplace summation.
+says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it is essentially Borel-Laplace summation.
 Our method uses just Laplace transform.
@@
 We leave a possible generalization of our result to other classes of ODEs and difference equations for further pubblications.
-\textcolor{orange}{[Let's do more compare-and-contrast!
+\textcolor{orange}{[Let us do more compare-and-contrast!
 Our problem space is sort of orthogonal to Braaksma's, but we use the same solution space, so it seems like there could be a cool interaction there.]}
@@
 Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
-In the study of Borel summation and resurgence, it's useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
+In the study of Borel summation and resurgence, it is useful to see the position domain as a {\em translation surface} $B$, and the frequency domain as one of its cotangent spaces.
 Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^*B$.
@@
 The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-We'll require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
+We will require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
 This kind of translation surface has a ``cylindrical end'' at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}(see Figure~\ref{fig:translation_surface}).
@@
 The translation structure gives $B$ a notion of direction as well as distance.
-Away from the zeros of $\lambda$, which we'll call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
+Away from the zeros of $\lambda$, which we will call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
 At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
@@
 \end{align*}
-To get a definition that generalizes to branch points, though, it's worth taking a fancier point of view.
+To get a definition that generalizes to branch points, though, it is worth taking a fancier point of view.
 Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
@@
 Hence, the Laplace transform $\laplace_{\zeta, b}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_b)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=b}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
-%Let's say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it's in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
+%Let us say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
+A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it is in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
 Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
@@
 Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-In addition, we'll set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$.
+In addition, we will set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$.
 Let $F = \laplace_{\zeta, 0} f$.
@@
 
-It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we'll achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
+It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we will achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
 \begin{definition}
@@
 \subsubsection{Change of translation chart}\label{transl-borel}
-We'll show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}.
-To be more precise, we'll show that the diagram
+We will show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}.
+To be more precise, we will show that the diagram
 \begin{center}
@@
 commutes, where the functions of the variable $z$ belong to the fiber $T^*_{\zeta=0}B$.
-If $z$ is a function on the fiber over $\zeta=b$, then it's enough to replace $\borel_\zeta$ with $\borel_{\zeta_b}$ and to use  $\laplace_{\zeta_b,0}$ as the inverse.
+If $z$ is a function on the fiber over $\zeta=b$, then it is enough to replace $\borel_\zeta$ with $\borel_{\zeta_b}$ and to use  $\laplace_{\zeta_b,0}$ as the inverse.
 %\color{orange}
@@
 Indeed, that's the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$.
-We'll discuss it in Section~\ref{convolution}.
+We will discuss it in Section~\ref{convolution}.
 
@@
 
-Finally in Section~\ref{sec:frac-diff-laplace}, we'll consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives both in the frequency and the position domain, and fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
-%We'll see that the Borel transform and formal Laplace transform commutes with the action of derivatives and moltiplication.
+Finally in Section~\ref{sec:frac-diff-laplace}, we will consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives both in the frequency and the position domain, and fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
+%We will see that the Borel transform and formal Laplace transform commutes with the action of derivatives and moltiplication.
 %from the space of Puiseux series in the frequency domain to  $\C\llbracket z^{-1}\rrbracket$
 
-We end this paragraph introducing the notation we'll be using in the following. 
+We end this paragraph introducing the notation we will be using in the following. 
 \begin{notation*}
@@
     it is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms.
-However we'll refer to \textcolor{magenta}{[standard reference]} for details.
+However we will refer to \textcolor{magenta}{[standard reference]} for details.
 \textcolor{magenta}{[see also section on Regularity for Laplace]}
@@
 \subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
-As we'll see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
+As we will see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
 \begin{defn}
@@
 Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We'll use the {\em Riemann-Liouville} convention.
+We will use the {\em Riemann-Liouville} convention.
 \begin{definition}\label{defn:frac_driv}
@@
 \begin{proof}
-We'll show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+We will show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
 \begin{align*}
@@
 \subsubsection{Regularity results}
-Let's recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
+Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
 %%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
@@
 In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$.
-Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we'll always leave that starting point out of the path.
+Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
 %%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
@@
 \end{proof}
+\color{RoyalBlue}
 \textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
-Let's use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
+Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
+
+\color{BlueViolet}
+Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on appropriate covers of punctured versions of $\C$, like the universal cover $\pi \maps \widetilde{\C^\times} \to \C^\times$.
 \begin{lemma}\label{lem:shifted_holo_closed}
+Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$.
+Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
+
+\color{RoyalBlue}\textcolor{orange}{[Rephrase more generally, without referring to $P$.} 
+$\tilde{\C}$
 Choose a root $-\alpha$ of $P$.
 Consider a simply connected open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ which touches but doesn't contain $\zeta = \alpha$, is star-shaped around $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
-Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it's two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it's one-to-one everywhere else.
+Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it is one-to-one everywhere else.
+\color{BlueViolet}
 \begin{center}
@@
 \end{center}
-For any real numbers $\sigma$, $\Lambda$ and any $\delta \in [0, 1)$, the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
+For any $\sigma, \Lambda \in \R$ and $\delta \in [0, 1)$ with $\sigma + \delta \notin \Z$, the intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
 \end{lemma}
@@
 Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
-The operator $\hol \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$ defined by
-\[ \hol \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
+The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
+Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
+\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
 is bounded.
-The intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\Upsilon_\Delta)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\hol - e^{2\pi i \delta}$, so it's closed.
+The intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i (\sigma + \delta)} - 1)$, so it is closed.
 \end{proof}
@@
 The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-In fact, up to scaling, it's asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
+In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
 \end{theorem}
 \begin{proof}
-Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed} \textcolor{orange}{[definition of $\widetilde{B}_{P(-\zeta)}$ should actually be down here]}.
 By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
@@
 Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4.
-To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we'll show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
 
@@
 
-Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
 \[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
@@
 
-%%Let's run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that
+%%Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that
 
@@
 %%The restriction map $\singexp{\sigma}{\Lambda}(\Upsilon) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega_\alpha)$ \textcolor{orange}{\ldots}
+\end{proof}
+\begin{lemma}
+The Poincar\'{e} solutions of Equation~\eqref{eq:I} are 1-Gevrey.
+\end{lemma}
+\begin{proof}
+This statement is equivalent to Proposition~2.2.1 of \cite{EcalleIII}, proven on p.~114.
 \end{proof}
@@
 If $\Psi_\alpha$ admits an asymptotic expansion $\tilde{\Psi}_\alpha$, then $\Psi_\alpha$ is a formal solution of Equation~\eqref{eqn:operator-P}, thus by Ramis Index Theorem is $1$-Gevrey.
-The Borel transform of $\tilde{\Psi}_\alpha$ is a germ of convergent power series, and by the properties of the Borel transform, it's a formal solution of $\hat{\mathcal{P}}_\alpha \phi=0$.
+The Borel transform of $\tilde{\Psi}_\alpha$ is a germ of convergent power series, and by the properties of the Borel transform, it is a formal solution of $\hat{\mathcal{P}}_\alpha \phi=0$.
 \textcolor{red}{[check the exponential term $e^{-z\alpha}$, otherwise get different points]}
@@
         \item the asymptotitics of $\Psi_\alpha$ \textcolor{LimeGreen}{[exist and]} are $1$-Gevrey
-        \item \textcolor{LimeGreen}{The solution $\Psi_\alpha$ has an asymptotic expansion} indeed it's the Laplace transform of $\psi_\alpha$, thus if we consider the Taylor expansion of $\psi_\alpha$ at $\zeta=\alpha$ and then we integrate term by term we can compute the asymptotic.
+        \item \textcolor{LimeGreen}{The solution $\Psi_\alpha$ has an asymptotic expansion} indeed it is the Laplace transform of $\psi_\alpha$, thus if we consider the Taylor expansion of $\psi_\alpha$ at $\zeta=\alpha$ and then we integrate term by term we can compute the asymptotic.
 Notice that Poincar\'e asymptotic doesn't have to be to a power series, but it can be mor generally to a trans-monomial.
@@
 In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction.
-We'll use \textcolor{magenta}{the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ [actually, use prototype solution instead]} to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$.
+We will use \textcolor{magenta}{the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ [actually, use prototype solution instead]} to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$.
 %%\begin{theorem}[Theorem~4 from \cite{reg-sing-volterra}]\label{thm:sing-soln}
@@
 This isomorphism identifies the analytic and formal versions of the integration operator $\partial^{-1}_{\zeta, \alpha}$.
-In the argument that follows, we'll only distinguish the analytic and formal interpretations of $\C\{\zeta_\alpha\}$ when we need to.
+In the argument that follows, we will only distinguish the analytic and formal interpretations of $\C\{\zeta_\alpha\}$ when we need to.
 
@@
 
-%%Let's recall some notation from the proof. For convenience, we let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+%%Let us recall some notation from the proof. For convenience, we let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
 
@@
 \end{proof}
-\textcolor{orange}{[We'll prove a formal analogue of Theorem~4 from \cite{reg-sing-volterra}.
+\textcolor{orange}{[We will prove a formal analogue of Theorem~4 from \cite{reg-sing-volterra}.
 We use essentially the same technique]}, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ under \color{Tan}{the non-archimedean norm
@@
 for some $\lambda > 1$.
-\textcolor{orange}{[My hope was to use a non-archimedean norm to give a contraction mapping theorem formulation of an argument that more and more terms match, but it's hard to split up the operator in a way that makes more and more terms match\ldots]}
+\textcolor{orange}{[My hope was to use a non-archimedean norm to give a contraction mapping theorem formulation of an argument that more and more terms match, but it is hard to split up the operator in a way that makes more and more terms match\ldots]}
 \begin{lemma}\label{lem:formal-general-volterra}
@@
 In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
-Instead of looking for an analytic solution, like we do in \cite{reg-sing-volterra}, we'll seek a formal solution $\fmlsolwhole$.
+Instead of looking for an analytic solution, like we do in \cite{reg-sing-volterra}, we will seek a formal solution $\fmlsolwhole$.
 First, we have to make sure the equation makes sense in the space of formal power series.
@@
 
-Now, let's run through the proof of Theorem~3, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ in the ``$\lambda$-adic'' norms described above.
-For simplicity, we'll specialize the proof to the case we consider in Theorem~4.
+Now, let us run through the proof of Theorem~3, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ in the ``$\lambda$-adic'' norms described above.
+For simplicity, we will specialize the proof to the case we consider in Theorem~4.
 First, picking an arbitrary point $\zeta = \eta$ in $\Omega_\alpha$, we show that the {\em prototype solution}
@@
 \end{equation}
-Then solving order by order in $n$ it's possible to compute the coefficients of the formal series $\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}$, which will turn out to be a $1$-Gevrey series because of Ramis
+Then solving order by order in $n$ it is possible to compute the coefficients of the formal series $\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}$, which will turn out to be a $1$-Gevrey series because of Ramis
 Index Theorem \cite{ramis_index}.
@@
 
-To prove Step $(b)$ we'll use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$.
+To prove Step $(b)$ we will use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$.
 First, recall that ${\psi}_\alpha$ is the uniques solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}.
@@
 where $\Lambda_a^\theta$ is the thimble through the critical point $a$.
-In this section, we'll prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
+In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
 The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
@@
 \end{proof}
-We'll now prove that $I$ is Borel regular:
+We will now prove that $I$ is Borel regular:
 \begin{theorem}\label{thm:maxim-proof}
@@
 
-Let's write $\approx$ when two functions are asymptotic at all orders around the base point; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
+Let us write $\approx$ when two functions are asymptotic at all orders around the base point; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
@@
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we'll show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with $\tilde{\iota}$.
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with $\tilde{\iota}$.
 We can rewrite the Taylor series for $\nu$ as
@@
 
-The kernel of $\partial_{\zeta, 0}^{\nu-1}$ is $\big(\zeta(p) - \zeta\big)^{\nu-1}$. It has an integrable singularity at $p$, and it's non-singular at $\zeta = 0$.
+The kernel of $\partial_{\zeta, 0}^{\nu-1}$ is $\big(\zeta(p) - \zeta\big)^{\nu-1}$. It has an integrable singularity at $p$, and it is non-singular at $\zeta = 0$.
 \end{verify}
@@
 Given any point $p \in \Omega$, choose a path $\gamma$ that runs through $\Omega$ from $\zeta = \alpha$ to $p$.
-Since $\gamma$ is the continous image of a closed interval, it's compact, so $\zeta$ is bounded
+Since $\gamma$ is the continous image of a closed interval, it is compact, so $\zeta$ is bounded
 
@@
     \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
-    Finally, we apply the $1/2$ derivative of both sides, recalling that it's a left inverse of the $1/2$ integral, and we find
+    Finally, we apply the $1/2$ derivative of both sides, recalling that it is a left inverse of the $1/2$ integral, and we find
     \begin{equation}\label{eqn:formula--1/2}\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
@@
 We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
-Let's say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
+Let us say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
 As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\Lambda_\alpha^\theta(\beta)$ in $X$.
@@
 \end{figure}
-Let's calculate the jump of $\int_{\Lambda_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
+Let us calculate the jump of $\int_{\Lambda_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
 Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
@@
 and it is 
-which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$. We'll see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
+which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
+We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
 
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{y^{-1/2} \Lambda_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\textcolor{magenta}{y^{-1/2} \Lambda_1}} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
 We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
@@
 with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^{(j)}} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda_{j}$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$ (see Figure \ref{fig:thimble_n_5}).
-
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+where $\Lambda^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
+By definition, $\Lambda^\theta_j$ is a preimage of the ray $\Gamma^\theta_{\mp 1}$ under the function $-T_n(u)$. The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
+\begin{center}
+\includegraphics[scale=0.3]{figures/thimble-n5.png} \\[1em]
+{\small Integration contour $\Lambda^{(j)}$ for the Airy--Lucas function with $n=5$.
+The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=\textcolor{magenta}{???}$.
+The light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
+\end{center}
 \begin{figure}[ht]
@@
    \includegraphics[scale=0.3]{figures/thimble-n5.png}
-    \caption{Integration contour $\Lambda_j$ for the Airy--Lucas function with $n=5$.
+    \caption{Integration contour $\Lambda^\theta_j$ for the Airy--Lucas function with $n=5$.
 The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=???$.
@@
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(k)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
 where
 \begin{equation}\label{integral:mod-bessel-rational-AL}
-K_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{z^{-{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(k)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name?
+K_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+\end{equation}
+Saying that $\widehat{\Ai}^{(j)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name?
 Is that standard?]}
@@
 
-Let's put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
+Let us put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
 \begin{equation}\label{eqn:reg-mod-bessel-AL}
@@
 We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We'll succeed when $\alpha^2 - 1 = 0$, and we'll see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
 
@@
 
-In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we'll see this approach succeed.
-For each root $\alpha_j$, we'll find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in Figure \ref{Fig:domain}.
+In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
+For each root $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in Figure \ref{Fig:domain}.
 We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
@@
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_1)$.
+Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_1)$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
@@
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$.
+Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$.
 In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
@@
 The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket$.
-We'll now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+We will now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
 
@@
 \subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
-\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
+We follow the reasoning of the proof of Theorem~\ref{lem:thimble_proj_formula-proof}.
+We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\Lambda^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
+Recalling that $\Lambda^\theta_j$ is a preimage of $\Gamma^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
+\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+\end{align*}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $u$, respectively.
+\par\color{RoyalBlue}\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
 We follow the reasoning of the proof of Theorem~\ref{thm:maxim}.
@@
 For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-
+Let us assume $z \in (0, \infty)$ for the rest of the section.
+\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}\color{black}
 \begin{center}
@@
 
-Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$:
+Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$: \textcolor{orange}{[If $u_+ = \cos(\phi)$, then $u_- = \cos(\overline{\phi})$]}
 
@@
 %For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
+Let us assume $z \in (0, \infty)$ for the rest of the section.
 \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
@@
   %  where $\Lambda'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
-  Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it's the reference in \cite{dlmf})
+  Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it is the reference in \cite{dlmf})
     \begin{align*}
@@
 
-Following the treatment of the Airy--Lucas functions, we'll rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ as thimble integrals with the function $f=4u^3-3u$.
+Following the treatment of the Airy--Lucas functions, we will rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ as thimble integrals with the function $f=4u^3-3u$.
 This follows from the change of coordinates $z=\tfrac{2}{3}y^{3/2}$, and gives $\mathrm{A}_1(y,p) = (12 z)^{\tfrac{1-p}{3}}\, I_+(z,p)$ with
@@
 However, the volume form $\nu_p$ is meromorphic, hence $f$ should be regarded as a function from $\C^*$ to $\C$.
-In particular, in this example we'll see that there is a new singularity at the origin due to the singularity of $\nu_p$.
-For simplicity, we'll restrict to the case $p=1$.
+In particular, in this example we will see that there is a new singularity at the origin due to the singularity of $\nu_p$.
+For simplicity, we will restrict to the case $p=1$.
 Then, $I_+(z,1)$ solves
@@
 If you strike the strip from above, it vibrates up and down.
-Let's suppose the vibrations are small, and uniform across the width of the strip, so we can describe them using the Euler--Bernoulli beam model~\cite[\S 12.4]{genta2009vibration}.
+Let us suppose the vibrations are small, and uniform across the width of the strip, so we can describe them using the Euler--Bernoulli beam model~\cite[\S 12.4]{genta2009vibration}.
 The vibration modes of frequency $\omega$ are described by the vertical displacement profiles $\Phi$ that satisfy the equation
@@
 \par\color{RoyalBlue}
-As we'll show in Section \ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 
+As we will show in Section~\ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 
 \begin{equation}
@@
 In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-%The method we'll demonstrate in Section~\ref{spatial} works for any differential equation
+%The method we will demonstrate in Section~\ref{spatial} works for any differential equation
 %\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
@@
 which is easier to solve.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it's slight and locally integrable at $\zeta = \alpha$.
+However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it is slight and locally integrable at $\zeta = \alpha$.
 
@@
 In Sections \ref{pos-root}\,--\,\ref{neg-root}, we’ll see this approach succeed.
-For each root $\alpha$, we'll find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
+For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
 We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
@@
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
+Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
@@
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-Let's find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
+Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
 In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
@@
 For $z \in (0, \infty)$, the contour $\mathcal{H}^1_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let's assume $z \in (0, \infty)$ for the rest of the section.
+Let us assume $z \in (0, \infty)$ for the rest of the section.
 \textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
@@
 \[ K = \frac{1}{i\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we'll follow below.
+This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we will follow below.
 
@@
 \textcolor{MediumSeaGreen}{[Focus on endlessly continuable functions instead?
-See~[Section~2, ``Variations on the resurgence of the gamma function''.]} \textcolor{red}{They have the special property that by studying their analytic continuation around one singularity, we can typically discover the germ of another singularity.} \textcolor{RoyalBlue}{They have the very special property that by studying one germ, we can typically reconstruct the others by looking at the behavior near the singular points.} \textcolor{MediumSeaGreen}{[They are ``self-reproducing'' in a certain remarkable way involving holonomy around singularities, as we'll see in the example below\ldots]} A prototypical class of resurgent functions is the so-called simple resurgent functions~\textcolor{magenta}{\cite[Section~1.2.3]{intro-to-ecalle}\{oops, this source defines simple resurgent functions in the frequency domain\}}.
+See~[Section~2, ``Variations on the resurgence of the gamma function''.]} \textcolor{red}{They have the special property that by studying their analytic continuation around one singularity, we can typically discover the germ of another singularity.} \textcolor{RoyalBlue}{They have the very special property that by studying one germ, we can typically reconstruct the others by looking at the behavior near the singular points.} \textcolor{MediumSeaGreen}{[They are ``self-reproducing'' in a certain remarkable way involving holonomy around singularities, as we will see in the example below\ldots]} A prototypical class of resurgent functions is the so-called simple resurgent functions~\textcolor{magenta}{\cite[Section~1.2.3]{intro-to-ecalle}\{oops, this source defines simple resurgent functions in the frequency domain\}}.
 namely an \textcolor{Maroon}{[resurgent]} analytic function $\hat{\phi}$ in the position domain with singularities $\omega$ such that
@@
 %A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-%We'll say a function is {\em slight} at $\zeta = 0$ if it can be written as
+%We will say a function is {\em slight} at $\zeta = 0$ if it can be written as
 %\begin{equation}\label{eqn:slight-defn}
@@
 \end{prop}
-%To prove this result, we'll need a little background.
+%To prove this result, we will need a little background.
 
@@
 If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it's locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
+A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it is locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
 

### 2024-03-16 exp-resurgence.tex
Finish proving stronger version of thm:has_ae_ODE
This actually gives Borel regularity; just need to change the statement.

@@
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
@@
 \color{BlueViolet}
-Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on appropriate covers of punctured versions of $\C$, like the universal cover $\pi \maps \widetilde{\C^\times} \to \C^\times$.
+Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
+The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
 \begin{lemma}\label{lem:shifted_holo_closed}
@@
 \end{center}
-For any $\sigma, \Lambda \in \R$ and $\delta \in [0, 1)$ with $\sigma + \delta \notin \Z$, the intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
+For any $\rho' \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma' \in (\rho'-1, \rho']$, the intersection
+\[ \zeta^{\rho'}\,\pi^*\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma'}{\Lambda}(\Upsilon) \]
+is a closed subspace of $\singexp{\sigma'}{\Lambda}(\Upsilon)$.
 \end{lemma}
@@
 Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
-The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
+The {\em variation} operator $\var \maps \singexp{\sigma'}{\Lambda}(\Upsilon) \to \singexp{\sigma'}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
 Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
@@
 is bounded.
-The intersection of $\zeta^{\sigma + \delta}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i (\sigma + \delta)} - 1)$, so it is closed.
+The intersection of $\zeta^{\rho'}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma'}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho'} - 1)$, so it is closed.
+\end{proof}
+\textcolor{orange}{[Add flavor text]}
+\begin{lemma}\label{lem:laplace-bridge}
+\textcolor{orange}{[Move to Laplace transform section?]} Consider an open sector $\Omega$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, but with its tip at $\zeta = 0$.
+Take some $\rho \in (-1,\infty)$.
+If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
+\textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
+\end{lemma}
+\begin{proof}
+By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+Write $\series{\varphi}$ out in the form
+\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
+observing that
+\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
+For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
+\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
+Taking the Laplace transform of both sides, we learn that
+\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
+where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.
+
+Proposition~\ref{prop:laplace-cont} tells us \textcolor{orange}{[as long as the opening angle of $\Omega$ is less than $\pi$]} that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$.
+This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
+\begin{align*}
+|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
+& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
+& \lesssim \Delta^{-1}
+\end{align*}
+along any ray. This, as discussed above, proves the desired result.
+
+%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
 \end{proof}
@@
 The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
 \end{theorem}
 \begin{proof}
-Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed} \textcolor{orange}{[definition of $\widetilde{B}_{P(-\zeta)}$ should actually be down here]}.
-By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
 \[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
@@
 and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself.
-It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies within the intersection of $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of the latter.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
 The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
@@
 
-%%Consider any $\rho > \tau$, recalling our assumption that $\tau > 0$.
-We know from Propositions \textcolor{orange}{\tt prop:smoothing} 9 and \textcolor{orange}{\tt prop:get-contraction} 10 of \cite{reg-sing-volterra} that $\softpart^\alpha$ maps
-%%\[ \singexp{\tau-1}{\Lambda}(\Upsilon) \to \singexp{\tau}{\Lambda}(\Upsilon) \]
-%%continuously and $\volterra^\alpha$ contracts $\singexp{\rho-1}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
-Under the same conditions, by working with Taylor series, we can show that $\softpart^\alpha$ maps
-%%\[ \zeta^{\tau-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau}\,\mathcal{O}(\pi \Upsilon) \]
-%%and $\volterra^\alpha$ maps $\zeta^{\rho-1}\,\mathcal{O}(\pi \Upsilon)$ to itself.
-\color{SlateBlue}
-\begin{itemize}
-\item Prove Theorem~3 using Picard iteration, using the {\em prototype solution}
-\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
-given by an arbitary point $b \in \Omega_\alpha$ as our initial guess.
-\item This expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, makes it clear that the prototype solution belongs to $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
-\item The operator $\volterra^\alpha$ preserves the intersection of $\zeta^{\sigma + \delta}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$.
-Hence, the Picard iteration sequence must lie in this subspace.
-\item We know from Lemma~\ref{lem:shifted_holo_closed} that the intersection of $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is a closed subspace of the latter.
-Hence, the solution $\psi_\alpha$ that Picard iteration converges to must also lie within this subspace.
-\color{SteelBlue}
-\item \textbf{[still to do]} Use Laplace transforms of truncated power series for $\psi_\alpha$ to show that $\Psi_\alpha$ has an asymptotic series?
-\end{itemize}
-\color{BlueViolet}
-
-%%Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that
-
-%%Picking an arbitrary point $b \in \Omega_\alpha$, we observe that the {\em prototype solution}
-%%\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right] \]
-
-%% \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]
-
-%%Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the subspace
-
-%%The restriction map $\singexp{\sigma}{\Lambda}(\Upsilon) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega_\alpha)$ \textcolor{orange}{\ldots}
-\end{proof}
-\begin{lemma}
-The Poincar\'{e} solutions of Equation~\eqref{eq:I} are 1-Gevrey.
-\end{lemma}
-\begin{proof}
-This statement is equivalent to Proposition~2.2.1 of \cite{EcalleIII}, proven on p.~114.
+Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\llbracket \zeta, \zeta^{-1} \rrbracket$.
+The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\llbracket \zeta \rrbracket$.
+Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+\textcolor{orange}{[How to rephrase without formal Laplace transform?
+Conclusion is stronger than statement; change statement accordingly.]}
 \end{proof}
@@
 where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $u$, respectively.
-\par\color{RoyalBlue}\textcolor{orange}{[\textbf{New phrasing for rewrite:} The critical point splits the thimble $\Lambda$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.]}
-We follow the reasoning of the proof of Theorem~\ref{thm:maxim}.
-We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $\textcolor{magenta}{-\zeta} = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Projecting $z^{-1/n} \Lambda^{(k)}$ to a contour $\gamma_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\gamma_z$ back to $z^{-1/n} \Lambda^{(k)}$, we get \textcolor{magenta}{[sign flipped]}
-
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2  \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,\frac{U_{m-1}(u)}{U_{n-1}(u)}\,d\zeta %\\
-%& = -\frac{1}{2\,\tfrac{n}{m} \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\gamma_z} e^{-z\zeta}\,F(1 - \tfrac{m}{n}, 1 + \tfrac{m}{n}, \tfrac{3}{2}, \tfrac{1}{2} \pm \tfrac{1}{2}\zeta)\,d\zeta.
-\end{align*}
-
-For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let us assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}\color{black}
 \begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\gamma_1$ \textcolor{magenta}{[reversed]} in the $\zeta$ plane, slightly off from the critical value $\zeta=1$.}
+\textcolor{orange}{[Do we still want a picture? Maybe draw the thimble in the $u$ plane]}
 \end{center}
 
+\color{MediumSpringGreen}
 Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$: \textcolor{orange}{[If $u_+ = \cos(\phi)$, then $u_- = \cos(\overline{\phi})$]}
@@
 
-where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.
+where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.\color{black}
 

### 2024-03-17 exp-resurgence.tex
State the Borel regularity result we just proved

@@
 \end{proof}
-\begin{theorem}[restatement of \ref{thm:has_ae_ODE}]
-The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
+\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
+The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, and the Borel sum of $\series{\Psi}_\alpha$ is $\Psi_\alpha$.
 \end{theorem}
@@
 Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-\textcolor{orange}{[How to rephrase without formal Laplace transform?
-Conclusion is stronger than statement; change statement accordingly.]}
+\textcolor{orange}{[How to rephrase without formal Laplace transform?]}
+
+Now, let's take the Borel sum of $\series{\Psi}_\alpha$.
+The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$.
+By definition, the sum of $\series{\psi}_\alpha$ is $\psi_\alpha$, and the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$ is $\Psi_\alpha$.
 \end{proof}

### 2024-03-18 exp-resurgence.tex
Adapt the ODE results in the intro to our new reasoning
Clean up old reasoning too.

@@
 Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$.
-Because this solution is so unique, its Laplace transform $\Psi_\alpha$ turns out to be Borel regular.
-
-%%The Laplace transform commutes this distinguishing behavior into asymptotics at $z = \infty$, which can be recognized even if we turn $\Phi$ into a formal series $
-
-%We can use the Laplace transform to convert $\mathcal{P}$ into a family of integral operators $\hat{\mathcal{P}}_\upsilon$ parameterized by the point $\zeta = \upsilon$ on the position domain.
+This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
 \color{BlueViolet}
@@
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
+of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}
-\begin{theorem}\label{thm:has_ae_ODE}
-The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} has an asymptotic expansion in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-In fact, up to scaling, it is asymptotic to the Poincar\'{e} solution found in that space \textcolor{orange}{[not defined yet?]}.
+The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$.
+By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
+\begin{theorem}\label{thm:is_Borel_sum}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
 \end{theorem}
-Combining our uniqueness and regularity results for $\psi_\alpha$ with uniqueness and regularity results for the Poincar\'{e} solutions, we can show that $\Psi_\alpha$ is Borel regular.
+With a little more work, encapsulated in Lemma~\textcolor{orange}{?} from Section~\textcolor{orange}{?}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
+\begin{theorem}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:is_Borel_sum}.
+\end{theorem}
 \begin{corollary}
@@
 \color{black}
-\color{Maroon}
-\begin{theorem}\label{thm:borel_reg_ODE}
-Choose a root $-\alpha$ of $P$.
+%%\color{Maroon}
+%%\begin{theorem}\label{thm:borel_reg_ODE}
+%%Choose a root $-\alpha$ of $P$.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
 Equation $\mathcal{P}\Psi=0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
-\end{theorem}
-\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
-\begin{corollary}\label{cor:borel_reg_ODE}
-For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
+%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
+%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
+%%\end{theorem}
+%%\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
+%%\begin{corollary}\label{cor:borel_reg_ODE}
+%%For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
 That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
-\end{corollary}
-\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable.
+%%\end{corollary}
+\textcolor{BlueViolet}{From an analytic perspective, Theorem~\ref{thm:is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
+On the other hand, if you prefer to work formally, you can take the Poincar\'{e} solutions as given and use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
+We do this in Section~\ref{sec:new-summability-proof}.}
+%%\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable.
 See Section~\ref{sec:new-summability-proof}.}
-\textcolor{violet}{[In another section, do the ``mirror image'' argument.
+%%\textcolor{violet}{[In another section, do the ``mirror image'' argument.
 Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way.
@@
 \end{theorem}
+\begin{center}
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=radial edge]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
+\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
+\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+  \fill \p circle (0.7mm);
+}
+\end{tikzpicture}
+
+{\small The domain $\Omega_\alpha$}
+\end{center}
 \begin{proof}
@@
 \begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
-The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, and the Borel sum of $\series{\Psi}_\alpha$ is $\Psi_\alpha$.
+The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+The series $\series{\Psi}_\alpha$ is Borel summable, and its Borel sum is $\Psi_\alpha$.
 \end{theorem}
@@
 
-%%The key step of our proof will be to show that $\psi_\alpha$ lies in
-
-%%The uniqueness part of the Theorem~4 ensures that restricting $\psi_\alpha$ to $\Omega_\alpha$ gives the analogous solution used in the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}.
-
-%%%In the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, we used Theorem~4 of \cite{reg-sing-volterra} to show that the equation $\mathcal
-
-%%%$\psi_\alpha$ in the affine subspace
-%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$
-
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
@@
 \end{proof}
-\color{black}
-%%%\color{Maroon}
-%%%\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
-%%%Choose a root $-\alpha$ of $P$.
-Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation
-%%%\begin{equation}\label{eqn:standard ODE}
-%%%\mathcal{P}\Psi=0
-%%%\end{equation}
-%%%has a unique solution $\Psi_\alpha$ in the affine subspace
-%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
-%%%\end{theorem}
-%%%\begin{proof}
-%Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}.
-Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}.
-Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.
-%
-%%%As a consequence of Theorem~4 \cite{reg-sing-volterra}, after rescaling by a constant, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
-%%%\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-%%%of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
-The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
-It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-%%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-%%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
-%%%\end{proof}
-\begin{theorem}
-\textcolor{Turquoise}{Assuming $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} admits an asymptotic expansion as $\Re z\to e^{i\theta}\infty$ along some rays contained in the sector $\Omega_\alpha$, then $\Psi_\alpha$ is Borel regular.} That solution $\Psi_\alpha$ from Theorem~\ref{thm:borel_reg_ODE_proof} is Borel regular.
-\end{theorem}
-\begin{proof}
-\color{Turquoise}
-If $\Psi_\alpha$ admits an asymptotic expansion $\tilde{\Psi}_\alpha$, then $\Psi_\alpha$ is a formal solution of Equation~\eqref{eqn:operator-P}, thus by Ramis Index Theorem is $1$-Gevrey.
-The Borel transform of $\tilde{\Psi}_\alpha$ is a germ of convergent power series, and by the properties of the Borel transform, it is a formal solution of $\hat{\mathcal{P}}_\alpha \phi=0$.
-\textcolor{red}{[check the exponential term $e^{-z\alpha}$, otherwise get different points]}
-\color{Violet}
-    \begin{itemize}
-        \item the asymptotitics of $\Psi_\alpha$ \textcolor{LimeGreen}{[exist and]} are $1$-Gevrey
-        \item \textcolor{LimeGreen}{The solution $\Psi_\alpha$ has an asymptotic expansion} indeed it is the Laplace transform of $\psi_\alpha$, thus if we consider the Taylor expansion of $\psi_\alpha$ at $\zeta=\alpha$ and then we integrate term by term we can compute the asymptotic.
-Notice that Poincar\'e asymptotic doesn't have to be to a power series, but it can be mor generally to a trans-monomial.
-I think we should state the definition for trans-monomials.
-        \begin{align}
-            \Psi_\alpha&=\int_\alpha^\infty e^{-z\zeta} \sum_{n=0}^\infty a_n (\zeta-\eta)^n d\zeta \\
-            & = \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z\zeta}   (\zeta-\eta)^n d\zeta+\int_\alpha^\infty e^{-z\zeta} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta \\
-            & = e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta + e^{-z\eta} \int_\alpha^\infty e^{-z(\zeta - \eta)} \sum_{n=N+1}^\infty a_n (\zeta-\eta)^n d\zeta
-        \end{align}
-        \begin{multline*}
-            \left|\Psi_\alpha- e^{-z\eta} \sum_{n=0}^N a_n \int_\alpha^\infty e^{-z(\zeta - \eta)} (\zeta-\eta)^n d\zeta\right|\leq e^{-\Re(z)|\eta|} \int_\alpha^R |e^{-z(\zeta - \eta)} |\sum_{n=N+1}^\infty R^{-n} |(\zeta-\eta)|^n d\zeta +\\
-            e^{-\Re(z)|\eta|} \int_R^\infty |e^{-z(\zeta - \eta)} | |\psi_\alpha| d\zeta \qquad\text{[use that $\psi_\alpha$ is exponentially bounded]}
-        \end{multline*}
-       \[\Psi_\alpha=\lim_{b \to (\zeta = \alpha)}\int_b^\infty e^{-z\zeta} f\;d\zeta \]
-       \item Say $\left|\Psi_\alpha - \int_b^{\infty}\right| \leq \epsilon$ over all $z$. Then $|z|^n\;\left|\Psi_\alpha - \int_b^{\infty}\right| \leq |z|^n \epsilon$
-       \item \begin{align*}
-       \int_\alpha^\infty e^{-z\zeta} |z|^n |\psi_\alpha-\text{poly}(\zeta)| d\zeta \\
-       \int_\alpha^\infty \left[\left(\tfrac{\partial}{\partial \zeta}\right)^n e^{-z\zeta}\right] |\psi_\alpha-\text{poly}(\zeta)| d\zeta
-       \end{align*}
-       \item Need $\lim_{z \to \infty} z^n |\Psi_\alpha - \text{poly}|$ for all $n \in \Z_{\ge 0}$
-        \item $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha}\C\lbrace\zeta_\alpha\rbrace$ and solves $\hat{\mathcal{P}}_\alpha\phi=0$
-        \item Integral looks like
-        \begin{align*}
-        \int_0^\infty e^{-z\zeta} f\;d\zeta & = \int_0^r e^{-z\zeta} f\;d\zeta + \int_r^\infty e^{-z\zeta} f\;d\zeta \\
-        & \text{``}\approx\text{''} \int_0^r e^{-z\zeta} f\;d\zeta + e^{-z \Re(\zeta)} \|f\|_1 \\
-        & \text{``}\approx\text{''} \|f\|_1 + e^{-zr} \|f\|_1
-        \end{align*}
-        \item $\hat{\mathcal{P}}_\alpha\phi=0$ admits a unique formal solution
-        \item  $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ \textcolor{LimeGreen}{[which exists]}
-    \end{itemize}
-\end{proof}
-\color{Maroon}
-\begin{figure}[h]
-\center
-\begin{tikzpicture}
-\newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
-  (-\spill, -\spill) (\spill, \spill)
-  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
-\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
-\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill \p circle (0.7mm);
-}
-\end{tikzpicture}
-\caption{The domain $\Omega_\alpha$}\label{Fig:domain}
-\end{figure}
-The key to our proof is recasting Equation~\eqref{eqn:standard ODE} as an integral equation in the position domain.
-This integral equation belongs to a well-behaved class of regular singular Volterra equations, which we study in~\cite{reg-sing-volterra}.
-In particular, it can be solved using Picard iteration, which refines an initial guess toward the unique solution in its basin of attraction.
-We will use \textcolor{magenta}{the guess $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$ [actually, use prototype solution instead]} to find a solution $\psi_\alpha$ with the same singularity at $\zeta_\alpha = 0$.
-%%\begin{theorem}[Theorem~4 from \cite{reg-sing-volterra}]\label{thm:sing-soln}
-%%The equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
-%%\[ \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
-%%\end{theorem}
-
-For the Borel regularity part of the proof, we need to make a connection between the analytic and formal worlds.
-To do this in the position domain, we again use Picard iteration.
-\textcolor{orange}{[This does seem to generalize Delabaere's argument!
-We should confirm and mention that.]}
-\begin{lemma}\label{lem:picard-power}
-In Theorem~4 of \cite{reg-sing-volterra}, the solution $\psi_\alpha$ can be expressed as the sum of a power series in $\zeta_\alpha^{\tau_\alpha - 1} \C\{\zeta_\alpha\}$.
-%%can be expressed as a convergent power series of the form
-%%\[ c_1 \zeta_\alpha^{\tau_\alpha - 1} + c_2 \zeta_\alpha^{\tau_\alpha} + c_3 \zeta_\alpha^{\tau_\alpha + 1} + c_4 \zeta_\alpha^{\tau_\alpha + 2} + \ldots. \]
-\end{lemma}
-\begin{proof}
-%%Theorem~\ref{thm:sing-soln} is a corollary of Theorem~\ref{thm:general_volterra} of \cite{reg-sing-volterra}.
-The ring of formal power series $\C\{\zeta_\alpha\}$ is isomorphic to the ring of germs of holomorphic functions at $\zeta = \alpha$.
-This isomorphism identifies the analytic and formal versions of the integration operator $\partial^{-1}_{\zeta, \alpha}$.
-In the argument that follows, we will only distinguish the analytic and formal interpretations of $\C\{\zeta_\alpha\}$ when we need to.
-
-For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
-The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
-%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
-\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
-and the perturbation
-%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
-\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
-
-Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
-\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
-lies in the space $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
-We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
-This is equivalent to solving the inhomogeneous equation
-\begin{equation}\label{eqn:inhomog-volterra}
-\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
-\end{equation}
-The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
-It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
-More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
-Starting with any initial guess $\solptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
-\begin{align*}
-\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
-\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
-\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
-& \;\;\vdots
-\end{align*}
-we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ to a solution.
-
-\textcolor{orange}{[\ldots]}
-
-%%Let us recall some notation from the proof. For convenience, we let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-
-%%For convenience, let $p = P(-\zeta_\alpha)$ and $q = Q(-\zeta_\alpha)$. In \cite{reg-sing-volterra}, we observed that the Volterra operator $\hardpart^\alpha$ with kernel
-%%Let $\hardpart^\alpha$ be the Volterra operator with kernel
-%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)} \]
-%%and let $\softpart^\alpha$ be the Volterra operator with kernel
-%%\[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
-
-%%For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-
-%%As we did in the proof of Theorem~\ref{thm:sing-soln} from \cite{reg-sing-volterra}, let
-
-%%\[ \hardker^\alpha(a,a') = -\frac{q(a')}{p(a)}, \]
-
-%%\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
-
-Since $p$ has a simple root at $\zeta = \alpha$, the prototypical part $\hardpart^\alpha$ sends $\C\{\zeta_\alpha\}$ to itself.
-In fact, for any real number $\sigma$ that's not a negative integer, $\hardpart^\alpha$ maps $\zeta^\sigma \C\{\zeta_\alpha\}$ to itself.
-Under the same condition on $\sigma$, the operator $R(\partial^{-1}_{\zeta, \alpha})$ is well-defined as a map from $\zeta_\alpha^\sigma \C\{\zeta_\alpha\}$ to itself,\footnote{This is easiest to see from the formal point of view.
-Multiplication by $R(\zeta)$ sends convergent series to convergent series, and $\partial^{-1}_{\zeta, \alpha}$ acts like multiplication by $\zeta$ followed by the map $\zeta^\rho \mapsto \tfrac{1}{\Gamma(\rho+1)} \zeta^\rho$.
-A convergent series stays convergent under any operation that leaves its coefficients the same or smaller.
-\textcolor{orange}{[Discuss convergence of the operator series from the analytic point of view?]}.} so the perturbation can be seen as a map $\softpart^\alpha \maps \zeta_\alpha^\sigma \C\{\zeta_\alpha\} \to \zeta_\alpha^{\sigma + 1} \C\{\zeta_\alpha\}$.
-
-\textcolor{orange}{[\ldots]}
-
-\end{proof}
-\textcolor{orange}{[We will prove a formal analogue of Theorem~4 from \cite{reg-sing-volterra}.
-We use essentially the same technique]}, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ under \color{Tan}{the non-archimedean norm
-\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = \lambda^{-(\sigma+n)} \]
-\color{Maroon}
-the weighted $L^1$ norm \textcolor{orange}{[whoops, not defined for all formal power series]}
-\[ \big| c_n \zeta_\alpha^{\sigma+n} + c_{n+1} \zeta_\alpha^{\sigma+n+1} + c_{n+2} \zeta_\alpha^{\sigma+n+2} + \ldots \big|_\lambda = |c_n| \lambda^{-(\sigma+n)} + |c_{n+1}| \lambda^{-(\sigma+n+1)} + |c_{n+2}| \lambda^{\sigma+n+2} + \ldots\]
-for some $\lambda > 1$.
-\textcolor{orange}{[My hope was to use a non-archimedean norm to give a contraction mapping theorem formulation of an argument that more and more terms match, but it is hard to split up the operator in a way that makes more and more terms match\ldots]}
-\begin{lemma}\label{lem:formal-general-volterra}
-The equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$ has a unique formal solution $\series{\psi}_\alpha$ in the affine subspace
-\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket \]
-of the space $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
-\end{lemma}
-\begin{proof}
-In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
-Instead of looking for an analytic solution, like we do in \cite{reg-sing-volterra}, we will seek a formal solution $\fmlsolwhole$.
-First, we have to make sure the equation makes sense in the space of formal power series.
-Let $\series{p} = P(-\zeta)$ and $\series{q} = Q(-\zeta)$, thinking of the polynomials as formal power series, and let $\series{R}$ be the Taylor series of $R$.
-The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
-%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
-\color{magenta}
-\[ \hardpart^\alpha = -\tfrac{1}{\series{p}} \circ \partial^{-1}_{\zeta, \alpha} \circ \series{q} \]
-\color{Maroon}
-and the perturbation
-\color{magenta}
-\[ \softpart^\alpha = \tfrac{1}{\series{p}} \circ \partial^{-2}_{\zeta, \alpha} \circ \series{R}\big(\partial^{-1}_{\zeta, \alpha}\big), \]
-[have to get a contraction somehow for this to work like I imagined] \color{Maroon} which are both written here as operators on $\C\llbracket \zeta_\alpha \rrbracket$.
-
-Now, let us run through the proof of Theorem~3, replacing the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ used in \cite{reg-sing-volterra} with the formal power series spaces $\zeta_\alpha^\sigma \C\llbracket \zeta_\alpha \rrbracket$ in the ``$\lambda$-adic'' norms described above.
-For simplicity, we will specialize the proof to the case we consider in Theorem~4.
-First, picking an arbitrary point $\zeta = \eta$ in $\Omega_\alpha$, we show that the {\em prototype solution}
-%%\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
-%%\[ \solproto = \frac{1}{\series{p}(a)} \exp\big(-\partial^{-1}_{\zeta, \eta} (\series{q}/\series{p})\big) \]
-\[ \fmlsolproto = \frac{1}{\series{p}} \left(\frac{\zeta}{\eta}\right)^{\tau_\alpha} \exp\left[-\partial^{-1}_{\zeta, \eta} \left( \frac{\series{q}}{\series{p}} + \frac{\tau_\alpha}{\zeta} \right)\right] \]
-satisfies the equation $\fmlsolproto = \hardpart^\alpha \fmlsolproto$.
-Our expression for the prototype solution, taken from \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, gives a convergent power series expansion of the analytic prototype solution defined in \cite{reg-sing-volterra}.
-
-This definition of the prototype solution is taken from an intermediate step of the calculate in Section~3.2.1 \textcolor{orange}{\tt sec:construction} of \cite{reg-sing-volterra}, in which
-
-to express the prototype solution as a formal power series that satisfies the same equation.
-The definition of $\tau_\alpha$ ensures that $\series{q}/\series{p} + \tau_\alpha/\zeta$ is in $\C\llbracket \zeta_\alpha \rrbracket$, so $\fmlsolproto$ is in $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
-
-Next, we look for a perturbation $\fmlsolptb$ that makes $\fmlsolwhole = \fmlsolproto + \fmlsolptb$ a solution of the Volterra equation we're trying to solve.
-This is equivalent to solving the inhomogeneous equation
-\begin{equation}\label{eqn:inhomog-volterra2}
-\fmlsolptb = \softpart^\alpha \fmlsolproto + \volterra^\alpha \fmlsolptb
-\end{equation}
-The central idea of the proof is to show that $\softpart^\alpha$ maps $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ and that $\volterra^\alpha$ is a contraction of $\zeta_\alpha^{\tau_\alpha - 1} \C\llbracket \zeta_\alpha \rrbracket$.
-
-$\solproto$ lies in $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$, that $\softpart^\alpha$ maps $\singexpalg{\tau_\alpha - 1}(\Omega_\alpha)$ into $\singexpalg{\tau_\alpha}(\Omega_\alpha)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ when $\Lambda$ is large enough.
-It follows, by the contraction mapping theorem, equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$.
-More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
-Starting with any initial guess $\fmlsolptb^{(0)} \in \singexp{\tau_\alpha}{\Lambda}(\Omega_\alpha)$ and defining
-\begin{align*}
-\fmlsolptb^{(1)} & = \volterra^\alpha \fmlsolptb^{(0)} \\
-\fmlsolptb^{(2)} & = \volterra^\alpha \fmlsolptb^{(1)} \\
-\fmlsolptb^{(3)} & = \volterra^\alpha \fmlsolptb^{(2)} \\
-& \;\;\vdots
-\end{align*}
-we get a sequence of functions that converges in $\zeta_\alpha^{\tau_\alpha} \C\llbracket \zeta_\alpha \rrbracket$ to a solution.
-
-\textcolor{orange}{[Argument of Loday-Richaud\ldots]}
-\end{proof}
-\begin{proof}
-Let $\hat{\mathcal{P}}_\alpha$ be the Volterra operator defined in Section~4.5 of \cite{reg-sing-volterra}.
-Take any holomorphic function $\phi$ on $\Omega_\alpha$ with a well-defined Laplace transform $\Phi = \laplace_{\zeta,\alpha}^{\theta} \phi$ \textcolor{magenta}{[choose $\theta$]}.
-Lemma~2 of \cite{reg-sing-volterra} shows that $\hat{\mathcal{P}}_\alpha \phi = 0$ if and only if $\mathcal{P}\Phi = 0$ \textcolor{magenta}{[the lemma only states one direction; change it before publication to state both directions]}.
-
-As a consequence of Theorem~\ref{thm:sing-soln}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
-\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
-The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
-It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
-
-To show that $\Psi_\alpha$ is Borel regular, first observe that by \textcolor{orange}{[Erdelyi \S 1.6---cite in appdendix; to get uniformity, we might need a constant-width strip, rather than a sector]}, the asymptotic expansion $\series{\Psi}_\alpha = \aexp^\theta \Psi_\alpha$ satisfies the same differential equation that $\Psi_\alpha$ does.
-In addition, the leadeing term of $\series{\Psi}_\alpha$ is $z^{-\tau_\alpha}$.
-Thus, $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ satisfies the same intergral equation that $\psi_\alpha$ does, and its leading term is $\frac{1}{\Gamma(\tau_\alpha)} \zeta^{\tau_\alpha - 1}$.
-\end{proof}
-\color{black}
-
-%As a consequence of Theorem 4 in {\tt reg-volterra} we get 
-%
-%\begin{theorem}\label{thm1-dim}
-%In the previous set-up, there exists a unique solution of $\hat{P}_j\psi_j=0$ with $\zeta_j=\zeta-\alpha_j$ and
-%\begin{equation}\label{P-hat_j}
-%\hat{P}_j:=P(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\alpha_j-\zeta_j)^r
-%\end{equation}
-%such that $\psi_j$ blows up as $\zeta^{\tau_j-1}$ at $\alpha_j$:
-%${\psi}_j(\zeta_j)=\zeta_j^{\tau_j-1}+f_j$ and $f_j\in\mathcal{HL}^{\infty,-\tau_j}(\Omega_j)$ with $\Omega_j$.
-%\end{theorem}
-
 \color{black}
@@
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
-For each root $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in Figure \ref{Fig:domain}.
+For each root $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in the figure from Theorem~\ref{thm:exist_uniq_ODE}\textcolor{RoyalBlue}{[Figure \ref{Fig:domain}]}.
 We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.

### 2024-03-18 exp-resurgence.tex
Drop old text from intro to ODE results

@@
 This operator will always have an irregular singularity at $z = \infty$.
-
-\color{Goldenrod}
-[These details are right above in Section~\ref{borel-reg:explanatory-power}!]
-\begin{equation}%\label{eqn:standard ODE}
-\mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_{d-1}(z^{-1})\,\partial_z^{d-1} \big],
-\end{equation}
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial, and $R_j(z^{-1})$ are holomorphic in some disk $|z| > A$ around $z = \infty$, for every $j=0,\ldots, d-1$.\footnote{Looking at the existence theorem in \cite[Theorem 4]{reg-sing-volterra}, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.} Furthermore we assume $P$ has simple zeros $P(-\alpha_j)=0$, $j=1,...,d$, $P'(-\alpha_j)\neq 0$ for $j=1,...,d$ and $Q(-\alpha_j)\neq 0$.
-Our equation has an irregular singularity at $\infty$ (see \cite[Definition 3.3.2]{diverg-resurg--ii}).
-\color{black}
 \begin{verify}
+\par
 Turn the ODE into a system: assume 
@@
 hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
+\par
 \end{verify}
-
-\color{gray}
-[This is now a corollary; moved to historical.] Under these assumptions, the space of formal solutions of $\mathcal{P}\Phi = 0$ has a basis $\series{\Psi}_1,...,\series{\Psi}_d$ of the form~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}
-\begin{equation}\label{formal solution}
-\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\series{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-1} \rrbracket,
-\end{equation}
-where $\tau_j$ is the non-zero complex number $Q(-\alpha_j)/P'(-\alpha_j)$.
-Since the roots $-\alpha_1, \ldots, -\alpha_n$ are distinct, this form determines the basis up to scaling, giving the space of formal solutions a distinguished frame.
-\textcolor{orange}{Add that the formal series is $1$-Gevrey.} Classically it was proved that the formal solutions of \eqref{formal solution} are Borel-Laplace summable and their Borel-Laplace sums satisfy the original differential equation (see for example \cite{ramis1991series,malgrange92,malgrange1995sommation,diverg-resurg--ii}\textcolor{magenta}{[Braaksma,check]}).
-Therefore, the distinguished frame of formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ becomes a distinguished frame of analytic solutions $\hat{\Psi}_1,...,\hat{\Psi}_d$.
-
-However, can we find a distinguished basis for solutions in a purely analytic way?
-This should be possible because of our regularity assumptions about the coefficients of $\mathcal{P}$.
-In fact, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to a formal frame (see \cite[Theorem 3.1]{diverg-resurg-iii}), but it is not a constructive method (see \cite[Chapter 14]{balser}).
-\color{black} \color{Goldenrod}[Let us try to move most of this detail to the proof section.] Conversely, we can explicitly build a distinguished basis of analytic solutions: first going to the position domain, we can consider $d$ integral operators of the form
-\begin{equation}
-\hat{P}_j:=P(-\zeta)+\partial_{\zeta,\alpha_j}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha_j}^{-2}\circ\sum_{r=0}^{d-1}R_r(\partial_{\zeta,\alpha_j}^{-1})\circ (-\zeta)^r
-\end{equation}
-labeled by the roots of $P$.
-This type of operator is the one we studied in \cite{reg-sing-volterra}, hence we know there exists a unique solution $\psi_j$ of $\hat{P}_j\psi_j=0$, such that $\psi_j$ blows-up as $\zeta_j^{\tau_j-1}$ at $\zeta_j=0$ and it has a controlled behavior on an open domain $\Omega_j$ which is star-shaped at $\alpha_j$ and avoids the other critical points (see the definition in Section \ref{borel_reg-ODE}).
-In addition, $\psi_j$ can be Laplace transformed, giving a analytic function $\Psi_j:=\laplace_{\zeta_j}^{\theta}\psi_j$.
-At this point, we may ask what is the relationship between the two frames of analytic solutions, namely the Borel sum $\hat{\Psi}_j$ of the formal solutions $\series{\Psi}_j$ and the Laplace transform of $\psi_j$.
-Our main result says they are actually proportional, hence proving Borel summation works \textcolor{orange}{[add reminder of what it means for Borel summation to ``work'']}.\color{black}
-\textcolor{Cyan}{Using the dictionary for the Laplace transform associated with some point $\zeta = \alpha$ in the frequency domain, (link section), we can turn $\mathcal{P}$ into an integral operator $\hat{\mathcal{P}}_\alpha$.
-If we choose $-\alpha$ to be a root of $P$, then $\hat{\mathcal{P}}_\alpha$ will have a regular singularity at $\zeta = \alpha$, and we understand a lot of details about its specific form~\cite{reg-sing-volterra}.
-We show in~\cite{reg-sing-volterra} that $\hat{\mathcal{P}}_\alpha \phi = 0$ has a distinguished solution $\psi_\alpha$ which is characterized by having a power-law singularity with a known exponent $\tau_\alpha - 1$ at $\zeta = \alpha$ and having exponentially bounded growth at infinity.}
-
 We know from experience that we can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
@@
 %\end{theorem}
-%
-\textcolor{red}{[Change or actually delete]}We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
+
+\textcolor{red}{[Change or actually delete]}
+\color{Violet}We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
 On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$.
@@
 Therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\tilde{\psi}_j$ is indeed summable and ${\psi}_\alpha$ is the analytic continuation of $\tilde{\psi}_\alpha$.
-
+\color{black}
 \subsubsection{Why does Borel summation work for thimble integrals?}

### 2024-03-18 exp-resurgence.tex
Rearrange ODE reasoning to match intro

@@
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
-\color{BlueViolet}
+\color{DarkBlue}
 \begin{theorem}\label{thm:exist_uniq_ODE}
@@
 %%%\end{itemize}
+\color{DarkBlue}
+\begin{theorem}\label{re:thm:exist_uniq_ODE}
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
+of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
+\end{theorem}
+\begin{center}
+\begin{tikzpicture}
+\newcommand{\spill}{4}
+\fill[violet!20, bezier bounding box, path fading=radial edge]
+  (-\spill, -\spill) (\spill, \spill)
+  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
+\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
+\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+  \fill \p circle (0.7mm);
+}
+\end{tikzpicture}
+
+{\small The domain $\Omega_\alpha$}
+\end{center}
+\begin{proof}
+After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
+The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
+By Theorem~\ref{translation} and the results of Section~\ref{sec:reg-decay}, the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ is a left-invertible map
+\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha). \]
+With $\Psi_\alpha = \laplace^\theta_{\zeta, \alpha} \psi_\alpha$, the desired result follows.
+\end{proof}
 \color{BlueViolet}
@@
 
-\color{BlueViolet}
+\color{DarkBlue}
 Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
@@
 Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it is one-to-one everywhere else.
-\color{BlueViolet}
+\color{DarkBlue}
 \begin{center}
@@
 \textcolor{orange}{[Add flavor text]}
+\begin{theorem}[restatement of \ref{thm:is_Borel_sum}]\label{re:thm:is_Borel_sum}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
+\end{theorem}
+\begin{proof}
+Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
+\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
+of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4.
+To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
+We'll do this by showing that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+
+For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
+In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
+The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
+%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
+\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
+and the perturbation
+%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
+\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
+
+Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
+lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
+We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
+This is equivalent to solving the inhomogeneous equation
+\begin{equation}\label{eqn:inhomog-volterra}
+\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
+\end{equation}
+The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
+It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
+Defining
+\begin{align*}
+\solptb^{(0)} & = \softpart^\alpha \solproto \\
+\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
+\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
+\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
+& \;\;\vdots
+\end{align*}
+we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.
+
+In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
+\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
+which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
+\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
+and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
+Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.
+
+Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\{\zeta, \zeta^{-1}\}$.
+The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
+By definition \textcolor{orange}{[to be added to the paper]}, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+
+When we take the Borel sum of $\series{\Psi}_\alpha$, we start by retracing the construction steps described above.
+The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$, and summation then inverts the Taylor expansion, bringing us back to $\psi_\alpha$.
+We finish the Borel summation by taking the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$, giving $\Psi_\alpha$ by definition.
+\end{proof}
+\textcolor{orange}{[Add flavor text]}
 \begin{lemma}\label{lem:laplace-bridge}
@@
 \end{proof}
+\color{BlueViolet}
 We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
@@
 
-Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\llbracket \zeta, \zeta^{-1} \rrbracket$.
-The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\llbracket \zeta \rrbracket$.
+Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\{\zeta, \zeta^{-1}\}$.
+The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
 Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.

### 2024-03-24 exp-resurgence.tex
Fixing mistakes noted by Aaron

@@
 
-The particular classes of problems we look at are level~1 ODEs and exponential period integrals over Lefschetz thimbles.
+The particular classes of problems we look at are level~1 ODEs and exponential period integrals over one dimensional Lefschetz thimbles.
 To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
@@
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we're allowed to take the Laplace transform at another point $b \in B$.
+This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we are allowed to take the Laplace transform at another point $b \in B$.
 This would be natural in our study of ODEs and thimble integrals.}
@@
 \begin{enumerate}
-\item Solving a single-level linear ODE, with level~$1$ \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii} \textcolor{orange}{[awkward?]}.
+\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
 Equation~\eqref{eqn:bessel-rescaled-1} is an example.
@@
 Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the spatial domain.
+On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
+
+We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thibmle}, for ODEs and thimble integrals, respectively.
+The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
 \subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
@@
 \end{verify}
-We know from experience that we can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
+We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
 However, this only works when there's a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
@@
 
-Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$.
+Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}.
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
@@
 \begin{theorem}\label{thm:exist_uniq_ODE}
-Choose a root $-\alpha$ of $P$.
-Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+Let $-\alpha$ be a root of $P$.
+Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
@@
 By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
-\begin{theorem}\label{thm:is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
+\begin{theorem}\label{thm:soln_is_Borel_sum}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
 \end{theorem}
 With a little more work, encapsulated in Lemma~\textcolor{orange}{?} from Section~\textcolor{orange}{?}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
-\begin{theorem}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:is_Borel_sum}.
+\begin{theorem}\label{thm:soln_is_asymptotic}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
 \end{theorem}
-\begin{corollary}
+\begin{corollary}\label{cor:soln_borel-reg}
 The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
 \end{corollary}
+From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
+On the other hand, if you prefer to work formally, you can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
+We do this in Section~\ref{sec:new-summability-proof}.
+
+In addition, as a consequence of Corollary~\ref{cor:soln_borel-reg} we deduce that the set of solutions $\Psi_\alpha$ for $-\alpha$ root of $P$, gives a frame of Borel regular solutions of equation $\mathcal{P}\Phi=0$.
+
+\textcolor{magenta}{[Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.]}
+
+\textcolor{orange}{[Prove existence of a frame of Borel regular solutions?]}
 \color{black}
-%%\color{Maroon}
-%%\begin{theorem}\label{thm:borel_reg_ODE}
-%%Choose a root $-\alpha$ of $P$.
-Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-Equation $\mathcal{P}\Psi=0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-%%\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-%%of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}. That solution is Borel regular.
-%%\end{theorem}
-%%\textcolor{violet}{If you prefer to work in the analytic world, you can use this result to prove the existence and Borel summability of special formal transmonomial solutions.}
-%%\begin{corollary}\label{cor:borel_reg_ODE}
-%%For each root $-\alpha$ of $P$, equation $\mathcal{P}\Psi=0$ has a formal solution in the transmonomial space $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$, which is unique up to scaling.
-That solution is Borel summable, and its Borel sum is a constant multiple of $\Psi_\alpha$.
-%%\end{corollary}
-\textcolor{BlueViolet}{From an analytic perspective, Theorem~\ref{thm:is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
-On the other hand, if you prefer to work formally, you can take the Poincar\'{e} solutions as given and use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
-We do this in Section~\ref{sec:new-summability-proof}.}
-%%\textcolor{violet}{On the other hand, if you prefer to work in the formal world, you can use Theorem~\ref{thm:borel_reg_ODE} to show that the Poincar\'{e} solutions are Borel summable.
-See Section~\ref{sec:new-summability-proof}.}
-%%\textcolor{violet}{[In another section, do the ``mirror image'' argument.
-Use the Poincar\'{e} algorithm to construct a formal transmonomial solution in the classical way.
-Use the Ramis Index Theorem to show that it is Gevrey-$1$, and then then use our existence and uniqueness result for regular singular Volterra equations to show that it is not only Gevrey-$1$, but in fact Borel summable.]}
-%%The formal solution whose existence is shown in Corollary~\ref{cor:borel_reg_ODE} is the Poincar\'{e} solution.
-%%\begin{corollary}
-%%\textcolor{orange}{[The Poincar\'{e} solution is Borel summable.]}
-%%\end{corollary}
-\color{black}
-\textcolor{Violet}{[This is sort of a mirror image of the Ramis Index Theorem?]}
-%\begin{theorem}[see Theorem \ref{thm2-dim}]\label{thm2}
-%The formal frame of solutions $\tilde{\Psi}_j$ is Borel summable \textcolor{orange}{[summability is the strongest part of the result]} and its Borel sum is proportional to $\Psi_j$.
-In fact, $\Psi_j$ is a Borel regular solution of \eqref{eqn:standard ODE}.
-\textcolor{orange}{[Alternate statement: look in Sauzin or Delabaere to get uniqueness of formal solution.]} \textcolor{orange}{[Split into theorem, which shows existence of Borel regular frame, and corollary, which shows that this implies a certain frame of formal solutions is Borel-summable and sums to actual solutions.]}
-%\end{theorem}
-
-\textcolor{red}{[Change or actually delete]}
-\color{Violet}We summarize the main steps of the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE} (the rigorous proofs are given in Section~\ref{borel_reg-ODE}).
-On the right-hand side of the diagram, we have the formal solution $\series{\Psi }_\alpha\in e^{-\alpha z}z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$ and its Borel transform $\series{\psi}_\alpha$.
-%Then, the theory of $1$-summability allows us to draw the ``square'' with corners $\hat{\psi}_j$ and its Laplace transform $\hat{\Psi}_j$.
-
-\begin{center}
-\begin{tikzcd}
-& & \text{ODE }\arrow[dd,"\laplace^{-1}",swap] & & \\
- {\Psi}_\alpha\arrow[urr, no head, tail] & & & & \tilde{\Psi}_\alpha\arrow[llu,"\text{formal}",swap, no head, tail]\arrow[dd,"\borel"]\\
-& & \text{IE} & & \\
-\psi_\alpha\arrow[urr, no head, tail]\arrow[uu,"\laplace"]\arrow[r,equal] & \hat{\psi}_\alpha & & & \tilde{\psi}_\alpha\arrow[llu, no head, tail]\arrow[lll,"\text{sum}"]
-\end{tikzcd}
-\end{center}
-
-Conversely, on the left-hand side, by our existence and uniqueness result \cite[Theorem 4]{reg-sing-volterra} we have an analytic function $\psi_\alpha$ with a distinguished behaviour near $\zeta=\alpha$, which solves the integral equation (IE) obtained as the inverse Laplace transform of the (ODE) (see \cite[Lemma 2]{reg-sing-volterra}).
-The key step is then comparing $\psi_\alpha$ and $\tilde{\psi}_\alpha$.
-First, by the properties of the Borel transform, it is easy to show that $\series{\psi}_\alpha$ is a formal solution of the integral equation (IE).
-Then, from the explicit formula for $\tilde{\Psi}_\alpha$, we can show that if $\tilde{\psi}_\alpha$ grows as $\psi_\alpha$ near $\zeta=\alpha$.
-Therefore, by our uniqueness result \cite[Theorem 4]{reg-sing-volterra}, we conclude that $\tilde{\psi}_j$ is indeed summable and ${\psi}_\alpha$ is the analytic continuation of $\tilde{\psi}_\alpha$.
-\color{black}
-\subsubsection{Why does Borel summation work for thimble integrals?}
+\subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thibmle}
 %\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
@@
 The Lefschetz thimble $\Lambda_a^\theta$ can be regarded as the component of $f^{-1}(\Gamma_\alpha^\theta)$ that goes through $a$.
-\textcolor{orange}{We could orient so that shifting $\Lambda_a$ to its left would make its projection run clockwise around $\Gamma_\alpha$.
+\textcolor{orange}{We could orient the thimble so that shifting $\Lambda_a$ to its left would make its projection run clockwise around $\Gamma_\alpha$.
 However, this only seems to be possible when $X$ is 1-dimensional.}
-
 \begin{figure}[ht]
@@
 \end{figure}
-Choose $a$ a ciritcal point of $f$ and $\alpha=f(a)$, let $I$ be the thimble integral through the thimble $\Lambda_a^\theta$,
+Choose a ciritcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:
 \begin{equation}
-I(z)\defeq\int_{\Lambda_a^\theta}e^{-zf}\nu
-\end{equation}
-our main results show that $I$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into Laplace transforms. We recall the well-known result
-\begin{lemma}[see Lemma \ref{lem:thimble_proj_formula-proof}]\label{lem:thimble_proj_formula}
-A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
+I_\alpha(z)\defeq\int_{\Lambda_a^\theta}e^{-zf}\nu.
+\end{equation}
+Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\Lambda_a^\theta)$.
+\textcolor{RoyalBlue}{[say more about this?]}.
+\textcolor{orange}{[As a start\ldots]} We recall the well-known result
+\begin{lemma}\label{lem:thimble_proj_formula}
+A function $\iota$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula}
-\iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda^\theta(\zeta)}\nu \right),
+\iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda^\theta(\zeta)}\nu \right),
 \end{equation}
@@
 %\end{remark}
-Then, Borel regularity for thimble integrals is stated in the following theorem: 
-\begin{theorem}[see Theorem \ref{thm:maxim-proof}]\label{thm:maxim}
-If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
+Then, the Borel regularity of thimble integrals is established by the following theorem: 
+\begin{theorem}\label{thm:maxim}
+If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Recall that $\theta$ is the direction of the ray $\Gamma^\theta_\alpha$.
-\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
-\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
+\item\label{part-2} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
 \end{enumerate}
@@
 \color{RoyalBlue}
-We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
+\textcolor{orange}{[Shorten, but maybe keep the basics.]} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
 %\[
@@
 Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
+
+\textcolor{magenta}{Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.}
 \color{black}
@@
 %\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we're trying to solve an ODE.
+%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we are trying to solve an ODE.
 %\end{itemize}
@@
 The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}.
-Then, Section~\ref{sec:proof_main_results} contains proofs of the main results: Theorem~\ref{thm:borel_reg_ODE} and Theorem~\ref{thm:maxim}.
+Then, Section~\ref{sec:proof_main_results} contains proofs of the main results.
 Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
@@
 At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
-This is possible, as we proved in~\cite{reg-sing-volterra}, and by our construction, these solutions turn out to be uniform 1-Gevrey asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Corollary~\ref{cor:borel_reg_ODE}).
-As briefly discussed in Section~\ref{sec:why_borel_ODE} in the sketch the proof of Theorem~\ref{thm:borel_reg_ODE} and Corollary~\ref{cor:borel_reg_ODE}, our result is based on going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
-Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange~\cite{malgrange--fourier} solves differential equations analytically in the position domain, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}).
+Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
+Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange solves differential equations analytically in the position domain~\cite{malgrange--fourier}, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
 
@@
 \textbf{Frequency domain} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
-\textbf{Position domain} & \'{E}calle: resurgence \textcolor{orange}{$\longleftarrow$} & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
+\textbf{Position domain} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
 & Fixed-point iteration~\cite{reg-sing-volterra} \\
@@
 
-In Section~\ref{borel_reg-ODE}, we show that we're all finding the same frame.
-The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and the properties of the Laplace transform guarantee that our solutions, cast into in the frequency domain, are asymptotic to Poincar\'{e}'s.
+In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame.
+The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and Theorem~\ref{thm:exist_uniq_ODE} guarantees that our solutions are asymptotic to Poincar\'{e}'s ones.
 \end{remark} 
@@
 \textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly.
-However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we're looking for.
+However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we are looking for.
 In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
@@
 \subsection{Analysis of the Laplace transform}\label{sec:laplace_analytic}
-
+%
 \subsubsection{Regularity and decay properties}\label{sec:reg-decay}
 %
-Let $\Omega_b \subset B$ be an open, simply connected set that touches but does not contain $\zeta=b$ (see Figure \ref{Fig:domain}).
-Suppose $\Omega_b$ contains the ray $\Gamma_{\zeta,b}^\theta$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_b)$ of holomorphic functions on $\Omega_b$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta|^\sigma$ as $\zeta$ approaches $b$.
-When $\sigma>-1$, the singularity at $\zeta=b$ is integrable.
-Hence, the Laplace transform $\laplace_{\zeta, b}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_b)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > 0$ in the fiber $T_{\zeta=b}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
-%Let us say a function $f$ is in $O_{\zeta, \alpha \leftarrow}(g)$ or $O_{\zeta, \alpha \rightarrow}(g)$, respectively, if $|f| \lesssim g$ on some neighborhood of the starting point or infinite end of $\Gamma_{\zeta, \alpha}$.
-A function is {\em subexponential} along $\Gamma_{\zeta, \alpha}$ if it is in $O_{\zeta, \alpha \rightarrow}(e^{c\zeta})$ for all $c > 0$ \textcolor{magenta}{[shall we write in formula?]}.
-Let $\mathcal{E}_{\zeta, \alpha}$ be the space of functions that are subexponential on $\Gamma_{\zeta, \alpha}$, integrable at the starting point, and locally integrable throughout.
-If $f$ is in $\mathcal{E}_{\zeta, \alpha}$, then $\laplace_{\zeta, \alpha} f$ is well-defined and holomorphic for $\Re(z) > 0$ on the part of $T^*B$ that lies over $\Gamma_{\zeta, \alpha}$~\cite[Section  5.6]{diverg-resurg-i}.
-
-\color{RoyalBlue}{$\singexpalg{\sigma}(\Omega_\alpha^\Lambda)$}
+\textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
+Suppose $\Omega_\beta$ contains the ray $\Gamma_{\zeta, \beta}^\theta$.
+In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$.
+When $\sigma>-1$, the singularity at $\zeta = \beta$ is integrable.
+Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
+
 \color{Maroon}
@@
 \end{proof}
-\color{RoyalBlue}
-\textcolor{orange}{[We might be able to remove the decay properties completely!]} The asymptotics of $f$ at the starting point of $\Gamma_{\zeta, \alpha}^\theta$ control the asymptotics of $\laplace_{\zeta, \alpha}^\theta f$ at the infinite end of $\Gamma_{z, 0}$.
-Once we see how this works for $\alpha = 0$, Section~\ref{translation} will do the rest.
-In addition, we will set $\theta=0$ to keep the notation simpler, but the results hold for every angle $\theta$.
-Let $F = \laplace_{\zeta, 0} f$.
-Equation~1.8 of \cite{laplace-tfm} shows\footnote{The argument cited still works in our generality.
-For holomorphic $f$, one can also use \cite[Equation 1.5]{sternin1995borel}.} that
-\[ f \in O_{\zeta, 0 \leftarrow}(1) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z}\right). \]
-More generally, for $\sigma > -1$ \textcolor{magenta}{[prove or cite]},
-\[ f \in O_{\zeta, 0 \leftarrow}(\zeta^\sigma) \quad\Longrightarrow\quad F \in O_{z, 0 \rightarrow}\left(\frac{1}{z^{1 + \sigma}}\right). \]
-Exact power law asymptotics relate similarly \textcolor{magenta}{[prove or cite]}:
-\[ f \sim \zeta^\tau \text{ at the start of } \Gamma_{\zeta, 0} \quad\Longrightarrow\quad F \sim \frac{\Gamma(1+\tau)}{z^{1+\tau}} \text{ at the end of } \Gamma_{z, 0}. \]
-\textcolor{magenta}{[The big-$O$ asymptotics dictionary is interesting, but we might not need it. Consider dropping.]}
 \color{black}
 %
-%
-%
 \subsection{The geometry of the Borel transform}\label{sec:geometry_borel}
+%
 The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
 \[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
-Here, we're thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
+Here, we are thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
 We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
@@
 \end{center}
-and it extends to formal power series by linearity 
+and it extends to formal power series by countable linearity:
 \begin{align*}
@@
 \end{align*}
-\begin{remark}
-The definition of the Borel transform can be easily extended to fractional power of $z$: indeed notice that   
+This definition extends straightforwardly to fractional powers of $z$. Observing that   
 \[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
-for every $\sigma\in\R\setminus\Z_{\leq 0}$. Thus 
-\begin{align*}
-\borel_\zeta(z^{-\sigma-1})\defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)} 
-\end{align*}
-and then extended by linearity to $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$. 
-\end{remark}
+for every $\rho \in \R \setminus \Z_{\leq 0}$, we define 
+\begin{align*}
+\borel_\zeta[z^{-\rho-1}] \defeq \frac{\zeta^{\rho}}{\Gamma(\rho+1)}.
+\end{align*}
+Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
 %\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
@@
 %\end{align*}
-If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
-\[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
-has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
-\begin{align*}
-  \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
-  &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
-  &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
-\end{align*}
-As a result, we can recover the Taylor series $\series{\varphi}$ from the series
-\[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
-using the Borel transform:
-\begin{align*}
-\borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
-&=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
-\end{align*}
-We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*_{\zeta = 0}B$.
-
-If we'd expanded $\varphi$ as a Taylor series ${\varphi}_b$ in the translated coordinate $\zeta_b$ from above, we could have taken the Laplace transform $\laplace_{\zeta_b,0}$ instead, giving a power series in $z^{-1}$ that represents a function on $T^*_{\zeta = b}B$.
-Using the Borel transform with respect to $\zeta_b$, defined like the formal inverse of $\laplace_{\zeta_b,0}$
+% \textcolor{PaleVioletRed}{[I can't quite see what this paragraph is doing.]} If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
+% \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
+% has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
+% \begin{align*}
+%   \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
+%   &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
+%   &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
+% \end{align*}
+% As a result, we can recover the Taylor series $\series{\varphi}$ from the series
+% \[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
+% using the Borel transform:
+% \begin{align*}
+% \borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
+% &=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
+% \end{align*}
+% We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*_{\zeta = 0}B$.
+
+On a different fiber of $T_{\zeta=b}^*B$, the Borel transform $\borel_{\zeta_b}$ in the translated coordinate $\zeta_b$ is defined as the inverse of the Laplace transform $\laplace_{\zeta_b,0}$ on monomials
 \begin{center}
@@
 \end{center}
-and extended to formal power series by linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$,
+and extended to formal power series by countable linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$.
 %\begin{align*}
@@
  %%\end{align*}
-we could again recover ${\varphi}_b$.
+%we could again recover ${\varphi}_b$.
 
@@
 
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
+A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[what does this mean?]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
 
@@
 \subsubsection{Action on translations in the frequency domain}
-Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can deduce how $\borel_\zeta$ acts on translations in the frequency domain, namely we can show that for $\varphi=\sum_{n=0}^\infty a_n z^{-n-1}$
-\[\borel_\zeta \mathsf{T}_{-c}^* \varphi=e^{-c\zeta }\borel_\zeta\varphi.\]
+Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
+It turns out that
+\[ \borel_\zeta \mathsf{T}_{-c}^* \series{\Phi} = e^{-c\zeta }\borel_\zeta \series{\Phi} \]
+for all $\series{\Phi} \in z^{-1}\,\C\llbracket z^{-1} \rrbracket$.
 Indeed, the following diagram
@@
 \subsection{Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
-The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-algebra homomorphisms between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.
-
-In fact, since $\borel_\zeta$ is deifned as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by linearity.
+The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-linear map between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.
+In fact, since $\borel_\zeta$ is deifned as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity.
 As a result, we find that the \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\]
-is a $\C$-algebra isomorphism whose inverse is the formal Laplace transform.
+is a $\C$-linear invertible map whose inverse is the formal Laplace transform.
+
+In addition, on both $\C\llbracket\zeta\rrbracket$ and $\C\llbracket z^{-1}\rrbracket$ there is the natural product given by the Cauchy product of formal power series, and by definition, the Borel transform extends to a $\C$-algebra isomorphism with inverse given by the formal Laplace transform.
 
 However, as we discussed in Section~\ref{sec:reg-decay}, the Laplace transform $\laplace_{\zeta,0}$ is naturally defined on the space of integrable, holomorphic functions, namely $\singexpalg{\sigma}(\Omega)\subset \zeta^{\sigma}\C\lbrace\zeta\rbrace$ for $\sigma>-1$, hence we might expect it extends to a $\C$-algebra homomorphism from $\singexpalg{\sigma}(\Omega)$ to $\mathcal{O}(H)$.
-Indeed, that's the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$.
+Indeed, that is the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$.
 We will discuss it in Section~\ref{convolution}.
@@
 \begin{notation*}
-We want to distinguish between formal series and holomorphic functions, as well as between the spatial domain (Borel plane) and the frequency domain ($z$-plane).
-Therefore we adopt the following notation:
+In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane).
+We have adopted a variable naming convention that makes these distinctions apparent at a glance.
+\color{LimeGreen}
+\begin{center}
+\begin{tabular}{c|c|c}
+& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\varphi$ & $\series{\varphi}$ \\[1mm]
+\end{tabular}
+\end{center}
+
+%%\begin{tabular}{ll}
+%%$\Phi$ & Upper-case letters without tildes represent holomorphic functions on the frequency domain.
+%%\end{tabular}
+\color{black}
 \begin{itemize}
-\item $\Phi$: upper-case letters are holomorphic functions on the frequency domain;
+\item $\Phi$: upper-case letters represent holomorphic functions on the frequency domain;
 \item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
@@
 Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we'd run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
+The condition $\alpha \in (0, 1)$ saves us from the trouble we would run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
 This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
@@
 \textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
+\color{DarkBlue}
+\subsection{Bridging the gap between analytic and formal objects}
+The spaces $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
+To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$.
+We need a way to make sure we stay in the subspace where the Taylor series exists.
+
+To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
+In the result below, our conditions on the open set $\Upsilon \subset \widetilde{\C^\times}$ imply that the projection $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$.
+A holomorphic function on $\pi \Upsilon$ is therefore guaranteed to have a Laurent series expansion around $\zeta = 0$.
+In fact, a holomorphic function on $\Upsilon$ will have a Laurent series expansion around $\zeta = 0$ only if it descends to a holomorphic function on $\pi \Upsilon$.
+In other words, by pulling back along $\pi$, we can think of the holomorphic function space $\mathcal{O}(\pi \Upsilon)$ as the subspace of $\mathcal{O}(\Upsilon)$ where the Laurent series around $\zeta = 0$ exists.
+
+\textcolor{RoyalBlue}{Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
+The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.}
+
+\begin{lemma}\label{lem:shifted_holo_closed}
+Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$.
+Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
+\begin{center}
+\begin{tikzpicture}
+  \newcommand{\spill}{4}
+  \fill[violet!20, bezier bounding box, path fading=radial edge]
+    (-\spill, -\spill) (\spill, \spill)
+    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
+  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
+  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
+  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
+  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+    \fill \p circle (0.7mm);
+  }
+\end{tikzpicture}
+\end{center}
+For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
+\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
+\end{lemma}
+\begin{proof}
+Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
+The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
+Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
+\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
+is bounded. The intersection of $\zeta^\rho\,\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho} - 1)$, so it is closed.
+\end{proof}
+If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$.
+That means its Laurent series is actually a Taylor series.
+\begin{prop}\label{prop:shifted_holo_series}
+Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
+\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
+\end{prop}
+\begin{proof}
+Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$.
+The definition of $\singexp{\sigma}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^\sigma |\varphi|$ is bounded on a punctured disk around $\zeta = 0$, which would be impossible if $\series{\varphi}$ included any $\zeta^{\rho-1},\;\zeta^{\rho-2},\;\zeta^{\rho-3}\ldots$ terms.
+That means $\series{\varphi}$ must belong to $\zeta^\rho\,\C\{\zeta\}$.
+\end{proof}
+
+Taylor expansion and summation form a two-way link between holomorphic functions and formal power series.
+For regular enough functions, the Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain.
+\textcolor{orange}{[Compare with Sokal's version of the Watson--Nevanlinna theorem?]}
+\begin{lemma}\label{lem:laplace-bridge}
+Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less.
+Take some $\rho \in (-1,\infty)$.
+If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to \textcolor{orange}{[backwards terminology?]} the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
+\textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
+\end{lemma}
+\begin{proof}
+By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+Write $\series{\varphi}$ out in the form
+\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
+observing that
+\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
+For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
+\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
+Taking the Laplace transform of both sides, we learn that
+\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
+where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.
+
+Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$.
+This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
+\begin{align*}
+|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
+& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
+& \lesssim \Delta^{-1}
+\end{align*}
+along any ray. This, as discussed above, proves the desired result.
+\end{proof}
+\color{black}
 \section{Proof of main results}\label{sec:proof_main_results}
@@
 \color{DarkBlue}
-\begin{theorem}\label{re:thm:exist_uniq_ODE}
+\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
 Choose a root $-\alpha$ of $P$.
@@
 Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
-
 \color{DarkBlue}
-Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
-The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
-\begin{lemma}\label{lem:shifted_holo_closed}
-Consider a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ which touches $\zeta = 0$ and is star-shaped around $\zeta = 0$.
-Suppose that $\pi \maps \Upsilon \to \C^\times$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C^\times$ which is star-shaped around $\zeta = 0$, and it is one-to-one everywhere else.
-
-\color{RoyalBlue}\textcolor{orange}{[Rephrase more generally, without referring to $P$.} 
-$\tilde{\C}$
-Choose a root $-\alpha$ of $P$.
-Consider a simply connected open set $\Upsilon \subset \widetilde{B}_{P(-\zeta)}$ which touches but doesn't contain $\zeta = \alpha$, is star-shaped around $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
-Suppose that $\pi \maps \Upsilon \to \C$ overlaps itself at the edges: it is two-to-one over a simply connected open set $\Upsilon_\Delta \subset \C$ which is star-shaped around $\zeta = \alpha$, and it is one-to-one everywhere else.
-\color{DarkBlue}
-\begin{center}
-\begin{tikzpicture}
-  \newcommand{\spill}{4}
-  \fill[violet!20, bezier bounding box, path fading=radial edge]
-    (-\spill, -\spill) (\spill, \spill)
-    (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
-  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
-  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
-  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
-  \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-    \fill \p circle (0.7mm);
-  }
-\end{tikzpicture}
-\end{center}
-For any $\rho' \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma' \in (\rho'-1, \rho']$, the intersection
-\[ \zeta^{\rho'}\,\pi^*\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma'}{\Lambda}(\Upsilon) \]
-is a closed subspace of $\singexp{\sigma'}{\Lambda}(\Upsilon)$.
-\end{lemma}
-\begin{proof}
-Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
-The {\em variation} operator $\var \maps \singexp{\sigma'}{\Lambda}(\Upsilon) \to \singexp{\sigma'}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
-Our notation follows the convention of \cite{diverg-resurg-i}, described before Definition~6.46.}
-\[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
-is bounded.
-The intersection of $\zeta^{\rho'}\,\pi^*\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma'}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho'} - 1)$, so it is closed.
-\end{proof}
 \textcolor{orange}{[Add flavor text]}
-\begin{theorem}[restatement of \ref{thm:is_Borel_sum}]\label{re:thm:is_Borel_sum}
+\begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
 The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
@@
 lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
-We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we're trying to solve.
+We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we are trying to solve.
 This is equivalent to solving the inhomogeneous equation
@@
 
-Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\{\zeta, \zeta^{-1}\}$.
-The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
+We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
 By definition \textcolor{orange}{[to be added to the paper]}, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
@@
 \textcolor{orange}{[Add flavor text]}
-\begin{lemma}\label{lem:laplace-bridge}
-\textcolor{orange}{[Move to Laplace transform section?]} Consider an open sector $\Omega$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, but with its tip at $\zeta = 0$.
-Take some $\rho \in (-1,\infty)$.
-If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
-\textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
-\end{lemma}
+\begin{theorem}[restatement of \ref{thm:soln_is_asymptotic}]\label{re:thm:soln_is_asymptotic}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
+\end{theorem}
 \begin{proof}
-By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
-Write $\series{\varphi}$ out in the form
-\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
-observing that
-\[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
-For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
-\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
-Taking the Laplace transform of both sides, we learn that
-\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
-where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.
-
-Proposition~\ref{prop:laplace-cont} tells us \textcolor{orange}{[as long as the opening angle of $\Omega$ is less than $\pi$]} that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$.
-This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
-\begin{align*}
-|z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
-& = \big(|z|/\Delta\big)^{\rho+n} \Delta^{-1} \\
-& \lesssim \Delta^{-1}
-\end{align*}
-along any ray. This, as discussed above, proves the desired result.
-
-%%\[ \varepsilon_n = a_n \zeta^{\rho+n} + a_1 \zeta^{\rho+n+1} + a_2 \zeta^{\rho+n+2} + a_{n+3} \zeta^{\rho+n+3} + \ldots \]
+In the proof of Theorem~\ref{re:thm:soln_is_Borel_sum}, we showed that the position-domain solution $\psi_\alpha \in \singexpalg{\tau_\alpha-1}(\Upsilon)$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
+Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi_\alpha}$ is the formal Laplace transform of $\series{\psi}_\alpha$, the desired result follows from Lemma~\ref{lem:laplace-bridge}.
 \end{proof}
 \color{BlueViolet}
-We're now ready to show that the solution $\Psi_\alpha$ is Borel regular.
+We are now ready to show that the solution $\Psi_\alpha$ is Borel regular.
 \begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
@@
 Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
-Let $I$ be the thimble integral
+Let $I_\alpha$ be the thimble integral
 \begin{equation}\label{exp-int}
-I \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
-\end{equation}
-where $\Lambda_a^\theta$ is the thimble through the critical point $a$.
+I_\alpha \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
+\end{equation}
+where $\Lambda_a^\theta$ is the thimble through the critical point $a$ and $\alpha=f(a)$.
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I$ as the Laplace transform of a function $\iota$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
+The first step will be to rewrite $I_\alpha$ as the Laplace transform of a function $\iota_\alpha$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
 \begin{lemma}\label{lem:thimble_proj_formula-proof}
-\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota$ with $I = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
+\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula-proof}
-    \iota = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
+    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
 \end{equation}
@@
 \begin{proof}
-    Let us recast the integral $I$ into the position domain.
+    Let us recast the integral $I_\alpha$ into the position domain.
 As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\Lambda_\alpha^\theta(\zeta)$ sweep backward along $\Lambda^-_\alpha(\zeta)$ and forward along $\Lambda^+_\alpha(\zeta)$, respectively.
@@
 \begin{align*}
-I(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
+I_\alpha(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
 & = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}\,d\zeta.
@@
 \begin{equation}\label{thimble-difference}
-{\iota}(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
+{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
 \end{equation}
 \end{proof}
-We will now prove that $I$ is Borel regular:
+We will now prove that $I_\alpha$ is Borel regular:
 \begin{theorem}\label{thm:maxim-proof}
-If the integral defining $I$ is absolutely convergent, then $I$ is Borel regular. More explicitly: 
+If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: 
 \begin{enumerate}
-\item\label{part-1} As $z \to \infty$ along the ray $z \in e^{-i\theta}\,\R_{>0}$, the function $I$ is asymptotic to a trans-monomial $\tilde{I}\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item\label{part-2} The series $\tilde{I}$ is $1$-Gevrey. In other words, $\tilde{\iota} \defeq \borel_\zeta \tilde{I}$ converges near $\zeta=\alpha$.
-\item\label{part-3} If you continue the sum of $\tilde{\iota}$ along the ray $\Gamma_\alpha^\theta$, and take its Laplace transform along that ray, you'll recover $I$.
+\item\label{part-1} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-2} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
 \end{enumerate}
@@
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{z \alpha} I \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{z \alpha} I_\alpha \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 as $z \to \infty$. Plugging in the Taylor series for $\nu$, we get
 \begin{align*}
-e^{z \alpha} I & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
+e^{z \alpha} I_\alpha & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
 & = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau.
@@
 \begin{align*}
-e^{z \alpha} I & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+e^{z \alpha} I_\alpha & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
 & = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
@@
 
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha} I(z)$.
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha} I_\alpha(z)$.
 In other words,
-\[ e^{z \alpha} I(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\[ e^{z \alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 To see why, cut the sum off after $N$ terms, and observe that
@@
 The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{z\alpha} I(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
-Hence, defining the formal series $\tilde{I}$
-\[\tilde{I}(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
-we get $\tilde{I}\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
+\[ e^{z\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
+Hence, defining the formal series $\tilde{I}_\alpha$
+\[\tilde{I}_\alpha(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
+we get $\tilde{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
 
@@
 \begin{align*}
-\tilde{\iota} & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
+\tilde{\iota}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
 &= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
@@
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with $\tilde{\iota}$.
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\tilde{\iota}_\alpha$.
 We can rewrite the Taylor series for $\nu$ as
@@
 taking the positive branch of the square root on $\Lambda^+_a$ and the negative branch on $\Lambda^-_a$.
-Plugging this into our expression for $\iota$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
-\begin{align*}
-\iota & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_a(\zeta)}^{\operatorname{end} \Lambda_a(\zeta)} \\
+Plugging this into our expression for $\iota_\alpha$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
+\begin{align*}
+\iota_\alpha & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_a(\zeta)}^{\operatorname{end} \Lambda_a(\zeta)} \\
 & = \sum_{m \ge 0} b_m^a \Big( [2\zeta_\alpha]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_\alpha]^{(m - 1)/2} \Big) \\
@@
 \end{align*}
-In particular, $\tilde{\iota}$ can be analytically continued along $\Gamma_\alpha^\theta$ and its sum is given by $\iota$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
+In particular, $\tilde{\iota}_\alpha$ can be analytically continued along $\Gamma_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
+%Thus, we can take the Laplace transform of $\phi_j$ and we find
 %\begin{align*}
@@
 \begin{remark}\label{rmk:1/2-deriv}
-    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi=z^{-1/2}I$, as its asymptotics won't have fractional power singularities.
-The proof follows the same argument we chose for $I$, but there's one subtulty to be aware of when rewriting $\Phi$ as the Laplace transform of a function $\phi$.
-Indeed, first notice that \[\phi = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota \]
+    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
+The proof follows the same argument we chose for $I_\alpha$, but there's one subtulty to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
+Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota_\alpha \]
     Then, we can take the $1/2$ fractional integral on both sides:
     \begin{align*}
-        \fracderiv{-1/2}{\zeta}{\alpha} \phi &= \fracderiv{-1}{\zeta}{\alpha} \, \iota \\
+        \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha &= \fracderiv{-1}{\zeta}{\alpha} \, \iota_\alpha \\
         & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\Lambda_a^\theta(\zeta)}\nu \right) \\
@@
     The second term vanishes because $\Lambda_\alpha^\theta(\alpha)$ is a single point, leaving
-    \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
+    \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
     Finally, we apply the $1/2$ derivative of both sides, recalling that it is a left inverse of the $1/2$ integral, and we find
-    \begin{equation}\label{eqn:formula--1/2}\phi= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
+    \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
     \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
@@
 \subsubsection{The big idea}\label{big-idea}
-We're going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
+We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
 We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
@@
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
-We're assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length isproportional to $st$, giving
+We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length isproportional to $st$, giving
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
@@
 \color{black}
-We're going to look for functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
+We are going to look for functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
 We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies equation~\eqref{eqn:triangular_cantilever} if and only if $v$ satisfies the integral equation
@@
 \textcolor{orange}{[Stokes? Thimbles?]}
+
+\textcolor{orange}{Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$}
 %\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}
-
+%
 \appendix
-
+%
 \section{The Airy equation}\label{airy-appendix}
-
+%
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 \end{equation}
-
+%
 \subsection{Asymptotic analysis}
@@
 This is an evidence of \cite[Theorem~4]{reg-sing-volterra}.
-
+%
 \subsection{Building a distinguished frame of analytic solutions}
@@
 From these expressions, we also noticed that $\hat{\phi}_i$ are simple resurgent functions.   
-
+%
 \subsection{Comparison with other treatments of the Airy equation}
-
-\subsubsection{Different Borel transform convention} Physicists often use a different version of the Borel transform:
+%
+\subsubsection{Other conventions for the Borel transform}
+%
+Physicists often use a different version of the Borel transform:
 \begin{align*}
@@
 This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
-It's sometimes convenient to $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
+It is related to the mathematician's Borel transform by the identity $\borel_\textit{phys}(f) = \borel(z^{-1} f)$.
 
@@
 
-In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions. He starts with the formal trans-monomial solutions of the Airy equation:
+\textcolor{orange}{[Need a transition here.]} In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions.
+He starts with the formal trans-monomial solutions of the Airy equation:
 
@@
 As we've seen in Section~\ref{sec:reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we'd like to work with differential equations in the spatial domain too.
+This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we would like to work with differential equations in the spatial domain too.
 In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.

### 2024-03-25 exp-resurgence.tex
Start rewriting Airy-Lucas thimble projection argument
Also, add comments from meeting.

@@
 \end{proof}
+\textcolor{magenta}{[Introduce bare $\widehat{\Omega}$]}
 \color{black}
@@
 \subsubsection{Action on translations in the frequency domain}
-Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
+\textcolor{Pink}{[Optional section; used in theory of difference equations in the frequency domain]} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
 It turns out that
@@
 \textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-\color{DarkBlue}
+
 \subsection{Bridging the gap between analytic and formal objects}
@@
   \newcommand{\spill}{4}
-  \fill[violet!20, bezier bounding box, path fading=radial edge]
+  \fill[ietcoast!20, bezier bounding box, path fading=radial edge]
     (-\spill, -\spill) (\spill, \spill)
     (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
-  \fill[violet!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
-  \fill[violet] circle (0.7mm) node[anchor=west, outer sep=1mm] {$\zeta = \alpha$};
-  \node[violet] at (-190:0.85) {$\Upsilon_\Delta$};
+  \fill[ietcoast!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
+  \fill[ietcoast] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
+  \node at (-190:0.85) {$\Upsilon_\Delta$};
   \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-    \fill \p circle (0.7mm);
+    \fill[ietcoast] \p circle (0.7mm);
   }
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-\textcolor{orange}{[Explain the contents of the section]}
-\subsubsection{Regularity results}
+In Section~\ref{sec:regularity-results}, we will prove Borel regularity of the solutions of a certain class of linear level-$1$ ODEs.
+Then, in Section~\ref{sec:new-summability-proof}, we will give a new proof of Borel summability of the Poincar\'e frame of solutions.
+\textcolor{Pink}{[Flavor text added; check over]}
+\subsubsection{Regularity results}\label{sec:regularity-results}
 Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
@@
 %%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
-\textcolor{orange}{[Discuss terminology, like in \tt{reg-sing-volterra}?]}
+\textcolor{orange}{[Transition text]}
 %%%\begin{itemize}
@@
 %%%\end{itemize}
-\color{DarkBlue}
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
@@
 \begin{center}
+%\begin{figure}
 \begin{tikzpicture}
 \newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
+\fill[ietcoast!20, bezier bounding box, path fading=radial edge]
   (-\spill, -\spill) (\spill, \spill)
   (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
-\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
+\fill[ietcoast] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
 \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill \p circle (0.7mm);
+  \fill[ietcoast] \p circle (0.7mm);
 }
@@
 
-{\small The domain $\Omega_\alpha$}
+{\small The domain $\Omega_\alpha$ \textcolor{orange}{[Cite as ``the figure after Lemma~***]}}
+%\end{figure}
 \end{center}
@@
 \end{proof}
-\color{BlueViolet}
-\begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE_proof}
-Choose a root $-\alpha$ of $P$ with $\tau_\alpha \in (0, \infty)$.
-Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
-The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
-\end{theorem}
-\begin{center}
-\begin{tikzpicture}
-\newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
-  (-\spill, -\spill) (\spill, \spill)
-  (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
-\fill[violet] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
-\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill \p circle (0.7mm);
-}
-\end{tikzpicture}
-
-{\small The domain $\Omega_\alpha$}
-\end{center}
-\begin{proof}
-After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
-\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
-of the space $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$.
-The same is true on any smaller sector created by shaving a sector off each edge of $\Omega_\alpha$.
-It follows, by the results of Section~\ref{sec:reg-decay} \textcolor{magenta}{[the domain $\Omega_\alpha$ needs to be a sector for this]}, that the equation $\mathcal{P}\Psi_\alpha = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \]
-of the space $\dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$.
-\end{proof}
 \color{RoyalBlue}
@@
 \begin{proof}
-Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{re:thm:exist_uniq_ODE}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
 By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
@@
 of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
-Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4.
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
@@
 \textcolor{orange}{[Add flavor text]}
+\color{black}
 \begin{theorem}[restatement of \ref{thm:soln_is_asymptotic}]\label{re:thm:soln_is_asymptotic}
@@
 In the proof of Theorem~\ref{re:thm:soln_is_Borel_sum}, we showed that the position-domain solution $\psi_\alpha \in \singexpalg{\tau_\alpha-1}(\Upsilon)$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
-Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi_\alpha}$ is the formal Laplace transform of $\series{\psi}_\alpha$, the desired result follows from Lemma~\ref{lem:laplace-bridge}.
+Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi}_\alpha$ is the formal Laplace transform of $\series{\psi}_\alpha$, the desired result follows from Lemma~\ref{lem:laplace-bridge}.
 \end{proof}
-\color{BlueViolet}
-We are now ready to show that the solution $\Psi_\alpha$ is Borel regular.
-\begin{theorem}[restatement of \ref{thm:borel_reg_ODE}]\label{thm:borel_reg_ODE_proof}
-The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE_proof} is asymptotic to a transmonomial $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-The series $\series{\Psi}_\alpha$ is Borel summable, and its Borel sum is $\Psi_\alpha$.
-\end{theorem}
-\begin{proof}
-Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{thm:exist_uniq_ODE_proof}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
-By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
-\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
-of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
-Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{thm:exist_uniq_ODE_proof}, as we can see from the uniqueness part of Theorem~4.
-To prove that $\Psi_\alpha$ has a the desired asymptotic expansion, we will show that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
-
-For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
-The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
-%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
-\[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
-and the perturbation
-%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
-\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
-
-Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
-\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
-lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
-We then look for a perturbation $\solptb$ that makes $\solwhole = \solproto + \solptb$ a solution of the Volterra equation we are trying to solve.
-This is equivalent to solving the inhomogeneous equation
-\begin{equation}\label{eqn:inhomog-volterra}
-\solptb = \softpart^\alpha \solproto + \volterra^\alpha \solptb
-\end{equation}
-The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
-It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
-Defining
-\begin{align*}
-\solptb^{(0)} & = \softpart^\alpha \solproto \\
-\solptb^{(1)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(0)} \\
-\solptb^{(2)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(1)} \\
-\solptb^{(3)} & = \softpart^\alpha \solproto + \volterra^\alpha \solptb^{(2)} \\
-& \;\;\vdots
-\end{align*}
-we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.
-
-In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
-\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
-which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
-\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
-and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself.
-It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
-Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.
-
-Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, we can now conclude that $\psi_\alpha$ is the sum of a shifted Laurent series in $\zeta^{\tau_\alpha-1}\,\C\{\zeta, \zeta^{-1}\}$.
-The definition of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^{\tau_\alpha-1} |\psi_\alpha|$ is bounded on a punctured disk around $\zeta = 0$, so in fact $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
-Therefore, by Lemma~\ref{lem:laplace-bridge}, the solution $\Psi_\alpha$ is asymptotic to the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$, which lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
-\textcolor{orange}{[How to rephrase without formal Laplace transform?]}
-
-Now, let's take the Borel sum of $\series{\Psi}_\alpha$.
-The Borel transform inverts the formal Laplace transform, bringing us back to $\series{\psi}_\alpha$.
-By definition, the sum of $\series{\psi}_\alpha$ is $\psi_\alpha$, and the Laplace transform $\laplace^\theta_{\zeta, \alpha} \psi_\alpha$ is $\Psi_\alpha$.
-\end{proof}
-\color{black}
+%
 \subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
@@
 When applicable, Borel summability is an effective method to produce an analytic frame of solutions from the formal Poincar\'e frame $\tilde{\Psi}_\alpha$.
-In particular, as a consequence of our result in Theorem~\ref{thm:borel_reg_ODE_proof} we deduce that the Poincar\'e frame of solutions is Borel summable (proving Corollary~\ref{cor:borel_reg_ODE}).
+In particular, as a consequence of our result in Theorem~\ref{re:thm:exist_uniq_ODE} we deduce that the Poincar\'e frame of solutions is Borel summable.
 \begin{theorem}\label{thm2-dim}
 For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket_1$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$.
-Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum $\hat{\Psi}_\alpha(z)$ is proportional to the analytic solution $\Psi_\alpha$ of Theorem~\ref{thm:borel_reg_ODE_proof}.
+Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum $\hat{\Psi}_\alpha(z)$ is proportional to the analytic solution $\Psi_\alpha$ of Theorem~\ref{re:thm:exist_uniq_ODE}.
 \end{theorem}
@@
 \begin{enumerate}
-\item\label{part-1} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item\label{part-2} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
+\item\label{part-1-prf} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-2-prf} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3-prf} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
 \end{enumerate}
@@
 \[\tilde{I}_\alpha(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
-we get $\tilde{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1}.
+we get $\tilde{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1-prf}.
 
@@
 We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\tilde{\iota}$ has a finite radius of convergence.
-This ends the proof of part \ref{part-2}.
+This ends the proof of part~\ref{part-2-prf}.
 %$|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part \ref{part-3} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\tilde{\iota}_\alpha$.
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\tilde{\iota}_\alpha$.
 We can rewrite the Taylor series for $\nu$ as
@@
 \begin{remark}\label{rmk:1/2-deriv}
-    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there's one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
+    \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there is one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
 The proof follows the same argument we chose for $I_\alpha$, but there's one subtulty to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
@@
 \center
+\begin{center}
 \begin{tikzpicture}
 \newcommand{\spill}{4}
-\fill[violet!20, bezier bounding box, path fading=radial edge]
+\newcommand{\slitsize}{0.4}
+\fill[ietcoast!20, bezier bounding box, path fading=radial edge]
   (-\spill, -\spill) (\spill, \spill)
   (0, 0) -- (180:\spill)
-  arc (180:113:\spill) -- (112:2) .. controls (112:1.7) and (111:1.7) .. (111:2) -- (111:\spill)
-  arc (111:50:\spill) -- (50:2.6) .. controls (50:2.2) and (49:2.2) .. (49:2.6) -- (49:\spill)
-  arc (49:-52:\spill) -- (-52:2.3) .. controls (-52:2) and (-53:2) .. (-53:2.3) -- (-53:\spill)
-  arc (-53:-180:\spill) -- (0, 0);
-  \node[anchor=north west, outer sep=1mm] at (46.5:2.46) {$\zeta=\beta$};
-\foreach \p in {(111.5:1.9), (49.5:2.4), (-52.5:2.2)} {
+  arc (180:107.5+\slitsize:\spill) -- (107.5+\spill/1.95*\slitsize:1.95) -- (107.5-\spill/1.95*\slitsize:1.95) -- (107.5-\slitsize:\spill)
+  arc (107.5-\slitsize:46.5+\slitsize:\spill) -- (46.5+\spill/2.46*\slitsize:2.46) -- (46.5-\spill/2.46*\slitsize:2.46) -- (46.5-\slitsize:\spill)
+  arc (46.5-\slitsize:-56+\slitsize:\spill) -- (-56+\spill/2.24*\slitsize:2.24) -- (-56-\spill/2.24*\slitsize:2.24) -- (-56-\slitsize:\spill)
+  arc (-56-\slitsize:-180:\spill) -- (0, 0);
+\node[anchor=north west] at (46.5:2.46) {$\zeta=\beta$};
+\foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
+  \draw[ietcoast!50] \p -- (0,0);
   \fill \p circle (0.7mm);
-  \draw[dashed,violet!50] \p -- (0,0); 
 }
-\fill[violet] circle (0.7mm) node[anchor=180, outer sep=1mm] {$\zeta = \alpha$};
+\fill[ietcoast] circle (0.7mm) node[anchor=180,black, outer sep=1mm] {$\zeta = \alpha$};
 \end{tikzpicture}
+\end{center}
 \caption{The domain $\Omega_\alpha$}\label{Fig:slit domain}
@@
     \includegraphics[scale=0.3]{figures/thimble_Airy.png}
-    \caption{\small The contour $\Lambda_1$ in the $u$ plane is represented by the light blue path.
+    \caption{\small In this picture of the $u$ plane, the light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively.
+The light path is the contour $\Lambda_1$.
 More generally, the dark blue contour corresponds to the preimage of the ray $+1+e^{i\theta}\infty$ and $\theta=$.
 While the light blue contour corresponds to the preimage of the ray $-1+e^{i\theta}\infty$.
-The gray regions correspond to the preimage of $\Re \zeta> \textcolor{orange}{const}$.
+The shadowed region is the preimage of the region where $\Re(\zeta) > 3.897\ldots$.
 \textcolor{orange}{[for Aaron: could you please add the correct constant in the description of the figure, and explain what are the different colored regions?
-Thanks]}}
+Thanks]}} \textcolor{BlueViolet}{[Right now, the program chooses the constant to be $\tfrac{3}{4} n^{3/2}$, so it's about $3.897$ in this picture.
+If you want to put something concrete, I could redraw the picture so that it's $4$.]}
     \label{fig:path_Airy}
@@
     \caption{Integration contour $\Lambda^\theta_j$ for the Airy--Lucas function with $n=5$.
-The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=???$.
-While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
+The dark blue contours correspond to the preimage of the ray \textcolor{magenta}{$1+e^{i\theta}\infty$ [convert to $\Gamma$]} and \textcolor{orange}{$\theta=???$}.
+While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.
+\textcolor{orange}{[Preferred version, with ``Figure'' label]}}
     \label{fig:thimble_n_5}
@@
 \end{equation}
-In fact, as we’ll see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
-
-Let us put equation~\eqref{eqn:mod-bessel-AL} in the form \eqref{eqn:standard ODE}:
+In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
+
+Let us put Equation~\eqref{eqn:mod-bessel-AL} in the form $\mathcal{P}\Phi=0$ with $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}:
 \begin{equation}\label{eqn:reg-mod-bessel-AL}
@@
 
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
+By the properties of the Laplace transform (we refer to Proposition~\ref{prop:L-int-op}), $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
 \begin{equation}\label{int-eq:spatial-mod-bessel-AL}
@@
 which is easier to solve.
-Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} won't satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
+Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
 However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (0,1)$.
@@
 \subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
-We follow the reasoning of the proof of Theorem~\ref{lem:thimble_proj_formula-proof}.
+We follow the reasoning of the proof of Lemma~\ref{lem:thimble_proj_formula-proof}.
 We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
@@
 \end{align*}
-where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $u$, respectively.
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\Lambda^\theta_j$, respectively.
 \begin{center}
-\textcolor{orange}{[Do we still want a picture? Maybe draw the thimble in the $u$ plane]}
+\textcolor{orange}{[Draw the thimble in the $u$ plane]}
 \end{center}
+
+\color{DarkTurquoise}
+Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
+On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\Lambda^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$.
+The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
+\begin{center}
+\textcolor{orange}{[Draw the lifted thimble in the $\phi$ plane]}
+\end{center}
+We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
+\begin{align*}
+\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
+&= \frac{\sin(m\phi)}{\sin(n \phi)}\\
+&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; \sin^2(n \phi)\Big) \\
+&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big).
+\end{align*}
+This equation holds straightforwardly in the disk $|\phi| < \tfrac{\pi}{2n}$.
+As the value of $\phi$ goes along the real axis from $0$ to $\tfrac{\pi}{2n}$, the value of $\zeta$ goes along the real axis from $-1$ to $0$, at which point the hypergeometric function in the expression above becomes singular.
+To continue further, we have to dodge the singularity by pushing the value of $\zeta$ off the real axis.
+If we dodge into the lower half of the $\zeta$ plane, the value of $1 - \zeta^2$ loops counterclockwise around the singularity.
+In this case, as $\zeta$ continues from $0$ to $1$, we can use identity~15.2.3 of \cite{dlmf} to write
+\begin{verify}
+\begin{align*}
+\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \tfrac{m}{n}\;{}_2F_1\big(a, b; c; 1-\zeta^2\big) \\
+& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma(a) \Gamma(b)} (-\zeta^2)^{c-a-b} {}_2 F_1\big(c-a, c-b; c-a-b+1; \zeta^2\big) \\
+& = \tfrac{m}{n}\;{}_2F_1\big(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}; \tfrac{3}{2}; 1-\zeta^2\big) \\
+& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma\big(\tfrac{1}{2} - \tfrac{m}{2n}\big) \Gamma\big(\tfrac{1}{2} + \tfrac{m}{2n}\big)} (-\zeta^2)^{1/2} {}_2 F_1\big(1 + \tfrac{m}{2n}, 1 - \tfrac{m}{2n}; \tfrac{3}{2}; \zeta^2\big)
+\end{align*}
+\end{verify}
+\begin{align*}
+\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
+& \quad - \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\tfrac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
+\end{align*}
+in terms of the principal branch of the hypergeometric function.
+
+Similarly, if we dodge into the upper half of the $\zeta$ plane, we can write
+\begin{align*}
+\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
+& \quad + \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\frac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
+\end{align*}
+as $\zeta$ continues from $0$ to $1$.
+
+Let us now lift this path to the $u$ plane, starting at $u = \tfrac{1}{2}$ when $\zeta = -1$.
+We can bring the lift to the incoming or outgoing branch of $\Lambda^\theta_1$ by dodging into the lower or upper half of the $\zeta$ plane, respectively.
 
@@
 \subsubsection{Thimble projection formula}
-In Theorem \ref{thm:maxim-dim}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
+In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
 \color{black}
@@
 We are going to look for functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies equation~\eqref{eqn:triangular_cantilever} if and only if $v$ satisfies the integral equation
+From Proposition~\ref{prop:L-int-op} we deduce that $\laplace_{\zeta, \alpha} v$ satisfies equation~\eqref{eqn:triangular_cantilever} if and only if $v$ satisfies the integral equation
 \begin{equation}\label{eqn:position_cantilever}
@@
 
-We can see from Section~\ref{L-int-op} that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
+From Proposition~\ref{prop:L-int-op}, we find that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
 \begin{equation}\label{int-eq:spatial-mod-bessel}
@@
 
-In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula~\eqref{formula1} using trigonometric substitution.
+In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula Equation~\eqref{eqn:formula-proof} using trigonometric substitution.
 As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
@@
 
-Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation \eqref{formula1} are resurgent.
+Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in Equation~\eqref{eqn:formula-proof} are resurgent.
 Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.

### 2024-03-26 exp-resurgence.tex
Finish rewriting Airy-Lucas thimble projection argument
It's hopefully finished, anyway.

@@
 where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_{\zeta = b}$ throughout this document.
+We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_b$ throughout this document.
+\textcolor{magenta}{[Notation conflict: we also use $\laplace_{\zeta, \alpha}$ to represent starting at $\zeta = \alpha$, giving the starting point as a coordinate value instead of a point $b$.]}
 
@@
 \item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} Following \cite{reg-sing-volterra}, we require $f\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
-\item The value of $z$ is in the half-plane $H_{\theta}$ centered around the ray $e^{-i\theta} [0, \infty)$.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
+\item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.
 \end{itemize}
@@
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
 where
 \begin{equation}\label{integral:mod-bessel-rational-AL}
-K_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+K^{(j)}_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
 \end{equation}
@@
 \begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
 \end{align*}
@@
 \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
-&= \frac{\sin(m\phi)}{\sin(n \phi)}\\
-&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; \sin^2(n \phi)\Big) \\
-&= \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big).
-\end{align*}
+& = \frac{\sin(m\phi)}{\sin(n \phi)}\\
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin^2(n \phi)\right) \\
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
+\end{align*}
+Initially, we only know that this equation holds in the disk $|\phi| < \tfrac{\pi}{2n}$.
+However, observing that the left-hand side is meromorphic throughout the $\phi$ plane, we can deduce by analytic continuation that the equation holds throughout the $\phi$ plane.
+
+Next, we simplify the integrand using identities 15.8.4 and 15.8.27--28 from \cite{dlmf}, which tell us that\begin{align*}
+&{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
+& =\; \hphantom{+} \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right) \Gamma\left(1 + \frac{m}{2n}\right)}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{1}{2};\;\zeta^2\right) \\
+& \hphantom{=}\; - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2} - \frac{m}{2n}\right) \Gamma\left(\frac{1}{2} + \frac{m}{2n}\right)}\;{}_2F_1\left(1 - \frac{m}{2n},\;1 + \frac{m}{2n};\;\frac{3}{2};\;\zeta^2\right) \\[3mm]
+& =\; \hphantom{+ \frac{0}{0}}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) + \hphantom{\frac{0}{0}}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\
+& \hphantom{=}\; + \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1+\frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) - \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\[3mm]
+& =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
+\end{align*}
+away from the line $\Re(\zeta) = 0$ and the rays $\Gamma^0_{\zeta,1}$ and $\Gamma^\pi_{\zeta,-1}$.
+
+Returning to the projected thimble integral
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
+we can see the integrand as the variation of the function
+\[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
+across the branch cut $\Gamma^\theta_{\zeta, \mp 1}$.
+When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$.
+Similarly, when $j$ is even, only the first term will contribute to the jump.
+We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}.
+For odd $j$, we have
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\Gamma^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+and for even $j$, we have \textcolor{magenta}{[check]}
+\[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\Gamma^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\]
+
+Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root}--\ref{neg-root}, we notice that
+\[ K^{(j)}_{m/n}(z) = \begin{cases}
+\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
+\frac{i}{2}\laplace_{\zeta, -1} v_{-1} \;\textcolor{magenta}{\text{(?)}} & j \text{ even}.
+\end{cases} \]
+
+\color{GreenYellow}
 This equation holds straightforwardly in the disk $|\phi| < \tfrac{\pi}{2n}$.
@@
 
-where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.\color{black}
+where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.
 
@@
 \end{align*}
-
+\color{black}
+%
 \subsubsection{A flavor of resurgence: the Stokes phenomena in the position domain}\label{resurgence-AL}
-
+%
 In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).

### 2024-03-26 exp-resurgence.tex
Revise first look at thimble integrals

@@
 \begin{equation}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel-rescaled-1}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
 \end{equation}
@@
 \begin{equation}
-e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel-ex}
+e^{z} \left[ \frac{(-1)!!}{z^{1/2}} + \frac{5}{72} \cdot \frac{1!!}{z^{3/2}} + \frac{385}{31104} \cdot \frac{3!!}{z^{5/2}} + \frac{17017}{6718464} \cdot \frac{5!!}{z^{7/2}} + \ldots \right] \label{series:bessel_ex}
 \end{equation}
 and its constant multiples (see \cite[equation 10.40.1]{dlmf}). As another example, you might rewrite the integral
-
-\[ \Phi(z) = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du \]
+\begin{equation}\label{int:bessel_ex}
+\Phi = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
+\end{equation}
 as
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel-ex}---up to a constant.\begin{verify}
-    see Mathematica document.
-\end{verify}
+using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$.
+Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.
+\begin{verify}[See Mathematica document.]\end{verify}
 
@@
 \item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-Equation~\eqref{eqn:bessel-rescaled-1} is an example.
+Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
@@
 %
-\item Evaluating a certain kind of integral: a one-dimensional {\em thimble integral}
-%
+\item Evaluating a one-dimensional {\em thimble integral}. Integral~\eqref{int:bessel_ex} is an example. More generally, we will consider integrals of the form
 \begin{equation*}
-I(z)\defeq\int_{\Lambda}\exp\big[-z f\big] \nu
+I = \int_{\Lambda}e^{-zf}\,\nu,
 \end{equation*}
-where $f\colon X\to \mathbb{C}$ is a holomorphic functions with isolated and non-degenerate critical points, $X$ is $1$-dimensional complex manifold, $\nu\in\Omega^1(X)$ is holomorphic $1$-form in $X$ and $\Lambda$ is a suitable contour such that $I(z)$ is a holomorphic function of $z$.
+where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\Lambda$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}.
+Under these conditions, $I$ is a holomorphic function of $z$.
 \end{enumerate}
 These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
+By playing with derivatives of a thimble integral, you can often find a linear ODE that the integral satisfies.
+Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
 
@@
 
-We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thibmle}, for ODEs and thimble integrals, respectively.
+We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thimble}, for ODEs and thimble integrals, respectively.
 The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
@@
 \color{black}
-\subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thibmle}
+\subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thimble}
 %\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
@@
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$.
-Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.
-\begin{lemma}\label{translation}
+Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
+Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$.
+The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.
+
+\textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$.
+Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.}
+\begin{lemma}%%\label{translation}
 Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
@@
 \end{lemma}
+\color{black}
+\color{RoyalBlue}
+\begin{lemma}%%\label{translation}
+Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
+   \begin{equation}
+    \label{change-chart}
+    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
+\end{equation}
+In other words, the diagram
+\begin{center}
+\begin{tikzcd}
+ \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
+& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
+\end{tikzcd}
+\end{center}
+commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
+\end{lemma}
+\color{black}
 \begin{proof}
@@
 \subsubsection{Action on transseries}\label{sec:action_transseries}
-
+%
+\color{DarkTurquoise}
+\color{RoyalBlue}
 A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[what does this mean?]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
@@
 It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we will achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
+\color{black}
 \begin{definition}
@@
 It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by Picard iteration.
+More explicitly, we can solve equation~\eqref{eqn:inhomog-volterra} by fixed-point iteration.
 Defining
@@
 \end{cases} \]
-
-\color{GreenYellow}
-This equation holds straightforwardly in the disk $|\phi| < \tfrac{\pi}{2n}$.
-As the value of $\phi$ goes along the real axis from $0$ to $\tfrac{\pi}{2n}$, the value of $\zeta$ goes along the real axis from $-1$ to $0$, at which point the hypergeometric function in the expression above becomes singular.
-To continue further, we have to dodge the singularity by pushing the value of $\zeta$ off the real axis.
-If we dodge into the lower half of the $\zeta$ plane, the value of $1 - \zeta^2$ loops counterclockwise around the singularity.
-In this case, as $\zeta$ continues from $0$ to $1$, we can use identity~15.2.3 of \cite{dlmf} to write
-\begin{verify}
-\begin{align*}
-\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \tfrac{m}{n}\;{}_2F_1\big(a, b; c; 1-\zeta^2\big) \\
-& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma(a) \Gamma(b)} (-\zeta^2)^{c-a-b} {}_2 F_1\big(c-a, c-b; c-a-b+1; \zeta^2\big) \\
-& = \tfrac{m}{n}\;{}_2F_1\big(\tfrac{1}{2} - \tfrac{m}{2n}, \tfrac{1}{2} + \tfrac{m}{2n}; \tfrac{3}{2}; 1-\zeta^2\big) \\
-& \quad + \tfrac{m}{n} \frac{2\pi i}{\Gamma\big(\tfrac{1}{2} - \tfrac{m}{2n}\big) \Gamma\big(\tfrac{1}{2} + \tfrac{m}{2n}\big)} (-\zeta^2)^{1/2} {}_2 F_1\big(1 + \tfrac{m}{2n}, 1 - \tfrac{m}{2n}; \tfrac{3}{2}; \zeta^2\big)
-\end{align*}
-\end{verify}
-\begin{align*}
-\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
-& \quad - \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\tfrac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
-\end{align*}
-in terms of the principal branch of the hypergeometric function.
-
-Similarly, if we dodge into the upper half of the $\zeta$ plane, we can write
-\begin{align*}
-\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} & = \frac{m}{n}\;{}_2F_1\Big(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1-\zeta^2\Big) \\
-& \quad + \frac{m}{n} \frac{2\pi \zeta}{\Gamma\big(\frac{1}{2} - \frac{m}{2n}\big) \Gamma\big(\frac{1}{2} + \frac{m}{2n}\big)} {}_2 F_1\Big(1 + \frac{m}{2n}, 1 - \frac{m}{2n}; \frac{3}{2}; \zeta^2\Big)
-\end{align*}
-as $\zeta$ continues from $0$ to $1$.
-
-Let us now lift this path to the $u$ plane, starting at $u = \tfrac{1}{2}$ when $\zeta = -1$.
-We can bring the lift to the incoming or outgoing branch of $\Lambda^\theta_1$ by dodging into the lower or upper half of the $\zeta$ plane, respectively.
-
-\color{MediumSpringGreen}
-Now we observe, that by properties of Chebyshev polynomials the integrand can be written as an explicit function of $\zeta$: \textcolor{orange}{[If $u_+ = \cos(\phi)$, then $u_- = \cos(\overline{\phi})$]}
-
-\begin{align*}
-\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))}&=\frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
-&=\frac{\sin(m\phi)}{\sin(n \phi)}\\
-&=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};\sin^2(n \phi)\right)\\
-&=\frac{m}{n}\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right) 
-\end{align*}
-where in the last step we use $-\zeta=T_n(u)=T_n(\cos\phi)=\cos(n\phi)$. Applying identity 15.8.4, 15.8.27 and 15.8.28 from \cite{dlmf},
-
-\begin{align*}
-    &{}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{3}{2};1-\zeta^2\right)=\\
-    &\qquad = \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right)\Gamma\left(1+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(\frac{1}{2}-\frac{m}{2n},\frac{1}{2}+\frac{m}{2n};\frac{1}{2};\zeta^2\right)+\\
-    &\qquad \qquad\qquad - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2}-\frac{m}{2n}\right)\Gamma\left(\frac{1}{2}+\frac{m}{2n}\right)} \,\,\, {}_2F_1\left(1-\frac{m}{2n},1+\frac{m}{2n};\frac{3}{2};\zeta^2\right)\\
-    &\qquad ={}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)+\\
-    &\qquad\qquad +\frac{1}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)-\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)\\
-    &\qquad =\frac{3}{2} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)+\frac{1}{2}{}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
-\end{align*}
-In addition, recall that ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ has a branch cut singularity at $\zeta=-1$ while ${}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ has a branch cut at $\zeta=1$; hence
-
-\begin{align*}
-    K_{m/n}(z)&=-\frac{m}{4 n\sinh(\tfrac{m}{n}i\pi)}\int_{\gamma_z}e^{-z\zeta} {}_2F_1\left(1-\frac{m}{n},1+\frac{m}{n};\frac{3}{2};\frac{1}{2}+\frac{\zeta}{2}\right) d\zeta\\
-    &=-\frac{1}{2}\int_{1}^{+\infty}e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right) d\zeta
-\end{align*}
-
-where in the second step we use the analytic continuation of the hypergeometric function \cite[Equation 15.2.3]{dlmf}.
-
-Finally, comparing this expression for $K_{m/n}$ with the expression for $v_1$ computed in Section \ref{pos-root} we notice that 
-\begin{align*}
-K_{m/n}(z)=\frac{i}{2}\laplace_{\zeta,1}v_1 .
-\end{align*}
 \color{black}

### 2024-03-27 exp-resurgence.tex
Updates from Overleaf
Prepare to merge local figure changes

@@
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4 u^3 - 3 u + 1$.
+using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$.
 Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.
@@
 \begin{defn}
+On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a power series
+\begin{equation}\label{series:asymp-defn}
+a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
+\end{equation}
+if, along each ray toward $\infty$,
+\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
+over all orders $n$. We will write
+\[ F \sim \sum_{n \geq 0} a_n z^{-n} \]
+to denote this relationship.
+\end{defn}
+\color{RoyalBlue}
+\begin{defn}
 On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
-\begin{equation}\label{series:asymp-defn}
+\begin{equation}%%\label{series:asymp-defn}
 \textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
@@
 is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$. We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]
+\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
+over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]}
 \end{defn}
+\color{black}
 \textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we will say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if
@@
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
-We will denote such map with the symbol $\aexp$.
+Since asymptotic expansions on overlapping sectors must agree, we can meaningfully take a function's asymptotic expansion along a ray:\textcolor{RoyalBlue}{We will denote such map with the symbol $\aexp$.
 More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e.
-as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.
+as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.}
 
@@
 \begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a power series of the form \eqref{series:asymp-defn} is {\em uniformly $1$-Gevrey asymptotic} to a holomorphic function $F$ if there's a constant $A \in (0, \infty)$ for which
-\[ \left|F - \left(\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
+On an open sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
+\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
 over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
@@
 \begin{tikzpicture}
+\renewcommand{\rfiber}{3}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\renewcommand{\phase}{35}
+\begin{fiber}[shade, phase=\phase]
+\end{fiber}
+\end{tikzpicture}
+\begin{tikzpicture}
 \newcommand{\size}{3}
@@
 \begin{tikzpicture}
+\renewcommand{\rfiber}{3}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\renewcommand{\phase}{35}
+\newcommand{\radius}{1}
+\begin{fiber}
+\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
+  \begin{scope}
+    \draw[ray] (0, 0) -- (\phase:\rshade);
+    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
+  \end{scope}
+\end{fiber}
+\end{tikzpicture}
+\begin{tikzpicture}
 \newcommand{\size}{3}
@@
 \newcommand{\radius}{1}
-\newcommand{\dis}{1.2}
 \begin{scope}
@@
 %%\end{tabular}
-\color{black}
+\color{RoyalBlue}
 \begin{itemize}
@@
 \end{itemize}
+\color{black}
 \end{notation*}
@@
     (190:1.5) arc (190:41:1.5) -- (41:\spill) arc (41:-48:\spill) -- (-48:1.3) arc (-48:-170:1.3) -- cycle;
-  \fill[ietcoast!35] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
-  \fill[ietcoast] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
-  \node at (-190:0.85) {$\Upsilon_\Delta$};
+  \fill[ietcoast!33] (0, 0) -- (-170:1.3) arc (-170:-210:1.3) -- cycle;
+  \fill[ietcoast!33!black] circle (0.7mm) node[anchor=west, black, outer sep=1mm] {$\zeta = \alpha$};
+  \node[ietcoast!33!black] at (-190:0.85) {$\Upsilon_\Delta$};
   \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-    \fill[ietcoast] \p circle (0.7mm);
+    \fill[ietcoast!33!black] \p circle (0.7mm);
   }
@@
 Take some $\rho \in (-1,\infty)$.
-If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to \textcolor{orange}{[backwards terminology?]} the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
+If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
 \textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
@@
   arc (-56-\slitsize:-180:\spill) -- (0, 0);
-\node[anchor=north west] at (46.5:2.46) {$\zeta=\beta$};
+\node[ietcoast!33!black, anchor=north west] at (46.5:2.46) {$\zeta = \beta$};
 \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \draw[ietcoast!50] \p -- (0,0);
-  \fill \p circle (0.7mm);
+  \draw[ietcoast] \p -- (0,0);
+  \fill[ietcoast!33!black] \p circle (0.7mm);
 }
-\fill[ietcoast] circle (0.7mm) node[anchor=180,black, outer sep=1mm] {$\zeta = \alpha$};
+\fill[ietcoast!33!black] circle (0.7mm) node[anchor=180, outer sep=1mm] {$\zeta = \alpha$};
 \end{tikzpicture}

### 2024-03-27 exp-resurgence.tex
Update Sokal and timble figures
Use same style and palette as phase space Laplace.

@@
 % === phase space laplace ===
-\include{../figures/phase-space-laplace.tex}
+\include{figures/phase-space-laplace.tex}
 
@@
 }
-
-\usepackage{etoolbox}
-
-\usetikzlibrary{math, 3d, calligraphy}
-
-% --- styles ---
-
-\definecolor{pwbeige}{RGB}{172, 146, 122}
-\definecolor{pworange}{RGB}{245, 153, 30}
-
-\tikzset{
-  surf/.style={pwbeige!10},
-  leaf/.style={thin, pwbeige!60},
-  sing/.style={thick, pworange},
-  ray/.style={thick}
-}
-
-% --- cotangent fibers ---
-
-\newcommand{\rfiber}{1.5}
-\pgfmathsetmacro{\rshade}{1.5*\rfiber}
-
-\newcommand{\drawfiber}{
-  \foreach \sgn in {-1, 1} {
-    \calligraphy[scale=\sgn, copperplate, heavy, heavy line width=0.25mm]
-      (\rfiber, \rfiber) -- (\rfiber, -\rfiber)
-      (\rfiber, -\rfiber) -- (-\rfiber, -\rfiber);
-  };
-}
-
-% set up PGF keys
-\pgfkeys{
-  /laplace/.cd,
-  drop/.store in=\fiberdrop,   drop/.value required,
-  shade/.store in=\fibershade, shade/.default=true,
-  degree/.store in=\fiberdeg,  degree/.value required,
-  phase/.store in=\fiberphase, phase/.value required,
-  dual/.store in=\fiberdual,   dual/.default=true
-}
-
-\newcommand{\fiberdescender}[1]{
-  \calligraphy[copperplate, light, thin] (0, -\rfiber) -- (0, -#1);
-}
-
-\newcommand{\fibershading}[2]{
-  \tikzmath{
-    \shadestart = (-90 - #1) / \fiberdeg;
-    \shadeend = (90 - #1) / \fiberdeg;
-  }
-  \fill[pwbeige!30, draw=pwbeige!60] (0, 0) -- (\shadestart:\rshade) arc (\shadestart:\shadeend:\rshade) -- cycle;
-}
-
-\newenvironment{fiber}[1][]{%
-  \pgfkeys{/laplace/.cd, drop=0, shade=false, degree=1, phase=0, #1}
-  \begin{scope}
-    \fill[surf] (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
-    \clip (-\rfiber, -\rfiber) rectangle (\rfiber, \rfiber);
-    \tikzmath{
-      if \fibershade then {
-        print \fibershading{\fiberphase}{0};
-      };
-    }
-}{% ...
-  \end{scope}
-  % see TikZ docs for branching statements
-  % https://tikz.dev/library-math#sec-58.5
-  \tikzmath{
-    if \fiberdrop > 0 then {
-      print \fiberdescender{\fiberdrop};
-    };
-  }
-  \drawfiber
-}
-
-\newcommand{\genfibercontent}[1][]{
-  \pgfkeys{/laplace/.cd, dual=false, #1}
-  \pgfmathsetmacro{\hatch}{\rfiber/8};
-  \pgfmathsetmacro{\firsthatch}{-\rfiber+\hatch}
-  \pgfmathsetmacro{\nexthatch}{-\rfiber+2*\hatch}
-  \pgfmathsetmacro{\hatchstop}{\rfiber-\hatch/2}
-  \foreach \y in {\firsthatch, \nexthatch, ..., \hatchstop} {
-    \tikzmath{
-      coordinate \drawfrom;
-      coordinate \drawto;
-      if \fiberdual then {
-        \drawfrom = (\y, -\rfiber);
-        \drawto = (\y, \rfiber);
-      } else {
-        \drawfrom = (-\rfiber, \y);
-        \drawto = (\rfiber, \y);
-      };
-    }
-    \draw[leaf] (\drawfrom) -- (\drawto);
-  };
-  \fill circle (\dotsize);
-}
-
-\newcommand{\singfibercontent}{
-  % nonsingular leaves
-  \foreach \sector in {30, 90, ..., 330} {
-    \tikzmath{
-      \farout = 45*floor((\sector + 59) / 45);
-      \tfarout = 3*(\farout - \sector);
-      \rfarout = \rfiber/sin(45+mod(\farout-45, 90));
-    }
-    \pgfmathsetmacro{\rmax}{sin(\tfarout) * pow(\rfarout, 3)}
-    \foreach \r in {0.5, 1.0, ..., \rmax} {
-      \pgfmathsetmacro{\win}{asin(\r/(2*\rmax))}
-      \draw[leaf, rotate=\sector, domain=\win:{180-\win}, variable=\t] plot ({\t/3}:{(\r/sin(\t))^(1/3)});
-    };
-
-    % singular leaves
-    \foreach \ang in {90, 210, 330} {
-      \draw[sing] (\ang:{-sqrt(2)*\rfiber}) -- (\ang:{sqrt(2)*\rfiber});
-    };
-    \fill[sing] circle (\dotsize);
-  };
-}
-
-% --- posititon plane ---
-
-\pgfmathsetmacro{\hatch}{2/3}
-\tikzmath{
-  \phase = 15;
-  \dotsize = 0.04;
-  \drop = 3.5;
-  \xsing = 2;
-  \zsing = 4*\hatch;
-  \xgen = 6;
-  \zgen = 8*\hatch;
-  \rcut = 1/5;
-}
-
-\newcommand{\ray}[2]{
-  \draw[ray] (#1, #2) -- (8, {#2 + (8-#1)*tan(\phase)});
-}
-
-% local picture of the Laplace transform
-\newcommand{\basicLaplace}{
-\begin{tikzpicture}[scale=0.9]
-% position space
-\begin{fiber}
-  \genfibercontent
-  \ray{0}{0}
-\end{fiber}
-\node[anchor=north, outer sep=1mm, font=\footnotesize]
-  at (0, -\rfiber) {position space};
-
-% frequency space
-\begin{scope}[shift={(4 + 0.25*8/3, 0)}]
-  \begin{fiber}[shade, phase=\phase]
-    \genfibercontent[dual]
-  \end{fiber}
-  \node[anchor=north, outer sep=1mm, font=\footnotesize]
-    at (0, -\rfiber) {frequency space};
-\end{scope}
-\end{tikzpicture}
-} % \basicLaplace
-
-% phase space picture of the Laplace transform
-\newcommand{\phaseSpaceLaplace}{
-\begin{tikzpicture}[z={(0.25cm, 0.2cm)}, scale=0.9]
-% position plane
-\begin{scope}[canvas is xz plane at y=0]
-  % surface
-  \fill[surf]
-    (0, 0) -- (0, \zsing-\rcut)
-    -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut})
-    -- (0, 8) --(8, 8) -- (8, 0) -- cycle;
-
-  % hatching
-  \pgfmathsetmacro{\nexthatch}{2*\hatch}
-  \pgfmathsetmacro{\singstop}{\zsing - \hatch/2}
-  \foreach \z in {\hatch, \nexthatch, ..., \singstop} {
-    \draw[leaf] (0, \z) -- (8, \z);
-  };
-  \pgfmathsetmacro{\singstart}{\zsing + \hatch}
-  \pgfmathsetmacro{\singnext}{\zsing + 2*\hatch}
-  \pgfmathsetmacro{\hatchstop}{8 - \hatch/2}
-  \foreach \z in {\singstart, \singnext, ..., \hatchstop} {
-    \draw[leaf] (0, \z) -- (8, \z);
-  };
-
-  % singular leaves
-  \begin{scope}[sing]
-    \draw (\xsing, \zsing) -- (8, \zsing);
-    \draw (0, \zsing-\rcut) -- ++(\xsing-\rcut, 0) arc (-90:90:\rcut) -- (0, {\zsing + \rcut});
-  \end{scope}
-
-  % integration rays
-  \ray{\xgen}{\zgen}
-  \ray{\xsing}{\zsing}
-
-  % outline
-  \calligraphy[copperplate, heavy, heavy line width=0.25mm]
-    (0, 0) -- (0, \zsing-\rcut)
-    (0, \zsing+\rcut) -- (0, 8)
-    (0, 8) -- (8, 8)
-    (8, 8) -- (8, 0)
-    (8, 0) -- (0, 0);
-\end{scope}
-
-% generic fiber
-\begin{scope}[canvas is xy plane at z=\zgen, shift={(\xgen, \drop)}]
-  \begin{fiber}[drop=\drop, shade, phase=\phase]
-    \genfibercontent[dual]
-  \end{fiber}
-\end{scope}
-
-% singular fiber
-\begin{scope}[canvas is xy plane at z=\zsing, shift={(\xsing, \drop)}]
-  \begin{fiber}[drop=\drop, shade, degree=3, phase=\phase]
-    \singfibercontent
-  \end{fiber}
-\end{scope}
-
-% generic point
-\fill (\xgen, 0, \zgen) circle (\dotsize);
-
-% singular point
-\fill[sing] (\xsing, 0, \zsing) circle (\dotsize);
-
-% labels
-\begin{scope}[overlay]
-  \node (surf label) at (9, 0, 4) {$B$};
-  \path (surf label) ++(0, \drop, 0) node {$T^*B$};
-  \node[outer sep=0.15mm, font=\footnotesize, align=left]
-    (cut label) at (-1.25, 1.2, \zsing) {branch cut \\ at conical \\ singularity};
-  \draw[->] (cut label) to[out=-75, in=180] (-0.25, 0, \zsing);
-\end{scope}
-\end{tikzpicture}
-} % \phaseSpaceLaplace
 
@@
 However, this only seems to be possible when $X$ is 1-dimensional.}
-\begin{figure}[ht]
+\begin{figure}[h]
     \centering
-    \includegraphics[scale=0.7]{figures/u_contour_5.pdf}
-    \hspace{1cm}
-    \includegraphics[scale=0.7]{figures/zeta_contour_5.pdf}
-    \caption{\textcolor{orange}{Change the pictures with the one centered at the critical values/points respectively}The preimage of a ray departing from the critical value and going to infinity along the positive real axis.}
+    \includegraphics[width=6.5cm]{figures/ray_1.png}
+    \hspace{0.5cm}
+    \includegraphics[width=6.5cm]{figures/thimble-n5_1.png}
+    \caption{The ray $\Gamma^{\pi/6}_{\zeta, 1}$ on the position domain, and its preimage in the $u$ plane.}
     \label{fig:thimble_vs_rays}
@@
 \renewcommand{\phase}{35}
-\begin{fiber}[shade, phase=\phase]
+\newcommand{\dis}{1.2}
+\begin{fiber}[shade, phase=\phase, dis=\dis]
+\genfibercontent[dual]
+\draw (0, 0) -- (-\phase:\rshade);
+\draw[rotate=-\phase] (\dis, -0.1) -- (\dis, 0.1);
+\draw (0, 0) -- (0.75, 0);
+\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
+\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$c$};
 \end{fiber}
@@
 \fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
-  \begin{scope}
+\genfibercontent
+\draw (0, 0) -- (0.75, 0);
 \draw[ray] (0, 0) -- (\phase:\rshade);
 \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
-  \end{scope}
 \end{fiber}

### 2024-03-27 exp-resurgence.tex
Show thimbles over both 1 and -1

@@
     \centering
-    \includegraphics[width=6.5cm]{figures/ray_1.png}
+    \includegraphics[width=6.5cm]{figures/rays.png}
     \hspace{0.5cm}
-    \includegraphics[width=6.5cm]{figures/thimble-n5_1.png}
-    \caption{The ray $\Gamma^{\pi/6}_{\zeta, 1}$ on the position domain, and its preimage in the $u$ plane.}
+    \includegraphics[width=6.5cm]{figures/thimbles-n5.png}
+    \caption{The rays $\Gamma^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}
     \label{fig:thimble_vs_rays}
 \end{figure}
-Choose a ciritcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:
+Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:
 \begin{equation}
@@
 \begin{center}
-\includegraphics[scale=0.3]{figures/thimble-n5.png} \\[1em]
+\includegraphics[width=10cm]{figures/thimbles-n5.png} \\[1em]
 {\small Integration contour $\Lambda^{(j)}$ for the Airy--Lucas function with $n=5$.
@@
     \centering
-   \includegraphics[scale=0.3]{figures/thimble-n5.png}
-    \caption{Integration contour $\Lambda^\theta_j$ for the Airy--Lucas function with $n=5$.
-The dark blue contours correspond to the preimage of the ray \textcolor{magenta}{$1+e^{i\theta}\infty$ [convert to $\Gamma$]} and \textcolor{orange}{$\theta=???$}.
-While the light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.
+   \includegraphics[width=10cm]{figures/thimbles-n5.png}
+    \caption{Integration contours $\Lambda^\theta_j$ for the Airy--Lucas functions with $n=5$.
+The dark and light thimbles are the preimages of the rays $\Gamma^{\pi/8}_{\zeta, 1}$ and $\Gamma^{\pi/8}_{\zeta, -1}$, respectively.
 \textcolor{orange}{[Preferred version, with ``Figure'' label]}}

### 2024-03-28 exp-resurgence.tex
Add meeting notes

@@
 \begin{equation}\label{int:bessel_ex}
-\Phi = \int_{\Lambda} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
-\end{equation}
-as
+\Phi = \int_{\mathcal{C}} \exp\left[-z \left(4 u^3 - 3 u\right)\right]\,du
+\end{equation}
+as \begin{verify}[see \texttt{notes/intro series computation.nb} and \texttt{notes/intro series computation.ipynb}]\end{verify}
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$.
-Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.
-\begin{verify}[See Mathematica document.]\end{verify}
+using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.
 
@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence we say $\series{\Phi}$ is {\em $1$-Gevrey}.
+\item If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}.
 We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
@@
 Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[change, explain, or link to notation]} its Laplace transform $\laplace_{\zeta,b}^\theta \hat{\phi}$ (see Section \ref{laplace:ordinary}) turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}:=\laplace_{\zeta,b}^\theta \hat{\phi}$ its {\em Borel sum} at $b$.
+\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $b$.
 \end{enumerate}
@@
 By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\Gamma_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\mathcal{J}_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
@@
 \begin{equation*}
-I = \int_{\Lambda}e^{-zf}\,\nu,
+I = \int_{\mathcal{C}}e^{-zf}\,\nu,
 \end{equation*}
-where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\Lambda$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}.
+where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}.
 Under these conditions, $I$ is a holomorphic function of $z$.
@@
 %\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
+Our treatment of thimble integrals will be based on our geometric picture of the Laplace transform, summarized in Section~
+
+\color{RoyalBlue}
 Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
@@
 The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-\textcolor{RoyalBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\Gamma_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\Gamma_\alpha^\theta$ which vanishes at $\alpha$.
-These are well-defined as long as $\Gamma_\alpha^\theta$ misses the critical values of $f$.
-Then, the preimage $f^{-1}(\Gamma_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\Gamma_\alpha^\theta$ misses the other critical values of $f$.
-The Lefschetz thimble $\Lambda_a^\theta$ can be regarded as the component of $f^{-1}(\Gamma_\alpha^\theta)$ that goes through $a$.
-\textcolor{orange}{We could orient the thimble so that shifting $\Lambda_a$ to its left would make its projection run clockwise around $\Gamma_\alpha$.
+\textcolor{NavyBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\mathcal{J}_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\mathcal{J}_\alpha^\theta$ which vanishes at $\alpha$.
+These are well-defined as long as $\mathcal{J}_\alpha^\theta$ misses the critical values of $f$.
+Then, the preimage $f^{-1}(\mathcal{J}_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\mathcal{J}_\alpha^\theta$ misses the other critical values of $f$.
+The Lefschetz thimble $\mathcal{C}_a^\theta$ can be regarded as the component of $f^{-1}(\mathcal{J}_\alpha^\theta)$ that goes through $a$.
+\textcolor{orange}{We could orient the thimble so that shifting $\mathcal{C}_a$ to its left would make its projection run clockwise around $\mathcal{J}_\alpha$.
 However, this only seems to be possible when $X$ is 1-dimensional.}
@@
     \includegraphics[width=6.5cm]{figures/thimbles-n5.png}
-    \caption{The rays $\Gamma^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}
+    \caption{The rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}
     \label{fig:thimble_vs_rays}
 \end{figure}
-Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\Lambda_a^\theta$:
+Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:
 \begin{equation}
-I_\alpha(z)\defeq\int_{\Lambda_a^\theta}e^{-zf}\nu.
-\end{equation}
-Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\Lambda_a^\theta)$.
+I_\alpha(z)\defeq\int_{\mathcal{C}_a^\theta}e^{-zf}\nu.
+\end{equation}
+Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
 \textcolor{RoyalBlue}{[say more about this?]}.
-\textcolor{orange}{[As a start\ldots]} We recall the well-known result
+\textcolor{orange}{[As a start\ldots]} We recall the well-known result\color{black}
 \begin{lemma}\label{lem:thimble_proj_formula}
@@
 \begin{equation}\label{eqn:formula}
-\iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda^\theta(\zeta)}\nu \right),
-\end{equation}
-where $\Lambda^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
-Notice that $\Lambda(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda$ needs an orientation, but the orientation is arbitrary.]}
+\iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\mathcal{C}^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\mathcal{C}(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\mathcal{C}$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
@@
 \item\label{part-1} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-Recall that $\theta$ is the direction of the ray $\Gamma^\theta_\alpha$.
+Recall that $\theta$ is the direction of the ray $\mathcal{J}^\theta_\alpha$.
 \item\label{part-2} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
+\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
 \end{enumerate}
@@
 %\begin{multline}
-%\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\Lambda_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\Lambda_j(\zeta')} \nu \right)\,d\zeta',
+%\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\mathcal{C}_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\mathcal{C}_j(\zeta')} \nu \right)\,d\zeta',
 %\end{multline}
-%where $\Lambda_j(\zeta)$ is the part of $\Lambda_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\Lambda_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_j$ needs an orientation, but the orientation is arbitrary.]}
+%where $\mathcal{C}_j(\zeta)$ is the part of $\mathcal{C}_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
+Notice that $\mathcal{C}_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\mathcal{C}_j$ needs an orientation, but the orientation is arbitrary.]}
 %\end{enumerate}
@@
 %\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\Lambda_\alpha}e^{-zf}\nu
+%I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu
 %\end{equation}
@@
 \end{center}
-When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
@@
 Our approach of solving regular singular Volterra equation---based on the contraction mapping theorem for suitable Banach spaces \cite{reg-sing-volterra}---is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
-What distinguishs our result from the one of Braaksma is to consider the Laplace transform of functions with integrable fractional power singuarities, and even if our result has been proved for linear level~1 ODEs, we allow holomorphic coefficents that are not necesserly Laplace transforms.
+\textcolor{orange}{Our approach differs from Braaksma's in two ways.
+[\ldots]} \textcolor{RoyalBlue}{What distinguishs our result from Braaksma's is considering the Laplace transform of functions with integrable fractional power singuarities, and even if our result has been proved for linear level~1 ODEs, we allow holomorphic coefficents that are not necesserly Laplace transforms.}
+
+In future work, it might be useful to combine our approach with Braaksma's
+
+Combining our approach with Braaksma's, to
 
@@
 & \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency domain} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
-\textbf{Position domain} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
+\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+\textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
 & Fixed-point iteration~\cite{reg-sing-volterra} \\
@@
 
-In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of $e^{i\theta}\infty$ under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
+In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of \textcolor{magenta}{$e^{i\theta}\infty$} under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
 Generic directions correspond to $\theta\neq \arg (\alpha-\beta)$.
@@
 
-In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z\to e^{i\theta}\infty$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
+In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z \to \infty$ in direction $\theta$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
 This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
@@
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
-\subsection{The geometry of the Laplace transform}
+\subsection{The geometry of the Laplace transform}\label{sec:geometry_laplace}
 Classically, the Laplace transform turns functions on the position domain into functions on the frequency domain.
@@
 commute.
-\subsubsection{Boundary}
-\textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
-%
+% \subsubsection{Boundary}
+% \textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
+% %
 \subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
@@
 \begin{equation}\label{laplace:int}
-\laplace_{\zeta}^\theta f\big|_b = \int_{\Gamma_{b}^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function and $\Gamma_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We’ll use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_b$ throughout this document.
+%%\laplace_{\zeta}^\theta f\big|_b =
+\int_{\mathcal{J}_{b}^\theta} e^{-z\zeta} f\,d\zeta,
+\end{equation}
+where $z$ is the frequency function and $\mathcal{J}_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$.
+We will use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_b$ throughout this document.
 \textcolor{magenta}{[Notation conflict: we also use $\laplace_{\zeta, \alpha}$ to represent starting at $\zeta = \alpha$, giving the starting point as a coordinate value instead of a point $b$.]}
@@
 \begin{itemize}
-\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\Gamma_b^\theta$.
-\item The ray $\Gamma_b^\theta$ avoids the branch points after leaving $b$.
+\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_b^\theta$.
+\item The ray $\mathcal{J}_b^\theta$ avoids the branch points after leaving $b$.
 \item The integral converges. We guarantee this by asking for a pair of simpler conditions.
@@
 \begin{itemize}
-\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\Gamma_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\Gamma_b^\theta$.
+\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\mathcal{J}_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
+We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\mathcal{J}_b^\theta$.
 \item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.
@@
 When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\Gamma_b^\theta$.
+Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_b^\theta$.
 The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*_bB$ along the $n$th-power map.
@@
 The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.
+\textcolor{PaleVioletRed}{[We use $\singexp{}{}$ in the diagram below, but it hasn't been introduced yet.
+Should we just use generic holomorphic function spaces instead?
+Note that multiplying $\mathcal{O}_{T^*B}(H)$ by $e^{bz}$ (marked in magenta) doesn't do anything.]}
 
@@
 \begin{tikzcd}
- \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
+ \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & \textcolor{magenta}{e^{bz}}\,\mathcal{O}_{T^*B}(H)\\
 & \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
@@
 \begin{align*}
-\laplace_{\zeta, b} \varphi & = \int_{\Gamma_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\Gamma_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
-& = e^{-b z} \int_{\Gamma_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
+\laplace_{\zeta, b} \varphi & = \int_{\mathcal{J}_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\mathcal{J}_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
+& = e^{-b z} \int_{\mathcal{J}_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
 & = e^{-b z} \laplace_{\zeta_b, 0} \varphi.
@@
     \begin{align*}
-\laplace_{\xi, 0} \varphi & = \int_{\Gamma_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
-& = \int_{\Gamma_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
+\laplace_{\xi, 0} \varphi & = \int_{\mathcal{J}_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
+& = \int_{\mathcal{J}_{\zeta, 0}} e^{-z \zeta}\,\varphi\;\mu\,d\zeta \\
 & = \mu\,\laplace_{\zeta, 0} \varphi
@@
 \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
-Suppose $\Omega_\beta$ contains the ray $\Gamma_{\zeta, \beta}^\theta$.
+Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$.
 In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$.
@@
 
-\color{Maroon}
+\color{NavyBlue}
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
@@
 \begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta f| & = \left| \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
-& \le \int_{\Gamma_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& \le \int_{\Gamma_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
+|\laplace_{\zeta_\alpha, 0}^\theta f| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
+& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
 \end{align*}
@@
 \begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta f| & \le \int_{\Gamma_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+|\laplace_{\zeta_\alpha, 0}^\theta f| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
 & = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
@@
 Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\textcolor{magenta}{\Lambda}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
-Parameterize $\textcolor{magenta}{\Lambda}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\textcolor{magenta}{\Lambda}$.
-Along $\Lambda$, we have
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\textcolor{magenta}{\mathcal{C}}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+Parameterize $\textcolor{magenta}{\mathcal{C}}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\textcolor{magenta}{\mathcal{C}}$.
+Along $\mathcal{C}$, we have
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
 for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-On $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
+On $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\mathcal{C}}$, we have
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]
 
-%%Choose a path $\textcolor{magenta}{\Lambda}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
+%%Choose a path $\textcolor{magenta}{\mathcal{C}}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
 %%\[ \Delta = m + \sin(\varepsilon)\,|t|, \]
@@
 
-%Choose any path $\textcolor{magenta}{\Lambda}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
+%Choose any path $\textcolor{magenta}{\mathcal{C}}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
 The inverse Laplace transform is given by the formula
@@
 The inverse Laplace transform is given by the formula
-\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\Lambda}} e^{z\zeta_\alpha} F\,dz. \]
+\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\mathcal{C}}} e^{z\zeta_\alpha} F\,dz. \]
 When $F$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\Lambda}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz \\
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\mathcal{C}}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz \\
 & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
@@
 
-%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\Lambda}$.
-Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\Lambda}$, we have
+%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\mathcal{C}}$.
+Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\mathcal{C}}$, we have
 %%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
@@
 %\begin{align*}
- %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\Gamma_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\Gamma_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
+ %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\mathcal{J}_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
+  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\mathcal{J}_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
   %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
@@
 \color{RoyalBlue}
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[what does this mean?]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
+A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[exponents must lie along a ray]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
 
@@
 \end{center}
-commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$. Notice that the functions of the varible $z$ are meant to be on the fiber $T^*_{\zeta=0}B$. 
+commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$.
+Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
 %\end{lemma}
 \subsubsection{Change of translation chart}\label{transl-borel}
+\textcolor{red}{[change $b$ with $\alpha$]}
 We will show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}.
@@
 
-Finally in Section~\ref{sec:frac-diff-laplace}, we will consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives both in the frequency and the position domain, and fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
-%We will see that the Borel transform and formal Laplace transform commutes with the action of derivatives and moltiplication.
-%from the space of Puiseux series in the frequency domain to  $\C\llbracket z^{-1}\rrbracket$
-
-We end this paragraph introducing the notation we will be using in the following. 
+Finally in Section~\ref{sec:frac-diff-laplace}, we will consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives in both the frequency and position domains, as well as fractional integrals and derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
+
 \begin{notation*}
@@
 \vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
-\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\varphi$ & $\series{\varphi}$ \\[1mm]
+\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
 \end{tabular}
 \end{center}
-
-%%\begin{tabular}{ll}
-%%$\Phi$ & Upper-case letters without tildes represent holomorphic functions on the frequency domain.
-%%\end{tabular}
-\color{RoyalBlue}
-\begin{itemize}
-\item $\Phi$: upper-case letters represent holomorphic functions on the frequency domain;
-\item $\tilde{\Phi}$: \textit{tilde} stands for formal series, so an upper-case letter with \textit{tilde} is a formal series in the frequency domain;
-\item $\phi$: lower-case letters are holomorphic functions on the frequency domain.
-Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the spatial domain into functions on the frequency domain, we might write $\laplace_{\zeta,0}\phi=\Phi$.
-\item $\tilde{\phi}$: lower-case letter with \textit{tilde} are formal series in the Borel plane. As we’ll see, the Borel transform of $\tilde{\Phi}$ is $\borel_\zeta \tilde{\Phi}=:\tilde{\phi}$; 
-\item $\hat{\phi}$: lower-case letters with \textit{hat} are the sum of the formal series $\tilde{\phi}$, when it exists.  
-\end{itemize}
+We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.
+\end{notation*}
+Here are some examples of this notation in action.
+Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the position domain into functions on the frequency domain, we might write $\laplace_{\zeta,0} \phi = \Phi$.
+On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
 \color{black}
-\end{notation*}
-%between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with th
-%In fact, we deduce that the Borel transform is an isomorphism between $1$-Gevrey series $z^{-1}\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$.
-\textcolor{orange}{[Why not say this more generally, with $\C\llbracket z^{-1} \rrbracket$ and $\C\llbracket\zeta\rrbracket$?]} The inverse of $\borel_\zeta$ is what we call a \textit{formal Laplace transform}.
-\textcolor{orange}{[This seems a little weird to me, since we define the Borel transform as a formal inverse to the Laplace transform.
-Wouldn't it be easier to define the formal Laplace transform as a formal version of the Laplace transform, and then define the Borel transform as its inverse?]} In addition, in Section \ref{convolution} we’ll prove that the Borel transform is an algebra homomoprhism.
-
+%
 \subsubsection{The convolution product}\label{convolution}
@@
     Let $\sigma>-1$ and $\Lambda>0$.
-The Laplace transform $\laplace_{\zeta,0}$ is $\C$-algebra homomorphism from $(\singexp{\sigma}{\Lambda}(\Omega),\ast)$ to to the space of holomorphic functions on the right-half-plane $\Re z>0$ with the standard multiplication of functions.
+The Laplace transform $\laplace_{\zeta,0}$ is a $\C$-algebra homomorphism from $(\singexp{\sigma}{\Lambda}(\Omega), \ast)$ to to the space of holomorphic functions on the right-half-plane $\Re z>0$ with the standard multiplication of functions.
 \end{prop}
@@
 \begin{remark}
-    it is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms.
+We saw in Section~\ref{sec:reg-decay} that when $\Omega$ is an appropriate sector, the Laplace transform on $\singexp{\sigma}{\Lambda}(\Omega)$ has a left inverse.
+In light of the proposition above, that means the Laplace transform is a $\C$-algebra isomorphism onto its image.
+    \color{RoyalBlue} It is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms.
 However we will refer to \textcolor{magenta}{[standard reference]} for details.
 \textcolor{magenta}{[see also section on Regularity for Laplace]}
+    \color{black}
 \end{remark}
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-Noting that $|z|/\Delta$ goes to a constant limit as $|z| \to \infty$ along any ray \textcolor{magenta}{[check; note that the constant isn't uniform!]}, we deduce that
+Noting that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \textcolor{magenta}{[check]},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
 \begin{align*}
@@
 To prove Step $(b)$ we will use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$.
-First, recall that ${\psi}_\alpha$ is the uniques solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}.
-Then, as shown in Lemma~\ref{lem:picard-power}, the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$.
+First, recall that ${\psi}_\alpha$ is the unique solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}.
+Then,\textcolor{orange}{[change as new argument]} , the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$.
 Since by direct computations $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$
@@
 
-Finally, we can Laplace transform $\hat{\psi}_\alpha$ along a ray $\Gamma_{\alpha}^\theta$ in $\Omega_\alpha$, proving the $\tilde{\Psi}_\alpha$ is Borel summable.
+Finally, we can Laplace transform $\hat{\psi}_\alpha$ along a ray $\mathcal{J}_{\alpha}^\theta$ in $\Omega_\alpha$, proving the $\tilde{\Psi}_\alpha$ is Borel summable.
 In addition, since $\tilde{\psi}_\alpha\propto\psi_\alpha$, their Laplace transform will be proportional too $\laplace_{\zeta,\alpha}^\theta\hat{\psi}_\alpha\propto \Psi_\alpha$.
@@
 \begin{equation}\label{exp-int}
-I_\alpha \defeq \int_{\Lambda_a^\theta} e^{-zf} \nu
-\end{equation}
-where $\Lambda_a^\theta$ is the thimble through the critical point $a$ and $\alpha=f(a)$.
+I_\alpha \defeq \int_{\mathcal{C}_a^\theta} e^{-zf} \nu
+\end{equation}
+where $\mathcal{C}_a^\theta$ is the thimble through the critical point $a$ and $\alpha=f(a)$.
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
@@
 \begin{equation}\label{eqn:formula-proof}
-    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right),
-\end{equation}
-where $\Lambda_\alpha^\theta(\zeta)$ is the part of $\Lambda_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
-Notice that $\Lambda_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\Lambda_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
+    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\mathcal{C}_\alpha^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\mathcal{C}_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
@@
     Let us recast the integral $I_\alpha$ into the position domain.
-As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\Lambda_\alpha^\theta(\zeta)$ sweep backward along $\Lambda^-_\alpha(\zeta)$ and forward along $\Lambda^+_\alpha(\zeta)$, respectively.
+As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\mathcal{C}_\alpha^\theta(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
 Hence, we have
 \begin{align*}
-I_\alpha(z) & = \int_{\Lambda_a^\theta} e^{-zf} \nu \\
-& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}\,d\zeta.
+I_\alpha(z) & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
+& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha^\theta(\zeta)}\,d\zeta.
 \end{align*}
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \Lambda_\alpha^\theta(\zeta)}^{\operatorname{end} \Lambda_\alpha^\theta(\zeta)}.
+{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha^\theta(\zeta)}.
 \end{equation}
@@
 \item\label{part-2-prf} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3-prf} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\Gamma_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
+\item\label{part-3-prf} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
 \end{enumerate}
@@
 Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
-Let $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$ be the parts of $\Lambda_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\Lambda^-_\alpha$ and $\Lambda^+_\alpha$, respectively.
+Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
+We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
 \textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
@@
 \end{align*}
-taking the positive branch of the square root on $\Lambda^+_a$ and the negative branch on $\Lambda^-_a$.
+taking the positive branch of the square root on $\mathcal{C}^+_a$ and the negative branch on $\mathcal{C}^-_a$.
 Plugging this into our expression for $\iota_\alpha$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
 \begin{align*}
-\iota_\alpha & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \Lambda_a(\zeta)}^{\operatorname{end} \Lambda_a(\zeta)} \\
+\iota_\alpha & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \mathcal{C}_a(\zeta)}^{\operatorname{end} \mathcal{C}_a(\zeta)} \\
 & = \sum_{m \ge 0} b_m^a \Big( [2\zeta_\alpha]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_\alpha]^{(m - 1)/2} \Big) \\
@@
 \end{align*}
-In particular, $\tilde{\iota}_\alpha$ can be analytically continued along $\Gamma_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
+In particular, $\tilde{\iota}_\alpha$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
 %Thus, we can take the Laplace transform of $\phi_j$ and we find
@@
 & \color{magenta} = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = 0}^\infty 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right).
-%%& = \int_{\Gamma_j^\theta} e^{-z\zeta_j} \iota_j\,d\zeta_j \\
-%%& = \int_{\Gamma_j^\theta} e^{-z\zeta_j} \left( \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right) d\zeta_j
+%%& = \int_{\mathcal{J}_j^\theta} e^{-z\zeta_j} \iota_j\,d\zeta_j \\
+%%& = \int_{\mathcal{J}_j^\theta} e^{-z\zeta_j} \left( \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right) d\zeta_j
 \end{align*}
@@
         \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha &= \fracderiv{-1}{\zeta}{\alpha} \, \iota_\alpha \\
-        & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\Lambda_a^\theta(\zeta)}\nu \right) \\
-        & = \int_{\Lambda_\alpha^\theta(\zeta)}\nu - \int_{\Lambda_\alpha^\theta(\alpha)}\nu.
-    \end{align*}
-    The second term vanishes because $\Lambda_\alpha^\theta(\alpha)$ is a single point, leaving
-    \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\Lambda_\alpha^\theta(\zeta)}\nu. \]
+        & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
+        & = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
+    \end{align*}
+    The second term vanishes because $\mathcal{C}_\alpha^\theta(\alpha)$ is a single point, leaving
+    \[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu. \]
     Finally, we apply the $1/2$ derivative of both sides, recalling that it is a left inverse of the $1/2$ integral, and we find
-    \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\Lambda_\alpha^\theta(\zeta)}\nu \right).\end{equation}
+    \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
     \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
@@
 We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
-Let us say $\Gamma_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
-As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\Lambda_\alpha^\theta(\beta)$ in $X$.
-This lets us analytically continue $\int_{\Lambda_\alpha^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
+Let us say $\mathcal{J}_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
+As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\mathcal{C}_\alpha^\theta(\beta)$ in $X$.
+This lets us analytically continue $\int_{\mathcal{C}_\alpha^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
 Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
@@
 \end{figure}
-Let us calculate the jump of $\int_{\Lambda_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
+Let us calculate the jump of $\int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
 Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
-The jump is then given by \[\int_{\Lambda_\alpha^\theta(\beta^+)} \nu - \int_{\Lambda_\alpha^\theta(\beta^-)} \nu\]
+The jump is then given by \[\int_{\mathcal{C}_\alpha^\theta(\beta^+)} \nu - \int_{\mathcal{C}_\alpha^\theta(\beta^-)} \nu\]
 and it is 
@@
 
-\textcolor{Navy}{Initially, the function $\int_{\Lambda_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\Lambda_j(\zeta)$.
-Since $\nu$ is holomorphic, the only way for $\int_{\Lambda_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\Lambda_j(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\Lambda_j(\zeta)$ come together, telling us that.}
+\textcolor{Navy}{Initially, the function $\int_{\mathcal{C}_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_j(\zeta)$.
+Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}_j(\zeta)$.
+At a critical point of $f$, the ends of the homotoped path $\mathcal{C}_j(\zeta)$ come together, telling us that.}
 \end{remark}
@@
 \begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \psi = 0.
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
 \end{equation}
 One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_{\Gamma} \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
-where $\Gamma$ is a path that comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$.
+\[ \Ai(y) = \frac{1}{2\pi i} \int_\gamma \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
+where $\gamma$ is a path that comes from $\infty$ at $-60^\circ$ and returns to $\infty$ at $60^\circ$.
+\textcolor{Pink}{[Figure~\ref{fig:path_Airy} shows integration contour after change of coordinates]}
 
@@
     \caption{\small In this picture of the $u$ plane, the light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively.
-The light path is the contour $\Lambda_1$.
+The light path is the contour $\mathcal{C}_1$.
 More generally, the dark blue contour corresponds to the preimage of the ray $+1+e^{i\theta}\infty$ and $\theta=$.
@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\textcolor{magenta}{y^{-1/2} \Lambda_1}} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way. Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
+where $\mathcal{C}^\theta_1$ is the preimage under \textcolor{orange}{[\ldots]} \textcolor{RoyalBlue}{We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way.
+Note that $4u^3 - 3u$ is the third Chebyshev polynomial.}
 
@@
 with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\Lambda^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\Lambda^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
-By definition, $\Lambda^\theta_j$ is a preimage of the ray $\Gamma^\theta_{\mp 1}$ under the function $-T_n(u)$. The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+where $\mathcal{C}^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
+By definition, $\mathcal{C}^\theta_j$ is a preimage of the ray $\mathcal{J}^\theta_{\mp 1}$ under the function $-T_n(u)$.
+The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
 \begin{center}
 \includegraphics[width=10cm]{figures/thimbles-n5.png} \\[1em]
-{\small Integration contour $\Lambda^{(j)}$ for the Airy--Lucas function with $n=5$.
+{\small Integration contour $\mathcal{C}^{(j)}$ for the Airy--Lucas function with $n=5$.
 The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=\textcolor{magenta}{???}$.
@@
    \includegraphics[width=10cm]{figures/thimbles-n5.png}
-    \caption{Integration contours $\Lambda^\theta_j$ for the Airy--Lucas functions with $n=5$.
-The dark and light thimbles are the preimages of the rays $\Gamma^{\pi/8}_{\zeta, 1}$ and $\Gamma^{\pi/8}_{\zeta, -1}$, respectively.
+    \caption{Integration contours $\mathcal{C}^\theta_j$ for the Airy--Lucas functions with $n=5$.
+The dark and light thimbles are the preimages of the rays $\mathcal{J}^{\pi/8}_{\zeta, 1}$ and $\mathcal{J}^{\pi/8}_{\zeta, -1}$, respectively.
 \textcolor{orange}{[Preferred version, with ``Figure'' label]}}
@@
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \textcolor{magenta}{\text{const.}}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
 where
 \begin{equation}\label{integral:mod-bessel-rational-AL}
-K^{(j)}_{m/n}(z) = \textcolor{magenta}{\text{const.}} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
-\end{equation}
-Saying that $\widehat{\Ai}^{(j)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K$ satisfies the modified Bessel $\frac{m}{n}$ equation \textcolor{orange}{[Why put the order $m/n$ in the name?
-Is that standard?]}
+K^{(j)}_{m/n}(z) = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}\int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+\end{equation}
+Saying that $\widehat{\Ai}^{(j)}_{n, m-1}$ satisfies the Airy-Lucas equation is equivalent to saying that $K^{(j)}_{m/n}$ satisfies the modified Bessel equation with parameter $\frac{m}{n}$:
 \begin{equation}\label{eqn:mod-bessel-AL}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
-
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] \Phi = 0.
+\end{equation}
+%%[DROPPED] In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
 Let us put Equation~\eqref{eqn:mod-bessel-AL} in the form $\mathcal{P}\Phi=0$ with $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}:
 \begin{equation}\label{eqn:reg-mod-bessel-AL}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] K = 0.
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] \Phi = 0.
 \end{equation}
@@
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
-For each root $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in the figure from Theorem~\ref{thm:exist_uniq_ODE}\textcolor{RoyalBlue}{[Figure \ref{Fig:domain}]}.
+For each root \textcolor{orange}{[switch to $\alpha$]} $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
 We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
+We learned in Section~\ref{sec:change-translation} that
 \[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} V_j \]
@@
 \begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \xi_1\big) \\[1mm]
 &=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
@@
 \begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} & {}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
 \end{alignat*}
@@
 We will now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+\textcolor{orange}{[We're following the version of the argument that shows the Poincar\'{e} solutions exist and are 1-Gevrey.]}
 
@@
 We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\Lambda^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
-Recalling that $\Lambda^\theta_j$ is a preimage of $\Gamma^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
+The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
+Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
 \begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Lambda^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
-\end{align*}
-where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\Lambda^\theta_j$, respectively.
+K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+\end{align*}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
 \begin{center}
@@
 Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
-On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\Lambda^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$.
+On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$.
 The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
@@
 \end{align*}
-away from the line $\Re(\zeta) = 0$ and the rays $\Gamma^0_{\zeta,1}$ and $\Gamma^\pi_{\zeta,-1}$.
+away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
 
 Returning to the projected thimble integral
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\Gamma^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
 we can see the integrand as the variation of the function
 \[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
-across the branch cut $\Gamma^\theta_{\zeta, \mp 1}$.
+across the branch cut $\mathcal{J}^\theta_{\zeta, \mp 1}$.
 When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$.
@@
 For odd $j$, we have
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\Gamma^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
 and for even $j$, we have \textcolor{magenta}{[check]}
-\[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\Gamma^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
 \]
@@
 \end{align*}
-we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\Lambda^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
+we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\mathcal{C}^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
 \begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\Lambda^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Lambda_j}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\Lambda_j}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\mathcal{C}^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
 \end{align}
-where $\Lambda_j$ is the path coming from infinity along $-i\pi+(2\pi i) j+(-\infty,0]$ and going to infinity along $i \pi+(2\pi i) j+[0,+\infty)$, as represented in Figure \ref{fig:bessel_unrolled}.
-In fact, since $\cosh(t)$ is periodic, the integral has the same value for every choice of $\Lambda_j$ with $j\in\Z$.
+where $\mathcal{C}_j$ is the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, as represented in Figure \ref{fig:bessel_unrolled}.
+Because $\cosh(t)$ is periodic, the integral has the same value for every choice of $\mathcal{C}_j$ with $j\in\Z$.
 \begin{figure}[ht]
@@
     \includegraphics[scale=0.3]{figures/Bessel0_unrolled_lightblue.png}
-    \caption{The paths $\Lambda_j$.}
+    \caption{The paths $\mathcal{C}_j$.}
     \label{fig:bessel_unrolled}
@@
 \begin{equation}\label{int:mod-bessel-gen}
- K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\Lambda_0} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
+ K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}_0} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
 \end{equation}
@@
    %    \notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-%\notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\Lambda'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
+%\notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\mathcal{C}'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
  %   \end{align*}
-  %  where $\Lambda'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
+  %  where $\mathcal{C}'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
   Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it is the reference in \cite{dlmf})
@@
 \end{align*}
-where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$. Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf}
-
+where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$.
+Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf} \textcolor{PaleVioletRed}{[Please clean up operators that are repeated across line breaks, like the $=$ below.
+I like the equation spacing in the ``Thimble projection reasoning for Airly-Lucas functions'' section; can we copy that here?]}
 \begin{multline*}
-     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) = \\
+     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
      =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
@@
 \begin{align*}
-\mathrm{A}_k(y,p)&=\frac{1}{2\pi i}\int_{\Gamma_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(y,p)&=\frac{1}{2\pi i}\int_{\Gamma_0}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
+\mathrm{A}_k(y,p)&=\frac{1}{2\pi i}\int_{\mathcal{J}_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
+\mathrm{B}_0(y,p)&=\frac{1}{2\pi i}\int_{\mathcal{J}_0}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
 \mathrm{B}_k(y,p)&=\int_{\gamma_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
 \end{align*}
-where the contours $\Gamma_k, \Gamma_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}. 
+where the contours $\mathcal{J}_k, \mathcal{J}_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}. 
 \begin{figure}[ht]
@@
     \draw[blue,very thick] (4,4) circle (0.5) ;
-    \node[blue,font=\tiny] at (4.5,3.5) {$\Gamma_0$};
-    \node[red,font=\tiny] at (1.4,1.3) {$\Gamma_1$};
+    \node[blue,font=\tiny] at (4.5,3.5) {$\mathcal{J}_0$};
+    \node[red,font=\tiny] at (1.4,1.3) {$\mathcal{J}_1$};
     \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
-    \node[red,font=\tiny] at (5.5,4.8) {$\Gamma_2$};
+    \node[red,font=\tiny] at (5.5,4.8) {$\mathcal{J}_2$};
     \draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
-     \node[red,font=\tiny] at (5.5,3.2) {$\Gamma_3$};
+     \node[red,font=\tiny] at (5.5,3.2) {$\mathcal{J}_3$};
     \draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
@@
 %
-\[I_+(z,p):=\frac{1}{2\pi i}\int_{z^{-1/3}\Gamma_1} e^{-z(4u^3-3u)} \frac{du}{u^p}\]
+\[I_+(z,p):=\frac{1}{2\pi i}\int_{z^{-1/3}\mathcal{J}_1} e^{-z(4u^3-3u)} \frac{du}{u^p}\]
 %
@@
   \begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\Lambda_{+}}e^{-z(4u^3-3u)}\, \frac{du}{u^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\Lambda_{+}}e^{-z(\tfrac{4}{12}\tfrac{t^3}{z}-3 (12 z)^{-1/3}t)}\frac{dt}{t^p} & u=(12 z)^{-\tfrac{1}{3}}t\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\Lambda_{+}}e^{-\left(\frac{t^3}{3}-(\tfrac{3}{2} z)^{2/3}t\right)}\frac{dt}{t^p} & \\
+I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4u^3-3u)}\, \frac{du}{u^p} &\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\mathcal{C}_{+}}e^{-z(\tfrac{4}{12}\tfrac{t^3}{z}-3 (12 z)^{-1/3}t)}\frac{dt}{t^p} & u=(12 z)^{-\tfrac{1}{3}}t\\
+&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\mathcal{C}_{+}}e^{-\left(\frac{t^3}{3}-(\tfrac{3}{2} z)^{2/3}t\right)}\frac{dt}{t^p} & \\
 &=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
@@
 
-\[ I_j(z) = \int_{\Lambda_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
-
-where $\Lambda_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
+\[ I_j(z) = \int_{\mathcal{C}_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
+
+where $\mathcal{C}_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
 We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$.
@@
     \begin{align*}
-        \int_{\Lambda_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
+        \int_{\mathcal{C}_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
     \end{align*}
@@
     \begin{align*}
-        \int_{\Lambda_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
+        \int_{\mathcal{C}_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
     \end{align*}
@@
 \begin{align*}
-    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\Lambda_+} e^{z (4t^3-3t)} du\\
-    &= 2\sqrt{-\tfrac{p}{3}} \int_{\Lambda_+} e^{z (4t^3-3t)} dt \\
+    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\mathcal{C}_+} e^{z (4t^3-3t)} du\\
+    &= 2\sqrt{-\tfrac{p}{3}} \int_{\mathcal{C}_+} e^{z (4t^3-3t)} dt \\
     &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
@@
 \begin{align*}
-    \int_{\Lambda} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
+    \int_{\mathcal{C}} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
     &= e^{i\pi/3} \int_q^{+e^{i\theta}\infty} e^{-z\zeta} \, \zeta_q^{-2/3}\,  d\zeta
@@
 \newcommand{\cthic}{0.1}
-\fill[black!10] (0, \cthic, 0) -- ++(6, 0, -\ctaper) -- ++(0, -2*\cthic, 0) -- ++(0, 0, 2*\ctaper) -- (0, -\cthic, 0);
+\fill[pwbeige!10] (0, \cthic, 0) -- ++(6, 0, -\ctaper) -- ++(0, -2*\cthic, 0) -- ++(0, 0, 2*\ctaper) -- (0, -\cthic, 0);
 \draw (0, -\cthic, 0) -- ++(\clen, 0, \ctaper) -- ++(0, 0, -2*\ctaper);
-\draw[black!50] (0, 0, 0) -- ++(\clen, 0, 0);
+\draw[pwbeige] (0, 0, 0) -- ++(\clen, 0, 0);
 \draw[->] (\clen, 0, 0) -- ++(1, 0, 0) node[anchor=west] {$z$};
@@
 Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}, indexed by the fourth roots of $\omega^2$.
-\par\color{RoyalBlue}
-As we will show in Section~\ref{shifting}, for $j=1,\ldots,4$, $v_j$ solves \eqref{eqn:position_j} if and only if $v_j$ solves the differential equation 
-\begin{equation}
-    \Big[\big[\zeta^4+\mu\big]\tfrac{\partial}{\partial\zeta}-2\zeta^3\Big]v_j = 0
-\end{equation}
-In particular, at $\zeta_j=\zeta-\alpha_j$ we find 
-\[v_j \propto \frac{1}{\zeta_j^{1/2}}\, \prod_{k\neq j}(\zeta_j-\alpha_k+\alpha_j)^{-1/2}.\]
-\color{black}
-\textcolor{orange}{[Stokes? Thimbles?]}
-
-\textcolor{orange}{Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$}
+\par\textcolor{orange}{[Stokes? Thimbles? Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$.]}
 %\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}
@@
 \begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\Lambda_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-and the contour $\Lambda_1$ is represented in Figure \ref{fig:path_Airy}.
+K(z) = i\sqrt{3} \int_{z^{-1/3}\mathcal{C}_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+and the contour $\mathcal{C}_1$ is represented in Figure \ref{fig:path_Airy}.
 Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
@@
 Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \Lambda_1$ to a contour $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \Lambda_1$, we have
+Projecting $z^{-1/3} \mathcal{C}_1$ to a contour \textcolor{magenta}{[rephrase in terms of ray]} $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \mathcal{C}_1$, we have
 \begin{equation}\label{integral:mod-bessel-zeta}
@@
 
-In addition to the solutions $v_1$ and $v_{-1}$ from Section~\ref{pos-root}\,--\, \ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
+In addition to the solutions $v_1$ and $v_{-1}$ from Sections~\ref{pos-root}\,--\,\ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
 \begin{alignat*}{2}
@@
 \textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
-The thimble $\Lambda_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
-Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\Lambda_1(\zeta)$ are then characterized by
+The thimble $\mathcal{C}_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
+Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_1(\zeta)$ are then characterized by
 \begin{align*}
@@
 \begin{align*}
-\int_{\Lambda_1(\zeta)} \nu & = \int_{\Lambda_1(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \Lambda_1(\zeta)}^{\operatorname{end} \Lambda_1(\zeta)}\\
+\int_{\mathcal{C}_1(\zeta)} \nu & = \int_{\mathcal{C}_1(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_1(\zeta)}^{\operatorname{end} \mathcal{C}_1(\zeta)}\\
  & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
@@
 then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\Lambda_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\Lambda_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
-\begin{align*}
-\fracderiv{-1/2}{\zeta}{1} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_1(\zeta')} \nu \right)\,d\zeta' \\
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
+\begin{align*}
+\fracderiv{-1/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_1(\zeta')} \nu \right)\,d\zeta' \\
 & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
@@
 \begin{align*}
-\fracderiv{3/2}{\zeta}{1} \left( \int_{\Lambda_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+\fracderiv{3/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
 & =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
@@
 %
-For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\Lambda_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
-\begin{align*}
-\int_{\Lambda_{-1}(\zeta)} \nu & = \int_{\Lambda_{-1}(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \Lambda_{-1}(\zeta)}^{\operatorname{end}\Lambda_{-1}(\zeta)}.
-\end{align*}
-The start and end points of $\Lambda_{-1}$ are characterized by
+For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\mathcal{C}_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_{-1}(\zeta)} \nu & = \int_{\mathcal{C}_{-1}(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_{-1}(\zeta)}^{\operatorname{end}\mathcal{C}_{-1}(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_{-1}$ are characterized by
 \begin{align*}
@@
 \begin{align*}
-\int_{\Lambda_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+\int_{\mathcal{C}_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
 & =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
@@
 \[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu =  (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\Lambda_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
-\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\Lambda_{-1}(\zeta')} \nu \right)\,d\zeta' \\
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
+\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_{-1}(\zeta')} \nu \right)\,d\zeta' \\
 & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\, (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \,d\xi' \big) \\
@@
 \begin{align*}
-\fracderiv{3/2}{\zeta}{-1} \left( \int_{\Lambda_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+\fracderiv{3/2}{\zeta}{-1} \left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
 & = - \tfrac{\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\

### 2024-03-28 exp-resurgence.tex
Make verifications and unstable references hideable

@@
 \usepackage{amsthm}
-%\usepackage{eqnarray}
 \usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
-\usepackage{bm} %% for putting series names in bold
-%%\usepackage{amsthm}
+%%\usepackage{bm} %% for putting series names in bold
 \usepackage{graphicx}
@@
 \usepackage{xparse} %% for squiggly underlines
-\usepackage{tikz-cd} %% for term norm scratch work
 \usepackage{tikz}
-%\usepackage{eqnarray}
+\usepackage{tikz-cd}
+\usepackage{rotating} % for \isoarrow
+\usepackage{environ} % to hide verifications and stuff
 
@@
 \newcommand{\Q}{\mathbb{Q}}
-\usepackage{tikz}
-\usepackage{tikz-cd}
-\usepackage{rotating}
 \newcommand*{\isoarrow}[1]{\arrow[#1,"\rotatebox{90}{\(\sim\)}"
@@
 
+% hideable verifications
+\newif\ifshowverify
+\showverifytrue
+\ifshowverify
+\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+\else
+\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
+\fi
+
+% hideable notes for unstable references
+\newif\ifshowunstable
+\showunstabletrue
+\ifshowunstable
+\newenvironment{unstable}{\color{YellowGreen}}{\color{black}}
+\else
+\NewEnviron{unstable}{\iffalse\expandafter\BODY\fi}
+\fi
+\newcommand{\citesection}[1]{\begin{unstable}\texttt{#1}\end{unstable}}
+
 % drafting environments
-\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
-\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+%%\usepackage{environ} % to hide verifications
+%%\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
+%%\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
 
@@
   (0, 0) -- (41:\spill) arc (41:-48:\spill) -- cycle;
-\fill[ietcoast] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
+\fill[ietcoast!33!black] circle (0.7mm) node[anchor=-15, outer sep=1mm] {$\zeta = \alpha$};
 \foreach \p in {(107.5:1.95), (46.5:2.46), (-56:2.24)} {
-  \fill[ietcoast] \p circle (0.7mm);
+  \fill[ietcoast!33!black] \p circle (0.7mm);
 }
@@
 
-In \textcolor{orange}{\tt sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
+In \citesection{sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
 \[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]

### 2024-03-28 exp-resurgence.tex
Remove extra indices from Airy-Lucas argument
Also, mark revisions needed to bring this section up to date.

@@
 Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (0,1)$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of order $\sigma=1/2$ at each regular singular point.
+However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (-1, 0)$.
+
+This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution \textcolor{magenta}{of order $\sigma=1/2$} at each regular singular point.
 We can see the regular singularities by moving the derivatives to the right:
@@
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
-For each root \textcolor{orange}{[switch to $\alpha$]} $\alpha_j$, we will find a solution $v_j$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma$, and $\Omega_j$ as in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
+For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ for some constant $\tau_\alpha \in (0, 1)$ and some domain $\Omega_\alpha$ resembling the one in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
+We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, \textcolor{magenta}{and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$}.
 We learned in Section~\ref{sec:change-translation} that
-\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} V_j \]
-where $V_j = \laplace_{\zeta_j, 0} v_\alpha$ and $\zeta = \alpha_j + \zeta_j$.
-We can see from Section~\ref{sec:reg-decay} that $V_j$ is asymptotic to a scalar multiple of $z^{-1 - \tau_j}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha_j} v_j = e^{-\alpha_j z} z^{-\tau_j} W_j, \]
-makes $W_j$ is asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
 %\color{Peru}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+Since $v_1$ \textcolor{magenta}{has order $-1/2$}, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
@@
 In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 1$:
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which \textcolor{magenta}{belongs to $\singexpalg{-1/2}$ at $\xi_1 = 1$}:
 \begin{alignat*}{2}
@@
 From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+Since $v_{-1}$, like our other solution, \textcolor{magenta}{has order $-1/2$}, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
 
@@
 The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_j\in\singexpalg{1/2}(\Omega_j)$.
+The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.
 \begin{verify}
-We get $v_j$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_j = \zeta^{\tau-1} + v_j'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
+We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau_\alpha-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
 Doesn't match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$.
@@
 v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
-& \Longrightarrow \zeta_j^\epsilon\,\zeta_j^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longrightarrow \zeta_j^{1-\tau}\,v_j' \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longrightarrow v_j' / \zeta_j^{\tau-1} \text{ goes to } 0 \text{ as } \zeta_j \text{ goes to } 0 \\
-& \Longleftrightarrow v_j' \in o\big(\zeta_j^{\tau-1}\big).
-\end{align*}
-In this case, $\tau = \tfrac{1}{2}$.
+& \Longrightarrow \zeta_j^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau_\alpha-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
+& \Longleftrightarrow v_j' \in o\big(\zeta_\alpha^{\tau_\alpha-1}\big).
+\end{align*}
+In this case, $\tau_\alpha = \tfrac{1}{2}$.
 \end{verify}
@@
 
-The Borel transform maps $e^{-\alpha_j z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ (see Section \ref{sec:action_transseries}), and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_j^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ into $\zeta_j^{-1/2}+ o\big(\zeta_j^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
+The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ \textcolor{magenta}{(see Section \ref{sec:action_transseries})}, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
+Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
+Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
 
@@
 It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling.
-That means $\borel\big[ e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j \big]$ must sum to a scalar multiple of $v_j$.
-Thus, if $e^{-\alpha_j z} z^{-1/2}\,\tilde{W}_j$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha_j} v_j$.
+That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
+Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
 

### 2024-03-28 exp-resurgence.tex
Revise generalized Airy example

@@
 \usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
+\usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} %% hat tip https://tex.stackexchange.com/a/247819
 %%\usepackage{bm} %% for putting series names in bold
@@
 \section{Examples}\label{sec:examples}
-
-\subsection{Airy}
-
+%
+\subsection{Airy}\label{sec:airy}
+%
 The Airy equation is
 \begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] F = 0.
 \end{equation}
@@
 \begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \psi = 0
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] F = 0
 \end{equation}
@@
 \subsection{Generalized Airy}
-In \cite{Reid} and \cite[Appendix]{drazin-reid} the authors introduce generalized Airy functions $A_k, B_0, B_k$, $k=1,2,3$ as approximate solutions of the Orr--Sommerfield fluid equation.
-They are defined as contour integral \cite[Section 9.13(ii)]{dlmf}
-
-\begin{align*}
-\mathrm{A}_k(y,p)&=\frac{1}{2\pi i}\int_{\mathcal{J}_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\C \\
-\mathrm{B}_0(y,p)&=\frac{1}{2\pi i}\int_{\mathcal{J}_0}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad p\in\Z \\
-\mathrm{B}_k(y,p)&=\int_{\gamma_k}e^{yt-\tfrac{t^3}{3}}\frac{dt}{t^p} \qquad k=1,2,3\,\, p\in\Z 
-\end{align*}
-where the contours $\mathcal{J}_k, \mathcal{J}_0, \gamma_k$ are represented in Figure \ref{fig:path-generalized-Airy}. 
+\color{NavyBlue}
+In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
+\begin{align*}
+\mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\hphantom{{}_{\le 0}},\quad k \in \{1,2,3\} \\
+\mathrm{B}_0(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{b}_0} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \Z \\
+\mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p}, & & p \in \Z_{\le 0},\quad k \in \{1,2,3\}
+\end{align*}
+which are defined by integrals along the contours $\mathscr{a}_k, \mathscr{b}_0, \mathscr{b}_k$ shown in Figure~\ref{fig:path-generalized-Airy}~\cite{drazin-reid}\cite[Section 9.13(ii)]{dlmf}.
 \begin{figure}[ht]
 \center
+\newcommand{\apathcolor}{ietcoast}
+\newcommand{\bpathcolor}{black}
 \begin{tikzpicture}
-    \draw[->] (4,0)--(4,8);
-    \draw[->] (0,4)--(8,4);
-    \draw[blue,very thick] (4,4) circle (0.5) ;
-    \node[blue,font=\tiny] at (4.5,3.5) {$\mathcal{J}_0$};
-    \node[red,font=\tiny] at (1.4,1.3) {$\mathcal{J}_1$};
-    \draw[red,very thick,->] (1,0.2) .. controls (3.5,4) .. (1,7.8);
-    \node[red,font=\tiny] at (5.5,4.8) {$\mathcal{J}_2$};
-    \draw[red,very thick,->] (1.8,8) .. controls (4,4.5) ..(8,4.4) ;
-     \node[red,font=\tiny] at (5.5,3.2) {$\mathcal{J}_3$};
-    \draw[red,very thick,->] (8,3.6) .. controls (4,3.5) ..(1.8,0) ;
-    \draw[orange,very thick,->] (4,4)--(6.5,4);
-    \draw[orange,very thick] (6.5,4)--(8,4);
-    \node[orange,font=\tiny,below] at (7,4) {$\gamma_1$};
-    \draw[orange,very thick,->] (4,4)--(2.7,6);
-    \draw[orange,very thick] (2.7,6)--(1.4,8);
-    \node[orange,font=\tiny,right] at (2.2,6) {$\gamma_2$};
-    \draw[orange,very thick,->] (4,4)--(2.7,2);
-    \draw[orange,very thick] (2.7,2)--(1.4,0);
-    \node[orange,font=\tiny,right] at (2.2,2) {$\gamma_3$};
-    \node at (5.1,4) {$\bullet$};
-    \node at (2.9,4) {$\bullet$};
-    \node[font=\tiny,below,right] at (2.3,3.8) {$-1$};
-    \node[font=\tiny,below] at (5.3,4) {$1$};
+\renewcommand{\dotsize}{0.08}
+\fill[pwbeige!10] circle(3.95);
+\begin{scope}[\bpathcolor, very thick, -stealth]
+  \draw (80:0.8) arc (80:400:0.8);
+  \node at (60:0.8) {$\mathscr{b}_0$};
+  \foreach \ang/\name in {0/1, 120/2, 240/3} {
+    \draw[very thick,-stealth] (0, 0) -- ++(\ang:4) node[anchor=\ang-180] {$\mathscr{b}_\name$};
+  };
+  \fill (1.25, 0) circle (\dotsize) node[anchor=north west] {$1$};
+  \draw[fill=white, thin] circle (\dotsize);
+\end{scope}
+\begin{scope}[\apathcolor, very thick, -stealth]
+  \foreach \ang/\name in {0/1, 120/2, 240/3} {
+    \draw[rotate=\ang] (-0.5, 0) +(-120:3.75) .. controls +(62:1) and +(0, -1.2) .. +(-0.75, 0) .. controls +(0, 1.2) and +(-62:1) .. +(120:3.75) node[midway, anchor=\ang+30] {$\mathscr{a}_\name$};
+  };
+  \fill (-1.25, 0) circle (\dotsize) node[anchor=north east] {$1$};
+\end{scope}
 \end{tikzpicture}
-    \caption{Representation of the path of integration for $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$ respectively in red, blue and orange.}\label{fig:path-generalized-Airy}
+\caption{The integration contours in the $t$ plane that define $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$.
+\textcolor{orange}{[Why are $y = \pm 1$ marked?
+Should we mark the critical points $\pm\tfrac{1}{2}$ instead?]}}\label{fig:path-generalized-Airy}
 \end{figure}
-
-Each generalized Airy function is a solution of
-\begin{equation}
-\left[\partial_y^3-y\partial_y+(p-1)\right]f=0
-\end{equation} 
-and if $p=0$ they reduce to the classical Airy functions.
-
-Following the treatment of the Airy--Lucas functions, we will rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ as thimble integrals with the function $f=4u^3-3u$.
-This follows from the change of coordinates $z=\tfrac{2}{3}y^{3/2}$, and gives $\mathrm{A}_1(y,p) = (12 z)^{\tfrac{1-p}{3}}\, I_+(z,p)$ with
-%
-\[I_+(z,p):=\frac{1}{2\pi i}\int_{z^{-1/3}\mathcal{J}_1} e^{-z(4u^3-3u)} \frac{du}{u^p}\]
-%
+These functions satisfy the generalized Airy equation
+\[ \left[\big(\tfrac{\partial}{\partial y}\big)^3 - y\,\tfrac{\partial}{\partial y} + (p-1)\right] \Phi = 0. \]
+When $p = 0$, this equation reduces to
+\[ \tfrac{\partial}{\partial y} \circ \left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0, \]
+which is equivalent to an inhomogeneous version of the classical Airy equation.
+
+As we did with the Airy--Lucas functions, we will use the substitution $t = 2uy^{1/2}$ to rewrite the generalized Airy function $\mathrm{A}_1(y,p)$ in terms of a thimble integral. We get
+\[ \mathrm{A}_1(y,p) = (12 z)^{(1-p)/3}\,I_+\big(\tfrac{2}{3}y^{3/2},p\big) \]
+with
+\[ I_+(z,p) = \frac{1}{2\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[-z\left(4u^3 - 3u\right)\right]\,\frac{du}{u^p}. \]
+To find the right contour $\mathcal{C}_1^\theta$, we first note that the mapping $\zeta = 4u^3 - 3u$ is familiar, up to a sign, from Section~\ref{sec:airy}.
+In particular, we already know its critical points $u = \pm\tfrac{1}{2}$ and the corresponding critical values $\zeta = \pm 1$.
+To get the desired integral, $\mathcal{C}_1^\theta$ should be the thimble through $u = -\tfrac{1}{2}$ over the ray $\mathcal{J}^\theta_1$.
+However, this thimble does not live on the complex plane, like it did for the classical Airy function.
+When $p$ is a positive integer, the volume form $du/u^p$ has a pole at $u = 0$, so we put $\mathcal{C}_1^\theta$ as a contour on $\C^\times$.
+More generally, for any complex value of $p$, we can put $\mathcal{C}_1^\theta$ on the universal cover $\widetilde{\C^\times}$.
 \begin{verify}
@@
 %
-Notice that, the critical points of $f$ are $\alpha_{\pm}=\pm\tfrac{1}{2}$, as in the Airy case.
-However, the volume form $\nu_p$ is meromorphic, hence $f$ should be regarded as a function from $\C^*$ to $\C$.
-In particular, in this example we will see that there is a new singularity at the origin due to the singularity of $\nu_p$.
-For simplicity, we will restrict to the case $p=1$.
-Then, $I_+(z,1)$ solves
-\begin{equation}\label{eq:I}
-\left[\partial_z^3-\partial_z+\frac{1}{z}\partial_z^2-\frac{1}{9}\frac{\partial_z}{z^2}\right]\varphi=0
-\end{equation}
-or equivalently, $\partial_z\varphi$ solves the modified Bessel equation \eqref{eqn:mod-bessel-AL} with parameter $1/3$.
-Therefore, following the reasoning of Section \ref{big-idea} and the results of Sections \ref{pos-root-AL} and \ref{neg-root-AL}, we get two analytic solutions of \eqref{eq:I}: $\laplace_{\zeta,1}v_{1,1}$ and $\laplace_{\zeta,-1}v_{-1,1}$
-\[ v_{1,1}=-i\sqrt{2}\, (\zeta_1+1)^{-1}\, \zeta_1^{-1/2}\, {}_2F_1\Big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};-\tfrac{1}{2}\zeta_{1}\Big)\]
-\[ v_{-1,1}=-\sqrt{2}\, (1-\zeta_{-1})^{-1}\, \zeta_{-1}^{-1/2}\, {}_2F_1\Big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};\tfrac{1}{2}\zeta_{-1}\Big)\]
-where $\zeta_1=\zeta-1$ and $\zeta_{-1}=\zeta+1$. 
+We will now show, in the case $p = 1$, that equation~\eqref{eqn:I} has a frame of Borel regular solutions---as long as the constant solution $\mathrm{B}_0(z, 1)$ counts as Borel regular.
+For $\mathrm{A}_1(y, p)$ to satisfy the generalized Airy equation, $I_+(z,1)$ must satisfy the equation
+\begin{equation}\label{eqn:I}
+\left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + z^{-1} \left(\tfrac{\partial}{\partial z}\right)^2 - \tfrac{1}{9} z^{-2} \right] \tfrac{\partial}{\partial z} \Phi = 0.
+\end{equation}
+Equivalently, $\tfrac{\partial}{\partial z} I_+(z, 1)$ satisfies the modified Bessel equation \eqref{eqn:reg-mod-bessel-AL} with parameter $1/3$.
+We can now follow the reasoning of Section~\ref{big-idea}, viewing that frequency domain differential equation~\eqref{eqn:I} as the image under $\laplace_{\zeta, \alpha}$ of the position domain integral equation
+\begin{equation}\label{int-eq:position-I}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] (-\zeta)\,v^{(1)} = 0.
+\end{equation}
+In Sections \ref{pos-root-AL} and \ref{neg-root-AL}, we found solutions $v_{\pm 1}$ of the closely related equation~\eqref{int-eq:spatial-mod-bessel-AL}, which we can turn into solutions $v^{(1)}_{\pm 1} = \zeta^{-1} v_{\pm 1}$ of equation~\eqref{int-eq:position-I}.
+
+At the critical values $\zeta = \pm 1$, we can build solutions $v^{(1)}_{\pm 1}$ of this equation from the solutions $v_{\pm 1}$ of equation~\eqref{int-eq:spatial-mod-bessel-AL} that we found in Sections \ref{pos-root-AL} and \ref{neg-root-AL}.
+Explicitly, in terms of the coordinates defined by $\zeta = 1 + \zeta_1$ and $\zeta = -1 + \zeta_{-1}$, these solutions are
+\begin{alignat*}{3}
+v^{(1)}_1 &=\;& -i\sqrt{2}\,(1 + \zeta_1)^{-1} &\,\zeta_1^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};-\tfrac{1}{2}\zeta_{1}\big) \\
+v^{(1)}_{-1} &=\;& \sqrt{2}\,(-1 + \zeta_{-1})^{-1} &\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};\tfrac{1}{2}\zeta_{-1}\big).
+\end{alignat*}
+Their Laplace transforms $V^{(1)}_1 = \laplace_{\zeta, 1} v^{(1)}_1$ and $V^{(1)}_{-1} = \laplace_{\zeta, -1} v^{(1)}_{-1}$ satisfy equation~\eqref{eqn:I}.
 \begin{verify}
-From the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eq:I}.
+From the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eqn:I}.
 Then we argue as follows:
@@
 \end{verify}
-Notice that $v_{1,1}\in\singexpalg{1/2}(\Omega_1)$, it has a simple pole at $\zeta_1=-1$ and it is a log--singularity at $\zeta_1=-2$.
-Similarly, $v_{-1,1}\in\singexpalg{1/2}(\Omega_{-1})$, it has a simple pole at $\zeta_{-1}=1$ and it is a log--singularity at $\zeta_{-1}=2$.
-
-Notice that $\laplace_{\zeta,1}v_{1,1}$ and $\laplace_{\zeta,-1}v_{-1,1}$ are not a frame of solutions; the equation \eqref{eq:I} is of degree three, but it is enough to consider the constant function $1=\laplace_\zeta \delta$ to build a frame of analytic solutions, where $\delta$ is the formal unit (see the definition in Section \ref{convolution}).
-In particular, $1=B_0(z,1)$ and confirms Borel regularity for the constant solution.
+Notice that $v^{(1)}_1$ belongs to $\singexpalg{-1/2}(\Omega_1)$, has a simple pole at $\zeta_1 = -1$, and has a logarithmic singularity at $\zeta_1 = -2$.
+Similarly, $v^{(1)}_{-1}$ belongs to $\singexpalg{1/2}(\Omega_{-1})$, has a simple pole at $\zeta_{-1} = 1$, and has a logarithmic singularity at $\zeta_{-1} = 2$.
+
+With an argument analogous to the one in Section~\ref{bessel-regularity-AL}, one should be able to show that $V^{(1)}_1$ and $V^{(1)}_{-1}$ are Borel regular.
+Since equation~\eqref{eqn:I} is third-order, we need one more Borel regular solution to make a frame.
+We choose the constant solution $1$, which can be seen as the Laplace transform of the formal convolution unit $\delta$ introduced in Section~\ref{convolution}.
+Interestingly, $1$ is actually the generalized Airy function $\mathrm{B}_0(z,1)$.
+\color{black}
 %
@@
 \subsubsection{Thimble projection formula}
-In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
+\textcolor{magenta}{[Are we hoping to fill this in later?
+We can hide it in a to-do comment, if so]} In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
 \color{black}
@@
 Furthermore, we can restrict to monic polynomials by setting $a_3=1$.}, we are going to consider thimble integrals of the form
-
 \[ I_j(z) = \int_{\mathcal{C}_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
-
 where $\mathcal{C}_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.

### 2024-03-28 exp-resurgence.tex
Finish revising definitions of asymptoticity

@@
 
+% hideable to-do notes
+\newif\ifshowtodo
+\showtodotrue
+\ifshowtodo
+\newenvironment{todo}{\color{Coral}}{\color{black}}
+\else
+\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
+\fi
+
 % drafting environments
@@
 \end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em transmonomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
+behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
 Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
@@
 The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-%\textcolor{magenta}{[Do we need to extend these definitions, and the associated theorems, to cover slight series?
-Hopefully it wouldn't be too hard, but it would be a pain.]}
 \begin{defn}
@@
 \color{black}
-\textcolor{orange}{Not all funtions are asymptotic to a power series, thus more generally, we will say a function $F$ is Poincar\'e asymptotic to a trans-monomial $e^{\lambda z}z^\tau\sum_{n=0}^Na_nz^{-n}$ for some positive $\lambda>0$ and $\tau\in(0,1)$ if
-\[\left|F - e^{\lambda z}z^{\tau}\left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\Re(z) \to \infty}\big(e^{\lambda\Re(z)}|z|^{\tau-n}\big).\]}
+This definition generalizes straightforwardly to ``fractionally shifted'' power series and trans-monomials.
+\begin{defn}
+On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a fractionally shifted trans-monomial
+\begin{equation}\label{trans-monom:asymp-defn}
+e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots\right)
+\end{equation}
+if, along each ray toward $\infty$,
+\[ \left|F - e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(e^{-\alpha|z|}\,z^{-\sigma-n}\big) \]
+over all orders $n$. We will again use $\sim$ to denote this relationship.
+\end{defn}
+
 If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
-The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: it is the function's {\em asymptotic expansion} on that sector.
+The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
-Since asymptotic expansions on overlapping sectors must agree, we can meaningfully take a function's asymptotic expansion along a ray:\textcolor{RoyalBlue}{We will denote such map with the symbol $\aexp$.
-More generally, when the asymptotic expansion is taken in the direction $\theta$ at infinity, i.e.
-as $z\to e^{i\theta}\infty$, we will write $\aexp^\theta$.}
-
+Since asymptotic expansions on overlapping sectors must agree, we can think of this homomorphism as being determined by a ray.
 \begin{defn}
-\textcolor{orange}{[Define $\aexp^\theta$ homomorphism that sends a function with an asymptotic expansion on a sector that contains the $\theta$-ray to its asymptotic expansion on that sector.\ldots]}
+For any direction $\theta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
+\[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
+is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta} (0, \infty)$.
+To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
 \end{defn}
-\textcolor{RoyalBlue}{The {\em asymptotic expansion} map $\aexp^\theta$ sends a holomorphic function that vanishes at $\infty$ to the unique power series of the form \eqref{series:asymp-defn} which is asymptotic to it on the half-plane $\Re e^{i\theta}z > 0$ (see \cite[Theorem~C.11]{nikolaev2023existence}).}
-
-\textcolor{orange}{[State theorem: differentiation commutes with $\aexp^\theta$ under certain circumstances.
+\begin{todo}[Mention Nevanlinna's theorem, re-stated as \cite[Theorem~C.11]{nikolaev2023existence}, somewhere later.]\end{todo}
+\begin{todo}[State the theorem that differentiation and integration commute with $\aexp^\theta$ under certain circumstances.
 See Erdelyi's {\em Asymptotic Expansions}, \S 1.6.
 For basic facts about uniform asymptoticity, see \S 5.7.2 of Mitschi and Sauzin.
-Theorem~5.20 and its rephrasing say that the Laplace transform of a function is uniformly asymptotic to the formal Laplace transform of the function's Taylor series.]}
+Theorem~5.20 and its rephrasing say that the Laplace transform of a function is uniformly asymptotic to the formal Laplace transform of the function's Taylor series.]\end{todo}
 
@@
 For regular enough functions, the Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain.
-\textcolor{orange}{[Compare with Sokal's version of the Watson--Nevanlinna theorem?]}
+\begin{todo}[Compare with Sokal's version of the Watson--Nevanlinna theorem?]\end{todo}
 \begin{lemma}\label{lem:laplace-bridge}
@@
 \end{lemma}
+\begin{remark}
+This result is similar to Theorem~5.20 of \cite{diverg-resurg-i}.
+It is weaker in that it does not establish Gevrey asymptoticity, but stronger in that it can be applied to functions with fractionally shifted Taylor expansions.
+\end{remark}
 \begin{proof}
@@
 \subsection{Modified Bessel}\label{sec:mod-bessel-lift}
-
-The modified Bessel equation is a generalization of equation~\eqref{eqn:mod-bessel-AL} where $\frac{m}{n}$ is replaced by a complex parameter $\mu$
+Our analysis of the Airy-Lucas functions boiled down to an analysis of equation~\eqref{eqn:mod-bessel-AL}: the modified Bessel equation with a rational parameter $\mu = \tfrac{m}{n}$.
+We now do a general analysis of the modified Bessel equation, allowing the parameter $\mu$ to be any complex number.
 \begin{equation}\label{eqn:mod-bessel}
@@
 \end{equation}
-On the one hand, this new condition does not really affect the argument we present in Section~\ref{bessel-regularity-AL}, so we briefly state the main results: 
+
+This generalization does not really affect the argument from Section~\ref{bessel-regularity-AL}, so we will only briefly state the analogous results:
 \begin{itemize}

### 2024-03-28 exp-resurgence.tex
Work out the contour confusion for modified Bessel

@@
 
-\textcolor{RoyalBlue}{
-Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
+% \textcolor{RoyalBlue}{
+% Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
 \textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
@@
 Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in\textcolor{red}{\mathcal{J}_\alpha^\theta:=} \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $b$.
 \end{enumerate}
+\textcolor{red}{[add figure]}
+
 The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
@@
 \[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
-is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta} (0, \infty)$.
+is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in \mathcal{J}_0^\infty$.
 To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
@@
 Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\textcolor{magenta}{\mathcal{C}}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
-Parameterize $\textcolor{magenta}{\mathcal{C}}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\textcolor{magenta}{\mathcal{C}}$.
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
 Along $\mathcal{C}$, we have
@@
 \subsubsection{Change of translation chart}\label{transl-borel}
-\textcolor{red}{[change $b$ with $\alpha$]}
 We will show that the Borel transform is compatible with the change of translation chart for the Laplace transform in Section~\ref{sec:change-translation}.
@@
 \begin{tikzcd}
-e^{-zb}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}  \arrow[r,"e^{zb}"]  & \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}\arrow[d, "\borel_{\zeta_b}"] \\
-\{1, \zeta, \zeta^2, \zeta^3, \ldots\}\arrow[u,"\laplace_{\zeta,b}"]\arrow[r,"\text{change chart}"'] &  \{1, \zeta_b, \zeta_b^2, \zeta_b^3, \ldots\}  
+e^{-z\alpha}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}  \arrow[r,"e^{z\alpha}"]  & \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \}\arrow[d, "\borel_{\zeta_\alpha}"] \\
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\}\arrow[u,"\laplace_{\zeta,\alpha}"]\arrow[r,"\text{change chart}"'] &  \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}  
 \end{tikzcd}
 \end{center}
-commutes, where the functions of $z$ are functions on the fiber $T^*_{\zeta=b}B$. 
+commutes, where the functions of $z$ are functions on the fiber $T^*_{\zeta=\alpha}B$. 
 \begin{proof}
 We want to show that 
-\[\borel_{\zeta_b}\left[e^{zb} \laplace_{\zeta,b}\big[\zeta^n\big]\right]=\zeta^n.\]
-Recall that $\borel_{\zeta_b}$
-is the formal inverse of $\laplace_{\zeta_b,0}$ on the cotangent fibre over $b$. Thus, taking the Borel transform on both side of the identity~\eqref{change-chart} we find
-  \begin{align*}
-      \borel_{\zeta_b}\left[e^{zb} \laplace_{\zeta,b}\big[\zeta^n\big]\right]&=\borel_{\zeta_b}\laplace_{\zeta_b,0}\big[\zeta^n\big]\\
-      &=\borel_{\zeta_b}\laplace_{\zeta_b,0}\left[\sum_{k=0}^n{n\choose k}\zeta_b^k b^{n-k}\right]\\
-      &=\sum_{k=0}^n{n\choose k} b^{n-k}\borel_{\zeta_b}\laplace_{\zeta_b,0}\big[\zeta_b^k \big]\\
-      &=\sum_{k=0}^n{n\choose k} b^{n-k}\zeta_b^k\\
+\[\borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\right]=\zeta^n.\]
+Recall that $\borel_{\zeta_\alpha}$
+is the formal inverse of $\laplace_{\zeta_\alpha,0}$ on the cotangent fibre over $\alpha$. Thus, taking the Borel transform on both side of the identity~\eqref{change-chart} we find
+  \begin{align*}
+      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\big[\zeta^n\big]\\
+      &=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\left[\sum_{k=0}^n{n\choose k}\zeta_\alpha^k \alpha^{n-k}\right]\\
+      &=\sum_{k=0}^n{n\choose k} \alpha^{n-k}\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\big[\zeta_\alpha^k \big]\\
+      &=\sum_{k=0}^n{n\choose k} \alpha^{n-k}\zeta_\alpha^k\\
       &=\zeta^n.
@@
 \begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] F = 0.
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
 \end{equation}
@@
 \begin{equation}\label{eqn:airy-lucas}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] F = 0
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - (m-1) y^{-1} \tfrac{\partial}{\partial y} - y^{n-2}\right] \Phi = 0
 \end{equation}
@@
 \[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
-and for even $j$, we have \textcolor{magenta}{[check]}
+and for even $j$, we have \begin{todo}{[check sign]}\end{todo}
 \[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
@@
 
-Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root}--\ref{neg-root}, we notice that
+Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root-AL}\;--\;\ref{neg-root-AL}, we notice that
 \[ K^{(j)}_{m/n}(z) = \begin{cases}
 \frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
-\frac{i}{2}\laplace_{\zeta, -1} v_{-1} \;\textcolor{magenta}{\text{(?)}} & j \text{ even}.
+\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
 \end{cases} \]
+\begin{verify}
+\begin{align*}
+\zeta & = 1 + \zeta_1 & -\zeta_1 & = 1 - \zeta \\
+\zeta & = -1 + \zeta_{-1} & \zeta_{-1} & = 1 + \zeta
+\end{align*}
+\begin{align*}
+\left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,\zeta_1^{-1/2} \\
+\left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,(-\zeta_{-1})^{-1/2} \\
+& = i\sqrt{2}\,\zeta_{-1}^{-1/2}
+\end{align*}
+\end{verify}
 \color{black}
@@
 \begin{equation}\label{eqn:mod-bessel}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \varphi = 0
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\mu^2 + z^2\big]\right] \Phi = 0
 \end{equation}
@@
 % \notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-%\notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\mathcal{C}'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
+% \notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\mathcal{C}'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
 % \end{align*}
@@
 \begin{align*}
-        2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)} da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b} db\\
-        &=-\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)} da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b) db\\
-        &=-\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)} da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)} da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b) db
+2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
+& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
+& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db
 \end{align*}
@@
 \begin{align*}
-   4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big]\\
-     &= \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right] da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right] da \\
-        &=2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh(a+i\pi) da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(i\pi+a) da\\
-        &=2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh(a-i\pi) da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(i\pi+a) da
-    \end{align*}
+4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
+& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
+& \textcolor{OrangeRed}{= 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da} \\
+& = 2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh\big(\mu(a-i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh\big(\mu(i\pi+a)\big)\,da
+\end{align*}
+\color{OrangeRed}
+Stop at the highlighted line! This simplifies to the integral
+\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
+along the contour $\gamma$ that runs rightward along $i\pi + \R$.
+
+\textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
+\par
 \end{verify}

### 2024-03-28 exp-resurgence.tex
Redo modified Bessel thimble projection with correct contour

@@
 \end{align*}
-we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as \textcolor{magenta}{[switching to the conventional sign for the projection map, so $\mathcal{C}^{(3)}$ now comes from $\infty$ at $-60^\circ$ and goes to $\infty$ at $60^\circ$]}
+we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as
 \begin{align}
-\notag K_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{z^{-\textcolor{DarkCyan}{1/n}}\mathcal{C}^{(k)}} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\textcolor{magenta}{\mathcal{C}_j}} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt.
+\notag K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_\gamma \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+\notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt,
 \end{align}
-where $\mathcal{C}_j$ is the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, as represented in Figure \ref{fig:bessel_unrolled}.
-Because $\cosh(t)$ is periodic, the integral has the same value for every choice of $\mathcal{C}_j$ with $j\in\Z$.
+using the path $\mathcal{C}^\theta_j$ described below.
+\begin{center}
+\begin{tabular}{l|l|l}
+When $j$ is\ldots & $\mathcal{C}^\theta_j$ comes from $-\infty$ along\ldots & and goes to $+\infty$ along\ldots \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} Odd & $(-\infty,0) + (j\pi-\theta)i$ & $(0, \infty) + (j\pi-\theta)i$ \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} Even & $(-\infty,0) + \big((j+1)\pi-\theta\big)i$ & $(0, \infty) + \big((j-1)\pi-\theta\big)i$ \\[1mm]
+\end{tabular}
+\end{center}
+Because $\cosh(t)$ is periodic, $j$ only affects the integral through its parity.
 \begin{figure}[ht]
     \centering
-    \includegraphics[scale=0.3]{figures/Bessel0_unrolled_lightblue.png}
+    \includegraphics[width=14cm]{figures/bessel-unrolled.png}
     \caption{The paths $\mathcal{C}_j$.}
@@
 
-For any $\mu \in \C \smallsetminus \Z$, we have a thimble integral representation of $K_{\mu}$ given by formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\textcolor{DarkCyan}{[Cite Watson too?]}
+For any $\mu \in \C \smallsetminus \Z$, the classical modified Bessel function $K_\mu(z)$ can be expressed as the thimble integral
 \begin{equation}\label{int:mod-bessel-gen}
- K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}_0} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt,
-\end{equation}
+ K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
+\end{equation}
+for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}{[Cite Watson too?]}\end{todo}.
 \begin{verify}
-% \begin{align*}
-% \notag K_\mu(z) & = \frac{\pi}{\sin(\mu \pi)} \cdot \frac{1}{2}\big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-% \notag & = \frac{1}{2i \sin(\mu \pi)} \int_{\mathcal{C}'} \exp\left[z \cosh(t)\right]\,\frac{1}{2}\left[e^{\mu t} - e^{-\mu t}\right]\,dt 
-% \end{align*}
-% where $\mathcal{C}'$ is a path that comes from $\infty$ along $-i \pi + (0, \infty)$ and goes to $\infty$ along $i \pi + (0, \infty)$ 
-Following Watson \textit{A treatment of Bessel function}, 1944, pp. 181 (it is the reference in \cite{dlmf})
+\par
+From equation~6.22(3) of Watson's \textit{A treatise on the theory of Bessel functions} (1944), p. 181 (the reference in \cite{dlmf}):
 \begin{align*}
@@
 & = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
-& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db
-\end{align*}
-hence 
+& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db.
+\end{align*}
+Hence,
 \begin{align*}
@@
 along the contour $\gamma$ that runs rightward along $i\pi + \R$.
-
 \textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
@@
 \end{verify}
-\textcolor{orange}{The integral converges when $z$ is in the right half-plane.} We get formula~\eqref{integral:mod-bessel-lifted} when we choose a rational parameter $\mu = m/n$.
-%
-%\begin{center}
-%    \begin{tikzpicture}
-%        \draw[->] (6,2)--(10,2);
-%        \draw[->] (8,0)--(8,4);
-%        \draw[red,thick,->] (10,1.8) .. controls (8,2) .. (10,2.2);
-%        %\draw[red,thick,->] (10,2)--(9,2);
-%        %\draw[red,thick] (9,2)--(8.5,2);
-%        %\draw[red,thick] (10,2)--(9.3,2);
-%        %\draw[red,thick,->] (8.5,2)--(9.3,2);
-%        \node[red,below, font=\tiny] at (10,1.8) {$\gamma_z$};
-%        \node[font=\tiny,below] at (8.5,2) {$1$};
-%    \end{tikzpicture}
-%\end{center}
-
+The integral converges when $z$ is in the right half-plane.
+Choosing a rational parameter $\mu = \tfrac{m}{n}$ gives formula~\eqref{integral:mod-bessel-lifted}, showing that $K^{(j)}_{m/n}(z)$ is the classical modified Bessel function $K_{m/n}(z)$ when $j$ is odd.
+
+\color{RoyalBlue}
 We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of the asymptotic of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
+\color{black}
+\textcolor{orange}{[\ldots]} We first recast the integral into the $\zeta$ plane by setting $-\zeta = \cosh(t)$
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta, \]
+where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. \textcolor{orange}{[\ldots]}
+\color{RoyalBlue}
 \begin{align*}
@@
 with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
-
+\color{black}
 \begin{equation}\label{eqn:borel_bessel0}

### 2024-03-28 exp-resurgence.tex
updates

@@
 \item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in\textcolor{red}{\mathcal{J}_\alpha^\theta:=} \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $b$.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$.
 \end{enumerate}
-\textcolor{red}{[add figure]}
+%
+%
+\begin{figure}[ht]
+\centering
+\basicLaplace
+\caption{\small{On the right, the ray $\mathcal{J}_\alpha^\theta$ in the position domain.
+On the left, the half plane in the frequency domain, where the Laplace transform $\laplace_{\zeta,0}^\theta \hat{\phi}$ is holomorphic.}}
+\end{figure}
 
@@
 \begin{defn}
-On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a power series
+On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a power series
 \begin{equation}\label{series:asymp-defn}
@@
 if, along each ray toward $\infty$,
-\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
+\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
 over all orders $n$. We will write
-\[ F \sim \sum_{n \geq 0} a_n z^{-n} \]
+\[ \Phi \sim \sum_{n \geq 0} a_n z^{-n} \]
 to denote this relationship.
@@
 \end{equation}
-is {\em asymptotic} to a holomorphic function $F$ if
-\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]}
+is {\em asymptotic} to a holomorphic function $\Phi$ if
+\[ \left|\Phi - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
+over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $\Phi$, namely we will write \[\Phi\sim \sum_{n\geq 1} a_n z^{-n}.\]}
 \end{defn}
@@
 \begin{defn}
-On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a fractionally shifted trans-monomial
+On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a fractionally shifted trans-monomial
 \begin{equation}\label{trans-monom:asymp-defn}
@@
 if, along each ray toward $\infty$,
-\[ \left|F - e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(e^{-\alpha|z|}\,z^{-\sigma-n}\big) \]
+\[ \left|\Phi - e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(e^{-\alpha|z|}\,z^{-\sigma-n}\big) \]
 over all orders $n$. We will again use $\sim$ to denote this relationship.
@@
 \begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
-\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
+On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
+\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
 over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
@@
 
-You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
+You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
 After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
@@
 We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
-However, this only works when there's a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
+However, this only works when there is a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
 Why?
@@
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
-\color{DarkBlue}
+%
 \begin{theorem}\label{thm:exist_uniq_ODE}
@@
 \end{theorem}
-With a little more work, encapsulated in Lemma~\textcolor{orange}{?} from Section~\textcolor{orange}{?}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
+With a little more work, encapsulated in Lemma~\ref{lem:shifted_holo_closed} from Section~\ref{sec:bridging}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
 \begin{theorem}\label{thm:soln_is_asymptotic}
@@
 \end{corollary}
+\begin{remark}
+Notice that the result of Theorem~\ref{thm:soln_is_asymptotic} is not a consequence of the general result that the Borel--Laplace sum of 1-Gevrey series $\series{\Phi}$ is uniform Gevrey asymptotic to $\series{\Phi}$ itself (see Theorem~5.20 in~\cite{diverg-resurg-i}).
+\end{remark}
 From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
@@
 \centering
-\basicLaplace
-\vspace{1cm}
-
 \phaseSpaceLaplace
@@
 \end{figure}
-
-We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
@@
 Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials.
-Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $F$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).
+Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).
 
@@
 \end{center}
-\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
 In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
@@
 At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
-To make this more concrete, note that around any point $b \in B$, there's a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there's a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
+To make this more concrete, note that around any point $b \in B$, there is a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
+\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there is a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
 In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
@@
 In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
-Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $F$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|F| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-The norm $\|F\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |F|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
+Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
 \textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.}
@@
 The inverse Laplace transform is given by the formula
-\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\mathcal{C}}} e^{z\zeta_\alpha} F\,dz. \]
-When $F$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
-\begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\mathcal{C}}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|F\|_{\sigma, \Lambda}\,dz \\
-& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
+\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\mathcal{C}}} e^{z\zeta_\alpha} \Phi\,dz. \]
+When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
+\begin{align*}
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\mathcal{C}}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
+& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
 \end{align*}
@@
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
-& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
-& \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
+& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
+& \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
 \end{align*}
 using the new parameter $s = \sin(\varepsilon/2)\,t$. Recognizing the integral in the last line as itself a Laplace transform, we have
-\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| \le e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
+\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
 which is what we wanted to show.
@@
 
-\subsection{Bridging the gap between analytic and formal objects}
+\subsection{Bridging the gap between analytic and formal objects}\label{sec:bridging}
 The spaces $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
@@
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
-We'll do this by showing that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+We will do this by showing that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
 
@@
     \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there is one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
-The proof follows the same argument we chose for $I_\alpha$, but there's one subtulty to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
+The proof follows the same argument we chose for $I_\alpha$, but there is one subtulty to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
 Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota_\alpha \]
@@
 \end{align}
+\color{black}
 \subsubsection{The case $\mu=0$}
@@
 with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
-\color{black}
 \begin{equation}\label{eqn:borel_bessel0}

### 2024-03-28 to-do.tex
Sync before working on proof of main results

@@
 \documentclass{article}
-
+\usepackage{xcolor}
+\newcommand{\singexp}[2]{\mathcal{H}L^\infty_{#1, #2}}
+\newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
+\newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
+\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
 \title{To-do}
@@
 \end{itemize}
+\color{gray}
 \subsection{Laplace and Borel transforms}
@@
 \end{itemize}
+\color{black}
 \item \textbf{(Aaron)} Understand why \texttt{lem:frac-deriv-Borel} works without boundary terms, and explain this in text.
@@
 \end{itemize}
+
+\section{brainstorm}
+\begin{itemize}
+    \item Section~\ref{borel_reg-ODE} and maybe other subsections--revise the proof of the main result for ODE taking into account the results in our paper
+    \item Do flagged revisions in Section~\ref{borel-reg-thimble}
+    \item Section~\ref{contour-argument-AL}---revise the general contour argument
+    \item Revise Section 2, using the formalism of $\singexp{\sigma}{\Lambda}(\Omega)$
+    \begin{itemize}
+    \item Replace formalism in Section~\ref{sec:reg-decay}
+    \end{itemize}
+    \item Check which examples are still in the framework of our theorem
+    \begin{itemize}
+    \item Start a storage document for shelved examples
+    \end{itemize}
+    \item Section~\ref{resurgence-AL}---Draw intersection points figure
+    \item Section~\ref{sec:mod-bessel-lift}---pin down contour
+    \item Explain contour figure in Airy example (explain what the regions indicate and what the color)
+    \begin{itemize}
+    \item Figure out how to release source code. How much do we need to clean it up? Is it okay that it relies on Shadertoy?
+    \end{itemize}
+    \item Look at ``Plan of the paper'' appendix and confirm that we've included everything we want
+    \begin{itemize}
+    \item Put future goals in storage document
+    \end{itemize}
+    \item Veronica doesn't like $\gamma_z$ as notation for Hankel contour. I'll suggest $\mathcal{H}_{1,z}$ where $1$ is the point where the path is centered. 
+\end{itemize}
 \end{document}

### 2024-03-28 exp-resurgence.tex
Updates from Overleaf
Manually resolve merge conflict
Correct some minor typos in the process.

@@
 \subsection{Goals and Results}
-
+%
 First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
@@
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
-%
 \begin{theorem}\label{thm:exist_uniq_ODE}
@@
 \begin{remark}
-Notice that the result of Theorem~\ref{thm:soln_is_asymptotic} is not a consequence of the general result that the Borel--Laplace sum of 1-Gevrey series $\series{\Phi}$ is uniform Gevrey asymptotic to $\series{\Phi}$ itself (see Theorem~5.20 in~\cite{diverg-resurg-i}).
+\textcolor{Maroon}{Notice that the result of Theorem~\ref{thm:soln_is_asymptotic} is not a consequence of the general result that the Borel--Laplace sum of 1-Gevrey series $\series{\Phi}$ is uniform Gevrey asymptotic to $\series{\Phi}$ itself (see Theorem~5.20 in~\cite{diverg-resurg-i}).}
 \end{remark}
@@
 If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example (see Figure \ref{fig:different_fibres}).
+
 \begin{figure}[ht]
@@
 \end{figure}
+
 We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
@@
 \end{center}
-\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
+\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum \textcolor{magenta}{$\hat{f}$} of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+In fact, we have $|\textcolor{magenta}{\hat{f}}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
 \begin{center}
@@
 In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
-%
-
-Near each branch point $b$, let's fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
+
+\textcolor{magenta}{[par break wanted?]} Near each branch point $b$, let us fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
 This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
@@
 \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there is one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
-The proof follows the same argument we chose for $I_\alpha$, but there is one subtulty to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
+The proof follows the same argument we chose for $I_\alpha$, but there is one subtlety to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
 Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota_\alpha \]

### 2024-03-29 exp-resurgence.tex
Better adapt basic Laplace transform picture to intro

@@
 \usepackage{fancyhdr}
+\usepackage[font=small, margin=1cm]{caption}
 \usepackage{enumitem}
@@
 Ask more about this.]}
-\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in\textcolor{red}{\mathcal{J}_\alpha^\theta:=} \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item If $\hat{\phi}$ also grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$.
 \end{enumerate}
-%
-%
-\begin{figure}[ht]
-\centering
+\begin{center}
 \basicLaplace
-\caption{\small{On the right, the ray $\mathcal{J}_\alpha^\theta$ in the position domain.
-On the left, the half plane in the frequency domain, where the Laplace transform $\laplace_{\zeta,0}^\theta \hat{\phi}$ is holomorphic.}}
-\end{figure}
+\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
+\end{center}
 
@@
 \subsubsection{Introducing Borel regularity}
-We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re e^{i\theta}z > 0$, we get a formal power series $\series{\Phi}$.
+We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$.
 
@@
 \Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel"] \\
+\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
 & & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
+\hat{\phi} \arrow[uu, mapsto, "\laplace_{\zeta, 0}^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
 \end{tikzcd}
@@
 We will therefore call this process {\em Borel regularization}.
-Explicitly, Borel regularization works in four steps.
+Explicitly, Borel regularization works in four steps:
 \begin{enumerate}
 \item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
-\item Take the Borel transform $\series{\phi} = \borel \series{\Phi}$.
+\item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
 \item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.%\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
@@
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we are allowed to take the Laplace transform at another point $b \in B$.
-This would be natural in our study of ODEs and thimble integrals.}
+This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$.
+The choice of base point will play an important role in our study of ODEs and thimble integrals.}
 \end{enumerate}
@@
 \end{theorem}
-With a little more work, encapsulated in Lemma~\ref{lem:shifted_holo_closed} from Section~\ref{sec:bridging}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
+We can use this result to show that $\Psi_\alpha$ is Borel regular.
+Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:shifted_holo_closed} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
+\color{RoyalBlue}
 \begin{theorem}\label{thm:soln_is_asymptotic}
@@
 \end{theorem}
+\color{black}
 \begin{corollary}\label{cor:soln_borel-reg}
-The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
+This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
 \end{corollary}
-\begin{remark}
-\textcolor{Maroon}{Notice that the result of Theorem~\ref{thm:soln_is_asymptotic} is not a consequence of the general result that the Borel--Laplace sum of 1-Gevrey series $\series{\Phi}$ is uniform Gevrey asymptotic to $\series{\Phi}$ itself (see Theorem~5.20 in~\cite{diverg-resurg-i}).}
-\end{remark}
+In many cases, by choosing from among the solutions $\Psi_\alpha$, we can build a frame of Borel-regular solutions of the equation $\mathcal{P}\Phi = 0$.
+
 From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
@@
 We do this in Section~\ref{sec:new-summability-proof}.
-
-In addition, as a consequence of Corollary~\ref{cor:soln_borel-reg} we deduce that the set of solutions $\Psi_\alpha$ for $-\alpha$ root of $P$, gives a frame of Borel regular solutions of equation $\mathcal{P}\Phi=0$.
-
-\textcolor{magenta}{[Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.]}
-
-\textcolor{orange}{[Prove existence of a frame of Borel regular solutions?]}
-\color{black}
 \subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thimble}
@@
 However, this only seems to be possible when $X$ is 1-dimensional.}
-\begin{figure}[h]
-    \centering
+\begin{center}
 \includegraphics[width=6.5cm]{figures/rays.png}
@@
 \includegraphics[width=6.5cm]{figures/thimbles-n5.png}
-    \caption{The rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}
-    \label{fig:thimble_vs_rays}
-\end{figure}
+\captionof{figure}{The rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}\label{fig:thimble_vs_rays}
+\end{center}
 Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:
@@
 %
-As part of the treatment, we have made use of some new perspectives on the Laplace transform (see Section~\ref{sec:Laplace-Borel-general}).
-Indeed, the Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the position domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-In particular, working with integral equations in the spatial domain will be our main strategy to prove Borel regularity for ODEs, building on our previous result \cite[Theorem 4]{reg-sing-volterra}.
-
-Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_{\zeta,b}^\theta$ is $T^*_{\zeta=b} B$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example (see Figure \ref{fig:different_fibres}).
-
-\begin{figure}[ht]
-\centering
+In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.
+
+Laplace transform methods for solving ODEs on the frequency domain traditionally relate them to ODEs on the position domain.
+We find, however, that it is easier and more natural to relate ODEs on the frequency domain to integral equations on the position domain.
+In particular, the good behavior of integral equations and their solutions is central to our proof that certain ODEs have Borel regular solutions.
+
+In Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
+Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent fiber $T^*_{\zeta = 0} B$.
+At a conical singularity of $B$, which cannot lie in the domain of a translation chart, the frequency domain has a more interesting shape, illustrated in Figure \ref{fig:different_fibres}.
+\begin{center}
 \phaseSpaceLaplace
-\caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
+\captionof{figure}{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
 However, the fiber over a singular point of $B$ has an interesting structure.
-Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
-    \label{fig:different_fibres}
-\end{figure}
-
-We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}\label{fig:different_fibres}
+\end{center}
+
+We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
@@
 Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
+These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $\Lambda$.
 \begin{center}
 \begin{tikzpicture}
-\renewcommand{\rfiber}{3}
-\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\setfiberscale{2.5}
 \renewcommand{\phase}{35}
@@
 \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
-\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$c$};
+\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
 \end{fiber}
 \end{tikzpicture}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\dis}{1.2}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
-  \begin{scope}[violet]
-    \draw (0, 0) -- (-\ang:\outsize);
-    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
-    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
-    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north west] at (-\size, \size) {$z$};
-\end{tikzpicture}
 \end{center}
-\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum \textcolor{magenta}{$\hat{f}$} of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\textcolor{magenta}{\hat{f}}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$.
+When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
+In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighborhood of the ray $\zeta \in e^{i\theta}[0, \infty)$.
 \begin{center}
 \begin{tikzpicture}
-\renewcommand{\rfiber}{3}
+\setfiberscale{2.5}
 \pgfmathsetmacro{\rshade}{1.5*\rfiber}
 \renewcommand{\phase}{35}
-\newcommand{\radius}{1}
+\newcommand{\radius}{0.85}
 \begin{fiber}
@@
 \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
 \end{fiber}
-\end{tikzpicture}
-\begin{tikzpicture}
-\newcommand{\size}{3}
-\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
-\newcommand{\ang}{35}
-\newcommand{\radius}{1}
-\begin{scope}
-  \clip (-\size, -\size) rectangle (\size, \size);
-  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
-  \begin{scope}[violet]
-    \draw (0, 0) -- (\ang:\outsize);
-    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
-    %%\begin{scope}[rotate=\ang]
-    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
-    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
-    %%\end{scope}
-    %%\fill (mark) circle (0.05);
-  \end{scope}
-\end{scope}
-%%\begin{scope}[violet]
-%%  \draw (0, 0) -- (center);
-%%  \fill (center) circle (0.05);
-%%\end{scope}
-\draw[->] (-\size, 0) -- (\size, 0);
-\draw[->] (0, -\size) -- (0, \size);
-\node[anchor=north west] at (-\size, \size) {$\zeta$};
 \end{tikzpicture}
@@
 Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^*B$.
-%
-\subsubsection{Translation surfaces, briefly}
+\par \textcolor{magenta}{Combine ``briefly,'' ``direction,'' and ``frequency'' into all one sub-sub-section}
+%
+\subsubsection{Background on translation surfaces}
+%
+\paragraph{Translation surfaces, briefly}
 %
@@
 The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-We will require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}(see Figure~\ref{fig:translation_surface}).
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{}
-    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
-    \label{fig:translation_surface}
-\end{figure}
-%
-\subsubsection{Direction}\label{transl:dir}
+\textcolor{magenta}{We will require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
+This kind of translation surface has a ``cylindrical end'' at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}(see Figure~\ref{fig:translation_surface}).}
+%%\begin{figure}[ht]
+%%    \centering
+%%    %\includegraphics{}
+%%    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
+%%    \label{fig:translation_surface}
+%%\end{figure}
+%
+\paragraph{Direction}\label{transl:dir}
 %
@@
 %
-\subsubsection{Frequency}\label{transl-freq}
+\paragraph{Frequency}\label{transl-freq}
 %
@@
 \end{center}
-commute.
+commute. Here, $\blankbox^n$ represents the $n$th power map.
 % \subsubsection{Boundary}
@@
 \textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
+\textcolor{magenta}{[Priority: update to $\zeta = \alpha$]} When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
 \begin{equation}\label{laplace:int}
@@
     \centering
-    \includegraphics[width=14cm]{figures/bessel-unrolled.png}
+    \includegraphics[width=10cm]{figures/bessel-unrolled.png}
     \caption{The paths $\mathcal{C}_j$.}

### 2024-03-29 exp-resurgence.tex
Revise Laplace transform section

@@
 This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$.
-The choice of base point will play an important role in our study of ODEs and thimble integrals.}
+The choice of starting point will play an important role in our study of ODEs and thimble integrals.}
 \end{enumerate}
@@
 Roughly speaking, the Laplace transform lifts holomorphic functions on $B$ to holomorphic functions on $T^*B$.
-\par \textcolor{magenta}{Combine ``briefly,'' ``direction,'' and ``frequency'' into all one sub-sub-section}
-%
-\subsubsection{Background on translation surfaces}
-%
-\paragraph{Translation surfaces, briefly}
+%
+\subsubsection{Background on translation surfaces}\label{sec:transl}
+%
+\paragraph{A brief definition}
 %
 A translation surface is a Riemann surface $B$ carrying a holomorphic $1$-form $\lambda$~\cite{zorich2006flat}.
-A translation chart is a local coordinate $\zeta$ with $d\zeta = \lambda$.
+A {\em translation chart} is a local coordinate $\zeta$ with $d\zeta = \lambda$.
 The standard metric on $\C$ pulls back along translation charts to a flat metric on $B$, with a conical singularity of angle $2\pi n$ wherever $\lambda$ has a zero of order $n-1 > 0$.
-\textcolor{magenta}{We will require $B$ to be finite-type and $\lambda$ to have a pole at each puncture.
-This kind of translation surface has a ``cylindrical end'' at each puncture where $\lambda$ has order $-1$, and a ``$|2n|$-planar end'' at each puncture where $\lambda$ has order $n-1 < -1$~\cite[Section 2.5]{gupta2013meromorphic} \textcolor{orange}{(or cite Aaron's article, which will hopefully present the same background in the translation surface context)}(see Figure~\ref{fig:translation_surface}).}
-%%\begin{figure}[ht]
-%%    \centering
-%%    %\includegraphics{}
-%%    \caption{On the left an example of translation surface with ``cylindrical end''. On the right, an example of translation surface with  ``$|2n|$-planar end''. }
-%%    \label{fig:translation_surface}
-%%\end{figure}
-%
-\paragraph{Direction}\label{transl:dir}
+
+We will call the zeros of $\lambda$ {\em branch points}.
+To explore the region around a branch point, it can be helpful to use a {\em translation parameter}: a function $\zeta$ which has $d\zeta = \lambda$, but is not necessarily a local coordinate.
+
+In all of our examples, $B$ will be a finite-type Riemann surface, and $\lambda$ will have a pole at each puncture.
+This level of generality allows for plenty of interesting behavior without letting $B$ get too messy.
+Sections~2.4\;--\;2.5 of \cite{gupta2013meromorphic} give a sense of what $B$ can look like near a pole of $\lambda$.
+%
+\paragraph{A sense of direction}
 %
 The translation structure gives $B$ a notion of direction as well as distance.
-Away from the zeros of $\lambda$, which we will call {\em branch points}, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
+Away from the branch points, we can talk about moving upward, rightward, or at any angle, just as we would on $\C$.
 At a branch point of cone angle $2\pi n$, we can also talk about moving upward, rightward, or at any angle in $\R/2\pi\Z$, but here there are $n$ directions that fit each description.
-To make this more concrete, note that around any point $b \in B$, there is a unique holomorphic function $\zeta_b$ that vanishes at $b$ and has $d\zeta_b = \lambda$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] there is a unique translation parameter $\zeta_b$ that vanishes at $b$.} This function is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering when $b$ is a branch point of cone angle $2\pi n$.
+To make this more concrete, note that around any point $b \in B$, there is a unique translation parameter $\zeta_b$ that vanishes at $b$.
+This parameter is a translation chart when $b$ is an ordinary point, and an $n$-fold branched covering of $\C$ when $b$ is a branch point of cone angle $2\pi n$.
 In either case, $\zeta_b \in e^{i\theta} [0, \infty)$ is a ray or a set of rays leaving $b$ at angle $\theta \in \R/2\pi\Z$.
 
-\textcolor{magenta}{[par break wanted?]} Near each branch point $b$, let us fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
+Near each branch point $b$, fix a coordinate $\omega_b$ with $\zeta_b = \tfrac{1}{n} \omega_b^n$, where $2\pi n$ is the cone angle at $b$.
 This lets us label each direction at $b$ with an ``extended angle'' in $\R/2\pi n\Z$.
@@
 %
-\paragraph{Frequency}\label{transl-freq}
-%
-The translation structure also gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$ \textcolor{orange}{[make it clear that $z$ is an almost-global chart on $T^*B$---for example, writing $z\colon T^*B\to\C^2$]}.
+\paragraph{The frequency coordinate}\label{transl-freq}
+%
+Over the complement $B'$ of the branch points, the translation structure gives us a holomorphic map $z \maps T^*B' \to \C$.
+This map is an isomorphism on every fiber, trivializing $T^*B$ almost globally.
+Over a branch point $b$ of cone angle $2\pi n$, we get an analogous isomorphism $z \maps T^*_bB^{\otimes n} \to \C$.
+In both cases, we will call $z$ the {\em frequency coordinate} of $B$.
+\par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
+
 At an ordinary point, we can define $z$ simply as the map
@@
 \end{align*}
-To get a definition that generalizes to branch points, though, it is worth taking a fancier point of view.
+To generalize $z$ to branch points, though, we need a more sophisticated definition.
 Recall that $T^*_bB = \van_b / \van_b^2$, where $\van_b$ is the ideal of holomorphic functions that vanish at $b$.
 Observing that $(f + \van_b)^n$ lies within $f^n + \van_b^{n+1}$ for any $f \in \van_b$, we can identify $T^*_bB^{\otimes n}$ with $\van_b^n / \van_b^{n+1}$ for $n \ge 1$.
-When $b$ is an ordinary point, the function $\zeta_b$ defined in Section~\ref{transl:dir} represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
+When $b$ is an ordinary point, the translation parameter $\zeta_b$ that vanishes at $b$ represents a nonzero element of $\van_b / \van_b^2$: the cotangent vector $\lambda\big|_b$.
 In general, $\zeta_b$ represents a nonzero element of $\van_b^n / \van_b^{n+1}$, where $2\pi n$ is the cone angle at $b$.
@@
 \end{align*}
-When $b$ is a branch point, the coordinate $\omega_b$ we chose in Section~\ref{transl:dir} gives us an isomorphism
+When $b$ is a branch point, the coordinate $\omega_b$ we fixed in ``A sense of direction'' gives us an isomorphism
 \begin{align*}
@@
 \end{center}
-commute. Here, $\blankbox^n$ represents the $n$th power map.
+commute. Here, $\blankbox^n$ represents the $n$th-power map.
 % \subsubsection{Boundary}
@@
 \subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
-Pick a local holomorphic function $\zeta$ on $B$ with $d\zeta = \lambda$, and an extended angle $\theta \in \R$.
-\textcolor{VioletRed}{[If we define ``translation parameter'' earlier, we can say:] Pick a translation parameter $\zeta$.} The {\em Laplace transform} $\laplace_\zeta^\theta$ turns a local holomorphic function $f$ on $B$ into a local holomorphic function on $T^*B$.
-\textcolor{magenta}{[Priority: update to $\zeta = \alpha$]} When $b \in B$ is an ordinary point, $\laplace_\zeta^\theta f$ is defined on $T_b^*B$ by the formula
+Pick a translation parameter $\zeta$ on $B$ and an extended angle $\theta \in \R$.
+The {\em Laplace transform} $\laplace_{\zeta, \alpha}^\theta$ turns a local holomorphic function $\phi$ on $B$ into a local holomorphic function on $T^*_{\zeta = 0} B$.
+When $\zeta = 0$ is an ordinary point, the Laplace transform is defined by the formula
 \begin{equation}\label{laplace:int}
-%%\laplace_{\zeta}^\theta f\big|_b =
-\int_{\mathcal{J}_{b}^\theta} e^{-z\zeta} f\,d\zeta,
-\end{equation}
-where $z$ is the frequency function and $\mathcal{J}_{b}^\theta$ is the ray that leaves $b$ at angle $\theta$.
-We will use the shorthand $\laplace_{\zeta, b}^\theta f := \laplace_\zeta^\theta f \big|_b$ throughout this document.
-\textcolor{magenta}{[Notation conflict: we also use $\laplace_{\zeta, \alpha}$ to represent starting at $\zeta = \alpha$, giving the starting point as a coordinate value instead of a point $b$.]}
-
+\laplace_{\zeta, \alpha}^\theta \phi = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta,
+\end{equation}
+where $z$ is the frequency function and $\mathcal{J}_{\zeta, \alpha}^\theta$ is the ray $\zeta \in \alpha + e^{i\theta} [0, \infty)$.
 To make sense of this formula, we ask for the following conditions.
 \begin{itemize}
-\item The base point $b$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_b^\theta$.
-\item The ray $\mathcal{J}_b^\theta$ avoids the branch points after leaving $b$.
-\item The integral converges. We guarantee this by asking for a pair of simpler conditions.
-%\color{RoyalBlue}
+\item The starting point $\zeta = \alpha$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = 0$.
+\item The integral converges. We ensure this by putting conditions on $\phi$ and $z$.
 \begin{itemize}
-\item With respect to the flat metric, $f$ is uniformly of exponential type $\Lambda$ along $\mathcal{J}_b^\theta$, and is locally integrable throughout.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$ there is a constant $A_\varepsilon$ (which depends on $\varepsilon$) such that $|f(x)|\leq A_\varepsilon e^{\Lambda+\varepsilon} $.
-We instead require that there exists a uniform constant $A$ such that for every $\varepsilon>0$ the bound holds.} \textcolor{Pink}{[Revise]} Following \cite{reg-sing-volterra}, we require $f \in \singexp{\sigma}{\Lambda}(\Omega_b)$, with $\sigma>-1$.\footnote{The condition $\sigma>-1$ guarantees the integrability at $\zeta=b$.} The set $\Omega_b$ is a tubular neighbourhood of $\mathcal{J}_b^\theta$.
-\item The value of $z$ is in the half-plane $H^{\theta}_\Lambda$ cut out by the inequality $\Re(e^{i\theta} z) > \Lambda$.
+\item With respect to the flat metric, $\phi$ is uniformly of exponential type $\Lambda$ along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and is locally integrable throughout the ray.\footnote{Recall that a function $\phi$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|\phi|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|\phi| \le A e^{\Lambda|\zeta|}$.}
+\item The value of $z$ satisfies the inequality $\Re(e^{i\theta} z) > \Lambda$, which cuts out a half-plane $H^\theta_\Lambda$ in $T^*_{\zeta = 0} B$.
 \end{itemize}
 \end{itemize}
-\color{black}
+For any $\sigma > -1$, the conditions on $\phi$ are satisfied by all of the functions in the spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ introduced in \cite{reg-sing-volterra}.
+Here, the domain $\Omega_\alpha$ must contain the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and the norm $\|\cdot\|_{\sigma, \Lambda}$ is taken with respect to $\zeta = \alpha$.
 \subsubsection{The Laplace transform over a branch point}
-When $b$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_\zeta^\theta f$ on $T_b^*B$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made at the end of Section~\ref{transl:dir}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_b^\theta$.
-The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $b$, so we pull it back to $T^*_bB$ along the $n$th-power map.
+When $\zeta = 0$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_{\zeta, \alpha}^\theta \phi$ on $T_{\zeta = 0}^*B$, as long as we take care of a few subtleties.
+Thanks to the labeling choices we made in Section~\ref{sec:transl}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $\zeta = 0$, so we pull it back to $T^*_{\zeta = 0} B$ along the $n$th-power map.
 This amounts to substituting $w_b^n$ for $z$ in formula~\eqref{laplace:int}.
-The half-plane $z \in H_{\theta}$ in $T_b^*B^{\otimes n}$ pulls back to $n$ sectors of angle $\pi/n$ in $T_b^*B$.
-We only define $\laplace_\zeta^\theta f$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+The inequality $\Re(e^{i\theta} z) > \Lambda$ cuts out a half-plane in $T_b^*B^{\otimes n}$, which pulls back to $n$ sector-like regions in $T_b^*B$ of angle $\pi/n$.
+We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
 %\color{gray}
@@
 We have adopted a variable naming convention that makes these distinctions apparent at a glance.
-\color{LimeGreen}
 \begin{center}
@@
 On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
-\color{black}
 %
@@
 %
-Let $\series{\phi},\series{\psi}\in\C\lbrace\zeta\rbrace$ be two convergent formal series in a neighbourhood of $\zeta=0$, and let $\hat{\phi}$ and $\hat{\psi}$ be respectively their sum in a common region of convergence, say $|\zeta|<R$.
-Then the convolution product $\hat{\phi}\ast\hat{\phi}$ is defined as
+Let $\series{\phi}, \series{\psi} \in \C\{\zeta\}$ be two convergent formal series in a neighbourhood of $\zeta=0$, and let $\hat{\phi}$ and $\hat{\psi}$ be respectively their sum in a common region of convergence, say $|\zeta|<R$.
+Then the convolution product $\hat{\phi}\ast\hat{\psi}$ is defined as
 \begin{equation}\label{eq:convolution}
@@
 \begin{proof}
-It is enough to show that
-\[\laplace_{\zeta,0}\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}\big[{\phi}\big]\laplace_{\zeta,0}\big[{\psi}\big],\]
-which indeed follows from simple integral computations (see for instance ~\cite[Theorem 2.39]{laplace-tfm}). 
+We just need to prove that
+\[ \laplace_{\zeta,0}[{\phi}\ast{\psi}] = \laplace_{\zeta,0}[{\phi}]\,\laplace_{\zeta,0}[{\psi}] \]
+for all $\phi, \psi \in \singexp{\sigma}{\Lambda}$. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm}.
 \end{proof}
@@
 We saw in Section~\ref{sec:reg-decay} that when $\Omega$ is an appropriate sector, the Laplace transform on $\singexp{\sigma}{\Lambda}(\Omega)$ has a left inverse.
-In light of the proposition above, that means the Laplace transform is a $\C$-algebra isomorphism onto its image.
-    \color{RoyalBlue} It is possible to define an inverse Laplace transform, so that $\laplace_{\zeta,0}$ becomes an algebra isomorphisms.
-However we will refer to \textcolor{magenta}{[standard reference]} for details.
-\textcolor{magenta}{[see also section on Regularity for Laplace]}
-    \color{black}
+This strengthens the proposition above, showing that the Laplace transform is a $\C$-algebra isomorphism onto its image.
 \end{remark}
@@
 %\end{proof}
+\color{PaleVioletRed}
+\subsubsection{Borel transforms on $1$-Gevrey series}
+[I've moved this section into Section~\ref{sec:bridging} (``Bridging the gap\ldots'') because it seems to be in the same spirit. If it should or must stay here, please let me know.]
+\color{black}
 \subsubsection{Borel transforms on $1$-Gevrey series}\label{sec:Borel-gevrey}
-So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.
-These formal series are the so-called $1$-Gevrey series:
+\textcolor{PaleVioletRed}{[This is an example of a ``run-on sentence.'' Please look for sentences like this and split them up, as shown above.
+$\rightarrow$]} \textcolor{OrangeRed}{So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.} These formal series are the so-called $1$-Gevrey series:
 \[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
@@
 \subsection{Bridging the gap between analytic and formal objects}\label{sec:bridging}
-The spaces $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
-To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\textcolor{LimeGreen}{\Lambda}}(\Omega)$.
+The spaces $\singexp{\rho}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
+To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\Lambda}(\Omega)$.
 We need a way to make sure we stay in the subspace where the Taylor series exists.
@@
 Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
-We can arrange for $\tau$ to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
-\textcolor{magenta}{[Point out that we can always accomplish this by changing the sign of $\tau$.]} Since $\nu$ is holomorphic, we can express it as a Taylor series
+By changing the sign of $\tau$, we can arrange for it to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+Since $\nu$ is holomorphic, we can express it as a Taylor series
 \[ \nu = \sum_{m \ge 0} b_m^a \tau^m\,d\tau \]

### 2024-03-29 exp-resurgence.tex
Move section on 1-Gevrey series to "Bridging the gap"
Start revising it too.

@@
 \textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$.
-Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_{b}B$, is compatible with $\laplace_{\zeta,b}$.}
-\begin{lemma}%%\label{translation}
+Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_\alpha B$, is compatible with $\laplace_{\zeta, \alpha}$.}
+\begin{lemma}\label{translation}
+If the Laplace transform of $\varphi$ is well-defined, then
+
 Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
@@
 \end{equation}
+\begin{todo}
 In other words, the diagram
 \begin{center}
-\begin{tikzcd}
- \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & \textcolor{magenta}{e^{bz}}\,\mathcal{O}_{T^*B}(H)\\
-& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
+\begin{tikzcd}[row sep=12mm, column sep=2mm]
+\mathcal{O}(T^*B) \arrow[rr, "e^{\alpha z}"] & & \mathcal{O}(T^*B)\\
+& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_\alpha, 0}"]\arrow[ur,swap,"\laplace_{\zeta, \alpha}"]
 \end{tikzcd}
 \end{center}
-commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
+commutes, where $H$ is the half-plane $\Re(z) > 0$.
+\end{todo}
 \end{lemma}
@@
 The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
-\textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.}
+\textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.} \textcolor{orange}{Note that these results don't depend on which cotangent fiber we're mapping into.
+$\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.}
 \begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
@@
 \begin{proof}
-Given some $f \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
-\begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta f| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} f\,d\zeta_\alpha \right| \\
-& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
+Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
+\begin{align*}
+|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
+& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
 \end{align*}
@@
 When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows.
-This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta f$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$.
-It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta f$ match where their domains overlap.
-We can therefore glue these functions together into one big Laplace transform of $f$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.
-
-We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta f$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$.
+This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$.
+It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap.
+We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.
+
+We can now simplify the calculation of $\laplace_{\zeta_\alpha, 0}^\theta \phi$ by looking at $\arg(z)$ and using the closest angle $\theta$ in the opening of $\Omega_\alpha$.
 This keeps $\Lambda - c_{z, \theta}|z|$ equal to $\Delta$, the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta f| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|f\|_{\sigma-1, \Lambda}\,dt.
-\end{align*}
-The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$. We can evaluate it by observing that this bound on the Laplace transform of $f$ is itself a Laplace transform:
-\[ |\laplace_{\zeta_\alpha, 0}^\theta f| \le \Gamma(\sigma) \Delta^{-\sigma} \|f\|_{\sigma-1, \Lambda}. \]
+|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
+\end{align*}
+The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$.
+We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
+\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
 In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
-\[ \|\laplace_{\zeta_\alpha, 0}^\theta f\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|f\|_{\sigma-1, \Lambda}, \]
+\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
 which is what we wanted to show.
@@
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
-for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-On $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\mathcal{C}}$, we have
+for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]
@@
 The inverse Laplace transform is given by the formula
-\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\textcolor{magenta}{\mathcal{C}}} e^{z\zeta_\alpha} \Phi\,dz. \]
+\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz. \]
 When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\textcolor{magenta}{\mathcal{C}}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
 & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
@@
 \end{align*}
-using the new parameter $s = \sin(\varepsilon/2)\,t$. Recognizing the integral in the last line as itself a Laplace transform, we have
+using the new parameter $s = \sin(\varepsilon/2)\,t$.
+Recognizing the integral in the last line as a Laplace transform integral, with the roles of position and frequency played by $s$ and $|\zeta_\alpha|$ respectively, we have
 \[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
 which is what we wanted to show.
-
-%%On $\Omega_\alpha^\varepsilon$, by construction, the angle $\arg(\zeta)$ is more than $\pi + \varepsilon/2$ away from the asymptotic directions of $\textcolor{magenta}{\mathcal{C}}$.
-Hence, on $\Omega_\alpha^\varepsilon \times \textcolor{magenta}{\mathcal{C}}$, we have
-%%\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big) \]
-%%for some constant $\lambda' \in \R$. It follows that
-%%\begin{align*}
-%%\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} F\right| & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon)\,|t|\right)} \Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma} \|F\|_{\sigma, \Lambda}\,dt \\
-%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon)\,t}\,dt \\
-%%& = e^{|\zeta_\alpha| \lambda'} \|F\|_{\sigma, \Lambda}\,\frac{\Delta_{\textcolor{magenta}{\Lambda}}^{-\sigma}}{2 \pi}\,\frac{2}{|\zeta_\alpha| \sin(\varepsilon)}
-%%\end{align*}
-\textcolor{orange}{[Oops, looks like we can't keep $\Delta$ constant along the integration path if we want to recover something with a $|\zeta_\alpha|^{\sigma-1}$ singularity.]}
 \end{proof}
@@
     \[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
-In other words, the following diagram 
+In other words, the diagram 
 \begin{center}
 \begin{tikzcd}[every arrow/.append style={shift left}]
-\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"']\arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"]    \\
+\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
 & & \\
-\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"']      &  & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha,0}"]\arrow{uu}{\laplace_{\zeta,\alpha}}
+\{1, \zeta, \zeta^2, \zeta^3, \ldots\} \arrow[rr, "\mathsf{T}_{-\alpha}^*"'] & & \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\}\arrow[lluu,"\laplace_{\zeta_\alpha, 0}" description]\arrow{uu}{\laplace_{\zeta, \alpha}}
 \end{tikzcd}
@@
 Then the convolution product $\hat{\phi}\ast\hat{\psi}$ is defined as
+\color{Maroon}
+\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta, \]
+where $\mathsf{R}$ is the $180^\circ$ rotation that exchanges $\zeta = 0$ with $a$. In other words, $\mathsf{R}^*\zeta = \zeta(a) - \zeta$.
+
+%%where we get $\phi_\text{flip}$ by pulling $\phi$ back along the transformation that moves $a$ to $\zeta = \alpha$ and then rotates $180 translating $a$ to $\zeta = \alpha$, rotating $180^\circ$, and
+\color{black}
 \begin{equation}\label{eq:convolution}
@@
 \color{black}
-\subsubsection{Borel transforms on $1$-Gevrey series}\label{sec:Borel-gevrey}
-\textcolor{PaleVioletRed}{[This is an example of a ``run-on sentence.'' Please look for sentences like this and split them up, as shown above.
-$\rightarrow$]} \textcolor{OrangeRed}{So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.} These formal series are the so-called $1$-Gevrey series:
+%
+\subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
+As we will see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
+\begin{defn}
+    Let $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, b}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, b} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =b}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
+where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_b,0}^{-\lambda}$: 
+%
+\begin{equation*}
+    \partial_{\zeta_b,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_b=0}^{p}(\zeta_b(p)-\zeta_b)^{\lambda-1} \varphi(\zeta_b+b)\, d\zeta_b.
+\end{equation*}} 
+\end{defn}
+Notice that the fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{b}\,\fracderiv{\mu}{\zeta}{b} & = \fracderiv{\lambda+\mu}{\zeta}{b} \qquad \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
+
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+We will use the {\em Riemann-Liouville} convention.
+\begin{definition}\label{defn:frac_driv}
+For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
+\end{definition}
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+\begin{prop}\label{prop:L-int-op}
+    Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
+    \begin{itemize}
+        \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
+         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
+        for every $\lambda\in\R_{<0}$;
+        \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
+Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
+         \item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
+        for every $n\in\Z_{\geq 0}$.
+    \end{itemize}
+\end{prop}
+\begin{proof}
+%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
+%\begin{align*}
+ %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
+  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
+   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
+%\end{align*}
+
+   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
+    \begin{align*}
+        z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
+        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
+        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
+        &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
+        \end{align*}
+        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
+\begin{align*}
+    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
+    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
+    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
+\end{align*}
+     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
+        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
+Similarly, one can prove \emph{iii)}.
+\end{proof}
+\begin{lemma}\label{lem:frac-deriv-Borel}
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
+\end{lemma}
+\begin{proof}
+We will show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+\begin{align*}
+\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
+& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
+\end{align*}
+by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
+\begin{equation}\label{frac-diff-laplace}
+\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
+\end{equation}
+for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
+& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
+\end{align*}
+Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
+The condition $\alpha \in (0, 1)$ saves us from the trouble we would run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
+This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
+\end{proof}
+We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
+\begin{prop}\label{prop:frac-der-int-borel}
+Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
+\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
+\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
+\end{itemize} 
+\end{prop}
+\begin{proof} 
+The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
+\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
+Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
+\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\partial_\zeta^\lambda\borel_\zeta\series{\Phi}\]
+where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
+
+Finally, $(iii)$ follows from a simple computation: 
+\begin{align*}
+\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
+&=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
+&=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
+&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
+\end{align*}
+\end{proof}
+\begin{remark}
+We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\tau\in\R\setminus\Z_{>0}$ 
+\[\fracderiv{\tau}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\tau \tilde{\Phi}\big]=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}.\]
+\begin{verify}
+\begin{align*}
+\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
+&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
+&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
+&=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
+\end{align*}
+Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
+$\tau>0$ and $\tau\notin\Z_{>0}$, 
+\[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
+\]
+and if $\tau<0$, by definition 
+\[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
+therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
+\end{verify}
+\end{remark}
+\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
+The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
+\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
+Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
+Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
+\begin{equation}
+    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
+\end{equation}
+where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\tilde{\phi}$ and $\tilde{\psi}$ in a neighbourhood of $\zeta=\alpha$.
+
+We also introduce $\delta_\alpha$ as the unit for the product $\ast_\alpha$
+\[\delta_\alpha\ast_\alpha\borel_\zeta(e^{-\alpha z}z^{-n-1}):=\borel_\zeta(1\cdot e^{-\alpha z} z^{-n-1})=\borel_\zeta\laplace_{\zeta,\alpha}\frac{\zeta_\alpha^n}{n!}=\frac{\zeta_\alpha^n}{n!},\]
+where in the last step we used the properties of $\borel_\zeta$ acting on transseries (see Section~\ref{sec:action_transseries}).
+More generally, if $\borel_\zeta\tilde{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
+\begin{remark}
+We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
+
+We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
+\begin{align*}
+    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta (z^{-\lambda})\ast_\alpha\phi
+\end{align*}
+where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
+Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
+%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
+Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
+For every $\lambda\in (-1,\infty)$
+\begin{multline*}
+    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
+    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
+\end{multline*}
+hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
+%Finally, recall that for every holomorphic function $\Phi$ regareded as a function on $T^*_{\zeta=b}B$, the Borel transform  the fractional integrals $\fracderiv{-\lambda}{\zeta}{b}\varphi$ and 
+%$\fracderiv{-\lambda}{\zeta_b}{0}\varphi$ coincide, therefore 
+%\begin{align}\label{change_chart_convolution}
+ %   \borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_b\borel_\zeta\series{\Phi}
+%\end{align}
+%in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $b\in B$.
+\end{remark}
+
+%\subsection{Differential equation}
+%\textcolor{orange}{Should we keep this section?}
+%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
+In these coordinates, we can write down the partial differential operator
+%\begin{equation}%%\label{laplace:op}
+%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
+%\end{equation}
+%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
+
+%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
+%\end{problem}
+%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
+\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
+
+\subsection{Bridging the gap between formal and analytic objects}\label{sec:bridging}
+%
+\subsubsection{Formal to analytic \textcolor{LimeGreen}{[title suggestions?]}}\label{sec:Borel-gevrey}
+%
+If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge.
+These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.
+Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
+They are characterized by the moderate growth of their coefficients.
+\begin{prop}
+A series
+\[ \sum_{n \ge -1} a_n z^{-n-1} \]
+is $1$-Gevrey if and only if there is some $A > 0$ with $|a_n| \lesssim A^n n!$ over all $n \ge 0$.
+\end{prop}
+\begin{proof}[Proof sketch]
+The Borel-transformed series
+\[ a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!} \]
+converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$.
+\end{proof}
+\color{RoyalBlue}
+\textcolor{PaleVioletRed}{[This is an example of a ``run-on sentence.'' Please look for sentences like this and split them up, like above $\rightarrow$]} \textcolor{OrangeRed}{So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.} These formal series are the so-called $1$-Gevrey series:
 \[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
@@
 \end{lemma}
+\color{black}
 Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (assuming they are series of $z$ on the fiber over $\zeta=0$), then following \cite[Definition 5.12]{diverg-resurg-i}, the convolution product $*$ of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
@@
 %\end{proof}
-
-%
-\subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
-As we will see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
-\begin{defn}
-    Let $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, b}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, b} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =b}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_b,0}^{-\lambda}$: 
-%
-\begin{equation*}
-    \partial_{\zeta_b,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_b=0}^{p}(\zeta_b(p)-\zeta_b)^{\lambda-1} \varphi(\zeta_b+b)\, d\zeta_b.
-\end{equation*}} 
-\end{defn}
-Notice that the fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{b}\,\fracderiv{\mu}{\zeta}{b} & = \fracderiv{\lambda+\mu}{\zeta}{b} \qquad \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} f$, which differ by operators that act on the germ of $f$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We will use the {\em Riemann-Liouville} convention.
-\begin{definition}\label{defn:frac_driv}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-\begin{prop}\label{prop:L-int-op}
-    Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
-    \begin{itemize}
-        \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
-         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
-        for every $\lambda\in\R_{<0}$;
-        \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
-Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
-         \item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
-        for every $n\in\Z_{\geq 0}$.
-    \end{itemize}
-\end{prop}
-\begin{proof}
-%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
-%\begin{align*}
- %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
-  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
-   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
-%\end{align*}
-
-   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
-    \begin{align*}
-        z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
-        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
-        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
-        &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
-        \end{align*}
-        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
-\begin{align*}
-    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
-    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
-    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
-\end{align*}
-     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
-        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
-This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
-Similarly, one can prove \emph{iii)}.
-\end{proof}
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
-\begin{proof}
-We will show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we would run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
-\begin{prop}\label{prop:frac-der-int-borel}
-Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
-\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
-\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
-\end{itemize} 
-\end{prop}
-\begin{proof} 
-The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
-\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
-Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
-\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\partial_\zeta^\lambda\borel_\zeta\series{\Phi}\]
-where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
-
-Finally, $(iii)$ follows from a simple computation: 
-\begin{align*}
-\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
-&=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
-&=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
-&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
-\end{align*}
-\end{proof}
-\begin{remark}
-We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\tau\in\R\setminus\Z_{>0}$ 
-\[\fracderiv{\tau}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\tau \tilde{\Phi}\big]=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}.\]
-\begin{verify}
-\begin{align*}
-\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
-&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
-&=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
-\end{align*}
-Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
-$\tau>0$ and $\tau\notin\Z_{>0}$, 
-\[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
-\]
-and if $\tau<0$, by definition 
-\[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
-therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
-\end{verify}
-\end{remark}
-\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
-The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
-\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
-Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
-Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
-\begin{equation}
-    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
-\end{equation}
-where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\tilde{\phi}$ and $\tilde{\psi}$ in a neighbourhood of $\zeta=\alpha$.
-
-We also introduce $\delta_\alpha$ as the unit for the product $\ast_\alpha$
-\[\delta_\alpha\ast_\alpha\borel_\zeta(e^{-\alpha z}z^{-n-1}):=\borel_\zeta(1\cdot e^{-\alpha z} z^{-n-1})=\borel_\zeta\laplace_{\zeta,\alpha}\frac{\zeta_\alpha^n}{n!}=\frac{\zeta_\alpha^n}{n!},\]
-where in the last step we used the properties of $\borel_\zeta$ acting on transseries (see Section~\ref{sec:action_transseries}).
-More generally, if $\borel_\zeta\tilde{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
-\begin{remark}
-We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
-
-We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
-\begin{align*}
-    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta z^{-\lambda}\ast_\alpha\phi
-\end{align*}
-where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
-Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
-%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
-Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
-For every $\lambda\in (-1,\infty)$
-\begin{multline*}
-    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
-    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
-\end{multline*}
-hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
-%Finally, recall that for every holomorphic function $\Phi$ regareded as a function on $T^*_{\zeta=b}B$, the Borel transform  the fractional integrals $\fracderiv{-\lambda}{\zeta}{b}\varphi$ and 
-%$\fracderiv{-\lambda}{\zeta_b}{0}\varphi$ coincide, therefore 
-%\begin{align}\label{change_chart_convolution}
- %   \borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_b\borel_\zeta\series{\Phi}
-%\end{align}
-%in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $b\in B$.
-\end{remark}
-
-%\subsection{Differential equation}
-%\textcolor{orange}{Should we keep this section?}
-%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-%\begin{equation}%%\label{laplace:op}
-%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-%\end{equation}
-%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-\subsection{Bridging the gap between analytic and formal objects}\label{sec:bridging}
+%
+\subsubsection{Analytic to formal \textcolor{LimeGreen}{[title suggestions?]}}
+%
 The spaces $\singexp{\rho}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.

### 2024-04-01 exp-resurgence.tex
Revise new proof of Borel summability
Also, revise intro to Airy and Airy-Lucas examples

@@
 \theoremstyle{definition}
-\newtheorem{defn}{Definition}
 \newtheorem{definition}{Definition}[section]
@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}.
-We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
+\item \textcolor{LimeGreen}{If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}.} We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
@@
 Ask more about this.]}
-\item If $\hat{\phi}$ also grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$.
+\item If $\hat{\phi}$ also grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
 \end{enumerate}
@@
 \basicLaplace
-\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}[0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
+\captionof{figure}{The Laplace transform $\laplace^\theta_{\zeta, \alpha}$ integrates a function along the ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$ in the position domain, turning it into a function on some half-plane $\Re(e^{i\theta} z) > \Lambda$ in the frequency domain.}
 \end{center}
@@
 The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
-\begin{defn}
+\begin{definition}
 On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a power series
-\begin{equation}\label{series:asymp-defn}
+\begin{equation}\label{series:asymp-definition}
 a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
@@
 to denote this relationship.
-\end{defn}
+\end{definition}
 \color{RoyalBlue}
-\begin{defn}
+\begin{definition}
 On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
-\begin{equation}%%\label{series:asymp-defn}
+\begin{equation}%%\label{series:asymp-definition}
 \textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
@@
 over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $\Phi$, namely we will write \[\Phi\sim \sum_{n\geq 1} a_n z^{-n}.\]}
-\end{defn}
+\end{definition}
 \color{black}
 This definition generalizes straightforwardly to ``fractionally shifted'' power series and trans-monomials.
-\begin{defn}
+\begin{definition}
 On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a fractionally shifted trans-monomial
-\begin{equation}\label{trans-monom:asymp-defn}
+\begin{equation}\label{trans-monom:asymp-definition}
 e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots\right)
@@
 over all orders $n$. We will again use $\sim$ to denote this relationship.
-\end{defn}
-
-If two power series of the form \eqref{series:asymp-defn} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
+\end{definition}
+
+If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
 The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
@@
 Since asymptotic expansions on overlapping sectors must agree, we can think of this homomorphism as being determined by a ray.
-\begin{defn}
+\begin{definition}
 For any direction $\theta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
 \[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
-is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in \mathcal{J}_0^\infty$.
+is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta}(0, \infty)$.
 To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
-\end{defn}
+\end{definition}
 \begin{todo}[Mention Nevanlinna's theorem, re-stated as \cite[Theorem~C.11]{nikolaev2023existence}, somewhere later.]\end{todo}
@@
 
-\begin{defn}\label{def:unif-gevrey-asymp}
-On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
+\begin{definition}\label{def:unif-gevrey-asymp}
+On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-definition} if there is a constant $A \in (0, \infty)$ for which
 \[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
 over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
-\end{defn}
+\end{definition}
 To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
@@
 Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
-More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
-where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
+More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form \textcolor{PaleVioletRed}{[I just noticed we use $\partial_z$ instead of $\tfrac{\partial}{\partial z}$ in \texttt{reg-sing-volterra}, where these equations were copied from.
+Could we switch to $\tfrac{\partial}{\partial z}$, as I've done provisionally?]}
+\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
+where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
 We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
@@
 Recall that $\theta$ is the direction of the ray $\mathcal{J}^\theta_\alpha$.
-\item\label{part-2} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-2} The series $\tilde{I}_\alpha$ \textcolor{LimeGreen}{[is $1$-Gevrey]}. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
 \item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
@@
 The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
-In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
+In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
 
@@
 We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we’ll make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}.
+For instance, for the Airy function we will make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}.
 \textcolor{red}{The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
@@
 If the Laplace transform of $\varphi$ is well-defined, then
-
-Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
    \begin{equation}
@@
 \end{proof}
-\begin{prop}
+\begin{prop}\label{prop:inverse_laplace_analytic}
 Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
@@
 \[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
-Here, we are thinking of $z$ as the standard coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
-We can get a function on $T^*_{\zeta = b}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_b$ defined by $\zeta = \zeta_b + b$:
-\[ \laplace_{\zeta_b, 0}\left[\frac{\zeta_b^n}{n!}\right] = z^{-n-1}. \]
+Here, we are thinking of $z$ as the frequency coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
+We can get a function on $T^*_{\zeta = \alpha}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_\alpha$ defined by $\zeta = \zeta_\alpha + \alpha$:
+\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}. \]
 On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
@@
 \borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}.
+\sum_{n \ge 0} a_n z^{-n-1} & \mapsto \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}.
 \end{align*}
 This definition extends straightforwardly to fractional powers of $z$. Observing that   
-\[\laplace_{\zeta,0}\big[\zeta^\sigma\big]=\Gamma(\sigma+1)z^{-\sigma-1}\]
-for every $\rho \in \R \setminus \Z_{\leq 0}$, we define 
-\begin{align*}
-\borel_\zeta[z^{-\rho-1}] \defeq \frac{\zeta^{\rho}}{\Gamma(\rho+1)}.
+\[\laplace_{\zeta,0}[\zeta^\sigma]=\Gamma(\sigma+1)z^{-\sigma-1}\]
+for every $\sigma \in \R \setminus \Z_{\leq 0}$, we define 
+\begin{align*}
+\borel_\zeta[z^{-\sigma-1}] \defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)}.
 \end{align*}
@@
 
-On a different fiber of $T_{\zeta=b}^*B$, the Borel transform $\borel_{\zeta_b}$ in the translated coordinate $\zeta_b$ is defined as the inverse of the Laplace transform $\laplace_{\zeta_b,0}$ on monomials
+On a different fiber of $T_{\zeta=\alpha}^*B$, the Borel transform $\borel_{\zeta_\alpha}$ in the translated coordinate $\zeta_\alpha$ is defined on monomials as the inverse of the Laplace transform $\laplace_{\zeta_\alpha,0}$
 \begin{center}
 \begin{tikzcd}[every arrow/.append style={shift left}]
- \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_b}} \\ \{1, \zeta_b, \frac{1}{2!} \zeta_b^2, \frac{1}{3!} \zeta_b^3, \ldots\} \arrow{u}{\laplace_{\zeta_b, 0}}
+ \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta_\alpha}} \\ \{1, \zeta_\alpha, \frac{1}{2!} \zeta_\alpha^2, \frac{1}{3!} \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta_\alpha, 0}}
 \end{tikzcd}
 \end{center}
-and extended to formal power series by countable linearity $\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_b \rrbracket$.
+It extends countable linearity to a map $\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_\alpha \rrbracket$.
 %\begin{align*}
@@
 commutes, where the functions of the variable $z$ belong to the fiber $T^*_{\zeta=0}B$.
-If $z$ is a function on the fiber over $\zeta=b$, then it is enough to replace $\borel_\zeta$ with $\borel_{\zeta_b}$ and to use  $\laplace_{\zeta_b,0}$ as the inverse.
+If $z$ is a function on the fiber over $\zeta=\alpha$, then it is enough to replace $\borel_\zeta$ with $\borel_{\zeta_\alpha}$ and to use  $\laplace_{\zeta_\alpha,0}$ as the inverse.
 %\color{orange}
@@
 %\color{black}
+%
 \subsection{Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
-The space of formal power series $\C\llbracket z^{-1}\rrbracket$ is a $\C$-algebra with unit $1$, thus by definition the Borel transform is a $\C$-linear map between $\C\llbracket z^{-1}\rrbracket$ and $\C\delta +\C\llbracket\zeta\rrbracket$, where $\delta:=\borel_\zeta (1)$ denotes the formal unit on $\C\llbracket\zeta\rrbracket$.
-In fact, since $\borel_\zeta$ is deifned as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity.
-As a result, we find that the \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\]
-is a $\C$-linear invertible map whose inverse is the formal Laplace transform.
-
-In addition, on both $\C\llbracket\zeta\rrbracket$ and $\C\llbracket z^{-1}\rrbracket$ there is the natural product given by the Cauchy product of formal power series, and by definition, the Borel transform extends to a $\C$-algebra isomorphism with inverse given by the formal Laplace transform.
-
-However, as we discussed in Section~\ref{sec:reg-decay}, the Laplace transform $\laplace_{\zeta,0}$ is naturally defined on the space of integrable, holomorphic functions, namely $\singexpalg{\sigma}(\Omega)\subset \zeta^{\sigma}\C\lbrace\zeta\rbrace$ for $\sigma>-1$, hence we might expect it extends to a $\C$-algebra homomorphism from $\singexpalg{\sigma}(\Omega)$ to $\mathcal{O}(H)$.
-Indeed, that is the case, but it requires to introduce the convolution product on the space of analytic functions $\zeta^{\sigma-1}\C\lbrace\zeta\rbrace$.
-We will discuss it in Section~\ref{convolution}.
-
-Consequently, also at the formal level we can restric to a subalgebra of $\C\llbracket z^{-1}\rrbracket$ whose image under $\borel_\zeta$ lies in $\C\lbrace\zeta\rbrace$.
-This subalgebra is the so called space of $1$-Gevrey series $\C\llbracket z^{-1}\rrbracket_1\subset\C\llbracket z^{-1}\rrbracket$ and $\borel_\zeta\colon \C\llbracket z^{-1}\rrbracket_1\to\C\delta+\C\lbrace\zeta\rbrace$ is a $\C$-algebra homomorphism (see Section~\ref{sec:Borel-gevrey}).
-
-Finally in Section~\ref{sec:frac-diff-laplace}, we will consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives in both the frequency and position domains, as well as fractional integrals and derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
-
+We begin this section introducing some notation.
 \begin{notation*}
@@
 On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
-%
-\subsubsection{The convolution product}\label{convolution}
-%
-Let $\series{\phi}, \series{\psi} \in \C\{\zeta\}$ be two convergent formal series in a neighbourhood of $\zeta=0$, and let $\hat{\phi}$ and $\hat{\psi}$ be respectively their sum in a common region of convergence, say $|\zeta|<R$.
-Then the convolution product $\hat{\phi}\ast\hat{\psi}$ is defined as
-\color{Maroon}
-\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta, \]
+\subsubsection*{Laplace transform as algebra homomorphism}
+The Laplace transform $\laplace_{\zeta,\alpha}$ is defined on the space of holomorphic functions in the position domain, integrable at $\zeta=\alpha$ and exponentially bounded at infinity.
+In particular, that subspace of holomorphic functions on $B$, it has a $\C$-algebra structure, with product given by the \textit{convolution product}.
+\begin{definition}\label{def:convolution}
+Let $\phi,\psi$ be two holomorphic functions on $B$.
+Choose a translation cooridnate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
+\begin{equation}\label{eq:convolution_def}
+    [\phi \ast_{\zeta, \alpha} \psi](a) := \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta,
+\end{equation}
 where $\mathsf{R}$ is the $180^\circ$ rotation that exchanges $\zeta = 0$ with $a$. In other words, $\mathsf{R}^*\zeta = \zeta(a) - \zeta$.
-
-%%where we get $\phi_\text{flip}$ by pulling $\phi$ back along the transformation that moves $a$ to $\zeta = \alpha$ and then rotates $180 translating $a$ to $\zeta = \alpha$, rotating $180^\circ$, and
-\color{black}
-\begin{equation}\label{eq:convolution}
-    \hat{\phi}\ast\hat{\psi}:=\int_0^{\zeta}\hat{\phi}(\zeta-\zeta')\hat{\psi}(\zeta')\, d\zeta'
-\end{equation}
-and it admits a convergent power series expansion for $|\zeta|<R$ (see \cite[Lemma 5.14]{diverg-resurg-i}).
-
-In addition, we can relax the assumption on $\series{\phi},\series{\psi}$ by allowing integrable singularties at $\zeta=0$, namely  $\series{\phi}\in\zeta^{\sigma}\C\lbrace\zeta\rbrace$ and $\series{\psi}\in\zeta^{\tau}\C\lbrace\zeta\rbrace$ with $\sigma,\tau>-1$.
-In this case, $\hat{\phi}$ and $\hat{\psi}$ will be respectively the sum of the series $\series{\phi}$ and $\series{\psi}$ in an open domain $\Omega\cap \lbrace |\zeta|<R\rbrace$ (that may not contain $\zeta=0$).
-In fact, this leads to the definition of the convolution product for functions in $\singexp{\sigma}{\Lambda}(\Omega)$:
+\end{definition}
+\begin{prop}
+    The $\laplace_{\zeta,\alpha}$ is an algebra homomorphims from the space of holomorphic functions integrable at zero and exponentially bounded at infinity, endowed with the convolution product, to the space of analytic function on the half-plane $\{\Re(z)>0\}$.
+\end{prop}
+\begin{proof}
+We just need to prove that
+\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}] \]
+for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
+\end{proof}
+%
+\begin{remark}
+   Notice that for $\alpha=0$, the definition of convolution in Equation~\eqref{eq:convolution_def} agrees with the standard deifinition (see \cite[Definition~5.12]{diverg-resurg-i}).
+In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast$, following the standard convention.   
+\end{remark}
+Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).
+
+In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism. 
 \begin{lemma}
-    Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega)$ for $\sigma>-1$, then $\phi\ast\psi\in\singexp{\sigma}{\Lambda}(\Omega)$.
+    Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
 \end{lemma}
@@
     \begin{align*}
-        | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
+    |\tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
         &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
@@
 \end{verify}
-In addition, we can show that $\laplace_{\zeta,0}$ is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on the right-half-plane $\Re z>0$. 
+\begin{corollary}
+    Let $\sigma>-1$ and $\Lambda>0$, the Laplace transform 
+    \[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\Omega_\alpha)\to\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
+    is a $\C$-algebra isomomorphism, with inverse defined in Proposition~\ref{prop:inverse_laplace_analytic}. 
+\end{corollary}
+
+\subsubsection*{Borel transform as algebra isomomrphism}
+The Borel transform $\borel_\zeta$ is defined on the space of formal power series $z^{-1}\C\llbracket z^{-1}\rrbracket$, which is a $\C$-algebra, with product given by the Cauchy product of formal power series.
+In addition, introducing the formal unit $\delta$, the Borel transform can be extended to $\C\llbracket z^{-1}\rrbracket$ (including constants), as $\borel_\zeta(1)=:\delta$.
+Therefore, the Borel transform is a $\C$-linear map
+ \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\,.\] 
+In fact, since $\borel_\zeta$ is defined as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity.
+As a result, we find that the Borel transform is a $\C$-linear invertible map whose inverse is the formal Laplace transform.
+
+In addition, on both $\C\llbracket\zeta\rrbracket$ and $\C\llbracket z^{-1}\rrbracket$ there is the natural product given by the Cauchy product of formal power series.
+However, the Borel transform does not extend to a $\C$-algebra isomorphism, because $\borel_\zeta\big(\series{\Phi}\series{\Psi}\big)$ is different from the Cauchy product $\borel_\zeta\series{\Phi}\borel_\zeta\series{\Psi}$.
+%
+In order to view the Borel transform as an algebra isomorphism, we should consider a different product on $\C\llbracket\zeta\rrbracket$, that is the convolution product of formal power series defined as follows:
+\begin{definition}\label{def:convolution_formal}
+    Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then 
+    \begin{equation}\label{eq: formal_convolution}
+ \series{\phi}\ast_{\zeta,0}\series{\psi}:=\sum_{n=0}^\infty c_n \frac{\zeta^n}{n!}\,,
+    \end{equation}
+    with $c_n=\sum_{j=0}^n a_j b_{n-j}$.
+\end{definition}
+Notice that the right hand side of Equation~\eqref{eq: formal_convolution} is the Borel transform of the Cauchy product of the formal series $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, namely if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
+ \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
+ Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+% Furthermore, since $\tilde{\phi},\tilde{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
+% \end{definition}
+Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
+
+We can further generalize this result to transseries: 
 \begin{prop}
-    Let $\sigma>-1$ and $\Lambda>0$.
-The Laplace transform $\laplace_{\zeta,0}$ is a $\C$-algebra homomorphism from $(\singexp{\sigma}{\Lambda}(\Omega), \ast)$ to to the space of holomorphic functions on the right-half-plane $\Re z>0$ with the standard multiplication of functions.
+    The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
+    \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
+    where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
+\end{prop}
+% \begin{proof}
+%     Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n-1}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n-1}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$, then 
+%     \begin{align*}
+%         \borel_\zeta\series{\Phi}\series{\Psi}&=
+%     \end{align*}
+% \end{proof}
+\begin{remark}
+   If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in Equation~\eqref{eq:convolution_def}.
+We will discuss it in Section~\ref{sec:Borel-gevrey}.
+\end{remark}
+%
+\subsection{Bridging the gap between formal and analytic objects}\label{sec:bridging}
+%
+%
+\subsubsection{Formal to analytic}\label{sec:Borel-gevrey}
+%
+If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge.
+\textcolor{LimeGreen}{These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.} Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
+They are characterized by the factorial growth of their coefficients.
+\begin{prop}\label{prop:gevrey_to_convergent}
+A series
+\[ \series{\Phi} = \sum_{n \ge -1} a_n z^{-n-1} \]
+is $1$-Gevrey if and only if its Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$ is convergent.
 \end{prop}
 \begin{proof}
-We just need to prove that
-\[ \laplace_{\zeta,0}[{\phi}\ast{\psi}] = \laplace_{\zeta,0}[{\phi}]\,\laplace_{\zeta,0}[{\psi}] \]
-for all $\phi, \psi \in \singexp{\sigma}{\Lambda}$. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm}.
+From the expression
+\[ \series{\phi} = a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}, \]
+we see that $\series{\phi}$ converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$. The constant $A$ is the radius of convergence of $\series{\phi}$.
 \end{proof}
-\begin{remark}
-We saw in Section~\ref{sec:reg-decay} that when $\Omega$ is an appropriate sector, the Laplace transform on $\singexp{\sigma}{\Lambda}(\Omega)$ has a left inverse.
-This strengthens the proposition above, showing that the Laplace transform is a $\C$-algebra isomorphism onto its image.
-\end{remark}
-%The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus in order to prove that $\borel_\zeta$ is an algebra homomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
-
-%Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
-%\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-%In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
-%\[
- %   \series{\psi}\ast\series{\phi}=\int_0^{\zeta}d\zeta' \series{\psi}(\zeta-\zeta')\series{\phi}(\zeta').
-%\]
-%\begin{lemma}
-%The convolution product induces an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$.
-%\end{lemma}
-%\begin{proof}
-%    Let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
-%\begin{verify}
- %   \begin{align*}
-  %      | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
-   %     &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
-    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
-    %\end{align*}
-%\end{verify}
-%\end{proof}
-%We deduce that also the Laplace transform is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
-%\begin{prop}
- %   Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
-Then the Laplace transform $\laplace_{\zeta,0}^\theta$ is $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
-%\end{prop}
-%\begin{proof}
-%First of all, from the properties of $\laplace_{\zeta,0}^\theta$ we know that if $\phi, \psi\in\singexp{\sigma}{\Lambda}(\Omega)$, then
-%\[\laplace_{\zeta,0}^\theta\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}^\theta\big[{\phi}\big]\laplace_{\zeta,0}^\theta\big[{\psi}\big],\]
-%see for instance \cite[Theorem 2.39]{laplace-tfm}.
-Then we should prove that $\delta$ is a unit: from its definition and the fact that $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we deduce that
- %   \[
-%\laplace_{\zeta,0}^\theta\big[\delta\big]:=\laplace_{\zeta,0}^\theta\big[\borel_\zeta(1)\big]=1.
- %   \]
-%Thus, $\delta$ behaves as a Dirac delta distribution acting on $\singexpalg{\sigma}(\Omega)$. Then, if ${\phi}\in\singexp{\sigma}{\Lambda}(\Omega)$
-  %   \begin{align*}
-%\big[\delta\ast\phi\big](p)&=\int_0^{\zeta(p)} \delta(\zeta(p)-\zeta)\phi(\zeta) \, d\zeta=\phi(p)
- %   \end{align*}
-%\end{proof}
-\color{PaleVioletRed}
-\subsubsection{Borel transforms on $1$-Gevrey series}
-[I've moved this section into Section~\ref{sec:bridging} (``Bridging the gap\ldots'') because it seems to be in the same spirit. If it should or must stay here, please let me know.]
-\color{black}
-%
-\subsubsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
-As we will see in Section~\ref{sec:examples}, it is useful to study the action of the Laplace and Borel transform on both fractional integral and fractional derivative operators.
-\begin{defn}
-    Let $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, b}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, b} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =b}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
-where $p$ is any point on the position domain $B$.\footnote{For completeness we also give the definition of the fractional integral $\partial_{\zeta_b,0}^{-\lambda}$: 
-%
-\begin{equation*}
-    \partial_{\zeta_b,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_b=0}^{p}(\zeta_b(p)-\zeta_b)^{\lambda-1} \varphi(\zeta_b+b)\, d\zeta_b.
-\end{equation*}} 
-\end{defn}
-Notice that the fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{b}\,\fracderiv{\mu}{\zeta}{b} & = \fracderiv{\lambda+\mu}{\zeta}{b} \qquad \lambda, \mu \in (-\infty, 0),
-\end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer (see \cite[Equation 35]{mladenov2014advanced}).
-
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\alpha}{\zeta}{0}$ are defined by composing $\fracderiv{\alpha-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\alpha-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ don't commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\alpha}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
-We will use the {\em Riemann-Liouville} convention.
-\begin{definition}\label{defn:frac_driv}
-For $\alpha \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\alpha}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\alpha}{\zeta}{0} \defeq \left(\tfrac{\partial}{\partial \zeta}\right)^{n+1} \fracderiv{\alpha-1}{\zeta}{0}. \]
-\end{definition}
-The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
-It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
-
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
-This extends the semigroup law:
-\begin{align*}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-\begin{prop}\label{prop:L-int-op}
-    Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
-    \begin{itemize}
-        \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
-         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
-        for every $\lambda\in\R_{<0}$;
-        \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
-Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
-         \item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
-        for every $n\in\Z_{\geq 0}$.
-    \end{itemize}
-\end{prop}
-\begin{proof}
-%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
-%\begin{align*}
- %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
-  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
-   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
-%\end{align*}
-
-   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
-    \begin{align*}
-        z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
-        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
-        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
-        &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
-        \end{align*}
-        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
-\begin{align*}
-    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
-    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
-    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
-\end{align*}
-     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
-        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
-This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
-Similarly, one can prove \emph{iii)}.
-\end{proof}
-\begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] =  \borel_\zeta \left(z^\mu z^{-(k+1)}\right). \]
-\end{lemma}
-\begin{proof}
-We will show that for any $\alpha \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{align*}
-\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right) \right] & = \frac{1}{\Gamma(1-\alpha)} \int_0^\zeta (\zeta-\zeta')^{-\alpha} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\alpha} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma(1-\alpha)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\alpha} t^k\,dt \\
-& = \frac{\zeta^{k-(\alpha-1)}}{\Gamma\big(k-(\alpha-1)+1\big)}
-\end{align*}
-by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
-\begin{equation}\label{frac-diff-laplace}
-\left(\tfrac{\partial}{\partial \zeta}\right)^{n+1}\,\partial^{\alpha-1}_{\zeta } \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] = \frac{\zeta^{k-(n+\alpha)}}{\Gamma\big(k-(n+\alpha)+1\big)}
-\end{equation}
-for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
-\tfrac{\partial}{\partial \zeta} \left(\tfrac{\partial}{\partial \zeta}\right)^{m+1}\,\partial^{\alpha-1}_{\zeta} \left[ \borel_\zeta \left(z^{-(k+1)}\right)(\zeta) \right] & = \tfrac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\alpha)}}{\big(k-(m+\alpha)\big)\,\Gamma\big(k-(m+\alpha)\big)} \right) \\
-& = \frac{\zeta^{k-(m+1+\alpha)}}{\Gamma\big(k-(m+\alpha)\big)}
-\end{align*}
-Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
-The condition $\alpha \in (0, 1)$ saves us from the trouble we would run into if $k-(m+\alpha)$ were in $\Z_{\le 0}$.
-This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
-\end{proof}
-We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
-\begin{prop}\label{prop:frac-der-int-borel}
-Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
-\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
-\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
-\end{itemize} 
-\end{prop}
-\begin{proof} 
-The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
-\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
-Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
-\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\partial_\zeta^\lambda\borel_\zeta\series{\Phi}\]
-where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
-
-Finally, $(iii)$ follows from a simple computation: 
-\begin{align*}
-\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
-&=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
-&=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
-&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
-\end{align*}
-\end{proof}
-\begin{remark}
-We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\tau\in\R\setminus\Z_{>0}$ 
-\[\fracderiv{\tau}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\tau \tilde{\Phi}\big]=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}.\]
-\begin{verify}
-\begin{align*}
-\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
-&=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
-&=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
-&=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
-\end{align*}
-Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
-$\tau>0$ and $\tau\notin\Z_{>0}$, 
-\[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
-\]
-and if $\tau<0$, by definition 
-\[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
-therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
-\end{verify}
-\end{remark}
+
+% Equivalntly, $1$-Gevrey series are caracterized as follows:
+% \begin{lemma}
+% Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
+Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
+% \end{lemma}
+% \begin{proof}
+%     If $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, and $\series{\Phi}(z)=\sum_{n=0}^\infty a_n z^{-n-1}$, then by definition, there exixst a constant $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\ge 0$.
+Therefore,
+%     \[\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\]
+%     which has finite radius of convergence $A^{-1}$. 
+%     Conversely, if $\borel_\zeta\series{\Phi}$ is a germ of analytic functions, i.e.
+$\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \zeta^n$ has finte radius of convergence $1/A$, for some constant $A>0$, then the formal Laplace transform of $\borel_\zeta\series{\Phi}$ gives
+%     \[\sum_{n=0}^\infty a_n\, n!\, z^{-n-1}\]
+%     and $|a_n n!|\le |a_n| n!\lesssim A^n n!$. 
+% \end{proof}
+The space of $1$-Gevrey series is close under the Cauchy product. In addition, 
+\[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
+extends to an algebra homomorphism, where $\C\{\zeta\}$ is endowed with the convolution product defined in Definition~\ref{def:convolution_formal}. 
+% \begin{definition}{(see \cite[Definition 5.12]{diverg-resurg-i})}
+%     Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=0$.
+Then, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
+% \[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+% Furthermore, since $\tilde{\phi},\tilde{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
+% \end{definition}
+% The definition of convolution product for germs of holomorphic functions at $\zeta=0$, can be generalized to germs of analytic functions at $\zeta=\alpha$, using the Borel transform $\borel_{\zeta_\alpha}$ on $1$-Gevrey series on the fiber over $\zeta=\alpha$.
+% \begin{definition}
+%     Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=\alpha$.
+Then, the convolution product of $\tilde{\phi}:=\borel_{\zeta_\alpha}\tilde{\Phi}$ and $\tilde{\psi}:=\borel_{\zeta_\alpha}\tilde{\Psi}$ is defined as
+% \[\borel_{\zeta_\alpha}(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast_{\zeta_\alpha,0}\tilde{\phi}.\]
+% Furthermore, the sum of $\tilde{\psi}\ast_{\zeta_\alpha,0}\tilde{\phi}$ is the convolution $\hat{\psi}\ast_{\zeta_\alpha,0}\hat{\phi}$. 
+% \end{definition}
+In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series:  
+% \begin{prop}
+%     Let $z$ be a coordinate on $T^*_{\zeta=\alpha}B$.
+The Borel transform $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket_1$ to $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$.
+% \end{prop}
+
+\textcolor{orange}{[mention convolution for transseries and difference between different fibers]}
+\color{RoyalBlue}
 \subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
@@
 \begin{remark}
-We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we’ll see how the definitions vary depending on the fibers of $T^*B$ in consideration.
+We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we will see how the definitions vary depending on the fibers of $T^*B$ in consideration.
 
@@
 hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
-%Finally, recall that for every holomorphic function $\Phi$ regareded as a function on $T^*_{\zeta=b}B$, the Borel transform  the fractional integrals $\fracderiv{-\lambda}{\zeta}{b}\varphi$ and 
-%$\fracderiv{-\lambda}{\zeta_b}{0}\varphi$ coincide, therefore 
-%\begin{align}\label{change_chart_convolution}
- %   \borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}\series{\Phi}=\borel_\zeta (z^{-\lambda})\ast_b\borel_\zeta\series{\Phi}
-%\end{align}
-%in fact equation \eqref{change_chart_convolution} can be regarded as a compatibility condition for the convolution product when different coordinate charts are chosen in a neighborhood of a smooth point $b\in B$.
 \end{remark}
-
-%\subsection{Differential equation}
-%\textcolor{orange}{Should we keep this section?}
-%If $\zeta$ is a translation chart for $B$, the functions $\zeta, z$ are Darboux coordinates on the part of $T^*B$ that lies over the domain of $\zeta$.
-In these coordinates, we can write down the partial differential operator
-%\begin{equation}%%\label{laplace:op}
-%\laplacepde_\zeta = \left(\frac{\partial}{\partial z} - \zeta\right) \frac{\partial}{\partial \zeta}.
-%\end{equation}
-%The multiplication by $\zeta$ is the only part of $\laplacepde_\zeta$ that depends on which $\zeta$ we choose.
-
-%Now we can pose a boundary value problem for each angle $\theta \in \R/2\pi\Z$: find a local holomorphic function $F$ on $T^*B$ that satisfies the equation $\laplacepde_\zeta F = 0$ and approaches zero when continued at fixed $z$ along rays of angle $\theta$.
-%\end{problem}
-%The Laplace transform $\laplace_\zeta^\theta$ turns local holomorphic functions on $B$ into solutions of this problem.
-\textcolor{orange}{In fact, it produces all the solutions \textbf{[check argument]}.[Veronica: I don't understand--why it produces all the solutions?]}
-
-\subsection{Bridging the gap between formal and analytic objects}\label{sec:bridging}
-%
-\subsubsection{Formal to analytic \textcolor{LimeGreen}{[title suggestions?]}}\label{sec:Borel-gevrey}
-%
-If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge.
-These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.
-Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
-They are characterized by the moderate growth of their coefficients.
-\begin{prop}
-A series
-\[ \sum_{n \ge -1} a_n z^{-n-1} \]
-is $1$-Gevrey if and only if there is some $A > 0$ with $|a_n| \lesssim A^n n!$ over all $n \ge 0$.
-\end{prop}
-\begin{proof}[Proof sketch]
-The Borel-transformed series
-\[ a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!} \]
-converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$.
-\end{proof}
-\color{RoyalBlue}
-\textcolor{PaleVioletRed}{[This is an example of a ``run-on sentence.'' Please look for sentences like this and split them up, like above $\rightarrow$]} \textcolor{OrangeRed}{So far, our discussion on the Borel transform was at the level of formal series, however there is a special class of formal series that behaves well under Borel transform, meaning that their Borel transform gives a germ of holomorphic functions at $\zeta=0$.} These formal series are the so-called $1$-Gevrey series:
-\[\tilde{\Phi}=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1\]
-is $1$-Gevrey if there exists $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\geq 0$.\footnote{In asymptotic analysis $k$-Gevrey series $\sum_{n\geq 0}a_nz^{-n}$ have coefficients that grow as $(n!)^{k}$, i.e.
-there exists $A>0$ such that $|a_n|\leq A^n (n!)^k$ for every $n\geq 0$.
-The Borel transform can be generalized in order to obtain germs of holomorphic function for higher Gevrey series.
-}
-\begin{lemma}
-Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
-\end{lemma}
 \color{black}
-Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (assuming they are series of $z$ on the fiber over $\zeta=0$), then following \cite[Definition 5.12]{diverg-resurg-i}, the convolution product $*$ of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
-\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-Furthermore, since $\tilde{\phi}$ and $\tilde{\psi}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is $\hat{\psi}\ast\hat{\phi}$ (see the discussion in Section~\ref{convolution}).
+%
+
   %It's not accidentely that we use the same symbol $*$ that denotes the convolution product to denote the product of two convergent series; indeed, as proved in , %the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
@@
 %
-\subsubsection{Analytic to formal \textcolor{LimeGreen}{[title suggestions?]}}
+\subsubsection{Analytic to formal}
 %
@@
 \color{black}
+
+%The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus in order to prove that $\borel_\zeta$ is an algebra homomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
+
+%Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
+%\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+%In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
+%\[
+ %   \series{\psi}\ast\series{\phi}=\int_0^{\zeta}d\zeta' \series{\psi}(\zeta-\zeta')\series{\phi}(\zeta').
+%\]
+%\begin{lemma}
+%The convolution product induces an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$.
+%\end{lemma}
+%\begin{proof}
+%    Let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
+%\begin{verify}
+ %   \begin{align*}
+  %      | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
+   %     &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
+    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+    %\end{align*}
+%\end{verify}
+%\end{proof}
+%We deduce that also the Laplace transform is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
+%\begin{prop}
+ %   Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
+Then the Laplace transform $\laplace_{\zeta,0}^\theta$ is $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
+%\end{prop}
+%\begin{proof}
+%First of all, from the properties of $\laplace_{\zeta,0}^\theta$ we know that if $\phi, \psi\in\singexp{\sigma}{\Lambda}(\Omega)$, then
+%\[\laplace_{\zeta,0}^\theta\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}^\theta\big[{\phi}\big]\laplace_{\zeta,0}^\theta\big[{\psi}\big],\]
+%see for instance \cite[Theorem 2.39]{laplace-tfm}.
+Then we should prove that $\delta$ is a unit: from its definition and the fact that $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we deduce that
+ %   \[
+%\laplace_{\zeta,0}^\theta\big[\delta\big]:=\laplace_{\zeta,0}^\theta\big[\borel_\zeta(1)\big]=1.
+ %   \]
+%Thus, $\delta$ behaves as a Dirac delta distribution acting on $\singexpalg{\sigma}(\Omega)$. Then, if ${\phi}\in\singexp{\sigma}{\Lambda}(\Omega)$
+  %   \begin{align*}
+%\big[\delta\ast\phi\big](p)&=\int_0^{\zeta(p)} \delta(\zeta(p)-\zeta)\phi(\zeta) \, d\zeta=\phi(p)
+ %   \end{align*}
+%\end{proof}
+%
+%
+\subsection{Action on fractional derivatives and fractional integrals}\label{sec:frac-diff-laplace}
+In this section, we will consider the action of $\borel_\zeta$ and $\laplace_{\zeta,0}$ with respect to the action of derivatives in both the frequency and position domains, as well as fractional integrals and derivatives $\fracderiv{\lambda}{\zeta}{0}$ in the position domain.
+This will be useful in Section~\ref{sec:examples}.
+
+In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}$ with $\sigma>-1$ and $\Lambda>0$. 
+\begin{definition}
+For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =\alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
+where $p$ is any point on the position domain $B$.%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
+% \begin{equation*}
+%     \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi \, d\zeta_\alpha.
+% \end{equation*}
+% }
+\end{definition}
+The fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0),
+\end{align*}
+and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[Equation 35]{mladenov2014advanced}.
+
+For $\mu \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\mu}{\zeta}{0}$ are defined by composing $\fracderiv{\mu-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
+However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ do not commute~\cite[equation 54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+We will use the {\em Riemann-Liouville} convention.
+\begin{definition}\label{definition:frac_driv}
+For $\mu \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\mu}{\zeta}{0}$ is defined by
+\[ \fracderiv{n+\mu}{\zeta}{0} \defeq \big(\tfrac{\partial}{\partial \zeta}\big)^{n+1} \fracderiv{\mu-1}{\zeta}{0}. \]
+\end{definition}
+The symbol $\fracderiv{\mu}{\zeta}{0}$ is now defined for any $\mu \in \R \smallsetminus \{0, 1, 2, 3, \ldots\}$.
+It denotes a fractional integral when $\mu$ is negative, and a fractional derivative when $\mu$ is a positive non-integer.
+
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+This extends the semigroup law:
+\begin{align*}
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\end{align*}
+\begin{prop}\label{prop:L-int-op}
+    Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
+    \begin{itemize}
+        \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
+         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
+        for every $\lambda\in\R_{<0}$;
+        \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
+Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
+         \item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
+        for every $n\in\Z_{\geq 0}$.
+    \end{itemize}
+\end{prop}
+\begin{proof}
+%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
+%\begin{align*}
+ %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
+  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
+   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
+%\end{align*}
+
+   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
+    \begin{align*}
+        z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
+        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
+        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
+        &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
+        \end{align*}
+        The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
+\begin{align*}
+    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
+    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
+    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
+\end{align*}
+     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
+        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
+Similarly, one can prove \emph{iii)}.
+\end{proof}
+\begin{lemma}\label{lem:frac-deriv-Borel}
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta } \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]. \]
+\end{lemma}
+\begin{proof}
+We will show that for any $\mu \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+\begin{align*}
+\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta')^{-\mu} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+& = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\mu-1)}}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\mu} t^k\,dt \\
+& = \frac{\zeta^{k-(\mu-1)}}{\Gamma\big(k-(\mu-1)+1\big)}
+\end{align*}
+by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
+\begin{equation}\label{frac-diff-laplace}
+\big(\tfrac{\partial}{\partial \zeta}\big)^{n+1}\,\partial^{\mu-1}_{\zeta } \borel_\zeta \big[z^{-(k+1)}\big] = \frac{\zeta^{k-(n+\mu)}}{\Gamma\big(k-(n+\mu)+1\big)}
+\end{equation}
+for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
+\begin{align*}
+\tfrac{\partial}{\partial \zeta} \big(\tfrac{\partial}{\partial \zeta}\big)^{m+1}\,\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\mu)}}{\big(k-(m+\mu)\big)\,\Gamma\big(k-(m+\mu)\big)} \right) \\
+& = \frac{\zeta^{k-(m+1+\mu)}}{\Gamma\big(k-(m+\mu)\big)}
+\end{align*}
+Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
+The condition $\mu \in (0, 1)$ saves us from the trouble we would run into if $k-(m+\mu)$ were in $\Z_{\le 0}$.
+This is how we avoid the initial value corrections that appear in ordinary derivatives of Borel transforms.
+\end{proof}
+We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
+\begin{prop}\label{prop:frac-der-int-borel}
+Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
+\begin{itemize}
+\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
+\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
+\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
+\end{itemize} 
+\end{prop}
+\begin{proof} 
+The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
+
+Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
+\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
+Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
+\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\fracderiv{\lambda}{\zeta}{0}\series{\Phi}\]
+where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
+
+Finally, $(iii)$ follows from a simple computation: 
+\begin{align*}
+\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
+&=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
+&=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
+&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
+\end{align*}
+\end{proof}
+% \begin{remark}
+% We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\lambda\in\R\setminus\Z_{>0}$ 
+% \[\fracderiv{\lambda}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\borel_\zeta (z^\lambda)\ast \borel_\zeta\tilde{\Phi}.\]
+% \begin{verify}
+% \begin{align*}
+% \fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
+% &=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
+% &=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
+% &=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
+% \end{align*}
+% Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
+% $\tau>0$ and $\tau\notin\Z_{>0}$, 
+% \[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
+% \]
+% and if $\tau<0$, by definition 
+% \[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
+% therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
+% \end{verify}
+% \end{remark}
+\color{RoyalBlue}
+We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ as convolution product.
+\begin{lemma}
+    Let us assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and $z$ to be a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
+    \[\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
+\end{lemma}
+\begin{proof}
+    First of all, notice that 
+    \begin{align*}
+    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi%=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi
+\end{align*}
+where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
+Then, by definition of fractional integral $\partial_{\zeta,\alpha}^{-\lambda}\phi$, we have
+\begin{align*}
+    \Big[\partial_{\zeta,\alpha}^{-\lambda}\phi\Big](p)=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi\, d\zeta=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p \mathsf{R}^{*}\zeta^{\lambda-1}\phi\, d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi\,.
+\end{align*}
+\end{proof}
+\begin{remark}
+
+\end{remark}
+% We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
+% \begin{align*}
+%     \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi%=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi
+% \end{align*}
+% where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
+Then, by definition of fractional integral $\partial_{\zeta,\alpha}^{-\lambda}\phi$, we have
+% \begin{align*}
+%     \borel_\zeta(z^{-\lambda}{\Phi})(p)=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi\, d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi\,.
+% \end{align*}
+% Hence \[\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
+% %However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
+% Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
+For every $\lambda\in (-1,\infty)$
+% \begin{multline*}
+%     \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
+%     =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
+% \end{multline*}
+% hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
+%
+%
+%
+\color{black}
 \section{Proof of main results}\label{sec:proof_main_results}
+%
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-In Section~\ref{sec:regularity-results}, we will prove Borel regularity of the solutions of a certain class of linear level-$1$ ODEs.
-Then, in Section~\ref{sec:new-summability-proof}, we will give a new proof of Borel summability of the Poincar\'e frame of solutions.
-\textcolor{Pink}{[Flavor text added; check over]}
+\color{NavyBlue}
+\textcolor{PaleVioletRed}{[Revised flavor text.]}
+In Section~\ref{sec:regularity-results}, we show that linear level~1 ODEs of a certain form always have Borel regular solutions, indexed by the characteristic roots of their constant-coefficient parts.
+These solutions turn out to be asymptotic to the formal series solutions found by Poincar\'{e}.
+
+In Section~\ref{sec:new-summability-proof}, we will look at the same class of ODEs from a more formal perspective, starting from the assumption that Poincar\'{e}'s solutions exist and are $1$-Gevrey.
+Using the existence and uniqueness results that characterize the Borel regular solutions, we give a new proof that Poincar\'{e}'s solutions are Borel summable.
+\color{black}
 \subsubsection{Regularity results}\label{sec:regularity-results}
-Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form
-%%\footnote{We follow Delabaere, rather than \'{E}calle, in only going on up to degree $d-1$; see \cite[Footnote~1 in Section 5.2.2.1]{diverg-resurg-iii}}
+Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
+Let $\mathcal{P}$ be a linear differential operator of the form \textcolor{PaleVioletRed}{[I just noticed we use $\partial_z$ instead of $\tfrac{\partial}{\partial z}$ in \texttt{reg-sing-volterra}, where these equations were copied from.
+Could we switch to $\tfrac{\partial}{\partial z}$, as I've done provisionally?]}
 \begin{equation}\label{eqn:operator-P}
-    \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}),
+\mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}),
 \end{equation}
@@
 \item $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
-\item $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
+\item $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$;
 \item $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
@@
 %%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
-\textcolor{orange}{[Transition text]}
+\textcolor{orange}{[Introduce $\hat{\mathcal{P}}_\alpha$?]} \textcolor{orange}{[Transition text]}
 %%%\begin{itemize}
@@
 Choose a root $-\alpha$ of $P$.
-Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
@@
 \subsubsection{A new proof of the Borel summability of the Poincar\'{e} solutions}\label{sec:new-summability-proof}
-%\textcolor{orange}{[Mention that this is a component of the earlier Borel regularity proof.]}
+%
+In~\cite{int-irreg}, Poincar\'{e} described a formal way to solve the equation $\mathcal{P}\series{\Phi} = 0$ for an operator of the form~\eqref{eqn:operator-P}.
+Choose a root $-\alpha$ of $P$, set $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$.
+Once the leading coefficient of $\series{\Psi}_\alpha$ is chosen, the rest of the coefficients are determined, and can be found order by order.
+The Ramis Index Theorem guarantees that $\series{\Psi}_\alpha$ will be $1$-Gevrey~\cite{ramis_index}.
+
+We have come this far in our discussion of Poincar\'{e}'s method through formal reasoning in the frequency domain.
+From here, there are various ways to show that $\series{\Psi}_\alpha$ is Borel summable.
+We do it by using Theorem~4 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
+\begin{theorem}
+Choose a root $-\alpha$ of $P$.
+Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
+If a $1$-Gevrey trans-monomial \textcolor{orange}{[define]} $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
+\end{theorem}
+\begin{proof}
+By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator described in Equation~\textcolor{magenta}{\textbf{(?)}}.
+By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$.
+Since the integrals in $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha$ converge absolutely, $\hat{\psi}_\alpha$ satisfies the same equation that its Taylor series does: $\hat{\mathcal{P}}_\alpha \hat{\psi}_\alpha = 0$.
+
+Since the series $\series{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \C\{\zeta\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
+Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
+We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match.
+This means, in particular, that $\hat{\psi}_\alpha$ can be analytically continued throughout $\Omega_\alpha$, and it is uniformly of exponential type on that sector.
+Thus, $\hat{\psi}_\alpha$ has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, meaning that $\series{\Psi}_\alpha$ is Borel summable along any such ray.
+Recalling how the solution $\Psi_\alpha$ was constructed in Theorem~\ref{re:thm:exist_uniq_ODE}, we see that the Borel sum of $\series{\Psi}_\alpha$ is $c\Psi_\alpha$.
+\end{proof}
+\par\color{RoyalBlue}
 Given a differential operator $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
@@
 
-\begin{figure}[ht]
-    \centering
-    %\includegraphics{figures/u_contour_3.pdf}
-    \includegraphics[scale=0.3]{figures/thimble_Airy.png}
-    \caption{\small In this picture of the $u$ plane, the light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively.
-The light path is the contour $\mathcal{C}_1$.
-More generally, the dark blue contour corresponds to the preimage of the ray $+1+e^{i\theta}\infty$ and $\theta=$.
-While the light blue contour corresponds to the preimage of the ray $-1+e^{i\theta}\infty$.
-The shadowed region is the preimage of the region where $\Re(\zeta) > 3.897\ldots$.
-\textcolor{orange}{[for Aaron: could you please add the correct constant in the description of the figure, and explain what are the different colored regions?
-Thanks]}} \textcolor{BlueViolet}{[Right now, the program chooses the constant to be $\tfrac{3}{4} n^{3/2}$, so it's about $3.897$ in this picture.
-If you want to put something concrete, I could redraw the picture so that it's $4$.]}
-    \label{fig:path_Airy}
-\end{figure}
-
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du. \]
-where $\mathcal{C}^\theta_1$ is the preimage under \textcolor{orange}{[\ldots]} \textcolor{RoyalBlue}{We have rescaled the contour by a factor of two, but it still approaches $\infty$ in the desired way.
-Note that $4u^3 - 3u$ is the third Chebyshev polynomial.}
-
-By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}, so we’ll go straight to the general case.
-However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be useful to see it on its own.
-For this reason, in Appendix~\ref{airy-appendix} we give a detailed treatment of the Airy function, specializing the general argument of all Airy-Lucas functions.
+\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
+where $\mathcal{C}^\theta_1$ is the contour that passes through the point $u = \tfrac{1}{2}$ and projects to the ray $\mathcal{J}^\theta_{\zeta, 1}$ under the mapping $-\zeta = 4u^3 - 3u$.
+\begin{center}
+\includegraphics[width=10cm]{figures/thimble_Airy.png}
+\captionof{figure}{These pictures of the $u$ and $\zeta$ planes show the contour $\mathcal{C}^{\pi/8}_1$ and its projection $\mathcal{J}^{\pi/8}_{\zeta, 1}$.
+\textcolor{orange}{[Add $\zeta$ plane picture.]} The light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively.
+The region $\Re(\zeta) > 4$ is shaded and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
+\end{center}
+
+Note that $4u^3 - 3u$ is the third Chebyshev polynomial.
+By considering other Chebyshev polynomials, we can situate the Airy function within the family of {\em Airy-Lucas functions}.
+Treating these functions as a family adds more insight than complexity, so we will go straight to the general case.
+However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be worth seeing on its own.
+In Appendix~\ref{airy-appendix}, we give a detailed treatment of the Airy function, specializing our arguments from the general case.
 
@@
 \end{equation}
-with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
-where $\mathcal{C}^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$. %%(see Figure \ref{fig:thimble_n_5}).
-By definition, $\mathcal{C}^\theta_j$ is a preimage of the ray $\mathcal{J}^\theta_{\mp 1}$ under the function $-T_n(u)$.
-The ray starts at the critical value $-1$ when $j$ is even, and $1$ when $j$ is odd.
+with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions, indexed by $j \in \{1, \ldots, n-1\}$, are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+where $\mathcal{C}^\theta_j$ is the contour that passes through the point $u = \cos\big(\tfrac{j}{n}\pi\big)$ and projects to the ray $\mathcal{J}^\theta_{\zeta, \pm 1}$ under the mapping $-\zeta = T_n(u)$.
+\textcolor{RoyalBlue}{where $\mathcal{C}^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$.
+By definition, $\mathcal{C}^\theta_j$ is a preimage of the ray $\mathcal{J}^\theta_{\mp 1}$ under the function $-T_n(u)$.} The ray starts at the critical value $1$ when $j$ is odd, and $-1$ when $j$ is even.
 \begin{center}
-\includegraphics[width=10cm]{figures/thimbles-n5.png} \\[1em]
-{\small Integration contour $\mathcal{C}^{(j)}$ for the Airy--Lucas function with $n=5$.
-The dark blue contours correspond to the preimage of the ray $1+e^{i\theta}\infty$ and $\theta=\textcolor{magenta}{???}$.
-The light blue contours correspond to the preimage of the ray $-1+e^{i\theta}\infty$.}
+\includegraphics[width=10cm]{figures/thimbles-n5.png}
+\captionof{figure}{The integration contours $\mathcal{C}^{\pi/8}_1, \ldots, \mathcal{C}^{\pi/8}_4$ for the Airy--Lucas functions with $n=5$.
+The dark and light thimbles are the preimages of the rays $\mathcal{J}^{\pi/8}_{\zeta, 1}$ and $\mathcal{J}^{\pi/8}_{\zeta, -1}$, respectively.}\label{fig:thimble_n_5}
 \end{center}
-\begin{figure}[ht]
-    \centering
-   \includegraphics[width=10cm]{figures/thimbles-n5.png}
-    \caption{Integration contours $\mathcal{C}^\theta_j$ for the Airy--Lucas functions with $n=5$.
-The dark and light thimbles are the preimages of the rays $\mathcal{J}^{\pi/8}_{\zeta, 1}$ and $\mathcal{J}^{\pi/8}_{\zeta, -1}$, respectively.
-\textcolor{orange}{[Preferred version, with ``Figure'' label]}}
-    \label{fig:thimble_n_5}
-\end{figure}
-
 \subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}1 & j \text{ even} \\ i & j \text{ odd}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
 where
@@
 This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.
-Although we’ll not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
+Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
 The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
@@
 \end{itemize}
-On the other hand, the thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we’ll discuss in the following Section~\ref{countable-cover}.
+On the other hand, the thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
 
@@
 In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
-%In both cases, we’ll compute the differential equation satisfied by $I$.
+%In both cases, we will compute the differential equation satisfied by $I$.
 
@@
 We are going to look for functions $v_j$ whose Laplace transforms $\laplace_{\zeta, \alpha_j} v_j$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We’ll succeed when $\alpha^2 - 1 = 0$, and we’ll see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+We’ll succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
 
@@
 \[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we’ll see this approach succeed.
+In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
 For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
@@
 \end{align*} 
-are formal solutions of the Airy equation. Notice that compared to Marino's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
+are formal solutions of the Airy equation. Notice that compared to Mari\~{n}o's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
 
@@
 %We will say a function is {\em slight} at $\zeta = 0$ if it can be written as
-%\begin{equation}\label{eqn:slight-defn}
+%\begin{equation}\label{eqn:slight-definition}
 %\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
@@
 
-%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-defn}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
+%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-definition}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
 The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.

### 2024-04-01 exp-resurgence.tex
Set end zone thresholds to integer values
Also, update Airy contour picture.

@@
 \begin{center}
-\includegraphics[width=6.5cm]{figures/rays.png}
+\includegraphics[width=6.5cm]{figures/rays_ge6.png}
 \hspace{0.5cm}
@@
 \begin{center}
-\includegraphics[width=10cm]{figures/thimble_Airy.png}
-\captionof{figure}{These pictures of the $u$ and $\zeta$ planes show the contour $\mathcal{C}^{\pi/8}_1$ and its projection $\mathcal{J}^{\pi/8}_{\zeta, 1}$.
-\textcolor{orange}{[Add $\zeta$ plane picture.]} The light and dark checks are the preimages of the upper and lower halves of the $\zeta$ plane, respectively.
-The region $\Re(\zeta) > 4$ is shaded and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
+\includegraphics[width=6.5cm]{figures/ray_1_ge3.png}
+\hspace{0.5cm}
+\includegraphics[width=6.5cm]{figures/thimble-n3_1.png}
+\captionof{figure}{The ray $\mathcal{J}^{\pi/8}_{\zeta, 1}$ in the $\zeta$ plane and its preimage $\mathcal{C}^{\pi/8}_1$ in the $u$ plane.
+The upper and lower halves of the $\zeta$ plane are colored light and dark, so their preimages form a checker pattern on the $u$ plane.
+The region $\Re(\zeta) > 3$ and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
 \end{center}

### 2024-04-02 exp-resurgence.tex
Redo order shifting section for functions with shifted Laurent expansions
This argument seems less subtle than the one for L^infinity functions, and it's
strong enough for our purposes, because we can show that the solutions we want
have shifted Laurent expansions.

@@
 \newcommand{\borel}{\mathcal{B}}
-\newcommand{\aexp}{\text{\ae}}
+\newcommand{\aexp}{\mathrm{\ae}}
 \newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
@@
 \item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
+equation~\eqref{eqn:bessel_rescaled_ex} is an example.
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form \textcolor{PaleVioletRed}{[I just noticed we use $\partial_z$ instead of $\tfrac{\partial}{\partial z}$ in \texttt{reg-sing-volterra}, where these equations were copied from.
@@
 
-The form of $\mathcal{P}$ derives from Equation~2.2.3 of \cite[pag.
+The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[pag.
 105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
@@
 \begin{theorem}\label{thm:maxim}
-If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: 
+If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: \textcolor{magenta}{[change restatement to match]}
 \begin{enumerate}
-\item\label{part-1} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-Recall that $\theta$ is the direction of the ray $\mathcal{J}^\theta_\alpha$.
-\item\label{part-2} The series $\tilde{I}_\alpha$ \textcolor{LimeGreen}{[is $1$-Gevrey]}. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
+\item\label{part-1} The function $I_\alpha$ has an asymptotic expansion $\series{I}_\alpha \defeq \aexp^\theta I_\alpha$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
+\item\label{part-2} The Borel transform $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3} The sum of $\tilde{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.
 \end{enumerate}
@@
 In Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
-Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent fiber $T^*_{\zeta = 0} B$.
-At a conical singularity of $B$, which cannot lie in the domain of a translation chart, the frequency domain has a more interesting shape, illustrated in Figure \ref{fig:different_fibres}.
+Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$.
+The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$.
 \begin{center}
 \phaseSpaceLaplace
-\captionof{figure}{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane.
-However, the fiber over a singular point of $B$ has an interesting structure.
-Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}\label{fig:different_fibres}
+\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point.
+The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
 \end{center}
@@
 The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
-In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
+In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
 
@@
 %\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[Equation~2.2.3, p.~105]{EcalleIII} covers operators like
+%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[equation~2.2.3, p.~105]{EcalleIII} covers operators like
 %\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
@@
 %
-\subsection{Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
+\subsection{The Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
 We begin this section introducing some notation.
@@
 On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
-\subsubsection*{Laplace transform as algebra homomorphism}
+\subsubsection*{The Laplace transform as algebra homomorphism}
 The Laplace transform $\laplace_{\zeta,\alpha}$ is defined on the space of holomorphic functions in the position domain, integrable at $\zeta=\alpha$ and exponentially bounded at infinity.
@@
 \begin{prop}
-    The $\laplace_{\zeta,\alpha}$ is an algebra homomorphims from the space of holomorphic functions integrable at zero and exponentially bounded at infinity, endowed with the convolution product, to the space of analytic function on the half-plane $\{\Re(z)>0\}$.
+The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphim from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.
 \end{prop}
@@
 \begin{remark}
-   Notice that for $\alpha=0$, the definition of convolution in Equation~\eqref{eq:convolution_def} agrees with the standard deifinition (see \cite[Definition~5.12]{diverg-resurg-i}).
+   Notice that for $\alpha=0$, the definition of convolution in equation~\eqref{eq:convolution_def} agrees with the standard deifinition (see \cite[Definition~5.12]{diverg-resurg-i}).
 In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast$, following the standard convention.   
@@
 
-\subsubsection*{Borel transform as algebra isomomrphism}
+\subsubsection*{The Borel transform as algebra isomomrphism}
 The Borel transform $\borel_\zeta$ is defined on the space of formal power series $z^{-1}\C\llbracket z^{-1}\rrbracket$, which is a $\C$-algebra, with product given by the Cauchy product of formal power series.
@@
 \begin{definition}\label{def:convolution_formal}
-    Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then 
+For any integers $m, n$%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then 
+\begin{equation}
+\frac{\zeta^m}{m!} \ast_{\zeta, 0} \frac{\zeta^n}{n!} \defeq \frac{\zeta^{m+n+1}}{(m+n+1)!} 
+\end{equation}
+\textcolor{LimeGreen}{This extends to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$ by countable linearity:}
+\begin{verify}
+\begin{align*}
+\frac{\zeta^m}{m!} \ast \frac{\zeta^n}{n} & = \borel_\zeta \left[ \laplace_{\zeta, 0}\left(\frac{\zeta^m}{m!}\right) \laplace_{\zeta, 0} \left(\frac{\zeta^n}{n!}\right) \right] \\
+& = \borel_\zeta[z^{-m-n-2}] \\
+\end{align*}
+\end{verify}
+\color{RoyalBlue}
 \begin{equation}\label{eq: formal_convolution}
@@
 with $c_n=\sum_{j=0}^n a_j b_{n-j}$.
+\color{black}
 \end{definition}
-Notice that the right hand side of Equation~\eqref{eq: formal_convolution} is the Borel transform of the Cauchy product of the formal series $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, namely if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
+Notice that the right hand side of equation~\eqref{eq: formal_convolution} is the Borel transform of the Cauchy product of the formal series $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, namely if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
  \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
@@
 \begin{remark}
-   If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in Equation~\eqref{eq:convolution_def}.
+   If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in equation~\eqref{eq:convolution_def}.
 We will discuss it in Section~\ref{sec:Borel-gevrey}.
@@
 
-In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}$ with $\sigma>-1$ and $\Lambda>0$. 
+In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}$ \textcolor{magenta}{[needs domain]} with $\sigma>-1$ and $\Lambda>0$.
 \begin{definition}
@@
 
-The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}=\text{Id}$ for all $\lambda \in (0, \infty)$.
+The Riemann-Liouville fractional derivative is a left inverse of the fractional integral, in the sense that $\fracderiv{\lambda}{\zeta}{ 0}\,\fracderiv{-\lambda}{\zeta}{0}$ is the identity for all $\lambda \in (0, \infty)$.
 This extends the semigroup law:
@@
 \end{align*}
+\color{DarkTurquoise}
+\begin{prop}\label{prop:deriv-cont}
+Suppose $\Omega$ contains an open subset $\Omega'$ on which $|\zeta| \lesssim \Delta$, where $\Delta$ is the distance to the boundary of $\Omega$.\footnote{This happens, for instance, when $\Omega$ and $\Omega'$ are sectors, and $\Omega$ contains the closure of $\Omega'$.} The derivative operator $\big(\tfrac{\partial}{\partial \zeta}\big)^n$, for $n \in \Z_{\ge 1}$ then gives a continuous map
+\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma-1}{\Lambda}(\Omega') \]
+for all $\sigma > -1$ and $\Lambda \in \R$.
+\end{prop}
+\begin{proof}
+Choose a constant $M$ for which $|\zeta| \le M\Delta$. Since $\Omega$ does not contain $\zeta = 0$, we know that $\Delta \le |\zeta|$ as well.
+
+Take some $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$, and let $\omega \defeq \big(\tfrac{\partial}{\partial \zeta}\big)^n \phi$.
+At any $a \in \Omega'$, applying Cauchy's inequality on a disk of radius $\Delta(a)/2$ tells us that
+\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} |\phi|, \]
+where $D_r(a)$ is the closed disk of radius $r$ around $a$. The definition of the norm on $\singexp{\sigma}{\Lambda}(\Omega)$ gives the bound
+\[ |\phi| \le |\zeta|^\sigma e^{\Lambda|\zeta|}\,\|\phi\|_{\sigma, \Lambda}, \]
+which we can plug into Cauchy's inequality to see that
+\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} \left(|\zeta|^\sigma e^{\Lambda|\zeta|}\,\|\phi\|_{\sigma, \Lambda}\right). \]
+Since $\Omega$ does not contain $\zeta = 0$, we know that $|\zeta| \le \Delta$, implying that
+\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} \left(|\Delta|^\sigma e^{\Lambda|\Delta|}\,\|\phi\|_{\sigma, \Lambda}\right). \]
+\end{proof}
+\color{black}
+\begin{prop}
+\end{prop}
 \begin{prop}\label{prop:L-int-op}
@@
 \item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
-         \item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$,
-        for every $\lambda\in\R_{<0}$;
+\item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$ for every $\lambda\in\R_{<0}$;
 \item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
@@
 \end{proof}
-\color{RoyalBlue}
 \textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
 Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
-\color{DarkBlue}
 \textcolor{orange}{[Add flavor text]}
@@
 of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
-Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4 of \cite{reg-sing-volterra}.
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
@@
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-In \cite{reg-sing-volterra}, to prove Theorem~4, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of Theorem~3.
+To prove Theorem~4 in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~3]{reg-sing-volterra}.
 The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
@@
 \end{equation}
-The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$ \textcolor{orange}{[check]}, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
+The central idea of the proof is to show that $\softpart^\alpha$ maps $\solproto$, and in fact all of $\singexpalg{\tau_\alpha - 1}(\Upsilon)$, into $\singexpalg{\tau_\alpha}(\Upsilon)$, and that $\volterra^\alpha$ is a contraction of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ when $\Lambda$ is large enough.
 It follows, by the contraction mapping theorem, that equation~\eqref{eqn:inhomog-volterra} has a unique solution $\solptb$ in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
@@
 \end{align*}
-we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution.
+we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution $f_*$.
 
@@
 It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-The solution $\solptb$ of equation~\eqref{eqn:inhomog-volterra} that this sequence converges to therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
+The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
 Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.
@@
 We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
-By definition \textcolor{orange}{[to be added to the paper]}, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
+By definition, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
 
@@
 \textcolor{orange}{[Add flavor text]}
-\color{black}
 \begin{theorem}[restatement of \ref{thm:soln_is_asymptotic}]\label{re:thm:soln_is_asymptotic}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
+\textcolor{magenta}{[revise organiztion to match intro]} The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
 \end{theorem}
@@
 We do it by using Theorem~4 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
-\begin{theorem}
+\begin{theorem}\label{thm:summability_ODE}
 Choose a root $-\alpha$ of $P$.
@@
 \begin{proof}
-By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator described in Equation~\textcolor{magenta}{\textbf{(?)}}.
+By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator described in equation~\textcolor{magenta}{\textbf{(?)}}.
 By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$.
@@
 \par\color{RoyalBlue}
-Given a differential operator $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
+Given a differential operator $\mathcal{P}$ as in equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
 \begin{equation}
@@
 If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly:
+\textcolor{orange}{[Change statement as in Intoduction]}
 \begin{enumerate}
-\item\label{part-1-prf} The function $I_\alpha$ is asymptotic, as $\Re (e^{-i\theta} z) \to \infty$, to a trans-monomial $\tilde{I}_\alpha\in e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-\item\label{part-2-prf} The series $\tilde{I}_\alpha$ is $1$-Gevrey. In other words, $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-1-prf} The function $I_\alpha$ has an asymptotic expansion $\series{I}_\alpha \defeq \aexp^\theta I_\alpha$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_\alpha$ that defines the thimble.
+\item\label{part-2-prf} The Borel transform $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
 \item\label{part-3-prf} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
@@
 which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
-We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
+%We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
 
@@
 %%[DROPPED] In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
-Let us put Equation~\eqref{eqn:mod-bessel-AL} in the form $\mathcal{P}\Phi=0$ with $\mathcal{P}$ as in Equation~\eqref{eqn:operator-P}:
+Let us put equation~\eqref{eqn:mod-bessel-AL} in the form $\mathcal{P}\Phi=0$ with $\mathcal{P}$ as in equation~\eqref{eqn:operator-P}:
 \begin{equation}\label{eqn:reg-mod-bessel-AL}
@@
 
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$ and $\tau_\alpha=1/2$.
+From the general theory of ODEs of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+where $\tau_\alpha = 1/2$, and the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
 From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n}(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp-AL}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{2}-\tfrac{m}{n})_1 (\tfrac{1}{2}+\frac{m}{n})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{2}-\tfrac{m}{n})_2 (\tfrac{1}{2}+\tfrac{m}{n})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{2}+\tfrac{m}{n})_3 (\tfrac{1}{2}+\tfrac{m}{n})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
+\series{W}_1 = 1 - \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_1 \left(\tfrac{1}{2}+\frac{m}{n}\right)_1}{2^1 \cdot 1!}\;z^{-1} + \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_2 \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_2}{2^2 \cdot 2!}\;z^{-2} - \frac{\left(\tfrac{1}{2}+\tfrac{m}{n}\right)_3 \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
 \end{equation}
@@
 Borel summation makes the analogy precise.
-We’ll see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is evidence of Theorem~4 from \cite{reg-sing-volterra}.
+We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
 %\subsection{Going to the spatial domain}\label{spatial-AL}
@@
 
-By the properties of the Laplace transform (we refer to Proposition~\ref{prop:L-int-op}), $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
+By the properties of the Laplace transform laid out in Proposition~\ref{prop:L-int-op}, a function $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
 \begin{equation}\label{int-eq:spatial-mod-bessel-AL}
@@
 \end{equation}
-It's tempting to differentiate both sides of this equation until we get
+It is tempting to differentiate both sides of this equation until we get
 \begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
@@
 Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_j)$, for some $\sigma\in (-1, 0)$.
+However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_\alpha)$, for some $\sigma\in (-1, 0)$.
 
@@
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+for $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
 We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
@@
 \end{align*}
-where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
-\begin{center}
-\textcolor{orange}{[Draw the thimble in the $u$ plane]}
-\end{center}
-
-\color{DarkTurquoise}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}
+
+\color{NavyBlue}
 Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
@@
 The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
-\begin{center}
-\textcolor{orange}{[Draw the lifted thimble in the $\phi$ plane]}
-\end{center}
+\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
+
 We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
@@
 Because $\cosh(t)$ is periodic, $j$ only affects the integral through its parity.
-\begin{figure}[ht]
-    \centering
+\begin{center}
 \includegraphics[width=10cm]{figures/bessel-unrolled.png}
-    \caption{The paths $\mathcal{C}_j$.}
-    \label{fig:bessel_unrolled}
-\end{figure}
+\captionof{figure}{The paths $\mathcal{C}^{\pi/8}_j$ in the $t$ plane.}\label{fig:bessel_unrolled}
+\end{center}
 
@@
 \subsection{Generalized Airy}
-\color{NavyBlue}
 In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
@@
   };
-  \fill (1.25, 0) circle (\dotsize) node[anchor=north west] {$1$};
+  \fill (1.25, 0) circle (\dotsize) node[anchor=north west] {$\tfrac{1}{2}$};
   \draw[fill=white, thin] circle (\dotsize);
@@
   };
-  \fill (-1.25, 0) circle (\dotsize) node[anchor=north east] {$1$};
+  \fill (-1.25, 0) circle (\dotsize) node[anchor=north east] {$-\tfrac{1}{2}$};
 \end{scope}
 \end{tikzpicture}
-\caption{The integration contours in the $t$ plane that define $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$.
-\textcolor{orange}{[Why are $y = \pm 1$ marked?
-Should we mark the critical points $\pm\tfrac{1}{2}$ instead?]}}\label{fig:path-generalized-Airy}
+\caption{The integration contours in the $t$ plane that define $\mathrm{A}_k,\mathrm{B}_0,\mathrm{B}_k$.}\label{fig:path-generalized-Airy}
 \end{figure}
@@
 Since equation~\eqref{eqn:I} is third-order, we need one more Borel regular solution to make a frame.
-We choose the constant solution $1$, which can be seen as the Laplace transform of the formal convolution unit $\delta$ introduced in Section~\ref{convolution}.
+We choose the constant solution $1$, which can be seen as the Laplace transform of the formal convolution unit $\delta$ introduced in Section~\ref{sec:borel-laplace-homom}.
 Interestingly, $1$ is actually the generalized Airy function $\mathrm{B}_0(z,1)$.
+%
+\begin{todo}
+\subsubsection{Thimble projection formula}
+In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
 \color{black}
-%
-\color{RoyalBlue}
-\subsubsection{Thimble projection formula}
-\textcolor{magenta}{[Are we hoping to fill this in later?
-We can hide it in a to-do comment, if so]} In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
-\color{black}
+\end{todo}
 \subsection{Third-order thimble integrals}
@@
 \subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
-Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
+\textcolor{orange}{[Convert to new version]} Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
 Projecting $z^{-1/3} \mathcal{C}_1$ to a contour \textcolor{magenta}{[rephrase in terms of ray]} $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \mathcal{C}_1$, we have
@@
 
-In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula Equation~\eqref{eqn:formula-proof} using trigonometric substitution.
+In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula equation~\eqref{eqn:formula-proof} using trigonometric substitution.
 As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
@@
 \end{align*}
-\subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
-\textcolor{orange}{[Add link to general references in intro].} Resurgent functions in the position domain are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}\{For definition in the position domain, cite \S 6.1 of Mitschi and Sauzin~\cite{diverg-resurg-i}\}}.
+% \subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
+% \textcolor{orange}{[Add link to general references in intro].} Resurgent functions in the position domain are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}\{For definition in the position domain, cite \S 6.1 of Mitschi and Sauzin~\cite{diverg-resurg-i}\}}.
 \textcolor{MediumSeaGreen}{[Focus on endlessly continuable functions instead?
@@
 
-\textcolor{Maroon}{[\ldots] resurgent function with the property that at each singularity $\omega$, we have an expansion of the form}
-\begin{align*}
-    \hat{\phi} = \frac{C_\omega}{\zeta_\omega}+\frac{S_\omega}{2\pi i} \log(\zeta_\omega)\,\series{\phi}_\omega + \text{ hol. funct.} \textcolor{Maroon}{[\text{convergent series in}\,\zeta_\omega]}
-\end{align*}
-where \textcolor{Maroon}{$\zeta = \omega + \zeta_\omega$, $\series{\phi}_\omega$ is a series in $\zeta_\omega$} $C_\omega, S_\omega$ are constants and $S_\omega$ is typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
+% \textcolor{Maroon}{[\ldots] resurgent function with the property that at each singularity $\omega$, we have an expansion of the form}
+% \begin{align*}
+%     \hat{\phi} = \frac{C_\omega}{\zeta_\omega}+\frac{S_\omega}{2\pi i} \log(\zeta_\omega)\,\series{\phi}_\omega + \text{ hol. funct.} \textcolor{Maroon}{[\text{convergent series in}\,\zeta_\omega]}
+% \end{align*}
+% where \textcolor{Maroon}{$\zeta = \omega + \zeta_\omega$, $\series{\phi}_\omega$ is a series in $\zeta_\omega$} $C_\omega, S_\omega$ are constants and $S_\omega$ is typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
 The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
-%The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$
-
-Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in Equation~\eqref{eqn:formula-proof} are resurgent.
+% %The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$
+
+% Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation~\eqref{eqn:formula-proof} are resurgent.
 Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.
@@
 For example, for the Airy function, we can expand $\hat{\phi}_1$ near $\zeta=-1$:
-\begin{align*}
-    \hat{\phi}_1(\zeta-1)=\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1+\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2+\frac{7436429}{53747712}\zeta^3+\ldots\right)  +\text{ hol.
+% \begin{align*}
+%     \hat{\phi}_1(\zeta-1)=\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1+\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2+\frac{7436429}{53747712}\zeta^3+\ldots\right)  +\text{ hol.
 funct.
 }
-\end{align*}
-
-Notice that $(1+\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2+\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin.
+% \end{align*}
+
+% Notice that $(1+\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2+\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin.
 So we see that expanding $\hat{\phi}_1$ at the singularity we see the germ of another singularity $\series{\phi}_{-1}$.
 Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
-\begin{align*}
-    \hat{\phi}_{-1}(\zeta+1)=-\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1-\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2-\frac{7436429}{53747712}\zeta^3+\ldots\right) +\text{ hol.
+% \begin{align*}
+%     \hat{\phi}_{-1}(\zeta+1)=-\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1-\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2-\frac{7436429}{53747712}\zeta^3+\ldots\right) +\text{ hol.
 funct.
 }
-\end{align*}
-where the germ $(1-\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2-\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin. 
-From these expressions, we also noticed that $\hat{\phi}_i$ are simple resurgent functions.   
+% \end{align*}
+% where the germ $(1-\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2-\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin. 
+% From these expressions, we also noticed that $\hat{\phi}_i$ are simple resurgent functions.   
 %
@@
 %%\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
-\textcolor{red}{Shall we review the content of \cite{reg-sing-volterra}?}
+\begin{todo}[Shall we review the content of \cite{reg-sing-volterra}?]\end{todo}
+\begin{todo}
 \subsection{Passing between the analytic world and the formal world}
-\textcolor{orange}{Show that the Taylor expansion of an analytic solution of an integral equation satisfies the same equation (or just cite the statement in Erdelyi).
-Cite the theorem of Erdelyi which shows that a solution of a differential equation (under certain conditions) has an asymptotic expansion, which satisfies the corresponding differential equation.}
-\subsection{Order shifting}\label{shifting}
-Consider holomorphic functions on a simply connected open domain $\Omega$ that touches but doesn't contain $\zeta = 0$.
-%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point.
-%We will say a function is {\em slight} at $\zeta = 0$ if it can be written as
+[Show that the Taylor expansion of an analytic solution of an integral equation satisfies the same equation (or just cite the statement in Erdelyi).
+Cite the theorem of Erdelyi which shows that a solution of a differential equation (under certain conditions) has an asymptotic expansion, which satisfies the corresponding differential equation.]
+\end{todo}
+\subsection{Order shifting for integro-differential equations}\label{shifting}
+Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
+As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.
+
+To make this statement precise, we need some terminology.
+For any $\sigma \in \R$, let us say that the {\em order} of a function in $\zeta^\sigma \mathcal{O}(\pi \Upsilon)$ is the lowest power appearing in its shifted Laurent expansion, or $-\infty$ if there is no lowest power.
+A function is locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
+For convenience, we will say that function is {\em regular} at $\zeta = 0$ if its order is a non-negative integer.
+\begin{prop}\label{prop:shifting}
+Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
+When $\psi \in \zeta^\rho \mathcal{O}(\pi \Upsilon)$ is locally integrable at $\zeta = 0$,
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+if and only if
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+where $h_n, \ldots, h_{-m} \in \mathcal{O}(\pi \Upsilon)$ are regular at $\zeta = 0$.
+\end{prop}
+\begin{proof}
+The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on functions which are locally integrable at $\zeta = 0$.
+
+To prove the forward implication, rewrite the first equation in the statement as
+\begin{equation}\label{eqn:diff-int-split}
+\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
+\end{equation}
+The function
+\[ \omega = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
+belongs to $\zeta^\rho \mathcal{O}(\pi \Upsilon)$.
+Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\tfrac{\partial}{\partial \zeta} \omega$ is locally integrable.
+Hence, $\omega$ has positive order, which means it vanishes as $\zeta \to 0$.
+
+Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\omega = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
+Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish as $\zeta \to 0$, this simplifies to
+\[ \omega = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
+which rearranges to the second equation in the statement.
+\end{proof}
+\color{LimeGreen}
+Let $\Omega$ be a simply connected domain that touches but does not contain $\zeta = 0$.
+In Theorem~4 of \cite{reg-sing-volterra}, under the additional assumption that $\Omega$ is star-shaped around $\zeta = 0$, we show that an integral equation of a certain form always has a unique solution in the affine subspace
+\[ \zeta^{\tau-1} + \singexpalg{\tau}(\Omega) \]
+of the space $\singexpalg{\tau-1}(\Omega)$, with $\tau \in (0, \infty)$.
+When $\tau$ is non-integer, this subspace has the convenient property that we can pass back and forth between integral and differential equations without worrying about boundary conditions.
+We use this fact in Sections~\textcolor{magenta}{(?)}\;--\;\textcolor{magenta}{(?)} to find explicit expressions for the integral equation solutions described above.
+
+%%As we saw in Sections~\ref{laplace:ordinary} and \ref{sec:reg-decay}, the function spaces $\singexpalg{\sigma}(\Omega)$ with $\sigma > -1$ are natural domains for the Laplace transform.
+When $\sigma$ is non-integer, these spaces have the convenient property that
+%---------
+%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. %We will say a function is {\em slight} at $\zeta = 0$ if it can be written as 
 %\begin{equation}\label{eqn:slight-definition}
@@
 %where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
+\color{RoyalBlue}
 As we've seen in Section~\ref{sec:reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
@@
 In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
-\begin{prop}\label{prop:shifting}
+\color{black}
+\begin{prop}%%\label{prop:shifting}
 Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
@@
 To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}\label{eqn:diff-int-split}
+\begin{equation}%%\label{eqn:diff-int-split}
 \tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.

### 2024-04-02 exp-resurgence.tex
Switch to language of germs
Finish "analytic to formal" and "order shifting". Start Airy-Lucas example.

@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item \textcolor{LimeGreen}{If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}.} We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
+\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
@@
 Ask more about this.]}
-\item If $\hat{\phi}$ also grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
@@
 \end{definition}
-\color{RoyalBlue}
-\begin{definition}
-On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
-\begin{equation}%%\label{series:asymp-definition}
-\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
-\end{equation}
-is {\em asymptotic} to a holomorphic function $\Phi$ if
-\[ \left|\Phi - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
-over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $\Phi$, namely we will write \[\Phi\sim \sum_{n\geq 1} a_n z^{-n}.\]}
-\end{definition}
-\color{black}
 This definition generalizes straightforwardly to ``fractionally shifted'' power series and trans-monomials.
@@
 The question of how that happens is the starting point for this paper.
-
-%\color{gray}
-%\begin{itemize}
-%\item \done{You can often find a formal power series $\tilde{\Phi} = \ldots$ that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
-For example\ldots}
-%\begin{itemize}
-%\item \done{Exponential integral: na\"{i}ve saddle point expansion.}
-%\item \done{ODE: formal solution.} Existence theorem in \cite{diverg-resurg-iii}?
-%\item Feynman diagram series?
-%\end{itemize}
-%\item Once you have $\tilde{\Phi}$, you might try applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it.
-%\begin{itemize}
-%\item \done{Borel summation work in three steps.
-First we turn the formal power series $\tilde{\Phi}$ \textcolor{magenta}{[$\tilde{\Phi}(z)$]} in the ``frequency variable'' $z$ into a formal power series $\tilde{\phi}$ in a new ``position variable'' $\zeta$.}
-%\item \done{The series $\tilde{\phi}$ turns out to have a \textcolor{magenta}{[finite]} positive radius of convergence, so it defines a holomorphic function $\hat{\phi}$.
-By analytic continuation, we can expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.}
-%\item \done{If $\hat{\phi}$ grows slowly enough along an infinite ray $\mathcal{J}_b^\theta := b + e^{i\theta}[0, \infty)$ \textcolor{magenta}{[decide notation]}, its Laplace transform $\laplace_b^\theta \hat{\phi} := \ldots$ is a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\laplace_b^\theta \hat{\phi}$ its {\em Borel sum} at $b$.}
-%\item {[Draw the square!]}
-%\end{itemize}
-%\item Different functions can be asymptotic to the same power series, and Borel summation picks one of them.
-%\item In many cases, it picks correctly, producing an actual solution to your problem.
-%\begin{itemize}
-%\item The question of how that happens is the starting point for this paper.
-%\item (In both of the cases that we study, the Borel sum of $\tilde{\Phi}$ is always taken at a zero of $\lambda$, rather than an arbitrary point in $B$.
-For ODEs, our treatment explains why the zeroes of $\lambda$ play a special role.)
-%\end{itemize}
-%\end{itemize}
-%\color{black}
+%
 \subsection{A new perspective: Borel regularity}
+%
 \subsubsection{Introducing Borel regularity}
-We consider an holomoprhic function $\Phi$, solution of our problem. Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$.
-
-%\textcolor{Tan}{We consider a new diagram: we start reading it from the upper-left corner, namely we assume there exists a holomorphic function $\Phi$ which is asymptotic to a formal power series $\series{\Phi}$ as $\Re e^{i\theta}z$ goes to $\infty$ in the direction of $\theta$}
-
+%
+Let us start again, \textcolor{orange}{[\ldots]}
+%%Instead of starting with a formal solution to a problem, as we did in Section~\ref{intro:summation}, let us start with a holomorphic solution $\Phi$.
+Suppose it has an asymptotic expansion \series{\Phi} \defeq \aexp^\theta \Phi$.
+
+Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$. 
 \begin{center}
@@
 In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
-\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
+\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
 which is what we wanted to show.
@@
 \begin{definition}\label{def:convolution_formal}
+Let $\zeta$ be a coordinate on $B$.
 For any integers $m, n$%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then
-\begin{equation}
+\begin{equation}\label{eq: covolution}
 \frac{\zeta^m}{m!} \ast_{\zeta, 0} \frac{\zeta^n}{n!} \defeq \frac{\zeta^{m+n+1}}{(m+n+1)!} 
 \end{equation}
-\textcolor{LimeGreen}{This extends to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$ by countable linearity:}
 \begin{verify}
@@
 \end{verify}
-\color{RoyalBlue}
-\begin{equation}\label{eq: formal_convolution}
-\series{\phi}\ast_{\zeta,0}\series{\psi}:=\sum_{n=0}^\infty c_n \frac{\zeta^n}{n!}\,,
-\end{equation}
-with $c_n=\sum_{j=0}^n a_j b_{n-j}$.
-\color{black}
+This extends to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$ by countable linearity:
+\begin{align*}
+   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}
+\end{align*}
 \end{definition}
-Notice that the right hand side of equation~\eqref{eq: formal_convolution} is the Borel transform of the Cauchy product of the formal series $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, namely if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
+Similarly, we can extend the deifnition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: covolution}
+\begin{equation}
+\frac{\zeta_\alpha^m}{m!} \ast_{\zeta_\alpha, 0} \frac{\zeta_\alpha^n}{n!} \defeq \frac{\zeta_\alpha^{m+n+1}}{(m+n+1)!} \,.
+\end{equation}
+We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+\begin{prop}
+    Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$.
+The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
+    \[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=\Big(\borel_\zeta\tilde{\Psi}\Big)\ast\Big(\borel_\zeta\tilde{\Phi}\Big).\]
+\end{prop}
+\begin{proof}
+    We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then
+    \begin{align*}
+\borel_\zeta(\series{\Psi}\series{\Phi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
+&=a_0b_0\delta + \sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^n}{n!}
+    \end{align*}
+\end{proof}
+Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
  \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
@@
 %
-The spaces $\singexp{\rho}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
-To study Borel summation, however, we also need to take Taylor series expansions around $\zeta = 0$, which cannot be done for all functions in $\singexp{\rho}{\Lambda}(\Omega)$.
-We need a way to make sure we stay in the subspace where the Taylor series exists.
-
-To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
+The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
+To study Borel summation, however, we also need to take shifted Taylor expansions around $\zeta = 0$, turning holomorphic functions $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$ into convergent power series $\series{\phi} \in \zeta^\rho \C\{\zeta\}$ with $\rho \ge \sigma$.
+When $\Omega$ touches but does not contain $\zeta = 0$, only some of its functions will have shifted Taylor expansions.
+We need a way to make sure we stay in a subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the shifted Taylor series exists.
+
+\color{HotPink}
+If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$.
+The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
+\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega), \]
+where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$.
+More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
+\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega). \]
+
+To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
+On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$.
+Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
+\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
+
+\color{black}\textcolor{SteelBlue}{To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
 In the result below, our conditions on the open set $\Upsilon \subset \widetilde{\C^\times}$ imply that the projection $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$.
@@
 In fact, a holomorphic function on $\Upsilon$ will have a Laurent series expansion around $\zeta = 0$ only if it descends to a holomorphic function on $\pi \Upsilon$.
-In other words, by pulling back along $\pi$, we can think of the holomorphic function space $\mathcal{O}(\pi \Upsilon)$ as the subspace of $\mathcal{O}(\Upsilon)$ where the Laurent series around $\zeta = 0$ exists.
+In other words, by pulling back along $\pi$, we can think of the holomorphic function space $\mathcal{O}(\pi \Upsilon)$ as the subspace of $\mathcal{O}(\Upsilon)$ where the Laurent series around $\zeta = 0$ exists.}
 
@@
 \end{center}
+\color{HotPink}
+For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
+\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+\color{black}
+\color{SteelBlue}
 For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
 \[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+\color{black}
 is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
@@
 \[ \var \varphi \big|_b = \varphi(b_+) - \varphi(b_-) \]
-is bounded. The intersection of $\zeta^\rho\,\mathcal{O}(\pi\Upsilon)$ with $\singexp{\sigma}{\Lambda}(\Upsilon)$ is the kernel of the bounded operator $\var - (e^{2\pi i \rho} - 1)$, so it is closed.
+is bounded.
+A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
+This operator is bounderd, so its kernel is closed.
 \end{proof}
+\color{SteelBlue}
 If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$.
@@
 \end{proof}
+\color{black}
 
@@
 \end{align*}
-\color{DarkTurquoise}
-\begin{prop}\label{prop:deriv-cont}
-Suppose $\Omega$ contains an open subset $\Omega'$ on which $|\zeta| \lesssim \Delta$, where $\Delta$ is the distance to the boundary of $\Omega$.\footnote{This happens, for instance, when $\Omega$ and $\Omega'$ are sectors, and $\Omega$ contains the closure of $\Omega'$.} The derivative operator $\big(\tfrac{\partial}{\partial \zeta}\big)^n$, for $n \in \Z_{\ge 1}$ then gives a continuous map
-\[ \singexp{\sigma}{\Lambda}(\Omega) \to \singexp{\sigma-1}{\Lambda}(\Omega') \]
-for all $\sigma > -1$ and $\Lambda \in \R$.
-\end{prop}
-\begin{proof}
-Choose a constant $M$ for which $|\zeta| \le M\Delta$. Since $\Omega$ does not contain $\zeta = 0$, we know that $\Delta \le |\zeta|$ as well.
-
-Take some $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$, and let $\omega \defeq \big(\tfrac{\partial}{\partial \zeta}\big)^n \phi$.
-At any $a \in \Omega'$, applying Cauchy's inequality on a disk of radius $\Delta(a)/2$ tells us that
-\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} |\phi|, \]
-where $D_r(a)$ is the closed disk of radius $r$ around $a$. The definition of the norm on $\singexp{\sigma}{\Lambda}(\Omega)$ gives the bound
-\[ |\phi| \le |\zeta|^\sigma e^{\Lambda|\zeta|}\,\|\phi\|_{\sigma, \Lambda}, \]
-which we can plug into Cauchy's inequality to see that
-\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} \left(|\zeta|^\sigma e^{\Lambda|\zeta|}\,\|\phi\|_{\sigma, \Lambda}\right). \]
-Since $\Omega$ does not contain $\zeta = 0$, we know that $|\zeta| \le \Delta$, implying that
-\[ |\omega(a)| \le \big(\Delta(a)/2\big)^{-n} \sup_{D_{\Delta(a)/2}(a)} \left(|\Delta|^\sigma e^{\Lambda|\Delta|}\,\|\phi\|_{\sigma, \Lambda}\right). \]
-\end{proof}
-\color{black}
-\begin{prop}
-\end{prop}
 \begin{prop}\label{prop:L-int-op}
@@
 \end{proof}
+\color{RoyalBlue}
 \textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
 Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
+\color{black}
 \textcolor{orange}{[Add flavor text]}
@@
 By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
-\[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
+\[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
 of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
@@
 In \citesection{sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
-\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right], \]
-which shows that it lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
-\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]
-and $\volterra^\alpha$ maps $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$ to itself.
-It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$.
-Recalling that the prototype solution lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$, we can deduce that $\psi_\alpha$ lies in that space too.
-
-We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
+\[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta_\alpha(a)}{\zeta_\alpha(b)}\right)^{\tau_\alpha} \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau_\alpha}{\zeta_\alpha} \right)\;d\zeta_\alpha\right], \]
+\textcolor{HotPink}{which shows that it represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$.}
+\textcolor{SteelBlue}{which shows that it lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}. By working with Taylor series, we can show that $\softpart^\alpha$ maps
+\textcolor{HotPink}{\[ \zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \to \zeta^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \]}
+\textcolor{SteelBlue}{\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]}
+and $\volterra^\alpha$ maps \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha}$} \textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$} to itself.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$} \textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta = \alpha}$} \textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}.
+Recalling that the prototype solution \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$} \textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}, we can deduce that $\psi_\alpha$ \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$.} \textcolor{SteelBlue}{lies in that space} too.
+
+\textcolor{HotPink}{We now cross over into the formal world, expanding $\psi_\alpha$ as} \textcolor{SteelBlue}{We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of} a shifted Taylor series $\series{\psi}_\alpha \in \zeta_\alpha^{\tau_\alpha-1}\,\C\{\zeta\}$.
 By definition, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
@@
 \end{proof}
-\par\color{RoyalBlue}
-Given a differential operator $\mathcal{P}$ as in equation~\eqref{eqn:operator-P}, Poincar\'e showed how to build a frame of formal solutions of the equation $\mathcal{P}\Psi=0$ with a simple algorithm: for every root $\alpha$ of $P$, let $\tau_\alpha:=Q(-\alpha)/P'(-\alpha)$ and consider the following ansatz
-\begin{equation}
-    \tilde{\Psi}_\alpha(z):=e^{-z\alpha}z^{-\tau_\alpha}\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket.
-\end{equation}
-Then solving order by order in $n$ it is possible to compute the coefficients of the formal series $\sum_{n=0}^\infty a_{\alpha,n}\, z^{-n}$, which will turn out to be a $1$-Gevrey series because of Ramis
-Index Theorem \cite{ramis_index}.
-When applicable, Borel summability is an effective method to produce an analytic frame of solutions from the formal Poincar\'e frame $\tilde{\Psi}_\alpha$.
-In particular, as a consequence of our result in Theorem~\ref{re:thm:exist_uniq_ODE} we deduce that the Poincar\'e frame of solutions is Borel summable.
-\begin{theorem}\label{thm2-dim}
-For each root $\alpha$ of $P$, let $\tilde{\Psi}_\alpha(z)\in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket_1$ be the formal solution of $\mathcal{P}\Psi=0$ with $a_{\alpha,0}=1$.
-Then $\series{\Psi}_\alpha(z)$ is Borel summable and its Borel sum $\hat{\Psi}_\alpha(z)$ is proportional to the analytic solution $\Psi_\alpha$ of Theorem~\ref{re:thm:exist_uniq_ODE}.
-\end{theorem}
-\begin{proof}
-We divide the proof in the following steps:
-\begin{itemize}
-\item[$(a)$] let $\series{\psi}_\alpha:=\borel_{\zeta}\series{\Psi}_\alpha$, then $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha=0$.
-\item[$(b)$] $\tilde{\psi}_\alpha\in\C\lbrace\zeta_\alpha\rbrace$ can be analytically continued and its sum $\hat{\psi}_\alpha$ solves $\hat{\mathcal{P}}_\alpha\hat{\psi}_\alpha=0$. 
-\item[$(c)$] $\hat{\psi}_\alpha$ admits a Laplace transform $\laplace_{\zeta,\alpha}^{\theta}\hat{\psi}_\alpha=:\hat{\Psi}_\alpha$ and that $\hat{\Psi}_\alpha\propto\Psi_\alpha $. 
-\end{itemize}
-Step $(a)$ follows from the properties of the Borel transform: recall from Section~\ref{sec:convolution-compatible} that $\tilde{\Psi}_\alpha$ is a transmonomial, thus the Borel transform of $z^{-\lambda}\tilde{\Psi}_\alpha$ is written in terms of the convolution product $\ast_{\alpha}$:
-\begin{align*}
-  \borel_{\zeta}\left(\mathcal{P}\series{\Psi}_\alpha\right)&= \left[P(-\zeta)+1\ast_{\alpha} Q(-\zeta)+\zeta \ast_{\alpha} \left(\sum_{r=0}^{d-1}\borel_\zeta(R_r(z^{-1}))\ast_{\alpha}(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
-  &=\left[P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\fracderiv{-2}{\zeta}{\alpha} \left(\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha} )(-\zeta)^r\right)\right]\series{\psi}_\alpha(\zeta_\alpha)\\
-  &=\hat{\mathcal{P}}_\alpha\tilde{\psi}_\alpha(\zeta_\alpha)
-\end{align*}
-Hence, the Borel transform of $\series{\Psi}_\alpha$ is a solution of $\hat{\mathcal{P}}_\alpha\series{\psi}_\alpha$=0.
-
-To prove Step $(b)$ we will use the properties of the integral equation $\hat{\mathcal{P}}_\alpha\psi=0$.
-First, recall that ${\psi}_\alpha$ is the unique solution of $\hat{\mathcal{P}}_\alpha\psi=0$ such that $\psi_\alpha\in\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ \cite[Theorem~4]{reg-sing-volterra}.
-Then,\textcolor{orange}{[change as new argument]} , the Taylor expansion of $\psi_\alpha$ is the formal solution of $\hat{\mathcal{P}}_\alpha\psi=0$ in $\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$.
-Since by direct computations $\tilde{\psi}_\alpha\in\zeta_\alpha^{\tau_\alpha-1}\C\lbrace\zeta_\alpha\rbrace$
-\[\tilde{\psi}_\alpha=\sum_{n=0}^\infty a_{\alpha,n}\frac{\zeta_\alpha^{n+\tau_\alpha-1}}{\Gamma(n+\tau_\alpha)},\]
-our uniquess result ensures that $\tilde{\psi}_\alpha$ is proportional to the Taylor expansion of $\psi_\alpha$ in their common region of convergence.
-Thus if $\hat{\psi}_\alpha$ denotes the sum of $\tilde{\psi}_\alpha$, we deduce that $\tilde{\psi}_\alpha\propto\psi_\alpha$.
-
-Finally, we can Laplace transform $\hat{\psi}_\alpha$ along a ray $\mathcal{J}_{\alpha}^\theta$ in $\Omega_\alpha$, proving the $\tilde{\Psi}_\alpha$ is Borel summable.
-In addition, since $\tilde{\psi}_\alpha\propto\psi_\alpha$, their Laplace transform will be proportional too $\laplace_{\zeta,\alpha}^\theta\hat{\psi}_\alpha\propto \Psi_\alpha$.
-This ends the proof of Step $(c)$.
-
-%First notice that if $\series{\Psi}_j=e^{-\alpha_jz}\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ solves $\mathcal{P}\Psi=0$ then $\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$ is a solution of $\mathcal{P}_j\Psi=0$ with
-
-%\begin{equation}
-%\mathcal{P}_j:=P(-\alpha_j+\partial_z)+\frac{1}{z}Q(-\alpha_j+\partial_z)+\frac{1}{z^2}\sum_{r=0}^dR_r(z^{-1})(-\alpha_j+\partial_z)^r
-%\end{equation}
-
-%Hence
-
-%\begin{
-
-%Then we take the (formal) Borel transform $\borel_\zeta$ of  $\mathcal{P}_j \sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}$
-
-%\begin{multline*}
-%\borel_\zeta\left(\mathcal{P}\series{\Psi}_j\right)=\borel_\zeta\left[e^{-\alpha_j z}\mathcal{P}_j\sum_{n=0}^{\infty}a_{j,n}z^{-n-\tau_j}\right]=\\
-%\left[P(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-1}\circ Q(-\alpha_j-\zeta_j)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\alpha_j-\zeta_j)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}\\
-%\left[P(-\zeta)+\partial_{\zeta_j,0}^{-1}\circ Q(-\zeta)+\partial_{\zeta_j,0}^{-2}\circ \sum_{r=0}^dR_r(\partial_{\zeta_j,0}^{-1})\circ (-\zeta)^r\right]\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}\zeta_j^{n+\tau_j-1}
-%\end{multline*}
-%where 
-%
-%\begin{align*}
-%\series{\psi}_j(\zeta_j):=\borel\series{\Psi}_j(\zeta_j)&=\borel\left(e^{-\alpha_j z}z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta_j)=\borel\left(z^{-\tau_j}\sum_{n=0}^{\infty}a_{j,n}z^{-n}\right)(\zeta-\alpha_j)\\
-%&=\sum_{n=0}^{\infty}\frac{a_{j,n}}{\Gamma(n+\tau_j)}(\zeta-\alpha_j)^{n+\tau_j-1}
-%\end{align*}
-
-\end{proof}
-
-%\color{Turquoise}
-%\begin{lemma}\label{step a}
-%    Let $\hat{\psi}_j$ be the unique solution of $\hat{P}_j\hat{\psi}_j=0$, then it admits a Laplace transform. 
-%\end{lemma}
-
-%\begin{proof}
- %   We’ll prove the following: 
-  %  \begin{itemize}
-   %     \item there are only a finite number of singularities in the Borel plane, hence there is a direction which avoids all the singularities;
-    %    \item the analytic continuation of $\hat{\psi}_j$ along that direction grows sub-exponentially. 
-    %\end{itemize}
-    %The singularities of $\hat{P}_j$ are at $P(-\alpha_j-\zeta_j)=0$, hence at $\zeta_j=\alpha_k-\alpha_j$ for every $k=1,...,d$.
-In fact, we can prove this statement using a perturbative method that goes back to \'Ecalle (see \cite{EcalleIII}, \cite[Section 2.5]{loday-Remy2011}).
-Let $\epsilon$ be a parameter and let $f_j(\zeta,\epsilon):=\sum_{k\geq 0}f_{j,k}(\zeta)\epsilon^k$ be a solution of
-   % \[\left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)+\epsilon\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r\right]f_j=0\]
-   % \textcolor{red}{such that $f_j(\zeta,1)=\hat{\psi}_j(\zeta)$}. We solve order by order in $\epsilon$: at order zero
-
-    %\begin{align*}
-     %   &P(-\zeta)f_{j,0}+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)f_{j,0}=0\\
-      %  &-P'(-\zeta)f_{j,0}+P(-\zeta)\partial_\zeta f_{j,0}+Q(-\zeta)f_{j,0}=0\\
-       % &P(-\zeta)\partial_\zeta f_{j,0}=P'(-\zeta)f_{j,0}-Q(-\zeta)f_{j,0}
-    %\end{align*}
-    %If $\zeta\neq\alpha_k$ for $k=1,...,d$ we can solve the first order equation and for $a\neq\alpha_k$
-    %\begin{align*}
-     %   f_{j,0}&=f_{j,0}(a)\cdot \exp\left(\int_a^{\zeta}\frac{P'(-t)-Q(-t)}{P(-t)}dt\right)\\
-      %  &=f_{j,0}(a)\cdot \frac{P(-a)}{P(-\zeta)}\exp\left(-\int_a^{\zeta}\frac{Q(-t)}{P(-t)}dt\right)
-    %\end{align*}
-    %Therefore, $f_{j,0}$ is singular at $\zeta=\alpha_k$ for every $k=1,...,d$ (or equivalently, at $\zeta_j=\alpha_k-\alpha_j$). Then, for $n\geq 1$
-
-    %\begin{align*}
-     %   \left[P(-\zeta)+\fracderiv{-1}{\zeta}{\alpha_j}\circ Q(-\zeta)\right]f_{j,n}=-\fracderiv{-2}{\zeta}{\alpha_j}\circ\sum_{r=0}^{d-1}R_r(\fracderiv{-1}{\zeta}{\alpha_j})\circ(-\zeta)^r f_{j,n-1}
-    %\end{align*}
-    %and since $R_r$ is entire, the right-hand side is an infinite sum of the convolution product of an entire function with $f_{j,n-1}$, hence it  has the same singularities as $f_{j,n-1}$ (see Lemma 6.15 \cite{diverg-resurg-i}).
-Therefore, we deduce $f_{j,1}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$ and inductively, $f_{j,n}$ is singular at $\zeta=\alpha_k$ for $k=1,...,d$.
-
-    %Let $\theta$ be the direction that avoids all the singularities, we now prove that the analytic continuation of $\hat{\psi}_j$ grows sub-exponentially.
-In fact, it is enough to adapt the Gr\"onwall lemma to integral equations (see Lemma 3.9 \cite{diverg-resurg-iii}]).
-   %Let $\Omega$ be the open domain where $\hat{\psi}_j$ is analytic and let $p$ be a point in $\Omega$ such that $\Omega':=\Omega\setminus B_{r}(\alpha_j)$ is star-shaped from $p$ ($B_r(\alpha_j)$ is the ball of radius $r$ and center in $\alpha_j$).
-By assumption on the coefficients of the ODE \eqref{eqn:standard ODE}
-   %\begin{align*}
-    %   a:=\sup_{\zeta\in\Omega'}\frac{|Q|(|\zeta|)}{|P(-\zeta)|}<\infty\, \qquad b:=\sup_{\zeta\in\Omega'}\frac{1}{|P(-\zeta)|}<\infty
-   %\end{align*}
-   %hence, for every $\zeta\in\Omega'$, writing $\xi=|\zeta|$ and $\zeta=p+\xi e^{i\eta}$
-   %\begin{align*}
-    %|\hat{\psi}_j(\zeta)|&\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-     %  &\leq \frac{1}{|P(-\zeta)|}\left[\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|}+\int_{|p|}^\xi \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-      % &\qquad +c\left[\int_{|\alpha_j|}^{|p|}|Q|(\rho) |\hat{\psi}_j(\rho e^{i\theta})|d\rho+\int_{|\alpha_j|}^{|p|} \sum_{r=0}^{d-1}|\hat{R}_r(\xi-\rho)|\cdot \rho^r |\hat{\psi}_j(\rho e^{i\theta})| d\rho\right]\\
-      % &\leq a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c \sum_{r=0}^{d-1}\int_{|p|}^\xi|\hat{R}_r(\xi-\rho)|\cdot \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho +\\
-      % &\qquad + a'\int_{|\alpha_j|}^{|p|}|\hat{\psi}_j(\rho e^{i\theta})|d\rho+ c\sum_{r=0}^{d-1}\int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot  \rho^r|\hat{\psi}_j(\rho e^{i\theta})| d\rho%\\
-      % %&\leq a \int_{|\alpha_j|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho \\
-      % %&=a \int_{|p|}^\xi  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|p|}^\xi |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho+\\
-      % %&\qquad + a \int_{|\alpha_j|}^{|p|}  |\hat{\psi}_j(\rho e^{i\theta})|d\rho +c  \sum_{r=0}^{d-1} \xi^{r} \int_{|\alpha_j|}^{|p|} |\hat{R}_r(\xi-\rho)|\cdot|\hat{\psi}_j(\rho e^{i\theta})| d\rho
-   %\end{align*}
-   %where $\hat{R}_r=\borel(z^{-2}R_r)$, for every $r=0,...,d-1$. 
-   %%For every $r=0,...,d-1$, we define $F_r(z)=R_r(z)$
-   %We want to show that for every $m\geq 0$, $|\hat{\psi}_j(\zeta)|<\hat{W}_m(\xi)$ for $\zeta$ on the ray $\zeta=p+\xi e^{i\theta}\in\Omega'$, where $\hat{W}_m$ is the unique solution of
-
-   %\begin{equation}
-    %   \hat{W}=m+a\ast_{|p|}\hat{W}+c\sum_{r=0}^{d-1}\hat{R}_r\ast_{|p|} (-\zeta^r\hat{W})
- %  \end{equation}
-
- %  \textcolor{red}{Be careful with derivatives: maybe rewrite Lemma 3.8 in such a way that includes them.
-This means that equation 27 is not anymore algebraic, but it will include terms of the form $R_r(z) \tilde{W}^{(r)}$.
-  % There is also another problem, the reasoning of Delabere in Lemma 3.9 requires the existence of a point $p_0$ in $\Omega'$ such that $|\hat{\psi}_j(p_0)|\leq |\hat{W}_m(p_0)|$ for every $m\geq 0$.
-Can we argue that $|\hat{\psi}_j(\rho e^{i\theta})|$ is bounded for $\rho\in [|\alpha_j|,|p|]$?
-}
-%\end{proof}
-\color{black}
 \subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
@@
 \subsubsection{Asymptotic analysis}\label{sec:asympt-AL}
-
-From the general theory of ODEs of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel-AL} has a basis of trans-monomials
+From the work of Poincar\'{e} and the Ramis Index Theorem, as discussed at the beginning of Section~\ref{sec:new-summability-proof}, we know that equation~\eqref{eqn:reg-mod-bessel-AL} has a frame of formal $1$-Gevrey trans-monomial solutions
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-where $\tau_\alpha = 1/2$, and the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
+where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
 From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n}(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
@@
 Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
-However, as we show in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $\singexpalg{\sigma}(\Omega_\alpha)$, for some $\sigma\in (-1, 0)$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution \textcolor{magenta}{of order $\sigma=1/2$} at each regular singular point.
+However, as we show in Appendix~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $(\zeta - \alpha)^\sigma \mathcal{O}_{\zeta = \alpha}$ for some $\sigma \in (-1, 0)$.
+
+This is good news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of the desired kind at each regular singular point.
 We can see the regular singularities by moving the derivatives to the right:
@@
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
-For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which is in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ for some constant $\tau_\alpha \in (0, 1)$ and some domain $\Omega_\alpha$ resembling the one in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel-AL}, \textcolor{magenta}{and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$}.
-We learned in Section~\ref{sec:change-translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-for $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
+We will see that $v_\alpha$
+\textcolor{LimeGreen}{Furthermore, we will show in Section~\ref{bessel-regularity-AL} that $v_\alpha$ can be analytically continued to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$, where $\Omega_\alpha$ is a sector with its tip at $\zeta = \alpha$.}
+%%and can be analytically continued to a sector $\Omega_\alpha$ with its tip at $\zeta = \alpha$. In fact $v_\alpha$ will belong to $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \cap$
+%%which is in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ for some constant $\tau_\alpha \in (0, 1)$ and some domain $\Omega_\alpha$ resembling the one in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
+It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
+We know from Section~\ref{sec:change-translation} that
+\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+Finally, observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we can then do the further decomposition
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
+where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
+
+\textcolor{LimeGreen}{We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+makes $W_\alpha$ asymptotic to a scalar multiple of \textcolor{magenta}{$z^{-1}$} at $z = \infty$.}
 %\color{Peru}
@@
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
-Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_1)$.
+Let us find a germ in $(\zeta-1)^{\tau_1-1}\,\mathcal{O}_{\zeta=1}$, for some $\tau_1 \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
 Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
@@
 \end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which belongs to $\singexpalg{1/2}$ at $\xi_1 = 0$:
+Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} that represents a germ in $\xi_1^{-1/2}\,\mathcal{O}_{\xi_1=0}$:
 \begin{alignat*}{2}
@@
 \end{alignat*}
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+From the argument in Section~\ref{big-idea} \textcolor{magenta}{(!)}, we know that $\laplace^\theta_{\zeta, 1} v_1$ is well-defined, satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
 Since $v_1$ \textcolor{magenta}{has order $-1/2$}, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
-Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} which belongs to $\singexpalg{\sigma}(\Omega_{-1})$.
+Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
 In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which \textcolor{magenta}{belongs to $\singexpalg{-1/2}$ at $\xi_1 = 1$}:
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
 \begin{alignat*}{2}
@@
 \subsection{Order shifting for integro-differential equations}\label{shifting}
-Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
-As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.
-
-To make this statement precise, we need some terminology.
+For a differential equation with a regular singularity at $\zeta = 0$, the Frobenius method typically gives a convergent power series solution in $\zeta^\rho\,\C\{\zeta\}$ for some $\rho \in \R$, which sums to a germ in $\zeta^\rho\,\mathcal{O}_{\zeta=0}$.
+When $\rho$ is a non-integer greater than $-1$, we can do a nice trick in this space of germs: we can pass back and forth between differential and integral equations without worrying about boundary conditions.
+
+\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
+As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.}
+
+\textcolor{SteelBlue}{To make this statement precise, we need some terminology.
 For any $\sigma \in \R$, let us say that the {\em order} of a function in $\zeta^\sigma \mathcal{O}(\pi \Upsilon)$ is the lowest power appearing in its shifted Laurent expansion, or $-\infty$ if there is no lowest power.
 A function is locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-For convenience, we will say that function is {\em regular} at $\zeta = 0$ if its order is a non-negative integer.
+For convenience, we will say that function is {\em regular} at $\zeta = 0$ if its order is a non-negative integer.}
 \begin{prop}\label{prop:shifting}
-Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
-When $\psi \in \zeta^\rho \mathcal{O}(\pi \Upsilon)$ is locally integrable at $\zeta = 0$,
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
+Consider a germ $\phi \in \zeta^\rho\,\mathcal{O}_{\zeta=0}$. When $\rho$ is a non-integer greater than $-1$,
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \phi = 0, \]
 if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m} \in \mathcal{O}(\pi \Upsilon)$ are regular at $\zeta = 0$.
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi = 0, \]
+assuming that the coefficients $h_n, \ldots, h_{-m}$ are in $\mathcal{O}_{\zeta=0}$.
 \end{prop}
 \begin{proof}
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on functions which are locally integrable at $\zeta = 0$.
+The reverse implication holds without any special condition on $\phi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on functions which are locally integrable at $\zeta = 0$.
 
@@
 \end{equation}
-The function
-\[ \omega = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-belongs to $\zeta^\rho \mathcal{O}(\pi \Upsilon)$.
-Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\tfrac{\partial}{\partial \zeta} \omega$ is locally integrable.
-Hence, $\omega$ has positive order, which means it vanishes as $\zeta \to 0$.
+The germ
+\[ f \defeq \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
+belongs to $\zeta^{\rho-(n-1)} \mathcal{O}(\pi \Upsilon)$.
+This tells us, in particular, that $f$ has a shifted Taylor expansion with no constant term.
+Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can also see that $\tfrac{\partial}{\partial \zeta}\,f$ belongs to $\zeta^\rho\,\mathcal{O}_{\zeta=0}$.
+Combining these observations, we can deduce that $f$ belongs to $\zeta^{\rho+1}\,\mathcal{O}_{\zeta=0}$.
+Since $\rho > -1$, that means $f$ vanishes at $\zeta = 0$.
 
 Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\omega = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish as $\zeta \to 0$, this simplifies to
-\[ \omega = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;f = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi. \]
+Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
+\[ f = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi, \]
 which rearranges to the second equation in the statement.
@@
 \color{LimeGreen}
-Let $\Omega$ be a simply connected domain that touches but does not contain $\zeta = 0$.
+Let $\Omega$ be a simply connected set that touches but does not contain $\zeta = 0$.
 In Theorem~4 of \cite{reg-sing-volterra}, under the additional assumption that $\Omega$ is star-shaped around $\zeta = 0$, we show that an integral equation of a certain form always has a unique solution in the affine subspace
@@
 Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
-Hence, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
+Hence \textcolor{orange}{[I think this is the implication thtat fails when $\phi$ has a constant term]}, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
 

### 2024-04-02 exp-resurgence.tex
Update Section history ODE

@@
 %\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there is a constant $c \in (0, \infty)$ with
 %\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
@@
 Let $-\alpha$ be a root of $P$.
-Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$.
+Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
@@
 %\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there's a constant $c \in (0, \infty)$ with
+%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there is a constant $c \in (0, \infty)$ with
 %\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
@@
 %\end{itemize}
-%\item Say there's a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
+%\item Say there is a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
 Then this is the only solution that can be expressed as a Laplace transform.
@@
 Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}.
-These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $\Lambda$.
+These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which does not contain $0$, and may be displaced from $0$ by some distance $\Lambda$.
 \begin{center}
@@
 
-The Watson--Nevanlinna--Sokal characterization of Borel regular functions is totally general, which means it can't take advantage of any extra structure provided by the problem you're trying to solve.
+The Watson--Nevanlinna--Sokal characterization of Borel regular functions is totally general, which means it cannot  take advantage of any extra structure provided by the problem you are trying to solve.
 We take the opposite approach, showing that certain functions are Borel regular just because of the extra structure provided by the problems they solve.
@@
 %
+The study of irregular singular differential equations in the complex domain has a long history, and interesting phenoma distinguish irregular singular equations to regular singular ones.
+Already at the formal level, irregular singular ODEs have a distinguished behaviour, namely they admit divergent formal series solutions in the form of trans-monomials.
+In particular, for level $1$ ODEs of the kind we study in this paper, the Poincar\'e method gives an algorithm to compute formal solutions of $\mathcal{P}\Phi=0$, see~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a r\^ole~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}).
+Then, the Ramis Index Theorem shows that the formal solutions $\tilde{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+\textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]} Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.
+
+Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the r\^ole of the position domain.
+Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform.
+In particular the Borel transform of the formal solution $\series{\Phi}$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
+For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
+Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
+However, the advantage of resurgence compared to the usual Borel summation, is in the study of the Stokes phenomena, which is another distinguished feature of irregular singular ODEs.
+Indeed, the Stokes phenoma is closely related to the fact that formal solutions are divergent, and the so called Stokes constants encode the ``jumps" of the underlying analytic solution which is deifned on sectors of openening angle $\pi$ and when extended by continuation on larger sectors it jumps by an exponentially small correction.
+As an example, the first order equation \[\Phi'=\Phi+\frac{1}{z}\] has formal solution $\series{\Phi}=\sum_{n=0}^\infty n!z^{-n-1}$.
+Then, its Borel transform has a simple pole at $\zeta=1$.
+Consequently, the ``jump'' of its Borel sum occurs across the positive real axis $\Re(z)>0$ and it is given by $2\pi ie^{-z}$.
+
+In a nutshell, the aim of resurgence is to study the analytic continuation of the Borel transform of a divergent series, in particular the location of sngularities in the position domain and Stokes constants computed after analytic continuation across the singularities.
+Then, the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) give the input to set-up a Riemann--Hilbert problem, whose solution would be a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
+
+So far we have been discussed the classical approaches to summability and reusrgence of formal solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
+In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
+Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral.
+This is the approahc we adopt in this paper, but our choice of Laplace transform integral to begin with is very special, i.e.
+it is a Borel regular solution.
+As for \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
+Indeed, building on our results of~\cite{reg-sing-volterra}, our approch will take the advantage of working on the position domain.
+A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
+However, with our approach, we can solve differetial equations with more general coefficients, and we plan to extend our results to systems of ODEs and generalize Braaksma's results.
+
+Summarizing, we collect the main methods to solve irregular singular ODEs in the following table stressing the difference between formal and analytic solutions in either the frequency and the position domain.
+\begin{center}
+\begin{tabular}{l|l|l}
+& \textbf{Analytic} & \textbf{Formal} \\ \hline
+\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+\textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
+& Fixed-point iteration~\cite{reg-sing-volterra} \\
+\end{tabular}
+\end{center}
+
+\color{RoyalBlue}
 From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
@@
 %
+\color{black}
 \subsection{Borel regularity for thimble integrals}
@@
 Should we just use generic holomorphic function spaces instead?
-Note that multiplying $\mathcal{O}_{T^*B}(H)$ by $e^{bz}$ (marked in magenta) doesn't do anything.]}
+Note that multiplying $\mathcal{O}_{T^*B}(H)$ by $e^{bz}$ (marked in magenta) does not do anything.]}
 
@@
 %\end{align*}
-% \textcolor{PaleVioletRed}{[I can't quite see what this paragraph is doing.]} If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
+% \textcolor{PaleVioletRed}{[I cannot  quite see what this paragraph is doing.]} If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
 % \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
@@
 For any integers $m, n$%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then
-\begin{equation}\label{eq: covolution}
-\frac{\zeta^m}{m!} \ast_{\zeta, 0} \frac{\zeta^n}{n!} \defeq \frac{\zeta^{m+n+1}}{(m+n+1)!} 
+\begin{equation}\label{eq: convolution_formal}
+\frac{\zeta^m}{m!} \ast_{\zeta, 0} \frac{\zeta^n}{n!} \defeq \frac{\zeta^{m+n+1}}{(m+n+1)!} \,.
 \end{equation}
@@
 \begin{align*}
-   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}
-\end{align*}
+   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}\,.
+\end{align*}
+Furthemore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta,0}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
+\[\frac{\zeta^n}{n!}\ast_{\zeta,0}\delta\defeq\frac{\zeta^n}{n!}\,,\]
+in other words, $\delta$ is the unit for the convolution. 
 \end{definition}
-Similarly, we can extend the deifnition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: covolution}
+Notice that from equation~\eqref{eq: convolution_formal} and the definition of the convolution with $\delta$, we deduce the convolution product is commutative with unit $\delta$.
+
+Similarly, we can extend the deifnition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
 \begin{equation}
@@
 \end{equation}
-We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+Then, the unit for $\ast_{\zeta_\alpha,0}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha,0}\frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
+We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product, to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
 \begin{prop}
@@
 The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
-    \[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=\Big(\borel_\zeta\tilde{\Psi}\Big)\ast\Big(\borel_\zeta\tilde{\Phi}\Big).\]
+    \[\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\borel_\zeta\tilde{\Phi}\ast\borel_\zeta\tilde{\Psi}.\]
 \end{prop}
 \begin{proof}
-    We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then
-    \begin{align*}
-\borel_\zeta(\series{\Psi}\series{\Phi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
-&=a_0b_0\delta + \sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^n}{n!}
+    We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then,
+    \begin{align*}
+\borel_\zeta(\series{\Phi}\series{\Psi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
+&=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
+&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
+&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
+&=\borel_\zeta\tilde{\Phi}\ast \borel_\zeta\tilde{\Psi}\,.
+%&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
+%&= a_0b_0\delta + \sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)
 \end{align*}
 \end{proof}
-Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
- \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
- Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+% Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
+%  \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
+%  Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
 % Furthermore, since $\tilde{\phi},\tilde{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
 % \end{definition}
-Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
-
-We can further generalize this result to transseries: 
-\begin{prop}
-    The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
-    \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
-    where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
-\end{prop}
+Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
+%We can further generalize this result to transseries:
+% \begin{prop}
+%     The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
+%     \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
+%     where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
+% \end{prop}
 % \begin{proof}
-%     Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n-1}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n-1}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$, then 
-%     \begin{align*}
-%         \borel_\zeta\series{\Phi}\series{\Psi}&=
-%     \end{align*}
+% Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$. 
+% %     \begin{align*}
+% %         \borel_\zeta\series{\Phi}\series{\Psi}&=
+% %     \end{align*}
 % \end{proof}
@@
 % \end{definition}
-In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series:  
+In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series.
+Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ edowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
 % \begin{prop}
@@
 % \end{prop}
-
-\textcolor{orange}{[mention convolution for transseries and difference between different fibers]}
-\color{RoyalBlue}
+\begin{verify}
 \subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
@@
 \end{remark}
-\color{black}
+\end{verify}
 %
@@
 \end{enumerate}
-%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, doesn't touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
+%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, does not touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
 \textcolor{orange}{[Introduce $\hat{\mathcal{P}}_\alpha$?]} \textcolor{orange}{[Transition text]}
@@
 In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$.
-Since $\Omega_\alpha$ doesn't contain $\zeta = \alpha$, we will always leave that starting point out of the path.
+Since $\Omega_\alpha$ does not contain $\zeta = \alpha$, we will always leave that starting point out of the path.
 %%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
-\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ doesn't touch any other critical point (that is, doesn't contain any other critical point in its closure).
+\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ does not touch any other critical point (that is, does not contain any other critical point in its closure).
 Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
@@
 For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
-We will see that $v_\alpha$
+We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other root.
 \textcolor{LimeGreen}{Furthermore, we will show in Section~\ref{bessel-regularity-AL} that $v_\alpha$ can be analytically continued to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$, where $\Omega_\alpha$ is a sector with its tip at $\zeta = \alpha$.}
@@
 It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
+Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
+\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
+for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
+
 We know from Section~\ref{sec:change-translation} that
@@
 for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-Finally, observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we can then do the further decomposition
+Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
@@
 We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau_\alpha-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
-Doesn't match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$.
+does not match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$.
 Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
@@
 The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ \textcolor{magenta}{(see Section \ref{sec:action_transseries})}, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, isn't this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
+Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, is not this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
 Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
@@
 \end{todo}
-\subsection{Third-order thimble integrals}
+\subsection{Third-degree thimble integrals}
+\color{DarkBlue}
+In this section, we consider the thimble integral
+\[ I(z) = \int_{\mathcal{C}} e^{-zg}\,du \]
+defined by a general third-degree polynomial map $g \maps \C \to \C$.
+By definition, the Lefschetz thimble $\mathcal{C}$ is a connected component of the preimage of a critical value of $g$.
+After taking various symmetries into account, we will find that there are essentially only two cases, distinguished by whether $g$ has two distinct critical points or a single degenerate one.
+\subsubsection{Symmetries of the integral}\label{sec:int-symm}
+First, we step back and consider the completely general thimble integral
+\[ J(z) = \int_{\mathcal{C}} e^{-zf}\,\nu \]
+defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on $X$.
+The affine group of $\C$ acts on $f$ by post-composition, and this action affects $J$ in a simple way.
+The affine group is generated by two kinds of transformations, which we consider separately.
+%%The affine group of $\C$ acts on $f$ by post-composition, and $\C^\times$ acts on $\nu$ by multiplication.
+These actions both affect $J$ in simple ways.
+The affine group is generated by two kinds of transformations, which we consider separately.
+\begin{itemize}
+\item[] \textbf{Translations}
+
+For any $c \in \C$, the translation action $f \mapsto f + c$ on maps corresponds to the action
+\[ J(z) \mapsto e^{-cz} J(z) \]
+on integrals. This is because
+\begin{align*}
+\int_\mathcal{C} e^{-z(f + c)}\,\nu & = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
+& = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
+& = e^{-cz} J(z).
+\end{align*}
+\item[] \textbf{Scaling-rotations}
+
+For any $r \in \C^\times$, the scaling-rotation action $f \mapsto rf$ corresponds to the action
+\[ J(z) \mapsto J(rz) \]
+on integrals. This is because
+\begin{align*}
+\int_\mathcal{C} e^{-z(rf)}\,\nu & = \int_\mathcal{C} e^{-(rz)f}\,\nu \\
+& = J(rz).
+\end{align*}
+%%\item[] \textbf{Multiplications}
+%%
+%%For any $s \in \C^\times$, the multiplication action $\nu \mapsto s\nu$ corresponds to the action
+%%\[ J(z) \mapsto s J(z) \]
+%%on integrals.
+\end{itemize}
+Next, we specialize to the case where $X$ is the complex plane, with standard coordinate $u$, and $\nu = du$.
+The affine group of $\C$ now acts on $f$ by pre-composition as well.
+To make sure that $\mathcal{C}$ remains a Lefschetz thimble, we act on it simultaneously by the inverse of whatever we precompose with $f$.
+\begin{itemize}
+\item[] \textbf{Translations}
+
+For any $c \in \C$, pulling $f$ back along the translation $\mathsf{T}_c^* u = u - c$ has no effect on the integral. This is because $du$ is translation-invariant.
+
+\item[] \textbf{Scaling-rotations}
+
+For any $s \in \C^\times$, the scaling-rotation action $\mathsf{M}_s^* u = s^{-1} u$ corresponds to the action
+\[ J(z) \mapsto s J(z) \]
+on integrals. This is because
+\begin{align*}
+\int_{\mathsf{M}_{1/s} \mathcal{C}} e^{-z \mathsf{M}_s^* f}\,du & = \int_\mathcal{C} e^{-zf}\,\mathsf{M}_{1/s}^* du \\
+& = \int_\mathcal{C} e^{-zf}\,s\,du \\
+& = s J(z).
+\end{align*}
+%%\item[] \textbf{Multiplications}
+%%
+%%For any $s \in \C^\times$, the multiplication action $\nu \mapsto s\nu$ corresponds to the action
+%%\[ J(z) \mapsto s J(z) \]
+%%on integrals.
+\end{itemize}
+\subsubsection{Reduction of the integral}
+We now return to our original thimble integral $I(z)$, defined by the third-degree polynomial map
+\[ g = a_3 u^3 + a_2 u^2 + a_1 u + a_0, \]
+and use the group actions from Section~\ref{sec:int-symm} to reduce it to its two essential cases.
+Our first move is to bring the polynomial into depressed form by post-composing it with a scaling by $\tfrac{1}{a_3}$ and pre-composing it with a translation by $\tfrac{1}{3} \tfrac{a_2}{a_3}$.
+\begin{center}
+\begin{tabular}{c|c|c}
+\textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
+$\displaystyle f \mapsto f/a_3$ & $\displaystyle u^3 + \frac{a_2}{a_3} u^2 + \frac{a_1}{a_3} u + \frac{a_0}{a_3}$ & $\displaystyle I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle \mathsf{T}_{a_2/3a_3}^*$ & $\displaystyle u^3 + pu + q$ & $\displaystyle I\left(\frac{z}{a_3}\right)$ \\[5mm]
+\end{tabular}
+\end{center}
+The coefficients of the depressed polynomial are given by the usual formulas,\footnote{\begin{align*}
+p & = \frac{a_1}{a_3} - \frac{1}{3} \left(\frac{a_2}{a_3}\right)^2 \\
+q & = \frac{a_0}{a_3} - \frac{1}{3} \frac{a_1 a_2}{a_3^2} + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3
+\end{align*}}
+and its critical points are $\pm\big(\tfrac{p}{3}\big)^{1/2}$. We make the critical values symmetric around $0$ by post-composing the polynomial with a translation by $-q$.
+\begin{center}
+\begin{tabular}{c|c|c}
+\textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
+$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+\end{tabular}
+\end{center}
+What we do next depends on how many critical points $g$ has.
+\begin{itemize}
+\item[] \textbf{Two distinct critical points}
+
+When $p$ is non-zero, $g$ has two distinct critical points.
+We bring them to $\pm \tfrac{1}{2}$ by pre-composing the polynomial with a scaling by $2\big(\tfrac{p}{3}\big)^{1/2}$.
+Then we bring the critical values to $\pm 1$ by post-composing with
+\begin{center}
+\begin{tabular}{c|c|c}
+\textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
+$\displaystyle \mathsf{M}_{-2i(p/3)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle -2i\left(\frac{p}{3}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & \\[5mm]
+\end{tabular}
+\end{center}
+\end{itemize}
+
+\color{black}
+
+\par\color{RoyalBlue}
 Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
@@
 \[ I_j(z) = \int_{\mathcal{C}_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
-where $\mathcal{C}_j$ is a thimble in $H_{1}^{B,z}$ through a critical point of $f$.
+where $\mathcal{C}_j$ is a thimble in \textcolor{magenta}{$H_{1}^{B,z}$} through a critical point of $f$.
 We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$.
 \footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}
+\color{black}
 Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:
@@
 \end{proof}
-\color{LimeGreen}
-Let $\Omega$ be a simply connected set that touches but does not contain $\zeta = 0$.
-In Theorem~4 of \cite{reg-sing-volterra}, under the additional assumption that $\Omega$ is star-shaped around $\zeta = 0$, we show that an integral equation of a certain form always has a unique solution in the affine subspace
-\[ \zeta^{\tau-1} + \singexpalg{\tau}(\Omega) \]
-of the space $\singexpalg{\tau-1}(\Omega)$, with $\tau \in (0, \infty)$.
-When $\tau$ is non-integer, this subspace has the convenient property that we can pass back and forth between integral and differential equations without worrying about boundary conditions.
-We use this fact in Sections~\textcolor{magenta}{(?)}\;--\;\textcolor{magenta}{(?)} to find explicit expressions for the integral equation solutions described above.
-
-%%As we saw in Sections~\ref{laplace:ordinary} and \ref{sec:reg-decay}, the function spaces $\singexpalg{\sigma}(\Omega)$ with $\sigma > -1$ are natural domains for the Laplace transform.
-When $\sigma$ is non-integer, these spaces have the convenient property that
-%---------
-%A function is {\em regular} at $\zeta = 0$ if it extends holomorphically over that point. %We will say a function is {\em slight} at $\zeta = 0$ if it can be written as 
-%\begin{equation}\label{eqn:slight-definition}
-%\zeta^{\alpha_1} f_1 + \ldots + \zeta^{\alpha_r} f_r + g
-%\end{equation}
-%where $f_1, \ldots, f_r$ are regular, $\alpha_1, \ldots, \alpha_r \in \R \smallsetminus \Z$, and $g, g', g'', \ldots$ go to zero at $\zeta = 0$.
-\color{RoyalBlue}
-As we've seen in Section~\ref{sec:reg-decay}, functions in $\singexpalg{\sigma}(\Omega)$ with $\sigma>-1$ play a special role in Laplace transform methods for linear differential equations.
-This is because differential equations in the frequency domain arise most naturally from integral equations in the spatial domain, but we would like to work with differential equations in the spatial domain too.
-In $\singexpalg{\sigma}(\Omega)$, differential and integral equations enjoy their simplest equivalence.
-\color{black}
-\begin{prop}%%\label{prop:shifting}
-Let $\psi\in\singexpalg{\sigma}(\Omega)$, and $\sigma>-1$
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi = 0, \]
-where $h_n, \ldots, h_{-m}$ are holomorphic functions.
-\end{prop}
-%To prove this result, we will need a little background.
-
-%Each slight function has a unique {\em normal form}: an expression of the form (\ref{eqn:slight-definition}) where $\alpha_1, \ldots, \alpha_r$ are distinct modulo $\Z$ and $f_1, \ldots, f_r$ are non-vanishing at $\zeta = 0$.
-The {\em order} of a slight function is the smallest power $\alpha_k$ in its normal form.
-If there are no $\zeta^\alpha f$ terms, we say the order is $\infty$.
-A slight function vanishes at $\zeta = 0$ if and only if its order is positive, and it is locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-
-%Multiplication by a regular function and differentiation with respect to $\zeta$ both preserve the space of slight functions.
-Integration from $\zeta = 0$ preserves the space of locally integrable slight functions.
-Thus, in general, integro-differential operators with regular coefficients send locally integrable slight functions to slight functions.
-Each basic operation has a simple effect on a slight function's order.
-Multiplication by $\zeta^n f$, where $f$ is regular and non-vanishing at $\zeta = 0$, adds $n$ to the order.
-Differentiation and integration add $-1$ and $1$, respectively.
-
-\begin{proof}%[Proof of Proposition~\ref{prop:shifting}]
-The reverse implication holds without any special condition on $\psi$, because $\tfrac{\partial}{\partial \zeta}\;\fracderiv{-1}{\zeta}{0}$ acts as the identity on all differentiable functions.
-
-To prove the forward implication, rewrite the first equation in the statement as
-\begin{equation}%%\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
-\end{equation}
-The function
-\[ \phi = \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-belongs to the function space $\singexpalg{\sigma}(\Omega)$.
-Looking at the right-hand side of equation~\eqref{eqn:diff-int-split}, we can see that $\phi'$ belongs to $\singexpalg{\sigma}(\Omega)$, and by assumption its order is greater than $-1$.
-Hence \textcolor{orange}{[I think this is the implication thtat fails when $\phi$ has a constant term]}, $\phi$ belongs to $\singexpalg{\sigma+1}(\Omega)$, which means it vanishes at $\zeta = 0$.
-
-Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;\phi = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi. \]
-Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ \phi = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \psi, \]
-which rearranges to the second equation in the statement.
-\end{proof}
-
 \newpage
-
 \bibliographystyle{plain}
 \bibliography{airy-resurgence}
-
 \end{document}

### 2024-04-03 exp-resurgence.tex
Commit detailed version of third-order thimble integrals

@@
 \item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
+In this case, we say $\series{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
 \end{enumerate}
@@
 & & \\
-\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \tilde{\phi} \arrow[ll, mapsto, "\text{sum}"] 
+\hat{\phi} \arrow[uu, mapsto, "\laplace_b^\theta"] & & \series{\phi} \arrow[ll, mapsto, "\text{sum}"] 
 \end{tikzcd}
@@
 \textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\tilde{\Phi}$ and $\tilde{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\tilde{\Phi}$ (i.e.
+Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\series{\Phi}$ and $\series{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\series{\Phi}$ (i.e.
 it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\tilde{\Phi}$, then $\tilde{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\tilde{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\tilde{\Phi}$ is the natural holomorphic function asymptotic to $\tilde{\Phi}$.]}
+P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\series{\Phi}$, then $\series{\Phi}$ is of Gevrey type.
+In addition, every Gevrey type series $\series{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
+When it is defined, the Borel sum of $\series{\Phi}$ is the natural holomorphic function asymptotic to $\series{\Phi}$.]}
 %\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
@@
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
-of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
+of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}
@@
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
-\item\label{part-2} The Borel transform $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3} The sum of $\tilde{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+\item\label{part-2} The Borel transform $\series{\iota}_\alpha \defeq \borel_\zeta \series{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3} The sum of $\series{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
 Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.
@@
 %\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
- %   Let $\tilde{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
+ %   Let $\series{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
 %\begin{enumerate}
-%\item The series $\tilde{\Phi}_j:=z^{1/2} \tilde{I}_j$ is $1$-Gevrey, thus $\tilde{\phi}_j(\zeta)\defeq\borel_\zeta(\tilde{\Phi}_j)$ converges near $\zeta=\alpha_j$
-%\item If you continue the sum of $\tilde{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
+%\item The series $\series{\Phi}_j:=z^{1/2} \series{I}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\series{\Phi}_j)$ converges near $\zeta=\alpha_j$
+%\item If you continue the sum of $\series{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
 %\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
@@
 %\begin{tikzcd}
-%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \tilde{I}\arrow[dd,"\borel"]\\
+%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \series{I}\arrow[dd,"\borel"]\\
 %& & &\\
-%\iota \arrow[r,equal] & \hat{\iota} & &\tilde{\iota} \arrow[ll, "\text{sum}"]
+%\iota \arrow[r,equal] & \hat{\iota} & &\series{\iota} \arrow[ll, "\text{sum}"]
 %\end{tikzcd}
@@
 Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain.
-Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\tilde{\iota}$.
+Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\series{\iota}_\alpha$.
 
@@
 %\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\tilde{\Psi}_1,...,\tilde{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
+%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
 %\begin{equation}
 %\label{formal solution}
-%\tilde{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
+%\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
 %\end{equation}
@@
 (proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\tilde{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
+%\item {[Thm 2]}: The Borel sum of the formal solutions $\series{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
 %\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
@@
 %& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \tilde{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
+%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \series{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
 %& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \tilde{\phi}\arrow[llu, no head, tail]
+%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \series{\phi}\arrow[llu, no head, tail]
 %\end{tikzcd}
@@
 %\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \tilde{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
+%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \series{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
 %& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \tilde{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
+%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \series{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
 %\end{tikzcd}
@@
 In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}).
-Then, the Ramis Index Theorem shows that the formal solutions $\tilde{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
-\textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]} Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.
+Then, the Ramis Index Theorem shows that the formal solutions $\series{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.
 
@@
 \color{RoyalBlue}
-From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\tilde{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\tilde{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Since the cirtical values are distinct, the transmonomials $\tilde{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame.
+From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\series{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\series{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Since the cirtical values are distinct, the transmonomials $\series{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame.
 Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}).
 To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-For example, the Ramis Index Theorem shows that the $\tilde{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+For example, the Ramis Index Theorem shows that the $\series{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
 \textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}
@@
 At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
-This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\tilde{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}).
+This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}).
 Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
@@
 %
-\textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
+% \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
 Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$.
@@
 
-\color{NavyBlue}
-Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
+Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less, as in Figure~\ref{fig:sectorial_domain-pos-fre}.
 In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
 Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\Omega_\alpha)$ into a Banach space.
+The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
 \textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.} \textcolor{orange}{Note that these results don't depend on which cotangent fiber we're mapping into.
 $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.}
+\begin{todo}
+\begin{center}
+\begin{tikzpicture}
+\setfiberscale{2.5}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\renewcommand{\phase}{35}
+\newcommand{\radius}{0.85}
+\begin{fiber}
+%\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
+\fill[pwbeige!30, bezier bounding box, path fading=radial edge]
+  (-4, -4) (4, 4)
+  (0, 0) -- (41:4) arc (41:-48:4) -- cycle;
+\genfibercontent
+%\draw (0, 0) -- (0.75, 0);
+%\draw[ray] (0, 0) -- (\phase:\rshade);
+%\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
+\node[anchor=-10, inner sep=2mm] at (0,0) {$\zeta = \alpha$};
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
+\end{fiber}
+\end{tikzpicture}
+\hspace{5mm}
+\begin{tikzpicture}
+\setfiberscale{2.5}
+\renewcommand{\phase}{35}
+\newcommand{\dis}{1.2}
+\begin{fiber}[shade, phase=\phase, dis=\dis]
+\genfibercontent[dual]
+\node[anchor=-10, inner sep=2mm] at (0,0) {$z = 0$};
+\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
+\end{fiber}
+\end{tikzpicture}
+\captionof{figure}{On the left, the sectorial domain $\Omega_\alpha$. On the right the domain $\Omega_\alpha^\Lambda$ \textcolor{orange}{Fix the figure}.}\label{fig:sectorial_domain-pos-fre}
+\end{center}
+\end{todo}
+%
 \begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
 Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, with a norm of at most $\Gamma(\sigma)$.
+For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
 \end{prop}
@@
 \begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
-& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& \le \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
+|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
+& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
 \end{align*}
@@
 \begin{align*}
-|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta, \alpha}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
+|\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
 & = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
@@
 \[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
-In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$ defined above, this bound says that
+In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
 \[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
@@
 \end{proof}
+\color{NavyBlue}
 \begin{prop}\label{prop:inverse_laplace_analytic}
@@
 Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+%
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left \textcolor{orange}{[can we add a figure to explain how we get a path?]}.
 Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
@@
 \[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz. \]
-When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\Omega_\alpha)$, we have the bound
+When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound
 \begin{align*}
@@
     \begin{align*}
-    |\tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
-        &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
-        &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-        &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+    |\series{\phi}\ast\series{\psi}|&=\left|\int_0^\zeta\series{\phi}(\zeta-\zeta')\series{\psi}(\zeta')\, d\zeta'\right|\\
+        &\le \int_0^\zeta |\series{\phi}(\zeta-\zeta')||\series{\psi}(\zeta')|\, d\zeta'\\
+        &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+        &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\series{\psi}||_{\sigma,\Lambda} ||\series{\phi}||_{\sigma,\Lambda}. 
     \end{align*}
@@
 The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
-    \[\borel_\zeta(\tilde{\Phi}\tilde{\Psi})=\borel_\zeta\tilde{\Phi}\ast\borel_\zeta\tilde{\Psi}.\]
+    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi}\ast\borel_\zeta\series{\Psi}.\]
 \end{prop}
@@
 &=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
-&=\borel_\zeta\tilde{\Phi}\ast \borel_\zeta\tilde{\Psi}\,.
+&=\borel_\zeta\series{\Phi}\ast \borel_\zeta\series{\Psi}\,.
 %&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
@@
 \end{proof}
-% Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is
-%  \[\tilde{\psi}\ast\tilde{\phi}=\borel_\zeta(\tilde{\Psi}\tilde{\Phi}).\]
+% Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is
+%  \[\series{\psi}\ast\series{\phi}=\borel_\zeta(\series{\Psi}\series{\Phi}).\]
 %  Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
-% Furthermore, since $\tilde{\phi},\tilde{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
+% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
 % \end{definition}
@@
 % \begin{lemma}
-% Let $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\tilde{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\tilde{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
+% Let $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
+Then, $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\series{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
 % \end{lemma}
@@
 % \begin{definition}{(see \cite[Definition 5.12]{diverg-resurg-i})}
-%     Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=0$.
-Then, the convolution product of $\tilde{\phi}:=\borel_\zeta\tilde{\Phi}$ and $\tilde{\psi}:=\borel_\zeta\tilde{\Psi}$ is defined as
-% \[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
-% Furthermore, since $\tilde{\phi},\tilde{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\tilde{\psi}\ast\tilde{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
+%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=0$.
+Then, the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is defined as
+% \[\borel_\zeta(\series{\Psi}\series{\Phi})=:\series{\psi}\ast\series{\phi}.\]
+% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
 % \end{definition}
@@
 % \begin{definition}
-%     Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=\alpha$.
-Then, the convolution product of $\tilde{\phi}:=\borel_{\zeta_\alpha}\tilde{\Phi}$ and $\tilde{\psi}:=\borel_{\zeta_\alpha}\tilde{\Psi}$ is defined as
-% \[\borel_{\zeta_\alpha}(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast_{\zeta_\alpha,0}\tilde{\phi}.\]
-% Furthermore, the sum of $\tilde{\psi}\ast_{\zeta_\alpha,0}\tilde{\phi}$ is the convolution $\hat{\psi}\ast_{\zeta_\alpha,0}\hat{\phi}$. 
+%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=\alpha$.
+Then, the convolution product of $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$ and $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ is defined as
+% \[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}.\]
+% Furthermore, the sum of $\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}$ is the convolution $\hat{\psi}\ast_{\zeta_\alpha,0}\hat{\phi}$. 
 % \end{definition}
@@
 \subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
-The convolution product is compatible with the change of translation chart: if $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
+The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
 \[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
-Furthermore, we can extend the previous definition to trans-series: let $\tilde{\Phi}, \tilde{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
+Furthermore, we can extend the previous definition to trans-series: let $\series{\Phi}, \series{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
 Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
@@
 \end{equation}
-where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\tilde{\phi}$ and $\tilde{\psi}$ in a neighbourhood of $\zeta=\alpha$.
+where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighbourhood of $\zeta=\alpha$.
 
@@
 where in the last step we used the properties of $\borel_\zeta$ acting on transseries (see Section~\ref{sec:action_transseries}).
-More generally, if $\borel_\zeta\tilde{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
+More generally, if $\borel_\zeta\series{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
 \begin{remark}
@@
 %\begin{proof}
- %   Let $\tilde{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ %with $|a_n|\leq A^n n!$ and $A>0$ then  
+ %   Let $\series{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ %with $|a_n|\leq A^n n!$ and $A>0$ then  
 %\begin{align*}
-%\borel_\zeta (z^{-\tau}\tilde{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
+%\borel_\zeta (z^{-\tau}\series{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
 %&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\int_0^\zeta\sum_{n\geq 0}\frac{a_{n+1}}{n!}(\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
@@
 %\end{align*}  
-%where in the third step we use that the Borel transform of $\tilde{\Phi}$ is convergent in a neighbourhood of $\zeta=0$.
+%where in the third step we use that the Borel transform of $\series{\Phi}$ is convergent in a neighbourhood of $\zeta=0$.
 and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
@@
 %
+\textcolor{red}{[Introduce the domain $\Omega$]}
 The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
@@
 \end{tikzpicture}
+\captionof{figure}{The domain $\Upsilon$ at $\zeta=\alpha$.}\label{fig:domain_Upsilon}
 \end{center}
@@
 Taylor expansion and summation form a two-way link between holomorphic functions and formal power series.
-For regular enough functions, the Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain.
+For regular enough functions, the formal Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain.
 \begin{todo}[Compare with Sokal's version of the Watson--Nevanlinna theorem?]\end{todo}
 \begin{lemma}\label{lem:laplace-bridge}
-Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less.
+Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less \begin{todo}(see Figure~\ref{fig:sectorial_domain-pos-fre} on the left)\end{todo}.
 Take some $\rho \in (-1,\infty)$.
 If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
-\textcolor{orange}{[Define formal Laplace transform into transmonomial spaces?]}
 \end{lemma}
@@
 \begin{proof}
-By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
+By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}.
 Write $\series{\varphi}$ out in the form
@@
 
-%Let $\tilde{\Phi}, \tilde{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
-%\[\borel_\zeta(\tilde{\Psi}\tilde{\Phi})=:\tilde{\psi}\ast\tilde{\phi}.\]
+%Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
+%\[\borel_\zeta(\series{\Psi}\series{\Phi})=:\series{\psi}\ast\series{\phi}.\]
 %In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
@@
 %\begin{proof}
-%    Let $\tilde{\phi},\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\tilde{\phi}\ast\tilde{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
+%    Let $\series{\phi},\series{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\series{\phi}\ast\series{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
 %\begin{verify}
  %   \begin{align*}
-  %      | \tilde{\phi}\ast\tilde{\psi}|&=\left|\int_0^\zeta\tilde{\phi}(\zeta-\zeta')\tilde{\psi}(\zeta')\, d\zeta'\right|\\
-   %     &\le \int_0^\zeta |\tilde{\phi}(\zeta-\zeta')||\tilde{\psi}(\zeta')|\, d\zeta'\\
-    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-    %    &\le ||\tilde{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\tilde{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\tilde{\psi}||_{\sigma,\Lambda} ||\tilde{\phi}||_{\sigma,\Lambda}. 
+  %      | \series{\phi}\ast\series{\psi}|&=\left|\int_0^\zeta\series{\phi}(\zeta-\zeta')\series{\psi}(\zeta')\, d\zeta'\right|\\
+   %     &\le \int_0^\zeta |\series{\phi}(\zeta-\zeta')||\series{\psi}(\zeta')|\, d\zeta'\\
+    %    &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+    %    &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
+    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\series{\psi}||_{\sigma,\Lambda} ||\series{\phi}||_{\sigma,\Lambda}. 
     %\end{align*}
@@
 
-In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}$ \textcolor{magenta}{[needs domain]} with $\sigma>-1$ and $\Lambda>0$.
+In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
 \begin{definition}
@@
 \begin{prop}\label{prop:frac-der-int-borel}
-Let $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\tilde{\Phi}$, then %and $\tilde{\phi}\defeq\borel_\zeta\tilde{\Phi}$
+Let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\series{\Phi}$, then %and $\series{\phi}\defeq\borel_\zeta\series{\Phi}$
 \begin{itemize}
-\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \tilde{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
-\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \tilde{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
-\item[(iii)] let $k\in\Z_{\ge 0}$ and $\tilde{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \tilde{\Phi}\big]=(-\zeta)^k\borel_\zeta\tilde{\Phi}$.\footnote{This property holds more generally for $\tilde{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
+\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \series{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
+\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
+\item[(iii)] let $k\in\Z_{\ge 0}$ and $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$.\footnote{This property holds more generally for $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
 \end{itemize} 
@@
 \[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
-Hence, if $\tilde{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\tilde{\Phi}$
-\[\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\fracderiv{\lambda}{\zeta}{0}\series{\Phi}\]
-where in the last step, we use that $\borel_\zeta\tilde{\Phi}$ is convergent.
+Hence, if $\series{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\series{\Phi}$
+\[\borel_\zeta \big[z^\lambda \series{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\fracderiv{\lambda}{\zeta}{0}\series{\Phi}\]
+where in the last step, we use that $\borel_\zeta\series{\Phi}$ is convergent.
 
@@
 \begin{align*}
-\borel_\zeta\big[\partial_z^k\tilde{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
+\borel_\zeta\big[\partial_z^k\series{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
 &=(-1)^k \sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!}\frac{\zeta^{n+k-1}}{(n+k-1)!}\\
 &=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
-&=(-\zeta)^k\borel_\zeta \tilde{\Phi}
+&=(-\zeta)^k\borel_\zeta \series{\Phi}
 \end{align*}
@@
 % We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\lambda\in\R\setminus\Z_{>0}$ 
-% \[\fracderiv{\lambda}{\zeta}{0}\big[\borel_\zeta\tilde{\Phi}\big]=\borel_\zeta \big[z^\lambda \tilde{\Phi}\big]=\borel_\zeta (z^\lambda)\ast \borel_\zeta\tilde{\Phi}.\]
+% \[\fracderiv{\lambda}{\zeta}{0}\big[\borel_\zeta\series{\Phi}\big]=\borel_\zeta \big[z^\lambda \series{\Phi}\big]=\borel_\zeta (z^\lambda)\ast \borel_\zeta\series{\Phi}.\]
 % \begin{verify}
 % \begin{align*}
-% \fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\borel_\zeta (z^\tau \tilde{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\tilde{\Phi}\\
+% \fracderiv{\tau}{\zeta}{0}\borel_\zeta\series{\Phi}=\borel_\zeta (z^\tau \series{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\series{\Phi}\\
 % &=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
@@
 % \[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
-% therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\tilde{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\tilde{\Phi}$. 
+% therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\series{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\series{\Phi}$. 
 % \end{verify}
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-\color{NavyBlue}
-\textcolor{PaleVioletRed}{[Revised flavor text.]}
 In Section~\ref{sec:regularity-results}, we show that linear level~1 ODEs of a certain form always have Borel regular solutions, indexed by the characteristic roots of their constant-coefficient parts.
@@
 Using the existence and uniqueness results that characterize the Borel regular solutions, we give a new proof that Poincar\'{e}'s solutions are Borel summable.
-\color{black}
+%
 \subsubsection{Regularity results}\label{sec:regularity-results}
@@
 %%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, does not touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
-\textcolor{orange}{[Introduce $\hat{\mathcal{P}}_\alpha$?]} \textcolor{orange}{[Transition text]}
+For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
+\begin{equation}\label{eq:hat_P}
+    \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1})
+\end{equation}
+From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
+ \textcolor{orange}{[Transition text]}
 %%%\begin{itemize}
@@
 \begin{center}
-%\begin{figure}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
-
-{\small The domain $\Omega_\alpha$ \textcolor{orange}{[Cite as ``the figure after Lemma~***]}}
-%\end{figure}
+\captionof{figure}{The sectorial domain $\Omega_\alpha$.}\label{fig:sectorial_domain--with roots P}
 \end{center}
@@
 Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{re:thm:exist_uniq_ODE}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
-By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace \textcolor{orange}{[use $\zeta_\alpha$ in place of $\zeta$ throughout proof]}
+By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
@@
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
-We will do this by showing that $\psi_\alpha$ lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
+We will do this by showing that $\psi_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
 
@@
 Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
-\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right) \]
+\[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta_\alpha\right) \]
 lies in the space $\singexpalg{\tau_\alpha - 1}(\Upsilon)$ and satisfies the equation $\solproto = \hardpart^\alpha \solproto$.
@@
 \textcolor{orange}{[Add flavor text]}
+\color{RoyalBlue}
 \begin{theorem}[restatement of \ref{thm:soln_is_asymptotic}]\label{re:thm:soln_is_asymptotic}
@@
 \end{theorem}
+\color{black}
+\begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is Borel regular.
+This is because $\Psi_\alpha$ is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
+\end{corollary}
 \begin{proof}
@@
 \begin{proof}
-By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator described in equation~\textcolor{magenta}{\textbf{(?)}}.
+By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator\eqref{eq:hat_P}.
 By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$.
@@
 We will now prove that $I_\alpha$ is Borel regular:
-\begin{theorem}\label{thm:maxim-proof}
+\begin{theorem}[restatement of~\ref{thm:maxim}]\label{thm:maxim-proof}
 If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: 
-\textcolor{orange}{[Change statement as in Intoduction]}
 \begin{enumerate}
 \item\label{part-1-prf} The function $I_\alpha$ has an asymptotic expansion $\series{I}_\alpha \defeq \aexp^\theta I_\alpha$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_\alpha$ that defines the thimble.
-\item\label{part-2-prf} The Borel transform $\tilde{\iota}_\alpha \defeq \borel_\zeta \tilde{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3-prf} By continuing the sum of $\tilde{\iota}_\alpha$ along the ray $\mathcal{J}_\alpha^\theta$, and taking its Laplace transform along that ray, we recover $I_\alpha$.
+Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
+\item\label{part-2-prf} The Borel transform $\series{\iota}_\alpha \defeq \borel_\zeta \series{I}_\alpha$ converges near $\zeta=\alpha$.
+\item\label{part-3-prf} The sum of $\series{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.
 \end{enumerate}
@@
 \[ e^{z\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
-Hence, defining the formal series $\tilde{I}_\alpha$
-\[\tilde{I}_\alpha(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
-we get $\tilde{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1-prf}.
+Hence, defining the formal series $\series{I}_\alpha$
+\[\series{I}_\alpha(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
+we get $\series{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1-prf}.
 
@@
 \begin{align*}
-\tilde{\iota}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
+\series{\iota}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
 &= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
 \end{align*}
-We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\tilde{\iota}$ has a finite radius of convergence.
+We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence.
 This ends the proof of part~\ref{part-2-prf}.
-%$|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\tilde{I}_j$ is $1$-Gevrey.
-
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\tilde{\iota}_\alpha$.
+%$|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\series{I}_j$ is $1$-Gevrey.
+
+\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\series{\iota}_\alpha$.
 We can rewrite the Taylor series for $\nu$ as
@@
 \end{align*}
-In particular, $\tilde{\iota}_\alpha$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
+In particular, $\series{\iota}_\alpha$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
 %Thus, we can take the Laplace transform of $\phi_j$ and we find
@@
 \textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there is one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
-The proof follows the same argument we chose for $I_\alpha$, but there is one subtlety to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
+The proof follows the same argument we use in the proof on Theorem~\ref{thm:maxim-proof} for $I_\alpha$, but there is one subtlety to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
 Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota_\alpha \]
@@
 Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
-\begin{figure}
-\center
 \begin{center}
@@
 \end{tikzpicture}
+\captionof{figure}{The domain $\Omega_\alpha$}\label{Fig:slit domain}
 \end{center}
-\caption{The domain $\Omega_\alpha$}\label{Fig:slit domain}
-\end{figure}
+
 Let us calculate the jump of $\int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
@@
 and it is 
-which turns out to be proportional to $\tilde{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
+which turns out to be proportional to $\series{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
 %We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
@@
 \begin{proof}
-    Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\tilde{I}_j$, namely 
+    Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\series{I}_j$, namely 
     \[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
@@
 \end{itemize}
-Next, we specialize to the case where $X$ is the complex plane, with standard coordinate $u$, and $\nu = du$.
+Next, we specialize to the case where $X$ is the complex plane and $\nu = du$, where $u$ is the standard coordinate.
 The affine group of $\C$ now acts on $f$ by pre-composition as well.
@@
 When $p$ is non-zero, $g$ has two distinct critical points.
-We bring them to $\pm \tfrac{1}{2}$ by pre-composing the polynomial with a scaling by $2\big(\tfrac{p}{3}\big)^{1/2}$.
-Then we bring the critical values to $\pm 1$ by post-composing with
+We can use our symmetries turn it into any other third-degree polynomial with distinct critical points.
+To illustrate, we will turn $g$ into the Chebyshev polynomial $T_3$ by moving its critical points to $\pm\tfrac{1}{2}$ and its critical values to $\pm 1$.
+
+\textcolor{RoyalBlue}{We bring them to $\pm \tfrac{1}{2}$ by pre-composing the polynomial with a scaling by $2\big(\tfrac{p}{3}\big)^{1/2}$.
+Then we bring the critical values to $\pm 1$ by post-composing with}
 \begin{center}
@@
 The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
-% %The main idea of resurgence is that studying the analytic continuation of $\tilde{\phi}_\omega$
+% %The main idea of resurgence is that studying the analytic continuation of $\series{\phi}_\omega$
 
@@
 \begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\tilde{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\series{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
+\series{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
 \end{align*}  
@@
 \end{equation}
-More generally, if $\tilde{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
+More generally, if $\series{\Phi}(z)\in z^{-1}\C \llbracket z^{-1} \rrbracket$, i.e. it has no constant term, then
 
 \begin{equation}
-\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\tilde{\Phi}=\borel\tilde{\Phi}.
+\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\series{\Phi}=\borel\series{\Phi}.
 \end{equation}
@@
 He considers the formal power series  
-\[\tilde{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
+\[\series{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
 such that
 \begin{align*}
-\tilde{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
-\tilde{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\tilde{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
+\series{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\series{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
+\series{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\series{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
 \end{align*} 
@@
 
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\tilde{\Phi}_{\pm}$ as a convolution product:
-
-\begin{align*}
-\hat{\phi}_+(\zeta):=\borel\tilde{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\tilde{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
+By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
+
+\begin{align*}
+\hat{\phi}_+(\zeta):=\borel\series{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\series{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
 \end{align*}
@@
 
-%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\tilde{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
+%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\series{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
 %
 %\begin{align*}
-%\tilde{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\tilde{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
+%\series{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
+%\series{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
 %\end{align*}
@@
 Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see \cite[Lemma 6.106]{diverg-resurg-i}).
-%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\tilde{\phi}_{\pm}(\zeta)$ are evident.
+%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\series{\phi}_{\pm}(\zeta)$ are evident.
 
@@
 
-\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, and a power $\rho \in \R \smallsetminus \Z$.
+\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}, and a power $\rho \in \R \smallsetminus \Z$.
 As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.}

### 2024-04-04 exp-resurgence.tex
Finish third-degree thimble integral
There are still some minor inconsistencies and things to be checked.

@@
 equation~\eqref{eqn:bessel_rescaled_ex} is an example.
-More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form \textcolor{PaleVioletRed}{[I just noticed we use $\partial_z$ instead of $\tfrac{\partial}{\partial z}$ in \texttt{reg-sing-volterra}, where these equations were copied from.
-Could we switch to $\tfrac{\partial}{\partial z}$, as I've done provisionally?]}
+More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
 \[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
@@
 %
-% \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
+%% \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
 Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$.
@@
 Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
-
-Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less, as in Figure~\ref{fig:sectorial_domain-pos-fre}.
-In this case, for any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
-Then, let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
-\textcolor{orange}{Cite \cite{sternin1995borel} better for the theorem.} \textcolor{orange}{Note that these results don't depend on which cotangent fiber we're mapping into.
-$\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.}
+%%
+Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
+For any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
 \begin{todo}
@@
 \begin{tikzpicture}
-\setfiberscale{2.5}
+\setfiberscale{2}
 \pgfmathsetmacro{\rshade}{1.5*\rfiber}
-\renewcommand{\phase}{35}
-\newcommand{\radius}{0.85}
+\newcommand{\dis}{1}
+\renewcommand{\phase}{0}
+\newcommand{\spread}{30}
+
 \begin{fiber}
-%\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
-\fill[pwbeige!30, bezier bounding box, path fading=radial edge]
-  (-4, -4) (4, 4)
-  (0, 0) -- (41:4) arc (41:-48:4) -- cycle;
+\fill[pwbeige!30, draw=pwbeige!60] (0, 0) -- (\phase-\spread:1.5*\rshade) -- (\phase+\spread:1.5*\rshade) -- cycle;
 \genfibercontent
-%\draw (0, 0) -- (0.75, 0);
-%\draw[ray] (0, 0) -- (\phase:\rshade);
-%\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
-\node[anchor=-10, inner sep=2mm] at (0,0) {$\zeta = \alpha$};
+\node[anchor=-11, inner sep=2mm] at (0,0) {$\zeta = \alpha$};
 \node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
 \end{fiber}
-\end{tikzpicture}
-\hspace{5mm}
-\begin{tikzpicture}
-\setfiberscale{2.5}
-\renewcommand{\phase}{35}
-\newcommand{\dis}{1.2}
-\begin{fiber}[shade, phase=\phase, dis=\dis]
+
+\begin{scope}[shift={(5.5, 0)}]
+\begin{fiber}[phase=\phase, dis=\dis]
+\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
 \genfibercontent[dual]
-\node[anchor=-10, inner sep=2mm] at (0,0) {$z = 0$};
-\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
+%%\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
 \node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
 \end{fiber}
+\end{scope}
 \end{tikzpicture}
-\captionof{figure}{On the left, the sectorial domain $\Omega_\alpha$. On the right the domain $\Omega_\alpha^\Lambda$ \textcolor{orange}{Fix the figure}.}\label{fig:sectorial_domain-pos-fre}
+\captionof{figure}{A sector $\Omega_\alpha$ in the position domain, and the corresponding union of half-planes $\widehat{\Omega}_\alpha^\Lambda$ in the frequency domain.}\label{fig:sectorial_domain-pos-fre}
 \end{center}
+\end{todo}
+Let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
+\begin{todo}\par
+[Cite \cite{sternin1995borel} better for the theorem.
+Note that these results don't depend on which cotangent fiber we're mapping into.
+$\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
 \end{todo}
@@
 %\color{black}
-\subsubsection{Action on transseries}\label{sec:action_transseries}
+\subsubsection{Action on trans-series}\label{sec:action_transseries}
 %
@@
 \color{RoyalBlue}
-A transseries is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[exponents must lie along a ray]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
+A trans-series is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[exponents must lie along a ray]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
 
@@
 \subsubsection{Regularity results}\label{sec:regularity-results}
-Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
-Let $\mathcal{P}$ be a linear differential operator of the form \textcolor{PaleVioletRed}{[I just noticed we use $\partial_z$ instead of $\tfrac{\partial}{\partial z}$ in \texttt{reg-sing-volterra}, where these equations were copied from.
-Could we switch to $\tfrac{\partial}{\partial z}$, as I've done provisionally?]}
+Let us recall the setting from Section~\ref{borel-reg:explanatory-power}. Let $\mathcal{P}$ be a linear differential operator of the form 
 \begin{equation}\label{eqn:operator-P}
@@
 and use the group actions from Section~\ref{sec:int-symm} to reduce it to its two essential cases.
-Our first move is to bring the polynomial into depressed form by post-composing it with a scaling by $\tfrac{1}{a_3}$ and pre-composing it with a translation by $\tfrac{1}{3} \tfrac{a_2}{a_3}$.
+We first put $g$ in depressed form by scaling the leading coefficient to $1$ and translating the mean of the critical points to $0$.\footnote{The coefficients of the depressed form are related to the original coefficients as follows:
+\begin{align*}
+p & = \frac{a_1}{a_3} - \frac{1}{3} \left(\frac{a_2}{a_3}\right)^2 \\
+q & = \frac{a_0}{a_3} - \frac{1}{3} \left(\frac{a_1}{a_3}\right)\left(\frac{a_2}{a_3}\right) + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3.
+\end{align*}} We then also translate the mean of the critical values to $0$.
 \begin{center}
@@
 \textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-$\displaystyle f \mapsto f/a_3$ & $\displaystyle u^3 + \frac{a_2}{a_3} u^2 + \frac{a_1}{a_3} u + \frac{a_0}{a_3}$ & $\displaystyle I\left(\frac{z}{a_3}\right)$ \\[5mm]
-$\displaystyle \mathsf{T}_{a_2/3a_3}^*$ & $\displaystyle u^3 + pu + q$ & $\displaystyle I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle f \mapsto \frac{f}{a_3}$ & $\displaystyle u^3 + \frac{a_2}{a_3} u^2 + \frac{a_1}{a_3} u + \frac{a_0}{a_3}$ & $\displaystyle \hphantom{e^{qz}} I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle \mathsf{T}_{(1/3)\,a_2/a_3}^*$ & $\displaystyle u^3 + pu + q$ & $\displaystyle \hphantom{e^{qz}} I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
 \end{tabular}
 \end{center}
-The coefficients of the depressed polynomial are given by the usual formulas,\footnote{\begin{align*}
-p & = \frac{a_1}{a_3} - \frac{1}{3} \left(\frac{a_2}{a_3}\right)^2 \\
-q & = \frac{a_0}{a_3} - \frac{1}{3} \frac{a_1 a_2}{a_3^2} + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3
-\end{align*}}
-and its critical points are $\pm\big(\tfrac{p}{3}\big)^{1/2}$. We make the critical values symmetric around $0$ by post-composing the polynomial with a translation by $-q$.
+Our next move depends on how many critical points $g$ has.
+\begin{itemize}
+\item[] \textbf{Two distinct critical points}
+
+When $p$ is non-zero, $g$ has two distinct critical points.
+We can use our symmetries turn it into any other third-degree polynomial with distinct critical points.
+To illustrate, we turn $g$ into the Chebyshev polynomial $T_3$ by scaling and rotating its critical points to $\pm\tfrac{1}{2}$ and its critical values to $\pm 1$.
 \begin{center}
@@
 \textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & $\displaystyle 4u^3 - 3u$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right)$ \\[5mm]
 \end{tabular}
 \end{center}
-What we do next depends on how many critical points $g$ has.
-\begin{itemize}
-\item[] \textbf{Two distinct critical points}
-
-When $p$ is non-zero, $g$ has two distinct critical points.
-We can use our symmetries turn it into any other third-degree polynomial with distinct critical points.
-To illustrate, we will turn $g$ into the Chebyshev polynomial $T_3$ by moving its critical points to $\pm\tfrac{1}{2}$ and its critical values to $\pm 1$.
-
-\textcolor{RoyalBlue}{We bring them to $\pm \tfrac{1}{2}$ by pre-composing the polynomial with a scaling by $2\big(\tfrac{p}{3}\big)^{1/2}$.
-Then we bring the critical values to $\pm 1$ by post-composing with}
-\begin{center}
-\begin{tabular}{c|c|c}
-\textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-$\displaystyle \mathsf{M}_{-2i(p/3)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle -2i\left(\frac{p}{3}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
-$f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & \\[5mm]
-\end{tabular}
-\end{center}
+We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel}:
+\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
+From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
+\[\left[\left(\frac{\partial}{\partial z}\right)^2 + 2\left(\frac{q}{a_3}\right)\frac{\partial}{\partial z} + \frac{1}{a_3^2} \left(\frac{4p^3}{27} + q^2\right) + \frac{1}{z} \left(\frac{\partial}{\partial z} + \frac{q}{a_3}\right) - \frac{1}{9z^2}\right] \Phi = 0.\]
+\begin{verify}
+\[\left[a_3^2 \left(\frac{\partial}{\partial z}\right)^2 + 2a_3 q \frac{\partial}{\partial z} + \left(\frac{4p^3}{27} + q^2\right) + \frac{a_3}{z} \left(a_3\frac{\partial}{\partial z} + q\right) - \frac{a_3^2}{9z^2}\right] \Phi = 0.\]
+\end{verify}
+\item[] \textbf{One degenerate critical point}
+
+When $p$ is zero, $g$ has a single degenerate critical point.
+Like we did in Appendix~\ref{airy-appendix} for the non-degenerate case, we will first study $I(z)$ by viewing it as a solution of an ODE, and we will then confirm our results using the thimble projection formula.
+
+By differentiating under the integral, we can see that $I(z)$ satisfies the equation
+\begin{equation}\label{eqn:degree-3-poly-1root}
+\left[\frac{\partial}{\partial z} + \frac{1}{3z}\right] \Phi = 0.
+\end{equation}
+A function $\laplace_{\zeta,\alpha}^{\theta} v$ satisfies this equation if and only if $v$ satisfies the integral equation
+\[ \left[ -\zeta + \tfrac{1}{3} \partial^{-1}_{\zeta, \alpha} \right] v = 0. \]
+When $\alpha = 0$, this equation has the solution
+\[ v_0 = \zeta^{-2/3}, \]
+whose Laplace transform
+\[ V_0 = \Gamma\big(\tfrac{1}{3})\,z^{-1/3} \]
+must be proportional to $I(z)$.
+
+We can confirm this result, and find the correct normalization, using the thimble projection formula:
+\begin{align*}
+\int_{\mathcal{C}} e^{-zu^3}\,du & = e^{i\pi/3} \int_{\mathcal{J}_{\zeta, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta^{-2/3}\,d\zeta \\
+& = \tfrac{1}{3}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
+\end{align*}
+The factor of $e^{i\pi/3}$ \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta^{-2/3}$ around $\zeta = 0$.
+
+\color{RoyalBlue}
+namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter. 
 \end{itemize}
-
+\subsubsection{Coalescence of critical values}
+We can recover the degenerate case by taking the limit of the non-degenerate case as $p$ goes to zero.
+Rearranging the relationship above between $I(z)$ and the modified Bessel function $K_{1/3}(z)$, we get the formula
+\[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
+Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
+\begin{todo}\par
+[Our treatments of the $e^{qz}$ factor disagree. With this version, the exponential factor goes to $1$ as $p \to 0$, which I think is consistent with the limit to the degenerate case. Comparison:]
+\begin{align*}
+    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\mathcal{C}_+} e^{z (4t^3-3t)} du\\
+    &= 2\sqrt{-\tfrac{p}{3}} \int_{\mathcal{C}_+} e^{z (4t^3-3t)} dt \\
+    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
+\end{align*}
+\end{todo}
+\begin{verify}
+\begin{align*}
+2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big)&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
+&=\frac{2}{3}\pi ip^{1/2}\left[\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{-1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}\right]\\
+&=\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\frac{2\pi }{3\sqrt{3}} e^{2\pi i/3} z^{1/3} p \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}
+\end{align*}
+Now we take the limit as $p\to 0$ and we find 
+\[\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)}=e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}\]
+\end{verify}
 \color{black}
@@
 %\end{equation*}
+\color{RoyalBlue}
 We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.
@@
 namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
+\color{black}
 
@@
     \[ e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) e^{-zq} z^{-1/3}.  \]
-    \begin{verify}
-        \begin{align*}
-            2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big)&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
-            &=\frac{2}{3}\pi ip^{1/2}\left[\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{-1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}\right]\\
-            &=\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\frac{2\pi }{3\sqrt{3}} e^{2\pi i/3} z^{1/3} p \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}
-        \end{align*}
-         Now we take the limit as $p\to 0$ and we find 
-         \[\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)}=e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}\]
-    \end{verify}
+
     From the properties of the Laplace transform, we then deduce

### 2024-04-05 exp-resurgence.tex
Work on Airy-Lucas example

@@
 For any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
-\begin{todo}
 \begin{center}
@@
 \begin{scope}[shift={(5.5, 0)}]
-\begin{fiber}[phase=\phase, dis=\dis]
+\begin{fiber}
 \fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
@@
 \end{center}
-\end{todo}
 Let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
-Choose any $\lambda' > \Lambda$.
+Choose any $\Lambda' > \Lambda$.
 Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
@@
 has a continuous left inverse
-\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\lambda'}(\Omega_\alpha^\varepsilon), \]
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
 with a norm of at most
@@
 Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$.
-Choosing some $\lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
-%
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left \textcolor{orange}{[can we add a figure to explain how we get a path?]}.
-Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
-Along $\mathcal{C}$, we have
+Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
+%
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+\begin{center}
+\begin{tikzpicture}
+\setfiberscale{2.5}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\newcommand{\dis}{1.25}
+\renewcommand{\phase}{0}
+\newcommand{\spread}{30}
+
+\newcommand{\pathdis}{1.5625}
+\newcommand{\pathspread}{20}
+
+\begin{fiber}
+% the region
+\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
+
+% grid lines and stuff
+\genfibercontent[dual]
+
+% the path
+\draw[very thick] (-\phase-\pathspread:\pathdis) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) arc (-\phase-\pathspread:-\phase+\pathspread:\pathdis) -- ++(-\phase+\pathspread+90:\rshade);
+
+% coordinate label
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
+\end{fiber}
+\end{tikzpicture}
+\captionof{figure}{The path $\mathcal{C}$.}
+\end{center}
+Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. Along $\mathcal{C}$, we have
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
@@
 %
-\textcolor{red}{[Introduce the domain $\Omega$]}
+Consider an open set $\Omega \subset \C$ that touches but does not contain $\zeta = 0$.
 The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
 To study Borel summation, however, we also need to take shifted Taylor expansions around $\zeta = 0$, turning holomorphic functions $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$ into convergent power series $\series{\phi} \in \zeta^\rho \C\{\zeta\}$ with $\rho \ge \sigma$.
-When $\Omega$ touches but does not contain $\zeta = 0$, only some of its functions will have shifted Taylor expansions.
-We need a way to make sure we stay in a subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the shifted Taylor series exists.
+The following discussion, leading up to Lemma~\ref{lem:shifted_holo_closed}, will help us stay within a subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the shifted Taylor series exists.
 
@@
 \begin{lemma}\label{lem:laplace-bridge}
-Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less \begin{todo}(see Figure~\ref{fig:sectorial_domain-pos-fre} on the left)\end{todo}.
+Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less\begin{todo}, as illustrated on the position-domain side of Figure~\ref{fig:sectorial_domain-pos-fre} [is it really that helpful to have a picture of this?]\end{todo}.
 Take some $\rho \in (-1,\infty)$.
@@
 We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other root.
+We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
 \textcolor{LimeGreen}{Furthermore, we will show in Section~\ref{bessel-regularity-AL} that $v_\alpha$ can be analytically continued to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$, where $\Omega_\alpha$ is a sector with its tip at $\zeta = \alpha$.}
@@
 \end{alignat*}
-From the argument in Section~\ref{big-idea} \textcolor{magenta}{(!)}, we know that $\laplace^\theta_{\zeta, 1} v_1$ is well-defined, satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
+
+From the expression above, we can see that $v_1$ has only two singularities in the complex plane: one at $\zeta_1 = 0$ from the factor of $\zeta_1^{-1/2}$, and one at $\zeta_1 = -2$ from the hypergeometric function.
+Therefore, $v_1$ is holomorphic throughout the sector $\Omega_1 = \C \smallsetminus \mathcal{J}^\pi_{\zeta_1, 0}$.
+Since $v_1$ has a power law singularity at $\infty$, it is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
+Therefore, it belongs to the space $\singexp{-1/2}{\Lambda}(\Omega_1)$ for all $\Lambda > 0$.
+By thinking about its shifted Taylor expansion around $\zeta_1 = 0$, we can see more precisely that $v_1$ belongs to
+\[ -i\sqrt{2}\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+for all $\Lambda > 0$.
+As discussed in Section~\ref{big-idea}, we conclude that $v_1$ has a well-defined Laplace transform along any ray from $\zeta = 1$ except the one going directly left.
+Its Laplace transform can be written as
+\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
+where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
+%%From the argument in Section~\ref{big-idea} \textcolor{magenta}{(!)}, we know that $\laplace^\theta_{\zeta, 1} v_1$ is well-defined, satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
 Since $v_1$ \textcolor{magenta}{has order $-1/2$}, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
@@
 v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
 \end{alignat*}
 where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
+By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
+\[ \sqrt{2}\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
+\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
+
+%%From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
 Since $v_{-1}$, like our other solution, \textcolor{magenta}{has order $-1/2$}, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
@@
 \subsubsection{Abstract argument for Borel regularity}\label{bessel-regularity-AL}
-The analysis in Sections~\ref{big-idea}--\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
+The analysis in Sections~\ref{big-idea}\;--\;\ref{neg-root-AL} picks out a frame in the space of analytic solutions of~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.
@@
 
-The Poincar\'{e} algorithm, as we saw in Section~\ref{sec:asympt-AL}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
-The frame is generated by trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket$.
-We will now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-\textcolor{orange}{[We're following the version of the argument that shows the Poincar\'{e} solutions exist and are 1-Gevrey.]}
-
-The Borel transform maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket$ into $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_j \rrbracket$ \textcolor{magenta}{(see Section \ref{sec:action_transseries})}, and it turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
-Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, is not this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
-Thus, if $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
+The Poincar\'{e} algorithm, as discussed in Sections \ref{sec:asympt-AL} and \ref{sec:new-summability-proof}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
+Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel-summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+\textcolor{RoyalBlue}{We will now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.} \textcolor{orange}{[We're following the version of the argument that shows the Poincar\'{e} solutions exist and are 1-Gevrey.]}
+
+The Borel transform $\borel_\zeta$ maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket_1$ into $\zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\}$, as discussed in Section~\ref{sec:action_transseries} \textcolor{orange}{[also cite convergence thing]}.
+In particular, it sends each Poincar\'{e} solution $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ to a convergent series $\series{v}_\alpha \in \zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\}$.
+Make a bounded sector $\Omega'_\alpha$ by intersecting $\Omega_\alpha$ with a disk around $\zeta_\alpha = 0$ whose radius is smaller than the radius of convergence of $\series{v}_\alpha$.
+On $\Omega'_\alpha$, the sum $\hat{v}_\alpha$ of $\series{v}_\alpha$ can be bounded by a shifted geometric series, showing that $\zeta_\alpha^{1/2} \hat{v}_\alpha$ is bounded by a constant.
+Therefore, $\hat{v}_\alpha$ belongs to $\singexpalg{-1/2}(\Omega'_\alpha)$.
+
+The Borel transform
+\[ \borel_\zeta \maps e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket_1 \to \zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\} \]
+also turns formal trans-monomial solutions of equation~\eqref{eqn:reg-mod-bessel-AL} into formal power series solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}.
+Thus, by the dominated convergence theorem, $\hat{v}_\alpha$ is an analytic solution of equation~\eqref{int-eq:spatial-mod-bessel-AL} on $\Omega'_\alpha$.
+The uniqueness part of Theorem~4 from \cite{reg-sing-volterra} then shows that $\hat{v}_\alpha$ must be a scalar multiple of the solution $v_\alpha$ we found in Sections \ref{big-idea}\;--\;\ref{neg-root-AL}.
+Since $v_\alpha$ belongs to $\singexpalg{-1/2}(\Omega_\alpha)$ for the full, unbounded sector $\Omega_\alpha$, it has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$.
+Therefore, the Poincar\'{e} solution $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ has a well-defined Borel sum along $\mathcal{J}^\theta_{\zeta, \alpha}$, which is a scalar multiple of $e^{-\alpha z} V_\alpha$.
+
+\par\color{RoyalBlue}Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, is not this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
+Thus, if $e^{-z} z^{-1/2}\,\series{W}_1$ and $e^z z^{-1/2}\,\series{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
 
@@
 It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\tilde{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-
+That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
+Thus, if $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
+\color{black}
+%
 \subsubsection{Confirmation of Borel regularity}\label{confirmation-borel-regularity}
-We can confirm the conclusion of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
+%
+We can verify the conclusions of Section~\ref{bessel-regularity-AL} using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
 We found in Section~\ref{sec:asympt-AL} that
@@
 Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-In fact, with the thimble projection reasoning, there is no ambiguity in the choice of the multiplicative constant.
+\textcolor{Maroon}{In fact, with the thimble projection reasoning, there is no ambiguity in the choice of the multiplicative constant.
+[Can we remove this sentence?]}
 
@@
 \subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
-We follow the reasoning of the proof of Lemma~\ref{lem:thimble_proj_formula-proof}.
-We can recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}.
+We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
 The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
@@
 \[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
-Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
+Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
 \begin{todo}\par
@@
 \begin{align*}
-2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big)&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
+i\sqrt{3}\,I(z) & = 2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big) \\
+&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
 &=\frac{2}{3}\pi ip^{1/2}\left[\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{-1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}\right]\\
@@
 Now we take the limit as $p\to 0$ and we find 
-\[\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)}=e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}\]
+\begin{align*}
+i\sqrt{3}\,I(z) & = \frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
+& = e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}
+\end{align*}
 \end{verify}
 \color{black}
-
-\par\color{RoyalBlue}
-Let $f\colon\C\to \C$ be a degree three polynomial\footnote{Every degree three polynomial $a_3 u^3+a_2 u^2+a_1 u+a_0$ can be written in the form $a_3u^3+pu+q$, after a change of coordinates $u\to u-\frac{a_2}{3 a_3}$.
-Furthermore, we can restrict to monic polynomials by setting $a_3=1$.}, we are going to consider thimble integrals of the form
-\[ I_j(z) = \int_{\mathcal{C}_j} \exp\left[z\big(u^3 + pu + q)\right]\,du \]
-where $\mathcal{C}_j$ is a thimble in \textcolor{magenta}{$H_{1}^{B,z}$} through a critical point of $f$.
-We can distinguish between the case when $f$ has two distinct critical points $x_+, x_-$ and only one critical point $x$, which correspond respectively to the case $p\neq 0$ and $p=0$.
-\footnote{Equivalently, the difference between the generic case ($p\neq 0$) and the degenerate one ($p=0$) is visible from the ODE perspective as in the former case $I$ is a solution of degree two ODE \[\left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0,\] while in the latter, $I$ solves a degree one ODE (see \eqref{eqn:degree-3-poly-1root}).}
-\color{black}
-Recall that translations and scaling-rotations act naturally on the image of $f\colon X\to \C$ ($f$ not necessarily a degree three polynomial), and their action transforms the thimble integral $I_j$ in the following ways:
-\begin{itemize}
-    \item \textbf{Action of translations:} let $q\in\C$, post-composing with translation of $q$ maps $f\to f+q$, thus 
-    \begin{align*}
-        \int_{\mathcal{C}_j}e^{z (f+q)} \nu &= e^{qz} I_j(z)
-    \end{align*}
-    \item  \textbf{Action of scaling-rotations:} let $\gamma\in\C$, post-composing with scaling-rotations by $\gamma$ maps $f\to \gamma\cdot f$, thus 
-    \begin{align*}
-        \int_{\mathcal{C}_j}e^{z (\gamma\cdot f)} \nu &= I_j(z \gamma)
-    \end{align*}
-\end{itemize}
-In particular, we can always reduce to study the thimble integral in simpler situations. 
-As an example, every degree three polynomial with distinct critical points can be transformed in the Chebyshev polynomial $T_3(t)=4 t^3-3t$, implying that the thimble integral $I_+$ can be transformed into the Airy--Lucas integral with parameter $m=1, n=3$.
-This follows by post-composing $f$ with a translation of $-q$ followed by a scaling-rotation of $\frac{ -i 3^{3/2}}{2 p^{3/2}}$
-\begin{align*}
-    f-q &= u^3 + pu \\
-    (f-q) \cdot \frac{ -i 3^{3/2}}{2 p^{3/2}} &= 4 \Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big)^{3} - 3\Big(\sqrt{-\tfrac{3}{p}} \tfrac{u}{2} \Big) \\
-    &= 4 t^3- 3t 
-\end{align*}
-with $t= \sqrt{-\frac{3}{p}} \frac{u}{2}$. Then the thimble integral $I_+$ gets transformed into 
-\begin{align*}
-    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\mathcal{C}_+} e^{z (4t^3-3t)} du\\
-    &= 2\sqrt{-\tfrac{p}{3}} \int_{\mathcal{C}_+} e^{z (4t^3-3t)} dt \\
-    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
-\end{align*}
-In particular, when $p\neq 0$, the thimble integral $I_+$ can be studied following the analysis of Appendix \ref{airy-appendix}. 
-%In both cases, we will compute the differential equation satisfied by $I$.
-
-%\begin{lemma}
- %Let $f(u)=u^3+pu+q$, 
-  %  \begin{itemize}
-   %     \item if $p\neq 0$, then $I_{\pm}(z)$ solves 
-    %    \begin{equation}\label{eqn:degree-3-poly-2roots}
-    %        \left[\partial_z^2 +2q \partial_z+\left(\frac{4p^3}{27}+q^2\right)+\frac{1}{z}\left(\partial_z +q \right)-\frac{1}{9z^2}\right]\Phi=0
-    %    \end{equation}
-    %    \item  if $p=0$, then $I(z)$ solves
-     %   \begin{equation}\label{eqn:degree-3-poly-1root}
-      %      \left[\partial_z+q+\frac{1}{3z}\right]I=0
-      %  \end{equation}
-    %\end{itemize}
-%\end{lemma}
-%\begin{proof}
- %   The proof follows from a direct computation. 
-%\end{proof}
-
-%Let us first assume $p\neq 0$, then $x_{\pm}=\pm\sqrt{-p/3}$ and the critical values are $\alpha_{\pm}=f(x_\pm)$.
-Notice that equation \eqref{eqn:degree-3-poly-2roots} admits slight solutions as $\tau_\pm=\frac{1}{2}$ (recall the definition of $\tau\pm=\frac{Q(-\alpha_\pm)}{P'(-\alpha_\pm)}$ as in Section \ref{borel_reg-ODE}), thus, for $\theta=-\arg z$, $\laplace_{\zeta,f(\alpha_\pm)}^{\theta}v_\pm$ solves \eqref{eqn:degree-3-poly-2roots} if and only $v_\pm$ solves
-
-%\begin{equation}\label{eqn:deg3-borel-ODE}
- %   \left[\Big[\zeta^2-2q\zeta+\big(\frac{4p^3}{27}+q^2\big)\Big]\partial_\zeta^2+3(\zeta-q)\partial_\zeta+\frac{8}{9}\right]v_\pm=0
-%\end{equation}
-
-%Let us find a solution of \eqref{eqn:deg3-borel-ODE} slight at $\zeta=\alpha_+$: in the new coordinate $\zeta_+:=\zeta-\alpha_+$, equation \eqref{eqn:deg3-borel-ODE} becomes
-
-%\begin{equation*}
- %   \left[\zeta_+ (\zeta_+ + \frac{4}{3}p\, x_+)\partial_{\zeta_+}^2+ \left[2p\, x_++3\zeta_{+}\right]\partial_{\zeta_+} +\frac{8}{9} \right]v_+=0
-%\end{equation*}
-
-%which is an hypergeometric equation in the coordinate $\xi=-\frac{3}{4p\,x_+}\zeta_+$
-
-%\begin{equation*}
- %   \left[\xi (1-\xi)\partial_{\xi}^2+ 3\big(\frac{1}{2}-\xi\big)\partial_{\xi}-\frac{8}{9} \right]v_+=0
-%\end{equation*}
-
-%and it admits a slight solution \textcolor{red}{the solution should match with the one of airy, so choose $w_2$ in DLMf list and not $w_1$}
-
-%\begin{align*}
- %   v_+ &= \xi^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\xi\right)\\
-  %  &=\left(\frac{3}{4p\,x_+}\zeta_+\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_+}\zeta_+\right). 
-%\end{align*}
-
-%Notice that $v_+$ is a hypergeometric function with the same parameters as the hypergeometric function $v_1$ in the example of Airy \S \ref{pos-root}. Similarly for $\zeta_-=\zeta-\alpha_-$
-
-%\begin{equation*}
-%    v_- =\left(\frac{3}{4p\,x_-}\zeta_-\right)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6} ;\frac{3}{2};1-\frac{3}{4p\,x_-}\zeta_-\right). 
-%\end{equation*}
 \color{RoyalBlue}
-We then consider the case when $p=0$, and we study it both as a solution of an ODE and as a thimble integral.
-First, notice that $I(z)$ solves
-       \begin{equation}\label{eqn:degree-3-poly-1root}
-          \left[\partial_z+q+\frac{1}{3z}\right]I=0
-       \end{equation}
-and we can find a Borel regular solution following the argument of Section~\ref{big-idea}: $\laplace_{\zeta,\alpha}^{\theta}v$ is a solution of \eqref{eqn:degree-3-poly-1root} if and only if $v$ is a solution of
-\begin{align*}
-   \left[ (\zeta-q)\partial_\zeta +\frac{2}{3}\right] v=0
-\end{align*}
-namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
-\color{black}
-
-The result is confirmed by the thimble projection reasoning which in this simple case reads
-\begin{align*}
-    \int_{\mathcal{C}} e^{-z (u^3+q)} du &= e^{-zq} e^{i\pi/3} \int_0^{+e^{i\theta}\infty} e^{-z\zeta} \zeta^{-2/3} d\zeta\\
-    &= e^{i\pi/3} \int_q^{+e^{i\theta}\infty} e^{-z\zeta} \, \zeta_q^{-2/3}\,  d\zeta
-\end{align*}
-where $e^{\pi i/3}$ accounts for the monodromy of $\zeta^{-2/3}$ at the origin.
 \begin{remark}
@@
 \end{remark}
+\color{black}
 \subsection{The triangular cantilever}\label{sec:catilever}

### 2024-04-06 exp-resurgence.tex
Finish "Lifting to a countable cover"

@@
 \end{definition}
-\begin{todo}[Mention Nevanlinna's theorem, re-stated as \cite[Theorem~C.11]{nikolaev2023existence}, somewhere later.]\end{todo}
-\begin{todo}[State the theorem that differentiation and integration commute with $\aexp^\theta$ under certain circumstances.
+\begin{todo}[Mention Nevanlinna's theorem, re-stated as \cite[Theorem~C.11]{nikolaev2023existence}, somewhere later?]\end{todo}
+\begin{todo}[State the theorem that differentiation and integration commute with $\aexp^\theta$ under certain circumstances?
 See Erdelyi's {\em Asymptotic Expansions}, \S 1.6.
@@
 %
-Let us start again, \textcolor{orange}{[\ldots]}
+Let us start again, \textcolor{orange}{[Revise\ldots]}
 %%Instead of starting with a formal solution to a problem, as we did in Section~\ref{intro:summation}, let us start with a holomorphic solution $\Phi$.
@@
 %
-First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+\textcolor{orange}{[Revise\ldots]} First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
 For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
@@
 \begin{theorem}\label{thm:soln_is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
 \end{theorem}
 We can use this result to show that $\Psi_\alpha$ is Borel regular.
-Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:shifted_holo_closed} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
-\color{RoyalBlue}
-\begin{theorem}\label{thm:soln_is_asymptotic}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
-\end{theorem}
-\color{black}
+Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
 \begin{corollary}\label{cor:soln_borel-reg}
@@
 %
-The study of irregular singular differential equations in the complex domain has a long history, and interesting phenoma distinguish irregular singular equations to regular singular ones.
+The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
 Already at the formal level, irregular singular ODEs have a distinguished behaviour, namely they admit divergent formal series solutions in the form of trans-monomials.
 In particular, for level $1$ ODEs of the kind we study in this paper, the Poincar\'e method gives an algorithm to compute formal solutions of $\mathcal{P}\Phi=0$, see~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a r\^ole~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a role~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+\begin{center}
+\textcolor{orange}{[Move the table or whatever up here. What are we trying to communicate, and how should the table look to communicate it?]}
+\end{center}
+\subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
 In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}).
@@
 Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.
-
-Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the r\^ole of the position domain.
+\subsubsection{\textcolor{orange}{[Resurgence section]}}
+Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the role of the position domain.
 Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform.
@@
 Then, the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) give the input to set-up a Riemann--Hilbert problem, whose solution would be a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
-
+\subsubsection{\textcolor{orange}{[Laplace transform methods section]}}
 So far we have been discussed the classical approaches to summability and reusrgence of formal solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
@@
 Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral.
-This is the approahc we adopt in this paper, but our choice of Laplace transform integral to begin with is very special, i.e.
+This is the approahc we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
 it is a Borel regular solution.
@@
 Indeed, building on our results of~\cite{reg-sing-volterra}, our approch will take the advantage of working on the position domain.
+
 A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
-However, with our approach, we can solve differetial equations with more general coefficients, and we plan to extend our results to systems of ODEs and generalize Braaksma's results.
-
-Summarizing, we collect the main methods to solve irregular singular ODEs in the following table stressing the difference between formal and analytic solutions in either the frequency and the position domain.
+However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.
+
+\textcolor{orange}{[Move this to beginning, and possibly revise]} Summarizing, we collect the main methods to solve irregular singular ODEs in the following table stressing the difference between formal and analytic solutions in either the frequency and the position domain.
 \begin{center}
@@
 %
-Over the complement $B'$ of the branch points, the translation structure gives us a holomorphic map $z \maps T^*B' \to \C$.
+\textcolor{DarkBlue}{Over the complement $B'$ of the branch points, the translation structure gives us a holomorphic map $z \maps T^*B' \to \C$.
 This map is an isomorphism on every fiber, trivializing $T^*B$ almost globally.
 Over a branch point $b$ of cone angle $2\pi n$, we get an analogous isomorphism $z \maps T^*_bB^{\otimes n} \to \C$.
-In both cases, we will call $z$ the {\em frequency coordinate} of $B$.
+In both cases, we will call $z$ the {\em frequency coordinate} of $B$.}
 \par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
@@
 The Laplace transforms $\laplace_{\zeta_\alpha, 0}$ and $\laplace_{\zeta, \alpha}$, which both turn functions on $B$ into functions on $T^*_{\zeta = \alpha}B$, are related in the following way.
-\textcolor{PaleVioletRed}{[We use $\singexp{}{}$ in the diagram below, but it hasn't been introduced yet.
-Should we just use generic holomorphic function spaces instead?
-Note that multiplying $\mathcal{O}_{T^*B}(H)$ by $e^{bz}$ (marked in magenta) does not do anything.]}
-
-\textcolor{RoyalBlue}{Let $b \in B$ be an ordinary point, and let $\zeta_b$ be the coordinate on $B$ for which $\zeta = \zeta(b) + \zeta_b$.
-Then the Laplace transform $\laplace_{\zeta_b,0}$, which turns functions on $B$ into functions on $T^*_\alpha B$, is compatible with $\laplace_{\zeta, \alpha}$.}
 \begin{lemma}\label{translation}
@@
 \end{center}
-commutes, where $H$ is the half-plane $\Re(z) > 0$.
+commutes.
 \end{todo}
 \end{lemma}
-\color{black}
-\color{RoyalBlue}
-\begin{lemma}%%\label{translation}
-Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega_b)$ with $\sigma>-1$ and for some $\Lambda>0$, then
-   \begin{equation}
-    \label{change-chart}
-    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
-\end{equation}
-In other words, the diagram
-\begin{center}
-\begin{tikzcd}
- \mathcal{O}_{T^*B}(H) \arrow[rr, "e^{bz}"]&  & e^{bz}\,\mathcal{O}_{T^*B}(H)\\
-& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_b,0}"]\arrow[ur,swap,"\laplace_{\zeta,b}"]  &  
-\end{tikzcd}
-\end{center}
-commutes, where $H$ is the half-plane $\Re(z) > 0$ (\textcolor{orange}{the coordinate $z$ is a global coordinate on $T^*B$}).
-\end{lemma}
-\color{black}
 \begin{proof}
@@
 \[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
-
-\color{black}\textcolor{SteelBlue}{To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
+\color{black}
+%%\textcolor{SteelBlue}{To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
 In the result below, our conditions on the open set $\Upsilon \subset \widetilde{\C^\times}$ imply that the projection $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$.
@@
 In other words, by pulling back along $\pi$, we can think of the holomorphic function space $\mathcal{O}(\pi \Upsilon)$ as the subspace of $\mathcal{O}(\Upsilon)$ where the Laurent series around $\zeta = 0$ exists.}
-
-\textcolor{RoyalBlue}{Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
+\par\textcolor{RoyalBlue}{Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
 The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.}
@@
 \color{black}
-\color{SteelBlue}
-For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
-\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
-\color{black}
+%%\color{SteelBlue}
+%%For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
+%%\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+%%\color{black}
 is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
@@
 \end{proof}
-\color{SteelBlue}
-If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$.
+%%\color{SteelBlue}
+%%If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$.
 That means its Laurent series is actually a Taylor series.
-\begin{prop}\label{prop:shifted_holo_series}
-Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
-\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
-is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
-\end{prop}
-\begin{proof}
-Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$.
+%%\begin{prop}\label{prop:shifted_holo_series}
+%%Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
+%%\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
+%%is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
+%%\end{prop}
+%%\begin{proof}
+%%Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$.
 The definition of $\singexp{\sigma}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^\sigma |\varphi|$ is bounded on a punctured disk around $\zeta = 0$, which would be impossible if $\series{\varphi}$ included any $\zeta^{\rho-1},\;\zeta^{\rho-2},\;\zeta^{\rho-3}\ldots$ terms.
 That means $\series{\varphi}$ must belong to $\zeta^\rho\,\C\{\zeta\}$.
-\end{proof}
-\color{black}
+%%\end{proof}
+%%\color{black}
 
@@
 \textcolor{HotPink}{which shows that it represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$.}
-\textcolor{SteelBlue}{which shows that it lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}. By working with Taylor series, we can show that $\softpart^\alpha$ maps
+%%\textcolor{SteelBlue}{which shows that it lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.}
+By working with Taylor series, we can show that $\softpart^\alpha$ maps
 \textcolor{HotPink}{\[ \zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \to \zeta^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \]}
-\textcolor{SteelBlue}{\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]}
-and $\volterra^\alpha$ maps \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha}$} \textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$} to itself.
-It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$} \textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta = \alpha}$} \textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}.
-Recalling that the prototype solution \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$} \textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}, we can deduce that $\psi_\alpha$ \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$.} \textcolor{SteelBlue}{lies in that space} too.
-
-\textcolor{HotPink}{We now cross over into the formal world, expanding $\psi_\alpha$ as} \textcolor{SteelBlue}{We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of} a shifted Taylor series $\series{\psi}_\alpha \in \zeta_\alpha^{\tau_\alpha-1}\,\C\{\zeta\}$.
+%%\textcolor{SteelBlue}{\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]}
+and $\volterra^\alpha$ maps \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha}$}
+%%\textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}
+to itself.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}
+%%\textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}
+, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta = \alpha}$}
+%%\textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}
+. Recalling that the prototype solution \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$}
+%%\textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}
+, we can deduce that $\psi_\alpha$ \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$}
+%%\textcolor{SteelBlue}{lies in that space}
+too.
+
+\textcolor{HotPink}{We now cross over into the formal world, expanding $\psi_\alpha$ as}
+%%\textcolor{SteelBlue}{We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of}
+a shifted Taylor series $\series{\psi}_\alpha \in \zeta_\alpha^{\tau_\alpha-1}\,\C\{\zeta\}$.
 By definition, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.
@@
 \textcolor{orange}{[Add flavor text]}
-\color{RoyalBlue}
-\begin{theorem}[restatement of \ref{thm:soln_is_asymptotic}]\label{re:thm:soln_is_asymptotic}
-\textcolor{magenta}{[revise organiztion to match intro]} The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{re:thm:soln_is_Borel_sum}.
-\end{theorem}
-\color{black}
 \begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
@@
 In the proof of Theorem~\ref{re:thm:soln_is_Borel_sum}, we showed that the position-domain solution $\psi_\alpha \in \singexpalg{\tau_\alpha-1}(\Upsilon)$ is the sum of a shifted Taylor series $\series{\psi}_\alpha \in \zeta^{\tau_\alpha-1}\,\C\{\zeta\}$.
-Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi}_\alpha$ is the formal Laplace transform of $\series{\psi}_\alpha$, the desired result follows from Lemma~\ref{lem:laplace-bridge}.
+Since $\Psi_\alpha$ is the Laplace transform of $\psi_\alpha$, and $\series{\Psi}_\alpha$ is the formal Laplace transform of $\series{\psi}_\alpha$, Lemma~\ref{lem:laplace-bridge} tells us that $\Psi_\alpha$ is asymptotic to $\series{\Psi}_\alpha$.
+Taking the Borel sum of $\series{\Psi}_\alpha$ gives us back $\Psi_\alpha$, by construction, so $\Psi_\alpha$ is Borel regular.
 \end{proof}
@@
 where $\gamma$ is a path that comes from $\infty$ at $-60^\circ$ and returns to $\infty$ at $60^\circ$.
-\textcolor{Pink}{[Figure~\ref{fig:path_Airy} shows integration contour after change of coordinates]}
 
@@
 with $n \in \{3, 4, 5, \ldots\}$ and $m \in \{1, 2, \ldots, n-1\}$. A few solutions, indexed by $j \in \{1, \ldots, n-1\}$, are given by the Airy-Lucas functions~\cite[equation~3.6]{charbonnier22}
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du, \]
+\begin{equation}\label{integral:AL}
+\widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du,
+\end{equation}
 where $\mathcal{C}^\theta_j$ is the contour that passes through the point $u = \cos\big(\tfrac{j}{n}\pi\big)$ and projects to the ray $\mathcal{J}^\theta_{\zeta, \pm 1}$ under the mapping $-\zeta = T_n(u)$.
-\textcolor{RoyalBlue}{where $\mathcal{C}^\theta_j$ is the Lefschetz thimble through $u = \cos\big(\tfrac{j}{n}\pi\big)$.
-By definition, $\mathcal{C}^\theta_j$ is a preimage of the ray $\mathcal{J}^\theta_{\mp 1}$ under the function $-T_n(u)$.} The ray starts at the critical value $1$ when $j$ is odd, and $-1$ when $j$ is even.
+The ray starts at the critical value $1$ when $j$ is odd, and $-1$ when $j$ is even.
+To ensure that the integral converges, $\theta$ should be near $-\tfrac{n}{2} \arg(y)$.
 \begin{center}
@@
 We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
-\textcolor{LimeGreen}{Furthermore, we will show in Section~\ref{bessel-regularity-AL} that $v_\alpha$ can be analytically continued to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$, where $\Omega_\alpha$ is a sector with its tip at $\zeta = \alpha$.}
-%%and can be analytically continued to a sector $\Omega_\alpha$ with its tip at $\zeta = \alpha$. In fact $v_\alpha$ will belong to $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \cap$
-%%which is in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ for some constant $\tau_\alpha \in (0, 1)$ and some domain $\Omega_\alpha$ resembling the one in the figure from Theorem~\ref{re:thm:exist_uniq_ODE}.
 It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
@@
 where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
-
-\textcolor{LimeGreen}{We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{-1 - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ asymptotic to a scalar multiple of \textcolor{magenta}{$z^{-1}$} at $z = \infty$.}
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
+%
 \subsubsection{Focus on $\zeta = 1$}\label{pos-root-AL}
+%
 Let us find a germ in $(\zeta-1)^{\tau_1-1}\,\mathcal{O}_{\zeta=1}$, for some $\tau_1 \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
@@
 where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
-%%From the argument in Section~\ref{big-idea} \textcolor{magenta}{(!)}, we know that $\laplace^\theta_{\zeta, 1} v_1$ is well-defined, satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ \textcolor{magenta}{has order $-1/2$}, the decomposition $V_1 = z^{-1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
+%
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root-AL}
+%
 Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
@@
 Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel-summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
-\textcolor{RoyalBlue}{We will now show that if these solutions are Borel-summable, their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.} \textcolor{orange}{[We're following the version of the argument that shows the Poincar\'{e} solutions exist and are 1-Gevrey.]}
-
-The Borel transform $\borel_\zeta$ maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket_1$ into $\zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\}$, as discussed in Section~\ref{sec:action_transseries} \textcolor{orange}{[also cite convergence thing]}.
+
+The Borel transform $\borel_\zeta$ maps $e^{-\alpha z} z^{-1/2}\,\C\llbracket z^{-1} \rrbracket_1$ into $\zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\}$, as discussed in Sections \ref{sec:action_transseries} and \ref{sec:new-summability-proof}.
 In particular, it sends each Poincar\'{e} solution $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ to a convergent series $\series{v}_\alpha \in \zeta_\alpha^{-1/2}\,\C\{\zeta_\alpha\}$.
@@
 Therefore, the Poincar\'{e} solution $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ has a well-defined Borel sum along $\mathcal{J}^\theta_{\zeta, \alpha}$, which is a scalar multiple of $e^{-\alpha z} V_\alpha$.
-
-\par\color{RoyalBlue}Summation sends convergent power series in $\zeta_\alpha^{-1/2}\,\C\llbracket \zeta_\alpha \rrbracket$ into $\zeta_\alpha^{-1/2}+ o\big(\zeta_\alpha^{-1/2}\big)$ \textcolor{orange}{[since the argument above is one-way, is not this weaker than being in $\singexpalg{-1/2}$?]}, and it turns convergent power series that satisfy a given fractional integral equation into holomorphic functions that satisfy the same equation \cite[Lemma 2]{reg-sing-volterra}.
-Thus, if $e^{-z} z^{-1/2}\,\series{W}_1$ and $e^z z^{-1/2}\,\series{W}_{-1}$ are $1$-Gevrey, their Borel transforms sum to solutions of equation~\eqref{int-eq:spatial-mod-bessel-AL}, which lie in $\singexpalg{-1/2}$ \textcolor{magenta}{[needs domain]} for $\alpha = 1$ and $\alpha = -1$, respectively.
-
-When $\alpha$ is $1$ or $-1$, equation~\eqref{int-eq:spatial-mod-bessel-AL} becomes the kind of singular integral equation discussed in Section~\ref{borel_reg-ODE}.
-It therefore has exactly one solution in $\singexpalg{1/2}$ \textcolor{orange}{[needs domain]}, up to scaling.
-That means $\borel\big[ e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha \big]$ must sum to a scalar multiple of $v_\alpha$.
-Thus, if $e^{-\alpha z} z^{-1/2}\,\series{W}_\alpha$ is Borel-summable, its Borel sum is a scalar multiple of $\laplace_{\zeta, \alpha} v_\alpha$.
-\color{black}
+It follows, by Lemma~\ref{lem:laplace-bridge}, that $e^{-\alpha z} V_\alpha$ is Borel regular.
 %
@@
 Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-\textcolor{Maroon}{In fact, with the thimble projection reasoning, there is no ambiguity in the choice of the multiplicative constant.
-[Can we remove this sentence?]}
 
@@
 Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
-
+%
 \subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
@@
 We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-The critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$ splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
-Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get \textcolor{magenta}{[mention that $\theta$ should be $\arg z$]}
+Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$.
+The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
+Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
 \begin{align*}%%\label{integral:mod-bessel-rational-zeta}
@@
 & = \frac{\sin(m\phi)}{\sin(n \phi)}\\
-& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin^2(n \phi)\right) \\
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
 & = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
@@
 
-Next, we simplify the integrand using identities 15.8.4 and 15.8.27--28 from \cite{dlmf}, which tell us that\begin{align*}
+Next, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
 &{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
@@
 %
+\textcolor{PaleVioletRed}{[Up to now, we've treated the Airy-Lucas functions as separate elements of a frame of solutions.
+Using the idea of resurgence, we see that they are actually more closely related.
+You can recover the frame from any one of its elements\ldots]}
+%%In Sections~\ref{confirmation-borel-regularity}\;--\;\ref{contour-argument-AL}, we
+
+\color{RoyalBlue}
 In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
 In both cases we find
-\begin{align*}
-    v_1(\zeta)= i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
+\color{black}
+\begin{align*}
+v_1(\zeta) = i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
 \end{align*}
@@
 \begin{align*}
-&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right)=\\
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right) \\
 &=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
@@
 \begin{equation}\label{resurgent-relation-1}
-    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1+i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
+    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
 \end{equation}
@@
 \textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
-
+%
 %\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
@@
 %\color{black}
-
+%
 \subsection{Modified Bessel}\label{sec:mod-bessel-lift}
@@
 \end{equation}
-
-This generalization does not really affect the argument from Section~\ref{bessel-regularity-AL}, so we will only briefly state the analogous results:
+The ODE reasoning of Sections \ref{big-idea}\;--\;\ref{confirmation-borel-regularity} works basically the same in this more general setting, so we will only briefly state the analogous results.
 \begin{itemize}
- \item \textbf{Asymptotic analysis}: equation~\eqref{eqn:mod-bessel} admits a basis of formal solutions \[\series{I}_{\mu,1}(z)=e^{-z} z^{-1/2} \tilde{W}_{\mu, 1} \quad \text{ and } \quad \series{I}_{\mu,-1}(z)=e^z z^{-1/2} \series{W}_{\mu, -1}\] with
- \begin{align*}
- \tilde{W}_{\mu,1} &= 1- \frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2} - \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3}+...\\
- \series{W}_{\mu,-1} &= 1+\frac{\big(\tfrac{1}{2}-\mu\big)\big(\frac{1}{2}+\mu\big)}{2 \cdot 1!} z^{-1} + \frac{\big(\tfrac{1}{2}-\mu\big)_2\big(\frac{1}{2}+\mu\big)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\big(\tfrac{1}{2}-\mu\big)_3\big(\frac{1}{2}+\mu\big)_3}{2^3 \cdot 3!} z^{-3} + ...
-\end{align*}   
- \item  \textbf{Frame of analytic solutions}: there exist two functions $v_{\mu, 1}, v_{\mu, -1}$ such that $\laplace_{\alpha}v_{\mu, \alpha}$ satisfies equation~\eqref{eqn:mod-bessel} and they are explicitly
-\begin{align*}
-v_{\mu, 1}&=-i\sqrt{2}\,\zeta_{1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_{1}\big)\\
-v_{\mu, -1}&=\sqrt{2}\,\zeta_{-1}^{-1/2}  {}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
-\item \textbf{Borel regularity} We can compare the Borel transform of the formal solutions $\series{W}_{\mu,\pm1}$ with the analytic solutions $v_{\mu,\pm 1}$.
-They agree (up to the choice of a constant), hence we have another example where Borel regularity can be explicitly verified.
+\item[] \textbf{Asymptotic analysis}
+
+Equation~\eqref{eqn:mod-bessel} has a basis of formal solutions \[ e^{-z} z^{-1/2}\,\series{W}_1 \quad \text{and} \quad e^z z^{-1/2}\,\series{W}_{-1}, \]
+given by
+\begin{align*}
+\series{W}_{\mu,1} & = 1 - \frac{\left(\tfrac{1}{2}-\mu\right)\left(\frac{1}{2}+\mu\right)}{2 \cdot 1!} z^{-1} + \frac{\left(\tfrac{1}{2}-\mu\right)_2\left(\frac{1}{2}+\mu\right)_2}{2^2 \cdot 2!} z^{-2} - \frac{\left(\tfrac{1}{2}-\mu\right)_3\left(\frac{1}{2}+\mu\right)_3}{2^3 \cdot 3!} z^{-3} + \ldots \\
+\series{W}_{\mu,-1} & = 1 + \frac{\left(\tfrac{1}{2}-\mu\right)\left(\frac{1}{2}+\mu\right)}{2 \cdot 1!} z^{-1} + \frac{\left(\tfrac{1}{2}-\mu\right)_2\left(\frac{1}{2}+\mu\right)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\left(\tfrac{1}{2}-\mu\right)_3\left(\frac{1}{2}+\mu\right)_3}{2^3 \cdot 3!} z^{-3} + \ldots
+\end{align*}   
+\item[]  \textbf{Frame of analytic solutions}
+
+Equation~\eqref{eqn:mod-bessel} also has a basis of analytic solutions $\laplace^\theta_{\zeta, 1} v_1$ and $\laplace^\theta_{\zeta, -1} v_{-1}$, which are the Laplace transforms of the functions
+\begin{align*}
+v_1 & = -i\sqrt{2}\,\zeta_{1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_{1}\big)\\
+v_{-1} & = \hphantom{-i}\sqrt{2}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{align*}
+along the directions $\theta \neq \pi$ and $\theta \neq 0$, respectively.
+\item[] \textbf{Borel regularity}
+
+The Borel transforms $\mathcal{B}_\zeta[z^{-1/2} e^{-\alpha z}\,\series{W}_{\pm 1}]$ sum to scalar multiples of $v_{\pm 1}$, implying through Lemma~\ref{lem:laplace-bridge} that the solutions $\laplace^\theta_{\zeta, \pm 1} v_{\pm 1}$ are Borel regular.
 \end{itemize}
-On the other hand, the thimble projection reasoning we describe in Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in the following Section~\ref{countable-cover}.
-
+On the other hand, the thimble projection reasoning of Section~\ref{contour-argument-AL} has to be generalized, as we will discuss in Section~\ref{countable-cover} below.
+%
 \subsubsection{Lifting to a countable cover}\label{countable-cover}
+%
 Formula~\eqref{integral:mod-bessel-rational-AL} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
@@
 When $j$ is\ldots & $\mathcal{C}^\theta_j$ comes from $-\infty$ along\ldots & and goes to $+\infty$ along\ldots \\[1mm] \hline
-\vphantom{\rule{0mm}{5mm}} Odd & $(-\infty,0) + (j\pi-\theta)i$ & $(0, \infty) + (j\pi-\theta)i$ \\[1mm] \hline
-\vphantom{\rule{0mm}{5mm}} Even & $(-\infty,0) + \big((j+1)\pi-\theta\big)i$ & $(0, \infty) + \big((j-1)\pi-\theta\big)i$ \\[1mm]
+\vphantom{\rule{0mm}{5mm}} Odd & $(-\infty,0) + (j\pi-\theta)i$ & $(0, \infty) + (j\pi+\theta)i$ \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} Even & $(-\infty,0) + \big((j+1)\pi-\theta\big)i$ & $(0, \infty) + \big((j-1)\pi+\theta\big)i$ \\[1mm]
 \end{tabular}
@@
 \begin{equation}\label{int:mod-bessel-gen}
- K_\mu(z) = \frac{1}{2 \sinh(\mu\,i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
+ K_\mu(z) = \frac{1}{2 \sinh(\mu i\pi)} \int_{\mathcal{C}^\theta_1} \exp\left[z \cosh(t)\right]\,\sinh(\mu t)\,dt
 \end{equation}
@@
 
-\color{RoyalBlue}
-We can now follow Section \ref{contour-argument-AL} to compute the Borel transform of the asymptotic of $K_\mu$ as an inverse Laplace transform: let $\zeta=-\cosh(t)$
-\color{black}
-\textcolor{orange}{[\ldots]} We first recast the integral into the $\zeta$ plane by setting $-\zeta = \cosh(t)$
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta, \]
-where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. \textcolor{orange}{[\ldots]}
+We can now apply the thimble projection formula, using the same reasoning as in Section~\ref{contour-argument-AL}.
+We first recast the integral into the $\zeta$ plane by setting $-\zeta = \cosh(t)$.
+This gives us the expression
+\[ K^{(j)}_\mu(z) = -\frac{1}{2\sinh(\mu i\pi)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta, \]
+where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. We then use identity~15.4.16 from \cite{dlmf} to write the integral explicitly in terms of $\zeta$:
+\begin{align*}
+\frac{\sinh(\mu t)}{\sinh(t)} & = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;-\sinh(t)^2\right) \\
+& = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;1 - \zeta^2\right).
+\end{align*}
+Like before, we can deduce by analytic continuation that this identity holds throughout the $t$ plane.
+
+Using formula~15.8.4 from \cite{dlmf}, followed by formulas 15.8.27 and 15.8.28 from the same source, we can repeat the arguments of Section~\ref{contour-argument-AL}, eventually rewriting the integrand as the variation of the function
+\[ \frac{\sinh(\mu t)}{\sinh(t)} = \frac{3\mu}{2}\;{}_2F_1\left(1 - \mu,\;1 + \mu;\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{\mu}{2}\;{}_2F_1\left(1 - \mu,\;1 + \mu;\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
+across the branch cut $\mathcal{J}^\theta_{\zeta, \mp 1}$.
+As before, the term that contributes to the jump is the one which is singular at the critical value where the branch cut starts.
+We use identity~15.2.3 from \cite{dlmf} to write the jump explicitly.
+For odd $j$, we get
+\[ K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+and for even $j$, we get \begin{todo}{[check sign]}\end{todo}
+\[ K^{(j)}_\mu(z) = -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\]
+
+\textcolor{orange}{[Old text\ldots]}
 \color{RoyalBlue}
@@
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
-\[ K_0(z) = \frac{1}{2\pi i} \int_ {\textcolor{orange}{\Omega}} \exp\left[z \cosh(t)\right]\,t\,dt. \]
-\textcolor{orange}{Choosing $\Omega$ to be the unit-speed path that runs from $\infty$ leftward to $-i\pi$, upward to $i\pi$, and rightward back to $\infty$,} we can rewrite this formula as
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \\
+\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_ {\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt. \]
+We will evaluate
+\[ K_0(z) \defeq K_0^{(1)}(z) - K_0^{(0)}(z). \]
+In this difference, the parts of $\mathcal{C}_1^\theta$ and $\mathcal{C}_0^\theta$ in the left half-plane cancel out, leaving the integral
+\[ K_0(z) = \frac{1}{2\pi i} \int_\mathscr{c} \exp\left[z \cosh(t)\right]\,t\,dt \]
+over the contour $\mathscr{c}$ that runs as follows:
+\begin{enumerate}
+\item Leftward along $(0, \infty) + (-\pi + \theta)i$.
+\item Upward along $(-\pi, \pi)i$.
+\item Rightward along $(0, \infty) + (\pi + \theta)i$.
+\end{enumerate}
+Since the integrand is an odd function, the upward part of the path integrates to zero. Since the integrand is also $2\pi i$-periodic, the leftward and rightward parts of the integral collapse to
+\begin{align*}
+K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[z \cosh(t)\right]\,2\pi i\,dt \\
 & = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
@@
 \end{align*}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}. Then equation \eqref{eqn:K-mu} gives
-\begin{equation}\label{eqn:borel_bessel0}
-    K_0(z)=\textcolor{red}{-}\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}, \frac{1}{2};\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta =  \int_1^\infty \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}} \, d\zeta .
-\end{equation}
+with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
+
+On the other hand, equation \eqref{eqn:K-mu} gives \textcolor{magenta}{[relationship? what are we trying to say?]}
+\begin{align*}\label{eqn:borel_bessel0}
+K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
+& = \int_{\mathcal{J}^\theta_{\zeta, 1}} \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}}\;d\zeta.
+\end{align*}
 \begin{verify}
@@
 %
+\textcolor{orange}{[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]}
+\color{LimeGreen}
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 \end{align*}
+\color{black}
 % \subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
@@
 %%\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
-\begin{todo}[Shall we review the content of \cite{reg-sing-volterra}?]\end{todo}
 \begin{todo}
@@
 When $\rho$ is a non-integer greater than $-1$, we can do a nice trick in this space of germs: we can pass back and forth between differential and integral equations without worrying about boundary conditions.
-
-\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}, and a power $\rho \in \R \smallsetminus \Z$.
+%
+%%\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}, and a power $\rho \in \R \smallsetminus \Z$.
 As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.}
-
-\textcolor{SteelBlue}{To make this statement precise, we need some terminology.
+%
+%%\textcolor{SteelBlue}{To make this statement precise, we need some terminology.
 For any $\sigma \in \R$, let us say that the {\em order} of a function in $\zeta^\sigma \mathcal{O}(\pi \Upsilon)$ is the lowest power appearing in its shifted Laurent expansion, or $-\infty$ if there is no lowest power.
@@
 \[ f \defeq \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi \]
-belongs to $\zeta^{\rho-(n-1)} \mathcal{O}(\pi \Upsilon)$.
+belongs to $\zeta^{\rho-(n-1)} \mathcal{O}_{\zeta = 0}$.
 This tells us, in particular, that $f$ has a shifted Taylor expansion with no constant term.

### 2024-04-06 exp-resurgence.tex
Finalize switch to germ notation
Change HotPink passages to black, and drop commented-out SteelBlue.

@@
 
-\color{HotPink}
 If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$.
@@
 \[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
-\color{black}
-%%\textcolor{SteelBlue}{To do this, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
-In the result below, our conditions on the open set $\Upsilon \subset \widetilde{\C^\times}$ imply that the projection $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$.
-A holomorphic function on $\pi \Upsilon$ is therefore guaranteed to have a Laurent series expansion around $\zeta = 0$.
-In fact, a holomorphic function on $\Upsilon$ will have a Laurent series expansion around $\zeta = 0$ only if it descends to a holomorphic function on $\pi \Upsilon$.
-In other words, by pulling back along $\pi$, we can think of the holomorphic function space $\mathcal{O}(\pi \Upsilon)$ as the subspace of $\mathcal{O}(\Upsilon)$ where the Laurent series around $\zeta = 0$ exists.}
 \par\textcolor{RoyalBlue}{Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
@@
 \end{center}
-\color{HotPink}
 For any $\sigma \in \R$, $\Lambda \in \R$, and non-integer $\rho \ge \sigma$, the intersection
 \[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
-\color{black}
-%%\color{SteelBlue}
-%%For any $\rho \in \R \smallsetminus \Z$, $\Lambda \in \R$ and $\sigma \in (\rho-1, \rho]$, the intersection
-%%\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
-%%\color{black}
 is a closed subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$.
@@
 \end{proof}
-%%\color{SteelBlue}
-%%If a function in $\zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ also belongs to $\singexp{\sigma}{\Lambda}(\Upsilon)$, its Laurent series cannot include any terms more singular than $\zeta^\sigma$.
-That means its Laurent series is actually a Taylor series.
-%%\begin{prop}\label{prop:shifted_holo_series}
-%%Under the conditions of Lemma~\ref{lem:shifted_holo_closed}, every function in
-%%\[ \zeta^\rho\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\sigma}{\Lambda}(\Upsilon) \]
-%%is the sum of a shifted Taylor series in $\zeta^\rho\,\C\{\zeta\}$.
-%%\end{prop}
-%%\begin{proof}
-%%Since $\pi \Upsilon$ contains a punctured disk around $\zeta = 0$, every function $\varphi \in \zeta^\rho\,\mathcal{O}(\pi \Upsilon)$ is the sum of a shifted Laurent series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta, \zeta^{-1}\}$.
-The definition of $\singexp{\sigma}{\Lambda}(\Upsilon)$ tells us that $|\zeta|^\sigma |\varphi|$ is bounded on a punctured disk around $\zeta = 0$, which would be impossible if $\series{\varphi}$ included any $\zeta^{\rho-1},\;\zeta^{\rho-2},\;\zeta^{\rho-3}\ldots$ terms.
-That means $\series{\varphi}$ must belong to $\zeta^\rho\,\C\{\zeta\}$.
-%%\end{proof}
-%%\color{black}
 
@@
 \[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta_\alpha(a)}{\zeta_\alpha(b)}\right)^{\tau_\alpha} \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau_\alpha}{\zeta_\alpha} \right)\;d\zeta_\alpha\right], \]
-\textcolor{HotPink}{which shows that it represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$.}
-%%\textcolor{SteelBlue}{which shows that it lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.}
-By working with Taylor series, we can show that $\softpart^\alpha$ maps
-\textcolor{HotPink}{\[ \zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \to \zeta^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \]}
-%%\textcolor{SteelBlue}{\[ \zeta^{\tau_\alpha-1}\,\mathcal{O}(\pi \Upsilon) \to \zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \]}
-and $\volterra^\alpha$ maps \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha}$}
-%%\textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}
-to itself.
-It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in \textcolor{HotPink}{$\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}
-%%\textcolor{SteelBlue}{$\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon) \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$}
-, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
-The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta = \alpha}$}
-%%\textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha}\,\mathcal{O}(\pi \Upsilon)$}
-. Recalling that the prototype solution \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$}
-%%\textcolor{SteelBlue}{lies in $\zeta^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$}
-, we can deduce that $\psi_\alpha$ \textcolor{HotPink}{represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$}
-%%\textcolor{SteelBlue}{lies in that space}
-too.
-
-\textcolor{HotPink}{We now cross over into the formal world, expanding $\psi_\alpha$ as}
-%%\textcolor{SteelBlue}{We now cross over into the formal world using Proposition~\ref{prop:shifted_holo_series}, which tells us that $\psi_\alpha$ is the sum of}
-a shifted Taylor series $\series{\psi}_\alpha \in \zeta_\alpha^{\tau_\alpha-1}\,\C\{\zeta\}$.
+which shows that it represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$. By working with Taylor series, we can show that $\softpart^\alpha$ maps
+\[ \zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta=\alpha} \to \zeta^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \]
+and $\volterra^\alpha$ maps $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha}$ to itself.
+It follows that the sequence $\solptb^{(0)}, \solptb^{(1)}, \solptb^{(2)}, \ldots$ lies in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta=\alpha} \cap \singexp{\tau_\alpha}{\Lambda}(\Upsilon)$, which by Lemma~\ref{lem:shifted_holo_closed} is a closed subspace of $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$.
+The limit $f_*$, which satisfies equation~\eqref{eqn:inhomog-volterra}, therefore represents a germ in $\zeta_\alpha^{\tau_\alpha}\,\mathcal{O}_{\zeta = \alpha}$.
+Recalling that the prototype solution represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$, we can deduce that $\psi_\alpha$ represents a germ in $\zeta_\alpha^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ too.
+
+We now cross over into the formal world, expanding $\psi_\alpha$ as a shifted Taylor series $\series{\psi}_\alpha \in \zeta_\alpha^{\tau_\alpha-1}\,\C\{\zeta\}$.
 By definition, the formal Laplace transform $\series{\Psi}_\alpha = \laplace_{\zeta, \alpha} \series{\psi}_\alpha$ lies in $e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$.

### 2024-04-06 exp-resurgence.tex
Revise intro to action on trans-series

@@
 %
-\color{DarkTurquoise}
-\color{RoyalBlue}
+\color{DarkBlue}
+{\em Trans-series} are formal objects that greatly generalize formal power series.
+Their full definition is quite involved~\cite{aniceto2019primer}, especially when complex exponents are allowed~\cite{van-der-hoeven2001complex}.
+We will only see examples of the simple form
+\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha, \]
+where $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+Each term $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ is called a {\em trans-monomial}.
+
+Trans-series of this form play a crucial role in the theory of ODEs with irregular singularities.
+In particular, they exhibit a formal analogue of the Stokes phenomenon: their asymptotics can change sharply from one direction to the next.
+Trans-monomials $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ can be ordered by $\Re(e^{i\theta} \alpha)$ for any direction $\theta$.
+When a trans-series converges, its sum becomes dominated by the lowest term in this ordering as $\Re(e^{-i\theta} z)$ grows.
+
+We can extend the definition of the Borel transform to trans-series by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
+\par\color{RoyalBlue}
 A trans-series is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[exponents must lie along a ray]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
@@
 \begin{definition}
-    The action of $\borel_\zeta$ on trans-monomials is the formal inverse of $\laplace_{\zeta,\alpha}$
-    \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha}z^{-n-1}\big]=e^{-z\alpha}z^{-n-1}\]
-    %\begin{center}
-%\begin{tikzcd}[every arrow/.append style={shift left}]
- %e^{-z\alpha}\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow{d}{\borel_{\zeta}} \\ \{1, \zeta_\alpha, \zeta_\alpha^2, \zeta_\alpha^3, \ldots\} \arrow{u}{\laplace_{\zeta,\alpha}}
-%\end{tikzcd}
-%\end{center}
-    and it extends by linearity to transseries. 
+On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
+\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
+The action of $\borel_\zeta$ extends to general trans-monomials and trans-series by countable linearity.
 \end{definition}
-In particular, from identity~\eqref{change-chart} we deduce 
-\begin{align*}
-    e^{-z\alpha}z^{-n-1}&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]\\
-     z^{-n-1}&=\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\zeta\alpha}z^{-n-1}\big]
-\end{align*}
-and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
+From this definition, and identity~\eqref{change-chart}, we deduce that
+\begin{align*}
+e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
+\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
+\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
+\end{align*}
+%%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
 %Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-
+%
 %We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$.
@@
 %\begin{lemma}
-    \[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
+%%%\[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
 In other words, the diagram 
@@
 \newpage
-\bibliographystyle{plain}
+\bibliographystyle{utphys}
 \bibliography{airy-resurgence}

### 2024-04-08 exp-resurgence.tex
Revise intro to Borel transform on trans-monomials

@@
 \newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
-\newcommand{\dualsingexp}[2]{\widehat{\mathcal{H}}L^\infty_{#1, #2}}
-\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
+\newcommand{\dualsingexp}[1]{\widehat{\mathcal{H}}L^\infty_{#1}}
+%%\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
 \newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments
@@
 \definecolor{plum}{RGB}{76, 0, 102}
-
-% === phase space laplace ===
-\include{figures/phase-space-laplace.tex}
 
@@
 \setcounter{tocdepth}{2}
+% === phase space laplace ===
+\include{figures/phase-space-laplace.tex}
 
@@
 \begin{document}
+
 \maketitle
@@
 %
+\color{DarkBlue}
 Let us start again, \textcolor{orange}{[Revise\ldots]}
@@
 Suppose it has an asymptotic expansion \series{\Phi} \defeq \aexp^\theta \Phi$.
+\color{black}
 
@@
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
-of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^{\textcolor{LimeGreen}{\bullet}}) \right] \]
+of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}
@@
 %\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
-Our treatment of thimble integrals will be based on our geometric picture of the Laplace transform, summarized in Section~
+%%Our treatment of thimble integrals will be based on our geometric picture of the Laplace transform, briefly sketched in Section~\ref{sec:other_results}.
+\textcolor{orange}{[Can you remind me why we discuss the geometric picture here?
+Is it to justify doing things in a coordinate-independent way?]}
+In Section~\ref{borel-reg:explanatory-power}, we gave the general form of a thimble integral associated with a map $f \maps X \to \C$.
+The important thing about $\C$ here turns out to be its {\em translation surface} structure, which picks out an atlas of charts related by translations and provides a global sense of direction.
+The geometry of translation surfaces, described more fully in Section~\ref{sec:transl}, provides a natural setting for the Laplace transform.
+It will therefore be useful to place thimble integrals in this setting as well.
+
+Given a translation chart $\zeta$ on a translation surface $B$, we write $\mathcal{J}_{\zeta, \alpha}^\theta$ to denote the ray in direction $\theta$ starting at $\zeta = \alpha$.
+Consider a map $f \maps X \to B$ with a critical value at $\zeta = \alpha$, supposing for the moment that $X$ is an $N$-dimensional complex manifold.
+Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$; a {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
+
+To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
+Near $a$ we can always find coordinates $t_1, \ldots, t_N$ on $X$ with $f = t_1^2 + \ldots + t_N^2$.
+
+%%To see why the term ``thimble'' is fitting, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
+Near $a$ we can always find coordinates $x_1, \ldots, x_N$ on $X$ in which $\mathcal{C}^\theta_a$ looks like the paraboloid
+where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}
 
@@
 \textcolor{orange}{[As a start\ldots]} We recall the well-known result\color{black}
-\begin{lemma}\label{lem:thimble_proj_formula}
-A function $\iota$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota$ is given by the {\em thimble projection formula}
+\begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
+A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula}
-\iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}^\theta(\zeta)}\nu \right),
-\end{equation}
-where $\mathcal{C}^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
-Notice that $\mathcal{C}(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\mathcal{C}$ needs an orientation, but the orientation is arbitrary.]}
+    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+\textcolor{magenta}{[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
@@
 %     
-\subsubsection{Other results}
-%
-In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.
+\subsubsection{Other results}\label{sec:other_results}
+%
+\paragraph{New perspectives on the Laplace transform}
+%
+\textcolor{orange}{[Revise\ldots]}\textcolor{RoyalBlue}{In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.}
 
@@
 \end{center}
-
-We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+%
+\paragraph{New and old examples}
+%
+We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
+\begin{todo}the anharmonic oscillator...).\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
@@
 For instance, for the Airy function we will make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}.
-\textcolor{red}{The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
-
+\begin{todo}The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).\end{todo} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
+%
+\paragraph{Links to resurgence}
+%
 Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
@@
 %\end{itemize}
-\subsection{Plan of the paper}
+\subsection{Organization of the paper}
 The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
@@
 We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-\textcolor{red}{The second one, Appendix~\ref{apx:generalities_ODEs}, reviews the main aspects of \cite{reg-sing-volterra}.}
+\textcolor{red}{Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.}
+%
+\subsection{Notation}
+In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane).
+We have adopted a variable naming convention that makes these distinctions apparent at a glance.
+\begin{notation*}
+Functions and series on the frequency and position domains are named as follows.
+\begin{center}
+\begin{tabular}{c|c|c}
+& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
+\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
+\end{tabular}
+\end{center}
+We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.
+
+The frequency and position variables $z$ and $\zeta$ are excepted from this convention.
+The frequency variable is lower-case, even though it lives on the frequency domain, and neither variable gets a tilde when it serves as a formal variable rather than a coordinate function.
+\end{notation*}
+
+Here are some examples of this notation in action.
+Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the position domain into functions on the frequency domain, we might write $\laplace_{\zeta,0} \phi = \Phi$.
+On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
 %
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
-Already at the formal level, irregular singular ODEs have a distinguished behaviour, namely they admit divergent formal series solutions in the form of trans-monomials.
-In particular, for level $1$ ODEs of the kind we study in this paper, the Poincar\'e method gives an algorithm to compute formal solutions of $\mathcal{P}\Phi=0$, see~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Then, the main question is how to ``promote'' a formal solution to an analytic one, and here is where summability methods will play a role~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-\begin{center}
-\textcolor{orange}{[Move the table or whatever up here. What are we trying to communicate, and how should the table look to communicate it?]}
-\end{center}
-\subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
-In fact, even if it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one (see~\cite[Chapter 14]{balser}).
-Then, the Ramis Index Theorem shows that the formal solutions $\series{\Phi}$ of $\mathcal{P}\Phi=0$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
-Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.
-\subsubsection{\textcolor{orange}{[Resurgence section]}}
-Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the role of the position domain.
-Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform.
-In particular the Borel transform of the formal solution $\series{\Phi}$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
-For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
-Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
-Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
-However, the advantage of resurgence compared to the usual Borel summation, is in the study of the Stokes phenomena, which is another distinguished feature of irregular singular ODEs.
-Indeed, the Stokes phenoma is closely related to the fact that formal solutions are divergent, and the so called Stokes constants encode the ``jumps" of the underlying analytic solution which is deifned on sectors of openening angle $\pi$ and when extended by continuation on larger sectors it jumps by an exponentially small correction.
-As an example, the first order equation \[\Phi'=\Phi+\frac{1}{z}\] has formal solution $\series{\Phi}=\sum_{n=0}^\infty n!z^{-n-1}$.
-Then, its Borel transform has a simple pole at $\zeta=1$.
-Consequently, the ``jump'' of its Borel sum occurs across the positive real axis $\Re(z)>0$ and it is given by $2\pi ie^{-z}$.
-
-In a nutshell, the aim of resurgence is to study the analytic continuation of the Borel transform of a divergent series, in particular the location of sngularities in the position domain and Stokes constants computed after analytic continuation across the singularities.
-Then, the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) give the input to set-up a Riemann--Hilbert problem, whose solution would be a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
-\subsubsection{\textcolor{orange}{[Laplace transform methods section]}}
-So far we have been discussed the classical approaches to summability and reusrgence of formal solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
-In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
-Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral.
-This is the approahc we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
-it is a Borel regular solution.
-As for \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
-Indeed, building on our results of~\cite{reg-sing-volterra}, our approch will take the advantage of working on the position domain.
-
-A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
-However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.
-
-\textcolor{orange}{[Move this to beginning, and possibly revise]} Summarizing, we collect the main methods to solve irregular singular ODEs in the following table stressing the difference between formal and analytic solutions in either the frequency and the position domain.
+At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials.
+In particular, the trans-monomial characterizes the different asymptotic behvaiours of the underlying analytic solution---whose existence is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
+Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.
+
+Since in this paper we focus on buidling a frame of solutions, without dicussing the Stokes phenomenon, we will describe below the main methods to solve irregular singular ODEs stressing the difference between formal and analytic solutions in either the frequency and the position domain.
+A summary is given in the following table
 \begin{center}
@@
 
+\subsubsection{Poincar\'e method and Borel--Laplace summation}
+For a level $1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\Phi_\alpha$ of the form
+\begin{equation}
+    \Phi_\alpha=e^{\alpha z} z^{-\tau} \sum_{n=0}^\infty a_n z^{-n}
+\end{equation}
+with $P(-\alpha)=0$ and $\tau=Q(-\alpha)/P'(-\alpha)$. We will refer to $\Phi_\alpha$ as Poincar\'{e}'s formal solutions.
+
+Then, although it is not contructive, the M.A.E.T.
+guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
+In particular, the Ramis Index Theorem shows that the formal solutions $\Phi_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+This motivated the desire to promote formal solutions to analytic ones through the development of summability methods, even beyond the study of level-$1$ ODEs~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+% \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
+% Although it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
+The Ramis Index Theorem shows that the formal solutions are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+\textcolor{orange}{[Revise\ldots]} \textcolor{RoyalBlue}{Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.}
+\subsubsection{\'Ecalle's resurgence theory}
+The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
+
+In a nutshell, the aim of resurgence is to study the analytic continuation of the Borel transform of a divergent series, in particular the location of sngularities in the position domain and Stokes constants computed after analytic continuation across the singularities.
+
+Recall, that resurgent $1$-Gevrey series have an endlessly analytically continuable Borel transform.
+Thus resurgence makes naturally a bridge between formal and analytic solutions in the position domain.
+Indeed, differential equations in the frequency domain can be turned into integral equations in the position domain, using the Borel transform.
+In particular the Borel transform of the formal solution $\series{\Phi}_\alpha$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
+For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
+Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
+
+However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
+This is an advantage of resurgence techniques compared to the usual Borel summation method.
+
+% Then, the Stokes phenomenon is another distiguishd feature of irregular singular ODEs, an it is closely related to the fact that formal solutions are divergent. 
+% Indeed, the so called Stokes constants encode the ``jumps" of the underlying analytic solution which are charcateriz to have different asymptotics in different sectors saparated by Stokes lines.
+and when extended by continuation on larger sectors it jumps by an exponentially small correction.
+As an example, the first order equation \[\Phi'=\Phi+\frac{1}{z}\] has formal solution $\series{\Phi}=\sum_{n=0}^\infty n!z^{-n-1}$.
+Then, its Borel transform has a simple pole at $\zeta=1$.
+Consequently, the ``jump'' of its Borel sum occurs across the positive real axis $\Re(z)>0$ and it is given by $2\pi ie^{-z}$.
+
+% Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the role of the position domain.
+Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform.
+In particular the Borel transform of the formal solution $\series{\Phi}$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
+For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
+Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
+Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
+
+\subsubsection{Laplace transform methods and fixed point iteration}
+So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
+In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
+Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral.
+This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
+it is a Borel regular solution.
+As for \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
+Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.
+%In addition, as we will show in Section~\ref{sec:new-summability-proof}.
+
+A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
+However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.
+
 \color{RoyalBlue}
@@
 At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
-This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Theorem~\ref{thm:soln_is_asymptotic}).
+This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Corollary~\ref{cor:soln_borel-reg}).
 Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.}
+\subsubsection{Thimble integral in physics}
+
+\subsubsection{Thimble integral in geometry}
+
+\subsubsection{Asymptotic of thimble integrals}
+Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
+
+In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z \to \infty$ in direction $\theta$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
+
+This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
+In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
+In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
+
+\color{RoyalBlue}
+Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
 In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion (see also \cite{Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}).
@@
 %    
+\color{black}
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 \par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
+\begin{center}
+\phaseSpaceLaplace
+\captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point.
+The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
+\end{center}
 
@@
 \end{proof}
-\color{NavyBlue}
 \begin{prop}\label{prop:inverse_laplace_analytic}
@@
 \end{center}
-Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$. Along $\mathcal{C}$, we have
+Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
+Along $\mathcal{C}$, we have \textcolor{orange}{where does the estimate come from?}
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
-for some $\mu \in (\lambda, \lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
-\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\lambda' - \sin(\varepsilon/2)\,|t|\big). \]
-
+for some $\mu \in (\Lambda, \Lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
+\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big). \]
+\textcolor{orange}{Why on $\mathcal{C}$ the real part of $z$ is bounded like that?}
 %%Choose a path $\textcolor{magenta}{\mathcal{C}}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
@@
 \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
-& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
+& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
 \end{align*}
@@
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
-& = e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
-& \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
+& \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
 \end{align*}
@@
 %\color{black}
-\subsubsection{Action on trans-series}\label{sec:action_transseries}
+\subsubsection{Action on trans-monomials}\label{sec:action_transseries}
 %
 \color{DarkBlue}
-{\em Trans-series} are formal objects that greatly generalize formal power series.
-Their full definition is quite involved~\cite{aniceto2019primer}, especially when complex exponents are allowed~\cite{van-der-hoeven2001complex}.
+\textcolor{orange}{[We can add ``As discussed in Section~[relevant historical section]''\ldots]} Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
+Formally, this behavior is captured in a {\em formal integral} solution: an expression
+\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
+in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
+
+Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.
+The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
+The trans-monomials in the spaces $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider.
+\color{black}
+%%
+%%{\em Trans-series} are formal objects that greatly generalize formal power series.
+Their full definition is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
 We will only see examples of the simple form
-\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha, \]
-where $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
-Each term $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ is called a {\em trans-monomial}.
-
-Trans-series of this form play a crucial role in the theory of ODEs with irregular singularities.
-In particular, they exhibit a formal analogue of the Stokes phenomenon: their asymptotics can change sharply from one direction to the next.
+%%\[  e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha, \]
+%%where $\alpha$ is a complex number, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+This is an example of a {\em trans-monomial}.
+%%
+%%Trans-monomials of this form play a crucial role in the theory of ODEs with irregular singularities. Linear combinations of such trans-monomials encode the Stokes phenomenon:
+%%
+%%In particular, they exhibit a formal analogue of the Stokes phenomenon: their asymptotics can change sharply from one direction to the next.
 Trans-monomials $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ can be ordered by $\Re(e^{i\theta} \alpha)$ for any direction $\theta$.
-When a trans-series converges, its sum becomes dominated by the lowest term in this ordering as $\Re(e^{-i\theta} z)$ grows.
-
-We can extend the definition of the Borel transform to trans-series by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
-\par\color{RoyalBlue}
-A trans-series is a generalization of usual power series, whose building blocks (called trans-monomials) are of the form $e^{\alpha_n z}\varphi_n$ where $\alpha_n$ is a sequence of complex numbers such that \textcolor{PaleVioletRed}{[exponents must lie along a ray]} $0=\alpha_0 e^{-i\theta}< \alpha_1 e^{-i\theta}<...<\alpha_n e^{-i\theta}<...$ and $\varphi_n\in\C\llbracket z^{-1}\rrbracket$ for every $n$:
-
-\[T_{\alpha,\varphi}:=\sum_{n=0}^{\infty} e^{\alpha_n z} \varphi_n(z) \]
-
-The main feature of $T_{\alpha,\varphi}$ is that its asymptotics as $\text{ Re } e^{i\theta}z \to +\infty$ is $\varphi_0$.
-In fact, they play a crucial role in the theory of ODEs with irregular singularities.
-
-It's natural to ask whether we can extend the definition of $\borel_\zeta$ to transseries, and we will achieve it using the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ in identity~\eqref{change-chart}.
-\color{black}
+When a trans-monomial \textcolor{orange}{[of this form]} converges, its sum becomes dominated by the lowest term in this ordering as $\Re(e^{-i\theta} z)$ grows.
+%%\[\sum_{\alpha\in A}  e^{\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
+%%$A$ is the set of roots of $P$.
+
+We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
 \begin{definition}
@@
 \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
-The action of $\borel_\zeta$ extends to general trans-monomials and trans-series by countable linearity.
+The action of $\borel_\zeta$ extends to general trans-monomials \textcolor{orange}{[of this form]} by countable linearity.
 \end{definition}
@@
 \subsection{The Borel and Laplace transforms as algebra homomorphisms}\label{sec:borel-laplace-homom}
-We begin this section introducing some notation.
-\begin{notation*}
-In reasoning about Borel summation, it is important to keep track of whether we are working with holomorphic functions or formal series, and whether we are working on the position domain (the Borel plane) or the frequency domain (the $z$ plane).
-We have adopted a variable naming convention that makes these distinctions apparent at a glance.
-\begin{center}
-\begin{tabular}{c|c|c}
-& \textbf{Analytic}: no tilde & \textbf{Formal}: tilde \\[1mm] \hline
-\vphantom{\rule{0mm}{5mm}} \textbf{Frequency domain}: upper case & $\Phi$ & $\series{\Phi}$ \\[1mm] \hline
-\vphantom{\rule{0mm}{5mm}} \textbf{Position domain}: lower case & $\phi$ & $\series{\phi}$ \\[1mm]
-\end{tabular}
-\end{center}
-We will sometimes use a hat to emphasize that we got a holomorphic function $\hat{\phi}$ by taking the sum of formal series $\series{\phi}$.
-\end{notation*}
-Here are some examples of this notation in action.
-Since the Laplace transform $\laplace_{\zeta, 0}$ turns functions on the position domain into functions on the frequency domain, we might write $\laplace_{\zeta,0} \phi = \Phi$.
-On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
+%
 \subsubsection*{The Laplace transform as algebra homomorphism}
@@
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
-\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha) \right] \]
-of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\widehat{\Omega}_\alpha)$ from Section~\ref{sec:reg-decay}.
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
+\begin{todo}[define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}
@@
 By Theorem~\ref{translation} and the results of Section~\ref{sec:reg-decay}, the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ is a left-invertible map
-\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexpalg{-\tau_\alpha-1}(\widehat{\Omega}_\alpha). \]
+\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^{\textcolor{LimeGreen}{\bullet}}). \]
 With $\Psi_\alpha = \laplace^\theta_{\zeta, \alpha} \psi_\alpha$, the desired result follows.
@@
 Take an open sector $\Omega_\alpha$ of the kind used in Theorem~\ref{re:thm:exist_uniq_ODE}, and expand it to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}.
-By Theorem~4 of \cite{reg-sing-volterra}, the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering space like $\widetilde{\C^\times}$.
+We can therefore use Theorem~4 of \cite{reg-sing-volterra} to show that $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
@@
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_\alpha$ as the Laplace transform of a function $\iota_\alpha$ which is explicitly given by the \textit{thimble projection formula}.% \eqref{eqn:formula-proof}.
-\begin{lemma}\label{lem:thimble_proj_formula-proof}
-\textcolor{magenta}{[Well-known result---see, e.g., \S 3.3 of \cite{pham}, which uses the variation $\nu/df$ instead of derivative of integral.]} A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
+The first step will be to rewrite $I_\alpha$ as the Laplace transform of a function $\iota_\alpha$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.
+\begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula-proof}
+A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula-proof}
-    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right),
-\end{equation}
-where $\mathcal{C}_\alpha^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
-Notice that $\mathcal{C}_\alpha^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
+    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+\end{equation}
+where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
 \textcolor{magenta}{[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
 \end{lemma}
+\begin{remark}
+In \cite{pham}, Pham describes this formula in a slightly different form, integrating the variation of $\nu/df$, instead of differentiating the integral as we do in equation~\ref{eqn:formula-proof}.
+\end{remark}
 \begin{proof}
@@
 which is easier to solve.
-Unfortunately, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
+Unfortunately, an analytic solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} will not satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} in general.
 However, as we show in Appendix~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel-AL} {\em will} satisfy equation~\eqref{int-eq:spatial-mod-bessel-AL} if it belongs to $(\zeta - \alpha)^\sigma \mathcal{O}_{\zeta = \alpha}$ for some $\sigma \in (-1, 0)$.
@@
 This is good news, because equation~\eqref{diff-eq:spatial-mod-bessel-AL} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a solution of the desired kind at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
+We can see the regular singularities by rewriting equation~\eqref{diff-eq:spatial-mod-bessel-AL} as follows:
 \[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
@@
 For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
-We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other root.
+We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other roots (see Figure~\ref{fig:sectorial_domain--with roots P}).
 We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
@@
 
-The Poincar\'{e} algorithm, as discussed in Sections \ref{sec:asympt-AL} and \ref{sec:new-summability-proof}, picks out a frame in the space of formal trans-series solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as discussed in Sections \ref{sec:asympt-AL} and \ref{sec:new-summability-proof}, picks out a frame in the \textcolor{magenta}{space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]} of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
@@
 
-\color{NavyBlue}
 Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
@@
 \[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
-across the branch cut $\mathcal{J}^\theta_{\zeta, \mp 1}$.
+\begin{verify}
+\begin{align*}
+\frac{m}{2n}\,\frac{2\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(1+\tfrac{m}{n}\big)} & = \frac{\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(\tfrac{m}{n}\big)} \\
+& = \pi i\,\frac{\sin\big(\pi\tfrac{m}{n}\big)}{\pi} \\
+& = i \sin\big(\pi\tfrac{m}{n}\big) \\
+&= \sinh\big(i\pi\tfrac{m}{n}\big)
+\end{align*}
+\end{verify}
+across the branch cut $\mathcal{J}^\theta_{\zeta, \pm 1}$.
 When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$.
@@
 \[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
-and for even $j$, we have \begin{todo}{[check sign]}\end{todo}
-\[ K^{(j)}_{m/n}(z) = -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+and for even $j$, we have
+\[ K^{(j)}_{m/n}(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
 \]
@@
 \[ K^{(j)}_{m/n}(z) = \begin{cases}
-\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
-\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
+\hphantom{-}\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
+-\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
 \end{cases} \]
@@
 %
+\color{DarkBlue}
 Formula~\eqref{integral:mod-bessel-rational-AL} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
@@
 \[ K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
-and for even $j$, we get \begin{todo}{[check sign]}\end{todo}
-\[ K^{(j)}_\mu(z) = -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+and for even $j$, we get
+\[ K^{(j)}_\mu(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
 \]
-
-\textcolor{orange}{[Old text\ldots]}
+\color{black}
+\par\textcolor{orange}{[Old text\ldots]}
 \color{RoyalBlue}
@@
 On the other hand, equation \eqref{eqn:K-mu} gives \textcolor{magenta}{[relationship? what are we trying to say?]}
-\begin{align*}\label{eqn:borel_bessel0}
-K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
-& = \int_{\mathcal{J}^\theta_{\zeta, 1}} \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}}\;d\zeta.
-\end{align*}
+\begin{align}
+K_0(z) & \notag = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
+&\label{eqn:borel_bessel0} = \int_{\mathcal{J}^\theta_{\zeta, 1}} \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}}\;d\zeta.
+\end{align}
 \begin{verify}
@@
 \subsection{Asymptotic analysis}
-From the general theory of ODE of Poincar\'e rank $1$, we know that the space of trans-series solutions of ~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
+From the general theory of ODE of Poincar\'e rank $1$, we know that the \textcolor{magenta}{space of trans-series solutions} of~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]

### 2024-04-09 exp-resurgence.tex
Revise Bessel 0 calculation

@@
 Given a translation chart $\zeta$ on a translation surface $B$, we write $\mathcal{J}_{\zeta, \alpha}^\theta$ to denote the ray in direction $\theta$ starting at $\zeta = \alpha$.
-Consider a map $f \maps X \to B$ with a critical value at $\zeta = \alpha$, supposing for the moment that $X$ is an $N$-dimensional complex manifold.
-Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$; a {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
-
-To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
+Consider a map $f \maps X \to B$ with a critical value at $\zeta = \alpha$.
+Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through one of the critical points that $f$ sends to $\zeta = \alpha$.
+When the complex manifold $X$ is one-dimensional, as it will be throughout this paper, a {\em Lefschetz thimble} is an oriented component of $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ that runs through a single, non-degenerate critical point of $f$.
+A one-dimensional Lefschetz thimble is determined up to orientation by the critical point $a$ that it runs through and the direction $\theta$ of the ray that it projects to, so we will often denote it with a symbol like $\mathcal{C}^\theta_a$.
+\begin{center}
+\includegraphics[width=6.5cm]{figures/rays_ge6.png}
+\hspace{0.5cm}
+\includegraphics[width=6.5cm]{figures/thimbles-n5.png}
+\captionof{figure}{On the left, we see the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the translation surface $B = \C$, where $\zeta$ is the standard coordinate.
+On the right, we see the complex manifold $X = \C$, colored according to a holomorphic map $f \maps X \to B$ whose critical values are $\zeta = \pm 1$.
+The Lefschetz thimbles over the rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ are shown.}
+\end{center}
+%%
+%%supposing for the moment that $X$ is an $N$-dimensional complex manifold.
+%%
+%%Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$.
+When {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
+
+For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
+Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
+Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
+\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
+Each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
+There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$.
+Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$.
+When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.
+
+\textcolor{orange}{[\ldots]}
+%%
+%%To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
 Near $a$ we can always find coordinates $t_1, \ldots, t_N$ on $X$ with $f = t_1^2 + \ldots + t_N^2$.
-
+%%
 %%To see why the term ``thimble'' is fitting, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
 Near $a$ we can always find coordinates $x_1, \ldots, x_N$ on $X$ in which $\mathcal{C}^\theta_a$ looks like the paraboloid
-where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}
+%%where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}
 
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsection{Borel regularity for level~$1$ ODEs}
+\subsection{Borel regularity for level~$1$ ODEs}\label{sec:history_ODE}
 %
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
-At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials.
+\color{DarkViolet}
+Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
+Formally, this behavior is captured in a {\em formal integral} solution: an expression
+\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{\varphi}_\alpha \]
+in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
+
+Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series} \footnote{The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, as indicated by the Poincar\'e method~\ref{sec:Poincare method}.
+Then, the existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
+\textcolor{DarkBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour.
+Their ``formal integral'' series solutions, discussed in Section~\ref{sec:action_transseries}, exhibit the {\em Stokes phenomenon}: asymptotic behavior that changes sharply from one direction to the next.
+The existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).} %\textcolor{RoyalBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials.
 In particular, the trans-monomial characterizes the different asymptotic behvaiours of the underlying analytic solution---whose existence is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
-Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.
-
-Since in this paper we focus on buidling a frame of solutions, without dicussing the Stokes phenomenon, we will describe below the main methods to solve irregular singular ODEs stressing the difference between formal and analytic solutions in either the frequency and the position domain.
-A summary is given in the following table
+Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.}
+\color{Maroon}
+Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
+Formally, this behavior is captured in a {\em formal integral} solution: an expression
+\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
+in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
+
+Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.
+The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
+The trans-monomials in the spaces $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider.
+\color{black}
+
+The formal integral solutions and the M.A.E.T.
+have inspired several other solution methods for linear level~1 ODEs.
+The ones we will discuss in this section are summarized in the following table.
+We classify solution methods by two features: whether the solutions they produce are analytic functions or formal series, and whether they solve the original equation on the frequency domain or an equivalent equation in the position domain.
+%\textcolor{RoyalBlue}{Since in this paper we focus on buidling a frame of solutions, without dicussing the Stokes phenomenon, we will describe below the main methods to solve irregular singular ODEs stressing the difference between formal and analytic solutions in either the frequency and the position domain.
+A summary is given in the following table}
 \begin{center}
@@
 & \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+\textbf{Frequency} &  & Poincar\'{e}: \textcolor{DarkBlue}{``formal integral'' series \textcolor{orange}{(?)}} \textcolor{DarkViolet}{trans-monomial ansatz}~\cite{int-irreg} \\ \hline
 \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
@@
 
-\subsubsection{Poincar\'e method and Borel--Laplace summation}
+\subsubsection{Poincar\'e method and Borel--Laplace summation}\label{sec:Poincare method}
 For a level $1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\Phi_\alpha$ of the form
+For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\series{\Phi}_\alpha$ of the form
 \begin{equation}
-    \Phi_\alpha=e^{\alpha z} z^{-\tau} \sum_{n=0}^\infty a_n z^{-n}
-\end{equation}
-with $P(-\alpha)=0$ and $\tau=Q(-\alpha)/P'(-\alpha)$. We will refer to $\Phi_\alpha$ as Poincar\'{e}'s formal solutions.
+\series{\Phi}_\alpha=e^{\alpha z} z^{-\tau_\alpha} \sum_{n=0}^\infty a_n z^{-n}
+\end{equation}
+with $P(-\alpha) = 0$ and $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$. We will refer to $\Phi_\alpha$ as Poincar\'{e}'s formal solutions.
 
@@
 Indeed, differential equations in the frequency domain can be turned into integral equations in the position domain, using the Borel transform.
-In particular the Borel transform of the formal solution $\series{\Phi}_\alpha$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
+In particular the Borel transform of the formal solution $\series{\Phi}_\alpha$ is a convergent power series, and its sum can be studied by in terms of the equation it satisfies.
 For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
@@
 %
-\textcolor{DarkBlue}{Over the complement $B'$ of the branch points, the translation structure gives us a holomorphic map $z \maps T^*B' \to \C$.
+Over the complement $B'$ of the branch points, the translation structure gives us a holomorphic map $z \maps T^*B' \to \C$.
 This map is an isomorphism on every fiber, trivializing $T^*B$ almost globally.
 Over a branch point $b$ of cone angle $2\pi n$, we get an analogous isomorphism $z \maps T^*_bB^{\otimes n} \to \C$.
-In both cases, we will call $z$ the {\em frequency coordinate} of $B$.}
-\par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
+In both cases, we will call $z$ the {\em frequency coordinate} of $B$.
+%\par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
 \begin{center}
@@
 \subsubsection{Action on trans-monomials}\label{sec:action_transseries}
-%
-\color{DarkBlue}
-\textcolor{orange}{[We can add ``As discussed in Section~[relevant historical section]''\ldots]} Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
-Formally, this behavior is captured in a {\em formal integral} solution: an expression
-\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
-in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
-For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
-
-Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.
-The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
-The trans-monomials in the spaces $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider.
-\color{black}
+%Recall from the discussion in Section~\ref{sec:history_ODE}, that formal solutions of irregular singualr ODEs are in form of trans-monomials. 
 %%
@@
 On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
+\color{DarkBlue}
+\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1} \big]=e^{-\alpha z} z^{-\nu-1}. \]
+\color{DarkViolet}
 \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
-The action of $\borel_\zeta$ extends to general trans-monomials \textcolor{orange}{[of this form]} by countable linearity.
+The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
+%The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ by countable linearity.
 \end{definition}
 From this definition, and identity~\eqref{change-chart}, we deduce that
+\color{DarkBlue}
+\begin{align*}
+e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = e^{-z\alpha} z^{-\nu-1} \\
+\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = z^{-\nu-1} \\
+\borel_{\zeta}\big[e^{-z\alpha}z^{-\nu-1}\big] & = \frac{\zeta_\alpha^\nu}{\Gamma(\nu+1)}.
+\end{align*}
+\color{DarkViolet}
 \begin{align*}
@@
 \end{align*}
+\color{black}
 %%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
@@
 %\end{lemma}
+
+\color{DarkViolet}
+Notice that the Borel transform extends to $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ for $\tau\in\R\setminus\Z$ by conutably linearity.
+In fact, as we argue at the end of Section~\ref{sec:geometry_borel}
+\[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\nu}{\Gamma(\tau+1)}.\]
+\color{black}
 \subsubsection{Change of translation chart}\label{transl-borel}
@@
 %
-\color{DarkBlue}
 Formula~\eqref{integral:mod-bessel-rational-AL} expresses the modified Bessel function $K_{m/n}$ as an exponential integral on a finite cover of $\C$.
@@
 For odd $j$, we get
-\[ K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+\begin{equation}\label{eq: K_j_mu at 1}
+  K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta,
+\end{equation}
 and for even $j$, we get
-\[ K^{(j)}_\mu(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
-\]
-\color{black}
-\par\textcolor{orange}{[Old text\ldots]}
-\color{RoyalBlue}
-\begin{align*}
-    K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
-    &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
-\end{align*}
-where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$.
+\begin{equation}\label{eq: K_j_mu at -1}
+ K^{(j)}_\mu(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\end{equation}
+
+% \color{black}
+% \par\textcolor{orange}{[Old text\ldots]}
+% \color{RoyalBlue}
+% \begin{align*}
+%     K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
+%     &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
+% \end{align*}
+% where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$.
 Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf} \textcolor{PaleVioletRed}{[Please clean up operators that are repeated across line breaks, like the $=$ below.
 I like the equation spacing in the ``Thimble projection reasoning for Airly-Lucas functions'' section; can we copy that here?]}
-\begin{multline*}
-     {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
-     =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
-\end{multline*}
-hence 
-%
-\[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
-%
-Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
-
-\begin{align}
-    K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
-    &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
-\end{align}
-\color{black}
-\subsubsection{The case $\mu=0$}
+% \begin{multline*}
+%      {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
+%      =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
+% \end{multline*}
+% hence 
+% %
+% \[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
+% %
+% Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
+
+% \begin{align}
+%     K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
+%     &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
+% \end{align}
+% \color{black}
+\subsubsection{The modified Bessel function with parameter $0$}
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 Since the integrand is an odd function, the upward part of the path integrates to zero. Since the integrand is also $2\pi i$-periodic, the leftward and rightward parts of the integral collapse to
-\begin{align*}
-K_0(z) & = \frac{1}{2\pi i} \int_0^\infty \exp\left[z \cosh(t)\right]\,2\pi i\,dt \\
-& = \int_0^\infty \exp\left[-z \cosh(t)\right]\,dt \\
-& = \int_1^\infty \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s},
-\end{align*}
+\begin{align}
+K_0(z) & = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t + \pi i)\right]\,\pi i\,dt \notag - \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t - \pi i)\right]\,\pi i\,dt \notag \\
+& = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \notag \\
+& = \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,dt \label{int:k0_cosh} \\
+& = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}, \notag
+\end{align}
 with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
 
-On the other hand, equation \eqref{eqn:K-mu} gives \textcolor{magenta}{[relationship? what are we trying to say?]}
-\begin{align}
-K_0(z) & \notag = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
-&\label{eqn:borel_bessel0} = \int_{\mathcal{J}^\theta_{\zeta, 1}} \frac{e^{-z\zeta}}{\sqrt{\zeta^2-1}}\;d\zeta.
-\end{align}
+To confirm that the calculation above is consistent with Section~\ref{countable-cover}, use formulas \eqref{eq: K_j_mu at 1} and \eqref{eq: K_j_mu at -1} to get
+\begin{align*}
+K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
+& \hphantom{=} - \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta
+\end{align*}
+The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent:
+\begin{equation}\label{eqn:borel_bessel0}
+K_0(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
+\end{equation}
+We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution.
 \begin{verify}
-    We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning: from the expression of $K_0$ 
+\par
+For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives
+\begin{align*}
+K^{(j)}_\mu(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
+& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} \\
+& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} \\
+& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} \\
+& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2}
+\end{align*}
+For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
+\begin{align*}
+K^{(j)}_\mu(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} d\zeta \\
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(?)}} \\
+& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
+& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+\end{align*}
+
+We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning. From the expression of $K_0$ 
 \begin{equation}
-        K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt
-    \end{equation}
-    we set $\zeta=\cosh(t)$, and choosing a branch for the square root
+K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt,
+\end{equation}
+we set $\zeta=\cosh(t)$. Choosing a branch for the square root
 \begin{align*}
@@
 \end{verify}
-
+%
 \subsection{Generalized Airy}
+%
 In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
@@
 \subsection{Third-degree thimble integrals}
-\color{DarkBlue}
 In this section, we consider the thimble integral
@@
 \item[] \textbf{One degenerate critical point}
-
 When $p$ is zero, $g$ has a single degenerate critical point.

### 2024-04-09 exp-resurgence.tex
general updates and revisions

@@
 %
-We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
+We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals \textcolor{VioletRed}{[These examples are all closely related; they're not just examples of second-order ODEs]}: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
 \begin{todo}the anharmonic oscillator...).\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
@@
 
-Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series} \footnote{The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, as indicated by the Poincar\'e method~\ref{sec:Poincare method}.
+Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.\footnote{For the full definition of a trans-series, see~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, because they are the ones used in the the Poincar\'e method, discussed in Section~\ref{sec:Poincare method}.
 Then, the existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
@@
 On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
-\color{DarkBlue}
-\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1} \big]=e^{-\alpha z} z^{-\nu-1}. \]
-\color{DarkViolet}
 \[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
 The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
-%The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ by countable linearity.
 \end{definition}
 From this definition, and identity~\eqref{change-chart}, we deduce that
-\color{DarkBlue}
-\begin{align*}
-e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = e^{-z\alpha} z^{-\nu-1} \\
-\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-\nu-1}\big] & = z^{-\nu-1} \\
-\borel_{\zeta}\big[e^{-z\alpha}z^{-\nu-1}\big] & = \frac{\zeta_\alpha^\nu}{\Gamma(\nu+1)}.
-\end{align*}
-\color{DarkViolet}
 \begin{align*}
@@
 \end{align*}
-\color{black}
 %%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
@@
 
-\color{DarkViolet}
-Notice that the Borel transform extends to $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ for $\tau\in\R\setminus\Z$ by conutably linearity.
-In fact, as we argue at the end of Section~\ref{sec:geometry_borel}
-\[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\nu}{\Gamma(\tau+1)}.\]
+\textcolor{DarkBlue}
+We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
+We conclude that
+\[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\tau}{\Gamma(\tau+1)}\]
+for any $\tau \in \R\setminus\Z$.
 \color{black}
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
-The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace \textcolor{orange}{[define $\widehat{\Omega}_\alpha$]}
+The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
@@
 The frame is generated by solutions of the form $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$, with $v_\alpha \in \singexpalg{-1/2}(\Omega_\alpha)$.
-\begin{verify}
-We get $v_\alpha$ from the existence result in Section~\ref{borel_reg-ODE}, which gives $v_\alpha = \zeta^{\tau_\alpha-1} + v_\alpha'$ with $\tau \in (0, \infty)$ and $v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega)$ \textcolor{magenta}{[What is this space?
-does not match notation from {\tt reg-sing-volterra}]} for some $\epsilon \in (0, 1]$.
-Looking back at the definitions of our weighted $L^\infty$ spaces, we can see that
-\begin{align*}
-v_j' \in \holoL{\infty, 1-\tau-\epsilon}(\Omega) & \Longrightarrow \zeta_j^{1-\tau-\epsilon}\,v_j' \text{ is bounded near } \zeta_j = 0 \\
-& \Longrightarrow \zeta_j^\epsilon\,\zeta_\alpha^{1-\tau-\epsilon}\,v_j' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow \zeta_\alpha^{1-\tau}\,v_\alpha' \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longrightarrow v_\alpha' / \zeta_\alpha^{\tau_\alpha-1} \text{ goes to } 0 \text{ as } \zeta_\alpha \text{ goes to } 0 \\
-& \Longleftrightarrow v_j' \in o\big(\zeta_\alpha^{\tau_\alpha-1}\big).
-\end{align*}
-In this case, $\tau_\alpha = \tfrac{1}{2}$.
-\end{verify}
 
@@
 \begin{align*}
-K^{(j)}_\mu(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
+K^{(j)}_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
 & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} \\
-& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} \\
-& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} \\
-& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2}
+& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
+& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
+& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
 \end{align*}
@@
 \begin{align*}
-K^{(j)}_\mu(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
+K^{(j)}_0(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
 & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} d\zeta \\
 & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(?)}} \\
+%%& = \color{DarkViolet}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
+%%& =  \color{DarkViolet} \frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
+%%& = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
 & = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
@@
 
-We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection reasoning. From the expression of $K_0$ 
+We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection formula, \eqref{eqn:formula-proof}. From the expression of $K_0$ 
 \begin{equation}
@@
 we finally get 
-\[\int_1^{\infty} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
+\[\int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
 \end{verify}
@@
 \end{verify}
-\color{black}
-\color{RoyalBlue}
-\begin{remark}
-    The degenerate case $p=0$ can be recovered from the generic case, taking the limit of $I_+(z)$ as $p\to 0$. Indeed, 
-    \[ e^{-zq} I_+(z)=2 \sqrt{-\frac{p}{3}} K_{1/3}\Big(\frac{2p^{3/2}}{i3^{3/2}}z\Big)\]
-    and its limit as $p\to 0$ can be computed from equations 10.25.2 and 10.27.4 in \cite{dlmf} giving 
-    \[ e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) e^{-zq} z^{-1/3}.  \]
-
-    From the properties of the Laplace transform, we then deduce
-    \[e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) e^{-zq} z^{-1/3}= e^{\pi i/3} e^{-qz} \laplace_{\zeta,0}(\zeta^{-2/3}) = e^{\pi i/3} \laplace_{\zeta_{-q},q}(\zeta^{-2/3})\]
-    which agrees with the thimble integral representation of $I$ computed above. 
-\end{remark}
-\color{black}
+%
 \subsection{The triangular cantilever}\label{sec:catilever}
+%
 A {\em triangular cantilever} is a flexible strip with constant thickness and linearly tapered width, clamped at the broad end so it sticks out horizontally like a diving board.

### 2024-04-09 exp-resurgence.tex
Finish revising intro to history of level 1 ODEs

@@
 \item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
-In this case, we say $\series{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
+In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
 \end{enumerate}
@@
 \end{definition}
-To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
+To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let us take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
 
@@
 You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
-After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them.
+After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them.
 In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
@@
 \color{DarkBlue}
-Let us start again, \textcolor{orange}{[Revise\ldots]}
-%%Instead of starting with a formal solution to a problem, as we did in Section~\ref{intro:summation}, let us start with a holomorphic solution $\Phi$.
-Suppose it has an asymptotic expansion \series{\Phi} \defeq \aexp^\theta \Phi$.
+We will look at the effectiveness of Borel summation from an analytic perspective, as a regularity property of problems and their holomorphic solutions.
+Suppose we have a holomorphic function $\Phi$ which is a solution of some problem.
+If the asymptotic expansion $\series{\Phi} = \ae^\theta \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
 \color{black}
-
-Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$. 
+\par\textcolor{RoyalBlue}{Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$.}
 \begin{center}
@@
 \end{center}
-If $\series{\Phi}$ is Borel-summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
-Since different functions can be asymptotic to the same power series, taking the Borel sum of the asymptotic series of $\Phi$ must smooth away some details.
+If $\series{\Phi}$ is Borel summable, as described in Section~\ref{intro:summation}, its Borel sum $\hat{\Phi}$ is a new holomorphic function.
+Since different functions can have the same asymptotic expansion, taking the Borel sum of the asymptotic expansion of a function must smooth away some details.
 We will therefore call this process {\em Borel regularization}.
@@
 \item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.%\textcolor{red}{This is possible, by definition, if $\series{\Phi}$ is $1$-Gevrey.[Veronica: I'll remove this!
-Being Gevrey implies that the Borel transform is convergent, not that we can analytically continue it]}
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
-This is possible, by definition, if $\series{\Phi}$ is Borel-summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$.
+This is possible, by definition, if $\series{\Phi}$ is Borel summable.\footnote{More generally, we could take the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ starting at any point $\zeta = \alpha$ in $B$.
 The choice of starting point will play an important role in our study of ODEs and thimble integrals.}
 \end{enumerate}
-We will say a function is {\em Borel-regularizable} if its asymptotic expansion is Borel-summable, ensuring that we can carry out the last two steps.
+We will say a function is {\em Borel regularizable} if its asymptotic expansion is well-defined and Borel summable, ensuring that we can carry out all the steps.
 
 Defining a regularization process picks out a class of regular functions: the ones that are invariant under regularization.
-We will say a function is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
+We will say a function is {\em Borel regular} if it is Borel regularizable and Borel regularization leaves it unchanged.
 In other words, $\Phi$ is Borel regular if $\hat{\Phi} = \Phi$.
@@
 
-Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.\footnote{For the full definition of a trans-series, see~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in the study of level-$1$ ODEs, because they are the ones used in the the Poincar\'e method, discussed in Section~\ref{sec:Poincare method}.
-Then, the existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
+Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.\footnote{For the full definition of a trans-series, see~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in this paper.
+Poincar\'{e}'s method for solving linear level-$1$ ODEs, discussed in Section~\ref{sec:Poincare method}, produces trans-monomial solutions in these spaces.
+The Poincar\'{e} solutions serve as the terms of a general formal integral.
+Each Poincar\'{e} solution is the asymptotic expansion of an analytic solution, whose existence is guaranteed---non-constructively---by the Main Asymptotic Existence Theorem (M.A.E.T.).
 \textcolor{DarkBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour.
@@
 & \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency} &  & Poincar\'{e}: \textcolor{DarkBlue}{``formal integral'' series \textcolor{orange}{(?)}} \textcolor{DarkViolet}{trans-monomial ansatz}~\cite{int-irreg} \\ \hline
+\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
 \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
@@
 However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.
-
-\color{RoyalBlue}
-From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\series{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\series{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+%
+%
+% \color{RoyalBlue}
+% From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\series{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\series{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
 Since the cirtical values are distinct, the transmonomials $\series{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame.
@@
 
-At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
+% At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
 This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Corollary~\ref{cor:soln_borel-reg}).
@@
 
-\begin{remark}
-Our approach of solving regular singular Volterra equation---based on the contraction mapping theorem for suitable Banach spaces \cite{reg-sing-volterra}---is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
+% \begin{remark}
+% Our approach of solving regular singular Volterra equation---based on the contraction mapping theorem for suitable Banach spaces \cite{reg-sing-volterra}---is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
 \textcolor{orange}{Our approach differs from Braaksma's in two ways.
@@
 
-In future work, it might be useful to combine our approach with Braaksma's
-
-Combining our approach with Braaksma's, to
-
-We leave a possible generalization of our result to other classes of ODEs and difference equations for further pubblications.
+% In future work, it might be useful to combine our approach with Braaksma's
+
+% Combining our approach with Braaksma's, to
+
+% We leave a possible generalization of our result to other classes of ODEs and difference equations for further pubblications.
 \textcolor{orange}{[Let us do more compare-and-contrast!
 Our problem space is sort of orthogonal to Braaksma's, but we use the same solution space, so it seems like there could be a cool interaction there.]}
-\end{remark}
-
-\begin{remark}
-There are many ways to build a frame of solutions for these kinds of ODEs.
-\begin{center}
-\begin{tabular}{l|l|l}
-& \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
-\textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
-& Fixed-point iteration~\cite{reg-sing-volterra} \\
-\end{tabular}
-\end{center}
-In the late 1800s, Poincar\'{e} did it formally in the frequency domain~\cite{int-irreg}.
+% \end{remark}
+
+% \begin{remark}
+% There are many ways to build a frame of solutions for these kinds of ODEs.
+% \begin{center}
+% \begin{tabular}{l|l|l}
+% & \textbf{Analytic} & \textbf{Formal} \\ \hline
+% \textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+% \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
+% & Fixed-point iteration~\cite{reg-sing-volterra} \\
+% \end{tabular}
+% \end{center}
+% In the late 1800s, Poincar\'{e} did it formally in the frequency domain~\cite{int-irreg}.
 In the late 1900s, \'{E}calle and later authors did it formally in the position domain~\cite{EcalleIII,loday-Remy2011}.
@@
 
-In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame.
+% In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame.
 The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and Theorem~\ref{thm:exist_uniq_ODE} guarantees that our solutions are asymptotic to Poincar\'{e}'s ones.
-\end{remark} 
-%
-%
-%
-\color{black}
+% \end{remark} 
+%
+%
+%
 \subsection{Borel regularity for thimble integrals}
@@
 \end{proof}
-\textcolor{magenta}{[Introduce bare $\widehat{\Omega}$]}
+\textcolor{magenta}{[Introduce $\widehat{\Omega}^\bullet$]}
 \color{black}
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
-If a $1$-Gevrey trans-monomial \textcolor{orange}{[define]} $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
+If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
 \end{theorem}
@@
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
-Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel-summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
+Reprising the proof of Theorem~\ref{thm:summability_ODE}, we will show that these solutions are Borel summable, and their Borel sums generate the same frame as $\laplace_{\zeta, 1} v_1$ and $\laplace_{\zeta, -1} v_{-1}$.
 
@@
 \end{align*}
-The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent:
+The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent: \textcolor{magenta}{[result is right, but reasoning is wrong: integrals can't be directly combined, because they use different contours]}
 \begin{equation}\label{eqn:borel_bessel0}
@@
 & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-%%& = \color{DarkViolet}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
-%%& =  \color{DarkViolet} \frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
-%%& = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
-& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
-& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+& = \color{DarkViolet}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
+& =  \color{DarkViolet} \frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
+& = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
+& = \color{DarkViolet} -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+%%& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
+%%& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
+%%& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
 \end{align*}
@@
 \int_\mathcal{C} e^{-z(f + c)}\,\nu & = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
-& = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
 & = e^{-cz} J(z).
@@
 $\displaystyle \mathsf{T}_{(1/3)\,a_2/a_3}^*$ & $\displaystyle u^3 + pu + q$ & $\displaystyle \hphantom{e^{qz}} I\left(\frac{z}{a_3}\right)$ \\[5mm]
-$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle \textcolor{DarkViolet}{e^{qz}\,I\left(\frac{z}{a_3}\right)}$ \\[5mm]
 \end{tabular}
@@
 \textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+a$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
 $\displaystyle f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & $\displaystyle 4u^3 - 3u$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right)$ \\[5mm]
@@
 \end{center}
-We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel}:
-\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
+We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel-rational-AL}:
+\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{zq}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
@@
 \[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
+\textcolor{DarkViolet}{\[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-a_3 qz\right] K_{1/3}\left(2i \left(\frac{p}{3}\right)^{3/2} z\right). \]}
 Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.

### 2024-04-10 exp-resurgence.tex
Revise history of Laplace transform methods

@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
-\color{DarkViolet}
 Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
@@
 Each Poincar\'{e} solution is the asymptotic expansion of an analytic solution, whose existence is guaranteed---non-constructively---by the Main Asymptotic Existence Theorem (M.A.E.T.).
-\textcolor{DarkBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour.
-Their ``formal integral'' series solutions, discussed in Section~\ref{sec:action_transseries}, exhibit the {\em Stokes phenomenon}: asymptotic behavior that changes sharply from one direction to the next.
-The existence of corresponding analytic solutions is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).} %\textcolor{RoyalBlue}{At the formal level, irregular singular ODEs already have distinctive behaviour: they admit divergent formal series solutions in the form of trans-monomials.
-In particular, the trans-monomial characterizes the different asymptotic behvaiours of the underlying analytic solution---whose existence is guaranteed by the Main Asymptotic Existence Theorem (M.A.E.T.).
-Then, the so called Stokes phenomenon, which is also a distinguished aspect of irregular singular ODEs, measures the ``jumps" of these analytic solutions with different asymptotics, after they are analytically continued.}
-\color{Maroon}
-Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
-Formally, this behavior is captured in a {\em formal integral} solution: an expression
-\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
-in which $A$ is a finite set of complex numbers, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
-For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
-
-Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.
-The full definition of a trans-series is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
-The trans-monomials in the spaces $e^{-\alpha z} z^\sigma\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider.
-\color{black}
-
-The formal integral solutions and the M.A.E.T.
-have inspired several other solution methods for linear level~1 ODEs.
+
+The Poincar\'{e} solutions and the M.A.E.T.
+have inspired several other methods for solving linear level~1 ODEs.
 The ones we will discuss in this section are summarized in the following table.
@@
 
-\subsubsection{Poincar\'e method and Borel--Laplace summation}\label{sec:Poincare method}
-For a level $1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+\subsubsection{The Poincar\'e method and Borel summation}\label{sec:Poincare method}
+\textcolor{orange}{[read and revise?]} For a level $1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
 For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\series{\Phi}_\alpha$ of the form
@@
 \end{equation}
-with $P(-\alpha) = 0$ and $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$. We will refer to $\Phi_\alpha$ as Poincar\'{e}'s formal solutions.
+with $P(-\alpha) = 0$ and $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$. We will refer to $\series{\Phi}_\alpha$ as Poincar\'{e}'s formal solutions.
 
@@
 guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
-In particular, the Ramis Index Theorem shows that the formal solutions $\Phi_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
+In particular, the Ramis Index Theorem shows that the formal solutions $\series{\Phi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
 This motivated the desire to promote formal solutions to analytic ones through the development of summability methods, even beyond the study of level-$1$ ODEs~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
@@
 \textcolor{orange}{[Revise\ldots]} \textcolor{RoyalBlue}{Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.}
-\subsubsection{\'Ecalle's resurgence theory}
-The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
+\subsubsection{\'{E}calle's theory of resurgence}
+\textcolor{orange}{[read and revise?]} The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
 
@@
 \subsubsection{Laplace transform methods and fixed point iteration}
-So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
+\textcolor{DarkBlue}{All of the historical approaches we have discussed so far start by looking for formal solutions.
+In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms.
+By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones.
+These solutions will turn out to be Borel regular.}
+\par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
 In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
@@
 This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
-it is a Borel regular solution.
-As for \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
-Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.
-%In addition, as we will show in Section~\ref{sec:new-summability-proof}.
-
-A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
-However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.
+it is a Borel regular solution.} \textcolor{DarkBlue}{We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain.
+This runs parallel to \'{E}calle's use of the Borel transform.
+Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.} \textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
+Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.} %In addition, as we will show in Section~\ref{sec:new-summability-proof}.
+
+\textcolor{DarkBlue}{The function spaces mentioned in Section~\ref{sec:laplace_analytic} play an important role in our approach.
+They also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.} \textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
+However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.}
 %
@@
 \subsubsection{Thimble integral in geometry}
-
+\textcolor{orange}{[move $N$-dim'l thimbles here]}
 \subsubsection{Asymptotic of thimble integrals}

### 2024-04-10 exp-resurgence.tex
Revise the history of the Poincaré method
Also, start revising the history of resurgence.

@@
 Formally, this behavior is captured in a {\em formal integral} solution: an expression
-\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{\varphi}_\alpha \]
-in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+\[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
+in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
 For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
@@
 Each term of a formal integral is an example of a {\em trans-monomial}---the basic building block of a {\em trans-series}.\footnote{For the full definition of a trans-series, see~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.} The trans-monomials in the spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$ are the only ones we will need to consider in this paper.
-Poincar\'{e}'s method for solving linear level-$1$ ODEs, discussed in Section~\ref{sec:Poincare method}, produces trans-monomial solutions in these spaces.
+Poincar\'{e}'s method for solving linear level~$1$ ODEs, discussed in Section~\ref{sec:Poincare method}, produces trans-monomial solutions in these spaces.
 The Poincar\'{e} solutions serve as the terms of a general formal integral.
@@
 \subsubsection{The Poincar\'e method and Borel summation}\label{sec:Poincare method}
-\textcolor{orange}{[read and revise?]} For a level $1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+\color{DarkBlue}
+An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
+These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
+Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve.
+The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} \colon P(-\alpha) = 0\}$.
+Poincar\'{e} guesses that each approximate solution $e^{-\alpha z}$ can be turned into an exact solution $e^{-\alpha z} \series{F}_\alpha$ using a formal correction factor $\series{F}_\alpha \in z^{-\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
+When $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$, the correction factor can be found order by order, starting from any chosen constant term.
+We will refer to the resulting solutions $e^{-\alpha z} \series{F}_\alpha \in e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ as Poincar\'{e}'s formal solutions.
+
+Although it is not contructive, the M.A.E.T.
+guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
+Furthermore, the Ramis Index Theorem tells us that the Borel transform sends Poincar\'{e}'s formal solutions to convergent series on the position domain---the first step toward proving Borel summability~\cite{ramis_index}.
+This has motivated the development of summability methods, which promote formal solutions to analytic ones~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+These methods can be applied both within and beyond the world of linear level~1 ODEs.
+\color{RoyalBlue}\par
+For a level~$1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
 For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\series{\Phi}_\alpha$ of the form
@@
 This motivated the desire to promote formal solutions to analytic ones through the development of summability methods, even beyond the study of level-$1$ ODEs~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
+\color{black}
 % \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
@@
 \subsubsection{\'{E}calle's theory of resurgence}
-\textcolor{orange}{[read and revise?]} The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
+\'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
+In a nutshell, resurgence provides information about the analytic continuation of the Borel transform of a divergent series.
+In particular, it reveals the locations of singularities in the position domain, and it quantifies the Stokes phenomenon in terms of ``Stokes constants'' describing analytic continuation around the singularities.
+
+A series is resurgent if its Borel transform converges to an endlessly analytically continuable function on the position domain.
+Thus, resurgence creates a bridge between formal and analytic solutions of problems in the position domain.
+\textcolor{orange}{[\ldots]}
+\color{RoyalBlue}\par
+The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
 
@@
 This is an advantage of resurgence techniques compared to the usual Borel summation method.
-
+\color{black}
 % Then, the Stokes phenomenon is another distiguishd feature of irregular singular ODEs, an it is closely related to the fact that formal solutions are divergent. 

### 2024-04-10 exp-resurgence.tex
Put Bessel 0 in "to do"

@@
 
-For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
+\textcolor{orange}{[move to historical]} For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
 Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
@@
 In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
-\subsection{Borel regularity for level~$1$ ODEs}\label{sec:history_ODE}
+\subsection{Solving level~$1$ ODEs}\label{sec:history_ODE}
 %
@@
 \subsubsection{\'{E}calle's theory of resurgence}
+\color{DarkBlue}
 \'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
@@
 \end{center}
-Let $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
+Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
+
+We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough.
 \begin{todo}\par
@@
 Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
+For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
 \end{prop}
@@
 \[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
-In terms of the metric on $\dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
+In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
 \[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
@@
 Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
-\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
+\[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
 has a continuous left inverse
-\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
 with a norm of at most
@@
 \[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz. \]
-When $\Phi$ is in $\dualsingexp{-\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound
+When $\Phi$ is in $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound
 \begin{align*}
@@
 \end{proof}
-\textcolor{magenta}{[Introduce $\widehat{\Omega}^\bullet$]}
-\color{black}
 %
@@
 
-In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism. 
+\textcolor{DarkBlue}{On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.}
+\par\textcolor{RoyalBlue}{In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.}
+\textcolor{magenta}{[actually need $\Omega_0$ in lemma]}
 \begin{lemma}
-    Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
+If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \textcolor{magenta}{[no; revise]} under the convolution product $\ast_{\zeta, \alpha}$.
+\textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
 \end{lemma}
+\begin{proof}
+Suppose $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. The convolution integral
+\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,|d\zeta| \]
+can then always be evaluated along the path $\zeta = (1-t)\,\alpha + t\,\zeta(a)$ parameterized by $t \in (0, 1)$.
+
+For any $\phi, \psi \in \singexp{\sigma}{\Lambda}(\Omega_\alpha)$, we have
+\begin{align*}
+\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & = \left| \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta \right| \\
+& \le \int_{\zeta = \alpha}^a |\psi|\,|\mathsf{R}^*\phi|\,|d\zeta| \\
+& \le \int_{\zeta = \alpha}^a \Big( |\zeta - \alpha|^\sigma e^{\Lambda|\zeta - \alpha|}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( |\zeta(a) - \zeta|^\sigma e^{\Lambda|\zeta(a) - \zeta|}\,\|\phi\|_{\sigma, \Lambda} \Big)\,|d\zeta|.
+\end{align*}
+Using the shorthand $\delta \defeq |\zeta(a) - \alpha|$, we compute
+\begin{align*}
+\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & \le \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,dt \\
+& = \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,d\zeta
+\end{align*}
+\end{proof}
 \begin{verify}
@@
         &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
+        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')|-\zeta+\zeta+\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta+\zeta'|}\, d\zeta'\\
+        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')(|\zeta|+|-\zeta+\zeta'|)^{\sigma}e^{\Lambda(|\zeta|+|-\zeta+\zeta'|)}\, d\zeta'\\
         &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
@@
 \begin{corollary}
-    Let $\sigma>-1$ and $\Lambda>0$, the Laplace transform 
-    \[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\Omega_\alpha)\to\dualsingexp{\sigma}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
+For any $\sigma > -1$ and $\Lambda > 0$, the Laplace transform 
+\[ \laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\Omega_\alpha) \to \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
 is a $\C$-algebra isomomorphism, with inverse defined in Proposition~\ref{prop:inverse_laplace_analytic}. 
@@
 
-Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}{\Lambda}(\widehat{\Omega}_0^\Lambda)$.
+Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$.
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
-\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \]
+\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\Lambda) \]
 for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
@@
 for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
+Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
 \[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
@@
 % \color{black}
+\begin{todo}
 \subsubsection{The modified Bessel function with parameter $0$}
@@
 \[ K_0(z) \defeq K_0^{(1)}(z) - K_0^{(0)}(z). \]
-In this difference, the parts of $\mathcal{C}_1^\theta$ and $\mathcal{C}_0^\theta$ in the left half-plane cancel out, leaving the integral
+In this difference, the parts of $\mathcal{C}_1^\theta$ and $\mathcal{C}_0^\theta$ in the left half-plane cancel out \textcolor{orange}{[$\theta$ is small]}, leaving the integral
 \[ K_0(z) = \frac{1}{2\pi i} \int_\mathscr{c} \exp\left[z \cosh(t)\right]\,t\,dt \]
@@
 \item Leftward along $(0, \infty) + (-\pi + \theta)i$.
-\item Upward along $(-\pi, \pi)i$.
+\item Upward along $(-\pi + \theta, \pi + \theta)i$.
 \item Rightward along $(0, \infty) + (\pi + \theta)i$.
@@
 \end{equation}
-We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution.
+We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
 \begin{verify}
@@
 & = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
-& = \color{DarkViolet} -\frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+& = \color{DarkViolet} -\frac{3}{2} \int_{\mathcal{J}^{\theta+\pi}_{\zeta, 1}} e^{z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
 %%& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
@@
 \end{align*}
+$\int_{-1}^{e^{i\theta}\infty} = \int_{-1}^{e^{-i\theta}\infty}+2 \int_{1}^{\infty}$
 
@@
 we finally get 
-\[\int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
+\[\int_{\mathcal{J}^0_{\zeta, 1}} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
 \end{verify}
 %
+\end{todo}
 \subsection{Generalized Airy}

### 2024-04-10 exp-resurgence.tex
Revert integral symmetry calculation to 870add4
Go back to state at "Finish third-degree thimble integral".

@@
 %
-\color{DarkBlue}
 We will look at the effectiveness of Borel summation from an analytic perspective, as a regularity property of problems and their holomorphic solutions.
@@
 If the asymptotic expansion $\series{\Phi} = \ae^\theta \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
-\color{black}
-\par\textcolor{RoyalBlue}{Taking its asymptotic expansion along the half-plane $\Re(e^{i\theta}z) > 0$, we get a formal power series $\series{\Phi}$.}
 \begin{center}
@@
 
-\textcolor{orange}{[move to historical]} For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
+\textcolor{PaleVioletRed}{[move to historical] For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
 Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
@@
 Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$.
-When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.
-
-\textcolor{orange}{[\ldots]}
+When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.}
 %%
@@
 
-\color{RoyalBlue}
+We are now ready to define a one-dimensional thimble integral precisely, and at our desired level of generality.
+\begin{definition}
+Fix a one-dimensional complex manifold $X$; a translation surface $B$; and a holomorphic map $f \maps X \to B$ with isolated, non-degenerate critical points.
+A one-dimensional {\em thimble integral} has the form
+\[ I = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu, \]
+where $\nu$ is a holomorphic $1$-form on $X$, $a$ is a critical point of $f$, and $\mathcal{C}^\theta_a$ is the Lefschetz thimble that runs through $a$ in direction $\theta$ with a chosen orientation.
+\end{definition}
+\color{RoyalBlue}\par
 Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
@@
 \subsubsection{The Poincar\'e method and Borel summation}\label{sec:Poincare method}
-\color{DarkBlue}
 An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
@@
 These methods can be applied both within and beyond the world of linear level~1 ODEs.
-\color{RoyalBlue}\par
-For a level~$1$ ODE of the kind we will study, these formal solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-For instance, for an ODE like the one in Section~\ref{borel-reg:explanatory-power}, a frame of formal solutions are given by trans-monomial $\series{\Phi}_\alpha$ of the form
-\begin{equation}
-\series{\Phi}_\alpha=e^{\alpha z} z^{-\tau_\alpha} \sum_{n=0}^\infty a_n z^{-n}
-\end{equation}
-with $P(-\alpha) = 0$ and $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$. We will refer to $\series{\Phi}_\alpha$ as Poincar\'{e}'s formal solutions.
-
-Then, although it is not contructive, the M.A.E.T.
-guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
-In particular, the Ramis Index Theorem shows that the formal solutions $\series{\Phi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
-This motivated the desire to promote formal solutions to analytic ones through the development of summability methods, even beyond the study of level-$1$ ODEs~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-\color{black}
+
 % \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
@@
 \subsubsection{Laplace transform methods and fixed point iteration}
-\textcolor{DarkBlue}{All of the historical approaches we have discussed so far start by looking for formal solutions.
+All of the historical approaches we have discussed so far start by looking for formal solutions.
 In this paper, we will focus on a different kind of approach, where we start by looking for analytic solutions expressed as Laplace transforms.
 By carefully choosing the starting point of the Laplace transform, we get analytic solutions which are asymptotic to Poincar\'{e}'s formal ones.
-These solutions will turn out to be Borel regular.}
-\par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
+These solutions will turn out to be Borel regular.
+% \par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
 In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
@@
 This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
-it is a Borel regular solution.} \textcolor{DarkBlue}{We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain.
+it is a Borel regular solution.}
+We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain.
 This runs parallel to \'{E}calle's use of the Borel transform.
-Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.} \textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
+Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.%\textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
 Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.} %In addition, as we will show in Section~\ref{sec:new-summability-proof}.
 
-\textcolor{DarkBlue}{The function spaces mentioned in Section~\ref{sec:laplace_analytic} play an important role in our approach.
+The function spaces mentioned in Section~\ref{sec:laplace_analytic} play an important role in our approach.
 They also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
-This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.} \textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
+This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
+%\textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
 However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.}
@@
 
-The Poincar\'{e} algorithm, as discussed in Sections \ref{sec:asympt-AL} and \ref{sec:new-summability-proof}, picks out a frame in the \textcolor{magenta}{space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]} of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \textcolor{magenta}{space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]} of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
@@
 $\displaystyle \mathsf{T}_{(1/3)\,a_2/a_3}^*$ & $\displaystyle u^3 + pu + q$ & $\displaystyle \hphantom{e^{qz}} I\left(\frac{z}{a_3}\right)$ \\[5mm]
-$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle \textcolor{DarkViolet}{e^{qz}\,I\left(\frac{z}{a_3}\right)}$ \\[5mm]
+$\displaystyle f \mapsto f - q$ & $\displaystyle u^3 + pu$ & $\displaystyle e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
 \end{tabular}
@@
 \textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-a$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
 $\displaystyle f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & $\displaystyle 4u^3 - 3u$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right)$ \\[5mm]
@@
 \end{center}
-We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel-rational-AL}:
-\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{zq}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
+\color{orange}Replace $\textcolor{DarkViolet}{e^{qz}}$ with $e^{q \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} z}$\color{black}
+
+We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel-rational-AL}:\textcolor{red}{[check the sign in (29), it seems positive $e^{zT_3(u)}$]}
+\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
+\color{orange}
+\begin{equation}
+    K_{1/3}(-z) = -\frac{3}{2}\,p^{-1/2} e^{zq \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2}}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right).
+\end{equation}
+\color{black}
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
@@
 \end{verify}
+\color{orange}
+Let us rewrite for simpicilty $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
+\begin{align*}
+    0&=I''+\frac{\beta^2-1}{\gamma^2}I+\frac{2\beta}{\gamma}I'+\frac{1}{z}\left(\frac{\beta}{\gamma^2}I+\frac{I'}{\gamma}\right)-\frac{1}{9\gamma^2}\frac{1}{z^2} I
+\end{align*}
+\color{black}
 \item[] \textbf{One degenerate critical point}
@@
 \[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
-\textcolor{DarkViolet}{\[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-a_3 qz\right] K_{1/3}\left(2i \left(\frac{p}{3}\right)^{3/2} z\right). \]}
 Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.

### 2024-04-11 exp-resurgence.tex
Correct degenerate case of cubic integral
It now agrees with the coalescence limit.

@@
 To illustrate, we turn $g$ into the Chebyshev polynomial $T_3$ by scaling and rotating its critical points to $\pm\tfrac{1}{2}$ and its critical values to $\pm 1$.
+Setting
+\[ r \defeq \frac{i}{2} \left(\frac{3}{p}\right)^{3/2}, \]
+we get
 \begin{center}
@@
 \textbf{Symmetry} & \textbf{Resulting polynomial} & \textbf{Resulting integral} \\[2mm]
-$\displaystyle \mathsf{M}_{(i/2)(3/p)^{1/2}}^*$ & $\displaystyle 2i\left(\frac{p}{3}\right)^{3/2} \left(4u^3 - 3u\right)$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
-$\displaystyle f \mapsto \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} f$ & $\displaystyle 4u^3 - 3u$ & $\displaystyle \frac{i}{2}\left(\frac{3}{p}\right)^{1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle \mathsf{M}_{rp/3}^*$ & $\displaystyle r^{-1} \left(-4u^3 + 3u\right)$ & $\displaystyle \frac{rp}{3}\,e^{qz}\,I\left(\frac{z}{a_3}\right)$ \\[5mm]
+$\displaystyle f \mapsto rf$ & $\displaystyle -4u^3 + 3u$ & $\displaystyle \frac{rp}{3}\,e^{qrz}\,I\left(\frac{rz}{a_3}\right)$ \\[5mm]
 \end{tabular}
 \end{center}
-\color{orange}Replace $\textcolor{DarkViolet}{e^{qz}}$ with $e^{q \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} z}$\color{black}
-
-We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel-rational-AL}:\textcolor{red}{[check the sign in (29), it seems positive $e^{zT_3(u)}$]}
-\[ K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{qz}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right). \]
-\color{orange}
+
+We can now relate the general third-degree thimble integral $I$ to the modified Bessel function $K_{1/3}$, defined in equation~\eqref{integral:mod-bessel-rational-AL}:
 \begin{equation}
-    K_{1/3}(-z) = -\frac{3}{2}\,p^{-1/2} e^{zq \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2}}\,I\left(\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right).
-\end{equation}
+K_{1/3}(z) = \frac{irp}{\sqrt{3}}\,e^{qrz}\,I\left(\frac{rz}{a_3}\right)
+\end{equation}
+\begin{verify}
+\begin{equation}
+K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{-zq \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2}}\,I\left(-\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right).
+\end{equation}
+\end{verify}
 \color{black}
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
-\[\left[\left(\frac{\partial}{\partial z}\right)^2 + 2\left(\frac{q}{a_3}\right)\frac{\partial}{\partial z} + \frac{1}{a_3^2} \left(\frac{4p^3}{27} + q^2\right) + \frac{1}{z} \left(\frac{\partial}{\partial z} + \frac{q}{a_3}\right) - \frac{1}{9z^2}\right] \Phi = 0.\]
+\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + 2a_3 q\,\tfrac{\partial}{\partial z} + a_3^2 (q^2 - r^{-2})\big] + z^{-1} \big(a_3 q + \tfrac{\partial}{\partial z}\big) - \tfrac{1}{9} z^{-2} \right] \Phi = 0 \]
 \begin{verify}
-\[\left[a_3^2 \left(\frac{\partial}{\partial z}\right)^2 + 2a_3 q \frac{\partial}{\partial z} + \left(\frac{4p^3}{27} + q^2\right) + \frac{a_3}{z} \left(a_3\frac{\partial}{\partial z} + q\right) - \frac{a_3^2}{9z^2}\right] \Phi = 0.\]
+With
+\begin{align*}
+w & = \frac{r}{a_3}\,z &
+\frac{\partial}{\partial w} & = \frac{a_3}{r} \frac{\partial}{\partial z}
+\end{align*}
+we have
+\[ K_{1/3}(z) = \frac{irp}{\sqrt{3}}\,e^{a_3 qw}\,I(w) \]
+
+Let us rewrite for simpicilty $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
+\begin{align*}
+0 &= I''(\gamma z)+\frac{\beta^2-1}{\gamma^2}I(\gamma z)+\frac{2\beta}{\gamma}I'(\gamma z)+\frac{1}{z}\left(\frac{\beta}{\gamma^2}I(\gamma z)+\frac{I'(\gamma z)}{\gamma}\right)-\frac{1}{9\gamma^2}\frac{1}{z^2} I(\gamma z) \\
+0 &= I''(t)+\frac{\beta^2-1}{\gamma^2}I(t)+\frac{2\beta}{\gamma}I'(t)+\frac{1}{t}\left(\frac{\beta}{\gamma}I(t)+I'(t)\right)-\frac{1}{9t^2} I(t)\\
+0 &= I''(t)+\frac{\beta^2}{\gamma^2}I(t)-\frac{1}{\gamma^2}I(t)+\frac{2\beta}{\gamma}I'(t)+\frac{1}{t}\frac{\beta}{\gamma}I(t)+\frac{1}{t}I'(t)-\frac{1}{9t^2} I(t)\\
+0 &= I''(t)+a_3^2q^2 I(t)-\frac{a_3^2}{r^2}I(t)+2a_3 qI'(t)+\frac{a_3 q}{t}I(t)+\frac{1}{t}I'(t)-\frac{1}{9t^2} I(t)
+\end{align*}
+
+Here's a double-check. Since $K_{1/3}(z)$ satisfies the modified Bessel equation~\eqref{eqn:mod-bessel},
+\begin{align*}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K_{1/3}(z) & = 0 \\
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \frac{irp}{\sqrt{3}}\,e^{a_3 qw}\,I(w) & = 0 \\
+\left[\big(\tfrac{a_3}{r} w\big)^2 \big(\tfrac{r}{a_3} \tfrac{\partial}{\partial w}\big)^2 + \big(\tfrac{a_3}{r} w\big) \tfrac{r}{a_3} \tfrac{\partial}{\partial w} - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r} w\big)^2\big]\right] e^{a_3 qw}\,I(w) & = 0 \\
+\left[w^2\big(\tfrac{\partial}{\partial w}\big)^2 + w \tfrac{\partial}{\partial w} - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] e^{a_3 qw}\,I(w) & = 0 \\
+e^{a_3 qw} \left[w^2 \big(\tfrac{\partial}{\partial w} + a_3 q\big)^2 + w \big(\tfrac{\partial}{\partial w} + a_3 q\big) - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] I(w) & = 0 \\
+\left[w^2 \big[\big(\tfrac{\partial}{\partial w}\big)^2 + 2a_3 q \tfrac{\partial}{\partial w} + (a_3 q)^2\big] + w \big(\tfrac{\partial}{\partial w} + a_3 q\big) - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] I(w) & = 0
+\end{align*}
 \end{verify}
-\color{orange}
-Let us rewrite for simpicilty $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
-\begin{align*}
-    0&=I''+\frac{\beta^2-1}{\gamma^2}I+\frac{2\beta}{\gamma}I'+\frac{1}{z}\left(\frac{\beta}{\gamma^2}I+\frac{I'}{\gamma}\right)-\frac{1}{9\gamma^2}\frac{1}{z^2} I
-\end{align*}
-\color{black}
+\begin{verify}
+Taking $p$ and $q$ to $0$ in
+\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + 2a_3 q\,\tfrac{\partial}{\partial z} + a_3^2 (q^2 - r^{-2})\big] + z^{-1} \big(a_3 q + \tfrac{\partial}{\partial z}\big) - \tfrac{1}{9} z^{-2} \right] \Phi = 0, \]
+we get
+\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + z^{-1} \tfrac{\partial}{\partial z} - \tfrac{1}{9} z^{-2} \right] \Phi = 0\]
+\end{verify}
 \item[] \textbf{One degenerate critical point}
@@
 We can confirm this result, and find the correct normalization, using the thimble projection formula:
+\color{RoyalBlue}
 \begin{align*}
@@
 \end{align*}
-The factor of $e^{i\pi/3}$ \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta^{-2/3}$ around $\zeta = 0$.
+\color{DarkBlue}
+\begin{align*}
+\int_{\mathcal{C}} e^{-zu^3}\,du & = (1 - e^{i\pi/3}) \int_{\mathcal{J}_{\zeta, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta^{-2/3}\,d\zeta \\
+& = \tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
+\end{align*}
+\color{black}
+The factor of \textcolor{DarkBlue}{$e^{i\pi/3} - 1$} \textcolor{RoyalBlue}{$e^{i\pi/3}$} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta^{-2/3}$ around $\zeta = 0$.
 
@@
 Rearranging the relationship above between $I(z)$ and the modified Bessel function $K_{1/3}(z)$, we get the formula
+\color{DarkBlue}
+\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qrz} K_{1/3}\left(\frac{a_3 z}{r}\right) \]
+\color{RoyalBlue}
 \[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
-Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
-\begin{todo}\par
-[Our treatments of the $e^{qz}$ factor disagree. With this version, the exponential factor goes to $1$ as $p \to 0$, which I think is consistent with the limit to the degenerate case. Comparison:]
-\begin{align*}
-    e^{-zq} I_+\left(-\tfrac{i 3^{3/2}}{2 p^{3/2}} z\right)&= \int_{\mathcal{C}_+} e^{z (4t^3-3t)} du\\
-    &= 2\sqrt{-\tfrac{p}{3}} \int_{\mathcal{C}_+} e^{z (4t^3-3t)} dt \\
-    &= 2\sqrt{-\tfrac{p}{3}} K_{1/3}(z). 
-\end{align*}
-\end{todo}
+\color{black}
+Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
 \begin{verify}
 \begin{align*}
+I(z) & = \frac{\sqrt{3}}{irp} e^{-qrz} K_{1/3}\left(\frac{a_3 z}{r}\right) \\
+& = \frac{\sqrt{3}}{irp} e^{-qrz} \frac{\pi}{2 \sin(\pi/3)} \left[ I_{-1/3}\left(\frac{a_3 z}{r}\right) - I_{1/3}\left(\frac{a_3 z}{r} \right)\right].
+\end{align*}
+We take the lowest-order term, which is the leading term of $I_{-1/3}(a_3 z / r)$:
+\begin{align*}
+I(z) & \approx \frac{\sqrt{3}}{irp} \frac{\pi}{2 \sin(\pi/3)} \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(-\tfrac{1}{3} + 1\big)} \\
+& = \frac{\sqrt{3}}{irp}\;\frac{1}{2}\;\Gamma\big(\tfrac{1}{3}\big)\,\Gamma\big(\tfrac{2}{3}\big) \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
+& = \frac{\sqrt{3}}{irp}\;\frac{1}{2}\;\Gamma\big(\tfrac{1}{3}\big)\,\Gamma\big(\tfrac{2}{3}\big) \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
+& = \frac{\sqrt{3}}{i a_3^{1/3} (2r)^{2/3} p} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3} \\
+& = \frac{\sqrt{3}}{i a_3^{1/3} (2r)^{2/3} p} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3}.
+\end{align*}
+Observing that $(2r)^{2/3} = e^{i(2/3)\pi }\,3/p$, we get
+\begin{align*}
+I(z) & \approx \frac{\sqrt{3}}{i a_3^{1/3}\,3e^{i(2/3)\pi}} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3} \\
+& = \frac{1}{i\sqrt{3}} a_3^{-1/3} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3}
+\end{align*}
+\textcolor{RoyalBlue}{\begin{align*}
 i\sqrt{3}\,I(z) & = 2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big) \\
@@
 & = e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}
-\end{align*}
+\end{align*}}
 \end{verify}

### 2024-04-11 exp-resurgence.tex
Correct the Bessel 0 example

@@
 % \color{black}
-\begin{todo}
 \subsubsection{The modified Bessel function with parameter $0$}
+\color{DarkBlue}
+When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
+\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_{\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt. \]
+Let us compute $K^{(1)}_{0}(z)$ using the contour $\mathcal{C}_1^0$, which runs rightward along the line $\Im(t) = \pi$.
+In the translated coordinate $w$ defined by $t = w + i\pi$, the integral becomes
+\begin{align*}
+K_0^{(1)}(z) & = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[z \cosh(w + i\pi)\right]\,(w + i\pi)\,dw \\
+& = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,w\,dw + \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,i\pi\,dw.
+\end{align*}
+The first integrand is odd with respect to $w = 0$, so it vanishes, leaving
+\begin{align}
+K_0^{(1)}(z) & = \frac{1}{2} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,dw \notag \\
+& = \int_0^\infty \exp\left[-z \cosh(w)\right]\,dw. \label{int:k0_cosh}
+\end{align}
+This is a special case of formula~10.32.9 from \cite{dlmf}. Rolling the $t$ plane up into a cylinder, parameterized by the coordinate $s = e^t$, we can express $K_0^{(1)}(z)$ as an exponential period:
+\[ K_0^{(1)}(z) = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}. \]
+
+To confirm that the calculation above is consistent with Section~\ref{countable-cover}, recall formula~\eqref{eq: K_j_mu at 1}:
+\[ K_0^{(1)}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta.
+\]
+The hypergeometric function in the integrand can be expressed algebraically using identity~15.4.13 from \cite{dlmf}.
+This leads to an expression for the integrand that makes its $\zeta_{\pm 1}^{1/2}$ singularities even more apparent:
+\begin{equation}\label{eqn:borel_bessel0}
+K_0^{(1)}(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
+\end{equation}
+We could get the same result from formula~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
+
+\color{RoyalBlue}
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 & = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \notag \\
-& = \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,dt \label{int:k0_cosh} \\
+& = \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,dt \label{int:k0_cosh_old} \\
 & = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}, \notag
@@
 \par
-For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives
+For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives \textcolor{GreenYellow}{(we were missing a factor of two in identity~15.4.13, so the highlighted factors of $1/2$ should be removed)}
 \begin{align*}
 K^{(j)}_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
-& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} \\
-& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-& = -\frac{1}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
-& = -\frac{2}{4} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
-\end{align*}
+& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} \\
+& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
+& = -\frac{1}{2} \textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
+& = -\textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+\end{align*}
+This is off by a sign from what we expect, but the sign could be accounted for by the branch cuts in the square roots.
 For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
@@
 K^{(j)}_0(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} (1 + \eta^2)^{-1/2} d\zeta \\
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \frac{1}{2} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-& = \color{DarkViolet}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
-& =  \color{DarkViolet} \frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
-& = \color{DarkViolet} \frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
-& = \color{DarkViolet} -\frac{3}{2} \int_{\mathcal{J}^{\theta+\pi}_{\zeta, 1}} e^{z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} d\zeta \\
+& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
+& = \color{DarkViolet}\textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
+& =  \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
+& = \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
+& = \color{DarkViolet} -\textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^{\theta+\pi}_{\zeta, 1}} e^{z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
 %%& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
@@
 \end{verify}
-%
-\end{todo}
+\color{black}
+%
 \subsection{Generalized Airy}

### 2024-04-13 exp-resurgence.tex
Sketch revised goals and results

@@
 %
-\textcolor{orange}{[Revise\ldots]} First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
+We present the results, proofs, and examples in this paper with a few central goals in mind.
+The first is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory.
+\textcolor{orange}{[\ldots]}
+
+Our second goal is to highlight how the problems we study become more regular when posed in the position domain (the Borel plane).
+When we take level~$1$ differential equations from the frequency domain to the position domain, we not only turn their irregular singularities into regular ones, but also turn them into integral equations, which provide more smoothness and can be solved more constructively.
+\textcolor{orange}{[Thimble integrals\ldots]}
+
+\textcolor{orange}{[Plentiful, novel examples.]}
+\color{RoyalBlue}\par
+First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
 For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
@@
 The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
+\color{black}
 \subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
@@
 When {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
-
-\textcolor{PaleVioletRed}{[move to historical] For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
-Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
-Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
-\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
-Each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
-There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$.
-Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$.
-When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.}
 %%
@@
 \subsubsection{Thimble integral in geometry}
+Thimble integrals can be used to explore the geometry of complex manifolds, and even to define a homology theory. To see how this works, it will be helpful to
+
+\textcolor{PaleVioletRed}{[move to historical] For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
+Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
+Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
+\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
+Each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
+There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$.
+Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$.
+When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.}
+
+\color{BlueViolet}
+\begin{itemize}
+\item Give definition in $N$ dimensions.
+\item Explain how can be seen in terms of homology (cite Pham).
+\end{itemize}
+\color{black}
+%
 \textcolor{orange}{[move $N$-dim'l thimbles here]}
-\subsubsection{Asymptotic of thimble integrals}
+%
+\subsubsection{Asymptotics of thimble integrals}
+%
 Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
@@
 \end{align*}
+\textcolor{orange}{[\ldots]}
 \end{proof}
@@
 \subsubsection{The modified Bessel function with parameter $0$}
-\color{DarkBlue}
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 \end{verify}
-\color{black}
+From this identity, you can deduce that $I(z)$ satisfies a second-order differential equation, analogous to the modified Bessel equation~\eqref{eqn:mod-bessel}.
+\begin{todo}\par
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
@@
 \end{verify}
+\end{todo}
 \item[] \textbf{One degenerate critical point}
@@
 \begin{equation}\label{eqn:degree-3-poly-1root}
-\left[\frac{\partial}{\partial z} + \frac{1}{3z}\right] \Phi = 0.
+\left[\frac{\partial}{\partial z} + \frac{1}{3z} +q \right] \Phi = 0.
 \end{equation}
 A function $\laplace_{\zeta,\alpha}^{\theta} v$ satisfies this equation if and only if $v$ satisfies the integral equation
-\[ \left[ -\zeta + \tfrac{1}{3} \partial^{-1}_{\zeta, \alpha} \right] v = 0. \]
-When $\alpha = 0$, this equation has the solution
-\[ v_0 = \zeta^{-2/3}, \]
+\[ \left[ -\zeta + \tfrac{1}{3} \partial^{-1}_{\zeta, \alpha} +q  \right] v = 0. \]
+When $\alpha = q$, this equation has the solution
+\[ v_q = \zeta_q^{-2/3}, \]
 whose Laplace transform
-\[ V_0 = \Gamma\big(\tfrac{1}{3})\,z^{-1/3} \]
+\[ V_q = e^{-zq} \Gamma\big(\tfrac{1}{3})\,z^{-1/3} \]
 must be proportional to $I(z)$.
@@
 \begin{align*}
-\int_{\mathcal{C}} e^{-zu^3}\,du & = (1 - e^{i\pi/3}) \int_{\mathcal{J}_{\zeta, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta^{-2/3}\,d\zeta \\
-& = \tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
+\int_{\mathcal{C}} e^{-z(u^3+q)}\,du & = (1 - e^{i\pi/3}) \int_{\mathcal{J}_{\zeta_q, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta_q^{-2/3}\,d\zeta_q \\
+& = e^{-zq}\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
 \end{align*}
 \color{black}
-The factor of \textcolor{DarkBlue}{$e^{i\pi/3} - 1$} \textcolor{RoyalBlue}{$e^{i\pi/3}$} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta^{-2/3}$ around $\zeta = 0$.
+The factor of \textcolor{DarkBlue}{$e^{i\pi/3} - 1$} \textcolor{RoyalBlue}{$e^{i\pi/3}$} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
 
@@
 Rearranging the relationship above between $I(z)$ and the modified Bessel function $K_{1/3}(z)$, we get the formula
-\color{DarkBlue}
-\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qrz} K_{1/3}\left(\frac{a_3 z}{r}\right) \]
-\color{RoyalBlue}
-\[ I(z) = -\frac{2}{3}\,p^{1/2} \exp\left[-2ia_3 \left(\frac{p}{3}\right)^{3/2} qz\right] K_{1/3}\left(2ia_3 \left(\frac{p}{3}\right)^{3/2} z\right). \]
-\color{black}
-Using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $q$ and $a_3$ held constant.
+\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qa_3z} K_{1/3}\left(\frac{a_3 z}{r}\right) \]
+Setting $q=0$, and using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $a_3$ held constant.
 \begin{verify}

### 2024-04-15 exp-resurgence.tex
Finish history of Écalle's theory of resurgence
Except for Kontsevich–Soibelman approach, which might deserve its own section.

@@
 %
+\color{DarkBlue}
 We present the results, proofs, and examples in this paper with a few central goals in mind.
-The first is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory.
-\textcolor{orange}{[\ldots]}
-
-Our second goal is to highlight how the problems we study become more regular when posed in the position domain (the Borel plane).
+Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory.
+In particular, we highlight results---like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals---that can be proven in purely analytic ways.
+
+Our second goal is to emphasize how the problems we study become more regular when posed in the position domain (the Borel plane).
 When we take level~$1$ differential equations from the frequency domain to the position domain, we not only turn their irregular singularities into regular ones, but also turn them into integral equations, which provide more smoothness and can be solved more constructively.
-\textcolor{orange}{[Thimble integrals\ldots]}
+When we write thimble integrals as Laplace transforms, their irregularly shaped integration contours collapse to rays in the position domain.
 
@@
 
-We are now ready to define a one-dimensional thimble integral precisely, and at our desired level of generality.
+We are now ready to define a one-dimensional thimble integral precisely, at our desired level of generality.
 \begin{definition}
@@
 \subsection{Organization of the paper}
-The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
+\textcolor{orange}{[Revise\ldots]} The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
 This could help the reader to contextualize our results in the literature.
@@
 Thus, resurgence creates a bridge between formal and analytic solutions of problems in the position domain.
-\textcolor{orange}{[\ldots]}
+
+The formal solutions of a level~$1$ ODE are always resurgent series~\cite[Proposition~2.2.1]{EcalleIII}.
+\'{E}calle proved this by using formal perturbation theory to solve a corresponding integral equation in the position domain.
+Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the pertrubation series would converge to an endlessly analytically continuable function.
+Loday-Richaud and Remy went on to show that this function always has a well-defined Laplace transform, so the corresponding formal solution in the frequency domain is Borel summable~\cite{loday-Remy2011}.
+Malgrange got similar results by working with differential equations, rather than integral equations, on the position domain~\cite{malgrange--fourier}.
+
+%%One can see this by using formal perturbation theory to solve a corresponding equation on the position domain---either an integral equation, as in the work of Loday-Richaud and Remy~\cite{loday-Remy2011}, or a differential equation, as in the work of Malgrange~\cite{malgrange--fourier}.
+\'{E}calle's ``formalism of singularities'' describes how the singularities of the perturbative solution propagate from one order of perturbation to the next.
+This information
+
+%%\'{E}calle's ``formalism of singularities'' can be used to show that Level~1 ODEs are a rich source of resurgent series.
+
+%%A resurgent analysis of a differential equation on the frequency domain begins by using formal perturbation theory to solve a corresponding equation on the position domain---either an integral equation, as in the work of Loday-Richaud and Remy~\cite{loday-Remy2011}, or a differential equation, as in the work of Malgrange~\cite{malgrange--fourier}.
+Ecalle's
+
+%%\textcolor{orange}{[Where does resurgence come in?]}
+
+\textcolor{orange}{[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]}
 \color{RoyalBlue}\par
@@
 \subsubsection{Thimble integral in geometry}
-Thimble integrals can be used to explore the geometry of complex manifolds, and even to define a homology theory. To see how this works, it will be helpful to
-
-\textcolor{PaleVioletRed}{[move to historical] For context, let us see how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
-Suppose for a moment that $X$ is $N$-dimensional, and consider a non-degenerate critical point $a$ that $f$ sends to $\zeta = \alpha$.
+\color{DarkBlue}
+Thimble integrals can be used to explore the geometry of complex manifolds, and even to define a homology theory.
+To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
+Suppose that $f \maps X \to B$ is a holomorphic map from an $N$-dimensional complex manifold $X$ to a translation surface $B$.
+Consider a translation chart $\zeta$ on $B$ and a non-degenerate critical point $a \in X$ that $f$ sends to $\zeta = \alpha$.
 Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
@@
 Since $O_N(\C)$ has only two connected components, distinguished by the sign of the determinant, a Lefschetz thimble is determined up to homotopy and orientation by the critical point $a$ and the direction $\theta$.
-When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.}
+When $N = 1$, the homotopy freedom disappears, because $O_1(\C)$ is the discrete group $\{\pm 1\}$.
 
@@
 \begin{itemize}
-\item Give definition in $N$ dimensions.
 \item Explain how can be seen in terms of homology (cite Pham).
@@
 %
-\textcolor{orange}{[move $N$-dim'l thimbles here]}
-%
 \subsubsection{Asymptotics of thimble integrals}
 %
+\textcolor{orange}{[Revise\ldots]}
+\color{DarkTurquoise}\par
 Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
@@
 \begin{remark}
-   Notice that for $\alpha=0$, the definition of convolution in equation~\eqref{eq:convolution_def} agrees with the standard deifinition (see \cite[Definition~5.12]{diverg-resurg-i}).
-In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast$, following the standard convention.   
+For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
+In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast$ [coordinate is necessary]}, following the standard convention.   
 \end{remark}
@@
 The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
-    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi}\ast\borel_\zeta\series{\Psi}.\]
+    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi}\textcolor{magenta}{\ast}\borel_\zeta\series{\Psi}.\]
 \end{prop}
@@
 &=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
-&=\borel_\zeta\series{\Phi}\ast \borel_\zeta\series{\Psi}\,.
+&=\borel_\zeta\series{\Phi} \textcolor{magenta}{\ast} \borel_\zeta\series{\Psi}\,.
 %&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
@@
 
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
+By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product: \textcolor{orange}{[which convolution is this?]}
 
@@
 \end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}$.
+ where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast \zeta^{-5/6}$.
 
@@
 \label{WKB_Airy} 
-\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
+\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] \psi(x, \eta) = 0 
 \end{equation}
@@
 \begin{align*}
-\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};s\right)\\
-\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};1-s\right)
+\psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};s\big)\\
+\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};1-s\big)
 \end{align*}
@@
 \label{Airy}
-\left[\left(\frac{d}{dw}\right)^2 -  w \right] f(w) = 0.
+\left[\big(\tfrac{d}{dw}\big)^2 -  w \right] f(w) = 0.
 \end{equation}
@@
 \begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
-&\left[\left(\frac{d}{dx}\right)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
-&\frac{d}{dx}\left[\frac{1}{2}x^{-1/2}\Phi+x^{1/2}\frac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
-&-\frac{1}{4}x^{-3/2}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+\frac{1}{2}x^{-1/2}\frac{d}{dx}\Phi+x^{1/2}\left(\frac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
-&\left[x^{1/2}\left(\frac{d}{dx}\right)^2+x^{-1/2}\frac{d}{dx}-\frac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
+&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
+&\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] x^{1/2}\Phi(q) = 0\\
+&\frac{d}{dx}\left[\tfrac{1}{2}x^{-1/2}\Phi+x^{1/2}\tfrac{d}{dx}\Phi\right]-\eta^2x^{3/2}\Phi=0\\
+&-\tfrac{1}{4}x^{-3/2}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+\tfrac{1}{2}x^{-1/2}\tfrac{d}{dx}\Phi+x^{1/2}\left(\tfrac{d}{dx}\right)^2\Phi-\eta^2x^{3/2}\Phi=0\\
+&\left[x^{1/2}\big(\tfrac{d}{dx}\big)^2+x^{-1/2}\tfrac{d}{dx}-\tfrac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
+&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
 \end{align*}
 \end{proof}
-Now rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
-\begin{align*}
-&\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{1}{2}\eta x^{-1/2}\frac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\eta^2x\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta x^{-1/2}\frac{d}{dq}-\frac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+\frac{3}{2}\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
+Now, rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
+\begin{align*}
+&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\frac{1}{2}\eta x^{-1/2}\tfrac{d}{dq}+x^{-1}\cdot\, \eta\,  x^{1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\eta^2x\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta x^{-1/2}\tfrac{d}{dq}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
+&\left[\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta^{-1} x^{-3/2}\tfrac{d}{dq}-\tfrac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
 %&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-&\left[\left(\frac{d}{dq}\right)^2+q^{-1}\frac{d}{dq}-\frac{1}{9}q^{-2}-1\right]\Phi=0
-\end{align*}
-
-therefore $\Phi(q)$ is a solution of the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
+&\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0.
+\end{align*}
+This shows that $\Phi(q)$ satisfies the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
 

### 2024-04-16 exp-resurgence.tex
Finish revising "Thimble integrals in geometry"

@@
 \subsubsection{\'{E}calle's theory of resurgence}
-\color{DarkBlue}
 \'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
@@
 \color{RoyalBlue}\par
-The developement of \'Ecalle's theory of resurgence introduced a new approach to the study of formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
-
-In a nutshell, the aim of resurgence is to study the analytic continuation of the Borel transform of a divergent series, in particular the location of sngularities in the position domain and Stokes constants computed after analytic continuation across the singularities.
-
-Recall, that resurgent $1$-Gevrey series have an endlessly analytically continuable Borel transform.
-Thus resurgence makes naturally a bridge between formal and analytic solutions in the position domain.
-Indeed, differential equations in the frequency domain can be turned into integral equations in the position domain, using the Borel transform.
-In particular the Borel transform of the formal solution $\series{\Phi}_\alpha$ is a convergent power series, and its sum can be studied by in terms of the equation it satisfies.
-For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
-Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
-Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
-
 However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
@@
 \color{black}
-% Then, the Stokes phenomenon is another distiguishd feature of irregular singular ODEs, an it is closely related to the fact that formal solutions are divergent. 
-% Indeed, the so called Stokes constants encode the ``jumps" of the underlying analytic solution which are charcateriz to have different asymptotics in different sectors saparated by Stokes lines.
-and when extended by continuation on larger sectors it jumps by an exponentially small correction.
-As an example, the first order equation \[\Phi'=\Phi+\frac{1}{z}\] has formal solution $\series{\Phi}=\sum_{n=0}^\infty n!z^{-n-1}$.
-Then, its Borel transform has a simple pole at $\zeta=1$.
-Consequently, the ``jump'' of its Borel sum occurs across the positive real axis $\Re(z)>0$ and it is given by $2\pi ie^{-z}$.
-
-% Still based on Borel summation, the approach of resurgence introduced by \'Ecalle in the '80 emphasizes the role of the position domain.
-Indeed, differential equation in the frequency domain can be turned into integral equation in the position domain, using the Borel transform.
-In particular the Borel transform of the formal solution $\series{\Phi}$ is a germ of analytic functions, and its analytic properties can be studied in terms of the equation they satisfy.
-For instance, in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
-Yet working in the position domain, one can turn the integral equation into a differential equation and trying to solve it analytically in the position domain, see~\cite{malgrange--fourier}.
-Then, going back to the frequency plane can be done with the Laplace transform, but it is usually a technincal analytic step.
-
+%
 \subsubsection{Laplace transform methods and fixed point iteration}
+%
 All of the historical approaches we have discussed so far start by looking for formal solutions.
@@
 In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.}
-\subsubsection{Thimble integral in physics}
-
-\subsubsection{Thimble integral in geometry}
-\color{DarkBlue}
-Thimble integrals can be used to explore the geometry of complex manifolds, and even to define a homology theory.
+\subsubsection{Thimble integrals in physics}
+
+\subsubsection{Thimble integrals in geometry}
+Thimble integrals can be used to explore the geometry of complex manifolds, and even to represent elements of a homology group.
 To see how this works, we first recall how the one-dimensional definition of a Lefschetz thimble arises from the general definition.
@@
 \[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
-Each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
+When the ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the other critical values of $f$, each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
 There are many such coordinate systems, but they are all related by local holomorphic maps from $X$ to the complex orthogonal group $O_N(\C)$.
@@
 
+Lefschetz thimbles for $f$ with direction $\theta$ represent classes in the ``rapid decay homology'' group $H^\theta_N(X,f)$.
+Roughly speaking, this group describes homology relative to the region where $\Re(e^{-i\theta} f)$ is large and positive.
+In this context, each thimble integral
+\[ \int_{\mathcal{C}}e^{-zf}\,\nu \]
+computes the pairing between a rapid decay homology class $\mathcal{C}$ and a ``twisted $1$-form'' $e^{-zf}\,\nu$.
+When all the critical points of $f$ are non-degenerate, Lefschetz thimbles actually form a basis for $H^\theta_N(X,f)$.
+As $\theta$ varies, the groups $H^\theta_N(X,f)$ fit together into a local system over the circle of directions, which is singular at the direction of each segment connecting a pair of critical values.
+The monodromy of this local system can be found using the Picard--Lefschetz formula~\cite[Section~1]{Arnold}\cite[Section~3.3, Part II]{pham}.
+
+Like solutions of level~$1$ ODEs, thimble integrals often exhibit the Stokes phenomenon.
+The Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles.
+Finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$.
+
+%%Equivalently, using the Borel regularity result \textcolor{magenta}{[do we really want this theorem, rather than the thimble projection formula?]} Theorem~\ref{thm:maxim}, we can express thimble integrals as Laplace transforms and reconstruct the monodromy of $H^\theta_N(X,f)$ from the associated Stokes constants.
+The Stokes
+%%\color{BlueViolet}
+%%\begin{itemize}
+%%\item Explain how can be seen in terms of homology (cite Pham).
+%%\item the Stokes constants are intersection number of thimbles, computed with Picard Lefschetz formula.
+%%\end{itemize}
+\color{black}
+%
+\subsubsection{Asymptotics of thimble integrals}
+%
+Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation.
+A thimble integral's asymptotic expansion is typically divergent, but the integral contains a hint about where to find the corresponding analytic object: the thimble itself, which is a real-analytic submanifold.
+
+\textcolor{orange}{[Keep revising\ldots]}
 \color{BlueViolet}
 \begin{itemize}
-\item Explain how can be seen in terms of homology (cite Pham).
+\item Traditionally, people study the asymptotic expansions of thimble integrals. This is the saddle point approximation.
+\item Problem: the resulting series is usually divergent. This is another source of divergent power series.
+\item In this case, we have a clue about where to find the corresponding analytic object, because the thimble itself is analytic.
+\item In fact, the thimble integral is almost a Laplace transform (cite Pham).
+%%\begin{itemize}
+%%\item ODE: get a formal series, resum it, check whether the result is an actual series.
+%%\item Thimble integral: get a formal series, resum it, check whether the result matches the original analytic thimble integral.
+%%\end{itemize}
 \end{itemize}
-\color{black}
-%
-\subsubsection{Asymptotics of thimble integrals}
-%
-\textcolor{orange}{[Revise\ldots]}
 \color{DarkTurquoise}\par
@@
 \color{RoyalBlue}
+\subsubsection*{Old stuff to distribute among new sections}
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
@@
 \begin{prop}
-The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphim from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.
+The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.
 \end{prop}
@@
 for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
+\textcolor{orange}{[add proof for $\alpha\neq 0$]}
+\begin{verify}
+\begin{align*}
+    \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}](a)&= \int_{\mathcal{J}^\theta_{\zeta, \alpha}} e^{-z\zeta(a)} \left(\int_{\zeta=\alpha}^a \psi \mathsf{R}^*\phi\;d\zeta\right)\;d\zeta
+\end{align*}
+
+    \begin{align*}
+         \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}]&=\int_\alpha^\infty e^{-z t}\phi(t)dt \int_\alpha^\infty e^{-z u} \psi(u) du \\
+         &=\int_\alpha^\infty \left(\int_\alpha^\infty  e^{-z (t+u)}\phi(t) \psi(u) du \right)dt \\
+         &=\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
+    \end{align*}
+    Define $\psi(s)=0$ if $s<\alpha$, thus $\psi(s-t)=0$ if $s<t+\alpha$, 
+    \begin{align*}
+        \int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
+    \end{align*}
+    Under the assumption that the integral is absolutely convergent, we can exchange the order of integration
+    \begin{align*}
+        \int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^\infty    \psi(s-t) \phi(t) dt \right)ds\\
+        &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^s    \psi(s-t) \phi(t) dt \right)ds \\
+        &=\int_\alpha^\infty e^{-z s} \phi\ast_{t,\alpha}\psi ds 
+    \end{align*}
+    \textcolor{orange}{[see Thm 5.25 \cite{diverg-resurg-i}]}
+\end{verify}
 \end{proof}
@@
 For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast$ [coordinate is necessary]}, following the standard convention.   
+In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast_\zeta$ [coordinate added]}, following the standard convention.   
 \end{remark}

### 2024-04-19 exp-resurgence.tex
Get ready to add SIMA manuscript class

@@
 \usepackage{fancyhdr}
-\usepackage[font=small, margin=1cm]{caption}
+\usepackage[margin=1cm]{caption}
 \usepackage{enumitem}
@@
 %
-\color{DarkBlue}
 We present the results, proofs, and examples in this paper with a few central goals in mind.
@@
 \subsubsection{Thimble integrals in physics}
-
+In physics, thimble integrals play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
+In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion~\cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}.
+\color{orange}
+For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
+\color{black}
+%
 \subsubsection{Thimble integrals in geometry}
@@
 %
-Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation.
-A thimble integral's asymptotic expansion is typically divergent, but the integral contains a hint about where to find the corresponding analytic object: the thimble itself, which is a real-analytic submanifold.
+\color{DarkBlue}
+Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
+A thimble integral's asymptotic expansion is typically divergent, \textbf{[but can be recovered using Borel summation]}
+\color{black}
 
 \textcolor{orange}{[Keep revising\ldots]}
+
 \color{BlueViolet}
 \begin{itemize}
-\item Traditionally, people study the asymptotic expansions of thimble integrals. This is the saddle point approximation.
-\item Problem: the resulting series is usually divergent. This is another source of divergent power series.
-\item In this case, we have a clue about where to find the corresponding analytic object, because the thimble itself is analytic.
-\item In fact, the thimble integral is almost a Laplace transform (cite Pham).
+\item In fact, the thimble integral is almost a Laplace transform (cite Pham and point to thimble projection formula in this paper)
+\item Can also recover analytic object using Borel summation.
+\begin{itemize}
+\item {[Transition into discussion similar to ``Laplace transform methods and fixed point iteration'' for ODEs]}
+\item This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
+\item \ldots but the integral contains a hint about where to find the corresponding analytic object: the thimble itself, which is a real-analytic submanifold.
+\end{itemize}
+\item {[Footnote:]} In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).
 %%\begin{itemize}
@@
 \color{DarkTurquoise}\par
-Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
-
-In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z \to \infty$ in direction $\theta$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
+\begin{itemize}
+\item Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions
+\item {[Toy model of situations where there's no well-defined thimble---like infinite-dimensional path integrals---or where the integral doesn't quite look like a thimble integral---like state integral in Chern-Simons.]}
+\end{itemize}
 
 This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
-In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
+In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms.
+We prove, from this, that they are Borel regular functions.
 In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
@@
 where $\mathsf{R}$ is the $180^\circ$ rotation that exchanges $\zeta = 0$ with $a$. In other words, $\mathsf{R}^*\zeta = \zeta(a) - \zeta$.
+\color{DarkTurquoise}
+\begin{itemize}
+\item Given a function $f$ on $B$, we will write $f'$ and $f''$ to denote the pullbacks of $f$ to the first and second factors, respectively, of $B \times B$.
+\end{itemize}
+
+\textcolor{orange}{\ldots} defined as
+\[ \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'', \]
+where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \textcolor{orange}{[check]}.
+\color{black}
 \end{definition}
@@
 \textcolor{orange}{[add proof for $\alpha\neq 0$]}
+\color{DarkTurquoise}
+\begin{align*}
+\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & \defeq \left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta \right)\left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \psi\,d\zeta \right) \\
+& = \left( \int_{\mathcal{J}_{\zeta', \alpha}^\theta} e^{-z\zeta'} \phi'\,d\zeta' \right)\left( \int_{\mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta''} \psi''\,d\zeta'' \right) \\
+& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;d\zeta' \wedge d\zeta''.
+\end{align*}
+Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \textcolor{orange}{[with $\zeta' + \zeta'' = \zeta$]}
+\begin{align*}
+\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;(d\zeta' + d\zeta'') \wedge d\zeta'' \\
+& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta}\,\phi'\,\psi''\;d\zeta \wedge d\zeta'' \\
+& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} \big(e^{-z\zeta}\;d\zeta\big) \wedge \big(\phi'\,\psi''\;d\zeta''\big) \\
+& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \left(\int_{\substack{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\;d\zeta''\right) d\zeta \\
+& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta}\,(\phi \ast_{\zeta, \alpha} \psi)\;d\zeta \\
+& = \laplace^\theta_{\zeta, \alpha}(\phi \ast_{\zeta, \alpha} \psi).
+\end{align*}
+\color{black}
 \begin{verify}

### 2024-04-19 sima/correspondence/sima-v2-changes.tex
Make corrections suggested by reviewer 2

\documentclass{letter}

\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}

% include signature image. based on suggestion from TeX.SE user Werner
%   https://tex.stackexchange.com/a/148458/6934
%%\makeatletter
%%\newcommand*{\signatureimg}[1]{\def\fromimg{#1}}
%%\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
%%  \stopbreaks
%%  \noindent
%%  \ifx\@empty\fromaddress\else
%%  \hspace*{\longindentation}\fi
%%  \parbox{\indentedwidth}{\raggedright
%%       \ignorespaces #1\\%
%%       \includegraphics[height=6\medskipamount]{\fromimg}\\%
%%       \ifx\@empty\fromsig
%%           \fromname
%%       \else \fromsig \fi\strut}%
%%   \par}
%%\makeatother

\address{Veronica Fantini \\
Institut des Hautes \'{E}tudes Scientifiques \\
Le Bois-Marie, 35 route de Chartres \\
F-91440 Bures-sur-Yvette, France}

\signature{\vspace{-12mm}Veronica Fantini \\
\url{fantini@ihes.fr} \\[6pt]
Aaron Fenyes \\
\url{aaron.fenyes@fareycircles.ooo}}

%%\signatureimg{placeholder-sig.pdf}

\date{March \textcolor{violet}{--}, 2023}

\begin{document}
\begin{letter}{}
\begin{tikzpicture}[remember picture,overlay]
\node[xshift=4.2cm, yshift=-3.5cm] at (current page.north west) {\pgftext{\includegraphics[height=4.02cm]{ihes-logo}}};
\end{tikzpicture}
\opening{Dear Prof. Lipton:}

\color{violet}
We addressed the co
\begin{itemize}
    \item We corrected the sign error that reviewer~2 noticed on line~275.
    \item We corrected the factorial $j!$ as reviewer~2 suggested on line~706.
     \item We corrected the factorial $j!$ as reviewer~2 suggested on line~730. We rewrote the decomposition of $Q$. 
     \item We corrected the sign error that reviewer~2 noticed on line~767.
      \item We corrected the typo that reviewer~2 noticed on line~781.
\end{itemize}
\color{black}
\closing{Best regards,}
\end{letter}
\end{document}

### 2024-04-19 sima/reg-sing-volterra_sima.tex
SIMA: Correct bibliography; change file names
Make corrections suggested by reviewer 2

--- 2023-10-31 siam/reg-sing-volterra.tex
@@
 \begin{equation}\label{eqn:sing-bound}
-\left|\frac{q}{p} - \frac{\tau}{\zeta}\right| < C
+\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
 \end{equation}
@@
 where
-\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 \end{align*}
-Now we expand $Q$ around $-\alpha$, using the decomposition $Q(\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(\zeta)$ to split up the last term of the expression above:
+Now we expand $Q$ around $-\alpha$, using the decomposition $Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta)$ to split up the last term of the expression above:
 \begin{equation}\label{eqn:split-numerator}
--\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
+-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
 \end{equation}
@@
 -\frac{Q(-\zeta)}{P(-\zeta)} & =
-\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
-&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(-\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
+&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
 \end{align*}
 Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
-\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)}\]
+\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\]
 Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.
@@
 \begin{align*}
-\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha.
+\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha.
 \end{align*}
 By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
-\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right|\]
+\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
 as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
@@
 where $Q_0, \ldots Q_{d-1}$ are polynomials of degree at most $d-1$.
-Next, knowing that $-\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
+Next, knowing that $\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
 We can then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
@@
 
-First, obseve that
+First, observe that
 \begin{align*}
 |\softker^\alpha(a, a')| & = \left|\frac{k_R(a, a')}{p(a)}\right| \\
-& \le \frac{1}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^{j+1} \\
-& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^j.
+& \le \frac{1}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{(j+1)!} \, |\zeta(a)-\zeta(a')|^{j+1} \\
+& = \frac{|\zeta(a)-\zeta(a')|}{|p(a)|} \sum_{j=0}^\infty \frac{|R_{j}|}{(j+1)!} \, |\zeta(a)-\zeta(a')|^j.
 \end{align*}
@@
 \begin{align*}
-\sum_{j=0}^\infty \frac{|R_{j}|}{j!} \, |\zeta(a)-\zeta(a')|^j
-& \lesssim \sum_{j=0}^\infty \frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
+\sum_{j=0}^\infty \frac{|R_{j}|}{(j+1)!} \, |\zeta(a)-\zeta(a')|^j
+& \lesssim \sum_{j=0}^\infty \left(\frac{1}{j+1}\right)\frac{\lambda_\Delta^j}{j!} \, |\zeta(a)-\zeta(a')|^j \\
 & \lesssim e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}
@@
 
-\bibliographystyle{utphys}
-\bibliography{airy-resurgence}
+\bibliographystyle{siamplain}
+\bibliography{reg-sing-volterra_sima.bib}
 \end{document}

### 2024-04-19 sima/correspondence/sima-v2-changes.tex
Remove contractions

@@
 \color{violet}
-We addressed the co
+Reviewer~2:
 \begin{itemize}
@@
 \end{itemize}
+Reviewer~1:
+\begin{itemize}
+\item There is no universal convention for naming the coordinates on the spaces involved in the Laplace transform. Conventions we have seen include:
+\begin{center}
+\begin{tabular}{c|c|l}
+Frequency varaible & Position variable & Source \\ \hline
+$z$ & $\zeta$ & Mitschi \& Sauzin \\
+$s$ & $t$ & Schiff \\
+$\hbar$ & $s$ & Mari\~{n}o \\
+\end{tabular}
+\end{center}
+From a physical perspective, the Laplace transform turns functions of position or time into functions of spatial or temporal frequency.
+The terms ``frequency'' and ``position'' thus unambiguously distinguish the two spaces involved in the Laplace transform.
+We use these terms to remind the reader which variable-naming convention we are using.
+\end{itemize}
 \color{black}

### 2024-04-19 sima/reg-sing-volterra_sima.tex
Remove contractions

@@
 Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
+In Section~\ref{sec:example}, we will see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
 This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.
@@
 From our experience with solving level~1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
-Let's say we've chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
+Suppose we have chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
 Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
@@
 \item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
-\item It's of exponential type, meaning that it's $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
+\item It is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
 \end{itemize}
@@
 Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
-We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-We'll apply our results to level $1$ differential equations in Section~\ref{sec:example}.
+We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+We will apply our results to level $1$ differential equations in Section~\ref{sec:example}.
 \subsection{Notation for uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we'll write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
@@
 Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$, and satisfies the following condition.
+Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
 \begin{conditions}
@@
 In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$.
-Since $\domain$ doesn't contain $\zeta = 0$, we'll always omit that starting point from the path.
+Since $\domain$ does not contain $\zeta = 0$, we will always omit that starting point from the path.
 \end{conditions}
@@
 \subsubsection{The prototype operator}\label{setting:basic}
-The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.
+The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.
 
@@
 \[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
-Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
+Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We will suppose this product can be written as a ratio
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
@@
 \begin{conditions}
-\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
+\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we will require, for simplicity, to be real and positive---the difference
 \[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
@@
 \end{conditions}
-For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
-We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
+For most of our results, we will need to make sure that $\domain$ does not touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
+We will also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
 These requirements can be combined into one condition.
@@
 \color{black}
-We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
+We will occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
 \begin{conditions}
@@
 
-Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
-The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
-To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
+We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
+The perturbation $\softpart$ does not have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we will show in Proposition \ref{prop:smoothing}).
+To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
 This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
@@
 Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$.
-We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity.
-We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
-Altogether, we'll require:
+We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
+We will also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+Altogether, we will require:
 \begin{conditions}
@@
 \end{conditions}
-Notice that this condition prevents $\softker$ from being separable---unless it's zero, of course.
+Notice that this condition prevents $\softker$ from being separable---unless it is zero, of course.
 
 Like $\hardker$, the combined kernel $k = \hardker + \softker$ of $\volterra$ grows in a controlled way when its arguments are near $\zeta = 0$, and when the difference between its arguments grows.
-We'll provide specific bounds in Section~\ref{sec:bounds on k}.
+We will provide specific bounds in Section~\ref{sec:bounds on k}.
 
@@
 \end{theorem}
-We'll prove this result in Section~\ref{sec:construction}.
+We will prove this result in Section~\ref{sec:construction}.
 
@@
 \end{theorem}
-We'll prove this result in Section~\ref{sec:asymptotics}.
+We will prove this result in Section~\ref{sec:asymptotics}.
 \begin{rmk}
@@
 
-When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we're trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
+When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
 We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
@@
 For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
-In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
+In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
 \end{theorem}
@@
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-Suppose we're also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
+Suppose we are also given a function $g$, which for some $\rho > \tau$ belongs to the space $\singexpalg{\rho-1}(\Omega)$ defined in Section~\ref{fn-spaces}.
 Then the inhomogeneous equation
@@
 \end{lemma}
-We'll prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
+We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
 The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.
 
-We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
 \begin{rmk}
@@
 Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
+Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
 Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
@@
 
-Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there's a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
+Fixing a real constant $\Lambda$, we restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
+One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we will equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
 With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
@@
 
-Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
+Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
 For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
@@
 \end{align*}
-The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it's bounded far from $\zeta = 0$ thanks to the decaying exponential.
+The function $|\zeta|^{\sigma'-\sigma}\,  e^{-(\Lambda-\Lambda') |\zeta|}$ is bounded near $\zeta = 0$ because the power of $|\zeta|$ is positive, and it is bounded far from $\zeta = 0$ thanks to the decaying exponential.
 Hence,
@@
 For each $\Lambda'$, we can get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
-For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we're ultimately working in the vector space of holomorphic functions on $\Omega$.
+For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are ultimately working in the vector space of holomorphic functions on $\Omega$.
 Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
@@
 The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
-We'll now show that the method works by proving those results.
+We will now show that the method works by proving those results.
 
 We start by constructing the prototype solution $\solproto$ from the kernel of $\hardpart$, which is the separable operator that gives $\volterra = \hardpart + \softpart$ its regular singularity.
-We'll show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
-
-To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
+We will show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+
+To see what the perturbation $\softpart$ does to $\solproto$, we will show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
 In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
@@
 Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
+To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 The proofs of the Proposition below can be combined together.}
-Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
+Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
 \begin{proposition}\label{prop:asymptotic at zero}
@@
 By Proposition~\ref{prop:asymptotic at zero}, we can find a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
-No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero on a bounded region, so we'll have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so we will have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
 
@@
 Setting $\lambda_0 = \lambda_\Delta + c_\Delta$, we have $|\solproto| \lesssim |\zeta|^{-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| \ge \delta$.
-Since we're assuming $\tau$ is real and positive, $|\zeta|^\tau$ can't get arbitrarily close to zero on the region $|\zeta| > \delta$.
+Since we are assuming $\tau$ is real and positive, $|\zeta|^\tau$ cannot get arbitrarily close to zero on the region $|\zeta| > \delta$.
 It follows that $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| \ge \delta$.
@@
 \begin{proof}
-It's enough to show that
+It is enough to show that
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
@@
 
-Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, let us look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 \subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
-Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$.
+Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we will show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$.
 This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
@@
 \begin{rmk}
-We're assuming that $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We'll take advantage of this in Section~\ref{sec:L-int-op}
+We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}
 \end{rmk}
@@
 Choose a constant $\Lambda \ge \lambda_\Delta$ big enough that $\solproto$ is in $\singexp{\tau-1}{\Lambda}(\domain)$.
-Since we're assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\softpart \solproto$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
+Since we are assuming $\tau$ is positive, we can apply Proposition~\ref{prop:smoothing}, concluding that $\softpart \solproto$ belongs to $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
 \end{proof}
@@
 \subsubsection{Overview}
-In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
+In this section, we will prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
 
@@
 \begin{rmk}
-For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
+For the argument, we will use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
 \end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Proposition~\ref{prop:whole-ker-near-bound}, which we'll state and prove in Section~\ref{sec:bounds on k}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+First, pick some $\sigma \in (\tau, \rho)$.\footnote{It is possible to fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
 \begin{equation}\label{near-limit}
@@
 Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$.
-In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
-In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
+In Section~\ref{near-bound}, we will bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
+In Section~\ref{far-bound}, we will see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
 Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-Now, we'll show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
+Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
 The condition tells us that
@@
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
-Choose a subset $\far \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
+Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
 \[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
@@
 \end{align*}
-for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 \begin{align*}
@@
 \]
-Let's again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+Let us again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
@@
 \end{align*}
-Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
+Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
 Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
@@
 \end{align*}
-we can rewrite the homogeneous equation we're trying to solve as an inhomogeneous equation for $\solptb$:
+we can rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
 \begin{align}
@@
 Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
-Since $\tau+\gamma > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
 Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
@@
 \[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
-of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it's in the interval
+of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it is in the interval
 \[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
@@
 Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-In an upcoming paper \cite{borel_reg}, we'll study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
+In an upcoming paper \cite{borel_reg}, we will study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
-So far, we've studied a Volterra equation with a regular singularity at $\zeta = 0$.
-When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we'll end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
-
-To adapt our previous reasoning to this more general situation, we'll reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
+So far, we have studied a Volterra equation with a regular singularity at $\zeta = 0$.
+When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we will end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
+
+To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
 The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
@@
 
-References to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, which we'll rewrite as $\zeta=\alpha$.
-For example, we'll now work on a domain that touches but doesn't contain $\zeta = \alpha$, introducing the notation $\domain_\alpha$ as a reminder of this change.
+References to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, which we will rewrite as $\zeta=\alpha$.
+For example, we will now work on a domain that touches but does not contain $\zeta = \alpha$, introducing the notation $\domain_\alpha$ as a reminder of this change.
 Condition~\eqref{cond:star} now says that $\domain_\alpha$ is star-shaped around $\zeta = \alpha$.
@@
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
 When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
@@
 \end{equation}
-It's a function on the frequency domain because it depends on the frequency variable $z$.
+It is a function on the frequency domain because it depends on the frequency variable $z$.
 \subsubsection{Action on integral operators}\label{sec:L-int-op}
@@
 For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
-We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
@@
 We can now state and prove the main result of this section.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and doesn't touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
-We'll show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
+We will show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
 By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
@@
 Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$.
 Then the equation
@@
 This is enough to show that $k_R$ is well-defined throughout $\C^2$.
-As we'll see later, it also leads to a useful bound on $k_R$.
+As we will see later, it also leads to a useful bound on $k_R$.
 \begin{verify}
@@
 
-Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Proposition~\ref{prop:alt-general_volterra}.
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are now working in the setting of Proposition~\ref{prop:alt-general_volterra}.
 To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
@@
 
-Since we're trying to bound $\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, let's rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
+Since we want to bound $\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ with a function of the difference $\omega(a, a') := \zeta(a) - \zeta(a')$, we will rewrite it as a rational function of $\omega(a, a')$ and $\zeta(a)$.
 First, rewrite
@@
 over all $a, a' \in \domain_\alpha$.
-Since $P_\alpha$ is a polynomial with a finite number of roots, and $\domain_\alpha$ doesn't touch any of the roots, $|P_\alpha(\zeta)|^{-1}$ is bounded on $\domain_\alpha$.
+Since $P_\alpha$ is a polynomial with a finite number of roots, and $\domain_\alpha$ does not touch any of the roots, $|P_\alpha(\zeta)|^{-1}$ is bounded on $\domain_\alpha$.
 We conclude that

### 2024-04-19 sima/reg-sing-volterra_sima.tex
Replace "tells us"

@@
 These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
-The first condition also tells us that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
+The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
 
@@
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-%\color{Tomato}
-%Furthermore, Condition \eqref{cond:diag-basic} tells us that for any $\sigma>0$ we can find a neighbourhood of $(0,0)\in\domain^2$ where 
-%\[|\hardker(a,a')|\le\frac{\sigma}{|\zeta(a)|}.\]
 \begin{verify}
@@
 \end{verify}
-\color{black}
+
 We will occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
@@
 
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ implies that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
 Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
@@
 \[ \|f\|_{\sigma,\Lambda}=\sup_{\Omega} |\zeta|^{-\sigma}\,e^{-\Lambda |\zeta|}\, |f|. \]
-The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, which tells us that
+The norm $\|\cdot\|_{\sigma, \Lambda'}$ is designed to give $|f| \le |\zeta|^\sigma\,e^{\Lambda'|\zeta|}\,\|f\|_{\sigma, \Lambda'}$, implying that
 \begin{align*}
@@
 To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 The subsequent argument, which we used to show that $\lim_{\zeta \to 0} \chi = 0$, actually supports a stronger conclusion: it shows that $|\chi| \lesssim |\zeta|^\tau$ on the region $|\zeta| < \delta$.
-This tells us that
+This implies that
 \[ |\solproto| \lesssim \left|\frac{1}{p}\right|\,|\zeta|^\tau \]
@@
 \begin{proof}
-First, choose some $\sigma_0 \in (\tau, \sigma)$. Condition~\eqref{cond:sing} tells us that by making $\delta > 0$ small enough, we can ensure that
+First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
@@
 Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
-The condition tells us that
+The condition guarantees that
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \subsubsection{Near the origin}\label{near-bound}
-Suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that
+Suppose that $a \in \near$. Then inequality~\eqref{near-limit} gives
 \begin{align*}
@@
 The base point for the construction can be chosen arbitrarily.
-Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$.
+Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$.
 Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of
@@
 \end{align}
-Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
+Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
 Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
@@
 \end{equation}
-First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. Equation~\eqref{eqn:split-numerator} tells us that
+First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from Equation~\eqref{eqn:split-numerator} that
 \begin{align*}
@@
 \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(-\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
-&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
+&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}\,.
 \end{align*}
 Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
-\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\]
+\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\,.
+\]
 Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.
@@
 \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha.
+|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
 \end{align*}

### 2024-04-29 sima/correspondence/sima-v2-changes.tex
Revise motivation

@@
 \begin{itemize}
+\item Reviewer~1 asked us to write more concisely and more formally.
+Where these goals conflict, we have prioritized conciseness.
+For example, we have continued to use ``small enough'' instead of ``sufficiently small.''
 \item There is no universal convention for naming the coordinates on the spaces involved in the Laplace transform. Conventions we have seen include:
@@
 We use these terms to remind the reader which variable-naming convention we are using.
+\item We have removed all contractions.
+\item We have removed the phrase ``tells us.''
+\item We use the phrase ``over all'' to emphasize that we are describing a uniform bound. This is now explained explicitly in the section ``Notation for uniform bounds.''
+\item We have changed our notation for uniform bounds to require the absolute value.
 \end{itemize}

### 2024-04-29 sima/reg-sing-volterra_sima.tex
Revise motivation

@@
 % operator under consideration
+\newcommand{\genvolterra}{\mathcal{W}}
+\newcommand{\genker}{w}
 \newcommand{\volterra}{\mathcal{V}}
@@
 \subsection{Motivation}\label{motivation}
+\color{brown}Classically, ODEs with an irregular singularity at infinity can be solved formally by ``normal series'' solutions~\cite{int-irreg}.
+These series are typicaly divergent, but summability methods allow to recover analytic solutions from them~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
+Remarkably, these ``resummed" analytic solutions are characterized by their asymptotic behaviour at infinity.
+In particular, under suitable assumptions on the ODE, a frame of solutions can be constructed by ``resumming" a frame of formal ones.
+The results of this paper are motivated by the desire to find the same frame of analytic solutions more directly, without the use of formal series.
+We do this in Section~\ref{sec:example} for a certain class of \emph{level}-1 ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
+In~\cite{borel_reg}, we show that these solutions match the ones obtained from summability methods.
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.
+
+In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a \textcolor{cyan}{real} ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$
+\[\big[\laplace\varphi\big](z):=\int_{\Gamma_{\zeta,0}}e^{-z\zeta}\varphi\; d\zeta \,,\]
+where $\Gamma_{\zeta,0}$ is a line issuing from $\zeta=0$.
+\begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
+Write $z$ in terms of its real and imaginary parts as $x + iy$.
+Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it.
+Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify}
+Through identities like
+\begin{align*}
+\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
+\laplace \psi\;\laplace \varphi & = \laplace(\psi * \varphi)\,,%\\
+%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+\end{align*}
+%where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, 
+the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+
+For instance, let $\mathcal{P}\Psi=0$ be the level-1 ODE of the kind studied in Section~\ref{sec:example}, with $\mathcal{P}$ being the differential operator 
+\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
+where $P$ a degree $d$ polynomial with distinct roots, $Q$ a degree $d-1$ polynomial non-vanishing at the roots of $P$, and the series $\sum_{j=0}^\infty R_j z^{-j}$ convergent for $|z|>A>0$.
+If $\Psi=\laplace\psi$, then
+\[
+\mathcal{P}\Psi=\mathcal{P}\big[\laplace\psi\big]=\laplace\big[\hat{\mathcal{P}}\psi\big]
+\]
+where $\hat{\mathcal{P}}$ is the integral operator 
+\[
+\hat{\mathcal{P}}\psi=P(-\zeta)\psi+\int_{0}^\zeta Q(-t)\psi\; dt+\int_0^\zeta \sum_{j=0}^\infty \frac{R_j}{(j+1)!} (\zeta-t)^{j+1}\psi\; dt \,.
+\]
+Therfore, the differential equation $\mathcal{P}\Psi=0$ is turned into the integral equation 
+\[\psi=\volterra\psi\,\]
+where $\volterra$ is the Volterra operator with kernel
+\[
+k(\zeta,t):=-\frac{Q(-t)}{P(-\zeta)}- \sum_{j=0}^\infty \frac{R_j}{(j+1)!} \frac{(\zeta-t)^{j+1}}{P(-\zeta)}\,.
+\]
+The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations. 
+Indeed, a Volterra operator $\volterra$ of the kind described above is expected to have a solution $\psi$ with the following feautures:
+\begin{itemize}
+    \item it has an $O(\zeta^{\tau_\alpha-1})$ singulairty at $\zeta=0$,
+    \item it is of exponential type, meaning that it is $O(e^{\Lambda|\zeta|})$ for some $\Lambda\in\R$, as $\zeta$ grows. 
+\end{itemize}
+These conditions are just strong enough to ensure that the solution $\psi$ has a well-defined Laplace transform $\Psi=\laplace\psi$, which by construction will satisfy the differential equation $\mathcal{P}\Psi=0$.
+The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
+
+Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
+We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+We will apply our results to level $1$ differential equations (of the kind described above) in Section~\ref{sec:example}.
+In particular, varying the contour of integration of the Laplace transform, so that the base point cooresponds to a root of $P$, we will construct solutions of the correspondent integral equation with a distinguished behaviour.
+
+This is a new approach to solve level $1$ ODEs with irregular singulatiries.
+Indeed, a classical alternative to Borel summability is given by the approach of Ecalle, which uses the Borel transform to turn differential equations to integral (convolution) equations.
+However, his approach to solve integral equations is by perturbation theory~\cite{EcalleIII} amd it have been applied also by other authors~\cite{loday-Remy2011,diverg-resurg-iii}.
+
+Furthermore, the Banach spaces $\singexp{\tau-1}{\Lambda}(\domain)$ are essentially new; in fact a similar definition was given in~\cite{braaksma2006laplace}.
+However, \textcolor{cyan}{[say why we are different from Braaksma]}
+\color{black}
+
+\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
+The results of this paper are motivated by the desire to find the same analytic solutions more directly, without the use of formal series.
+We do this in Section~\ref{sec:example} for a certain class of level~$1$ ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
+In~\cite{borel_reg}, we show that these solutions match the ones obtained through resummation.
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.}
+
+%%\textcolor{blue}{A classical way to solve an ODE with an irregular singularity at infinity is to start with formal solutions, in the shape of ``normal series''~\cite{int-irreg}.
+These series are typicaly divergent, but one can use summability methods to recover analytic solutions from them~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
+The results of this paper are motivated by the desire to find the same analytic solutions more directly, without the use of formal series.
+We do this in Section~\ref{sec:example} for a certain class of level~$1$ ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
+In~\cite{borel_reg}, we show that these solutions match the ones obtained from summability methods.
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.%
+%%%%Many classical differential equations, including the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
+%%}
+
 In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
@@
 
+\color{blue}
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
+For instance, in Section~\ref{sec:example}, we consider equations of the form
+\begin{equation}\label{eqn:intro-level-1}
+\left[ P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}) \right] \Phi = 0
+\end{equation}
+given by polynomials $P$, $Q$ and a holomorphic function $R(z^{-1})$ satisfying some extra conditions.
+A function of the form $\Phi = \laplace \varphi$ satisfies this equation if and only if $\varphi$ satisfies the integral equation
+\begin{equation}\label{eqn:intro-use-dict}
+\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0.
+\end{equation}
+The integral operator remains well-defined if we make $\zeta$ a complex coordinate and seek solutions $\varphi$ which extend holomorphically into the complex position domain.
+
+Equation~\eqref{eqn:intro-level-1} can be solved by resumming normal series, as described earlier.
+Each resummed solution is characterized by its $e^{-\alpha z} z^{-\tau_\alpha}$ asymptotics, where $-\alpha$ is a root of $P$ and $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$ is real and positive.
+To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
+Equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well.
+We seek a solution $\psi_\alpha$ which
+
+%%The integral operator $\partial^{-1}$ in equation~\ref{eqn:intro-use-dict} then becomes the integration $\partial^{-1}_{\zeta, \alpha}$ based at $\zeta = \alpha$.
+
+%%Equation~\ref{eqn:intro-use-dict} then uses the integral operator $\partial_{\zeta, \alpha}$ based at $\zeta = \alpha$.
+
+%%We then hope for the resulting version of equation~\eqref{eqn:intro-use-dict} to have a solution $\psi_\alpha$ with the following features: \textcolor{orange}{We then look for a solution $\psi_\alpha$ of (the resulting version of equation~\ref{eqn:intro-use-dict}) which:}
+
+%%take the Laplace transform using $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
+We must then solve equation~\eqref{eqn:intro-use-dict}, with the integration base point similarly shifted to $\zeta = \alpha$,
+
+%%find a solution of equation~\eqref{eqn:intro-use-dict} with the following features:
+\begin{itemize}
+\item has an $O\big((\zeta - \alpha)^{\tau_\alpha-1}\big)$ singularity at $\zeta = \alpha$; and
+\item is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
+\end{itemize}
+These conditions ensure that $\psi_\alpha$ has a well-defined Laplace transform, and the first condition gives $\laplace_{\zeta, \alpha} \psi_\alpha$ the desired asymptotics.
+
+The theory of Volterra equations is well-suited to this solution method.
+By embodying our conditions on $\psi_\alpha$ in a Banach space, defined in Section~\ref{fn-spaces}, we can solve equations like~\eqref{eqn:intro-use-dict} using the contraction mapping theorem, taking advantage of the regularizing effect of the relevant Volterra operators.
+This establishes the existence and uniqueness of $\psi_\alpha$, as stated in Theorem~\ref{thm:example}.
+Since integral operators on the position domain correspond directly to multiplication operators on the frequency domain, with no need to worry about initial values, we know immediately that $\laplace_{\zeta, \alpha} \psi_\alpha$ satisfies equation~\eqref{eqn:intro-level-1}, even when $\psi_\alpha$ blows up at $\zeta = \alpha$.
+By isolating the features of equation~\ref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get our main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
+
+Our results build on known methods for solving differential equations with irregular singularities.
+Our focus on integral equations in the position domain, and the singularities of their solutions, recalls \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
+One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.
+The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
+
+%%The existence and uniqueness of $\psi_\alpha$, stated as Theorem~\ref{thm:example}, follow from \textcolor{orange}{This gives} an existence and uniqueness result for
+
+%%The technique we use to solve equation~\eqref{eqn:intro-use-dict} applies to a wider class of regular singular Volterra equations. This paper focuses on stating and proving it in general,
+
+%%The Banach spaces we use also appear in the work of Braaksma, who uses them to study resummation for systems of ODEs whose coefficients are Laplace transforms.
+
+%%They also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
+
+%%\textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
+However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.}
+
+%%%%%%%%
+
+%%Our conditions on $\psi_\alpha$ define a Banach space of holomorphic functions, as discussed in Section~\ref{fn-spaces}.
+
+%%Our conditions place $\psi_\alpha$ in the Banach space $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}, where we can use the contraction mapping theorem to prove the existence and uniqueness of solutions for equations like~\ref{eqn:intro-use-dict}.
+
+%%Functions with the desired analytic properties form a Banach space of the form $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}, so we can use the contraction mapping theorem to prove that $\psi_\alpha$ exists and is un
+\color{violet}
+\begin{itemize}
+\item Unlike differential operators, integral operators on the position domain can be turned into differential operators on the position domain without boundary terms.
+\item {[Should we say this?]} Working in weighted $L^\infty$ spaces automatically shows that solutions are of exponential type, so their Laplace transforms are well-defined.
+In summability methods, this is the most challenging step.
+\item Linked to \'{E}calle's formal methods.
+\item Function spaces are used by Braaksma.
+\end{itemize}
+\color{black}
+
+%%The existence and uniqueness of such a solution $\psi_\alpha$ follows from the more general existence and uniqueness result stated in Section~\ref{sec:results}.
+
+%%Our goal is to prove the existence and uniqueness of $\psi_\alpha$. We will achieve it by proving a more general existence and uniqueness result, stated in Section~\ref{sec:results}.
+
+%%, by embodying the conditions on $\psi_\alpha$ in a Banach space of holomorphic functions---the space $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
+We will apply our results to level $1$ differential equations (of the kind described above) in Section~\ref{sec:example}.
+
+%%The first condition gives the Laplace transform of $\laplace_{\zeta,\alpha}\psi_\alpha$ the desired asymptotics, and the second condition ensures that $\laplace_{\zeta,\alpha}$ is well-defined.
+
+%%Both conditions ensure that $\laplace_{\zeta,\alpha}$ is well-defined, and in addition the first one gives $\laplace_{\zeta,\alpha}\psi_\alpha$ the desired asymptotics.
+
+%%For this kind of ODE, the special resummed solutions described earlier are indexed by the roots of $P$.
+In fact, they turn out to be the Laplace transforms $\Psi_\alpha = \laplace \psi_\alpha$ of holomorphic functions $\psi_\alpha$ associated with the roots $-\alpha$ of $P$.
+\color{black}
+
+%%see that the equation $\mathcal{P}\Phi = 0$ in the frequency domain corresponds to a holomorphic Volterra equation $\hat{\mathcal{P}}\varphi = 0$ on the position domain, where $\Phi = \laplace \varphi$.}
+
+%%Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
 Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino}\cite[Section 2.4]{sternin1995borel}.
 
-Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
+\color{violet}
+%%\begin{itemize}
+%%\item Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
+%%\item Both resurgence and summability methods pick out special solutions on the position domain, characterized by the way they blow up at the regular singularities.
+%%\item The properties of Volterra equations are especially well-suited to studying these singular solutions.
+%%\begin{itemize}
+%%\item Unlike differential operators, integral operators on the position domain can be turned into differential operators on the position domain without boundary terms.
+%%\item {[Should we say this?]} Working in weighted $L^\infty$ spaces automatically shows that solutions are of exponential type, so their Laplace transforms are well-defined.
+In summability methods, this is the most challenging step.
+%%\end{itemize}
+%%\item {[Alternate phrasing]} These special singular solutions are troublesome for standard Laplace transform techniques.
+%%\begin{itemize}
+%%\item One would traditionally turn the Volterra operator on the position domain into a differential operator by post-composing with derivatives.
+However, this comes at the cost of introducing boundary terms.
+For singular solutions, making sense of the boundary terms is not straightforward.
+%%\end{itemize}
+%%\end{itemize}
+\color{black}
+\textcolor{orange}{Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
 In Section~\ref{sec:example}, we will see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
-This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.
+This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.}
 \begin{verify}
@@
 
-From our experience with solving level~1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
-Suppose we have chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
+From our experience with solving level~1 differential equations by \textcolor{magenta}{Borel summation}, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
+Suppose \textcolor{red}{we have chosen} the position variable $\zeta$ is chosen so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
 Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
@@
 We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-We will apply our results to level $1$ differential equations in Section~\ref{sec:example}.
-\subsection{Notation for uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+\textcolor{orange}{We will apply our results to level $1$ differential equations in Section~\ref{sec:example}.} \textcolor{violet}{[Mention Theorem~\ref{thm:example} and Lemma~\ref{lem:use-dict}]}
+\color{blue}
+\subsection{Convention for coordinates}
+\textcolor{orange}{[\ldots]}
+\color{violet}
+\begin{itemize}
+\item Don't mention translation surfaces.
+\item Maybe talk about branched covers of the complex plane, which we need to describe the singular solutions?
+\end{itemize}
+\color{brown}
+\begin{itemize}
+    \item mention that $\zeta=0$ is not special, and having in mind the application to ODEs, we need to consider different coordinates.
+Thus, we think it's appropriate to use the coordinate free notation.
+    \item Coordinate free notation is easy to generalize to translation surfaces.
+    \item If the reader is familiar with the analysis notation, he should read $\zeta(a)$ as $\zeta$, and the variable inside the integral as ?? 
+\end{itemize}
+\color{black}
+\subsection{Notation}
+\subsubsection{Uniform bounds}
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
+If the bound invovles an explicit variable, we will say that it holds over all values of the variable.
+For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
+\subsubsection{Boundary points}
+A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
+If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$.
+This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
+
 \subsection{Setting}\label{setting}
@@
 Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
+
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
@@
 \end{conditions}
-For the applications we have in mind, $\domain$ might look something like the set pictured below.
+For the applications we have in mind, $\domain$ typically resembles the set pictured below.
 \begin{center}
@@
 \end{center}
+%
 \subsubsection{The prototype operator}\label{setting:basic}
-The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.
-
-Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
-\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
-Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We will suppose this product can be written as a ratio
+The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.
+
+Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
+% \color{red}
+% Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
+% \[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
+% Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We will suppose this product can be written as a ratio
+% \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
+% where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:\color{brown}
+\begin{definition}\label{defn:volterra}
+A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
+\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
+defined by an integral
+\[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
+in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
+\end{definition}
+\begin{definition}
+A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
+\end{definition}
+For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
+for some $p, q \in \mathcal{H}(\Omega)$.
+
+For the purposes of this paper, $\hardpart$ has a {\em regular singularity} at $\zeta=0$ if the following condition holds.
+
+%%The Volterra operator $\hardpart$ has a regular singularity at $\zeta=0$ if the following condition holds
 \begin{conditions}
-\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we will require, for simplicity, to be real and positive---the difference
+\condconst{sing}{\tau}\label{cond:sing}For some constant $\tau > 0$, the difference
 \[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
 is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
-In addition, for each $\sigma > \tau$, the bound
-\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
+In addition, for each $\sigma > \tau$, there is a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$ on which
+\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|}. \]
 \end{conditions}
-For most of our results, we will need to make sure that $\domain$ does not touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
+For most of our results, we will need to make sure that $\domain$ does not touch any singularities of $\hardker$ other than the one at $\zeta = 0$.
 We will also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
@@
 \end{conditions}
-This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
+This condition explains why $\domain$ \textcolor{brown}{might have the shape} illustrated in Section~\ref{setting:domain}.
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 \begin{verify}
-    By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+    By Condition \eqref{cond:diag-basic} \textcolor{red}{we can find} there exists $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
@@
 
-We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
-The perturbation $\softpart$ does not have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we will show in Proposition \ref{prop:smoothing}).
+We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$\textcolor{brown}{, where $\softpart$ has non-separable kernel, and it regularizes the action of $\softpart$ at the singularity, as we will show in Proposition \ref{prop:smoothing}.} \textcolor{blue}{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
 To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound \textcolor{red}{on how fast $\softker$ grows away from the diagonal} to the growth of $\softker$ away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{red}{For some constant} There exists a constant $\gamma > 0$, \textcolor{red}{we have} such that
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
-\[ f = \hardpart f \]
+\begin{equation}\label{eq:hardpart}
+f = \hardpart f    
+\end{equation}
 has the {\em prototype solution}
@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
+With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} it is guaranteed that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
 The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
@@
 \end{rmk}
-
-When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
+%
+\textcolor{red}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated}, but its regular singularity at $\zeta = 0$ stays essentially the same.
 We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
@@
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
-\[f = \volterra f\]
+\begin{equation}\label{eq:volterra-general}
+f = \volterra f  
+\end{equation}
 has a unique solution $f$ in the affine subspace
@@
 
+\color{red}For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
+In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.\color{black}
+\end{theorem}
+\color{brown}
+\begin{rmk}
    For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
 In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
-\end{theorem}
+\textcolor{cyan}{I'm confused by this remark too.}
+\end{rmk}
+\color{black}
 This result will follow from a more general result about inhomogeneous equations.
@@
 
-We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation~\eqref{eq:volterra-general} \textcolor{red}{we want to solve} as an inhomogeneous equation in a more regular space.
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
@@
 \[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) \]
-when $\rho > \tau$ is low enough, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
+when $\rho > \tau$ is \textcolor{red}{low enough} sufficiently small, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
 \end{rmk}
@@
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
-Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
-Give $\cont(\domain)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
+\textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
+Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{brown}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$ with the compact-open topology.
+This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
 The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-
+\color{red}
 Fixing a real constant $\Lambda$, we restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
 One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we will equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
 With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
 That means the inclusion is continuous.
+\color{brown}
+For $\Lambda\in\R$, let 
+\[\|f\|_{0,\Lambda} := \sup_\domain e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
+\begin{definition}
+    We define the normed space
+    \[\singexp{0}{\Lambda}(\domain):=\{ f\in\holo(\domain)\,\vert\, \|f\|_{0,\Lambda}<+\infty\}\,.\]
+\end{definition}
+\begin{rmk}
+    The space $\singexp{0}{\Lambda}(\domain)$ can be seen as the space of functions uniformly bounded by constant multiples of $e^{\Lambda |\zeta|}$.
+\end{rmk}
+With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
+That means the inclusion is continuous.
+\color{red}
 \begin{proposition}\label{exp-complete}
@@
 
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ implies that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
-This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
+The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ implies that for any $r > 0$, \textcolor{red}{we can find some} there exists $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\Omega)$ implies pointwise convergence, \textcolor{red}{we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$} we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows.
+This shows that \textcolor{red}{our} the sequence $f_k$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
+\textcolor{red}{We can also see} In addition, from this argument it follows that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
 \begin{align*}
@@
 \end{proof}
-
+\color{black}
 Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
-For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
+\color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
 Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
-Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
+Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we \textcolor{red}{can} generalize Proposition~\ref{exp-complete}:
+\color{brown}
+For $\sigma\in\R$, let 
+\[\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
+\begin{definition}
+    We define the normed space
+    \[\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega):=\{f\in\holo(\domain)\,\vert \, \|f\|_{\sigma,\Lambda}<+\infty\}\,.\]
+\end{definition}
+\begin{rmk}
+    The above is a space of functions uniformly bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda |\zeta|}$.
+\end{rmk}
+\color{black}
 \begin{proposition}
@@
 \end{proposition}
+\color{brown}
+\begin{proof}
+Let $\{f_n\}_{n=1}^\infty\subset\singexp{\sigma}{\Lambda}(\domain)$ be a Cauchy sequence.
+The inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each norm on $\sup_K |f|$ on $\holo(\domain)$, where $K \subset \Omega$ is compact.
+Hence, $\{f_n\}_{n=1}^\infty$ is a Cauchy sequence also in $\holo(\domain)$.
+The latter being complete~\cite[Proposition~3.5]{fnl-cpx-anal}, the sequence converges to a function $f\in\holo(\domain)$.
+
+By the Cauchy property on $\singexp{\sigma}{\Lambda}(\Omega)$, for any $r > 0$ there exists $n$ such that $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ for every $k \ge n$.
+Since convergence in $\holo(\Omega)$ implies pointwise convergence, we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows.
+This implies that the sequence $\{f_n\}_{n=1}^\infty$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
+In addition, from this argument it follows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
+\begin{align*}
+|\zeta|^{-\sigma}e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
+& \le r + \|f_n\|_{\sigma,\Lambda}
+\end{align*}
+for the corresponding $n$, showing that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
+\end{proof}
+\color{black}
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
@@
 \end{proof}
-As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.
-Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
-Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
+As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.\color{brown}\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
+\begin{definition}
+    Let $\sigma, \Lambda\in\R$. We define the space
+    \[\singexpalg{\sigma}(\domain):=\bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain)\,,\]
+    equipped with the finest topology that makes continuos the inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$. 
+\end{definition}
+The finest topology that makes the inclusion continuos is \textcolor{cyan}{[...]}
+\color{red} Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
+Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we \textcolor{red}{can} give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
+\color{brown}
+\color{black}
 \begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
@@
 \begin{proof}
-For each $\Lambda'$, we can get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
+\color{red}
+For each $\Lambda'$, we \textcolor{red}{can} get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing \textcolor{red}{some} $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
 For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are ultimately working in the vector space of holomorphic functions on $\Omega$.
 Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
+
+\color{brown}
+For every $\Lambda'$, there is a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ obtained by choosing $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$.
+
+For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are working in the space of holomprhic functions on $\domain$.
+In the topology of $\singexpalg{\sigma'}(\domain)$, this gives the desired continuos inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
+\color{black}
 \end{proof}
@@
 \subsection{Overview}
+\color{red}
 The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
-We will now show that the method works by proving those results.
+In this section, we show that the method works by proving those results.
 
@@
 
-Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+\textcolor{red}{Now we know that} Therefore $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
 To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
 This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
+
+\color{brown}
+In this section, we prove the results outlined in Section~\ref{sec:results}, demonstrating a method for solving the singular Voletrra equation $f=\volterra f$.
+
+We start by constructing the prototype solution $f_0$ of $f=\softpart f$, and show in Section~\ref{sec:proto-construction-regularity} that $f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
+
+In Section~\ref{sec:image under soft_part}, we show that the perturbation $\softpart$ has a smoothing effect on $f_0$, reducing the power-law singularity at $\zeta=0$.
+In particular, it turns out that $\softpart f_0\in\singexpalg{\tau-1+\gamma}(\domain)$.
+\color{black}
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
-
 \subsubsection{Construction}\label{sec:construction}
@@
 
-By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
+By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} there exists a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
@@
 \end{equation}
-whenever $|\zeta| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
+whenever $|\zeta| < \delta$. \textcolor{red}{We can take advantage of} We use this bound by rewriting the integral in the definition of $\chi$:
 \begin{align*}
@@
 
-Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
+Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} for a given $\sigma>0$ there exists a radius $r<\delta$ for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
-whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we \textcolor{red}{can} deduce that
 \begin{align*}
@@
 
-By Proposition~\ref{prop:asymptotic at zero}, we can find a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+By Proposition~\ref{prop:asymptotic at zero}, \textcolor{red}{we can find} there exists a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
 No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so we will have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
@@
 \end{align*}
-over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. One consequence is that, for some $c_\Delta > 0$, we have
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$.
+\textcolor{red}{One consequence is that} \textcolor{violet}{[is this really an equivalent statement?
+check again]} \textcolor{brown}{Namely,} for some $c_\Delta > 0$, we have
 \[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
 whenever $|\zeta(a)| \ge \delta$.
-Applying this bound along the diagonal in $\domain^2$, we learn that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we \textcolor{red}{learn} get that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
 On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we reason that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{red}{reason} deduce that
 \begin{align*}
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, \textcolor{red}{for some constant $M$} there is some $M\in\C$ for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
-at $\zeta = 0$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
+at $\zeta = 0$. \textcolor{red}{Like we did} As in the proof of Theorem~\ref{thm:basic_volterra}, we \textcolor{red}{reason} deduce that
 \begin{align*}
@@
 \end{align*}
-Since $\zeta(b)^{-\tau}$ is a constant, the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want.
-
-With a little work, the $\zeta/p$ factor also looks like what we want. Condition \eqref{cond:reg-p} implies that
+Since $\zeta(b)^{-\tau}$ is a constant, \textcolor{red}{the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want} the factor $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ is proportional to $\zeta^{\tau-1}$.
+
+\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} Then, Condition \eqref{cond:reg-p} implies that
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, let us look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, let us look at the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} there exists a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
-Observing that $|\eta| \le C |\zeta|$ in $\near$, we can conclude that
+Observing that $|\eta| \le C |\zeta|$ in $\near$, we \textcolor{red}{can} conclude that
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
@@
 
-Combining the arguments above, we learn that
+Combining the arguments above, we \textcolor{red}{learn} find that
 \begin{align*}
@@
 \end{align*}
-The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
+The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$.
+\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} The integral defines Euler's beta function, so
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\textcolor{red}{Our assumptions that} Since $\gamma > 0$ and $\sigma > -1$, \textcolor{red}{ensure that} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\domain)$ by making $\Lambda$ big enough.
+Then, for each $\rho > \tau$, there is some $\Lambda_\text{\rm lower} \in \R$ such that
+\[\volterra\colon\singexp{\rho-1}{\Lambda}(\domain)\to\singexp{\rho-1}{\Lambda}(\domain)\]
+is a contraction for all $\Lambda > \Lambda_\text{\rm lower}$.
 \end{proposition}
 \begin{rmk}
-For the argument, we will use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
+The threshold $\Lambda_\text{\rm lower}$ is always greater than $\lambda_\Delta$, and often much greater.
 \end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{It is possible to fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+First, pick some $\sigma \in (\tau, \rho)$.\footnote{\textcolor{red}{It is possible to fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.}} Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, shows that there is a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
 \begin{equation}\label{near-limit}
@@
 for all $a, a' \in \near$.
-By choosing a small enough positive radius $\delta$, we can take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$.
+We take $\near$ to be the part of $\domain$ where $|\zeta| < \delta$, for some small enough positive radius $\delta$.
 Complementarily, let $\far$ be the part of $\domain$ where $\delta \le |\zeta|$.
@@
 \begin{proposition}\label{prop:whole-ker-near-bound}
-Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
+\color{red}
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we \textcolor{red}{can} ensure that
 \[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
 by keeping $a$ and $a'$ close enough to $\zeta = 0$.
+
+\color{brown}
+If $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, then for any $\sigma > \tau$ there exists a neighbourhood $\mathcal{U}$ of $\zeta=0$ in $\domain$ such that
+\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
+for any $(a,a')\in\mathcal{U}^2$.
+\color{black}
 \end{proposition}
 \begin{proof}
-First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
+First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{red}{can} ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
-The condition guarantees that
+\textcolor{red}{Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want can be made sufficienlty small by keeping $a$ and $a'$ close to $\zeta = 0$.
+The condition guarantees that}
+
+\textcolor{brown}{Condition~\eqref{cond:eps-lambda} implies that}
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
-Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
+Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.\footnote{\textcolor{red}{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.}} Then, for any $\lambda > \lambda_\Delta$, we have
 \[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
@@
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \]
-grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
+grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we \textcolor{red}{can} bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
@@
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
-for any choice of integration path.\footnote{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
+for any choice of integration path.\footnote{\textcolor{red}{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} not clear} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
 \begin{align*}
@@
 \end{align*}
-for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+for any integration path that stays within $\near$.
+\textcolor{red}{Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path} \textcolor{brown}{Since $\near$ \textcolor{magenta}{is star-shaped [why?]} at $\zeta=0$, the path of integration can be chosen to be a segment } $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 \begin{align*}
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, we can find a constant $M$ for which
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} there is some $M\in\R_{>0}$ for which
 \[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
-for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
+for all $a \in \far$.
+Note that only the first argument of $k$ has its domain restricted\textcolor{red}{; this bound holds throughout $\domain$ in the second argument}, \textcolor{violet}{[rephrase]} while the second varies in $\domain$.
+Applying this bound, we \textcolor{red}{learn} that
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
@@
 Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
+Then \textcolor{red}{we can make our bound} there is an uniform bound over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
@@
 To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately.
-At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
+At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we \textcolor{red}{can} use a worst-case estimate on the exponential factor:
 \begin{align*}
@@
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
-Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
+\color{red}Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
 Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
@@
 Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
+
+\color{brown}
+Choose $\Lambda$ sufficienlty large that $\volterra$ is a contraction, by Proposition~\ref{prop:get-contraction}.
+Take $g\in\singexpalg{\rho-1}(\Omega)$.
+By definition, $g$ also belong to $\singexp{\rho-1}{\Lambda}(\Omega)$.
+Therefore,
+\[f \mapsto \volterra f + g\]
+is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem. 
+\textcolor{cyan}{[I'm confused by the next part of the argument]}
+\color{black}
 \end{proof}
@@
 \end{align*}
-we can rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
+we \textcolor{red}{can} rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
 \begin{align}
@@
 
-Now, we just want to show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
+\textcolor{red}{Now, we just want to} Next, we show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
 
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, we can use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+In this case, we \textcolor{red}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
 Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
@@
 \begin{proposition}\label{prop:alt-general_volterra}
-Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other conditions we assume in {\em Theorem~\ref{thm:general_volterra}}.
-Then, as long as $\rho > \tau$ is low enough, the equation
-\[f = \volterra f\]
+Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the \textcolor{red}{other conditions we assume in} assumptions of {\em Theorem~\ref{thm:general_volterra}}.
+Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} for $\tau<\rho<\tau+\min(\gamma,\epsilon,1)$, the Equation~\eqref{eqn:orig-homog}
+\textcolor{red}{
+\begin{equation}
+f = \volterra f
+\end{equation}}
 has a unique solution $f$ in the affine subspace
 \[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
-of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it is in the interval
-\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
+of the space $\singexpalg{\tau-1}(\domain)$. \textcolor{red}{To be precise, $\rho$ is low enough when it is in the interval
+\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]}
 \end{proposition}
@@
 \subsection{Overview}
-We can use our understanding of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-In particular, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We \textcolor{red}{can use our understanding of} use regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+In particular, we \textcolor{red}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 Let $\mathcal{P}$ be a linear differential operator of the form
-\[ \mathcal{P} = P(\partial_z) + \frac{1}{z} Q(\partial_z) + \frac{1}{z^2} R(z^{-1}), \]
+\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
 where
@@
 \item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that's non-zero at every root of $P$;
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$;
 \item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
@@
 
-To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
+\textcolor{red}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
 This substitution leads to several other reinterpretations, summarized below.
@@
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
-When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{red}{that leaves} originating from $\zeta=\alpha$ \textcolor{red}{at angle} in the direction of $\theta$.
+\color{red} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
 The Laplace transform of $\varphi$ is defined by the formula
-\begin{equation}\label{laplace:int} 
+\begin{equation}%\label{laplace:int} 
 \laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
@@
 It is a function on the frequency domain because it depends on the frequency variable $z$.
+\color{brown}
+Let $\Pi_\Lambda^\theta:=\{z\in\C \,\vert \, \Re(z e^{i\theta})>\Lambda\}$. If $\Gamma_{\zeta, \alpha}^\theta$ is contained in $\domain_\alpha$, the Laplace transform 
+\[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\domain_\alpha)\to\holo(\Pi_\Lambda^\theta)\]
+is defined by
+\begin{equation}\label{laplace:int} 
+(\laplace_{\zeta, \alpha}^{\theta} \varphi)(z) := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
+\end{equation}
+\color{black}
 \subsubsection{Action on integral operators}\label{sec:L-int-op}
@@
 \[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
-for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
+for each $a \in \domain_\alpha$. It obeys the \textcolor{red}{expected} semigroup law \cite[Section~1.3]{mladenov2014advanced}
 \begin{align*}
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{red}{you can use} differentiation under the integral \textcolor{red}{to show} shows that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \subsection{Going to the position domain}
-Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
+Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} differential operators in the frequency domain become \textcolor{red}{into} Volterra operators in the position domain.
 \begin{lemma}\label{lem:use-dict}
-For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
-\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
+\textcolor{cyan}{For each root $-\alpha$ of $P$} \textcolor{brown}{For each $\alpha\in\C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
+\color{cyan}\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
+\color{brown}
+\begin{equation}\label{eq:hat-P-alpha}
+    \big[\hat{\mathcal{P}}_\alpha\varphi\big](a):=\big[P(-\zeta)\varphi\big](a)+ \int_{\zeta=\alpha}^a Q(-\zeta) \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, 
+\end{equation}
+where
+\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\color{black}
 If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
@@
 \begin{rmk}
-For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
+\textcolor{red}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
 We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
@@
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
-Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{red}{can work out} find that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
 Hence,
@@
 
-We can now state and prove the main result of this section.
+We \textcolor{red}{can} now state and prove the main result of this section.
 Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
@@
 \begin{theorem}\label{thm:example}
-Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$.
-Then the equation
+Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
+$\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$. Then the equation
 \[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
@@
 \begin{proof}[Proof of Theorem~\ref{thm:example}]
-Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+\color{red}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
@@
 \[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\color{brown}
+Choose a root $-\alpha$ of $P$ such that $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
+The equation $\hat{\mathcal{P}}_\alpha\varphi=0$, with $\hat{\mathcal{P}}_\alpha$ as in Equation~\eqref{eq:hat-P-alpha}, is explicitly
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0\,. \]
+\color{black}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
-Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
-
-The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+ \textcolor{red}{Now we can write} Equation~\eqref{eqn:divided} can be written as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+
+\textcolor{red}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
 One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
 To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
-Consequently, for any $\lambda > A$, we have $|R_{j}| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
+Consequently, for any $\lambda > A$, we have $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
 This is enough to show that $k_R$ is well-defined throughout $\C^2$.
-As we will see later, it also leads to a useful bound on $k_R$.
+As we will see later, it also leads to a useful bound on $k_R$.}
+
+\textcolor{brown}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+Indeed, since $R(z^{-1})$ is holomorphic on the disk $|z| > A$, we have that for any $\lambda > A$, $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
+}
 \begin{verify}
@@
 
-Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are now working in the setting of Proposition~\ref{prop:alt-general_volterra}.
-To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are \textcolor{red}{now working} in the setting of Proposition~\ref{prop:alt-general_volterra}.
+To apply the proposition, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
 \begin{itemize}
@@
 \end{align*}
-By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
+By bringing $\zeta(a')$ closer to $\alpha$, \textcolor{red}{we can make} the middle term
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
+ca be made \textcolor{magenta}{sufficiently small} \textcolor{red}{as small as we want}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{red}{we can make} the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-as small as we want. Hence, for any $\sigma > \tau_\alpha$, the bound
+can be made \textcolor{magenta}{sufficielty small} \textcolor{red}{as small as we want}. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
@@
 Next, knowing that $\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
-We can then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
+We \textcolor{red}{can} then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
 \[ \big(\zeta(a)-\alpha\big)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]
@@
 \end{itemize}
-We can now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
+We \textcolor{red}{can} now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
 \end{proof}

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Commit after meeting

@@
 \subsection{Motivation}\label{motivation}
-\color{brown}Classically, ODEs with an irregular singularity at infinity can be solved formally by ``normal series'' solutions~\cite{int-irreg}.
+%%\color{brown}Classically, ODEs with an irregular singularity at infinity can be solved formally by ``normal series'' solutions~\cite{int-irreg}.
 These series are typicaly divergent, but summability methods allow to recover analytic solutions from them~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
@@
 
-In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a \textcolor{cyan}{real} ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$
-\[\big[\laplace\varphi\big](z):=\int_{\Gamma_{\zeta,0}}e^{-z\zeta}\varphi\; d\zeta \,,\]
-where $\Gamma_{\zeta,0}$ is a line issuing from $\zeta=0$.
+%%In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a \textcolor{cyan}{real} ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$
+%%\[\big[\laplace\varphi\big](z):=\int_{\Gamma_{\zeta,0}}e^{-z\zeta}\varphi\; d\zeta \,,\]
+%%where $\Gamma_{\zeta,0}$ is a line issuing from $\zeta=0$.
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify}
-Through identities like
-\begin{align*}
-\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-\laplace \psi\;\laplace \varphi & = \laplace(\psi * \varphi)\,,%\\
-%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
-\end{align*}
+%%Through identities like
+%%\begin{align*}
+%%\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
+%%\laplace \psi\;\laplace \varphi & = \laplace(\psi * \varphi)\,,%\\
+%%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+%%\end{align*}
 %where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, 
-the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
-
-For instance, let $\mathcal{P}\Psi=0$ be the level-1 ODE of the kind studied in Section~\ref{sec:example}, with $\mathcal{P}$ being the differential operator 
-\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
-where $P$ a degree $d$ polynomial with distinct roots, $Q$ a degree $d-1$ polynomial non-vanishing at the roots of $P$, and the series $\sum_{j=0}^\infty R_j z^{-j}$ convergent for $|z|>A>0$.
+%%the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. 
+%%
+%%For instance, let $\mathcal{P}\Psi=0$ be the level-1 ODE of the kind studied in Section~\ref{sec:example}, with $\mathcal{P}$ being the differential operator 
+%%\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
+%%where $P$ a degree $d$ polynomial with distinct roots, $Q$ a degree $d-1$ polynomial non-vanishing at the roots of $P$, and the series $\sum_{j=0}^\infty R_j z^{-j}$ convergent for $|z|>A>0$.
 If $\Psi=\laplace\psi$, then
-\[
-\mathcal{P}\Psi=\mathcal{P}\big[\laplace\psi\big]=\laplace\big[\hat{\mathcal{P}}\psi\big]
-\]
-where $\hat{\mathcal{P}}$ is the integral operator 
-\[
-\hat{\mathcal{P}}\psi=P(-\zeta)\psi+\int_{0}^\zeta Q(-t)\psi\; dt+\int_0^\zeta \sum_{j=0}^\infty \frac{R_j}{(j+1)!} (\zeta-t)^{j+1}\psi\; dt \,.
-\]
-Therfore, the differential equation $\mathcal{P}\Psi=0$ is turned into the integral equation 
-\[\psi=\volterra\psi\,\]
-where $\volterra$ is the Volterra operator with kernel
-\[
-k(\zeta,t):=-\frac{Q(-t)}{P(-\zeta)}- \sum_{j=0}^\infty \frac{R_j}{(j+1)!} \frac{(\zeta-t)^{j+1}}{P(-\zeta)}\,.
-\]
-The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations. 
-Indeed, a Volterra operator $\volterra$ of the kind described above is expected to have a solution $\psi$ with the following feautures:
-\begin{itemize}
-    \item it has an $O(\zeta^{\tau_\alpha-1})$ singulairty at $\zeta=0$,
-    \item it is of exponential type, meaning that it is $O(e^{\Lambda|\zeta|})$ for some $\Lambda\in\R$, as $\zeta$ grows. 
-\end{itemize}
-These conditions are just strong enough to ensure that the solution $\psi$ has a well-defined Laplace transform $\Psi=\laplace\psi$, which by construction will satisfy the differential equation $\mathcal{P}\Psi=0$.
+%%\[
+%%\mathcal{P}\Psi=\mathcal{P}\big[\laplace\psi\big]=\laplace\big[\hat{\mathcal{P}}\psi\big]
+%%\]
+%%where $\hat{\mathcal{P}}$ is the integral operator 
+%%\[
+%%\hat{\mathcal{P}}\psi=P(-\zeta)\psi+\int_{0}^\zeta Q(-t)\psi\; dt+\int_0^\zeta \sum_{j=0}^\infty \frac{R_j}{(j+1)!} (\zeta-t)^{j+1}\psi\; dt \,.
+%%\]
+%%Therfore, the differential equation $\mathcal{P}\Psi=0$ is turned into the integral equation 
+%%\[\psi=\volterra\psi\,\]
+%%where $\volterra$ is the Volterra operator with kernel
+%%\[
+%%k(\zeta,t):=-\frac{Q(-t)}{P(-\zeta)}- \sum_{j=0}^\infty \frac{R_j}{(j+1)!} \frac{(\zeta-t)^{j+1}}{P(-\zeta)}\,.
+%%\]
+%%The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations. 
+%%Indeed, a Volterra operator $\volterra$ of the kind described above is expected to have a solution $\psi$ with the following feautures:
+%%\begin{itemize}
+%%    \item it has an $O(\zeta^{\tau_\alpha-1})$ singulairty at $\zeta=0$,
+%%    \item it is of exponential type, meaning that it is $O(e^{\Lambda|\zeta|})$ for some $\Lambda\in\R$, as $\zeta$ grows. 
+%%\end{itemize}
+%%These conditions are just strong enough to ensure that the solution $\psi$ has a well-defined Laplace transform $\Psi=\laplace\psi$, which by construction will satisfy the differential equation $\mathcal{P}\Psi=0$.
 The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-
-Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
+%%
+%%Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
 We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
@@
 In particular, varying the contour of integration of the Laplace transform, so that the base point cooresponds to a root of $P$, we will construct solutions of the correspondent integral equation with a distinguished behaviour.
-
-This is a new approach to solve level $1$ ODEs with irregular singulatiries.
+%%
+%%This is a new approach to solve level $1$ ODEs with irregular singulatiries.
 Indeed, a classical alternative to Borel summability is given by the approach of Ecalle, which uses the Borel transform to turn differential equations to integral (convolution) equations.
 However, his approach to solve integral equations is by perturbation theory~\cite{EcalleIII} amd it have been applied also by other authors~\cite{loday-Remy2011,diverg-resurg-iii}.
-
-Furthermore, the Banach spaces $\singexp{\tau-1}{\Lambda}(\domain)$ are essentially new; in fact a similar definition was given in~\cite{braaksma2006laplace}.
+%%
+%%Furthermore, the Banach spaces $\singexp{\tau-1}{\Lambda}(\domain)$ are essentially new; in fact a similar definition was given in~\cite{braaksma2006laplace}.
 However, \textcolor{cyan}{[say why we are different from Braaksma]}
-\color{black}
-
-\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+%%\color{black}
+%%
+%%\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
 These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
@@
 Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.}
-
-%%\textcolor{blue}{A classical way to solve an ODE with an irregular singularity at infinity is to start with formal solutions, in the shape of ``normal series''~\cite{int-irreg}.
-These series are typicaly divergent, but one can use summability methods to recover analytic solutions from them~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
-The results of this paper are motivated by the desire to find the same analytic solutions more directly, without the use of formal series.
-We do this in Section~\ref{sec:example} for a certain class of level~$1$ ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
-In~\cite{borel_reg}, we show that these solutions match the ones obtained from summability methods.
-Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.%
-%%%%Many classical differential equations, including the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
-%%}
-
-In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+%%
+%% ---------
+%%In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
-\begin{align*}
-\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
-\end{align*}
-where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+%%\begin{align*}
+%%\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
+%%\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
+%%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+%%\end{align*}
+%%where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.
-
+%%
 \color{blue}
@@
 %%Functions with the desired analytic properties form a Banach space of the form $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}, so we can use the contraction mapping theorem to prove that $\psi_\alpha$ exists and is un
-\color{violet}
-\begin{itemize}
-\item Unlike differential operators, integral operators on the position domain can be turned into differential operators on the position domain without boundary terms.
-\item {[Should we say this?]} Working in weighted $L^\infty$ spaces automatically shows that solutions are of exponential type, so their Laplace transforms are well-defined.
-In summability methods, this is the most challenging step.
-\item Linked to \'{E}calle's formal methods.
-\item Function spaces are used by Braaksma.
-\end{itemize}
-\color{black}
-
-%%The existence and uniqueness of such a solution $\psi_\alpha$ follows from the more general existence and uniqueness result stated in Section~\ref{sec:results}.
-
-%%Our goal is to prove the existence and uniqueness of $\psi_\alpha$. We will achieve it by proving a more general existence and uniqueness result, stated in Section~\ref{sec:results}.
-
-%%, by embodying the conditions on $\psi_\alpha$ in a Banach space of holomorphic functions---the space $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-We will apply our results to level $1$ differential equations (of the kind described above) in Section~\ref{sec:example}.
-
-%%The first condition gives the Laplace transform of $\laplace_{\zeta,\alpha}\psi_\alpha$ the desired asymptotics, and the second condition ensures that $\laplace_{\zeta,\alpha}$ is well-defined.
-
-%%Both conditions ensure that $\laplace_{\zeta,\alpha}$ is well-defined, and in addition the first one gives $\laplace_{\zeta,\alpha}\psi_\alpha$ the desired asymptotics.
-
-%%For this kind of ODE, the special resummed solutions described earlier are indexed by the roots of $P$.
-In fact, they turn out to be the Laplace transforms $\Psi_\alpha = \laplace \psi_\alpha$ of holomorphic functions $\psi_\alpha$ associated with the roots $-\alpha$ of $P$.
-\color{black}
-
-%%see that the equation $\mathcal{P}\Phi = 0$ in the frequency domain corresponds to a holomorphic Volterra equation $\hat{\mathcal{P}}\varphi = 0$ on the position domain, where $\Phi = \laplace \varphi$.}
-
-%%Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino}\cite[Section 2.4]{sternin1995borel}.
-
-\color{violet}
-%%\begin{itemize}
-%%\item Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-%%\item Both resurgence and summability methods pick out special solutions on the position domain, characterized by the way they blow up at the regular singularities.
-%%\item The properties of Volterra equations are especially well-suited to studying these singular solutions.
-%%\begin{itemize}
-%%\item Unlike differential operators, integral operators on the position domain can be turned into differential operators on the position domain without boundary terms.
-%%\item {[Should we say this?]} Working in weighted $L^\infty$ spaces automatically shows that solutions are of exponential type, so their Laplace transforms are well-defined.
-In summability methods, this is the most challenging step.
-%%\end{itemize}
-%%\item {[Alternate phrasing]} These special singular solutions are troublesome for standard Laplace transform techniques.
-%%\begin{itemize}
-%%\item One would traditionally turn the Volterra operator on the position domain into a differential operator by post-composing with derivatives.
-However, this comes at the cost of introducing boundary terms.
-For singular solutions, making sense of the boundary terms is not straightforward.
-%%\end{itemize}
-%%\end{itemize}
-\color{black}
-\textcolor{orange}{Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
+%%
+%%\color{black}
+%%\textcolor{orange}{Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
 In Section~\ref{sec:example}, we will see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
 This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.}
-\begin{verify}
-[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
+%%\begin{verify}
+%%[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
 This example works because the linear density of the beam and the second moment of area perpemdicular to the vibration direction are proportional, so they both end up in the $P(\partial)$ term.]\end{verify}
-
-From our experience with solving level~1 differential equations by \textcolor{magenta}{Borel summation}, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
+%%
+%%From our experience with solving level~1 differential equations by \textcolor{magenta}{Borel summation}, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
 Suppose \textcolor{red}{we have chosen} the position variable $\zeta$ is chosen so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
 Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
-\begin{itemize}
-\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
-\item It is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
-\end{itemize}
-These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
+%%\begin{itemize}
+%%\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
+%%\item It is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
+%%\end{itemize}
+%%These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
 The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-
-Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
+%%
+%%Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
 We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
@@
 \subsection{Convention for coordinates}
+Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain.
+Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$.
+We therefore expect our results to be used in calculations involving multiple coordinates.
+The ways we talk about points, functions, and coordinates are meant to promote clarity in calculations of this kind.
+
+Functions---like the coordinates $\zeta$ and $\zeta_\alpha$, and the solutions $\psi_\alpha$---
+
+%%%For convenience, we state and prove our main results for a Volterra equation with a regular singularity at $\zeta = 0$. However, we are careful
+
+%%Our notation for points and coordinates are meant to minimize confusion when switching back and forth between coordinates.
+
+%%In the motivating example, equation~\eqref{eqn:intro-use-dict}, the solution $\psi_\alpha$ associated with a root $-\alpha$ of $P$ is most easily expressed in terms of the translated position coordinate $\zeta_\alpha = \zeta - \alpha$.
+
+%%In the motivating example of equation~\eqref{eqn:intro-use-dict}, it is useful to switch back and forth between the coordinates $\zeta_\alpha = \zeta - \alpha$ associated with different roots $-\alpha$ of $P$.
+We have therefore written our results and proofs in a way that makes
+
 \textcolor{orange}{[\ldots]}
@@
 \begin{itemize}
-\item Don't mention translation surfaces.
+\item Can mention translation surfaces, but don't define.
 \item Maybe talk about branched covers of the complex plane, which we need to describe the singular solutions?
+\item Can identify the number $\zeta(a)$ with the point $a$.
+%%\item In the theory of resurgence, the position domain is often a Riemann surface $B$ with a branched covering map $B \to \C$.
 \end{itemize}
@@
 \begin{itemize}
-    \item mention that $\zeta=0$ is not special, and having in mind the application to ODEs, we need to consider different coordinates.
-Thus, we think it's appropriate to use the coordinate free notation.
+\item mention that $\zeta=0$ is not special, and having in mind the application to ODEs, we need to consider different coordinates. Thus, we think it's appropriate to use the coordinate free notation.
 \item Coordinate free notation is easy to generalize to translation surfaces.
 \item If the reader is familiar with the analysis notation, he should read $\zeta(a)$ as $\zeta$, and the variable inside the integral as ?? 
+\begin{itemize}
+\item You can think of $f$ as the pullback $f(\zeta)$, and then $f(\zeta(\zeta - \alpha))$
+\item $f:M\to N$, $\zeta:M\to\C$, $\phi:N\to\C$, 
+    \item A tangent vector at $x \in M$ is a linear map $v \maps T_x^*M \to \C$.
+Similarly, a tangent vector at $f(x) \in N$ is a linear map $T_{f(x)}^*N \to \C$.
+Define $f_* v \cdot d_x\phi = v \cdot f^* d_{f(x)}\phi = v \cdot d_x(f^* \phi)$ for all functions $\phi$ on $N$.
+    \item $f:M\to\C$, $\zeta:M\to\C$
+    \item if you write $f(a)=\zeta(a)^2+3$, $a\in M$ \textcolor{orange}{[we would write this as $f = \zeta^2 + 3$]}
+    \item if $M=\C$
+    \item $f = \zeta^2 + 3$. Equivalently $f = \big((\zeta - 5) + 5\big)^2 + 3$, or.
+    \item $f=\zeta^2+3$ or equivalently $f(\zeta)=\zeta^2+3$
+    \begin{itemize}
+    \item When you evaluate $f$ at $\zeta = 0$, you get $0^2 + 3 = 3$.
+    \item When you evaluate $f$ at $\zeta = 2$, you get $2^2 + 3 = 7$.
+    \end{itemize}
+    \item $\zeta-\alpha \longrightarrow f(\zeta-\alpha)=(\zeta-\alpha)^2+3$
+    \item $\zeta=0$, $f(0)=3$
+    \begin{itemize}
+    \item Suppose $\alpha = 5$. \item When you evaluate $f(\zeta_5 + 5)$ at $\zeta_5 = 0$, you get $5^2 + 3 = 28$.
+    \item Suppose $\alpha = 5$. \item When you evaluate $f(\zeta - 5)$ at $\zeta = 0$, you get $(-5)^2 + 3 = 28$.
+    \end{itemize}
+\end{itemize}
 \end{itemize}
@@
 \textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
-Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{brown}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$ with the compact-open topology.
+Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{brown}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
 This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
@@
     We define the normed space
-    \[\singexp{0}{\Lambda}(\domain):=\{ f\in\holo(\domain)\,\vert\, \|f\|_{0,\Lambda}<+\infty\}\,.\]
+    \[\singexp{0}{\Lambda}(\domain):=\{ f\in\holo(\domain) : \|f\|_{0,\Lambda}<+\infty\}\,.\]
 \end{definition}
@@
 \end{proof}
-As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.\color{brown}\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
 We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
+\color{blue}
 \begin{definition}
-    Let $\sigma, \Lambda\in\R$. We define the space
+For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ as the union
+\[ \bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain) \]
+equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
+\end{definition}
+\color{brown}
+\begin{definition}
+    Let $\sigma \in \R$. We define the space
     \[\singexpalg{\sigma}(\domain):=\bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain)\,,\]
-    equipped with the finest topology that makes continuos the inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$. 
+    equipped with the finest topology that makes continuous the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$. 
 \end{definition}
-The finest topology that makes the inclusion continuos is \textcolor{cyan}{[...]}
 \color{red} Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
@@
 \subsection{Overview}
+\color{blue}
+\textcolor{orange}{[Revise and implement]}
 \color{red}
@@
 
+\color{brown}
+In this section, we prove the results outlined in Section~\ref{sec:results}, demonstrating a method for solving the singular Voletrra equation $f=\volterra f$.
+
+We start by constructing the prototype solution $f_0$ of $f=\softpart f$, and show in Section~\ref{sec:proto-construction-regularity} that $f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
+
+In Section~\ref{sec:image under soft_part}, we show that the perturbation $\softpart$ has a smoothing effect on $f_0$, reducing the power-law singularity at $\zeta=0$.
+In particular, it turns out that $\softpart f_0\in\singexpalg{\tau-1+\gamma}(\domain)$.
+\color{black}
+
 \textcolor{red}{Now we know that} Therefore $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
@@
 This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
-
-\color{brown}
-In this section, we prove the results outlined in Section~\ref{sec:results}, demonstrating a method for solving the singular Voletrra equation $f=\volterra f$.
-
-We start by constructing the prototype solution $f_0$ of $f=\softpart f$, and show in Section~\ref{sec:proto-construction-regularity} that $f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
-
-In Section~\ref{sec:image under soft_part}, we show that the perturbation $\softpart$ has a smoothing effect on $f_0$, reducing the power-law singularity at $\zeta=0$.
-In particular, it turns out that $\softpart f_0\in\singexpalg{\tau-1+\gamma}(\domain)$.
-\color{black}
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 
-By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} there exists a radius $\delta>0$ and a constant $C$ such that
+By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
@@
 It follows, as discussed above, that $\hardpart \solproto = \solproto$.
+\color{orange}
+For $\tau\in\C$
+\begin{equation}
+    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\frac{\zeta(a)}{\zeta(b)}\right)
+\end{equation}
+so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate".
+I'm not very confortable with rotations, so probably I'll not add this complication.
+I'm also afraid we should be more carefull with these mooving domains, if we allow rotations.
+So maybe better not make things too complicated for the sake of generality.
+We have a good list of examples that fit in our pictures.
+\color{black}
 \end{proof}
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, \textcolor{red}{for some constant $M$} there is some $M\in\C$ for which,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then\textcolor{red}{, for some constant $M$} \textcolor{blue}{there is some $M\in\C$} for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \end{align*}
-Since $\zeta(b)^{-\tau}$ is a constant, \textcolor{red}{the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want} the factor $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ is proportional to $\zeta^{\tau-1}$.
+\textcolor{blue}{Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.}
+\textcolor{pink}{Since $\zeta(b)^{-\tau}$ is a constant, \textcolor{red}{the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want} the factor $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ is proportional to $\zeta^{\tau-1}$.}
 
@@
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$.
-\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} The integral defines Euler's beta function, so
+\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral in the last step is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-\textcolor{red}{Our assumptions that} Since $\gamma > 0$ and $\sigma > -1$, \textcolor{red}{ensure that} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\textcolor{red}{Our assumptions that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} \textcolor{red}{ensure that} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 for any integration path that stays within $\near$.
-\textcolor{red}{Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path} \textcolor{brown}{Since $\near$ \textcolor{magenta}{is star-shaped [why?]} at $\zeta=0$, the path of integration can be chosen to be a segment } $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+\textcolor{blue}{Since $\domain$ is star-shaped around $\zeta = 0$, so is $\near$.
+\textcolor{orange}{[\ldots]}} \textcolor{red}{Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path} \textcolor{brown}{Since $\near$ \textcolor{magenta}{is star-shaped [why?]} at $\zeta=0$, the path of integration can be chosen to be a segment } $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 \begin{align*}
@@
 By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} there is some $M\in\R_{>0}$ for which
-\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
-for all $a \in \far$.
-Note that only the first argument of $k$ has its domain restricted\textcolor{red}{; this bound holds throughout $\domain$ in the second argument}, \textcolor{violet}{[rephrase]} while the second varies in $\domain$.
-Applying this bound, we \textcolor{red}{learn} that
+\textcolor{red}{\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]}
+\textcolor{blue}{\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]}
+\textcolor{blue}{for all $a \in \far$ and $a' \in \Omega$.}\textcolor{red}{for all $a \in \far$.} \textcolor{pink}{Note that only the first argument of $k$ has its domain restricted\textcolor{red}{; this bound holds throughout $\domain$ in the second argument}, \textcolor{violet}{[rephrase]} \textcolor{brown}{while the second varies in $\domain$}.} Applying this bound, we \textcolor{red}{learn} that
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
@@
 Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
-Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
-
-To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.\color{black} \textcolor{violet}{[condense and simplify]}
+
+To see that the fixed point is \textcolor{red}{still} unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem. 
-\textcolor{cyan}{[I'm confused by the next part of the argument]}
 \color{black}
@@
 Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the \textcolor{red}{other conditions we assume in} assumptions of {\em Theorem~\ref{thm:general_volterra}}.
-Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} for $\tau<\rho<\tau+\min(\gamma,\epsilon,1)$, the Equation~\eqref{eqn:orig-homog}
+Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} \textcolor{brown}{for $\tau<\rho\le\tau+\min(\gamma,\epsilon,1)$}, the Equation~\eqref{eqn:orig-homog}
 \textcolor{red}{
@@
 \textcolor{red}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
-This substitution leads to several other reinterpretations, summarized below.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} \textcolor{brown}{To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} This substitution leads to several other reinterpretations, summarized below.
 

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Restore first paragraphs of motivation
The paragraphs are taken from commit 9663080. They seem to have gotten
lost in the next commit, f2bc12d.

@@
 \subsection{Motivation}\label{motivation}
-%%\color{brown}Classically, ODEs with an irregular singularity at infinity can be solved formally by ``normal series'' solutions~\cite{int-irreg}.
-These series are typicaly divergent, but summability methods allow to recover analytic solutions from them~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
-Remarkably, these ``resummed" analytic solutions are characterized by their asymptotic behaviour at infinity.
-In particular, under suitable assumptions on the ODE, a frame of solutions can be constructed by ``resumming" a frame of formal ones.
-The results of this paper are motivated by the desire to find the same frame of analytic solutions more directly, without the use of formal series.
-We do this in Section~\ref{sec:example} for a certain class of \emph{level}-1 ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
-In~\cite{borel_reg}, we show that these solutions match the ones obtained from summability methods.
-Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.
-
-%%In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a \textcolor{cyan}{real} ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$
-%%\[\big[\laplace\varphi\big](z):=\int_{\Gamma_{\zeta,0}}e^{-z\zeta}\varphi\; d\zeta \,,\]
-%%where $\Gamma_{\zeta,0}$ is a line issuing from $\zeta=0$.
-\begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
-Write $z$ in terms of its real and imaginary parts as $x + iy$.
-Since the integrand is holomorphic with respect to $z$, the operator $\frac{\partial}{\partial\overline{z}} = \frac{1}{2}\left(\frac{\partial}{\partial x} + i\frac{\partial}{\partial x}\right)$ annihilates it.
-Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify}
-%%Through identities like
-%%\begin{align*}
-%%\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-%%\laplace \psi\;\laplace \varphi & = \laplace(\psi * \varphi)\,,%\\
-%%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
-%%\end{align*}
-%where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, 
-%%the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain. 
-%%
-%%For instance, let $\mathcal{P}\Psi=0$ be the level-1 ODE of the kind studied in Section~\ref{sec:example}, with $\mathcal{P}$ being the differential operator 
-%%\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
-%%where $P$ a degree $d$ polynomial with distinct roots, $Q$ a degree $d-1$ polynomial non-vanishing at the roots of $P$, and the series $\sum_{j=0}^\infty R_j z^{-j}$ convergent for $|z|>A>0$.
-If $\Psi=\laplace\psi$, then
-%%\[
-%%\mathcal{P}\Psi=\mathcal{P}\big[\laplace\psi\big]=\laplace\big[\hat{\mathcal{P}}\psi\big]
-%%\]
-%%where $\hat{\mathcal{P}}$ is the integral operator 
-%%\[
-%%\hat{\mathcal{P}}\psi=P(-\zeta)\psi+\int_{0}^\zeta Q(-t)\psi\; dt+\int_0^\zeta \sum_{j=0}^\infty \frac{R_j}{(j+1)!} (\zeta-t)^{j+1}\psi\; dt \,.
-%%\]
-%%Therfore, the differential equation $\mathcal{P}\Psi=0$ is turned into the integral equation 
-%%\[\psi=\volterra\psi\,\]
-%%where $\volterra$ is the Volterra operator with kernel
-%%\[
-%%k(\zeta,t):=-\frac{Q(-t)}{P(-\zeta)}- \sum_{j=0}^\infty \frac{R_j}{(j+1)!} \frac{(\zeta-t)^{j+1}}{P(-\zeta)}\,.
-%%\]
-%%The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations. 
-%%Indeed, a Volterra operator $\volterra$ of the kind described above is expected to have a solution $\psi$ with the following feautures:
-%%\begin{itemize}
-%%    \item it has an $O(\zeta^{\tau_\alpha-1})$ singulairty at $\zeta=0$,
-%%    \item it is of exponential type, meaning that it is $O(e^{\Lambda|\zeta|})$ for some $\Lambda\in\R$, as $\zeta$ grows. 
-%%\end{itemize}
-%%These conditions are just strong enough to ensure that the solution $\psi$ has a well-defined Laplace transform $\Psi=\laplace\psi$, which by construction will satisfy the differential equation $\mathcal{P}\Psi=0$.
-The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-%%
-%%Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
-We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-We will apply our results to level $1$ differential equations (of the kind described above) in Section~\ref{sec:example}.
-In particular, varying the contour of integration of the Laplace transform, so that the base point cooresponds to a root of $P$, we will construct solutions of the correspondent integral equation with a distinguished behaviour.
-%%
-%%This is a new approach to solve level $1$ ODEs with irregular singulatiries.
-Indeed, a classical alternative to Borel summability is given by the approach of Ecalle, which uses the Borel transform to turn differential equations to integral (convolution) equations.
-However, his approach to solve integral equations is by perturbation theory~\cite{EcalleIII} amd it have been applied also by other authors~\cite{loday-Remy2011,diverg-resurg-iii}.
-%%
-%%Furthermore, the Banach spaces $\singexp{\tau-1}{\Lambda}(\domain)$ are essentially new; in fact a similar definition was given in~\cite{braaksma2006laplace}.
-However, \textcolor{cyan}{[say why we are different from Braaksma]}
-%%\color{black}
-%%
-%%\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+\color{blue}
+\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
 These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
@@
 Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.}
-%%
-%% ---------
-%%In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+
+In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 Using the comparison version of Leibniz's rule for improper integrals (Theorem~11.10 of A First Course in Real Analysis, by Protter and Morrey) with $\frac{\partial}{\partial x}$ and $\frac{\partial}{\partial y}$, we see that $\frac{\partial}{\partial\overline{z}}$ annihilates the whole integral.]\end{verify} Through identities like
-%%\begin{align*}
-%%\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-%%\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-%%z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
-%%\end{align*}
-%%where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+\begin{align*}
+\frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
+\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
+z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+\end{align*}
+where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.
-%%
-\color{blue}
+
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
@@
 We seek a solution $\psi_\alpha$ which
-
-%%The integral operator $\partial^{-1}$ in equation~\ref{eqn:intro-use-dict} then becomes the integration $\partial^{-1}_{\zeta, \alpha}$ based at $\zeta = \alpha$.
-
-%%Equation~\ref{eqn:intro-use-dict} then uses the integral operator $\partial_{\zeta, \alpha}$ based at $\zeta = \alpha$.
-
-%%We then hope for the resulting version of equation~\eqref{eqn:intro-use-dict} to have a solution $\psi_\alpha$ with the following features: \textcolor{orange}{We then look for a solution $\psi_\alpha$ of (the resulting version of equation~\ref{eqn:intro-use-dict}) which:}
-
-%%take the Laplace transform using $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
-We must then solve equation~\eqref{eqn:intro-use-dict}, with the integration base point similarly shifted to $\zeta = \alpha$,
-
-%%find a solution of equation~\eqref{eqn:intro-use-dict} with the following features:
 \begin{itemize}
@@
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-
-%%The existence and uniqueness of $\psi_\alpha$, stated as Theorem~\ref{thm:example}, follow from \textcolor{orange}{This gives} an existence and uniqueness result for
-
-%%The technique we use to solve equation~\eqref{eqn:intro-use-dict} applies to a wider class of regular singular Volterra equations. This paper focuses on stating and proving it in general,
-
-%%The Banach spaces we use also appear in the work of Braaksma, who uses them to study resummation for systems of ODEs whose coefficients are Laplace transforms.
-
-%%They also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
-This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-
-%%\textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
-However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.}
-
-%%%%%%%%
-
-%%Our conditions on $\psi_\alpha$ define a Banach space of holomorphic functions, as discussed in Section~\ref{fn-spaces}.
-
-%%Our conditions place $\psi_\alpha$ in the Banach space $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}, where we can use the contraction mapping theorem to prove the existence and uniqueness of solutions for equations like~\ref{eqn:intro-use-dict}.
-
-%%Functions with the desired analytic properties form a Banach space of the form $\singexp{\tau_\alpha-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}, so we can use the contraction mapping theorem to prove that $\psi_\alpha$ exists and is un
-%%
-%%\color{black}
-%%\textcolor{orange}{Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we will see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
-This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.}
-%%\begin{verify}
-%%[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
-This example works because the linear density of the beam and the second moment of area perpemdicular to the vibration direction are proportional, so they both end up in the $P(\partial)$ term.]\end{verify}
-%%
-%%From our experience with solving level~1 differential equations by \textcolor{magenta}{Borel summation}, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
-Suppose \textcolor{red}{we have chosen} the position variable $\zeta$ is chosen so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
-Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
-%%\begin{itemize}
-%%\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
-%%\item It is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
-%%\end{itemize}
-%%These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
-The first condition also implies that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-%%
-%%Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
-We will achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-\textcolor{orange}{We will apply our results to level $1$ differential equations in Section~\ref{sec:example}.} \textcolor{violet}{[Mention Theorem~\ref{thm:example} and Lemma~\ref{lem:use-dict}]}
-\color{blue}
 \subsection{Convention for coordinates}

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Revise the proof of proposition `exp-complete`
Also, revise other passages for conciseness and formality.

@@
 Since integral operators on the position domain correspond directly to multiplication operators on the frequency domain, with no need to worry about initial values, we know immediately that $\laplace_{\zeta, \alpha} \psi_\alpha$ satisfies equation~\eqref{eqn:intro-level-1}, even when $\psi_\alpha$ blows up at $\zeta = \alpha$.
-By isolating the features of equation~\ref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get our main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
+By isolating the features of equation~\ref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get the main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
 
 Our results build on known methods for solving differential equations with irregular singularities.
-Our focus on integral equations in the position domain, and the singularities of their solutions, recalls \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
+Our focus on integral equations in the position domain, and the singularities of their solutions, \textcolor{orange}{recalls [reword]} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
 One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.
@@
 
-Functions---like the coordinates $\zeta$ and $\zeta_\alpha$, and the solutions $\psi_\alpha$---
-
-%%%For convenience, we state and prove our main results for a Volterra equation with a regular singularity at $\zeta = 0$. However, we are careful
-
-%%Our notation for points and coordinates are meant to minimize confusion when switching back and forth between coordinates.
-
-%%In the motivating example, equation~\eqref{eqn:intro-use-dict}, the solution $\psi_\alpha$ associated with a root $-\alpha$ of $P$ is most easily expressed in terms of the translated position coordinate $\zeta_\alpha = \zeta - \alpha$.
-
-%%In the motivating example of equation~\eqref{eqn:intro-use-dict}, it is useful to switch back and forth between the coordinates $\zeta_\alpha = \zeta - \alpha$ associated with different roots $-\alpha$ of $P$.
-We have therefore written our results and proofs in a way that makes
+We
+
+%%We will typically speak in terms of functions on spaces, not functions of coordinates.
+
+%%Functions---like the coordinates $\zeta$ and $\zeta_\alpha$, and the solutions $\psi_\alpha$---will be defined directly on the position or frequency domain, not as functions of a particular coordinate.
 
@@
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
-\begin{equation}\label{eq:volterra-general}
-f = \volterra f  
-\end{equation}
+\[ f = \volterra f \]
 has a unique solution $f$ in the affine subspace
@@
 
-We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation~\eqref{eq:volterra-general} \textcolor{red}{we want to solve} as an inhomogeneous equation in a more regular space.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting \textcolor{blue}{the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$} as an inhomogeneous equation in a more regular space.
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
@@
 \[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) \]
-when $\rho > \tau$ is \textcolor{red}{low enough} sufficiently small, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
+when $\rho > \tau$ is \textcolor{blue!50}{low enough}, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
 \end{rmk}
@@
 \subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
-Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
+Throughout this paper, as described in Section~\ref{motivation}, the \textcolor{magenta}{``}position\textcolor{magenta}{'' [why are these quote marks nencessary?
+we've already introduced the term ``position'']} variable $\zeta$ will be the standard coordinate on $\C$.
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
 \textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
-Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{brown}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
+Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
 This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
@@
 That means the inclusion is continuous.
+\color{blue}
+\begin{proposition}\label{exp-complete}
+The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
+\end{proposition}
+\begin{proof}
+Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\Omega)$.
+This sequence is Cauchy in $\holo(\Omega)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$.
+Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
+
+The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\Omega)$ implies pointwise convergence, it follows that $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
+This reasoning shows that $f_1, f_2, f_3, \ldots$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$.
+It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
+\begin{align*}
+|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_n| \\
+& \le r + \|f_n\|_{\sigma,\Lambda}
+\end{align*}
+for the corresponding $n$, so $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f|$ is bounded.
+\end{proof}
 \color{red}
-\begin{proposition}\label{exp-complete}
+\begin{proposition}%%\label{exp-complete}
 The space $\singexp{0}{\Lambda}(\domain)$ is complete.
@@
 for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
-\end{proof}
-\color{black}
+\end{proof}\color{black}
+
 Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
@@
 \[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
-Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ greatly simplifies the calculation of $\hardpart \solproto$. For each $a \in \domain$,
+Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \textcolor{blue}{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
 \begin{align*}
@@
 \end{align*}
-Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \chi = 0$.
-
-By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a radius $\delta>0$ and a constant $C$ such that
+\textcolor{blue}{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.
+
+By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
@@
 \end{equation}
-whenever $|\zeta| < \delta$. \textcolor{red}{We can take advantage of} We use this bound by rewriting the integral in the definition of $\chi$:
+whenever $|\zeta| < \delta$. \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} by rewriting the integral in the definition of $\chi$:
 \begin{align*}
@@
 \begin{equation}
-    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\frac{\zeta(a)}{\zeta(b)}\right)
+    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
 \end{equation}
@@
 \begin{proof}
-Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that Inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta| < \delta$.
+Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta| < \delta$.
 The subsequent argument, which we used to show that $\lim_{\zeta \to 0} \chi = 0$, actually supports a stronger conclusion: it shows that $|\chi| \lesssim |\zeta|^\tau$ on the region $|\zeta| < \delta$.
@@
 
-By Proposition~\ref{prop:asymptotic at zero}, \textcolor{red}{we can find} there exists a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
-No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so we will have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+By Proposition~\ref{prop:asymptotic at zero}, \textcolor{blue}{there is} a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, \textcolor{blue}{$e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so} $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
 
@@
 \end{align*}
-over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$.
-\textcolor{red}{One consequence is that} \textcolor{violet}{[is this really an equivalent statement?
-check again]} \textcolor{brown}{Namely,} for some $c_\Delta > 0$, we have
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. \textcolor{blue}{The last bound means that for some $c_\Delta > 0$,}
 \[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
 whenever $|\zeta(a)| \ge \delta$.
-Applying this bound along the diagonal in $\domain^2$, we \textcolor{red}{learn} get that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we \textcolor{blue}{conclude} that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
 On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
@@
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
-at $\zeta = 0$. \textcolor{red}{Like we did} As in the proof of Theorem~\ref{thm:basic_volterra}, we \textcolor{red}{reason} deduce that
+at $\zeta = 0$. \textcolor{blue}{As in} the proof of Theorem~\ref{thm:basic_volterra}, we \textcolor{blue}{compute}
 \begin{align*}
@@
 
-\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} Then, Condition \eqref{cond:reg-p} implies that
+\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} \textcolor{pink}{Then,} Condition \eqref{cond:reg-p} implies that
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, let us look at the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} there exists a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, let us look at the exponential factor.
+By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 
-Combining the arguments above, we \textcolor{red}{learn} find that
+\textcolor{blue}{Together, the arguments above show that}\textcolor{pink}{Combining the arguments above, we \textcolor{red}{learn} \textcolor{blue}{find} that}
 \begin{align*}
@@
 \end{align*}
-at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
+at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$.
+Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we \textcolor{blue}{reach} the desired result.
 \end{proof}
@@
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$.
-\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral in the last step is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-\textcolor{red}{Our assumptions that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} \textcolor{red}{ensure that} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\textcolor{red}{Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-\begin{proposition}\label{prop:whole-ker-near-bound}
+\color{blue}\begin{proposition}\label{prop:whole-ker-near-bound}
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
+Then, for any $\sigma > \tau$, there is a neighborhood $\Sigma \subset \Omega$ of $\zeta = 0$ with the property that
+\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
+for all $a, a' \in \Sigma$.
+\end{proposition}\color{black}
+\begin{proposition}%%\label{prop:whole-ker-near-bound}
 \color{red}
@@
 \begin{proof}
-First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{red}{can} ensure that
+First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{blue!50}{can} ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
@@
 
-To see that the fixed point is \textcolor{red}{still} unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+To see that the fixed point is \textcolor{red}{still} unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 \end{proof}
-\begin{proposition}\label{prop:alt-general_volterra}
+\color{blue}\begin{proposition}\label{prop:alt-general_volterra}
+Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}.
+Then, for each $\rho \in (\tau,\;\tau + \min\{\gamma, \epsilon, 1\}]$, the equation
+\[f = \volterra f\]
+has a unique solution $f$ in the affine subspace
+\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
+of the space $\singexpalg{\tau-1}(\domain)$.
+\end{proposition}
+\color{pink}\begin{proposition}%%\label{prop:alt-general_volterra}
 Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the \textcolor{red}{other conditions we assume in} assumptions of {\em Theorem~\ref{thm:general_volterra}}.
-Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} \textcolor{brown}{for $\tau<\rho\le\tau+\min(\gamma,\epsilon,1)$}, the Equation~\eqref{eqn:orig-homog}
+Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} \textcolor{brown}{for $\tau<\rho\le\tau+\min(\gamma,\epsilon,1)$}, equation~\eqref{eqn:orig-homog}
 \textcolor{red}{
@@
 \[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]}
-\end{proposition}
-
+\end{proposition}\color{black}
+%
 \begin{proof}
@@
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
-Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{red}{can work out} find that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{blue}{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
 Hence,
@@
 
-We \textcolor{red}{can} now state and prove the main result of this section.
+We \textcolor{blue!50}{can} now state and prove the main result of this section.
 Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Work on definitions of weighted L-infinity spaces
Also do other revisions, like condensing the outline of the main argument.

@@
 This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
-The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
+\textcolor{orange}{By the maximum principle and the connectedness of $\domain$, each of the seminorms $\sup_K |\cdot|$ is actually a norm.} The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
 \color{red}
@@
 That means the inclusion is continuous.
-\color{brown}
+\par\color{blue}
+\begin{definition}
+For any $\sigma, \Lambda \in \R$, let
+\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
+be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ \textcolor{orange}{functions bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$}, equipped with the norm
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
+\end{definition}
+With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K |\zeta|^\sigma e^{\Lambda |\zeta|}$.
+That means the inclusion is continuous.
+%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
+\par\color{brown}
 For $\Lambda\in\R$, let 
@@
 \begin{proof}
-Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\Omega)$.
-This sequence is Cauchy in $\holo(\Omega)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$.
-Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
-
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, it follows that $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
+Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\domain)$.
+This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$.
+Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
+
+The Cauchy property in $\singexp{\sigma}{\Lambda}(\domain)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
 This reasoning shows that $f_1, f_2, f_3, \ldots$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$.
@@
 \begin{align*}
-|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f_n| \\
+|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
 & \le r + \|f_n\|_{\sigma,\Lambda}
 \end{align*}
-for the corresponding $n$, so $|\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f|$ is bounded.
+for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
 \end{proof}
@@
 
-Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
-\color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
+\textcolor{pink}{Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.} \color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
 Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
@@
 \color{black}
-\begin{proposition}
+\color{pink}\begin{proposition}
 The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
@@
 \end{proof}
-As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
 We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
+
+\textcolor{violet}{As we mentioned in Section~\ref{sec:fn-space-defs} [now removed]}\textcolor{pink}{, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.}\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} \textcolor{pink}{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}}
 \color{blue}
@@
 \begin{proposition}\label{prop:inclus-lt-pow-alg}
-When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
+When $\sigma' > \sigma$, there is a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
 \end{proposition}
@@
 \color{blue}
-\textcolor{orange}{[Revise and implement]}
-\color{red}
+In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+
+We first construct the prototype solution $\solproto$ from the kernel of $\hardpart$.
+We show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+
+We then study how the perturbation $\softpart$ affects $\solproto$.
+We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
+\par\textcolor{orange}{[Keep revising]} \color{red}
 The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
@@
 
-\textcolor{red}{Now we know that} Therefore $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+\textcolor{red}{Now we know that} \textcolor{brown}{Therefore} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
 To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
@@
 \end{equation}
-whenever $|\zeta| < \delta$. \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} by rewriting the integral in the definition of $\chi$:
+whenever $|\zeta| < \delta$.
+\textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:} \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} \textcolor{pink}{by rewriting the integral in the definition of $\chi$:}
 \begin{align*}

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Go back to introducing sing-exp spaces in two stages

@@
 % symbology
+\newcommand{\N}{\mathbb{N}}
 \newcommand{\Z}{\mathbb{Z}}
@@
 Since integral operators on the position domain correspond directly to multiplication operators on the frequency domain, with no need to worry about initial values, we know immediately that $\laplace_{\zeta, \alpha} \psi_\alpha$ satisfies equation~\eqref{eqn:intro-level-1}, even when $\psi_\alpha$ blows up at $\zeta = \alpha$.
-By isolating the features of equation~\ref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get the main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
+By isolating the features of equation~\eqref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get the main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
 
@@
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-\subsection{Convention for coordinates}
+\subsection{Formalism for coordinates}
 Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain.
@@
 We therefore expect our results to be used in calculations involving multiple coordinates.
-The ways we talk about points, functions, and coordinates are meant to promote clarity in calculations of this kind.
-
-We
+Our formalism for points, functions, and coordinates is tailored to such calculations.
+
+From now on, we will carefully respect the distinction between points and coordinates.
+A point is a location in space, while a coordinate is a function on space.
+For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$.
+A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$.
+Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
+
+\textcolor{orange}{[talk about integration]} For a function $\varphi$ defined on a simply connected subset of the position domain,
+
+%%Coordinates, like the frequency coordinate $z$ and the position coordinates $\zeta$ and $\zeta_\alpha$,
 
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound \textcolor{red}{on how fast $\softker$ grows away from the diagonal} to the growth of $\softker$ away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound \textcolor{red}{on how fast $\softker$ grows away from the diagonal} \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{red}{For some constant} There exists a constant $\gamma > 0$, \textcolor{red}{we have} such that
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{red}{For some constant $\gamma > 0$, we have} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{equation}
-Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
+Changing the base point $b \in \domain$ \textcolor{blue}{only} multiplies $f_0$ by a non-zero constant.
 \end{theorem}
@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} it is guaranteed that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
+With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
 The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
@@
 %
-\textcolor{red}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated}, but its regular singularity at $\zeta = 0$ stays essentially the same.
+\textcolor{red}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated}, but its regular singularity at $\zeta = 0$ \textcolor{violet}{stays [make previous part of sentence consistent]} essentially the same.
 We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
@@
 In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
-\textcolor{cyan}{I'm confused by this remark too.}
+\textcolor{orange}{[Place in a remark and prove in a proposition, as with the remark stating the result of Proposition~\ref{prop:alt-general_volterra}.]}
 \end{rmk}
@@
 \subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
-Throughout this paper, as described in Section~\ref{motivation}, the \textcolor{magenta}{``}position\textcolor{magenta}{'' [why are these quote marks nencessary?
-we've already introduced the term ``position'']} variable $\zeta$ will be the standard coordinate on $\C$.
+Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
-\textcolor{red}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
-Give $\cont(\domain)$ the compact-open topology, recalling that this} \textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
+\textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
 This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
-\textcolor{orange}{By the maximum principle and the connectedness of $\domain$, each of the seminorms $\sup_K |\cdot|$ is actually a norm.} The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
+
+The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
+\textcolor{blue}{We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.}
+%%Within $\holo(\domain)$, we define a normed subspace consisting of functions which are uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
 \color{red}
@@
 \par\color{blue}
+\begin{definition}\label{def:exp}
+For any $\Lambda \in \R$, let
+\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
+be the subspace consisting of functions $f$ with $f \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
+\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
+\end{definition}
+With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
+That means the inclusion is continuous.
+%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
+\begin{rmk}
+The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$.
+A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+Definition~\ref{def:exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
+We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
 \begin{definition}
@@
 \[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
-be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ \textcolor{orange}{functions bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$}, equipped with the norm
+be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
 \[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
 \end{definition}
-With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K |\zeta|^\sigma e^{\Lambda |\zeta|}$.
-That means the inclusion is continuous.
-%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
+The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
 \par\color{brown}
@@
 \begin{proof}
-Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{\sigma}{\Lambda}(\domain)$.
+Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$.
 This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$.
@@
 Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
-This reasoning shows that $f_1, f_2, f_3, \ldots$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$.
+This reasoning shows that $(f_j)_{j \in \N}$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$.
 It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
@@
 \end{proof}
-One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
+\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} Taking the union of these spaces over all $\Lambda \in \R$, we get the subspace that contains all exponential-type functions which are bounded by constant multiples of $|\zeta|^\sigma$ near zero.}
 

### 2024-04-30 sima/reg-sing-volterra_sima.tex
Revise inclusions between sing-exp spaces

@@
 \usetikzlibrary{fadings}
+\usetikzlibrary{cd}
 
@@
 The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-\textcolor{blue}{We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.}
-%%Within $\holo(\domain)$, we define a normed subspace consisting of functions which are uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
-\color{red}
-Fixing a real constant $\Lambda$, we restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
-With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
-That means the inclusion is continuous.
-\par\color{blue}
-\begin{definition}\label{def:exp}
+\color{blue}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
+\begin{definition}\label{def:unif-exp}
 For any $\Lambda \in \R$, let
@@
 A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-Definition~\ref{def:exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
+Definition~\ref{def:unif-exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
 We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
@@
 The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
-\par\color{brown}
-For $\Lambda\in\R$, let 
-\[\|f\|_{0,\Lambda} := \sup_\domain e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
-\begin{definition}
-    We define the normed space
-    \[\singexp{0}{\Lambda}(\domain):=\{ f\in\holo(\domain) : \|f\|_{0,\Lambda}<+\infty\}\,.\]
-\end{definition}
-\begin{rmk}
-    The space $\singexp{0}{\Lambda}(\domain)$ can be seen as the space of functions uniformly bounded by constant multiples of $e^{\Lambda |\zeta|}$.
-\end{rmk}
-With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
-That means the inclusion is continuous.
-\color{blue}
 \begin{proposition}\label{exp-complete}
@@
 for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
-\end{proof}
-\color{red}
-\begin{proposition}%%\label{exp-complete}
-The space $\singexp{0}{\Lambda}(\domain)$ is complete.
-\end{proposition}
-\begin{proof}
-Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$.
-The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too.
-Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
-
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ implies that for any $r > 0$, \textcolor{red}{we can find some} there exists $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, \textcolor{red}{we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$} we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows.
-This shows that \textcolor{red}{our} the sequence $f_k$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-\textcolor{red}{We can also see} In addition, from this argument it follows that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
-\begin{align*}
-e^{-\Lambda |\zeta|}\,|f| & \le e^{-\Lambda |\zeta|}\,|f - f_n| + e^{-\Lambda |\zeta|}\,|f_n| \\
-& \le r + \|f_n\|_{0,\Lambda}
-\end{align*}
-for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
-\end{proof}\color{black}
-
-\textcolor{pink}{Now, let us relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.} \color{red} For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
-Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
-Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we \textcolor{red}{can} generalize Proposition~\ref{exp-complete}:
-\color{brown}
-For $\sigma\in\R$, let 
-\[\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,,\qquad f\in\holo(\domain)\,.\]
-\begin{definition}
-    We define the normed space
-    \[\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega):=\{f\in\holo(\domain)\,\vert \, \|f\|_{\sigma,\Lambda}<+\infty\}\,.\]
-\end{definition}
-\begin{rmk}
-    The above is a space of functions uniformly bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda |\zeta|}$.
-\end{rmk}
-\color{black}
-\color{pink}\begin{proposition}
-The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
-\end{proposition}
-\color{brown}
-\begin{proof}
-Let $\{f_n\}_{n=1}^\infty\subset\singexp{\sigma}{\Lambda}(\domain)$ be a Cauchy sequence.
-The inclusion map $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each norm on $\sup_K |f|$ on $\holo(\domain)$, where $K \subset \Omega$ is compact.
-Hence, $\{f_n\}_{n=1}^\infty$ is a Cauchy sequence also in $\holo(\domain)$.
-The latter being complete~\cite[Proposition~3.5]{fnl-cpx-anal}, the sequence converges to a function $f\in\holo(\domain)$.
-
-By the Cauchy property on $\singexp{\sigma}{\Lambda}(\Omega)$, for any $r > 0$ there exists $n$ such that $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ for every $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, we get that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$, as $k$ grows.
-This implies that the sequence $\{f_n\}_{n=1}^\infty$ converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-In addition, from this argument it follows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
-\begin{align*}
-|\zeta|^{-\sigma}e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
-& \le r + \|f_n\|_{\sigma,\Lambda}
-\end{align*}
-for the corresponding $n$, showing that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
 \end{proof}
@@
 \end{proof}
-\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} Taking the union of these spaces over all $\Lambda \in \R$, we get the subspace that contains all exponential-type functions which are bounded by constant multiples of $|\zeta|^\sigma$ near zero.}
-
-\textcolor{violet}{As we mentioned in Section~\ref{sec:fn-space-defs} [now removed]}\textcolor{pink}{, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.}\footnote{\textcolor{orange}{[footnote moved because of rephrasing above]} \textcolor{pink}{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}}
+%\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
 \color{blue}
-\begin{definition}
-For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ as the union
-\[ \bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain) \]
+
+The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
+The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace.
+The spaces $\singexp{\sigma}{\Lambda}(\domain)$ fit together analogously for other $\sigma \in \R$.
+\begin{definition}\label{def:exp-top}
+For any $\sigma \in \R$, let $\singexpalg{\sigma}(\domain)$ be the union
+\[ \bigcup_{\Lambda \in \R} \singexp{\sigma}{\Lambda}(\domain) \]
 equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
@@
 Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we \textcolor{red}{can} give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
-\color{brown}
 \color{black}
@@
 \end{proposition}
+\color{blue}
 \begin{proof}
-\color{red}
+For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
+\begin{center}
+\begin{tikzcd}[column sep=25mm, labels={inner sep=0.75ex}]
+\singexp{\sigma'}{\Lambda'}(\domain) \arrow[r, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-lt-pow-gt-exp}}"'] & \singexp{\sigma}{\Lambda}(\domain) \arrow[r, hook, "\text{\footnotesize Definition~\ref{def:exp-top}}"'] & \singexpalg{\sigma}(\domain).
+\end{tikzcd}
+\end{center}
+For any $\Lambda'' < \Lambda'$, the inclusions
+\begin{center}
+\begin{tikzcd}[row sep=6mm, column sep=8mm, labels={inner sep=0.75ex}]
+\singexp{\sigma'}{\Lambda''}(\domain) \arrow[rr, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"] \arrow[rd, hook] & & \singexp{\sigma'}{\Lambda'}(\domain) \arrow[ld, hook] \\
+& \singexpalg{\sigma}(\domain)
+\end{tikzcd}
+\end{center}
+%%\begin{center}
+%%\begin{tikzcd}[row sep=2mm, column sep=15mm, labels={inner sep=1ex,}]
+%%\singexp{\sigma'}{\Lambda'}(\Omega) \arrow[rd, hook] \\
+%%& \singexpalg{\sigma}(\Omega) \\
+%%\singexp{\sigma'}{\Lambda''}(\Omega) \arrow[ru, hook] \arrow[uu, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"]
+%%\end{tikzcd}
+%%\end{center}
+automatically commute, because as non-topological linear maps they are all inclusions between subspaces of $\holo(\domain)$.
+The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
+\par\color{red}
 For each $\Lambda'$, we \textcolor{red}{can} get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing \textcolor{red}{some} $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
@@
 Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
-
-\color{brown}
+\par\color{brown}
 For every $\Lambda'$, there is a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ obtained by choosing $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$.

### 2024-05-01 sima/reg-sing-volterra_sima.tex
Revise definition of Laplace transform

@@
 -\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
-& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
-\end{align*}
-Exponentiating both sides, we see that
+& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta.
+\end{align*}
+Exponentiating both sides \textcolor{blue}{shows that}
 \[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
@@
 for any integration path that stays within $\near$.
-\textcolor{blue}{Since $\domain$ is star-shaped around $\zeta = 0$, so is $\near$.
-\textcolor{orange}{[\ldots]}} \textcolor{red}{Taking advantage of the fact that $\near$ is a sector of a disk, let us use the straight path} \textcolor{brown}{Since $\near$ \textcolor{magenta}{is star-shaped [why?]} at $\zeta=0$, the path of integration can be chosen to be a segment } $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+\textcolor{blue}{Noting} that $\near$ is \textcolor{blue}{star-shaped by construction, we} use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
 \begin{align*}
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} there is some $M\in\R_{>0}$ for which
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} \textcolor{blue}{there is some $M\in\R_{>0}$} for which
 \textcolor{red}{\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]}
@@
 Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then \textcolor{red}{we can make our bound} there is an uniform bound over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
+Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
@@
 
-\textcolor{red}{Now, we just want to} Next, we show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
+\textcolor{red}{Now, we just want to} \textcolor{brown}{Next, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
 
@@
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{red}{that leaves} originating from $\zeta=\alpha$ \textcolor{red}{at angle} in the direction of $\theta$.
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$.
+Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} \textcolor{blue!50}{that leaves} $\zeta=\alpha$ \textcolor{blue!50}{at angle} $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
+\[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
+is defined for all $\sigma > -1$ and $\Lambda \in \R$. Its action on a function $\varphi$ is given by the formula
+\begin{equation}\label{laplace:int}
+\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
+\end{equation}
 \color{red} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
 The Laplace transform of $\varphi$ is defined by the formula
-\begin{equation}%\label{laplace:int} 
+\begin{equation}%%\label{laplace:int} 
 \laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
@@
 is defined by
-\begin{equation}\label{laplace:int} 
+\begin{equation}%%\label{laplace:int} 
 (\laplace_{\zeta, \alpha}^{\theta} \varphi)(z) := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.

### 2024-05-01 sima/reg-sing-volterra_sima.tex
Review and accept some changes
Accepted removal: red to pink. Declined to remove: red to light blue.

@@
 \end{conditions}
-This condition explains why $\domain$ \textcolor{brown}{might have the shape} illustrated in Section~\ref{setting:domain}.
-As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+\textcolor{blue}{This condition explains the shape of the example domain $\domain$ illustrated in Section~\ref{setting:domain}.} \textcolor{pink}{This condition explains why $\domain$ \textcolor{brown}{might have the shape} illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 \begin{verify}
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound \textcolor{red}{on how fast $\softker$ grows away from the diagonal} \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound \textcolor{pink}{on how fast $\softker$ grows away from the diagonal} \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{red}{For some constant $\gamma > 0$, we have} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{pink}{For some constant $\gamma > 0$, we have} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 
-\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} \textcolor{pink}{Then,} Condition \eqref{cond:reg-p} implies that
+\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} \textcolor{pink}{Then,} \textcolor{blue}{Condition \eqref{cond:reg-p} implies that}
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
-Observing that $|\eta| \le C |\zeta|$ in $\near$, we \textcolor{red}{can} conclude that
+Observing that $|\eta| \le C |\zeta|$ in $\near$, we \textcolor{pink}{can} conclude that
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
@@
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$.
-\textcolor{red}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+\textcolor{pink}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-\textcolor{red}{Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\textcolor{pink}{Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 \begin{proposition}%%\label{prop:whole-ker-near-bound}
-\color{red}
+\color{pink}
 Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we \textcolor{red}{can} ensure that
@@
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-\textcolor{red}{Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want can be made sufficienlty small by keeping $a$ and $a'$ close to $\zeta = 0$.
+\textcolor{pink}{Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
 The condition guarantees that}
 
-\textcolor{brown}{Condition~\eqref{cond:eps-lambda} implies that}
+\textcolor{blue}{Condition~\eqref{cond:eps-lambda} implies that}
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
-\color{red}Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
+\color{blue}Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
+Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top} guarantee that this is possible.
+The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
+\par\color{blue!50!green}Choose $\Lambda \in \R$ large enough to make $\volterra$ a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ an element of $\singexp{\rho-1}{\Lambda}(\Omega)$.
+This is possible by Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top}.
+Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
+\par\color{pink}Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
 Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
@@
 
-To see that the fixed point is \textcolor{red}{still} unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+To see that the fixed point is \textcolor{pink}{still} unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 \begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
-Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}, which satisfies the equation
-\[ \solproto = \hardpart \solproto. \]
+Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}.\textcolor{pink}{, which satisfies the equation
+\[ \solproto = \hardpart \solproto. \]}
 The base point for the construction can be chosen arbitrarily.
@@
 \end{align*}
-we \textcolor{red}{can} rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
+we \textcolor{pink}{can} rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
 \begin{align}
@@
 
-\textcolor{red}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
+\textcolor{blue}{To use our previous reasoning in this more general setting, we must reinterpret its language.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} \textcolor{red}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
 The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} \textcolor{brown}{To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} This substitution leads to several other reinterpretations, summarized below.
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{red}{you can use} differentiation under the integral \textcolor{red}{to show} shows that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{red}{you can use} \textcolor{brown}{differentiation under the integral} \textcolor{red}{to show} \textcolor{brown}{shows} that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \begin{rmk}
-\textcolor{red}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
-We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\textcolor{red}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to have any possibility of being well-defined, the ray $\Gamma_{\zeta, \alpha}^\theta$ must lie within $\domain_\alpha$.} We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
@@
 \end{align*}
-By bringing $\zeta(a')$ closer to $\alpha$, \textcolor{red}{we can make} the middle term
+By bringing $\zeta(a')$ closer to $\alpha$, \textcolor{blue!50}{we can make} the middle term
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-ca be made \textcolor{magenta}{sufficiently small} \textcolor{red}{as small as we want}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{red}{we can make} the sum
+\textcolor{brown}{can be made} \textcolor{blue}{arbitrarily small} \textcolor{red}{as small as we want}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{blue!50}{we can make} the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-can be made \textcolor{magenta}{sufficielty small} \textcolor{red}{as small as we want}. Hence, for any $\sigma > \tau_\alpha$, the bound
+\textcolor{brown}{can be made} \textcolor{blue}{arbitrarily small} \textcolor{red}{as small as we want}. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
@@
 \end{itemize}
-We \textcolor{red}{can} now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
+We \textcolor{blue!50}{can} now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
 \end{proof}

### 2024-05-01 sima/reg-sing-volterra_sima.tex
Clean up old versions of accepted changes

@@
 \end{conditions}
-\textcolor{blue}{This condition explains the shape of the example domain $\domain$ illustrated in Section~\ref{setting:domain}.} \textcolor{pink}{This condition explains why $\domain$ \textcolor{brown}{might have the shape} illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+\textcolor{blue}{This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 \begin{verify}
@@
 
-We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$\textcolor{brown}{, where $\softpart$ has non-separable kernel, and it regularizes the action of $\softpart$ at the singularity, as we will show in Proposition \ref{prop:smoothing}.} \textcolor{blue}{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
+We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
+\textcolor{blue}{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
 To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound \textcolor{pink}{on how fast $\softker$ grows away from the diagonal} \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{pink}{For some constant $\gamma > 0$, we have} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{proof}
-%\textcolor{blue}{One might describe the functions in $\singexp{\sigma}{\Lambda}(\domain)$ as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ (which may depends on $\varepsilon$) such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.}
-\color{blue}
-
-The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
+\color{blue}The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
 The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace.
@@
 equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
-\end{definition}
-\color{brown}
-\begin{definition}
-    Let $\sigma \in \R$. We define the space
-    \[\singexpalg{\sigma}(\domain):=\bigcup_{\Lambda\in\R}\singexp{\sigma}{\Lambda}(\domain)\,,\]
-    equipped with the finest topology that makes continuous the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$. 
-\end{definition}
-\color{red} Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
-Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we \textcolor{red}{can} give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
-\color{black}
+\end{definition}\color{black}
 \begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
@@
 \end{proposition}
-\color{blue}
-\begin{proof}
+\color{blue}\begin{proof}
 For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
@@
 \end{center}
-%%\begin{center}
-%%\begin{tikzcd}[row sep=2mm, column sep=15mm, labels={inner sep=1ex,}]
-%%\singexp{\sigma'}{\Lambda'}(\Omega) \arrow[rd, hook] \\
-%%& \singexpalg{\sigma}(\Omega) \\
-%%\singexp{\sigma'}{\Lambda''}(\Omega) \arrow[ru, hook] \arrow[uu, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"]
-%%\end{tikzcd}
-%%\end{center}
 automatically commute, because as non-topological linear maps they are all inclusions between subspaces of $\holo(\domain)$.
 The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
-\par\color{red}
-For each $\Lambda'$, we \textcolor{red}{can} get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing \textcolor{red}{some} $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
-For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are ultimately working in the vector space of holomorphic functions on $\Omega$.
-Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
-\par\color{brown}
-For every $\Lambda'$, there is a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ obtained by choosing $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$.
-
-For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we are working in the space of holomprhic functions on $\domain$.
-In the topology of $\singexpalg{\sigma'}(\domain)$, this gives the desired continuos inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
-\color{black}
-\end{proof}
+\end{proof}\color{black}
 \section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
@@
 We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
-\par\textcolor{orange}{[Keep revising]} \color{red}
-The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
-In this section, we show that the method works by proving those results.
-
-We start by constructing the prototype solution $\solproto$ from the kernel of $\hardpart$, which is the separable operator that gives $\volterra = \hardpart + \softpart$ its regular singularity.
-We will show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
-
-To see what the perturbation $\softpart$ does to $\solproto$, we will show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
-
-\color{brown}
-In this section, we prove the results outlined in Section~\ref{sec:results}, demonstrating a method for solving the singular Voletrra equation $f=\volterra f$.
-
-We start by constructing the prototype solution $f_0$ of $f=\softpart f$, and show in Section~\ref{sec:proto-construction-regularity} that $f_0\in\singexp{\tau-1+\gamma}{\Lambda}(\domain)$.
-
-In Section~\ref{sec:image under soft_part}, we show that the perturbation $\softpart$ has a smoothing effect on $f_0$, reducing the power-law singularity at $\zeta=0$.
-In particular, it turns out that $\softpart f_0\in\singexpalg{\tau-1+\gamma}(\domain)$.
-\color{black}
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.\color{black}
 
@@
 \end{equation}
-whenever $|\zeta| < \delta$.
-\textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:} \textcolor{red}{We can take advantage of} \textcolor{magenta}{We use this bound [we do not use the bound yet]} \textcolor{pink}{by rewriting the integral in the definition of $\chi$:}
+whenever $|\zeta| < \delta$. \textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:}
 \begin{align*}
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{red}{reason} deduce that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{red}{reason} \textcolor{brown}{deduce} that
 \begin{align*}
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then\textcolor{red}{, for some constant $M$} \textcolor{blue}{there is some $M\in\C$} for which,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then \textcolor{blue}{there is some $M\in\C$} for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
-Observing that $|\eta| \le C |\zeta|$ in $\near$, we \textcolor{pink}{can} conclude that
+Observing that $|\eta| \le C |\zeta|$ in $\near$, we conclude that
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
@@
 
-\textcolor{blue}{Together, the arguments above show that}\textcolor{pink}{Combining the arguments above, we \textcolor{red}{learn} \textcolor{blue}{find} that}
+\textcolor{blue}{Together, the arguments above show that}
 \begin{align*}
@@
 \end{align*}
-The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$.
-\textcolor{pink}{Recognizing the integral as an evaluation of the beta function, we \textcolor{red}{can} rewrite the bound as} \textcolor{brown}{The integral defines Euler's beta function, so} \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-\textcolor{pink}{Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that} \textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 \end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{\textcolor{red}{It is possible to fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.}} Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, shows that there is a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+First, pick some $\sigma \in (\tau, \rho)$.
+Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, shows that there is a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
 \begin{equation}\label{near-limit}
@@
 \end{proposition}\color{black}
-\begin{proposition}%%\label{prop:whole-ker-near-bound}
-\color{pink}
-Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we \textcolor{red}{can} ensure that
-\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
-by keeping $a$ and $a'$ close enough to $\zeta = 0$.
-
-\color{brown}
-If $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}, then for any $\sigma > \tau$ there exists a neighbourhood $\mathcal{U}$ of $\zeta=0$ in $\domain$ such that
-\[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
-for any $(a,a')\in\mathcal{U}^2$.
-\color{black}
-\end{proposition}
 \begin{proof}
-First, choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{blue!50}{can} ensure that
+\textcolor{blue}{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{blue!50}{can} ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-\textcolor{pink}{Now, we will show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
-The condition guarantees that}
 
@@
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \]
-grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we \textcolor{red}{can} bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
+grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we \textcolor{blue!50}{can} bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
@@
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
-for any choice of integration path.\footnote{\textcolor{red}{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} not clear} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
+for any choice of integration path.\footnote{\textcolor{red}{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} \textcolor{green}{[not clear]}} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
 \begin{align*}
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{red}{we can find a constant} \textcolor{blue}{there is some $M\in\R_{>0}$} for which
-\textcolor{red}{\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]}
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{blue}{there is some $M\in\R_{>0}$} for which
 \textcolor{blue}{\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]}
-\textcolor{blue}{for all $a \in \far$ and $a' \in \Omega$.}\textcolor{red}{for all $a \in \far$.} \textcolor{pink}{Note that only the first argument of $k$ has its domain restricted\textcolor{red}{; this bound holds throughout $\domain$ in the second argument}, \textcolor{violet}{[rephrase]} \textcolor{brown}{while the second varies in $\domain$}.} Applying this bound, we \textcolor{red}{learn} that
+\textcolor{blue}{for all $a \in \far$ and $a' \in \Omega$.} \textcolor{blue}{This bound implies that}
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
@@
 To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately.
-At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we \textcolor{red}{can} use a worst-case estimate on the exponential factor:
+At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we use a worst-case estimate on the exponential factor:
 \begin{align*}
@@
 Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top} guarantee that this is possible.
-The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
-\par\color{blue!50!green}Choose $\Lambda \in \R$ large enough to make $\volterra$ a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ an element of $\singexp{\rho-1}{\Lambda}(\Omega)$.
-This is possible by Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top}.
-Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
-\par\color{pink}Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
-Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
-Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.\color{black} \textcolor{violet}{[condense and simplify]}
-
-To see that the fixed point is \textcolor{pink}{still} unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.\color{black}
+
+To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 Together, these arguments show that the fixed point is unique in $\singexpalg{\rho-1}(\Omega)$.
-
-\color{brown}
-Choose $\Lambda$ sufficienlty large that $\volterra$ is a contraction, by Proposition~\ref{prop:get-contraction}.
-Take $g\in\singexpalg{\rho-1}(\Omega)$.
-By definition, $g$ also belong to $\singexp{\rho-1}{\Lambda}(\Omega)$.
-Therefore,
-\[f \mapsto \volterra f + g\]
-is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem. 
-\color{black}
 \end{proof}
 \begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
-Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}.\textcolor{pink}{, which satisfies the equation
-\[ \solproto = \hardpart \solproto. \]}
+Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}.
 The base point for the construction can be chosen arbitrarily.
@@
 of the space $\singexpalg{\tau-1}(\domain)$.
-\end{proposition}
-\color{pink}\begin{proposition}%%\label{prop:alt-general_volterra}
-Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the \textcolor{red}{other conditions we assume in} assumptions of {\em Theorem~\ref{thm:general_volterra}}.
-Then, \textcolor{red}{as long as $\rho > \tau$ is low enough} \textcolor{brown}{for $\tau<\rho\le\tau+\min(\gamma,\epsilon,1)$}, equation~\eqref{eqn:orig-homog}
-\textcolor{red}{
-\begin{equation}
-f = \volterra f
-\end{equation}}
-has a unique solution $f$ in the affine subspace
-\[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
-of the space $\singexpalg{\tau-1}(\domain)$. \textcolor{red}{To be precise, $\rho$ is low enough when it is in the interval
-\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]}
 \end{proposition}\color{black}
-%
 \begin{proof}
@@
 \textcolor{blue}{To use our previous reasoning in this more general setting, we must reinterpret its language.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} \textcolor{red}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} \textcolor{pink}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
 The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} \textcolor{brown}{To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} This substitution leads to several other reinterpretations, summarized below.
@@
 \end{equation}
-\color{red} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
+\color{pink} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
 The Laplace transform of $\varphi$ is defined by the formula
@@
 \[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
-for each $a \in \domain_\alpha$. It obeys the \textcolor{red}{expected} semigroup law \cite[Section~1.3]{mladenov2014advanced}
+for each $a \in \domain_\alpha$. It obeys the semigroup law \cite[Section~1.3]{mladenov2014advanced}
 \begin{align*}
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{red}{you can use} \textcolor{brown}{differentiation under the integral} \textcolor{red}{to show} \textcolor{brown}{shows} that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{blue}{differentiation under the integral shows} that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \subsection{Going to the position domain}
-Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} differential operators in the frequency domain become \textcolor{red}{into} Volterra operators in the position domain.
+Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} \textcolor{brown}{differential operators in the frequency domain become} \textcolor{red}{into} Volterra operators in the position domain.
 \begin{lemma}\label{lem:use-dict}
@@
 \begin{rmk}
-\textcolor{red}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to have any possibility of being well-defined, the ray $\Gamma_{\zeta, \alpha}^\theta$ must lie within $\domain_\alpha$.} We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to have any possibility of being well-defined, the ray $\Gamma_{\zeta, \alpha}^\theta$ must lie within $\domain_\alpha$.} We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
@@
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-\textcolor{brown}{can be made} \textcolor{blue}{arbitrarily small} \textcolor{red}{as small as we want}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{blue!50}{we can make} the sum
+\textcolor{blue}{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{blue!50}{we can make} the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-\textcolor{brown}{can be made} \textcolor{blue}{arbitrarily small} \textcolor{red}{as small as we want}. Hence, for any $\sigma > \tau_\alpha$, the bound
+\textcolor{blue}{arbitrarily small}. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Reorganize proof of `thm:example`

@@
 \textcolor{orange}{[talk about integration]} For a function $\varphi$ defined on a simply connected subset of the position domain,
+
+\textcolor{orange}{Integrals will typically resemble this one:}
+\[ \int_{\zeta = \beta}^a \varphi\,d\zeta \]
+\[ \int_b^a \varphi\,d\zeta \]
+
+\textcolor{orange}{The integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$.
+On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.}
+
+In the integral
+\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{1/2} \varphi\,d\zeta, \]
+notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
 
@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
-The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
+\textcolor{blue}{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{blue!50!green}{Stronger constraints on $\hardpart$ can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{pink}{With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
 %\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
@@
 %
-\textcolor{red}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated}, but its regular singularity at $\zeta = 0$ \textcolor{violet}{stays [make previous part of sentence consistent]} essentially the same.
-We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+\textcolor{pink}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.} \textcolor{blue}{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore expect \textcolor{pink}{to find} a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
@@
 
-Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} for a given $\sigma>0$ there exists a radius $r<\delta$ for which
+Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} \textcolor{brown}{for a given $\sigma>0$ there exists a radius $r<\delta$} for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
@@
 
-Now, let us look at the exponential factor.
+Now, \textcolor{blue}{consider} \textcolor{pink}{let us look at} the exponential factor.
 By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
@@
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
-Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.\footnote{\textcolor{red}{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.}} Then, for any $\lambda > \lambda_\Delta$, we have
+Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.
+Then, for any $\lambda > \lambda_\Delta$, we have
 \[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
@@
 \]
-Let us again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+\textcolor{blue}{We} again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
@@
 \end{align*}
-Let us set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
+\textcolor{red}{Let us set} \textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows.
 Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
@@
 
-\textcolor{red}{Now, we just want to} \textcolor{brown}{Next, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
+\textcolor{pink}{Now, we just want to} \textcolor{brown}{Next, we} \textcolor{blue}{Finally, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
 
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, we \textcolor{red}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+In this case, we \textcolor{pink}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
 Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
@@
 \subsection{Overview}
-We \textcolor{red}{can use our understanding of} use regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-In particular, we \textcolor{red}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We can use our \textcolor{pink}{understanding} \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+\textcolor{pink}{In particular} \textcolor{blue}{Under certain conditions}, we \textcolor{blue!50}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 \subsection{Going to the position domain}
-Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} \textcolor{brown}{differential operators in the frequency domain become} \textcolor{red}{into} Volterra operators in the position domain.
+\textcolor{blue}{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
+\textcolor{pink}{Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} differential operators in the frequency domain into \textcolor{blue}{integral} operators in the position domain.}
 \begin{lemma}\label{lem:use-dict}
-\textcolor{cyan}{For each root $-\alpha$ of $P$} \textcolor{brown}{For each $\alpha\in\C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
-\color{cyan}\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
-\color{brown}
-\begin{equation}\label{eq:hat-P-alpha}
-    \big[\hat{\mathcal{P}}_\alpha\varphi\big](a):=\big[P(-\zeta)\varphi\big](a)+ \int_{\zeta=\alpha}^a Q(-\zeta) \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, 
-\end{equation}
-where
-\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
-\color{black}
+For \textcolor{blue}{any $\alpha \in \C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the \textcolor{blue}{integral} operator 
+\[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
 If $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
 \end{lemma}
-
 \begin{rmk}
-\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to have any possibility of being well-defined, the ray $\Gamma_{\zeta, \alpha}^\theta$ must lie within $\domain_\alpha$.} We will see later that for our results to apply, $\domain_\alpha$ cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \textcolor{blue}{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
 \end{rmk}
+\color{blue}\begin{rmk}\label{rmk:use-dict-explicit}
+To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
+\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta, \]
+where
+\[ k_R(a,a') := \sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\end{rmk}\color{black}
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
@@
 \end{theorem}
-\begin{proof}[Proof of Theorem~\ref{thm:example}]
+\begin{proof}
+\color{blue}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
+When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]
 \color{red}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
@@
 To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
-When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
+When we write $\hat{\mathcal{P}}_\alpha$ explicitly as \textcolor{blue}{an integral} operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
 \[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
@@
 \color{brown}
-Choose a root $-\alpha$ of $P$ such that $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+\textcolor{orange}{[simplification based on kernel being given in lemma]} Choose a root $-\alpha$ of $P$ such that $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
- \textcolor{red}{Now we can write} Equation~\eqref{eqn:divided} can be written as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
-
-\textcolor{red}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+ \textcolor{pink}{Now we can write} Equation~\eqref{eqn:divided} \textcolor{blue}{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+
+\textcolor{blue}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+To see this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
+It follows that for any $\lambda > A$, we have $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
+The power series defining $k_R$ therefore converges everywhere.}
+
+\textcolor{pink}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
 One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
@@
 
-Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are \textcolor{red}{now working} in the setting of Proposition~\ref{prop:alt-general_volterra}.
-To apply the proposition, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
+\textcolor{blue}{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
+
+\textcolor{pink}{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are \textcolor{red}{now working} in the setting of Proposition~\ref{prop:alt-general_volterra}.
+To apply the proposition, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
 \begin{itemize}
@@
 Next, knowing that $\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
-We \textcolor{red}{can} then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
+We \textcolor{blue!50}{can} then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
 \[ \big(\zeta(a)-\alpha\big)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Drop old text; work on remaining rephrasings

@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-\textcolor{blue}{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{blue!50!green}{Stronger constraints on $\hardpart$ can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} \textcolor{pink}{With stronger constraints on $\hardpart$, \textcolor{red}{we can also ensure} \textcolor{brown}{it is guaranteed} that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
+\textcolor{blue}{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
 %\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
@@
 \end{rmk}
-%
-\textcolor{pink}{When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we are trying to solve gets more complicated} \textcolor{brown}{For the pertubed operator $\volterra=\hardpart+\softpart$, the equation $f=\volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.} \textcolor{blue}{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore expect \textcolor{pink}{to find} a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+
+\textcolor{blue}{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \textcolor{blue}{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{red}{reason} \textcolor{brown}{deduce} that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{blue}{deduce} that
 \begin{align*}
@@
 \textcolor{blue}{Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.}
-\textcolor{pink}{Since $\zeta(b)^{-\tau}$ is a constant, \textcolor{red}{the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want} the factor $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ is proportional to $\zeta^{\tau-1}$.}
-
-\textcolor{red}{With a little work, the $\zeta/p$ factor also looks like what we want.} \textcolor{pink}{Then,} \textcolor{blue}{Condition \eqref{cond:reg-p} implies that}
+
+\textcolor{blue}{Condition \eqref{cond:reg-p} implies that}
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, \textcolor{blue}{consider} \textcolor{pink}{let us look at} the exponential factor.
-By Condition~\eqref{cond:sing}, \textcolor{red}{we can find} \textcolor{brown}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, \textcolor{blue}{consider} the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 \textcolor{red}{Let us set} \textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then \textcolor{red}{we can make our bound uniform} \textcolor{brown}{there is an uniform bound} over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
+\textcolor{blue}{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
+over all $a \in \far$.
 
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately.
+To see this in the trickiest case, where $\rho < 1$, \textcolor{blue}{consider} the beginning and end of the integration path separately.
 At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we use a worst-case estimate on the exponential factor:
@@
 \subsection{Overview}
-We can use our \textcolor{pink}{understanding} \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-\textcolor{pink}{In particular} \textcolor{blue}{Under certain conditions}, we \textcolor{blue!50}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We can use our \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+\textcolor{blue}{Under certain conditions}, we \textcolor{blue!50}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 \textcolor{blue}{To use our previous reasoning in this more general setting, we must reinterpret its language.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} \textcolor{pink}{To adapt our previous reasoning to this more general situation, we will reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} \textcolor{brown}{To adapt our previous results to this more general situation, the role of the coordinate $\zeta$ is Sections~\ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.} This substitution leads to several other reinterpretations, summarized below.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} This substitution leads to several other reinterpretations, summarized below.
 
@@
 \laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
-\end{equation}
-\color{pink} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we \textcolor{red}{can} define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
-The Laplace transform of $\varphi$ is defined by the formula
-\begin{equation}%%\label{laplace:int} 
-\laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
-\end{equation}
-It is a function on the frequency domain because it depends on the frequency variable $z$.
-\color{brown}
-Let $\Pi_\Lambda^\theta:=\{z\in\C \,\vert \, \Re(z e^{i\theta})>\Lambda\}$. If $\Gamma_{\zeta, \alpha}^\theta$ is contained in $\domain_\alpha$, the Laplace transform 
-\[\laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\domain_\alpha)\to\holo(\Pi_\Lambda^\theta)\]
-is defined by
-\begin{equation}%%\label{laplace:int} 
-(\laplace_{\zeta, \alpha}^{\theta} \varphi)(z) := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
 \end{equation}
@@
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]
-\color{red}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
-The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.
-
-To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
-When we write $\hat{\mathcal{P}}_\alpha$ explicitly as \textcolor{blue}{an integral} operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
-where
-\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
-\color{brown}
-\textcolor{orange}{[simplification based on kernel being given in lemma]} Choose a root $-\alpha$ of $P$ such that $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
-The equation $\hat{\mathcal{P}}_\alpha\varphi=0$, with $\hat{\mathcal{P}}_\alpha$ as in Equation~\eqref{eq:hat-P-alpha}, is explicitly
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0\,. \]
-\color{black}
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]\color{black}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
- \textcolor{pink}{Now we can write} Equation~\eqref{eqn:divided} \textcolor{blue}{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+Equation~\eqref{eqn:divided} \textcolor{blue}{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
 
@@
 The power series defining $k_R$ therefore converges everywhere.}
-
-\textcolor{pink}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
-One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
-To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
-Consequently, for any $\lambda > A$, we have $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
-This is enough to show that $k_R$ is well-defined throughout $\C^2$.
-As we will see later, it also leads to a useful bound on $k_R$.}
-
-\textcolor{brown}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
-Indeed, since $R(z^{-1})$ is holomorphic on the disk $|z| > A$, we have that for any $\lambda > A$, $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
-}
 \begin{verify}
@@
 \textcolor{blue}{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
-
-\textcolor{pink}{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we are \textcolor{red}{now working} in the setting of Proposition~\ref{prop:alt-general_volterra}.
-To apply the proposition, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
 \begin{itemize}

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Finish rephrasings

@@
 
-\textcolor{red}{Now we know that} \textcolor{brown}{Therefore} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, we will show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we will see in Section~\ref{sec:existence and uniqueness}.
+\textcolor{pink}{Now we know that} \textcolor{brown}{Therefore} \textcolor{blue}{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, \textcolor{blue}{we show} in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \textcolor{blue}{show} \textcolor{pink}{will see} in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 
-Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} \textcolor{brown}{for a given $\sigma>0$ there exists a radius $r<\delta$} for which
+\textcolor{pink}{Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} \textcolor{brown}{for a given $\sigma>0$ there exists a radius $r<\delta$}} \textcolor{blue}{Choose some $\sigma > \tau$.
+By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
-whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we \textcolor{red}{can} deduce that
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, \textcolor{blue}{we deduce} that
 \begin{align*}
@@
 \end{align*}
-\textcolor{red}{Let us set} \textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows.
+\textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows.
 \textcolor{blue}{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
@@
 
-\textcolor{pink}{Now, we just want to} \textcolor{brown}{Next, we} \textcolor{blue}{Finally, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
+\textcolor{blue}{Finally, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
 
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, we \textcolor{pink}{can} use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+In this case, we use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
 Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
@@
 \textcolor{blue}{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
-\textcolor{pink}{Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ \textcolor{red}{we can turn} differential operators in the frequency domain into \textcolor{blue}{integral} operators in the position domain.}
 \begin{lemma}\label{lem:use-dict}
@@
 \begin{rmk}
-\textcolor{pink}{For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray} \textcolor{brown}{A necessary condition for the Laplace transform to be well-defined is that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.} \textcolor{blue}{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \textcolor{blue}{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\textcolor{blue}{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \textcolor{blue}{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Drop the last of the old text
Finalize preserved wordings too.

@@
 Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
-% \color{red}
-% Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
-% \[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
-% Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We will suppose this product can be written as a ratio
-% \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-% where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:\color{brown}
 \begin{definition}\label{defn:volterra}
@@
 \begin{verify}
-    By Condition \eqref{cond:diag-basic} \textcolor{red}{we can find} there exists $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
+By Condition \eqref{cond:diag-basic} we can find $c>0$ such that \[ | \hardker(a, a') | \le \frac{c}{|\zeta(a)|} e^{\lambda_\Delta|\zeta(a)-\zeta(a')|} \]
 then setting $\delta=\frac{\log(\sigma/c)}{2\lambda_\Delta}$, we deduce that for every $|\zeta(a)|\le\delta$ and  $|\zeta(a')|\le\delta$
@@
 \[ \zeta^{\tau-1} + \singexpalg{\rho-1}(\domain) \]
-when $\rho > \tau$ is \textcolor{blue!50}{low enough}, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
+when $\rho > \tau$ is low enough, as described in Proposition~\ref{prop:alt-general_volterra} from Section~\ref{sec:existence and uniqueness}.
 \end{rmk}
@@
 
-\textcolor{pink}{Now we know that} \textcolor{brown}{Therefore} \textcolor{blue}{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+\textcolor{blue}{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
 To confirm this, \textcolor{blue}{we show} in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \textcolor{blue}{show} \textcolor{pink}{will see} in Section~\ref{sec:existence and uniqueness}.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \textcolor{blue}{show} in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 
-\textcolor{pink}{Now, using Condition~\eqref{cond:sing} again, \textcolor{red}{choose some $\sigma > \tau$ and find a radius $r < \delta$} \textcolor{brown}{for a given $\sigma>0$ there exists a radius $r<\delta$}} \textcolor{blue}{Choose some $\sigma > \tau$.
-By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
+\textcolor{blue}{Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
@@
 \begin{proof}
-\textcolor{blue}{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we \textcolor{blue!50}{can} ensure that
+\textcolor{blue}{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
@@
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \]
-grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we \textcolor{blue!50}{can} bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
+grows polynomially with respect to $|\zeta(a)-\zeta(a')|$, we can bound it with any growing exponential function of $|\zeta(a)-\zeta(a')|$. In particular,
 \[ 1 + |\zeta(a)-\zeta(a')|^\gamma \lesssim e^{(\lambda - \lambda_\Delta) |\zeta(a)-\zeta(a')|} \]
@@
 \end{align*}
-we \textcolor{pink}{can} rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
+we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
 \begin{align}
@@
 We can use our \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-\textcolor{blue}{Under certain conditions}, we \textcolor{blue!50}{can} build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+\textcolor{blue}{Under certain conditions}, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$.
-Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} \textcolor{blue!50}{that leaves} $\zeta=\alpha$ \textcolor{blue!50}{at angle} $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
+Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
 \[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
@@
 
-We \textcolor{blue!50}{can} now state and prove the main result of this section.
+We can now state and prove the main result of this section.
 Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
@@
 \end{align*}
-By bringing $\zeta(a')$ closer to $\alpha$, \textcolor{blue!50}{we can make} the middle term
+By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-\textcolor{blue}{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, \textcolor{blue!50}{we can make} the sum
+\textcolor{blue}{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
@@
 Next, knowing that $\alpha$ is a root of $p$, rewrite $p$ in the form $(\zeta - \alpha)\,P_\alpha(\zeta)$, where $P_\alpha$ is a polynomial of degree $d-1$.
-We \textcolor{blue!50}{can} then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
+We can then write $-\big(\zeta(a) - \alpha\big)\,\hardker^\alpha(a, a')$ in the form
 \[ \big(\zeta(a)-\alpha\big)\,\frac{q(a')}{p(a)} = \frac{Q_{d-1}\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a')^{d-1} + \ldots + \frac{Q_1\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}\;\omega(a, a') + \frac{Q_0\big(\zeta(a)\big)}{P_\alpha\big(\zeta(a)\big)}, \]
@@
 \end{itemize}
-We \textcolor{blue!50}{can} now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
+We can now apply Proposition~\ref{prop:alt-general_volterra}, yielding the desired result.
 \end{proof}

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Separate expanded uniqueness result

@@
 
-\color{red}For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
+\color{pink}For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
 In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.\color{black}
 \end{theorem}
+\color{blue}
+\begin{corollary}\label{cor:expand_uniq}
+Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
+\end{corollary}
 \color{brown}
@@
 Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
-
-\textcolor{blue}{Finally, we} show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
-
+\end{proof}
+\color{blue}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, we use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
-Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+In this case, the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
 
@@
 In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\gamma}(\Omega)$.
-Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-\end{proof}
+Under this inclusion, any solution of equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+\end{proof}\color{black}
 \color{blue}\begin{proposition}\label{prop:alt-general_volterra}

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Drop old expanded uniqueness text

@@
 Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
-
-\color{pink}For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
-In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.\color{black}
 \end{theorem}
-\color{blue}
-\begin{corollary}\label{cor:expand_uniq}
+\color{blue}\begin{corollary}\label{cor:expand_uniq}
 Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
-\end{corollary}
-\color{brown}
-\begin{rmk}
-For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
-In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity will not reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
-\textcolor{orange}{[Place in a remark and prove in a proposition, as with the remark stating the result of Proposition~\ref{prop:alt-general_volterra}.]}
-\end{rmk}
-\color{black}
+\end{corollary}\color{black}
 This result will follow from a more general result about inhomogeneous equations.

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Finish drafting formalism for coordinates

@@
 \section{Introduction}\label{sec:intro}
-\subsection{Motivation}\label{motivation}
+\subsection{Motivation}\label{sec:motivation}
 \color{blue}
@@
 \subsection{Formalism for coordinates}
+\subsubsection{Rationale}
 Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain.
@@
 
+For simplicity, we use $\C$ as the position domain throughout this article.
+In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
+\subsubsection{Points and coordinates}
 From now on, we will carefully respect the distinction between points and coordinates.
@@
 Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
-
-\textcolor{orange}{[talk about integration]} For a function $\varphi$ defined on a simply connected subset of the position domain,
-
-\textcolor{orange}{Integrals will typically resemble this one:}
-\[ \int_{\zeta = \beta}^a \varphi\,d\zeta \]
-\[ \int_b^a \varphi\,d\zeta \]
-
-\textcolor{orange}{The integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$.
-On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.}
-
+\subsubsection{Integration}
+When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$.
+On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.
+These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$.
+When a bound depends on a particular choice of integration path, we will specify the path in the surrounding text.
 In the integral
-\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{1/2} \varphi\,d\zeta, \]
+\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta, \]
 notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
-
-%%Coordinates, like the frequency coordinate $z$ and the position coordinates $\zeta$ and $\zeta_\alpha$,
-
-%%We will typically speak in terms of functions on spaces, not functions of coordinates.
-
-%%Functions---like the coordinates $\zeta$ and $\zeta_\alpha$, and the solutions $\psi_\alpha$---will be defined directly on the position or frequency domain, not as functions of a particular coordinate.
-
-\textcolor{orange}{[\ldots]}
-\color{violet}
-\begin{itemize}
-\item Can mention translation surfaces, but don't define.
-\item Maybe talk about branched covers of the complex plane, which we need to describe the singular solutions?
-\item Can identify the number $\zeta(a)$ with the point $a$.
-%%\item In the theory of resurgence, the position domain is often a Riemann surface $B$ with a branched covering map $B \to \C$.
-\end{itemize}
-\color{brown}
-\begin{itemize}
-\item mention that $\zeta=0$ is not special, and having in mind the application to ODEs, we need to consider different coordinates. Thus, we think it's appropriate to use the coordinate free notation.
-\item Coordinate free notation is easy to generalize to translation surfaces.
-\item If the reader is familiar with the analysis notation, he should read $\zeta(a)$ as $\zeta$, and the variable inside the integral as ?? 
-\begin{itemize}
-\item You can think of $f$ as the pullback $f(\zeta)$, and then $f(\zeta(\zeta - \alpha))$
-\item $f:M\to N$, $\zeta:M\to\C$, $\phi:N\to\C$, 
-    \item A tangent vector at $x \in M$ is a linear map $v \maps T_x^*M \to \C$.
-Similarly, a tangent vector at $f(x) \in N$ is a linear map $T_{f(x)}^*N \to \C$.
-Define $f_* v \cdot d_x\phi = v \cdot f^* d_{f(x)}\phi = v \cdot d_x(f^* \phi)$ for all functions $\phi$ on $N$.
-    \item $f:M\to\C$, $\zeta:M\to\C$
-    \item if you write $f(a)=\zeta(a)^2+3$, $a\in M$ \textcolor{orange}{[we would write this as $f = \zeta^2 + 3$]}
-    \item if $M=\C$
-    \item $f = \zeta^2 + 3$. Equivalently $f = \big((\zeta - 5) + 5\big)^2 + 3$, or.
-    \item $f=\zeta^2+3$ or equivalently $f(\zeta)=\zeta^2+3$
-    \begin{itemize}
-    \item When you evaluate $f$ at $\zeta = 0$, you get $0^2 + 3 = 3$.
-    \item When you evaluate $f$ at $\zeta = 2$, you get $2^2 + 3 = 7$.
-    \end{itemize}
-    \item $\zeta-\alpha \longrightarrow f(\zeta-\alpha)=(\zeta-\alpha)^2+3$
-    \item $\zeta=0$, $f(0)=3$
-    \begin{itemize}
-    \item Suppose $\alpha = 5$. \item When you evaluate $f(\zeta_5 + 5)$ at $\zeta_5 = 0$, you get $5^2 + 3 = 28$.
-    \item Suppose $\alpha = 5$. \item When you evaluate $f(\zeta - 5)$ at $\zeta = 0$, you get $(-5)^2 + 3 = 28$.
-    \end{itemize}
-\end{itemize}
-\end{itemize}
-\color{black}
+\subsubsection{Plugging into formal expressions}
+Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$.
+The correspondence between operators on the position and frequency domains will lead to expressions of this kind.
+In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\color{black}
 \subsection{Notation}
@@
 \subsubsection{The domain}\label{setting:domain}
-Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
+Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
 
@@
 \subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
-Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
+Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Drop comment about integration path choice
Lower-case equation references

@@
 These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$.
-When a bound depends on a particular choice of integration path, we will specify the path in the surrounding text.
 In the integral
@@
 \begin{corollary}\label{cor:pertub_f0}
-Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}.
+Consider the prototype solution $\solproto$ from equation~\eqref{eqn:test_solution}.
 If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
@@
 Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
-Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
+Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+Equivalently, equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
 \end{proof}
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.
+and agrees with ordinary repeated integration when $\nu$ is an integer \cite[equation~35]{mladenov2014advanced}.
 
@@
 \end{equation}
-First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from Equation~\eqref{eqn:split-numerator} that
+First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from equation~\eqref{eqn:split-numerator} that
 \begin{align*}
@@
 holds when $a$ and $a'$ are close enough to $\zeta = \alpha$.
-Taking the absolute value of both sides of Equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
+Taking the absolute value of both sides of equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
 \begin{align*}

### 2024-05-02 sima/reg-sing-volterra_sima.tex
Revise sentence about Écalle

@@
 Our results build on known methods for solving differential equations with irregular singularities.
-Our focus on integral equations in the position domain, and the singularities of their solutions, \textcolor{orange}{recalls [reword]} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
+Our focus on integral equations in the position domain, and the singularities of their solutions, recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence.
+However our method differs from the one of Loday-Richaud and Remy who instead used a formal approach to find solutions in the position domain~\cite{loday-Remy2011}.} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
 One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Propose rewrite of sentence about Écalle

@@
 Our results build on known methods for solving differential equations with irregular singularities.
-Our focus on integral equations in the position domain, and the singularities of their solutions, recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence.
+Our focus on integral equations in the position domain, and the singularities of their solutions, \textcolor{cyan}{recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}.
+One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions.} \textcolor{pink}{recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence.
 However our method differs from the one of Loday-Richaud and Remy who instead used a formal approach to find solutions in the position domain~\cite{loday-Remy2011}.} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
-One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.
-The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.} The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Remove footnote on 1-forms and densities
It's been made redundant by the discussion of integration in the coordinate
formalism section.

@@
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
-for any choice of integration path.\footnote{\textcolor{red}{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} \textcolor{green}{[not clear]}} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
+for any choice of integration path.
+The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
 \begin{align*}

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Cite reference on densities

@@
 \subsubsection{Integration}
-When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$.
+When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}.
 On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.

### 2024-05-03 sima/correspondence/sima-v2-changes.tex
Go back to introducing sing-exp spaces in two stages
Drop complex tau scratch work

@@
 \usepackage{graphicx}
+\usepackage{amssymb}
 \usepackage{tikz}
@@
 \item We have changed our notation for uniform bounds to require the absolute value.
+\item the seminorm is a seminorm, because we can choose $K=\{\mathsf{pt}\}$
 \end{itemize}
+\color{orange}
+For $\tau\in\mathbb{C}$
+\begin{equation}
+    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
+\end{equation}
+so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate".
+I'm not very confortable with rotations, so probably I'll not add this complication.
+I'm also afraid we should be more carefull with these mooving domains, if we allow rotations.
+So maybe better not make things too complicated for the sake of generality.
+We have a good list of examples that fit in our pictures.
+\color{black}
 \color{black}

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Drop complex tau scratch work

@@
 It follows, as discussed above, that $\hardpart \solproto = \solproto$.
-\color{orange}
-For $\tau\in\C$
-\begin{equation}
-    \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau=\exp\left(\Re(\tau) \textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}+i\Im(\tau)\textcolor{magenta}{\log} \frac{\zeta(a)}{\zeta(b)}\right)
-\end{equation}
-so if $\Re(\tau)>0$ and it is bigger than $\Im(\tau)$ the first term dominates in the limit $\zeta\to0$...but maybe we don't need ``bigger than $\Im(\tau)$", as ``we can rotate".
-I'm not very confortable with rotations, so probably I'll not add this complication.
-I'm also afraid we should be more carefull with these mooving domains, if we allow rotations.
-So maybe better not make things too complicated for the sake of generality.
-We have a good list of examples that fit in our pictures.
-\color{black}
 \end{proof}

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Remove unused function space macros
Accept rewritten sentence about Écalle

@@
 \newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
-\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
-\newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
 
@@
 Our results build on known methods for solving differential equations with irregular singularities.
-Our focus on integral equations in the position domain, and the singularities of their solutions, \textcolor{cyan}{recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}.
-One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions.} \textcolor{pink}{recalls \textcolor{orange}{recalls the approach of \'Ecalle's theory of resurgence.
-However our method differs from the one of Loday-Richaud and Remy who instead used a formal approach to find solutions in the position domain~\cite{loday-Remy2011}.} \'{E}calle's \textcolor{orange}{[and Remy \& Loday-Richaud's?]} theory of resurgence~\cite{EcalleIII}.
-One of our motivations is to understand \'{E}calle's theory from an analytic perspective, without reference to formal solutions.} The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+Our focus on integral equations in the position domain, and the singularities of their solutions, recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}.
+One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions.
+The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
@@
 \subsubsection{Regularity}\label{sec:asymptotics}
-%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}.
-The proofs of the Proposition below can be combined together.}
 Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Make revision highlighting switchable

@@
 \usepackage{graphicx}
-%%\usepackage[svgnames]{xcolor} % for verifications
 \usepackage{environ} % to hide verifications
@@
 
+% revision highlighting
+\newif\ifhighlightrevs
+\highlightrevsfalse
+\ifhighlightrevs
+\newenvironment{rev}{\color{red!60!black}}{\color{black}}
+\newcommand{\revtext}[1]{\textcolor{red!50!black}{#1}}
+\else
+\newenvironment{rev}{}{}
+\newcommand{\revtext}[1]{#1}
+\fi
+
 % colors
@@
 \subsection{Motivation}\label{sec:motivation}
-\color{blue}
-\textcolor{blue}{An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+\begin{rev}An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
 These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
@@
 In~\cite{borel_reg}, we show that these solutions match the ones obtained through resummation.
-Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.}
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.\end{rev}
 
@@
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-For instance, in Section~\ref{sec:example}, we consider equations of the form
+\begin{rev}For instance, in Section~\ref{sec:example}, we consider equations of the form
 \begin{equation}\label{eqn:intro-level-1}
@@
 The correspondence between operators on the position and frequency domains will lead to expressions of this kind.
-In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\color{black}
+In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\end{rev}
 \subsection{Notation}
@@
 \end{conditions}
-\textcolor{blue}{This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+\revtext{This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 \begin{verify}
@@
 We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
-\textcolor{blue}{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
+\revtext{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
 To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound \textcolor{blue}{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound \revtext{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \textcolor{blue}{There is a constant $\gamma > 0$ for which}
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \revtext{There is a constant $\gamma > 0$ for which}
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{equation}
-Changing the base point $b \in \domain$ \textcolor{blue}{only} multiplies $f_0$ by a non-zero constant.
+Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
 \end{theorem}
@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-\textcolor{blue}{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
-%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
+\revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
 \begin{theorem}\label{thm:proto-growth}
@@
 
-\textcolor{blue}{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \textcolor{blue}{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
@@
 \end{theorem}
-\color{blue}\begin{corollary}\label{cor:expand_uniq}
+\begin{rev}\begin{corollary}\label{cor:expand_uniq}
 Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
-\end{corollary}\color{black}
+\end{corollary}\end{rev}
 This result will follow from a more general result about inhomogeneous equations.
@@
 
-We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting \textcolor{blue}{the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$} as an inhomogeneous equation in a more regular space.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting \revtext{the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$} as an inhomogeneous equation in a more regular space.
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
@@
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
-\textcolor{blue}{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
+\revtext{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
 This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
@@
 The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-\color{blue}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
+\begin{rev}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
 \begin{definition}\label{def:unif-exp}
@@
 That means the inclusion is continuous.
-%%\textcolor{orange}{$\{f \in \holo(\domain) : f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}\}$}
 \begin{rmk}
@@
 \end{proof}
-\color{black}
+\end{rev}
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
@@
 \end{proof}
-\color{blue}The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
+\begin{rev}The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
 The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace.
@@
 equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
-\end{definition}\color{black}
+\end{definition}\end{rev}
 \begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
@@
 \end{proposition}
-\color{blue}\begin{proof}
+\begin{rev}\begin{proof}
 For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
@@
 The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
-\end{proof}\color{black}
+\end{proof}\end{rev}
 \section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
 \subsection{Overview}
-\color{blue}
-In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+\begin{rev}In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
 
@@
 We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.\color{black}
-
-\textcolor{blue}{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, \textcolor{blue}{we show} in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \textcolor{blue}{show} in Section~\ref{sec:existence and uniqueness}.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.\end{rev}
+
+\revtext{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, \revtext{we show} in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \revtext{show} in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 \[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
-Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \textcolor{blue}{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
+Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \revtext{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
 \begin{align*}
@@
 \end{align*}
-\textcolor{blue}{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.
-
-By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a radius $\delta>0$ and a constant $C$ such that
+\revtext{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.
+
+By Condition~\eqref{cond:sing}, \revtext{there exist} a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
@@
 \end{equation}
-whenever $|\zeta| < \delta$. \textcolor{blue}{To use this bound, we rewrite the integral in the definition of $\chi$:}
+whenever $|\zeta| < \delta$. \revtext{To use this bound, we rewrite the integral in the definition of $\chi$:}
 \begin{align*}
@@
 \end{align*}
-Exponentiating both sides \textcolor{blue}{shows that}
+Exponentiating both sides \revtext{shows that}
 \[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
@@
 
-\textcolor{blue}{Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
+\revtext{Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
-whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, \textcolor{blue}{we deduce} that
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, \revtext{we deduce} that
 \begin{align*}
@@
 
-By Proposition~\ref{prop:asymptotic at zero}, \textcolor{blue}{there is} a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
-No matter which value of $\lambda_0$ we pick, \textcolor{blue}{$e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so} $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+By Proposition~\ref{prop:asymptotic at zero}, \revtext{there is} a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, \revtext{$e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so} $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
 
@@
 \end{align*}
-over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. \textcolor{blue}{The last bound means that for some $c_\Delta > 0$,}
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. \revtext{The last bound means that for some $c_\Delta > 0$,}
 \[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
 whenever $|\zeta(a)| \ge \delta$.
-Applying this bound along the diagonal in $\domain^2$, we \textcolor{blue}{conclude} that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we \revtext{conclude} that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
 On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \textcolor{blue}{deduce} that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \revtext{deduce} that
 \begin{align*}
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then \textcolor{blue}{there is some $M\in\C$} for which,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then \revtext{there is some $M\in\C$} for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
-at $\zeta = 0$. \textcolor{blue}{As in} the proof of Theorem~\ref{thm:basic_volterra}, we \textcolor{blue}{compute}
+at $\zeta = 0$. \revtext{As in} the proof of Theorem~\ref{thm:basic_volterra}, we \revtext{compute}
 \begin{align*}
@@
 \end{align*}
-\textcolor{blue}{Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.}
-
-\textcolor{blue}{Condition \eqref{cond:reg-p} implies that}
+\revtext{Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.}
+
+\revtext{Condition \eqref{cond:reg-p} implies that}
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, \textcolor{blue}{consider} the exponential factor. By Condition~\eqref{cond:sing}, \textcolor{blue}{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, \revtext{consider} the exponential factor. By Condition~\eqref{cond:sing}, \revtext{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 
-\textcolor{blue}{Together, the arguments above show that}
+\revtext{Together, the arguments above show that}
 \begin{align*}
@@
 at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$.
-Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we \textcolor{blue}{reach} the desired result.
+Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we \revtext{reach} the desired result.
 \end{proof}
@@
 \end{align*}
-The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \textcolor{blue}{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \revtext{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
-\textcolor{blue}{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\revtext{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
@@
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-\color{blue}\begin{proposition}\label{prop:whole-ker-near-bound}
+\begin{rev}\begin{proposition}\label{prop:whole-ker-near-bound}
 Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
@@
 for all $a, a' \in \Sigma$.
-\end{proposition}\color{black}
+\end{proposition}\end{rev}
 \begin{proof}
-\textcolor{blue}{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
+\revtext{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
@@
 
-\textcolor{blue}{Condition~\eqref{cond:eps-lambda} implies that}
+\revtext{Condition~\eqref{cond:eps-lambda} implies that}
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{align*}
-for any integration path that stays within $\near$.
-\textcolor{blue}{Noting} that $\near$ is \textcolor{blue}{star-shaped by construction, we} use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
+for any integration path that stays within $\near$. \revtext{Noting} that $\near$ is \revtext{star-shaped by construction, we} use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
 \begin{align*}
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \textcolor{blue}{there is some $M\in\R_{>0}$} for which
-\textcolor{blue}{\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]}
-\textcolor{blue}{for all $a \in \far$ and $a' \in \Omega$.} \textcolor{blue}{This bound implies that}
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \revtext{there is some $M\in\R_{>0}$} for which
+\revtext{\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]}
+\revtext{for all $a \in \far$ and $a' \in \Omega$.} \revtext{This bound implies that}
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
-\textcolor{blue}{We} again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+\revtext{We} again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
@@
 \end{align*}
-\textcolor{blue}{Set} $\Lambda > \lambda$, \textcolor{blue}{so} the exponential factor shrinks as $|\zeta(a)|$ grows.
-\textcolor{blue}{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
+\revtext{Set} $\Lambda > \lambda$, \revtext{so} the exponential factor shrinks as $|\zeta(a)|$ grows. \revtext{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
@@
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, \textcolor{blue}{consider} the beginning and end of the integration path separately.
+To see this in the trickiest case, where $\rho < 1$, \revtext{consider} the beginning and end of the integration path separately.
 At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we use a worst-case estimate on the exponential factor:
@@
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
-\color{blue}Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
+\revtext{Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
 Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top} guarantee that this is possible.
-The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.\color{black}
+The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.}
 
@@
 \end{proof}
-\color{blue}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
+\begin{rev}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
@@
 Under this inclusion, any solution of equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-\end{proof}\color{black}
-\color{blue}\begin{proposition}\label{prop:alt-general_volterra}
+\end{proof}\end{rev}
+\revtext{\begin{proposition}\label{prop:alt-general_volterra}
 Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}.
@@
 of the space $\singexpalg{\tau-1}(\domain)$.
-\end{proposition}\color{black}
+\end{proposition}}
 \begin{proof}
@@
 \subsection{Overview}
-We can use our \textcolor{blue}{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-\textcolor{blue}{Under certain conditions}, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We can use our \revtext{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+\revtext{Under certain conditions}, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 
-\textcolor{blue}{To use our previous reasoning in this more general setting, we must reinterpret its language.
+\revtext{To use our previous reasoning in this more general setting, we must reinterpret its language.
 The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} This substitution leads to several other reinterpretations, summarized below.
@@
 \subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \textcolor{blue}{$\zeta=\alpha$.
-Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \textcolor{blue}{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\textcolor{blue}{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \color{blue}the Laplace transform
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \revtext{$\zeta=\alpha$.
+Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \revtext{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\revtext{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \revtext{the Laplace transform
 \[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
@@
 \laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
-\end{equation}
-\color{black}
+\end{equation}}
+
 \subsubsection{Action on integral operators}\label{sec:L-int-op}
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \textcolor{blue}{differentiation under the integral shows} that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \revtext{differentiation under the integral shows} that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \subsection{Going to the position domain}
-\textcolor{blue}{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
+\revtext{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
 \begin{lemma}\label{lem:use-dict}
-For \textcolor{blue}{any $\alpha \in \C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the \textcolor{blue}{integral} operator 
+For \revtext{any $\alpha \in \C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the \revtext{integral} operator 
 \[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
@@
 \begin{rmk}
-\textcolor{blue}{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \textcolor{blue}{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+\revtext{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \revtext{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
 \end{rmk}
-\color{blue}\begin{rmk}\label{rmk:use-dict-explicit}
+\revtext{\begin{rmk}\label{rmk:use-dict-explicit}
 To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
@@
 \[ k_R(a,a') := \sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
-\end{rmk}\color{black}
+\end{rmk}}
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
-Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \textcolor{blue}{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \revtext{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
 Hence,
@@
 \begin{proof}
-\color{blue}Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
+\revtext{Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
 To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]\color{black}
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
-Equation~\eqref{eqn:divided} \textcolor{blue}{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
-
-\textcolor{blue}{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+Equation~\eqref{eqn:divided} \revtext{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+
+\revtext{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
 To see this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
@@
 
-\textcolor{blue}{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
+\revtext{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
 \begin{itemize}
@@
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-\textcolor{blue}{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
+\revtext{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-\textcolor{blue}{arbitrarily small}. Hence, for any $\sigma > \tau_\alpha$, the bound
+\revtext{arbitrarily small}. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Explain that "touches" is a nearness relation

@@
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-\subsection{Formalism for coordinates}
+\subsection{Formalism for coordinates}\label
 \subsubsection{Rationale}
@@
 \subsubsection{Boundary points}
-A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
+We will say that a subset of a topological space {\em touches} the points in its closure.
+This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
 If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$.

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Write bound on |f| instead of f

@@
 \newif\ifhighlightrevs
-\highlightrevsfalse
+\highlightrevstrue
 \ifhighlightrevs
-\newenvironment{rev}{\color{red!60!black}}{\color{black}}
-\newcommand{\revtext}[1]{\textcolor{red!50!black}{#1}}
+\newenvironment{rev}{\color{revred}}{\color{black}}
+\newcommand{\revtext}[1]{\textcolor{revred}{#1}}
 \else
@@
 \definecolor{veriforest}{RGB}{0, 80, 40}
+\definecolor{revred}{RGB}{153, 0, 0}
 
@@
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-\subsection{Formalism for coordinates}\label
+\subsection{Formalism for coordinates}\label{sec:formalism}
 \subsubsection{Rationale}
@@
 \[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
-be the subspace consisting of functions $f$ with $f \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
+be the subspace consisting of functions $f$ with $|f| \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
 \[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
@@
 \[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
-be the subspace consisting of functions $f$ with $f \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
+be the subspace consisting of functions $f$ with $|f| \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
 \[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]

### 2024-05-03 sima/reg-sing-volterra_sima.tex
Assume explicitly that P has a suitable root

@@
 \subsubsection{Uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write \revtext{$|\varphi| \lesssim \omega$} to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
@@
 For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
-\subsubsection{Boundary points}
+\begin{rev}\subsubsection{Boundary points}
 We will say that a subset of a topological space {\em touches} the points in its closure.
@@
 If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$.
-This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
-
+This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.\end{rev}
 \subsection{Setting}\label{setting}
@@
 \end{center}
-%
-\subsubsection{The prototype operator}\label{setting:basic}
+\begin{rev}\subsubsection{The prototype operator}\label{setting:basic}
 The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.
@@
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-for some $p, q \in \mathcal{H}(\Omega)$.
+for some $p, q \in \mathcal{H}(\Omega)$.\end{rev}
 
 For the purposes of this paper, $\hardpart$ has a {\em regular singularity} at $\zeta=0$ if the following condition holds.
-
-%%The Volterra operator $\hardpart$ has a regular singularity at $\zeta=0$ if the following condition holds
 \begin{conditions}
@@
 \end{align*}
-\revtext{Set} $\Lambda > \lambda$, \revtext{so} the exponential factor shrinks as $|\zeta(a)|$ grows. \revtext{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
+\revtext{Set $\Lambda > \lambda$, so} the exponential factor shrinks as $|\zeta(a)|$ grows. \revtext{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
@@
 \begin{theorem}\label{thm:example}
-Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
+\revtext{Suppose $P$ has a root $-\alpha$} where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
 $\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$. Then the equation
@@
 \begin{proof}
-\revtext{Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
+\revtext{To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes

### 2024-05-04 exp-resurgence.tex
Revise motivation
Drop old text from countable cover and Bessel 0

@@
 \item Given a function $f$ on $B$, we will write $f'$ and $f''$ to denote the pullbacks of $f$ to the first and second factors, respectively, of $B \times B$.
+\item For a kernel $k$ on $B \times B$, we the corresponding integral kernel operator would be
+\[ \mathcal{V}\phi = \int_0^\zeta k\,\phi'\,d\zeta' \]
+If we have, for example, $k = (\zeta - \zeta')^\rho$ and $\phi' = (\zeta')^k$, then
+\[ \mathcal{V}\phi = \int_0^\zeta (\zeta - \zeta')^\rho\,(\zeta')^k\,d\zeta' \]
+\item Suppose you have
+\[ \omega = e^\zeta - 1 = \zeta + \tfrac{1}{2!} \zeta^2 + \tfrac{1}{3!} \zeta^3 + \ldots \]
+Then
+\[ \zeta = \log(1 + \omega) = \omega + \tfrac{1}{2} \omega^2 + \tfrac{1}{3} \omega^3 + \ldots \]
+Do you say $\zeta(\omega)$?
+Or $\omega(\zeta)$?
+What does $\omega(\zeta + 1)$ mean?
+Define $f = \zeta + \omega$.
+What is $f(\omega + 1)$?
+$f(\zeta) = \zeta + \omega(\zeta)$.
+So $f(\omega) = \log(1 + \omega) + \omega$, so $f(\zeta) = \zeta + e^\zeta - 1$?
+\[ \int_0^\zeta (\zeta^2 + \zeta'^2)\,d\zeta' \]
+\[ \int_{\zeta=0}^a (\zeta(a)^2 + \zeta^2)\,d\zeta \]
+\[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]
 \end{itemize}
@@
 & = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
-& \textcolor{OrangeRed}{= 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da} \\
-& = 2\int_{-\infty}^0 e^{z\cosh(-\pi i+a)} \sinh\big(\mu(a-i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh\big(\mu(i\pi+a)\big)\,da
-\end{align*}
-\color{OrangeRed}
-Stop at the highlighted line! This simplifies to the integral
+& = 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da.
+\end{align*}
+This simplifies to the integral
 \[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
 along the contour $\gamma$ that runs rightward along $i\pi + \R$.
-\textcolor{magenta}{The integral on the next line is {\em not} the path coming from infinity along $(-\infty,0) + 2\pi i (j - \tfrac{1}{2})$ and returning to infinity along $(0, \infty) + 2\pi i (j + \tfrac{1}{2})$, because it skips the segment along $i(-\pi, \pi)$.}
 \par
@@
 We could get the same result from formula~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
-
-\color{RoyalBlue}
-When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
-\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_ {\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt. \]
-We will evaluate
-\[ K_0(z) \defeq K_0^{(1)}(z) - K_0^{(0)}(z). \]
-In this difference, the parts of $\mathcal{C}_1^\theta$ and $\mathcal{C}_0^\theta$ in the left half-plane cancel out \textcolor{orange}{[$\theta$ is small]}, leaving the integral
-\[ K_0(z) = \frac{1}{2\pi i} \int_\mathscr{c} \exp\left[z \cosh(t)\right]\,t\,dt \]
-over the contour $\mathscr{c}$ that runs as follows:
-\begin{enumerate}
-\item Leftward along $(0, \infty) + (-\pi + \theta)i$.
-\item Upward along $(-\pi + \theta, \pi + \theta)i$.
-\item Rightward along $(0, \infty) + (\pi + \theta)i$.
-\end{enumerate}
-Since the integrand is an odd function, the upward part of the path integrates to zero. Since the integrand is also $2\pi i$-periodic, the leftward and rightward parts of the integral collapse to
-\begin{align}
-K_0(z) & = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t + \pi i)\right]\,\pi i\,dt \notag - \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[z \cosh(t - \pi i)\right]\,\pi i\,dt \notag \\
-& = \frac{1}{2\pi i} \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,2\pi i\,dt \notag \\
-& = \int_{\mathcal{J}^0_{t, 0}} \exp\left[-z \cosh(t)\right]\,dt \label{int:k0_cosh_old} \\
-& = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}, \notag
-\end{align}
-with $s = e^t$. This is a special case of formula~10.32.9 from \cite{dlmf}.
-
-To confirm that the calculation above is consistent with Section~\ref{countable-cover}, use formulas \eqref{eq: K_j_mu at 1} and \eqref{eq: K_j_mu at -1} to get
-\begin{align*}
-K_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
-& \hphantom{=} - \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta
-\end{align*}
-The hypergeometric function in the integrand can be simplified away using identity~15.4.13 from \cite{dlmf}, leaving an expression that makes the $\zeta_{\pm 1}^{1/2}$ singularities of the integrand even more apparent: \textcolor{magenta}{[result is right, but reasoning is wrong: integrals can't be directly combined, because they use different contours]}
-\begin{equation}\label{eqn:borel_bessel0}
-K_0(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
-\end{equation}
-We could get the same result from equation~\eqref{int:k0_cosh} by trigonometric substitution. This is a special case of formula~10.32.8 from \cite{dlmf}.
-\begin{verify}
-\par
-For odd $j$, with $-\eta^2 = \tfrac{1}{2} - \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at 1} gives \textcolor{GreenYellow}{(we were missing a factor of two in identity~15.4.13, so the highlighted factors of $1/2$ should be removed)}
-\begin{align*}
-K^{(j)}_0(z) & = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta \\
-& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} \\
-& = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-& = -\frac{1}{2} \textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
-& = -\textcolor{GreenYellow}{\frac{1}{2}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
-\end{align*}
-This is off by a sign from what we expect, but the sign could be accounted for by the branch cuts in the square roots.
-For even $j$, with $-\eta^2 = \tfrac{1}{2} + \tfrac{\zeta}{2}$, equation~\eqref{eq: K_j_mu at -1} gives
-\begin{align*}
-K^{(j)}_0(z) & = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2},\;\frac{1}{2};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta \\
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} (1 + \eta^2)^{-1/2} d\zeta \\
-& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} \textcolor{GreenYellow}{\frac{1}{2}} \left(\frac{1}{2} - \frac{\zeta}{2}\right)^{-1/2} d\zeta \\
-& = \color{DarkViolet}\textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left[\left(-\frac{1}{2}-\frac{\zeta}{2}\right)  \left(\frac{1}{2} - \frac{\zeta}{2}\right)\right]^{-1/2} d\zeta  \\
-& =  \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{4}+\frac{\zeta^2}{4}\right)^{-1/2} d\zeta  \\
-& = \color{DarkViolet} \textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta \\
-& = \color{DarkViolet} -\textcolor{GreenYellow}{\frac{1}{2}} 3 \int_{\mathcal{J}^{\theta+\pi}_{\zeta, 1}} e^{z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
-%%& = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \textcolor{Tomato}{i} \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} \frac{\textcolor{Tomato}{i}}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2} d\zeta \textcolor{Tomato}{\quad\text{(is this justified?)}} \\
-%%& = \textcolor{Tomato}{-}\frac{3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(\frac{\zeta^2}{4}-\frac{1}{4}\right)^{-1/2} d\zeta \\
-%%& = \textcolor{Tomato}{-}\frac{2 \cdot 3}{4} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} (\zeta^2 - 1)^{-1/2} d\zeta
-\end{align*}
-$\int_{-1}^{e^{i\theta}\infty} = \int_{-1}^{e^{-i\theta}\infty}+2 \int_{1}^{\infty}$
-
-We can also verify equation \eqref{eqn:borel_bessel0} using the thimble projection formula, \eqref{eqn:formula-proof}. From the expression of $K_0$ 
-\begin{equation}
-K_0(z)=\int_0^{\infty} \exp(-z\cosh(t)) dt,
-\end{equation}
-we set $\zeta=\cosh(t)$. Choosing a branch for the square root
-\begin{align*}
-d\zeta & = \sinh(t) dt\\
-& =  \sqrt{\zeta^2-1} \, dt
-\end{align*}
-we finally get 
-\[\int_{\mathcal{J}^0_{\zeta, 1}} e^{-z\zeta} \frac{d\zeta}{\sqrt{\zeta^2-1}}\]
-\end{verify}
-\color{black}
 %

### 2024-05-04 exp-resurgence.tex
Revise "A flavor of resurgence" a bit

@@
 
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, as the Stokes constants are the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula (in particular, they are integers in a suitable normalization), see \cite[Section 5]{pham} and \cite[Chapter ??]{Arnold}.
-However, in the Airy--Lucas example, $f$ is not Morse (unless $n=3$), hence we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
-\textcolor{orange}{ I think we should argue we have the action of the permutation which leaves the base unchanged but gives a }
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \textcolor{orange}{[typically]} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
+Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~\textcolor{orange}{??}]{Arnold}.
+However, in the Airy--Lucas example, $f$ is not Morse unless $n=3$.
+Hence, we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
+\textcolor{orange}{[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]}
 %

### 2024-05-04 exp-resurgence.tex
Revise unshifted thimble projection derivation

@@
 In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
-In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
+In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see \cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
 
@@
 \begin{remark}\label{rmk:1/2-deriv}
-\textcolor{orange}{[Spirit of the remark: if you want to run the argument above for $\Phi_\alpha$, you can, but there is one subtlety you should be aware of\ldots]} For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
+\color{Navy}
+For some applications, it is more convenient to work with $\Phi_\alpha=z^{-1/2}I_\alpha$, whose asymptotic series has integer powers.
+The argument we use to prove of Theorem~\ref{thm:maxim-proof} can also be used to show that $\Phi_\alpha$ is Borel regular, but the thimble projection formula is trickier in this case.
+Proposition~\ref{prop:L-int-op} tells us that $\Phi_\alpha = \laplace^\theta_{\zeta, \alpha} \phi_\alpha$ for
+\[\phi_\alpha \defeq \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_\alpha. \]
+To get the thimble projection formula for $\phi_\alpha$, take the $1/2$ fractional integral of both sides:
+\begin{align*}
+    \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha &= \fracderiv{-1}{\zeta}{\alpha} \, \iota_\alpha \\
+    & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
+    & = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
+\end{align*}
+The second term vanishes because $\mathcal{C}_\alpha^\theta(\alpha)$ is a single point, leaving
+\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu. \]
+The $1/2$ fractional derivative is a left inverse of the $1/2$ fractional integral. Applying it to both sides, we find that
+\begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
+\color{RoyalBlue}
+For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
 The proof follows the same argument we use in the proof on Theorem~\ref{thm:maxim-proof} for $I_\alpha$, but there is one subtlety to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
-Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha} \, \iota_\alpha \]
+Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_\alpha \]
 Then, we can take the $1/2$ fractional integral on both sides:
@@
 \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
+\color{black}
 \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}

### 2024-05-04 exp-resurgence.tex
Make old text and brainstorms hideable
Also add draft environment.

@@
 
-% hideable to-do notes
+% hideable to-do notes and brainstorming
 \newif\ifshowtodo
@@
 \newenvironment{todo}{\color{Coral}}{\color{black}}
+\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
 \else
 \NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
+\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
 \fi
 
-% drafting environments
-%%\usepackage{environ} % to hide verifications
-%%\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
-%%\newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+% hideable old text
+\newif\ifshowold
+\showoldtrue
+\ifshowold
+\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
+\else
+\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
+\fi
+
+% more drafting environments
+\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
+\newenvironment{revised}{\color{DarkBlue}}{\color{black}}
 
@@
 \textcolor{orange}{[Plentiful, novel examples.]}
-\color{RoyalBlue}\par
+\begin{old}\par
 First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
@@
 The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
-\color{black}
+\end{old}
 \subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
@@
 \end{definition}
-\color{RoyalBlue}\par
+\begin{old}\par
 Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
@@
 I_\alpha(z)\defeq\int_{\mathcal{C}_a^\theta}e^{-zf}\nu.
-\end{equation}
-Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
-\textcolor{RoyalBlue}{[say more about this?]}.
-\textcolor{orange}{[As a start\ldots]} We recall the well-known result\color{black}
+\end{equation}\end{old}
+\begin{draft}Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
+\begin{todo}[say more about this?]\end{todo}.
+\textcolor{orange}{[As a start\ldots]} We recall the well-known result\end{draft}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
@@
 %\color{black}
-\color{RoyalBlue}
+\begin{draft}
 \textcolor{orange}{[Shorten, but maybe keep the basics.]} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
@@
 \textcolor{magenta}{Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.}
-\color{black}
+\end{draft}
 %% the following remark has been moved to Section of the proof
@@
 %
-\textcolor{orange}{[Revise\ldots]}\textcolor{RoyalBlue}{In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.}
+\begin{draft}In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.\end{draft}
 
@@
 \textcolor{orange}{[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]}
-\color{RoyalBlue}\par
+\begin{old}\par
 However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
 This is an advantage of resurgence techniques compared to the usual Borel summation method.
-\color{black}
+\end{old}
 %
@@
 %
-\color{DarkBlue}
+\begin{revised}
 Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
-A thimble integral's asymptotic expansion is typically divergent, \textbf{[but can be recovered using Borel summation]}
-\color{black}
+A thimble integral's asymptotic expansion is typically divergent, \begin{draft}[but can be recovered using Borel summation]\end{draft}
+\end{revised}
 
@@
 
-\color{BlueViolet}
-\begin{itemize}
+\begin{brainstorm}
 \item In fact, the thimble integral is almost a Laplace transform (cite Pham and point to thimble projection formula in this paper)
@@
 %%\end{itemize}
-\end{itemize}
+\end{brainstorm}
+\begin{brainstorm}
 \color{DarkTurquoise}\par
-\begin{itemize}
 \item Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions
 \item {[Toy model of situations where there's no well-defined thimble---like infinite-dimensional path integrals---or where the integral doesn't quite look like a thimble integral---like state integral in Chern-Simons.]}
-\end{itemize}
-
-This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
+\end{brainstorm}
+
+\begin{draft}This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
 In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms.
 We prove, from this, that they are Borel regular functions.
-In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
-
-\color{RoyalBlue}
+In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).\end{draft}
+
+\begin{old}
 \subsubsection*{Old stuff to distribute among new sections}
@@
 %    
-\color{black}
+\end{old}
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 where $\mathsf{R}$ is the $180^\circ$ rotation that exchanges $\zeta = 0$ with $a$. In other words, $\mathsf{R}^*\zeta = \zeta(a) - \zeta$.
-\color{DarkTurquoise}
-\begin{itemize}
+\begin{brainstorm}
 \item Given a function $f$ on $B$, we will write $f'$ and $f''$ to denote the pullbacks of $f$ to the first and second factors, respectively, of $B \times B$.
@@
 \[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]
-\end{itemize}
-
-\textcolor{orange}{\ldots} defined as
+\item \textcolor{orange}{\ldots} defined as
 \[ \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'', \]
 where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \textcolor{orange}{[check]}.
-\color{black}
+\end{brainstorm}
 \end{definition}
@@
 \textcolor{orange}{[add proof for $\alpha\neq 0$]}
-\color{DarkTurquoise}
-\begin{align*}
+\begin{brainstorm}
+\item \begin{align*}
 \laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & \defeq \left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta \right)\left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \psi\,d\zeta \right) \\
@@
 \end{align*}
-Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \textcolor{orange}{[with $\zeta' + \zeta'' = \zeta$]}
+\item Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \textcolor{orange}{[with $\zeta' + \zeta'' = \zeta$]}
 \begin{align*}
@@
 \end{align*}
-\color{black}
+\end{brainstorm}
 \begin{verify}
@@
 
-\textcolor{DarkBlue}{On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.}
-\par\textcolor{RoyalBlue}{In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.}
+\begin{revised}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.\end{revised}
+\begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
 \textcolor{magenta}{[actually need $\Omega_0$ in lemma]}
@@
 is a $\C$-algebra isomomorphism, with inverse defined in Proposition~\ref{prop:inverse_laplace_analytic}. 
-\end{corollary}
-
+\end{corollary}\end{old}
+%
 \subsubsection*{The Borel transform as algebra isomomrphism}
+%
 The Borel transform $\borel_\zeta$ is defined on the space of formal power series $z^{-1}\C\llbracket z^{-1}\rrbracket$, which is a $\C$-algebra, with product given by the Cauchy product of formal power series.
@@
 If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge.
-\textcolor{LimeGreen}{These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.} Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
+\begin{old}\textcolor{LimeGreen}{These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.}\end{old} Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
 They are characterized by the factorial growth of their coefficients.
@@
 \[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
-\par\textcolor{RoyalBlue}{Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
-The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.}
+\begin{brainstorm}
+\item Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
+The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
+\end{brainstorm}
 
@@
 % \end{remark}
-\color{RoyalBlue}
+\begin{old}
 We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ as convolution product.
@@
 %
-\color{black}
+\end{old}
 \section{Proof of main results}\label{sec:proof_main_results}
@@
 \end{proof}
-\color{RoyalBlue}
+\begin{old}
 \textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
 Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
-\color{black}
+\end{old}
 \textcolor{orange}{[Add flavor text]}
@@
 
-\textcolor{RoyalBlue}{[Analytic/position version starts here.]} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\series{\iota}_\alpha$.
+\begin{todo}[Analytic/position version starts here.]\end{todo} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\series{\iota}_\alpha$.
 We can rewrite the Taylor series for $\nu$ as
@@
 
-\color{RoyalBlue}
+\begin{old}
 Lemma~\ref{lem:thimble_proj_formula-proof} tells us that
@@
 %%\end{align*}
-\color{black}
+\end{old}
 \end{proof}
 \begin{remark}\label{rmk:1/2-deriv}
-\color{Navy}
+\begin{revised}
 For some applications, it is more convenient to work with $\Phi_\alpha=z^{-1/2}I_\alpha$, whose asymptotic series has integer powers.
@@
 \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
-\color{RoyalBlue}
+\end{revised}
+\begin{old}
 For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
@@
 \textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
+\end{old}
 \end{remark}
@@
 
-\textcolor{Navy}{Initially, the function $\int_{\mathcal{C}_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_j(\zeta)$.
+\begin{revised}Initially, the function $\int_{\mathcal{C}_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_j(\zeta)$.
 Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}_j(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\mathcal{C}_j(\zeta)$ come together, telling us that.}
+At a critical point of $f$, the ends of the homotoped path $\mathcal{C}_j(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
 \end{remark}
-\textcolor{orange}{
+\begin{todo}
 \begin{corollary}\label{simple-res-thimble}
@@
 \end{proof}
-}
+\end{todo}
 \begin{remark}\label{rmk:Pham formula}
@@
 %
-\textcolor{PaleVioletRed}{[Up to now, we've treated the Airy-Lucas functions as separate elements of a frame of solutions.
+\begin{brainstorm}
+\item Up to now, we've treated the Airy-Lucas functions as separate elements of a frame of solutions.
 Using the idea of resurgence, we see that they are actually more closely related.
-You can recover the frame from any one of its elements\ldots]}
-%%In Sections~\ref{confirmation-borel-regularity}\;--\;\ref{contour-argument-AL}, we
-
-\color{RoyalBlue}
-In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
-In both cases we find
-\color{black}
+You can recover the frame from any one of its elements\ldots
+\end{brainstorm}
+\begin{draft}In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
+In both cases we find\end{draft}
 \begin{align*}
@@
 
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \textcolor{orange}{[typically]} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
+It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \begin{revised}typically\end{revised} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
 Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~\textcolor{orange}{??}]{Arnold}.
@@
 We can confirm this result, and find the correct normalization, using the thimble projection formula:
-\color{RoyalBlue}
+\begin{old}
 \begin{align*}
@@
 \end{align*}
-\color{DarkBlue}
+\end{old}
+\begin{revised}
 \begin{align*}
@@
 \end{align*}
-\color{black}
-The factor of \textcolor{DarkBlue}{$e^{i\pi/3} - 1$} \textcolor{RoyalBlue}{$e^{i\pi/3}$} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
-
-\color{RoyalBlue}
-namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter. 
+\end{revised}
+The factor of \begin{revised}$e^{i\pi/3} - 1$\end{revised} \begin{old}$e^{i\pi/3}$\end{old} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
+\begin{brainstorm}
+\item namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
+\end{brainstorm}
 \end{itemize}
@@
 \end{align*}
-\textcolor{RoyalBlue}{\begin{align*}
+\begin{old}\begin{align*}
 i\sqrt{3}\,I(z) & = 2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big) \\
@@
 & = e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}
-\end{align*}}
+\end{align*}\end{old}
 \end{verify}
@@
 \textcolor{orange}{[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]}
-\color{LimeGreen}
+\begin{old}
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 \end{align*}
-\color{black}
+\end{old}
 % \subsubsection{An eye on resurgence}\label{apx:eye-res-airy}

### 2024-05-04 exp-resurgence.tex
Put to-do comments in to-do environments

@@
 
-\textcolor{orange}{[Plentiful, novel examples.]}
+\begin{todo}[Plentiful, novel examples.]\end{todo}
 \begin{old}\par
@@
 \begin{todo}[say more about this?]\end{todo}.
-\textcolor{orange}{[As a start\ldots]} We recall the well-known result\end{draft}
+\begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
@@
 Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]}
+\begin{todo}[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]\end{todo}
 \end{lemma}
@@
 \begin{theorem}\label{thm:maxim}
-If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: \textcolor{magenta}{[change restatement to match]}
+If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: \begin{todo}[change restatement to match]\end{todo}
 \begin{enumerate}
@@
 \begin{draft}
-\textcolor{orange}{[Shorten, but maybe keep the basics.]} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
+\begin{todo}[Shorten, but maybe keep the basics.]\end{todo} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
 %\[
@@
 
-\textcolor{magenta}{Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.}
+\begin{todo}[Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.]\end{todo}
 \end{draft}
@@
 %
+\begin{draft}
 \paragraph{New and old examples}
 %
-We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals \textcolor{VioletRed}{[These examples are all closely related; they're not just examples of second-order ODEs]}: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
-\begin{todo}the anharmonic oscillator...).\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals \begin{todo}[These examples are all closely related; they're not just examples of second-order ODEs]\end{todo}: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
+\begin{todo}[the anharmonic oscillator\ldots]\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
@@
 \subsection{Organization of the paper}
-\textcolor{orange}{[Revise\ldots]} The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
+The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
 This could help the reader to contextualize our results in the literature.
@@
 We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-\textcolor{red}{Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.}
+\begin{todo}[Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.]\end{todo}
+\end{draft}
 %
@@
 
-\textcolor{orange}{[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]}
+\begin{todo}[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]\end{todo}
 \begin{old}\par
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.}
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
+\begin{todo}[Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}
 \subsubsection{Thimble integrals in physics}
@@
 In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion~\cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}.
-\color{orange}
+\begin{todo}
 For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\color{black}
+\end{todo}
 %
@@
 
-\textcolor{orange}{[Keep revising\ldots]}
+\begin{todo}[Keep revising\ldots]\end{todo}
 
@@
 For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\textcolor{orange}{Take a look at Witten's paper on knots} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly.
+\begin{todo}Take a look at Witten's paper on knots\end{todo} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly.
 However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we are looking for.
-In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.\textcolor{Maroon}{This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.}
-
-In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.\textcolor{orange}{add references---Maxim's mirror symmetry talk, Varchenko}.} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of \textcolor{magenta}{$e^{i\theta}\infty$} under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
+In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.
+\begin{todo}[This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.]\end{todo}
+
+In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
+\begin{todo}[Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of \begin{draft}$e^{i\theta}\infty$\end{draft} under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
 Generic directions correspond to $\theta\neq \arg (\alpha-\beta)$.
@@
 Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
-Along $\mathcal{C}$, we have \textcolor{orange}{where does the estimate come from?}
+\begin{draft}Along $\mathcal{C}$, we have \begin{todo}[where does the estimate come from?]\end{todo}
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
@@
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big). \]
-\textcolor{orange}{Why on $\mathcal{C}$ the real part of $z$ is bounded like that?}
+\begin{todo}[Why on $\mathcal{C}$ the real part of $z$ is bounded like that?]\end{todo}\end{draft}
 %%Choose a path $\textcolor{magenta}{\mathcal{C}}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
@@
 
-\textcolor{DarkBlue}
+\begin{revised}
 We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
@@
 for any $\tau \in \R\setminus\Z$.
-\color{black}
+\end{revised}
 \subsubsection{Change of translation chart}\label{transl-borel}
@@
 \subsubsection{Action on translations in the frequency domain}
-\textcolor{Pink}{[Optional section; used in theory of difference equations in the frequency domain]} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
+\begin{todo}[Optional section; used in theory of difference equations in the frequency domain]\end{todo} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
 It turns out that
@@
 \[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]
-\item \textcolor{orange}{\ldots} defined as
+\item \textcolor{orange}{[\ldots]} defined as
 \[ \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'', \]
-where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \textcolor{orange}{[check]}.
+where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \begin{todo}[check]\end{todo}.
 \end{brainstorm}
@@
 for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
-\textcolor{orange}{[add proof for $\alpha\neq 0$]}
+\begin{todo}[Add proof for $\alpha\neq 0$.]\end{todo}
 \begin{brainstorm}
@@
 \end{align*}
-\item Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \textcolor{orange}{[with $\zeta' + \zeta'' = \zeta$]}
+\item Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \begin{todo}[with $\zeta' + \zeta'' = \zeta$]\end{todo}
 \begin{align*}
@@
 \end{align*}
-\textcolor{orange}{[see Thm 5.25 \cite{diverg-resurg-i}]}
+\textcolor{orange}{See Theorem 5.25 of \cite{diverg-resurg-i}}
 \end{verify}
@@
 For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by \textcolor{magenta}{$\ast_\zeta$ [coordinate added]}, following the standard convention.   
+In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[coordinate added]\end{todo}, following the standard convention.   
 \end{remark}
@@
 \begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
-\textcolor{magenta}{[actually need $\Omega_0$ in lemma]}
+\begin{todo}[actually need $\Omega_0$ in lemma]\end{todo}
 \begin{lemma}
-If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \textcolor{magenta}{[no; revise]} under the convolution product $\ast_{\zeta, \alpha}$.
+If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \begin{todo}[no; revise]\end{todo} under the convolution product $\ast_{\zeta, \alpha}$.
 \textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
@@
 \end{align*}
-\textcolor{orange}{[\ldots]}
+\begin{todo}[\ldots]\end{todo}
 \end{proof}
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-Noting that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \textcolor{magenta}{[check]},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
+Noting that \begin{draft}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{draft},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
 \begin{align*}
@@
 From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
- \textcolor{orange}{[Transition text]}
+\begin{todo}[Transition text]\end{todo}
 %%%\begin{itemize}
@@
 \end{old}
-\textcolor{orange}{[Add flavor text]}
+\begin{todo}[Add flavor text]\end{todo}
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
@@
 \end{proof}
-\textcolor{orange}{[Add flavor text]}
+\begin{todo}[Add flavor text]\end{todo}
 \begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
@@
 
-By the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} \textcolor{magenta}{[define $\approx$]}
+By the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} \begin{todo}[define $\approx$]\end{todo}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
@@
 \begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
-\color{black}
-\textcolor{orange}{[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]}
+\begin{todo}[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]\end{todo}
 \end{old}
@@
 
-The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \textcolor{magenta}{space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]} of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \begin{draft}***\end{draft} \begin{todo}space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]\end{todo} of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
@@
 It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \begin{revised}typically\end{revised} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
-Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~\textcolor{orange}{??}]{Arnold}.
+Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[\begin{todo}Chapter~??\end{todo}]{Arnold}.
 However, in the Airy--Lucas example, $f$ is not Morse unless $n=3$.
 Hence, we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
-\textcolor{orange}{[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]}
+\begin{todo}[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]\end{todo}
 %
@@
 Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}, indexed by the fourth roots of $\omega^2$.
-\par\textcolor{orange}{[Stokes? Thimbles? Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$.]}
+\begin{todo}\par[Stokes? Thimbles? Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$.]\end{todo}
 %\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}
@@
 %
-\textcolor{orange}{[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]}
+\begin{todo}[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]\end{todo}
 \begin{old}
@@
 \subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
-\textcolor{orange}{[Convert to new version]} Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \mathcal{C}_1$ to a contour \textcolor{magenta}{[rephrase in terms of ray]} $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \mathcal{C}_1$, we have
+\begin{todo}[Convert to new version]\end{todo} Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
+Projecting $z^{-1/3} \mathcal{C}_1$ to a contour \begin{todo}[rephrase in terms of ray]\end{todo} $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \mathcal{C}_1$, we have
 \begin{equation}\label{integral:mod-bessel-zeta}
@@
 Let us assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
+\begin{todo}[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]\end{todo}
 \begin{center}
@@
 \end{align*}}
-\textcolor{orange}{[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]}
+\begin{todo}[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]\end{todo}
 The thimble $\mathcal{C}_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
@@
 
-\textcolor{orange}{[Need a transition here.]} In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions.
+\begin{todo}[Need a transition here.]\end{todo} In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions.
 He starts with the formal trans-monomial solutions of the Airy equation:
@@
 
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product: \textcolor{orange}{[which convolution is this?]}
+By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product: \begin{todo}[which convolution is this?]\end{todo}
 

### 2024-05-04 exp-resurgence.tex
Make draft version
Set stroke for tubular neighborhood

@@
 \newif\ifshowverify
-\showverifytrue
+\showverifyfalse
 \ifshowverify
@@
 \newif\ifshowunstable
-\showunstabletrue
+\showunstablefalse
 \ifshowunstable
@@
 \newif\ifshowtodo
-\showtodotrue
+\showtodofalse
 \ifshowtodo
@@
 \newif\ifshowold
-\showoldtrue
+\showoldfalse
 \ifshowold
@@
 \title{The regularity of ODEs and thimble integrals \\
-with respect to Borel summation}
+with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}}
 %%\color{Tan} Borel summation as a regularization, and \\
@@
 \begin{fiber}
-\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
+\fill[pwbeige!30, draw=pwbeige!60, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
 \genfibercontent

### 2024-05-26 exp-resurgence.tex
Divide up tasks

@@
 \usepackage{amsthm}
+\usepackage[square,numbers,sort,compress]{natbib}
 \usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
@@
 \newif\ifshowverify
-\showverifyfalse
+\showverifytrue
 \ifshowverify
@@
 \newif\ifshowunstable
-\showunstablefalse
+\showunstabletrue
 \ifshowunstable
@@
 \newif\ifshowtodo
-\showtodofalse
+\showtodotrue
 \ifshowtodo
@@
 \newif\ifshowold
-\showoldfalse
+\showoldtrue
 \ifshowold
@@
 A one-dimensional {\em thimble integral} has the form
-\[ I = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu, \]
+\[ I_a = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu, \]
 where $\nu$ is a holomorphic $1$-form on $X$, $a$ is a critical point of $f$, and $\mathcal{C}^\theta_a$ is the Lefschetz thimble that runs through $a$ in direction $\theta$ with a chosen orientation.
+Since $I_a$ depends on the frequency coordinate $z$, it is a holomorphic function on the frequency domain.
 \end{definition}
@@
 \end{equation}\end{old}
-\begin{draft}Our main results show that $I_\alpha$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
-\begin{todo}[say more about this?]\end{todo}.
+\begin{draft}Our main results show that $I_a$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
+\begin{todo}[no need to say more; just get to the results]\end{todo}.
 \begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
-A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
+A function $\iota_a$ with $I_a = \laplace_{\zeta, \alpha}^\theta \iota_a$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula}
-    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
 \end{equation}
@@
 %\end{remark}
-Then, the Borel regularity of thimble integrals is established by the following theorem: 
+\begin{draft}Then, the Borel regularity of thimble integrals is established by the following theorem:\end{draft}
 \begin{theorem}\label{thm:maxim}
-If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: \begin{todo}[change restatement to match]\end{todo}
+If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly: \begin{todo}[change restatement to match]\end{todo}
 \begin{enumerate}
-\item\label{part-1} The function $I_\alpha$ has an asymptotic expansion $\series{I}_\alpha \defeq \aexp^\theta I_\alpha$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
-\item\label{part-2} The Borel transform $\series{\iota}_\alpha \defeq \borel_\zeta \series{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3} The sum of $\series{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
-Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.
+\item\label{part-2} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
+\item\label{part-3} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+Its Laplace transform along that ray is well-defined, and equal to $I_a$.
 \end{enumerate}
@@
 \begin{draft}
-\begin{todo}[Shorten, but maybe keep the basics.]\end{todo} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
+\begin{todo}[Shorten or remove.
+The original intent was to highlight similarity with Borel regularity diagram, but the statement of the theorem now matches the diagram closely.]\end{todo} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
 %\[
@@
 Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\series{\iota}_\alpha$.
-
-\begin{todo}[Discuss where to find proofs, similarly to \texttt{reg-sing-volterra}.]\end{todo}
 \end{draft}
@@
 %
-We illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals \begin{todo}[These examples are all closely related; they're not just examples of second-order ODEs]\end{todo}: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}).
-\begin{todo}[the anharmonic oscillator\ldots]\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
+\begin{todo}[First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
+\begin{todo}[Transition: many well-known examples reduce to special cases of these\ldots]\end{todo} the Airy--Lucas functions (Section~\ref{example_AL}), the Airy function (Appendix~\ref{airy-appendix}).
+\begin{todo}[the anharmonic oscillator---see ``A Primer on Resurgent Transseries,'' appendices B--C]\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
 On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
+\begin{todo}[Mention that some classical integral formulas for modified Bessel functions are actually thimble integrals.]\end{todo} The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
 In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
@@
 %
-Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
+\begin{todo}[The examples we study all involve {\em resurgent functions} in the position domain.] [Say a tiny bit about what resurgence does or is good for.]\end{todo} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
 The resurgence of linear ODEs have been intensively studied \cite{loday1994stokes,diverg-resurg--ii} and many results are also known for non-linear ODEs \cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
@@
 %%\textcolor{orange}{[Where does resurgence come in?]}
-
-\begin{todo}[Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain. New section?]\end{todo}
+\subsubsection{Equivalence to Riemann--Hilbert problems}
+\begin{todo}\textbf{V}\end{todo} \begin{todo}[Update title.] [Focus on Kontsevich and Soibelman's example, where the R--H problem turns out to be solvable.] [Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain.
+New section?]\end{todo}
+Add brief description of general RH, when it can be solves like Boalch, KS, Tom, GMN
 \begin{old}\par
@@
 %
-\subsection{Borel regularity for thimble integrals}
+\subsection{Thimble integrals}
 %
@@
 \subsubsection{Thimble integrals in physics}
-In physics, thimble integrals play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion~\cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}.
-\begin{todo}
-For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\end{todo}
+\begin{todo}\textbf{A} [Thimble integrals in optics?
+Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} In physics, thimble integrals play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
+In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion, see some examples in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
+For instance, in $\mathcal{N}=2$ $d=2$ QFT given by Landau--Ginzburg theories, Cecotti--Vafa showed that instantons can be computed using Picard--Lefschetz formulas, indeed the so called wall--crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91}.
+Similarly, in the study of complex Chern--Simons theory, the path integral can be studied using a decomposition in thimble integrals and arguing as in the finite dimesional set-up~\cite{gukov-marino-purtrov-resurgence,Witten}.
+\textcolor{orange}{[Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]}
 %
@@
 
-Lefschetz thimbles for $f$ with direction $\theta$ represent classes in the ``rapid decay homology'' group $H^\theta_N(X,f)$.
+Lefschetz thimbles for $f$ with direction $\theta$ represent classes in the ``rapid decay homology'' group $H^\theta_N(X,f)$~\cite{pham}\cite[Section~1.1]{fresan-notes}.
 Roughly speaking, this group describes homology relative to the region where $\Re(e^{-i\theta} f)$ is large and positive.
@@
 Like solutions of level~$1$ ODEs, thimble integrals often exhibit the Stokes phenomenon.
-The Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles.
-Finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$.
-
+For one dimensional thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
+More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent developement~\cite{kontsevich2024holomorphic}).
 %%Equivalently, using the Borel regularity result \textcolor{magenta}{[do we really want this theorem, rather than the thimble projection formula?]} Theorem~\ref{thm:maxim}, we can express thimble integrals as Laplace transforms and reconstruct the monodromy of $H^\theta_N(X,f)$ from the associated Stokes constants.
@@
 Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
-A thimble integral's asymptotic expansion is typically divergent, \begin{draft}[but can be recovered using Borel summation]\end{draft}
+A thimble integral's asymptotic expansion is typically divergent, but the integral can often be recovered using Borel summation.
+\begin{draft}[but can be recovered using Borel summation]\end{draft}
 \end{revised}
 
-\begin{todo}[Keep revising\ldots]\end{todo}
+\begin{todo}\textbf{A} [Keep revising. We agree that this outline is good.]\end{todo}
 
@@
 \end{brainstorm}
-\begin{brainstorm}
-\color{DarkTurquoise}\par
-\item Classical examples of $1$-dimensional thimble integrals (with polynomial $f$) are special functions
-\item {[Toy model of situations where there's no well-defined thimble---like infinite-dimensional path integrals---or where the integral doesn't quite look like a thimble integral---like state integral in Chern-Simons.]}
-\end{brainstorm}
 
@@
 In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).\end{draft}
-
-\begin{old}
-\subsubsection*{Old stuff to distribute among new sections}
-Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion (see also \cite{Berry_Howls,Berry1991,costin_kruskal,Howls97,Howls,pham1988resurgence}).
-For instance, in complex Chern--Simons theory, one could decompose the path integral in thimble integrals and arguing as in the finite dimesional set-up to study the Witten--Reshetikhin--Turaev invariants of $3$ manifolds \cite{gukov-marino-purtrov-resurgence,Witten}.
-\begin{todo}Take a look at Witten's paper on knots\end{todo} More generally, we could think of a problem that is known to admit a thimble integral solution but that's hard to be defined explicitly.
-However, we know the perturbative expansion of the expected solution; then Borel regularity tells us that the Borel sum of the pertubative series is the solution we are looking for.
-In fact, the Laplace transform ray (namely the ray along which the Laplace trasnform is defined) is often a ``collapsed'' thimble.
-\begin{todo}[This is the bit about turning a perturbative series back into a thimble integral, taking advantage of the fact that the Laplace transform ray is often a ``collapsed'' thimble.]\end{todo}
-
-In the algebraic geometric set-up, namely when $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
-\begin{todo}[Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}} In fact, the thimbles represent classes in the homology $H^{B,\theta}_N(X,f)$ which are relative to the preimage of \begin{draft}$e^{i\theta}\infty$\end{draft} under the funtion $f$, for a generic direction $\theta$.\footnote{The relative homology $H_i^{\theta}(X,f)$ is defined as the limit as $c\to e^{i\theta}\infty$, of $H_i^{\theta}(X,f^{-1}(S_c^+))$, where $S_c^+=\lbrace \zeta\in\C \vert \Re \zeta> c\rbrace$.
-Generic directions correspond to $\theta\neq \arg (\alpha-\beta)$.
-} Furthermore, if $f$ has non-degenerate critical points, they form a basis for $H_N^{B,\theta}(X,f)$.
-Then varying $\theta$, $H_N^{B,\theta}(X,f)$ forms a local system over $S^1=\R/2\pi \Z$ singular at $\theta=\arg(\alpha-\beta)$, and whose monodromy can be computed by Picard--Lefschetz formula (we refer to \cite[Section~1]{Arnold} and \cite[Section~3.3, Part II]{pham}).
-Equivalently, the monodromy data can be computed as the Stokes phenomena for Laplace transforms; indeed as a consequence of our Borel regularity result Theorem~\ref{thm:maxim}, thimble integrals can be turned into Laplace transforms.
-
-Classical examples of thimble integrals (with polynomial $f$) are special functions, thus the Borel summability properties of their asymptotics can be studied either analytically (through the \textit{thimble projection reasoning} see the discussion in Section~\ref{sec:examples}) or geometrically (in terms of a certain Riemann--Hilbert problem \cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}).
-
-In the $N$-dimensional analog of our set-up \ref{borel-reg:explanatory-power} the thimbles are actually steepest descent paths from the critical points; thus the asymptotic behaviour as $z \to \infty$ in direction $\theta$ can be studied using the steepest descent method \cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.\footnote{In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).} However, the asymptotics of thimble integrals is typically a formal power series, and choosing a suitable resummation technique one should be able to recover the original function.
-This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
-In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms, hence they are Borel regular functions.
-In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see \cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).
-
- %In addition, they typically come as \textcolor{orange}{[Stokes phenomena in one case ... in the other is ...]}
-
-%\textcolor{orange}{hyperasymptotics \cite{Berry_Howls,Berry1991,Howls97,Howls}}
-%\color{DarkTurquoise}
-%These questions have been classically addressed by Pham \cite[Section 3.3]{pham}, Malgrange \cite[Theorem 6]{Malgrange22}, Berry and Howls \cite{Berry_Howls} and Sternin and Shatalov \cite[Theorem 3.9 and 3.10]{sternin1995borel}.
-In addition, the study of thimble integrals plays an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-Physicists often use Borel summation, resurgence and related techniques to assign values to these integrals \cite{costin_kruskal,pham1988resurgence}.
-%\color{black}
-%%Our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see Fenyes's lecture \cite{Fenyes-ihes-lecture}).
-In a nutshell, we use that thimble integrals are generalized Laplace transforms, to show they are indeed Borel regular functions.
-%    
-\end{old}
+%
 \section{The Laplace and Borel transforms}\label{sec:Laplace-Borel-general}
@@
 \begin{proof}
-Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
+\begin{todo}\textbf{A} [Use $a$ subscript instead of $\alpha$ for $I$ and $\iota$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
 Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.

### 2024-05-26 exp-resurgence.tex
Work on thimble integrals: physics and asymptotics

@@
 \subsubsection{Thimble integrals in physics}
-\begin{todo}\textbf{A} [Thimble integrals in optics?
-Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} In physics, thimble integrals play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities.
-In this context, physicists often use Borel summation, resurgence and related techniques to assign values to these integrals going beyond their pertubative expansion, see some examples in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
+\begin{revised}In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\begin{todo}[cite IH\'{E}S lecture]\end{todo}.
+For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.\end{revised} \begin{todo}\textbf{A} [Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} \begin{revised}In the path integral picture of quantum mechanics, which draws inspiration from wave optics,\end{revised} infinite-dimensional \begin{revised}thimble integrals\end{revised} are supposed to give the expectation values of observable quantities.
+In this context, \begin{revised}the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.
+Some examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.\end{revised}
 For instance, in $\mathcal{N}=2$ $d=2$ QFT given by Landau--Ginzburg theories, Cecotti--Vafa showed that instantons can be computed using Picard--Lefschetz formulas, indeed the so called wall--crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91}.
@@
 Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
-A thimble integral's asymptotic expansion is typically divergent, but the integral can often be recovered using Borel summation.
-\begin{draft}[but can be recovered using Borel summation]\end{draft}
+The asymptotic expansion of a thimble integral is typically divergent, but its Borel sum often matches the integral it came from.
+In other words, thimble integrals tend to be Borel regular.
+
+To understand why this happens, we first shift our focus from the thimble integral to the corresponding analytic object in the position domain.
+The integral contains a hint about where to find this analytic object: the thimble itself, which is a real-analytic submanifold of a complex manifold.
+When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula-proof} to turn it into a function whose Laplce transform is the thimble integral.
+\begin{todo}[Add footnote about results under more general conditions.]\end{todo}
+
+\begin{todo}\textbf{[Alternate phrasing]}Our first step toward understanding why is to express the thimble integral as the Laplace transform of an analytic function on the position domain.
+A thimble integral contains a hint about where to find corresponding analytic object in the position domain: the thimble itself, which is a real-analytic submanifold of a complex manifold.
+\textbf{[\ldots]}\end{todo}
 \end{revised}
 
-\begin{todo}\textbf{A} [Keep revising. We agree that this outline is good.]\end{todo}
+\begin{todo}\textbf{A} [Started revising. How do you like this version?]\end{todo}
 

### 2024-06-01 exp-resurgence.tex
Index by critical point, not critical value, in thimble integral proofs

@@
 \end{definition}
+\begin{todo}[\textbf{A} \textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}
 \begin{old}\par
@@
 \begin{theorem}\label{thm:maxim}
-If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly: \begin{todo}[change restatement to match]\end{todo}
+If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
 \begin{enumerate}
@@
 \begin{draft}
-\begin{todo}[Shorten or remove.
+\begin{todo}[Shorten or remove---leaning toward remove.
+Go for consistency with the end of the ODE results section.
 The original intent was to highlight similarity with Borel regularity diagram, but the statement of the theorem now matches the diagram closely.]\end{todo} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
@@
 %
-\begin{draft}In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.\end{draft}
+\begin{todo}\textbf{A} [Revise]\end{todo} \begin{draft}In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.\end{draft}
 
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity at $\infty$ often exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
+Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
 Formally, this behavior is captured in a {\em formal integral} solution: an expression
@@
 %%\textcolor{orange}{[Where does resurgence come in?]}
-\subsubsection{Equivalence to Riemann--Hilbert problems}
-\begin{todo}\textbf{V}\end{todo} \begin{todo}[Update title.] [Focus on Kontsevich and Soibelman's example, where the R--H problem turns out to be solvable.] [Kontsevich and Soibelman: Riemann-Hilbert problem in analytic frequency domain from Stokes constants in the formal position domain.
-New section?]\end{todo}
-Add brief description of general RH, when it can be solves like Boalch, KS, Tom, GMN
+\subsubsection{Solving Riemann--Hilbert problems}
+Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
+In this case, solutions of the ODE are (local) flat sections for the corresponding connection.
+Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem.
+
+To formulate the Riemann--Hilbert problem, we should fix the asymptotic behvaiour of the solution as $z\to0,\infty$ and its discontinuities, namely the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray.
+Then a solution is given by piecewise analytic function, holomorphic away from the rays and with the prescirbed asymptotics and discontinuities.
+
+Solutions of Riemann--Hilbert problems were computed explicitly in many examples~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
+In particular, in~\cite[Section~6.2.1]{kontsevich2022analyticity} the authors discuss a Riemann--Hilbert problem for thimble integrals in terms of analytic wall-crossing structures conjecturally describing resurgent series.
+
+\begin{brainstorm}
+\item A level~1 ODE can be seen as the flatness condition for sections of a meromorphic connection.
+\item As a result, we can occasionally use the theory of meromorphic connections to solve level~1 ODEs.
+\item Briefly recall what a Riemann--Hilbert problem is.
+\item Describe Maxim's formalism for understanding R--H problems through wall-crossing
+\item Discuss examples where the Riemann--Hilbert problem corresponding to an ODE can be solved.
+\begin{itemize}
+\item Dubrovin
+\item Kontsevich--Soibelman
+\item Bridgeland
+\item Gaiotto--Moore--Nietzke
+\end{itemize}
+\end{brainstorm}
 \begin{old}\par
@@
 \subsubsection{Thimble integrals in physics}
-\begin{revised}In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\begin{todo}[cite IH\'{E}S lecture]\end{todo}.
+\begin{revised}In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
 For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.\end{revised} \begin{todo}\textbf{A} [Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} \begin{revised}In the path integral picture of quantum mechanics, which draws inspiration from wave optics,\end{revised} infinite-dimensional \begin{revised}thimble integrals\end{revised} are supposed to give the expectation values of observable quantities.
-In this context, \begin{revised}the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.
-Some examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.\end{revised}
-For instance, in $\mathcal{N}=2$ $d=2$ QFT given by Landau--Ginzburg theories, Cecotti--Vafa showed that instantons can be computed using Picard--Lefschetz formulas, indeed the so called wall--crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91}.
-Similarly, in the study of complex Chern--Simons theory, the path integral can be studied using a decomposition in thimble integrals and arguing as in the finite dimesional set-up~\cite{gukov-marino-purtrov-resurgence,Witten}.
-\textcolor{orange}{[Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]}
+In this context, \begin{revised}the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.\end{revised}
+For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
+Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91}.
+Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}.
+Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
+\begin{todo}[Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
 %
@@
 In other words, thimble integrals tend to be Borel regular.
-
-To understand why this happens, we first shift our focus from the thimble integral to the corresponding analytic object in the position domain.
+Theorem~\ref{thm:maxim} explains why this happens in the one-dimensional case.
+
+To prove Theorem~\ref{thm:maxim}, we first shift our focus from the thimble integral to the corresponding analytic object in the position domain.
 The integral contains a hint about where to find this analytic object: the thimble itself, which is a real-analytic submanifold of a complex manifold.
-When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula-proof} to turn it into a function whose Laplce transform is the thimble integral.
-\begin{todo}[Add footnote about results under more general conditions.]\end{todo}
-
-\begin{todo}\textbf{[Alternate phrasing]}Our first step toward understanding why is to express the thimble integral as the Laplace transform of an analytic function on the position domain.
-A thimble integral contains a hint about where to find corresponding analytic object in the position domain: the thimble itself, which is a real-analytic submanifold of a complex manifold.
-\textbf{[\ldots]}\end{todo}
-\end{revised}
-
-\begin{todo}\textbf{A} [Started revising. How do you like this version?]\end{todo}
+When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula} to turn it into a function whose Laplce transform is the thimble integral.
+This formula generalizes to higher-dimensional thimbles and thimbles based at degenerate critical points~\cite[Section 1.2.2]{mistegard_phdthesis}.\end{revised}
+
+\begin{todo}\textbf{A} [Done.]\end{todo}
 
@@
 Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
-\begin{draft}Along $\mathcal{C}$, we have \begin{todo}[where does the estimate come from?]\end{todo}
+\begin{draft}Along $\mathcal{C}$, we have \begin{todo}[\textbf{A} where does the estimate come from?]\end{todo}
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
@@
 \laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
-\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
+\borel_{\zeta}\big[e^{-\alpha z}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
 \end{align*}
@@
 We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
-We conclude that
+We conclude, in particular, that
 \[\borel_{\zeta}\big[e^{-z\alpha}z^{-\tau-1}\big] = \frac{\zeta_\alpha^\tau}{\Gamma(\tau+1)}\]
@@
 \subsubsection{Action on translations in the frequency domain}
-\begin{todo}[Optional section; used in theory of difference equations in the frequency domain]\end{todo} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
+\begin{todo}[Explain that this section is optional, used in theory of difference equations in the frequency domain]\end{todo} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
 It turns out that
@@
 \[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]
-\item \textcolor{orange}{[\ldots]} defined as
-\[ \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'', \]
+\item \begin{todo}\textbf{A} [Draft definition section in this alternate notation]\end{todo} Alternate notation: \textcolor{orange}{[\ldots]} defined as
+\begin{equation}
+    \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'',
+\end{equation}
 where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \begin{todo}[check]\end{todo}.
+\item Draw diagram
 \end{brainstorm}
@@
 \[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}] \]
+\begin{todo}
+\textbf{A} \textbf{V} [Find and prove correct statement. Maybe it should be\ldots]
+\[ \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}] = \laplace_{\zeta_\alpha,0}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
+\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
+\end{todo}
 for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
@@
 For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[coordinate added]\end{todo}, following the standard convention.   
+In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[Add coordinate to $\ast$ elsewhere too]\end{todo}, following the standard convention.   
 \end{remark}
@@
 
-\begin{revised}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.\end{revised}
+\begin{revised}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.\end{revised} \begin{todo}Write more if needed, and also make sure it's actually correct.
+The old text below has mistakes.\end{todo}
 \begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
@@
 In addition, on both $\C\llbracket\zeta\rrbracket$ and $\C\llbracket z^{-1}\rrbracket$ there is the natural product given by the Cauchy product of formal power series.
-However, the Borel transform does not extend to a $\C$-algebra isomorphism, because $\borel_\zeta\big(\series{\Phi}\series{\Psi}\big)$ is different from the Cauchy product $\borel_\zeta\series{\Phi}\borel_\zeta\series{\Psi}$.
-%
-In order to view the Borel transform as an algebra isomorphism, we should consider a different product on $\C\llbracket\zeta\rrbracket$, that is the convolution product of formal power series defined as follows:
+However, the Borel transform does not extend to a $\C$-algebra isomorphism, because $\borel_\zeta\big(\series{\Phi}\series{\Psi}\big)$ is different from the Cauchy product $(\borel_\zeta \series{\Phi})(\borel_\zeta \series{\Psi})$.
+
+To see the Borel transform as an algebra isomorphism, we must use a different product on $\C\llbracket\zeta\rrbracket$: the convolution product for formal power series.
+Let $\zeta$ be a coordinate on $B$.
+For any integers $m, n$,%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then
+\begin{equation}\label{eq: convolution_formal}
+\frac{\zeta^m}{m!} \ast_{\zeta} \frac{\zeta^n}{n!} = \frac{\zeta^{m+n+1}}{(m+n+1)!} \,.
+\end{equation}
+\begin{verify}
+\begin{align*}
+\frac{\zeta^m}{m!} \ast_\zeta \frac{\zeta^n}{n} & = \borel_\zeta \left[ \laplace_{\zeta, 0}\left(\frac{\zeta^m}{m!}\right) \laplace_{\zeta, 0} \left(\frac{\zeta^n}{n!}\right) \right] \\
+& = \borel_\zeta[z^{-m-n-2}] \\
+\end{align*}
+\end{verify}
 \begin{definition}\label{def:convolution_formal}
-Let $\zeta$ be a coordinate on $B$.
-For any integers $m, n$%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then
-\begin{equation}\label{eq: convolution_formal}
-\frac{\zeta^m}{m!} \ast_{\zeta, 0} \frac{\zeta^n}{n!} \defeq \frac{\zeta^{m+n+1}}{(m+n+1)!} \,.
-\end{equation}
-\begin{verify}
-\begin{align*}
-\frac{\zeta^m}{m!} \ast \frac{\zeta^n}{n} & = \borel_\zeta \left[ \laplace_{\zeta, 0}\left(\frac{\zeta^m}{m!}\right) \laplace_{\zeta, 0} \left(\frac{\zeta^n}{n!}\right) \right] \\
-& = \borel_\zeta[z^{-m-n-2}] \\
-\end{align*}
-\end{verify}
-This extends to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$ by countable linearity:
-\begin{align*}
-   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}\,.
-\end{align*}
-Furthemore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta,0}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
-\[\frac{\zeta^n}{n!}\ast_{\zeta,0}\delta\defeq\frac{\zeta^n}{n!}\,,\]
+We extend the convolution product $\ast_\zeta$ by countable linearity to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$:
+\begin{align*}
+   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast_\zeta\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast_\zeta\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}\,.
+\end{align*}
+Furthemore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
+\[\frac{\zeta^n}{n!}\ast_{\zeta}\delta\defeq\frac{\zeta^n}{n!}\,,\]
 in other words, $\delta$ is the unit for the convolution. 
@@
 \begin{equation}
-\frac{\zeta_\alpha^m}{m!} \ast_{\zeta_\alpha, 0} \frac{\zeta_\alpha^n}{n!} \defeq \frac{\zeta_\alpha^{m+n+1}}{(m+n+1)!} \,.
+\frac{\zeta_\alpha^m}{m!} \ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!} \defeq \frac{\zeta_\alpha^{m+n+1}}{(m+n+1)!} \,.
 \end{equation}
@@
 The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
-    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi}\textcolor{magenta}{\ast}\borel_\zeta\series{\Psi}.\]
+    \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
 \end{prop}
@@
 &=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
+&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
 &=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
-&=\borel_\zeta\series{\Phi} \textcolor{magenta}{\ast} \borel_\zeta\series{\Psi}\,.
+&=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
 %&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
@@
 % \end{definition}
-Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
+\begin{todo}[Shorten to a reminder that $z$ is an almost-global coordinate on cotangent spaces, so this also works in other fibers.]\end{todo} Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
 %We can further generalize this result to transseries:
@@
 \begin{brainstorm}
-\item Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
+\item \begin{todo}[Find right phrasing]\end{todo} Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
 The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
@@
 \[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =\alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
-where $p$ is any point on the position domain $B$.%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+where $p$ is any point on the position domain $B$.
+\begin{todo}[If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
 Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
@@
         z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
-        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast \phi\Big]\\
+        &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
         &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
@@
 \begin{align*}
-\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta')^{-\mu} \frac{{\zeta'}^k}{\Gamma(k+1)}\,d\zeta' \\
+\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta')^{-\mu} \frac{(\zeta')^k}{\Gamma(k+1)}\,d\zeta' \\
 & = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
@@
 % \end{remark}
+\begin{todo}[Not needed?]\end{todo}
 \begin{old}
@@
 \begin{proof}
-    Let us recast the integral $I_\alpha$ into the position domain.
-As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\mathcal{C}_\alpha^\theta(\zeta)$ sweep backward along $\mathcal{C}^-_\alpha(\zeta)$ and forward along $\mathcal{C}^+_\alpha(\zeta)$, respectively.
+We first recast the integral $I_\alpha$ into the position domain.
+As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\mathcal{C}_a^\theta(\zeta)$ sweep backward along $\mathcal{C}^-_a(\zeta)$ and forward along $\mathcal{C}^+_a(\zeta)$, respectively.
 Hence, we have
 \begin{align*}
-I_\alpha(z) & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
-& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha^\theta(\zeta)}\,d\zeta.
+I_a & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
+& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta.
 \end{align*}
@@
 \end{proof}
-We will now prove that $I_\alpha$ is Borel regular:
+We will now prove that $I_a$ is Borel regular:
 \begin{theorem}[restatement of~\ref{thm:maxim}]\label{thm:maxim-proof}
-If the integral defining $I_\alpha$ is absolutely convergent, then $I_\alpha$ is Borel regular. More explicitly: 
+If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
 \begin{enumerate}
-\item\label{part-1-prf} The function $I_\alpha$ has an asymptotic expansion $\series{I}_\alpha \defeq \aexp^\theta I_\alpha$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
-\item\label{part-2-prf} The Borel transform $\series{\iota}_\alpha \defeq \borel_\zeta \series{I}_\alpha$ converges near $\zeta=\alpha$.
-\item\label{part-3-prf} The sum of $\series{\iota}_\alpha$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
-Its Laplace transform along that ray is well-defined, and equal to $I_\alpha$.
+\item\label{part-2-prf} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
+\item\label{part-3-prf} The sum of $\series{\iota}_a$ can be analytically continued along the ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+Its Laplace transform along that ray is well-defined, and equal to $I_a$.
 \end{enumerate}
@@
 \begin{todo}\textbf{A} [Use $a$ subscript instead of $\alpha$ for $I$ and $\iota$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
-Let $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
-By changing the sign of $\tau$, we can arrange for it to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_\alpha$ and $\mathcal{C}^+_\alpha$, respectively.
+Let $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
+By changing the sign of $\tau$, we can arrange for it to be valued in $(-\infty, 0]$ and $[0,\infty)$ on $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$, respectively.
 Since $\nu$ is holomorphic, we can express it as a Taylor series
@@
 
-Let us write $\approx$ when two functions are asymptotic at all orders around the base point; by the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
+We write $\approx$ to say that two functions are asymptotic at all orders around the base point \begin{todo}[what point?]\end{todo}.
+By the method of steepest descentz,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{z \alpha} I_\alpha \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
+\[ e^{z \alpha} I_a \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 as $z \to \infty$. Plugging in the Taylor series for $\nu$, we get
 \begin{align*}
-e^{z \alpha} I_\alpha & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
+e^{z \alpha} I_a & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
 & = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau.
@@
 \begin{align*}
-e^{z \alpha} I_\alpha & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
+e^{z \alpha} I_a & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
 & = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
@@
 
-The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha} I_\alpha(z)$.
+The annoying $e^{-z\varepsilon^2/2}$ correction terms are crucial for the convergence of the sum, but we can get rid of them and still have a formal series asymptotic to $e^{-z \alpha} I_a$.
 In other words,
@@
 %\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
-The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~(5)]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{z\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
-Hence, defining the formal series $\series{I}_\alpha$
-\[\series{I}_\alpha(z):=e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
-we get $\series{I}_\alpha\in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1-prf}.
-
-Using the porperties of the Borel tranform acting on trans-mononials \ref{sec:action_transseries} we get 
-\begin{align*}
-\series{\iota}_\alpha & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
+The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~5]{chiani-dardari-book}, allowing the simpler estimate
+\[ e^{z\alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
+Hence, defining the formal series $\series{I}_a$
+\[\series{I}_a \defeq e^{-z\alpha} z^{-1/2}\, \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-n}\]
+we get $\series{I}_a \in e^{-z\alpha}z^{-1/2}\C\llbracket z^{-1}\rrbracket$. This ends the proof of part \ref{part-1-prf}.
+
+Using the properties of the Borel tranform acting on trans-mononials \ref{sec:action_transseries} we get 
+\begin{align*}
+\series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
 &= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
@@
 
-\begin{todo}[Analytic/position version starts here.]\end{todo} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_\alpha$ at $\zeta=\alpha$ agrees with $\series{\iota}_\alpha$.
+\begin{todo}[Analytic/position version starts here.]\end{todo} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_a$ at $\zeta=\alpha$ agrees with $\series{\iota}_a$.
 We can rewrite the Taylor series for $\nu$ as
@@
 \end{align*}
-In particular, $\series{\iota}_\alpha$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_\alpha$.
-%Thus, we can take the Laplace transform of $\phi_j$ and we find
+In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_a$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
 %\begin{align*}
@@
 \begin{revised}
-For some applications, it is more convenient to work with $\Phi_\alpha=z^{-1/2}I_\alpha$, whose asymptotic series has integer powers.
-The argument we use to prove of Theorem~\ref{thm:maxim-proof} can also be used to show that $\Phi_\alpha$ is Borel regular, but the thimble projection formula is trickier in this case.
-Proposition~\ref{prop:L-int-op} tells us that $\Phi_\alpha = \laplace^\theta_{\zeta, \alpha} \phi_\alpha$ for
-\[\phi_\alpha \defeq \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_\alpha. \]
-To get the thimble projection formula for $\phi_\alpha$, take the $1/2$ fractional integral of both sides:
-\begin{align*}
-    \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha &= \fracderiv{-1}{\zeta}{\alpha} \, \iota_\alpha \\
+For some applications, it is more convenient to work with $\Phi_a \defeq z^{-1/2} I_a$, whose asymptotic series has integer powers.
+The argument we use to prove of Theorem~\ref{thm:maxim-proof} can also be used to show that $\Phi_a$ is Borel regular, but the thimble projection formula is trickier in this case.
+Proposition~\ref{prop:L-int-op} tells us that $\Phi_a = \laplace^\theta_{\zeta, \alpha} \phi_a$ for
+\[\phi_a \defeq \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_a. \]
+To get the thimble projection formula for $\phi_a$, take the $1/2$ fractional integral of both sides:
+\begin{align*}
+    \fracderiv{-1/2}{\zeta}{\alpha} \phi_a & = \fracderiv{-1}{\zeta}{\alpha} \, \iota_a \\
     & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
-    & = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
-\end{align*}
-The second term vanishes because $\mathcal{C}_\alpha^\theta(\alpha)$ is a single point, leaving
-\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu. \]
+    & = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
+\end{align*}
+The second term vanishes because $\mathcal{C}_a^\theta(\alpha)$ is a single point, leaving
+\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_a = \int_{\mathcal{C}_a^\theta(\zeta)}\nu. \]
 The $1/2$ fractional derivative is a left inverse of the $1/2$ fractional integral. Applying it to both sides, we find that
-\begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
+\begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right).\end{equation}
 \end{revised}
@@
 Let us say $\mathcal{J}_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
-As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\mathcal{C}_\alpha^\theta(\beta)$ in $X$.
-This lets us analytically continue $\int_{\mathcal{C}_\alpha^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
+As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\mathcal{C}_a^\theta(\beta)$ in $X$.
+This lets us analytically continue $\int_{\mathcal{C}_a^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
 Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
@@
 
-Let us calculate the jump of $\int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
+We will calculate the jump of $\int_{\mathcal{C}_a^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
 Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
-The jump is then given by \[\int_{\mathcal{C}_\alpha^\theta(\beta^+)} \nu - \int_{\mathcal{C}_\alpha^\theta(\beta^-)} \nu\]
+The jump is then given by \[\int_{\mathcal{C}_a^\theta(\beta^+)} \nu - \int_{\mathcal{C}_a^\theta(\beta^-)} \nu\]
 and it is 
@@
 
-\begin{revised}Initially, the function $\int_{\mathcal{C}_j(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha_j, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_j(\zeta)$.
-Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}_j(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}_j(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\mathcal{C}_j(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
+\begin{revised}Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$.
+Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$.
+At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
 \end{remark}
@@
 \begin{remark}\label{rmk:Pham formula}
-    When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}$ explicitly as 
+\begin{todo}[Add critical point index to $\iota$ and $I$?]\end{todo} When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}$ explicitly as
 \begin{equation}\label{eqn:Pham}

### 2024-06-01 exp-resurgence.tex
Switch more thimble indices to critical point

@@
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_\alpha$ as the Laplace transform of a function $\iota_\alpha$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.
+The first step will be to rewrite $I_a$ as the Laplace transform of a function $\iota_a$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula-proof}
-A function $\iota_\alpha$ with $I_\alpha = \laplace_{\zeta, \alpha}^\theta \iota_\alpha$ is given by the {\em thimble projection formula}
+A function $\iota_a$ with $I_a = \laplace_{\zeta, \alpha}^\theta \iota_a$ is given by the {\em thimble projection formula}
 \begin{equation}\label{eqn:formula-proof}
-    \iota_\alpha = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
 \end{equation}
@@
 \begin{proof}
-We first recast the integral $I_\alpha$ into the position domain.
+We first recast the integral $I_a$ into the position domain.
 As $\zeta$ goes rightward from $\alpha$ with angle $\theta$, the start and end points of $\mathcal{C}_a^\theta(\zeta)$ sweep backward along $\mathcal{C}^-_a(\zeta)$ and forward along $\mathcal{C}^+_a(\zeta)$, respectively.
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_\alpha^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_\alpha^\theta(\zeta)}.
+{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
 \end{equation}
@@
     & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
-    & = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
+    & = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_a^\theta(\alpha)}\nu.
 \end{align*}

### 2024-06-01 exp-resurgence.tex
Correct even more indices to critical points

@@
 \subsection{Borel regularity for thimble integrals}\label{borel-reg-thimble}
-
-Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
-Let $I_\alpha$ be the thimble integral
+%
+\begin{draft}Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
+Let $I_a$ be the thimble integral
 \begin{equation}\label{exp-int}
-I_\alpha \defeq \int_{\mathcal{C}_a^\theta} e^{-zf} \nu
-\end{equation}
-where $\mathcal{C}_a^\theta$ is the thimble through the critical point $a$ and $\alpha=f(a)$.
+I_a \defeq \int_{\mathcal{C}_a^\theta} e^{-zf} \nu
+\end{equation}
+where $\mathcal{C}_a^\theta$ is the thimble through the critical point $a$.
+Let $\alpha$ be the associated critical value, $f(a)$.
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_a$ as the Laplace transform of a function $\iota_a$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.
+The first step will be to rewrite $I_a$ as the Laplace transform of a function $\iota_a$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.\end{draft}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula-proof}
@@
 In other words,
-\[ e^{z \alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\[ e^{z \alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 To see why, cut the sum off after $N$ terms, and observe that
@@
 taking the positive branch of the square root on $\mathcal{C}^+_a$ and the negative branch on $\mathcal{C}^-_a$.
-Plugging this into our expression for $\iota_\alpha$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
-\begin{align*}
-\iota_\alpha & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \mathcal{C}_a(\zeta)}^{\operatorname{end} \mathcal{C}_a(\zeta)} \\
+Plugging this into our expression for $\iota_a$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
+\begin{align*}
+\iota_a & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \mathcal{C}_a(\zeta)}^{\operatorname{end} \mathcal{C}_a(\zeta)} \\
 & = \sum_{m \ge 0} b_m^a \Big( [2\zeta_\alpha]^{(m - 1)/2} - (-1)^{m-1}[2\zeta_\alpha]^{(m - 1)/2} \Big) \\

### 2024-06-02 exp-resurgence.tex
Revise intro to thimble integral results

@@
 Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory.
-In particular, we highlight results---like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals---that can be proven in purely analytic ways.
+In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.
 
@@
 
-\begin{todo}[Plentiful, novel examples.]\end{todo}
+\begin{todo}[Plentiful, novel examples.]\end{todo} Our third goal is to
 \begin{old}\par
@@
 A one-dimensional Lefschetz thimble is determined up to orientation by the critical point $a$ that it runs through and the direction $\theta$ of the ray that it projects to, so we will often denote it with a symbol like $\mathcal{C}^\theta_a$.
+\begin{revised}Because a Lefschetz thimble can only run through a single critical point $a$, the ray that it projects to cannot touch any critical value except $f(a)$.\end{revised}
 \begin{center}
@@
 \end{definition}
-\begin{todo}[\textbf{A} \textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}
+\begin{todo}[\textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}
 \begin{old}\par
-Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
+\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
 We will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
@@
 \end{center}
-Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:
+\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:
 \begin{equation}
@@
 \begin{todo}[no need to say more; just get to the results]\end{todo}.
-\begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}
+\begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}\par
+\begin{revised}We will present a proof that one-dimensional thimble integrals are always Borel regular.
+The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.\end{revised}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
@@
 \begin{proof}
+\begin{todo}
+   \textbf{V} temptative proof
+   \end{todo}
+   First we notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
+   \begin{align*}
+       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta''\\
+       &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
+   \end{align*}
+   where $\zeta'=s\zeta_\alpha+\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
+   \begin{align*}
+       \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}]&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta, \alpha}{\psi}]\\
+       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
+       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi''\,ds 
+   \end{align*}
+   by exchanging the order of integration we find 
+   \begin{align*}
+        &=\int_0^1 ds\,\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z(\zeta_\alpha s+\alpha)} \phi' \psi'' \\
+        &=\int_0^1 ds\,\int_{\Gamma_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi' \psi'' 
+   \end{align*}
+   Exchanging one more time the order of integration we get
+    \begin{align*}
+        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi'\\
+        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,0}} dt\, e^{-zt} \phi\\
+   \end{align*}
+   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,0}$ as $s$ varies in $[0,1]$.
+\end{proof}
+\begin{proof}
 We just need to prove that
@@
 \begin{proof}
-\begin{todo}\textbf{A} [Use $a$ subscript instead of $\alpha$ for $I$ and $\iota$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
+\begin{todo}\textbf{V} [Check that $\alpha$ subscripts have been converted to $a$ for $I$, $\iota$, and $\mathcal{C}$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
 Let $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.

### 2024-06-02 exp-resurgence.tex
Go over new calculation of Laplace transform of convolution

@@
 \subsubsection{Solving Riemann--Hilbert problems}
-Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
+\begin{todo}[\textbf{A} Read through]\end{todo} Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
 In this case, solutions of the ODE are (local) flat sections for the corresponding connection.
@@
 \begin{prop}
-The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.
+\begin{todo}[Correct and rewrite!]\end{todo}
+\begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
+\begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
+\begin{todo}[\textbf{A} \textbf{V} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
+\begin{draft}
+\begin{align*}
+\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]
+\end{align*}
+\end{draft}
 \end{prop}
@@
 \begin{todo}
-   \textbf{V} temptative proof
+   \textbf{V} fix notation, add $\theta$
    \end{todo}
@@
         &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi'\\
-        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,0}} dt\, e^{-zt} \phi\\
-   \end{align*}
-   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,0}$ as $s$ varies in $[0,1]$.
+        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,\alpha}} dt\, e^{-zt} \phi\\
+   \end{align*}
+   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,\alpha}$ as $s$ varies in $[0,1]$.
+\begin{todo}[Check claim: as coordinates on the position domain, $t = \zeta'$.
+If true, clarify argument.]\end{todo}
 \end{proof}

### 2024-06-02 exp-resurgence.tex
Move statement that convolution preserves holomorphic L-infinity space

@@
 \end{definition}
+\begin{todo}[Show that Laplace transform preserves domain of Laplace transform]\end{todo}
+\begin{draft}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
+The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta, 0}$.\end{draft}
 \begin{prop}
@@
 \end{proof}
-\begin{proof}
-We just need to prove that
-\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}] \]
-\begin{todo}
-\textbf{A} \textbf{V} [Find and prove correct statement. Maybe it should be\ldots]
-\[ \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}] = \laplace_{\zeta_\alpha,0}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
-\[ \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}] = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta_\alpha,0}[{\psi}] \]
-\end{todo}
-for all $\phi, \psi$ with a well-defined Laplace transform. This can be shown by direct computation, done for instance in Theorem 2.39 of \cite{laplace-tfm} for $\alpha=0$.
-\begin{todo}[Add proof for $\alpha\neq 0$.]\end{todo}
-\begin{brainstorm}
-\item \begin{align*}
-\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & \defeq \left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta \right)\left( \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \psi\,d\zeta \right) \\
-& = \left( \int_{\mathcal{J}_{\zeta', \alpha}^\theta} e^{-z\zeta'} \phi'\,d\zeta' \right)\left( \int_{\mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta''} \psi''\,d\zeta'' \right) \\
-& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;d\zeta' \wedge d\zeta''.
-\end{align*}
-\item Since $d\zeta'' \wedge d\zeta'' = 0$, we can rewrite this as \begin{todo}[with $\zeta' + \zeta'' = \zeta$]\end{todo}
-\begin{align*}
-\laplace_{\zeta, \alpha}(\phi)\,\laplace_{\zeta,\alpha}(\psi) & = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z(\zeta' + \zeta'')}\,\phi'\,\psi''\;(d\zeta' + d\zeta'') \wedge d\zeta'' \\
-& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} e^{-z\zeta}\,\phi'\,\psi''\;d\zeta \wedge d\zeta'' \\
-& = \int_{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta} \big(e^{-z\zeta}\;d\zeta\big) \wedge \big(\phi'\,\psi''\;d\zeta''\big) \\
-& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \left(\int_{\substack{\mathcal{J}_{\zeta', \alpha}^\theta \times \mathcal{J}_{\zeta'', \alpha}^\theta \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\;d\zeta''\right) d\zeta \\
-& = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta}\,(\phi \ast_{\zeta, \alpha} \psi)\;d\zeta \\
-& = \laplace^\theta_{\zeta, \alpha}(\phi \ast_{\zeta, \alpha} \psi).
-\end{align*}
-\end{brainstorm}
-\begin{verify}
-\begin{align*}
-\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}](a)&= \int_{\mathcal{J}^\theta_{\zeta, \alpha}} e^{-z\zeta(a)} \left(\int_{\zeta=\alpha}^a \psi \mathsf{R}^*\phi\;d\zeta\right)\;d\zeta
-\end{align*}
-
-\begin{align*}
-\laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,\alpha}[{\psi}]&=\int_\alpha^\infty e^{-z t}\phi(t)dt \int_\alpha^\infty e^{-z u} \psi(u) du \\
-&=\int_\alpha^\infty \left(\int_\alpha^\infty  e^{-z (t+u)}\phi(t) \psi(u) du \right)dt \\
-&=\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
-\end{align*}
-Define $\psi(s)=0$ if $s<\alpha$, thus $\psi(s-t)=0$ if $s<t+\alpha$, 
-\begin{align*}
-\int_\alpha^\infty \left(\int_{t+\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt 
-\end{align*}
-Under the assumption that the integral is absolutely convergent, we can exchange the order of integration
-\begin{align*}
-\int_\alpha^\infty \left(\int_{\alpha}^\infty   e^{-z s} \psi(s-t) \phi(t) ds \right)dt &=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^\infty    \psi(s-t) \phi(t) dt \right)ds\\
-&=\int_\alpha^\infty e^{-z s} \left(\int_{\alpha}^s    \psi(s-t) \phi(t) dt \right)ds \\
-&=\int_\alpha^\infty e^{-z s} \phi\ast_{t,\alpha}\psi ds 
-\end{align*}
-\textcolor{orange}{See Theorem 5.25 of \cite{diverg-resurg-i}}
-\end{verify}
-\end{proof}
 %
@@
 
-\begin{revised}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$, and the Laplace transform is an algebra isomorphism.\end{revised} \begin{todo}Write more if needed, and also make sure it's actually correct.
-The old text below has mistakes.\end{todo}
+\begin{todo}Move before calculation of Laplace transform of convolution, write more if needed, and also make sure it's actually correct. The old text below has mistakes.\end{todo}
 \begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
@@
 &=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
-&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
+&=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
 &=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
@@
 where $p$ is any point on the position domain $B$.
-\begin{todo}[If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+\begin{todo}[\textbf{V} If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
 Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:

### 2024-06-02 exp-resurgence.tex
Drop old text from fractional integral section

@@
 \end{proof}
-% \begin{remark}
-% We notice that properties $(i)$ and $(ii)$ of Proposition~\ref{prop:frac-der-int-borel} are special cases of the convolution product: for every $\lambda\in\R\setminus\Z_{>0}$ 
-% \[\fracderiv{\lambda}{\zeta}{0}\big[\borel_\zeta\series{\Phi}\big]=\borel_\zeta \big[z^\lambda \series{\Phi}\big]=\borel_\zeta (z^\lambda)\ast \borel_\zeta\series{\Phi}.\]
-% \begin{verify}
-% \begin{align*}
-% \fracderiv{\tau}{\zeta}{0}\borel_\zeta\series{\Phi}=\borel_\zeta (z^\tau \series{\Phi})&=\borel_\zeta (z^\tau)\ast \borel_\zeta\series{\Phi}\\
-% &=\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\ast\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\\
-% &=\int_0^\zeta \frac{(\zeta')^{-\tau-1}}{\Gamma(-\tau)}\sum_{n= 0}^\infty a_n\frac{(\zeta-\zeta')^n}{n!}d\zeta'\\
-% &=\sum_{n= 0}^\infty\frac{a_n}{n!}\frac{1}{\Gamma(-\tau)}\zeta^{n-\tau}\frac{\Gamma(n+1)\Gamma(-\tau)}{\Gamma(n-\tau+1)}
-% \end{align*}
-% Recall from Lemma~\ref{lem:frac-deriv-Borel} that for every 
-% $\tau>0$ and $\tau\notin\Z_{>0}$, 
-% \[\frac{\zeta^{n-\tau}}{\Gamma(n-\tau+1)}=\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]
-% \]
-% and if $\tau<0$, by definition 
-% \[\fracderiv{\tau}{\zeta}{0}\Big[\frac{\zeta^n}{n!}\Big]=\frac{1}{\Gamma(-\tau)}\int_0^\zeta (\zeta')\frac{(\zeta-\zeta')^n}{n!}d\zeta'\]
-% therefore, we deduce $\fracderiv{\tau}{\zeta}{0}\borel_\zeta\series{\Phi}=\frac{\zeta^{\tau-1}}{\Gamma(-\tau)}\ast\borel_\zeta\series{\Phi}$. 
-% \end{verify}
-% \end{remark}
-\begin{todo}[Not needed?]\end{todo}
-\begin{old}
-We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ as convolution product.
-\begin{lemma}
-    Let us assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and $z$ to be a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
-    \[\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
-\end{lemma}
-\begin{proof}
-    First of all, notice that 
-    \begin{align*}
-    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi%=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi
-\end{align*}
-where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
-Then, by definition of fractional integral $\partial_{\zeta,\alpha}^{-\lambda}\phi$, we have
-\begin{align*}
-    \Big[\partial_{\zeta,\alpha}^{-\lambda}\phi\Big](p)=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi\, d\zeta=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p \mathsf{R}^{*}\zeta^{\lambda-1}\phi\, d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi\,.
-\end{align*}
-\end{proof}
-\begin{remark}
-
-\end{remark}
-% We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
-% \begin{align*}
-%     \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi%=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi
-% \end{align*}
-% where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
-Then, by definition of fractional integral $\partial_{\zeta,\alpha}^{-\lambda}\phi$, we have
-% \begin{align*}
-%     \borel_\zeta(z^{-\lambda}{\Phi})(p)=\frac{1}{\Gamma(\lambda)}\int_{\zeta=\alpha}^p (\zeta(p)-\zeta)^{\lambda-1}\phi\, d\zeta=\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\phi\,.
-% \end{align*}
-% Hence \[\borel_\zeta (z^{-\lambda})\ast_{\zeta,\alpha}\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
-% %However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
-% Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
-For every $\lambda\in (-1,\infty)$
-% \begin{multline*}
-%     \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
-%     =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
-% \end{multline*}
-% hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
-%
-%
-%
-\end{old}
+%
 \section{Proof of main results}\label{sec:proof_main_results}

### 2024-06-02 exp-resurgence.tex
Revise Pham's singularity formula

@@
 \begin{remark}
-In \cite{pham}, Pham describes this formula in a slightly different form, integrating the variation of $\nu/df$, instead of differentiating the integral as we do in equation~\ref{eqn:formula-proof}.
+In \cite{pham}, Pham describes this formula in a slightly different form, integrating the variation of $\nu/df$, instead of differentiating the integral as we do in equation~\eqref{eqn:formula-proof}.
 \end{remark}
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_\alpha(\zeta) = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
+{\iota}_\alpha = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
 \end{equation}
@@
 \begin{remark}\label{rmk:1/2-deriv}
-\begin{revised}
+\begin{todo}[\textbf{V} Read through, and remove \texttt{revised} if good]\end{todo}\begin{revised}
 For some applications, it is more convenient to work with $\Phi_a \defeq z^{-1/2} I_a$, whose asymptotic series has integer powers.
@@
 \begin{remark}\label{rmk:Pham formula}
-\begin{todo}[Add critical point index to $\iota$ and $I$?]\end{todo} When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write ${\iota}$ explicitly as
+When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} gives us an explicit expression for the singularity of the function $\iota_a$ from Lemma~\ref{lem:thimble_proj_formula-proof}.
+For some coefficients $c_k$ which depend on $f$, $\nu$, and the thimble $\mathcal{C}_a^\theta$, we have
 \begin{equation}\label{eqn:Pham}
-(-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
-\end{equation}
-for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\ell}$ be defined as
+\iota_a \in (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta_{\zeta, \alpha}^{(-N/2 - k)} + \mathcal{O}_{\zeta = \alpha},
+\end{equation}
+where the singularities
 \begin{equation*}
-\delta^{-\ell}:=\begin{cases}
-\frac{\zeta^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \ell\in\mathbb{N}^*\\
+\delta_{\zeta,\alpha}^{(-\ell)}:=\begin{cases}
+\displaystyle\frac{\zeta_\alpha^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta_\alpha)+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\in\mathbb{N}^*\\
 & \\
-\frac{(-\zeta)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \text{ hol. funct.} & \text{ if } \ell\notin \mathbb{N}^* 
+\displaystyle\frac{(-\zeta_\alpha)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\notin \mathbb{N}^* \,.
 \end{cases}
 \end{equation*}
-In particular, if $N=1$, the inverse Laplace transform of $I$ has a fractional power singularity of order $1/2$ at the origin, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
+can be seen as fractional derivatives of the Dirac delta distribution.
+In particular, if $N=1$, the inverse Laplace transform of the function $I_a$ from Equation~\eqref{exp-int} has a singularity of the form $\zeta_\alpha^{1/2}$, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
 %as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.

### 2024-06-06 exp-resurgence.tex
Fix the convolution prodcut

@@
 %\end{remark}
-\begin{draft}Then, the Borel regularity of thimble integrals is established by the following theorem:\end{draft}
+\begin{revised}Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.\end{revised}
 \begin{theorem}\label{thm:maxim}
@@
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
+\begin{todo}[Change $b$ to $\alpha$?]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
 Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$.
@@
 In particular, that subspace of holomorphic functions on $B$, it has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-\begin{definition}\label{def:convolution}
+\begin{old}
+    \begin{definition}%\label{def:convolution}
 Let $\phi,\psi$ be two holomorphic functions on $B$.
 Choose a translation cooridnate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
-\begin{equation}\label{eq:convolution_def}
+\begin{equation}%\label{eq:convolution_def}
 [\phi \ast_{\zeta, \alpha} \psi](a) := \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta,
@@
 The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta, 0}$.\end{draft}
+% \begin{prop}
+% \begin{todo}[Correct and rewrite!]\end{todo}
+% \begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
+% \begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
+% \begin{todo}[\textbf{A} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
+% \begin{draft}
+% \begin{align*}
+% \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]
+% \end{align*}
+% \end{draft}
+% \end{prop}
+\end{old}
+\begin{definition}\label{def:convolution}
+Let $\phi,\psi$ be two holomorphic functions on $B$.
+Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
+\begin{equation}\label{eq:convolution_def}
+\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta'
+\end{equation}
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is defined similalrly. \begin{todo}
+    Is it clear the convolution is holomorphic??
+\end{todo}  
+\end{definition}
+On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
+The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
+\begin{prop}\label{prop:convolution_iso_laplace}
+Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then 
+\begin{equation}
+    \laplace_{\zeta_\alpha,0}[\phi\ast_{\zeta_\alpha,0}\psi]=\laplace_{\zeta_\alpha,0}[\phi]\,\laplace_{\zeta_\alpha,0}[\psi]\,.
+\end{equation}
+\end{prop}
+\begin{proof}
+Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
+   \begin{align*}
+       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
+       &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
+   \end{align*}
+where $\zeta'=s\zeta_\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$.
+
+First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. Indeed it is uniform of exponential type
+\begin{align*}
+   \big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi'|\,|\psi''|\\
+   &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
+   & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}
+\end{align*}
+where $c''=\max\{c,c'\}$. \begin{todo}
+    How do we check it is locally integrable???
+\end{todo}
+%   
+Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
+     \begin{align*}
+       \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
+       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
+       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi' \psi''\,ds 
+   \end{align*}
+   by exchanging the order of integration we find 
+   \begin{align*}
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi'' \\
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z\zeta'' \frac{s}{1-s}} \phi' \psi'' 
+   \end{align*}
+   Setting $t=\zeta''\frac{s}{1-s}$ we find
+    \begin{align*}
+        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi''\,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z\zeta'' \frac{s}{1-s}} \phi'\\
+        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\mathcal{J}_{t,0}} dt\, e^{-zt} \phi\\
+   \end{align*}
+   where as $s$ varies in $[0,1]$ we get that $t$ follows the ray $\mathcal{J}_{t,0}$. 
+\end{proof}
+More generally we can show that the product of two Laplace transforms based at different points is the Laplce transform of the convolution.
 \begin{prop}
-\begin{todo}[Correct and rewrite!]\end{todo}
-\begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
-\begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
-\begin{todo}[\textbf{A} \textbf{V} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
-\begin{draft}
-\begin{align*}
-\laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]
-\end{align*}
-\end{draft}
+Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 
+\begin{equation}
+    \laplace_{\zeta,\alpha+\beta}[\phi\ast_{\zeta,\alpha+\beta}\psi]=\laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
+\end{equation}    
 \end{prop}
@@
 \begin{todo}
-   \textbf{V} fix notation, add $\theta$
+   \textbf{V} add $\theta$
    \end{todo}
-   First we notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-   \begin{align*}
-       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta''\\
-       &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
-   \end{align*}
-   where $\zeta'=s\zeta_\alpha+\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
-   \begin{align*}
-       \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta, \alpha}{\psi}]&=e^{-z\alpha}\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta, \alpha}{\psi}]\\
-       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
-       &=e^{-z\alpha}\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi''\,ds 
+  Notice that the convolution product can be rewritten by introducing the coordinates $\eta'=\zeta'-\beta$ and $\eta''=\zeta''+\beta$
+   \begin{align*}
+       \phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
+       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\,,
+   \end{align*}
+   where $\mathcal{S}'(\eta)$ is the line segment from $\eta'=\alpha$ to $\eta'=\zeta_\beta$ and simlarly, $\mathcal{S}''(\eta)$ is the line segment from $\eta''=\zeta_\alpha$ to $\eta''=\beta$.
+\begin{todo}\textbf{V} [explain why this choice of coords is better than $\eta'$ and $\eta''$]\end{todo} Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution
+    \begin{align*}
+       \phi \ast_{\zeta, \alpha+\beta} \psi
+       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\\
+       &=\zeta_{\alpha+\beta}\,\int_0^1 \phi' \psi''\,ds\,,
+   \end{align*}
+   where $\eta'=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta''=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
+     \begin{align*}
+       \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
+       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi' \psi''\,ds \\
+       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi' \psi''\,ds
    \end{align*}
@@
    \begin{align*}
-        &=\int_0^1 ds\,\int_{\Gamma_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z(\zeta_\alpha s+\alpha)} \phi' \psi'' \\
-        &=\int_0^1 ds\,\int_{\Gamma_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi' \psi'' 
-   \end{align*}
-   Exchanging one more time the order of integration we get
-    \begin{align*}
-        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z(\zeta'' \frac{s}{1-s}+\alpha)} \phi'\\
-        &=\int_{\Gamma_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\Gamma_{t,\alpha}} dt\, e^{-zt} \phi\\
-   \end{align*}
-   where we have introduced the coordinate $t=\zeta''\frac{s}{1-s}+\alpha$ which gives the ray $\Gamma_{t,\alpha}$ as $s$ varies in $[0,1]$.
-\begin{todo}[Check claim: as coordinates on the position domain, $t = \zeta'$.
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi' \psi'' \\
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta'',\beta}}d\eta''\,\frac{\eta''}{(1-s)^2}\,e^{-z\eta''} (\eta''-\beta) e^{-z( (\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi' \psi''\,,
+   \end{align*}
+   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta''}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta''-\beta}{1-s}$.
+Then, exchanging one more time the order of integration we get
+    \begin{align*}
+        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_0^1 ds\,\frac{\eta''-\beta}{(1-s)^2}e^{-z((\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi'\\
+        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_{\mathcal{J}_{t,\alpha}} dt\, e^{-zt} \phi\\
+   \end{align*}
+   where we have introduced the coordinate $t=(\eta''-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{t,\alpha}$ as $s$ varies in $[0,1]$.
+\begin{todo}[Check claim: as coordinates on the position domain, $t = \eta'$.
 If true, clarify argument.]\end{todo}

### 2024-06-14 exp-resurgence.tex
Mostly finalize thimble integral result section
Still need to decide on last paragraph.

@@
 
-\begin{todo}[Plentiful, novel examples.]\end{todo} Our third goal is to
+Our third goal is to illustrate the results we discuss with detailed examples involving a diversity of Borel regular functions.
+We treat several examples both as thimble integrals and as solutions of level~1 ODEs, so you can compare these parallel explanations of how Borel regularity arises.
+We include ODEs of both second degree and higher degree.
+Using the widely discussed example of the Airy function, we compare our treatment with other approaches and conventions found in the literature.
+
+\begin{draft}\begin{todo}\textbf{A}\end{todo} We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
+Our examples are in \begin{todo}???\end{todo}.
+Section~\begin{todo}???\end{todo} describes the layout of the paper in more detail.
+\end{draft}
 \begin{old}\par
@@
 A one-dimensional Lefschetz thimble is determined up to orientation by the critical point $a$ that it runs through and the direction $\theta$ of the ray that it projects to, so we will often denote it with a symbol like $\mathcal{C}^\theta_a$.
-\begin{revised}Because a Lefschetz thimble can only run through a single critical point $a$, the ray that it projects to cannot touch any critical value except $f(a)$.\end{revised}
+Because, by our definition, a Lefschetz thimble can only run through a single critical point $a$, the ray that it projects to cannot touch any critical value except $f(a)$.
 \begin{center}
@@
 \end{definition}
-\begin{todo}[\textbf{V} Check whether anything from the old text is missing from the revised text.]\end{todo}
-\begin{old}\par
-\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Consider a thimble integral of the form described in Section~\ref{borel-reg:explanatory-power}.
-We will define our setting in the language of translation surfaces, to make clear the connection with our geometric picture of the Laplace transform.
-The codomain of $f$ has a natural structure of translation surface---a Riemann surface carrying a holomorphic 1-form $d\zeta$, and $\zeta$ is a translation coordinate.
-\textcolor{NavyBlue}{[The important thing about $\C$, where $f$ takes values, is that it is a translation surface---\ldots]} For each critical point $a$, let $\mathcal{J}_\alpha^\theta$ be the ray going to infinity with an angle $\theta$ from the critical value $\alpha$, and let $\zeta_{\alpha}$ be the translation coordinate around $\mathcal{J}_\alpha^\theta$ which vanishes at $\alpha$.
-These are well-defined as long as $\mathcal{J}_\alpha^\theta$ misses the critical values of $f$.
-Then, the preimage $f^{-1}(\mathcal{J}_\alpha^\theta)$ is a bunch of disjoint curves (see Figure \ref{fig:thimble_vs_rays}), as long as $\mathcal{J}_\alpha^\theta$ misses the other critical values of $f$.
-The Lefschetz thimble $\mathcal{C}_a^\theta$ can be regarded as the component of $f^{-1}(\mathcal{J}_\alpha^\theta)$ that goes through $a$.
-\textcolor{orange}{We could orient the thimble so that shifting $\mathcal{C}_a$ to its left would make its projection run clockwise around $\mathcal{J}_\alpha$.
-However, this only seems to be possible when $X$ is 1-dimensional.}
-\begin{center}
-\includegraphics[width=6.5cm]{figures/rays_ge6.png}
-\hspace{0.5cm}
-\includegraphics[width=6.5cm]{figures/thimbles-n5.png}
-\captionof{figure}{The rays $\mathcal{J}^{\pi/8}_{\zeta, \pm 1}$ on the position domain, and their preimages in the $u$ plane.}\label{fig:thimble_vs_rays}
-\end{center}
-\begin{todo}[A: nothing in this paragraph is missing]\end{todo} Choose a critcal point $a$ of $f$, noting the associated critical value $\alpha = f(a)$, and let $I_\alpha$ be a thimble integral through the thimble $\mathcal{C}_a^\theta$:
-\begin{equation}
-I_\alpha(z)\defeq\int_{\mathcal{C}_a^\theta}e^{-zf}\nu.
-\end{equation}\end{old}
-\begin{draft}Our main results show that $I_a$ is Borel regular as a conseuqence of the fact that thimble integrals can be turned into a Laplace transform on the ray $f(\mathcal{C}_a^\theta)$.
-\begin{todo}[no need to say more; just get to the results]\end{todo}.
-\begin{todo}[As a start\ldots\end{todo} We recall the well-known result\end{draft}\par
-\begin{revised}We will present a proof that one-dimensional thimble integrals are always Borel regular.
-The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.\end{revised}
+We will present a proof that one-dimensional thimble integrals are always Borel regular.
+The proof hinges on the following well-known formula, which can be used to express any one-dimensional thimble integral as a Laplace transform.
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula}
@@
 where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
-Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\begin{todo}[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]\end{todo}
 \end{lemma}
-%\begin{remark}
-%The operator $\fracderiv{1/2}{\zeta}{\alpha}$ is the fractional derivative based at $\zeta = \alpha$, as defined in Section~\ref{L-int-op}:
-%\begin{align*}
-%\partial^{1/2}_{\zeta, \alpha} & \defeq \tfrac{\partial}{\partial \zeta} \, \partial^{3/2}_{\zeta, %\alpha} \\[2mm]
-%[\partial^{3/2}_{\zeta, \alpha} g](p) & \defeq \frac{1}{\Gamma(\tfrac{1}{2})} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} g\,d\zeta.
-%\end{align*}
-%\begin{verify}
-%\begin{align*}
-%[\partial^{0+1/2}_{\zeta, \alpha} f](p) & = \left(\tfrac{\partial}{\partial \zeta}\right)^{0+1} \partial^{1/2-1}_{\zeta, \alpha} \\
-%& = \left(\tfrac{\partial}{\partial \zeta(p)}\right)^{0+1} \frac{1}{\Gamma(1-1/2)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-1/2} f\,d\zeta
-%\end{align*}
-%\end{verify}
-%\end{remark}
-\begin{revised}Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.\end{revised}
+Notice that the path $\mathcal{C}_a^\theta(\zeta)$ used in the lemma starts and ends in $f^{-1}(\zeta)$.
+
+Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
 \begin{theorem}\label{thm:maxim}
@@
 \subsubsection{Solving Riemann--Hilbert problems}
-\begin{todo}[\textbf{A} Read through]\end{todo} Sometimes level 1 ODEs can be regarded as the local version of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
+\begin{todo}[\textbf{A} Read through]\end{todo} \begin{old}Sometimes\end{old} \begin{draft}always\end{draft} level 1 ODEs can be regarded as the \begin{old}local version\end{old} \begin{draft}coordinate expressions\end{draft} of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
 In this case, solutions of the ODE are (local) flat sections for the corresponding connection.
 Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem.
+\begin{todo}
+    add reference
+\end{todo}
 
@@
 
-Solutions of Riemann--Hilbert problems were computed explicitly in many examples~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
-In particular, in~\cite[Section~6.2.1]{kontsevich2022analyticity} the authors discuss a Riemann--Hilbert problem for thimble integrals in terms of analytic wall-crossing structures conjecturally describing resurgent series.
+In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
+\begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in~\cite[Section~6.2.1]{kontsevich2022analyticity} Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
+As we mention in Section~\ref{borel-reg:explanatory-power} every thimble integral satisfies some ODE.
+Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgnt series.
 
@@
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-\begin{todo}[Change $b$ to $\alpha$?]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
+\begin{todo}[Change $b$ to $\alpha$?\textbf{V} Did it]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
 Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$.
@@
     \label{change-chart}
-    e^{-bz} \laplace_{\zeta_b, 0} \varphi = \laplace_{\zeta, b} \varphi.
+    e^{-z\alpha} \laplace_{\zeta_\alpha, 0} \varphi = \laplace_{\zeta, \alpha} \varphi.
 \end{equation}
@@
 \begin{align*}
-\laplace_{\zeta, b} \varphi & = \int_{\mathcal{J}_{\zeta,b}} e^{-z \zeta}\,\varphi\;d\zeta \\
-& = \int_{\mathcal{J}_{\zeta_b,0}} e^{-z(b + \zeta_b)}\,\varphi\;d\zeta_b \\
-& = e^{-b z} \int_{\mathcal{J}_{\zeta_b,0}} e^{-z\zeta_b}\,\varphi\;d\zeta_b \\
-& = e^{-b z} \laplace_{\zeta_b, 0} \varphi.
+\laplace_{\zeta, \alpha} \varphi & = \int_{\mathcal{J}_{\zeta,\alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
+& = \int_{\mathcal{J}_{\zeta_\alpha,0}} e^{-z(\alpha + \zeta_\alpha)}\,\varphi\;d\zeta_\alpha \\
+& = e^{-z\alpha } \int_{\mathcal{J}_{\zeta_\alpha,0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
+& = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi.
 \end{align*}
@@
 \begin{definition}\label{def:convolution}
-Let $\phi,\psi$ be two holomorphic functions on $B$.
+\begin{todo}\textbf{A} read through copied definition\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$.
 Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
@@
 \begin{prop}\label{prop:convolution_iso_laplace}
-Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined. Then 
+\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined.
+Then
 \begin{equation}
@@
 \begin{proof}
-Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-   \begin{align*}
-       \phi \ast_{\zeta, \alpha} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
+\begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
+   \begin{align*}
+       \phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta_\alpha}} \phi'\,\psi''\,d\zeta'\\
        &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
@@
 \end{align*}
-where $c''=\max\{c,c'\}$. \begin{todo}
-    How do we check it is locally integrable???
-\end{todo}
+where $c''=\max\{c,c'\}$.
+\begin{draft}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{draft}
 %   
@@
 \begin{todo}
-   \textbf{V} add $\theta$
+[\textbf{V} add $\theta$] [\textbf{A} read through proof]
 \end{todo}
@@
    \end{align*}
-   where $\eta'=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta''=\beta s+(1-s)\zeta_\alpha$. Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
+   \begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\eta'=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta''=\beta s+(1-s)\zeta_\alpha$.
+Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
      \begin{align*}
@@
 %
-\subsection{Comparison with other treatments of the Airy equation}
+\subsection{Comparison with other treatments of the Airy equation}\label{airy-comparison}
 %

### 2024-06-14 exp-resurgence.tex
Polish thimble integral section

@@
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
-\begin{theorem}\label{thm:exist_uniq_ODE}
+\begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
 Let $-\alpha$ be a root of $P$.
@@
 By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
-\begin{theorem}\label{thm:soln_is_Borel_sum}
+\begin{theorem}[also \ref{re:thm:soln_is_Borel_sum}]\label{thm:soln_is_Borel_sum}
 The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
@@
 Because of the fractional power $z^{-\tau_\alpha}$, we use Lemma~\ref{lem:laplace-bridge} instead of a more standard result on the asymptotics of a Borel sum, such as Theorem~5.20 of \cite{diverg-resurg-i}.
-\begin{corollary}\label{cor:soln_borel-reg}
+\begin{corollary}[also \ref{re:cor:soln_borel-reg}]\label{cor:soln_borel-reg}
 The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
@@
 From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
-On the other hand, if you prefer to work formally, you can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
+On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
 We do this in Section~\ref{sec:new-summability-proof}.
@@
 Once we know $\iota_a$, we can go through the steps of the Borel regularization process and show that we end up with the same function we started with.
-\begin{theorem}\label{thm:maxim}
+\begin{theorem}[also \ref{thm:maxim-proof}]\label{thm:maxim}
 If the integral defining $I_a$ is absolutely convergent, then $I_a$ is Borel regular. More explicitly:
@@
 \end{theorem}
-%\color{Goldenrod}
-%Then, our main result for thimble integrals is proving they are indeed Borel regular:
-%\begin{theorem}[see Theorem \ref{thm:maxim-dim}]
- %   Let $\series{I}_{j}(z)\in e^{-z \alpha_j} z^{-1/2} \C\llbracket z^{-1}\rrbracket$ be the asymptotic expansion of $I_j$ as $\Re z e^{i\theta}\to \infty$ for the generic direction $\theta$. Then:
-%\begin{enumerate}
-%\item The series $\series{\Phi}_j:=z^{1/2} \series{I}_j$ is $1$-Gevrey, thus $\series{\phi}_j(\zeta)\defeq\borel_\zeta(\series{\Phi}_j)$ converges near $\zeta=\alpha_j$
-%\item If you continue the sum of $\series{\phi}_j$ along the ray $ e^{i\theta}[\alpha_j,+\infty)$, and take its Laplace transform along that ray, you'll recover $z^{1/2} I_j$.
-%\item\label{part3} For any $\zeta$ on the ray going rightward from $\alpha_j$, we have a \textit{thimble projection formula}
-%\begin{multline}
-%\hat{\phi}_{j}(\zeta)=\fracderiv{3/2}{\zeta}{\alpha_j} \left( \int_{\mathcal{C}_j(\zeta)}\nu \right)=\left(\tfrac{\partial}{\partial \zeta}\right)^2\,\frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{\alpha_j}^\zeta (\zeta-\zeta')^{-1/2}\left( \int_{\mathcal{C}_j(\zeta')} \nu \right)\,d\zeta',
-%\end{multline}
-%where $\mathcal{C}_j(\zeta)$ is the part of $\mathcal{C}_j$ that goes through $f^{-1}([\alpha_j, \zeta])$.
-Notice that $\mathcal{C}_j(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\textcolor{magenta}{[The thimble $\mathcal{C}_j$ needs an orientation, but the orientation is arbitrary.]}
-%\end{enumerate}
-%\end{theorem}
-%\color{black}
-\begin{draft}
-\begin{todo}[Shorten or remove---leaning toward remove.
-Go for consistency with the end of the ODE results section.
-The original intent was to highlight similarity with Borel regularity diagram, but the statement of the theorem now matches the diagram closely.]\end{todo} We sketch the proofs of the main results in the following diagram (for the rigorous ones see Section~\ref{borel-reg-thimble}):
-%\[
-%\begin{tikzcd}
-%{I} \arrow[rrr,"\aexp^{\theta}"]\arrow[dd, swap,"\laplace^{-1} "] &  & & \series{I}\arrow[dd,"\borel"]\\
-%& & &\\
-%\iota \arrow[r,equal] & \hat{\iota} & &\series{\iota} \arrow[ll, "\text{sum}"]
-%\end{tikzcd}
-%\]
-On the one hand, with a change of coordinates, the thimble integral $I$ can be written as a Laplace type integral, i.e.
-as the Laplace transform of a function $\iota$, written explicitly in equation~\eqref{eqn:formula}.
-On the other hand, we compute the asymptotic expansion of $I$ using the saddle point approximation, which turns out to be a formal $1$-Gevrey series in the frequency domain.
-Consequently, its Borel transform $\series{\iota}$ is a germ of holomorphic functions at $\zeta=\alpha$ in the position domain.
-Finally, we will show that the Taylor expansion of $\iota$ at $\zeta=\alpha$ agrees with~$\series{\iota}_\alpha$.
-\end{draft}
-%% the following remark has been moved to Section of the proof
-%\begin{remark}\label{rmk:Pham formula}
-%    Equation \eqref{eqn:formula} gives an explicit expression for $\phi_j$ in terms of $\nu$ and of the pre-image of the ray $e^{i\theta}[\alpha_j,\zeta)$ via $f$.
-When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} allows to write $\hat{\iota}_j$ explicitly as
-%    \begin{equation}\label{eqn:Pham}
- %       (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta^{-\frac{N}{2}-k}+ \text{ hol. funct.}
- %   \end{equation}
-%for some coefficients $c_k$ which depends on $f$ and $\nu$, and with $\delta^{-\alpha}$ be defined as
- %  \begin{equation*}
-  %     \delta^{-\alpha}:=\begin{cases}
-   %        \frac{\zeta^{\alpha-1}}{-2\pi i(\alpha-1)!}\log(\zeta) + \text{ hol. funct.} & \text{ if } \alpha\in\mathbb{N}^*\\
-    %       & \\
-     %      \frac{(-\zeta)^{\alpha-1}}{2\pi i \Gamma(-\alpha)}+ \text{ hol. funct.} & \text{ if } \alpha\notin \mathbb{N}^* 
-      % \end{cases}
-   %\end{equation*}
-%In particular, if $N=1$, from equation \eqref{eqn:Pham} we deduce that $\hat{\phi}_j$ is the $1/2-$ derivative of $\hat{\iota}_j$, \textcolor{orange}{hence it has simple singularities \ref{simple-res-thimble}.} We expect this result to hold beyond the polynomial case.
-We also expect that equation \eqref{eqn:formula} can be generalized to the $N$-dimensional case replacing the $3/2$-derivative with the $(N+1)/2$ one.
-%\end{remark}
+\begin{todo}[In parallel with the ODE results, does this theorem help us accomplish something interesting or justify a point of view?]\end{todo}
 %

### 2024-06-14 exp-resurgence.tex
Work on "New perspectives on the Laplace transform"
We just need to solidify the opening sentence now.

@@
 %
-\begin{todo}\textbf{A} [Revise]\end{todo} \begin{draft}In our study of Borel regularity, we use some new perspectives on the Laplace transform, discussed in Section~\ref{sec:Laplace-Borel-general}.\end{draft}
-
-Laplace transform methods for solving ODEs on the frequency domain traditionally relate them to ODEs on the position domain.
-We find, however, that it is easier and more natural to relate ODEs on the frequency domain to integral equations on the position domain.
-In particular, the good behavior of integral equations and their solutions is central to our proof that certain ODEs have Borel regular solutions.
+\begin{todo}\textbf{A} [Revise]\end{todo} \begin{draft}In our results, it is important to distinguish and relate Laplace transforms based at different points on the position domain.
+To help describe how these transformations fit together, we introduce a geometric picture of the Laplace and Borel transforms\ldots\end{draft}
 
@@
 \end{center}
+
+We also depart slightly from traditional Laplace transform methods for solving ODEs.
+One traditionally relates ODEs on the frequency domain to ODEs on the position domain~\cite{braaksma2006laplace,laplace-tfm}, but we find it more natural to relate them to integral equations on the position domain.
+The good behavior of integral equations and their solutions is central to our proof that certain ODEs have Borel regular solutions.
 %
@@
 %
-\begin{todo}[First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
+\begin{todo}[\textbf{A} First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
 \begin{todo}[Transition: many well-known examples reduce to special cases of these\ldots]\end{todo} the Airy--Lucas functions (Section~\ref{example_AL}), the Airy function (Appendix~\ref{airy-appendix}).

### 2024-06-14 exp-resurgence.tex
Finalize "Asymptotics of thimble integrals"

@@
 %
-\begin{revised}
 Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
@@
 When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula} to turn it into a function whose Laplce transform is the thimble integral.
-This formula generalizes to higher-dimensional thimbles and thimbles based at degenerate critical points~\cite[Section 1.2.2]{mistegard_phdthesis}.\end{revised}
-
-\begin{todo}\textbf{A} [Done.]\end{todo}
-
-\begin{brainstorm}
-\item In fact, the thimble integral is almost a Laplace transform (cite Pham and point to thimble projection formula in this paper)
-\item Can also recover analytic object using Borel summation.
-\begin{itemize}
-\item {[Transition into discussion similar to ``Laplace transform methods and fixed point iteration'' for ODEs]}
-\item This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
-\item \ldots but the integral contains a hint about where to find the corresponding analytic object: the thimble itself, which is a real-analytic submanifold.
-\end{itemize}
-\item {[Footnote:]} In fact, analougus results hold when $f$ satisfies milder assumptions (see for instance~\cite[Section 1.2.2]{mistegard_phdthesis}).
-%%\begin{itemize}
-%%\item ODE: get a formal series, resum it, check whether the result is an actual series.
-%%\item Thimble integral: get a formal series, resum it, check whether the result matches the original analytic thimble integral.
-%%\end{itemize}
-\end{brainstorm}
-
-\begin{draft}This raises the question we address in this paper, namely to understand why Borel summation is effective for $1$-dimensional thimbles integrals.
-In a nutshell, our result follows from the fact that thimble integrals are generalized Laplace transforms.
-We prove, from this, that they are Borel regular functions.
-In addition, our approach wants to focus on the role of the position domain and it emphasizes how the geometry of the Laplace transform is the natural framework to describe Borel regularity for thimbles integrals (see~\cite{Fenyes-ihes-lecture} and Section~\ref{sec:Laplace-Borel-general}).\end{draft}
+This formula generalizes to higher-dimensional thimbles~\cite{pham} and thimbles based at degenerate critical points~\cite[Section 1.2.2]{mistegard_phdthesis}.
 %

### 2024-06-14 exp-resurgence.tex
Drop change of chart diagram

@@
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-\begin{todo}[Change $b$ to $\alpha$?\textbf{V} Did it]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
+\begin{todo}[Change $b$ to $\alpha$?
+\textit{V} Did it \textbf{A} Double-check]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
 Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$.
@@
 \end{equation}
-\begin{todo}
-In other words, the diagram
-\begin{center}
-\begin{tikzcd}[row sep=12mm, column sep=2mm]
-\mathcal{O}(T^*B) \arrow[rr, "e^{\alpha z}"] & & \mathcal{O}(T^*B)\\
-& \singexp{\sigma}{\Lambda}(\Omega_b) \arrow[ul, "\laplace_{\zeta_\alpha, 0}"]\arrow[ur,swap,"\laplace_{\zeta, \alpha}"]
-\end{tikzcd}
-\end{center}
-commutes.
-\end{todo}
 \end{lemma}

### 2024-06-21 exp-resurgence.tex
Revise intro to new perspectives on Laplace transform

@@
 
-The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[pag.
-105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
+The form of $\mathcal{P}$ derives from equation~2.2.3 of \cite[p.~105]{EcalleIII}, which encompasses both linear and nonlinear ODEs of level $1$.
 Borel summation is more involved for the nonlinear ones, raising the question of whether our analysis generalizes.
@@
 %
-\begin{todo}\textbf{A} [Revise]\end{todo} \begin{draft}In our results, it is important to distinguish and relate Laplace transforms based at different points on the position domain.
-To help describe how these transformations fit together, we introduce a geometric picture of the Laplace and Borel transforms\ldots\end{draft}
-
-In Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
+\begin{revised}For Borel summation to work as intended, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point.
+To explain this aspect of Borel regularity,\end{revised} we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
 Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$.
 The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$.
+The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
 \begin{center}
@@
 
-We also depart slightly from traditional Laplace transform methods for solving ODEs.
+We depart slightly from traditional Laplace transform methods for solving ODEs.
 One traditionally relates ODEs on the frequency domain to ODEs on the position domain~\cite{braaksma2006laplace,laplace-tfm}, but we find it more natural to relate them to integral equations on the position domain.
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91}.
+Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91} \begin{todo}[can't find the terms ``wall-crossing'' or ``Stokes phenomenon'' in this reference]\end{todo}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}.
@@
     \begin{align*}
-        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_0^1 ds\,\frac{\eta''-\beta}{(1-s)^2}e^{-z((\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi'\\
-        &=\int_{\mathcal{J}_{\eta'',0}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_{\mathcal{J}_{t,\alpha}} dt\, e^{-zt} \phi\\
+        &=\int_{\mathcal{J}_{\eta'',\beta}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_0^1 ds\,\frac{\eta''-\beta}{(1-s)^2}e^{-z((\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi'\\
+        &=\int_{\mathcal{J}_{\eta'',\beta}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_{\mathcal{J}_{t,\alpha}} dt\, e^{-zt} \phi\\
    \end{align*}
@@
 In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
+\begin{old}
 \begin{definition}
@@
 where $p$ is any point on the position domain $B$.
+\end{definition}
+\end{old}
+\begin{definition}
+For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta'\in\mathcal{S}'(\zeta)} \big(\zeta-\zeta'\big)^{-\nu} \phi\,d\zeta', \]
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.
 \begin{todo}[\textbf{V} If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?

### 2024-06-22 exp-resurgence.tex
Decide fractional integral definition notation

@@
 %
-\begin{revised}For Borel summation to work as intended, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point.
+\begin{revised}For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point.
 To explain this aspect of Borel regularity,\end{revised} we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
@@
 %
+\begin{draft}We illustrate our main results with detailed treatments of several examples.
+Generalizing the classic example of the Airy equation, we find frames of Borel regular solutions for all of the Airy--Lucas equations.
+Noting that these equations reduce to the modified Borel equation with positive rational coefficients, we also discuss Borel regularity for\end{draft}
 \begin{todo}[\textbf{A} First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{CV91} \begin{todo}[can't find the terms ``wall-crossing'' or ``Stokes phenomenon'' in this reference]\end{todo}.
+Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}.
 Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
-\begin{todo}[Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
+\begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
 %
@@
 For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta'\in\mathcal{S}'(\zeta)} \big(\zeta-\zeta'\big)^{-\nu} \phi\,d\zeta', \]
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.
-\begin{todo}[\textbf{V} If we switch to $'$, $''$ notation, also convert this.]\end{todo}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}'(\zeta)} \big(\zeta-\zeta'\big)^{-\nu} \phi' \,d\zeta', \]
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
 Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
@@
 \end{definition}
-The fractional integral obeys the expected semigroup law \cite[Section  1.3]{mladenov2014advanced}
+\begin{todo}[\textbf{A} Explain that we're using the $'$, $''$ notation, and $\zeta - \zeta'$ is an expression for the function $\zeta''$ on the second factor.]\end{todo}
+
+The fractional integral obeys the semigroup law \cite[Section  1.3]{mladenov2014advanced}
 \begin{align*}

### 2024-06-22 exp-resurgence.tex
Revised Rermark 4.5

@@
 %
-\begin{draft}We illustrate our main results with detailed treatments of several examples.
-Generalizing the classic example of the Airy equation, we find frames of Borel regular solutions for all of the Airy--Lucas equations.
-Noting that these equations reduce to the modified Borel equation with positive rational coefficients, we also discuss Borel regularity for\end{draft}
+\begin{revised}We illustrate our main results with detailed treatments of several examples.
+Generalizing the classic example of the Airy equation, we find frames of Borel regular solutions for the Airy--Lucas and generalized Airy equations.
+Noting that the Airy--Lucas equations reduce to the modified Bessel equation with certain rational values of the parameter, we also find Borel regular solutions of the general modified Bessel equation.\end{revised}
 \begin{todo}[\textbf{A} First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
@@
 &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
-        &=\laplace_{\zeta,0} \int_0^{\zeta}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi(\zeta') d\zeta'\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}'(\zeta)}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
 &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
 \end{align*}
+\begin{todo}[or: where we use the notation from Definition~\{\ldots\}]\end{todo} where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=0$ to $\zeta' = \zeta$.
 The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
@@
 I_a & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
-& = \int_{\alpha}^{e^{i\theta} \infty} e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta.
+& = \int_{\mathcal{J}_{\zeta,\alpha}^\theta}e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta.
 \end{align*}
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_\alpha = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
+{\iota}_a = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
 \end{equation}
 \end{proof}
-We will now prove that $I_a$ is Borel regular:
+We will now prove that $I_a$ is Borel regular.
 \begin{theorem}[restatement of~\ref{thm:maxim}]\label{thm:maxim-proof}
@@
 \item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
-Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
+Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble and $\alpha=f(a)$.
 \item\label{part-2-prf} The Borel transform $\series{\iota}_a \defeq \borel_\zeta \series{I}_a$ converges near $\zeta = \alpha$.
@@
 \begin{proof}
-\begin{todo}\textbf{V} [Check that $\alpha$ subscripts have been converted to $a$ for $I$, $\iota$, and $\mathcal{C}$.]\end{todo} Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - f(a)$.
+Since $f$ has non--degenerate critical points, we can find a holomorphic chart $\tau$ around $a$ with $\tfrac{1}{2} \tau^2 = f - \alpha$.
 Let $\mathcal{C}^-_a$ and $\mathcal{C}^+_a$ be the parts of $\mathcal{C}_a^\theta$ that go from the past ($-e^{-i\theta}\infty$) to $a$ and from $a$ to the future ($+e^{-i\theta}\infty$), respectively.
@@
 
-We write $\approx$ to say that two functions are asymptotic at all orders around the base point \begin{todo}[what point?]\end{todo}.
-By the method of steepest descentz,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
+We write $\approx$ to say that two functions are asymptotic to all orders.
+By the method of steepest descent,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
 %%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
@@
 \end{align*}
-In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_\alpha^\theta$ and its sum is given by $\iota_a$. %Thus, we can take the Laplace transform of $\phi_j$ and we find
+In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_{\zeta,\alpha}^\theta$ and its sum is given by $\iota_a$.
+%Thus, we can take the Laplace transform of $\phi_j$ and we find
 %\begin{align*}
@@
 \begin{remark}\label{rmk:1/2-deriv}
-\begin{todo}[\textbf{V} Read through, and remove \texttt{revised} if good]\end{todo}\begin{revised}
 For some applications, it is more convenient to work with $\Phi_a \defeq z^{-1/2} I_a$, whose asymptotic series has integer powers.
@@
 \begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right).\end{equation}
-\end{revised}
 \begin{old}

### 2024-06-24 exp-resurgence.tex
Confirm revision of "New and old examples"
Also, add thimble integral for cantilever vibrations.

@@
 %
-\begin{draft}
 \paragraph{New and old examples}
@@
 \begin{revised}We illustrate our main results with detailed treatments of several examples.
-Generalizing the classic example of the Airy equation, we find frames of Borel regular solutions for the Airy--Lucas and generalized Airy equations.
-Noting that the Airy--Lucas equations reduce to the modified Bessel equation with certain rational values of the parameter, we also find Borel regular solutions of the general modified Bessel equation.\end{revised}
+Generalizing the classic example of the Airy equation (Appendix~\ref{airy-appendix}), we find frames of Borel regular solutions for the Airy--Lucas and generalized Airy equations (Sections \ref{example_AL} and \ref{sec:gen-airy}).
+Noting that the Airy--Lucas equations reduce to special cases of the modified Bessel equation, we also find Borel regular solutions of the general modified Bessel equation (Section~\ref{sec:mod-bessel-lift}).
+Similarly, noting that the Airy function is a thimble integral with a third-degree polynomial in the exponent, we show that a general third-degree thimble integral is Borel regular (Section~\ref{sec:deg3}).
+Finally, as an example of a fourth-order ODE, we solve the equation describing the vibration of a triangular cantilever (Section~\ref{sec:catilever}).
+
+Each of our examples focuses on either a level~1 ODE whose solutions can be expressed as thimble integrals or a thimble integral that satisfies a level~1 ODE.
+This provides an opportunity to compare different explanations for why each example function is Borel regular.
+
+In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. \begin{todo}[\ldots]\end{todo}
+\end{revised}
+
+\begin{old}
 \begin{todo}[\textbf{A} First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
@@
 In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
-
+\end{old}
+
+\begin{draft}
 Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
@@
 %
-\begin{draft}Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu\in\Gamma(X,\Omega^1)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
+\begin{draft}Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ \begin{todo}[this originally said $\Gamma(X,\Omega^1)$, but shouldn't it be either $\Omega^{1,0}(X)$ or $\Gamma\big(X, \Lambda^{1,0} (X)\big)$?]\end{todo} and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
 Let $I_a$ be the thimble integral
@@
 \begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right).\end{equation}
-\begin{old}
-For some applications, it might be more convenient to study Borel regularity of $\Phi_\alpha=z^{-1/2}I_\alpha$, as its asymptotics will not have fractional power singularities.
-The proof follows the same argument we use in the proof on Theorem~\ref{thm:maxim-proof} for $I_\alpha$, but there is one subtlety to be aware of when rewriting $\Phi_\alpha$ as the Laplace transform of a function $\phi_\alpha$.
-Indeed, first notice that \[\phi_\alpha = \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_\alpha \]
-Then, we can take the $1/2$ fractional integral on both sides:
-\begin{align*}
-    \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha &= \fracderiv{-1}{\zeta}{\alpha} \, \iota_\alpha \\
-    & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
-    & = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu - \int_{\mathcal{C}_\alpha^\theta(\alpha)}\nu.
-\end{align*}
-The second term vanishes because $\mathcal{C}_\alpha^\theta(\alpha)$ is a single point, leaving
-\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_\alpha = \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu. \]
-Finally, we apply the $1/2$ derivative of both sides, recalling that it is a left inverse of the $1/2$ integral, and we find
-\begin{equation}\label{eqn:formula--1/2}\phi_\alpha= \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_\alpha^\theta(\zeta)}\nu \right).\end{equation}
 \begin{todo}[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]\end{todo}
-\end{old}
 \end{remark}
@@
 It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \begin{revised}typically\end{revised} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
-Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[\begin{todo}Chapter~??\end{todo}]{Arnold}.
+Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~1]{Arnold}.
 However, in the Airy--Lucas example, $f$ is not Morse unless $n=3$.
@@
 %
-\subsection{Generalized Airy}
+\subsection{Generalized Airy}\label{sec:gen-airy}
 %
@@
 \end{todo}
-\subsection{Third-degree thimble integrals}
+\subsection{Third-degree thimble integrals}\label{sec:deg3}
 In this section, we consider the thimble integral
@@
 %
+\subsubsection{Setting}
 A {\em triangular cantilever} is a flexible strip with constant thickness and linearly tapered width, clamped at the broad end so it sticks out horizontally like a diving board.
@@
 \color{black}
-We are going to look for functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
+\subsubsection{Solving the differential equation}
+We seek functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
 From Proposition~\ref{prop:L-int-op} we deduce that $\laplace_{\zeta, \alpha} v$ satisfies equation~\eqref{eqn:triangular_cantilever} if and only if $v$ satisfies the integral equation
@@
 we learn that
-\[ v_\text{uni} = \frac{1}{\sqrt{\zeta^4 - \omega^2}} \]
-satisfies equation~\eqref{eqn:position_cantilever} whenever $\alpha^4 - \omega = 0$.
+\begin{equation}
+v_\text{uni} = \frac{1}{\sqrt{\zeta^4 - \omega^2}}
+\end{equation}
+satisfies equation~\eqref{eqn:position_cantilever} whenever $\alpha^4 - \omega^2 = 0$.
 Thus, a single ``universal solution'' in the position domain leads to four linearly independent solutions $V_\alpha = \laplace_{\zeta, \alpha} v_\text{uni}$ of equation~\eqref{eqn:triangular_cantilever}, indexed by the fourth roots of $\omega^2$.
-\begin{todo}\par[Stokes? Thimbles? Mathematica gives solution ${}_0 F_3\big(; \tfrac{1}{2}, \tfrac{3}{4}, \tfrac{3}{4}; \tfrac{1}{16} z^4\big)$.]\end{todo}
+\subsubsection{Expressing the solutions as thimble integrals}
+We can now use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to express the solutions found above as thimble integrals.
+In terms of the Jacobi elliptic function $\operatorname{sd}$, we have
+\begin{equation}\label{eq:cantilever-thimble}
+V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du,  \end{equation}
+where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$.
+\begin{todo}[Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
+
+To confirm equation~\eqref{eq:cantilever-thimble}, use Jacobi's transformations to rewrite the relationship between $\zeta$ and $u$ in terms of $\operatorname{sn}$.
+\[ \zeta = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big). \]
+\begin{verify}
+Jacobi's imaginary transform gives
+\begin{align*}
+-i \operatorname{sn}\big(2i \omega^{1/2} u, \sqrt{1-\sqrt{2}^2}\big) & = \operatorname{sc}(2\omega^{1/2} u, \sqrt{2}) \\
+\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = i \operatorname{sc}\big(2\omega^{1/2} u,\sqrt{2}\big)
+\end{align*}
+Jacobi's real transform gives
+\begin{align*}
+\frac{1}{2\omega^{1/2}} \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
+i \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big).
+\end{align*}
+Altogether, we have
+\begin{align*}
+\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
+\omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)
+\end{align*}
+\end{verify}
+Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
+\begin{equation}
+F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
+\end{equation}
+we learn that
+\begin{align*}
+F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u \\
+\frac{\omega^{-1/2}\;d\zeta}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;du \\
+\frac{d\zeta}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = du \\
+\frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] & = du.
+\end{align*}
+\begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
 %\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}

### 2024-06-24 exp-resurgence.tex
Drop draft text from "New and old examples"

@@
 %
-\begin{revised}We illustrate our main results with detailed treatments of several examples.
+We illustrate our main results with detailed treatments of several examples.
 Generalizing the classic example of the Airy equation (Appendix~\ref{airy-appendix}), we find frames of Borel regular solutions for the Airy--Lucas and generalized Airy equations (Sections \ref{example_AL} and \ref{sec:gen-airy}).
@@
 
+\begin{revised}
 In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. \begin{todo}[\ldots]\end{todo}
 \end{revised}
-
-\begin{old}
-\begin{todo}[\textbf{A} First mention more classical examples; then talk about Airy-Lucas and cantilever.]\end{todo} We illustrate our main results with detailed treatments of several examples: we will mostly focus on [modified Bessel functions, which are] degree two ODEs that admit a frame of solutions expressed as thimble integrals.
-\begin{todo}[Transition: many well-known examples reduce to special cases of these\ldots]\end{todo} the Airy--Lucas functions (Section~\ref{example_AL}), the Airy function (Appendix~\ref{airy-appendix}).
-\begin{todo}[the anharmonic oscillator---see ``A Primer on Resurgent Transseries,'' appendices B--C]\end{todo} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms.
-On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations.
-\begin{todo}[Mention that some classical integral formulas for modified Bessel functions are actually thimble integrals.]\end{todo} The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}.
-In the Airy example (see Section~\ref{airy-appendix}) we will compute the \textit{thimble projection formula} directly.%, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).
-\end{old}
 

### 2024-06-24 exp-resurgence.tex
Drop draft text from proof of thm:maxim-proof

@@
 By the method of steepest descent,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).}
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
 \[ e^{z \alpha} I_a \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
@@
 The right-hand side goes to $0$ as $\Re(z)$ grows.
-%Hence,
-%\[ e^{-z\zeta_\alpha} I_\alpha(z) \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^\alpha\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
 The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~5]{chiani-dardari-book}, allowing the simpler estimate
@@
 This ends the proof of part~\ref{part-2-prf}.
-%$|a_{j,n}| \lesssim \left(\tfrac{2}{\varepsilon^2}\right)^n\,n!\,$, showing that $\series{I}_j$ is $1$-Gevrey.
-
-\begin{todo}[Analytic/position version starts here.]\end{todo} The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_a$ at $\zeta=\alpha$ agrees with $\series{\iota}_a$.
+
+The proof of part~\ref{part-3-prf} relies on the thimble projection formula \eqref{eqn:formula-proof}: we will show that the Taylor expansion of $\iota_a$ at $\zeta=\alpha$ agrees with $\series{\iota}_a$.
 We can rewrite the Taylor series for $\nu$ as
@@
 In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_{\zeta,\alpha}^\theta$ and its sum is given by $\iota_a$.
-%Thus, we can take the Laplace transform of $\phi_j$ and we find
-%\begin{align*}
- %   \laplace_{\zeta,\alpha_j}^\theta \phi_j &= \laplace_{\zeta,\alpha_j}^\theta \fracderiv{-1/2}{\zeta}{\alpha_j} \iota_j \\
- %   &= z^{-1/2} \laplace_{\zeta,\alpha_j}^\theta  \iota_j \\
- %   &= z^{-1/2} I_j
-%\end{align*}
-
-\begin{old}
-Lemma~\ref{lem:thimble_proj_formula-proof} tells us that
-\begin{align*}
-I_j & = \laplace_{\zeta, \alpha_j}^\theta \iota_j \\
-e^{z\alpha_j} I_j & = \laplace_{\zeta_j, 0}^\theta \iota_j \\
-& = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} + \textcolor{orange}{\zeta^{N+1/2} f}\right) \\
-& \color{magenta} = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = 0}^\infty 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right).
-%%& = \int_{\mathcal{J}_j^\theta} e^{-z\zeta_j} \iota_j\,d\zeta_j \\
-%%& = \int_{\mathcal{J}_j^\theta} e^{-z\zeta_j} \left( \sum_{n \ge 0} 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right) d\zeta_j
-\end{align*}
-Over any finite number of terms, we can exchange the sum with the Laplace transform, giving
-\begin{align*}
-e^{z\alpha_j} I_j & = \Delta_n + \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j\,\laplace_{\zeta_j, 0}^\theta \zeta_j^{n - 1/2} \\
-& = \Delta_n + \sum_{n = 0}^N 2^{n+1/2} b_{2n}^j \Gamma(n + \tfrac{1}{2})\,z^{-n - 1/2} \\
-& = \Delta_n + \sum_{n = 0}^N \sqrt{2\pi}\,(2n - 1)!!\,b_{2n}^j\,z^{-n - 1/2},
-\end{align*}
-where
-\[ \Delta_n = \laplace_{\zeta_j, 0}^\theta \left( \sum_{n = N+1}^\infty 2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right). \]
-\begin{verify}
-\begin{align*}
-2^n \Gamma(n + \tfrac{1}{2}) & = \sqrt{\pi}\,(2n - 1)!! \\
-2^{n + 1/2} \Gamma(n + \tfrac{1}{2}) & = \sqrt{2\pi}\,(2n - 1)!!
-\end{align*}
-\end{verify}
-
-\begin{prop}
-Consider a function
-\[ \varphi = \sum_{\kappa \in K} a_\kappa \zeta^\kappa \]
-defined by a power series with real exponents $K \subset (-1, \infty)$, with a positive lower bound on the distances between the exponents.
-If the series converges throughout the disk $|\zeta| < \varepsilon$, then
-\[ \partial_{\zeta, 0}^{-\nu} \varphi = \sum_{\kappa \in K} \tfrac{\Gamma(\kappa+1)}{\Gamma(\kappa+\nu+1)} \zeta^{\kappa + \nu} \]
-on that disk.
-\end{prop}
-\begin{proof}
-The convergence of the series for $\varphi$ in the disk $|\zeta| < \varepsilon$ implies that for each $\eta \in (0, \varepsilon)$, we have $|a_\kappa| \lesssim \eta^{-\kappa}$ over all $\kappa \in K$.
-The
-\end{proof}
-\begin{verify}
-Reference for monomials: ``Evaluation of Fractional Integrals and Derivatives of Elementary Functions''
-
-For convenience, think of $K$ as sequence, in increasing order. At any point $\zeta = \rho$ with $|\rho| < \varepsilon$, the series defining $\varphi$ converges, implying that
-\begin{align*}
-& \lim_{\kappa \in K} |a_\kappa \rho^\kappa| = 0 \\
-& \lim_{\kappa \in K} |a_\kappa| |\rho|^\kappa = 0 \\
-& |a_\kappa| |\rho|^\kappa \lesssim 1 \text{ over all } \kappa \in K \\
-& |a_\kappa| \lesssim |\rho|^{-\kappa} \text{ over all } \kappa \in K.
-\end{align*}
-In other words, for every $r \in (0, \varepsilon)$, we have $|a_\kappa| \lesssim r^{-\kappa}$ over all $\kappa in K$.
-
-Hence, on the region $|\zeta| < |\rho|$, we have
-\begin{align*}
-|\varphi| & \le \sum_{\kappa \in K} |a_n| |\zeta|^\kappa \\
-& \lesssim \sum_{\kappa \in K} r^{-\kappa} |\zeta|^\kappa \\
-& = \sum_{\kappa \in K} |\zeta/r|^\kappa.
-\end{align*}
-In the disk $|\zeta| < r$, the ratio $|\zeta/r|$ is smaller than $1$, so increasing its exponent always decreases the value.
-
-Let $c > 0$ be the lower bound on the distances between the exponents.
-Choose some $\lambda \in (-1, \infty)$ so that $K \subset (\lambda, \infty)$.
-For each $n \in \mathbb{N}_{\ge 0}$, the $n$th element of $K$ must be greater than $\lambda + nc$, so
-\begin{align*}
-|\varphi| & \lesssim \sum_{n = 0}^\infty |\zeta/r|^{\lambda + nc} \\
-& = |\zeta/r|^\lambda \sum_{n = 0}^\infty (|\zeta/r|^c)^n \\
-& = \frac{|\zeta/r|^\lambda}{1 - |\zeta/r|^c} \\
-& = \frac{1}{|\zeta/\rho| - |\zeta/r|^{1+c}}.
-\end{align*}
-We now see that the series defining $\varphi$ converges absolutely on $|\zeta| < |\rho|$.
-
-The kernel of $\partial_{\zeta, 0}^{\nu-1}$ is $\big(\zeta(p) - \zeta\big)^{\nu-1}$. It has an integrable singularity at $p$, and it is non-singular at $\zeta = 0$.
-\end{verify}
-
-\begin{prop}
-Suppose $f_0, f_1, f_2, \ldots$ is a sequence of holomorphic functions on some connected domain $\Omega$, and the series $\sum_{k=0}^\infty |f_k|$ converges at each point in $\Omega$.
-Then, for any $\nu > 0$,
-\[ \partial_{\zeta, \alpha}^{-\nu} \left( \sum_{k=0}^\infty f_k \right) = \sum_{k=0}^\infty \partial_{\zeta, \alpha}^{-\nu} f_k \]
-throughout $\Omega$.
-\end{prop}
-\begin{proof}
-Given any point $p \in \Omega$, choose a path $\gamma$ that runs through $\Omega$ from $\zeta = \alpha$ to $p$.
-Since $\gamma$ is the continous image of a closed interval, it is compact, so $\zeta$ is bounded
-
-Recalling that
-\[ [\partial^{\nu-1}_{\zeta, \alpha} f](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta = \alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} f\,d\zeta, \]
-\textcolor{orange}{[\ldots]}
-\end{proof}
-
-By the steepest descent method,\footnote{The details can be found in \cite{miller2006applied}: follow the proof of Proposition~2.1 in through equation~(2.9).} \begin{todo}[define $\approx$]\end{todo}
-%%\[ e^{-z\zeta_\alpha} I_\alpha(z) \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-\[ e^{z \alpha_j} I_j \approx \int_{\tau \in [-\varepsilon, \varepsilon]} e^{-z\tau^2/2} \nu \]
-as $z \to \infty$ along the ray $e^{-i\theta}\, \R_{> 0}$.
-%%Since the Taylor series for $\nu$ converges in the disk $|\tau| < \varepsilon$, we know that $|b_m^j| \lesssim \varepsilon^{-m}$ over all $m \ge 0$, giving
-%%\[ \left| e^{-z\zeta_j}\;2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right| \lesssim 2^{n+1/2} \varepsilon^{-2n} e^{-\Re(z\zeta_j)} |\zeta_j|^{n - 1/2}. \]
-%%When $z\zeta_j \in \R_{> 0}$, that implies
-%%\begin{align*}
-%%\left| e^{-z\zeta_j}\;2^{n+1/2} b_{2n}^j \zeta_j^{n - 1/2} \right| \lesssim 2^{n+1/2} \varepsilon^{-2n} e^{-|z||\zeta_j|} |\zeta_j|^{n - 1/2}.
-%%\end{align*}
-\end{old}
 \end{proof}

### 2024-06-27 exp-resurgence.tex
Finish revising intro sections

@@
 \begin{revised}
-In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions. \begin{todo}[\ldots]\end{todo}
-\end{revised}
-
-\begin{draft}
-Among the examples we study, some of them have been discussed many times, using different approaches and conventions.
-We try to give an idea of how all these different treatments fit together.
-For instance, for the Airy function we will make a comparison with \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei}.
-\begin{todo}The anharmonic oscillator was also discussed in (\cite{bender-wu}, \cite[Appendix B]{aniceto2019primer} and \cite[Section 2.5.3]{sternin1995borel}).\end{todo} Other examples haven't been discussed much, as for Airy--Lucas functions \cite[Equation 3.2]{charbonnier22}.
+In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions.
+In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
+\end{revised} \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
 %
@@
 %
-\begin{todo}[The examples we study all involve {\em resurgent functions} in the position domain.] [Say a tiny bit about what resurgence does or is good for.]\end{todo} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
+\begin{revised}The examples we study all involve {\em resurgent functions} in the position domain.
+\begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+Geometric arguments show that when a thimble integral is algebraic \begin{todo}[how is this related to the conditions in \cite{kontsevich2022analyticity}?]\end{todo}, like the ones we use as examples in this paper \begin{todo}[check; does this include the cantilever example?]\end{todo}, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
+Conjecturally, this property extends to more general thimble integrals, like the last example in \cite{Maxim_slide_ERC}.
+The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.\end{revised}
+\begin{old}\par\begin{todo}[The examples we study all involve {\em resurgent functions} in the position domain.] [Say a tiny bit about what resurgence does or is good for.]\end{todo} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
 The resurgence of linear ODEs have been intensively studied \cite{loday1994stokes,diverg-resurg--ii} and many results are also known for non-linear ODEs \cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
 For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see the last example in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional thimble integrals are toy-models that show some features of resurgent functions.
-
+Despite their simplicity, our examples of linear ODEs and of 1-dimensional thimble integrals are toy-models that show some features of resurgent functions.\end{old}
 %\color{gray}
@@
 %\end{itemize}
-
+%
+%
+%
 %\subsection{Stokes phenomenon}
@@
 \subsection{Organization of the paper}
-The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
+\begin{revised}
+%
+\begin{paragraph}{Section~\ref{sec:historical-context}}
+We contextualize our work by reviewing some classical results related to Borel regularity.
+These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.\end{paragraph}
+%
+\begin{paragraph}{Section~\ref{sec:Laplace-Borel-general}}
+We introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results.
+To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.
+\end{paragraph}
+%
+\begin{paragraph}{Section~\ref{sec:proof_main_results}}
+We restate and prove our main results.
+\end{paragraph}
+%
+\begin{paragraph}{Section~\ref{sec:examples}}
+We illustrate our results by working through detailed examples of how Borel regular functions arise, both as $1$-dimensional thimble integrals and as solutions of level~$1$ ODEs.
+\end{paragraph}
+%
+\begin{paragraph}{Appendix~\ref{airy-appendix}}
+Reprising our analysis of the Airy--Lucas equations in Section~\ref{sec:examples}, we focus on the Airy equation as a concrete special case.
+We then explain how our treatment lines up with other discussions of the Airy equation in the literature on Borel summation.
+\end{paragraph}
+%
+\begin{paragraph}{Appendix~\ref{apx:generalities_ODEs}}
+We prove a fact about the relationship between integral and differential equations which is used in some of our examples.
+\end{paragraph}
+%
+\end{revised}
+
+\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
 This could help the reader to contextualize our results in the literature.
@@
 \item The starting point $\zeta = \alpha$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
-\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = 0$.
+\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = \textcolor{orange}{\alpha}$.
 \item The integral converges. We ensure this by putting conditions on $\phi$ and $z$.
@@
 
-\begin{revised}
 We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
@@
 for any $\tau \in \R\setminus\Z$.
-\end{revised}
+
 \subsubsection{Change of translation chart}\label{transl-borel}
@@
 
-The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \begin{draft}***\end{draft} \begin{todo}space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]\end{todo} of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \begin{draft}formal solutions\end{draft} \begin{todo}space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]\end{todo} of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.
@@
 Using the idea of resurgence, we see that they are actually more closely related.
-You can recover the frame from any one of its elements\ldots
+You can recover the frame from any one of its elements by studying the analytic continuation in the Borel plane.
 \end{brainstorm}
@@
 \end{revised}
-The factor of \begin{revised}$e^{i\pi/3} - 1$\end{revised} \begin{old}$e^{i\pi/3}$\end{old} \begin{todo}[check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
+The factor of \begin{revised}$e^{i\pi/3} - 1$\end{revised} \begin{old}$e^{i\pi/3}$\end{old} \begin{todo}[\textbf{V} check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$. 
 \begin{brainstorm}
@@
 
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product: \begin{todo}[which convolution is this?]\end{todo}
+By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
 
@@
 \end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast \zeta^{-5/6}$.
+ where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast_{\zeta} \zeta^{-5/6}$.
 
@@
 where $s=t/2+1/2$. 
-The same hypergeometric functions have been computed in Section \ref{Airy} as the Borel transform of the formal solutions of the Airy equation
+The same hypergeometric functions have been computed in Section~\ref{sec:airy} as the Borel transform of the formal solutions of the Airy equation
 

### 2024-06-27 exp-resurgence.tex
Finalize degree-3 thimble integral calculation

@@
 With the substitution $t = 2uy^{1/2}$, we can rewrite the Airy integral as
-\[ \Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du, \]
+\begin{equation}\label{eqn:airy-distillation}
+\Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du,
+\end{equation}
 where $\mathcal{C}^\theta_1$ is the contour that passes through the point $u = \tfrac{1}{2}$ and projects to the ray $\mathcal{J}^\theta_{\zeta, 1}$ under the mapping $-\zeta = 4u^3 - 3u$.
@@
 \end{equation}
-
+%
 \subsubsection{Asymptotic analysis}\label{sec:asympt-AL}
+%
 From the work of Poincar\'{e} and the Ramis Index Theorem, as discussed at the beginning of Section~\ref{sec:new-summability-proof}, we know that equation~\eqref{eqn:reg-mod-bessel-AL} has a frame of formal $1$-Gevrey trans-monomial solutions
@@
 where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
-From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n}(z) \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n} \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp-AL}
@@
 \end{equation}
-
+%
 The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
@@
 We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
-%\subsection{Going to the spatial domain}\label{spatial-AL}
+%
 \subsubsection{The big idea}\label{big-idea}
+%
 We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
@@
 We can confirm this result, and find the correct normalization, using the thimble projection formula:
-\begin{old}
-\begin{align*}
-\int_{\mathcal{C}} e^{-zu^3}\,du & = e^{i\pi/3} \int_{\mathcal{J}_{\zeta, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta^{-2/3}\,d\zeta \\
-& = \tfrac{1}{3}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
-\end{align*}
-\end{old}
-\begin{revised}
 \begin{align*}
@@
 \end{align*}
-\end{revised}
-The factor of \begin{revised}$e^{i\pi/3} - 1$\end{revised} \begin{old}$e^{i\pi/3}$\end{old} \begin{todo}[\textbf{V} check]\end{todo} comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$. 
+The factor of $e^{i\pi/3} - 1$ comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$. 
 \begin{brainstorm}
@@
 \end{align*}
-\begin{old}\begin{align*}
-i\sqrt{3}\,I(z) & = 2\sqrt{\frac{-p}{3}} K_{1/3}\Big(\frac{2ip^{3/2}}{3^{3/2}}z\Big) \\
-&=2\sqrt{\frac{-p}{3}}\left[\frac{\pi}{2\sin(\pi/3)}\Big(I_{-1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)-I_{1/3}\big(\tfrac{2ip^{3/2}}{3^{3/2}}z\big)\Big)\right]\\
-&=\frac{2}{3}\pi ip^{1/2}\left[\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{-1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\Big(\frac{ip^{3/2}}{3^{3/2}}z\Big)^{1/3}\sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}\right]\\
-&=\frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{2}{3})}-\frac{2\pi }{3\sqrt{3}} e^{2\pi i/3} z^{1/3} p \sum_{k\geq 0}\frac{(-\tfrac{p^3}{3}z^2)^k}{k!\Gamma(k+\tfrac{4}{3})}
-\end{align*}
-Now we take the limit as $p\to 0$ and we find 
-\begin{align*}
-i\sqrt{3}\,I(z) & = \frac{2\pi}{\sqrt{3}} e^{\pi i/3} z^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
-& = e^{\pi i/3} \Gamma\big(\tfrac{1}{3}\big) z^{-1/3}
-\end{align*}\end{old}
 \end{verify}
@@
 \section{The Airy equation}\label{airy-appendix}
-%
+\begin{draft}
+\subsection{Rewriting as a modified Bessel equation}
+Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing
+\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+where
+\begin{equation}\label{integral:mod-bessel}
+K(z) = i\sqrt{3} \int_{z^{-1/3}\mathcal{C}_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
+\end{equation}
+and $\mathcal{C}^\theta_1$ is the contour described in Section~\ref{sec:airy}. Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
+\begin{equation}\label{eqn:mod-bessel-1/3}
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
+\end{equation}
+In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}. Like we did in equation~\eqref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as 
+\begin{equation}\label{eqn:reg-mod-bessel}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
+\end{equation}
+%
+\end{draft}
+%
+\begin{draft}
+\subsection{Asymptotic analysis}%%\label{sec:asympt}
+%
+From the work of Poincar\'{e} and the Ramis Index Theorem, as discussed at the beginning of Section~\ref{sec:new-summability-proof}, we know that equation~\eqref{eqn:reg-mod-bessel} has a frame of formal $1$-Gevrey trans-monomial solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
+From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+\begin{equation}\label{bessel-asymp}
+\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
+\end{equation}
+%
+The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+which seem analogous to the trans-monomials above.
+Borel summation makes the analogy precise.
+We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
+%
+\end{draft}
 \begin{todo}[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]\end{todo}

### 2024-06-27 exp-resurgence.tex
Mostly finalize "Thimble integrals in physics"

@@
 
-\begin{revised}
 In the literature on Borel summation, the Airy equation has been discussed many times, using different approaches and conventions.
 In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
-\end{revised} \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
+ \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
 %
@@
 \subsubsection{Thimble integrals in physics}
-\begin{revised}In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
-For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.\end{revised} \begin{todo}\textbf{A} [Mention Voros, and maybe Knoll--Schaeffer?]\end{todo} \begin{revised}In the path integral picture of quantum mechanics, which draws inspiration from wave optics,\end{revised} infinite-dimensional \begin{revised}thimble integrals\end{revised} are supposed to give the expectation values of observable quantities.
-In this context, \begin{revised}the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.\end{revised}
+In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
+For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.
+\begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer].
+[This inspired Voros's work in ``The return of the quartic oscillator'']\end{todo} In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities.
+In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
@@
 Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
-\begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions? Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
+\begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions?
+Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
 %
@@
 
-The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in the \begin{draft}formal solutions\end{draft} \begin{todo}space of formal trans-series solutions [wrong: formal integral is not a trans-series because of direction conflict; say in footnote what the space is]\end{todo} of equation~\eqref{eqn:reg-mod-bessel-AL}.
+The Poincar\'{e} algorithm, as discussed in Section~\ref{sec:asympt-AL} picks out a frame in a space of formal solutions of equation~\eqref{eqn:reg-mod-bessel-AL}.
 The frame is generated by $1$-Gevrey trans-monomial solutions of the form $e^{-z} z^{-1/2}\,\tilde{W}_1$ and $e^z z^{-1/2}\,\tilde{W}_{-1}$, with $\tilde{W}_j \in \C\llbracket z^{-1} \rrbracket_1$.

### 2024-06-27 exp-resurgence.tex
Finalize "links to resurgence"

@@
 %
-\begin{revised}The examples we study all involve {\em resurgent functions} in the position domain.
+The examples we study all involve {\em resurgent functions} in the position domain.
 \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
-Geometric arguments show that when a thimble integral is algebraic \begin{todo}[how is this related to the conditions in \cite{kontsevich2022analyticity}?]\end{todo}, like the ones we use as examples in this paper \begin{todo}[check; does this include the cantilever example?]\end{todo}, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
-Conjecturally, this property extends to more general thimble integrals, like the last example in \cite{Maxim_slide_ERC}.
-The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.\end{revised}
-\begin{old}\par\begin{todo}[The examples we study all involve {\em resurgent functions} in the position domain.] [Say a tiny bit about what resurgence does or is good for.]\end{todo} Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interest in mathematics and physics.
-The resurgence of linear ODEs have been intensively studied \cite{loday1994stokes,diverg-resurg--ii} and many results are also known for non-linear ODEs \cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
-For algebraic thimble integrals of the type we studied in this paper, the resurgence of their asymptotic expansion can be understood geometrically (see \cite{Maxim_slide_ERC}, \cite[Section 6.2]{kontsevich2022analyticity}), however for more general exponential integrals (see the last example in \cite{Maxim_slide_ERC}) resurgence remains conjectural.
-Despite their simplicity, our examples of linear ODEs and of 1-dimensional thimble integrals are toy-models that show some features of resurgent functions.\end{old}
+Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
+Conjecturally, this property extends to more general thimble integrals---perhaps even infinite-dimensional ones \cite[examples~5--6]{Maxim_slide_ERC}.
+The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.
 %\color{gray}

### 2024-06-27 exp-resurgence.tex
Drop old draft of intro

@@
 The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.
-%\color{gray}
-%\begin{itemize}
-%\item The central goal of this paper is to lay out two kinds of problems where we can prove that the Borel sum of a formal power series solution is always an actual solution.
-%\begin{itemize}
-%\item The first problem is evaluating a certain kind of exponential integral: a one-dimensional {\em thimble integral}.
-%\item The second problem is solving a certain kind of ODE.
-%\item These two problems are closely linked.
-By playing with derivatives of an exponential integral, you can often find a linear ODE that the integral satisfies.
-Conversely, for many classical ODEs, there are useful bases of exponential integral solutions.
-%\item \textcolor{magenta}{(Does this touch the Picard-Lefshetz perspective? Betti / de Rham relationship: ODE is a connection, and exponential integrals give flat sections?)}
-%\end{itemize}
-%
-%\item Clearly separate the parts of the theory that deal with holomorphic functions and formal power series.
-%\begin{itemize}
-%\item we can do that also for thimble integrals (this is part 4 of Thm 5.1 in {\tt draft2.pdf})
-%\end{itemize}
-%\item (Super-motivation: why do the zeroes of $\lambda$ play a special role?) As part of the treatment, we've made use of some new perspectives on the Laplace transform.
-%\begin{itemize}
-%\item \textbf{Geometric picture.} The spatial domain $B$ is a translation surface.
-If $b \in B$ is non-singular, the frequency domain for $\laplace_b^\theta$ is $T^* B_b$.
-If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example.
-%\item \textbf{A new dictionary for ODEs.} The Laplace transform is often used to solve ODEs on the frequency domain by relating them to ODEs on the spatial domain.
-We find, however, that it is much easier and more natural to relate ODEs on the frequency domain to integral equations on the spatial domain.
-%\begin{itemize}
-%\item This clarifies why we take the Borel sums at zeroes of $\lambda$ when we are trying to solve an ODE.
-%\end{itemize}
-%\end{itemize}
-%\item Our picture helps explain why it is useful to work on the Borel plane (the position domain).
-%\begin{itemize}
-%\item Integral equations are more regular than differential equations.
-%\item A thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-%\end{itemize}
-%\item Illustrate with detailed treatments of several examples.
-%\begin{itemize}
-%\item Contour argument (thimble integrals)
-%\item solving integral equation (ODE)
-%\item How thimble integrals and ODE are related in our examples?
-%\end{itemize}
-%\begin{itemize}
-%\item Some have been discussed many times, using different approaches and conventions.
-We will try to give an idea of how all these different treatments fit together.
-$\bullet$ The Airy function (Marino, Sauzin).
-$\bullet$ The anharmonic oscillator (Bender--Wu, Schiappa).
-%\item Others haven't been discussed much.
-%\end{itemize}
-%\item Recently, resurgence theory (first developed by \'Ecalle in the '80) has attracted interests in math and physics as a powerful alternative to Borel summability.
-Resurgence of lienar ODEs have been studied (see Costin slides for ReNewQuantum).
-Many results are also known for non linear ODEs (see Schiappa PI, Costin PI).
-For algebraic exponential integrals of the type we studied in this paper, resurgence of their asymptotic expansion can be understood geometrically (see Maxim's slides ReNewQuantum), however for more general exponential integrals (see examples in Maxim's talk) resurgence remains a conjecture.
-Despite their simplicity, our examples of linear ODEs and of exponential integrals show some features of resurgence and they are toy model to get a feeling on \'Ecalle formalism.
-%\item \textcolor{magenta}{The examples give a place to compare more complicated formalisms like the Picard-Lefshetz (Morse theory) or Ecalle formalisms? [How do we work this into the introduction?]}
-%\begin{itemize}
-%\item thimble integrals are geometric in the sense of being pairing between homology and cohomology 
-%\item computation of Stokes constants via Picard--Lefschetz theory
-%\end{itemize}
-%\end{itemize}
-
-%\subsection{Why does Borel resummation work?}
-%
-%\color{gray}
-%
-%Borel resummation is a way of turning a formal power series
-%\[ \series{\varphi} = z^\sigma \left( \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \frac{\varphi_3}{z^4} + \ldots \right), \]
-%with $\sigma \in [0, 1)$, into a function which is asymptotic to $\series{\varphi}$ as $z \to \infty$.
-Different functions can be asymptotic to the same power series, and Borel resummation picks one of them, performing an implicit regularization~\textbf{[arXiv:1705.03071, or maybe arXiv:1412.6614]}.
-When a function matches the Borel sum of its asymptotic series, we will say it is {\em Borel regular}.
-Several familiar kinds of regularity imply Borel regularity, and shed light on why it occurs.
-%%%Knowing that a function is Borel regular gives us extra information about it---enough to reconstruct it from its asymptotic series. What's the nature of this extra information?
-%%%Since different functions can be asymptotic to the same power series, Borel resummation must involve an {\em implicit regularization}, restricting its range to a class of functions which are uniquely determined by their formal power series.
-%\begin{itemize}
-%\item \textbf{Having a good asymptotic approximation}
-%
-%Let $R_N$ be the difference between a function and the partial sum
-%\[ \frac{\varphi_0}{z} + \frac{\varphi_1}{z^2} + \frac{\varphi_2}{z^3} + \ldots + \frac{\varphi_{N-2}}{z^{N-1}} \]
-%of its asymptotic series. Watson showed a century ago that the function is Borel regular whenever there is a constant $c \in (0, \infty)$ with
-%\[ |R_N| \le \frac{c^{N+1} N!}{|z|^N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity (Sokal, ``An improvement of Watson's theorem on Borel summability''; Hardy, {\em Divergent Series}, Theorem~136; Watson, ``A theory of asymptotic series,'' \S 8?).
-%\color{black}
-%
-%\item \textbf{Satisfying a singular differential equation}
-%
-%\begin{itemize}
-%\item This is the setup. We restrict to ODEs with irregular singularity at $\infty$ and of Poincaré rank $1$: 
-%\begin{equation}\label{eqn:standard ODE}
-%\Big[ P(\partial_z)+\frac{1}{z}Q_1(\partial_z)+\sum_{j=2}^d z^{-j}R_j(\partial_z)\Big]\Psi=0
-%\end{equation}
-%where $P(\lambda)$ is a (monic) degree $d$ polynomial, $Q(\lambda)$ is a degree $d-1$ polynomial and $R_j$ is a degree $d-j$ polynomial.
-\textcolor{magenta}{[Looking at the existence theorem in {\tt airy-resurgence} 2.1.3, we could apply this reasoning on the analytic side for more general equations, but this particular case makes it easier to talk about the formal side as well.]} Furthermore we assume $P$ has simple zeros $P(\alpha_j)=0$, $j=1,...,d$ and $Q(\alpha_j)\neq 0$.
-%\item \color{DarkTurquoise}
-%I think we can go more general? If I'm not mistaken, \'{E}calle's equation form \cite[equation~2.2.3, p.~105]{EcalleIII} covers operators like
-%\[ P(\partial_z) + \frac{1}{z} Q_1(\partial_z) + \frac{1}{z^2}\big[ R_0(z^{-1}) + R_1(z^{-1})\,\partial_z + \ldots + R_d(z^{-1})\,\partial_z^d \b], \]
-%where $P$ and $Q$ are as above, and $R_0, \ldots, R_d$ are holomorphic functions on $\C$.
-%\color{black}
-%\item (backgrounds) Under these assumptions, 
-%\begin{itemize}
-%\item \eqref{eqn:standard ODE} admits a basis of formal solutions: let $\tau_j:=Q(-\alpha_j)/P'(-\alpha_j)\in\mathbb{Q}^*$, then the formal solutions $\series{\Psi}_1,...,\series{\Psi}_d$ are of the form \cite{int-irreg} \cite[Proposition~2.2.7, p.~111]{EcalleIII}
-%\begin{equation}
-%\label{formal solution}
-%\series{\Psi}_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{F}_j(z)\in e^{-\alpha_j z } z^{-\tau_j}\,\C \llbracket z^{-\tau_j} \rrbracket
-%\end{equation}
-%Notice that this basis is distinguished only up to scaling, so we have a distinguished frame in the space of formal solutions. 
-%\item \eqref{formal solution} is Borel-Laplace summable and its Borel-Laplace sum $\Psi_j$ satisfies the original equation \eqref{eqn:standard ODE}
-%\item as a consequence, the distinguished frame of formal solutions become a distinguished frame of analytic solutions $\Psi_1,...,\Psi_d$.  
-%\end{itemize}
-%\item Can we see there exists a distinguished basis in a purely analytic way?
-YES.
-[Thm 1]% The reason is the existence theorem gives for every $\alpha_j$ a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-%\item why Borel summations of $\tilde{\Psi_1},...,\tilde{\Psi_d}$ finds this solutions? because they are an analytic frame of Borel regular functions. 
-%\begin{itemize}
-%\item {[Thm 1]}: for every $\alpha_j$ there exists a unique solution in the $\zeta$-plane which blows-up in a certain way at $\alpha_j$: ${\phi}_j(\zeta_j)=\zeta_j^{-\tau_j}+\tilde{f}_j$, $\zeta_j=\zeta-\alpha_j$.
-(proof based on existence theorem \ref{frac_int_exist})
-%\item {[Thm 2]}: The Borel sum of the formal solutions $\series{\Psi}_j$ are the same as the Laplace transform of the solutions of Thm 1. 
-%\item Cor of Thm 2: the Laplace transform of solutions of Thm 1 are Borel regular.   
-%\end{itemize}
-%\item Say there is a unique solution (up to scaling) that shrinks as you go right; everything else blows up exponentially.
-Then this is the only solution that can be expressed as a Laplace transform.
-[Follows from Aaron's argument in Airy resurgence, even if Aaron works with more general ODEs]
-%
-%\item Draw diagram showing formal vs. holomorphic solutions in time vs. frequency domains.
-%
-%\begin{center}
-%\begin{tikzcd}
-%& & ODE\arrow[dd,"\borel"]\arrow[dd,"\laplace^{-1}",swap] & & \\
-%\Phi\arrow[rru,dotted, no head, tail] &\textcolor{red}{\hat{\Phi}}\arrow[ur,red, no head, tail] & & & \series{\Phi}\arrow[llu,"formal",swap, no head, tail]\arrow[dd,"\borel"]\\
-%& & IE & & \\
-%\phi\arrow[rru, no head, tail]\arrow[uu,"\laplace"]& \textcolor{red}{\hat{\phi}}\arrow[ur, no head, tail]\arrow[rrr,"sum",mapsfrom,red]\arrow[uu,"\laplace"]& & & \series{\phi}\arrow[llu, no head, tail]
-%\end{tikzcd}
-%\end{center}
-%
-%where the arrow in red are a consequence of multisummability.
-In addition, we can distinguish on the right hand side of the diagram the formal solutions and on the left hand side the holomorphic ones.
-On the upper part of the diagram the functions in the $z$-plane while on the lower part the functions in the Borel plane $\zeta$-plane.
-%\item  
-%there are many ways to see this problem have a distinguished base of solutions, Poincar\'e see it formally in the $z$-plane, \textcolor{red}{\'Ecalle figured it out how to see it formally in the Borel plane}, our results shows how to see it analytically in  the Borel plane.
-%\item  M.A.E.T.
-says you can start in formal $z$-plane but it is not really constructive (see Balser chap 14); going from formal $\zeta$ to analytic is constructive and it is essentially Borel-Laplace summation.
-Our method uses just Laplace transform.
-%\item How do we know we are picking the same frame?
-from properties of Laplace transform we get solution asymptotics to Poincar\'e frame.
-From uniqueness result we get a frame equivalent to \'Ecalle's frame.
-%\item multi-summability is a regularity result starting form the formal solution in the $z$-plane.
-Borel regularity is instead based on the analytic solution in the $z$-plane.
-The argument we gave about getting the same frame is what proves Borel regularity of $\Psi_j$.
-%\end{itemize}
-%
-%\color{DarkBlue}
-%
-%\item \textbf{Being a thimble integral}
-%
-%\begin{itemize}
-%\item This is the setup. Let $X$ be an algebraic variety of dimension $N$, $f\colon X\to \mathbb{C}$ be a holomorphic Morse function with only simple critical points and $\nu\in\Gamma(X,\Omega^N)$.
-%\begin{itemize}
-%\item recall theory of homology and cohomology to define the thimbles integrals. Pham has briefly discussed it, but apparently was introduced by Malgrange, Milnor and ?.  
-%\end{itemize} 
-%\item background: Pham prove Borel regularity for exponential integral in N-dimension and without assuming Morse critical points (but only isolated).
-His proof is geometric [it may be useful to add it in Appendix].
-%\item \textcolor{red}{We give an analytic proof analogous of Pham.}
-%\item I think we should separate what can we do in general for N-dimensional integral and what is special for the $1$-dimensional one. 
-%\item {[Thm 4]} 1-dim thimbles integrals are Borel regular, namely let 
-%\begin{equation}
-%I_{\alpha}(z)\defeq\int_{\mathcal{C}_\alpha}e^{-zf}\nu
-%\end{equation}
-%
-%then the following diagram is commutative
-%\begin{equation}
-%\begin{tikzcd}
-%I_{\alpha}(z) \arrow[r,"\ae^\theta"] & \series{I}_{\alpha}(z)\arrow[dd,"\borel"]\\
-%& \\
-%\hat{\iota}_\alpha(\zeta)\arrow[uu, "\laplace^\theta_\alpha "] & \series{\iota}_{\alpha}(\zeta) \arrow[l, "\text{sum}"]
-%\end{tikzcd}
-%\end{equation}
-%\begin{itemize}
-%\item on the one hand take asymptotic expansion of integral via saddle point approximation and then study the Borel Laplace sum of the divergent series [from left upper corners clockwise]
-%\item on the other hand \textcolor{red}{see that the thimble integral is a generalized Laplace transform (which in certain cases can be rewritten as a usual Laplace transform).}
-%\item A priori, the Laplace transform of $\hat{\iota}_\alpha(\zeta)$ and $I_{\alpha}(z)$ have the same asymptotic behaviour in a given sector (indeed taking the asymptotic of $I_\alpha(z)$ we \textit{loose} information); however Borel regularity guarantees that $I_{\alpha}(z)=\laplace^{\theta}\hat{\iota}_{\alpha}$ in a given sector.
-%\item A corollary of [Thm 4] is the fractional derivative formula.
-%\item Conjecturally, we expect $\hat{\varphi}_\alpha(\zeta)$ to have simple singularities. 
-%\end{itemize}
-%\item From the result of Pham we can deduce Stokes constants are always integers as they are intersection numbers (use same argument of Maxim).
-See also the argument of KS21 sec 6.2 in the framework of analytic WCFs.
-Prove integrality of Stokes constants using the fractional integral formula vs differential equation (see example in Appendix C)
-%\end{itemize}
-%
-%
-%
-%\subsection{Stokes phenomenon}
-%\begin{itemize}
-%\item For Bessel functions, we can see explicitly how solutions jump when the Laplace transform angle crosses a critical value.
-%\item The jump comes from the branch cut difference identity for hypergeometric functions.
-%\item Possible interpretation of the Stokes factors as intersections numbers in Morse--Novikov theory \textbf{[ask Maxim]}
-%\end{itemize}
+\begin{todo}[Link to Section~\ref{resurgence-AL}]\end{todo}
+%
 \subsection{Organization of the paper}
@@
 \end{revised}
-
-\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
+\begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
 This could help the reader to contextualize our results in the literature.
@@
 We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-\begin{todo}[Appendix~\ref{apx:generalities_ODEs} reviews the main aspects of \cite{reg-sing-volterra}.]\end{todo}
+\begin{todo}[Appendix~\ref{apx:generalities_ODEs}?]\end{todo}
 \end{draft}

### 2024-06-30 exp-resurgence.tex
Finish updating specialization to Airy

@@
 The jump is then given by \[\int_{\mathcal{C}_a^\theta(\beta^+)} \nu - \int_{\mathcal{C}_a^\theta(\beta^-)} \nu\]
-and it is 
-which turns out to be proportional to $\series{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
+and it turns out to be proportional to $\series{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
 %We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
@@
 We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
-It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}{\Lambda}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
+It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
 Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
@@
 By thinking about its shifted Taylor expansion around $\zeta_1 = 0$, we can see more precisely that $v_1$ belongs to
-\[ -i\sqrt{2}\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+\[ -i\sqrt{2}\,\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
 for all $\Lambda > 0$.
@@
 By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
-\[ \sqrt{2}\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
 for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
@@
 %
-\subsubsection{Thimble projection reasoning for Airy-Lucas functions}\label{contour-argument-AL}
+\subsubsection{Thimble projection reasoning}\label{contour-argument-AL}
 We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}.
@@
 \end{verify}
-\color{black}
 %
@@
 \end{align*}
-which has a fractional power singularity at $\zeta=1$.
-In addition, the hypergeometric function ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is convergent at $\zeta=1$ therefore $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.
-More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$.
+\begin{revised}The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.\end{revised} More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$.
 Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
@@
 \end{equation}
-namely, that the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$.
-This is an instance of \textit{resurgent functions}, introduced by \'Ecalle in \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.
-Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
+namely, that \begin{todo}[\end{todo} the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$ \begin{todo}]\end{todo}.
+\begin{revised}This is an example of the of the \em{resurgence} phenomenon introduced by \'{E}calle \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.\end{revised} Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) \begin{todo}[The key here is that we can understand the Stokes phenomenon without completing the Borel summation process---that is, without taking the Laplace transform to go back to the frequency domain.]\end{todo} there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
 The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
@@
 \begin{draft}
-\subsection{Rewriting as a modified Bessel equation}
+\subsection{Specializing from the Airy--Lucas examples\begin{todo}[improve title]\end{todo}}
+\subsubsection{Rewriting as a modified Bessel equation}
 Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing
@@
 \begin{equation}\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\mathcal{C}_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
+K(z) = i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du
 \end{equation}
@@
 \begin{draft}
-\subsection{Asymptotic analysis}%%\label{sec:asympt}
-%
-From the work of Poincar\'{e} and the Ramis Index Theorem, as discussed at the beginning of Section~\ref{sec:new-summability-proof}, we know that equation~\eqref{eqn:reg-mod-bessel} has a frame of formal $1$-Gevrey trans-monomial solutions
+\subsubsection{Asymptotic analysis}%%\label{sec:asympt}
+%
+We know from the formal theory of level~$1$ ODEs that equation~\eqref{eqn:reg-mod-bessel} has a frame of formal $1$-Gevrey trans-monomial solutions
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
 where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
-From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+Specializing the solution formulas given in Section~\ref{sec:asympt-AL}, we find that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp}
@@
 %
-The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
+The analogous holomorphic solutions
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
+which we will describe in Section~\ref{big-idea-airy}, can be recovered from the formal solutions using Borel summation, as we will see in Section~\ref{bessel-regularity}.
+This confirms Theorem~\ref{thm:summability_ODE}.
+%
+\subsubsection{The big idea}\label{big-idea-airy}
+%
+As discussed in Section~\ref{big-idea}, a function $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
+
+%%We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
+We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
+
+%%By the properties of the Laplace transform laid out in Proposition~\ref{prop:L-int-op}, a function $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
+\begin{equation}\label{int-eq:spatial-mod-bessel}
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\end{equation}
+Every solution of equation~\eqref{int-eq:spatial-mod-bessel} will also satisfy the differential equation
+\begin{equation}\label{diff-eq:spatial-mod-bessel}
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0
+\end{equation}
+obtained by differentiating twice on both sides.
+Conversely, as shown in Appendix~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} will satisfy equation~\eqref{int-eq:spatial-mod-bessel} if it belongs to $(\zeta - \alpha)^\sigma \mathcal{O}_{\zeta = \alpha}$ for some $\sigma \in (-1, 0)$.
+Rewriting equation~\eqref{diff-eq:spatial-mod-bessel} as
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0 \]
+emphasizes the regular singularities at the roots of $\zeta^2 - 1$.
+This will lead us, in Sections~\ref{pos-root}\,--\,\ref{neg-root}, to a solution $v_\alpha \in (\zeta - \alpha)^{1/2}\,\mathcal{O}_{\zeta = \alpha}$ for each root $\alpha$.
+
+As described in Section~\ref{big-idea}, each solution $v_\alpha$ will extend to a function in \begin{todo}[\ldots]\end{todo}
+
+%%In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
+For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
+We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other roots (see Figure~\ref{fig:sectorial_domain--with roots P}).
+We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
+It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
+Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
+%%\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\Lambda) \]
+%%for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
+
+%%We know from Section~\ref{sec:change-translation} that
+%%\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+%%for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
+%%\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+%%where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
+%
+\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+%
+Switching to the translation coordinate $\zeta_1$ defined by $\zeta = 1 + \zeta_1$, and then to the rescaled coordinate $\xi_1$ defined by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
+\begin{equation}%%\label{diff-eq:hypergeom-pos}
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0,
+\end{equation}
+as described in Section~\ref{pos-root-AL}. The solution $v_1 \in (\zeta-1)^{-1/2}\,\mathcal{O}_{\zeta=1}$ found in that section specifies to
+\begin{alignat*}{2}
+v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\[1mm]
+&=\;& -i\sqrt{2}\,\zeta_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
+\end{alignat*}
+in the Airy equation case.
+As discussed in Section~\ref{pos-root-AL}, $v_1$ is holomorphic throughout the sector $\Omega_1 = \C \smallsetminus \mathcal{J}^\pi_{\zeta_1, 0}$, and it belongs to the space
+\[ -i\sqrt{2}\,\zeta_1^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+for all $\Lambda > 0$. Its Laplace transform can be written as
+\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
+where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
+%
+\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+%
+We now switch to the translation coordinate $\zeta_{-1}$ defined by $\zeta = -1 + \zeta_{-1}$.
+The solution $v_{-1} \in (\zeta+1)^{-1/2}\,\mathcal{O}_{\zeta=-1}$ found in Section~\ref{neg-root-AL} specifies to
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
+\end{alignat*}
+in the Airy equation case. By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
+\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+for all $\Lambda > 0$. Its Laplace transform can be written as
+\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
+%
+\begin{old}
+Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
+In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
+Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
+\begin{alignat*}{2}
+v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
+\end{alignat*}
+where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
+By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
+\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
+for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
+\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
+\end{old}
+%
+\subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
+In Section~\ref{contour-argument}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions.
+We now specialize even further, down to the case of the Airy function.
+\begin{todo}[\ldots]\end{todo}
+\begin{align*}
+K(z) & = \begin{todo}-\end{todo}i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
+& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right]
+%% & = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_+^2 - 1} - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_-^2 - 1} \right]
+\end{align*}
+\begin{verify}
+\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+K(z) & = \frac{3}{2 \sinh\big(\tfrac{1}{3}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+\end{align*}
+\end{verify}
+Recognizing $4u^3 - 3u$ as the Chebyshev polynomial $T_3(u)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(3\phi)$.
+On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_1$ to the path $\tfrac{\pi}{3} + i\R$.
+The incoming and outgoing branches lift to $\tfrac{\pi}{3} - i[0, \infty)$ and $\tfrac{\pi}{3} + i[0, \infty)$, respectively.
+\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
+
+Recognizing $4u^2 - 1$ as the Chebyshev polynomial $U_2(u)$, we can use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
+\begin{align*}
+\frac{1}{4 \cos(\phi)^2 - 1} & = \frac{1}{U_2(\cos(\phi))} \\
+& = \frac{\sin(\phi)}{\sin(3\phi)} \\
+& = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
+& = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;1 - \zeta^2\right).
+\end{align*}
+Just as in Section~\ref{contour-argument}, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
+&{}_2F_1\left(\frac{1}{3},\;\frac{2}{3}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
+& =\; \hphantom{+} \frac{\pi}{\Gamma\left(\frac{1}{3}\right) \Gamma\left(\frac{2}{3}\right)}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{1}{2};\;\zeta^2\right) \\
+& \hphantom{=}\; - \frac{\pi \zeta}{\Gamma\left(\frac{1}{3}\right) \Gamma\left(\frac{2}{3}\right)}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;\zeta^2\right) \\[3mm]
+& =\; \hphantom{+ \frac{0}{0}}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) + \hphantom{\frac{0}{0}}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\
+& \hphantom{=}\; + \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) - \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\[3mm]
+& =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
+\end{align*}
+away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
+
+In the projected thimble integral
+\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
+we can now see the integrand as the variation of the function
+\[ \frac{1}{4\cos(\phi)^2 - 1} = \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{6}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
+across the branch cut $\mathcal{J}^\theta_{\zeta,1}$.
+The first term is regular at $\zeta = 1$, so only the second term contributes to the jump.
+We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}:
+\[ K(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{6},\;\frac{5}{6};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta.
+\]
+Comparing this expression with the expression for $V_1$ in Section~\ref{pos-root}, we see that
+\[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
+%
+\begin{old}\par
+We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}.
+We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
+Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$.
+The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
+Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
+\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+\end{align*}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}
+
+Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
+On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$.
+The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
+\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
+
+We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
+\begin{align*}
+\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
+& = \frac{\sin(m\phi)}{\sin(n \phi)}\\
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
+\end{align*}
+Initially, we only know that this equation holds in the disk $|\phi| < \tfrac{\pi}{2n}$.
+However, observing that the left-hand side is meromorphic throughout the $\phi$ plane, we can deduce by analytic continuation that the equation holds throughout the $\phi$ plane.
+
+Next, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
+&{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
+& =\; \hphantom{+} \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right) \Gamma\left(1 + \frac{m}{2n}\right)}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{1}{2};\;\zeta^2\right) \\
+& \hphantom{=}\; - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2} - \frac{m}{2n}\right) \Gamma\left(\frac{1}{2} + \frac{m}{2n}\right)}\;{}_2F_1\left(1 - \frac{m}{2n},\;1 + \frac{m}{2n};\;\frac{3}{2};\;\zeta^2\right) \\[3mm]
+& =\; \hphantom{+ \frac{0}{0}}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) + \hphantom{\frac{0}{0}}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\
+& \hphantom{=}\; + \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1+\frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) - \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\[3mm]
+& =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
+\end{align*}
+away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
+
+Returning to the projected thimble integral
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
+we can see the integrand as the variation of the function
+\[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
+\begin{verify}
+\begin{align*}
+\frac{m}{2n}\,\frac{2\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(1+\tfrac{m}{n}\big)} & = \frac{\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(\tfrac{m}{n}\big)} \\
+& = \pi i\,\frac{\sin\big(\pi\tfrac{m}{n}\big)}{\pi} \\
+& = i \sin\big(\pi\tfrac{m}{n}\big) \\
+&= \sinh\big(i\pi\tfrac{m}{n}\big)
+\end{align*}
+\end{verify}
+across the branch cut $\mathcal{J}^\theta_{\zeta, \pm 1}$.
+When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$.
+Similarly, when $j$ is even, only the first term will contribute to the jump.
+We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}.
+For odd $j$, we have
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+and for even $j$, we have
+\[ K^{(j)}_{m/n}(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\]
+
+Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root-AL}\;--\;\ref{neg-root-AL}, we notice that
+\[ K^{(j)}_{m/n}(z) = \begin{cases}
+\hphantom{-}\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
+-\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
+\end{cases} \]
+\begin{verify}
+\begin{align*}
+\zeta & = 1 + \zeta_1 & -\zeta_1 & = 1 - \zeta \\
+\zeta & = -1 + \zeta_{-1} & \zeta_{-1} & = 1 + \zeta
+\end{align*}
+\begin{align*}
+\left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,\zeta_1^{-1/2} \\
+\left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,(-\zeta_{-1})^{-1/2} \\
+& = i\sqrt{2}\,\zeta_{-1}^{-1/2}
+\end{align*}
+\end{verify}
+\end{old}
+%
+\subsection{Thimble projection formula}\label{thimble-proj-airy}
+In Section~\ref{contour-argument-airy}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy function.
+In this section, as an alternative, we will simply apply Lemma~\ref{lem:thimble_proj_formula-proof}, using trigonometric substitution.
+The lemma tells us that $K$ is the Laplace transform of
+\[ \kappa_1 = -i\sqrt{3}\,\frac{\partial}{\partial \zeta}\left(\int_{\mathcal{C}_1^\theta(\zeta)} du\right). \]
+Based on the variable $\phi$ from Section~\ref{contour-argument-airy}, we introduce a new variable $\eta$ defined by $\phi = \tfrac{\pi}{3} + i\eta$, with $u = \cos\big(\tfrac{\pi}{3} + i\eta\big)$ and $\zeta = \cos\big(\pi + 3i\eta\big)$.
+We can lift the thimble $\mathcal{C}^\theta_1$ to the path $\eta \in \R$.
+Its incoming and outgoing branches lift to $(-\infty, 0]$ and $[0, \infty)$, respectively.
+Using the variable $\eta$, we calculate:
+\begin{align*}
+\int_{\mathcal{C}_1^\theta(\zeta)} du & = u \Big|_{\operatorname{start} \mathcal{C}^\theta_1(\zeta)}^{\operatorname{end} \mathcal{C}^\theta_1(\zeta)} \\
+& = u_+ - u_-.
+\end{align*}
+Like in Section~\ref{contour-argument}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
+They give the values of $u$ after lifting to the incoming and outgoing branches of $\mathcal{C}^\theta_1$, respectively.
+We define functions $\eta_-$ and $\eta_+$ similarly, by lifting from the position domain to $\eta \in (-\infty, 0]$ and $\eta \in [0, \infty)$.
+Observing that $\eta_- = -\eta_+$, we can continue the calculation:
+\begin{align*}
+\int_{\mathcal{C}_1^\theta(\zeta)} du & = \cos\big(\tfrac{\pi}{3} + i\eta_+\big) - \cos\big(\tfrac{\pi}{3} + i\eta_-\big) \\
+& = \cos\big(\tfrac{\pi}{3} + i\eta_+\big) - \cos\big(\tfrac{\pi}{3} - i\eta_+\big) \\
+& = \big[\cos\big(\tfrac{\pi}{3}\big) \cos(i\eta_+) - \sin\big(\tfrac{\pi}{3}\big) \sin(i\eta_+)\big] \\
+& \qquad - \big[\cos\big(\tfrac{\pi}{3}\big) \cos(-i\eta_+) - \sin\big(\tfrac{\pi}{3}\big) \sin(-i\eta_+)\big] \\
+& = -2 \sin\big(\tfrac{\pi}{3}\big) \sin(-i\eta_+) \\
+& = i\sqrt{3}\,\sinh(\eta_+).
+\end{align*}
+\begin{verify}
+\begin{align*}
+-2 \sin\big(\tfrac{\pi}{3}\big) \sin(-i\eta_+) & = -2 \tfrac{\sqrt{3}}{2}\;i\sinh(-\eta_+) \\
+& = -i\sqrt{3}\,\sinh(-\eta_+).
+\end{align*}
+\end{verify}
+Identity 15.4.16 from \cite{dlmf} implies that
+%% \[ \sinh(\eta_+) = \tfrac{1}{3} \sinh(3\eta_+)\;{}_2 F_1\left(\frac{1}{3}, \frac{2}{3}; \frac{3}{2}; \sin(3\eta_+)^2\right) \]
+\[ \sinh(\eta_+) = \frac{2}{3} \sinh\big(\tfrac{3}{2}\eta_+\big)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right). \]
+Noticing that $\tfrac{1}{2}(1 - \zeta) = -\sinh\big(\tfrac{3}{2}\eta_+\big)^2$, we conclude that
+\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right), \]
+\begin{verify}
+\begin{align*}
+\int_{\mathcal{C}_1^\theta(\zeta)} du & = \frac{2i}{\sqrt{3}} \sinh\left(\frac{3}{2}\eta_+\right)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right) \\
+& = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right).
+\end{align*}
+\end{verify}
+It follows, through identity~15.5.4 from \cite{dlmf}, that
+\begin{align*}
+\kappa_1 & = 2\,\frac{\partial}{\partial \zeta} \left[ \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right) \right] \\
+& = -\frac{1}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{1}{2}; \frac{1}{2} - \frac{\zeta}{2}\right),
+\end{align*}
+matching the conclusion of Section~\ref{contour-argument-airy}.
+%
+\begin{old}\par
+In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula equation~\eqref{eqn:formula-proof} using trigonometric substitution.
+As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
+
+\textcolor{RoyalBlue}{[\ldots] this time applying the thimble projection formula to the generalized Cardano's formula.}
+
+\textcolor{Peru}{Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
+\begin{align*}
+    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
+    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
+\end{align*}}
+\begin{todo}[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]\end{todo}
+The thimble $\mathcal{C}_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
+Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_1(\zeta)$ are then characterized by
+\begin{align*}
+u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = \cosh(3\theta).
+\end{align*}
+It follows that
+\begin{align*}
+\int_{\mathcal{C}_1(\zeta)} \nu & = \int_{\mathcal{C}_1(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_1(\zeta)}^{\operatorname{end} \mathcal{C}_1(\zeta)}\\
+ & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
+& = -i\sqrt{3}\,\sinh(\theta).
+\end{align*}
+Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh\big(\tfrac{3}{2} \theta\big)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
+\[ \sinh( \theta) = \tfrac{1}{3} \sinh\big( \tfrac{3}{2}\theta\big)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh\big(\tfrac{3}{2}\theta\big)^2\big) \]
+then shows us that
+\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
+\begin{align*}
+\fracderiv{-1/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_1(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
+& = -i \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = \frac{i}{2} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
+\begin{align*}
+\fracderiv{3/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+%
+For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\mathcal{C}_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
+\begin{align*}
+\int_{\mathcal{C}_{-1}(\zeta)} \nu & = \int_{\mathcal{C}_{-1}(\zeta)} du \\
+& = u \Big|_{\operatorname{start} \mathcal{C}_{-1}(\zeta)}^{\operatorname{end}\mathcal{C}_{-1}(\zeta)}.
+\end{align*}
+The start and end points of $\mathcal{C}_{-1}$ are characterized by
+\begin{align*}
+u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
+\zeta & = -\tfrac{2}{3} \cosh(3\theta),
+\end{align*}
+so
+\begin{align*}
+\int_{\mathcal{C}_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
+& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
+& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
+& = i\sqrt{3}\,\sinh(\theta)
+\end{align*}
+Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
+\[ \sinh(\theta) = \sinh(\theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
+then shows us that
+\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu =  (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
+Now we can evaluate the half-integral of $\int_{\mathcal{C}_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
+\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_{-1}(\zeta')} \nu \right)\,d\zeta' \\
+& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\, (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \,d\xi' \big) \\
+& =  \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
+\end{align*}
+Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
+\begin{align*}
+\fracderiv{3/2}{\zeta}{-1} \left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
+& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
+\end{align*}
+\end{old}
 %
 \end{draft}
-\begin{todo}[If we don't have time to redo this section, let's just drop it for now, since you can recover it from the Airy-Lucas section without too much work.]\end{todo}
+%
 \begin{old}
+\begin{todo}\par\textbf{[Really old version starts here]}\end{todo}
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 \[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
-
+%
 \subsection{Thimble projection formula}
-
+%
 In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula equation~\eqref{eqn:formula-proof} using trigonometric substitution.

### 2024-06-30 exp-resurgence.tex
Work on "A flavor of resurgence"

@@
 Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\ldots]\end{todo}\end{revised}
+At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\textbf{A} \textbf{V} \ldots]\end{todo}\end{revised}
 \end{remark}
@@
 %
-\begin{brainstorm}
-\item Up to now, we've treated the Airy-Lucas functions as separate elements of a frame of solutions.
-Using the idea of resurgence, we see that they are actually more closely related.
-You can recover the frame from any one of its elements by studying the analytic continuation in the Borel plane.
-\end{brainstorm}
-\begin{draft}In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
-In both cases we find\end{draft}
-\begin{align*}
-v_1(\zeta) = i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)
-\end{align*}
-\begin{revised}The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a \textit{singularity} in the formalism of \'Ecalle's resurgent functions.\end{revised} More precisely, we can consider ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right)$ as a new holomorphic function (analytic continuation of a new germ at the origin), which has a branch cut singularity at $\zeta=-1$.
-Using equation \cite[15.2.3]{dlmf}, we can compute the analytic continuation of this germ at $\zeta=-1$:
+\begin{revised}
+So far, we have treated the Airy--Lucas functions as separate elements of a frame of solutions.
+However, \'{E}calle's theory of {\em resurgence} reveals that these solutions are deeply intertwined.
+In fact, you can recover the whole frame from any one of its elements by studying the analytic continuation of the corresponding function on the position domain.
+
+\begin{old}In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
+In both cases we find\par\end{old}
+As an example, consider the Borel regular solution $e^{-z} V_1$ of the modified Bessel equation~\eqref{eqn:mod-bessel-AL}, which we found by solving an integral equation in Section~\ref{big-idea} and by evaluating a thimble integral in Section~\ref{contour-argument-AL}.
+This solution arises as the Laplace transform $\laplace^\theta_{\zeta, 1} v_1$ of the function
+%%\[ v_1 = i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right), \]
+\[ v_1 = i \left(\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
+on the position domain.
+The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a {\em singularity} in the formalism of resurgent functions.
+We can see ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ as a new holomorphic function, analytically continued from a germ at $\zeta = 1$.
+This new function has a branch cut singularity at $\zeta=-1$, and we can find the jump across the branch cut $\zeta \in (-\infty, -1]$ using equation~15.2.3 from \cite{dlmf}.
+Along the branch cut, we have
+\begin{old}
 \begin{align*}
@@
 &=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2 i\cos(\pi m/n) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos(\pi m/n) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos(\pi m/n)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
-\end{align*}
-Hence, we deduce  
+&=2 i\cos\big(\tfrac{m}{n}\pi\big) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
+\end{align*}
+\end{old}
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right) \\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2i\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2i\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
+\end{align*}
+Thus, for any point $p$ on the branch cut,
+\begin{draft}
 \begin{equation}\label{resurgent-relation-1}
-    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos(\pi m/n)  v_{-1}(\zeta)
-\end{equation}
-namely, that \begin{todo}[\end{todo} the germ of the singularity at $\zeta=1$ knows about the germ of the singularity at $\zeta=-1$ \begin{todo}]\end{todo}.
-\begin{revised}This is an example of the of the \em{resurgence} phenomenon introduced by \'{E}calle \cite{EcalleI,EcalleII,EcalleIII}\footnote{If the reader is interested in resurgence, it may be useful to look at the following review \cite{diverg-resurg-i,Dorigoni,aniceto2019primer}.}.\end{revised} Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) \begin{todo}[The key here is that we can understand the Stokes phenomenon without completing the Borel summation process---that is, without taking the Laplace transform to go back to the frequency domain.]\end{todo} there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
+v_1(p_+) - v_1(p_-)=2i \cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p), \begin{todo}\text{[wrong]}\end{todo}
+\end{equation}
+\end{draft}
+\begin{old}
+\begin{equation}\label{resurgent-relation-1}
+    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos\big(\tfrac{m}{n}\pi\big) v_{-1}(\zeta)
+\end{equation}
+\end{old}
+where $v_1(p_+)$ and $v_1(p_-)$ respectively denote the evaluation of $v_1(p)$ by analytic continuation from from above and below the branch cut.
+The appearance of the function $v_{-1}$ corresponding to the other Borel regular solution $e^z V_{-1}$ is an example of the {\em resurgence} phenomenon~\cite{EcalleI,EcalleII,EcalleIII}.
+
+Reviews like \cite{diverg-resurg-i,Dorigoni,aniceto2019primer} discuss many details and applications of resurgence.
+We would like to emphasize one application: through resurgence, we can use calculations in the position domain to understand the Stokes phenomenon in the frequency domain.
+This lets us skip the last and often trickiest step of Borel summation: using the Laplace transform to map the functions under consideration back into the frequency domain.
+The {\em formalism of singularities} and the {\em alien calculus} are two of the tools that make this possible.
+\begin{todo}[The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.]\end{todo}
+\end{revised}
+\begin{old}\par
+Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
 The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
-
+\end{old}
+
+\begin{draft}
 We can repeat the same reasoning with $v_{-1}$:
@@
 \begin{equation}\label{resurgent-realtion-2}
-    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
+v_{-1}(p_+) - v_1(p_-)=2i \cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p),
+%%    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
 \end{equation}
@@
 \begin{todo}[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]\end{todo}
+\end{draft}
 %

### 2024-06-30 exp-resurgence.tex
Tidy up Airy appendix for proofreading

@@
 \section{The Airy equation}\label{airy-appendix}
-\begin{draft}
-\subsection{Specializing from the Airy--Lucas examples\begin{todo}[improve title]\end{todo}}
+\subsection{Specializing from the Airy--Lucas examples \begin{todo}[improve title]\end{todo}}
+\begin{revised}
+\subsubsection{Motivation}
+Since the Airy equation is a widely used example in the study of Borel summation and resurgence, we find it useful to repeat the Airy--Lucas example calculations from Sections~\ref{sec:airy}--\ref{example_AL} in this special case, with the parameters set to $n = 3$ and $m = 1$.
+In particular, this makes it easier to compare our approaches and conventions with others from the literature, as we do in Section~\ref{airy-comparison}.
 \subsubsection{Rewriting as a modified Bessel equation}
@@
 %
-\end{draft}
-%
-\begin{draft}
+\end{revised}
+%
 \subsubsection{Asymptotic analysis}%%\label{sec:asympt}
+\begin{revised}
 %
@@
 As discussed in Section~\ref{big-idea}, a function $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-
-%%We are going to look for functions $v_\alpha$ whose Laplace transforms $\laplace_{\zeta, \alpha} v_\alpha$ satisfy equation~\eqref{eqn:reg-mod-bessel-AL}.
-We will succeed when $\alpha^2 - 1 = 0$, and we will see that $K_{m/n}$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-%%By the properties of the Laplace transform laid out in Proposition~\ref{prop:L-int-op}, a function $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel-AL} if and only if $v$ satisfies the integral equation
 \begin{equation}\label{int-eq:spatial-mod-bessel}
@@
 As described in Section~\ref{big-idea}, each solution $v_\alpha$ will extend to a function in \begin{todo}[\ldots]\end{todo}
+\end{revised}
 
@@
 %
+\begin{revised}
 Switching to the translation coordinate $\zeta_1$ defined by $\zeta = 1 + \zeta_1$, and then to the rescaled coordinate $\xi_1$ defined by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
@@
 where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
+\end{revised}
 %
@@
 %
+\begin{revised}
 We now switch to the translation coordinate $\zeta_{-1}$ defined by $\zeta = -1 + \zeta_{-1}$.
@@
 where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
-%
-\begin{old}
+\end{revised}
+\begin{old}\par
 Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
@@
 \subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
-In Section~\ref{contour-argument}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions.
+\begin{revised}
+In Section~\ref{contour-argument-AL}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions.
 We now specialize even further, down to the case of the Airy function.
@@
 \[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
-%
+\end{revised}
 \begin{old}\par
@@
 \subsection{Thimble projection formula}\label{thimble-proj-airy}
+\begin{revised}
 In Section~\ref{contour-argument-airy}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy function.
@@
 \end{align*}
-Like in Section~\ref{contour-argument}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
+Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
 They give the values of $u$ after lifting to the incoming and outgoing branches of $\mathcal{C}^\theta_1$, respectively.
@@
 matching the conclusion of Section~\ref{contour-argument-airy}.
-%
+\end{revised}
 \begin{old}\par
@@
 \end{old}
-%
-\end{draft}
 %
@@
 makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-%\textcolor{Magenta}{Show that $W_1$ is asymptotic to $\tilde{W}_1$!}
-%\color{Peru}
-%\begin{align*}
-%\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ (\zeta - 1)(\zeta + 1) - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v & = 0
-%\end{align*}
-%\color{Sienna}
-%\begin{align*}
-%\left[ \big[ 2 + 2(2\zeta) \tfrac{\partial}{\partial \zeta} + (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 \big] - \big[ 1 + \zeta \tfrac{\partial}{\partial \zeta} \big] - \big(\tfrac{1}{3}\big)^2 \right] v & = 0 \\
-%\left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0 \\
-%\left[ (\zeta - 1)(\zeta + 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v & = 0
-%\end{align*}
-%\color{black}
-%%In terms of the coordinate $\zeta_\alpha$ with $\zeta = \alpha + \zeta_\alpha$, this equation is written
-%%\begin{equation}\label{eqn:centered-mod-bessel}
-%%\[ \left[ \big[ \zeta_\alpha (\zeta_\alpha + 2\alpha) + \alpha^2 - 1 \big] + \fracderiv{-1}{\zeta_\alpha}{0} \circ \big[ \zeta_\alpha + \alpha \big] - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta_\alpha}{0} \right] w = 0.
-\]
-%%\end{equation}
-\subsubsection{Focus on $\zeta = 1$}\label{pos-root}
+\subsubsection{Focus on $\zeta = 1$}%%\label{pos-root}
 Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
@@
 Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}\label{neg-root}
+\subsubsection{Focus on $\zeta = -1$}%%\label{neg-root}
 Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
@@
 In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-\subsection{Borel regularity}\label{bessel-regularity}
+\subsection{Borel regularity}%%\label{bessel-regularity}
 Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
@@
 analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-\subsection{Thimble projection reasoning for the Airy function}\label{contour-argument}
+\subsection{Thimble projection reasoning for the Airy function}%%\label{contour-argument}
 \begin{todo}[Convert to new version]\end{todo} Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.

### 2024-06-30 exp-resurgence.tex
Define dualsingexp colimit space

@@
 We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough.
+Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
+\begin{todo}\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?\end{todo}
 \begin{todo}\par
@@
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
-\begin{todo}[define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
+\begin{todo}[\textbf{A} define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
 \end{theorem}

### 2024-06-30 exp-resurgence.tex
Work on Riemann-Hilbert section

@@
 \subsubsection{Solving Riemann--Hilbert problems}
-\begin{todo}[\textbf{A} Read through]\end{todo} \begin{old}Sometimes\end{old} \begin{draft}always\end{draft} level 1 ODEs can be regarded as the \begin{old}local version\end{old} \begin{draft}coordinate expressions\end{draft} of some global operators, namely as meromorphic connections on some principal bundles (also known as \textit{opers}~\cite{BD-opers}).
-In this case, solutions of the ODE are (local) flat sections for the corresponding connection.
-Therefore, we could use the theory of meromorphic connections to study ODEs, in particular by solving a Riemann--Hilbert problem.
-\begin{todo}
-    add reference
-\end{todo}
-
-To formulate the Riemann--Hilbert problem, we should fix the asymptotic behvaiour of the solution as $z\to0,\infty$ and its discontinuities, namely the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray.
+\begin{todo}[\textbf{A} Read through]\end{todo} \begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
+Local solutions of the ODE correspond to local flat sections of the connection.
+We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
+In particular, we can solve a level~$1$ ODE by solving a Riemann--Hilbert problem.\begin{todo}[add reference]\end{todo}
+
+To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the solution at $z = 0$ and $z = \infty$,\end{revised} and we also fix its discontinuities---the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray.
 Then a solution is given by piecewise analytic function, holomorphic away from the rays and with the prescirbed asymptotics and discontinuities.
@@
 In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
-\begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in~\cite[Section~6.2.1]{kontsevich2022analyticity} Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
-As we mention in Section~\ref{borel-reg:explanatory-power} every thimble integral satisfies some ODE.
+\begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
+As mentioned in Section~\ref{borel-reg:explanatory-power}, every thimble integral satisfies some ODE.
 Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgnt series.

### 2024-06-30 exp-resurgence.tex
Revise through all of "A flavor of resurgence"

@@
 %
-\begin{revised}For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point.
-To explain this aspect of Borel regularity,\end{revised} we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
+For Borel summation to work as described in Theorems~\ref{thm:soln_is_Borel_sum} and~\ref{thm:maxim}, one usually needs to take the Laplace and Borel transforms using a particular position coordinate and integration base point.
+To explain this aspect of Borel regularity, we introduce a geometric picture of the Laplace and Borel transforms, generalizing the position domain from the complex plane to a translation surface $B$.
 Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$.
@@
 %%\[ v_1 = i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right), \]
-\[ v_1 = i \left(\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
+\[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
 on the position domain.
-The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a {\em singularity} in the formalism of resurgent functions.
+The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a {\em singularity} in the formalism of resurgent functions~\cite[Section~2]{sauzin2021variations}.
 We can see ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ as a new holomorphic function, analytically continued from a germ at $\zeta = 1$.
-This new function has a branch cut singularity at $\zeta=-1$, and we can find the jump across the branch cut $\zeta \in (-\infty, -1]$ using equation~15.2.3 from \cite{dlmf}.
+This new function has a branch cut singularity at $\zeta=-1$, and we can find its jump across the branch cut $\zeta \in (-\infty, -1]$ using equation~15.2.3 from \cite{dlmf}.
 Along the branch cut, we have
@@
 &{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right) \\
-&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2i\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2i\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
-\end{align*}
-Thus, for any point $p$ on the branch cut,
-\begin{draft}
-\begin{equation}\label{resurgent-relation-1}
-v_1(p_+) - v_1(p_-)=2i \cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p), \begin{todo}\text{[wrong]}\end{todo}
-\end{equation}
-\end{draft}
-\begin{old}
-\begin{equation}\label{resurgent-relation-1}
-    v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos\big(\tfrac{m}{n}\pi\big) v_{-1}(\zeta)
-\end{equation}
-\end{old}
-where $v_1(p_+)$ and $v_1(p_-)$ respectively denote the evaluation of $v_1(p)$ by analytic continuation from from above and below the branch cut.
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2i\cos\big(\tfrac{m}{n}\pi\big) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=2\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
+&=\left(-\frac{\zeta_{1}}{2}\right)^{1/2}\,2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}\;.
+\end{align*}
+Multiplying both sides by $(-\zeta_1/2)^{-1/2}$ reveals a formula for the jump of $v_1$ across the branch cut. For any point $p$ on the branch cut,
+\begin{equation}\label{eqn:resurg-rel-1}
+v_1(p_-) - v_1(p_+) = 2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p),
+\end{equation}
+%%\begin{old}
+%%\begin{equation}%%\label{resurgent-relation-1}
+%% v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos\big(\tfrac{m}{n}\pi\big) v_{-1}(\zeta)
+%%\end{equation}
+%%\end{old}
+where $v_1(p_-)$ and $v_1(p_+)$ respectively denote the evaluation of $v_1(p)$ by analytic continuation from from the regions $\Im(\zeta) < 0$ and $\Im(\zeta) > 0$.
 The appearance of the function $v_{-1}$ corresponding to the other Borel regular solution $e^z V_{-1}$ is an example of the {\em resurgence} phenomenon~\cite{EcalleI,EcalleII,EcalleIII}.
@@
 \begin{todo}[The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.]\end{todo}
-\end{revised}
 \begin{old}\par
@@
 
-\begin{draft}
+To compute the Stokes constants for the Airy--Lucas functions, we first repeat the calculation above for
+\[ v_{-1} = \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right). \]
+We find that
+\begin{align*}
+&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right) \\
+&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right) \\
+&=2i\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right) \\
+&=-2\cos\big(\tfrac{m}{n}\pi\big) \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right) \\
+&=-2\cos\big(\tfrac{m}{n}\pi\big)\,\left(-\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right) \\
+&=\left(\frac{\zeta_{-1}}{2}\right)^{1/2}\,(-2)\cos\big(\tfrac{m}{n}\pi\big)\,v_1\;.
+\end{align*}
+Multiplying both sides by $(\zeta_{-1}/2)^{-1/2}$ gives the jump formula
+\begin{equation}\label{eqn:resurg-rel-2}
+v_{-1}(p_+) - v_{-1}(p_-) = -2\cos\big(\tfrac{m}{n}\pi\big)\,v_1(p)
+\end{equation}
+for any point $p$ on the branch cut $\zeta \in [1, \infty)$, where again $v_{-1}(p_+)$ and $v_{-1}(p_-)$ denote evaluation by analytic continuation from $\Im(\zeta) > 0$ and $\Im(\zeta) < 0$.
+\end{revised}
+\begin{old}\par
 We can repeat the same reasoning with $v_{-1}$:
@@
 and the analogue of \eqref{resurgent-relation-1} is 
-\begin{equation}\label{resurgent-realtion-2}
+\begin{equation}%%\label{resurgent-realtion-2}
 v_{-1}(p_+) - v_1(p_-)=2i \cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p),
@@
 \end{equation}
+\end{old}
+
+\begin{revised}
+Equations \eqref{eqn:resurg-rel-1} and \eqref{eqn:resurg-rel-2} are a manifestation of the Stokes phenomenon in the position domain.
+When we vary the direction of integration for the Laplace transform, we expect discontinuities at $\laplace^\pi_{\zeta,1}$ and $\laplace^0_{\zeta,-1}$, because each of the contours $\mathcal{J}^\pi_{\zeta,1}$ and $\mathcal{J}^0_{\zeta,-1}$ hits a singularity other than its starting point.
+The Stokes constant for each critical direction relates the results of the Laplace transforms on either side.
+In our example,
+\begin{align*}
+\laplace_{\zeta,1}^{\pi+\varepsilon} v_1 - \hphantom{{}_{-}}\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = \hphantom{-}2\cos\big(\tfrac{m}{n}\pi\big) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
+\laplace_{\zeta,-1}^{\varepsilon} v_{-1} - \laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = -2\cos\big(\tfrac{m}{n}\pi\big) \, e^z \, \laplace_{\zeta,1} v_{1}\;.
+\end{align*}
+so the stokes constants for the directions $\pi$ and $0$ are $2\cos\big(\tfrac{m}{n}\pi\big)$ and $-2\cos\big(\tfrac{m}{n}\pi\big)$, respectively.
+\end{revised}
+\begin{old}\par
 Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are a manifestation of the Stokes phenomena, already in the position domain.
@@
 thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$\footnote{If we think of the Laplace transforms of $v_1$ and $v_{-1}$ as a frame of solutions for the Airy--Lucas differential equation, the equations above define the so-called Stokes matrices for the ODE.}.
-
-It may be surprising that the Stokes constants depend on $\cos(\pi m/n)$, because the Stokes constants are \begin{revised}typically\end{revised} the intersection number of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
+\end{old}
+
+\begin{revised}
+Because the Airy--Lucas functions can always be expressed as thimble integrals, it may seem surprising that the Stokes constants are not always integers.
+For thimble integrals given by Morse functions, the Stokes constants are the intersection numbers of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula~\cite[Section 5]{pham}\cite[Chapter~1]{Arnold}.
+However, the functions $T_n(u)$ defining the Airy--Lucas thimble integrals~\eqref{integral:mod-bessel-rational-AL} are only Morse in the Airy case $n = 3$ and the degenerate limit $n \to \infty$ that we will discuss in Section~\ref{sec:bessel-0}.
+In the other cases, we speculate that the Stokes constants are non-integer because there are multiple thimbles over each critical value.
+\end{revised}
+
+\begin{old}
+The Stokes constants are typically the intersection numbers of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
 Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~1]{Arnold}.
-However, in the Airy--Lucas example, $f$ is not Morse unless $n=3$.
+However, in the Airy--Lucas example, the thimble integral exponent $f$ is not Morse unless $n=3$.
 Hence, we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
 \begin{todo}[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]\end{todo}
-\end{draft}
+\end{old}
 %
@@
 % \color{black}
-\subsubsection{The modified Bessel function with parameter $0$}
+\subsubsection{The modified Bessel function with parameter $0$}\label{sec:bessel-0}
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 %
-\subsubsection{Asymptotic analysis}%%\label{sec:asympt}
+\subsubsection{Asymptotic analysis}\label{sec:asympt-airy}
 \begin{revised}
@@
 \[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which we will describe in Section~\ref{big-idea-airy}, can be recovered from the formal solutions using Borel summation, as we will see in Section~\ref{bessel-regularity}.
+which we will describe in Section~\ref{big-idea-airy}, can be recovered from the formal solutions using Borel summation.
+We showed this abstractly in Section~\ref{bessel-regularity-AL}, and we will confirm it concretely in Section~\ref{confirmation-borel-regularity-airy}.
 This confirms Theorem~\ref{thm:summability_ODE}.
@@
 
-As described in Section~\ref{big-idea}, each solution $v_\alpha$ will extend to a function in \begin{todo}[\ldots]\end{todo}
+As described in Section~\ref{big-idea}, each solution $v_\alpha$ will extend to a function in $\singexpalg{-1/2}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other roots.
+\begin{todo}[\ldots]\end{todo}
 \end{revised}
-
-%%In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
+\begin{old}
+In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
 For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
@@
 Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
-%%\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\Lambda) \]
-%%for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
-
-%%We know from Section~\ref{sec:change-translation} that
-%%\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-%%for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
+\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\Lambda) \]
+for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
+
+We know from Section~\ref{sec:change-translation} that
+\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
 Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
-%%\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-%%where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
+\end{old}
 %
@@
 %
+\subsubsection{Confirmation of Borel regularity}\label{confirmation-borel-regularity-airy}
+\begin{revised}
+%
+We can verify the conclusions of Section~\ref{bessel-regularity-AL} in the Airy case using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
+We found in Section~\ref{sec:asympt-airy} that
+\begin{align*}
+\tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
+\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
+\end{align*}
+Repeating the computation in Section~\ref{confirmation-borel-regularity}, we find that
+\[ \borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!}, \]
+making it apparent that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+Looking back at Section~\ref{pos-root}, we recognize this as a scalar multiple of $v_1$.
+
+Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.
+
+\end{revised}
+\begin{old}
+Just as in Section~\ref{confirmation-borel-regularity}, we compute
+\begin{align*}
+\borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
+& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
+& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
+\end{align*}
+we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
+
+Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
+\end{old}
+%
 \subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
@@
 \end{align*}
-Just as in Section~\ref{contour-argument}, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
+Just as in Section~\ref{contour-argument-AL}, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
 &{}_2F_1\left(\frac{1}{3},\;\frac{2}{3}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
@@
 %
-\subsection{Thimble projection formula}\label{thimble-proj-airy}
+\subsubsection{Thimble projection formula}\label{thimble-proj-airy}
 \begin{revised}

### 2024-06-30 exp-resurgence.tex
Finalize "A flavor of resurgence"

@@
 \begin{todo}\textbf{A} read through copied definition\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$.
-Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
+Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
+The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is a holomorphic function on $B$ defined as
 \begin{equation}\label{eq:convolution_def}
@@
 \end{equation}
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is defined similalrly. \begin{todo}
-    Is it clear the convolution is holomorphic??
-\end{todo}  
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is defined similalrly.
+Notice that the integrand is a function on $B \times B$.
+Each function on $B$ appearing in the expression is decorated with $'$ or $''$ to specify whether it should be seen as a function on the first or the second factor of $B \times B$\begin{todo}[Is it clear the convolution is holomorphic??]\end{todo}
 \end{definition}
@@
 
-   The result of \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product: for every $\tau\in\R_{<0}\cup(0,1)$
+Results \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau\in\R_{<0}\cup(0,1)$
 \begin{align*}
@@
 %
-\begin{revised}
+
 So far, we have treated the Airy--Lucas functions as separate elements of a frame of solutions.
@@
 
-\begin{old}In the previous sections, we have seen how to compute the Borel transform of a formal frame of solutions of the modified Bessel equation with parameter $m/n$ (Section \ref{confirmation-borel-regularity}) or equivalently of the asymptotic expansion of thimble integrals $K_{m/n}$ (Section \ref{contour-argument-AL}).
-In both cases we find\par\end{old}
 As an example, consider the Borel regular solution $e^{-z} V_1$ of the modified Bessel equation~\eqref{eqn:mod-bessel-AL}, which we found by solving an integral equation in Section~\ref{big-idea} and by evaluating a thimble integral in Section~\ref{contour-argument-AL}.
@@
 Along the branch cut, we have
-\begin{old}
-\begin{align*}
-&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right) \\
-&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2 i\cos\big(\tfrac{m}{n}\pi\big) \left(-\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos\big(\tfrac{m}{n}\pi\big) \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=2\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)
-\end{align*}
-\end{old}
+
 \begin{align*}
@@
 Reviews like \cite{diverg-resurg-i,Dorigoni,aniceto2019primer} discuss many details and applications of resurgence.
+Berry and Howls also discuss the optimal truncation of thimble integrals from a resurgence point of view~\cite{Berry_Howls}.
 We would like to emphasize one application: through resurgence, we can use calculations in the position domain to understand the Stokes phenomenon in the frequency domain.
@@
 The {\em formalism of singularities} and the {\em alien calculus} are two of the tools that make this possible.
-\begin{todo}[The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.]\end{todo}
-\begin{old}\par
-Although we will not discuss more about resurgence, we would like to point out that among the great advantages of resurgence (for instance compared to Borel summability) there are the \textit{formalism of singularities} and the \textit{Alien calculus} which allow to understand the Stokes phenomena working in the position domain.
-The same phenomena were described by Berry and Howls \cite{Berry_Howls} who noticed that divergent asymptotic expansions of thimble integrals encode the contribution of other critical values.
-\end{old}
 
@@
 for any point $p$ on the branch cut $\zeta \in [1, \infty)$, where again $v_{-1}(p_+)$ and $v_{-1}(p_-)$ denote evaluation by analytic continuation from $\Im(\zeta) > 0$ and $\Im(\zeta) < 0$.
-\end{revised}
-\begin{old}\par
-We can repeat the same reasoning with $v_{-1}$:
-\begin{align*}
-    v_{-1}(\zeta)=  \left(\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)
-\end{align*}
-and ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}+\frac{\zeta}{2}\right)$ is singular at $\zeta=1$. Hence
-\begin{align*}
-&{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right)=\\
-&=\frac{2\pi i}{\Gamma\big(\tfrac{1}{2}-\tfrac{m}{n}\big)\Gamma\big(\tfrac{1}{2}+\tfrac{m}{n}\big)} \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
-&=2 i\cos(\pi m/n) \left(\frac{\zeta_{1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{m}{n},-\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right) \\
-&=2i \cos(\pi m/n)\, \left(\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_{1}}{2}\right)
-\end{align*}
-and the analogue of \eqref{resurgent-relation-1} is 
-\begin{equation}%%\label{resurgent-realtion-2}
-v_{-1}(p_+) - v_1(p_-)=2i \cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p),
-%%    v_{-1}(\zeta-1+i\varepsilon)-v_{-1}(\zeta-1-i\varepsilon)= -2i\cos(\pi m/n) v_1(\zeta).
-\end{equation}
-\end{old}
-
-\begin{revised}
+
 Equations \eqref{eqn:resurg-rel-1} and \eqref{eqn:resurg-rel-2} are a manifestation of the Stokes phenomenon in the position domain.
@@
 so the stokes constants for the directions $\pi$ and $0$ are $2\cos\big(\tfrac{m}{n}\pi\big)$ and $-2\cos\big(\tfrac{m}{n}\pi\big)$, respectively.
-\end{revised}
-\begin{old}\par
-Equations \eqref{resurgent-relation-1} and \eqref{resurgent-realtion-2} are a manifestation of the Stokes phenomena, already in the position domain.
-Indeed, when we start varying the contour of integration for the Laplace transform, we know that $\laplace_{\zeta,1}^\pi$ and $\laplace_{\zeta,-1}^0$ are not well defined because the contour hits the other singularity (respectively at $\zeta=-1$ and $\zeta=1$).
-The Stokes phenomenon consists of comparing the Laplace transform below and above the critical direction and it quantifies the jump as a constant (the so-called Stokes constant) times another function.
-In our example:
-\begin{align*}
-    \laplace_{\zeta,1}^{\pi+\varepsilon} v_1-\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = 2 i \cos(\pi m/n) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
-    \laplace_{\zeta,-1}^{\varepsilon} v_{-1}-\laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = - 2 i \cos(\pi m/n)  \, e^z \, \laplace_{\zeta,1} v_{1} 
-\end{align*}
-thus the Stokes constants are respectively $\pm 2i \cos(\pi m/n)$\footnote{If we think of the Laplace transforms of $v_1$ and $v_{-1}$ as a frame of solutions for the Airy--Lucas differential equation, the equations above define the so-called Stokes matrices for the ODE.}.
-\end{old}
-
-\begin{revised}
+
 Because the Airy--Lucas functions can always be expressed as thimble integrals, it may seem surprising that the Stokes constants are not always integers.
@@
 In the other cases, we speculate that the Stokes constants are non-integer because there are multiple thimbles over each critical value.
-\end{revised}
-
-\begin{old}
-The Stokes constants are typically the intersection numbers of \textit{dual pairs of thimbles}, according to Picard--Lefschetz formula.
-Stokes constants that arise in this way are integers in a suitable normalization \cite[Section 5]{pham}\cite[Chapter~1]{Arnold}.
-However, in the Airy--Lucas example, the thimble integral exponent $f$ is not Morse unless $n=3$.
-Hence, we have to interpret the $\cos(\pi m/n)$ as a consequence of the ambiguity on the lift of a path in the position domain.
-\begin{todo}[I think we should argue we have the action of the permutation which leaves the base unchanged but gives a\ldots]\end{todo}
-\end{old}
 %

### 2024-06-30 exp-resurgence.tex
First shot at convolution notation cleanup

@@
 \newtheorem*{notation*}{Notation}
+\newtheorem{notation}{Notation}
 
@@
 \item The starting point $\zeta = \alpha$ is in the domain of $\zeta$. Once we have this, we can continue $\zeta$ along the whole ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
-\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = \textcolor{orange}{\alpha}$.
+\item The ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the branch points after leaving $\zeta = \alpha$.
 \item The integral converges. We ensure this by putting conditions on $\phi$ and $z$.
@@
 \subsubsection*{The Laplace transform as algebra homomorphism}
-The Laplace transform $\laplace_{\zeta,\alpha}$ is defined on the space of holomorphic functions in the position domain, integrable at $\zeta=\alpha$ and exponentially bounded at infinity.
-In particular, that subspace of holomorphic functions on $B$, it has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-\begin{old}
-    \begin{definition}%\label{def:convolution}
+The Laplace transform $\laplace_{\zeta,\alpha}$ is defined on the space of holomorphic functions in the position domain which are integrable at $\zeta=\alpha$ and exponentially bounded at infinity.
+This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
+Since we will define the convolution product in terms of an integral along a path in $B \times B$, we must first introduce notation to help us express the integrand.
+\begin{notation}\label{notn:prod}
+The product space $B \times B$ comes with projection maps $\pi', \pi'' \maps B \times B \to B$ onto the first and second factors, respectively.
+Given a function $\phi$ on $B$, we denote $\phi \circ \pi'$ by $\phi'$ and $\phi \circ \pi''$ by $\phi''$.
+\end{notation}
+\begin{definition}\label{def:convolution}
 Let $\phi,\psi$ be two holomorphic functions on $B$.
-Choose a translation cooridnate $\zeta$ on $B$ and a base point $\zeta=\alpha$, then the convolution product $\phi\ast_{\zeta,\alpha}\psi$ is an holomorphic function on $B$ defined as
-\begin{equation}%\label{eq:convolution_def}
-[\phi \ast_{\zeta, \alpha} \psi](a) := \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta,
-\end{equation}
-where $\mathsf{R}$ is the $180^\circ$ rotation that exchanges $\zeta = 0$ with $a$. In other words, $\mathsf{R}^*\zeta = \zeta(a) - \zeta$.
-\begin{brainstorm}
-\item Given a function $f$ on $B$, we will write $f'$ and $f''$ to denote the pullbacks of $f$ to the first and second factors, respectively, of $B \times B$.
-\item For a kernel $k$ on $B \times B$, we the corresponding integral kernel operator would be
-\[ \mathcal{V}\phi = \int_0^\zeta k\,\phi'\,d\zeta' \]
-If we have, for example, $k = (\zeta - \zeta')^\rho$ and $\phi' = (\zeta')^k$, then
-\[ \mathcal{V}\phi = \int_0^\zeta (\zeta - \zeta')^\rho\,(\zeta')^k\,d\zeta' \]
-\item Suppose you have
-\[ \omega = e^\zeta - 1 = \zeta + \tfrac{1}{2!} \zeta^2 + \tfrac{1}{3!} \zeta^3 + \ldots \]
-Then
-\[ \zeta = \log(1 + \omega) = \omega + \tfrac{1}{2} \omega^2 + \tfrac{1}{3} \omega^3 + \ldots \]
-Do you say $\zeta(\omega)$?
-Or $\omega(\zeta)$?
-What does $\omega(\zeta + 1)$ mean?
-Define $f = \zeta + \omega$.
-What is $f(\omega + 1)$?
-$f(\zeta) = \zeta + \omega(\zeta)$.
-So $f(\omega) = \log(1 + \omega) + \omega$, so $f(\zeta) = \zeta + e^\zeta - 1$?
-\[ \int_0^\zeta (\zeta^2 + \zeta'^2)\,d\zeta' \]
-\[ \int_{\zeta=0}^a (\zeta(a)^2 + \zeta^2)\,d\zeta \]
-\[ \int_{\zeta=0}^a (\zeta^2 + \zeta^2)\,d\zeta \]
-\item \begin{todo}\textbf{A} [Draft definition section in this alternate notation]\end{todo} Alternate notation: \textcolor{orange}{[\ldots]} defined as
-\begin{equation}
-    \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'',
-\end{equation}
-where $\mathcal{S}'(\zeta)$ is the line segment connecting $\zeta' = \alpha$ to $\zeta' = \zeta$, and $\mathcal{S}''(\zeta)$ is defined similarly \begin{todo}[check]\end{todo}.
-\item Draw diagram
-\end{brainstorm}
+Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
+The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
+\begin{equation}\label{eq:convolution_def}
+\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta',
+\end{equation}
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta-\alpha$ to $\zeta''=0$. 
 \end{definition}
-\begin{todo}[Show that Laplace transform preserves domain of Laplace transform]\end{todo}
-\begin{draft}On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
-The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta, 0}$.\end{draft}
-% \begin{prop}
-% \begin{todo}[Correct and rewrite!]\end{todo}
-% \begin{old}The Laplace transform $\laplace^\theta_{\zeta,\alpha}$ is a homomorphism from the algebra of locally integrable, exponentially bounded holomorphic functions, equipped with the convolution product, to the algebra of analytic functions on the half-plane $\Re(e^{i\theta} z) > 0$, equipped with the usual product.\end{old}
-% \begin{todo}[Check: if Laplace transform of convolution is well-defined, then product of Laplace transforms is well-defined]\end{todo}
-% \begin{todo}[\textbf{A} Redo argument with $\ast_{\zeta, \beta}$]\end{todo}
-% \begin{draft}
-% \begin{align*}
-% \laplace_{\zeta,\alpha}[{\phi}\ast_{\zeta,\alpha}{\psi}] & = \laplace_{\zeta,\alpha}[{\phi}]\,\laplace_{\zeta,0}[{\psi}]
-% \end{align*}
-% \end{draft}
-% \end{prop}
-\end{old}
-\begin{definition}\label{def:convolution}
-\begin{todo}\textbf{A} read through copied definition\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$.
-Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
-The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is a holomorphic function on $B$ defined as
-\begin{equation}\label{eq:convolution_def}
-\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta'
-\end{equation}
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is defined similalrly.
-Notice that the integrand is a function on $B \times B$.
-Each function on $B$ appearing in the expression is decorated with $'$ or $''$ to specify whether it should be seen as a function on the first or the second factor of $B \times B$\begin{todo}[Is it clear the convolution is holomorphic??]\end{todo}
-\end{definition}
-On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
+The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.
+\begin{todo}[Is it clear the convolution is holomorphic?]\end{todo} On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
 The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
@@
 In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
-\begin{old}
-\begin{definition}
-For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](p) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta =\alpha}^p \big(\zeta(p)-\zeta\big)^{-\nu} \phi\,d\zeta, \]
-where $p$ is any point on the position domain $B$.
-\end{definition}
-\end{old}
 \begin{definition}
@@
 \end{definition}
-\begin{todo}[\textbf{A} Explain that we're using the $'$, $''$ notation, and $\zeta - \zeta'$ is an expression for the function $\zeta''$ on the second factor.]\end{todo}
+Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ along our integration path.
 
@@
 
-Results \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau\in\R_{<0}\cup(0,1)$
+Results \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
 \begin{align*}
@@
 &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}'(\zeta)}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
-&=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi
-\end{align*}
-\begin{todo}[or: where we use the notation from Definition~\{\ldots\}]\end{todo} where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=0$ to $\zeta' = \zeta$.
+&=\laplace_{\zeta,0} \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}}\frac{(\zeta'')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
+&=\laplace_{\zeta,0} \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
+&=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi,
+\end{align*}
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=0$ to $\zeta' = \zeta$, $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta$ to $\zeta''=0$, and we are taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ on the integration path.
 The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
@@
 %\end{align*}
-
 \subsubsection{Integral formula for hypergeometric functions}
-
-In \cite{diverg-resurg-i} the author studies summability and resurgent properties of solutions of the Airy equation.
-
-He considers the formal power series  
+%
+In \cite{diverg-resurg-i} the author studies summability and resurgent properties of solutions of the Airy equation. He considers the formal power series
 \[\series{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
@@
 By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
-
 \begin{align*}
@@
  where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast_{\zeta} \zeta^{-5/6}$.
-
 %Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\series{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
@@
 Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
-
 \begin{align*}

### 2024-07-01 exp-resurgence.tex
Mention that we don't use frequency-domain translations

@@
 Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
-\begin{todo}\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?\end{todo}
+\begin{todo}[\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?]\end{todo}
 \begin{todo}\par
@@
 \subsubsection{Action on translations in the frequency domain}
-\begin{todo}[Explain that this section is optional, used in theory of difference equations in the frequency domain]\end{todo} Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
+Translations in the frequency domain do not play any role in our work, but they do appear in other contexts---for example, in Laplace transform methods for difference equations.
+Since $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we can use the properties of the Laplace transform to deduce how $\borel_\zeta$ acts on translations in the frequency domain.
 It turns out that

### 2024-07-01 exp-resurgence.tex
Tidy up Laplace and Borel identities

@@
 We want to show that 
-\[\borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\right]=\zeta^n.\]
+\[\borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]=\zeta^n.\]
 Recall that $\borel_{\zeta_\alpha}$
@@
   \begin{align*}
-      \borel_{\zeta_\alpha}\left[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\right]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\big[\zeta^n\big]\\
+      \borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\big[\zeta^n\big]\\
       &=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\left[\sum_{k=0}^n{n\choose k}\zeta_\alpha^k \alpha^{n-k}\right]\\
@@
 \end{remark}
-Notice that, assuming the Taylor expansion of $\phi$ and $\psi$ at $\zeta=\alpha$ are convergent in a disk of radius $R$, then the convolution $\phi\ast_{\zeta,\alpha}\psi$ has a convergent Taylor expansion at $\zeta=\alpha$ in the disk of radius $R$ (when $\alpha=0$, see \cite[Lemma 5.14]{diverg-resurg-i} for a proof).
+When the Taylor expansions of $\phi$ and $\psi$ around $\zeta=\alpha$ converge in a disk of radius $R$, the Taylor expansion of the convolution $\phi\ast_{\zeta,\alpha}\psi$ around $\zeta=\alpha$ also converges in a disk of radius $R$.
+This is proven for $\alpha = 0$ in Lemma~5.14 of \cite{diverg-resurg-i}.
 
@@
 \end{align*}
+\begin{revised}
 \begin{prop}\label{prop:L-int-op}
-Let $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, then
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} for every $\mu\in(0,1)$, $\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$;
-\item[(ii)] \emph{[fractional integral]} $\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$ for every $\lambda\in\R_{<0}$;
-\item[(iii)] \emph{[derivative]} let $n\in\Z_{>0}$ and assume that $ \phi^{(k)}(0)=0$ for every $k=0,\ldots,n$.
-Then $\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$;
-\item[(iv)] $\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$, 
-for every $n\in\Z_{\geq 0}$.
-\end{itemize}
+For any $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, we have
+\begin{enumerate}[label=(\roman*)]
+\item\label{res:frac-deriv} \textbf{Fractional derivatives}
+
+$\laplace_{\zeta,0} \big[\fracderiv{\mu}{\zeta}{0} \phi\big] = z^{\mu} \laplace_{\zeta,0} \phi$ for every $\mu\in(0,1)$;
+\item\label{res:frac-int} \textbf{Fractional integrals}
+
+$\laplace_{\zeta,0} \big[\fracderiv{\lambda}{\zeta}{0} \phi\big] = z^{\lambda} \laplace_{\zeta,0} \phi$ for every $\lambda\in(-\infty,0)$;
+\item\label{res:whole-deriv} \textbf{Whole derivatives}
+
+$\laplace_{\zeta,0} \big[\big(\frac{\partial}{\partial\zeta}\big)^n \phi\big] = z^{n} \laplace_{\zeta,0} \phi$ for all $n\in\{1, 2, 3, \ldots\}$, under the condition that $\phi^{(0)}, \phi^{(1)}, \ldots, \phi^{(n)}$ all vanish at $\zeta = 0$;
+\item\label{res:monom-mult} \textbf{Monomial multiplication}
+
+$\laplace_{\zeta,0} \big[\zeta^n \phi\big] = \big(-\frac{\partial}{\partial z}\big)^n \laplace_{\zeta,0} \phi$ for every $n\in\{0,1,2,3,\ldots\}$.
+\end{enumerate}
 \end{prop}
+\end{revised}
 \begin{proof}
@@
 
-Results \emph{(i)} and \emph{(ii)} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
+Results \ref{res:frac-deriv} and \ref{res:frac-int} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
 \begin{align*}
@@
 where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=0$ to $\zeta' = \zeta$, $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta$ to $\zeta''=0$, and we are taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ on the integration path.
-The result of $(iii)$ follows by repetedly using integration by part and the fact that boundary terms vanish:
+Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:
 \begin{align*}
@@
 \end{align*}
-     Finally, the proof of $(iv)$ follows by integration by parts and the fact that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$.   
+Result~\ref{res:monom-mult} is also proven by repeated integration by parts, with the assumption that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ ensuring that the integral converges.
         %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
@@
 We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
+\begin{revised}
 \begin{prop}\label{prop:frac-der-int-borel}
-Let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$ %and let $\hat{\phi}$ be the sum of $\borel_\zeta\series{\Phi}$, then %and $\series{\phi}\defeq\borel_\zeta\series{\Phi}$
-\begin{itemize}
-\item[(i)] \emph{[fractional derivative]} $\borel_\zeta\big[ z^\mu \, \series{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$, for every $\mu\in\R_{> 0}$;
-\item[(ii)] \emph{[fractional integral]} $\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$, for every $\lambda\in\R_{<0}$; 
-\item[(iii)] let $k\in\Z_{\ge 0}$ and $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$.\footnote{This property holds more generally for $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$, without restricting to $1$-Gevrey series.}
-\end{itemize} 
+Let for any $1$-Gevrey series $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, we have
+\begin{enumerate}[label=(\roman*)]
+\item\label{res:frac-deriv-borel} \textbf{Fractional derivatives}
+
+$\borel_\zeta\big[ z^\mu \, \series{\Phi}\big]=\fracderiv{\mu}{\zeta}{0}\, \borel_\zeta\series{\Phi}$ for every $\mu\in(0, \infty)$;
+\item\label{res:frac-int-borel} \textbf{Fractional integrals}
+
+$\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$ for every $\lambda\in(-\infty, 0)$;
+\item\label{res:whole-deriv-borel} \textbf{Whole derivatives} let $k\in\Z_{\ge 0}$ and $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$.\footnote{This property holds more generally for series in $\C\llbracket z^{-1}\rrbracket$, even ones that are not $1$-Gevrey.}
+\end{enumerate} 
 \end{prop}
 \begin{proof} 
-The proof of $(i)$ follows from Lemma \ref{lem:frac-deriv-Borel}.
-
-Then, to prove $(ii)$, first notice that for $\lambda\in\R_{< 0}$  
+Result~\ref{res:frac-deriv-borel} follows from Lemma~\ref{lem:frac-deriv-Borel}.
+
+To prove result~\ref{res:frac-int-borel}, first notice that for $\lambda \in \R_{< 0}$,
 \[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
-Hence, if $\series{\Phi}=\sum_{n\geq 0}a_n z^{-n}$ %and $\hat{\phi}$ denotes the sum of $\borel_\zeta\series{\Phi}$
-\[\borel_\zeta \big[z^\lambda \series{\Phi}\big]=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)}=\sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n=\fracderiv{\lambda}{\zeta}{0}\series{\Phi}\]
-where in the last step, we use that $\borel_\zeta\series{\Phi}$ is convergent.
-
-Finally, $(iii)$ follows from a simple computation: 
+Then, given a series $\series{\Phi} = \sum_{n\geq 0} a_n z^{-n}$, we compute
+\begin{align*}
+\borel_\zeta \big[z^\lambda \series{\Phi}\big] & = \sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)} \\
+& = \sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{n!}\frac{n!}{\Gamma(n-\lambda+1)} \\
+& = \sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n \\
+& = \fracderiv{\lambda}{\zeta}{0}\series{\Phi}.
+\end{align*}
+using the fact that $\borel_\zeta\series{\Phi}$ is convergent in the last step.
+
+Finally, result~\ref{res:whole-deriv-borel} follows from a simple computation: 
 \begin{align*}
@@
 &=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
-&=(-\zeta)^k\borel_\zeta \series{\Phi}
+&=(-\zeta)^k\borel_\zeta \series{\Phi}.
 \end{align*}
 \end{proof}
+\end{revised}
 %

### 2024-07-01 exp-resurgence.tex
Try to patch thimble integral resurgence remark

@@
 By Theorem~\ref{translation} and the results of Section~\ref{sec:reg-decay}, the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ is a left-invertible map
-\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^{\textcolor{LimeGreen}{\bullet}}). \]
+\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet). \]
 With $\Psi_\alpha = \laplace^\theta_{\zeta, \alpha} \psi_\alpha$, the desired result follows.
@@
 %
-\begin{draft}Recall the setting from Section~\ref{borel-reg:explanatory-power}: let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ \begin{todo}[this originally said $\Gamma(X,\Omega^1)$, but shouldn't it be either $\Omega^{1,0}(X)$ or $\Gamma\big(X, \Lambda^{1,0} (X)\big)$?]\end{todo} and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
+\begin{revised}Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
+Let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
 Let $I_a$ be the thimble integral
@@
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step will be to rewrite $I_a$ as the Laplace transform of a function $\iota_a$ which is explicitly given by the well-known formula that we will call the \textit{thimble projection formula}.\end{draft}
+The first step is to rewrite $I_a$ as the Laplace transform of a function $\iota_a$, which is given explicitly by the well-known formula that we will call the \textit{thimble projection formula}.\end{revised}
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula-proof}
@@
 Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
-\begin{todo}[The thimble $\mathcal{C}_a^\theta$ needs an orientation, but the orientation is arbitrary.]\end{todo}
 \end{lemma}
@@
 \fracderiv{-1/2}{\zeta}{\alpha} \phi_a & = \fracderiv{-1}{\zeta}{\alpha} \, \iota_a \\
-    & = \fracderiv{-1}{\zeta}{\alpha} \partial_\zeta \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
+& = \fracderiv{-1}{\zeta}{\alpha} \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
 & = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_a^\theta(\alpha)}\nu.
@@
 \begin{remark}
+\begin{revised}We can use the thimble projection formula to show that each function $\iota_\alpha$ is resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
+Let $\mathcal{J}_\alpha(\beta)$ be the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
+As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\mathcal{C}_a^\theta(\beta)$ in $X$.
+This lets us analytically continue $\int_{\mathcal{C}_a^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
+Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\zeta = \infty$, as shown in Figure~\ref{Fig:slit domain}.\end{revised}
+\begin{old}\par
 We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
@@
 Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
+\end{old}
 \begin{center}
@@
 \end{center}
-
-We will calculate the jump of $\int_{\mathcal{C}_a^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
-Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the points we get by infinitesimally increasing or decreasing $\theta_\beta$.
+\begin{revised}Initially, the function $\int_{\mathcal{C}_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_a(\zeta)$.
+Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to become singular is for something to go wrong with the hotmotopy of $\mathcal{C}_a(\zeta)$, which can only happen at the critical values of $f$.
+Therefore, $\mathcal{C}_a(\zeta)$ is endlessly analytically continuable away from the critical values of $f$.
+Resurgent functions have resurgent derivatives \begin{todo}[check]\end{todo}, so $\iota_\alpha$ is resurgent too.\end{revised}
+\begin{old}\par
+\begin{todo}[Incorporate this additional work]\end{todo} We will calculate the jump of $\int_{\mathcal{C}_a^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
+Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the values we get by infinitesimally increasing or decreasing $\theta_\beta$.
 The jump is then given by \[\int_{\mathcal{C}_a^\theta(\beta^+)} \nu - \int_{\mathcal{C}_a^\theta(\beta^-)} \nu\]
@@
 
-\begin{revised}Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$.
+\begin{todo}[This paragraph is marked as revised]\end{todo} Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$.
 Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\textbf{A} \textbf{V} \ldots]\end{todo}\end{revised}
+At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\textbf{A} \textbf{V} \ldots]\end{todo}
+\end{old}
 \end{remark}

### 2024-07-01 exp-resurgence.tex
Finish revising Riemann-Hilbert intro

@@
 \begin{draft}\begin{todo}\textbf{A}\end{todo} We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
-Our examples are in \begin{todo}???\end{todo}.
+Our examples are in Section~\ref{sec:examples}.
 Section~\begin{todo}???\end{todo} describes the layout of the paper in more detail.
@@
 \subsubsection{Solving Riemann--Hilbert problems}
-\begin{todo}[\textbf{A} Read through]\end{todo} \begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
+\begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
 Local solutions of the ODE correspond to local flat sections of the connection.
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, we can solve a level~$1$ ODE by solving a Riemann--Hilbert problem.\begin{todo}[add reference]\end{todo}
-
-To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the solution at $z = 0$ and $z = \infty$,\end{revised} and we also fix its discontinuities---the Stokes data prescribing the jumps of a frame of solutions across each Stokes ray.
-Then a solution is given by piecewise analytic function, holomorphic away from the rays and with the prescirbed asymptotics and discontinuities.
+In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE.
+\begin{todo}[Add reference]\end{todo}
+
+To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray.
+A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.\end{revised}
 
 In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
-\begin{draft}These cases include some Riemann--Hilbert problems arising from level~1 ODEs.\end{draft} For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
+These cases include some Riemann--Hilbert problems arising from level~1 ODEs.
+For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
 As mentioned in Section~\ref{borel-reg:explanatory-power}, every thimble integral satisfies some ODE.
-Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgnt series.
+Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgent series.
 

### 2024-07-01 exp-resurgence.tex
Drop brainstorming and draft text from intro

@@
 Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgent series.
-
-\begin{brainstorm}
-\item A level~1 ODE can be seen as the flatness condition for sections of a meromorphic connection.
-\item As a result, we can occasionally use the theory of meromorphic connections to solve level~1 ODEs.
-\item Briefly recall what a Riemann--Hilbert problem is.
-\item Describe Maxim's formalism for understanding R--H problems through wall-crossing
-\item Discuss examples where the Riemann--Hilbert problem corresponding to an ODE can be solved.
+\begin{todo}\par
+Discuss examples where the Riemann--Hilbert problem corresponding to an ODE can be solved.
 \begin{itemize}
@@
 \end{itemize}
-\end{brainstorm}
-\begin{old}\par
-However, more absractly, taking as input the set of Stokes data (namely the Stokes ray emanating from the singulairties and the associated Stokes constants) one can set-up a Riemann--Hilbert problem, whose solution would give a frame of analytic solutions of the ODEs~\cite{kontsevich2022analyticity}.
-This is an advantage of resurgence techniques compared to the usual Borel summation method.
-\end{old}
+\end{todo}
 %
@@
 These solutions will turn out to be Borel regular.
-% \par \textcolor{RoyalBlue}{So far we have been discussing the classical approaches to summability and reusrgence of formal divergent solutions of irregular singular ODEs, but a different approach would be to look for analytic solutions of $\mathcal{P}\Phi=0$.
-In other words, we can solve irregular singular ODEs in the frequency domain starting with an analytic \emph{ansatz}.
-Here the standard approach is the so called Laplace method, which takes as \emph{ansatz} a Laplace transform integral.
-This is the approach we adopt in this paper, but our choice of Laplace transform integral is very special, i.e.
-it is a Borel regular solution.}
+
 We use the Laplace transform to turn differential equations on the frequency domain into integral equations on the position domain.
 This runs parallel to \'{E}calle's use of the Borel transform.
-Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.%\textcolor{RoyalBlue}{Like in \'Ecalle's method, the Laplace transform method turns differential equations in the frequency domain into integral equations in the position domain.
-Then, building on our existence and uniqueness results of~\cite{reg-sing-volterra}, we show that analytic solutions of the Laplace transformed ODE can be computed with Picard iteration.} %In addition, as we will show in Section~\ref{sec:new-summability-proof}.
+Building on the existence and uniqueness results we proved in~\cite{reg-sing-volterra}, we use Picard iteration to solve the integral equation in the position domain, and to show that the corresponding solution in the frequency domain is Borel regularizable.
 
@@
 This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
-%\textcolor{RoyalBlue}{A similar approach was taken by Braaksma in~\cite{braaksma2006laplace}, where also the same function spaces we will introduce in Section~\ref{sec:laplace_analytic} have been used to solve system of ODEs whose coefficients are in the form of Laplace transforms.
-However, with our approach, we can solve differetial equations with more general coefficients, and it will be interesting to extend our results to systems of ODEs and generalize Braaksma's results.}
-%
-%
-% \color{RoyalBlue}
-% From a formal perspective, the general theory of linear level~$1$ ODEs suggests to look for formal solutions $\series{\Psi}_\alpha$ of $\mathcal{P}\Phi=0$ in the transmonomial space $\series{\Psi}_\alpha\in e^{-\alpha z} z^{-\tau_\alpha}\C\llbracket z^{-1}\rrbracket$, where $\tau_\alpha=Q(-\alpha)/P’(-\alpha)$~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Since the cirtical values are distinct, the transmonomials $\series{\Psi}_\alpha$ determine a basis up to scaling, giving the space of formal solutions a distinguished frame.
-Then, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of an analytic frame of solutions asymptotic to the formal one, but it  does not give a way to construct that analytic frame (see~\cite[Chapter 14]{balser}).
-To get a constructive proof, a classical approach was to investigate Borel summability of the formal solutions~\cite{loday-Remy2011,diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-For example, the Ramis Index Theorem shows that the $\series{\Psi}_\alpha$ are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
-\textcolor{orange}{[Mention connection to index, in Loday-Richaud, and to the way orders get shifted?]}
-
-% At the same time, a natural question we can ask is whether we can build an analytic frame of solutions, without looking for a formal frame.
-This is possible, as we proved in Theorem~\ref{thm:exist_uniq_ODE} (building on our previous results in~\cite{reg-sing-volterra}), and these solutions turn out to be asymptotic to the formal solutions $\series{\Psi}_\alpha$ (see Corollary~\ref{cor:soln_borel-reg}).
-Recall that the key aspect in the proof of our result~\cite[Theorem~4]{reg-sing-volterra} is going to the position domain and study solutions of an integral equation with a special behaviour at the singular points $\zeta=\alpha$.
-Although our approach and the classical one of Borel summability both focus on the importance of the position domain, we study different equations: on the one hand, we solve integral equations in the position domain; on the other hand, Malgrange solves differential equations analytically in the position domain~\cite{malgrange--fourier}, and in~\cite{loday-Remy2011}, Loday-Richaud and Remy solve perturbed integral equations formally in the position domain (following the approach of \'Ecalle~\cite{EcalleIII}).
-
-% \begin{remark}
-% Our approach of solving regular singular Volterra equation---based on the contraction mapping theorem for suitable Banach spaces \cite{reg-sing-volterra}---is analogous to the one that Braaksma used to solve a different class of non-linear ODEs and difference equations whose coefficients are written as Laplace transforms~\cite{braaksma2006laplace}.
-\textcolor{orange}{Our approach differs from Braaksma's in two ways.
-[\ldots]} \textcolor{RoyalBlue}{What distinguishs our result from Braaksma's is considering the Laplace transform of functions with integrable fractional power singuarities, and even if our result has been proved for linear level~1 ODEs, we allow holomorphic coefficents that are not necesserly Laplace transforms.}
-
-% In future work, it might be useful to combine our approach with Braaksma's
-
-% Combining our approach with Braaksma's, to
-
-% We leave a possible generalization of our result to other classes of ODEs and difference equations for further pubblications.
-\textcolor{orange}{[Let us do more compare-and-contrast!
-Our problem space is sort of orthogonal to Braaksma's, but we use the same solution space, so it seems like there could be a cool interaction there.]}
-% \end{remark}
-
-% \begin{remark}
-% There are many ways to build a frame of solutions for these kinds of ODEs.
-% \begin{center}
-% \begin{tabular}{l|l|l}
-% & \textbf{Analytic} & \textbf{Formal} \\ \hline
-% \textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
-% \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
-% & Fixed-point iteration~\cite{reg-sing-volterra} \\
-% \end{tabular}
-% \end{center}
-% In the late 1800s, Poincar\'{e} did it formally in the frequency domain~\cite{int-irreg}.
-In the late 1900s, \'{E}calle and later authors did it formally in the position domain~\cite{EcalleIII,loday-Remy2011}.
-\'{E}calle also showed that each of his formal solutions sums to a resurgent analytic solution, from which a frame of analytic solutions can be extracted.
-Most recently, we directly constructed a frame of analytic solutions in the position domain~\cite{reg-sing-volterra}.
-
-% In Section~\ref{borel_reg-ODE}, we show that we are all finding the same frame.
-The uniqueness part of \cite[Theorem~4]{reg-sing-volterra} shows that \'{E}calle's formal solutions sum to our analytic ones, and Theorem~\ref{thm:exist_uniq_ODE} guarantees that our solutions are asymptotic to Poincar\'{e}'s ones.
-% \end{remark} 
-%
-%
 %

### 2024-07-01 exp-resurgence.tex
Finalize goals and results section

@@
 
-\begin{draft}\begin{todo}\textbf{A}\end{todo} We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
+\begin{revised}We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
 Our examples are in Section~\ref{sec:examples}.
-Section~\begin{todo}???\end{todo} describes the layout of the paper in more detail.
-\end{draft}
-\begin{old}\par
-First of all, we want to clearly separate the parts of the theory that deal with holomorphic functions and formal series.
-For ODEs, we proved in \cite[Theorem~4]{reg-sing-volterra} how to build an analytic frame of solutions with an explicit growth behavior, while for thimble integrals we will prove in part 3 of Theorem~\ref{thm:maxim} that there is an explicit analytic function whose Laplace transform is the thimble integral itself.
-\textcolor{Maroon}{[In other words, we go directly from the frequency--analytic quadrant to the position--analytic quadrant, without passing through the formal side.]}
-
-Second of all, we want to explain why it is useful to work in the position domain (the Borel plane): on the one hand integral equations are more regular than differential equations.
-On the other hand, a thimble integral in the frequency domain can be recast as the Laplace transform of a function in the position domain.
-
-We will present the statements of our main results in Section~\ref{sec:why_borel_ODE} and Section~\ref{sec:why_borel_thimble}, for ODEs and thimble integrals, respectively.
-The corresponding proofs are collected in Section~\ref{sec:proof_main_results}.
-\end{old}
+Section~\ref{sec:org} describes the layout of the paper in more detail.\end{revised}
+%
 \subsubsection{Why does Borel summation work for solutions of level $1$ ODEs?}\label{sec:why_borel_ODE}
-%\textcolor{DarkCyan}{[Let us try to move some technical detail from here to the section where the result is proved. For example:]}
 %
@@
 %
-\subsection{Organization of the paper}
+\subsection{Organization of the paper}\label{sec:org}
 \begin{revised}

### 2024-07-01 exp-resurgence.tex
Finish opening paragraph of Airy thimble projection reasoning

@@
 We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$.
+Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ runs through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$.
 The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
@@
 K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right],
 \end{align*}
@@
 \section{The Airy equation}\label{airy-appendix}
-\subsection{Specializing from the Airy--Lucas examples \begin{todo}[improve title]\end{todo}}
+\subsection{Specializing from the Airy--Lucas example}
 \begin{revised}
@@
 where
-\begin{equation}\label{integral:mod-bessel}
+\begin{equation}\label{integral:mod-bessel-airy}
 K(z) = i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du
@@
 \end{revised}
-\begin{old}\par
-Let us find a germ in $(\zeta+1)^{\tau_{-1}-1}\,\mathcal{O}_{\zeta=-1}$, for some $\tau_{-1} \in (0, 1)$, that satisfies equation~\eqref{diff-eq:spatial-mod-bessel-AL}.
-In the rescaled coordinate from Section~\ref{pos-root-AL}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} that represents a germ in $(1-\xi_1)^{-1/2}\,\mathcal{O}_{\xi_1=1}$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-By the same reasoning as before, $v_{-1}$ is holomorphic throughout the sector $\Omega_{-1} = \C \smallsetminus \mathcal{J}^0_{\zeta_{-1}, 0}$, and it belongs to the space
-\[ \sqrt{2}\,\zeta_{-1}^{-1/2} + \singexp{1/2}{\Lambda}(\Omega_1) \]
-for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
-\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
-\end{old}
 %
 \subsubsection{Confirmation of Borel regularity}\label{confirmation-borel-regularity-airy}
+%
 \begin{revised}
-%
 We can verify the conclusions of Section~\ref{bessel-regularity-AL} in the Airy case using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
@@
 Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.
-
 \end{revised}
-\begin{old}
-Just as in Section~\ref{confirmation-borel-regularity}, we compute
-\begin{align*}
-\borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(k+\frac{1}{2}\big)} \\
-& = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
-we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
-Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
-
-Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
-Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
-\end{old}
 %
 \subsubsection{Thimble projection reasoning}\label{contour-argument-airy}
+%
 \begin{revised}
@@
 We now specialize even further, down to the case of the Airy function.
-\begin{todo}[\ldots]\end{todo}
-\begin{align*}
-K(z) & = \begin{todo}-\end{todo}i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
-& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right]
-%% & = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_+^2 - 1} - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} \frac{e^{-z\zeta}\,d\zeta}{4u_-^2 - 1} \right]
-\end{align*}
+Like in Section~\ref{contour-argument-AL}, we first recast integral~\eqref{integral:mod-bessel-airy} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$, which implies that $-d\zeta = 3(4u^2 - 1)\,du$.
+Recall from Section~\ref{sec:airy} that the integration contour $\mathcal{C}^\theta_1$ runs through the critical point $u = \tfrac{1}{2}$, with its direction determined by the parameter $\theta$.
+The critical point splits $\mathcal{C}^\theta_1$ into two pieces: the incoming branch, where the orientation of the thimble runs toward the critical point, and the outgoing branch, where the orientation points away.
+Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get \begin{todo}[Check sign of first line]\end{todo}
 \begin{verify}
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+\begin{align*}
 K(z) & = \frac{3}{2 \sinh\big(\tfrac{1}{3}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
@@
 \end{verify}
+\begin{align*}
+K(z) & = -i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
+& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right],
+\end{align*}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
 Recognizing $4u^3 - 3u$ as the Chebyshev polynomial $T_3(u)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(3\phi)$.
@@
 In the projected thimble integral
-\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
+\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
 we can now see the integrand as the variation of the function
@@
 where
-\begin{equation}\label{integral:mod-bessel}
+\begin{equation}%%\label{integral:mod-bessel}
 K(z) = i\sqrt{3} \int_{z^{-1/3}\mathcal{C}_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.

### 2024-07-01 exp-resurgence.tex
Remove scaffolding from Airy specialization

@@
 \end{revised}
-\begin{old}\par
-We can also study the Airy-Lucas functions by applying the thimble projection formula to integral~\eqref{integral:mod-bessel-rational-AL}, specializing the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof}.
-We recast integral~\eqref{integral:mod-bessel-rational-AL} into the $\zeta$ plane by setting $-\zeta = T_n(u)$, which implies that $-d\zeta = n U_{n-1}(u)\,du$.
-Recall from below equation~\eqref{integral:AL} that the integration contour $\mathcal{C}^\theta_j$ run through the critical point $u = \cos\big(\tfrac{j}{n}\pi\big)$, with its direction determined by the parameter $\theta$.
-The critical point splits $\mathcal{C}^\theta_j$ into two pieces: the {\em incoming} branch, where the orientation of the thimble runs toward the critical point, and the {\em outgoing} branch, where the orientation points away.
-Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
-K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
-\end{align*}
-where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}
-
-Since the Chebyshev polynomial $T_n$ is defined by the identity $T_n(\cos(\phi)) = \cos(n\phi)$, we introduce a new variable $\phi$ with $u = \cos(\phi)$ and $-\zeta = \cos(n\phi)$.
-On the $\phi$ plane, which is an infinite branched cover of the $u$ plane, we can lift $\mathcal{C}^\theta_j$ to the path $\tfrac{j}{n}\pi + i\R$.
-The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
-\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
-
-We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
-\begin{align*}
-\frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
-& = \frac{\sin(m\phi)}{\sin(n \phi)}\\
-& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
-& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
-\end{align*}
-Initially, we only know that this equation holds in the disk $|\phi| < \tfrac{\pi}{2n}$.
-However, observing that the left-hand side is meromorphic throughout the $\phi$ plane, we can deduce by analytic continuation that the equation holds throughout the $\phi$ plane.
-
-Next, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
-&{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
-& =\; \hphantom{+} \frac{\pi}{\Gamma\left(1-\frac{m}{2n}\right) \Gamma\left(1 + \frac{m}{2n}\right)}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{1}{2};\;\zeta^2\right) \\
-& \hphantom{=}\; - \frac{\pi \zeta}{\Gamma\left(\frac{1}{2} - \frac{m}{2n}\right) \Gamma\left(\frac{1}{2} + \frac{m}{2n}\right)}\;{}_2F_1\left(1 - \frac{m}{2n},\;1 + \frac{m}{2n};\;\frac{3}{2};\;\zeta^2\right) \\[3mm]
-& =\; \hphantom{+ \frac{0}{0}}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) + \hphantom{\frac{0}{0}}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\
-& \hphantom{=}\; + \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1+\frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) - \frac{1}{2}\;{}_2F_1\left(1-\frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \\[3mm]
-& =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
-\end{align*}
-away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
-
-Returning to the projected thimble integral
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
-we can see the integrand as the variation of the function
-\[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
-\begin{verify}
-\begin{align*}
-\frac{m}{2n}\,\frac{2\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(1+\tfrac{m}{n}\big)} & = \frac{\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(\tfrac{m}{n}\big)} \\
-& = \pi i\,\frac{\sin\big(\pi\tfrac{m}{n}\big)}{\pi} \\
-& = i \sin\big(\pi\tfrac{m}{n}\big) \\
-&= \sinh\big(i\pi\tfrac{m}{n}\big)
-\end{align*}
-\end{verify}
-across the branch cut $\mathcal{J}^\theta_{\zeta, \pm 1}$.
-When $j$ is odd, only the second term will contribute to the jump, because the first term is regular at $\zeta = 1$.
-Similarly, when $j$ is even, only the first term will contribute to the jump.
-We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}.
-For odd $j$, we have
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
-and for even $j$, we have
-\[ K^{(j)}_{m/n}(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
-\]
-
-Comparing the expressions above with the expressions for $v_{\pm 1}$ computed in Sections~\ref{pos-root-AL}\;--\;\ref{neg-root-AL}, we notice that
-\[ K^{(j)}_{m/n}(z) = \begin{cases}
-\hphantom{-}\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
--\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
-\end{cases} \]
-\begin{verify}
-\begin{align*}
-\zeta & = 1 + \zeta_1 & -\zeta_1 & = 1 - \zeta \\
-\zeta & = -1 + \zeta_{-1} & \zeta_{-1} & = 1 + \zeta
-\end{align*}
-\begin{align*}
-\left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,\zeta_1^{-1/2} \\
-\left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,(-\zeta_{-1})^{-1/2} \\
-& = i\sqrt{2}\,\zeta_{-1}^{-1/2}
-\end{align*}
-\end{verify}
-\end{old}
 %
 \subsubsection{Thimble projection formula}\label{thimble-proj-airy}
+%
 \begin{revised}
@@
 \end{revised}
-\begin{old}\par
-In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula equation~\eqref{eqn:formula-proof} using trigonometric substitution.
-As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
-
-\textcolor{RoyalBlue}{[\ldots] this time applying the thimble projection formula to the generalized Cardano's formula.}
-
-\textcolor{Peru}{Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
-\begin{align*}
-    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
-    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
-\end{align*}}
-\begin{todo}[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]\end{todo}
-The thimble $\mathcal{C}_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
-Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_1(\zeta)$ are then characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \cosh(3\theta).
-\end{align*}
-It follows that
-\begin{align*}
-\int_{\mathcal{C}_1(\zeta)} \nu & = \int_{\mathcal{C}_1(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_1(\zeta)}^{\operatorname{end} \mathcal{C}_1(\zeta)}\\
- & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta).
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh\big(\tfrac{3}{2} \theta\big)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
-\[ \sinh( \theta) = \tfrac{1}{3} \sinh\big( \tfrac{3}{2}\theta\big)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh\big(\tfrac{3}{2}\theta\big)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
-\begin{align*}
-\fracderiv{-1/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_1(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
-& = -i \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = \frac{i}{2} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
-\begin{align*}
-\fracderiv{3/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-%
-For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\mathcal{C}_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_{-1}(\zeta)} \nu & = \int_{\mathcal{C}_{-1}(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_{-1}(\zeta)}^{\operatorname{end}\mathcal{C}_{-1}(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_{-1}$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
-\[ \sinh(\theta) = \sinh(\theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu =  (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
-\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_{-1}(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\, (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \,d\xi' \big) \\
-& =  \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
-\begin{align*}
-\fracderiv{3/2}{\zeta}{-1} \left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-\end{old}
-%
 \begin{old}

### 2024-07-01 exp-resurgence.tex
Drop really old version of Airy appendix
Keep "Another solution," though, since that hasn't been replaced by a
newer equivalent.

@@
 \begin{old}
-\begin{todo}\par\textbf{[Really old version starts here]}\end{todo}
-\subsubsection{Rewriting as a modified Bessel equation}
-We can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
-where
-\begin{equation}%%\label{integral:mod-bessel}
-K(z) = i\sqrt{3} \int_{z^{-1/3}\mathcal{C}_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du.
-\end{equation}
-and the contour $\mathcal{C}_1$ is represented in Figure \ref{fig:path_Airy}.
-Saying that $\Ai$ satisfies the Airy equation is equivalent to saying that $K$ satisfies the modified Bessel equation
-\begin{equation}\label{eqn:mod-bessel-1/3}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
-\end{equation}
-In fact, $K$ is the modified Bessel function $K_{1/3}$~\cite[equation~9.6.1]{dlmf}.
-%The method we will demonstrate in Section~\ref{spatial} works for any differential equation
-%\[ \left[ P\big(\tfrac{\partial}{\partial z}\big) + z^{-1} Q\big(\tfrac{\partial}{\partial z}\big) + z^{-2} R(z^{-1}) \right] \varphi = 0, \]
-%where $P$ is a polynomial, $Q$ is a polynomial of one degree lower, and $R$ is an entire function.
-Like we did in equation~\eqref{eqn:reg-mod-bessel-AL}, we can rewrite the modified Bessel equation above as
-
-\begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
-\end{equation}
-%
-\subsection{Asymptotic analysis}
-From the general theory of ODE of Poincar\'e rank $1$, we know that the \textcolor{magenta}{space of trans-series solutions} of~\eqref{eqn:reg-mod-bessel} has a basis of trans-monomials
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \} \]
-where the $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket$ are formal power series in $z^{-1}$.
-From equations 10.40.2 and 10.17.1 of \cite{dlmf}, we learn that $K \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
-\begin{equation}\label{bessel-asymp}
-\series{W}_1 = 1 - \frac{(\tfrac{1}{6})_1 (\tfrac{5}{6})_1}{2^1 \cdot 1!}\;z^{-1} + \frac{(\tfrac{1}{6})_2 (\tfrac{5}{6})_2}{2^2 \cdot 2!}\;z^{-2} - \frac{(\tfrac{1}{6})_3 (\tfrac{5}{6})_3}{2^3 \cdot 3!}\;z^{-3} + \ldots
-\end{equation}
-The holomorphic analysis in Section~\ref{spatial} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
-which seem analogous to the trans-monomials above.
-Borel summation makes the analogy precise.
-We’ll see in Section~\ref{bessel-regularity} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$.
-This is an evidence of \cite[Theorem~4]{reg-sing-volterra}.
-%
-\subsection{Building a distinguished frame of analytic solutions}
-\subsubsection{Going to the spatial domain}\label{spatial}
-%\subsubsection{The big idea}\label{big-idea}
-We are going to look for functions $v_j$ whose Laplace transforms $\laplace_{\zeta, \alpha_j} v_j$ satisfy equation~\eqref{eqn:reg-mod-bessel}.
-We’ll succeed when $\alpha^2 - 1 = 0$, and we will see that $K$ is a scalar multiple of $\laplace_{\zeta, 1} v_1$.
-
-From Proposition~\ref{prop:L-int-op}, we find that $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:reg-mod-bessel} if and only if $v$ satisfies the integral equation
-\begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
-\end{equation}
-It's tempting to differentiate both sides of this equation until we get
-\begin{equation}\label{diff-eq:spatial-mod-bessel}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \right] v = 0,
-\end{equation}
-which is easier to solve.
-However, as we learned in Section~\ref{shifting}, a solution of equation~\eqref{diff-eq:spatial-mod-bessel} satisfies equation~\eqref{int-eq:spatial-mod-bessel} if it is slight and locally integrable at $\zeta = \alpha$.
-
-This is great news, because equation~\eqref{diff-eq:spatial-mod-bessel} has a regular singularity at each root of $\zeta^2 - 1$, and the Frobenius method often gives a slight solution at each regular singular point.
-We can see the regular singularities by moving the derivatives to the right:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{1}{3}\big)^2 \big] \right] v = 0. \]
-In Sections \ref{pos-root}\,--\,\ref{neg-root}, we will see this approach succeed.
-For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = \alpha$.
-We know the function $\laplace_{\zeta, \alpha} v_\alpha$ will satisfy equation~\eqref{eqn:reg-mod-bessel}, and we can even find its asymptotics from the order $\tau_\alpha$ of $v_\alpha$.
-We learned in Section~\ref{translation} that
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-where $V_\alpha = \laplace_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-We can see from Section~\ref{sec:reg-decay} that $V_\alpha$ is asymptotic to a scalar multiple of $z^{ - \tau_\alpha}$ at $z = \infty$, so the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-makes $W_\alpha$ is asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = 1$}%%\label{pos-root}
-Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = 1$.
-Define a new coordinate $\zeta_1$ on $\C$ so that $\zeta = 1 + \zeta_1$.
-In this coordinate, equation~\eqref{diff-eq:spatial-mod-bessel} looks like
-\begin{equation}%%\label{diff-eq:spatial-mod-bessel-pos}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-With another change of coordinate, given by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}\label{diff-eq:hypergeom-pos}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0.
-\end{equation}
-Looking through the twenty-four expressions for Kummer's six solutions, we find one \cite[formula~15.10.12]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 0$:
-\begin{alignat*}{2}
-v_1 &=\;& \hphantom{-i\sqrt{2}}\,\xi_1^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi_1\big) \\
-&=\;& -i\,\left(\frac{\zeta_1}{2}\right)^{-1/2} & {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)
-\end{alignat*}
-From the argument in Section~\ref{spatial}, we know that $\laplace_{\zeta, 1} v_1$ satisfies equation~\eqref{eqn:reg-mod-bessel}, and can be written as $e^{-z} V_1$, where $V_1 = \laplace_{\zeta_1, 0} v_1$.
-Since $v_1$ has order $-1/2$, the decomposition $V_1 = z^{1/2} W_1$ makes $W_1$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-\subsubsection{Focus on $\zeta = -1$}%%\label{neg-root}
-Let us find a solution of equation~\eqref{diff-eq:spatial-mod-bessel} which is slight and locally integrable at $\zeta = -1$.
-In the rescaled coordinate from Section~\ref{pos-root}, this is the point $\xi_1 = 1$.
-Looking again through Kummer's table of solutions, we find another expression \cite[formula~15.10.14]{dlmf} which is manifestly slight and locally integrable at $\xi_1 = 1$:
-\begin{alignat*}{2}
-v_{-1} &=\;& (1-\xi_1)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi_1\big) \\
-&=\;& \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} & F\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{alignat*}
-where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
-From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, has order $-1/2$, the same decomposition $V_{-1} = z^{1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $z^{-1}$ at $z = \infty$.
-
-In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
-Kummer's solutions typically come from six different hypergeometric equations, which are related by the M\"{o}bius transformations that permute their singularities.
-In our case, though, exchanging $1$ with $-1$ keeps equation~\eqref{diff-eq:spatial-mod-bessel} the same.
-%\color{DodgerBlue}
-%If we follow the routine from Section~\ref{pos-root}, rewriting equation~\eqref{diff-eq:spatial-mod-bessel} in the coordinate $\zeta_{-1}$ and then rewriting it again in a more recognizable form, we arrive at the hypergeometric equation
-%\[ \left[\xi_{-1} (1 - \xi_{-1}) \big(\tfrac{\partial}{\partial \xi_{-1}}\big)^2 + 3(\tfrac{1}{2} - \xi_{-1}) \tfrac{\partial}{\partial \xi_{-1}} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0, \]
-%where $\zeta_{-1} = 2\xi_{-1}$.
-This is the same as what we get by substituting $\xi_{-1}$ for $\xi_1$ in Section~\ref{pos-root}!
-In other words, the holomorphic map that pulls $\xi_{-1}$ back to $\xi_1$.
-\subsection{Borel regularity}%%\label{bessel-regularity}
-Recall that $\tilde{W}_1$ is a formal solution of \eqref{eqn:reg-mod-bessel}
-\begin{equation}
-\tilde{W}_1(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n}.
-\end{equation}
-Our goal is to prove that the Borel sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1=\laplace_{\zeta_1,0}v_1$. 
-%
-%\subsubsection{Borel sum of $\tilde{W}_1$}
-%
-%Let us first compute the Borel transform of $\tilde{W}_1$:
-%
-%
-%\begin{align*}
-%\tilde{w}_1(\zeta)&=\delta+\sum_{n=1}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta^{n-1}}{\Gamma(n)}\\
-%&=\delta -\frac{1}{2}\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_{n+1}\left(\frac{5}{6}\right)_{n+1}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{1}{2}\frac{\Gamma(\frac{7}{6})\Gamma(\frac{11}{6})}{\Gamma(\frac{1}{6})\Gamma(\frac{5}{6})}\sum_{n=0}^{\infty}\frac{\left(\frac{7}{6}\right)_{n}\left(\frac{11}{6}\right)_{n}}{\Gamma(n+2)n!}\frac{(-\zeta)^n}{2^n}\\
-%&=\delta-\frac{5}{72}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2,-\frac{\zeta}{2}\right)
-%\end{align*}
-Let us compute the Borel transform of $z^{-1/2}\tilde{W}_1$: notice that the appropriate coordinate is $\zeta_1$ 
-\begin{align*}
-\borel\left[z^{-1/2}\tilde{W}_1(z)\right](\zeta_1)&=\borel\left[\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}z^{-n-\frac{1}{2}} \right](\zeta_1)\\
-&=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{(-1)^n}{2^n}\frac{\zeta_1^{n-\frac{1}{2}}}{\Gamma(n+\frac{1}{2})}\\
-&=\zeta_1^{-1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta_1}{2}\right)
-\end{align*}
-Comparing with the solution $v_1$ computed in Section~\ref{pos-root} we notice that \[v_1(\zeta_1)\propto \borel\left[z^{-1/2}\tilde{W}_1\right](\zeta_1)\]
-therefore the Borel Laplace sum of $z^{-1/2}\tilde{W}_1$ is proportional to $V_1$.
-In particular, both $K$ and $e^{-z}V_1$ are analytic solutions of the Airy equation~\eqref{eqn:reg-mod-bessel} and they have the same asymptotics at $\infty$ up to a multiplicative constant.
-
-Similarly, if we consider the formal power series
-\begin{equation}
-\tilde{W}_{-1}(z)=\sum_{n=0}^{\infty}\frac{\left(\frac{1}{6}\right)_n\left(\frac{5}{6}\right)_n}{n!}\frac{1}{2^n}z^{-n}
-\end{equation}
-analogous computations give that $v_{-1}(\zeta_{-1})\propto\borel\left[z^{-1/2}\tilde{W}_{-1}\right](\zeta_{-1})$.
-\subsection{Thimble projection reasoning for the Airy function}%%\label{contour-argument}
-\begin{todo}[Convert to new version]\end{todo} Generalizing from Section~\ref{contour-argument-AL}, we can recast integral~\eqref{integral:mod-bessel} into the $\zeta$ plane by setting $-\zeta = 4u^3 - 3u$.
-Projecting $z^{-1/3} \mathcal{C}_1$ to a contour \begin{todo}[rephrase in terms of ray]\end{todo} $\mathcal{H}^1_z$ in the $\zeta$ plane and choosing the branch of $u$ that lifts $\mathcal{H}^1_z$ back to $z^{-1/3} \mathcal{C}_1$, we have
-\begin{equation}\label{integral:mod-bessel-zeta}
-K = \frac{i}{\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta}\frac{d\zeta}{4u^2 - 1}.
-\end{equation}
-For $z \in (0, \infty)$, the contour $\mathcal{H}^1_z$ runs clockwise around $[1, \infty)$, as shown below.
-Let us assume $z \in (0, \infty)$ for the rest of the section.
-\begin{todo}[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]\end{todo}
-\begin{center}
-\includegraphics{figures/zeta_contour_3.pdf} \\[1em]
-{\small The contour $\mathcal{H}^1_z$ in the $\zeta$ plane.}
-\end{center}
-From formula~15.4.14 in \cite{dlmf}, we learn that for our desired branch of $u$,
-\[ \frac{1}{4u^2 - 1} = -F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big), \]
-so we can rewrite integral~\eqref{integral:mod-bessel-zeta} as
-\[ K = \frac{1}{i\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big)\;d\zeta. \]
-This gives us an alternate route to the conclusion of Section~\ref{spatial}, which we will follow below.
-
-In addition to the solutions $v_1$ and $v_{-1}$ from Sections~\ref{pos-root}\,--\,\ref{neg-root}, equation~\eqref{diff-eq:spatial-mod-bessel} has the solutions
-\begin{alignat*}{2}
-g_1 &\;=\;& & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi_1\big) \\
-g_{-1} &\;=\;&  & {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi_1\big),
-\end{alignat*}
-given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-
-The quadratic transformation identity 15.8.27 from \cite{dlmf} shows that\footnote{Note that $2\Gamma(\tfrac{1}{2})\Gamma(\tfrac{3}{2}) = 2\Gamma(\tfrac{1}{2})\,\tfrac{1}{2}\Gamma(\tfrac{1}{2}) = \pi$ and $\big[\Gamma(\tfrac{5}{6})\Gamma(\tfrac{7}{6})\big]^{-1} = \big[\Gamma(\tfrac{5}{6})\,\tfrac{1}{6}\Gamma(\tfrac{1}{6})\big]^{-1} = \frac{6\sin(\tfrac{1}{6} \pi)}{\pi} = \frac{3}{\pi}$.}
-\[ F\big(\tfrac{1}{3}, \tfrac{2}{3}; \tfrac{1}{2}; \zeta^2\big) = \tfrac{1}{3}(g_1 + g_{-1}), \]
-so we have
-\[ K = \frac{1}{i\,3\sqrt{3}} \int_{\mathcal{H}^1_z} e^{-z\zeta} (g_1 + g_{-1})\;d\zeta. \]
-The solution $g_{-1}$ is holomorphic on $\zeta \in [1, \infty)$, so it integrates to zero.
-The solution $g_1$, in contrast, is non-meromorphic at $\zeta = 1$.
-Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is $-\tfrac{3\sqrt{3}}{2}\,v_1$,
-as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(\tfrac{2}{3})\Gamma(\tfrac{4}{3})\big]^{-1} = \big[\Gamma(\tfrac{2}{3})\,\tfrac{1}{3}\Gamma(\tfrac{1}{3})\big]^{-1} = \frac{3\sin(\tfrac{1}{3} \pi)}{\pi} = \frac{3\sqrt{3}}{2\pi}$.} by equation~15.2.3 from \cite{dlmf}.
-Hence,
-\begin{align*}
-K & = \frac{i}{2} \int^\infty_1 e^{-z\zeta} v_1\;d\zeta \\
-e^z K & = \frac{i}{2} \int^\infty_1 e^{-z(\zeta - 1)} v_1\;d\zeta \\
-e^z K & = \tfrac{i}{2} \laplace_{\zeta_1} v_1,
-\end{align*}
-just as we found in Section~\ref{bessel-regularity}. However, in this case, we get an exact equality (compared to the proportionality of Section~\ref{bessel-regularity}). 
 \subsubsection{Another solution}
-Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
+\begin{todo}\par\textbf{[From the really old version]}\end{todo} Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
 \[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
@@
 %
-\subsection{Thimble projection formula}
-%
-In the Airy-Lucas integral, $f$ is a Chebyshev polynomial, so we can do a thimble projection technique (see Section~\ref{contour-argument-AL}) or apply the thimble projection formula equation~\eqref{eqn:formula-proof} using trigonometric substitution.
-As an example of how one might reason in the latter case, we look at the Airy function, given by $f = 4u^3-3u$.
-
-\textcolor{RoyalBlue}{[\ldots] this time applying the thimble projection formula to the generalized Cardano's formula.}
-
-\textcolor{Peru}{Recall that the roots of $f(u)-\zeta$ can be written explicitly as 
-\begin{align*}
-    u(\zeta)&=\cos\Big(\frac{1}{3}\arccos\zeta-\frac{2\pi k}{3}\Big) \quad k=0,1,2\\
-    &={}_2F_1\Big(-\frac{1}{6},\frac{1}{6};\frac{1}{2};1-\zeta^2\Big)
-\end{align*}}
-\begin{todo}[Add the numerical check to show simple resurgence. For example, maybe graph exponential of the magnitude of function on position domain]\end{todo}
-The thimble $\mathcal{C}_1$ can be parametrized by the path $\theta \mapsto \cosh(\theta - \tfrac{2}{3}\pi i)$.
-Since $4u^3 - 3u$ is the third Chebyshev polynomial and $\cosh$ is $2\pi$-periodic in the imaginary direction, the start and end points of $\mathcal{C}_1(\zeta)$ are then characterized by
-\begin{align*}
-u & = \cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = \cosh(3\theta).
-\end{align*}
-It follows that
-\begin{align*}
-\int_{\mathcal{C}_1(\zeta)} \nu & = \int_{\mathcal{C}_1(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_1(\zeta)}^{\operatorname{end} \mathcal{C}_1(\zeta)}\\
- & = \cosh(\theta - \tfrac{2}{3}\pi i) - \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& = \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad - \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(-\tfrac{2}{3}\pi i) \\
-& = -i\sqrt{3}\,\sinh(\theta).
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 - \zeta)$, and notice that $\xi = -\sinh\big(\tfrac{3}{2} \theta\big)^2$ at the start and end points. The identity~15.4.16 \cite{dlmf}
-\[ \sinh( \theta) = \tfrac{1}{3} \sinh\big( \tfrac{3}{2}\theta\big)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh\big(\tfrac{3}{2}\theta\big)^2\big) \]
-then shows us that
-\[ \frac{i}{\sqrt{3}} \int_{\mathcal{C}_1(\zeta)} \nu = (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_1} \nu$ using Bateman's fractional integral formula for hypergeometric functions see \cite[Section 4.1]{koornwinder2015fractional}.
-\begin{align*}
-\fracderiv{-1/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_1(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi' - \xi)^{-1/2} \Big[ -{i}{\sqrt{3}}\, (-\xi)^{1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big) \Big] \,\big( -\,d\xi' \big) \\
-& = -i \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = \frac{i}{2} \sqrt{\pi}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}.
-\begin{align*}
-\fracderiv{3/2}{\zeta}{1} \left( \int_{\mathcal{C}_1(\zeta)} \nu \right) & = \left(-\tfrac{\partial}{\partial \xi}\right)^2 \left[ \frac{i\sqrt{\pi}}{2}\,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& =  \tfrac{i\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = \tfrac{i\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
-%
-For completeness, we repeat the computations for $\hat{\phi}_{-1}$: the thimble $\mathcal{C}_{-1}$ can be parametrized by the path $\theta \mapsto -\cosh(\theta - \tfrac{2}{3}\pi i)$. Hence,
-\begin{align*}
-\int_{\mathcal{C}_{-1}(\zeta)} \nu & = \int_{\mathcal{C}_{-1}(\zeta)} du \\
-& = u \Big|_{\operatorname{start} \mathcal{C}_{-1}(\zeta)}^{\operatorname{end}\mathcal{C}_{-1}(\zeta)}.
-\end{align*}
-The start and end points of $\mathcal{C}_{-1}$ are characterized by
-\begin{align*}
-u & = -\cosh(\mp\theta - \tfrac{2}{3}\pi i) \\
-\zeta & = -\tfrac{2}{3} \cosh(3\theta),
-\end{align*}
-so
-\begin{align*}
-\int_{\mathcal{C}_{-1}(\zeta)} \nu & =- \cosh(\theta - \tfrac{2}{3}\pi i) + \cosh(-\theta - \tfrac{2}{3}\pi i) \\
-& =- \big[\cosh(\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& \quad + \big[\cosh(-\theta) \cosh(-\tfrac{2}{3}\pi i) + \sinh(-\theta) \sinh(-\tfrac{2}{3}\pi i)\big] \\
-& = 2\sinh(\theta) \sinh(\tfrac{2}{3}\pi i) \\
-& = i\sqrt{3}\,\sinh(\theta)
-\end{align*}
-Let $\xi = \tfrac{1}{2}(1 + \zeta)$, and notice that $\xi =- \sinh( \theta)^2$ at the start and end points. The identity~15.4.16 in \cite{dlmf}
-\[ \sinh(\theta) = \sinh(\theta)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; -\sinh(\theta)^2\big) \]
-then shows us that
-\[ -\frac{i}{\sqrt{3}} \int_{\mathcal{C}_-(\zeta)} \nu =  (-\xi)^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi\big). \]
-Now we can evaluate the half-integral of $\int_{\mathcal{C}_{-1}} \nu$ using Bateman's fractional integral formula for hypergeometric functions: \begin{align*}
-\fracderiv{-1/2}{\zeta}{-1}\left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_{-1}^\zeta (\zeta - \zeta')^{-1/2} \left( \int_{\mathcal{C}_{-1}(\zeta')} \nu \right)\,d\zeta' \\
-& = \frac{1}{\Gamma\big(\tfrac{1}{2}\big)} \int_0^\xi  (\xi - \xi')^{-1/2} \Big[{i}{\sqrt{3}}\, (-\xi')^{1/2}\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{3}{2}; \xi' \big) \Big] \,\big( \,d\xi' \big) \\
-& =  \frac{\Gamma\big(\tfrac{3}{2}\big)}{\Gamma(2)} (-\xi)\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\xi\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big).
-\end{align*}
-Finally, we differentiate twice using 15.5.4 and 15.5.1 from \cite{dlmf}
-\begin{align*}
-\fracderiv{3/2}{\zeta}{-1} \left( \int_{\mathcal{C}_{-1}(\zeta)} \nu \right) & = \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ - \tfrac{\sqrt{\pi}}{2} \,\xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2} \left(\tfrac{\partial}{\partial \xi}\right)^2 \left[ \xi\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 2; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{\partial}{\partial \xi} \left[ {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; 1; \xi\big) \right] \\
-& = - \tfrac{\sqrt{\pi}}{2}\,\tfrac{5}{12}\, {}_2F_1\big(\tfrac{7}{6}, \tfrac{11}{6}; 2; \xi\big).
-\end{align*}
 \end{old}

### 2024-07-01 exp-resurgence.tex
Polish comparison section

@@
 \section{The Airy equation}\label{airy-appendix}
-\subsection{Specializing from the Airy--Lucas example}
+\subsection{Specializing from the Airy--Lucas example}\label{sec:spec-to-airy}
 \begin{revised}
@@
 
-\begin{todo}[Need a transition here.]\end{todo} In \cite{lectures-Marino}, the author studies the Airy functions as an example of resurgent functions.
-He starts with the formal trans-monomial solutions of the Airy equation:
+In \cite{lectures-Marino}, Mari\~{n}o studies the Airy functions as an example of resurgent functions. He starts with the formal trans-monomial solutions of the Airy equation:
 
@@
 \series{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
-\series{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})
+\series{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})\,,
 \end{align*}  
@@
 %
-In \cite{diverg-resurg-i} the author studies summability and resurgent properties of solutions of the Airy equation. He considers the formal power series
+In \cite{diverg-resurg-i}, Mitschi and Sauzin study summability and resurgent properties of solutions of the Airy equation. They consider the formal power series
 \[\series{\Phi}_{\pm}(z)\defeq \sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}z^{-n}\]
@@
 \end{align*} 
-are formal solutions of the Airy equation. Notice that compared to Mari\~{n}o's formal solutions, Sauzin adopts a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
-
-By looking for solutions of the Borel transformed equation, he wrote the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
+are formal solutions of the Airy equation. Notice that compared to Mari\~{n}o's formal solutions, Mitschi and Sauzin adopt a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
+
+Seeking solutions of the Borel-transformed equation, Mitschi and Sauzin write the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
 \begin{align*}
@@
 
-Notice that the function $\hat{\chi}(\zeta)$ is an hypergeometric function:
-\begin{align*}
-\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast \zeta^{-5/6}\\
+Notice that $\hat{\chi}(\zeta)$ is a hypergeometric function:
+\begin{align*}
+\hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast_\zeta \zeta^{-5/6}\\
 &=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}\int_0^{\zeta}(2\zeta'+\zeta'^2)^{-1/6} (\zeta-\zeta')^{-5/6}d\zeta'\\
@@
 \end{align*}
-where in the last step we use the Euler formula for hypergeometric functions \footnote{The Euler formula is \begin{equation}\label{Euler formula}
+where in the last step we use the Euler formula for hypergeometric functions.\footnote{The Euler formula is \begin{equation}\label{Euler formula}
 {}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
-\end{equation}}. Then, by taking derivatives we recover $\hat{\phi}_{\pm}(\zeta)$:
-
+\end{equation}} By taking derivatives, we recover $\hat{\phi}_{\pm}(\zeta)$: 
 \begin{align*}
@@
 The main advantage of writing Gauss hypergeometric functions as a convolution product relies on \'Ecalle's singularity theory.
-Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities (see part c of \cite[Section 6.14.5]{diverg-resurg-i}).
-Furthermore, the author proves that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions (see \cite[Lemma 6.106]{diverg-resurg-i}).
+Indeed $(2\zeta+\zeta^2)^{-1/6}$ extends analytically to the universal cover of $\C\setminus\lbrace 0,-2\rbrace$ and the convolution with $\zeta^{-5/6}$ does not change the set of singularities \cite[Section~6.14.5(c)]{diverg-resurg-i}.
+Furthermore, Mitschi and Sauzin prove that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions \cite[Lemma 6.106]{diverg-resurg-i}.
 %Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\series{\phi}_{\pm}(\zeta)$ are evident.
-
+%
 \subsubsection{Comparison with exact WKB}
-
-Kawai and Takei study the WKB analysis of the Airy--type Schrodinger equation
-
+%
+In \cite{kawai-takei}, Kawai and Takei \begin{revised}carry out an exact\end{revised} WKB analysis of the Airy-type Schr\"{o}dinger equation
 \begin{equation}
@@
 \end{equation}
-as $\eta\to\infty$.
+\begin{revised}in the $\eta \to \infty$ limit\end{revised}.
 They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
@@
 \psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};s\big)\\
-\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};1-s\big)
-\end{align*}
-where $s=t/2+1/2$. 
-The same hypergeometric functions have been computed in Section~\ref{sec:airy} as the Borel transform of the formal solutions of the Airy equation
-
+\psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};1-s\big)\,,
+\end{align*}
+where $s=t/2+1/2$. \begin{revised}We found the same hypergeometric functions in the position domain while solving the Airy equation
 \begin{equation}
 \label{Airy}
-\left[\big(\tfrac{d}{dw}\big)^2 -  w \right] f(w) = 0.
-\end{equation}
-
-Although the two equations look closely related (they are equivalent by the change of coordinates $w=x\eta^{2/3}$), the Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$ (which is the conjugate variable of $t$) while the Borel transform of $f(w)$ is computed with respect to $w$.
-So we need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
-
-First of all notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
+\left[\big(\tfrac{d}{dw}\big)^2 -  w \right] f(w) = 0
+\end{equation}
+in Section~\ref{sec:spec-to-airy}.
+Although the two equations look closely related, and they are equivalent under the change of coordinates $w=x\eta^{2/3}$, they differ in an important way.
+The Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$, the conjugate variable of $t$, while the Borel transform of $f(w)$ is computed with respect to $w$.\end{revised} We need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
+
+\begin{revised}To do this, first\end{revised} notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
 \begin{align*}
@@
 \end{align*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ solves 
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$.
+Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ \begin{revised}satisfies\end{revised}
 \begin{equation}
@@
 \begin{remark}
-The change of coordinate $q=\frac{2}{3}\eta x^{3/2}$ is not casual: recall that the WKB ansatz for a Schrodinger type equation is
-
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB ansatz for a Schrodinger type equation is
 \begin{equation}
-\psi(x,\eta)=\exp\left(\int_{x_0}^xS(\eta,x')dx'\right)
-\end{equation} 
- and $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. In addition, for the Airy--type Schrodinger equation 
- \begin{align*}
- S_{-1}^2=x
- \end{align*}
-hence, up to a choice of sign for the square root
-\begin{align*}
-q&=\frac{2}{3}\eta x^{3/2}=\eta\int_0^x\sqrt{x'}dx'=\eta\int_{0}^xS_{-1}(x')dx'.
-\end{align*}
+\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')dx'\right),
+\end{equation}
+with $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. For the Airy-type Schrodinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
+\[ q = \frac{2}{3}\eta x^{3/2}=\eta\int_0^x (x')^{1/2}\;dx' = \eta\int_{0}^x S_{-1}(x')\;dx'. \]
 We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.

### 2024-07-01 exp-resurgence.tex
Link to "A flavor of resurgence" from intro
Change some `draft` environments to `revised`
Also, alphabetically order thanks in acknowledgments.

@@
 The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.
-\begin{todo}[Link to Section~\ref{resurgence-AL}]\end{todo}
+\begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
 %
@@
 
-We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
+We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
 %
@@
 In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
-\begin{todo}[Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}
+\begin{todo}[\textbf{V} Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}
 \subsubsection{Thimble integrals in physics}
@@
 Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
-\begin{draft}Along $\mathcal{C}$, we have \begin{todo}[\textbf{A} where does the estimate come from?]\end{todo}
+\begin{revised}Along $\mathcal{C}$, we have \begin{todo}[\textbf{A} where does the estimate come from?]\end{todo}
 \[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
@@
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big). \]
-\begin{todo}[Why on $\mathcal{C}$ the real part of $z$ is bounded like that?]\end{todo}\end{draft}
-%%Choose a path $\textcolor{magenta}{\mathcal{C}}$ through $\widehat{\Omega}_\alpha^\Lambda$ on which
-%%\[ \Delta = m + \sin(\varepsilon)\,|t|, \]
-%%where $t$ is an arc length parameter.
-
-%Choose any path $\textcolor{magenta}{\mathcal{C}}$ that runs through $\widehat{\Omega}_\alpha^\Lambda$ at a constant distance from the boundary, oriented so that the boundary is on its left.
-The inverse Laplace transform is given by the formula
+\begin{todo}[Why on $\mathcal{C}$ the real part of $z$ is bounded like that?]\end{todo}\end{revised}
 
@@
 where $c''=\max\{c,c'\}$.
-\begin{draft}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{draft}
+\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{revised}
 %   

### 2024-07-01 exp-resurgence.tex
Drop old draft passages about `reg-sing-volterra` on coverings

@@
 This is proven for $\alpha = 0$ in Lemma~5.14 of \cite{diverg-resurg-i}.
-
-\begin{todo}Move before calculation of Laplace transform of convolution, write more if needed, and also make sure it's actually correct. The old text below has mistakes.\end{todo}
-\begin{old}\par In addition, the convolution product induces a $\C$-algebra structure on the space $\singexp{\sigma}{\Lambda}$, and the Laplace transform is an algebra isomorphism.
-\begin{todo}[actually need $\Omega_0$ in lemma]\end{todo}
-\begin{lemma}
-If $\Omega_0$ is star-shaped around $\zeta = 0$, then for any $\sigma > -1$ and $\Lambda > 0$, the space $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ is closed \begin{todo}[no; revise]\end{todo} under the convolution product $\ast_{\zeta, \alpha}$.
-\textcolor{RoyalBlue}{Let $\phi,\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, then $\phi\ast_{\zeta,\alpha}\psi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.}
-\end{lemma}
-\begin{proof}
-Suppose $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$. The convolution integral
-\[ [\phi \ast_{\zeta, \alpha} \psi](a) = \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,|d\zeta| \]
-can then always be evaluated along the path $\zeta = (1-t)\,\alpha + t\,\zeta(a)$ parameterized by $t \in (0, 1)$.
-
-For any $\phi, \psi \in \singexp{\sigma}{\Lambda}(\Omega_\alpha)$, we have
-\begin{align*}
-\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & = \left| \int_{\zeta = \alpha}^a \psi\,\mathsf{R}^*\phi\,d\zeta \right| \\
-& \le \int_{\zeta = \alpha}^a |\psi|\,|\mathsf{R}^*\phi|\,|d\zeta| \\
-& \le \int_{\zeta = \alpha}^a \Big( |\zeta - \alpha|^\sigma e^{\Lambda|\zeta - \alpha|}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( |\zeta(a) - \zeta|^\sigma e^{\Lambda|\zeta(a) - \zeta|}\,\|\phi\|_{\sigma, \Lambda} \Big)\,|d\zeta|.
-\end{align*}
-Using the shorthand $\delta \defeq |\zeta(a) - \alpha|$, we compute
-\begin{align*}
-\big| [\phi \ast_{\zeta, \alpha} \psi](a) \big| & \le \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,dt \\
-& = \int_{\zeta = \alpha}^a \Big( [\delta t]^\sigma e^{\Lambda\delta t}\,\|\psi\|_{\sigma, \Lambda} \Big)\,\Big( [\delta(1-t)]^\sigma e^{\Lambda\delta(1-t)}\,\|\phi\|_{\sigma, \Lambda} \Big)\,d\zeta
-\end{align*}
-\begin{todo}[\ldots]\end{todo}
-\end{proof}
-\begin{verify}
-\begin{proof}
-    \begin{align*}
-    |\series{\phi}\ast\series{\psi}|&=\left|\int_0^\zeta\series{\phi}(\zeta-\zeta')\series{\psi}(\zeta')\, d\zeta'\right|\\
-        &\le \int_0^\zeta |\series{\phi}(\zeta-\zeta')||\series{\psi}(\zeta')|\, d\zeta'\\
-        &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')|-\zeta+\zeta+\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta+\zeta'|}\, d\zeta'\\
-        &\le ||\series{\psi}||_{\sigma,\Lambda}  \int_0^\zeta\series{\phi}(\zeta-\zeta')(|\zeta|+|-\zeta+\zeta'|)^{\sigma}e^{\Lambda(|\zeta|+|-\zeta+\zeta'|)}\, d\zeta'\\
-        &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-        &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\series{\psi}||_{\sigma,\Lambda} ||\series{\phi}||_{\sigma,\Lambda}. 
-    \end{align*}
-\end{proof}
-\end{verify}
-\begin{corollary}
-For any $\sigma > -1$ and $\Lambda > 0$, the Laplace transform 
-\[ \laplace_{\zeta,\alpha}^\theta\colon\singexp{\sigma}{\Lambda}(\Omega_\alpha) \to \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
-is a $\C$-algebra isomomorphism, with inverse defined in Proposition~\ref{prop:inverse_laplace_analytic}. 
-\end{corollary}\end{old}
 %
@@
 \[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
-\begin{brainstorm}
-\item \begin{todo}[Find right phrasing]\end{todo} Our arguments in \cite{reg-sing-volterra} took place on the complex plane, but they work just as well on appropriate covers of punctured complex planes.
-The universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$ is a convenient setting for the following result.
-\end{brainstorm}
-
 \begin{lemma}\label{lem:shifted_holo_closed}
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-Noting that \begin{draft}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{draft},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
+Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
 \begin{align*}
@@
 \end{proof}
-\begin{old}
-\textcolor{orange}{[\ldots]} Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering of $\C$ which is branched at the roots of $P(-\zeta)$.
-Let us use the covering $\pi \maps \widetilde{B}_{P(-\zeta)} \to \C$ built by puncturing $\C$ at the roots of $P(-\zeta)$, taking the universal cover, and then gluing the roots back in as infinite-order branch points.
-\end{old}
 \begin{todo}[Add flavor text]\end{todo}

### 2024-07-01 exp-resurgence.tex
Define 1-Gevrey series
Make sure the term isn't used before it's defined.

@@
 From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
-On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
+On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that \begin{revised}their Borel transforms converge\end{revised}, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
 We do this in Section~\ref{sec:new-summability-proof}.
 \subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thimble}
-%\textcolor{DarkCyan}{Let $X$ be an $N$-dimensional complex manifold, and $f\colon X\to\C$ a proper holomorphic map with non-degenerate critical points.}
-%%Our treatment of thimble integrals will be based on our geometric picture of the Laplace transform, briefly sketched in Section~\ref{sec:other_results}.
-\textcolor{orange}{[Can you remind me why we discuss the geometric picture here?
-Is it to justify doing things in a coordinate-independent way?]}
 In Section~\ref{borel-reg:explanatory-power}, we gave the general form of a thimble integral associated with a map $f \maps X \to \C$.
@@
 If we want to get analytic information from the Borel transform---for example, by doing Borel summation---we should focus on the series whose Borel transforms converge.
-\begin{old}\textcolor{LimeGreen}{These are the {\em $1$-Gevrey} series mentioned in Section~\ref{intro:summation}.}\end{old} Within $\C \llbracket z^{-1} \rrbracket$, the $1$-Gevrey series form a subspace $\C \llbracket z^{-1} \rrbracket_1$.
+These series, called {\em $1$-Gevrey} series, form a subspace $\C \llbracket z^{-1} \rrbracket_1$ within $\C \llbracket z^{-1} \rrbracket$.
 They are characterized by the factorial growth of their coefficients.
+\begin{revised}
+\begin{definition}
+A series
+\[ \sum_{n \ge -1} a_n z^{-n-1} \]
+is {\em $1$-Gevrey} if there is some $A > 0$ with $|a_n| \lesssim A^n n!$ over all $n \ge 0$.
+\end{definition}
+\end{revised}
 \begin{prop}\label{prop:gevrey_to_convergent}
@@
 
-In Section~\ref{sec:new-summability-proof}, we will look at the same class of ODEs from a more formal perspective, starting from the assumption that Poincar\'{e}'s solutions exist and are $1$-Gevrey.
+In Section~\ref{sec:new-summability-proof}, we will look at the same class of ODEs from a more formal perspective, starting from the assumption that Poincar\'{e}'s solutions exist and their Borel transforms converge.
 Using the existence and uniqueness results that characterize the Borel regular solutions, we give a new proof that Poincar\'{e}'s solutions are Borel summable.

### 2024-07-01 exp-resurgence.tex
Finish specializing "big idea" to Airy case

@@
 They are characterized by the factorial growth of their coefficients.
-\begin{revised}
 \begin{definition}
@@
 \end{definition}
-\end{revised}
 \begin{prop}\label{prop:gevrey_to_convergent}
@@
 As described in Section~\ref{big-idea}, each solution $v_\alpha$ will extend to a function in $\singexpalg{-1/2}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other roots.
-\begin{todo}[\ldots]\end{todo}
+The arguments of Section~\ref{big-idea} go on to show that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
+\[ cz^{-\tau_\alpha} + \dualsingexp{-3/2}(\widehat{\Omega}_\alpha^\Lambda) \]
+for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}. Continuing through Section~\ref{big-idea}, we get the decomposition
+\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
+for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and the further decomposition
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-1/2} W_\alpha, \]
+where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
+
+The argument from Section~\ref{bessel-regularity-AL} shows that the solutions $e^{-\alpha z} V_\alpha$ are Borel regular.
+This argument is just as simple in general as it is in the Airy case, so we will not repeat it.
 \end{revised}
-\begin{old}
+\begin{old}\par
 In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.

### 2024-07-01 exp-resurgence.tex
Drop scaffolding from "big idea" for Airy

@@
 
-The argument from Section~\ref{bessel-regularity-AL} shows that the solutions $e^{-\alpha z} V_\alpha$ are Borel regular.
+The argument in Section~\ref{bessel-regularity-AL} shows that the solutions $e^{-\alpha z} V_\alpha$ are Borel regular.
 This argument is just as simple in general as it is in the Airy case, so we will not repeat it.
 \end{revised}
-\begin{old}\par
-In Sections \ref{pos-root-AL}\,--\,\ref{neg-root-AL}, we will see this approach succeed.
-For each root $\alpha$, we will find a solution $v_\alpha$ of equation~\eqref{diff-eq:spatial-mod-bessel-AL} that belongs to $(\zeta - \alpha)^{\tau_\alpha-1}\,\mathcal{O}_{\zeta = \alpha}$ for some constant $\tau_\alpha \in (0, 1)$.
-We will express $v_\alpha$ explicitly enough to see that it extends to a function in $\singexpalg{\tau_\alpha-1}(\Omega_\alpha)$ on any sector $\Omega_\alpha$ that has its tip at $\zeta = \alpha$ and does not touch the other roots (see Figure~\ref{fig:sectorial_domain--with roots P}).
-We will also be able to see that $v_\alpha$ is uniformly of exponential type $\Lambda$ for any $\Lambda > 0$.
-It follows by Proposition~\ref{prop:laplace-cont} that for any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$, the Laplace transform $\laplace^\theta_{\zeta, \alpha} v_\alpha$ is a well-defined element of $\dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$ that satisfies equation~\eqref{eqn:reg-mod-bessel-AL}.
-Using the technique from the proof of Lemma~\ref{lem:laplace-bridge}, we can see more precisely that $\laplace^\theta_{\zeta, \alpha} v_\alpha$ belongs to
-\[ cz^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\Lambda) \]
-for some non-zero constant $c$, confirming the existence part of Theorem~\ref{re:thm:exist_uniq_ODE}.
-
-We know from Section~\ref{sec:change-translation} that
-\[ \laplace^\theta_{\zeta, \alpha} v_\alpha = e^{-\alpha z} V_\alpha \]
-for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$.
-Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
-where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
-\end{old}
 %

### 2024-07-01 exp-resurgence.tex
Clean up thimble results draft text
Also, uncolor bullet in `dualsingexp` colimit space.

@@
 The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
-\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^{\textcolor{LimeGreen}{\bullet}}) \right] \]
+\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
 of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
@@
 \end{center}
-%%
-%%supposing for the moment that $X$ is an $N$-dimensional complex manifold.
-%%
-%%Each connected component of the preimage $f^{-1}(\mathcal{J}_{\zeta, \alpha}^\theta)$ runs through a critical point of $f$.
-When {\em Lefschetz thimble} is a component that runs through a non-degenerate critical point.
-%%
-%%To \textcolor{orange}{[\ldots]}, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
-Near $a$ we can always find coordinates $t_1, \ldots, t_N$ on $X$ with $f = t_1^2 + \ldots + t_N^2$.
-%%
-%%To see why the term ``thimble'' is fitting, consider a non-degenerate critical point $a$ in the preimage of $\zeta = \alpha$, and let $\mathcal{C}^\theta_a$ be the Lefschetz thimble that runs through it.
-Near $a$ we can always find coordinates $x_1, \ldots, x_N$ on $X$ in which $\mathcal{C}^\theta_a$ looks like the paraboloid
-%%where $\zeta = \alpha + \zeta_\alpha$. \textcolor{orange}{[\ldots]}
 

### 2024-07-01 exp-resurgence.tex
Promote order shifting to top-level appendix

@@
 %
-\begin{paragraph}{Appendix~\ref{apx:generalities_ODEs}}
+\begin{paragraph}{Appendix~\ref{shifting}}
 We prove a fact about the relationship between integral and differential equations which is used in some of our examples.
@@
 We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-\begin{todo}[Appendix~\ref{apx:generalities_ODEs}?]\end{todo}
+\begin{todo}[Appendix~\ref{shifting}?]\end{todo}
 \end{draft}
@@
 \end{remark} 
-
-\section{Facts about differential and integral equations}\label{apx:generalities_ODEs}
-%%\section{Generalities about ODEs and Integral Equations}\label{apx:generalities_ODEs}
-\begin{todo}
-\subsection{Passing between the analytic world and the formal world}
-[Show that the Taylor expansion of an analytic solution of an integral equation satisfies the same equation (or just cite the statement in Erdelyi).
-Cite the theorem of Erdelyi which shows that a solution of a differential equation (under certain conditions) has an asymptotic expansion, which satisfies the corresponding differential equation.]
-\end{todo}
-\subsection{Order shifting for integro-differential equations}\label{shifting}
+%
+\section{Order shifting for integro-differential equations}\label{shifting}
 For a differential equation with a regular singularity at $\zeta = 0$, the Frobenius method typically gives a convergent power series solution in $\zeta^\rho\,\C\{\zeta\}$ for some $\rho \in \R$, which sums to a germ in $\zeta^\rho\,\mathcal{O}_{\zeta=0}$.
 When $\rho$ is a non-integer greater than $-1$, we can do a nice trick in this space of germs: we can pass back and forth between differential and integral equations without worrying about boundary conditions.
-%
-%%\textcolor{SteelBlue}{Consider an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}, and a power $\rho \in \R \smallsetminus \Z$.
-As a solution space for integro-differential equations on $\Upsilon$, the function space $\zeta^\rho \mathcal{O}(\pi \Upsilon)$ has a convenient feature: we can pass back and forth between integral and differential equations without worrying about boundary conditions.}
-%
-%%\textcolor{SteelBlue}{To make this statement precise, we need some terminology.
-For any $\sigma \in \R$, let us say that the {\em order} of a function in $\zeta^\sigma \mathcal{O}(\pi \Upsilon)$ is the lowest power appearing in its shifted Laurent expansion, or $-\infty$ if there is no lowest power.
-A function is locally integrable at $\zeta = 0$ if and only if its order is greater than $-1$.
-For convenience, we will say that function is {\em regular} at $\zeta = 0$ if its order is a non-negative integer.}
 \begin{prop}\label{prop:shifting}

### 2024-07-01 borel-regularity.tex
Rename main draft to `borel-regularity`
Rename bibliography too.
Drop commented-out draft text from intro

--- 2024-07-01 exp-resurgence.tex
@@
 Through Borel summation, one can often reconstruct an analytic solution of a problem from its asymptotic expansion.
-%%can often turn a formal solution of a problem into an analytic one.
 We view the effectiveness of Borel summation as a regularity property of the solution, and we show that the solutions of certain differential equation and integration problems are regular in this sense.
@@
 To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
-
-% \textcolor{RoyalBlue}{
-% Borel regularity is a new approach to Borel summability, that present Borel summation as a regularization process and it explains the effectiveness of Borel summability, namely that Borel summation can be used to reconstruct analytic functions from their asymptotics.
-\textcolor{orange}{[Highlight analytic perspective more?]} Borel regular functions shows up in two classes of examples: as solutions of certain level $1$ ODEs and as integrals over Lefschetz thimbles.
-In addition, we give a geometric description of the Borel plane.}
 \end{abstract}
@@
 %
-%
-%
 \section{Introduction}
+%
 \subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
-%%\subsection{A familiar process: Borel summation}\label{intro:summation}
-You can often find a formal power series %\textcolor{magenta}{[double-check that this matches the $\tau$ from the position domain]}
+You can often find a formal power series \begin{todo}[double-check that this matches the $\tau$ from the position domain]\end{todo}
 \[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-%\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
-Ask more about this.]}
+\begin{todo}[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
+Ask more about this.]\end{todo}
 \item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
@@
 Conversely, for many classical ODEs, there are useful bases of thimble integral solutions.
-
-%Notice that our starting point is quite different: we assume $\Phi$ is a holomorphic functions such that it is either a thimble integral or it solves an ODE with irregular singularity at $\infty$.
-Then we prove $\Phi$ is Borel regular and in both cases, our proves follow the heuristic of the diagram above.
-We’ll give precise statements in the following section.
-
-%%\item {\em A priori}, we should expect $\hat{\Phi}$ to be different from $\Phi$, because we lose information in passing from $\Phi$ to its asymptotic series.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ is a regularization process, because it smooths away some perturbations---the ones that are asymptotic to zero along the given ray.
-We will call it {\em Borel regularization}.
-%%\item Taking the Borel sum of the asymptotic series of $\Phi$ can be seen as a regularization process, because taking asymptotics erases information.
-We will call this process {\em Borel regularization}.
-%\begin{itemize}
-%\item We will say $\Phi$ is {\em Borel-regularizable} if it is asymptotic to a Borel-summable power series.
-%\item We will say $\Phi$ is {\em Borel regular} if it is Borel-regularizable and Borel regularization leaves it unchanged.
-%\item We have the following vector space inclusions:
-%\[ \text{Borel regular functions} \subset \text{Borel-regularizable functions} \subset \text{holomorphic functions}. \]
-%\item Borel regular functions have been characterized in the literature before; Watson showed a century ago \textcolor{orange}{[Watson]} that a function $\Phi$ is Borel regular whenever there is a constant $c \in (0, \infty)$ with
-%\[ |\Phi(z)-\sum_{k=0}^Nc_kz^{-k}| \le c^{N+1} N!|z|^{-N} \]
-%over all orders $N$ and all $z$ in a wide enough wedge around infinity. 
-%
-%Nevanlinna's improvement of Watson's theorem (Sokal, ``An improvement of Watson's theorem on Borel summability'') tells us that for a function $\Phi$ with a well-defined inverse Laplace transform $\phi$, the following conditions are equivalent \textcolor{magenta}{[double check]}:
-%\begin{itemize}
-%\item $\Phi$ is Borel regular.
-%\item $\Phi$ is approximated well, in a certain sense (a weak version of being ``Gevrey-asymptotic''), by its asymptotic series.
-%\item $\phi$ grows at most exponentially along the Laplace transform ray.
-%\end{itemize}
-%\item When its domain is restricted to the space of Gevrey power series, Borel summation is invertible.
-\textcolor{magenta}{[Need to find a good reference for this, because a small change in the statement would mess up our conclusion.
-Does \texttt{arXiv:2112.08792}, \S A.2 have the statement we want?]} Thus, Borel regularization acts as a projection operator on the space of Borel-regularizable functions.\textcolor{orange}{[Veronica: Do you mean that if $\Phi\sim\series{\Phi}$ and $\series{\Phi}$ is Gevrey and Borel summable, then $\Phi=\laplace\circ\borel\series{\Phi}$ (i.e.
-it is Borel regular)?
-P.Ramis proved that if $\Phi$ is Gevrey asymptotic to $\series{\Phi}$, then $\series{\Phi}$ is of Gevrey type.
-In addition, every Gevrey type series $\series{\Phi}$ is the Gevrey asymptotics of a holomorphic function.
-When it is defined, the Borel sum of $\series{\Phi}$ is the natural holomorphic function asymptotic to $\series{\Phi}$.]}
-%\item Borel regularity can help explain why Borel summation is so effective at solving certain kinds of problems, like the ones in Section~\ref{intro:summation}.
-%\item The formal solutions of a problem are typically supposed to generalize the actual solutions, in the sense that they include the asymptotic series of the actual solutions.
-%\item In this case, every Borel regular solution can be found by taking the Borel sum of a formal solution.
-%\item \ldots
-%\end{itemize}
-
+%
 \subsection{Goals and Results}
@@
 We take the opposite approach, showing that certain functions are Borel regular just because of the extra structure provided by the problems they solve.
-
-%%a function $\Phi$ holomorphic in a sectorial neighbourhood $\mathsf{A}_\theta:=\{z\in\C \vert \Re(e^{i\theta}z)\}$ is Borel regular.
-Indeed let $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket$ be the ``Gevrey-asymptotics'' of $\Phi$ as $\Re(e^{i\theta}z)\to \infty$, then its Borel transform $\hat{\phi}\defeq\borel\series{\Phi}$ is a germ of holomorphic function at the origin and it can be analytically continued in a tubular neighbourhood of the ray $e^{i\theta}[0,\infty)$ with at most exponential growth at infinity.
-Hence $\Phi$ is Borel-regularizable.
-In addition, $\series{\phi}$ converges uniformly to a holomorphic function $\phi(\zeta)$ whose Laplace transform coincides with $\Phi(z)$.
-In particular, we learn that being ``Gevrey-asymptotic'' to a formal series is a sufficient condition for Borel regularity.
+%
 \subsection{Solving level~$1$ ODEs}\label{sec:history_ODE}
@@
 We classify solution methods by two features: whether the solutions they produce are analytic functions or formal series, and whether they solve the original equation on the frequency domain or an equivalent equation in the position domain.
-%\textcolor{RoyalBlue}{Since in this paper we focus on buidling a frame of solutions, without dicussing the Stokes phenomenon, we will describe below the main methods to solve irregular singular ODEs stressing the difference between formal and analytic solutions in either the frequency and the position domain.
-A summary is given in the following table}
 \begin{center}
@@
 \end{center}
-
-\subsubsection{The Poincar\'e method and Borel summation}\label{sec:Poincare method}
+%
+\subsubsection{The Poincar\'{e} method and Borel summation}\label{sec:Poincare method}
+%
 An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
@@
 These methods can be applied both within and beyond the world of linear level~1 ODEs.
-
-% \subsubsection{\textcolor{orange}{[M.A.E.T. section]}}
-% Although it is not contructive, the Main Asymptotic Existence Theorem (M.A.E.T.) guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
-The Ramis Index Theorem shows that the formal solutions are 1-Gevrey series---the first step in proving Borel~summability~\cite{ramis_index}.
-\textcolor{orange}{[Revise\ldots]} \textcolor{RoyalBlue}{Furthermore, after checking the solution $\series{\Phi}$ is Borel summable, another argument is needed to show that the Borel sum solve the original equation---a priori, the Borel sum is only Gevrey asymptotic to the solution $\series{\Phi}$.}
+%
 \subsubsection{\'{E}calle's theory of resurgence}
+%
 \'{E}calle's theory of resurgence introduced a new perspective on formal solutions, mostly focused on the analysis of the position domain~\cite{EcalleIII,loday-Remy2011}.
@@
 Malgrange got similar results by working with differential equations, rather than integral equations, on the position domain~\cite{malgrange--fourier}.
-
-%%One can see this by using formal perturbation theory to solve a corresponding equation on the position domain---either an integral equation, as in the work of Loday-Richaud and Remy~\cite{loday-Remy2011}, or a differential equation, as in the work of Malgrange~\cite{malgrange--fourier}.
-\'{E}calle's ``formalism of singularities'' describes how the singularities of the perturbative solution propagate from one order of perturbation to the next.
-This information
-
-%%\'{E}calle's ``formalism of singularities'' can be used to show that Level~1 ODEs are a rich source of resurgent series.
-
-%%A resurgent analysis of a differential equation on the frequency domain begins by using formal perturbation theory to solve a corresponding equation on the position domain---either an integral equation, as in the work of Loday-Richaud and Remy~\cite{loday-Remy2011}, or a differential equation, as in the work of Malgrange~\cite{malgrange--fourier}.
-Ecalle's
-
-%%\textcolor{orange}{[Where does resurgence come in?]}
+%
 \subsubsection{Solving Riemann--Hilbert problems}
+%
 \begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
@@
 More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent developement~\cite{kontsevich2024holomorphic}).
-%%Equivalently, using the Borel regularity result \textcolor{magenta}{[do we really want this theorem, rather than the thimble projection formula?]} Theorem~\ref{thm:maxim}, we can express thimble integrals as Laplace transforms and reconstruct the monodromy of $H^\theta_N(X,f)$ from the associated Stokes constants.
-The Stokes
-%%\color{BlueViolet}
-%%\begin{itemize}
-%%\item Explain how can be seen in terms of homology (cite Pham).
-%%\item the Stokes constants are intersection number of thimbles, computed with Picard Lefschetz formula.
-%%\end{itemize}
-\color{black}
 %
@@
 In both cases, we will call $z$ the {\em frequency coordinate} of $B$.
-%\par\textcolor{RoyalBlue}{The translation structure gives us an isomorphism $z \maps T^*_bB \to \C$ when $b \in B$ is an ordinary point, and an isomorphism $z \maps T^*_bB^{\otimes n} \to \C$ when $b$ is a branch point of cone angle $2\pi n$.}
 \begin{center}
@@
 commute. Here, $\blankbox^n$ represents the $n$th-power map.
-% \subsubsection{Boundary}
-% \textcolor{red}{\textbf{Discuss the visual boundary, citing Lemma~3.1 of Dankwart's thesis \textit{On the large-scale geometry of flat surfaces} for the description of geodesics.}}
-% %
+%
 \subsubsection{The Laplace transform over an ordinary point}\label{laplace:ordinary}
+%
 Pick a translation parameter $\zeta$ on $B$ and an extended angle $\theta \in \R$.
@@
 We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
-%\color{gray}
-%\subsection{The geometry of the Borel transform}
-%\begin{itemize}
-  %\item The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-It's a formal inverse of the $\laplace_{\zeta, 0}$.
-  %\item Formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$, we can extend the Borel transform to trans-series, defining $\borel\textcolor{orange}{_\zeta} \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta \rrbracket$ as the formal inverse of $\laplace_{\zeta, \alpha}$.
-  %\begin{itemize}
-   % \item In other words, when $\borel_\zeta$ acts on formal power series, it formally inverts $\laplace_\zeta$ on the cotangent fiber over $0$.
-\textcolor{magenta}{When it acts on other trans-monomials, it formally inverts $\laplace_\zeta$ on other cotangent fibers.
-[Not quite\ldots figure out how to make this precise.] }
-  %\end{itemize}
-  %\item consequently, $\borel_{\zeta_\alpha}$ acts on trans-monomials $e^{z\alpha}\C\llbracket z^{-1}\rrbracket$ and it formally inverts $\laplace_{\zeta_\alpha}$ on the cotangent fibre over $0$. 
-%\end{itemize}
-%\color{black}
 \subsubsection{Change of translation chart}\label{sec:change-translation}
@@
 \bibliographystyle{utphys}
-\bibliography{airy-resurgence}
+\bibliography{borel-regularity}
 \end{document}

### 2024-07-01 borel-regularity.tex
Tidy up Borel whole derivatives statement

@@
 $\borel_\zeta\big[z^\lambda\, \series{\Phi}\big]=\fracderiv{\lambda}{\zeta}{0}\,\borel_\zeta\series{\Phi}$ for every $\lambda\in(-\infty, 0)$;
-\item\label{res:whole-deriv-borel} \textbf{Whole derivatives} let $k\in\Z_{\ge 0}$ and $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$, then $\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$.\footnote{This property holds more generally for series in $\C\llbracket z^{-1}\rrbracket$, even ones that are not $1$-Gevrey.}
+\item\label{res:whole-deriv-borel} \textbf{Whole derivatives}
+
+$\borel_\zeta\big[\partial_z^{k} \series{\Phi}\big]=(-\zeta)^k\borel_\zeta\series{\Phi}$ for all $k\in\{0, 1, 2, 3, \ldots\}$, under the condition that $\series{\Phi}\in z^{-k-1}\llbracket z^{-1}\rrbracket_1$.\footnote{This property holds for all series in $\C\llbracket z^{-1}\rrbracket$, even ones that are not $1$-Gevrey.}
 \end{enumerate} 

### 2024-07-01 borel-regularity.tex
Drop draft text from Laplace-Borel basics section
Also, correct a typo.

@@
 Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
-%\textcolor{orange}{[Parallel ``algebraic'' formula is the simplest definition, but the geometry is there, and the second formula captures the geometry.]}
-
-%The Borel transform on $T^*B_{\zeta = 0}$ is the $\C$-linear map
-%\begin{align*}
-%\borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}.
-%\end{align*}
-%In general, by linearity,
-%\begin{align*}
-%\borel_\zeta\big[a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \big] = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots.
-%\end{align*}
-% \textcolor{PaleVioletRed}{[I cannot  quite see what this paragraph is doing.]} If a function $\varphi$ belongs to $\singexpalg{0}(\Omega)$, and its Taylor series
-% \[ \series{\varphi} = a_1 + a_2 \zeta + a_3 \frac{\zeta^2}{2!} + a_4 \frac{\zeta^3}{3!} + \ldots \]
-% has an infinite radius of convergence, then the Taylor coefficients decay fast enough for us to take the Laplace transform term by term~\cite[Theorem 5.20]{diverg-resurg-i}:
-% \begin{align*}
-%   \laplace_{\zeta, 0}\varphi&=\laplace_{\zeta,0}\left[\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}\right]\\
-%   &=\sum_{n=0}^\infty a_{n+1}\,\laplace_{\zeta,0}\left[\frac{\zeta^n}{n!}\right]\\
-%   &=\sum_{n=0}^\infty a_{n+1}z^{-n-1}
-% \end{align*}
-% As a result, we can recover the Taylor series $\series{\varphi}$ from the series
-% \[ \series{\Phi} = a_1 z^{-1} + a_2 z^{-2} + a_3 z^{-3} + a_4 z^{-4} + \ldots \]
-% using the Borel transform:
-% \begin{align*}
-% \borel_\zeta \series{\Phi}&=\borel_\zeta\left[\sum_{n=0}^\infty a_{n+1}z^{-n-1}\right]\\
-% &=\sum_{n=0}^\infty a_{n+1}\frac{\zeta^n}{n!}.
-% \end{align*}
-% We took the Borel transform with respect to the coordinate $\zeta$ because $\series{\Phi}$ represents a holomorphic function on the cotangent space $T^*_{\zeta = 0}B$.
 
@@
 It extends countable linearity to a map $\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket  \to \C \llbracket \zeta_\alpha \rrbracket$.
-%\begin{align*}
-%\borel_{\zeta_b} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C %\llbracket \zeta_b \rrbracket \\
-%\sum_{n=0}a_n z^{-n-1} & \mapsto \sum_{n=0}^\infty a_n \frac{\zeta_b^n}{n!},
-%\end{align*}
-%%\begin{align*}
- %%    \borel_{\zeta_b}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_b \rrbracket  \\
-  %%   z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- %%\end{align*}
-%we could again recover ${\varphi}_b$.
-
-%Summarizing, we can describe the geometry of Borel and Laplace transforms by drawing the following diagram
-%\begin{center}
-%\begin{tikzcd}[every arrow/.append style={shift left}]
- %\text{functions on } T^*_{\zeta=0}B \arrow{d}{\borel_{\zeta}} & & \text{functions on } T^*_{\zeta=b}B \arrow{d}{\borel_{\zeta_b}}\arrow[ll,swap,"\mathsf{T}_b^*"] \\ 
- %\text{functions of } \zeta \arrow{u}{\laplace_{\zeta, 0}}\arrow[rr,"\mathsf{T}_b"'] & & \text{functions of } \zeta_b \arrow{u}{\laplace_{\zeta_b, 0}}
-%\end{tikzcd}
-%\end{center}
-%where $\mathsf{T}_b$ denotes the translation map $\mathsf{T}_b(\zeta)=\zeta_b$. \textcolor{orange}{I don't like much the word function and the map $\mathsf{T}_b$, but we could change later.}
-
-%%It's also possible to recover the definition of $\mathcal{B}_{\zeta,\alpha}$ from the properties of $\laplace_{\zeta_\alpha,0}$, as discussed in Section~\ref{transl-borel}.
-
-%%%We then could've recovered the Taylor series of $\varphi$ using the Borel transform on $T^*B_{\zeta = \alpha}$, which is defined as
-%%%\begin{align*}
-%%%\borel_{\zeta_\alpha} \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta_\alpha \rrbracket \\
-%%z^{-n-1} & \mapsto \frac{\zeta_\alpha^n}{n!}.
-%%\end{align*}
-
-%%%working in a different cotangent space $T^*B_{\zeta = \alpha}$, we'd take the Borel transform with respect to $\zeta_\alpha$ instead, as described in Section~\ref{transl-borel}.
-
-%\color{Peru}
-%\textbf{[Draft version]} The Borel transform $\borel\textcolor{orange}{_\zeta}$ turns formal power series in $z^{-1}$---which represent functions defined all non-singular cotangent spaces---into formal power series in $\zeta$.
-More precisely, $\borel_\zeta$ is a $\C$-linear map
-%\begin{align*}
-%\borel\textcolor{orange}{_\zeta} \maps \C \llbracket z^{-1} \rrbracket & \to \C\delta \oplus \C \llbracket \zeta \rrbracket \\
-%1 & \mapsto \delta\vphantom{\frac{1}{1}} \\
-%z^{-n-1} & \mapsto \frac{\zeta^n}{n!}\qquad\text{when } n \ge 0
-%\end{align*}
-%where $\delta$ is a ``convolution unit'', namely $\phi\ast \delta= \delta\ast \phi= \phi$ (see convolution below \textcolor{magenta}{[add convolution]}).
-
-%%It follows that $\borel_\zeta$ is a formal inverse of the $\laplace_{\zeta, 0}$: let $\varphi=\sum_{n=0}^{\infty}a_n \zeta^n$
-%\begin{align*}
- %   \borel_\zeta \laplace_{\zeta}\varphi&=\borel_\zeta \left[\int_{\mathcal{J}_{\zeta,0}}e^{-z\zeta} \varphi d\zeta\right]\\
-  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n \int_{\mathcal{J}_{\zeta,0}} e^{-z\zeta}\zeta^n d\zeta\right]\\
-  %  &=\borel_\zeta\left[\sum_{n=0}^{\infty}a_n z^{-n-1}n! \right]\\
-  %  &=\sum_{n=0}^{\infty}a_n \frac{\zeta^n}{n!}
-%\end{align*}
-%where in the second step we formally interchange the integral and the sum. 
-%\color{black}
+%
 \subsubsection{Action on trans-monomials}\label{sec:action_transseries}
-%Recall from the discussion in Section~\ref{sec:history_ODE}, that formal solutions of irregular singualr ODEs are in form of trans-monomials. 
-%%
-%%{\em Trans-series} are formal objects that greatly generalize formal power series.
-Their full definition is quite involved, especially when complex exponents are allowed~\cite{EcalleIII,van-der-hoeven2001complex,costin_transseries,costin_summability}.
-We will only see examples of the simple form
-%%\[  e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha, \]
-%%where $\alpha$ is a complex number, each $\sigma_\alpha$ is a real number, and each $\series{\varphi}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
-This is an example of a {\em trans-monomial}.
-%%
-%%Trans-monomials of this form play a crucial role in the theory of ODEs with irregular singularities. Linear combinations of such trans-monomials encode the Stokes phenomenon:
-%%
-%%In particular, they exhibit a formal analogue of the Stokes phenomenon: their asymptotics can change sharply from one direction to the next.
-Trans-monomials $e^{-\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha$ can be ordered by $\Re(e^{i\theta} \alpha)$ for any direction $\theta$.
-When a trans-monomial \textcolor{orange}{[of this form]} converges, its sum becomes dominated by the lowest term in this ordering as $\Re(e^{-i\theta} z)$ grows.
-%%\[\sum_{\alpha\in A}  e^{\alpha z} z^{\sigma_\alpha} \series{\varphi}_\alpha \]
-%%$A$ is the set of roots of $P$.
-
+%
 We can extend the definition of the Borel transform to these trans-monomials by recognizing that $\laplace_{\zeta, \alpha}$ sends ordinary monomials to trans-monomials, and then taking advantage of the relationship between $\laplace_{\zeta, \alpha}$ and $\laplace_{\zeta_\alpha, 0}$ given by identity~\eqref{change-chart}.
@@
 \end{align*}
-%%%and taking the inverse of $\laplace_{\zeta_\alpha,0}$ we find
-%Indeed it is possible by formalizing the change of variable identity that relates $\laplace_{\zeta, \alpha}$ to $\laplace_{\zeta_\alpha, 0}$ (see Section \ref{translation} identity \eqref{change-chart}).
-%
-%We extend the Borel transform to transseries, defining \[\borel_\zeta \maps e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \to \C\llbracket \zeta_\alpha \rrbracket\] as the formal inverse of $\laplace_{\zeta, \alpha}$.
-To be more precise, we define the action on trans-monomial so that the diagram
-%%\begin{center}
-%%\begin{tikzcd}
-%%& e^{-\alpha z} \C\llbracket z^{-1} \rrbracket \arrow[rd, "\borel_\zeta"] \\
-%%\C\llbracket \zeta \rrbracket \arrow[ru, "\laplace_{\zeta, \alpha}"] \arrow[rr, "\text{change of variable}"'] & & \C\llbracket \zeta_\alpha \rrbracket
-%%\end{tikzcd}
-%%\end{center}
-%\begin{lemma}
-%%%\[\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big]=\frac{\zeta_\alpha^n}{n!}.\]
 In other words, the diagram 
@@
 Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
-%\end{lemma}
 
@@
 \end{proof}
- %Therefore, we learn that $\borel_{\zeta_\alpha}$ is a $\C$-linear map from formal power series in the frequency variable $z$ to formal power series in the position variable $\zeta_\alpha$, it is defined by
- %\begin{align*}
-    % \borel_{\zeta_\alpha}\colon z^{-1}\C\llbracket z^{-1}\rrbracket &\to \C\llbracket \zeta_\alpha \rrbracket  \\
-    % z^{-n-1}& \mapsto \frac{\zeta_\alpha^n}{n!} \qquad \text{ when } n\geq 0
- %\end{align*}
-%\textcolor{orange}{[Move to beginning?]} Furthermore, we learn that the action of $\borel_{\zeta_\alpha}$ extends to trans-monomials: $\borel_{\zeta_\alpha}\colon e^{z\alpha}\C\llbracket z^{-1}\rrbracket\to \C\llbracket \zeta  \rrbracket$ as the formal inverse of $\laplace_{\zeta_\alpha,-\alpha}$.
+%
 \subsubsection{Action on translations in the frequency domain}
+%
 Translations in the frequency domain do not play any role in our work, but they do appear in other contexts---for example, in Laplace transform methods for difference equations.
@@
 &=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
-%&=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{j-1}}{(j-1)!}\ast\frac{\zeta^{n-j-1}}{(n-j-1)!}\\
-%&= a_0b_0\delta + \sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}   \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)
 \end{align*}
 \end{proof}
-% Notice that if $z$ is the coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n-1}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n-1}$, then the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is
-%  \[\series{\psi}\ast\series{\phi}=\borel_\zeta(\series{\Psi}\series{\Phi}).\]
-%  Hence, if $z$ denotes a coordinate on $T^*_{\zeta=0}B$, the Borel transform $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, and $\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
-% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
-% \end{definition}
 \begin{todo}[Shorten to a reminder that $z$ is an almost-global coordinate on cotangent spaces, so this also works in other fibers.]\end{todo} Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
@@
 
-% Equivalntly, $1$-Gevrey series are caracterized as follows:
-% \begin{lemma}
-% Let $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket$.
-Then, $\series{\Phi}\in\C \llbracket z^{-1} \rrbracket_1$ is $1$-Gevrey if and only if $\borel_\zeta\series{\Phi}\in\C\lbrace\zeta\rbrace$ is a germ of holomorphic functions.
-% \end{lemma}
-% \begin{proof}
-%     If $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, and $\series{\Phi}(z)=\sum_{n=0}^\infty a_n z^{-n-1}$, then by definition, there exixst a constant $A>0$ such that $|a_n|\lesssim A^n n!$ for all $n\ge 0$.
-Therefore,
-%     \[\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\]
-%     which has finite radius of convergence $A^{-1}$. 
-%     Conversely, if $\borel_\zeta\series{\Phi}$ is a germ of analytic functions, i.e.
-$\borel_\zeta\series{\Phi}=\sum_{n=0}^\infty a_n \zeta^n$ has finte radius of convergence $1/A$, for some constant $A>0$, then the formal Laplace transform of $\borel_\zeta\series{\Phi}$ gives
-%     \[\sum_{n=0}^\infty a_n\, n!\, z^{-n-1}\]
-%     and $|a_n n!|\le |a_n| n!\lesssim A^n n!$. 
-% \end{proof}
-The space of $1$-Gevrey series is close under the Cauchy product. In addition, 
+The space of $1$-Gevrey series is closed under the Cauchy product. In addition, 
 \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
 extends to an algebra homomorphism, where $\C\{\zeta\}$ is endowed with the convolution product defined in Definition~\ref{def:convolution_formal}.
-% \begin{definition}{(see \cite[Definition 5.12]{diverg-resurg-i})}
-%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=0$.
-Then, the convolution product of $\series{\phi}:=\borel_\zeta\series{\Phi}$ and $\series{\psi}:=\borel_\zeta\series{\Psi}$ is defined as
-% \[\borel_\zeta(\series{\Psi}\series{\Phi})=:\series{\psi}\ast\series{\phi}.\]
-% Furthermore, since $\series{\phi},\series{\psi}\in\C\{\zeta\}$ are convergent formal series, it follows that the sum of $\series{\psi}\ast\series{\phi}$ is the convolution $\hat{\psi}\ast\hat{\phi}$, where $\hat{\phi},\hat{\psi}$ are the sums of $\series{\phi}, \series{\psi}$ respectively.
-% \end{definition}
-% The definition of convolution product for germs of holomorphic functions at $\zeta=0$, can be generalized to germs of analytic functions at $\zeta=\alpha$, using the Borel transform $\borel_{\zeta_\alpha}$ on $1$-Gevrey series on the fiber over $\zeta=\alpha$.
-% \begin{definition}
-%     Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$, and $z$ be a coordinate on the cotangent fiber over $\zeta=\alpha$.
-Then, the convolution product of $\series{\phi}:=\borel_{\zeta_\alpha}\series{\Phi}$ and $\series{\psi}:=\borel_{\zeta_\alpha}\series{\Psi}$ is defined as
-% \[\borel_{\zeta_\alpha}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}.\]
-% Furthermore, the sum of $\series{\psi}\ast_{\zeta_\alpha,0}\series{\phi}$ is the convolution $\hat{\psi}\ast_{\zeta_\alpha,0}\hat{\phi}$. 
-% \end{definition}
 In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series.
 Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ edowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
-% \begin{prop}
-%     Let $z$ be a coordinate on $T^*_{\zeta=\alpha}B$.
-The Borel transform $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket_1$ to $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$.
-% \end{prop}
 \begin{verify}
@@
 \end{verify}
-%
-
-  %It's not accidentely that we use the same symbol $*$ that denotes the convolution product to denote the product of two convergent series; indeed, as proved in , %the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
-%\[
- %   \hat{\psi}\ast\hat{\phi}=\int_0^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta'),
-%\]
-%and we refer to \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i} for a proof. 
-%\textcolor{orange}{check Lemma 5.14}{where $\hat{\phi}$ and $\hat{\psi}$ are the sum of $\series{\phi}$ and $\series{\psi}$, respectively. }
-%\begin{prop}
- %   Let $\tau\in\mathbb{R}\setminus\Z_{<0}$, then $\borel_\zeta$ is a $\C$-algebra homomorphism from $1$-Gevrey formal power series $z^{-\tau} \C\llbracket z^{-1} \rrbracket$ to the germs of holomorphic functions $\zeta^{\tau-1} \C\{ z^{-1} \}$.
-%\end{prop}
-%\begin{proof}
- %   Let $\series{\Phi}(z)=\sum_{n\geq 0}a_nz^{-n}\in\C \llbracket z^{-1} \rrbracket_1$ %with $|a_n|\leq A^n n!$ and $A>0$ then  
-%\begin{align*}
-%\borel_\zeta (z^{-\tau}\series{\Phi})&=\frac{\zeta^{\tau-1}}{\Gamma(\tau)}\ast\left(a_0\delta+\sum_{n\geq 0}a_{n+1}\frac{\zeta^n}{n!}\right)\\
-%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\int_0^\zeta\sum_{n\geq 0}\frac{a_{n+1}}{n!}(\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
-%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\frac{1}{\Gamma(\tau)}\sum_{n\geq 0} \frac{a_{n+1}}{n!} \int_0^\zeta (\zeta-\zeta')^{\tau-1}(\zeta')^n\, d\zeta'\\
-%&=a_0\frac{\zeta^{\tau-1}}{\Gamma(\tau)}+\sum_{n\geq 0}a_{n+1} \frac{\zeta^{n+\tau}}{\Gamma(1+n+\tau)}
-%\end{align*}  
-%where in the third step we use that the Borel transform of $\series{\Phi}$ is convergent in a neighbourhood of $\zeta=0$.
-and \[\left|\frac{a_{n+1}}{\Gamma(1+n+\tau)}\right|\leq A^{n+1}\frac{\Gamma(n+2)}{|\Gamma(n+1+\tau)|} \]
-%which grows as $n(n+1)^{-\tau} A^{n+1}$.
-%\begin{verify}
- %   we use $\Gamma(n+1+\tau)\sim \Gamma(n+1) (n+1)^\tau$ as $n\to\infty$. 
-%\end{verify}
-%\end{proof}
 %

### 2024-07-01 borel-regularity.tex
Drop unused package
Hide `verify`, `unstable`, `todo`, `old` environments
Correct DLMF citation
Hide draft text and turn off revision highlighting
Change organization from list to paragraphs

@@
 \usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} %% hat tip https://tex.stackexchange.com/a/247819
-%%\usepackage{bm} %% for putting series names in bold
 \usepackage{graphicx}
@@
 
-% more drafting environments
+% hideable draft text
+\newif\ifshowdraft
+\showdraftfalse
+\ifshowdraft
 \newenvironment{draft}{\color{SlateBlue}}{\color{black}}
+\else
+\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
+\fi
+
+% highlightable revisions
+\newif\ifhighlightrevs
+\highlightrevsfalse
+\ifhighlightrevs
 \newenvironment{revised}{\color{DarkBlue}}{\color{black}}
+\else
+\newenvironment{revised}{}{}
+\fi
 
@@
 \subsection{Organization of the paper}\label{sec:org}
+%
 \begin{revised}
-%
-\begin{paragraph}{Section~\ref{sec:historical-context}}
-We contextualize our work by reviewing some classical results related to Borel regularity.
-These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.\end{paragraph}
-%
-\begin{paragraph}{Section~\ref{sec:Laplace-Borel-general}}
-We introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results.
+In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity.
+These results come from the literature on asymptotics, ODEs, and integrals over Lefschetz thimbles.
+
+In section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results.
 To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.
-\end{paragraph}
-%
-\begin{paragraph}{Section~\ref{sec:proof_main_results}}
-We restate and prove our main results.
-\end{paragraph}
-%
-\begin{paragraph}{Section~\ref{sec:examples}}
-We illustrate our results by working through detailed examples of how Borel regular functions arise, both as $1$-dimensional thimble integrals and as solutions of level~$1$ ODEs.
-\end{paragraph}
-%
-\begin{paragraph}{Appendix~\ref{airy-appendix}}
-Reprising our analysis of the Airy--Lucas equations in Section~\ref{sec:examples}, we focus on the Airy equation as a concrete special case.
+
+In Section~\ref{sec:proof_main_results}, we restate and prove our main results.
+In Section~\ref{sec:examples}, we illustrate our results by working through detailed examples of how Borel regular functions arise, both as $1$-dimensional thimble integrals and as solutions of level~$1$ ODEs.
+
+In Appendix~\ref{airy-appendix}, reprising our analysis of the Airy--Lucas equations in Section~\ref{sec:examples}, we focus on the Airy equation as a concrete special case.
 We then explain how our treatment lines up with other discussions of the Airy equation in the literature on Borel summation.
-\end{paragraph}
-%
-\begin{paragraph}{Appendix~\ref{shifting}}
-We prove a fact about the relationship between integral and differential equations which is used in some of our examples.
-\end{paragraph}
-%
+
+In Appendix~\ref{shifting}, we prove a fact about the relationship between integral and differential equations which is used in some of our examples.
 \end{revised}
+%
 \begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.

### 2024-07-29 borel-regularity.tex
Use explicit moving point instead of dot in some integrals

@@
 In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
-For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\begin{todo}[``the mathematical physics of rainbows and glories'']\end{todo}.
+For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\cite{rainbows+glories}.
 \begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer].
@@
 The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
-
-We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough.
+\begin{todo}[Explain more why we write in terms of the distance function $\Delta$]\end{todo}
+
+To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$.
 Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
-\begin{todo}[\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?]\end{todo}
+\begin{todo}[\textbf{A} Put this definition into its own block]\end{todo}
 \begin{todo}\par
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
+\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
 Choose any $\Lambda' > \Lambda$.
@@
 \begin{lemma}\label{lem:laplace-bridge}
-Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less\begin{todo}, as illustrated on the position-domain side of Figure~\ref{fig:sectorial_domain-pos-fre} [is it really that helpful to have a picture of this?]\end{todo}.
+Let $\Omega$ be an open sector with $\zeta = 0$ at its tip, and an opening angle of $\pi$ or less.
 Take some $\rho \in (-1,\infty)$.
@@
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
-\begin{todo}[\textbf{A} define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
+of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.\begin{todo} Cite the definition rather than the Section\end{todo}
 \end{theorem}
@@
 
-Since the series $\series{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \C\{\zeta\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
-Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
-We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+\begin{todo}[Confirm that we should have $\zeta_\alpha$ rather than $\zeta$ here]\end{todo} Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
+Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
+We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match.
@@
 \begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right).\end{equation}
-\begin{todo}[This argument works for any function that vanishes at $\alpha$, so maybe we should instead prove it generally in the section on fractional calculus.]\end{todo}
 \end{remark}
@@
 \delta_{\zeta,\alpha}^{(-\ell)}:=\begin{cases}
-\displaystyle\frac{\zeta_\alpha^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta_\alpha)+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\in\mathbb{N}^*\\
+\displaystyle\frac{\zeta_\alpha^{\ell-1}}{-2\pi i(\ell-1)!}\log(\zeta_\alpha)+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell \in \Z_{> 0}\\
 & \\
-\displaystyle\frac{(-\zeta_\alpha)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell\notin \mathbb{N}^* \,.
+\displaystyle\frac{(-\zeta_\alpha)^{\ell-1}}{2\pi i\, \Gamma(-\ell)}+ \mathcal{O}_{\zeta = \alpha} & \text{ if } \ell \notin \Z_{> 0} \,.
 \end{cases}
@@
 \end{align*}
-where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively. \begin{todo}[Draw the thimble in the $u$ plane?]\end{todo}
+where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
 

### 2024-07-29 sima/reg-sing-volterra_sima.tex
Commit before dropping old text
Use explicit moving point instead of dot in some integrals

@@
 \newenvironment{brainstorm}{\color{violet}\begin{itemize}}{\end{itemize}\color{black}}
+\newenvironment{todo}{\color{violet}}{\color{black}}
 
@@
 \ifhighlightrevs
-\newenvironment{rev}{\color{revred}}{\color{black}}
-\newcommand{\revtext}[1]{\textcolor{revred}{#1}}
+\newenvironment{rev}{\color{ietocean}}{\color{black}}
+\newcommand{\revtext}[1]{\textcolor{ietocean}{#1}}
+\newenvironment{revtwo}{\color{revred}}{\color{black}}
+\newcommand{\revtwotext}[1]{\textcolor{revred}{#1}}
 \else
@@
 \newcommand{\revtext}[1]{#1}
+\newenvironment{revtwo}{}{}
+\newcommand{\revtwotext}[1]{#1}
+\fi
+
+% notation change highlighting
+\newif\ifhighlightnewnotation
+\highlightnewnotationtrue
+\ifhighlightnewnotation
+\newenvironment{newnot}{\color{orange}}{\color{black}}
+\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
+\newenvironment{oldnot}{\color{cyan}}{\color{black}}
+\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
+\else
+\newenvironment{newnot}{}{}
+\newenvironment{oldnot}{}{}
+\newcommand{\newnottext}[1]{#1}
 \fi
@@
 In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+It is the integral transform defined by the equation
+\[ \laplace \varphi := \int_{\Gamma_\zeta} e^{-z\zeta} \varphi\;d\zeta\,, \]
+where $\Gamma_\zeta$ is the ray $\zeta \in (0, \infty)$.
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 \frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
+\laplace \psi\;\laplace\varphi & = \laplace(\psi * \varphi) \\
+z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi\,,
 \end{align*}
@@
 \begin{equation}\label{eqn:intro-use-dict}
-\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0.
+\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0\,.
 \end{equation}
@@
 To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
-Equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well.
+This version of the Laplace transform is defined in Section~\ref{sec:definition_Laplace}.
+A function of the form $\Phi = \laplace_{\zeta, \alpha} \varphi$ satisfies equation~\eqref{eqn:intro-level-1} if and only if $\varphi$ satisfies the integral equation
+%%use the Laplace transform based at $\zeta = \alpha$, equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well:
+\[ \big[ P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}) \big] \varphi = 0\,, \]
+where $\partial^{-1}_{\zeta, \alpha}$ is integration with base point $\zeta = \alpha$:
+\[ [\partial^{-1}_{\zeta, \alpha} \varphi](a) := \int_{\zeta = \alpha}^a \varphi\;d\zeta\,. \]
 We seek a solution $\psi_\alpha$ which
@@
 In the integral
-\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta, \]
+\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta\,, \]
 notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
+
+\begin{revtwo}
+Sometimes, in expressions like
+\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\,d\zeta(a')\,, \]
+it is useful to give a name $a'$ to the point moving along the integration path.
+In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.
+\end{revtwo}
 \subsubsection{Plugging into formal expressions}
@@
 defined by an integral
+\begin{oldnot}
 \[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
+\end{oldnot}
+\begin{newnot}\begin{todo}[Possibility: use moving point to write kernel with both arguments]\end{todo}
+\[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
+\end{newnot}
+\begin{newnot}\begin{todo}[Possibility: ``integration along $\zeta''$ with $\zeta'$ fixed]\end{todo}
+\[ \genvolterra\,\varphi = \int_{0}^{\zeta} \genker\,\varphi''\;d\zeta''\Big|_{\zeta' = \zeta} \]
+\end{newnot}
 in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
@@
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-for some $p, q \in \mathcal{H}(\Omega)$.\end{rev}
+for some $p, q \in \mathcal{H}(\Omega)$. \end{rev}\begin{revtwo}Explicitly,
+\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
+\end{revtwo}
 
@@
 
-We now perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
-\revtext{The perturbation $\softpart$ will be non-separable,}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
-To get the smoothing effect, we will require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
+We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
+\begin{oldnot}
+\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
+\end{oldnot}
+\begin{newnot}
+\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
+\end{newnot}
+will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
+To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
 This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
@@
 \begin{theorem}\label{thm:basic_volterra}
-Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
+\begin{revtwo}Suppose the operator%%$\hardpart$
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
+\end{revtwo}
+satisfies {\em Condition \eqref{cond:sing}}. Then the equation
 \begin{equation}\label{eq:hardpart}
@@
 \revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
+\begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces.
+Every function $f \in \singexpalg{\sigma}(\domain)$ has a finite norm
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f| \]
+for some $\Lambda \in \R$.
+\end{revtwo}
 \begin{theorem}\label{thm:proto-growth}
-Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
+\begin{revtwo}Suppose the operator%%$\hardpart$
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
+\end{revtwo}
+satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
 
@@
 \begin{theorem}\label{thm:general_volterra}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
+\begin{oldnot}
+\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
+\end{oldnot}
+\begin{newnot}
+\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
+\end{newnot}
+\end{revtwo}
+satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
 \[ f = \volterra f \]
@@
 For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
+\begin{oldnot}
 \begin{align*}
@@
 \end{align*}
-By Condition~\eqref{cond:eps-lambda},
-\begin{align*}
-\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
+\end{oldnot}
+\begin{newnot}
+\begin{align*}
+|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
+&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
+&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|
+\end{align*}
+\end{newnot}
+By Condition~\eqref{cond:eps-lambda}, \begin{todo}[notation updated]\end{todo}
+\begin{newnot}
+\begin{align*}
+\int_{\zeta=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
 &\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
@@
 \end{align*}
+\end{newnot}
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \revtext{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+\begin{oldnot}
 \[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
 \]
+\end{oldnot}
+\begin{newnot}
+\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
+\]
+\end{newnot}
 \revtext{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\begin{oldnot}
 \[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
+\end{oldnot}
+\begin{newnot}
+\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
+\end{newnot}
 we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
@@
 The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
+\begin{oldnot}
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)\,\varphi\;d\zeta| \]
+\end{oldnot}
+\begin{newnot}
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
+\end{newnot}
 for any choice of integration path.
 The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
-& = \|\varphi\|_{\rho-1, \Lambda}  \int_0^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
-\end{align*}
+\begin{oldnot}
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
+& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
+\end{align*}
+\end{oldnot}
+\begin{newnot}
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
+& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
+\end{align*}
+\end{newnot}
 What we do next depends on whether $a$ is in $\near$ or $\far$.
@@
 |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le
-\|\varphi\|_{\rho-1, \Lambda}  \int_0^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
-& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_0^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
+\|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
+& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
 \end{align*}
@@
 \revtext{for all $a \in \far$ and $a' \in \Omega$.} \revtext{This bound implies that}
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \subsection{The Laplace transform}
-\subsubsection{Definition}
+\subsubsection{Definition}\label{sec:definition_Laplace}
 Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \revtext{$\zeta=\alpha$.
@@
 To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
+\begin{oldnot}
 \[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta, \]
+\end{oldnot}
+\begin{newnot}
+\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a'), \]
+\end{newnot}
 where
@@
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]}
+\begin{oldnot}
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]
+\end{oldnot}
+\begin{newnot}
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
+\end{newnot}}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
-\begin{equation}\label{eqn:divided}
+\begin{oldnot}
+\begin{equation}%%\label{eqn:divided}
 \varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
 \end{equation}
+\end{oldnot}
+\begin{newnot}
+\begin{equation}\label{eqn:divided}
+\varphi(a) = -\int_{\zeta(a')=\alpha}^a \frac{q(a')}{p(a)} \, \varphi(a') \; d\zeta(a') - \int_{\zeta(a')=\alpha}^a \frac{k_R(a, a')}{p(a)} \, \varphi(a') \, d\zeta(a').
+\end{equation}
+\end{newnot}
 Let $\hardpart^\alpha$ be the Volterra operator with kernel

### 2024-08-05 sima/reg-sing-volterra_sima.tex
Match new notation from "Regular singular Volterra"

@@
 
+\begin{revtwo}
 In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
@@
 where $\Gamma_\zeta$ is the ray $\zeta \in (0, \infty)$.     
+\end{revtwo}
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
+\begin{revtwo}
+Explicitly,
+\[ \laplace_{\zeta,\alpha} \varphi := \int_{\Gamma_{\zeta,\alpha}} e^{-z\zeta} \varphi\;d\zeta\,, \]
+where $\Gamma_{\zeta,\alpha}$ is the ray $\zeta \in (\alpha, \infty)$.    
 This version of the Laplace transform is defined in Section~\ref{sec:definition_Laplace}.
@@
 These conditions ensure that $\psi_\alpha$ has a well-defined Laplace transform, and the first condition gives $\laplace_{\zeta, \alpha} \psi_\alpha$ the desired asymptotics.
+\end{revtwo}
 

### 2024-08-05 sima/reg-sing-volterra_sima.tex
Settle on explicit moving point notation
Drop the old-notation versions of the equations.

@@
 defined by an integral
-\begin{oldnot}
-\[ [\genvolterra\,\varphi](a) = \int_{\zeta = 0}^a \genker(a, \cdot)\,\varphi\;d\zeta \]
-\end{oldnot}
-\begin{newnot}\begin{todo}[Possibility: use moving point to write kernel with both arguments]\end{todo}
+\begin{revtwo}
 \[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
-\end{newnot}
-\begin{newnot}\begin{todo}[Possibility: ``integration along $\zeta''$ with $\zeta'$ fixed]\end{todo}
-\[ \genvolterra\,\varphi = \int_{0}^{\zeta} \genker\,\varphi''\;d\zeta''\Big|_{\zeta' = \zeta} \]
-\end{newnot}
+\end{revtwo}
 in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
@@
 We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
-\begin{oldnot}
-\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
-\end{oldnot}
-\begin{newnot}
 \[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
-\end{newnot}
 will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
@@
 \begin{revtwo}Suppose the operator%%$\hardpart$
-\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
 \end{revtwo}
@@
 \begin{theorem}\label{thm:proto-growth}
-\begin{revtwo}Suppose the operator%%$\hardpart$
-\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta \]
+\begin{revtwo}Suppose the operator
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
 \end{revtwo}
@@
 Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
-\begin{oldnot}
-\[ [\softpart\,\varphi](a) := \int_{\zeta = 0}^a \softker(a, \cdot)\,\varphi\;d\zeta \]
-\end{oldnot}
-\begin{newnot}
 \[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
-\end{newnot}
 \end{revtwo}
@@
 For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
-\begin{oldnot}
-\begin{align*}
-|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
-\end{align*}
-\end{oldnot}
-\begin{newnot}
-\begin{align*}
-|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|
-\end{align*}
-\end{newnot}
-By Condition~\eqref{cond:eps-lambda}, \begin{todo}[notation updated]\end{todo}
-\begin{newnot}
-\begin{align*}
-\int_{\zeta=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
-\end{align*}
-\end{newnot}
+\begin{revtwo}
+\begin{align*}
+& |\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert \\
+& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
+& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|\,.
+\end{align*}
+\end{revtwo}
+By Condition~\eqref{cond:eps-lambda},
+\begin{revtwo}
+\begin{align*}
+& \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \\
+& \qquad \lesssim \int_{\zeta(a')=0}^a \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} |\zeta(a')|^{\sigma}\, e^{\Lambda|\zeta(a')|}\;|d\zeta(a')|\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
+\end{align*}
+\end{revtwo}
 The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \revtext{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
-\begin{oldnot}
-\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
+\begin{revtwo}
+\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,.
 \]
-\end{oldnot}
-\begin{newnot}
-\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
-\]
-\end{newnot}
+\end{revtwo}
 \revtext{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
-\begin{oldnot}
-\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
-\end{oldnot}
-\begin{newnot}
-\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
-\end{newnot}
+\begin{revtwo}
+\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,, \]
+\end{revtwo}
 we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
@@
 The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
-\begin{oldnot}
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)\,\varphi\;d\zeta| \]
-\end{oldnot}
-\begin{newnot}
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
-\end{newnot}
+\begin{revtwo}
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
+\end{revtwo}
 for any choice of integration path.
 The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
-\begin{oldnot}
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta = 0}^a |k(a,\cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
-& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
-\end{align*}
-\end{oldnot}
-\begin{newnot}
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
-& = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
-\end{align*}
-\end{newnot}
+\begin{revtwo}
+\begin{align*}
+&|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \\
+& \qquad \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
+& \qquad = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
+\end{align*}
+\end{revtwo}
 What we do next depends on whether $a$ is in $\near$ or $\far$.
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le
 \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
 & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\;dt \\
@@
 \revtext{for all $a \in \far$ and $a' \in \Omega$.} \revtext{This bound implies that}
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
@@
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
 & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.
@@
 \revtext{Set $\Lambda > \lambda$, so} the exponential factor shrinks as $|\zeta(a)|$ grows. \revtext{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
 over all $a \in \far$.
@@
 To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
-\begin{oldnot}
-\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta, \]
-\end{oldnot}
-\begin{newnot}
+\begin{revtwo}
 \[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a'), \]
-\end{newnot}
+\end{revtwo}
 where
@@
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\begin{oldnot}
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0. \]
-\end{oldnot}
-\begin{newnot}
+\begin{revtwo}
 \[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
-\end{newnot}}
+\end{revtwo}}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
-\begin{oldnot}
-\begin{equation}%%\label{eqn:divided}
-\varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
-\end{equation}
-\end{oldnot}
-\begin{newnot}
+\begin{revtwo}
 \begin{equation}\label{eqn:divided}
@@
 \end{equation}
-\end{newnot}
+\end{revtwo}
 Let $\hardpart^\alpha$ be the Volterra operator with kernel

### 2024-08-05 sima/reg-sing-volterra_sima.tex
Remove round-1 revision highlighting

@@
 \ifhighlightrevs
-\newenvironment{rev}{\color{ietocean}}{\color{black}}
-\newcommand{\revtext}[1]{\textcolor{ietocean}{#1}}
 \newenvironment{revtwo}{\color{revred}}{\color{black}}
@@
 \else
-\newenvironment{rev}{}{}
-\newcommand{\revtext}[1]{#1}
 \newenvironment{revtwo}{}{}
@@
 \subsection{Motivation}\label{sec:motivation}
-\begin{rev}An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
 These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
@@
 In~\cite{borel_reg}, we show that these solutions match the ones obtained through resummation.
-Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.\end{rev}
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.
 
@@
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-\begin{rev}For instance, in Section~\ref{sec:example}, we consider equations of the form
+For instance, in Section~\ref{sec:example}, we consider equations of the form
 \begin{equation}\label{eqn:intro-level-1}
@@
 The correspondence between operators on the position and frequency domains will lead to expressions of this kind.
-In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.\end{rev}
+In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.
 \subsection{Notation}
 \subsubsection{Uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write \revtext{$|\varphi| \lesssim \omega$} to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
@@
 For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
-\begin{rev}\subsubsection{Boundary points}
+\subsubsection{Boundary points}
 We will say that a subset of a topological space {\em touches} the points in its closure.
@@
 If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$.
-This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.\end{rev}
+This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
 \subsection{Setting}\label{setting}
@@
 \end{center}
-\begin{rev}\subsubsection{The prototype operator}\label{setting:basic}
+\subsubsection{The prototype operator}\label{setting:basic}
 The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.
@@
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-for some $p, q \in \mathcal{H}(\Omega)$. \end{rev}\begin{revtwo}Explicitly,
+for some $p, q \in \mathcal{H}(\Omega)$. \begin{revtwo}Explicitly,
 \[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
@@
 \end{conditions}
-\revtext{This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.} As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
+This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.
+As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
 \begin{verify}
@@
 We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
-We will also put an exponential bound \revtext{on the growth of $\softker$ away from the diagonal}, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+We will also put an exponential bound on the growth of $\softker$ away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
 Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} \revtext{There is a constant $\gamma > 0$ for which}
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} There is a constant $\gamma > 0$ for which
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{equation}
-Changing the base point $b \in \domain$ \revtext{only} multiplies $f_0$ by a non-zero constant.
+Changing the base point $b \in \domain$ only multiplies $f_0$ by a non-zero constant.
 \end{theorem}
@@
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-\revtext{When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.} The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
+When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.
+The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
 \begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces.
@@
 
-\revtext{The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.} We might therefore \revtext{expect a solution} that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.
+We might therefore expect a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
@@
 \end{theorem}
-\begin{rev}\begin{corollary}\label{cor:expand_uniq}
+\begin{corollary}\label{cor:expand_uniq}
 Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
-\end{corollary}\end{rev}
+\end{corollary}
 This result will follow from a more general result about inhomogeneous equations.
@@
 
-We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting \revtext{the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$} as an inhomogeneous equation in a more regular space.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ as an inhomogeneous equation in a more regular space.
 To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
@@
 Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
-\revtext{Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
-This} is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
+Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
+This is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
 
 The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-\begin{rev}We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
+We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
 \begin{definition}\label{def:unif-exp}
@@
 \end{proof}
-\end{rev}
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
@@
 \end{proof}
-\begin{rev}The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
+The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
 The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace.
@@
 equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
-\end{definition}\end{rev}
+\end{definition}
 \begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
@@
 \end{proposition}
-\begin{rev}\begin{proof}
+\begin{proof}
 For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
@@
 The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
-\end{proof}\end{rev}
+\end{proof}
 \section{Solving holomorphic Volterra equations}\label{sec:proof_main_results}
 \subsection{Overview}
-\begin{rev}In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
 
@@
 We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
-In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.\end{rev}
-
-\revtext{We conclude that} $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, \revtext{we show} in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we \revtext{show} in Section~\ref{sec:existence and uniqueness}.
+In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
+
+We conclude that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, we show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we show in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
@@
 \[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
-Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ \revtext{simplifies} the calculation of $\hardpart \solproto$. For each $a \in \domain$,
+Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ simplifies the calculation of $\hardpart \solproto$. For each $a \in \domain$,
 \begin{align*}
@@
 \end{align*}
-\revtext{To prove that $\hardpart \solproto = \solproto$, we must now} show that $\lim_{\zeta \to 0} \chi = 0$.
-
-By Condition~\eqref{cond:sing}, \revtext{there exist} a radius $\delta>0$ and a constant $C$ such that
+To prove that $\hardpart \solproto = \solproto$, we must now show that $\lim_{\zeta \to 0} \chi = 0$.
+
+By Condition~\eqref{cond:sing}, there exist a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
@@
 \end{equation}
-whenever $|\zeta| < \delta$. \revtext{To use this bound, we rewrite the integral in the definition of $\chi$:}
+whenever $|\zeta| < \delta$. To use this bound, we rewrite the integral in the definition of $\chi$:
 \begin{align*}
@@
 \end{align*}
-Exponentiating both sides \revtext{shows that}
+Exponentiating both sides shows that
 \[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
@@
 
-\revtext{Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$} for which
+Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$ for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
-whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, \revtext{we deduce} that
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we deduce that
 \begin{align*}
@@
 
-By Proposition~\ref{prop:asymptotic at zero}, \revtext{there is} a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
-No matter which value of $\lambda_0$ we pick, \revtext{$e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so} $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+By Proposition~\ref{prop:asymptotic at zero}, there is a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, $e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
 
@@
 \end{align*}
-over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. \revtext{The last bound means that for some $c_\Delta > 0$,}
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. The last bound means that for some $c_\Delta > 0$,
 \[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
 whenever $|\zeta(a)| \ge \delta$.
-Applying this bound along the diagonal in $\domain^2$, we \revtext{conclude} that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we conclude that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
 On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we \revtext{deduce} that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we deduce that
 \begin{align*}
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then \revtext{there is some $M\in\C$} for which,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then there is some $M\in\C$ for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
-at $\zeta = 0$. \revtext{As in} the proof of Theorem~\ref{thm:basic_volterra}, we \revtext{compute}
+at $\zeta = 0$. As in the proof of Theorem~\ref{thm:basic_volterra}, we compute
 \begin{align*}
@@
 \end{align*}
-\revtext{Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.}
-
-\revtext{Condition \eqref{cond:reg-p} implies that}
+Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.
+
+Condition \eqref{cond:reg-p} implies that
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, \revtext{consider} the exponential factor. By Condition~\eqref{cond:sing}, \revtext{there exist} a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, consider the exponential factor. By Condition~\eqref{cond:sing}, there exists a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 
-\revtext{Together, the arguments above show that}
+Together, the arguments above show that
 \begin{align*}
@@
 \end{align*}
-at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$.
-Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we \revtext{reach} the desired result.
+at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we reach the desired result.
 \end{proof}
@@
 \end{revtwo}
-The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. \revtext{The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so}
+The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so
 \begin{revtwo}
@@
 \end{revtwo}
-\revtext{Since $\gamma > 0$ and $\sigma > -1$,} the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+Since $\gamma > 0$ and $\sigma > -1$, the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
 \begin{revtwo}
@@
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-\begin{rev}\begin{proposition}\label{prop:whole-ker-near-bound}
+\begin{proposition}\label{prop:whole-ker-near-bound}
 Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
@@
 for all $a, a' \in \Sigma$.
-\end{proposition}\end{rev}
+\end{proposition}
 \begin{proof}
-\revtext{Choose} some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
+Choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
@@
 
-\revtext{Condition~\eqref{cond:eps-lambda} implies that}
+Condition~\eqref{cond:eps-lambda} implies that
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 \end{align*}
-for any integration path that stays within $\near$. \revtext{Noting} that $\near$ is \revtext{star-shaped by construction, we} use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
+for any integration path that stays within $\near$. Noting that $\near$ is star-shaped by construction, we use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
 \begin{align*}
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, \revtext{there is some $M\in\R_{>0}$} for which
-\revtext{\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]}
-\revtext{for all $a \in \far$ and $a' \in \Omega$.} \revtext{This bound implies that}
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, there is some $M\in\R_{>0}$ for which
+\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]
+for all $a \in \far$ and $a' \in \Omega$. This bound implies that
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
-\revtext{We} again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+We again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
@@
 \end{align*}
-\revtext{Set $\Lambda > \lambda$, so} the exponential factor shrinks as $|\zeta(a)|$ grows. \revtext{Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound}
+Set $\Lambda > \lambda$, so the exponential factor shrinks as $|\zeta(a)|$ grows. Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound
 \[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
@@
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, \revtext{consider} the beginning and end of the integration path separately.
+To see this in the trickiest case, where $\rho < 1$, consider the beginning and end of the integration path separately.
 At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we use a worst-case estimate on the exponential factor:
@@
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
-\revtext{Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
+Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
 Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top} guarantee that this is possible.
-The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.}
+The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
 
@@
 \end{proof}
-\begin{rev}\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
+\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
 First, suppose $\rho \in (\tau, \tau+\gamma)$.
@@
 Under this inclusion, any solution of equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-\end{proof}\end{rev}
-\revtext{\begin{proposition}\label{prop:alt-general_volterra}
+\end{proof}
+\begin{proposition}\label{prop:alt-general_volterra}
 Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}.
@@
 of the space $\singexpalg{\tau-1}(\domain)$.
-\end{proposition}}
+\end{proposition}
 \begin{proof}
@@
 \subsection{Overview}
-We can use our \revtext{analysis} of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-\revtext{Under certain conditions}, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We can use our analysis of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+Under certain conditions, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 
-\revtext{To use our previous reasoning in this more general setting, we must reinterpret its language.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.} This substitution leads to several other reinterpretations, summarized below.
+To use our previous reasoning in this more general setting, we must reinterpret its language.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.
+This substitution leads to several other reinterpretations, summarized below.
 
@@
 \subsubsection{Definition}\label{sec:definition_Laplace}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain \revtext{$\zeta=\alpha$.
-Let} $\Gamma_{\zeta, \alpha}^\theta$ be the ray \revtext{in the position domain} that leaves $\zeta=\alpha$ at angle $\theta$\revtext{, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.} When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, \revtext{the Laplace transform
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$.
+Let $\Gamma_{\zeta, \alpha}^\theta$ be the ray in the position domain that leaves $\zeta=\alpha$ at angle $\theta$, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.
+When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform
 \[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
@@
 \laplace_{\zeta, \alpha}^{\theta} \varphi := \int_{\Gamma_{\zeta,\alpha}^\theta} e^{-z\zeta} \varphi\;d\zeta.
-\end{equation}}
+\end{equation}
 
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, \revtext{differentiation under the integral shows} that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, differentiation under the integral shows that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \subsection{Going to the position domain}
-\revtext{Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.}
+Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.
 \begin{lemma}\label{lem:use-dict}
-For \revtext{any $\alpha \in \C$}, let $\hat{\mathcal{P}}_{\alpha}$ be the \revtext{integral} operator 
+For any $\alpha \in \C$, let $\hat{\mathcal{P}}_{\alpha}$ be the integral operator 
 \[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
@@
 \begin{rmk}
-\revtext{For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.} We will see later that for our results to apply, $\domain_\alpha$ \revtext{also} cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.
+We will see later that for our results to apply, $\domain_\alpha$ also cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
 \end{rmk}
-\revtext{\begin{rmk}\label{rmk:use-dict-explicit}
+\begin{rmk}\label{rmk:use-dict-explicit}
 To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
@@
 \[ k_R(a,a') := \sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
-\end{rmk}}
+\end{rmk}
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
-Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we \revtext{find that} $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we find that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
 Hence,
@@
 \begin{theorem}\label{thm:example}
-\revtext{Suppose $P$ has a root $-\alpha$} where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
+Suppose $P$ has a root $-\alpha$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
 $\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$. Then the equation
@@
 \begin{proof}
-\revtext{To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
+To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
 When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
@@
 \[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
-\end{revtwo}}
+\end{revtwo}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
-Equation~\eqref{eqn:divided} \revtext{can be written} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
-
-\revtext{The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
+Equation~\eqref{eqn:divided} can be written as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+
+The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
 To see this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
 It follows that for any $\lambda > A$, we have $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
-The power series defining $k_R$ therefore converges everywhere.}
+The power series defining $k_R$ therefore converges everywhere.
 \begin{verify}
@@
 
-\revtext{Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.}
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
 \begin{itemize}
@@
 \[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
-\revtext{arbitrarily small}. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
+arbitrarily small. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-\revtext{arbitrarily small}. Hence, for any $\sigma > \tau_\alpha$, the bound
+arbitrarily small. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]

### 2024-08-12 sima/reg-sing-volterra_sima.tex
Color version for second round of revisions

@@
 \frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-\laplace \psi\;\laplace\varphi & = \laplace(\psi * \varphi) \\
+\laplace \revtwotext{\psi}\;\laplace\varphi & = \laplace(\revtwotext{\psi} * \varphi) \\
 z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi\,,
@@
 \[ \laplace_{\zeta,\alpha} \varphi := \int_{\Gamma_{\zeta,\alpha}} e^{-z\zeta} \varphi\;d\zeta\,, \]
-where $\Gamma_{\zeta,\alpha}$ is the ray $\zeta \in (\alpha, \infty)$.    
+where $\Gamma_{\zeta,\alpha}$ is the ray $\zeta \in \alpha + (0, \infty)$.    
 This version of the Laplace transform is defined in Section~\ref{sec:definition_Laplace}.
@@
 Sometimes, in expressions like
-\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\,d\zeta(a')\,, \]
+\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\;d\zeta(a')\,, \]
 it is useful to give a name $a'$ to the point moving along the integration path.
@@
 for some $p, q \in \mathcal{H}(\Omega)$. \begin{revtwo}Explicitly,
-\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta=0}^{a} \frac{q}{p(a)}\,\varphi\;d\zeta\,. \]
+\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a')\,. \]
 \end{revtwo}
@@
 satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
-\[ f = \volterra f \]
-has a unique solution $f$ in the affine subspace
+\[ f = \volterra f, \]
+\revtwotext{where $\volterra = \hardpart + \softpart$,} has a unique solution $f$ in the affine subspace
 \[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
@@
 \begin{rmk}
-We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}
+We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}.
 \end{rmk}
@@
 In summary, the beginning of the integral is bounded by a decaying exponential function of $(\Lambda - \lambda)\delta$, and the end of the integral is bounded by a reciprocal function of $(\Lambda - \lambda)\delta$.
-That means we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)|$ as small as we want over all $a \in \far$.
+That means we can make $|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big|$ as small as we want over all $a \in \far$.
 This completes our proof of Proposition~\ref{prop:get-contraction}.
@@
 Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-In an upcoming paper \cite{borel_reg}, we will study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
+In~\cite{borel_reg}, we study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
@@
 \begin{revtwo}
-\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a'), \]
+\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta(a')=\alpha}^a q(a') \, \varphi(a') \; d\zeta(a') + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a'), \]
 \end{revtwo}
@@
 \begin{revtwo}
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta(a')=\alpha}^a q(a') \, \varphi(a') \; d\zeta(a') + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
 \end{revtwo}

### 2024-08-18 borel-regularity.tex
Match new notation from "Regular singular Volterra"
change notation for convolution, dropping the "prime" and "double prime" notation

@@
 \newif\ifhighlightrevs
-\highlightrevsfalse
+\highlightrevstrue
 \ifhighlightrevs
@@
 We do this in Section~\ref{sec:new-summability-proof}.
+
+As discussed in Section~\ref{sec:history_ODE}, the novel aspect of Theorem~\ref{thm:exist_uniq_ODE} is that it is stated and proved in the world of functional analysis, rather than the world of formal series.
+Theorem~\ref{thm:soln_is_Borel_sum} is a new proof of a special case of an old result mentioned in Section~\ref{sec:Poincare method}: the multisummability of formal solutions of linear systems of ODEs~\cite{ramis1991series,braaksma2006laplace}.
+The new proof is interesting because it starts from the analytic solutions found in Theorem~\ref{thm:exist_uniq_ODE}, rather than the formal solutions found by Poincar\'{e}.
 \subsubsection{Why does Borel summation work for thimble integrals?}\label{sec:why_borel_thimble}
@@
 %
+\begin{todo}Add the notation for integrals\end{todo}
 \subsection{Acknowledgements}
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont}, and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
-Choose any $\Lambda' > \Lambda$.
-Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
+\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
+\begin{old}Choose any $\Lambda' > \Lambda$.\end{old} \begin{revised}Let $\Lambda' = \Lambda / \cos(\Theta)$.\end{revised} Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
 \[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
@@
 \renewcommand{\phase}{0}
-\newcommand{\spread}{30}
-
-\newcommand{\pathdis}{1.5625}
+\newcommand{\spread}{55.5}
+\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}
+
+%%\newcommand{\pathdis}{1.5625}
+%%\newcommand{\pathoffset}{0.375}
 \newcommand{\pathspread}{20}
@@
 % the region
-\fill[pwbeige!30, draw=pwbeige!60] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
+\fill[pwbeige!30, draw=pwbeige!60, thick] (-\phase-\spread:\dis) +(-\phase-\spread-90:\rshade) -- +(0, 0) arc (-\phase-\spread:-\phase+\spread:\dis) -- ++(-\phase+\spread+90:\rshade) -- (\rshade, \rshade) -- (\rshade, -\rshade) -- (0, -\rshade) -- cycle;
 
@@
 
+% the construction lines
+\begin{scope}[pwbeige!80!black]
+\draw (\peakdis, 0) +(-\phase-\spread-90:1.5*\rshade) -- +(0, 0) -- +(-\phase+\spread+90:1.5*\rshade);
+\end{scope}
+
 % the path
-\draw[very thick] (-\phase-\pathspread:\pathdis) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) arc (-\phase-\pathspread:-\phase+\pathspread:\pathdis) -- ++(-\phase+\pathspread+90:\rshade);
+\draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
+%%\draw[very thick] (-\phase-\pathspread:\pathdis) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) arc (-\phase-\pathspread:-\phase+\pathspread:\pathdis) -- ++(-\phase+\pathspread+90:\rshade);
 
@@
 \end{tikzpicture}
-\captionof{figure}{The path $\mathcal{C}$.}
+\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}
 \end{center}
@@
 The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
-\begin{equation}\label{eq:convolution_def}
+\begin{revised}
+\begin{equation}%%\label{eq:convolution_def}
+\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
+\end{equation}
+\end{revised}
+\begin{old}
+\begin{equation}%%\label{eq:convolution_def}
 \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta',
 \end{equation}
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta-\alpha$ to $\zeta''=0$. 
+\end{old}
+\begin{old}where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta-\alpha$ to $\zeta''=0$.\end{old}
+\begin{revised}where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.\end{revised}
 \end{definition}
@@
 \begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
+\begin{old}
    \begin{align*}
@@
 where $\zeta'=s\zeta_\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$.
-
+\end{old}
+\begin{revised}
+\begin{align*}
+\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta(a)\\
+&=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
+\end{align*}
+where $\zeta(a)=s\zeta_\alpha$ and consequently $\zeta(a')=\zeta_\alpha (1-s)$.  
+\end{revised}
 First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. Indeed it is uniform of exponential type
+\begin{old}
 \begin{align*}
@@
 \end{align*}
+\end{old}
+\begin{revised}
+\begin{align*}
+   \big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi(a)|\,|\psi(a')|\\
+   &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
+   & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}
+\end{align*}    
+\end{revised}
 where $c''=\max\{c,c'\}$.
-\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{revised}
+\begin{old}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{old}
+\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a) \psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+This guarantees that $\phi(a) \psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}
 %   
 Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
+\begin{old}
      \begin{align*}
@@
    \end{align*}
+   \end{old}
+   \begin{revised}
+      \begin{align*}
+       \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
+       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi(a) \psi(a')\,ds \\
+       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi(a) \psi(a')\,ds 
+   \end{align*}      
+   \end{revised}
    by exchanging the order of integration we find
+   \begin{old}
    \begin{align*}
@@
    \end{align*}
+   \end{old}
+   \begin{revised}
+   \begin{align*}
+    &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
+    &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a')\,\frac{\zeta(a')}{(1-s)^2}\,e^{-z\zeta(a')} e^{-z\zeta(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
+   \end{align*}    
+   \end{revised}
+   \begin{old}
    Setting $t=\zeta''\frac{s}{1-s}$ we find
@@
      where as $s$ varies in $[0,1]$ we get that $t$ follows the ray $\mathcal{J}_{t,0}$. 
+   \end{old}
+   \begin{revised}
+   Using that $\zeta(a)=\zeta(a')\frac{s}{1-s}$ holds on the integration contour, we find
+    \begin{align*}
+    &=\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta(a')}{(1-s)^2}e^{-z\zeta(a') \frac{s}{1-s}} \phi(a)\\
+    &=\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta(a),0}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)\\
+   \end{align*} 
+    where as $s$ varies in $[0,1]$ we get that $\zeta(a)$ follows the ray $\mathcal{J}_{\zeta(a),0}$. 
+   \end{revised}
+
 \end{proof}
@@
 \end{todo}
+\begin{old}
   Notice that the convolution product can be rewritten by introducing the coordinates $\eta'=\zeta'-\beta$ and $\eta''=\zeta''+\beta$
@@
 If true, clarify argument.]\end{todo}
+   \end{old}
+   \begin{revised}
+     Notice that the convolution product can be rewritten by introducing the coordinates $\eta(a)=\zeta(a)-\beta$ and $\eta(a')=\zeta(a')+\beta$
+   \begin{align*}
+       \phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
+       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\,,
+   \end{align*}
+   where $\mathcal{S}(\eta)$ is the line segment from $\eta(a)=\alpha$ to $\eta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\eta)$ is the line segment from $\eta(a')=\zeta_\alpha$ to $\eta(a')=\beta$.
+\begin{todo}\textbf{V} [explain why this choice of coords is better than $\eta'$ and $\eta''$]\end{todo} Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution
+    \begin{align*}
+       \phi \ast_{\zeta, \alpha+\beta} \psi
+       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\\
+       &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a) \psi(a')\,ds\,,
+   \end{align*}
+   \begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\eta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta(a')=\beta s+(1-s)\zeta_\alpha$.
+Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
+     \begin{align*}
+       \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
+       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a) \psi(a')\,ds \\
+       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a) \psi(a')\,ds
+   \end{align*}
+   by exchanging the order of integration we find 
+   \begin{align*}
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi(a) \psi(a') \\
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta(a'),\beta}}\frac{d\eta(a')}{(1-s)^2}\,e^{-z\eta(a')} (\eta(a')-\beta) e^{-z( (\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
+   \end{align*}
+   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta(a')-\beta}{1-s}$.
+Then, exchanging one more time the order of integration we get
+    \begin{align*}
+        &=\int_{\mathcal{J}_{\eta(a'),\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\eta(a')-\beta}{(1-s)^2}e^{-z((\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
+        &=\int_{\mathcal{J}_{\eta(a'),\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_{\mathcal{J}_{\eta(a),\alpha}} d\eta(a)\, e^{-z\eta(a)} \phi(a)\\
+   \end{align*}
+   where on the integration path we have $\eta(a)=(\eta(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\zeta(a),\alpha}$ as $s$ varies in $[0,1]$.   
+   \end{revised}
 \end{proof}
@@
 For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
+\begin{old}
 \[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}'(\zeta)} \big(\zeta-\zeta'\big)^{-\nu} \phi' \,d\zeta', \]
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.
+
+Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ along our integration path.
+\end{old}
+\begin{revised}
+ \[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
+\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
+where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
+
+Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta(a') = \zeta - \zeta(a)$ along our integration path.
+\end{revised}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
 Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
@@
 \end{definition}
-Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ along our integration path.
-
 The fractional integral obeys the semigroup law \cite[Section  1.3]{mladenov2014advanced}
@@
 Results \ref{res:frac-deriv} and \ref{res:frac-int} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
+\begin{old}
 \begin{align*}
@@
 Similarly, one can prove \emph{iii)}.
+\end{old}
+\begin{revised}
+\begin{align*}
+z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
+&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta)}\frac{(\zeta-\zeta(a))^{-\tau-1}}{\Gamma(-\tau)} \phi(a) d\zeta(a)\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta) }\frac{(\zeta-\zeta(a))^{-\tau-1}}{\Gamma(-\tau)} \phi(a) d\zeta(a)\\
+&=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi,
+\end{align*}
+where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
+Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:
+\begin{align*}
+    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
+    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
+    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
+\end{align*}
+Result~\ref{res:monom-mult} is also proven by repeated integration by parts, with the assumption that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ ensuring that the integral converges.
+        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
+This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
+Similarly, one can prove \emph{iii)}.
+\end{revised}
 \end{proof}
@@
 We will show that for any $\mu \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+\begin{old}
 \begin{align*}
@@
 \end{align*}
+\end{old}
+\begin{revised}
+\begin{align*}
+\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta(a))^{-\mu} \frac{(\zeta(a))^k}{\Gamma(k+1)}\,d\zeta(a) \\
+& = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\mu-1)}}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\mu} t^k\,dt \\
+& = \frac{\zeta^{k-(\mu-1)}}{\Gamma\big(k-(\mu-1)+1\big)}
+\end{align*}    
+\end{revised}
 by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that

### 2024-09-03 borel-regularity.tex
Add context for thimble integral results

@@
 \end{theorem}
-\begin{todo}[In parallel with the ODE results, does this theorem help us accomplish something interesting or justify a point of view?]\end{todo}
+\begin{draft}
+This result confirms the expectations that thimble integrals are equal to the Borel resummation of its asymptotics~\cite[Section~2]{dunne-unsal}.
+Although the same result is conjectured to hold in higher dimensions, our proof might not straighfowardly generalize, hence we leave the discussion to future works.
+
+Notice also that an alternative proof can be done using Nevanlinna's theorem~\cite{nevanlinna}, but it will require an accurate control of the asymptotics of $I_a$, which should be uniform and 1-Gevrey in a large enough sector.
+Instead, our approach avoids the analysis of the asymptotics by working in the position domain.
+In fact, we use that $I_a$ can be regarded as a Laplace trasnform.
+\end{draft}
+\begin{revised}
+For one-dimensional thimbles, this result confirms the expectation that evaluating a thimble integral should be equivalent to taking the Borel sum of its asymptotic series~\cite[Section~2]{dunne-unsal}.
+Confirming this expectation in higher dimensions would be an interesting topic for future work, since our argument may not generalize straightforwardly.
+
+As an alternative to our argument, Theorem~\ref{thm:maxim} could be deduced from Nevanlinna's theorem~\cite{nevanlinna}.
+However, that would require a careful asymptotic analysis of $I_a$: one would have to show that its asymptotic series is $1$-Gevrey and uniformly asymptotic to it on a large enough sector.
+We avoid this asymptotic analysis by working in the position domain and recasting $I_a$ as a Laplace transform integral.
+\end{revised}
 %
@@
 %
-\begin{revised}
 In Section~\ref{sec:historical-context}, we contextualize our work by reviewing some classical results related to Borel regularity.
@@
 
-In section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results.
+In Section~\ref{sec:Laplace-Borel-general}, we introduce a geometric perspective on the Laplace and Borel transforms, which will be useful for stating and proving our results.
 To make this section more self-contained, we review basic definitions and properties in Section~\ref{laplace:ordinary} and the beginnings of Sections \ref{sec:geometry_borel} and \ref{sec:borel-laplace-homom}.
@@
 In Appendix~\ref{shifting}, we prove a fact about the relationship between integral and differential equations which is used in some of our examples.
-\end{revised}
-%
-\begin{todo}\par [Consider going back to non-separated style.]\end{todo}\begin{draft}The paper is organized as follows: in Section~\ref{sec:historical-context} we review some well-known results concerning Borel regularity which dates back to the classical theory of asymptotics, ODEs and integrals over Lefschetz thimbles.
-This could help the reader to contextualize our results in the literature.
-Then, in Section~\ref{sec:Laplace-Borel-general} is devoted to define the new geometric picture of the Borel and Laplace transform.
-The reader who is not familiar with the formalism of Borel and Laplace transforms might start with Sections \ref{laplace:ordinary}, the beginning of Section~\ref{sec:geometry_borel} and of Section~\ref{sec:borel-laplace-homom}.
-Then, Section~\ref{sec:proof_main_results} contains proofs of the main results.
-Finally, in Section~\ref{sec:examples} we give a detailed treatment of different examples both from the ODE perspective and from the thimble integral one.
-We include Appendix~\ref{airy-appendix} that contains a detailed treatment of the Airy example, and it is recommended for readers less familiar to the subject.
-\begin{todo}[Appendix~\ref{shifting}?]\end{todo}
-\end{draft}
 %
@@
 %
-\begin{todo}Add the notation for integrals\end{todo}
+\begin{todo}[Add the notation for integrals. Reference regular singular Volterra paper, and also more or less copy its notation description.]\end{todo}
 \subsection{Acknowledgements}
@@
 %
-\begin{revised}A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
+A level~$1$ ODE can be seen as the coordinate expression of a meromorphic connection on a principal bundle---specifically, the kind of meromorphic connection called an {\em oper}~\cite{BD-opers}.
 Local solutions of the ODE correspond to local flat sections of the connection.
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE.
-\begin{todo}[Add reference]\end{todo}
+In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
 
 To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray.
-A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.\end{revised}
+A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.
 
@@
 Kontsevich and Soibelman also explain why the asymptotics of these thimble integrals are resurgent series.
-\begin{todo}\par
-Discuss examples where the Riemann--Hilbert problem corresponding to an ODE can be solved.
-\begin{itemize}
-\item Dubrovin
-\item Kontsevich--Soibelman
-\item Bridgeland
-\item Gaiotto--Moore--Nietzke
-\end{itemize}
-\end{todo}
 %
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as period integrals \cite{deligne2007singularites,Maxim_lectures,pham}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals \cite{deligne2007singularites,Maxim_lectures}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
 \begin{todo}[\textbf{V} Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-\begin{todo}[\textbf{A} Correct proof, and possibly remove constant]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
+\begin{todo}[\textbf{A} Correct proof, and possibly remove constant] [\textbf{V} read it]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
 \begin{old}Choose any $\Lambda' > \Lambda$.\end{old} \begin{revised}Let $\Lambda' = \Lambda / \cos(\Theta)$.\end{revised} Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
@@
 \begin{proof}
-Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$.
+\begin{revised}The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc.
+Extend the rays until they meet, forming the boundary of a sector with opening angle $\pi - \Theta$.
+Expand that sector by angle $\varepsilon/2$ on both sides.
+The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.\end{revised}\begin{old}Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$.
 Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
 %
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.
+The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.\end{old}
 \begin{center}
@@
 %%\newcommand{\pathoffset}{0.375}
-\newcommand{\pathspread}{20}
+\newcommand{\pathspread}{35}
 
@@
 \end{tikzpicture}
-\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}
+\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}\label{fig:ref-path}
 \end{center}
-Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
-\begin{revised}Along $\mathcal{C}$, we have \begin{todo}[\textbf{A} where does the estimate come from?]\end{todo}
-\[ \Delta \ge \mu + \sin(\varepsilon/2)\,|t|, \]
-for some $\mu \in (\Lambda, \Lambda')$, where $\Delta$ is still the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
-\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big). \]
-\begin{todo}[Why on $\mathcal{C}$ the real part of $z$ is bounded like that?]\end{todo}\end{revised}
+\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon/2$.
+Parameterize it using the arc length parameter $t$ which is zero where the rays meet.
+Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
+\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,. \]
+On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
+\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
+\begin{todo}[Justify bound and add pictures.]\end{todo}\end{revised}
 
@@
 \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
-& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\mu + \sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
+& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised} \|\Phi\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised}\,dt,
 \end{align*}
@@
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|} \big(\mu + |s|\big)^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
-& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} \big(\mu + s\big)^{-\sigma}\,ds \\
-& \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s} s^{-\sigma}\,ds
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|}\begin{revised}\,|s|^{-\sigma}\end{revised}\,\frac{ds}{\sin(\varepsilon/2)} \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\begin{revised}\,s^{-\sigma}\end{revised}\,ds \\
+& \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\begin{revised}\,s^{-\sigma}\end{revised}\,ds
 \end{align*}
@@
 This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-Since we will define the convolution product in terms of an integral along a path in $B \times B$, we must first introduce notation to help us express the integrand.
+\begin{old}Since we will define the convolution product in terms of an integral along a path in $B \times B$, we must first introduce notation to help us express the integrand.
 \begin{notation}\label{notn:prod}
@@
 \end{notation}
+\end{old}
 \begin{definition}\label{def:convolution}
@@
 \begin{align*}
-\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta(a)\\
+\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
 &=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
 \end{align*}
-where $\zeta(a)=s\zeta_\alpha$ and consequently $\zeta(a')=\zeta_\alpha (1-s)$.  
+where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
 \end{revised}
-First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$. Indeed it is uniform of exponential type
+First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
+It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
 \begin{old}
@@
 &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
-   & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}
+& \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}\,.
 \end{align*}    
 \end{revised}
-where $c''=\max\{c,c'\}$.
 \begin{old}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
 This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{old}
-\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a) \psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi(a) \psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}
+\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}
 %   
@@
     &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
-    &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a')\,\frac{\zeta(a')}{(1-s)^2}\,e^{-z\zeta(a')} e^{-z\zeta(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
+    &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a')\,\frac{\zeta_\alpha(a')}{(1-s)^2}\,e^{-z\zeta_\alpha(a')} e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
    \end{align*}    
@@
    \begin{revised}
-   Using that $\zeta(a)=\zeta(a')\frac{s}{1-s}$ holds on the integration contour, we find
-    \begin{align*}
-    &=\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta(a')}{(1-s)^2}e^{-z\zeta(a') \frac{s}{1-s}} \phi(a)\\
-    &=\int_{\mathcal{J}_{\zeta(a'),0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta(a),0}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)\\
-   \end{align*} 
-    where as $s$ varies in $[0,1]$ we get that $\zeta(a)$ follows the ray $\mathcal{J}_{\zeta(a),0}$. 
+   Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
+    \begin{align*}
+    &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta_\alpha(a')}{(1-s)^2}e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\\
+    &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta_\alpha,0}} d\zeta_\alpha(a)\, e^{-z\zeta_\alpha(a)} \phi(a)\\
+   \end{align*} 
+    where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
    \end{revised}
@@
 \begin{todo}
-[\textbf{V} add $\theta$] [\textbf{A} read through proof]
+[\textbf{V} add $\theta$, or explain that it's missing, Fix proof] [\textbf{A} read through proof]
 \end{todo}
@@
    where $\mathcal{S}(\eta)$ is the line segment from $\eta(a)=\alpha$ to $\eta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\eta)$ is the line segment from $\eta(a')=\zeta_\alpha$ to $\eta(a')=\beta$.
-\begin{todo}\textbf{V} [explain why this choice of coords is better than $\eta'$ and $\eta''$]\end{todo} Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution
+The coordinate $\eta$ would simplify the computations by showing the dependence on the base point of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.
+
+   Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution  
     \begin{align*}
@@
         &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi(a) \psi(a') \\
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta(a'),\beta}}\frac{d\eta(a')}{(1-s)^2}\,e^{-z\eta(a')} (\eta(a')-\beta) e^{-z( (\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta,\beta}}\frac{d\eta(a')}{(1-s)^2}\,e^{-z\eta(a')} (\eta(a')-\beta) e^{-z( (\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
    \end{align*}
@@
     \begin{align*}
-        &=\int_{\mathcal{J}_{\eta(a'),\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\eta(a')-\beta}{(1-s)^2}e^{-z((\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
-        &=\int_{\mathcal{J}_{\eta(a'),\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_{\mathcal{J}_{\eta(a),\alpha}} d\eta(a)\, e^{-z\eta(a)} \phi(a)\\
-   \end{align*}
-   where on the integration path we have $\eta(a)=(\eta(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\zeta(a),\alpha}$ as $s$ varies in $[0,1]$.   
+        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\eta(a')-\beta}{(1-s)^2}e^{-z((\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
+        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_{\mathcal{J}_{\eta,\alpha}} d\eta(a)\, e^{-z\eta(a)} \phi(a)\\
+   \end{align*}
+   where on the integration path we have $\eta(a)=(\eta(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\eta,\alpha}$ as $s$ varies in $[0,1]$.   
    \end{revised}
@@
 \begin{remark}
-For $\alpha=0$, the Definition~\label{def:convolution} agrees with the standard deifinition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by \begin{draft}$\ast_\zeta$\end{draft} \begin{todo}[Add coordinate to $\ast$ elsewhere too]\end{todo}, following the standard convention.   
+For $\alpha=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
+In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$, following the standard convention. \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
 \end{remark}
@@
 Then, the unit for $\ast_{\zeta_\alpha,0}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha,0}\frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
-We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product, to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
 \begin{prop}
@@
 \end{proof}
-\begin{todo}[Shorten to a reminder that $z$ is an almost-global coordinate on cotangent spaces, so this also works in other fibers.]\end{todo} Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product, to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
+\begin{todo}[Maybe shorten to a reminder that $z$ is an almost-global coordinate on cotangent spaces, so this also works in other fibers.]\end{todo} Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
 %We can further generalize this result to transseries:
@@
 \begin{remark}
-   If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in equation~\eqref{eq:convolution_def}.
+If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in Definition~\ref{def:convolution}.
 We will discuss it in Section~\ref{sec:Borel-gevrey}.
@@
 For regular enough functions, the formal Laplace transform preserves a one-way vestige of this link: it turns Taylor expansions on the position domain into asymptotic expansions on the frequency domain.
-\begin{todo}[Compare with Sokal's version of the Watson--Nevanlinna theorem?]\end{todo}
 \begin{lemma}\label{lem:laplace-bridge}
@@
 If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
+\begin{todo}[Clarify domain of $\Phi$]\end{todo}
 \end{lemma}
 \begin{remark}
-This result is similar to Theorem~5.20 of \cite{diverg-resurg-i}.
+This result is similar to Theorem~5.20 of~\cite{diverg-resurg-i}.
 It is weaker in that it does not establish Gevrey asymptoticity, but stronger in that it can be applied to functions with fractionally shifted Taylor expansions.
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
-Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
+Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check; specify domain of ray]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
 \begin{align*}
@@
 \end{align*}
-along any ray. This, as discussed above, proves the desired result.
+along any ray \begin{todo}[specify domain of ray]\end{todo}. This, as discussed above, proves the desired result.
 \end{proof}
@@
 \begin{revised}
- \[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
-\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
+%%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
+\[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
 where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
 
-Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta(a') = \zeta - \zeta(a)$ along our integration path.
+%% Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta(a') = \zeta - \zeta(a)$ along our integration path.
 \end{revised}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
@@
 \begin{align*}
-z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
-&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta)}\frac{(\zeta-\zeta(a))^{-\tau-1}}{\Gamma(-\tau)} \phi(a) d\zeta(a)\\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta) }\frac{(\zeta-\zeta(a))^{-\tau-1}}{\Gamma(-\tau)} \phi(a) d\zeta(a)\\
+z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\left[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\right] \laplace_{\zeta,0}\phi\\
+&=\laplace_{\zeta,0}\left[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\right] \\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta)}\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta) }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
 &=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi,
@@
 \begin{align*}
-\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta(a))^{-\mu} \frac{(\zeta(a))^k}{\Gamma(k+1)}\,d\zeta(a) \\
+\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta \big(\zeta-\zeta(a)\big)^{-\mu} \frac{\zeta(a)^k}{\Gamma(k+1)}\,d\zeta(a) \\
 & = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
@@
 
-\begin{todo}[Confirm that we should have $\zeta_\alpha$ rather than $\zeta$ here]\end{todo} Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
+\begin{todo}[\textbf{A} Confirm that we should have $\zeta_\alpha$ rather than $\zeta$ here; \textit{V} Confirmed]\end{todo} Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
 Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
@@
 taking the positive branch of the square root on $\mathcal{C}^+_a$ and the negative branch on $\mathcal{C}^-_a$.
-Plugging this into our expression for $\iota_a$ (in Theorem \ref{lem:thimble_proj_formula-proof}), we learn that
+Plugging this into our expression for $\iota_a$ (in Lemma~\ref{lem:thimble_proj_formula-proof}), we learn that
 \begin{align*}
@@
 \[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
-Then by Pham's result (see \eqref{rmk:Pham formula}) we know 
+Then by Pham's result (see~\eqref{rmk:Pham formula}) we know 
 \[\hat{\iota}_j(\zeta_j)=\frac{(-\zeta_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-\zeta_j)^{-k} + \text{ hol. funct. }\]
@@
 can be seen as fractional derivatives of the Dirac delta distribution.
-In particular, if $N=1$, the inverse Laplace transform of the function $I_a$ from Equation~\eqref{exp-int} has a singularity of the form $\zeta_\alpha^{1/2}$, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
+In particular, if $N=1$, the inverse Laplace transform of the function $I_a$ from equation~\eqref{exp-int} has a singularity of the form $\zeta_\alpha^{1/2}$, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
 %as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.
@@
 \end{equation}
-for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}{[Cite Watson too?]}\end{todo}.
+for $|\theta| < \tfrac{\pi}{2}$.
+This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}[Explain the finagling at least a little bit, maybe in a footnote]\end{todo}.
 \begin{verify}
@@
 \begin{equation}
-K_{1/3}(z) = \frac{irp}{\sqrt{3}}\,e^{qrz}\,I\left(\frac{rz}{a_3}\right)
+K_{1/3}(z) = \frac{irp}{\sqrt{3}}\,e^{qrz}\,I\left(\frac{rz}{a_3}\right)\,.
 \end{equation}
@@
 \end{verify}
+\begin{old}
 From this identity, you can deduce that $I(z)$ satisfies a second-order differential equation, analogous to the modified Bessel equation~\eqref{eqn:mod-bessel}.
+\end{old}
+\begin{revised}
+From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
+\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + 2a_3 q\,\tfrac{\partial}{\partial z} + a_3^2 (q^2 - r^{-2})\big] + z^{-1} \big(a_3 q + \tfrac{\partial}{\partial z}\big) - \tfrac{1}{9} z^{-2} \right] \Phi = 0\,.
+\]
+\end{revised}
 \begin{todo}\par
@@
 The factor of $e^{i\pi/3} - 1$ comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
-\begin{brainstorm}
-\item namely $v=(\zeta-q)^{-2/3}=\zeta_q^{-2/3}={}_2F_1\left(a,\frac{2}{3};a;1-\zeta_q\right)$, where $\zeta_q=\zeta-q$ and $a\in\C$ is a free parameter.
-\end{brainstorm}
 \end{itemize}

### 2024-09-09 borel-regularity.tex
Make notes during meeting

@@
 \end{theorem}
-\begin{draft}
-This result confirms the expectations that thimble integrals are equal to the Borel resummation of its asymptotics~\cite[Section~2]{dunne-unsal}.
-Although the same result is conjectured to hold in higher dimensions, our proof might not straighfowardly generalize, hence we leave the discussion to future works.
-
-Notice also that an alternative proof can be done using Nevanlinna's theorem~\cite{nevanlinna}, but it will require an accurate control of the asymptotics of $I_a$, which should be uniform and 1-Gevrey in a large enough sector.
-Instead, our approach avoids the analysis of the asymptotics by working in the position domain.
-In fact, we use that $I_a$ can be regarded as a Laplace trasnform.
-\end{draft}
-\begin{revised}
 For one-dimensional thimbles, this result confirms the expectation that evaluating a thimble integral should be equivalent to taking the Borel sum of its asymptotic series~\cite[Section~2]{dunne-unsal}.
@@
 We avoid this asymptotic analysis by working in the position domain and recasting $I_a$ as a Laplace transform integral.
-\end{revised}
 %
@@
 %
-The examples we study all involve {\em resurgent functions} in the position domain.
-\begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+The examples we study all involve {\em resurgent functions} in the position domain. \begin{draft}
+    The theory of resurgence introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}
+\end{draft} \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
 Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
@@
 
-%%\newcommand{\pathdis}{1.5625}
-%%\newcommand{\pathoffset}{0.375}
 \newcommand{\pathspread}{35}
+\newcommand{\angmarkrad}{1}
+\newcommand{\distmarkrad}{2.5}
+\pgfmathsetmacro{\bdrydist}{\distmarkrad*sin(\pathspread-\spread)}
 
@@
 \draw (\peakdis, 0) +(-\phase-\spread-90:1.5*\rshade) -- +(0, 0) -- +(-\phase+\spread+90:1.5*\rshade);
+\draw[shorten <=0.3mm, shorten >=0.4mm] (\peakdis, 0) ++(\phase+\spread+90:\angmarkrad) arc[start angle=\phase+\spread+90, delta angle=\pathspread-\spread, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-90+0.5*\spread+0.5*\pathspread)] {$\tfrac{\varepsilon}{2}$};
+%%\draw (\peakdis, 0) ++(-\phase-\spread-90:\angmarkrad) arc [start angle=\phase-\spread-90, delta angle=\spread-\pathspread, radius=\angmarkrad] node[midway, circle, inner sep=1, anchor=90-0.5*\spread-0.5*\pathspread] {$\tfrac{\varepsilon}{2}$};
+\draw[shorten >=0.3mm] (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) -- ++(\phase+\spread:\bdrydist) node[midway, circle, inner sep=0, anchor=-90+\spread] {$t \sin(\tfrac{\varepsilon}{2})$};
 \end{scope}
@@
 \draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
-%%\draw[very thick] (-\phase-\pathspread:\pathdis) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) arc (-\phase-\pathspread:-\phase+\pathspread:\pathdis) -- ++(-\phase+\pathspread+90:\rshade);
+\draw (\peakdis, 0) ++(\phase+\pathspread+90:0.5*\distmarkrad) node[anchor=180+\pathspread] {$t$};
+\draw (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) +(\pathspread:1mm) -- +(180+\pathspread:1mm);
 
@@
 \end{tikzpicture}
-\captionof{figure}{The thick, black line is the path $\mathcal{C}$.}\label{fig:ref-path}
+\captionof{figure}{The thick black line is the path $\mathcal{C}$.}\label{fig:ref-path}
 \end{center}
-\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon/2$.
+\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
 Parameterize it using the arc length parameter $t$ which is zero where the rays meet.
 Along $\mathcal{C}$, the distance $\Delta$ to the boundary of $\widehat{\Omega}_\alpha^\Lambda$ satisfies the estimate
-\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,. \]
-On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
+\[ \Delta \ge \sin(\varepsilon/2)\,|t|\,, \]
+as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
@@
 \begin{align*}
-\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
+\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
 &=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
@@
 First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
-It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
+\begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
 \begin{old}
@@
    \end{revised}
-   by exchanging the order of integration we find
+   by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
    \begin{old}
@@
 \begin{revised}
-     Notice that the convolution product can be rewritten by introducing the coordinates $\eta(a)=\zeta(a)-\beta$ and $\eta(a')=\zeta(a')+\beta$
+The convolution product can be rewritten by introducing the coordinates $\zeta_\beta$ and $\zeta_{-\beta}$:
 \begin{align*}
 \phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
-       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\,,
-   \end{align*}
-   where $\mathcal{S}(\eta)$ is the line segment from $\eta(a)=\alpha$ to $\eta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\eta)$ is the line segment from $\eta(a')=\zeta_\alpha$ to $\eta(a')=\beta$.
-The coordinate $\eta$ would simplify the computations by showing the dependence on the base point of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.
+&=\int_{\substack{\mathcal{S}(\zeta_{\beta}) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_{\beta}(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
+\end{align*}
+where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$.
+This change of coordinates simplifies our computations by showing how the convolution product depends on the base points of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.
 
@@
     \phi \ast_{\zeta, \alpha+\beta} \psi
-       &=\int_{\substack{\mathcal{S}(\eta) \times \mathcal{S}'(\eta) \\ \eta(a) + \eta(a') = \zeta}} \phi(a)\,\psi(a')\,d\eta(a)\\
+    &=\int_{\substack{\mathcal{S}(\zeta_\beta) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_\beta(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
     &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a) \psi(a')\,ds\,,
 \end{align*}
-   \begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\eta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta(a')=\beta s+(1-s)\zeta_\alpha$.
+\begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\zeta_\beta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\zeta_{-\beta}(a')=\beta s+(1-s)\zeta_\alpha$.
 Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
@@
     \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
-       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a) \psi(a')\,ds \\
-       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a) \psi(a')\,ds
-   \end{align*}
-   by exchanging the order of integration we find 
+    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a)\,\psi(a')\,ds \\
+    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a)\, \psi(a')\,ds\,.
+\end{align*}
+By exchanging the order of integration we find 
 \begin{align*}
         &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi(a) \psi(a') \\
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta,\beta}}\frac{d\eta(a')}{(1-s)^2}\,e^{-z\eta(a')} (\eta(a')-\beta) e^{-z( (\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
-   \end{align*}
-   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta(a')-\beta}{1-s}$.
+        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta,\beta}}\frac{d\zeta(a')}{(1-s)^2}\,e^{-z\zeta_{-\beta}(a')} (\zeta_{-\beta}(a')-\beta) e^{-z( (\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
+   \end{align*}
+   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\zeta_{-\beta}(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\zeta_{-\beta}(a')-\beta}{1-s}$ \begin{todo}[this comes from the expression for $\zeta_{-\beta}(a')$ above, by subtracting $\beta$ from both sides and then rearranging]\end{todo}.
 Then, exchanging one more time the order of integration we get
     \begin{align*}
-        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\eta(a')-\beta}{(1-s)^2}e^{-z((\eta(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
-        &=\int_{\mathcal{J}_{\eta,\beta}}d\eta(a') \,e^{-z\eta(a')}  \psi(a') \,\int_{\mathcal{J}_{\eta,\alpha}} d\eta(a)\, e^{-z\eta(a)} \phi(a)\\
-   \end{align*}
-   where on the integration path we have $\eta(a)=(\eta(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\eta,\alpha}$ as $s$ varies in $[0,1]$.   
+        &=\int_{\mathcal{J}_{\eta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
+        &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta_\beta(a)} \phi(a)\\
+         &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)
+   \end{align*}
+   where on the integration path we have $\zeta(a)=(\zeta_{-\beta}(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\zeta,\alpha}$ as $s$ varies in $[0,1]$.   
    \end{revised}
@@
 where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$.
-\begin{todo}[Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
+\begin{todo}[\textbf{A} Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
 
@@
 \end{align*}
-\begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
+\begin{todo}[Note that this presents $V_\alpha$ as the Laplace transform of $v_\text{uni}$.]\end{todo} \begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
 %\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}

### 2024-09-19 borel-regularity.tex
Format for print

@@
 
-\begin{revised}We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
+We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
 Our examples are in Section~\ref{sec:examples}.
-Section~\ref{sec:org} describes the layout of the paper in more detail.\end{revised}
+Section~\ref{sec:org} describes the layout of the paper in more detail.
 %
@@
 From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
-On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that \begin{revised}their Borel transforms converge\end{revised}, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
+On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that their Borel transforms converge, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
 We do this in Section~\ref{sec:new-summability-proof}.
@@
 %
-The examples we study all involve {\em resurgent functions} in the position domain. \begin{draft}
-    The theory of resurgence introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}
-\end{draft} \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+The examples we study all involve {\em resurgent functions} in the position domain. \color{cyan}
+    The theory of resurgence, introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}, studies the analytic properties of the Borel transform of divergent series in the frequency domain.
+In a nutshell it provides an effective tool to compute subleading order contributions and occasionally leads to the resummation of the original divergent series.
+\color{black} \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
 Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
@@
 The linear ODEs and $1$-dimensional thimble integrals that we study provide toy examples of how resurgent functions arise and behave.
-\begin{revised}As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.\end{revised}
+As a concrete example, in Section~\ref{resurgence-AL}, we use resurgence to find the Stokes constants of the Airy--Lucas equations.
 %
@@
 \end{align*}
+\textcolor{red}{I don't see what changed in the last step}
+
 using the new parameter $s = \sin(\varepsilon/2)\,t$.
@@
     &=\int_{\substack{\mathcal{S}(\zeta_\beta) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_\beta(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
-    &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a) \psi(a')\,ds\,,
+    &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
 \end{align*}
@@
 \begin{align*}
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi(a) \psi(a') \\
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta,\beta}}\frac{d\zeta(a')}{(1-s)^2}\,e^{-z\zeta_{-\beta}(a')} (\zeta_{-\beta}(a')-\beta) e^{-z( (\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a) \psi(a')\,,
+&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\beta s+(1-s)\zeta_\alpha)} e^{-z(\alpha(1-s)+s\zeta_\beta)}\phi(a)\,\psi(a') \\
+&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta,0}}\frac{d\zeta(a')}{(1-s)^2}\,e^{-z\zeta_{-\beta}(a')} (\zeta_{-\beta}(a')-\beta) e^{-z( (\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\,\psi(a')\,,
 \end{align*}
@@
 \begin{align*}
-        &=\int_{\mathcal{J}_{\eta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
-        &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta_\beta(a)} \phi(a)\\
-         &=\int_{\mathcal{J}_{\zeta,\beta}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)
-   \end{align*}
-   where on the integration path we have $\zeta(a)=(\zeta_{-\beta}(a')-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{\zeta,\alpha}$ as $s$ varies in $[0,1]$.   
+&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
+&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha+\beta)} \phi(a)\\
+&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha+\beta}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)
+\end{align*}
+where on the integration path we have $\zeta(a)=(\zeta_{-\beta}(a')-\beta)\frac{s}{1-s}+\alpha+\beta$ which moves $a$ \begin{todo}(?)\end{todo} along the ray $\mathcal{J}_{\zeta,\alpha+\beta}$ as $s$ varies in $[0,1]$.
 \end{revised}
@@
 \end{align*}
-\begin{revised}
 \begin{prop}\label{prop:L-int-op}
@@
 \end{prop}
-\end{revised}
 \begin{proof}
@@
 We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
-\begin{revised}
 \begin{prop}\label{prop:frac-der-int-borel}
@@
 \end{proof}
-\end{revised}
 %
@@
 %
-\begin{revised}Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
+Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
 Let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
@@
 In this section, we will prove that thimble integrals of the form \eqref{exp-int} are Borel regular.
-The first step is to rewrite $I_a$ as the Laplace transform of a function $\iota_a$, which is given explicitly by the well-known formula that we will call the \textit{thimble projection formula}.\end{revised}
+The first step is to rewrite $I_a$ as the Laplace transform of a function $\iota_a$, which is given explicitly by the well-known formula that we will call the \textit{thimble projection formula}.
+%
 \begin{lemma}[adapted from {\cite[Section~3.3]{pham}}]\label{lem:thimble_proj_formula-proof}
@@
 \end{verify}
-\begin{old}
-From this identity, you can deduce that $I(z)$ satisfies a second-order differential equation, analogous to the modified Bessel equation~\eqref{eqn:mod-bessel}.
-\end{old}
-\begin{revised}
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
@@
 \]
-\end{revised}
-\begin{todo}\par
-From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
-\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + 2a_3 q\,\tfrac{\partial}{\partial z} + a_3^2 (q^2 - r^{-2})\big] + z^{-1} \big(a_3 q + \tfrac{\partial}{\partial z}\big) - \tfrac{1}{9} z^{-2} \right] \Phi = 0 \]
 \begin{verify}
@@
 \end{verify}
-\end{todo}
+
 \item[] \textbf{One degenerate critical point}
@@
 %
-In \cite{kawai-takei}, Kawai and Takei \begin{revised}carry out an exact\end{revised} WKB analysis of the Airy-type Schr\"{o}dinger equation
+In \cite{kawai-takei}, Kawai and Takei carry out an exact WKB analysis of the Airy-type Schr\"{o}dinger equation
 \begin{equation}
@@
 \end{equation}
-\begin{revised}in the $\eta \to \infty$ limit\end{revised}.
+in the $\eta \to \infty$ limit.
 They define $\psi_B(x, y)$ as the inverse Laplace transform of $\psi(x, \eta)$ with respect to $\eta$.
@@
 \end{align*}
-where $s=t/2+1/2$. \begin{revised}We found the same hypergeometric functions in the position domain while solving the Airy equation
+where $s=t/2+1/2$. We found the same hypergeometric functions in the position domain while solving the Airy equation
 \begin{equation}
@@
 Although the two equations look closely related, and they are equivalent under the change of coordinates $w=x\eta^{2/3}$, they differ in an important way.
-The Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$, the conjugate variable of $t$, while the Borel transform of $f(w)$ is computed with respect to $w$.\end{revised} We need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
-
-\begin{revised}To do this, first\end{revised} notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
+The Borel transform of $\psi$ is computed with respect to $\frac{2}{3}\eta x^{3/2}$, the conjugate variable of $t$, while the Borel transform of $f(w)$ is computed with respect to $w$.
+We need to find a different change of coordinates to explain why the Borel transforms of $\psi(x,\eta)$ and $f(w)$ are given by the same hypergeometric function.
+
+To do this, first notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
 \begin{align*}
@@
 \end{align*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$.
-Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ \begin{revised}satisfies\end{revised}
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ satisfies
 \begin{equation}

### 2024-09-19 sima/reg-sing-volterra_sima.tex
change notation for convolution, dropping the "prime" and "double prime" notation
Format for print

@@
-\documentclass[review]{siamart220329}
+\documentclass[final]{siamart220329}
 
@@
 % list formatting
+\setlist[itemize]{topsep=3mm, itemsep=1.8mm, parsep=1.2mm}
 \newlist{conditions}{itemize}{1}
-\setlist[conditions]{leftmargin=26mm, rightmargin=12mm}
+\setlist[conditions]{leftmargin=26mm, rightmargin=12mm, topsep=2.5mm, itemsep=1.8mm, parsep=1.2mm}
 \makeatletter
@@
 \newif\ifhighlightrevs
-\highlightrevstrue
+\highlightrevsfalse
 \ifhighlightrevs
@@
 % notation change highlighting
-\newif\ifhighlightnewnotation
-\highlightnewnotationtrue
-\ifhighlightnewnotation
-\newenvironment{newnot}{\color{orange}}{\color{black}}
-\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
-\newenvironment{oldnot}{\color{cyan}}{\color{black}}
-\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
-\else
-\newenvironment{newnot}{}{}
-\newenvironment{oldnot}{}{}
-\newcommand{\newnottext}[1]{#1}
-\fi
+%%\newif\ifhighlightnewnotation
+%%\highlightnewnotationfalse
+%%\ifhighlightnewnotation
+%%\newenvironment{newnot}{\color{orange}}{\color{black}}
+%%\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
+%%\newenvironment{oldnot}{\color{cyan}}{\color{black}}
+%%\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
+%%\else
+%%\newenvironment{newnot}{}{}
+%%\newenvironment{oldnot}{}{}
+%%\newcommand{\newnottext}[1]{#1}
+%%\fi
 
@@
 For the applications we have in mind, $\domain$ typically resembles the set pictured below.
+\vspace{2mm}
+
 \begin{center}
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.92]
 \newcommand{\spill}{4}
@@
 \begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
-First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion
+\[\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)\]
+given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
 Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
@@
 \end{align*}
-Now we expand $Q$ around $-\alpha$, using the decomposition $Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta)$ to split up the last term of the expression above:
-\begin{equation}\label{eqn:split-numerator}
--\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
-\end{equation}
+Now we expand $Q$ around $-\alpha$, using the decomposition
+\[ Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta) \]
+to split up the last term of the expression above:
+\begin{multline}\label{eqn:split-numerator}
+-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \\
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
+\end{multline}
 First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from equation~\eqref{eqn:split-numerator} that
@@
 \begin{align*}
-\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
+\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\ & \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\
+& \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
 \end{align*}

### 2024-10-03 borel-regularity.tex
Correct sign error in Airy example
Also, work on convolution argument.

@@
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
-of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
+of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Definition~\ref{def:H_hat}.
 \end{theorem}
@@
 %
-The examples we study all involve {\em resurgent functions} in the position domain. \color{cyan}
-    The theory of resurgence, introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}, studies the analytic properties of the Borel transform of divergent series in the frequency domain.
-In a nutshell it provides an effective tool to compute subleading order contributions and occasionally leads to the resummation of the original divergent series.
-\color{black} \begin{todo}[Say a tiny bit about what resurgence does or is good for.]\end{todo} The theory of resurgence has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+The examples we study all involve {\em resurgent functions} in the position domain.
+\begin{revised}The theory of resurgence, introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}, describes divergent series in the frequency domain in terms of the analytic properties of their Borel transforms.
+Resurgent analysis is an effective tool for computing ``subleading contributions'' in perturbation theory, and it occasionally leads to the resummation of the original divergent series.
+It\end{revised} has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+
 Geometric arguments show that when a thimble integral has a holomorphic Morse function in the exponent, as we have in at least some of our examples, the corresponding function on the position domain is always resurgent~\cite{Maxim_slide_ERC}\cite[Section 6.2]{kontsevich2022analyticity}.
@@
 %
-\begin{todo}[Add the notation for integrals. Reference regular singular Volterra paper, and also more or less copy its notation description.]\end{todo}
+\begin{revised}
+We will also follow the convention of~\cite{reg-sing-volterra} for integrals. 
+\begin{notation*}
+When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}.
+On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.
+These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$.
+In the integral
+\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta\,, \]
+notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
+
+Sometimes, in expressions like
+\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\;d\zeta(a')\,, \]
+it is useful to give a name $a'$ to the point moving along the integration path.
+In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.
+\end{notation*}
+%    
+\end{revised}
+%
 \subsection{Acknowledgements}
@@
 %
-The study of irregular singular differential equations on complex domains has a long history, and interesting phenoma distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behavior that changes sharpy from from direction to the next.
+The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones.
+Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behavior that changes sharply from from direction to the next.
 Formally, this behavior is captured in a {\em formal integral} solution: an expression
@@
 
-Although it is not contructive, the M.A.E.T.
+Although it is not constructive, the M.A.E.T.
 guarantees the existence of a frame of analytic solutions asymptotic to Poincar\'{e}'s formal ones~\cite[Chapter~14]{balser}.
@@
 
-To formulate the Riemann--Hilbert problem, we fix the asymptotic behvaiour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray.
-A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescirbed asymptotics and discontinuities.
+To formulate the Riemann--Hilbert problem, we fix the asymptotic behaviour of the frame of solutions at $z = 0$ and $z = \infty$, and we also fix its discontinuities---the Stokes data prescribing how the frame jumps across each Stokes ray.
+A solution is then given by a piecewise analytic function which is holomorphic away from the Stokes rays and has the prescribed asymptotics and discontinuities.
 
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional alegbraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals \cite{deligne2007singularites,Maxim_lectures}.\footnote{In particular, they find application in mirror symmetry for Fano varieties as they encode the Gromov--Witten invariants.
-\begin{todo}[\textbf{V} Add references---Maxim's mirror symmetry talk, Varchenko.]\end{todo}}
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional algebraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals \cite{deligne2007singularites,Maxim_lectures}.
 \subsubsection{Thimble integrals in physics}
@@
 For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\cite{rainbows+glories}.
-\begin{todo}The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model'' [Knoll--Schaeffer].
-[This inspired Voros's work in ``The return of the quartic oscillator'']\end{todo} In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities.
+The formalism of wave optics can also be applied to the scattering of quantum particles---for example, in the ``nuclear optical model''~\cite{nuclear-optical, nuclear-mie}.
+Knoll and Schaeffer's use of thimble integrals to describe nuclear scattering eigenstates~\cite{semiclass-scat} inspired Voros to find the energy eigenstates of the quartic oscillator by resumming the asymptotic series of thimble integrals~\cite{quartic-return}.
+
+In the path integral picture of quantum mechanics, which draws inspiration from wave optics, infinite-dimensional thimble integrals are supposed to give the expectation values of observable quantities.
 In this context, the integral's formal asymptotic expansion is often better-defined than the integral itself, so physicists use Borel summation, resurgence, and related techniques to assign the integral a value.
@@
 Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
-Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimesion~\cite{gukov-marino-purtrov-resurgence,Witten}.
+Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}.
 Other examples can be found in~\cite{costin_kruskal,Garoufalidis--CS,GTM--CS,GGM,dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua,Berry_Howls,Berry1991,Howls97,Howls,pham1988resurgence,Unsal--resurgence-gauge}.
-\begin{todo}[\textbf{V} Is it true that all thimble integrals describes instantions?
-Can we have (higher dimensional) thimble integrals describing renormalons?]\end{todo}
 %
@@
 For one dimensional thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
-More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent developement~\cite{kontsevich2024holomorphic}).
+More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent development~\cite{kontsevich2024holomorphic}).
 %
@@
 The integral contains a hint about where to find this analytic object: the thimble itself, which is a real-analytic submanifold of a complex manifold.
-When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula} to turn it into a function whose Laplce transform is the thimble integral.
+When the thimble is one-dimensional, we can use the well-known formula in Lemma~\ref{lem:thimble_proj_formula} to turn it into a function whose Laplace transform is the thimble integral.
 This formula generalizes to higher-dimensional thimbles~\cite{pham} and thimbles based at degenerate critical points~\cite[Section 1.2.2]{mistegard_phdthesis}.
@@
 \end{itemize}
-For any $\sigma > -1$, the conditions on $\phi$ are satisfied by all of the functions in the spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ introduced in \cite{reg-sing-volterra}.
+For any $\sigma > -1$, the conditions on $\phi$ are satisfied by all of the functions in the spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ introduced in \cite[Definition~2.3]{reg-sing-volterra}.
 Here, the domain $\Omega_\alpha$ must contain the ray $\mathcal{J}_{\zeta, \alpha}^\theta$, and the norm $\|\cdot\|_{\sigma, \Lambda}$ is taken with respect to $\zeta = \alpha$.
+
+\begin{revised}
+We recall the definition of $\singexp{\sigma}{\Lambda}(\Omega)$ below. Let $\holo(\Omega)$ denote the space of holomorphic functions on the domain $\Omega$. 
+\begin{definition}\label{def:HL_inf}
+For any $\sigma, \Lambda \in \R$, let
+\[ \singexp{\sigma}{\Lambda}(\Omega) \subset \holo(\Omega) \]
+be the subspace consisting of functions $f$ with $|f| \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\Omega$, equipped with the norm
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]       
+\end{definition} 
+\end{revised}
 \subsubsection{The Laplace transform over a branch point}
@@
 \end{center}
+\begin{revised}
+\begin{definition}\label{def:H_hat}
 Let $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ be the space of holomorphic functions $\Phi$ on $\widehat{\Omega}_\alpha^\Lambda$ with $|\Phi| \lesssim \Delta^\sigma$, where $\Delta$ is the function that measures distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
 The norm $\|\Phi\|_{\sigma, \Lambda} = \sup_{\widehat{\Omega}_\alpha^\Lambda} \Delta^{-\sigma} |\Phi|$ turns $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ into a Banach space.
+\end{definition}    
+\end{revised}
 \begin{todo}[Explain more why we write in terms of the distance function $\Delta$]\end{todo}
-
+\begin{revised}
 To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$.
 Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
-\begin{todo}[\textbf{A} Put this definition into its own block]\end{todo}
+\end{revised}
 \begin{todo}\par
-[Cite \cite{sternin1995borel} better for the theorem.
-Note that these results don't depend on which cotangent fiber we're mapping into.
-$\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
+[Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
 \end{todo}
 %
-\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
+\begin{prop}[Following~\cite{sternin1995borel}]\label{prop:laplace-cont}
 Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-\begin{todo}[\textbf{A} Correct proof, and possibly remove constant] [\textbf{V} read it]\end{todo} \begin{old}Let $\Omega_\alpha$ be an open sector of the kind described in Proposition~\ref{prop:laplace-cont},\end{old} \begin{revised}Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$,\end{revised} and let $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ be the open sector created by cutting a sector of angle $\varepsilon > 0$ off each edge of $\Omega_\alpha$.
-\begin{old}Choose any $\Lambda' > \Lambda$.\end{old} \begin{revised}Let $\Lambda' = \Lambda / \cos(\Theta)$.\end{revised} Under the conditions of Proposition~\ref{prop:laplace-cont}, the Laplace transform
+Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$, and let $\Lambda' = \Lambda / \cos(\Theta)$.
+Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
 \[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
@@
 \[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
+Here, $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ is the open sector created by cutting a sector of angle $\varepsilon$ off each edge of $\Omega_\alpha$.
 \end{prop}
 \begin{proof}
-\begin{revised}The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc.
+The boundary of $\widehat{\Omega}_\alpha^\Lambda$ consists of two rays connected by a circular arc.
 Extend the rays until they meet, forming the boundary of a sector with opening angle $\pi - \Theta$.
 Expand that sector by angle $\varepsilon/2$ on both sides.
-The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.\end{revised}\begin{old}Define the sector $\Omega_\alpha^{\varepsilon/2} \subset \Omega_\alpha$ similarly to $\Omega_\alpha^\varepsilon$.
-Choosing some $\Lambda' > \Lambda$, let $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'} \subset \widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda'$ over all angles $\theta$ in the opening of $\Omega_\alpha^{\varepsilon/2}$.
-%
-The boundary of $\widehat{\Omega}_\alpha^{\varepsilon/2, \Lambda'}$ forms a path $\mathcal{C}$, which we orient so that the boundary of $\widehat{\Omega}_\alpha^\Lambda$ is on its left.\end{old}
+The edges of the expanded sector form a path $\mathcal{C}$ within $\widehat{\Omega}_\alpha^\Lambda$, as shown in Figure~\ref{fig:ref-path}.
 \begin{center}
@@
 \end{center}
-\begin{old}Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.\end{old} \begin{revised}The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
+Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
 Parameterize it using the arc length parameter $t$ which is zero where the rays meet.
@@
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
-\begin{todo}[Justify bound and add pictures.]\end{todo}\end{revised}
+\begin{todo}[Justify bound and add pictures.]\end{todo}
 
@@
 \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
-& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised} \|\Phi\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \begin{revised}\big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\end{revised}\,dt,
+& \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
 \end{align*}
@@
 \begin{align*}
-\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|}\begin{revised}\,|s|^{-\sigma}\end{revised}\,\frac{ds}{\sin(\varepsilon/2)} \\
-& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\begin{revised}\,s^{-\sigma}\end{revised}\,ds \\
-& \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\begin{revised}\,s^{-\sigma}\end{revised}\,ds
-\end{align*}
-\textcolor{red}{I don't see what changed in the last step}
-
+\left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|}\,|s|^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\,s^{-\sigma}\,ds
+\end{align*}
 using the new parameter $s = \sin(\varepsilon/2)\,t$.
@@
 \end{center}
-commutes, where $\mathsf{T}_{-\alpha}$ denotes traslation by $-\alpha$.
+commutes, where $\mathsf{T}_{-\alpha}$ denotes translation by $-\alpha$.
 Notice that $\laplace_{\zeta, 0}$ and $\laplace_{\zeta, \alpha}$ produce functions on the fiber $T^*_{\zeta = 0}B$, while $\laplace_{\zeta_\alpha, 0}$ produces functions on the fiber $T^*_{\zeta = \alpha}B$, so this argument depends on the fact that $z$ is defined almost globally $T^*B$.
@@
 This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-\begin{old}Since we will define the convolution product in terms of an integral along a path in $B \times B$, we must first introduce notation to help us express the integrand.
-\begin{notation}\label{notn:prod}
-The product space $B \times B$ comes with projection maps $\pi', \pi'' \maps B \times B \to B$ onto the first and second factors, respectively.
-Given a function $\phi$ on $B$, we denote $\phi \circ \pi'$ by $\phi'$ and $\phi \circ \pi''$ by $\phi''$.
-\end{notation}
-\end{old}
 \begin{definition}\label{def:convolution}
@@
 The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
-\begin{revised}
 \begin{equation}%%\label{eq:convolution_def}
@@
 \end{equation}
-\end{revised}
-\begin{old}
-\begin{equation}%%\label{eq:convolution_def}
-\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}'(\zeta)\times\mathcal{S}''(\zeta)\\ \zeta'+\zeta''=\zeta}} \phi' \psi'' d\zeta',
-\end{equation}
-\end{old}
-\begin{old}where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$, and $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta-\alpha$ to $\zeta''=0$.\end{old}
-\begin{revised}where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.\end{revised}
+where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
 \end{definition}
@@
 \begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-\begin{old}
-   \begin{align*}
-       \phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta_\alpha}} \phi'\,\psi''\,d\zeta'\\
-       &=\zeta_\alpha\,\int_0^1 \phi' \psi''\,ds\,,
-   \end{align*}
-where $\zeta'=s\zeta_\alpha$ and consequently $\zeta''=\zeta_\alpha (1-s)$.
-\end{old}
 \begin{revised}
@@
 \begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
-\begin{old}
-\begin{align*}
-   \big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi'|\,|\psi''|\\
-   &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
-   & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}
-\end{align*}
-\end{old}
 \begin{revised}
@@
 \end{align*}    
-\end{revised}
-\begin{old}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi' \psi''$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi' \psi''$ is integrable over the interval $s \in [0, 1]$.\end{old}
-\begin{revised}Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
 This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}
@@
 Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
-\begin{old}
-     \begin{align*}
-       \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
-       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi' \psi''\,ds \\
-       &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi' \psi''\,ds 
-   \end{align*}
-   \end{old}
 \begin{revised}
@@
 by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
-   \begin{old}
-   \begin{align*}
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi' \psi'' \\
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta'',0}}d\zeta''\,\frac{\zeta''}{(1-s)^2}\,e^{-z\zeta''} e^{-z\zeta'' \frac{s}{1-s}} \phi' \psi'' 
-   \end{align*}
-   \end{old}
 \begin{revised}
@@
 \end{revised}
-   \begin{old}
-   Setting $t=\zeta''\frac{s}{1-s}$ we find
-    \begin{align*}
-        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi''\,\int_0^1 ds\,\frac{\zeta''}{(1-s)^2}e^{-z\zeta'' \frac{s}{1-s}} \phi'\\
-        &=\int_{\mathcal{J}_{\zeta'',0}}d\zeta'' \,e^{-z\zeta''}  \psi'' \,\int_{\mathcal{J}_{t,0}} dt\, e^{-zt} \phi\\
-   \end{align*}
-     where as $s$ varies in $[0,1]$ we get that $t$ follows the ray $\mathcal{J}_{t,0}$. 
-   \end{old}
 \begin{revised}
@@
 \end{revised}
-
 \end{proof}
-More generally we can show that the product of two Laplace transforms based at different points is the Laplce transform of the convolution.
+More generally we can show that the product of two Laplace transforms based at different points is the Laplace transform of the convolution.
 \begin{prop}
@@
 \end{todo}
-\begin{old}
-  Notice that the convolution product can be rewritten by introducing the coordinates $\eta'=\zeta'-\beta$ and $\eta''=\zeta''+\beta$
-   \begin{align*}
-       \phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}} \phi'\,\psi''\,d\zeta'\\
-       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\,,
-   \end{align*}
-   where $\mathcal{S}'(\eta)$ is the line segment from $\eta'=\alpha$ to $\eta'=\zeta_\beta$ and simlarly, $\mathcal{S}''(\eta)$ is the line segment from $\eta''=\zeta_\alpha$ to $\eta''=\beta$.
-\begin{todo}\textbf{V} [explain why this choice of coords is better than $\eta'$ and $\eta''$]\end{todo} Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution
-    \begin{align*}
-       \phi \ast_{\zeta, \alpha+\beta} \psi
-       &=\int_{\substack{\mathcal{S}'(\eta) \times \mathcal{S}''(\eta) \\ \eta' + \eta'' = \zeta}} \phi'\,\psi''\,d\eta'\\
-       &=\zeta_{\alpha+\beta}\,\int_0^1 \phi' \psi''\,ds\,,
-   \end{align*}
-   \begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\eta'=(1-s)\alpha+s\zeta_\beta$ and consequently $\eta''=\beta s+(1-s)\zeta_\alpha$.
-Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
-     \begin{align*}
-       \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
-       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi' \psi''\,ds \\
-       &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi' \psi''\,ds
-   \end{align*}
-   by exchanging the order of integration we find 
-   \begin{align*}
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\alpha(1-s)+s\zeta_\beta)} e^{-z(\beta s+(1-s)\zeta_\alpha)} \phi' \psi'' \\
-        &=\int_0^1 ds\,\int_{\mathcal{J}_{\eta'',\beta}}d\eta''\,\frac{\eta''}{(1-s)^2}\,e^{-z\eta''} (\eta''-\beta) e^{-z( (\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi' \psi''\,,
-   \end{align*}
-   where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\eta''}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\eta''-\beta}{1-s}$.
-Then, exchanging one more time the order of integration we get
-    \begin{align*}
-        &=\int_{\mathcal{J}_{\eta'',\beta}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_0^1 ds\,\frac{\eta''-\beta}{(1-s)^2}e^{-z((\eta''-\beta) \frac{s}{1-s}+\alpha)} \phi'\\
-        &=\int_{\mathcal{J}_{\eta'',\beta}}d\eta'' \,e^{-z\eta''}  \psi'' \,\int_{\mathcal{J}_{t,\alpha}} dt\, e^{-zt} \phi\\
-   \end{align*}
-   where we have introduced the coordinate $t=(\eta''-\beta)\frac{s}{1-s}+\alpha$ which mooves along the ray $\mathcal{J}_{t,\alpha}$ as $s$ varies in $[0,1]$.
-\begin{todo}[Check claim: as coordinates on the position domain, $t = \eta'$.
-If true, clarify argument.]\end{todo}
-\end{old}
+\color{violet}
+In the convolution integral, $a$ and $a'$ move so that $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$ while $\zeta(a')$ goes from $\zeta_{\alpha+\beta}$ to $0$.
+
+\begin{align*}
+    \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=\int_{\mathcal{J}_{\zeta,\alpha+\beta}}d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\, \psi(a')\, d\zeta(a)
+\end{align*}
+
+Equivalently, $a$ and $a'$ move so that $\zeta_{\textcolor{magenta}{\alpha}}(a)$ runs from $\zeta_{\alpha+\beta}$ to $0$ while $\zeta_{\textcolor{magenta}{\beta}}(a')$ goes from $\zeta$ to $0$.
+In particular, we introduce the parameter $s\in [0,1]$ so that $\zeta(a)=(1-s)(\alpha+\beta)+s\zeta-\beta$ and $\zeta(a')=(1-s)\zeta+\beta$.
+\color{black}
 \begin{revised}
@@
 \end{align*}
-where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and simlarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$.
+where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and similarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$.
 This change of coordinates simplifies our computations by showing how the convolution product depends on the base points of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.
@@
 %
-\subsubsection*{The Borel transform as algebra isomomrphism}
+\subsubsection*{The Borel transform as algebra isomorphism}
 %
@@
 \end{align*}
-Furthemore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
+Furthermore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
 \[\frac{\zeta^n}{n!}\ast_{\zeta}\delta\defeq\frac{\zeta^n}{n!}\,,\]
@@
 
-Similarly, we can extend the deifnition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
+Similarly, we can extend the definition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
 \begin{equation}
@@
 Then, the unit for $\ast_{\zeta_\alpha,0}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha,0}\frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
-We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed wiht the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
+We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
 \begin{prop}
@@
 \begin{remark}
-If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, repsectively, as defined in Definition~\ref{def:convolution}.
+If $\series{\phi}, \series{\psi}$ are convergent formal power series in $\C\{\zeta\}$, their convolution product is convergent too, and its sum is the convolution of the sums of $\series{\phi}, \series{\psi}$, respectively, as defined in Definition~\ref{def:convolution}.
 We will discuss it in Section~\ref{sec:Borel-gevrey}.
@@
 In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series.
-Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ edowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
+Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ endowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
 \begin{verify}
@@
 A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
-This operator is bounderd, so its kernel is closed.
+This operator is bounded, so its kernel is closed.
 \end{proof}
@@
 For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-\begin{old}
-\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi] \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}'(\zeta)} \big(\zeta-\zeta'\big)^{-\nu} \phi' \,d\zeta', \]
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=\alpha$ to $\zeta'=\zeta$.
-
-Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ along our integration path.
-\end{old}
-\begin{revised}
+%
 %%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
@@
 %% Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta(a') = \zeta - \zeta(a)$ along our integration path.
-\end{revised}%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
+
+%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
 Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
@@
 Results \ref{res:frac-deriv} and \ref{res:frac-int} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
-\begin{old}
-\begin{align*}
-z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\Big] \laplace_{\zeta,0}\phi\\
-&=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\Big] \\
-&=\laplace_{\zeta,0} \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}}\frac{(\zeta'')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
-&=\laplace_{\zeta,0} \int_{\substack{\mathcal{S}'(\zeta) \times \mathcal{S}''(\zeta) \\ \zeta' + \zeta'' = \zeta}}\frac{(\zeta-\zeta')^{-\tau-1}}{\Gamma(-\tau)} \phi' d\zeta'\\
-&=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi,
-\end{align*}
-where $\mathcal{S}'(\zeta)$ is the line segment from $\zeta'=0$ to $\zeta' = \zeta$, $\mathcal{S}''(\zeta)$ is the line segment from $\zeta''=\zeta$ to $\zeta''=0$, and we are taking advantage of the fact that $\zeta'' = \zeta - \zeta'$ on the integration path.
-Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:
-\begin{align*}
-    z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
-    &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
-    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
-\end{align*}
-Result~\ref{res:monom-mult} is also proven by repeated integration by parts, with the assumption that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ ensuring that the integral converges.
-        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
-This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
-Similarly, one can prove \emph{iii)}.
-\end{old}
 \begin{revised}
@@
 We will show that for any $\mu \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
-\begin{old}
-\begin{align*}
-\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta (\zeta-\zeta')^{-\mu} \frac{(\zeta')^k}{\Gamma(k+1)}\,d\zeta' \\
-& = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\mu-1)}}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\mu} t^k\,dt \\
-& = \frac{\zeta^{k-(\mu-1)}}{\Gamma\big(k-(\mu-1)+1\big)}
-\end{align*}
-\end{old}
 \begin{revised}
@@
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
-of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.\begin{todo} Cite the definition rather than the Section\end{todo}
+of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ in Definition~\ref{def:H_hat}.
 \end{theorem}
@@
 Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4 of \cite{reg-sing-volterra}.
-To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to expess $\psi_\alpha$ as the sum of a convergent power series.
+To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to express $\psi_\alpha$ as the sum of a convergent power series.
 We will do this by showing that $\psi_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha - 1}\,\mathcal{O}(\pi \Upsilon)$.
@@
 Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\zeta = \infty$, as shown in Figure~\ref{Fig:slit domain}.\end{revised}
-\begin{old}\par
-We can use the $1/2$ derivative formula~\eqref{eqn:formula--1/2} to see that the functions $\phi$ are all resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
-Let us say $\mathcal{J}_\alpha^\theta(\beta)$ is the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
-As long as this path avoids the critical values of $f$, it lifts uniquely along $f$ to a path $\mathcal{C}_a^\theta(\beta)$ in $X$.
-This lets us analytically continue $\int_{\mathcal{C}_a^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
-Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\infty$ (see Figure~\ref{Fig:slit domain}).
-\end{old}
 \begin{center}
@@
 \begin{revised}Initially, the function $\int_{\mathcal{C}_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_a(\zeta)$.
-Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to become singular is for something to go wrong with the hotmotopy of $\mathcal{C}_a(\zeta)$, which can only happen at the critical values of $f$.
+Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to become singular is for something to go wrong with the homotopy of $\mathcal{C}_a(\zeta)$, which can only happen at the critical values of $f$.
 Therefore, $\mathcal{C}_a(\zeta)$ is endlessly analytically continuable away from the critical values of $f$.
@@
 
-\begin{todo}[This paragraph is marked as revised]\end{todo} Initially, the function $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}^\theta_a(\zeta)$.
-Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to be singular is for something to go wrong with the hotmotopy of $\mathcal{C}^\theta_a(\zeta)$.
-At a critical point of $f$, the ends of the homotoped path $\mathcal{C}^\theta_a(\zeta)$ come together, telling us that \begin{todo}[\textbf{A} \textbf{V} \ldots]\end{todo}
 \end{old}
@@
 \subsection{Specializing from the Airy--Lucas example}\label{sec:spec-to-airy}
-\begin{revised}
 \subsubsection{Motivation}
@@
 Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing
-\[ \Ai(y) = \tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+\[ \Ai(y) = -\tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
 where
 \begin{equation}\label{integral:mod-bessel-airy}
-K(z) = i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du
+K(z) = -i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du
 \end{equation}
@@
 %
-\end{revised}
-%
 \subsubsection{Asymptotic analysis}\label{sec:asympt-airy}
-\begin{revised}
 %
@@
 This argument is just as simple in general as it is in the Airy case, so we will not repeat it.
-\end{revised}
 %
@@
 %
-\begin{revised}
 Switching to the translation coordinate $\zeta_1$ defined by $\zeta = 1 + \zeta_1$, and then to the rescaled coordinate $\xi_1$ defined by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
@@
 where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
-\end{revised}
 %
 \subsubsection{Focus on $\zeta = -1$}\label{neg-root}
-%
-\begin{revised}
 We now switch to the translation coordinate $\zeta_{-1}$ defined by $\zeta = -1 + \zeta_{-1}$.
@@
 where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
-\end{revised}
 %
@@
 %
-\begin{revised}
 We can verify the conclusions of Section~\ref{bessel-regularity-AL} in the Airy case using our explicit expressions for the formal power series $\tilde{W}_\alpha$ and the functions $v_\alpha$.
@@
 Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.
-\end{revised}
 %
@@
 %
-\begin{revised}
 In Section~\ref{contour-argument-AL}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy--Lucas functions.
@@
 The critical point splits $\mathcal{C}^\theta_1$ into two pieces: the incoming branch, where the orientation of the thimble runs toward the critical point, and the outgoing branch, where the orientation points away.
-Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get \begin{todo}[Check sign of first line]\end{todo}
+Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get
 \begin{verify}
@@
 \[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
-\end{revised}
 %
@@
 %
-\begin{revised}
 In Section~\ref{contour-argument-airy}, we specialized the reasoning behind Lemma~\ref{lem:thimble_proj_formula-proof} to the case of the Airy function.
@@
 matching the conclusion of Section~\ref{contour-argument-airy}.
-\end{revised}
-\begin{old}
-\subsubsection{Another solution}
-\begin{todo}\par\textbf{[From the really old version]}\end{todo} Section~\ref{contour-argument} associates the solution $K$ of equation~\eqref{eqn:mod-bessel} with the solution $g_1$ of equation~\eqref{diff-eq:hypergeom-pos}, which contributes the pole at $\zeta = 1$ of
-\[ \frac{du}{d\zeta} = \frac{1}{4u^2 - 1} = \tfrac{1}{3}(g_1 + g_{-1}). \]
-The solution $g_{-1}$, which contributes the pole at $\zeta = -1$, is associated with another solution of equation~\eqref{eqn:reg-mod-bessel}.
-To express this other solution as a Laplace transform, following the method of Section~\ref{contour-argument}, we would use the solution
-\[ v_{-1} = (1-\xi)^{-1/2} \,\, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \]
-of equation~\eqref{diff-eq:spatial-mod-bessel}, given by formula~15.10.14 from \cite{dlmf}. This is the only solution, up to scale, which has a fractional power singularity at $\zeta = -1$.
-
-In summary, the thimble projection technique of solving equation~\eqref{eqn:reg-mod-bessel} is associated with the basis
-\begin{align*}
-g_{1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; \xi\big) \\
-g_{-1} & = {}_2F_1\big(\tfrac{2}{3}, \tfrac{4}{3}; \tfrac{3}{2}; 1-\xi\big)
-\end{align*}
-of solutions for equation~\eqref{diff-eq:spatial-mod-bessel}, given by formulas 15.10.11 and 15.10.13 from \cite{dlmf}.
-These solutions contribute the poles at $\xi = 1$ and $\xi = 0$, respectively, of a generic solution.
-
-The Laplace transformation method of solving equation~\eqref{eqn:reg-mod-bessel}, on the other hand, is associated with the basis
-\begin{alignat*}{2}
-v_{-1} &\;=\;& (1-\xi)^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; 1-\xi\big) \\
-v_1 &\;=\:& \xi^{-1/2} & \, {}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; \xi\big)
-\end{alignat*}
-given by formulas 15.10.14 and 15.10.12 from \cite{dlmf}. These solutions, up to scale, are the only ones with fractional power singularities.
-
-Identities 15.10.18, and 15.10.22 from \cite{dlmf} give the change of basis
-\begin{alignat*}{3}
-v_{-1} &\;=\;&\tfrac{1}{\sqrt{3}}\,g_{-1} &\;+\;& \tfrac{1}{2}\,v_1 \\
-v_1 &\;=\;& \tfrac{1}{\sqrt{3}}\,g_{1} &\;+\;& \tfrac{1}{2}\,v_{-1}.
-\end{alignat*}
-Summing these identities, we see that
-\[ g_1 + g_{-1} = \tfrac{\sqrt{3}}{2}\,(f_1 + f_{-1}), \]
-giving the alternate decomposition
-\[ \frac{du}{d\zeta} = \tfrac{1}{2\sqrt{3}}\,(f_1 + f_{-1}). \]
-%
-\end{old}
-% \subsubsection{An eye on resurgence}\label{apx:eye-res-airy}
-% \textcolor{orange}{[Add link to general references in intro].} Resurgent functions in the position domain are characterized by being ``endlessly analytically continuable'' away from their singularities~\textcolor{magenta}{\cite[Section~1.2.2]{intro-to-ecalle}\{this paper only defines resurgent functions in the frequency domain\}\{For definition in the position domain, cite \S 6.1 of Mitschi and Sauzin~\cite{diverg-resurg-i}\}}.
-\textcolor{MediumSeaGreen}{[Focus on endlessly continuable functions instead?
-See~[Section~2, ``Variations on the resurgence of the gamma function''.]} \textcolor{red}{They have the special property that by studying their analytic continuation around one singularity, we can typically discover the germ of another singularity.} \textcolor{RoyalBlue}{They have the very special property that by studying one germ, we can typically reconstruct the others by looking at the behavior near the singular points.} \textcolor{MediumSeaGreen}{[They are ``self-reproducing'' in a certain remarkable way involving holonomy around singularities, as we will see in the example below\ldots]} A prototypical class of resurgent functions is the so-called simple resurgent functions~\textcolor{magenta}{\cite[Section~1.2.3]{intro-to-ecalle}\{oops, this source defines simple resurgent functions in the frequency domain\}}.
-namely an \textcolor{Maroon}{[resurgent]} analytic function $\hat{\phi}$ in the position domain with singularities $\omega$ such that
-
-% \textcolor{Maroon}{[\ldots] resurgent function with the property that at each singularity $\omega$, we have an expansion of the form}
-% \begin{align*}
-%     \hat{\phi} = \frac{C_\omega}{\zeta_\omega}+\frac{S_\omega}{2\pi i} \log(\zeta_\omega)\,\series{\phi}_\omega + \text{ hol. funct.} \textcolor{Maroon}{[\text{convergent series in}\,\zeta_\omega]}
-% \end{align*}
-% where \textcolor{Maroon}{$\zeta = \omega + \zeta_\omega$, $\series{\phi}_\omega$ is a series in $\zeta_\omega$} $C_\omega, S_\omega$ are constants and $S_\omega$ is typically assumed to be integral (in a suitable normalization) and called the Stokes constant of the singularity $\omega$.
-The goal of resurgence is to investigate the location of the singularities together with their Stokes constants and the corresponding germs $\series{\phi}_\omega$.
-% %The main idea of resurgence is that studying the analytic continuation of $\series{\phi}_\omega$
-
-% Thimbles integrals are good candidates to understand the structure of resurgent functions; indeed the functions $\hat{\phi}_j$ in equation~\eqref{eqn:formula-proof} are resurgent.
-Their resurgent structure can be easily reconstructed: if $\nu$ is holomorphic, then $\hat{\phi}_j$ is singular at $\zeta_j=\alpha_k$ for $k\neq j$.
-Hence the set of singularities is given by the critical values of $f$.
-Then, the computation of the Stokes constants and of the other germs $\series{\phi}_k$ is done by studying $\hat{\phi}_j$ near its singular points.
-For example, for the Airy function, we can expand $\hat{\phi}_1$ near $\zeta=-1$:
-% \begin{align*}
-%     \hat{\phi}_1(\zeta-1)=\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1+\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2+\frac{7436429}{53747712}\zeta^3+\ldots\right)  +\text{ hol.
-funct.
-}
-% \end{align*}
-
-% Notice that $(1+\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2+\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor series of $\hat{\phi}_{-1}$ at the origin.
-So we see that expanding $\hat{\phi}_1$ at the singularity we see the germ of another singularity $\series{\phi}_{-1}$.
-Analogously, if we expand $\hat{\phi}_{-1}$ near $\zeta=1$ we find
-% \begin{align*}
-%     \hat{\phi}_{-1}(\zeta+1)=-\frac{36}{5\pi}\frac{1}{\zeta}+\frac{1}{2\pi}\log(\zeta) \left(1-\frac{77}{144}\zeta+\frac{17017}{62208}\zeta^2-\frac{7436429}{53747712}\zeta^3+\ldots\right) +\text{ hol.
-funct.
-}
-% \end{align*}
-% where the germ $(1-\tfrac{77}{144}\zeta+\tfrac{17017}{62208}\zeta^2-\tfrac{7436429}{53747712}\zeta^3+\ldots)$ is the Taylor expansion of $\hat{\phi}_1$ at the origin. 
-% From these expressions, we also noticed that $\hat{\phi}_i$ are simple resurgent functions.   
 %

### 2024-10-03 borel-regularity.tex
Write up 2d integral argument for convolution result

@@
 \newif\ifshowdraft
-\showdraftfalse
+\showdrafttrue
 \ifshowdraft
@@
 Then
-\begin{equation}
+\begin{equation*}
 \laplace_{\zeta_\alpha,0}[\phi\ast_{\zeta_\alpha,0}\psi]=\laplace_{\zeta_\alpha,0}[\phi]\,\laplace_{\zeta_\alpha,0}[\psi]\,.
-\end{equation}
+\end{equation*}
 \end{prop}
@@
 Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 
-\begin{equation}
-    \laplace_{\zeta,\alpha+\beta}[\phi\ast_{\zeta,\alpha+\beta}\psi]=\laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
+\begin{equation}\label{eqn:gen-laplace-convol}
+\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha+\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
 \end{equation}    
@@
 \end{todo}
+\begin{draft}
+The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
+\]
+In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta - (\alpha + \beta)$ to $0$.
+
+The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{M} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
+Thus, on $\mathcal{N}$, we have the identity
+\begin{align*}
+d\zeta(a) + d\zeta(a') & = d\zeta \\
+d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
+d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
+\end{align*}
+which we can substitute into the integral above to get
+\begin{align*}
+\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{M} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+& = \int_\mathcal{M} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+\end{align*}
+\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$.
+Something seems off here.
+The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$.
+At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.
+
+In my drawings, I assumed that the tip of the wedge $\mathcal{N}$ would be at the point where $\zeta(a) = \alpha$, $\zeta(a') = \beta$, and $\zeta = \alpha + \beta$.
+Now I'm skeptical about that.
+Is that point even in $\mathcal{N}$?
+If so, what distinguishes it from all the other points on the line $\zeta(a) + \zeta(a') = \alpha + \beta$?
+Since $\alpha$ and $\beta$ can vary without changing the left-hand side of equation~\eqref{eqn:gen-laplace-convol}, we must need to make a choice somewhere\ldots
+
+Maybe me actually need to change the statement? I think the argument might wrap up neatly if the convolution on the left-hand side were $\phi \ast_{\zeta_\alpha, \beta} \psi$ instead.
+\end{todo}
+\begin{align*}
+\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
+\end{align*}
+\end{draft}
+
 \color{violet}

### 2024-10-11 borel-regularity.tex
Write out new proposed convolution statement
Sketch new definition of convolution

@@
 \end{definition}
-The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.
-\begin{todo}[Is it clear the convolution is holomorphic?]\end{todo} On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
+\color{Turquoise}
+\begin{definition}\label{def:convolution}
+Let $\phi\in\singexpalg{\sigma}(\Omega_\alpha),\psi\in\singexpalg{\sigma'}(\Omega_\beta)$ .
+Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \gamma$.
+The convolution product $\phi\ast_{\zeta,\gamma}\psi$ is the function on $B$ defined by the integral
+\begin{equation}%%\label{eq:convolution_def}
+\phi \ast_{\zeta, \gamma} \psi \defeq \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta_\beta)\\ \zeta_\alpha(a)+\zeta_\beta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
+\end{equation}
+where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=\gamma$ to $\zeta_\alpha(a)=\zeta$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a')=\zeta-\gamma$ to $\zeta_\beta(a')=0$.
+\end{definition}
+\color{black}
+\begin{revised}
+\begin{lemma}
+Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$.
+The convolution $\phi\ast_{\zeta,\alpha+\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1 + \sigma + \sigma'$.
+\end{lemma}
+\begin{proof}
+\begin{align*}
+\left|\phi\ast_{\zeta,\alpha}\psi\right|&\le\int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
+& = \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|\,,
+\end{align*}
+where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a)=\zeta_\alpha$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta_\alpha$ to $\zeta(a')=0$.
+We introduce the variable $s\in[0,1]$ such that $\zeta_\alpha(a)=s\zeta_\alpha$ and $\zeta_\alpha(a')=(1-s)\zeta_\alpha$:
+\begin{align*}
+  \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|&= |\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds\,.
+\end{align*}
+Since $\phi$ and $\psi$ have bounded norms,
+\begin{align*}
+|\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_\alpha|^{1+\sigma+\sigma'}\int_0^1  |s|^{\sigma}e^{\Lambda s |\zeta_\alpha|}\,|1-s|^{\sigma'}e^{\Lambda' (1-s)|\zeta_\alpha|}\,ds\\
+&\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\int_0^1  s^{\sigma}\,(1-s)^{\sigma'}\,ds\\
+&=\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\,.
+\end{align*}
+\end{proof}
+\end{revised}
+\begin{old}
+The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.\end{old}
+
+On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
 The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
 \begin{prop}\label{prop:convolution_iso_laplace}
-\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined.
-Then
-\begin{equation*}
-\laplace_{\zeta_\alpha,0}[\phi\ast_{\zeta_\alpha,0}\psi]=\laplace_{\zeta_\alpha,0}[\phi]\,\laplace_{\zeta_\alpha,0}[\psi]\,.
-\end{equation*}
+\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} \begin{revised}For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have\end{revised} \begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined.
+Then\end{old}
+\begin{equation}\label{eqn:laplace-convol1}
+\laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
+\end{equation}
+\begin{todo}
+Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
+\end{todo}
 \end{prop}
 \begin{proof}
+\begin{revised}
+The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
+\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
+\]
+In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.
+
+The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
+\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
+Thus, on $\mathcal{N}$, we have the identity
+\begin{align*}
+d\zeta(a) + d\zeta(a') & = d\zeta \\
+d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
+d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
+\end{align*}
+which we can substitute into the integral above to get
+\begin{align*}
+\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+\end{align*}
+
+By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$.
+From the definitions of the paths $\mathcal{S}(\zeta)$ and $\mathcal{S}'(\zeta)$, it follows that the ranges of $\zeta(a)$ and $\zeta(a')$ on $\mathcal{N}$ are also both $[0, \infty)$.
+In fact, projection onto the $a$ and $a'$ factors of $B^3$ identifies $\mathcal{N}$ with $\mathcal{J}_{\zeta(a), 0} \times \mathcal{J}_{\zeta(a'), 0} \subset B^2$.
+We can therefore factorize the integral above using Fubini's theorem, yielding the desired identity:
+\begin{align*}
+\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+\end{align*}
+\end{revised}
+\begin{old}
 \begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-\begin{revised}
 \begin{align*}
@@
 where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
-\end{revised}
 First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
 \begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
-\begin{revised}
 \begin{align*}
@@
 Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.\end{revised}
+This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.
 %   
 Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
-\begin{revised}
 \begin{align*}
@@
 \end{align*}      
-\end{revised}
 by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
-\begin{revised}
 \begin{align*}
@@
 \end{align*}    
-\end{revised}
-\begin{revised}
 Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
@@
 where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
-\end{revised}
+\end{old}
 \end{proof}
@@
 \end{todo}
+\begin{revised}
+The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
+\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}}  \phi(a)\,\psi(a')\, d\zeta_\alpha(a)\,.
+\]
+In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta_\alpha)$ where $\zeta_\alpha(a)$ runs from $\beta$ to $\zeta_\alpha$, while $a'$ follows the straight path $\mathcal{S}'(\zeta_\alpha)$ where $\zeta_\alpha(a')$ runs from $\zeta_\alpha - \beta$ to $0$.
+\end{revised}
 \begin{draft}
@@
 The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
-\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{M} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
 The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
@@
 \begin{align*}
-\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{M} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
-& = \int_\mathcal{M} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
 \end{align*}
@@
 
-Maybe me actually need to change the statement? I think the argument might wrap up neatly if the convolution on the left-hand side were $\phi \ast_{\zeta_\alpha, \beta} \psi$ instead.
+Maybe we need to change the statement to
+\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,. \]
+I think the argument might wrap up neatly in that case.
 \end{todo}
@@
 
-In our treatmeant, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
+In our treatment, we will restrict the Borel transform to the space of $1$-Gevrey series and the Laplace transform to $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ with $\sigma>-1$ and $\Lambda>0$, for some domain $\Omega_\alpha$ as in Figure~\ref{fig:sectorial_domain-pos-fre}.
 \begin{definition}

### 2024-10-13 borel-regularity.tex
Change Lemma 3.10 after new definition of convolution

@@
 \begin{definition}\label{def:convolution}
-Let $\phi\in\singexpalg{\sigma}(\Omega_\alpha),\psi\in\singexpalg{\sigma'}(\Omega_\beta)$ .
-Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \gamma$.
-The convolution product $\phi\ast_{\zeta,\gamma}\psi$ is the function on $B$ defined by the integral
+Choose $\phi \in \singexpalg{\sigma}(\Omega_\alpha),\psi \in \singexpalg{\sigma'}(\Omega_\beta)$ \begin{todo}[refine]\end{todo}.
+Choose a translation coordinate $\zeta$ on $B$.
+The convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
 \begin{equation}%%\label{eq:convolution_def}
-\phi \ast_{\zeta, \gamma} \psi \defeq \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta_\beta)\\ \zeta_\alpha(a)+\zeta_\beta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
-\end{equation}
-where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=\gamma$ to $\zeta_\alpha(a)=\zeta$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a')=\zeta-\gamma$ to $\zeta_\beta(a')=0$.
+\phi \ast_{\zeta, \alpha, \beta} \psi \defeq \int_{\mathcal{S}_{\zeta, \alpha, \beta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
+\end{equation}
+where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path $[0, 1] \to B^2$ given by
+\begin{align*}
+\zeta_\alpha(a) & = t\zeta_{\alpha+\beta} \\
+\zeta_\beta(a') & = (1-t)\zeta_{\alpha+\beta}
+\end{align*}
+in terms of the standard coordinate $t$ on $[0, 1]$.
+
+%%line segment in $B^2$ where $\zeta_\alpha(a)$ goes from $0$ to $\zeta_{\alpha + \beta}$ and $\zeta_\beta(a')$ goes from $\zeta_{\alpha + \beta}$ to $0$ with $\zeta(a) + \zeta(a') = \zeta$ at all times.
+
+%%where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a) = \zeta_{\alpha + \beta}$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a') = \zeta_{\alpha + \beta}$ to $\zeta_\beta(a') = 0$.
 \end{definition}
@@
 Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$.
-The convolution $\phi\ast_{\zeta,\alpha+\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1 + \sigma + \sigma'$.
+The convolution $\phi\ast_{\zeta,\alpha,\beta}\psi$ belongs to $\singexp{\sigma''}{\Lambda''}(\Omega_{\alpha+\beta})$, where $\Lambda'' = \Lambda + \Lambda'$ and $\sigma'' = 1+\sigma+\sigma'$.
 \end{lemma}
@@
 \begin{align*}
-\left|\phi\ast_{\zeta,\alpha}\psi\right|&\le\int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
-& = \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|\,,
-\end{align*}
-where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a)=\zeta_\alpha$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta_\alpha$ to $\zeta(a')=0$.
-We introduce the variable $s\in[0,1]$ such that $\zeta_\alpha(a)=s\zeta_\alpha$ and $\zeta_\alpha(a')=(1-s)\zeta_\alpha$:
-\begin{align*}
-  \int_{\substack{\mathcal{S}(\zeta_\alpha)\times\mathcal{S}'(\zeta)\\ \zeta_\alpha(a)+\zeta(a')=\zeta_\alpha}} |\phi(a)|\,|\psi(a')|\,|d\zeta_\alpha(a)|&= |\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds\,.
-\end{align*}
+\left|\phi\ast_{\zeta,\alpha,\beta}\psi\right|&\le\int_{\mathcal{S}_{\zeta,\alpha,\beta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
+& = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}| dt\,,
+\end{align*}
+where we use $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$. 
 Since $\phi$ and $\psi$ have bounded norms,
 \begin{align*}
-|\zeta_\alpha|\int_0^1 |\phi(a)|\,|\psi(a')|\, ds&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_\alpha|^{1+\sigma+\sigma'}\int_0^1  |s|^{\sigma}e^{\Lambda s |\zeta_\alpha|}\,|1-s|^{\sigma'}e^{\Lambda' (1-s)|\zeta_\alpha|}\,ds\\
-&\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\int_0^1  s^{\sigma}\,(1-s)^{\sigma'}\,ds\\
-&=\lesssim |\zeta_\alpha| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_\alpha|}\,.
+|\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\, dt&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|^{1+\sigma+\sigma'}\int_0^1  |t|^{\sigma}e^{\Lambda t |\zeta_{\alpha+\beta}|}\,|1-t|^{\sigma'}e^{\Lambda' (1-t)|\zeta_{\alpha+\beta}|}\,dt\\
+&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\int_0^1  t^{\sigma}\,(1-t)^{\sigma'}\,dt\\
+&\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\,.
 \end{align*}

### 2024-10-15 borel-regularity.tex
Prove the convolution proposition using the new definition

@@
 This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-\begin{definition}\label{def:convolution}
-Let $\phi,\psi$ be two holomorphic functions on $B$.
+% \begin{definition}\label{def:convolution}
+% Let $\phi,\psi$ be two holomorphic functions on $B$.
 Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
 The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
-\begin{equation}%%\label{eq:convolution_def}
-\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
-\end{equation}
-where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
-\end{definition}
+% \begin{equation}%%\label{eq:convolution_def}
+% \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
+% \end{equation}
+% where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
+% \end{definition}
 \color{Turquoise}
@@
 in terms of the standard coordinate $t$ on $[0, 1]$.
-
-%%line segment in $B^2$ where $\zeta_\alpha(a)$ goes from $0$ to $\zeta_{\alpha + \beta}$ and $\zeta_\beta(a')$ goes from $\zeta_{\alpha + \beta}$ to $0$ with $\zeta(a) + \zeta(a') = \zeta$ at all times.
-
-%%where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a) = \zeta_{\alpha + \beta}$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a') = \zeta_{\alpha + \beta}$ to $\zeta_\beta(a') = 0$.
 \end{definition}
 \color{black}
+\begin{notation*}
+ When $\alpha=\beta$ we denote $\ast_{\zeta,\alpha,\beta}$ simply by $\ast_{\zeta,\alpha}$.
+For $\alpha=\beta=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$.
+\begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
+\end{notation*}
+
+%%line segment in $B^2$ where $\zeta_\alpha(a)$ goes from $0$ to $\zeta_{\alpha + \beta}$ and $\zeta_\beta(a')$ goes from $\zeta_{\alpha + \beta}$ to $0$ with $\zeta(a) + \zeta(a') = \zeta$ at all times.
+
+%%where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a) = \zeta_{\alpha + \beta}$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a') = \zeta_{\alpha + \beta}$ to $\zeta_\beta(a') = 0$.
 \begin{revised}
@@
 \left|\phi\ast_{\zeta,\alpha,\beta}\psi\right|&\le\int_{\mathcal{S}_{\zeta,\alpha,\beta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
-& = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}| dt\,,
+& = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}|\,dt\,,
 \end{align*}
@@
 \begin{align*}
-|\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\, dt&\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|^{1+\sigma+\sigma'}\int_0^1  |t|^{\sigma}e^{\Lambda t |\zeta_{\alpha+\beta}|}\,|1-t|^{\sigma'}e^{\Lambda' (1-t)|\zeta_{\alpha+\beta}|}\,dt\\
+|\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\,dt &\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|\int_0^1  |\zeta_\alpha(a)|^{\sigma}e^{\Lambda  |\zeta_{\alpha}(a)|}\,|\zeta_\beta(a')|^{\sigma'}e^{\Lambda' |\zeta_{\beta}(a')|}\,dt\\
+&= \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|^{1+\sigma+\sigma'}\int_0^1  |t|^{\sigma}e^{\Lambda t |\zeta_{\alpha+\beta}|}\,|1-t|^{\sigma'}e^{\Lambda' (1-t)|\zeta_{\alpha+\beta}|}\,dt\\
 &\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\int_0^1  t^{\sigma}\,(1-t)^{\sigma'}\,dt\\
@@
 The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.\end{old} 
-
-On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
-The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
-\begin{prop}\label{prop:convolution_iso_laplace}
-\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} \begin{revised}For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have\end{revised} \begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined.
-Then\end{old}
-\begin{equation}\label{eqn:laplace-convol1}
-\laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
-\end{equation}
-\begin{todo}
-Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
-\end{todo}
-\end{prop}
-\begin{proof}
-\begin{revised}
-The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
-\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
+% \begin{prop}\label{prop:convolution_iso_laplace}
+% For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have
+% \begin{equation}\label{eqn:laplace-convol1}
+% \laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
+% \end{equation}
+% \begin{todo}
+% Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
+% \end{todo}
+% \end{prop}
+% \begin{proof}
+% \begin{revised}
+% The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
+% \[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
 \]
-In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.
-
-The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
-\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
-The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
+% In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.
+
+% The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
+% \[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+% The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
 Thus, on $\mathcal{N}$, we have the identity
-\begin{align*}
-d\zeta(a) + d\zeta(a') & = d\zeta \\
-d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
-d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
-\end{align*}
-which we can substitute into the integral above to get
-\begin{align*}
-\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
-& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
-\end{align*}
-
-By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$.
+% \begin{align*}
+% d\zeta(a) + d\zeta(a') & = d\zeta \\
+% d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
+% d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
+% \end{align*}
+% which we can substitute into the integral above to get
+% \begin{align*}
+% \laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+% & = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+% \end{align*}
+
+% By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$.
 From the definitions of the paths $\mathcal{S}(\zeta)$ and $\mathcal{S}'(\zeta)$, it follows that the ranges of $\zeta(a)$ and $\zeta(a')$ on $\mathcal{N}$ are also both $[0, \infty)$.
@@
 We can therefore factorize the integral above using Fubini's theorem, yielding the desired identity:
-\begin{align*}
-\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
-\end{align*}
-\end{revised}
-\begin{old}
-\begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-\begin{align*}
-\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
-&=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
-\end{align*}
-where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
-First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
+% \begin{align*}
+% \laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
+% \end{align*}
+% \end{revised}
+% \begin{old}
+% \begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
+% \begin{align*}
+% \phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
+% &=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
+% \end{align*}
+% where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
+% First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
 \begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
-\begin{align*}
-\big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi(a)|\,|\psi(a')|\\
-&\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
-& \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}\,.
-\end{align*}    
-Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
+% \begin{align*}
+% \big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi(a)|\,|\psi(a')|\\
+% &\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
+% & \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}\,.
+% \end{align*}    
+% Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
 This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.
-%   
-Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
-\begin{align*}
-\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi(a) \psi(a')\,ds \\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi(a) \psi(a')\,ds 
-\end{align*}      
-by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
-\begin{align*}
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a')\,\frac{\zeta_\alpha(a')}{(1-s)^2}\,e^{-z\zeta_\alpha(a')} e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
-\end{align*}    
-Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
-\begin{align*}
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta_\alpha(a')}{(1-s)^2}e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta_\alpha,0}} d\zeta_\alpha(a)\, e^{-z\zeta_\alpha(a)} \phi(a)\\
-\end{align*} 
-where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
-\end{old}
-\end{proof}
-More generally we can show that the product of two Laplace transforms based at different points is the Laplace transform of the convolution.
+% %   
+% Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
+% \begin{align*}
+% \laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
+% &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi(a) \psi(a')\,ds \\
+% &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi(a) \psi(a')\,ds 
+% \end{align*}      
+% by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
+% \begin{align*}
+% &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
+% &=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a')\,\frac{\zeta_\alpha(a')}{(1-s)^2}\,e^{-z\zeta_\alpha(a')} e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
+% \end{align*}    
+% Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
+% \begin{align*}
+% &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta_\alpha(a')}{(1-s)^2}e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\\
+% &=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta_\alpha,0}} d\zeta_\alpha(a)\, e^{-z\zeta_\alpha(a)} \phi(a)\\
+% \end{align*} 
+% where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
+% \end{old}
+% \end{proof}
+We can show that the product of two Laplace transforms based at different points is the Laplace transform of the convolution.
 \begin{prop}
-Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 
+Take $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$, with $\sigma,\sigma'\in (-1,\infty)$.\begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined.\end{old} Then
 \begin{equation}\label{eqn:gen-laplace-convol}
-\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha+\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
+\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha,\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
 \end{equation}    
@@
 The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
-\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}}  \phi(a)\,\psi(a')\, d\zeta_\alpha(a)\,.
+\begin{align*}
+\laplace_{\zeta,\alpha,\beta}[\phi \ast_{\zeta,\alpha, \beta} \psi] &= \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\mathcal{S}_{\zeta,\alpha,\beta}} \phi(a)\,\psi(a')\, d\zeta(a)\,.
+\end{align*}
+where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path described in Definition~\ref{def:convolution}. On this path, the equation
+\begin{equation}\label{eq:slice-plane}
+\zeta_\alpha(a) + \zeta_\beta(a') = \zeta_{\alpha+\beta}
+\end{equation}
+holds, and the coordinates $\zeta_\alpha(a)$ and $\zeta_\beta(a')$ have the same argument as $\zeta_{\alpha+\beta}$.
+In particular, over the ray $\mathcal{J}_{\zeta, \alpha+\beta}$, the coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$ and $\zeta_{\alpha+\beta}$ are all real and non-negative.
+The point where $\mathcal{S}_{\zeta, \alpha, \beta}$ starts has $\zeta_\alpha(a) = 0$, and the point where $\mathcal{S}_{\zeta, \alpha, \beta}$ ends has $\zeta_\beta(a') = 0$.
+
+The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ within the complex three-dimensional space $B^3$:
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+The coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$, $\zeta_{\alpha+\beta}$ parameterize $B^3$, and the real wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ is cut out by equation~\eqref{eq:slice-plane} and the conditions
+\begin{align*}
+a & \in \mathcal{J}_{\zeta, \alpha} \\
+a' & \in \mathcal{J}_{\zeta, \beta} \\
+\zeta_{\alpha+\beta} & \in [0, \infty)\,.
+\end{align*}
+Equation~\eqref{eq:slice-plane} can be rewritten as $\zeta(a) + \zeta(a') = \zeta$, which implies the identities
+\begin{align*}
+d\zeta(a) + d\zeta(a') & = d\zeta \\
+d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
+d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,.
+\end{align*}
+We can substitute the last identity into the integral over $\mathcal{N}_{\zeta, \alpha, \beta}$ to get
+\begin{align*}
+\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].
+\end{align*}
+Thinking of $\mathcal{N}_{\zeta, \alpha, \beta}$ as the graph of $\zeta_\alpha(a) + \zeta_\beta(a')$ over the quadrant $\mathcal{J}_{\zeta, \alpha} \times \mathcal{J}_{\zeta, \beta}$, we can use Fubini's theorem to express the integral as the product
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right].
 \]
-In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta_\alpha)$ where $\zeta_\alpha(a)$ runs from $\beta$ to $\zeta_\alpha$, while $a'$ follows the straight path $\mathcal{S}'(\zeta_\alpha)$ where $\zeta_\alpha(a')$ runs from $\zeta_\alpha - \beta$ to $0$.
 \end{revised}
@@
 The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
-\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
+\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta, \alpha+\beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
 \]
@@
 %
+
+\begin{corollary}\label{prop:convolution_iso_laplace}
+For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have
+\begin{equation}\label{eqn:laplace-convol1}
+\laplace_{\zeta,0}[\phi\ast_{\zeta}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
+\end{equation}
+\end{corollary}
+On a domain $\Omega$ which is star-shaped around $\zeta = 0$, the convolution product $\ast_{\zeta}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega)$.
+The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta}$.
 \begin{remark}
-For $\alpha=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$, following the standard convention. \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
-\end{remark}
 When the Taylor expansions of $\phi$ and $\psi$ around $\zeta=\alpha$ converge in a disk of radius $R$, the Taylor expansion of the convolution $\phi\ast_{\zeta,\alpha}\psi$ around $\zeta=\alpha$ also converges in a disk of radius $R$.
 This is proven for $\alpha = 0$ in Lemma~5.14 of \cite{diverg-resurg-i}.
+\end{remark}
 %

### 2024-10-15 sima/reg-sing-volterra_sima.tex
Tweak spacing
Prove the convolution proposition using the new definition

@@
 \newlist{conditions}{itemize}{1}
-\setlist[conditions]{leftmargin=26mm, rightmargin=12mm, topsep=2.5mm, itemsep=1.8mm, parsep=1.2mm}
+\setlist[conditions]{leftmargin=26mm, rightmargin=12mm, topsep=3mm, itemsep=1.8mm, parsep=1.2mm}
 \makeatletter
@@
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
-If the bound invovles an explicit variable, we will say that it holds over all values of the variable.
+If the bound involves an explicit variable, we will say that it holds over all values of the variable.
 For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
@@
 This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
-If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighboorhood $U \subset \C$ of $p$.
+If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighborhood $U \subset \C$ of $p$.
 This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
@@
 \begin{center}
-\begin{tikzpicture}[scale=0.92]
+\begin{tikzpicture}[scale=0.9]
 \newcommand{\spill}{4}

### 2024-10-15 borel-regularity.tex
Do small clarifications

--- 2024-10-13 borel-regularity.tex
@@
 %
-%% \textcolor{orange}{[Revise]} Let $\Omega_\beta \subset B$ be an open, simply connected set that touches but does not contain $\zeta = \beta$, as shown \textcolor{RoyalBlue}{(see Figure \ref{Fig:domain})}.
-Suppose $\Omega_\beta$ contains the ray $\mathcal{J}_{\zeta, \beta}^\theta$.
-In \cite{reg-sing-volterra} we introduce the function space $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ of holomorphic functions on $\Omega_\beta$ which are uniformly of exponential type $\Lambda$ and blow up like $|\zeta - \beta|^\sigma$ as $\zeta$ approaches $\beta$.
-When $\sigma>-1$, the singularity at $\zeta = \beta$ is integrable.
-Hence, the Laplace transform $\laplace_{\zeta, \beta}^\theta$ turns elements of $\singexp{\sigma}{\Lambda}(\Omega_\beta)$ into well-defined holomorphic functions on the half-plane $\Re(e^{i\theta} z) > \Lambda$ in the cotangent space $T_{\zeta = \beta}^*B$~\cite[Section  5.6]{diverg-resurg-i}.
-%%
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
@@
 This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-\begin{definition}\label{def:convolution}
-Let $\phi,\psi$ be two holomorphic functions on $B$.
+% \begin{definition}\label{def:convolution}
+% Let $\phi,\psi$ be two holomorphic functions on $B$.
 Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
 The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
-\begin{equation}%%\label{eq:convolution_def}
-\phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
-\end{equation}
-where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
-\end{definition}
-\color{Turquoise}
+% \begin{equation}%%\label{eq:convolution_def}
+% \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
+% \end{equation}
+% where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
+% \end{definition}
 \begin{definition}\label{def:convolution}
-Choose $\phi \in \singexpalg{\sigma}(\Omega_\alpha),\psi \in \singexpalg{\sigma'}(\Omega_\beta)$ \begin{todo}[refine]\end{todo}.
 Choose a translation coordinate $\zeta$ on $B$.
-The convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
+Let $\Omega_\alpha \subset B$ be an open set with the point $\zeta = \alpha$ on its boundary, and let $\Omega_\beta \subset B$ be an open set with $\zeta = \beta$ on its boundary.
+For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
 \begin{equation}%%\label{eq:convolution_def}
@@
 in terms of the standard coordinate $t$ on $[0, 1]$.
-
-%%line segment in $B^2$ where $\zeta_\alpha(a)$ goes from $0$ to $\zeta_{\alpha + \beta}$ and $\zeta_\beta(a')$ goes from $\zeta_{\alpha + \beta}$ to $0$ with $\zeta(a) + \zeta(a') = \zeta$ at all times.
-
-%%where $\mathcal{S}(\zeta_\alpha)$ is the line segment from $\zeta_\alpha(a)=0$ to $\zeta_\alpha(a) = \zeta_{\alpha + \beta}$, and $\mathcal{S}'(\zeta_\beta)$ is the line segment from $\zeta_\beta(a') = \zeta_{\alpha + \beta}$ to $\zeta_\beta(a') = 0$.
 \end{definition}
-\color{black}
-\begin{revised}
+\begin{notation*}
+ When $\alpha=\beta$ we denote $\ast_{\zeta,\alpha,\beta}$ simply by $\ast_{\zeta,\alpha}$.
+For $\alpha=\beta=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$.
+\begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
+\end{notation*}
 \begin{lemma}
@@
 \end{proof}
-\end{revised}
-\begin{old}
-The function $\phi \ast_{\zeta, \alpha} \psi$ is holomorphic, as long as it is well-defined.\end{old}
-
-On a domain $\Omega_\alpha$ which is star-shaped around $\zeta = \alpha$, the convolution product $\ast_{\zeta, \alpha}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$.
-The Laplace transform $\laplace_{\zeta_\alpha, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta_\alpha, 0}$.
-\begin{prop}\label{prop:convolution_iso_laplace}
-\begin{todo}[Replace $\zeta_\alpha$ with $\zeta$ throughout statement and proof, unless there's some obstacle.]\end{todo} \begin{revised}For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have\end{revised} \begin{old}Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transform $\laplace_{\zeta_\alpha,0}$ is well defined.
-Then\end{old}
-\begin{equation}\label{eqn:laplace-convol1}
-\laplace_{\zeta,0}[\phi\ast_{\zeta,0}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
-\end{equation}
-\begin{todo}
-Add assumption that the Laplace transform of the convolution is well defined. I think we could simply assume $\phi,\psi$ being of exponential type.    
-\end{todo}
+The product of two Laplace transforms based at different points is the Laplace transform of the convolution.
+\begin{prop}
+For any $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$ with $\sigma,\sigma'\in (-1,\infty)$, we have
+\begin{equation}\label{eqn:gen-laplace-convol}
+\laplace^\theta_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha,\beta} \psi] = \laplace^\theta_{\zeta,\alpha}[\phi]\,\laplace^\theta_{\zeta,\beta}[\psi]\,.
+\end{equation}    
 \end{prop}
+More generally, this proposition holds for any holomorphic functions $\phi$ and $\psi$ for which the convolution and all of the Laplace transforms in equation~\eqref{eqn:gen-laplace-convol} are well-defined.
 \begin{proof}
-\begin{revised}
-The left-hand side of equation~\eqref{eqn:laplace-convol1} expands to
-\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_{\mathcal{J}_{\zeta, 0}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
-\]
-In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $0$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta$ to $0$.
-
-The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
-\[ \laplace_{\zeta,0}[{\phi}\ast_{\zeta, 0}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
-The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
-Thus, on $\mathcal{N}$, we have the identity
-\begin{align*}
-d\zeta(a) + d\zeta(a') & = d\zeta \\
-d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta\\
-d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
-\end{align*}
-which we can substitute into the integral above to get
-\begin{align*}
-\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
-& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
-\end{align*}
-
-By construction, the range of $\zeta$ on $\mathcal{N}$ is $[0, \infty)$.
-From the definitions of the paths $\mathcal{S}(\zeta)$ and $\mathcal{S}'(\zeta)$, it follows that the ranges of $\zeta(a)$ and $\zeta(a')$ on $\mathcal{N}$ are also both $[0, \infty)$.
-In fact, projection onto the $a$ and $a'$ factors of $B^3$ identifies $\mathcal{N}$ with $\mathcal{J}_{\zeta(a), 0} \times \mathcal{J}_{\zeta(a'), 0} \subset B^2$.
-We can therefore factorize the integral above using Fubini's theorem, yielding the desired identity:
-\begin{align*}
-\laplace_{\zeta,0}[{\phi}\ast_{\zeta,0}{\psi}] & = \left[ \int_{\mathcal{J}_{\zeta(a), 0}} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \left[ \int_{\mathcal{J}_{\zeta(a'), 0}} e^{-z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
-\end{align*}
-\end{revised}
-\begin{old}
-\begin{todo}Check whether anything would change for non-zero $\theta$.\end{todo} Notice that the convolution product can be rewritten by introducing the parameter $s\in [0,1]$
-\begin{align*}
-\phi \ast_{\zeta_\alpha,0} \psi &= \int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}} \phi(a)\,\psi(a')\,d\zeta_\alpha(a)\\
-&=\zeta_\alpha\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
-\end{align*}
-where $\zeta_\alpha(a)=s\zeta_\alpha$ and consequently $\zeta_\alpha(a')=(1-s) \zeta_\alpha$.  
-First, we show that the convolution product $\phi \ast_{\zeta_\alpha,0} \psi$ is in the domain of the Laplace transform $\laplace_{\zeta_\alpha,0}$.
-\begin{todo}[Right now, we're only assuming that $\phi$ and $\psi$ have well-defined Laplace transforms, which doesn't imply that they're uniformly of exponential type]\end{todo} It is uniformly of exponential type $c'' := \max\{c, c'\}$, because
-\begin{align*}
-\big|\phi \ast_{\zeta_\alpha,0} \psi\big|&\leq |\zeta_\alpha|\int_0^1 ds \,|\phi(a)|\,|\psi(a')|\\
-&\lesssim |\zeta_\alpha| \int_0^1 ds\, e^{c |\alpha+s\zeta_\alpha|}\,e^{c'|(1-s)\zeta_\alpha|}\\
-& \lesssim |\zeta_\alpha|  e^{c'' |\zeta_\alpha|}\,.
-\end{align*}    
-Note that if $\phi$ and $\psi$ have integrable singularities at $\zeta_\alpha = 0$, the product $\phi(a)\,\psi(a')$ has both singularities, but in different positions---one at $s = 0$, and the other at $s = 1$.
-This guarantees that $\phi(a)\,\psi(a')$ is integrable over the interval $s \in [0, 1]$.
-%   
-Then, the Laplace transform of $\phi \ast_{\zeta_\alpha,0} \psi$ reads
-\begin{align*}
-\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]&=\laplace_{\zeta_\alpha,0}[{\phi}\ast_{\zeta_\alpha,0}{\psi}]\\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,e^{-z\zeta_\alpha}\zeta_\alpha\, \int_0^1 \phi(a) \psi(a')\,ds \\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\, \int_0^1 \zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z s \zeta_\alpha} \phi(a) \psi(a')\,ds 
-\end{align*}      
-by exchanging the order of integration we find \begin{todo}[recalling that $\zeta_\alpha(a') = (1-s)\zeta_\alpha$ on the integration path that defines the convolution]\end{todo}
-\begin{align*}
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha\,\zeta_\alpha\,e^{-z\zeta_\alpha(1-s)} e^{-z\zeta_\alpha s} \phi(a) \psi(a') \\
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a')\,\frac{\zeta_\alpha(a')}{(1-s)^2}\,e^{-z\zeta_\alpha(a')} e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\,\psi(a') 
-\end{align*}    
-Using that $\zeta_\alpha(a)=\zeta_\alpha(a')\frac{s}{1-s}$ holds on the integration contour, we find
-\begin{align*}
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a')\,\int_0^1 ds\,\frac{\zeta_\alpha(a')}{(1-s)^2}e^{-z\zeta_\alpha(a') \frac{s}{1-s}} \phi(a)\\
-&=\int_{\mathcal{J}_{\zeta_\alpha,0}}d\zeta_\alpha(a') \,e^{-z\zeta_\alpha(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta_\alpha,0}} d\zeta_\alpha(a)\, e^{-z\zeta_\alpha(a)} \phi(a)\\
-\end{align*} 
-where as $s$ varies in $[0,1]$ we get that $a$ follows the ray $\mathcal{J}_{\zeta_\alpha,0}$ \begin{todo}[check this statement]\end{todo}.
-\end{old}
-\end{proof}
-More generally we can show that the product of two Laplace transforms based at different points is the Laplace transform of the convolution.
-\begin{prop}
-Let $\phi,\psi$ be two holomorphic functions on $B$ whose Laplace transforms $\laplace_{\zeta,\alpha}\phi$ and $\laplace_{\zeta,\beta}\psi$ are well defined. Then 
-\begin{equation}\label{eqn:gen-laplace-convol}
-\laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta,\alpha+\beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,.
-\end{equation}    
-\end{prop}
-\begin{proof}
-\begin{todo}
-[\textbf{V} add $\theta$, or explain that it's missing, Fix proof] [\textbf{A} read through proof]
-\end{todo}
-\begin{revised}
+For simplicity, we will write out the proof for $\theta = 0$. The proof for general $\theta$ is analogous.
+
 The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
-\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta_\alpha) \times \mathcal{S}'(\zeta_\alpha) \\ \zeta_\alpha(a) + \zeta_\alpha(a') = \zeta_\alpha}}  \phi(a)\,\psi(a')\, d\zeta_\alpha(a)\,.
-\]
-In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta_\alpha)$ where $\zeta_\alpha(a)$ runs from $\beta$ to $\zeta_\alpha$, while $a'$ follows the straight path $\mathcal{S}'(\zeta_\alpha)$ where $\zeta_\alpha(a')$ runs from $\zeta_\alpha - \beta$ to $0$.
-\end{revised}
-\begin{draft}
-The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
-\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\,\psi(a')\, d\zeta(a)\,.
-\]
-In the convolution integral, $a$ follows the straight path $\mathcal{S}(\zeta)$ where $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$, while $a'$ follows the straight path $\mathcal{S}'(\zeta)$ where $\zeta(a')$ runs from $\zeta - (\alpha + \beta)$ to $0$.
-
-The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}$ within the complex three-dimensional space $B^3$:
-\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] = \int_\mathcal{N} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
-The coordinates $\zeta(a)$, $\zeta(a')$, $\zeta$ parameterize $B^3$, and the real wedge $\mathcal{N}$ lies within the complex surface cut out by the equation equation $\zeta(a) + \zeta(a') = \zeta$.
-Thus, on $\mathcal{N}$, we have the identity
+\begin{align*}
+\laplace_{\zeta,\alpha,\beta}[\phi \ast_{\zeta,\alpha, \beta} \psi] &= \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\mathcal{S}_{\zeta,\alpha,\beta}} \phi(a)\,\psi(a')\, d\zeta(a)\,.
+\end{align*}
+where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path described in Definition~\ref{def:convolution}. On this path, the equation
+\begin{equation}\label{eq:slice-plane}
+\zeta_\alpha(a) + \zeta_\beta(a') = \zeta_{\alpha+\beta}
+\end{equation}
+holds, and the coordinates $\zeta_\alpha(a)$ and $\zeta_\beta(a')$ have the same argument as $\zeta_{\alpha+\beta}$.
+In particular, over the ray $\mathcal{J}_{\zeta, \alpha+\beta}$, the coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$ and $\zeta_{\alpha+\beta}$ are all real and non-negative.\footnote{For general $\theta$, we have the condition that $\zeta_\alpha(a)$, $\zeta_\beta(a')$ and $\zeta_{\alpha+\beta}$ all lie on the ray $e^{i\theta}[0, \infty)$.} The point where $\mathcal{S}_{\zeta, \alpha, \beta}$ starts has $\zeta_\alpha(a) = 0$, and the point where $\mathcal{S}_{\zeta, \alpha, \beta}$ ends has $\zeta_\beta(a') = 0$.
+
+The convolution and Laplace integrals can be combined into an integral over a real two-dimensional wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ within the complex three-dimensional space $B^3$:
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z\zeta}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta\,. \]
+The coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$, $\zeta_{\alpha+\beta}$ parameterize $B^3$, and the real wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ is cut out by equation~\eqref{eq:slice-plane} and the conditions
+\begin{align*}
+a & \in \mathcal{J}_{\zeta, \alpha} \\
+a' & \in \mathcal{J}_{\zeta, \beta} \\
+\zeta_{\alpha+\beta} & \in [0, \infty)\,.
+\end{align*}
+Equation~\eqref{eq:slice-plane} can be rewritten as $\zeta(a) + \zeta(a') = \zeta$, which implies the identities
 \begin{align*}
@@
 d\zeta(a) \wedge \big[d\zeta(a) + d\zeta(a')\big] & = d\zeta(a) \wedge d\zeta \\
-d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,,
-\end{align*}
-which we can substitute into the integral above to get
-\begin{align*}
-\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_\mathcal{N} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
-& = \int_\mathcal{N} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
-\end{align*}
-\begin{todo}Now we need to explain why the grid lines can be projected to $\mathcal{J}_{\zeta(a), \alpha}$ and $\mathcal{J}_{\zeta(a'), \beta}$.
-Something seems off here.
-The tip of the wedge $\mathcal{N}$ should be at $\zeta = \alpha + \beta$, since that's the beginning of the ray $\mathcal{J}_{\zeta, \alpha + \beta}$.
-At that point, though, according to our definitions, $\mathcal{S}(\zeta)$ should consist of the point $\zeta(a) = \alpha + \beta$, and $\mathcal{S}'(\zeta)$ should consist of the point $\zeta(a') = 0$.
-
-In my drawings, I assumed that the tip of the wedge $\mathcal{N}$ would be at the point where $\zeta(a) = \alpha$, $\zeta(a') = \beta$, and $\zeta = \alpha + \beta$.
-Now I'm skeptical about that.
-Is that point even in $\mathcal{N}$?
-If so, what distinguishes it from all the other points on the line $\zeta(a) + \zeta(a') = \alpha + \beta$?
-Since $\alpha$ and $\beta$ can vary without changing the left-hand side of equation~\eqref{eqn:gen-laplace-convol}, we must need to make a choice somewhere\ldots
-
-Maybe we need to change the statement to
-\[ \laplace_{\zeta,\alpha+\beta}[\phi \ast_{\zeta_\alpha, \beta} \psi] = \laplace_{\zeta,\alpha}[\phi]\,\laplace_{\zeta,\beta}[\psi]\,. \]
-I think the argument might wrap up neatly in that case.
-\end{todo}
-\begin{align*}
-\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}] & = \int_{?} e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \int_{?} e^{z\zeta(a')}\,\psi(a')\,d\zeta(a')
-\end{align*}
-\end{draft}
-
-\color{violet}
-In the convolution integral, $a$ and $a'$ move so that $\zeta(a)$ runs from $\alpha+\beta$ to $\zeta$ while $\zeta(a')$ goes from $\zeta_{\alpha+\beta}$ to $0$.
-
-\begin{align*}
-\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=\int_{\mathcal{J}_{\zeta,\alpha+\beta}}d\zeta\,e^{-z\zeta}\int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}}  \phi(a)\, \psi(a')\, d\zeta(a)
-\end{align*}
-
-Equivalently, $a$ and $a'$ move so that $\zeta_{\textcolor{magenta}{\alpha}}(a)$ runs from $\zeta_{\alpha+\beta}$ to $0$ while $\zeta_{\textcolor{magenta}{\beta}}(a')$ goes from $\zeta$ to $0$.
-In particular, we introduce the parameter $s\in [0,1]$ so that $\zeta(a)=(1-s)(\alpha+\beta)+s\zeta-\beta$ and $\zeta(a')=(1-s)\zeta+\beta$.
-\color{black}
-\begin{revised}
-The convolution product can be rewritten by introducing the coordinates $\zeta_\beta$ and $\zeta_{-\beta}$:
-\begin{align*}
-\phi \ast_{\zeta, \alpha+\beta} \psi &= \int_{\substack{\mathcal{S}(\zeta) \times \mathcal{S}'(\zeta) \\ \zeta(a) + \zeta(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
-&=\int_{\substack{\mathcal{S}(\zeta_{\beta}) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_{\beta}(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
-\end{align*}
-where $\mathcal{S}(\zeta_{\beta})$ is the line segment from $\zeta_\beta(a)=\alpha$ to $\zeta_\beta(a)=\zeta_\beta$ and similarly, $\mathcal{S}'(\zeta_{-\beta})$ is the line segment from $\zeta_{-\beta}(a')=\zeta_\alpha$ to $\zeta_{-\beta}(a')=\beta$.
-This change of coordinates simplifies our computations by showing how the convolution product depends on the base points of the Laplace transforms $\laplace_{\zeta,\alpha}[\phi]$ and $\laplace_{\zeta,\beta}[\psi]$.
-
-Following the argument in the proof of Proposition~\ref{prop:convolution_iso_laplace}, we introduce the parameter $s\in [0,1]$ and we rewrite the convolution  
-\begin{align*}
-    \phi \ast_{\zeta, \alpha+\beta} \psi
-    &=\int_{\substack{\mathcal{S}(\zeta_\beta) \times \mathcal{S}'(\zeta_{-\beta}) \\ \zeta_\beta(a) + \zeta_{-\beta}(a') = \zeta}} \phi(a)\,\psi(a')\,d\zeta(a)\\
-    &=\zeta_{\alpha+\beta}\,\int_0^1 \phi(a)\,\psi(a')\,ds\,,
-\end{align*}
-\begin{todo}[\textbf{A} Does this expression change when $\theta \neq 0$?]\end{todo} where $\zeta_\beta(a)=(1-s)\alpha+s\zeta_\beta$ and consequently $\zeta_{-\beta}(a')=\beta s+(1-s)\zeta_\alpha$.
-Then, the Laplace transform of $\phi \ast_{\zeta, \alpha} \psi$ reads
-\begin{align*}
-    \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]&=e^{-z(\alpha+\beta)}\laplace_{\zeta_{\alpha+\beta},0}[{\phi}\ast_{\zeta, \alpha+\beta}{\psi}]\\
-    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,e^{-z\zeta_{\alpha+\beta}}\zeta_{\alpha+\beta}\, \int_0^1 \phi(a)\,\psi(a')\,ds \\
-    &=e^{-z(\alpha+\beta)}\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\, \int_0^1 \zeta_{\alpha+\beta}\,e^{-z(1-s)\zeta_{\alpha+\beta}} e^{-z s\zeta_{\alpha+\beta}} \phi(a)\, \psi(a')\,ds\,.
-\end{align*}
-By exchanging the order of integration we find 
-\begin{align*}
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta_{\alpha+\beta},0}}d\zeta_{\alpha+\beta}\,\zeta_{\alpha+\beta}\,e^{-z(\beta s+(1-s)\zeta_\alpha)} e^{-z(\alpha(1-s)+s\zeta_\beta)}\phi(a)\,\psi(a') \\
-&=\int_0^1 ds\,\int_{\mathcal{J}_{\zeta,0}}\frac{d\zeta(a')}{(1-s)^2}\,e^{-z\zeta_{-\beta}(a')} (\zeta_{-\beta}(a')-\beta) e^{-z( (\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\,\psi(a')\,,
-\end{align*}
-where in the second step we use $d\zeta_{\alpha+\beta}=d\zeta_\alpha=\frac{d\zeta_{-\beta}(a')}{1-s}$ and $\zeta_{\alpha+\beta}=\frac{\zeta_{-\beta}(a')-\beta}{1-s}$ \begin{todo}[this comes from the expression for $\zeta_{-\beta}(a')$ above, by subtracting $\beta$ from both sides and then rearranging]\end{todo}.
-Then, exchanging one more time the order of integration we get
-\begin{align*}
-&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta_{-\beta}(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha)} \phi(a)\\
-&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_0^1 ds\,\frac{\zeta_{-\beta}(a')-\beta}{(1-s)^2}e^{-z((\zeta_{-\beta}(a')-\beta) \frac{s}{1-s}+\alpha+\beta)} \phi(a)\\
-&=\int_{\mathcal{J}_{\zeta,0}}d\zeta(a') \,e^{-z\zeta(a')}  \psi(a') \,\int_{\mathcal{J}_{\zeta,\alpha+\beta}} d\zeta(a)\, e^{-z\zeta(a)} \phi(a)
-\end{align*}
-where on the integration path we have $\zeta(a)=(\zeta_{-\beta}(a')-\beta)\frac{s}{1-s}+\alpha+\beta$ which moves $a$ \begin{todo}(?)\end{todo} along the ray $\mathcal{J}_{\zeta,\alpha+\beta}$ as $s$ varies in $[0,1]$.
-\end{revised}
+d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,.
+\end{align*}
+We can substitute the last identity into the integral over $\mathcal{N}_{\zeta, \alpha, \beta}$ to get
+\begin{align*}
+\laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
+& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].
+\end{align*}
+Thinking of $\mathcal{N}_{\zeta, \alpha, \beta}$ as the graph of $\zeta_\alpha(a) + \zeta_\beta(a')$ over the quadrant $\mathcal{J}_{\zeta, \alpha} \times \mathcal{J}_{\zeta, \beta}$, we can use Fubini's theorem to express the integral as the product
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right].
+\]
 \end{proof}
 %
+\begin{corollary}\label{prop:convolution_iso_laplace}
+For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have
+\begin{equation}\label{eqn:laplace-convol1}
+\laplace_{\zeta,0}[\phi\ast_{\zeta}\psi]=\laplace_{\zeta,0}[\phi]\,\laplace_{\zeta,0}[\psi]\,.
+\end{equation}
+\end{corollary}
+On a domain $\Omega$ which is star-shaped around $\zeta = 0$, the convolution product $\ast_{\zeta}$ induces a $\C$-algebra structure on $\singexp{\sigma}{\Lambda}(\Omega)$.
+The Laplace transform $\laplace_{\zeta, 0}$ is special, because it is an algebra isomorphism with respect to $\ast_{\zeta}$.
 \begin{remark}
-For $\alpha=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}.
-In addition, we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$, following the standard convention. \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
-\end{remark}
 When the Taylor expansions of $\phi$ and $\psi$ around $\zeta=\alpha$ converge in a disk of radius $R$, the Taylor expansion of the convolution $\phi\ast_{\zeta,\alpha}\psi$ around $\zeta=\alpha$ also converges in a disk of radius $R$.
 This is proven for $\alpha = 0$ in Lemma~5.14 of \cite{diverg-resurg-i}.
+\end{remark}
 %
@@
 
-Similarly, we can extend the definition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha,0}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
+\begin{old}
+Similarly, we can extend the definition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
 \begin{equation}
@@
 \end{equation}
-Then, the unit for $\ast_{\zeta_\alpha,0}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha,0}\frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
+Then, the unit for $\ast_{\zeta_\alpha}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
+\end{old}
 We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
 \begin{prop}
-    Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$.
-The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
+Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$. The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
 \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
@@
 \end{proof}
-\begin{todo}[Maybe shorten to a reminder that $z$ is an almost-global coordinate on cotangent spaces, so this also works in other fibers.]\end{todo} Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha,0}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
+Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
 %We can further generalize this result to transseries:
@@
 In fact, we deduce that the Borel transform induces an algebra homomorphism on $1$-Gevrey series.
-Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ endowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha,0}$.
+Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ endowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha}$.
 \begin{verify}
@@
 %
-Consider an open set $\Omega \subset \C$ that touches but does not contain $\zeta = 0$.
-The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
+Consider an open set $\Omega \subset \C$ that touches but does not contain $\zeta = 0$.\footnote{We say that a subset of a topological space {\em touches} the points in its closure.
+This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} The spaces $\singexp{\sigma}{\Lambda}(\Omega)$ from \cite{reg-sing-volterra} are convenient for analytic discussions of the Laplace transform, as we saw in Section~\ref{sec:reg-decay}.
 To study Borel summation, however, we also need to take shifted Taylor expansions around $\zeta = 0$, turning holomorphic functions $\phi \in \singexp{\sigma}{\Lambda}(\Omega)$ into convergent power series $\series{\phi} \in \zeta^\rho \C\{\zeta\}$ with $\rho \ge \sigma$.
@@
 Take some $\rho \in (-1,\infty)$.
-If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0} \series{\varphi}$.
-\begin{todo}[Clarify domain of $\Phi$]\end{todo}
+If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0}^\theta \series{\varphi}$ on the domain $\widehat{\Omega}_0^\Lambda$ defined in Section~\ref{sec:reg-decay}.
+\begin{todo}[Switch from $\rho$ to $\sigma$?]\end{todo}
 \end{lemma}
@@
 \[ \series{\Phi} = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \frac{a_2}{z^{\rho+3}} + \frac{a_3}{z^{\rho+4}} + \ldots. \]
-For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\sigma+n}{\Lambda}(\Upsilon)$ by the equation
+For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\rho+n}{\Lambda}(\Upsilon)$ by the equation
 \[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
@@
 Because of the conditions we put on $\Omega$, we can apply Proposition~\ref{prop:laplace-cont}, which tells us that $E_n$ lies in $\dualsingexp{-\rho-n-1}(\widehat{\Omega}_0^\Lambda)$.
-This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_\alpha^\Lambda$.
+This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_0^\Lambda$.
 Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check; specify domain of ray]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
@@
 &=\laplace_{\zeta,0}\left[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\right] \\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta)}\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}(\zeta) }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
-&=\laplace_{\zeta,0}\fracderiv{\tau}{\zeta}{0}\phi,
-\end{align*}
-where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
+&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0,0}}\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0,0} }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
+&=\laplace_{\zeta,0}\big[\fracderiv{\tau}{\zeta}{0}\phi\big],
+\end{align*}
+where $\mathcal{S}_{\zeta,0,0}$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
 Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:

### 2024-10-23 borel-regularity.tex
Do some to-dos in the introduction

@@
 \subsection{The unreasonable effectiveness of Borel summation}\label{intro:summation}
-You can often find a formal power series \begin{todo}[double-check that this matches the $\tau$ from the position domain]\end{todo}
+You can often find a formal power series
 \[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\begin{todo}[Nikita has a complementary picture where the Borel plane is the cotangent fiber?
-Ask more about this.]\end{todo}
 \item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
@@
 \end{definition}
-\begin{todo}[Mention Nevanlinna's theorem, re-stated as \cite[Theorem~C.11]{nikolaev2023existence}, somewhere later?]\end{todo}
-\begin{todo}[State the theorem that differentiation and integration commute with $\aexp^\theta$ under certain circumstances?
-See Erdelyi's {\em Asymptotic Expansions}, \S 1.6.
-For basic facts about uniform asymptoticity, see \S 5.7.2 of Mitschi and Sauzin.
-Theorem~5.20 and its rephrasing say that the Laplace transform of a function is uniformly asymptotic to the formal Laplace transform of the function's Taylor series.]\end{todo}
-
 \begin{definition}\label{def:unif-gevrey-asymp}
@@
 The examples we study all involve {\em resurgent functions} in the position domain.
-\begin{revised}The theory of resurgence, introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}, describes divergent series in the frequency domain in terms of the analytic properties of their Borel transforms.
+The theory of resurgence, introduced by \'Ecalle~\cite{EcalleI,EcalleII,EcalleIII}, describes divergent series in the frequency domain in terms of the analytic properties of their Borel transforms.
 Resurgent analysis is an effective tool for computing ``subleading contributions'' in perturbation theory, and it occasionally leads to the resummation of the original divergent series.
-It\end{revised} has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+It has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
 
@@
 
-The frequency and position variables $z$ and $\zeta$ are excepted from this convention.
-The frequency variable is lower-case, even though it lives on the frequency domain, and neither variable gets a tilde when it serves as a formal variable rather than a coordinate function.
+The frequency and position coordinates $z$ and $\zeta$ are excepted from this convention.
+The frequency coordinates is lower-case, even though it lives on the frequency domain, and neither variable gets a tilde when it serves as a formal variable rather than a coordinate function.
 \end{notation*}
@@
 On the other hand, the Borel transform $\borel_\zeta$ turns formal series in the frequency variable into formal series in the position variable, so we might write $\series{\phi} = \borel_\zeta \series{\Phi}$.
-%
-\begin{revised}
-We will also follow the convention of~\cite{reg-sing-volterra} for integrals. 
-\begin{notation*}
-When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}.
+
+We will follow our convention from~\cite{reg-sing-volterra} for integrals along paths. 
+\begin{notation*}[reproduced from Section~1.2.3 of~\cite{reg-sing-volterra}]
+When we integrate a holomorphic function along a path, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}.
 On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.
@@
 \end{notation*}
-%    
-\end{revised}
 %
@@
 %
-Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
+\begin{todo}[Mention \cite{kontsevich-Fourier-exact}]\end{todo} Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
 The asymptotic expansion of a thimble integral is typically divergent, but its Borel sum often matches the integral it came from.
@@
 
-\begin{revised}
-We recall the definition of $\singexp{\sigma}{\Lambda}(\Omega)$ below. Let $\holo(\Omega)$ denote the space of holomorphic functions on the domain $\Omega$. 
+For convenience, we recall the definition of $\singexp{\sigma}{\Lambda}(\Omega)$. Let $\holo(\Omega)$ denote the space of holomorphic functions on the domain $\Omega$. 
 \begin{definition}\label{def:HL_inf}
@@
 \end{definition}
-\end{revised}
 \subsubsection{The Laplace transform over a branch point}
@@
 Suppose $\Omega_\alpha$ is an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
-For any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$.
+For any $\Lambda \in \R$, let $\widehat{\Omega}_\alpha^\Lambda$ be the union of the half-planes $\Re(e^{i\theta} z) > \Lambda$ over all angles $\theta$ in the opening of $\Omega_\alpha$, as illustrated in Figure~\ref{fig:sectorial_domain-pos-fre}.
+The domain $\widehat{\Omega}_\alpha^\Lambda$ is defined wherever $z$ is well-defined: in $T_b^*B$ over each ordinary point $b \in B$, and in $T_b^*B^{\otimes n}$ over each branch point $b \in B$ with cone angle $2\pi n$.
 \begin{center}
@@
 \genfibercontent[dual]
-%%\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$\Lambda$};
 \node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
@@
 \end{center}
-\begin{revised}
+To describe the image of the Laplace transform $\laplace_{\zeta,\alpha}$, we introduce frequency-domain counterparts for the function spaces $\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ from Definition~\ref{def:HL_inf}.
+%
 \begin{definition}\label{def:H_hat}
@@
 \end{definition}
-\end{revised}
-\begin{todo}[Explain more why we write in terms of the distance function $\Delta$]\end{todo}
-\begin{revised}
 To make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough, it is helpful to have a space that encompasses $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ for all $\Lambda$.
 Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into.
-\end{revised}
-\begin{todo}\par
-[Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
-\end{todo}
 %
@@
 %%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
-\[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}(\zeta)} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
-where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
+\[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}_{\zeta,\alpha}} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
+where $\mathcal{S}_{\zeta,\alpha}$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
 
@@
 \begin{proof}
-%where in the last step we repetedly use integration by part and the fact that boundary terms vanish. %Then we deduce that   
-%\begin{align*}
- %   z^\mu\laplace_{\zeta,0}\phi&= \laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\Big] \laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\\
-  %  &=\laplace_{\zeta,0}\Big[\frac{\zeta^{-\alpha-1}}{\Gamma(-\alpha)}\ast \partial_\zeta^n\phi\Big]\\
-   % &=z^n\laplace_{\zeta,0}\Big[\fracderiv{\lambda}{\zeta}{0}\partial_\zeta^n \phi\Big]
-%\end{align*}
-
 Results \ref{res:frac-deriv} and \ref{res:frac-int} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
-\begin{revised}
 \begin{align*}
@@
 &=\laplace_{\zeta,0}\left[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)} \ast_\zeta \phi\right] \\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0,0}}\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
-&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0,0} }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0}}\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
+&=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0} }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
 &=\laplace_{\zeta,0}\big[\fracderiv{\tau}{\zeta}{0}\phi\big],
 \end{align*}
-where $\mathcal{S}_{\zeta,0,0}$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
+where $\mathcal{S}_{\zeta,0}$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
 Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:
@@
 Result~\ref{res:monom-mult} is also proven by repeated integration by parts, with the assumption that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ ensuring that the integral converges.
-        %from a 2d integration argument, akin to the one in \cite[Theorem~2.39]{laplace-tfm}.
-This generalizes the Laplace transform's action on derivatives: using differentiation under the integral we prove \emph{ii)} (see also \cite[Theorem~1.34]{laplace-tfm}).
-Similarly, one can prove \emph{iii)}.
-\end{revised}
 \end{proof}
 \begin{lemma}\label{lem:frac-deriv-Borel}
-For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta } \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]. \]
+\begin{todo}[Clarify whether this statement is purely algebraic or a combination of algebraic and analytic.
+Add zero subscript for formal integral operator]\end{todo} For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+\[ \partial^\mu_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]. \]
 \end{lemma}
@@
 \begin{align*}
-\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta \big(\zeta-\zeta(a)\big)^{-\mu} \frac{\zeta(a)^k}{\Gamma(k+1)}\,d\zeta(a) \\
+\partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta \big(\zeta-\zeta(a)\big)^{-\mu} \frac{\zeta(a)^k}{\Gamma(k+1)}\,d\zeta(a) \\
 & = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
@@
 \begin{equation}\label{frac-diff-laplace}
-\big(\tfrac{\partial}{\partial \zeta}\big)^{n+1}\,\partial^{\mu-1}_{\zeta } \borel_\zeta \big[z^{-(k+1)}\big] = \frac{\zeta^{k-(n+\mu)}}{\Gamma\big(k-(n+\mu)+1\big)}
+\big(\tfrac{\partial}{\partial \zeta}\big)^{n+1}\,\partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] = \frac{\zeta^{k-(n+\mu)}}{\Gamma\big(k-(n+\mu)+1\big)}
 \end{equation}
@@
 \begin{align*}
-\tfrac{\partial}{\partial \zeta} \big(\tfrac{\partial}{\partial \zeta}\big)^{m+1}\,\partial^{\mu-1}_{\zeta} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\mu)}}{\big(k-(m+\mu)\big)\,\Gamma\big(k-(m+\mu)\big)} \right) \\
+\tfrac{\partial}{\partial \zeta} \big(\tfrac{\partial}{\partial \zeta}\big)^{m+1}\,\partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\mu)}}{\big(k-(m+\mu)\big)\,\Gamma\big(k-(m+\mu)\big)} \right) \\
 & = \frac{\zeta^{k-(m+1+\mu)}}{\Gamma\big(k-(m+\mu)\big)}
@@
 Therefore, $\mathcal{C}_a(\zeta)$ is endlessly analytically continuable away from the critical values of $f$.
-Resurgent functions have resurgent derivatives \begin{todo}[check]\end{todo}, so $\iota_\alpha$ is resurgent too.\end{revised}
+Resurgent functions have resurgent derivatives,\footnote{This is because analytically continuing a function to a given open set automatically continues its derivative to the same open set.} so $\iota_\alpha$ is resurgent too.\end{revised}
 \begin{old}\par

### 2024-10-23 borel-regularity.tex
Remove redundant definition of algebraic convolution
The previous definition already works for any translation coordinate.

@@
 
-\begin{old}
-Similarly, we can extend the definition of $\ast$ to a different coordinate $\zeta_\alpha$ on $B$, the convolution product will be denoted by $\ast_{\zeta_\alpha}$ and the definition will be analogous of equation~\eqref{eq: convolution_formal}
-\begin{equation}
-\frac{\zeta_\alpha^m}{m!} \ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!} \defeq \frac{\zeta_\alpha^{m+n+1}}{(m+n+1)!} \,.
-\end{equation}
-Then, the unit for $\ast_{\zeta_\alpha}$ will be denoted by $\delta$, namely \[\delta\ast_{\zeta_\alpha} \frac{\zeta_\alpha^n}{n!}\defeq\frac{\zeta_\alpha^n}{n!}\,.\]
-\end{old}
 We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.

### 2024-10-23 borel-regularity.tex
Clarify formality of Borel integral dictionary

@@
 If $\varphi \in \singexp{\rho}{\Lambda}(\Omega)$ is the sum of a power series $\series{\varphi} \in \zeta^\rho\,\C\{\zeta\}$, then its Laplace transform $\Phi = \laplace_{\zeta, 0}^\theta \varphi$ is asymptotic to the formal Laplace transform $\series{\Phi} = \laplace_{\zeta, 0}^\theta \series{\varphi}$ on the domain $\widehat{\Omega}_0^\Lambda$ defined in Section~\ref{sec:reg-decay}.
-\begin{todo}[Switch from $\rho$ to $\sigma$?]\end{todo}
 \end{lemma}
@@
 \end{remark}
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{lem:laplace-bridge}]
 By adding points within the disk around $\zeta = 0$ where $\series{\varphi}$ converges, expand $\Omega$ to an open set $\Upsilon \subset \widetilde{\C^\times}$ of the kind used in Lemma~\ref{lem:shifted_holo_closed}, Figure~\ref{fig:domain_Upsilon}.
@@
 \begin{lemma}\label{lem:frac-deriv-Borel}
-\begin{todo}[Clarify whether this statement is purely algebraic or a combination of algebraic and analytic.
-Add zero subscript for formal integral operator]\end{todo} For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
+For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
 \[ \partial^\mu_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]. \]
@@
 \begin{proof}
-We will show that for any $\mu \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$. First, evaluate
+Because every operation in the statement maps monomials to monomials, we do not need to distinguish carefully between formal and analytic arguments.
+Using a mostly analytic argument, we will show that for any $\mu \in (0, 1)$ and any integer $n \ge 0$, the claim holds with $\mu = n + \alpha$.
+First, evaluate
 \begin{revised}

### 2024-10-23 borel-regularity.tex
Remove old, incorrect corollary

@@
 \end{remark}
-\begin{todo}
-\begin{corollary}\label{simple-res-thimble}
-If $f$ and $\nu$ are polynomials, the function ${\phi}=\fracderiv{-1/2}{\zeta}{\alpha}\iota$ defined in Remark~\ref{rmk:1/2-deriv} has simple resurgent singularities at $\zeta=\beta$, for all $\beta$ roots of $P$ such that $\beta\neq\alpha$.
-\end{corollary}
-\begin{proof}
-Recall ${\phi}_\alpha$ is the sum of the Borel transform of $z^{1/2}\series{I}_j$, namely 
-\[\hat{\phi}_j(\zeta)=\fracderiv{1/2}{\zeta}{\alpha_j}\hat{\iota}_j=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\hat{\iota}_j(s)\, ds\]
-Then by Pham's result (see~\eqref{rmk:Pham formula}) we know 
-\[\hat{\iota}_j(\zeta_j)=\frac{(-\zeta_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-\zeta_j)^{-k} + \text{ hol. funct. }\]
-hence 
-\[\hat{\iota}_j(\zeta)=\int_{\alpha_j}^\zeta(\zeta-s)^{-3/2}\frac{(-s+\alpha_j)^{-1/2}}{2\pi i\Gamma(-\tfrac{1}{2})}\sum_{k=0}^\infty c_k (-s+\alpha_j)^{-k} \, ds + \text{ hol. funct. }\]
-\end{proof}
-\end{todo}
 \begin{remark}\label{rmk:Pham formula}

### 2024-10-23 borel-regularity.tex
Remove jump argument that's too hard to finish

@@
 \end{center}
-\begin{revised}Initially, the function $\int_{\mathcal{C}_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_a(\zeta)$.
+Initially, the function $\int_{\mathcal{C}_a(\zeta)} \nu$ is only defined for $\zeta$ on the ray $[\alpha, \infty)$, but it can be analytically continued to points off the ray by homotopy of the path $\mathcal{C}_a(\zeta)$.
 Since $\nu$ is holomorphic, the only way for $\int_{\mathcal{C}^\theta_a(\zeta)} \nu$ to become singular is for something to go wrong with the homotopy of $\mathcal{C}_a(\zeta)$, which can only happen at the critical values of $f$.
 Therefore, $\mathcal{C}_a(\zeta)$ is endlessly analytically continuable away from the critical values of $f$.
-Resurgent functions have resurgent derivatives,\footnote{This is because analytically continuing a function to a given open set automatically continues its derivative to the same open set.} so $\iota_\alpha$ is resurgent too.\end{revised}
-\begin{old}\par
-\begin{todo}[Incorporate this additional work]\end{todo} We will calculate the jump of $\int_{\mathcal{C}_a^\theta(\zeta)}\nu$ across the cut starting at $\zeta = \beta$.
-Write $\beta$ as $\alpha + re^{i\theta_\beta}$, and let $\beta^+$ and $\beta^-$ be the values we get by infinitesimally increasing or decreasing $\theta_\beta$.
-The jump is then given by \[\int_{\mathcal{C}_a^\theta(\beta^+)} \nu - \int_{\mathcal{C}_a^\theta(\beta^-)} \nu\]
-and it turns out to be proportional to $\series{\phi}_\beta$, namely to the germ of analytic functions at $\zeta_\alpha=\beta$.
-%We will see an example of this behaviour in Appendix~\ref{apx:eye-res-airy}.
-
-\end{old}
+Resurgent functions have resurgent derivatives,\footnote{This is because analytically continuing a function to a given open set automatically continues its derivative to the same open set.} so $\iota_\alpha$ is resurgent too.
 \end{remark}

### 2024-10-23 borel-regularity.tex
Plan to revise cantilever thimble integral calculation

@@
 \end{remark}
-\begin{proof}
+\begin{proof}[Proof of Lemma~\ref{lem:thimble_proj_formula-proof}]
 We first recast the integral $I_a$ into the position domain.
@@
 \begin{remark}
-\begin{revised}We can use the thimble projection formula to show that each function $\iota_\alpha$ is resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
+We can use the thimble projection formula to show that each function $\iota_\alpha$ is resurgent, in the sense of \'{E}calle~\cite[Section~1]{EcalleI}.
 Let $\mathcal{J}_\alpha(\beta)$ be the straight path from $\zeta = \alpha$ to $\zeta = \beta$ in $\C$.
@@
 This lets us analytically continue $\int_{\mathcal{C}_a^\theta(\zeta)} \nu$ to a star-shaped domain $\Omega_\alpha \subset \C$.
-Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\zeta = \infty$, as shown in Figure~\ref{Fig:slit domain}.\end{revised}
+Intuitively, $\Omega_\alpha$ is constructed by drawing rays from $\zeta = \alpha$ through all of the other critical values, and then cutting $\C$ along the parts of those rays that go from the other critical values to $\zeta = \infty$, as shown in Figure~\ref{Fig:slit domain}.
 \begin{center}
@@
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
-We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length isproportional to $st$, giving
+We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length is proportional to $st$, giving
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
@@
 \color{black}
-\subsubsection{Solving the differential equation}
+\subsubsection{Solving the differential equation}\label{sec:solve-cantilever-eqn}
 We seek functions $v$ and points $\zeta = \alpha$ for which the Laplace transform $\laplace_{\zeta, \alpha} v$ satisfies the differential equation~\eqref{eqn:triangular_cantilever}.
@@
 \subsubsection{Expressing the solutions as thimble integrals}
-We can now use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to express the solutions found above as thimble integrals.
+If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to find $v_\text{uni}$.
+Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.
+\begin{todo}[Do the argument in reverse, starting with the expression that looks like $v_\text{uni}$]\end{todo}
+
+Suppose $V_\alpha$ can be expressed as a thimble integral.
+
+\begin{todo}[The narrative here doesn't seem to make sense.
+Rewrite]\end{todo} \begin{old}We can now use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to express the solutions found above as thimble integrals.
 In terms of the Jacobi elliptic function $\operatorname{sd}$, we have
@@
 \end{align*}
+\end{old}
 \begin{todo}[Note that this presents $V_\alpha$ as the Laplace transform of $v_\text{uni}$.]\end{todo} \begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}

### 2024-11-06 borel-regularity.tex
Fill in proof details in formal-analytic bridge

@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional algebraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals \cite{deligne2007singularites,Maxim_lectures}.
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional algebraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals~\cite{deligne2007singularites,Maxim_lectures,kontsevich-Fourier-exact,kontsevich2024holomorphic,fresan-notes}.
 \subsubsection{Thimble integrals in physics}
@@
 %
-\begin{todo}[Mention \cite{kontsevich-Fourier-exact}]\end{todo} Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
+Thimble integrals are traditionally understood through their asymptotics, which can be found with the saddle point approximation~\cite{andersen2020resurgence,delabaere-howls,delabaere_dillinger_pham,Delabaere-Pham99,dingle1973asymptotic,Malgrange22,Pham83}.
 The asymptotic expansion of a thimble integral is typically divergent, but its Borel sum often matches the integral it came from.
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$, and let $\Lambda' = \Lambda / \cos(\Theta)$.
-Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
+Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$, and let $\Lambda' = \Lambda / \cos(\Theta)$.\textcolor{red}{Who is $\Lambda$?
+Add assumption on $\sigma$} Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
 \[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
@@
 \end{center}
-Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
+Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
+The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
 Parameterize it using the arc length parameter $t$ which is zero where the rays meet.
@@
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
-\begin{todo}[Justify bound and add pictures.]\end{todo}
+\begin{todo}[Justify bounds in words.]\end{todo}
+\begin{center}
+\begin{tikzpicture}
+\setfiberscale{2.5}
+\pgfmathsetmacro{\rshade}{1.5*\rfiber}
+\newcommand{\dis}{1.25}
+\renewcommand{\phase}{0}
+\newcommand{\spread}{55.5}
+\pgfmathsetmacro{\peakdis}{\dis / cos(\spread)}
+
+\newcommand{\pathspread}{35}
+\newcommand{\angmarkrad}{1}
+\newcommand{\distmarkrad}{2.5}
+\pgfmathsetmacro{\bdrydist}{\distmarkrad*sin(\pathspread-\spread)}
+
+\begin{fiber}[shade, phase=\phase+2*\pathspread-\spread, dis=\peakdis]
+
+% grid lines and stuff
+\genfibercontent[dual]
+
+% the construction lines
+\begin{scope}[pwbeige!80!black]
+\draw (\peakdis, 0) +(-\phase-\spread-90:1.5*\rshade) -- +(0, 0) -- +(-\phase+\spread+90:1.5*\rshade);
+\draw (\peakdis, 0) -- +(\phase+2*\pathspread-\spread+90:1.5*\rshade);
+\draw[shorten <=0.3mm, shorten >=0.4mm] (\peakdis, 0) ++(\phase+\spread+90:\angmarkrad) arc[start angle=\phase+\spread+90, delta angle=\pathspread-\spread, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-90+0.5*\spread+0.5*\pathspread)] {$\tfrac{\varepsilon}{2}$};
+\draw[shorten <=0.4mm, shorten >=0.3mm] (\peakdis, 0) ++(\phase+\pathspread+90:\angmarkrad) arc[start angle=\phase+\pathspread+90, delta angle=\pathspread-\spread, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-90+1.5*\pathspread-0.5*\spread)] {$\tfrac{\varepsilon}{2}$};
+\draw[shorten >=0.3mm] (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) -- ++(\phase+2*\pathspread-\spread-180:\bdrydist) coordinate[midway] (dist-anchor);
+\end{scope}
+
+% the path
+\draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
+%%\draw (\peakdis, 0) ++(\phase+\pathspread+90:0.75*\distmarkrad) node[anchor=180+\pathspread] {$t$};
+\draw (\peakdis, 0) ++(\phase+\pathspread+90:0.7*\distmarkrad) node[circle, inner sep=0.5, fill=pwbeige!10] {$t$};
+\draw (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) +(\pathspread:1mm) -- +(180+\pathspread:1mm);
+
+% coordinate label
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$z$};
+\end{fiber}
+
+% point at node boundary
+\begin{scope}[pwbeige!80!black]
+\draw[out=165, in=30, -stealth] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$} to (1.9, 1.6);
+\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
+\end{scope}
+\end{tikzpicture}
+\captionof{figure}{\begin{todo}[\ldots] Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$.\end{todo}}
+\end{center}
 
@@
 \begin{notation*}
- When $\alpha=\beta$ we denote $\ast_{\zeta,\alpha,\beta}$ simply by $\ast_{\zeta,\alpha}$.
-For $\alpha=\beta=0$, Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we will denote $\ast_{\zeta,0}$ simply by $\ast_\zeta$.
-\begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
+\begin{revised}We denote $\ast_{\zeta,\alpha,\alpha}$ by $\ast_{\zeta,\alpha}$ for short.
+The definition of $\ast_{\zeta, 0, 0}$ given by Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we denote this operation simply by $\ast_\zeta$.\end{revised} \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
 \end{notation*}
@@
 \begin{proof}
+From Definition~\ref{def:convolution}, we get the bound
 \begin{align*}
@@
 \end{align*}
-where we use $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$. 
-Since $\phi$ and $\psi$ have bounded norms,
+using the fact that $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$ in the second step. We can then bound the right-hand side in terms of the norms of $\phi$ and $\psi$:
 \begin{align*}
@@
 \end{proof}
-The product of two Laplace transforms based at different points is the Laplace transform of the convolution.
+The product of two Laplace transforms based at different points is the Laplace transform of a convolution.
 \begin{prop}
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_0^\Lambda$.
-Noting that \begin{revised}$|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray \begin{todo}[check; specify domain of ray]\end{todo}\end{revised},\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} we deduce that
+\begin{revised}Observe that $\widehat{\Omega}_0^\Lambda$ is a union of half-planes, the distance to the boundary of each half-plane increases linearly along any ray that intersects the half-plane, and $\Delta$ is the infimum of these distances.
+From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\end{revised}\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
 \begin{align*}
@@
 \end{align*}
-along any ray \begin{todo}[specify domain of ray]\end{todo}. This, as discussed above, proves the desired result.
+along any ray \begin{revised}that intersects $\widehat{\Omega}_0^\Lambda$\end{revised}. This, as discussed above, proves the desired result.
 \end{proof}
@@
 However, since the Airy function is a classic example in the study of Borel summation and resurgence, it may be worth seeing on its own.
-In Appendix~\ref{airy-appendix}, we give a detailed treatment of the Airy function, specializing our arguments from the general case.
+In Appendix~\ref{airy-appendix}, we give a detailed treatment of the Airy function, specializing our arguments.
 
@@
 \subsubsection{Expressing the solutions as thimble integrals}
-If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to find $v_\text{uni}$.
+If we had a thimble integral expression for $V_\alpha$, we could use the thimble projection formula, as written in equation~\eqref{eqn:formula-proof}, to find $v_\text{uni}$.
 Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.
 \begin{todo}[Do the argument in reverse, starting with the expression that looks like $v_\text{uni}$]\end{todo}
-
-Suppose $V_\alpha$ can be expressed as a thimble integral.
+\begin{revised}
+Equation~\eqref{eqn:formula-proof} becomes
+\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
+\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)d\zeta. \]
+\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = d\Big[ \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)\Big]. \]
+If we guess that $\operatorname{start} \mathcal{C}_a^\theta(\zeta) = -\operatorname{end} \mathcal{C}_a^\theta(\zeta)$, we can rewrite the equation above as
+\[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
+\end{revised}
+
+\begin{revised}
+We assume that $V_\alpha$ has the following expression 
+\[\int_{\mathcal{C}_a^\theta}e^{-z f} du\]
+for unknown function $f$, and $\mathcal{C}_a^\theta:=f^{-1}\big((\alpha,e^{i\theta}\infty)\big)$ with $f(a)=\alpha$. Then, for $\zeta=f$ equation~\eqref{thimble-difference} becomes
+\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}. \]
+Let us guess that $f$ maps the real $u$ axis into the real $\zeta$ axis, so $f$ is equivariant with respect to conjugation and the path $\mathcal{C}_a^\theta$ is symmetric with respect to conjugation.
+Then we can rewrite the equation above as
+\begin{align*}
+\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \frac{du}{df} \\
+\frac{1}{2} \left[ \frac{df}{\sqrt{\zeta^4 - \omega^2}} \right] & = du \\
+\frac{1}{2} \left[ \frac{f^* d\zeta}{\sqrt{\zeta^4 - \omega^2}} \right] & = du
+\end{align*}
+\begin{align*}
+\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \frac{du}{df} \\
+\frac{1}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = \frac{du}{df} \\
+\frac{\omega^{-1/2}}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;\frac{du}{df} \\
+F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u\,,
+\end{align*}
+% \begin{align*}
+% \frac{1}{\sqrt{\zeta^4-\omega^2}}&=2 \frac{du}{df}\\
+% \frac{1}{\sqrt{1 - \omega^{-2} \zeta^4}} &= 2i\omega^{1/2}\bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)} \\
+% \frac{1}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i\omega^{1/2}\bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}\\ 
+% \frac{\partial}{\partial\zeta}\Big[F(\omega^{-1/2} \zeta; i)\Big] &= \bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}
+% \end{align*}
+where the function $F$ is the inverse of the elliptic sin function $\operatorname{sn}$
+\begin{equation}
+F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,.
+\end{equation}
+\end{revised}
+%Suppose $V_\alpha$ can be expressed as a thimble integral.
 
@@
 \begin{prop}\label{prop:shifting}
-Consider a germ $\phi \in \zeta^\rho\,\mathcal{O}_{\zeta=0}$. When $\rho$ is a non-integer greater than $-1$,
+Consider a germ $\phi \in \zeta^\rho\,\mathcal{O}_{\zeta=0}$. When $\rho$ is a non-integer greater than~$-1$,
 \[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \phi = 0, \]

### 2024-11-13 borel-regularity.tex
Rewrite cantilever thimble integral argument

@@
 \end{align*}
-where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$.
-When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows.
+where $c_{z, \theta} = \cos\big(\arg(z) + \theta\big)$.
+When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta_\alpha|$ grows.
 This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \begin{prop}\label{prop:inverse_laplace_analytic}
-Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$, and let $\Lambda' = \Lambda / \cos(\Theta)$.\textcolor{red}{Who is $\Lambda$?
-Add assumption on $\sigma$} Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
+Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$.
+Choose some $\sigma > 0$ and $\Lambda \ge 0$, and let $\Lambda' = \Lambda / \cos(\Theta)$.
+Under the conditions of Proposition~\ref{prop:laplace-cont}, for any $\varepsilon \in (0, \tfrac{\Theta}{2})$, the Laplace transform
 \[ \laplace_{\zeta_\alpha, 0}^\theta \maps \singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \]
@@
 \[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
-\begin{todo}[Justify bounds in words.]\end{todo}
+\begin{todo}[Justify bounds in words: Fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$, and look at the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, as shown in Figure~\ref{fig:bound-real-part}.
+The curve $\mathcal{C}$ lies entirely outside this half-plane, so we have $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout it.
+Each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$.
+Therefore, as we move along the curve $\mathcal{C}$, the distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at rate $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.]\end{todo}
 \begin{center}
@@
 \end{tikzpicture}
-\captionof{figure}{\begin{todo}[\ldots] Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$.\end{todo}}
+\captionof{figure}{\begin{todo}[\ldots] Polish figure: label half-plane $(>)$ instead of boundary $(=)$.
+Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$.
+Maybe add some figure copies (without the extra label stuff) where the angle of the half-plane varies.\end{todo}}\label{fig:bound-real-part}
 \end{center}
@@
 This means that $|E_n| \lesssim \Delta^{-\rho-n-1}$, where $\Delta$ is the distance to the boundary of $\widehat{\Omega}_0^\Lambda$.
-\begin{revised}Observe that $\widehat{\Omega}_0^\Lambda$ is a union of half-planes, the distance to the boundary of each half-plane increases linearly along any ray that intersects the half-plane, and $\Delta$ is the infimum of these distances.
-From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\end{revised}\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
+Observe that $\widehat{\Omega}_0^\Lambda$ is a union of half-planes, the distance to the boundary of each half-plane increases linearly along any ray that intersects the half-plane, and $\Delta$ is the infimum of these distances.
+From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
 \begin{align*}
@@
 \end{align*}
-along any ray \begin{revised}that intersects $\widehat{\Omega}_0^\Lambda$\end{revised}. This, as discussed above, proves the desired result.
+along any ray that intersects $\widehat{\Omega}_0^\Lambda$. This, as discussed above, proves the desired result.
 \end{proof}
@@
 \end{equation}
-where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}([\alpha,\zeta e^{i\theta}])$.
+where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$.
 Notice that $\mathcal{C}_a^\theta(\zeta)$ starts and ends in $f^{-1}(\zeta)$.
@@
 Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.
-\begin{todo}[Do the argument in reverse, starting with the expression that looks like $v_\text{uni}$]\end{todo}
 \begin{revised}
+We hope to express $V_\alpha$ in the form
+\[ \int_{\mathcal{C}_a^\theta}e^{-z f} du, \]
+where $f$ is a holomorphic function on $\C$, $u$ is the standard coordinate on $\C$, $a$ is a critical point of $f$ with $f(a) = \alpha$, and $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$.
+We know from equation~\eqref{thimble-difference} that this thimble integral will evaluate to $V_\alpha$ as long as
+\begin{equation}\label{eqn:cantilever-thimble-difference}
+\frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)},
+\end{equation}
+where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$.
+Recognizing the left-hand side, $v_\text{uni}$, as the integrand of an elliptic integral, we guess that
+\[ f = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)\,, \]
+since the Jacobi elliptic function $\operatorname{sd}$ is the inverse of an incomplete elliptic integral.
+To confirm that this equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we first use Jacobi's transformations to rewrite $f$ in terms of $\operatorname{sn}$:
+\[ f = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big)\,. \]
+In terms of the incomplete elliptic integral
+\[ F(x; k) := \int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,, \]
+we then have
+\begin{align*}
+F(\omega^{-1/2} f; i) & = 2i \omega^{1/2} u \\
+\frac{\omega^{-1/2}\;df}{\sqrt{1 - (\omega^{-1/2} f)^4}} & = 2i \omega^{1/2}\;du \\
+\frac{1}{2i \omega \sqrt{1 - \omega^{-2} f^4}} & = \frac{du}{df}\,.
+\end{align*}
+We can simplify this to
+\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
+by taking the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
+so we have
+\begin{equation}\label{eqn:cantilever-endpoint}
+\frac{1}{2}\left[\frac{1}{\sqrt{\zeta^4 - \omega^2}}\right] = \left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,,
+\end{equation}
+with the branch of the square root determined by analytic continuation along $\mathcal{C}_a^\theta$ from $a$.
+
+From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd at $a$ with respect to $u$, implying that
+\[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
+We can therefore rewrite equation~\eqref{eqn:cantilever-endpoint} as
+\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,, \]
+confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du. \]
+
+%%Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
+%%\begin{equation}
+%%F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
+%%\end{equation}
+\end{revised}
+
+\begin{draft}
 Equation~\eqref{eqn:formula-proof} becomes
@@
 \[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
-\end{revised}
-
-\begin{revised}
+\end{draft}
+
+\begin{draft}
 We assume that $V_\alpha$ has the following expression 
@@
 for unknown function $f$, and $\mathcal{C}_a^\theta:=f^{-1}\big((\alpha,e^{i\theta}\infty)\big)$ with $f(a)=\alpha$. Then, for $\zeta=f$ equation~\eqref{thimble-difference} becomes
-\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}. \]
+\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}. \]
 Let us guess that $f$ maps the real $u$ axis into the real $\zeta$ axis, so $f$ is equivariant with respect to conjugation and the path $\mathcal{C}_a^\theta$ is symmetric with respect to conjugation.
@@
 \begin{align*}
-\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \frac{du}{df} \\
+\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)} \\
 \frac{1}{2} \left[ \frac{df}{\sqrt{\zeta^4 - \omega^2}} \right] & = du \\
@@
 \end{align*}
-% \begin{align*}
-% \frac{1}{\sqrt{\zeta^4-\omega^2}}&=2 \frac{du}{df}\\
-% \frac{1}{\sqrt{1 - \omega^{-2} \zeta^4}} &= 2i\omega^{1/2}\bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)} \\
-% \frac{1}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i\omega^{1/2}\bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}\\ 
-% \frac{\partial}{\partial\zeta}\Big[F(\omega^{-1/2} \zeta; i)\Big] &= \bigg[\frac{du}{df}\bigg]_{\mathrm{start}\, \mathcal{C}_a^\theta(\zeta)}^{\mathrm{end}\, \mathcal{C}_a^\theta(\zeta)}
-% \end{align*}
 where the function $F$ is the inverse of the elliptic sin function $\operatorname{sn}$
@@
 \end{equation}
-\end{revised}
+\end{draft}
 %Suppose $V_\alpha$ can be expressed as a thimble integral.

### 2024-11-14 borel-regularity.tex
Justify bound in inverse Laplace regularity proof

@@
 as shown in Figure~\ref{fig:ref-path}. On $\Omega_\alpha^\varepsilon \times \mathcal{C}$, we have
-\[ \Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,. \]
-\begin{todo}[Justify bounds in words: Fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$, and look at the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, as shown in Figure~\ref{fig:bound-real-part}.
-The curve $\mathcal{C}$ lies entirely outside this half-plane, so we have $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout it.
-Each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$.
-Therefore, as we move along the curve $\mathcal{C}$, the distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at rate $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.]\end{todo}
+\begin{equation}\label{eqn:inverse-laplace-exp-bound}
+\Re(z\zeta_\alpha) \le |\zeta_\alpha| \big(\Lambda' - \sin(\varepsilon/2)\,|t|\big)\,.
+\end{equation}
+\begin{revised}To see why this bound holds, fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$.
+Consider the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, illustrated in Figure~\ref{fig:bound-real-part} for an extreme value of $\zeta_\alpha$.\end{revised}
 \begin{center}
@@
 \begin{scope}[pwbeige!80!black]
-\draw[out=165, in=30, -stealth] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$} to (1.9, 1.6);
+\draw[out=170, in=25] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$} to (2.1, 1.7);
 \draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
@@
 \end{tikzpicture}
-\captionof{figure}{\begin{todo}[\ldots] Polish figure: label half-plane $(>)$ instead of boundary $(=)$.
-Mention that the phase of $\zeta_\alpha$ has been chosen to bring the line $\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$ as close as possible to $\mathcal{C}$.
-Maybe add some figure copies (without the extra label stuff) where the angle of the half-plane varies.\end{todo}}\label{fig:bound-real-part}
+\captionof{figure}{\begin{revised}For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$.
+This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.\end{revised} \begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
 \end{center}
+\begin{revised}By construction, the curve $\mathcal{C}$ lies entirely outside this half-plane, which means that $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout $\mathcal{C}$.
+In fact, each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$.
+Therefore, as we move outward along $\mathcal{C}$, our distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at a rate of at least $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.\end{revised}
 

### 2024-11-14 borel-regularity.tex
Remove cantilever thimble integral drafts

@@
 Since we found $v_\text{uni}$ in Section~\ref{sec:solve-cantilever-eqn}, we can work backwards from equation~\eqref{thimble-difference} to guess a thimble integral expression for $V_\alpha$.
-\begin{revised}
 We hope to express $V_\alpha$ in the form
 \[ \int_{\mathcal{C}_a^\theta}e^{-z f} du, \]
-where $f$ is a holomorphic function on $\C$, $u$ is the standard coordinate on $\C$, $a$ is a critical point of $f$ with $f(a) = \alpha$, and $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$.
+where the function $f$ is a holomorphic function on $\C$, the function $u$ is the standard coordinate on $\C$, the point $a$ is a critical point of $f$ with $f(a) = \alpha$, and the path $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$.
 We know from equation~\eqref{thimble-difference} that this thimble integral will evaluate to $V_\alpha$ as long as
@@
 confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
-\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du. \]
-
-%%Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
-%%\begin{equation}
-%%F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
-%%\end{equation}
-\end{revised}
-
-\begin{draft}
-Equation~\eqref{eqn:formula-proof} becomes
-\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
-\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)d\zeta. \]
-\[ \frac{d\zeta}{\sqrt{\zeta^4-\omega^2}} = d\Big[ \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right)\Big]. \]
-If we guess that $\operatorname{start} \mathcal{C}_a^\theta(\zeta) = -\operatorname{end} \mathcal{C}_a^\theta(\zeta)$, we can rewrite the equation above as
-\[ \frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\,du \right). \]
-\end{draft}
-
-\begin{draft}
-We assume that $V_\alpha$ has the following expression 
-\[\int_{\mathcal{C}_a^\theta}e^{-z f} du\]
-for unknown function $f$, and $\mathcal{C}_a^\theta:=f^{-1}\big((\alpha,e^{i\theta}\infty)\big)$ with $f(a)=\alpha$. Then, for $\zeta=f$ equation~\eqref{thimble-difference} becomes
-\[ \frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}. \]
-Let us guess that $f$ maps the real $u$ axis into the real $\zeta$ axis, so $f$ is equivariant with respect to conjugation and the path $\mathcal{C}_a^\theta$ is symmetric with respect to conjugation.
-Then we can rewrite the equation above as
-\begin{align*}
-\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)} \\
-\frac{1}{2} \left[ \frac{df}{\sqrt{\zeta^4 - \omega^2}} \right] & = du \\
-\frac{1}{2} \left[ \frac{f^* d\zeta}{\sqrt{\zeta^4 - \omega^2}} \right] & = du
-\end{align*}
-\begin{align*}
-\frac{1}{2} \left[ \frac{1}{\sqrt{\zeta^4 - \omega^2}} \right] & = \frac{du}{df} \\
-\frac{1}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = \frac{du}{df} \\
-\frac{\omega^{-1/2}}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;\frac{du}{df} \\
-F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u\,,
-\end{align*}
-where the function $F$ is the inverse of the elliptic sin function $\operatorname{sn}$
-\begin{equation}
-F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,.
-\end{equation}
-\end{draft}
-%Suppose $V_\alpha$ can be expressed as a thimble integral.
-
-\begin{todo}[The narrative here doesn't seem to make sense.
-Rewrite]\end{todo} \begin{old}We can now use the thimble projection formula, as written in equation~\eqref{thimble-difference}, to express the solutions found above as thimble integrals.
-In terms of the Jacobi elliptic function $\operatorname{sd}$, we have
-\begin{equation}\label{eq:cantilever-thimble}
-V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du,  \end{equation}
-where $a$ is a preimage of $\zeta = \alpha$ under the map $\zeta = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)$.
-\begin{todo}[\textbf{A} Show thimble picture.]\end{todo} Since exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
-
-To confirm equation~\eqref{eq:cantilever-thimble}, use Jacobi's transformations to rewrite the relationship between $\zeta$ and $u$ in terms of $\operatorname{sn}$.
-\[ \zeta = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big). \]
-\begin{verify}
-Jacobi's imaginary transform gives
-\begin{align*}
--i \operatorname{sn}\big(2i \omega^{1/2} u, \sqrt{1-\sqrt{2}^2}\big) & = \operatorname{sc}(2\omega^{1/2} u, \sqrt{2}) \\
-\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = i \operatorname{sc}\big(2\omega^{1/2} u,\sqrt{2}\big)
-\end{align*}
-Jacobi's real transform gives
-\begin{align*}
-\frac{1}{2\omega^{1/2}} \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
-i \operatorname{sc}\big(2\omega^{1/2} u, \tfrac{1}{1/\sqrt{2}}\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big).
-\end{align*}
-Altogether, we have
-\begin{align*}
-\operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i \omega^{1/2} \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \\
-\omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big) & = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)
-\end{align*}
-\end{verify}
-Knowing that the inverse of $\operatorname{sn}$ is the incomplete elliptic integral
-\begin{equation}
-F(x;k):=\int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,,
-\end{equation}
-we learn that
-\begin{align*}
-F(\omega^{-1/2} \zeta; i) & = 2i \omega^{1/2} u \\
-\frac{\omega^{-1/2}\;d\zeta}{\sqrt{1 - (\omega^{-1/2} \zeta)^4}} & = 2i \omega^{1/2}\;du \\
-\frac{d\zeta}{2i \omega \sqrt{1 - \omega^{-2} \zeta^4}} & = du \\
-\frac{1}{2}\left[\frac{d\zeta}{\sqrt{\zeta^4 - \omega^2}}\right] & = du.
-\end{align*}
-\end{old}
-\begin{todo}[Note that this presents $V_\alpha$ as the Laplace transform of $v_\text{uni}$.]\end{todo} \begin{todo}[Explain how symmetry of thimble gives $v_\text{uni}$ under thimble projection formula.]\end{todo}
-%\subsection{The anharmonic oscillator}\label{sec:anharmonic_oscillator}
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,. \]
+Since the exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
 %

### 2024-11-14 borel-regularity.tex
Remove commented-out draft text

@@
 Each translation chart $\zeta$ gives a different version of the Laplace transform, whose associated frequency domain is the cotangent space $T^*_{\zeta = 0} B$.
-The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$.
-The details of this picture are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
+The frequency coordinate $z$ is a canonical coordinate on $T^*_{\zeta = 0}B$, or on $T^*_{\zeta = 0}B^{\otimes n}$ if $\zeta = 0$ is a singularity with cone angle $2\pi n$, as illustrated in Figure~\ref{fig:geometric-picture-intro}.
+The details of this perspective are discussed in Sections \ref{sec:geometry_laplace} and \ref{sec:geometry_borel}.
 \begin{center}
@@
 \captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point.
-The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
+The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}\label{fig:geometric-picture-intro}
 \end{center}
@@
 In both cases, we will call $z$ the {\em frequency coordinate} of $B$.
+Both cases are illustrated in Figure~\ref{fig:geometric-picture} below.
 \begin{center}
@@
 \captionof{figure}{The frequency coordinate $z$ on the cotangent spaces of an ordinary point and a singular point.
-The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}
+The singularity shown here has cone angle $6\pi$, like the singularities of the translation surface associated with the Airy function.}\label{fig:geometric-picture}
 \end{center}
@@
 \begin{equation}\label{eq: convolution_formal}
-\frac{\zeta^m}{m!} \ast_{\zeta} \frac{\zeta^n}{n!} = \frac{\zeta^{m+n+1}}{(m+n+1)!} \,.
+\frac{\zeta^m}{m!} \ast_\zeta \frac{\zeta^n}{n!} = \frac{\zeta^{m+n+1}}{(m+n+1)!} \,.
 \end{equation}
@@
 \end{align*}
-Furthermore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_{\zeta}\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
-\[\frac{\zeta^n}{n!}\ast_{\zeta}\delta\defeq\frac{\zeta^n}{n!}\,,\]
+Furthermore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_\zeta\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
+\[\frac{\zeta^n}{n!}\ast_\zeta\delta\defeq\frac{\zeta^n}{n!}\,,\]
 in other words, $\delta$ is the unit for the convolution. 
@@
 \subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
+\begin{brainstorm}
+\item It's probably not worth updating the convolutions to new notation.
+\end{brainstorm}
 The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
@@
 Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
-%However, if we consider a different fiber on $T^*B$, we have to modify the definition of convolution product in order to generalize properties (i) and (ii): indeed assuming $\series{\Phi}=\laplace_{\zeta_\alpha,0}\phi$ we have for every $\lambda\in (0,\infty)$
 Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
@@
 \end{proof}
-\color{black}
-
-%The space of $1$-Gevrey formal series is a $\C$-algebra with unit $1$, thus in order to prove that $\borel_\zeta$ is an algebra homomorphism between $\C\llbracket z^{-1}\rrbracket_1$ and $\C\lbrace\zeta\rbrace$ we should endow $\C\lbrace\zeta\rbrace$ with the convolution product and with the formal unit $\delta\defeq\borel_\zeta 1$.
-
-%Let $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ (where we assume they are series on the fiber over $\zeta=0$), then 
-%\[\borel_\zeta(\series{\Psi}\series{\Phi})=:\series{\psi}\ast\series{\phi}.\]
-%In addition, as proved in \cite[Definition 5.12 and Lemma 5.14]{diverg-resurg-i}, the convolution product $\ast$ can be explicitly characterized as \textcolor{orange}{[maybe just define it on holomorphic functions first, and then extend to all formal series by linearity via Taylor series]}
-%\[
- %   \series{\psi}\ast\series{\phi}=\int_0^{\zeta}d\zeta' \series{\psi}(\zeta-\zeta')\series{\phi}(\zeta').
-%\]
-%\begin{lemma}
-%The convolution product induces an algebra structure on the space $\singexp{\sigma}{\Lambda}(\Omega)$.
-%\end{lemma}
-%\begin{proof}
-%    Let $\series{\phi},\series{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$, then a simple computation shows $\series{\phi}\ast\series{\psi}\in\singexp{\sigma}{\Lambda}(\Omega)$.
-%\begin{verify}
- %   \begin{align*}
-  %      | \series{\phi}\ast\series{\psi}|&=\left|\int_0^\zeta\series{\phi}(\zeta-\zeta')\series{\psi}(\zeta')\, d\zeta'\right|\\
-   %     &\le \int_0^\zeta |\series{\phi}(\zeta-\zeta')||\series{\psi}(\zeta')|\, d\zeta'\\
-    %    &\le ||\series{\psi}||_{\sigma,\Lambda} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta'|^{\sigma}e^{\Lambda|\zeta'|}\, d\zeta'\\
-    %    &\le ||\series{\psi}||_{\sigma,\Lambda} |\zeta|^{\sigma}e^{\Lambda|\zeta|} \int_0^\zeta\series{\phi}(\zeta-\zeta')|\zeta-\zeta'|^{\sigma}e^{\Lambda|\zeta-\zeta'|}\, d\zeta'\\
-    %    &\le |\zeta|^{\sigma}e^{\Lambda|\zeta|} ||\series{\psi}||_{\sigma,\Lambda} ||\series{\phi}||_{\sigma,\Lambda}. 
-    %\end{align*}
-%\end{verify}
-%\end{proof}
-%We deduce that also the Laplace transform is a $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to the space of holomorphic functions on $H_\theta$.  
-%\begin{prop}
- %   Let $\sigma>-1$, $\Lambda>0$ and $\theta\in [0,2\pi)$.
-Then the Laplace transform $\laplace_{\zeta,0}^\theta$ is $\C$-algebra homomorphism from $\singexp{\sigma}{\Lambda}(\Omega)$ to $\mathcal{O}(H_\theta)$.
-%\end{prop}
-%\begin{proof}
-%First of all, from the properties of $\laplace_{\zeta,0}^\theta$ we know that if $\phi, \psi\in\singexp{\sigma}{\Lambda}(\Omega)$, then
-%\[\laplace_{\zeta,0}^\theta\big[{\phi}\ast{\psi}\big]=\laplace_{\zeta,0}^\theta\big[{\phi}\big]\laplace_{\zeta,0}^\theta\big[{\psi}\big],\]
-%see for instance \cite[Theorem 2.39]{laplace-tfm}.
-Then we should prove that $\delta$ is a unit: from its definition and the fact that $\borel_\zeta$ is the formal inverse of $\laplace_{\zeta,0}$, we deduce that
- %   \[
-%\laplace_{\zeta,0}^\theta\big[\delta\big]:=\laplace_{\zeta,0}^\theta\big[\borel_\zeta(1)\big]=1.
- %   \]
-%Thus, $\delta$ behaves as a Dirac delta distribution acting on $\singexpalg{\sigma}(\Omega)$. Then, if ${\phi}\in\singexp{\sigma}{\Lambda}(\Omega)$
-  %   \begin{align*}
-%\big[\delta\ast\phi\big](p)&=\int_0^{\zeta(p)} \delta(\zeta(p)-\zeta)\phi(\zeta) \, d\zeta=\phi(p)
- %   \end{align*}
-%\end{proof}
-%
 %
@@
 In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
-\color{black}
 \end{todo}
@@
 \end{verify}
-\color{black}
 \subsubsection{Solving the differential equation}\label{sec:solve-cantilever-eqn}
@@
 \end{align*}
- where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast_{\zeta} \zeta^{-5/6}$.
-%Notice that $\tilde{W}_{1,2}(\tfrac{2}{3}\hbar)=\series{\Phi}_{\pm}(z)$ for $\hbar=z^{-1}$, hence 
-%
-%\begin{align*}
-%\series{\phi}_{+}(\zeta)&=\borel\tilde{W}_{1}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta-\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right) \\
-%\series{\phi}_{-}(\zeta)&=\borel\tilde{W}_{2}(\tfrac{2}{3}\zeta)=\frac{1}{2\pi}\delta+\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right) 
-%\end{align*}
-%which up to a constant factor for $\delta$, they agree with our results.
+ where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast_\zeta \zeta^{-5/6}$.
 

### 2024-11-14 borel-regularity.tex
Do some checks and cleanup

@@
 On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
-\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-\alpha z} z^{-n-1} \big]=e^{-\alpha z} z^{-n-1}. \]
-The action of $\borel_\zeta$ extends to all of $e^{-\alpha z} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
+\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha} z^{-n-1} \big]=e^{-z\alpha} z^{-n-1}. \]
+The action of $\borel_\zeta$ extends to all of $e^{-z\alpha} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
 \end{definition}
@@
 \begin{align*}
-e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
-\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-\alpha z} z^{-n-1}\big] & = z^{-n-1} \\
-\borel_{\zeta}\big[e^{-\alpha z}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
+e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-z\alpha} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
+\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-z\alpha} z^{-n-1}\big] & = z^{-n-1} \\
+\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
 \end{align*}
@@
 \begin{tikzcd}[every arrow/.append style={shift left}]
-\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-\alpha z} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
+\{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd,"\borel_\zeta"'] \arrow[rr,"e^{-z\alpha}"]& & e^{-z\alpha} \{z^{-1}, z^{-2}, z^{-3}, z^{-4}, \ldots \} \arrow[dd, "\borel_\zeta"] \\
 & & \\
@@
 
-We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-\alpha z} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
+We can extend the Borel transform to the fractionally shifted trans-monomial spaces $e^{-z\alpha} z^\tau\,\C\llbracket z^{-1} \rrbracket$, where $\tau \in \R \setminus \Z$, by applying the same argument to the definition at the end of Section~\ref{sec:geometry_borel}.
 We conclude, in particular, that
@@
 \begin{notation*}
-\begin{revised}We denote $\ast_{\zeta,\alpha,\alpha}$ by $\ast_{\zeta,\alpha}$ for short.
-The definition of $\ast_{\zeta, 0, 0}$ given by Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we denote this operation simply by $\ast_\zeta$.\end{revised} \begin{todo}[Make sure we've added the coordinate to $\ast$ everywhere else too.]\end{todo}
+We denote $\ast_{\zeta,\alpha,\alpha}$ by $\ast_{\zeta,\alpha}$ for short.
+The definition of $\ast_{\zeta, 0, 0}$ given by Definition~\ref{def:convolution} agrees with the standard definition of convolution \cite[Definition~5.12]{diverg-resurg-i}, so we denote this operation simply by $\ast_\zeta$.
 \end{notation*}
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[Equation 35]{mladenov2014advanced}.
+and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[equation~35]{mladenov2014advanced}.
 
 For $\mu \in (0, 1)$ and integers $n \ge 0$, fractional derivatives $\fracderiv{n+\mu}{\zeta}{0}$ are defined by composing $\fracderiv{\mu-1}{\zeta}{0}$ with powers of $\tfrac{\partial}{\partial \zeta}$.
-However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ do not commute~\cite[equation 54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero (see \cite[Section 1.3]{mladenov2014advanced}---original source \cite{podlubny}).
+However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ do not commute~\cite[equation~54]{mladenov2014advanced}.
+Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero~\cite[Section 1.3]{mladenov2014advanced}\cite{podlubny} \begin{todo}[Was there a reason to emphasize that Podlubny is the original source?]\end{todo}.
 We will use the {\em Riemann-Liouville} convention.
@@
 First, evaluate
-\begin{revised}
 \begin{align*}
 \partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta \big(\zeta-\zeta(a)\big)^{-\mu} \frac{\zeta(a)^k}{\Gamma(k+1)}\,d\zeta(a) \\
-& = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu} (\zeta t)^k\,\zeta\,dt \\
-& = \frac{\zeta^{k-(\mu-1)}}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\mu} t^k\,dt \\
+& = \frac{1}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (\zeta-\zeta t)^{-\mu}\,(\zeta t)^k\,\zeta\,dt \\
+& = \frac{\zeta^{k-(\mu-1)}}{\Gamma(1-\mu)\,\Gamma(k+1)} \int_0^1 (1-t)^{-\mu}\,t^k\,dt \\
 & = \frac{\zeta^{k-(\mu-1)}}{\Gamma\big(k-(\mu-1)+1\big)}
 \end{align*}
-\end{revised}
-by reducing the integral to Euler's beta function (see \cite[Identity 5.12.1]{dlmf}). This establishes that
+by reducing the integral to Euler's beta function~\cite[identity 5.12.1]{dlmf}. This establishes that
 \begin{equation}\label{frac-diff-laplace}
@@
 \begin{prop}\label{prop:frac-der-int-borel}
-Let for any $1$-Gevrey series $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, we have
+For any $1$-Gevrey series $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, we have
 \begin{enumerate}[label=(\roman*)]
@@
 \begin{proof}
-By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator\eqref{eq:hat_P}.
+By Proposition~\ref{prop:frac-der-int-borel}, the Borel transform $\series{\psi}_\alpha = \borel_\zeta \series{\Psi}_\alpha$ is a formal solution of the equation $\hat{\mathcal{P}}_\alpha \series{\psi}_\alpha = 0$, where $\hat{\mathcal{P}}_\alpha$ is the operator \eqref{eq:hat_P}.
 By Proposition~\ref{prop:gevrey_to_convergent}, the series $\series{\psi}_\alpha$ converges to a holomorphic function $\hat{\psi}_\alpha$ on some open set $\Omega_\text{near}$ created by restricting $\Omega_\alpha$ to a small disk around of $\zeta = \alpha$.
@@
 
-\begin{todo}[\textbf{A} Confirm that we should have $\zeta_\alpha$ rather than $\zeta$ here; \textit{V} Confirmed]\end{todo} Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
+Since the series $\series{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \C\{\zeta_\alpha\}$, the function $\hat{\psi}_\alpha$ lies in $\zeta_\alpha^{\tau_\alpha-1} \mathcal{O}(\Omega_\text{near})$.
 Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
@@
 \begin{remark}\label{rmk:Pham formula}
-When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham \cite[Equation 2.4, II partie]{pham} gives us an explicit expression for the singularity of the function $\iota_a$ from Lemma~\ref{lem:thimble_proj_formula-proof}.
+When $f$ and $\nu$ are polynomials and $X$ is $N$-dimensional, a result of Pham~\cite[equation 2.4, II partie]{pham} gives us an explicit expression for the singularity of the function $\iota_a$ from Lemma~\ref{lem:thimble_proj_formula-proof}.
 For some coefficients $c_k$ which depend on $f$, $\nu$, and the thimble $\mathcal{C}_a^\theta$, we have
@@
 where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
-From \cite[Equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n} \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
+From \cite[equations 10.40.2 and 10.17.1]{dlmf}, we learn that $K_{m/n} \sim \left(\tfrac{\pi}{2}\right)^{1/2} e^{-z} z^{-1/2}\,\series{W}_1$, with
 \begin{equation}\label{bessel-asymp-AL}
@@
 
-Equations \eqref{eqn:resurg-rel-1} and \eqref{eqn:resurg-rel-2} are a manifestation of the Stokes phenomenon in the position domain.
+Equations~\eqref{eqn:resurg-rel-1} and~\eqref{eqn:resurg-rel-2} are a manifestation of the Stokes phenomenon in the position domain.
 When we vary the direction of integration for the Laplace transform, we expect discontinuities at $\laplace^\pi_{\zeta,1}$ and $\laplace^0_{\zeta,-1}$, because each of the contours $\mathcal{J}^\pi_{\zeta,1}$ and $\mathcal{J}^0_{\zeta,-1}$ hits a singularity other than its starting point.

### 2024-11-14 borel-regularity.tex
Clean up bibliography

@@
 for $|\theta| < \tfrac{\pi}{2}$.
-This formula can be deduced, with a lot of finagling, from formulas 10.32(ii) and 10.27.4 of \cite{dlmf}\begin{todo}[Explain the finagling at least a little bit, maybe in a footnote]\end{todo}.
+This formula can be deduced, with a lot of finagling, from formulas 10.32.12 and 10.27.4 of \cite{dlmf}\begin{todo}[\textit{For after v2:} Explain the finagling at least a little bit, maybe in a footnote]\end{todo}.
 \begin{verify}

### 2024-11-14 borel-regularity.tex
Remove old titles and draft marker
Turn off most development environments
Leave revision highlighting on.

@@
 \newif\ifshowdraft
-\showdrafttrue
+\showdraftfalse
 \ifshowdraft
@@
 \title{The regularity of ODEs and thimble integrals \\
-with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}}
-%%\color{Tan} Borel summation as a regularization, and \\
-%%the regularity of ODEs and thimble integrals \\
-%%\color{CornflowerBlue} Borel summation as a regularization: \\
-%%Borel regularity for ODEs and thimble integrals \\
-%%Borel regularity for ODEs and Thimble Integrals
-%%\textcolor{Maroon}{Borel summation: new perspectives and examples (?)} \\
-%% \color{Violet}Differential equations, thimble integrals, \\
-%%and Borel summation as a regularization
+with respect to Borel summation}
 \author{Veronica Fantini and Aaron Fenyes}
+\date{}
 
@@
 \end{equation}
-%%\begin{old}
-%%\begin{equation}%%\label{resurgent-relation-1}
-%% v_1(\zeta+1+i\varepsilon)-v_1(\zeta+1-i\varepsilon)=2i \cos\big(\tfrac{m}{n}\pi\big) v_{-1}(\zeta)
-%%\end{equation}
-%%\end{old}
 where $v_1(p_-)$ and $v_1(p_+)$ respectively denote the evaluation of $v_1(p)$ by analytic continuation from from the regions $\Im(\zeta) < 0$ and $\Im(\zeta) > 0$.

### 2024-11-14 borel-regularity.tex
Remove extra sentence; check spellings
Remove more commented-out draft text.

@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
+\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighbourhood of $\zeta = 0$.
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
@@
 When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighborhood of the ray $\zeta \in e^{i\theta}[0, \infty)$.
+In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighbourhood of the ray $\zeta \in e^{i\theta}[0, \infty)$.
 \begin{center}
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behavior that changes sharply from from direction to the next.
-Formally, this behavior is captured in a {\em formal integral} solution: an expression
+Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from from direction to the next.
+Formally, this behaviour is captured in a {\em formal integral} solution: an expression
 \[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
@@
 When $\zeta = 0$ is a branch point, we can still use formula~\eqref{laplace:int} to define $\laplace_{\zeta, \alpha}^\theta \phi$ on $T_{\zeta = 0}^*B$, as long as we take care of a few subtleties.
-Thanks to the labeling choices we made in Section~\ref{sec:transl}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
+Thanks to the labelling choices we made in Section~\ref{sec:transl}, the extended angle $\theta \in \R$ still picks out a ray $\mathcal{J}_{\zeta, \alpha}^\theta$.
 The function $z$ is defined on $T_b^*B^{\otimes n}$, where $2\pi n$ is cone angle at $\zeta = 0$, so we pull it back to $T^*_{\zeta = 0} B$ along the $n$th-power map.
@@
 The inequality $\Re(e^{i\theta} z) > \Lambda$ cuts out a half-plane in $T_b^*B^{\otimes n}$, which pulls back to $n$ sector-like regions in $T_b^*B$ of angle $\pi/n$.
-We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centred around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
 \subsubsection{Change of translation chart}\label{sec:change-translation}
@@
 \end{center}
-Parameterize $\mathcal{C}$ using the arc length parameter $t$ which is zero at the midpoint of the circular arc part of $\mathcal{C}$.
 The path $\mathcal{C}$ is made of two rays, which meet at an angle of $\pi - \Theta + \varepsilon$.
@@
 \end{equation}
-\begin{revised}To see why this bound holds, fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$.
-Consider the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, illustrated in Figure~\ref{fig:bound-real-part} for an extreme value of $\zeta_\alpha$.\end{revised}
+To see why this bound holds, fix a value of the coordinate $\zeta_\alpha$ representing a point in $\Omega_\alpha^\varepsilon$.
+Consider the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$, illustrated in Figure~\ref{fig:bound-real-part} for an extreme value of $\zeta_\alpha$.
 \begin{center}
@@
 \end{tikzpicture}
-\captionof{figure}{\begin{revised}For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$.
-This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.\end{revised} \begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
+\captionof{figure}{For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$.
+This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.
+\begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
 \end{center}
-\begin{revised}By construction, the curve $\mathcal{C}$ lies entirely outside this half-plane, which means that $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout $\mathcal{C}$.
+By construction, the curve $\mathcal{C}$ lies entirely outside this half-plane, which means that $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) \le \Lambda'$ throughout $\mathcal{C}$.
 In fact, each of the rays that make up $\mathcal{C}$ makes an angle of at least $\varepsilon/2$ with the boundary line $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) = \Lambda'$.
-Therefore, as we move outward along $\mathcal{C}$, our distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at a rate of at least $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.\end{revised}
+Therefore, as we move outward along $\mathcal{C}$, our distance to the boundary of the half-plane $\Re\big(z \tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$ increases at a rate of at least $\sin(\tfrac{\varepsilon}{2})$ with respect to the arc length parameter $t$.
 
@@
 
-If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$.
+If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighbourhood of $\zeta = 0$.
 The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
@@
 To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
-On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$.
+On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighbourhood of $\zeta = 0$ in $\C$.
 Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
@@
 \begin{proof}
-Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counterclockwise of $b_-$ around $\zeta = \alpha$.
+Each point $b \in \Upsilon_\Delta$ has two preimages $b_+, b_- \in \Upsilon$, where $b_+$ is $2\pi$ counter-clockwise of $b_-$ around $\zeta = \alpha$.
 The {\em variation} operator $\var \maps \singexp{\sigma}{\Lambda}(\Upsilon) \to \singexp{\sigma}{\Lambda}(\Upsilon_\Delta)$, defined by\footnote{The target of the variation operator is a space of functions on $\Upsilon_\Delta$ because the variation is defined only on the overlap.
@@
 is bounded.
-A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
+A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighbourhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
 This operator is bounded, so its kernel is closed.
@@
 \end{enumerate}
-%%For each root $-\alpha$ of $P$, choose an open sector $\Omega_\alpha \subset \C$ that has $\zeta = \alpha$ at its tip, does not touch any other root of $P(-\zeta)$, and has an opening angle of $\pi$ or less.
 For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
@@
 \begin{todo}[Transition text]\end{todo}
-%%%\begin{itemize}
-%%%\item The set $\Omega_\alpha$ is star-shaped around $\zeta = \alpha$.
-In other words, for any $a \in \Omega_\alpha$, a straight path from $\zeta = \alpha$ to $a$ stays in $\Omega_\alpha$.
-Since $\Omega_\alpha$ does not contain $\zeta = \alpha$, we will always leave that starting point out of the path.
-%%%\item The set $\Omega_\alpha$ does not contain the tubular neighborhood of the other critical points, as shown in Figure \ref{Fig:domain}.
-\textcolor{orange}{[In ``Regular singular Volterra,'' we assume that $\Omega_\alpha$ does not touch any other critical point (that is, does not contain any other critical point in its closure).
-Under the star-shaped assumption, I think that implies avoiding tubular neighborhoods of the shadow rays.]}
-%%%\end{itemize}
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
@@
 The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
-%%\[ \hardpart^\alpha = -\tfrac{1}{P(-\zeta)} \circ \partial^{-1}_{\zeta, \alpha} \circ Q(-\zeta) \]
 \[ \hardpart^\alpha = -\tfrac{1}{p} \circ \partial^{-1}_{\zeta, \alpha} \circ q \]
 and the perturbation
-%%\[ \softpart^\alpha = \tfrac{1}{P(-\zeta)} \circ \partial^{-2}_{\zeta, \alpha} \circ R(\partial^{-1}_{\zeta, \alpha}) \]
 \[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
@@
 
-Using the properties of the Borel tranform acting on trans-mononials \ref{sec:action_transseries} we get 
+Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
 \begin{align*}
@@
 \captionof{figure}{The ray $\mathcal{J}^{\pi/8}_{\zeta, 1}$ in the $\zeta$ plane and its preimage $\mathcal{C}^{\pi/8}_1$ in the $u$ plane.
-The upper and lower halves of the $\zeta$ plane are colored light and dark, so their preimages form a checker pattern on the $u$ plane.
+The upper and lower halves of the $\zeta$ plane are coloured light and dark, so their preimages form a checker pattern on the $u$ plane.
 The region $\Re(\zeta) > 3$ and its preimage in the $u$ plane are shaded.}\label{fig:path_Airy}
@@
 \subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
-We can distill the most interesting parts of the Airy-Lucas function by writing
+We can distil the most interesting parts of the Airy-Lucas function by writing
 \[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighbourhood of $z \in [0, \infty)$.
 
@@
 
-Let us rewrite for simpicilty $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
+Let us rewrite for simplicity $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
 \begin{align*}
@@
 \subsubsection{Rewriting as a modified Bessel equation}
-Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing
+Starting from equation~\eqref{eqn:airy-distillation}, we can distil the most interesting part of the Airy function by writing
 \[ \Ai(y) = -\tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighbourhood of $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighbourhood of $z \in [0, \infty)$.
 %
@@
 \end{align*}
-Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
+Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighbourhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
 They give the values of $u$ after lifting to the incoming and outgoing branches of $\mathcal{C}^\theta_1$, respectively.
@@
 \begin{remark}
-The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB ansatz for a Schrodinger type equation is
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB ansatz for a Schr\"{o}dinger type equation is
 \begin{equation}
@@
 \end{equation}
-with $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. For the Airy-type Schrodinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
+with $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. For the Airy-type Schr\"odinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
 \[ q = \frac{2}{3}\eta x^{3/2}=\eta\int_0^x (x')^{1/2}\;dx' = \eta\int_{0}^x S_{-1}(x')\;dx'. \]
-We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schrodinger equation and the Borel transform of the associated ODE.
+We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')\;dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schr\"{o}dinger equation and the Borel transform of the associated ODE.
 \end{remark} 

### 2024-11-14 borel-regularity.tex
Revise comparison to physicists' Borel transform
Remove more commented-out draft text.

@@
 This subspace of holomorphic functions on $B$ has a $\C$-algebra structure, with product given by the \textit{convolution product}.
-% \begin{definition}\label{def:convolution}
-% Let $\phi,\psi$ be two holomorphic functions on $B$.
-Choose a translation coordinate $\zeta$ on $B$ and a base point $\zeta = \alpha$.
-The convolution product $\phi\ast_{\zeta,\alpha}\psi$ is the function on $B$ defined by the integral
-% \begin{equation}%%\label{eq:convolution_def}
-% \phi \ast_{\zeta, \alpha} \psi \defeq \int_{\substack{\mathcal{S}(\zeta)\times\mathcal{S}'(\zeta)\\ \zeta(a)+\zeta(a')=\zeta}} \phi(a)\,\psi(a')\,d\zeta(a),
-% \end{equation}
-% where $\mathcal{S}(\zeta)$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$, and $\mathcal{S}'(\zeta)$ is the line segment from $\zeta(a')=\zeta-\alpha$ to $\zeta(a')=0$.
-% \end{definition}
 \begin{definition}\label{def:convolution}
@@
 For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
-\begin{equation}%%\label{eq:convolution_def}
+\begin{equation}
 \phi \ast_{\zeta, \alpha, \beta} \psi \defeq \int_{\mathcal{S}_{\zeta, \alpha, \beta}} \phi(a)\,\psi(a')\,d\zeta(a)\,,
@@
 For $\nu \in (-\infty, 1)$, the \textit{fractional integral} $\partial^{\nu-1}_{\zeta, \alpha}$ is defined by
-%
-%%\[ [\partial^{\nu-1}_{\zeta, \alpha} \phi](a) \defeq \frac{1}{\Gamma(1-\nu)} \int_{\zeta=\alpha}^a \big(\zeta(a)-\zeta\big)^{-\nu} \phi \,d\zeta\,. \] 
 \[ \partial^{\nu-1}_{\zeta, \alpha} \phi \defeq \frac{1}{\Gamma(1-\nu)} \int_{\mathcal{S}_{\zeta,\alpha}} \big(\zeta-\zeta(a)\big)^{-\nu} \phi(a) \,d\zeta(a)\,, \]
 where $\mathcal{S}_{\zeta,\alpha}$ is the line segment from $\zeta(a)=\alpha$ to $\zeta(a)=\zeta$.
-
-%% Here, we are using Notation~\ref{notn:prod} and taking advantage of the fact that $\zeta(a') = \zeta - \zeta(a)$ along our integration path.
-
-%\footnote{\textcolor{magenta}{Why highlight this special case of the definition above?
-Is it important to use $\lambda$ instead of $\nu-1$?} For completeness we also give the \textcolor{magenta}{[redundant] definition} of the fractional integral $\partial_{\zeta_\alpha,0}^{-\lambda}$:
-% \begin{equation*}
-%     \partial_{\zeta_\alpha,0}^{-\lambda}\varphi(p)\defeq\frac{1}{\Gamma(\lambda)}\int_{\zeta_\alpha=0}^{p}(\zeta_\alpha(p)-\zeta_\alpha)^{\lambda-1} \varphi \, d\zeta_\alpha.
-% \end{equation*}
-% }
 \end{definition}
@@
 In particular, if $N=1$, the inverse Laplace transform of the function $I_a$ from equation~\eqref{exp-int} has a singularity of the form $\zeta_\alpha^{1/2}$, as we compute explicitly in the proof of Theorem~\ref{thm:maxim-proof}.
-%as computed in Remark~\ref{rmk:1/2-deriv} the inverse Laplace tranform of $z^{-1/2} I$ is the $1/2$-derivative of ${\iota}$, hence it has \textcolor{orange}{simple singularities (see Corollary~\ref{simple-res-thimble})}.
-\textcolor{magenta}{We expect this result to hold beyond the polynomial case.} We also expect that equation \eqref{eqn:formula-proof} can be generalized to the $N$-dimensional case replacing the $1/2$-derivative with the $N/2$ one.
 \end{remark}
@@
 
-%%From the argument in Section~\ref{big-idea}, we know that $\laplace_{\zeta, -1} v_{-1}$ satisfies equation~\eqref{eqn:mod-bessel-AL}, and can be written as $e^z V_{-1}$, where $V_{-1} = \laplace_{\zeta_{-1}, 0} v_{-1}$.
-Since $v_{-1}$, like our other solution, \textcolor{magenta}{has order $-1/2$}, the same decomposition $V_{-1} = z^{-1/2} W_{-1}$ makes $W_{-1}$ asymptotic to a scalar multiple of $1+O(z^{-1})$ at $z = \infty$.
-
 In this example, $v_1$ and $v_{-1}$ happen to be related by a symmetry: the M\"{o}bius transformation that pulls $\zeta$ back to $-\zeta$.
@@
 This solution arises as the Laplace transform $\laplace^\theta_{\zeta, 1} v_1$ of the function
-%%\[ v_1 = i \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{1}{2}-\frac{\zeta}{2}\right), \]
 \[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
@@
 In the other cases, we speculate that the Stokes constants are non-integer because there are multiple thimbles over each critical value.
-%
-%\textcolor{DarkCyan}{where the sign must be chosen so that $\pm\zeta$ stays in the left half-plane over the whole integration path (?)}.
-%For $z \in (0, \infty)$, the contour $\gamma_z$ runs \textcolor{magenta}{counterclockwise} around $[1, \infty)$, as shown below\textcolor{DarkCyan}{, so we have to choose the negative sign above (?)}.
-Let us assume $z \in (0, \infty)$ for the rest of the section.
-\textcolor{magenta}{[Our conclusions should probably hold whenever $\operatorname{Re}(z) > 0$.]}
-
-%The integrand is non-meromorphic at $\zeta = 1$. Along the branch cut $\zeta \in [1, \infty)$, its above-minus-below difference is
-%\begin{align*}
-%& -(2\pi i)\tfrac{n}{2\pi m} \sin(\tfrac{m}{n} \pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta) \\
-%= & -\tfrac{n}{m} \sinh(\tfrac{m}{n}\,i\pi)\,(\pm\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} {}_2F_1(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} \mp \tfrac{1}{2}\zeta),
-%\end{align*}
-%as given\footnote{Note that $\Gamma(\tfrac{3}{2}) \Gamma(\tfrac{1}{2})^{-1} = \tfrac{1}{2}$ and $\big[\Gamma(1 - \tfrac{m}{n})\Gamma(1 + \tfrac{m}{n})\big]^{-1} = \big[\Gamma(1 - \tfrac{m}{n})\,\tfrac{m}{n}\Gamma(\tfrac{m}{n})\big]^{-1} = \tfrac{n}{m\pi} \sin(\tfrac{m}{n} \pi)$.} by equation~15.2.3 from \cite{dlmf}.
-Hence, $K_{m/n}$ turns out to be the Laplace transform along $(1, \infty)$ of
-%\[ \tfrac{1}{2}\,(-\tfrac{1}{2}\zeta - \tfrac{1}{2})^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-%\color{DarkCyan}
-%Guessing the branch of the square root for consistency with the numerically checked result in Section~\ref{contour-argument}, we get
-%\[ \tfrac{i}{2}\,(\tfrac{1}{2} + \tfrac{1}{2}\zeta)^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2} + \tfrac{1}{2}\zeta). \]
-%In other words, $K_{m/n} = \tfrac{i}{2} \laplace_{\zeta, -1} v_{-1}$ with
-%\[ v_{-1} = \sqrt{2}\,\zeta_{-1}^{-1/2} F(\tfrac{1}{2} - \tfrac{m}{n}, \tfrac{1}{2} + \tfrac{m}{n}, \tfrac{1}{2}, \tfrac{1}{2}\zeta_{-1}), \]
-%where $\zeta = -1 + \zeta_{-1}$.
-%\color{black}
-%
 \subsection{Modified Bessel}\label{sec:mod-bessel-lift}
@@
 \end{equation}
-
-% \color{black}
-% \par\textcolor{orange}{[Old text\ldots]}
-% \color{RoyalBlue}
-% \begin{align*}
-%     K_\mu(z)& = -\frac{1}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\,\frac{\sinh(\mu t)}{\sinh(t)}\,d\zeta  & \\
-%     &=-\frac{\mu}{2 \sinh(\mu\,i\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right)\,d\zeta & \cite[15.4.16]{dlmf}
-% \end{align*}
-% where $\gamma_z$ is Hankel contour coming from $\infty$ to $1$ and then going back to $\infty$.
-Using formula \cite[15.8.4]{dlmf}, followed by \cite[15.8.27]{dlmf} and \cite[15.8.28]{dlmf} \textcolor{PaleVioletRed}{[Please clean up operators that are repeated across line breaks, like the $=$ below.
-I like the equation spacing in the ``Thimble projection reasoning for Airly-Lucas functions'' section; can we copy that here?]}
-% \begin{multline*}
-%      {}_2F_1\left(\frac{1+\mu}{2},\frac{1-\mu}{2};\frac{3}{2};1-\zeta^2\right) \textcolor{magenta}{=} \\
-%      =\frac{3}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1-\zeta}{2}\right)+\frac{1}{2}\, {}_2F_1\left(1-\mu,1+\mu,\frac{3}{2};\frac{1+\zeta}{2}\right)
-% \end{multline*}
-% hence 
-% %
-% \[K_\mu(z)=\frac{\mu\, i}{4 \sin(\mu\pi)} \int_{\gamma_z} e^{-z \zeta}\, {}_2F_1\left(1-\mu,1+\mu;\frac{3}{2};\frac{1+\zeta}{2}\right)\,d\zeta\]
-% %
-% Equation \cite[15.2.3]{dlmf} gives the analytic continuation of hypergeometric functions across the branch cut:
-
-% \begin{align}
-%     K_{\mu}(z)& \label{eqn:K-mu}=-\frac{1}{2}\int_1^\infty e^{-z\zeta} \, \left(\frac{\zeta-1}{2}\right)^{-1/2} \,\, {}_2F_1\left(\frac{1}{2}-\mu, \frac{1}{2}+\mu;\frac{1}{2};\frac{1-\zeta}{2}\right)  d\zeta\\
-%     &  \notag=-\frac{i}{2}\laplace_{\zeta,1} v_{\mu,1} . 
-% \end{align}
-% \color{black}
+%
 \subsubsection{The modified Bessel function with parameter $0$}\label{sec:bessel-0}
+%
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
@@
 The affine group is generated by two kinds of transformations, which we consider separately.
-%%The affine group of $\C$ acts on $f$ by post-composition, and $\C^\times$ acts on $\nu$ by multiplication.
-These actions both affect $J$ in simple ways.
-The affine group is generated by two kinds of transformations, which we consider separately.
 \begin{itemize}
@@
 \end{align*}
-%%\item[] \textbf{Multiplications}
-%%
-%%For any $s \in \C^\times$, the multiplication action $\nu \mapsto s\nu$ corresponds to the action
-%%\[ J(z) \mapsto s J(z) \]
-%%on integrals.
 \end{itemize}
@@
 Switching to the translation coordinate $\zeta_1$ defined by $\zeta = 1 + \zeta_1$, and then to the rescaled coordinate $\xi_1$ defined by $\zeta_1 = -2\xi_1$, we can rewrite equation~\eqref{diff-eq:spatial-mod-bessel} as the hypergeometric equation
-\begin{equation}%%\label{diff-eq:hypergeom-pos}
+\begin{equation}
 \left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0,
@@
 \end{align*}
-%Notice that $\tilde{W}_{1,2}(\hbar)$ are proportional to $\tilde{W}_{\pm}(z)$ with $z=\hbar^{-1}$. However, their Borel transforms are two different hypergeometric functions:
-Then, by applying the two definitions of the Borel transform $\borel_{\textit{phys}}$ and $\borel$, on the one hand we have  
+By applying the two versions $\borel_{\textit{phys}}$ and $\borel$ of the Borel transform, we get
 \begin{align*}
@@
 \end{align*}
-on the other hand, we find
+and
 \begin{align*}
@@
 &=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%w_{\pm}(\zeta)&=c_{1,2}\,\,{}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right) &\qquad \text{see \eqref{eq:hat+}\eqref{eq:hat-}}
-\end{align*}
-%That ambiguity comes from the different definitions of Borel transforms: 
-%\begin{align*}
-%\borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
-%&=\frac{1}{2\pi}\delta+\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n+1}\frac{\Gamma(n+1+\frac{5}{6})\Gamma(n+1+\frac{1}{6})}{(n+1)!}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{3}{4}\sum_{n=0}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{11}{6})\Gamma(n+\frac{7}{6})}{\Gamma(n+2)}\frac{\zeta^{n}}{n!}\\
-%&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)%\\
-%%&=\frac{1}{2\pi}\delta\mp \frac{5}{48}\frac{1}{c_{1,2}}w_{\pm}(\zeta)
-%\end{align*}
-
-and comparing the two solutions we notice that up to the factor of $\delta$
-
+&=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)\,.
+\end{align*}
+Comparing the two solutions, we notice that up to the factor of $\delta$,
 \begin{equation}\label{Borel-W12}
-\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta) 
+\borel(\tilde{W}_{1,2})(\zeta)-\frac{1}{2\pi}\delta=\mp \frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)=\frac{d}{d\zeta}\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\,.
 \end{equation}
@@
 In particular, $\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\left[z^{-1/2}\tilde{W}_{1}\right]\left(\frac{2}{3}\zeta\right)=v_1(\zeta)$. 
-
-%Recall that $v_1$ (computed in Section~\ref{pos-root}) is proportional to the Borel transform of $ z^{-1/2}\tilde{W}_1(z)$ (see Section~\ref{bessel-regularity}).
-We want to compare $v_1$ with the \textit{physic} Borel transform $\borel_{\textit{phys}}$ of $z^{-1/2}\tilde{W}_1$:
-%
-%\begin{align*}
-%\borel_{\textit{phys}}(z^{-1/2}\tilde{W}_{1})\left(\frac{2}{3}\zeta\right)&=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(-\frac{1}{2}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n+\frac{1}{2}}}{\Gamma(n+3/2)}\\
-%&=\frac{1}{2\pi}\zeta^{-1/2}\sum_{n=0}^{\infty}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!\Gamma(n+3/2)}\left(-\frac{\zeta}{2}\right)^{n+1}\\
-%&=\frac{1}{2\pi}\zeta^{1/2}\,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right) 
-%\end{align*}
-%
-%Now taking the $-1$- derivative of $v_1(\zeta)$ we get
-%
-%\begin{align*}
-%\partial_\zeta^{-1} v_1&=\frac{1}{\Gamma(1)}\int_0^{\zeta}(\zeta-\zeta') v_1(\zeta')d\zeta'\\
-%&=\int_0^{\zeta}(\zeta-\zeta') \zeta'^{-1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{1}{2};-\frac{\zeta'}{2}\right)d\zeta'\\
-%&=\frac{\Gamma(1/2)}{\Gamma(3/2)}\zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)\\
-%&=2 \zeta^{1/2} \,\, {}_2F_1\left(\frac{1}{6},\frac{5}{6};\frac{3}{2};-\frac{\zeta}{2}\right)
-%\end{align*}
+%
 \subsubsection{Integral formula for hypergeometric functions}
@@
 Furthermore, Mitschi and Sauzin prove that $\hat{\phi}_{\pm}(\zeta)$ are simple resurgent functions \cite[Lemma 6.106]{diverg-resurg-i}.
-%Therefore, from the expression of $\chi(\zeta)$ as a convolution product, the resurgent properties of $\series{\phi}_{\pm}(\zeta)$ are evident.
 %
@@
 &\left[\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta^{-1} x^{-3/2}\tfrac{d}{dq}-\tfrac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-%&\left[\left(\frac{d}{dq}\right)^2+\eta^{-1} x^{-3/2}\frac{d}{dq}-\frac{1}{9}\eta^{-2}x^{-3}-1\right]\Phi=0\\
 &\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0.

### 2024-11-15 borel-regularity.tex
Add position domain to inverse Laplace regularity figure

@@
 \draw[shorten <=0.3mm, shorten >=0.4mm] (\peakdis, 0) ++(\phase+\spread+90:\angmarkrad) arc[start angle=\phase+\spread+90, delta angle=\pathspread-\spread, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-90+0.5*\spread+0.5*\pathspread)] {$\tfrac{\varepsilon}{2}$};
-%%\draw (\peakdis, 0) ++(-\phase-\spread-90:\angmarkrad) arc [start angle=\phase-\spread-90, delta angle=\spread-\pathspread, radius=\angmarkrad] node[midway, circle, inner sep=1, anchor=90-0.5*\spread-0.5*\pathspread] {$\tfrac{\varepsilon}{2}$};
 \draw[shorten >=0.3mm] (\peakdis, 0) ++(\phase+\pathspread+90:\distmarkrad) -- ++(\phase+\spread:\bdrydist) node[midway, circle, inner sep=0, anchor=-90+\spread] {$t \sin(\tfrac{\varepsilon}{2})$};
@@
 
+\pgfmathsetmacro{\sectorshave}{2*(\spread - \pathspread)}
+\pgfmathsetmacro{\shavedspread}{\spread - \sectorshave}
+
+\begin{fiber}
+\fill[pwbeige!30, draw=pwbeige!60] (0, 0) -- (\phase-\shavedspread:1.5*\rshade) -- (\phase+\shavedspread:1.5*\rshade) -- cycle;
+
+% the construction lines
+\begin{scope}[pwbeige!80!black]
+\draw (\phase-\spread:1.5*\rshade) -- (0, 0) -- (\phase+\spread:1.5*\rshade);
+\draw[shorten <=0.3mm, shorten >=0.3mm] (\phase+\shavedspread:\angmarkrad) arc[start angle=\phase+\shavedspread, delta angle=\sectorshave, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-180+0.5*\spread+0.5*\pathspread)] {$\varepsilon$};
+\draw[shorten <=0.3mm, shorten >=0.3mm] (\phase-\shavedspread:\angmarkrad) arc[start angle=\phase-\shavedspread, delta angle=-\sectorshave, radius=\angmarkrad] node [midway, circle, inner sep=1, anchor=-180-0.5*\spread-0.5*\pathspread)] {$\varepsilon$};
+\end{scope}
+
+% chosen point
+\fill (\phase-\shavedspread:1.7) circle (1.25*\dotsize);
+
+\genfibercontent
+\node[anchor=-11, inner sep=2mm] at (0,0) {$\zeta = \alpha$};
+\node[anchor=north west, inner sep=2mm] at (-\rfiber, \rfiber) {$\zeta$};
+\end{fiber}
+
+\begin{scope}[shift={(6.5, 0)}] % frequency domain
+
 \begin{fiber}[shade, phase=\phase+2*\pathspread-\spread, dis=\peakdis]
@@
 \draw[very thick] (\peakdis, 0) +(-\phase-\pathspread-90:\rshade) -- +(0, 0) -- +(-\phase+\pathspread+90:\rshade);
-%%\draw (\peakdis, 0) ++(\phase+\pathspread+90:0.75*\distmarkrad) node[anchor=180+\pathspread] {$t$};
 \draw (\peakdis, 0) ++(\phase+\pathspread+90:0.7*\distmarkrad) node[circle, inner sep=0.5, fill=pwbeige!10] {$t$};
@@
 
-% point at node boundary
+% outside labels
 \begin{scope}[pwbeige!80!black]
-\draw[out=170, in=25] (3.0, 1.8) node[anchor=west, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$} to (2.1, 1.7);
-\draw[out=-100, in=110, shorten >=0.5mm, -stealth] (1.1, 2.8) node[anchor=south, inner sep=0.5] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
+\draw[out=-55, in=90] (1.7, 3.2) node[anchor=-35, inner sep=1] {$\Re\big(z\tfrac{\zeta_\alpha}{|\zeta_\alpha|}\big) > \Lambda'$} to (2.1, 1.9);
+\draw[out=-15, in=105, shorten >=0.5mm, -stealth] (0.6, 2.9) node[anchor=east, inner sep=2] {$t \sin(\tfrac{\varepsilon}{2})$} to (dist-anchor);
 \end{scope}
+
+\end{scope} % frequency domain
 \end{tikzpicture}
 \captionof{figure}{For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$.
-This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions actually require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.
+This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.
 \begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}

### 2024-11-15 borel-regularity.tex
Name ODE unknown more consistently
Tweak lemma statement

@@
 Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
-The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
+The equation $\mathcal{P}\Phi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
 \[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet) \right] \]
@@
 Let $\Omega_\alpha \subset B$ be an open set with the point $\zeta = \alpha$ on its boundary, and let $\Omega_\beta \subset B$ be an open set with $\zeta = \beta$ on its boundary.
-For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
+For any $\phi \in \singexpalg{\sigma}(\Omega_\alpha)$ and $\psi \in \singexpalg{\sigma'}(\Omega_\beta)$ with $\sigma,\sigma'\in (-1,\infty)$, the convolution product $\phi \ast_{\zeta, \alpha, \beta} \psi$ is the function on $B$ defined by the integral
 \begin{equation}
@@
 \begin{corollary}\label{prop:convolution_iso_laplace}
-For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$, with $\sigma, \sigma' \in (-1, \infty)$, we have
+For any two functions $\phi \in \singexpalg{\sigma}(\Omega)$ and $\psi \in \singexpalg{\sigma'}(\Omega)$ with $\sigma, \sigma' \in (-1, \infty)$, we have
 \begin{equation}\label{eqn:laplace-convol1}

### 2024-12-17 sima/reg-sing-volterra_sima.tex
Revise wording during proofing

@@
 This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
-If $\Omega \subset \C$ touches the $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighborhood $U \subset \C$ of $p$.
+If $\Omega \subset \C$ touches the point $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighborhood $U \subset \C$ of $p$.
 This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
@@
 We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ as an inhomogeneous equation in a more regular space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to prove that $\softpart$ improves on the regularity ascribed by Theorem~\ref{thm:proto-growth} to the prototype solution $f_0$.
 \begin{rmk}
@@
 In Section~\ref{far-bound}, we will see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
-Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
-Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
+Together, these results will show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
+Since we set $\sigma < \rho$, this will prove Proposition~\ref{prop:get-contraction}.
 \subsubsection{Bounds on the perturbed kernel}\label{sec:bounds on k}

### 2025-01-03 borel-regularity.tex
Define tau_alpha before it's used in statements

@@
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
-We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
+We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), \textcolor{orange}{and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE})}.
 
@@
 \begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
-Let $-\alpha$ be a root of $P$.
+Let $-\alpha$ be a root of $P$ \textcolor{orange}{where $\tau_\alpha$ is real and positive}.
 Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
@@
 %
-An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
+An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ \textcolor{orange}{indexed by the roots $-\alpha$ of $P$, where $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$}.
 These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
 Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve.
-The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} \colon P(-\alpha) = 0\}$.
+The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} : P(-\alpha) = 0\}$.
 Poincar\'{e} guesses that each approximate solution $e^{-\alpha z}$ can be turned into an exact solution $e^{-\alpha z} \series{F}_\alpha$ using a formal correction factor $\series{F}_\alpha \in z^{-\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
-When $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$, the correction factor can be found order by order, starting from any chosen constant term.
+\textcolor{orange}{The} correction factor can be found order by order, starting from any chosen constant term.
 We will refer to the resulting solutions $e^{-\alpha z} \series{F}_\alpha \in e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ as Poincar\'{e}'s formal solutions.
@@
 \begin{equation}\label{eq:hat_P}
-    \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1})
-\end{equation}
-From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
+\hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1})\,,
+\end{equation}
+\textcolor{orange}{and define the constant $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.} From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
 \begin{todo}[Transition text]\end{todo}
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ \textcolor{orange}{where $\tau_\alpha$ is real and positive}.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
@@
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
 \end{theorem}
@@
 In~\cite{int-irreg}, Poincar\'{e} described a formal way to solve the equation $\mathcal{P}\series{\Phi} = 0$ for an operator of the form~\eqref{eqn:operator-P}.
-Choose a root $-\alpha$ of $P$, set $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$.
+Choose a root $-\alpha$ of $P$ and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$, \textcolor{orange}{recalling that $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$}.
 Once the leading coefficient of $\series{\Psi}_\alpha$ is chosen, the rest of the coefficients are determined, and can be found order by order.
@@
 \begin{theorem}\label{thm:summability_ODE}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ \textcolor{orange}{where $\tau_\alpha$ is real and positive}.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.

### 2025-01-03 sima/reg-sing-volterra_sima.tex
Define tau_alpha before it's used in statements

@@
 An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
-These series are typicaly divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
+These series are typically divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
 The results of this paper are motivated by the desire to find the same analytic solutions more directly, without the use of formal series.
@@
 \end{align*}
-where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+where $\partial^{-\nu}$ is the Riemann--Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.

### 2025-01-03 borel-regularity.tex
Remove revision coloring

--- 2024-11-15 borel-regularity.tex
@@
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
-We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}).
+We will restrict our attention to the case where the roots of $P$ are simple (see Section \ref{borel_reg-ODE}), and to the solutions associated with roots $-\alpha$ where $\tau_\alpha:=\frac{Q(-\alpha)}{P'(-\alpha)}$ is real and positive (see Theorem~\ref{thm:exist_uniq_ODE}).
 
@@
 \begin{theorem}[also \ref{re:thm:exist_uniq_ODE}]\label{thm:exist_uniq_ODE}
-Let $-\alpha$ be a root of $P$.
+Let $-\alpha$ be a root of $P$ where $\tau_\alpha$ is real and positive.
 Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
@@
 %
-An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
+An ODE of the form described in Section~\ref{borel-reg:explanatory-power} always has a frame of solutions in the trans-monomial spaces $e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ indexed by the roots $-\alpha$ of $P$, where $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.
 These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
 Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve.
-The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} \colon P(-\alpha) = 0\}$.
+The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} : P(-\alpha) = 0\}$.
 Poincar\'{e} guesses that each approximate solution $e^{-\alpha z}$ can be turned into an exact solution $e^{-\alpha z} \series{F}_\alpha$ using a formal correction factor $\series{F}_\alpha \in z^{-\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$.
-When $\tau_\alpha = Q(-\alpha) / P'(-\alpha)$, the correction factor can be found order by order, starting from any chosen constant term.
+The correction factor can be found order by order, starting from any chosen constant term.
 We will refer to the resulting solutions $e^{-\alpha z} \series{F}_\alpha \in e^{-\alpha z} z^{\tau_\alpha}\,\C\llbracket z^{-1} \rrbracket$ as Poincar\'{e}'s formal solutions.
@@
 If $z$ is a function on the fiber over $\zeta=\alpha$, then it is enough to replace $\borel_\zeta$ with $\borel_{\zeta_\alpha}$ and to use  $\laplace_{\zeta_\alpha,0}$ as the inverse.
-%\color{orange}
-%\subsubsection{Action on power series with fractional exponents}
-%\color{black}
 %
@@
 \begin{equation}\label{eq:hat_P}
-    \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1})
-\end{equation}
+\hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1})\,,
+\end{equation}
+and define the constant $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.
 From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
@@
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ where $\tau_\alpha$ is real and positive.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
@@
 In~\cite{int-irreg}, Poincar\'{e} described a formal way to solve the equation $\mathcal{P}\series{\Phi} = 0$ for an operator of the form~\eqref{eqn:operator-P}.
-Choose a root $-\alpha$ of $P$, set $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$.
+Choose a root $-\alpha$ of $P$ and look for a formal solution $\series{\Psi}_\alpha$ in the space $e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket$, recalling that $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.
 Once the leading coefficient of $\series{\Psi}_\alpha$ is chosen, the rest of the coefficients are determined, and can be found order by order.
@@
 \begin{theorem}\label{thm:summability_ODE}
-Choose a root $-\alpha$ of $P$.
+Choose a root $-\alpha$ of $P$ where $\tau_\alpha$ is real and positive.
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.

### 2025-01-03 borel-regularity.tex
Clean up macros

@@
 \newcommand{\dualsingexp}[1]{\widehat{\mathcal{H}}L^\infty_{#1}}
-%%\newcommand{\dualsingexpalg}[1]{\dualsingexp{#1}{\bullet}}
-\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% remove once we stop using old arguments
-
-%% editing
-\newcommand{\done}[1]{\textcolor{gray}{#1}}
 
@@
 Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
-\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
@@
 Thimble integrals have been studied from different perspectives: in physics, they play an important technical role in quantum mechanics, where infinite-dimensional exponential integrals are supposed to give the expectation values of observable quantities \cite{dunne-unsal2,dunne-unsal,Fauvet_Menous_Queva,Tanizaki:2014tua}.
-In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional algebraic variety over $\C$ and $f$ is a proper map $f\colon X\to\C$, thimble integrals are known as exponential period integrals~\cite{deligne2007singularites,Maxim_lectures,kontsevich-Fourier-exact,kontsevich2024holomorphic,fresan-notes}.
+In the algebraic geometric set-up, namely when, following the notation introduced in Section~\ref{borel-reg:explanatory-power}, $X$ is an $N$-dimensional algebraic variety over $\C$ and $f$ is a proper map $f\maps X\to\C$, thimble integrals are known as exponential period integrals~\cite{deligne2007singularites,Maxim_lectures,kontsevich-Fourier-exact,kontsevich2024holomorphic,fresan-notes}.
 \subsubsection{Thimble integrals in physics}
@@
 Therefore, the Borel transform is a $\C$-linear map
- \[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\,.\] 
+ \[\borel_\zeta\maps\C\llbracket z^{-1}\rrbracket\to\C\delta + \C\llbracket\zeta\rrbracket\,.\] 
 In fact, since $\borel_\zeta$ is defined as the formal inverse of $\laplace_{\zeta,0}$ we can introduce the \textit{formal Laplace transform} as the map from $\C\llbracket \zeta\rrbracket$ to $z^{-1}\C\llbracket z^{-1}\rrbracket$ which acts as $\laplace_{\zeta,0}$ on monomials $\zeta^k$ and then it extends by countable linearity.
@@
 Similarly, $\borel_{\zeta_\alpha}$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta_\alpha\rrbracket$ endowed with the convolution product $\ast_{\zeta_\alpha}$, where $z$ is a coordinate on $T^*_{\zeta=\alpha}B$.
-%We can further generalize this result to transseries:
-% \begin{prop}
-%     The Borel transform $\borel_\zeta$ induces an algebra homomorphism 
-%     \[\borel_\zeta\colon e^{-\alpha z}\C\llbracket z^{-1}\rrbracket\to \C\delta_\alpha+\C\llbracket\zeta_\alpha\rrbracket\]
-%     where $\delta_\alpha:=\borel_{\zeta}e^{-z\alpha}$. 
-% \end{prop}
-% \begin{proof}
-% Let $\series{\Phi}=e^{-\alpha z}\sum_{n=0}^\infty a_n z^{-n}\,, \series{\Psi}=e^{-\alpha z}\sum_{n=0}^\infty b_nz^{-n}\in e^{-\alpha z}\C\llbracket z^{-1}\rrbracket$. 
-% %     \begin{align*}
-% %         \borel_\zeta\series{\Phi}\series{\Psi}&=
-% %     \end{align*}
-% \end{proof}
+%
 \begin{remark}
@@
 The space of $1$-Gevrey series is closed under the Cauchy product. In addition, 
-\[\borel_\zeta\colon\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
+\[\borel_\zeta\maps\C\llbracket z^{-1}\rrbracket_1\to\C\delta + \C\{\zeta\}\]
 extends to an algebra homomorphism, where $\C\{\zeta\}$ is endowed with the convolution product defined in Definition~\ref{def:convolution_formal}.
@@
 Let us recall the setting from Section~\ref{borel-reg:explanatory-power}.
-Let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ and a holomorphic function $f\colon X\to\C$ with non--degenerate critical points.
+Let $X$ be a $1$-dimensional complex manifold equipped with a volume form $\nu \in \Omega^{1,0}(X)$ and a holomorphic function $f\maps X\to\C$ with non--degenerate critical points.
 Let $I_a$ be the thimble integral

### 2025-01-28 sima/correspondence/sima-cover.tex
Snapshot before preparing last arXiv version

\documentclass{letter}

\usepackage{url}
\usepackage{graphicx}
\usepackage{tikz}

% include signature image. based on suggestion from TeX.SE user Werner
%   https://tex.stackexchange.com/a/148458/6934
%%\makeatletter
%%\newcommand*{\signatureimg}[1]{\def\fromimg{#1}}
%%\renewcommand{\closing}[1]{\par\nobreak\vspace{\parskip}%
%%  \stopbreaks
%%  \noindent
%%  \ifx\@empty\fromaddress\else
%%  \hspace*{\longindentation}\fi
%%  \parbox{\indentedwidth}{\raggedright
%%       \ignorespaces #1\\%
%%       \includegraphics[height=6\medskipamount]{\fromimg}\\%
%%       \ifx\@empty\fromsig
%%           \fromname
%%       \else \fromsig \fi\strut}%
%%   \par}
%%\makeatother

\address{Campbell Wheeler \\
Institut des Hautes \'{E}tudes Scientifiques \\
Le Bois-Marie, 35 route de Chartres \\
F-91440 Bures-sur-Yvette, France}

\signature{\vspace{-12mm}Campbell Wheeler \\
\url{wheeler@ihes.fr} \\[6pt]
Veronica Fantini \\
\url{veronica.fantini@universite-paris-saclay.fr}}

%%\signatureimg{placeholder-sig.pdf}

\date{January 10, 2025}

\begin{document}
\begin{letter}{}
\begin{tikzpicture}[remember picture,overlay]
\node[xshift=4.2cm, yshift=-3.5cm] at (current page.north west) {\pgftext{\includegraphics[height=4.02cm]{ihes-logo}}};
\end{tikzpicture}
\opening{Dear Prof. Lipton:}

We would like to submit the enclosed manuscript, ``Regular singular Volterra equations on complex domains,'' for publication in the \textit{SIAM Journal on Mathematical Analysis}. We believe this work is suitable for \textit{SIMA} because it is motivated by problems from mathematical physics, but its results are primarily analytical, and \textit{SIMA} is known for including both areas in its scope.

We have been using a new Laplace transform method to study certain special solutions of irregular singular ODEs, which appear often in work on resurgence and Borel summability. To characterize this method, we need function spaces and analytic results that we have not seen in the literature; we wrote this manuscript to describe them.

Because Laplace transform methods are widely used in science and engineering, we hope these spaces and results may be of interest beyond the scope of our work. This hope is reinforced by the physical flavor of the example ODEs mentioned in the introduction, which include the Airy equation from optics and the equation describing
the vibration modes of a solid triangular cantilever.

Our method turns ODEs into Volterra equations, which have appeared often in \textit{SIMA}. Articles by people in our field---including Tamara Grava, our suggested editor---have also appeared here. We therefore believe that \textit{SIMA} brings together readers from usually-separated communities that might be interested in this work.
\closing{Best regards,}
\end{letter}
\end{document}

### 2025-01-28 sima/correspondence/sima-cover.tex
Revert accidental changes to cover letter
This reverts commit 8eb7acca3edcc637157af873d4393e0cd7a6185f.

@@
 
-\address{Campbell Wheeler \\
+\address{Veronica Fantini \\
 Institut des Hautes \'{E}tudes Scientifiques \\
@@
 
-\signature{\vspace{-12mm}Campbell Wheeler \\
-\url{wheeler@ihes.fr} \\[6pt]
-Veronica Fantini \\
-\url{veronica.fantini@universite-paris-saclay.fr}}
+\signature{\vspace{-12mm}Veronica Fantini \\
+\url{fantini@ihes.fr} \\[6pt]
+Aaron Fenyes \\
+\url{aaron.fenyes@fareycircles.ooo}}
 
@@
 
-\date{January 10, 2025}
+\date{Octobter 31, 2023}
 

### 2025-01-28 reg-sing-volterra.tex
Delete stray period
Typos correction, update to-do list
Update article to SIMA version
Also, update bibliography with changes made during proofing. Capitalize
"Stokes" in the bibliography: a typo we missed during proofing.

--- 2023-09-01 reg-sing-volterra.tex
@@
 \usepackage{graphicx}
-\usepackage[svgnames]{xcolor} % for verifications
 \usepackage{environ} % to hide verifications
@@
 \theoremstyle{definition}
+\newtheorem{definition}{Definition}
 \newtheorem{rmk}{Remark}
 \theoremstyle{plain}
-\newtheorem{prop}{Proposition}
+\newtheorem{proposition}{Proposition}
 \newtheorem{lemma}{Lemma}
-\newtheorem{thm}{Theorem}
-\newtheorem{cor}{Corollary}
+\newtheorem{theorem}{Theorem}
+\newtheorem{corollary}{Corollary}
 
 % list formatting
+\setlist[itemize]{topsep=3mm, itemsep=1.8mm, parsep=1.2mm}
 \newlist{conditions}{itemize}{1}
-\setlist[conditions]{leftmargin=26mm, rightmargin=12mm}
+\setlist[conditions]{leftmargin=26mm, rightmargin=12mm, topsep=3mm, itemsep=1.8mm, parsep=1.2mm}
 \makeatletter
@@
 \newcommand{\singexpalg}[1]{\singexp{#1}{\bullet}}
-\newcommand{\holoL}[1]{\mathcal{H}L^{#1}} %% may no longer be needed
-\newcommand{\expHoloL}[2]{\mathcal{H}L^{#1}_{#2}} %% may no longer be needed
 
 % operator under consideration
+\newcommand{\genvolterra}{\mathcal{W}}
+\newcommand{\genker}{w}
 \newcommand{\volterra}{\mathcal{V}}
@@
 \fi
+
+% revision highlighting
+\newif\ifhighlightrevs
+\highlightrevsfalse
+\ifhighlightrevs
+\newenvironment{revtwo}{\color{revred}}{\color{black}}
+\newcommand{\revtwotext}[1]{\textcolor{revred}{#1}}
+\else
+\newenvironment{revtwo}{}{}
+\newcommand{\revtwotext}[1]{#1}
+\fi
+
+% notation change highlighting
+%%\newif\ifhighlightnewnotation
+%%\highlightnewnotationfalse
+%%\ifhighlightnewnotation
+%%\newenvironment{newnot}{\color{orange}}{\color{black}}
+%%\newcommand{\newnottext}[1]{\textcolor{orange}{#1}}
+%%\newenvironment{oldnot}{\color{cyan}}{\color{black}}
+%%\newcommand{\oldnottext}[1]{\textcolor{cyan}{#1}}
+%%\else
+%%\newenvironment{newnot}{}{}
+%%\newenvironment{oldnot}{}{}
+%%\newcommand{\newnottext}[1]{#1}
+%%\fi
 
@@
 \definecolor{ietlagoon}{RGB}{0, 216, 180}
+\definecolor{veriforest}{RGB}{0, 80, 40}
+\definecolor{revred}{RGB}{153, 0, 0}
 
@@
 \section{Introduction}\label{sec:intro}
-\subsection{Motivation}\label{motivation}
+\subsection{Motivation}\label{sec:motivation}
+An ordinary differential equation with an irregular singularity at infinity comes with a special family of formal solutions: ``normal series'' characterized by their formal asymptotics at infinity~\cite{int-irreg}.
+These series are typically divergent, but they can be ``resummed'' to produce analytic solutions~\cite{loday1994stokes,diverg-resurg--ii,loday-Remy2011,malgrange1995sommation,ramis1991series}.
+The results of this paper are motivated by the desire to find the same analytic solutions more directly, without the use of formal series.
+We do this in Section~\ref{sec:example} for a certain class of level~$1$ ODEs, using new Laplace transform methods tailored to the special properties of the analytic solutions that we seek.
+In~\cite{borel_reg}, we show that these solutions match the ones obtained through resummation.
+Since the Laplace transform methods we use may be of wider interest, we describe them here in a general and self-contained way.
+
+\begin{revtwo}
 In its most basic form, the Laplace transform $\laplace$ turns exponential-type functions of a real ``position'' variable $\zeta$ into holomorphic functions of a complex ``frequency'' variable $z$.
+It is the integral transform defined by the equation
+\[ \laplace \varphi := \int_{\Gamma_\zeta} e^{-z\zeta} \varphi\;d\zeta\,, \]
+where $\Gamma_\zeta$ is the ray $\zeta \in (0, \infty)$.     
+\end{revtwo}
 \begin{verify}[Suppose the magnitude of the Laplace transform integrand is Riemann-integrable on $(0, \infty)$.
@@
 \frac{\partial}{\partial z} \laplace \varphi & = \laplace(-\zeta\varphi) \\
-\laplace k\;\laplace \varphi & = \laplace(k * \varphi) \\
-z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi,
-\end{align*}
-where $\partial^{-\nu}$ is the Riemann-Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
+\laplace \revtwotext{\psi}\;\laplace\varphi & = \laplace(\revtwotext{\psi} * \varphi) \\
+z^{-\nu} \laplace \varphi & = \laplace\,\partial^{-\nu} \varphi\,,
+\end{align*}
+where $\partial^{-\nu}$ is the Riemann--Liouville fractional integral of order $\nu \in (0, \infty)$, the Laplace transform pulls differential operators on the frequency domain back to Volterra integral operators on the position domain.
 The favorable regularity properties and comprehensive theory of Volterra equations can thus be brought to bear on linear differential equations.
@@
 Some differential equations pull back to Volterra equations with real-analytic kernels, which extend to holomorphic Volterra equations on complex extensions of the position domain.
-Solutions that look unrelated in the frequency domain may turn out to be linked by analytic continuation along the complex position domain, as seen in the phenomenon of {\em resurgence} \cite{EcalleIII}\cite{lectures-marino}\cite[Section 2.4]{sternin1995borel}.
-
-Differential equations with irregular singularities in the frequency domain can pull back to Volterra equations with regular singularities in the position domain.
-In Section~\ref{sec:example}, we'll see this helpful behavior in a certain subclass of what Ecalle calls {\em level~1} differential equations, which includes classical examples like the modified Bessel equation, the equation describing the vibration modes of a solid triangular cantilever~\cite[from Equation~12.58]{genta2009vibration}, and the Airy equation after a change of coordinate.
-This last example generalizes to the Airy-Lucas equations, a family of level~1 equations that feature in current research~\cite[Equations 3.2]{charbonnier22}.
-\begin{verify}
-[The differential operator for the cantilever is $(\partial^4 + \omega^2 c_1) + \tfrac{1}{z} c_2 \partial^3$, where $\omega$ is the vibration frequency and $c_1, c_2$ are constants.
-This example works because the linear density of the beam and the second moment of area perpemdicular to the vibration direction are proportional, so they both end up in the $P(\partial)$ term.]\end{verify}
-
-From our experience with solving level~1 differential equations by Borel summation, we expect each of the corresponding integral equations to have a special kind of solution when the integration base point coincides with a regular singularity.
-Let's say we've chosen the position variable $\zeta$ so that the integration base point is at $\zeta = 0$, and our position-domain Volterra operator has a holomorphic kernel $k(a, a')$ with a $\tau/\zeta(a)$ singularity.
-Assuming the residue $\tau$ is real and positive, we expect to find a solution with the following features:
+For instance, in Section~\ref{sec:example}, we consider equations of the form
+\begin{equation}\label{eqn:intro-level-1}
+\left[ P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}) \right] \Phi = 0
+\end{equation}
+given by polynomials $P$, $Q$ and a holomorphic function $R(z^{-1})$ satisfying some extra conditions.
+A function of the form $\Phi = \laplace \varphi$ satisfies this equation if and only if $\varphi$ satisfies the integral equation
+\begin{equation}\label{eqn:intro-use-dict}
+\big[ P(-\zeta)+\partial^{-1}\circ Q(-\zeta)+\partial^{-2}\circ R(\partial^{-1}) \big] \varphi = 0\,.
+\end{equation}
+The integral operator remains well-defined if we make $\zeta$ a complex coordinate and seek solutions $\varphi$ which extend holomorphically into the complex position domain.
+
+Equation~\eqref{eqn:intro-level-1} can be solved by resumming normal series, as described earlier.
+Each resummed solution is characterized by its $e^{-\alpha z} z^{-\tau_\alpha}$ asymptotics, where $-\alpha$ is a root of $P$ and $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$ is real and positive.
+To obtain this solution analytically through Laplace transform methods, we must take the Laplace transform $\laplace_{\zeta,\alpha}$ that uses $\zeta = \alpha$ in place of the traditional $\zeta = 0$ as the integration base point.
+\begin{revtwo}
+Explicitly,
+\[ \laplace_{\zeta,\alpha} \varphi := \int_{\Gamma_{\zeta,\alpha}} e^{-z\zeta} \varphi\;d\zeta\,, \]
+where $\Gamma_{\zeta,\alpha}$ is the ray $\zeta \in \alpha + (0, \infty)$.    
+This version of the Laplace transform is defined in Section~\ref{sec:definition_Laplace}.
+A function of the form $\Phi = \laplace_{\zeta, \alpha} \varphi$ satisfies equation~\eqref{eqn:intro-level-1} if and only if $\varphi$ satisfies the integral equation
+%%use the Laplace transform based at $\zeta = \alpha$, equation~\eqref{eqn:intro-use-dict} then comes out based at $\zeta = \alpha$ as well:
+\[ \big[ P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}) \big] \varphi = 0\,, \]
+where $\partial^{-1}_{\zeta, \alpha}$ is integration with base point $\zeta = \alpha$:
+\[ [\partial^{-1}_{\zeta, \alpha} \varphi](a) := \int_{\zeta = \alpha}^a \varphi\;d\zeta\,. \]
+We seek a solution $\psi_\alpha$ which
 \begin{itemize}
-\item It has an $O\big(\zeta^{\tau-1}\big)$ singularity at $\zeta = 0$.
-\item It's of exponential type, meaning that it's $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
+\item has an $O\big((\zeta - \alpha)^{\tau_\alpha-1}\big)$ singularity at $\zeta = \alpha$; and
+\item is of exponential type, meaning that it is $O\big(e^{\Lambda|\zeta|}\big)$ for some $\Lambda \in \R$ as $\zeta$ grows.
 \end{itemize}
-These conditions are just strong enough to ensure that the solution has a well-defined Laplace transform, which by construction will satisfy the differential equation we started with in the frequency domain.
-The first condition also tells us that the Laplace-transformed solution is $O(z^{-\tau})$ as the frequency variable $z$ grows.
-
-Our goal is to justify the expectations above with an existence and uniqueness result, stated in Section~\ref{sec:results}.
-We'll achieve it by embodying our expectations in a Banach space of holomorphic functions---the space $\singexp{\tau-1}{\Lambda}(\domain)$ defined in Section~\ref{fn-spaces}.
-We'll apply our results to level $1$ differential equations in Section~\ref{sec:example}.
-\subsection{Notation for uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we'll write $\varphi \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+These conditions ensure that $\psi_\alpha$ has a well-defined Laplace transform, and the first condition gives $\laplace_{\zeta, \alpha} \psi_\alpha$ the desired asymptotics.
+\end{revtwo}
+
+The theory of Volterra equations is well-suited to this solution method.
+By embodying our conditions on $\psi_\alpha$ in a Banach space, defined in Section~\ref{fn-spaces}, we can solve equations like~\eqref{eqn:intro-use-dict} using the contraction mapping theorem, taking advantage of the regularizing effect of the relevant Volterra operators.
+This establishes the existence and uniqueness of $\psi_\alpha$, as stated in Theorem~\ref{thm:example}.
+Since integral operators on the position domain correspond directly to multiplication operators on the frequency domain, with no need to worry about initial values, we know immediately that $\laplace_{\zeta, \alpha} \psi_\alpha$ satisfies equation~\eqref{eqn:intro-level-1}, even when $\psi_\alpha$ blows up at $\zeta = \alpha$.
+By isolating the features of equation~\eqref{eqn:intro-use-dict} that make our contraction mapping argument possible, we get the main result of this paper: the general existence and uniqueness result stated in Section~\ref{sec:results}.
+
+Our results build on known methods for solving differential equations with irregular singularities.
+Our focus on integral equations in the position domain, and the singularities of their solutions, recalls the approach of Loday-Richaud and Remy, who use a mix of formal and analytic methods inspired by \'{E}calle's theory of resurgence~\cite{loday-Remy2011, EcalleIII}.
+One of our motivations is to understand resurgence from an analytic perspective, without reference to formal solutions.
+The Banach spaces we use to achieve this also appear in the work of Braaksma, who uses them to solve systems of ODEs whose coefficients are expressed as Laplace transforms~\cite{braaksma2006laplace}.
+This overlap suggests an opportunity to combine the two approaches, extending our results to systems of equations, and Braaksma's to equations with more general coefficients.
+\subsection{Formalism for coordinates}\label{sec:formalism}
+\subsubsection{Rationale}
+Our motivating example, equation~\eqref{eqn:intro-use-dict}, has regular singularities at various points $\zeta = \alpha$ on the position domain.
+Each associated solution $\psi_\alpha$ is most easily expressed in terms of its own translated position coordinate $\zeta_\alpha = \zeta - \alpha$.
+We therefore expect our results to be used in calculations involving multiple coordinates.
+Our formalism for points, functions, and coordinates is tailored to such calculations.
+
+For simplicity, we use $\C$ as the position domain throughout this article.
+In the study of resurgence, however, the position domain is often a Riemann surface over $\C$, or even a more general ``translation surface.'' Thanks to our choice of formalism, our results and their proofs generalize immediately to this setting.
+\subsubsection{Points and coordinates}
+From now on, we will carefully respect the distinction between points and coordinates.
+A point is a location in space, while a coordinate is a function on space.
+For example, the position coordinates $\zeta$ and $\zeta_\alpha$ are functions on the position domain, just like the integral equation solutions $\psi_\alpha$.
+A coordinate, like $\zeta$, can be evaluated at a point $b$, yielding a number $\beta := \zeta(b)$.
+Conversely, the point $b$ can be described as the place where $\zeta = \beta$.
+\subsubsection{Integration}
+When we integrate, the integrand will always be either a 1-form, like $\varphi\,d\zeta$, or a density, like $|\varphi\,d\zeta|$~\cite[Section~1.8]{local-viewpoint}.
+On a simply connected domain, all integration paths are equivalent, so we will typically specify an integral by its start and end points.
+These points may be given directly, as in the expression $\int_b^a \varphi\,d\zeta$, or described in terms of coordinates, as in the equivalent expression $\int_{\zeta = \beta}^a \varphi\,d\zeta$.
+In the integral
+\[ \int_{\zeta = \beta}^a \big(\zeta(a) - \zeta\big)^{-1/2} \varphi\,d\zeta\,, \]
+notice that $\zeta(a)$ is a number, which stays constant throughout the integration, while $\zeta$ is a function, whose value changes along the integration path.
+
+\begin{revtwo}
+Sometimes, in expressions like
+\[ \int_{\zeta(a') = \beta}^a w(a, a')\,\varphi(a')\;d\zeta(a')\,, \]
+it is useful to give a name $a'$ to the point moving along the integration path.
+In this case, all of the functions and differential forms whose values change along the integration path are explicitly evaluated at $a'$.
+\end{revtwo}
+\subsubsection{Plugging into formal expressions}
+Plugging a function $\varphi$ into a formal polynomial or power series $P$ gives a new function $P(\varphi)$.
+The correspondence between operators on the position and frequency domains will lead to expressions of this kind.
+In Section~\ref{sec:motivation}, for example, we saw that the differential operator $P\big(\tfrac{\partial}{\partial z}\big)$ on the frequency domain corresponds to multiplication by the function $P(-\zeta)$ on the position domain.
+\subsection{Notation}
+\subsubsection{Uniform bounds}
+Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
+If the bound involves an explicit variable, we will say that it holds over all values of the variable.
+For example, we will write ``$|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$'' to mean ``there is a constant $M$ such that for all $j \in \{0, 1, 2, \ldots\}$, the inequality $|R_j| \le M \lambda^j$ holds.''
+\subsubsection{Boundary points}
+We will say that a subset of a topological space {\em touches} the points in its closure.
+This is a way of expressing the nearness relation associated with the topology~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.
+If $\Omega \subset \C$ touches the point $p \in \C$, we define a neighborhood of $p$ in $\Omega$ to be $U \cap \Omega$ for some open neighborhood $U \subset \C$ of $p$.
+This agrees with the usual definition of a neighborhood when $p$ is an element of $\Omega$.
 \subsection{Setting}\label{setting}
 \subsubsection{The domain}\label{setting:domain}
-Throughout this paper, as described in Section~\ref{motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$, and satisfies the following condition.
+Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
+
+Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
 \begin{conditions}
@@
 In other words, for any $a \in \domain$, a straight path from $\zeta = 0$ to $a$ stays in $\domain$.
-Since $\domain$ doesn't contain $\zeta = 0$, we'll always omit that starting point from the path.
+Since $\domain$ does not contain $\zeta = 0$, we will always omit that starting point from the path.
 \end{conditions}
-For the applications we have in mind, $\domain$ might look something like the set pictured below.
+For the applications we have in mind, $\domain$ typically resembles the set pictured below.
+\vspace{2mm}
+
 \begin{center}
-\begin{tikzpicture}
+\begin{tikzpicture}[scale=0.9]
 \newcommand{\spill}{4}
@@
 \subsubsection{The prototype operator}\label{setting:basic}
-The prototypical example of the kind of operator we'll be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel and a regular singularity at $\zeta = 0$.
-
-Being a holomorphic Volterra operator means that $\hardpart$ sends each holomorphic function $\varphi$ on $\domain$ to a new holomorphic function
-\[ [\hardpart\,\varphi](a) = \int_{\zeta = 0}^a \hardker(a, \cdot)\,\varphi\;d\zeta. \]
-Being separable means that the kernel $\hardker(a, a')$ factors into a function of $a$ times a function of $a'$. We'll suppose this product can be written as a ratio
+The prototypical example of the kind of operator we will be working with is a holomorphic Volterra operator $\hardpart$ with a separable kernel $\hardker$ and a regular singularity at $\zeta = 0$.
+
+Let $\holo(\domain)$ be the space of holomorphic functions on $\domain$.
+\begin{definition}\label{defn:volterra}
+A {\em holomorphic Volterra operator} on $\domain$ is a linear operator
+\[\genvolterra\colon\holo(\domain)\to\holo(\domain) \]
+defined by an integral
+\begin{revtwo}
+\[ [\genvolterra\,\varphi](a) = \int_{\zeta(a') = 0}^a \genker(a, a')\,\varphi(a')\;d\zeta(a') \]
+\end{revtwo}
+in which the {\em kernel} $w$ is a holomorphic function on $\Omega^2$.
+\end{definition}
+\begin{definition}
+A holomorphic Volterra operator is {\em separable} if its kernel factors as a product of two functions, one on each factor of $\Omega^2$.
+\end{definition}
+For the prototype operator $\hardpart$, we will suppose that the kernel $\hardker$ can be written as a ratio
 \[ \hardker(a, a') = - \frac{q(a')}{p(a)}, \]
-where $p$ and $q$ are holomorphic functions on $\domain$. Having a regular singularity at $\zeta = 0$ means the following:
+for some $p, q \in \mathcal{H}(\Omega)$. \begin{revtwo}Explicitly,
+\[ \big[\hardpart \varphi\big](a) = - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a')\,. \]
+\end{revtwo}
+
+For the purposes of this paper, $\hardpart$ has a {\em regular singularity} at $\zeta=0$ if the following condition holds.
 \begin{conditions}
-\condconst{sing}{\tau}\label{cond:sing} For some non-zero constant $\tau$---which we'll require, for simplicity, to be real and positive---the difference
+\condconst{sing}{\tau}\label{cond:sing}For some constant $\tau > 0$, the difference
 \[ \hardker(a, a) - \frac{\tau}{\zeta(a)} \]
 is bounded on a neighborhood of $\zeta(a) = 0$ in $\domain$.
-In addition, for each $\sigma > \tau$, the bound
-\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|} \]
-holds over some neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\domain^2$. 
+In addition, for each $\sigma > \tau$, there is a neighborhood of $\big(\zeta(a), \zeta(a')\big) = (0, 0)$ in $\Omega^2$ on which
+\[ |\hardker(a, a')| < \frac{\sigma}{|\zeta(a)|}. \]
 \end{conditions}
-For most of our results, we'll need to make sure that $\domain$ doesn't touch any singularities of $\hardpart$ other than the one at $\zeta = 0$.
-We'll also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
+For most of our results, we will need to make sure that $\domain$ does not touch any singularities of $\hardker$ other than the one at $\zeta = 0$.
+We will also need to control $\hardker(a, a')$ when $a$ is away from $\zeta = 0$, requiring $\hardker$ to be bounded on the diagonal in $\domain^2$ and to grow at most exponentially as we move away from the diagonal.
 These requirements can be combined into one condition.
@@
 \end{conditions}
-This condition explains why $\domain$ might have the sort of shape illustrated in Section~\ref{setting:domain}.
+This condition explains the shape of the example domain illustrated in Section~\ref{setting:domain}.
 As $\domain$ stretches out toward infinity, it has to part around the zeros of $p$, keeping well away from every zero except the one at $\zeta = 0$.
-%\color{Tomato}
-%Furthermore, Condition \eqref{cond:diag-basic} tells us that for any $\sigma>0$ we can find a neighbourhood of $(0,0)\in\domain^2$ where 
-%\[|\hardker(a,a')|\le\frac{\sigma}{|\zeta(a)|}.\]
 \begin{verify}
@@
 \end{verify}
-\color{black}
-We'll occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
+
+We will occasionally mention an optional condition on $p$ that allows us to state our main results more explicitly.
 \begin{conditions}
@@
 
-Now, let's perturb $\hardpart$ to a more general operator $\volterra=\hardpart +\softpart$.
-The perturbation $\softpart$ doesn't have a separable kernel,\footnote{Unless $\softpart$ is zero, of course.} but does have a smoothing effect that counteracts the singularity of $\hardpart$ (as we'll show in Proposition \ref{prop:smoothing}).
-To get the smoothing effect, we'll require the kernel $\softker$ of $\softpart$ to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
+We now perturb $\hardpart$ to a more general operator $\volterra = \hardpart +\softpart$. \begin{revtwo}The perturbation
+\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
+will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
+To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
 This requirement, combined with two others, will be made precise in Condition~\eqref{cond:eps-lambda}.
@@
 Since $\softpart$ is a holomorphic Volterra operator, $\softker$ is a holomorphic function on $\domain^2$.
-We'll allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we won't allow any sharper singularity.
-We'll also put an exponential bound on how fast $\softker$ grows away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
-Altogether, we'll require:
+We will allow $\softker(a, a')$ to have a simple pole at $\zeta(a) = 0$, like $\hardker(a, a')$ does, but we will not allow any sharper singularity.
+We will also put an exponential bound on the growth of $\softker$ away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
+Altogether, we will require:
 \begin{conditions}
-\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} For some constant $\gamma > 0$, we have
+\condconst{diag$_\star$}{\gamma, \lambda_\Delta}\label{cond:eps-lambda} There is a constant $\gamma > 0$ for which
 \[ |\softker(a, a')| \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 For the prototypical operator $\hardpart$ described in Section~\ref{setting:basic}, this solution can be written explicitly.
-\begin{thm}\label{thm:basic_volterra}
-Suppose $\hardpart$ satisfies {\em Condition \eqref{cond:sing}}. Then the equation
-\[ f = \hardpart f \]
+\begin{theorem}\label{thm:basic_volterra}
+\begin{revtwo}Suppose the operator%%$\hardpart$
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
+\end{revtwo}
+satisfies {\em Condition \eqref{cond:sing}}. Then the equation
+\begin{equation}\label{eq:hardpart}
+f = \hardpart f    
+\end{equation}
 has the {\em prototype solution}
@@
 \end{equation}
-Changing the base point $b \in \domain$ just multiplies $f_0$ by a non-zero constant.
-\end{thm}
-We'll prove this result in Section~\ref{sec:construction}.
+Changing the base point $b \in \domain$ only multiplies $f_0$ by a non-zero constant.
+\end{theorem}
+We will prove this result in Section~\ref{sec:construction}.
 
 The solution $\solproto$ from Theorem~\ref{thm:basic_volterra} has, at worst, a mild power-law singularity at $\zeta = 0$.
-With stronger constraints on $\hardpart$, we can also ensure that $\solproto$ grows at most exponentially as $|\zeta| \to \infty$.
+When $\hardpart$ is especially regular, $\solproto$ also grows at most exponentially as $|\zeta| \to \infty$.
 The function spaces defined in Section~\ref{fn-spaces} express both of these regularity properties.
-%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, it'll be enough to assume Condition \eqref{cond:diag-basic} to state Theorem \ref{thm:proto-growth}.}
-\begin{thm}\label{thm:proto-growth}
-Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
+\begin{revtwo}We will state our results in terms of the spaces $\singexpalg{\sigma}(\domain)$, which are defined as unions of normed spaces.
+Every function $f \in \singexpalg{\sigma}(\domain)$ has a finite norm
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f| \]
+for some $\Lambda \in \R$.
+\end{revtwo}
+\begin{theorem}\label{thm:proto-growth}
+\begin{revtwo}Suppose the operator
+\[ \big[\hardpart \varphi\big](a) := - \int_{\zeta(a')=0}^{a} \frac{q(a')}{p(a)}\,\varphi(a')\;d\zeta(a') \]
+\end{revtwo}
+satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
 
 Suppose $\hardpart$ also satisfies {\em Condition~\eqref{cond:diag-basic}}. Then $f_0$ belongs to the space $\singexpalg{\tau-1}(\domain)$ defined in Section~\ref{fn-spaces}.
-\end{thm}
-We'll prove this result in Section~\ref{sec:asymptotics}.
+\end{theorem}
+We will prove this result in Section~\ref{sec:asymptotics}.
 \begin{rmk}
@@
 
-When we perturb $\hardpart$ to the more general operator $\volterra = \hardpart + \softpart$ from Section~\ref{setting:perturbed}, the equation we're trying to solve gets more complicated, but its regular singularity at $\zeta = 0$ stays essentially the same.
-We might therefore expect to find a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
+The perturbed equation $f = \volterra f$ is more complicated, but its regular singularity at $\zeta = 0$ is essentially the same.
+We might therefore expect a solution that looks like $\solproto$ near the singularity, differing only by a less singular perturbation.
 If we strengthen the constraints on $\hardpart$ a little more, this expectation is fulfilled.
-\begin{thm}\label{thm:general_volterra}
-Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
-\[f = \volterra f\]
-has a unique solution $f$ in the affine subspace
+\begin{theorem}\label{thm:general_volterra}
+Suppose $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and \begin{revtwo}the perturbation
+\[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
+\end{revtwo}
+satisfies {\em Condition~\eqref{cond:eps-lambda}}. Then the equation
+\[ f = \volterra f, \]
+\revtwotext{where $\volterra = \hardpart + \softpart$,} has a unique solution $f$ in the affine subspace
 \[ f_0 + \singexpalg{\tau-1+\gamma}(\Omega) \]
@@
 Here, $f_0$ is the prototype solution \eqref{eqn:test_solution} from Theorems \ref{thm:basic_volterra}--\ref{thm:proto-growth}, which belongs to the space $\singexpalg{\tau-1}(\domain)$.
-
-For any $\rho > \tau$, the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$.
-In other words, lowering $\rho$ into $(\tau, \tau+\gamma)$ to allow a sharper singularity won't reveal any more solutions, and raising $\rho$ too high to admit the solution found in $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ will leave no solution at all.
-\end{thm}
+\end{theorem}
+\begin{corollary}\label{cor:expand_uniq}
+Under the conditions of Theorem~\ref{thm:general_volterra}, for any $\rho > \tau$, the equation $f = \volterra f$ has at most one solution in $f_0 + \singexpalg{\rho-1}(\Omega)$. 
+\end{corollary}
 This result will follow from a more general result about inhomogeneous equations.
@@
 \end{lemma}
-We'll prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
+We will prove Lemma~\ref{lem:perturbed_volterra} in Sections \ref{sec:V is a contraction}--\ref{sec:existence and uniqueness}, using the contraction mapping theorem.
 The heart of the argument is Proposition~\ref{prop:get-contraction}, which shows us how to find relevant subspaces where $\volterra$ is a contraction.
 
-We'll reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation we want to solve as an inhomogeneous equation in a more regular space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we'll use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} proving that $\softpart$ improves on the regularity of $f_0$ described by Theorem~\ref{thm:proto-growth}.
+We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ as an inhomogeneous equation in a more regular space.
+To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to prove that $\softpart$ improves on the regularity ascribed by Theorem~\ref{thm:proto-growth} to the prototype solution $f_0$.
 \begin{rmk}
@@
 \subsection{Weighted holomorphic $L^{\infty}$ spaces}\label{sec:fn-space-defs}
-Throughout this paper, as described in Section~\ref{motivation}, the ``position'' variable $\zeta$ will be the standard coordinate on $\C$.
-Take a simply connected open set $\domain \subset \C$ that touches but doesn't contain $\zeta = 0$.
-Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$.
-Give $\cont(\domain)$ the compact-open topology, recalling that this is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
+Throughout this paper, as described in Section~\ref{sec:motivation}, the position variable $\zeta$ will be the standard coordinate on $\C$.
+Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$.
+Let $\cont(\domain)$ be the space of continuous complex-valued functions on $\domain$, equipped with the compact-open topology.
+This is the coarsest topology in which the seminorm $f \mapsto \sup_K |f|$ is continuous for every compact subset $K \subset \domain$~\cite[Example~2.6 and Section~4 notes]{fnl-cpx-anal}.
+
 The holomorphic functions form a closed subspace $\holo(\domain) \subset \cont(\domain)$~\cite[Proposition~3.14]{fnl-cpx-anal}.
-
-Fixing a real constant $\Lambda$, let's restrict our attention to holomorphic functions on $\domain$ which are bounded by constant multiples of $e^{\Lambda|\zeta|}$.
-One might describe these functions as being uniformly of exponential type $\Lambda$.\footnote{Recall that a function is of exponential type $\Lambda$ if for every $\varepsilon>0$, there's a constant $A_\varepsilon$---which may depends on $\varepsilon$---such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
-We instead require a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.} They form a space $\singexp{0}{\Lambda}(\domain)$, which we'll equip with the norm $\|f\|_{0,\Lambda} = \sup_\domain e^{-\Lambda|\zeta|}\,|f|$.
+We first restrict our attention to holomorphic functions on $\domain$ which are uniformly of exponential type $\Lambda \in \R$.
+\begin{definition}\label{def:unif-exp}
+For any $\Lambda \in \R$, let
+\[ \singexp{0}{\Lambda}(\domain) \subset \holo(\domain) \]
+be the subspace consisting of functions $f$ with $|f| \lesssim e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
+\[ \|f\|_{0, \Lambda} := \sup_\Omega e^{-\Lambda|\zeta|}\,|f|. \]
+\end{definition}
 With respect to the seminorm on $\holo(\domain)$ given by a compact set $K \subset \domain$, the inclusion map $\singexp{0}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ has norm $\sup_K e^{\Lambda |\zeta|}$.
 That means the inclusion is continuous.
-\begin{prop}\label{exp-complete}
-The space $\singexp{0}{\Lambda}(\domain)$ is complete.
-\end{prop}
+\begin{rmk}
+The subspace of functions of exponential type $\Lambda$ strictly contains $\singexp{0}{\Lambda}(\domain)$.
+A function $f$ is of exponential type $\Lambda$ if for every $\varepsilon>0$, there is a constant $A_\varepsilon$ such that $|f|\le A_\varepsilon e^{(\Lambda+\varepsilon)|\zeta|}$.
+Definition~\ref{def:unif-exp} instead requires a uniform constant $A$ such that $|f| \le A e^{\Lambda|\zeta|}$.\end{rmk}
+We now relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
+\begin{definition}
+For any $\sigma, \Lambda \in \R$, let
+\[ \singexp{\sigma}{\Lambda}(\domain) \subset \holo(\domain) \]
+be the subspace consisting of functions $f$ with $|f| \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\domain$, equipped with the norm
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]
+\end{definition}
+The inclusion $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is again continuous.
+\begin{proposition}\label{exp-complete}
+The space $\singexp{\sigma}{\Lambda}(\domain)$ is complete.
+\end{proposition}
 \begin{proof}
-Take a Cauchy sequence $f_1, f_2, f_3, \ldots \in \singexp{0}{\Lambda}(\Omega)$.
-The inclusion map $\singexp{0}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is bounded with respect to each of the seminorms on $\holo(\Omega)$ given by $|f| \mapsto \sup_K |f|$ for compact subsets $K \subset \Omega$, so our sequence is Cauchy in $\holo(\Omega)$ too.
-Since $\holo(\Omega)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\Omega)$ will always converge in the topology of $\holo(\Omega)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
-
-The Cauchy property in $\singexp{0}{\Lambda}(\Omega)$ tells us that for any $r > 0$, we can find some $n$ for which $e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
-Since convergence in $\holo(\Omega)$ implies pointwise convergence, we can see as $k$ grows that $e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
-This shows that our sequence converges to $f$ in the norm $\|\cdot\|_{0,\Lambda}$.
-We can also see from this argument that $f$ is in $\singexp{0}{\Lambda}(\domain)$: picking some $r > 0$, we observe that
-\begin{align*}
-e^{-\Lambda |\zeta|}\,|f| & \le e^{-\Lambda |\zeta|}\,|f - f_n| + e^{-\Lambda |\zeta|}\,|f_n| \\
-& \le r + \|f_n\|_{0,\Lambda}
-\end{align*}
-for the corresponding $n$, showing that $e^{-\Lambda |\zeta|}\,|f|$ is bounded.
-\end{proof}
-
-Now, let's relax our norm to allow both exponential growth at infinity and a power-law singularity at $\zeta = 0$.
-For any $\sigma \in \R$, let $\singexp{\sigma}{\Lambda}(\Omega)$ be the space of holomorphic functions on $\Omega$ which are bounded by constant multiples of $|\zeta|^\sigma e^{\Lambda|\zeta|}$.
-Give it the norm $\|f\|_{\sigma,\Lambda} = \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|$.
-Reprising the arguments from above, we can show that the inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \holo(\Omega)$ is continuous, and we can generalize Proposition~\ref{exp-complete}:
-\begin{prop}
-The space $\singexp{\sigma}{\Lambda}(\Omega)$ is complete.
-\end{prop}
+Take a Cauchy sequence $(f_j)_{j \in \N}$ in $\singexp{\sigma}{\Lambda}(\domain)$.
+This sequence is Cauchy in $\holo(\domain)$ as well, because the inclusion map $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \holo(\domain)$ is bounded with respect to each of the seminorms on $\holo(\domain)$ given by $f \mapsto \sup_K |f|$ for compact subsets $K \subset \domain$.
+Since $\holo(\domain)$ is complete~\cite[Proposition~3.5]{fnl-cpx-anal},\footnote{That is, a sequence which is Cauchy in each of the seminorms on $\holo(\domain)$ will always converge in the topology of $\holo(\domain)$, which is the coarsest topology in which all of the seminorms are continuous.} our sequence converges to a function $f$ there.
+
+The Cauchy property in $\singexp{\sigma}{\Lambda}(\domain)$ says that for any $r > 0$, there is some $n$ for which $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_k - f_n| \le r$ whenever $k \ge n$.
+Since convergence in $\holo(\domain)$ implies pointwise convergence, it follows that $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f - f_n| \le r$.
+This reasoning shows that $(f_j)_{j \in \N}$ converges to $f$ in the norm $\|\cdot\|_{\sigma, \Lambda}$.
+It also shows that $f$ is in $\singexp{\sigma}{\Lambda}(\domain)$: picking some $r > 0$, we have
+\begin{align*}
+|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f| & \le |\zeta|^\sigma e^{-\Lambda |\zeta|}\,|f - f_n| + |\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f_n| \\
+& \le r + \|f_n\|_{\sigma,\Lambda}
+\end{align*}
+for the corresponding $n$, so $|\zeta|^{-\sigma} e^{-\Lambda |\zeta|}\,|f|$ is bounded.
+\end{proof}
 \subsection{Continuous inclusions between different $\singexp{\sigma}{\Lambda}(\Omega)$}\label{sec:inclusions}
-\begin{prop}\label{prop:inclus-ge-exp}
+\begin{proposition}\label{prop:inclus-ge-exp}
 If $\Lambda'\leq\Lambda$, the inclusion map $\singexp{\sigma}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-As we mentioned in Section~\ref{sec:fn-space-defs}, one might describe $\singexp{0}{\Lambda}(\domain)$ as the space of functions on $\domain$ which are uniformly of exponential type $\Lambda$.
-Taking the union of these spaces over all $\Lambda \in \R$, we get the space $\singexpalg{0}(\domain)$ that contains all functions of exponential type.
-Having continuous inclusions between the subspaces $\singexp{0}{\Lambda}(\domain)$ as $\Lambda$ increases, we can give $\singexpalg{0}(\domain)$ a meaningful topology: the finest topology that makes all the inclusions $\singexp{0}{\Lambda}(\domain) \hookrightarrow \singexpalg{0}(\domain)$ continuous.\footnote{In category-theoretic language, $\singexpalg{0}(\domain)$ is the limit of the family $\singexp{0}{\Lambda}(\domain)$.} For any $\sigma \in \R$, we define $\singexpalg{\sigma}(\domain)$ similarly.
-\begin{prop}\label{prop:inclus-lt-pow-gt-exp}
+The union $\bigcup_{\Lambda \in \R} \singexp{0}{\Lambda}(\domain)$ is the subspace comprising all functions of exponential type.
+The continuous inclusions between the $\singexp{0}{\Lambda}(\domain)$ define a limit topology on this subspace.
+The spaces $\singexp{\sigma}{\Lambda}(\domain)$ fit together analogously for other $\sigma \in \R$.
+\begin{definition}\label{def:exp-top}
+For any $\sigma \in \R$, let $\singexpalg{\sigma}(\domain)$ be the union
+\[ \bigcup_{\Lambda \in \R} \singexp{\sigma}{\Lambda}(\domain) \]
+equipped with the finest topology that makes all the inclusions $\singexp{\sigma}{\Lambda}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ continuous.
+\end{definition}
+\begin{proposition}\label{prop:inclus-lt-pow-gt-exp}
 If $\sigma'>\sigma$ and $\Lambda'<\Lambda$, the inclusion map $\singexp{\sigma'}{\Lambda'}(\Omega)\hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ is continuous.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 \end{proof}
-\begin{prop}\label{prop:inclus-lt-pow-alg}
-When $\sigma' > \sigma$, there's a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
-\end{prop}
+\begin{proposition}\label{prop:inclus-lt-pow-alg}
+When $\sigma' > \sigma$, there is a continuous inclusion $\singexpalg{\sigma'}(\domain)\hookrightarrow \singexpalg{\sigma}(\domain)$.
+\end{proposition}
 \begin{proof}
-For each $\Lambda'$, we can get a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusion $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexp{\sigma}{\Lambda}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-gt-exp} with the continuous inclusion $\singexp{\sigma}{\Lambda}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ that we get by definition.
-For any $\Lambda'' < \Lambda'$, the inclusions $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ and $\singexp{\sigma'}{\Lambda'}(\Omega) \hookrightarrow \singexpalg{\sigma}(\Omega)$ constructed above automatically commute with the inclusion $\singexp{\sigma'}{\Lambda''}(\Omega) \hookrightarrow \singexp{\sigma'}{\Lambda'}(\Omega)$ given by Proposition~\ref{prop:inclus-ge-exp}, because we're ultimately working in the vector space of holomorphic functions on $\Omega$.
-Because of how the topology on $\singexpalg{\sigma'}(\Omega)$ is defined, this gives us the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$.
+For each $\Lambda'$, we define a continuous inclusion $\singexp{\sigma'}{\Lambda'}(\domain) \hookrightarrow \singexpalg{\sigma}(\domain)$ by choosing some $\Lambda > \Lambda'$ and composing the continuous inclusions
+\begin{center}
+\begin{tikzcd}[column sep=25mm, labels={inner sep=0.75ex}]
+\singexp{\sigma'}{\Lambda'}(\domain) \arrow[r, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-lt-pow-gt-exp}}"'] & \singexp{\sigma}{\Lambda}(\domain) \arrow[r, hook, "\text{\footnotesize Definition~\ref{def:exp-top}}"'] & \singexpalg{\sigma}(\domain).
+\end{tikzcd}
+\end{center}
+For any $\Lambda'' < \Lambda'$, the inclusions
+\begin{center}
+\begin{tikzcd}[row sep=6mm, column sep=8mm, labels={inner sep=0.75ex}]
+\singexp{\sigma'}{\Lambda''}(\domain) \arrow[rr, hook, "\text{\footnotesize Proposition~\ref{prop:inclus-ge-exp}}"] \arrow[rd, hook] & & \singexp{\sigma'}{\Lambda'}(\domain) \arrow[ld, hook] \\
+& \singexpalg{\sigma}(\domain)
+\end{tikzcd}
+\end{center}
+automatically commute, because as non-topological linear maps they are all inclusions between subspaces of $\holo(\domain)$.
+The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
 \end{proof}
@@
 \subsection{Overview}
-The results stated in Section~\ref{sec:results} lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
-We'll now show that the method works by proving those results.
-
-We start by constructing the prototype solution $\solproto$ from the kernel of $\hardpart$, which is the separable operator that gives $\volterra = \hardpart + \softpart$ its regular singularity.
-We'll show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
-
-To see what the perturbation $\softpart$ does to $\solproto$, we'll show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
+In this section, we prove the results stated in Section~\ref{sec:results}, which lay out a method for solving the regular singular Volterra equation $\solwhole = \volterra \solwhole$.
+
+We first construct the prototype solution $\solproto$ from the kernel of $\hardpart$.
+We show in Section~\ref{sec:proto-construction-regularity} that $\solproto$ satisfies the equation $\solproto = \hardpart \solproto$ and belongs to the space $\singexp{\tau-1}{\lambda_0}(\domain)$.
+
+We then study how the perturbation $\softpart$ affects $\solproto$.
+We show in Section~\ref{sec:image under soft_part} that $\softpart$ has a smoothing effect, reducing the sharpness of any power-law singularity at $\zeta = 0$.
 In particular, it sends $\solproto$ into $\singexpalg{\tau-1+\gamma}(\domain)$.
 
-Now we know that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
-To confirm this, we'll show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
-This tells us that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we'll see in Section~\ref{sec:existence and uniqueness}.
+We conclude that $\volterra$ sends $\solproto$ into the affine subspace $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, suggesting that the equation $\solwhole = \volterra \solwhole$ has a solution there.
+To confirm this, we show in Section~\ref{sec:V is a contraction} that $\volterra$ is a contraction of $\singexp{\tau-1+\gamma}{\Lambda}(\domain)$ when $\Lambda$ is large enough.
+This implies that $\volterra$ has a unique fixed point in $\solproto + \singexpalg{\tau-1+\gamma}(\domain)$, as we show in Section~\ref{sec:existence and uniqueness}.
 \subsection{Construction and regularity of the prototype solution \\ \textit{(proof of Theorems~\ref{thm:basic_volterra}--\ref{thm:proto-growth})}}\label{sec:proto-construction-regularity}
-
 \subsubsection{Construction}\label{sec:construction}
@@
 \[ \chi(a) = \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta\right). \]
-Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ greatly simplifies the calculation of $\hardpart \solproto$. For each $a \in \domain$,
+Observing that $d\chi = -(q/p)\,\chi\;d\zeta$ simplifies the calculation of $\hardpart \solproto$. For each $a \in \domain$,
 \begin{align*}
@@
 \end{align*}
-Now, to prove that $\hardpart \solproto = \solproto$, we just need to show that $\lim_{\zeta \to 0} \chi = 0$.
-
-By Condition~\eqref{cond:sing}, we can find a radius $\delta>0$ and a constant $C$ such that
+To prove that $\hardpart \solproto = \solproto$, we must now show that $\lim_{\zeta \to 0} \chi = 0$.
+
+By Condition~\eqref{cond:sing}, there exist a radius $\delta>0$ and a constant $C$ such that
 \begin{equation}\label{eqn:sing-bound}
-\left|\frac{q}{p} - \frac{\tau}{\zeta}\right| < C
+\left|\frac{q}{p} + \frac{\tau}{\zeta}\right| < C
 \end{equation}
-whenever $|\zeta| < \delta$. We can take advantage of this bound by rewriting the integral in the definition of $\chi$:
+whenever $|\zeta| < \delta$. To use this bound, we rewrite the integral in the definition of $\chi$:
 \begin{align*}
 -\int_b^a \frac{q}{p}\;d\zeta & = \int_b^a \frac{\tau}{\zeta}\;d\zeta - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta \\
-& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta
-\end{align*}
-Exponentiating both sides, we see that
+& = \tau \log\left(\frac{\zeta(a)}{\zeta(b)}\right) - \int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta.
+\end{align*}
+Exponentiating both sides shows that
 \[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
@@
 \subsubsection{Regularity}\label{sec:asymptotics}
-%\textcolor{Tomato}{If we change Condition \eqref{cond:sing}, then we might simply have proof of Theorem \ref{thm:proto-growth} assuming only Condition \eqref{cond:diag-basic}.
-The proofs of the Proposition below can be combined together.}
-Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We'll prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
-\begin{prop}\label{prop:asymptotic at zero}
+Theorem~\ref{thm:proto-growth} comprises two results with different conditions. We will prove them separately as Propositions \ref{prop:asymptotic at zero} and \ref{prop:asymptotic at infinity}.
+\begin{proposition}\label{prop:asymptotic at zero}
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:sing}}. Then, on a small enough neighborhood of $\zeta = 0$, we have $|\solproto| \lesssim |\zeta|^{\tau-1}$.
-\end{prop}
+\end{proposition}
 
 \begin{proof}
-Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that Inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta| < \delta$.
+Go back to the proof of Theorem~\ref{thm:basic_volterra}, where we found a radius $\delta > 0$ and a constant $C$ such that inequality~\eqref{eqn:sing-bound} holds whenever $|\zeta| < \delta$.
 The subsequent argument, which we used to show that $\lim_{\zeta \to 0} \chi = 0$, actually supports a stronger conclusion: it shows that $|\chi| \lesssim |\zeta|^\tau$ on the region $|\zeta| < \delta$.
-This tells us that
+This implies that
 \[ |\solproto| \lesssim \left|\frac{1}{p}\right|\,|\zeta|^\tau \]
@@
 
-Now, using Condition~\eqref{cond:sing} again, choose some $\sigma > \tau$ and find a radius $r < \delta$ for which
+Choose some $\sigma > \tau$. By Condition~\eqref{cond:sing}, there is a radius $r < \delta$ for which
 \[ \left|\frac{q(a')}{p(a)}\right| < \frac{\sigma}{|\zeta(a)|} \]
-whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we can deduce that
+whenever $|\zeta(a)| < r$ and $|\zeta(a')| < r$. Choosing a point $b'$ with $|\zeta(b')| < r$ and $q(b') \neq 0$, we deduce that
 \begin{align*}
@@
 
-By Proposition~\ref{prop:asymptotic at zero}, we can find a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
-No matter which value of $\lambda_0$ we pick, we know that $e^{\lambda_0|\zeta|}$ can't get arbitrarily close to zero on a bounded region, so we'll have $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
+By Proposition~\ref{prop:asymptotic at zero}, there is a radius $\delta > 0$ for which $|\solproto| \lesssim |\zeta|^{\tau-1}$ over the region $|\zeta| < \delta$.
+No matter which value of $\lambda_0$ we pick, $e^{\lambda_0|\zeta|}$ cannot get arbitrarily close to zero on a bounded region, so $|\solproto| \lesssim |\zeta|^{\tau-1} e^{\lambda_0|\zeta|}$ over the region $|\zeta| < \delta$.
 
@@
 \end{align*}
-over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. One consequence is that, for some $c_\Delta > 0$, we have
+over all $a, a' \in \domain$ with $|\zeta(a)| \ge \delta$. The last bound means that for some $c_\Delta > 0$,
 \[ |\hardker(a, a')| \le c_\Delta e^{\lambda_\Delta |\zeta(a) - \zeta(a')|} \]
 whenever $|\zeta(a)| \ge \delta$.
-Applying this bound along the diagonal in $\domain^2$, we learn that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
+Applying this bound along the diagonal in $\domain^2$, we conclude that $|q/p| \le c_\Delta$ on the region $|\zeta| \ge \delta$.
 On the other hand, by fixing some arbitrary  $b' \in \domain$, we see that
@@
 \end{align*}
-over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we reason that
+over all $a \in \domain$ with $|\zeta(a)| \ge \delta$. Using both of the bounds we just found, we deduce that
 \begin{align*}
@@
 \end{proof}
-\begin{prop}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then, for some constant $M$,
+\begin{proposition}\label{prop:better-proto-estimate}
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then there is some $M\in\C$ for which,
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
 at $\zeta = 0$, where $\epsilon'=\min\{\epsilon, 1\}$.
-\end{prop}
+\end{proposition}
 \begin{proof}
-It's enough to show that
+It is enough to show that
 \[ \solproto \in M\zeta^{\tau-1} \Big[1 + O\big(|\zeta|^{\epsilon'}\big)\Big] \]
-at $\zeta = 0$. Like we did in the proof of Theorem~\ref{thm:basic_volterra}, we reason that
+at $\zeta = 0$. As in the proof of Theorem~\ref{thm:basic_volterra}, we compute
 \begin{align*}
@@
 \end{align*}
-Since $\zeta(b)^{-\tau}$ is a constant, the $\zeta(b)^{-\tau}\,\zeta^{\tau-1}$ factor looks like what we want.
-
-With a little work, the $\zeta/p$ factor also looks like what we want. Condition \eqref{cond:reg-p} implies that
+Note that $\zeta(b)^{-\tau}$ is a constant, which will eventually be absorbed into $M$.
+
+Condition \eqref{cond:reg-p} implies that
 \[ \frac{\zeta}{p} \in B^{-1} + O\big(|\zeta|^{\epsilon}\big), \]
@@
 
-Now, let's look at the exponential factor. By Condition~\eqref{cond:sing}, we can find a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
+Now, consider the exponential factor. By Condition~\eqref{cond:sing}, there exists a constant $C$ and a neighborhood $\domain_\text{near}$ of $\zeta = 0$ for which
 \[ \left| \frac{q}{p}+\frac{\tau}{\zeta} \right| < C \]
@@
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] = e^{\eta(b)} e^{-\eta(a)}. \]
-Observing that $|\eta| \le C |\zeta|$ in $\near$, we can conclude that
+Observing that $|\eta| \le C |\zeta|$ in $\near$, we conclude that
 \[ \exp\left[-\int_b^a\left(\frac{q}{p}+\frac{\tau}{\zeta}\right) d\zeta\right] \in e^{\eta(b)} \Big[ 1 + O\big(|\zeta(a)|\big) \Big] \]
@@
 
-Combining the arguments above, we learn that
+Together, the arguments above show that
 \begin{align*}
@@
 \end{align*}
-at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we get the desired result.
+at $\zeta = 0$, with $M = \zeta(b)^{-\tau} B^{-1} e^{\eta(b)}$. Observing that $O\big(|\zeta|^{\epsilon}\big) + O\big(|\zeta|\big) = O\big(|\zeta|^{\epsilon'}\big)$, we reach the desired result.
 \end{proof}
 \subsection{Showing that $\softpart$ makes the prototype solution less singular \\ \textit{(toward Theorem~\ref{thm:general_volterra})}}\label{sec:image under soft_part}
-Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we'll show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$.
+Now that we know the prototype solution $\solproto$ belongs to $\singexpalg{\tau-1}(\domain)$, we will show that $\softpart$ reduces the sharpness of its singularity at $\zeta = 0$, mapping it into $\singexpalg{\tau-1+\gamma}(\domain)$.
 This is a consequence of the general smoothing effect of $\softpart$, described in the following result.
 
-\begin{prop}\label{prop:smoothing}
+\begin{proposition}\label{prop:smoothing}
 Under {\em Condition~\eqref{cond:eps-lambda}}, the operator $\softpart$ maps
@@
 continuously for all $\Lambda\geq \lambda_{\Delta}$ and $\sigma>-1$.
-\end{prop}
+\end{proposition}
 \begin{rmk}
-We're assuming that $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We'll take advantage of this in Section~\ref{sec:L-int-op}
+We assume $\gamma > 0$, but this result holds even under the weaker assumption that $\gamma > -1$. We will take advantage of this in Section~\ref{sec:L-int-op}.
 \end{rmk}
@@
 For any function $f\in\singexp{\sigma}{\Lambda}(\domain)$,
-\begin{align*}
-|\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |f| \, |d\zeta| \\
-&\leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \|f\|_{\sigma,\Lambda} \, |d\zeta| 
-\end{align*}
+\begin{revtwo}
+\begin{align*}
+& |\zeta(a)|^{-(\sigma+\gamma)} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert \\
+& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |f(a')| \, |d\zeta(a')| \\
+& \qquad \leq |\zeta(a)|^{-(\sigma+\gamma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \|f\|_{\sigma,\Lambda} \, |d\zeta(a')|\,.
+\end{align*}
+\end{revtwo}
 By Condition~\eqref{cond:eps-lambda},
-\begin{align*}
-\int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| &\lesssim \int_{\zeta=0}^a \frac{|\zeta(a)-\zeta|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta|} |\zeta|^{\sigma}\, e^{\Lambda|\zeta|}\;|d\zeta|\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
-&\lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
-\end{align*}
-The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. Recognizing the integral as an evaluation of the beta function, we can rewrite the bound as
-\[ \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}.
+\begin{revtwo}
+\begin{align*}
+& \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \\
+& \qquad \lesssim \int_{\zeta(a')=0}^a \frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|} e^{\lambda_\Delta |\zeta(a)-\zeta(a')|} |\zeta(a')|^{\sigma}\, e^{\Lambda|\zeta(a')|}\;|d\zeta(a')|\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma} \int_{0}^1 (1-t)^\gamma e^{\lambda_\Delta |\zeta(a)|(1-t)} t^{\sigma}\, e^{\Lambda|\zeta(a)| t}\;dt\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,  \int_{0}^1 (1-t)^\gamma  t^{\sigma}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)| t}\;dt\\
+& \qquad \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\lambda_\Delta |\zeta(a)|}\,e^{(\Lambda-\lambda_\Delta)|\zeta(a)|}\int_{0}^1 (1-t)^\gamma  t^{\sigma}\;dt.
+\end{align*}
+\end{revtwo}
+The last step takes advantage of the assumption that $\Lambda \ge \lambda_\Delta$. The integral on the last line is Euler's beta integral~\cite[equation~5.12.1]{dlmf}, so
+\begin{revtwo}
+\[ \int_{\zeta(a')=0}^a |\softker(a, a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim |\zeta(a)|^{\gamma+\sigma}\, e^{\Lambda |\zeta(a)|} \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,.
 \]
-Our assumptions that $\gamma > 0$ and $\sigma > -1$ ensure that the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
-\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta=0}^a |\softker(a,\cdot)|\, |\zeta|^{\sigma}\, e^{\Lambda |\zeta|} \, |d\zeta| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}, \]
+\end{revtwo}
+Since $\gamma > 0$ and $\sigma > -1$, the gamma functions are well-defined.\footnote{We could even weaken the constraint on $\gamma$, allowing any $\gamma > -1$.} Rearranging to get
+\begin{revtwo}
+\[ |\zeta(a)|^{-(\gamma+\sigma)}\, e^{-\Lambda |\zeta(a)|} \int_{\zeta(a')=0}^a |\softker(a,a')|\, |\zeta(a')|^{\sigma}\, e^{\Lambda |\zeta(a')|} \, |d\zeta(a')| \lesssim \frac{\Gamma(\gamma+1)\Gamma(\sigma+1)}{\Gamma(\sigma+\gamma+2)}\,, \]
+\end{revtwo}
 we conclude that $|\zeta(a)|^{-\sigma-\gamma} \, e^{-\Lambda |\zeta(a)|} \, \Big \vert \big[ \softpart f\big](a)\Big\vert$ is uniformly bounded in $\domain$. 
 \end{proof}
-\begin{cor}\label{cor:pertub_f0}
-Consider the prototype solution $\solproto$ from Equation~\eqref{eqn:test_solution}.
+\begin{corollary}\label{cor:pertub_f0}
+Consider the prototype solution $\solproto$ from equation~\eqref{eqn:test_solution}.
 If $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}, then $\softpart \solproto$ belongs to $\singexpalg{\tau-1+\gamma}(\domain)$.
-\end{cor}
+\end{corollary}
 \begin{proof}
@@
 \subsubsection{Overview}
-In this section, we'll prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
-
-\begin{prop}\label{prop:get-contraction}
+In this section, we will prove the following proposition. %We assume $\volterra$ satisfies Conditions \eqref{cond:sing}, \eqref{cond:diag-basic} and \eqref{cond:eps-lambda}.
+
+\begin{proposition}\label{prop:get-contraction}
 Suppose that $\hardpart$ satisfies {\em Conditions \eqref{cond:sing}} and \eqref{cond:diag-basic}, and $\softpart$ satisfies {\em Condition \eqref{cond:eps-lambda}}.
-Then, for each $\rho > \tau$, we can ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\domain)$ by making $\Lambda$ big enough.
-\end{prop}
+Then, for each $\rho > \tau$, there is some $\Lambda_\text{\rm lower} \in \R$ such that
+\[\volterra\colon\singexp{\rho-1}{\Lambda}(\domain)\to\singexp{\rho-1}{\Lambda}(\domain)\]
+is a contraction for all $\Lambda > \Lambda_\text{\rm lower}$.
+\end{proposition}
 \begin{rmk}
-For the argument, we'll use, ``big enough'' always requires $\Lambda > \lambda_\Delta$, and may require $\Lambda \gg \lambda_\Delta$.
+The threshold $\Lambda_\text{\rm lower}$ is always greater than $\lambda_\Delta$, and often much greater.
 \end{rmk}
-First, pick some $\sigma \in (\tau, \rho)$.\footnote{If you'd like, you can fix a choice of $\sigma$---for example, taking $\sigma = \frac{1}{2}(\tau + \rho)$.} By Proposition~\ref{prop:whole-ker-near-bound}, which we'll state and prove in Section~\ref{sec:bounds on k}, we can find a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
+First, pick some $\sigma \in (\tau, \rho)$.
+Proposition~\ref{prop:whole-ker-near-bound}, which we will state and prove in Section~\ref{sec:bounds on k}, shows that there is a neighborhood $\near \subset \domain$ of $\zeta = 0$ with the property that
 \begin{equation}\label{near-limit}
@@
 Take any function $\varphi \in \singexp{\rho}{\Lambda}(\domain)$.
-In Section~\ref{near-bound}, we'll bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
-In Section~\ref{far-bound}, we'll see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
-Together, these results show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
-Since we set $\sigma < \rho$, this proves Proposition~\ref{prop:get-contraction}.
+In Section~\ref{near-bound}, we will bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by $\tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ on $\near$.
+In Section~\ref{far-bound}, we will see that by making $\Lambda$ big enough, we can bound $|\zeta|^{-(\rho-1)}\,e^{-\Lambda|\zeta|}\,|\volterra\varphi|$ by an arbitrarily small constant multiple of $\|\varphi\|_{\rho-1, \Lambda}$ on $\far$.
+Together, these results will show that $\|\volterra \varphi\|_{\rho-1, \Lambda} \le \tfrac{\sigma}{\rho} \|\varphi\|_{\rho-1, \Lambda}$ when $\Lambda$ is large enough.
+Since we set $\sigma < \rho$, this will prove Proposition~\ref{prop:get-contraction}.
 \subsubsection{Bounds on the perturbed kernel}\label{sec:bounds on k}
@@
 One bound, which works when both arguments of $\kerwhole$ are close to $\zeta = 0$, will be used in Section~\ref{near-bound}.
-\begin{prop}\label{prop:whole-ker-near-bound}
-Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}. Then, for any $\sigma > \tau$, we can ensure that
+\begin{proposition}\label{prop:whole-ker-near-bound}
+Suppose $\hardpart$ satisfies Condition~\eqref{cond:sing}, and $\softpart$ satisfies Condition~\eqref{cond:eps-lambda}.
+Then, for any $\sigma > \tau$, there is a neighborhood $\Sigma \subset \Omega$ of $\zeta = 0$ with the property that
 \[ |\kerwhole(a, a')| \le \frac{\sigma}{|\zeta(a)|} \]
-by keeping $a$ and $a'$ close enough to $\zeta = 0$.
-\end{prop}
+for all $a, a' \in \Sigma$.
+\end{proposition}
 \begin{proof}
-First, choose some $\sigma_0 \in (\tau, \sigma)$. Condition~\eqref{cond:sing} tells us that by making $\delta > 0$ small enough, we can ensure that
+Choose some $\sigma_0 \in (\tau, \sigma)$. From Condition~\eqref{cond:sing}, by making $\delta > 0$ small enough, we can ensure that
 \[ |\hardker(a, a')| \le \frac{\sigma_0}{|\zeta(a)|} \]
 whenever $|\zeta(a)| < \delta$ and $|\zeta(a')| < \delta$.
-Now, we'll show that under Condition~\eqref{cond:eps-lambda}, we can make $|\softker(a, a')|$ as small as we want by keeping $a$ and $a'$ close to $\zeta = 0$.
-The condition tells us that
+
+Condition~\eqref{cond:eps-lambda} implies that
 \[ | \softker(a, a') | \lesssim\frac{|\zeta(a)-\zeta(a')|^\gamma}{|\zeta(a)|}\,e^{\lambda_\Delta|\zeta(a)-\zeta(a')|}\]
@@
 Another bound, which works when the first argument of $\kerwhole$ is kept away from $\zeta = 0$, will be used in Section~\ref{far-bound}.
-\begin{prop}\label{prop:whole-ker-far-bound}
+\begin{proposition}\label{prop:whole-ker-far-bound}
 Suppose $\hardpart$ satisfies {\em Condition~\eqref{cond:diag-basic}}, and $\softpart$ satisfies {\em Condition~\eqref{cond:eps-lambda}}.
-Choose a subset $\far \subset \domain$ that doesn't touch $\zeta = 0$.\footnote{A subset of a topological space {\em touches} the points in its closure~\cite[Chapter~5, Definition~2.11]{joshi1983gen-top}.} Then, for any $\lambda > \lambda_\Delta$, we have
+Choose a subset $\far \subset \domain$ that does not touch $\zeta = 0$.
+Then, for any $\lambda > \lambda_\Delta$, we have
 \[ |\kerwhole(a,a')| \lesssim e^{\lambda |\zeta(a)-\zeta(a')|} \]
 over all $a \in \far$ and $a' \in \domain$.
-\end{prop}
+\end{proposition}
 \begin{proof}
@@
 over all $a \in \far$ and $a' \in \domain$. This simplifies to the desired result.
-\end{proof}.
+\end{proof}
 \subsubsection{First steps toward showing that $\volterra$ is a contraction}\label{first-steps}
 The first steps of our calculation are the same throughout $\domain$. For each $a \in \domain$, we have
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)\,\varphi\;d\zeta| \]
-for any choice of integration path.\footnote{The absolute value of a $1$-form, like $|k(a, \cdot)\,\varphi\;d\zeta|$, is a density on $\C$---a norm on tangent vectors.} The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_0^a |k(a, \cdot)|\,|\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta| \\
-& = \|\varphi\|_{\rho-1, \Lambda}  \int_0^a |k(a, \cdot)|\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|
-\end{align*}
+\begin{revtwo}
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')\,\varphi(a')\;d\zeta(a')| \]
+\end{revtwo}
+for any choice of integration path.
+The norm on $\singexp{\rho-1}{\Lambda}(\domain)$ is designed to give the bound $|\varphi| \le |\zeta|^{\rho-1}\,e^{\Lambda |\zeta|}\,\|\varphi\|_{\rho-1, \Lambda}$, so
+\begin{revtwo}
+\begin{align*}
+&|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \\
+& \qquad \le |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}  \int_{\zeta(a') = 0}^a |k(a, a')|\,|\zeta(a')|^{\rho-1}\,e^{\Lambda |\zeta(a')|}\,\|\varphi\|_{\rho-1, \Lambda}\;|d\zeta(a')| \\
+& \qquad = \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta(a') = 0}^a |k(a, a')|\,\left|\frac{\zeta(a')}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta(a')|)}\;|d\zeta(a')|
+\end{align*}
+\end{revtwo}
 What we do next depends on whether $a$ is in $\near$ or $\far$.
 \subsubsection{Near the origin}\label{near-bound}
-Suppose that $a \in \near$. Then inequality~\eqref{near-limit} tells us that
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le
-\|\varphi\|_{\rho-1, \Lambda}  \int_0^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
-& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_0^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
-\end{align*}
-for any integration path that stays within $\near$. Taking advantage of the fact that $\near$ is a sector of a disk, let's use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
-\begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+Suppose that $a \in \near$. Then inequality~\eqref{near-limit} gives
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le
+\|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \frac{\sigma}{|\zeta(a)|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta| \\
+& \le \sigma \|\varphi\|_{\rho-1, \Lambda}  \int_{\zeta = 0}^a \left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;\left|\frac{d\zeta}{\zeta(a)}\right|
+\end{align*}
+for any integration path that stays within $\near$. Noting that $\near$ is star-shaped by construction, we use the straight path $\zeta = t \zeta(a)$, with $t \in (0, 1]$:
+\begin{align*}
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
 & \le \sigma \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\;dt \\
@@
 Choose some $\lambda > \lambda_\Delta$.
-By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, we can find a constant $M$ for which
-\[ |k(a, \cdot)| \le M e^{\lambda |\zeta(a) - \zeta|} \]
-for all $a \in \far$. Note that only the first argument of $k$ has its domain restricted; this bound holds throughout $\domain$ in the second argument. Applying this bound, we learn that
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le \|\varphi\|_{\rho-1, \Lambda} \int_0^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
+By Proposition~\ref{prop:whole-ker-far-bound} from Section~\ref{sec:bounds on k}, there is some $M\in\R_{>0}$ for which
+\[ |k(a, a')| \le M e^{\lambda |\zeta(a) - \zeta(a')|} \]
+for all $a \in \far$ and $a' \in \Omega$. This bound implies that
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le \|\varphi\|_{\rho-1, \Lambda} \int_{\zeta = 0}^a M e^{\lambda |\zeta(a) - \zeta|}\,\left|\frac{\zeta}{\zeta(a)}\right|^{\rho-1}\,e^{-\Lambda(|\zeta(a)| - |\zeta|)}\;|d\zeta|.
 \]
-Let's again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
+We again use the straight integration path $\zeta = t \zeta(a)$, with $t \in (0, 1]$.
 Along this path, $|\zeta(a) - \zeta| = |\zeta(a)| - |\zeta|$, allowing us to combine the exponential factors in our bound:
 \begin{align*}
-|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
+|\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| & \le \|\varphi\|_{\rho-1, \Lambda} \int_0^1 M e^{\lambda |\zeta(a)|(1 - t)}\,t^{\rho-1}\,e^{-\Lambda |\zeta(a)|(1 - t)}\;dt \\
 & \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)|\zeta(a)|(1 - t)}\;dt.
 \end{align*}
-Let's set $\Lambda > \lambda$, ensuring that the exponential factor shrinks as $|\zeta(a)|$ grows.
-Then we can make our bound uniform over all $a \in \far$, since $|\zeta(a)| \ge \delta$ for these points:
-\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,|[\volterra\varphi](a)| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
+Set $\Lambda > \lambda$, so the exponential factor shrinks as $|\zeta(a)|$ grows. Since $|\zeta(a)| \ge \delta$ for all $a \in \far$, we then have the uniform bound
+\[ |\zeta(a)|^{-(\rho-1)}\,e^{-\Lambda|\zeta(a)|}\,\big|[\volterra\varphi](a)\big| \le M \|\varphi\|_{\rho-1, \Lambda} \int_0^1 t^{\rho-1}\,e^{-(\Lambda - \lambda)\delta(1 - t)}\;dt. \]
+over all $a \in \far$.
 
 We can make this bound less than one, as required to show that $\volterra$ is a contraction, by increasing $\Lambda$.
-To see this in the trickiest case, where $\rho < 1$, it helps to look at the beginning and end of the integration path separately.
-At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we can use a worst-case estimate on the exponential factor:
+To see this in the trickiest case, where $\rho < 1$, consider the beginning and end of the integration path separately.
+At the beginning of the path---for $t \in \big(0, \tfrac{1}{5}\big]$, say---we use a worst-case estimate on the exponential factor:
 \begin{align*}
@@
 \begin{proof}[Proof of Lemma~\ref{lem:perturbed_volterra}]
-Choose $\Lambda$ large enough to ensure that $\volterra$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$ and $g$ belongs to $\singexp{\rho-1}{\Lambda}(\Omega)$.
-Proposition~\ref{prop:get-contraction} guarantees that we can do the former, given our assumptions about $\volterra$ and $\rho$, and the definition of $\singexpalg{\rho-1}(\Omega)$ guarantees that we can also do the latter.
-Our choice of $\Lambda$ ensures that the affine map $f \mapsto \volterra f + g$ is also a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
-
-To see that the fixed point is still unique in the bigger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
+Choose $\Lambda \in \R$ large enough that $\singexp{\rho-1}{\Lambda}(\Omega)$ contains $g$ and is contracted by $\volterra$.
+Proposition~\ref{prop:get-contraction} and Definition~\ref{def:exp-top} guarantee that this is possible.
+The affine map $f \mapsto \volterra f + g$ is a contraction of $\singexp{\rho-1}{\Lambda}(\Omega)$, and thus has a unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ by the contraction mapping theorem.
+
+To see that the fixed point is unique in the larger space $\singexpalg{\rho-1}(\Omega)$, first recall from Proposition~\ref{prop:inclus-ge-exp} that we have inclusions $\singexp{\rho-1}{\Lambda'}(\Omega) \hookrightarrow \singexp{\rho-1}{\Lambda}(\Omega)$ for all $\Lambda' \le \Lambda$.
 Any fixed point in $\singexp{\rho-1}{\Lambda'}(\Omega)$ must map to the unique fixed point in $\singexp{\rho-1}{\Lambda}(\Omega)$ under this inclusion.
@@
 \begin{proof}[Proof of Theorem~\ref{thm:general_volterra}]
-Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}, which satisfies the equation
-\[ \solproto = \hardpart \solproto. \]
+Start with the prototype solution $\solproto$ constructed in Theorem~\ref{thm:basic_volterra}.
 The base point for the construction can be chosen arbitrarily.
-Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} tells us that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$.
+Under our assumptions about $\volterra$, Theorem~\ref{thm:proto-growth} ensures that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$.
 Our goal is to find a perturbation $\solptb \in \singexpalg{\tau-1+\gamma}(\domain)$ that makes $\solwhole = \solproto + \solptb$ a solution of
@@
 \end{align*}
-we can rewrite the homogeneous equation we're trying to solve as an inhomogeneous equation for $\solptb$:
+we rewrite the homogeneous equation we are trying to solve as an inhomogeneous equation for $\solptb$:
 \begin{align}
@@
 \end{align}
-Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} tells us that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
-Since $\tau+\gamma > \tau$, and we've made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-Equivalently, Equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
-
-Now, we just want to show that the uniqueness of the solution still holds in $f_0 + \singexpalg{\rho-1}(\Omega)$ for any $\rho > \tau$.
-
-First, suppose $\rho \in (\tau, \tau+\gamma)$.
-In this case, we can use the inclusion $\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)$ given by Proposition~\ref{prop:inclus-lt-pow-alg} to see that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
-Lemma~\ref{lem:perturbed_volterra} then guarantees that Equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+Since we know that $\solproto$ is in $\singexpalg{\tau-1}(\domain)$, Proposition~\ref{prop:smoothing} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\tau-1+\gamma}(\domain)$.
+Since $\tau+\gamma > \tau$, and we have made all the necessary assumptions about $\volterra$, Lemma~\ref{lem:perturbed_volterra} guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution $\solptb$ in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+Equivalently, equation~\eqref{eqn:orig-homog} has a unique solution $f$ in $f_0 + \singexpalg{\tau-1+\gamma}(\domain)$.
+\end{proof}
+\begin{proof}[Proof of Corollary~\ref{cor:expand_uniq}]
+First, suppose $\rho \in (\tau, \tau+\gamma)$. In this case, the inclusion
+\[\singexpalg{\tau-1+\gamma}(\Omega) \hookrightarrow \singexpalg{\rho-1}(\Omega)\]
+given by Proposition~\ref{prop:inclus-lt-pow-alg} shows that the inhomogeneous term $\softpart\solproto$ is in $\singexpalg{\rho-1}(\Omega)$.
+Lemma~\ref{lem:perturbed_volterra} then guarantees that equation~\eqref{eqn:equiv-inhomog} has a unique solution in $\singexpalg{\rho-1}(\Omega)$---which must be the solution we already found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
 
@@
 In this case, Proposition~\ref{prop:inclus-lt-pow-alg} gives an inclusion $\singexpalg{\rho-1}(\Omega) \hookrightarrow \singexpalg{\tau-1+\gamma}(\Omega)$.
-Under this inclusion, any solution of Equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
-\end{proof}
-\begin{prop}\label{prop:alt-general_volterra}
-Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other conditions we assume in {\em Theorem~\ref{thm:general_volterra}}.
-Then, as long as $\rho > \tau$ is low enough, the equation
+Under this inclusion, any solution of equation~\eqref{eqn:equiv-inhomog} that we might find in $\singexpalg{\rho-1}(\Omega)$ must match the unique solution we found in $\singexpalg{\tau-1+\gamma}(\Omega)$.
+\end{proof}
+\begin{proposition}\label{prop:alt-general_volterra}
+Suppose $\volterra$ satisfies {\em Condition~\eqref{cond:reg-p}} in addition to the other assumptions of {\em Theorem~\ref{thm:general_volterra}}.
+Then, for each $\rho \in (\tau,\;\tau + \min\{\gamma, \epsilon, 1\}]$, the equation
 \[f = \volterra f\]
@@
 \[ \zeta^{\tau-1}+\singexpalg{\rho-1}(\domain) \]
-of the space $\singexpalg{\tau-1}(\domain)$. To be precise, $\rho$ is low enough when it's in the interval
-\[ (\tau, \tau + \min\{\gamma, \epsilon, 1\}]. \]
-\end{prop}
-
+of the space $\singexpalg{\tau-1}(\domain)$.
+\end{proposition}
 \begin{proof}
@@
 \subsection{Overview}
-We can use our understanding of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
-In particular, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
+We can use our analysis of regular singular Volterra equations to study so-called \textit{level~1 differential equations}, which each have an irregular singularity at $\infty$.
+Under certain conditions, we can build a set of analytic solutions in the frequency domain by solving certain regular singular Volterra equations in the position domain.
 Our main results guarantee that these position domain solutions exist, are unique, and have well-defined Laplace transforms.
@@
 Equations of the form $\mathcal{P}\Phi = 0$ are a sub-class of what Ecalle calls {\em level~1} differential equations~\cite[Section~2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-In an upcoming paper \cite{borel_reg}, we'll study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
+In~\cite{borel_reg}, we study various examples of such equations using Laplace transform methods, with the help of our existence and uniqueness result Theorem~\ref{thm:general_volterra}.
 \subsection{Notation}\label{sec:notation_alpha}
-So far, we've studied a Volterra equation with a regular singularity at $\zeta = 0$.
-When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we'll end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
-
-To adapt our previous reasoning to this more general situation, we'll reinterpret the language of Sections \ref{sec:intro}--\ref{sec:proof_main_results} whenever we refer to it Section~\ref{sec:example}.
-The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will now be played by $\zeta-\alpha$.
+So far, we have studied a Volterra equation with a regular singularity at $\zeta = 0$.
+When we use Laplace transform methods to solve a level~1 differential equation $\mathcal{P}\Phi = 0$ in the frequency domain, we will end up with several Volterra equations $\hat{\mathcal{P}}_\alpha \varphi = 0$ in the position domain, each with a regular singularity at a different root $\zeta = \alpha$ of the polynomial $P(-\zeta)$.
+
+To use our previous reasoning in this more general setting, we must reinterpret its language.
+The role of the coordinate $\zeta$ in Sections \ref{sec:intro}--\ref{sec:proof_main_results} will be played by $\zeta-\alpha$ in Section~\ref{sec:example}.
 This substitution leads to several other reinterpretations, summarized below.
 
-References to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, which we'll rewrite as $\zeta=\alpha$.
-For example, we'll now work on a domain that touches but doesn't contain $\zeta = \alpha$, introducing the notation $\domain_\alpha$ as a reminder of this change.
+References to the point $\zeta=0$ become references to the point $\zeta-\alpha=0$, which we will rewrite as $\zeta=\alpha$.
+For example, we will now work on a domain that touches but does not contain $\zeta = \alpha$, introducing the notation $\domain_\alpha$ as a reminder of this change.
 Condition~\eqref{cond:star} now says that $\domain_\alpha$ is star-shaped around $\zeta = \alpha$.
@@
 \subsection{The Laplace transform}
-\subsubsection{Definition}
-Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but doesn't contain $\zeta=\alpha$, and let $\Gamma_{\zeta, \alpha}^\theta$ be the ray that leaves $\zeta=\alpha$ at angle $\theta$.
-When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, we can define the Laplace transform $\laplace_{\zeta, \alpha}^{\theta}$, which maps functions in $\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$ and $\Lambda\in\R$ to holomorphic functions on the half-plane $\Re(z e^{-i\theta}) > \Lambda$ in the frequency domain~\cite[Section 5.6]{diverg-resurg-i}.
-The Laplace transform of $\varphi$ is defined by the formula
+\subsubsection{Definition}\label{sec:definition_Laplace}
+Let $\domain_\alpha$ be a simply connected open subset of $\C$ that touches but does not contain $\zeta=\alpha$.
+Let $\Gamma_{\zeta, \alpha}^\theta$ be the ray in the position domain that leaves $\zeta=\alpha$ at angle $\theta$, and let $\Pi^{-\theta}_\Lambda$ be the half-plane $\Re(z e^{i\theta}) > \Lambda$ in the frequency domain.
+When $\domain_\alpha$ contains $\Gamma_{\zeta, \alpha}^\theta$, the Laplace transform
+\[ \laplace_{\zeta, \alpha}^{\theta} \maps \singexp{\sigma}{\Lambda}(\domain_\alpha) \to \holo(\Pi^{-\theta}_\Lambda) \]
+is defined for all $\sigma > -1$ and $\Lambda \in \R$. Its action on a function $\varphi$ is given by the formula
 \begin{equation}\label{laplace:int}
@@
 \end{equation}
-It's a function on the frequency domain because it depends on the frequency variable $z$.
+
 \subsubsection{Action on integral operators}\label{sec:L-int-op}
@@
 \[ [\partial^{-\nu}_{\zeta, \alpha} \varphi](a) := \frac{1}{\Gamma(\nu)} \int_{\zeta = \alpha}^a \big(\zeta(a)-\zeta\big)^{\nu-1} \varphi\;d\zeta \]
-for each $a \in \domain_\alpha$. It obeys the expected semigroup law \cite[Section~1.3]{mladenov2014advanced}
+for each $a \in \domain_\alpha$. It obeys the semigroup law \cite[Section~1.3]{mladenov2014advanced}
 \begin{align*}
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \cite[Equation~35]{mladenov2014advanced}.
+and agrees with ordinary repeated integration when $\nu$ is an integer \cite[equation~35]{mladenov2014advanced}.
 
 Fractional integration has a smoothing effect: it reduces the sharpness of any power-law singularity at $\zeta = \alpha$.
-\begin{prop}\label{prop:frac-int-smoothing}
+\begin{proposition}\label{prop:frac-int-smoothing}
 For each $\nu \in (0, \infty)$, the fractional integral $\fracderiv{-\nu}{\zeta}{\alpha}$ maps
@@
 for all $\nu \in (0, \infty)$ and $\varphi\in\singexp{\sigma}{\Lambda}(\domain_\alpha)$ with $\sigma>-1$.
-This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, you can use differentiation under the integral to show that~\cite[Theorem~1.34]{laplace-tfm}
+This mirrors the Laplace transform's action on multiplication operators: under the same conditions on $\varphi$, differentiation under the integral shows that~\cite[Theorem~1.34]{laplace-tfm}
 \[ \laplace_{\zeta,\alpha}^\theta (\zeta^n \varphi) = \big({-\tfrac{\partial}{\partial z}}\big)^n \laplace_{\zeta,\alpha}^\theta \varphi \]
@@
 \subsection{Going to the position domain}
-Using the properties of the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$ we can turn differential operators in the frequency domain into Volterra operators in the position domain. 
+Under the Laplace transform $\laplace_{\zeta,\alpha}^{\theta}$, differential operators on the frequency domain pull back to integral operators on the position domain.
 \begin{lemma}\label{lem:use-dict}
-For each root $-\alpha$ of $P$, let $\hat{\mathcal{P}}_{\alpha}$ be the Volterra operator 
+For any $\alpha \in \C$, let $\hat{\mathcal{P}}_{\alpha}$ be the integral operator 
 \[ \hat{\mathcal{P}}_\alpha:=P(-\zeta)+\partial_{\zeta,\alpha}^{-1}\circ Q(-\zeta)+\partial_{\zeta,\alpha}^{-2}\circ R(\partial_{\zeta,\alpha}^{-1}). \]
@@
 \end{lemma}
-
 \begin{rmk}
-For the Laplace transform to have any hope of being well-defined, we have to choose the direction $\theta$ so that the ray $\Gamma_{\zeta, \alpha}^\theta$ stays within $\domain_\alpha$.
-We'll see later that for our results to apply, $\domain_\alpha$ can't touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
+For the Laplace transform to be well-defined, $\domain_\alpha$ must contain the ray $\Gamma_{\zeta, \alpha}^\theta$ as a necessary condition.
+We will see later that for our results to apply, $\domain_\alpha$ also cannot touch any zero of $P(-\zeta)$ other than $\zeta = \alpha$.
 As a result, $\domain_\alpha$ might look like the domain illustrated in Section \ref{setting:domain}, reinterpreting the origin as $\zeta = \alpha$.
 \end{rmk}
+\begin{rmk}\label{rmk:use-dict-explicit}
+To write $\hat{\mathcal{P}}_\alpha$ more explicitly, let $p := P(-\zeta)$ and $q := Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$. Then
+\begin{revtwo}
+\[ \big[\hat{\mathcal{P}}_\alpha\varphi\big](a) = \big[ p\, \varphi \big](a) + \int_{\zeta(a')=\alpha}^a q(a') \, \varphi(a') \; d\zeta(a') + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a'), \]
+\end{revtwo}
+where
+\[ k_R(a,a') := \sum_{j=0}^\infty \frac{R_{j}}{(j+1)!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\end{rmk}
 \begin{proof}[Proof of Lemma~\ref{lem:use-dict}]
-Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we can work out that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
+Comparing the definitions of $\mathcal{P}$ and $\hat{\mathcal{P}}_\alpha$, and using the properties of the Laplace transform discussed in Section~\ref{sec:L-int-op}, we find that $\mathcal{P} \laplace_{\zeta,\alpha}^\theta = \laplace_{\zeta,\alpha}^\theta \hat{\mathcal{P}}_\alpha$.
 Hence,
@@
 We can now state and prove the main result of this section.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and doesn't touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
-We'll show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
+Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$ and does not touch any other roots of $P(-\zeta)$, as illustrated in Section~\ref{setting:domain} under the reinterpretation from Section \ref{sec:notation_alpha}.
+We will show that the Volterra equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution of a certain form on $\domain_\alpha$.
 By Lemma~\ref{lem:use-dict}, the Laplace transform of this solution satisfies the equation $\mathcal{P}\Phi = 0$.
-\begin{thm}\label{thm:example}
-Consider a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-Choose a simply connected open set $\domain_\alpha$ that touches $\zeta = \alpha$, and doesn't touch any other root of $P(-\zeta)$.
-Then the equation
+\begin{theorem}\label{thm:example}
+Suppose $P$ has a root $-\alpha$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive. Choose a simply connected open set $\domain_\alpha$ that touches
+$\zeta = \alpha$, and does not touch any other root of $P(-\zeta)$. Then the equation
 \[ \hat{\mathcal{P}}_\alpha \psi_\alpha = 0 \]
@@
 of the space $\singexpalg{\tau_\alpha-1}(\domain_\alpha)$.
-\end{thm}
-\begin{proof}[Proof of Theorem~\ref{thm:example}]
-Choose a root $-\alpha$ of $P$ where $\tau_\alpha := Q(-\alpha)/P'(-\alpha)$ is real and positive.
-For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$, noting that $\zeta = \alpha$ is a root of $p$.
-The conditions laid out in Section~\ref{sec:level 1 ODE} guarantee that $\frac{\partial}{\partial \zeta} p$ and $q$ are both non-zero $\zeta = \alpha$.
-
-To apply Proposition~\ref{prop:alt-general_volterra}, we need to rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
-When we write $\hat{\mathcal{P}}_\alpha$ explicitly as a Volterra operator, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
-\[ \big[ p\, \varphi \big](a) + \int_{\zeta=\alpha}^a q \, \varphi \; d\zeta + \int_{\zeta=\alpha}^a k_R(a,\cdot) \, \varphi \, d\zeta = 0, \]
-where
-\[ k_R(a,a')=\sum_{j=0}^\infty \frac{R_{j}}{j!} \, \big(\zeta(a)-\zeta(a')\big)^{j+1} . \]
+\end{theorem}
+\begin{proof}
+To apply Proposition~\ref{prop:alt-general_volterra}, we must rewrite the equation $\hat{\mathcal{P}}_{\alpha}\varphi = 0$ in the form $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha$ is a Volterra operator of the kind described in Section~\ref{setting} under the reinterpretation from Section~\ref{sec:notation_alpha}.
+When $\hat{\mathcal{P}}_\alpha$ is written as in Remark~\ref{rmk:use-dict-explicit}, the equation $\hat{\mathcal{P}}_{\alpha} \varphi = 0$ becomes
+\begin{revtwo}
+\[ \big[ p\, \varphi \big](a) + \int_{\zeta(a')=\alpha}^a q(a') \, \varphi(a') \; d\zeta(a') + \int_{\zeta(a')=\alpha}^a k_R(a, a') \, \varphi(a') \, d\zeta(a') = 0. \]
+\end{revtwo}
 Isolating $p\,\varphi$ on the left and dividing both sides by $p$ yields the equivalent equation
+\begin{revtwo}
 \begin{equation}\label{eqn:divided}
-\varphi(a) = -\int_{\zeta=\alpha}^a \frac{q}{p(a)} \, \varphi \; d\zeta - \int_{\zeta=\alpha}^a \frac{k_R(a,\cdot)}{p(a)} \, \varphi \, d\zeta.
+\varphi(a) = -\int_{\zeta(a')=\alpha}^a \frac{q(a')}{p(a)} \, \varphi(a') \; d\zeta(a') - \int_{\zeta(a')=\alpha}^a \frac{k_R(a, a')}{p(a)} \, \varphi(a') \, d\zeta(a').
 \end{equation}
+\end{revtwo}
 Let $\hardpart^\alpha$ be the Volterra operator with kernel
@@
 \[ \softker^\alpha(a,a') = -\frac{k_R(a,a')}{p(a)}. \]
-Now we can write Equation~\eqref{eqn:divided} as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
+Equation~\eqref{eqn:divided} can be written as $\varphi = \volterra^\alpha \varphi$, where $\volterra^\alpha = \hardpart^\alpha + \softpart^\alpha$.
 
 The kernel of $\volterra^\alpha$ extends meromorphically over all of $\C^2$.
-One part of this observation demands some explanation: we need to confirm that the power series defining $k_R$ converges everywhere.
-To do this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
-Consequently, for any $\lambda > A$, we have $|R_{j}| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
-This is enough to show that $k_R$ is well-defined throughout $\C^2$.
-As we'll see later, it also leads to a useful bound on $k_R$.
+To see this, recall that $R(z^{-1})$ is holomorphic on the disk $|z| > A$.
+It follows that for any $\lambda > A$, we have $|R_j| \lesssim \lambda^j$ over all $j \in \{0, 1, 2, \ldots\}$.
+The power series defining $k_R$ therefore converges everywhere.
 \begin{verify}
@@
 
-Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we're now working in the setting of Proposition~\ref{prop:alt-general_volterra}.
-To apply the theorem, we just need to show that $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
+Since $\hardpart^\alpha$ has a separable kernel of the form described in Section~\ref{setting:basic}, we can apply Proposition~\ref{prop:alt-general_volterra} as long as $\hardpart^\alpha$ and $\softpart^\alpha$ satisfy the required conditions from Section~\ref{setting}.
 \begin{itemize}
@@
 \end{align*}
-Now we expand $Q$ around $-\alpha$, using the decomposition $Q(\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(\zeta)$ to split up the last term of the expression above:
-\begin{equation}\label{eqn:split-numerator}
--\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
-\end{equation}
-First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. Equation~\eqref{eqn:split-numerator} tells us that
+Now we expand $Q$ around $-\alpha$, using the decomposition
+\[ Q(-\zeta) = Q(-\alpha)+(\zeta-\alpha)\,Q_\alpha(-\zeta) \]
+to split up the last term of the expression above:
+\begin{multline}\label{eqn:split-numerator}
+-\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)} = \\
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)} + \frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)} + \frac{Q(-\alpha)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}.
+\end{multline}
+First, we want to show that $-q/p-\tau_\alpha/(\zeta-\alpha)$ is bounded on a neighborhood of $\zeta = \alpha$ in $\domain_\alpha$. It follows from equation~\eqref{eqn:split-numerator} that
 \begin{align*}
 -\frac{Q(-\zeta)}{P(-\zeta)} & =
-\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
-&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}
+\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{(\zeta - \alpha)\,Q_\alpha(-\zeta)}{P'(-\alpha)\,(\zeta - \alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)} \\
+&=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)} + \frac{Q(-\alpha)}{P'(-\alpha)\,(\zeta - \alpha)}\,.
 \end{align*}
 Recalling that $\tau_\alpha = Q(-\alpha)/P'(-\alpha)$, we conclude that
-\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(\zeta)}{P'(-\alpha)}\]
+\[-\frac{Q(-\zeta)}{P(-\zeta)}-\frac{\tau_\alpha}{\zeta-\alpha}=\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \frac{Q(-\zeta)}{P'(-\beta)\,(\zeta - \beta)} + \frac{Q_\alpha(-\zeta)}{P'(-\alpha)}\,.
+\]
 Since $Q$ and $Q_\alpha$ are polynomials, the right-hand side is bounded on any neighborhood of $\zeta = \alpha$ that avoids the other roots of $p$ and avoids infinity.
@@
 holds when $a$ and $a'$ are close enough to $\zeta = \alpha$.
-Taking the absolute value of both sides of Equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
-\begin{align*}
-\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
-|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha.
+Taking the absolute value of both sides of equation~\eqref{eqn:split-numerator}, and using the assumption that $\tau_\alpha$ is real and positive, we see that
+\begin{align*}
+\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\ & \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{(\zeta(a') - \alpha)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)\,\big(\zeta(a) - \alpha\big)}\right| + \left|\frac{\tau_\alpha}{\zeta(a) - \alpha}\right| \\
+|\zeta(a) - \alpha|\left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| & \le \\
+& \hspace{-15mm} \sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right| + \left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right| + \tau_\alpha\,.
 \end{align*}
 By bringing $\zeta(a')$ closer to $\alpha$, we can make the middle term
-\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(\zeta(a')\big)}{P'(-\alpha)}\right|\]
-as small as we want. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
+\[\left|\frac{\big(\zeta(a') - \alpha\big)\,Q_\alpha\big(-\zeta(a')\big)}{P'(-\alpha)}\right|\]
+arbitrarily small. Similarly, by bringing $\zeta(a)$ closer to $\alpha$, we can make the sum
 \[\sum_{\substack{-\beta \in \roots \\ \beta \neq \alpha}} \left|\frac{Q\big(-\zeta(a')\big)\,\big(\zeta(a) - \alpha\big)}{P'(-\beta)\,\big(\zeta(a) - \beta\big)}\right|\]
-as small as we want. Hence, for any $\sigma > \tau_\alpha$, the bound
+arbitrarily small. Hence, for any $\sigma > \tau_\alpha$, the bound
 \[|\zeta(a)-\alpha| \, \left|\frac{Q\big(-\zeta(a')\big)}{P\big(-\zeta(a)\big)}\right| \le \sigma \]
@@
 
-\bibliographystyle{utphys}
-\bibliography{reg-sing-volterra}
+\bibliographystyle{siamplain}
+\bibliography{reg-sing-volterra.bib}
 \end{document}

### 2025-01-28 reg-sing-volterra.tex
Adjust theorem numbering to match published version

@@
 
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{proposition}[theorem]{Proposition}
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}
-\newtheorem{rmk}{Remark}
-\theoremstyle{plain}
-\newtheorem{proposition}{Proposition}
-\newtheorem{lemma}{Lemma}
-\newtheorem{theorem}{Theorem}
-\newtheorem{corollary}{Corollary}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{rmk}[theorem]{Remark}
 
@@
 \subsubsection{Uniform bounds}
-Given a complex-valued function $\varphi$ and a non-negative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
+Given a complex-valued function $\varphi$ and a nonnegative, real-valued function $\omega$, we will write $|\varphi| \lesssim \omega$ to say that $|\varphi|$ is bounded by a constant multiple of $\omega$.
 Unless we say otherwise, the bound holds throughout the domain where both functions are defined.
@@
 
-Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$, and satisfies the following condition.
+Take a simply connected open set $\domain \subset \C$ that touches but does not contain $\zeta = 0$ and that satisfies the following condition.
 \begin{conditions}
@@
 \condconst{reg-p}{B, \epsilon}\label{cond:reg-p}
-For some non-zero constant $B$ and some $\epsilon > 0$,
+For some nonzero constant $B$ and some $\epsilon > 0$,
 \[ p \in B\zeta + O\big(|\zeta|^{1 + \epsilon}\big) \]
@@
 \[ [\softpart\,\varphi](a) := \int_{\zeta(a') = 0}^a \softker(a, a')\,\varphi(a')\;d\zeta(a') \]
-will be non-separable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
+will be nonseparable,\end{revtwo}\footnote{Unless $\softpart$ is zero, of course.} but it will have a regularizing effect, as we will show in Proposition \ref{prop:smoothing}.
 To get the smoothing effect, we will require \revtwotext{the kernel $\softker$} to vanish to some order $\gamma > 0$ on the diagonal in $\domain^2$.
@@
 We will also put an exponential bound on the growth of $\softker$ away from the diagonal, mimicking Condition~\eqref{cond:diag-basic} on $\hardker$.
-Altogether, we will require:
+Altogether, we will require the following:
 \begin{conditions}
@@
 \end{equation}
-Changing the base point $b \in \domain$ only multiplies $f_0$ by a non-zero constant.
+Changing the base point $b \in \domain$ only multiplies $f_0$ by a nonzero constant.
 \end{theorem}
@@
 We will reduce Theorem~\ref{thm:general_volterra} to Lemma~\ref{lem:perturbed_volterra} in Section~\ref{sec:existence and uniqueness}, by rewriting the homogeneous equation $f = \volterra f$ in the subspace $f_0 + \singexpalg{\tau-1+\gamma}(\Omega)$ as an inhomogeneous equation in a more regular space.
-To show that the inhomogeneous term, $\softpart f_0$, is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to prove that $\softpart$ improves on the regularity ascribed by Theorem~\ref{thm:proto-growth} to the prototype solution $f_0$.
+To show that the inhomogeneous term $\softpart f_0$ is regular enough, we will use Proposition~\ref{prop:smoothing} from Section~\ref{sec:image under soft_part} to prove that $\softpart$ improves on the regularity ascribed by Theorem~\ref{thm:proto-growth} to the prototype solution $f_0$.
 \begin{rmk}
@@
 \end{center}
-automatically commute, because as non-topological linear maps they are all inclusions between subspaces of $\holo(\domain)$.
+automatically commute, because as nontopological linear maps they are all inclusions between subspaces of $\holo(\domain)$.
 The existence of the desired continuous inclusion $\singexpalg{\sigma'}(\Omega)\hookrightarrow \singexpalg{\sigma}(\Omega)$ then follows from the universal property of the limit topology.
@@
 \[ \chi(a) = \left(\frac{\zeta(a)}{\zeta(b)}\right)^\tau \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau}{\zeta} \right)\;d\zeta\right]. \]
-Recalling that a change of base point just multiplies $\solproto$ by a non-zero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
+Recalling that a change of base point just multiplies $\solproto$ by a nonzero constant, choose the base point $b \in \Omega$ so that $|\zeta(b)| = \delta/2$.
 The exponential factor in the formula above is then bounded between $\exp\big({-\tfrac{3}{2}C\delta}\big)$ and $\exp\big(\tfrac{3}{2}C\delta\big)$ whenever $|\zeta(a)| < \delta$.
@@
 \begin{proposition}\label{prop:better-proto-estimate}
-Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then there is some $M\in\C$ for which,
+Suppose $\hardpart$ satisfies {\em Conditions~\eqref{cond:reg-p}} and \eqref{cond:sing}. Then there is some $M\in\C$ for which
 \[ \solproto \in M\zeta^{\tau-1} + O(|\zeta|^{\tau-1+\epsilon'}) \]
@@
 \item[$\bullet$] $P$ is a monic degree-$d$ polynomial whose roots are all simple; 
-\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$;
+\item[$\bullet$] $Q$ is a degree-$(d-1)$ polynomial that is nonzero at every root of $P$;
 \item[$\bullet$] $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$. In particular, the power series
@@
 \end{align*}
-and agrees with ordinary repeated integration when $\nu$ is an integer \cite[equation~35]{mladenov2014advanced}.
+and agrees with ordinary repeated integration when $\nu$ is an integer \cite[equation~(35)]{mladenov2014advanced}.
 

### 2025-08-27 SIGMA/borel-regularity-SIGMA.tex
Start correcting the triangular cantilever example

--- 2025-01-03 borel-regularity.tex
@@
 \ifhighlightrevs
-\newenvironment{revised}{\color{DarkBlue}}{\color{black}}
+\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
 \else
@@
 
-The particular classes of problems we look at are level~1 ODEs and exponential period integrals over one dimensional Lefschetz thimbles.
+The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over \begin{revised}one-dimensional\end{revised} Lefschetz thimbles.
 To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
@@
 \end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.
-Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{\begin{revised} Trans-mononials can be of different kind, for example fractional powers of $z$ can appear at the exponent.
+In this paper we will only deal with trans-monomial of the form $e^{-\alpha z}$, for some $\alpha\in\C$.\end{revised}} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
 \begin{equation}
@@
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the transmonomial~\eqref{series:bessel_ex}, up to a constant.
+using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$.
+Na\"{i}vely integrating term by term, you again get the \begin{revised}trans-monomial\end{revised}~\eqref{series:bessel_ex}, up to a constant.
 
@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighbourhood of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$.
+\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$.
+Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$\begin{revised},\end{revised} the continuation of $d\zeta$.
 \item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
@@
 
-If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal; this can be deduced from the triangle inequality.
-The power series which is asymptotic to a given function on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
+\begin{revised}If a function is asymptotic to two power series of the form \eqref{series:asymp-definition}, those series must be equal;\end{revised}
+\begin{old}If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal;\end{old} this can be deduced from the triangle inequality.
+The power series which \begin{old}is asymptotic to\end{old} a given function \begin{revised}is asymptotic to\end{revised} on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
@@
 \begin{enumerate}[start=4]
-\item By construction, $\aexp^\theta \hat{\Phi} = \series{\Phi}$.
+\item By construction, $\begin{revised}\aexp^{-\theta}\end{revised} \hat{\Phi} = \series{\Phi}$.
 It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^\theta", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\begin{revised}\aexp^{-\theta}\end{revised}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 
-You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution.
+You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is \begin{revised}the asymptotic expansion of\end{revised} an actual solution.
 After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them.
 In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
-The question of how that happens is the starting point for this paper.
+\begin{revised}Borel recognized this phenomenon as a key motivation for the study of divergent series \cite{borel-memoire,borel-lecons}, and much has been said about it since (Section~\ref{sec:historical-context});\end{revised} \begin{revised}the\end{revised} question of how \begin{revised}it\end{revised} happens is the starting point for this paper.
 %
@@
 Suppose we have a holomorphic function $\Phi$ which is a solution of some problem.
-If the asymptotic expansion $\series{\Phi} = \ae^\theta \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
+If the asymptotic expansion $\series{\Phi} = \ae^{-\theta} \Phi$ is well-defined, it should be a formal solution of the same problem; we can take this as a basic requirement for our concept of a formal solution.
 \begin{center}
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\begin{revised}-\end{revised}\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\aexp^{\begin{revised}-\end{revised}\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
 & & \\
@@
 \begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
+\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.\footnote{\begin{revised}The choice of $-\theta$ in the asymptotic expansion is dictated by our convention for the Laplace transform that we decide to take in direction $\theta$, like we do in step $4.$.
+As explained in Section~2.1, the sign of the angle $\theta$ should be consistent between the asymptotic expansion and the Laplace transform.\end{revised}}
 \item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface with a distinguished $1$-form, as before.
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface \begin{revised}$B$\end{revised} with a distinguished $1$-form, as before.
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
@@
 \begin{enumerate}
-\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-equation~\eqref{eqn:bessel_rescaled_ex} is an example.
+\item Solving a level~$1$\footnote{\begin{revised}The level of linear ODE at a singular point is defined by looking at the Newton polygon associated to the equation, and it corresponds to its positive slope~\cite[Proposition~3.3.14]{diverg-resurg--ii} \end{revised}} linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
+Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
@@
 \end{equation*}
-where $X$ is $1$-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}.
+where $X$ is one-dimensional complex manifold; $f \maps X \to \C$ is a holomorphic function with isolated, non-degenerate critical points; $\nu \in \Omega^1(X)$ is holomorphic $1$-form on $X$, and $\mathcal{C}$ is {\em Lefschetz thimble}---a type of contour described in Section~\ref{sec:why_borel_thimble}.
 Under these conditions, $I$ is a holomorphic function of $z$.
@@
 Our first goal is to discuss Borel summability in a way that carefully separates the analytic and formal sides of the theory.
-In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~1 ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.
+In particular, we highlight results that can be proven in purely analytic ways, like Theorem~\ref{thm:exist_uniq_ODE} for level~$1$ ODEs and Lemma~\ref{lem:thimble_proj_formula} for thimble integrals.
 
@@
 Our third goal is to illustrate the results we discuss with detailed examples involving a diversity of Borel regular functions.
-We treat several examples both as thimble integrals and as solutions of level~1 ODEs, so you can compare these parallel explanations of how Borel regularity arises.
+We treat several examples both as thimble integrals and as solutions of level~$1$ ODEs, so you can compare these parallel explanations of how Borel regularity arises.
 We include ODEs of both second degree and higher degree.
@@
 We state our main results in Sections~\ref{sec:why_borel_ODE}--\ref{sec:why_borel_thimble} and prove them in Section~\ref{sec:proof_main_results}.
-Our examples are in Section~\ref{sec:examples}.
+Our examples are given in Section~\ref{sec:examples}.
 Section~\ref{sec:org} describes the layout of the paper in more detail.
@@
 %
-Consider a linear level-$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}.
+Consider a linear level~$1$ differential operator $\mathcal{P}$ of the form described in~Section~\ref{borel-reg:explanatory-power}.
 This operator will always have an irregular singularity at $z = \infty$.
@@
 We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
-However, this only works when there is a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
+However, this only works when there is a coincidence between \begin{revised}the\end{revised} exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
 Why?
 
-A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function on $\phi$ the position domain.
+A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function \begin{revised} $\phi$ on\end{revised} the position domain.
 In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.
 
-Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}.
+Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~\begin{revised}4.6\end{revised}]{reg-sing-volterra}.
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
@@
 
-From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
+From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the \begin{revised}Ansatz\end{revised} that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
 On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that their Borel transforms converge, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
@@
 \begin{enumerate}
-\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \begin{revised}\aexp^{-\theta}\end{revised} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
@@
 
-Each of our examples focuses on either a level~1 ODE whose solutions can be expressed as thimble integrals or a thimble integral that satisfies a level~1 ODE.
+Each of our examples focuses on either a level~$1$ ODE whose solutions can be expressed as thimble integrals or a thimble integral that satisfies a level~$1$ ODE.
 This provides an opportunity to compare different explanations for why each example function is Borel regular.
@@
 Resurgent analysis is an effective tool for computing ``subleading contributions'' in perturbation theory, and it occasionally leads to the resummation of the original divergent series.
-It has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about non-linear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
+It has been applied extensively to linear ODEs \cite{loday1994stokes,diverg-resurg--ii}, and it has yielded results about nonlinear ODEs as well~\cite{costin-PI,costin_kruskal,diverg-resurg-iii,schiappa-PI}.
 
@@
 
-We thank Fondation Mathematique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
 
@@
 When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over a constant-radius neighbourhood of the ray $\zeta \in e^{i\theta}[0, \infty)$.
+In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over \begin{revised}any\end{revised} constant-radius \begin{revised}neighborhood\end{revised} of the ray $\zeta \in e^{i\theta}[0, \infty)$.
 \begin{center}
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from from direction to the next.
+Analytic solutions of a linear ODE with an irregular singularity\begin{revised}, say at $\infty$,\end{revised} exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from direction to the next.
 Formally, this behaviour is captured in a {\em formal integral} solution: an expression
@@
 The Poincar\'{e} solutions and the M.A.E.T.
-have inspired several other methods for solving linear level~1 ODEs.
+have inspired several other methods for solving linear level~$1$ ODEs.
 The ones we will discuss in this section are summarized in the following table.
@@
 & \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency} &  & Poincar\'{e}: trans-monomial ansatz~\cite{int-irreg} \\ \hline
+\textbf{Frequency} &  & Poincar\'{e}: trans-monomial \begin{revised}Ansatz\end{revised}~\cite{int-irreg} \\ \hline
 \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
@@
 This has motivated the development of summability methods, which promote formal solutions to analytic ones~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-These methods can be applied both within and beyond the world of linear level~1 ODEs.
+These methods can be applied both within and beyond the world of linear level~$1$ ODEs\begin{revised}, including nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}\end{revised}.
 %
@@
 \'{E}calle proved this by using formal perturbation theory to solve a corresponding integral equation in the position domain.
-Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the pertrubation series would converge to an endlessly analytically continuable function.
+Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the \begin{revised}perturbation\end{revised} series would converge to an endlessly analytically continuable function.
 Loday-Richaud and Remy went on to show that this function always has a well-defined Laplace transform, so the corresponding formal solution in the frequency domain is Borel summable~\cite{loday-Remy2011}.
 Malgrange got similar results by working with differential equations, rather than integral equations, on the position domain~\cite{malgrange--fourier}.
+
+\begin{revised}\'{E}calle's theory not only shed light on Borel summation, but also generalized it.
+\'{E}calle introduced generalized resummation methods that use ``well-behaved averages'' to handle infinite sequences of singularities along the summation axis~\cite{EcalleI,Écalle-dulac,menous-mould,menous_phdthesis}.\end{revised}
 %
@@
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, given an ODE, we can set up a Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
+In particular, given an ODE, we can set up a \begin{revised}classical\end{revised} Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
 
@@
 In many cases, the solutions of Riemann--Hilbert problems can be found explicitly~\cite{Dubrovin-tt_star,Dubrovin-Heun,GMN1,Tom-RH-1,Tom-RH-conifold,BBS-RH}.
-These cases include some Riemann--Hilbert problems arising from level~1 ODEs.
+These cases include some Riemann--Hilbert problems arising from level~$1$ ODEs.
 For example, in Section~6.2.1 of \cite{kontsevich2022analyticity}, Kontsevich and Soibelman discuss a Riemann--Hilbert problem for thimble integrals using the formalism of analytic wall-crossing structures.
@@
 \subsubsection{Thimble integrals in physics}
-In wave optics, a thimble integral can arise when we adds up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
+In wave optics, a thimble integral can arise when we \begin{revised}add\end{revised} up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
 For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\cite{rainbows+glories}.
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the so called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
+Indeed, the \begin{revised}so-called\end{revised} wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}.
@@
 Like solutions of level~$1$ ODEs, thimble integrals often exhibit the Stokes phenomenon.
-For one dimensional thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
+For \begin{revised}one-dimensional\end{revised} thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
 More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent development~\cite{kontsevich2024holomorphic}).
@@
 \end{equation}
-where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighbourhood of $\zeta=\alpha$.
+where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a \begin{revised}neighborhood\end{revised} of $\zeta=\alpha$.
 
@@
 
-If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighbourhood of $\zeta = 0$.
+If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a \begin{revised}neighborhood\end{revised} of $\zeta = 0$.
 The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
@@
 To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
-On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighbourhood of $\zeta = 0$ in $\C$.
+On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$ in $\C$.
 Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
@@
 is bounded.
-A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighbourhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
+A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
 This operator is bounded, so its kernel is closed.
@@
 \subsection{Borel regularity for ODEs}\label{borel_reg-ODE}
-In Section~\ref{sec:regularity-results}, we show that linear level~1 ODEs of a certain form always have Borel regular solutions, indexed by the characteristic roots of their constant-coefficient parts.
+In Section~\ref{sec:regularity-results}, we show that linear level~$1$ ODEs of a certain form always have Borel regular solutions, indexed by the characteristic roots of their constant-coefficient parts.
 These solutions turn out to be asymptotic to the formal series solutions found by Poincar\'{e}.
@@
 and define the constant $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.
-From Lemma~2 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
+From Lemma~\begin{revised}4.3\end{revised} in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
 \begin{todo}[Transition text]\end{todo}
@@
 \begin{proof}
-After rescaling by a constant, Theorem~4 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+After rescaling by a constant, Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
@@
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\begin{revised}\series{\Psi}_\alpha\end{revised} = 0$.
 \end{theorem}
@@
 Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering space like $\widetilde{\C^\times}$.
-We can therefore use Theorem~4 of \cite{reg-sing-volterra} to show that $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+We can therefore use Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} to show that $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
 of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
-Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4 of \cite{reg-sing-volterra}.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra}.
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to express $\psi_\alpha$ as the sum of a convergent power series.
@@
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-To prove Theorem~4 in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~3]{reg-sing-volterra}.
+To prove Theorem~\begin{revised}4.6\end{revised} in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~\begin{revised}1.6\end{revised}]{reg-sing-volterra}.
 The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
@@
 
-Let us run through the proof of Theorem~3, specialized to the case we consider in Theorem~4. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+Let us run through the proof of Theorem~\begin{revised}1.6\end{revised}, specialized to the case we consider in Theorem~\begin{revised}4.6\end{revised}.
+First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
 \[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta_\alpha\right) \]
@@
 From here, there are various ways to show that $\series{\Psi}_\alpha$ is Borel summable.
-We do it by using Theorem~4 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
+We do it by using Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
 \begin{theorem}\label{thm:summability_ODE}
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
-If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is proportional to the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
+If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum \begin{revised}is a scalar multiple of\end{revised} the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
 \end{theorem}
@@
 Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
-We know from Theorem~4 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has unique solution in the $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+We know from Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ \begin{revised}has a unique\end{revised} solution in the \begin{revised}affine space\end{revised} $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match.
@@
 \begin{enumerate}
-\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^\theta I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \begin{revised}\aexp^{-\theta}\end{revised} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble and $\alpha=f(a)$.
@@
 \end{align*}
-By the dominated convergence theorem,\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+\begin{revised}Applying the dominated convergence theorem on the right-hand side, we deduce that\end{revised}\footnote{Notice that the sum over $k$ is empty when $n = 0$.
 Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
@@
 Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is proportional to the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
+We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ \begin{revised}is a scalar multiple of\end{revised} the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
 %
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of \begin{revised}any\end{revised} $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighbourhood of $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function \begin{revised}on\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}any\end{revised} $z \in [0, \infty)$.
 
@@
 Thus, by the dominated convergence theorem, $\hat{v}_\alpha$ is an analytic solution of equation~\eqref{int-eq:spatial-mod-bessel-AL} on $\Omega'_\alpha$.
-The uniqueness part of Theorem~4 from \cite{reg-sing-volterra} then shows that $\hat{v}_\alpha$ must be a scalar multiple of the solution $v_\alpha$ we found in Sections \ref{big-idea}\;--\;\ref{neg-root-AL}.
+The uniqueness part of Theorem~\begin{revised}4.6\end{revised} from \cite{reg-sing-volterra} then shows that $\hat{v}_\alpha$ must be a scalar multiple of the solution $v_\alpha$ we found in Sections \ref{big-idea}\;--\;\ref{neg-root-AL}.
 Since $v_\alpha$ belongs to $\singexpalg{-1/2}(\Omega_\alpha)$ for the full, unbounded sector $\Omega_\alpha$, it has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$.
@@
 \[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
-on the position domain.
+on the position domain\begin{revised}, with $\zeta=1+\zeta_1$ as before\end{revised}.
 The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a {\em singularity} in the formalism of resurgent functions~\cite[Section~2]{sauzin2021variations}.
@@
 \[ J(z) = \int_{\mathcal{C}} e^{-zf}\,\nu \]
-defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on $X$.
+defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on \begin{revised} a complex $N$-dimensional manifold\end{revised} $X$.
 The affine group of $\C$ acts on $f$ by post-composition, and this action affects $J$ in a simple way.
@@
 \end{equation}
-where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, we've adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
+where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, \begin{revised}we have\end{revised} adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
 
@@
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
-We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length is proportional to $st$, giving
+We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length \begin{revised}is a scalar multiple of\end{revised} $st$, giving
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
@@
 Recognizing the left-hand side, $v_\text{uni}$, as the integrand of an elliptic integral, we guess that
-\[ f = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)\,, \]
+\begin{equation}\label{eqn:cantilever-guess}
+f = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)\,,
+\end{equation}
 since the Jacobi elliptic function $\operatorname{sd}$ is the inverse of an incomplete elliptic integral.
-To confirm that this equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we first use Jacobi's transformations to rewrite $f$ in terms of $\operatorname{sn}$:
+\begin{revised}To confirm that equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we recall in general that the function
+\[ x = \tfrac{\lambda\mu}{\sqrt{\lambda^2 + \mu^2}}\,\operatorname{sd}\big(u, \tfrac{\mu}{\sqrt{\lambda^2 + \mu^2}}\big) \]
+can be written implicitly in the form~\cite[equation 17.4.51]{Abramowitz-Stegun}
+\[ \sqrt{\lambda^2 + \mu^2} \int_0^x \frac{dt}{\sqrt{(\lambda^2 + t^2)(\mu^2 - t^2)}} = u\,, \]
+and therefore satisfies the differential equation
+\[ \frac{\sqrt{\lambda^2 + \mu^2}\,dx}{\sqrt{(\lambda^2 + x^2)(\mu^2 - x^2)}} = du\,. \]
+Setting both $\lambda$ and $\mu$ to $\omega^{1/2}$, we see that the function
+\[ x = \tfrac{1}{\sqrt{2}}\,\omega^{1/2}\,\operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \]
+satisfies the differential equation
+\[ \frac{\sqrt{2}\,\omega^{1/2}\,dx}{\sqrt{\omega^2 - x^4}} = du\,. \]
+That means the function $f$ from equation~\eqref{eqn:cantilever-guess} satisfies the differential equation
+\[ \frac{df}{2i \omega \sqrt{1 - \omega^{-2} f^4}} = du\,, \]
+which simplifies to
+\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
+when we take the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. \begin{verify}
+To confirm that equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we recall in general that the function
+\[ x = \tfrac{\lambda\mu}{\sqrt{\lambda^2 + \mu^2}}\,\operatorname{sd}\big(w, \tfrac{\mu}{\sqrt{\lambda^2 + \mu^2}}\big) \]
+can be written implicitly in the form~\cite[equation 17.4.51]{Abramowitz-Stegun}
+\[ \sqrt{\lambda^2 + \mu^2} \int_0^x \frac{dt}{\sqrt{(\lambda^2 + t^2)(\mu^2 - t^2)}} = w\,, \]
+and therefore satisfies the differential equation
+\[ \frac{\sqrt{\lambda^2 + \mu^2}\,dx}{\sqrt{(\lambda^2 + x^2)(\mu^2 - x^2)}} = dw\,. \]
+Setting both $\lambda$ and $\mu$ to $\sqrt{2}$ and $w=2\sqrt{2}\omega^{1/2} u$, we see that the function
+\[ x = \operatorname{sd}\Big(2\sqrt{2}\omega^{1/2} u, \tfrac{1}{\sqrt{2}}\Big) \]
+satisfies the differential equation
+\[ \frac{dx}{\sqrt{4 - x^4}} = \sqrt{2}\,\omega^{1/2}\,du\,. \]
+That means the function $f$ from equation~\eqref{eqn:cantilever-guess} satisfies the differential equation
+\[ \frac{df}{2i \omega \sqrt{1 - \omega^{-2} f^4}} = du\,, \]
+which simplifies to
+\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
+when we take the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. 
+\end{verify}
+\end{revised}\begin{old}To confirm that this equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we first use Jacobi's transformations to rewrite $f$ in terms of $\operatorname{sn}$:
 \[ f = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big)\,. \]
@@
 \[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
-by taking the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
+by taking the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$.\end{old} By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
 so we have
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighbourhood of $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius neighbourhood of $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of $z \in [0, \infty)$.
 %
@@
 \end{align*}
-Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighbourhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
+Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a \begin{revised}neighborhood\end{revised} of $\mathcal{J}_{\zeta, 1}$ in the position domain.
 They give the values of $u$ after lifting to the incoming and outgoing branches of $\mathcal{C}^\theta_1$, respectively.
@@
 \begin{remark}
-The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB ansatz for a Schr\"{o}dinger type equation is
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB \begin{revised}Ansatz\end{revised} for a Schr\"{o}dinger type equation is
 \begin{equation}
@@
 \bibliographystyle{utphys}
-\bibliography{borel-regularity}
+%\bibliographystyle{plain}
+\bibliography{borel-regularity-SIGMA}
 \end{document}

### 2025-10-22 SIGMA/borel-regularity-SIGMA.tex
Commit first-round revisions

@@
 \item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$\begin{revised},\end{revised} the continuation of $d\zeta$.
-\item If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
+Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$\begin{revised}, which is\end{revised} the continuation of $d\zeta$.
+\item\label{step:borel-sum} If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
 In this case, we say $\series{\Phi}$ is {\em Borel summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$ in the direction $\theta$.
@@
 \begin{definition}
-For any direction $\theta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
-\[ \aexp^\theta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
-is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\theta}(0, \infty)$.
-To be in the domain of $\aexp^\theta$, a function just needs to have an asymptotic expansion on one such sector.
+For any direction \begin{revised}$\vartheta$\end{revised} and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
+\[ \aexp^{\begin{revised}\vartheta\end{revised}} \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
+is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\begin{revised}\vartheta\end{revised}}(0, \infty)$.
+To be in the domain of $\aexp^{\begin{revised}\vartheta\end{revised}}$, a function just needs to have an asymptotic expansion on one such sector.
 \end{definition}
@@
 \end{definition}
-To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let us take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
+To compare the Borel sum $\hat{\Phi}$ from step~\ref{step:borel-sum} with the original series $\series{\Phi}$, let us take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.
 
@@
 \end{enumerate}
+\begin{revised}Note that the Borel sum and the asymptotic expansion are taken along the complementary directions $\theta$ and $-\theta$, respectively.\end{revised}
 
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{\begin{revised}-\end{revised}\theta}"]& & \\
-\hat{\Phi} \arrow[rr, "\aexp^{\begin{revised}-\end{revised}\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\begin{revised}\aexp^{-\theta}\end{revised}"]& & \\
+\hat{\Phi} \arrow[rr, "\begin{revised}\aexp^{-\theta}\end{revised}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
 & & \\
@@
 \begin{enumerate}
-\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.\footnote{\begin{revised}The choice of $-\theta$ in the asymptotic expansion is dictated by our convention for the Laplace transform that we decide to take in direction $\theta$, like we do in step $4.$.
-As explained in Section~2.1, the sign of the angle $\theta$ should be consistent between the asymptotic expansion and the Laplace transform.\end{revised}}
+\item Take the asymptotic expansion $\series{\Phi} = \aexp^{-\theta} \Phi$.
 \item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
@@
 \begin{enumerate}
-\item Solving a level~$1$\footnote{\begin{revised}The level of linear ODE at a singular point is defined by looking at the Newton polygon associated to the equation, and it corresponds to its positive slope~\cite[Proposition~3.3.14]{diverg-resurg--ii} \end{revised}} linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.
-Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
+\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{\begin{revised}Calling a linear ODE {\em level~$1$} is an short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
+In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.\end{revised}} Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity\begin{revised}, say at $\infty$,\end{revised} exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from direction to the next.
+Analytic solutions of a linear ODE with an irregular singularity\begin{old}, say at $\infty$,\end{old} exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from \begin{revised}one\end{revised} direction to the next.
 Formally, this behaviour is captured in a {\em formal integral} solution: an expression
 \[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
-in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$.
+in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$\begin{revised}, where $z$ is a coordinate that puts the singularity at $z = \infty$\end{revised}.
 For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
@@
 This has motivated the development of summability methods, which promote formal solutions to analytic ones~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-These methods can be applied both within and beyond the world of linear level~$1$ ODEs\begin{revised}, including nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}\end{revised}.
+These methods can be applied both within and beyond the world of linear level~$1$ ODEs\begin{old}, including nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}\end{old}.
+\begin{revised}For instance, Costin has applied them to a broad class of nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}.\end{revised}
 %
@@
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\begin{revised}\series{\Psi}_\alpha\end{revised} = 0$.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\begin{revised}\series{\Psi}\end{revised} = 0$.
 \end{theorem}
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of \begin{revised}any\end{revised} $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on \begin{revised}the slit plane\end{revised} $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of \begin{revised}the ray\end{revised} $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function \begin{revised}on\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}any\end{revised} $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function \begin{revised}on the slit plane\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in [0, \infty)$.
 
@@
 \[ J(z) = \int_{\mathcal{C}} e^{-zf}\,\nu \]
-defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on \begin{revised} a complex $N$-dimensional manifold\end{revised} $X$.
+defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on \begin{revised} a complex manifold\end{revised} $X$.
 The affine group of $\C$ acts on $f$ by post-composition, and this action affects $J$ in a simple way.
@@
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
-We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length \begin{revised}is a scalar multiple of\end{revised} $st$, giving
+We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length is a scalar multiple of $st$, giving
 \[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
@@
 where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$.
-Recognizing the left-hand side, $v_\text{uni}$, as the integrand of an elliptic integral, we guess that
-\begin{equation}\label{eqn:cantilever-guess}
-f = 2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big)\,,
-\end{equation}
-since the Jacobi elliptic function $\operatorname{sd}$ is the inverse of an incomplete elliptic integral.
-\begin{revised}To confirm that equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we recall in general that the function
-\[ x = \tfrac{\lambda\mu}{\sqrt{\lambda^2 + \mu^2}}\,\operatorname{sd}\big(u, \tfrac{\mu}{\sqrt{\lambda^2 + \mu^2}}\big) \]
-can be written implicitly in the form~\cite[equation 17.4.51]{Abramowitz-Stegun}
-\[ \sqrt{\lambda^2 + \mu^2} \int_0^x \frac{dt}{\sqrt{(\lambda^2 + t^2)(\mu^2 - t^2)}} = u\,, \]
-and therefore satisfies the differential equation
-\[ \frac{\sqrt{\lambda^2 + \mu^2}\,dx}{\sqrt{(\lambda^2 + x^2)(\mu^2 - x^2)}} = du\,. \]
-Setting both $\lambda$ and $\mu$ to $\omega^{1/2}$, we see that the function
-\[ x = \tfrac{1}{\sqrt{2}}\,\omega^{1/2}\,\operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \]
-satisfies the differential equation
-\[ \frac{\sqrt{2}\,\omega^{1/2}\,dx}{\sqrt{\omega^2 - x^4}} = du\,. \]
-That means the function $f$ from equation~\eqref{eqn:cantilever-guess} satisfies the differential equation
-\[ \frac{df}{2i \omega \sqrt{1 - \omega^{-2} f^4}} = du\,, \]
-which simplifies to
-\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
-when we take the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. \begin{verify}
-To confirm that equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we recall in general that the function
-\[ x = \tfrac{\lambda\mu}{\sqrt{\lambda^2 + \mu^2}}\,\operatorname{sd}\big(w, \tfrac{\mu}{\sqrt{\lambda^2 + \mu^2}}\big) \]
-can be written implicitly in the form~\cite[equation 17.4.51]{Abramowitz-Stegun}
-\[ \sqrt{\lambda^2 + \mu^2} \int_0^x \frac{dt}{\sqrt{(\lambda^2 + t^2)(\mu^2 - t^2)}} = w\,, \]
-and therefore satisfies the differential equation
-\[ \frac{\sqrt{\lambda^2 + \mu^2}\,dx}{\sqrt{(\lambda^2 + x^2)(\mu^2 - x^2)}} = dw\,. \]
-Setting both $\lambda$ and $\mu$ to $\sqrt{2}$ and $w=2\sqrt{2}\omega^{1/2} u$, we see that the function
-\[ x = \operatorname{sd}\Big(2\sqrt{2}\omega^{1/2} u, \tfrac{1}{\sqrt{2}}\Big) \]
-satisfies the differential equation
-\[ \frac{dx}{\sqrt{4 - x^4}} = \sqrt{2}\,\omega^{1/2}\,du\,. \]
-That means the function $f$ from equation~\eqref{eqn:cantilever-guess} satisfies the differential equation
-\[ \frac{df}{2i \omega \sqrt{1 - \omega^{-2} f^4}} = du\,, \]
-which simplifies to
-\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
-when we take the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$. 
+\begin{revised}We can guess a function $f$ with this property by noting that equation~\eqref{eqn:cantilever-thimble-difference} looks like one of the differential equations that characterize the Jacobi elliptic functions.
+
+The Jacobi function
+\[ x = \operatorname{sd}(t, k) \]
+with elliptic modulus $k \in [0, 1]$ satisfies the differential equation~\cite[equation~22.13.5]{dlmf}
+\[ \frac{1}{\sqrt{\big(1 - k'^2 x^2\big)\big(1 + k^2 x^2\big)}} = \frac{dt}{dx}\,, \]
+where $k' \in [0, 1]$ is the complementary modulus given by $k^2 + k'^2 = 1$. In particular, the function
+\[ x = \operatorname{sd}\big(t, \tfrac{1}{\sqrt{2}}\big) \]
+satisfies the equation
+\begin{verify}
+\[ \frac{1}{\sqrt{\big(1 - \tfrac{1}{2} x^2\big)\big(1 + \tfrac{1}{2} x^2\big)}} = \frac{dt}{dx} \]
 \end{verify}
-\end{revised}\begin{old}To confirm that this equation~\eqref{eqn:cantilever-thimble-difference} holds for this guess, we first use Jacobi's transformations to rewrite $f$ in terms of $\operatorname{sn}$:
-\[ f = \omega^{1/2} \operatorname{sn}\big(2i \omega^{1/2} u, i\big)\,. \]
-In terms of the incomplete elliptic integral
-\[ F(x; k) := \int_0^x \frac{dt}{\sqrt{(1-t^2)(1-k^2t^2)}}\,, \]
-we then have
-\begin{align*}
-F(\omega^{-1/2} f; i) & = 2i \omega^{1/2} u \\
-\frac{\omega^{-1/2}\;df}{\sqrt{1 - (\omega^{-1/2} f)^4}} & = 2i \omega^{1/2}\;du \\
-\frac{1}{2i \omega \sqrt{1 - \omega^{-2} f^4}} & = \frac{du}{df}\,.
-\end{align*}
-We can simplify this to
-\[ \frac{1}{2}\left[\frac{1}{\sqrt{f^4 - \omega^2}}\right] = \frac{du}{df} \]
-by taking the branch of $\sqrt{f^4 - \omega^2}$ that evaluates to $i\omega$ when $f = 0$.\end{old} By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
+\[ \frac{1}{\sqrt{1 - \tfrac{1}{4} x^4}} = \frac{dt}{dx}\,. \]
+Introducing, for convenience, the constant $\varepsilon = (\omega/2)^{1/2}$, we can deduce that the function
+\[ f = i\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \]
+satisfies the equation
+\[ \frac{1}{2} \left[ \frac{1}{\sqrt{f^4 - \omega^2}} \right] = \frac{du}{df} \]
+when we choose the branch of the square root that evaluates to $i\omega^2$ when $f = 0$.\end{revised} By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
 so we have
@@
 
-From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd at $a$ with respect to $u$, implying that
+\begin{verify}
+To verify the guess for $f$, set $f = i \varepsilon x$ and $t = 4 \varepsilon u$ in the differential equation satisfied by $x = \operatorname{sd}(t, \tfrac{1}{\sqrt{2}})$. We get
+\begin{align*}
+\frac{1}{\sqrt{1 - \tfrac{1}{4} (i\varepsilon)^{-4} f^4}} & = \frac{4 \varepsilon\,du}{(i\varepsilon)^{-1}\,df} \\
+\frac{1}{4i \varepsilon^2 \sqrt{1 - \tfrac{1}{4} \varepsilon^{-4} f^4}} & = \frac{du}{df} \\
+\frac{1}{2i\sqrt{4\varepsilon^4 - f^4}} & = \frac{du}{df} \\
+\frac{1}{2} \left[ \frac{1}{\sqrt{f^4 - 4\varepsilon^4}} \right] & = \frac{du}{df}\,,
+\end{align*}
+where in the last step we choose the branch of the square root that evaluates to $2i\varepsilon^2$ when $f = 0$.
+\end{verify}
+
+From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd \begin{old}at $a$\end{old} with respect to $u$, implying that
 \[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
@@
 confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
-\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\,2i\omega \operatorname{sd}\big(u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,. \]
-Since the exponent is doubly periodic, with period lattice $L = \tfrac{1}{\sqrt{2}}\Z + i\Z$, we can take the thimble to be a real submanifold of the torus $\C / L$.
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\begin{revised}i\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big)\end{revised} \right]\;du\,\begin{revised},\end{revised} \]
+\begin{revised}where $\varepsilon = (\omega/2)^{1/2}$ is the convenience constant we introduced earlier. The exponent is doubly periodic, with period lattice~\cite[table~22.4.1]{dlmf}
+\[ L = \varepsilon^{-1} K\big(\tfrac{1}{\sqrt{2}}\big)\big[\Z + \tfrac{1}{2}(1 + i)\,\Z\big]\,, \]
+where $K$ is the complete elliptic integral~\cite[formula~19.2.8]{dlmf}
+\[ K(k) = \int_0^1 \frac{dx}{\sqrt{(1 - x^2)(1 - k^2 x^2)}}\,. \]
+We can therefore take the thimble to be a real submanifold of the torus $\C / L$.\end{revised}
 %
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on $z \notin (-\infty, 0]$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on \begin{revised}the slit plane\end{revised} $z \notin (-\infty, 0]$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function \begin{revised}on the slit plane\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in [0, \infty)$.
 %

### 2025-10-22 SIGMA/borel-regularity-SIGMA.tex
Remove `revised` environments and `old` text
All of this stuff was supposed to be hidden, so ideally this removal
wouldn't affect the rendered document. However, it turns out that a
hidden `old` environment had led to a missing space between words in
one place. Removing the environment corrects the spacing.

@@
 \ifshowold
-\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
+%%\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
 \else
-\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
+%%\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
 \fi
@@
 \ifshowdraft
-\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
+%%\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
 \else
-\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
+%%\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
 \fi
@@
 \ifhighlightrevs
-\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
+%%\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
 \else
-\newenvironment{revised}{}{}
+%%\newenvironment{revised}{}{}
 \fi
@@
 
-The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over \begin{revised}one-dimensional\end{revised} Lefschetz thimbles.
+The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over one-dimensional Lefschetz thimbles.
 To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
@@
 \end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{\begin{revised} Trans-mononials can be of different kind, for example fractional powers of $z$ can appear at the exponent.
-In this paper we will only deal with trans-monomial of the form $e^{-\alpha z}$, for some $\alpha\in\C$.\end{revised}} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different kind, for example fractional powers of $z$ can appear at the exponent.
+In this paper we will only deal with trans-monomial of the form $e^{-\alpha z}$, for some $\alpha\in\C$.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
 \begin{equation}
@@
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
-using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$.
-Na\"{i}vely integrating term by term, you again get the \begin{revised}trans-monomial\end{revised}~\eqref{series:bessel_ex}, up to a constant.
+using the substitution $\tfrac{1}{2} t^2 = 4u^3 - 3u + 1$. Na\"{i}vely integrating term by term, you again get the trans-monomial~\eqref{series:bessel_ex}, up to a constant.
 
@@
 \item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
-\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$.
-Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$\begin{revised}, which is\end{revised} the continuation of $d\zeta$.
+\item If $\series{\phi}$ has a positive radius of convergence, we sum it to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$.
+Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$, which is the continuation of $d\zeta$.
 \item\label{step:borel-sum} If $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in \alpha + e^{i\theta}(0, \infty)$, its Laplace transform $\hat{\Phi} := \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane.
@@
 
-\begin{revised}If a function is asymptotic to two power series of the form \eqref{series:asymp-definition}, those series must be equal;\end{revised}
-\begin{old}If two power series of the form \eqref{series:asymp-definition} are asymptotic to the same function, they must be equal;\end{old} this can be deduced from the triangle inequality.
-The power series which \begin{old}is asymptotic to\end{old} a given function \begin{revised}is asymptotic to\end{revised} on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
+If a function is asymptotic to two power series of the form \eqref{series:asymp-definition}, those series must be equal; this can be deduced from the triangle inequality.
+The power series which a given function is asymptotic to on a given open sector, if it exists, is therefore an intrinsic property of the function: we call it the function's {\em asymptotic expansion} on that sector.
 The functions that have asymptotic expansions on a given sector form a ring~\cite[Section~A.4]{nikolaev2023existence}, and the map that sends such a function to its asymptotic expansion is a ring homomorphism.
@@
 \begin{definition}
-For any direction \begin{revised}$\vartheta$\end{revised} and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
-\[ \aexp^{\begin{revised}\vartheta\end{revised}} \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
-is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\begin{revised}\vartheta\end{revised}}(0, \infty)$.
-To be in the domain of $\aexp^{\begin{revised}\vartheta\end{revised}}$, a function just needs to have an asymptotic expansion on one such sector.
+For any direction $\vartheta$ and any trans-monomial space $e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket$, the {\em asymptotic expansion} homomorphism
+\[ \aexp^\vartheta \maps \mathcal{O}(\C) \to e^{\alpha z} z^{-\sigma} \C \llbracket z^{-1} \rrbracket \]
+is the partially defined map that sends a holomorphic function on an open subset of $\C$ to its asymptotic expansion on a sector containing the end of the ray $z \in e^{i\vartheta}(0, \infty)$.
+To be in the domain of $\aexp^\vartheta$, a function just needs to have an asymptotic expansion on one such sector.
 \end{definition}
@@
 \begin{enumerate}[start=4]
-\item By construction, $\begin{revised}\aexp^{-\theta}\end{revised} \hat{\Phi} = \series{\Phi}$.
+\item By construction, $\aexp^{-\theta} \hat{\Phi} = \series{\Phi}$.
 It turns out that $\hat{\Phi}$ is not only asymptotic to $\series{\Phi}$, but {\em {uniformly} $1$-Gevrey}-asymptotic~\cite[Corollary~5.23]{diverg-resurg-i}.
 \end{enumerate}
-\begin{revised}Note that the Borel sum and the asymptotic expansion are taken along the complementary directions $\theta$ and $-\theta$, respectively.\end{revised}
+Note that the Borel sum and the asymptotic expansion are taken along the complementary directions $\theta$ and $-\theta$, respectively.
 
@@
 & \text{problem} & \\
-\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\begin{revised}\aexp^{-\theta}\end{revised}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
+\hat{\Phi} \arrow[ru, dotted, no head, tail] \arrow[rr, mapsto, "\aexp^{-\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[lu, no head, tail, "\parbox{10mm}{\centering\scriptsize formally solves}"'] \arrow[dd, mapsto, "\borel"] \\
 & & \\
@@
 
-You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is \begin{revised}the asymptotic expansion of\end{revised} an actual solution.
+You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is the asymptotic expansion of an actual solution.
 After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them.
 In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem.
-\begin{revised}Borel recognized this phenomenon as a key motivation for the study of divergent series \cite{borel-memoire,borel-lecons}, and much has been said about it since (Section~\ref{sec:historical-context});\end{revised} \begin{revised}the\end{revised} question of how \begin{revised}it\end{revised} happens is the starting point for this paper.
+Borel recognized this phenomenon as a key motivation for the study of divergent series \cite{borel-memoire,borel-lecons}, and much has been said about it since (Section~\ref{sec:historical-context}); the question of how it happens is the starting point for this paper.
 %
@@
 & \text{problem} & \\
-\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\begin{revised}\aexp^{-\theta}\end{revised}"]& & \\
-\hat{\Phi} \arrow[rr, "\begin{revised}\aexp^{-\theta}\end{revised}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
+\Phi \arrow[ru, no head, tail, swap, "\text{solves}"' ] \arrow[rrd, mapsto, "\aexp^{-\theta}"]& & \\
+\hat{\Phi} \arrow[rr, "\aexp^{-\theta}", "\text{($1$-Gevrey)}"'] & & \series{\Phi} \arrow[luu, no head, tail, swap, "\parbox{10mm}{\centering\scriptsize formally solves}"] \arrow[dd, mapsto, "\borel_\zeta"] \\
 & & \\
@@
 \item Take the Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$.
-\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface \begin{revised}$B$\end{revised} with a distinguished $1$-form, as before.
+\item Take the sum $\hat{\phi}$ of $\series{\phi}$, and expand its domain to a Riemann surface $B$ with a distinguished $1$-form, as before.
 \item Take the Laplace transform $\hat{\Phi} = \laplace_{\zeta, 0}^\theta \hat{\phi}$.
@@
 \begin{enumerate}
-\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{\begin{revised}Calling a linear ODE {\em level~$1$} is an short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
-In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.\end{revised}} Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
+\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is an short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
+In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.} Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
@@
 We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
-However, this only works when there is a coincidence between \begin{revised}the\end{revised} exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
+However, this only works when there is a coincidence between the exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$.
 Why?
 
-A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function \begin{revised} $\phi$ on\end{revised} the position domain.
+A first clue is the observation that every solution we get from Borel summation is, by definition, the Laplace transform $\Phi = \laplace_{\zeta,\alpha}^\theta \phi$ of a function $\phi$ on the position domain.
 In fact, the differential equation $\mathcal{P}\Phi = 0$ is equivalent to an integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$.
 
-Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~\begin{revised}4.6\end{revised}]{reg-sing-volterra}.
+Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4.6]{reg-sing-volterra}.
 This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
@@
 
-From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the \begin{revised}Ansatz\end{revised} that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
+From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the Ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$.
 On the other hand, from a formal perspective, one can start from the computation of the Poincar\'{e} solutions and the observation that their Borel transforms converge, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability.
@@
 \begin{enumerate}
-\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \begin{revised}\aexp^{-\theta}\end{revised} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
@@
 When the half-plane extends along the $-\theta$ direction, the sum $\hat{\phi}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction.
-In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over \begin{revised}any\end{revised} constant-radius \begin{revised}neighborhood\end{revised} of the ray $\zeta \in e^{i\theta}[0, \infty)$.
+In fact, we have $|\hat{\phi}| \lesssim e^{\Lambda |\zeta|}$ uniformly over any constant-radius neighborhood of the ray $\zeta \in e^{i\theta}[0, \infty)$.
 \begin{center}
@@
 The study of irregular singular differential equations on complex domains has a long history, and interesting phenomena distinguish irregular singular equations from regular singular ones.
-Analytic solutions of a linear ODE with an irregular singularity\begin{old}, say at $\infty$,\end{old} exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from \begin{revised}one\end{revised} direction to the next.
+Analytic solutions of a linear ODE with an irregular singularity exhibit the Stokes phenomenon: asymptotic behaviour that changes sharply from one direction to the next.
 Formally, this behaviour is captured in a {\em formal integral} solution: an expression
 \[ \sum_{\alpha \in A} e^{-\alpha z} z^{\tau_\alpha} \series{F}_\alpha \]
-in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$\begin{revised}, where $z$ is a coordinate that puts the singularity at $z = \infty$\end{revised}.
+in which $A$ is a finite set of complex numbers, each $\tau_\alpha$ is a real number, and each $\series{F}_\alpha$ is a formal power series in $\C\llbracket z^{-1} \rrbracket$, where $z$ is a coordinate that puts the singularity at $z = \infty$.
 For each direction $\theta$, the term with the lowest value of $\Re(e^{i\theta} \alpha)$ represents the dominant contribution to the solution's asymptotic behavior.
@@
 & \textbf{Analytic} & \textbf{Formal} \\ \hline
-\textbf{Frequency} &  & Poincar\'{e}: trans-monomial \begin{revised}Ansatz\end{revised}~\cite{int-irreg} \\ \hline
+\textbf{Frequency} &  & Poincar\'{e}: trans-monomial Ansatz~\cite{int-irreg} \\ \hline
 \textbf{Position} & \'{E}calle: resurgence  & \'{E}calle: formal perturbation theory~\cite{EcalleIII,loday-Remy2011} \\
@@
 This has motivated the development of summability methods, which promote formal solutions to analytic ones~\cite{diverg-resurg--ii,malgrange--fourier,malgrange1995sommation,malgrange92,ramis1991series}.
-These methods can be applied both within and beyond the world of linear level~$1$ ODEs\begin{old}, including nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}\end{old}.
-\begin{revised}For instance, Costin has applied them to a broad class of nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}.\end{revised}
+These methods can be applied both within and beyond the world of linear level~$1$ ODEs.
+For instance, Costin has applied them to a broad class of nonlinear systems of ODEs~\cite{Costin:borel-sum-non-linear}.
 %
@@
 \'{E}calle proved this by using formal perturbation theory to solve a corresponding integral equation in the position domain.
-Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the \begin{revised}perturbation\end{revised} series would converge to an endlessly analytically continuable function.
+Using the ``formalism of singularities'' to understand how the singularities of the perturbative solution would propagate from one order of perturbation to the next, \'{E}calle showed that the perturbation series would converge to an endlessly analytically continuable function.
 Loday-Richaud and Remy went on to show that this function always has a well-defined Laplace transform, so the corresponding formal solution in the frequency domain is Borel summable~\cite{loday-Remy2011}.
@@
 
-\begin{revised}\'{E}calle's theory not only shed light on Borel summation, but also generalized it.
-\'{E}calle introduced generalized resummation methods that use ``well-behaved averages'' to handle infinite sequences of singularities along the summation axis~\cite{EcalleI,Écalle-dulac,menous-mould,menous_phdthesis}.\end{revised}
+\'{E}calle's theory not only shed light on Borel summation, but also generalized it.
+\'{E}calle introduced generalized resummation methods that use ``well-behaved averages'' to handle infinite sequences of singularities along the summation axis~\cite{EcalleI,Écalle-dulac,menous-mould,menous_phdthesis}.
 %
@@
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, given an ODE, we can set up a \begin{revised}classical\end{revised} Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
+In particular, given an ODE, we can set up a classical Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
 
@@
 \subsubsection{Thimble integrals in physics}
-In wave optics, a thimble integral can arise when we \begin{revised}add\end{revised} up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
+In wave optics, a thimble integral can arise when we add up the secondary waves emanating from all the points along a wavefront~\cite{Fenyes-ihes-lecture}.
 For example, the Airy integral approximates the sum of the secondary waves coming from a wavefront with an inflection point~\cite{rainbows+glories}.
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the \begin{revised}so-called\end{revised} wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
+Indeed, the so-called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}.
@@
 Like solutions of level~$1$ ODEs, thimble integrals often exhibit the Stokes phenomenon.
-For \begin{revised}one-dimensional\end{revised} thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
+For one-dimensional thimble integrals, the Stokes constants can be interpreted geometrically as intersection numbers for pairs of thimbles~\cite{kontsevich2022analyticity}.
 More generally, finding the Stokes constants is equivalent to finding the monodromy of the local system $H^\theta_N(X,f)$ (see the recent development~\cite{kontsevich2024holomorphic}).
@@
 \end{equation}
-where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a \begin{revised}neighborhood\end{revised} of $\zeta=\alpha$.
+where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighborhood of $\zeta=\alpha$.
 
@@
 
-If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a \begin{revised}neighborhood\end{revised} of $\zeta = 0$.
+If a function on $\Omega$ has an ordinary Taylor expansion in $\C\{\zeta\}$, summing the series extends the function to a neighborhood of $\zeta = 0$.
 The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
@@
 To study this subspace, it will be helpful to work on the universal covering $\pi \maps \widetilde{\C^\times} \to \C^\times$.
-On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$ in $\C$.
+On a simply connected open set $\Upsilon \subset \widetilde{\C^\times}$ that touches $\zeta = 0$, a function has an ordinary Taylor expansion around $\zeta = 0$ if and only if it descends and extends to a holomorphic function on a neighborhood of $\zeta = 0$ in $\C$.
 Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
@@
 is bounded.
-A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a \begin{revised}neighborhood\end{revised} of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
+A function in $\singexp{\sigma}{\Lambda}(\Upsilon)$ descends and extends to a function on a neighborhood of $\zeta = 0$ in $\C$ if and only if it lies in the kernel of $\var - (e^{2\pi i \rho} - 1)$.
 This operator is bounded, so its kernel is closed.
@@
 and define the constant $\tau_\alpha := \frac{Q(-\alpha)}{P'(-\alpha)}$.
-From Lemma~\begin{revised}4.3\end{revised} in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
+From Lemma~4.3 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
 \begin{todo}[Transition text]\end{todo}
@@
 \begin{proof}
-After rescaling by a constant, Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+After rescaling by a constant, Theorem~4.6 of \cite{reg-sing-volterra} tells us that the equation $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Omega_\alpha) \]
@@
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
-The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\begin{revised}\series{\Psi}\end{revised} = 0$.
+The analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE} is the Borel sum of a formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Psi} = 0$.
 \end{theorem}
@@
 Our arguments in \cite{reg-sing-volterra} took place on $\C$, but they work just as well on a covering space like $\widetilde{\C^\times}$.
-We can therefore use Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} to show that $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
+We can therefore use Theorem~4.6 of \cite{reg-sing-volterra} to show that $\hat{\mathcal{P}}_\alpha \psi_\alpha = 0$ has a unique solution $\psi_\alpha$ in the affine subspace
 \[ \frac{\zeta_\alpha^{\tau_\alpha-1}}{\Gamma(\tau_\alpha)} + \singexpalg{\tau_\alpha}(\Upsilon) \]
 of the space $\singexpalg{\tau_\alpha-1}(\Upsilon)$.
-Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra}.
+Restricting this solution to $\Omega_\alpha$ gives the analogous solution from the proof of Theorem~\ref{re:thm:exist_uniq_ODE}, as we can see from the uniqueness part of Theorem~4.6 of \cite{reg-sing-volterra}.
 To express $\Psi_\alpha = \laplace_{\zeta, \alpha} \psi_\alpha$ as the Borel sum of a trans-monomial, we first need to express $\psi_\alpha$ as the sum of a convergent power series.
@@
 For convenience, let $p = P(-\zeta)$ and $q = Q(-\zeta)$.
-To prove Theorem~\begin{revised}4.6\end{revised} in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~\begin{revised}1.6\end{revised}]{reg-sing-volterra}.
+To prove Theorem~4.6 in \cite{reg-sing-volterra}, we rewrite the equation $\hat{\mathcal{P}}_\alpha \solwhole = 0$ as a regular singular Volterra equation $\solwhole = \volterra^\alpha \solwhole$ that satisfies the conditions of the underlying existence and uniqueness result~\cite[Theorem~1.6]{reg-sing-volterra}.
 The operator $\volterra^\alpha$ is the sum of the ``prototypical'' part
@@
 
-Let us run through the proof of Theorem~\begin{revised}1.6\end{revised}, specialized to the case we consider in Theorem~\begin{revised}4.6\end{revised}.
-First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
+Let us run through the proof of Theorem~1.6, specialized to the case we consider in Theorem~4.6. First, picking an arbitrary point $b \in \Omega_\alpha$, we show that the {\em prototype solution}
 \[ \solproto(a) = \frac{1}{p(a)} \exp\left(-\int_{b}^{a}\frac{q}{p}\;d\zeta_\alpha\right) \]
@@
 From here, there are various ways to show that $\series{\Psi}_\alpha$ is Borel summable.
-We do it by using Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
+We do it by using Theorem~4.6 of \cite{reg-sing-volterra} to show that the relevant integral equation in the position domain has a unique analytic solution.
 \begin{theorem}\label{thm:summability_ODE}
@@
 Choose an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and does not touch any other root of $P(-\zeta)$.
-If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum \begin{revised}is a scalar multiple of\end{revised} the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
+If a $1$-Gevrey trans-monomial $\series{\Psi}_\alpha \in e^{-z\alpha} z^{-\tau_\alpha}\C\llbracket z^{-1} \rrbracket_1$ satisfies the equation $\mathcal{P} \series{\Psi}_\alpha = 0$, then it is Borel summable at $\alpha$ along any ray in $\Omega_\alpha$, and its Borel sum is a scalar multiple of the analogous analytic solution $\Psi_\alpha$ from Theorem~\ref{re:thm:exist_uniq_ODE}.
 \end{theorem}
@@
 Since $\Omega_\text{near}$ is bounded, this implies that $\hat{\psi}_\alpha$ lies in $c \zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\text{near})$, where $c$ is the leading coefficient of $\series{\psi}_\alpha$.
-We know from Theorem~\begin{revised}4.6\end{revised} of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ \begin{revised}has a unique\end{revised} solution in the \begin{revised}affine space\end{revised} $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
+We know from Theorem~4.6 of \cite{reg-sing-volterra} that the equation $\hat{\mathcal{P}}_\alpha \varphi = 0$ has a unique solution in the affine space $\zeta_\alpha^{\tau_\alpha-1} + \singexpalg{\tau_\alpha}(\Omega_\alpha)$.
 The same theorem applies on the domain $\Omega_\text{near}$, where its uniqueness provision shows that $\hat{\psi}_\alpha$ and $c\psi_\alpha$ must match.
@@
 \begin{enumerate}
-\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \begin{revised}\aexp^{-\theta}\end{revised} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble and $\alpha=f(a)$.
@@
 \end{align*}
-\begin{revised}Applying the dominated convergence theorem on the right-hand side, we deduce that\end{revised}\footnote{Notice that the sum over $k$ is empty when $n = 0$.
+Applying the dominated convergence theorem on the right-hand side, we deduce that\footnote{Notice that the sum over $k$ is empty when $n = 0$.
 Following convention, we extend the double factorial to all odd integers by its recurrence relation, giving $(-1)!!
@@
 Borel summation makes the analogy precise.
-We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ \begin{revised}is a scalar multiple of\end{revised} the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
+We will see in Section~\ref{bessel-regularity-AL} that each $z^{-\tau_\alpha}\,W_\alpha$ is a scalar multiple of the Borel sum of $z^{-\tau_\alpha}\,\series{W}_\alpha$, as required by Theorem~\ref{thm:summability_ODE}.
 %
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on \begin{revised}the slit plane\end{revised} $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of \begin{revised}the ray\end{revised} $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function \begin{revised}on the slit plane\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.
 
@@
 Thus, by the dominated convergence theorem, $\hat{v}_\alpha$ is an analytic solution of equation~\eqref{int-eq:spatial-mod-bessel-AL} on $\Omega'_\alpha$.
-The uniqueness part of Theorem~\begin{revised}4.6\end{revised} from \cite{reg-sing-volterra} then shows that $\hat{v}_\alpha$ must be a scalar multiple of the solution $v_\alpha$ we found in Sections \ref{big-idea}\;--\;\ref{neg-root-AL}.
+The uniqueness part of Theorem~4.6 from \cite{reg-sing-volterra} then shows that $\hat{v}_\alpha$ must be a scalar multiple of the solution $v_\alpha$ we found in Sections \ref{big-idea}\;--\;\ref{neg-root-AL}.
 Since $v_\alpha$ belongs to $\singexpalg{-1/2}(\Omega_\alpha)$ for the full, unbounded sector $\Omega_\alpha$, it has a well-defined Laplace transform along any ray $\mathcal{J}^\theta_{\zeta, \alpha}$ in $\Omega_\alpha$.
@@
 \[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
-on the position domain\begin{revised}, with $\zeta=1+\zeta_1$ as before\end{revised}.
+on the position domain, with $\zeta=1+\zeta_1$ as before.
 The function $v_1$ is singular at $\zeta = 1$, but the hypergeometric factor ${}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)$ is analytic at that point, so $v_1$ has the typical form of a {\em singularity} in the formalism of resurgent functions~\cite[Section~2]{sauzin2021variations}.
@@
 \[ J(z) = \int_{\mathcal{C}} e^{-zf}\,\nu \]
-defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on \begin{revised} a complex manifold\end{revised} $X$.
+defined by an arbitrary holomorphic map $f \maps X \to \C$ and an arbitrary $1$-form $\nu$ on a complex manifold $X$.
 The affine group of $\C$ acts on $f$ by post-composition, and this action affects $J$ in a simple way.
@@
 \end{equation}
-where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, \begin{revised}we have\end{revised} adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
+where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, we have adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
 
@@
 where $\mathcal{C}_a^\theta(\zeta)$ is the part of $\mathcal{C}_a^\theta$ that goes through $f^{-1}\big([\alpha,\zeta e^{i\theta}]\big)$.
-\begin{revised}We can guess a function $f$ with this property by noting that equation~\eqref{eqn:cantilever-thimble-difference} looks like one of the differential equations that characterize the Jacobi elliptic functions.
+We can guess a function $f$ with this property by noting that equation~\eqref{eqn:cantilever-thimble-difference} looks like one of the differential equations that characterize the Jacobi elliptic functions.
 
@@
 \[ \frac{1}{2} \left[ \frac{1}{\sqrt{f^4 - \omega^2}} \right] = \frac{du}{df} \]
-when we choose the branch of the square root that evaluates to $i\omega^2$ when $f = 0$.\end{revised} By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
+when we choose the branch of the square root that evaluates to $i\omega^2$ when $f = 0$. By definition, $f\big(\operatorname{end} \mathcal{C}_a^\theta(\zeta)\big) = \zeta$
 so we have
@@
 
-From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd \begin{old}at $a$\end{old} with respect to $u$, implying that
+From our formula for $f$ in terms of $\operatorname{sd}$, we can see that $f$ is odd with respect to $u$, implying that
 \[ \left.\frac{du}{df}\right|_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)} = -\left.\frac{du}{df}\right|_{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,. \]
@@
 confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
-\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -z\begin{revised}i\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big)\end{revised} \right]\;du\,\begin{revised},\end{revised} \]
-\begin{revised}where $\varepsilon = (\omega/2)^{1/2}$ is the convenience constant we introduced earlier. The exponent is doubly periodic, with period lattice~\cite[table~22.4.1]{dlmf}
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -zi\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,, \]
+where $\varepsilon = (\omega/2)^{1/2}$ is the convenience constant we introduced earlier. The exponent is doubly periodic, with period lattice~\cite[table~22.4.1]{dlmf}
 \[ L = \varepsilon^{-1} K\big(\tfrac{1}{\sqrt{2}}\big)\big[\Z + \tfrac{1}{2}(1 + i)\,\Z\big]\,, \]
@@
 \[ K(k) = \int_0^1 \frac{dx}{\sqrt{(1 - x^2)(1 - k^2 x^2)}}\,. \]
-We can therefore take the thimble to be a real submanifold of the torus $\C / L$.\end{revised}
+We can therefore take the thimble to be a real submanifold of the torus $\C / L$.
 %
@@
 \[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
-where $W_1$ is a holomorphic function on \begin{revised}the slit plane\end{revised} $z \notin (-\infty, 0]$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in (-\infty, 0]$.
+where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
 %
@@
 \[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
-where $W_{-1}$ is a holomorphic function \begin{revised}on the slit plane\end{revised} $z \notin [0, \infty)$ which is bounded outside any constant-radius \begin{revised}neighborhood\end{revised} of \begin{revised}the ray\end{revised} $z \in [0, \infty)$.
+where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.
 %
@@
 \end{align*}
-Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a \begin{revised}neighborhood\end{revised} of $\mathcal{J}_{\zeta, 1}$ in the position domain.
+Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
 They give the values of $u$ after lifting to the incoming and outgoing branches of $\mathcal{C}^\theta_1$, respectively.
@@
 \begin{remark}
-The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB \begin{revised}Ansatz\end{revised} for a Schr\"{o}dinger type equation is
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB Ansatz for a Schr\"{o}dinger type equation is
 \begin{equation}

### 2025-10-22 SIGMA/borel-regularity-SIGMA.tex
Make second-round revisions

@@
 \newif\ifhighlightrevs
-\highlightrevsfalse
+\highlightrevstrue
 \ifhighlightrevs
-%%\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
+\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
 \else
-%%\newenvironment{revised}{}{}
+\newenvironment{revised}{}{}
 \fi
@@
 \end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different kind, for example fractional powers of $z$ can appear at the exponent.
-In this paper we will only deal with trans-monomial of the form $e^{-\alpha z}$, for some $\alpha\in\C$.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different \begin{revised}kinds:\end{revised} for example\begin{revised},\end{revised} fractional powers of $z$ can appear \begin{revised}in\end{revised} the \begin{revised}exponential\end{revised}.
+In this paper\begin{revised}, however,\end{revised} we will only deal with \begin{revised}trans-monomials\end{revised} of the form \begin{revised}$e^{-\alpha z}\,\series{\Phi}$ for $\alpha \in \C$\end{revised}.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
 \begin{equation}
@@
 
-You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is the asymptotic expansion of an actual solution.
+You \begin{revised}cannot\end{revised} be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is the asymptotic expansion of an actual solution.
 After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them.
@@
 \begin{enumerate}
-\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is an short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
+\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is \begin{revised}a short\end{revised} way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
 In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.} Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
@@
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, given an ODE, we can set up a classical Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
+In particular, given an ODE, we can set up a \begin{revised}generalized\end{revised} Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
 
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the so-called wall-crossing phenomenon is equivalent to Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
+Indeed, the so-called wall-crossing phenomenon is equivalent to \begin{revised}the\end{revised} Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}.
@@
 confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
-\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ -zi\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,, \]
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ \begin{revised}-z\,i\varepsilon\end{revised} \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,, \]
 where $\varepsilon = (\omega/2)^{1/2}$ is the convenience constant we introduced earlier. The exponent is doubly periodic, with period lattice~\cite[table~22.4.1]{dlmf}
@@
 \begin{remark}
-The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB Ansatz for a Schr\"{o}dinger type equation is
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB Ansatz for a \begin{revised}Schr\"{o}dinger\end{revised} equation is
 \begin{equation}
-\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')dx'\right),
-\end{equation}
-with $S(\eta,x)=\sum_{k\geq -1}S_k(x)\eta^{-k}$. For the Airy-type Schr\"odinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
+\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')\begin{revised}\;dx'\end{revised}\right),
+\end{equation}
+with $S(\eta,x)=\sum_{k\geq -1} S_k(x)\,\eta^{-k}$. For the Airy-type Schr\"odinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
 \[ q = \frac{2}{3}\eta x^{3/2}=\eta\int_0^x (x')^{1/2}\;dx' = \eta\int_{0}^x S_{-1}(x')\;dx'. \]

### 2025-10-24 SIGMA/borel-regularity-SIGMA.tex
Remove to-do items; add a transition

@@
 In Section~\ref{airy-comparison}, we explain how the treatments in \cite[Section 2.2]{lectures-Marino}, \cite[Section 6.14]{diverg-resurg-i}, and \cite[Section 2.2]{kawai-takei} line up with ours.
- \begin{todo}Other treatments of the anharmonic oscillator: \cite{bender-wu}\cite[Appendix B]{aniceto2019primer}\cite[Section 2.5.3]{sternin1995borel}).\end{todo}
 %
@@
 The inequality $\Re(e^{i\theta} z) > \Lambda$ cuts out a half-plane in $T_b^*B^{\otimes n}$, which pulls back to $n$ sector-like regions in $T_b^*B$ of angle $\pi/n$.
-We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centred around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
+We only define $\laplace_{\zeta, \alpha}^\theta \phi$ on one of them: the one centered around the ray $w_b \in e^{-i\theta/n}[0, \infty)$.
 \subsubsection{Change of translation chart}\label{sec:change-translation}
-\begin{todo}[Change $b$ to $\alpha$?
-\textit{V} Did it \textbf{A} Double-check]\end{todo} Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
+Suppose $\zeta$ is a translation chart on $B$, and $\zeta = \alpha$ is an ordinary point.
 Let $\zeta_\alpha$ be the translation chart with $\zeta = \alpha + \zeta_\alpha$.
@@
 \end{proof}
-We now consider a rescale of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+We now consider a \begin{revised}rescaling\end{revised} of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
 The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
@@
 \captionof{figure}{For this figure, we have chosen a value of $\zeta_\alpha$ representing a point on the boundary of the sector $\Omega_\alpha^\varepsilon$.
-This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.
-\begin{todo}[Add $\zeta$ sector picture]\end{todo}}\label{fig:bound-real-part}
+This is a worst-case scenario for inequality~\eqref{eqn:inverse-laplace-exp-bound}, since our assumptions require $\zeta_\alpha$ to represent a point inside $\Omega_\alpha^\varepsilon$.}\label{fig:bound-real-part}
 \end{center}
@@
 However, $\fracderiv{\mu-1}{\zeta}{0}$ and $\tfrac{\partial}{\partial \zeta}$ do not commute~\cite[equation~54]{mladenov2014advanced}.
-Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero~\cite[Section 1.3]{mladenov2014advanced}\cite{podlubny} \begin{todo}[Was there a reason to emphasize that Podlubny is the original source?]\end{todo}.
+Various ordering conventions give various definitions of $\fracderiv{n+\mu}{\zeta}{0} \phi$, which differ by operators that act on the germ of $\phi$ at zero~\cite[Section 1.3]{mladenov2014advanced}\cite{podlubny}.
 We will use the {\em Riemann-Liouville} convention.
@@
 From Lemma~4.3 in~\cite{reg-sing-volterra}, we know that if $\psi_\alpha$ satisfies the equation $\hat{\mathcal{P}}_\alpha\psi_\alpha=0$, then its Laplace transform $\Psi_\alpha:=\laplace_{\zeta,\alpha}^{\theta}\psi_\alpha$ satisfies the equation $\mathcal{P}\Psi_\alpha=0$, as long as the Laplace transform is well-defined.
-\begin{todo}[Transition text]\end{todo}
+
+\begin{revised}We can now pick out some special solutions of the equation $\mathcal{P}\Psi = 0$, which are associated with roots of $P$.
+We will see in Corollary~\ref{re:cor:soln_borel-reg} of Theorem~\ref{re:thm:soln_is_Borel_sum} that these solutions are Borel regular.\end{revised}
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
@@
 \end{proof}
-\begin{todo}[Add flavor text]\end{todo}
 \begin{theorem}[restatement of \ref{thm:soln_is_Borel_sum}]\label{re:thm:soln_is_Borel_sum}
@@
 \end{proof}
-\begin{todo}[Add flavor text]\end{todo}
 \begin{corollary}[restatement of \ref{cor:soln_borel-reg}]\label{re:cor:soln_borel-reg}
@@
 The incoming and outgoing branches lift to $\tfrac{j}{n}\pi - i[0, \infty)$ and $\tfrac{j}{n}\pi + i[0, \infty)$, respectively.
-\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
 
@@
 \end{equation}
-for $|\theta| < \tfrac{\pi}{2}$.
-This formula can be deduced, with a lot of finagling, from formulas 10.32.12 and 10.27.4 of \cite{dlmf}\begin{todo}[\textit{For after v2:} Explain the finagling at least a little bit, maybe in a footnote]\end{todo}.
+for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32.12 and 10.27.4 of \cite{dlmf}.
 \begin{verify}
@@
 %
-\begin{todo}
-\subsubsection{Thimble projection formula}
-In Theorem~\ref{thm:maxim-proof}, we proved a $3/2$-derivative formula to compute the Borel transform of the asymptotics of a thimble integral.
-\end{todo}
 \subsection{Third-degree thimble integrals}\label{sec:deg3}
@@
 The incoming and outgoing branches lift to $\tfrac{\pi}{3} - i[0, \infty)$ and $\tfrac{\pi}{3} + i[0, \infty)$, respectively.
-\begin{todo}[Draw the lifted thimble in the $\phi$ plane?]\end{todo}
 

### 2025-10-24 SIGMA/SIGMA_submission/example.tex
Drop unused environments, commands, and drafts

\RequirePackage{ifpdf}
\ifpdf % We are running pdfTeX in pdf mode
\documentclass[pdftex]{sigma}
\else
\documentclass{sigma}
\fi

%%% !!!uncomment to enumerate the equations throught the sections!!!
%\numberwithin{equation}{section}

%%% !!!uncomment to enumerate the statements throught the sections!!!
%\numberwithin{theorem}{section}
%\numberwithin{proposition}{section}
%\numberwithin{lemma}{section}
%\numberwithin{corollary}{section}
%\numberwithin{definition}{section}
%\numberwithin{example}{section}
%\numberwithin{remark}{section}
%\numberwithin{note}{section}

%%% !!!uncomment to enumerate the statements continuously inside the sections (e.g. Theorem 3.1, Remark 3.2, Lemma 3.3 etc.)!!!
%\newtheorem{Theorem}{Theorem}[section]
%\newtheorem{Corollary}[Theorem]{Corollary}
%\newtheorem{Lemma}[Theorem]{Lemma}
%\newtheorem{Proposition}[Theorem]{Proposition}
% { \theoremstyle{definition}
%\newtheorem{Definition}[Theorem]{Definition}
%\newtheorem{Note}[Theorem]{Note}
%\newtheorem{Example}[Theorem]{Example}
%\newtheorem{Remark}[Theorem]{Remark} }

\numberwithin{equation}{section}

\newtheorem{Theorem}{Theorem}[section]
\newtheorem*{Theorem*}{Theorem}
\newtheorem{Corollary}[Theorem]{Corollary}
\newtheorem{Lemma}[Theorem]{Lemma}
\newtheorem{Proposition}[Theorem]{Proposition}
 { \theoremstyle{definition}
\newtheorem{Definition}[Theorem]{Definition}
\newtheorem{Note}[Theorem]{Note}
\newtheorem{Example}[Theorem]{Example}
\newtheorem{Remark}[Theorem]{Remark} }

\begin{document}

\renewcommand{\PaperNumber}{***}

\FirstPageHeading

\ShortArticleName{Example Article for SIGMA}

\ArticleName{Example Article for SIGMA}

% Names of the authors for the title of the paper
\Author{First Names LASTNAME~$^{\rm a}$ and Second COAUTHOR~$^{\rm b}$}

\AuthorNameForHeading{F.N.~Lastname and S.~Coauthor}

\Address{$^{\rm a)}$~Address of First Author, Country} % Address of First Author
\EmailD{\href{mailto:email@address}{email@address}} % E-mail address of First Author
\URLaddressD{\url{http://www.home.org/~myHome/}} %URL address of First Author

% Address of Second Author
\Address{$^{\rm b)}$~Address of Second Author, Country}
\EmailD{\href{mailto:email@address}{email@address}} % E-mail address of Second Author

% In the case of the same organization, please use the following standard
%\Author{First Names LASTNAME and Second COAUTHOR}
%\AuthoqNameForHeading{F.N. Lastname and S. Coauthor}
%\Address{Address of Author(s), Country}
%\Email{\href{mailto:email@address}{email1@address}, \href{mailto:email@address}{email2@address}}
%\URLaddress{\url{URL1}, \url{URL2})

\ArticleDates{Received ???, in final form ????; Published online ????}

\Abstract{This is an example article for the refereed online open access journal
``Symmetry, Integrability and Geometry: Methods and Applications''.}

\Keywords{?????; ?????; ?????; ?????}
%Please type here List of Keywords for your article separated by semicolon.

\Classification{?????; ?????; ?????} % e.g. 35A30; 81Q05
% For 2020 Mathematics Subject Classification see https://mathscinet.ams.org/mathscinet/msc/msc2020.html

\section{Introduction}

{\it Symmetry, Integrability and Geometry: Methods and Applications}
({\it SIGMA})\footnote{SIGMA is a non-profit, volunteer-run project operated by
scientists from Department of Mathematical Physics,
Institute of Mathematics of National Academy of Sciences of Ukraine,
3 Tereshchenkivs'ka Str., Kyiv-4, 01024 Ukraine,  \url{https://www.imath.kiev.ua/~appmath/}.}
is refereed online open access\footnote{Nevertheless, despite open access, we {\bf do not charge authors for publication}, i.e., SIGMA is no-fee open-access journal.} journal for speedy publication in the following areas:
\begin{itemize}
\itemsep=0pt
\item geometrical methods in mathematical physics;
\item Lie theory and differential equations;
\item  classical and quantum integrable systems;
\item  dynamical systems and chaos;
\item  exactly and quasi-exactly solvable models;
\item Lie groups and algebras, representation theory;
\item  orthogonal polynomials and special functions;
\item  quantum algebras, quantum groups and noncommutative geometry;
\item  supersymmetry and supergravity, strings and branes;
\item  cosmology and quantum gravity.
\end{itemize}

Research papers are considered for publication
if they have not been published previously, and are not under consideration elsewhere.
We would like to remind to the authors that papers are published to be read,
and the authors should compose their works with as wide audience
in mind as is consistent with the maintenance of
scientific quality (we, certainly, mean the qualified audience).
Review papers on recent
developments and comments to the published papers are particularly welcome.
The authors retain ownership of the copyright with respect to their papers published in SIGMA under the terms of the Creative Commons Attribution-ShareAlike License, \url{http://creativecommons.org/licenses/by-sa/4.0/}.

We plan to publish papers online immediately after their
accepting for publication.
{\it The length of an article is not limited.}

Submitting a paper to the journal can be done in two way:
\begin{enumerate}
\itemsep=0pt
\item[--] submit the paper to the \href{https://arxiv.org/}{arXiv} and send archive number to
\href{mailto:editor@sigma-journal.com}{editor@sigma-journal.com} or
\item[--] send zipped paper in TeX/LaTeX format by e-mail directly to
\href{mailto:editor@sigma-journal.com}{editor@sigma-journal.com} (with {\tt pdf-} or {\tt ps-}file).
\end{enumerate}
After accepting the article for publication in SIGMA authors shall prepare the paper
in the \LaTeX2$\epsilon$ format, using the style file
{\bf sigma.cls}, according to the requirements listed below (this is {\bf mandatory}).
The style file {\bf sigma.cls} was created on the basis of the standard style
article. The font size is {\tt 11pt}. The following style packages are used:
{\tt amsthm}, {\tt amsmath}, {\tt latexsym}, {\tt amssymb}, {\tt epsfig}, {\tt graphics}.
Authors can use for preparation of their articles
other standard style packages.

We kindly ask you do not use abbreviations for standard \LaTeX commands!

Please address requests for additional information to \href{mailto:editor@sigma-journal.com}{editor@sigma-journal.com}.

After preparation of the paper for publishing we will send
the author(s) the
{\tt pdf-}file of the paper for final checking that should
be completed in a~week.

\section{Displayed mathematics}

The equations presented in separate lines are to be given by means
of separators {\tt equation} or their versions for numbered
equations and {\tt displaymath} of their versions  for
non-numbered equations. It is not allowed to use \verb_$$ ... $$_
as separators as they do not provide left-side justification
adopted in SIGMA. {\it Only equations referred in the paper
should be numbered}. Equations should be numbered through all the
paper (or by sections). All references to equations are to be
organized by means of the labels:
\begin{equation}
(a+b)^2=a^2+2ab+b^2.\label{eq1}
\end{equation}
The equation~\eqref{eq1} is an example of numbered equation,
and the following gives an example of a non-numbered equation
\[
a^2-b^2=(a-b)(a+b).
\]
Equations set in multiple rows, as e.g.\ equations
\eqref{equation2}, \eqref{equation3}
are to be typeset using separators
{\tt gather}, {\tt gather*}, {\tt split}, {\tt aligned} and similar to them
\begin{gather}
(a+b)\left(a^2-ab+b^2\right)\nonumber\\
\qquad {} =a^3+b^3,\label{equation2}\\
(a-b)\left(a^2+ab+b^2\right)=a^3-b^3.\label{equation3}
\end{gather}

\section{Theorem like environments}

Environments for theorems, lemmas, corollaries, propositions, definitions,
examples, remarks, notes and the like are defined in the {\bf sigma.cls}.\footnote{The numeration can be changed using environments defined in the preamble of this source.}

\begin{Theorem}\label{theorem1}
This is an example of theorem.
\end{Theorem}

\begin{proof}
The text of a proof of the Theorem~\ref{theorem1}.
\end{proof}

\begin{Theorem*}
This is an example of unnumbered theorem.
\end{Theorem*}

\begin{Lemma}\label{lemma1}
This is an example of lemma.
\end{Lemma}

\begin{proof}
Example of particular case proof ends with an equation:
  \begin{equation*}
    a\Longrightarrow b, \qquad b \Longrightarrow c. \tag*{\qed}
  \end{equation*}
  \renewcommand{\qed}{}
\end{proof}

\begin{Corollary}\label{corollary1}
This is an example of corollary.
\end{Corollary}

\begin{Proposition}\label{proposition1}
This is an example of proposition.
\end{Proposition}

\begin{Definition}\label{definition1}
This is an example of definition.
\end{Definition}

\begin{Example}\label{example1}
This is an example.
\end{Example}

\begin{Remark}\label{remark1}
This is an example of remark.
\end{Remark}

\begin{Note}\label{note1}
This is an example of note.
\end{Note}

\section{About figures}

If a paper contains pictures, then it is necessary to submit together with
the paper text the relevant files in the formats {\tt eps}, {\tt pdf}, {\tt jpg}, {\tt bmp}, containing high quality images.
Font size of legends at the pictures should not exceed {\tt 10pt}.
Please use the packages  {\tt graphics} or {\tt epsfig} for incorporation of pictures.

\section{About references}

The references should be presented according to the examples given \cite{Calogero,Harrison2005,KajiwaraK/MasudaT/NoumiM/OhtaY/YamadaY:2006,Olver,Patera,Perelman,Witten};
usage of BibTeX is welcome (see example.bib, sigma.bst).
Note that the full name of the reference cited should be given together with
complete publishing data\footnote{You can use free MathSciNet \url{https://mathscinet.ams.org/mathscinet-mref}, inSPIRE \url{https://inspirehep.net/} tools for creating and verifying references.} and it is not desirable to join a few references as single item. Also we would like to ask you to indicate DOI and arXiv numbers for the reference you cited if they are available.
The order of references should be determined in the alphabetical order.
Every reference given in the bibliography should be cited in the text!
All citations of the references are to be organized by means of
the labels (e.g.~\verb_\cite{Olver1986}_).

\appendix

\section{First appendix}
We kindly ask the authors to give all technical details of paper in the form of Appendices.

\subsection*{Acknowledgements}

The text of acknowledgements to funds, colleagues, referees, etc. should be typed at the end of the paper, before references.

\bibliographystyle{sigma}
%\bibliography{example}

\end{document}

### 2025-10-24 SIGMA/borel-regularity-SIGMA.tex
Drop unused environments, commands, and drafts

@@
 \usepackage[square,numbers,sort,compress]{natbib}
-\usepackage{stmaryrd} %% needed for mapsto arrows in commutative diagrams
-\usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} %% hat tip https://tex.stackexchange.com/a/247819
+\usepackage{stmaryrd} % needed for mapsto arrows in commutative diagrams
+\usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} % hat tip https://tex.stackexchange.com/a/247819
 \usepackage{graphicx}
@@
 \usepackage[svgnames]{xcolor} %% for revisions
-\usepackage{xparse} %% for squiggly underlines
+\usepackage{xparse} %% for squiggly underlines (keep to be safe)
 \usepackage{tikz}
@@
 \newcommand{\maps}{\colon}
-\newcommand{\acts}{\mathbin{\raisebox{\depth}{\rotatebox{-90}{$\circlearrowright$}}}}
 
@@
 \newcommand{\softpart}{\mathcal{V}_\star}
-%%\newcommand{\kerwhole}{k}
 \newcommand{\hardker}{k_0}
-%%\newcommand{\softker}{k_\star}
 \newcommand{\solwhole}{f}
@@
 \newcommand{\fmlsolptb}{\series{f}_\star}
-%%\newcommand{\roots}{\mathfrak{B}}
 \DeclareMathOperator{\var}{var}
-
-%% for the figure
-% colors
-\definecolor{smoked}{RGB}{216, 212, 204}
-\definecolor{mauve}{RGB}{200, 55, 171}
-\definecolor{apricot}{RGB}{250, 144, 4}
-\definecolor{sky}{RGB}{66, 169, 244}
-\definecolor{plum}{RGB}{76, 0, 102}
 
@@
 \newcommand{\blankbox}{{\fboxsep 0pt \colorbox{lightgray}{\phantom{$h$}}}}
-\newcommand{\laplacepde}{\mathcal{D}}
 \newcommand{\van}{\mathfrak{m}}
@@
                      =}
-\newcommand*{\defeqin}{\mathrel{\vcenter{\lineskiplimit0pt\baselineskip0.5ex
-                     \hbox{\scriptsize.}\hbox{\scriptsize.}}}%
-                     =}
-
-%%\let\Re\relax
-%%\DeclareMathOperator{\Re}{Re}
 
@@
 \newcommand{\aexp}{\mathrm{\ae}}
-\newcommand{\deriv}[3]{\partial^{#1}_{#2 \text{ from } #3}}
 
@@
 \newtheorem{lemma}[definition]{Lemma}
-%\newtheorem{conjecture}[definition]{Conjecture}
-\newtheorem{claim}[definition]{Claim}
-%\newtheorem{exercise}[definition]{Exercise}
 \newtheorem*{notation*}{Notation}
@@
 
-% hideable notes for unstable references
-\newif\ifshowunstable
-\showunstablefalse
-\ifshowunstable
-\newenvironment{unstable}{\color{YellowGreen}}{\color{black}}
-\else
-\NewEnviron{unstable}{\iffalse\expandafter\BODY\fi}
-\fi
-\newcommand{\citesection}[1]{\begin{unstable}\texttt{#1}\end{unstable}}
-
-% hideable to-do notes and brainstorming
-\newif\ifshowtodo
-\showtodofalse
-\ifshowtodo
-\newenvironment{todo}{\color{Coral}}{\color{black}}
-\newenvironment{brainstorm}{\color{BlueViolet}\begin{itemize}}{\end{itemize}\color{black}}
-\else
-\NewEnviron{todo}{\iffalse\expandafter\BODY\fi}
-\NewEnviron{brainstorm}{\iffalse\expandafter\BODY\fi}
-\fi
-
-% hideable old text
-\newif\ifshowold
-\showoldfalse
-\ifshowold
-%%\newenvironment{old}{\color{RoyalBlue}}{\color{black}}
-\else
-%%\NewEnviron{old}{\iffalse\expandafter\BODY\fi}
-\fi
-
-% hideable draft text
-\newif\ifshowdraft
-\showdraftfalse
-\ifshowdraft
-%%\newenvironment{draft}{\color{SlateBlue}}{\color{black}}
-\else
-%%\NewEnviron{draft}{\iffalse\expandafter\BODY\fi}
-\fi
-
 % highlightable revisions
@@
 % colors
-\definecolor{ietocean}{RGB}{0, 30, 140}
 \definecolor{ietcoast}{RGB}{0, 150, 173}
-\definecolor{ietlagoon}{RGB}{0, 216, 180}
 
@@
 \setcounter{tocdepth}{2}
+
 % === phase space laplace ===
@@
 Let $\zeta$ be a coordinate on $B$.
-For any integers $m, n$,%%Let $\series{\phi}=\sum_{n=0}^\infty a_n\frac{\zeta^n}{n!}\,, \series{\psi}=\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\in\C\llbracket\zeta\rrbracket$, then
+For any integers $m, n$,
 \begin{equation}\label{eq: convolution_formal}
@@
 \subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
-\begin{brainstorm}
+\begin{itemize}
 \item It's probably not worth updating the convolutions to new notation.
-\end{brainstorm}
+\end{itemize}
 The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
@@
 
-In \citesection{sec:construction} Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
+In Section~3.2.1 of \cite{reg-sing-volterra}, we rewrite the prototype solution in the form
 \[ \solproto(a) = \frac{1}{p(a)} \left(\frac{\zeta_\alpha(a)}{\zeta_\alpha(b)}\right)^{\tau_\alpha} \exp\left[-\int_b^a \left( \frac{q}{p} + \frac{\tau_\alpha}{\zeta_\alpha} \right)\;d\zeta_\alpha\right], \]
@@
 \end{equation}
-%%[DROPPED] In fact, as we will see in Section~\ref{contour-argument-AL}, $K$ is the modified Bessel function $K_{{m/n}}$.
 Let us put equation~\eqref{eqn:mod-bessel-AL} in the form $\mathcal{P}\Phi=0$ with $\mathcal{P}$ as in equation~\eqref{eqn:operator-P}:
@@
 Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
-\begin{align*}%%\label{integral:mod-bessel-rational-zeta}
+\begin{align*}
 K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
@@
 Identity 15.4.16 from \cite{dlmf} implies that
-%% \[ \sinh(\eta_+) = \tfrac{1}{3} \sinh(3\eta_+)\;{}_2 F_1\left(\frac{1}{3}, \frac{2}{3}; \frac{3}{2}; \sin(3\eta_+)^2\right) \]
 \[ \sinh(\eta_+) = \frac{2}{3} \sinh\big(\tfrac{3}{2}\eta_+\big)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right). \]

### 2025-10-24 SIGMA/SIGMA_submission/borel_reg_submission.tex
Start a SIGMA-formatted copy
removed "revised" environment from submission file

--- 2025-10-24 SIGMA/borel-regularity-SIGMA.tex
@@
 
-% highlightable revisions
-\newif\ifhighlightrevs
-\highlightrevstrue
-\ifhighlightrevs
-\newenvironment{revised}{\color{OrangeRed}}{\color{black}}
-\else
-\newenvironment{revised}{}{}
-\fi
-
 % colors
@@
 \end{equation}
-behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different \begin{revised}kinds:\end{revised} for example\begin{revised},\end{revised} fractional powers of $z$ can appear \begin{revised}in\end{revised} the \begin{revised}exponential\end{revised}.
-In this paper\begin{revised}, however,\end{revised} we will only deal with \begin{revised}trans-monomials\end{revised} of the form \begin{revised}$e^{-\alpha z}\,\series{\Phi}$ for $\alpha \in \C$\end{revised}.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
+behave near $z = \infty$, you might start by looking for formal {\em trans-monomial} solutions $e^{-\alpha z}\,\series{\Phi}$, where $\series{\Phi}$ is a formal power series of the kind above.\footnote{Trans-mononials can be of different kinds: for example, fractional powers of $z$ can appear in the exponential.
+In this paper, however, we will only deal with trans-monomials of the form $e^{-\alpha z}\,\series{\Phi}$ for $\alpha \in \C$.} Setting $\alpha = -1$ and $\tau = \tfrac{1}{2}$ gives a well-behaved recurrence relation for $\series{\Phi}$, which produces the solution
 \begin{equation}
@@
 
-You \begin{revised}cannot\end{revised} be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is the asymptotic expansion of an actual solution.
+You cannot be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is the asymptotic expansion of an actual solution.
 After all, $\series{\Phi}$ is asymptotic to many functions; Borel summation simply picks one of them.
@@
 \begin{enumerate}
-\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is \begin{revised}a short\end{revised} way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
+\item Solving a level~$1$ linear ODE \cite[Section 2.1]{EcalleIII}\cite[Section~5.2.2.1]{diverg-resurg-iii}.\footnote{Calling a linear ODE {\em level~$1$} is a short way of saying that it has ``a single level, equal to $1$, at infinity.'' That means a certain Newton polygon associated with its singularity at infinity has exactly one positive-slope side, which has slope~$1$.
 In general, the {\em levels} of a linear ODE at a given singularity are the slopes of the positive-slope sides of the associated Newton polygon~\cite[Proposition~3.3.14]{diverg-resurg--ii}.} Equation~\eqref{eqn:bessel_rescaled_ex} is an example.
@@
 We can therefore use the theory of meromorphic connections to study level~$1$ ODEs.
-In particular, given an ODE, we can set up a \begin{revised}generalized\end{revised} Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
+In particular, given an ODE, we can set up a generalized Riemann--Hilbert problem whose solution would encode a frame of analytic solutions of the ODE~\cite[Section~3.2]{Dubrovin-Heun}.
 
@@
 For instance, in the two-dimensional, $\mathcal{N}=2$ supersymmetric QFTs given by Landau--Ginzburg theories, Cecotti and Vafa showed that instantons can be computed using Picard--Lefschetz formulas.
-Indeed, the so-called wall-crossing phenomenon is equivalent to \begin{revised}the\end{revised} Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
+Indeed, the so-called wall-crossing phenomenon is equivalent to the Stokes phenomenon for thimble integrals~\cite{Cecotti:1992rm}.
 Similarly, in complex Chern--Simons theory, the path integral can be studied by decomposing it into thimble integrals and then arguing as in finite dimension~\cite{gukov-marino-purtrov-resurgence,Witten}.
@@
 \end{proof}
-We now consider a \begin{revised}rescaling\end{revised} of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
+We now consider a rescaling of the translation structure of $B$, expanding displacements by a factor of $\mu \in (0, \infty)$.
 The coordinate $\xi = \mu\zeta$ is a chart for the new translation structure.
@@
 
-\begin{revised}We can now pick out some special solutions of the equation $\mathcal{P}\Psi = 0$, which are associated with roots of $P$.
-We will see in Corollary~\ref{re:cor:soln_borel-reg} of Theorem~\ref{re:thm:soln_is_Borel_sum} that these solutions are Borel regular.\end{revised}
+We can now pick out some special solutions of the equation $\mathcal{P}\Psi = 0$, which are associated with roots of $P$.
+We will see in Corollary~\ref{re:cor:soln_borel-reg} of Theorem~\ref{re:thm:soln_is_Borel_sum} that these solutions are Borel regular.
 \begin{theorem}[restatement of \ref{thm:exist_uniq_ODE}]\label{re:thm:exist_uniq_ODE}
@@
 confirming that our guess for $f$ satisfies equation~\eqref{eqn:cantilever-thimble-difference}. It follows that
-\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[ \begin{revised}-z\,i\varepsilon\end{revised} \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,, \]
+\[ V_\alpha = \int_{\mathcal{C}_a^\theta} \exp\left[-z\,i\varepsilon \operatorname{sd}\big(4\varepsilon u, \tfrac{1}{\sqrt{2}}\big) \right]\;du\,, \]
 where $\varepsilon = (\omega/2)^{1/2}$ is the convenience constant we introduced earlier. The exponent is doubly periodic, with period lattice~\cite[table~22.4.1]{dlmf}
@@
 \begin{remark}
-The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB Ansatz for a \begin{revised}Schr\"{o}dinger\end{revised} equation is
+The new coordinate $q = \frac{2}{3}\eta x^{3/2}$ is carefully chosen. Recall that the WKB Ansatz for a Schr\"{o}dinger equation is
 \begin{equation}
-\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')\begin{revised}\;dx'\end{revised}\right),
+\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')\;dx'\right),
 \end{equation}
@@
 %\bibliographystyle{plain}
-\bibliography{borel-regularity-SIGMA}
+\bibliography{biblio_borel_reg}
 \end{document}

### 2025-10-24 SIGMA/SIGMA_submission/borel_reg_submission.tex
removed "verify" environment from borel-reg-submission

@@
 
-% hideable verifications
-\newif\ifshowverify
-\showverifyfalse
-\ifshowverify
-\newenvironment{verify}{\color{ForestGreen}}{\color{black}}
-\else
-\NewEnviron{verify}{\iffalse\expandafter\BODY\fi}
-\fi
-
 % colors
@@
 \end{equation}
-as \begin{verify}[see \texttt{notes/intro series computation.nb} and \texttt{notes/intro series computation.ipynb}]\end{verify}
+as
 \[ e^{z}\, \frac{1}{2\sqrt{3}}\, \int_{-\infty}^\infty e^{-z t^2/2} \left[ 1 - \frac{\sqrt{3}}{9} t + \frac{5}{72} t^2 - \frac{4\sqrt{3}}{243} t^3 + \frac{385}{31104} t^4 - \frac{7\sqrt{3}}{2187} t^5 + \frac{17017}{6718464} t^6 - \ldots \right] dt \]
@@
 This operator will always have an irregular singularity at $z = \infty$.
-\begin{verify}
-\par
-Turn the ODE into a system: assume 
-\begin{align*}
-P(\lambda) & = P_0 + P_1 \lambda + \ldots + P_d \lambda^d \\
-Q(\lambda) & = Q_0 + Q_1 \lambda + \ldots + Q_{d-1} \lambda^{d-1}
-\end{align*}
-then the ODE $\mathcal{P}\psi=0$ is equivalent to the system 
-    \begin{equation}
-        \frac{d}{dz}Y= B(z) Y 
-    \end{equation}
-    \[
-    B(z)=\begin{pmatrix}
-            0 & 1 & 0 & \ldots & 0 \\
-            0 & 0 & 1 & \ldots & 0 \\
-            \vdots & &\ddots & & 1\\
-            b_{1}(z) & & b_j(z) & \ldots & b_{d-1}(z)
-        \end{pmatrix}, \quad Y=\begin{pmatrix}
-            \psi \\
-            \psi ' \\
-            \vdots \\
-            \psi^{(d-1)}
-        \end{pmatrix}
-    \]
-
- and $b_j(z)=-P_j-\frac{1}{z}Q_j-\frac{R_j(z)}{z^2}$. A formal system of solutions is given by the matrix 
-\begin{equation}
-    Y=\begin{pmatrix}
-       \psi_1 & \psi_2 & \ldots & \psi_d  \\
-       \psi_1' & \psi_2' & \ldots & \psi_d'  \\
-       \vdots & \vdots  & \ldots & \vdots  \\
-       \psi_1^{(d-1)} & \psi_2^{(d-1)} & \ldots & \psi_d^{(d-1)} 
-    \end{pmatrix}, \qquad \psi_j(z)=e^{-\alpha_j z}z^{-\tau_j}\tilde{f}_j
-\end{equation}
-
-To prove that $z=\infty$ is an irregular singular point we change coordinates and set $w=1/z$:
-
- \begin{equation}
-        -w^2 \frac{d}{dw}Y= B(1/w) Y 
-    \end{equation}
-
-and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
-\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
-hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
-\par
-\end{verify}
+%
 We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
@@
 These solutions can be found systematically, using an algorithm described by Poincar\'{e}~\cite{int-irreg}\cite[Proposition~2.2.7, p.~111]{EcalleIII}.
-Poincar\'{e} observes \begin{verify}(Section~3)\end{verify} that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve.
+Poincar\'{e} observes that when $z$ is large, the constant-coefficient equation $P\big(\tfrac{\partial}{\partial z}\big) \Phi = 0$ approximates the equation $\mathcal{P}\Phi = 0$ that we are trying to solve.
 The solutions of this approximate equation are the exponentials $\{e^{-\alpha z} : P(-\alpha) = 0\}$.
@@
 \end{equation}
-\begin{verify}
-\begin{align*}
-\frac{\zeta^m}{m!} \ast_\zeta \frac{\zeta^n}{n} & = \borel_\zeta \left[ \laplace_{\zeta, 0}\left(\frac{\zeta^m}{m!}\right) \laplace_{\zeta, 0} \left(\frac{\zeta^n}{n!}\right) \right] \\
-& = \borel_\zeta[z^{-m-n-2}] \\
-\end{align*}
-\end{verify}
 \begin{definition}\label{def:convolution_formal}
@@
 Similarly, if $z$ is coordinate on the fiber over $\zeta=\alpha$, the Borel transform $\borel_{\zeta_\alpha}$ induces an isomorphism between $\C\llbracket z^{-1}\rrbracket_1$ endowed with the Cauchy product, and $\C\delta+\C\{\zeta_\alpha\}$ endowed with the convolution $\ast_{\zeta_\alpha}$.
-\begin{verify}
-\subsubsection{Compatibility of the convolution product with the geometry}\label{sec:convolution-compatible}
-\begin{itemize}
-\item It's probably not worth updating the convolutions to new notation.
-\end{itemize}
-The convolution product is compatible with the change of translation chart: if $\series{\Phi}, \series{\Psi}\in \C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=b}B$ and let $\series{\psi}:=\borel_{\zeta_b}\series{\Psi}$ and $\series{\phi}:=\borel_{\zeta_b}\series{\Phi}$
-\[\borel_{\zeta_b}(\series{\Psi}\series{\Phi})=\hat{\psi}\ast \hat{\phi}=\int_{0}^{\zeta_b}\hat{\psi}(\zeta_b-\zeta')\hat{\phi}(\zeta')d\zeta'\]
-Furthermore, we can extend the previous definition to trans-series: let $\series{\Phi}, \series{\Psi}\in e^{-z\alpha}\C \llbracket z^{-1} \rrbracket_1$ be series on $T^*_{\zeta=0} B$, we define \[\borel_{\zeta}(\series{\Psi}\series{\Phi})=:\series{\psi}\ast_\alpha\series{\phi}.\]
-Then the sum of $\series{\psi}\ast_\alpha\series{\phi}$ can be explicitly written as 
-\begin{equation}
-    \hat{\psi}\ast_\alpha\hat{\phi}=\int_\alpha^{\zeta}d\zeta' \hat{\psi}(\zeta-\zeta')\hat{\phi}(\zeta')
-\end{equation}
-where $\hat{\phi}$ and $\hat{\psi}$ denote respectively the sum of $\series{\phi}$ and $\series{\psi}$ in a neighborhood of $\zeta=\alpha$.
-
-We also introduce $\delta_\alpha$ as the unit for the product $\ast_\alpha$
-\[\delta_\alpha\ast_\alpha\borel_\zeta(e^{-\alpha z}z^{-n-1}):=\borel_\zeta(1\cdot e^{-\alpha z} z^{-n-1})=\borel_\zeta\laplace_{\zeta,\alpha}\frac{\zeta_\alpha^n}{n!}=\frac{\zeta_\alpha^n}{n!},\]
-where in the last step we used the properties of $\borel_\zeta$ acting on transseries (see Section~\ref{sec:action_transseries}).
-More generally, if $\borel_\zeta\series{\Phi}$ extends to an analytic function $\hat{\phi}\in\singexpalg{\sigma}(\Omega_\alpha)$ for $\sigma>-1$, we deduce that $\delta_\alpha\ast_\alpha\hat{\phi}=\hat{\phi}\ast_\alpha\delta_\alpha=\hat{\phi}$.
-\begin{remark}
-We can express the fractional integrals/derivatives $\fracderiv{\lambda}{\zeta}{\alpha}$ and $\fracderiv{\lambda}{\zeta_\alpha}{0}$ as convolution products, and we will see how the definitions vary depending on the fibers of $T^*B$ in consideration.
-
-We first assume $\Phi=\laplace_{\zeta,\alpha}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_\alpha)$, and assume $z$ is a function on $T^*_{\zeta=0}B$. Then, for every $\lambda\in (-1,\infty)$
-\begin{align*}
-    \borel_\zeta(z^{-\lambda}{\Phi})=\borel_\zeta(z^{-\lambda}\laplace_{\zeta,\alpha}\phi)&=\borel_\zeta(\laplace_{\zeta,\alpha}\partial_{\zeta,\alpha}^{-\lambda}\phi)=\partial_{\zeta,\alpha}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{\alpha}^\zeta (\zeta-t)^{\lambda-1}\phi(t)dt=\borel_\zeta (z^{-\lambda})\ast_\alpha\phi
-\end{align*}
-where we use the identity $\laplace_{\zeta, \alpha}\,\fracderiv{-\lambda}{\zeta}{\alpha} \varphi = z^{-\lambda} \laplace_{\zeta, \alpha} \varphi$, that generalizes properties $(i)$ and $(ii)$ in Proposition~\ref{prop:L-int-op}.
-Hence \[\borel_\zeta (z^{-\lambda})\ast_\alpha\borel_\zeta{\Phi}=\fracderiv{-\lambda}{\zeta}{\alpha}\big[\borel_\zeta\Phi\big].\]
-Then, we study the case when $\Phi$ and $z$ are functions on the fiber over $\zeta=b$, and we assume $\Phi=\laplace_{\zeta_b,0}\phi$ for $\phi\in\singexpalg{\sigma}(\Omega_b)$.
-For every $\lambda\in (-1,\infty)$
-\begin{multline*}
-    \borel_{\zeta_b}\big[z^{-\lambda}\Phi\big]=\borel_{\zeta_b}\big[z^{-\lambda}\laplace_{\zeta_b,0}\phi\big]=\borel_{\zeta_b}\big[\laplace_{\zeta_b,0}\partial_{\zeta_b,0}^{-\lambda}\phi\big]=\partial_{\zeta_b,0}^{-\lambda}\phi=\frac{1}{\Gamma(\lambda)}\int_{0}^{\zeta_b} (\zeta_b-t)^{\lambda-1}\phi(t)dt\\
-    =\borel_{\zeta_b}(z^{-\lambda})\ast\phi
-\end{multline*}
-hence,  \[\partial_{\zeta_b,0}^{-\lambda}\big[\borel_{\zeta_b}\Phi\big]=\borel_{\zeta_b} (z^{-\lambda})\ast\borel_{\zeta_b}{\Phi}.\]
-\end{remark}
-\end{verify}
 %
@@
 \[ \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} = \frac{3m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{m}{2n}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) \]
-\begin{verify}
-\begin{align*}
-\frac{m}{2n}\,\frac{2\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(1+\tfrac{m}{n}\big)} & = \frac{\pi i}{\Gamma\big(1-\tfrac{m}{n}\big)\Gamma\big(\tfrac{m}{n}\big)} \\
-& = \pi i\,\frac{\sin\big(\pi\tfrac{m}{n}\big)}{\pi} \\
-& = i \sin\big(\pi\tfrac{m}{n}\big) \\
-&= \sinh\big(i\pi\tfrac{m}{n}\big)
-\end{align*}
-\end{verify}
 across the branch cut $\mathcal{J}^\theta_{\zeta, \pm 1}$.
@@
 \end{cases} \]
-\begin{verify}
-\begin{align*}
-\zeta & = 1 + \zeta_1 & -\zeta_1 & = 1 - \zeta \\
-\zeta & = -1 + \zeta_{-1} & \zeta_{-1} & = 1 + \zeta
-\end{align*}
-\begin{align*}
-\left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,\zeta_1^{-1/2} \\
-\left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} & = \sqrt{2}\,(-\zeta_{-1})^{-1/2} \\
-& = i\sqrt{2}\,\zeta_{-1}^{-1/2}
-\end{align*}
-\end{verify}
 %
@@
 \end{equation}
-for $|\theta| < \tfrac{\pi}{2}$. This formula can be deduced, with a lot of finagling, from formulas 10.32.12 and 10.27.4 of \cite{dlmf}.
-\begin{verify}
-\par
-From equation~6.22(3) of Watson's \textit{A treatise on the theory of Bessel functions} (1944), p. 181 (the reference in \cite{dlmf}):
-\begin{align*}
-2\pi i \, I_\mu(z) &= \int_{+\infty}^0 e^{z\cosh(-\pi i+a)-\mu(-i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{-\pi}^{\pi} e^{z\cosh(ib)-\mu i b}\,db\\
-& = -\int_{-\infty}^0 e^{z\cosh(-\pi i-a)+\mu(i \pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i \pi  +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db\\
-& = -\int_{-\infty}^0 e^{z\cosh(\pi i+a)+\mu(i\pi +a)}\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)-\mu(i\pi +a)}\,da +\int_{0}^{\pi} e^{z\cosh(ib)}\cosh(i\mu b)\,db.
-\end{align*}
-Hence,
-\begin{align*}
-4 i \sin(\mu \pi) K_\mu(z) & = 2\pi i \big[ I_{-\mu}(z) - I_\mu(z) \big] \\
-& = \int_{-\infty}^0 e^{z\cosh(\pi i+a)}\left[-e^{-\mu(i\pi +a)}+e^{\mu(i\pi +a)}\right]\,da + \int_{0}^{+\infty} e^{z\cosh(\pi i+a)}\left[e^{\mu(i\pi +a)}-e^{-\mu(i\pi +a)}\right]\,da \\
-& = 2\int_{-\infty}^0 e^{z\cosh(\pi i+a)} \sinh\big(\mu(a+i\pi)\big)\,da + 2\int_{0}^{+\infty} e^{z\cosh(\pi i+a)} \sinh(\mu(i\pi+a)\big)\,da.
-\end{align*}
-This simplifies to the integral
-\[ 2 \int_\gamma e^{z\cosh(t)} \sinh(\mu t)\,dt \]
-along the contour $\gamma$ that runs rightward along $i\pi + \R$.
-\par
-\end{verify}
+for $|\theta| < \tfrac{\pi}{2}$.
+This formula can be deduced, with a lot of finagling, from formulas 10.32.12 and 10.27.4 of \cite{dlmf}.
 The integral converges when $z$ is in the right half-plane.
@@
 More generally, for any complex value of $p$, we can put $\mathcal{C}_1^\theta$ on the universal cover $\widetilde{\C^\times}$.
-\begin{verify}
-\begin{align*}
-I_{+}(z,p)&=\frac{1}{2\pi i}\int_{\mathcal{C}_{+}}e^{-z(4u^3-3u)}\, \frac{du}{u^p} &\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\mathcal{C}_{+}}e^{-z(\tfrac{4}{12}\tfrac{t^3}{z}-3 (12 z)^{-1/3}t)}\frac{dt}{t^p} & u=(12 z)^{-\tfrac{1}{3}}t\\
-&=\frac{1}{2\pi i}(12 z)^{(p-1)/3}\int_{z^{1/3}\mathcal{C}_{+}}e^{-\left(\frac{t^3}{3}-(\tfrac{3}{2} z)^{2/3}t\right)}\frac{dt}{t^p} & \\
-&=(12 z)^{(p-1)/3}\mathrm{A}_1((\tfrac{3}{2}z)^{2/3},p)
-\end{align*}  
-\end{verify}
 %
@@
 Their Laplace transforms $V^{(1)}_1 = \laplace_{\zeta, 1} v^{(1)}_1$ and $V^{(1)}_{-1} = \laplace_{\zeta, -1} v^{(1)}_{-1}$ satisfy equation~\eqref{eqn:I}.
-\begin{verify}
-From the result about the Bessel equation, we know there exists two analytic functions $v_1$ and $v_{-1}$ such that $\varphi_1$ and $\varphi_2$ defined by $\partial_z\varphi_1=\laplace_{\zeta,1}v_1$ and $\partial_z\varphi_2=\laplace_{\zeta,-1}v_{-1}$, give a frame of analytic solutions of \eqref{eqn:I}.
-Then we argue as follows:
-\begin{align*}
-    \partial_z\varphi_1&=\laplace_{\zeta,1}v_1\\
-    \varphi_1-\varphi_1(a)&=\int_a^z\int_1^{\infty}e^{-y\zeta} v_1 d\zeta \, dy\\
-    &=\int_1^{\infty}d\zeta\,  v_1 \, \int_a^ze^{-y\zeta}  \, dy\\
-    &=\int_1^{\infty}d\zeta\,  v_1 \, \Big[\frac{e^{-\zeta a}}{\zeta}-\frac{e^{-z\zeta}}{\zeta}\Big]\\
-    &=\laplace_{\zeta,1} \tfrac{v_1}{\zeta}-\Big[\laplace_{\zeta,1}\tfrac{v_1}{\zeta}\Big](a)
-\end{align*}
-\end{verify}
 Notice that $v^{(1)}_1$ belongs to $\singexpalg{-1/2}(\Omega_1)$, has a simple pole at $\zeta_1 = -1$, and has a logarithmic singularity at $\zeta_1 = -2$.
@@
 \end{equation}
-\begin{verify}
-\begin{equation}
-K_{1/3}(z) = -\frac{3}{2}\,p^{-1/2} e^{-zq \frac{1}{2i} \left(\frac{3}{p}\right)^{3/2}}\,I\left(-\frac{1}{2i} \left(\frac{3}{p}\right)^{3/2} \frac{z}{a_3}\right).
-\end{equation}
-\end{verify}
 From this identity, we can see that $I(z)$ satisfies a transformed version of the modified Bessel equation:
@@
 \]
-\begin{verify}
-With
-\begin{align*}
-w & = \frac{r}{a_3}\,z &
-\frac{\partial}{\partial w} & = \frac{a_3}{r} \frac{\partial}{\partial z}
-\end{align*}
-we have
-\[ K_{1/3}(z) = \frac{irp}{\sqrt{3}}\,e^{a_3 qw}\,I(w) \]
-
-Let us rewrite for simplicity $K_{1/3}(z)=\alpha e^{\beta z} I(\gamma z)$, then using that $K_{1/3}$ is a solution of the modified Bessel equation~\eqref{eqn:mod-bessel} we get
-\begin{align*}
-0 &= I''(\gamma z)+\frac{\beta^2-1}{\gamma^2}I(\gamma z)+\frac{2\beta}{\gamma}I'(\gamma z)+\frac{1}{z}\left(\frac{\beta}{\gamma^2}I(\gamma z)+\frac{I'(\gamma z)}{\gamma}\right)-\frac{1}{9\gamma^2}\frac{1}{z^2} I(\gamma z) \\
-0 &= I''(t)+\frac{\beta^2-1}{\gamma^2}I(t)+\frac{2\beta}{\gamma}I'(t)+\frac{1}{t}\left(\frac{\beta}{\gamma}I(t)+I'(t)\right)-\frac{1}{9t^2} I(t)\\
-0 &= I''(t)+\frac{\beta^2}{\gamma^2}I(t)-\frac{1}{\gamma^2}I(t)+\frac{2\beta}{\gamma}I'(t)+\frac{1}{t}\frac{\beta}{\gamma}I(t)+\frac{1}{t}I'(t)-\frac{1}{9t^2} I(t)\\
-0 &= I''(t)+a_3^2q^2 I(t)-\frac{a_3^2}{r^2}I(t)+2a_3 qI'(t)+\frac{a_3 q}{t}I(t)+\frac{1}{t}I'(t)-\frac{1}{9t^2} I(t)
-\end{align*}
-
-Here's a double-check. Since $K_{1/3}(z)$ satisfies the modified Bessel equation~\eqref{eqn:mod-bessel},
-\begin{align*}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K_{1/3}(z) & = 0 \\
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] \frac{irp}{\sqrt{3}}\,e^{a_3 qw}\,I(w) & = 0 \\
-\left[\big(\tfrac{a_3}{r} w\big)^2 \big(\tfrac{r}{a_3} \tfrac{\partial}{\partial w}\big)^2 + \big(\tfrac{a_3}{r} w\big) \tfrac{r}{a_3} \tfrac{\partial}{\partial w} - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r} w\big)^2\big]\right] e^{a_3 qw}\,I(w) & = 0 \\
-\left[w^2\big(\tfrac{\partial}{\partial w}\big)^2 + w \tfrac{\partial}{\partial w} - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] e^{a_3 qw}\,I(w) & = 0 \\
-e^{a_3 qw} \left[w^2 \big(\tfrac{\partial}{\partial w} + a_3 q\big)^2 + w \big(\tfrac{\partial}{\partial w} + a_3 q\big) - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] I(w) & = 0 \\
-\left[w^2 \big[\big(\tfrac{\partial}{\partial w}\big)^2 + 2a_3 q \tfrac{\partial}{\partial w} + (a_3 q)^2\big] + w \big(\tfrac{\partial}{\partial w} + a_3 q\big) - \big[\big(\tfrac{1}{3}\big)^2 + \big(\tfrac{a_3}{r}\big)^2 w^2\big]\right] I(w) & = 0
-\end{align*}
-\end{verify}
-\begin{verify}
-Taking $p$ and $q$ to $0$ in
-\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + 2a_3 q\,\tfrac{\partial}{\partial z} + a_3^2 (q^2 - r^{-2})\big] + z^{-1} \big(a_3 q + \tfrac{\partial}{\partial z}\big) - \tfrac{1}{9} z^{-2} \right] \Phi = 0, \]
-we get
-\[ \left[ \big[\big(\tfrac{\partial}{\partial z}\big)^2 + z^{-1} \tfrac{\partial}{\partial z} - \tfrac{1}{9} z^{-2} \right] \Phi = 0\]
-\end{verify}
-
 \item[] \textbf{One degenerate critical point}
@@
 Setting $q=0$, and using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $a_3$ held constant.
-\begin{verify}
-\begin{align*}
-I(z) & = \frac{\sqrt{3}}{irp} e^{-qrz} K_{1/3}\left(\frac{a_3 z}{r}\right) \\
-& = \frac{\sqrt{3}}{irp} e^{-qrz} \frac{\pi}{2 \sin(\pi/3)} \left[ I_{-1/3}\left(\frac{a_3 z}{r}\right) - I_{1/3}\left(\frac{a_3 z}{r} \right)\right].
-\end{align*}
-We take the lowest-order term, which is the leading term of $I_{-1/3}(a_3 z / r)$:
-\begin{align*}
-I(z) & \approx \frac{\sqrt{3}}{irp} \frac{\pi}{2 \sin(\pi/3)} \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(-\tfrac{1}{3} + 1\big)} \\
-& = \frac{\sqrt{3}}{irp}\;\frac{1}{2}\;\Gamma\big(\tfrac{1}{3}\big)\,\Gamma\big(\tfrac{2}{3}\big) \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
-& = \frac{\sqrt{3}}{irp}\;\frac{1}{2}\;\Gamma\big(\tfrac{1}{3}\big)\,\Gamma\big(\tfrac{2}{3}\big) \left(\frac{a_3 z}{2r}\right)^{-1/3} \frac{1}{\Gamma\big(\tfrac{2}{3}\big)} \\
-& = \frac{\sqrt{3}}{i a_3^{1/3} (2r)^{2/3} p} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3} \\
-& = \frac{\sqrt{3}}{i a_3^{1/3} (2r)^{2/3} p} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3}.
-\end{align*}
-Observing that $(2r)^{2/3} = e^{i(2/3)\pi }\,3/p$, we get
-\begin{align*}
-I(z) & \approx \frac{\sqrt{3}}{i a_3^{1/3}\,3e^{i(2/3)\pi}} \Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3} \\
-& = \frac{1}{i\sqrt{3}} a_3^{-1/3} e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\;z^{-1/3}
-\end{align*}
-\end{verify}
 %
@@
 where $z$ is the distance from the tip along the strip's axis.\footnote{To keep the equation simple, we have adjusted the units of time so that the strip's elasticity, density, and taper are absorbed into the frequency parameter.}
-
-\begin{verify}
-The vertical displacement of a vibrating beam is annihilated by the operator
-\[ \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 + m \big(\tfrac{\partial}{\partial t}\big)^2, \]
-as described in equation~12.58 of \cite{genta2009vibration}.
-Here, $m$ is the mass per unit length, $E$ is the elastic modulus, and $I_\text{roll}$ is the second moment of area about the axis the beam ``rolls'' around as it vibrates.
-We can write the displacement as $\cos(\omega t)$ times a time-independent envelope, which is annihilated by the operator
-\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ EI_\text{roll} \circ \big(\tfrac{\partial}{\partial z}\big)^2 - m\omega^2. \]
-We are assuming the cantilever has a rectangular cross-section with half-width $s$ and half-thickness $t$, so its second moment of area about the side-to-side axis is $\tfrac{4}{3}st^3$, mass per unit length is a scalar multiple of $st$, giving
-\[ \mathcal{P} = \big(\tfrac{\partial}{\partial z}\big)^2 \circ \tfrac{4}{3}Et^3 s \circ \big(\tfrac{\partial}{\partial z}\big)^2 - t\omega^2 s. \]
-For the triangular cantilever, $t$ is constant, and $s = \sigma z$ for some constant $\sigma$. Letting $c_1 = \tfrac{4}{3}\sigma Et^3$ and $c_2 = t\sigma\omega^2$, we have
-\begin{align*}
-\mathcal{P} & = \big(\tfrac{\partial}{\partial z}\big)^2 \circ c_1 z \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
-& = c_1 \tfrac{\partial}{\partial z} \circ \big[ 1 + z \tfrac{\partial}{\partial z} \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
-& = c_1 \circ \big[ \tfrac{\partial}{\partial z} + \tfrac{\partial}{\partial z} + z \big(\tfrac{\partial}{\partial z}\big)^2 \big] \circ \big(\tfrac{\partial}{\partial z}\big)^2 - c_2 z \\
-& = c_1 2\big(\tfrac{\partial}{\partial z}\big)^3 + c_1 z \big(\tfrac{\partial}{\partial z}\big)^4 - c_2 z \\
-\tfrac{1}{c_1 z} \mathcal{P} & = \tfrac{2}{z} \big(\tfrac{\partial}{\partial z}\big)^3 + \big(\tfrac{\partial}{\partial z}\big)^4 - \tfrac{c_2}{c_1}.
-\end{align*}
-Now, set $\mu = \tfrac{c_2}{c_1} = \tfrac{3}{4} \tfrac{1}{E} \big(\tfrac{\omega}{t}\big)^2$.
-This example works because the linear density of the beam and the second moment of area about the side-to-side axis are proportional, so they both end up in the $P(\partial/\partial z)$ term.\par
-\end{verify}
+%
 \subsubsection{Solving the differential equation}\label{sec:solve-cantilever-eqn}
@@
 satisfies the equation
-\begin{verify}
-\[ \frac{1}{\sqrt{\big(1 - \tfrac{1}{2} x^2\big)\big(1 + \tfrac{1}{2} x^2\big)}} = \frac{dt}{dx} \]
-\end{verify}
 \[ \frac{1}{\sqrt{1 - \tfrac{1}{4} x^4}} = \frac{dt}{dx}\,. \]
@@
 with the branch of the square root determined by analytic continuation along $\mathcal{C}_a^\theta$ from $a$.
-
-\begin{verify}
-To verify the guess for $f$, set $f = i \varepsilon x$ and $t = 4 \varepsilon u$ in the differential equation satisfied by $x = \operatorname{sd}(t, \tfrac{1}{\sqrt{2}})$. We get
-\begin{align*}
-\frac{1}{\sqrt{1 - \tfrac{1}{4} (i\varepsilon)^{-4} f^4}} & = \frac{4 \varepsilon\,du}{(i\varepsilon)^{-1}\,df} \\
-\frac{1}{4i \varepsilon^2 \sqrt{1 - \tfrac{1}{4} \varepsilon^{-4} f^4}} & = \frac{du}{df} \\
-\frac{1}{2i\sqrt{4\varepsilon^4 - f^4}} & = \frac{du}{df} \\
-\frac{1}{2} \left[ \frac{1}{\sqrt{f^4 - 4\varepsilon^4}} \right] & = \frac{du}{df}\,,
-\end{align*}
-where in the last step we choose the branch of the square root that evaluates to $2i\varepsilon^2$ when $f = 0$.
-\end{verify}
 
@@
 Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get
-\begin{verify}
-\begin{align*}
-K(z) & = \frac{3}{2 \sinh\big(\tfrac{1}{3}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]
-\end{align*}
-\end{verify}
 \begin{align*}
@@
 \end{align*}
-\begin{verify}
-\begin{align*}
--2 \sin\big(\tfrac{\pi}{3}\big) \sin(-i\eta_+) & = -2 \tfrac{\sqrt{3}}{2}\;i\sinh(-\eta_+) \\
-& = -i\sqrt{3}\,\sinh(-\eta_+).
-\end{align*}
-\end{verify}
 Identity 15.4.16 from \cite{dlmf} implies that
@@
 \[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right), \]
-\begin{verify}
-\begin{align*}
-\int_{\mathcal{C}_1^\theta(\zeta)} du & = \frac{2i}{\sqrt{3}} \sinh\left(\frac{3}{2}\eta_+\right)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right) \\
-& = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right).
-\end{align*}
-\end{verify}
 It follows, through identity~15.5.4 from \cite{dlmf}, that

### 2025-10-24 SIGMA/SIGMA_submission/borel_reg_submission.tex
Added SIGMA template, replaced align* with equation* and split, check the spacing at the end, hide our hyperref, hide packages already in sigma.cls, add their theorem style and replace prop with Proposition

@@
-\documentclass{article}
+\RequirePackage{ifpdf}
+\ifpdf % We are running pdfTeX in pdf mode
+\documentclass[pdftex]{sigma}
+\else
+\documentclass{sigma}
+\fi
 
@@
 \usepackage[hmargin=1.5in]{geometry}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{amsthm}
 \usepackage[square,numbers,sort,compress]{natbib}
@@
 \usepackage[scr=boondoxo, scrscaled=1.05]{mathalpha} % hat tip https://tex.stackexchange.com/a/247819
-\usepackage{graphicx}
+%\usepackage{graphicx}
 \usepackage{fancyhdr}
@@
 \usepackage{rotating} % for \isoarrow
-\usepackage{environ} % to hide verifications and stuff
 
@@
 
-% theorem environments
-\theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{remark}[definition]{Remark}
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
-\newtheorem{prop}[definition]{Proposition}
-\newtheorem{corollary}[theorem]{Corollary}
-\newtheorem{lemma}[definition]{Lemma}
+% % theorem environments
+% \theoremstyle{definition}
+% \newtheorem{definition}{Definition}[section]
+% \newtheorem{remark}[definition]{Remark}
+%\theoremstyle{plain}
+% \newtheorem{theorem}{Theorem}[section]
+% \newtheorem{prop}[definition]{Proposition}
+% \newtheorem{corollary}[theorem]{Corollary}
+% \newtheorem{lemma}[definition]{Lemma}
+% \newtheorem*{notation*}{Notation}
+% \newtheorem{notation}{Notation}
+\renewcommand{\PaperNumber}{103}
+
+% colors
+\definecolor{ietcoast}{RGB}{0, 150, 173}
+
+% pretty prince hyperref must always be the last thing in the preamble, always
+% \usepackage{hyperref}
+% \hypersetup{
+%   colorlinks,
+%   linkcolor={ietcoast},
+%   citecolor={ietcoast},
+%   urlcolor={ietcoast}
+% }
+
+\numberwithin{equation}{section}
+
+\newtheorem{Theorem}{Theorem}[section]
+\newtheorem{Corollary}[Theorem]{Corollary}
+\newtheorem{Lemma}[Theorem]{Lemma}
+\newtheorem{Proposition}[Theorem]{Proposition}
+ { \theoremstyle{definition}
+\newtheorem{Definition}[Theorem]{Definition}
+\newtheorem{Note}[Theorem]{Note}
+\newtheorem{Example}[Theorem]{Example}
+\newtheorem{Remark}[Theorem]{Remark} }
 \newtheorem*{notation*}{Notation}
@@
 
-% colors
-\definecolor{ietcoast}{RGB}{0, 150, 173}
-
-% pretty prince hyperref must always be the last thing in the preamble, always
-\usepackage{hyperref}
-\hypersetup{
-  colorlinks,
-  linkcolor={ietcoast},
-  citecolor={ietcoast},
-  urlcolor={ietcoast}
-}
-
-\setcounter{tocdepth}{2}
+%\setcounter{tocdepth}{2}
 
@@
 
-\title{The regularity of ODEs and thimble integrals \\
-with respect to Borel summation}
-\author{Veronica Fantini and Aaron Fenyes}
-\date{}
-
 \begin{document}
 
-\maketitle
-
-\begin{abstract}
-Through Borel summation, one can often reconstruct an analytic solution of a problem from its asymptotic expansion.
+\FirstPageHeading
+
+\ShortArticleName{The regularity of ODEs and thimble integrals with respect to Borel summation}
+
+\ArticleName{The regularity of ODEs and thimble integrals with respect to Borel summation}
+
+% Names of the authors for the title of the paper
+\Author{Veronica FANTINI~$^{\rm a}$ and Aaron FENYES~$^{\rm b}$}
+
+\AuthorNameForHeading{V.~Fantini and A.~Fenyes}
+
+\Address{$^{\rm a)}$~Laboratoire Mathématique d'Orsay, France} % Address of First Author
+\EmailD{\href{mailto:veronica.fantini@universite-paris-saclay.fr}{veronica.fantini@universite-paris-saclay.fr}} % E-mail address of First Author
+\URLaddressD{\url{https://sites.google.com/view/vfantini/home-page}} %URL address of First Author
+
+% Address of Second Author
+\Address{$^{\rm b)}$~Address of Second Author, Country}
+\EmailD{\href{mailto:email@address}{email@address}} % E-mail address of Second Author
+
+% In the case of the same organization, please use the following standard
+%\Author{First Names LASTNAME and Second COAUTHOR}
+%\AuthoqNameForHeading{F.N. Lastname and S. Coauthor}
+%\Address{Address of Author(s), Country}
+%\Email{\href{mailto:email@address}{email1@address}, \href{mailto:email@address}{email2@address}}
+%\URLaddress{\url{URL1}, \url{URL2})
+
+\ArticleDates{Received ???, in final form ????; Published online ????}
+
+\Abstract{Through Borel summation, one can often reconstruct an analytic solution of a problem from its asymptotic expansion.
 We view the effectiveness of Borel summation as a regularity property of the solution, and we show that the solutions of certain differential equation and integration problems are regular in this sense.
@@
 The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over one-dimensional Lefschetz thimbles.
-To expand the variety of examples available in the literature, we treat various examples of these problems in detail.
-\end{abstract}
-\tableofcontents
+To expand the variety of examples available in the literature, we treat various examples of these problems in detail.}
+
+\Keywords{Borel summation; Laplace transform; Borel transform; resurgence; translation surfaces; thimble integrals; ordinary differential equations; irregular singularities; divergent series; asymptotics; Stokes phenomena; Stokes constants; Airy function; Airy-Lucas function; generalized Airy function; modified Bessel equation; triangular cantilever}
+%Please type here List of Keywords for your article separated by semicolon.
+
+\Classification{30B10; 30B40; 34M03; 40G10} % e.g. 35A30; 81Q05
+% For 2020 Mathematics Subject Classification see https://mathscinet.ams.org/mathscinet/msc/msc2020.html
+
 %
@@
 At an ordinary point, we can define $z$ simply as the map
-\begin{align*}
+\begin{equation*}
+\begin{split}
 z \maps T^*_bB & \to \C \\
 \lambda\big|_b & \mapsto 1.
-\end{align*}
+\end{split}
+\end{equation*}
 To generalize $z$ to branch points, though, we need a more sophisticated definition.
@@
 We define $z$ as the isomorphism
-\begin{align*}
+\begin{equation*}\begin{split}
 z \maps \van_b^n / \van_b^{n+1} & \to \C \\
 \zeta_b + \van^{n+1} & \mapsto 1.
-\end{align*}
+\end{split}\end{equation*}
 When $b$ is a branch point, the coordinate $\omega_b$ we fixed in ``A sense of direction'' gives us an isomorphism
-\begin{align*}
+\begin{equation*}\begin{split}
 w_b \maps T^*_bB & \to \C \\
 \omega_b + \van^2 & \mapsto 1
-\end{align*}
+\end{split}\end{equation*}
 that makes the diagram
@@
 With a change of variable in the integral that defines the Laplace transform, we see that
-\begin{align*}
+\begin{equation*}\begin{split}
 \laplace_{\zeta, \alpha} \varphi & = \int_{\mathcal{J}_{\zeta,\alpha}} e^{-z \zeta}\,\varphi\;d\zeta \\
@@
 & = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi.
-\end{align*}
+\end{split}\end{equation*}
 \end{proof}
@@
     From the computation 
-    \begin{align*}
+    \begin{equation*}\begin{split}
 \laplace_{\xi, 0} \varphi & = \int_{\mathcal{J}_{\xi, 0}} e^{-x\xi}\,\varphi\;d\xi \\
@@
 & = \mu\,\laplace_{\zeta, 0} \varphi
-\end{align*}
+\end{split}\end{equation*}
 we get the desired result. 
@@
 %
-\begin{prop}[Following~\cite{sternin1995borel}]\label{prop:laplace-cont}
+\begin{Proposition}[Following~\cite{sternin1995borel}]\label{prop:laplace-cont}
 Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less.
 For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
-\end{prop}
+\end{Proposition}
 \begin{proof}
 Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
-\begin{align*}
+\begin{equation*}\begin{split}
 |\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
@@
 & \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
-\end{align*}
+\end{split}\end{equation*}
 where $c_{z, \theta} = \cos\big(\arg(z) + \theta\big)$.
@@
 It follows that
-\begin{align*}
+\begin{equation*}\begin{split}
 |\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
 & = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
-\end{align*}
+\end{split}\end{equation*}
 The integral on the last line converges throughout $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \end{proof}
-\begin{prop}\label{prop:inverse_laplace_analytic}
+\begin{Proposition}\label{prop:inverse_laplace_analytic}
 Let $\Omega_\alpha$ be an open sector with tip $\zeta = \alpha$ and opening angle $\Theta \le \pi$.
@@
 Here, $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ is the open sector created by cutting a sector of angle $\varepsilon$ off each edge of $\Omega_\alpha$.
-\end{prop}
+\end{Proposition}
 \begin{proof}
@@
 When $\Phi$ is in $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound
-\begin{align*}
+\begin{equation*}\begin{split}
 \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le \frac{1}{2 \pi} \int_{\mathcal{C}} e^{\Re(z\zeta_\alpha)} \Delta^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dz \\
@@
 & = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
-\end{align*}
+\end{split}\end{equation*}
 which we can rewrite as
-\begin{align*}
+\begin{equation*}\begin{split}
 \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| & \le e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \,|s|}\,|s|^{-\sigma}\,\frac{ds}{\sin(\varepsilon/2)} \\
 & = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{\pi\,\sin(\varepsilon/2)} \int_0^\infty e^{-|\zeta_\alpha|s}\,s^{-\sigma}\,ds
-\end{align*}
+\end{split}\end{equation*}
 using the new parameter $s = \sin(\varepsilon/2)\,t$.
@@
 and it extends to formal power series by countable linearity:
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
 \sum_{n \ge 0} a_n z^{-n-1} & \mapsto \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}.
-\end{align*}
+\end{split}\end{equation*}
 This definition extends straightforwardly to fractional powers of $z$. Observing that   
@@
 for every $\sigma \in \R \setminus \Z_{\leq 0}$, we define 
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_\zeta[z^{-\sigma-1}] \defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)}.
-\end{align*}
+\end{split}\end{equation*}
 Then, for any $\sigma \in \R \setminus \Z_{\leq 0}$, we can extend by countable linearity to the space $z^{-\sigma}\C\llbracket z^{-1}\rrbracket$ of ``fractionally shifted'' formal power series.
@@
 From this definition, and identity~\eqref{change-chart}, we deduce that
-\begin{align*}
+\begin{equation*}\begin{split}
 e^{-z\alpha}\laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-z\alpha} z^{-n-1}\big] & = e^{-z\alpha} z^{-n-1} \\
@@
 \borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
-\end{align*}
+\end{split}\end{equation*}
 In other words, the diagram 
@@
 is the formal inverse of $\laplace_{\zeta_\alpha,0}$ on the cotangent fibre over $\alpha$. Thus, taking the Borel transform on both side of the identity~\eqref{change-chart} we find
-  \begin{align*}
+  \begin{equation*}\begin{split}
       \borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]&=\borel_{\zeta_\alpha}\laplace_{\zeta_\alpha,0}\big[\zeta^n\big]\\
@@
       &=\zeta^n.
-  \end{align*}
+  \end{split}\end{equation*}
 \end{proof}
@@
 where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path $[0, 1] \to B^2$ given by
-\begin{align*}
+\begin{equation*}\begin{split}
 \zeta_\alpha(a) & = t\zeta_{\alpha+\beta} \\
 \zeta_\beta(a') & = (1-t)\zeta_{\alpha+\beta}
-\end{align*}
+\end{split}\end{equation*}
 in terms of the standard coordinate $t$ on $[0, 1]$.
@@
 From Definition~\ref{def:convolution}, we get the bound
-\begin{align*}
+\begin{equation*}\begin{split}
 \left|\phi\ast_{\zeta,\alpha,\beta}\psi\right|&\le\int_{\mathcal{S}_{\zeta,\alpha,\beta}} |\phi(a)|\,|\psi(a')|\,|d\zeta(a)| \\
 & = \int_0^1|\phi(a)|\,|\psi(a')|\,|\zeta_{\alpha+\beta}|\,dt\,,
-\end{align*}
+\end{split}\end{equation*}
 using the fact that $d\zeta(a)=d\zeta_\alpha(a)=d(t\zeta_{\alpha+\beta})=\zeta_{\alpha+\beta}\,dt$ in the second step. We can then bound the right-hand side in terms of the norms of $\phi$ and $\psi$:
-\begin{align*}
+\begin{equation*}\begin{split}
 |\zeta_{\alpha+\beta}|\int_0^1 |\phi(a)|\,|\psi(a')|\,dt &\le \|\phi\|_{\sigma,\Lambda} \|\psi\|_{\sigma',\Lambda'} |\zeta_{\alpha+\beta}|\int_0^1  |\zeta_\alpha(a)|^{\sigma}e^{\Lambda  |\zeta_{\alpha}(a)|}\,|\zeta_\beta(a')|^{\sigma'}e^{\Lambda' |\zeta_{\beta}(a')|}\,dt\\
@@
 &\lesssim |\zeta_{\alpha+\beta}| ^{1+\sigma+\sigma'} e^{(\Lambda+\Lambda')|\zeta_{\alpha+\beta}|}\,.
-\end{align*}
+\end{split}\end{equation*}
 \end{proof}
 The product of two Laplace transforms based at different points is the Laplace transform of a convolution.
-\begin{prop}
+\begin{Proposition}
 For any $\phi\in\singexp{\sigma}{\Lambda}(\Omega_\alpha)$ and $\psi\in\singexp{\sigma'}{\Lambda'}(\Omega_\beta)$ with $\sigma,\sigma'\in (-1,\infty)$, we have
@@
 \end{equation}    
-\end{prop}
+\end{Proposition}
 More generally, this proposition holds for any holomorphic functions $\phi$ and $\psi$ for which the convolution and all of the Laplace transforms in equation~\eqref{eqn:gen-laplace-convol} are well-defined.
@@
 The left-hand side of equation~\eqref{eqn:gen-laplace-convol} expands to
-\begin{align*}
+\begin{equation*}\begin{split}
 \laplace_{\zeta,\alpha,\beta}[\phi \ast_{\zeta,\alpha, \beta} \psi] &= \int_{\mathcal{J}_{\zeta, \alpha+\beta}} d\zeta\,e^{-z\zeta}\int_{\mathcal{S}_{\zeta,\alpha,\beta}} \phi(a)\,\psi(a')\, d\zeta(a)\,.
-\end{align*}
+\end{split}\end{equation*}
 where $\mathcal{S}_{\zeta, \alpha, \beta}$ is the path described in Definition~\ref{def:convolution}. On this path, the equation
@@
 The coordinates $\zeta_\alpha(a)$, $\zeta_\beta(a')$, $\zeta_{\alpha+\beta}$ parameterize $B^3$, and the real wedge $\mathcal{N}_{\zeta, \alpha, \beta}$ is cut out by equation~\eqref{eq:slice-plane} and the conditions
-\begin{align*}
+\begin{equation*}\begin{split}
 a & \in \mathcal{J}_{\zeta, \alpha} \\
@@
 \zeta_{\alpha+\beta} & \in [0, \infty)\,.
-\end{align*}
+\end{split}\end{equation*}
 Equation~\eqref{eq:slice-plane} can be rewritten as $\zeta(a) + \zeta(a') = \zeta$, which implies the identities
-\begin{align*}
+\begin{equation*}\begin{split}
 d\zeta(a) + d\zeta(a') & = d\zeta \\
@@
 d\zeta(a) \wedge d\zeta(a') & = d\zeta(a) \wedge d\zeta\,.
-\end{align*}
+\end{split}\end{equation*}
 We can substitute the last identity into the integral over $\mathcal{N}_{\zeta, \alpha, \beta}$ to get
-\begin{align*}
+\begin{equation*}\begin{split}
 \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
 & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].
-\end{align*}
+\end{split}\end{equation*}
 Thinking of $\mathcal{N}_{\zeta, \alpha, \beta}$ as the graph of $\zeta_\alpha(a) + \zeta_\beta(a')$ over the quadrant $\mathcal{J}_{\zeta, \alpha} \times \mathcal{J}_{\zeta, \beta}$, we can use Fubini's theorem to express the integral as the product
@@
 We extend the convolution product $\ast_\zeta$ by countable linearity to the whole ring of formal power series $\C\llbracket\zeta\rrbracket$:
-\begin{align*}
+\begin{equation*}
    \left( \sum_{n=0}^\infty a_n \frac{\zeta^n}{n!}\right)\ast_\zeta\left(\sum_{n=0}^\infty b_n\frac{\zeta^n}{n!}\right)=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\left[\frac{\zeta^j}{j!}\ast_\zeta\frac{\zeta^{n-j}}{(n-j)!}\right]=\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n+1}}{(n+1)!}\,.
-\end{align*}
+\end{equation*}
 Furthermore, we define the convolution product of $\delta$ with monomials: \[\delta\ast_\zeta\frac{\zeta^n}{n!}\defeq\frac{\zeta^n}{n!}\,,\]
@@
 We can show that $\borel_\zeta$ is an algebra homomorphism from $\C\llbracket z^{-1}\rrbracket$ endowed with the Cauchy product to $\C\delta+\C\llbracket\zeta\rrbracket$ endowed with the convolution product.
-\begin{prop}
+\begin{Proposition}
 Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$. The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
 \[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
-\end{prop}
+\end{Proposition}
 \begin{proof}
     We assume $\series{\Phi}=\sum_{n=0}^\infty a_nz^{-n}$ and $\series{\Psi}=\sum_{n=0}^\infty b_nz^{-n}$. Then,
-    \begin{align*}
+    \begin{equation*}
+    \begin{split}
 \borel_\zeta(\series{\Phi}\series{\Psi})&=\borel_\zeta\left(\sum_{n=0}^\infty\sum_{j=0}^na_jb_{n-j}z^{-n}\right)\\
 &=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
+&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\\
+&\quad +\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
 &=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
 &=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.
-\end{align*}
+\end{split}
+\end{equation*}
 \end{proof}
@@
 \end{definition}
-\begin{prop}\label{prop:gevrey_to_convergent}
+\begin{Proposition}\label{prop:gevrey_to_convergent}
 A series
@@
 is $1$-Gevrey if and only if its Borel transform $\series{\phi} = \borel_\zeta \series{\Phi}$ is convergent.
-\end{prop}
+\end{Proposition}
 \begin{proof}
@@
 From this, we can deduce that $|z|/\Delta$ goes to a constant limit as $z \to \infty$ along any ray that intersects $\widehat{\Omega}_0^\Lambda$.\footnote{The constant limit is not uniform over all rays, so we are showing that $\Phi$ is asymptotic, but not necessarily uniformly asymptotic, to $\series{\Phi}$.} We then reason that
-\begin{align*}
+\begin{equation*}\begin{split}
 |z^{\rho+n} E_n| & \lesssim |z|^{\rho+n} \Delta^{-\rho-n-1} \\
@@
 & \lesssim \Delta^{-1}
-\end{align*}
+\end{split}\end{equation*}
 along any ray that intersects $\widehat{\Omega}_0^\Lambda$. This, as discussed above, proves the desired result.
@@
 The fractional integral obeys the semigroup law \cite[Section  1.3]{mladenov2014advanced}
-\begin{align*}
+\begin{equation*}\begin{split}
 \fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0),
-\end{align*}
+\end{split}\end{equation*}
 and agrees with ordinary repeated integration when $\nu$ is an integer~\cite[equation~35]{mladenov2014advanced}.
@@
 This extends the semigroup law:
-\begin{align*}
+\begin{equation*}\begin{split}
 \fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
-\end{align*}
-\begin{prop}\label{prop:L-int-op}
+\end{split}\end{equation*}
+\begin{Proposition}\label{prop:L-int-op}
 For any $\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and $\Lambda>0$, we have
@@
 \end{enumerate}
-\end{prop}
+\end{Proposition}
 \begin{proof}
 Results \ref{res:frac-deriv} and \ref{res:frac-int} follow from the properties of the Laplace transform with respect to the convolution product. For every $\tau \in (-\infty, 0) \cup (0,1)$,
-\begin{align*}
+\begin{equation*}\begin{split}
 z^\tau\laplace_{\zeta,0}\phi&=\laplace_{\zeta,0}\left[\frac{\zeta^{-\tau-1}}{\Gamma(-\tau)}\right] \laplace_{\zeta,0}\phi\\
@@
 &=\laplace_{\zeta,0}\big[\fracderiv{\tau}{\zeta}{0}\phi\big],
-\end{align*}
+\end{split}\end{equation*}
 where $\mathcal{S}_{\zeta,0}$ is the line segment from $\zeta(a)=0$ to $\zeta(a) = \zeta$.
 Result~\ref{res:whole-deriv} is proven by repeated integration by parts, with the condition on $\phi^{(0)}, \phi^{(1)}, \ldots \phi^{(n)}$ ensuring that the boundary terms vanish:
-\begin{align*}
+\begin{equation*}\begin{split}
     z^n\laplace_{\zeta,0}\phi&=\int_0^\infty e^{-z\zeta} z^n \phi \, d\zeta\\
@@
     &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
-\end{align*}
+\end{split}\end{equation*}
 Result~\ref{res:monom-mult} is also proven by repeated integration by parts, with the assumption that $\zeta^n\phi\in\singexp{\sigma}{\Lambda}(\Omega)$ ensuring that the integral converges.
@@
 First, evaluate
-\begin{align*}
+\begin{equation*}\begin{split}
 \partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{1}{\Gamma(1-\mu)} \int_0^\zeta \big(\zeta-\zeta(a)\big)^{-\mu} \frac{\zeta(a)^k}{\Gamma(k+1)}\,d\zeta(a) \\
@@
 & = \frac{\zeta^{k-(\mu-1)}}{\Gamma\big(k-(\mu-1)+1\big)}
-\end{align*}
+\end{split}\end{equation*}
 by reducing the integral to Euler's beta function~\cite[identity 5.12.1]{dlmf}. This establishes that
@@
 for $n = -1$. If \eqref{frac-diff-laplace} holds for $n = m$, it also holds for $n = m+1$, because
-\begin{align*}
+\begin{equation*}\begin{split}
 \tfrac{\partial}{\partial \zeta} \big(\tfrac{\partial}{\partial \zeta}\big)^{m+1}\,\partial^{\mu-1}_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] & = \frac{\partial}{\partial \zeta} \left( \frac{\zeta^{k-(m+\mu)}}{\big(k-(m+\mu)\big)\,\Gamma\big(k-(m+\mu)\big)} \right) \\
 & = \frac{\zeta^{k-(m+1+\mu)}}{\Gamma\big(k-(m+\mu)\big)}
-\end{align*}
+\end{split}\end{equation*}
 Hence, \eqref{frac-diff-laplace} holds for all $n \ge -1$, and the desired result quickly follows.
@@
 We can now prove the properties of the Borel transform analogous to the one of the Laplace transform from Proposition~\ref{prop:L-int-op}.
-\begin{prop}\label{prop:frac-der-int-borel}
+\begin{Proposition}\label{prop:frac-der-int-borel}
 For any $1$-Gevrey series $\series{\Phi}\in\C\llbracket z^{-1}\rrbracket_1$, we have
@@
 \end{enumerate} 
-\end{prop}
+\end{Proposition}
 \begin{proof} 
@@
 Then, given a series $\series{\Phi} = \sum_{n\geq 0} a_n z^{-n}$, we compute
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_\zeta \big[z^\lambda \series{\Phi}\big] & = \sum_{n\geq 0}a_n\frac{\zeta^{n-\lambda}}{\Gamma(n-\lambda+1)} \\
@@
 & = \fracderiv{\lambda}{\zeta}{0}\series{\Phi}.
-\end{align*}
+\end{split}\end{equation*}
 using the fact that $\borel_\zeta\series{\Phi}$ is convergent in the last step.
@@
 Finally, result~\ref{res:whole-deriv-borel} follows from a simple computation: 
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_\zeta\big[\partial_z^k\series{\Phi}\big]&=\borel_\zeta\left[\sum_{n=k+1}^\infty a_n \frac{(n+k-1)!}{(n-1)!} (-1)^{k} z^{-n-k}\right]\\
@@
 &=(-\zeta)^k\borel_\zeta \series{\Phi}.
-\end{align*}
+\end{split}\end{equation*}
 \end{proof}
@@
 Defining
-\begin{align*}
+\begin{equation*}\begin{split}
 \solptb^{(0)} & = \softpart^\alpha \solproto \\
@@
 & \;\;\vdots
-\end{align*}
+\end{split}\end{equation*}
 we get a sequence of functions that converges in $\singexp{\tau_\alpha}{\Lambda}(\Upsilon)$ to a solution $f_*$.
@@
 Hence, we have
-\begin{align*}
+\begin{equation*}\begin{split}
 I_a & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
 & = \int_{\mathcal{J}_{\zeta,\alpha}^\theta}e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta.
-\end{align*}
+\end{split}\end{equation*}
 Noticing that the right-hand side is a Laplace transform, we learn that
@@
 as $z \to \infty$. Plugging in the Taylor series for $\nu$, we get
-\begin{align*}
+\begin{equation*}
+\begin{split}
 e^{z \alpha} I_a & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
 & = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau.
-\end{align*}
+\end{split}
+\end{equation*}
 Applying the dominated convergence theorem on the right-hand side, we deduce that\footnote{Notice that the sum over $k$ is empty when $n = 0$.
@@
 = 1$.}
-\begin{align*}
+\begin{equation*}
+\begin{split}
 e^{z \alpha} I_a & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
 & = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
-\end{align*}
+\end{split}
+\end{equation*}
 
@@
 To see why, cut the sum off after $N$ terms, and observe that
-\begin{align*}
+\begin{equation*}
+\begin{split}
   \Bigg | \sum_{n= 0}^N(2n-1)!!
@@
 b_{2n}^a n|z|^{-n}.
-\end{align*}
+  \end{split}
+\end{equation*}
 The right-hand side goes to $0$ as $\Re(z)$ grows.
@@
 Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
-\begin{align*}
+\begin{equation*}
+\begin{split}
 \series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
 &= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
-\end{align*}
+\end{split}
+\end{equation*}
 We know from the definition of $\varepsilon$ that $\left|b_n^a\right| \varepsilon^n \lesssim 1$, thus we deduce that $\series{\iota}$ has a finite radius of convergence.
@@
 We can rewrite the Taylor series for $\nu$ as
-\begin{align*}
+\begin{equation*}\begin{split}
 \nu & = \sum_{n \ge 0} b_n^a [2(f - \alpha)]^{(n - 1)/2}\,df,
-\end{align*}
+\end{split}\end{equation*}
 taking the positive branch of the square root on $\mathcal{C}^+_a$ and the negative branch on $\mathcal{C}^-_a$.
 Plugging this into our expression for $\iota_a$ (in Lemma~\ref{lem:thimble_proj_formula-proof}), we learn that
-\begin{align*}
+\begin{equation*}\begin{split}
 \iota_a & = \left[ \sum_{m \ge 0} b_m^a [2(f - \alpha)]^{(m - 1)/2} \right]_{\operatorname{start} \mathcal{C}_a(\zeta)}^{\operatorname{end} \mathcal{C}_a(\zeta)} \\
@@
 & = \sum_{n \ge 0} 2^{n+1/2} b_{2n}^a \zeta_\alpha^{n - 1/2}
-\end{align*}
-In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_{\zeta,\alpha}^\theta$ and its sum is given by $\iota_a$.
+\end{split}\end{equation*}
+In particular, $\series{\iota}_a$ can be analytically continued along $\mathcal{J}_{\zeta,\alpha}^\theta$ and its sum is given by~$\iota_a$.
 \end{proof}
@@
 To get the thimble projection formula for $\phi_a$, take the $1/2$ fractional integral of both sides:
-\begin{align*}
+\begin{equation*}\begin{split}
 \fracderiv{-1/2}{\zeta}{\alpha} \phi_a & = \fracderiv{-1}{\zeta}{\alpha} \, \iota_a \\
@@
 & = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_a^\theta(\alpha)}\nu.
-\end{align*}
+\end{split}\end{equation*}
 The second term vanishes because $\mathcal{C}_a^\theta(\alpha)$ is a single point, leaving
@@
 We found in Section~\ref{sec:asympt-AL} that
-\begin{align*}
+\begin{equation*}\begin{split}
 \tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
 \tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
+\end{split}\end{equation*}
 Computing
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] & = \borel_\zeta \left[ e^{-z} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k-\frac{1}{2}} \right] \\
@@
 & = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
-\end{align*}
+\end{split}\end{equation*}
 we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
@@
 Recalling that $\mathcal{C}^\theta_j$ is a preimage of $\mathcal{J}^\theta_{\zeta, \mp 1}$, we get
-\begin{align*}
+\begin{equation*}\begin{split}
 K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
 & = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right],
-\end{align*}
+\end{split}\end{equation*}
 where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
@@
 We can now use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
-\begin{align*}
+\begin{equation*}\begin{split}
 \frac{U_{m-1}(\cos(\phi))}{U_{n-1}(\cos(\phi))} &= \frac{\sin(m\phi)}{\sin(\phi)}\frac{\sin(\phi)}{\sin(n \phi)}\\
@@
 & = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
-\end{align*}
+\end{split}\end{equation*}
 Initially, we only know that this equation holds in the disk $|\phi| < \tfrac{\pi}{2n}$.
@@
 
-Next, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
+Next, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{equation*}\begin{split}
 &{}_2F_1\left(\frac{1}{2} - \frac{m}{2n}, \frac{1}{2} + \frac{m}{2n}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
@@
 & =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(1 - \frac{m}{n},\;1 + \frac{m}{n};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
-\end{align*}
+\end{split}\end{equation*}
 away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
@@
 
-\begin{align*}
+\begin{equation*}\begin{split}
 &{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}-i\varepsilon\right) \\
@@
 &=\left(-\frac{\zeta_{1}}{2}\right)^{1/2}\,2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}\;.
-\end{align*}
+\end{split}\end{equation*}
 Multiplying both sides by $(-\zeta_1/2)^{-1/2}$ reveals a formula for the jump of $v_1$ across the branch cut. For any point $p$ on the branch cut,
@@
 We find that
-\begin{align*}
+\begin{equation*}\begin{split}
 &{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}+i\varepsilon\right)-{}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}-i\varepsilon\right) \\
@@
 &=\left(\frac{\zeta_{-1}}{2}\right)^{1/2}\,(-2)\cos\big(\tfrac{m}{n}\pi\big)\,v_1\;.
-\end{align*}
+\end{split}\end{equation*}
 Multiplying both sides by $(\zeta_{-1}/2)^{-1/2}$ gives the jump formula
@@
 In our example,
-\begin{align*}
+\begin{equation*}\begin{split}
 \laplace_{\zeta,1}^{\pi+\varepsilon} v_1 - \hphantom{{}_{-}}\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = \hphantom{-}2\cos\big(\tfrac{m}{n}\pi\big) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
 \laplace_{\zeta,-1}^{\varepsilon} v_{-1} - \laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = -2\cos\big(\tfrac{m}{n}\pi\big) \, e^z \, \laplace_{\zeta,1} v_{1}\;.
-\end{align*}
+\end{split}\end{equation*}
 so the stokes constants for the directions $\pi$ and $0$ are $2\cos\big(\tfrac{m}{n}\pi\big)$ and $-2\cos\big(\tfrac{m}{n}\pi\big)$, respectively.
@@
 given by
-\begin{align*}
+\begin{equation*}\begin{split}
 \series{W}_{\mu,1} & = 1 - \frac{\left(\tfrac{1}{2}-\mu\right)\left(\frac{1}{2}+\mu\right)}{2 \cdot 1!} z^{-1} + \frac{\left(\tfrac{1}{2}-\mu\right)_2\left(\frac{1}{2}+\mu\right)_2}{2^2 \cdot 2!} z^{-2} - \frac{\left(\tfrac{1}{2}-\mu\right)_3\left(\frac{1}{2}+\mu\right)_3}{2^3 \cdot 3!} z^{-3} + \ldots \\
 \series{W}_{\mu,-1} & = 1 + \frac{\left(\tfrac{1}{2}-\mu\right)\left(\frac{1}{2}+\mu\right)}{2 \cdot 1!} z^{-1} + \frac{\left(\tfrac{1}{2}-\mu\right)_2\left(\frac{1}{2}+\mu\right)_2}{2^2 \cdot 2!} z^{-2}+ \frac{\left(\tfrac{1}{2}-\mu\right)_3\left(\frac{1}{2}+\mu\right)_3}{2^3 \cdot 3!} z^{-3} + \ldots
-\end{align*}   
+\end{split}\end{equation*}   
 \item[]  \textbf{Frame of analytic solutions}
@@
 Equation~\eqref{eqn:mod-bessel} also has a basis of analytic solutions $\laplace^\theta_{\zeta, 1} v_1$ and $\laplace^\theta_{\zeta, -1} v_{-1}$, which are the Laplace transforms of the functions
-\begin{align*}
+\begin{equation*}\begin{split}
 v_1 & = -i\sqrt{2}\,\zeta_{1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_{1}\big)\\
 v_{-1} & = \hphantom{-i}\sqrt{2}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\mu, \tfrac{1}{2}+\mu; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)
-\end{align*}
+\end{split}\end{equation*}
 along the directions $\theta \neq \pi$ and $\theta \neq 0$, respectively.
@@
 Setting $u = \cosh(t/n)$ and recalling that
-\begin{align*}
+\begin{equation*}\begin{split}
 \cosh(n\tau) & = T_n(\cosh(\tau)) \\
 \sinh(m\tau) & = U_{m-1}(\cosh(\tau)) \sinh(\tau),
-\end{align*}
+\end{split}\end{equation*}
 we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as
-\begin{align}
+\begin{equation}\begin{split}
 \notag K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_\gamma \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
@@
 \label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt,
-\end{align}
+\end{split}\end{equation}
 using the path $\mathcal{C}^\theta_j$ described below.
@@
 where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. We then use identity~15.4.16 from \cite{dlmf} to write the integral explicitly in terms of $\zeta$:
-\begin{align*}
+\begin{equation*}\begin{split}
 \frac{\sinh(\mu t)}{\sinh(t)} & = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;-\sinh(t)^2\right) \\
 & = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;1 - \zeta^2\right).
-\end{align*}
+\end{split}\end{equation*}
 Like before, we can deduce by analytic continuation that this identity holds throughout the $t$ plane.
@@
 In the translated coordinate $w$ defined by $t = w + i\pi$, the integral becomes
-\begin{align*}
+\begin{equation*}\begin{split}
 K_0^{(1)}(z) & = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[z \cosh(w + i\pi)\right]\,(w + i\pi)\,dw \\
 & = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,w\,dw + \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,i\pi\,dw.
-\end{align*}
+\end{split}\end{equation*}
 The first integrand is odd with respect to $w = 0$, so it vanishes, leaving
-\begin{align}
+\begin{equation}\begin{split}
 K_0^{(1)}(z) & = \frac{1}{2} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,dw \notag \\
 & = \int_0^\infty \exp\left[-z \cosh(w)\right]\,dw. \label{int:k0_cosh}
-\end{align}
+\end{split}\end{equation}
 This is a special case of formula~10.32.9 from \cite{dlmf}. Rolling the $t$ plane up into a cylinder, parameterized by the coordinate $s = e^t$, we can express $K_0^{(1)}(z)$ as an exponential period:
@@
 In \cite{Reid} and the appendix of \cite{drazin-reid}, Drazin and Reid construct approximate solutions of the Orr--Sommerfield fluid equation using the generalized Airy functions
-\begin{align*}
+\begin{equation*}\begin{split}
 \mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\hphantom{{}_{\le 0}},\quad k \in \{1,2,3\} \\
@@
 \mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p}, & & p \in \Z_{\le 0},\quad k \in \{1,2,3\}
-\end{align*}
+\end{split}\end{equation*}
 which are defined by integrals along the contours $\mathscr{a}_k, \mathscr{b}_0, \mathscr{b}_k$ shown in Figure~\ref{fig:path-generalized-Airy}~\cite{drazin-reid}\cite[Section 9.13(ii)]{dlmf}.
@@
 on integrals. This is because
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_\mathcal{C} e^{-z(f + c)}\,\nu & = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
 & = e^{-cz} J(z).
-\end{align*}
+\end{split}\end{equation*}
 \item[] \textbf{Scaling-rotations}
@@
 on integrals. This is because
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_\mathcal{C} e^{-z(rf)}\,\nu & = \int_\mathcal{C} e^{-(rz)f}\,\nu \\
 & = J(rz).
-\end{align*}
+\end{split}\end{equation*}
 \end{itemize}
@@
 on integrals. This is because
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_{\mathsf{M}_{1/s} \mathcal{C}} e^{-z \mathsf{M}_s^* f}\,du & = \int_\mathcal{C} e^{-zf}\,\mathsf{M}_{1/s}^* du \\
@@
 & = s J(z).
-\end{align*}
+\end{split}\end{equation*}
 \end{itemize}
@@
 We first put $g$ in depressed form by scaling the leading coefficient to $1$ and translating the mean of the critical points to $0$.\footnote{The coefficients of the depressed form are related to the original coefficients as follows:
-\begin{align*}
+\begin{equation*}\begin{split}
 p & = \frac{a_1}{a_3} - \frac{1}{3} \left(\frac{a_2}{a_3}\right)^2 \\
 q & = \frac{a_0}{a_3} - \frac{1}{3} \left(\frac{a_1}{a_3}\right)\left(\frac{a_2}{a_3}\right) + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3.
-\end{align*}} We then also translate the mean of the critical values to $0$.
+\end{split}\end{equation*}} We then also translate the mean of the critical values to $0$.
 \begin{center}
@@
 We can confirm this result, and find the correct normalization, using the thimble projection formula:
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_{\mathcal{C}} e^{-z(u^3+q)}\,du & = (1 - e^{i\pi/3}) \int_{\mathcal{J}_{\zeta_q, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta_q^{-2/3}\,d\zeta_q \\
 & = e^{-zq}\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
-\end{align*}
+\end{split}\end{equation*}
 The factor of $e^{i\pi/3} - 1$ comes from the monodromy of $\zeta_q^{-2/3}$ around $\zeta_q = 0$.
@@
 We found in Section~\ref{sec:asympt-airy} that
-\begin{align*}
+\begin{equation*}\begin{split}
 \tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
 \tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
-\end{align*}
+\end{split}\end{equation*}
 Repeating the computation in Section~\ref{confirmation-borel-regularity}, we find that
@@
 Recalling that $\mathcal{C}^\theta_1$ is a preimage of $\mathcal{J}^\theta_{\zeta,1}$, we get
-\begin{align*}
+\begin{equation*}\begin{split}
 K(z) & = -i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
 & = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right],
-\end{align*}
+\end{split}\end{equation*}
 where $u_-$ and $u_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$, respectively.
@@
 Recognizing $4u^2 - 1$ as the Chebyshev polynomial $U_2(u)$, we can use identity~15.4.16 from \cite{dlmf} to write the integrand explicitly in terms of $\zeta$:
-\begin{align*}
+\begin{equation*}\begin{split}
 \frac{1}{4 \cos(\phi)^2 - 1} & = \frac{1}{U_2(\cos(\phi))} \\
@@
 & = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;1 - \zeta^2\right).
-\end{align*}
-Just as in Section~\ref{contour-argument-AL}, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{align*}
+\end{split}\end{equation*}
+Just as in Section~\ref{contour-argument-AL}, we simplify the integrand using identities 15.8.4 and 15.8.27\;--\;15.8.28 from \cite{dlmf}, which tell us that\begin{equation*}\begin{split}
 &{}_2F_1\left(\frac{1}{3},\;\frac{2}{3}; \frac{3}{2}; 1 - \zeta^2\right) \\[3mm]
@@
 & =\; \hphantom{+} \frac{3}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\frac{1}{2} - \frac{\zeta}{2}\right) + \frac{1}{2}\;{}_2F_1\left(\frac{2}{3},\;\frac{4}{3};\;\frac{3}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right)
-\end{align*}
+\end{split}\end{equation*}
 away from the line $\Re(\zeta) = 0$ and the rays $\mathcal{J}^0_{\zeta,1}$ and $\mathcal{J}^\pi_{\zeta,-1}$.
@@
 Using the variable $\eta$, we calculate:
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_{\mathcal{C}_1^\theta(\zeta)} du & = u \Big|_{\operatorname{start} \mathcal{C}^\theta_1(\zeta)}^{\operatorname{end} \mathcal{C}^\theta_1(\zeta)} \\
 & = u_+ - u_-.
-\end{align*}
+\end{split}\end{equation*}
 Like in Section~\ref{contour-argument-AL}, the functions $u_-$ and $u_+$ are functions on a neighborhood of $\mathcal{J}_{\zeta, 1}$ in the position domain.
@@
 Observing that $\eta_- = -\eta_+$, we can continue the calculation:
-\begin{align*}
+\begin{equation*}\begin{split}
 \int_{\mathcal{C}_1^\theta(\zeta)} du & = \cos\big(\tfrac{\pi}{3} + i\eta_+\big) - \cos\big(\tfrac{\pi}{3} + i\eta_-\big) \\
@@
 & = i\sqrt{3}\,\sinh(\eta_+).
-\end{align*}
+\end{split}\end{equation*}
 Identity 15.4.16 from \cite{dlmf} implies that
@@
 It follows, through identity~15.5.4 from \cite{dlmf}, that
-\begin{align*}
+\begin{equation*}\begin{split}
 \kappa_1 & = 2\,\frac{\partial}{\partial \zeta} \left[ \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right) \right] \\
 & = -\frac{1}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{1}{2}; \frac{1}{2} - \frac{\zeta}{2}\right),
-\end{align*}
+\end{split}\end{equation*}
 matching the conclusion of Section~\ref{contour-argument-airy}.
@@
 Physicists often use a different version of the Borel transform:
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
 z^{-n} & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
+\end{split}\end{equation*}
 This version avoids sending $1$ to the convolution unit $\delta$, at the cost of no longer mapping multiplication to convolution or inverting the formal Laplace transform.
@@
 For problems involving a small parameter $\hbar$ rather than a large parameter $z$, physicists also define
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
 \hbar^n & \mapsto \frac{\zeta^n}{n!}.
-\end{align*}
+\end{split}\end{equation*}
 From a combinatorial perspective, this is just the transformation that sends an ordinary generating function to the corresponding exponential generating function.
@@
 
-\begin{align*}
+\begin{equation*}\begin{split}
 \series{\Phi}_{\mathrm{Ai}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{-\tfrac{2}{3}x^{3/2}}\tilde{W}_1(x^{-3/2})\\
 \series{\Phi}_{\mathrm{Bi}}(x)&=\frac{1}{2\sqrt{\pi}}x^{-1/4}e^{\tfrac{2}{3}x^{3/2}}\tilde{W}_2(x^{-3/2})\,,
-\end{align*}  
+\end{split}\end{equation*}  
 where 
-\begin{align*}
+\begin{equation*}\begin{split}
 \tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
-\end{align*}
+\end{split}\end{equation*}
 By applying the two versions $\borel_{\textit{phys}}$ and $\borel$ of the Borel transform, we get
-\begin{align*}
+\begin{equation*}\begin{split}
 w_{1,2}(\zeta)&\defeq\borel_{\textit{phys}}(\tilde{W}_{1,2})(\zeta)\\
@@
 &={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;\mp\frac{3}{4}\zeta\right) 
-\end{align*}
+\end{split}\end{equation*}
 and
-\begin{align*}
+\begin{equation*}\begin{split}
 \borel(\tilde{W}_{1,2})(\zeta)&=\frac{1}{2\pi}\delta+\sum_{n=1}^{\infty} \frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\frac{\zeta^{n-1}}{(n-1)!}\\
@@
 &=\frac{1}{2\pi}\delta\mp\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\mp\frac{3}{4}\zeta\right)\,.
-\end{align*}
+\end{split}\end{equation*}
 Comparing the two solutions, we notice that up to the factor of $\delta$,
@@
 such that
-\begin{align*}
+\begin{equation*}\begin{split}
 \series{\Phi}_{\mathrm{Ai}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{-\tfrac{2}{3}y^{3/2}}\series{\Phi}_{+}\left(\tfrac{2}{3}y^{3/2}\right)\\
 \series{\Phi}_{\mathrm{Bi}}(y)&=\frac{1}{2\sqrt{\pi}}y^{-1/4}e^{\tfrac{2}{3}y^{3/2}}\series{\Phi}_{-}\left(\tfrac{2}{3}y^{3/2}\right)
-\end{align*} 
+\end{split}\end{equation*} 
 are formal solutions of the Airy equation. Notice that compared to Mari\~{n}o's formal solutions, Mitschi and Sauzin adopt a different change of coordinates $z=\frac{2}{3}y^{3/2}$.
@@
 Seeking solutions of the Borel-transformed equation, Mitschi and Sauzin write the Borel transform of $\series{\Phi}_{\pm}$ as a convolution product:
-\begin{align*}
+\begin{equation*}\begin{split}
 \hat{\phi}_+(\zeta):=\borel\series{\Phi}_+=\delta+\frac{d}{d\zeta}\hat{\chi}(\zeta)  \qquad \hat{\phi}_-(\zeta):=\borel\series{\Phi}_-=\delta-\frac{d}{d\zeta}\hat{\chi}(-\zeta)
-\end{align*}
+\end{split}\end{equation*}
  where $\hat{\chi}(\zeta)=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6} \ast_\zeta \zeta^{-5/6}$.
@@
 Notice that $\hat{\chi}(\zeta)$ is a hypergeometric function:
-\begin{align*}
+\begin{equation*}\begin{split}
 \hat{\chi}(\zeta)&=\frac{2^{1/6}}{\Gamma(1/6)\Gamma(5/6)}(2\zeta+\zeta^2)^{-1/6}\ast_\zeta \zeta^{-5/6}\\
@@
 &={}_2F_1\left(\frac{1}{6},\frac{5}{6};1;-\frac{\zeta}{2}\right)
-\end{align*}
+\end{split}\end{equation*}
 where in the last step we use the Euler formula for hypergeometric functions.\footnote{The Euler formula is \begin{equation}\label{Euler formula}
@@
 \end{equation}} By taking derivatives, we recover $\hat{\phi}_{\pm}(\zeta)$: 
-\begin{align*}
+\begin{equation*}\begin{split}
 \hat{\phi}_+(\zeta)&=\delta-\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)=\delta-\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;-\frac{\zeta}{2}\right)\\
 \hat{\phi}_-(\zeta)&=\delta+\frac{1}{2}\frac{5}{36}\,\, {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)=\delta+\frac{2}{3}\frac{5}{48} {}_2F_1\left(\frac{7}{6},\frac{11}{6};2;\frac{\zeta}{2}\right)
-\end{align*} 
+\end{split}\end{equation*} 
 and up to a multiplicative constant they match our computations for $\borel(\tilde{W}_{1,2})$ (see equation~\eqref{Borel-W12}).
@@
 In the coordinate $t=\frac{3}{2}yx^{-3/2}$ they find an explicit formula for $\psi_B(x,y)$ in terms of Gauss hypergeometric functions:
-\begin{align*}
+\begin{equation*}\begin{split}
 \psi_{+,B}(x,y)&=\frac{1}{x}\phi_+(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}s^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};s\big)\\
 \psi_{-,B}(x,y)&=\frac{1}{x}\phi_-(t)=\frac{\sqrt{3}}{2\sqrt{\pi}}\frac{1}{x}(1-s)^{-1/2}\, {}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};1-s\big)\,,
-\end{align*}
+\end{split}\end{equation*}
 where $s=t/2+1/2$. We found the same hypergeometric functions in the position domain while solving the Airy equation
@@
 To do this, first notice that if $\eta$ and $y$ are conjugate variables under Borel transform, meaning 
-\begin{align*}
+\begin{equation*}\begin{split}
 \sum_{n\geq 0}a_n\eta^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_n}{n!} y^{n} 
-\end{align*} 
+\end{split}\end{equation*} 
 then $t=\frac{3}{2}yx^{-3/2}$ is the conjugate variable of $q=\frac{2}{3}\eta x^{3/2}$ up to correction by a factor of $\frac{3}{2}x^{-3/2}$
-\begin{align*}
+\begin{equation*}\begin{split}
 \sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
-\end{align*}
+\end{split}\end{equation*}
 In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ satisfies
@@
 \begin{proof}
-\begin{align*}
+\begin{equation*}\begin{split}
 &\left[\big(\tfrac{d}{dx}\big)^2 - \eta^2 x \right] \psi(x, \eta) = 0\\
@@
 &\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
-\end{align*}
+\end{split}\end{equation*}
 \end{proof}
 Now, rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
-\begin{align*}
+\begin{equation*}\begin{split}
 &\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\\
@@
 &\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0.
-\end{align*}
+\end{split}\end{equation*}
 This shows that $\Phi(q)$ satisfies the transformed Airy equation \eqref{eqn:reg-mod-bessel}.
@@
 When $\rho$ is a non-integer greater than $-1$, we can do a nice trick in this space of germs: we can pass back and forth between differential and integral equations without worrying about boundary conditions.
-\begin{prop}\label{prop:shifting}
+\begin{Proposition}\label{prop:shifting}
 Consider a germ $\phi \in \zeta^\rho\,\mathcal{O}_{\zeta=0}$. When $\rho$ is a non-integer greater than~$-1$,
@@
 assuming that the coefficients $h_n, \ldots, h_{-m}$ are in $\mathcal{O}_{\zeta=0}$.
-\end{prop}
+\end{Proposition}
 \begin{proof}

### 2025-10-24 SIGMA/SIGMA_submission/borel_reg_submission.tex
Moved acknowledge section before references (as required) and thanks referees

@@
 \end{notation*}
-%
-\subsection{Acknowledgements}
-This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
-
-We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
-
-We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
 %
@@
 
-Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
+Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries}~we~get 
 \begin{equation*}
@@
 \end{proof}
-\newpage
-\bibliographystyle{utphys}
+
+\subsection*{Acknowledgements}
+This paper is a result of the ERC-SyG project, Recursive and Exact New Quantum Theory (ReNewQuantum) which received funding from the European Research Council (ERC) under the European Union's Horizon 2020 research and innovation programme under grant agreement No 810573.
+
+We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+
+We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
+We would like to thank the anonymous referees for many helpful suggestions.
+
+\bibliographystyle{sigma}
 %\bibliographystyle{plain}

### 2025-11-02 SIGMA/SIGMA_submission/borel_reg_submission.tex
Correct mistakes in conversion to SIGMA format

@@
 \usepackage{url}
-\usepackage[hmargin=1.5in]{geometry}
 \usepackage[square,numbers,sort,compress]{natbib}
@@
 
+% acrobat color magic, courtesy of Tex.SE user prettygully
+% http://tex.stackexchange.com/a/9266/6934
+\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
+
 % % theorem environments
@@
 % \newtheorem{notation}{Notation}
-\renewcommand{\PaperNumber}{103}
+\renewcommand{\PaperNumber}{***}
 
@@
 %\setcounter{tocdepth}{2}
-
-% === phase space laplace ===
 \include{figures/phase-space-laplace.tex}
@@
 By taking a geometric perspective on the Laplace and Borel transforms, we also clarify why ``Borel regular'' solutions are associated with special points on the Borel plane.
-
 The particular classes of problems we look at are level~$1$ ODEs and exponential period integrals over one-dimensional Lefschetz thimbles.
@@
 This operator will always have an irregular singularity at $z = \infty$.
-%
 We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions.
@@
 \begin{enumerate}
-\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-\frac{1}{2}} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble.
@@
 \'{E}calle's theory not only shed light on Borel summation, but also generalized it.
-\'{E}calle introduced generalized resummation methods that use ``well-behaved averages'' to handle infinite sequences of singularities along the summation axis~\cite{EcalleI,Écalle-dulac,menous-mould,menous_phdthesis}.
+\'{E}calle introduced generalized resummation methods that use ``well-behaved averages'' to handle infinite sequences of singularities along the summation axis~\cite{EcalleI,ecalle-dulac,menous-mould,menous_phdthesis}.
 %
@@
 &=a_0b_0\delta +\sum_{n=1}^\infty\sum_{j=0}^na_jb_{n-j}\frac{\zeta^{n-1}}{(n-1)!}\\
-&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}+\\
-&\quad +\sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
+&=a_0b_0\delta+a_0\sum_{n=1}^\infty b_{n}\frac{\zeta^{n-1}}{(n-1)!}+b_0\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!} \\
+&\qquad + \sum_{n=1}^\infty\sum_{j=1}^{n-1}a_jb_{n-j}\left[\frac{\zeta^{j-1}}{(j-1)!} \ast_\zeta \frac{\zeta^{n-j-1}}{(n-j-1)!}\right]\\
 &=\left(a_0\delta+\sum_{n=1}^\infty a_n\frac{\zeta^{n-1}}{(n-1)!}\right)\ast_\zeta\left(b_0\delta+\sum_{n=1}^\infty b_n\frac{\zeta^{n-1}}{(n-1)!}\right)\\
@@
 \begin{enumerate}
-\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-1/2} \C\llbracket z^{-1}\rrbracket$.
+\item\label{part-1-prf} The function $I_a$ has an asymptotic expansion $\series{I}_a \defeq \aexp^{-\theta} I_a$, which lies in the space $e^{-z \alpha} z^{-\frac{1}{2}} \C\llbracket z^{-1}\rrbracket$.
 Here, $\theta$ is the direction of the ray $\mathcal{J}^\theta_{\zeta, \alpha}$ that defines the thimble and $\alpha=f(a)$.
@@
 \subsubsection{Rewriting as a modified Bessel $\frac{m}{n}$ equation}
-We can distil the most interesting parts of the Airy-Lucas function by writing
+We can distill the most interesting parts of the Airy-Lucas function by writing
 \[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
@@
 we can rewrite formula~\eqref{integral:mod-bessel-rational-AL} as
-\begin{equation}\begin{split}
+\begin{flalign}
 \notag K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_\gamma \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
@@
 \label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt,
-\end{split}\end{equation}
+\end{flalign}
 using the path $\mathcal{C}^\theta_j$ described below.
@@
 The first integrand is odd with respect to $w = 0$, so it vanishes, leaving
-\begin{equation}\begin{split}
+\begin{flalign}
 K_0^{(1)}(z) & = \frac{1}{2} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,dw \notag \\
 & = \int_0^\infty \exp\left[-z \cosh(w)\right]\,dw. \label{int:k0_cosh}
-\end{split}\end{equation}
+\end{flalign}
 This is a special case of formula~10.32.9 from \cite{dlmf}. Rolling the $t$ plane up into a cylinder, parameterized by the coordinate $s = e^t$, we can express $K_0^{(1)}(z)$ as an exponential period:

### 2025-11-02 SIGMA/borel-regularity-SIGMA.tex
Correct mistakes in conversion to SIGMA format
Clarify section reference; add missing period

@@
 \newcommand{\aexp}{\mathrm{\ae}}
+
+% acrobat color magic, courtesy of Tex.SE user prettygully
+% http://tex.stackexchange.com/a/9266/6934
+\pdfpageattr{/Group <</S /Transparency /I true /CS /DeviceRGB>>}
 
@@
 
-Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries} we get 
+Using the properties of the Borel transform acting on trans-mononials (Section~\ref{sec:action_transseries}) we get
 \begin{align*}
 \series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
-&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
+&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}\,.
 \end{align*}

### 2025-11-02 SIGMA/SIGMA_submission/borel_reg_submission.tex
Clarify section reference; add missing period
Polish acknowledgements

@@
 
-Using the properties of the Borel transform acting on trans-mononials \ref{sec:action_transseries}~we~get 
+Using the properties of the Borel transform acting on trans-mononials (Section~\ref{sec:action_transseries}) we get
 \begin{equation*}
@@
 \series{\iota}_a & = \sqrt{2\pi} \sum_{n \ge 0} (2n - 1)!! \,b_{2n}^a\,\frac{\zeta_\alpha^{n+\tfrac{1}{2}}}{\Gamma(n+\tfrac{1}{2})} \\
-&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}
+&= \sqrt{2\pi} \sum_{n \ge 0} \frac{2^n}{\sqrt{\pi}} \,b_{2n}^a\,\zeta_\alpha^{n+\tfrac{1}{2}}\,.
 \end{split}
@@
 
-We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+We thank Fondation Math\'{e}matique Jacques Hadamard for supporting the visit of the second author at IH\'{E}S, under the program \textit{Junior Scientific Visibility}.
 
 We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
-We would like to thank the anonymous referees for many helpful suggestions.
+We thank the referees for their careful reading, thoughtful comments, and useful references.
 

### 2025-11-02 SIGMA/borel-regularity-SIGMA.tex
Polish acknowledgements

@@
 
-We thank Fondation Mathématique Jacques Hadamard for supporting the visit of the second author at IH\'ES, under the program \textit{Junior Scientific Visibility}.
+We thank Fondation Math\'{e}matique Jacques Hadamard for supporting the visit of the second author at IH\'{E}S, under the program \textit{Junior Scientific Visibility}.
 
 We thank Fr\'{e}d\'{e}ric Fauvet, Maxim Kontsevich, Andrew Neitzke, and David Sauzin for fruitful discussions and suggestions.
+We thank the referees for their careful reading, thoughtful comments, and useful references.
 %

### 2025-11-04 SIGMA/SIGMA_submission/borel_reg_submission.tex
Add second author's contact info
Add space at the end of equations before punctuation

@@
 % Address of Second Author
-\Address{$^{\rm b)}$~Address of Second Author, Country}
-\EmailD{\href{mailto:email@address}{email@address}} % E-mail address of Second Author
+\Address{$^{\rm b)}$~Studio Infinity, USA}
+\EmailD{\href{mailto:aaron.fenyes@fareycircles.ooo}
+{aaron.fenyes@fareycircles.ooo}} % E-mail address of Second Author
+\URLaddressD{\url{https://ooo.fareycircles.ooo}} %URL address of Second Author
 
@@
 You can often find a formal power series
-\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots, \]
+\[ \series{\Phi} = \frac{c_0}{z^\tau} + \frac{c_1}{z^{\tau+1}} + \frac{c_2}{z^{\tau+2}} + \frac{c_3}{z^{\tau+3}} + \ldots\,, \]
 with $\tau \in (0, 1]$, that looks or acts like a solution to a problem whose actual solutions are holomorphic functions of $z$.
@@
 \begin{equation}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0. \label{eqn:bessel_rescaled_ex}
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] \Phi= 0\,. \label{eqn:bessel_rescaled_ex}
 \end{equation}
@@
 More generally, we will consider equations of the form $\mathcal{P} \Phi = 0$ given by a differential operator of the form
-\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}), \]
+\[ \mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1})\,, \]
 where $P$ is a monic degree-$d$ polynomial, $Q$ is a degree-$(d-1)$ polynomial that is non-zero at every root of $P$, and $R(z^{-1})$ is holomorphic in some disk $|z| > A$ around $z = \infty$.
@@
 \begin{equation*}
-I = \int_{\mathcal{C}}e^{-zf}\,\nu,
+I = \int_{\mathcal{C}}e^{-zf}\,\nu\,,
 \end{equation*}
@@
 A one-dimensional {\em thimble integral} has the form
-\[ I_a = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu, \]
+\[ I_a = \int_{\mathcal{C}_a^\theta} e^{-zf}\,\nu\,, \]
 where $\nu$ is a holomorphic $1$-form on $X$, $a$ is a critical point of $f$, and $\mathcal{C}^\theta_a$ is the Lefschetz thimble that runs through $a$ in direction $\theta$ with a chosen orientation.
@@
 \begin{equation}\label{eqn:formula}
-    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+    \iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right)\,,
 \end{equation}
@@
 Near $a$, we can always find coordinates $t_1, \ldots, t_N$ on $X$ with
-\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2). \]
+\[ f^*\zeta = \alpha + e^{i \theta} (t_1^2 + \ldots + t_N^2)\,. \]
 When the ray $\mathcal{J}_{\zeta, \alpha}^\theta$ avoids the other critical values of $f$, each such coordinate system defines a Lefschetz thimble: the oriented real-analytic submanifold where $t_1, \ldots, t_N$ are real.
@@
 z \maps T^*_bB & \to \C \\
-\lambda\big|_b & \mapsto 1.
+\lambda\big|_b & \mapsto 1\,.
 \end{split}
@@
 z \maps \van_b^n / \van_b^{n+1} & \to \C \\
-\zeta_b + \van^{n+1} & \mapsto 1.
+\zeta_b + \van^{n+1} & \mapsto 1\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{laplace:int}
-\laplace_{\zeta, \alpha}^\theta \phi = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta,
+\laplace_{\zeta, \alpha}^\theta \phi = \int_{\mathcal{J}_{\zeta, \alpha}^\theta} e^{-z\zeta} \phi\,d\zeta\,,
 \end{equation}
@@
 be the subspace consisting of functions $f$ with $|f| \lesssim |\zeta|^\sigma e^{\Lambda|\zeta|}$ over $\Omega$, equipped with the norm
-\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|. \]       
+\[ \|f\|_{\sigma,\Lambda} := \sup_\Omega |\zeta|^{-\sigma} e^{-\Lambda|\zeta|}\,|f|\,. \]       
 \end{definition}
@@
     \label{change-chart}
-    e^{-z\alpha} \laplace_{\zeta_\alpha, 0} \varphi = \laplace_{\zeta, \alpha} \varphi.
+    e^{-z\alpha} \laplace_{\zeta_\alpha, 0} \varphi = \laplace_{\zeta, \alpha} \varphi\,.
 \end{equation}
@@
 & = e^{-z\alpha } \int_{\mathcal{J}_{\zeta_\alpha,0}} e^{-z\zeta_\alpha}\,\varphi\;d\zeta_\alpha \\
-& = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi.
+& = e^{-z\alpha } \laplace_{\zeta_\alpha, 0} \varphi\,.
 \end{split}\end{equation*}
@@
 Let $\varphi\in\singexp{\sigma}{\Lambda}(\Omega)$ with $\sigma>-1$ and for some $\Lambda>0$, then
-    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi. \]
+    \[ \laplace_{\xi, 0} \varphi = \mu\,\laplace_{\zeta, 0} \varphi\,. \]
 \end{lemma}
@@
 & \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
+& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|\,,
 \end{split}\end{equation*}
@@
 |\laplace_{\zeta_\alpha, 0}^\theta \phi| & \le \int_{\mathcal{J}_{\zeta_\alpha, 0}^{\arg(z)}} e^{-\Delta|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
-& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt.
+& = \int_0^\infty e^{-\Delta t} t^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,dt\,.
 \end{split}\end{equation*}
@@
 We can evaluate it by observing that it is a Laplace transform integral, with the roles of position and frequency played by $t$ and $\Delta$ respectively:
-\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}. \]
+\[ |\laplace_{\zeta_\alpha, 0}^\theta \phi| \le \Gamma(\sigma) \Delta^{-\sigma} \|\phi\|_{\sigma-1, \Lambda}\,. \]
 In terms of the metric on $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ defined above, this bound says that
-\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}, \]
+\[ \|\laplace_{\zeta_\alpha, 0}^\theta \phi\|_{-\sigma, \Lambda} \le \Gamma(\sigma) \|\phi\|_{\sigma-1, \Lambda}\,, \]
 which is what we wanted to show.
@@
 has a continuous left inverse
-\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon), \]
+\[ \left(\laplace_{\zeta_\alpha, 0}^\theta\right)^{-1} \maps \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda) \to \singexp{\sigma-1}{\Lambda'}(\Omega_\alpha^\varepsilon)\,, \]
 with a norm of at most
-\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}. \]
+\[ \frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)}\,. \]
 Here, $\Omega_\alpha^\varepsilon \subset \Omega_\alpha$ is the open sector created by cutting a sector of angle $\varepsilon$ off each edge of $\Omega_\alpha$.
@@
 The inverse Laplace transform is given by the formula
-\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz. \]
+\[ \big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi = \frac{1}{2 \pi i} \int_{\mathcal{C}} e^{z\zeta_\alpha} \Phi\,dz\,. \]
 When $\Phi$ is in $\dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, we have the bound
@@
 & \le \frac{1}{2 \pi} \int_{-\infty}^\infty e^{|\zeta_\alpha| \left(\Lambda' - \sin(\varepsilon/2)\,|t|\right)} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma} \|\Phi\|_{\sigma, \Lambda}\,dt \\
-& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt,
+& = e^{|\zeta_\alpha| \Lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{1}{2 \pi} \int_{-\infty}^\infty e^{-|\zeta_\alpha| \sin(\varepsilon/2)\,|t|} \big(\sin(\varepsilon/2)\,|t|\big)^{-\sigma}\,dt\,,
 \end{split}\end{equation*}
@@
 Recognizing the integral in the last line as a Laplace transform integral, with the roles of position and frequency played by $s$ and $|\zeta_\alpha|$ respectively, we have
-\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}, \]
+\[ \left|\big(\laplace_{\zeta_\alpha, 0}^\theta\big)^{-1} \Phi\right| \le e^{|\zeta_\alpha| \lambda'} \|\Phi\|_{\sigma, \Lambda}\,\frac{\Gamma(1-\sigma)}{\pi\,\sin(\varepsilon/2)} |\zeta_\alpha|^{\sigma-1}\,, \]
 which is what we wanted to show.
@@
 The Laplace transform $\laplace_{\zeta, 0}$ acts in an especially simple way on powers of the coordinate $\zeta$:
-\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}. \]
+\[ \laplace_{\zeta, 0}\left[\frac{\zeta^n}{n!}\right] = z^{-n-1}\,. \]
 Here, we are thinking of $z$ as the frequency coordinate on $T^*_{\zeta = 0}B$, as described in Section~\ref{transl-freq}.
 We can get a function on $T^*_{\zeta = \alpha}B$ instead by taking the Laplace transform with respect to the coordinate $\zeta_\alpha$ defined by $\zeta = \zeta_\alpha + \alpha$:
-\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}. \]
+\[ \laplace_{\zeta_\alpha, 0}\left[\frac{\zeta_\alpha^n}{n!}\right] = z^{-n-1}\,. \]
 On each cotangent space, we can define a formal inverse of the Laplace transform by turning negative powers of $z$ back into powers of the appropriate translation coordinate.
@@
 \borel_\zeta \maps z^{-1} \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\sum_{n \ge 0} a_n z^{-n-1} & \mapsto \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}.
+\sum_{n \ge 0} a_n z^{-n-1} & \mapsto \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}\,.
 \end{split}\end{equation*}
@@
 \begin{equation*}\begin{split}
-\borel_\zeta[z^{-\sigma-1}] \defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)}.
+\borel_\zeta[z^{-\sigma-1}] \defeq \frac{\zeta^{\sigma}}{\Gamma(\sigma+1)}\,.
 \end{split}\end{equation*}
@@
 On each ordinary monomial within a trans-monomial, $\borel_\zeta$ acts as the formal inverse of $\laplace_{\zeta,\alpha}$:
-\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha} z^{-n-1} \big]=e^{-z\alpha} z^{-n-1}. \]
+\[\laplace_{\zeta,\alpha}\borel_\zeta\big[e^{-z\alpha} z^{-n-1} \big]=e^{-z\alpha} z^{-n-1}\,. \]
 The action of $\borel_\zeta$ extends to all of $e^{-z\alpha} \C\llbracket z^{-1} \rrbracket$ by countable linearity.
@@
 \laplace_{\zeta_\alpha,0}\borel_\zeta\big[e^{-z\alpha} z^{-n-1}\big] & = z^{-n-1} \\
-\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}.
+\borel_{\zeta}\big[e^{-z\alpha}z^{-n-1}\big] & = \frac{\zeta_\alpha^n}{n!}\,.
 \end{split}\end{equation*}
@@
 We want to show that 
-\[\borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]=\zeta^n.\]
+\[\borel_{\zeta_\alpha}\Big[e^{z\alpha} \laplace_{\zeta,\alpha}\big[\zeta^n\big]\Big]=\zeta^n\,.\]
 Recall that $\borel_{\zeta_\alpha}$
@@
       &=\sum_{k=0}^n{n\choose k} \alpha^{n-k}\zeta_\alpha^k\\
-      &=\zeta^n.
+      &=\zeta^n\,.
   \end{split}\end{equation*}
@@
 \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] & = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} e^{-z[\zeta(a) + \zeta(a')]}\,\phi(a)\, \psi(a')\,d\zeta(a) \wedge d\zeta(a') \\
-& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right].
+& = \int_{\mathcal{N}_{\zeta, \alpha, \beta}} \left[ e^{-z\zeta(a)}\,\phi(a)\,d\zeta(a) \right] \wedge \left[ e^{z\zeta(a')}\,\psi(a')\,d\zeta(a') \right]\,.
 \end{split}\end{equation*}
 Thinking of $\mathcal{N}_{\zeta, \alpha, \beta}$ as the graph of $\zeta_\alpha(a) + \zeta_\beta(a')$ over the quadrant $\mathcal{J}_{\zeta, \alpha} \times \mathcal{J}_{\zeta, \beta}$, we can use Fubini's theorem to express the integral as the product
-\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right].
+\[ \laplace_{\zeta,\alpha+\beta}[{\phi}\ast_{\zeta, \alpha,\beta}{\psi}] = \left[ \int_{\mathcal{J}_{\zeta, \alpha}} e^{-z\zeta}\,\phi\,d\zeta \right] \left[ \int_{\mathcal{J}_{\zeta,\beta}} e^{-z\zeta}\,\psi\,d\zeta \right]\,.
 \]
@@
 Let $z$ be a coordinate on the cotangent fiber over $\zeta=0$, and $\series{\Phi},\series{\Psi}\in\C\llbracket z^{-1}\rrbracket$. The Borel transform $\borel_\zeta$ is an algebra homomorphism, namely
-\[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}.\]
+\[\borel_\zeta(\series{\Phi}\series{\Psi})=\borel_\zeta\series{\Phi} \ast_\zeta \borel_\zeta\series{\Psi}\,.\]
 \end{Proposition}
@@
 From the expression
-\[ \series{\phi} = a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}, \]
+\[ \series{\phi} = a_{-1} \delta + \sum_{n \ge 0} a_n \frac{\zeta^n}{n!}\,, \]
 we see that $\series{\phi}$ converges if and only if there is some $A > 0$ with $|a_n / n!| \lesssim A^n$ over all $n \ge 0$. The constant $A$ is the radius of convergence of $\series{\phi}$.
@@
 The subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the ordinary Taylor series exists can thus be seen as the intersection
-\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega), \]
+\[ \mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega)\,, \]
 where $\mathcal{O}_{\zeta = \alpha}$ is the algebra of germs of holomorphic functions at $\zeta$.
 More generally, for any $\rho \ge \sigma$, the subspace of $\singexp{\sigma}{\Lambda}(\Omega)$ where the $\rho$-shifted Taylor series exists can be seen as the intersection
-\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega). \]
+\[ \zeta^\rho\,\mathcal{O}_{\zeta = \alpha} \cap \singexp{\sigma}{\Lambda}(\Omega)\,. \]
 
@@
 Thus, once again, we can see the subspace of $\singexp{\sigma}{\Lambda}(\Upsilon)$ where the $\rho$-shifted Taylor series exists as the intersection
-\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon). \]
+\[ \zeta^\rho\,\mathcal{O}_{\zeta = 0} \cap \singexp{\sigma}{\Lambda}(\Upsilon)\,. \]
 \begin{lemma}\label{lem:shifted_holo_closed}
@@
 Write $\series{\varphi}$ out in the form
-\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots, \]
+\[ \series{\varphi} = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + a_2 \frac{\zeta^{\rho+2}}{\Gamma(\rho+3)} + a_3 \frac{\zeta^{\rho+3}}{\Gamma(\rho+4)} + \ldots\,, \]
 observing that
@@
 For each $n \in \Z_{\ge 0}$, define the tail sum $\varepsilon_n \in \singexp{\rho+n}{\Lambda}(\Upsilon)$ by the equation
-\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n. \]
+\[ \varphi = a_0 \frac{\zeta^\rho}{\Gamma(\rho+1)} + a_1 \frac{\zeta^{\rho+1}}{\Gamma(\rho+2)} + \ldots + a_{n-1} \frac{\zeta^{\rho+n-1}}{\Gamma(\rho+n)} + \varepsilon_n\,. \]
 Taking the Laplace transform of both sides, we learn that
-\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n, \]
+\[ \Phi = \frac{a_0}{z^{\rho+1}} + \frac{a_1}{z^{\rho+2}} + \ldots + \frac{a_{n-1}}{z^{\rho+n}} + E_n\,, \]
 where $E_n = \laplace_{\zeta, 0}^\theta \varepsilon_n$. To show that $\Phi$ is asymptotic to $\series{\Phi}$, we just need to prove that $|z^{\rho+n} E_n| \to 0$ as $|z| \to \infty$ along every ray.
@@
 \begin{equation*}\begin{split}
-\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0),
+\fracderiv{\lambda}{\zeta}{\alpha}\,\fracderiv{\mu}{\zeta}{\alpha} & = \fracderiv{\lambda+\mu}{\zeta}{\alpha} \qquad \lambda, \mu \in (-\infty, 0)\,,
 \end{split}\end{equation*}
@@
 For $\mu \in (0, 1)$ and integers $n \ge 0$, the {\em Riemann-Liouville fractional derivative} $\fracderiv{n+\mu}{\zeta}{0}$ is defined by
-\[ \fracderiv{n+\mu}{\zeta}{0} \defeq \big(\tfrac{\partial}{\partial \zeta}\big)^{n+1} \fracderiv{\mu-1}{\zeta}{0}. \]
+\[ \fracderiv{n+\mu}{\zeta}{0} \defeq \big(\tfrac{\partial}{\partial \zeta}\big)^{n+1} \fracderiv{\mu-1}{\zeta}{0}\,. \]
 \end{definition}
@@
 \begin{equation*}\begin{split}
-\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0).
+\fracderiv{\lambda}{\zeta}{0}\,\fracderiv{\mu}{\zeta}{0} & = \fracderiv{\lambda+\mu}{\zeta}{0} & \lambda \in \R \smallsetminus \{0, 1, 2, 3, \ldots\},\quad\mu \in (-\infty, 0)\,.
 \end{split}\end{equation*}
@@
 &=\laplace_{\zeta,0} \int_{\mathcal{S}_{\zeta,0} }\frac{\big(\zeta-\zeta(a)\big)^{-\tau-1}}{\Gamma(-\tau)} \phi(a)\,d\zeta(a)\\
-&=\laplace_{\zeta,0}\big[\fracderiv{\tau}{\zeta}{0}\phi\big],
+&=\laplace_{\zeta,0}\big[\fracderiv{\tau}{\zeta}{0}\phi\big]\,,
 \end{split}\end{equation*}
@@
     &=(-1)^n\int_0^\infty \partial_\zeta^n \big[e^{-z\zeta}\big]  \phi\, d\zeta\\
-    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big].
+    &=\laplace_{\zeta,0}\big[\partial_\zeta^n \phi\big]\,.
 \end{split}\end{equation*}
@@
 For any non-integer $\mu \in (0, \infty)$ and any integer $k \ge 0$,
-\[ \partial^\mu_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]. \]
+\[ \partial^\mu_{\zeta,0} \borel_\zeta \big[z^{-(k+1)}\big] =  \borel_\zeta \big[z^\mu z^{-(k+1)}\big]\,. \]
 \end{lemma}
@@
 To prove result~\ref{res:frac-int-borel}, first notice that for $\lambda \in \R_{< 0}$,
-\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}.\] 
+\[\fracderiv{\lambda}{\zeta}{0}\zeta^{k}=\zeta^{k-\lambda}\frac{k!}{\Gamma(k-\lambda+1)}\,.\] 
 Then, given a series $\series{\Phi} = \sum_{n\geq 0} a_n z^{-n}$, we compute
@@
 & = \sum_{n\geq 0} \frac{a_n}{n!}\,\fracderiv{\lambda}{\zeta}{0}\zeta^n \\
-& = \fracderiv{\lambda}{\zeta}{0}\series{\Phi}.
+& = \fracderiv{\lambda}{\zeta}{0}\series{\Phi}\,.
 \end{split}\end{equation*}
@@
 &=(-\zeta)^k\sum_{n=k+1}^\infty a_n \frac{\zeta^{n-1}}{(n-1)!}\\
-&=(-\zeta)^k\borel_\zeta \series{\Phi}.
+&=(-\zeta)^k\borel_\zeta \series{\Phi}\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{eqn:operator-P}
-\mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1}),
+\mathcal{P} = P\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z} Q\big(\tfrac{\partial}{\partial z}\big) + \frac{1}{z^2} R(z^{-1})\,,
 \end{equation}
@@
 By Theorem~\ref{translation} and the results of Section~\ref{sec:reg-decay}, the Laplace transform $\laplace^\theta_{\zeta, \alpha}$ is a left-invertible map
-\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet). \]
+\[ \singexpalg{\tau_\alpha}(\Omega_\alpha) \to e^{-\alpha z} \dualsingexp{-\tau_\alpha-1}(\widehat{\Omega}_\alpha^\bullet)\,. \]
 With $\Psi_\alpha = \laplace^\theta_{\zeta, \alpha} \psi_\alpha$, the desired result follows.
@@
 and the perturbation
-\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big). \]
+\[ \softpart^\alpha = \tfrac{1}{p} \circ \partial^{-2}_{\zeta, \alpha} \circ R\big(\partial^{-1}_{\zeta, \alpha}\big)\,. \]
 
@@
 \begin{equation}\label{eqn:formula-proof}
-\iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right),
+\iota_a = \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right)\,,
 \end{equation}
@@
 I_a & = \int_{\mathcal{C}_a^\theta} e^{-zf} \nu \\
-& = \int_{\mathcal{J}_{\zeta,\alpha}^\theta}e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta.
+& = \int_{\mathcal{J}_{\zeta,\alpha}^\theta}e^{-z\zeta} \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,d\zeta\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{thimble-difference}
-{\iota}_a = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}.
+{\iota}_a = \left[\frac{\nu}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,.
 \end{equation}
@@
 e^{z \alpha} I_a & \approx \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{m \ge 0} b_m^a \tau^m\,d\tau \\
-& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau.
+& = \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \sum_{n \ge 0} b_{2n}^a \tau^{2n}\,d\tau\,.
 \end{split}
@@
 e^{z \alpha} I_a & \approx \sum_{n \ge 0} b_{2n}^a \int_{-\varepsilon}^\varepsilon e^{-z\tau^2/2} \tau^{2n}\,d\tau \\
-& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right].
+& = \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a \left[ \sqrt{2\pi}\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big) - 2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \right]\,.
 \end{split}
@@
 In other words,
-\[ e^{z \alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big). \]
+\[ e^{z \alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\,b_{2n}^a\,z^{-(n+1/2)} \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)\,. \]
 To see why, cut the sum off after $N$ terms, and observe that
@@
 b_{2n}^a  2e^{-z\varepsilon^2/2} \sum_{\substack{k \in \mathbb{N}_+ \\ k \le n}} \frac{\varepsilon^{2k-1}}{(2k-1)!!} z^{-n+k-1} \Bigg | &\leq  2 e^{-\Re (z) \varepsilon^2/2} \sum_{n=0}^N(2n-1)!!
-b_{2n}^a n|z|^{-n}.
+b_{2n}^a n|z|^{-n}\,.
   \end{split}
@@
 The differences $1 - \operatorname{erf}\big(\varepsilon \sqrt{z/2}\big)$ shrink exponentially as $z$ grows \cite[inequality~5]{chiani-dardari-book}, allowing the simpler estimate
-\[ e^{z\alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}. \]
+\[ e^{z\alpha} I_a \sim \sqrt{2\pi} \sum_{n \ge 0} (2n-1)!!\, b_{2n}^a \,z^{-(n+1/2)}\,. \]
 Hence, defining the formal series $\series{I}_a$
@@
 \begin{equation*}\begin{split}
-\nu & = \sum_{n \ge 0} b_n^a [2(f - \alpha)]^{(n - 1)/2}\,df,
+\nu & = \sum_{n \ge 0} b_n^a [2(f - \alpha)]^{(n - 1)/2}\,df\,,
 \end{split}\end{equation*}
@@
 Proposition~\ref{prop:L-int-op} tells us that $\Phi_a = \laplace^\theta_{\zeta, \alpha} \phi_a$ for
-\[\phi_a \defeq \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_a. \]
+\[\phi_a \defeq \fracderiv{-1/2}{\zeta}{\alpha}\,\iota_a\,. \]
 To get the thimble projection formula for $\phi_a$, take the $1/2$ fractional integral of both sides:
@@
 & = \fracderiv{-1}{\zeta}{\alpha} \frac{\partial}{\partial \zeta} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right) \\
-& = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_a^\theta(\alpha)}\nu.
+& = \int_{\mathcal{C}_a^\theta(\zeta)}\nu - \int_{\mathcal{C}_a^\theta(\alpha)}\nu\,.
 \end{split}\end{equation*}
 The second term vanishes because $\mathcal{C}_a^\theta(\alpha)$ is a single point, leaving
-\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_a = \int_{\mathcal{C}_a^\theta(\zeta)}\nu. \]
+\[ \fracderiv{-1/2}{\zeta}{\alpha} \phi_a = \int_{\mathcal{C}_a^\theta(\zeta)}\nu\,. \]
 The $1/2$ fractional derivative is a left inverse of the $1/2$ fractional integral. Applying it to both sides, we find that
-\begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right).\end{equation}
+\begin{equation}\label{eqn:formula--1/2} \phi_a = \fracderiv{1/2}{\zeta}{\alpha} \left( \int_{\mathcal{C}_a^\theta(\zeta)}\nu \right)\,.\end{equation}
 \end{remark}
@@
 \begin{equation}\label{eqn:Pham}
-\iota_a \in (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta_{\zeta, \alpha}^{(-N/2 - k)} + \mathcal{O}_{\zeta = \alpha},
+\iota_a \in (-1)^{\frac{N(N-1)}{2}}  \sum_{k=0}^\infty c_k\, \delta_{\zeta, \alpha}^{(-N/2 - k)} + \mathcal{O}_{\zeta = \alpha}\,,
 \end{equation}
@@
 \begin{equation}\label{eqn:airy}
-\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0.
+\left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0\,.
 \end{equation}
 One solution is given by the Airy function,
-\[ \Ai(y) = \frac{1}{2\pi i} \int_\gamma \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt, \]
+\[ \Ai(y) = \frac{1}{2\pi i} \int_\gamma \exp\left(\tfrac{1}{3}t^3 - yt\right)\,dt\,, \]
 where $\gamma$ is a path that comes from $\infty$ at $-60^\circ$ and returns to $\infty$ at $60^\circ$.
@@
 \begin{equation}\label{eqn:airy-distillation}
-\Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du,
+\Ai(y) = y^{1/2}\;\frac{1}{\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[\tfrac{2}{3}y^{3/2} \left(4u^3 - 3u\right)\right]\,du\,,
 \end{equation}
@@
 \begin{equation}\label{integral:AL}
-\widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du,
+\widehat{\Ai}^{(j)}_{n, m-1}(y) = \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\} \frac{y^{m/2}}{\pi} \int_{\mathcal{C}^\theta_j} \exp\left[\tfrac{2}{n} y^{n/2}\,T_n(u)\right]\,U_{m-1}(u)\,du\,,
 \end{equation}
@@
 We can distill the most interesting parts of the Airy-Lucas function by writing
-\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big), \]
+\[ \widehat{\Ai}^{(j)}_{n, m-1}(y) = \frac{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}{n\pi} \left\{\begin{array}{ll}i & j \text{ odd} \\ 1 & j \text{ even}\end{array}\right\}\,y^{{m/2}}\,K^{(j)}_{m/n}\big(\tfrac{2}{n} y^{n/2}\big)\,, \]
 where
 \begin{equation}\label{integral:mod-bessel-rational-AL}
-K^{(j)}_{m/n}(z) = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}\int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du.
+K^{(j)}_{m/n}(z) = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)}\int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du\,.
 \end{equation}
@@
 \begin{equation}\label{eqn:mod-bessel-AL}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] \Phi = 0.
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{m}{n} \big)^2 + z^2\big]\right] \Phi = 0\,.
 \end{equation}
@@
 \begin{equation}\label{eqn:reg-mod-bessel-AL}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] \Phi = 0.
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big({\tfrac{m}{n}}\big)^2 z^{-2} \right] \Phi = 0\,.
 \end{equation}
@@
 From the work of Poincar\'{e} and the Ramis Index Theorem, as discussed at the beginning of Section~\ref{sec:new-summability-proof}, we know that equation~\eqref{eqn:reg-mod-bessel-AL} has a frame of formal $1$-Gevrey trans-monomial solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}\,, \]
 where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
@@
 The holomorphic analysis in Section~\ref{big-idea} will give us holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}\,, \]
 which seem analogous to the trans-monomials above.
@@
 \begin{equation}\label{int-eq:spatial-mod-bessel-AL}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0\,.
 \end{equation}
@@
 \begin{equation}\label{diff-eq:spatial-mod-bessel-AL}
-\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0,
+\left[ \big(\tfrac{\partial}{\partial \zeta}\big)^2 \circ \big[ \zeta^2 - 1 \big] - \tfrac{\partial}{\partial \zeta} \circ \zeta - \big(\tfrac{m}{n}\big)^2 \right] v = 0\,,
 \end{equation}
@@
 We can see the regular singularities by rewriting equation~\eqref{diff-eq:spatial-mod-bessel-AL} as follows:
-\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0. \]
+\[ \left[ (\zeta^2 - 1) \big(\tfrac{\partial}{\partial \zeta}\big)^2 + 3\zeta \tfrac{\partial}{\partial \zeta} + \big[ 1 - \big(\tfrac{m}{n}\big)^2 \big] \right] v = 0\,. \]
 
@@
 Observing that multiplication by $z^{-\tau_\alpha}$ gives an isometry $\dualsingexp{0}(\widehat{\Omega}_\alpha^\Lambda) \to \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\Lambda)$, we can do the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha, \]
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-\tau_\alpha} W_\alpha\,, \]
 where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \begin{equation}\label{diff-eq:spatial-mod-bessel-pos-AL}
-\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
+\left[\zeta_1(2 + \zeta_1) \big(\tfrac{\partial}{\partial \zeta_1}\big)^2 + 3(1 + \zeta_1) \tfrac{\partial}{\partial \zeta_1} + \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0\,.
 \end{equation}
@@
 \begin{equation}\label{diff-eq:hypergeom-pos-AL}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0.
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{m}{n}\big)^2\big]\right] v = 0\,.
 \end{equation}
@@
 Its Laplace transform can be written as
-\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
+\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1\,, \]
 where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
@@
 &=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
-\end{alignat*}
+\,\end{alignat*}
 where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
@@
 \tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
+\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}\,.
 \end{split}\end{equation*}
@@
 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{k!} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^{k-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big) \left(\frac{1}{2}\right)_k} \\
-& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!},
+& = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{2}-\tfrac{m}{n}\right)_k \left(\tfrac{1}{2}+\tfrac{m}{n}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!}\,,
 \end{split}\end{equation*}
 we see that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)\,. \]
 Looking back at Section~\ref{pos-root-AL}, we recognize this as a scalar multiple of $v_1$.
@@
 Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)\,. \]
 Looking back at Section~\ref{neg-root-AL}, we recognize this as a scalar multiple of $v_{-1}$.
@@
 K^{(j)}_{m/n}(z) & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z T_n(u)\right]\,U_{m-1}(u)\,du \\
-& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right],
+& = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \left[ \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_+)}{U_{n-1}(u_+)}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta}\,\frac{U_{m-1}(u_-)}{U_{n-1}(u_-)}\,d\zeta \right]\,,
 \end{split}\end{equation*}
@@
 & = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
-& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right).
+& = \frac{m}{n}\;{}_2F_1\left(\frac{1}{2} - \frac{m}{2n},\;\frac{1}{2} + \frac{m}{2n};\;\frac{3}{2};\;1 - \zeta^2\right)\,.
 \end{split}\end{equation*}
@@
 Returning to the projected thimble integral
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta, \]
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2\sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{U_{m-1}(u_+)}{U_{n-1}(u_+)} - \frac{U_{m-1}(u_-)}{U_{n-1}(u_-)} \right] d\zeta\,, \]
 we can see the integrand as the variation of the function
@@
 For odd $j$, we have
-\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta, \]
+\[ K^{(j)}_{m/n}(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta\,, \]
 and for even $j$, we have
-\[ K^{(j)}_{m/n}(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+\[ K^{(j)}_{m/n}(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \frac{m}{n},\;\frac{1}{2} + \frac{m}{n};\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta\,.
 \]
@@
 \hphantom{-}\frac{i}{2}\laplace_{\zeta, 1} v_1 & j \text{ odd} \\
--\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}.
+-\frac{3i}{2}\laplace_{\zeta, -1} v_{-1} & j \text{ even}\,.
 \end{cases} \]
@@
 This solution arises as the Laplace transform $\laplace^\theta_{\zeta, 1} v_1$ of the function
-\[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right), \]
+\[ v_1 = \left(-\frac{\zeta_1}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right)\,, \]
 on the position domain, with $\zeta=1+\zeta_1$ as before.
@@
 &=2\cos\big(\tfrac{m}{n}\pi\big)\, \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} \left(-\frac{\zeta_{1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right) \\
-&=\left(-\frac{\zeta_{1}}{2}\right)^{1/2}\,2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}\;.
+&=\left(-\frac{\zeta_{1}}{2}\right)^{1/2}\,2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{eqn:resurg-rel-1}
-v_1(p_-) - v_1(p_+) = 2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p),
+v_1(p_-) - v_1(p_+) = 2\cos\big(\tfrac{m}{n}\pi\big)\,v_{-1}(p)\,,
 \end{equation}
@@
 To compute the Stokes constants for the Airy--Lucas functions, we first repeat the calculation above for
-\[ v_{-1} = \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right). \]
+\[ v_{-1} = \left(\frac{\zeta_{-1}}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};\frac{\zeta_{-1}}{2}\right)\,. \]
 We find that
@@
 &=-2\cos\big(\tfrac{m}{n}\pi\big)\,\left(-\frac{\zeta_{1}}{2}\right)^{-1/2} \left(\frac{\zeta_{-1}}{2}\right)^{1/2}\, {}_2F_1\left(\frac{1}{2}-\frac{m}{n},\frac{1}{2}+\frac{m}{n};\frac{1}{2};-\frac{\zeta_1}{2}\right) \\
-&=\left(\frac{\zeta_{-1}}{2}\right)^{1/2}\,(-2)\cos\big(\tfrac{m}{n}\pi\big)\,v_1\;.
+&=\left(\frac{\zeta_{-1}}{2}\right)^{1/2}\,(-2)\cos\big(\tfrac{m}{n}\pi\big)\,v_1\,.
 \end{split}\end{equation*}
@@
 \laplace_{\zeta,1}^{\pi+\varepsilon} v_1 - \hphantom{{}_{-}}\laplace_{\zeta,1}^{\pi-\varepsilon} v_1 & = \hphantom{-}2\cos\big(\tfrac{m}{n}\pi\big) \, e^{-z}\, \laplace_{\zeta,-1}^{\pi} v_{-1} \\
-\laplace_{\zeta,-1}^{\varepsilon} v_{-1} - \laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = -2\cos\big(\tfrac{m}{n}\pi\big) \, e^z \, \laplace_{\zeta,1} v_{1}\;.
+\laplace_{\zeta,-1}^{\varepsilon} v_{-1} - \laplace_{\zeta,-1}^{-\varepsilon} v_{-1} & = -2\cos\big(\tfrac{m}{n}\pi\big) \, e^z \, \laplace_{\zeta,1} v_{1}\,.
 \end{split}\end{equation*}
@@
 \notag & = \frac{n}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,U_{m-1}(\cosh(t/n))\,\sinh(t/n)\,d(t/n) \\
-\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt,
+\label{integral:mod-bessel-lifted} & = \frac{1}{2 \sinh\big(\tfrac{m}{n}\,i\pi\big)} \int_{\mathcal{C}^\theta_j} \exp\left[z \cosh(t)\right]\,\sinh\big(\tfrac{m}{n}\,t\big)\,dt\,,
 \end{flalign}
@@
 This gives us the expression
-\[ K^{(j)}_\mu(z) = -\frac{1}{2\sinh(\mu i\pi)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta, \]
+\[ K^{(j)}_\mu(z) = -\frac{1}{2\sinh(\mu i\pi)} \int_{\mathcal{J}^\theta_{\zeta, \mp 1}} e^{-z\zeta} \left[ \frac{\sinh(\mu t_+)}{\sinh(t_+)} - \frac{\sinh(\mu t_-)}{\sinh(t_-)} \right] d\zeta\,, \]
 where $t_-$ and $t_+$ are the lifts to the incoming and outgoing branches of $\mathcal{C}^\theta_j$. We then use identity~15.4.16 from \cite{dlmf} to write the integral explicitly in terms of $\zeta$:
@@
 \frac{\sinh(\mu t)}{\sinh(t)} & = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;-\sinh(t)^2\right) \\
-& = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;1 - \zeta^2\right).
+& = \mu\;{}_2F_1\left(\frac{1}{2} - \frac{\mu}{2},\;\frac{1}{2} + \frac{\mu}{2};\;\frac{3}{2};\;1 - \zeta^2\right)\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{eq: K_j_mu at 1}
-  K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta,
+  K^{(j)}_\mu(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta\,,
 \end{equation}
@@
 \begin{equation}\label{eq: K_j_mu at -1}
- K^{(j)}_\mu(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta.
+ K^{(j)}_\mu(z) = \frac{3}{2} \int_{\mathcal{J}^\theta_{\zeta, -1}} e^{-z\zeta} \left(-\frac{1}{2}-\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{2} - \mu,\;\frac{1}{2} + \mu;\;\frac{1}{2};\;\frac{1}{2} + \frac{\zeta}{2}\right) d\zeta\,.
 \end{equation}
@@
 When $\mu$ goes to $0$, formula~\eqref{int:mod-bessel-gen} becomes
-\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_{\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt. \]
+\[ K_0^{(j)}(z) = \frac{1}{2\pi i} \int_{\mathcal{C}_j^\theta} \exp\left[z \cosh(t)\right]\,t\,dt\,. \]
 Let us compute $K^{(1)}_{0}(z)$ using the contour $\mathcal{C}_1^0$, which runs rightward along the line $\Im(t) = \pi$.
@@
 K_0^{(1)}(z) & = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[z \cosh(w + i\pi)\right]\,(w + i\pi)\,dw \\
-& = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,w\,dw + \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,i\pi\,dw.
+& = \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,w\,dw + \frac{1}{2\pi i} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,i\pi\,dw\,.
 \end{split}\end{equation*}
@@
 K_0^{(1)}(z) & = \frac{1}{2} \int_{-\infty}^\infty \exp\left[-z \cosh(w)\right]\,dw \notag \\
-& = \int_0^\infty \exp\left[-z \cosh(w)\right]\,dw. \label{int:k0_cosh}
+& = \int_0^\infty \exp\left[-z \cosh(w)\right]\,dw\,. \label{int:k0_cosh}
 \end{flalign}
 This is a special case of formula~10.32.9 from \cite{dlmf}. Rolling the $t$ plane up into a cylinder, parameterized by the coordinate $s = e^t$, we can express $K_0^{(1)}(z)$ as an exponential period:
-\[ K_0^{(1)}(z) = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}. \]
+\[ K_0^{(1)}(z) = \int_{\mathcal{J}^0_{s, 1}} \exp\left[-z\,\tfrac{1}{2}\left(s + \tfrac{1}{s}\right)\right]\,\frac{ds}{s}\,. \]
 
@@
 \begin{equation}\label{eqn:borel_bessel0}
-K_0^{(1)}(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta.
+K_0^{(1)}(z) = \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\big(\zeta^2 - 1\big)^{-1/2}\;d\zeta\,.
 \end{equation}
@@
 \begin{equation*}\begin{split}
-\mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\hphantom{{}_{\le 0}},\quad k \in \{1,2,3\} \\
+\mathrm{A}_k(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{a}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \C\,,\hphantom{{}_{\le 0}}\quad k \in \{1,2,3\} \\
 \mathrm{B}_0(y,p) & = \frac{1}{2\pi i}\int_{\mathscr{b}_0} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \Z \\
-\mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p}, & & p \in \Z_{\le 0},\quad k \in \{1,2,3\}
+\mathrm{B}_k(y,p) & = \hphantom{\frac{1}{2\pi i}} \int_{\mathscr{b}_k} \exp\big[yt-\tfrac{t^3}{3}\big]\,\frac{dt}{t^p} & & p \in \Z_{\le 0}\,,\quad k \in \{1,2,3\}
 \end{split}\end{equation*}
@@
 These functions satisfy the generalized Airy equation
-\[ \left[\big(\tfrac{\partial}{\partial y}\big)^3 - y\,\tfrac{\partial}{\partial y} + (p-1)\right] \Phi = 0. \]
+\[ \left[\big(\tfrac{\partial}{\partial y}\big)^3 - y\,\tfrac{\partial}{\partial y} + (p-1)\right] \Phi = 0\,. \]
 When $p = 0$, this equation reduces to
-\[ \tfrac{\partial}{\partial y} \circ \left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0, \]
+\[ \tfrac{\partial}{\partial y} \circ \left[\big(\tfrac{\partial}{\partial y}\big)^2 - y\right] \Phi = 0\,, \]
 which is equivalent to an inhomogeneous version of the classical Airy equation.
@@
 with
-\[ I_+(z,p) = \frac{1}{2\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[-z\left(4u^3 - 3u\right)\right]\,\frac{du}{u^p}. \]
+\[ I_+(z,p) = \frac{1}{2\pi i} \int_{\mathcal{C}^\theta_1} \exp\left[-z\left(4u^3 - 3u\right)\right]\,\frac{du}{u^p}\,. \]
 To find the right contour $\mathcal{C}_1^\theta$, we first note that the mapping $\zeta = 4u^3 - 3u$ is familiar, up to a sign, from Section~\ref{sec:airy}.
@@
 \begin{equation}\label{eqn:I}
-\left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + z^{-1} \left(\tfrac{\partial}{\partial z}\right)^2 - \tfrac{1}{9} z^{-2} \right] \tfrac{\partial}{\partial z} \Phi = 0.
+\left[\big[\big(\tfrac{\partial}{\partial z}\big)^2 - 1\big] + z^{-1} \left(\tfrac{\partial}{\partial z}\right)^2 - \tfrac{1}{9} z^{-2} \right] \tfrac{\partial}{\partial z} \Phi = 0\,.
 \end{equation}
@@
 \begin{equation}\label{int-eq:position-I}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] (-\zeta)\,v^{(1)} = 0.
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] (-\zeta)\,v^{(1)} = 0\,.
 \end{equation}
@@
 v^{(1)}_1 &=\;& -i\sqrt{2}\,(1 + \zeta_1)^{-1} &\,\zeta_1^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};-\tfrac{1}{2}\zeta_{1}\big) \\
-v^{(1)}_{-1} &=\;& \sqrt{2}\,(-1 + \zeta_{-1})^{-1} &\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};\tfrac{1}{2}\zeta_{-1}\big).
+v^{(1)}_{-1} &=\;& \sqrt{2}\,(-1 + \zeta_{-1})^{-1} &\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{6},\tfrac{5}{6};\tfrac{1}{2};\tfrac{1}{2}\zeta_{-1}\big)\,.
 \end{alignat*}
@@
 \int_\mathcal{C} e^{-z(f + c)}\,\nu & = e^{-cz} \int_\mathcal{C} e^{-zf}\,\nu \\
-& = e^{-cz} J(z).
+& = e^{-cz} J(z)\,.
 \end{split}\end{equation*}
@@
 & = \int_\mathcal{C} e^{-zf}\,s\,du \\
-& = s J(z).
+& = s J(z)\,.
 \end{split}\end{equation*}
@@
 p & = \frac{a_1}{a_3} - \frac{1}{3} \left(\frac{a_2}{a_3}\right)^2 \\
-q & = \frac{a_0}{a_3} - \frac{1}{3} \left(\frac{a_1}{a_3}\right)\left(\frac{a_2}{a_3}\right) + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3.
+q & = \frac{a_0}{a_3} - \frac{1}{3} \left(\frac{a_1}{a_3}\right)\left(\frac{a_2}{a_3}\right) + \frac{2}{27} \left(\frac{a_2}{a_3}\right)^3\,.
 \end{split}\end{equation*}} We then also translate the mean of the critical values to $0$.
@@
 Setting
-\[ r \defeq \frac{i}{2} \left(\frac{3}{p}\right)^{3/2}, \]
+\[ r \defeq \frac{i}{2} \left(\frac{3}{p}\right)^{3/2}\,, \]
 we get
@@
 \begin{equation}\label{eqn:degree-3-poly-1root}
-\left[\frac{\partial}{\partial z} + \frac{1}{3z} +q \right] \Phi = 0.
+\left[\frac{\partial}{\partial z} + \frac{1}{3z} +q \right] \Phi = 0\,.
 \end{equation}
 A function $\laplace_{\zeta,\alpha}^{\theta} v$ satisfies this equation if and only if $v$ satisfies the integral equation
-\[ \left[ -\zeta + \tfrac{1}{3} \partial^{-1}_{\zeta, \alpha} +q  \right] v = 0. \]
+\[ \left[ -\zeta + \tfrac{1}{3} \partial^{-1}_{\zeta, \alpha} +q  \right] v = 0\,. \]
 When $\alpha = q$, this equation has the solution
-\[ v_q = \zeta_q^{-2/3}, \]
+\[ v_q = \zeta_q^{-2/3}\,, \]
 whose Laplace transform
@@
 \int_{\mathcal{C}} e^{-z(u^3+q)}\,du & = (1 - e^{i\pi/3}) \int_{\mathcal{J}_{\zeta_q, 0}^\theta} e^{-z\zeta}\,\tfrac{1}{3}\zeta_q^{-2/3}\,d\zeta_q \\
-& = e^{-zq}\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}.
+& = e^{-zq}\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3})\,z^{-1/3}\,.
 \end{split}\end{equation*}
@@
 \begin{equation}\label{eqn:triangular_cantilever}
-    \left[\big[\big(\tfrac{\partial}{\partial z}\big)^4 - \omega^2\big] + \tfrac{2}{z}\big(\tfrac{\partial}{\partial z}\big)^3\right] \Phi = 0,
+    \left[\big[\big(\tfrac{\partial}{\partial z}\big)^4 - \omega^2\big] + \tfrac{2}{z}\big(\tfrac{\partial}{\partial z}\big)^3\right] \Phi = 0\,,
 \end{equation}
@@
 \begin{equation}\label{eqn:position_cantilever}
-\left[ \big[ \zeta^4 - \omega^2 \big] - 2\fracderiv{-1}{\zeta}{\alpha} \circ \zeta^3 \right] v = 0.
+\left[ \big[ \zeta^4 - \omega^2 \big] - 2\fracderiv{-1}{\zeta}{\alpha} \circ \zeta^3 \right] v = 0\,.
 \end{equation}
@@
 We hope to express $V_\alpha$ in the form
-\[ \int_{\mathcal{C}_a^\theta}e^{-z f} du, \]
+\[ \int_{\mathcal{C}_a^\theta}e^{-z f} du\,, \]
 where the function $f$ is a holomorphic function on $\C$, the function $u$ is the standard coordinate on $\C$, the point $a$ is a critical point of $f$ with $f(a) = \alpha$, and the path $\mathcal{C}_a^\theta$ is the component of $f^{-1}\big(\alpha + e^{i\theta}[0, \infty)\big)$ that runs through $a$.
@@
 \begin{equation}\label{eqn:cantilever-thimble-difference}
-\frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)},
+\frac{1}{\sqrt{\zeta^4-\omega^2}} = \left[\frac{du}{df}\right]_{\operatorname{start} \mathcal{C}_a^\theta(\zeta)}^{\operatorname{end} \mathcal{C}_a^\theta(\zeta)}\,,
 \end{equation}
@@
 \subsubsection{Rewriting as a modified Bessel equation}
-Starting from equation~\eqref{eqn:airy-distillation}, we can distil the most interesting part of the Airy function by writing
-\[ \Ai(y) = -\tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big), \]
+Starting from equation~\eqref{eqn:airy-distillation}, we can distill the most interesting part of the Airy function by writing
+\[ \Ai(y) = -\tfrac{1}{\pi\sqrt{3}}\,y^{1/2}\,K\big(\tfrac{2}{3} y^{3/2}\big)\,, \]
 where
@@
 \begin{equation}\label{eqn:mod-bessel-1/3}
-\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0.
+\left[z^2 \big(\tfrac{\partial}{\partial z}\big)^2 + z \tfrac{\partial}{\partial z} - \big[\big(\tfrac{1}{3}\big)^2 + z^2\big]\right] K = 0\,.
 \end{equation}
@@
 \begin{equation}\label{eqn:reg-mod-bessel}
-\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0.
+\left[ \big[ \big(\tfrac{\partial}{\partial z}\big)^2 - 1 \big] + z^{-1} \tfrac{\partial}{\partial z} - \big(\tfrac{1}{3}\big)^2 z^{-2} \right] K = 0\,.
 \end{equation}
@@
 We know from the formal theory of level~$1$ ODEs that equation~\eqref{eqn:reg-mod-bessel} has a frame of formal $1$-Gevrey trans-monomial solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,\series{W}_\alpha \mid \alpha^2 - 1 = 0 \}\,, \]
 where $\tau_\alpha = 1/2$ and $\series{W}_\alpha\in\C\llbracket z^{-1} \rrbracket_1$.
@@
 The analogous holomorphic solutions
-\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}, \]
+\[ \{ e^{-\alpha z} z^{-\tau_\alpha}\,W_\alpha \mid \alpha^2 - 1 = 0 \}\,, \]
 which we will describe in Section~\ref{big-idea-airy}, can be recovered from the formal solutions using Borel summation.
@@
 \begin{equation}\label{int-eq:spatial-mod-bessel}
-\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0.
+\left[ \big[ \zeta^2 - 1 \big] - \fracderiv{-1}{\zeta}{\alpha} \circ \zeta - \big(\tfrac{1}{3}\big)^2 \fracderiv{-2}{\zeta}{\alpha} \right] v = 0\,.
 \end{equation}
@@
 for $V_\alpha \defeq \laplace^\theta_{\zeta_\alpha, 0} v_\alpha$ and $\zeta = \alpha + \zeta_\alpha$, and the further decomposition
-\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-1/2} W_\alpha, \]
+\[ \laplace_{\zeta, \alpha} v_\alpha = e^{-\alpha z} z^{-1/2} W_\alpha\,, \]
 where $W_\alpha$ is a bounded holomorphic function on $\widehat{\Omega}_\alpha^\Lambda$.
@@
 \begin{equation}
-\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0,
+\left[\xi_1 (1 - \xi_1) \big(\tfrac{\partial}{\partial \xi_1}\big)^2 + 3(\tfrac{1}{2} - \xi_1) \tfrac{\partial}{\partial \xi_1} - \big[1 - \big(\tfrac{1}{3}\big)^2\big]\right] v = 0\,,
 \end{equation}
@@
 for all $\Lambda > 0$. Its Laplace transform can be written as
-\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1, \]
+\[ \laplace^\theta_{\zeta, 1} v_1 = e^{-z} z^{-1/2}\,W_1\,, \]
 where $W_1$ is a holomorphic function on the slit plane $z \notin (-\infty, 0]$ which is bounded outside any constant-radius neighborhood of the ray $z \in (-\infty, 0]$.
@@
 for all $\Lambda > 0$. Its Laplace transform can be written as
-\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
+\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}\,, \]
 where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.
@@
 \tilde{W}_1 & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(-\frac{1}{2}\right)^k z^{-k} \\
-\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}.
+\tilde{W}_{-1} & = \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{k!} \left(\frac{1}{2}\right)^k z^{-k}\,.
 \end{split}\end{equation*}
 Repeating the computation in Section~\ref{confirmation-borel-regularity}, we find that
-\[ \borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!}, \]
+\[ \borel_\zeta \big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big] = \frac{\zeta_1^{-\frac{1}{2}}}{\Gamma\big(\frac{1}{2}\big)} \sum_{k = 0}^{\infty} \frac{\left(\tfrac{1}{6}\right)_k \left(\tfrac{5}{6}\right)_k}{\left(\frac{1}{2}\right)_k} \left(-\frac{1}{2}\right)^k \frac{\zeta_1^k}{k!}\,, \]
 making it apparent that $\borel\big[ e^{-z} z^{-1/2}\,\tilde{W}_1 \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big). \]
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_1^{-1/2}\,{}_2F_1\big(\tfrac{1}{6}, \tfrac{5}{6}; \tfrac{1}{2}; -\tfrac{1}{2}\zeta_1\big)\,. \]
 Looking back at Section~\ref{pos-root}, we recognize this as a scalar multiple of $v_1$.
@@
 Through a similar calculation, we see that $\borel\big[ e^z z^{-1/2}\,\tilde{W}_{-1} \big]$ sums to
-\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big). \]
+\[ \tfrac{1}{\Gamma(1/2)}\,\zeta_{-1}^{-1/2}\,{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)\,. \]
 Looking back at Section~\ref{neg-root}, we recognize this as a scalar multiple of $v_{-1}$.
@@
 K(z) & = -i\sqrt{3} \int_{\mathcal{C}^\theta_1} \exp\left[z \left(4u^3 - 3u\right)\right]\,du \\
-& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right],
+& = \frac{i}{\sqrt{3}} \left[ \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_+^2 - 1}\,d\zeta - \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\,\frac{1}{4u_-^2 - 1}\,d\zeta \right]\,,
 \end{split}\end{equation*}
@@
 & = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;\sin(n \phi)^2\right) \\
-& = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;1 - \zeta^2\right).
+& = \frac{1}{3}\;{}_2F_1\left(\frac{1}{3},\;\frac{2}{3};\;\frac{3}{2};\;1 - \zeta^2\right)\,.
 \end{split}\end{equation*}
@@
 In the projected thimble integral
-\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta, \]
+\[ K(z) = \frac{i}{\sqrt{3}} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta}\left[\frac{1}{4u_+^2 - 1} - \frac{1}{4u_-^2 - 1}\right]\,d\zeta\,, \]
 we can now see the integrand as the variation of the function
@@
 We can write the jump explicitly using identity~15.2.3 from \cite{dlmf}:
-\[ K(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{6},\;\frac{5}{6};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta.
+\[ K(z) = -\frac{1}{2} \int_{\mathcal{J}^\theta_{\zeta, 1}} e^{-z\zeta} \left(-\frac{1}{2}+\frac{\zeta}{2}\right)^{-1/2} {}_2F_1\left(\frac{1}{6},\;\frac{5}{6};\;\frac{1}{2};\;\frac{1}{2} - \frac{\zeta}{2}\right) d\zeta\,.
 \]
 Comparing this expression with the expression for $V_1$ in Section~\ref{pos-root}, we see that
-\[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1. \]
+\[ K(z) = \tfrac{i}{2}\laplace_{\zeta, 1} v_1\,. \]
 %
@@
 The lemma tells us that $K$ is the Laplace transform of
-\[ \kappa_1 = -i\sqrt{3}\,\frac{\partial}{\partial \zeta}\left(\int_{\mathcal{C}_1^\theta(\zeta)} du\right). \]
+\[ \kappa_1 = -i\sqrt{3}\,\frac{\partial}{\partial \zeta}\left(\int_{\mathcal{C}_1^\theta(\zeta)} du\right)\,. \]
 Based on the variable $\phi$ from Section~\ref{contour-argument-airy}, we introduce a new variable $\eta$ defined by $\phi = \tfrac{\pi}{3} + i\eta$, with $u = \cos\big(\tfrac{\pi}{3} + i\eta\big)$ and $\zeta = \cos\big(\pi + 3i\eta\big)$.
@@
 \int_{\mathcal{C}_1^\theta(\zeta)} du & = u \Big|_{\operatorname{start} \mathcal{C}^\theta_1(\zeta)}^{\operatorname{end} \mathcal{C}^\theta_1(\zeta)} \\
-& = u_+ - u_-.
+& = u_+ - u_-\,.
 \end{split}\end{equation*}
@@
 & = -2 \sin\big(\tfrac{\pi}{3}\big) \sin(-i\eta_+) \\
-& = i\sqrt{3}\,\sinh(\eta_+).
+& = i\sqrt{3}\,\sinh(\eta_+)\,.
 \end{split}\end{equation*}
 Identity 15.4.16 from \cite{dlmf} implies that
-\[ \sinh(\eta_+) = \frac{2}{3} \sinh\big(\tfrac{3}{2}\eta_+\big)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right). \]
+\[ \sinh(\eta_+) = \frac{2}{3} \sinh\big(\tfrac{3}{2}\eta_+\big)\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; -\sinh\big(\tfrac{3}{2}\eta_+\big)^2\right)\,. \]
 Noticing that $\tfrac{1}{2}(1 - \zeta) = -\sinh\big(\tfrac{3}{2}\eta_+\big)^2$, we conclude that
-\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right), \]
+\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,, \]
 It follows, through identity~15.5.4 from \cite{dlmf}, that
@@
 \kappa_1 & = 2\,\frac{\partial}{\partial \zeta} \left[ \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right) \right] \\
-& = -\frac{1}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{1}{2}; \frac{1}{2} - \frac{\zeta}{2}\right),
+& = -\frac{1}{2} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{-1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{1}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,,
 \end{split}\end{equation*}
@@
 \borel_{\textit{phys}} \maps \C \llbracket z^{-1} \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-z^{-n} & \mapsto \frac{\zeta^n}{n!}.
+z^{-n} & \mapsto \frac{\zeta^n}{n!}\,.
 \end{split}\end{equation*}
@@
 \borel_{\textit{phys}} \maps \C \llbracket \hbar \rrbracket & \to \C \llbracket \zeta \rrbracket \\
-\hbar^n & \mapsto \frac{\zeta^n}{n!}.
+\hbar^n & \mapsto \frac{\zeta^n}{n!}\,.
 \end{split}\end{equation*}
@@
 \begin{equation*}\begin{split}
-\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n.
+\tilde{W}_{1,2}(\hbar)=\sum_{n=0}^{\infty}\frac{1}{2\pi}\left(\mp\frac{3}{4}\right)^{n}\frac{\Gamma(n+\frac{5}{6})\Gamma(n+\frac{1}{6})}{n!}\hbar^n\,.
 \end{split}\end{equation*}
@@
 \begin{equation}
-\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\series{\Phi}=\borel\series{\Phi}.
+\frac{d}{d\zeta}\circ\borel_{\textit{phys}}\series{\Phi}=\borel\series{\Phi}\,.
 \end{equation}
@@
 where in the last step we use the Euler formula for hypergeometric functions.\footnote{The Euler formula is \begin{equation}\label{Euler formula}
-{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt.
+{}_{2}F_1\left(a,b;c;x\right)=\frac{\Gamma(c)}{\Gamma(b)\Gamma(c-b)}\int_0^1 t^{b-1}(1-t)^{c-b-1}(1-xt)^{-a}dt\,.
 \end{equation}} By taking derivatives, we recover $\hat{\phi}_{\pm}(\zeta)$: 
@@
 \begin{equation*}\begin{split}
-\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}.
+\sum_{n\geq 0}a_nq^{-n-1}=\sum_{n\geq 0}a_nx^{-3/2(n+1)}\left(\frac{2}{3}\eta\right)^{-n-1}  \overset{\borel}{\longrightarrow} \sum_{n\geq 0}\frac{a_nx^{-3/2(n+1)}}{n!}\left(\frac{3}{2}\right)^{n+1}  y^{n}=\frac{3}{2}x^{-3/2}\sum_{n\geq 0}\frac{a_n}{n!} t^{n}\,.
 \end{split}\end{equation*}
@@
 &\left[\big(\tfrac{d}{dq}\big)^2+\tfrac{3}{2}\eta^{-1} x^{-3/2}\tfrac{d}{dq}-\tfrac{1}{4}\eta^{-2}x^{-3}-1\right]\Phi=0\\
-&\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0.
+&\left[\big(\tfrac{d}{dq}\big)^2+q^{-1}\tfrac{d}{dq}-\tfrac{1}{9}q^{-2}-1\right]\Phi=0\,.
 \end{split}\end{equation*}
@@
 \begin{equation}
-\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')\;dx'\right),
+\psi(x,\eta) = \exp\left(\int_{x_0}^xS(\eta,x')\;dx'\right)\,,
 \end{equation}
 with $S(\eta,x)=\sum_{k\geq -1} S_k(x)\,\eta^{-k}$. For the Airy-type Schr\"odinger equation, we have $S_{-1}^2 = x$, so up to a choice of sign for the square root,
-\[ q = \frac{2}{3}\eta x^{3/2}=\eta\int_0^x (x')^{1/2}\;dx' = \eta\int_{0}^x S_{-1}(x')\;dx'. \]
+\[ q = \frac{2}{3}\eta x^{3/2}=\eta\int_0^x (x')^{1/2}\;dx' = \eta\int_{0}^x S_{-1}(x')\;dx'\,. \]
 We expect that the change of coordinates $q=\eta\int_0^{x}S_{-1}(x')\;dx'$ would explain the analogies between the Borel transform of the WKB solution of a Schr\"{o}dinger equation and the Borel transform of the associated ODE.
@@
 Consider a germ $\phi \in \zeta^\rho\,\mathcal{O}_{\zeta=0}$. When $\rho$ is a non-integer greater than~$-1$,
-\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \phi = 0, \]
+\[ \left[ \sum_{k = 0}^n \big(\tfrac{\partial}{\partial \zeta}\big)^k \circ h_k + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \phi = 0\,, \]
 if and only if
-\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi = 0, \]
+\[ \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k + \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi = 0\,, \]
 assuming that the coefficients $h_n, \ldots, h_{-m}$ are in $\mathcal{O}_{\zeta=0}$.
@@
 \begin{equation}\label{eqn:diff-int-split}
-\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi.
+\tfrac{\partial}{\partial \zeta} \left[ \sum_{k = 1}^n \big(\tfrac{\partial}{\partial \zeta}\big)^{k-1} \circ h_k \right] \psi = -\left[ h_0 + \sum_{k = 1}^m \fracderiv{-k}{\zeta}{0} \circ h_{-k} \right] \psi\,.
 \end{equation}
@@
 Integrating both sides of equation~\eqref{eqn:diff-int-split}, we get
-\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;f = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi. \]
+\[ \fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}\;f = -\left[ \fracderiv{-1}{\zeta}{0} \circ h_0 + \sum_{k = 1}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi\,. \]
 Since $\fracderiv{-1}{\zeta}{0}\;\tfrac{\partial}{\partial \zeta}$ acts as the identity on functions that vanish at $\zeta = 0$, this simplifies to
-\[ f = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi, \]
+\[ f = -\left[ \sum_{k = 0}^m \fracderiv{-k-1}{\zeta}{0} \circ h_{-k} \right] \phi\,, \]
 which rearranges to the second equation in the statement.

### 2025-11-04 SIGMA/SIGMA_submission/borel_reg_submission.tex
Finalize third-round revisions

@@
 v_{-1} &=\;& (1-\xi_1)^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; 1-\xi_1\big) \\[1mm]
-&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big),
-\,\end{alignat*}
+&=\;& \sqrt{2}\,\zeta_{-1}^{-1/2} &\;{}_2F_1\big(\tfrac{1}{2}-\tfrac{m}{n}, \tfrac{1}{2}+\tfrac{m}{n}; \tfrac{1}{2}; \tfrac{1}{2}\zeta_{-1}\big)\,,
+\end{alignat*}
 where $\zeta_{-1}$ is the coordinate with $\zeta = -1 + \zeta_{-1}$.
@@
 for all $\Lambda > 0$. It has a well-defined Laplace transform along any ray from $\zeta = -1$ except the one going directly right, and its Laplace transform can be written as
-\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}, \]
+\[ \laplace^\theta_{\zeta, -1} v_1 = e^z z^{-1/2}\,W_{-1}\,, \]
 where $W_{-1}$ is a holomorphic function on the slit plane $z \notin [0, \infty)$ which is bounded outside any constant-radius neighborhood of the ray $z \in [0, \infty)$.
@@
 More generally, for any complex value of $p$, we can put $\mathcal{C}_1^\theta$ on the universal cover $\widetilde{\C^\times}$.
-%
 We will now show, in the case $p = 1$, that equation~\eqref{eqn:I} has a frame of Borel regular solutions---as long as the constant solution $\mathrm{B}_0(z, 1)$ counts as Borel regular.
@@
 Rearranging the relationship above between $I(z)$ and the modified Bessel function $K_{1/3}(z)$, we get the formula
-\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qa_3z} K_{1/3}\left(\frac{a_3 z}{r}\right) \]
+\[ I(z) = \frac{\sqrt{3}}{irp} e^{-qa_3z} K_{1/3}\left(\frac{a_3 z}{r}\right)\,. \]
 Setting $q=0$, and using the Taylor expansion of $K_{1/3}(z)$ around $z = 0$, given by equations 10.25.2 and 10.27.4 of \cite{dlmf}, we can see that $I(z)$ converges pointwise to $\tfrac{1}{i\sqrt{3}}\,e^{i\pi/3}\,\Gamma\big(\tfrac{1}{3}\big)\,z^{-1/3}$ as $p$ goes to zero with $a_3$ held constant.
@@
 Observing that
-\[ \tfrac{\partial}{\partial \zeta} \sqrt{\zeta^4 - \omega^2} = \frac{2\zeta^3}{\sqrt{\zeta^4 - \omega^2}}, \]
+\[ \tfrac{\partial}{\partial \zeta} \sqrt{\zeta^4 - \omega^2} = \frac{2\zeta^3}{\sqrt{\zeta^4 - \omega^2}}\,, \]
 we learn that
@@
 Noticing that $\tfrac{1}{2}(1 - \zeta) = -\sinh\big(\tfrac{3}{2}\eta_+\big)^2$, we conclude that
-\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,, \]
+\[ \int_{\mathcal{C}_1^\theta(\zeta)} du = \frac{2i}{\sqrt{3}} \left(-\frac{1}{2} + \frac{\zeta}{2}\right)^{1/2}\;{}_2 F_1\left(\frac{1}{6}, \frac{5}{6}; \frac{3}{2}; \frac{1}{2} - \frac{\zeta}{2}\right)\,.
+\]
 It follows, through identity~15.5.4 from \cite{dlmf}, that
@@
 \end{split}\end{equation*}
-In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}, then $\Phi(q)$ satisfies
+In addition, $\psi_{B,\pm}(x,y)=\frac{1}{x}\phi_{\pm}(t)$, therefore we expect that $\psi(x,\eta)=x^{1/2}\Phi(q)$. Assume that $\psi(x,y)$ is a solution of \eqref{WKB_Airy}. Then $\Phi(q)$ satisfies
 \begin{equation}
 \label{eq_Phi}
-\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0
-\end{equation}
-
-\begin{proof}
+\left[\left(\frac{d}{dx}\right)^2+x^{-1}\frac{d}{dx}-\frac{1}{4}x^{-2} - \eta^2 x \right] \Phi(q) = 0\,,
+\end{equation}
+because
 \begin{equation*}\begin{split}
@@
 &\left[x^{1/2}\big(\tfrac{d}{dx}\big)^2+x^{-1/2}\tfrac{d}{dx}-\tfrac{1}{4}x^{-3/2}-\eta^2x^{3/2}\right]\Phi=0\\
-&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0
-\end{split}\end{equation*}
-\end{proof}
+&\left[\big(\tfrac{d}{dx}\big)^2+x^{-1}\tfrac{d}{dx}-\tfrac{1}{4}x^{-2}-\eta^2x\right]\Phi=0\,.
+\end{split}\end{equation*}
+%
 Now, rewrite \eqref{eq_Phi} in the coordinates $q=\frac{2}{3}\eta x^{3/2}$: 
